### 2014-11-28 Optimization - Journal of Climate/template.tex
Creation of the document structure

%% Version 4.3.2, 25 August 2014
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template.tex --  LaTeX-based template for submissions to the 
% American Meteorological Society
%
% Template developed by Amy Hendrickson, 2013, TeXnology Inc., 
% amyh@texnology.com, http://www.texnology.com
% following earlier work by Brian Papa, American Meteorological Society
%
% Email questions to latex@ametsoc.org.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PREAMBLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Start with one of the following:
% DOUBLE-SPACED VERSION FOR SUBMISSION TO THE AMS
\documentclass{ametsoc}

% TWO-COLUMN JOURNAL PAGE LAYOUT---FOR AUTHOR USE ONLY
% \documentclass[twocol]{ametsoc}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% To be entered only if twocol option is used

\journal{jcli}

%  Please choose a journal abbreviation to use above from the following list:
% 
%   jamc     (Journal of Applied Meteorology and Climatology)
%   jtech     (Journal of Atmospheric and Oceanic Technology)
%   jhm      (Journal of Hydrometeorology)
%   jpo     (Journal of Physical Oceanography)
%   jas      (Journal of Atmospheric Sciences)	
%   jcli      (Journal of Climate)
%   mwr      (Monthly Weather Review)
%   wcas      (Weather, Climate, and Society)
%   waf       (Weather and Forecasting)
%   bams (Bulletin of the American Meteorological Society)
%   ei    (Earth Interactions)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Citations should be of the form ``author year''  not ``author, year''
\bibpunct{(}{)}{;}{a}{}{,}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% To be entered by author:

%% May use \\ to break lines in title:

\title{Global Optimization of the Analogue Method by Means of Genetic Algorithms}

%%% Enter authors' names, as you see in this example:
%%% Use \correspondingauthor{} and \thanks{Current Affiliation:...}
%%% immediately following the appropriate author.
%%%
%%% Note that the \correspondingauthor{} command is NECESSARY.
%%% The \thanks{} commands are OPTIONAL.

    %\authors{Author One\correspondingauthor{Author One, 
    % American Meteorological Society, 
    % 45 Beacon St., Boston, MA 02108.}
% and Author Two\thanks{Current affiliation: American Meteorological Society, 
    % 45 Beacon St., Boston, MA 02108.}}

\authors{Pascal Horton\correspondingauthor{Terranum, Rue de l'industrie 35 bis, 1030 Bussigny-pr\`{e}s-Lausanne, Switzerland.}}

%% Follow this form:
    % \affiliation{American Meteorological Society, 
    % Boston, Massachusetts.}

\affiliation{University of Lausanne, Lausanne, and Terranum,  Bussigny-pr\`{e}s-Lausanne, Switzerland}

%% Follow this form:
    %\email{latex@ametsoc.org}

\email{pascal.horton@terranum.ch}

%% If appropriate, add additional authors, different affiliations:
    %\extraauthor{Extra Author}
    %\extraaffil{Affiliation, City, State/Province, Country}

\extraauthor{Michel Jaboyedoff}
\extraaffil{University of Lausanne, Lausanne, Switzerland}

%% May repeat for a additional authors/affiliations:

%\extraauthor{}
%\extraaffil{}

\extraauthor{Charles Obled}
\extraaffil{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%
% Enter your abstract here
% Abstracts should not exceed 250 words in length!
%
% For BAMS authors only: If your article requires a Capsule Summary, please place the capsule text at the end of your abstract
% and identify it as the capsule. Example: This is the end of the abstract. (Capsule Summary) This is the capsule summary.

\abstract{Enter the text of your abstract here.}

\begin{document}

%% Necessary!
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MAIN BODY OF PAPER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

%% In all cases, if there is only one entry of this type within
%% the higher level heading, use the star form: 
%%
% \section{Section title}
% \subsection*{subsection}
% text...
% \section{Section title}

%vs

% \section{Section title}
% \subsection{subsection one}
% text...
% \subsection{subsection two}
% \section{Section title}

%%%
% \section{First primary heading}

% \subsection{First secondary heading}

% \subsubsection{First tertiary heading}

% \paragraph{First quaternary heading}

\section{Introduction}

\section{Classic calibration of the analogue method}

\subsection{Methodology}

\subsection{Limits of the classic calibration}

\section{Characterization of the parameters space}

\subsection{Monte-Carlo analysis}

\subsection{Parameters that should be optimized}

\subsection{Possible new degrees of freedom}

\section{Adapting the genetic algorithms}

\subsection{Basic concepts of the genetic algorithms}

\subsection{Structure and operators}

\subsection{Implementation and contraints}

\subsection{Recommendations of parameterization}

\section{Optimization of the analogy of atmospheric circulation}

\section{Optimization of the analogy with humidity variables}

\section{Conclusions and perspectives}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\acknowledgments
Start acknowledgments here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% APPENDIXES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Use \appendix if there is only one appendix.
%\appendix

% Use \appendix[A], \appendix}[B], if you have multiple appendixes.
%\appendix[A]

%% Appendix title is necessary! For appendix title:
%\appendixtitle{}

%%% Appendix section numbering (note, skip \section and begin with \subsection)
% \subsection{First primary heading}

% \subsubsection{First secondary heading}

% \paragraph{First tertiary heading}

%% Important!
%\appendcaption{<appendix letter and number>}{<caption>} 
%must be used for figures and tables in appendixes, e.g.,
%
%\begin{figure}
%\noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
%\appendcaption{A1}{Caption here.}
%\end{figure}
%
% All appendix figures/tables should be placed in order AFTER the main figures/tables, i.e., tables, appendix tables, figures, appendix figures.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Make your BibTeX bibliography by using these commands:
% \bibliographystyle{ametsoc2014}
% \bibliography{references}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TABLES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Enter tables at the end of the document, before figures.
%%
%
%\begin{table}[t]
%\caption{This is a sample table caption and table layout.  Enter as many tables as
%  necessary at the end of your manuscript. Table from Lorenz (1963).}\label{t1}
%\begin{center}
%\begin{tabular}{ccccrrcrc}
%\hline\hline
%$N$ & $X$ & $Y$ & $Z$\\
%\hline
% 0000 & 0000 & 0010 & 0000 \\
% 0005 & 0004 & 0012 & 0000 \\
% 0010 & 0009 & 0020 & 0000 \\
% 0015 & 0016 & 0036 & 0002 \\
% 0020 & 0030 & 0066 & 0007 \\
% 0025 & 0054 & 0115 & 0024 \\
%\hline
%\end{tabular}
%\end{center}
%\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIGURES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Enter figures at the end of the document, after tables.
%%
%
%\begin{figure}[t]
%  \noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
%  \caption{Enter the caption for your figure here.  Repeat as
%  necessary for each of your figures. Figure from \protect\cite{Knutti2008}.}\label{f1}
%\end{figure}

\end{document}

### 2014-11-28 Optimization - Journal of Climate/template.tex
Update of the paper structure.
Writing the article on optimization.

@@
 \section{Introduction}
+...
+\cite{Horton2012b}
 
-\section{Classic calibration of the analogue method}
+\section{Calibration of the analogue method}
+...
 
-\subsection{Methodology}
+\subsection{Data}
+...
+
+\subsection{The analogue method}
+...
+
+\cite{Horton2012}
+
+\subsection{Calibration framework}
+
+The calibration of the analogue method is usually done in a perfect prognosis \citep{Klein1959a} framework \citep{BenDaoud2010a, Bontron2004a}.
+Perfect prognosis uses observed or reanalyzed data to calibrate the relationship between predictors and predictands.
+Then, when used in operational forecasting, this relationship is applied to global model forecasts, that contains larger uncertainties.
+This framework allow us to identify relationships that are as close as possible to the natural links between predictors and predictands, by reducing uncertainties related to numerical forecasting models.
+However, no model is perfect, and even reanalysis data contains a bias that cannot be ignored.
+For this reason, the statistical relationships identified in the perfect prognosis framework should be applied to model outputs that are as similar as possible to the model used to elaborate the reanalysis.
+
+Another reason for working in a perfect prognosis framework is that numerical models evolve continuously, and so does the forecast they provide.
+Re-forecasts allows us to work on a homogeneous dataset, as they are regularly reprocessed.
+However, it would involve that we need to redo the calibration procedure every time a new version is available, in order to reduce the bias \citep{Wilson2002a}.
+Moreover, the reforecasts are not re-processed for every new version of the model, meaning we still end up with a bias between the forecast and the archive.
+Finally, the length of reanalyses datasets are usually much longer than reforecast datasets, which allows us to identify more robust relationships.
+The size of the archive is indeed an important criteria for the analogue method.
+
+The statistical relationship is established on a calibration period that is as long as possible.
+For every day of this period, a search for analogues is processed, the precipitation data are associated with the corresponding dates and a forecast score is calculated.
+During the search for analogues situations, 120 days around the target date are excluded (thus excluding data in the same year) in order to consider only truly independent candidates days.
+
+A validation period is always considered.
+It consists of an independent period that is never used as target neither candidate date.
+Validating the parameters of the analogue method is very important in order to avoid over-parametrization and thus to ensure that the statistical relationship is valid on another period.
+
+The accuracy of the parameters is evaluated by means of the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
+Let the precipitation variable be denoted $x$ with $x^{0}$ the observed value, and $F(x)$ the predicted cumulative distribution functions (cdf).
+The mean CRPS of a forecast series of length $n$ can be written:
+
+\begin{equation}
+\label{eq:CRPS}
+CRPS = \frac{1}{n} \sum_{i=1}^{n} \left(  \int_{-\infty}^{+\infty} \left[ F_{i}(x)-H_{i}(x-x_{i}^{0})\right]^{2} dx \right) 
+\end{equation}
+where $H(x-x_{i}^{0})$ is the Heaviside function that is null when $x-x_{i}^{0}<0$, and has the value 1 otherwise.
+
+The mean CRPS is processed on the calibration, respectively the validation periods.
+It means that we average the scores on all days, may they be dry, slightly rainy or with heavy precipitation.
+There is actually a weighting by the number: climatologically, non-rainy days are often more frequent (of course, depending on the location) and it is essential to forecast them well.
+The days with heavy precipitation are rare, but can instead provide individual scores ($CRPS_{j}$) very penalizing, which implies that the optimization will also try to forecast them accurately.
+However, these aspects are not explicitly controlled.
+
+\subsection{The classic calibration approach}
+
+The calibration procedure that we call ''classic'' was developed by \citet{Bontron2004a} at the LTHE laborytory (INPG, Grenoble).
+It determines the optimal settings for the different variables of each level of analogy.
+The analogy levels (eg the atmospheric circulation or humidity variables) are calibrated sequentially.
+The procedure consists of the following steps \citet{Bontron2004a}:
+
+\begin{enumerate}
+	\item Manual choice of the following parameters:
+	\begin{itemize}
+		\item meteorological variable,
+		\item atmospheric level,
+		\item time frame (hour of observation),
+		\item initial analogue numbers.
+	\end{itemize}
+
+	\item For every level of analogy:
+	\begin{enumerate}
+		\item Identification of the most skilled unitary cell (1 point for humidity variables and 4 for the geopotential fields when using the S1 criteria) over a large domain.
+Every point (or cell) of the full domain is assessed jointly on every predictor of the level of analogy (consisting generally of the same variable, but on different atmospheric levels and at different hours).
+		\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain. The detailed stages are the followings:
+		\begin{enumerate}
+			\item The unitary spatial window is expanded in every 4 directions successively. The performance score is processed for these 4 windows.
+			\item Only the direction providing the best improvement is applied to our spatial window.
+			\item From this new spatial window, an increase in every 4 directions is once again assessed, and the best improvement is applied.
+			\item The spatial window grows up by repeating the previous steps, until no improvement is reached.
+		\end{enumerate}
+		\item The number of analogues is optimized for the current level of analogy.
+		\item A new level of analogy can be added, based on other variables on predefined atmospheric levels and time frames.
+The analogue number for the next level of analogy is initiated at a chosen value.
+Then, the procedure starts again from step (a).
+The parameters calibrated on the previous analogue levels are fixed and do not change (except the number of analogues, at the final stage).
+	\end{enumerate}
+	\item Finally, the numbers of analogues are re-assessed for the different analogue levels. This is done iteratively by varying the number of analogues of each level in a systematic way.
+\end{enumerate}
+
+Calibration is done in stages, to determine the optimal parameters systematically.
+The steps are distinct and previously optimized parameters are generally not reassessed.
+\citet{Bontron2004a} notes however that ''this type of algorithm, which is changing the parameters of a model in a unique path, can lead to the best solution, provided that there is no local optima''.
+The advantage of this method is that it is fast and has low computing requirements.
+We added small improvements to this method by allowing the spatial windows to do other moves, such as:
+
+\begin{itemize}
+	\item increase in 2 simultaneous directions,
+	\item decrease in 1 or 2 simultaneous directions,
+	\item expansion or contraction (in every direction),
+	\item shift of the window (without resizing) in 8 directions (including diagonals),
+	\item and finally all the moves described above, but with a factor of 2, 3, or more.
+For example, we try to increase by 2 units in one (or more) direction.
+This allows to skip one size that may not be optimal.
+\end{itemize}
+
+These supplementary steps often result in spatial windows that are a bit different, but the performance gain is rather marginal.
 
 \subsection{Limits of the classic calibration}
+...
 
 \section{Characterization of the parameters space}
+...
 
 \subsection{Monte-Carlo analysis}
+...
 
 \subsection{Parameters that should be optimized}
+...
 
 \subsection{Possible new degrees of freedom}
+...
 
 \section{Adapting the genetic algorithms}
+...
 
 \subsection{Basic concepts of the genetic algorithms}
+...
 
 \subsection{Structure and operators}
+...
 
 \subsection{Implementation and contraints}
+...
 
 \subsection{Recommendations of parameterization}
+...
 
 \section{Optimization of the analogy of atmospheric circulation}
+...
+
+\subsection{Which parameters are optimized ?}
+...
+
+\subsection{Results of the optimization of atmospheric circulation}
+...
+
+\subsection{Discussion}
+...
 
 \section{Optimization of the analogy with humidity variables}
+...
+
+\subsection{Results of the optimization on both analogy levels}
+...
+
+\subsection{Successive optimization vs global optimization}
+...
+
+\subsection{Discussion}
+...
 
 \section{Conclusions and perspectives}
+...
 
@@
 
+\bibliographystyle{ametsoc2014}
+% \bibliography{references}
+\bibliography{../_refs/_articles-optimization}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-11-29 Optimization - Journal of Climate/template.tex
Writing the article on optimization.

@@
 % \documentclass[twocol]{ametsoc}
+
+\usepackage{multirow}
+\usepackage{gensymb}
 
@@
 \subsection{Data}
-...
+
+The analogue method relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series we want to forecast.
+
+Predictors are generally reanalysis datasets (and outputs of a global numerical weather prediction models for the target situation in operational forecasting, which is not the topic of this paper).
+We will work here with the NCEP/NCAR reanalysis \citep[6-hourly, 17 atmospheric levels at a resolution of 2.5\degree, see][]{Kalnay1996a}, but it can be any other reanalysis.
+
+The predictand (which is to be predicted) is here the daily precipitation (6~a.m.
+to 6~a.m.
+the next day) measured at the MeteoSwiss' stations network, for the period 1962-2007.
+The time series from every available gauging station were averaged over subregions in order to smooth local effects \citep{Obled2002a, Marty2012}.
 
 \subsection{The analogue method}
-...
 
-\cite{Horton2012}
+The analogue method is a downscaling technique based on the idea expressed by \citet{Lorenz1969a}.
+It aims at forecasting a predictand, often the daily precipitation, on the basis of predictor variables describing the synoptic atmospheric circulation.
+Its main hypothesis is that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Bontron2005}.
+
+Multiple variations of the methods are possible, and some aspects and parameters will not be detailed hereafter.
+There are mainly 2 implementations that are used most often: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on humidity variables \citep{Obled2002a, Bontron2005, Marty2012}.
+
+The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table_params_R1}): For a target date, we evaluate the similarity of the atmospheric circulation with every day of the archive by processing the S1 criteria \citep[Eq.\ (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
+\citet{Bontron2005} showed that the geopotential heights at 500~hPa and 1000~hPa are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criteria performs better than scores based on absolute distances.
+The reason for such better results is that the S1 criteria allows comparing the circulation pattern, by means of the gradients, rather than the absolute value of the geopotential heights.
+To cope with seasonal effects, candidate data are extracted for every year from the archive within a period of 4 months centred around the target date.
+
+\begin{equation}
+\label{eq:S1}
+S1=100 \frac {\displaystyle \sum_{i} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
+{\displaystyle \sum_{i} max\left\lbrace \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert \right\rbrace }
+\end{equation}
+where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points in the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
+The differences are processed separately in both directions.
+The smaller the S1 values are, the more similar the pressure fields.
+
+The $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day.
+The number of analogues, $N_{1}$, is a parameter to calibrate.
+It has an optimum clearly identifiable that is often around 50 dates when we consider only one level of analogy.
+
+Then, the daily observed precipitation amount of the $N_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
+
+The other most know method adds a second level of analogy on humidity variables (Table \ref{table_params_R2}).
+The predictor that \citet{Bontron2004a} found as optimal for the France territory is a humidity index made of the multiplication of the precipitable water with the relative humidity at 850~hPa.
+\cite{Horton2012b} confirmed that this product is better than any other variable from the NCEP/NCAR reanalysis considered independently.
+When adding a second level of analogy, we subsample $N_{2}$ (30) dates in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
+When we add a second level of analogy, we keep a higher number of analogues on the first level (70 instead of 50).
 
@@
 
-\section{Optimization of the analogy of atmospheric circulation}
+\section{Global optimization of the analogue method}
 ...
 
-\subsection{Which parameters are optimized ?}
+\subsection{Case study description}
+
+The study area is the alpine upper Rhône catchment in Switzerland (Fig.\ \ref{figure_map}).
+The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$.
+This region in the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at providing a real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
+The first global optimizations were part of the MINERVE project \citep{Horton2012, Horton2012b}.
+
+\subsection{Optimization of the analogy of atmospheric circulation}
 ...
 
-\subsection{Results of the optimization of atmospheric circulation}
+\subsubsection{Which parameters are optimized ?}
 ...
 
-\subsection{Discussion}
+\subsubsection{Results of the optimization of atmospheric circulation}
 ...
 
-\section{Optimization of the analogy with humidity variables}
+\subsubsection{Discussion}
 ...
 
-\subsection{Results of the optimization on both analogy levels}
+\subsection{Optimization of the analogy with humidity variables}
 ...
 
-\subsection{Successive optimization vs global optimization}
+\subsubsection{Results of the optimization on both analogy levels}
 ...
 
-\subsection{Discussion}
+\subsubsection{Successive optimization vs global optimization}
+...
+
+\subsubsection{Discussion}
 ...
@@
 
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Parameters of the reference method on the atmospheric circulation.}
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Analogues nb} \\ 
+			\hline 
+			preselection & \multicolumn{4}{c}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & geopotential hgt 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
+			& geopotential hgt 500~hPa & 24~h & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table_params_R1}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Parameters of the reference method with humidity variables.}
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Analogues nb} \\ 
+			\hline 
+			preselection & \multicolumn{4}{c}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & geopotential hgt 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
+			& geopotential hgt 500~hPa & 24~h & & \\ 
+			\hline
+			\multirow{2}{*}{2} & precipitable water * relative humidity 850~hPa & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{30} \\
+			& precipitable water * relative humidity 850~hPa & 24~h & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table_params_R2}
+\end{table}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=8.3cm]{figure_map.pdf}}
+	\caption{Location of the alpine Rhône catchment in Switzerland. (source: Swisstopo)}
+	\label{figure_map}
+\end{figure}
+
 \end{document}

### 2014-12-05 Optimization - Journal of Climate/template.tex
Writing the article on optimization.

@@
 
-\affiliation{University of Lausanne, Lausanne, and Terranum,  Bussigny-pr\`{e}s-Lausanne, Switzerland}
+\affiliation{University of Lausanne, and Terranum,  Bussigny-pr\`{e}s-Lausanne, Switzerland}
 
@@
 ...
-\cite{Horton2012b}
+\cite{Horton2012a}
 
@@
 Predictors are generally reanalysis datasets (and outputs of a global numerical weather prediction models for the target situation in operational forecasting, which is not the topic of this paper).
-We will work here with the NCEP/NCAR reanalysis \citep[6-hourly, 17 atmospheric levels at a resolution of 2.5\degree, see][]{Kalnay1996a}, but it can be any other reanalysis.
+We will work here with the NCEP/NCAR reanalysis \citep[6-hourly, 17 atmospheric levels at a resolution of 2.5\degree, see][]{Kalnay1996}, but it can be any other reanalysis.
 
@@
 the next day) measured at the MeteoSwiss' stations network, for the period 1962-2007.
-The time series from every available gauging station were averaged over subregions in order to smooth local effects \citep{Obled2002a, Marty2012}.
+The time series from every available gauging station were averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.
 
@@
 
-The analogue method is a downscaling technique based on the idea expressed by \citet{Lorenz1969a}.
+The analogue method is a downscaling technique based on the idea expressed by \citet{Lorenz1969}.
 It aims at forecasting a predictand, often the daily precipitation, on the basis of predictor variables describing the synoptic atmospheric circulation.
@@
 Multiple variations of the methods are possible, and some aspects and parameters will not be detailed hereafter.
-There are mainly 2 implementations that are used most often: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on humidity variables \citep{Obled2002a, Bontron2005, Marty2012}.
+There are mainly 2 implementations that are used most often: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on humidity variables \citep{Obled2002, Bontron2005, Marty2012}.
 
@@
 The other most know method adds a second level of analogy on humidity variables (Table \ref{table_params_R2}).
-The predictor that \citet{Bontron2004a} found as optimal for the France territory is a humidity index made of the multiplication of the precipitable water with the relative humidity at 850~hPa.
-\cite{Horton2012b} confirmed that this product is better than any other variable from the NCEP/NCAR reanalysis considered independently.
+The predictor that \citet{Bontron2004} found as optimal for the France territory is a humidity index made of the multiplication of the precipitable water with the relative humidity at 850~hPa.
+\cite{Horton2012a} confirmed that this product is better than any other variable from the NCEP/NCAR reanalysis considered independently.
 When adding a second level of analogy, we subsample $N_{2}$ (30) dates in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
@@
 
-The calibration of the analogue method is usually done in a perfect prognosis \citep{Klein1959a} framework \citep{BenDaoud2010a, Bontron2004a}.
+The calibration of the analogue method is usually done in a perfect prognosis \citep{Klein1959} framework \citep{BenDaoud2010, Bontron2004}.
 Perfect prognosis uses observed or reanalyzed data to calibrate the relationship between predictors and predictands.
@@
 Re-forecasts allows us to work on a homogeneous dataset, as they are regularly reprocessed.
-However, it would involve that we need to redo the calibration procedure every time a new version is available, in order to reduce the bias \citep{Wilson2002a}.
+However, it would involve that we need to redo the calibration procedure every time a new version is available, in order to reduce the bias \citep{Wilson2002}.
 Moreover, the reforecasts are not re-processed for every new version of the model, meaning we still end up with a bias between the forecast and the archive.
@@
 
-The calibration procedure that we call ''classic'' was developed by \citet{Bontron2004a} at the LTHE laborytory (INPG, Grenoble).
+The calibration procedure that we call ''classic'' was developed by \citet{Bontron2004} at the LTHE laborytory (INPG, Grenoble).
 It determines the optimal settings for the different variables of each level of analogy.
 The analogy levels (eg the atmospheric circulation or humidity variables) are calibrated sequentially.
-The procedure consists of the following steps \citet{Bontron2004a}:
+The procedure consists of the following steps \citet{Bontron2004}:
 
@@
 The steps are distinct and previously optimized parameters are generally not reassessed.
-\citet{Bontron2004a} notes however that ''this type of algorithm, which is changing the parameters of a model in a unique path, can lead to the best solution, provided that there is no local optima''.
+\citet{Bontron2004} notes however that ''\textit{this type of algorithm, which is changing the parameters of a model in a unique path, can lead to the best solution, provided that there is no local optima}''.
 The advantage of this method is that it is fast and has low computing requirements.
@@
 
-These supplementary steps often result in spatial windows that are a bit different, but the performance gain is rather marginal.
+These supplementary steps often result in spatial windows that are a bit different, but the performance gain is rather marginal (gain of 0.2\%).
+These methods are available in the open source software AtmoSwing (Analogue Technique MOdel for Statistical Weather forecastING, www.atmoswing.org).
 
-\subsection{Limits of the classic calibration}
-...
+\section{Motivation for a global optimization}
 
-\section{Characterization of the parameters space}
-...
+The classic calibration is fast to optimize one spatial window for a given atmospheric level and temporal window.
+However, it doesn't provide an objective choice of the atmospheric level and temporal window.
+The only option is to try systematically every combination, which may be acceptable for no more than 2 levels.
+However, \citet{Horton2012} showed that additional atmospheric levels may improve the method.
 
-\subsection{Monte-Carlo analysis}
+We observed during the calibration of the analogue method that the resulting parameters vary with the initial choices (such as the number of analogues).
+In addition, the different levels of analogy (on the atmospheric circulation and the humidity variables) are always calibrated sequentially.
+However, we can not exclude any dependency between them, which could lead us to select other parameters if we calibrate them together.
+Simultaneous calibration of all parameters has never been undertaken so far.
+Only a global optimization can be able to optimize all parameters of all analogy levels simultaneously.
+
+When creating the classic calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters and wrote: '' \textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent.
+We will present our results by first searching the best variable [note: e.g.
+choice of the atmospheric level and the temporal window for the geopotential height] on a chosen spatial window, and next, the best window for the chosen variable.
+However, even by repeating the process, are we sure to have found the optimal combination?} ''.
+And later in his work: '' \textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution} ''.
+\citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of the analogue method and concludes that one needs to be an expert to know their respective influence, their sensitivity and their nonlinear interactions.
+\citet{BenDaoud2010}, when calibrating the analogue method, also stated that '' \textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously } ''.
+The configuration of the analogue method resulting from a classic approach is likely to be a local optimum.
+
+The analogue method needs to be adapted to every new region it is applied, because the leading meteorological influences are specific to this region.
+Even the choice of the atmospheric level and the temporal window should be reconsidered, when not the variable itself.
+For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012} found no interest in this variable in an Alpine environment, because the vertical velocity is mainly related to the orographic effect, and was thus already well related to the atmospheric circulation itself.
+So, when adapting the analogue method to a new region, we should assess systematically every combination of atmospheric levels, time and spatial windows, which is an intensive task.
+This procedure can be automatized by a global optimization technique.
+
+Our ambition was then to assess the feasibility of an automatic optimization of the analogue method through various techniques.
+The objective is to find an approach to optimize all parameters simultaneously, and thus be able to identify the global optimum in the parameter space.
+In addition, it can overcome the systematic manual assessments of certain parameters such as atmospheric levels and time windows.
+Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the atmospheric levels, and the consideration of non-overlapping spatial windows between the atmospheric levels.
+
+\citet{Horton2012} assessed the ability of the \citep{Nelder1965a} method based on a simplex approach.
+This technique didn't provide satisfying results and failed at identifying the global optimum.
+Indeed, the optimized parameters didn't converge and many local optimums came out.
+The parameters space of the analogue method is very complex and not appropriate for a linear optimization technique.
+
+\subsection{Characterization of the parameters space}
 ...
@@
 \section{Adapting the genetic algorithms}
-...
+
+Genetic algorithms (GAs) come from the world of stochastic optimization, more specifically from metaheuristic approaches.
+These are stochastic iterative algorithms that behave like search algorithms by exploiting the characteristics of a problem and are particularly suitable for complex parameters spaces.
+
+Genetic algorithms are part of the family of evolutionary algorithms \citet{Back1993c, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
+GAs are the most used technique from evolutionary algorithms \citep{Back1993b}, and they are constantly improving \citep{Haupt2004}.
+However, with time, the different methods of evolutionary algorithms tend to be similar and share many commonalities \citep{Back1996b, Haupt2004}.
+
+The method was developed by \citet{Holland1992} and was popularized by \citet{Goldberg1989}.
+Unlike a linear or local optimization, GAs seek the global optimum on a complex surface, theoretically without restrictions, but with no guarantee to reach it.
 
 \subsection{Basic concepts of the genetic algorithms}
-...
+
+GAs mimic the evolution of a population of individuals in a new environment, by applying rules based on natural processes, such as DNA mutation, chromosomes crossover, natural selection, etc.
+It simulates the fact in the natural environment, the most suitable individuals tend to survive longer, to reproduce more easily, and so to influence coming generations by providing some genes that provide some good performance in a certain domain.
+Generation after generation, the DNA mixes and the strong genes cumulate in some individuals \citep{Beasley1996}.
+Globally, the fitness of the population to its environment increases, while retaining enough variety to not converge too quickly to a local optimum.
+
+9.5.1.2 Quand utiliser des algorithmes genetiques
 
 \subsection{Structure and operators}
-...
+
+The combination of strong genes by the operator of chromosomes crossover is theoretically the most important operating mechanism in the conventional GAs \citep{Holland1992b,Back1993}.
+However, many studies identify the mutation process as main operator, and crossovers as secondary \citep[see][]{Back1992,Back1996,Back1996b,Smith1997,Deb1999,Haupt2004,Costa2005,Costa2007}.
 
@@
 This region in the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at providing a real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
-The first global optimizations were part of the MINERVE project \citep{Horton2012, Horton2012b}.
+The first global optimizations were part of the MINERVE project \citep{Horton2012, Horton2012a}.
 
@@
 \acknowledgments
-Start acknowledgments here.
+Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of.
+
+Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE project which started this research.
+NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.
+Precipitation time series provided by MeteoSwiss.
 
@@
 
-\bibliographystyle{ametsoc2014}
+\bibliographystyle{ametsoc2014_no_url}
 % \bibliography{references}

### 2015-01-09 Optimization - Journal of Climate/template.tex
Writing the article on optimization.

@@
 
-The method was developed by \citet{Holland1992} and was popularized by \citet{Goldberg1989}.
+The method was developed by \citet{Holland1992b} and was popularized by \citet{Goldberg1989}.
 Unlike a linear or local optimization, GAs seek the global optimum on a complex surface, theoretically without restrictions, but with no guarantee to reach it.
@@
 It simulates the fact in the natural environment, the most suitable individuals tend to survive longer, to reproduce more easily, and so to influence coming generations by providing some genes that provide some good performance in a certain domain.
-Generation after generation, the DNA mixes and the strong genes cumulate in some individuals \citep{Beasley1996}.
+Generation after generation, the DNA mixes and the strong genes cumulate in some individuals \citep{Beasley1996a}.
 Globally, the fitness of the population to its environment increases, while retaining enough variety to not converge too quickly to a local optimum.
 
-9.5.1.2 Quand utiliser des algorithmes genetiques
+Applications of GAs are very diversified as they can handle many parameters of various types \citep{Joines1996a}, even with very complex cost surfaces \citep{Haupt2004}.
+GAs work remarkably well with intervariable dependences \citep{Haupt2004}.
+The objective function to optimize (often named fitness function in this context) can be of different types (mathematical function, experimental or numerical modeling).
+Only the resulting value is used for optimization.
+Indeed, these algorithms do not require any knowledge of the problem, which can be used as black-box.
+
+By means of the reproduction operator and the natural selection, the GAs focus on the most promising regions of the parameter space \citep{Holland1992b}.
+Points (parameters sets) are densified in these areas because the strong genes of the best individuals propagate from generation to generation.
+
+Two conditions guarantee in theory the convergence to the global optimum \citep{Zitzler2004a}:
+
+\begin{enumerate}
+	\item Parameters mutations that can allow to explore the entire parameter space, thus ensures that any value can be achieved with a non-zero probability.
+	\item A rule of elitism ensuring that an optimal solution can not be lost or damaged.
+\end{enumerate}
+
+Practically, GAs allow rapidly approaching satisfactory solutions, but they do not provide the optimum solution for sure \citep{Zitzler2004a}.
+It is indeed mainly a matter of time.
+When the optimizer gets closer to the global optimum, any new improvement takes more time to appear, and the final adjustment of the parameters is very time consuming \citep{Back1993a}.
+For problems that require a significant amount of time in order to evaluate the objective function, as in our case, we have to limit the number of generations to get reasonable processing time.
+Thus, different acceptable solutions can result from one or more optimizations \citep{Holland1992b}.
+This is a strength and a weakness of GAs: they are very good at exploring complex parameters spaces in order to identify the most promising areas, but they will not necessarily find the best solution with the optimal values of all parameters \citep{Holland1992b}.
 
@@
 
-The combination of strong genes by the operator of chromosomes crossover is theoretically the most important operating mechanism in the conventional GAs \citep{Holland1992b,Back1993}.
-However, many studies identify the mutation process as main operator, and crossovers as secondary \citep[see][]{Back1992,Back1996,Back1996b,Smith1997,Deb1999,Haupt2004,Costa2005,Costa2007}.
+The GAs optimize a population of individuals (parameters sets).
+Each individual contains a chromosome (parameters of the analogue method in our case).
+We call gene every parameter that constitutes the chromosome.
+
+The combination of strong genes by the operator of chromosomes crossover is theoretically the most important operating mechanism in the conventional GAs \citep{Holland1992b,Back1993b}.
+However, many studies identify the mutation process as main operator, and crossovers as secondary \citep[see][]{Back1992a,Back1996a,Back1996b,Smith1997a,Deb1999,Haupt2004,Costa2005a,Costa2007a}.
 

### 2015-01-09 Optimization - Journal of Climate/template.tex
Writing the article on optimization.

@@
 We call gene every parameter that constitutes the chromosome.
+The parameters to optimize have long been coded in binary form and assembled as strings in the canonical GAs \citep{Goldberg1989}.
+Encoding and decoding steps were needed to transform the variable from its floating-point representation into its binary representation, and vice versa, which introduce quantification errors \citep{Haupt2004}.
+According to \citet{Holland1992b}, working with binary chromosomes was supposed to be more efficient \citep{Goldberg1990a, Back1993b}.
+However, more and more applications use floating-point representations, allowing to avoid the coding and decoding steps and the quantification errors \citep{Haupt2004}, and which also often resulted in a performance improvement \citep{Goldberg1990a}.
+It is thus now considered that for continuous variables, a floating-point representation is more suited \citep{Michalewicz1996, Herrera1998a, Haupt2004, Back1996b, Gaffney2010a}.
+
+There are numerous implementation variants of GAs often optimal for a given problem \citep{Hart1991a,Schraudolph1992a}.
+However, the structure of the method (Figure \ref{figure_structure_gas}) resulting from the work of \citet{Holland1992b} is common to most applications \citep{Back1993b}.
+The divergences are the operators implementation, through significantly different algorithms, which has an important effect on the results \citep{Gaffney2010a}.
+
+All operators we used and their options, applied to real coding, are described in the following sections. Many other operators exist, but we will only present the ones we evaluated.
+
+\subsubsection{Genesis of the population}
+
+The first step of the optimization is to generate the initial population.
+A population is a set of $N$ individuals (each of which represents a point in the space of potential solutions, a parameters set of the analogue method in our application) that we are going to make evolve.
+A generation is the population at a given time.
+
+A random initialization based on a uniform distribution is the most current version.
+The size $N$ of the population is often a compromise between the computation time and the quality of the solution.
+$N$ must allow sufficient sampling of the solutions field \citep{Beasley1996a}, and should thus vary as a function of chromosome size (ie the number of parameters to be optimized).
+In our application, we found the following ranges to be accurate in average:
+
+\begin{itemize}
+	\item $50<N<100$ for a very simple implementation of the analogue method (1 level of analogy with 2 atmospheric levels),
+
+	\item $N\approx200$ for a bit more complex method (1 level of analogy with 4 atmospheric levels, or 2 level of analogy with less atmospheric levels),
+
+	\item $N\approx500$ for significantly more complex methods (2-3 levels of analogy with 4 atmospheric levels for the atmospheric circulation, and 2 to 4 levels for the analogy humidity),
+\end{itemize}
+
+We didn't find any improvement with $N>500$, the results were even surprisingly of a lower quality.
+However, this cannot be generalized and depends on the analogue method to optimize, and supposedly on the characteristics of the processes generating the precipitations in a given region.
+
+\subsubsection{Natural selection}
+
+Natural selection is performed on the basis of the objective function values.
+The selection allows to only keep a certain part of the population, usually half ($N/2$), which can access the mating pool (intermediate generation with $N_{mp}$ members).
+If $N_{mp}$ is too high, the reproduction rate is too low, whereas if it is too small, the strong traits of individuals do not have the ability to accumulate in the same chromosome \citep{Haupt2004}.
+Several techniques exist, such as:
+
+\begin{itemize}
+	\item \textbf{$N_{mp}$-elitism} \citep{Michalewicz1996}: the population is sorted according to the value of the objective function and only the better half is preserved.
+
+	\item \textbf{Tournament selection} \citep{Michalewicz1996, Zitzler2004a}: two individuals are randomly selected and fight.
+The one with the highest score is chosen, but with a certain probability, in order to reduce the selection pressure.
+This procedure is repeated until the mating pool is full.
+Individuals can be selected several times, and thus be represented several times in the mating pool.
+\end{itemize}
+
+\subsubsection{Selection of the couples}
 
@@
 
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=10.3cm]{figure_structure_gas.pdf}}
+	\caption{Genetic algorithms operational flowchart}
+	\label{figure_structure_gas}
+\end{figure}
+
 \end{document}

### 2015-01-09 Optimization - Journal of Climate/template.tex
Writing the article on optimization.

@@
 
+Individuals of the mating pool can reproduce. It begins with the selection of pairs (the parents). The techniques implemented in this work are the following:
+
+\begin{itemize}
+	\item \textbf{Rank pairing}: individuals are gathered in pairs according to their rank (classified on the performance scores).
+Consecutive ranks are put together (odd rows are associated with even rows).
+This approach is easy to achieve, but does not look like a natural process.
+
+	\item \textbf{Random pairing}: two individuals are randomly selected to form a couple, according to a uniform law.
+
+	\item \textbf{Roulette wheel weighting}: the roulette technique refers to gambling.
+But unlike casino roulette, this one is biased.
+Each individual is associated with a sector of the wheel with a certain opening angle, which is its probability of selection \citep{Haupt2004}.
+The probability assigned to the individuals is proportional to their fitness (objective function), so that the most adapted individuals have the greatest probability of reproduction.
+There are two techniques for weighting the individuals of the mating pool:
+	\begin{itemize}
+		\item Roulette wheel weighting on rank: the probability of each individual depends on its rank $n$:
+		\begin{equation}
+		p_{n}=\dfrac{N_{mp}-n+1}{\sum^{N_{mp}}_{n=1}n}
+		\label{equation_mating_rank_weighting}
+		\end{equation}
+
+		\item Roulette wheel weighting on fitness: the selection probability is calculated based on the value of the objective function.
+This approach gives more weight to the best individuals when the distribution of scores is wide, while the weight is almost similar when all individuals have approximately the same score \citep{Haupt2004}.
+The probability $p_{n}$ of each individual is calculated by the equation \ref{equation_mating_score_weighting}:
+		\begin{equation}
+		p_{n}=\frac{score_{n}-score_{N_{mp}}}{\sum_{n=1}^{N_{mp}} (score_{n}-score_{N_{mp}})}
+		\label{equation_mating_score_weighting}
+		\end{equation}
+		In our application, the last individual ($N_{mp}$) has zero probability of being selected.
+	\end{itemize}
+
+	\item \textbf{Tournament selection}: This operator is similar to that used in natural selection, but is applied here for the successive selection of each parent.
+To select a parent, a number of individuals (2 or 3) are randomly picked and the best is kept.
+This operation is performed twice, once for each partner.
+This approach imitates the breeding competition in nature \citep{Haupt2004}.
+\end{itemize}
+
+\subsubsection{Chromosome crossover}
+
+Once the two parents selected for breeding, they combine their chromosomes and produce two children, bringing the number of individuals in the population of $N_{mp}$ back to $N$ (the parents also return back in the total population in order to complement the next generation).
+The combination of chromosomes is carried out using a crossover operator, thereby generating two offspring having characteristics derived from both parents.
+Chromosome crossover widens the search space and favours the combination of strong genes, which can result in more suited children.
+It allows a mixing of genes and accumulation of positive mutations.
+
+The evaluated crossover operators are the following:
+
+\begin{itemize}
+	\item \textbf{Single-point crossover}: a crossover point is randomly chosen for the pair. The genes (our parameters) located after that point are exchanged in between the two chromosomes.
+
+	\item \textbf{Two-point crossover}: works like the single-point crossover, but there are two intersections defining the segments to exchange.
+This approach, which significantly extends the search space for the children, is considered more efficient than the previous \citep{Beasley1993b, Haupt2004}.
+
+	\item \textbf{Multiple-point crossover} \citep{DeJong1975a}: it is a generalization of the previous, with a number of crossover points up to the number of genes.
+
+	\item \textbf{Uniform crossover} \citep{Syswerda1989}: for each gene of the chromosome, it is randomly chosen to exchange or not the values between the parents.
+
+	\item \textbf{Binary-like crossover} \citep{Haupt2004}: chromosome crossover on a binary coding can generate new values for variables located at intersection points, since the crossovers are applied at the bit level, thus often within a gene.
+This is not the case for the floating-point representation, since the crossover is performed between the genes.
+To reproduce the behaviour present in the original algorithms, which introduces new information, \citet{Haupt2004} propose an operator that combines standard crossover with an interpolation approach.
+The genes located after a crossover point are exchanged, but the gene located at the intersection is modified as follows:
+	\begin{equation}
+	\left\lbrace \begin{array}{l} 
+	g_{e1,n} = g_{p1,n} - \beta (g_{p1,n} - g_{p2,n}) \\
+	g_{e2,n} = g_{p2,n} + \beta (g_{p1,n} - g_{p2,n}) \\
+	\end{array} \right.
+	\label{eq:GA_mating_as_binary}
+	\end{equation}
+	\noindent
+	where $\beta$ is a random value between 0 and 1.
+
+	\item \textbf{Blending method} \citep{Radcliffe1991}: in this approach, instead of exchanging the genes in between the chromosome after a crossover point, these are combined by linear combination.
+	\begin{equation}
+	\left\lbrace \begin{array}{l} 
+	g_{e1,n} = \beta g_{p1,n} + (1-\beta)g_{p2,n} \\ 
+	g_{e2,n} = (1-\beta) g_{p1,n} + \beta g_{p2,n} \\
+	\end{array} \right.
+	\label{eq:GA_mating_blending_method}
+	\end{equation}
+	\noindent
+
+	%ou $g_{e1,n}$ et $g_{e2,n}$ sont les $n$-ieme gènes des deux enfants, $g_{p1,n}$ et $g_{p2,n}$ ceux des parents, et $\beta$ est un nombre aléatoire entre 0 et 1.
+Pour $\beta = 0.5$, on obtient la moyenne pour cette variable.
+
+\end{itemize}
+
+	\citet{Michalewicz1996} a montré que cette méthode fonctionne bien pour différentes applications.
+Le choix des variables à mélanger peut être fait de différentes manières, par exemple toutes les variables à droite ou à gauche du point de croisement \citep{Haupt2004}.
+Les croisements peuvent également être multiples.
+Les gènes des chromosomes sont alors mélangés en conservant le même $\beta$, ou en le changeant pour chaque gène.
+Ces méthodes produisent des enfants ayant des variables comprises entre les valeurs des parents, sans sortir de cet intervalle.
+
+	\item \textbf{Croisement linéaire} \citep[\textit{linear crossover}]{Wright1991}: afin de permettre aux variables de prendre des valeurs en dehors de l'intervalle défini par les parents, une méthode d'extrapolation est nécessaire.
+Trois enfants sont alors générés à partir des deux parents, selon l'équation \ref{eq:GA_mating_linear_crossover}.
+Il y a donc moins de couples sélectionnés pour compléter la population.
+
+	\begin{equation}
+	\left\lbrace \begin{array}{l} 
+	g_{e1,n} = 0.5 g_{p1,n} + 0.5 g_{p2,n} \\ 
+	g_{e2,n} = 1.5 g_{p1,n} - 0.5 g_{p2,n} \\ 
+	g_{e3,n} = - 0.5 g_{p1,n} + 1.5 g_{p2,n} \\ 
+	\end{array} \right.
+	\label{eq:GA_mating_linear_crossover}
+	\end{equation}
+
+	\newpage
+
+	\item \textbf{Croisement heuristique} \citep[\textit{heuristic crossover},][]{Michalewicz1996}: le croisement heuristique est une variation de ces dernières méthodes, qui calcule les valeurs des nouveaux gènes selon l'équation suivante:
+
+	\begin{equation}
+	\left\lbrace \begin{array}{l} 
+	g_{e1,n} = \beta (g_{p1,n} - g_{p2,n}) + g_{p1,n} \\
+	g_{e2,n} = \beta (g_{p2,n} - g_{p1,n}) + g_{p2,n} \\
+	\end{array} \right.
+	\label{eq:GA_mating_heuristic_crossover}
+	\end{equation}
+
+	\item \textbf{Interpolation linéaire} (\textit{linear interpolation}): au contraire des techniques précédentes, nous ne faisons plus de croisement, mais une interpolation linéaire sur tous les gènes du couple.
+Les enfants sont donc situés sur une ligne connectant les deux parents.
+
+	\begin{equation}
+	\left\lbrace \begin{array}{l} 
+	ind_{e1} = ind_{p1} - \beta (ind_{p1} - ind_{p2}) \\
+	ind_{e2} = ind_{p2} + \beta (ind_{p1} - ind_{p2}) \\
+	\end{array} \right.
+	\label{eq:GA_mating_linear_interpolation}
+	\end{equation}
+	\noindent
+	où $ind_{e1}$ et $ind_{e2}$ sont les individus enfants, $ind_{p1}$ et $ind_{p2}$ les parents, et $\beta$ est une valeur aléatoire entre 0 et 1. $\beta$ est le même pour chaque variable.
+
+	\item \textbf{Interpolation libre} (\textit{free interpolation}): cette technique effectue une interpolation sur chaque gène, tout comme la précédente; mais dans ce cas, le facteur de pondération change pour chaque gène:
+
+	\begin{equation}
+	\left\lbrace \begin{array}{l} 
+	ind_{e1} = ind_{p1} - [\beta_{1} (g_{p1,1} - g_{p2,1}), \beta_{2} (g_{p1,2} - g_{p2,2}), ..., \beta_{Ng} (g_{p1,N_{g}} - g_{p2,N_{g}})] \\
+	ind_{e2} = ind_{p2} + [\beta_{1} (g_{p1,1} - g_{p2,1}), \beta_{2} (g_{p1,2} - g_{p2,2}), ..., \beta_{Ng} (g_{p1,N_{g}} - g_{p2,N_{g}})] \\
+	\end{array} \right.
+	\label{eq:GA_mating_free_interpolation}
+	\end{equation}
+	\noindent
+	où $ind_{e1}$ et $ind_{e2}$ sont les individus enfants, $ind_{p1}$ et $ind_{p2}$ les parents, $N_{g}$ le nombre de gènes, et $\beta_{n}$ sont des valeurs aléatoires (entre 0 et 1) indépendantes.
+
+De multiples autres méthodes ou variantes existent, combinant les avantages de différentes approches.
+La performance des variantes étant liée au problème à traiter, nous ne pouvons pas identifier a priori la meilleure technique pour notre étude.
+
 The combination of strong genes by the operator of chromosomes crossover is theoretically the most important operating mechanism in the conventional GAs \citep{Holland1992b,Back1993b}.

### 2015-01-16 Optimization - Journal of Climate/template.tex
End of the crossover techniques.

--- 2015-01-09 Optimization - Journal of Climate/template.tex
@@
 
+Individuals of the mating pool can reproduce. It begins with the selection of pairs (the parents). The techniques implemented in this work are the following:
+
+\begin{itemize}
+	\item \textbf{Rank pairing}: individuals are gathered in pairs according to their rank (classified on the performance scores).
+Consecutive ranks are put together (odd rows are associated with even rows).
+This approach is easy to achieve, but does not look like a natural process.
+
+	\item \textbf{Random pairing}: two individuals are randomly selected to form a couple, according to a uniform law.
+
+	\item \textbf{Roulette wheel weighting}: the roulette technique refers to gambling.
+But unlike casino roulette, this one is biased.
+Each individual is associated with a sector of the wheel with a certain opening angle, which is its probability of selection \citep{Haupt2004}.
+The probability assigned to the individuals is proportional to their fitness (objective function), so that the most adapted individuals have the greatest probability of reproduction.
+There are two techniques for weighting the individuals of the mating pool:
+	\begin{itemize}
+		\item Roulette wheel weighting on rank: the probability of each individual depends on its rank $n$:
+		\begin{equation}
+		p_{n}=\dfrac{N_{mp}-n+1}{\sum^{N_{mp}}_{n=1}n}
+		\label{equation_mating_rank_weighting}
+		\end{equation}
+
+		\item Roulette wheel weighting on fitness: the selection probability is calculated based on the value of the objective function.
+This approach gives more weight to the best individuals when the distribution of scores is wide, while the weight is almost similar when all individuals have approximately the same score \citep{Haupt2004}.
+The probability $p_{n}$ of each individual is calculated by the equation \ref{equation_mating_score_weighting}:
+		\begin{equation}
+		p_{n}=\frac{score_{n}-score_{N_{mp}}}{\sum_{n=1}^{N_{mp}} (score_{n}-score_{N_{mp}})}
+		\label{equation_mating_score_weighting}
+		\end{equation}
+		In our application, the last individual ($N_{mp}$) has zero probability of being selected.
+	\end{itemize}
+
+	\item \textbf{Tournament selection}: This operator is similar to that used in natural selection, but is applied here for the successive selection of each parent.
+To select a parent, a number of individuals (2 or 3) are randomly picked and the best is kept.
+This operation is performed twice, once for each partner.
+This approach imitates the breeding competition in nature \citep{Haupt2004}.
+\end{itemize}
+
+\subsubsection{Chromosome crossover}
+
+Once the two parents selected for breeding, they combine their chromosomes and produce two children, bringing the number of individuals in the population of $N_{mp}$ back to $N$ (the parents also return back in the total population in order to complement the next generation).
+The combination of chromosomes is carried out using a crossover operator, thereby generating two offspring having characteristics derived from both parents.
+Chromosome crossover widens the search space and favours the combination of strong genes, which can result in more suited children.
+It allows a mixing of genes and accumulation of positive mutations.
+
+The evaluated crossover operators are the following:
+
+\begin{itemize}
+	\item \textbf{Single-point crossover}: a crossover point is randomly chosen for the pair. The genes (our parameters) located after that point are exchanged in between the two chromosomes.
+
+	\item \textbf{Two-point crossover}: works like the single-point crossover, but there are two intersections defining the segments to exchange.
+This approach, which significantly extends the search space for the children, is considered more efficient than the previous \citep{Beasley1993a, Haupt2004}.
+
+	\item \textbf{Multiple-point crossover} \citep{DeJong1975a}: it is a generalization of the previous, with a number of crossover points up to the number of genes.
+
+	\item \textbf{Uniform crossover} \citep{Syswerda1989}: for each gene of the chromosome, it is randomly chosen to exchange or not the values between the parents.
+
+	\item \textbf{Binary-like crossover} \citep{Haupt2004}: chromosome crossover on a binary coding can generate new values for variables located at intersection points, since the crossovers are applied at the bit level, thus often within a gene.
+This is not the case for the floating-point representation, since the crossover is performed between the genes.
+To reproduce the behaviour present in the original algorithms, which introduces new information, \citet{Haupt2004} propose an operator that combines standard crossover with an interpolation approach.
+The genes located after a crossover point are exchanged, but the gene located at the intersection is modified as follows (equation \ref{equation_mating_as_binary}):
+	\begin{equation}
+	\left\lbrace \begin{array}{l} 
+	g_{o1,n} = g_{p1,n} - \beta (g_{p1,n} - g_{p2,n}) \\
+	g_{o2,n} = g_{p2,n} + \beta (g_{p1,n} - g_{p2,n}) \\
+	\end{array} \right.
+	\label{equation_mating_as_binary}
+	\end{equation}
+	where $g_{o1,n}$ and $g_{o2,n}$ are the $n$-th gene of the two new offspring, and $g_{p1,n}$ and $g_{p2,n}$ are those of the two parents. $\beta$ is a random value between 0 and 1.
+
+	\item \textbf{Blending method} \citep{Radcliffe1991a}: in this approach, instead of exchanging the genes in between the chromosomes after one or multiple crossover points, these are combined by linear combination (equation \ref{equation_mating_blending_method}).
+The genes of the parents are blended together using a random value ($\beta$) that can be unique for the whole chromosome, or that can change for every gene.
+The genes of the offspring are bounded by the genes of the parents, no value can be out of their range.
+	\begin{equation}
+	\left\lbrace \begin{array}{l} 
+	g_{o1,n} = \beta g_{p1,n} + (1-\beta)g_{p2,n} \\ 
+	g_{o2,n} = (1-\beta) g_{p1,n} + \beta g_{p2,n} \\
+	\end{array} \right.
+	\label{equation_mating_blending_method}
+	\end{equation}
+
+	\item \textbf{Linear crossover} \citep{Wright1991a}: in order to allow the genes to take values outside the interval defined by the parents, a method of extrapolation is necessary.
+Linear crossover introduces such an approach, and produces three children from two parents, following equation \ref{equation_mating_linear_crossover}.
+Less couples are required in order to fill up the generation.
+	\begin{equation}
+	\left\lbrace \begin{array}{l} 
+	g_{o1,n} = 0.5 g_{p1,n} + 0.5 g_{p2,n} \\ 
+	g_{o2,n} = 1.5 g_{p1,n} - 0.5 g_{p2,n} \\ 
+	g_{e3,n} = - 0.5 g_{p1,n} + 1.5 g_{p2,n} \\ 
+	\end{array} \right.
+	\label{equation_mating_linear_crossover}
+	\end{equation}
+
+	\item \textbf{Heuristic crossover} \citep{Michalewicz1996}: it is a variation of the latter methods that relies on the following equation:
+	\begin{equation}
+	\left\lbrace \begin{array}{l} 
+	g_{o1,n} = \beta (g_{p1,n} - g_{p2,n}) + g_{p1,n} \\
+	g_{o2,n} = \beta (g_{p2,n} - g_{p1,n}) + g_{p2,n} \\
+	\end{array} \right.
+	\label{equation_mating_heuristic_crossover}
+	\end{equation}
+
+	\item \textbf{Linear interpolation}: unlike previous techniques, this technique does not rely on crossover points, but on a linear interpolation on every gene of the couple (equation \ref{equation_mating_linear_interpolation}).
+	\begin{equation}
+	\left\lbrace \begin{array}{l} 
+	c_{o1} = c_{p1} - \beta (c_{p1} - c_{p2}) \\
+	c_{o2} = c_{p2} + \beta (c_{p1} - c_{p2}) \\
+	\end{array} \right.
+	\label{equation_mating_linear_interpolation}
+	\end{equation}
+	where $c_{o1}$ and $c_{o2}$ are the full chromosomes of the offspring, and $c_{p1}$ an $c_{p2}$ are the ones of the parents.
+As before, $\beta$ is a random value between 0 and 1, and is here the same for every gene.
+
+	\item \textbf{Free interpolation}: this technique performs interpolation on each gene, like the previous one; but in this case, the weighting factor changes for each gene:
+	\begin{equation}
+	\left\lbrace \begin{array}{l} 
+	c_{o1} = c_{p1} - [\beta_{1} (g_{p1,1} - g_{p2,1}), \beta_{2} (g_{p1,2}\\
+	~~~~~~~~~~~~ - g_{p2,2}), ..., \beta_{Ng} (g_{p1,N_{g}} - g_{p2,N_{g}})] \\
+	c_{o2} = c_{p2} + [\beta_{1} (g_{p1,1} - g_{p2,1}), \beta_{2} (g_{p1,2}\\
+	~~~~~~~~~~~~ - g_{p2,2}), ..., \beta_{Ng} (g_{p1,N_{g}} - g_{p2,N_{g}})] \\
+	\end{array} \right.
+	\label{equation_mating_free_interpolation}
+	\end{equation}
+	where $N_{g}$ is the number of genes, and $\beta$ is here independent between the genes.
+
+\end{itemize}
+
+Many other methods or variations exist, combining the advantages of different approaches.
+The performance of the variants being related to the problem to be addressed, we can not identify a priori the best technique for our application.
+
+\subsubsection{Mutation}
+
 The combination of strong genes by the operator of chromosomes crossover is theoretically the most important operating mechanism in the conventional GAs \citep{Holland1992b,Back1993b}.

### 2015-01-16 Optimization - Journal of Climate/template.tex
Mutation operator under writing.

@@
 
+The mutation operator is a direct modification of genes.
+In a binary coding, it is implemented as an inversion of one bit in a chromosome, while in real coding, it is done by changing the value of a gene.
+Mutations add diversity to the population and prevent a freeze of the evolution, or a genetic drift to a local optimum.
+Thus, it makes the convergence to the global optimum theoretically possible \citep{Beasley1993a}, as they allow exploring beyond the current region of the variable space.
+They therefore help prevent the algorithm to converge too quickly to a local optimum and bring new characteristics that were not present in the original population \citep{Haupt2004}.
+
+The evaluated and developed mutation operators are the following:
+
+\begin{itemize}
+	\item \textbf{Uniform mutation}: The mutation rate is constant and equal for every gene of each individual; they all have the same probability to mutate.
+When a gene is selected for mutation, a new random value is assigned, according to a uniform law.
+
+	\item \textbf{Uniform variable mutation} \citep{Fogarty1989}: a variable mutation rate over the generations was first suggested by \citet{Holland1992b} and evaluated by \citet{Fogarty1989}.
+It improved significantly the performance of GAs.
+In most applications, the mutation rate decreases with the generations, in a deterministic and global (for all individuals) manner \citep{Back1992b}.
+Its optimum configuration depends on the size of the chromosomes, of the properties of the objective function, and of the population size \citep{Back1992b}.
+We implemented this operator according to equation \ref{equation_mutation_uniformvariable}.
+	\begin{equation}
+	p_{n,G} = p_{G_{0}}+\left( \dfrac{p_{G_{0}}-p_{G_{m,p}}}{G_{m,p}} \right) min\left\lbrace G,G_{m,p}\right\rbrace 
+	\label{equation_mutation_uniformvariable}
+	\end{equation}
+	where $p_{n,G}$ is the mutation rate (probability) of the gene $n$ for generation number $G$, $G_{m,p}$ is the maximum number of generations during which the mutation rate varies.
+$p_{G_{0}}$ is the initial mutation probability, and $p_{G_{m,p}}$ is the final one.
+$p_{G_{0}}$, $p_{G_{m,p}}$ and $G_{m,p}$ are the three controlling parameters of the operator.
+The evolution of the mutation rate is linear.
+
+	\item \textbf{Constant normal mutation}: many users use a normal distributions to generate new values. The gene $g$ that mutate becomes:
+	\begin{equation}
+	g' = N(g,\sigma^{2})
+	\label{equation_mutating_normal_distribution}
+	\end{equation}
+	where $\sigma$ is the standard deviation of the distribution.
+The disadvantage of this technique is that an accurate value of $\sigma$ must be chosen \citep{Haupt2004}, which is impossible to know beforehand.
+
+\end{itemize}
+
+	\item \textbf{Mutation normale variable}: selon la même logique que la mutation uniforme variable, nous avons établi un opérateur de mutation utilisant une distribution normale avec un taux de mutation et un écart-type variables.
+Le taux de mutation est calculé par l'équation \ref{equation_utation_uniformvariable}.
+Sur ce même principe, nous faisons varier linéairement (diminution avec le nombre de générations) l'écart-type au fil des générations:
+
+	\begin{equation}
+	\sigma_{n,G} = \sigma_{G_{0}}+\left( \dfrac{\sigma_{G_{0}}-\sigma_{G_{m,sdev}}}{G_{m,sdev}} \right) min\left\lbrace G,G_{m,sdev}\right\rbrace 
+	\label{equation_mutation_normalvariable}
+	\end{equation}
+	\noindent
+	où $\sigma_{n,G}$ est l'écart type du gène $n$ à la génération $G$, $\sigma_{G_{0}}$ est l'écart type de départ, $\sigma_{G_{m,sdev}}$ est l'écart type final, $G_{m,sdev}$ le nombre maximum de générations durant lesquelles l'écart type varie.
+$p_{G_{0}}$, $p_{G_{m,p}}$, $G_{m,p}$, $\sigma_{G_{0}}$, $\sigma_{G_{m,sdev}}$ et $G_{m,sdev}$ sont les six paramètres de la méthode.
+
+	\item \textbf{Mutation non uniforme} \citep[\textit{non-uniform mutation},][]{Michalewicz1996}: lorsqu'un gène est sélectionné pour muter, un déplacement aléatoire lui est appliqué selon les lois suivantes.
+Deux nombres aléatoires, $r_{1}$ déterminant la direction du déplacement et $r_{2}$ sa magnitude, sont tirés selon une loi uniforme dans le domaine [0,1].
+La nouvelle valeur du gène est donnée par l'équation suivante:
+
+	\begin{equation}
+	g_{n}^{'} = 
+	\left\lbrace \begin{array}{l l} 
+	g_{n} + \left(b_{n}-g_{n}\right) r_{2} \left(1 - \dfrac{G}{G_{max}} \right)^{2} & si \; r_{1} < 0.5 \\
+	g_{n} - \left(g_{n}-a_{n}\right) r_{2} \left(1 - \dfrac{G}{G_{max}} \right)^{2} & si \; r_{1} \geq 0.5 \\
+	\end{array} \right.
+	\label{equation_mutation_nonuniform_original}
+	\end{equation}
+	\noindent
+	où $a_{n}$ est la borne inférieure du $n$-ième gène, $b_{n}$ sa borne supérieure, $G$ la génération actuelle, $G_{max}$ le nombre maximum de générations.
+
+	Nous avons adapté cet opérateur à notre application, qui ne se base pas sur un nombre de générations prédéfini:
+
+	\begin{equation}
+	g_{n}^{'} = 
+	\left\lbrace \begin{array}{l l} 
+	g_{n} + \left(b_{n}-g_{n}\right) r_{2} \left(1 - \min \left\lbrace \dfrac{G}{G_{m,r}}, 1 \right\rbrace \left(1-\omega\right) \right)^{2} & si \; r_{1} < 0.5 \\
+	g_{n} - \left(g_{n}-a_{n}\right) r_{2} \left(1 - \min \left\lbrace \dfrac{G}{G_{m,r}}, 1 \right\rbrace \left(1-\omega\right) \right)^{2} & si \; r_{1} \geq 0.5 \\
+	\end{array} \right.
+	\label{equation_mutation_nonuniform}
+	\end{equation}
+	\noindent
+	où $G_{m,r}$ est le nombre maximum de générations durant lesquelles l'amplitude de la recherche varie, et $\omega$ un seuil choisi par l'utilisateur afin de conserver un rayon de recherche minimum lorsque $G>G_{m,r}$ .
+
+	Lors des premières générations, le domaine d'exploration couvre tout l'espace des paramètres.
+En revanche, ce domaine se réduit au fil des générations, permettant une exploitation des solutions locales.
+
+	\item \textbf{Taux de mutation adaptatif individuel} \citep[\textit{adaptative mutation rate},][]{Back1992}: s'inspirant des techniques de stratégies d'évolution \citep[\textit{Evolution Strategies}, voir][]{Rechenberg1973, Schwefel1981}, \citet{Back1992} introduit une notion d'auto-adaptation aux algorithmes génétiques.
+Le principe est de distribuer des paramètres de contrôle de l'optimisation dans les individus eux-mêmes, et donc de décentraliser partiellement le contrôle de l'évolution, ce qui a pour but de réduire la paramétrisation des AGs et de permettre aux algorithmes de s'autogérer.
+Pour ce faire, la première méthode consiste en l'introduction d'un taux de mutation par individu.
+Lors de chaque mutation, le taux lui-même mute selon sa propre probabilité \citep{Back1992}.
+Puis l'éventuel nouveau taux est utilisé pour muter individuellement les gènes de l'individu.
+Ainsi, lorsque ce taux diminue, il aura moins de chance d'être lui-même muté.
+Les mutations sont effectuées selon une distribution uniforme constante.
+Nous avons choisi ici de ne pas altérer ce taux de mutation lors des opérations de reproduction.
+
+	Cette approche est proche des phénomènes naturels d'adaptation.
+Une population moins bien adaptée à son environnement évolue en effet plus rapidement qu'une population mieux adaptée.
+Ainsi, dans notre application, un individu mal adapté ayant une probabilité de mutation trop faible sera vite dépassé par les autres membres de la population et tendrait à disparaître.
+Au contraire, lorsque la population commence à converger, un taux de mutation trop important est néfaste, et l'individu concerné risque de se dégrader rapidement.
+
+	Les taux de mutation initiaux sont tirés aléatoirement \citep{Back1992} et la méthode n'a aucun paramètre.
+D'autres approches existent pour introduire une auto-adaptation \citep[voir p.ex.][]{Smith1997,Deb1999,Deb2001}.
+
+	\item \textbf{Rayon de recherche adaptatif individuel}: en nous inspirant de la mutation non uniforme, nous introduisons un rayon de recherche dans l'approche du taux de mutation adaptatif individuel.
+Ce rayon de recherche $r_{a}$, borné entre 0 et 1, est également adaptatif et se comporte de manière similaire au taux de mutation adaptatif.
+Dans le but de dissocier son évolution de celle du taux de mutation, sa propre valeur est considérée dans un premier temps comme taux d'auto-mutation pour éventuellement muter avant d'être utilisée comme rayon de recherche normalisé.
+La valeur d'un gène après mutation est donnée par la formule suivante, qui est une simplification de la mutation non uniforme:
+
+	\begin{equation}
+	g_{n}^{'} = 
+	\left\lbrace \begin{array}{l l} 
+	g_{n} + \left(b_{n}-g_{n}\right) r_{2} r_{a} & si \; r_{1} < 0.5 \\
+	g_{n} - \left(g_{n}-a_{n}\right) r_{2} r_{a} & si \; r_{1} \geq 0.5 \\
+	\end{array} \right.
+	\label{equation_mutation_rayon_adaptatif}
+	\end{equation}
+	\noindent
+	où $r_{1}$ et $r_{2}$ sont tirés aléatoirement, de la même manière que pour la mutation non uniforme. Aucun paramètre externe n'est donc nécessaire.
+
+	\item \textbf{Chromosome de taux de mutation adaptatifs} \citep[\textit{n adaptative mutation rate},][]{Back1992}: de manière analogue au taux de mutation adaptatif individuel, cette approche laisse le contrôle de la vitesse d'évolution aux individus eux-mêmes.
+La différence est ici que chaque gène a un taux de mutation propre.
+Le principal avantage est que le réglage de la mutation peut se faire beaucoup plus finement \citep{Smith1997}.
+Nous considérons donc un second chromosome contenant les taux de mutation correspondant à chaque gène du chromosome de base.
+Nous choisissons l'approche de \citet{Magnin2006}, qui est de considérer les chromosomes en parallèle plutôt que de les concaténer.
+
+	Le fonctionnement de la mutation et de l'auto-mutation est similaire au cas du taux de mutation adaptatif individuel, mais de manière distribuée dans le chromosome.
+Une autre différence est que nous appliquons ici les mêmes opérations de croisement que celles que subissent les gènes du chromosome de base, et ceci pour les mêmes points de croisement.
+Ainsi, lors d'un échange de gènes, les enfants héritent également des taux de mutation propres à chacun de ces gènes.
+
+	\item \textbf{Chromosome de rayons de recherche adaptatifs}: cet opérateur combine les fonctionnements du chromosome de taux de mutation adaptatifs et du rayon de recherche adaptatif.
+De manière analogue, l'individu possède 3 chromosomes, le premier contenant les valeurs à optimiser, le second les taux de mutation distribués, et le dernier les rayons de recherche distribués.
+À nouveau, aucun paramètre externe n'est requis.
+
+	\item \textbf{Mutation multi-échelles}: en nous inspirant de la mutation non uniforme, nous proposons une approche également basée sur un rayon de recherche, celui-ci n'étant cependant pas décroissant avec le temps.
+Il est en effet difficile d'anticiper la vitesse de convergence et donc de paramétrer la mutation non uniforme.
+Le rayon de recherche $r_{a}$ de l'équation \ref{equation_mutation_rayon_adaptatif} est ici tiré aléatoirement, pour chaque individu, entre 4 valeurs équiprobables: 1, 0.5, 0.1, 0.02.
+Ainsi, l'évolution des individus est un mélange d'exploration et d'exploitation au lieu d'être une transition de l'un à l'autre.
+Le seul paramètre externe est le taux de mutation qui est fixe.
+	\vspace{2mm}
+
+Lorsque le gène à muter est représenté par une liste d'éléments distincts (p.ex.
+variable ou niveau atmosphérique, ou critère d'analogie), un tirage d'une nouvelle valeur selon une distribution uniforme est toujours utilisé.
+Il ne fait en effet pas sens d'utiliser des opérateurs fonctionnant sur des principes de proximité lorsque celle-ci n'existe pas.
+
 \subsection{Implementation and contraints}

### 2015-01-19 Optimization - Journal of Climate/template.tex
End of the operators description.

--- 2015-01-16 Optimization - Journal of Climate/template.tex
@@
 
+The mutation operator is a direct modification of genes.
+In a binary coding, it is implemented as an inversion of one bit in a chromosome, while in real coding, it is done by changing the value of a gene.
+Mutations add diversity to the population and prevent a freeze of the evolution, or a genetic drift to a local optimum.
+Thus, it makes the convergence to the global optimum theoretically possible \citep{Beasley1993a}, as they allow exploring beyond the current region of the variable space.
+They therefore help prevent the algorithm to converge too quickly to a local optimum and bring new characteristics that were not present in the original population \citep{Haupt2004}.
+
+The evaluated and developed mutation operators are the following:
+
+\begin{itemize}
+	\item \textbf{Uniform mutation}: The mutation rate is constant and equal for every gene of each individual; they all have the same probability to mutate.
+When a gene is selected for mutation, a new random value is assigned, according to a uniform law.
+
+	\item \textbf{Variable uniform mutation} \citep{Fogarty1989}: a variable mutation rate over the generations was first suggested by \citet{Holland1992b} and evaluated by \citet{Fogarty1989}.
+It improved significantly the performance of GAs.
+In most applications, the mutation rate decreases with the generations, in a deterministic and global (for all individuals) manner \citep{Back1992b}.
+Its optimum configuration depends on the size of the chromosomes, of the properties of the objective function, and of the population size \citep{Back1992b}.
+We implemented this operator according to equation \ref{equation_mutation_uniformvariable}.
+	\begin{equation}
+	p_{n,G} = p_{G_{0}}+\left( \dfrac{p_{G_{0}}-p_{G_{m,p}}}{G_{m,p}} \right) min\left\lbrace G,G_{m,p}\right\rbrace 
+	\label{equation_mutation_uniformvariable}
+	\end{equation}
+	where $p_{n,G}$ is the mutation rate (probability) of the gene $n$ for generation number $G$, $G_{m,p}$ is the maximum number of generations during which the mutation rate varies.
+$p_{G_{0}}$ is the initial mutation probability, and $p_{G_{m,p}}$ is the final one.
+$p_{G_{0}}$, $p_{G_{m,p}}$ and $G_{m,p}$ are the three controlling parameters of the operator.
+The evolution of the mutation rate is linear.
+
+	\item \textbf{Constant normal mutation}: many users use a normal distributions to generate new values. The gene $g$ that mutate becomes:
+	\begin{equation}
+	g' = N(g,\sigma^{2})
+	\label{equation_mutating_normal_distribution}
+	\end{equation}
+	where $\sigma$ is the standard deviation of the distribution.
+The disadvantage of this technique is that an accurate value of $\sigma$ must be chosen \citep{Haupt2004}, which is impossible to know beforehand.
+
+	\item \textbf{Variable normal mutation}: with the same logic that the variable uniform mutation, we tested a mutation operator using a normal distribution with a variable mutation rate and standard deviation.
+The mutation rate is calculated with equation \ref{equation_mutation_uniformvariable}.
+On the same principle, we decrease linearly the standard deviation over the generations:
+	\begin{equation}
+	\sigma_{n,G} = \sigma_{G_{0}}+\left( \dfrac{\sigma_{G_{0}}-\sigma_{G_{m,\sigma}}}{G_{m,\sigma}} \right) min\left\lbrace G,G_{m,\sigma}\right\rbrace 
+	\label{equation_mutation_normalvariable}
+	\end{equation}
+	where $\sigma_{n,G}$ is the standard deviation of gene $n$ et generation number $G$, $\sigma_{G_{0}}$ is the initial standard deviation, $\sigma_{G_{m,\sigma}}$ is the final standard deviation, $G_{m,\sigma}$ is the maximum number of generations during which the standard deviation varies.
+$p_{G_{0}}$, $p_{G_{m,p}}$, $G_{m,p}$, $\sigma_{G_{0}}$, $\sigma_{G_{m,\sigma}}$ and $G_{m,\sigma}$ are the six parameters of the method.
+
+	\item \textbf{Non-uniform mutation} \citep{Michalewicz1996}: two random numbers are picked based on a uniform law: $r_{1}$, which determines the direction of the change, and $r_{2}$, which determines its magnitude.
+The new value of the gene is given by the following equation:
+	\begin{equation}
+	g_{n}^{'} = 
+	\left\lbrace \begin{array}{l l} 
+	g_{n} + \left(b_{n}-g_{n}\right) r_{2} \left(1 - \dfrac{G}{G_{m}} \right)^{2} & if \; r_{1} < 0.5 \\
+	g_{n} - \left(g_{n}-a_{n}\right) r_{2} \left(1 - \dfrac{G}{G_{m}} \right)^{2} & if \; r_{1} \geq 0.5 \\
+	\end{array} \right.
+	\label{equation_mutation_nonuniform_original}
+	\end{equation}
+	where $a_{n}$ is the is the lower bound of the $n$-th gene, $b_{n}$ its upper bound, $G$ the present generation, and $G_{m}$ the maximum number of generations.
+
+	We adapted this operator for our application, which is not based on a predefined number of generations:
+	\begin{equation}
+	g_{n}^{'} = 
+	\left\lbrace \begin{array}{l l} 
+	g_{n} + \left(b_{n}-g_{n}\right) r_{2} \left(1 - \min \left\lbrace \dfrac{G}{G_{m,r}}, 1 \right\rbrace \left(1-\omega\right) \right)^{2} & if \; r_{1} < 0.5 \\
+	g_{n} - \left(g_{n}-a_{n}\right) r_{2} \left(1 - \min \left\lbrace \dfrac{G}{G_{m,r}}, 1 \right\rbrace \left(1-\omega\right) \right)^{2} & if \; r_{1} \geq 0.5 \\
+	\end{array} \right.
+	\label{equation_mutation_nonuniform}
+	\end{equation}
+	where $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a threshold chosen by the user to maintain a minimum search radius when $G>G_{m,r}$.
+During the first generations, the exploration extent covers the entire parameters space.
+However, this area is reduced over generations, allowing exploitation of local solutions.
+
+	\item \textbf{Individual adaptive mutation rate} \citep{Back1992a}: based on the ides of Evolution Strategies \citep[see][]{Rechenberg1973, Schwefel1981}, \citet{Back1992a} introduced a concept of self-adaptive genetic algorithms.
+The idea is to distribute control parameters within individuals themselves, which partially decentralize control of the evolution.
+It allows reducing the parameterization of GAs and introducing a notion of self-management.
+The first approach is the introduction of a mutation rate per individual, that mutates itself under its own probability \citep{Back1992a}.
+Then, the eventual new rate is used to mutate the genes of the individual.
+Thus, as this rate decreases, it will have less probability of being itself mutated.
+This approach is close to the natural adaptation phenomena.
+A population less suited to its environment is changing faster than better adapted population.
+Mutations are performed according to a constant uniform distribution.
+The initial mutation rates are randomly chosen \citep{Back1992a} and the method has no parameter.
+Other approaches exist to introduce a self-adaptation \citep[see][]{Smith1997a,Deb1999,Deb2001a}.
+
+	\item \textbf{Individual adaptive search radius} \citep{Horton2012}: based on the ideas of the non-uniform mutation, we introduce a search radius in the approach of individual adaptive mutation rates.
+This search radius $r_{a}$, bounded between 0 and 1, is also adaptive and behaves similarly to the adaptive mutation rates.
+In order to separate its evolution to the one of the mutation rate, its own value is considered initially as a self-mutation rate to eventually mutate before being used as a normalized search radius.
+The value of a mutated gene is given by the following equation, which is a simplification of the non-uniform mutation:
+	\begin{equation}
+	g_{n}^{'} = 
+	\left\lbrace \begin{array}{l l} 
+	g_{n} + \left(b_{n}-g_{n}\right) r_{2} r_{a} & if \; r_{1} < 0.5 \\
+	g_{n} - \left(g_{n}-a_{n}\right) r_{2} r_{a} & if \; r_{1} \geq 0.5 \\
+	\end{array} \right.
+	\label{equation_mutation_rayon_adaptatif}
+	\end{equation}
+	where $r_{1}$ and $r_{2}$ are randomly selected, in the same way as for the non-uniform mutation. No external parameter is therefore necessary.
+
+	\item \textbf{Chromosome of adaptive mutation rate} \citep[\textit{n adaptative mutation rate},][]{Back1992a}: analogously to the individual adaptive mutation rate, this approach leaves the control of the evolution rate to the individuals themselves.
+The difference here is that each gene has a specific mutation rate.
+The main advantage is that the tuning of the mutation can be much more precise \citep{Smith1997a}.
+We therefore consider a second chromosome containing the mutation rate for each gene of the first chromosome.
+The operations of mutation and self-mutation are similar to the case of the individual adaptive mutation rate, but in a distributed way, within the chromosome.
+Another difference is that we apply the same crossover operations as those applied to the first chromosome, and this for the same crossing points.
+Thus, during an exchange of genes, children also inherit the mutation rates specific for each of these genes.
+
+	\item \textbf{Chromosome of adaptive search radius} \citep{Horton2012}: we introduced this operator that combines the operations of the chromosome of adaptive mutation rate to our adaptive search radius approach.
+Similarly, an individual has 3 chromosomes: the first containing the values to be optimized, the second containing the distributed mutation rate, and the last one, the distributed search radius.
+Again, no external parameters are required.
+
+	\item \textbf{Multi-scale mutation} \citep{Horton2012}: finally, we developed another approach, that is also based on the search radius concept.
+However, the latter is not decreasing with time.
+Methods based on a reduction of the mutation rate or radius simulate a transition from the exploration phase to the exploitation one.
+The idea is consistent as long as we are confident that the algorithm will converge towards the global optimum.
+Indeed, one the algorithm is in the exploitation mode, it is very unlikely to go out of the minima it converges to.
+We wanted to test an approach that combines both exploration and exploitation during the whole optimization.
+Thus, we considered the search radius $r_{a}$ of equation \ref{equation_mutation_rayon_adaptatif} as a random value for each individual, but restricted to 4 equiprobable values: 1, 0.5, 0.1, 0.02.
+The only external parameter is the mutation rate which is fixed.
+
+\end{itemize}
+
+When the gene to mutate is represented by a list of distinct values (eg meteorological variable or analogy criterion), the random choice of a new value is always based on a uniform distribution, without notion of search radius.
+There is indeed no meaning to use operators based on principles of proximity when the latter does not exist.
+
+\subsubsection{Elitism}
+
+We used a process of elitism on natural selection as well as on mutations.
+This ensures the survival of the best individual so that we do not lose a better solution.
+This approach is very common in the field of GAs \citep{Haupt2004}.
+After the natural selection operator, if the best individual has not been selected, it is copied to the mating pool instead of an individual randomly picked.
+After mutation, if the best individual has mutated and if its new version has a lower score than the original, the latter is reinserted instead of an individual randomly chosen.
+
+\subsubsection{Ending the optimization}
+
+The convergence check determines whether the solution is acceptable and if the algorithm may stop.
+The stopping criteria are not often well documented in GAs case studies \citep{Haupt2004}.
+We chose to stop the optimization if the best individual does not change for $x$ generations.
+This value should not be too low to allow the algorithm to escape from a local minimum.
+In addition, the rate of improvement decreases with the progression of the optimization.
+It is thus common that the best individual does not evolve over generations when we get closer to the global solution.
+
 \subsection{Implementation and contraints}

### 2015-01-23 Optimization - Journal of Climate/template.tex
Comparison of the operators.

@@
 % DOUBLE-SPACED VERSION FOR SUBMISSION TO THE AMS
-\documentclass{ametsoc}
+%\documentclass{ametsoc}
 
 % TWO-COLUMN JOURNAL PAGE LAYOUT---FOR AUTHOR USE ONLY
-% \documentclass[twocol]{ametsoc}
+ \documentclass[twocol]{ametsoc}
 
@@
 The only option is to try systematically every combination, which may be acceptable for no more than 2 levels.
-However, \citet{Horton2012} showed that additional atmospheric levels may improve the method.
+However, \citet{Horton2012a} showed that additional atmospheric levels may improve the method.
 
@@
 Even the choice of the atmospheric level and the temporal window should be reconsidered, when not the variable itself.
-For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012} found no interest in this variable in an Alpine environment, because the vertical velocity is mainly related to the orographic effect, and was thus already well related to the atmospheric circulation itself.
+For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012a} found no interest in this variable in an Alpine environment, because the vertical velocity is mainly related to the orographic effect, and was thus already well related to the atmospheric circulation itself.
 So, when adapting the analogue method to a new region, we should assess systematically every combination of atmospheric levels, time and spatial windows, which is an intensive task.
@@
 
-\citet{Horton2012} assessed the ability of the \citep{Nelder1965a} method based on a simplex approach.
+\citet{Horton2012a} assessed the ability of the \citep{Nelder1965a} method based on a simplex approach.
 This technique didn't provide satisfying results and failed at identifying the global optimum.
@@
 $N$ must allow sufficient sampling of the solutions field \citep{Beasley1996a}, and should thus vary as a function of chromosome size (ie the number of parameters to be optimized).
-In our application, we found the following ranges to be accurate in average:
-
-\begin{itemize}
-	\item $50<N<100$ for a very simple implementation of the analogue method (1 level of analogy with 2 atmospheric levels),
-
-	\item $N\approx200$ for a bit more complex method (1 level of analogy with 4 atmospheric levels, or 2 level of analogy with less atmospheric levels),
-
-	\item $N\approx500$ for significantly more complex methods (2-3 levels of analogy with 4 atmospheric levels for the atmospheric circulation, and 2 to 4 levels for the analogy humidity),
-\end{itemize}
-
-We didn't find any improvement with $N>500$, the results were even surprisingly of a lower quality.
-However, this cannot be generalized and depends on the analogue method to optimize, and supposedly on the characteristics of the processes generating the precipitations in a given region.
 
@@
 
-	\item \textbf{Individual adaptive search radius} \citep{Horton2012}: based on the ideas of the non-uniform mutation, we introduce a search radius in the approach of individual adaptive mutation rates.
+	\item \textbf{Individual adaptive search radius} \citep{Horton2012a}: based on the ideas of the non-uniform mutation, we introduce a search radius in the approach of individual adaptive mutation rates.
 This search radius $r_{a}$, bounded between 0 and 1, is also adaptive and behaves similarly to the adaptive mutation rates.
@@
 
-	\item \textbf{Chromosome of adaptive search radius} \citep{Horton2012}: we introduced this operator that combines the operations of the chromosome of adaptive mutation rate to our adaptive search radius approach.
+	\item \textbf{Chromosome of adaptive search radius} \citep{Horton2012a}: we introduced this operator that combines the operations of the chromosome of adaptive mutation rate to our adaptive search radius approach.
 Similarly, an individual has 3 chromosomes: the first containing the values to be optimized, the second containing the distributed mutation rate, and the last one, the distributed search radius.
@@
 
-	\item \textbf{Multi-scale mutation} \citep{Horton2012}: finally, we developed another approach, that is also based on the search radius concept.
+	\item \textbf{Multi-scale mutation} \citep{Horton2012a}: finally, we developed another approach, that is also based on the search radius concept.
 However, the latter is not decreasing with time.
@@
 It is thus common that the best individual does not evolve over generations when we get closer to the global solution.
+We chose a value of $x=20$ generations.
 
 \subsection{Implementation and contraints}
-...
+
+Some constraints need to be taken into account.
+For example, when a crossover or a mutation operation resulted in a parameter value standing out of the authorized bounds, it had to be brought back within the limits.
+Moreover, the parameters are of different nature: some are continuous, such as the weight, some are discretized, such as the analogues number, or the spatial windows, and finally, some are independent elements in an array, such as the choice of the meteorological variable.
+New values resulting from the optimizer needs to respect the type of data it represents.
+
+Other constraints exist in between the parameters, such as the atmospheric level of the humidity flux that has to be consistent in between the relative humidity and the two wind components.
+Another example is the weighting of the different atmospheric levels which has to be normalized.
+
+GAs are very computationally intensive because they require many evaluations of the objective function.
+These assessments are very long in our application, as they require calculating and assessing a forecast for every day of the calibration period.
+In order to reduce the computation time, we avoid recalculating the score of an individual who has previously been evaluated and that has not changed.
+We keep the score of each individual living in the selection until it mutates.
+
+The assessment (calculation of the objective function) of each member of the population of a generation is completely independent and can be performed in parallel on different processors of a computer \citep{Haupt2004, Alliot2005}.
+We implemented this technique and the resulting time savings was very important.
+In order to perform optimizations for multiple time series, the use of a cluster is a necessity, which our code allows.
 
 \subsection{Recommendations of parameterization}
-...
+
+The GAs parameterization, such as the mutation rate, population size, natural selection options, and so on, is difficult given the high number of existing variants, each developed for a specific problem \citep{Haupt2004, Costa2007a}.
+This parameterization depends on the objective function, implementation variants, the bounds of variables to be optimized, and performance indicators.
+Thus, different studies suggest very different parameterization.
+
+A key element of the parameterization of GAs is finding the right balance between exploration and exploitation \citep{Back1992a, Smith1997a}.
+Exploration is characterized by a relatively high probability to assess the regions of the parameters space that have not yet been visited.
+This probability must be sufficiently large at the beginning of the optimization, so that the algorithm is capable of identifying the region where the global optimum is located.
+Exploitation is characterized by a local search in an area of interest, and generally makes small movements.
+The latter is interesting to refine the results at the end of the optimization.
+
+\citet{DeJong1975a} and \citet{Grefenstette1986} compared different implementations and parameterizations of GAs on functions of varying complexity.
+They observed that a small population size improves the initial performance, while a large population improves long-term performance; the size of the population should be selected between 50 and 100.
+They also observed that the ratio of the population to keep for the mating pool is around 50\% (45\% to 60\%).
+
+Values of the mutation rate varies broadly between the studies: from 0.001 \citep{DeJong1975a} to 0.2 \citet{Haupt2004}.
+\citet{Back1996b} showed that mutation rates higher than the usual ranges are more optimal at the beginning of optimization, allowing further exploration.
+The combination of a small population and a high mutation rate works best for the first generations \citep{DeJong1975a, Back1996b, Haupt2004}, but as we could observe, it does not guarantee the quality of the final result.
+Incremental approaches with varying mutation rates are certainly more optimal but more complex to implement \citep{Back1996a, Back1996b}.
+
+\subsubsection{Comparison process and results}
+
+One of our goals being to make recommendations of parameterization for optimization of the analogue method, proceeded systematically.
+The results are summarized hereafter \citep[see][for the details]{Horton2012a}.
+We used concepts from the factorial design approach \citep[see eg.][]{Costa2005,Costa2007,Mariano2010}, which is sometimes used for comparative analysis of different parameterizations of GAs.
+We processed by stages, analyzing in details and in a systematic way every variants of the implemented operators, in combination with multiple other options and parameters in order to take into account eventual co-dependencies.
+
+In order to evaluate a combination of operators/options, we processed 10 optimizations for one parameterization of GAs. The performances were characterized by four indicators:
+
+\begin{itemize}
+	\item mean score: average of the final scores of the 10 optimizations,
+	\item convergence: the number of optimizations that converged to a supposed global optimum,
+	\item number of generations: characterization of the convergence speed,
+	\item number of evaluations of the objective function: characterization of the required calculation time (more realistic than the number of generations).
+\end{itemize}
+
+This comparison required tens of thousands of optimizations that were performed on a cluster of the University of Lausanne. The results, detailed in \citet{Horton2012a} are synthesized hereafter:
+
+\begin{itemize}
+	\item \textbf{Population size}: we found the following ranges to be accurate in average:
+	\begin{itemize}
+		\item $50<N<100$ for a very simple implementation of the analogue method (1 level of analogy with 2 atmospheric levels),
+
+		\item $N\approx200$ for a bit more complex method (1 level of analogy with 4 atmospheric levels, or 2 level of analogy with less atmospheric levels),
+
+		\item $N\approx500$ for significantly more complex methods (2-3 levels of analogy with 4 atmospheric levels for the atmospheric circulation, and 2 to 4 levels for the analogy humidity),
+	\end{itemize}
+	We didn't find any improvement with $N>500$, the results were even surprisingly of a lower quality.
+However, this cannot be generalized and depends on the analogue method to optimize, and supposedly on the characteristics of the processes generating the precipitations in a given region.
+
+	\item \textbf{Natural selection}: this operator has no significant influence, and both tested implementations work fine.
+
+	\item \textbf{Selection of couples}: 6 variants of the couples selection were assessed.
+The performance of these variants are relatively close, both in terms of score, convergence, and number of evaluations.
+The random pairing performed the most poorly, when the tournament selection with 3 candidates is slightly superior.
+The roulette wheel weighting is not far behind, but it is less effective in terms of convergence and number of evaluations.
+This operator has not a significant role in our application.
+
+	\item \textbf{Chromosomes crossover}: we compared 21 different options of the crossover operators.
+This analysis revealed some slightly better options, some bad ones, and many averages.
+Among the bad operators, we find first the heuristic crossover, which is also more demanding in number of evaluations, as well as the linear crossover.
+Binary-like crossovers (especially with 2 points of intersection, whether $\beta$ is shared or not) are significantly better than the others, especially in terms of convergence.
+The two points crossover is relatively close.
+Other operators can be considered usable, yet may not be optimal.
+Once again, this operator is not the key of the GAs parameterization.
+
+	\item \textbf{Mutation}: we compared the 10 mutation operators with different options, bringing the number of variations of this operator to 110.
+We immediately observed that the mutation operator has a very important role on the performance of the optimizations of the analogue method, and that the other reproduction operators seem of secondary importance.
+This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction.
+He even suggests, in opposition with the theory of \citet{Holland1992a}, that chromosomes crossovers have mostly a corrective role of mutation operations.
+Various studies have also identified the importance of the mutation operator relative to reproduction \citep[see eg.][]{Back1992a, Back1996b, Smith1997a, Deb1999, Haupt2004, Costa2005a, Costa2007a}.
+
+	The mutation operators based on a variable normal or uniform law work very poorly and are difficult to configure.
+We then observe many operators more or less with the same scores and requiring a variable amount of assessments.
+The convergence analysis allows us to highlight three best operators:
+
+	\begin{itemize}
+		\item Non-uniform mutation \citep{Michalewicz1996}: this operator is good in terms of convergence, mainly when the number of parameters to optimize is rather low.
+The number of required evaluations, however, can be quite substantial.
+The main disadvantage of the non-uniform mutation is the complexity of its parameterization, which is difficult to estimate a priori.
+These parameters must be carefully chosen to be in line with the evolution rate of the population, and are therefore dependent on the problem being treated.
+We could observe that the $\omega$ coefficient does not influence performance.
+The role of $G_{max}$ is rather difficult to judge, but does not seem essential.
+The mutation rate was found to be important.
+The difficulty is that the optimal value seems to be very case-related.
+Indeed, by even changing the precipitation time series (ie optimizing for another region), but not the complexity of the analogue method, the optimal mutation rate changes, making it impossible to estimate in advance.
+
+		\item Chromosome of adaptive search radius \citep{Horton2012a}: unlike the previous one, this operator is very robust, as it requires no option and is self-managing.
+It may be sometimes a little bit less efficient for simple problems, but does not require parameterization, which is an important advantage.
+It is interesting to notice that our insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, eg, the chromosome of adaptive mutation rate).
+
+		\item Multi-scale mutation \citep{Horton2012a}: finally, our multi-scale mutation, which also performs pretty well, can as well be seen as fairly robust, since it requires only one parameter, the mutation rate.
+Our tests seem to indicate that a high mutation rate here is preferable.
+	\end{itemize}
+
+	It may be wise to perform multiple optimizations and to consider these three operators in parallel in order to obtain results from algorithms that are either sometimes more efficient or more robust.
+It is interesting to note that the three best techniques incorporate a notion of search distance.
+It is likely that this notion is the key to these algorithms, for our application, and allows them to initially explore the parameter domain, and then to converge.
+The search radius in fact directly represents the notion of transition between exploration and exploitation, in our opinion more than a possible evolution of mutation rates.
+
+	\item \textbf{Other options}: A ratio of 50\% for the mating pool seems to be a good choice.
+
+\end{itemize}
+
+\subsubsection{Recommended parameterization of GAs}
 

### 2015-01-23 Optimization - Journal of Climate/template.tex
Removal of the sub-lists.

@@
 	\item Manual choice of the following parameters:
-	\begin{itemize}
+	\begin{enumerate}
 		\item meteorological variable,
@@
 		\item initial analogue numbers.
-	\end{itemize}
+	\end{enumerate}
 
@@
 The advantage of this method is that it is fast and has low computing requirements.
-We added small improvements to this method by allowing the spatial windows to do other moves, such as:
-
-\begin{itemize}
-	\item increase in 2 simultaneous directions,
-	\item decrease in 1 or 2 simultaneous directions,
-	\item expansion or contraction (in every direction),
-	\item shift of the window (without resizing) in 8 directions (including diagonals),
-	\item and finally all the moves described above, but with a factor of 2, 3, or more.
+We added small improvements to this method by allowing the spatial windows to do other moves, such as: (1) increase in 2 simultaneous directions, (2) decrease in 1 or 2 simultaneous directions, (3) expansion or contraction (in every direction), (4) shift of the window (without resizing) in 8 directions (including diagonals), (5) and finally all the moves described above, but with a factor of 2, 3, or more.
 For example, we try to increase by 2 units in one (or more) direction.
 This allows to skip one size that may not be optimal.
-\end{itemize}
 
@@
 There are two techniques for weighting the individuals of the mating pool:
-	\begin{itemize}
-		\item Roulette wheel weighting on rank: the probability of each individual depends on its rank $n$:
+
+	\textit{Roulette wheel weighting on rank}: the probability of each individual depends on its rank $n$:
 	\begin{equation}
@@
 
-		\item Roulette wheel weighting on fitness: the selection probability is calculated based on the value of the objective function.
+	\textit{Roulette wheel weighting on fitness}: the selection probability is calculated based on the value of the objective function.
 This approach gives more weight to the best individuals when the distribution of scores is wide, while the weight is almost similar when all individuals have approximately the same score \citep{Haupt2004}.
@@
 	In our application, the last individual ($N_{mp}$) has zero probability of being selected.
-	\end{itemize}
 
@@
 	\item \textbf{Population size}: we found the following ranges to be accurate in average:
-	\begin{itemize}
-		\item $50<N<100$ for a very simple implementation of the analogue method (1 level of analogy with 2 atmospheric levels),
 
-		\item $N\approx200$ for a bit more complex method (1 level of analogy with 4 atmospheric levels, or 2 level of analogy with less atmospheric levels),
+	$50<N<100$ for a very simple implementation of the analogue method (1 level of analogy with 2 atmospheric levels),
 
-		\item $N\approx500$ for significantly more complex methods (2-3 levels of analogy with 4 atmospheric levels for the atmospheric circulation, and 2 to 4 levels for the analogy humidity),
-	\end{itemize}
+	$N\approx200$ for a bit more complex method (1 level of analogy with 4 atmospheric levels, or 2 level of analogy with less atmospheric levels),
+
+	$N\approx500$ for significantly more complex methods (2-3 levels of analogy with 4 atmospheric levels for the atmospheric circulation, and 2 to 4 levels for the analogy humidity),
+
 	We didn't find any improvement with $N>500$, the results were even surprisingly of a lower quality.
@@
 
-	\begin{itemize}
-		\item Non-uniform mutation \citep{Michalewicz1996}: this operator is good in terms of convergence, mainly when the number of parameters to optimize is rather low.
+	\textit{Non-uniform mutation} \citep{Michalewicz1996}: this operator is good in terms of convergence, mainly when the number of parameters to optimize is rather low.
 The number of required evaluations, however, can be quite substantial.
@@
 
-		\item Chromosome of adaptive search radius \citep{Horton2012a}: unlike the previous one, this operator is very robust, as it requires no option and is self-managing.
+	\textit{Chromosome of adaptive search radius} \citep{Horton2012a}: unlike the previous one, this operator is very robust, as it requires no option and is self-managing.
 It may be sometimes a little bit less efficient for simple problems, but does not require parameterization, which is an important advantage.
@@
 
-		\item Multi-scale mutation \citep{Horton2012a}: finally, our multi-scale mutation, which also performs pretty well, can as well be seen as fairly robust, since it requires only one parameter, the mutation rate.
+	\textit{Multi-scale mutation} \citep{Horton2012a}: finally, our multi-scale mutation, which also performs pretty well, can as well be seen as fairly robust, since it requires only one parameter, the mutation rate.
 Our tests seem to indicate that a high mutation rate here is preferable.
-	\end{itemize}
 

### 2015-01-23 Optimization - Journal of Climate/template.tex
End of the operators comparison !

@@
 % DOUBLE-SPACED VERSION FOR SUBMISSION TO THE AMS
-%\documentclass{ametsoc}
+\documentclass{ametsoc}
 
 % TWO-COLUMN JOURNAL PAGE LAYOUT---FOR AUTHOR USE ONLY
- \documentclass[twocol]{ametsoc}
+%\documentclass[twocol]{ametsoc}
 
@@
 
-	\item \textbf{Natural selection}: this operator has no significant influence, and both tested implementations work fine.
+	\item \textbf{Natural selection}: this operator has no significant influence, and both tested implementations work fine, with a slightly better performance for the ratio-elitism.
 
@@
 We could observe that the $\omega$ coefficient does not influence performance.
-The role of $G_{max}$ is rather difficult to judge, but does not seem essential.
+The role of $G_{m}$ is rather difficult to judge, but does not seem essential.
 The mutation rate was found to be important.
@@
 
+We evaluated the optimization by genetic algorithms on methods of varying complexity, with a large number of combinations of operators to be able to make recommendations for optimizing the analogue method.
+Our conclusions are:
+
+\begin{itemize}
+	\item The optimization does not systematically converge to the global optimum  (but still often nearby), which is why we recommend doing several optimizations in parallel in order to compare the results, analyze the convergence, and keep the best.
+
+	\item The population size should be in accordance with the complexity of the method to optimize: from 50 for the simple ones, up to 500 for the most complex methods.
+
+	\item The value of the ratio for the intermediate population is not so important, and value of 50\% seems quite appropriate.
+
+	\item Ratio-elitism is slightly better than tournaments for the natural selection operator, but it is not decisive.
+
+	\item The performance of the operators for the couples selection perform relatively similarly.
+The roulette wheel weighting and the tournament selection are more efficient in terms of convergence and the required number of evaluations.
+
+	\item Most crossover operators have relatively similar performance. Binary-like crossover, especially with two points of intersection, are better than others, especially for convergence.
+
+	\item Mutation has a clearly dominant influence.
+Three mutation operators stand out, two of which we have developed: the non-uniform mutation, the chromosome of adaptive search radius, and the multi-scale mutation.
+The latter two are more robust as they have less or even no parameter.
+
+\end{itemize}
+
+In order to make an optimization of the analogue method with genetic algorithms, it may be wise to consider these three mutation operators in parallel.
+We would then combine algorithms that are sometimes faster to other that are more robust.
+In order to be confident in the optimized methods, we propose using a set of the following mutation operators:
+
+\begin{itemize}
+	\setlength\itemsep{-2px}
+	\item 1x non-uniform, $p_{mut}=0.1$, $G_{m}=50$, $\omega=0.1$
+	\item 1x non-uniform, $p_{mut}=0.1$, $G_{m}=100$, $\omega=0.1$
+	\item 1x non-uniform, $p_{mut}=0.2$, $G_{m}=100$, $\omega=0.1$
+	\item 1x multi-scale,  $p_{mut}=0.1$
+	\item 1x multi-scale,  $p_{mut}=0.2$
+	\item 3x chromosome of adaptive search radius
+\end{itemize}
+
 \section{Global optimization of the analogue method}
@@
 \subsection{Optimization of the analogy of atmospheric circulation}
-...
+
+We optimize here simultaneously the choice of the atmospheric levels, the time of the observation, the spatial windows and the number of analogues!
+An evaluation of all these parameters with the classic calibration requires multiple assessments of all possible combinations.
+In addition, these studies are often carried out with a spatial window of fixed size and a fixed number of analogues.
+So we hope to find solutions as good or better, but automatically.
 
@@
 ...
+
+%\item Mutation non uniforme: cet opérateur présente potentiellement le meilleur taux de convergence, pour autant qu'il soit bien paramétré.
+En revanche, si l'évolution de la population n'a pas été correctement estimée au préalable, et que nous choisissons une mauvaise valeur parmi ses trois paramètres, l'optimisation peut être médiocre.
+Son potentiel est donc prometteur, mais l'opérateur est difficile à maîtriser, car les paramètres sont nombreux et leur valeur dépend du problème à optimiser.
+%\item Chromosome de rayons de recherche adaptatifs: nous avons élaboré le chromosome de rayons de recherche adaptatifs en nous inspirant du chromosome de taux de mutation adaptatifs.
+Notre version est plus performante, car elle intègre une notion de distance dans l'espace des paramètres, qui décroît avec l'évolution de la population, améliorant ainsi la convergence.
+Une grande force de cet opérateur est qu'il ne nécessite aucun paramètre, il s'autocontrôle et évolue avec la population, ce qui le rend très robuste.
+%\item Mutation multi-échelles: la mutation multi-échelles est une nouvelle approche qui ne cherche pas une évolution de l'opérateur de mutation, mais qui effectue des recherches globales, régionales et locales en tout temps.
+Il est ainsi constamment en train d'explorer l'espace des paramètres complet et d'exploiter l'information locale, les deux aspects importants des algorithmes génétiques.
+Il ne nécessite qu'un seul paramètre, qui est le taux de mutation.
+Celui-ci doit cependant être bien choisi, et cette valeur change en fonction de la méthode à optimiser.
 

### 2015-01-30 Optimization - Journal of Climate/template.tex
Summary of the results.

@@
 % DOUBLE-SPACED VERSION FOR SUBMISSION TO THE AMS
-\documentclass{ametsoc}
+%\documentclass{ametsoc}
 
 % TWO-COLUMN JOURNAL PAGE LAYOUT---FOR AUTHOR USE ONLY
-%\documentclass[twocol]{ametsoc}
+\documentclass[twocol]{ametsoc}
 
@@
 \subsection{Data}
+\label{section_data}
 
@@
 to 6~a.m.
-the next day) measured at the MeteoSwiss' stations network, for the period 1962-2007.
+the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008.
 The time series from every available gauging station were averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.
@@
 \subsection{The analogue method}
+\label{section_analog_method}
 
@@
 \citet{Bontron2004} notes however that ''\textit{this type of algorithm, which is changing the parameters of a model in a unique path, can lead to the best solution, provided that there is no local optima}''.
-The advantage of this method is that it is fast and has low computing requirements.
+The advantage of this method is that it is fast, it provides acceptable results, and it has low computing requirements.
 We added small improvements to this method by allowing the spatial windows to do other moves, such as: (1) increase in 2 simultaneous directions, (2) decrease in 1 or 2 simultaneous directions, (3) expansion or contraction (in every direction), (4) shift of the window (without resizing) in 8 directions (including diagonals), (5) and finally all the moves described above, but with a factor of 2, 3, or more.
@@
 
-\subsection{Parameters that should be optimized}
-...
-
-\subsection{Possible new degrees of freedom}
-...
-
 \section{Adapting the genetic algorithms}
@@
 The idea is to distribute control parameters within individuals themselves, which partially decentralize control of the evolution.
-It allows reducing the parameterization of GAs and introducing a notion of self-management.
+It allows reducing the parametrization of GAs and introducing a notion of self-management.
 The first approach is the introduction of a mutation rate per individual, that mutates itself under its own probability \citep{Back1992a}.
@@
 
-\subsection{Implementation and contraints}
+\subsection{Implementation and constraints}
 
@@
 
-\subsection{Recommendations of parameterization}
-
-The GAs parameterization, such as the mutation rate, population size, natural selection options, and so on, is difficult given the high number of existing variants, each developed for a specific problem \citep{Haupt2004, Costa2007a}.
-This parameterization depends on the objective function, implementation variants, the bounds of variables to be optimized, and performance indicators.
-Thus, different studies suggest very different parameterization.
-
-A key element of the parameterization of GAs is finding the right balance between exploration and exploitation \citep{Back1992a, Smith1997a}.
+\subsection{Recommendations of parametrization}
+
+The GAs parametrization, such as the mutation rate, population size, natural selection options, and so on, is difficult given the high number of existing variants, each developed for a specific problem \citep{Haupt2004, Costa2007a}.
+This parametrization depends on the objective function, implementation variants, the bounds of variables to be optimized, and performance indicators.
+Thus, different studies suggest very different parametrization.
+
+A key element of the parametrization of GAs is finding the right balance between exploration and exploitation \citep{Back1992a, Smith1997a}.
 Exploration is characterized by a relatively high probability to assess the regions of the parameters space that have not yet been visited.
@@
 
-\citet{DeJong1975a} and \citet{Grefenstette1986} compared different implementations and parameterizations of GAs on functions of varying complexity.
+\citet{DeJong1975a} and \citet{Grefenstette1986} compared different implementations and parametrizations of GAs on functions of varying complexity.
 They observed that a small population size improves the initial performance, while a large population improves long-term performance; the size of the population should be selected between 50 and 100.
@@
 
-One of our goals being to make recommendations of parameterization for optimization of the analogue method, proceeded systematically.
+One of our goals being to make recommendations of parametrization for optimization of the analogue method, proceeded systematically.
 The results are summarized hereafter \citep[see][for the details]{Horton2012a}.
-We used concepts from the factorial design approach \citep[see eg.][]{Costa2005,Costa2007,Mariano2010}, which is sometimes used for comparative analysis of different parameterizations of GAs.
-We processed by stages, analyzing in details and in a systematic way every variants of the implemented operators, in combination with multiple other options and parameters in order to take into account eventual co-dependencies.
-
-In order to evaluate a combination of operators/options, we processed 10 optimizations for one parameterization of GAs. The performances were characterized by four indicators:
+We used concepts from the factorial design approach \citep[see eg.][]{Costa2005,Costa2007,Mariano2010}, which is sometimes used for comparative analysis of different parametrizations of GAs.
+We processed by stages, analysing in details and in a systematic way every variants of the implemented operators, in combination with multiple other options and parameters in order to take into account eventual co-dependencies.
+
+In order to evaluate a combination of operators/options, we processed 10 optimizations for one parametrization of GAs. The performances were characterized by four indicators:
 
@@
 Other operators can be considered usable, yet may not be optimal.
-Once again, this operator is not the key of the GAs parameterization.
+Once again, this operator is not the key of the GAs parametrization.
 
@@
 The number of required evaluations, however, can be quite substantial.
-The main disadvantage of the non-uniform mutation is the complexity of its parameterization, which is difficult to estimate a priori.
+The main disadvantage of the non-uniform mutation is the complexity of its parametrization, which is difficult to estimate a priori.
 These parameters must be carefully chosen to be in line with the evolution rate of the population, and are therefore dependent on the problem being treated.
@@
 	\textit{Chromosome of adaptive search radius} \citep{Horton2012a}: unlike the previous one, this operator is very robust, as it requires no option and is self-managing.
-It may be sometimes a little bit less efficient for simple problems, but does not require parameterization, which is an important advantage.
+It may be sometimes a little bit less efficient for simple problems, but does not require parametrization, which is an important advantage.
 It is interesting to notice that our insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, eg, the chromosome of adaptive mutation rate).
@@
 
-\subsubsection{Recommended parameterization of GAs}
+\subsubsection{Recommended parametrization of GAs}
 
@@
 \begin{itemize}
-	\item The optimization does not systematically converge to the global optimum  (but still often nearby), which is why we recommend doing several optimizations in parallel in order to compare the results, analyze the convergence, and keep the best.
+	\item The optimization does not systematically converge to the global optimum  (but still often nearby), which is why we recommend doing several optimizations in parallel in order to compare the results, analyse the convergence, and keep the best.
 
@@
 \begin{itemize}
-	\setlength\itemsep{-2px}
+	\setlength\itemsep{-4px}
 	\item 1x non-uniform, $p_{mut}=0.1$, $G_{m}=50$, $\omega=0.1$
@@
 \section{Global optimization of the analogue method}
-...
+
+We made different attempts to improve the analogue method by means of genetic algorithms.
+A summary of the main results are provided here \citep[see][for the details]{Horton2012a}.
+The analogue method has to be adapted to every new location it is applied.
+We will focus here on an application to the Swiss Alps.
+Even though the results may differ from one place to another, the applicability of GAs to the analogue method remains universal.
 
@@
 
+The 48 years period (see section \ref{section_data}) was divided into a calibration period and a validation period.
+Using data independent from the calibration period to validate our results is very important in order to assess the robustness of the improvements and to avoid overparametrization of the method.
+
+In order to reduce potential bias related to trends in the climate change or to the evolution in measurement techniques, the selection of the validation period is evenly distributed over the entire series.
+Thus, we select one year every six years for validation, which represents a total of eight years for the validation and forty for calibration.
+The choice of the sequence was made in order to have similar statistical characteristics between the calibration and the validation periods.
+
 \subsection{Optimization of the analogy of atmospheric circulation}
 
-We optimize here simultaneously the choice of the atmospheric levels, the time of the observation, the spatial windows and the number of analogues!
-An evaluation of all these parameters with the classic calibration requires multiple assessments of all possible combinations.
+We first optimized the analogy of atmospheric circulation alone, without humidity variables.
+We started from the most simple method, and increased the complexity of the method, thus the number of degrees of freedom in order to identify the ones that are of particular interest.
+Thus, the tested parametrization evolved iteratively in complexity.
+We do not provide the detailed results of the intermediate stages \citep[see][for the details]{Horton2012a}, but only the main conclusions.
+
+We first considered the reference method for the analogy of the atmospheric circulation, based on the 500 and 1000~hPa levels.
+We let the optimizer choose the number of analogues, both spatial windows with no overlapping constraint, as well as the temporal window (hours of observation of the geopotential).
+The classic calibration cannot automatically choose the temporal window, neither handle non-overlapping spatial windows, and finally it cannot optimize all parameters simultaneously.
+With these improvements, we could gain a relative improvement of the CRPSS of 3.97\% and 2.45\% in average for the calibration and the validation periods respectively.
+Some tests showed that most of the gains are due to the non-overlapping spatial windows.
+
+Then, we provided an additional degree of freedom to the AGs by letting them choose the atmospheric levels along with the other parameters.
+Evaluation of atmospheric levels is also a non-automated process in the classic calibration.
+However, we could observe that the choice of this degree of freedom improves the optimization time and may decrease the number of simulations which converge to a single solution.
+However, most solutions are very close in terms of score.
+The averaged relative improvement of the CRPSS is 5.63\% for the calibration and 3.82\% for the validation period.
+The atmospheric levels that were chosen are 500~hPa or 700~hPa for the upper level, and 925~hPa or 1000~hPa (most often) for the lower level.
+
+Parallel analyses showed that the analogy of circulation is incomplete, and that the geopotential still contains relevant data that can improve the statistical relationship.
+So we added a third predictor that the optimizer can use along with the previous parameters.
+There is no constraint on the predictors, so that the same atmospheric level can be selected multiple times.
+Some improvements were found on the score, both for the calibration and the validation periods, confirming that this additional information is beneficial for the quality of the forecast.
+We then tried with 4 predictors, and so on, up to 8.
+Every time we added a new predictor to optimize, the score on the calibration period increased, but always in a smaller extent.
+However, the validation period dropped after 4 predictors, revealing an over-parametrization of the method, and thus a lack of robustness.
+Moreover, the complexity of the method increases, and its interpretation becomes more and more difficult.
+We thus found that considering 4 predictors is optimal for our case study, since the gain in CRPSS is significant.
+It can not be excluded that another number would prevail under other meteorological conditions.
+
+Finally, we added a weighting of these 4 predictors (atmospheric levels), which is also optimized by GAs.
+The weighting operates in the combination of the S1 criteria of every level, which were previously averaged with equal weights.
+The role of this new degree of freedom is to give more weight to the levels with greater predictive capacity, and to consider the geopotential variability changes with altitude.
+
+\subsubsection{Which parameters are optimized ?}
+
+The method we finally optimized for the analogy of the atmospheric circulation, based on 4 levels of the geopotential, is made of the following degrees of freedom:
+
+\begin{itemize}
+	\setlength\itemsep{-4px}
+	\item the atmospheric levels (4 degrees)
+	\item the temporal windows (4)
+	\item the spatial windows (16)
+	\item the weights (4)
+	\item the number of analogues (1).
+\end{itemize}
+
+This sums up to 29 degrees of freedom that are optimize simultaneously.
+
+\subsubsection{Results of the optimization of atmospheric circulation}
+...
+
+\subsubsection{Discussion}
+...
+
+%Nous avons cherché à identifier quelle part du gain est attribuable à quel nouveau degré de liberté par rapport à la méthode M6.
+De manière générale, nous avons remarqué qu'il y a une forte dépendance entre ces paramètres (fenêtres spatiales, fenêtres temporelles et pondération des niveaux atmosphériques), et qu'il n'est pas recommandable de les considérer séparément.
+Par exemple, l'introduction des poids (non réoptimisés) dans les paramètres de la méthode M6 a un effet en moyenne nul, mais peut engendrer des pertes non négligeables sur les scores de certains groupements.
+
+%An evaluation of all these parameters with the classic calibration requires multiple assessments of all possible combinations.
 In addition, these studies are often carried out with a spatial window of fixed size and a fixed number of analogues.
@@
 
-\subsubsection{Which parameters are optimized ?}
+\subsection{Optimization of the analogy with humidity variables}
+
+We previously worked with a method based on a unique level of analogy.
+However, we know that humidity variables in a second level of analogy do provide improvements to the method (section \ref{section_analog_method}).
+So we also want to optimize the humidity index, which is a combination of the relative humidity and the precipitable water.
+In order to do so, we had to introduce a constraint to the optimizer, so that it selects the same temporal window for both variables.
+
+We proceeded to an optimization of both levels of analogy simultaneously. This implies that the analogy of the atmospheric circulation may change due to the new humidity information.
+
+When we introduce 2 predictors for the humidity analogy, the number of degrees of freedom raises to 42, and to 54 when we add 4 predictors.
+
+%We tried first to optimize the humidity predictors while keeping the same parameters for the first level of analogy on the atmospheric circulation.
+The results were not really satisfying, mainly on the scores of the validation.
+-> POUR FLUX !
+
+\subsubsection{Results of the optimization on both analogy levels}
 ...
 
-\subsubsection{Results of the optimization of atmospheric circulation}
-...
+%Ces optimisations ont mené à des paramétrisations différentes de l'analogie de circulation par rapport à précédemment.
+Il existe donc bien des relations entre les paramètres des différents niveaux d'analogie, soit entre la circulation atmosphérique et le flux d'humidité.
+Ainsi, en connaissance de l'information du flux d'humidité, la méthode préférera une représentation différente de la circulation.
+Cet aspect n'a encore jamais été mis en évidence, car les outils habituels de calibration ne le permettent pas.
+
+%Pour tenir compte des dépendances entre les paramètres des différents niveaux d'analogie, il est nécessaire d'utiliser une méthode d'optimisation globale telle que les AGs.
 
@@
 
-\subsection{Optimization of the analogy with humidity variables}
-...
-
-\subsubsection{Results of the optimization on both analogy levels}
-...
-
-\subsubsection{Successive optimization vs global optimization}
-...
-
-\subsubsection{Discussion}
-...
+We also tried optimizing the humidity flux, which is composed of the humidity index multiplied with the wind flux.
+However, the results were not as good as when we considered the humidity index alone.
+This may be related to the fact that the optimizer tries to provide the best analogy of the atmospheric circulation in the first place, which makes the wind information less relevant in the second level of analogy.
 

### 2015-02-06 Optimization - Journal of Climate/template.tex
Removing some bullet lists.

@@
 Every point (or cell) of the full domain is assessed jointly on every predictor of the level of analogy (consisting generally of the same variable, but on different atmospheric levels and at different hours).
-		\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain. The detailed stages are the followings:
-		\begin{enumerate}
-			\item The unitary spatial window is expanded in every 4 directions successively. The performance score is processed for these 4 windows.
-			\item Only the direction providing the best improvement is applied to our spatial window.
-			\item From this new spatial window, an increase in every 4 directions is once again assessed, and the best improvement is applied.
-			\item The spatial window grows up by repeating the previous steps, until no improvement is reached.
-		\end{enumerate}
+		\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain.
+The detailed stages are the followings: (i) The unitary spatial window is expanded in every 4 directions successively.
+The performance score is processed for these 4 windows.
+(ii) Only the direction providing the best improvement is applied to our spatial window.
+(iii) From this new spatial window, an increase in every 4 directions is once again assessed, and the best improvement is applied.
+(iv) The spatial window grows up by repeating the previous steps, until no improvement is reached.
 		\item The number of analogues is optimized for the current level of analogy.
@@
 
-Two conditions guarantee in theory the convergence to the global optimum \citep{Zitzler2004a}:
-
-\begin{enumerate}
-	\item Parameters mutations that can allow to explore the entire parameter space, thus ensures that any value can be achieved with a non-zero probability.
-	\item A rule of elitism ensuring that an optimal solution can not be lost or damaged.
-\end{enumerate}
+Two conditions guarantee in theory the convergence to the global optimum \citep{Zitzler2004a}: (1) Parameters mutations that can allow to explore the entire parameter space, thus ensures that any value can be achieved with a non-zero probability.
+(2) A rule of elitism ensuring that an optimal solution can not be lost or damaged.
 

### 2015-02-06 Optimization - Journal of Climate/template.tex
First draft of the conclusions.

@@
 \subsubsection{Discussion}
-...
-
+
+The optimization of the analogue method by means of genetic algorithms has been undertaken in stages by releasing progressively new degrees of freedom.
+This approach allowed us to differentiate contributions to performance gains, as well as to identify possible over-parametrization.
+The main improvements for our case study are due to the following factors:
+
+\begin{itemize}
+	\item Using 4 atmospheric levels for the analogy of circulation.
+It seems to be the optimal number for the studied region.
+Beyond that value the validation score drops, revealing a lost in robustness due to over-parametrization.
+	\item The automatic and joint optimization of all parameters: the analogues number, the choice of the atmospheric levels and the time windows, and the spatial windows.
+These parameters are highly interdependent, so we need to optimize them jointly in order to identify optimal combinations.
+Traditional calibration procedures based on a systematic assessment of every combination is no more possible when considering more than 2 atmospheric levels.
+	\item The introduction of distinct spatial windows between atmospheric levels.
+Indeed, the synoptic circulation is characterized by features with very different scales depending on the height, and important information for predicting rainfall is not necessarily located in the same area from one level to another.
+	\item The weighting of the analogy criteria between different atmospheric levels.
+It can be influenced by the variability of the geopotential with altitude, and the change of some levels significance with the targeted region.
+	\item The joint optimization of the circulation and humidity analogy levels, that are usually calibrated successively.
+We have been able to demonstrate that there is a dependency between the analogy levels, and that in order to approach the optimal parameters, we must consider them jointly.
+\end{itemize}
+
+GAs are very useful to optimize complex variants of the analogue method, and to assess new degrees of freedom that were not available so far.
+However, it can be dangerous to add too many parameters to optimize.
+Indeed, the optimizer will probably use them to successfully improve the calibration score, but the validation control remains very important in order to determine if we are actually improving the method, or if we are over-parametrizing it.
+
+The convergence of parallel optimizations decreases when the method to optimize becomes more and more complex.
+The optimizer do not always converge to the exact global optimum, but to its surroundings.
+This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that we have to stop it before the end due to the required processing time.
+The resulting parameters may sometimes present significant differences, even though the score is almost similar.
+Through some Monte-Carlo analyses of the parameter space properties of the analogue method, \citet{Horton2012a} showed that some parameters of the method have a wide range of acceptable values.
+The spatial windows, for example, can be larger than the optimal size without much impact on the score, while they cannot be smaller \citep[see also][]{Bontron2004}.
+We could also observe that the choice of the atmospheric level is not a parameter as discrete as we would have thought, and that choosing another level may have reduced consequences on the performance.
+This is particularly true for higher atmospheric levels and can be more critical for lower layers.
+It was thus interesting to sometimes get several sets of near-optimal parameters, but with some nuances, in order to have an idea of the sensitivity of the parameters for a given region, and to compare the score on the validation period.
+In this regard, a cross-validation approach may be recommended.
+
+We tried to optimize the preselection period (the 4-months window) jointly with the other parameters, but we did not get improvement.
 We also tried optimizing the humidity flux, which is composed of the humidity index multiplied with the wind flux.
@@
 
+GAs are relatively heavy to implement and require an IT infrastructure capable of performing thousands hours of calculations.
+However, they automatically optimize all parameters of the analogue method, what the classic calibration does not allow.
+We therefore save much human time that was required to assess successively numerous combinations of parameters (particularly the choice of the atmospheric levels and the temporal windows).
+The ability to optimize jointly all parameters has been important given the strong dependencies between them and between levels of analogy.
+
+% Cet aspect a été confirmé par l'optimisation, qui propose de petites fenêtres pour les niveaux supérieurs, et de grandes fenêtres pour les altitudes proches du sol.
+Notre hypothèse est que l'information des gradients des couches supérieures au-dessus du bassin suffit à résumer l'orientation et la vitesse des masses d'air d'intérêt, qui sont potentiellement liées à un forçage par-dessus la barrière orographique.
+De manière complémentaire, les fenêtres plus étendues pour les basses couches cherchent à intégrer la structure de la circulation, car celle-ci renseigne sur les centres actifs et sur le chemin qu'a parcouru la masse d'air éventuellement chargée en humidité avant d'arriver sur la zone d'intérêt.
+
 \section{Conclusions and perspectives}
-...
+
+We could observe strong dependencies between the parameters of the analogue method.
+Thus, the classic calibration, which optimizes the parameters successively, may not lead to the optimal combination.
+Moreover, it contains several manual systematic assessment, such as the choice of the atmospheric levels and the temporal windows.
+
+In order to automatically optimize the analogue method, we evaluated the genetic algorithms, a global optimization technique, that is able to solve complex problems.
+Given the large number of existing operators and options, we had to evaluate systematically multiple variants in order to identify which operators are important, and which variant works best for the analogue method.
+We could thus identify that the mutation operator is a key element for our application, and provided new variants that were found to be efficient.
+Recommendations were established for a relevant use of GAs for the optimization of the analogue method.
+
+GAs provide parametrizations of the analogue method that exceed performance results of classic calibration.
+In addition, they are used to select the atmospheric levels and the time windows automatically, which was not possible with traditional tools and which can save a considerable amount of human time.
+A great advantage of a global optimization is its ability to approach or reach optimal parameter values when they are considered jointly.
+
+We were able to identify that there is a parametric dependence between the analogy of circulation and the moisture humidity.
+When we consider the two levels together, the optimal parameters of the analogy of circulation are different.
+This complexity can only be exploited in a suitable manner by global optimization methods.
+
+For our case study, there seems to be an optimum number of atmospheric levels to consider for the analogy of circulation, which is four, before losing performance in validation.
+We have also been able to improve the analogy of circulation by introducing a weighting between atmospheric levels, and considering independent spatial windows between levels.
+
+However, there is a risk of over-parametrization with this type of approach. It is therefore important to always evaluate the proposed parameters over an independent period for validation.
 
@@
 Celui-ci doit cependant être bien choisi, et cette valeur change en fonction de la méthode à optimiser.
+
+% Finalement, les AGs, tels qu'ils ont été implémentés, sont également en mesure de choisir les variables prédicteurs d'intérêt.
+Si nous n'avons plus vraiment de doute sur le choix des variables pour la prévision des précipitations, en raison des multiples travaux réalisés sur ce sujet, nous ne connaissons pas a priori les variables qui seraient les plus informatives pour prévoir un autre prédictand, comme la température, la grêle ou le vent.
+Ces outils d'optimisation peuvent alors explorer les variables et nous proposer les meilleures combinaisons.
+Toutefois, l'automatisation de variables composées (par exemple le flux d'humidité) présentera toujours quelques limites.
 

### 2015-07-21 Optimization - Journal of Climate/template.tex
Addition of the figures of the spatial windows.

@@
 \usepackage{gensymb}
+\usepackage{subcaption}
 
@@
 There are numerous implementation variants of GAs often optimal for a given problem \citep{Hart1991a,Schraudolph1992a}.
-However, the structure of the method (Figure \ref{figure_structure_gas}) resulting from the work of \citet{Holland1992b} is common to most applications \citep{Back1993b}.
+However, the structure of the method (Figure \ref{fig:structure_gas}) resulting from the work of \citet{Holland1992b} is common to most applications \citep{Back1993b}.
 The divergences are the operators implementation, through significantly different algorithms, which has an important effect on the results \citep{Gaffney2010a}.
@@
 
-The study area is the alpine upper Rhône catchment in Switzerland (Fig.\ \ref{figure_map}).
+The study area is the alpine upper Rhône catchment in Switzerland (Fig.\ \ref{fig:map}).
 The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$.
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.3cm]{figure_map.pdf}}
+	\centerline{\includegraphics[width=8.3cm]{figures/figure_map.pdf}}
 	\caption{Location of the alpine Rhône catchment in Switzerland. (source: Swisstopo)}
-	\label{figure_map}
+	\label{fig:map}
 \end{figure}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=10.3cm]{figure_structure_gas.pdf}}
+	\centerline{\includegraphics[width=8.3cm]{figures/figure_structure_gas.pdf}}
 	\caption{Genetic algorithms operational flowchart}
-	\label{figure_structure_gas}
+	\label{fig:structure_gas}
 \end{figure}
 
+\begin{figure}[htb]
+	\centering
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4/Spatial_windows_1.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4/Spatial_windows_2.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4/Spatial_windows_3.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4/Spatial_windows_4.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4/Spatial_windows_5.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4/Spatial_windows_6.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4/Spatial_windows_7.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4/Spatial_windows_8.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4/Spatial_windows_9.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4/Spatial_windows_10.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/legend.png}
+	\end{subfigure}
+	\caption{Optimized spatial windows for the analogy of atmospheric circulation on 4 atmospheric levels.
+The atmospheric levels are ordered by increasing pressure and increasing time for the same levels.}
+	\label{fig:spatial_windows_z4}
+\end{figure}
+
+\begin{figure}[htb]
+	\centering
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi2/Spatial_windows_1.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi2/Spatial_windows_2.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi2/Spatial_windows_3.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi2/Spatial_windows_4.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi2/Spatial_windows_5.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi2/Spatial_windows_6.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi2/Spatial_windows_7.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi2/Spatial_windows_8.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi2/Spatial_windows_9.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi2/Spatial_windows_10.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/legend.png}
+	\end{subfigure}
+	\caption{Optimized spatial windows for the analogy of atmospheric circulation on 4 atmospheric levels and the analogy on the humidity index on 2 atmospheric levels.
+The atmospheric levels are ordered by increasing pressure and increasing time for the same levels.}
+	\label{fig:spatial_windows_z4-hi2}
+\end{figure}
+
+\begin{figure}[htb]
+	\centering
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi4/Spatial_windows_1.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi4/Spatial_windows_2.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi4/Spatial_windows_3.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi4/Spatial_windows_4.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi4/Spatial_windows_5.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi4/Spatial_windows_6.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi4/Spatial_windows_7.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi4/Spatial_windows_8.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi4/Spatial_windows_9.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.1cm]{figures/spatial_win_z4-hi4/Spatial_windows_10.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/legend.png}
+	\end{subfigure}
+	\caption{Optimized spatial windows for the analogy of atmospheric circulation on 4 atmospheric levels and the analogy on the humidity index on 4 atmospheric levels.
+The atmospheric levels are ordered by increasing pressure and increasing time for the same levels.}
+	\label{fig:spatial_windows_z4-hi4}
+\end{figure}
+
 \end{document}

### 2015-07-22 Optimization - Journal of Climate/template.tex
Addition of the resulting parameters.

--- 2015-02-06 Optimization - Journal of Climate/template.tex
@@
 
-The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table_params_R1}): For a target date, we evaluate the similarity of the atmospheric circulation with every day of the archive by processing the S1 criteria \citep[Eq.\ (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
+The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): For a target date, we evaluate the similarity of the atmospheric circulation with every day of the archive by processing the S1 criteria \citep[Eq.\ (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
 \citet{Bontron2005} showed that the geopotential heights at 500~hPa and 1000~hPa are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criteria performs better than scores based on absolute distances.
@@
 
-The other most know method adds a second level of analogy on humidity variables (Table \ref{table_params_R2}).
+The other most know method adds a second level of analogy on humidity variables (Table \ref{table:params_R2}).
 The predictor that \citet{Bontron2004} found as optimal for the France territory is a humidity index made of the multiplication of the precipitable water with the relative humidity at 850~hPa.
@@
 		\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Analogues nb} \\ 
-			\hline 
-			preselection & \multicolumn{4}{c}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{2}{*}{1} & geopotential hgt 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
-			& geopotential hgt 500~hPa & 24~h & & \\ 
+			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+			\hline 
+			preselection & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & Z 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
+			& Z 500~hPa & 24~h & & \\ 
 			\hline 
@@
 	\end{center}
-	\label{table_params_R1}
+	\label{table:params_R1}
 \end{table}
@@
 		\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Analogues nb} \\ 
-			\hline 
-			preselection & \multicolumn{4}{c}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{2}{*}{1} & geopotential hgt 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
-			& geopotential hgt 500~hPa & 24~h & & \\ 
-			\hline
-			\multirow{2}{*}{2} & precipitable water * relative humidity 850~hPa & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{30} \\
-			& precipitable water * relative humidity 850~hPa & 24~h & & \\ 
+			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+			\hline 
+			preselection & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & Z 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
+			& Z 500~hPa & 24~h & & \\ 
+			\hline
+			\multirow{2}{*}{2} & TPW * RH 850~hPa & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{30} \\
+			& TPW * RH 850~hPa & 24~h & & \\ 
 			\hline 
@@
 	\end{center}
-	\label{table_params_R2}
+	\label{table:params_R2}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Parameters of an analogy on the atmospheric circulation (4 levels) optimized for the Chablais region.
+The columns are the followings: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
+	\begin{center}
+		\begin{tabular}{ccccccc}
+			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
+			\hline 
+			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & -2.5 - 15.0 \degree E & \multirow{2}{*}{32\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{28} \\
+			& & & 37.5 - 57.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z700} & \multirow{2}{*}{24~h} & 2.5 - 10.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
+			& & & 42.5 - 45.0 \degree N & & & \\ 
+			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{6~h} & -5.0 - 15.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
+			& & & 42.5 - 47.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
+			& & & 40.0 - 50.0 \degree N & & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:params_GA_z4}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation at the different groupments.}
+	\begin{center}
+		\begin{tabular}{ccccccccc}
+			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
+			\hline 
+			1  & Z &   &   &   & Z &   &   & ZZ \\
+			2  & Z &   &   &   & Z &   &   & ZZ \\
+			3  & Z &   &   &   & Z &   &   & ZZ \\
+			4  & Z &   &   &   & Z &   &   & ZZ \\
+			5  &   &   & Z &   & Z &   &   & ZZ \\
+			6  &   &   & Z &   & Z &   &   & ZZ \\
+			7  &   &   & Z &   & Z &   &   & ZZ \\
+			8  &   &   & Z &   & Z &   &   & ZZ \\
+			9  &   &   & Z &   & Z &   &   & ZZ \\
+			10 &   &   &   & Z & Z &   &   & ZZ \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:levels_GA_z4}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Parameters of an analogy on the atmospheric circulation (4 levels) and the humidity index (2 levels), optimized for the Chablais region.
+The columns are the followings: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
+	\begin{center}
+		\begin{tabular}{ccccccc}
+			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
+			\hline 
+			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & 0.0 - 15.0 \degree E & \multirow{2}{*}{23\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
+			& & & 42.5 - 55.0 \degree N & & & \\ 
+			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{25\%} & & \\ 
+			& & & 40.0 - 45.0 \degree N & & & \\ 
+			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
+			& & & 42.5 - 47.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
+			& & & 40.0 - 47.5 \degree N & & & \\ 
+			\hline 
+			\multirow{4}{*}{2} & TPW & \multirow{2}{*}{12~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{57\%} & \multirow{4}{*}{RMSE} & \multirow{4}{*}{25} \\
+			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
+			& TPW & \multirow{2}{*}{24~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{43\%} & & \\ 
+			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:params_GA_z4_hi2}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation at the different groupments.}
+	\begin{center}
+		\begin{tabular}{ccccccccc}
+			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
+			\hline 
+			1  & Z &   & Z &   &   & Z &   & Z \\
+			2  & Z &   &   &   & Z & Z &   & Z \\
+			3  & Z &   &   &   & Z & Z & Z &   \\
+			4  &   &   & Z &   & Z & Z &   & Z \\
+			5  &   & Z &   &   & Z &   & ZZ &   \\
+			6  &   & Z &   &   & Z & Z &   & Z \\
+			7  &   & Z &   &   & Z & Z &   & Z \\
+			8  &   &   & Z &   & Z &   & ZZ &   \\
+			9  &   & Z &   &   & Z & Z & Z &   \\
+			10 &   & Z &   &   & Z & Z &   & Z \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:levels_GA_z4_hi2}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation at the different groupments.}
+	\begin{center}
+		\begin{tabular}{ccccccccc}
+			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
+			\hline 
+			1  &   &   &   &   & HH &   &   &   \\
+			2  &   &   &   &   & HH &   &   &   \\
+			3  &   &   &   &   & HH &   &   &   \\
+			4  &   &   &   & H & H &   &   &   \\
+			5  &   &   &   &   & HH &   &   &   \\
+			6  &   &   &   & H & H &   &   &   \\
+			7  &   &   &   & H & H &   &   &   \\
+			8  &   &   &   & H & H &   &   &   \\
+			9  &   &   &   & H & H &   &   &   \\
+			10 &   &   &   & H & H &   &   &   \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:levels_GA_z4_hi2_H}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Parameters of an analogy on the atmospheric circulation (4 levels) and the humidity index (4 levels), optimized for the Chablais region.
+The columns are the followings: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
+	\begin{center}
+		\begin{tabular}{ccccccc}
+			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
+			\hline 
+			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{8}{*}{1} &  \multirow{2}{*}{Z400} & \multirow{2}{*}{6~h} & -5.0 - 12.5 \degree E & \multirow{2}{*}{20\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
+			& & & 45.0 - 52.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
+			& & & 40.0 - 45.0 \degree N & & & \\ 
+			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
+			& & & 42.5 - 47.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
+			& & & 40.0 - 47.5 \degree N & & & \\ 
+			\hline 
+			\multirow{8}{*}{2} & TPW & \multirow{2}{*}{24~h} & 7.5 - 10.0 \degree E & \multirow{2}{*}{27\%} & \multirow{8}{*}{RMSE} & \multirow{8}{*}{25} \\
+			& *RH500 & & 45.0 - 47.5 \degree N & & & \\ 
+			& TPW & \multirow{2}{*}{12~h} & 5.0 - 7.5 \degree E & \multirow{2}{*}{41\%} & & \\ 
+			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
+			& TPW & \multirow{2}{*}{18~h} & 0.0 - 7.5 \degree E & \multirow{2}{*}{19\%} & & \\ 
+			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
+			& TPW & \multirow{2}{*}{24~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{13\%} & & \\ 
+			& *RH850 & & 45.0 - 47.5 \degree N & & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:params_GA_z4_hi4}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation at the different groupments.}
+	\begin{center}
+		\begin{tabular}{ccccccccc}
+			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
+			\hline 
+			1  &   & Z & Z &   &   & Z &   & Z \\
+			2  &   & Z &   &   & ZZ &   &   & Z \\
+			3  &   & Z &   &   & Z & Z & Z &   \\
+			4  &   &   & Z &   & Z & Z &   & Z \\
+			5  &   & Z & Z &   &   & Z &   & Z \\
+			6  &   & Z & Z &   &   & Z &   & Z \\
+			7  &   & Z &   &   & ZZ &   &   & Z \\
+			8  &   &   & Z & Z &   & Z &   & Z \\
+			9  &   & Z &   &   & Z & Z & Z &   \\
+			10 &   & Z & Z &   &   & ZZ &   &   \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:levels_GA_z4_hi4}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation at the different groupments.}
+	\begin{center}
+		\begin{tabular}{ccccccccc}
+			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
+			\hline 
+			1  &   &   & H &   & HH & H &   &   \\
+			2  &   &   &   & H & HH & H &   &   \\
+			3  &   &   &   & H & HHH &   &   &   \\
+			4  &   &   &   & HH & HH &   &   &   \\
+			5  &   &   &   & HH & HH &   &   &   \\
+			6  &   &   &   & HH & H & H &   &   \\
+			7  &   &   &   & HH & H & H &   &   \\
+			8  &   &   &   & HH & H & H &   &   \\
+			9  &   &   & H & H & H & H &   &   \\
+			10 &   &   &   & H & HH & H &   &   \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:levels_GA_z4_hi4_H}
 \end{table}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=10.3cm]{figure_structure_gas.pdf}}
+	\centerline{\includegraphics[width=8.3cm]{figures/figure_structure_gas.pdf}}
 	\caption{Genetic algorithms operational flowchart}
-	\label{figure_structure_gas}
+	\label{fig:structure_gas}
 \end{figure}
 
+\begin{figure}[htb]
+	\centering
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_1.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_2.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_3.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_4.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_5.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_6.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_7.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_8.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_9.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_10.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/legend.png}
+	\end{subfigure}
+	\caption{Optimized spatial windows for the analogy of atmospheric circulation on 4 atmospheric levels.
+The atmospheric levels are ordered by increasing pressure and increasing time for the same levels.}
+	\label{fig:spatial_windows_z4}
+\end{figure}
+
+\begin{figure}[htb]
+	\centering
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_1.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_2.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_3.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_4.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_5.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_6.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_7.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_8.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_9.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_10.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/legend.png}
+	\end{subfigure}
+	\caption{Optimized spatial windows for the analogy of atmospheric circulation on 4 atmospheric levels and the analogy on the humidity index on 2 atmospheric levels.
+The atmospheric levels are ordered by increasing pressure and increasing time for the same levels.}
+	\label{fig:spatial_windows_z4-hi2}
+\end{figure}
+
+\begin{figure}[htb]
+	\centering
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_1.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_2.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_3.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_4.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_5.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_6.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_7.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_8.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_9.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_10.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/legend.png}
+	\end{subfigure}
+	\caption{Optimized spatial windows for the analogy of atmospheric circulation on 4 atmospheric levels and the analogy on the humidity index on 4 atmospheric levels.
+The atmospheric levels are ordered by increasing pressure and increasing time for the same levels.}
+	\label{fig:spatial_windows_z4-hi4}
+\end{figure}
+
 \end{document}

### 2015-07-23 Optimization - Journal of Climate/template.tex
Addition of the levels synthesis figure.
Addition of the parameters crossing tables.

@@
 
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=8.3cm]{figures/figure_levels_weights.pdf}}
+	\caption{Optimized weighting for the atmospheric levels of the circulation analogy.}
+	\label{fig:levels_weights}
+\end{figure}
+
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=8.3cm]{figures/figure_levels_weights_average.pdf}}
+	\caption{Optimized weighting for the atmospheric levels of the circulation analogy.}
+	\label{fig:levels_weights_average}
+\end{figure}
+
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=8.3cm]{figures/figure_evolution.pdf}}
+	\caption{Example of the best individuals evolution of 8 independent optimizations.}
+	\label{fig:evolution}
+\end{figure}
+
+\clearpage
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 1, calibration period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4_calib.pdf}}
+	\label{table:crossing_z4_calib}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 1, validation period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4_valid.pdf}}
+	\label{table:crossing_z4_valid}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 2, calibration period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_calib.pdf}}
+	\label{table:crossing_z4-hi2_calib}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 2, validation period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_valid.pdf}}
+	\label{table:crossing_z4-hi2_valid}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 3, calibration period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_calib.pdf}}
+	\label{table:crossing_z4-hi4_calib}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 3, validation period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_valid.pdf}}
+	\label{table:crossing_z4-hi4_valid}
+\end{table}
+
 \end{document}

### 2015-07-24 Optimization - Journal of Climate/template.tex
Changing structure.
Addition of the scores tables.

@@
 \usepackage{subcaption}
+\usepackage{xcolor,colortbl}
+
+% After http://tex.stackexchange.com/questions/94799/how-do-i-color-table-columns-and-rows
+\newcommand{\mc}[2]{\multicolumn{#1}{c}{#2}}
+\definecolor{Gray}{gray}{0.85}
+\definecolor{LightCyan}{rgb}{0.88,1,1}
+\newcolumntype{a}{>{\columncolor{Gray}}c}
 
@@
 
-\section{Calibration of the analogue method}
-...
-
-\subsection{Data}
-\label{section_data}
-
-The analogue method relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series we want to forecast.
-
-Predictors are generally reanalysis datasets (and outputs of a global numerical weather prediction models for the target situation in operational forecasting, which is not the topic of this paper).
-We will work here with the NCEP/NCAR reanalysis \citep[6-hourly, 17 atmospheric levels at a resolution of 2.5\degree, see][]{Kalnay1996}, but it can be any other reanalysis.
-
-The predictand (which is to be predicted) is here the daily precipitation (6~a.m.
-to 6~a.m.
-the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008.
-The time series from every available gauging station were averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.
-
-\subsection{The analogue method}
-\label{section_analog_method}
-
 The analogue method is a downscaling technique based on the idea expressed by \citet{Lorenz1969}.
@@
 Its main hypothesis is that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Bontron2005}.
+
+\subsection{The analogue method}
+\label{section_analog_method}
 
@@
 When we add a second level of analogy, we keep a higher number of analogues on the first level (70 instead of 50).
+
+\subsection{Data}
+\label{section_data}
+
+The analogue method relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series we want to forecast.
+
+Predictors are generally reanalysis datasets (and outputs of a global numerical weather prediction models for the target situation in operational forecasting, which is not the topic of this paper).
+We will work here with the NCEP/NCAR reanalysis \citep[6-hourly, 17 atmospheric levels at a resolution of 2.5\degree, see][]{Kalnay1996}, but it can be any other reanalysis.
+
+The predictand (which is to be predicted) is here the daily precipitation (6~a.m.
+to 6~a.m.
+the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008.
+The time series from every available gauging station were averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.
 
@@
 
-\section{Motivation for a global optimization}
+\subsection{Motivation for a global optimization}
 
@@
 
-\subsection{Characterization of the parameters space}
-...
-
-\section{Adapting the genetic algorithms}
+\section{Adjusting genetic algorithms}
 
@@
 
+\clearpage
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 1, calibration period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4_calib.pdf}}
+	\label{table:crossing_z4_calib}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 1, validation period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4_valid.pdf}}
+	\label{table:crossing_z4_valid}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 2, calibration period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_calib.pdf}}
+	\label{table:crossing_z4-hi2_calib}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 2, validation period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_valid.pdf}}
+	\label{table:crossing_z4-hi2_valid}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 3, calibration period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_calib.pdf}}
+	\label{table:crossing_z4-hi4_calib}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 3, validation period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_valid.pdf}}
+	\label{table:crossing_z4-hi4_valid}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized analogy of atmospheric circulation.}
+	\begin{center}
+		\begin{tabular}{rrarara}
+			\hline 
+			\textbf{ID} & \multicolumn{2}{c}{\textbf{z4}} & \multicolumn{2}{c}{\textbf{z4-hi2}} & \multicolumn{2}{c}{\textbf{z4-hi4}} \\ 
+			\hline 
+			 & calib & valid & calib & valid & calib & valid \\ 
+			\hline 
+			\textbf{1} & 13.6 & 13.0 & 11.9 & 9.9 & 12.8 & 9.6 \\ \hline
+			\textbf{2} & 13.3 & 7.5 & 11.2 & 9.4 & 12.5 & 10.8 \\ \hline
+			\textbf{3} & 12.2 & 9.0 & 13.2 & 12.0 & 14.1 & 13.5 \\ \hline
+			\textbf{4} & 14.2 & 10.5 & 12.4 & 10.6 & 14.5 & 12.5 \\ \hline
+			\textbf{5} & 14.5 & 8.8 & 12.5 & 9.1 & 14.1 & 10.0 \\ \hline
+			\textbf{6} & 13.3 & 8.6 & 11.5 & 8.2 & 14.1 & 8.4 \\ \hline
+			\textbf{7} & 22.8 & 10.6 & 19.7 & 15.7 & 21.7 & 16.3 \\ \hline
+			\textbf{8} & 20.7 & 11.9 & 19.2 & 13.5 & 20.8 & 14.0 \\ \hline
+			\textbf{9} & 14.4 & 9.5 & 15.8 & 15.2 & 16.7 & 14.1 \\ \hline
+			\textbf{10} & 14.2 & 9.4 & 12.9 & 11.2 & 14.6 & 11.8 \\ \hline
+			\textbf{av.} & \textbf{15.3} & \textbf{9.9} &\textbf{14.0} & \textbf{11.5} & \textbf{15.6} & \textbf{12.1} \\ \hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:scores}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized analogy of atmospheric circulation.}
+	\begin{center}
+		\begin{tabular}{rrarara}
+			\hline 
+			\textbf{ID} & \multicolumn{2}{c}{\textbf{$P\geq1 mm$}} & \multicolumn{2}{c}{\textbf{$P\geq1 0.1\cdot P10$}} & \multicolumn{2}{c}{\textbf{$P\geq1 0.5\cdot P10$}} \\ 
+			\hline 
+			 & calib & valid & calib & valid & calib & valid \\ 
+			\hline 
+			\textbf{1} & 10.2 & 9.4 & 8.5 & 7.9 & 17.0 & 14.2 \\ \hline 
+			\textbf{2} & 9.9 & 3.4 & 10.2 & 7.3 & 19.3 & 13.7 \\ \hline 
+			\textbf{3} & 13.3 & 10.5 & 13.3 & 10.9 & 19.7 & 9.7 \\ \hline 
+			\textbf{4} & 11.0 & 7.4 & 12.9 & 10.0 & 23.2 & 23.8 \\ \hline 
+			\textbf{5} & 8.6 & 4.2 & 10.9 & 6.2 & 25.2 & 23.8 \\ \hline 
+			\textbf{6} & 10.5 & 5.1 & 11.1 & 7.1 & 21.2 & 41.1 \\ \hline 
+			\textbf{7} & 24.3 & 12.4 & 33.1 & 26.0 & 71.2 & 104.3 \\ \hline 
+			\textbf{8} & 19.0 & 12.7 & 26.2 & 19.2 & 39.4 & 34.9 \\ \hline 
+			\textbf{9} & 12.4 & 6.8 & 13.8 & 9.9 & 24.9 & 48.1 \\ \hline 
+			\textbf{10} & 13.6 & 6.8 & 14.4 & 6.9 & 29.9 & 31.5 \\ \hline 
+			\textbf{av.} &\textbf{ 13.3} & \textbf{7.9} & \textbf{15.4} & \textbf{11.1} & \textbf{29.1} & \textbf{34.5} \\ \hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:scores_z4}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized analogy of atmospheric circulation and humidity variables (2 levels).}
+	\begin{center}
+		\begin{tabular}{rrarara}
+			\hline 
+			\textbf{ID} & \multicolumn{2}{c}{\textbf{$P\geq1 mm$}} & \multicolumn{2}{c}{\textbf{$P\geq1 0.1\cdot P10$}} & \multicolumn{2}{c}{\textbf{$P\geq1 0.5\cdot P10$}} \\ 
+			\hline 
+			 & calib & valid & calib & valid & calib & valid \\ 
+			\hline 
+			\textbf{1} & 12.6 & 9.3 & 12.4 & 9.7 & 15.8 & 11.0 \\ \hline 
+			\textbf{2} & 10.4 & 7.7 & 11.2 & 10.5 & 18.9 & 16.6 \\ \hline 
+			\textbf{3} & 14.5 & 11.6 & 14.1 & 11.4 & 18.7 & 14.6 \\ \hline 
+			\textbf{4} & 11.4 & 9.4 & 11.5 & 11.6 & 14.9 & 22.7 \\ \hline 
+			\textbf{5} & 11.8 & 8.0 & 12.2 & 8.9 & 12.0 & 12.8 \\ \hline 
+			\textbf{6} & 11.3 & 7.1 & 11.2 & 8.0 & 15.3 & 29.1 \\ \hline 
+			\textbf{7} & 20.5 & 15.5 & 25.2 & 24.0 & 43.0 & 79.5 \\ \hline
+			\textbf{8} & 19.3 & 15.7 & 23.1 & 18.6 & 25.2 & 31.7 \\ \hline 
+			\textbf{9} & 17.0 & 15.4 & 17.4 & 16.5 & 23.7 & 39.4 \\ \hline 
+			\textbf{10} & 12.9 & 9.6 & 13.8 & 11.1 & 28.5 & 32.1 \\ \hline 
+			\textbf{av.} &\textbf{14.2} & \textbf{10.9} & \textbf{15.2} & \textbf{13.0} & \textbf{21.6} & \textbf{28.9} \\ \hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:scores_z4-hi2}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized analogy of atmospheric circulation and humidity variables (4 levels).}
+	\begin{center}
+		\begin{tabular}{rrarara}
+			\hline 
+			\textbf{ID} & \multicolumn{2}{c}{\textbf{P$\geq1$ mm}} & \multicolumn{2}{c}{\textbf{P$\geq1$ 0.1$\cdot$ P10}} & \multicolumn{2}{c}{\textbf{$P\geq1 0.5\cdot P10$}} \\ 
+			\hline 
+			 & calib & valid & calib & valid & calib & valid \\ 
+			\hline 
+			\textbf{1} & 21.2 & 17.9 & 13.4 & 9.3 & 17.8 & 13.3 \\ \hline 
+			\textbf{2} & 12.6 & 8.9 & 9.5 & 10.0 & 16.7 & 15.6 \\ \hline 
+			\textbf{3} & 17.0 & 16.1 & 14.0 & 12.4 & 21.3 & 15.9 \\ \hline 
+			\textbf{4} & 9.4 & 6.1 & 13.3 & 12.4 & 19.8 & 22.7 \\ \hline 
+			\textbf{5} & 16.4 & 8.7 & 13.3 & 9.9 & 15.5 & 19.8 \\ \hline 
+			\textbf{6} & 22.6 & 12.2 & 11.9 & 6.7 & 17.0 & 26.9 \\ \hline 
+			\textbf{7} & 14.6 & 4.9 & 24.7 & 23.5 & 42.7 & 87.6 \\ \hline 
+			\textbf{8} & 21.8 & 21.6 & 25.7 & 19.3 & 32.3 & 26.6 \\ \hline 
+			\textbf{9} & 20.2 & 18.9 & 17.4 & 14.2 & 24.5 & 33.9 \\ \hline 
+			\textbf{10} & 21.7 & 14.8 & 14.8 & 11.7 & 29.2 & 29.1 \\ \hline 
+			\textbf{av.} &\textbf{17.7} & \textbf{13.0} & \textbf{15.8} & \textbf{12.9} & \textbf{23.7} & \textbf{29.2} \\ \hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:scores_z4-hi4}
+\end{table}
+
+\clearpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\clearpage
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 1, calibration period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4_calib.pdf}}
-	\label{table:crossing_z4_calib}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 1, validation period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4_valid.pdf}}
-	\label{table:crossing_z4_valid}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 2, calibration period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_calib.pdf}}
-	\label{table:crossing_z4-hi2_calib}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 2, validation period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_valid.pdf}}
-	\label{table:crossing_z4-hi2_valid}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 3, calibration period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_calib.pdf}}
-	\label{table:crossing_z4-hi4_calib}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 3, validation period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_valid.pdf}}
-	\label{table:crossing_z4-hi4_valid}
-\end{table}
-
 \end{document}

### 2015-08-03 Optimization - Journal of Climate/template.tex
Changing figures order.

@@
 \section{Introduction}
-...
-\cite{Horton2012a}
 
@@
 	\item 1x multi-scale,  $p_{mut}=0.1$
-	\item 1x multi-scale,  $p_{mut}=0.2$
-	\item 3x chromosome of adaptive search radius
+	\item 2x chromosome of adaptive search radius
 \end{itemize}
 
-\section{Global optimization of the analogue method}
-
-We made different attempts to improve the analogue method by means of genetic algorithms.
-A summary of the main results are provided here \citep[see][for the details]{Horton2012a}.
+\section{Example case study}
+
 The analogue method has to be adapted to every new location it is applied.
@@
 Even though the results may differ from one place to another, the applicability of GAs to the analogue method remains universal.
+We made different attempts to improve the analogue method for the Swiss Alps, by means of genetic algorithms.
+A summary of the main results are provided here \citep[see][for the details]{Horton2012a}.
 
@@
 The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$.
-This region in the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at providing a real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
-The first global optimizations were part of the MINERVE project \citep{Horton2012, Horton2012a}.
+This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at providing a real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
+Even thought the region is rather small, the meteorological influences related to extreme weather conditions varies substantially within it \citep[see]{Horton2012}.
+Based on different climatological analyses, the gauging stations in the catchment were clustered in 10~groupments (Fig.\ \ref{fig:map}) :
+
+\begin{enumerate}
+	\setlength\itemsep{-4px}
+	\item Swiss Chablais
+	\item Trient Valley
+	\item West Bernese Alps
+	\item Lower Rhone Valley
+	\item Left side valleys
+	\item Southern ridges
+	\item Upper Rhone Valley
+	\item Southeast ridges
+	\item East Bernese Alps
+	\item Conches Valley
+\end{enumerate}
 
@@
 
-In order to reduce potential bias related to trends in the climate change or to the evolution in measurement techniques, the selection of the validation period is evenly distributed over the entire series.
+In order to reduce potential bias related to trends in the climate change or to the evolution in measurement techniques, the selection of the validation period is evenly distributed over the entire series \citep{BenDaoud2010}.
 Thus, we select one year every six years for validation, which represents a total of eight years for the validation and forty for calibration.
@@
 We first optimized the analogy of atmospheric circulation alone, without humidity variables.
-We started from the most simple method, and increased the complexity of the method, thus the number of degrees of freedom in order to identify the ones that are of particular interest.
+We started from the most simple analogue method, and increased the complexity in order to identify the degrees of freedom that are of particular interest.
 Thus, the tested parametrization evolved iteratively in complexity.
@@
 Evaluation of atmospheric levels is also a non-automated process in the classic calibration.
-However, we could observe that the choice of this degree of freedom improves the optimization time and may decrease the number of simulations which converge to a single solution.
+However, we could observe that the choice of this degree of freedom increases the optimization time and may decrease the number of simulations that converge to a single solution.
 However, most solutions are very close in terms of score.
@@
 Parallel analyses showed that the analogy of circulation is incomplete, and that the geopotential still contains relevant data that can improve the statistical relationship.
-So we added a third predictor that the optimizer can use along with the previous parameters.
+Therefore, we added a third predictor (still the geopotential height) that the optimizer can use along with the previous parameters.
 There is no constraint on the predictors, so that the same atmospheric level can be selected multiple times.
@@
 We then tried with 4 predictors, and so on, up to 8.
-Every time we added a new predictor to optimize, the score on the calibration period increased, but always in a smaller extent.
+Every time we added a new predictor to optimize, the score on the calibration period increased, but always more in a smaller extent.
 However, the validation period dropped after 4 predictors, revealing an over-parametrization of the method, and thus a lack of robustness.
@@
 
-The method we finally optimized for the analogy of the atmospheric circulation, based on 4 levels of the geopotential, is made of the following degrees of freedom:
+The method we finally optimized for the analogy of the atmospheric circulation, based on 4 levels of the geopotential, and that we will name z4, is made of the following degrees of freedom:
 
@@
 
-\subsubsection{Results of the optimization of atmospheric circulation}
-...
-
-\subsubsection{Discussion}
+\subsubsection{Results for the atmospheric circulation}
+
+The resulting optimized parameters for z4 vary from one groupment to another.
+An example of the detailed parameters is provided for the Swiss Chablais in Table \ref{table:params_GA_z4}.
+The optimized spatial windows are given for every groupment in Figure \ref{fig:spatial_windows_z4}, and the selected atmospheric levels in Table \ref{table:levels_GA_z4}.
+The i
+
+\subsubsection{Analysis}
 ...
@@
 
-\subsubsection{Results of the optimization on both analogy levels}
+\subsubsection{Results for both analogy levels}
 ...
@@
 
-\subsubsection{Discussion}
+\subsubsection{Analysis}
+...
+
+\subsection{Discussion}
 
@@
 	\footnotesize
-	\caption{Parameters of an analogy on the atmospheric circulation (4 levels) optimized for the Chablais region.
-The columns are the followings: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
+	\caption{Parameters of the z4 method (analogy on 4 levels of the atmospheric circulation) optimized for the Chablais region.
+The columns are the following: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
 	\begin{center}
@@
 	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation at the different groupments.}
+	\caption{Atmospheric levels automatically selected for the z4 method at the different groupments.}
 	\begin{center}
@@
 	\footnotesize
-	\caption{Parameters of an analogy on the atmospheric circulation (4 levels) and the humidity index (2 levels), optimized for the Chablais region.
-The columns are the followings: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
-			\hline 
-			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & 0.0 - 15.0 \degree E & \multirow{2}{*}{23\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
-			& & & 42.5 - 55.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{25\%} & & \\ 
-			& & & 40.0 - 45.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
-			& & & 42.5 - 47.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
-			& & & 40.0 - 47.5 \degree N & & & \\ 
-			\hline 
-			\multirow{4}{*}{2} & TPW & \multirow{2}{*}{12~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{57\%} & \multirow{4}{*}{RMSE} & \multirow{4}{*}{25} \\
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{24~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{43\%} & & \\ 
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_GA_z4_hi2}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation at the different groupments.}
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
-			\hline 
-			1  & Z &   & Z &   &   & Z &   & Z \\
-			2  & Z &   &   &   & Z & Z &   & Z \\
-			3  & Z &   &   &   & Z & Z & Z &   \\
-			4  &   &   & Z &   & Z & Z &   & Z \\
-			5  &   & Z &   &   & Z &   & ZZ &   \\
-			6  &   & Z &   &   & Z & Z &   & Z \\
-			7  &   & Z &   &   & Z & Z &   & Z \\
-			8  &   &   & Z &   & Z &   & ZZ &   \\
-			9  &   & Z &   &   & Z & Z & Z &   \\
-			10 &   & Z &   &   & Z & Z &   & Z \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_z4_hi2}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation at the different groupments.}
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
-			\hline 
-			1  &   &   &   &   & HH &   &   &   \\
-			2  &   &   &   &   & HH &   &   &   \\
-			3  &   &   &   &   & HH &   &   &   \\
-			4  &   &   &   & H & H &   &   &   \\
-			5  &   &   &   &   & HH &   &   &   \\
-			6  &   &   &   & H & H &   &   &   \\
-			7  &   &   &   & H & H &   &   &   \\
-			8  &   &   &   & H & H &   &   &   \\
-			9  &   &   &   & H & H &   &   &   \\
-			10 &   &   &   & H & H &   &   &   \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_z4_hi2_H}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Parameters of an analogy on the atmospheric circulation (4 levels) and the humidity index (4 levels), optimized for the Chablais region.
-The columns are the followings: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
-			\hline 
-			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{8}{*}{1} &  \multirow{2}{*}{Z400} & \multirow{2}{*}{6~h} & -5.0 - 12.5 \degree E & \multirow{2}{*}{20\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
-			& & & 45.0 - 52.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
-			& & & 40.0 - 45.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
-			& & & 42.5 - 47.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
-			& & & 40.0 - 47.5 \degree N & & & \\ 
-			\hline 
-			\multirow{8}{*}{2} & TPW & \multirow{2}{*}{24~h} & 7.5 - 10.0 \degree E & \multirow{2}{*}{27\%} & \multirow{8}{*}{RMSE} & \multirow{8}{*}{25} \\
-			& *RH500 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{12~h} & 5.0 - 7.5 \degree E & \multirow{2}{*}{41\%} & & \\ 
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{18~h} & 0.0 - 7.5 \degree E & \multirow{2}{*}{19\%} & & \\ 
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{24~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{13\%} & & \\ 
-			& *RH850 & & 45.0 - 47.5 \degree N & & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_GA_z4_hi4}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation at the different groupments.}
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
-			\hline 
-			1  &   & Z & Z &   &   & Z &   & Z \\
-			2  &   & Z &   &   & ZZ &   &   & Z \\
-			3  &   & Z &   &   & Z & Z & Z &   \\
-			4  &   &   & Z &   & Z & Z &   & Z \\
-			5  &   & Z & Z &   &   & Z &   & Z \\
-			6  &   & Z & Z &   &   & Z &   & Z \\
-			7  &   & Z &   &   & ZZ &   &   & Z \\
-			8  &   &   & Z & Z &   & Z &   & Z \\
-			9  &   & Z &   &   & Z & Z & Z &   \\
-			10 &   & Z & Z &   &   & ZZ &   &   \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_z4_hi4}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation at the different groupments.}
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
-			\hline 
-			1  &   &   & H &   & HH & H &   &   \\
-			2  &   &   &   & H & HH & H &   &   \\
-			3  &   &   &   & H & HHH &   &   &   \\
-			4  &   &   &   & HH & HH &   &   &   \\
-			5  &   &   &   & HH & HH &   &   &   \\
-			6  &   &   &   & HH & H & H &   &   \\
-			7  &   &   &   & HH & H & H &   &   \\
-			8  &   &   &   & HH & H & H &   &   \\
-			9  &   &   & H & H & H & H &   &   \\
-			10 &   &   &   & H & HH & H &   &   \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_z4_hi4_H}
-\end{table}
-
-\clearpage
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 1, calibration period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4_calib.pdf}}
-	\label{table:crossing_z4_calib}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 1, validation period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4_valid.pdf}}
-	\label{table:crossing_z4_valid}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 2, calibration period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_calib.pdf}}
-	\label{table:crossing_z4-hi2_calib}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 2, validation period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_valid.pdf}}
-	\label{table:crossing_z4-hi2_valid}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 3, calibration period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_calib.pdf}}
-	\label{table:crossing_z4-hi4_calib}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 3, validation period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_valid.pdf}}
-	\label{table:crossing_z4-hi4_valid}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized analogy of atmospheric circulation.}
+	\caption{Improvement (\%) of the CRPSS of the three methods.
+For z4, the improvement is relative to the reference method on the atmospheric circulation.
+For z4-hi2 and z4-hi4, the improvement is relative to the reference method on the circulation and humidity variables.}
 	\begin{center}
@@
 	\footnotesize
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized analogy of atmospheric circulation.}
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4 method.}
 	\begin{center}
@@
 			\hline 
-			\textbf{ID} & \multicolumn{2}{c}{\textbf{$P\geq1 mm$}} & \multicolumn{2}{c}{\textbf{$P\geq1 0.1\cdot P10$}} & \multicolumn{2}{c}{\textbf{$P\geq1 0.5\cdot P10$}} \\ 
+			\textbf{ID} & \multicolumn{2}{c}{\textbf{P\(\geq\)1 mm}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.1\(\cdot\)P10}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.5\(\cdot\)P10}} \\ 
 			\hline 
@@
 
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4, calibration period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4_calib.pdf}}
+	\label{table:crossing_z4_calib}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4, validation period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4_valid.pdf}}
+	\label{table:crossing_z4_valid}
+\end{table}
+
+\clearpage
+
 \begin{table}[htbp]
 	\footnotesize
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized analogy of atmospheric circulation and humidity variables (2 levels).}
+	\caption{Parameters of the z4-hi2 method (atmospheric circulation on 4 levels and humidity index on 2 levels), optimized for the Chablais region.
+The columns are the followings: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
+	\begin{center}
+		\begin{tabular}{ccccccc}
+			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
+			\hline 
+			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & 0.0 - 15.0 \degree E & \multirow{2}{*}{23\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
+			& & & 42.5 - 55.0 \degree N & & & \\ 
+			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{25\%} & & \\ 
+			& & & 40.0 - 45.0 \degree N & & & \\ 
+			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
+			& & & 42.5 - 47.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
+			& & & 40.0 - 47.5 \degree N & & & \\ 
+			\hline 
+			\multirow{4}{*}{2} & TPW & \multirow{2}{*}{12~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{57\%} & \multirow{4}{*}{RMSE} & \multirow{4}{*}{25} \\
+			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
+			& TPW & \multirow{2}{*}{24~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{43\%} & & \\ 
+			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:params_GA_z4_hi2}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation of the z4-hi2 method, at the different groupments.}
+	\begin{center}
+		\begin{tabular}{ccccccccc}
+			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
+			\hline 
+			1  & Z &   & Z &   &   & Z &   & Z \\
+			2  & Z &   &   &   & Z & Z &   & Z \\
+			3  & Z &   &   &   & Z & Z & Z &   \\
+			4  &   &   & Z &   & Z & Z &   & Z \\
+			5  &   & Z &   &   & Z &   & ZZ &   \\
+			6  &   & Z &   &   & Z & Z &   & Z \\
+			7  &   & Z &   &   & Z & Z &   & Z \\
+			8  &   &   & Z &   & Z &   & ZZ &   \\
+			9  &   & Z &   &   & Z & Z & Z &   \\
+			10 &   & Z &   &   & Z & Z &   & Z \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:levels_GA_z4_hi2}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Atmospheric levels automatically selected for the analogy of humidity of the z4-hi2 method, at the different groupments.}
+	\begin{center}
+		\begin{tabular}{ccccccccc}
+			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
+			\hline 
+			1  &   &   &   &   & HH &   &   &   \\
+			2  &   &   &   &   & HH &   &   &   \\
+			3  &   &   &   &   & HH &   &   &   \\
+			4  &   &   &   & H & H &   &   &   \\
+			5  &   &   &   &   & HH &   &   &   \\
+			6  &   &   &   & H & H &   &   &   \\
+			7  &   &   &   & H & H &   &   &   \\
+			8  &   &   &   & H & H &   &   &   \\
+			9  &   &   &   & H & H &   &   &   \\
+			10 &   &   &   & H & H &   &   &   \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:levels_GA_z4_hi2_H}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi2 method.}
 	\begin{center}
@@
 
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, calibration period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_calib.pdf}}
+	\label{table:crossing_z4-hi2_calib}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, validation period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_valid.pdf}}
+	\label{table:crossing_z4-hi2_valid}
+\end{table}
+
+\clearpage
+
 \begin{table}[htbp]
 	\footnotesize
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized analogy of atmospheric circulation and humidity variables (4 levels).}
+	\caption{Parameters of the z4-hi4 method (atmospheric circulation on 4 levels and humidity index on 4 levels), optimized for the Chablais region.
+The columns are the followings: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
+	\begin{center}
+		\begin{tabular}{ccccccc}
+			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
+			\hline 
+			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{8}{*}{1} &  \multirow{2}{*}{Z400} & \multirow{2}{*}{6~h} & -5.0 - 12.5 \degree E & \multirow{2}{*}{20\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
+			& & & 45.0 - 52.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
+			& & & 40.0 - 45.0 \degree N & & & \\ 
+			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
+			& & & 42.5 - 47.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
+			& & & 40.0 - 47.5 \degree N & & & \\ 
+			\hline 
+			\multirow{8}{*}{2} & TPW & \multirow{2}{*}{24~h} & 7.5 - 10.0 \degree E & \multirow{2}{*}{27\%} & \multirow{8}{*}{RMSE} & \multirow{8}{*}{25} \\
+			& *RH500 & & 45.0 - 47.5 \degree N & & & \\ 
+			& TPW & \multirow{2}{*}{12~h} & 5.0 - 7.5 \degree E & \multirow{2}{*}{41\%} & & \\ 
+			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
+			& TPW & \multirow{2}{*}{18~h} & 0.0 - 7.5 \degree E & \multirow{2}{*}{19\%} & & \\ 
+			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
+			& TPW & \multirow{2}{*}{24~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{13\%} & & \\ 
+			& *RH850 & & 45.0 - 47.5 \degree N & & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:params_GA_z4_hi4}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation of the z4-hi4 method, at the different groupments.}
+	\begin{center}
+		\begin{tabular}{ccccccccc}
+			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
+			\hline 
+			1  &   & Z & Z &   &   & Z &   & Z \\
+			2  &   & Z &   &   & ZZ &   &   & Z \\
+			3  &   & Z &   &   & Z & Z & Z &   \\
+			4  &   &   & Z &   & Z & Z &   & Z \\
+			5  &   & Z & Z &   &   & Z &   & Z \\
+			6  &   & Z & Z &   &   & Z &   & Z \\
+			7  &   & Z &   &   & ZZ &   &   & Z \\
+			8  &   &   & Z & Z &   & Z &   & Z \\
+			9  &   & Z &   &   & Z & Z & Z &   \\
+			10 &   & Z & Z &   &   & ZZ &   &   \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:levels_GA_z4_hi4}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Atmospheric levels automatically selected for the analogy of humidity of the z4-hi4 method,at the different groupments.}
+	\begin{center}
+		\begin{tabular}{ccccccccc}
+			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
+			\hline 
+			1  &   &   & H &   & HH & H &   &   \\
+			2  &   &   &   & H & HH & H &   &   \\
+			3  &   &   &   & H & HHH &   &   &   \\
+			4  &   &   &   & HH & HH &   &   &   \\
+			5  &   &   &   & HH & HH &   &   &   \\
+			6  &   &   &   & HH & H & H &   &   \\
+			7  &   &   &   & HH & H & H &   &   \\
+			8  &   &   &   & HH & H & H &   &   \\
+			9  &   &   & H & H & H & H &   &   \\
+			10 &   &   &   & H & HH & H &   &   \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:levels_GA_z4_hi4_H}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi4 method.}
 	\begin{center}
@@
 			\hline 
-			\textbf{ID} & \multicolumn{2}{c}{\textbf{P$\geq1$ mm}} & \multicolumn{2}{c}{\textbf{P$\geq1$ 0.1$\cdot$ P10}} & \multicolumn{2}{c}{\textbf{$P\geq1 0.5\cdot P10$}} \\ 
+			\textbf{ID} & \multicolumn{2}{c}{\textbf{P\(\geq\)1 mm}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.1\(\cdot\)P10}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.5\(\cdot\)P10}} \\ 
 			\hline 
@@
 
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi4, calibration period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_calib.pdf}}
+	\label{table:crossing_z4-hi4_calib}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi4, validation period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_valid.pdf}}
+	\label{table:crossing_z4-hi4_valid}
+\end{table}
+
 \clearpage
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.3cm]{figures/figure_map.pdf}}
-	\caption{Location of the alpine Rhône catchment in Switzerland. (source: Swisstopo)}
-	\label{fig:map}
-\end{figure}
-
-\begin{figure}[htb]
 	\centerline{\includegraphics[width=8.3cm]{figures/figure_structure_gas.pdf}}
@@
 \begin{figure}[htb]
+	\centerline{\includegraphics[width=8.3cm]{figures/figure_map.pdf}}
+	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland. (source: Swisstopo)}
+	\label{fig:map}
+\end{figure}
+
+\begin{figure}[htb]
 	\centering
@@
 	\end{subfigure}
-	\caption{Optimized spatial windows for the analogy of atmospheric circulation on 4 atmospheric levels.
+	\caption{Optimized spatial windows for the z4 method (analogy of atmospheric circulation on 4 atmospheric levels).
 The atmospheric levels are ordered by increasing pressure and increasing time for the same levels.}
@@
 	\end{subfigure}
-	\caption{Optimized spatial windows for the analogy of atmospheric circulation on 4 atmospheric levels and the analogy on the humidity index on 2 atmospheric levels.
+	\caption{Optimized spatial windows for the z4-hi2 method (analogy of atmospheric circulation on 4 atmospheric levels and the analogy on the humidity index on 2 atmospheric levels).
 The atmospheric levels are ordered by increasing pressure and increasing time for the same levels.}
@@
 	\end{subfigure}
-	\caption{Optimized spatial windows for the analogy of atmospheric circulation on 4 atmospheric levels and the analogy on the humidity index on 4 atmospheric levels.
+	\caption{Optimized spatial windows for the z4-hi4 method (analogy of atmospheric circulation on 4 atmospheric levels and the analogy on the humidity index on 4 atmospheric levels).
 The atmospheric levels are ordered by increasing pressure and increasing time for the same levels.}

### 2015-08-05 Optimization - Journal of Climate/template.tex
Writing the analysis of the circulation optimization.

@@
 The optimized spatial windows are given for every groupment in Figure \ref{fig:spatial_windows_z4}, and the selected atmospheric levels in Table \ref{table:levels_GA_z4}.
-The i
+
+The improvement of the CRPSS score relatively to the reference method on the atmospheric circulation is provided in Table \ref{table:scores} and is in average of 15.3 \% in calibration and 9.9 \% in validation.
+The score was also calculated for three precipitation thresholds: P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_z4}).
+The score increases with the precipitation threshold: in average, respectively, 13.3\%, 15.4\% and 29.1\% in calibration and 7.9\%, 11.1\% and 34.5\% for the validation period.
+The optimized method improves thus even more days with significant precipitation than standard days.
+
+To assess the cross-compatibility of the parameters, we applied those optimized for one groupment to the others.
+The resulting losses or gains of the CRPSS are displayed in Table \ref{table:crossing_z4_calib} for the calibration period and in Table \ref{table:crossing_z4_valid} for the validation period.
 
 \subsubsection{Analysis}
-...
+
+The choices of the atmospheric levels for the analogy of circulation show a great homogeneity and is spatially consistent (Table \ref{table:levels_GA_z4}).
+First of all, the level 1000~hPa is selected twice (the first time at 6 or 12~h, and the second always at 30~h) and the 700~hPa is selected once for every region (always at 24~h).
+The level which varies from one region to another is the upper level (always at 12~h), that is 300~hPa for the North-West part of the catchment, 500~hPa for most of the groupments, and 600~hPa for the Conches Valley.
+Its spatial distribution is however homogeneous.
+The optimizer thus provided consistent choices of atmospheric levels and temporal windows, which depicts a significant preference in the analogue method, and the success of our GAs to provide consistent results.
+The automatic choice of the atmospheric levels is a big advantage of a global optimization, as it was not possible to assess all combinations of 4 levels with the classic calibration procedure.
+
+The resulting spatial windows (Figure \ref{fig:spatial_windows_z4}) may look very diverse first, but there are significant similarities for groupments located within the same vicinity.
+The first 4 groupments are characterized by a large spatial window on the upper level, whereas it becomes smaller for the other regions.
+For most groupments, the second level (700~hPa) is represented by thin and longitudinally extended domains.
+The third level (1000~hPa at 6 or 12~h) also contains longitudinally extended domains, but a bit larger.
+The last one (1000~hPa at 30~h) is rather large and squared.
+Surprisingly, regions number 5 (Left side valleys) and 6 (Southern ridges) have exactly the same spatial windows, which suggest that they behave in a similar way and thus could have been merged.
+This similarity is a good sign for the accuracy of our optimized parameters.
+
+The scores show significant improvements for both the calibration and the validation period (Table \ref{table:scores}).
+Even more interestingly, the results for higher precipitation thresholds (Table \ref{table:scores_thresholds_z4}) show the largest improvements.
+This is of particular interest in the framework of flood forecasting.
+
+The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the calibration period when they are calibrated for the given groupment (Table \ref{table:crossing_z4_calib}).
+However, the losses in CRPSS are not of the same amplitude between the different regions.
+Indeed, the Upper Rhone Valley (7) and moreover the Southeast ridges (8) seem to behave significantly differently.
+Parameter sets from other regions perform poorly for these groupments, and vice versa.
+Nevertheless, both groupments seem quite inter-compatible.
+This points to the importance of taking into account leading meteorological influences during groupment creation, which is not always best represented by the distance separating them.
+Globally, the same pattern can be observed for the validation period (Table \ref{table:crossing_z4_valid}), but in this case, minor improvements may be observed when crossing the parameters.
+The reason being that the independant validation period contains other events that may be better forecasted by other parameters sets.
+The relative small differences in score between parametrizations indicate that even though the parameters may differ significantly, the performance may not be drastically affected.
+Even a change in the atmospheric level does not mean a radical drop of the score.
+A different parametrization leads to a different selection of the analogue days, and thus to an improvement of the forecast of certain weather conditions at the expense of others.
+This raises the question of optimizing more specifically for extreme weather conditions only.
 
@@
 	\end{center}
-	\label{table:scores_z4}
+	\label{table:scores_thresholds_z4}
 \end{table}
@@
 	\end{center}
-	\label{table:scores_z4-hi2}
+	\label{table:scores_thresholds_z4-hi2}
 \end{table}
@@
 	\end{center}
-	\label{table:scores_z4-hi4}
+	\label{table:scores_thresholds_z4-hi4}
 \end{table}

### 2015-08-12 Optimization - Journal of Climate/template.tex
Discussion and conclusions.

@@
 % DOUBLE-SPACED VERSION FOR SUBMISSION TO THE AMS
-%\documentclass{ametsoc}
+\documentclass{ametsoc}
 
 % TWO-COLUMN JOURNAL PAGE LAYOUT---FOR AUTHOR USE ONLY
-\documentclass[twocol]{ametsoc}
+%\documentclass[twocol]{ametsoc}
 
@@
 
-\authors{Pascal Horton\correspondingauthor{Terranum, Rue de l'industrie 35 bis, 1030 Bussigny-pr\`{e}s-Lausanne, Switzerland.}}
+\authors{Pascal Horton\correspondingauthor{Terranum, Rue de l'industrie 35 bis, 1030 Bussigny, Switzerland.}}
 
@@
 
-\affiliation{University of Lausanne, and Terranum,  Bussigny-pr\`{e}s-Lausanne, Switzerland}
+\affiliation{University of Lausanne and Terranum, Lausanne, Switzerland}
 
@@
 
-\email{pascal.horton@terranum.ch}
+\email{pascal.horton@alumnil.unil.ch}
 
@@
 
-\subsubsection{Results for the atmospheric circulation}
+\subsubsection{Results for the z4 method}
 
@@
 
-The improvement of the CRPSS score relatively to the reference method on the atmospheric circulation is provided in Table \ref{table:scores} and is in average of 15.3 \% in calibration and 9.9 \% in validation.
+The resulting CRPSS scores are provided in Table \ref{table:scores} and is in average 35.8 \% in calibration and 35.5 \% in validation.
+The improvement of the CRPSS score relatively to the reference method on the atmospheric circulation is provided in Table \ref{table:scores_diff} and is in average 15.3 \% in calibration and 9.9 \% in validation.
 The score was also calculated for three precipitation thresholds: P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_z4}).
@@
 
-The scores show significant improvements for both the calibration and the validation period (Table \ref{table:scores}).
+The scores show significant improvements for both the calibration and the validation period (Table \ref{table:scores_diff}).
 Even more interestingly, the results for higher precipitation thresholds (Table \ref{table:scores_thresholds_z4}) show the largest improvements.
@@
 
-%Nous avons cherché à identifier quelle part du gain est attribuable à quel nouveau degré de liberté par rapport à la méthode M6.
-De manière générale, nous avons remarqué qu'il y a une forte dépendance entre ces paramètres (fenêtres spatiales, fenêtres temporelles et pondération des niveaux atmosphériques), et qu'il n'est pas recommandable de les considérer séparément.
-Par exemple, l'introduction des poids (non réoptimisés) dans les paramètres de la méthode M6 a un effet en moyenne nul, mais peut engendrer des pertes non négligeables sur les scores de certains groupements.
-
-%An evaluation of all these parameters with the classic calibration requires multiple assessments of all possible combinations.
-In addition, these studies are often carried out with a spatial window of fixed size and a fixed number of analogues.
-So we hope to find solutions as good or better, but automatically.
-
 \subsection{Optimization of the analogy with humidity variables}
@@
 
+Two methods were assessed: one with 2 humidity predictors (humidity index on 2 atmospheric levels or at 2 different hours) named z4-hi2, and one with 4 humidity predictors named z4-hi4.
+When we introduce 2 predictors for the humidity analogy, the number of degrees of freedom raises to 42, and to 54 when we add 4 predictors.
+
 We proceeded to an optimization of both levels of analogy simultaneously. This implies that the analogy of the atmospheric circulation may change due to the new humidity information.
 
-When we introduce 2 predictors for the humidity analogy, the number of degrees of freedom raises to 42, and to 54 when we add 4 predictors.
-
-%We tried first to optimize the humidity predictors while keeping the same parameters for the first level of analogy on the atmospheric circulation.
-The results were not really satisfying, mainly on the scores of the validation.
--> POUR FLUX !
-
-\subsubsection{Results for both analogy levels}
-...
-
-%Ces optimisations ont mené à des paramétrisations différentes de l'analogie de circulation par rapport à précédemment.
-Il existe donc bien des relations entre les paramètres des différents niveaux d'analogie, soit entre la circulation atmosphérique et le flux d'humidité.
-Ainsi, en connaissance de l'information du flux d'humidité, la méthode préférera une représentation différente de la circulation.
-Cet aspect n'a encore jamais été mis en évidence, car les outils habituels de calibration ne le permettent pas.
-
-%Pour tenir compte des dépendances entre les paramètres des différents niveaux d'analogie, il est nécessaire d'utiliser une méthode d'optimisation globale telle que les AGs.
+\subsubsection{Results for z4-hi2 and z4-hi4 methods}
+
+As previously, the optimized parameters differ from one region to another, and this event to a greater extent.
+Detailed examples are still provided for the Swiss Chablais region in Table \ref{table:params_GA_z4_hi2} for z4-hi2 and in Table \ref{table:params_GA_z4_hi4} for z4-hi4.
+The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_z4-hi2} for z4-hi2, along with the selected atmospheric levels for the circulation analogy (Table \ref{table:levels_GA_z4_hi2}) and the humidity analogy (Table \ref{table:levels_GA_z4_hi2_H}).
+Correspondingly, for the method z4-hi4, the spatial windows are shown in Figure \ref{fig:spatial_windows_z4-hi4} and the selected atmospheric levels are presented in Tables \ref{table:levels_GA_z4_hi4} and \ref{table:levels_GA_z4_hi4_H}.
+
+The CRPSS scores of the optimized methods are provided in Table \ref{table:scores} and amounts to slightly more than 40 \% for both methods and for both periods.
+This results in a relative improvements that ranges from 11.5 \% to 15.6 \% compared to the reference method on the humidity analogy (Table \ref{table:scores_diff}).
+As for the method z4, methods z4-hi2 and z4-hi4 present improvements of the forecast of significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
+The improvement are relatively similar for z4-hi2 (Table \ref{table:scores_thresholds_z4-hi2}) and z4-hi4 (Table \ref{table:scores_thresholds_z4-hi4}), with slightly superior scores for the latter on small precipitation (P\(\geq\)1 mm) and extremes (P\(\geq\)0.5\(\cdot\)P10).
+
+The parameters cross-compatibility has also been assessed for the methods with humidity variables, and are shown in Tables \ref{table:crossing_z4-hi2_calib} and \ref{table:crossing_z4-hi2_valid} for the method z4-hi2, and Tables \ref{table:crossing_z4-hi4_calib} and \ref{table:crossing_z4-hi4_valid} for z4-hi4.
 
 \subsubsection{Analysis}
-...
+
+When optimizing a method made of 2 levels of analogy, the introduction of humidity variables in the second level has an influence on the parameter values of the first level.
+This is first visible on the choice of the atmospheric levels for the circulation analogy, where the 1000~hPa that was previously systematically selected twice (Table \ref{table:levels_GA_z4}) is now less chosen (once or even not at all) for both za-hi2 (Table \ref{table:levels_GA_z4_hi2}) and za-hi4 (Table \ref{table:levels_GA_z4_hi4}).
+There is indeed a shift of the previously selected 1000~hPa for higher levels, which is even slightly stronger with 4 humidity predictors than with 2.
+This change is likely due to the fact that when considering only the circulation analogy, the method tries to take into account information that can serve as proxy for humidity assessment, whereas it doesn't need it with the humidity index.
+This aspect has never been demonstrated, as usual calibration tools do not allow it.
+It can only be assessed by a global optimization technique that can tune jointly both levels of analogy.
+
+The selected levels for the analogy on the humidity index is strongly centred around the 700~hPa and 600~hPa.
+No other value has been selected when considering 2 atmospheric levels (Table \ref{table:levels_GA_z4_hi2_H}), and when considering 4 levels, the 850~hPa is quite often chosen, and the 500~hPa more rarely.
+However, even is this latter method, the 700~hPa and 600~hPa still hold 78 \% of the selected levels.
+It is thus more efficient to consider one of this level multiple times at different hours rather than using another atmospheric level.
+Besides, the optimizer never chose the same atmospheric level at the same hour for any variable.
+
+The choice of the temporal windows for the atmospheric circulation is similar to the preceding optimization (in the order of increasing pressure: 12~h, 24/30~h, 12~h, 30~h), but sometimes with a bit more variability.
+When it comes to the humidity analogy, there is a clear trend to select 12~h and 24~h when considering 2 predictors.
+The z4-hi4 method presents more variability on the choice of the temporal windows for the humidity index.
+
+The optimized spatial windows on the atmospheric circulation have also changed (Figures \ref{fig:spatial_windows_z4-hi2} and \ref{fig:spatial_windows_z4-hi4}).
+The very large domains on the upper level of the 4 first groupments are not present anymore, and more variability can be observed.
+The selected points for the analogy on the humidity index are always located nearby the catchment, including 1 of the nearest point from the reanalysis dataset, and the spatial windows are relatively small.
+Thus, for our case study, there is no need to look for distant humidity information and the search could be reduced to a smaller domain.
+
+The CRPSS scores were improved by considering the humidity information (Table \ref{table:scores}).
+The optimized methods also perform better than the reference method based on the humidity index (Table \ref{table:scores_diff}).
+However, there is no drastic difference between both z4-hi2 and z4-hi4 methods, which suggests that considering 4 humidity predictors is not absolutely necessary.
+When it comes to improvements for days with precipitation above our 3 thresholds (P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the forecast, mainly for heavy rainfall.
+
+The analysis of the parameters cross-compatibility (Tables \ref{table:crossing_z4-hi2_calib} to \ref{table:crossing_z4-hi4_valid}) is also very similar to the one on the circulation analogy only.
+The same pattern can be observed, with a drop of performance for the regions under different meteorological influences.
+However, the losses of performance are globally more important than before, suggesting that more complex methods with humidity variables are less transposable to another region, even though it is location within the same grid of the reanalysis dataset.
 
@@
 Indeed, the synoptic circulation is characterized by features with very different scales depending on the height, and important information for predicting rainfall is not necessarily located in the same area from one level to another.
+The optimized spatial windows are consistent in between the groupments.
 	\item The weighting of the analogy criteria between different atmospheric levels.
 It can be influenced by the variability of the geopotential with altitude, and the change of some levels significance with the targeted region.
+There is a trend for the weighting of circulation predictors to decrease with the increase in pressure, as one can see in Figure \ref{fig:levels_weights} for the method z4, and in Figure \ref{fig:levels_weights_average} for the averages over the 3 methods.
+However, the values stay around equity.
+This may not be the most influencing factor, and we may suggest to remove it first when trying to reduce the number of degrees of freedom.
 	\item The joint optimization of the circulation and humidity analogy levels, that are usually calibrated successively.
@@
 The optimizer do not always converge to the exact global optimum, but to its surroundings.
-This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that we have to stop it before the end due to the required processing time.
+This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that we have to stop it before the end, due to the required processing time (see Figure \ref{fig:evolution} as example).
 The resulting parameters may sometimes present significant differences, even though the score is almost similar.
@@
 We also tried optimizing the humidity flux, which is composed of the humidity index multiplied with the wind flux.
-However, the results were not as good as when we considered the humidity index alone.
+However, the results were not better than when we considered the humidity index alone.
 This may be related to the fact that the optimizer tries to provide the best analogy of the atmospheric circulation in the first place, which makes the wind information less relevant in the second level of analogy.
+
+As we could observe, methods with a higher complexity that integrate humidity predictors are less transposable than simpler ones.
+We also noticed in another unpublished work, that it is by far better to optimize for 2 regions jointly rather than to optimize on one and to apply its parametrization to the other.
+Finally, the creation of the groupments is an important stage and should be handled with care.
+Indeed, as we could observe, the geographical proximity is not always the leading factor to define a groupment.
+For example, the Southeast ridges groupment do not behave like its surrounding and differ in its parametrization, due to different leading meteorological influences.
 
@@
 
-% Cet aspect a été confirmé par l'optimisation, qui propose de petites fenêtres pour les niveaux supérieurs, et de grandes fenêtres pour les altitudes proches du sol.
-Notre hypothèse est que l'information des gradients des couches supérieures au-dessus du bassin suffit à résumer l'orientation et la vitesse des masses d'air d'intérêt, qui sont potentiellement liées à un forçage par-dessus la barrière orographique.
-De manière complémentaire, les fenêtres plus étendues pour les basses couches cherchent à intégrer la structure de la circulation, car celle-ci renseigne sur les centres actifs et sur le chemin qu'a parcouru la masse d'air éventuellement chargée en humidité avant d'arriver sur la zone d'intérêt.
-
 \section{Conclusions and perspectives}
+
+In order to automatically optimize the analogue method, we evaluated the genetic algorithms, a global optimization technique, that is able to solve complex problems.
+Given the large number of existing operators and options, we had to evaluate systematically multiple variants in order to identify which operators are important, and which variant works best for the analogue method.
+We could thus identify that the mutation operator is a key element for our application, and provided new variants that were found to be efficient, such as the Chromosome of adaptive search radius that seems to be very reliable (no control parameter) and efficient .
+Recommendations were established for a relevant use of GAs for the optimization of the analogue method.
+
+The parameters resulting from the optimization are very consistent for the analogy of the atmospheric circulation, in terms of choice of the pressure levels, and the temporal and spatial windows.
+There are clear trends or even identical results for regions under similar meteorological influences, which confirm that the optimized parameters are coherent, despite an eventual first impression of a great variability in the spatial windows.
+When adding humidity variables, the results show a higher variability, but remains highly acceptable and coherent.
+Indeed, the choice of the pressure level for the humidity index is for example very constant.
 
@@
 Moreover, it contains several manual systematic assessment, such as the choice of the atmospheric levels and the temporal windows.
-
-In order to automatically optimize the analogue method, we evaluated the genetic algorithms, a global optimization technique, that is able to solve complex problems.
-Given the large number of existing operators and options, we had to evaluate systematically multiple variants in order to identify which operators are important, and which variant works best for the analogue method.
-We could thus identify that the mutation operator is a key element for our application, and provided new variants that were found to be efficient.
-Recommendations were established for a relevant use of GAs for the optimization of the analogue method.
-
-GAs provide parametrizations of the analogue method that exceed performance results of classic calibration.
-In addition, they are used to select the atmospheric levels and the time windows automatically, which was not possible with traditional tools and which can save a considerable amount of human time.
+GAs, however, can select the atmospheric levels and the time windows automatically, which can save a considerable amount of human time.
 A great advantage of a global optimization is its ability to approach or reach optimal parameter values when they are considered jointly.
@@
 We have also been able to improve the analogy of circulation by introducing a weighting between atmospheric levels, and considering independent spatial windows between levels.
-
-However, there is a risk of over-parametrization with this type of approach. It is therefore important to always evaluate the proposed parameters over an independent period for validation.
-
-%\item Mutation non uniforme: cet opérateur présente potentiellement le meilleur taux de convergence, pour autant qu'il soit bien paramétré.
-En revanche, si l'évolution de la population n'a pas été correctement estimée au préalable, et que nous choisissons une mauvaise valeur parmi ses trois paramètres, l'optimisation peut être médiocre.
-Son potentiel est donc prometteur, mais l'opérateur est difficile à maîtriser, car les paramètres sont nombreux et leur valeur dépend du problème à optimiser.
+However, there is a risk of over-parametrization with this type of approach.
+It is therefore important to always evaluate the proposed parameters over an independent period for validation.
+
+GAs provide parametrizations of the analogue method that exceed performance results of classic calibration.
+In addition, we could observe that the forecasts for days with strong precipitation were significantly more improved, which is clearly interesting in the framework of flood forecasting.
+
+Perspective .........
+
 %\item Chromosome de rayons de recherche adaptatifs: nous avons élaboré le chromosome de rayons de recherche adaptatifs en nous inspirant du chromosome de taux de mutation adaptatifs.
@@
 Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of.
+Thanks to Renaud Marty for his fruitful collaboration over the years.
 
@@
 	\footnotesize
+	\caption{CRPSS score (\%) of the three optimized methods.}
+	\begin{center}
+		\begin{tabular}{rrarara}
+			\hline 
+			\textbf{ID} & \multicolumn{2}{c}{\textbf{z4}} & \multicolumn{2}{c}{\textbf{z4-hi2}} & \multicolumn{2}{c}{\textbf{z4-hi4}} \\ 
+			\hline 
+			& calib & valid & calib & valid & calib & valid \\ 
+			\hline 
+			\textbf{1} & 40.3 & 38.5 & 45.5 & 43.8 & 45.9 & 43.6 \\ \hline
+			\textbf{2} & 37.8 & 34.9 & 42.4 & 40.8 & 42.9 & 41.3 \\ \hline
+			\textbf{3} & 36.6 & 33.9 & 41.4 & 39.0 & 41.8 & 39.5 \\ \hline
+			\textbf{4} & 31.2 & 30.8 & 36.1 & 36.4 & 36.8 & 37.1 \\ \hline
+			\textbf{5} & 34.4 & 36.5 & 38.6 & 41.4 & 39.2 & 41.8 \\ \hline
+			\textbf{6} & 37.0 & 39.9 & 41.0 & 44.5 & 41.9 & 44.6 \\ \hline
+			\textbf{7} & 30.0 & 30.1 & 33.8 & 34.6 & 34.4 & 34.8 \\ \hline
+			\textbf{8} & 37.7 & 40.1 & 40.7 & 43.1 & 41.2 & 43.3 \\ \hline
+			\textbf{9} & 33.1 & 30.0 & 38.4 & 36.6 & 38.7 & 36.3 \\ \hline
+			\textbf{10} & 40.0 & 40.0 & 42.6 & 42.9 & 43.3 & 43.2 \\ \hline
+			\textbf{av.} & \textbf{35.8} & \textbf{35.5} &\textbf{40.1} & \textbf{40.3} & \textbf{40.6} & \textbf{40.5} \\ \hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:scores}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
 	\caption{Improvement (\%) of the CRPSS of the three methods.
@@
 	\end{center}
-	\label{table:scores}
+	\label{table:scores_diff}
 \end{table}
@@
 	\footnotesize
-	\caption{Parameters of the z4-hi2 method (atmospheric circulation on 4 levels and humidity index on 2 levels), optimized for the Chablais region.
-The columns are the followings: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
+	\caption{Parameters of the z4-hi2 method (atmospheric circulation on 4 levels and humidity index on 2 levels), optimized for the Chablais region. Same conventions as Table \ref{table:params_GA_z4}.}
 	\begin{center}
@@
 	\label{table:params_GA_z4_hi2}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Parameters of the z4-hi4 method (atmospheric circulation on 4 levels and humidity index on 4 levels), optimized for the Chablais region. Same conventions as Table \ref{table:params_GA_z4}.}
+	\begin{center}
+		\begin{tabular}{ccccccc}
+			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
+			\hline 
+			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{8}{*}{1} &  \multirow{2}{*}{Z400} & \multirow{2}{*}{6~h} & -5.0 - 12.5 \degree E & \multirow{2}{*}{20\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
+			& & & 45.0 - 52.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
+			& & & 40.0 - 45.0 \degree N & & & \\ 
+			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
+			& & & 42.5 - 47.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
+			& & & 40.0 - 47.5 \degree N & & & \\ 
+			\hline 
+			\multirow{8}{*}{2} & TPW & \multirow{2}{*}{24~h} & 7.5 - 10.0 \degree E & \multirow{2}{*}{27\%} & \multirow{8}{*}{RMSE} & \multirow{8}{*}{25} \\
+			& *RH500 & & 45.0 - 47.5 \degree N & & & \\ 
+			& TPW & \multirow{2}{*}{12~h} & 5.0 - 7.5 \degree E & \multirow{2}{*}{41\%} & & \\ 
+			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
+			& TPW & \multirow{2}{*}{18~h} & 0.0 - 7.5 \degree E & \multirow{2}{*}{19\%} & & \\ 
+			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
+			& TPW & \multirow{2}{*}{24~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{13\%} & & \\ 
+			& *RH850 & & 45.0 - 47.5 \degree N & & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:params_GA_z4_hi4}
 \end{table}
@@
 	\label{table:levels_GA_z4_hi2_H}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation of the z4-hi4 method, at the different groupments.}
+	\begin{center}
+		\begin{tabular}{ccccccccc}
+			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
+			\hline 
+			1  &   & Z & Z &   &   & Z &   & Z \\
+			2  &   & Z &   &   & ZZ &   &   & Z \\
+			3  &   & Z &   &   & Z & Z & Z &   \\
+			4  &   &   & Z &   & Z & Z &   & Z \\
+			5  &   & Z & Z &   &   & Z &   & Z \\
+			6  &   & Z & Z &   &   & Z &   & Z \\
+			7  &   & Z &   &   & ZZ &   &   & Z \\
+			8  &   &   & Z & Z &   & Z &   & Z \\
+			9  &   & Z &   &   & Z & Z & Z &   \\
+			10 &   & Z & Z &   &   & ZZ &   &   \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:levels_GA_z4_hi4}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Atmospheric levels automatically selected for the analogy of humidity of the z4-hi4 method,at the different groupments.}
+	\begin{center}
+		\begin{tabular}{ccccccccc}
+			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
+			\hline 
+			1  &   &   & H &   & HH & H &   &   \\
+			2  &   &   &   & H & HH & H &   &   \\
+			3  &   &   &   & H & HHH &   &   &   \\
+			4  &   &   &   & HH & HH &   &   &   \\
+			5  &   &   &   & HH & HH &   &   &   \\
+			6  &   &   &   & HH & H & H &   &   \\
+			7  &   &   &   & HH & H & H &   &   \\
+			8  &   &   &   & HH & H & H &   &   \\
+			9  &   &   & H & H & H & H &   &   \\
+			10 &   &   &   & H & HH & H &   &   \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:levels_GA_z4_hi4_H}
 \end{table}
@@
 
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, calibration period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_calib.pdf}}
-	\label{table:crossing_z4-hi2_calib}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, validation period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_valid.pdf}}
-	\label{table:crossing_z4-hi2_valid}
-\end{table}
-
-\clearpage
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Parameters of the z4-hi4 method (atmospheric circulation on 4 levels and humidity index on 4 levels), optimized for the Chablais region.
-The columns are the followings: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
-			\hline 
-			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{8}{*}{1} &  \multirow{2}{*}{Z400} & \multirow{2}{*}{6~h} & -5.0 - 12.5 \degree E & \multirow{2}{*}{20\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
-			& & & 45.0 - 52.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
-			& & & 40.0 - 45.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
-			& & & 42.5 - 47.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
-			& & & 40.0 - 47.5 \degree N & & & \\ 
-			\hline 
-			\multirow{8}{*}{2} & TPW & \multirow{2}{*}{24~h} & 7.5 - 10.0 \degree E & \multirow{2}{*}{27\%} & \multirow{8}{*}{RMSE} & \multirow{8}{*}{25} \\
-			& *RH500 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{12~h} & 5.0 - 7.5 \degree E & \multirow{2}{*}{41\%} & & \\ 
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{18~h} & 0.0 - 7.5 \degree E & \multirow{2}{*}{19\%} & & \\ 
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{24~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{13\%} & & \\ 
-			& *RH850 & & 45.0 - 47.5 \degree N & & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_GA_z4_hi4}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation of the z4-hi4 method, at the different groupments.}
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
-			\hline 
-			1  &   & Z & Z &   &   & Z &   & Z \\
-			2  &   & Z &   &   & ZZ &   &   & Z \\
-			3  &   & Z &   &   & Z & Z & Z &   \\
-			4  &   &   & Z &   & Z & Z &   & Z \\
-			5  &   & Z & Z &   &   & Z &   & Z \\
-			6  &   & Z & Z &   &   & Z &   & Z \\
-			7  &   & Z &   &   & ZZ &   &   & Z \\
-			8  &   &   & Z & Z &   & Z &   & Z \\
-			9  &   & Z &   &   & Z & Z & Z &   \\
-			10 &   & Z & Z &   &   & ZZ &   &   \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_z4_hi4}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of humidity of the z4-hi4 method,at the different groupments.}
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
-			\hline 
-			1  &   &   & H &   & HH & H &   &   \\
-			2  &   &   &   & H & HH & H &   &   \\
-			3  &   &   &   & H & HHH &   &   &   \\
-			4  &   &   &   & HH & HH &   &   &   \\
-			5  &   &   &   & HH & HH &   &   &   \\
-			6  &   &   &   & HH & H & H &   &   \\
-			7  &   &   &   & HH & H & H &   &   \\
-			8  &   &   &   & HH & H & H &   &   \\
-			9  &   &   & H & H & H & H &   &   \\
-			10 &   &   &   & H & HH & H &   &   \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_z4_hi4_H}
-\end{table}
-
 \begin{table}[htbp]
@@
 \begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, calibration period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_calib.pdf}}
+	\label{table:crossing_z4-hi2_calib}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, validation period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_valid.pdf}}
+	\label{table:crossing_z4-hi2_valid}
+\end{table}
+
+\begin{table}[htb]
 	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi4, calibration period.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.3cm]{figures/figure_structure_gas.pdf}}
+	\centerline{\includegraphics[width=7.9cm]{figures/figure_structure_gas.pdf}}
 	\caption{Genetic algorithms operational flowchart}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.3cm]{figures/figure_map.pdf}}
+	\centerline{\includegraphics[width=7.9cm]{figures/figure_map.pdf}}
 	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland. (source: Swisstopo)}
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_1.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_1.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_2.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_2.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_3.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_3.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_4.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_4.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_5.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_5.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_6.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_6.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_7.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_7.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_8.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_8.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_9.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_9.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_10.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_10.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_1.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_1.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_2.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_2.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_3.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_3.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_4.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_4.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_5.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_5.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_6.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_6.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_7.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_7.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_8.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_8.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_9.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_9.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_10.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_10.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_1.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_1.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_2.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_2.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_3.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_3.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_4.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_4.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_5.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_5.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_6.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_6.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_7.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_7.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_8.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_8.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_9.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_9.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_10.png}
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_10.png}
 	\end{subfigure}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.3cm]{figures/figure_levels_weights.pdf}}
-	\caption{Optimized weighting for the atmospheric levels of the circulation analogy.}
+	\centerline{\includegraphics[width=7.9cm]{figures/figure_levels_weights.pdf}}
+	\caption{Optimized weighting for the atmospheric levels of the z4 method.}
 	\label{fig:levels_weights}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.3cm]{figures/figure_levels_weights_average.pdf}}
-	\caption{Optimized weighting for the atmospheric levels of the circulation analogy.}
+	\centerline{\includegraphics[width=7.9cm]{figures/figure_levels_weights_average.pdf}}
+	\caption{Averaged weighting for the atmospheric levels of the circulation analogy of the three methods.}
 	\label{fig:levels_weights_average}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.3cm]{figures/figure_evolution.pdf}}
+	\centerline{\includegraphics[width=7.9cm]{figures/figure_evolution.pdf}}
 	\caption{Example of the best individuals evolution of 8 independent optimizations.}

### 2015-08-12 Optimization - Journal of Climate/template.tex
Personal corrections.

@@
 
-\abstract{Enter the text of your abstract here.}
+\abstract{The analogues method is based on a statistical relationship between synoptic atmospheric variables and local weather, which we aim at forecasting.
+This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic procedure.
+This classic calibration is relatively fast and provide acceptable results, but it has strong constraints, is made of successive steps and thus cannot handle parameters dependencies, and mainly, it cannot calibrate automatically some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared.
+In order to surpass these limitations, we assessed a global optimization technique, namely genetic algorithms, that can optimize jointly all parameters of the method and thus provide a global optimum by taking into account the parameters dependencies.
+Moreover, it can calibrate parameters that were previously manually assessed, and can take into account new degrees of freedom that were unthinkable before.
+These kind of optimization techniques need however to be tailored to the problem to solve.
+We had to assess multiple combinations of algorithms, and even to develop new operators, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of genetic algorithms to optimize the analogue method.
+These recommendations are the primary outcome of this work, as it opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.
+We then applied the optimizer to the Rh\^{o}e catchment in the Swiss Alps and obtained coherent results which significantly improve the performance of the forecasting by analogy.
+The optimizer allowed us to calibrate jointly all parameters of the method and to add a weighting of the criteria per pressure level, as well as non-overlapping spatial windows.}
 
@@
 \section{Introduction}
-
-The analogue method is a downscaling technique based on the idea expressed by \citet{Lorenz1969}.
+\label{section_intro}
+
+The analogue method is a downscaling technique based on the idea expressed by \citet{Lorenz1969}, that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Bontron2005}.
 It aims at forecasting a predictand, often the daily precipitation, on the basis of predictor variables describing the synoptic atmospheric circulation.
-Its main hypothesis is that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Bontron2005}.
+Many parameters define this relationship, which are usually calibrated by means of a semi-automatic procedure.
 
@@
 
-Multiple variations of the methods are possible, and some aspects and parameters will not be detailed hereafter.
-There are mainly 2 implementations that are used most often: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on humidity variables \citep{Obled2002, Bontron2005, Marty2012}.
-
-The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): For a target date, we evaluate the similarity of the atmospheric circulation with every day of the archive by processing the S1 criteria \citep[Eq.\ (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
-\citet{Bontron2005} showed that the geopotential heights at 500~hPa and 1000~hPa are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criteria performs better than scores based on absolute distances.
-The reason for such better results is that the S1 criteria allows comparing the circulation pattern, by means of the gradients, rather than the absolute value of the geopotential heights.
-To cope with seasonal effects, candidate data are extracted for every year from the archive within a period of 4 months centred around the target date.
+Multiple variations of the methods exist, and some aspects and parameters will not be detailed hereafter.
+There are mainly 2 parametrizations that are used most often: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on humidity variables \citep{Obled2002, Bontron2005, Marty2012}.
+
+The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): We assess the similarity of the atmospheric circulation of a target date with every day of the archive by processing the S1 criteria \citep[Eq.\ (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
+\citet{Bontron2005} showed that the geopotential height at 500~hPa and 1000~hPa are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criteria performs better than scores based on absolute distances.
+The reason for such better results is that the S1 criteria allows comparing the circulation pattern, by means of the gradients, rather than the absolute value of the geopotential height.
+To cope with seasonal effects, candidate dates are extracted within a period of 4 months centred around the target date, for every year of the archive.
 
@@
 The number of analogues, $N_{1}$, is a parameter to calibrate.
-It has an optimum clearly identifiable that is often around 50 dates when we consider only one level of analogy.
-
 Then, the daily observed precipitation amount of the $N_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
 
-The other most know method adds a second level of analogy on humidity variables (Table \ref{table:params_R2}).
-The predictor that \citet{Bontron2004} found as optimal for the France territory is a humidity index made of the multiplication of the precipitable water with the relative humidity at 850~hPa.
-\cite{Horton2012a} confirmed that this product is better than any other variable from the NCEP/NCAR reanalysis considered independently.
-When adding a second level of analogy, we subsample $N_{2}$ (30) dates in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
-When we add a second level of analogy, we keep a higher number of analogues on the first level (70 instead of 50).
+The other most know parametrization adds a second level of analogy on humidity variables (Table \ref{table:params_R2}).
+The predictor that \citet{Bontron2004} found optimal for the France territory is a humidity index made of the product of the precipitable water with the relative humidity at 850~hPa.
+\cite{Horton2012a} confirmed that this index is better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis considered independently.
+When adding a second level of analogy, we subsample $N_{2}$ dates in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
+When we add a second level of analogy, we keep a higher number of analogues on the first level.
 
@@
 Predictors are generally reanalysis datasets (and outputs of a global numerical weather prediction models for the target situation in operational forecasting, which is not the topic of this paper).
-We will work here with the NCEP/NCAR reanalysis \citep[6-hourly, 17 atmospheric levels at a resolution of 2.5\degree, see][]{Kalnay1996}, but it can be any other reanalysis.
-
-The predictand (which is to be predicted) is here the daily precipitation (6~a.m.
+We will work here with the NCEP/NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996}, but it can be any other reanalysis dataset.
+
+The predictand (which is to be predicted) is in our case the daily precipitation (6~a.m.
 to 6~a.m.
@@
 
-The calibration of the analogue method is usually done in a perfect prognosis \citep{Klein1959} framework \citep{BenDaoud2010, Bontron2004}.
+The calibration of the analogue method is usually carried out in a perfect prognosis \citep{Klein1959} framework \citep{BenDaoud2010, Bontron2004}.
 Perfect prognosis uses observed or reanalyzed data to calibrate the relationship between predictors and predictands.
@@
 This framework allow us to identify relationships that are as close as possible to the natural links between predictors and predictands, by reducing uncertainties related to numerical forecasting models.
-However, no model is perfect, and even reanalysis data contains a bias that cannot be ignored.
+However, no model is perfect, and even reanalysis data contain a bias that cannot be ignored.
 For this reason, the statistical relationships identified in the perfect prognosis framework should be applied to model outputs that are as similar as possible to the model used to elaborate the reanalysis.
@@
 Another reason for working in a perfect prognosis framework is that numerical models evolve continuously, and so does the forecast they provide.
-Re-forecasts allows us to work on a homogeneous dataset, as they are regularly reprocessed.
-However, it would involve that we need to redo the calibration procedure every time a new version is available, in order to reduce the bias \citep{Wilson2002}.
+Re-forecasts would allow us to work on a homogeneous dataset, as they are regularly reprocessed.
+However, we would need to redo the calibration procedure every time a new version is available, in order to reduce the bias \citep{Wilson2002}.
 Moreover, the reforecasts are not re-processed for every new version of the model, meaning we still end up with a bias between the forecast and the archive.
@@
 The accuracy of the parameters is evaluated by means of the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
-Let the precipitation variable be denoted $x$ with $x^{0}$ the observed value, and $F(x)$ the predicted cumulative distribution functions (cdf).
+It allows assessing the predicted cumulative distribution functions $F(y)$ compared to the observed value $y^{0}$.
+The better the forecast, the smaller the score.
 The mean CRPS of a forecast series of length $n$ can be written:
@@
 \label{eq:CRPS}
-CRPS = \frac{1}{n} \sum_{i=1}^{n} \left(  \int_{-\infty}^{+\infty} \left[ F_{i}(x)-H_{i}(x-x_{i}^{0})\right]^{2} dx \right) 
+CRPS = \frac{1}{n} \sum_{i=1}^{n} \left(  \int_{-\infty}^{+\infty} \left[ F_{i}(y)-H_{i}(y-y_{i}^{0})\right]^{2} dy \right) 
 \end{equation}
-where $H(x-x_{i}^{0})$ is the Heaviside function that is null when $x-x_{i}^{0}<0$, and has the value 1 otherwise.
-
-The mean CRPS is processed on the calibration, respectively the validation periods.
-It means that we average the scores on all days, may they be dry, slightly rainy or with heavy precipitation.
-There is actually a weighting by the number: climatologically, non-rainy days are often more frequent (of course, depending on the location) and it is essential to forecast them well.
-The days with heavy precipitation are rare, but can instead provide individual scores ($CRPS_{j}$) very penalizing, which implies that the optimization will also try to forecast them accurately.
-However, these aspects are not explicitly controlled.
+where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value 1 otherwise.
+The mean CRPS is averaged on the calibration, respectively the validation periods, on all days, may they be dry, slightly rainy or with heavy precipitation.
+
+This score is now commonly used for the evaluation of continuous variables prediction systems \citep{Casati2008, Marty2010}.
+To compare the value of the score in regard to a reference, we often consider its skill score value, and use the climatological distribution as the reference.
+The CRPSS (\textit{Continuous Ranked Probability Skill Score}) is thus defined as following:
+
+\begin{equation}
+\label{eq:CRPSS}
+CRPSS = \dfrac{CRPS-CRPS_{r}}{CRPS_{p}-CRPS_{r}} = 1-\dfrac{CRPS}{CRPS_{r}}
+\end{equation}
+where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect forecast ($CRPS_{p} = 0$).
 
@@
 
-The calibration procedure that we call ''classic'' was developed by \citet{Bontron2004} at the LTHE laborytory (INPG, Grenoble).
-It determines the optimal settings for the different variables of each level of analogy.
-The analogy levels (eg the atmospheric circulation or humidity variables) are calibrated sequentially.
-The procedure consists of the following steps \citet{Bontron2004}:
+The calibration procedure that we call ''classic'' was developed by \citet{Bontron2004} at the LTHE laboratory (INPG, Grenoble).
+It determines the optimal parameters for the different variables of each level of analogy.
+The analogy levels (eg the atmospheric circulation or humidity index) are calibrated sequentially.
+The procedure consists of the following steps \citep{Bontron2004}:
 
 \begin{enumerate}
-	\item Manual choice of the following parameters:
+	\item Manual selection of the following parameters:
 	\begin{enumerate}
 		\item meteorological variable,
-		\item atmospheric level,
-		\item time frame (hour of observation),
+		\item pressure level,
+		\item temporal window (hour of observation),
 		\item initial analogue numbers.
@@
 	\begin{enumerate}
-		\item Identification of the most skilled unitary cell (1 point for humidity variables and 4 for the geopotential fields when using the S1 criteria) over a large domain.
-Every point (or cell) of the full domain is assessed jointly on every predictor of the level of analogy (consisting generally of the same variable, but on different atmospheric levels and at different hours).
+		\item Identification of the most skilled unitary cell (1 point for humidity variables and 4 for the geopotential height when using the S1 criteria) over a large domain.
+Every point (or cell) of the full domain is assessed jointly on all predictors of the level of analogy (consisting generally of the same variable, but on different pressure levels and at different hours).
 		\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain.
@@
 		\item The number of analogues is optimized for the current level of analogy.
-		\item A new level of analogy can be added, based on other variables on predefined atmospheric levels and time frames.
-The analogue number for the next level of analogy is initiated at a chosen value.
-Then, the procedure starts again from step (a).
+		\item A new level of analogy can be added, based on other variables (such as the humidity index) on predefined pressure levels and time frames.
+The number of analogues for the next level of analogy is initiated at a chosen value.
+Then, the procedure starts again from step (a) for the new level.
 The parameters calibrated on the previous analogue levels are fixed and do not change (except the number of analogues, at the final stage).
 	\end{enumerate}
-	\item Finally, the numbers of analogues are re-assessed for the different analogue levels. This is done iteratively by varying the number of analogues of each level in a systematic way.
+	\item Finally, the numbers of analogues are re-assessed for the different levels of analogy. This is done iteratively by varying the number of analogues of each level in a systematic way.
 \end{enumerate}
 
-Calibration is done in stages, to determine the optimal parameters systematically.
-The steps are distinct and previously optimized parameters are generally not reassessed.
-\citet{Bontron2004} notes however that ''\textit{this type of algorithm, which is changing the parameters of a model in a unique path, can lead to the best solution, provided that there is no local optima}''.
+The calibration is thus done in successive steps.
+Previously calibrated parameters are generally not reassessed.
 The advantage of this method is that it is fast, it provides acceptable results, and it has low computing requirements.
-We added small improvements to this method by allowing the spatial windows to do other moves, such as: (1) increase in 2 simultaneous directions, (2) decrease in 1 or 2 simultaneous directions, (3) expansion or contraction (in every direction), (4) shift of the window (without resizing) in 8 directions (including diagonals), (5) and finally all the moves described above, but with a factor of 2, 3, or more.
+We added small improvements to this method by allowing the spatial windows to do other moves, such as: (1) increase in 2 simultaneous directions, (2) decrease in 1 or 2 simultaneous directions, (3) expansion or contraction (in every direction), (4) shift of the window (without resizing) in 8 directions (including diagonals), and finally (5) all the moves described above, but with a factor of 2, 3, or more.
 For example, we try to increase by 2 units in one (or more) direction.
@@
 
-These supplementary steps often result in spatial windows that are a bit different, but the performance gain is rather marginal (gain of 0.2\%).
+These supplementary steps often result in spatial windows that are a bit different, but the performance gain is rather marginal.
 These methods are available in the open source software AtmoSwing (Analogue Technique MOdel for Statistical Weather forecastING, www.atmoswing.org).
@@
 
-The classic calibration is fast to optimize one spatial window for a given atmospheric level and temporal window.
-However, it doesn't provide an objective choice of the atmospheric level and temporal window.
+The classic calibration is fast to optimize one spatial window for a given pressure level and temporal window.
+However, it doesn't provide an objective selection of the pressure level and temporal window.
 The only option is to try systematically every combination, which may be acceptable for no more than 2 levels.
-However, \citet{Horton2012a} showed that additional atmospheric levels may improve the method.
+However, \citet{Horton2012a} showed that additional pressure levels may improve the method.
 
 We observed during the calibration of the analogue method that the resulting parameters vary with the initial choices (such as the number of analogues).
-In addition, the different levels of analogy (on the atmospheric circulation and the humidity variables) are always calibrated sequentially.
-However, we can not exclude any dependency between them, which could lead us to select other parameters if we calibrate them together.
+In addition, the different levels of analogy (eg on the atmospheric circulation and the humidity index) are always calibrated sequentially.
+However, we can not exclude any dependency between them, which could lead us to select another parametrization if we calibrate them together.
 Simultaneous calibration of all parameters has never been undertaken so far.
-Only a global optimization can be able to optimize all parameters of all analogy levels simultaneously.
+Only a global optimization technique can be able to optimize all parameters of all analogy levels simultaneously.
 
@@
 We will present our results by first searching the best variable [note: e.g.
-choice of the atmospheric level and the temporal window for the geopotential height] on a chosen spatial window, and next, the best window for the chosen variable.
-However, even by repeating the process, are we sure to have found the optimal combination?} ''.
+selection of the pressure level and the temporal window for the geopotential height] on a chosen spatial window, and next, the best window for the chosen variable.
+However, even by repeating the process, are we sure to obtain the optimal combination?} ''.
 And later in his work: '' \textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution} ''.
@@
 \citet{BenDaoud2010}, when calibrating the analogue method, also stated that '' \textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously } ''.
-The configuration of the analogue method resulting from a classic approach is likely to be a local optimum.
 
 The analogue method needs to be adapted to every new region it is applied, because the leading meteorological influences are specific to this region.
-Even the choice of the atmospheric level and the temporal window should be reconsidered, when not the variable itself.
-For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012a} found no interest in this variable in an Alpine environment, because the vertical velocity is mainly related to the orographic effect, and was thus already well related to the atmospheric circulation itself.
-So, when adapting the analogue method to a new region, we should assess systematically every combination of atmospheric levels, time and spatial windows, which is an intensive task.
+Even the selection of the pressure level and the temporal window should be reconsidered, when not the variable itself.
+For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012a} found no interest in this variable in an Alpine environment, because in the Alps, the vertical motion is mainly controlled by orographic effects, and was thus already well related to the atmospheric circulation itself.
+So, when adapting the analogue method to a new region, we should assess systematically every combination of pressure levels, time and spatial windows, which is an intensive task.
 This procedure can be automatized by a global optimization technique.
@@
 Our ambition was then to assess the feasibility of an automatic optimization of the analogue method through various techniques.
-The objective is to find an approach to optimize all parameters simultaneously, and thus be able to identify the global optimum in the parameter space.
-In addition, it can overcome the systematic manual assessments of certain parameters such as atmospheric levels and time windows.
-Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the atmospheric levels, and the consideration of non-overlapping spatial windows between the atmospheric levels.
-
-\citet{Horton2012a} assessed the ability of the \citep{Nelder1965a} method based on a simplex approach.
+The objective was to find an approach to optimize all parameters simultaneously, and thus be able to identify the global optimum in the parameter space.
+In addition, it can overcome the systematic manual assessments of certain parameters such as the selection of the pressure levels and time windows.
+Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the pressure levels, and the consideration of non-overlapping spatial windows between the pressure levels.
+
+\citet{Horton2012a} assessed the ability of the \citet{Nelder1965a} method based on a simplex approach.
 This technique didn't provide satisfying results and failed at identifying the global optimum.
-Indeed, the optimized parameters didn't converge and many local optimums came out.
-The parameters space of the analogue method is very complex and not appropriate for a linear optimization technique.
+Indeed, the results didn't converge and many local optimums came out.
+The parameter space of the analogue method is very complex and not appropriate for a linear optimization technique.
+Genetic algorithms were found to be much more relevant for such application.
 
@@
 Genetic algorithms (GAs) come from the world of stochastic optimization, more specifically from metaheuristic approaches.
-These are stochastic iterative algorithms that behave like search algorithms by exploiting the characteristics of a problem and are particularly suitable for complex parameters spaces.
-
-Genetic algorithms are part of the family of evolutionary algorithms \citet{Back1993c, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
+These are stochastic iterative algorithms that behave like search algorithms by exploiting the characteristics of a problem and are particularly suitable for complex parameter spaces.
+
+Genetic algorithms are part of the family of evolutionary algorithms \citep{Back1993b, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
 GAs are the most used technique from evolutionary algorithms \citep{Back1993b}, and they are constantly improving \citep{Haupt2004}.
@@
 
-The method was developed by \citet{Holland1992b} and was popularized by \citet{Goldberg1989}.
-Unlike a linear or local optimization, GAs seek the global optimum on a complex surface, theoretically without restrictions, but with no guarantee to reach it.
+The method was originally developed by \citet{Holland1992b} and popularized by \citet{Goldberg1989}.
+Unlike a linear or local optimization, GAs seek the global optimum on a complex surface, theoretically without restriction, but with no guarantee to reach it.
 
@@
 GAs mimic the evolution of a population of individuals in a new environment, by applying rules based on natural processes, such as DNA mutation, chromosomes crossover, natural selection, etc.
-It simulates the fact in the natural environment, the most suitable individuals tend to survive longer, to reproduce more easily, and so to influence coming generations by providing some genes that provide some good performance in a certain domain.
+It simulates the fact that in a natural environment, the most suitable individuals tend to survive longer, to reproduce more easily, and so to influence coming generations by providing genes that provide some good performance in a certain domain.
 Generation after generation, the DNA mixes and the strong genes cumulate in some individuals \citep{Beasley1996a}.
@@
 Only the resulting value is used for optimization.
-Indeed, these algorithms do not require any knowledge of the problem, which can be used as black-box.
+Indeed, these algorithms do not require any knowledge of the problem, which can be used as black-box, but they must be adapted in order to perform optimally.
 
 By means of the reproduction operator and the natural selection, the GAs focus on the most promising regions of the parameter space \citep{Holland1992b}.
-Points (parameters sets) are densified in these areas because the strong genes of the best individuals propagate from generation to generation.
-
-Two conditions guarantee in theory the convergence to the global optimum \citep{Zitzler2004a}: (1) Parameters mutations that can allow to explore the entire parameter space, thus ensures that any value can be achieved with a non-zero probability.
-(2) A rule of elitism ensuring that an optimal solution can not be lost or damaged.
+Points (parameter sets) are densified in these areas because the strong genes of the best individuals propagate from generation to generation.
+
+Two conditions guarantee in theory the convergence to the global optimum \citep{Zitzler2004a}: (1) Parameters mutations that can allow to explore the entire parameter space, thereby ensures that any value can be achieved with a non-zero probability.
+(2) A rule of elitism ensuring that an optimal solution cannot be lost or damaged.
 
@@
 It is indeed mainly a matter of time.
-When the optimizer gets closer to the global optimum, any new improvement takes more time to appear, and the final adjustment of the parameters is very time consuming \citep{Back1993a}.
+When the optimizer gets closer to the global optimum, any new improvement takes more time to appear (see figure \ref{fig:evolution}), and the final adjustment of the parameters is very time consuming \citep{Back1993a}.
 For problems that require a significant amount of time in order to evaluate the objective function, as in our case, we have to limit the number of generations to get reasonable processing time.
 Thus, different acceptable solutions can result from one or more optimizations \citep{Holland1992b}.
-This is a strength and a weakness of GAs: they are very good at exploring complex parameters spaces in order to identify the most promising areas, but they will not necessarily find the best solution with the optimal values of all parameters \citep{Holland1992b}.
+This is a strength and a weakness of GAs: they are very good at exploring complex parameter spaces in order to identify the most promising areas, but they will not necessarily find the best solution with the optimal values of all parameters \citep{Holland1992b}.
 
@@
 
-The GAs optimize a population of individuals (parameters sets).
+The GAs optimize a population of individuals (parameter sets).
 Each individual contains a chromosome (parameters of the analogue method in our case).
@@
 The first step of the optimization is to generate the initial population.
-A population is a set of $N$ individuals (each of which represents a point in the space of potential solutions, a parameters set of the analogue method in our application) that we are going to make evolve.
+A population is a set of $N$ individuals (each of which represents a point in the space of potential solutions, a parameter set of the analogue method in our application) that we are going to make evolve.
 A generation is the population at a given time.
@@
 
-Natural selection is performed on the basis of the objective function values.
+Natural selection is performed on the basis of the values of the objective function.
 The selection allows to only keep a certain part of the population, usually half ($N/2$), which can access the mating pool (intermediate generation with $N_{mp}$ members).
@@
 
-	\item \textbf{Tournament selection}: This operator is similar to that used in natural selection, but is applied here for the successive selection of each parent.
+	\item \textbf{Tournament selection}: This operator is similar to the one used in natural selection, but is applied here for the successive selection of each parent.
 To select a parent, a number of individuals (2 or 3) are randomly picked and the best is kept.
@@
 
-Once the two parents selected for breeding, they combine their chromosomes and produce two children, bringing the number of individuals in the population of $N_{mp}$ back to $N$ (the parents also return back in the total population in order to complement the next generation).
+Once the two parents are selected for breeding, they combine their chromosomes and produce two children, bringing the number of individuals in the population back to $N$ (the parents also return back in the total population in order to complement the next generation).
 The combination of chromosomes is carried out using a crossover operator, thereby generating two offspring having characteristics derived from both parents.
@@
 The mutation operator is a direct modification of genes.
-In a binary coding, it is implemented as an inversion of one bit in a chromosome, while in real coding, it is done by changing the value of a gene.
+In a binary coding, it is implemented as an inversion of some bits in a chromosome, while in real coding, it is done by changing the gene values.
 Mutations add diversity to the population and prevent a freeze of the evolution, or a genetic drift to a local optimum.
-Thus, it makes the convergence to the global optimum theoretically possible \citep{Beasley1993a}, as they allow exploring beyond the current region of the variable space.
-They therefore help prevent the algorithm to converge too quickly to a local optimum and bring new characteristics that were not present in the original population \citep{Haupt2004}.
+Thus, it makes the convergence to the global optimum theoretically possible \citep{Beasley1993a}, as they allow exploring beyond the current region of the parameter space.
+They therefore help preventing the algorithm to converge too quickly to a local optimum and bring new characteristics that were not present in the original population \citep{Haupt2004}.
 
@@
 
-	\item \textbf{Constant normal mutation}: many users use a normal distributions to generate new values. The gene $g$ that mutate becomes:
+	\item \textbf{Constant normal mutation}: many use normal distributions to generate new values. The gene $g$ that mutate becomes:
 	\begin{equation}
@@
 	where $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a threshold chosen by the user to maintain a minimum search radius when $G>G_{m,r}$.
-During the first generations, the exploration extent covers the entire parameters space.
+During the first generations, the exploration extent covers the entire parameter space.
 However, this area is reduced over generations, allowing exploitation of local solutions.
 
-	\item \textbf{Individual adaptive mutation rate} \citep{Back1992a}: based on the ides of Evolution Strategies \citep[see][]{Rechenberg1973, Schwefel1981}, \citet{Back1992a} introduced a concept of self-adaptive genetic algorithms.
+	\item \textbf{Individual adaptive mutation rate} \citep{Back1992a}: based on the ideas of Evolution Strategies \citep[see][]{Rechenberg1973, Schwefel1981}, \citet{Back1992a} introduced a concept of self-adaptive genetic algorithms.
 The idea is to distribute control parameters within individuals themselves, which partially decentralize control of the evolution.
@@
 This approach is close to the natural adaptation phenomena.
-A population less suited to its environment is changing faster than better adapted population.
+A population less suited to its environment is changing faster than better adapted populations.
 Mutations are performed according to a constant uniform distribution.
@@
 
-	\item \textbf{Individual adaptive search radius} \citep{Horton2012a}: based on the ideas of the non-uniform mutation, we introduce a search radius in the approach of individual adaptive mutation rates.
+	\item \textbf{Individual adaptive search radius}: based on the ideas of the non-uniform mutation, we introduce a search radius in the approach of individual adaptive mutation rates.
 This search radius $r_{a}$, bounded between 0 and 1, is also adaptive and behaves similarly to the adaptive mutation rates.
-In order to separate its evolution to the one of the mutation rate, its own value is considered initially as a self-mutation rate to eventually mutate before being used as a normalized search radius.
+In order to separate its evolution from the one of the mutation rate, its own value is considered initially as a self-mutation rate to eventually mutate before being used as a normalized search radius.
 The value of a mutated gene is given by the following equation, which is a simplification of the non-uniform mutation:
@@
 
-	\item \textbf{Chromosome of adaptive search radius} \citep{Horton2012a}: we introduced this operator that combines the operations of the chromosome of adaptive mutation rate to our adaptive search radius approach.
+	\item \textbf{Chromosome of adaptive search radius}: we introduced this operator that combines the operations of the chromosome of adaptive mutation rate to our adaptive search radius approach.
 Similarly, an individual has 3 chromosomes: the first containing the values to be optimized, the second containing the distributed mutation rate, and the last one, the distributed search radius.
@@
 
-	\item \textbf{Multi-scale mutation} \citep{Horton2012a}: finally, we developed another approach, that is also based on the search radius concept.
+	\item \textbf{Multi-scale mutation}: finally, we developed another approach, that is also based on the search radius concept.
 However, the latter is not decreasing with time.
@@
 The idea is consistent as long as we are confident that the algorithm will converge towards the global optimum.
-Indeed, one the algorithm is in the exploitation mode, it is very unlikely to go out of the minima it converges to.
+Indeed, once the algorithm is in the exploitation mode, it is very unlikely to go out of the region it converges to.
 We wanted to test an approach that combines both exploration and exploitation during the whole optimization.
@@
 
-We used a process of elitism on natural selection as well as on mutations.
+We used a process of elitism on the natural selection as well as on mutations.
 This ensures the survival of the best individual so that we do not lose a better solution.
@@
 The convergence check determines whether the solution is acceptable and if the algorithm may stop.
-The stopping criteria are not often well documented in GAs case studies \citep{Haupt2004}.
+The stopping criteria are not often well documented in GAs case studies.
 We chose to stop the optimization if the best individual does not change for $x$ generations.
-This value should not be too low to allow the algorithm to escape from a local minimum.
+This value should not be too low to allow the algorithm to escape from a local optima.
 In addition, the rate of improvement decreases with the progression of the optimization.
-It is thus common that the best individual does not evolve over generations when we get closer to the global solution.
+It is thus common that the best individual does not evolve over several generations when we get closer to the global solution.
 We chose a value of $x=20$ generations.
@@
 Some constraints need to be taken into account.
-For example, when a crossover or a mutation operation resulted in a parameter value standing out of the authorized bounds, it had to be brought back within the limits.
-Moreover, the parameters are of different nature: some are continuous, such as the weight, some are discretized, such as the analogues number, or the spatial windows, and finally, some are independent elements in an array, such as the choice of the meteorological variable.
-New values resulting from the optimizer needs to respect the type of data it represents.
-
-Other constraints exist in between the parameters, such as the atmospheric level of the humidity flux that has to be consistent in between the relative humidity and the two wind components.
-Another example is the weighting of the different atmospheric levels which has to be normalized.
+For example, when a crossover or a mutation operation results in a parameter value standing out of the authorized bounds, it has to be brought back within the limits.
+Moreover, the parameters are of different nature: some are continuous, such as the weight, some are discretized, such as the analogues number, or the spatial windows, and finally, some are independent elements in an array, such as the selection of the meteorological variable.
+New values resulting from the optimizer need to respect the type of data it represents.
+
+Other constraints exist in between the parameters, such as the temporal window of the humidity index that has to be consistent in between the relative humidity and the precipitable water.
+Another example is the weighting of the different pressure levels which has to be normalized.
 
@@
 
-The assessment (calculation of the objective function) of each member of the population of a generation is completely independent and can be performed in parallel on different processors of a computer \citep{Haupt2004, Alliot2005}.
+The assessment (calculation of the objective function) of each member of the population of a generation is completely independent and can be performed in parallel on different processors of a computer \citep{Alliot2005}.
 We implemented this technique and the resulting time savings was very important.
@@
 The GAs parametrization, such as the mutation rate, population size, natural selection options, and so on, is difficult given the high number of existing variants, each developed for a specific problem \citep{Haupt2004, Costa2007a}.
-This parametrization depends on the objective function, implementation variants, the bounds of variables to be optimized, and performance indicators.
+This parametrization depends on the objective function, implementation variants, the range of the parameters to be optimized, and performance indicators.
 Thus, different studies suggest very different parametrization.
@@
 A key element of the parametrization of GAs is finding the right balance between exploration and exploitation \citep{Back1992a, Smith1997a}.
-Exploration is characterized by a relatively high probability to assess the regions of the parameters space that have not yet been visited.
+Exploration is characterized by a relatively high probability to assess the regions of the parameter space that have not yet been visited.
 This probability must be sufficiently large at the beginning of the optimization, so that the algorithm is capable of identifying the region where the global optimum is located.
@@
 \citet{DeJong1975a} and \citet{Grefenstette1986} compared different implementations and parametrizations of GAs on functions of varying complexity.
-They observed that a small population size improves the initial performance, while a large population improves long-term performance; the size of the population should be selected between 50 and 100.
+They observed that a small population size improves the initial performance, while a large population improves long-term performance.
 They also observed that the ratio of the population to keep for the mating pool is around 50\% (45\% to 60\%).
 
-Values of the mutation rate varies broadly between the studies: from 0.001 \citep{DeJong1975a} to 0.2 \citet{Haupt2004}.
-\citet{Back1996b} showed that mutation rates higher than the usual ranges are more optimal at the beginning of optimization, allowing further exploration.
+Values of the mutation rate varies broadly between the studies: from 0.001 \citep{DeJong1975a} to 0.2 \citep{Haupt2004}.
+\citet{Back1996b} showed that mutation rates higher than the usual ranges are more optimal at the beginning of the optimization, allowing further exploration.
 The combination of a small population and a high mutation rate works best for the first generations \citep{DeJong1975a, Back1996b, Haupt2004}, but as we could observe, it does not guarantee the quality of the final result.
@@
 
-One of our goals being to make recommendations of parametrization for optimization of the analogue method, proceeded systematically.
+One of our goals being to make recommendations of parametrization in order to optimize the analogue method, we proceeded systematically.
 The results are summarized hereafter \citep[see][for the details]{Horton2012a}.
-We used concepts from the factorial design approach \citep[see eg.][]{Costa2005,Costa2007,Mariano2010}, which is sometimes used for comparative analysis of different parametrizations of GAs.
+We used concepts from the factorial design approach \citep[see eg.][]{Costa2005a,Costa2007a,Mariano2010a}, which is sometimes used for comparative analysis of different parametrizations of GAs.
 We processed by stages, analysing in details and in a systematic way every variants of the implemented operators, in combination with multiple other options and parameters in order to take into account eventual co-dependencies.
@@
 
-	$50<N<100$ for a very simple implementation of the analogue method (1 level of analogy with 2 atmospheric levels),
-
-	$N\approx200$ for a bit more complex method (1 level of analogy with 4 atmospheric levels, or 2 level of analogy with less atmospheric levels),
-
-	$N\approx500$ for significantly more complex methods (2-3 levels of analogy with 4 atmospheric levels for the atmospheric circulation, and 2 to 4 levels for the analogy humidity),
+	$50<N<100$ for a very simple implementation of the analogue method (1 level of analogy with 2 pressure levels),
+
+	$N\approx200$ for a bit more complex method (1 level of analogy with 4 pressure levels, or 2 level of analogy with less pressure levels),
+
+	$N\approx500$ for significantly more complex methods (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the humidity analogy),
 
@@
 The performance of these variants are relatively close, both in terms of score, convergence, and number of evaluations.
-The random pairing performed the most poorly, when the tournament selection with 3 candidates is slightly superior.
+The random pairing performed the most poorly, when the tournament selection with 3 candidates was slightly superior.
 The roulette wheel weighting is not far behind, but it is less effective in terms of convergence and number of evaluations.
@@
 
-	\item \textbf{Mutation}: we compared the 10 mutation operators with different options, bringing the number of variations of this operator to 110.
+	\item \textbf{Mutation}: we compared the 10 mutation operators with different options, bringing the number of variations of this operator up to 110.
 We immediately observed that the mutation operator has a very important role on the performance of the optimizations of the analogue method, and that the other reproduction operators seem of secondary importance.
@@
 He even suggests, in opposition with the theory of \citet{Holland1992a}, that chromosomes crossovers have mostly a corrective role of mutation operations.
-Various studies have also identified the importance of the mutation operator relative to reproduction \citep[see eg.][]{Back1992a, Back1996b, Smith1997a, Deb1999, Haupt2004, Costa2005a, Costa2007a}.
+Various studies have also identified the importance of the mutation operator relatively to reproduction \citep[see eg.][]{Back1992a, Back1996b, Smith1997a, Deb1999, Haupt2004, Costa2005a, Costa2007a}.
 
@@
 The difficulty is that the optimal value seems to be very case-related.
-Indeed, by even changing the precipitation time series (ie optimizing for another region), but not the complexity of the analogue method, the optimal mutation rate changes, making it impossible to estimate in advance.
-
-	\textit{Chromosome of adaptive search radius} \citep{Horton2012a}: unlike the previous one, this operator is very robust, as it requires no option and is self-managing.
-It may be sometimes a little bit less efficient for simple problems, but does not require parametrization, which is an important advantage.
-It is interesting to notice that our insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, eg, the chromosome of adaptive mutation rate).
-
-	\textit{Multi-scale mutation} \citep{Horton2012a}: finally, our multi-scale mutation, which also performs pretty well, can as well be seen as fairly robust, since it requires only one parameter, the mutation rate.
-Our tests seem to indicate that a high mutation rate here is preferable.
+Indeed, by even changing the precipitation time series (ie optimizing for another subregion), but not the complexity of the analogue method, the optimal mutation rate changes, making it impossible to estimate in advance.
+
+	\textit{Chromosome of adaptive search radius}: unlike the previous one, our new operator is very robust, as it requires no option and is auto-adapting.
+It may be sometimes a little bit slower for simple problems, but does not require parametrization, which is an important advantage.
+It is interesting to notice that our insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).
+
+	\textit{Multi-scale mutation}: finally, our multi-scale mutation, which also performs pretty well, can as well be seen as fairly robust, since it requires only one parameter, the mutation rate.
+However, it can also be difficult to estimate a correct value a priori.
 
@@
 	\item The performance of the operators for the couples selection perform relatively similarly.
-The roulette wheel weighting and the tournament selection are more efficient in terms of convergence and the required number of evaluations.
-
-	\item Most crossover operators have relatively similar performance. Binary-like crossover, especially with two points of intersection, are better than others, especially for convergence.
+The roulette wheel weighting and the tournament selection are more efficient in terms of convergence and required number of evaluations.
+
+	\item Most crossover operators have relatively similar performance. Binary-like crossover with two points of intersection are better than others, especially for convergence.
 
 	\item Mutation has a clearly dominant influence.
-Three mutation operators stand out, two of which we have developed: the non-uniform mutation, the chromosome of adaptive search radius, and the multi-scale mutation.
-The latter two are more robust as they have less or even no parameter.
+Three mutation operators stand out, two of which we have developed: the non-uniform mutation, the multi-scale mutation, and the chromosome of adaptive search radius.
+The latter is the most robust as it has no controlling parameter.
 
@@
 The analogue method has to be adapted to every new location it is applied.
-We will focus here on an application to the Swiss Alps.
+We improved the analogue method for the Swiss Alps, by means of genetic algorithms.
+A summary of the main results are provided here \citep[see][for the details]{Horton2012a}.
 Even though the results may differ from one place to another, the applicability of GAs to the analogue method remains universal.
-We made different attempts to improve the analogue method for the Swiss Alps, by means of genetic algorithms.
-A summary of the main results are provided here \citep[see][for the details]{Horton2012a}.
 
@@
 
-The study area is the alpine upper Rhône catchment in Switzerland (Fig.\ \ref{fig:map}).
+The study area is the alpine upper Rh\^{o}ne catchment in Switzerland (Fig.\ \ref{fig:map}).
 The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$.
 This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at providing a real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
-Even thought the region is rather small, the meteorological influences related to extreme weather conditions varies substantially within it \citep[see]{Horton2012}.
-Based on different climatological analyses, the gauging stations in the catchment were clustered in 10~groupments (Fig.\ \ref{fig:map}) :
+Even thought the region is rather small, the meteorological influences related to extreme weather conditions varies substantially within it \citep[see][]{Horton2012}.
+Based on different climatological analyses, the gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}) :
 
@@
 
-The 48 years period (see section \ref{section_data}) was divided into a calibration period and a validation period.
+The 48 years precipitation dataset (see section \ref{section_intro}.\ref{section_data}) was divided into a calibration period and a validation period.
 Using data independent from the calibration period to validate our results is very important in order to assess the robustness of the improvements and to avoid overparametrization of the method.
@@
 In order to reduce potential bias related to trends in the climate change or to the evolution in measurement techniques, the selection of the validation period is evenly distributed over the entire series \citep{BenDaoud2010}.
-Thus, we select one year every six years for validation, which represents a total of eight years for the validation and forty for calibration.
+Thus, we selected one year every six years for validation, which represents a total of 8 years for the validation and 40 for calibration.
 The choice of the sequence was made in order to have similar statistical characteristics between the calibration and the validation periods.
@@
 
-We first optimized the analogy of atmospheric circulation alone, without humidity variables.
+We first optimized the analogy of atmospheric circulation alone, without humidity variables, for our 10 subregions.
 We started from the most simple analogue method, and increased the complexity in order to identify the degrees of freedom that are of particular interest.
@@
 
-Then, we provided an additional degree of freedom to the AGs by letting them choose the atmospheric levels along with the other parameters.
-Evaluation of atmospheric levels is also a non-automated process in the classic calibration.
-However, we could observe that the choice of this degree of freedom increases the optimization time and may decrease the number of simulations that converge to a single solution.
-However, most solutions are very close in terms of score.
-The averaged relative improvement of the CRPSS is 5.63\% for the calibration and 3.82\% for the validation period.
-The atmospheric levels that were chosen are 500~hPa or 700~hPa for the upper level, and 925~hPa or 1000~hPa (most often) for the lower level.
+Then, we provided an additional degree of freedom to the AGs by letting them choose the pressure levels along with the other parameters.
+Evaluation of pressure levels is also a non-automated process in the classic calibration.
+We could observe that this degree of freedom increases the optimization time and may decrease the number of simulations that converge to a single solution.
+However, most solutions were very close in terms of score.
+The averaged relative improvement of the CRPSS is 5.63\% for the calibration and 3.82\% for the validation periods.
+The pressure levels that were chosen are 500~hPa or 700~hPa for the upper level, and 925~hPa or 1000~hPa (most often) for the lower level.
 
 Parallel analyses showed that the analogy of circulation is incomplete, and that the geopotential still contains relevant data that can improve the statistical relationship.
-Therefore, we added a third predictor (still the geopotential height) that the optimizer can use along with the previous parameters.
-There is no constraint on the predictors, so that the same atmospheric level can be selected multiple times.
+Therefore, we added a third predictor (still the geopotential height) that the optimizer could use along with the previous parameters.
+There was no constraint on the predictors, so that the same pressure level could be selected multiple times.
 Some improvements were found on the score, both for the calibration and the validation periods, confirming that this additional information is beneficial for the quality of the forecast.
 We then tried with 4 predictors, and so on, up to 8.
-Every time we added a new predictor to optimize, the score on the calibration period increased, but always more in a smaller extent.
-However, the validation period dropped after 4 predictors, revealing an over-parametrization of the method, and thus a lack of robustness.
-Moreover, the complexity of the method increases, and its interpretation becomes more and more difficult.
+Every time we added a new predictor to optimize, the score on the calibration period increased, but always more to a smaller extent.
+However, the score on the validation period dropped after 4 predictors, revealing an over-parametrization of the method, and thus a lack of robustness.
 We thus found that considering 4 predictors is optimal for our case study, since the gain in CRPSS is significant.
@@
 
-Finally, we added a weighting of these 4 predictors (atmospheric levels), which is also optimized by GAs.
-The weighting operates in the combination of the S1 criteria of every level, which were previously averaged with equal weights.
+Finally, we added a weighting of these 4 predictors (pressure levels), which is also optimized by GAs.
+The weighting operates in the combination of the S1 criteria processed on every level, which were previously averaged with equal weights.
 The role of this new degree of freedom is to give more weight to the levels with greater predictive capacity, and to consider the geopotential variability changes with altitude.
@@
 	\setlength\itemsep{-4px}
-	\item the atmospheric levels (4 degrees)
-	\item the temporal windows (4)
-	\item the spatial windows (16)
-	\item the weights (4)
-	\item the number of analogues (1).
+	\item the selection of the pressure levels (4 degrees)
+	\item the temporal windows (4 degrees)
+	\item the spatial windows (16 degrees)
+	\item the weights (4 degrees)
+	\item the number of analogues (1 degrees).
 \end{itemize}
@@
 
-The resulting optimized parameters for z4 vary from one groupment to another.
+The resulting optimized parameters for z4 vary from one subregion to another.
 An example of the detailed parameters is provided for the Swiss Chablais in Table \ref{table:params_GA_z4}.
-The optimized spatial windows are given for every groupment in Figure \ref{fig:spatial_windows_z4}, and the selected atmospheric levels in Table \ref{table:levels_GA_z4}.
+The optimized spatial windows are given for every subregion in Figure \ref{fig:spatial_windows_z4}, and the selected pressure levels in Table~\ref{table:levels_GA_z4}.
 
@@
 The score was also calculated for three precipitation thresholds: P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_z4}).
-The score increases with the precipitation threshold: in average, respectively, 13.3\%, 15.4\% and 29.1\% in calibration and 7.9\%, 11.1\% and 34.5\% for the validation period.
-The optimized method improves thus even more days with significant precipitation than standard days.
-
-To assess the cross-compatibility of the parameters, we applied those optimized for one groupment to the others.
+The gain in score increases with the precipitation threshold: in average, respectively for the different thresholds, 13.3\%, 15.4\% and 29.1\% in calibration and 7.9\%, 11.1\% and 34.5\% for the validation period.
+The optimized method improves thus even more the forecasts for days with significant precipitation than usual days.
+
+To assess the cross-compatibility of the parameters, we applied those optimized for one subregion to the others.
 The resulting losses or gains of the CRPSS are displayed in Table \ref{table:crossing_z4_calib} for the calibration period and in Table \ref{table:crossing_z4_valid} for the validation period.
@@
 
-The choices of the atmospheric levels for the analogy of circulation show a great homogeneity and is spatially consistent (Table \ref{table:levels_GA_z4}).
-First of all, the level 1000~hPa is selected twice (the first time at 6 or 12~h, and the second always at 30~h) and the 700~hPa is selected once for every region (always at 24~h).
-The level which varies from one region to another is the upper level (always at 12~h), that is 300~hPa for the North-West part of the catchment, 500~hPa for most of the groupments, and 600~hPa for the Conches Valley.
+The selections of the pressure levels for the analogy of circulation show a great homogeneity and is spatially consistent (Table \ref{table:levels_GA_z4}).
+First of all, the level 1000~hPa is selected twice (the first time at 6 or 12~h, and the second always at 30~h) and the 700~hPa is selected once for every subregion (always at 24~h).
+The level which varies from one subregion to another is the upper level (always at 12~h), that is 300~hPa for the North-West part of the catchment, 500~hPa for most of the subregions, and 600~hPa for the Conches Valley.
 Its spatial distribution is however homogeneous.
-The optimizer thus provided consistent choices of atmospheric levels and temporal windows, which depicts a significant preference in the analogue method, and the success of our GAs to provide consistent results.
-The automatic choice of the atmospheric levels is a big advantage of a global optimization, as it was not possible to assess all combinations of 4 levels with the classic calibration procedure.
-
-The resulting spatial windows (Figure \ref{fig:spatial_windows_z4}) may look very diverse first, but there are significant similarities for groupments located within the same vicinity.
-The first 4 groupments are characterized by a large spatial window on the upper level, whereas it becomes smaller for the other regions.
-For most groupments, the second level (700~hPa) is represented by thin and longitudinally extended domains.
+The optimizer thus provided consistent selections of pressure levels and temporal windows, which depicts a significant preference in the analogue method, and the success of our GAs to provide consistent results.
+The automatic selection of the pressure levels is a big advantage of a global optimization, as it is not possible to assess all combinations of 4 levels with the classic calibration procedure.
+
+The resulting spatial windows (Figure \ref{fig:spatial_windows_z4}) may look very diverse first, but there are significant similarities for subregions located within the same vicinity.
+The first 4 subregions are characterized by a large spatial window on the upper level, whereas it becomes smaller for the other subregions.
+For most subregions, the second level (700~hPa) is represented by thin and longitudinally extended domains.
 The third level (1000~hPa at 6 or 12~h) also contains longitudinally extended domains, but a bit larger.
 The last one (1000~hPa at 30~h) is rather large and squared.
-Surprisingly, regions number 5 (Left side valleys) and 6 (Southern ridges) have exactly the same spatial windows, which suggest that they behave in a similar way and thus could have been merged.
+Surprisingly, subregions number 5 (Left side valleys) and 6 (Southern ridges) have exactly the same spatial windows, which suggest that they behave in a similar way and thus could have been merged.
 This similarity is a good sign for the accuracy of our optimized parameters.
@@
 
-The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the calibration period when they are calibrated for the given groupment (Table \ref{table:crossing_z4_calib}).
-However, the losses in CRPSS are not of the same amplitude between the different regions.
+The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the calibration period when they are calibrated for the given subregion (Table \ref{table:crossing_z4_calib}).
+However, the losses in CRPSS are not of the same amplitude between the different subregions.
 Indeed, the Upper Rhone Valley (7) and moreover the Southeast ridges (8) seem to behave significantly differently.
-Parameter sets from other regions perform poorly for these groupments, and vice versa.
-Nevertheless, both groupments seem quite inter-compatible.
-This points to the importance of taking into account leading meteorological influences during groupment creation, which is not always best represented by the distance separating them.
+This is indeed a climatological reality, as this subregion is the most sensitive to southerly flows \citep{Horton2012}.
+Parameter sets from other subregions perform poorly for these subregions, and vice versa.
+Nevertheless, both subregions seem quite inter-compatible.
+This points to the importance of taking into account leading meteorological influences during subregion creation, which is not always best represented by the geographical distance separating them.
 Globally, the same pattern can be observed for the validation period (Table \ref{table:crossing_z4_valid}), but in this case, minor improvements may be observed when crossing the parameters.
-The reason being that the independant validation period contains other events that may be better forecasted by other parameters sets.
+The reason being that the independant validation period contains other events that may be better forecasted by other parameter sets.
 The relative small differences in score between parametrizations indicate that even though the parameters may differ significantly, the performance may not be drastically affected.
-Even a change in the atmospheric level does not mean a radical drop of the score.
+Even a change in the pressure level does not mean a radical drop of the score.
 A different parametrization leads to a different selection of the analogue days, and thus to an improvement of the forecast of certain weather conditions at the expense of others.
@@
 We previously worked with a method based on a unique level of analogy.
-However, we know that humidity variables in a second level of analogy do provide improvements to the method (section \ref{section_analog_method}).
-So we also want to optimize the humidity index, which is a combination of the relative humidity and the precipitable water.
+However, we know that humidity variables in a second level of analogy do provide improvements to the method (section \ref{section_intro}.\ref{section_analog_method}).
+So we also wanted to optimize the humidity index, which is a combination of the relative humidity and the precipitable water.
 In order to do so, we had to introduce a constraint to the optimizer, so that it selects the same temporal window for both variables.
 
-Two methods were assessed: one with 2 humidity predictors (humidity index on 2 atmospheric levels or at 2 different hours) named z4-hi2, and one with 4 humidity predictors named z4-hi4.
+Two methods were assessed: one with 2 humidity predictors (humidity index on 2 pressure levels or at 2 different hours) named z4-hi2, and one with 4 humidity predictors named z4-hi4.
 When we introduce 2 predictors for the humidity analogy, the number of degrees of freedom raises to 42, and to 54 when we add 4 predictors.
@@
 
-As previously, the optimized parameters differ from one region to another, and this event to a greater extent.
-Detailed examples are still provided for the Swiss Chablais region in Table \ref{table:params_GA_z4_hi2} for z4-hi2 and in Table \ref{table:params_GA_z4_hi4} for z4-hi4.
-The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_z4-hi2} for z4-hi2, along with the selected atmospheric levels for the circulation analogy (Table \ref{table:levels_GA_z4_hi2}) and the humidity analogy (Table \ref{table:levels_GA_z4_hi2_H}).
-Correspondingly, for the method z4-hi4, the spatial windows are shown in Figure \ref{fig:spatial_windows_z4-hi4} and the selected atmospheric levels are presented in Tables \ref{table:levels_GA_z4_hi4} and \ref{table:levels_GA_z4_hi4_H}.
+As previously, the optimized parameters differ from one subregion to another, and this event to a greater extent.
+Detailed examples are still provided for the Swiss Chablais subregion in Table \ref{table:params_GA_z4_hi2} for z4-hi2 and in Table \ref{table:params_GA_z4_hi4} for z4-hi4.
+The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_z4-hi2} for z4-hi2, along with the selected pressure levels for the circulation analogy (Table \ref{table:levels_GA_z4_hi2}) and the humidity analogy (Table \ref{table:levels_GA_z4_hi2_H}).
+Correspondingly, for the method z4-hi4, the spatial windows are shown in Figure \ref{fig:spatial_windows_z4-hi4} and the selected pressure levels are presented in Tables \ref{table:levels_GA_z4_hi4} and \ref{table:levels_GA_z4_hi4_H}.
 
@@
 This results in a relative improvements that ranges from 11.5 \% to 15.6 \% compared to the reference method on the humidity analogy (Table \ref{table:scores_diff}).
-As for the method z4, methods z4-hi2 and z4-hi4 present improvements of the forecast of significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
+As for z4, the z4-hi2 and z4-hi4 methods present improvements of the forecast of significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
 The improvement are relatively similar for z4-hi2 (Table \ref{table:scores_thresholds_z4-hi2}) and z4-hi4 (Table \ref{table:scores_thresholds_z4-hi4}), with slightly superior scores for the latter on small precipitation (P\(\geq\)1 mm) and extremes (P\(\geq\)0.5\(\cdot\)P10).
@@
 When optimizing a method made of 2 levels of analogy, the introduction of humidity variables in the second level has an influence on the parameter values of the first level.
-This is first visible on the choice of the atmospheric levels for the circulation analogy, where the 1000~hPa that was previously systematically selected twice (Table \ref{table:levels_GA_z4}) is now less chosen (once or even not at all) for both za-hi2 (Table \ref{table:levels_GA_z4_hi2}) and za-hi4 (Table \ref{table:levels_GA_z4_hi4}).
+This is first visible on the selection of the pressure levels for the circulation analogy, where the 1000~hPa that was previously systematically selected twice (Table \ref{table:levels_GA_z4}) is now less chosen (once or even not at all) for both za-hi2 (Table \ref{table:levels_GA_z4_hi2}) and za-hi4 (Table \ref{table:levels_GA_z4_hi4}).
 There is indeed a shift of the previously selected 1000~hPa for higher levels, which is even slightly stronger with 4 humidity predictors than with 2.
 This change is likely due to the fact that when considering only the circulation analogy, the method tries to take into account information that can serve as proxy for humidity assessment, whereas it doesn't need it with the humidity index.
-This aspect has never been demonstrated, as usual calibration tools do not allow it.
+This aspect has never been demonstrated, as classic calibration tools do not allow it.
 It can only be assessed by a global optimization technique that can tune jointly both levels of analogy.
 
-The selected levels for the analogy on the humidity index is strongly centred around the 700~hPa and 600~hPa.
-No other value has been selected when considering 2 atmospheric levels (Table \ref{table:levels_GA_z4_hi2_H}), and when considering 4 levels, the 850~hPa is quite often chosen, and the 500~hPa more rarely.
-However, even is this latter method, the 700~hPa and 600~hPa still hold 78 \% of the selected levels.
-It is thus more efficient to consider one of this level multiple times at different hours rather than using another atmospheric level.
-Besides, the optimizer never chose the same atmospheric level at the same hour for any variable.
-
-The choice of the temporal windows for the atmospheric circulation is similar to the preceding optimization (in the order of increasing pressure: 12~h, 24/30~h, 12~h, 30~h), but sometimes with a bit more variability.
+The selected pressure levels for the analogy on the humidity index are strongly centred around 700~hPa and 600~hPa.
+No other value has been selected when considering 2 pressure levels (Table \ref{table:levels_GA_z4_hi2_H}), and when considering 4 levels, the 850~hPa and 500~hPa levels are additionally selected.
+However, even in this latter method, the 700~hPa and 600~hPa levels still hold 78 \% of the selection.
+It is thus more efficient, in terms of forecasting performance, to consider one of this level multiple times at different hours rather than using another pressure level.
+Besides, the optimizer never chose the same pressure level at the same hour for any variable, even though it was allowed to do so.
+
+The selection of the temporal windows for the atmospheric circulation is similar to the preceding optimization (in the order of increasing pressure: 12~h, 24/30~h, 12~h, 30~h), but sometimes with a bit more variability.
 When it comes to the humidity analogy, there is a clear trend to select 12~h and 24~h when considering 2 predictors.
-The z4-hi4 method presents more variability on the choice of the temporal windows for the humidity index.
-
-The optimized spatial windows on the atmospheric circulation have also changed (Figures \ref{fig:spatial_windows_z4-hi2} and \ref{fig:spatial_windows_z4-hi4}).
-The very large domains on the upper level of the 4 first groupments are not present anymore, and more variability can be observed.
-The selected points for the analogy on the humidity index are always located nearby the catchment, including 1 of the nearest point from the reanalysis dataset, and the spatial windows are relatively small.
+The z4-hi4 method presents more variability on the selection of the temporal windows for the humidity index.
+
+The optimized spatial windows for the atmospheric circulation have also changed (Figures \ref{fig:spatial_windows_z4-hi2} and \ref{fig:spatial_windows_z4-hi4}).
+The very large domains on the upper level of the 4 first subregions are not present anymore, and more variability can be observed.
+The selected points for the analogy on the humidity index are always located nearby the catchment, including at least 1 of the nearest points from the reanalysis dataset, and the spatial windows are relatively small.
 Thus, for our case study, there is no need to look for distant humidity information and the search could be reduced to a smaller domain.
@@
 The analysis of the parameters cross-compatibility (Tables \ref{table:crossing_z4-hi2_calib} to \ref{table:crossing_z4-hi4_valid}) is also very similar to the one on the circulation analogy only.
-The same pattern can be observed, with a drop of performance for the regions under different meteorological influences.
-However, the losses of performance are globally more important than before, suggesting that more complex methods with humidity variables are less transposable to another region, even though it is location within the same grid of the reanalysis dataset.
+The same pattern can be observed, with a drop of performance for the subregions under different meteorological influences.
+However, the losses of performance are globally more important than before, suggesting that more complex methods with humidity variables are less transposable to another subregion, even though it is located within the same grid of the reanalysis dataset.
 
@@
 The optimization of the analogue method by means of genetic algorithms has been undertaken in stages by releasing progressively new degrees of freedom.
-This approach allowed us to differentiate contributions to performance gains, as well as to identify possible over-parametrization.
+This approach allowed us to differentiate the contributions to performance gains, as well as to identify possible over-parametrization.
 The main improvements for our case study are due to the following factors:
@@
 \begin{itemize}
-	\item Using 4 atmospheric levels for the analogy of circulation.
+	\item Using 4 pressure levels for the analogy of circulation.
 It seems to be the optimal number for the studied region.
 Beyond that value the validation score drops, revealing a lost in robustness due to over-parametrization.
-	\item The automatic and joint optimization of all parameters: the analogues number, the choice of the atmospheric levels and the time windows, and the spatial windows.
+	\item The automatic and joint optimization of all parameters: the analogues number, the selection of the pressure levels and the time windows, and the spatial windows.
 These parameters are highly interdependent, so we need to optimize them jointly in order to identify optimal combinations.
-Traditional calibration procedures based on a systematic assessment of every combination is no more possible when considering more than 2 atmospheric levels.
-	\item The introduction of distinct spatial windows between atmospheric levels.
+Traditional calibration procedures based on a systematic assessment of every combination is no more possible when considering more than 2 pressure levels.
+	\item The introduction of distinct spatial windows between pressure levels.
 Indeed, the synoptic circulation is characterized by features with very different scales depending on the height, and important information for predicting rainfall is not necessarily located in the same area from one level to another.
-The optimized spatial windows are consistent in between the groupments.
-	\item The weighting of the analogy criteria between different atmospheric levels.
+The optimized spatial windows are consistent in between the subregions.
+	\item The weighting of the analogy criteria between different pressure levels.
 It can be influenced by the variability of the geopotential with altitude, and the change of some levels significance with the targeted region.
@@
 The spatial windows, for example, can be larger than the optimal size without much impact on the score, while they cannot be smaller \citep[see also][]{Bontron2004}.
-We could also observe that the choice of the atmospheric level is not a parameter as discrete as we would have thought, and that choosing another level may have reduced consequences on the performance.
-This is particularly true for higher atmospheric levels and can be more critical for lower layers.
+We could also observe that the selection of the pressure level is not a parameter as discrete as we would have thought, and that choosing another level may have reduced consequences on the performance.
+This is particularly true for higher pressure levels and can be more critical for lower layers.
 It was thus interesting to sometimes get several sets of near-optimal parameters, but with some nuances, in order to have an idea of the sensitivity of the parameters for a given region, and to compare the score on the validation period.
-In this regard, a cross-validation approach may be recommended.
+In this regard, a cross-validation technique may be advisable.
+An approach that can also be recommended, and that we use, is to first explore a wide range of the parameter space with some optimizations, and to narrow it according to the results for more targeted optimizations that are likely to go faster and to perform better.
 
@@
 As we could observe, methods with a higher complexity that integrate humidity predictors are less transposable than simpler ones.
-We also noticed in another unpublished work, that it is by far better to optimize for 2 regions jointly rather than to optimize on one and to apply its parametrization to the other.
-Finally, the creation of the groupments is an important stage and should be handled with care.
-Indeed, as we could observe, the geographical proximity is not always the leading factor to define a groupment.
-For example, the Southeast ridges groupment do not behave like its surrounding and differ in its parametrization, due to different leading meteorological influences.
-
-GAs are relatively heavy to implement and require an IT infrastructure capable of performing thousands hours of calculations.
+We also noticed in another unpublished work, that it is by far better to optimize for 2 subregions jointly rather than to optimize on one and to apply its parametrization to the other.
+Finally, the creation of the subregions is an important process and should be handled with care.
+Indeed, the geographical proximity is not always the leading factor to define a subregion.
+For example, the Southeast ridges subregion do not behave like its surrounding and differ in its parametrization, due to different leading meteorological influences.
+
+GAs are relatively heavy on processing and require an IT infrastructure capable of performing thousands hours of calculations.
 However, they automatically optimize all parameters of the analogue method, what the classic calibration does not allow.
-We therefore save much human time that was required to assess successively numerous combinations of parameters (particularly the choice of the atmospheric levels and the temporal windows).
-The ability to optimize jointly all parameters has been important given the strong dependencies between them and between levels of analogy.
+We therefore save much human time that was required to assess successively numerous combinations of parameters (particularly the selection of the pressure levels and the temporal windows).
+The ability to optimize jointly all parameters is important given the strong dependencies between them and between the levels of analogy.
 
@@
 
-In order to automatically optimize the analogue method, we evaluated the genetic algorithms, a global optimization technique, that is able to solve complex problems.
-Given the large number of existing operators and options, we had to evaluate systematically multiple variants in order to identify which operators are important, and which variant works best for the analogue method.
+In order to automatically optimize the analogue method, we evaluated genetic algorithms, a global optimization technique, that is able to solve complex problems.
+Given the large number of existing operators and options, we had to evaluate systematically multiple variants to identify which operators are important, and which variant works best for the analogue method.
 We could thus identify that the mutation operator is a key element for our application, and provided new variants that were found to be efficient, such as the Chromosome of adaptive search radius that seems to be very reliable (no control parameter) and efficient .
 Recommendations were established for a relevant use of GAs for the optimization of the analogue method.
-
-The parameters resulting from the optimization are very consistent for the analogy of the atmospheric circulation, in terms of choice of the pressure levels, and the temporal and spatial windows.
-There are clear trends or even identical results for regions under similar meteorological influences, which confirm that the optimized parameters are coherent, despite an eventual first impression of a great variability in the spatial windows.
+However, there may still be possible improvements, through new operators, in order to improve the optimization performance and speed.
+
+The parameters resulting from the optimization are very consistent for the analogy of the atmospheric circulation, in terms of selection of the pressure levels, and the temporal and spatial windows.
+There are clear trends or even identical results for subregions under similar meteorological influences, which confirm that the optimized parameters are coherent, despite an eventual first impression of a great variability in the spatial windows.
 When adding humidity variables, the results show a higher variability, but remains highly acceptable and coherent.
-Indeed, the choice of the pressure level for the humidity index is for example very constant.
+Indeed, the selection of the pressure level for the humidity index is for example very constant.
 
@@
 Thus, the classic calibration, which optimizes the parameters successively, may not lead to the optimal combination.
-Moreover, it contains several manual systematic assessment, such as the choice of the atmospheric levels and the temporal windows.
-GAs, however, can select the atmospheric levels and the time windows automatically, which can save a considerable amount of human time.
+Moreover, it contains several manual systematic assessment, such as the selection of the pressure levels and the temporal windows.
+GAs, however, can select the pressure levels and the time windows automatically, which can save a considerable amount of human time.
 A great advantage of a global optimization is its ability to approach or reach optimal parameter values when they are considered jointly.
@@
 
-For our case study, there seems to be an optimum number of atmospheric levels to consider for the analogy of circulation, which is four, before losing performance in validation.
-We have also been able to improve the analogy of circulation by introducing a weighting between atmospheric levels, and considering independent spatial windows between levels.
-However, there is a risk of over-parametrization with this type of approach.
-It is therefore important to always evaluate the proposed parameters over an independent period for validation.
-
-GAs provide parametrizations of the analogue method that exceed performance results of classic calibration.
+For our case study, there seems to be an optimum number of pressure levels to consider for the analogy of circulation, which is four, before losing performance in validation.
+We have also been able to improve the analogy of circulation by introducing a weighting between pressure levels, and considering independent spatial windows between levels.
+
+GAs provide parametrizations of the analogue method that exceed the performance of the classic calibration.
 In addition, we could observe that the forecasts for days with strong precipitation were significantly more improved, which is clearly interesting in the framework of flood forecasting.
 
-Perspective .........
-
-%\item Chromosome de rayons de recherche adaptatifs: nous avons élaboré le chromosome de rayons de recherche adaptatifs en nous inspirant du chromosome de taux de mutation adaptatifs.
-Notre version est plus performante, car elle intègre une notion de distance dans l'espace des paramètres, qui décroît avec l'évolution de la population, améliorant ainsi la convergence.
-Une grande force de cet opérateur est qu'il ne nécessite aucun paramètre, il s'autocontrôle et évolue avec la population, ce qui le rend très robuste.
-%\item Mutation multi-échelles: la mutation multi-échelles est une nouvelle approche qui ne cherche pas une évolution de l'opérateur de mutation, mais qui effectue des recherches globales, régionales et locales en tout temps.
-Il est ainsi constamment en train d'explorer l'espace des paramètres complet et d'exploiter l'information locale, les deux aspects importants des algorithmes génétiques.
-Il ne nécessite qu'un seul paramètre, qui est le taux de mutation.
-Celui-ci doit cependant être bien choisi, et cette valeur change en fonction de la méthode à optimiser.
-
-% Finalement, les AGs, tels qu'ils ont été implémentés, sont également en mesure de choisir les variables prédicteurs d'intérêt.
-Si nous n'avons plus vraiment de doute sur le choix des variables pour la prévision des précipitations, en raison des multiples travaux réalisés sur ce sujet, nous ne connaissons pas a priori les variables qui seraient les plus informatives pour prévoir un autre prédictand, comme la température, la grêle ou le vent.
-Ces outils d'optimisation peuvent alors explorer les variables et nous proposer les meilleures combinaisons.
-Toutefois, l'automatisation de variables composées (par exemple le flux d'humidité) présentera toujours quelques limites.
+This work is by far not exhaustive and means to open a door for new explorations with the analogues methods.
+It becomes possible to even let the optimizer chose the meteorological variable to be used as predictor, as well as the analogy criteria.
+It is already possible to undertake such data mining with our code.
+Moreover, the analogue method has been explored for decades for precipitation forecasting, but very few work analysis its potential for other predictands.
+A global optimizer, such as GAs, can speed up this assessment significantly.
 
@@
 			\hline 
-			preselection & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
 			\hline 
@@
 	\footnotesize
-	\caption{Parameters of the z4 method (analogy on 4 levels of the atmospheric circulation) optimized for the Chablais region.
+	\caption{Parameters of the z4 method (analogy on 4 levels of the atmospheric circulation) optimized for the Chablais subregion.
 The columns are the following: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
@@
 	\footnotesize
-	\caption{Atmospheric levels automatically selected for the z4 method at the different groupments.}
+	\caption{Atmospheric levels automatically selected for the z4 method at the different subregions.}
 	\begin{center}
@@
 	\footnotesize
-	\caption{Parameters of the z4-hi2 method (atmospheric circulation on 4 levels and humidity index on 2 levels), optimized for the Chablais region. Same conventions as Table \ref{table:params_GA_z4}.}
+	\caption{Parameters of the z4-hi2 method (atmospheric circulation on 4 levels and humidity index on 2 levels), optimized for the Chablais subregion.
+Same conventions as Table \ref{table:params_GA_z4}.}
 	\begin{center}
@@
 	\footnotesize
-	\caption{Parameters of the z4-hi4 method (atmospheric circulation on 4 levels and humidity index on 4 levels), optimized for the Chablais region. Same conventions as Table \ref{table:params_GA_z4}.}
+	\caption{Parameters of the z4-hi4 method (atmospheric circulation on 4 levels and humidity index on 4 levels), optimized for the Chablais subregion.
+Same conventions as Table \ref{table:params_GA_z4}.}
 	\begin{center}
@@
 	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation of the z4-hi2 method, at the different groupments.}
+	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation of the z4-hi2 method, at the different subregions.}
 	\begin{center}
@@
 	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of humidity of the z4-hi2 method, at the different groupments.}
+	\caption{Atmospheric levels automatically selected for the analogy of humidity of the z4-hi2 method, at the different subregions.}
 	\begin{center}
@@
 	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation of the z4-hi4 method, at the different groupments.}
+	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation of the z4-hi4 method, at the different subregions.}
 	\begin{center}
@@
 	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of humidity of the z4-hi4 method,at the different groupments.}
+	\caption{Atmospheric levels automatically selected for the analogy of humidity of the z4-hi4 method,at the different subregions.}
 	\begin{center}
@@
 	\end{subfigure}
-	\caption{Optimized spatial windows for the z4 method (analogy of atmospheric circulation on 4 atmospheric levels).
-The atmospheric levels are ordered by increasing pressure and increasing time for the same levels.}
+	\caption{Optimized spatial windows for the z4 method (analogy of atmospheric circulation on 4 pressure levels).
+The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
 	\label{fig:spatial_windows_z4}
@@
 	\end{subfigure}
-	\caption{Optimized spatial windows for the z4-hi2 method (analogy of atmospheric circulation on 4 atmospheric levels and the analogy on the humidity index on 2 atmospheric levels).
-The atmospheric levels are ordered by increasing pressure and increasing time for the same levels.}
+	\caption{Optimized spatial windows for the z4-hi2 method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the humidity index on 2 pressure levels).
+The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
 	\label{fig:spatial_windows_z4-hi2}
@@
 	\end{subfigure}
-	\caption{Optimized spatial windows for the z4-hi4 method (analogy of atmospheric circulation on 4 atmospheric levels and the analogy on the humidity index on 4 atmospheric levels).
-The atmospheric levels are ordered by increasing pressure and increasing time for the same levels.}
+	\caption{Optimized spatial windows for the z4-hi4 method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the humidity index on 4 pressure levels).
+The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
 	\label{fig:spatial_windows_z4-hi4}
@@
 	\centerline{\includegraphics[width=7.9cm]{figures/figure_levels_weights.pdf}}
-	\caption{Optimized weighting for the atmospheric levels of the z4 method.}
+	\caption{Optimized weighting for the pressure levels of the z4 method.}
 	\label{fig:levels_weights}
@@
 	\centerline{\includegraphics[width=7.9cm]{figures/figure_levels_weights_average.pdf}}
-	\caption{Averaged weighting for the atmospheric levels of the circulation analogy of the three methods.}
+	\caption{Averaged weighting for the pressure levels of the circulation analogy of the three methods.}
 	\label{fig:levels_weights_average}

### 2015-10-13 AtmoSwing - Geoscientific Model Development/template.tex
Moving content from the optimization paper to the AtmoSwing one.

--- 2015-08-12 Optimization - Journal of Climate/template.tex
@@
-%% Version 4.3.2, 25 August 2014
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Template.tex --  LaTeX-based template for submissions to the 
-% American Meteorological Society
-%
-% Template developed by Amy Hendrickson, 2013, TeXnology Inc., 
-% amyh@texnology.com, http://www.texnology.com
-% following earlier work by Brian Papa, American Meteorological Society
-%
-% Email questions to latex@ametsoc.org.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PREAMBLE
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Start with one of the following:
-% DOUBLE-SPACED VERSION FOR SUBMISSION TO THE AMS
-\documentclass{ametsoc}
-
-% TWO-COLUMN JOURNAL PAGE LAYOUT---FOR AUTHOR USE ONLY
-%\documentclass[twocol]{ametsoc}
-
-\usepackage{multirow}
-\usepackage{gensymb}
-\usepackage{subcaption}
-\usepackage{xcolor,colortbl}
-
-% After http://tex.stackexchange.com/questions/94799/how-do-i-color-table-columns-and-rows
-\newcommand{\mc}[2]{\multicolumn{#1}{c}{#2}}
-\definecolor{Gray}{gray}{0.85}
-\definecolor{LightCyan}{rgb}{0.88,1,1}
-\newcolumntype{a}{>{\columncolor{Gray}}c}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% To be entered only if twocol option is used
-
-\journal{jcli}
-
-%  Please choose a journal abbreviation to use above from the following list:
-% 
-%   jamc     (Journal of Applied Meteorology and Climatology)
-%   jtech     (Journal of Atmospheric and Oceanic Technology)
-%   jhm      (Journal of Hydrometeorology)
-%   jpo     (Journal of Physical Oceanography)
-%   jas      (Journal of Atmospheric Sciences)	
-%   jcli      (Journal of Climate)
-%   mwr      (Monthly Weather Review)
-%   wcas      (Weather, Climate, and Society)
-%   waf       (Weather and Forecasting)
-%   bams (Bulletin of the American Meteorological Society)
-%   ei    (Earth Interactions)
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Citations should be of the form ``author year''  not ``author, year''
-\bibpunct{(}{)}{;}{a}{}{,}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%% To be entered by author:
-
-%% May use \\ to break lines in title:
-
-\title{Global Optimization of the Analogue Method by Means of Genetic Algorithms}
-
-%%% Enter authors' names, as you see in this example:
-%%% Use \correspondingauthor{} and \thanks{Current Affiliation:...}
-%%% immediately following the appropriate author.
-%%%
-%%% Note that the \correspondingauthor{} command is NECESSARY.
-%%% The \thanks{} commands are OPTIONAL.
-
-    %\authors{Author One\correspondingauthor{Author One, 
-    % American Meteorological Society, 
-    % 45 Beacon St., Boston, MA 02108.}
-% and Author Two\thanks{Current affiliation: American Meteorological Society, 
-    % 45 Beacon St., Boston, MA 02108.}}
-
-\authors{Pascal Horton\correspondingauthor{Terranum, Rue de l'industrie 35 bis, 1030 Bussigny, Switzerland.}}
-
-%% Follow this form:
-    % \affiliation{American Meteorological Society, 
-    % Boston, Massachusetts.}
-
-\affiliation{University of Lausanne and Terranum, Lausanne, Switzerland}
-
-%% Follow this form:
-    %\email{latex@ametsoc.org}
-
-\email{pascal.horton@alumnil.unil.ch}
-
-%% If appropriate, add additional authors, different affiliations:
-    %\extraauthor{Extra Author}
-    %\extraaffil{Affiliation, City, State/Province, Country}
-
-\extraauthor{Michel Jaboyedoff}
-\extraaffil{University of Lausanne, Lausanne, Switzerland}
-
-%% May repeat for a additional authors/affiliations:
-
-%\extraauthor{}
-%\extraaffil{}
-
-\extraauthor{Charles Obled}
-\extraaffil{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% ABSTRACT
-%
-% Enter your abstract here
-% Abstracts should not exceed 250 words in length!
-%
-% For BAMS authors only: If your article requires a Capsule Summary, please place the capsule text at the end of your abstract
-% and identify it as the capsule. Example: This is the end of the abstract. (Capsule Summary) This is the capsule summary.
-
-\abstract{The analogues method is based on a statistical relationship between synoptic atmospheric variables and local weather, which we aim at forecasting.
-This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic procedure.
-This classic calibration is relatively fast and provide acceptable results, but it has strong constraints, is made of successive steps and thus cannot handle parameters dependencies, and mainly, it cannot calibrate automatically some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared.
-In order to surpass these limitations, we assessed a global optimization technique, namely genetic algorithms, that can optimize jointly all parameters of the method and thus provide a global optimum by taking into account the parameters dependencies.
-Moreover, it can calibrate parameters that were previously manually assessed, and can take into account new degrees of freedom that were unthinkable before.
-These kind of optimization techniques need however to be tailored to the problem to solve.
-We had to assess multiple combinations of algorithms, and even to develop new operators, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of genetic algorithms to optimize the analogue method.
-These recommendations are the primary outcome of this work, as it opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.
-We then applied the optimizer to the Rh\^{o}e catchment in the Swiss Alps and obtained coherent results which significantly improve the performance of the forecasting by analogy.
-The optimizer allowed us to calibrate jointly all parameters of the method and to add a weighting of the criteria per pressure level, as well as non-overlapping spatial windows.}
+%% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
+%% ---------------------------------
+%% This template should be used for copernicus.cls
+%% The class file and some style files are bundled in the Copernicus Latex Package which can be downloaded from the different journal webpages.
+%% For further assistance please contact the Copernicus Publications at: publications@copernicus.org
+%% http://publications.copernicus.org
+
+%% Please use the following documentclass and Journal Abbreviations for Discussion Papers and Final Revised Papers.
+
+%% 2-Column Papers and Discussion Papers
+\documentclass[gmd, manuscript]{copernicus}
+
+%% Journal Abbreviations (Please use the same for Discussion Papers and Final Revised Papers)
+
+% Geoscientific Model Development (gmd)
+% Hydrology and Earth System Sciences (hess)
+
+%% \usepackage commands included in the copernicus.cls:
+%\usepackage[german, english]{babel}
+%\usepackage{tabularx}
+%\usepackage{cancel}
+%\usepackage{multirow}
+%\usepackage{supertabular}
+%\usepackage{algorithmic}
+%\usepackage{algorithm}
+%\usepackage{float}
+%\usepackage{subfig}
+%\usepackage{rotating}
 
@@
 
-%% Necessary!
+\linenumbers
+
+\title{AtmoSwing (v1.4): Analog Technique Model for Statistical weather forecastING}
+
+% \Author[affil]{given_name}{surname}
+
+\Author[1,2]{Pascal}{Horton}
+\Author[1]{Michel}{Jaboyedoff}
+\Author[3]{Charles}{Obled}
+
+\affil[1]{University of Lausanne, Lausanne, Switzerland}
+\affil[2]{Terranum, Lausanne, Switzerland}
+\affil[3]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}
+
+%% The [] brackets identify the author with the corresponding affiliation. 1, 2, 3, etc. should be inserted.
+
+\runningtitle{TEXT}
+
+\runningauthor{TEXT}
+
+\correspondence{Pascal Horton (pascal.horton@alumnil.unil.ch)}
+
+\received{}
+\pubdiscuss{} %% only important for two-stage journals
+\revised{}
+\accepted{}
+\published{}
+
+%% These dates will be inserted by Copernicus Publications during the typesetting process.
+
+\firstpage{1}
+
 \maketitle
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% MAIN BODY OF PAPER
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-
-%% In all cases, if there is only one entry of this type within
-%% the higher level heading, use the star form: 
-%%
-% \section{Section title}
-% \subsection*{subsection}
-% text...
-% \section{Section title}
-
-%vs
-
-% \section{Section title}
-% \subsection{subsection one}
-% text...
-% \subsection{subsection two}
-% \section{Section title}
-
-%%%
-% \section{First primary heading}
-
-% \subsection{First secondary heading}
-
-% \subsubsection{First tertiary heading}
-
-% \paragraph{First quaternary heading}
-
-\section{Introduction}
-\label{section_intro}
-
-The analogue method is a downscaling technique based on the idea expressed by \citet{Lorenz1969}, that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Bontron2005}.
-It aims at forecasting a predictand, often the daily precipitation, on the basis of predictor variables describing the synoptic atmospheric circulation.
-Many parameters define this relationship, which are usually calibrated by means of a semi-automatic procedure.
-
-\subsection{The analogue method}
-\label{section_analog_method}
-
-Multiple variations of the methods exist, and some aspects and parameters will not be detailed hereafter.
-There are mainly 2 parametrizations that are used most often: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on humidity variables \citep{Obled2002, Bontron2005, Marty2012}.
-
-The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): We assess the similarity of the atmospheric circulation of a target date with every day of the archive by processing the S1 criteria \citep[Eq.\ (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
-\citet{Bontron2005} showed that the geopotential height at 500~hPa and 1000~hPa are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criteria performs better than scores based on absolute distances.
-The reason for such better results is that the S1 criteria allows comparing the circulation pattern, by means of the gradients, rather than the absolute value of the geopotential height.
-To cope with seasonal effects, candidate dates are extracted within a period of 4 months centred around the target date, for every year of the archive.
-
-\begin{equation}
-\label{eq:S1}
-S1=100 \frac {\displaystyle \sum_{i} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
-{\displaystyle \sum_{i} max\left\lbrace \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert \right\rbrace }
-\end{equation}
-where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points in the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
-The differences are processed separately in both directions.
-The smaller the S1 values are, the more similar the pressure fields.
-
-The $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day.
-The number of analogues, $N_{1}$, is a parameter to calibrate.
-Then, the daily observed precipitation amount of the $N_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
-
-The other most know parametrization adds a second level of analogy on humidity variables (Table \ref{table:params_R2}).
-The predictor that \citet{Bontron2004} found optimal for the France territory is a humidity index made of the product of the precipitable water with the relative humidity at 850~hPa.
-\cite{Horton2012a} confirmed that this index is better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis considered independently.
-When adding a second level of analogy, we subsample $N_{2}$ dates in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
-When we add a second level of analogy, we keep a higher number of analogues on the first level.
-
-\subsection{Data}
-\label{section_data}
-
-The analogue method relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series we want to forecast.
-
-Predictors are generally reanalysis datasets (and outputs of a global numerical weather prediction models for the target situation in operational forecasting, which is not the topic of this paper).
-We will work here with the NCEP/NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996}, but it can be any other reanalysis dataset.
-
-The predictand (which is to be predicted) is in our case the daily precipitation (6~a.m.
-to 6~a.m.
-the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008.
-The time series from every available gauging station were averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.
+\begin{abstract}
+% TODO: write
+
+\end{abstract}
+
+\introduction  %% \introduction[modified heading if necessary]
+% TODO: write
+
+\section{The analogue method}
+
+As AtmoSwing does not rely heavily on one variant of the analogue method, but can implement different parametrization, we gathered here several references of possible implementations as well as the main evolution steps of the analogue method.
+This latter summarizes the improvements that were brought, as well as discontinued approaches that were found less relevant (such as the use of PCA on the predictors).
+
+\subsection{Principles}
+
+The analogue method is based on the principle that two similar synoptic situations may produce similar local effects \citep{Lorenz1956}.
+The perfect analogy does not exist, but sufficiently similar situations leading to similar effects can be identified.
+Thus, two states of the atmosphere that are alike are called analogues \citep{Lorenz1969}.
+To be relevant, this analogy must be selected by optimizing the following elements:
+
+\begin{itemize}
+	\item The analogy variable (the predictor) must contain synoptic information having indirect dependency with the local weather and the target variable (often the precipitation).
+	\item The spatial window is the domain on which the analogy variable is considered. The ideal size of this area is one that maximizes useful information.
+	\item The temporal window is the hour of day at which we consider the analogy variable. The analogy can be instantaneous (eg. 12~h~UTC) or averaged over a period (eg. 24~h).
+	\item The analogy period is the time of year in which similar situations are being sought. Thus, we compare situations with a similar distribution of solar energy \citep{Lorenz1969}.
+	\item The analogy criterion, needed to compare the variables on the chosen spatial and temporal windows, is a score used for ranking past situations according to their degree of similarity with the target situation \citep{Bontron2004}.
+	\item The ideal number of analogues situations is the best compromise in order to take into account local variability and to maximize useful synoptic information  \citep{Bontron2004}.
+\end{itemize}
+
+Because of the chaotic nature of the atmosphere, two analogue situations quickly diverge over time \citep{Lorenz1969}.
+Thus, the method has strong limitations regarding the temporal extrapolation \citep{Bontron2004}.
+Numerical models being more capable of simulating the dynamic evolution of the atmosphere, the temporal extrapolation of the synoptic variables is left to them.
+The search for analogy aims thus at connecting the forecasted synoptic situation with a local predictand (temperature, precipitation ...), which is more difficult to simulate by numerical models.
+
+The analogue method is being used for many years at EDF (\'{E}lectricit\'{e} de France), to build precipitation and temperature scenarios \citep{Desaint2008a}.
+It is also operational at the Compagnie Nationale du Rh\^{o}ne (CNR, France) and some flood forecasting services (SPC) in France and Switzerland \citep{Marty2010,GarciaHernandez2009b,Horton2012}.
+
+\subsection{Its evolution}
+
+\citet{Lorenz1969} introduced the concept and established the basis of the method.
+He considered looking for analogues on the geopotential field (at 200, 500 and 850~hPa) with a corrected Euclidean distance averaged on the 3 levels.
+In addition, the analogue situations were to belong to the same period of the year to be comparable in terms of distribution of solar energy.
+
+The use of the analogue method for operational forecasting of daily precipitation originates in the work of \citet{Duband1970,Duband1974,Duband1981}.
+It was then designed for operational forecasting at EDF (\'{E}lectricit\'{e} de France) in order to better manage water resources and flood risks.
+The geopotential height at 700~hPa and 00~h was used for its higher stability than the sea level pressure (SLP) field, and its sensitivity to the atmospheric disturbances \citep{Guilbaud1997}.
+However, the SLP at 06~h was also used for determining the intensity of precipitation, as well as the temperature at 700~hPa as indicator of the thermal state of the air mass \citep{Duband1974}.
+The data were then based on 37 radiosounding over Europe and condensed by a principal component analysis.
+The first 25 analogues on the geopotential at 700~hPa were considered, and multiple local regressions between precipitation, SLP, and the temperature at 700~hPa were established on these analogues before being applied to the target situation \citep{Guilbaud1997}.
+The archives were split by season to consider comparable situations in terms of distribution of solar energy \citep{Lorenz1969}.
+This initial rigid division into seasons was then transformed into a moving selection of more or less two months around the target date.
+The forecast was then performed only on the basis of observations and was temporally extrapolated to the following two days.
+After a few years, this statistical temporal extrapolation was abandoned in favor of a statistical adaptation using predictors resulting from an global numerical model, allowing a forecast over the following 4~days.
+
+Thereafter, the geopotential was considered at 1000~hPa and 700~hPa and the analogues selection was done in two stages: first according to an Euclidean distance in the space of the principal components of the geopotential field at 700~hPa, and then according to a correlation criterion (on the geopotential field at 700 and 1000~hPa, as well as on the thickness between these two levels) in order to remove days too dissimilar \citep{Guilbaud1997}.
+The regression approach to determining precipitation was eventually abandoned in favor of the probabilistic forecasting (synthesized by the percentiles 20, 60 and 90~\%), as it is performed today by interpolating linearly over the cumulative empirical distribution of daily precipitation measured at the analogue days \citep{Guilbaud1997,Guilbaud1998}.
+
+\citet{Wilson1980} sought the 20 best analogues on the geopotential field at 500 and 1000~hPa using the Teweles-Wobus (S1) criterion (Eq.
+\ref{eq:S1}), which allows for a comparison of the gradients and thus an analogy of the atmospheric circulation.
+\citet{Woodcock1980} used the same criterion on the SLP fields to select 50~analogues in order to forecast maximum daily temperatures.
+\citet{Yacowar1975} considered the 20 best analogues on the maximum of the sum of correlations on the two fields.
+This work has demonstrated the best performance of the analogues method compared to regression methods, as well as the interest to search for analogues on two (500 and 1000~hPa) geopotential fields combined \citep{Guilbaud1997}.
+
+\citet{Mandon1985} introduced a second level of analogy and assessed different variables, such as wind, humidity, air temperature, surface temperature of the Mediterranean, the product of wind and the 700~hPa moisture, as well as a second barometric criteria differentiated according to the season.
+\citet{Vallee1986} continued to work on the second level of analogy and considered the wind at 700~hPa \& 12~h in order to improve heavy precipitation events for a region in France susceptible to southerly flows.
+
+Taking advantage of higher-performance IT tools \citet{Guilbaud1997} stopped using PCA in order to work directly with the raw data interpolated on grids, which was an improvement, especially when considering the S1 criterion (already used for analogues selection by\citealp{Wilson1980} and \citealp{Woodcock1980}) instead of the Euclidean distance.
+This score gives importance to the similarity of atmospheric circulation rather than absolute values of the pressure field.
+After comparing this criterion to other criteria from the literature, or combinations of these, \citet{Guilbaud1998} found that S1 is the most efficient.
+They also pointed out the benefit of using 2 atmospheric levels instead of one (also instead of the thickness), and to also consider 2 temporal windows \citep{Obled2002}.
+When using multiple predictors, they combined the criteria values calculated on each atmospheric level and each temporal window using an arithmetic mean.
+Finally, they also suggested using a second level of analogy on lower layers humidity and introduced the Ranked Probability Score \citep{Epstein1969} to assess the forecast quality, which was found to be more relevant that the Brier score \citep{Brier1950}.
+
+\subsection{References implementations}
+% TODO: write
+
+\subsection{Datasets}
+% TODO: write
+
+\section{Software basics}
+% TODO: write
+
+\subsection{Structure}
+% TODO: write
+
+\subsection{Modular approach}
+% TODO: write
+
+\subsection{Technical specifications}
+% TODO: write
+% Language and libraries
+
+\subsection{Performance}
+% TODO: write
+
+\subsection{Unit tests}
+% TODO: write
+
+\section{The forecaster module}
+% TODO: write
+
+\section{The viewer module}
+% TODO: write
+
+\section{The calibrator module}
+% TODO: write
 
@@
 where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect forecast ($CRPS_{p} = 0$).
+
+\subsection{Implemented forecasts scores}
+% TODO: write
 
@@
 
-\subsection{Motivation for a global optimization}
-
-The classic calibration is fast to optimize one spatial window for a given pressure level and temporal window.
-However, it doesn't provide an objective selection of the pressure level and temporal window.
-The only option is to try systematically every combination, which may be acceptable for no more than 2 levels.
-However, \citet{Horton2012a} showed that additional pressure levels may improve the method.
-
-We observed during the calibration of the analogue method that the resulting parameters vary with the initial choices (such as the number of analogues).
-In addition, the different levels of analogy (eg on the atmospheric circulation and the humidity index) are always calibrated sequentially.
-However, we can not exclude any dependency between them, which could lead us to select another parametrization if we calibrate them together.
-Simultaneous calibration of all parameters has never been undertaken so far.
-Only a global optimization technique can be able to optimize all parameters of all analogy levels simultaneously.
-
-When creating the classic calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters and wrote: '' \textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent.
-We will present our results by first searching the best variable [note: e.g.
-selection of the pressure level and the temporal window for the geopotential height] on a chosen spatial window, and next, the best window for the chosen variable.
-However, even by repeating the process, are we sure to obtain the optimal combination?} ''.
-And later in his work: '' \textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution} ''.
-\citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of the analogue method and concludes that one needs to be an expert to know their respective influence, their sensitivity and their nonlinear interactions.
-\citet{BenDaoud2010}, when calibrating the analogue method, also stated that '' \textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously } ''.
-
-The analogue method needs to be adapted to every new region it is applied, because the leading meteorological influences are specific to this region.
-Even the selection of the pressure level and the temporal window should be reconsidered, when not the variable itself.
-For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012a} found no interest in this variable in an Alpine environment, because in the Alps, the vertical motion is mainly controlled by orographic effects, and was thus already well related to the atmospheric circulation itself.
-So, when adapting the analogue method to a new region, we should assess systematically every combination of pressure levels, time and spatial windows, which is an intensive task.
-This procedure can be automatized by a global optimization technique.
-
-Our ambition was then to assess the feasibility of an automatic optimization of the analogue method through various techniques.
-The objective was to find an approach to optimize all parameters simultaneously, and thus be able to identify the global optimum in the parameter space.
-In addition, it can overcome the systematic manual assessments of certain parameters such as the selection of the pressure levels and time windows.
-Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the pressure levels, and the consideration of non-overlapping spatial windows between the pressure levels.
-
-\citet{Horton2012a} assessed the ability of the \citet{Nelder1965a} method based on a simplex approach.
-This technique didn't provide satisfying results and failed at identifying the global optimum.
-Indeed, the results didn't converge and many local optimums came out.
-The parameter space of the analogue method is very complex and not appropriate for a linear optimization technique.
-Genetic algorithms were found to be much more relevant for such application.
-
-\section{Adjusting genetic algorithms}
+\subsection{Monte-Carlo analysis}
+
+\subsection{Optimization}
+
+\section{The global optimization tools}
 
@@
 
-\section{Example case study}
-
-The analogue method has to be adapted to every new location it is applied.
-We improved the analogue method for the Swiss Alps, by means of genetic algorithms.
-A summary of the main results are provided here \citep[see][for the details]{Horton2012a}.
-Even though the results may differ from one place to another, the applicability of GAs to the analogue method remains universal.
-
-\subsection{Case study description}
-
-The study area is the alpine upper Rh\^{o}ne catchment in Switzerland (Fig.\ \ref{fig:map}).
-The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$.
-This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at providing a real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
-Even thought the region is rather small, the meteorological influences related to extreme weather conditions varies substantially within it \citep[see][]{Horton2012}.
-Based on different climatological analyses, the gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}) :
-
-\begin{enumerate}
-	\setlength\itemsep{-4px}
-	\item Swiss Chablais
-	\item Trient Valley
-	\item West Bernese Alps
-	\item Lower Rhone Valley
-	\item Left side valleys
-	\item Southern ridges
-	\item Upper Rhone Valley
-	\item Southeast ridges
-	\item East Bernese Alps
-	\item Conches Valley
-\end{enumerate}
-
-The 48 years precipitation dataset (see section \ref{section_intro}.\ref{section_data}) was divided into a calibration period and a validation period.
-Using data independent from the calibration period to validate our results is very important in order to assess the robustness of the improvements and to avoid overparametrization of the method.
-
-In order to reduce potential bias related to trends in the climate change or to the evolution in measurement techniques, the selection of the validation period is evenly distributed over the entire series \citep{BenDaoud2010}.
-Thus, we selected one year every six years for validation, which represents a total of 8 years for the validation and 40 for calibration.
-The choice of the sequence was made in order to have similar statistical characteristics between the calibration and the validation periods.
-
-\subsection{Optimization of the analogy of atmospheric circulation}
-
-We first optimized the analogy of atmospheric circulation alone, without humidity variables, for our 10 subregions.
-We started from the most simple analogue method, and increased the complexity in order to identify the degrees of freedom that are of particular interest.
-Thus, the tested parametrization evolved iteratively in complexity.
-We do not provide the detailed results of the intermediate stages \citep[see][for the details]{Horton2012a}, but only the main conclusions.
-
-We first considered the reference method for the analogy of the atmospheric circulation, based on the 500 and 1000~hPa levels.
-We let the optimizer choose the number of analogues, both spatial windows with no overlapping constraint, as well as the temporal window (hours of observation of the geopotential).
-The classic calibration cannot automatically choose the temporal window, neither handle non-overlapping spatial windows, and finally it cannot optimize all parameters simultaneously.
-With these improvements, we could gain a relative improvement of the CRPSS of 3.97\% and 2.45\% in average for the calibration and the validation periods respectively.
-Some tests showed that most of the gains are due to the non-overlapping spatial windows.
-
-Then, we provided an additional degree of freedom to the AGs by letting them choose the pressure levels along with the other parameters.
-Evaluation of pressure levels is also a non-automated process in the classic calibration.
-We could observe that this degree of freedom increases the optimization time and may decrease the number of simulations that converge to a single solution.
-However, most solutions were very close in terms of score.
-The averaged relative improvement of the CRPSS is 5.63\% for the calibration and 3.82\% for the validation periods.
-The pressure levels that were chosen are 500~hPa or 700~hPa for the upper level, and 925~hPa or 1000~hPa (most often) for the lower level.
-
-Parallel analyses showed that the analogy of circulation is incomplete, and that the geopotential still contains relevant data that can improve the statistical relationship.
-Therefore, we added a third predictor (still the geopotential height) that the optimizer could use along with the previous parameters.
-There was no constraint on the predictors, so that the same pressure level could be selected multiple times.
-Some improvements were found on the score, both for the calibration and the validation periods, confirming that this additional information is beneficial for the quality of the forecast.
-We then tried with 4 predictors, and so on, up to 8.
-Every time we added a new predictor to optimize, the score on the calibration period increased, but always more to a smaller extent.
-However, the score on the validation period dropped after 4 predictors, revealing an over-parametrization of the method, and thus a lack of robustness.
-We thus found that considering 4 predictors is optimal for our case study, since the gain in CRPSS is significant.
-It can not be excluded that another number would prevail under other meteorological conditions.
-
-Finally, we added a weighting of these 4 predictors (pressure levels), which is also optimized by GAs.
-The weighting operates in the combination of the S1 criteria processed on every level, which were previously averaged with equal weights.
-The role of this new degree of freedom is to give more weight to the levels with greater predictive capacity, and to consider the geopotential variability changes with altitude.
-
-\subsubsection{Which parameters are optimized ?}
-
-The method we finally optimized for the analogy of the atmospheric circulation, based on 4 levels of the geopotential, and that we will name z4, is made of the following degrees of freedom:
-
-\begin{itemize}
-	\setlength\itemsep{-4px}
-	\item the selection of the pressure levels (4 degrees)
-	\item the temporal windows (4 degrees)
-	\item the spatial windows (16 degrees)
-	\item the weights (4 degrees)
-	\item the number of analogues (1 degrees).
-\end{itemize}
-
-This sums up to 29 degrees of freedom that are optimize simultaneously.
-
-\subsubsection{Results for the z4 method}
-
-The resulting optimized parameters for z4 vary from one subregion to another.
-An example of the detailed parameters is provided for the Swiss Chablais in Table \ref{table:params_GA_z4}.
-The optimized spatial windows are given for every subregion in Figure \ref{fig:spatial_windows_z4}, and the selected pressure levels in Table~\ref{table:levels_GA_z4}.
-
-The resulting CRPSS scores are provided in Table \ref{table:scores} and is in average 35.8 \% in calibration and 35.5 \% in validation.
-The improvement of the CRPSS score relatively to the reference method on the atmospheric circulation is provided in Table \ref{table:scores_diff} and is in average 15.3 \% in calibration and 9.9 \% in validation.
-The score was also calculated for three precipitation thresholds: P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_z4}).
-The gain in score increases with the precipitation threshold: in average, respectively for the different thresholds, 13.3\%, 15.4\% and 29.1\% in calibration and 7.9\%, 11.1\% and 34.5\% for the validation period.
-The optimized method improves thus even more the forecasts for days with significant precipitation than usual days.
-
-To assess the cross-compatibility of the parameters, we applied those optimized for one subregion to the others.
-The resulting losses or gains of the CRPSS are displayed in Table \ref{table:crossing_z4_calib} for the calibration period and in Table \ref{table:crossing_z4_valid} for the validation period.
-
-\subsubsection{Analysis}
-
-The selections of the pressure levels for the analogy of circulation show a great homogeneity and is spatially consistent (Table \ref{table:levels_GA_z4}).
-First of all, the level 1000~hPa is selected twice (the first time at 6 or 12~h, and the second always at 30~h) and the 700~hPa is selected once for every subregion (always at 24~h).
-The level which varies from one subregion to another is the upper level (always at 12~h), that is 300~hPa for the North-West part of the catchment, 500~hPa for most of the subregions, and 600~hPa for the Conches Valley.
-Its spatial distribution is however homogeneous.
-The optimizer thus provided consistent selections of pressure levels and temporal windows, which depicts a significant preference in the analogue method, and the success of our GAs to provide consistent results.
-The automatic selection of the pressure levels is a big advantage of a global optimization, as it is not possible to assess all combinations of 4 levels with the classic calibration procedure.
-
-The resulting spatial windows (Figure \ref{fig:spatial_windows_z4}) may look very diverse first, but there are significant similarities for subregions located within the same vicinity.
-The first 4 subregions are characterized by a large spatial window on the upper level, whereas it becomes smaller for the other subregions.
-For most subregions, the second level (700~hPa) is represented by thin and longitudinally extended domains.
-The third level (1000~hPa at 6 or 12~h) also contains longitudinally extended domains, but a bit larger.
-The last one (1000~hPa at 30~h) is rather large and squared.
-Surprisingly, subregions number 5 (Left side valleys) and 6 (Southern ridges) have exactly the same spatial windows, which suggest that they behave in a similar way and thus could have been merged.
-This similarity is a good sign for the accuracy of our optimized parameters.
-
-The scores show significant improvements for both the calibration and the validation period (Table \ref{table:scores_diff}).
-Even more interestingly, the results for higher precipitation thresholds (Table \ref{table:scores_thresholds_z4}) show the largest improvements.
-This is of particular interest in the framework of flood forecasting.
-
-The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the calibration period when they are calibrated for the given subregion (Table \ref{table:crossing_z4_calib}).
-However, the losses in CRPSS are not of the same amplitude between the different subregions.
-Indeed, the Upper Rhone Valley (7) and moreover the Southeast ridges (8) seem to behave significantly differently.
-This is indeed a climatological reality, as this subregion is the most sensitive to southerly flows \citep{Horton2012}.
-Parameter sets from other subregions perform poorly for these subregions, and vice versa.
-Nevertheless, both subregions seem quite inter-compatible.
-This points to the importance of taking into account leading meteorological influences during subregion creation, which is not always best represented by the geographical distance separating them.
-Globally, the same pattern can be observed for the validation period (Table \ref{table:crossing_z4_valid}), but in this case, minor improvements may be observed when crossing the parameters.
-The reason being that the independant validation period contains other events that may be better forecasted by other parameter sets.
-The relative small differences in score between parametrizations indicate that even though the parameters may differ significantly, the performance may not be drastically affected.
-Even a change in the pressure level does not mean a radical drop of the score.
-A different parametrization leads to a different selection of the analogue days, and thus to an improvement of the forecast of certain weather conditions at the expense of others.
-This raises the question of optimizing more specifically for extreme weather conditions only.
-
-\subsection{Optimization of the analogy with humidity variables}
-
-We previously worked with a method based on a unique level of analogy.
-However, we know that humidity variables in a second level of analogy do provide improvements to the method (section \ref{section_intro}.\ref{section_analog_method}).
-So we also wanted to optimize the humidity index, which is a combination of the relative humidity and the precipitable water.
-In order to do so, we had to introduce a constraint to the optimizer, so that it selects the same temporal window for both variables.
-
-Two methods were assessed: one with 2 humidity predictors (humidity index on 2 pressure levels or at 2 different hours) named z4-hi2, and one with 4 humidity predictors named z4-hi4.
-When we introduce 2 predictors for the humidity analogy, the number of degrees of freedom raises to 42, and to 54 when we add 4 predictors.
-
-We proceeded to an optimization of both levels of analogy simultaneously. This implies that the analogy of the atmospheric circulation may change due to the new humidity information.
-
-\subsubsection{Results for z4-hi2 and z4-hi4 methods}
-
-As previously, the optimized parameters differ from one subregion to another, and this event to a greater extent.
-Detailed examples are still provided for the Swiss Chablais subregion in Table \ref{table:params_GA_z4_hi2} for z4-hi2 and in Table \ref{table:params_GA_z4_hi4} for z4-hi4.
-The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_z4-hi2} for z4-hi2, along with the selected pressure levels for the circulation analogy (Table \ref{table:levels_GA_z4_hi2}) and the humidity analogy (Table \ref{table:levels_GA_z4_hi2_H}).
-Correspondingly, for the method z4-hi4, the spatial windows are shown in Figure \ref{fig:spatial_windows_z4-hi4} and the selected pressure levels are presented in Tables \ref{table:levels_GA_z4_hi4} and \ref{table:levels_GA_z4_hi4_H}.
-
-The CRPSS scores of the optimized methods are provided in Table \ref{table:scores} and amounts to slightly more than 40 \% for both methods and for both periods.
-This results in a relative improvements that ranges from 11.5 \% to 15.6 \% compared to the reference method on the humidity analogy (Table \ref{table:scores_diff}).
-As for z4, the z4-hi2 and z4-hi4 methods present improvements of the forecast of significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
-The improvement are relatively similar for z4-hi2 (Table \ref{table:scores_thresholds_z4-hi2}) and z4-hi4 (Table \ref{table:scores_thresholds_z4-hi4}), with slightly superior scores for the latter on small precipitation (P\(\geq\)1 mm) and extremes (P\(\geq\)0.5\(\cdot\)P10).
-
-The parameters cross-compatibility has also been assessed for the methods with humidity variables, and are shown in Tables \ref{table:crossing_z4-hi2_calib} and \ref{table:crossing_z4-hi2_valid} for the method z4-hi2, and Tables \ref{table:crossing_z4-hi4_calib} and \ref{table:crossing_z4-hi4_valid} for z4-hi4.
-
-\subsubsection{Analysis}
-
-When optimizing a method made of 2 levels of analogy, the introduction of humidity variables in the second level has an influence on the parameter values of the first level.
-This is first visible on the selection of the pressure levels for the circulation analogy, where the 1000~hPa that was previously systematically selected twice (Table \ref{table:levels_GA_z4}) is now less chosen (once or even not at all) for both za-hi2 (Table \ref{table:levels_GA_z4_hi2}) and za-hi4 (Table \ref{table:levels_GA_z4_hi4}).
-There is indeed a shift of the previously selected 1000~hPa for higher levels, which is even slightly stronger with 4 humidity predictors than with 2.
-This change is likely due to the fact that when considering only the circulation analogy, the method tries to take into account information that can serve as proxy for humidity assessment, whereas it doesn't need it with the humidity index.
-This aspect has never been demonstrated, as classic calibration tools do not allow it.
-It can only be assessed by a global optimization technique that can tune jointly both levels of analogy.
-
-The selected pressure levels for the analogy on the humidity index are strongly centred around 700~hPa and 600~hPa.
-No other value has been selected when considering 2 pressure levels (Table \ref{table:levels_GA_z4_hi2_H}), and when considering 4 levels, the 850~hPa and 500~hPa levels are additionally selected.
-However, even in this latter method, the 700~hPa and 600~hPa levels still hold 78 \% of the selection.
-It is thus more efficient, in terms of forecasting performance, to consider one of this level multiple times at different hours rather than using another pressure level.
-Besides, the optimizer never chose the same pressure level at the same hour for any variable, even though it was allowed to do so.
-
-The selection of the temporal windows for the atmospheric circulation is similar to the preceding optimization (in the order of increasing pressure: 12~h, 24/30~h, 12~h, 30~h), but sometimes with a bit more variability.
-When it comes to the humidity analogy, there is a clear trend to select 12~h and 24~h when considering 2 predictors.
-The z4-hi4 method presents more variability on the selection of the temporal windows for the humidity index.
-
-The optimized spatial windows for the atmospheric circulation have also changed (Figures \ref{fig:spatial_windows_z4-hi2} and \ref{fig:spatial_windows_z4-hi4}).
-The very large domains on the upper level of the 4 first subregions are not present anymore, and more variability can be observed.
-The selected points for the analogy on the humidity index are always located nearby the catchment, including at least 1 of the nearest points from the reanalysis dataset, and the spatial windows are relatively small.
-Thus, for our case study, there is no need to look for distant humidity information and the search could be reduced to a smaller domain.
-
-The CRPSS scores were improved by considering the humidity information (Table \ref{table:scores}).
-The optimized methods also perform better than the reference method based on the humidity index (Table \ref{table:scores_diff}).
-However, there is no drastic difference between both z4-hi2 and z4-hi4 methods, which suggests that considering 4 humidity predictors is not absolutely necessary.
-When it comes to improvements for days with precipitation above our 3 thresholds (P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the forecast, mainly for heavy rainfall.
-
-The analysis of the parameters cross-compatibility (Tables \ref{table:crossing_z4-hi2_calib} to \ref{table:crossing_z4-hi4_valid}) is also very similar to the one on the circulation analogy only.
-The same pattern can be observed, with a drop of performance for the subregions under different meteorological influences.
-However, the losses of performance are globally more important than before, suggesting that more complex methods with humidity variables are less transposable to another subregion, even though it is located within the same grid of the reanalysis dataset.
-
-\subsection{Discussion}
-
-The optimization of the analogue method by means of genetic algorithms has been undertaken in stages by releasing progressively new degrees of freedom.
-This approach allowed us to differentiate the contributions to performance gains, as well as to identify possible over-parametrization.
-The main improvements for our case study are due to the following factors:
-
-\begin{itemize}
-	\item Using 4 pressure levels for the analogy of circulation.
-It seems to be the optimal number for the studied region.
-Beyond that value the validation score drops, revealing a lost in robustness due to over-parametrization.
-	\item The automatic and joint optimization of all parameters: the analogues number, the selection of the pressure levels and the time windows, and the spatial windows.
-These parameters are highly interdependent, so we need to optimize them jointly in order to identify optimal combinations.
-Traditional calibration procedures based on a systematic assessment of every combination is no more possible when considering more than 2 pressure levels.
-	\item The introduction of distinct spatial windows between pressure levels.
-Indeed, the synoptic circulation is characterized by features with very different scales depending on the height, and important information for predicting rainfall is not necessarily located in the same area from one level to another.
-The optimized spatial windows are consistent in between the subregions.
-	\item The weighting of the analogy criteria between different pressure levels.
-It can be influenced by the variability of the geopotential with altitude, and the change of some levels significance with the targeted region.
-There is a trend for the weighting of circulation predictors to decrease with the increase in pressure, as one can see in Figure \ref{fig:levels_weights} for the method z4, and in Figure \ref{fig:levels_weights_average} for the averages over the 3 methods.
-However, the values stay around equity.
-This may not be the most influencing factor, and we may suggest to remove it first when trying to reduce the number of degrees of freedom.
-	\item The joint optimization of the circulation and humidity analogy levels, that are usually calibrated successively.
-We have been able to demonstrate that there is a dependency between the analogy levels, and that in order to approach the optimal parameters, we must consider them jointly.
-\end{itemize}
-
-GAs are very useful to optimize complex variants of the analogue method, and to assess new degrees of freedom that were not available so far.
-However, it can be dangerous to add too many parameters to optimize.
-Indeed, the optimizer will probably use them to successfully improve the calibration score, but the validation control remains very important in order to determine if we are actually improving the method, or if we are over-parametrizing it.
-
-The convergence of parallel optimizations decreases when the method to optimize becomes more and more complex.
-The optimizer do not always converge to the exact global optimum, but to its surroundings.
-This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that we have to stop it before the end, due to the required processing time (see Figure \ref{fig:evolution} as example).
-The resulting parameters may sometimes present significant differences, even though the score is almost similar.
-Through some Monte-Carlo analyses of the parameter space properties of the analogue method, \citet{Horton2012a} showed that some parameters of the method have a wide range of acceptable values.
-The spatial windows, for example, can be larger than the optimal size without much impact on the score, while they cannot be smaller \citep[see also][]{Bontron2004}.
-We could also observe that the selection of the pressure level is not a parameter as discrete as we would have thought, and that choosing another level may have reduced consequences on the performance.
-This is particularly true for higher pressure levels and can be more critical for lower layers.
-It was thus interesting to sometimes get several sets of near-optimal parameters, but with some nuances, in order to have an idea of the sensitivity of the parameters for a given region, and to compare the score on the validation period.
-In this regard, a cross-validation technique may be advisable.
-An approach that can also be recommended, and that we use, is to first explore a wide range of the parameter space with some optimizations, and to narrow it according to the results for more targeted optimizations that are likely to go faster and to perform better.
-
-We tried to optimize the preselection period (the 4-months window) jointly with the other parameters, but we did not get improvement.
-We also tried optimizing the humidity flux, which is composed of the humidity index multiplied with the wind flux.
-However, the results were not better than when we considered the humidity index alone.
-This may be related to the fact that the optimizer tries to provide the best analogy of the atmospheric circulation in the first place, which makes the wind information less relevant in the second level of analogy.
-
-As we could observe, methods with a higher complexity that integrate humidity predictors are less transposable than simpler ones.
-We also noticed in another unpublished work, that it is by far better to optimize for 2 subregions jointly rather than to optimize on one and to apply its parametrization to the other.
-Finally, the creation of the subregions is an important process and should be handled with care.
-Indeed, the geographical proximity is not always the leading factor to define a subregion.
-For example, the Southeast ridges subregion do not behave like its surrounding and differ in its parametrization, due to different leading meteorological influences.
-
-GAs are relatively heavy on processing and require an IT infrastructure capable of performing thousands hours of calculations.
-However, they automatically optimize all parameters of the analogue method, what the classic calibration does not allow.
-We therefore save much human time that was required to assess successively numerous combinations of parameters (particularly the selection of the pressure levels and the temporal windows).
-The ability to optimize jointly all parameters is important given the strong dependencies between them and between the levels of analogy.
-
-\section{Conclusions and perspectives}
-
-In order to automatically optimize the analogue method, we evaluated genetic algorithms, a global optimization technique, that is able to solve complex problems.
-Given the large number of existing operators and options, we had to evaluate systematically multiple variants to identify which operators are important, and which variant works best for the analogue method.
-We could thus identify that the mutation operator is a key element for our application, and provided new variants that were found to be efficient, such as the Chromosome of adaptive search radius that seems to be very reliable (no control parameter) and efficient .
-Recommendations were established for a relevant use of GAs for the optimization of the analogue method.
-However, there may still be possible improvements, through new operators, in order to improve the optimization performance and speed.
-
-The parameters resulting from the optimization are very consistent for the analogy of the atmospheric circulation, in terms of selection of the pressure levels, and the temporal and spatial windows.
-There are clear trends or even identical results for subregions under similar meteorological influences, which confirm that the optimized parameters are coherent, despite an eventual first impression of a great variability in the spatial windows.
-When adding humidity variables, the results show a higher variability, but remains highly acceptable and coherent.
-Indeed, the selection of the pressure level for the humidity index is for example very constant.
-
-We could observe strong dependencies between the parameters of the analogue method.
-Thus, the classic calibration, which optimizes the parameters successively, may not lead to the optimal combination.
-Moreover, it contains several manual systematic assessment, such as the selection of the pressure levels and the temporal windows.
-GAs, however, can select the pressure levels and the time windows automatically, which can save a considerable amount of human time.
-A great advantage of a global optimization is its ability to approach or reach optimal parameter values when they are considered jointly.
-
-We were able to identify that there is a parametric dependence between the analogy of circulation and the moisture humidity.
-When we consider the two levels together, the optimal parameters of the analogy of circulation are different.
-This complexity can only be exploited in a suitable manner by global optimization methods.
-
-For our case study, there seems to be an optimum number of pressure levels to consider for the analogy of circulation, which is four, before losing performance in validation.
-We have also been able to improve the analogy of circulation by introducing a weighting between pressure levels, and considering independent spatial windows between levels.
-
-GAs provide parametrizations of the analogue method that exceed the performance of the classic calibration.
-In addition, we could observe that the forecasts for days with strong precipitation were significantly more improved, which is clearly interesting in the framework of flood forecasting.
-
-This work is by far not exhaustive and means to open a door for new explorations with the analogues methods.
-It becomes possible to even let the optimizer chose the meteorological variable to be used as predictor, as well as the analogy criteria.
-It is already possible to undertake such data mining with our code.
-Moreover, the analogue method has been explored for decades for precipitation forecasting, but very few work analysis its potential for other predictands.
-A global optimizer, such as GAs, can speed up this assessment significantly.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% ACKNOWLEDGMENTS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-\acknowledgments
+\conclusions  %% \conclusions[modified heading if necessary]
+% TODO: write
+
+\appendix
+\section{}    %% Appendix A
+
+\subsection{}                               %% Appendix A1, A2, etc.
+
+\begin{acknowledgements}
 Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of.
@@
 Precipitation time series provided by MeteoSwiss.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% APPENDIXES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% Use \appendix if there is only one appendix.
-%\appendix
-
-% Use \appendix[A], \appendix}[B], if you have multiple appendixes.
-%\appendix[A]
-
-%% Appendix title is necessary! For appendix title:
-%\appendixtitle{}
-
-%%% Appendix section numbering (note, skip \section and begin with \subsection)
-% \subsection{First primary heading}
-
-% \subsubsection{First secondary heading}
-
-% \paragraph{First tertiary heading}
-
-%% Important!
-%\appendcaption{<appendix letter and number>}{<caption>} 
-%must be used for figures and tables in appendixes, e.g.,
-%
-%\begin{figure}
-%\noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
-%\appendcaption{A1}{Caption here.}
+\end{acknowledgements}
+
+%% REFERENCES
+
+%% The reference list is compiled as follows:
+
+%\begin{thebibliography}{}
+%
+%\bibitem[AUTHOR(YEAR)]{LABEL}
+%REFERENCE 1
+%
+%\bibitem[AUTHOR(YEAR)]{LABEL}
+%REFERENCE 2
+%
+%\end{thebibliography}
+
+\bibliographystyle{copernicus}
+\bibliography{../_refs/_articles-atmoswing}
+
+%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
+%% authors experienced with BibTeX only have to include the following two lines:
+%%
+%% \bibliographystyle{copernicus}
+%% \bibliography{example.bib}
+%%
+%% URLs and DOIs can be entered in your BibTeX file as:
+%%
+%% URL = {http://www.xyz.org/~jones/idx_g.htm}
+%% DOI = {10.5194/xyz}
+
+%% LITERATURE CITATIONS
+%%
+%% command                        & example result
+%% \citet{jones90}|               & Jones et al. (1990)
+%% \citep{jones90}|               & (Jones et al., 1990)
+%% \citep{jones90,jones93}|       & (Jones et al., 1990, 1993)
+%% \citep[p.~32]{jones90}|        & (Jones et al., 1990, p.~32)
+%% \citep[e.g.,][]{jones90}|      & (e.g., Jones et al., 1990)
+%% \citep[e.g.,][p.~32]{jones90}| & (e.g., Jones et al., 1990, p.~32)
+%% \citeauthor{jones90}|          & Jones et al.
+%% \citeyear{jones90}|            & 1990
+
+%% FIGURES
+
+%% ONE-COLUMN FIGURES
+
+%%f
+%\begin{figure}[t]
+%\includegraphics[width=8.3cm]{FILE NAME}
+%\caption{TEXT}
 %\end{figure}
 %
-% All appendix figures/tables should be placed in order AFTER the main figures/tables, i.e., tables, appendix tables, figures, appendix figures.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% REFERENCES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Make your BibTeX bibliography by using these commands:
-% \bibliographystyle{ametsoc2014}
-% \bibliography{references}
-
-\bibliographystyle{ametsoc2014_no_url}
-% \bibliography{references}
-\bibliography{../_refs/_articles-optimization}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% TABLES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Enter tables at the end of the document, before figures.
-%%
-%
+%%% TWO-COLUMN FIGURES
+%
+%%f
+%\begin{figure*}[t]
+%\includegraphics[width=12cm]{FILE NAME}
+%\caption{TEXT}
+%\end{figure*}
+%
+%
+%%% TABLES
+%%%
+%%% The different columns must be seperated with a & command and should
+%%% end with \\ to identify the column brake.
+%
+%%% ONE-COLUMN TABLE
+%
+%%t
 %\begin{table}[t]
-%\caption{This is a sample table caption and table layout.  Enter as many tables as
-%  necessary at the end of your manuscript. Table from Lorenz (1963).}\label{t1}
-%\begin{center}
-%\begin{tabular}{ccccrrcrc}
-%\hline\hline
-%$N$ & $X$ & $Y$ & $Z$\\
-%\hline
-% 0000 & 0000 & 0010 & 0000 \\
-% 0005 & 0004 & 0012 & 0000 \\
-% 0010 & 0009 & 0020 & 0000 \\
-% 0015 & 0016 & 0036 & 0002 \\
-% 0020 & 0030 & 0066 & 0007 \\
-% 0025 & 0054 & 0115 & 0024 \\
-%\hline
+%\caption{TEXT}
+%\begin{tabular}{column = lcr}
+%\tophline
+%
+%\middlehline
+%
+%\bottomhline
 %\end{tabular}
-%\end{center}
+%\belowtable{} % Table Footnotes
 %\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Parameters of the reference method on the atmospheric circulation.}
-	\begin{center}
-		\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-			\hline 
-			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{2}{*}{1} & Z 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
-			& Z 500~hPa & 24~h & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_R1}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Parameters of the reference method with humidity variables.}
-	\begin{center}
-		\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-			\hline 
-			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{2}{*}{1} & Z 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
-			& Z 500~hPa & 24~h & & \\ 
-			\hline
-			\multirow{2}{*}{2} & TPW * RH 850~hPa & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{30} \\
-			& TPW * RH 850~hPa & 24~h & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_R2}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Parameters of the z4 method (analogy on 4 levels of the atmospheric circulation) optimized for the Chablais subregion.
-The columns are the following: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
-			\hline 
-			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & -2.5 - 15.0 \degree E & \multirow{2}{*}{32\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{28} \\
-			& & & 37.5 - 57.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z700} & \multirow{2}{*}{24~h} & 2.5 - 10.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
-			& & & 42.5 - 45.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{6~h} & -5.0 - 15.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
-			& & & 42.5 - 47.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
-			& & & 40.0 - 50.0 \degree N & & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_GA_z4}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Atmospheric levels automatically selected for the z4 method at the different subregions.}
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
-			\hline 
-			1  & Z &   &   &   & Z &   &   & ZZ \\
-			2  & Z &   &   &   & Z &   &   & ZZ \\
-			3  & Z &   &   &   & Z &   &   & ZZ \\
-			4  & Z &   &   &   & Z &   &   & ZZ \\
-			5  &   &   & Z &   & Z &   &   & ZZ \\
-			6  &   &   & Z &   & Z &   &   & ZZ \\
-			7  &   &   & Z &   & Z &   &   & ZZ \\
-			8  &   &   & Z &   & Z &   &   & ZZ \\
-			9  &   &   & Z &   & Z &   &   & ZZ \\
-			10 &   &   &   & Z & Z &   &   & ZZ \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_z4}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{CRPSS score (\%) of the three optimized methods.}
-	\begin{center}
-		\begin{tabular}{rrarara}
-			\hline 
-			\textbf{ID} & \multicolumn{2}{c}{\textbf{z4}} & \multicolumn{2}{c}{\textbf{z4-hi2}} & \multicolumn{2}{c}{\textbf{z4-hi4}} \\ 
-			\hline 
-			& calib & valid & calib & valid & calib & valid \\ 
-			\hline 
-			\textbf{1} & 40.3 & 38.5 & 45.5 & 43.8 & 45.9 & 43.6 \\ \hline
-			\textbf{2} & 37.8 & 34.9 & 42.4 & 40.8 & 42.9 & 41.3 \\ \hline
-			\textbf{3} & 36.6 & 33.9 & 41.4 & 39.0 & 41.8 & 39.5 \\ \hline
-			\textbf{4} & 31.2 & 30.8 & 36.1 & 36.4 & 36.8 & 37.1 \\ \hline
-			\textbf{5} & 34.4 & 36.5 & 38.6 & 41.4 & 39.2 & 41.8 \\ \hline
-			\textbf{6} & 37.0 & 39.9 & 41.0 & 44.5 & 41.9 & 44.6 \\ \hline
-			\textbf{7} & 30.0 & 30.1 & 33.8 & 34.6 & 34.4 & 34.8 \\ \hline
-			\textbf{8} & 37.7 & 40.1 & 40.7 & 43.1 & 41.2 & 43.3 \\ \hline
-			\textbf{9} & 33.1 & 30.0 & 38.4 & 36.6 & 38.7 & 36.3 \\ \hline
-			\textbf{10} & 40.0 & 40.0 & 42.6 & 42.9 & 43.3 & 43.2 \\ \hline
-			\textbf{av.} & \textbf{35.8} & \textbf{35.5} &\textbf{40.1} & \textbf{40.3} & \textbf{40.6} & \textbf{40.5} \\ \hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Improvement (\%) of the CRPSS of the three methods.
-For z4, the improvement is relative to the reference method on the atmospheric circulation.
-For z4-hi2 and z4-hi4, the improvement is relative to the reference method on the circulation and humidity variables.}
-	\begin{center}
-		\begin{tabular}{rrarara}
-			\hline 
-			\textbf{ID} & \multicolumn{2}{c}{\textbf{z4}} & \multicolumn{2}{c}{\textbf{z4-hi2}} & \multicolumn{2}{c}{\textbf{z4-hi4}} \\ 
-			\hline 
-			& calib & valid & calib & valid & calib & valid \\ 
-			\hline 
-			\textbf{1} & 13.6 & 13.0 & 11.9 & 9.9 & 12.8 & 9.6 \\ \hline
-			\textbf{2} & 13.3 & 7.5 & 11.2 & 9.4 & 12.5 & 10.8 \\ \hline
-			\textbf{3} & 12.2 & 9.0 & 13.2 & 12.0 & 14.1 & 13.5 \\ \hline
-			\textbf{4} & 14.2 & 10.5 & 12.4 & 10.6 & 14.5 & 12.5 \\ \hline
-			\textbf{5} & 14.5 & 8.8 & 12.5 & 9.1 & 14.1 & 10.0 \\ \hline
-			\textbf{6} & 13.3 & 8.6 & 11.5 & 8.2 & 14.1 & 8.4 \\ \hline
-			\textbf{7} & 22.8 & 10.6 & 19.7 & 15.7 & 21.7 & 16.3 \\ \hline
-			\textbf{8} & 20.7 & 11.9 & 19.2 & 13.5 & 20.8 & 14.0 \\ \hline
-			\textbf{9} & 14.4 & 9.5 & 15.8 & 15.2 & 16.7 & 14.1 \\ \hline
-			\textbf{10} & 14.2 & 9.4 & 12.9 & 11.2 & 14.6 & 11.8 \\ \hline
-			\textbf{av.} & \textbf{15.3} & \textbf{9.9} &\textbf{14.0} & \textbf{11.5} & \textbf{15.6} & \textbf{12.1} \\ \hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores_diff}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4 method.}
-	\begin{center}
-		\begin{tabular}{rrarara}
-			\hline 
-			\textbf{ID} & \multicolumn{2}{c}{\textbf{P\(\geq\)1 mm}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.1\(\cdot\)P10}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.5\(\cdot\)P10}} \\ 
-			\hline 
-			& calib & valid & calib & valid & calib & valid \\ 
-			\hline 
-			\textbf{1} & 10.2 & 9.4 & 8.5 & 7.9 & 17.0 & 14.2 \\ \hline 
-			\textbf{2} & 9.9 & 3.4 & 10.2 & 7.3 & 19.3 & 13.7 \\ \hline 
-			\textbf{3} & 13.3 & 10.5 & 13.3 & 10.9 & 19.7 & 9.7 \\ \hline 
-			\textbf{4} & 11.0 & 7.4 & 12.9 & 10.0 & 23.2 & 23.8 \\ \hline 
-			\textbf{5} & 8.6 & 4.2 & 10.9 & 6.2 & 25.2 & 23.8 \\ \hline 
-			\textbf{6} & 10.5 & 5.1 & 11.1 & 7.1 & 21.2 & 41.1 \\ \hline 
-			\textbf{7} & 24.3 & 12.4 & 33.1 & 26.0 & 71.2 & 104.3 \\ \hline 
-			\textbf{8} & 19.0 & 12.7 & 26.2 & 19.2 & 39.4 & 34.9 \\ \hline 
-			\textbf{9} & 12.4 & 6.8 & 13.8 & 9.9 & 24.9 & 48.1 \\ \hline 
-			\textbf{10} & 13.6 & 6.8 & 14.4 & 6.9 & 29.9 & 31.5 \\ \hline 
-			\textbf{av.} &\textbf{ 13.3} & \textbf{7.9} & \textbf{15.4} & \textbf{11.1} & \textbf{29.1} & \textbf{34.5} \\ \hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores_thresholds_z4}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4, calibration period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4_calib.pdf}}
-	\label{table:crossing_z4_calib}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4, validation period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4_valid.pdf}}
-	\label{table:crossing_z4_valid}
-\end{table}
-
-\clearpage
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Parameters of the z4-hi2 method (atmospheric circulation on 4 levels and humidity index on 2 levels), optimized for the Chablais subregion.
-Same conventions as Table \ref{table:params_GA_z4}.}
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
-			\hline 
-			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & 0.0 - 15.0 \degree E & \multirow{2}{*}{23\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
-			& & & 42.5 - 55.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{25\%} & & \\ 
-			& & & 40.0 - 45.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
-			& & & 42.5 - 47.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
-			& & & 40.0 - 47.5 \degree N & & & \\ 
-			\hline 
-			\multirow{4}{*}{2} & TPW & \multirow{2}{*}{12~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{57\%} & \multirow{4}{*}{RMSE} & \multirow{4}{*}{25} \\
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{24~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{43\%} & & \\ 
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_GA_z4_hi2}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Parameters of the z4-hi4 method (atmospheric circulation on 4 levels and humidity index on 4 levels), optimized for the Chablais subregion.
-Same conventions as Table \ref{table:params_GA_z4}.}
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
-			\hline 
-			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{8}{*}{1} &  \multirow{2}{*}{Z400} & \multirow{2}{*}{6~h} & -5.0 - 12.5 \degree E & \multirow{2}{*}{20\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
-			& & & 45.0 - 52.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
-			& & & 40.0 - 45.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
-			& & & 42.5 - 47.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
-			& & & 40.0 - 47.5 \degree N & & & \\ 
-			\hline 
-			\multirow{8}{*}{2} & TPW & \multirow{2}{*}{24~h} & 7.5 - 10.0 \degree E & \multirow{2}{*}{27\%} & \multirow{8}{*}{RMSE} & \multirow{8}{*}{25} \\
-			& *RH500 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{12~h} & 5.0 - 7.5 \degree E & \multirow{2}{*}{41\%} & & \\ 
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{18~h} & 0.0 - 7.5 \degree E & \multirow{2}{*}{19\%} & & \\ 
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{24~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{13\%} & & \\ 
-			& *RH850 & & 45.0 - 47.5 \degree N & & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_GA_z4_hi4}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation of the z4-hi2 method, at the different subregions.}
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
-			\hline 
-			1  & Z &   & Z &   &   & Z &   & Z \\
-			2  & Z &   &   &   & Z & Z &   & Z \\
-			3  & Z &   &   &   & Z & Z & Z &   \\
-			4  &   &   & Z &   & Z & Z &   & Z \\
-			5  &   & Z &   &   & Z &   & ZZ &   \\
-			6  &   & Z &   &   & Z & Z &   & Z \\
-			7  &   & Z &   &   & Z & Z &   & Z \\
-			8  &   &   & Z &   & Z &   & ZZ &   \\
-			9  &   & Z &   &   & Z & Z & Z &   \\
-			10 &   & Z &   &   & Z & Z &   & Z \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_z4_hi2}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of humidity of the z4-hi2 method, at the different subregions.}
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
-			\hline 
-			1  &   &   &   &   & HH &   &   &   \\
-			2  &   &   &   &   & HH &   &   &   \\
-			3  &   &   &   &   & HH &   &   &   \\
-			4  &   &   &   & H & H &   &   &   \\
-			5  &   &   &   &   & HH &   &   &   \\
-			6  &   &   &   & H & H &   &   &   \\
-			7  &   &   &   & H & H &   &   &   \\
-			8  &   &   &   & H & H &   &   &   \\
-			9  &   &   &   & H & H &   &   &   \\
-			10 &   &   &   & H & H &   &   &   \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_z4_hi2_H}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation of the z4-hi4 method, at the different subregions.}
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
-			\hline 
-			1  &   & Z & Z &   &   & Z &   & Z \\
-			2  &   & Z &   &   & ZZ &   &   & Z \\
-			3  &   & Z &   &   & Z & Z & Z &   \\
-			4  &   &   & Z &   & Z & Z &   & Z \\
-			5  &   & Z & Z &   &   & Z &   & Z \\
-			6  &   & Z & Z &   &   & Z &   & Z \\
-			7  &   & Z &   &   & ZZ &   &   & Z \\
-			8  &   &   & Z & Z &   & Z &   & Z \\
-			9  &   & Z &   &   & Z & Z & Z &   \\
-			10 &   & Z & Z &   &   & ZZ &   &   \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_z4_hi4}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of humidity of the z4-hi4 method,at the different subregions.}
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
-			\hline 
-			1  &   &   & H &   & HH & H &   &   \\
-			2  &   &   &   & H & HH & H &   &   \\
-			3  &   &   &   & H & HHH &   &   &   \\
-			4  &   &   &   & HH & HH &   &   &   \\
-			5  &   &   &   & HH & HH &   &   &   \\
-			6  &   &   &   & HH & H & H &   &   \\
-			7  &   &   &   & HH & H & H &   &   \\
-			8  &   &   &   & HH & H & H &   &   \\
-			9  &   &   & H & H & H & H &   &   \\
-			10 &   &   &   & H & HH & H &   &   \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_z4_hi4_H}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi2 method.}
-	\begin{center}
-		\begin{tabular}{rrarara}
-			\hline 
-			\textbf{ID} & \multicolumn{2}{c}{\textbf{P\(\geq\)1 mm}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.1\(\cdot\)P10}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.5\(\cdot\)P10}} \\ 
-			\hline 
-			& calib & valid & calib & valid & calib & valid \\ 
-			\hline 
-			\textbf{1} & 12.6 & 9.3 & 12.4 & 9.7 & 15.8 & 11.0 \\ \hline 
-			\textbf{2} & 10.4 & 7.7 & 11.2 & 10.5 & 18.9 & 16.6 \\ \hline 
-			\textbf{3} & 14.5 & 11.6 & 14.1 & 11.4 & 18.7 & 14.6 \\ \hline 
-			\textbf{4} & 11.4 & 9.4 & 11.5 & 11.6 & 14.9 & 22.7 \\ \hline 
-			\textbf{5} & 11.8 & 8.0 & 12.2 & 8.9 & 12.0 & 12.8 \\ \hline 
-			\textbf{6} & 11.3 & 7.1 & 11.2 & 8.0 & 15.3 & 29.1 \\ \hline 
-			\textbf{7} & 20.5 & 15.5 & 25.2 & 24.0 & 43.0 & 79.5 \\ \hline
-			\textbf{8} & 19.3 & 15.7 & 23.1 & 18.6 & 25.2 & 31.7 \\ \hline 
-			\textbf{9} & 17.0 & 15.4 & 17.4 & 16.5 & 23.7 & 39.4 \\ \hline 
-			\textbf{10} & 12.9 & 9.6 & 13.8 & 11.1 & 28.5 & 32.1 \\ \hline 
-			\textbf{av.} &\textbf{14.2} & \textbf{10.9} & \textbf{15.2} & \textbf{13.0} & \textbf{21.6} & \textbf{28.9} \\ \hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores_thresholds_z4-hi2}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi4 method.}
-	\begin{center}
-		\begin{tabular}{rrarara}
-			\hline 
-			\textbf{ID} & \multicolumn{2}{c}{\textbf{P\(\geq\)1 mm}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.1\(\cdot\)P10}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.5\(\cdot\)P10}} \\ 
-			\hline 
-			& calib & valid & calib & valid & calib & valid \\ 
-			\hline 
-			\textbf{1} & 21.2 & 17.9 & 13.4 & 9.3 & 17.8 & 13.3 \\ \hline 
-			\textbf{2} & 12.6 & 8.9 & 9.5 & 10.0 & 16.7 & 15.6 \\ \hline 
-			\textbf{3} & 17.0 & 16.1 & 14.0 & 12.4 & 21.3 & 15.9 \\ \hline 
-			\textbf{4} & 9.4 & 6.1 & 13.3 & 12.4 & 19.8 & 22.7 \\ \hline 
-			\textbf{5} & 16.4 & 8.7 & 13.3 & 9.9 & 15.5 & 19.8 \\ \hline 
-			\textbf{6} & 22.6 & 12.2 & 11.9 & 6.7 & 17.0 & 26.9 \\ \hline 
-			\textbf{7} & 14.6 & 4.9 & 24.7 & 23.5 & 42.7 & 87.6 \\ \hline 
-			\textbf{8} & 21.8 & 21.6 & 25.7 & 19.3 & 32.3 & 26.6 \\ \hline 
-			\textbf{9} & 20.2 & 18.9 & 17.4 & 14.2 & 24.5 & 33.9 \\ \hline 
-			\textbf{10} & 21.7 & 14.8 & 14.8 & 11.7 & 29.2 & 29.1 \\ \hline 
-			\textbf{av.} &\textbf{17.7} & \textbf{13.0} & \textbf{15.8} & \textbf{12.9} & \textbf{23.7} & \textbf{29.2} \\ \hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores_thresholds_z4-hi4}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, calibration period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_calib.pdf}}
-	\label{table:crossing_z4-hi2_calib}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, validation period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_valid.pdf}}
-	\label{table:crossing_z4-hi2_valid}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi4, calibration period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_calib.pdf}}
-	\label{table:crossing_z4-hi4_calib}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi4, validation period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_valid.pdf}}
-	\label{table:crossing_z4-hi4_valid}
-\end{table}
-
-\clearpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% FIGURES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Enter figures at the end of the document, after tables.
-%%
-%
-%\begin{figure}[t]
-%  \noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
-%  \caption{Enter the caption for your figure here.  Repeat as
-%  necessary for each of your figures. Figure from \protect\cite{Knutti2008}.}\label{f1}
-%\end{figure}
-
-\begin{figure}[htb]
-	\centerline{\includegraphics[width=7.9cm]{figures/figure_structure_gas.pdf}}
-	\caption{Genetic algorithms operational flowchart}
-	\label{fig:structure_gas}
-\end{figure}
-
-\begin{figure}[htb]
-	\centerline{\includegraphics[width=7.9cm]{figures/figure_map.pdf}}
-	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland. (source: Swisstopo)}
-	\label{fig:map}
-\end{figure}
-
-\begin{figure}[htb]
-	\centering
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_1.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_2.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_3.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_4.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_5.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_6.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_7.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_8.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_9.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_10.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/legend.png}
-	\end{subfigure}
-	\caption{Optimized spatial windows for the z4 method (analogy of atmospheric circulation on 4 pressure levels).
-The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
-	\label{fig:spatial_windows_z4}
-\end{figure}
-
-\begin{figure}[htb]
-	\centering
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_1.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_2.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_3.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_4.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_5.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_6.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_7.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_8.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_9.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_10.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/legend.png}
-	\end{subfigure}
-	\caption{Optimized spatial windows for the z4-hi2 method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the humidity index on 2 pressure levels).
-The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
-	\label{fig:spatial_windows_z4-hi2}
-\end{figure}
-
-\begin{figure}[htb]
-	\centering
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_1.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_2.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_3.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_4.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_5.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_6.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_7.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_8.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_9.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_10.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/legend.png}
-	\end{subfigure}
-	\caption{Optimized spatial windows for the z4-hi4 method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the humidity index on 4 pressure levels).
-The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
-	\label{fig:spatial_windows_z4-hi4}
-\end{figure}
-
-\begin{figure}[htb]
-	\centerline{\includegraphics[width=7.9cm]{figures/figure_levels_weights.pdf}}
-	\caption{Optimized weighting for the pressure levels of the z4 method.}
-	\label{fig:levels_weights}
-\end{figure}
-
-\begin{figure}[htb]
-	\centerline{\includegraphics[width=7.9cm]{figures/figure_levels_weights_average.pdf}}
-	\caption{Averaged weighting for the pressure levels of the circulation analogy of the three methods.}
-	\label{fig:levels_weights_average}
-\end{figure}
-
-\begin{figure}[htb]
-	\centerline{\includegraphics[width=7.9cm]{figures/figure_evolution.pdf}}
-	\caption{Example of the best individuals evolution of 8 independent optimizations.}
-	\label{fig:evolution}
-\end{figure}
+%
+%%% TWO-COLUMN TABLE
+%
+%%t
+%\begin{table*}[t]
+%\caption{TEXT}
+%\begin{tabular}{column = lcr}
+%\tophline
+%
+%\middlehline
+%
+%\bottomhline
+%\end{tabular}
+%\belowtable{} % Table Footnotes
+%\end{table*}
+%
+%
+%%% NUMBERING OF FIGURES AND TABLES
+%%%
+%%% If figures and tables must be numbered 1a, 1b, etc. the following command
+%%% should be inserted before the begin{} command.
+%
+%\addtocounter{figure}{-1}\renewcommand{\thefigure}{\arabic{figure}a}
+%
+%
+%%% MATHEMATICAL EXPRESSIONS
+%
+%%% All papers typeset by Copernicus Publications follow the math typesetting regulations
+%%% given by the IUPAC Green Book (IUPAC: Quantities, Units and Symbols in Physical Chemistry,
+%%% 2nd Edn., Blackwell Science, available at: http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf, 1993).
+%%%
+%%% Physical quantities/variables are typeset in italic font (t for time, T for Temperature)
+%%% Indices which are not defined are typeset in italic font (x, y, z, a, b, c)
+%%% Items/objects which are defined are typeset in roman font (Car A, Car B)
+%%% Descriptions/specifications which are defined by itself are typeset in roman font (abs, rel, ref, tot, net, ice)
+%%% Abbreviations from 2 letters are typeset in roman font (RH, LAI)
+%%% Vectors are identified in bold italic font using \vec{x}
+%%% Matrices are identified in bold roman font
+%%% Multiplication signs are typeset using the LaTeX commands \times (for vector products, grids, and exponential notations) or \cdot
+%%% The character * should not be applied as mutliplication sign
+%
+%
+%%% EQUATIONS
+%
+%%% Single-row equation
+%
+%\begin{equation}
+%
+%\end{equation}
+%
+%%% Multiline equation
+%
+%\begin{align}
+%& 3 + 5 = 8\\
+%& 3 + 5 = 8\\
+%& 3 + 5 = 8
+%\end{align}
+%
+%
+%%% MATRICES
+%
+%\begin{matrix}
+%x & y & z\\
+%x & y & z\\
+%x & y & z\\
+%\end{matrix}
+%
+%
+%%% ALGORITHM
+%
+%\begin{algorithm}
+%\caption{…}
+%\label{a1}
+%\begin{algorithmic}
+%…
+%\end{algorithmic}
+%\end{algorithm}
+%
+%
+%%% CHEMICAL FORMULAS AND REACTIONS
+%
+%%% For formulas embedded in the text, please use \chem{}
+%
+%%% The reaction environment creates labels including the letter R, i.e. (R1), (R2), etc.
+%
+%\begin{reaction}
+%%% \rightarrow should be used for normal (one-way) chemical reactions
+%%% \rightleftharpoons should be used for equilibria
+%%% \leftrightarrow should be used for resonance structures
+%\end{reaction}
+%
+%
+%%% PHYSICAL UNITS
+%%%
+%%% Please use \unit{} and apply the exponential notation
 

### 2015-10-13 Optimization - Journal of Climate/template.tex
Moving content from the optimization paper to the AtmoSwing one.

@@
 
-\subsection{The analogue method}
+The analogue method has to be adapted to every new location it is applied.
+We improved the analogue method for the Swiss Alps, by means of genetic algorithms.
+A summary of the main results are provided here \citep[see][for the details]{Horton2012a}.
+Even though the results may differ from one place to another, the applicability of GAs to the analogue method remains universal.
+
+\section{The analogue method}
 \label{section_analog_method}
@@
 
-\subsection{Calibration framework}
-
-The calibration of the analogue method is usually carried out in a perfect prognosis \citep{Klein1959} framework \citep{BenDaoud2010, Bontron2004}.
-Perfect prognosis uses observed or reanalyzed data to calibrate the relationship between predictors and predictands.
-Then, when used in operational forecasting, this relationship is applied to global model forecasts, that contains larger uncertainties.
-This framework allow us to identify relationships that are as close as possible to the natural links between predictors and predictands, by reducing uncertainties related to numerical forecasting models.
-However, no model is perfect, and even reanalysis data contain a bias that cannot be ignored.
-For this reason, the statistical relationships identified in the perfect prognosis framework should be applied to model outputs that are as similar as possible to the model used to elaborate the reanalysis.
-
-Another reason for working in a perfect prognosis framework is that numerical models evolve continuously, and so does the forecast they provide.
-Re-forecasts would allow us to work on a homogeneous dataset, as they are regularly reprocessed.
-However, we would need to redo the calibration procedure every time a new version is available, in order to reduce the bias \citep{Wilson2002}.
-Moreover, the reforecasts are not re-processed for every new version of the model, meaning we still end up with a bias between the forecast and the archive.
-Finally, the length of reanalyses datasets are usually much longer than reforecast datasets, which allows us to identify more robust relationships.
-The size of the archive is indeed an important criteria for the analogue method.
-
-The statistical relationship is established on a calibration period that is as long as possible.
-For every day of this period, a search for analogues is processed, the precipitation data are associated with the corresponding dates and a forecast score is calculated.
-During the search for analogues situations, 120 days around the target date are excluded (thus excluding data in the same year) in order to consider only truly independent candidates days.
-
-A validation period is always considered.
-It consists of an independent period that is never used as target neither candidate date.
-Validating the parameters of the analogue method is very important in order to avoid over-parametrization and thus to ensure that the statistical relationship is valid on another period.
-
-The accuracy of the parameters is evaluated by means of the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
-It allows assessing the predicted cumulative distribution functions $F(y)$ compared to the observed value $y^{0}$.
-The better the forecast, the smaller the score.
-The mean CRPS of a forecast series of length $n$ can be written:
-
-\begin{equation}
-\label{eq:CRPS}
-CRPS = \frac{1}{n} \sum_{i=1}^{n} \left(  \int_{-\infty}^{+\infty} \left[ F_{i}(y)-H_{i}(y-y_{i}^{0})\right]^{2} dy \right) 
-\end{equation}
-where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value 1 otherwise.
-The mean CRPS is averaged on the calibration, respectively the validation periods, on all days, may they be dry, slightly rainy or with heavy precipitation.
-
-This score is now commonly used for the evaluation of continuous variables prediction systems \citep{Casati2008, Marty2010}.
-To compare the value of the score in regard to a reference, we often consider its skill score value, and use the climatological distribution as the reference.
-The CRPSS (\textit{Continuous Ranked Probability Skill Score}) is thus defined as following:
-
-\begin{equation}
-\label{eq:CRPSS}
-CRPSS = \dfrac{CRPS-CRPS_{r}}{CRPS_{p}-CRPS_{r}} = 1-\dfrac{CRPS}{CRPS_{r}}
-\end{equation}
-where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect forecast ($CRPS_{p} = 0$).
-
-\subsection{The classic calibration approach}
-
-The calibration procedure that we call ''classic'' was developed by \citet{Bontron2004} at the LTHE laboratory (INPG, Grenoble).
-It determines the optimal parameters for the different variables of each level of analogy.
-The analogy levels (eg the atmospheric circulation or humidity index) are calibrated sequentially.
-The procedure consists of the following steps \citep{Bontron2004}:
-
-\begin{enumerate}
-	\item Manual selection of the following parameters:
-	\begin{enumerate}
-		\item meteorological variable,
-		\item pressure level,
-		\item temporal window (hour of observation),
-		\item initial analogue numbers.
-	\end{enumerate}
-
-	\item For every level of analogy:
-	\begin{enumerate}
-		\item Identification of the most skilled unitary cell (1 point for humidity variables and 4 for the geopotential height when using the S1 criteria) over a large domain.
-Every point (or cell) of the full domain is assessed jointly on all predictors of the level of analogy (consisting generally of the same variable, but on different pressure levels and at different hours).
-		\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain.
-The detailed stages are the followings: (i) The unitary spatial window is expanded in every 4 directions successively.
-The performance score is processed for these 4 windows.
-(ii) Only the direction providing the best improvement is applied to our spatial window.
-(iii) From this new spatial window, an increase in every 4 directions is once again assessed, and the best improvement is applied.
-(iv) The spatial window grows up by repeating the previous steps, until no improvement is reached.
-		\item The number of analogues is optimized for the current level of analogy.
-		\item A new level of analogy can be added, based on other variables (such as the humidity index) on predefined pressure levels and time frames.
-The number of analogues for the next level of analogy is initiated at a chosen value.
-Then, the procedure starts again from step (a) for the new level.
-The parameters calibrated on the previous analogue levels are fixed and do not change (except the number of analogues, at the final stage).
-	\end{enumerate}
-	\item Finally, the numbers of analogues are re-assessed for the different levels of analogy. This is done iteratively by varying the number of analogues of each level in a systematic way.
-\end{enumerate}
-
-The calibration is thus done in successive steps.
-Previously calibrated parameters are generally not reassessed.
-The advantage of this method is that it is fast, it provides acceptable results, and it has low computing requirements.
-We added small improvements to this method by allowing the spatial windows to do other moves, such as: (1) increase in 2 simultaneous directions, (2) decrease in 1 or 2 simultaneous directions, (3) expansion or contraction (in every direction), (4) shift of the window (without resizing) in 8 directions (including diagonals), and finally (5) all the moves described above, but with a factor of 2, 3, or more.
-For example, we try to increase by 2 units in one (or more) direction.
-This allows to skip one size that may not be optimal.
-
-These supplementary steps often result in spatial windows that are a bit different, but the performance gain is rather marginal.
-These methods are available in the open source software AtmoSwing (Analogue Technique MOdel for Statistical Weather forecastING, www.atmoswing.org).
-
-\subsection{Motivation for a global optimization}
+\section{Motivation for a global optimization}
 
@@
 
-\section{Adjusting genetic algorithms}
-
-Genetic algorithms (GAs) come from the world of stochastic optimization, more specifically from metaheuristic approaches.
-These are stochastic iterative algorithms that behave like search algorithms by exploiting the characteristics of a problem and are particularly suitable for complex parameter spaces.
-
-Genetic algorithms are part of the family of evolutionary algorithms \citep{Back1993b, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
-GAs are the most used technique from evolutionary algorithms \citep{Back1993b}, and they are constantly improving \citep{Haupt2004}.
-However, with time, the different methods of evolutionary algorithms tend to be similar and share many commonalities \citep{Back1996b, Haupt2004}.
-
-The method was originally developed by \citet{Holland1992b} and popularized by \citet{Goldberg1989}.
-Unlike a linear or local optimization, GAs seek the global optimum on a complex surface, theoretically without restriction, but with no guarantee to reach it.
-
-\subsection{Basic concepts of the genetic algorithms}
-
-GAs mimic the evolution of a population of individuals in a new environment, by applying rules based on natural processes, such as DNA mutation, chromosomes crossover, natural selection, etc.
-It simulates the fact that in a natural environment, the most suitable individuals tend to survive longer, to reproduce more easily, and so to influence coming generations by providing genes that provide some good performance in a certain domain.
-Generation after generation, the DNA mixes and the strong genes cumulate in some individuals \citep{Beasley1996a}.
-Globally, the fitness of the population to its environment increases, while retaining enough variety to not converge too quickly to a local optimum.
-
-Applications of GAs are very diversified as they can handle many parameters of various types \citep{Joines1996a}, even with very complex cost surfaces \citep{Haupt2004}.
-GAs work remarkably well with intervariable dependences \citep{Haupt2004}.
-The objective function to optimize (often named fitness function in this context) can be of different types (mathematical function, experimental or numerical modeling).
-Only the resulting value is used for optimization.
-Indeed, these algorithms do not require any knowledge of the problem, which can be used as black-box, but they must be adapted in order to perform optimally.
-
-By means of the reproduction operator and the natural selection, the GAs focus on the most promising regions of the parameter space \citep{Holland1992b}.
-Points (parameter sets) are densified in these areas because the strong genes of the best individuals propagate from generation to generation.
-
-Two conditions guarantee in theory the convergence to the global optimum \citep{Zitzler2004a}: (1) Parameters mutations that can allow to explore the entire parameter space, thereby ensures that any value can be achieved with a non-zero probability.
-(2) A rule of elitism ensuring that an optimal solution cannot be lost or damaged.
-
-Practically, GAs allow rapidly approaching satisfactory solutions, but they do not provide the optimum solution for sure \citep{Zitzler2004a}.
-It is indeed mainly a matter of time.
-When the optimizer gets closer to the global optimum, any new improvement takes more time to appear (see figure \ref{fig:evolution}), and the final adjustment of the parameters is very time consuming \citep{Back1993a}.
-For problems that require a significant amount of time in order to evaluate the objective function, as in our case, we have to limit the number of generations to get reasonable processing time.
-Thus, different acceptable solutions can result from one or more optimizations \citep{Holland1992b}.
-This is a strength and a weakness of GAs: they are very good at exploring complex parameter spaces in order to identify the most promising areas, but they will not necessarily find the best solution with the optimal values of all parameters \citep{Holland1992b}.
-
-\subsection{Structure and operators}
-
-The GAs optimize a population of individuals (parameter sets).
-Each individual contains a chromosome (parameters of the analogue method in our case).
-We call gene every parameter that constitutes the chromosome.
-The parameters to optimize have long been coded in binary form and assembled as strings in the canonical GAs \citep{Goldberg1989}.
-Encoding and decoding steps were needed to transform the variable from its floating-point representation into its binary representation, and vice versa, which introduce quantification errors \citep{Haupt2004}.
-According to \citet{Holland1992b}, working with binary chromosomes was supposed to be more efficient \citep{Goldberg1990a, Back1993b}.
-However, more and more applications use floating-point representations, allowing to avoid the coding and decoding steps and the quantification errors \citep{Haupt2004}, and which also often resulted in a performance improvement \citep{Goldberg1990a}.
-It is thus now considered that for continuous variables, a floating-point representation is more suited \citep{Michalewicz1996, Herrera1998a, Haupt2004, Back1996b, Gaffney2010a}.
-
-There are numerous implementation variants of GAs often optimal for a given problem \citep{Hart1991a,Schraudolph1992a}.
-However, the structure of the method (Figure \ref{fig:structure_gas}) resulting from the work of \citet{Holland1992b} is common to most applications \citep{Back1993b}.
-The divergences are the operators implementation, through significantly different algorithms, which has an important effect on the results \citep{Gaffney2010a}.
-
-All operators we used and their options, applied to real coding, are described in the following sections. Many other operators exist, but we will only present the ones we evaluated.
-
-\subsubsection{Genesis of the population}
-
-The first step of the optimization is to generate the initial population.
-A population is a set of $N$ individuals (each of which represents a point in the space of potential solutions, a parameter set of the analogue method in our application) that we are going to make evolve.
-A generation is the population at a given time.
-
-A random initialization based on a uniform distribution is the most current version.
-The size $N$ of the population is often a compromise between the computation time and the quality of the solution.
-$N$ must allow sufficient sampling of the solutions field \citep{Beasley1996a}, and should thus vary as a function of chromosome size (ie the number of parameters to be optimized).
-
-\subsubsection{Natural selection}
-
-Natural selection is performed on the basis of the values of the objective function.
-The selection allows to only keep a certain part of the population, usually half ($N/2$), which can access the mating pool (intermediate generation with $N_{mp}$ members).
-If $N_{mp}$ is too high, the reproduction rate is too low, whereas if it is too small, the strong traits of individuals do not have the ability to accumulate in the same chromosome \citep{Haupt2004}.
-Several techniques exist, such as:
-
-\begin{itemize}
-	\item \textbf{$N_{mp}$-elitism} \citep{Michalewicz1996}: the population is sorted according to the value of the objective function and only the better half is preserved.
-
-	\item \textbf{Tournament selection} \citep{Michalewicz1996, Zitzler2004a}: two individuals are randomly selected and fight.
-The one with the highest score is chosen, but with a certain probability, in order to reduce the selection pressure.
-This procedure is repeated until the mating pool is full.
-Individuals can be selected several times, and thus be represented several times in the mating pool.
-\end{itemize}
-
-\subsubsection{Selection of the couples}
-
-Individuals of the mating pool can reproduce. It begins with the selection of pairs (the parents). The techniques implemented in this work are the following:
-
-\begin{itemize}
-	\item \textbf{Rank pairing}: individuals are gathered in pairs according to their rank (classified on the performance scores).
-Consecutive ranks are put together (odd rows are associated with even rows).
-This approach is easy to achieve, but does not look like a natural process.
-
-	\item \textbf{Random pairing}: two individuals are randomly selected to form a couple, according to a uniform law.
-
-	\item \textbf{Roulette wheel weighting}: the roulette technique refers to gambling.
-But unlike casino roulette, this one is biased.
-Each individual is associated with a sector of the wheel with a certain opening angle, which is its probability of selection \citep{Haupt2004}.
-The probability assigned to the individuals is proportional to their fitness (objective function), so that the most adapted individuals have the greatest probability of reproduction.
-There are two techniques for weighting the individuals of the mating pool:
-
-	\textit{Roulette wheel weighting on rank}: the probability of each individual depends on its rank $n$:
-	\begin{equation}
-	p_{n}=\dfrac{N_{mp}-n+1}{\sum^{N_{mp}}_{n=1}n}
-	\label{equation_mating_rank_weighting}
-	\end{equation}
-
-	\textit{Roulette wheel weighting on fitness}: the selection probability is calculated based on the value of the objective function.
-This approach gives more weight to the best individuals when the distribution of scores is wide, while the weight is almost similar when all individuals have approximately the same score \citep{Haupt2004}.
-The probability $p_{n}$ of each individual is calculated by the equation \ref{equation_mating_score_weighting}:
-	\begin{equation}
-	p_{n}=\frac{score_{n}-score_{N_{mp}}}{\sum_{n=1}^{N_{mp}} (score_{n}-score_{N_{mp}})}
-	\label{equation_mating_score_weighting}
-	\end{equation}
-	In our application, the last individual ($N_{mp}$) has zero probability of being selected.
-
-	\item \textbf{Tournament selection}: This operator is similar to the one used in natural selection, but is applied here for the successive selection of each parent.
-To select a parent, a number of individuals (2 or 3) are randomly picked and the best is kept.
-This operation is performed twice, once for each partner.
-This approach imitates the breeding competition in nature \citep{Haupt2004}.
-\end{itemize}
-
-\subsubsection{Chromosome crossover}
-
-Once the two parents are selected for breeding, they combine their chromosomes and produce two children, bringing the number of individuals in the population back to $N$ (the parents also return back in the total population in order to complement the next generation).
-The combination of chromosomes is carried out using a crossover operator, thereby generating two offspring having characteristics derived from both parents.
-Chromosome crossover widens the search space and favours the combination of strong genes, which can result in more suited children.
-It allows a mixing of genes and accumulation of positive mutations.
-
-The evaluated crossover operators are the following:
-
-\begin{itemize}
-	\item \textbf{Single-point crossover}: a crossover point is randomly chosen for the pair. The genes (our parameters) located after that point are exchanged in between the two chromosomes.
-
-	\item \textbf{Two-point crossover}: works like the single-point crossover, but there are two intersections defining the segments to exchange.
-This approach, which significantly extends the search space for the children, is considered more efficient than the previous \citep{Beasley1993a, Haupt2004}.
-
-	\item \textbf{Multiple-point crossover} \citep{DeJong1975a}: it is a generalization of the previous, with a number of crossover points up to the number of genes.
-
-	\item \textbf{Uniform crossover} \citep{Syswerda1989}: for each gene of the chromosome, it is randomly chosen to exchange or not the values between the parents.
-
-	\item \textbf{Binary-like crossover} \citep{Haupt2004}: chromosome crossover on a binary coding can generate new values for variables located at intersection points, since the crossovers are applied at the bit level, thus often within a gene.
-This is not the case for the floating-point representation, since the crossover is performed between the genes.
-To reproduce the behaviour present in the original algorithms, which introduces new information, \citet{Haupt2004} propose an operator that combines standard crossover with an interpolation approach.
-The genes located after a crossover point are exchanged, but the gene located at the intersection is modified as follows (equation \ref{equation_mating_as_binary}):
-	\begin{equation}
-	\left\lbrace \begin{array}{l} 
-	g_{o1,n} = g_{p1,n} - \beta (g_{p1,n} - g_{p2,n}) \\
-	g_{o2,n} = g_{p2,n} + \beta (g_{p1,n} - g_{p2,n}) \\
-	\end{array} \right.
-	\label{equation_mating_as_binary}
-	\end{equation}
-	where $g_{o1,n}$ and $g_{o2,n}$ are the $n$-th gene of the two new offspring, and $g_{p1,n}$ and $g_{p2,n}$ are those of the two parents. $\beta$ is a random value between 0 and 1.
-
-	\item \textbf{Blending method} \citep{Radcliffe1991a}: in this approach, instead of exchanging the genes in between the chromosomes after one or multiple crossover points, these are combined by linear combination (equation \ref{equation_mating_blending_method}).
-The genes of the parents are blended together using a random value ($\beta$) that can be unique for the whole chromosome, or that can change for every gene.
-The genes of the offspring are bounded by the genes of the parents, no value can be out of their range.
-	\begin{equation}
-	\left\lbrace \begin{array}{l} 
-	g_{o1,n} = \beta g_{p1,n} + (1-\beta)g_{p2,n} \\ 
-	g_{o2,n} = (1-\beta) g_{p1,n} + \beta g_{p2,n} \\
-	\end{array} \right.
-	\label{equation_mating_blending_method}
-	\end{equation}
-
-	\item \textbf{Linear crossover} \citep{Wright1991a}: in order to allow the genes to take values outside the interval defined by the parents, a method of extrapolation is necessary.
-Linear crossover introduces such an approach, and produces three children from two parents, following equation \ref{equation_mating_linear_crossover}.
-Less couples are required in order to fill up the generation.
-	\begin{equation}
-	\left\lbrace \begin{array}{l} 
-	g_{o1,n} = 0.5 g_{p1,n} + 0.5 g_{p2,n} \\ 
-	g_{o2,n} = 1.5 g_{p1,n} - 0.5 g_{p2,n} \\ 
-	g_{e3,n} = - 0.5 g_{p1,n} + 1.5 g_{p2,n} \\ 
-	\end{array} \right.
-	\label{equation_mating_linear_crossover}
-	\end{equation}
-
-	\item \textbf{Heuristic crossover} \citep{Michalewicz1996}: it is a variation of the latter methods that relies on the following equation:
-	\begin{equation}
-	\left\lbrace \begin{array}{l} 
-	g_{o1,n} = \beta (g_{p1,n} - g_{p2,n}) + g_{p1,n} \\
-	g_{o2,n} = \beta (g_{p2,n} - g_{p1,n}) + g_{p2,n} \\
-	\end{array} \right.
-	\label{equation_mating_heuristic_crossover}
-	\end{equation}
-
-	\item \textbf{Linear interpolation}: unlike previous techniques, this technique does not rely on crossover points, but on a linear interpolation on every gene of the couple (equation \ref{equation_mating_linear_interpolation}).
-	\begin{equation}
-	\left\lbrace \begin{array}{l} 
-	c_{o1} = c_{p1} - \beta (c_{p1} - c_{p2}) \\
-	c_{o2} = c_{p2} + \beta (c_{p1} - c_{p2}) \\
-	\end{array} \right.
-	\label{equation_mating_linear_interpolation}
-	\end{equation}
-	where $c_{o1}$ and $c_{o2}$ are the full chromosomes of the offspring, and $c_{p1}$ an $c_{p2}$ are the ones of the parents.
-As before, $\beta$ is a random value between 0 and 1, and is here the same for every gene.
-
-	\item \textbf{Free interpolation}: this technique performs interpolation on each gene, like the previous one; but in this case, the weighting factor changes for each gene:
-	\begin{equation}
-	\left\lbrace \begin{array}{l} 
-	c_{o1} = c_{p1} - [\beta_{1} (g_{p1,1} - g_{p2,1}), \beta_{2} (g_{p1,2}\\
-	~~~~~~~~~~~~ - g_{p2,2}), ..., \beta_{Ng} (g_{p1,N_{g}} - g_{p2,N_{g}})] \\
-	c_{o2} = c_{p2} + [\beta_{1} (g_{p1,1} - g_{p2,1}), \beta_{2} (g_{p1,2}\\
-	~~~~~~~~~~~~ - g_{p2,2}), ..., \beta_{Ng} (g_{p1,N_{g}} - g_{p2,N_{g}})] \\
-	\end{array} \right.
-	\label{equation_mating_free_interpolation}
-	\end{equation}
-	where $N_{g}$ is the number of genes, and $\beta$ is here independent between the genes.
-
-\end{itemize}
-
-Many other methods or variations exist, combining the advantages of different approaches.
-The performance of the variants being related to the problem to be addressed, we can not identify a priori the best technique for our application.
-
-\subsubsection{Mutation}
-
-The combination of strong genes by the operator of chromosomes crossover is theoretically the most important operating mechanism in the conventional GAs \citep{Holland1992b,Back1993b}.
-However, many studies identify the mutation process as main operator, and crossovers as secondary \citep[see][]{Back1992a,Back1996a,Back1996b,Smith1997a,Deb1999,Haupt2004,Costa2005a,Costa2007a}.
-
-The mutation operator is a direct modification of genes.
-In a binary coding, it is implemented as an inversion of some bits in a chromosome, while in real coding, it is done by changing the gene values.
-Mutations add diversity to the population and prevent a freeze of the evolution, or a genetic drift to a local optimum.
-Thus, it makes the convergence to the global optimum theoretically possible \citep{Beasley1993a}, as they allow exploring beyond the current region of the parameter space.
-They therefore help preventing the algorithm to converge too quickly to a local optimum and bring new characteristics that were not present in the original population \citep{Haupt2004}.
-
-The evaluated and developed mutation operators are the following:
-
-\begin{itemize}
-	\item \textbf{Uniform mutation}: The mutation rate is constant and equal for every gene of each individual; they all have the same probability to mutate.
-When a gene is selected for mutation, a new random value is assigned, according to a uniform law.
-
-	\item \textbf{Variable uniform mutation} \citep{Fogarty1989}: a variable mutation rate over the generations was first suggested by \citet{Holland1992b} and evaluated by \citet{Fogarty1989}.
-It improved significantly the performance of GAs.
-In most applications, the mutation rate decreases with the generations, in a deterministic and global (for all individuals) manner \citep{Back1992b}.
-Its optimum configuration depends on the size of the chromosomes, of the properties of the objective function, and of the population size \citep{Back1992b}.
-We implemented this operator according to equation \ref{equation_mutation_uniformvariable}.
-	\begin{equation}
-	p_{n,G} = p_{G_{0}}+\left( \dfrac{p_{G_{0}}-p_{G_{m,p}}}{G_{m,p}} \right) min\left\lbrace G,G_{m,p}\right\rbrace 
-	\label{equation_mutation_uniformvariable}
-	\end{equation}
-	where $p_{n,G}$ is the mutation rate (probability) of the gene $n$ for generation number $G$, $G_{m,p}$ is the maximum number of generations during which the mutation rate varies.
-$p_{G_{0}}$ is the initial mutation probability, and $p_{G_{m,p}}$ is the final one.
-$p_{G_{0}}$, $p_{G_{m,p}}$ and $G_{m,p}$ are the three controlling parameters of the operator.
-The evolution of the mutation rate is linear.
-
-	\item \textbf{Constant normal mutation}: many use normal distributions to generate new values. The gene $g$ that mutate becomes:
-	\begin{equation}
-	g' = N(g,\sigma^{2})
-	\label{equation_mutating_normal_distribution}
-	\end{equation}
-	where $\sigma$ is the standard deviation of the distribution.
-The disadvantage of this technique is that an accurate value of $\sigma$ must be chosen \citep{Haupt2004}, which is impossible to know beforehand.
-
-	\item \textbf{Variable normal mutation}: with the same logic that the variable uniform mutation, we tested a mutation operator using a normal distribution with a variable mutation rate and standard deviation.
-The mutation rate is calculated with equation \ref{equation_mutation_uniformvariable}.
-On the same principle, we decrease linearly the standard deviation over the generations:
-	\begin{equation}
-	\sigma_{n,G} = \sigma_{G_{0}}+\left( \dfrac{\sigma_{G_{0}}-\sigma_{G_{m,\sigma}}}{G_{m,\sigma}} \right) min\left\lbrace G,G_{m,\sigma}\right\rbrace 
-	\label{equation_mutation_normalvariable}
-	\end{equation}
-	where $\sigma_{n,G}$ is the standard deviation of gene $n$ et generation number $G$, $\sigma_{G_{0}}$ is the initial standard deviation, $\sigma_{G_{m,\sigma}}$ is the final standard deviation, $G_{m,\sigma}$ is the maximum number of generations during which the standard deviation varies.
-$p_{G_{0}}$, $p_{G_{m,p}}$, $G_{m,p}$, $\sigma_{G_{0}}$, $\sigma_{G_{m,\sigma}}$ and $G_{m,\sigma}$ are the six parameters of the method.
-
-	\item \textbf{Non-uniform mutation} \citep{Michalewicz1996}: two random numbers are picked based on a uniform law: $r_{1}$, which determines the direction of the change, and $r_{2}$, which determines its magnitude.
-The new value of the gene is given by the following equation:
-	\begin{equation}
-	g_{n}^{'} = 
-	\left\lbrace \begin{array}{l l} 
-	g_{n} + \left(b_{n}-g_{n}\right) r_{2} \left(1 - \dfrac{G}{G_{m}} \right)^{2} & if \; r_{1} < 0.5 \\
-	g_{n} - \left(g_{n}-a_{n}\right) r_{2} \left(1 - \dfrac{G}{G_{m}} \right)^{2} & if \; r_{1} \geq 0.5 \\
-	\end{array} \right.
-	\label{equation_mutation_nonuniform_original}
-	\end{equation}
-	where $a_{n}$ is the is the lower bound of the $n$-th gene, $b_{n}$ its upper bound, $G$ the present generation, and $G_{m}$ the maximum number of generations.
-
-	We adapted this operator for our application, which is not based on a predefined number of generations:
-	\begin{equation}
-	g_{n}^{'} = 
-	\left\lbrace \begin{array}{l l} 
-	g_{n} + \left(b_{n}-g_{n}\right) r_{2} \left(1 - \min \left\lbrace \dfrac{G}{G_{m,r}}, 1 \right\rbrace \left(1-\omega\right) \right)^{2} & if \; r_{1} < 0.5 \\
-	g_{n} - \left(g_{n}-a_{n}\right) r_{2} \left(1 - \min \left\lbrace \dfrac{G}{G_{m,r}}, 1 \right\rbrace \left(1-\omega\right) \right)^{2} & if \; r_{1} \geq 0.5 \\
-	\end{array} \right.
-	\label{equation_mutation_nonuniform}
-	\end{equation}
-	where $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a threshold chosen by the user to maintain a minimum search radius when $G>G_{m,r}$.
-During the first generations, the exploration extent covers the entire parameter space.
-However, this area is reduced over generations, allowing exploitation of local solutions.
-
-	\item \textbf{Individual adaptive mutation rate} \citep{Back1992a}: based on the ideas of Evolution Strategies \citep[see][]{Rechenberg1973, Schwefel1981}, \citet{Back1992a} introduced a concept of self-adaptive genetic algorithms.
-The idea is to distribute control parameters within individuals themselves, which partially decentralize control of the evolution.
-It allows reducing the parametrization of GAs and introducing a notion of self-management.
-The first approach is the introduction of a mutation rate per individual, that mutates itself under its own probability \citep{Back1992a}.
-Then, the eventual new rate is used to mutate the genes of the individual.
-Thus, as this rate decreases, it will have less probability of being itself mutated.
-This approach is close to the natural adaptation phenomena.
-A population less suited to its environment is changing faster than better adapted populations.
-Mutations are performed according to a constant uniform distribution.
-The initial mutation rates are randomly chosen \citep{Back1992a} and the method has no parameter.
-Other approaches exist to introduce a self-adaptation \citep[see][]{Smith1997a,Deb1999,Deb2001a}.
-
-	\item \textbf{Individual adaptive search radius}: based on the ideas of the non-uniform mutation, we introduce a search radius in the approach of individual adaptive mutation rates.
-This search radius $r_{a}$, bounded between 0 and 1, is also adaptive and behaves similarly to the adaptive mutation rates.
-In order to separate its evolution from the one of the mutation rate, its own value is considered initially as a self-mutation rate to eventually mutate before being used as a normalized search radius.
-The value of a mutated gene is given by the following equation, which is a simplification of the non-uniform mutation:
-	\begin{equation}
-	g_{n}^{'} = 
-	\left\lbrace \begin{array}{l l} 
-	g_{n} + \left(b_{n}-g_{n}\right) r_{2} r_{a} & if \; r_{1} < 0.5 \\
-	g_{n} - \left(g_{n}-a_{n}\right) r_{2} r_{a} & if \; r_{1} \geq 0.5 \\
-	\end{array} \right.
-	\label{equation_mutation_rayon_adaptatif}
-	\end{equation}
-	where $r_{1}$ and $r_{2}$ are randomly selected, in the same way as for the non-uniform mutation. No external parameter is therefore necessary.
-
-	\item \textbf{Chromosome of adaptive mutation rate} \citep[\textit{n adaptative mutation rate},][]{Back1992a}: analogously to the individual adaptive mutation rate, this approach leaves the control of the evolution rate to the individuals themselves.
-The difference here is that each gene has a specific mutation rate.
-The main advantage is that the tuning of the mutation can be much more precise \citep{Smith1997a}.
-We therefore consider a second chromosome containing the mutation rate for each gene of the first chromosome.
-The operations of mutation and self-mutation are similar to the case of the individual adaptive mutation rate, but in a distributed way, within the chromosome.
-Another difference is that we apply the same crossover operations as those applied to the first chromosome, and this for the same crossing points.
-Thus, during an exchange of genes, children also inherit the mutation rates specific for each of these genes.
-
-	\item \textbf{Chromosome of adaptive search radius}: we introduced this operator that combines the operations of the chromosome of adaptive mutation rate to our adaptive search radius approach.
-Similarly, an individual has 3 chromosomes: the first containing the values to be optimized, the second containing the distributed mutation rate, and the last one, the distributed search radius.
-Again, no external parameters are required.
-
-	\item \textbf{Multi-scale mutation}: finally, we developed another approach, that is also based on the search radius concept.
-However, the latter is not decreasing with time.
-Methods based on a reduction of the mutation rate or radius simulate a transition from the exploration phase to the exploitation one.
-The idea is consistent as long as we are confident that the algorithm will converge towards the global optimum.
-Indeed, once the algorithm is in the exploitation mode, it is very unlikely to go out of the region it converges to.
-We wanted to test an approach that combines both exploration and exploitation during the whole optimization.
-Thus, we considered the search radius $r_{a}$ of equation \ref{equation_mutation_rayon_adaptatif} as a random value for each individual, but restricted to 4 equiprobable values: 1, 0.5, 0.1, 0.02.
-The only external parameter is the mutation rate which is fixed.
-
-\end{itemize}
-
-When the gene to mutate is represented by a list of distinct values (eg meteorological variable or analogy criterion), the random choice of a new value is always based on a uniform distribution, without notion of search radius.
-There is indeed no meaning to use operators based on principles of proximity when the latter does not exist.
-
-\subsubsection{Elitism}
-
-We used a process of elitism on the natural selection as well as on mutations.
-This ensures the survival of the best individual so that we do not lose a better solution.
-This approach is very common in the field of GAs \citep{Haupt2004}.
-After the natural selection operator, if the best individual has not been selected, it is copied to the mating pool instead of an individual randomly picked.
-After mutation, if the best individual has mutated and if its new version has a lower score than the original, the latter is reinserted instead of an individual randomly chosen.
-
-\subsubsection{Ending the optimization}
-
-The convergence check determines whether the solution is acceptable and if the algorithm may stop.
-The stopping criteria are not often well documented in GAs case studies.
-We chose to stop the optimization if the best individual does not change for $x$ generations.
-This value should not be too low to allow the algorithm to escape from a local optima.
-In addition, the rate of improvement decreases with the progression of the optimization.
-It is thus common that the best individual does not evolve over several generations when we get closer to the global solution.
-We chose a value of $x=20$ generations.
-
-\subsection{Implementation and constraints}
-
-Some constraints need to be taken into account.
-For example, when a crossover or a mutation operation results in a parameter value standing out of the authorized bounds, it has to be brought back within the limits.
-Moreover, the parameters are of different nature: some are continuous, such as the weight, some are discretized, such as the analogues number, or the spatial windows, and finally, some are independent elements in an array, such as the selection of the meteorological variable.
-New values resulting from the optimizer need to respect the type of data it represents.
-
-Other constraints exist in between the parameters, such as the temporal window of the humidity index that has to be consistent in between the relative humidity and the precipitable water.
-Another example is the weighting of the different pressure levels which has to be normalized.
-
-GAs are very computationally intensive because they require many evaluations of the objective function.
-These assessments are very long in our application, as they require calculating and assessing a forecast for every day of the calibration period.
-In order to reduce the computation time, we avoid recalculating the score of an individual who has previously been evaluated and that has not changed.
-We keep the score of each individual living in the selection until it mutates.
-
-The assessment (calculation of the objective function) of each member of the population of a generation is completely independent and can be performed in parallel on different processors of a computer \citep{Alliot2005}.
-We implemented this technique and the resulting time savings was very important.
-In order to perform optimizations for multiple time series, the use of a cluster is a necessity, which our code allows.
-
-\subsection{Recommendations of parametrization}
-
-The GAs parametrization, such as the mutation rate, population size, natural selection options, and so on, is difficult given the high number of existing variants, each developed for a specific problem \citep{Haupt2004, Costa2007a}.
-This parametrization depends on the objective function, implementation variants, the range of the parameters to be optimized, and performance indicators.
-Thus, different studies suggest very different parametrization.
-
-A key element of the parametrization of GAs is finding the right balance between exploration and exploitation \citep{Back1992a, Smith1997a}.
-Exploration is characterized by a relatively high probability to assess the regions of the parameter space that have not yet been visited.
-This probability must be sufficiently large at the beginning of the optimization, so that the algorithm is capable of identifying the region where the global optimum is located.
-Exploitation is characterized by a local search in an area of interest, and generally makes small movements.
-The latter is interesting to refine the results at the end of the optimization.
-
-\citet{DeJong1975a} and \citet{Grefenstette1986} compared different implementations and parametrizations of GAs on functions of varying complexity.
-They observed that a small population size improves the initial performance, while a large population improves long-term performance.
-They also observed that the ratio of the population to keep for the mating pool is around 50\% (45\% to 60\%).
-
-Values of the mutation rate varies broadly between the studies: from 0.001 \citep{DeJong1975a} to 0.2 \citep{Haupt2004}.
-\citet{Back1996b} showed that mutation rates higher than the usual ranges are more optimal at the beginning of the optimization, allowing further exploration.
-The combination of a small population and a high mutation rate works best for the first generations \citep{DeJong1975a, Back1996b, Haupt2004}, but as we could observe, it does not guarantee the quality of the final result.
-Incremental approaches with varying mutation rates are certainly more optimal but more complex to implement \citep{Back1996a, Back1996b}.
-
-\subsubsection{Comparison process and results}
-
-One of our goals being to make recommendations of parametrization in order to optimize the analogue method, we proceeded systematically.
-The results are summarized hereafter \citep[see][for the details]{Horton2012a}.
-We used concepts from the factorial design approach \citep[see eg.][]{Costa2005a,Costa2007a,Mariano2010a}, which is sometimes used for comparative analysis of different parametrizations of GAs.
-We processed by stages, analysing in details and in a systematic way every variants of the implemented operators, in combination with multiple other options and parameters in order to take into account eventual co-dependencies.
-
-In order to evaluate a combination of operators/options, we processed 10 optimizations for one parametrization of GAs. The performances were characterized by four indicators:
-
-\begin{itemize}
-	\item mean score: average of the final scores of the 10 optimizations,
-	\item convergence: the number of optimizations that converged to a supposed global optimum,
-	\item number of generations: characterization of the convergence speed,
-	\item number of evaluations of the objective function: characterization of the required calculation time (more realistic than the number of generations).
-\end{itemize}
-
-This comparison required tens of thousands of optimizations that were performed on a cluster of the University of Lausanne. The results, detailed in \citet{Horton2012a} are synthesized hereafter:
-
-\begin{itemize}
-	\item \textbf{Population size}: we found the following ranges to be accurate in average:
-
-	$50<N<100$ for a very simple implementation of the analogue method (1 level of analogy with 2 pressure levels),
-
-	$N\approx200$ for a bit more complex method (1 level of analogy with 4 pressure levels, or 2 level of analogy with less pressure levels),
-
-	$N\approx500$ for significantly more complex methods (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the humidity analogy),
-
-	We didn't find any improvement with $N>500$, the results were even surprisingly of a lower quality.
-However, this cannot be generalized and depends on the analogue method to optimize, and supposedly on the characteristics of the processes generating the precipitations in a given region.
-
-	\item \textbf{Natural selection}: this operator has no significant influence, and both tested implementations work fine, with a slightly better performance for the ratio-elitism.
-
-	\item \textbf{Selection of couples}: 6 variants of the couples selection were assessed.
-The performance of these variants are relatively close, both in terms of score, convergence, and number of evaluations.
-The random pairing performed the most poorly, when the tournament selection with 3 candidates was slightly superior.
-The roulette wheel weighting is not far behind, but it is less effective in terms of convergence and number of evaluations.
-This operator has not a significant role in our application.
-
-	\item \textbf{Chromosomes crossover}: we compared 21 different options of the crossover operators.
-This analysis revealed some slightly better options, some bad ones, and many averages.
-Among the bad operators, we find first the heuristic crossover, which is also more demanding in number of evaluations, as well as the linear crossover.
-Binary-like crossovers (especially with 2 points of intersection, whether $\beta$ is shared or not) are significantly better than the others, especially in terms of convergence.
-The two points crossover is relatively close.
-Other operators can be considered usable, yet may not be optimal.
-Once again, this operator is not the key of the GAs parametrization.
-
-	\item \textbf{Mutation}: we compared the 10 mutation operators with different options, bringing the number of variations of this operator up to 110.
-We immediately observed that the mutation operator has a very important role on the performance of the optimizations of the analogue method, and that the other reproduction operators seem of secondary importance.
-This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction.
-He even suggests, in opposition with the theory of \citet{Holland1992a}, that chromosomes crossovers have mostly a corrective role of mutation operations.
-Various studies have also identified the importance of the mutation operator relatively to reproduction \citep[see eg.][]{Back1992a, Back1996b, Smith1997a, Deb1999, Haupt2004, Costa2005a, Costa2007a}.
-
-	The mutation operators based on a variable normal or uniform law work very poorly and are difficult to configure.
-We then observe many operators more or less with the same scores and requiring a variable amount of assessments.
-The convergence analysis allows us to highlight three best operators:
-
-	\textit{Non-uniform mutation} \citep{Michalewicz1996}: this operator is good in terms of convergence, mainly when the number of parameters to optimize is rather low.
-The number of required evaluations, however, can be quite substantial.
-The main disadvantage of the non-uniform mutation is the complexity of its parametrization, which is difficult to estimate a priori.
-These parameters must be carefully chosen to be in line with the evolution rate of the population, and are therefore dependent on the problem being treated.
-We could observe that the $\omega$ coefficient does not influence performance.
-The role of $G_{m}$ is rather difficult to judge, but does not seem essential.
-The mutation rate was found to be important.
-The difficulty is that the optimal value seems to be very case-related.
-Indeed, by even changing the precipitation time series (ie optimizing for another subregion), but not the complexity of the analogue method, the optimal mutation rate changes, making it impossible to estimate in advance.
-
-	\textit{Chromosome of adaptive search radius}: unlike the previous one, our new operator is very robust, as it requires no option and is auto-adapting.
-It may be sometimes a little bit slower for simple problems, but does not require parametrization, which is an important advantage.
-It is interesting to notice that our insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).
-
-	\textit{Multi-scale mutation}: finally, our multi-scale mutation, which also performs pretty well, can as well be seen as fairly robust, since it requires only one parameter, the mutation rate.
-However, it can also be difficult to estimate a correct value a priori.
-
-	It may be wise to perform multiple optimizations and to consider these three operators in parallel in order to obtain results from algorithms that are either sometimes more efficient or more robust.
-It is interesting to note that the three best techniques incorporate a notion of search distance.
-It is likely that this notion is the key to these algorithms, for our application, and allows them to initially explore the parameter domain, and then to converge.
-The search radius in fact directly represents the notion of transition between exploration and exploitation, in our opinion more than a possible evolution of mutation rates.
-
-	\item \textbf{Other options}: A ratio of 50\% for the mating pool seems to be a good choice.
-
-\end{itemize}
-
-\subsubsection{Recommended parametrization of GAs}
-
-We evaluated the optimization by genetic algorithms on methods of varying complexity, with a large number of combinations of operators to be able to make recommendations for optimizing the analogue method.
-Our conclusions are:
-
-\begin{itemize}
-	\item The optimization does not systematically converge to the global optimum  (but still often nearby), which is why we recommend doing several optimizations in parallel in order to compare the results, analyse the convergence, and keep the best.
-
-	\item The population size should be in accordance with the complexity of the method to optimize: from 50 for the simple ones, up to 500 for the most complex methods.
-
-	\item The value of the ratio for the intermediate population is not so important, and value of 50\% seems quite appropriate.
-
-	\item Ratio-elitism is slightly better than tournaments for the natural selection operator, but it is not decisive.
-
-	\item The performance of the operators for the couples selection perform relatively similarly.
-The roulette wheel weighting and the tournament selection are more efficient in terms of convergence and required number of evaluations.
-
-	\item Most crossover operators have relatively similar performance. Binary-like crossover with two points of intersection are better than others, especially for convergence.
-
-	\item Mutation has a clearly dominant influence.
-Three mutation operators stand out, two of which we have developed: the non-uniform mutation, the multi-scale mutation, and the chromosome of adaptive search radius.
-The latter is the most robust as it has no controlling parameter.
-
-\end{itemize}
-
-In order to make an optimization of the analogue method with genetic algorithms, it may be wise to consider these three mutation operators in parallel.
-We would then combine algorithms that are sometimes faster to other that are more robust.
-In order to be confident in the optimized methods, we propose using a set of the following mutation operators:
-
-\begin{itemize}
-	\setlength\itemsep{-4px}
-	\item 1x non-uniform, $p_{mut}=0.1$, $G_{m}=50$, $\omega=0.1$
-	\item 1x non-uniform, $p_{mut}=0.1$, $G_{m}=100$, $\omega=0.1$
-	\item 1x non-uniform, $p_{mut}=0.2$, $G_{m}=100$, $\omega=0.1$
-	\item 1x multi-scale,  $p_{mut}=0.1$
-	\item 2x chromosome of adaptive search radius
-\end{itemize}
-
-\section{Example case study}
-
-The analogue method has to be adapted to every new location it is applied.
-We improved the analogue method for the Swiss Alps, by means of genetic algorithms.
-A summary of the main results are provided here \citep[see][for the details]{Horton2012a}.
-Even though the results may differ from one place to another, the applicability of GAs to the analogue method remains universal.
-
-\subsection{Case study description}
+\section{Case study description}
 
@@
 
-\subsection{Optimization of the analogy of atmospheric circulation}
+\section{Optimization of the analogy of atmospheric circulation}
 
@@
 
-\subsubsection{Which parameters are optimized ?}
+\subsection{Which parameters are optimized ?}
 
@@
 
-\subsubsection{Results for the z4 method}
+\subsection{Results for the z4 method}
 
@@
 
-\subsubsection{Analysis}
+\subsection{Analysis}
 
@@
 
-\subsection{Optimization of the analogy with humidity variables}
+\section{Optimization of the analogy with humidity variables}
 
@@
 
-\subsubsection{Results for z4-hi2 and z4-hi4 methods}
+\subsection{Results for z4-hi2 and z4-hi4 methods}
 
@@
 
-\subsection{Discussion}
+\section{Discussion}
 

### 2015-10-13 AtmoSwing - Geoscientific Model Development/template.tex
Structure of the method.

@@
 \subsection{Its evolution}
+\label{sec:method:evolution}
 
@@
 
+\citet{Bontron2004} could benefit from the newly available NCEP/NCAR reanalysis data.
+This dataset being more homogeneous, much longer, and contained more variables than what was previously used, he could systematically assess a large selection of variables in the analogue method combined with different criteria.
+He thus confirmed the interest of the geopotential height along with the S1 criterion for the first level of analogy.
+He has also shown that the choice of the temporal window (time of observation) has a higher importance than the atmospheric level for the performance of the method.
+By assessing multiple combinations of atmospheric levels and temporal windows, he concluded that the coupled geopotential heights at 1000~hPa \& 12~h and 500~hPa \& 24~h provided the best performance for the studied region.
+
+He also assessed several variables for the second level of analogy and identified the humidity variables (precipitable water and relative humidity) and vertical velocity to be the most relevant.
+Finally, he found that the product of relative humidity and precipitable water gave the best performance.
+
+He noted the relevance of defining different spatial windows for each region, rather than a single window to the entire territory.
+These windows are more able to represent the specific atmospheric influences for the region.
+In order to assess the forecast, he introduced the Continuous Ranked Probability Score \citep[CRPS, Eq.
+\ref{eq:CRPS}, ][]{Brown1974}, which discards the issue of determining classes as with the RPS previously in use.
+
+\citet{BenDaoud2010} applied the analogue method in the context of large flatter catchments, out of an Alpine environment (Sa\^{o}ne, Seine).
+He evaluated several variables usually used in weather forecasting, amongst them the air temperature and the vertical velocity that presented a potential interest.
+The temperature (at the nearest grid point, on the 925~hPa (36~h) and 600~hPa (12~h) levels) could replace the rigid selection of $\pm$ 60 days around the target date by a more dynamic screening of similar situations in terms of air masses.
+The seasonal effect is indeed also present in the temperature data.
+The vertical velocity was used as an additional level of analogy, between the analogy of atmospheric circulation and the one on humidity, to account for fronts.
+Finally, he selected the humidity variables at 700~hPa instead of 850~Pa.
+
+\citet{Bliefernicht2010} proposed to add a weighting to the grid points of the predictor to overcome a comparison on a fixed-size window, and to give more importance to regions with relevant atmospheric circulation information.
+However, he noticed that there is a risk of overparametrization and a simplification of the weighting fields may be necessary, and that the performance was not stable between the calibration and the validation periods.
+He also compare the performance of the analogues method with a forecasting method based on a weather types approach, and concluded that the analogues method was more efficient.
+
+% TODO : Sabine
+% TODO : Jérémie Chardon
+
+\subsection{Present structure}
+
+Although multiple variations of the method exist, they generally share the same basics and the same structure.
+We want here to forecast the daily precipitation (the predictand) for a target day (at a defined lead time) and have long archives of both the predictand and predictor variables.
+The generic structure is the following:
+
+\begin{enumerate}
+	\item Preselection: to cope with seasonal effects, candidate dates are extracted from the archive within a period of four months centered around the target date, for every year of the archive.
+Alternatively, the candidate dates can be selected based on similar air temperature \citep{BenDaoud2010}.
+
+	\item First level of analogy: we subsample $N_{1}$ dates within all the candidates provided by the preselection, by means of an analogy ranking.
+The first level of analogy is always the atmospheric circulation when it comes to precipitation forecasting.
+We thus assess the similarity of the atmospheric circulation of our target date with all the situations provided by the preselection by means of the S1 criteria \citep[Eq.\ref{eq:S1}, ][see also section \ref{sec:method:evolution}]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
+
+	\begin{equation}
+	\label{eq:S1}
+	S1=100 \frac {\displaystyle \sum_{i} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
+	{\displaystyle \sum_{i} max\left\lbrace \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert \right\rbrace }
+	\end{equation}
+	where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points in the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
+The differences are processed separately in both directions.
+The smaller the S1 values are, the more similar the pressure fields.
+
+	The $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day. The number of analogues, $N_{1}$, is a parameter to calibrate.
+
+	\item Subsequent level(s) of analogy: we can then subsample once again the $N_{1}$ analogues on the basis of another variable in order to obtain a lower number of analogue dates, $N_{2}$.
+The S1 criterion is usually not relevant for other predictors that the atmospheric circulation.
+Other classic criteria represent absolute distances: Mean Absolute Error (MAE) and Root Mean Squared Error (RMSE), the latest being most often used.
+These are more relevant to compare humidity variables for example.
+
+	This process can be repeated, by subsampling a decreasing number of analogues, $N_{i}$, according to a ranking processed on various meteorological variables.
+
+	\item Probabilistic forecast: then, the daily observed precipitation amount (or another predictand of interest) of the $N_{i}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
+The empirical frequencies are processed for every value of the predictand, after classification, based on the Gringorten parameters (for a Gumbel or exponential law).
+
+\end{enumerate}
+
 \subsection{References implementations}
@@
 
-\subsection{Datasets}
-% TODO: write
+\subsection{Data}
+% TODO: write
+
+The analogue method relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series we want to forecast.
+
+Predictors are generally reanalysis datasets (and outputs of a global numerical weather prediction models for the target situation in operational forecasting, which is not the topic of this paper).
+We will work here with the NCEP/NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996}, but it can be any other reanalysis dataset.
+
+The predictand (which is to be predicted) is in our case the daily precipitation (6~a.m.
+to 6~a.m.
+the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008.
+The time series from every available gauging station were averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.
+
+%\citet{Djerboua2001} a également proposé de normaliser la pluie par la pluie décennale à la station (ou groupement), ce qui nous permet de mieux identifier les contributions les plus importantes en précipitations.
+
+%Par une étude de sensibilité, \citet{Bontron2004} a déterminé un plafonnement de la longueur de l'archive nécessaire à 30 ans pour la prévision en général, et à 40 ans pour les événements intenses.
+Il a également mis en lumière la dépendance entre le nombre d'analogues optimal et la taille de l'archive: plus l'archive est courte, plus le nombre d'analogues diminue.
+En faisant varier la résolution des grilles de prédicteurs, il en a conclu que l'augmentation en performance n'est pas significative pour l'analogie de circulation en deçà d'une résolution de 5\degres .
+Cependant, elle semble plus importante pour le second niveau d'analogie sur les humidités, qui sont des variables plus locales.
+
+%\citet{BenDaoud2010} a dans un premier temps évalué les réanalyses européennes ERA-40 \citep{Uppala1999}, avec une résolution de 1.125\degres, par rapport aux réanalyses américaines du NCEP/NCAR à 2.5\degres\ \citep{Kalnay1996} utilisées jusqu'alors.
+Il a identifié une légère amélioration des performances, mais pas assez substantielle pour vraiment justifier un changement d'archive \citep{BenDaoud2008}.
 
@@
 % TODO: write
+
+%\citet{Djerboua2001} a appliqué la méthode développée par \citet{Guilbaud1997} en prévision opérationnelle dans le cadre du projet MAP \citep[\textit{Mesoscale Alpine Programme}, voir][]{Binder1996}, lors de la période spéciale d'observation \citep{Bougeault2001}.
+Il a relevé que le quantile 60~\% prévoyait le mieux les quantités de précipitations pour les situations normales, mais que lorsque la pluie observée était forte à extrême, le quantile 90~\% s'avérait être un meilleur témoin.
+Il convient donc de porter une attention particulière au quantile 90~\% qui, lorsqu'il monte brutalement, peut être le signe d'une situation propice à un événement de nature extrême, par la présence de plusieurs analogues dans la distribution avec des cumuls observés significatifs \citep{Djerboua2001}.
+En opérationnel, les prévisionnistes doivent prêter attention à la distribution des meilleures analogues.
+Si, par exemple, celle-ci est décalée vers des valeurs plus élevées, il y a un risque de sous-estimer l'événement.
+
+%En comparant les performances des modèles de Météo France avec la méthode des analogues, il en a conclu que les modèles numériques sont meilleurs pour la prévision du jour même, alors que les analogues deviennent plus concurrentielles (et meilleures pour les bassins de taille moyenne) pour les échéances suivantes.
+
+% En opérationnel, ce second niveau est pertinent jusqu'à une échéance de 3~jours. Au-delà, les prévisions d'humidité ne sont pas assez performantes pour être utiles.
+
+%En analysant les distributions de précipitations issues des analogues, \citet{Bontron2004} a identifié le quantile 60~\% comme étant le plus informatif pour l'occurrence des précipitations, et le quantile 90~\% pour la prévision des précipitations moyennes à fortes ($P > P10/10$, soit un dixième de la pluie décennale).
+
+%En opérationnel, ces niveaux supplémentaires se sont montrés utiles pour les deux à trois premières échéances, mais au-delà, toutes les méthodes deviennent équivalentes à l'analogie sur la circulation, car les autres variables, comme la vitesse verticale, sont alors mal prévues.
 
@@
 
+\section{Perspectives}
+
+%\citet{Thevenot2004} a étudié plusieurs aspects de la méthode des analogues en utilisation opérationnelle.
+Le premier a consisté à intégrer les prévisions d'ensemble du Centre Européen de Prévision Météorologique à Moyen Terme (CEPMMT, ou \textit{European Centre for Medium-Range Weather Forecasts}, ECMWF).
+Cette approche permet de tenir compte des incertitudes sur les prédicteurs issus du modèle global.
+Son implémentation est une combinaison des journées analogues retenues, associées à chacune des traces.
+La distribution des précipitations est ensuite établie sur l'ensemble des analogues.
+Ainsi, certaines journées peuvent être représentées plusieurs fois.
+À partir d'une échéance de 4 jours, la prévision sur l'ensemble des traces se montre plus performante que celle effectuée sur le seul contrôle déterministe.
+
+%Il a aussi effectué une calibration du nombre d'analogues à retenir en fonction de l'échéance pour la prévision déterministe, ainsi que pour la prévision d'ensemble.
+Pour la prévision déterministe, le nombre d'analogues pour les deux premières échéances est identique à celui de la prévision parfaite \citep[calibration sur les réanalyses,][]{Klein1963}, puis croît de manière importante jusqu'à tendre vers l'ensemble de la climatologie.
+Cette optimisation a été effectuée sur la méthode à un niveau d'analogie (analogie de circulation), mais n'a pas pu être entreprise de manière aussi rigoureuse sur le second niveau d'analogie.
+
+%\citet{Marty2010} a appliqué plusieurs scores de validation aux quantiles de la distribution des prévisions opérationnelles de la méthode des analogues.
+Il en a conclu que la détection de l'occurrence des pluies était mieux prévue par les quantiles médians (50 à 70~\%), avec un optimum à 60~\%.
+Toutefois, pour les pluies significatives, le quantile 90~\% donnait les meilleures performances.
+En comparant les résultats des analogues et des prévisions d'ensemble, pour le quantile 90~\%, il a observé que, à partir de $P = 0.16 \cdot P10$, les analogues donnaient trop d'alertes, alors que les ensembles n'en émettaient pas assez.
+La prévision opérationnelle par analogie était meilleure que celle des ensembles considérés, et ceci particulièrement pour les forts cumuls \citep{Marty2010}.
+Le gain des analogues provient principalement d'une meilleure justesse, pour une moins bonne finesse.
+Au contraire, les prévisions d'ensemble sont très fines, mais manquent un peu de justesse.
+
+%Lors de l'analyse du biais des résultats de la méthode des analogues en opérationnel (également des ensembles), il a observé que la fréquence prévue des pluies nulles ($F(0)$) était biaisée et sous-estimait la fréquence réelle des précipitations nulles.
+Au contraire, les fréquences prévues des pluies positives ($F_{+}$) surestimaient les fréquences observées.
+Ainsi, par exemple, le quantile 50~\% de la distribution prévue correspondrait au quantile réel 32~\%, et le 90~\% prévu au 81~\% réel.
+Il a donc proposé une correction des biais.
+
+%En analysant le biais de la méthode des analogues en prévision parfaite (voir section \ref{sec:etat_art:calibration}), il a observé que $F(0)$ et $F_{+}$ n'étaient que très légèrement biaisés, et que les biais observés précédemment avaient donc une origine externe (l'échantillon des prévisions du modèle numérique global utilisé).
+Toutefois, en appliquant un conditionnement par $F(0)$, il est apparu que \og \textit{si la journée cible est prévue pour être plutôt humide ($F(0) \leq 0.10$), les fréquences de $F_{+}$ sont surestimées (et les quantiles de précipitations sont dès lors sous-estimés)}\fg{}, et au contraire, que \og \textit{si elle est prévue pour être plutôt sèche avec une probabilité moyenne ($F(0) > 0.20$), alors les fréquences $F_{+}$ sont sous-estimées (et les quantiles de précipitations sont dès lors surestimés)}\fg{}.
+Il a donc proposé une méthode de correction a priori en appliquant un coefficient correctif sur chaque fréquence quantilique en fonction de $F(0)$, puis en déterminant la distribution a posteriori, ajustée selon la loi Gamma à deux paramètres.
+Cette correction s'est avérer améliorer les performances des prévisions pour les journées à fortes précipitations.
+
+%Il a encore proposé une désagrégation temporelle à 6 et 12~h des prévisions de la méthode des analogues pour une utilisation opérationnelle dans une chaîne hydrométéorologique.
+La meilleure méthode identifiée consistait à utiliser les cumuls prévus par la méthode des analogues à un pas de temps journalier, et de leur appliquer la chronologie des prévisions d'ensemble, lesquels reproduisent bien la répartition infrajournalière.
+
 \conclusions  %% \conclusions[modified heading if necessary]

### 2015-10-15 AtmoSwing - Geoscientific Model Development/template.tex
Adding the parameterization tables.

@@
 %% 2-Column Papers and Discussion Papers
-\documentclass[gmd, manuscript]{copernicus}
+%\documentclass[gmd, manuscript]{copernicus}
+\documentclass[gmd]{copernicus}
 
@@
 
+The most common usage of the analogue method is for precipitation forecasting. Thus, the evolution presented hereafter focuses on this predictand.
+
 \citet{Lorenz1969} introduced the concept and established the basis of the method.
@@
 % TODO : Jérémie Chardon
+% TODO : Horton
 
@@
 
-\subsection{References implementations}
-% TODO: write
+\subsection{References implementations for precipitation forecasting}
+
+The evolution of the analogue method for precipitation forecasting led to several improvements.
+However, some of these are specific for a certain region and are not relevant for others, and some perform better depending on the lead time.
+Thereby, we cannot provide a single best parameterization for the method, neither rank them from worst to best.
+We will thus provide the references implementations of the most recent method variant, in the chronological order they appeared.
+
+%\subsection{R0, les origines}
+%\label{sec:etat_art:R0}
+
+%Une référence préliminaire résulte des travaux de \citet{Guilbaud1997} et \citet{Obled2002}.
+Elle est constituée d'un seul niveau d'analogie sur la circulation atmosphérique considérée à 1000~hPa et 700~hPa (R0a, Table \ref{table:R0a}) ou 500~hPa (R0b, Table \ref{table:R0b}).
+Le critère S1 de Teweles-Wobus est alors utilisé pour comparer les champs de géopotentiel.
+
+\begin{table}[htbp]
+	\caption{R0a.}
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+			\hline
+			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & Z700 & 00, 24~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
+			& Z1000 & 00, 24~h & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:R0a}
+\end{table}
+
+\begin{table}[htbp]
+	\caption{R0b.}
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+			\hline 
+			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & Z500 & 00, 24~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
+			& Z1000 & 00, 24~h & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:R0b}
+\end{table}
+
+%\subsection{R1, analogie de circulation}
+%\label{sec:etat_art:R1}
+%\review{6}
+
+%Ce que nous considérerons comme notre première référence est l'analogie de circulation (R1, Table \ref{table:R1}) optimisée par \citet{Bontron2004}.
+Ce dernier a observé que le choix de l'heure était plus important que celui du niveau atmosphérique.
+La méthode est alors constituée du géopotentiel à deux niveaux atmosphériques et à des heures différentes.
+
+\begin{table}[htbp]
+	\caption{R1.}
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+			\hline 
+			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
+			& Z500 & 24~h & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:R1}
+\end{table}
+
+%\subsection{R2, prise en compte de l'humidité}
+%\label{sec:etat_art:R2}
+%\review{6}
+
+%Toujours d'après les travaux de \citet{Bontron2004}, la référence suivante (R2, Table \ref{table:R2}) intègre un second niveau d'analogie sur un indice d'humidité: le produit de l'humidité relative à 850~hPa et de l'eau précipitable de la colonne.
+Cette variable ne représente pas une grandeur physique réelle, mais exprime le contenu en eau de la colonne et sa proximité ou son éloignement de la saturation (à 850~hPa).
+
+\begin{table}[htbp]
+	\caption{R2.}
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+			\hline 
+			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
+			& Z500 & 24~h & & \\ 
+			\hline
+			2 & TPW * RH850 & 12, 24~h & RMSE & 30 \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:R2}
+\end{table}
+
+%\subsection{R3, prise en compte du flux d'humidité}
+%\label{sec:etat_art:R3}
+
+%\citet{Marty2010} a recalibré les paramètres déterminés par \citet{Bontron2004} pour une application infrajournalière (résolution temporelle de 12~h), et sur la base d'un jeu de données de réanalyses plus complet.
+Il a proposé deux modèles avec un second niveau d'analogie sur l'humidité (R3a, Table \ref{table:R3a}) ou le flux d'humidité au niveau 700~hPa (R3b, Table \ref{table:R3b}) ou 925~hPa (R3c, Table \ref{table:R3c}).
+Les heures et les niveaux changent par rapport à ceux établis par \citet{Bontron2004}, car ceux-ci n'étaient alors pas disponibles.
+
+\begin{table}[htbp]
+	\caption{R3a.}
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+			\hline 
+			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{75} \\
+			& Z500 & 18~h & & \\ 
+			\hline
+			2 & TPW * RH925 & 06, 18~h & RMSE & 30 \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:R3a}
+\end{table}
+
+\begin{table}[htbp]
+	\caption{R3b.}
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+			\hline 
+			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{60} \\
+			& Z 500~hPa & 18~h & & \\ 
+			\hline
+			2 & V700 * TPW * RH700 & 06, 18~h & RMSE & 25 \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:R3b}
+\end{table}
+
+\begin{table}[htbp]
+	\caption{R3c.}
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+			\hline 
+			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{60} \\
+			& Z 500~hPa & 18~h & & \\ 
+			\hline
+			2 & V925 * TPW * RH925 & 06, 18~h & RMSE & 25 \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:R3c}
+\end{table}
+
+%Le flux d'humidité est composé du produit de l'eau précipitable et de l'humidité relative, multiplié par la norme de la vitesse du vent ($V$).
+
+%\subsection{R4, présélection sur les températures}
+%\label{sec:etat_art:R4}
+%\review{6}
+
+%La quatrième référence reconsidère la sélection des journées candidates à l'analogie et utilise la présélection sur les températures introduite par \citet{BenDaoud2010}.
+Nous nous affranchissons donc de la sélection d'une période de 4 mois centrée sur la date pour une approche plus dynamique qui tient différemment compte de l'effet de saisonnalité.
+Le nombre d'analogues de la présélection est équivalent au nombre de jours que nous aurions retenus par la période de $\pm 60$ jours, soit $N_{0} = 60 \cdot 2 \cdot n_{a}$, où $n_{a}$ est le nombre d'années de la période de calibration.
+Mais la sélection est ici fondée sur un critère de similitude thermique au droit de la région cible.
+
+\begin{table}[htbp]
+	\caption{R4a.}
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+			\hline
+			\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
+			& T600 & 12~h & & \\ 
+			\hline 
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
+			& Z 500~hPa & 24~h & & \\ 
+			\hline
+			2 & TPW * RH850 & 12, 24~h & RMSE & 25 \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:R4a}
+\end{table}
+
+\begin{table}[htbp]
+	\caption{R4b.}
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+			\hline
+			\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
+			& T600 & 12~h & & \\ 
+			\hline 
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
+			& Z 500~hPa & 24~h & & \\ 
+			\hline
+			\multirow{2}{*}{2} & TPW * RH925 & 12, 24~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
+			& TPW * RH700 & 12, 24~h & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:R4b}
+\end{table}
+
+\begin{table}[htbp]
+	\caption{R4c.}
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+			\hline
+			\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
+			& T600 & 12~h & & \\ 
+			\hline 
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
+			& Z 500~hPa & 24~h & & \\ 
+			\hline
+			\multirow{2}{*}{2} & TPW * RH925 & 06-30~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
+			& TPW * RH700 & 06-30~h & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:R4c}
+\end{table}
+
+%Trois références sont donc retenues ici: la première (R4a, Table \ref{table:R4a}) considère le niveau d'analogie sur l'humidité tel que l'a défini \citet{Bontron2004}, la deuxième (R4b, Table \ref{table:R4b}) intègre les niveaux d'humidité calibrés par \citet{BenDaoud2010}, et la troisième (R4c, Table \ref{table:R4c}) considère toutes les heures d'observation disponibles pour ce dernier niveau d'analogie.
+
+%\subsection{R5, prise en compte des mouvements verticaux}
+%\label{sec:etat_art:R5}
+
+%\citet{BenDaoud2010} a encore ajouté un niveau d'analogie sur les mouvements verticaux.
+Ce niveau vient s'insérer entre l'analogie de circulation et celle de l'humidité.
+À nouveau, nous considérons une première référence (R5a, Table \ref{table:R5a}) avec les paramètres d'humidité selon \citet{Bontron2004}, et une seconde (R5b, Table \ref{table:R5b}) avec les paramètres de \citet{BenDaoud2010}.
+
+\begin{table}[htbp]
+	\caption{R5a.}
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+			\hline
+			\multirow{2}{*}{0} & T925 (1 point) & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
+			& T600 (1 point) & 12~h & & \\ 
+			\hline 
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{170} \\
+			& Z 500~hPa & 24~h & & \\ 
+			\hline
+			2 & W850 & 06-24~h & RMSE & 70 \\
+			\hline
+			3 & TPW * RH850 & 12, 24~h & RMSE & 25 \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:R5a}
+\end{table}
+
+\begin{table}[htbp]
+	\caption{R5b.}
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+			\hline
+			\multirow{2}{*}{0} & T925 (1 point) & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
+			& T600 (1 point) & 12~h & & \\ 
+			\hline 
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{170} \\
+			& Z 500~hPa & 24~h & & \\ 
+			\hline
+			2 & W850 & 06-24~h & RMSE & 70 \\
+			\hline
+			\multirow{2}{*}{3} & TPW * RH925 & 12, 24~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
+			& TPW * RH700 & 12, 24~h & & \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:R5b}
+\end{table}
 
@@
 Il a identifié une légère amélioration des performances, mais pas assez substantielle pour vraiment justifier un changement d'archive \citep{BenDaoud2008}.
+
+\subsection{Discussion}
+% TODO: write
+
+%\citet{Bliefernicht2010} a observé que la performance de la méthode est plus élevée en hiver qu'en été.
+Ainsi, la relation entre les prédicteurs synoptiques et les précipitations locales est plus faible en été, en raison des pluies d'origine convective qui ont un caractère plus aléatoire.
+
+%La méthode des analogues, ou une forme proche, a également été utilisée pour la prévision à court ou moyen terme des températures journalières \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, des vents \citep{Gordon1987}, des avalanches \citep{Obled1980, Bolognesi1993}, de l'insolation \citep{Bois1981}, et de la trajectoire de cyclones tropicaux \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+
+%\citet{Guilbaud1997} a effectué une recherche bibliographique des utilisations de la méthode en prévision à long terme et a identifié des applications opérationnelles pour des prévisions mensuelles dans de nombreux pays, notamment au Canada \citep{Shabbar1986}, en Hongrie \citep{Toth1989}, aux Pays-Bas \citep{Nap1981}, et en Angleterre \citep{Murray1974}, ainsi que des prévisions saisonnières : \citet{Barnett1978}, \citet{Bergen1982} et \citet{Livezey1988}.
+
+%L'utilisation de la méthode des analogues en tant que technique d'adaptation de modèles climatiques fait l'objet d'un nombre croissant d'études \citep{Zorita1999,Wetterhall2005,Matulla2008}.
+\citet{Wetterhall2007} ont également utilisé la méthode des analogues en Suède, dans le cadre d'une étude sur le réchauffement climatique, et la trouvent simple, mais moins performante que d'autres méthodes plus complexes.
+Cependant, ils n'utilisent que la pression au niveau de la mer en tant que prédicteur, et considèrent uniquement la meilleure analogue.
+Ces deux aspects ne sont clairement pas optimaux, et une qualité médiocre de la méthode n'est alors pas surprenante.
+L'implémentation actuelle de la méthode (voir section \ref{sec:etat_art:implementation_actuelle}) fournit clairement des résultats plus pertinents.
+
+%Une version de la méthode a été évaluée dans le projet STARDEX \citep[\textit{STAtistical and Regional dynamical Downscaling of EXtremes for European regions}, voir][]{Goodess2003, Stardex2005}.
+Un des objectifs du projet étant de comparer différentes méthodes de descente d'échelle pour la détermination des extrêmes météorologiques, la méthode des analogues a été mise en concurrence avec d'autres techniques et a été sélectionnée parmi les plus intéressantes \citep{Maheras2005, Schmidli2007}.
+
+%\citet{GibergansBaguena2007} ont implémenté la méthode pour des prévisions de précipitations journalières en Catalogne.
+Ils ont considéré le géopotentiel à 700 et 1000~hPa, ainsi que l'épaisseur entre ces deux niveaux pour la recherche d'analogie de circulation, puis ont appliqué une seconde sélection sur la base de données locales obtenues par radiosondage: indices de stabilité, eau précipitable, température, etc...
+
+%\citet{Hamill2006} ont utilisé une approche par analogie sur les reprévisions du modèle global des États-Unis (GFS, voir sections \ref{sec:donnees:previsions_GFS} et \ref{sec:donnees:resimulations_GFS}).
+Cette application a permis de corriger des erreurs systématiques dans les prévisions d'ensemble des températures et des précipitations.
+En effet, l'approche statistique a mis en évidence certains biais dans les prévisions du modèle numérique, qui ont pu être ajustés par la prise en compte de la climatologie locale intrinsèque à la méthode des analogues.
+De plus, la dispersion des analogues étant plus importante que celle des prévisions d'ensemble, la sous-dispersion de ces dernières a pu être corrigée à l'aide des analogues \citep{Hamill2006}.
+Une des raisons invoquées pour la bonne performance de la méthode des analogues par rapport au modèle numérique global est le fait que ce dernier a une orographie lissée, qui ne tient pas compte des réelles spécificités locales, ce que permet l'approche par analogie.
+
+%La méthode présente cependant des limites dont il faut être conscient.
+La première est la nécessité de disposer d'une archive conséquente de la variable cible à un pas de temps pertinent, ici les précipitations.
+Sans une base de données de prédictands de plusieurs décennies, la méthode n'est pas applicable.
+
+%Les archives des prédicteurs sont également importantes et plus particulièrement leur homogénéité.
+Nous disposons actuellement de jeux de données de réanalyses (voir section \ref{sec:donnees:reanalyses1_ncep}) de bonne qualité, mais contenant tout de même des discontinuités significatives dues à la densification des réseaux de mesures et au déploiement de nouvelles techniques de mesure et de l'imagerie satellitaire.
+Nous ne pourrons a priori jamais complètement éliminer cette hétérogénéité, car les données demeureront manquantes.
+Toutefois, la qualité de ces données les rend tout à fait utilisables pour la méthode des analogues, et ceci partout sur le globe !
+
+%Un aspect supplémentaire concerne les différences entre les prédicteurs disponibles en temps réel et les archives de ces prédicteurs.
+En effet, les deux jeux de données n'ont généralement pas la même climatologie, car ils ne résultent pas du même modèle, et n'ont pas été élaborés de la même manière.
+Il existe des alternatives, telles que l'utilisation en opérationnel de prévisions émises par un modèle figé, conjointement à des archives élaborées par ce même modèle en reprévision.
+
+%Toutefois, les prévisions que nous utiliserions de cette manière ne seraient pas à l'état de l'art, et les reprévisions (archives) contiendraient des erreurs et des incertitudes beaucoup plus importantes que des réanalyses.
+Il convient donc d'utiliser des prédicteurs robustes qui dépendent au minimum des spécificités du modèle numérique.
+
+%Une autre limite réside dans le fait que les événements extrêmes peuvent être sous-représentés dans l'échantillon d'analogues considéré.
+En effet, dans une archive météorologique d'une durée limitée, les événements correspondants à des temps de retour élevés ne sont pas très nombreux.
+Leur représentation est certainement inférieure au nombre d'analogues que nous retenons, ce qui peut biaiser la prévision.
+
+%Enfin, \citet{Bliefernicht2007} ont montré que les prévisions sont moins bonnes en été.
+Ceci est dû à la part plus importante de la convection durant les mois chauds.
+Les variables de la circulation synoptique ne sont en effet pas à même de prévoir la localisation des cellules orageuses.
+Ceci a également été constaté par \citet{BenDaoud2010}, qui avait mis en place un modèle spécifique pour les mois d'été (du 15 juin au 15 septembre).
+Nous pouvons estimer que les prédicteurs sont à reconsidérer (variables, niveaux, etc.), et que leur domaine peut être différent.
+Le problème est que, durant cette période, on peut également rencontrer situations classiques avec une circulation atmosphérique dominante comme dans les autres saisons, ou des situations de marais barométriques accompagnées d'un fort risque de convection locale, sans signature dans les variables synoptiques.
 

### 2015-10-15 AtmoSwing - Geoscientific Model Development/template.tex
Addition of the nomenclature.

@@
 
-\subsection{Its evolution}
+\subsection{Evolution of the method}
 \label{sec:method:evolution}
@@
 
-\subsection{References implementations for precipitation forecasting}
+\subsection{Proposed nomenclature}
+
+Variants of the analogue method parameterization are numerous and it is not always easy to reference them in a short and descriptive way.
+We thus propose a basic nomenclature (Figure \ref{figure:nomenclature}) in order to give an idea of the structure in a simple identifier.
+This one cannot describe all the parameters of the method, but quickly illustrate the structure of the implementation.
+This is particularly useful when working with a global optimization method, where nothing is fixed but the very structure of the method.
+
+\begin{figure}[htbp]
+	\includegraphics[width=8.3cm]{figures/nomenclature.pdf}
+	\caption{Proposed structure for naming the parameterizations of the analogue method.}
+	\label{figure:nomenclature}
+\end{figure}
+
+The naming contains different blocs (separated by an hyphen) for the various levels of analogy.
+It starts with the specification of the preselection (P; can be omitted when comparing methods with the same preselection approaches), which can be nowadays of 2 types:
+\begin{itemize}
+	\setlength\itemsep{-2px}
+	\item C: calendar period ($\pm 60$ days around the target date)
+	\item T: based on air temperature \citep{BenDaoud2010}
+\end{itemize}
+
+Then, the following levels of analogy are listed.
+They may start with an optional A (for analogy) when other methods are mixed into the parameterization \citep[see eg.
+][]{Chardon2014}.
+For every level of analogy, we first provide the number of variables used (combination of atmospheric levels and time of observation) and then give the short name of the variable (according eg to ECMWF conventions; in upper case), for example:
+\begin{itemize}
+	\setlength\itemsep{-2px}
+	\item Z : geopotential (circulation)
+	\item HI : humidity index (TPW * RH)
+	\item HF : humidity flux (V * TPW * RH)
+	\item TPW : total precipitable water
+	\item V : wind velocity
+	\item W : vertical velocity
+\end{itemize}
+
+In order to keep the identifier simple, no value of atmospheric level neither time of observation is specified.
+Moreover, the analogy criterion is not specified and is supposed to be S1 for Z and RMSE for the other variables.
+If anything changes from these conventions, it can be noted as a flag.
+The flag (lower case) can also give other information, such as the optimization method:
+\begin{itemize}
+	\setlength\itemsep{-2px}
+	\item cc : classic calibration (can be omitted as considered as default, see section \ref{sec:classic})
+	\item go : global optimization (by means of genetic algorithms for example, see section \ref{sec:gas})
+\end{itemize}
+
+This nomenclature can be adapted to specific needs, or simplified for a better readability (eg. by removing the specification of the preselection). Examples are provided in the following section.
+
+\subsection{References for precipitation forecasting}
 
@@
 
-%\subsection{R0, les origines}
-%\label{sec:etat_art:R0}
-
-%Une référence préliminaire résulte des travaux de \citet{Guilbaud1997} et \citet{Obled2002}.
-Elle est constituée d'un seul niveau d'analogie sur la circulation atmosphérique considérée à 1000~hPa et 700~hPa (R0a, Table \ref{table:R0a}) ou 500~hPa (R0b, Table \ref{table:R0b}).
-Le critère S1 de Teweles-Wobus est alors utilisé pour comparer les champs de géopotentiel.
+The first parameterization comes from the work of \citet{Guilbaud1997} and \citet{Obled2002}.
+It consists of a single level of analogy on the atmospheric circulation.
+The score S1 (Teweles-Wobus, Eq.
+\ref{eq:S1}) is processed on the geopotential height at 1000~hPa (Z1000) and 700~hPa (Z700) (Table \ref{table:R0a}) or 500~hPa (Z500) (Table \ref{table:R0b}), both at 00~h and 24~h.
+The number of analogues considered is 50.
 
 \begin{table}[htbp]
-	\caption{R0a.}
-	\begin{center}
+	\caption{Method of type PC-4Z proposed by \citep{Guilbaud1997}.}
 	\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-			\hline
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline
 		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-			\hline 
+		\middlehline 
 		\multirow{2}{*}{1} & Z700 & 00, 24~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
 		& Z1000 & 00, 24~h & & \\ 
-			\hline 
+		\bottomhline 
 	\end{tabular} 
-	\end{center}
 	\label{table:R0a}
@@
 \begin{table}[htbp]
-	\caption{R0b.}
-	\begin{center}
+	\caption{Variant of the PC-4Z method proposed by \citep{Guilbaud1997}.}
 	\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-			\hline 
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline 
 		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-			\hline 
+		\middlehline 
 		\multirow{2}{*}{1} & Z500 & 00, 24~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
 		& Z1000 & 00, 24~h & & \\ 
-			\hline 
+		\bottomhline 
 	\end{tabular} 
-	\end{center}
 	\label{table:R0b}
@@
 \begin{table}[htbp]
-	\caption{R1.}
-	\begin{center}
+	\caption{Method of type PC-2Z proposed by \citep{Bontron2004}.}
 	\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-			\hline 
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline 
 		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-			\hline 
+		\middlehline 
 		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
 		& Z500 & 24~h & & \\ 
-			\hline 
+		\bottomhline 
 	\end{tabular} 
-	\end{center}
 	\label{table:R1}
@@
 \begin{table}[htbp]
-	\caption{R2.}
-	\begin{center}
+	\caption{Method of type PC-2Z-2HI proposed by \citep{Bontron2004}.}
 	\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-			\hline 
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline 
 		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-			\hline 
+		\middlehline 
 		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
 		& Z500 & 24~h & & \\ 
-			\hline
+		\middlehline
 		2 & TPW * RH850 & 12, 24~h & RMSE & 30 \\
-			\hline 
+		\bottomhline 
 	\end{tabular} 
-	\end{center}
 	\label{table:R2}
@@
 \begin{table}[htbp]
-	\caption{R3a.}
-	\begin{center}
+	\caption{Method of type PC-2Z-2HI proposed by \citep{Marty2010}.}
 	\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-			\hline 
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline 
 		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-			\hline 
+		\middlehline 
 		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{75} \\
 		& Z500 & 18~h & & \\ 
-			\hline
+		\middlehline
 		2 & TPW * RH925 & 06, 18~h & RMSE & 30 \\
-			\hline 
+		\bottomhline 
 	\end{tabular} 
-	\end{center}
 	\label{table:R3a}
@@
 \begin{table}[htbp]
-	\caption{R3b.}
-	\begin{center}
+	\caption{Method of type PC-2Z-2HF proposed by \citep{Marty2010}.}
 	\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-			\hline 
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline 
 		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-			\hline 
+		\middlehline 
 		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{60} \\
 		& Z 500~hPa & 18~h & & \\ 
-			\hline
+		\middlehline
 		2 & V700 * TPW * RH700 & 06, 18~h & RMSE & 25 \\
-			\hline 
+		\bottomhline 
 	\end{tabular} 
-	\end{center}
 	\label{table:R3b}
@@
 \begin{table}[htbp]
-	\caption{R3c.}
-	\begin{center}
+	\caption{Method of type PC-2Z-2HF proposed by \citep{Marty2010}.}
 	\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-			\hline 
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline 
 		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-			\hline 
+		\middlehline 
 		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{60} \\
 		& Z 500~hPa & 18~h & & \\ 
-			\hline
+		\middlehline
 		2 & V925 * TPW * RH925 & 06, 18~h & RMSE & 25 \\
-			\hline 
+		\bottomhline 
 	\end{tabular} 
-	\end{center}
 	\label{table:R3c}
@@
 \begin{table}[htbp]
-	\caption{R4a.}
-	\begin{center}
+	\caption{Method of type P2T-2Z-2HI proposed by \citep{BenDaoud2010}.}
 	\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-			\hline
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline
 		\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
 		& T600 & 12~h & & \\ 
-			\hline 
+		\middlehline 
 		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
 		& Z 500~hPa & 24~h & & \\ 
-			\hline
+		\middlehline
 		2 & TPW * RH850 & 12, 24~h & RMSE & 25 \\
-			\hline 
+		\bottomhline 
 	\end{tabular} 
-	\end{center}
 	\label{table:R4a}
@@
 \begin{table}[htbp]
-	\caption{R4b.}
-	\begin{center}
+	\caption{Method of type P2T-2Z-4HI proposed by \citep{BenDaoud2010}.}
 	\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-			\hline
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline
 		\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
 		& T600 & 12~h & & \\ 
-			\hline 
+		\middlehline 
 		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
 		& Z 500~hPa & 24~h & & \\ 
-			\hline
+		\middlehline
 		\multirow{2}{*}{2} & TPW * RH925 & 12, 24~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
 		& TPW * RH700 & 12, 24~h & & \\ 
-			\hline 
+		\bottomhline 
 	\end{tabular} 
-	\end{center}
 	\label{table:R4b}
@@
 \begin{table}[htbp]
-	\caption{R4c.}
-	\begin{center}
+	\caption{Method of type P2T-2Z-10HI proposed by \citep{BenDaoud2010}.}
 	\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-			\hline
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline
 		\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
 		& T600 & 12~h & & \\ 
-			\hline 
+		\middlehline 
 		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
 		& Z 500~hPa & 24~h & & \\ 
-			\hline
+		\middlehline
 		\multirow{2}{*}{2} & TPW * RH925 & 06-30~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
 		& TPW * RH700 & 06-30~h & & \\ 
-			\hline 
+		\bottomhline 
 	\end{tabular} 
-	\end{center}
 	\label{table:R4c}
@@
 \begin{table}[htbp]
-	\caption{R5a.}
-	\begin{center}
+	\caption{Method of type P2T-2Z-4W-2HI proposed by \citep{BenDaoud2010}.}
 	\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-			\hline
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline
 		\multirow{2}{*}{0} & T925 (1 point) & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
 		& T600 (1 point) & 12~h & & \\ 
-			\hline 
+		\middlehline 
 		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{170} \\
 		& Z 500~hPa & 24~h & & \\ 
-			\hline
+		\middlehline
 		2 & W850 & 06-24~h & RMSE & 70 \\
-			\hline
+		\middlehline
 		3 & TPW * RH850 & 12, 24~h & RMSE & 25 \\
-			\hline 
+		\bottomhline 
 	\end{tabular} 
-	\end{center}
 	\label{table:R5a}
@@
 \begin{table}[htbp]
-	\caption{R5b.}
-	\begin{center}
+	\caption{Method of type P2T-2Z-4W-4HI proposed by \citep{BenDaoud2010}.}
 	\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-			\hline
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline
 		\multirow{2}{*}{0} & T925 (1 point) & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
 		& T600 (1 point) & 12~h & & \\ 
-			\hline 
+		\middlehline 
 		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{170} \\
 		& Z 500~hPa & 24~h & & \\ 
-			\hline
+		\middlehline
 		2 & W850 & 06-24~h & RMSE & 70 \\
-			\hline
+		\middlehline
 		\multirow{2}{*}{3} & TPW * RH925 & 12, 24~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
 		& TPW * RH700 & 12, 24~h & & \\
-			\hline 
+		\bottomhline 
 	\end{tabular}
-	\end{center}
 	\label{table:R5b}
+\end{table}
+
+\begin{table}[htbp]
+	\caption{Method of type PC-4Zo proposed by \citep{Horton2012}.}
+	\begin{tabular}{ccccc}
+
+	\end{tabular}
+	\label{table:R6a}
+\end{table}
+
+\begin{table}[htbp]
+	\caption{Method of type PC-4Zo-2HIo proposed by \citep{Horton2012}.}
+	\begin{tabular}{ccccc}
+
+	\end{tabular}
+	\label{table:R6b}
 \end{table}
@@
 \subsection{The classic calibration approach}
+\label{sec:classic}
 
@@
 \section{The global optimization tools}
+\label{sec:gas}
 

### 2015-10-15 AtmoSwing - Geoscientific Model Development/template.tex
Changing humidity to moisture.

@@
 
-\citet{Mandon1985} introduced a second level of analogy and assessed different variables, such as wind, humidity, air temperature, surface temperature of the Mediterranean, the product of wind and the 700~hPa moisture, as well as a second barometric criteria differentiated according to the season.
+\citet{Mandon1985} introduced a second level of analogy and assessed different variables, such as wind, moisture, air temperature, surface temperature of the Mediterranean, the product of wind and the 700~hPa moisture, as well as a second barometric criteria differentiated according to the season.
 \citet{Vallee1986} continued to work on the second level of analogy and considered the wind at 700~hPa \& 12~h in order to improve heavy precipitation events for a region in France susceptible to southerly flows.
@@
 When using multiple predictors, they combined the criteria values calculated on each atmospheric level and each temporal window using an arithmetic mean.
-Finally, they also suggested using a second level of analogy on lower layers humidity and introduced the Ranked Probability Score \citep{Epstein1969} to assess the forecast quality, which was found to be more relevant that the Brier score \citep{Brier1950}.
+Finally, they also suggested using a second level of analogy on lower layers moisture and introduced the Ranked Probability Score \citep{Epstein1969} to assess the forecast quality, which was found to be more relevant that the Brier score \citep{Brier1950}.
 
@@
 
-He also assessed several variables for the second level of analogy and identified the humidity variables (precipitable water and relative humidity) and vertical velocity to be the most relevant.
+He also assessed several variables for the second level of analogy and identified the moisture variables (precipitable water and relative humidity) and vertical velocity to be the most relevant.
 Finally, he found that the product of relative humidity and precipitable water gave the best performance.
@@
 The seasonal effect is indeed also present in the temperature data.
-The vertical velocity was used as an additional level of analogy, between the analogy of atmospheric circulation and the one on humidity, to account for fronts.
-Finally, he selected the humidity variables at 700~hPa instead of 850~Pa.
+The vertical velocity was used as an additional level of analogy, between the analogy of atmospheric circulation and the one on moisture, to account for fronts.
+Finally, he selected the moisture variables at 700~hPa instead of 850~Pa.
 
@@
 Other classic criteria represent absolute distances: Mean Absolute Error (MAE) and Root Mean Squared Error (RMSE), the latest being most often used.
-These are more relevant to compare humidity variables for example.
+These are more relevant to compare moisture variables for example.
 
@@
 	\item Z : geopotential (circulation)
-	\item HI : humidity index (TPW * RH)
-	\item HF : humidity flux (V * TPW * RH)
+	\item MI : moisture index (TPW * RH)
+	\item MF : moisture flux (V * TPW * RH)
 	\item TPW : total precipitable water
@@
 \begin{table}[htbp]
-	\caption{Method of type PC-4Z proposed by \citep{Guilbaud1997}.}
+	\caption{Method of type PC-4Z proposed by \citet{Guilbaud1997}.}
 	\begin{tabular}{ccccc}
@@
 \begin{table}[htbp]
-	\caption{Variant of the PC-4Z method proposed by \citep{Guilbaud1997}.}
+	\caption{Variant of the PC-4Z method, by \citet{Guilbaud1997}.}
 	\begin{tabular}{ccccc}
@@
 
-%\subsection{R1, analogie de circulation}
-%\label{sec:etat_art:R1}
-%\review{6}
-
-%Ce que nous considérerons comme notre première référence est l'analogie de circulation (R1, Table \ref{table:R1}) optimisée par \citet{Bontron2004}.
-Ce dernier a observé que le choix de l'heure était plus important que celui du niveau atmosphérique.
-La méthode est alors constituée du géopotentiel à deux niveaux atmosphériques et à des heures différentes.
+The analogy on the atmospheric circulation (Table \ref{table:R1}) proposed by \citet{Bontron2004} is still, at the time of writing, often used, and considered as a reference for benchmarking new parameterizations.
+He noticed that the choice of the temporal window was more important than the atmospheric level.
+The method consists of the geopotential height on two atmospheric levels : 1000~hPa (Z1000) at 12~h and 500~hPa (Z700) at 24~h.
 
 \begin{table}[htbp]
-	\caption{Method of type PC-2Z proposed by \citep{Bontron2004}.}
+	\caption{Method of type PC-2Z proposed by \citet{Bontron2004}.}
 	\begin{tabular}{ccccc}
@@
 
-%\subsection{R2, prise en compte de l'humidité}
-%\label{sec:etat_art:R2}
-%\review{6}
-
-%Toujours d'après les travaux de \citet{Bontron2004}, la référence suivante (R2, Table \ref{table:R2}) intègre un second niveau d'analogie sur un indice d'humidité: le produit de l'humidité relative à 850~hPa et de l'eau précipitable de la colonne.
-Cette variable ne représente pas une grandeur physique réelle, mais exprime le contenu en eau de la colonne et sa proximité ou son éloignement de la saturation (à 850~hPa).
+\citep{Bontron2004} then added a second level of analogy (Table \ref{table:R2}) on a moisture index : the product of relative humidity at 850~hPa (RH850) and total precipitable water (TPW).
+This index does not represent an actual physical quantity, but expresses the water content of the column and its proximity to saturation.
 
 \begin{table}[htbp]
-	\caption{Method of type PC-2Z-2HI proposed by \citep{Bontron2004}.}
+	\caption{Method of type PC-2Z-2HI proposed by \citet{Bontron2004}.}
 	\begin{tabular}{ccccc}
@@
 
-%\subsection{R3, prise en compte du flux d'humidité}
-%\label{sec:etat_art:R3}
+\citet{Marty2010} tested other temporal windows for intraday application on the basis of a more comprehensive reanalysis dataset.
+He first proposed to change the hours of observation for both levels of analogy (both for 06~h and 18~h), and selected the 925~hPa level for the moisture analogy (Table \ref{table:R3a}).
+
+He proposed two models with a second level of analogy moisture (3a, Table \ ref {table: R3a}) or the moisture flux at ~ 700 hPa (3b, Table \ ref {table: 3b} ) or ~ 925 hPa (3c, Table \ ref {table: 3c}).
+The hours and levels change from those established by \ citet Bontron2004 {}, because they were not available then.
 
@@
 \begin{table}[htbp]
-	\caption{Method of type PC-2Z-2HI proposed by \citep{Marty2010}.}
+	\caption{Method of type PC-2Z-2HI proposed by \citet{Marty2010}.}
 	\begin{tabular}{ccccc}
@@
 
+Then, \citet{Marty2010} changed the humi
+
 \begin{table}[htbp]
-	\caption{Method of type PC-2Z-2HF proposed by \citep{Marty2010}.}
+	\caption{Method of type PC-2Z-2HF proposed by \citet{Marty2010}.}
 	\begin{tabular}{ccccc}
@@
 \begin{table}[htbp]
-	\caption{Method of type PC-2Z-2HF proposed by \citep{Marty2010}.}
+	\caption{Method of type PC-2Z-2HF proposed by \citet{Marty2010}.}
 	\begin{tabular}{ccccc}
@@
 \begin{table}[htbp]
-	\caption{Method of type P2T-2Z-2HI proposed by \citep{BenDaoud2010}.}
+	\caption{Method of type P2T-2Z-2HI proposed by \citet{BenDaoud2010}.}
 	\begin{tabular}{ccccc}
@@
 \begin{table}[htbp]
-	\caption{Method of type P2T-2Z-4HI proposed by \citep{BenDaoud2010}.}
+	\caption{Method of type P2T-2Z-4HI proposed by \citet{BenDaoud2010}.}
 	\begin{tabular}{ccccc}
@@
 \begin{table}[htbp]
-	\caption{Method of type P2T-2Z-10HI proposed by \citep{BenDaoud2010}.}
+	\caption{Method of type P2T-2Z-10HI proposed by \citet{BenDaoud2010}.}
 	\begin{tabular}{ccccc}
@@
 \begin{table}[htbp]
-	\caption{Method of type P2T-2Z-4W-2HI proposed by \citep{BenDaoud2010}.}
+	\caption{Method of type P2T-2Z-4W-2HI proposed by \citet{BenDaoud2010}.}
 	\begin{tabular}{ccccc}
@@
 \begin{table}[htbp]
-	\caption{Method of type P2T-2Z-4W-4HI proposed by \citep{BenDaoud2010}.}
+	\caption{Method of type P2T-2Z-4W-4HI proposed by \citet{BenDaoud2010}.}
 	\begin{tabular}{ccccc}
@@
 \begin{table}[htbp]
-	\caption{Method of type PC-4Zo proposed by \citep{Horton2012}.}
+	\caption{Method of type PC-4Zgo proposed by \citet{Horton2012}.}
 	\begin{tabular}{ccccc}
@@
 \begin{table}[htbp]
-	\caption{Method of type PC-4Zo-2HIo proposed by \citep{Horton2012}.}
+	\caption{Method of type PC-4Zgo-2HIgo proposed by \citet{Horton2012}.}
 	\begin{tabular}{ccccc}
@@
 It determines the optimal parameters for the different variables of each level of analogy.
-The analogy levels (eg the atmospheric circulation or humidity index) are calibrated sequentially.
+The analogy levels (eg the atmospheric circulation or moisture index) are calibrated sequentially.
 The procedure consists of the following steps \citep{Bontron2004}:
@@
 	\begin{enumerate}
-		\item Identification of the most skilled unitary cell (1 point for humidity variables and 4 for the geopotential height when using the S1 criteria) over a large domain.
+		\item Identification of the most skilled unitary cell (1 point for moisture variables and 4 for the geopotential height when using the S1 criteria) over a large domain.
 Every point (or cell) of the full domain is assessed jointly on all predictors of the level of analogy (consisting generally of the same variable, but on different pressure levels and at different hours).
@@
 		\item The number of analogues is optimized for the current level of analogy.
-		\item A new level of analogy can be added, based on other variables (such as the humidity index) on predefined pressure levels and time frames.
+		\item A new level of analogy can be added, based on other variables (such as the moisture index) on predefined pressure levels and time frames.
 The number of analogues for the next level of analogy is initiated at a chosen value.
@@
 
-Other constraints exist in between the parameters, such as the temporal window of the humidity index that has to be consistent in between the relative humidity and the precipitable water.
+Other constraints exist in between the parameters, such as the temporal window of the moisture index that has to be consistent in between the relative humidity and the precipitable water.
 Another example is the weighting of the different pressure levels which has to be normalized.
@@
 
-	$N\approx500$ for significantly more complex methods (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the humidity analogy),
+	$N\approx500$ for significantly more complex methods (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the moisture analogy),
 

### 2015-10-15 Optimization - Journal of Climate/template.tex
Changing humidity to moisture.

@@
 Multiple variations of the methods exist, and some aspects and parameters will not be detailed hereafter.
-There are mainly 2 parametrizations that are used most often: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on humidity variables \citep{Obled2002, Bontron2005, Marty2012}.
+There are mainly 2 parametrizations that are used most often: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
 
@@
 
-The other most know parametrization adds a second level of analogy on humidity variables (Table \ref{table:params_R2}).
-The predictor that \citet{Bontron2004} found optimal for the France territory is a humidity index made of the product of the precipitable water with the relative humidity at 850~hPa.
+The other most know parametrization adds a second level of analogy on moisture variables (Table \ref{table:params_R2}).
+The predictor that \citet{Bontron2004} found optimal for the France territory is a moisture index made of the product of the precipitable water with the relative humidity at 850~hPa.
 \cite{Horton2012a} confirmed that this index is better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis considered independently.
@@
 We observed during the calibration of the analogue method that the resulting parameters vary with the initial choices (such as the number of analogues).
-In addition, the different levels of analogy (eg on the atmospheric circulation and the humidity index) are always calibrated sequentially.
+In addition, the different levels of analogy (eg on the atmospheric circulation and the moisture index) are always calibrated sequentially.
 However, we can not exclude any dependency between them, which could lead us to select another parametrization if we calibrate them together.
@@
 
-We first optimized the analogy of atmospheric circulation alone, without humidity variables, for our 10 subregions.
+We first optimized the analogy of atmospheric circulation alone, without moisture variables, for our 10 subregions.
 We started from the most simple analogue method, and increased the complexity in order to identify the degrees of freedom that are of particular interest.
@@
 
-\section{Optimization of the analogy with humidity variables}
+\section{Optimization of the analogy with moisture variables}
 
 We previously worked with a method based on a unique level of analogy.
-However, we know that humidity variables in a second level of analogy do provide improvements to the method (section \ref{section_intro}.\ref{section_analog_method}).
-So we also wanted to optimize the humidity index, which is a combination of the relative humidity and the precipitable water.
+However, we know that moisture variables in a second level of analogy do provide improvements to the method (section \ref{section_intro}.\ref{section_analog_method}).
+So we also wanted to optimize the moisture index, which is a combination of the relative humidity and the precipitable water.
 In order to do so, we had to introduce a constraint to the optimizer, so that it selects the same temporal window for both variables.
 
-Two methods were assessed: one with 2 humidity predictors (humidity index on 2 pressure levels or at 2 different hours) named z4-hi2, and one with 4 humidity predictors named z4-hi4.
-When we introduce 2 predictors for the humidity analogy, the number of degrees of freedom raises to 42, and to 54 when we add 4 predictors.
-
-We proceeded to an optimization of both levels of analogy simultaneously. This implies that the analogy of the atmospheric circulation may change due to the new humidity information.
+Two methods were assessed: one with 2 moisture predictors (moisture index on 2 pressure levels or at 2 different hours) named z4-hi2, and one with 4 moisture predictors named z4-hi4.
+When we introduce 2 predictors for the moisture analogy, the number of degrees of freedom raises to 42, and to 54 when we add 4 predictors.
+
+We proceeded to an optimization of both levels of analogy simultaneously. This implies that the analogy of the atmospheric circulation may change due to the new moisture information.
 
@@
 Detailed examples are still provided for the Swiss Chablais subregion in Table \ref{table:params_GA_z4_hi2} for z4-hi2 and in Table \ref{table:params_GA_z4_hi4} for z4-hi4.
-The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_z4-hi2} for z4-hi2, along with the selected pressure levels for the circulation analogy (Table \ref{table:levels_GA_z4_hi2}) and the humidity analogy (Table \ref{table:levels_GA_z4_hi2_H}).
+The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_z4-hi2} for z4-hi2, along with the selected pressure levels for the circulation analogy (Table \ref{table:levels_GA_z4_hi2}) and the moisture analogy (Table \ref{table:levels_GA_z4_hi2_H}).
 Correspondingly, for the method z4-hi4, the spatial windows are shown in Figure \ref{fig:spatial_windows_z4-hi4} and the selected pressure levels are presented in Tables \ref{table:levels_GA_z4_hi4} and \ref{table:levels_GA_z4_hi4_H}.
@@
 The CRPSS scores of the optimized methods are provided in Table \ref{table:scores} and amounts to slightly more than 40 \% for both methods and for both periods.
-This results in a relative improvements that ranges from 11.5 \% to 15.6 \% compared to the reference method on the humidity analogy (Table \ref{table:scores_diff}).
+This results in a relative improvements that ranges from 11.5 \% to 15.6 \% compared to the reference method on the moisture analogy (Table \ref{table:scores_diff}).
 As for z4, the z4-hi2 and z4-hi4 methods present improvements of the forecast of significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
@@
 
-The parameters cross-compatibility has also been assessed for the methods with humidity variables, and are shown in Tables \ref{table:crossing_z4-hi2_calib} and \ref{table:crossing_z4-hi2_valid} for the method z4-hi2, and Tables \ref{table:crossing_z4-hi4_calib} and \ref{table:crossing_z4-hi4_valid} for z4-hi4.
+The parameters cross-compatibility has also been assessed for the methods with moisture variables, and are shown in Tables \ref{table:crossing_z4-hi2_calib} and \ref{table:crossing_z4-hi2_valid} for the method z4-hi2, and Tables \ref{table:crossing_z4-hi4_calib} and \ref{table:crossing_z4-hi4_valid} for z4-hi4.
 
@@
 
-When optimizing a method made of 2 levels of analogy, the introduction of humidity variables in the second level has an influence on the parameter values of the first level.
+When optimizing a method made of 2 levels of analogy, the introduction of moisture variables in the second level has an influence on the parameter values of the first level.
 This is first visible on the selection of the pressure levels for the circulation analogy, where the 1000~hPa that was previously systematically selected twice (Table \ref{table:levels_GA_z4}) is now less chosen (once or even not at all) for both za-hi2 (Table \ref{table:levels_GA_z4_hi2}) and za-hi4 (Table \ref{table:levels_GA_z4_hi4}).
-There is indeed a shift of the previously selected 1000~hPa for higher levels, which is even slightly stronger with 4 humidity predictors than with 2.
-This change is likely due to the fact that when considering only the circulation analogy, the method tries to take into account information that can serve as proxy for humidity assessment, whereas it doesn't need it with the humidity index.
+There is indeed a shift of the previously selected 1000~hPa for higher levels, which is even slightly stronger with 4 moisture predictors than with 2.
+This change is likely due to the fact that when considering only the circulation analogy, the method tries to take into account information that can serve as proxy for moisture assessment, whereas it doesn't need it with the moisture index.
 This aspect has never been demonstrated, as classic calibration tools do not allow it.
@@
 
-The selected pressure levels for the analogy on the humidity index are strongly centred around 700~hPa and 600~hPa.
+The selected pressure levels for the analogy on the moisture index are strongly centred around 700~hPa and 600~hPa.
 No other value has been selected when considering 2 pressure levels (Table \ref{table:levels_GA_z4_hi2_H}), and when considering 4 levels, the 850~hPa and 500~hPa levels are additionally selected.
@@
 The selection of the temporal windows for the atmospheric circulation is similar to the preceding optimization (in the order of increasing pressure: 12~h, 24/30~h, 12~h, 30~h), but sometimes with a bit more variability.
-When it comes to the humidity analogy, there is a clear trend to select 12~h and 24~h when considering 2 predictors.
-The z4-hi4 method presents more variability on the selection of the temporal windows for the humidity index.
+When it comes to the moisture analogy, there is a clear trend to select 12~h and 24~h when considering 2 predictors.
+The z4-hi4 method presents more variability on the selection of the temporal windows for the moisture index.
 
@@
 The very large domains on the upper level of the 4 first subregions are not present anymore, and more variability can be observed.
-The selected points for the analogy on the humidity index are always located nearby the catchment, including at least 1 of the nearest points from the reanalysis dataset, and the spatial windows are relatively small.
-Thus, for our case study, there is no need to look for distant humidity information and the search could be reduced to a smaller domain.
-
-The CRPSS scores were improved by considering the humidity information (Table \ref{table:scores}).
-The optimized methods also perform better than the reference method based on the humidity index (Table \ref{table:scores_diff}).
-However, there is no drastic difference between both z4-hi2 and z4-hi4 methods, which suggests that considering 4 humidity predictors is not absolutely necessary.
+The selected points for the analogy on the moisture index are always located nearby the catchment, including at least 1 of the nearest points from the reanalysis dataset, and the spatial windows are relatively small.
+Thus, for our case study, there is no need to look for distant moisture information and the search could be reduced to a smaller domain.
+
+The CRPSS scores were improved by considering the moisture information (Table \ref{table:scores}).
+The optimized methods also perform better than the reference method based on the moisture index (Table \ref{table:scores_diff}).
+However, there is no drastic difference between both z4-hi2 and z4-hi4 methods, which suggests that considering 4 moisture predictors is not absolutely necessary.
 When it comes to improvements for days with precipitation above our 3 thresholds (P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the forecast, mainly for heavy rainfall.
@@
 The same pattern can be observed, with a drop of performance for the subregions under different meteorological influences.
-However, the losses of performance are globally more important than before, suggesting that more complex methods with humidity variables are less transposable to another subregion, even though it is located within the same grid of the reanalysis dataset.
+However, the losses of performance are globally more important than before, suggesting that more complex methods with moisture variables are less transposable to another subregion, even though it is located within the same grid of the reanalysis dataset.
 
@@
 This may not be the most influencing factor, and we may suggest to remove it first when trying to reduce the number of degrees of freedom.
-	\item The joint optimization of the circulation and humidity analogy levels, that are usually calibrated successively.
+	\item The joint optimization of the circulation and moisture analogy levels, that are usually calibrated successively.
 We have been able to demonstrate that there is a dependency between the analogy levels, and that in order to approach the optimal parameters, we must consider them jointly.
@@
 We tried to optimize the preselection period (the 4-months window) jointly with the other parameters, but we did not get improvement.
-We also tried optimizing the humidity flux, which is composed of the humidity index multiplied with the wind flux.
-However, the results were not better than when we considered the humidity index alone.
+We also tried optimizing the moisture flux, which is composed of the moisture index multiplied with the wind flux.
+However, the results were not better than when we considered the moisture index alone.
 This may be related to the fact that the optimizer tries to provide the best analogy of the atmospheric circulation in the first place, which makes the wind information less relevant in the second level of analogy.
 
-As we could observe, methods with a higher complexity that integrate humidity predictors are less transposable than simpler ones.
+As we could observe, methods with a higher complexity that integrate moisture predictors are less transposable than simpler ones.
 We also noticed in another unpublished work, that it is by far better to optimize for 2 subregions jointly rather than to optimize on one and to apply its parametrization to the other.
@@
 There are clear trends or even identical results for subregions under similar meteorological influences, which confirm that the optimized parameters are coherent, despite an eventual first impression of a great variability in the spatial windows.
-When adding humidity variables, the results show a higher variability, but remains highly acceptable and coherent.
-Indeed, the selection of the pressure level for the humidity index is for example very constant.
+When adding moisture variables, the results show a higher variability, but remains highly acceptable and coherent.
+Indeed, the selection of the pressure level for the moisture index is for example very constant.
 
@@
 
-We were able to identify that there is a parametric dependence between the analogy of circulation and the moisture humidity.
+We were able to identify that there is a parametric dependence between the analogy of circulation and the moisture.
 When we consider the two levels together, the optimal parameters of the analogy of circulation are different.
@@
 	\footnotesize
-	\caption{Parameters of the reference method with humidity variables.}
+	\caption{Parameters of the reference method with moisture variables.}
 	\begin{center}
@@
 For z4, the improvement is relative to the reference method on the atmospheric circulation.
-For z4-hi2 and z4-hi4, the improvement is relative to the reference method on the circulation and humidity variables.}
+For z4-hi2 and z4-hi4, the improvement is relative to the reference method on the circulation and moisture variables.}
 	\begin{center}
@@
 	\footnotesize
-	\caption{Parameters of the z4-hi2 method (atmospheric circulation on 4 levels and humidity index on 2 levels), optimized for the Chablais subregion.
+	\caption{Parameters of the z4-hi2 method (atmospheric circulation on 4 levels and moisture index on 2 levels), optimized for the Chablais subregion.
 Same conventions as Table \ref{table:params_GA_z4}.}
@@
 	\footnotesize
-	\caption{Parameters of the z4-hi4 method (atmospheric circulation on 4 levels and humidity index on 4 levels), optimized for the Chablais subregion.
+	\caption{Parameters of the z4-hi4 method (atmospheric circulation on 4 levels and moisture index on 4 levels), optimized for the Chablais subregion.
 Same conventions as Table \ref{table:params_GA_z4}.}
@@
 	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of humidity of the z4-hi2 method, at the different subregions.}
+	\caption{Atmospheric levels automatically selected for the analogy of moisture of the z4-hi2 method, at the different subregions.}
 	\begin{center}
@@
 	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of humidity of the z4-hi4 method,at the different subregions.}
+	\caption{Atmospheric levels automatically selected for the analogy of moisture of the z4-hi4 method,at the different subregions.}
 	\begin{center}
@@
 	\end{subfigure}
-	\caption{Optimized spatial windows for the z4-hi2 method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the humidity index on 2 pressure levels).
+	\caption{Optimized spatial windows for the z4-hi2 method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 2 pressure levels).
 The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
@@
 	\end{subfigure}
-	\caption{Optimized spatial windows for the z4-hi4 method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the humidity index on 4 pressure levels).
+	\caption{Optimized spatial windows for the z4-hi4 method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 4 pressure levels).
 The pressure levels are ordered by increasing pressure and increasing time for the same levels.}

### 2015-10-15 AtmoSwing - Geoscientific Model Development/template.tex
Removing some method tables and writing data.

@@
 It is also operational at the Compagnie Nationale du Rh\^{o}ne (CNR, France) and some flood forecasting services (SPC) in France and Switzerland \citep{Marty2010,GarciaHernandez2009b,Horton2012}.
+
+\subsection{Data}
+% TODO: write
+
+The analogue method relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series we want to forecast.
+
+Predictors are generally reanalysis datasets (as archive) and outputs of a global numerical weather prediction models for the target situation in operational forecasting.
+Reanalysis datasets, such as the NCEP/NCAR reanalysis I \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996}, the NCEP/DOE reanalysis II \citep{Kanamitsu2002}, ERA-40 \citep{Uppala2005} are often used and can be inputed in AtmoSwing.
+Other observed predictors can also be used, such as Sea Surface Temperature \citep[SST, ][]{Reynolds2007}.
+The predictors describing the target situation in operational forecasting can for example result from GFS \citep[Global Forecast System,][]{Kanamitsu1991,Kanamitsu1989}, which is operated by NCEP and NOAA.
+
+\citet{Bontron2004} determined that the length of the archive should be 30 years to forecast usual situations, and 40 years for intense events.
+He also highlighted the dependence between the optimal number of analogues and the archive size: the shorter the archive, the lower the number of analogues.
+By varying the resolution of the predictors grids, he concluded that the performance increase is not significant for the analogy of atmospheric circulation below a resolution of 5\textdegree.
+However, it seems more important for the second level of analogy on moisture, which are more local variables.
+\citet{BenDaoud2010} assessed the European reanalysis ERA-40 \citep{Uppala2005} with a resolution of 1.125\textdegree.
+He identified a slight performance improvement, but not substantial enough to really justify an archive change \citep{BenDaoud2008}.
+
+The predictand is the local meteorological variable of interest.
+It can be 6-houry data, or more often daily time series, but has to be consistent with the time step of the predictors (at least, not finer).
+The most used predictor is the daily precipitation, usually averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.
+These time series are frequently normalized by the precipitation value for a return period of 10~years \citep{Djerboua2001}.
+This normalization allows for an easier comparison between subregions subject to different precipitation regimes, and thus to better identify the most important contributions.
 
@@
 The score S1 (Teweles-Wobus, Eq.
-\ref{eq:S1}) is processed on the geopotential height at 1000~hPa (Z1000) and 700~hPa (Z700) (Table \ref{table:R0a}) or 500~hPa (Z500) (Table \ref{table:R0b}), both at 00~h and 24~h.
+\ref{eq:S1}) is processed on the geopotential height at 1000~hPa (Z1000) and 700~hPa (Z700) or 500~hPa (Z500) (Table \ref{table:R0}), both at 00~h and 24~h.
 The number of analogues considered is 50.
@@
 		\middlehline 
-		\multirow{2}{*}{1} & Z700 & 00, 24~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
-		& Z1000 & 00, 24~h & & \\ 
+		\multirow{2}{*}{1} & Z1000 & 00, 24~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
+		& Z700 $^{\dagger}$ & 00, 24~h & & \\ 
 		\bottomhline 
 	\end{tabular} 
-	\label{table:R0a}
-\end{table}
-
-\begin{table}[htbp]
-	\caption{Variant of the PC-4Z method, by \citet{Guilbaud1997}.}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline 
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{2}{*}{1} & Z500 & 00, 24~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
-		& Z1000 & 00, 24~h & & \\ 
-		\bottomhline 
-	\end{tabular} 
-	\label{table:R0b}
+	\belowtable{$\dagger$ or Z500 as an alternative}
+	\label{table:R0}
 \end{table}
@@
 \begin{table}[htbp]
-	\caption{Method of type PC-2Z-2HI proposed by \citet{Bontron2004}.}
+	\caption{Method of type PC-2Z-2MI proposed by \citet{Bontron2004}.}
 	\begin{tabular}{ccccc}
@@
 He first proposed to change the hours of observation for both levels of analogy (both for 06~h and 18~h), and selected the 925~hPa level for the moisture analogy (Table \ref{table:R3a}).
-
-He proposed two models with a second level of analogy moisture (3a, Table \ ref {table: R3a}) or the moisture flux at ~ 700 hPa (3b, Table \ ref {table: 3b} ) or ~ 925 hPa (3c, Table \ ref {table: 3c}).
-The hours and levels change from those established by \ citet Bontron2004 {}, because they were not available then.
-
-%\citet{Marty2010} a recalibré les paramètres déterminés par \citet{Bontron2004} pour une application infrajournalière (résolution temporelle de 12~h), et sur la base d'un jeu de données de réanalyses plus complet.
-Il a proposé deux modèles avec un second niveau d'analogie sur l'humidité (R3a, Table \ref{table:R3a}) ou le flux d'humidité au niveau 700~hPa (R3b, Table \ref{table:R3b}) ou 925~hPa (R3c, Table \ref{table:R3c}).
-Les heures et les niveaux changent par rapport à ceux établis par \citet{Bontron2004}, car ceux-ci n'étaient alors pas disponibles.
+The selected hours and atmospheric levels were not available before.
 
 \begin{table}[htbp]
-	\caption{Method of type PC-2Z-2HI proposed by \citet{Marty2010}.}
+	\caption{Method of type PC-2Z-2MI proposed by \citet{Marty2010}.}
 	\begin{tabular}{ccccc}
@@
 
-Then, \citet{Marty2010} changed the humi
+Then, \citet{Marty2010} changed the moisture index into the moisture flux by adding the wind velocity (V700 or V925) component in the multiplication.
+He considered this flux at 700~hPa or 925~hPa (Table \ref{table:R3b}).
 
 \begin{table}[htbp]
-	\caption{Method of type PC-2Z-2HF proposed by \citet{Marty2010}.}
+	\caption{Method of type PC-2Z-2MF proposed by \citet{Marty2010}.}
 	\begin{tabular}{ccccc}
@@
 		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{60} \\
-		& Z 500~hPa & 18~h & & \\ 
-		\middlehline
-		2 & V700 * TPW * RH700 & 06, 18~h & RMSE & 25 \\
+		& Z500 & 18~h & & \\ 
+		\middlehline
+		2 & V700 * TPW * RH700 $^{\dagger}$ & 06, 18~h & RMSE & 25 \\
 		\bottomhline 
 	\end{tabular} 
+	\belowtable{$\dagger$ or V925 * TPW * RH925 as an alternative}
 	\label{table:R3b}
@@
 
+The next reference method was developed by \citet{BenDaoud2010} and introduces a change in the preselection.
+The calendar selection ($\pm 60$ days around the target date) was then replaced by a preselection based on air temperature at 925~hPa (36~h) and 600~hPa (12h).
+The number of preselected dates is equivalent to the number of days we would have chosen with the calendar approach, and thus depends on the archive size: $N_{0} = 60 \cdot 2 \cdot n_{a}$ where $n_{a}$ is the number of years in the calibration period.
+This analogy on air temperature is performed at the closest point to the catchment
+
+\citet{BenDaoud2010} also reconsidered the parameters of the moisture index and ended up with both 925~hPa and 700~hPa levels, at 12~h and 24~h, or at every time step (6~h) between 06~h and 30~h (Table \ref{table:R4b}).
+
 \begin{table}[htbp]
-	\caption{Method of type PC-2Z-2HF proposed by \citet{Marty2010}.}
+	\caption{Method of type P2T-2Z-4MI (or P2T-2Z-10MI for the alternative version), by \citet{BenDaoud2010}.}
 	\begin{tabular}{ccccc}
@@
 		\middlehline
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{60} \\
-		& Z 500~hPa & 18~h & & \\ 
-		\middlehline
-		2 & V925 * TPW * RH925 & 06, 18~h & RMSE & 25 \\
+		\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
+		& T600 & 12~h & & \\ 
+		\middlehline 
+		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
+		& Z500 & 24~h & & \\ 
+		\middlehline
+		\multirow{2}{*}{2} & TPW * RH925 & 12, 24~h $^{\dagger}$ & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
+		& TPW * RH700 & 12, 24~h $^{\dagger}$ & & \\ 
 		\bottomhline 
 	\end{tabular} 
-	\label{table:R3c}
+	\belowtable{$\dagger$ or 06-30~h as an alternative}
+	\label{table:R4b}
 \end{table}
 
-%Le flux d'humidité est composé du produit de l'eau précipitable et de l'humidité relative, multiplié par la norme de la vitesse du vent ($V$).
-
-%\subsection{R4, présélection sur les températures}
-%\label{sec:etat_art:R4}
-%\review{6}
-
-%La quatrième référence reconsidère la sélection des journées candidates à l'analogie et utilise la présélection sur les températures introduite par \citet{BenDaoud2010}.
-Nous nous affranchissons donc de la sélection d'une période de 4 mois centrée sur la date pour une approche plus dynamique qui tient différemment compte de l'effet de saisonnalité.
-Le nombre d'analogues de la présélection est équivalent au nombre de jours que nous aurions retenus par la période de $\pm 60$ jours, soit $N_{0} = 60 \cdot 2 \cdot n_{a}$, où $n_{a}$ est le nombre d'années de la période de calibration.
-Mais la sélection est ici fondée sur un critère de similitude thermique au droit de la région cible.
+Subsequently, \citet{BenDaoud2010} added an additionally level of analogy, between the circulation and the moisture analogy (Table \ref{table:R5}), based on vertical velocity at 850~hPa (W850).
+This method was developed for large plains in France, but was found to be not relevant for an Alpine environment where topography is mostly responsible for uplift of air masses \citep{Horton2012}.
 
 \begin{table}[htbp]
-	\caption{Method of type P2T-2Z-2HI proposed by \citet{BenDaoud2010}.}
+	\caption{Method of type P2T-2Z-4W-4MI, by \citet{BenDaoud2010}.}
 	\begin{tabular}{ccccc}
@@
 		\middlehline
-		\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
-		& T600 & 12~h & & \\ 
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
-		& Z 500~hPa & 24~h & & \\ 
-		\middlehline
-		2 & TPW * RH850 & 12, 24~h & RMSE & 25 \\
-		\bottomhline 
-	\end{tabular} 
-	\label{table:R4a}
-\end{table}
-
-\begin{table}[htbp]
-	\caption{Method of type P2T-2Z-4HI proposed by \citet{BenDaoud2010}.}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline
-		\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
-		& T600 & 12~h & & \\ 
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
-		& Z 500~hPa & 24~h & & \\ 
-		\middlehline
-		\multirow{2}{*}{2} & TPW * RH925 & 12, 24~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
-		& TPW * RH700 & 12, 24~h & & \\ 
-		\bottomhline 
-	\end{tabular} 
-	\label{table:R4b}
-\end{table}
-
-\begin{table}[htbp]
-	\caption{Method of type P2T-2Z-10HI proposed by \citet{BenDaoud2010}.}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline
-		\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
-		& T600 & 12~h & & \\ 
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
-		& Z 500~hPa & 24~h & & \\ 
-		\middlehline
-		\multirow{2}{*}{2} & TPW * RH925 & 06-30~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
-		& TPW * RH700 & 06-30~h & & \\ 
-		\bottomhline 
-	\end{tabular} 
-	\label{table:R4c}
-\end{table}
-
-%Trois références sont donc retenues ici: la première (R4a, Table \ref{table:R4a}) considère le niveau d'analogie sur l'humidité tel que l'a défini \citet{Bontron2004}, la deuxième (R4b, Table \ref{table:R4b}) intègre les niveaux d'humidité calibrés par \citet{BenDaoud2010}, et la troisième (R4c, Table \ref{table:R4c}) considère toutes les heures d'observation disponibles pour ce dernier niveau d'analogie.
-
-%\subsection{R5, prise en compte des mouvements verticaux}
-%\label{sec:etat_art:R5}
-
-%\citet{BenDaoud2010} a encore ajouté un niveau d'analogie sur les mouvements verticaux.
-Ce niveau vient s'insérer entre l'analogie de circulation et celle de l'humidité.
-À nouveau, nous considérons une première référence (R5a, Table \ref{table:R5a}) avec les paramètres d'humidité selon \citet{Bontron2004}, et une seconde (R5b, Table \ref{table:R5b}) avec les paramètres de \citet{BenDaoud2010}.
-
-\begin{table}[htbp]
-	\caption{Method of type P2T-2Z-4W-2HI proposed by \citet{BenDaoud2010}.}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline
 		\multirow{2}{*}{0} & T925 (1 point) & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
@@
 		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{170} \\
-		& Z 500~hPa & 24~h & & \\ 
-		\middlehline
-		2 & W850 & 06-24~h & RMSE & 70 \\
-		\middlehline
-		3 & TPW * RH850 & 12, 24~h & RMSE & 25 \\
-		\bottomhline 
-	\end{tabular} 
-	\label{table:R5a}
-\end{table}
-
-\begin{table}[htbp]
-	\caption{Method of type P2T-2Z-4W-4HI proposed by \citet{BenDaoud2010}.}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline
-		\multirow{2}{*}{0} & T925 (1 point) & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
-		& T600 (1 point) & 12~h & & \\ 
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{170} \\
-		& Z 500~hPa & 24~h & & \\ 
+		& Z500 & 24~h & & \\ 
 		\middlehline
@@
 	\end{tabular}
-	\label{table:R5b}
+	\label{table:R5}
 \end{table}
 
+\citet{Horton2012} identified that the analogy on the atmospheric circulation may not be comprehensive, and that a significant gain was obtained by considering 4 atmospheric levels (1000, 850, 700, and 500~hPa at 12 or 24~h) instead of 2 (Table \ref{table:R6}).
+No number of analogues ($N_{1}$) was provided globally, as it was calibrated for every subregion.
+Considering a method only based on the atmospheric circulation has an interest for operational forecasting, where moisture variables are less well forecasted over a lead time of a few days.
+An equivalent structure was also optimized by means of generic algorithms (PC-4Zgo), which is the topic of another paper.
+
 \begin{table}[htbp]
-	\caption{Method of type PC-4Zgo proposed by \citet{Horton2012}.}
+	\caption{Method of type PC-4Z proposed by \citet{Horton2012}.}
 	\begin{tabular}{ccccc}
-
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline 
+		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+		\middlehline 
+		\multirow{4}{*}{1} & Z1000 & 12~h & \multirow{4}{*}{S1} & \multirow{4}{*}{$N_{1}$} \\
+		& Z850 & 24~h & & \\ 
+		& Z700 & 12~h & & \\ 
+		& Z500 & 24~h & & \\ 
+		\bottomhline 
 	\end{tabular}
-	\label{table:R6a}
+	\label{table:R6}
 \end{table}
 
+\citet{Horton2012} also integrated an analogy on the moisture flux, after the circulation analogy on the 4 atmospheric levels (Table \ref{table:R7}).
+The number of analogues ($N_{1}$, $N_{2}$) were also calibrated for every subregion.
+Similarly, an equivalent structure was optimized (PC-4Zgo-2MIgo).
+
 \begin{table}[htbp]
-	\caption{Method of type PC-4Zgo-2HIgo proposed by \citet{Horton2012}.}
+	\caption{Method of type PC-4Z-2MI, by \citet{Horton2012}.}
 	\begin{tabular}{ccccc}
-
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline 
+		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+		\middlehline 
+		\multirow{4}{*}{1} & Z1000 & 12~h & \multirow{4}{*}{S1} & \multirow{4}{*}{$N_{1}$} \\
+		& Z850 & 24~h & & \\ 
+		& Z700 & 12~h & & \\ 
+		& Z500 & 24~h & & \\ 
+		\middlehline
+		2 & V700 * TPW * RH700 & 12, 24~h & RMSE & $N_{2}$ \\
+		\bottomhline 
 	\end{tabular}
-	\label{table:R6b}
+	\label{table:R7}
 \end{table}
 
-\subsection{Data}
-% TODO: write
-
-The analogue method relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series we want to forecast.
-
-Predictors are generally reanalysis datasets (and outputs of a global numerical weather prediction models for the target situation in operational forecasting, which is not the topic of this paper).
-We will work here with the NCEP/NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996}, but it can be any other reanalysis dataset.
-
-The predictand (which is to be predicted) is in our case the daily precipitation (6~a.m.
-to 6~a.m.
-the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008.
-The time series from every available gauging station were averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.
-
-%\citet{Djerboua2001} a également proposé de normaliser la pluie par la pluie décennale à la station (ou groupement), ce qui nous permet de mieux identifier les contributions les plus importantes en précipitations.
-
-%Par une étude de sensibilité, \citet{Bontron2004} a déterminé un plafonnement de la longueur de l'archive nécessaire à 30 ans pour la prévision en général, et à 40 ans pour les événements intenses.
-Il a également mis en lumière la dépendance entre le nombre d'analogues optimal et la taille de l'archive: plus l'archive est courte, plus le nombre d'analogues diminue.
-En faisant varier la résolution des grilles de prédicteurs, il en a conclu que l'augmentation en performance n'est pas significative pour l'analogie de circulation en deçà d'une résolution de 5\degres .
-Cependant, elle semble plus importante pour le second niveau d'analogie sur les humidités, qui sont des variables plus locales.
-
-%\citet{BenDaoud2010} a dans un premier temps évalué les réanalyses européennes ERA-40 \citep{Uppala1999}, avec une résolution de 1.125\degres, par rapport aux réanalyses américaines du NCEP/NCAR à 2.5\degres\ \citep{Kalnay1996} utilisées jusqu'alors.
-Il a identifié une légère amélioration des performances, mais pas assez substantielle pour vraiment justifier un changement d'archive \citep{BenDaoud2008}.
+% TODO : Sabine
+% TODO : Jérémie Chardon
 

### 2015-10-21 AtmoSwing - Geoscientific Model Development/template.tex
Merging the evolution of the method with references.

@@
 This normalization allows for an easier comparison between subregions subject to different precipitation regimes, and thus to better identify the most important contributions.
-
-\subsection{Evolution of the method}
-\label{sec:method:evolution}
-
-The most common usage of the analogue method is for precipitation forecasting. Thus, the evolution presented hereafter focuses on this predictand.
-
-\citet{Lorenz1969} introduced the concept and established the basis of the method.
-He considered looking for analogues on the geopotential field (at 200, 500 and 850~hPa) with a corrected Euclidean distance averaged on the 3 levels.
-In addition, the analogue situations were to belong to the same period of the year to be comparable in terms of distribution of solar energy.
-
-The use of the analogue method for operational forecasting of daily precipitation originates in the work of \citet{Duband1970,Duband1974,Duband1981}.
-It was then designed for operational forecasting at EDF (\'{E}lectricit\'{e} de France) in order to better manage water resources and flood risks.
-The geopotential height at 700~hPa and 00~h was used for its higher stability than the sea level pressure (SLP) field, and its sensitivity to the atmospheric disturbances \citep{Guilbaud1997}.
-However, the SLP at 06~h was also used for determining the intensity of precipitation, as well as the temperature at 700~hPa as indicator of the thermal state of the air mass \citep{Duband1974}.
-The data were then based on 37 radiosounding over Europe and condensed by a principal component analysis.
-The first 25 analogues on the geopotential at 700~hPa were considered, and multiple local regressions between precipitation, SLP, and the temperature at 700~hPa were established on these analogues before being applied to the target situation \citep{Guilbaud1997}.
-The archives were split by season to consider comparable situations in terms of distribution of solar energy \citep{Lorenz1969}.
-This initial rigid division into seasons was then transformed into a moving selection of more or less two months around the target date.
-The forecast was then performed only on the basis of observations and was temporally extrapolated to the following two days.
-After a few years, this statistical temporal extrapolation was abandoned in favor of a statistical adaptation using predictors resulting from an global numerical model, allowing a forecast over the following 4~days.
-
-Thereafter, the geopotential was considered at 1000~hPa and 700~hPa and the analogues selection was done in two stages: first according to an Euclidean distance in the space of the principal components of the geopotential field at 700~hPa, and then according to a correlation criterion (on the geopotential field at 700 and 1000~hPa, as well as on the thickness between these two levels) in order to remove days too dissimilar \citep{Guilbaud1997}.
-The regression approach to determining precipitation was eventually abandoned in favor of the probabilistic forecasting (synthesized by the percentiles 20, 60 and 90~\%), as it is performed today by interpolating linearly over the cumulative empirical distribution of daily precipitation measured at the analogue days \citep{Guilbaud1997,Guilbaud1998}.
-
-\citet{Wilson1980} sought the 20 best analogues on the geopotential field at 500 and 1000~hPa using the Teweles-Wobus (S1) criterion (Eq.
-\ref{eq:S1}), which allows for a comparison of the gradients and thus an analogy of the atmospheric circulation.
-\citet{Woodcock1980} used the same criterion on the SLP fields to select 50~analogues in order to forecast maximum daily temperatures.
-\citet{Yacowar1975} considered the 20 best analogues on the maximum of the sum of correlations on the two fields.
-This work has demonstrated the best performance of the analogues method compared to regression methods, as well as the interest to search for analogues on two (500 and 1000~hPa) geopotential fields combined \citep{Guilbaud1997}.
-
-\citet{Mandon1985} introduced a second level of analogy and assessed different variables, such as wind, moisture, air temperature, surface temperature of the Mediterranean, the product of wind and the 700~hPa moisture, as well as a second barometric criteria differentiated according to the season.
-\citet{Vallee1986} continued to work on the second level of analogy and considered the wind at 700~hPa \& 12~h in order to improve heavy precipitation events for a region in France susceptible to southerly flows.
-
-Taking advantage of higher-performance IT tools \citet{Guilbaud1997} stopped using PCA in order to work directly with the raw data interpolated on grids, which was an improvement, especially when considering the S1 criterion (already used for analogues selection by\citealp{Wilson1980} and \citealp{Woodcock1980}) instead of the Euclidean distance.
-This score gives importance to the similarity of atmospheric circulation rather than absolute values of the pressure field.
-After comparing this criterion to other criteria from the literature, or combinations of these, \citet{Guilbaud1998} found that S1 is the most efficient.
-They also pointed out the benefit of using 2 atmospheric levels instead of one (also instead of the thickness), and to also consider 2 temporal windows \citep{Obled2002}.
-When using multiple predictors, they combined the criteria values calculated on each atmospheric level and each temporal window using an arithmetic mean.
-Finally, they also suggested using a second level of analogy on lower layers moisture and introduced the Ranked Probability Score \citep{Epstein1969} to assess the forecast quality, which was found to be more relevant that the Brier score \citep{Brier1950}.
-
-\citet{Bontron2004} could benefit from the newly available NCEP/NCAR reanalysis data.
-This dataset being more homogeneous, much longer, and contained more variables than what was previously used, he could systematically assess a large selection of variables in the analogue method combined with different criteria.
-He thus confirmed the interest of the geopotential height along with the S1 criterion for the first level of analogy.
-He has also shown that the choice of the temporal window (time of observation) has a higher importance than the atmospheric level for the performance of the method.
-By assessing multiple combinations of atmospheric levels and temporal windows, he concluded that the coupled geopotential heights at 1000~hPa \& 12~h and 500~hPa \& 24~h provided the best performance for the studied region.
-
-He also assessed several variables for the second level of analogy and identified the moisture variables (precipitable water and relative humidity) and vertical velocity to be the most relevant.
-Finally, he found that the product of relative humidity and precipitable water gave the best performance.
-
-He noted the relevance of defining different spatial windows for each region, rather than a single window to the entire territory.
-These windows are more able to represent the specific atmospheric influences for the region.
-In order to assess the forecast, he introduced the Continuous Ranked Probability Score \citep[CRPS, Eq.
-\ref{eq:CRPS}, ][]{Brown1974}, which discards the issue of determining classes as with the RPS previously in use.
-
-\citet{BenDaoud2010} applied the analogue method in the context of large flatter catchments, out of an Alpine environment (Sa\^{o}ne, Seine).
-He evaluated several variables usually used in weather forecasting, amongst them the air temperature and the vertical velocity that presented a potential interest.
-The temperature (at the nearest grid point, on the 925~hPa (36~h) and 600~hPa (12~h) levels) could replace the rigid selection of $\pm$ 60 days around the target date by a more dynamic screening of similar situations in terms of air masses.
-The seasonal effect is indeed also present in the temperature data.
-The vertical velocity was used as an additional level of analogy, between the analogy of atmospheric circulation and the one on moisture, to account for fronts.
-Finally, he selected the moisture variables at 700~hPa instead of 850~Pa.
-
-\citet{Bliefernicht2010} proposed to add a weighting to the grid points of the predictor to overcome a comparison on a fixed-size window, and to give more importance to regions with relevant atmospheric circulation information.
-However, he noticed that there is a risk of overparametrization and a simplification of the weighting fields may be necessary, and that the performance was not stable between the calibration and the validation periods.
-He also compare the performance of the analogues method with a forecasting method based on a weather types approach, and concluded that the analogues method was more efficient.
-
-% TODO : Sabine
-% TODO : Jérémie Chardon
-% TODO : Horton
 
@@
 
-\subsection{References for precipitation forecasting}
+\subsection{Evolution of the method and examples}
+\label{sec:method:evolution}
 
@@
 Thereby, we cannot provide a single best parameterization for the method, neither rank them from worst to best.
-We will thus provide the references implementations of the most recent method variant, in the chronological order they appeared.
-
-The first parameterization comes from the work of \citet{Guilbaud1997} and \citet{Obled2002}.
-It consists of a single level of analogy on the atmospheric circulation.
-The score S1 (Teweles-Wobus, Eq.
-\ref{eq:S1}) is processed on the geopotential height at 1000~hPa (Z1000) and 700~hPa (Z700) or 500~hPa (Z500) (Table \ref{table:R0}), both at 00~h and 24~h.
-The number of analogues considered is 50.
+We will thus provide some examples of parameterizations of the most recent method variant, in the chronological order they appeared.
+The most common usage of the analogue method is for precipitation forecasting.
+Thus, the evolution presented hereafter focuses on this predictand.
+
+\citet{Lorenz1969} introduced the concept and established the basis of the method.
+He considered looking for analogues on the geopotential field (at 200, 500 and 850~hPa) with a corrected Euclidean distance averaged on the 3 levels.
+In addition, the analogue situations were to belong to the same period of the year to be comparable in terms of distribution of solar energy.
+
+The use of the analogue method for operational forecasting of daily precipitation originates in the work of \citet{Duband1970,Duband1974,Duband1981}.
+It was then designed for operational forecasting at EDF (\'{E}lectricit\'{e} de France) in order to better manage water resources and flood risks.
+The geopotential height at 700~hPa and 00~h was used for its higher stability than the sea level pressure (SLP) field, and its sensitivity to the atmospheric disturbances \citep{Guilbaud1997}.
+However, the SLP at 06~h was also used for determining the intensity of precipitation, as well as the temperature at 700~hPa as indicator of the thermal state of the air mass \citep{Duband1974}.
+The data were then based on 37 radiosounding over Europe and condensed by a principal component analysis.
+The first 25 analogues on the geopotential at 700~hPa were considered, and multiple local regressions between precipitation, SLP, and the temperature at 700~hPa were established on these analogues before being applied to the target situation \citep{Guilbaud1997}.
+The archives were split by season to consider comparable situations in terms of distribution of solar energy \citep{Lorenz1969}.
+This initial rigid division into seasons was then transformed into a moving selection of more or less two months around the target date.
+The forecast was then performed only on the basis of observations and was temporally extrapolated to the following two days.
+After a few years, this statistical temporal extrapolation was abandoned in favor of a statistical adaptation using predictors resulting from an global numerical model, allowing a forecast over the following 4~days.
+
+Thereafter, the geopotential was considered at 1000~hPa and 700~hPa and the analogues selection was done in two stages: first according to an Euclidean distance in the space of the principal components of the geopotential field at 700~hPa, and then according to a correlation criterion (on the geopotential field at 700 and 1000~hPa, as well as on the thickness between these two levels) in order to remove days too dissimilar \citep{Guilbaud1997}.
+The regression approach to determining precipitation was eventually abandoned in favor of the probabilistic forecasting (synthesized by the percentiles 20, 60 and 90~\%), as it is performed today by interpolating linearly over the cumulative empirical distribution of daily precipitation measured at the analogue days \citep{Guilbaud1997,Guilbaud1998}.
+
+\citet{Wilson1980} sought the 20 best analogues on the geopotential field at 500 and 1000~hPa using the Teweles-Wobus (S1) criterion (Eq.
+\ref{eq:S1}), which allows for a comparison of the gradients and thus an analogy of the atmospheric circulation.
+\citet{Woodcock1980} used the same criterion on the SLP fields to select 50~analogues in order to forecast maximum daily temperatures.
+\citet{Yacowar1975} considered the 20 best analogues on the maximum of the sum of correlations on the two fields.
+This work has demonstrated the best performance of the analogues method compared to regression methods, as well as the interest to search for analogues on two (500 and 1000~hPa) geopotential fields combined \citep{Guilbaud1997}.
+
+\citet{Mandon1985} introduced a second level of analogy and assessed different variables, such as wind, moisture, air temperature, surface temperature of the Mediterranean, the product of wind and the 700~hPa moisture, as well as a second barometric criteria differentiated according to the season.
+\citet{Vallee1986} continued to work on the second level of analogy and considered the wind at 700~hPa \& 12~h in order to improve heavy precipitation events for a region in France susceptible to southerly flows.
+
+Taking advantage of higher-performance IT tools \citet{Guilbaud1997} stopped using PCA in order to work directly with the raw data interpolated on grids, which was an improvement, especially when considering the S1 criterion (already used for analogues selection by\citealp{Wilson1980} and \citealp{Woodcock1980}) instead of the Euclidean distance.
+This score gives importance to the similarity of atmospheric circulation rather than absolute values of the pressure field.
+After comparing this criterion to other criteria from the literature, or combinations of these, \citet{Guilbaud1998} found that S1 is the most efficient.
+They also pointed out the benefit of using 2 atmospheric levels, 1000~hPa (Z1000) and 700~hPa (Z700) or 500~hPa (Z500), instead of one (also instead of the thickness), and to also consider 2 temporal windows, 00~h and 24~h \citep{Obled2002}.
+The number of analogues considered is 50 (Table \ref{table:R0}).
+When using multiple predictors, they combined the criteria values calculated on each atmospheric level and each temporal window using an arithmetic mean.
+Finally, they also suggested using a second level of analogy on lower layers moisture and introduced the Ranked Probability Score \citep{Epstein1969} to assess the forecast quality, which was found to be more relevant that the Brier score \citep{Brier1950}.
 
@@
 
-The analogy on the atmospheric circulation (Table \ref{table:R1}) proposed by \citet{Bontron2004} is still, at the time of writing, often used, and considered as a reference for benchmarking new parameterizations.
-He noticed that the choice of the temporal window was more important than the atmospheric level.
-The method consists of the geopotential height on two atmospheric levels : 1000~hPa (Z1000) at 12~h and 500~hPa (Z700) at 24~h.
+\citet{Bontron2004} could benefit from the newly available NCEP/NCAR reanalysis data.
+This dataset being more homogeneous, much longer, and contained more variables than what was previously used, he could systematically assess a large selection of variables in the analogue method combined with different criteria.
+He thus confirmed the interest of the geopotential height along with the S1 criterion for the first level of analogy.
+He has also shown that the choice of the temporal window (time of observation) has a higher importance than the atmospheric level for the performance of the method.
+By assessing multiple combinations of atmospheric levels and temporal windows, he concluded that the coupled geopotential heights at 1000~hPa (Z1000) \& 12~h and 500~hPa (Z500) \& 24~h provided the best performance for the studied region (Table \ref{table:R1}).
+The analogy on the atmospheric circulation proposed by \citet{Bontron2004} is still, at the time of writing, often used operationally, and considered as a reference for benchmarking new parameterizations \citep{Horton2012, Daoud2015}.
 
@@
 
-\citep{Bontron2004} then added a second level of analogy (Table \ref{table:R2}) on a moisture index : the product of relative humidity at 850~hPa (RH850) and total precipitable water (TPW).
+\citep{Bontron2004} also assessed several variables for the second level of analogy and identified the moisture variables (precipitable water and relative humidity) and vertical velocity to be the most relevant.
+Finally, he found that a moisture index made of the product of relative humidity at 850~hPa (RH850) and total precipitable water (TPW) gave the best performance (Table \ref{table:R2}).
 This index does not represent an actual physical quantity, but expresses the water content of the column and its proximity to saturation.
@@
 \end{table}
+
+He noted the relevance of defining different spatial windows for each region, rather than a single window to the entire territory.
+These windows are more able to represent the specific atmospheric influences for the region.
+In order to assess the forecast, he introduced the Continuous Ranked Probability Score \citep[CRPS, Eq.
+\ref{eq:CRPS}, ][]{Brown1974}, which discards the issue of determining classes as with the RPS previously in use.
 
@@
 
-The next reference method was developed by \citet{BenDaoud2010} and introduces a change in the preselection.
-The calendar selection ($\pm 60$ days around the target date) was then replaced by a preselection based on air temperature at 925~hPa (36~h) and 600~hPa (12h).
+\citet{BenDaoud2010} applied the analogue method in the context of large floodplains, out of an Alpine environment (Sa\^{o}ne, Seine).
+He evaluated several variables usually used in weather forecasting, amongst them the air temperature and the vertical velocity that presented a potential interest.
+The temperature (at the nearest grid point, on the 925~hPa (36~h) and 600~hPa (12~h) levels) could replace the rigid calendar preselection of $\pm$ 60 days around the target date by a more dynamic screening of similar situations in terms of air masses.
+The seasonal effect is indeed also present in the temperature data.
 The number of preselected dates is equivalent to the number of days we would have chosen with the calendar approach, and thus depends on the archive size: $N_{0} = 60 \cdot 2 \cdot n_{a}$ where $n_{a}$ is the number of years in the calibration period.
-This analogy on air temperature is performed at the closest point to the catchment
-
 \citet{BenDaoud2010} also reconsidered the parameters of the moisture index and ended up with both 925~hPa and 700~hPa levels, at 12~h and 24~h, or at every time step (6~h) between 06~h and 30~h (Table \ref{table:R4b}).
@@
 \end{table}
+
+\citet{Bliefernicht2010} proposed to add a weighting to the grid points of the predictor to overcome a comparison on a fixed-size window, and to give more importance to regions with relevant atmospheric circulation information.
+However, he noticed that there is a risk of overparametrization and a simplification of the weighting fields may be necessary, and that the performance was not stable between the calibration and the validation periods.
+He also compare the performance of the analogues method with a forecasting method based on a weather types approach, and concluded that the analogues method was more efficient.
 

### 2015-10-21 AtmoSwing - Geoscientific Model Development/template.tex
Addition of the discussion on the analogue method.

@@
 Thus, the evolution presented hereafter focuses on this predictand.
+However, the analogue method, or an equivalent, was also used for short to medium term forecasting of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+\citet{Guilbaud1997} performed a literature review about the use of the analogue method in long-term forecasting and identified operational applications for monthly forecasts in many countries, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal forecasts: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
 
@@
 
-The use of the analogue method for operational forecasting of daily precipitation originates in the work of \citet{Duband1970,Duband1974,Duband1981}.
+The use of the analogue method for operational forecasting of daily precipitation originates in the work of \citet{Duband1970, Duband1974, Duband1981}.
 It was then designed for operational forecasting at EDF (\'{E}lectricit\'{e} de France) in order to better manage water resources and flood risks.
@@
 Thereafter, the geopotential was considered at 1000~hPa and 700~hPa and the analogues selection was done in two stages: first according to an Euclidean distance in the space of the principal components of the geopotential field at 700~hPa, and then according to a correlation criterion (on the geopotential field at 700 and 1000~hPa, as well as on the thickness between these two levels) in order to remove days too dissimilar \citep{Guilbaud1997}.
-The regression approach to determining precipitation was eventually abandoned in favor of the probabilistic forecasting (synthesized by the percentiles 20, 60 and 90~\%), as it is performed today by interpolating linearly over the cumulative empirical distribution of daily precipitation measured at the analogue days \citep{Guilbaud1997,Guilbaud1998}.
+The regression approach to determining precipitation was eventually abandoned in favor of the probabilistic forecasting (synthesized by the percentiles 20, 60 and 90~\%), as it is performed today by interpolating linearly over the cumulative empirical distribution of daily precipitation measured at the analogue days \citep{Guilbaud1997, Guilbaud1998}.
 
@@
 \ref{eq:CRPS}, ][]{Brown1974}, which discards the issue of determining classes as with the RPS previously in use.
+
+\citet{Gibergans-Baguena2007} implemented the method for daily precipitation forecasts in Catalonia.
+They considered the geopotential at 700 and 1000~hPa, and the thickness between these two levels, to search for analogy of circulation, and then applied a second selection on local data from radiosonde: stability indexes, precipitable water, temperature, etc.
 
@@
 
-\subsection{Discussion}
-% TODO: write
-
-%\citet{Bliefernicht2010} a observé que la performance de la méthode est plus élevée en hiver qu'en été.
-Ainsi, la relation entre les prédicteurs synoptiques et les précipitations locales est plus faible en été, en raison des pluies d'origine convective qui ont un caractère plus aléatoire.
-
-%La méthode des analogues, ou une forme proche, a également été utilisée pour la prévision à court ou moyen terme des températures journalières \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, des vents \citep{Gordon1987}, des avalanches \citep{Obled1980, Bolognesi1993}, de l'insolation \citep{Bois1981}, et de la trajectoire de cyclones tropicaux \citep{Keenan1981, Sievers2000, Fraedrich2003}.
-
-%\citet{Guilbaud1997} a effectué une recherche bibliographique des utilisations de la méthode en prévision à long terme et a identifié des applications opérationnelles pour des prévisions mensuelles dans de nombreux pays, notamment au Canada \citep{Shabbar1986}, en Hongrie \citep{Toth1989}, aux Pays-Bas \citep{Nap1981}, et en Angleterre \citep{Murray1974}, ainsi que des prévisions saisonnières : \citet{Barnett1978}, \citet{Bergen1982} et \citet{Livezey1988}.
-
-%L'utilisation de la méthode des analogues en tant que technique d'adaptation de modèles climatiques fait l'objet d'un nombre croissant d'études \citep{Zorita1999,Wetterhall2005,Matulla2008}.
-\citet{Wetterhall2007} ont également utilisé la méthode des analogues en Suède, dans le cadre d'une étude sur le réchauffement climatique, et la trouvent simple, mais moins performante que d'autres méthodes plus complexes.
-Cependant, ils n'utilisent que la pression au niveau de la mer en tant que prédicteur, et considèrent uniquement la meilleure analogue.
-Ces deux aspects ne sont clairement pas optimaux, et une qualité médiocre de la méthode n'est alors pas surprenante.
-L'implémentation actuelle de la méthode (voir section \ref{sec:etat_art:implementation_actuelle}) fournit clairement des résultats plus pertinents.
-
-%Une version de la méthode a été évaluée dans le projet STARDEX \citep[\textit{STAtistical and Regional dynamical Downscaling of EXtremes for European regions}, voir][]{Goodess2003, Stardex2005}.
-Un des objectifs du projet étant de comparer différentes méthodes de descente d'échelle pour la détermination des extrêmes météorologiques, la méthode des analogues a été mise en concurrence avec d'autres techniques et a été sélectionnée parmi les plus intéressantes \citep{Maheras2005, Schmidli2007}.
-
-%\citet{GibergansBaguena2007} ont implémenté la méthode pour des prévisions de précipitations journalières en Catalogne.
-Ils ont considéré le géopotentiel à 700 et 1000~hPa, ainsi que l'épaisseur entre ces deux niveaux pour la recherche d'analogie de circulation, puis ont appliqué une seconde sélection sur la base de données locales obtenues par radiosondage: indices de stabilité, eau précipitable, température, etc...
-
-%\citet{Hamill2006} ont utilisé une approche par analogie sur les reprévisions du modèle global des États-Unis (GFS, voir sections \ref{sec:donnees:previsions_GFS} et \ref{sec:donnees:resimulations_GFS}).
-Cette application a permis de corriger des erreurs systématiques dans les prévisions d'ensemble des températures et des précipitations.
-En effet, l'approche statistique a mis en évidence certains biais dans les prévisions du modèle numérique, qui ont pu être ajustés par la prise en compte de la climatologie locale intrinsèque à la méthode des analogues.
-De plus, la dispersion des analogues étant plus importante que celle des prévisions d'ensemble, la sous-dispersion de ces dernières a pu être corrigée à l'aide des analogues \citep{Hamill2006}.
-Une des raisons invoquées pour la bonne performance de la méthode des analogues par rapport au modèle numérique global est le fait que ce dernier a une orographie lissée, qui ne tient pas compte des réelles spécificités locales, ce que permet l'approche par analogie.
-
-%La méthode présente cependant des limites dont il faut être conscient.
-La première est la nécessité de disposer d'une archive conséquente de la variable cible à un pas de temps pertinent, ici les précipitations.
-Sans une base de données de prédictands de plusieurs décennies, la méthode n'est pas applicable.
-
-%Les archives des prédicteurs sont également importantes et plus particulièrement leur homogénéité.
-Nous disposons actuellement de jeux de données de réanalyses (voir section \ref{sec:donnees:reanalyses1_ncep}) de bonne qualité, mais contenant tout de même des discontinuités significatives dues à la densification des réseaux de mesures et au déploiement de nouvelles techniques de mesure et de l'imagerie satellitaire.
-Nous ne pourrons a priori jamais complètement éliminer cette hétérogénéité, car les données demeureront manquantes.
-Toutefois, la qualité de ces données les rend tout à fait utilisables pour la méthode des analogues, et ceci partout sur le globe !
-
-%Un aspect supplémentaire concerne les différences entre les prédicteurs disponibles en temps réel et les archives de ces prédicteurs.
-En effet, les deux jeux de données n'ont généralement pas la même climatologie, car ils ne résultent pas du même modèle, et n'ont pas été élaborés de la même manière.
-Il existe des alternatives, telles que l'utilisation en opérationnel de prévisions émises par un modèle figé, conjointement à des archives élaborées par ce même modèle en reprévision.
-
-%Toutefois, les prévisions que nous utiliserions de cette manière ne seraient pas à l'état de l'art, et les reprévisions (archives) contiendraient des erreurs et des incertitudes beaucoup plus importantes que des réanalyses.
-Il convient donc d'utiliser des prédicteurs robustes qui dépendent au minimum des spécificités du modèle numérique.
-
-%Une autre limite réside dans le fait que les événements extrêmes peuvent être sous-représentés dans l'échantillon d'analogues considéré.
-En effet, dans une archive météorologique d'une durée limitée, les événements correspondants à des temps de retour élevés ne sont pas très nombreux.
-Leur représentation est certainement inférieure au nombre d'analogues que nous retenons, ce qui peut biaiser la prévision.
-
-%Enfin, \citet{Bliefernicht2007} ont montré que les prévisions sont moins bonnes en été.
-Ceci est dû à la part plus importante de la convection durant les mois chauds.
-Les variables de la circulation synoptique ne sont en effet pas à même de prévoir la localisation des cellules orageuses.
-Ceci a également été constaté par \citet{BenDaoud2010}, qui avait mis en place un modèle spécifique pour les mois d'été (du 15 juin au 15 septembre).
-Nous pouvons estimer que les prédicteurs sont à reconsidérer (variables, niveaux, etc.), et que leur domaine peut être différent.
-Le problème est que, durant cette période, on peut également rencontrer situations classiques avec une circulation atmosphérique dominante comme dans les autres saisons, ou des situations de marais barométriques accompagnées d'un fort risque de convection locale, sans signature dans les variables synoptiques.
+\subsection{Discussion on the method}
+
+A version of the analogue method was evaluated during the project STARDEX \citep[\textit{STAtistical and Regional dynamical Downscaling of EXtremes for European regions}, see][]{Goodess2003, Stardex2005}.
+One of the project goals was to compare various downscaling methods for the determination of weather extremes, and the analogue method was selected among the most interesting from various techniques \citep{Maheras2005, Schmidli2007}.
+Its use as adaptation method of climate models is also the subject of a growing number of studies \citep{Zorita1999, Wetterhall2005, Wetterhall2007, Matulla2007, Chardon2014, Dayon2015}.
+
+\citet{Hamill2006} used an analogy based approach on the GFS reforecasts in order to correct systematic errors in the ensemble forecasts of temperature and precipitation.
+Indeed, the statistical approach showed some bias in estimates of the numerical model, which may have been adjusted by taking into account the intrinsic local climatology from the analogues method.
+Moreover, the under-dispersion of the ensemble forecast from the numerical model has been corrected using analogues \citep{Hamill2006}.
+Correction of ensemble forecast under-dispersion by means of the analogue method is also used operationally at EDF.
+
+\citet{Bliefernicht2010} observed that the performance of the analogue method is higher for winter than for summer.
+The relationship between synoptic predictors and local rainfall is lower in summer, due to convective precipitation that present a higher spatial variability and that depend on other parameters.
+Variables describing the synoptic circulation are indeed not able to predict the location of thunderstorm cells.
+This was also observed by \citet{BenDaoud2010}, who set up a specific model for the summer months (June 15 to September 15).
+
+One of the method limitations is the need for a substantial archive of the predictand variable, for example measured precipitations.
+Without data on several decades, the method is not applicable.
+Long predictor archives are also required, but this problem is usually solved with reanalysis data, which are not perfect in terms of homogeneity, but can be considered of sufficient quality.
+Moreover,  reanalysis data are available all around the world, which represent a great potential for the analogue method.
+Another issue, still about data, concerns the operational forecasting: predictors describing forecasted target situations and the ones from the archive are not fully homogeneous, as they usually don't result from the same model.
+It is therefore necessary to use robust predictors that depend from the numerical model characteristics at a minimum extent.
+
+Another limitation is the fact that extreme events may be under-represented in the considered sample of analogue dates.
+Indeed, in a limited weather archive, events with high return periods are not so numerous.
+Their number is certainly lower than the number of analogues we consider, which can introduce a bias in the forecast.
+There are however techniques to correct this bias \citep[see][]{Marty2010}.
+
+It is legitimate to raise the question of the relevance of an approach based on archives of past situations in a context of climate change.
+The first potential issue is a possible change in atmospheric circulation.
+\citep{Philipp2007} observed certain trends in the synoptic atmospheric circulation over Europe, but with moderate frequencies.
+Moreover, the basic laws governing the atmosphere behavior will not be transformed \citep{Hewitson1996}.
+The assumption is that a large part of local climate change will result from changes in intensity, frequency and persistence of synoptic variables, but with other characteristics substantially similar to the present situation \citep{Hewitson1996}.
+Thus, if the archive of weather situations is long enough, it is reasonable to assume that a large part of future situations is already represented, even those whose frequency will change under different climatic conditions \citep{Wetterhall2005}.
+In addition, climate change is relatively slow, and through continuous updating of the archive, the analogue method will incorporate new information progressively with no big discontinuity.
 

### 2015-10-22 AtmoSwing - Geoscientific Model Development/template.tex
Writing the basis of AtmoSwing and the Forecaster module.

@@
 \subsection{Data}
-% TODO: write
+\label{sec:data}
 
@@
 This normalization allows for an easier comparison between subregions subject to different precipitation regimes, and thus to better identify the most important contributions.
+Most users also apply a root square to this last ratio in order to reduce the weight of the extreme predictand values, but we generally don't.
 
@@
 \section{Software basics}
+
+AtmoSwing is made of 3 main modules (Figure \ref{figure:flowchart_modules_atmoswing}) that are standalone, but do share a common code basis: the Forecaster, to process the operational forecasting, the Viewer, to display the forecast in a GIS environment, and the Optimizer, to calibrate/optimize the statistical relationship defining the analogy for a given predictand time series.
+Separating the Forecaster and the Viewer allows to automate the forecast on a server and to quickly display the results locally.
+The code is written in object oriented C++ and relies on the wxWidgets \citep{Smart2006} library to provide a cross-platform native experience to users.
+The software can thus be compiled on MS Windows, Linux / Unix, Mac (OS X, iOS), both in 32-bit and 64-bit.
+
+\begin{figure}[htbp]
+	\includegraphics[width=8.3cm]{figures/logo.pdf}
+	\caption{The AtmoSwing logo and its 3 modules: the Forecaster, the Viewer and the Optimizer.}
+	\label{figure:logo}
+\end{figure}
+
+The source code in under version control (with Mercurial), and is open source (on Bitbucket, www.atmoswing.org).
+Developments have been made with an approach of unit tests.
+A collection of 500+ tests are frequently evaluated and completed during development, in order to verify that code changes do not introduce regression.
+Every analogy criterion, prediction score, searching and sorting functions, data manipulation, and so on, is tested.
+The integration tests specific to the analogue method rely on the results of another analogue sorting software developed in Grenoble.
+They result from a comparison work done with the help of R.
+Marty in order to ensure that the results of AtmoSwing are exactly equivalent to their model, given the same parameters and data.
+These tests are part of the checks carried out regularly, so that these results are always reproducible.
+
+\subsection{Modular approach}
+
+An AtmoSwing great strength is that it is designed to process analogy forecasting in a modular fashion.
+The structure of the analogy method (number of analogy levels, number of predictors) is built dynamically (Figure \ref{figure:flowchart_modules_atmoswing}), and nothing is fixed a priori.
+The software then performs successively as many analogy levels as the user specified, with all the predictors he wants.
+Each level of analogy processed results in an object containing target dates, analogue dates, values of the analogy criteria, and other data.
+This object can be saved in a NetCDF file and/or can be injected into a new analogy level.
+The whole structure of the method is defined in an XML file generated by the user.
+
+\begin{figure}[htbp]
+	\includegraphics[width=8.3cm]{figures/flowchart_modules_atmoswing.pdf}
+	\caption{Simplified organizational chart of the analogue method implementation in AtmoSwing.}
+	\label{figure:flowchart_modules_atmoswing}
+\end{figure}
+
+Each implementation of the analogue method (see section \ref{sec:method:evolution}) may enter this scheme, even if it consists of manipulated variables (e.g.
+moisture index).
+Various preprocessing functions are implemented, as the calculation of the moisture index or flux, multiplication operations or calculation of the gradients.
+The user can specify the preprocessing method and the predictors to use, dynamically, in the XML file.
+
+\subsection{Performance}
+
+Although processing an analogue forecast for a given target date is fast, when optimizing the method, forecasts are processed over a long periods of several decades, which is time consuming.
+Thus, great effort has been made in order to reduce the processing time to a minimum.
+Waste of time were identified with profiling tools and cut down at different levels.
+The software also use the linear algebra library Eigen 3 \citep{Guennebaud2010} for calculations on vectors and matrices, which resulted in time saving.
+Obviously, multi-threading is also implemented.
+
+First, every identified redundancy has been removed.
+Then, when looking for a certain date or data, the search looks first in the proximity where it is likely to be found instead of exploring an entire array.
+Similar data are not loaded twice, but shared pointers are used.
+Many other improvements allowed saving time, for example the use of the quicksort method \citep{Hoare1962a} to sort the date vectors according to the values of analogy criteria.
+Different implementations were tested (many remain in the code as alternatives) in order to select the most efficient: for example, when storing analogue dates according to their criteria value, it is faster to insert them in a fixed-size array rather than storing them all and sorting the array subsequently.
+
+The major performance gains were obtained by:
+\vspace*{-2mm}
+\begin{itemize}
+	\setlength\itemsep{-2px}
+	\item reduction of the array sizes used in the calculations,
+	\item use of pointers (and therefore the decrease of data copies),
+	\item better search for dates in temporal vectors starting from the previous index,
+	\item better management of the analogue vectors,
+	\item preprocessed gradients on geopotential fields when using the S1 criteria,
+	\item and finally the implementation of parallel calculations (multi-threading).
+\end{itemize}
+
+\section{AtmoSwing Forecaster}
+
+The Forecaster module allows to process operational forecasts.
+This software processes a current or past forecasting, defined by an XML file.
+A list of parameterizations (defined by external XML files) is processed successively.
+The software can compiled with a GUI (), or without in order to be used on a headless server through a command line interface.
+Processing a forecast requires very low computing capabilities and can be done on a low-end computer.
+
+\begin{figure}[htbp]
+	\includegraphics[width=8.3cm]{figures/atmoswing-forecaster.png}
+	\caption{Graphical user interface of the Forecaster module. A list of different parameterizations is being processed.}
+	\label{figure:atmoswing-forecaster-gui}
+\end{figure}
+
+The software first downloads the predictor describing the target situation, such as GFS outputs \citep[Global Forecast System,][see section \ref{sec:data}]{Kanamitsu1991,Kanamitsu1989}.
+It then interpolates the gridded data to match the resolution of the archive (for example 2.5\textdegree\ in the case of the NCEP/NCAP reanalysis I).
+The analogues dates are next sought according to the provided parameterization, and the predictand data are associated with the corresponding dates.
+The results are finally saved in auto-describing NetCDF files.
+If required, a synthetic XML is generated for an easier integration on a web platform for example.
+Every step of the forecast, from the predictor downloading to the final results, is done in the software (and controlled through configuration), without use of external scripts (e.g.
+for data conversion).
+
+The command-line interface allows to start the process for the most recent date, a selected past date, or the last $x$ days (as long as the predictors are available on the provider server).
+When there is nothing to process (no new predictor data available), the execution just stops, leading to no loss of computing resources.
+The recommended use is thus to set up a cron task on a Linux server in order to trigger the forecast every 30 minutes.
+When using GFS outputs, this would provide 4 forecasts a day with a reduced delay between GFS outputs availability and the analogue forecast.
+
+\section{AtmoSwing Viewer}
 % TODO: write
 
-\subsection{Structure}
-% TODO: write
-
-\subsection{Modular approach}
-% TODO: write
-
-\subsection{Technical specifications}
-% TODO: write
-% Language and libraries
-
-\subsection{Performance}
-% TODO: write
-
-\subsection{Unit tests}
-% TODO: write
-
-\section{The forecaster module}
-% TODO: write
-
-\section{The viewer module}
-% TODO: write
+Automatically loads the most recent forecasts
+GIS layers
+Workspace
+Alarm panel
+
+%When working on a region with different parameterizations per subregion, these parameterizations are applied to the wh
 
@@
 
-\section{The calibrator module}
+\section{AtmoSwing Optimizer}
 % TODO: write
@@
 \appendix
-\section{}    %% Appendix A
+\section{Appendix A}    %% Appendix A
 

### 2015-10-22 AtmoSwing - Geoscientific Model Development/template.tex
Adding the Viewer screenshots.

@@
 
+A user interface allows the creation of the precipitation database.
+Its generation consists in extracting the time series from text files in order to process them and save a database in the NetCDF format.
+During the process, Gumbel adjustments are automatically calculated in order to determine the values of different return periods.
+The time series are normalized by a selected return period (default 10~years) and their square root is eventually processed.
+The final database file contains both the raw and the normalized series, as well as characteristics of the gauging stations and some metadata.
+
 \section{AtmoSwing Viewer}
-% TODO: write
+
+The Viewer module allows displaying the resulting forecast files in an interactive GIS environment (Figure \ref{figure:atmoswing-viewer-gui}).
+
+\begin{figure*}[t]
+	\includegraphics[width=18cm]{figures/atmoswing-viewer.png}
+	\caption{Graphical user interface of the Viewer module.}
+	\label{figure:atmoswing-viewer-gui}
+\end{figure*}
+
+\begin{figure}[htbp]
+	\includegraphics[width=8.3cm]{figures/atmoswing-viewer-snail.png}
+	\caption{Visualization of multiple lead times on the map.}
+	\label{figure:atmoswing-viewer-snail}
+\end{figure}
+
+\begin{figure}[htbp]
+	\includegraphics[width=8.3cm]{figures/atmoswing-viewer-timeseries.png}
+	\caption{Visualization of the forecasted time series.}
+	\label{figure:atmoswing-viewer-timeseries}
+\end{figure}
+
+\begin{figure}[htbp]
+	\includegraphics[width=8.3cm]{figures/atmoswing-viewer-distribution.png}
+	\caption{Visualization of the forecasted precipitation distribution for a given lead time.}
+	\label{figure:atmoswing-viewer-distribution}
+\end{figure}
 
@@
 Alarm panel
+
+%
+%L'outil de visualisation présente plusieurs niveaux de synthèse des prévisions.
+L'utilisateur peut ainsi passer d'un aperçu très global des tendances au détail des analogues à la station.
+Les différents niveaux d'agrégation, du plus général au plus détaillé, sont les suivants:
+%
+%\begin{itemize}\addtolength{\itemsep}{0.5\baselineskip}
+%	\vspace{2mm}
+%	\item \textbf{Le panneau des alarmes}: après ouverture des fichiers de prévision, un panneau latéral (voir Figure \ref{fig:Atmoswing_viewer}) présente une grille synthétisant tous les modèles (lignes) et toutes les échéances (colonnes).
+La couleur affichée dans une cellule de la grille, correspondant donc à un modèle (paramétrisation de la méthode des analogues) et une échéance, est la valeur maximale prévue de toutes les stations (pour un temps de retour et un quantile choisi par l'utilisateur); ce panneau permet d'identifier en un coup d'?il si une situation critique est prévue pour au moins une station par un modèle et pour une échéance.
+%	
+%	\item \textbf{La carte des échéances}: la première carte proposée à l'utilisateur est une synthèse des prochaines échéances pour un modèle donné (Figure \ref{fig:Atmoswing_carte_echeances}).
+Nous avons conçu une représentation symbologique permettant un affichage synthétique: à l'emplacement de chaque station, une bande circulaire est affichée avec un casier par échéance.
+%	
+%	\newpage
+%	\vspace*{-30mm}
+%	
+%	Le nombre de casiers est ajusté au nombre d'échéances.
+La couleur attribuée à chaque casier est proportionnelle à la valeur prévue pour l'échéance en question.
+Cette représentation offre un rapide aperçu des jours à venir et permet d'identifier facilement un éventuel événement prévu par une paramétrisation des analogues.
+Elle offre une visualisation spatio-temporelle globale avant d'entrer davantage dans les détails du modèle.
+L'utilisateur peut passer d'un modèle à un autre en les sélectionnant dans la barre latérale (voir Figure \ref{fig:Atmoswing_viewer}).
+Il peut également ajuster la représentation des prévisions en choisissant une normalisation par un des nombreux temps de retour proposés, et en sélectionnant un quantile spécifique (20~\%, 60~\% ou 90~\%).
+%	
+%	\item \textbf{La carte journalière}: l'utilisateur peut ensuite afficher la carte pour une échéance du modèle (voir Figure \ref{fig:Atmoswing_carte_echeance_unique}) afin de mieux visualiser la spatialisation des précipitations et d'accéder directement aux valeurs attendues (affichées à chaque station).
+Un curseur situé sur le haut de la carte permet de changer d'échéance.
+%	
+%	\item \textbf{Les séries temporelles}: lorsqu'une station est sélectionnée (sur la carte ou dans la liste déroulante de la barre latérale), le graphique de la série temporelle prévue s'affiche (Figure \ref{fig:Atmoswing_serie_temporelle}).
+Les options d'affichage sont les suivantes:
+%	\begin{itemize}
+%		\item les 3 quantiles classiques (20~\%, 60~\%, 90~\%) sous forme de lignes bleues épaisses;
+%		\item tous les dixièmes de quantiles par des surfaces grisées;
+%		\item toutes les analogues sous forme de petites croix grises;
+%		\item les 5 ou 10 meilleures analogues par des croix jaunes, oranges, ou rouges.
+Les couleurs sont proportionnelles aux rangs des analogues.
+Le rouge est pour la meilleure analogue et le jaune pour la 5\ieme\ ou 10\ieme\ ;
+%		\item la valeur du temps de retour de 10 ans, ou de tous les temps de retour, sous la forme de traits rouges;
+%		\item les traces des anciennes prévisions, afin d'évaluer la cohérence temporelle.
+%	\end{itemize}
+%	
+%	\item \textbf{Les distributions}: pour une station et une date choisie, l'utilisateur peut visualiser les distributions du critère d'analogie (Figure \ref{fig:Atmoswing_distrib_critere}) et des précipitations (Figure \ref{fig:Atmoswing_distrib_precip}).
+La distribution du critère d'analogie permet d'identifier d'éventuelles discontinuités dans les valeurs des critères et donc de porter plus de crédit aux meilleures analogues.
+Le graphique des précipitations permet de comparer la distribution de toutes les analogues et celle des 5 ou 10 meilleures.
+%	
+%	\item \textbf{Le détail des analogues}: le détail des dates analogues, des valeurs du critère et des précipitations associées peut être affiché dans un tableur interactif (Figure \ref{fig:Atmoswing_liste_analogues}).
+%	
+%\end{itemize}
+%
+%\vfill\vfill\vfill
+%
+%\begin{figure}[htbp]
+%	\vspace*{2mm}
+%	\begin{center}
+%		\begin{minipage}[c]{10cm}
+%			\includegraphics[width=10cm]{Atmoswing_carte_echeances.jpg}
+%		\end{minipage}
+%		\hspace{0.5cm}
+%		\begin{minipage}[c]{3.8cm}
+%			\includegraphics[width=3.8cm]{Atmoswing_bande_echeances.pdf}
+%		\end{minipage}
+%	\end{center}
+%	\vspace{-2mm}
+%	\caption[Carte avec toutes les échéances, et symbole élaboré à cette fin.]{Carte avec toutes les échéances, et symbole élaboré à cette fin.}
+%	\label{fig:Atmoswing_carte_echeances}
+%\end{figure}
+%
+%\vfill\vfill\vfill
+%
+%\begin{figure}[htbp]
+%	\vspace*{2mm}
+%	\begin{center}
+%		\includegraphics[width=10cm]{Atmoswing_carte_echeance_unique.jpg}
+%	\end{center}
+%	\vspace{-2mm}
+%	\caption[Carte pour une échéance.]{Carte pour une échéance.}
+%	\label{fig:Atmoswing_carte_echeance_unique}
+%\end{figure}
+%
+%\begin{figure}[htbp]
+%	\vspace*{2mm}
+%	\begin{center}
+%		\includegraphics[width=10cm]{Atmoswing_serie_temporelle.jpg}
+%	\end{center}
+%	\vspace{-2mm}
+%	\caption[Graphique de l'évolution temporelle pour une station.]{Graphique de l'évolution temporelle pour une station.}
+%	\label{fig:Atmoswing_serie_temporelle}
+%\end{figure}
+%
+%\begin{figure}[htbp]
+%	\vspace*{2mm}
+%	\begin{center}
+%		\includegraphics[width=10cm]{Atmoswing_distrib_critere.jpg}
+%	\end{center}
+%	\vspace{-2mm}
+%	\caption[Graphique de la distribution du critère d'analogie des journées analogues.]{Graphique de la distribution du critère d'analogie des journées analogues.}
+%	\label{fig:Atmoswing_distrib_critere}
+%\end{figure}
+%
+%\begin{figure}[htbp]
+%	\vspace*{2mm}
+%	\begin{center}
+%		\includegraphics[width=10cm]{Atmoswing_distrib_precip.jpg}
+%	\end{center}
+%	\vspace{-2mm}
+%	\caption[Graphique de la distribution des valeurs de précipitations des journées analogues.]{Graphique de la distribution des valeurs de précipitations des journées analogues.}
+%	\label{fig:Atmoswing_distrib_precip}
+%\end{figure}
+%
+%\begin{figure}[htbp]
+%	\vspace*{2mm}
+%	\begin{center}
+%		\includegraphics[width=9cm]{Atmoswing_liste_analogues.jpg}
+%	\end{center}
+%	\vspace{-2mm}
+%	\caption[Liste des journées analogues et de leurs précipitations associées.]{Liste des journées analogues et de leurs précipitations associées.}
+%	\label{fig:Atmoswing_liste_analogues}
+%\end{figure}
+%
+%
+%Lors de la calibration (section \ref{sec:implementation:calibration}), nous avons déterminé des paramètres de la méthode des analogues optimaux pour certaines régions.
+Ces paramètres sont donc certainement plus robustes que s'ils avaient été établis directement à la station.
+Toutefois, lors du calcul de prévision, nous appliquons ces paramètres à l'échelle de la station individuelle.
+Ce choix a été fait pour offrir la plus grande résolution possible à l'utilisateur, dans le cadre du projet MINERVE.
+De plus, alors que les paramètres sont optimaux pour une région précise, ils sont ici appliqués à l'ensemble des stations.
+Nous avons donc une carte complète par modèle (paramétrisation).
+Le but de cette approche est d'éviter de mélanger des dates sur une même carte, et donc d'amalgamer différentes influences atmosphériques.
+Les divers modèles présentent toujours une répartition des précipitations cohérente spatialement, avec des tendances claires.
+Il incombe à l'utilisateur de choisir le modèle approprié pour la région où semble se profiler un événement.
+%
+%En plus des librairies listées précédemment, le logiciel de visualisation intègre:
+%\begin{itemize}
+%	\item VroomGIS: une bibliothèque SIG pour l'affichage de données géoréférencées, développé par L. Schreiber au CREALP (\textit{Centre de recherche sur l'environnement alpin});
+%	\item wxPlotCtrl: une librairie permettant d'afficher des graphiques interactifs.
+%\end{itemize}
+
+% + check annexe D.6
 
@@
 
-\subsection{Optimization}
+\subsection{Global optimization}
 

### 2015-10-27 AtmoSwing - Geoscientific Model Development/template.tex
The Viewer section is now written.

--- 2015-10-22 AtmoSwing - Geoscientific Model Development/template.tex
@@
 
-\runningtitle{TEXT}
-
-\runningauthor{TEXT}
+\runningtitle{AtmoSwing}
+
+\runningauthor{P. Horton et al.}
 
@@
 
+A user interface allows the creation of the precipitation database.
+Its generation consists in extracting the time series from text files in order to process them and save a database in the NetCDF format.
+During the process, Gumbel adjustments are automatically calculated in order to determine the values of different return periods.
+The time series are normalized by a selected return period (default 10~years) and their square root is eventually processed.
+The final database file contains both the raw and the normalized series, as well as characteristics of the gauging stations and some metadata.
+
 \section{AtmoSwing Viewer}
-% TODO: write
-
-Automatically loads the most recent forecasts
-GIS layers
-Workspace
-Alarm panel
-
-%When working on a region with different parameterizations per subregion, these parameterizations are applied to the wh
-
-%\citet{Djerboua2001} a appliqué la méthode développée par \citet{Guilbaud1997} en prévision opérationnelle dans le cadre du projet MAP \citep[\textit{Mesoscale Alpine Programme}, voir][]{Binder1996}, lors de la période spéciale d'observation \citep{Bougeault2001}.
-Il a relevé que le quantile 60~\% prévoyait le mieux les quantités de précipitations pour les situations normales, mais que lorsque la pluie observée était forte à extrême, le quantile 90~\% s'avérait être un meilleur témoin.
-Il convient donc de porter une attention particulière au quantile 90~\% qui, lorsqu'il monte brutalement, peut être le signe d'une situation propice à un événement de nature extrême, par la présence de plusieurs analogues dans la distribution avec des cumuls observés significatifs \citep{Djerboua2001}.
-En opérationnel, les prévisionnistes doivent prêter attention à la distribution des meilleures analogues.
-Si, par exemple, celle-ci est décalée vers des valeurs plus élevées, il y a un risque de sous-estimer l'événement.
-
-%En comparant les performances des modèles de Météo France avec la méthode des analogues, il en a conclu que les modèles numériques sont meilleurs pour la prévision du jour même, alors que les analogues deviennent plus concurrentielles (et meilleures pour les bassins de taille moyenne) pour les échéances suivantes.
-
-% En opérationnel, ce second niveau est pertinent jusqu'à une échéance de 3~jours. Au-delà, les prévisions d'humidité ne sont pas assez performantes pour être utiles.
-
-%En analysant les distributions de précipitations issues des analogues, \citet{Bontron2004} a identifié le quantile 60~\% comme étant le plus informatif pour l'occurrence des précipitations, et le quantile 90~\% pour la prévision des précipitations moyennes à fortes ($P > P10/10$, soit un dixième de la pluie décennale).
-
-%En opérationnel, ces niveaux supplémentaires se sont montrés utiles pour les deux à trois premières échéances, mais au-delà, toutes les méthodes deviennent équivalentes à l'analogie sur la circulation, car les autres variables, comme la vitesse verticale, sont alors mal prévues.
+
+\subsection{The graphical user interface }
+
+The Viewer module allows displaying the resulting forecast files in an interactive GIS environment (Figure \ref{figure:atmoswing-viewer-gui}).
+During the forecast, different parametrization variants of the same type of method may be applied to a region; the reason being that some parameterizations may be specific for a subregion, when its meteorological influences differ, which is often the case even in relatively small catchments \citep{Horton2012}.
+The Viewer automatically gathers the similar methods and provides a composite view of the optimal forecasts per subregion.
+The user can however choose to display a specific parameterization for the whole region, which is more consistent in terms of homogeneity of the analogue dates.
+
+\begin{figure*}[t]
+	\includegraphics[width=18cm]{figures/atmoswing-viewer.png}
+	\caption{Graphical user interface of the Viewer module.}
+	\label{figure:atmoswing-viewer-gui}
+\end{figure*}
+
+The software provides several levels of synthesis of the forecasts.
+When it is opened, it automatically loads the most recent forecasts.
+It first offers a quick overview of possible alerts by means of color codes on the lead time switcher (upper right in the GUI, see Figure \ref{figure:atmoswing-viewer-gui}), which synthesizes the worst case scenario, or in the alarms panel (on the left part of the GUI).
+The alarms panel offers a synthesis of the higher forecasted values over the region, for the different methods and the different lead times.
+By default, the colors are expressed relatively to 10-year return period values, for the $90^{th}$ percentile (can be changed in the preferences).
+This higher level of synthesis allows to quickly identify potential critical situations in the days ahead.
+
+Then, the user can explore the forecasts more in details, starting from the map provided by the GUI (Figure \ref{figure:atmoswing-viewer-gui}).
+The map display the forecast of the selected parameterization (upper left) and the selected lead time (upper right).
+The displayed method is by default a composite of the parameterization variants for the region, but the user can choose a specific parameterization for the whole region by opening the tree view and selecting a child element.
+We also allowed a display of all lead times on a single map by means of a symbolic representation on a circular band with a box for every lead time (Figure \ref{figure:atmoswing-viewer-snail}).
+The number of boxes is dynamically adjusted to the number of lead times.
+This representation offers a global spatiotemporal display for a chosen parameterization.
+
+Color scales in the map are easily controlled by choosing the predictand ratio (raw value or ratio to different return periods) and the quantile of the distribution (on the left part of the GUI).
+Representation relatively to a return time better expresses the meaning of a certain precipitation amount for a given region, as climatology can be drastically different between two locations in a mountainous area, even if they are close to each other.
+All information relative to a rain gauge station (or stations groups), such as its location, its name, or the values of different return periods, are stored in the forecast files, in order to be displayable for end users who do not have the predictand database.
+
+\begin{figure}[htbp]
+	\includegraphics[width=8.3cm]{figures/atmoswing-viewer-snail.png}
+	\caption{Visualization of multiple lead times on the map.}
+	\label{figure:atmoswing-viewer-snail}
+\end{figure}
+
+By clicking on a station (forecast points) on the map (or by selection in a dropdown list on the left), a new window appears with a plot of the forecasted time series (Figure \ref{figure:atmoswing-viewer-timeseries}).
+By default, the plot contains the usual 3 considered percentiles (90$^{th}$, 60$^{th}$, and 20$^{th}$), along with the 10 best analogues with a color code from yellow (10$^{th}$) to red (1$^{st}$).
+The 10 year return period is also displayed in order to put the forecast in perspective.
+The user can choose to hide any data or to display supplementary information (all analogues, all 10$^{th}$ percentiles, or all return periods) in the left panel.
+Traces of old forecasts are also automatically loaded and displayed in order to inform on the stability of the forecasts.
+
+\begin{figure}[htbp]
+	\includegraphics[width=8.3cm]{figures/atmoswing-viewer-timeseries.png}
+	\caption{Visualization of the forecasted time series.}
+	\label{figure:atmoswing-viewer-timeseries}
+\end{figure}
+
+\begin{figure}[htbp]
+	\includegraphics[width=8.3cm]{figures/atmoswing-viewer-distribution.png}
+	\caption{Visualization of the forecasted precipitation distribution for a given lead time.}
+	\label{figure:atmoswing-viewer-distribution}
+\end{figure}
+
+The user can even go into further details and display the predictand cumulative distribution for a given lead time (Figure \ref{figure:atmoswing-viewer-distribution}).
+This information is useful when working on extreme precipitation, as comparing the distribution of all analogues versus the 10 best analogues provides information in order to interpret the forecast (trend to under/overestimation).
+Distribution of the analogy criteria can also be displayed in order to identify eventual discontinuities in the criteria values.
+
+Finally, one can see the details of the analogue dates, along with the predictand and the criteria values in an interactive spreadsheet.
+
+AtmoSwing Viewer relies on workspaces to specify the path to the forecast directories and the GIS layers.
+Many GIS formats are supported thanks to the GDAL and VroomGIS libraries.
+One can have as many layers as desired, and can control their display properties.
+It is thus easy to switch from a forecast for a region to another by opening a workspace file (XML format).
+
+\subsection{Interpreting a forecast}
+
+\citet{Djerboua2001} applied the method developed by \citet{Guilbaud1997} in operational forecasting as part of the MAP project \citep[\textit{Mesoscale Alpine Programme}, see][]{Binder1996} during the special observation period \citep{Bougeault2001}.
+He noted that the 60$^{th}$ percentile was better to forecast precipitation amounts for common situations, but for strong to extreme events, the 90$^{th}$ percentile turned out to be a better indicator.
+It is therefore necessary to pay particular attention to the 90$^{th}$ percentile which, when reaching high values, may be indicative of a situation related to extreme precipitations, due the presence of several analogue dates with significant observed precipitations amounts in the distribution \citep{Djerboua2001}.
+\citet{Bontron2004} made the same observation: he found the 60$^{th}$ percentile to be best for occurrence forecasting, but the 90$^{th}$ percentile to be the most informative in order to forecast medium to high precipitation amounts ($P > P10/10$, one tenth of the 10-year return period value).
+In this regard, operators should pay particular attention to the distribution of the best analogues.
+If, for example, it is shifted to higher values, there is a risk of under-estimating the event when considering the middle of the full distribution.
+
+When comparing the performance of Meteo France numerical models along with the analogue method, \citet{Djerboua2001} concluded that the numerical models are better at predicting the current day, but the analogue method becomes more competitive for the following lead times.
+It is indeed very interesting in early warning approaches, as it is able to identify a potentially critical situation one week ahead.
+
+All analogy methods rely on atmospheric circulation information, while some add subsequent levels of analogy on moisture or other thermodynamic predictors (see section \ref{sec:method:evolution}).
+However, these subsequent predictors were found to be relevant only on the first 3~lead times, and not much further, due to higher uncertainties in their forecast.
+This was found to be the case of moisture indexes and vertical velocity.
+The user has to keep this aspect in mind when interpreting forecasts over a range of lead times.
 

### 2015-10-27 AtmoSwing - Geoscientific Model Development/template.tex
Adding verification scores.

@@
 \section{AtmoSwing Optimizer}
-% TODO: write
+
+AtmoSwing Optimizer is a single tool that integrates different optimization methods, presented in section \ref{sec:atmoswing-calibration} to \ref{sec:atmoswing-optimization}.
 
@@
 Validating the parameters of the analogue method is very important in order to avoid over-parametrization and thus to ensure that the statistical relationship is valid on another period.
-
-The accuracy of the parameters is evaluated by means of the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
+In order to account for climate change and the evolution of the measuring techniques, it is recommended to use a noncontinuous period for validating, distributed over the whole archive \citep{BenDaoud2010}.
+The user can thus specify a list of the years to keep for the validation and AtmoSwing Optimizer handles this aspect easily by both removing the validation years from possible candidate situations, and by automatically processing the validation score at the end of the optimization.
+
+\subsection{Implemented forecasts scores}
+
+Most often, the accuracy of the parameters for precipitations forecasting is evaluated by means of the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
+It is the only score we detail here (in section \ref{sec:prob_forecasts}).
+In addition, other scores are implemented in AtmoSwing Optimizer.
+The following sections list the scores presently available, but will not detail them.
+
+\subsubsection{Discrete deterministic forecasts}
+
+Deterministic forecasts consider no uncertainty.
+A single value is provided for a variable.
+The first group of this type of forecast is based on discrete values, also called categories.
+These scores are used, for example, to evaluate a deterministic prediction of threshold exceedance.
+In our case, the continuous probabilistic nature of an analogy forecast can be transformed into a discrete forecast by considering a threshold exceedance and a fixed percentile from the distribution.
+These scores rely on a contingency table, which is here a table containing the sums of observed / unobserved and predicted / unpredicted events \citep{Wilks2006}.
+On the basis of this table, multiple scores can be processed within AtmoSwing:
+
+\begin{itemize}
+	\setlength\itemsep{-1mm}
+	\item Proportion correct \citep{Finley1884}
+	\item Threat Score \citep{Gilbert1884}
+	\item Bias
+	\item False Alarm Ratio
+	\item Hit Rate or Probabiliy of Detection
+	\item False Alarm Rate
+	\item Heidke Skill Score \citep{Heidke1926}
+	\item Peirce Skill Score \citep{Peirce1884}
+	\item Gilbert Skill Score or Equitable Threat Score \citep{Gilbert1884}
+\end{itemize}
+
+\subsubsection{Continuous deterministic forecasts}
+
+The difference of the continuous deterministic forecasts compared to discrete ones is that they provide non-discrete values that must be evaluated with distance measures.
+In our application, the distribution of the analogues is summarized by a chosen percentile.
+Available scores are the following:
+
+\begin{itemize}
+	\setlength\itemsep{-1mm}
+	\item Mean Absolute Error
+	\item Root Mean Squared Error
+\end{itemize}
+
+\subsubsection{Discrete probabilistic forecasts}
+
+In the case of discrete probabilistic forecasts, we work with probabilities of occurrence or probability of belonging to a certain category. The implemented options are:
+
+\begin{itemize}
+	\setlength\itemsep{-1mm}
+	\item Brier Score \citep{Brier1950, Toth2003}
+	\item ROC diagramm \citep[Relative Operating Characteristic or Receiver Operating Characteristic,][]{Mason1982}
+	\item RPS \citep[Ranked Probability Score,][]{Epstein1969}
+	\item SEEPS \citep[Stable Equitable Error in Probability Space,][]{Rodwell2010,Rodwell2011}
+\end{itemize}
+
+\subsubsection{Continuous probabilistic forecasts}
+\label{sec:prob_forecasts}
+
+Continuous probabilistic forecasts of a variable are issued in the form of the expected statistical distribution for this variable.
+They are expressed either in terms of distribution or by probability density, which need to compared an observed value.
+This is the situation we meet when forecasting precipitations with the analogue method.
+
+We mainly rely on the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
 It allows assessing the predicted cumulative distribution functions $F(y)$ compared to the observed value $y^{0}$.
@@
 
-\subsection{Implemented forecasts scores}
-% TODO: write
+The CRPS can be decomposed into several indicators, also implemented into AtmoSwing Optimizer, such as:
+
+\begin{itemize}
+	\setlength\itemsep{-1mm}
+	\item Reliability \citep{Hersbach2000}
+	\item Resolution / uncertainty \citep{Hersbach2000}
+	\item Sharpness \citep{Bontron2004}
+	\item Accuracy \citep{Bontron2004}
+\end{itemize}
+
+Finally, the rank diagram \citep{Talagrand1997} and its accuracy as defined by \citet{Candille2005} are also available.
 
 \subsection{The classic calibration approach}
-\label{sec:classic}
-
-The calibration procedure that we call ''classic'' was developed by \citet{Bontron2004} at the LTHE laboratory (INPG, Grenoble).
+\label{sec:atmoswing-calibration}
+
+The calibration procedure that we call ''classic'', but which is also named optimization procedure \cite[eg.
+by ][]{BenDaoud2015}, was developed by \citet{Bontron2004} at the LTHE laboratory (INPG, Grenoble).
 It determines the optimal parameters for the different variables of each level of analogy.
-The analogy levels (eg the atmospheric circulation or moisture index) are calibrated sequentially.
+The analogy levels (eg.
+the atmospheric circulation or moisture index) are calibrated sequentially.
 The procedure consists of the following steps \citep{Bontron2004}:
@@
 	\begin{enumerate}
-		\item Identification of the most skilled unitary cell (1 point for moisture variables and 4 for the geopotential height when using the S1 criteria) over a large domain.
+		\item Identification of the most skilled unitary cell (1~point for moisture variables and 4 for the geopotential height when using the S1 criteria) over a large domain.
 Every point (or cell) of the full domain is assessed jointly on all predictors of the level of analogy (consisting generally of the same variable, but on different pressure levels and at different hours).
@@
 \subsection{Global optimization}
-
-\section{The global optimization tools}
+\label{sec:atmoswing-optimization}
+
+\section{Genetic algorithms}
 \label{sec:gas}
@@
 \appendix
-\section{Appendix A}    %% Appendix A
-
-\subsection{}                               %% Appendix A1, A2, etc.
+%\section{}    %% Appendix A
+
+%\subsection{}                               %% Appendix A1, A2, etc.
 
 \begin{acknowledgements}
-Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of.
-Thanks to Renaud Marty for his fruitful collaboration over the years.
+Thanks to Lucien Schreiber and Richard Metzger for their programming advices. Thanks to Renaud Marty for his active involvement in testing AtmoSwing against his code base.
 

### 2015-10-29 AtmoSwing - Geoscientific Model Development/template.tex
Monte Carlo section written.

@@
 
-\subsection{The classic calibration approach}
+\subsection{The sequential calibration}
 \label{sec:atmoswing-calibration}
 
-The calibration procedure that we call ''classic'', but which is also named optimization procedure \cite[eg.
+The calibration procedure that we call ''sequential'' or ''classic'', but which is also named ''optimization'' \cite[eg.
 by ][]{BenDaoud2015}, was developed by \citet{Bontron2004} at the LTHE laboratory (INPG, Grenoble).
-It determines the optimal parameters for the different variables of each level of analogy.
+It is a semi-automatic procedure that determines the optimal parameters for the different variables of each level of analogy.
 The analogy levels (eg.
@@
 
-The calibration is thus done in successive steps.
+The calibration is thus done in successive steps, on a limited number of parameters.
 Previously calibrated parameters are generally not reassessed.
 The advantage of this method is that it is fast, it provides acceptable results, and it has low computing requirements.
-We added small improvements to this method by allowing the spatial windows to do other moves, such as: (1) increase in 2 simultaneous directions, (2) decrease in 1 or 2 simultaneous directions, (3) expansion or contraction (in every direction), (4) shift of the window (without resizing) in 8 directions (including diagonals), and finally (5) all the moves described above, but with a factor of 2, 3, or more.
+
+We added small improvements to this method, and named it ''classic+'', by allowing the spatial windows to do other moves, such as: (1) increase in 2 simultaneous directions, (2) decrease in 1 or 2 simultaneous directions, (3) expansion or contraction (in every direction), (4) shift of the window (without resizing) in 8 directions (including diagonals), and finally (5) all the moves described above, but with a factor of 2, 3, or more.
 For example, we try to increase by 2 units in one (or more) direction.
 This allows to skip one size that may not be optimal.
-
 These supplementary steps often result in spatial windows that are a bit different, but the performance gain is rather marginal.
-These methods are available in the open source software AtmoSwing (Analogue Technique MOdel for Statistical Weather forecastING, www.atmoswing.org).
 
 \subsection{Monte-Carlo analysis}
+
+A Monte-Carlo analysis is also implemented in AtmoSwing.
+It performs thousands assessments of random parameters within given ranges.
+This method is not efficient to find the best parameters set, but helps to better understand the sensitivity of the parameters.
+
+For example, a Monte-Carlo analysis was performed on the PC-2Z (Table \ref{table:R1}) method for the southeastern crests on the upper Rh\^{o}ne catchment in Switzerland, with 10,000 random selections of its parameters according to a uniform law (the analysis was also performed in other subregions of the upper Rh\^{o}ne catchment in Switzerland, but the conclusions depicted here are similar).
+Unlike conventional calibration, the spatial windows on Z500 and Z1000 were not necessarily overlapping.
+Thus, 9 parameters were varying together (8 for the spatial windows and 1 for the number of analogues)
+
+Figure \ref{figure:monte_carlo_r1} presents the resulting scatter of random exploration of the parameters space, along with the results of the sequential calibration (red cross).
+Results are illustrated here for the 4 parameters defining the spatial window on Z500.
+Despite the high number of simulations, the upper portion of the distributions seems incomplete, and the score of the sequential calibration is not matched.
+Although the method is poor to find efficiently the best parameters, it is informative as to the shape of the scatter plots.
+
+The shape of the scatter plots from Figure \ref{figure:monte_carlo_r1} reveals a low sensitivity as to the exact location of the spatial windows.
+There is a maximum threshold for minimum longitudes and latitudes and, conversely, a minimum threshold for maximum latitudes and longitudes, but outside of these limits, the distribution slope is more gentle.
+A spatial window can thus be a bit larger than its optimal size without a significant drop in performance, as long as it includes at least one critical region.
+This was also observed by \citet{Bontron2004}, who noted that ''\textit{performance slowly decrease if we consider a slightly too large window, while the use of too small windows results in strong performance loss}''.
+The dilution of a part of the relevant synoptic information has therefore not necessarily a significant negative impact on performance, while ignoring some of this information leads to undesirable loss of performance.
+It is the same for the analogues number (not shown), for which, past an optimum, the upper slope of the distribution decreases slowly.
+
+\begin{figure}[htbp]
+	\includegraphics[width=8.3cm]{figures/monte_carlo_r1.png}
+	\caption{Example of a Monte Carlo analysis on the PC-2Z (Table \ref{table:R1}) method.
+Results are illustrated for the 4 parameters defining the spatial window on Z500, along with the results of the sequential calibration (red cross).}
+	\label{figure:monte_carlo_r1}
+\end{figure}
+
+The same analysis has been conducted on the method with 2 levels of analogy, PC-2Z-2MI (Table \ref{table:R2}), and the results on the number of analogues on the 1st and the 2nd level are illustrated in Figure \ref{figure:monte_carlo_r2}.
+One can see that the method is not very sensitive to the number of analogues on the first level of analogy, when considering a second level afterwards, as long as this number is not too small.
+The trend on the second level is more apparent, but a large tolerance seems possible.
+
+\begin{figure}[htbp]
+	\includegraphics[width=8.3cm]{figures/monte_carlo_r2.png}
+	\caption{Example of a Monte Carlo analysis on the PC-2Z-2MI (Table \ref{table:R2}) method.
+Results are illustrated for the number of analogues on the 1st and 2nd level of analogy, along with the results of the sequential calibration (red cross).}
+	\label{figure:monte_carlo_r2}
+\end{figure}
+
+The use of such a random method allows informing on the parameters sensitivity, and so on the importance of the expected precision of the calibration results.
+It helps understanding how different parameterizations can end up to relatively similar performances.
+Using Mote Carlo analyses allows to easily display the parameters sensitivity while allowing a high degree of freedom to the method.
 
@@
 \label{sec:atmoswing-optimization}
+
+The sequential calibration cannot optimize all parameters of the method, as several are manually selected, such as the meteorological variable, the pressure level and the temporal windows.
+Testing multiple combinations of these can be cumbersome, especially when considering multiple predictors within the same level of analogy.
+Moreover, the parameters are calibrated successively within the same level of analogy, and in-between them.
+
+We thus decided to explore optimization techniques that can handle all parameters fully automatically.
+We first assessed the \citet{Nelder1965a} method, which was found to be unsuitable for this purpose.
+Due to the complexity of the method and its non-linearity, a technique of global optimization is required.
+We thus implemented Genetic algorithms in AtmoSwing Optimizer in order to perform a global optimization of the analogue method.
+This article is not about discussing the results of such a technique, but describing the details of the implementation.
+The demonstration of the benefit brought by such an approach is the topic of another article.
+The details of the implementation being numerous, the description is provided in the next dedicated section (\ref{sec:gas}).
 

### 2015-10-29 AtmoSwing - Geoscientific Model Development/template.tex
Using the AM abbreviation.

@@
 
-As AtmoSwing does not rely heavily on one variant of the analogue method, but can implement different parametrization, we gathered here several references of possible implementations as well as the main evolution steps of the analogue method.
+As AtmoSwing does not rely heavily on one variant of the analogue method (AM), but can implement different parametrization, we gathered here several references of possible implementations as well as the main evolution steps of the AM.
 This latter summarizes the improvements that were brought, as well as discontinued approaches that were found less relevant (such as the use of PCA on the predictors).
@@
 
-The analogue method is based on the principle that two similar synoptic situations may produce similar local effects \citep{Lorenz1956}.
+The AM is based on the principle that two similar synoptic situations may produce similar local effects \citep{Lorenz1956}.
 The perfect analogy does not exist, but sufficiently similar situations leading to similar effects can be identified.
@@
 Because of the chaotic nature of the atmosphere, two analogue situations quickly diverge over time \citep{Lorenz1969}.
-Thus, the method has strong limitations regarding the temporal extrapolation \citep{Bontron2004}.
+Thus, the AM has strong limitations regarding the temporal extrapolation \citep{Bontron2004}.
 Numerical models being more capable of simulating the dynamic evolution of the atmosphere, the temporal extrapolation of the synoptic variables is left to them.
@@
 
-The analogue method is being used for many years at EDF (\'{E}lectricit\'{e} de France), to build precipitation and temperature scenarios \citep{Desaint2008a}.
+The AM is being used for many years at EDF (\'{E}lectricit\'{e} de France), to build precipitation and temperature scenarios \citep{Desaint2008a}.
 It is also operational at the Compagnie Nationale du Rh\^{o}ne (CNR, France) and some flood forecasting services (SPC) in France and Switzerland \citep{Marty2010,GarciaHernandez2009b,Horton2012}.
@@
 
-The analogue method relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series we want to forecast.
+The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series we want to forecast.
 
@@
 
-Although multiple variations of the method exist, they generally share the same basics and the same structure.
+Although multiple variations of the AM exist, they generally share the same basics and the same structure.
 We want here to forecast the daily precipitation (the predictand) for a target day (at a defined lead time) and have long archives of both the predictand and predictor variables.
@@
 
-Variants of the analogue method parameterization are numerous and it is not always easy to reference them in a short and descriptive way.
+Variants of the AM parameterization are numerous and it is not always easy to reference them in a short and descriptive way.
 We thus propose a basic nomenclature (Figure \ref{figure:nomenclature}) in order to give an idea of the structure in a simple identifier.
-This one cannot describe all the parameters of the method, but quickly illustrate the structure of the implementation.
-This is particularly useful when working with a global optimization method, where nothing is fixed but the very structure of the method.
+This one cannot describe all the parameters of the AM, but quickly illustrate the structure of the implementation.
+This is particularly useful when working with a global optimization method, where nothing is fixed but the very structure of the AM.
 
@@
 	\includegraphics[width=8.3cm]{figures/nomenclature.pdf}
-	\caption{Proposed structure for naming the parameterizations of the analogue method.}
+	\caption{Proposed structure for naming the parameterizations of the AM.}
 	\label{figure:nomenclature}
@@
 The naming contains different blocs (separated by an hyphen) for the various levels of analogy.
-It starts with the specification of the preselection (P; can be omitted when comparing methods with the same preselection approaches), which can be nowadays of 2 types:
+It starts with the specification of the preselection (P; can be omitted when comparing AMs with the same preselection approaches), which can be nowadays of 2 types:
 \begin{itemize}
@@
 
-The evolution of the analogue method for precipitation forecasting led to several improvements.
+The evolution of the AM for precipitation forecasting led to several improvements.
 However, some of these are specific for a certain region and are not relevant for others, and some perform better depending on the lead time.
-Thereby, we cannot provide a single best parameterization for the method, neither rank them from worst to best.
-We will thus provide some examples of parameterizations of the most recent method variant, in the chronological order they appeared.
-The most common usage of the analogue method is for precipitation forecasting.
+Thereby, we cannot provide a single best parameterization for the AM, neither rank them from worst to best.
+We will thus provide some examples of parameterizations of the most recent AM variant, in the chronological order they appeared.
+The most common usage of the AM is for precipitation forecasting.
 Thus, the evolution presented hereafter focuses on this predictand.
-However, the analogue method, or an equivalent, was also used for short to medium term forecasting of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
-\citet{Guilbaud1997} performed a literature review about the use of the analogue method in long-term forecasting and identified operational applications for monthly forecasts in many countries, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal forecasts: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
-
-\citet{Lorenz1969} introduced the concept and established the basis of the method.
+However, the AM, or an equivalent, was also used for short to medium term forecasting of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+\citet{Guilbaud1997} performed a literature review about the use of the AM in long-term forecasting and identified operational applications for monthly forecasts in many countries, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal forecasts: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
+
+\citet{Lorenz1969} introduced the concept and established the basis of the AM.
 He considered looking for analogues on the geopotential field (at 200, 500 and 850~hPa) with a corrected Euclidean distance averaged on the 3 levels.
@@
 
-The use of the analogue method for operational forecasting of daily precipitation originates in the work of \citet{Duband1970, Duband1974, Duband1981}.
+The use of the AM for operational forecasting of daily precipitation originates in the work of \citet{Duband1970, Duband1974, Duband1981}.
 It was then designed for operational forecasting at EDF (\'{E}lectricit\'{e} de France) in order to better manage water resources and flood risks.
@@
 \citet{Yacowar1975} considered the 20 best analogues on the maximum of the sum of correlations on the two fields.
-This work has demonstrated the best performance of the analogues method compared to regression methods, as well as the interest to search for analogues on two (500 and 1000~hPa) geopotential fields combined \citep{Guilbaud1997}.
+This work has demonstrated the best performance of the AM compared to regression methods, as well as the interest to search for analogues on two (500 and 1000~hPa) geopotential fields combined \citep{Guilbaud1997}.
 
@@
 \citet{Bontron2004} could benefit from the newly available NCEP/NCAR reanalysis data.
-This dataset being more homogeneous, much longer, and contained more variables than what was previously used, he could systematically assess a large selection of variables in the analogue method combined with different criteria.
+This dataset being more homogeneous, much longer, and contained more variables than what was previously used, he could systematically assess a large selection of variables in the AM combined with different criteria.
 He thus confirmed the interest of the geopotential height along with the S1 criterion for the first level of analogy.
-He has also shown that the choice of the temporal window (time of observation) has a higher importance than the atmospheric level for the performance of the method.
+He has also shown that the choice of the temporal window (time of observation) has a higher importance than the atmospheric level for the performance of the AM.
 By assessing multiple combinations of atmospheric levels and temporal windows, he concluded that the coupled geopotential heights at 1000~hPa (Z1000) \& 12~h and 500~hPa (Z500) \& 24~h provided the best performance for the studied region (Table \ref{table:R1}).
@@
 
-\citet{Gibergans-Baguena2007} implemented the method for daily precipitation forecasts in Catalonia.
+\citet{Gibergans-Baguena2007} implemented the AM for daily precipitation forecasts in Catalonia.
 They considered the geopotential at 700 and 1000~hPa, and the thickness between these two levels, to search for analogy of circulation, and then applied a second selection on local data from radiosonde: stability indexes, precipitable water, temperature, etc.
@@
 
-\citet{BenDaoud2010} applied the analogue method in the context of large floodplains, out of an Alpine environment (Sa\^{o}ne, Seine).
+\citet{BenDaoud2010} applied the AM in the context of large floodplains, out of an Alpine environment (Sa\^{o}ne, Seine).
 He evaluated several variables usually used in weather forecasting, amongst them the air temperature and the vertical velocity that presented a potential interest.
@@
 Subsequently, \citet{BenDaoud2010} added an additionally level of analogy, between the circulation and the moisture analogy (Table \ref{table:R5}), based on vertical velocity at 850~hPa (W850).
-This method was developed for large plains in France, but was found to be not relevant for an Alpine environment where topography is mostly responsible for uplift of air masses \citep{Horton2012}.
+This AM was developed for large plains in France, but was found to be not relevant for an Alpine environment where topography is mostly responsible for uplift of air masses \citep{Horton2012}.
 
@@
 However, he noticed that there is a risk of overparametrization and a simplification of the weighting fields may be necessary, and that the performance was not stable between the calibration and the validation periods.
-He also compare the performance of the analogues method with a forecasting method based on a weather types approach, and concluded that the analogues method was more efficient.
+He also compare the performance of the AM with a forecasting method based on a weather types approach, and concluded that the AM was more efficient.
 
@@
 No number of analogues ($N_{1}$) was provided globally, as it was calibrated for every subregion.
-Considering a method only based on the atmospheric circulation has an interest for operational forecasting, where moisture variables are less well forecasted over a lead time of a few days.
+Considering a AM only based on the atmospheric circulation has an interest for operational forecasting, where moisture variables are less well forecasted over a lead time of a few days.
 An equivalent structure was also optimized by means of generic algorithms (PC-4Zgo), which is the topic of another paper.
@@
 
-A version of the analogue method was evaluated during the project STARDEX \citep[\textit{STAtistical and Regional dynamical Downscaling of EXtremes for European regions}, see][]{Goodess2003, Stardex2005}.
-One of the project goals was to compare various downscaling methods for the determination of weather extremes, and the analogue method was selected among the most interesting from various techniques \citep{Maheras2005, Schmidli2007}.
+A version of the AM was evaluated during the project STARDEX \citep[\textit{STAtistical and Regional dynamical Downscaling of EXtremes for European regions}, see][]{Goodess2003, Stardex2005}.
+One of the project goals was to compare various downscaling methods for the determination of weather extremes, and the AM was selected among the most interesting from various techniques \citep{Maheras2005, Schmidli2007}.
 Its use as adaptation method of climate models is also the subject of a growing number of studies \citep{Zorita1999, Wetterhall2005, Wetterhall2007, Matulla2007, Chardon2014, Dayon2015}.
@@
 \citet{Hamill2006} used an analogy based approach on the GFS reforecasts in order to correct systematic errors in the ensemble forecasts of temperature and precipitation.
-Indeed, the statistical approach showed some bias in estimates of the numerical model, which may have been adjusted by taking into account the intrinsic local climatology from the analogues method.
+Indeed, the statistical approach showed some bias in estimates of the numerical model, which may have been adjusted by taking into account the intrinsic local climatology from the AM.
 Moreover, the under-dispersion of the ensemble forecast from the numerical model has been corrected using analogues \citep{Hamill2006}.
-Correction of ensemble forecast under-dispersion by means of the analogue method is also used operationally at EDF.
-
-\citet{Bliefernicht2010} observed that the performance of the analogue method is higher for winter than for summer.
+Correction of ensemble forecast under-dispersion by means of the AM is also used operationally at EDF.
+
+\citet{Bliefernicht2010} observed that the performance of the AM is higher for winter than for summer.
 The relationship between synoptic predictors and local rainfall is lower in summer, due to convective precipitation that present a higher spatial variability and that depend on other parameters.
@@
 
-One of the method limitations is the need for a substantial archive of the predictand variable, for example measured precipitations.
-Without data on several decades, the method is not applicable.
+One of the AM limitations is the need for a substantial archive of the predictand variable, for example measured precipitations.
+Without data on several decades, the AM is not applicable.
 Long predictor archives are also required, but this problem is usually solved with reanalysis data, which are not perfect in terms of homogeneity, but can be considered of sufficient quality.
-Moreover,  reanalysis data are available all around the world, which represent a great potential for the analogue method.
+Moreover,  reanalysis data are available all around the world, which represent a great potential for the AM.
 Another issue, still about data, concerns the operational forecasting: predictors describing forecasted target situations and the ones from the archive are not fully homogeneous, as they usually don't result from the same model.
@@
 Thus, if the archive of weather situations is long enough, it is reasonable to assume that a large part of future situations is already represented, even those whose frequency will change under different climatic conditions \citep{Wetterhall2005}.
-In addition, climate change is relatively slow, and through continuous updating of the archive, the analogue method will incorporate new information progressively with no big discontinuity.
+In addition, climate change is relatively slow, and through continuous updating of the archive, the AM will incorporate new information progressively with no big discontinuity.
 
@@
 Every analogy criterion, prediction score, searching and sorting functions, data manipulation, and so on, is tested.
-The integration tests specific to the analogue method rely on the results of another analogue sorting software developed in Grenoble.
+The integration tests specific to the  AM rely on the results of another analogue sorting software developed in Grenoble.
 They result from a comparison work done with the help of R.
@@
 An AtmoSwing great strength is that it is designed to process analogy forecasting in a modular fashion.
-The structure of the analogy method (number of analogy levels, number of predictors) is built dynamically (Figure \ref{figure:flowchart_modules_atmoswing}), and nothing is fixed a priori.
+The structure of the AM (number of analogy levels, number of predictors) is built dynamically (Figure \ref{figure:flowchart_modules_atmoswing}), and nothing is fixed a priori.
 The software then performs successively as many analogy levels as the user specified, with all the predictors he wants.
@@
 This object can be saved in a NetCDF file and/or can be injected into a new analogy level.
-The whole structure of the method is defined in an XML file generated by the user.
+The whole structure of the AM is defined in an XML file generated by the user.
 
@@
 	\includegraphics[width=8.3cm]{figures/flowchart_modules_atmoswing.pdf}
-	\caption{Simplified organizational chart of the analogue method implementation in AtmoSwing.}
+	\caption{Simplified organizational chart of the AM implementation in AtmoSwing.}
 	\label{figure:flowchart_modules_atmoswing}
@@
 
-Each implementation of the analogue method (see section \ref{sec:method:evolution}) may enter this scheme, even if it consists of manipulated variables (e.g.
+Each implementation of the AM (see section \ref{sec:method:evolution}) may enter this scheme, even if it consists of manipulated variables (e.g.
 moisture index).
@@
 
-Although processing an analogue forecast for a given target date is fast, when optimizing the method, forecasts are processed over a long periods of several decades, which is time consuming.
+Although processing an analogue forecast for a given target date is fast, when optimizing the AM, forecasts are processed over a long periods of several decades, which is time consuming.
 Thus, great effort has been made in order to reduce the processing time to a minimum.
@@
 The Viewer module allows displaying the resulting forecast files in an interactive GIS environment (Figure \ref{figure:atmoswing-viewer-gui}).
-During the forecast, different parametrization variants of the same type of method may be applied to a region; the reason being that some parameterizations may be specific for a subregion, when its meteorological influences differ, which is often the case even in relatively small catchments \citep{Horton2012}.
-The Viewer automatically gathers the similar methods and provides a composite view of the optimal forecasts per subregion.
+During the forecast, different parametrization variants of the same type of AM may be applied to a region; the reason being that some parameterizations may be specific for a subregion, when its meteorological influences differ, which is often the case even in relatively small catchments \citep{Horton2012}.
+The Viewer automatically gathers the similar AMs and provides a composite view of the optimal forecasts per subregion.
 The user can however choose to display a specific parameterization for the whole region, which is more consistent in terms of homogeneity of the analogue dates.
@@
 It first offers a quick overview of possible alerts by means of color codes on the lead time switcher (upper right in the GUI, see Figure \ref{figure:atmoswing-viewer-gui}), which synthesizes the worst case scenario, or in the alarms panel (on the left part of the GUI).
-The alarms panel offers a synthesis of the higher forecasted values over the region, for the different methods and the different lead times.
+The alarms panel offers a synthesis of the higher forecasted values over the region, for the different AMs and the different lead times.
 By default, the colors are expressed relatively to 10-year return period values, for the $90^{th}$ percentile (can be changed in the preferences).
@@
 The map display the forecast of the selected parameterization (upper left) and the selected lead time (upper right).
-The displayed method is by default a composite of the parameterization variants for the region, but the user can choose a specific parameterization for the whole region by opening the tree view and selecting a child element.
+The displayed AM is by default a composite of the parameterization variants for the region, but the user can choose a specific parameterization for the whole region by opening the tree view and selecting a child element.
 We also allowed a display of all lead times on a single map by means of a symbolic representation on a circular band with a box for every lead time (Figure \ref{figure:atmoswing-viewer-snail}).
@@
 
-\citet{Djerboua2001} applied the method developed by \citet{Guilbaud1997} in operational forecasting as part of the MAP project \citep[\textit{Mesoscale Alpine Programme}, see][]{Binder1996} during the special observation period \citep{Bougeault2001}.
+\citet{Djerboua2001} applied the AM developed by \citet{Guilbaud1997} in operational forecasting as part of the MAP project \citep[\textit{Mesoscale Alpine Programme}, see][]{Binder1996} during the special observation period \citep{Bougeault2001}.
 He noted that the 60$^{th}$ percentile was better to forecast precipitation amounts for common situations, but for strong to extreme events, the 90$^{th}$ percentile turned out to be a better indicator.
@@
 
-When comparing the performance of Meteo France numerical models along with the analogue method, \citet{Djerboua2001} concluded that the numerical models are better at predicting the current day, but the analogue method becomes more competitive for the following lead times.
+When comparing the performance of Meteo France numerical models along with the AM, \citet{Djerboua2001} concluded that the numerical models are better at predicting the current day, but the AM becomes more competitive for the following lead times.
 It is indeed very interesting in early warning approaches, as it is able to identify a potentially critical situation one week ahead.
 
-All analogy methods rely on atmospheric circulation information, while some add subsequent levels of analogy on moisture or other thermodynamic predictors (see section \ref{sec:method:evolution}).
+All AMs rely on atmospheric circulation information, while some add subsequent levels of analogy on moisture or other thermodynamic predictors (see section \ref{sec:method:evolution}).
 However, these subsequent predictors were found to be relevant only on the first 3~lead times, and not much further, due to higher uncertainties in their forecast.
@@
 
-The calibration of the analogue method is usually carried out in a perfect prognosis \citep{Klein1959} framework \citep{BenDaoud2010, Bontron2004}.
+The calibration of the AM is usually carried out in a perfect prognosis \citep{Klein1959} framework \citep{BenDaoud2010, Bontron2004}.
 Perfect prognosis uses observed or reanalyzed data to calibrate the relationship between predictors and predictands.
@@
 Finally, the length of reanalyses datasets are usually much longer than reforecast datasets, which allows us to identify more robust relationships.
-The size of the archive is indeed an important criteria for the analogue method.
+The size of the archive is indeed an important criteria for the AM.
 
@@
 It consists of an independent period that is never used as target neither candidate date.
-Validating the parameters of the analogue method is very important in order to avoid over-parametrization and thus to ensure that the statistical relationship is valid on another period.
+Validating the parameters of the AM is very important in order to avoid over-parametrization and thus to ensure that the statistical relationship is valid on another period.
 In order to account for climate change and the evolution of the measuring techniques, it is recommended to use a noncontinuous period for validating, distributed over the whole archive \citep{BenDaoud2010}.
@@
 They are expressed either in terms of distribution or by probability density, which need to compared an observed value.
-This is the situation we meet when forecasting precipitations with the analogue method.
+This is the situation we meet when forecasting precipitations with the AM.
 
@@
 
-For example, a Monte-Carlo analysis was performed on the PC-2Z (Table \ref{table:R1}) method for the southeastern crests on the upper Rh\^{o}ne catchment in Switzerland, with 10,000 random selections of its parameters according to a uniform law (the analysis was also performed in other subregions of the upper Rh\^{o}ne catchment in Switzerland, but the conclusions depicted here are similar).
+For example, a Monte-Carlo analysis was performed on the PC-2Z (Table \ref{table:R1}) AM for the southeastern crests on the upper Rh\^{o}ne catchment in Switzerland, with 10,000 random selections of its parameters according to a uniform law (the analysis was also performed in other subregions of the upper Rh\^{o}ne catchment in Switzerland, but the conclusions depicted here are similar).
 Unlike conventional calibration, the spatial windows on Z500 and Z1000 were not necessarily overlapping.
@@
 	\includegraphics[width=8.3cm]{figures/monte_carlo_r1.png}
-	\caption{Example of a Monte Carlo analysis on the PC-2Z (Table \ref{table:R1}) method.
+	\caption{Example of a Monte Carlo analysis on the PC-2Z (Table \ref{table:R1}) AM.
 Results are illustrated for the 4 parameters defining the spatial window on Z500, along with the results of the sequential calibration (red cross).}
@@
 
-The same analysis has been conducted on the method with 2 levels of analogy, PC-2Z-2MI (Table \ref{table:R2}), and the results on the number of analogues on the 1st and the 2nd level are illustrated in Figure \ref{figure:monte_carlo_r2}.
-One can see that the method is not very sensitive to the number of analogues on the first level of analogy, when considering a second level afterwards, as long as this number is not too small.
+The same analysis has been conducted on the AM with 2 levels of analogy, PC-2Z-2MI (Table \ref{table:R2}), and the results on the number of analogues on the 1st and the 2nd level are illustrated in Figure \ref{figure:monte_carlo_r2}.
+One can see that the AM is not very sensitive to the number of analogues on the first level of analogy, when considering a second level afterwards, as long as this number is not too small.
 The trend on the second level is more apparent, but a large tolerance seems possible.
@@
 	\includegraphics[width=8.3cm]{figures/monte_carlo_r2.png}
-	\caption{Example of a Monte Carlo analysis on the PC-2Z-2MI (Table \ref{table:R2}) method.
+	\caption{Example of a Monte Carlo analysis on the PC-2Z-2MI (Table \ref{table:R2}) AM.
 Results are illustrated for the number of analogues on the 1st and 2nd level of analogy, along with the results of the sequential calibration (red cross).}
@@
 It helps understanding how different parameterizations can end up to relatively similar performances.
-Using Mote Carlo analyses allows to easily display the parameters sensitivity while allowing a high degree of freedom to the method.
+Using Mote Carlo analyses allows to easily display the parameters sensitivity while allowing a high degree of freedom to the AM.
 
@@
 
-The sequential calibration cannot optimize all parameters of the method, as several are manually selected, such as the meteorological variable, the pressure level and the temporal windows.
+The sequential calibration cannot optimize all parameters of the AM, as several are manually selected, such as the meteorological variable, the pressure level and the temporal windows.
 Testing multiple combinations of these can be cumbersome, especially when considering multiple predictors within the same level of analogy.
@@
 We first assessed the \citet{Nelder1965a} method, which was found to be unsuitable for this purpose.
-Due to the complexity of the method and its non-linearity, a technique of global optimization is required.
-We thus implemented Genetic algorithms in AtmoSwing Optimizer in order to perform a global optimization of the analogue method.
+Due to the complexity of the AM and its non-linearity, a technique of global optimization is required.
+We thus implemented Genetic algorithms in AtmoSwing Optimizer in order to perform a global optimization of the AM.
 This article is not about discussing the results of such a technique, but describing the details of the implementation.
@@
 
-Practically, GAs allow rapidly approaching satisfactory solutions, but they do not provide the optimum solution for sure \citep{Zitzler2004a}.
-It is indeed mainly a matter of time.
-When the optimizer gets closer to the global optimum, any new improvement takes more time to appear (see figure \ref{fig:evolution}), and the final adjustment of the parameters is very time consuming \citep{Back1993a}.
-For problems that require a significant amount of time in order to evaluate the objective function, as in our case, we have to limit the number of generations to get reasonable processing time.
-Thus, different acceptable solutions can result from one or more optimizations \citep{Holland1992b}.
-This is a strength and a weakness of GAs: they are very good at exploring complex parameter spaces in order to identify the most promising areas, but they will not necessarily find the best solution with the optimal values of all parameters \citep{Holland1992b}.
-
 \subsection{Structure and operators}
@@
 The GAs optimize a population of individuals (parameter sets).
-Each individual contains a chromosome (parameters of the analogue method in our case).
+Each individual contains a chromosome (parameters of the AM in our case).
 We call gene every parameter that constitutes the chromosome.
@@
 The first step of the optimization is to generate the initial population.
-A population is a set of $N$ individuals (each of which represents a point in the space of potential solutions, a parameter set of the analogue method in our application) that we are going to make evolve.
+A population is a set of $N$ individuals (each of which represents a point in the space of potential solutions, a parameter set of the AM in our application) that we are going to make evolve.
 A generation is the population at a given time.
@@
 
-One of our goals being to make recommendations of parametrization in order to optimize the analogue method, we proceeded systematically.
+One of our goals being to make recommendations of parametrization in order to optimize the AM, we proceeded systematically.
 The results are summarized hereafter \citep[see][for the details]{Horton2012a}.
@@
 
-	$50<N<100$ for a very simple implementation of the analogue method (1 level of analogy with 2 pressure levels),
-
-	$N\approx200$ for a bit more complex method (1 level of analogy with 4 pressure levels, or 2 level of analogy with less pressure levels),
-
-	$N\approx500$ for significantly more complex methods (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the moisture analogy),
+	$50<N<100$ for a very simple implementation of the AM (1 level of analogy with 2 pressure levels),
+
+	$N\approx200$ for a bit more complex AM (1 level of analogy with 4 pressure levels, or 2 level of analogy with less pressure levels),
+
+	$N\approx500$ for significantly more complex AMS (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the moisture analogy),
 
 	We didn't find any improvement with $N>500$, the results were even surprisingly of a lower quality.
-However, this cannot be generalized and depends on the analogue method to optimize, and supposedly on the characteristics of the processes generating the precipitations in a given region.
+However, this cannot be generalized and depends on the AM to optimize, and supposedly on the characteristics of the processes generating the precipitations in a given region.
 
@@
 	\item \textbf{Mutation}: we compared the 10 mutation operators with different options, bringing the number of variations of this operator up to 110.
-We immediately observed that the mutation operator has a very important role on the performance of the optimizations of the analogue method, and that the other reproduction operators seem of secondary importance.
+We immediately observed that the mutation operator has a very important role on the performance of the optimizations of the AM, and that the other reproduction operators seem of secondary importance.
 This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction.
@@
 The difficulty is that the optimal value seems to be very case-related.
-Indeed, by even changing the precipitation time series (ie optimizing for another subregion), but not the complexity of the analogue method, the optimal mutation rate changes, making it impossible to estimate in advance.
+Indeed, by even changing the precipitation time series (ie optimizing for another subregion), but not the complexity of the AM, the optimal mutation rate changes, making it impossible to estimate in advance.
 
@@
 
-We evaluated the optimization by genetic algorithms on methods of varying complexity, with a large number of combinations of operators to be able to make recommendations for optimizing the analogue method.
+We evaluated the optimization by genetic algorithms on AMs of varying complexity, with a large number of combinations of operators to be able to make recommendations for optimizing the AM.
 Our conclusions are:
@@
 
-	\item The population size should be in accordance with the complexity of the method to optimize: from 50 for the simple ones, up to 500 for the most complex methods.
+	\item The population size should be in accordance with the complexity of the AM to optimize: from 50 for the simple ones, up to 500 for the most complex AMs.
 
@@
 
-In order to make an optimization of the analogue method with genetic algorithms, it may be wise to consider these three mutation operators in parallel.
+In order to make an optimization of the AM with genetic algorithms, it may be wise to consider these three mutation operators in parallel.
 We would then combine algorithms that are sometimes faster to other that are more robust.
-In order to be confident in the optimized methods, we propose using a set of the following mutation operators:
+In order to be confident in the optimized AMs, we propose using a set of the following mutation operators:
 

### 2015-10-29 AtmoSwing - Geoscientific Model Development/template.tex
Editing the GAs section.

@@
 
-\section{Genetic algorithms}
+\section{Optimization using Genetic algorithms}
 \label{sec:gas}
@@
 The divergences are the operators implementation, through significantly different algorithms, which has an important effect on the results \citep{Gaffney2010a}.
+
+\begin{figure}[htb]
+	\includegraphics[width=8.3cm]{figures/figure_structure_gas.pdf}
+	\caption{Genetic algorithms operational flowchart}
+	\label{fig:structure_gas}
+\end{figure}
 
@@
 
-	$N\approx500$ for significantly more complex AMS (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the moisture analogy),
+	$N\approx500$ for significantly more complex AMs (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the moisture analogy),
 
@@
 \begin{acknowledgements}
-Thanks to Lucien Schreiber and Richard Metzger for their programming advices. Thanks to Renaud Marty for his active involvement in testing AtmoSwing against his code base.
+Thanks to Lucien Schreiber and Richard Metzger for their programming advices.
+Thanks to Renaud Marty for his active involvement in testing AtmoSwing against his code base.
+Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of.
 

### 2015-10-29 Optimization - Journal of Climate/template.tex
Editing the GAs section.

@@
 Genetic algorithms were found to be much more relevant for such application.
+
+\section{Genetic algorithms}
+
+%TODO: write this section
+
+Practically, GAs allow rapidly approaching satisfactory solutions, but they do not provide the optimum solution for sure \citep{Zitzler2004a}.
+It is indeed mainly a matter of time.
+When the optimizer gets closer to the global optimum, any new improvement takes more time to appear (see figure \ref{fig:evolution}), and the final adjustment of the parameters is very time consuming \citep{Back1993a}.
+For problems that require a significant amount of time in order to evaluate the objective function, as in our case, we have to limit the number of generations to get reasonable processing time.
+Thus, different acceptable solutions can result from one or more optimizations \citep{Holland1992b}.
+This is a strength and a weakness of GAs: they are very good at exploring complex parameter spaces in order to identify the most promising areas, but they will not necessarily find the best solution with the optimal values of all parameters \citep{Holland1992b}.
 
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=7.9cm]{figures/figure_structure_gas.pdf}}
-	\caption{Genetic algorithms operational flowchart}
-	\label{fig:structure_gas}
-\end{figure}
-
-\begin{figure}[htb]
 	\centerline{\includegraphics[width=7.9cm]{figures/figure_map.pdf}}

### 2015-10-29 AtmoSwing - Geoscientific Model Development/template.tex
Getting data from the thesis.

@@
 % TODO: write
+
+%Reasoning by analogy is rather widespread in different domains of sciences or engineering.
+In hydrometeorology, it consists, given a certain situation, in looking into the past to retrieve situations that can be considered similar and therefore with consequences that may be expected similar to the situation at hand.
+By situation, we often think of the atmospheric situation over a rather wide domain, but it may also be the atmospheric profile at a radio-sounding station or the air-snow state at a given mountain observing station.
+And usually, by consequence, we often mean and focus on only one given variable of interest (but sometimes more than one), like the occurrence of  hail, storm, avalanches, or the wind, the radiation, or the precipitation over a given domain and duration period?
+
+%As a general setting, the required ingredient are a couple of archives, one describing the situation through as many variables as possible, called predictors, and another one giving, for those situations, the value of the variable of interest for engineering purpose, called predictand.
+Obviously, one understands that the longest and the richest the candidate archive of predictors, the more chance there will be to extract good analogs for a target situation, and to derive what could be the resulting value of the predictand, or at least a conditional range constrained by the predictors values.
+
+%Usually, this predictand value could be derived in a rather physical-dynamic approach  by modelising the chain of processes linking the predictors to the predictand.
+However, the model may be extremely complex, time consuming, or some processes may be poorly known or parameterised.
+Conversely, the hope is that given the past archive of predictors, enough situations analog to a target one could be found so that a reasonable value, or set of values, will be found for the predictand, at a reasonable coding and computing-time costs.
+This is particularly true for  a predictand much required in hydrometeorological applications, namely the precipitation amount over a given domain and time duration.
+The processes involved range from large scale dynamical states of the atmosphere down to very small scale microphysical processes that are not all documented and still less monitored, so that models proposing such simulation are extremely complex, data-demanding, and time consuming.
+Therefore the idea that, with an appropriate set of archives, one may by pass all these modeling aspects by recuperating the predictang values observed from past analog situations?
+
+%The purpose of this paper is not to argue in favour or against this approach, which has proved to be used efficiently either in forecasting or more recently in climate studies, and capable of challenging more classical approaches based on meteorological modeling.
+In forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies, it is more and more used to downscale the results of global climate model simulation runs.
+In this last case, although the GCM represents the large or regional scale evolutions of the atmosphere, it would be far too computer intensive to get down to variables such as precipitation at a rather small and representative scale.
+Therefore the idea to rely on past observations to bypass these unaffordable small scale simulations and to go from the large scale situation proposed by the GCM to the end variables like precipitation by searching anlogs in the past and present archive.
+
+%However, how efficient, useful or promising it may seem, this approach is not straightforward.
+Usually the type of predictand is imposed by some practical needs or constraints.
+Considering a precipitation variable, ones has to decide upon the duration of accumulation, (e.g.
+from 6hourly to daily or several day totals) according for example to the size or response time of a the catchments to be managed.
+But we must also consider the availability and quality of a long enough time serie.
+
+%As for the predictors describing the large scale predictors, hopefully we can now rely on products elaborated collectively by the atmospheric community and called reanalyses, commonly available over 40 years or more, and easily accessible.
+However, many problems remain and choices to be done?
+Given the predictand selected, the different values of which are hypothetically associated with different large scale situations, how should we characterize such situation?
+Which predictors are the most important, over which spatial and time domains?.
+Obviously we known that looking for two meteorological situations that would be similar over the whole globe is hopeless (an argument used against the analog approch see vanderwool????) , but we feel, and verify, that there is no such need, and that similarity can be restricted to a rather small domain, but which, given our specific predictand?
+How many predictors should we use, given that they are often interelated, and many may ne useless for our purpose?
+How many analogs should be extracted to propose an appropriate predictand value?
+etc?
+
+%Therefore the approach appears predictand-specific but also dependent on the archive of predictors.
+And many choices have to be made, or many paremeters to be fixed, in order to try to optimise it.
+Up to now, this has be done partly manually,  essentially sequentially, one choice after another, without systematic calling into question?
+Therefore the risk of staying on a local optimum that does not fully exploit the potential of the method and of the archive.
+
+%This is the problem addressed by this paper : how could we hopefully get to or come closer to the optimum  that could be expected from the available data.
 
@@
 	\setlength\itemsep{-2px}
-	\item cc : classic calibration (can be omitted as considered as default, see section \ref{sec:classic})
+	\item sc : sequential calibration (can be omitted as considered as default, see section \ref{sec:atmoswing-calibration})
 	\item go : global optimization (by means of genetic algorithms for example, see section \ref{sec:gas})
@@
 
-The software first downloads the predictor describing the target situation, such as GFS outputs \citep[Global Forecast System,][see section \ref{sec:data}]{Kanamitsu1991,Kanamitsu1989}.
+The software first downloads the predictor describing the target situation, such as 1\textdegree\ GFS outputs \citep[Global Forecast System,][see section \ref{sec:data}]{Kanamitsu1991,Kanamitsu1989}.
 It then interpolates the gridded data to match the resolution of the archive (for example 2.5\textdegree\ in the case of the NCEP/NCAP reanalysis I).
@@
 
+%TODO: complete that:
+
+%Lors du passage de la prévision parfaite à la prévision opérationnelle, il faut tenir compte de l'incertitude croissante des données utilisées.
+Une option, pour en tenir compte, consiste à moduler le nombre d'analogues et à l'augmenter avec l'éloignement de l'échéance.
+En effet, pour des échéances lointaines, le modèle global n'est plus informatif, et la prévision des pluies devient la distribution climatologique, donc celle obtenue en prenant toutes les journées de l'archive comme analogues.
+Cela ne peut se faire que par apprentissage sur une archive suffisamment longue de prévisions du modèle considéré.
+La longueur de cette archive pose elle-même problème, car il faut au minimum 3 ou 4 ans d'archive pour que les résultats (le choix optimal du nombre d'analogues à utiliser pour chaque échéance) se stabilisent.
+De plus, sur de telles périodes, le modèle numérique a souvent évolué; une archive reconstituée des prévisions à l'aide d'une version actuelle du modèle est donc préférable (voir section \ref{sec:donnees:resimulations_GFS} sur les reprévisions).
+
+%Toutefois, cette analyse étant conséquente, elle n'a pas pu être réalisée dans le présent travail.
+Nous nous basons alors sur les travaux de \citet{Thevenot2004}, qui a réalisé cet exercice pour le territoire français en partant de l'archive de prévision du modèle européen (environ 5 années de prévision).
+
+%\citet{Thevenot2004} a calibré le nombre d'analogues pour les 5 premières échéances.
+Puisque, pour certains modèles, nous considérons une échéance jusqu'à 7 jours, nous avons cherché à extrapoler la courbe qu'il proposait.
+Afin de rester le plus objectif possible, nous avons calé une loi polynomiale du deuxième ordre sur ces valeurs.
+Nous considérons donc les deux premières échéances constantes, avec un nombre d'analogues égal à celui obtenu en prévision parfaite (lors de la calibration avec les réanalyses), puis nous calons la courbe sur les échéances suivantes.
+Sur cette base, nous extrapolons le nombre d'analogues à 7 jours (voir Figure \ref{fig:implementation:Ajustement_nb_analogues_echeances}).
+
+%Cette approche est certes discutable, une recalibration restant préférable, mais elle nous permet de nous approcher de nombres d'analogues bien plus adaptés en opérationnel que les nombres issus de la calibration en prévision parfaite.
+Ces courbes ne devraient pas non plus être extrapolées beaucoup plus loin, car les erreurs ainsi effectuées vont certainement croître.
+
+%À l'ère de la prévision d'ensemble, il serait également intéressant de considérer ce type de données pour la prévision par analogie, d'autant plus que \citet{Thevenot2004} en a obtenu un gain en performances.
+Les paramètres, plus particulièrement le nombre d'analogues, doivent être réévalués pour une application à un modèle ensembliste.
+
 \section{AtmoSwing Viewer}
@@
 All AMs rely on atmospheric circulation information, while some add subsequent levels of analogy on moisture or other thermodynamic predictors (see section \ref{sec:method:evolution}).
-However, these subsequent predictors were found to be relevant only on the first 3~lead times, and not much further, due to higher uncertainties in their forecast.
+However, these subsequent predictors were found to be relevant only on the first 3~days, and not much further, due to higher uncertainties in their forecast.
 This was found to be the case of moisture indexes and vertical velocity.
@@
 
+%La méthode des analogues est habituellement calibrée sur toute l'année, et la paramétrisation est identique pour chaque saison.
+Or les influences principales peuvent changer d'une saison à l'autre, et nous pourrions imaginer que les paramètres optimaux pour une période de l'année ne le soient pas pour une autre.
+Ainsi, une calibration par saison mérite d'être explorée.
+Cela amène néanmoins quelques difficultés dans les périodes de transition entre saisons, où nous pourrions ne pas être optimaux.
+De plus, nous pouvons parfois rencontrer des épisodes caractéristiques d'une certaine saison dans une autre.
+
+%Il nous semble nécessaire de poursuivre les recherches dans l'approche par analogie, spécifiquement pour les événements de fortes précipitations, afin d'être en mesure de bien les caractériser.
+L'élaboration de paramétrisations de la méthode des analogues optimisées pour les extrêmes nous semble intéressante, tant que celles-ci sont considérées en parallèle de méthodes optimales pour l'ensemble des situations.
+
+%Les méthodes que nous proposons, ainsi que les méthodes de référence, décrivent en premier lieu l'information de la circulation atmosphérique, puis en second, celle de l'humidité.
+Après les événements de 2011 en Ligurie, nous estimons qu'il serait intéressant d'ajouter un troisième niveau d'analogie pour caractériser le déclenchement des précipitations, et donc pour déterminer si les forts cumuls sont plus probables à proximité des côtes en raison d'une très forte convection, ou si les masses d'air humides sont en mesure d'atteindre le bassin du Rhône.
+\citet{BenDaoud2010} intègre les mouvements verticaux dans la recherche d'analogie, mais nous avons vu que cette variable n'est pas pertinente pour notre région.
+Des variables de nature thermique semblaient pouvoir améliorer la prévision dans le bassin supérieur du Rhône, particulièrement pour les crêtes du sud-est.
+
+%Nous avons travaillé ici avec des fenêtres spatiales rectangulaires, où tous les points ont le même poids.
+\citet{Bliefernicht2010} avait introduit une pondération des points de grille en adaptant des formes elliptiques sur les champs des variables synoptiques.
+La méthode des analogues qu'il a considérée étant différente de notre version, le succès de cette démarche n'est pas garanti.
+Toutefois, il serait intéressant de l'évaluer sur les différents niveaux d'analogie.
+De même, nous pourrions imaginer calculer les gradients réels en tenant compte des distances horizontales.
+Ceci pourrait permettre de tenir compte de la déformation de la grille, laquelle s'accentue lorsque l'on s'éloigne de l'équateur.
+
+%Les outils d'optimisation globale permettent d'explorer automatiquement des jeux de données pour en extraire les variables les plus pertinentes.
+Il devient ainsi possible de chercher à prévoir un autre prédictand, par exemple la température, la limite des chutes de neige, l'occurrence de grêle, ou le vent, en laissant les algorithmes choisir les meilleures variables et les paramètres associés.
+
+%Il semble que la méthode des analogues doive être adaptée spécifiquement à chaque région, et que cela n'est pas un défaut, mais est lié à une réalité physique.
+Ainsi, plusieurs études proposent des paramétrisations différentes en lien avec les processus météorologiques propres au lieu où elles ont été appliquées:
+
+\vspace{2mm}
+\begin{itemize}\addtolength{\itemsep}{0.5\baselineskip}
+	\item %Dans les Cévennes, \citet{Marty2010} a identifié le niveau 925~hPa comme étant optimal pour l'analogie d'humidité.
+Les masses d'air arrivant dans cette région par un flux de sud viennent en effet de se charger en humidité sur la Méditerranée, et cette humidité est vraisemblablement encore située dans les basses couches.
+	\item %Dans les grandes plaines de l'est de la France, \citet{BenDaoud2010} a au contraire trouvé que le niveau 700~hPa est préférable.
+Cette humidité provient de l'Atlantique et se trouve effectivement transportée à cette altitude par la circulation générale.
+	\item %Nous avons également identifié le niveau 700~hPa comme étant optimal pour la comparaison du flux d'humidité dans le bassin alpin du Rhône.
+Cette humidité, même si elle peut provenir en partie de la Méditerranée, doit franchir la barrière des Alpes pour être efficace en termes de précipitations.
+Le niveau 700~hPa doit donc correspondre à une certaine réalité liée à l'altitude moyenne des bassins versants affectés et aux observations des radiosondages réanalysées par le modèle numérique global.
+\end{itemize}
+\vspace{2mm}
+
+%De même, la taille optimale des bassins cibles dépend de leur environnement topogra-phique, ainsi que des principales influences météorologiques.
+Ainsi, l'optimum semble se situer entre 200 et 400~km$^{2}$ pour les Cévennes \citep{Bontron2004}, et entre 3000 et 6000~km$^{2}$ pour les grandes plaines de l'est de la France \citep{BenDaoud2010}.
+De même, certaines variables prédicteurs (p.ex.
+la vitesse verticale) n'ont un sens que pour ces grands bassins, en raison, entre autres, de leur résolution (2.5\degres).
+La vitesse verticale ne présente pas d'intérêt dans le bassin du Rhône en Suisse, en raison de sa petite taille relativement aux données synoptiques, et en raison du rôle dominant joué par la topographie.
+Il restera donc toujours des adaptations locales à faire pour utiliser la méthode dans une nouvelle région.
+
+%Il est également important d'introduire la technique de correction du biais développée par \citet{Marty2010}.
+De plus, il serait encore prudent de réoptimiser au moins le nombre d'analogues en fonction de l'échéance.
+En effet, celui-ci a été approximé sur la base de travaux réalisés dans un contexte différent.
+
+%Pour ce qui est de la méthode des analogues, des indicateurs issus des détails de la prévision, par exemple l'identification automatique d'une différence entre la distribution globale et celle des meilleures analogues, pourraient s'avérer utiles.
+Une autre information possible serait une interprétation semi-automatique proposant le quantile de la distribution qu'il est conseillé de considérer.
+
+%Une désagrégation temporelle des précipitations journalières serait nécessaire pour l'alimentation d'un modèle hydrologique.
+Il existe différentes techniques permettant de réaliser une série temporelle infrajournalière, dont celle présentée par \citet{Marty2010}, qui a l'avantage de se rapprocher de la chronologie attendue de l'événement.
+Nous pourrions également imaginer utiliser les cumuls prévus par les analogues pour mettre à l'échelle les grilles issues des prévisions du modèle COSMO-2, tout en exploitant leur cohérence spatiale.
+
 \conclusions  %% \conclusions[modified heading if necessary]

### 2015-11-02 AtmoSwing - Geoscientific Model Development/template.tex
First version of the introduction for AtmoSwing.

@@
 \introduction  %% \introduction[modified heading if necessary]
-% TODO: write
-
-%Reasoning by analogy is rather widespread in different domains of sciences or engineering.
+
+Reasoning by analogy is rather widespread in different domains of sciences or engineering.
 In hydrometeorology, it consists, given a certain situation, in looking into the past to retrieve situations that can be considered similar and therefore with consequences that may be expected similar to the situation at hand.
 By situation, we often think of the atmospheric situation over a rather wide domain, but it may also be the atmospheric profile at a radio-sounding station or the air-snow state at a given mountain observing station.
-And usually, by consequence, we often mean and focus on only one given variable of interest (but sometimes more than one), like the occurrence of  hail, storm, avalanches, or the wind, the radiation, or the precipitation over a given domain and duration period?
-
-%As a general setting, the required ingredient are a couple of archives, one describing the situation through as many variables as possible, called predictors, and another one giving, for those situations, the value of the variable of interest for engineering purpose, called predictand.
-Obviously, one understands that the longest and the richest the candidate archive of predictors, the more chance there will be to extract good analogs for a target situation, and to derive what could be the resulting value of the predictand, or at least a conditional range constrained by the predictors values.
-
-%Usually, this predictand value could be derived in a rather physical-dynamic approach  by modelising the chain of processes linking the predictors to the predictand.
+By consequence, we often focus on one (or more) local variable of interest, such as the occurrence of hail, storm, avalanches, or the amount of wind or precipitation over a given region.
+
+As a general setting, the required ingredient are a couple of archives, one describing the situation through different variables, called predictors, and another one giving, for those situations, the value of the local variable of interest for engineering purpose, called predictand.
+Obviously, one understands that the longest and the richest the candidate archive of predictors, the more chance there will be to extract good analogues for a target situation in order to derive a conditional range of predictand values.
+As for the predictors, we can now hopefully rely on rich reanalysis products, commonly available over 40 years or more, and easily accessible.
+
+Usually, the predictand values could be derived in a rather physical-dynamic approach  by modeling the chain of processes linking the predictors to the predictand.
 However, the model may be extremely complex, time consuming, or some processes may be poorly known or parameterised.
-Conversely, the hope is that given the past archive of predictors, enough situations analog to a target one could be found so that a reasonable value, or set of values, will be found for the predictand, at a reasonable coding and computing-time costs.
+Conversely, the hope is that given the past archive of predictors, enough situations analogues to a target one could be found so that reasonable values will be found for the predictand, at a reasonable coding and computing-time costs.
 This is particularly true for a predictand much required in hydrometeorological applications, namely the precipitation amount over a given domain and time duration.
-The processes involved range from large scale dynamical states of the atmosphere down to very small scale microphysical processes that are not all documented and still less monitored, so that models proposing such simulation are extremely complex, data-demanding, and time consuming.
-Therefore the idea that, with an appropriate set of archives, one may by pass all these modeling aspects by recuperating the predictang values observed from past analog situations?
-
-%The purpose of this paper is not to argue in favour or against this approach, which has proved to be used efficiently either in forecasting or more recently in climate studies, and capable of challenging more classical approaches based on meteorological modeling.
-In forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies, it is more and more used to downscale the results of global climate model simulation runs.
-In this last case, although the GCM represents the large or regional scale evolutions of the atmosphere, it would be far too computer intensive to get down to variables such as precipitation at a rather small and representative scale.
-Therefore the idea to rely on past observations to bypass these unaffordable small scale simulations and to go from the large scale situation proposed by the GCM to the end variables like precipitation by searching anlogs in the past and present archive.
-
-%However, how efficient, useful or promising it may seem, this approach is not straightforward.
+The processes involved range from large scale dynamical states of the atmosphere down to very small scale microphysical processes, requiring models that are extremely complex, data-demanding, and time consuming.
+Therefore, with an appropriate set of archives, one may bypass all these modeling aspects by obtaining the predictand values observed from past analogue situations.
+
+The purpose of this paper is not to argue in favour or against this approach, which has proved to be used efficiently either in operational forecasting or more recently in climate studies, and which is capable of challenging more classical approaches based on meteorological modeling.
+In operational forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies, it is more and more used to downscale the results of global climate model simulation runs.
+In operational, it should however not to be considered as a substitution for numerical weather prediction models, but as a complement in order to get a fast and independent forecast that is known to be accurate several days in advance.
+It therefore enriches the analysis of a potential critical situation for flood forecasting, for example, and is very interesting in early warning.
+
+However, how efficient and useful it may seem, this approach is not straightforward.
 Usually the type of predictand is imposed by some practical needs or constraints.
 Considering a precipitation variable, ones has to decide upon the duration of accumulation, (e.g.
-from 6hourly to daily or several day totals) according for example to the size or response time of a the catchments to be managed.
-But we must also consider the availability and quality of a long enough time serie.
-
-%As for the predictors describing the large scale predictors, hopefully we can now rely on products elaborated collectively by the atmospheric community and called reanalyses, commonly available over 40 years or more, and easily accessible.
-However, many problems remain and choices to be done?
-Given the predictand selected, the different values of which are hypothetically associated with different large scale situations, how should we characterize such situation?
-Which predictors are the most important, over which spatial and time domains?.
-Obviously we known that looking for two meteorological situations that would be similar over the whole globe is hopeless (an argument used against the analog approch see vanderwool????) , but we feel, and verify, that there is no such need, and that similarity can be restricted to a rather small domain, but which, given our specific predictand?
-How many predictors should we use, given that they are often interelated, and many may ne useless for our purpose?
-How many analogs should be extracted to propose an appropriate predictand value?
-etc?
-
-%Therefore the approach appears predictand-specific but also dependent on the archive of predictors.
-And many choices have to be made, or many paremeters to be fixed, in order to try to optimise it.
-Up to now, this has be done partly manually,  essentially sequentially, one choice after another, without systematic calling into question?
-Therefore the risk of staying on a local optimum that does not fully exploit the potential of the method and of the archive.
-
-%This is the problem addressed by this paper : how could we hopefully get to or come closer to the optimum  that could be expected from the available data.
+from 6-hourly to daily or several day totals) according for example to the size or response time of a the catchments to be managed.
+We must also consider the availability and quality of a long enough time series.
+Moreover, the analogy is restricted to a selection of variables at a specific time and over optimized spatial domains, that are compared by means of a chosen criteria that can rank the candidate days from the archive with a distance quantification.
+The approach appears predictand-specific but also dependent on the archive of predictors.
+Thus, the analogy is defined by many parameters (choice of the predictor variable, the temporal and spatial windows, and the number of analogues to consider) that are not straightforward to determine.
+
+Up to now, the optimization of the method has been undertaken by semi-automatic calibration procedures.
+However, the choice of predictor variables, pressure levels and temporal windows were still to be chosen manually before optimizing the spatial windows and the number of analogues.
+Moreover, the semi-automatic technique proceeds to the optimization sequentially, ignoring potential dependencies between the parameters of the method.
+Thus, optimizing the method with the semi-automatic technique is laborious, as many combinations of predictors (variables, pressure levels, temporal windows) have to be assessed.
+Moreover, due to its sequential approach, the risk of ending in a local optimum is high and can not be avoided.
+We thus propose a global optimization approach by means of Genetic algorithms, tailored to the analogue method (AM).
+
+We will first present the AM along with various implementations, as the optimal version of the method may vary with the location of interest, and as all these can be processed with AtmoSwing.
+The software will then be presented, and its modules detailed, such as the Forecaster and the Viewer that are tools for operational use, and the Optimizer that allows optimizing the method for a given predictand time series.
+Finally, a section will be dedicated to the optimization by means of Genetic algorithm, and our recommended usage.
 
@@
 The whole structure of the AM is defined in an XML file generated by the user.
+Even the time step of the method (6 or 24~hours for example) is a dynamic parameter.
 
@@
 The software provides several levels of synthesis of the forecasts.
-When it is opened, it automatically loads the most recent forecasts.
+When it is opened, it automatically loads the most recent forecasts, eliminating the need to manually open files.
 It first offers a quick overview of possible alerts by means of color codes on the lead time switcher (upper right in the GUI, see Figure \ref{figure:atmoswing-viewer-gui}), which synthesizes the worst case scenario, or in the alarms panel (on the left part of the GUI).
@@
 	\left\lbrace \begin{array}{l l} 
-	g_{n} + \left(b_{n}-g_{n}\right) r_{2} \left(1 - \min \left\lbrace \dfrac{G}{G_{m,r}}, 1 \right\rbrace \left(1-\omega\right) \right)^{2} & if \; r_{1} < 0.5 \\
-	g_{n} - \left(g_{n}-a_{n}\right) r_{2} \left(1 - \min \left\lbrace \dfrac{G}{G_{m,r}}, 1 \right\rbrace \left(1-\omega\right) \right)^{2} & if \; r_{1} \geq 0.5 \\
+	g_{n} + \left(b_{n}-g_{n}\right) r_{2} \varphi^{2} & if \; r_{1} < 0.5 \\
+	g_{n} - \left(g_{n}-a_{n}\right) r_{2} \varphi^{2} & if \; r_{1} \geq 0.5 \\
 	\end{array} \right.
@@
 	\end{equation}
+
+	with
+
+	\begin{equation}
+		\varphi = 1 - \min \left\lbrace \dfrac{G}{G_{m,r}}, 1 \right\rbrace \left(1-\omega\right)
+	\end{equation}
+
 	where $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a threshold chosen by the user to maintain a minimum search radius when $G>G_{m,r}$.
@@
 
-\section{Perspectives}
+\conclusions[Conclusions and perspectives]
+
+Processing operational forecasts by means of AtmoSwing requests very low computing infrastructure and can provide useful information, such as early warning for extreme precipitation, in the case of an application in flood forecasting.
+The Forecaster is very flexible as it builds the desired method in a dynamic way, and can thus implement multiple variants of the AM.
+The Viewer offers a user-friendly display of the forecast, with different levels of synthesis and details.
+
+In order to automatically optimize the analogue method, we evaluated genetic algorithms, a global optimization technique, that is able to solve complex problems.
+Given the large number of existing operators and options, we had to evaluate systematically multiple variants to identify which operators are important, and which variant works best for the analogue method.
+We could thus identify that the mutation operator is a key element for our application, and provided new variants that were found to be efficient, such as the Chromosome of adaptive search radius that seems to be very reliable (no control parameter) and efficient .
+Recommendations were established for a relevant use of GAs for the optimization of the analogue method.
+However, there may still be possible improvements, through new operators, in order to improve the optimization performance and speed.
 
@@
 
-\conclusions  %% \conclusions[modified heading if necessary]
-% TODO: write
-
 \appendix
@@
 NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.
-Precipitation time series provided by MeteoSwiss.
 \end{acknowledgements}

### 2015-11-02 Optimization - Journal of Climate/template.tex
First version of the introduction for AtmoSwing.

@@
 Even though the results may differ from one place to another, the applicability of GAs to the analogue method remains universal.
+
+%In operational forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies, it is more and more used to downscale the results of global climate model simulation runs.
+In this last case, although the GCM represents the large or regional scale evolutions of the atmosphere, it would be far too computer intensive to get down to variables such as precipitation at a rather small and representative scale.
+Therefore the idea to rely on past observations to bypass these unaffordable small scale simulations and to go from the large scale situation proposed by the GCM to the end variables like precipitation by searching anlogs in the past and present archive.
 
@@
 
-In order to automatically optimize the analogue method, we evaluated genetic algorithms, a global optimization technique, that is able to solve complex problems.
-Given the large number of existing operators and options, we had to evaluate systematically multiple variants to identify which operators are important, and which variant works best for the analogue method.
-We could thus identify that the mutation operator is a key element for our application, and provided new variants that were found to be efficient, such as the Chromosome of adaptive search radius that seems to be very reliable (no control parameter) and efficient .
-Recommendations were established for a relevant use of GAs for the optimization of the analogue method.
-However, there may still be possible improvements, through new operators, in order to improve the optimization performance and speed.
-
 The parameters resulting from the optimization are very consistent for the analogy of the atmospheric circulation, in terms of selection of the pressure levels, and the temporal and spatial windows.

### 2015-11-02 AtmoSwing - Geoscientific Model Development/template.tex
First version of the conclusion.

@@
 By assessing multiple combinations of atmospheric levels and temporal windows, he concluded that the coupled geopotential heights at 1000~hPa (Z1000) \& 12~h and 500~hPa (Z500) \& 24~h provided the best performance for the studied region (Table \ref{table:R1}).
-The analogy on the atmospheric circulation proposed by \citet{Bontron2004} is still, at the time of writing, often used operationally, and considered as a reference for benchmarking new parameterizations \citep{Horton2012, Daoud2015}.
+The analogy on the atmospheric circulation proposed by \citet{Bontron2004} is still, at the time of writing, often used operationally, and considered as a reference for benchmarking new parameterizations \citep{Horton2012, BenDaoud2015}.
 
@@
 \end{table}
+
+The optimal predictors vary from one region to another, along with the leading atmospheric processes.
+We will thus never get a unique parameterization of the AM valid for any place on earth, but the method needs to be adapted to the local conditions and to the size of the catchment of interest.
+Thus, there will always be local adaptations to be made for use in a new region.
 
@@
 
+When using a parameterization of the AM, previously optimized in perfect prognosis, in operational forecasting, we should take into account the increasing uncertainty of the predictor with the lead time.
+An option, proposed by \citet{Thevenot2004}, is to increase the number of analogues with the lead time.
+These values should be optimized, for every lead time, by using reforecast data of the model considered for operational forecasting.
+
 The command-line interface allows to start the process for the most recent date, a selected past date, or the last $x$ days (as long as the predictors are available on the provider server).
@@
 
-%TODO: complete that:
-
-%Lors du passage de la prévision parfaite à la prévision opérationnelle, il faut tenir compte de l'incertitude croissante des données utilisées.
-Une option, pour en tenir compte, consiste à moduler le nombre d'analogues et à l'augmenter avec l'éloignement de l'échéance.
-En effet, pour des échéances lointaines, le modèle global n'est plus informatif, et la prévision des pluies devient la distribution climatologique, donc celle obtenue en prenant toutes les journées de l'archive comme analogues.
-Cela ne peut se faire que par apprentissage sur une archive suffisamment longue de prévisions du modèle considéré.
-La longueur de cette archive pose elle-même problème, car il faut au minimum 3 ou 4 ans d'archive pour que les résultats (le choix optimal du nombre d'analogues à utiliser pour chaque échéance) se stabilisent.
-De plus, sur de telles périodes, le modèle numérique a souvent évolué; une archive reconstituée des prévisions à l'aide d'une version actuelle du modèle est donc préférable (voir section \ref{sec:donnees:resimulations_GFS} sur les reprévisions).
-
-%Toutefois, cette analyse étant conséquente, elle n'a pas pu être réalisée dans le présent travail.
-Nous nous basons alors sur les travaux de \citet{Thevenot2004}, qui a réalisé cet exercice pour le territoire français en partant de l'archive de prévision du modèle européen (environ 5 années de prévision).
-
-%\citet{Thevenot2004} a calibré le nombre d'analogues pour les 5 premières échéances.
-Puisque, pour certains modèles, nous considérons une échéance jusqu'à 7 jours, nous avons cherché à extrapoler la courbe qu'il proposait.
-Afin de rester le plus objectif possible, nous avons calé une loi polynomiale du deuxième ordre sur ces valeurs.
-Nous considérons donc les deux premières échéances constantes, avec un nombre d'analogues égal à celui obtenu en prévision parfaite (lors de la calibration avec les réanalyses), puis nous calons la courbe sur les échéances suivantes.
-Sur cette base, nous extrapolons le nombre d'analogues à 7 jours (voir Figure \ref{fig:implementation:Ajustement_nb_analogues_echeances}).
-
-%Cette approche est certes discutable, une recalibration restant préférable, mais elle nous permet de nous approcher de nombres d'analogues bien plus adaptés en opérationnel que les nombres issus de la calibration en prévision parfaite.
-Ces courbes ne devraient pas non plus être extrapolées beaucoup plus loin, car les erreurs ainsi effectuées vont certainement croître.
-
-%À l'ère de la prévision d'ensemble, il serait également intéressant de considérer ce type de données pour la prévision par analogie, d'autant plus que \citet{Thevenot2004} en a obtenu un gain en performances.
-Les paramètres, plus particulièrement le nombre d'analogues, doivent être réévalués pour une application à un modèle ensembliste.
-
 \section{AtmoSwing Viewer}
@@
 	\includegraphics[width=18cm]{figures/atmoswing-viewer.png}
-	\caption{Graphical user interface of the Viewer module.}
+	\caption{Graphical user interface of the Viewer module (Elevation data from The Shuttle Radar Topography Mission (SRTM), and hydrological network from SwissTopo).}
 	\label{figure:atmoswing-viewer-gui}
@@
 	\includegraphics[width=8.3cm]{figures/atmoswing-viewer-snail.png}
-	\caption{Visualization of multiple lead times on the map.}
+	\caption{Visualization of multiple lead times on the map (Elevation data from the SRTM, and hydrological network from SwissTopo).}
 	\label{figure:atmoswing-viewer-snail}
@@
 
-\subsection{Interpreting a forecast}
+\subsection{Interpreting a precipitation forecast}
 
@@
 If, for example, it is shifted to higher values, there is a risk of under-estimating the event when considering the middle of the full distribution.
+
+\citet{Marty2010} applied several validation scores to the quantiles of the AM distribution in operational forecasting.
+He concluded that the detection of the precipitation occurrence was better predicted by median quantiles (50-70~\%), with an optimum to 60~\%.
+However, for significant rainfall, the 90$^{th}$ percentile gave the best performance.
+Comparing the results from the AM to an ensemble forecast, \citet{Marty2010} found the AM to be better than the considered ensembles, particularly for strong precipitation.
+The gain of the AM comes from a greater accuracy for a poorer sharpness, when the ensemble forecasts are very sharp, but lack a bit of accuracy.
 
@@
 The Viewer offers a user-friendly display of the forecast, with different levels of synthesis and details.
+The Optimizer implements different optimization techniques, such as the sequential approach, a Monte-Carlo method, and a global optimization technique.
 
@@
 However, there may still be possible improvements, through new operators, in order to improve the optimization performance and speed.
-
-%\citet{Thevenot2004} a étudié plusieurs aspects de la méthode des analogues en utilisation opérationnelle.
-Le premier a consisté à intégrer les prévisions d'ensemble du Centre Européen de Prévision Météorologique à Moyen Terme (CEPMMT, ou \textit{European Centre for Medium-Range Weather Forecasts}, ECMWF).
-Cette approche permet de tenir compte des incertitudes sur les prédicteurs issus du modèle global.
-Son implémentation est une combinaison des journées analogues retenues, associées à chacune des traces.
-La distribution des précipitations est ensuite établie sur l'ensemble des analogues.
-Ainsi, certaines journées peuvent être représentées plusieurs fois.
-À partir d'une échéance de 4 jours, la prévision sur l'ensemble des traces se montre plus performante que celle effectuée sur le seul contrôle déterministe.
-
-%Il a aussi effectué une calibration du nombre d'analogues à retenir en fonction de l'échéance pour la prévision déterministe, ainsi que pour la prévision d'ensemble.
-Pour la prévision déterministe, le nombre d'analogues pour les deux premières échéances est identique à celui de la prévision parfaite \citep[calibration sur les réanalyses,][]{Klein1963}, puis croît de manière importante jusqu'à tendre vers l'ensemble de la climatologie.
-Cette optimisation a été effectuée sur la méthode à un niveau d'analogie (analogie de circulation), mais n'a pas pu être entreprise de manière aussi rigoureuse sur le second niveau d'analogie.
-
-%\citet{Marty2010} a appliqué plusieurs scores de validation aux quantiles de la distribution des prévisions opérationnelles de la méthode des analogues.
-Il en a conclu que la détection de l'occurrence des pluies était mieux prévue par les quantiles médians (50 à 70~\%), avec un optimum à 60~\%.
-Toutefois, pour les pluies significatives, le quantile 90~\% donnait les meilleures performances.
-En comparant les résultats des analogues et des prévisions d'ensemble, pour le quantile 90~\%, il a observé que, à partir de $P = 0.16 \cdot P10$, les analogues donnaient trop d'alertes, alors que les ensembles n'en émettaient pas assez.
-La prévision opérationnelle par analogie était meilleure que celle des ensembles considérés, et ceci particulièrement pour les forts cumuls \citep{Marty2010}.
-Le gain des analogues provient principalement d'une meilleure justesse, pour une moins bonne finesse.
-Au contraire, les prévisions d'ensemble sont très fines, mais manquent un peu de justesse.
-
-%Lors de l'analyse du biais des résultats de la méthode des analogues en opérationnel (également des ensembles), il a observé que la fréquence prévue des pluies nulles ($F(0)$) était biaisée et sous-estimait la fréquence réelle des précipitations nulles.
-Au contraire, les fréquences prévues des pluies positives ($F_{+}$) surestimaient les fréquences observées.
-Ainsi, par exemple, le quantile 50~\% de la distribution prévue correspondrait au quantile réel 32~\%, et le 90~\% prévu au 81~\% réel.
-Il a donc proposé une correction des biais.
-
-%En analysant le biais de la méthode des analogues en prévision parfaite (voir section \ref{sec:etat_art:calibration}), il a observé que $F(0)$ et $F_{+}$ n'étaient que très légèrement biaisés, et que les biais observés précédemment avaient donc une origine externe (l'échantillon des prévisions du modèle numérique global utilisé).
-Toutefois, en appliquant un conditionnement par $F(0)$, il est apparu que \og \textit{si la journée cible est prévue pour être plutôt humide ($F(0) \leq 0.10$), les fréquences de $F_{+}$ sont surestimées (et les quantiles de précipitations sont dès lors sous-estimés)}\fg{}, et au contraire, que \og \textit{si elle est prévue pour être plutôt sèche avec une probabilité moyenne ($F(0) > 0.20$), alors les fréquences $F_{+}$ sont sous-estimées (et les quantiles de précipitations sont dès lors surestimés)}\fg{}.
-Il a donc proposé une méthode de correction a priori en appliquant un coefficient correctif sur chaque fréquence quantilique en fonction de $F(0)$, puis en déterminant la distribution a posteriori, ajustée selon la loi Gamma à deux paramètres.
-Cette correction s'est avérer améliorer les performances des prévisions pour les journées à fortes précipitations.
-
-%Il a encore proposé une désagrégation temporelle à 6 et 12~h des prévisions de la méthode des analogues pour une utilisation opérationnelle dans une chaîne hydrométéorologique.
-La meilleure méthode identifiée consistait à utiliser les cumuls prévus par la méthode des analogues à un pas de temps journalier, et de leur appliquer la chronologie des prévisions d'ensemble, lesquels reproduisent bien la répartition infrajournalière.
-
-%La méthode des analogues est habituellement calibrée sur toute l'année, et la paramétrisation est identique pour chaque saison.
-Or les influences principales peuvent changer d'une saison à l'autre, et nous pourrions imaginer que les paramètres optimaux pour une période de l'année ne le soient pas pour une autre.
-Ainsi, une calibration par saison mérite d'être explorée.
-Cela amène néanmoins quelques difficultés dans les périodes de transition entre saisons, où nous pourrions ne pas être optimaux.
-De plus, nous pouvons parfois rencontrer des épisodes caractéristiques d'une certaine saison dans une autre.
-
-%Il nous semble nécessaire de poursuivre les recherches dans l'approche par analogie, spécifiquement pour les événements de fortes précipitations, afin d'être en mesure de bien les caractériser.
-L'élaboration de paramétrisations de la méthode des analogues optimisées pour les extrêmes nous semble intéressante, tant que celles-ci sont considérées en parallèle de méthodes optimales pour l'ensemble des situations.
-
-%Les méthodes que nous proposons, ainsi que les méthodes de référence, décrivent en premier lieu l'information de la circulation atmosphérique, puis en second, celle de l'humidité.
-Après les événements de 2011 en Ligurie, nous estimons qu'il serait intéressant d'ajouter un troisième niveau d'analogie pour caractériser le déclenchement des précipitations, et donc pour déterminer si les forts cumuls sont plus probables à proximité des côtes en raison d'une très forte convection, ou si les masses d'air humides sont en mesure d'atteindre le bassin du Rhône.
-\citet{BenDaoud2010} intègre les mouvements verticaux dans la recherche d'analogie, mais nous avons vu que cette variable n'est pas pertinente pour notre région.
-Des variables de nature thermique semblaient pouvoir améliorer la prévision dans le bassin supérieur du Rhône, particulièrement pour les crêtes du sud-est.
-
-%Nous avons travaillé ici avec des fenêtres spatiales rectangulaires, où tous les points ont le même poids.
-\citet{Bliefernicht2010} avait introduit une pondération des points de grille en adaptant des formes elliptiques sur les champs des variables synoptiques.
-La méthode des analogues qu'il a considérée étant différente de notre version, le succès de cette démarche n'est pas garanti.
-Toutefois, il serait intéressant de l'évaluer sur les différents niveaux d'analogie.
-De même, nous pourrions imaginer calculer les gradients réels en tenant compte des distances horizontales.
-Ceci pourrait permettre de tenir compte de la déformation de la grille, laquelle s'accentue lorsque l'on s'éloigne de l'équateur.
-
-%Les outils d'optimisation globale permettent d'explorer automatiquement des jeux de données pour en extraire les variables les plus pertinentes.
-Il devient ainsi possible de chercher à prévoir un autre prédictand, par exemple la température, la limite des chutes de neige, l'occurrence de grêle, ou le vent, en laissant les algorithmes choisir les meilleures variables et les paramètres associés.
-
-%Il semble que la méthode des analogues doive être adaptée spécifiquement à chaque région, et que cela n'est pas un défaut, mais est lié à une réalité physique.
-Ainsi, plusieurs études proposent des paramétrisations différentes en lien avec les processus météorologiques propres au lieu où elles ont été appliquées:
-
-\vspace{2mm}
-\begin{itemize}\addtolength{\itemsep}{0.5\baselineskip}
-	\item %Dans les Cévennes, \citet{Marty2010} a identifié le niveau 925~hPa comme étant optimal pour l'analogie d'humidité.
-Les masses d'air arrivant dans cette région par un flux de sud viennent en effet de se charger en humidité sur la Méditerranée, et cette humidité est vraisemblablement encore située dans les basses couches.
-	\item %Dans les grandes plaines de l'est de la France, \citet{BenDaoud2010} a au contraire trouvé que le niveau 700~hPa est préférable.
-Cette humidité provient de l'Atlantique et se trouve effectivement transportée à cette altitude par la circulation générale.
-	\item %Nous avons également identifié le niveau 700~hPa comme étant optimal pour la comparaison du flux d'humidité dans le bassin alpin du Rhône.
-Cette humidité, même si elle peut provenir en partie de la Méditerranée, doit franchir la barrière des Alpes pour être efficace en termes de précipitations.
-Le niveau 700~hPa doit donc correspondre à une certaine réalité liée à l'altitude moyenne des bassins versants affectés et aux observations des radiosondages réanalysées par le modèle numérique global.
+Usage of this global optimization greatly eases the adaptation of the AM to new regions (with different leading meteorological processes) or to new predictands, as the optimization is performed automatically and globally.
+
+Several additions would be nice to have in AtmoSwing for operational forecasting.
+The first one would be using outputs from multiple global NWP models within one forecast, namely making multi-models forecasts, in order to take into account the variability between various providers.
+In the same direction, \citet{Thevenot2004} showed the benefit of using ensembles of global NWP forecasts as input for the method.
+This approach takes into account the uncertainties on predictors from the global model.
+Its implementation is a combination of the selected analogue days associated with each of the traces.
+Rainfall distribution is then established on all analogues.
+The forecast on the ensemble was found to be more accurate than the deterministic control for a lead time of 4 days and more \citep{Thevenot2004}.
+
+Next, a bias correction should be implemented.
+\citet{Marty2010} has indeed observed that the frequency of the forecasted days without precipitation was biased and underestimated the actual frequency of zero precipitation.
+On the contrary, the frequency of the forecasted days with precipitation overestimated the observed frequencies.
+On this basis, \citet{Marty2010} proposed a bias correction technique, that should be implemented as well.
+This issue occurs in operational forecasting and was not observed in perfect prognosis.
+
+The analogue method evolves, but there are still many possibilities to be assessed. Amongst them, we can mention:
+
+\begin{itemize}
+	\item an optimization per season in order to get parameterizations specific to the leading processes during the period in question;
+	\item optimizations specific for extreme events, with an objective function tailored to the determination of the most critical situations;
+	\item a weighting of the predictor grids, in order to get free of fixed rectangular spatial windows;
+	\item assessment of potential indicators based on the properties of the distribution of all analogues or the 10 best, for example;
+	\item assessment of the relevance of an automatic interpretation of the distribution in order to provide the most likely expected value;
 \end{itemize}
-\vspace{2mm}
-
-%De même, la taille optimale des bassins cibles dépend de leur environnement topogra-phique, ainsi que des principales influences météorologiques.
-Ainsi, l'optimum semble se situer entre 200 et 400~km$^{2}$ pour les Cévennes \citep{Bontron2004}, et entre 3000 et 6000~km$^{2}$ pour les grandes plaines de l'est de la France \citep{BenDaoud2010}.
-De même, certaines variables prédicteurs (p.ex.
-la vitesse verticale) n'ont un sens que pour ces grands bassins, en raison, entre autres, de leur résolution (2.5\degres).
-La vitesse verticale ne présente pas d'intérêt dans le bassin du Rhône en Suisse, en raison de sa petite taille relativement aux données synoptiques, et en raison du rôle dominant joué par la topographie.
-Il restera donc toujours des adaptations locales à faire pour utiliser la méthode dans une nouvelle région.
-
-%Il est également important d'introduire la technique de correction du biais développée par \citet{Marty2010}.
-De plus, il serait encore prudent de réoptimiser au moins le nombre d'analogues en fonction de l'échéance.
-En effet, celui-ci a été approximé sur la base de travaux réalisés dans un contexte différent.
-
-%Pour ce qui est de la méthode des analogues, des indicateurs issus des détails de la prévision, par exemple l'identification automatique d'une différence entre la distribution globale et celle des meilleures analogues, pourraient s'avérer utiles.
-Une autre information possible serait une interprétation semi-automatique proposant le quantile de la distribution qu'il est conseillé de considérer.
-
-%Une désagrégation temporelle des précipitations journalières serait nécessaire pour l'alimentation d'un modèle hydrologique.
-Il existe différentes techniques permettant de réaliser une série temporelle infrajournalière, dont celle présentée par \citet{Marty2010}, qui a l'avantage de se rapprocher de la chronologie attendue de l'événement.
-Nous pourrions également imaginer utiliser les cumuls prévus par les analogues pour mettre à l'échelle les grilles issues des prévisions du modèle COSMO-2, tout en exploitant leur cohérence spatiale.
+
+The global optimization tools allow easily adapting the AM to new regions by taking into account local meteorological influences, and has thus a great potential of use.
+Moreover, it allows exploring automatically datasets in order to extract the most relevant variables.
+It is thus possible to try assessing other predictands, such as the temperature, the limit of snowfall, the occurrence of hail, or wind, while leaving the algorithms select the best variables and the associated parameters.
 
@@
 %\bibitem[AUTHOR(YEAR)]{LABEL}
-%REFERENCE 1
+% Reference 1
 %
 %\bibitem[AUTHOR(YEAR)]{LABEL}
-%REFERENCE 2
+% Reference 2
 %

### 2015-11-02 AtmoSwing - Geoscientific Model Development/template.tex
First version of the abstract.

@@
 \begin{abstract}
-% TODO: write
+
+The analogue method allows forecasting local meteorological variables of interest (predictand), such as the daily precipitation, on the basis of synoptic variables (predictors).
+It relies on the fact that similar meteorological influences are likely to result in similar local effects.
+This statistical relationship is thus based on archive of observed data, and used in order to operationally forecast the coming days, or to evaluate future conditions under a changing climate.
+
+AtmoSwing is an open source software that implement the analogue method in a very flexible way, so that different variants can be handled dynamically, by parameterization.
+It is made of 3 tools: the Forecaster to perform operational forecasts, the Viewer to display the results, and the Optimizer to establish the statistical relationship between the predictand and predictors.
+
+The Optimizer integrates the most used technique, that is a semi-automatic sequential approach, as well as Monte-Carlo analyses, and especially a global optimization technique by means of Genetic algorithms.
+The global optimization can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
+Indeed, it allows taking into account parameters inter-dependencies, adding new degrees of freedom, and choosing objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
+
+These kind of optimization techniques need however to be tailored to the problem to solve.
+We had to assess multiple combinations of algorithms, and even to develop new operators, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of genetic algorithms to optimize the analogue method.
+These recommendations are a consequent outcome of this work, as it opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.
 
@@
 
-\appendix
+%\appendix
 %\section{}    %% Appendix A
@@
 %\subsection{}     %% Appendix A1, A2, etc.
+
+\section*{Code availability}
+
+AtmoSwing is developed under the Mercurial distributed revision control, and the source code can be found at:
+
+\begin{itemize}
+	\item http://www.atmoswing.org
+	\item https://bitbucket.org/atmoswing/atmoswing
+\end{itemize}
+
+To get access to the frozen version at the time of writing (v1.4.2), the following address can be used:
+
+\begin{itemize}
+	\item bitbucket.org/atmoswing/atmoswing/commits/tag/1.4.2
+\end{itemize}
+
+The Forecaster and the Viewer are fully available, whereas the open version of the Optimizer includes all methods but the Genetic algorithms.
+These are planed to be released in the future, but not at the time of writing, due to lacking documentation and necessary return on investment made by Terranum.
 

### 2015-11-02 Optimization - Journal of Climate/template.tex
First version of the abstract.

@@
 This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic procedure.
-This classic calibration is relatively fast and provide acceptable results, but it has strong constraints, is made of successive steps and thus cannot handle parameters dependencies, and mainly, it cannot calibrate automatically some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared.
+This sequential calibration is relatively fast and provide acceptable results, but it has strong constraints, is made of successive steps and thus cannot handle parameters dependencies, and mainly, it cannot calibrate automatically some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared.
 In order to surpass these limitations, we assessed a global optimization technique, namely genetic algorithms, that can optimize jointly all parameters of the method and thus provide a global optimum by taking into account the parameters dependencies.
 Moreover, it can calibrate parameters that were previously manually assessed, and can take into account new degrees of freedom that were unthinkable before.
-These kind of optimization techniques need however to be tailored to the problem to solve.
-We had to assess multiple combinations of algorithms, and even to develop new operators, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of genetic algorithms to optimize the analogue method.
-These recommendations are the primary outcome of this work, as it opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.
+
 We then applied the optimizer to the Rh\^{o}e catchment in the Swiss Alps and obtained coherent results which significantly improve the performance of the forecasting by analogy.
@@
 
+%TODO: complete
+
 The parameters resulting from the optimization are very consistent for the analogy of the atmospheric circulation, in terms of selection of the pressure levels, and the temporal and spatial windows.

### 2015-11-02 AtmoSwing - Geoscientific Model Development/template.tex
Corrections from Michel.

@@
 
-When using a parameterization of the AM, previously optimized in perfect prognosis, in operational forecasting, we should take into account the increasing uncertainty of the predictor with the lead time.
+When using a parameterization of the AM, previously optimized in perfect prognosis \citep[optimization on the reanalysis dataset, without taking into account the uncertainty of operational forecasts,][]{Klein1963}, in operational forecasting, we should take into account the increasing uncertainty of the predictor with the lead time.
 An option, proposed by \citet{Thevenot2004}, is to increase the number of analogues with the lead time.
@@
 Another reason for working in a perfect prognosis framework is that numerical models evolve continuously, and so does the forecast they provide.
-Re-forecasts would allow us to work on a homogeneous dataset, as they are regularly reprocessed.
+Considering re-forecasts would allow us to work on a homogeneous dataset, as they are regularly reprocessed with a defined version of the model.
 However, we would need to redo the calibration procedure every time a new version is available, in order to reduce the bias \citep{Wilson2002}.
@@
 We mainly rely on the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
-It allows assessing the predicted cumulative distribution functions $F(y)$ compared to the observed value $y^{0}$.
+It allows assessing the predicted cumulative distribution functions $F(y)$, for example of the precipitation values from analogue situations, compared to the observed value $y^{0}$.
 The better the forecast, the smaller the score.
@@
 \end{equation}
-where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect forecast ($CRPS_{p} = 0$).
+where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect forecast (which implies $CRPS_{p}~=~0$).
 
@@
 (iv) The spatial window grows up by repeating the previous steps, until no improvement is reached.
-		\item The number of analogues is optimized for the current level of analogy.
+		\item The number of analogue situations is optimized for the current level of analogy.
 		\item A new level of analogy can be added, based on other variables (such as the moisture index) on predefined pressure levels and time frames.
@@
 There are numerous implementation variants of GAs often optimal for a given problem \citep{Hart1991a,Schraudolph1992a}.
-However, the structure of the method (Figure \ref{fig:structure_gas}) resulting from the work of \citet{Holland1992b} is common to most applications \citep{Back1993b}.
 The divergences are the operators implementation, through significantly different algorithms, which has an important effect on the results \citep{Gaffney2010a}.
+However, the structure of the method (Figure \ref{fig:structure_gas}) resulting from the work of \citet{Holland1992b} is common to most applications \citep{Back1993b}, and consists in the following steps:
+
+\begin{enumerate}
+	\item A population of $N$ individuals (parameter sets of the AM) is randomly generated, which constitutes the initial population.
+	\item The fitness (performance score or objective function) of every individual is assessed.
+	\item A natural selection is applied, after which only the best individuals remain, which constitutes the intermediate generation.
+	\item From this intermediate generation, couples are formed according to given rules.
+	\item These couples proceed to reproduction, or chromosome crossover, in order to mix their genes (parameters) according to the operator version.
+New children are generated in order to fill the intermediate generation back to $N$ individuals.
+	\item Parents and children are then subject to mutation, where some genes get affected, meaning some parameter values are randomly changed.
+	\item The new formed generation is then re-assessed.
+	\item According to the ending criteria, the optimization ends or starts again for another iteration.
+\end{enumerate}
 
@@
 	\item \textbf{Tournament selection} \citep{Michalewicz1996, Zitzler2004a}: two individuals are randomly selected and fight.
-The one with the highest score is chosen, but with a certain probability, in order to reduce the selection pressure.
+The one with the highest performance score is chosen, but with a certain probability, in order to reduce the selection pressure.
 This procedure is repeated until the mating pool is full.
@@
 	\textit{Roulette wheel weighting on fitness}: the selection probability is calculated based on the value of the objective function.
-This approach gives more weight to the best individuals when the distribution of scores is wide, while the weight is almost similar when all individuals have approximately the same score \citep{Haupt2004}.
+This approach gives more weight to the best individuals when the distribution of performance scores is wide, while the weight is almost similar when all individuals have approximately the same performance score \citep{Haupt2004}.
 The probability $p_{n}$ of each individual is calculated by the equation \ref{equation_mating_score_weighting}:
@@
 
-	\item \textbf{Individual adaptive search radius}: based on the ideas of the non-uniform mutation, we introduce a search radius in the approach of individual adaptive mutation rates.
+	\item \textbf{Individual adaptive search radius} (new): based on the ideas of the non-uniform mutation, we introduce a search radius in the approach of individual adaptive mutation rates.
 This search radius $r_{a}$, bounded between 0 and 1, is also adaptive and behaves similarly to the adaptive mutation rates.
@@
 
-	\item \textbf{Chromosome of adaptive search radius}: we introduced this operator that combines the operations of the chromosome of adaptive mutation rate to our adaptive search radius approach.
+	\item \textbf{Chromosome of adaptive search radius} (new): we introduced this operator that combines the operations of the chromosome of adaptive mutation rate to our adaptive search radius approach.
 Similarly, an individual has 3 chromosomes: the first containing the values to be optimized, the second containing the distributed mutation rate, and the last one, the distributed search radius.
@@
 
-	\item \textbf{Multi-scale mutation}: finally, we developed another approach, that is also based on the search radius concept.
+	\item \textbf{Multi-scale mutation} (new): finally, we developed another approach, that is also based on the search radius concept.
 However, the latter is not decreasing with time.
@@
 We wanted to test an approach that combines both exploration and exploitation during the whole optimization.
-Thus, we considered the search radius $r_{a}$ of equation \ref{equation_mutation_rayon_adaptatif} as a random value for each individual, but restricted to 4 equiprobable values: 1, 0.5, 0.1, 0.02.
+Thus, we considered the search radius $r_{a}$ of equation \ref{equation_mutation_rayon_adaptatif} as a random value for each individual, but restricted to 4 equiprobable values: 1, 0.5, 0.1, 0.02, which range from full exploration to fine exploitation.
 The only external parameter is the mutation rate which is fixed.
@@
 After the natural selection operator, if the best individual has not been selected, it is copied to the mating pool instead of an individual randomly picked.
-After mutation, if the best individual has mutated and if its new version has a lower score than the original, the latter is reinserted instead of an individual randomly chosen.
+After mutation, if the best individual has mutated and if its new version has a lower performance score than the original, the latter is also reinserted in the mating pool instead of an individual randomly chosen.
 
@@
 These assessments are very long in our application, as they require calculating and assessing a forecast for every day of the calibration period.
-In order to reduce the computation time, we avoid recalculating the score of an individual who has previously been evaluated and that has not changed.
+In order to reduce the computation time, we avoid recalculating the performance score of an individual who has previously been evaluated and that has not changed.
 We keep the score of each individual living in the selection until it mutates.
@@
 \begin{itemize}
-	\item mean score: average of the final scores of the 10 optimizations,
+	\item mean performance score: average of the final scores of the 10 optimizations,
 	\item convergence: the number of optimizations that converged to a supposed global optimum,
@@
 \begin{itemize}
-	\item \textbf{Population size}: we found the following ranges to be accurate in average:
+	\item \textbf{Population size $N$}: we found the following ranges to be accurate in average for the population size (number of parameter sets of the AM):
 
@@
 	\item \textbf{Selection of couples}: 6 variants of the couples selection were assessed.
-The performance of these variants are relatively close, both in terms of score, convergence, and number of evaluations.
+The performance of these variants are relatively close, both in terms of performance score, convergence, and number of evaluations.
 The random pairing performed the most poorly, when the tournament selection with 3 candidates was slightly superior.
@@
 	The mutation operators based on a variable normal or uniform law work very poorly and are difficult to configure.
-We then observe many operators more or less with the same scores and requiring a variable amount of assessments.
+We then observe many operators more or less with the same performance scores and requiring a variable amount of assessments.
 The convergence analysis allows us to highlight three best operators:
@@
 The Forecaster and the Viewer are fully available, whereas the open version of the Optimizer includes all methods but the Genetic algorithms.
-These are planed to be released in the future, but not at the time of writing, due to lacking documentation and necessary return on investment made by Terranum.
+These are planed to be released in the future, but not at the time of writing.
 

### 2015-11-03 AtmoSwing - Geoscientific Model Development/template.tex
Moving GAs out of the AtmoSwing article.

@@
 The Optimizer integrates the most used technique, that is a semi-automatic sequential approach, as well as Monte-Carlo analyses, and especially a global optimization technique by means of Genetic algorithms.
-The global optimization can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
-Indeed, it allows taking into account parameters inter-dependencies, adding new degrees of freedom, and choosing objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
-
-These kind of optimization techniques need however to be tailored to the problem to solve.
-We had to assess multiple combinations of algorithms, and even to develop new operators, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of genetic algorithms to optimize the analogue method.
-These recommendations are a consequent outcome of this work, as it opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.
+
+%TODO: rewrite
 
@@
 
-Up to now, the optimization of the method has been undertaken by semi-automatic calibration procedures.
-However, the choice of predictor variables, pressure levels and temporal windows were still to be chosen manually before optimizing the spatial windows and the number of analogues.
-Moreover, the semi-automatic technique proceeds to the optimization sequentially, ignoring potential dependencies between the parameters of the method.
-Thus, optimizing the method with the semi-automatic technique is laborious, as many combinations of predictors (variables, pressure levels, temporal windows) have to be assessed.
-Moreover, due to its sequential approach, the risk of ending in a local optimum is high and can not be avoided.
-We thus propose a global optimization approach by means of Genetic algorithms, tailored to the analogue method (AM).
-
 We will first present the AM along with various implementations, as the optimal version of the method may vary with the location of interest, and as all these can be processed with AtmoSwing.
 The software will then be presented, and its modules detailed, such as the Forecaster and the Viewer that are tools for operational use, and the Optimizer that allows optimizing the method for a given predictand time series.
-Finally, a section will be dedicated to the optimization by means of Genetic algorithm, and our recommended usage.
 
@@
 	\item sc : sequential calibration (can be omitted as considered as default, see section \ref{sec:atmoswing-calibration})
-	\item go : global optimization (by means of genetic algorithms for example, see section \ref{sec:gas})
+	\item go : global optimization (by means of genetic algorithms for example)
 \end{itemize}
@@
 
-The sequential calibration cannot optimize all parameters of the AM, as several are manually selected, such as the meteorological variable, the pressure level and the temporal windows.
-Testing multiple combinations of these can be cumbersome, especially when considering multiple predictors within the same level of analogy.
-Moreover, the parameters are calibrated successively within the same level of analogy, and in-between them.
-
-We thus decided to explore optimization techniques that can handle all parameters fully automatically.
-We first assessed the \citet{Nelder1965a} method, which was found to be unsuitable for this purpose.
-Due to the complexity of the AM and its non-linearity, a technique of global optimization is required.
-We thus implemented Genetic algorithms in AtmoSwing Optimizer in order to perform a global optimization of the AM.
-This article is not about discussing the results of such a technique, but describing the details of the implementation.
-The demonstration of the benefit brought by such an approach is the topic of another article.
-The details of the implementation being numerous, the description is provided in the next dedicated section (\ref{sec:gas}).
-
-\section{Optimization using Genetic algorithms}
-\label{sec:gas}
-
-Genetic algorithms (GAs) come from the world of stochastic optimization, more specifically from metaheuristic approaches.
-These are stochastic iterative algorithms that behave like search algorithms by exploiting the characteristics of a problem and are particularly suitable for complex parameter spaces.
-
-Genetic algorithms are part of the family of evolutionary algorithms \citep{Back1993b, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
-GAs are the most used technique from evolutionary algorithms \citep{Back1993b}, and they are constantly improving \citep{Haupt2004}.
-However, with time, the different methods of evolutionary algorithms tend to be similar and share many commonalities \citep{Back1996b, Haupt2004}.
-
-The method was originally developed by \citet{Holland1992b} and popularized by \citet{Goldberg1989}.
-Unlike a linear or local optimization, GAs seek the global optimum on a complex surface, theoretically without restriction, but with no guarantee to reach it.
-
-\subsection{Basic concepts of the genetic algorithms}
-
-GAs mimic the evolution of a population of individuals in a new environment, by applying rules based on natural processes, such as DNA mutation, chromosomes crossover, natural selection, etc.
-It simulates the fact that in a natural environment, the most suitable individuals tend to survive longer, to reproduce more easily, and so to influence coming generations by providing genes that provide some good performance in a certain domain.
-Generation after generation, the DNA mixes and the strong genes cumulate in some individuals \citep{Beasley1996a}.
-Globally, the fitness of the population to its environment increases, while retaining enough variety to not converge too quickly to a local optimum.
-
-Applications of GAs are very diversified as they can handle many parameters of various types \citep{Joines1996a}, even with very complex cost surfaces \citep{Haupt2004}.
-GAs work remarkably well with intervariable dependences \citep{Haupt2004}.
-The objective function to optimize (often named fitness function in this context) can be of different types (mathematical function, experimental or numerical modeling).
-Only the resulting value is used for optimization.
-Indeed, these algorithms do not require any knowledge of the problem, which can be used as black-box, but they must be adapted in order to perform optimally.
-
-By means of the reproduction operator and the natural selection, the GAs focus on the most promising regions of the parameter space \citep{Holland1992b}.
-Points (parameter sets) are densified in these areas because the strong genes of the best individuals propagate from generation to generation.
-
-Two conditions guarantee in theory the convergence to the global optimum \citep{Zitzler2004a}: (1) Parameters mutations that can allow to explore the entire parameter space, thereby ensures that any value can be achieved with a non-zero probability.
-(2) A rule of elitism ensuring that an optimal solution cannot be lost or damaged.
-
-\subsection{Structure and operators}
-
-The GAs optimize a population of individuals (parameter sets).
-Each individual contains a chromosome (parameters of the AM in our case).
-We call gene every parameter that constitutes the chromosome.
-The parameters to optimize have long been coded in binary form and assembled as strings in the canonical GAs \citep{Goldberg1989}.
-Encoding and decoding steps were needed to transform the variable from its floating-point representation into its binary representation, and vice versa, which introduce quantification errors \citep{Haupt2004}.
-According to \citet{Holland1992b}, working with binary chromosomes was supposed to be more efficient \citep{Goldberg1990a, Back1993b}.
-However, more and more applications use floating-point representations, allowing to avoid the coding and decoding steps and the quantification errors \citep{Haupt2004}, and which also often resulted in a performance improvement \citep{Goldberg1990a}.
-It is thus now considered that for continuous variables, a floating-point representation is more suited \citep{Michalewicz1996, Herrera1998a, Haupt2004, Back1996b, Gaffney2010a}.
-
-There are numerous implementation variants of GAs often optimal for a given problem \citep{Hart1991a,Schraudolph1992a}.
-The divergences are the operators implementation, through significantly different algorithms, which has an important effect on the results \citep{Gaffney2010a}.
-However, the structure of the method (Figure \ref{fig:structure_gas}) resulting from the work of \citet{Holland1992b} is common to most applications \citep{Back1993b}, and consists in the following steps:
-
-\begin{enumerate}
-	\item A population of $N$ individuals (parameter sets of the AM) is randomly generated, which constitutes the initial population.
-	\item The fitness (performance score or objective function) of every individual is assessed.
-	\item A natural selection is applied, after which only the best individuals remain, which constitutes the intermediate generation.
-	\item From this intermediate generation, couples are formed according to given rules.
-	\item These couples proceed to reproduction, or chromosome crossover, in order to mix their genes (parameters) according to the operator version.
-New children are generated in order to fill the intermediate generation back to $N$ individuals.
-	\item Parents and children are then subject to mutation, where some genes get affected, meaning some parameter values are randomly changed.
-	\item The new formed generation is then re-assessed.
-	\item According to the ending criteria, the optimization ends or starts again for another iteration.
-\end{enumerate}
-
-\begin{figure}[htb]
-	\includegraphics[width=8.3cm]{figures/figure_structure_gas.pdf}
-	\caption{Genetic algorithms operational flowchart}
-	\label{fig:structure_gas}
-\end{figure}
-
-All operators we used and their options, applied to real coding, are described in the following sections. Many other operators exist, but we will only present the ones we evaluated.
-
-\subsubsection{Genesis of the population}
-
-The first step of the optimization is to generate the initial population.
-A population is a set of $N$ individuals (each of which represents a point in the space of potential solutions, a parameter set of the AM in our application) that we are going to make evolve.
-A generation is the population at a given time.
-
-A random initialization based on a uniform distribution is the most current version.
-The size $N$ of the population is often a compromise between the computation time and the quality of the solution.
-$N$ must allow sufficient sampling of the solutions field \citep{Beasley1996a}, and should thus vary as a function of chromosome size (ie the number of parameters to be optimized).
-
-\subsubsection{Natural selection}
-
-Natural selection is performed on the basis of the values of the objective function.
-The selection allows to only keep a certain part of the population, usually half ($N/2$), which can access the mating pool (intermediate generation with $N_{mp}$ members).
-If $N_{mp}$ is too high, the reproduction rate is too low, whereas if it is too small, the strong traits of individuals do not have the ability to accumulate in the same chromosome \citep{Haupt2004}.
-Several techniques exist, such as:
-
-\begin{itemize}
-	\item \textbf{$N_{mp}$-elitism} \citep{Michalewicz1996}: the population is sorted according to the value of the objective function and only the better half is preserved.
-
-	\item \textbf{Tournament selection} \citep{Michalewicz1996, Zitzler2004a}: two individuals are randomly selected and fight.
-The one with the highest performance score is chosen, but with a certain probability, in order to reduce the selection pressure.
-This procedure is repeated until the mating pool is full.
-Individuals can be selected several times, and thus be represented several times in the mating pool.
-\end{itemize}
-
-\subsubsection{Selection of the couples}
-
-Individuals of the mating pool can reproduce. It begins with the selection of pairs (the parents). The techniques implemented in this work are the following:
-
-\begin{itemize}
-	\item \textbf{Rank pairing}: individuals are gathered in pairs according to their rank (classified on the performance scores).
-Consecutive ranks are put together (odd rows are associated with even rows).
-This approach is easy to achieve, but does not look like a natural process.
-
-	\item \textbf{Random pairing}: two individuals are randomly selected to form a couple, according to a uniform law.
-
-	\item \textbf{Roulette wheel weighting}: the roulette technique refers to gambling.
-But unlike casino roulette, this one is biased.
-Each individual is associated with a sector of the wheel with a certain opening angle, which is its probability of selection \citep{Haupt2004}.
-The probability assigned to the individuals is proportional to their fitness (objective function), so that the most adapted individuals have the greatest probability of reproduction.
-There are two techniques for weighting the individuals of the mating pool:
-
-	\textit{Roulette wheel weighting on rank}: the probability of each individual depends on its rank $n$:
-	\begin{equation}
-	p_{n}=\dfrac{N_{mp}-n+1}{\sum^{N_{mp}}_{n=1}n}
-	\label{equation_mating_rank_weighting}
-	\end{equation}
-
-	\textit{Roulette wheel weighting on fitness}: the selection probability is calculated based on the value of the objective function.
-This approach gives more weight to the best individuals when the distribution of performance scores is wide, while the weight is almost similar when all individuals have approximately the same performance score \citep{Haupt2004}.
-The probability $p_{n}$ of each individual is calculated by the equation \ref{equation_mating_score_weighting}:
-	\begin{equation}
-	p_{n}=\frac{score_{n}-score_{N_{mp}}}{\sum_{n=1}^{N_{mp}} (score_{n}-score_{N_{mp}})}
-	\label{equation_mating_score_weighting}
-	\end{equation}
-	In our application, the last individual ($N_{mp}$) has zero probability of being selected.
-
-	\item \textbf{Tournament selection}: This operator is similar to the one used in natural selection, but is applied here for the successive selection of each parent.
-To select a parent, a number of individuals (2 or 3) are randomly picked and the best is kept.
-This operation is performed twice, once for each partner.
-This approach imitates the breeding competition in nature \citep{Haupt2004}.
-\end{itemize}
-
-\subsubsection{Chromosome crossover}
-
-Once the two parents are selected for breeding, they combine their chromosomes and produce two children, bringing the number of individuals in the population back to $N$ (the parents also return back in the total population in order to complement the next generation).
-The combination of chromosomes is carried out using a crossover operator, thereby generating two offspring having characteristics derived from both parents.
-Chromosome crossover widens the search space and favours the combination of strong genes, which can result in more suited children.
-It allows a mixing of genes and accumulation of positive mutations.
-
-The evaluated crossover operators are the following:
-
-\begin{itemize}
-	\item \textbf{Single-point crossover}: a crossover point is randomly chosen for the pair. The genes (our parameters) located after that point are exchanged in between the two chromosomes.
-
-	\item \textbf{Two-point crossover}: works like the single-point crossover, but there are two intersections defining the segments to exchange.
-This approach, which significantly extends the search space for the children, is considered more efficient than the previous \citep{Beasley1993a, Haupt2004}.
-
-	\item \textbf{Multiple-point crossover} \citep{DeJong1975a}: it is a generalization of the previous, with a number of crossover points up to the number of genes.
-
-	\item \textbf{Uniform crossover} \citep{Syswerda1989}: for each gene of the chromosome, it is randomly chosen to exchange or not the values between the parents.
-
-	\item \textbf{Binary-like crossover} \citep{Haupt2004}: chromosome crossover on a binary coding can generate new values for variables located at intersection points, since the crossovers are applied at the bit level, thus often within a gene.
-This is not the case for the floating-point representation, since the crossover is performed between the genes.
-To reproduce the behaviour present in the original algorithms, which introduces new information, \citet{Haupt2004} propose an operator that combines standard crossover with an interpolation approach.
-The genes located after a crossover point are exchanged, but the gene located at the intersection is modified as follows (equation \ref{equation_mating_as_binary}):
-	\begin{equation}
-	\left\lbrace \begin{array}{l} 
-	g_{o1,n} = g_{p1,n} - \beta (g_{p1,n} - g_{p2,n}) \\
-	g_{o2,n} = g_{p2,n} + \beta (g_{p1,n} - g_{p2,n}) \\
-	\end{array} \right.
-	\label{equation_mating_as_binary}
-	\end{equation}
-	where $g_{o1,n}$ and $g_{o2,n}$ are the $n$-th gene of the two new offspring, and $g_{p1,n}$ and $g_{p2,n}$ are those of the two parents. $\beta$ is a random value between 0 and 1.
-
-	\item \textbf{Blending method} \citep{Radcliffe1991a}: in this approach, instead of exchanging the genes in between the chromosomes after one or multiple crossover points, these are combined by linear combination (equation \ref{equation_mating_blending_method}).
-The genes of the parents are blended together using a random value ($\beta$) that can be unique for the whole chromosome, or that can change for every gene.
-The genes of the offspring are bounded by the genes of the parents, no value can be out of their range.
-	\begin{equation}
-	\left\lbrace \begin{array}{l} 
-	g_{o1,n} = \beta g_{p1,n} + (1-\beta)g_{p2,n} \\ 
-	g_{o2,n} = (1-\beta) g_{p1,n} + \beta g_{p2,n} \\
-	\end{array} \right.
-	\label{equation_mating_blending_method}
-	\end{equation}
-
-	\item \textbf{Linear crossover} \citep{Wright1991a}: in order to allow the genes to take values outside the interval defined by the parents, a method of extrapolation is necessary.
-Linear crossover introduces such an approach, and produces three children from two parents, following equation \ref{equation_mating_linear_crossover}.
-Less couples are required in order to fill up the generation.
-	\begin{equation}
-	\left\lbrace \begin{array}{l} 
-	g_{o1,n} = 0.5 g_{p1,n} + 0.5 g_{p2,n} \\ 
-	g_{o2,n} = 1.5 g_{p1,n} - 0.5 g_{p2,n} \\ 
-	g_{e3,n} = - 0.5 g_{p1,n} + 1.5 g_{p2,n} \\ 
-	\end{array} \right.
-	\label{equation_mating_linear_crossover}
-	\end{equation}
-
-	\item \textbf{Heuristic crossover} \citep{Michalewicz1996}: it is a variation of the latter methods that relies on the following equation:
-	\begin{equation}
-	\left\lbrace \begin{array}{l} 
-	g_{o1,n} = \beta (g_{p1,n} - g_{p2,n}) + g_{p1,n} \\
-	g_{o2,n} = \beta (g_{p2,n} - g_{p1,n}) + g_{p2,n} \\
-	\end{array} \right.
-	\label{equation_mating_heuristic_crossover}
-	\end{equation}
-
-	\item \textbf{Linear interpolation}: unlike previous techniques, this technique does not rely on crossover points, but on a linear interpolation on every gene of the couple (equation \ref{equation_mating_linear_interpolation}).
-	\begin{equation}
-	\left\lbrace \begin{array}{l} 
-	c_{o1} = c_{p1} - \beta (c_{p1} - c_{p2}) \\
-	c_{o2} = c_{p2} + \beta (c_{p1} - c_{p2}) \\
-	\end{array} \right.
-	\label{equation_mating_linear_interpolation}
-	\end{equation}
-	where $c_{o1}$ and $c_{o2}$ are the full chromosomes of the offspring, and $c_{p1}$ an $c_{p2}$ are the ones of the parents.
-As before, $\beta$ is a random value between 0 and 1, and is here the same for every gene.
-
-	\item \textbf{Free interpolation}: this technique performs interpolation on each gene, like the previous one; but in this case, the weighting factor changes for each gene:
-	\begin{equation}
-	\left\lbrace \begin{array}{l} 
-	c_{o1} = c_{p1} - [\beta_{1} (g_{p1,1} - g_{p2,1}), \beta_{2} (g_{p1,2}\\
-	~~~~~~~~~~~~ - g_{p2,2}), ..., \beta_{Ng} (g_{p1,N_{g}} - g_{p2,N_{g}})] \\
-	c_{o2} = c_{p2} + [\beta_{1} (g_{p1,1} - g_{p2,1}), \beta_{2} (g_{p1,2}\\
-	~~~~~~~~~~~~ - g_{p2,2}), ..., \beta_{Ng} (g_{p1,N_{g}} - g_{p2,N_{g}})] \\
-	\end{array} \right.
-	\label{equation_mating_free_interpolation}
-	\end{equation}
-	where $N_{g}$ is the number of genes, and $\beta$ is here independent between the genes.
-
-\end{itemize}
-
-Many other methods or variations exist, combining the advantages of different approaches.
-The performance of the variants being related to the problem to be addressed, we can not identify a priori the best technique for our application.
-
-\subsubsection{Mutation}
-
-The combination of strong genes by the operator of chromosomes crossover is theoretically the most important operating mechanism in the conventional GAs \citep{Holland1992b,Back1993b}.
-However, many studies identify the mutation process as main operator, and crossovers as secondary \citep[see][]{Back1992a,Back1996a,Back1996b,Smith1997a,Deb1999,Haupt2004,Costa2005a,Costa2007a}.
-
-The mutation operator is a direct modification of genes.
-In a binary coding, it is implemented as an inversion of some bits in a chromosome, while in real coding, it is done by changing the gene values.
-Mutations add diversity to the population and prevent a freeze of the evolution, or a genetic drift to a local optimum.
-Thus, it makes the convergence to the global optimum theoretically possible \citep{Beasley1993a}, as they allow exploring beyond the current region of the parameter space.
-They therefore help preventing the algorithm to converge too quickly to a local optimum and bring new characteristics that were not present in the original population \citep{Haupt2004}.
-
-The evaluated and developed mutation operators are the following:
-
-\begin{itemize}
-	\item \textbf{Uniform mutation}: The mutation rate is constant and equal for every gene of each individual; they all have the same probability to mutate.
-When a gene is selected for mutation, a new random value is assigned, according to a uniform law.
-
-	\item \textbf{Variable uniform mutation} \citep{Fogarty1989}: a variable mutation rate over the generations was first suggested by \citet{Holland1992b} and evaluated by \citet{Fogarty1989}.
-It improved significantly the performance of GAs.
-In most applications, the mutation rate decreases with the generations, in a deterministic and global (for all individuals) manner \citep{Back1992b}.
-Its optimum configuration depends on the size of the chromosomes, of the properties of the objective function, and of the population size \citep{Back1992b}.
-We implemented this operator according to equation \ref{equation_mutation_uniformvariable}.
-	\begin{equation}
-	p_{n,G} = p_{G_{0}}+\left( \dfrac{p_{G_{0}}-p_{G_{m,p}}}{G_{m,p}} \right) min\left\lbrace G,G_{m,p}\right\rbrace 
-	\label{equation_mutation_uniformvariable}
-	\end{equation}
-	where $p_{n,G}$ is the mutation rate (probability) of the gene $n$ for generation number $G$, $G_{m,p}$ is the maximum number of generations during which the mutation rate varies.
-$p_{G_{0}}$ is the initial mutation probability, and $p_{G_{m,p}}$ is the final one.
-$p_{G_{0}}$, $p_{G_{m,p}}$ and $G_{m,p}$ are the three controlling parameters of the operator.
-The evolution of the mutation rate is linear.
-
-	\item \textbf{Constant normal mutation}: many use normal distributions to generate new values. The gene $g$ that mutate becomes:
-	\begin{equation}
-	g' = N(g,\sigma^{2})
-	\label{equation_mutating_normal_distribution}
-	\end{equation}
-	where $\sigma$ is the standard deviation of the distribution.
-The disadvantage of this technique is that an accurate value of $\sigma$ must be chosen \citep{Haupt2004}, which is impossible to know beforehand.
-
-	\item \textbf{Variable normal mutation}: with the same logic that the variable uniform mutation, we tested a mutation operator using a normal distribution with a variable mutation rate and standard deviation.
-The mutation rate is calculated with equation \ref{equation_mutation_uniformvariable}.
-On the same principle, we decrease linearly the standard deviation over the generations:
-	\begin{equation}
-	\sigma_{n,G} = \sigma_{G_{0}}+\left( \dfrac{\sigma_{G_{0}}-\sigma_{G_{m,\sigma}}}{G_{m,\sigma}} \right) min\left\lbrace G,G_{m,\sigma}\right\rbrace 
-	\label{equation_mutation_normalvariable}
-	\end{equation}
-	where $\sigma_{n,G}$ is the standard deviation of gene $n$ et generation number $G$, $\sigma_{G_{0}}$ is the initial standard deviation, $\sigma_{G_{m,\sigma}}$ is the final standard deviation, $G_{m,\sigma}$ is the maximum number of generations during which the standard deviation varies.
-$p_{G_{0}}$, $p_{G_{m,p}}$, $G_{m,p}$, $\sigma_{G_{0}}$, $\sigma_{G_{m,\sigma}}$ and $G_{m,\sigma}$ are the six parameters of the method.
-
-	\item \textbf{Non-uniform mutation} \citep{Michalewicz1996}: two random numbers are picked based on a uniform law: $r_{1}$, which determines the direction of the change, and $r_{2}$, which determines its magnitude.
-The new value of the gene is given by the following equation:
-	\begin{equation}
-	g_{n}^{'} = 
-	\left\lbrace \begin{array}{l l} 
-	g_{n} + \left(b_{n}-g_{n}\right) r_{2} \left(1 - \dfrac{G}{G_{m}} \right)^{2} & if \; r_{1} < 0.5 \\
-	g_{n} - \left(g_{n}-a_{n}\right) r_{2} \left(1 - \dfrac{G}{G_{m}} \right)^{2} & if \; r_{1} \geq 0.5 \\
-	\end{array} \right.
-	\label{equation_mutation_nonuniform_original}
-	\end{equation}
-	where $a_{n}$ is the is the lower bound of the $n$-th gene, $b_{n}$ its upper bound, $G$ the present generation, and $G_{m}$ the maximum number of generations.
-
-	We adapted this operator for our application, which is not based on a predefined number of generations:
-	\begin{equation}
-	g_{n}^{'} = 
-	\left\lbrace \begin{array}{l l} 
-	g_{n} + \left(b_{n}-g_{n}\right) r_{2} \varphi^{2} & if \; r_{1} < 0.5 \\
-	g_{n} - \left(g_{n}-a_{n}\right) r_{2} \varphi^{2} & if \; r_{1} \geq 0.5 \\
-	\end{array} \right.
-	\label{equation_mutation_nonuniform}
-	\end{equation}
-
-	with
-
-	\begin{equation}
-		\varphi = 1 - \min \left\lbrace \dfrac{G}{G_{m,r}}, 1 \right\rbrace \left(1-\omega\right)
-	\end{equation}
-
-	where $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a threshold chosen by the user to maintain a minimum search radius when $G>G_{m,r}$.
-During the first generations, the exploration extent covers the entire parameter space.
-However, this area is reduced over generations, allowing exploitation of local solutions.
-
-	\item \textbf{Individual adaptive mutation rate} \citep{Back1992a}: based on the ideas of Evolution Strategies \citep[see][]{Rechenberg1973, Schwefel1981}, \citet{Back1992a} introduced a concept of self-adaptive genetic algorithms.
-The idea is to distribute control parameters within individuals themselves, which partially decentralize control of the evolution.
-It allows reducing the parametrization of GAs and introducing a notion of self-management.
-The first approach is the introduction of a mutation rate per individual, that mutates itself under its own probability \citep{Back1992a}.
-Then, the eventual new rate is used to mutate the genes of the individual.
-Thus, as this rate decreases, it will have less probability of being itself mutated.
-This approach is close to the natural adaptation phenomena.
-A population less suited to its environment is changing faster than better adapted populations.
-Mutations are performed according to a constant uniform distribution.
-The initial mutation rates are randomly chosen \citep{Back1992a} and the method has no parameter.
-Other approaches exist to introduce a self-adaptation \citep[see][]{Smith1997a,Deb1999,Deb2001a}.
-
-	\item \textbf{Individual adaptive search radius} (new): based on the ideas of the non-uniform mutation, we introduce a search radius in the approach of individual adaptive mutation rates.
-This search radius $r_{a}$, bounded between 0 and 1, is also adaptive and behaves similarly to the adaptive mutation rates.
-In order to separate its evolution from the one of the mutation rate, its own value is considered initially as a self-mutation rate to eventually mutate before being used as a normalized search radius.
-The value of a mutated gene is given by the following equation, which is a simplification of the non-uniform mutation:
-	\begin{equation}
-	g_{n}^{'} = 
-	\left\lbrace \begin{array}{l l} 
-	g_{n} + \left(b_{n}-g_{n}\right) r_{2} r_{a} & if \; r_{1} < 0.5 \\
-	g_{n} - \left(g_{n}-a_{n}\right) r_{2} r_{a} & if \; r_{1} \geq 0.5 \\
-	\end{array} \right.
-	\label{equation_mutation_rayon_adaptatif}
-	\end{equation}
-	where $r_{1}$ and $r_{2}$ are randomly selected, in the same way as for the non-uniform mutation. No external parameter is therefore necessary.
-
-	\item \textbf{Chromosome of adaptive mutation rate} \citep[\textit{n adaptative mutation rate},][]{Back1992a}: analogously to the individual adaptive mutation rate, this approach leaves the control of the evolution rate to the individuals themselves.
-The difference here is that each gene has a specific mutation rate.
-The main advantage is that the tuning of the mutation can be much more precise \citep{Smith1997a}.
-We therefore consider a second chromosome containing the mutation rate for each gene of the first chromosome.
-The operations of mutation and self-mutation are similar to the case of the individual adaptive mutation rate, but in a distributed way, within the chromosome.
-Another difference is that we apply the same crossover operations as those applied to the first chromosome, and this for the same crossing points.
-Thus, during an exchange of genes, children also inherit the mutation rates specific for each of these genes.
-
-	\item \textbf{Chromosome of adaptive search radius} (new): we introduced this operator that combines the operations of the chromosome of adaptive mutation rate to our adaptive search radius approach.
-Similarly, an individual has 3 chromosomes: the first containing the values to be optimized, the second containing the distributed mutation rate, and the last one, the distributed search radius.
-Again, no external parameters are required.
-
-	\item \textbf{Multi-scale mutation} (new): finally, we developed another approach, that is also based on the search radius concept.
-However, the latter is not decreasing with time.
-Methods based on a reduction of the mutation rate or radius simulate a transition from the exploration phase to the exploitation one.
-The idea is consistent as long as we are confident that the algorithm will converge towards the global optimum.
-Indeed, once the algorithm is in the exploitation mode, it is very unlikely to go out of the region it converges to.
-We wanted to test an approach that combines both exploration and exploitation during the whole optimization.
-Thus, we considered the search radius $r_{a}$ of equation \ref{equation_mutation_rayon_adaptatif} as a random value for each individual, but restricted to 4 equiprobable values: 1, 0.5, 0.1, 0.02, which range from full exploration to fine exploitation.
-The only external parameter is the mutation rate which is fixed.
-
-\end{itemize}
-
-When the gene to mutate is represented by a list of distinct values (eg meteorological variable or analogy criterion), the random choice of a new value is always based on a uniform distribution, without notion of search radius.
-There is indeed no meaning to use operators based on principles of proximity when the latter does not exist.
-
-\subsubsection{Elitism}
-
-We used a process of elitism on the natural selection as well as on mutations.
-This ensures the survival of the best individual so that we do not lose a better solution.
-This approach is very common in the field of GAs \citep{Haupt2004}.
-After the natural selection operator, if the best individual has not been selected, it is copied to the mating pool instead of an individual randomly picked.
-After mutation, if the best individual has mutated and if its new version has a lower performance score than the original, the latter is also reinserted in the mating pool instead of an individual randomly chosen.
-
-\subsubsection{Ending the optimization}
-
-The convergence check determines whether the solution is acceptable and if the algorithm may stop.
-The stopping criteria are not often well documented in GAs case studies.
-We chose to stop the optimization if the best individual does not change for $x$ generations.
-This value should not be too low to allow the algorithm to escape from a local optima.
-In addition, the rate of improvement decreases with the progression of the optimization.
-It is thus common that the best individual does not evolve over several generations when we get closer to the global solution.
-We chose a value of $x=20$ generations.
-
-\subsection{Implementation and constraints}
-
-Some constraints need to be taken into account.
-For example, when a crossover or a mutation operation results in a parameter value standing out of the authorized bounds, it has to be brought back within the limits.
-Moreover, the parameters are of different nature: some are continuous, such as the weight, some are discretized, such as the analogues number, or the spatial windows, and finally, some are independent elements in an array, such as the selection of the meteorological variable.
-New values resulting from the optimizer need to respect the type of data it represents.
-
-Other constraints exist in between the parameters, such as the temporal window of the moisture index that has to be consistent in between the relative humidity and the precipitable water.
-Another example is the weighting of the different pressure levels which has to be normalized.
-
-GAs are very computationally intensive because they require many evaluations of the objective function.
-These assessments are very long in our application, as they require calculating and assessing a forecast for every day of the calibration period.
-In order to reduce the computation time, we avoid recalculating the performance score of an individual who has previously been evaluated and that has not changed.
-We keep the score of each individual living in the selection until it mutates.
-
-The assessment (calculation of the objective function) of each member of the population of a generation is completely independent and can be performed in parallel on different processors of a computer \citep{Alliot2005}.
-We implemented this technique and the resulting time savings was very important.
-In order to perform optimizations for multiple time series, the use of a cluster is a necessity, which our code allows.
-
-\subsection{Recommendations of parametrization}
-
-The GAs parametrization, such as the mutation rate, population size, natural selection options, and so on, is difficult given the high number of existing variants, each developed for a specific problem \citep{Haupt2004, Costa2007a}.
-This parametrization depends on the objective function, implementation variants, the range of the parameters to be optimized, and performance indicators.
-Thus, different studies suggest very different parametrization.
-
-A key element of the parametrization of GAs is finding the right balance between exploration and exploitation \citep{Back1992a, Smith1997a}.
-Exploration is characterized by a relatively high probability to assess the regions of the parameter space that have not yet been visited.
-This probability must be sufficiently large at the beginning of the optimization, so that the algorithm is capable of identifying the region where the global optimum is located.
-Exploitation is characterized by a local search in an area of interest, and generally makes small movements.
-The latter is interesting to refine the results at the end of the optimization.
-
-\citet{DeJong1975a} and \citet{Grefenstette1986} compared different implementations and parametrizations of GAs on functions of varying complexity.
-They observed that a small population size improves the initial performance, while a large population improves long-term performance.
-They also observed that the ratio of the population to keep for the mating pool is around 50\% (45\% to 60\%).
-
-Values of the mutation rate varies broadly between the studies: from 0.001 \citep{DeJong1975a} to 0.2 \citep{Haupt2004}.
-\citet{Back1996b} showed that mutation rates higher than the usual ranges are more optimal at the beginning of the optimization, allowing further exploration.
-The combination of a small population and a high mutation rate works best for the first generations \citep{DeJong1975a, Back1996b, Haupt2004}, but as we could observe, it does not guarantee the quality of the final result.
-Incremental approaches with varying mutation rates are certainly more optimal but more complex to implement \citep{Back1996a, Back1996b}.
-
-\subsubsection{Comparison process and results}
-
-One of our goals being to make recommendations of parametrization in order to optimize the AM, we proceeded systematically.
-The results are summarized hereafter \citep[see][for the details]{Horton2012a}.
-We used concepts from the factorial design approach \citep[see eg.][]{Costa2005a,Costa2007a,Mariano2010a}, which is sometimes used for comparative analysis of different parametrizations of GAs.
-We processed by stages, analysing in details and in a systematic way every variants of the implemented operators, in combination with multiple other options and parameters in order to take into account eventual co-dependencies.
-
-In order to evaluate a combination of operators/options, we processed 10 optimizations for one parametrization of GAs. The performances were characterized by four indicators:
-
-\begin{itemize}
-	\item mean performance score: average of the final scores of the 10 optimizations,
-	\item convergence: the number of optimizations that converged to a supposed global optimum,
-	\item number of generations: characterization of the convergence speed,
-	\item number of evaluations of the objective function: characterization of the required calculation time (more realistic than the number of generations).
-\end{itemize}
-
-This comparison required tens of thousands of optimizations that were performed on a cluster of the University of Lausanne. The results, detailed in \citet{Horton2012a} are synthesized hereafter:
-
-\begin{itemize}
-	\item \textbf{Population size $N$}: we found the following ranges to be accurate in average for the population size (number of parameter sets of the AM):
-
-	$50<N<100$ for a very simple implementation of the AM (1 level of analogy with 2 pressure levels),
-
-	$N\approx200$ for a bit more complex AM (1 level of analogy with 4 pressure levels, or 2 level of analogy with less pressure levels),
-
-	$N\approx500$ for significantly more complex AMs (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the moisture analogy),
-
-	We didn't find any improvement with $N>500$, the results were even surprisingly of a lower quality.
-However, this cannot be generalized and depends on the AM to optimize, and supposedly on the characteristics of the processes generating the precipitations in a given region.
-
-	\item \textbf{Natural selection}: this operator has no significant influence, and both tested implementations work fine, with a slightly better performance for the ratio-elitism.
-
-	\item \textbf{Selection of couples}: 6 variants of the couples selection were assessed.
-The performance of these variants are relatively close, both in terms of performance score, convergence, and number of evaluations.
-The random pairing performed the most poorly, when the tournament selection with 3 candidates was slightly superior.
-The roulette wheel weighting is not far behind, but it is less effective in terms of convergence and number of evaluations.
-This operator has not a significant role in our application.
-
-	\item \textbf{Chromosomes crossover}: we compared 21 different options of the crossover operators.
-This analysis revealed some slightly better options, some bad ones, and many averages.
-Among the bad operators, we find first the heuristic crossover, which is also more demanding in number of evaluations, as well as the linear crossover.
-Binary-like crossovers (especially with 2 points of intersection, whether $\beta$ is shared or not) are significantly better than the others, especially in terms of convergence.
-The two points crossover is relatively close.
-Other operators can be considered usable, yet may not be optimal.
-Once again, this operator is not the key of the GAs parametrization.
-
-	\item \textbf{Mutation}: we compared the 10 mutation operators with different options, bringing the number of variations of this operator up to 110.
-We immediately observed that the mutation operator has a very important role on the performance of the optimizations of the AM, and that the other reproduction operators seem of secondary importance.
-This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction.
-He even suggests, in opposition with the theory of \citet{Holland1992a}, that chromosomes crossovers have mostly a corrective role of mutation operations.
-Various studies have also identified the importance of the mutation operator relatively to reproduction \citep[see eg.][]{Back1992a, Back1996b, Smith1997a, Deb1999, Haupt2004, Costa2005a, Costa2007a}.
-
-	The mutation operators based on a variable normal or uniform law work very poorly and are difficult to configure.
-We then observe many operators more or less with the same performance scores and requiring a variable amount of assessments.
-The convergence analysis allows us to highlight three best operators:
-
-	\textit{Non-uniform mutation} \citep{Michalewicz1996}: this operator is good in terms of convergence, mainly when the number of parameters to optimize is rather low.
-The number of required evaluations, however, can be quite substantial.
-The main disadvantage of the non-uniform mutation is the complexity of its parametrization, which is difficult to estimate a priori.
-These parameters must be carefully chosen to be in line with the evolution rate of the population, and are therefore dependent on the problem being treated.
-We could observe that the $\omega$ coefficient does not influence performance.
-The role of $G_{m}$ is rather difficult to judge, but does not seem essential.
-The mutation rate was found to be important.
-The difficulty is that the optimal value seems to be very case-related.
-Indeed, by even changing the precipitation time series (ie optimizing for another subregion), but not the complexity of the AM, the optimal mutation rate changes, making it impossible to estimate in advance.
-
-	\textit{Chromosome of adaptive search radius}: unlike the previous one, our new operator is very robust, as it requires no option and is auto-adapting.
-It may be sometimes a little bit slower for simple problems, but does not require parametrization, which is an important advantage.
-It is interesting to notice that our insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).
-
-	\textit{Multi-scale mutation}: finally, our multi-scale mutation, which also performs pretty well, can as well be seen as fairly robust, since it requires only one parameter, the mutation rate.
-However, it can also be difficult to estimate a correct value a priori.
-
-	It may be wise to perform multiple optimizations and to consider these three operators in parallel in order to obtain results from algorithms that are either sometimes more efficient or more robust.
-It is interesting to note that the three best techniques incorporate a notion of search distance.
-It is likely that this notion is the key to these algorithms, for our application, and allows them to initially explore the parameter domain, and then to converge.
-The search radius in fact directly represents the notion of transition between exploration and exploitation, in our opinion more than a possible evolution of mutation rates.
-
-	\item \textbf{Other options}: A ratio of 50\% for the mating pool seems to be a good choice.
-
-\end{itemize}
-
-\subsubsection{Recommended parametrization of GAs}
-
-We evaluated the optimization by genetic algorithms on AMs of varying complexity, with a large number of combinations of operators to be able to make recommendations for optimizing the AM.
-Our conclusions are:
-
-\begin{itemize}
-	\item The optimization does not systematically converge to the global optimum  (but still often nearby), which is why we recommend doing several optimizations in parallel in order to compare the results, analyse the convergence, and keep the best.
-
-	\item The population size should be in accordance with the complexity of the AM to optimize: from 50 for the simple ones, up to 500 for the most complex AMs.
-
-	\item The value of the ratio for the intermediate population is not so important, and value of 50\% seems quite appropriate.
-
-	\item Ratio-elitism is slightly better than tournaments for the natural selection operator, but it is not decisive.
-
-	\item The performance of the operators for the couples selection perform relatively similarly.
-The roulette wheel weighting and the tournament selection are more efficient in terms of convergence and required number of evaluations.
-
-	\item Most crossover operators have relatively similar performance. Binary-like crossover with two points of intersection are better than others, especially for convergence.
-
-	\item Mutation has a clearly dominant influence.
-Three mutation operators stand out, two of which we have developed: the non-uniform mutation, the multi-scale mutation, and the chromosome of adaptive search radius.
-The latter is the most robust as it has no controlling parameter.
-
-\end{itemize}
-
-In order to make an optimization of the AM with genetic algorithms, it may be wise to consider these three mutation operators in parallel.
-We would then combine algorithms that are sometimes faster to other that are more robust.
-In order to be confident in the optimized AMs, we propose using a set of the following mutation operators:
-
-\begin{itemize}
-	\setlength\itemsep{-4px}
-	\item 1x non-uniform, $p_{mut}=0.1$, $G_{m}=50$, $\omega=0.1$
-	\item 1x non-uniform, $p_{mut}=0.1$, $G_{m}=100$, $\omega=0.1$
-	\item 1x non-uniform, $p_{mut}=0.2$, $G_{m}=100$, $\omega=0.1$
-	\item 1x multi-scale,  $p_{mut}=0.1$
-	\item 2x chromosome of adaptive search radius
-\end{itemize}
+Due to the limitation of the sequential approach, we implemented a global optimization technique based on Genetic algorithms.
+This allows for a fully automatic and objective optimization of the AM.
+However, as this topic is rather consequent, it will be the subject of another publication.
 
@@
 The Optimizer implements different optimization techniques, such as the sequential approach, a Monte-Carlo method, and a global optimization technique.
-
-In order to automatically optimize the analogue method, we evaluated genetic algorithms, a global optimization technique, that is able to solve complex problems.
-Given the large number of existing operators and options, we had to evaluate systematically multiple variants to identify which operators are important, and which variant works best for the analogue method.
-We could thus identify that the mutation operator is a key element for our application, and provided new variants that were found to be efficient, such as the Chromosome of adaptive search radius that seems to be very reliable (no control parameter) and efficient .
-Recommendations were established for a relevant use of GAs for the optimization of the analogue method.
-However, there may still be possible improvements, through new operators, in order to improve the optimization performance and speed.
-Usage of this global optimization greatly eases the adaptation of the AM to new regions (with different leading meteorological processes) or to new predictands, as the optimization is performed automatically and globally.
 
@@
 
-The global optimization tools allow easily adapting the AM to new regions by taking into account local meteorological influences, and has thus a great potential of use.
-Moreover, it allows exploring automatically datasets in order to extract the most relevant variables.
-It is thus possible to try assessing other predictands, such as the temperature, the limit of snowfall, the occurrence of hail, or wind, while leaving the algorithms select the best variables and the associated parameters.
+%TODO: rework
 
@@
 
-AtmoSwing is developed under the Mercurial distributed revision control, and the source code can be found at:
+AtmoSwing is open source, under the CDDL license. It is developed under the Mercurial distributed revision control, and the source code can be found at:
 
@@
 
-The Forecaster and the Viewer are fully available, whereas the open version of the Optimizer includes all methods but the Genetic algorithms.
-These are planed to be released in the future, but not at the time of writing.
-
 \begin{acknowledgements}
-Thanks to Lucien Schreiber and Richard Metzger for their programming advices.
-Thanks to Renaud Marty for his active involvement in testing AtmoSwing against his code base.
-Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of.
+Thanks to Lucien Schreiber and Richard Metzger for their programming advices. Thanks to Renaud Marty for his active involvement in testing AtmoSwing against his code base.
 

### 2015-11-03 Genetic algorithms - Journal of Climate/template.tex
Moving GAs out of the AtmoSwing article.

%% Version 4.3.2, 25 August 2014
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template.tex --  LaTeX-based template for submissions to the 
% American Meteorological Society
%
% Template developed by Amy Hendrickson, 2013, TeXnology Inc., 
% amyh@texnology.com, http://www.texnology.com
% following earlier work by Brian Papa, American Meteorological Society
%
% Email questions to latex@ametsoc.org.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PREAMBLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Start with one of the following:
% DOUBLE-SPACED VERSION FOR SUBMISSION TO THE AMS
\documentclass{ametsoc}

% TWO-COLUMN JOURNAL PAGE LAYOUT---FOR AUTHOR USE ONLY
%\documentclass[twocol]{ametsoc}

\usepackage{multirow}
\usepackage{gensymb}
\usepackage{subcaption}
\usepackage{xcolor,colortbl}

% After http://tex.stackexchange.com/questions/94799/how-do-i-color-table-columns-and-rows
\newcommand{\mc}[2]{\multicolumn{#1}{c}{#2}}
\definecolor{Gray}{gray}{0.85}
\definecolor{LightCyan}{rgb}{0.88,1,1}
\newcolumntype{a}{>{\columncolor{Gray}}c}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% To be entered only if twocol option is used

\journal{jcli}

%  Please choose a journal abbreviation to use above from the following list:
% 
%   jamc     (Journal of Applied Meteorology and Climatology)
%   jtech     (Journal of Atmospheric and Oceanic Technology)
%   jhm      (Journal of Hydrometeorology)
%   jpo     (Journal of Physical Oceanography)
%   jas      (Journal of Atmospheric Sciences)	
%   jcli      (Journal of Climate)
%   mwr      (Monthly Weather Review)
%   wcas      (Weather, Climate, and Society)
%   waf       (Weather and Forecasting)
%   bams (Bulletin of the American Meteorological Society)
%   ei    (Earth Interactions)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Citations should be of the form ``author year''  not ``author, year''
\bibpunct{(}{)}{;}{a}{}{,}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% To be entered by author:

%% May use \\ to break lines in title:

\title{Global Optimization of the Analogue Method by Means of Genetic Algorithms}

%%% Enter authors' names, as you see in this example:
%%% Use \correspondingauthor{} and \thanks{Current Affiliation:...}
%%% immediately following the appropriate author.
%%%
%%% Note that the \correspondingauthor{} command is NECESSARY.
%%% The \thanks{} commands are OPTIONAL.

    %\authors{Author One\correspondingauthor{Author One, 
    % American Meteorological Society, 
    % 45 Beacon St., Boston, MA 02108.}
% and Author Two\thanks{Current affiliation: American Meteorological Society, 
    % 45 Beacon St., Boston, MA 02108.}}

\authors{Pascal Horton\correspondingauthor{Terranum, Rue de l'industrie 35 bis, 1030 Bussigny, Switzerland.}}

%% Follow this form:
    % \affiliation{American Meteorological Society, 
    % Boston, Massachusetts.}

\affiliation{University of Lausanne and Terranum, Lausanne, Switzerland}

%% Follow this form:
    %\email{latex@ametsoc.org}

\email{pascal.horton@alumnil.unil.ch}

%% If appropriate, add additional authors, different affiliations:
    %\extraauthor{Extra Author}
    %\extraaffil{Affiliation, City, State/Province, Country}

\extraauthor{Michel Jaboyedoff}
\extraaffil{University of Lausanne, Lausanne, Switzerland}

%% May repeat for a additional authors/affiliations:

%\extraauthor{}
%\extraaffil{}

\extraauthor{Charles Obled}
\extraaffil{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%
% Enter your abstract here
% Abstracts should not exceed 250 words in length!
%
% For BAMS authors only: If your article requires a Capsule Summary, please place the capsule text at the end of your abstract
% and identify it as the capsule. Example: This is the end of the abstract. (Capsule Summary) This is the capsule summary.

\abstract{

	The global optimization can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now. Indeed, it allows taking into account parameters inter-dependencies, adding new degrees of freedom, and choosing objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).

	These kind of optimization techniques need however to be tailored to the problem to solve. We had to assess multiple combinations of algorithms, and even to develop new operators, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of genetic algorithms to optimize the analogue method. These recommendations are a consequent outcome of this work, as it opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.

	}

\begin{document}

%% Necessary!
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MAIN BODY OF PAPER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

%% In all cases, if there is only one entry of this type within
%% the higher level heading, use the star form: 
%%
% \section{Section title}
% \subsection*{subsection}
% text...
% \section{Section title}

%vs

% \section{Section title}
% \subsection{subsection one}
% text...
% \subsection{subsection two}
% \section{Section title}

%%%
% \section{First primary heading}

% \subsection{First secondary heading}

% \subsubsection{First tertiary heading}

% \paragraph{First quaternary heading}

\section{Introduction}
\label{section_intro}

The sequential calibration cannot optimize all parameters of the AM, as several are manually selected, such as the meteorological variable, the pressure level and the temporal windows. Testing multiple combinations of these can be cumbersome, especially when considering multiple predictors within the same level of analogy. Moreover, the parameters are calibrated successively within the same level of analogy, and in-between them.

We thus decided to explore optimization techniques that can handle all parameters fully automatically. We first assessed the \citet{Nelder1965a} method, which was found to be unsuitable for this purpose. Due to the complexity of the AM and its non-linearity, a technique of global optimization is required. We thus implemented Genetic algorithms in AtmoSwing Optimizer in order to perform a global optimization of the AM. This article is not about discussing the results of such a technique, but describing the details of the implementation. The demonstration of the benefit brought by such an approach is the topic of another article. The details of the implementation being numerous, the description is provided in the next dedicated section (\ref{sec:gas}).

Up to now, the optimization of the method has been undertaken by semi-automatic calibration procedures. However, the choice of predictor variables, pressure levels and temporal windows were still to be chosen manually before optimizing the spatial windows and the number of analogues. Moreover, the semi-automatic technique proceeds to the optimization sequentially, ignoring potential dependencies between the parameters of the method. Thus, optimizing the method with the semi-automatic technique is laborious, as many combinations of predictors (variables, pressure levels, temporal windows) have to be assessed. Moreover, due to its sequential approach, the risk of ending in a local optimum is high and can not be avoided. We thus propose a global optimization approach by means of Genetic algorithms, tailored to the analogue method (AM).

\section{The analogue method}
\label{section_analog_method}

\section{Motivation for a global optimization}

\section{Optimization using Genetic algorithms}
\label{sec:gas}

Genetic algorithms (GAs) come from the world of stochastic optimization, more specifically from metaheuristic approaches. These are stochastic iterative algorithms that behave like search algorithms by exploiting the characteristics of a problem and are particularly suitable for complex parameter spaces.

Genetic algorithms are part of the family of evolutionary algorithms \citep{Back1993b, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection. GAs are the most used technique from evolutionary algorithms \citep{Back1993b}, and they are constantly improving \citep{Haupt2004}. However, with time, the different methods of evolutionary algorithms tend to be similar and share many commonalities \citep{Back1996b, Haupt2004}.

The method was originally developed by \citet{Holland1992b} and popularized by \citet{Goldberg1989}. Unlike a linear or local optimization, GAs seek the global optimum on a complex surface, theoretically without restriction, but with no guarantee to reach it.

\subsection{Basic concepts of the genetic algorithms}

GAs mimic the evolution of a population of individuals in a new environment, by applying rules based on natural processes, such as DNA mutation, chromosomes crossover, natural selection, etc. It simulates the fact that in a natural environment, the most suitable individuals tend to survive longer, to reproduce more easily, and so to influence coming generations by providing genes that provide some good performance in a certain domain. Generation after generation, the DNA mixes and the strong genes cumulate in some individuals \citep{Beasley1996a}. Globally, the fitness of the population to its environment increases, while retaining enough variety to not converge too quickly to a local optimum.

Applications of GAs are very diversified as they can handle many parameters of various types \citep{Joines1996a}, even with very complex cost surfaces \citep{Haupt2004}. GAs work remarkably well with intervariable dependences \citep{Haupt2004}. The objective function to optimize (often named fitness function in this context) can be of different types (mathematical function, experimental or numerical modeling). Only the resulting value is used for optimization. Indeed, these algorithms do not require any knowledge of the problem, which can be used as black-box, but they must be adapted in order to perform optimally.

By means of the reproduction operator and the natural selection, the GAs focus on the most promising regions of the parameter space \citep{Holland1992b}. Points (parameter sets) are densified in these areas because the strong genes of the best individuals propagate from generation to generation.

Two conditions guarantee in theory the convergence to the global optimum \citep{Zitzler2004a}: (1) Parameters mutations that can allow to explore the entire parameter space, thereby ensures that any value can be achieved with a non-zero probability. (2) A rule of elitism ensuring that an optimal solution cannot be lost or damaged.

\subsection{Structure and operators}

The GAs optimize a population of individuals (parameter sets). Each individual contains a chromosome (parameters of the AM in our case). We call gene every parameter that constitutes the chromosome. The parameters to optimize have long been coded in binary form and assembled as strings in the canonical GAs \citep{Goldberg1989}. Encoding and decoding steps were needed to transform the variable from its floating-point representation into its binary representation, and vice versa, which introduce quantification errors \citep{Haupt2004}. According to \citet{Holland1992b}, working with binary chromosomes was supposed to be more efficient \citep{Goldberg1990a, Back1993b}. However, more and more applications use floating-point representations, allowing to avoid the coding and decoding steps and the quantification errors \citep{Haupt2004}, and which also often resulted in a performance improvement \citep{Goldberg1990a}. It is thus now considered that for continuous variables, a floating-point representation is more suited \citep{Michalewicz1996, Herrera1998a, Haupt2004, Back1996b, Gaffney2010a}.

There are numerous implementation variants of GAs often optimal for a given problem \citep{Hart1991a,Schraudolph1992a}. The divergences are the operators implementation, through significantly different algorithms, which has an important effect on the results \citep{Gaffney2010a}. However, the structure of the method (Figure \ref{fig:structure_gas}) resulting from the work of \citet{Holland1992b} is common to most applications \citep{Back1993b}, and consists in the following steps:

\begin{enumerate}
	\item A population of $N$ individuals (parameter sets of the AM) is randomly generated, which constitutes the initial population.
	\item The fitness (performance score or objective function) of every individual is assessed.
	\item A natural selection is applied, after which only the best individuals remain, which constitutes the intermediate generation.
	\item From this intermediate generation, couples are formed according to given rules.
	\item These couples proceed to reproduction, or chromosome crossover, in order to mix their genes (parameters) according to the operator version. New children are generated in order to fill the intermediate generation back to $N$ individuals.
	\item Parents and children are then subject to mutation, where some genes get affected, meaning some parameter values are randomly changed.
	\item The new formed generation is then re-assessed.
	\item According to the ending criteria, the optimization ends or starts again for another iteration.
\end{enumerate}

\begin{figure}[htb]
	\includegraphics[width=8.3cm]{figures/figure_structure_gas.pdf}
	\caption{Genetic algorithms operational flowchart}
	\label{fig:structure_gas}
\end{figure}

All operators we used and their options, applied to real coding, are described in the following sections. Many other operators exist, but we will only present the ones we evaluated.

\subsubsection{Genesis of the population}

The first step of the optimization is to generate the initial population. A population is a set of $N$ individuals (each of which represents a point in the space of potential solutions, a parameter set of the AM in our application) that we are going to make evolve. A generation is the population at a given time.

A random initialization based on a uniform distribution is the most current version. The size $N$ of the population is often a compromise between the computation time and the quality of the solution. $N$ must allow sufficient sampling of the solutions field \citep{Beasley1996a}, and should thus vary as a function of chromosome size (ie the number of parameters to be optimized).

\subsubsection{Natural selection}

Natural selection is performed on the basis of the values of the objective function. The selection allows to only keep a certain part of the population, usually half ($N/2$), which can access the mating pool (intermediate generation with $N_{mp}$ members). If $N_{mp}$ is too high, the reproduction rate is too low, whereas if it is too small, the strong traits of individuals do not have the ability to accumulate in the same chromosome \citep{Haupt2004}. Several techniques exist, such as:

\begin{itemize}
	\item \textbf{$N_{mp}$-elitism} \citep{Michalewicz1996}: the population is sorted according to the value of the objective function and only the better half is preserved.

	\item \textbf{Tournament selection} \citep{Michalewicz1996, Zitzler2004a}: two individuals are randomly selected and fight. The one with the highest performance score is chosen, but with a certain probability, in order to reduce the selection pressure. This procedure is repeated until the mating pool is full. Individuals can be selected several times, and thus be represented several times in the mating pool.
\end{itemize}

\subsubsection{Selection of the couples}

Individuals of the mating pool can reproduce. It begins with the selection of pairs (the parents). The techniques implemented in this work are the following:

\begin{itemize}
	\item \textbf{Rank pairing}: individuals are gathered in pairs according to their rank (classified on the performance scores). Consecutive ranks are put together (odd rows are associated with even rows). This approach is easy to achieve, but does not look like a natural process.

	\item \textbf{Random pairing}: two individuals are randomly selected to form a couple, according to a uniform law.

	\item \textbf{Roulette wheel weighting}: the roulette technique refers to gambling. But unlike casino roulette, this one is biased. Each individual is associated with a sector of the wheel with a certain opening angle, which is its probability of selection \citep{Haupt2004}. The probability assigned to the individuals is proportional to their fitness (objective function), so that the most adapted individuals have the greatest probability of reproduction. There are two techniques for weighting the individuals of the mating pool:

	\textit{Roulette wheel weighting on rank}: the probability of each individual depends on its rank $n$:
	\begin{equation}
	p_{n}=\dfrac{N_{mp}-n+1}{\sum^{N_{mp}}_{n=1}n}
	\label{equation_mating_rank_weighting}
	\end{equation}

	\textit{Roulette wheel weighting on fitness}: the selection probability is calculated based on the value of the objective function. This approach gives more weight to the best individuals when the distribution of performance scores is wide, while the weight is almost similar when all individuals have approximately the same performance score \citep{Haupt2004}. The probability $p_{n}$ of each individual is calculated by the equation \ref{equation_mating_score_weighting}:
	\begin{equation}
	p_{n}=\frac{score_{n}-score_{N_{mp}}}{\sum_{n=1}^{N_{mp}} (score_{n}-score_{N_{mp}})}
	\label{equation_mating_score_weighting}
	\end{equation}
	In our application, the last individual ($N_{mp}$) has zero probability of being selected.

	\item \textbf{Tournament selection}: This operator is similar to the one used in natural selection, but is applied here for the successive selection of each parent. To select a parent, a number of individuals (2 or 3) are randomly picked and the best is kept. This operation is performed twice, once for each partner. This approach imitates the breeding competition in nature \citep{Haupt2004}.
\end{itemize}

\subsubsection{Chromosome crossover}

Once the two parents are selected for breeding, they combine their chromosomes and produce two children, bringing the number of individuals in the population back to $N$ (the parents also return back in the total population in order to complement the next generation). The combination of chromosomes is carried out using a crossover operator, thereby generating two offspring having characteristics derived from both parents. Chromosome crossover widens the search space and favours the combination of strong genes, which can result in more suited children. It allows a mixing of genes and accumulation of positive mutations.

The evaluated crossover operators are the following:

\begin{itemize}
	\item \textbf{Single-point crossover}: a crossover point is randomly chosen for the pair. The genes (our parameters) located after that point are exchanged in between the two chromosomes.

	\item \textbf{Two-point crossover}: works like the single-point crossover, but there are two intersections defining the segments to exchange. This approach, which significantly extends the search space for the children, is considered more efficient than the previous \citep{Beasley1993a, Haupt2004}.

	\item \textbf{Multiple-point crossover} \citep{DeJong1975a}: it is a generalization of the previous, with a number of crossover points up to the number of genes.

	\item \textbf{Uniform crossover} \citep{Syswerda1989}: for each gene of the chromosome, it is randomly chosen to exchange or not the values between the parents.

	\item \textbf{Binary-like crossover} \citep{Haupt2004}: chromosome crossover on a binary coding can generate new values for variables located at intersection points, since the crossovers are applied at the bit level, thus often within a gene. This is not the case for the floating-point representation, since the crossover is performed between the genes. To reproduce the behaviour present in the original algorithms, which introduces new information, \citet{Haupt2004} propose an operator that combines standard crossover with an interpolation approach. The genes located after a crossover point are exchanged, but the gene located at the intersection is modified as follows (equation \ref{equation_mating_as_binary}):
	\begin{equation}
	\left\lbrace \begin{array}{l} 
	g_{o1,n} = g_{p1,n} - \beta (g_{p1,n} - g_{p2,n}) \\
	g_{o2,n} = g_{p2,n} + \beta (g_{p1,n} - g_{p2,n}) \\
	\end{array} \right.
	\label{equation_mating_as_binary}
	\end{equation}
	where $g_{o1,n}$ and $g_{o2,n}$ are the $n$-th gene of the two new offspring, and $g_{p1,n}$ and $g_{p2,n}$ are those of the two parents. $\beta$ is a random value between 0 and 1.

	\item \textbf{Blending method} \citep{Radcliffe1991a}: in this approach, instead of exchanging the genes in between the chromosomes after one or multiple crossover points, these are combined by linear combination (equation \ref{equation_mating_blending_method}). The genes of the parents are blended together using a random value ($\beta$) that can be unique for the whole chromosome, or that can change for every gene. The genes of the offspring are bounded by the genes of the parents, no value can be out of their range.
	\begin{equation}
	\left\lbrace \begin{array}{l} 
	g_{o1,n} = \beta g_{p1,n} + (1-\beta)g_{p2,n} \\ 
	g_{o2,n} = (1-\beta) g_{p1,n} + \beta g_{p2,n} \\
	\end{array} \right.
	\label{equation_mating_blending_method}
	\end{equation}

	\item \textbf{Linear crossover} \citep{Wright1991a}: in order to allow the genes to take values outside the interval defined by the parents, a method of extrapolation is necessary. Linear crossover introduces such an approach, and produces three children from two parents, following equation \ref{equation_mating_linear_crossover}. Less couples are required in order to fill up the generation.
	\begin{equation}
	\left\lbrace \begin{array}{l} 
	g_{o1,n} = 0.5 g_{p1,n} + 0.5 g_{p2,n} \\ 
	g_{o2,n} = 1.5 g_{p1,n} - 0.5 g_{p2,n} \\ 
	g_{e3,n} = - 0.5 g_{p1,n} + 1.5 g_{p2,n} \\ 
	\end{array} \right.
	\label{equation_mating_linear_crossover}
	\end{equation}

	\item \textbf{Heuristic crossover} \citep{Michalewicz1996}: it is a variation of the latter methods that relies on the following equation:
	\begin{equation}
	\left\lbrace \begin{array}{l} 
	g_{o1,n} = \beta (g_{p1,n} - g_{p2,n}) + g_{p1,n} \\
	g_{o2,n} = \beta (g_{p2,n} - g_{p1,n}) + g_{p2,n} \\
	\end{array} \right.
	\label{equation_mating_heuristic_crossover}
	\end{equation}

	\item \textbf{Linear interpolation}: unlike previous techniques, this technique does not rely on crossover points, but on a linear interpolation on every gene of the couple (equation \ref{equation_mating_linear_interpolation}).
	\begin{equation}
	\left\lbrace \begin{array}{l} 
	c_{o1} = c_{p1} - \beta (c_{p1} - c_{p2}) \\
	c_{o2} = c_{p2} + \beta (c_{p1} - c_{p2}) \\
	\end{array} \right.
	\label{equation_mating_linear_interpolation}
	\end{equation}
	where $c_{o1}$ and $c_{o2}$ are the full chromosomes of the offspring, and $c_{p1}$ an $c_{p2}$ are the ones of the parents. As before, $\beta$ is a random value between 0 and 1, and is here the same for every gene.

	\item \textbf{Free interpolation}: this technique performs interpolation on each gene, like the previous one; but in this case, the weighting factor changes for each gene:
	\begin{equation}
	\left\lbrace \begin{array}{l} 
	c_{o1} = c_{p1} - [\beta_{1} (g_{p1,1} - g_{p2,1}), \beta_{2} (g_{p1,2}\\
	~~~~~~~~~~~~ - g_{p2,2}), ..., \beta_{Ng} (g_{p1,N_{g}} - g_{p2,N_{g}})] \\
	c_{o2} = c_{p2} + [\beta_{1} (g_{p1,1} - g_{p2,1}), \beta_{2} (g_{p1,2}\\
	~~~~~~~~~~~~ - g_{p2,2}), ..., \beta_{Ng} (g_{p1,N_{g}} - g_{p2,N_{g}})] \\
	\end{array} \right.
	\label{equation_mating_free_interpolation}
	\end{equation}
	where $N_{g}$ is the number of genes, and $\beta$ is here independent between the genes.

\end{itemize}

Many other methods or variations exist, combining the advantages of different approaches. The performance of the variants being related to the problem to be addressed, we can not identify a priori the best technique for our application.

\subsubsection{Mutation}

The combination of strong genes by the operator of chromosomes crossover is theoretically the most important operating mechanism in the conventional GAs \citep{Holland1992b,Back1993b}. However, many studies identify the mutation process as main operator, and crossovers as secondary \citep[see][]{Back1992a,Back1996a,Back1996b,Smith1997a,Deb1999,Haupt2004,Costa2005a,Costa2007a}.

The mutation operator is a direct modification of genes. In a binary coding, it is implemented as an inversion of some bits in a chromosome, while in real coding, it is done by changing the gene values. Mutations add diversity to the population and prevent a freeze of the evolution, or a genetic drift to a local optimum. Thus, it makes the convergence to the global optimum theoretically possible \citep{Beasley1993a}, as they allow exploring beyond the current region of the parameter space. They therefore help preventing the algorithm to converge too quickly to a local optimum and bring new characteristics that were not present in the original population \citep{Haupt2004}.

The evaluated and developed mutation operators are the following:

\begin{itemize}
	\item \textbf{Uniform mutation}: The mutation rate is constant and equal for every gene of each individual; they all have the same probability to mutate. When a gene is selected for mutation, a new random value is assigned, according to a uniform law.

	\item \textbf{Variable uniform mutation} \citep{Fogarty1989}: a variable mutation rate over the generations was first suggested by \citet{Holland1992b} and evaluated by \citet{Fogarty1989}. It improved significantly the performance of GAs. In most applications, the mutation rate decreases with the generations, in a deterministic and global (for all individuals) manner \citep{Back1992b}. Its optimum configuration depends on the size of the chromosomes, of the properties of the objective function, and of the population size \citep{Back1992b}. We implemented this operator according to equation \ref{equation_mutation_uniformvariable}.
	\begin{equation}
	p_{n,G} = p_{G_{0}}+\left( \dfrac{p_{G_{0}}-p_{G_{m,p}}}{G_{m,p}} \right) min\left\lbrace G,G_{m,p}\right\rbrace 
	\label{equation_mutation_uniformvariable}
	\end{equation}
	where $p_{n,G}$ is the mutation rate (probability) of the gene $n$ for generation number $G$, $G_{m,p}$ is the maximum number of generations during which the mutation rate varies. $p_{G_{0}}$ is the initial mutation probability, and $p_{G_{m,p}}$ is the final one. $p_{G_{0}}$, $p_{G_{m,p}}$ and $G_{m,p}$ are the three controlling parameters of the operator. The evolution of the mutation rate is linear.

	\item \textbf{Constant normal mutation}: many use normal distributions to generate new values. The gene $g$ that mutate becomes:
	\begin{equation}
	g' = N(g,\sigma^{2})
	\label{equation_mutating_normal_distribution}
	\end{equation}
	where $\sigma$ is the standard deviation of the distribution. The disadvantage of this technique is that an accurate value of $\sigma$ must be chosen \citep{Haupt2004}, which is impossible to know beforehand.

	\item \textbf{Variable normal mutation}: with the same logic that the variable uniform mutation, we tested a mutation operator using a normal distribution with a variable mutation rate and standard deviation. The mutation rate is calculated with equation \ref{equation_mutation_uniformvariable}. On the same principle, we decrease linearly the standard deviation over the generations:
	\begin{equation}
	\sigma_{n,G} = \sigma_{G_{0}}+\left( \dfrac{\sigma_{G_{0}}-\sigma_{G_{m,\sigma}}}{G_{m,\sigma}} \right) min\left\lbrace G,G_{m,\sigma}\right\rbrace 
	\label{equation_mutation_normalvariable}
	\end{equation}
	where $\sigma_{n,G}$ is the standard deviation of gene $n$ et generation number $G$, $\sigma_{G_{0}}$ is the initial standard deviation, $\sigma_{G_{m,\sigma}}$ is the final standard deviation, $G_{m,\sigma}$ is the maximum number of generations during which the standard deviation varies. $p_{G_{0}}$, $p_{G_{m,p}}$, $G_{m,p}$, $\sigma_{G_{0}}$, $\sigma_{G_{m,\sigma}}$ and $G_{m,\sigma}$ are the six parameters of the method.

	\item \textbf{Non-uniform mutation} \citep{Michalewicz1996}: two random numbers are picked based on a uniform law: $r_{1}$, which determines the direction of the change, and $r_{2}$, which determines its magnitude. The new value of the gene is given by the following equation:
	\begin{equation}
	g_{n}^{'} = 
	\left\lbrace \begin{array}{l l} 
	g_{n} + \left(b_{n}-g_{n}\right) r_{2} \left(1 - \dfrac{G}{G_{m}} \right)^{2} & if \; r_{1} < 0.5 \\
	g_{n} - \left(g_{n}-a_{n}\right) r_{2} \left(1 - \dfrac{G}{G_{m}} \right)^{2} & if \; r_{1} \geq 0.5 \\
	\end{array} \right.
	\label{equation_mutation_nonuniform_original}
	\end{equation}
	where $a_{n}$ is the is the lower bound of the $n$-th gene, $b_{n}$ its upper bound, $G$ the present generation, and $G_{m}$ the maximum number of generations.

	We adapted this operator for our application, which is not based on a predefined number of generations:
	\begin{equation}
	g_{n}^{'} = 
	\left\lbrace \begin{array}{l l} 
	g_{n} + \left(b_{n}-g_{n}\right) r_{2} \varphi^{2} & if \; r_{1} < 0.5 \\
	g_{n} - \left(g_{n}-a_{n}\right) r_{2} \varphi^{2} & if \; r_{1} \geq 0.5 \\
	\end{array} \right.
	\label{equation_mutation_nonuniform}
	\end{equation}

	with

	\begin{equation}
	\varphi = 1 - \min \left\lbrace \dfrac{G}{G_{m,r}}, 1 \right\rbrace \left(1-\omega\right)
	\end{equation}

	where $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a threshold chosen by the user to maintain a minimum search radius when $G>G_{m,r}$. During the first generations, the exploration extent covers the entire parameter space. However, this area is reduced over generations, allowing exploitation of local solutions.

	\item \textbf{Individual adaptive mutation rate} \citep{Back1992a}: based on the ideas of Evolution Strategies \citep[see][]{Rechenberg1973, Schwefel1981}, \citet{Back1992a} introduced a concept of self-adaptive genetic algorithms. The idea is to distribute control parameters within individuals themselves, which partially decentralize control of the evolution. It allows reducing the parametrization of GAs and introducing a notion of self-management. The first approach is the introduction of a mutation rate per individual, that mutates itself under its own probability \citep{Back1992a}. Then, the eventual new rate is used to mutate the genes of the individual. Thus, as this rate decreases, it will have less probability of being itself mutated. This approach is close to the natural adaptation phenomena. A population less suited to its environment is changing faster than better adapted populations. Mutations are performed according to a constant uniform distribution. The initial mutation rates are randomly chosen \citep{Back1992a} and the method has no parameter. Other approaches exist to introduce a self-adaptation \citep[see][]{Smith1997a,Deb1999,Deb2001a}.

	\item \textbf{Individual adaptive search radius} (new): based on the ideas of the non-uniform mutation, we introduce a search radius in the approach of individual adaptive mutation rates. This search radius $r_{a}$, bounded between 0 and 1, is also adaptive and behaves similarly to the adaptive mutation rates. In order to separate its evolution from the one of the mutation rate, its own value is considered initially as a self-mutation rate to eventually mutate before being used as a normalized search radius. The value of a mutated gene is given by the following equation, which is a simplification of the non-uniform mutation:
	\begin{equation}
	g_{n}^{'} = 
	\left\lbrace \begin{array}{l l} 
	g_{n} + \left(b_{n}-g_{n}\right) r_{2} r_{a} & if \; r_{1} < 0.5 \\
	g_{n} - \left(g_{n}-a_{n}\right) r_{2} r_{a} & if \; r_{1} \geq 0.5 \\
	\end{array} \right.
	\label{equation_mutation_rayon_adaptatif}
	\end{equation}
	where $r_{1}$ and $r_{2}$ are randomly selected, in the same way as for the non-uniform mutation. No external parameter is therefore necessary.

	\item \textbf{Chromosome of adaptive mutation rate} \citep[\textit{n adaptative mutation rate},][]{Back1992a}: analogously to the individual adaptive mutation rate, this approach leaves the control of the evolution rate to the individuals themselves. The difference here is that each gene has a specific mutation rate. The main advantage is that the tuning of the mutation can be much more precise \citep{Smith1997a}. We therefore consider a second chromosome containing the mutation rate for each gene of the first chromosome. The operations of mutation and self-mutation are similar to the case of the individual adaptive mutation rate, but in a distributed way, within the chromosome. Another difference is that we apply the same crossover operations as those applied to the first chromosome, and this for the same crossing points. Thus, during an exchange of genes, children also inherit the mutation rates specific for each of these genes.

	\item \textbf{Chromosome of adaptive search radius} (new): we introduced this operator that combines the operations of the chromosome of adaptive mutation rate to our adaptive search radius approach. Similarly, an individual has 3 chromosomes: the first containing the values to be optimized, the second containing the distributed mutation rate, and the last one, the distributed search radius. Again, no external parameters are required.

	\item \textbf{Multi-scale mutation} (new): finally, we developed another approach, that is also based on the search radius concept. However, the latter is not decreasing with time. Methods based on a reduction of the mutation rate or radius simulate a transition from the exploration phase to the exploitation one. The idea is consistent as long as we are confident that the algorithm will converge towards the global optimum. Indeed, once the algorithm is in the exploitation mode, it is very unlikely to go out of the region it converges to. We wanted to test an approach that combines both exploration and exploitation during the whole optimization. Thus, we considered the search radius $r_{a}$ of equation \ref{equation_mutation_rayon_adaptatif} as a random value for each individual, but restricted to 4 equiprobable values: 1, 0.5, 0.1, 0.02, which range from full exploration to fine exploitation. The only external parameter is the mutation rate which is fixed.

\end{itemize}

When the gene to mutate is represented by a list of distinct values (eg meteorological variable or analogy criterion), the random choice of a new value is always based on a uniform distribution, without notion of search radius. There is indeed no meaning to use operators based on principles of proximity when the latter does not exist.

\subsubsection{Elitism}

We used a process of elitism on the natural selection as well as on mutations. This ensures the survival of the best individual so that we do not lose a better solution. This approach is very common in the field of GAs \citep{Haupt2004}. After the natural selection operator, if the best individual has not been selected, it is copied to the mating pool instead of an individual randomly picked. After mutation, if the best individual has mutated and if its new version has a lower performance score than the original, the latter is also reinserted in the mating pool instead of an individual randomly chosen.

\subsubsection{Ending the optimization}

The convergence check determines whether the solution is acceptable and if the algorithm may stop. The stopping criteria are not often well documented in GAs case studies. We chose to stop the optimization if the best individual does not change for $x$ generations. This value should not be too low to allow the algorithm to escape from a local optima. In addition, the rate of improvement decreases with the progression of the optimization. It is thus common that the best individual does not evolve over several generations when we get closer to the global solution. We chose a value of $x=20$ generations.

\subsection{Implementation and constraints}

Some constraints need to be taken into account. For example, when a crossover or a mutation operation results in a parameter value standing out of the authorized bounds, it has to be brought back within the limits. Moreover, the parameters are of different nature: some are continuous, such as the weight, some are discretized, such as the analogues number, or the spatial windows, and finally, some are independent elements in an array, such as the selection of the meteorological variable. New values resulting from the optimizer need to respect the type of data it represents.

Other constraints exist in between the parameters, such as the temporal window of the moisture index that has to be consistent in between the relative humidity and the precipitable water. Another example is the weighting of the different pressure levels which has to be normalized.

GAs are very computationally intensive because they require many evaluations of the objective function. These assessments are very long in our application, as they require calculating and assessing a forecast for every day of the calibration period. In order to reduce the computation time, we avoid recalculating the performance score of an individual who has previously been evaluated and that has not changed. We keep the score of each individual living in the selection until it mutates.

The assessment (calculation of the objective function) of each member of the population of a generation is completely independent and can be performed in parallel on different processors of a computer \citep{Alliot2005}. We implemented this technique and the resulting time savings was very important. In order to perform optimizations for multiple time series, the use of a cluster is a necessity, which our code allows.

\subsection{Recommendations of parametrization}

The GAs parametrization, such as the mutation rate, population size, natural selection options, and so on, is difficult given the high number of existing variants, each developed for a specific problem \citep{Haupt2004, Costa2007a}. This parametrization depends on the objective function, implementation variants, the range of the parameters to be optimized, and performance indicators. Thus, different studies suggest very different parametrization.

A key element of the parametrization of GAs is finding the right balance between exploration and exploitation \citep{Back1992a, Smith1997a}. Exploration is characterized by a relatively high probability to assess the regions of the parameter space that have not yet been visited. This probability must be sufficiently large at the beginning of the optimization, so that the algorithm is capable of identifying the region where the global optimum is located. Exploitation is characterized by a local search in an area of interest, and generally makes small movements. The latter is interesting to refine the results at the end of the optimization.

\citet{DeJong1975a} and \citet{Grefenstette1986} compared different implementations and parametrizations of GAs on functions of varying complexity. They observed that a small population size improves the initial performance, while a large population improves long-term performance. They also observed that the ratio of the population to keep for the mating pool is around 50\% (45\% to 60\%).

Values of the mutation rate varies broadly between the studies: from 0.001 \citep{DeJong1975a} to 0.2 \citep{Haupt2004}. \citet{Back1996b} showed that mutation rates higher than the usual ranges are more optimal at the beginning of the optimization, allowing further exploration. The combination of a small population and a high mutation rate works best for the first generations \citep{DeJong1975a, Back1996b, Haupt2004}, but as we could observe, it does not guarantee the quality of the final result. Incremental approaches with varying mutation rates are certainly more optimal but more complex to implement \citep{Back1996a, Back1996b}.

\subsubsection{Comparison process and results}

One of our goals being to make recommendations of parametrization in order to optimize the AM, we proceeded systematically. The results are summarized hereafter \citep[see][for the details]{Horton2012a}. We used concepts from the factorial design approach \citep[see eg.][]{Costa2005a,Costa2007a,Mariano2010a}, which is sometimes used for comparative analysis of different parametrizations of GAs. We processed by stages, analysing in details and in a systematic way every variants of the implemented operators, in combination with multiple other options and parameters in order to take into account eventual co-dependencies.

In order to evaluate a combination of operators/options, we processed 10 optimizations for one parametrization of GAs. The performances were characterized by four indicators:

\begin{itemize}
	\item mean performance score: average of the final scores of the 10 optimizations,
	\item convergence: the number of optimizations that converged to a supposed global optimum,
	\item number of generations: characterization of the convergence speed,
	\item number of evaluations of the objective function: characterization of the required calculation time (more realistic than the number of generations).
\end{itemize}

This comparison required tens of thousands of optimizations that were performed on a cluster of the University of Lausanne. The results, detailed in \citet{Horton2012a} are synthesized hereafter:

\begin{itemize}
	\item \textbf{Population size $N$}: we found the following ranges to be accurate in average for the population size (number of parameter sets of the AM):

	$50<N<100$ for a very simple implementation of the AM (1 level of analogy with 2 pressure levels),

	$N\approx200$ for a bit more complex AM (1 level of analogy with 4 pressure levels, or 2 level of analogy with less pressure levels),

	$N\approx500$ for significantly more complex AMs (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the moisture analogy),

	We didn't find any improvement with $N>500$, the results were even surprisingly of a lower quality. However, this cannot be generalized and depends on the AM to optimize, and supposedly on the characteristics of the processes generating the precipitations in a given region.

	\item \textbf{Natural selection}: this operator has no significant influence, and both tested implementations work fine, with a slightly better performance for the ratio-elitism.

	\item \textbf{Selection of couples}: 6 variants of the couples selection were assessed. The performance of these variants are relatively close, both in terms of performance score, convergence, and number of evaluations. The random pairing performed the most poorly, when the tournament selection with 3 candidates was slightly superior. The roulette wheel weighting is not far behind, but it is less effective in terms of convergence and number of evaluations. This operator has not a significant role in our application.

	\item \textbf{Chromosomes crossover}: we compared 21 different options of the crossover operators. This analysis revealed some slightly better options, some bad ones, and many averages. Among the bad operators, we find first the heuristic crossover, which is also more demanding in number of evaluations, as well as the linear crossover. Binary-like crossovers (especially with 2 points of intersection, whether $\beta$ is shared or not) are significantly better than the others, especially in terms of convergence. The two points crossover is relatively close. Other operators can be considered usable, yet may not be optimal. Once again, this operator is not the key of the GAs parametrization.

	\item \textbf{Mutation}: we compared the 10 mutation operators with different options, bringing the number of variations of this operator up to 110. We immediately observed that the mutation operator has a very important role on the performance of the optimizations of the AM, and that the other reproduction operators seem of secondary importance. This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction. He even suggests, in opposition with the theory of \citet{Holland1992a}, that chromosomes crossovers have mostly a corrective role of mutation operations. Various studies have also identified the importance of the mutation operator relatively to reproduction \citep[see eg.][]{Back1992a, Back1996b, Smith1997a, Deb1999, Haupt2004, Costa2005a, Costa2007a}.

	The mutation operators based on a variable normal or uniform law work very poorly and are difficult to configure. We then observe many operators more or less with the same performance scores and requiring a variable amount of assessments. The convergence analysis allows us to highlight three best operators:

	\textit{Non-uniform mutation} \citep{Michalewicz1996}: this operator is good in terms of convergence, mainly when the number of parameters to optimize is rather low. The number of required evaluations, however, can be quite substantial. The main disadvantage of the non-uniform mutation is the complexity of its parametrization, which is difficult to estimate a priori. These parameters must be carefully chosen to be in line with the evolution rate of the population, and are therefore dependent on the problem being treated. We could observe that the $\omega$ coefficient does not influence performance. The role of $G_{m}$ is rather difficult to judge, but does not seem essential. The mutation rate was found to be important. The difficulty is that the optimal value seems to be very case-related. Indeed, by even changing the precipitation time series (ie optimizing for another subregion), but not the complexity of the AM, the optimal mutation rate changes, making it impossible to estimate in advance.

	\textit{Chromosome of adaptive search radius}: unlike the previous one, our new operator is very robust, as it requires no option and is auto-adapting. It may be sometimes a little bit slower for simple problems, but does not require parametrization, which is an important advantage. It is interesting to notice that our insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).

	\textit{Multi-scale mutation}: finally, our multi-scale mutation, which also performs pretty well, can as well be seen as fairly robust, since it requires only one parameter, the mutation rate. However, it can also be difficult to estimate a correct value a priori.

	It may be wise to perform multiple optimizations and to consider these three operators in parallel in order to obtain results from algorithms that are either sometimes more efficient or more robust. It is interesting to note that the three best techniques incorporate a notion of search distance. It is likely that this notion is the key to these algorithms, for our application, and allows them to initially explore the parameter domain, and then to converge. The search radius in fact directly represents the notion of transition between exploration and exploitation, in our opinion more than a possible evolution of mutation rates.

	\item \textbf{Other options}: A ratio of 50\% for the mating pool seems to be a good choice.

\end{itemize}

\subsubsection{Recommended parametrization of GAs}

We evaluated the optimization by genetic algorithms on AMs of varying complexity, with a large number of combinations of operators to be able to make recommendations for optimizing the AM. Our conclusions are:

\begin{itemize}
	\item The optimization does not systematically converge to the global optimum  (but still often nearby), which is why we recommend doing several optimizations in parallel in order to compare the results, analyse the convergence, and keep the best.

	\item The population size should be in accordance with the complexity of the AM to optimize: from 50 for the simple ones, up to 500 for the most complex AMs.

	\item The value of the ratio for the intermediate population is not so important, and value of 50\% seems quite appropriate.

	\item Ratio-elitism is slightly better than tournaments for the natural selection operator, but it is not decisive.

	\item The performance of the operators for the couples selection perform relatively similarly. The roulette wheel weighting and the tournament selection are more efficient in terms of convergence and required number of evaluations.

	\item Most crossover operators have relatively similar performance. Binary-like crossover with two points of intersection are better than others, especially for convergence.

	\item Mutation has a clearly dominant influence. Three mutation operators stand out, two of which we have developed: the non-uniform mutation, the multi-scale mutation, and the chromosome of adaptive search radius. The latter is the most robust as it has no controlling parameter.

\end{itemize}

In order to make an optimization of the AM with genetic algorithms, it may be wise to consider these three mutation operators in parallel. We would then combine algorithms that are sometimes faster to other that are more robust. In order to be confident in the optimized AMs, we propose using a set of the following mutation operators:

\begin{itemize}
	\setlength\itemsep{-4px}
	\item 1x non-uniform, $p_{mut}=0.1$, $G_{m}=50$, $\omega=0.1$
	\item 1x non-uniform, $p_{mut}=0.1$, $G_{m}=100$, $\omega=0.1$
	\item 1x non-uniform, $p_{mut}=0.2$, $G_{m}=100$, $\omega=0.1$
	\item 1x multi-scale,  $p_{mut}=0.1$
	\item 2x chromosome of adaptive search radius
\end{itemize}

\section{Conclusions}

In order to automatically optimize the analogue method, we evaluated genetic algorithms, a global optimization technique, that is able to solve complex problems. Given the large number of existing operators and options, we had to evaluate systematically multiple variants to identify which operators are important, and which variant works best for the analogue method. We could thus identify that the mutation operator is a key element for our application, and provided new variants that were found to be efficient, such as the Chromosome of adaptive search radius that seems to be very reliable (no control parameter) and efficient . Recommendations were established for a relevant use of GAs for the optimization of the analogue method. However, there may still be possible improvements, through new operators, in order to improve the optimization performance and speed. Usage of this global optimization greatly eases the adaptation of the AM to new regions (with different leading meteorological processes) or to new predictands, as the optimization is performed automatically and globally.

The global optimization tools allow easily adapting the AM to new regions by taking into account local meteorological influences, and has thus a great potential of use. Moreover, it allows exploring automatically datasets in order to extract the most relevant variables. It is thus possible to try assessing other predictands, such as the temperature, the limit of snowfall, the occurrence of hail, or wind, while leaving the algorithms select the best variables and the associated parameters.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\acknowledgments
Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of. Thanks to Renaud Marty for his fruitful collaboration over the years.

Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE project which started this research. NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/. Precipitation time series provided by MeteoSwiss.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% APPENDIXES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Use \appendix if there is only one appendix.
%\appendix

% Use \appendix[A], \appendix}[B], if you have multiple appendixes.
%\appendix[A]

%% Appendix title is necessary! For appendix title:
%\appendixtitle{}

%%% Appendix section numbering (note, skip \section and begin with \subsection)
% \subsection{First primary heading}

% \subsubsection{First secondary heading}

% \paragraph{First tertiary heading}

%% Important!
%\appendcaption{<appendix letter and number>}{<caption>} 
%must be used for figures and tables in appendixes, e.g.,
%
%\begin{figure}
%\noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
%\appendcaption{A1}{Caption here.}
%\end{figure}
%
% All appendix figures/tables should be placed in order AFTER the main figures/tables, i.e., tables, appendix tables, figures, appendix figures.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Make your BibTeX bibliography by using these commands:
% \bibliographystyle{ametsoc2014}
% \bibliography{references}

\bibliographystyle{ametsoc2014_no_url}
% \bibliography{references}
\bibliography{../_refs/_articles-gas}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TABLES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Enter tables at the end of the document, before figures.
%%
%
%\begin{table}[t]
%\caption{This is a sample table caption and table layout.  Enter as many tables as
%  necessary at the end of your manuscript. Table from Lorenz (1963).}\label{t1}
%\begin{center}
%\begin{tabular}{ccccrrcrc}
%\hline\hline
%$N$ & $X$ & $Y$ & $Z$\\
%\hline
% 0000 & 0000 & 0010 & 0000 \\
% 0005 & 0004 & 0012 & 0000 \\
% 0010 & 0009 & 0020 & 0000 \\
% 0015 & 0016 & 0036 & 0002 \\
% 0020 & 0030 & 0066 & 0007 \\
% 0025 & 0054 & 0115 & 0024 \\
%\hline
%\end{tabular}
%\end{center}
%\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIGURES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Enter figures at the end of the document, after tables.
%%
%
%\begin{figure}[t]
%  \noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
%  \caption{Enter the caption for your figure here.  Repeat as
%  necessary for each of your figures. Figure from \protect\cite{Knutti2008}.}\label{f1}
%\end{figure}

\end{document}

### 2015-11-03 AtmoSwing - Geoscientific Model Development/template.tex
Moving GAs out of the AtmoSwing article.

@@
 It relies on the fact that similar meteorological influences are likely to result in similar local effects.
-This statistical relationship is thus based on archive of observed data, and used in order to operationally forecast the coming days, or to evaluate future conditions under a changing climate.
+This statistical relationship is thus based on archives of observed data, and used in order to operationally forecast the coming days, or to evaluate future conditions under a changing climate.
 
@@
 	\setlength\itemsep{-1mm}
-	\item Brier Score \citep{Brier1950, Toth2003}
+	\item Brier Score \citep{Brier1950}
 	\item ROC diagramm \citep[Relative Operating Characteristic or Receiver Operating Characteristic,][]{Mason1982}
@@
 
-Due to the limitation of the sequential approach, we implemented a global optimization technique based on Genetic algorithms.
+Due to limitations of the sequential approach, we decided to explore optimization techniques that can handle all parameters fully automatically.
+We first assessed the \citet{Nelder1965a} method, which was found to be unsuitable for this purpose.
+Because of the complexity of the AM and its non-linearity, a technique of global optimization is required.
+We thus implemented Genetic algorithms in AtmoSwing Optimizer in order to perform a global optimization of the AM.
 This allows for a fully automatic and objective optimization of the AM.
-However, as this topic is rather consequent, it will be the subject of another publication.
+However, as this topic is rather consequent and the code base is not yet released, it will be the subject of another publication.
 

### 2015-11-03 Genetic algorithms - Journal of Climate/template.tex
Moving GAs out of the AtmoSwing article.

@@
 
-\abstract{
-
-	The global optimization can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
+\abstract{The global optimization can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
 Indeed, it allows taking into account parameters inter-dependencies, adding new degrees of freedom, and choosing objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
-
 	These kind of optimization techniques need however to be tailored to the problem to solve.
@@
 These recommendations are a consequent outcome of this work, as it opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.
-
 	}
@@
 
-We thus decided to explore optimization techniques that can handle all parameters fully automatically.
-We first assessed the \citet{Nelder1965a} method, which was found to be unsuitable for this purpose.
-Due to the complexity of the AM and its non-linearity, a technique of global optimization is required.
-We thus implemented Genetic algorithms in AtmoSwing Optimizer in order to perform a global optimization of the AM.
  This article is not about discussing the results of such a technique, but describing the details of the implementation.
 The demonstration of the benefit brought by such an approach is the topic of another article.
-The details of the implementation being numerous, the description is provided in the next dedicated section (\ref{sec:gas}).
 

### 2015-11-03 AtmoSwing - Geoscientific Model Development/template.tex
Adding some content to the abstract.

@@
 
-AtmoSwing is an open source software that implement the analogue method in a very flexible way, so that different variants can be handled dynamically, by parameterization.
+AtmoSwing is an open source software that implement the analogue method in a very flexible way, so that different variants can be handled dynamically, by parameterization trough XML files.
 It is made of 3 tools: the Forecaster to perform operational forecasts, the Viewer to display the results, and the Optimizer to establish the statistical relationship between the predictand and predictors.
 
-The Optimizer integrates the most used technique, that is a semi-automatic sequential approach, as well as Monte-Carlo analyses, and especially a global optimization technique by means of Genetic algorithms.
-
-%TODO: rewrite
+The Forecaster handles every required step internally, such as predictors downloading and parsing, grid interpolation, analogy sorting, without external scripts or file conversion.
+The processing of a forecast is extremely lightweight in terms of IT infrastructure; it can indeed run on almost any computer.
+
+The Viewer displays the forecasts in an interactive GIS environment.
+It contains several layers of syntheses and details in order to provide a quick overview of the potential critical situations in the coming days, as well as the possibility for the user to go into the details of the forecasted predictand and criteria distributions.
+Several tips coming from the literature are provided in order to help interpreting the forecasts.
+
+The Optimizer integrates the most used technique, that is a semi-automatic sequential approach, as well as Monte-Carlo analyses, and a global optimization technique by means of Genetic algorithms.
+It allows establishing the statistical relationship between predictors and predictands.
 
@@
 
-%TODO: rework
-
 %\appendix

### 2015-11-04 Genetic algorithms - Journal of Climate/template.tex
Moving some content around

@@
 \documentclass[twocol]{ametsoc}
-
-\usepackage{multirow}
-\usepackage{gensymb}
-\usepackage{subcaption}
-\usepackage{xcolor,colortbl}
-
-% After http://tex.stackexchange.com/questions/94799/how-do-i-color-table-columns-and-rows
-\newcommand{\mc}[2]{\multicolumn{#1}{c}{#2}}
-\definecolor{Gray}{gray}{0.85}
-\definecolor{LightCyan}{rgb}{0.88,1,1}
-\newcolumntype{a}{>{\columncolor{Gray}}c}
 
@@
 
-\abstract{The global optimization can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
+\abstract{The analogues method is based on a statistical relationship between synoptic atmospheric variables and local weather, which we aim at forecasting.
+This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic procedure.
+This sequential calibration is relatively fast and provide acceptable results, but it has strong constraints, is made of successive steps and thus cannot handle parameters dependencies, and mainly, it cannot calibrate automatically some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared.
+In order to surpass these limitations, we assessed a global optimization technique, namely genetic algorithms, that can optimize jointly all parameters of the method and thus provide a global optimum by taking into account the parameters dependencies.
+Moreover, it can calibrate parameters that were previously manually assessed, and can take into account new degrees of freedom that were unthinkable before.
+	The global optimization can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
 Indeed, it allows taking into account parameters inter-dependencies, adding new degrees of freedom, and choosing objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
@@
 \section{Motivation for a global optimization}
+
+The classic calibration is fast to optimize one spatial window for a given pressure level and temporal window.
+However, it doesn't provide an objective selection of the pressure level and temporal window.
+The only option is to try systematically every combination, which may be acceptable for no more than 2 levels.
+However, \citet{Horton2012a} showed that additional pressure levels may improve the method.
+
+We observed during the calibration of the analogue method that the resulting parameters vary with the initial choices (such as the number of analogues).
+In addition, the different levels of analogy (eg on the atmospheric circulation and the moisture index) are always calibrated sequentially.
+However, we can not exclude any dependency between them, which could lead us to select another parametrization if we calibrate them together.
+Simultaneous calibration of all parameters has never been undertaken so far.
+Only a global optimization technique can be able to optimize all parameters of all analogy levels simultaneously.
+
+When creating the classic calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters and wrote: '' \textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent.
+We will present our results by first searching the best variable [note: e.g.
+selection of the pressure level and the temporal window for the geopotential height] on a chosen spatial window, and next, the best window for the chosen variable.
+However, even by repeating the process, are we sure to obtain the optimal combination?} ''.
+And later in his work: '' \textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution} ''.
+\citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of the analogue method and concludes that one needs to be an expert to know their respective influence, their sensitivity and their nonlinear interactions.
+\citet{BenDaoud2010}, when calibrating the analogue method, also stated that '' \textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously } ''.
+
+The analogue method needs to be adapted to every new region it is applied, because the leading meteorological influences are specific to this region.
+Even the selection of the pressure level and the temporal window should be reconsidered, when not the variable itself.
+For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012a} found no interest in this variable in an Alpine environment, because in the Alps, the vertical motion is mainly controlled by orographic effects, and was thus already well related to the atmospheric circulation itself.
+So, when adapting the analogue method to a new region, we should assess systematically every combination of pressure levels, time and spatial windows, which is an intensive task.
+This procedure can be automatized by a global optimization technique.
+
+Our ambition was then to assess the feasibility of an automatic optimization of the analogue method through various techniques.
+The objective was to find an approach to optimize all parameters simultaneously, and thus be able to identify the global optimum in the parameter space.
+In addition, it can overcome the systematic manual assessments of certain parameters such as the selection of the pressure levels and time windows.
+Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the pressure levels, and the consideration of non-overlapping spatial windows between the pressure levels.
+
+\citet{Horton2012a} assessed the ability of the \citet{Nelder1965a} method based on a simplex approach.
+This technique didn't provide satisfying results and failed at identifying the global optimum.
+Indeed, the results didn't converge and many local optimums came out.
+The parameter space of the analogue method is very complex and not appropriate for a linear optimization technique.
+Genetic algorithms were found to be much more relevant for such application.
 

### 2015-11-04 Optimization - Journal of Climate/template.tex
Corrections from Michel.
Moving some content around

@@
 
-\abstract{The analogues method is based on a statistical relationship between synoptic atmospheric variables and local weather, which we aim at forecasting.
-This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic procedure.
-This sequential calibration is relatively fast and provide acceptable results, but it has strong constraints, is made of successive steps and thus cannot handle parameters dependencies, and mainly, it cannot calibrate automatically some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared.
-In order to surpass these limitations, we assessed a global optimization technique, namely genetic algorithms, that can optimize jointly all parameters of the method and thus provide a global optimum by taking into account the parameters dependencies.
-Moreover, it can calibrate parameters that were previously manually assessed, and can take into account new degrees of freedom that were unthinkable before.
-
+\abstract{
 We then applied the optimizer to the Rh\^{o}e catchment in the Swiss Alps and obtained coherent results which significantly improve the performance of the forecasting by analogy.
 The optimizer allowed us to calibrate jointly all parameters of the method and to add a weighting of the criteria per pressure level, as well as non-overlapping spatial windows.}
-
 \begin{document}
@@
 
-Predictors are generally reanalysis datasets (and outputs of a global numerical weather prediction models for the target situation in operational forecasting, which is not the topic of this paper).
+Predictors are generally reanalysis datasets.
 We will work here with the NCEP/NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996}, but it can be any other reanalysis dataset.
@@
 The time series from every available gauging station were averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.
-
-\section{Motivation for a global optimization}
-
-The classic calibration is fast to optimize one spatial window for a given pressure level and temporal window.
-However, it doesn't provide an objective selection of the pressure level and temporal window.
-The only option is to try systematically every combination, which may be acceptable for no more than 2 levels.
-However, \citet{Horton2012a} showed that additional pressure levels may improve the method.
-
-We observed during the calibration of the analogue method that the resulting parameters vary with the initial choices (such as the number of analogues).
-In addition, the different levels of analogy (eg on the atmospheric circulation and the moisture index) are always calibrated sequentially.
-However, we can not exclude any dependency between them, which could lead us to select another parametrization if we calibrate them together.
-Simultaneous calibration of all parameters has never been undertaken so far.
-Only a global optimization technique can be able to optimize all parameters of all analogy levels simultaneously.
-
-When creating the classic calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters and wrote: '' \textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent.
-We will present our results by first searching the best variable [note: e.g.
-selection of the pressure level and the temporal window for the geopotential height] on a chosen spatial window, and next, the best window for the chosen variable.
-However, even by repeating the process, are we sure to obtain the optimal combination?} ''.
-And later in his work: '' \textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution} ''.
-\citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of the analogue method and concludes that one needs to be an expert to know their respective influence, their sensitivity and their nonlinear interactions.
-\citet{BenDaoud2010}, when calibrating the analogue method, also stated that '' \textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously } ''.
-
-The analogue method needs to be adapted to every new region it is applied, because the leading meteorological influences are specific to this region.
-Even the selection of the pressure level and the temporal window should be reconsidered, when not the variable itself.
-For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012a} found no interest in this variable in an Alpine environment, because in the Alps, the vertical motion is mainly controlled by orographic effects, and was thus already well related to the atmospheric circulation itself.
-So, when adapting the analogue method to a new region, we should assess systematically every combination of pressure levels, time and spatial windows, which is an intensive task.
-This procedure can be automatized by a global optimization technique.
-
-Our ambition was then to assess the feasibility of an automatic optimization of the analogue method through various techniques.
-The objective was to find an approach to optimize all parameters simultaneously, and thus be able to identify the global optimum in the parameter space.
-In addition, it can overcome the systematic manual assessments of certain parameters such as the selection of the pressure levels and time windows.
-Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the pressure levels, and the consideration of non-overlapping spatial windows between the pressure levels.
-
-\citet{Horton2012a} assessed the ability of the \citet{Nelder1965a} method based on a simplex approach.
-This technique didn't provide satisfying results and failed at identifying the global optimum.
-Indeed, the results didn't converge and many local optimums came out.
-The parameter space of the analogue method is very complex and not appropriate for a linear optimization technique.
-Genetic algorithms were found to be much more relevant for such application.
 

### 2015-11-04 Genetic algorithms - Journal of Climate/template.tex
Removal of the custom references stylesheet.
Modifying structure.

@@
 
-\section{Optimization using Genetic algorithms}
+\section{Assessed Genetic Algorithms variants}
 \label{sec:gas}
 
-Genetic algorithms (GAs) come from the world of stochastic optimization, more specifically from metaheuristic approaches.
+Genetic Algorithms (GAs) come from the world of stochastic optimization, more specifically from metaheuristic approaches.
 These are stochastic iterative algorithms that behave like search algorithms by exploiting the characteristics of a problem and are particularly suitable for complex parameter spaces.
@@
 \begin{figure}[htb]
-	\includegraphics[width=8.3cm]{figures/figure_structure_gas.pdf}
+	\noindent\includegraphics[width=19pc,angle=0]{figures/figure_structure_gas.pdf}\\
 	\caption{Genetic algorithms operational flowchart}
@@
 
-\subsection{Recommendations of parametrization}
+\section{Recommendations of parametrization}
 
@@
 
-\subsubsection{Comparison process and results}
+\subsection{Comparison process and results}
 
@@
 
-\subsubsection{Recommended parametrization of GAs}
+\subsection{Recommended parametrization of GAs}
 
@@
 % Make your BibTeX bibliography by using these commands:
-% \bibliographystyle{ametsoc2014}
-% \bibliography{references}
-
-\bibliographystyle{ametsoc2014_no_url}
+\bibliographystyle{ametsoc2014}
 % \bibliography{references}

### 2015-11-04 AtmoSwing - Geoscientific Model Development/template.tex
Specification of MINERVE.

@@
 
-Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE project which started this research.
+Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
 NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.

### 2015-11-04 Optimization case study - Journal of Hydrology/template.tex
Removal of the custom references stylesheet.
Modifying structure.
Specification of MINERVE.

--- 2015-11-04 Optimization - Journal of Climate/template.tex
@@
 
-\title{Global Optimization of the Analogue Method by Means of Genetic Algorithms}
+\title{Using Genetic Algorithms to Optimize the Analogue Method for Precipitation forecasting in the Swiss Alps}
 

### 2015-11-13 Genetic algorithms - Journal of Climate/template.tex
Adding detailed results.

@@
 \subsubsection{Mutation}
+\label{sec:gas:mutation}
 
@@
 
-\section{Recommendations of parametrization}
+\section{Assessment process and results}
 
@@
 
-\subsection{Comparison process and results}
+\subsection{Comparison process}
 
@@
 We used concepts from the factorial design approach \citep[see eg.][]{Costa2005a,Costa2007a,Mariano2010a}, which is sometimes used for comparative analysis of different parametrizations of GAs.
+It allows isolating the effect of a parameter under different combinations of the other options.
 We processed by stages, analysing in details and in a systematic way every variants of the implemented operators, in combination with multiple other options and parameters in order to take into account eventual co-dependencies.
@@
 \end{itemize}
+
+Given the large number of operators and options of the method, it is not possible to systematically assess each combination.
+We thus proceeded in stages, but for each comprehensive comparison of an operator type, two very different variants of other operators are considered to take account of indirect effects.
+
+\begin{enumerate}
+	\item Assessment of all breeding operators, thus every combination of selection of couples and chromosome crossover variants, along with variants of the other options.
+	\item Assessment of the mutation operator
+	\item Evaluation of other options of the method
+\end{enumerate}
+
+\subsection{Success of the approach}
+
+After a short first overview of the results, GAs have quicky been proven successful at optimizing the AM.
+Indeed, the performance score of the sequential approach has been quickly exceeded without adding any new parameter to the method (Figure \ref{fig:gas_evolution_good}).
+Even GAs parametrization that we will consider further as inadequate (Figure \ref{fig:gas_evolution_bad}) did significantly better that the sequential approach.
+
+\begin{figure}[htb]
+	\begin{center}
+		\noindent\includegraphics[width=19pc,angle=0]{figures/gas_evolution_good.pdf}\\
+	\end{center}
+	\caption{Evolution of the score of the best individuals over generations for the 10 optimizations processed for a given parametrization.
+The green line represents the score of the sequential approach and the blue one, the supposed global optimum.}
+	\label{fig:gas_evolution_good}
+\end{figure}
+
+\begin{figure}[htb]
+	\begin{center}
+		\noindent\includegraphics[width=19pc,angle=0]{figures/gas_evolution_bad.pdf}\\
+	\end{center}
+	\caption{Same as Figure \ref{fig:gas_evolution_good}, but for a GAs parametrization considered as less relevant.}
+	\label{fig:gas_evolution_bad}
+\end{figure}
+
+\subsection{Results}
+
+The results illustrate the effect of an operator when its contribution is isolated from the other operators.
+It means that we compare the effect of the studied operator when all the other operators are equivalent, while assessing multiple combinations.
+We then summarizes this contribution relatively to the other options, as a percentage of gain/loss regarding the mean of all variants.
+For example, to evaluate the performance of the uniform crossover operator, we compare some indicators between its performance and the average of performance of all crossover operators while retaining the same population size, the same mutation operators, natural selection, and selection of couples.
+
+\subsubsection{Breeding operators}
+
+We evaluated every combination of 6 options for the couples selection (Table \ref{tab:assessed_couples_selection_operators}) and 21 for the chromosome crossover operators (Table \ref{tab:assessed_crossover_operators}), along with variants of the other operators.
+This results in 1,008 combinations, requiring 10,080 optimizations.
+
+\begin{table}[htbp]
+	\caption{Assessed operator for couples selection.}
+	\begin{center}
+		\begin{tabular}{ll}
+			\hline\hline  & \textbf{Couples selection operators} \\ 
+			\hline 
+			A & Rank pairing \\ 
+			B & Random pairing \\ 
+			C & Roulette wheel weighting on rank \\ 
+			D & Roulette wheel weighting on fitness \\ 
+			E & Tournament selection (3 candidates) \\ 
+			F & Tournament selection (4 candidates) \\ 
+			\hline 
+		\end{tabular}
+	\end{center}
+	\label{tab:assessed_couples_selection_operators}
+\end{table}
+
+\begin{table}[htbp]
+	\caption{Assessed operators for chromosome crossover.}
+	\begin{center}
+		\begin{tabular}{ll}
+			\hline\hline  & \textbf{Chromosome crossover operators} \\ 
+			\hline 
+			1 & Single-point crossover \\
+			2 & Two-point crossover \\
+			3 & Multiple-point crossover (3 points) \\
+			4 & Multiple-point crossover (5 points) \\
+			5 & Uniform crossover \\
+			6 & Blending method (2 points, unshared $\beta$) \\
+			7 & Blending method (4 points, unshared $\beta$) \\
+			8 & Blending method (2 points, shared $\beta$) \\
+			9 & Blending method (4 points, shared $\beta$) \\
+			10 & Linear crossover (2 points) \\
+			11 & Linear crossover (4 points) \\
+			12 & Heuristic crossover (2 points, unshared $\beta$) \\
+			13 & Heuristic crossover (4 points, unshared $\beta$) \\
+			14 & Heuristic crossover (2 points, shared $\beta$) \\
+			15 & Heuristic crossover (4 points, shared $\beta$) \\
+			16 & Binary-like crossover (2 points, unshared $\beta$) \\
+			17 & Binary-like crossover (4 points, unshared $\beta$) \\
+			18 & Binary-like crossover (2 points, shared $\beta$) \\
+			19 & Binary-like crossover (4 points, shared $\beta$) \\
+			20 & Linear interpolation \\
+			21 & Free interpolation \\
+			\hline
+		\end{tabular}
+	\end{center}
+	\label{tab:assessed_crossover_operators}
+\end{table}
+
+After this first assessment, the importance of the mutation operator was obvious \cite[see][for the details]{Horton2012a}, and its leading influence on the optimization performance was evident.
+However, the effect of the operators and options other than the ones related to breeding will be detailed later.
+
+\begin{figure}[htb]
+	\begin{center}
+		\noindent\includegraphics[width=7cm,angle=0]{figures/operator_selectcoupl_score.pdf}\\
+	\end{center}
+	\caption{Influence of the couples selection operators on the optimization performance.
+The box extends from the lower to upper quartile values of the data, with a line at the median.
+The whiskers extend from the box to 1.5 times the interquartile range.
+Flier points are those past the end of the whiskers.
+The star represents the median.}
+	\label{fig:operator_selectcoupl_score}
+\end{figure}
+
+\begin{figure*}[htb]
+	\begin{center}
+		\noindent\includegraphics[width=16cm,angle=0]{figures/operator_crossover_score.pdf}\\
+	\end{center}
+	\caption{Influence of the chromosome crossover operators on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+	\label{fig:operator_crossover_score}
+\end{figure*}
+
+The performance of the couples selection operator are relatively close (Figure \ref{fig:operator_selectcoupl_score}).
+Overall, we observe that the random pairing is the least good operator and the tournament selection with 3~candidates is slightly superior to others.
+Convergence analysis (not shown) presents similar trends to the scores.
+The influence on the number of assessments (not shown) reveals that the operators providing the worst scores are also those who need a higher number of evaluations.
+This analysis invites us to reject the rank and random pairing, and to consider the roulette wheel weighting or tournament selections, these being substantially better in terms of convergence and number of necessary evaluations.
+
+Analysis of crossover operators (Figure \ref{fig:operator_crossover_score}) reveal some slightly superior options, some inappropriate, and many averages.
+Among the inappropriate operators, we find first the heuristic crossover, which is also more demanding in terms of evaluation number, and the linear crossover.
+Binary-like crossover (especially with 2 points of intersection, whether $\beta$ is shared or not) are significantly better than the others, especially in terms of convergence (not shown).
+The two-point intersection is also relatively close.
+Other operators can also be considered usable.
+
+\subsubsection{Mutation operator}
+
+Having identified the leading role of the mutation operator, we strongly focused the sensitivity analysis on this operator.
+Each of the 10 different implementations (see section \ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Table \ref{tab:assessed_mutation_operators}), bringing the number of variations of this operator up to 109.
+We also did some optimizations without any mutation as a reference.
+Along with variants of the other operators \citep[see][for the details]{Horton2012a}, it resulted in 660 combinations (so 6,600 optimizations).
+
+\begin{table}[htbp]
+	\caption{Assessed mutation operators with the number of variants considered (combination of parameters).}
+	\begin{center}
+		\begin{tabular}{llc}
+			\hline\hline  & \textbf{Mutation operator} & \textbf{Variants}\\ 
+			\hline 
+			1 & Uniform mutation & 3 \\
+			2 & Variable uniform mutation & 27 \\
+			3 & Constant normal mutation & 9 \\
+			4 & Variable normal mutation & 36 \\
+			5 & Non-uniform mutation & 27 \\
+			6 & Individual adaptive mutation rate & 1 \\
+			7 & Individual adaptive search radius & 1 \\
+			8 & Chromosome of adaptive mutation rate & 1 \\
+			9 & Chromosome of adaptive search radius & 1 \\
+			10 & Mutli-scale mutation & 3 \\
+			11 & No mutation & 1 \\
+			\hline
+		\end{tabular}
+	\end{center}
+	\label{tab:assessed_mutation_operators}
+\end{table}
+
+\begin{figure}[htb]
+	\begin{center}
+		\noindent\includegraphics[width=7cm,angle=0]{figures/operator_mutation_score.pdf}\\
+	\end{center}
+	\caption{Influence of the mutation operators on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+	\label{fig:operator_mutation_score}
+\end{figure}
+
+Figure \ref{fig:operator_mutation_score} show the results of this analysis and illustrates the important role of the mutation on the performance of the optimizations.
+Optimizations without mutation (last box on the Figure) are inferior to most mutation operators, and the scale of the influence of the mutation operators is significantly more important than those for the other options.
+The details of the analysis \citep[see][]{Horton2012a} show that the other reproduction operators seem of secondary importance.
+This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction.
+He even suggests, in opposition with the theory of \citet{Holland1992a}, that chromosomes crossovers have mostly a corrective role of mutation operations.
+Various studies have also identified the importance of the mutation operator relatively to reproduction \citep[see eg.][]{Back1992a, Back1996b, Smith1997a, Deb1999, Haupt2004, Costa2005a, Costa2007a}.
+
+The mutation operators based on a variable normal or uniform law work very poorly and are difficult to configure.
+We then observe many operators more or less with the same performance scores and requiring a variable amount of assessments.
+The convergence analysis \citep[see][]{Horton2012a} allows us to highlight three best operators:
+
+\begin{itemize}
+
+	\item \textit{Non-uniform mutation} \citep{Michalewicz1996}: this operator is good in terms of convergence, mainly when the number of parameters to optimize is rather low.
+The number of required evaluations, however, can be quite substantial.
+The main disadvantage of the non-uniform mutation is the complexity of its parametrization, which is difficult to estimate a priori.
+These parameters must be carefully chosen to be in line with the evolution rate of the population, and are therefore dependent on the problem being treated.
+We could observe that the $\omega$ coefficient does not influence performance.
+The role of $G_{m}$ is rather difficult to judge, but does not seem essential.
+The mutation rate was found to be important.
+The difficulty is that the optimal value seems to be very case-related.
+Indeed, by even changing the precipitation time series (ie optimizing for another subregion), but not the complexity of the AM, the optimal mutation rate changes, making it impossible to estimate in advance.
+
+	\item \textit{Chromosome of adaptive search radius} (new): unlike the previous one, our new operator is very robust, as it requires no option and is auto-adapting.
+It may be sometimes a little bit slower for simple problems, but does not require parametrization, which is an important advantage.
+It is interesting to notice that our insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).
+
+	\item \textit{Multi-scale mutation} (new): finally, our multi-scale mutation, which also performs pretty well, requires one parameter, the mutation rate.
+However, it can also be difficult to estimate a correct value a priori.
+
+\end{itemize}
+
+\subsubsection{Other options}
+
+The analysis of the natural selection operator (Figure \ref{fig:operator_selectnat_score}) reveals a slight preference for the ratio-elitism compared to the tournament selection, but not so significant.
+Furthermore, the number of evaluations is similar.
+This operator, or at least the two assessed versions, do not appear to significantly influence the optimization performances.
+
+\begin{figure}[htb]
+	\begin{center}
+		\noindent\includegraphics[width=4cm,angle=0]{figures/operator_selectnat_score.pdf}\\
+	\end{center}
+	\caption{Influence of the natural selection operators on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+	\label{fig:operator_selectnat_score}
+\end{figure}
+
+The size of the population has an effect on the performance of the optimization (Figure \ref{fig:option_taillepop_score}).
+A bigger population leads to better results, but also to significantly longer optimizations.
+Indeed, the required number of evaluation, and thus the required time, is approximately proportional to the population size.
+The optimal size seems to depend on the complexity of the AM to optimize: a more complex AM (ie.
+with more degrees of freedom) requires a bigger population size.
+A rule of thumb based on different experiences is provided in the next section.
+
+\begin{figure}[htb]
+	\begin{center}
+		\noindent\includegraphics[width=4cm,angle=0]{figures/option_taillepop_score.pdf}\\
+	\end{center}
+	\caption{Influence of the population size on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+	\label{fig:option_taillepop_score}
+\end{figure}
+
+We also assessed the influence of the size of the intermediate population (ratio of the total population) selected for mating (Figure \ref{fig:option_popratio_score}).
+It appears that a big ratio is not optimal.
+However, it does not appear that this parameter is critical to the quality of the optimizations, provided it is not too big.
+A value of 50~\% seems a wise choice.
+
+\begin{figure}[htb]
+	\begin{center}
+		\noindent\includegraphics[width=4cm,angle=0]{figures/option_popratio_score.pdf}\\
+	\end{center}
+	\caption{Influence of the intermediate population ratio on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+	\label{fig:option_popratio_score}
+\end{figure}
+
+\subsection{Synthesis}
 
@@
 
-	\item \textbf{Mutation}: we compared the 10 mutation operators with different options, bringing the number of variations of this operator up to 110.
-We immediately observed that the mutation operator has a very important role on the performance of the optimizations of the AM, and that the other reproduction operators seem of secondary importance.
-This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction.
-He even suggests, in opposition with the theory of \citet{Holland1992a}, that chromosomes crossovers have mostly a corrective role of mutation operations.
-Various studies have also identified the importance of the mutation operator relatively to reproduction \citep[see eg.][]{Back1992a, Back1996b, Smith1997a, Deb1999, Haupt2004, Costa2005a, Costa2007a}.
-
-	The mutation operators based on a variable normal or uniform law work very poorly and are difficult to configure.
-We then observe many operators more or less with the same performance scores and requiring a variable amount of assessments.
-The convergence analysis allows us to highlight three best operators:
-
-	\textit{Non-uniform mutation} \citep{Michalewicz1996}: this operator is good in terms of convergence, mainly when the number of parameters to optimize is rather low.
-The number of required evaluations, however, can be quite substantial.
-The main disadvantage of the non-uniform mutation is the complexity of its parametrization, which is difficult to estimate a priori.
-These parameters must be carefully chosen to be in line with the evolution rate of the population, and are therefore dependent on the problem being treated.
-We could observe that the $\omega$ coefficient does not influence performance.
-The role of $G_{m}$ is rather difficult to judge, but does not seem essential.
-The mutation rate was found to be important.
-The difficulty is that the optimal value seems to be very case-related.
-Indeed, by even changing the precipitation time series (ie optimizing for another subregion), but not the complexity of the AM, the optimal mutation rate changes, making it impossible to estimate in advance.
-
-	\textit{Chromosome of adaptive search radius}: unlike the previous one, our new operator is very robust, as it requires no option and is auto-adapting.
-It may be sometimes a little bit slower for simple problems, but does not require parametrization, which is an important advantage.
-It is interesting to notice that our insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).
-
-	\textit{Multi-scale mutation}: finally, our multi-scale mutation, which also performs pretty well, can as well be seen as fairly robust, since it requires only one parameter, the mutation rate.
-However, it can also be difficult to estimate a correct value a priori.
+	\item \textbf{Mutation}: In our application, the mutation operator has a leading effect and should be chosen with care.
+We identified 3 more efficient variants: \textit{Non-uniform mutation} \citep{Michalewicz1996} that performs well but is difficult to parametrize, the \textit{Multi-scale mutation} (new) which needs only 1 parameter, and the \textit{Chromosome of adaptive search radius} (new), which is the most robust option as it has no parameter and always performed well.
 
@@
 
-\subsection{Recommended parametrization of GAs}
+\section{Recommended parametrization of GAs}
 
@@
 	\setlength\itemsep{-4px}
-	\item 1x non-uniform, $p_{mut}=0.1$, $G_{m}=50$, $\omega=0.1$
+	\item 1x non-uniform, $p_{mut}=0.05$, $G_{m}=100$, $\omega=0.1$
 	\item 1x non-uniform, $p_{mut}=0.1$, $G_{m}=100$, $\omega=0.1$

### 2015-11-17 Genetic algorithms - Journal of Climate/template.tex
Addition of the results of the mutation analyses.

@@
 
+\begin{table}[htbp]
+	\caption{Further assessments of mutation operators.}
+	\begin{center}
+		\begin{tabular}{llrrr}
+			\hline\hline  & \textbf{Mutation operator} & \textbf{$p_{mut}$} & \textbf{$G_{max}$} & \textbf{$\omega$}\\ 
+			\hline 1 & Non-uniform mutation & 0.01 & 50 & 0.1 \\
+			2 & Non-uniform mutation & 0.05 & 50 & 0.1 \\
+			3 & Non-uniform mutation & 0.1 & 50 & 0.1 \\
+			4 & Non-uniform mutation & 0.2 & 50 & 0.1 \\
+			5 & Non-uniform mutation & 0.4 & 50 & 0.1 \\
+			6 & Non-uniform mutation & 0.01 & 100 & 0.1 \\
+			7 & Non-uniform mutation & 0.05 & 100 & 0.1 \\
+			8 & Non-uniform mutation & 0.1 & 100 & 0.1 \\
+			9 & Non-uniform mutation & 0.2 & 100 & 0.1 \\
+			10 & Non-uniform mutation & 0.4 & 100 & 0.1 \\
+			11 & Mutli-scale mutation &  0.01 &&\\
+			12 & Mutli-scale mutation &  0.05 && \\
+			13 & Mutli-scale mutation &  0.1 && \\
+			14 & Mutli-scale mutation &  0.2 && \\
+			15 & Mutli-scale mutation &  0.4 && \\
+			16 & \multicolumn{4}{l}{Chromosome of adaptive search radius} \\
+			\hline
+		\end{tabular}
+	\end{center}
+	\label{tab:assessed_mutation_operators_bis}
+\end{table}
+
+\begin{figure*}[htb]
+	\begin{center}
+		\noindent\includegraphics[width=14cm,angle=0]{figures/operator_mutation_score_atmlevel.pdf}\\
+	\end{center}
+	\caption{Influence of the mutation operators on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+	\label{fig:operator_mutation_score_atmlevel}
+\end{figure*}
+
+\begin{figure*}[htb]
+	\begin{center}
+		\noindent\includegraphics[width=14cm,angle=0]{figures/operator_mutation_score_rhoneamont.pdf}\\
+	\end{center}
+	\caption{Influence of the mutation operators on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+	\label{fig:operator_mutation_score_rhoneamont}
+\end{figure*}
+
+\begin{figure*}[htb]
+	\begin{center}
+		\noindent\includegraphics[width=14cm,angle=0]{figures/operator_mutation_score_r2.pdf}\\
+	\end{center}
+	\caption{Influence of the mutation operators on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+	\label{fig:operator_mutation_score_r2}
+\end{figure*}
+
+\begin{figure*}[htb]
+	\begin{center}
+		\noindent\includegraphics[width=14cm,angle=0]{figures/operator_mutation_score_r4.pdf}\\
+	\end{center}
+	\caption{Influence of the mutation operators on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+	\label{fig:operator_mutation_score_r4}
+\end{figure*}
+
 \subsubsection{Other options}

### 2015-11-17 Genetic algorithms - Journal of Climate/template.tex
Addition of the details of the mutation operator.

@@
 We processed by stages, analysing in details and in a systematic way every variants of the implemented operators, in combination with multiple other options and parameters in order to take into account eventual co-dependencies.
-
-In order to evaluate a combination of operators/options, we processed 10 optimizations for one parametrization of GAs. The performances were characterized by four indicators:
-
-\begin{itemize}
-	\item mean performance score: average of the final scores of the 10 optimizations,
-	\item convergence: the number of optimizations that converged to a supposed global optimum,
-	\item number of generations: characterization of the convergence speed,
-	\item number of evaluations of the objective function: characterization of the required calculation time (more realistic than the number of generations).
-\end{itemize}
+Our goal here is not to focus on the performance score we obtain through optimization, neither the values of the new optimized parameters \citep[covered in][]{Horton2016b}, but to explain how to use GAs to optimize AMs in an efficient way.
+
+In order to evaluate a combination of operators/options, we processed 10 optimizations for one parametrization of GAs.
+The performances were characterized by four indicators: (i) mean performance score: average of the final scores of the 10 optimizations, (ii) convergence: the number of optimizations that converged to a supposed global optimum, (iii) number of generations: characterization of the convergence speed, and (iv) number of evaluations of the objective function: characterization of the required calculation time (more realistic than the number of generations).
 
@@
 	\end{center}
-	\caption{Influence of the couples selection operators on the optimization performance.
+	\caption{Influence of the couples selection operators (Table \ref{tab:assessed_couples_selection_operators}) on the optimization performance.
 The box extends from the lower to upper quartile values of the data, with a line at the median.
@@
 Flier points are those past the end of the whiskers.
-The star represents the median.}
+The star represents the median.
+The gray box highlights the best options.}
 	\label{fig:operator_selectcoupl_score}
@@
 	\end{center}
-	\caption{Influence of the chromosome crossover operators on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+	\caption{Influence of the chromosome crossover operators (Table \ref{tab:assessed_crossover_operators}) on the optimization performance.
+Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
 	\label{fig:operator_crossover_score}
@@
 	\end{center}
-	\caption{Influence of the mutation operators on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+	\caption{Influence of the mutation operators (Table \ref{tab:assessed_mutation_operators}) on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
 	\label{fig:operator_mutation_score}
@@
 We then observe many operators more or less with the same performance scores and requiring a variable amount of assessments.
-The convergence analysis \citep[see][]{Horton2012a} allows us to highlight three best operators:
-
-\begin{itemize}
-
-	\item \textit{Non-uniform mutation} \citep{Michalewicz1996}: this operator is good in terms of convergence, mainly when the number of parameters to optimize is rather low.
-The number of required evaluations, however, can be quite substantial.
-The main disadvantage of the non-uniform mutation is the complexity of its parametrization, which is difficult to estimate a priori.
-These parameters must be carefully chosen to be in line with the evolution rate of the population, and are therefore dependent on the problem being treated.
-We could observe that the $\omega$ coefficient does not influence performance.
-The role of $G_{m}$ is rather difficult to judge, but does not seem essential.
-The mutation rate was found to be important.
-The difficulty is that the optimal value seems to be very case-related.
-Indeed, by even changing the precipitation time series (ie optimizing for another subregion), but not the complexity of the AM, the optimal mutation rate changes, making it impossible to estimate in advance.
-
-	\item \textit{Chromosome of adaptive search radius} (new): unlike the previous one, our new operator is very robust, as it requires no option and is auto-adapting.
-It may be sometimes a little bit slower for simple problems, but does not require parametrization, which is an important advantage.
-It is interesting to notice that our insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).
-
-	\item \textit{Multi-scale mutation} (new): finally, our multi-scale mutation, which also performs pretty well, requires one parameter, the mutation rate.
-However, it can also be difficult to estimate a correct value a priori.
-
-\end{itemize}
+The convergence analysis \citep[see][]{Horton2012a} allows us to highlight three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
+Because of the importance of the mutation operator on the resulting performance, we studied its role and parametrization in more detail.
+Thus, we performed different optimizations using variants of these 3 operators (Table \ref{tab:assessed_mutation_operators_bis}).
 
@@
 	\end{center}
-	\caption{Influence of the mutation operators on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+	\caption{Influence of the mutation operators (Table \ref{tab:assessed_mutation_operators_bis}) on the optimization performance, leaving the optimizer choose the pressure level of the atmospheric circulation analogy (single level of analogy).
+The predictand is precipitation over a subcatchment in the Swiss Alps (Binn-Simplon region).
+The red line represents the score of the sequential calibration and the blue line, the score of the optimization without automatic selection of the pressure levels.
+Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
 	\label{fig:operator_mutation_score_atmlevel}
@@
 	\end{center}
-	\caption{Influence of the mutation operators on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+	\caption{Same as Figure \ref{fig:operator_mutation_score_atmlevel}, but for another region in the Swiss Alps (Bottom Rhone valley), with different atmospheric influences.}
 	\label{fig:operator_mutation_score_rhoneamont}
@@
 	\end{center}
-	\caption{Influence of the mutation operators on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+	\caption{Same as Figure \ref{fig:operator_mutation_score_atmlevel}, but with a second level of analogy on moisture variables.}
 	\label{fig:operator_mutation_score_r2}
@@
 	\end{center}
-	\caption{Influence of the mutation operators on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+	\caption{Same as Figure \ref{fig:operator_mutation_score_r2}, but with a preselection on air temperature rather than a fixed calendar window.}
 	\label{fig:operator_mutation_score_r4}
 \end{figure*}
+
+The first analysis was the optimization of the precipitation forecasting over a subcatchment (Binn-Simplon region) in the Swiss Alps (Figure \ref{fig:operator_mutation_score_atmlevel}).
+The optimizer could choose the 2 pressure levels of the atmospheric circulation analogy (method with a single level of analogy).
+The resulting performance score is obviously superior to the one from the sequential calibration (red line on Figure \ref{fig:operator_mutation_score_atmlevel}).
+For most options, it is also slightly better than the results from the optimization without selection of the pressure levels (blue line).
+A clear breakthrough of the performances was not expected, as the former selection of pressure levels results from intensive work \citep{Bontron2004}.
+This application however demonstrates that, when correctly parametrized, GAs can automatically and successfully choose the pressure levels.
+However, some less relevant optimizations do not match the previous results.
+We could clearly observe, through different applications, that the automatic selection of the pressure level significantly increases the difficulty for GAs to converge to a unique solution, ideally the global optimum.
+A difficulty is that the pressure levels are considered within the optimization without continuity between values, and thus the approaches relying on distance in the parameters space, such as the search radius, cannot fully exploit the properties that make them efficient.
+However, even though the results show a certain variability, most of them present very good performance scores, despite different parameters of the AM.
+As illustrated in \cite{Horton2016}, the surface response of the parameters space of the AM is rather gentle in certain regions, meaning it allows for different values of some parameters without significantly impacting the performance score.
+
+Then, we performed the same optimization, but for another region, sensitive to other meteorological influences (Figure \ref{fig:operator_mutation_score_rhoneamont}), in order to assess eventual dependencies of the operator with the predictand.
+Even though we can observe differences with Figure \ref{fig:operator_mutation_score_atmlevel}, it is globally the same options that perform better.
+
+Next, we added a second level of analogy on moisture variables (Figure \ref{fig:operator_mutation_score_r2}).
+The optimizer had to optimize both levels of analogy simultaneously.
+Once again, despite the difficulty to optimize simultaneously both levels of analogy, the results were better than the sequential calibration (red line on Figure \ref{fig:operator_mutation_score_r2}).
+And finally, we added a preselection on air temperature instead of the fixed calendar window, as proposed by \cite{BenDaoud2010}.
+The results show generally higher scores (Figure \ref{fig:operator_mutation_score_r4}), demonstrating the success of the optimizer to take advantage of this new degree of liberty, and its capacity to handle optimization of 3 analogy levels jointly.
+Again, the most relevant options are generally the same.
+
+After analysis of the most relevant mutation operators, we can raise the following advice:
+
+\begin{itemize}
+
+	\item \textit{Non-uniform mutation} \citep{Michalewicz1996}: this operator is good in terms of convergence, mainly when the number of parameters to optimize is rather low.
+The number of required evaluations, however, can be quite substantial.
+The main disadvantage of the non-uniform mutation is the complexity of its parametrization, which is difficult to estimate a priori.
+These parameters must be carefully chosen to be in line with the evolution rate of the population, and are therefore dependent on the problem being treated.
+We could observe that the $\omega$ coefficient does not influence performance.
+The role of $G_{m}$ is rather difficult to judge, but does not seem essential.
+The mutation rate was found to be important.
+The difficulty is that the optimal value seems to be very case-related.
+Indeed, by even changing the precipitation time series (ie optimizing for another subregion), but not the complexity of the AM, the optimal mutation rate changes, making it impossible to estimate in advance.
+
+	\item \textit{Chromosome of adaptive search radius} (new): unlike the previous one, our new operator is very robust, as it requires no option and is auto-adapting.
+It may be sometimes a little bit slower for simple problems, but does not require parametrization, which is an important advantage.
+It is interesting to notice that our insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).
+
+	\item \textit{Multi-scale mutation} (new): finally, our multi-scale mutation, which also performs pretty well, requires one parameter, the mutation rate.
+However, it can also be difficult to estimate a correct value a priori.
+
+\end{itemize}
 
@@
 	\setlength\itemsep{-4px}
+	\item 1x non-uniform, $p_{mut}=0.05$, $G_{m}=50$, $\omega=0.1$
 	\item 1x non-uniform, $p_{mut}=0.05$, $G_{m}=100$, $\omega=0.1$
 	\item 1x non-uniform, $p_{mut}=0.1$, $G_{m}=100$, $\omega=0.1$
-	\item 1x non-uniform, $p_{mut}=0.2$, $G_{m}=100$, $\omega=0.1$
 	\item 1x multi-scale,  $p_{mut}=0.1$

### 2015-11-17 Genetic algorithms - Journal of Climate/template.tex
Removing redundant analyses.

@@
 The performance of the couples selection operator are relatively close (Figure \ref{fig:operator_selectcoupl_score}).
-Overall, we observe that the random pairing is the least good operator and the tournament selection with 3~candidates is slightly superior to others.
-Convergence analysis (not shown) presents similar trends to the scores.
-The influence on the number of assessments (not shown) reveals that the operators providing the worst scores are also those who need a higher number of evaluations.
-This analysis invites us to reject the rank and random pairing, and to consider the roulette wheel weighting or tournament selections, these being substantially better in terms of convergence and number of necessary evaluations.
+Overall, we observe that the random pairing performed the most poorly, whereas the tournament selection with 3~candidates is slightly superior to others.
+The roulette wheel weighting is almost equivalent, but is a bit less effective in terms of convergence and number of evaluations (not shown).
+This operator has not a significant role in our application.
 
 Analysis of crossover operators (Figure \ref{fig:operator_crossover_score}) reveal some slightly superior options, some inappropriate, and many averages.
-Among the inappropriate operators, we find first the heuristic crossover, which is also more demanding in terms of evaluation number, and the linear crossover.
+Among the inappropriate operators, we find first the heuristic crossover, which is also more demanding in terms of evaluation number, as well as the linear crossover.
 Binary-like crossover (especially with 2 points of intersection, whether $\beta$ is shared or not) are significantly better than the others, especially in terms of convergence (not shown).
-The two-point intersection is also relatively close.
+The two-point crossover is also relatively close.
 Other operators can also be considered usable.
@@
 
-After analysis of the most relevant mutation operators, we can raise the following advice:
+After analysis of the most relevant mutation operators, we can raise the following advice (detailed parametrization are provided in section \ref{sec:recommendations}):
 
@@
 It is interesting to notice that our insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).
+If one had to choose a single option for the mutation operator, we would recommend the chromosome of adaptive search radius, as it was proven effective and needs no parameter.
 
@@
 \end{itemize}
+
+In our application, the mutation operator has a leading effect and should be chosen with care.
+It may be wise to perform multiple optimizations and to consider these three operators in parallel in order to obtain results from algorithms that are either sometimes more efficient or more robust.
+It is interesting to note that the three best techniques incorporate a notion of search distance.
+It is likely that this notion is the key to these algorithms, for our application, and allows them to initially explore the parameter domain, and then to converge.
+The search radius in fact directly represents the notion of transition between exploration and exploitation, in our opinion more than a possible evolution of mutation rates.
 
@@
 
-The size of the population has an effect on the performance of the optimization (Figure \ref{fig:option_taillepop_score}).
+The size of the population ($N$) has an effect on the performance of the optimization (Figure \ref{fig:option_taillepop_score}).
 A bigger population leads to better results, but also to significantly longer optimizations.
@@
 with more degrees of freedom) requires a bigger population size.
-A rule of thumb based on different experiences is provided in the next section.
+A rule of thumb based on different experiences (not shown here) is provided hereafter:
+
+\begin{itemize}
+	\item $50<N\leqslant100$ for a very simple implementation of the AM (1 level of analogy with 2 pressure levels),
+	\item $N\approx200$ for a bit more complex AM (1 level of analogy with 4 pressure levels, or 2 level of analogy with less pressure levels),
+	\item $N\approx500$ for significantly more complex AMs (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the moisture analogy).
+\end{itemize}
+
+We didn't find any improvement with $N>500$, the results were even surprisingly of a lower quality.
+However, this relies on a limited number of case studies and cannot be generalized.
+It depends on the AM to optimize, and supposedly on the characteristics of the processes generating the precipitations in a given region.
 
@@
 
-\subsection{Synthesis}
-
-This comparison required tens of thousands of optimizations that were performed on a cluster of the University of Lausanne. The results, detailed in \citet{Horton2012a} are synthesized hereafter:
-
-\begin{itemize}
-	\item \textbf{Population size $N$}: we found the following ranges to be accurate in average for the population size (number of parameter sets of the AM):
-
-	$50<N<100$ for a very simple implementation of the AM (1 level of analogy with 2 pressure levels),
-
-	$N\approx200$ for a bit more complex AM (1 level of analogy with 4 pressure levels, or 2 level of analogy with less pressure levels),
-
-	$N\approx500$ for significantly more complex AMs (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the moisture analogy),
-
-	We didn't find any improvement with $N>500$, the results were even surprisingly of a lower quality.
-However, this cannot be generalized and depends on the AM to optimize, and supposedly on the characteristics of the processes generating the precipitations in a given region.
-
-	\item \textbf{Natural selection}: this operator has no significant influence, and both tested implementations work fine, with a slightly better performance for the ratio-elitism.
-
-	\item \textbf{Selection of couples}: 6 variants of the couples selection were assessed.
-The performance of these variants are relatively close, both in terms of performance score, convergence, and number of evaluations.
-The random pairing performed the most poorly, when the tournament selection with 3 candidates was slightly superior.
-The roulette wheel weighting is not far behind, but it is less effective in terms of convergence and number of evaluations.
-This operator has not a significant role in our application.
-
-	\item \textbf{Chromosomes crossover}: we compared 21 different options of the crossover operators.
-This analysis revealed some slightly better options, some bad ones, and many averages.
-Among the bad operators, we find first the heuristic crossover, which is also more demanding in number of evaluations, as well as the linear crossover.
-Binary-like crossovers (especially with 2 points of intersection, whether $\beta$ is shared or not) are significantly better than the others, especially in terms of convergence.
-The two points crossover is relatively close.
-Other operators can be considered usable, yet may not be optimal.
-Once again, this operator is not the key of the GAs parametrization.
-
-	\item \textbf{Mutation}: In our application, the mutation operator has a leading effect and should be chosen with care.
-We identified 3 more efficient variants: \textit{Non-uniform mutation} \citep{Michalewicz1996} that performs well but is difficult to parametrize, the \textit{Multi-scale mutation} (new) which needs only 1 parameter, and the \textit{Chromosome of adaptive search radius} (new), which is the most robust option as it has no parameter and always performed well.
-
-	It may be wise to perform multiple optimizations and to consider these three operators in parallel in order to obtain results from algorithms that are either sometimes more efficient or more robust.
-It is interesting to note that the three best techniques incorporate a notion of search distance.
-It is likely that this notion is the key to these algorithms, for our application, and allows them to initially explore the parameter domain, and then to converge.
-The search radius in fact directly represents the notion of transition between exploration and exploitation, in our opinion more than a possible evolution of mutation rates.
-
-	\item \textbf{Other options}: A ratio of 50\% for the mating pool seems to be a good choice.
-
-\end{itemize}
-
 \section{Recommended parametrization of GAs}
+\label{sec:recommendations}
 

### 2015-11-18 Genetic algorithms - Journal of Climate/template.tex
Removing bold.

@@
 \begin{itemize}
-	\item \textbf{$N_{mp}$-elitism} \citep{Michalewicz1996}: the population is sorted according to the value of the objective function and only the better half is preserved.
-
-	\item \textbf{Tournament selection} \citep{Michalewicz1996, Zitzler2004a}: two individuals are randomly selected and fight.
+	\item $N_{mp}$-elitism \citep{Michalewicz1996}: the population is sorted according to the value of the objective function and only the better half is preserved.
+
+	\item Tournament selection \citep{Michalewicz1996, Zitzler2004a}: two individuals are randomly selected and fight.
 The one with the highest performance score is chosen, but with a certain probability, in order to reduce the selection pressure.
@@
 \begin{itemize}
-	\item \textbf{Rank pairing}: individuals are gathered in pairs according to their rank (classified on the performance scores).
+	\item Rank pairing: individuals are gathered in pairs according to their rank (classified on the performance scores).
 Consecutive ranks are put together (odd rows are associated with even rows).
@@
 
-	\item \textbf{Random pairing}: two individuals are randomly selected to form a couple, according to a uniform law.
-
-	\item \textbf{Roulette wheel weighting}: the roulette technique refers to gambling.
+	\item Random pairing: two individuals are randomly selected to form a couple, according to a uniform law.
+
+	\item Roulette wheel weighting: the roulette technique refers to gambling.
 But unlike casino roulette, this one is biased.
@@
 
-	\item \textbf{Tournament selection}: This operator is similar to the one used in natural selection, but is applied here for the successive selection of each parent.
+	\item Tournament selection: This operator is similar to the one used in natural selection, but is applied here for the successive selection of each parent.
 To select a parent, a number of individuals (2 or 3) are randomly picked and the best is kept.
@@
 \begin{itemize}
-	\item \textbf{Single-point crossover}: a crossover point is randomly chosen for the pair. The genes (our parameters) located after that point are exchanged in between the two chromosomes.
-
-	\item \textbf{Two-point crossover}: works like the single-point crossover, but there are two intersections defining the segments to exchange.
+	\item Single-point crossover: a crossover point is randomly chosen for the pair. The genes (our parameters) located after that point are exchanged in between the two chromosomes.
+
+	\item Two-point crossover: works like the single-point crossover, but there are two intersections defining the segments to exchange.
 This approach, which significantly extends the search space for the children, is considered more efficient than the previous \citep{Beasley1993a, Haupt2004}.
 
-	\item \textbf{Multiple-point crossover} \citep{DeJong1975a}: it is a generalization of the previous, with a number of crossover points up to the number of genes.
-
-	\item \textbf{Uniform crossover} \citep{Syswerda1989}: for each gene of the chromosome, it is randomly chosen to exchange or not the values between the parents.
-
-	\item \textbf{Binary-like crossover} \citep{Haupt2004}: chromosome crossover on a binary coding can generate new values for variables located at intersection points, since the crossovers are applied at the bit level, thus often within a gene.
+	\item Multiple-point crossover \citep{DeJong1975a}: it is a generalization of the previous, with a number of crossover points up to the number of genes.
+
+	\item Uniform crossover \citep{Syswerda1989}: for each gene of the chromosome, it is randomly chosen to exchange or not the values between the parents.
+
+	\item Binary-like crossover \citep{Haupt2004}: chromosome crossover on a binary coding can generate new values for variables located at intersection points, since the crossovers are applied at the bit level, thus often within a gene.
 This is not the case for the floating-point representation, since the crossover is performed between the genes.
@@
 
-	\item \textbf{Blending method} \citep{Radcliffe1991a}: in this approach, instead of exchanging the genes in between the chromosomes after one or multiple crossover points, these are combined by linear combination (equation \ref{equation_mating_blending_method}).
+	\item Blending method \citep{Radcliffe1991a}: in this approach, instead of exchanging the genes in between the chromosomes after one or multiple crossover points, these are combined by linear combination (equation \ref{equation_mating_blending_method}).
 The genes of the parents are blended together using a random value ($\beta$) that can be unique for the whole chromosome, or that can change for every gene.
@@
 
-	\item \textbf{Linear crossover} \citep{Wright1991a}: in order to allow the genes to take values outside the interval defined by the parents, a method of extrapolation is necessary.
+	\item Linear crossover \citep{Wright1991a}: in order to allow the genes to take values outside the interval defined by the parents, a method of extrapolation is necessary.
 Linear crossover introduces such an approach, and produces three children from two parents, following equation \ref{equation_mating_linear_crossover}.
@@
 
-	\item \textbf{Heuristic crossover} \citep{Michalewicz1996}: it is a variation of the latter methods that relies on the following equation:
+	\item Heuristic crossover \citep{Michalewicz1996}: it is a variation of the latter methods that relies on the following equation:
 	\begin{equation}
@@
 
-	\item \textbf{Linear interpolation}: unlike previous techniques, this technique does not rely on crossover points, but on a linear interpolation on every gene of the couple (equation \ref{equation_mating_linear_interpolation}).
+	\item Linear interpolation: unlike previous techniques, this technique does not rely on crossover points, but on a linear interpolation on every gene of the couple (equation \ref{equation_mating_linear_interpolation}).
 	\begin{equation}
@@
 
-	\item \textbf{Free interpolation}: this technique performs interpolation on each gene, like the previous one; but in this case, the weighting factor changes for each gene:
+	\item Free interpolation: this technique performs interpolation on each gene, like the previous one; but in this case, the weighting factor changes for each gene:
 	\begin{equation}
@@
 \begin{itemize}
-	\item \textbf{Uniform mutation}: The mutation rate is constant and equal for every gene of each individual; they all have the same probability to mutate.
+	\item Uniform mutation: The mutation rate is constant and equal for every gene of each individual; they all have the same probability to mutate.
 When a gene is selected for mutation, a new random value is assigned, according to a uniform law.
 
-	\item \textbf{Variable uniform mutation} \citep{Fogarty1989}: a variable mutation rate over the generations was first suggested by \citet{Holland1992b} and evaluated by \citet{Fogarty1989}.
+	\item Variable uniform mutation \citep{Fogarty1989}: a variable mutation rate over the generations was first suggested by \citet{Holland1992b} and evaluated by \citet{Fogarty1989}.
 It improved significantly the performance of GAs.
@@
 
-	\item \textbf{Constant normal mutation}: many use normal distributions to generate new values. The gene $g$ that mutate becomes:
+	\item Constant normal mutation: many use normal distributions to generate new values. The gene $g$ that mutate becomes:
 	\begin{equation}
@@
 
-	\item \textbf{Variable normal mutation}: with the same logic that the variable uniform mutation, we tested a mutation operator using a normal distribution with a variable mutation rate and standard deviation.
+	\item Variable normal mutation: with the same logic that the variable uniform mutation, we tested a mutation operator using a normal distribution with a variable mutation rate and standard deviation.
 The mutation rate is calculated with equation \ref{equation_mutation_uniformvariable}.
@@
 
-	\item \textbf{Non-uniform mutation} \citep{Michalewicz1996}: two random numbers are picked based on a uniform law: $r_{1}$, which determines the direction of the change, and $r_{2}$, which determines its magnitude.
+	\item Non-uniform mutation \citep{Michalewicz1996}: two random numbers are picked based on a uniform law: $r_{1}$, which determines the direction of the change, and $r_{2}$, which determines its magnitude.
 The new value of the gene is given by the following equation:
@@
 
-	\item \textbf{Individual adaptive mutation rate} \citep{Back1992a}: based on the ideas of Evolution Strategies \citep[see][]{Rechenberg1973, Schwefel1981}, \citet{Back1992a} introduced a concept of self-adaptive genetic algorithms.
+	\item Individual adaptive mutation rate \citep{Back1992a}: based on the ideas of Evolution Strategies \citep[see][]{Rechenberg1973, Schwefel1981}, \citet{Back1992a} introduced a concept of self-adaptive genetic algorithms.
 The idea is to distribute control parameters within individuals themselves, which partially decentralize control of the evolution.
@@
 
-	\item \textbf{Individual adaptive search radius} (new): based on the ideas of the non-uniform mutation, we introduce a search radius in the approach of individual adaptive mutation rates.
+	\item Individual adaptive search radius (new): based on the ideas of the non-uniform mutation, we introduce a search radius in the approach of individual adaptive mutation rates.
 This search radius $r_{a}$, bounded between 0 and 1, is also adaptive and behaves similarly to the adaptive mutation rates.
@@
 
-	\item \textbf{Chromosome of adaptive mutation rate} \citep[\textit{n adaptative mutation rate},][]{Back1992a}: analogously to the individual adaptive mutation rate, this approach leaves the control of the evolution rate to the individuals themselves.
+	\item Chromosome of adaptive mutation rate \citep[\textit{n adaptative mutation rate},][]{Back1992a}: analogously to the individual adaptive mutation rate, this approach leaves the control of the evolution rate to the individuals themselves.
 The difference here is that each gene has a specific mutation rate.
@@
 
-	\item \textbf{Chromosome of adaptive search radius} (new): we introduced this operator that combines the operations of the chromosome of adaptive mutation rate to our adaptive search radius approach.
+	\item Chromosome of adaptive search radius (new): we introduced this operator that combines the operations of the chromosome of adaptive mutation rate to our adaptive search radius approach.
 Similarly, an individual has 3 chromosomes: the first containing the values to be optimized, the second containing the distributed mutation rate, and the last one, the distributed search radius.
@@
 
-	\item \textbf{Multi-scale mutation} (new): finally, we developed another approach, that is also based on the search radius concept.
+	\item Multi-scale mutation (new): finally, we developed another approach, that is also based on the search radius concept.
 However, the latter is not decreasing with time.

### 2015-11-18 Genetic algorithms - Journal of Climate/template.tex
Rewriting the abstract.

@@
 
-\abstract{The analogues method is based on a statistical relationship between synoptic atmospheric variables and local weather, which we aim at forecasting.
+\abstract{The analogues method is based on a statistical relationship between synoptic atmospheric variables (predictors) and local weather (predictand), which we aim at forecasting.
 This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic procedure.
-This sequential calibration is relatively fast and provide acceptable results, but it has strong constraints, is made of successive steps and thus cannot handle parameters dependencies, and mainly, it cannot calibrate automatically some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared.
-In order to surpass these limitations, we assessed a global optimization technique, namely genetic algorithms, that can optimize jointly all parameters of the method and thus provide a global optimum by taking into account the parameters dependencies.
-Moreover, it can calibrate parameters that were previously manually assessed, and can take into account new degrees of freedom that were unthinkable before.
-	The global optimization can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
-Indeed, it allows taking into account parameters inter-dependencies, adding new degrees of freedom, and choosing objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
+This sequential calibration has strong limitations: it is made of successive steps and thus cannot handle parameters dependencies, and it cannot automatically optimize some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared.
+In order to surpass these limitations, a global optimization technique was assessed, namely genetic algorithms, which can optimize jointly all parameters of the method and get closer to a global optimum by taking into account the parameters dependencies.
+Moreover, it can choose objectively parameters that were previously manually assessed, and can take into account new degrees of freedom that were unthinkable before.
 These kind of optimization techniques need however to be tailored to the problem to solve.
@@
 
-The classic calibration is fast to optimize one spatial window for a given pressure level and temporal window.
+The sequential calibration is fast to optimize one spatial window for a given pressure level and temporal window.
 However, it doesn't provide an objective selection of the pressure level and temporal window.
@@
 
-When creating the classic calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters and wrote: '' \textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent.
+When creating the sequential calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters and wrote: '' \textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent.
 We will present our results by first searching the best variable [note: e.g.

### 2015-11-18 Optimization case study - Journal of Hydrology/template.tex
Rewriting the abstract.

@@
 \abstract{
+
+	The global optimization can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
+Indeed, it allows taking into account parameters inter-dependencies, adding new degrees of freedom, and choosing objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
+
 We then applied the optimizer to the Rh\^{o}e catchment in the Swiss Alps and obtained coherent results which significantly improve the performance of the forecasting by analogy.

### 2015-11-18 AtmoSwing - Geoscientific Model Development/template.tex
Addition of the details of the mutation operator.
First version of the introduction.

@@
 
-\subsection{Evolution of the method and examples}
+\subsection{Evolution of the method for precipitation forecasting}
 \label{sec:method:evolution}
@@
 This allows for a fully automatic and objective optimization of the AM.
-However, as this topic is rather consequent and the code base is not yet released, it will be the subject of another publication.
+However, as this topic is rather consequent and the code base is not yet released, it will be the subject of other publications \cite[see][]{Horton2016a, Horton2016b}.
 

### 2015-11-18 Genetic algorithms - Journal of Climate/template.tex
First version of the introduction.

@@
 
-The sequential calibration cannot optimize all parameters of the AM, as several are manually selected, such as the meteorological variable, the pressure level and the temporal windows.
+The analogue method (AM) relies on the hypothesis that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Lorenz1956, Lorenz1969, Duband1970, Bontron2005}.
+The principle is sampling a certain number of past situations based on different atmospheric variables (predictors) in order to build a probabilistic forecast for a local weather variable (predictand).
+The most common usage of the AM is for precipitation forecasting \citep[eg.]{Guilbaud1997, Bontron2005, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, BenDaoud2015}, but AMs, or equivalent, were also used for short to medium term forecasting of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+Applications for monthly forecasts in many countries also exist, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal forecasts: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
+
+The purpose of this paper is not to present in details the AM and its different parametrizations, which can be found in \citet{Horton2016} or \citet{BenDaoud2015}.
+The concepts one needs to understand here are the following: the AM consists in searching $N$ past situations in a meteorological archive (typically reanalysis) that are the most similar, according to an analogy criteria, and to extract the observed values of the local weather variable of interest from another archive (typically local time series) in order to build the cumulative distribution considered as the probabilistic forecast for the target day.
+Predictors can be multiple, for example the geopotential height at different pressure levels on different temporal windows (time of observation).
+The method is usually made of multiple levels of analogy, leading to successive subsampling on predictors of different nature (eg.
+atmospheric circulation, moisture variables, vertical motion, and air temperature).
+
+Even though the method is rather simple compared to numerical weather prediction models, it contains a certain number of parameters one needs to determine, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criteria itself, and finally the number of analogue situations to keep at each subsampling level.
+Up to now, the optimization of the method has been undertaken by semi-automatic sequential calibration procedures \citep[see][for its definition]{Bontron2004, Horton2016}.
+However, the choice of predictor variables, pressure levels and temporal windows were still to be chosen manually before optimizing the spatial windows and the number of analogues.
 Testing multiple combinations of these can be cumbersome, especially when considering multiple predictors within the same level of analogy.
-Moreover, the parameters are calibrated successively within the same level of analogy, and in-between them.
-
- This article is not about discussing the results of such a technique, but describing the details of the implementation.
-The demonstration of the benefit brought by such an approach is the topic of another article.
-
-Up to now, the optimization of the method has been undertaken by semi-automatic calibration procedures.
-However, the choice of predictor variables, pressure levels and temporal windows were still to be chosen manually before optimizing the spatial windows and the number of analogues.
-Moreover, the semi-automatic technique proceeds to the optimization sequentially, ignoring potential dependencies between the parameters of the method.
-Thus, optimizing the method with the semi-automatic technique is laborious, as many combinations of predictors (variables, pressure levels, temporal windows) have to be assessed.
+Moreover, the sequential technique proceeds to the optimization sequentially, ignoring potential dependencies between the parameters of the method, may they be within a single level of analogy or between them.
+Thus, optimizing the method with the sequential technique is laborious, as many combinations of predictors (variables, pressure levels, temporal windows) have to be assessed.
 Moreover, due to its sequential approach, the risk of ending in a local optimum is high and can not be avoided.
-We thus propose a global optimization approach by means of Genetic algorithms, tailored to the analogue method (AM).
-
-\section{The analogue method}
-\label{section_analog_method}
+
+In order to overcome these limitations, two optimization techniques were assessed.
+First, \citet{Horton2012a} assessed the ability of the \citet{Nelder1965a} method based on a simplex approach.
+This technique didn't provide satisfying results and failed at identifying the global optimum.
+Indeed, the results didn't converge and many local optimums came out.
+The parameter space of the analogue method is very complex and not appropriate for a linear optimization technique.
+The conclusion was that global optimization techniques were necessary in order to calibrate AMs.
+The relevance of Genetic Algorithms (GAs) is presented here, which doesn't exclude that other global optimization techniques could also be successful.
+
+This article is not about discussing the details of the results of an optimization with GAs, but describing how to use GAs in order to successfully optimize AMs.
+Indeed, GAs variants are numerous and they always need to be tailored to the problem to be addressed.
+This requires intensive and systematic comparisons of operators and options in order to identify the key factors leading the optimization and the respective sensitivity of the options.
+These analyses are presented here and result in recommendations for the use of GAs when applied to AMs.
+The demonstration of the benefit brought by such an approach in a specific case study is the topic of \cite{Horton2016b}.
+
+We will begin with a motivation for a global optimization (section \ref{sec:motivation}) and then present the concepts of GAs as well as the assessed operators (section \ref{sec:gas}).
+The comparative analyses of the operators and their results are presented in section \ref{sec:assessment}, which lead us to the recommendations in section \ref{sec:recommendations}.
 
 \section{Motivation for a global optimization}
+\label{sec:motivation}
 
@@
 Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the pressure levels, and the consideration of non-overlapping spatial windows between the pressure levels.
-
-\citet{Horton2012a} assessed the ability of the \citet{Nelder1965a} method based on a simplex approach.
-This technique didn't provide satisfying results and failed at identifying the global optimum.
-Indeed, the results didn't converge and many local optimums came out.
-The parameter space of the analogue method is very complex and not appropriate for a linear optimization technique.
-Genetic algorithms were found to be much more relevant for such application.
 
@@
 \section{Assessment process and results}
+\label{sec:assessment}
 

### 2015-11-18 Genetic algorithms - Journal of Climate/template.tex
First version of the conclusion.

@@
 
-In order to automatically optimize the analogue method, we evaluated genetic algorithms, a global optimization technique, that is able to solve complex problems.
-Given the large number of existing operators and options, we had to evaluate systematically multiple variants to identify which operators are important, and which variant works best for the analogue method.
-We could thus identify that the mutation operator is a key element for our application, and provided new variants that were found to be efficient, such as the Chromosome of adaptive search radius that seems to be very reliable (no control parameter) and efficient .
-Recommendations were established for a relevant use of GAs for the optimization of the analogue method.
-However, there may still be possible improvements, through new operators, in order to improve the optimization performance and speed.
-Usage of this global optimization greatly eases the adaptation of the AM to new regions (with different leading meteorological processes) or to new predictands, as the optimization is performed automatically and globally.
-
-The global optimization tools allow easily adapting the AM to new regions by taking into account local meteorological influences, and has thus a great potential of use.
+In order to automatically optimize the analogue method and to get rid of the limitations of the usual sequential calibration, genetic algorithms were evaluated.
+Given the large number of existing operators and options, we had to evaluate systematically multiple variants to identify which operators are important, and which variant works best for the AM.
+We could thus identify that the mutation operator is a key element for our application, and provided new variants that were found to be efficient, such as the chromosome of adaptive search radius that seems to be very reliable (no control parameter) and efficient.
+Recommendations were established for a relevant use of GAs for the optimization of AMs.
+
+We do not exclude that another global optimization methods or other operators of GAs may perform better.
+The relevance of such approach has now been proven as it results in parametrization of AMs that are relevant and fully automatically established.
+A global optimization is the only way to take into account all the dependencies between parameters and levels of analogy.
+
+The global optimization approach allow easily adapting the AM to new regions by taking into account local meteorological influences, and has thus a great potential of use.
 Moreover, it allows exploring automatically datasets in order to extract the most relevant variables.

### 2015-11-18 Genetic algorithms - Journal of Climate/template.tex
Adding acronyms.

@@
 Indeed, the results didn't converge and many local optimums came out.
-The parameter space of the analogue method is very complex and not appropriate for a linear optimization technique.
+The parameter space of the AM is very complex and not appropriate for a linear optimization technique.
 The conclusion was that global optimization techniques were necessary in order to calibrate AMs.
@@
 
-We observed during the calibration of the analogue method that the resulting parameters vary with the initial choices (such as the number of analogues).
+We observed during the calibration of the AM that the resulting parameters vary with the initial choices (such as the number of analogues).
 In addition, the different levels of analogy (eg on the atmospheric circulation and the moisture index) are always calibrated sequentially.
@@
 And later in his work: '' \textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution} ''.
-\citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of the analogue method and concludes that one needs to be an expert to know their respective influence, their sensitivity and their nonlinear interactions.
-\citet{BenDaoud2010}, when calibrating the analogue method, also stated that '' \textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously } ''.
-
-The analogue method needs to be adapted to every new region it is applied, because the leading meteorological influences are specific to this region.
+\citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of the AM and concludes that one needs to be an expert to know their respective influence, their sensitivity and their nonlinear interactions.
+\citet{BenDaoud2010}, when calibrating the AM, also stated that '' \textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously } ''.
+
+The AM needs to be adapted to every new region it is applied, because the leading meteorological influences are specific to this region.
 Even the selection of the pressure level and the temporal window should be reconsidered, when not the variable itself.
 For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012a} found no interest in this variable in an Alpine environment, because in the Alps, the vertical motion is mainly controlled by orographic effects, and was thus already well related to the atmospheric circulation itself.
-So, when adapting the analogue method to a new region, we should assess systematically every combination of pressure levels, time and spatial windows, which is an intensive task.
+So, when adapting the AM to a new region, we should assess systematically every combination of pressure levels, time and spatial windows, which is an intensive task.
 This procedure can be automatized by a global optimization technique.
 
-Our ambition was then to assess the feasibility of an automatic optimization of the analogue method through various techniques.
+Our ambition was then to assess the feasibility of an automatic optimization of the AM through various techniques.
 The objective was to find an approach to optimize all parameters simultaneously, and thus be able to identify the global optimum in the parameter space.
@@
 
-Genetic algorithms are part of the family of evolutionary algorithms \citep{Back1993b, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
+GAs are part of the family of evolutionary algorithms \citep{Back1993b, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
 GAs are the most used technique from evolutionary algorithms \citep{Back1993b}, and they are constantly improving \citep{Haupt2004}.
@@
 
-	\item Individual adaptive mutation rate \citep{Back1992a}: based on the ideas of Evolution Strategies \citep[see][]{Rechenberg1973, Schwefel1981}, \citet{Back1992a} introduced a concept of self-adaptive genetic algorithms.
+	\item Individual adaptive mutation rate \citep{Back1992a}: based on the ideas of Evolution Strategies \citep[see][]{Rechenberg1973, Schwefel1981}, \citet{Back1992a} introduced a concept of self-adaptive GAs.
 The idea is to distribute control parameters within individuals themselves, which partially decentralize control of the evolution.
@@
 
-We evaluated the optimization by genetic algorithms on AMs of varying complexity, with a large number of combinations of operators to be able to make recommendations for optimizing the AM.
-Our conclusions are:
+We evaluated the optimization by GAs on AMs of varying complexity, with a large number of combinations of operators to be able to make recommendations for optimizing the AM. Our conclusions are:
 
@@
 
-In order to make an optimization of the AM with genetic algorithms, it may be wise to consider these three mutation operators in parallel.
+In order to make an optimization of the AM with GAs, it may be wise to consider these three mutation operators in parallel.
 We would then combine algorithms that are sometimes faster to other that are more robust.
@@
 
-In order to automatically optimize the analogue method and to get rid of the limitations of the usual sequential calibration, genetic algorithms were evaluated.
+In order to automatically optimize the AM and to get rid of the limitations of the usual sequential calibration, GAs were evaluated.
 Given the large number of existing operators and options, we had to evaluate systematically multiple variants to identify which operators are important, and which variant works best for the AM.

### 2015-11-18 Optimization case study - Journal of Hydrology/template.tex
Adding acronyms.

@@
 \abstract{
-
 	The global optimization can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
 Indeed, it allows taking into account parameters inter-dependencies, adding new degrees of freedom, and choosing objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
-
 We then applied the optimizer to the Rh\^{o}e catchment in the Swiss Alps and obtained coherent results which significantly improve the performance of the forecasting by analogy.

### 2015-11-18 Genetic algorithms - Journal of Climate/template.tex
Reducing the text...

@@
 The purpose of this paper is not to present in details the AM and its different parametrizations, which can be found in \citet{Horton2016} or \citet{BenDaoud2015}.
-The concepts one needs to understand here are the following: the AM consists in searching $N$ past situations in a meteorological archive (typically reanalysis) that are the most similar, according to an analogy criteria, and to extract the observed values of the local weather variable of interest from another archive (typically local time series) in order to build the cumulative distribution considered as the probabilistic forecast for the target day.
+The concepts one needs to understand here are the following: the AM consists in searching a certain number of past situations in a meteorological archive (typically reanalysis) that are the most similar, according to an analogy criteria, and to extract the observed values of the local weather variable of interest from another archive (typically local time series) in order to build the cumulative distribution considered as the probabilistic forecast for the target day.
 Predictors can be multiple, for example the geopotential height at different pressure levels on different temporal windows (time of observation).
@@
 However, it doesn't provide an objective selection of the pressure level and temporal window.
-The only option is to try systematically every combination, which may be acceptable for no more than 2 levels.
-However, \citet{Horton2012a} showed that additional pressure levels may improve the method.
-
-We observed during the calibration of the AM that the resulting parameters vary with the initial choices (such as the number of analogues).
-In addition, the different levels of analogy (eg on the atmospheric circulation and the moisture index) are always calibrated sequentially.
-However, we can not exclude any dependency between them, which could lead us to select another parametrization if we calibrate them together.
+The only option is to try systematically every combination, which becomes cumbersome already with 2 pressure levels, whereas it seems profitable to consider even more \citep{Horton2012a}.
+
+We observed during the AM calibration that the resulting parameters vary with the initial choices (such as the number of analogues).
+In addition, the different levels of analogy (eg.
+on the atmospheric circulation and the moisture index) are always calibrated sequentially.
+However, we cannot exclude any dependency between them, which could lead us to select another parametrization if we calibrate them together.
 Simultaneous calibration of all parameters has never been undertaken so far.
@@
 The AM needs to be adapted to every new region it is applied, because the leading meteorological influences are specific to this region.
-Even the selection of the pressure level and the temporal window should be reconsidered, when not the variable itself.
-For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012a} found no interest in this variable in an Alpine environment, because in the Alps, the vertical motion is mainly controlled by orographic effects, and was thus already well related to the atmospheric circulation itself.
-So, when adapting the AM to a new region, we should assess systematically every combination of pressure levels, time and spatial windows, which is an intensive task.
+Even the selection of the pressure levels and the temporal windows should be reconsidered, when not the variable itself.
+For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012a} found no interest in this variable in an Alpine environment, because the vertical motion, which is mainly controlled by orographic effects, was already well related to the atmospheric circulation itself.
+So, when adapting the AM to a new region, one should assess systematically every combination of pressure levels, temporal and spatial windows, which is an intensive task.
 This procedure can be automatized by a global optimization technique.
 
-Our ambition was then to assess the feasibility of an automatic optimization of the AM through various techniques.
-The objective was to find an approach to optimize all parameters simultaneously, and thus be able to identify the global optimum in the parameter space.
-In addition, it can overcome the systematic manual assessments of certain parameters such as the selection of the pressure levels and time windows.
-Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the pressure levels, and the consideration of non-overlapping spatial windows between the pressure levels.
+Our ambition was then to assess the feasibility of an automatic optimization of the AM in order to assess all parameters simultaneously, and thus to be able to get nearer to the global optimum in the parameters space.
+In addition, it can overcome the systematic manual assessments of all pressure levels and temporal windows.
+Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the pressure levels \cite[see]{Horton2016b}, and the consideration of non-overlapping spatial windows between the pressure levels.
 
@@
 Applications of GAs are very diversified as they can handle many parameters of various types \citep{Joines1996a}, even with very complex cost surfaces \citep{Haupt2004}.
-GAs work remarkably well with intervariable dependences \citep{Haupt2004}.
 The objective function to optimize (often named fitness function in this context) can be of different types (mathematical function, experimental or numerical modeling).
@@
 
-By means of the reproduction operator and the natural selection, the GAs focus on the most promising regions of the parameter space \citep{Holland1992b}.
-Points (parameter sets) are densified in these areas because the strong genes of the best individuals propagate from generation to generation.
-
 Two conditions guarantee in theory the convergence to the global optimum \citep{Zitzler2004a}: (1) Parameters mutations that can allow to explore the entire parameter space, thereby ensures that any value can be achieved with a non-zero probability.
@@
 
-The GAs optimize a population of individuals (parameter sets).
+The GAs optimize a population of $N$ individuals (parameter sets).
 Each individual contains a chromosome (parameters of the AM in our case).
 We call gene every parameter that constitutes the chromosome.
-The parameters to optimize have long been coded in binary form and assembled as strings in the canonical GAs \citep{Goldberg1989}.
-Encoding and decoding steps were needed to transform the variable from its floating-point representation into its binary representation, and vice versa, which introduce quantification errors \citep{Haupt2004}.
-According to \citet{Holland1992b}, working with binary chromosomes was supposed to be more efficient \citep{Goldberg1990a, Back1993b}.
-However, more and more applications use floating-point representations, allowing to avoid the coding and decoding steps and the quantification errors \citep{Haupt2004}, and which also often resulted in a performance improvement \citep{Goldberg1990a}.
-It is thus now considered that for continuous variables, a floating-point representation is more suited \citep{Michalewicz1996, Herrera1998a, Haupt2004, Back1996b, Gaffney2010a}.
-
-There are numerous implementation variants of GAs often optimal for a given problem \citep{Hart1991a,Schraudolph1992a}.
+The floating-point representation \citep[instead of the canonical binary, see][]{Goldberg1989, Goldberg1990a, Holland1992b} of the genes was considered, as it was found more suited in multiple applications \citep{Michalewicz1996, Herrera1998a, Haupt2004, Back1996b, Gaffney2010a}.
+
+There are numerous implementation variants of GAs often optimal for a given problem \citep{Hart1991a, Schraudolph1992a}.
 The divergences are the operators implementation, through significantly different algorithms, which has an important effect on the results \citep{Gaffney2010a}.
@@
 	\item The fitness (performance score or objective function) of every individual is assessed.
-	\item A natural selection is applied, after which only the best individuals remain, which constitutes the intermediate generation.
-	\item From this intermediate generation, couples are formed according to given rules.
+	\item A natural selection is applied, after which only the best individuals remain, which constitutes the intermediate generation (IG).
+	\item From this IG, couples are formed according to given rules.
 	\item These couples proceed to reproduction, or chromosome crossover, in order to mix their genes (parameters) according to the operator version.
-New children are generated in order to fill the intermediate generation back to $N$ individuals.
+New children are generated in order to fill the IG back to $N$ individuals.
 	\item Parents and children are then subject to mutation, where some genes get affected, meaning some parameter values are randomly changed.
@@
 
-All operators we used and their options, applied to real coding, are described in the following sections. Many other operators exist, but we will only present the ones we evaluated.
+All operators we used and their options, applied to floating-point coding, are described in the following sections. Many other operators exist, but we will only present the ones we evaluated.
 
@@
 Natural selection is performed on the basis of the values of the objective function.
-The selection allows to only keep a certain part of the population, usually half ($N/2$), which can access the mating pool (intermediate generation with $N_{mp}$ members).
+The selection allows to only keep a certain part of the population, usually half ($N/2$), which can access the IG (with $N_{mp}$ members).
 If $N_{mp}$ is too high, the reproduction rate is too low, whereas if it is too small, the strong traits of individuals do not have the ability to accumulate in the same chromosome \citep{Haupt2004}.
@@
 The one with the highest performance score is chosen, but with a certain probability, in order to reduce the selection pressure.
-This procedure is repeated until the mating pool is full.
-Individuals can be selected several times, and thus be represented several times in the mating pool.
+This procedure is repeated until the IG is full.
+Individuals can be selected several times, and thus be represented several times in the IG.
 \end{itemize}
@@
 
-Individuals of the mating pool can reproduce. It begins with the selection of pairs (the parents). The techniques implemented in this work are the following:
+Individuals of the IG can reproduce. It begins with the selection of pairs (the parents). The techniques implemented in this work are the following:
 
@@
 
-	\item Roulette wheel weighting: the roulette technique refers to gambling.
-But unlike casino roulette, this one is biased.
+	\item Roulette wheel weighting: this technique refers to gambling, but with a biased roulette.
 Each individual is associated with a sector of the wheel with a certain opening angle, which is its probability of selection \citep{Haupt2004}.
 The probability assigned to the individuals is proportional to their fitness (objective function), so that the most adapted individuals have the greatest probability of reproduction.
-There are two techniques for weighting the individuals of the mating pool:
+There are two techniques for weighting the individuals of the IG:
 
@@
 	\textit{Roulette wheel weighting on fitness}: the selection probability is calculated based on the value of the objective function.
-This approach gives more weight to the best individuals when the distribution of performance scores is wide, while the weight is almost similar when all individuals have approximately the same performance score \citep{Haupt2004}.
 The probability $p_{n}$ of each individual is calculated by the equation \ref{equation_mating_score_weighting}:
@@
 	\item Two-point crossover: works like the single-point crossover, but there are two intersections defining the segments to exchange.
-This approach, which significantly extends the search space for the children, is considered more efficient than the previous \citep{Beasley1993a, Haupt2004}.
+This approach, which significantly extends the search space for the children, is considered more efficient than the previous \citep{Beasley1993a}.
 
@@
 Linear crossover introduces such an approach, and produces three children from two parents, following equation \ref{equation_mating_linear_crossover}.
-Less couples are required in order to fill up the generation.
+Less couples are required in order to fill up the population.
 	\begin{equation}
@@
 Many other methods or variations exist, combining the advantages of different approaches.
-The performance of the variants being related to the problem to be addressed, we can not identify a priori the best technique for our application.
+The performance of the variants being related to the problem to be addressed, one cannot identify a priori the best technique for any application.
 
@@
 The combination of strong genes by the operator of chromosomes crossover is theoretically the most important operating mechanism in the conventional GAs \citep{Holland1992b,Back1993b}.
-However, many studies identify the mutation process as main operator, and crossovers as secondary \citep[see][]{Back1992a,Back1996a,Back1996b,Smith1997a,Deb1999,Haupt2004,Costa2005a,Costa2007a}.
+However, many studies identify the mutation process as main operator, and crossovers as secondary \citep[see][]{Back1992a, Back1996a, Back1996b, Smith1997a, Deb1999, Costa2005a, Costa2007a}.
 
 The mutation operator is a direct modification of genes.
-In a binary coding, it is implemented as an inversion of some bits in a chromosome, while in real coding, it is done by changing the gene values.
+In real coding, it is done by changing the gene values.
 Mutations add diversity to the population and prevent a freeze of the evolution, or a genetic drift to a local optimum.
-Thus, it makes the convergence to the global optimum theoretically possible \citep{Beasley1993a}, as they allow exploring beyond the current region of the parameter space.
-They therefore help preventing the algorithm to converge too quickly to a local optimum and bring new characteristics that were not present in the original population \citep{Haupt2004}.
+Thus, it makes the convergence to the global optimum theoretically possible \citep{Beasley1993a}, as they allow exploring beyond the current region of the parameter space by bringing new characteristics that were not present in the original population \citep{Haupt2004}.
 
@@
 	\item Variable uniform mutation \citep{Fogarty1989}: a variable mutation rate over the generations was first suggested by \citet{Holland1992b} and evaluated by \citet{Fogarty1989}.
-It improved significantly the performance of GAs.
 In most applications, the mutation rate decreases with the generations, in a deterministic and global (for all individuals) manner \citep{Back1992b}.
@@
 
-	\item Constant normal mutation: many use normal distributions to generate new values. The gene $g$ that mutate becomes:
+	\item Constant normal mutation: many applications use normal distributions to generate new values. The gene $g$ that mutate becomes:
 	\begin{equation}
@@
 
-	\item Variable normal mutation: with the same logic that the variable uniform mutation, we tested a mutation operator using a normal distribution with a variable mutation rate and standard deviation.
+	\item Variable normal mutation: with the same logic as the variable uniform mutation, we tested a mutation operator using a normal distribution with a variable mutation rate and standard deviation.
 The mutation rate is calculated with equation \ref{equation_mutation_uniformvariable}.
@@
 	\end{equation}
-	where $\sigma_{n,G}$ is the standard deviation of gene $n$ et generation number $G$, $\sigma_{G_{0}}$ is the initial standard deviation, $\sigma_{G_{m,\sigma}}$ is the final standard deviation, $G_{m,\sigma}$ is the maximum number of generations during which the standard deviation varies.
+	where $\sigma_{n,G}$ is the standard deviation of gene $n$ and generation number $G$, $\sigma_{G_{0}}$ is the initial standard deviation, $\sigma_{G_{m,\sigma}}$ is the final standard deviation, $G_{m,\sigma}$ is the maximum number of generations during which the standard deviation varies.
 $p_{G_{0}}$, $p_{G_{m,p}}$, $G_{m,p}$, $\sigma_{G_{0}}$, $\sigma_{G_{m,\sigma}}$ and $G_{m,\sigma}$ are the six parameters of the method.
@@
 Thus, as this rate decreases, it will have less probability of being itself mutated.
-This approach is close to the natural adaptation phenomena.
-A population less suited to its environment is changing faster than better adapted populations.
+This approach is close to the natural adaptation phenomena: a population less suited to its environment is changing faster than better adapted populations.
 Mutations are performed according to a constant uniform distribution.
 The initial mutation rates are randomly chosen \citep{Back1992a} and the method has no parameter.
-Other approaches exist to introduce a self-adaptation \citep[see][]{Smith1997a,Deb1999,Deb2001a}.
+Other approaches exist to introduce a self-adaptation \citep[see][]{Smith1997a, Deb1999, Deb2001a}.
 
@@
 This approach is very common in the field of GAs \citep{Haupt2004}.
-After the natural selection operator, if the best individual has not been selected, it is copied to the mating pool instead of an individual randomly picked.
-After mutation, if the best individual has mutated and if its new version has a lower performance score than the original, the latter is also reinserted in the mating pool instead of an individual randomly chosen.
+After the natural selection operator, if the best individual has not been selected, it is copied to the IG instead of an individual randomly picked.
+After mutation, if the best individual has mutated and if its new version has a lower performance score than the original, the latter is also reinserted in the IG instead of an individual randomly chosen.
 
@@
 They observed that a small population size improves the initial performance, while a large population improves long-term performance.
-They also observed that the ratio of the population to keep for the mating pool is around 50\% (45\% to 60\%).
+They also observed that the ratio of the population to keep for the IG is around 50\% (45\% to 60\%).
 
@@
 
-We also assessed the influence of the size of the intermediate population (ratio of the total population) selected for mating (Figure \ref{fig:option_popratio_score}).
+We also assessed the influence of the size of the IG (ratio of the total population) selected for mating (Figure \ref{fig:option_popratio_score}).
 It appears that a big ratio is not optimal.
@@
 	\end{center}
-	\caption{Influence of the intermediate population ratio on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+	\caption{Influence of the intermediate population (IG) ratio on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
 	\label{fig:option_popratio_score}
@@
 
-	\item The value of the ratio for the intermediate population is not so important, and value of 50\% seems quite appropriate.
+	\item The value of the ratio for the IG is not so important, and value of 50\% seems quite appropriate.
 

### 2015-11-18 Genetic algorithms - Journal of Climate/template.tex
Reducing the text...

@@
 
+A key element of the parametrization of GAs is finding the right balance between exploration and exploitation \citep{Back1992a, Smith1997a}.
+Exploration is characterized by a relatively high probability to assess the regions of the parameter space that have not yet been visited.
+This probability must be sufficiently large at the beginning of the optimization, so that the algorithm is capable of identifying the region where the global optimum is located.
+Exploitation is characterized by a local search in an area of interest, and generally makes small movements.
+The latter is interesting to refine the results at the end of the optimization.
+
 \subsection{Structure and operators}
@@
 
-	\item Chromosome of adaptive mutation rate \citep[\textit{n adaptative mutation rate},][]{Back1992a}: analogously to the individual adaptive mutation rate, this approach leaves the control of the evolution rate to the individuals themselves.
+	\item Chromosome of adaptive mutation rate \citep[or \textit{n adaptative mutation rate},][]{Back1992a}: analogously to the individual adaptive mutation rate, this approach leaves the control of the evolution rate to the individuals themselves.
 The difference here is that each gene has a specific mutation rate.
@@
 	\item Chromosome of adaptive search radius (new): we introduced this operator that combines the operations of the chromosome of adaptive mutation rate to our adaptive search radius approach.
-Similarly, an individual has 3 chromosomes: the first containing the values to be optimized, the second containing the distributed mutation rate, and the last one, the distributed search radius.
+Similarly, an individual has 3 chromosomes: the first containing the values to be optimized, the second the distributed mutation rate, and the last one, the distributed search radius.
 Again, no external parameters are required.
@@
 Methods based on a reduction of the mutation rate or radius simulate a transition from the exploration phase to the exploitation one.
-The idea is consistent as long as we are confident that the algorithm will converge towards the global optimum.
-Indeed, once the algorithm is in the exploitation mode, it is very unlikely to go out of the region it converges to.
 We wanted to test an approach that combines both exploration and exploitation during the whole optimization.
@@
 
-When the gene to mutate is represented by a list of distinct values (eg meteorological variable or analogy criterion), the random choice of a new value is always based on a uniform distribution, without notion of search radius.
-There is indeed no meaning to use operators based on principles of proximity when the latter does not exist.
+When the gene to mutate is represented by a list of distinct values (eg meteorological variable or analogy criterion), the random choice of a new value is always based on a uniform distribution, without notion of distance in the parameters space.
 
@@
 This ensures the survival of the best individual so that we do not lose a better solution.
-This approach is very common in the field of GAs \citep{Haupt2004}.
 After the natural selection operator, if the best individual has not been selected, it is copied to the IG instead of an individual randomly picked.
@@
 It is thus common that the best individual does not evolve over several generations when we get closer to the global solution.
-We chose a value of $x=20$ generations.
+A value of $x=20$ generations was chosen.
 
@@
 For example, when a crossover or a mutation operation results in a parameter value standing out of the authorized bounds, it has to be brought back within the limits.
-Moreover, the parameters are of different nature: some are continuous, such as the weight, some are discretized, such as the analogues number, or the spatial windows, and finally, some are independent elements in an array, such as the selection of the meteorological variable.
+Moreover, the parameters are of different nature: some are continuous, such as the weighting between pressure levels, some are discretized, such as the analogues number, or the spatial windows, and finally, some are independent elements in an array, such as the selection of the meteorological variable.
 New values resulting from the optimizer need to respect the type of data it represents.
 
-Other constraints exist in between the parameters, such as the temporal window of the moisture index that has to be consistent in between the relative humidity and the precipitable water.
+Other constraints exist in between the parameters, such as the temporal window of the moisture index \cite[see][]{Horton2016} that has to be consistent in between the relative humidity and the precipitable water.
 Another example is the weighting of the different pressure levels which has to be normalized.
@@
 GAs are very computationally intensive because they require many evaluations of the objective function.
-These assessments are very long in our application, as they require calculating and assessing a forecast for every day of the calibration period.
+These assessments are very long in our application, as they require calculating and assessing a forecast for every day of the calibration period, thus over several decades.
 In order to reduce the computation time, we avoid recalculating the performance score of an individual who has previously been evaluated and that has not changed.
@@
 
-The assessment (calculation of the objective function) of each member of the population of a generation is completely independent and can be performed in parallel on different processors of a computer \citep{Alliot2005}.
-We implemented this technique and the resulting time savings was very important.
+As the assessment (calculation of the objective function) of each member of the population of a generation is completely independent, it was performed in parallel on different processors of a computer, as suggested by \citet{Alliot2005}.
 In order to perform optimizations for multiple time series, the use of a cluster is a necessity, which our code allows.
@@
 The GAs parametrization, such as the mutation rate, population size, natural selection options, and so on, is difficult given the high number of existing variants, each developed for a specific problem \citep{Haupt2004, Costa2007a}.
-This parametrization depends on the objective function, implementation variants, the range of the parameters to be optimized, and performance indicators.
+The parametrization depends on the objective function, implementation variants, the range of the parameters to be optimized, and performance indicators.
 Thus, different studies suggest very different parametrization.
-
-A key element of the parametrization of GAs is finding the right balance between exploration and exploitation \citep{Back1992a, Smith1997a}.
-Exploration is characterized by a relatively high probability to assess the regions of the parameter space that have not yet been visited.
-This probability must be sufficiently large at the beginning of the optimization, so that the algorithm is capable of identifying the region where the global optimum is located.
-Exploitation is characterized by a local search in an area of interest, and generally makes small movements.
-The latter is interesting to refine the results at the end of the optimization.
 
@@
 \citet{Back1996b} showed that mutation rates higher than the usual ranges are more optimal at the beginning of the optimization, allowing further exploration.
-The combination of a small population and a high mutation rate works best for the first generations \citep{DeJong1975a, Back1996b, Haupt2004}, but as we could observe, it does not guarantee the quality of the final result.
 Incremental approaches with varying mutation rates are certainly more optimal but more complex to implement \citep{Back1996a, Back1996b}.
@@
 
-In order to evaluate a combination of operators/options, we processed 10 optimizations for one parametrization of GAs.
-The performances were characterized by four indicators: (i) mean performance score: average of the final scores of the 10 optimizations, (ii) convergence: the number of optimizations that converged to a supposed global optimum, (iii) number of generations: characterization of the convergence speed, and (iv) number of evaluations of the objective function: characterization of the required calculation time (more realistic than the number of generations).
-
-Given the large number of operators and options of the method, it is not possible to systematically assess each combination.
-We thus proceeded in stages, but for each comprehensive comparison of an operator type, two very different variants of other operators are considered to take account of indirect effects.
-
-\begin{enumerate}
-	\item Assessment of all breeding operators, thus every combination of selection of couples and chromosome crossover variants, along with variants of the other options.
-	\item Assessment of the mutation operator
-	\item Evaluation of other options of the method
-\end{enumerate}
+In order to evaluate a combination of operators/options, we processed 10 optimizations per parametrization of GAs.
+The performances were characterized by four indicators: (i) mean performance score: average of the final scores of the 10 optimizations, (ii) convergence: the number of optimizations that converged to a supposed global optimum, (iii) number of generations: characterization of the convergence speed, and (iv) number of evaluations of the objective function: characterization of the required calculation time.
 
@@
 
-After a short first overview of the results, GAs have quicky been proven successful at optimizing the AM.
+After a first overview of the results, GAs have quicky been proven successful at optimizing the AM.
 Indeed, the performance score of the sequential approach has been quickly exceeded without adding any new parameter to the method (Figure \ref{fig:gas_evolution_good}).
@@
 
-\subsection{Results}
+\subsection{Results of the comparison}
 
@@
 It means that we compare the effect of the studied operator when all the other operators are equivalent, while assessing multiple combinations.
-We then summarizes this contribution relatively to the other options, as a percentage of gain/loss regarding the mean of all variants.
-For example, to evaluate the performance of the uniform crossover operator, we compare some indicators between its performance and the average of performance of all crossover operators while retaining the same population size, the same mutation operators, natural selection, and selection of couples.
+We then summarize this contribution relatively to the other options, as a percentage of gain/loss regarding the mean of all variants.
+For example, to evaluate the performance of the uniform crossover operator, we compare its performance to the average of all crossover operators while retaining the same population size, the same mutation operators, natural selection, and selection of couples.
+
+From the very beginning of the assessments, the importance of the mutation operator was obvious \cite[see][for the details]{Horton2012a}, and its leading influence on the optimization performance was evident.
+Its role is analyzed later on.
 
@@
 
-After this first assessment, the importance of the mutation operator was obvious \cite[see][for the details]{Horton2012a}, and its leading influence on the optimization performance was evident.
-However, the effect of the operators and options other than the ones related to breeding will be detailed later.
-
 \begin{figure}[htb]
@@
 The performance of the couples selection operator are relatively close (Figure \ref{fig:operator_selectcoupl_score}).
-Overall, we observe that the random pairing performed the most poorly, whereas the tournament selection with 3~candidates is slightly superior to others.
-The roulette wheel weighting is almost equivalent, but is a bit less effective in terms of convergence and number of evaluations (not shown).
-This operator has not a significant role in our application.
+Overall, we observe that the tournament selection with 3~candidates is slightly superior to others, along with the roulette wheel weighting.
+This last one is however a bit less effective in terms of convergence and number of evaluations (not shown).
+The couples selection operator has not a significant role in our application.
 
 Analysis of crossover operators (Figure \ref{fig:operator_crossover_score}) reveal some slightly superior options, some inappropriate, and many averages.
-Among the inappropriate operators, we find first the heuristic crossover, which is also more demanding in terms of evaluation number, as well as the linear crossover.
 Binary-like crossover (especially with 2 points of intersection, whether $\beta$ is shared or not) are significantly better than the others, especially in terms of convergence (not shown).
-The two-point crossover is also relatively close.
-Other operators can also be considered usable.
+Others operators can also be considered usable.
 
 \subsubsection{Mutation operator}
-
-Having identified the leading role of the mutation operator, we strongly focused the sensitivity analysis on this operator.
-Each of the 10 different implementations (see section \ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Table \ref{tab:assessed_mutation_operators}), bringing the number of variations of this operator up to 109.
+\label{sec:assessment:mutation}
+
+Having identified the leading role of the mutation operator, the sensitivity analysis focused on it.
+Each of the 10 different implementations (see section \ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Table \ref{tab:assessed_mutation_operators}), bringing the number of its variations up to 109.
 We also did some optimizations without any mutation as a reference.
@@
 Figure \ref{fig:operator_mutation_score} show the results of this analysis and illustrates the important role of the mutation on the performance of the optimizations.
-Optimizations without mutation (last box on the Figure) are inferior to most mutation operators, and the scale of the influence of the mutation operators is significantly more important than those for the other options.
+Those without mutation (last box on the Figure) are inferior to most mutation operators, and the scale of the influence of this operator is significantly more important than those for the other options.
 The details of the analysis \citep[see][]{Horton2012a} show that the other reproduction operators seem of secondary importance.
@@
 
-The mutation operators based on a variable normal or uniform law work very poorly and are difficult to configure.
+The mutation operators based on a variable normal or variable uniform laws work very poorly and are difficult to configure.
 We then observe many operators more or less with the same performance scores and requiring a variable amount of assessments.
@@
 The optimizer could choose the 2 pressure levels of the atmospheric circulation analogy (method with a single level of analogy).
-The resulting performance score is obviously superior to the one from the sequential calibration (red line on Figure \ref{fig:operator_mutation_score_atmlevel}).
+The resulting performance score \citep[CRPSS = skill score of the CRPS, see][]{Brown1974} is obviously superior to the one from the sequential calibration (red line on Figure \ref{fig:operator_mutation_score_atmlevel}).
 For most options, it is also slightly better than the results from the optimization without selection of the pressure levels (blue line).
@@
 However, even though the results show a certain variability, most of them present very good performance scores, despite different parameters of the AM.
-As illustrated in \cite{Horton2016}, the surface response of the parameters space of the AM is rather gentle in certain regions, meaning it allows for different values of some parameters without significantly impacting the performance score.
 
@@
 
-Next, we added a second level of analogy on moisture variables (Figure \ref{fig:operator_mutation_score_r2}).
-The optimizer had to optimize both levels of analogy simultaneously.
+Next, we added a second level of analogy (Figure \ref{fig:operator_mutation_score_r2}) on moisture variables \citep[see][]{Bontron2004, Horton2016}.
+GAs had to optimize both levels of analogy simultaneously.
 Once again, despite the difficulty to optimize simultaneously both levels of analogy, the results were better than the sequential calibration (red line on Figure \ref{fig:operator_mutation_score_r2}).
-And finally, we added a preselection on air temperature instead of the fixed calendar window, as proposed by \cite{BenDaoud2010}.
-The results show generally higher scores (Figure \ref{fig:operator_mutation_score_r4}), demonstrating the success of the optimizer to take advantage of this new degree of liberty, and its capacity to handle optimization of 3 analogy levels jointly.
+And finally, we added a preselection on air temperature instead of the fixed calendar window, as proposed by \cite{BenDaoud2015}.
+The results show generally higher scores (Figure \ref{fig:operator_mutation_score_r4}), demonstrating the success of the optimizer to take advantage of this new degree of freedom, and its capacity to handle optimization of 3 analogy levels jointly.
 Again, the most relevant options are generally the same.
@@
 The number of required evaluations, however, can be quite substantial.
-The main disadvantage of the non-uniform mutation is the complexity of its parametrization, which is difficult to estimate a priori.
-These parameters must be carefully chosen to be in line with the evolution rate of the population, and are therefore dependent on the problem being treated.
+The main disadvantage of the non-uniform mutation is the number of parameters it requires, that are difficult to estimate a priori.
 We could observe that the $\omega$ coefficient does not influence performance.
@@
 The mutation rate was found to be important.
-The difficulty is that the optimal value seems to be very case-related.
-Indeed, by even changing the precipitation time series (ie optimizing for another subregion), but not the complexity of the AM, the optimal mutation rate changes, making it impossible to estimate in advance.
+The difficulty is that the optimal value may be case-related.
 
 	\item \textit{Chromosome of adaptive search radius} (new): unlike the previous one, our new operator is very robust, as it requires no option and is auto-adapting.
-It may be sometimes a little bit slower for simple problems, but does not require parametrization, which is an important advantage.
 It is interesting to notice that our insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).
-If one had to choose a single option for the mutation operator, we would recommend the chromosome of adaptive search radius, as it was proven effective and needs no parameter.
-
-	\item \textit{Multi-scale mutation} (new): finally, our multi-scale mutation, which also performs pretty well, requires one parameter, the mutation rate.
+If one had to choose a single option for the mutation operator, we would recommend this one, as it was proven effective and needs no parameter.
+
+	\item \textit{Multi-scale mutation} (new): finally, the multi-scale mutation, which also performs pretty well, requires one parameter, the mutation rate.
 However, it can also be difficult to estimate a correct value a priori.
@@
 In our application, the mutation operator has a leading effect and should be chosen with care.
-It may be wise to perform multiple optimizations and to consider these three operators in parallel in order to obtain results from algorithms that are either sometimes more efficient or more robust.
+It may be wise to perform multiple optimizations and to consider these three operators in parallel in order to obtain results from options that are either sometimes more efficient or more robust.
 It is interesting to note that the three best techniques incorporate a notion of search distance.
@@
 The analysis of the natural selection operator (Figure \ref{fig:operator_selectnat_score}) reveals a slight preference for the ratio-elitism compared to the tournament selection, but not so significant.
-Furthermore, the number of evaluations is similar.
 This operator, or at least the two assessed versions, do not appear to significantly influence the optimization performances.
@@
 with more degrees of freedom) requires a bigger population size.
-A rule of thumb based on different experiences (not shown here) is provided hereafter:
+A rule of thumb based on a limited number of case studies (not shown here) is provided hereafter:
 
 \begin{itemize}
-	\item $50<N\leqslant100$ for a very simple implementation of the AM (1 level of analogy with 2 pressure levels),
+	\item $N\approx100$ for a very simple implementations of the AM (1 level of analogy with 2 pressure levels),
 	\item $N\approx200$ for a bit more complex AM (1 level of analogy with 4 pressure levels, or 2 level of analogy with less pressure levels),
@@
 
-We didn't find any improvement with $N>500$, the results were even surprisingly of a lower quality.
-However, this relies on a limited number of case studies and cannot be generalized.
-It depends on the AM to optimize, and supposedly on the characteristics of the processes generating the precipitations in a given region.
-
 \begin{figure}[htb]
@@
 We also assessed the influence of the size of the IG (ratio of the total population) selected for mating (Figure \ref{fig:option_popratio_score}).
-It appears that a big ratio is not optimal.
-However, it does not appear that this parameter is critical to the quality of the optimizations, provided it is not too big.
+It does not appear that this parameter is critical to the quality of the optimizations, provided it is not too big.
 A value of 50~\% seems a wise choice.
@@
 \begin{itemize}
-	\item The optimization does not systematically converge to the global optimum  (but still often nearby), which is why we recommend doing several optimizations in parallel in order to compare the results, analyse the convergence, and keep the best.
-
-	\item The population size should be in accordance with the complexity of the AM to optimize: from 50 for the simple ones, up to 500 for the most complex AMs.
+	\item The population size should be in accordance with the complexity of the AM to optimize: from 100 for the simple ones, up to 500 for the most complex AMs.
 
@@
 	\item Mutation has a clearly dominant influence.
-Three mutation operators stand out, two of which we have developed: the non-uniform mutation, the multi-scale mutation, and the chromosome of adaptive search radius.
+Three mutation operators stand out, two of which are new: the non-uniform mutation, the multi-scale mutation, and the chromosome of adaptive search radius.
 The latter is the most robust as it has no controlling parameter.
@@
 
-In order to make an optimization of the AM with GAs, it may be wise to consider these three mutation operators in parallel.
-We would then combine algorithms that are sometimes faster to other that are more robust.
+The optimization does not systematically converge to the global optimum  (but still often nearby), which is why we recommend doing several optimizations in parallel in order to compare the results, analyze the convergence, and keep the best.
+It may be wise to consider the three mutation operators in parallel.
+It would then combine algorithms that are sometimes faster and other that are more robust.
 In order to be confident in the optimized AMs, we propose using a set of the following mutation operators:
@@
 Given the large number of existing operators and options, we had to evaluate systematically multiple variants to identify which operators are important, and which variant works best for the AM.
-We could thus identify that the mutation operator is a key element for our application, and provided new variants that were found to be efficient, such as the chromosome of adaptive search radius that seems to be very reliable (no control parameter) and efficient.
+We could thus identify that the mutation operator is a key element for our application, and provided new variants that were found to be efficient, such as the chromosome of adaptive search radius that is very robust (no control parameter).
 Recommendations were established for a relevant use of GAs for the optimization of AMs.

### 2015-11-19 Optimization case study - Journal of Hydrology/template.tex
Simplification of the pressure levels tables.

@@
 \end{equation}
-where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points in the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
+where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points of the grid describing the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
 The differences are processed separately in both directions.
@@
 	\footnotesize
-	\caption{Atmospheric levels automatically selected for the z4 method at the different subregions.}
+	\caption{Pressure levels ($\sim$) automatically selected for the z4 method at the different subregions.}
 	\begin{center}
@@
 			\hline 
-			1  & Z &   &   &   & Z &   &   & ZZ \\
-			2  & Z &   &   &   & Z &   &   & ZZ \\
-			3  & Z &   &   &   & Z &   &   & ZZ \\
-			4  & Z &   &   &   & Z &   &   & ZZ \\
-			5  &   &   & Z &   & Z &   &   & ZZ \\
-			6  &   &   & Z &   & Z &   &   & ZZ \\
-			7  &   &   & Z &   & Z &   &   & ZZ \\
-			8  &   &   & Z &   & Z &   &   & ZZ \\
-			9  &   &   & Z &   & Z &   &   & ZZ \\
-			10 &   &   &   & Z & Z &   &   & ZZ \\
+			1  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
+			2  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
+			3  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
+			4  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
+			5  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
+			6  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
+			7  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
+			8  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
+			9  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
+			10 &   &   &   & $\sim$ & $\sim$ &   &   & $\sim \sim$ \\
 			\hline 
@@
 	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation of the z4-hi2 method, at the different subregions.}
+	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the z4-hi2 method, at the different subregions.}
 	\begin{center}
@@
 			\hline 
-			1  & Z &   & Z &   &   & Z &   & Z \\
-			2  & Z &   &   &   & Z & Z &   & Z \\
-			3  & Z &   &   &   & Z & Z & Z &   \\
-			4  &   &   & Z &   & Z & Z &   & Z \\
-			5  &   & Z &   &   & Z &   & ZZ &   \\
-			6  &   & Z &   &   & Z & Z &   & Z \\
-			7  &   & Z &   &   & Z & Z &   & Z \\
-			8  &   &   & Z &   & Z &   & ZZ &   \\
-			9  &   & Z &   &   & Z & Z & Z &   \\
-			10 &   & Z &   &   & Z & Z &   & Z \\
+			1  & $\sim$ &   & $\sim$ &   & $\bullet \bullet$  & $\sim$ &   & $\sim$ \\
+			2  & $\sim$ &   &   &   & $\sim \bullet \bullet$ & $\sim$ &   & $\sim$ \\
+			3  & $\sim$ &   &   &   & $\sim \bullet \bullet$ & $\sim$ & $\sim$ &   \\
+			4  &   &   & $\sim$ & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
+			5  &   & $\sim$ &   &   & $\sim \bullet \bullet$ &   & $\sim \sim$ &   \\
+			6  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
+			7  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
+			8  &   &   & $\sim$ & $\bullet$ & $\sim \bullet$ &   & $\sim \sim$ &   \\
+			9  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ & $\sim$ &   \\
+			10 &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
 			\hline 
@@
 	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of moisture of the z4-hi2 method, at the different subregions.}
+	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the z4-hi4 method, at the different subregions.}
 	\begin{center}
@@
 			\hline 
-			1  &   &   &   &   & HH &   &   &   \\
-			2  &   &   &   &   & HH &   &   &   \\
-			3  &   &   &   &   & HH &   &   &   \\
-			4  &   &   &   & H & H &   &   &   \\
-			5  &   &   &   &   & HH &   &   &   \\
-			6  &   &   &   & H & H &   &   &   \\
-			7  &   &   &   & H & H &   &   &   \\
-			8  &   &   &   & H & H &   &   &   \\
-			9  &   &   &   & H & H &   &   &   \\
-			10 &   &   &   & H & H &   &   &   \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_z4_hi2_H}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation of the z4-hi4 method, at the different subregions.}
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
-			\hline 
-			1  &   & Z & Z &   &   & Z &   & Z \\
-			2  &   & Z &   &   & ZZ &   &   & Z \\
-			3  &   & Z &   &   & Z & Z & Z &   \\
-			4  &   &   & Z &   & Z & Z &   & Z \\
-			5  &   & Z & Z &   &   & Z &   & Z \\
-			6  &   & Z & Z &   &   & Z &   & Z \\
-			7  &   & Z &   &   & ZZ &   &   & Z \\
-			8  &   &   & Z & Z &   & Z &   & Z \\
-			9  &   & Z &   &   & Z & Z & Z &   \\
-			10 &   & Z & Z &   &   & ZZ &   &   \\
+			1  &   & $\sim$ & $\sim \bullet$ &   & $\bullet \bullet$ & $\sim \bullet$ &   & $\sim$ \\
+			2  &   & $\sim$ &   & $\bullet$ & $\sim \sim \bullet \bullet$ & $\bullet$ &   & $\sim$ \\
+			3  &   & $\sim$ &   & $\bullet$ & $\sim \bullet \bullet \bullet$ & $\sim$ & $\sim$ &   \\
+			4  &   &   & $\sim$ & $\bullet \bullet$ & $\sim \bullet \bullet$ & $\sim$ &   & $\sim$ \\
+			5  &   & $\sim$ & $\sim$ & $\bullet \bullet$ & $\bullet \bullet$ & $\sim$ &   & $\sim$ \\
+			6  &   & $\sim$ & $\sim$ & $\bullet \bullet$ & $\bullet$ & $\sim \bullet$ &   & $\sim$ \\
+			7  &   & $\sim$ &   & $\bullet \bullet$ & $\sim \sim \bullet$ & $\bullet$ &   & $\sim$ \\
+			8  &   &   & $\sim$ & $\sim \bullet \bullet$ & $\bullet$ & $\sim \bullet$ &   & $\sim$ \\
+			9  &   & $\sim$ &  $\bullet$ & $\bullet$ & $\sim \bullet$ & $\sim \bullet$ & $\sim$ &   \\
+			10 &   & $\sim$ & $\sim$ & $\bullet$ & $\bullet \bullet$ & $\sim \sim \bullet$ &   &   \\
 			\hline 
@@
 	\label{table:levels_GA_z4_hi4}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of moisture of the z4-hi4 method,at the different subregions.}
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
-			\hline 
-			1  &   &   & H &   & HH & H &   &   \\
-			2  &   &   &   & H & HH & H &   &   \\
-			3  &   &   &   & H & HHH &   &   &   \\
-			4  &   &   &   & HH & HH &   &   &   \\
-			5  &   &   &   & HH & HH &   &   &   \\
-			6  &   &   &   & HH & H & H &   &   \\
-			7  &   &   &   & HH & H & H &   &   \\
-			8  &   &   &   & HH & H & H &   &   \\
-			9  &   &   & H & H & H & H &   &   \\
-			10 &   &   &   & H & HH & H &   &   \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_z4_hi4_H}
 \end{table}
@@
 	\centerline{\includegraphics[width=7.9cm]{figures/figure_evolution.pdf}}
-	\caption{Example of the best individuals evolution of 8 independent optimizations.}
+	\caption{Example of the evolution of the performance score of the best individual over 8 independent optimizations.}
 	\label{fig:evolution}

### 2015-11-19 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Changing for the Journal of Hydrology template.

--- 2015-11-19 Optimization case study - Journal of Hydrology/template.tex
@@
-%% Version 4.3.2, 25 August 2014
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Template.tex --  LaTeX-based template for submissions to the 
-% American Meteorological Society
-%
-% Template developed by Amy Hendrickson, 2013, TeXnology Inc., 
-% amyh@texnology.com, http://www.texnology.com
-% following earlier work by Brian Papa, American Meteorological Society
-%
-% Email questions to latex@ametsoc.org.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PREAMBLE
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Start with one of the following:
-% DOUBLE-SPACED VERSION FOR SUBMISSION TO THE AMS
-%\documentclass{ametsoc}
-
-% TWO-COLUMN JOURNAL PAGE LAYOUT---FOR AUTHOR USE ONLY
-\documentclass[twocol]{ametsoc}
+\documentclass[5p]{elsarticle}
+%\documentclass[review]{elsarticle}
+
+\usepackage{lineno,hyperref}
+\modulolinenumbers[5]
+
+\journal{Journal of Hydrology}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% To be entered only if twocol option is used
-
-\journal{jcli}
-
-%  Please choose a journal abbreviation to use above from the following list:
-% 
-%   jamc     (Journal of Applied Meteorology and Climatology)
-%   jtech     (Journal of Atmospheric and Oceanic Technology)
-%   jhm      (Journal of Hydrometeorology)
-%   jpo     (Journal of Physical Oceanography)
-%   jas      (Journal of Atmospheric Sciences)	
-%   jcli      (Journal of Climate)
-%   mwr      (Monthly Weather Review)
-%   wcas      (Weather, Climate, and Society)
-%   waf       (Weather and Forecasting)
-%   bams (Bulletin of the American Meteorological Society)
-%   ei    (Earth Interactions)
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Citations should be of the form ``author year''  not ``author, year''
-\bibpunct{(}{)}{;}{a}{}{,}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%% To be entered by author:
-
-%% May use \\ to break lines in title:
+%%%%%%%%%%%%%%%%%%%%%%%
+%% Elsevier bibliography styles
+%%%%%%%%%%%%%%%%%%%%%%%
+%% To change the style, put a % in front of the second line of the current style and
+%% remove the % from the second line of the style you would like to use.
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Numbered
+%\bibliographystyle{model1-num-names}
+
+%% Numbered without titles
+%\bibliographystyle{model1a-num-names}
+
+%% Harvard
+%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
+
+%% Vancouver numbered
+%\usepackage{numcompress}\bibliographystyle{model3-num-names}
+
+%% Vancouver name/year
+\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
+
+%% APA style
+%\bibliographystyle{model5-names}\biboptions{authoryear}
+
+%% AMA style
+%\usepackage{numcompress}\bibliographystyle{model6-num-names}
+
+%% `Elsevier LaTeX' style
+%\bibliographystyle{elsarticle-num}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{document}
+
+\begin{frontmatter}
 
@@
 
-%%% Enter authors' names, as you see in this example:
-%%% Use \correspondingauthor{} and \thanks{Current Affiliation:...}
-%%% immediately following the appropriate author.
-%%%
-%%% Note that the \correspondingauthor{} command is NECESSARY.
-%%% The \thanks{} commands are OPTIONAL.
-
-    %\authors{Author One\correspondingauthor{Author One, 
-    % American Meteorological Society, 
-    % 45 Beacon St., Boston, MA 02108.}
-% and Author Two\thanks{Current affiliation: American Meteorological Society, 
-    % 45 Beacon St., Boston, MA 02108.}}
-
-\authors{Pascal Horton\correspondingauthor{Terranum, Rue de l'industrie 35 bis, 1030 Bussigny, Switzerland.}}
-
-%% Follow this form:
-    % \affiliation{American Meteorological Society, 
-    % Boston, Massachusetts.}
-
-\affiliation{University of Lausanne and Terranum, Lausanne, Switzerland}
-
-%% Follow this form:
-    %\email{latex@ametsoc.org}
-
-\email{pascal.horton@alumnil.unil.ch}
-
-%% If appropriate, add additional authors, different affiliations:
-    %\extraauthor{Extra Author}
-    %\extraaffil{Affiliation, City, State/Province, Country}
-
-\extraauthor{Michel Jaboyedoff}
-\extraaffil{University of Lausanne, Lausanne, Switzerland}
-
-%% May repeat for a additional authors/affiliations:
-
-%\extraauthor{}
-%\extraaffil{}
-
-\extraauthor{Charles Obled}
-\extraaffil{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% ABSTRACT
-%
-% Enter your abstract here
-% Abstracts should not exceed 250 words in length!
-%
-% For BAMS authors only: If your article requires a Capsule Summary, please place the capsule text at the end of your abstract
-% and identify it as the capsule. Example: This is the end of the abstract. (Capsule Summary) This is the capsule summary.
-
-\abstract{
+%% Group authors per affiliation:
+\author[unil,terranum]{Pascal Horton\corref{mycorrespondingauthor}}
+\cortext[mycorrespondingauthor]{Corresponding author}
+\ead{pascal.horton@alumnil.unil.ch}
+
+\author[unil]{Michel Jaboyedoff}
+\author[lthe]{Charles Obled}
+
+\address[unil]{University of Lausanne, Lausanne, Switzerland}
+\address[terranum]{Terranum LLC, Rue de l'industrie 35 bis, 1030 Bussigny, Switzerland}
+\address[lthe]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}
+
+\begin{abstract}
 The global optimization can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
@@
 We then applied the optimizer to the Rh\^{o}e catchment in the Swiss Alps and obtained coherent results which significantly improve the performance of the forecasting by analogy.
-The optimizer allowed us to calibrate jointly all parameters of the method and to add a weighting of the criteria per pressure level, as well as non-overlapping spatial windows.}
-\begin{document}
-
-%% Necessary!
-\maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% MAIN BODY OF PAPER
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-
-%% In all cases, if there is only one entry of this type within
-%% the higher level heading, use the star form: 
-%%
-% \section{Section title}
-% \subsection*{subsection}
-% text...
-% \section{Section title}
-
-%vs
-
-% \section{Section title}
-% \subsection{subsection one}
-% text...
-% \subsection{subsection two}
-% \section{Section title}
-
-%%%
-% \section{First primary heading}
-
-% \subsection{First secondary heading}
-
-% \subsubsection{First tertiary heading}
-
-% \paragraph{First quaternary heading}
+The optimizer allowed us to calibrate jointly all parameters of the method and to add a weighting of the criteria per pressure level, as well as non-overlapping spatial windows.
+\end{abstract}
+
+\begin{keyword}
+Precipitation\sep
+Analogue method\sep
+Optimization\sep
+Genetic algorithms\sep
+Alpine climate
+\end{keyword}
+
+\end{frontmatter}
+
+\linenumbers
 
@@
 
+\begin{table}[htbp]
+	\caption{Parameters of the reference method on the atmospheric circulation.}
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline Level & Variable & Hour & Criteria & Nb \\ 
+			\hline 
+			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & Z 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
+			& Z 500~hPa & 24~h & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:params_R1}
+\end{table}
+
 The $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day.
@@
 When we add a second level of analogy, we keep a higher number of analogues on the first level.
+
+\begin{table}[htbp]
+	\caption{Parameters of the reference method with moisture variables.}
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline Level & Variable & Hour & Criteria & Nb \\ 
+			\hline 
+			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & Z 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
+			& Z 500~hPa & 24~h & & \\ 
+			\hline
+			\multirow{2}{*}{2} & TPW * RH 850~hPa & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{30} \\
+			& TPW * RH 850~hPa & 24~h & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:params_R2}
+\end{table}
 
@@
 \begin{enumerate}
-	\setlength\itemsep{-4px}
 	\item Swiss Chablais
@@
 
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=7.9cm]{figures/figure_map.pdf}}
+	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland. (source: Swisstopo)}
+	\label{fig:map}
+\end{figure}
+
 The 48 years precipitation dataset (see section \ref{section_intro}.\ref{section_data}) was divided into a calibration period and a validation period.
@@
 
+\begin{table}[htbp]
+	\caption{Parameters of the z4 method (analogy on 4 levels of the atmospheric circulation) optimized for the Chablais subregion.
+The columns are the following: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
+	\begin{center}
+		\begin{tabular}{ccccccc}
+			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
+			\hline 
+			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & -2.5 - 15.0 \degree E & \multirow{2}{*}{32\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{28} \\
+			& & & 37.5 - 57.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z700} & \multirow{2}{*}{24~h} & 2.5 - 10.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
+			& & & 42.5 - 45.0 \degree N & & & \\ 
+			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{6~h} & -5.0 - 15.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
+			& & & 42.5 - 47.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
+			& & & 40.0 - 50.0 \degree N & & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:params_GA_z4}
+\end{table}
+
+\begin{table}[htbp]
+	\caption{Pressure levels ($\sim$) automatically selected for the z4 method at the different subregions.}
+	\begin{center}
+		\begin{tabular}{ccccccccc}
+			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
+			\hline 
+			1  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
+			2  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
+			3  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
+			4  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
+			5  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
+			6  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
+			7  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
+			8  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
+			9  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
+			10 &   &   &   & $\sim$ & $\sim$ &   &   & $\sim \sim$ \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:levels_GA_z4}
+\end{table}
+
+\begin{figure}[htb]
+	\centering
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_1.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_2.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_3.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_4.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_5.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_6.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_7.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_8.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_9.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_10.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4/legend.png}
+	\end{subfigure}
+	\caption{Optimized spatial windows for the z4 method (analogy of atmospheric circulation on 4 pressure levels).
+The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
+	\label{fig:spatial_windows_z4}
+\end{figure}
+
 The resulting CRPSS scores are provided in Table \ref{table:scores} and is in average 35.8 \% in calibration and 35.5 \% in validation.
@@
 
+\begin{table}[htbp]
+	\caption{CRPSS score (\%) of the three optimized methods.}
+	\begin{center}
+		\begin{tabular}{rrarara}
+			\hline 
+			\textbf{ID} & \multicolumn{2}{c}{\textbf{z4}} & \multicolumn{2}{c}{\textbf{z4-hi2}} & \multicolumn{2}{c}{\textbf{z4-hi4}} \\ 
+			\hline 
+			& calib & valid & calib & valid & calib & valid \\ 
+			\hline 
+			\textbf{1} & 40.3 & 38.5 & 45.5 & 43.8 & 45.9 & 43.6 \\ \hline
+			\textbf{2} & 37.8 & 34.9 & 42.4 & 40.8 & 42.9 & 41.3 \\ \hline
+			\textbf{3} & 36.6 & 33.9 & 41.4 & 39.0 & 41.8 & 39.5 \\ \hline
+			\textbf{4} & 31.2 & 30.8 & 36.1 & 36.4 & 36.8 & 37.1 \\ \hline
+			\textbf{5} & 34.4 & 36.5 & 38.6 & 41.4 & 39.2 & 41.8 \\ \hline
+			\textbf{6} & 37.0 & 39.9 & 41.0 & 44.5 & 41.9 & 44.6 \\ \hline
+			\textbf{7} & 30.0 & 30.1 & 33.8 & 34.6 & 34.4 & 34.8 \\ \hline
+			\textbf{8} & 37.7 & 40.1 & 40.7 & 43.1 & 41.2 & 43.3 \\ \hline
+			\textbf{9} & 33.1 & 30.0 & 38.4 & 36.6 & 38.7 & 36.3 \\ \hline
+			\textbf{10} & 40.0 & 40.0 & 42.6 & 42.9 & 43.3 & 43.2 \\ \hline
+			\textbf{av.} & \textbf{35.8} & \textbf{35.5} &\textbf{40.1} & \textbf{40.3} & \textbf{40.6} & \textbf{40.5} \\ \hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:scores}
+\end{table}
+
+\begin{table}[htbp]
+	\caption{Improvement (\%) of the CRPSS of the three methods.
+For z4, the improvement is relative to the reference method on the atmospheric circulation.
+For z4-hi2 and z4-hi4, the improvement is relative to the reference method on the circulation and moisture variables.}
+	\begin{center}
+		\begin{tabular}{rrarara}
+			\hline 
+			\textbf{ID} & \multicolumn{2}{c}{\textbf{z4}} & \multicolumn{2}{c}{\textbf{z4-hi2}} & \multicolumn{2}{c}{\textbf{z4-hi4}} \\ 
+			\hline 
+			& calib & valid & calib & valid & calib & valid \\ 
+			\hline 
+			\textbf{1} & 13.6 & 13.0 & 11.9 & 9.9 & 12.8 & 9.6 \\ \hline
+			\textbf{2} & 13.3 & 7.5 & 11.2 & 9.4 & 12.5 & 10.8 \\ \hline
+			\textbf{3} & 12.2 & 9.0 & 13.2 & 12.0 & 14.1 & 13.5 \\ \hline
+			\textbf{4} & 14.2 & 10.5 & 12.4 & 10.6 & 14.5 & 12.5 \\ \hline
+			\textbf{5} & 14.5 & 8.8 & 12.5 & 9.1 & 14.1 & 10.0 \\ \hline
+			\textbf{6} & 13.3 & 8.6 & 11.5 & 8.2 & 14.1 & 8.4 \\ \hline
+			\textbf{7} & 22.8 & 10.6 & 19.7 & 15.7 & 21.7 & 16.3 \\ \hline
+			\textbf{8} & 20.7 & 11.9 & 19.2 & 13.5 & 20.8 & 14.0 \\ \hline
+			\textbf{9} & 14.4 & 9.5 & 15.8 & 15.2 & 16.7 & 14.1 \\ \hline
+			\textbf{10} & 14.2 & 9.4 & 12.9 & 11.2 & 14.6 & 11.8 \\ \hline
+			\textbf{av.} & \textbf{15.3} & \textbf{9.9} &\textbf{14.0} & \textbf{11.5} & \textbf{15.6} & \textbf{12.1} \\ \hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:scores_diff}
+\end{table}
+
+\begin{table}[htbp]
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4 method.}
+	\begin{center}
+		\begin{tabular}{rrarara}
+			\hline 
+			\textbf{ID} & \multicolumn{2}{c}{\textbf{P\(\geq\)1 mm}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.1\(\cdot\)P10}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.5\(\cdot\)P10}} \\ 
+			\hline 
+			& calib & valid & calib & valid & calib & valid \\ 
+			\hline 
+			\textbf{1} & 10.2 & 9.4 & 8.5 & 7.9 & 17.0 & 14.2 \\ \hline 
+			\textbf{2} & 9.9 & 3.4 & 10.2 & 7.3 & 19.3 & 13.7 \\ \hline 
+			\textbf{3} & 13.3 & 10.5 & 13.3 & 10.9 & 19.7 & 9.7 \\ \hline 
+			\textbf{4} & 11.0 & 7.4 & 12.9 & 10.0 & 23.2 & 23.8 \\ \hline 
+			\textbf{5} & 8.6 & 4.2 & 10.9 & 6.2 & 25.2 & 23.8 \\ \hline 
+			\textbf{6} & 10.5 & 5.1 & 11.1 & 7.1 & 21.2 & 41.1 \\ \hline 
+			\textbf{7} & 24.3 & 12.4 & 33.1 & 26.0 & 71.2 & 104.3 \\ \hline 
+			\textbf{8} & 19.0 & 12.7 & 26.2 & 19.2 & 39.4 & 34.9 \\ \hline 
+			\textbf{9} & 12.4 & 6.8 & 13.8 & 9.9 & 24.9 & 48.1 \\ \hline 
+			\textbf{10} & 13.6 & 6.8 & 14.4 & 6.9 & 29.9 & 31.5 \\ \hline 
+			\textbf{av.} &\textbf{ 13.3} & \textbf{7.9} & \textbf{15.4} & \textbf{11.1} & \textbf{29.1} & \textbf{34.5} \\ \hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:scores_thresholds_z4}
+\end{table}
+
 To assess the cross-compatibility of the parameters, we applied those optimized for one subregion to the others.
 The resulting losses or gains of the CRPSS are displayed in Table \ref{table:crossing_z4_calib} for the calibration period and in Table \ref{table:crossing_z4_valid} for the validation period.
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4, calibration period.}
+	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4_calib.pdf}}
+	\label{table:crossing_z4_calib}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4, validation period.}
+	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4_valid.pdf}}
+	\label{table:crossing_z4_valid}
+\end{table}
 
@@
 
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Parameters of the z4-hi2 method (atmospheric circulation on 4 levels and moisture index on 2 levels), optimized for the Chablais subregion.
+Same conventions as Table \ref{table:params_GA_z4}.}
+	\begin{center}
+		\begin{tabular}{ccccccc}
+			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
+			\hline 
+			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & 0.0 - 15.0 \degree E & \multirow{2}{*}{23\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
+			& & & 42.5 - 55.0 \degree N & & & \\ 
+			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{25\%} & & \\ 
+			& & & 40.0 - 45.0 \degree N & & & \\ 
+			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
+			& & & 42.5 - 47.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
+			& & & 40.0 - 47.5 \degree N & & & \\ 
+			\hline 
+			\multirow{4}{*}{2} & TPW & \multirow{2}{*}{12~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{57\%} & \multirow{4}{*}{RMSE} & \multirow{4}{*}{25} \\
+			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
+			& TPW & \multirow{2}{*}{24~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{43\%} & & \\ 
+			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:params_GA_z4_hi2}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Parameters of the z4-hi4 method (atmospheric circulation on 4 levels and moisture index on 4 levels), optimized for the Chablais subregion.
+Same conventions as Table \ref{table:params_GA_z4}.}
+	\begin{center}
+		\begin{tabular}{ccccccc}
+			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
+			\hline 
+			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{8}{*}{1} &  \multirow{2}{*}{Z400} & \multirow{2}{*}{6~h} & -5.0 - 12.5 \degree E & \multirow{2}{*}{20\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
+			& & & 45.0 - 52.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
+			& & & 40.0 - 45.0 \degree N & & & \\ 
+			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
+			& & & 42.5 - 47.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
+			& & & 40.0 - 47.5 \degree N & & & \\ 
+			\hline 
+			\multirow{8}{*}{2} & TPW & \multirow{2}{*}{24~h} & 7.5 - 10.0 \degree E & \multirow{2}{*}{27\%} & \multirow{8}{*}{RMSE} & \multirow{8}{*}{25} \\
+			& *RH500 & & 45.0 - 47.5 \degree N & & & \\ 
+			& TPW & \multirow{2}{*}{12~h} & 5.0 - 7.5 \degree E & \multirow{2}{*}{41\%} & & \\ 
+			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
+			& TPW & \multirow{2}{*}{18~h} & 0.0 - 7.5 \degree E & \multirow{2}{*}{19\%} & & \\ 
+			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
+			& TPW & \multirow{2}{*}{24~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{13\%} & & \\ 
+			& *RH850 & & 45.0 - 47.5 \degree N & & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:params_GA_z4_hi4}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the z4-hi2 method, at the different subregions.}
+	\begin{center}
+		\begin{tabular}{ccccccccc}
+			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
+			\hline 
+			1  & $\sim$ &   & $\sim$ &   & $\bullet \bullet$  & $\sim$ &   & $\sim$ \\
+			2  & $\sim$ &   &   &   & $\sim \bullet \bullet$ & $\sim$ &   & $\sim$ \\
+			3  & $\sim$ &   &   &   & $\sim \bullet \bullet$ & $\sim$ & $\sim$ &   \\
+			4  &   &   & $\sim$ & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
+			5  &   & $\sim$ &   &   & $\sim \bullet \bullet$ &   & $\sim \sim$ &   \\
+			6  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
+			7  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
+			8  &   &   & $\sim$ & $\bullet$ & $\sim \bullet$ &   & $\sim \sim$ &   \\
+			9  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ & $\sim$ &   \\
+			10 &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:levels_GA_z4_hi2}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the z4-hi4 method, at the different subregions.}
+	\begin{center}
+		\begin{tabular}{ccccccccc}
+			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
+			\hline 
+			1  &   & $\sim$ & $\sim \bullet$ &   & $\bullet \bullet$ & $\sim \bullet$ &   & $\sim$ \\
+			2  &   & $\sim$ &   & $\bullet$ & $\sim \sim \bullet \bullet$ & $\bullet$ &   & $\sim$ \\
+			3  &   & $\sim$ &   & $\bullet$ & $\sim \bullet \bullet \bullet$ & $\sim$ & $\sim$ &   \\
+			4  &   &   & $\sim$ & $\bullet \bullet$ & $\sim \bullet \bullet$ & $\sim$ &   & $\sim$ \\
+			5  &   & $\sim$ & $\sim$ & $\bullet \bullet$ & $\bullet \bullet$ & $\sim$ &   & $\sim$ \\
+			6  &   & $\sim$ & $\sim$ & $\bullet \bullet$ & $\bullet$ & $\sim \bullet$ &   & $\sim$ \\
+			7  &   & $\sim$ &   & $\bullet \bullet$ & $\sim \sim \bullet$ & $\bullet$ &   & $\sim$ \\
+			8  &   &   & $\sim$ & $\sim \bullet \bullet$ & $\bullet$ & $\sim \bullet$ &   & $\sim$ \\
+			9  &   & $\sim$ &  $\bullet$ & $\bullet$ & $\sim \bullet$ & $\sim \bullet$ & $\sim$ &   \\
+			10 &   & $\sim$ & $\sim$ & $\bullet$ & $\bullet \bullet$ & $\sim \sim \bullet$ &   &   \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:levels_GA_z4_hi4}
+\end{table}
+
+\begin{figure}[htb]
+	\centering
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_1.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_2.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_3.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_4.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_5.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_6.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_7.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_8.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_9.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_10.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/legend.png}
+	\end{subfigure}
+	\caption{Optimized spatial windows for the z4-hi2 method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 2 pressure levels).
+The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
+	\label{fig:spatial_windows_z4-hi2}
+\end{figure}
+
+\begin{figure}[htb]
+	\centering
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_1.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_2.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_3.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_4.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_5.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_6.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_7.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_8.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_9.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_10.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/legend.png}
+	\end{subfigure}
+	\caption{Optimized spatial windows for the z4-hi4 method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 4 pressure levels).
+The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
+	\label{fig:spatial_windows_z4-hi4}
+\end{figure}
+
 The CRPSS scores of the optimized methods are provided in Table \ref{table:scores} and amounts to slightly more than 40 \% for both methods and for both periods.
@@
 
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi2 method.}
+	\begin{center}
+		\begin{tabular}{rrarara}
+			\hline 
+			\textbf{ID} & \multicolumn{2}{c}{\textbf{P\(\geq\)1 mm}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.1\(\cdot\)P10}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.5\(\cdot\)P10}} \\ 
+			\hline 
+			& calib & valid & calib & valid & calib & valid \\ 
+			\hline 
+			\textbf{1} & 12.6 & 9.3 & 12.4 & 9.7 & 15.8 & 11.0 \\ \hline 
+			\textbf{2} & 10.4 & 7.7 & 11.2 & 10.5 & 18.9 & 16.6 \\ \hline 
+			\textbf{3} & 14.5 & 11.6 & 14.1 & 11.4 & 18.7 & 14.6 \\ \hline 
+			\textbf{4} & 11.4 & 9.4 & 11.5 & 11.6 & 14.9 & 22.7 \\ \hline 
+			\textbf{5} & 11.8 & 8.0 & 12.2 & 8.9 & 12.0 & 12.8 \\ \hline 
+			\textbf{6} & 11.3 & 7.1 & 11.2 & 8.0 & 15.3 & 29.1 \\ \hline 
+			\textbf{7} & 20.5 & 15.5 & 25.2 & 24.0 & 43.0 & 79.5 \\ \hline
+			\textbf{8} & 19.3 & 15.7 & 23.1 & 18.6 & 25.2 & 31.7 \\ \hline 
+			\textbf{9} & 17.0 & 15.4 & 17.4 & 16.5 & 23.7 & 39.4 \\ \hline 
+			\textbf{10} & 12.9 & 9.6 & 13.8 & 11.1 & 28.5 & 32.1 \\ \hline 
+			\textbf{av.} &\textbf{14.2} & \textbf{10.9} & \textbf{15.2} & \textbf{13.0} & \textbf{21.6} & \textbf{28.9} \\ \hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:scores_thresholds_z4-hi2}
+\end{table}
+
+\begin{table}[htbp]
+	\footnotesize
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi4 method.}
+	\begin{center}
+		\begin{tabular}{rrarara}
+			\hline 
+			\textbf{ID} & \multicolumn{2}{c}{\textbf{P\(\geq\)1 mm}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.1\(\cdot\)P10}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.5\(\cdot\)P10}} \\ 
+			\hline 
+			& calib & valid & calib & valid & calib & valid \\ 
+			\hline 
+			\textbf{1} & 21.2 & 17.9 & 13.4 & 9.3 & 17.8 & 13.3 \\ \hline 
+			\textbf{2} & 12.6 & 8.9 & 9.5 & 10.0 & 16.7 & 15.6 \\ \hline 
+			\textbf{3} & 17.0 & 16.1 & 14.0 & 12.4 & 21.3 & 15.9 \\ \hline 
+			\textbf{4} & 9.4 & 6.1 & 13.3 & 12.4 & 19.8 & 22.7 \\ \hline 
+			\textbf{5} & 16.4 & 8.7 & 13.3 & 9.9 & 15.5 & 19.8 \\ \hline 
+			\textbf{6} & 22.6 & 12.2 & 11.9 & 6.7 & 17.0 & 26.9 \\ \hline 
+			\textbf{7} & 14.6 & 4.9 & 24.7 & 23.5 & 42.7 & 87.6 \\ \hline 
+			\textbf{8} & 21.8 & 21.6 & 25.7 & 19.3 & 32.3 & 26.6 \\ \hline 
+			\textbf{9} & 20.2 & 18.9 & 17.4 & 14.2 & 24.5 & 33.9 \\ \hline 
+			\textbf{10} & 21.7 & 14.8 & 14.8 & 11.7 & 29.2 & 29.1 \\ \hline 
+			\textbf{av.} &\textbf{17.7} & \textbf{13.0} & \textbf{15.8} & \textbf{12.9} & \textbf{23.7} & \textbf{29.2} \\ \hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:scores_thresholds_z4-hi4}
+\end{table}
+
 The parameters cross-compatibility has also been assessed for the methods with moisture variables, and are shown in Tables \ref{table:crossing_z4-hi2_calib} and \ref{table:crossing_z4-hi2_valid} for the method z4-hi2, and Tables \ref{table:crossing_z4-hi4_calib} and \ref{table:crossing_z4-hi4_valid} for z4-hi4.
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, calibration period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_calib.pdf}}
+	\label{table:crossing_z4-hi2_calib}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, validation period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_valid.pdf}}
+	\label{table:crossing_z4-hi2_valid}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi4, calibration period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_calib.pdf}}
+	\label{table:crossing_z4-hi4_calib}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi4, validation period.}
+	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_valid.pdf}}
+	\label{table:crossing_z4-hi4_valid}
+\end{table}
 
@@
 
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=7.9cm]{figures/figure_levels_weights.pdf}}
+	\caption{Optimized weighting for the pressure levels of the z4 method.}
+	\label{fig:levels_weights}
+\end{figure}
+
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=7.9cm]{figures/figure_levels_weights_average.pdf}}
+	\caption{Averaged weighting for the pressure levels of the circulation analogy of the three methods.}
+	\label{fig:levels_weights_average}
+\end{figure}
+
 GAs are very useful to optimize complex variants of the analogue method, and to assess new degrees of freedom that were not available so far.
@@
 
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=7.9cm]{figures/figure_evolution.pdf}}
+	\caption{Example of the evolution of the performance score of the best individual over 8 independent optimizations.}
+	\label{fig:evolution}
+\end{figure}
+
 We tried to optimize the preselection period (the 4-months window) jointly with the other parameters, but we did not get improvement.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% ACKNOWLEDGMENTS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-\acknowledgments
+\section*{Acknowledgments}
 Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% APPENDIXES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% Use \appendix if there is only one appendix.
-%\appendix
-
-% Use \appendix[A], \appendix}[B], if you have multiple appendixes.
-%\appendix[A]
-
-%% Appendix title is necessary! For appendix title:
-%\appendixtitle{}
-
-%%% Appendix section numbering (note, skip \section and begin with \subsection)
-% \subsection{First primary heading}
-
-% \subsubsection{First secondary heading}
-
-% \paragraph{First tertiary heading}
-
-%% Important!
-%\appendcaption{<appendix letter and number>}{<caption>} 
-%must be used for figures and tables in appendixes, e.g.,
-%
-%\begin{figure}
-%\noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
-%\appendcaption{A1}{Caption here.}
-%\end{figure}
-%
-% All appendix figures/tables should be placed in order AFTER the main figures/tables, i.e., tables, appendix tables, figures, appendix figures.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% REFERENCES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Make your BibTeX bibliography by using these commands:
-\bibliographystyle{ametsoc2014}
-% \bibliography{references}
+\section*{References}
+
 \bibliography{../_refs/_articles-optimization}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% TABLES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Enter tables at the end of the document, before figures.
-%%
-%
-%\begin{table}[t]
-%\caption{This is a sample table caption and table layout.  Enter as many tables as
-%  necessary at the end of your manuscript. Table from Lorenz (1963).}\label{t1}
-%\begin{center}
-%\begin{tabular}{ccccrrcrc}
-%\hline\hline
-%$N$ & $X$ & $Y$ & $Z$\\
-%\hline
-% 0000 & 0000 & 0010 & 0000 \\
-% 0005 & 0004 & 0012 & 0000 \\
-% 0010 & 0009 & 0020 & 0000 \\
-% 0015 & 0016 & 0036 & 0002 \\
-% 0020 & 0030 & 0066 & 0007 \\
-% 0025 & 0054 & 0115 & 0024 \\
-%\hline
-%\end{tabular}
-%\end{center}
-%\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Parameters of the reference method on the atmospheric circulation.}
-	\begin{center}
-		\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-			\hline 
-			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{2}{*}{1} & Z 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
-			& Z 500~hPa & 24~h & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_R1}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Parameters of the reference method with moisture variables.}
-	\begin{center}
-		\begin{tabular}{ccccc}
-			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-			\hline 
-			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{2}{*}{1} & Z 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
-			& Z 500~hPa & 24~h & & \\ 
-			\hline
-			\multirow{2}{*}{2} & TPW * RH 850~hPa & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{30} \\
-			& TPW * RH 850~hPa & 24~h & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_R2}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Parameters of the z4 method (analogy on 4 levels of the atmospheric circulation) optimized for the Chablais subregion.
-The columns are the following: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
-			\hline 
-			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & -2.5 - 15.0 \degree E & \multirow{2}{*}{32\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{28} \\
-			& & & 37.5 - 57.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z700} & \multirow{2}{*}{24~h} & 2.5 - 10.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
-			& & & 42.5 - 45.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{6~h} & -5.0 - 15.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
-			& & & 42.5 - 47.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
-			& & & 40.0 - 50.0 \degree N & & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_GA_z4}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Pressure levels ($\sim$) automatically selected for the z4 method at the different subregions.}
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
-			\hline 
-			1  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
-			2  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
-			3  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
-			4  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
-			5  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
-			6  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
-			7  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
-			8  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
-			9  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
-			10 &   &   &   & $\sim$ & $\sim$ &   &   & $\sim \sim$ \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_z4}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{CRPSS score (\%) of the three optimized methods.}
-	\begin{center}
-		\begin{tabular}{rrarara}
-			\hline 
-			\textbf{ID} & \multicolumn{2}{c}{\textbf{z4}} & \multicolumn{2}{c}{\textbf{z4-hi2}} & \multicolumn{2}{c}{\textbf{z4-hi4}} \\ 
-			\hline 
-			& calib & valid & calib & valid & calib & valid \\ 
-			\hline 
-			\textbf{1} & 40.3 & 38.5 & 45.5 & 43.8 & 45.9 & 43.6 \\ \hline
-			\textbf{2} & 37.8 & 34.9 & 42.4 & 40.8 & 42.9 & 41.3 \\ \hline
-			\textbf{3} & 36.6 & 33.9 & 41.4 & 39.0 & 41.8 & 39.5 \\ \hline
-			\textbf{4} & 31.2 & 30.8 & 36.1 & 36.4 & 36.8 & 37.1 \\ \hline
-			\textbf{5} & 34.4 & 36.5 & 38.6 & 41.4 & 39.2 & 41.8 \\ \hline
-			\textbf{6} & 37.0 & 39.9 & 41.0 & 44.5 & 41.9 & 44.6 \\ \hline
-			\textbf{7} & 30.0 & 30.1 & 33.8 & 34.6 & 34.4 & 34.8 \\ \hline
-			\textbf{8} & 37.7 & 40.1 & 40.7 & 43.1 & 41.2 & 43.3 \\ \hline
-			\textbf{9} & 33.1 & 30.0 & 38.4 & 36.6 & 38.7 & 36.3 \\ \hline
-			\textbf{10} & 40.0 & 40.0 & 42.6 & 42.9 & 43.3 & 43.2 \\ \hline
-			\textbf{av.} & \textbf{35.8} & \textbf{35.5} &\textbf{40.1} & \textbf{40.3} & \textbf{40.6} & \textbf{40.5} \\ \hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Improvement (\%) of the CRPSS of the three methods.
-For z4, the improvement is relative to the reference method on the atmospheric circulation.
-For z4-hi2 and z4-hi4, the improvement is relative to the reference method on the circulation and moisture variables.}
-	\begin{center}
-		\begin{tabular}{rrarara}
-			\hline 
-			\textbf{ID} & \multicolumn{2}{c}{\textbf{z4}} & \multicolumn{2}{c}{\textbf{z4-hi2}} & \multicolumn{2}{c}{\textbf{z4-hi4}} \\ 
-			\hline 
-			& calib & valid & calib & valid & calib & valid \\ 
-			\hline 
-			\textbf{1} & 13.6 & 13.0 & 11.9 & 9.9 & 12.8 & 9.6 \\ \hline
-			\textbf{2} & 13.3 & 7.5 & 11.2 & 9.4 & 12.5 & 10.8 \\ \hline
-			\textbf{3} & 12.2 & 9.0 & 13.2 & 12.0 & 14.1 & 13.5 \\ \hline
-			\textbf{4} & 14.2 & 10.5 & 12.4 & 10.6 & 14.5 & 12.5 \\ \hline
-			\textbf{5} & 14.5 & 8.8 & 12.5 & 9.1 & 14.1 & 10.0 \\ \hline
-			\textbf{6} & 13.3 & 8.6 & 11.5 & 8.2 & 14.1 & 8.4 \\ \hline
-			\textbf{7} & 22.8 & 10.6 & 19.7 & 15.7 & 21.7 & 16.3 \\ \hline
-			\textbf{8} & 20.7 & 11.9 & 19.2 & 13.5 & 20.8 & 14.0 \\ \hline
-			\textbf{9} & 14.4 & 9.5 & 15.8 & 15.2 & 16.7 & 14.1 \\ \hline
-			\textbf{10} & 14.2 & 9.4 & 12.9 & 11.2 & 14.6 & 11.8 \\ \hline
-			\textbf{av.} & \textbf{15.3} & \textbf{9.9} &\textbf{14.0} & \textbf{11.5} & \textbf{15.6} & \textbf{12.1} \\ \hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores_diff}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4 method.}
-	\begin{center}
-		\begin{tabular}{rrarara}
-			\hline 
-			\textbf{ID} & \multicolumn{2}{c}{\textbf{P\(\geq\)1 mm}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.1\(\cdot\)P10}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.5\(\cdot\)P10}} \\ 
-			\hline 
-			& calib & valid & calib & valid & calib & valid \\ 
-			\hline 
-			\textbf{1} & 10.2 & 9.4 & 8.5 & 7.9 & 17.0 & 14.2 \\ \hline 
-			\textbf{2} & 9.9 & 3.4 & 10.2 & 7.3 & 19.3 & 13.7 \\ \hline 
-			\textbf{3} & 13.3 & 10.5 & 13.3 & 10.9 & 19.7 & 9.7 \\ \hline 
-			\textbf{4} & 11.0 & 7.4 & 12.9 & 10.0 & 23.2 & 23.8 \\ \hline 
-			\textbf{5} & 8.6 & 4.2 & 10.9 & 6.2 & 25.2 & 23.8 \\ \hline 
-			\textbf{6} & 10.5 & 5.1 & 11.1 & 7.1 & 21.2 & 41.1 \\ \hline 
-			\textbf{7} & 24.3 & 12.4 & 33.1 & 26.0 & 71.2 & 104.3 \\ \hline 
-			\textbf{8} & 19.0 & 12.7 & 26.2 & 19.2 & 39.4 & 34.9 \\ \hline 
-			\textbf{9} & 12.4 & 6.8 & 13.8 & 9.9 & 24.9 & 48.1 \\ \hline 
-			\textbf{10} & 13.6 & 6.8 & 14.4 & 6.9 & 29.9 & 31.5 \\ \hline 
-			\textbf{av.} &\textbf{ 13.3} & \textbf{7.9} & \textbf{15.4} & \textbf{11.1} & \textbf{29.1} & \textbf{34.5} \\ \hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores_thresholds_z4}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4, calibration period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4_calib.pdf}}
-	\label{table:crossing_z4_calib}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4, validation period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4_valid.pdf}}
-	\label{table:crossing_z4_valid}
-\end{table}
-
-\clearpage
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Parameters of the z4-hi2 method (atmospheric circulation on 4 levels and moisture index on 2 levels), optimized for the Chablais subregion.
-Same conventions as Table \ref{table:params_GA_z4}.}
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
-			\hline 
-			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & 0.0 - 15.0 \degree E & \multirow{2}{*}{23\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
-			& & & 42.5 - 55.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{25\%} & & \\ 
-			& & & 40.0 - 45.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
-			& & & 42.5 - 47.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
-			& & & 40.0 - 47.5 \degree N & & & \\ 
-			\hline 
-			\multirow{4}{*}{2} & TPW & \multirow{2}{*}{12~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{57\%} & \multirow{4}{*}{RMSE} & \multirow{4}{*}{25} \\
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{24~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{43\%} & & \\ 
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_GA_z4_hi2}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Parameters of the z4-hi4 method (atmospheric circulation on 4 levels and moisture index on 4 levels), optimized for the Chablais subregion.
-Same conventions as Table \ref{table:params_GA_z4}.}
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
-			\hline 
-			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{8}{*}{1} &  \multirow{2}{*}{Z400} & \multirow{2}{*}{6~h} & -5.0 - 12.5 \degree E & \multirow{2}{*}{20\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
-			& & & 45.0 - 52.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
-			& & & 40.0 - 45.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
-			& & & 42.5 - 47.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
-			& & & 40.0 - 47.5 \degree N & & & \\ 
-			\hline 
-			\multirow{8}{*}{2} & TPW & \multirow{2}{*}{24~h} & 7.5 - 10.0 \degree E & \multirow{2}{*}{27\%} & \multirow{8}{*}{RMSE} & \multirow{8}{*}{25} \\
-			& *RH500 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{12~h} & 5.0 - 7.5 \degree E & \multirow{2}{*}{41\%} & & \\ 
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{18~h} & 0.0 - 7.5 \degree E & \multirow{2}{*}{19\%} & & \\ 
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{24~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{13\%} & & \\ 
-			& *RH850 & & 45.0 - 47.5 \degree N & & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_GA_z4_hi4}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the z4-hi2 method, at the different subregions.}
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
-			\hline 
-			1  & $\sim$ &   & $\sim$ &   & $\bullet \bullet$  & $\sim$ &   & $\sim$ \\
-			2  & $\sim$ &   &   &   & $\sim \bullet \bullet$ & $\sim$ &   & $\sim$ \\
-			3  & $\sim$ &   &   &   & $\sim \bullet \bullet$ & $\sim$ & $\sim$ &   \\
-			4  &   &   & $\sim$ & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
-			5  &   & $\sim$ &   &   & $\sim \bullet \bullet$ &   & $\sim \sim$ &   \\
-			6  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
-			7  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
-			8  &   &   & $\sim$ & $\bullet$ & $\sim \bullet$ &   & $\sim \sim$ &   \\
-			9  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ & $\sim$ &   \\
-			10 &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_z4_hi2}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the z4-hi4 method, at the different subregions.}
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
-			\hline 
-			1  &   & $\sim$ & $\sim \bullet$ &   & $\bullet \bullet$ & $\sim \bullet$ &   & $\sim$ \\
-			2  &   & $\sim$ &   & $\bullet$ & $\sim \sim \bullet \bullet$ & $\bullet$ &   & $\sim$ \\
-			3  &   & $\sim$ &   & $\bullet$ & $\sim \bullet \bullet \bullet$ & $\sim$ & $\sim$ &   \\
-			4  &   &   & $\sim$ & $\bullet \bullet$ & $\sim \bullet \bullet$ & $\sim$ &   & $\sim$ \\
-			5  &   & $\sim$ & $\sim$ & $\bullet \bullet$ & $\bullet \bullet$ & $\sim$ &   & $\sim$ \\
-			6  &   & $\sim$ & $\sim$ & $\bullet \bullet$ & $\bullet$ & $\sim \bullet$ &   & $\sim$ \\
-			7  &   & $\sim$ &   & $\bullet \bullet$ & $\sim \sim \bullet$ & $\bullet$ &   & $\sim$ \\
-			8  &   &   & $\sim$ & $\sim \bullet \bullet$ & $\bullet$ & $\sim \bullet$ &   & $\sim$ \\
-			9  &   & $\sim$ &  $\bullet$ & $\bullet$ & $\sim \bullet$ & $\sim \bullet$ & $\sim$ &   \\
-			10 &   & $\sim$ & $\sim$ & $\bullet$ & $\bullet \bullet$ & $\sim \sim \bullet$ &   &   \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_z4_hi4}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi2 method.}
-	\begin{center}
-		\begin{tabular}{rrarara}
-			\hline 
-			\textbf{ID} & \multicolumn{2}{c}{\textbf{P\(\geq\)1 mm}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.1\(\cdot\)P10}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.5\(\cdot\)P10}} \\ 
-			\hline 
-			& calib & valid & calib & valid & calib & valid \\ 
-			\hline 
-			\textbf{1} & 12.6 & 9.3 & 12.4 & 9.7 & 15.8 & 11.0 \\ \hline 
-			\textbf{2} & 10.4 & 7.7 & 11.2 & 10.5 & 18.9 & 16.6 \\ \hline 
-			\textbf{3} & 14.5 & 11.6 & 14.1 & 11.4 & 18.7 & 14.6 \\ \hline 
-			\textbf{4} & 11.4 & 9.4 & 11.5 & 11.6 & 14.9 & 22.7 \\ \hline 
-			\textbf{5} & 11.8 & 8.0 & 12.2 & 8.9 & 12.0 & 12.8 \\ \hline 
-			\textbf{6} & 11.3 & 7.1 & 11.2 & 8.0 & 15.3 & 29.1 \\ \hline 
-			\textbf{7} & 20.5 & 15.5 & 25.2 & 24.0 & 43.0 & 79.5 \\ \hline
-			\textbf{8} & 19.3 & 15.7 & 23.1 & 18.6 & 25.2 & 31.7 \\ \hline 
-			\textbf{9} & 17.0 & 15.4 & 17.4 & 16.5 & 23.7 & 39.4 \\ \hline 
-			\textbf{10} & 12.9 & 9.6 & 13.8 & 11.1 & 28.5 & 32.1 \\ \hline 
-			\textbf{av.} &\textbf{14.2} & \textbf{10.9} & \textbf{15.2} & \textbf{13.0} & \textbf{21.6} & \textbf{28.9} \\ \hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores_thresholds_z4-hi2}
-\end{table}
-
-\begin{table}[htbp]
-	\footnotesize
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi4 method.}
-	\begin{center}
-		\begin{tabular}{rrarara}
-			\hline 
-			\textbf{ID} & \multicolumn{2}{c}{\textbf{P\(\geq\)1 mm}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.1\(\cdot\)P10}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.5\(\cdot\)P10}} \\ 
-			\hline 
-			& calib & valid & calib & valid & calib & valid \\ 
-			\hline 
-			\textbf{1} & 21.2 & 17.9 & 13.4 & 9.3 & 17.8 & 13.3 \\ \hline 
-			\textbf{2} & 12.6 & 8.9 & 9.5 & 10.0 & 16.7 & 15.6 \\ \hline 
-			\textbf{3} & 17.0 & 16.1 & 14.0 & 12.4 & 21.3 & 15.9 \\ \hline 
-			\textbf{4} & 9.4 & 6.1 & 13.3 & 12.4 & 19.8 & 22.7 \\ \hline 
-			\textbf{5} & 16.4 & 8.7 & 13.3 & 9.9 & 15.5 & 19.8 \\ \hline 
-			\textbf{6} & 22.6 & 12.2 & 11.9 & 6.7 & 17.0 & 26.9 \\ \hline 
-			\textbf{7} & 14.6 & 4.9 & 24.7 & 23.5 & 42.7 & 87.6 \\ \hline 
-			\textbf{8} & 21.8 & 21.6 & 25.7 & 19.3 & 32.3 & 26.6 \\ \hline 
-			\textbf{9} & 20.2 & 18.9 & 17.4 & 14.2 & 24.5 & 33.9 \\ \hline 
-			\textbf{10} & 21.7 & 14.8 & 14.8 & 11.7 & 29.2 & 29.1 \\ \hline 
-			\textbf{av.} &\textbf{17.7} & \textbf{13.0} & \textbf{15.8} & \textbf{12.9} & \textbf{23.7} & \textbf{29.2} \\ \hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores_thresholds_z4-hi4}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, calibration period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_calib.pdf}}
-	\label{table:crossing_z4-hi2_calib}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, validation period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_valid.pdf}}
-	\label{table:crossing_z4-hi2_valid}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi4, calibration period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_calib.pdf}}
-	\label{table:crossing_z4-hi4_calib}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi4, validation period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_valid.pdf}}
-	\label{table:crossing_z4-hi4_valid}
-\end{table}
-
-\clearpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% FIGURES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Enter figures at the end of the document, after tables.
-%%
-%
-%\begin{figure}[t]
-%  \noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
-%  \caption{Enter the caption for your figure here.  Repeat as
-%  necessary for each of your figures. Figure from \protect\cite{Knutti2008}.}\label{f1}
-%\end{figure}
-
-\begin{figure}[htb]
-	\centerline{\includegraphics[width=7.9cm]{figures/figure_map.pdf}}
-	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland. (source: Swisstopo)}
-	\label{fig:map}
-\end{figure}
-
-\begin{figure}[htb]
-	\centering
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_1.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_2.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_3.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_4.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_5.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_6.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_7.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_8.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_9.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_10.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/legend.png}
-	\end{subfigure}
-	\caption{Optimized spatial windows for the z4 method (analogy of atmospheric circulation on 4 pressure levels).
-The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
-	\label{fig:spatial_windows_z4}
-\end{figure}
-
-\begin{figure}[htb]
-	\centering
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_1.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_2.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_3.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_4.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_5.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_6.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_7.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_8.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_9.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_10.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/legend.png}
-	\end{subfigure}
-	\caption{Optimized spatial windows for the z4-hi2 method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 2 pressure levels).
-The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
-	\label{fig:spatial_windows_z4-hi2}
-\end{figure}
-
-\begin{figure}[htb]
-	\centering
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_1.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_2.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_3.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_4.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_5.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_6.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_7.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_8.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_9.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_10.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/legend.png}
-	\end{subfigure}
-	\caption{Optimized spatial windows for the z4-hi4 method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 4 pressure levels).
-The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
-	\label{fig:spatial_windows_z4-hi4}
-\end{figure}
-
-\begin{figure}[htb]
-	\centerline{\includegraphics[width=7.9cm]{figures/figure_levels_weights.pdf}}
-	\caption{Optimized weighting for the pressure levels of the z4 method.}
-	\label{fig:levels_weights}
-\end{figure}
-
-\begin{figure}[htb]
-	\centerline{\includegraphics[width=7.9cm]{figures/figure_levels_weights_average.pdf}}
-	\caption{Averaged weighting for the pressure levels of the circulation analogy of the three methods.}
-	\label{fig:levels_weights_average}
-\end{figure}
-
-\begin{figure}[htb]
-	\centerline{\includegraphics[width=7.9cm]{figures/figure_evolution.pdf}}
-	\caption{Example of the evolution of the performance score of the best individual over 8 independent optimizations.}
-	\label{fig:evolution}
-\end{figure}
-
 \end{document}

### 2015-11-19 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Improving tables display.

@@
 \usepackage{subcaption}
-\usepackage{xcolor,colortbl}
-
-% After http://tex.stackexchange.com/questions/94799/how-do-i-color-table-columns-and-rows
-\newcommand{\mc}[2]{\multicolumn{#1}{c}{#2}}
-\definecolor{Gray}{gray}{0.85}
-\definecolor{LightCyan}{rgb}{0.88,1,1}
-\newcolumntype{a}{>{\columncolor{Gray}}c}
 
@@
 %% Harvard
-%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
+\bibliographystyle{model2-names}\biboptions{authoryear}
 
@@
 %% Vancouver name/year
-\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
+%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
 
@@
 	\caption{Parameters of the reference method on the atmospheric circulation.}
+	\footnotesize
 	\begin{center}
 		\begin{tabular}{ccccc}
-			\hline Level & Variable & Hour & Criteria & Nb \\ 
+			\hline
+			Level & Variable & Hour & Criteria & Nb \\ 
 			\hline 
@@
 	\caption{Parameters of the reference method with moisture variables.}
+	\footnotesize
 	\begin{center}
 		\begin{tabular}{ccccc}
-			\hline Level & Variable & Hour & Criteria & Nb \\ 
+			\hline 
+			Level & Variable & Hour & Criteria & Nb \\ 
 			\hline 
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=7.9cm]{figures/figure_map.pdf}}
+	\centerline{\includegraphics[width=\linewidth]{figures/figure_map.pdf}}
 	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland. (source: Swisstopo)}
@@
 The columns are the following: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
+	\footnotesize
 	\begin{center}
 		\begin{tabular}{ccccccc}
-			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
+			\hline L & V & H & D & W & C & N \\ 
 			\hline 
@@
 	\caption{Pressure levels ($\sim$) automatically selected for the z4 method at the different subregions.}
+	\footnotesize
 	\begin{center}
 		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
+			\hline ID & 300 & 400 & 500 & 600 & 700 & 850 & 925 & 1000 \\ 
 			\hline 
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_1.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_1.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_2.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_2.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_3.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_3.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_4.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_4.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_5.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_5.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_6.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_6.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_7.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_7.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_8.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_8.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_9.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_9.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/Spatial_windows_10.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_10.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4/legend.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/legend.png}
 	\end{subfigure}
@@
 	\caption{CRPSS score (\%) of the three optimized methods.}
+	\footnotesize
 	\begin{center}
-		\begin{tabular}{rrarara}
+		\begin{tabular}{ccccccc}
 			\hline 
-			\textbf{ID} & \multicolumn{2}{c}{\textbf{z4}} & \multicolumn{2}{c}{\textbf{z4-hi2}} & \multicolumn{2}{c}{\textbf{z4-hi4}} \\ 
-			\hline 
+			ID & \multicolumn{2}{c}{z4} & \multicolumn{2}{c}{z4-hi2} & \multicolumn{2}{c}{z4-hi4} \\ 
 			& calib & valid & calib & valid & calib & valid \\ 
 			\hline 
-			\textbf{1} & 40.3 & 38.5 & 45.5 & 43.8 & 45.9 & 43.6 \\ \hline
-			\textbf{2} & 37.8 & 34.9 & 42.4 & 40.8 & 42.9 & 41.3 \\ \hline
-			\textbf{3} & 36.6 & 33.9 & 41.4 & 39.0 & 41.8 & 39.5 \\ \hline
-			\textbf{4} & 31.2 & 30.8 & 36.1 & 36.4 & 36.8 & 37.1 \\ \hline
-			\textbf{5} & 34.4 & 36.5 & 38.6 & 41.4 & 39.2 & 41.8 \\ \hline
-			\textbf{6} & 37.0 & 39.9 & 41.0 & 44.5 & 41.9 & 44.6 \\ \hline
-			\textbf{7} & 30.0 & 30.1 & 33.8 & 34.6 & 34.4 & 34.8 \\ \hline
-			\textbf{8} & 37.7 & 40.1 & 40.7 & 43.1 & 41.2 & 43.3 \\ \hline
-			\textbf{9} & 33.1 & 30.0 & 38.4 & 36.6 & 38.7 & 36.3 \\ \hline
-			\textbf{10} & 40.0 & 40.0 & 42.6 & 42.9 & 43.3 & 43.2 \\ \hline
-			\textbf{av.} & \textbf{35.8} & \textbf{35.5} &\textbf{40.1} & \textbf{40.3} & \textbf{40.6} & \textbf{40.5} \\ \hline 
+			1 & 40.3 & 38.5 & 45.5 & 43.8 & 45.9 & 43.6 \\
+			2 & 37.8 & 34.9 & 42.4 & 40.8 & 42.9 & 41.3 \\
+			3 & 36.6 & 33.9 & 41.4 & 39.0 & 41.8 & 39.5 \\
+			4 & 31.2 & 30.8 & 36.1 & 36.4 & 36.8 & 37.1 \\
+			5 & 34.4 & 36.5 & 38.6 & 41.4 & 39.2 & 41.8 \\
+			6 & 37.0 & 39.9 & 41.0 & 44.5 & 41.9 & 44.6 \\
+			7 & 30.0 & 30.1 & 33.8 & 34.6 & 34.4 & 34.8 \\
+			8 & 37.7 & 40.1 & 40.7 & 43.1 & 41.2 & 43.3 \\
+			9 & 33.1 & 30.0 & 38.4 & 36.6 & 38.7 & 36.3 \\
+			10 & 40.0 & 40.0 & 42.6 & 42.9 & 43.3 & 43.2 \\
+			\hline
+			av. & 35.8 & 35.5 & 40.1 & 40.3 & 40.6 & 40.5 \\ 
+			\hline 
 		\end{tabular} 
@@
 For z4-hi2 and z4-hi4, the improvement is relative to the reference method on the circulation and moisture variables.}
+	\footnotesize
 	\begin{center}
-		\begin{tabular}{rrarara}
+		\begin{tabular}{ccccccc}
 			\hline 
-			\textbf{ID} & \multicolumn{2}{c}{\textbf{z4}} & \multicolumn{2}{c}{\textbf{z4-hi2}} & \multicolumn{2}{c}{\textbf{z4-hi4}} \\ 
-			\hline 
+			ID & \multicolumn{2}{c}{z4} & \multicolumn{2}{c}{z4-hi2} & \multicolumn{2}{c}{z4-hi4} \\ 
 			& calib & valid & calib & valid & calib & valid \\ 
 			\hline 
-			\textbf{1} & 13.6 & 13.0 & 11.9 & 9.9 & 12.8 & 9.6 \\ \hline
-			\textbf{2} & 13.3 & 7.5 & 11.2 & 9.4 & 12.5 & 10.8 \\ \hline
-			\textbf{3} & 12.2 & 9.0 & 13.2 & 12.0 & 14.1 & 13.5 \\ \hline
-			\textbf{4} & 14.2 & 10.5 & 12.4 & 10.6 & 14.5 & 12.5 \\ \hline
-			\textbf{5} & 14.5 & 8.8 & 12.5 & 9.1 & 14.1 & 10.0 \\ \hline
-			\textbf{6} & 13.3 & 8.6 & 11.5 & 8.2 & 14.1 & 8.4 \\ \hline
-			\textbf{7} & 22.8 & 10.6 & 19.7 & 15.7 & 21.7 & 16.3 \\ \hline
-			\textbf{8} & 20.7 & 11.9 & 19.2 & 13.5 & 20.8 & 14.0 \\ \hline
-			\textbf{9} & 14.4 & 9.5 & 15.8 & 15.2 & 16.7 & 14.1 \\ \hline
-			\textbf{10} & 14.2 & 9.4 & 12.9 & 11.2 & 14.6 & 11.8 \\ \hline
-			\textbf{av.} & \textbf{15.3} & \textbf{9.9} &\textbf{14.0} & \textbf{11.5} & \textbf{15.6} & \textbf{12.1} \\ \hline 
+			1 & 13.6 & 13.0 & 11.9 & 9.9 & 12.8 & 9.6 \\
+			2 & 13.3 & 7.5 & 11.2 & 9.4 & 12.5 & 10.8 \\
+			3 & 12.2 & 9.0 & 13.2 & 12.0 & 14.1 & 13.5 \\
+			4 & 14.2 & 10.5 & 12.4 & 10.6 & 14.5 & 12.5 \\
+			5 & 14.5 & 8.8 & 12.5 & 9.1 & 14.1 & 10.0 \\
+			6 & 13.3 & 8.6 & 11.5 & 8.2 & 14.1 & 8.4 \\
+			7 & 22.8 & 10.6 & 19.7 & 15.7 & 21.7 & 16.3 \\
+			8 & 20.7 & 11.9 & 19.2 & 13.5 & 20.8 & 14.0 \\
+			9 & 14.4 & 9.5 & 15.8 & 15.2 & 16.7 & 14.1 \\
+			10 & 14.2 & 9.4 & 12.9 & 11.2 & 14.6 & 11.8 \\
+			\hline
+			av. & 15.3 & 9.9 & 14.0 & 11.5 & 15.6 & 12.1 \\ 
+			\hline 
 		\end{tabular} 
@@
 	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4 method.}
+	\footnotesize
 	\begin{center}
-		\begin{tabular}{rrarara}
+		\begin{tabular}{ccccccc}
 			\hline 
-			\textbf{ID} & \multicolumn{2}{c}{\textbf{P\(\geq\)1 mm}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.1\(\cdot\)P10}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.5\(\cdot\)P10}} \\ 
-			\hline 
+			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\ 
 			& calib & valid & calib & valid & calib & valid \\ 
 			\hline 
-			\textbf{1} & 10.2 & 9.4 & 8.5 & 7.9 & 17.0 & 14.2 \\ \hline 
-			\textbf{2} & 9.9 & 3.4 & 10.2 & 7.3 & 19.3 & 13.7 \\ \hline 
-			\textbf{3} & 13.3 & 10.5 & 13.3 & 10.9 & 19.7 & 9.7 \\ \hline 
-			\textbf{4} & 11.0 & 7.4 & 12.9 & 10.0 & 23.2 & 23.8 \\ \hline 
-			\textbf{5} & 8.6 & 4.2 & 10.9 & 6.2 & 25.2 & 23.8 \\ \hline 
-			\textbf{6} & 10.5 & 5.1 & 11.1 & 7.1 & 21.2 & 41.1 \\ \hline 
-			\textbf{7} & 24.3 & 12.4 & 33.1 & 26.0 & 71.2 & 104.3 \\ \hline 
-			\textbf{8} & 19.0 & 12.7 & 26.2 & 19.2 & 39.4 & 34.9 \\ \hline 
-			\textbf{9} & 12.4 & 6.8 & 13.8 & 9.9 & 24.9 & 48.1 \\ \hline 
-			\textbf{10} & 13.6 & 6.8 & 14.4 & 6.9 & 29.9 & 31.5 \\ \hline 
-			\textbf{av.} &\textbf{ 13.3} & \textbf{7.9} & \textbf{15.4} & \textbf{11.1} & \textbf{29.1} & \textbf{34.5} \\ \hline 
+			1 & 10.2 & 9.4 & 8.5 & 7.9 & 17.0 & 14.2 \\ 
+			2 & 9.9 & 3.4 & 10.2 & 7.3 & 19.3 & 13.7 \\ 
+			3 & 13.3 & 10.5 & 13.3 & 10.9 & 19.7 & 9.7 \\ 
+			4 & 11.0 & 7.4 & 12.9 & 10.0 & 23.2 & 23.8 \\ 
+			5 & 8.6 & 4.2 & 10.9 & 6.2 & 25.2 & 23.8 \\ 
+			6 & 10.5 & 5.1 & 11.1 & 7.1 & 21.2 & 41.1 \\ 
+			7 & 24.3 & 12.4 & 33.1 & 26.0 & 71.2 & 104.3 \\ 
+			8 & 19.0 & 12.7 & 26.2 & 19.2 & 39.4 & 34.9 \\ 
+			9 & 12.4 & 6.8 & 13.8 & 9.9 & 24.9 & 48.1 \\ 
+			10 & 13.6 & 6.8 & 14.4 & 6.9 & 29.9 & 31.5 \\ 
+			\hline 
+			av. & 13.3 & 7.9 & 15.4 & 11.1 & 29.1 & 34.5 \\ 
+			\hline 
 		\end{tabular} 
@@
 \begin{table}[htbp]
-	\footnotesize
 	\caption{Parameters of the z4-hi2 method (atmospheric circulation on 4 levels and moisture index on 2 levels), optimized for the Chablais subregion.
 Same conventions as Table \ref{table:params_GA_z4}.}
+	\footnotesize
 	\begin{center}
 		\begin{tabular}{ccccccc}
-			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
+			\hline L & V & H & D & W & C & N \\ 
 			\hline 
@@
 \begin{table}[htbp]
-	\footnotesize
 	\caption{Parameters of the z4-hi4 method (atmospheric circulation on 4 levels and moisture index on 4 levels), optimized for the Chablais subregion.
 Same conventions as Table \ref{table:params_GA_z4}.}
+	\footnotesize
 	\begin{center}
 		\begin{tabular}{ccccccc}
-			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
+			\hline L & V & H & D & W & C & N \\ 
 			\hline 
@@
 \begin{table}[htbp]
+	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the z4-hi2 method, at the different subregions.}
 	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the z4-hi2 method, at the different subregions.}
 	\begin{center}
 		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
+			\hline ID & 300 & 400 & 500 & 600 & 700 & 850 & 925 & 1000 \\ 
 			\hline 
@@
 \begin{table}[htbp]
+	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the z4-hi4 method, at the different subregions.}
 	\footnotesize
-	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the z4-hi4 method, at the different subregions.}
 	\begin{center}
 		\begin{tabular}{ccccccccc}
-			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
+			\hline ID & 300 & 400 & 500 & 600 & 700 & 850 & 925 & 1000 \\ 
 			\hline 
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_1.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_1.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_2.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_2.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_3.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_3.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_4.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_4.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_5.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_5.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_6.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_6.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_7.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_7.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_8.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_8.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_9.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_9.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/Spatial_windows_10.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_10.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/legend.png}
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/legend.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_1.png}
+		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_1.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_2.png}
+		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_2.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_3.png}
+		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_3.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_4.png}
+		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_4.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_5.png}
+		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_5.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_6.png}
+		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_6.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_7.png}
+		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_7.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_8.png}
+		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_8.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_9.png}
+		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_9.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/Spatial_windows_10.png}
+		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_10.png}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/legend.png}
+		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/legend.png}
 	\end{subfigure}
@@
 \begin{table}[htbp]
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi2 method.}
 	\footnotesize
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi2 method.}
 	\begin{center}
-		\begin{tabular}{rrarara}
+		\begin{tabular}{ccccccc}
 			\hline 
-			\textbf{ID} & \multicolumn{2}{c}{\textbf{P\(\geq\)1 mm}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.1\(\cdot\)P10}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.5\(\cdot\)P10}} \\ 
-			\hline 
+			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\  
 			& calib & valid & calib & valid & calib & valid \\ 
 			\hline 
-			\textbf{1} & 12.6 & 9.3 & 12.4 & 9.7 & 15.8 & 11.0 \\ \hline 
-			\textbf{2} & 10.4 & 7.7 & 11.2 & 10.5 & 18.9 & 16.6 \\ \hline 
-			\textbf{3} & 14.5 & 11.6 & 14.1 & 11.4 & 18.7 & 14.6 \\ \hline 
-			\textbf{4} & 11.4 & 9.4 & 11.5 & 11.6 & 14.9 & 22.7 \\ \hline 
-			\textbf{5} & 11.8 & 8.0 & 12.2 & 8.9 & 12.0 & 12.8 \\ \hline 
-			\textbf{6} & 11.3 & 7.1 & 11.2 & 8.0 & 15.3 & 29.1 \\ \hline 
-			\textbf{7} & 20.5 & 15.5 & 25.2 & 24.0 & 43.0 & 79.5 \\ \hline
-			\textbf{8} & 19.3 & 15.7 & 23.1 & 18.6 & 25.2 & 31.7 \\ \hline 
-			\textbf{9} & 17.0 & 15.4 & 17.4 & 16.5 & 23.7 & 39.4 \\ \hline 
-			\textbf{10} & 12.9 & 9.6 & 13.8 & 11.1 & 28.5 & 32.1 \\ \hline 
-			\textbf{av.} &\textbf{14.2} & \textbf{10.9} & \textbf{15.2} & \textbf{13.0} & \textbf{21.6} & \textbf{28.9} \\ \hline 
+			1 & 12.6 & 9.3 & 12.4 & 9.7 & 15.8 & 11.0 \\
+			2 & 10.4 & 7.7 & 11.2 & 10.5 & 18.9 & 16.6 \\ 
+			3 & 14.5 & 11.6 & 14.1 & 11.4 & 18.7 & 14.6 \\ 
+			4 & 11.4 & 9.4 & 11.5 & 11.6 & 14.9 & 22.7 \\ 
+			5 & 11.8 & 8.0 & 12.2 & 8.9 & 12.0 & 12.8 \\ 
+			6 & 11.3 & 7.1 & 11.2 & 8.0 & 15.3 & 29.1 \\ 
+			7 & 20.5 & 15.5 & 25.2 & 24.0 & 43.0 & 79.5 \\
+			8 & 19.3 & 15.7 & 23.1 & 18.6 & 25.2 & 31.7 \\ 
+			9 & 17.0 & 15.4 & 17.4 & 16.5 & 23.7 & 39.4 \\ 
+			10 & 12.9 & 9.6 & 13.8 & 11.1 & 28.5 & 32.1 \\ 
+			\hline 
+			av. & 14.2 & 10.9 & 15.2 & 13.0 & 21.6 & 28.9 \\ 
+			\hline 
 		\end{tabular} 
@@
 \begin{table}[htbp]
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi4 method.}
 	\footnotesize
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi4 method.}
 	\begin{center}
-		\begin{tabular}{rrarara}
+		\begin{tabular}{ccccccc}
 			\hline 
-			\textbf{ID} & \multicolumn{2}{c}{\textbf{P\(\geq\)1 mm}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.1\(\cdot\)P10}} & \multicolumn{2}{c}{\textbf{P\(\geq\)0.5\(\cdot\)P10}} \\ 
-			\hline 
+			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\ 
 			& calib & valid & calib & valid & calib & valid \\ 
 			\hline 
-			\textbf{1} & 21.2 & 17.9 & 13.4 & 9.3 & 17.8 & 13.3 \\ \hline 
-			\textbf{2} & 12.6 & 8.9 & 9.5 & 10.0 & 16.7 & 15.6 \\ \hline 
-			\textbf{3} & 17.0 & 16.1 & 14.0 & 12.4 & 21.3 & 15.9 \\ \hline 
-			\textbf{4} & 9.4 & 6.1 & 13.3 & 12.4 & 19.8 & 22.7 \\ \hline 
-			\textbf{5} & 16.4 & 8.7 & 13.3 & 9.9 & 15.5 & 19.8 \\ \hline 
-			\textbf{6} & 22.6 & 12.2 & 11.9 & 6.7 & 17.0 & 26.9 \\ \hline 
-			\textbf{7} & 14.6 & 4.9 & 24.7 & 23.5 & 42.7 & 87.6 \\ \hline 
-			\textbf{8} & 21.8 & 21.6 & 25.7 & 19.3 & 32.3 & 26.6 \\ \hline 
-			\textbf{9} & 20.2 & 18.9 & 17.4 & 14.2 & 24.5 & 33.9 \\ \hline 
-			\textbf{10} & 21.7 & 14.8 & 14.8 & 11.7 & 29.2 & 29.1 \\ \hline 
-			\textbf{av.} &\textbf{17.7} & \textbf{13.0} & \textbf{15.8} & \textbf{12.9} & \textbf{23.7} & \textbf{29.2} \\ \hline 
+			1 & 21.2 & 17.9 & 13.4 & 9.3 & 17.8 & 13.3 \\ 
+			2 & 12.6 & 8.9 & 9.5 & 10.0 & 16.7 & 15.6 \\ 
+			3 & 17.0 & 16.1 & 14.0 & 12.4 & 21.3 & 15.9 \\ 
+			4 & 9.4 & 6.1 & 13.3 & 12.4 & 19.8 & 22.7 \\ 
+			5 & 16.4 & 8.7 & 13.3 & 9.9 & 15.5 & 19.8 \\ 
+			6 & 22.6 & 12.2 & 11.9 & 6.7 & 17.0 & 26.9 \\ 
+			7 & 14.6 & 4.9 & 24.7 & 23.5 & 42.7 & 87.6 \\ 
+			8 & 21.8 & 21.6 & 25.7 & 19.3 & 32.3 & 26.6 \\ 
+			9 & 20.2 & 18.9 & 17.4 & 14.2 & 24.5 & 33.9 \\ 
+			10 & 21.7 & 14.8 & 14.8 & 11.7 & 29.2 & 29.1 \\ 
+			\hline 
+			av. & 17.7 & 13.0 & 15.8 & 12.9 & 23.7 & 29.2 \\ 
+			\hline 
 		\end{tabular} 
@@
 	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, calibration period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_calib.pdf}}
+	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi2_calib.pdf}}
 	\label{table:crossing_z4-hi2_calib}
@@
 	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, validation period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi2_valid.pdf}}
+	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi2_valid.pdf}}
 	\label{table:crossing_z4-hi2_valid}
@@
 	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi4, calibration period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_calib.pdf}}
+	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi4_calib.pdf}}
 	\label{table:crossing_z4-hi4_calib}
@@
 	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi4, validation period.}
-	\centerline{\includegraphics[width=8.3cm]{figures/table_crossing_z4-hi4_valid.pdf}}
+	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi4_valid.pdf}}
 	\label{table:crossing_z4-hi4_valid}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=7.9cm]{figures/figure_levels_weights.pdf}}
+	\centerline{\includegraphics[width=\linewidth]{figures/figure_levels_weights.pdf}}
 	\caption{Optimized weighting for the pressure levels of the z4 method.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=7.9cm]{figures/figure_levels_weights_average.pdf}}
+	\centerline{\includegraphics[width=\linewidth]{figures/figure_levels_weights_average.pdf}}
 	\caption{Averaged weighting for the pressure levels of the circulation analogy of the three methods.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=7.9cm]{figures/figure_evolution.pdf}}
+	\centerline{\includegraphics[width=\linewidth]{figures/figure_evolution.pdf}}
 	\caption{Example of the evolution of the performance score of the best individual over 8 independent optimizations.}

### 2015-11-19 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Moving the figures at the end of the document.

@@
 
-\begin{figure}[htb]
-	\centerline{\includegraphics[width=\linewidth]{figures/figure_map.pdf}}
-	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland. (source: Swisstopo)}
-	\label{fig:map}
-\end{figure}
-
 The 48 years precipitation dataset (see section \ref{section_intro}.\ref{section_data}) was divided into a calibration period and a validation period.
@@
 
-\section{Optimization of the analogy of atmospheric circulation}
+\section{Optimization of the circulation analogy}
 
@@
 
-\begin{figure}[htb]
-	\centering
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_1.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_2.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_3.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_4.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_5.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_6.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_7.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_8.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_9.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_10.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/legend.png}
-	\end{subfigure}
-	\caption{Optimized spatial windows for the z4 method (analogy of atmospheric circulation on 4 pressure levels).
-The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
-	\label{fig:spatial_windows_z4}
-\end{figure}
-
 The resulting CRPSS scores are provided in Table \ref{table:scores} and is in average 35.8 \% in calibration and 35.5 \% in validation.
@@
 
-\begin{table}[htb]
+\begin{table}[htbp]
 	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4, calibration period.}
@@
 
-\begin{table}[htb]
+\begin{table}[htbp]
 	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4, validation period.}
@@
 
-\section{Optimization of the analogy with moisture variables}
+\section{Optimization of the moisture analogy}
 
@@
 Detailed examples are still provided for the Swiss Chablais subregion in Table \ref{table:params_GA_z4_hi2} for z4-hi2 and in Table \ref{table:params_GA_z4_hi4} for z4-hi4.
-The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_z4-hi2} for z4-hi2, along with the selected pressure levels for the circulation analogy (Table \ref{table:levels_GA_z4_hi2}) and the moisture analogy (Table \ref{table:levels_GA_z4_hi2_H}).
-Correspondingly, for the method z4-hi4, the spatial windows are shown in Figure \ref{fig:spatial_windows_z4-hi4} and the selected pressure levels are presented in Tables \ref{table:levels_GA_z4_hi4} and \ref{table:levels_GA_z4_hi4_H}.
+The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_z4-hi2} for z4-hi2, along with the selected pressure levels for both the circulation and the moisture analogy (Table \ref{table:levels_GA_z4_hi2}).
+Correspondingly, for the method z4-hi4, the spatial windows are shown in Figure \ref{fig:spatial_windows_z4-hi4} and the selected pressure levels are presented in Tables \ref{table:levels_GA_z4_hi4}.
 
@@
 
+The CRPSS scores of the optimized methods are provided in Table \ref{table:scores} and amounts to slightly more than 40 \% for both methods and for both periods.
+This results in a relative improvements that ranges from 11.5 \% to 15.6 \% compared to the reference method on the moisture analogy (Table \ref{table:scores_diff}).
+As for z4, the z4-hi2 and z4-hi4 methods present improvements of the forecast of significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
+The improvement are relatively similar for z4-hi2 (Table \ref{table:scores_thresholds_z4-hi2}) and z4-hi4 (Table \ref{table:scores_thresholds_z4-hi4}), with slightly superior scores for the latter on small precipitation (P\(\geq\)1 mm) and extremes (P\(\geq\)0.5\(\cdot\)P10).
+
+\begin{table}[htbp]
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi2 method.}
+	\footnotesize
+	\begin{center}
+		\begin{tabular}{ccccccc}
+			\hline 
+			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\  
+			& calib & valid & calib & valid & calib & valid \\ 
+			\hline 
+			1 & 12.6 & 9.3 & 12.4 & 9.7 & 15.8 & 11.0 \\
+			2 & 10.4 & 7.7 & 11.2 & 10.5 & 18.9 & 16.6 \\ 
+			3 & 14.5 & 11.6 & 14.1 & 11.4 & 18.7 & 14.6 \\ 
+			4 & 11.4 & 9.4 & 11.5 & 11.6 & 14.9 & 22.7 \\ 
+			5 & 11.8 & 8.0 & 12.2 & 8.9 & 12.0 & 12.8 \\ 
+			6 & 11.3 & 7.1 & 11.2 & 8.0 & 15.3 & 29.1 \\ 
+			7 & 20.5 & 15.5 & 25.2 & 24.0 & 43.0 & 79.5 \\
+			8 & 19.3 & 15.7 & 23.1 & 18.6 & 25.2 & 31.7 \\ 
+			9 & 17.0 & 15.4 & 17.4 & 16.5 & 23.7 & 39.4 \\ 
+			10 & 12.9 & 9.6 & 13.8 & 11.1 & 28.5 & 32.1 \\ 
+			\hline 
+			av. & 14.2 & 10.9 & 15.2 & 13.0 & 21.6 & 28.9 \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:scores_thresholds_z4-hi2}
+\end{table}
+
+\begin{table}[htbp]
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi4 method.}
+	\footnotesize
+	\begin{center}
+		\begin{tabular}{ccccccc}
+			\hline 
+			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\ 
+			& calib & valid & calib & valid & calib & valid \\ 
+			\hline 
+			1 & 21.2 & 17.9 & 13.4 & 9.3 & 17.8 & 13.3 \\ 
+			2 & 12.6 & 8.9 & 9.5 & 10.0 & 16.7 & 15.6 \\ 
+			3 & 17.0 & 16.1 & 14.0 & 12.4 & 21.3 & 15.9 \\ 
+			4 & 9.4 & 6.1 & 13.3 & 12.4 & 19.8 & 22.7 \\ 
+			5 & 16.4 & 8.7 & 13.3 & 9.9 & 15.5 & 19.8 \\ 
+			6 & 22.6 & 12.2 & 11.9 & 6.7 & 17.0 & 26.9 \\ 
+			7 & 14.6 & 4.9 & 24.7 & 23.5 & 42.7 & 87.6 \\ 
+			8 & 21.8 & 21.6 & 25.7 & 19.3 & 32.3 & 26.6 \\ 
+			9 & 20.2 & 18.9 & 17.4 & 14.2 & 24.5 & 33.9 \\ 
+			10 & 21.7 & 14.8 & 14.8 & 11.7 & 29.2 & 29.1 \\ 
+			\hline 
+			av. & 17.7 & 13.0 & 15.8 & 12.9 & 23.7 & 29.2 \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:scores_thresholds_z4-hi4}
+\end{table}
+
+The parameters cross-compatibility has also been assessed for the methods with moisture variables, and are shown in Tables \ref{table:crossing_z4-hi2_calib} and \ref{table:crossing_z4-hi2_valid} for the method z4-hi2, and Tables \ref{table:crossing_z4-hi4_calib} and \ref{table:crossing_z4-hi4_valid} for z4-hi4.
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, calibration period.}
+	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi2_calib.pdf}}
+	\label{table:crossing_z4-hi2_calib}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, validation period.}
+	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi2_valid.pdf}}
+	\label{table:crossing_z4-hi2_valid}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi4, calibration period.}
+	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi4_calib.pdf}}
+	\label{table:crossing_z4-hi4_calib}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi4, validation period.}
+	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi4_valid.pdf}}
+	\label{table:crossing_z4-hi4_valid}
+\end{table}
+
+\subsection{Analysis}
+
+When optimizing a method made of 2 levels of analogy, the introduction of moisture variables in the second level has an influence on the parameter values of the first level.
+This is first visible on the selection of the pressure levels for the circulation analogy, where the 1000~hPa that was previously systematically selected twice (Table \ref{table:levels_GA_z4}) is now less chosen (once or even not at all) for both za-hi2 (Table \ref{table:levels_GA_z4_hi2}) and za-hi4 (Table \ref{table:levels_GA_z4_hi4}).
+There is indeed a shift of the previously selected 1000~hPa for higher levels, which is even slightly stronger with 4 moisture predictors than with 2.
+This change is likely due to the fact that when considering only the circulation analogy, the method tries to take into account information that can serve as proxy for moisture assessment, whereas it doesn't need it with the moisture index.
+This aspect has never been demonstrated, as classic calibration tools do not allow it.
+It can only be assessed by a global optimization technique that can tune jointly both levels of analogy.
+
+The selected pressure levels for the analogy on the moisture index are strongly centred around 700~hPa and 600~hPa.
+No other value has been selected when considering 2 pressure levels (Table \ref{table:levels_GA_z4_hi2}), and when considering 4 levels, the 850~hPa and 500~hPa levels are additionally selected.
+However, even in this latter method, the 700~hPa and 600~hPa levels still hold 78 \% of the selection.
+It is thus more efficient, in terms of forecasting performance, to consider one of this level multiple times at different hours rather than using another pressure level.
+Besides, the optimizer never chose the same pressure level at the same hour for any variable, even though it was allowed to do so.
+
+The selection of the temporal windows for the atmospheric circulation is similar to the preceding optimization (in the order of increasing pressure: 12~h, 24/30~h, 12~h, 30~h), but sometimes with a bit more variability.
+When it comes to the moisture analogy, there is a clear trend to select 12~h and 24~h when considering 2 predictors.
+The z4-hi4 method presents more variability on the selection of the temporal windows for the moisture index.
+
+The optimized spatial windows for the atmospheric circulation have also changed (Figures \ref{fig:spatial_windows_z4-hi2} and \ref{fig:spatial_windows_z4-hi4}).
+The very large domains on the upper level of the 4 first subregions are not present anymore, and more variability can be observed.
+The selected points for the analogy on the moisture index are always located nearby the catchment, including at least 1 of the nearest points from the reanalysis dataset, and the spatial windows are relatively small.
+Thus, for our case study, there is no need to look for distant moisture information and the search could be reduced to a smaller domain.
+
+The CRPSS scores were improved by considering the moisture information (Table \ref{table:scores}).
+The optimized methods also perform better than the reference method based on the moisture index (Table \ref{table:scores_diff}).
+However, there is no drastic difference between both z4-hi2 and z4-hi4 methods, which suggests that considering 4 moisture predictors is not absolutely necessary.
+When it comes to improvements for days with precipitation above our 3 thresholds (P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the forecast, mainly for heavy rainfall.
+
+The analysis of the parameters cross-compatibility (Tables \ref{table:crossing_z4-hi2_calib} to \ref{table:crossing_z4-hi4_valid}) is also very similar to the one on the circulation analogy only.
+The same pattern can be observed, with a drop of performance for the subregions under different meteorological influences.
+However, the losses of performance are globally more important than before, suggesting that more complex methods with moisture variables are less transposable to another subregion, even though it is located within the same grid of the reanalysis dataset.
+
+\section{Discussion}
+
+The optimization of the analogue method by means of genetic algorithms has been undertaken in stages by releasing progressively new degrees of freedom.
+This approach allowed us to differentiate the contributions to performance gains, as well as to identify possible over-parametrization.
+The main improvements for our case study are due to the following factors:
+
+\begin{itemize}
+	\item Using 4 pressure levels for the analogy of circulation.
+It seems to be the optimal number for the studied region.
+Beyond that value the validation score drops, revealing a lost in robustness due to over-parametrization.
+	\item The automatic and joint optimization of all parameters: the analogues number, the selection of the pressure levels and the time windows, and the spatial windows.
+These parameters are highly interdependent, so we need to optimize them jointly in order to identify optimal combinations.
+Traditional calibration procedures based on a systematic assessment of every combination is no more possible when considering more than 2 pressure levels.
+	\item The introduction of distinct spatial windows between pressure levels.
+Indeed, the synoptic circulation is characterized by features with very different scales depending on the height, and important information for predicting rainfall is not necessarily located in the same area from one level to another.
+The optimized spatial windows are consistent in between the subregions.
+	\item The weighting of the analogy criteria between different pressure levels.
+It can be influenced by the variability of the geopotential with altitude, and the change of some levels significance with the targeted region.
+There is a trend for the weighting of circulation predictors to decrease with the increase in pressure, as one can see in Figure \ref{fig:levels_weights} for the method z4, and in Figure \ref{fig:levels_weights_average} for the averages over the 3 methods.
+However, the values stay around equity.
+This may not be the most influencing factor, and we may suggest to remove it first when trying to reduce the number of degrees of freedom.
+	\item The joint optimization of the circulation and moisture analogy levels, that are usually calibrated successively.
+We have been able to demonstrate that there is a dependency between the analogy levels, and that in order to approach the optimal parameters, we must consider them jointly.
+\end{itemize}
+
+GAs are very useful to optimize complex variants of the analogue method, and to assess new degrees of freedom that were not available so far.
+However, it can be dangerous to add too many parameters to optimize.
+Indeed, the optimizer will probably use them to successfully improve the calibration score, but the validation control remains very important in order to determine if we are actually improving the method, or if we are over-parametrizing it.
+
+The convergence of parallel optimizations decreases when the method to optimize becomes more and more complex.
+The optimizer do not always converge to the exact global optimum, but to its surroundings.
+This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that we have to stop it before the end, due to the required processing time (see Figure \ref{fig:evolution} as example).
+The resulting parameters may sometimes present significant differences, even though the score is almost similar.
+Through some Monte-Carlo analyses of the parameter space properties of the analogue method, \citet{Horton2012a} showed that some parameters of the method have a wide range of acceptable values.
+The spatial windows, for example, can be larger than the optimal size without much impact on the score, while they cannot be smaller \citep[see also][]{Bontron2004}.
+We could also observe that the selection of the pressure level is not a parameter as discrete as we would have thought, and that choosing another level may have reduced consequences on the performance.
+This is particularly true for higher pressure levels and can be more critical for lower layers.
+It was thus interesting to sometimes get several sets of near-optimal parameters, but with some nuances, in order to have an idea of the sensitivity of the parameters for a given region, and to compare the score on the validation period.
+In this regard, a cross-validation technique may be advisable.
+An approach that can also be recommended, and that we use, is to first explore a wide range of the parameter space with some optimizations, and to narrow it according to the results for more targeted optimizations that are likely to go faster and to perform better.
+
+We tried to optimize the preselection period (the 4-months window) jointly with the other parameters, but we did not get improvement.
+We also tried optimizing the moisture flux, which is composed of the moisture index multiplied with the wind flux.
+However, the results were not better than when we considered the moisture index alone.
+This may be related to the fact that the optimizer tries to provide the best analogy of the atmospheric circulation in the first place, which makes the wind information less relevant in the second level of analogy.
+
+As we could observe, methods with a higher complexity that integrate moisture predictors are less transposable than simpler ones.
+We also noticed in another unpublished work, that it is by far better to optimize for 2 subregions jointly rather than to optimize on one and to apply its parametrization to the other.
+Finally, the creation of the subregions is an important process and should be handled with care.
+Indeed, the geographical proximity is not always the leading factor to define a subregion.
+For example, the Southeast ridges subregion do not behave like its surrounding and differ in its parametrization, due to different leading meteorological influences.
+
+GAs are relatively heavy on processing and require an IT infrastructure capable of performing thousands hours of calculations.
+However, they automatically optimize all parameters of the analogue method, what the classic calibration does not allow.
+We therefore save much human time that was required to assess successively numerous combinations of parameters (particularly the selection of the pressure levels and the temporal windows).
+The ability to optimize jointly all parameters is important given the strong dependencies between them and between the levels of analogy.
+
+\section{Conclusions and perspectives}
+
+%TODO: complete
+
+The parameters resulting from the optimization are very consistent for the analogy of the atmospheric circulation, in terms of selection of the pressure levels, and the temporal and spatial windows.
+There are clear trends or even identical results for subregions under similar meteorological influences, which confirm that the optimized parameters are coherent, despite an eventual first impression of a great variability in the spatial windows.
+When adding moisture variables, the results show a higher variability, but remains highly acceptable and coherent.
+Indeed, the selection of the pressure level for the moisture index is for example very constant.
+
+We could observe strong dependencies between the parameters of the analogue method.
+Thus, the classic calibration, which optimizes the parameters successively, may not lead to the optimal combination.
+Moreover, it contains several manual systematic assessment, such as the selection of the pressure levels and the temporal windows.
+GAs, however, can select the pressure levels and the time windows automatically, which can save a considerable amount of human time.
+A great advantage of a global optimization is its ability to approach or reach optimal parameter values when they are considered jointly.
+
+We were able to identify that there is a parametric dependence between the analogy of circulation and the moisture.
+When we consider the two levels together, the optimal parameters of the analogy of circulation are different.
+This complexity can only be exploited in a suitable manner by global optimization methods.
+
+For our case study, there seems to be an optimum number of pressure levels to consider for the analogy of circulation, which is four, before losing performance in validation.
+We have also been able to improve the analogy of circulation by introducing a weighting between pressure levels, and considering independent spatial windows between levels.
+
+GAs provide parametrizations of the analogue method that exceed the performance of the classic calibration.
+In addition, we could observe that the forecasts for days with strong precipitation were significantly more improved, which is clearly interesting in the framework of flood forecasting.
+
+This work is by far not exhaustive and means to open a door for new explorations with the analogues methods.
+It becomes possible to even let the optimizer chose the meteorological variable to be used as predictor, as well as the analogy criteria.
+It is already possible to undertake such data mining with our code.
+Moreover, the analogue method has been explored for decades for precipitation forecasting, but very few work analysis its potential for other predictands.
+A global optimizer, such as GAs, can speed up this assessment significantly.
+
+\section*{Acknowledgments}
+Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of.
+Thanks to Renaud Marty for his fruitful collaboration over the years.
+
+Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
+NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.
+Precipitation time series provided by MeteoSwiss.
+
+\section*{References}
+
+\bibliography{../_refs/_articles-optimization}
+
+%% FIGURES
+
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=\linewidth]{figures/figure_map.pdf}}
+	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland. (source: Swisstopo)}
+	\label{fig:map}
+\end{figure}
+
+\begin{figure}[htb]
+	\centering
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_1.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_2.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_3.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_4.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_5.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_6.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_7.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_8.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_9.png}
+	\end{subfigure}%
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_10.png}
+	\end{subfigure}
+	\begin{subfigure}{.5\columnwidth}
+		\centering
+		\includegraphics[width=4.2cm]{figures/spatial_win_z4/legend.png}
+	\end{subfigure}
+	\caption{Optimized spatial windows for the z4 method (analogy of atmospheric circulation on 4 pressure levels).
+The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
+	\label{fig:spatial_windows_z4}
+\end{figure}
+
 \begin{figure}[htb]
@@
 
-The CRPSS scores of the optimized methods are provided in Table \ref{table:scores} and amounts to slightly more than 40 \% for both methods and for both periods.
-This results in a relative improvements that ranges from 11.5 \% to 15.6 \% compared to the reference method on the moisture analogy (Table \ref{table:scores_diff}).
-As for z4, the z4-hi2 and z4-hi4 methods present improvements of the forecast of significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
-The improvement are relatively similar for z4-hi2 (Table \ref{table:scores_thresholds_z4-hi2}) and z4-hi4 (Table \ref{table:scores_thresholds_z4-hi4}), with slightly superior scores for the latter on small precipitation (P\(\geq\)1 mm) and extremes (P\(\geq\)0.5\(\cdot\)P10).
-
-\begin{table}[htbp]
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi2 method.}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline 
-			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\  
-			& calib & valid & calib & valid & calib & valid \\ 
-			\hline 
-			1 & 12.6 & 9.3 & 12.4 & 9.7 & 15.8 & 11.0 \\
-			2 & 10.4 & 7.7 & 11.2 & 10.5 & 18.9 & 16.6 \\ 
-			3 & 14.5 & 11.6 & 14.1 & 11.4 & 18.7 & 14.6 \\ 
-			4 & 11.4 & 9.4 & 11.5 & 11.6 & 14.9 & 22.7 \\ 
-			5 & 11.8 & 8.0 & 12.2 & 8.9 & 12.0 & 12.8 \\ 
-			6 & 11.3 & 7.1 & 11.2 & 8.0 & 15.3 & 29.1 \\ 
-			7 & 20.5 & 15.5 & 25.2 & 24.0 & 43.0 & 79.5 \\
-			8 & 19.3 & 15.7 & 23.1 & 18.6 & 25.2 & 31.7 \\ 
-			9 & 17.0 & 15.4 & 17.4 & 16.5 & 23.7 & 39.4 \\ 
-			10 & 12.9 & 9.6 & 13.8 & 11.1 & 28.5 & 32.1 \\ 
-			\hline 
-			av. & 14.2 & 10.9 & 15.2 & 13.0 & 21.6 & 28.9 \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores_thresholds_z4-hi2}
-\end{table}
-
-\begin{table}[htbp]
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi4 method.}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline 
-			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\ 
-			& calib & valid & calib & valid & calib & valid \\ 
-			\hline 
-			1 & 21.2 & 17.9 & 13.4 & 9.3 & 17.8 & 13.3 \\ 
-			2 & 12.6 & 8.9 & 9.5 & 10.0 & 16.7 & 15.6 \\ 
-			3 & 17.0 & 16.1 & 14.0 & 12.4 & 21.3 & 15.9 \\ 
-			4 & 9.4 & 6.1 & 13.3 & 12.4 & 19.8 & 22.7 \\ 
-			5 & 16.4 & 8.7 & 13.3 & 9.9 & 15.5 & 19.8 \\ 
-			6 & 22.6 & 12.2 & 11.9 & 6.7 & 17.0 & 26.9 \\ 
-			7 & 14.6 & 4.9 & 24.7 & 23.5 & 42.7 & 87.6 \\ 
-			8 & 21.8 & 21.6 & 25.7 & 19.3 & 32.3 & 26.6 \\ 
-			9 & 20.2 & 18.9 & 17.4 & 14.2 & 24.5 & 33.9 \\ 
-			10 & 21.7 & 14.8 & 14.8 & 11.7 & 29.2 & 29.1 \\ 
-			\hline 
-			av. & 17.7 & 13.0 & 15.8 & 12.9 & 23.7 & 29.2 \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores_thresholds_z4-hi4}
-\end{table}
-
-The parameters cross-compatibility has also been assessed for the methods with moisture variables, and are shown in Tables \ref{table:crossing_z4-hi2_calib} and \ref{table:crossing_z4-hi2_valid} for the method z4-hi2, and Tables \ref{table:crossing_z4-hi4_calib} and \ref{table:crossing_z4-hi4_valid} for z4-hi4.
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, calibration period.}
-	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi2_calib.pdf}}
-	\label{table:crossing_z4-hi2_calib}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, validation period.}
-	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi2_valid.pdf}}
-	\label{table:crossing_z4-hi2_valid}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi4, calibration period.}
-	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi4_calib.pdf}}
-	\label{table:crossing_z4-hi4_calib}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi4, validation period.}
-	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi4_valid.pdf}}
-	\label{table:crossing_z4-hi4_valid}
-\end{table}
-
-\subsection{Analysis}
-
-When optimizing a method made of 2 levels of analogy, the introduction of moisture variables in the second level has an influence on the parameter values of the first level.
-This is first visible on the selection of the pressure levels for the circulation analogy, where the 1000~hPa that was previously systematically selected twice (Table \ref{table:levels_GA_z4}) is now less chosen (once or even not at all) for both za-hi2 (Table \ref{table:levels_GA_z4_hi2}) and za-hi4 (Table \ref{table:levels_GA_z4_hi4}).
-There is indeed a shift of the previously selected 1000~hPa for higher levels, which is even slightly stronger with 4 moisture predictors than with 2.
-This change is likely due to the fact that when considering only the circulation analogy, the method tries to take into account information that can serve as proxy for moisture assessment, whereas it doesn't need it with the moisture index.
-This aspect has never been demonstrated, as classic calibration tools do not allow it.
-It can only be assessed by a global optimization technique that can tune jointly both levels of analogy.
-
-The selected pressure levels for the analogy on the moisture index are strongly centred around 700~hPa and 600~hPa.
-No other value has been selected when considering 2 pressure levels (Table \ref{table:levels_GA_z4_hi2_H}), and when considering 4 levels, the 850~hPa and 500~hPa levels are additionally selected.
-However, even in this latter method, the 700~hPa and 600~hPa levels still hold 78 \% of the selection.
-It is thus more efficient, in terms of forecasting performance, to consider one of this level multiple times at different hours rather than using another pressure level.
-Besides, the optimizer never chose the same pressure level at the same hour for any variable, even though it was allowed to do so.
-
-The selection of the temporal windows for the atmospheric circulation is similar to the preceding optimization (in the order of increasing pressure: 12~h, 24/30~h, 12~h, 30~h), but sometimes with a bit more variability.
-When it comes to the moisture analogy, there is a clear trend to select 12~h and 24~h when considering 2 predictors.
-The z4-hi4 method presents more variability on the selection of the temporal windows for the moisture index.
-
-The optimized spatial windows for the atmospheric circulation have also changed (Figures \ref{fig:spatial_windows_z4-hi2} and \ref{fig:spatial_windows_z4-hi4}).
-The very large domains on the upper level of the 4 first subregions are not present anymore, and more variability can be observed.
-The selected points for the analogy on the moisture index are always located nearby the catchment, including at least 1 of the nearest points from the reanalysis dataset, and the spatial windows are relatively small.
-Thus, for our case study, there is no need to look for distant moisture information and the search could be reduced to a smaller domain.
-
-The CRPSS scores were improved by considering the moisture information (Table \ref{table:scores}).
-The optimized methods also perform better than the reference method based on the moisture index (Table \ref{table:scores_diff}).
-However, there is no drastic difference between both z4-hi2 and z4-hi4 methods, which suggests that considering 4 moisture predictors is not absolutely necessary.
-When it comes to improvements for days with precipitation above our 3 thresholds (P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the forecast, mainly for heavy rainfall.
-
-The analysis of the parameters cross-compatibility (Tables \ref{table:crossing_z4-hi2_calib} to \ref{table:crossing_z4-hi4_valid}) is also very similar to the one on the circulation analogy only.
-The same pattern can be observed, with a drop of performance for the subregions under different meteorological influences.
-However, the losses of performance are globally more important than before, suggesting that more complex methods with moisture variables are less transposable to another subregion, even though it is located within the same grid of the reanalysis dataset.
-
-\section{Discussion}
-
-The optimization of the analogue method by means of genetic algorithms has been undertaken in stages by releasing progressively new degrees of freedom.
-This approach allowed us to differentiate the contributions to performance gains, as well as to identify possible over-parametrization.
-The main improvements for our case study are due to the following factors:
-
-\begin{itemize}
-	\item Using 4 pressure levels for the analogy of circulation.
-It seems to be the optimal number for the studied region.
-Beyond that value the validation score drops, revealing a lost in robustness due to over-parametrization.
-	\item The automatic and joint optimization of all parameters: the analogues number, the selection of the pressure levels and the time windows, and the spatial windows.
-These parameters are highly interdependent, so we need to optimize them jointly in order to identify optimal combinations.
-Traditional calibration procedures based on a systematic assessment of every combination is no more possible when considering more than 2 pressure levels.
-	\item The introduction of distinct spatial windows between pressure levels.
-Indeed, the synoptic circulation is characterized by features with very different scales depending on the height, and important information for predicting rainfall is not necessarily located in the same area from one level to another.
-The optimized spatial windows are consistent in between the subregions.
-	\item The weighting of the analogy criteria between different pressure levels.
-It can be influenced by the variability of the geopotential with altitude, and the change of some levels significance with the targeted region.
-There is a trend for the weighting of circulation predictors to decrease with the increase in pressure, as one can see in Figure \ref{fig:levels_weights} for the method z4, and in Figure \ref{fig:levels_weights_average} for the averages over the 3 methods.
-However, the values stay around equity.
-This may not be the most influencing factor, and we may suggest to remove it first when trying to reduce the number of degrees of freedom.
-	\item The joint optimization of the circulation and moisture analogy levels, that are usually calibrated successively.
-We have been able to demonstrate that there is a dependency between the analogy levels, and that in order to approach the optimal parameters, we must consider them jointly.
-\end{itemize}
-
 \begin{figure}[htb]
@@
 
-GAs are very useful to optimize complex variants of the analogue method, and to assess new degrees of freedom that were not available so far.
-However, it can be dangerous to add too many parameters to optimize.
-Indeed, the optimizer will probably use them to successfully improve the calibration score, but the validation control remains very important in order to determine if we are actually improving the method, or if we are over-parametrizing it.
-
-The convergence of parallel optimizations decreases when the method to optimize becomes more and more complex.
-The optimizer do not always converge to the exact global optimum, but to its surroundings.
-This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that we have to stop it before the end, due to the required processing time (see Figure \ref{fig:evolution} as example).
-The resulting parameters may sometimes present significant differences, even though the score is almost similar.
-Through some Monte-Carlo analyses of the parameter space properties of the analogue method, \citet{Horton2012a} showed that some parameters of the method have a wide range of acceptable values.
-The spatial windows, for example, can be larger than the optimal size without much impact on the score, while they cannot be smaller \citep[see also][]{Bontron2004}.
-We could also observe that the selection of the pressure level is not a parameter as discrete as we would have thought, and that choosing another level may have reduced consequences on the performance.
-This is particularly true for higher pressure levels and can be more critical for lower layers.
-It was thus interesting to sometimes get several sets of near-optimal parameters, but with some nuances, in order to have an idea of the sensitivity of the parameters for a given region, and to compare the score on the validation period.
-In this regard, a cross-validation technique may be advisable.
-An approach that can also be recommended, and that we use, is to first explore a wide range of the parameter space with some optimizations, and to narrow it according to the results for more targeted optimizations that are likely to go faster and to perform better.
-
 \begin{figure}[htb]
@@
 
-We tried to optimize the preselection period (the 4-months window) jointly with the other parameters, but we did not get improvement.
-We also tried optimizing the moisture flux, which is composed of the moisture index multiplied with the wind flux.
-However, the results were not better than when we considered the moisture index alone.
-This may be related to the fact that the optimizer tries to provide the best analogy of the atmospheric circulation in the first place, which makes the wind information less relevant in the second level of analogy.
-
-As we could observe, methods with a higher complexity that integrate moisture predictors are less transposable than simpler ones.
-We also noticed in another unpublished work, that it is by far better to optimize for 2 subregions jointly rather than to optimize on one and to apply its parametrization to the other.
-Finally, the creation of the subregions is an important process and should be handled with care.
-Indeed, the geographical proximity is not always the leading factor to define a subregion.
-For example, the Southeast ridges subregion do not behave like its surrounding and differ in its parametrization, due to different leading meteorological influences.
-
-GAs are relatively heavy on processing and require an IT infrastructure capable of performing thousands hours of calculations.
-However, they automatically optimize all parameters of the analogue method, what the classic calibration does not allow.
-We therefore save much human time that was required to assess successively numerous combinations of parameters (particularly the selection of the pressure levels and the temporal windows).
-The ability to optimize jointly all parameters is important given the strong dependencies between them and between the levels of analogy.
-
-\section{Conclusions and perspectives}
-
-%TODO: complete
-
-The parameters resulting from the optimization are very consistent for the analogy of the atmospheric circulation, in terms of selection of the pressure levels, and the temporal and spatial windows.
-There are clear trends or even identical results for subregions under similar meteorological influences, which confirm that the optimized parameters are coherent, despite an eventual first impression of a great variability in the spatial windows.
-When adding moisture variables, the results show a higher variability, but remains highly acceptable and coherent.
-Indeed, the selection of the pressure level for the moisture index is for example very constant.
-
-We could observe strong dependencies between the parameters of the analogue method.
-Thus, the classic calibration, which optimizes the parameters successively, may not lead to the optimal combination.
-Moreover, it contains several manual systematic assessment, such as the selection of the pressure levels and the temporal windows.
-GAs, however, can select the pressure levels and the time windows automatically, which can save a considerable amount of human time.
-A great advantage of a global optimization is its ability to approach or reach optimal parameter values when they are considered jointly.
-
-We were able to identify that there is a parametric dependence between the analogy of circulation and the moisture.
-When we consider the two levels together, the optimal parameters of the analogy of circulation are different.
-This complexity can only be exploited in a suitable manner by global optimization methods.
-
-For our case study, there seems to be an optimum number of pressure levels to consider for the analogy of circulation, which is four, before losing performance in validation.
-We have also been able to improve the analogy of circulation by introducing a weighting between pressure levels, and considering independent spatial windows between levels.
-
-GAs provide parametrizations of the analogue method that exceed the performance of the classic calibration.
-In addition, we could observe that the forecasts for days with strong precipitation were significantly more improved, which is clearly interesting in the framework of flood forecasting.
-
-This work is by far not exhaustive and means to open a door for new explorations with the analogues methods.
-It becomes possible to even let the optimizer chose the meteorological variable to be used as predictor, as well as the analogy criteria.
-It is already possible to undertake such data mining with our code.
-Moreover, the analogue method has been explored for decades for precipitation forecasting, but very few work analysis its potential for other predictands.
-A global optimizer, such as GAs, can speed up this assessment significantly.
-
-\section*{Acknowledgments}
-Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of.
-Thanks to Renaud Marty for his fruitful collaboration over the years.
-
-Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
-NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.
-Precipitation time series provided by MeteoSwiss.
-
-\section*{References}
-
-\bibliography{../_refs/_articles-optimization}
-
 \end{document}

### 2015-11-19 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Removing tables and figures for z4-hi4.

@@
 
+Due to significant similarities between the results from z4-hi2 and z4-hi4, the latter will only be partly shown in order to improve readability.
+
 As previously, the optimized parameters differ from one subregion to another, and this event to a greater extent.
-Detailed examples are still provided for the Swiss Chablais subregion in Table \ref{table:params_GA_z4_hi2} for z4-hi2 and in Table \ref{table:params_GA_z4_hi4} for z4-hi4.
+Detailed examples are still provided for the Swiss Chablais subregion in Table \ref{table:params_GA_z4_hi2} for z4-hi2.
 The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_z4-hi2} for z4-hi2, along with the selected pressure levels for both the circulation and the moisture analogy (Table \ref{table:levels_GA_z4_hi2}).
-Correspondingly, for the method z4-hi4, the spatial windows are shown in Figure \ref{fig:spatial_windows_z4-hi4} and the selected pressure levels are presented in Tables \ref{table:levels_GA_z4_hi4}.
 
@@
 \begin{table}[htbp]
-	\caption{Parameters of the z4-hi4 method (atmospheric circulation on 4 levels and moisture index on 4 levels), optimized for the Chablais subregion.
-Same conventions as Table \ref{table:params_GA_z4}.}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline L & V & H & D & W & C & N \\ 
-			\hline 
-			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{8}{*}{1} &  \multirow{2}{*}{Z400} & \multirow{2}{*}{6~h} & -5.0 - 12.5 \degree E & \multirow{2}{*}{20\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
-			& & & 45.0 - 52.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
-			& & & 40.0 - 45.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
-			& & & 42.5 - 47.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
-			& & & 40.0 - 47.5 \degree N & & & \\ 
-			\hline 
-			\multirow{8}{*}{2} & TPW & \multirow{2}{*}{24~h} & 7.5 - 10.0 \degree E & \multirow{2}{*}{27\%} & \multirow{8}{*}{RMSE} & \multirow{8}{*}{25} \\
-			& *RH500 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{12~h} & 5.0 - 7.5 \degree E & \multirow{2}{*}{41\%} & & \\ 
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{18~h} & 0.0 - 7.5 \degree E & \multirow{2}{*}{19\%} & & \\ 
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{24~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{13\%} & & \\ 
-			& *RH850 & & 45.0 - 47.5 \degree N & & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_GA_z4_hi4}
-\end{table}
-
-\begin{table}[htbp]
 	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the z4-hi2 method, at the different subregions.}
@@
 
-\begin{table}[htbp]
-	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the z4-hi4 method, at the different subregions.}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline ID & 300 & 400 & 500 & 600 & 700 & 850 & 925 & 1000 \\ 
-			\hline 
-			1  &   & $\sim$ & $\sim \bullet$ &   & $\bullet \bullet$ & $\sim \bullet$ &   & $\sim$ \\
-			2  &   & $\sim$ &   & $\bullet$ & $\sim \sim \bullet \bullet$ & $\bullet$ &   & $\sim$ \\
-			3  &   & $\sim$ &   & $\bullet$ & $\sim \bullet \bullet \bullet$ & $\sim$ & $\sim$ &   \\
-			4  &   &   & $\sim$ & $\bullet \bullet$ & $\sim \bullet \bullet$ & $\sim$ &   & $\sim$ \\
-			5  &   & $\sim$ & $\sim$ & $\bullet \bullet$ & $\bullet \bullet$ & $\sim$ &   & $\sim$ \\
-			6  &   & $\sim$ & $\sim$ & $\bullet \bullet$ & $\bullet$ & $\sim \bullet$ &   & $\sim$ \\
-			7  &   & $\sim$ &   & $\bullet \bullet$ & $\sim \sim \bullet$ & $\bullet$ &   & $\sim$ \\
-			8  &   &   & $\sim$ & $\sim \bullet \bullet$ & $\bullet$ & $\sim \bullet$ &   & $\sim$ \\
-			9  &   & $\sim$ &  $\bullet$ & $\bullet$ & $\sim \bullet$ & $\sim \bullet$ & $\sim$ &   \\
-			10 &   & $\sim$ & $\sim$ & $\bullet$ & $\bullet \bullet$ & $\sim \sim \bullet$ &   &   \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_z4_hi4}
-\end{table}
-
 The CRPSS scores of the optimized methods are provided in Table \ref{table:scores} and amounts to slightly more than 40 \% for both methods and for both periods.
@@
 As for z4, the z4-hi2 and z4-hi4 methods present improvements of the forecast of significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
-The improvement are relatively similar for z4-hi2 (Table \ref{table:scores_thresholds_z4-hi2}) and z4-hi4 (Table \ref{table:scores_thresholds_z4-hi4}), with slightly superior scores for the latter on small precipitation (P\(\geq\)1 mm) and extremes (P\(\geq\)0.5\(\cdot\)P10).
+The improvement are relatively similar for z4-hi2 (Table \ref{table:scores_thresholds_z4-hi2}) and z4-hi4 (not shown), with slightly superior scores for the latter on small precipitation (P\(\geq\)1 mm : 17.7\% and 13.0\%) and extremes (P\(\geq\)0.5\(\cdot\)P10 : 23.7\% and 29.2\%).
 
@@
 
-\begin{table}[htbp]
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi4 method.}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline 
-			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\ 
-			& calib & valid & calib & valid & calib & valid \\ 
-			\hline 
-			1 & 21.2 & 17.9 & 13.4 & 9.3 & 17.8 & 13.3 \\ 
-			2 & 12.6 & 8.9 & 9.5 & 10.0 & 16.7 & 15.6 \\ 
-			3 & 17.0 & 16.1 & 14.0 & 12.4 & 21.3 & 15.9 \\ 
-			4 & 9.4 & 6.1 & 13.3 & 12.4 & 19.8 & 22.7 \\ 
-			5 & 16.4 & 8.7 & 13.3 & 9.9 & 15.5 & 19.8 \\ 
-			6 & 22.6 & 12.2 & 11.9 & 6.7 & 17.0 & 26.9 \\ 
-			7 & 14.6 & 4.9 & 24.7 & 23.5 & 42.7 & 87.6 \\ 
-			8 & 21.8 & 21.6 & 25.7 & 19.3 & 32.3 & 26.6 \\ 
-			9 & 20.2 & 18.9 & 17.4 & 14.2 & 24.5 & 33.9 \\ 
-			10 & 21.7 & 14.8 & 14.8 & 11.7 & 29.2 & 29.1 \\ 
-			\hline 
-			av. & 17.7 & 13.0 & 15.8 & 12.9 & 23.7 & 29.2 \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores_thresholds_z4-hi4}
-\end{table}
-
-The parameters cross-compatibility has also been assessed for the methods with moisture variables, and are shown in Tables \ref{table:crossing_z4-hi2_calib} and \ref{table:crossing_z4-hi2_valid} for the method z4-hi2, and Tables \ref{table:crossing_z4-hi4_calib} and \ref{table:crossing_z4-hi4_valid} for z4-hi4.
+The parameters cross-compatibility has also been assessed for the methods with moisture variables, and are shown in Tables \ref{table:crossing_z4-hi2_calib} and \ref{table:crossing_z4-hi2_valid} for the method z4-hi2 (not shown for z4-hi4, but similar).
 
@@
 
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi4, calibration period.}
-	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi4_calib.pdf}}
-	\label{table:crossing_z4-hi4_calib}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi4, validation period.}
-	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi4_valid.pdf}}
-	\label{table:crossing_z4-hi4_valid}
-\end{table}
-
 \subsection{Analysis}
@@
 When optimizing a method made of 2 levels of analogy, the introduction of moisture variables in the second level has an influence on the parameter values of the first level.
-This is first visible on the selection of the pressure levels for the circulation analogy, where the 1000~hPa that was previously systematically selected twice (Table \ref{table:levels_GA_z4}) is now less chosen (once or even not at all) for both za-hi2 (Table \ref{table:levels_GA_z4_hi2}) and za-hi4 (Table \ref{table:levels_GA_z4_hi4}).
+This is first visible on the selection of the pressure levels for the circulation analogy, where the 1000~hPa that was previously systematically selected twice (Table \ref{table:levels_GA_z4}) is now less chosen (once or even not at all) for both za-hi2 (Table \ref{table:levels_GA_z4_hi2}) and za-hi4 (not shown).
 There is indeed a shift of the previously selected 1000~hPa for higher levels, which is even slightly stronger with 4 moisture predictors than with 2.
@@
 
-The optimized spatial windows for the atmospheric circulation have also changed (Figures \ref{fig:spatial_windows_z4-hi2} and \ref{fig:spatial_windows_z4-hi4}).
+The optimized spatial windows for the atmospheric circulation have also changed (Figure \ref{fig:spatial_windows_z4-hi2}; results of z4-hi4 are not shown but present the same trends).
 The very large domains on the upper level of the 4 first subregions are not present anymore, and more variability can be observed.
@@
 The optimized methods also perform better than the reference method based on the moisture index (Table \ref{table:scores_diff}).
-However, there is no drastic difference between both z4-hi2 and z4-hi4 methods, which suggests that considering 4 moisture predictors is not absolutely necessary.
+However, there is no drastic difference between both z4-hi2 and z4-hi4 methods, which suggests that considering 4 moisture predictors is not necessary.
 When it comes to improvements for days with precipitation above our 3 thresholds (P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the forecast, mainly for heavy rainfall.
 
-The analysis of the parameters cross-compatibility (Tables \ref{table:crossing_z4-hi2_calib} to \ref{table:crossing_z4-hi4_valid}) is also very similar to the one on the circulation analogy only.
+The analysis of the parameters cross-compatibility (Tables \ref{table:crossing_z4-hi2_calib} and \ref{table:crossing_z4-hi2_valid}) is also very similar to the one on the circulation analogy only (results for z4-hi4 not shown as very similar).
 The same pattern can be observed, with a drop of performance for the subregions under different meteorological influences.
@@
 \begin{figure}[htb]
-	\centering
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_1.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_2.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_3.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_4.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_5.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_6.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_7.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_8.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_9.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/Spatial_windows_10.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[ width=4.2cm]{figures/spatial_win_z4-hi4/legend.png}
-	\end{subfigure}
-	\caption{Optimized spatial windows for the z4-hi4 method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 4 pressure levels).
-The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
-	\label{fig:spatial_windows_z4-hi4}
-\end{figure}
-
-\begin{figure}[htb]
 	\centerline{\includegraphics[width=\linewidth]{figures/figure_levels_weights.pdf}}

### 2015-11-19 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Using acronyms.

@@
 \section{Introduction}
-\label{section_intro}
+\label{sec:intro}
 
-The analogue method is a downscaling technique based on the idea expressed by \citet{Lorenz1969}, that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Bontron2005}.
+The analogue method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1969}, that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Bontron2005}.
 It aims at forecasting a predictand, often the daily precipitation, on the basis of predictor variables describing the synoptic atmospheric circulation.
@@
 
-The analogue method has to be adapted to every new location it is applied.
-We improved the analogue method for the Swiss Alps, by means of genetic algorithms.
+The AM has to be adapted to every new location it is applied.
+We improved the AM for the Swiss Alps, by means of Genetic Algorithms (GAs).
 A summary of the main results are provided here \citep[see][for the details]{Horton2012a}.
-Even though the results may differ from one place to another, the applicability of GAs to the analogue method remains universal.
+Even though the results may differ from one place to another, the applicability of GAs to the AM remains universal.
 
@@
 \section{The analogue method}
-\label{section_analog_method}
+\label{sec:analog_method}
 
@@
 \subsection{Data}
-\label{section_data}
+\label{sec:data}
 
-The analogue method relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series we want to forecast.
+The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series we want to forecast.
 
@@
 
-The 48 years precipitation dataset (see section \ref{section_intro}.\ref{section_data}) was divided into a calibration period and a validation period.
+The 48 years precipitation dataset (see section \ref{sec:intro}.\ref{sec:data}) was divided into a calibration period and a validation period.
 Using data independent from the calibration period to validate our results is very important in order to assess the robustness of the improvements and to avoid overparametrization of the method.
@@
 We first optimized the analogy of atmospheric circulation alone, without moisture variables, for our 10 subregions.
-We started from the most simple analogue method, and increased the complexity in order to identify the degrees of freedom that are of particular interest.
+We started from the most simple AM, and increased the complexity in order to identify the degrees of freedom that are of particular interest.
 Thus, the tested parametrization evolved iteratively in complexity.
@@
 We let the optimizer choose the number of analogues, both spatial windows with no overlapping constraint, as well as the temporal window (hours of observation of the geopotential).
-The classic calibration cannot automatically choose the temporal window, neither handle non-overlapping spatial windows, and finally it cannot optimize all parameters simultaneously.
+The sequential calibration cannot automatically choose the temporal window, neither handle non-overlapping spatial windows, and finally it cannot optimize all parameters simultaneously.
 With these improvements, we could gain a relative improvement of the CRPSS of 3.97\% and 2.45\% in average for the calibration and the validation periods respectively.
@@
 Then, we provided an additional degree of freedom to the AGs by letting them choose the pressure levels along with the other parameters.
-Evaluation of pressure levels is also a non-automated process in the classic calibration.
+Evaluation of pressure levels is also a non-automated process in the sequential calibration.
 We could observe that this degree of freedom increases the optimization time and may decrease the number of simulations that converge to a single solution.
@@
 Its spatial distribution is however homogeneous.
-The optimizer thus provided consistent selections of pressure levels and temporal windows, which depicts a significant preference in the analogue method, and the success of our GAs to provide consistent results.
-The automatic selection of the pressure levels is a big advantage of a global optimization, as it is not possible to assess all combinations of 4 levels with the classic calibration procedure.
+The optimizer thus provided consistent selections of pressure levels and temporal windows, which depicts a significant preference in the AM, and the success of our GAs to provide consistent results.
+The automatic selection of the pressure levels is a big advantage of a global optimization, as it is not possible to assess all combinations of 4 levels with the sequential calibration procedure.
 
@@
 We previously worked with a method based on a unique level of analogy.
-However, we know that moisture variables in a second level of analogy do provide improvements to the method (section \ref{section_intro}.\ref{section_analog_method}).
+However, we know that moisture variables in a second level of analogy do provide improvements to the method (section \ref{sec:intro}.\ref{sec:analog_method}).
 So we also wanted to optimize the moisture index, which is a combination of the relative humidity and the precipitable water.
@@
 This change is likely due to the fact that when considering only the circulation analogy, the method tries to take into account information that can serve as proxy for moisture assessment, whereas it doesn't need it with the moisture index.
-This aspect has never been demonstrated, as classic calibration tools do not allow it.
+This aspect has never been demonstrated, as sequential calibration tools do not allow it.
 It can only be assessed by a global optimization technique that can tune jointly both levels of analogy.
@@
 
-The optimization of the analogue method by means of genetic algorithms has been undertaken in stages by releasing progressively new degrees of freedom.
+The optimization of the AM by means of GAs has been undertaken in stages by releasing progressively new degrees of freedom.
 This approach allowed us to differentiate the contributions to performance gains, as well as to identify possible over-parametrization.
@@
 
-GAs are very useful to optimize complex variants of the analogue method, and to assess new degrees of freedom that were not available so far.
+GAs are very useful to optimize complex variants of the AM, and to assess new degrees of freedom that were not available so far.
 However, it can be dangerous to add too many parameters to optimize.
@@
 The resulting parameters may sometimes present significant differences, even though the score is almost similar.
-Through some Monte-Carlo analyses of the parameter space properties of the analogue method, \citet{Horton2012a} showed that some parameters of the method have a wide range of acceptable values.
+Through some Monte-Carlo analyses of the parameter space properties of the AM, \citet{Horton2012a} showed that some parameters of the method have a wide range of acceptable values.
 The spatial windows, for example, can be larger than the optimal size without much impact on the score, while they cannot be smaller \citep[see also][]{Bontron2004}.
@@
 GAs are relatively heavy on processing and require an IT infrastructure capable of performing thousands hours of calculations.
-However, they automatically optimize all parameters of the analogue method, what the classic calibration does not allow.
+However, they automatically optimize all parameters of the AM, what the sequential calibration does not allow.
 We therefore save much human time that was required to assess successively numerous combinations of parameters (particularly the selection of the pressure levels and the temporal windows).
@@
 
-We could observe strong dependencies between the parameters of the analogue method.
-Thus, the classic calibration, which optimizes the parameters successively, may not lead to the optimal combination.
+We could observe strong dependencies between the parameters of the AM.
+Thus, the sequential calibration, which optimizes the parameters successively, may not lead to the optimal combination.
 Moreover, it contains several manual systematic assessment, such as the selection of the pressure levels and the temporal windows.
@@
 
-GAs provide parametrizations of the analogue method that exceed the performance of the classic calibration.
+GAs provide parametrizations of the AM that exceed the performance of the sequential calibration.
 In addition, we could observe that the forecasts for days with strong precipitation were significantly more improved, which is clearly interesting in the framework of flood forecasting.
 
-This work is by far not exhaustive and means to open a door for new explorations with the analogues methods.
+This work is by far not exhaustive and means to open a door for new explorations with the AMs.
 It becomes possible to even let the optimizer chose the meteorological variable to be used as predictor, as well as the analogy criteria.
 It is already possible to undertake such data mining with our code.
-Moreover, the analogue method has been explored for decades for precipitation forecasting, but very few work analysis its potential for other predictands.
+Moreover, the AM has been explored for decades for precipitation forecasting, but very few work analysis its potential for other predictands.
 A global optimizer, such as GAs, can speed up this assessment significantly.

### 2015-11-19 Optimization case study - Journal of Hydrology/elsarticle-template.tex
First version of the abstract.

@@
 
-\title{Using Genetic Algorithms to Optimize the Analogue Method for Precipitation forecasting in the Swiss Alps}
+\title{Using Genetic Algorithms to Optimize the Analogue Method for Precipitation Forecasting in the Swiss Alps}
 
@@
 \begin{abstract}
-The global optimization can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
-Indeed, it allows taking into account parameters inter-dependencies, adding new degrees of freedom, and choosing objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
-We then applied the optimizer to the Rh\^{o}e catchment in the Swiss Alps and obtained coherent results which significantly improve the performance of the forecasting by analogy.
-The optimizer allowed us to calibrate jointly all parameters of the method and to add a weighting of the criteria per pressure level, as well as non-overlapping spatial windows.
+The analogue method is often used to forecast precipitation based on predictors variables provided by global models.
+The method samples a selection of days in the archives that are similar to the target day to forecast, and consider the corresponding observed precipitation (the predictand) as the conditional distribution for the target day.
+The statistical relationship between predictors and predictands relies on some parameters that characterize how and where the similitude between two atmospheric situations has to be defined.
+
+This relationship is usually established by a semi-automatic sequential procedure that has strong limitations.
+A new global optimization approach relying on Genetic Algorithms can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
+It allows taking into account parameters inter-dependencies, adding new degrees of freedom, and choosing objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
+
+In this work, the global optimization is applied to the Rh\^{o}e catchment in the Swiss Alps in order to show its interest and the relevance of the resulting parameters.
+Indeed, not only the performance increases, but the parameters are obtained automatically and objectively, which reduces effort-hours when adapting the method to a new region or for a new predictand.
+Moreover, the approach allows for new degrees of freedom, such as a weighting between the pressure levels and non overlapping spatial windows.
 \end{abstract}

### 2015-11-19 Optimization case study - Journal of Hydrology/elsarticle-template.tex
First version of the introduction.

@@
 
-The analogue method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1969}, that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Bontron2005}.
-It aims at forecasting a predictand, often the daily precipitation, on the basis of predictor variables describing the synoptic atmospheric circulation.
-Many parameters define this relationship, which are usually calibrated by means of a semi-automatic procedure.
+The analogue method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1956, Lorenz1969}, that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Duband1970, Bontron2005}.
+It aims at forecasting a predictand, often the daily precipitation \citep[eg.]{Guilbaud1997, Bontron2005, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, BenDaoud2015}, on the basis of predictor variables describing the synoptic atmospheric circulation.
+Other predictands are also often considered \citep[see][for a non-exhaustive list]{Horton2016}.
 
-The AM has to be adapted to every new location it is applied.
-We improved the AM for the Swiss Alps, by means of Genetic Algorithms (GAs).
-A summary of the main results are provided here \citep[see][for the details]{Horton2012a}.
-Even though the results may differ from one place to another, the applicability of GAs to the AM remains universal.
-
-%In operational forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies, it is more and more used to downscale the results of global climate model simulation runs.
+In operational forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies, it is newly used to downscale the results of global climate model (GCM) simulation runs.
 In this last case, although the GCM represents the large or regional scale evolutions of the atmosphere, it would be far too computer intensive to get down to variables such as precipitation at a rather small and representative scale.
 Therefore the idea to rely on past observations to bypass these unaffordable small scale simulations and to go from the large scale situation proposed by the GCM to the end variables like precipitation by searching anlogs in the past and present archive.
+
+The method can be made of multiple successive subsampling steps, each of them relying on different meteorological variables.
+A certain number of parameters define the relationship between predictors and predictands, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criteria itself, and finally the number of analogue situations to keep at each subsampling level.
+These parameters are usually calibrated by means of a semi-automatic sequential procedure \citep[see][for the details]{Bontron2004, Horton2016}.
+This sequential approach has strong limitations: (i) it cannot automatically choose the pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it could not handle new degrees of freedom, such as a weighting between the pressure levels.
+Thus, even if the processing involved is relatively fast, the sequential approach requires laborious assessments of predictors combinations (variables, pressure levels, temporal windows), and present a high risk of ending in a local optimum due to subjective initial choices and lack of consideration of parameters dependencies.
+
+With the perspective to overcome these limitations, a global optimization technique, namely Genetic Algorithms (GAs) was introduced by \citet{Horton2016a}.
+An intensive assessment work resulted in recommendations of parametrization of GAs in order to optimize AMs successfully.
+The present paper is based on these recommendations and apply them to precipitation forecasting for the upper Rh\^{o}e catchment in the Swiss Alps.
+It aims at proving the relevance of a fully-automatic, objective, and global, optimization technique for AMs.
+The applications are indeed numerous, as the AM has to be adapted to every new location it is applied, or to any new predictand it should forecast.
+
+A short overview of AMs is presented in section \ref{sec:analog_method}, as well as a summary of Genetic Algorithms in section \ref{sec:gas}.
+Section \ref{sec:case_study} describes the case study area.
+The results are first detailed for the optimization of the analogy on the atmospheric circulation only (section \ref{sec:optim_circul}), before being extended to a method adding a second level of analogy on moisture variables (section \ref{sec:optim_moisture}).
+General discussions (section \ref{sec:discussion}) and conclusions (section \ref{sec:conclusions}) follow.
 
@@
 
-Multiple variations of the methods exist, and some aspects and parameters will not be detailed hereafter.
-There are mainly 2 parametrizations that are used most often: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
+Multiple variations of the methods exist, and most of them will not be detailed hereafter \cite[see][for more comprehensive listings]{Horton2016, BenDaoud2015}.
+However, there are mainly 2 parametrizations that are most often used for precipitation forecasting: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
 
-The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): We assess the similarity of the atmospheric circulation of a target date with every day of the archive by processing the S1 criteria \citep[Eq.\ (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
+The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): The similarity of the atmospheric circulation of a target date with every day of the archive is assessed by processing the S1 criteria \citep[Eq.\ (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
 \citet{Bontron2005} showed that the geopotential height at 500~hPa and 1000~hPa are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criteria performs better than scores based on absolute distances.
@@
 \section{Genetic algorithms}
+\label{sec:gas}
 
@@
 \section{Case study description}
+\label{sec:case_study}
 
@@
 \section{Optimization of the circulation analogy}
+\label{sec:optim_circul}
 
@@
 \section{Optimization of the moisture analogy}
+\label{sec:optim_moisture}
 
@@
 \section{Discussion}
+\label{sec:discussion}
 
@@
 \section{Conclusions and perspectives}
+\label{sec:conclusions}
 

### 2015-11-19 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Using nomenclature.

@@
 
-The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): The similarity of the atmospheric circulation of a target date with every day of the archive is assessed by processing the S1 criteria \citep[Eq.\ (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
+The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): the similarity of the atmospheric circulation of a target date with every day of the archive is assessed by processing the S1 criteria \citep[Eq.\ (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
 \citet{Bontron2005} showed that the geopotential height at 500~hPa and 1000~hPa are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criteria performs better than scores based on absolute distances.
@@
 To cope with seasonal effects, candidate dates are extracted within a period of 4 months centred around the target date, for every year of the archive.
+Following the nomenclature proposed by \citet{Horton2016}, this method will be named 2Z.
 
@@
 \end{equation}
-where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points of the grid describing the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
+where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points of the gridded data describing the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
 The differences are processed separately in both directions.
@@
 \begin{table}[htbp]
-	\caption{Parameters of the reference method on the atmospheric circulation.}
+	\caption{Parameters of the reference method on the atmospheric circulation (2Z).}
 	\footnotesize
@@
 \begin{table}[htbp]
-	\caption{Parameters of the reference method with moisture variables.}
+	\caption{Parameters of the reference method with moisture variables (2Z-2MI).}
 	\footnotesize
@@
 
-The method we finally optimized for the analogy of the atmospheric circulation, based on 4 levels of the geopotential, and that we will name z4, is made of the following degrees of freedom:
+The method we finally optimized for the analogy of the atmospheric circulation, based on 4 levels of the geopotential, and that we will name 4Zo, is made of the following degrees of freedom:
 
@@
 
-\subsection{Results for the z4 method}
+\subsection{Results for the 4Zo method}
 
-The resulting optimized parameters for z4 vary from one subregion to another.
-An example of the detailed parameters is provided for the Swiss Chablais in Table \ref{table:params_GA_z4}.
-The optimized spatial windows are given for every subregion in Figure \ref{fig:spatial_windows_z4}, and the selected pressure levels in Table~\ref{table:levels_GA_z4}.
+The resulting optimized parameters for 4Zo vary from one subregion to another.
+An example of the detailed parameters is provided for the Swiss Chablais in Table \ref{table:params_GA_4Zo}.
+The optimized spatial windows are given for every subregion in Figure \ref{fig:spatial_windows_4Zo}, and the selected pressure levels in Table~\ref{table:levels_GA_4Zo}.
 
 \begin{table}[htbp]
-	\caption{Parameters of the z4 method (analogy on 4 levels of the atmospheric circulation) optimized for the Chablais subregion.
+	\caption{Parameters of the 4Zo method (analogy on 4 levels of the atmospheric circulation) optimized for the Chablais subregion.
 The columns are the following: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
@@
 	\end{center}
-	\label{table:params_GA_z4}
+	\label{table:params_GA_4Zo}
 \end{table}
@@
 \begin{table}[htbp]
-	\caption{Pressure levels ($\sim$) automatically selected for the z4 method at the different subregions.}
+	\caption{Pressure levels ($\sim$) automatically selected for the 4Zo method at the different subregions.}
 	\footnotesize
@@
 	\end{center}
-	\label{table:levels_GA_z4}
+	\label{table:levels_GA_4Zo}
 \end{table}
@@
 The improvement of the CRPSS score relatively to the reference method on the atmospheric circulation is provided in Table \ref{table:scores_diff} and is in average 15.3 \% in calibration and 9.9 \% in validation.
-The score was also calculated for three precipitation thresholds: P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_z4}).
+The score was also calculated for three precipitation thresholds: P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_4Zo}).
 The gain in score increases with the precipitation threshold: in average, respectively for the different thresholds, 13.3\%, 15.4\% and 29.1\% in calibration and 7.9\%, 11.1\% and 34.5\% for the validation period.
@@
 			\hline 
-			ID & \multicolumn{2}{c}{z4} & \multicolumn{2}{c}{z4-hi2} & \multicolumn{2}{c}{z4-hi4} \\ 
+			ID & \multicolumn{2}{c}{4Zo} & \multicolumn{2}{c}{4Zo-2MIo} & \multicolumn{2}{c}{4Zo-4MIo} \\ 
 			& calib & valid & calib & valid & calib & valid \\ 
@@
 	\caption{Improvement (\%) of the CRPSS of the three methods.
-For z4, the improvement is relative to the reference method on the atmospheric circulation.
-For z4-hi2 and z4-hi4, the improvement is relative to the reference method on the circulation and moisture variables.}
+For 4Zo, the improvement is relative to the reference method on the atmospheric circulation.
+For 4Zo-2MIo and 4Zo-4MIo, the improvement is relative to the reference method on the circulation and moisture variables.}
 	\footnotesize
@@
 \begin{table}[htbp]
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4 method.}
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo method.}
 	\footnotesize
@@
 	\end{center}
-	\label{table:scores_thresholds_z4}
+	\label{table:scores_thresholds_4Zo}
 \end{table}
@@
 To assess the cross-compatibility of the parameters, we applied those optimized for one subregion to the others.
-The resulting losses or gains of the CRPSS are displayed in Table \ref{table:crossing_z4_calib} for the calibration period and in Table \ref{table:crossing_z4_valid} for the validation period.
+The resulting losses or gains of the CRPSS are displayed in Table \ref{table:crossing_4Zo_calib} for the calibration period and in Table \ref{table:crossing_4Zo_valid} for the validation period.
 
 \begin{table}[htbp]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4, calibration period.}
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo, calibration period.}
 	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4_calib.pdf}}
-	\label{table:crossing_z4_calib}
+	\label{table:crossing_4Zo_calib}
 \end{table}
@@
 \begin{table}[htbp]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4, validation period.}
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo, validation period.}
 	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4_valid.pdf}}
-	\label{table:crossing_z4_valid}
+	\label{table:crossing_4Zo_valid}
 \end{table}
@@
 
-The selections of the pressure levels for the analogy of circulation show a great homogeneity and is spatially consistent (Table \ref{table:levels_GA_z4}).
+The selections of the pressure levels for the analogy of circulation show a great homogeneity and is spatially consistent (Table \ref{table:levels_GA_4Zo}).
 First of all, the level 1000~hPa is selected twice (the first time at 6 or 12~h, and the second always at 30~h) and the 700~hPa is selected once for every subregion (always at 24~h).
@@
 
-The resulting spatial windows (Figure \ref{fig:spatial_windows_z4}) may look very diverse first, but there are significant similarities for subregions located within the same vicinity.
+The resulting spatial windows (Figure \ref{fig:spatial_windows_4Zo}) may look very diverse first, but there are significant similarities for subregions located within the same vicinity.
 The first 4 subregions are characterized by a large spatial window on the upper level, whereas it becomes smaller for the other subregions.
@@
 The scores show significant improvements for both the calibration and the validation period (Table \ref{table:scores_diff}).
-Even more interestingly, the results for higher precipitation thresholds (Table \ref{table:scores_thresholds_z4}) show the largest improvements.
+Even more interestingly, the results for higher precipitation thresholds (Table \ref{table:scores_thresholds_4Zo}) show the largest improvements.
 This is of particular interest in the framework of flood forecasting.
 
-The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the calibration period when they are calibrated for the given subregion (Table \ref{table:crossing_z4_calib}).
+The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the calibration period when they are calibrated for the given subregion (Table \ref{table:crossing_4Zo_calib}).
 However, the losses in CRPSS are not of the same amplitude between the different subregions.
@@
 This points to the importance of taking into account leading meteorological influences during subregion creation, which is not always best represented by the geographical distance separating them.
-Globally, the same pattern can be observed for the validation period (Table \ref{table:crossing_z4_valid}), but in this case, minor improvements may be observed when crossing the parameters.
+Globally, the same pattern can be observed for the validation period (Table \ref{table:crossing_4Zo_valid}), but in this case, minor improvements may be observed when crossing the parameters.
 The reason being that the independant validation period contains other events that may be better forecasted by other parameter sets.
@@
 
-Two methods were assessed: one with 2 moisture predictors (moisture index on 2 pressure levels or at 2 different hours) named z4-hi2, and one with 4 moisture predictors named z4-hi4.
+Two methods were assessed: one with 2 moisture predictors (moisture index on 2 pressure levels or at 2 different hours) named 4Zo-2MIo, and one with 4 moisture predictors named 4Zo-4MIo.
 When we introduce 2 predictors for the moisture analogy, the number of degrees of freedom raises to 42, and to 54 when we add 4 predictors.
@@
 
-\subsection{Results for z4-hi2 and z4-hi4 methods}
+\subsection{Results for 4Zo-2MIo and 4Zo-4MIo methods}
 
-Due to significant similarities between the results from z4-hi2 and z4-hi4, the latter will only be partly shown in order to improve readability.
+Due to significant similarities between the results from 4Zo-2MIo and 4Zo-4MIo, the latter will only be partly shown in order to improve readability.
 
 As previously, the optimized parameters differ from one subregion to another, and this event to a greater extent.
-Detailed examples are still provided for the Swiss Chablais subregion in Table \ref{table:params_GA_z4_hi2} for z4-hi2.
-The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_z4-hi2} for z4-hi2, along with the selected pressure levels for both the circulation and the moisture analogy (Table \ref{table:levels_GA_z4_hi2}).
+Detailed examples are still provided for the Swiss Chablais subregion in Table \ref{table:params_GA_4Zo_2MIo} for 4Zo-2MIo.
+The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_4Zo-2MIo} for 4Zo-2MIo, along with the selected pressure levels for both the circulation and the moisture analogy (Table \ref{table:levels_GA_4Zo_2MIo}).
 
 \begin{table}[htbp]
-	\caption{Parameters of the z4-hi2 method (atmospheric circulation on 4 levels and moisture index on 2 levels), optimized for the Chablais subregion.
-Same conventions as Table \ref{table:params_GA_z4}.}
+	\caption{Parameters of the 4Zo-2MIo method (atmospheric circulation on 4 levels and moisture index on 2 levels), optimized for the Chablais subregion.
+Same conventions as Table \ref{table:params_GA_4Zo}.}
 	\footnotesize
@@
 	\end{center}
-	\label{table:params_GA_z4_hi2}
+	\label{table:params_GA_4Zo_2MIo}
 \end{table}
@@
 \begin{table}[htbp]
-	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the z4-hi2 method, at the different subregions.}
+	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the 4Zo-2MIo method, at the different subregions.}
 	\footnotesize
@@
 	\end{center}
-	\label{table:levels_GA_z4_hi2}
+	\label{table:levels_GA_4Zo_2MIo}
 \end{table}
@@
 This results in a relative improvements that ranges from 11.5 \% to 15.6 \% compared to the reference method on the moisture analogy (Table \ref{table:scores_diff}).
-As for z4, the z4-hi2 and z4-hi4 methods present improvements of the forecast of significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
-The improvement are relatively similar for z4-hi2 (Table \ref{table:scores_thresholds_z4-hi2}) and z4-hi4 (not shown), with slightly superior scores for the latter on small precipitation (P\(\geq\)1 mm : 17.7\% and 13.0\%) and extremes (P\(\geq\)0.5\(\cdot\)P10 : 23.7\% and 29.2\%).
+As for 4Zo, the 4Zo-2MIo and 4Zo-4MIo methods present improvements of the forecast of significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
+The improvement are relatively similar for 4Zo-2MIo (Table \ref{table:scores_thresholds_4Zo-2MIo}) and 4Zo-4MIo (not shown), with slightly superior scores for the latter on small precipitation (P\(\geq\)1 mm : 17.7\% and 13.0\%) and extremes (P\(\geq\)0.5\(\cdot\)P10 : 23.7\% and 29.2\%).
 
 \begin{table}[htbp]
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized z4-hi2 method.}
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo-2MIo method.}
 	\footnotesize
@@
 	\end{center}
-	\label{table:scores_thresholds_z4-hi2}
+	\label{table:scores_thresholds_4Zo-2MIo}
 \end{table}
 
-The parameters cross-compatibility has also been assessed for the methods with moisture variables, and are shown in Tables \ref{table:crossing_z4-hi2_calib} and \ref{table:crossing_z4-hi2_valid} for the method z4-hi2 (not shown for z4-hi4, but similar).
+The parameters cross-compatibility has also been assessed for the methods with moisture variables, and are shown in Tables \ref{table:crossing_4Zo-2MIo_calib} and \ref{table:crossing_4Zo-2MIo_valid} for the method 4Zo-2MIo (not shown for 4Zo-4MIo, but similar).
 
 \begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, calibration period.}
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo-2MIo, calibration period.}
 	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi2_calib.pdf}}
-	\label{table:crossing_z4-hi2_calib}
+	\label{table:crossing_4Zo-2MIo_calib}
 \end{table}
@@
 \begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method z4-hi2, validation period.}
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo-2MIo, validation period.}
 	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi2_valid.pdf}}
-	\label{table:crossing_z4-hi2_valid}
+	\label{table:crossing_4Zo-2MIo_valid}
 \end{table}
@@
 When optimizing a method made of 2 levels of analogy, the introduction of moisture variables in the second level has an influence on the parameter values of the first level.
-This is first visible on the selection of the pressure levels for the circulation analogy, where the 1000~hPa that was previously systematically selected twice (Table \ref{table:levels_GA_z4}) is now less chosen (once or even not at all) for both za-hi2 (Table \ref{table:levels_GA_z4_hi2}) and za-hi4 (not shown).
+This is first visible on the selection of the pressure levels for the circulation analogy, where the 1000~hPa that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) is now less chosen (once or even not at all) for both 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}) and 4Zo-4MIo (not shown).
 There is indeed a shift of the previously selected 1000~hPa for higher levels, which is even slightly stronger with 4 moisture predictors than with 2.
@@
 The selected pressure levels for the analogy on the moisture index are strongly centred around 700~hPa and 600~hPa.
-No other value has been selected when considering 2 pressure levels (Table \ref{table:levels_GA_z4_hi2}), and when considering 4 levels, the 850~hPa and 500~hPa levels are additionally selected.
+No other value has been selected when considering 2 pressure levels (Table \ref{table:levels_GA_4Zo_2MIo}), and when considering 4 levels, the 850~hPa and 500~hPa levels are additionally selected.
 However, even in this latter method, the 700~hPa and 600~hPa levels still hold 78 \% of the selection.
@@
 When it comes to the moisture analogy, there is a clear trend to select 12~h and 24~h when considering 2 predictors.
-The z4-hi4 method presents more variability on the selection of the temporal windows for the moisture index.
+The 4Zo-4MIo method presents more variability on the selection of the temporal windows for the moisture index.
 
-The optimized spatial windows for the atmospheric circulation have also changed (Figure \ref{fig:spatial_windows_z4-hi2}; results of z4-hi4 are not shown but present the same trends).
+The optimized spatial windows for the atmospheric circulation have also changed (Figure \ref{fig:spatial_windows_4Zo-2MIo}; results of 4Zo-4MIo are not shown but present the same trends).
 The very large domains on the upper level of the 4 first subregions are not present anymore, and more variability can be observed.
@@
 The optimized methods also perform better than the reference method based on the moisture index (Table \ref{table:scores_diff}).
-However, there is no drastic difference between both z4-hi2 and z4-hi4 methods, which suggests that considering 4 moisture predictors is not necessary.
+However, there is no drastic difference between both 4Zo-2MIo and 4Zo-4MIo methods, which suggests that considering 4 moisture predictors is not necessary.
 When it comes to improvements for days with precipitation above our 3 thresholds (P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the forecast, mainly for heavy rainfall.
 
-The analysis of the parameters cross-compatibility (Tables \ref{table:crossing_z4-hi2_calib} and \ref{table:crossing_z4-hi2_valid}) is also very similar to the one on the circulation analogy only (results for z4-hi4 not shown as very similar).
+The analysis of the parameters cross-compatibility (Tables \ref{table:crossing_4Zo-2MIo_calib} and \ref{table:crossing_4Zo-2MIo_valid}) is also very similar to the one on the circulation analogy only (results for 4Zo-4MIo not shown as very similar).
 The same pattern can be observed, with a drop of performance for the subregions under different meteorological influences.
@@
 It can be influenced by the variability of the geopotential with altitude, and the change of some levels significance with the targeted region.
-There is a trend for the weighting of circulation predictors to decrease with the increase in pressure, as one can see in Figure \ref{fig:levels_weights} for the method z4, and in Figure \ref{fig:levels_weights_average} for the averages over the 3 methods.
+There is a trend for the weighting of circulation predictors to decrease with the increase in pressure, as one can see in Figure \ref{fig:levels_weights} for the method 4Zo, and in Figure \ref{fig:levels_weights_average} for the averages over the 3 methods.
 However, the values stay around equity.
@@
 	\end{subfigure}
-	\caption{Optimized spatial windows for the z4 method (analogy of atmospheric circulation on 4 pressure levels).
+	\caption{Optimized spatial windows for the 4Zo method (analogy of atmospheric circulation on 4 pressure levels).
 The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
-	\label{fig:spatial_windows_z4}
+	\label{fig:spatial_windows_4Zo}
 \end{figure}
@@
 	\end{subfigure}
-	\caption{Optimized spatial windows for the z4-hi2 method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 2 pressure levels).
+	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 2 pressure levels).
 The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
-	\label{fig:spatial_windows_z4-hi2}
+	\label{fig:spatial_windows_4Zo-2MIo}
 \end{figure}
@@
 	\centerline{\includegraphics[width=\linewidth]{figures/figure_levels_weights.pdf}}
-	\caption{Optimized weighting for the pressure levels of the z4 method.}
+	\caption{Optimized weighting for the pressure levels of the 4Zo method.}
 	\label{fig:levels_weights}

### 2015-11-19 Optimization case study - Journal of Hydrology/elsarticle-template.tex
First version of the analogue method description.

@@
 \usepackage{subcaption}
+%\usepackage{amsmath}
 
@@
 
+\subsection{References}
+\label{sec:references}
+
 Multiple variations of the methods exist, and most of them will not be detailed hereafter \cite[see][for more comprehensive listings]{Horton2016, BenDaoud2015}.
-However, there are mainly 2 parametrizations that are most often used for precipitation forecasting: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
+However, there are mainly 2 parametrizations that are most often used for precipitation forecasting and that will be considered as reference: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
 
@@
 
-The other most know parametrization adds a second level of analogy on moisture variables (Table \ref{table:params_R2}).
+The other most know parametrization adds a second level of analogy on moisture variables (method 2Z-2MI, Table \ref{table:params_R2}).
 The predictor that \citet{Bontron2004} found optimal for the France territory is a moisture index made of the product of the precipitable water with the relative humidity at 850~hPa.
@@
 Predictors are generally reanalysis datasets.
-We will work here with the NCEP/NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996}, but it can be any other reanalysis dataset.
+The NCEP/NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} are used here, but it can be any other reanalysis dataset.
 
-The predictand (which is to be predicted) is in our case the daily precipitation (6~a.m.
+The predictand (which is to be predicted) is in here the daily precipitation (6~a.m.
 to 6~a.m.
@@
 The time series from every available gauging station were averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.
+
+\subsection{Performance assessment}
+\label{sec:score}
+
+The most used score to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
+It allows assessing the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$.
+The better the forecast, the smaller the score.
+The mean CRPS of a forecast series of length $n$ can be written:
+
+\begin{equation}
+\label{eq:CRPS}
+CRPS = \frac{1}{n} \sum_{i=1}^{n} \left(  \int_{-\infty}^{+\infty} \left[ F_{i}(y)-H_{i}(y-y_{i}^{0})\right]^{2} dy \right) 
+\end{equation}
+where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value 1 otherwise.
+The mean CRPS is averaged on the calibration, respectively the validation periods, on all days.
+
+This score is now commonly used for the evaluation of continuous variables prediction systems \citep{Casati2008, Marty2010}.
+To compare the value of the score in regard to a reference, we often consider its skill score value, and use the climatological distribution as the reference.
+The CRPSS (\textit{Continuous Ranked Probability Skill Score}) is thus defined as following:
+
+\begin{equation}
+\label{eq:CRPSS}
+CRPSS = \frac{CRPS-CRPS_{r}}{CRPS_{p}-CRPS_{r}} = 1-\frac{CRPS}{CRPS_{r}}
+\end{equation}
+where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect forecast (which implies $CRPS_{p}~=~0$).
 

### 2015-11-19 Optimization case study - Journal of Hydrology/elsarticle-template.tex
First version of the GAs description.

@@
 Predictors are generally reanalysis datasets.
-The NCEP/NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} are used here, but it can be any other reanalysis dataset.
+NCEP-NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} are used here, but it can be any other reanalysis dataset.
 
@@
 
-%TODO: write this section
-
+Genetic Algorithms (GAs) were developed by \citet{Holland1992b} and popularized by \citet{Goldberg1989}.
+They are part of evolutionary algorithms \citep{Back1993b, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
+GAs seek the global optimum on a complex surface, theoretically without restriction.
 Practically, GAs allow rapidly approaching satisfactory solutions, but they do not provide the optimum solution for sure \citep{Zitzler2004a}.
@@
 This is a strength and a weakness of GAs: they are very good at exploring complex parameter spaces in order to identify the most promising areas, but they will not necessarily find the best solution with the optimal values of all parameters \citep{Holland1992b}.
+
+The optimizations were performed based on the recommended GAs parametrization for AMs as described in \citet{Horton2016a}.
+As the optimization is mostly sensitive to the mutation operator (that randomly changes some values in the parameters sets), we consider parallel optimizations with variants of this operator, according to \citet{Horton2016a}:
+
+\begin{itemize}
+	\item 3x non-uniform mutation \citep{Michalewicz1996} with varying parameters,
+	\item 1x multi-scale mutation \citep{Horton2016a},
+	\item 2x chromosome of adaptive search radius \citep{Horton2016a}
+\end{itemize}
+
+A population size of 500 individuals (parameters sets of the AM) was considered, and the optimization was stopped when the best individual (with the highest CRPSS performance score) did not evolve for 20 generations (cycles of the optimization).
 

### 2015-11-20 AtmoSwing - Geoscientific Model Development/template.tex
Using nomenclature.
Michel's corrections.

@@
 	\item sc : sequential calibration (can be omitted as considered as default, see section \ref{sec:atmoswing-calibration})
-	\item go : global optimization (by means of genetic algorithms for example)
+	\item go (or just ''o'') : global optimization (by means of genetic algorithms for example)
 \end{itemize}
@@
 However, we would need to redo the calibration procedure every time a new version is available, in order to reduce the bias \citep{Wilson2002}.
-Moreover, the reforecasts are not re-processed for every new version of the model, meaning we still end up with a bias between the forecast and the archive.
-Finally, the length of reanalyses datasets are usually much longer than reforecast datasets, which allows us to identify more robust relationships.
+Moreover, the length of reanalyses datasets are usually much longer than reforecast datasets, which allows us to identify more robust relationships.
 The size of the archive is indeed an important criteria for the AM.
@@
 \begin{acknowledgements}
-Thanks to Lucien Schreiber and Richard Metzger for their programming advices. Thanks to Renaud Marty for his active involvement in testing AtmoSwing against his code base.
+Thanks to Lucien Schreiber and Richard Metzger for their programming advices.
+Thanks to Renaud Marty for his active involvement in testing AtmoSwing against his code base.
+Thanks to Dominique B\'{e}rod for his support.
 
 Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
+The fruitful collaboration with the Laboratoire d?Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
 NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.

### 2015-11-20 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Michel's corrections.

@@
 \end{equation}
-where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect forecast (which implies $CRPS_{p}~=~0$).
+where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect forecast (which implies $CRPS_{p}~=~0$). A better forecast is characterized by an increase in CRPSS.
 
@@
 
-We first optimized the analogy of atmospheric circulation alone, without moisture variables, for our 10 subregions.
+We first optimized the analogy of atmospheric circulation alone, without moisture variables, for the 10 subregions.
 We started from the most simple AM, and increased the complexity in order to identify the degrees of freedom that are of particular interest.
@@
 
-We first considered the reference method for the analogy of the atmospheric circulation, based on the 500 and 1000~hPa levels.
-We let the optimizer choose the number of analogues, both spatial windows with no overlapping constraint, as well as the temporal window (hours of observation of the geopotential).
-The sequential calibration cannot automatically choose the temporal window, neither handle non-overlapping spatial windows, and finally it cannot optimize all parameters simultaneously.
-With these improvements, we could gain a relative improvement of the CRPSS of 3.97\% and 2.45\% in average for the calibration and the validation periods respectively.
+We first considered the reference method for the analogy of the atmospheric circulation (2Z, Table \ref{table:params_R1}), based on the 500 and 1000~hPa levels.
+We let the optimizer choose the number of analogues, both spatial windows with no overlapping constraint, as well as the temporal window (hours of observation of the geopotential), what the sequential calibration cannot do.
+With these degrees of freedom, we could gain a relative CRPSS improvement of 3.97\% and 2.45\% in average for the calibration and the validation periods respectively.
 Some tests showed that most of the gains are due to the non-overlapping spatial windows.
+This is not a tremendous improvement, but it demonstrated that the optimizer was able to get relevant parameters.
 
-Then, we provided an additional degree of freedom to the AGs by letting them choose the pressure levels along with the other parameters.
-Evaluation of pressure levels is also a non-automated process in the sequential calibration.
+Then, we provided an additional degree of freedom to the AGs by letting them choose the pressure levels along with the other parameters, which is also a non-automated process in the sequential calibration.
 We could observe that this degree of freedom increases the optimization time and may decrease the number of simulations that converge to a single solution.
@@
 Every time we added a new predictor to optimize, the score on the calibration period increased, but always more to a smaller extent.
-However, the score on the validation period dropped after 4 predictors, revealing an over-parametrization of the method, and thus a lack of robustness.
-We thus found that considering 4 predictors is optimal for our case study, since the gain in CRPSS is significant.
-It can not be excluded that another number would prevail under other meteorological conditions.
+However, the score value on the validation period dropped after 4 predictors, revealing an over-parametrization of the method, and thus a lack of robustness.
+Thus, considering 4 predictors is optimal for our case study, since the gain in CRPSS is significant.
+It cannot be excluded that another number would prevail in another region under other meteorological conditions.
 
@@
 
-The method we finally optimized for the analogy of the atmospheric circulation, based on 4 levels of the geopotential, and that we will name 4Zo, is made of the following degrees of freedom:
+The method finally optimized for the atmospheric circulation analogy, based on 4 levels of the geopotential, and that we will name 4Zo, is made of the following degrees of freedom:
 
@@
 	\item the temporal windows (4 degrees)
-	\item the spatial windows (16 degrees)
+	\item the spatial windows (4x4 degrees)
 	\item the weights (4 degrees)
-	\item the number of analogues (1 degrees).
+	\item the number of analogues (1 degree).
 \end{itemize}
@@
 An example of the detailed parameters is provided for the Swiss Chablais in Table \ref{table:params_GA_4Zo}.
-The optimized spatial windows are given for every subregion in Figure \ref{fig:spatial_windows_4Zo}, and the selected pressure levels in Table~\ref{table:levels_GA_4Zo}.
+The optimized spatial windows are given for every subregion in Figure \ref{fig:spatial_windows_4Zo}, and the selected pressure levels in Table \ref{table:levels_GA_4Zo}.
 
@@
 	\caption{Parameters of the 4Zo method (analogy on 4 levels of the atmospheric circulation) optimized for the Chablais subregion.
-The columns are the following: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
+The columns are the following: L = level of analogy, V = meteorological variable, H = hour of observation or temporal window, D = domain or spatial window, W = weighting of the score for the selected pressure levels, C = criteria, N = number of analogues.}
 	\footnotesize
@@
 \begin{table}[htbp]
-	\caption{CRPSS score (\%) of the three optimized methods.}
+	\caption{CRPSS score (\%) of the three optimized methods (4Zo is the atmospheric circulation analogy detailed in the present section; 4Zo-2MIo and 4Zo-4MIo add a second level of analogy on moisture indexes, as explained in section \ref{sec:optim_moisture}).}
 	\footnotesize
@@
 \begin{table}[htbp]
-	\caption{Improvement (\%) of the CRPSS of the three methods.
-For 4Zo, the improvement is relative to the reference method on the atmospheric circulation.
-For 4Zo-2MIo and 4Zo-4MIo, the improvement is relative to the reference method on the circulation and moisture variables.}
+	\caption{Same as Table \ref{table:scores}, but expressed as the CRPSS improvement (\%) compared to the reference methods.
+For 4Zo, the improvement is relative to the reference method on the atmospheric circulation (2Z, Table \ref{table:params_R1}).
+For 4Zo-2MIo and 4Zo-4MIo, the improvement is relative to the reference method on the circulation and moisture variables (2Z-2MI, Table \ref{table:params_R2}).}
 	\footnotesize
@@
 Thanks to Renaud Marty for his fruitful collaboration over the years.
+Thanks to Dominique B\'{e}rod for his support.
 
 Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
+The fruitful collaboration with the Laboratoire d’Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
 NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.

### 2015-11-20 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Using acronyms for calibration and validation periods.

@@
 
-The 48 years precipitation dataset (see section \ref{sec:intro}.\ref{sec:data}) was divided into a calibration period and a validation period.
-Using data independent from the calibration period to validate our results is very important in order to assess the robustness of the improvements and to avoid overparametrization of the method.
+The 48 years precipitation dataset (see section \ref{sec:intro}.\ref{sec:data}) was divided into a calibration period (CP) and a validation period (VP).
+Using data independent from the CP to validate our results is very important in order to assess the robustness of the improvements and to avoid overparametrization of the method.
 
-In order to reduce potential bias related to trends in the climate change or to the evolution in measurement techniques, the selection of the validation period is evenly distributed over the entire series \citep{BenDaoud2010}.
-Thus, we selected one year every six years for validation, which represents a total of 8 years for the validation and 40 for calibration.
-The choice of the sequence was made in order to have similar statistical characteristics between the calibration and the validation periods.
+In order to reduce potential bias related to trends in the climate change or to the evolution in measurement techniques, the selection of the VP is evenly distributed over the entire series \citep{BenDaoud2010}.
+Thus, we selected one year every six years for validation, which represents a total of 8 years for the VP and 40 for CP.
+The choice of the sequence was made in order to have similar statistical characteristics between the CP and the VP.
 
@@
 We let the optimizer choose the number of analogues, both spatial windows with no overlapping constraint, as well as the temporal window (hours of observation of the geopotential), what the sequential calibration cannot do.
-With these degrees of freedom, we could gain a relative CRPSS improvement of 3.97\% and 2.45\% in average for the calibration and the validation periods respectively.
+With these degrees of freedom, we could gain a relative CRPSS improvement of 3.97\% and 2.45\% in average for the CP and the VP respectively.
 Some tests showed that most of the gains are due to the non-overlapping spatial windows.
@@
 However, most solutions were very close in terms of score.
-The averaged relative improvement of the CRPSS is 5.63\% for the calibration and 3.82\% for the validation periods.
+The averaged relative improvement of the CRPSS is 5.63\% for the CP and 3.82\% for the VP.
 The pressure levels that were chosen are 500~hPa or 700~hPa for the upper level, and 925~hPa or 1000~hPa (most often) for the lower level.
@@
 There was no constraint on the predictors, so that the same pressure level could be selected multiple times.
-Some improvements were found on the score, both for the calibration and the validation periods, confirming that this additional information is beneficial for the quality of the forecast.
+Some improvements were found on the score, both for the CP and the VP, confirming that this additional information is beneficial for the quality of the forecast.
 We then tried with 4 predictors, and so on, up to 8.
-Every time we added a new predictor to optimize, the score on the calibration period increased, but always more to a smaller extent.
-However, the score value on the validation period dropped after 4 predictors, revealing an over-parametrization of the method, and thus a lack of robustness.
+Every time we added a new predictor to optimize, the score on the CP increased, but always more to a smaller extent.
+However, the score value on the VP dropped after 4 predictors, revealing an over-parametrization of the method, and thus a lack of robustness.
 Thus, considering 4 predictors is optimal for our case study, since the gain in CRPSS is significant.
@@
 An example of the detailed parameters is provided for the Swiss Chablais in Table \ref{table:params_GA_4Zo}.
-The optimized spatial windows are given for every subregion in Figure \ref{fig:spatial_windows_4Zo}, and the selected pressure levels in Table \ref{table:levels_GA_4Zo}.
+The optimized spatial windows are given for every subregion in Figure \ref{fig:spatial_windows_4Zo}, and the selected pressure levels in Table~\ref{table:levels_GA_4Zo}.
 
-\begin{table}[htbp]
+\begin{table}[htb]
 	\caption{Parameters of the 4Zo method (analogy on 4 levels of the atmospheric circulation) optimized for the Chablais subregion.
@@
 
-\begin{table}[htbp]
+\begin{table}[htb]
 	\caption{Pressure levels ($\sim$) automatically selected for the 4Zo method at the different subregions.}
@@
 
-The resulting CRPSS scores are provided in Table \ref{table:scores} and is in average 35.8 \% in calibration and 35.5 \% in validation.
-The improvement of the CRPSS score relatively to the reference method on the atmospheric circulation is provided in Table \ref{table:scores_diff} and is in average 15.3 \% in calibration and 9.9 \% in validation.
-The score was also calculated for three precipitation thresholds: P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_4Zo}).
-The gain in score increases with the precipitation threshold: in average, respectively for the different thresholds, 13.3\%, 15.4\% and 29.1\% in calibration and 7.9\%, 11.1\% and 34.5\% for the validation period.
-The optimized method improves thus even more the forecasts for days with significant precipitation than usual days.
-
-\begin{table}[htbp]
+\begin{table}[htb]
 	\caption{CRPSS score (\%) of the three optimized methods (4Zo is the atmospheric circulation analogy detailed in the present section; 4Zo-2MIo and 4Zo-4MIo add a second level of analogy on moisture indexes, as explained in section \ref{sec:optim_moisture}).}
@@
 			ID & \multicolumn{2}{c}{4Zo} & \multicolumn{2}{c}{4Zo-2MIo} & \multicolumn{2}{c}{4Zo-4MIo} \\ 
-			& calib & valid & calib & valid & calib & valid \\ 
+			& CP & VP & CP & VP & CP & VP \\ 
 			\hline 
@@
 
-\begin{table}[htbp]
+\begin{table}[htb]
 	\caption{Same as Table \ref{table:scores}, but expressed as the CRPSS improvement (\%) compared to the reference methods.
@@
 
-\begin{table}[htbp]
+\begin{table}[htb]
 	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo method.}
@@
 			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\ 
-			& calib & valid & calib & valid & calib & valid \\ 
+			& CP & VP & CP & VP & CP & VP \\ 
 			\hline 
@@
 
+The resulting CRPSS scores are provided in Table \ref{table:scores} and are in average 35.8 \% for the CP and 35.5 \% for the VP.
+The improvement of the CRPSS score relatively to the reference method on the atmospheric circulation is provided in Table \ref{table:scores_diff} and is in average 15.3 \% for the CP and 9.9 \% for the VP.
+The score was also calculated for three precipitation thresholds: P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_4Zo}).
+The gain in score increases with the precipitation threshold: in average, respectively for the different thresholds, 13.3\%, 15.4\% and 29.1\% for the CP and 7.9\%, 11.1\% and 34.5\% for the VP.
+The optimized method improves thus even more the forecasts for days with significant precipitation than usual days.
+
 To assess the cross-compatibility of the parameters, we applied those optimized for one subregion to the others.
-The resulting losses or gains of the CRPSS are displayed in Table \ref{table:crossing_4Zo_calib} for the calibration period and in Table \ref{table:crossing_4Zo_valid} for the validation period.
+The resulting losses or gains of the CRPSS are displayed in Table \ref{table:crossing_4Zo_calib} for the CP and in Table \ref{table:crossing_4Zo_valid} for the VP.
 
@@
 
-The scores show significant improvements for both the calibration and the validation period (Table \ref{table:scores_diff}).
+The scores show significant improvements for both the CP and the VP (Table \ref{table:scores_diff}).
 Even more interestingly, the results for higher precipitation thresholds (Table \ref{table:scores_thresholds_4Zo}) show the largest improvements.
@@
 
-The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the calibration period when they are calibrated for the given subregion (Table \ref{table:crossing_4Zo_calib}).
+The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the CP when they are calibrated for the given subregion (Table \ref{table:crossing_4Zo_calib}).
 However, the losses in CRPSS are not of the same amplitude between the different subregions.
@@
 This points to the importance of taking into account leading meteorological influences during subregion creation, which is not always best represented by the geographical distance separating them.
-Globally, the same pattern can be observed for the validation period (Table \ref{table:crossing_4Zo_valid}), but in this case, minor improvements may be observed when crossing the parameters.
-The reason being that the independant validation period contains other events that may be better forecasted by other parameter sets.
+Globally, the same pattern can be observed for the VP (Table \ref{table:crossing_4Zo_valid}), but in this case, minor improvements may be observed when crossing the parameters.
+The reason being that the independant VP contains other events that may be better forecasted by other parameter sets.
 The relative small differences in score between parametrizations indicate that even though the parameters may differ significantly, the performance may not be drastically affected.
@@
 			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\  
-			& calib & valid & calib & valid & calib & valid \\ 
+			& CP & VP & CP & VP & CP & VP \\ 
 			\hline 
@@
 This is particularly true for higher pressure levels and can be more critical for lower layers.
-It was thus interesting to sometimes get several sets of near-optimal parameters, but with some nuances, in order to have an idea of the sensitivity of the parameters for a given region, and to compare the score on the validation period.
+It was thus interesting to sometimes get several sets of near-optimal parameters, but with some nuances, in order to have an idea of the sensitivity of the parameters for a given region, and to compare the score on the VP.
 In this regard, a cross-validation technique may be advisable.

### 2015-11-20 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Some personal corrections.

@@
 The gain in score increases with the precipitation threshold: in average, respectively for the different thresholds, 13.3\%, 15.4\% and 29.1\% for the CP and 7.9\%, 11.1\% and 34.5\% for the VP.
-The optimized method improves thus even more the forecasts for days with significant precipitation than usual days.
+The optimized improves thus even more the forecasts for days with significant precipitation than usual days.
 
@@
 \begin{table}[htbp]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo, validation period.}
+	\caption{Same as Table \ref{table:crossing_4Zo_calib} but for the validation period.}
 	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4_valid.pdf}}
@@
 
-The selections of the pressure levels for the analogy of circulation show a great homogeneity and is spatially consistent (Table \ref{table:levels_GA_4Zo}).
-First of all, the level 1000~hPa is selected twice (the first time at 6 or 12~h, and the second always at 30~h) and the 700~hPa is selected once for every subregion (always at 24~h).
-The level which varies from one subregion to another is the upper level (always at 12~h), that is 300~hPa for the North-West part of the catchment, 500~hPa for most of the subregions, and 600~hPa for the Conches Valley.
+The automatic selections of the pressure levels (Table \ref{table:levels_GA_4Zo}) and the temporal windows (not shown) for the analogy of circulation show a great homogeneity and are spatially consistent.
+First of all, the level 1000~hPa is always selected twice (the first time at 6 or 12~h, and the second always at 30~h) and the 700~hPa is selected once for every subregion (always at 24~h).
+The level which varies from one subregion to another is the upper level (however always at 12~h), that is 300~hPa for the North-West part of the catchment, 500~hPa for most of the subregions, and 600~hPa for the Conches Valley.
 Its spatial distribution is however homogeneous.
@@
 The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the CP when they are calibrated for the given subregion (Table \ref{table:crossing_4Zo_calib}).
-However, the losses in CRPSS are not of the same amplitude between the different subregions.
+However, the losses in CRPSS when exchanging the parameters are not of the same amplitude between the different subregions.
 Indeed, the Upper Rhone Valley (7) and moreover the Southeast ridges (8) seem to behave significantly differently.
@@
 Parameter sets from other subregions perform poorly for these subregions, and vice versa.
-Nevertheless, both subregions seem quite inter-compatible.
-This points to the importance of taking into account leading meteorological influences during subregion creation, which is not always best represented by the geographical distance separating them.
+This points to the importance of taking into account leading meteorological influences during discretization, that are not always best represented by their physical distance.
 Globally, the same pattern can be observed for the VP (Table \ref{table:crossing_4Zo_valid}), but in this case, minor improvements may be observed when crossing the parameters.
@@
 The relative small differences in score between parametrizations indicate that even though the parameters may differ significantly, the performance may not be drastically affected.
-Even a change in the pressure level does not mean a radical drop of the score.
+Even a change in the pressure level does not mean a radical drop of the score value.
 A different parametrization leads to a different selection of the analogue days, and thus to an improvement of the forecast of certain weather conditions at the expense of others.
@@
 We previously worked with a method based on a unique level of analogy.
-However, we know that moisture variables in a second level of analogy do provide improvements to the method (section \ref{sec:intro}.\ref{sec:analog_method}).
-So we also wanted to optimize the moisture index, which is a combination of the relative humidity and the precipitable water.
+However, we know that moisture variables as a second level of analogy do provide improvements to the method (section \ref{sec:analog_method}).
+The moisture index, which is a combination of the relative humidity and the precipitable water, has thus also been optimized.
 In order to do so, we had to introduce a constraint to the optimizer, so that it selects the same temporal window for both variables.
@@
 Two methods were assessed: one with 2 moisture predictors (moisture index on 2 pressure levels or at 2 different hours) named 4Zo-2MIo, and one with 4 moisture predictors named 4Zo-4MIo.
-When we introduce 2 predictors for the moisture analogy, the number of degrees of freedom raises to 42, and to 54 when we add 4 predictors.
+When introducing 2 predictors for the moisture analogy, the number of degrees of freedom raises to 42, and to 54 with 4 predictors.
 
@@
 
-As previously, the optimized parameters differ from one subregion to another, and this event to a greater extent.
+As previously, the optimized parameters differ from one subregion to another, and this even to a greater extent.
 Detailed examples are still provided for the Swiss Chablais subregion in Table \ref{table:params_GA_4Zo_2MIo} for 4Zo-2MIo.
@@
 
-The CRPSS scores of the optimized methods are provided in Table \ref{table:scores} and amounts to slightly more than 40 \% for both methods and for both periods.
-This results in a relative improvements that ranges from 11.5 \% to 15.6 \% compared to the reference method on the moisture analogy (Table \ref{table:scores_diff}).
-As for 4Zo, the 4Zo-2MIo and 4Zo-4MIo methods present improvements of the forecast of significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
-The improvement are relatively similar for 4Zo-2MIo (Table \ref{table:scores_thresholds_4Zo-2MIo}) and 4Zo-4MIo (not shown), with slightly superior scores for the latter on small precipitation (P\(\geq\)1 mm : 17.7\% and 13.0\%) and extremes (P\(\geq\)0.5\(\cdot\)P10 : 23.7\% and 29.2\%).
-
 \begin{table}[htbp]
@@
 
+The CRPSS scores of the optimized methods are provided in Table \ref{table:scores} and amounts to slightly more than 40 \% for both methods and for both periods.
+This results in a relative improvements that ranges from 11.5 \% to 15.6 \% compared to the reference method on the moisture analogy (Table \ref{table:scores_diff}).
+As for 4Zo, the 4Zo-2MIo and 4Zo-4MIo methods present improvements of the forecast for significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
+The improvement are relatively similar for 4Zo-2MIo (Table \ref{table:scores_thresholds_4Zo-2MIo}) and 4Zo-4MIo (not shown), with slightly superior scores for the latter on small precipitation (P\(\geq\)1 mm : 17.7\% and 13.0\%) and extremes (P\(\geq\)0.5\(\cdot\)P10 : 23.7\% and 29.2\%).
+
 The parameters cross-compatibility has also been assessed for the methods with moisture variables, and are shown in Tables \ref{table:crossing_4Zo-2MIo_calib} and \ref{table:crossing_4Zo-2MIo_valid} for the method 4Zo-2MIo (not shown for 4Zo-4MIo, but similar).
@@
 \begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo-2MIo, validation period.}
+	\caption{Same as Table \ref{table:crossing_4Zo-2MIo_calib} but for the validation period.}
 	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi2_valid.pdf}}
@@
 This change is likely due to the fact that when considering only the circulation analogy, the method tries to take into account information that can serve as proxy for moisture assessment, whereas it doesn't need it with the moisture index.
-This aspect has never been demonstrated, as sequential calibration tools do not allow it.
+This aspect has never been demonstrated before, as sequential calibration tools do not allow it.
 It can only be assessed by a global optimization technique that can tune jointly both levels of analogy.
@@
 The selected pressure levels for the analogy on the moisture index are strongly centred around 700~hPa and 600~hPa.
-No other value has been selected when considering 2 pressure levels (Table \ref{table:levels_GA_4Zo_2MIo}), and when considering 4 levels, the 850~hPa and 500~hPa levels are additionally selected.
+No other value has been selected when considering 2 pressure levels (Table \ref{table:levels_GA_4Zo_2MIo}), and when considering 4 levels, 850~hPa and 500~hPa are sometimes also selected (not shown).
 However, even in this latter method, the 700~hPa and 600~hPa levels still hold 78 \% of the selection.
@@
 When it comes to the moisture analogy, there is a clear trend to select 12~h and 24~h when considering 2 predictors.
-The 4Zo-4MIo method presents more variability on the selection of the temporal windows for the moisture index.
 
@@
 The same pattern can be observed, with a drop of performance for the subregions under different meteorological influences.
-However, the losses of performance are globally more important than before, suggesting that more complex methods with moisture variables are less transposable to another subregion, even though it is located within the same grid of the reanalysis dataset.
+However, the losses of performance are globally more important than before, suggesting that more complex methods with moisture variables are less transposable to another subregion, even though it is located within the same grid cell of the reanalysis dataset.
 
@@
 Beyond that value the validation score drops, revealing a lost in robustness due to over-parametrization.
-	\item The automatic and joint optimization of all parameters: the analogues number, the selection of the pressure levels and the time windows, and the spatial windows.
+	\item The automatic and joint optimization of all parameters: the analogues number, the selection of the pressure levels and the temporal windows, and the spatial windows.
 These parameters are highly interdependent, so we need to optimize them jointly in order to identify optimal combinations.
@@
 The resulting parameters may sometimes present significant differences, even though the score is almost similar.
-Through some Monte-Carlo analyses of the parameter space properties of the AM, \citet{Horton2012a} showed that some parameters of the method have a wide range of acceptable values.
+Through some Monte-Carlo analyses of the parameter space properties of the AM, \citet{Horton2012a} showed that some parameters of the method have a wide range of acceptable values \citep[see also][]{Horton2016}.
 The spatial windows, for example, can be larger than the optimal size without much impact on the score, while they cannot be smaller \citep[see also][]{Bontron2004}.
@@
 In this regard, a cross-validation technique may be advisable.
-An approach that can also be recommended, and that we use, is to first explore a wide range of the parameter space with some optimizations, and to narrow it according to the results for more targeted optimizations that are likely to go faster and to perform better.
+An approach that can also be recommended is to first explore a wide range of the parameter space with some optimizations, and to narrow it according to the results for more targeted optimizations that are likely to go faster and to perform better.
 
@@
 We also noticed in another unpublished work, that it is by far better to optimize for 2 subregions jointly rather than to optimize on one and to apply its parametrization to the other.
-Finally, the creation of the subregions is an important process and should be handled with care.
-Indeed, the geographical proximity is not always the leading factor to define a subregion.
+Finally, the discretization in subregions is an important process and should be handled with care.
+Indeed, the physical distance is not always the leading factor to define a subregion.
 For example, the Southeast ridges subregion do not behave like its surrounding and differ in its parametrization, due to different leading meteorological influences.
@@
 
-%TODO: complete
-
-The parameters resulting from the optimization are very consistent for the analogy of the atmospheric circulation, in terms of selection of the pressure levels, and the temporal and spatial windows.
+The parameters resulting from the optimization by GAs are very consistent for the analogy of the atmospheric circulation, in terms of selection of the pressure levels, and the temporal and spatial windows.
 There are clear trends or even identical results for subregions under similar meteorological influences, which confirm that the optimized parameters are coherent, despite an eventual first impression of a great variability in the spatial windows.
@@
 
-We were able to identify that there is a parametric dependence between the analogy of circulation and the moisture.
-When we consider the two levels together, the optimal parameters of the analogy of circulation are different.
+We were able to identify that there is a parametric dependence between the analogy of circulation and the moisture variables.
+When we consider the two levels together, the optimal parameters of the circulation analogy are different.
 This complexity can only be exploited in a suitable manner by global optimization methods.
@@
 
-GAs provide parametrizations of the AM that exceed the performance of the sequential calibration.
+GAs provide parametrizations of AMs that exceed the performance of the sequential calibration.
 In addition, we could observe that the forecasts for days with strong precipitation were significantly more improved, which is clearly interesting in the framework of flood forecasting.
 
-This work is by far not exhaustive and means to open a door for new explorations with the AMs.
+This work is by far not exhaustive and means to open a door for new explorations of AMs with GAs.
 It becomes possible to even let the optimizer chose the meteorological variable to be used as predictor, as well as the analogy criteria.

### 2015-11-20 Genetic algorithms - Journal of Climate/template.tex
Michel's corrections.
Removing we/our in the article on GAs.

@@
 These kind of optimization techniques need however to be tailored to the problem to solve.
-We had to assess multiple combinations of algorithms, and even to develop new operators, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of genetic algorithms to optimize the analogue method.
+Multiple combinations of algorithms had to be assessed, and even new operators were developed, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of genetic algorithms to optimize the analogue method.
 These recommendations are a consequent outcome of this work, as it opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.
@@
 
-We observed during the AM calibration that the resulting parameters vary with the initial choices (such as the number of analogues).
+During the AM calibration it has been found that the resulting parameters may vary with initial choices (such as the number of analogues).
 In addition, the different levels of analogy (eg.
 on the atmospheric circulation and the moisture index) are always calibrated sequentially.
-However, we cannot exclude any dependency between them, which could lead us to select another parametrization if we calibrate them together.
+However, any dependency between them cannot be excluded, which could lead us to select another parametrization if calibrated together.
 Simultaneous calibration of all parameters has never been undertaken so far.
@@
 
-Our ambition was then to assess the feasibility of an automatic optimization of the AM in order to assess all parameters simultaneously, and thus to be able to get nearer to the global optimum in the parameters space.
+The goal was then to assess the feasibility of an automatic optimization of the AM in order to assess all parameters simultaneously, and thus to be able to get nearer to the global optimum in the parameters space.
 In addition, it can overcome the systematic manual assessments of all pressure levels and temporal windows.
@@
 The GAs optimize a population of $N$ individuals (parameter sets).
-Each individual contains a chromosome (parameters of the AM in our case).
-We call gene every parameter that constitutes the chromosome.
+Each individual contains a chromosome (parameters of the AM in this case).
+Genes are all parameters constituting the chromosome.
 The floating-point representation \citep[instead of the canonical binary, see][]{Goldberg1989, Goldberg1990a, Holland1992b} of the genes was considered, as it was found more suited in multiple applications \citep{Michalewicz1996, Herrera1998a, Haupt2004, Back1996b, Gaffney2010a}.
@@
 
-All operators we used and their options, applied to floating-point coding, are described in the following sections. Many other operators exist, but we will only present the ones we evaluated.
+All considered operators and their options, applied to floating-point coding, are described in the following sections. Many other operators exist, but only the ones evaluated are presented.
 
@@
 The first step of the optimization is to generate the initial population.
-A population is a set of $N$ individuals (each of which represents a point in the space of potential solutions, a parameter set of the AM in our application) that we are going to make evolve.
+A population is a set of $N$ individuals (each of which represents a point in the space of potential solutions, a parameter set of the AM in this application) that are going to evolve.
 A generation is the population at a given time.
@@
 	\end{equation}
-	In our application, the last individual ($N_{mp}$) has zero probability of being selected.
+	In this application, the last individual ($N_{mp}$) has zero probability of being selected.
 
@@
 \begin{itemize}
-	\item Single-point crossover: a crossover point is randomly chosen for the pair. The genes (our parameters) located after that point are exchanged in between the two chromosomes.
+	\item Single-point crossover: a crossover point is randomly chosen for the pair. The genes (AM parameters) located after that point are exchanged in between the two chromosomes.
 
@@
 Its optimum configuration depends on the size of the chromosomes, of the properties of the objective function, and of the population size \citep{Back1992b}.
-We implemented this operator according to equation \ref{equation_mutation_uniformvariable}.
+This operator was implemented according to equation \ref{equation_mutation_uniformvariable}.
 	\begin{equation}
@@
 
-	\item Variable normal mutation: with the same logic as the variable uniform mutation, we tested a mutation operator using a normal distribution with a variable mutation rate and standard deviation.
+	\item Variable normal mutation: with the same logic as the variable uniform mutation, a mutation operator was tested using a normal distribution with a variable mutation rate and standard deviation.
 The mutation rate is calculated with equation \ref{equation_mutation_uniformvariable}.
-On the same principle, we decrease linearly the standard deviation over the generations:
+On the same principle, the standard deviation decreases linearly over the generations:
 	\begin{equation}
@@
 
-	We adapted this operator for our application, which is not based on a predefined number of generations:
+	This operator was adapted for this application, which is not based on a predefined number of generations:
 	\begin{equation}
@@
 
-	\item Individual adaptive search radius (new): based on the ideas of the non-uniform mutation, we introduce a search radius in the approach of individual adaptive mutation rates.
+	\item Individual adaptive search radius (new): based on the ideas of the non-uniform mutation, a search radius was introduced in the approach of individual adaptive mutation rates.
 This search radius $r_{a}$, bounded between 0 and 1, is also adaptive and behaves similarly to the adaptive mutation rates.
@@
 The main advantage is that the tuning of the mutation can be much more precise \citep{Smith1997a}.
-We therefore consider a second chromosome containing the mutation rate for each gene of the first chromosome.
+A second chromosome containing the mutation rate for each gene of the first chromosome was therefore considered.
 The operations of mutation and self-mutation are similar to the case of the individual adaptive mutation rate, but in a distributed way, within the chromosome.
-Another difference is that we apply the same crossover operations as those applied to the first chromosome, and this for the same crossing points.
+Another difference is that the same crossover operations are applied as those applied to the first chromosome, and this for the same crossing points.
 Thus, during an exchange of genes, children also inherit the mutation rates specific for each of these genes.
 
-	\item Chromosome of adaptive search radius (new): we introduced this operator that combines the operations of the chromosome of adaptive mutation rate to our adaptive search radius approach.
+	\item Chromosome of adaptive search radius (new): this operator combines the operations of the chromosome of adaptive mutation rate to the adaptive search radius approach.
 Similarly, an individual has 3 chromosomes: the first containing the values to be optimized, the second the distributed mutation rate, and the last one, the distributed search radius.
@@
 
-	\item Multi-scale mutation (new): finally, we developed another approach, that is also based on the search radius concept.
+	\item Multi-scale mutation (new): finally, another approach was developed that is also based on the search radius concept.
 However, the latter is not decreasing with time.
 Methods based on a reduction of the mutation rate or radius simulate a transition from the exploration phase to the exploitation one.
-We wanted to test an approach that combines both exploration and exploitation during the whole optimization.
-Thus, we considered the search radius $r_{a}$ of equation \ref{equation_mutation_rayon_adaptatif} as a random value for each individual, but restricted to 4 equiprobable values: 1, 0.5, 0.1, 0.02, which range from full exploration to fine exploitation.
+The idea was to test an approach that combines both exploration and exploitation during the whole optimization.
+Thus, the search radius $r_{a}$ of equation \ref{equation_mutation_rayon_adaptatif} was considered as a random value for each individual, but restricted to 4 equiprobable values: 1, 0.5, 0.1, 0.02, which range from full exploration to fine exploitation.
 The only external parameter is the mutation rate which is fixed.
@@
 
-We used a process of elitism on the natural selection as well as on mutations.
-This ensures the survival of the best individual so that we do not lose a better solution.
+A process of elitism was introduced on the natural selection as well as on mutations.
+This ensures the survival of the best individual so that a better solution is never lost.
 After the natural selection operator, if the best individual has not been selected, it is copied to the IG instead of an individual randomly picked.
@@
 The stopping criteria are not often well documented in GAs case studies.
-We chose to stop the optimization if the best individual does not change for $x$ generations.
+The optimization is here stopped if the best individual does not change for $x$ generations.
 This value should not be too low to allow the algorithm to escape from a local optima.
 In addition, the rate of improvement decreases with the progression of the optimization.
-It is thus common that the best individual does not evolve over several generations when we get closer to the global solution.
+It is thus common that the best individual does not evolve over several generations when getting closer to the global solution.
 A value of $x=20$ generations was chosen.
@@
 GAs are very computationally intensive because they require many evaluations of the objective function.
-These assessments are very long in our application, as they require calculating and assessing a forecast for every day of the calibration period, thus over several decades.
-In order to reduce the computation time, we avoid recalculating the performance score of an individual who has previously been evaluated and that has not changed.
-We keep the score of each individual living in the selection until it mutates.
+These assessments are very long in this application, as they require calculating and assessing a forecast for every day of the calibration period, thus over several decades.
+In order to reduce the computation time, recalculating the performance score of an individual who has previously been evaluated and that has not changed was avoided.
+Thus, the score of each individual living in the selection was kept until it mutates.
 
@@
 
-One of our goals being to make recommendations of parametrization in order to optimize the AM, we proceeded systematically.
+One of the goals being to make recommendations of parametrization in order to optimize the AM, a systematic procedure was adopted.
 The results are summarized hereafter \citep[see][for the details]{Horton2012a}.
-We used concepts from the factorial design approach \citep[see eg.][]{Costa2005a,Costa2007a,Mariano2010a}, which is sometimes used for comparative analysis of different parametrizations of GAs.
+Concepts were taken from the factorial design approach \citep[see eg.][]{Costa2005a,Costa2007a,Mariano2010a}, which is sometimes used for comparative analysis of different parametrizations of GAs.
 It allows isolating the effect of a parameter under different combinations of the other options.
-We processed by stages, analysing in details and in a systematic way every variants of the implemented operators, in combination with multiple other options and parameters in order to take into account eventual co-dependencies.
-Our goal here is not to focus on the performance score we obtain through optimization, neither the values of the new optimized parameters \citep[covered in][]{Horton2016b}, but to explain how to use GAs to optimize AMs in an efficient way.
-
-In order to evaluate a combination of operators/options, we processed 10 optimizations per parametrization of GAs.
+A procedure by stages was adopted, analyzing in details and in a systematic way every variants of the implemented operators, in combination with multiple other options and parameters in order to take into account eventual co-dependencies.
+The goal here is not to focus on the performance score obtained through optimization, neither the values of the new optimized parameters \citep[covered in][]{Horton2016b}, but to explain how to use GAs to optimize AMs in an efficient way.
+
+In order to evaluate a combination of operators/options, 10 optimizations per parametrization of GAs were processed.
 The performances were characterized by four indicators: (i) mean performance score: average of the final scores of the 10 optimizations, (ii) convergence: the number of optimizations that converged to a supposed global optimum, (iii) number of generations: characterization of the convergence speed, and (iv) number of evaluations of the objective function: characterization of the required calculation time.
@@
 Indeed, the performance score of the sequential approach has been quickly exceeded without adding any new parameter to the method (Figure \ref{fig:gas_evolution_good}).
-Even GAs parametrization that we will consider further as inadequate (Figure \ref{fig:gas_evolution_bad}) did significantly better that the sequential approach.
+Even GAs parametrization that will be further considered as inadequate (Figure \ref{fig:gas_evolution_bad}) did significantly better that the sequential approach.
 
@@
 It means that we compare the effect of the studied operator when all the other operators are equivalent, while assessing multiple combinations.
-We then summarize this contribution relatively to the other options, as a percentage of gain/loss regarding the mean of all variants.
-For example, to evaluate the performance of the uniform crossover operator, we compare its performance to the average of all crossover operators while retaining the same population size, the same mutation operators, natural selection, and selection of couples.
+This contribution is then summarized relatively to the other options, as a percentage of gain/loss regarding the mean of all variants.
+For example, to evaluate the performance of the uniform crossover operator, its performance is compared to the average of all crossover operators while retaining the same population size, the same mutation operators, natural selection, and selection of couples.
 
@@
 
-We evaluated every combination of 6 options for the couples selection (Table \ref{tab:assessed_couples_selection_operators}) and 21 for the chromosome crossover operators (Table \ref{tab:assessed_crossover_operators}), along with variants of the other operators.
+Every combination of 6 options for the couples selection (Table \ref{tab:assessed_couples_selection_operators}) and 21 for the chromosome crossover operators (Table \ref{tab:assessed_crossover_operators}) were evaluated, along with variants of the other operators.
 This results in 1,008 combinations, requiring 10,080 optimizations.
@@
 The performance of the couples selection operator are relatively close (Figure \ref{fig:operator_selectcoupl_score}).
-Overall, we observe that the tournament selection with 3~candidates is slightly superior to others, along with the roulette wheel weighting.
+Overall, the tournament selection with 3~candidates is slightly superior to others, along with the roulette wheel weighting.
 This last one is however a bit less effective in terms of convergence and number of evaluations (not shown).
-The couples selection operator has not a significant role in our application.
+The couples selection operator has not a significant role in this application.
 
@@
 Each of the 10 different implementations (see section \ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Table \ref{tab:assessed_mutation_operators}), bringing the number of its variations up to 109.
-We also did some optimizations without any mutation as a reference.
+Some optimizations without any mutation were also performed as a reference.
 Along with variants of the other operators \citep[see][for the details]{Horton2012a}, it resulted in 660 combinations (so 6,600 optimizations).
@@
 The mutation operators based on a variable normal or variable uniform laws work very poorly and are difficult to configure.
-We then observe many operators more or less with the same performance scores and requiring a variable amount of assessments.
-The convergence analysis \citep[see][]{Horton2012a} allows us to highlight three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
-Because of the importance of the mutation operator on the resulting performance, we studied its role and parametrization in more detail.
-Thus, we performed different optimizations using variants of these 3 operators (Table \ref{tab:assessed_mutation_operators_bis}).
+Many operators present more or less with the same performance scores and require a variable amount of assessments.
+The convergence analysis \citep[see][]{Horton2012a} allows to highlight three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
+Because of the importance of the mutation operator on the resulting performance, its role and parametrization were studied in more detail.
+Thus, different optimizations were performed using variants of these 3 operators (Table \ref{tab:assessed_mutation_operators_bis}).
 
@@
 However, some less relevant optimizations do not match the previous results.
-We could clearly observe, through different applications, that the automatic selection of the pressure level significantly increases the difficulty for GAs to converge to a unique solution, ideally the global optimum.
+Through different applications, the automatic selection of the pressure level was shown to significantly increase the difficulty for GAs to converge to a unique solution, ideally the global optimum.
 A difficulty is that the pressure levels are considered within the optimization without continuity between values, and thus the approaches relying on distance in the parameters space, such as the search radius, cannot fully exploit the properties that make them efficient.
@@
 
-Then, we performed the same optimization, but for another region, sensitive to other meteorological influences (Figure \ref{fig:operator_mutation_score_rhoneamont}), in order to assess eventual dependencies of the operator with the predictand.
-Even though we can observe differences with Figure \ref{fig:operator_mutation_score_atmlevel}, it is globally the same options that perform better.
-
-Next, we added a second level of analogy (Figure \ref{fig:operator_mutation_score_r2}) on moisture variables \citep[see][]{Bontron2004, Horton2016}.
+Then, the same optimization was performed, but for another region, sensitive to other meteorological influences (Figure \ref{fig:operator_mutation_score_rhoneamont}), in order to assess eventual dependencies of the operator with the predictand.
+Even though differences can be observed with Figure \ref{fig:operator_mutation_score_atmlevel}, it is globally the same options that perform better.
+
+Next, a second level of analogy was added (Figure \ref{fig:operator_mutation_score_r2}) on moisture variables \citep[see][]{Bontron2004, Horton2016}.
 GAs had to optimize both levels of analogy simultaneously.
 Once again, despite the difficulty to optimize simultaneously both levels of analogy, the results were better than the sequential calibration (red line on Figure \ref{fig:operator_mutation_score_r2}).
-And finally, we added a preselection on air temperature instead of the fixed calendar window, as proposed by \cite{BenDaoud2015}.
+And finally, a preselection on air temperature was added instead of the fixed calendar window, as proposed by \cite{BenDaoud2015}.
 The results show generally higher scores (Figure \ref{fig:operator_mutation_score_r4}), demonstrating the success of the optimizer to take advantage of this new degree of freedom, and its capacity to handle optimization of 3 analogy levels jointly.
@@
 
-After analysis of the most relevant mutation operators, we can raise the following advice (detailed parametrization are provided in section \ref{sec:recommendations}):
+After analysis of the most relevant mutation operators, the following advice can be raised (detailed parametrization are provided in section \ref{sec:recommendations}):
 
@@
 The main disadvantage of the non-uniform mutation is the number of parameters it requires, that are difficult to estimate a priori.
-We could observe that the $\omega$ coefficient does not influence performance.
+The $\omega$ coefficient does not influence performance.
 The role of $G_{m}$ is rather difficult to judge, but does not seem essential.
@@
 
-	\item \textit{Chromosome of adaptive search radius} (new): unlike the previous one, our new operator is very robust, as it requires no option and is auto-adapting.
-It is interesting to notice that our insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).
+	\item \textit{Chromosome of adaptive search radius} (new): unlike the previous one, this new operator is very robust, as it requires no option and is auto-adapting.
+It is interesting to notice that the insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).
 If one had to choose a single option for the mutation operator, we would recommend this one, as it was proven effective and needs no parameter.
@@
 
-In our application, the mutation operator has a leading effect and should be chosen with care.
+In this application, the mutation operator has a leading effect and should be chosen with care.
 It may be wise to perform multiple optimizations and to consider these three operators in parallel in order to obtain results from options that are either sometimes more efficient or more robust.
 It is interesting to note that the three best techniques incorporate a notion of search distance.
-It is likely that this notion is the key to these algorithms, for our application, and allows them to initially explore the parameter domain, and then to converge.
+It is likely that this notion is the key to these algorithms, for this application, and allows them to initially explore the parameter domain, and then to converge.
 The search radius in fact directly represents the notion of transition between exploration and exploitation, in our opinion more than a possible evolution of mutation rates.
@@
 
-We also assessed the influence of the size of the IG (ratio of the total population) selected for mating (Figure \ref{fig:option_popratio_score}).
+The influence of the size of the IG (ratio of the total population) selected for mating was also assessed (Figure \ref{fig:option_popratio_score}).
 It does not appear that this parameter is critical to the quality of the optimizations, provided it is not too big.
@@
 
-We evaluated the optimization by GAs on AMs of varying complexity, with a large number of combinations of operators to be able to make recommendations for optimizing the AM. Our conclusions are:
+Optimizations by GAs on AMs of varying complexity were performed with a large number of combinations of operators in order to make recommendations for optimizing the AM. The conclusions are:
 
@@
 
-The optimization does not systematically converge to the global optimum  (but still often nearby), which is why we recommend doing several optimizations in parallel in order to compare the results, analyze the convergence, and keep the best.
+The optimization does not systematically converge to the global optimum (but still often nearby), which is why it is recommended to do several optimizations in parallel in order to compare the results, analyze the convergence, and keep the best.
 It may be wise to consider the three mutation operators in parallel.
@@
 In order to automatically optimize the AM and to get rid of the limitations of the usual sequential calibration, GAs were evaluated.
-Given the large number of existing operators and options, we had to evaluate systematically multiple variants to identify which operators are important, and which variant works best for the AM.
-We could thus identify that the mutation operator is a key element for our application, and provided new variants that were found to be efficient, such as the chromosome of adaptive search radius that is very robust (no control parameter).
+Given the large number of existing operators and options, multiple variants were evaluated systematically in order to identify which operators are important, and which variant works best for the AM.
+The mutation operator was identified as a key element for this application, and provided new variants that were found to be efficient, such as the chromosome of adaptive search radius that is very robust (no control parameter).
 Recommendations were established for a relevant use of GAs for the optimization of AMs.
 
-We do not exclude that another global optimization methods or other operators of GAs may perform better.
+It is not excluded that another global optimization methods or other operators of GAs may perform better.
 The relevance of such approach has now been proven as it results in parametrization of AMs that are relevant and fully automatically established.

### 2015-11-23 AtmoSwing - Geoscientific Model Development/template.tex
Removing we/our in all articles.

@@
 In hydrometeorology, it consists, given a certain situation, in looking into the past to retrieve situations that can be considered similar and therefore with consequences that may be expected similar to the situation at hand.
-By situation, we often think of the atmospheric situation over a rather wide domain, but it may also be the atmospheric profile at a radio-sounding station or the air-snow state at a given mountain observing station.
-By consequence, we often focus on one (or more) local variable of interest, such as the occurrence of hail, storm, avalanches, or the amount of wind or precipitation over a given region.
+By situation, one often thinks of the atmospheric situation over a rather wide domain, but it may also be the atmospheric profile at a radio-sounding station or the air-snow state at a given mountain observing station.
+By consequence, one often focuses on a local variable of interest, such as the occurrence of hail, storm, avalanches, or the amount of wind or precipitation over a given region.
 
@@
 Obviously, one understands that the longest and the richest the candidate archive of predictors, the more chance there will be to extract good analogues for a target situation in order to derive a conditional range of predictand values.
-As for the predictors, we can now hopefully rely on rich reanalysis products, commonly available over 40 years or more, and easily accessible.
+As for the predictors, one can now hopefully rely on rich reanalysis products, commonly available over 40 years or more, and easily accessible.
 
@@
 from 6-hourly to daily or several day totals) according for example to the size or response time of a the catchments to be managed.
-We must also consider the availability and quality of a long enough time series.
+The availability and quality of a long enough time series must also be considered.
 Moreover, the analogy is restricted to a selection of variables at a specific time and over optimized spatial domains, that are compared by means of a chosen criteria that can rank the candidate days from the archive with a distance quantification.
@@
 
-We will first present the AM along with various implementations, as the optimal version of the method may vary with the location of interest, and as all these can be processed with AtmoSwing.
+The AM will first be presented along with various implementations, as the optimal version of the method may vary with the location of interest, and as all these can be processed with AtmoSwing.
 The software will then be presented, and its modules detailed, such as the Forecaster and the Viewer that are tools for operational use, and the Optimizer that allows optimizing the method for a given predictand time series.
@@
 
-As AtmoSwing does not rely heavily on one variant of the analogue method (AM), but can implement different parametrization, we gathered here several references of possible implementations as well as the main evolution steps of the AM.
+As AtmoSwing does not rely heavily on one variant of the analogue method (AM), but can implement different parametrization, several references of possible implementations are gathered here, as well as the main evolution steps of the AM.
 This latter summarizes the improvements that were brought, as well as discontinued approaches that were found less relevant (such as the use of PCA on the predictors).
@@
 	\item The spatial window is the domain on which the analogy variable is considered. The ideal size of this area is one that maximizes useful information.
-	\item The temporal window is the hour of day at which we consider the analogy variable. The analogy can be instantaneous (eg. 12~h~UTC) or averaged over a period (eg. 24~h).
-	\item The analogy period is the time of year in which similar situations are being sought. Thus, we compare situations with a similar distribution of solar energy \citep{Lorenz1969}.
+	\item The temporal window is the hour of day at which the analogy variable is considered. The analogy can be instantaneous (eg. 12~h~UTC) or averaged over a period (eg. 24~h).
+	\item The analogy period is the time of year in which similar situations are being sought. Thus, only situations with a similar distribution of solar energy are compared \citep{Lorenz1969}.
 	\item The analogy criterion, needed to compare the variables on the chosen spatial and temporal windows, is a score used for ranking past situations according to their degree of similarity with the target situation \citep{Bontron2004}.
@@
 
-The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series we want to forecast.
+The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series one wants to forecast.
 
@@
 Although multiple variations of the AM exist, they generally share the same basics and the same structure.
-We want here to forecast the daily precipitation (the predictand) for a target day (at a defined lead time) and have long archives of both the predictand and predictor variables.
+For example, let's say we want here to forecast the daily precipitation (the predictand) for a target day (at a defined lead time) and have long archives of both the predictand and predictor variables.
 The generic structure is the following:
@@
 
-	\item First level of analogy: we subsample $N_{1}$ dates within all the candidates provided by the preselection, by means of an analogy ranking.
+	\item First level of analogy: $N_{1}$ dates are subsampled within all the candidates provided by the preselection, by means of an analogy ranking.
 The first level of analogy is always the atmospheric circulation when it comes to precipitation forecasting.
-We thus assess the similarity of the atmospheric circulation of our target date with all the situations provided by the preselection by means of the S1 criteria \citep[Eq.\ref{eq:S1}, ][see also section \ref{sec:method:evolution}]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
+The similarity of the atmospheric circulation of the target date is thus assessed with all the situations provided by the preselection by means of the S1 criteria \citep[Eq.\ref{eq:S1}, ][see also section \ref{sec:method:evolution}]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
 
@@
 
-	\item Subsequent level(s) of analogy: we can then subsample once again the $N_{1}$ analogues on the basis of another variable in order to obtain a lower number of analogue dates, $N_{2}$.
+	\item Subsequent level(s) of analogy: the $N_{1}$ analogues are subsampled once again on the basis of another variable in order to obtain a lower number of analogue dates, $N_{2}$.
 The S1 criterion is usually not relevant for other predictors that the atmospheric circulation.
@@
 ][]{Chardon2014}.
-For every level of analogy, we first provide the number of variables used (combination of atmospheric levels and time of observation) and then give the short name of the variable (according eg to ECMWF conventions; in upper case), for example:
+For every level of analogy, one first provides the number of variables used (combination of atmospheric levels and time of observation) and then give the short name of the variable (according eg to ECMWF conventions; in upper case), for example:
 \begin{itemize}
@@
 However, some of these are specific for a certain region and are not relevant for others, and some perform better depending on the lead time.
-Thereby, we cannot provide a single best parameterization for the AM, neither rank them from worst to best.
-We will thus provide some examples of parameterizations of the most recent AM variant, in the chronological order they appeared.
+Thereby, one cannot provide a single best parameterization for the AM, neither rank them from worst to best.
+Some examples of parameterizations of the most recent AM variant will thus be provided, in the chronological order they appeared.
 The most common usage of the AM is for precipitation forecasting.
@@
 The seasonal effect is indeed also present in the temperature data.
-The number of preselected dates is equivalent to the number of days we would have chosen with the calendar approach, and thus depends on the archive size: $N_{0} = 60 \cdot 2 \cdot n_{a}$ where $n_{a}$ is the number of years in the calibration period.
+The number of preselected dates is equivalent to the number of days one would have chosen with the calendar approach, and thus depends on the archive size: $N_{0} = 60 \cdot 2 \cdot n_{a}$ where $n_{a}$ is the number of years in the calibration period.
 \citet{BenDaoud2010} also reconsidered the parameters of the moisture index and ended up with both 925~hPa and 700~hPa levels, at 12~h and 24~h, or at every time step (6~h) between 06~h and 30~h (Table \ref{table:R4b}).
@@
 The optimal predictors vary from one region to another, along with the leading atmospheric processes.
-We will thus never get a unique parameterization of the AM valid for any place on earth, but the method needs to be adapted to the local conditions and to the size of the catchment of interest.
+One will thus never get a unique parameterization of the AM valid for any place on earth, but the method needs to be adapted to the local conditions and to the size of the catchment of interest.
 Thus, there will always be local adaptations to be made for use in a new region.
@@
 Indeed, in a limited weather archive, events with high return periods are not so numerous.
-Their number is certainly lower than the number of analogues we consider, which can introduce a bias in the forecast.
+Their number is certainly lower than the number of analogues considered, which can introduce a bias in the forecast.
 There are however techniques to correct this bias \citep[see][]{Marty2010}.
@@
 
-When using a parameterization of the AM, previously optimized in perfect prognosis \citep[optimization on the reanalysis dataset, without taking into account the uncertainty of operational forecasts,][]{Klein1963}, in operational forecasting, we should take into account the increasing uncertainty of the predictor with the lead time.
+When using a parameterization of the AM, previously optimized in perfect prognosis \citep[optimization on the reanalysis dataset, without taking into account the uncertainty of operational forecasts,][]{Klein1963}, in operational forecasting, one should take into account the increasing uncertainty of the predictor with the lead time.
 An option, proposed by \citet{Thevenot2004}, is to increase the number of analogues with the lead time.
@@
 Considering re-forecasts would allow us to work on a homogeneous dataset, as they are regularly reprocessed with a defined version of the model.
-However, we would need to redo the calibration procedure every time a new version is available, in order to reduce the bias \citep{Wilson2002}.
+However, one would need to redo the calibration procedure every time a new version is available, in order to reduce the bias \citep{Wilson2002}.
 Moreover, the length of reanalyses datasets are usually much longer than reforecast datasets, which allows us to identify more robust relationships.
@@
 Most often, the accuracy of the parameters for precipitations forecasting is evaluated by means of the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
-It is the only score we detail here (in section \ref{sec:prob_forecasts}).
+It is the only score that will be detailed hereafter (in section \ref{sec:prob_forecasts}).
 In addition, other scores are implemented in AtmoSwing Optimizer.
@@
 
-In the case of discrete probabilistic forecasts, we work with probabilities of occurrence or probability of belonging to a certain category. The implemented options are:
+In the case of discrete probabilistic forecasts, one works with probabilities of occurrence or probability of belonging to a certain category. The implemented options are:
 
@@
 Continuous probabilistic forecasts of a variable are issued in the form of the expected statistical distribution for this variable.
-They are expressed either in terms of distribution or by probability density, which need to compared an observed value.
-This is the situation we meet when forecasting precipitations with the AM.
-
-We mainly rely on the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
+They are expressed either in terms of distribution or by probability density, which need to be compared an observed value.
+This is the situation one meets when forecasting precipitations with the AM.
+
+Most applications mainly rely on the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
 It allows assessing the predicted cumulative distribution functions $F(y)$, for example of the precipitation values from analogue situations, compared to the observed value $y^{0}$.
@@
 This score is now commonly used for the evaluation of continuous variables prediction systems \citep{Casati2008, Marty2010}.
-To compare the value of the score in regard to a reference, we often consider its skill score value, and use the climatological distribution as the reference.
+To compare the value of the score in regard to a reference, one often considers its skill score value, and use the climatological distribution as the reference.
 The CRPSS (\textit{Continuous Ranked Probability Skill Score}) is thus defined as following:
@@
 The performance score is processed for these 4 windows.
-(ii) Only the direction providing the best improvement is applied to our spatial window.
+(ii) Only the direction providing the best improvement is applied to the spatial window.
 (iii) From this new spatial window, an increase in every 4 directions is once again assessed, and the best improvement is applied.
@@
 
-We added small improvements to this method, and named it ''classic+'', by allowing the spatial windows to do other moves, such as: (1) increase in 2 simultaneous directions, (2) decrease in 1 or 2 simultaneous directions, (3) expansion or contraction (in every direction), (4) shift of the window (without resizing) in 8 directions (including diagonals), and finally (5) all the moves described above, but with a factor of 2, 3, or more.
-For example, we try to increase by 2 units in one (or more) direction.
+Small improvements were added to this method, and named it ''classic+'', by allowing the spatial windows to do other moves, such as: (1) increase in 2 simultaneous directions, (2) decrease in 1 or 2 simultaneous directions, (3) expansion or contraction (in every direction), (4) shift of the window (without resizing) in 8 directions (including diagonals), and finally (5) all the moves described above, but with a factor of 2, 3, or more.
+For example, an increase by 2 units in one (or more) direction is assessed.
 This allows to skip one size that may not be optimal.
@@
 Due to limitations of the sequential approach, we decided to explore optimization techniques that can handle all parameters fully automatically.
-We first assessed the \citet{Nelder1965a} method, which was found to be unsuitable for this purpose.
+The \citet{Nelder1965a} method was first assessed, but was found to be unsuitable for this purpose.
 Because of the complexity of the AM and its non-linearity, a technique of global optimization is required.
-We thus implemented Genetic algorithms in AtmoSwing Optimizer in order to perform a global optimization of the AM.
+Genetic algorithms were thus implemented in AtmoSwing Optimizer in order to perform a global optimization of the AM.
 This allows for a fully automatic and objective optimization of the AM.
@@
 
-The analogue method evolves, but there are still many possibilities to be assessed. Amongst them, we can mention:
+The analogue method evolves, but there are still many possibilities to be assessed. Amongst them, one can mention:
 

### 2015-11-23 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Removing we/our in all articles.

@@
 \cite{Horton2012a} confirmed that this index is better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis considered independently.
-When adding a second level of analogy, we subsample $N_{2}$ dates in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
-When we add a second level of analogy, we keep a higher number of analogues on the first level.
+When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
+When a second level of analogy is added, a higher number of analogues is kept on the first level.
 
@@
 When the optimizer gets closer to the global optimum, any new improvement takes more time to appear (see figure \ref{fig:evolution}), and the final adjustment of the parameters is very time consuming \citep{Back1993a}.
-For problems that require a significant amount of time in order to evaluate the objective function, as in our case, we have to limit the number of generations to get reasonable processing time.
+For problems that require a significant amount of time in order to evaluate the objective function, as in the case of AMs, the number of generations has to be limited in order to get reasonable processing time.
 Thus, different acceptable solutions can result from one or more optimizations \citep{Holland1992b}.
@@
 The optimizations were performed based on the recommended GAs parametrization for AMs as described in \citet{Horton2016a}.
-As the optimization is mostly sensitive to the mutation operator (that randomly changes some values in the parameters sets), we consider parallel optimizations with variants of this operator, according to \citet{Horton2016a}:
+As the optimization is mostly sensitive to the mutation operator (that randomly changes some values in the parameters sets), parallel optimizations are considered with variants of this operator, according to \citet{Horton2016a}:
 
@@
 The 48 years precipitation dataset (see section \ref{sec:intro}.\ref{sec:data}) was divided into a calibration period (CP) and a validation period (VP).
-Using data independent from the CP to validate our results is very important in order to assess the robustness of the improvements and to avoid overparametrization of the method.
+Using data independent from the CP to validate the results is very important in order to assess the robustness of the improvements and to avoid overparametrization of the method.
 
 In order to reduce potential bias related to trends in the climate change or to the evolution in measurement techniques, the selection of the VP is evenly distributed over the entire series \citep{BenDaoud2010}.
-Thus, we selected one year every six years for validation, which represents a total of 8 years for the VP and 40 for CP.
+Thus, one year every six years were selected for validation, which represents a total of 8 years for the VP and 40 for CP.
 The choice of the sequence was made in order to have similar statistical characteristics between the CP and the VP.
@@
 
-We first optimized the analogy of atmospheric circulation alone, without moisture variables, for the 10 subregions.
+The analogy of atmospheric circulation alone was first optimized, without moisture variables, for the 10 subregions.
 We started from the most simple AM, and increased the complexity in order to identify the degrees of freedom that are of particular interest.
 Thus, the tested parametrization evolved iteratively in complexity.
-We do not provide the detailed results of the intermediate stages \citep[see][for the details]{Horton2012a}, but only the main conclusions.
+The detailed results of the intermediate stages are not provided \citep[see][for the details]{Horton2012a}, but only the main conclusions.
 
-We first considered the reference method for the analogy of the atmospheric circulation (2Z, Table \ref{table:params_R1}), based on the 500 and 1000~hPa levels.
-We let the optimizer choose the number of analogues, both spatial windows with no overlapping constraint, as well as the temporal window (hours of observation of the geopotential), what the sequential calibration cannot do.
-With these degrees of freedom, we could gain a relative CRPSS improvement of 3.97\% and 2.45\% in average for the CP and the VP respectively.
+The reference method for the analogy of the atmospheric circulation (2Z, Table \ref{table:params_R1}), based on the 500 and 1000~hPa levels, was first considered.
+The optimizer had to choose the number of analogues, both spatial windows with no overlapping constraint, as well as the temporal window (hours of observation of the geopotential), what the sequential calibration cannot do.
+With these degrees of freedom, a relative CRPSS improvement of 3.97\% and 2.45\% in average was obtained for the CP and the VP respectively.
 Some tests showed that most of the gains are due to the non-overlapping spatial windows.
@@
 
-Then, we provided an additional degree of freedom to the AGs by letting them choose the pressure levels along with the other parameters, which is also a non-automated process in the sequential calibration.
-We could observe that this degree of freedom increases the optimization time and may decrease the number of simulations that converge to a single solution.
+Then, an additional degree of freedom was provided to the AGs by letting them choose the pressure levels along with the other parameters, which is also a non-automated process in the sequential calibration.
+This degree of freedom increased the optimization time and may decrease the number of simulations that converge to a single solution.
 However, most solutions were very close in terms of score.
@@
 Parallel analyses showed that the analogy of circulation is incomplete, and that the geopotential still contains relevant data that can improve the statistical relationship.
-Therefore, we added a third predictor (still the geopotential height) that the optimizer could use along with the previous parameters.
+Therefore, a third predictor was added (still the geopotential height) that the optimizer could use along with the previous parameters.
 There was no constraint on the predictors, so that the same pressure level could be selected multiple times.
@@
 We then tried with 4 predictors, and so on, up to 8.
-Every time we added a new predictor to optimize, the score on the CP increased, but always more to a smaller extent.
+Every time a new predictor to optimize was added, the score on the CP increased, but always more to a smaller extent.
 However, the score value on the VP dropped after 4 predictors, revealing an over-parametrization of the method, and thus a lack of robustness.
-Thus, considering 4 predictors is optimal for our case study, since the gain in CRPSS is significant.
+Thus, considering 4 predictors is optimal for this case study, since the gain in CRPSS is significant.
 It cannot be excluded that another number would prevail in another region under other meteorological conditions.
 
-Finally, we added a weighting of these 4 predictors (pressure levels), which is also optimized by GAs.
+Finally, a weighting of these 4 predictors (pressure levels) was added, which is also optimized by GAs.
 The weighting operates in the combination of the S1 criteria processed on every level, which were previously averaged with equal weights.
@@
 
-The method finally optimized for the atmospheric circulation analogy, based on 4 levels of the geopotential, and that we will name 4Zo, is made of the following degrees of freedom:
+The method finally optimized for the atmospheric circulation analogy, based on 4 levels of the geopotential, and that will be name 4Zo, is made of the following degrees of freedom:
 
@@
 
-To assess the cross-compatibility of the parameters, we applied those optimized for one subregion to the others.
+To assess the parameters cross-compatibility, those optimized for one subregion were applied to the others.
 The resulting losses or gains of the CRPSS are displayed in Table \ref{table:crossing_4Zo_calib} for the CP and in Table \ref{table:crossing_4Zo_valid} for the VP.
@@
 Its spatial distribution is however homogeneous.
-The optimizer thus provided consistent selections of pressure levels and temporal windows, which depicts a significant preference in the AM, and the success of our GAs to provide consistent results.
+The optimizer thus provided consistent selections of pressure levels and temporal windows, which depicts a significant preference in the AM, and the success of GAs to provide consistent results.
 The automatic selection of the pressure levels is a big advantage of a global optimization, as it is not possible to assess all combinations of 4 levels with the sequential calibration procedure.
@@
 Surprisingly, subregions number 5 (Left side valleys) and 6 (Southern ridges) have exactly the same spatial windows, which suggest that they behave in a similar way and thus could have been merged.
-This similarity is a good sign for the accuracy of our optimized parameters.
+This similarity is a good sign for the accuracy of the optimized parameters.
 
@@
 
-We previously worked with a method based on a unique level of analogy.
-However, we know that moisture variables as a second level of analogy do provide improvements to the method (section \ref{sec:analog_method}).
+It is known that moisture variables as a second level of analogy do provide improvements to the method (section \ref{sec:analog_method}).
 The moisture index, which is a combination of the relative humidity and the precipitable water, has thus also been optimized.
-In order to do so, we had to introduce a constraint to the optimizer, so that it selects the same temporal window for both variables.
+In order to do so, a constraint to the optimizer had to be introduced, so that it selects the same temporal window for both variables.
 
@@
 
-We proceeded to an optimization of both levels of analogy simultaneously. This implies that the analogy of the atmospheric circulation may change due to the new moisture information.
+The optimization was processed on both levels of analogy simultaneously. This implies that the analogy of the atmospheric circulation may change due to the new moisture information.
 
@@
 The selected points for the analogy on the moisture index are always located nearby the catchment, including at least 1 of the nearest points from the reanalysis dataset, and the spatial windows are relatively small.
-Thus, for our case study, there is no need to look for distant moisture information and the search could be reduced to a smaller domain.
+Thus, for this case study, there is no need to look for distant moisture information and the search could be reduced to a smaller domain.
 
@@
 However, there is no drastic difference between both 4Zo-2MIo and 4Zo-4MIo methods, which suggests that considering 4 moisture predictors is not necessary.
-When it comes to improvements for days with precipitation above our 3 thresholds (P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the forecast, mainly for heavy rainfall.
+When it comes to improvements for days with precipitation above the 3 thresholds (P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the forecast, mainly for heavy rainfall.
 
@@
 This approach allowed us to differentiate the contributions to performance gains, as well as to identify possible over-parametrization.
-The main improvements for our case study are due to the following factors:
+The main improvements for the resent case study are due to the following factors:
 
@@
 	\item The automatic and joint optimization of all parameters: the analogues number, the selection of the pressure levels and the temporal windows, and the spatial windows.
-These parameters are highly interdependent, so we need to optimize them jointly in order to identify optimal combinations.
+These parameters are highly interdependent, so one needs to optimize them jointly in order to identify optimal combinations.
 Traditional calibration procedures based on a systematic assessment of every combination is no more possible when considering more than 2 pressure levels.
@@
 	\item The joint optimization of the circulation and moisture analogy levels, that are usually calibrated successively.
-We have been able to demonstrate that there is a dependency between the analogy levels, and that in order to approach the optimal parameters, we must consider them jointly.
+We have been able to demonstrate that there is a dependency between the analogy levels, and that in order to approach the optimal parameters, one must consider them jointly.
 \end{itemize}
@@
 However, it can be dangerous to add too many parameters to optimize.
-Indeed, the optimizer will probably use them to successfully improve the calibration score, but the validation control remains very important in order to determine if we are actually improving the method, or if we are over-parametrizing it.
+Indeed, the optimizer will probably use them to successfully improve the calibration score, but the validation control remains very important in order to determine if one is actually improving the method, or if it is being over-parametrized.
 
@@
 The optimizer do not always converge to the exact global optimum, but to its surroundings.
-This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that we have to stop it before the end, due to the required processing time (see Figure \ref{fig:evolution} as example).
+This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that one has to stop it before the end, due to the required processing time (see Figure \ref{fig:evolution} as example).
 The resulting parameters may sometimes present significant differences, even though the score is almost similar.
@@
 
-We tried to optimize the preselection period (the 4-months window) jointly with the other parameters, but we did not get improvement.
-We also tried optimizing the moisture flux, which is composed of the moisture index multiplied with the wind flux.
-However, the results were not better than when we considered the moisture index alone.
+We tried to optimize the preselection period (the 4-months window) jointly with the other parameters, but no improvement was observed.
+Optimizing the moisture flux, which is composed of the moisture index multiplied with the wind flux, was also assessed.
+However, the results were not better than when considering the moisture index alone.
 This may be related to the fact that the optimizer tries to provide the best analogy of the atmospheric circulation in the first place, which makes the wind information less relevant in the second level of analogy.
 
-As we could observe, methods with a higher complexity that integrate moisture predictors are less transposable than simpler ones.
-We also noticed in another unpublished work, that it is by far better to optimize for 2 subregions jointly rather than to optimize on one and to apply its parametrization to the other.
+As it has been observed, methods with a higher complexity that integrate moisture predictors are less transposable than simpler ones.
+It was also noticed in another unpublished work, that it is by far better to optimize for 2 subregions jointly rather than to optimize on one and to apply its parametrization to the other.
 Finally, the discretization in subregions is an important process and should be handled with care.
@@
 However, they automatically optimize all parameters of the AM, what the sequential calibration does not allow.
-We therefore save much human time that was required to assess successively numerous combinations of parameters (particularly the selection of the pressure levels and the temporal windows).
+Therefore, much human time is saved, that was previously required to assess successively numerous combinations of parameters (particularly the selection of the pressure levels and the temporal windows).
 The ability to optimize jointly all parameters is important given the strong dependencies between them and between the levels of analogy.
@@
 
-We could observe strong dependencies between the parameters of the AM.
+Strong dependencies between the parameters of the AM could be observed.
 Thus, the sequential calibration, which optimizes the parameters successively, may not lead to the optimal combination.
@@
 
-We were able to identify that there is a parametric dependence between the analogy of circulation and the moisture variables.
-When we consider the two levels together, the optimal parameters of the circulation analogy are different.
+A parametric dependence between the analogy of circulation and the moisture variables could be identified.
+When the two levels are considered together, the optimal parameters of the circulation analogy are different.
 This complexity can only be exploited in a suitable manner by global optimization methods.
 
-For our case study, there seems to be an optimum number of pressure levels to consider for the analogy of circulation, which is four, before losing performance in validation.
-We have also been able to improve the analogy of circulation by introducing a weighting between pressure levels, and considering independent spatial windows between levels.
+For the present case study, there seems to be an optimum number of pressure levels to consider for the analogy of circulation, which is four, before losing performance in validation.
+The analogy of circulation has also been improved by introducing a weighting between pressure levels, and considering independent spatial windows between levels.
 
 GAs provide parametrizations of AMs that exceed the performance of the sequential calibration.
-In addition, we could observe that the forecasts for days with strong precipitation were significantly more improved, which is clearly interesting in the framework of flood forecasting.
+In addition, it as been observed that the forecasts for days with strong precipitation were significantly more improved, which is clearly interesting in the framework of flood forecasting.
 
@@
 It becomes possible to even let the optimizer chose the meteorological variable to be used as predictor, as well as the analogy criteria.
-It is already possible to undertake such data mining with our code.
+It is already possible to undertake such approach with our code.
 Moreover, the AM has been explored for decades for precipitation forecasting, but very few work analysis its potential for other predictands.

### 2015-11-24 AtmoSwing - Geoscientific Model Development/template.tex
Personal corrections of AtmoSwing for v1.

@@
 
-AtmoSwing is an open source software that implement the analogue method in a very flexible way, so that different variants can be handled dynamically, by parameterization trough XML files.
-It is made of 3 tools: the Forecaster to perform operational forecasts, the Viewer to display the results, and the Optimizer to establish the statistical relationship between the predictand and predictors.
-
-The Forecaster handles every required step internally, such as predictors downloading and parsing, grid interpolation, analogy sorting, without external scripts or file conversion.
+AtmoSwing is an open source software that implements the analogue method in a very flexible way, so that different variants can be handled dynamically, by parameterization trough XML files.
+It is made of 3 tools: the Forecaster to perform operational forecasts, the Viewer to display the results, and the Optimizer to establish the relationship between the predictand and predictors.
+
+The Forecaster handles every required processing internally, such as predictors downloading and parsing, grid interpolation, analogy sorting, without external scripts or file conversion.
 The processing of a forecast is extremely lightweight in terms of IT infrastructure; it can indeed run on almost any computer.
@@
 
-The Optimizer integrates the most used technique, that is a semi-automatic sequential approach, as well as Monte-Carlo analyses, and a global optimization technique by means of Genetic algorithms.
-It allows establishing the statistical relationship between predictors and predictands.
+The Optimizer integrates the common semi-automatic sequential approach, as well as Monte-Carlo analyses, and a global optimization technique by means of Genetic algorithms.
 
@@
 In hydrometeorology, it consists, given a certain situation, in looking into the past to retrieve situations that can be considered similar and therefore with consequences that may be expected similar to the situation at hand.
-By situation, one often thinks of the atmospheric situation over a rather wide domain, but it may also be the atmospheric profile at a radio-sounding station or the air-snow state at a given mountain observing station.
+By situation, one often thinks of the atmospheric situation over a rather wide domain.
 By consequence, one often focuses on a local variable of interest, such as the occurrence of hail, storm, avalanches, or the amount of wind or precipitation over a given region.
@@
 However, the model may be extremely complex, time consuming, or some processes may be poorly known or parameterised.
-Conversely, the hope is that given the past archive of predictors, enough situations analogues to a target one could be found so that reasonable values will be found for the predictand, at a reasonable coding and computing-time costs.
+Conversely, given the past archive of predictors, enough situations analogues to a target one could be found so that reasonable values will be obtained for the predictand, at a reasonable coding and computing-time costs.
 This is particularly true for a predictand much required in hydrometeorological applications, namely the precipitation amount over a given domain and time duration.
@@
 In operational forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies, it is more and more used to downscale the results of global climate model simulation runs.
-In operational, it should however not to be considered as a substitution for numerical weather prediction models, but as a complement in order to get a fast and independent forecast that is known to be accurate several days in advance.
+In operational, it should however not be considered as a substitution for numerical weather prediction models, but as a complement in order to get a fast and independent forecast that is known to be accurate several days in advance.
 It therefore enriches the analysis of a potential critical situation for flood forecasting, for example, and is very interesting in early warning.
@@
 Usually the type of predictand is imposed by some practical needs or constraints.
-Considering a precipitation variable, ones has to decide upon the duration of accumulation, (e.g.
+Considering a precipitation variable, one has to decide upon the duration of accumulation, (e.g.
 from 6-hourly to daily or several day totals) according for example to the size or response time of a the catchments to be managed.
@@
 The approach appears predictand-specific but also dependent on the archive of predictors.
-Thus, the analogy is defined by many parameters (choice of the predictor variable, the temporal and spatial windows, and the number of analogues to consider) that are not straightforward to determine.
-
-The AM will first be presented along with various implementations, as the optimal version of the method may vary with the location of interest, and as all these can be processed with AtmoSwing.
-The software will then be presented, and its modules detailed, such as the Forecaster and the Viewer that are tools for operational use, and the Optimizer that allows optimizing the method for a given predictand time series.
+
+The AM will first be presented along with various implementations (section \ref{sec:method}), as the optimal version of the method may vary with the location of interest, and as all these can be processed with AtmoSwing.
+The software will then be presented (section \ref{sec:atmoswing}), and its modules detailed, such as the Forecaster (section \ref{sec:forecaster}) and the Viewer (section \ref{sec:viewer}) that are tools for operational use, and the Optimizer (section \ref{sec:optimizer}) that allows optimizing the method for a given predictand time series.
 
 \section{The analogue method}
-
-As AtmoSwing does not rely heavily on one variant of the analogue method (AM), but can implement different parametrization, several references of possible implementations are gathered here, as well as the main evolution steps of the AM.
+\label{sec:method}
+
+As AtmoSwing does not rely on one variant of the analogue method (AM), but can implement different parametrization, several examples of possible implementations are gathered here, as well as the main evolution steps of the AM.
 This latter summarizes the improvements that were brought, as well as discontinued approaches that were found less relevant (such as the use of PCA on the predictors).
@@
 \begin{itemize}
-	\item The analogy variable (the predictor) must contain synoptic information having indirect dependency with the local weather and the target variable (often the precipitation).
+	\item The analogy variable (the predictor) must contain synoptic information having indirect dependency with the local weather and the target predictand (often the precipitation).
 	\item The spatial window is the domain on which the analogy variable is considered. The ideal size of this area is one that maximizes useful information.
-	\item The temporal window is the hour of day at which the analogy variable is considered. The analogy can be instantaneous (eg. 12~h~UTC) or averaged over a period (eg. 24~h).
-	\item The analogy period is the time of year in which similar situations are being sought. Thus, only situations with a similar distribution of solar energy are compared \citep{Lorenz1969}.
-	\item The analogy criterion, needed to compare the variables on the chosen spatial and temporal windows, is a score used for ranking past situations according to their degree of similarity with the target situation \citep{Bontron2004}.
-	\item The ideal number of analogues situations is the best compromise in order to take into account local variability and to maximize useful synoptic information  \citep{Bontron2004}.
+	\item The temporal window is the hour of day at which the analogy variable is considered.
+	\item The preselection, which is often a period of the year in which similar situations are being sought.
+Thus, only situations with a similar distribution of solar energy are compared \citep{Lorenz1969}.
+	\item The analogy criterion, needed to compare the variables on the chosen spatial and temporal windows, is a score used for ranking past situations according to their degree of similarity with the target situation.
+	\item The ideal number of analogue situations is the best compromise in order to take into account local variability and to maximize useful synoptic information \citep{Bontron2004}.
 \end{itemize}
@@
 Other observed predictors can also be used, such as Sea Surface Temperature \citep[SST, ][]{Reynolds2007}.
-The predictors describing the target situation in operational forecasting can for example result from GFS \citep[Global Forecast System,][]{Kanamitsu1991,Kanamitsu1989}, which is operated by NCEP and NOAA.
+The predictors describing the target situation in operational forecasting can, for example, result from GFS \citep[Global Forecast System,][]{Kanamitsu1991,Kanamitsu1989}, which is operated by NCEP and NOAA.
 
 \citet{Bontron2004} determined that the length of the archive should be 30 years to forecast usual situations, and 40 years for intense events.
-He also highlighted the dependence between the optimal number of analogues and the archive size: the shorter the archive, the lower the number of analogues.
+He also highlighted the dependency between the optimal number of analogues and the archive size: the shorter the archive, the lower the number of analogues.
 By varying the resolution of the predictors grids, he concluded that the performance increase is not significant for the analogy of atmospheric circulation below a resolution of 5\textdegree.
@@
 The predictand is the local meteorological variable of interest.
-It can be 6-houry data, or more often daily time series, but has to be consistent with the time step of the predictors (at least, not finer).
-The most used predictor is the daily precipitation, usually averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.
+It can be 6-houry data, or more often daily time series, but has to be consistent with the time step of the predictors.
+The most used predictand is the daily precipitation, usually averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.
 These time series are frequently normalized by the precipitation value for a return period of 10~years \citep{Djerboua2001}.
 This normalization allows for an easier comparison between subregions subject to different precipitation regimes, and thus to better identify the most important contributions.
-Most users also apply a root square to this last ratio in order to reduce the weight of the extreme predictand values, but we generally don't.
+Most users also apply a root square to this last ratio in order to reduce the weight of the extreme predictand values, but we generally don't, in order to let to extremes a certain importance.
 
@@
 For example, let's say we want here to forecast the daily precipitation (the predictand) for a target day (at a defined lead time) and have long archives of both the predictand and predictor variables.
-The generic structure is the following:
+The generic structure, illustrated for precipitation forecasting, is the following:
 
@@
 The first level of analogy is always the atmospheric circulation when it comes to precipitation forecasting.
-The similarity of the atmospheric circulation of the target date is thus assessed with all the situations provided by the preselection by means of the S1 criteria \citep[Eq.\ref{eq:S1}, ][see also section \ref{sec:method:evolution}]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
+The similarity of the atmospheric circulation of the target date with the candidate situations is thus assessed on the geopotential by means of the S1 criteria \citep[Eq.\ref{eq:S1}, ][see also section \ref{sec:method:evolution}]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
 
@@
 	\end{equation}
-	where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points in the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
+	where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points from the grid of the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
 The differences are processed separately in both directions.
-The smaller the S1 values are, the more similar the pressure fields.
+The smaller the S1 values, the more similar the pressure fields.
 
@@
 Variants of the AM parameterization are numerous and it is not always easy to reference them in a short and descriptive way.
-We thus propose a basic nomenclature (Figure \ref{figure:nomenclature}) in order to give an idea of the structure in a simple identifier.
+We thus propose a basic nomenclature (Figure \ref{figure:nomenclature}) in order to express the structure in a simple identifier.
 This one cannot describe all the parameters of the AM, but quickly illustrate the structure of the implementation.
@@
 ][]{Chardon2014}.
-For every level of analogy, one first provides the number of variables used (combination of atmospheric levels and time of observation) and then give the short name of the variable (according eg to ECMWF conventions; in upper case), for example:
+For every level of analogy, the number of variables used (combination of atmospheric levels and time of observation) is first provided, and then the short name of the variable is given (according eg to ECMWF conventions; in upper case), for example:
 \begin{itemize}
@@
 The geopotential height at 700~hPa and 00~h was used for its higher stability than the sea level pressure (SLP) field, and its sensitivity to the atmospheric disturbances \citep{Guilbaud1997}.
-However, the SLP at 06~h was also used for determining the intensity of precipitation, as well as the temperature at 700~hPa as indicator of the thermal state of the air mass \citep{Duband1974}.
+However, the SLP at 06~h was also used for determining the precipitation intensity, as well as the temperature at 700~hPa as indicator of the thermal state of the air mass \citep{Duband1974}.
 The data were then based on 37 radiosounding over Europe and condensed by a principal component analysis.
@@
 The forecast was then performed only on the basis of observations and was temporally extrapolated to the following two days.
-After a few years, this statistical temporal extrapolation was abandoned in favor of a statistical adaptation using predictors resulting from an global numerical model, allowing a forecast over the following 4~days.
+After a few years, this statistical temporal extrapolation was abandoned in favor of a statistical adaptation using predictors resulting from a numerical model, allowing a forecast over the following 4~days.
 
@@
 \ref{eq:S1}), which allows for a comparison of the gradients and thus an analogy of the atmospheric circulation.
+This work has demonstrated the best performance of the AM compared to regression methods, as well as the interest to search for analogues on two (500 and 1000~hPa) geopotential fields combined \citep{Guilbaud1997}.
 \citet{Woodcock1980} used the same criterion on the SLP fields to select 50~analogues in order to forecast maximum daily temperatures.
-\citet{Yacowar1975} considered the 20 best analogues on the maximum of the sum of correlations on the two fields.
-This work has demonstrated the best performance of the AM compared to regression methods, as well as the interest to search for analogues on two (500 and 1000~hPa) geopotential fields combined \citep{Guilbaud1997}.
 
@@
 
-Taking advantage of higher-performance IT tools \citet{Guilbaud1997} stopped using PCA in order to work directly with the raw data interpolated on grids, which was an improvement, especially when considering the S1 criterion (already used for analogues selection by\citealp{Wilson1980} and \citealp{Woodcock1980}) instead of the Euclidean distance.
-This score gives importance to the similarity of atmospheric circulation rather than absolute values of the pressure field.
+Taking advantage of higher-performance IT tools \citet{Guilbaud1997} stopped using PCA in order to work directly with the raw data interpolated on grids, which resulted in an improvement, especially when considering the S1 criterion (already used for analogues selection by \citealp{Wilson1980} and \citealp{Woodcock1980}) instead of the Euclidean distance.
 After comparing this criterion to other criteria from the literature, or combinations of these, \citet{Guilbaud1998} found that S1 is the most efficient.
 They also pointed out the benefit of using 2 atmospheric levels, 1000~hPa (Z1000) and 700~hPa (Z700) or 500~hPa (Z500), instead of one (also instead of the thickness), and to also consider 2 temporal windows, 00~h and 24~h \citep{Obled2002}.
-The number of analogues considered is 50 (Table \ref{table:R0}).
+The number of analogues considered was 50 (Table \ref{table:R0}).
 When using multiple predictors, they combined the criteria values calculated on each atmospheric level and each temporal window using an arithmetic mean.
@@
 \begin{table}[htbp]
-	\caption{Method of type PC-4Z proposed by \citet{Guilbaud1997}.}
+	\caption{Method of type PC-4Z proposed by \citet{Guilbaud1997}.
+The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window).
+The criteria used for the current level of analogy is then provided, as well as the number of analogues.}
 	\begin{tabular}{ccccc}
@@
 \citet{Bontron2004} could benefit from the newly available NCEP/NCAR reanalysis data.
-This dataset being more homogeneous, much longer, and contained more variables than what was previously used, he could systematically assess a large selection of variables in the AM combined with different criteria.
+This dataset being more homogeneous, much longer, and containing more variables than what was previously used, he could systematically assess a large selection of variables in the AM combined with different criteria.
 He thus confirmed the interest of the geopotential height along with the S1 criterion for the first level of analogy.
@@
 \begin{table}[htbp]
-	\caption{Method of type PC-2Z proposed by \citet{Bontron2004}.}
+	\caption{Method of type PC-2Z proposed by \citet{Bontron2004}. Same conventions as Table \ref{table:R0}}
 	\begin{tabular}{ccccc}
@@
 
-\citep{Bontron2004} also assessed several variables for the second level of analogy and identified the moisture variables (precipitable water and relative humidity) and vertical velocity to be the most relevant.
+\citet{Bontron2004} also assessed several variables for the second level of analogy and identified the moisture variables (precipitable water and relative humidity) and vertical velocity to be the most relevant.
 Finally, he found that a moisture index made of the product of relative humidity at 850~hPa (RH850) and total precipitable water (TPW) gave the best performance (Table \ref{table:R2}).
@@
 \begin{table}[htbp]
-	\caption{Method of type PC-2Z-2MI proposed by \citet{Bontron2004}.}
+	\caption{Method of type PC-2Z-2MI proposed by \citet{Bontron2004}. Same conventions as Table \ref{table:R0}}
 	\begin{tabular}{ccccc}
@@
 \begin{table}[htbp]
-	\caption{Method of type PC-2Z-2MI proposed by \citet{Marty2010}.}
+	\caption{Method of type PC-2Z-2MI proposed by \citet{Marty2010}. Same conventions as Table \ref{table:R0}}
 	\begin{tabular}{ccccc}
@@
 \begin{table}[htbp]
-	\caption{Method of type PC-2Z-2MF proposed by \citet{Marty2010}.}
+	\caption{Method of type PC-2Z-2MF proposed by \citet{Marty2010}. Same conventions as Table \ref{table:R0}}
 	\begin{tabular}{ccccc}
@@
 
-\citet{BenDaoud2010} applied the AM in the context of large floodplains, out of an Alpine environment (Sa\^{o}ne, Seine).
+\citet{BenDaoud2010} applied the AM in the context of large floodplains (Sa\^{o}ne, Seine).
 He evaluated several variables usually used in weather forecasting, amongst them the air temperature and the vertical velocity that presented a potential interest.
-The temperature (at the nearest grid point, on the 925~hPa (36~h) and 600~hPa (12~h) levels) could replace the rigid calendar preselection of $\pm$ 60 days around the target date by a more dynamic screening of similar situations in terms of air masses.
+The temperature (at the nearest grid point, on the 925~hPa \& 36~h and 600~hPa \& 12~h levels) could replace the rigid calendar preselection of $\pm$ 60 days around the target date by a more dynamic screening of similar situations in terms of air masses.
 The seasonal effect is indeed also present in the temperature data.
@@
 \begin{table}[htbp]
-	\caption{Method of type P2T-2Z-4MI (or P2T-2Z-10MI for the alternative version), by \citet{BenDaoud2010}.}
+	\caption{Method of type P2T-2Z-4MI (or P2T-2Z-10MI for the alternative version), by \citet{BenDaoud2010}. Same conventions as Table \ref{table:R0}}
 	\begin{tabular}{ccccc}
@@
 Subsequently, \citet{BenDaoud2010} added an additionally level of analogy, between the circulation and the moisture analogy (Table \ref{table:R5}), based on vertical velocity at 850~hPa (W850).
-This AM was developed for large plains in France, but was found to be not relevant for an Alpine environment where topography is mostly responsible for uplift of air masses \citep{Horton2012}.
+This AM was developed for large floodplains in France, but was found to be not relevant for an Alpine environment where topography is mostly responsible for uplift of air masses \citep{Horton2012}.
 
 \begin{table}[htbp]
-	\caption{Method of type P2T-2Z-4W-4MI, by \citet{BenDaoud2010}.}
+	\caption{Method of type P2T-2Z-4W-4MI, by \citet{BenDaoud2010}. Same conventions as Table \ref{table:R0}}
 	\begin{tabular}{ccccc}
@@
 \citet{Bliefernicht2010} proposed to add a weighting to the grid points of the predictor to overcome a comparison on a fixed-size window, and to give more importance to regions with relevant atmospheric circulation information.
-However, he noticed that there is a risk of overparametrization and a simplification of the weighting fields may be necessary, and that the performance was not stable between the calibration and the validation periods.
+However, he noticed that there is a risk of overparametrization as the performance was not stable between the calibration and the validation periods, and a simplification of the weighting fields may be necessary.
 He also compare the performance of the AM with a forecasting method based on a weather types approach, and concluded that the AM was more efficient.
@@
 No number of analogues ($N_{1}$) was provided globally, as it was calibrated for every subregion.
-Considering a AM only based on the atmospheric circulation has an interest for operational forecasting, where moisture variables are less well forecasted over a lead time of a few days.
-An equivalent structure was also optimized by means of generic algorithms (PC-4Zgo), which is the topic of another paper.
+Considering an AM only based on the atmospheric circulation has an interest for operational forecasting, where moisture variables are less well forecasted for a lead time of a few days.
+An equivalent structure was also optimized by means of generic algorithms (PC-4Zgo), which is the topic of another paper \citep{Horton2016b}.
 
 \begin{table}[htbp]
-	\caption{Method of type PC-4Z proposed by \citet{Horton2012}.}
+	\caption{Method of type PC-4Z proposed by \citet{Horton2012}. Same conventions as Table \ref{table:R0}}
 	\begin{tabular}{ccccc}
@@
 The number of analogues ($N_{1}$, $N_{2}$) were also calibrated for every subregion.
-Similarly, an equivalent structure was optimized (PC-4Zgo-2MIgo).
+Similarly, an equivalent structure was optimized \citep[PC-4Zgo-2MIgo,][]{Horton2016b}.
 
 \begin{table}[htbp]
-	\caption{Method of type PC-4Z-2MI, by \citet{Horton2012}.}
+	\caption{Method of type PC-4Z-2MI, by \citet{Horton2012}. Same conventions as Table \ref{table:R0}}
 	\begin{tabular}{ccccc}
@@
 Another issue, still about data, concerns the operational forecasting: predictors describing forecasted target situations and the ones from the archive are not fully homogeneous, as they usually don't result from the same model.
-It is therefore necessary to use robust predictors that depend from the numerical model characteristics at a minimum extent.
+It is therefore necessary to use robust variables that depend from the numerical model characteristics at a minimum extent.
 
@@
 The first potential issue is a possible change in atmospheric circulation.
-\citep{Philipp2007} observed certain trends in the synoptic atmospheric circulation over Europe, but with moderate frequencies.
+\citet{Philipp2007} observed certain trends in the synoptic atmospheric circulation over Europe, but with moderate frequencies.
 Moreover, the basic laws governing the atmosphere behavior will not be transformed \citep{Hewitson1996}.
@@
 \section{Software basics}
-
-AtmoSwing is made of 3 main modules (Figure \ref{figure:flowchart_modules_atmoswing}) that are standalone, but do share a common code basis: the Forecaster, to process the operational forecasting, the Viewer, to display the forecast in a GIS environment, and the Optimizer, to calibrate/optimize the statistical relationship defining the analogy for a given predictand time series.
+\label{sec:atmoswing}
+
+AtmoSwing is made of 3 main modules (Figure \ref{figure:logo}) that are standalone, but do share a common code basis: the Forecaster, to process the operational forecasting, the Viewer, to display the forecast in a GIS environment, and the Optimizer, to calibrate/optimize the statistical relationship defining the analogy for a given predictand time series.
 Separating the Forecaster and the Viewer allows to automate the forecast on a server and to quickly display the results locally.
@@
 The source code in under version control (with Mercurial), and is open source (on Bitbucket, www.atmoswing.org).
-Developments have been made with an approach of unit tests.
+Developments have been made with a test driven development (TDD) approach.
 A collection of 500+ tests are frequently evaluated and completed during development, in order to verify that code changes do not introduce regression.
@@
 
-Although processing an analogue forecast for a given target date is fast, when optimizing the AM, forecasts are processed over a long periods of several decades, which is time consuming.
+Although processing an analogue forecast for a given target date is fast, when optimizing the AM, forecasts are processed over long periods of several decades, which is time consuming.
 Thus, great effort has been made in order to reduce the processing time to a minimum.
@@
 	\item use of pointers (and therefore the decrease of data copies),
-	\item better search for dates in temporal vectors starting from the previous index,
+	\item better search for dates in temporal vectors starting from the previous index (reduction of the range of the array to explore),
 	\item better management of the analogue vectors,
@@
 \section{AtmoSwing Forecaster}
+\label{sec:forecaster}
 
@@
 This software processes a current or past forecasting, defined by an XML file.
-A list of parameterizations (defined by external XML files) is processed successively.
-The software can compiled with a GUI (), or without in order to be used on a headless server through a command line interface.
+A list of parameterizations is processed successively.
+The software can be compiled with a GUI (graphical user interface, Figure \ref{figure:atmoswing-forecaster-gui}), or without in order to be used on a headless server through a command line interface.
 Processing a forecast requires very low computing capabilities and can be done on a low-end computer.
@@
 When using a parameterization of the AM, previously optimized in perfect prognosis \citep[optimization on the reanalysis dataset, without taking into account the uncertainty of operational forecasts,][]{Klein1963}, in operational forecasting, one should take into account the increasing uncertainty of the predictor with the lead time.
-An option, proposed by \citet{Thevenot2004}, is to increase the number of analogues with the lead time.
+An available option, proposed by \citet{Thevenot2004}, is to increase the number of analogues with the lead time.
 These values should be optimized, for every lead time, by using reforecast data of the model considered for operational forecasting.
 
-The command-line interface allows to start the process for the most recent date, a selected past date, or the last $x$ days (as long as the predictors are available on the provider server).
+The command-line interface allows to start the process for the present date, a selected past date, or the last $x$ days (as long as the predictors are available on the provider server).
 When there is nothing to process (no new predictor data available), the execution just stops, leading to no loss of computing resources.
@@
 Its generation consists in extracting the time series from text files in order to process them and save a database in the NetCDF format.
-During the process, Gumbel adjustments are automatically calculated in order to determine the values of different return periods.
+During the process, Gumbel adjustments are automatically calculated in order to determine the values corresponding to different return periods.
 The time series are normalized by a selected return period (default 10~years) and their square root is eventually processed.
@@
 \section{AtmoSwing Viewer}
+\label{sec:viewer}
 
@@
 Representation relatively to a return time better expresses the meaning of a certain precipitation amount for a given region, as climatology can be drastically different between two locations in a mountainous area, even if they are close to each other.
-All information relative to a rain gauge station (or stations groups), such as its location, its name, or the values of different return periods, are stored in the forecast files, in order to be displayable for end users who do not have the predictand database.
+All information relative to a rain gauge station (or catchments), such as its location, its name, or the values of different return periods, are stored in the forecast files, in order to be displayable for end users who do not have the predictand database.
 
@@
 The user can even go into further details and display the predictand cumulative distribution for a given lead time (Figure \ref{figure:atmoswing-viewer-distribution}).
-This information is useful when working on extreme precipitation, as comparing the distribution of all analogues versus the 10 best analogues provides information in order to interpret the forecast (trend to under/overestimation).
-Distribution of the analogy criteria can also be displayed in order to identify eventual discontinuities in the criteria values.
-
-Finally, one can see the details of the analogue dates, along with the predictand and the criteria values in an interactive spreadsheet.
+This is useful when working on extreme precipitation, as comparing the distribution of all analogues versus the 10 best analogues provides information in order to interpret the forecast (trend to under/overestimation).
+Distribution of the analogy criteria (not shown) can also be displayed in order to identify eventual discontinuities in the criteria values.
+
+Finally, one can see the details of the analogue dates, along with the predictand and the criteria values in an interactive spreadsheet (not shown).
 
@@
 He concluded that the detection of the precipitation occurrence was better predicted by median quantiles (50-70~\%), with an optimum to 60~\%.
-However, for significant rainfall, the 90$^{th}$ percentile gave the best performance.
+However, once again, for significant rainfall, the 90$^{th}$ percentile gave the best performance.
 Comparing the results from the AM to an ensemble forecast, \citet{Marty2010} found the AM to be better than the considered ensembles, particularly for strong precipitation.
@@
 \section{AtmoSwing Optimizer}
+\label{sec:optimizer}
 
@@
 
-The calibration of the AM is usually carried out in a perfect prognosis \citep{Klein1959} framework \citep{BenDaoud2010, Bontron2004}.
+The calibration of the AM is usually carried out in a perfect prognosis \citep{Klein1959} framework \citep{Bontron2004, BenDaoud2010}.
 Perfect prognosis uses observed or reanalyzed data to calibrate the relationship between predictors and predictands.
@@
 The statistical relationship is established on a calibration period that is as long as possible.
-For every day of this period, a search for analogues is processed, the precipitation data are associated with the corresponding dates and a forecast score is calculated.
+For every day of this period, a search for analogues is processed, the predictand data are associated with the corresponding dates and a forecast score is calculated.
 During the search for analogues situations, 120 days around the target date are excluded (thus excluding data in the same year) in order to consider only truly independent candidates days.
@@
 A validation period is always considered.
-It consists of an independent period that is never used as target neither candidate date.
+It consists of an independent period that is never used as target neither candidate.
 Validating the parameters of the AM is very important in order to avoid over-parametrization and thus to ensure that the statistical relationship is valid on another period.
@@
 Continuous probabilistic forecasts of a variable are issued in the form of the expected statistical distribution for this variable.
-They are expressed either in terms of distribution or by probability density, which need to be compared an observed value.
+They are expressed either in terms of distribution or by probability density, which needs to be compared to an observed value.
 This is the situation one meets when forecasting precipitations with the AM.
@@
 Most applications mainly rely on the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
-It allows assessing the predicted cumulative distribution functions $F(y)$, for example of the precipitation values from analogue situations, compared to the observed value $y^{0}$.
+It allows assessing the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$.
 The better the forecast, the smaller the score.
@@
 Previously calibrated parameters are generally not reassessed.
-The advantage of this method is that it is fast, it provides acceptable results, and it has low computing requirements.
-
-Small improvements were added to this method, and named it ''classic+'', by allowing the spatial windows to do other moves, such as: (1) increase in 2 simultaneous directions, (2) decrease in 1 or 2 simultaneous directions, (3) expansion or contraction (in every direction), (4) shift of the window (without resizing) in 8 directions (including diagonals), and finally (5) all the moves described above, but with a factor of 2, 3, or more.
+The advantage of this method is that it is relatively fast, it provides acceptable results, and it has low computing requirements.
+
+Small improvements were added to this method, then named ''classic+'', by allowing the spatial windows to do other moves, such as: (1) increase in 2 simultaneous directions, (2) decrease in 1 or 2 simultaneous directions, (3) expansion or contraction (in every direction), (4) shift of the window (without resizing) in 8 directions (including diagonals), and finally (5) all the moves described above, but with a factor of 2, 3, or more.
 For example, an increase by 2 units in one (or more) direction is assessed.
@@
 The shape of the scatter plots from Figure \ref{figure:monte_carlo_r1} reveals a low sensitivity as to the exact location of the spatial windows.
-There is a maximum threshold for minimum longitudes and latitudes and, conversely, a minimum threshold for maximum latitudes and longitudes, but outside of these limits, the distribution slope is more gentle.
+There is a maximum threshold for minimum longitudes and latitudes and, inversely, a minimum threshold for maximum latitudes and longitudes, but outside of these limits, the distribution slope is more gentle.
 A spatial window can thus be a bit larger than its optimal size without a significant drop in performance, as long as it includes at least one critical region.
-This was also observed by \citet{Bontron2004}, who noted that ''\textit{performance slowly decrease if we consider a slightly too large window, while the use of too small windows results in strong performance loss}''.
+This was also observed by \citet{Bontron2004}, who noted that ''\textit{performance slowly decreases if we consider a slightly too large window, while the use of too small windows results in strong performance loss}''.
 The dilution of a part of the relevant synoptic information has therefore not necessarily a significant negative impact on performance, while ignoring some of this information leads to undesirable loss of performance.
@@
 This allows for a fully automatic and objective optimization of the AM.
-However, as this topic is rather consequent and the code base is not yet released, it will be the subject of other publications \cite[see][]{Horton2016a, Horton2016b}.
+However, as this topic is rather consequent and the code base is not yet released, it is the subject of other publications \cite[see][]{Horton2016a, Horton2016b}.
 
@@
 Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
-The fruitful collaboration with the Laboratoire d?Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
+The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
 NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.

### 2015-11-24 Genetic algorithms - Journal of Climate/template.tex
Personal corrections of GAs for v1.

@@
 \abstract{The analogues method is based on a statistical relationship between synoptic atmospheric variables (predictors) and local weather (predictand), which we aim at forecasting.
-This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic procedure.
-This sequential calibration has strong limitations: it is made of successive steps and thus cannot handle parameters dependencies, and it cannot automatically optimize some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared.
+This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic sequential procedure.
+This calibration approach has strong limitations: it is made of successive steps and thus cannot handle parameters dependencies, and it cannot automatically optimize some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared.
 In order to surpass these limitations, a global optimization technique was assessed, namely genetic algorithms, which can optimize jointly all parameters of the method and get closer to a global optimum by taking into account the parameters dependencies.
@@
 These kind of optimization techniques need however to be tailored to the problem to solve.
-Multiple combinations of algorithms had to be assessed, and even new operators were developed, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of genetic algorithms to optimize the analogue method.
-These recommendations are a consequent outcome of this work, as it opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.
+Multiple combinations of algorithms had to be assessed, and even new operators were developed, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of Genetic Algorithms to optimize the analogue method.
+These recommendations are the main outcome of this work.
+It opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.
 }
@@
 The analogue method (AM) relies on the hypothesis that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Lorenz1956, Lorenz1969, Duband1970, Bontron2005}.
-The principle is sampling a certain number of past situations based on different atmospheric variables (predictors) in order to build a probabilistic forecast for a local weather variable (predictand).
-The most common usage of the AM is for precipitation forecasting \citep[eg.]{Guilbaud1997, Bontron2005, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, BenDaoud2015}, but AMs, or equivalent, were also used for short to medium term forecasting of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+The principle consists in sampling a certain number of past situations based on different atmospheric variables (predictors) in order to build a probabilistic forecast for a local weather variable of interest (predictand).
+The most common usage of the AM is for precipitation forecasting \citep[eg.][]{Guilbaud1997, Bontron2005, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, BenDaoud2015}, but AMs, or equivalent, were also used for short to medium term forecasting of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
 Applications for monthly forecasts in many countries also exist, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal forecasts: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
@@
 The purpose of this paper is not to present in details the AM and its different parametrizations, which can be found in \citet{Horton2016} or \citet{BenDaoud2015}.
-The concepts one needs to understand here are the following: the AM consists in searching a certain number of past situations in a meteorological archive (typically reanalysis) that are the most similar, according to an analogy criteria, and to extract the observed values of the local weather variable of interest from another archive (typically local time series) in order to build the cumulative distribution considered as the probabilistic forecast for the target day.
-Predictors can be multiple, for example the geopotential height at different pressure levels on different temporal windows (time of observation).
+The concepts one needs to understand here are the following: the AM consists in searching a certain number of past situations in a meteorological archive (typically reanalysis) that are the most similar, according to an analogy criteria, and to extract the observed values of the local weather variable of interest from another archive (typically local time series) in order to build the empirical distribution considered as the probabilistic forecast for the target day.
+Predictors can be multiple: for example the geopotential height at different pressure levels on different temporal windows (time of observation).
 The method is usually made of multiple levels of analogy, leading to successive subsampling on predictors of different nature (eg.
@@
 Even though the method is rather simple compared to numerical weather prediction models, it contains a certain number of parameters one needs to determine, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criteria itself, and finally the number of analogue situations to keep at each subsampling level.
+
+The AM needs to be adapted to every new region it is applied, because the leading meteorological influences are specific per region.
+Even the selection of the pressure levels and the temporal windows should be reconsidered, when not the variable itself.
+For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012a} found no interest in this variable in an Alpine environment, because the vertical motion, which is mainly controlled by orographic effects, was already well related to the atmospheric circulation itself.
+
 Up to now, the optimization of the method has been undertaken by semi-automatic sequential calibration procedures \citep[see][for its definition]{Bontron2004, Horton2016}.
@@
 Testing multiple combinations of these can be cumbersome, especially when considering multiple predictors within the same level of analogy.
+Thus, optimizing the method with the sequential technique is laborious, as many combinations of predictors (variables, pressure levels, temporal windows) have to be assessed.
 Moreover, the sequential technique proceeds to the optimization sequentially, ignoring potential dependencies between the parameters of the method, may they be within a single level of analogy or between them.
-Thus, optimizing the method with the sequential technique is laborious, as many combinations of predictors (variables, pressure levels, temporal windows) have to be assessed.
-Moreover, due to its sequential approach, the risk of ending in a local optimum is high and can not be avoided.
+However, any dependency between them cannot be excluded, which could lead us to select another parametrization if calibrated together.
+Simultaneous calibration of all parameters has never been undertaken so far.
+Thus, due to its sequential approach, the risk of ending in a local optimum is high and can not be avoided.
+Indeed, during the AM calibration it has been found that the resulting parameters may vary with initial choices (such as the number of analogues).
+
+When creating the sequential calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters and wrote: ''\textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent.
+We will present our results by first searching the best variable [note: e.g.
+selection of the pressure level and the temporal window for the geopotential height] on a chosen spatial window, and next, the best window for the chosen variable.
+However, even by repeating the process, are we sure to obtain the optimal combination?}''.
+And later in his work: ''\textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution}''.
+\citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of the AM and concludes that one needs to be an expert to know their respective influence, their sensitivity and their nonlinear interactions.
+\citet{BenDaoud2010}, when calibrating the AM, also stated that ''\textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously }''.
 
@@
 First, \citet{Horton2012a} assessed the ability of the \citet{Nelder1965a} method based on a simplex approach.
-This technique didn't provide satisfying results and failed at identifying the global optimum.
-Indeed, the results didn't converge and many local optimums came out.
-The parameter space of the AM is very complex and not appropriate for a linear optimization technique.
-The conclusion was that global optimization techniques were necessary in order to calibrate AMs.
-The relevance of Genetic Algorithms (GAs) is presented here, which doesn't exclude that other global optimization techniques could also be successful.
+This technique did not provide satisfying results and failed at converging toward a unique solution.
+The parameter space of the AM is very complex and is not appropriate for a linear optimization technique.
+The conclusion was that global optimization techniques were necessary in order to calibrate AMs, as it is the only way to optimize all parameters of all analogy levels simultaneously.
+In addition, it can overcome the systematic manual assessments of all pressure levels and temporal windows.
+Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the pressure levels \citep[see][]{Horton2016b}, and the consideration of non-overlapping spatial windows between the pressure levels.
+The relevance of Genetic Algorithms (GAs) is presented here, which does not exclude that other global optimization techniques could also be successful.
 
@@
 These analyses are presented here and result in recommendations for the use of GAs when applied to AMs.
-The demonstration of the benefit brought by such an approach in a specific case study is the topic of \cite{Horton2016b}.
-
-We will begin with a motivation for a global optimization (section \ref{sec:motivation}) and then present the concepts of GAs as well as the assessed operators (section \ref{sec:gas}).
+The demonstration of the benefit brought by such an approach in a specific case study is the topic of \citet{Horton2016b}.
+
+We will begin by presenting the concepts of GAs as well as the assessed operators (section \ref{sec:gas}).
 The comparative analyses of the operators and their results are presented in section \ref{sec:assessment}, which lead us to the recommendations in section \ref{sec:recommendations}.
-
-\section{Motivation for a global optimization}
-\label{sec:motivation}
-
-The sequential calibration is fast to optimize one spatial window for a given pressure level and temporal window.
-However, it doesn't provide an objective selection of the pressure level and temporal window.
-The only option is to try systematically every combination, which becomes cumbersome already with 2 pressure levels, whereas it seems profitable to consider even more \citep{Horton2012a}.
-
-During the AM calibration it has been found that the resulting parameters may vary with initial choices (such as the number of analogues).
-In addition, the different levels of analogy (eg.
-on the atmospheric circulation and the moisture index) are always calibrated sequentially.
-However, any dependency between them cannot be excluded, which could lead us to select another parametrization if calibrated together.
-Simultaneous calibration of all parameters has never been undertaken so far.
-Only a global optimization technique can be able to optimize all parameters of all analogy levels simultaneously.
-
-When creating the sequential calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters and wrote: '' \textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent.
-We will present our results by first searching the best variable [note: e.g.
-selection of the pressure level and the temporal window for the geopotential height] on a chosen spatial window, and next, the best window for the chosen variable.
-However, even by repeating the process, are we sure to obtain the optimal combination?} ''.
-And later in his work: '' \textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution} ''.
-\citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of the AM and concludes that one needs to be an expert to know their respective influence, their sensitivity and their nonlinear interactions.
-\citet{BenDaoud2010}, when calibrating the AM, also stated that '' \textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously } ''.
-
-The AM needs to be adapted to every new region it is applied, because the leading meteorological influences are specific to this region.
-Even the selection of the pressure levels and the temporal windows should be reconsidered, when not the variable itself.
-For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012a} found no interest in this variable in an Alpine environment, because the vertical motion, which is mainly controlled by orographic effects, was already well related to the atmospheric circulation itself.
-So, when adapting the AM to a new region, one should assess systematically every combination of pressure levels, temporal and spatial windows, which is an intensive task.
-This procedure can be automatized by a global optimization technique.
-
-The goal was then to assess the feasibility of an automatic optimization of the AM in order to assess all parameters simultaneously, and thus to be able to get nearer to the global optimum in the parameters space.
-In addition, it can overcome the systematic manual assessments of all pressure levels and temporal windows.
-Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the pressure levels \cite[see]{Horton2016b}, and the consideration of non-overlapping spatial windows between the pressure levels.
 
@@
 
-GAs are part of the family of evolutionary algorithms \citep{Back1993b, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
-GAs are the most used technique from evolutionary algorithms \citep{Back1993b}, and they are constantly improving \citep{Haupt2004}.
-However, with time, the different methods of evolutionary algorithms tend to be similar and share many commonalities \citep{Back1996b, Haupt2004}.
+GAs are part of the family of Evolutionary Algorithms \citep{Back1993b, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
+GAs are the most used technique from Evolutionary Algorithms \citep{Back1993b}, and they are constantly improving \citep{Haupt2004}.
+However, with time, the different methods of Evolutionary Algorithms tend to be similar and share many commonalities \citep{Back1996b, Haupt2004}.
 
@@
 
-\subsection{Basic concepts of the genetic algorithms}
+\subsection{Basic concepts of the Genetic Algorithms}
 
 GAs mimic the evolution of a population of individuals in a new environment, by applying rules based on natural processes, such as DNA mutation, chromosomes crossover, natural selection, etc.
-It simulates the fact that in a natural environment, the most suitable individuals tend to survive longer, to reproduce more easily, and so to influence coming generations by providing genes that provide some good performance in a certain domain.
 Generation after generation, the DNA mixes and the strong genes cumulate in some individuals \citep{Beasley1996a}.
-Globally, the fitness of the population to its environment increases, while retaining enough variety to not converge too quickly to a local optimum.
-
-Applications of GAs are very diversified as they can handle many parameters of various types \citep{Joines1996a}, even with very complex cost surfaces \citep{Haupt2004}.
-The objective function to optimize (often named fitness function in this context) can be of different types (mathematical function, experimental or numerical modeling).
-Only the resulting value is used for optimization.
-Indeed, these algorithms do not require any knowledge of the problem, which can be used as black-box, but they must be adapted in order to perform optimally.
+
+Applications of GAs are very diversified as they can handle many problems of various types \citep{Joines1996a}, even with very complex cost surfaces \citep{Haupt2004}.
+The objective function to optimize (often named fitness function in this context) can be of different types, only the resulting value is used for optimization.
+Indeed, these algorithms do not require any knowledge of the problem, but they must be adapted in order to perform optimally.
 
@@
 Each individual contains a chromosome (parameters of the AM in this case).
-Genes are all parameters constituting the chromosome.
+Genes are the parameters constituting the chromosome.
 The floating-point representation \citep[instead of the canonical binary, see][]{Goldberg1989, Goldberg1990a, Holland1992b} of the genes was considered, as it was found more suited in multiple applications \citep{Michalewicz1996, Herrera1998a, Haupt2004, Back1996b, Gaffney2010a}.
 
-There are numerous implementation variants of GAs often optimal for a given problem \citep{Hart1991a, Schraudolph1992a}.
+There are numerous implementation variants of GAs, often optimal for a given problem \citep{Hart1991a, Schraudolph1992a}.
 The divergences are the operators implementation, through significantly different algorithms, which has an important effect on the results \citep{Gaffney2010a}.
@@
 	\noindent\includegraphics[width=19pc,angle=0]{figures/figure_structure_gas.pdf}\\
-	\caption{Genetic algorithms operational flowchart}
+	\caption{Genetic Algorithms operational flowchart}
 	\label{fig:structure_gas}
@@
 Natural selection is performed on the basis of the values of the objective function.
-The selection allows to only keep a certain part of the population, usually half ($N/2$), which can access the IG (with $N_{mp}$ members).
-If $N_{mp}$ is too high, the reproduction rate is too low, whereas if it is too small, the strong traits of individuals do not have the ability to accumulate in the same chromosome \citep{Haupt2004}.
+The selection allows to only keep a certain part of the population, usually half ($N/2$), which can access the IG (with $N_{IG}$ members).
+If $N_{IG}$ is too high, the reproduction rate is too low, whereas if it is too small, the strong traits of individuals do not have the ability to accumulate in the same chromosome \citep{Haupt2004}.
 Several techniques exist, such as:
@@
 \begin{itemize}
-	\item $N_{mp}$-elitism \citep{Michalewicz1996}: the population is sorted according to the value of the objective function and only the better half is preserved.
+	\item $N_{IG}$-elitism \citep{Michalewicz1996}: the population is sorted according to the value of the objective function and only the better half is preserved.
 
@@
 	\item Roulette wheel weighting: this technique refers to gambling, but with a biased roulette.
-Each individual is associated with a sector of the wheel with a certain opening angle, which is its probability of selection \citep{Haupt2004}.
+Each individual is associated with a sector of the wheel with a certain opening angle, which is its probability of selection.
 The probability assigned to the individuals is proportional to their fitness (objective function), so that the most adapted individuals have the greatest probability of reproduction.
@@
 	\begin{equation}
-	p_{n}=\dfrac{N_{mp}-n+1}{\sum^{N_{mp}}_{n=1}n}
+	p_{n}=\dfrac{N_{IG}-n+1}{\sum^{N_{IG}}_{n=1}n}
 	\label{equation_mating_rank_weighting}
@@
 	\begin{equation}
-	p_{n}=\frac{score_{n}-score_{N_{mp}}}{\sum_{n=1}^{N_{mp}} (score_{n}-score_{N_{mp}})}
+	p_{n}=\frac{score_{n}-score_{N_{IG}}}{\sum_{n=1}^{N_{IG}} (score_{n}-score_{N_{IG}})}
 	\label{equation_mating_score_weighting}
 	\end{equation}
-	In this application, the last individual ($N_{mp}$) has zero probability of being selected.
+	In this application, the last individual ($N_{IG}$) has zero probability of being selected.
 
@@
 The combination of chromosomes is carried out using a crossover operator, thereby generating two offspring having characteristics derived from both parents.
-Chromosome crossover widens the search space and favours the combination of strong genes, which can result in more suited children.
 It allows a mixing of genes and accumulation of positive mutations.
@@
 
-Many other methods or variations exist, combining the advantages of different approaches.
-The performance of the variants being related to the problem to be addressed, one cannot identify a priori the best technique for any application.
-
 \subsubsection{Mutation}
@@
 	\end{equation}
-	where $\sigma$ is the standard deviation of the distribution.
-The disadvantage of this technique is that an accurate value of $\sigma$ must be chosen \citep{Haupt2004}, which is impossible to know beforehand.
-
-	\item Variable normal mutation: with the same logic as the variable uniform mutation, a mutation operator was tested using a normal distribution with a variable mutation rate and standard deviation.
+	where $\sigma$ is the standard deviation of the distribution, which has to be estimated.
+
+	\item Variable normal mutation (new): with the same logic as the variable uniform mutation, a mutation operator was tested using a normal distribution with a variable mutation rate and standard deviation.
 The mutation rate is calculated with equation \ref{equation_mutation_uniformvariable}.
@@
 Thus, as this rate decreases, it will have less probability of being itself mutated.
-This approach is close to the natural adaptation phenomena: a population less suited to its environment is changing faster than better adapted populations.
 Mutations are performed according to a constant uniform distribution.
@@
 	\item Individual adaptive search radius (new): based on the ideas of the non-uniform mutation, a search radius was introduced in the approach of individual adaptive mutation rates.
-This search radius $r_{a}$, bounded between 0 and 1, is also adaptive and behaves similarly to the adaptive mutation rates.
+This search radius $r_{a}$, bounded between 0 and 1 (relatively to the parameters ranges), is also adaptive and behaves similarly to the adaptive mutation rates.
 In order to separate its evolution from the one of the mutation rate, its own value is considered initially as a self-mutation rate to eventually mutate before being used as a normalized search radius.
@@
 For example, when a crossover or a mutation operation results in a parameter value standing out of the authorized bounds, it has to be brought back within the limits.
-Moreover, the parameters are of different nature: some are continuous, such as the weighting between pressure levels, some are discretized, such as the analogues number, or the spatial windows, and finally, some are independent elements in an array, such as the selection of the meteorological variable.
+Moreover, the parameters are of different nature: some are continuous, some are discretized, and finally, some are independent elements in an array, such as the selection of the meteorological variable.
 New values resulting from the optimizer need to respect the type of data it represents.
@@
 Other constraints exist in between the parameters, such as the temporal window of the moisture index \cite[see][]{Horton2016} that has to be consistent in between the relative humidity and the precipitable water.
-Another example is the weighting of the different pressure levels which has to be normalized.
 
@@
 Even GAs parametrization that will be further considered as inadequate (Figure \ref{fig:gas_evolution_bad}) did significantly better that the sequential approach.
+The amplitude of the improvement is not the main outcome here.
+The most important point is that GAs are proven successful at optimizing AMs automatically, globally, and objectively.
 
@@
 	\caption{Evolution of the score of the best individuals over generations for the 10 optimizations processed for a given parametrization.
-The green line represents the score of the sequential approach and the blue one, the supposed global optimum.}
+The green line (bottom) represents the score of the sequential approach and the blue one (top), the supposed global optimum.}
 	\label{fig:gas_evolution_good}
@@
 Every combination of 6 options for the couples selection (Table \ref{tab:assessed_couples_selection_operators}) and 21 for the chromosome crossover operators (Table \ref{tab:assessed_crossover_operators}) were evaluated, along with variants of the other operators.
-This results in 1,008 combinations, requiring 10,080 optimizations.
+This resulted in 1,008 combinations, requiring 10,080 optimizations.
 
@@
 
-Having identified the leading role of the mutation operator, the sensitivity analysis focused on it.
+Having identified the leading role of the mutation operator, the next sensitivity analysis focused on it.
 Each of the 10 different implementations (see section \ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Table \ref{tab:assessed_mutation_operators}), bringing the number of its variations up to 109.
 Some optimizations without any mutation were also performed as a reference.
-Along with variants of the other operators \citep[see][for the details]{Horton2012a}, it resulted in 660 combinations (so 6,600 optimizations).
+Along with variants of the other operators \citep[see][for the details]{Horton2012a}, this resulted in 660 combinations (so 6,600 optimizations).
 
@@
 The details of the analysis \citep[see][]{Horton2012a} show that the other reproduction operators seem of secondary importance.
-This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction.
-He even suggests, in opposition with the theory of \citet{Holland1992a}, that chromosomes crossovers have mostly a corrective role of mutation operations.
-Various studies have also identified the importance of the mutation operator relatively to reproduction \citep[see eg.][]{Back1992a, Back1996b, Smith1997a, Deb1999, Haupt2004, Costa2005a, Costa2007a}.
+This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction, as well as other authors (see section \ref{sec:gas}.\ref{sec:gas:mutation}).
 
 The mutation operators based on a variable normal or variable uniform laws work very poorly and are difficult to configure.
-Many operators present more or less with the same performance scores and require a variable amount of assessments.
+Many operators present more or less the same performance scores and require a variable amount of assessments.
 The convergence analysis \citep[see][]{Horton2012a} allows to highlight three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
-Because of the importance of the mutation operator on the resulting performance, its role and parametrization were studied in more detail.
-Thus, different optimizations were performed using variants of these 3 operators (Table \ref{tab:assessed_mutation_operators_bis}).
+Thus, different optimizations were further performed using variants of these 3 operators (Table \ref{tab:assessed_mutation_operators_bis}).
 
@@
 For most options, it is also slightly better than the results from the optimization without selection of the pressure levels (blue line).
-A clear breakthrough of the performances was not expected, as the former selection of pressure levels results from intensive work \citep{Bontron2004}.
+A clear breakthrough of the performances was not expected, as the former selection of pressure levels results from intensive comparative work \citep{Bontron2004}.
 This application however demonstrates that, when correctly parametrized, GAs can automatically and successfully choose the pressure levels.
@@
 \begin{itemize}
-	\item $N\approx100$ for a very simple implementations of the AM (1 level of analogy with 2 pressure levels),
+	\item $N\approx100$ for very simple implementations of the AM (1 level of analogy with 2 pressure levels),
 	\item $N\approx200$ for a bit more complex AM (1 level of analogy with 4 pressure levels, or 2 level of analogy with less pressure levels),
@@
 	\item Mutation has a clearly dominant influence.
-Three mutation operators stand out, two of which are new: the non-uniform mutation, the multi-scale mutation, and the chromosome of adaptive search radius.
+Three mutation operators stand out: the non-uniform mutation, the multi-scale mutation, and the chromosome of adaptive search radius.
 The latter is the most robust as it has no controlling parameter.
@@
 In order to automatically optimize the AM and to get rid of the limitations of the usual sequential calibration, GAs were evaluated.
-Given the large number of existing operators and options, multiple variants were evaluated systematically in order to identify which operators are important, and which variant works best for the AM.
-The mutation operator was identified as a key element for this application, and provided new variants that were found to be efficient, such as the chromosome of adaptive search radius that is very robust (no control parameter).
+Given the large number of existing operators and options, multiple variants were assessed systematically in order to identify which operators are important, and which variants work best for the AM.
+The mutation operator was identified as a key element for this application, and new variants that were found to be efficient were provided, such as the chromosome of adaptive search radius that is very robust (no control parameter).
 Recommendations were established for a relevant use of GAs for the optimization of AMs.
 
-It is not excluded that another global optimization methods or other operators of GAs may perform better.
-The relevance of such approach has now been proven as it results in parametrization of AMs that are relevant and fully automatically established.
+It is not excluded that another global optimization method or other operators of GAs may perform better.
+The relevance of such approach has now been proven as it results in parametrization of AMs that are relevant and fully automatically, globally and objectively established.
 A global optimization is the only way to take into account all the dependencies between parameters and levels of analogy.
 
-The global optimization approach allow easily adapting the AM to new regions by taking into account local meteorological influences, and has thus a great potential of use.
+The global optimization approach allows easily adapting the AM to new regions by taking into account local meteorological influences, and has thus a great potential of use.
 Moreover, it allows exploring automatically datasets in order to extract the most relevant variables.
@@
 Thanks to Renaud Marty for his fruitful collaboration over the years.
-Thanks to Dominique B\'{e}rod for his support.
+Thanks to Dominique B\'{e}rod for his support and to Michel Bierlaire for his advices on optimization methods.
 

### 2015-11-25 Genetic algorithms - Journal of Climate/template.tex
Personal corrections of Optimization case study for v1.

@@
 Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
-The fruitful collaboration with the Laboratoire d’Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
+The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
 NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.

### 2015-11-25 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Personal corrections of Optimization case study for v1.

@@
 \address[unil]{University of Lausanne, Lausanne, Switzerland}
-\address[terranum]{Terranum LLC, Rue de l'industrie 35 bis, 1030 Bussigny, Switzerland}
+\address[terranum]{Terranum, Rue de l'industrie 35 bis, 1030 Bussigny, Switzerland}
 \address[lthe]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}
@@
 The method samples a selection of days in the archives that are similar to the target day to forecast, and consider the corresponding observed precipitation (the predictand) as the conditional distribution for the target day.
-The statistical relationship between predictors and predictands relies on some parameters that characterize how and where the similitude between two atmospheric situations has to be defined.
+The relationship between predictors and predictands relies on some parameters that characterize how and where the similitude between two atmospheric situations is defined.
 
@@
 
-In this work, the global optimization is applied to the Rh\^{o}e catchment in the Swiss Alps in order to show its interest and the relevance of the resulting parameters.
+In this work, the global optimization is applied to the Rh\^{o}ne catchment in the Swiss Alps in order to show its interest and the relevance of the resulting parameters.
 Indeed, not only the performance increases, but the parameters are obtained automatically and objectively, which reduces effort-hours when adapting the method to a new region or for a new predictand.
@@
 The analogue method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1956, Lorenz1969}, that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Duband1970, Bontron2005}.
-It aims at forecasting a predictand, often the daily precipitation \citep[eg.]{Guilbaud1997, Bontron2005, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, BenDaoud2015}, on the basis of predictor variables describing the synoptic atmospheric circulation.
+It aims at forecasting a predictand, often the daily precipitation \citep[eg.][]{Guilbaud1997, Bontron2005, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, BenDaoud2015}, on the basis of predictor variables describing the synoptic atmospheric circulation.
 Other predictands are also often considered \citep[see][for a non-exhaustive list]{Horton2016}.
 
-In operational forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies, it is newly used to downscale the results of global climate model (GCM) simulation runs.
+In operational forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies, it is used to downscale the results of global climate model (GCM) simulation runs.
 In this last case, although the GCM represents the large or regional scale evolutions of the atmosphere, it would be far too computer intensive to get down to variables such as precipitation at a rather small and representative scale.
-Therefore the idea to rely on past observations to bypass these unaffordable small scale simulations and to go from the large scale situation proposed by the GCM to the end variables like precipitation by searching anlogs in the past and present archive.
+Therefore the idea is to rely on past observations to bypass these unaffordable small scale simulations and to go from the large scale situation proposed by the GCM to the end variables like precipitation by searching analogues in the archives.
 
@@
 This sequential approach has strong limitations: (i) it cannot automatically choose the pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it could not handle new degrees of freedom, such as a weighting between the pressure levels.
-Thus, even if the processing involved is relatively fast, the sequential approach requires laborious assessments of predictors combinations (variables, pressure levels, temporal windows), and present a high risk of ending in a local optimum due to subjective initial choices and lack of consideration of parameters dependencies.
+Thus, even if the processing involved is relatively fast, the sequential approach requires laborious assessments of predictors combinations (variables, pressure levels, temporal windows), and present a high risk of ending in a local optimum due to subjective initial choices and lack of consideration of parameters inter-dependencies.
 
-With the perspective to overcome these limitations, a global optimization technique, namely Genetic Algorithms (GAs) was introduced by \citet{Horton2016a}.
+With the perspective to overcome these limitations, a global optimization by Genetic Algorithms (GAs) was introduced by \citet{Horton2016a}.
 An intensive assessment work resulted in recommendations of parametrization of GAs in order to optimize AMs successfully.
-The present paper is based on these recommendations and apply them to precipitation forecasting for the upper Rh\^{o}e catchment in the Swiss Alps.
+The present paper is based on these recommendations and apply them to precipitation forecasting for the upper Rh\^{o}ne catchment in the Swiss Alps.
 It aims at proving the relevance of a fully-automatic, objective, and global, optimization technique for AMs.
@@
 Multiple variations of the methods exist, and most of them will not be detailed hereafter \cite[see][for more comprehensive listings]{Horton2016, BenDaoud2015}.
-However, there are mainly 2 parametrizations that are most often used for precipitation forecasting and that will be considered as reference: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
+However, there are mainly 2 parameterizations that are most often used for precipitation forecasting and that will be considered as reference: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
 
-The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): the similarity of the atmospheric circulation of a target date with every day of the archive is assessed by processing the S1 criteria \citep[Eq.\ (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
-\citet{Bontron2005} showed that the geopotential height at 500~hPa and 1000~hPa are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criteria performs better than scores based on absolute distances.
+The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): the similarity of the atmospheric circulation of a target date with every day of the archive is assessed by processing the S1 criteria \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
+\citet{Bontron2005} showed that the geopotential height at 500~hPa (Z500) and 1000~hPa (Z1000) are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criteria performs better than scores based on absolute distances.
 The reason for such better results is that the S1 criteria allows comparing the circulation pattern, by means of the gradients, rather than the absolute value of the geopotential height.
-To cope with seasonal effects, candidate dates are extracted within a period of 4 months centred around the target date, for every year of the archive.
+To cope with seasonal effects, candidate dates are extracted within a period of 4 months centered around the target date, for every year of the archive.
 Following the nomenclature proposed by \citet{Horton2016}, this method will be named 2Z.
@@
 The differences are processed separately in both directions.
-The smaller the S1 values are, the more similar the pressure fields.
+The smaller the S1 values, the more similar the pressure fields.
 
-\begin{table}[htbp]
-	\caption{Parameters of the reference method on the atmospheric circulation (2Z).}
+\begin{table}[htb]
+	\caption{Parameters of the reference method on the atmospheric circulation (2Z).
+The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window).
+The criteria used for the current level of analogy is then provided, as well as the number of analogues.}
 	\footnotesize
@@
 			\hline 
-			\multirow{2}{*}{1} & Z 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
-			& Z 500~hPa & 24~h & & \\ 
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
+			& Z500 & 24~h & & \\ 
 			\hline 
@@
 The other most know parametrization adds a second level of analogy on moisture variables (method 2Z-2MI, Table \ref{table:params_R2}).
-The predictor that \citet{Bontron2004} found optimal for the France territory is a moisture index made of the product of the precipitable water with the relative humidity at 850~hPa.
-\cite{Horton2012a} confirmed that this index is better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis considered independently.
+The predictor that \citet{Bontron2004} found optimal for the France territory is a moisture index made of the product of the precipitable water with the relative humidity at 850~hPa (RH850).
+\cite{Horton2012a} confirmed that this index is also better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis considered independently.
 When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
@@
 
-\begin{table}[htbp]
-	\caption{Parameters of the reference method with moisture variables (2Z-2MI).}
+\begin{table}[htb]
+	\caption{Parameters of the reference method with moisture variables (2Z-2MI). Same conventions as Table \ref{table:params_R1}}
 	\footnotesize
@@
 			\hline 
-			\multirow{2}{*}{1} & Z 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
-			& Z 500~hPa & 24~h & & \\ 
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
+			& Z500 & 24~h & & \\ 
 			\hline
-			\multirow{2}{*}{2} & TPW * RH 850~hPa & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{30} \\
-			& TPW * RH 850~hPa & 24~h & & \\ 
+			\multirow{2}{*}{2} & TPW * RH850 & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{30} \\
+			& TPW * RH850 & 24~h & & \\ 
 			\hline 
@@
 Predictors are generally reanalysis datasets.
-NCEP-NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} are used here, but it can be any other reanalysis dataset.
+NCEP-NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} are used here, but it could be any other reanalysis dataset.
 
-The predictand (which is to be predicted) is in here the daily precipitation (6~a.m.
+The predictand (which is to be predicted) is here the daily precipitation (6~a.m.
 to 6~a.m.
@@
 
-The most used score to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
-It allows assessing the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$.
+The score that is most often used to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
+It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$.
 The better the forecast, the smaller the score.
@@
 
-This score is now commonly used for the evaluation of continuous variables prediction systems \citep{Casati2008, Marty2010}.
-To compare the value of the score in regard to a reference, one often considers its skill score value, and use the climatological distribution as the reference.
+In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution as the reference.
 The CRPSS (\textit{Continuous Ranked Probability Skill Score}) is thus defined as following:
@@
 Genetic Algorithms (GAs) were developed by \citet{Holland1992b} and popularized by \citet{Goldberg1989}.
-They are part of evolutionary algorithms \citep{Back1993b, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
+They are part of Evolutionary Algorithms \citep{Back1993b, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
 GAs seek the global optimum on a complex surface, theoretically without restriction.
@@
 It is indeed mainly a matter of time.
-When the optimizer gets closer to the global optimum, any new improvement takes more time to appear (see figure \ref{fig:evolution}), and the final adjustment of the parameters is very time consuming \citep{Back1993a}.
+When the optimizer gets closer to the global optimum, any new improvement takes more time to appear (see for example Figure \ref{fig:evolution}), and the final adjustment of the parameters is very time consuming \citep{Back1993a}.
 For problems that require a significant amount of time in order to evaluate the objective function, as in the case of AMs, the number of generations has to be limited in order to get reasonable processing time.
 Thus, different acceptable solutions can result from one or more optimizations \citep{Holland1992b}.
-This is a strength and a weakness of GAs: they are very good at exploring complex parameter spaces in order to identify the most promising areas, but they will not necessarily find the best solution with the optimal values of all parameters \citep{Holland1992b}.
+This is a strength and a weakness of GAs: they are very good at exploring complex parameter spaces in order to identify the most promising areas, but they will not necessarily always find the best solution with the optimal values of all parameters \citep{Holland1992b}.
 
@@
 
-A population size of 500 individuals (parameters sets of the AM) was considered, and the optimization was stopped when the best individual (with the highest CRPSS performance score) did not evolve for 20 generations (cycles of the optimization).
+A population size of 500 individuals (parameter sets of the AM) was considered, and the optimization was stopped when the best individual (with the highest CRPSS performance score) did not evolve for 20 generations (cycles of the optimization).
 
@@
 This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at providing a real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
-Even thought the region is rather small, the meteorological influences related to extreme weather conditions varies substantially within it \citep[see][]{Horton2012}.
+Even though the region is rather small, the meteorological influences related to extreme weather conditions varies substantially within it \citep[see][]{Horton2012}.
 Based on different climatological analyses, the gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}) :
@@
 The 48 years precipitation dataset (see section \ref{sec:intro}.\ref{sec:data}) was divided into a calibration period (CP) and a validation period (VP).
-Using data independent from the CP to validate the results is very important in order to assess the robustness of the improvements and to avoid overparametrization of the method.
+Using data independent from the CP to validate the results is very important in order to assess the robustness of the improvements and to avoid over-parametrization of the method.
 
-In order to reduce potential bias related to trends in the climate change or to the evolution in measurement techniques, the selection of the VP is evenly distributed over the entire series \citep{BenDaoud2010}.
+In order to reduce potential bias related to trends linked to climate change or to the evolution in measurement techniques, the selection of the VP is evenly distributed over the entire series \citep{BenDaoud2010}.
 Thus, one year every six years were selected for validation, which represents a total of 8 years for the VP and 40 for CP.
@@
 
-The analogy of atmospheric circulation alone was first optimized, without moisture variables, for the 10 subregions.
+The analogy of the atmospheric circulation was optimized for the 10 subregions.
 We started from the most simple AM, and increased the complexity in order to identify the degrees of freedom that are of particular interest.
 Thus, the tested parametrization evolved iteratively in complexity.
-The detailed results of the intermediate stages are not provided \citep[see][for the details]{Horton2012a}, but only the main conclusions.
+The detailed results of the intermediate stages are not provided \citep[see][for the details]{Horton2012a}.
 
 The reference method for the analogy of the atmospheric circulation (2Z, Table \ref{table:params_R1}), based on the 500 and 1000~hPa levels, was first considered.
-The optimizer had to choose the number of analogues, both spatial windows with no overlapping constraint, as well as the temporal window (hours of observation of the geopotential), what the sequential calibration cannot do.
+The optimizer had to choose the number of analogues, both spatial windows with no overlapping constraint, as well as the temporal windows (hours of observation of the geopotential), what the sequential calibration cannot do.
 With these degrees of freedom, a relative CRPSS improvement of 3.97\% and 2.45\% in average was obtained for the CP and the VP respectively.
@@
 
-Then, an additional degree of freedom was provided to the AGs by letting them choose the pressure levels along with the other parameters, which is also a non-automated process in the sequential calibration.
+Then, an additional degree of freedom was provided to the GAs by letting them choose the pressure levels along with the other parameters, which is also a non-automated process in the sequential calibration.
 This degree of freedom increased the optimization time and may decrease the number of simulations that converge to a single solution.
@@
 Parallel analyses showed that the analogy of circulation is incomplete, and that the geopotential still contains relevant data that can improve the statistical relationship.
-Therefore, a third predictor was added (still the geopotential height) that the optimizer could use along with the previous parameters.
+Therefore, a third predictor was added (still on the geopotential height) that the optimizer could use along with the previous parameters.
 There was no constraint on the predictors, so that the same pressure level could be selected multiple times.
@@
 However, the score value on the VP dropped after 4 predictors, revealing an over-parametrization of the method, and thus a lack of robustness.
-Thus, considering 4 predictors is optimal for this case study, since the gain in CRPSS is significant.
+Considering 4 predictors is optimal for this case study, since the gain in CRPSS is significant.
 It cannot be excluded that another number would prevail in another region under other meteorological conditions.
 
-Finally, a weighting of these 4 predictors (pressure levels) was added, which is also optimized by GAs.
+Finally, a weighting of the criteria values per pressure level was added, which is also optimized by GAs.
 The weighting operates in the combination of the S1 criteria processed on every level, which were previously averaged with equal weights.
@@
 
-The method finally optimized for the atmospheric circulation analogy, based on 4 levels of the geopotential, and that will be name 4Zo, is made of the following degrees of freedom:
+The chosen method for the atmospheric circulation analogy, based on 4 levels of the geopotential, and that will be name 4Zo, is made of the following degrees of freedom:
 
@@
 
-This sums up to 29 degrees of freedom that are optimize simultaneously.
+This sums up to 29 degrees of freedom that are optimized simultaneously.
 
@@
 The gain in score increases with the precipitation threshold: in average, respectively for the different thresholds, 13.3\%, 15.4\% and 29.1\% for the CP and 7.9\%, 11.1\% and 34.5\% for the VP.
-The optimized improves thus even more the forecasts for days with significant precipitation than usual days.
+The optimization improves thus even more the forecasts for days with significant precipitation than usual days.
 
 To assess the parameters cross-compatibility, those optimized for one subregion were applied to the others.
-The resulting losses or gains of the CRPSS are displayed in Table \ref{table:crossing_4Zo_calib} for the CP and in Table \ref{table:crossing_4Zo_valid} for the VP.
-
-\begin{table}[htbp]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo, calibration period.}
-	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4_calib.pdf}}
-	\label{table:crossing_4Zo_calib}
-\end{table}
-
-\begin{table}[htbp]
-	\caption{Same as Table \ref{table:crossing_4Zo_calib} but for the validation period.}
-	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4_valid.pdf}}
-	\label{table:crossing_4Zo_valid}
-\end{table}
+The resulting losses or gains of the CRPSS are displayed in Figure \ref{fig:crossing_4Zo_calib} for the CP and in Figure \ref{fig:crossing_4Zo_valid} for the VP.
 
@@
 First of all, the level 1000~hPa is always selected twice (the first time at 6 or 12~h, and the second always at 30~h) and the 700~hPa is selected once for every subregion (always at 24~h).
-The level which varies from one subregion to another is the upper level (however always at 12~h), that is 300~hPa for the North-West part of the catchment, 500~hPa for most of the subregions, and 600~hPa for the Conches Valley.
+The level which varies from one subregion to another is the upper level (however always at 12~h), which is 300~hPa for the North-West part of the catchment, 500~hPa for most of the subregions, and 600~hPa for the Conches Valley.
 Its spatial distribution is however homogeneous.
@@
 The last one (1000~hPa at 30~h) is rather large and squared.
-Surprisingly, subregions number 5 (Left side valleys) and 6 (Southern ridges) have exactly the same spatial windows, which suggest that they behave in a similar way and thus could have been merged.
+Subregions number 5 (Left side valleys) and 6 (Southern ridges) have exactly the same spatial windows, which suggest that they behave in a similar way and thus could have been merged.
 This similarity is a good sign for the accuracy of the optimized parameters.
@@
 
-The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the CP when they are calibrated for the given subregion (Table \ref{table:crossing_4Zo_calib}).
+The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the CP when they are calibrated for the given subregion (Figure \ref{fig:crossing_4Zo_calib}).
 However, the losses in CRPSS when exchanging the parameters are not of the same amplitude between the different subregions.
@@
 Parameter sets from other subregions perform poorly for these subregions, and vice versa.
-This points to the importance of taking into account leading meteorological influences during discretization, that are not always best represented by their physical distance.
-Globally, the same pattern can be observed for the VP (Table \ref{table:crossing_4Zo_valid}), but in this case, minor improvements may be observed when crossing the parameters.
-The reason being that the independant VP contains other events that may be better forecasted by other parameter sets.
-The relative small differences in score between parametrizations indicate that even though the parameters may differ significantly, the performance may not be drastically affected.
+This points to the importance of taking into account leading meteorological influences during discretization, that are not always best represented by the physical distance.
+Globally, the same pattern can be observed for the VP (Figure \ref{fig:crossing_4Zo_valid}), but in this case, minor improvements may be observed when crossing the parameters.
+The reason being that the independent VP contains other events that may be better forecasted by other parameter sets.
+The relative small differences in score between parameterizations indicate that even though the parameters may differ significantly, the performance may not be drastically affected.
 Even a change in the pressure level does not mean a radical drop of the score value.
 A different parametrization leads to a different selection of the analogue days, and thus to an improvement of the forecast of certain weather conditions at the expense of others.
-This raises the question of optimizing more specifically for extreme weather conditions only.
+This raises the question of optimizing more specifically for extreme weather conditions in priority.
 
@@
 
-\begin{table}[htbp]
+\begin{table}[htb]
 	\caption{Parameters of the 4Zo-2MIo method (atmospheric circulation on 4 levels and moisture index on 2 levels), optimized for the Chablais subregion.
@@
 
-\begin{table}[htbp]
+\begin{table}[htb]
 	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the 4Zo-2MIo method, at the different subregions.}
@@
 
-\begin{table}[htbp]
+\begin{table}[htb]
 	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo-2MIo method.}
@@
 
-The parameters cross-compatibility has also been assessed for the methods with moisture variables, and are shown in Tables \ref{table:crossing_4Zo-2MIo_calib} and \ref{table:crossing_4Zo-2MIo_valid} for the method 4Zo-2MIo (not shown for 4Zo-4MIo, but similar).
-
-\begin{table}[htb]
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo-2MIo, calibration period.}
-	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi2_calib.pdf}}
-	\label{table:crossing_4Zo-2MIo_calib}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Same as Table \ref{table:crossing_4Zo-2MIo_calib} but for the validation period.}
-	\centerline{\includegraphics[width=\linewidth]{figures/table_crossing_z4-hi2_valid.pdf}}
-	\label{table:crossing_4Zo-2MIo_valid}
-\end{table}
+The parameters cross-compatibility has also been assessed for the methods with moisture variables, and are shown in Figures \ref{fig:crossing_4Zo-2MIo_calib} and \ref{fig:crossing_4Zo-2MIo_valid} for the method 4Zo-2MIo (not shown for 4Zo-4MIo, but similar).
 
@@
 There is indeed a shift of the previously selected 1000~hPa for higher levels, which is even slightly stronger with 4 moisture predictors than with 2.
-This change is likely due to the fact that when considering only the circulation analogy, the method tries to take into account information that can serve as proxy for moisture assessment, whereas it doesn't need it with the moisture index.
+This change is likely due to the fact that when considering only the circulation analogy, the method tries to take into account information that can serve as proxy for moisture assessment, whereas it does not need it with the moisture index.
 This aspect has never been demonstrated before, as sequential calibration tools do not allow it.
@@
 
-The selected pressure levels for the analogy on the moisture index are strongly centred around 700~hPa and 600~hPa.
+The selected pressure levels for the analogy on the moisture index are strongly centered around 700~hPa and 600~hPa.
 No other value has been selected when considering 2 pressure levels (Table \ref{table:levels_GA_4Zo_2MIo}), and when considering 4 levels, 850~hPa and 500~hPa are sometimes also selected (not shown).
@@
 
-The analysis of the parameters cross-compatibility (Tables \ref{table:crossing_4Zo-2MIo_calib} and \ref{table:crossing_4Zo-2MIo_valid}) is also very similar to the one on the circulation analogy only (results for 4Zo-4MIo not shown as very similar).
+The analysis of the parameters cross-compatibility (Figures \ref{fig:crossing_4Zo-2MIo_calib} and \ref{fig:crossing_4Zo-2MIo_valid}) is also very similar to the one on the circulation analogy only (results for 4Zo-4MIo not shown as very similar).
 The same pattern can be observed, with a drop of performance for the subregions under different meteorological influences.
 However, the losses of performance are globally more important than before, suggesting that more complex methods with moisture variables are less transposable to another subregion, even though it is located within the same grid cell of the reanalysis dataset.
+The meteorological influences should be taken into account.
 
@@
 This approach allowed us to differentiate the contributions to performance gains, as well as to identify possible over-parametrization.
-The main improvements for the resent case study are due to the following factors:
+The main improvements for the present case study are due to the following factors:
 
@@
 	\item The introduction of distinct spatial windows between pressure levels.
-Indeed, the synoptic circulation is characterized by features with very different scales depending on the height, and important information for predicting rainfall is not necessarily located in the same area from one level to another.
+The synoptic circulation is characterized by features with very different scales depending on the height, and important information for predicting rainfall is not necessarily located in the same area from one level to another.
 The optimized spatial windows are consistent in between the subregions.
@@
 This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that one has to stop it before the end, due to the required processing time (see Figure \ref{fig:evolution} as example).
-The resulting parameters may sometimes present significant differences, even though the score is almost similar.
+The resulting parameters may sometimes present non negligible differences, even though the score is almost similar.
 Through some Monte-Carlo analyses of the parameter space properties of the AM, \citet{Horton2012a} showed that some parameters of the method have a wide range of acceptable values \citep[see also][]{Horton2016}.
@@
 This is particularly true for higher pressure levels and can be more critical for lower layers.
-It was thus interesting to sometimes get several sets of near-optimal parameters, but with some nuances, in order to have an idea of the sensitivity of the parameters for a given region, and to compare the score on the VP.
+It was thus interesting to sometimes get several sets of near-optimal parameters, but with some nuances, in order to get an idea of the sensitivity of the parameters for a given region, and to compare the score on the VP.
 In this regard, a cross-validation technique may be advisable.
@@
 
-The parameters resulting from the optimization by GAs are very consistent for the analogy of the atmospheric circulation, in terms of selection of the pressure levels, and the temporal and spatial windows.
+The parameters resulting from the optimization by GAs are very consistent in terms of selection of the pressure levels, and the temporal and spatial windows.
 There are clear trends or even identical results for subregions under similar meteorological influences, which confirm that the optimized parameters are coherent, despite an eventual first impression of a great variability in the spatial windows.
 When adding moisture variables, the results show a higher variability, but remains highly acceptable and coherent.
-Indeed, the selection of the pressure level for the moisture index is for example very constant.
 
@@
 
-A parametric dependence between the analogy of circulation and the moisture variables could be identified.
+A parametric dependence between the analogy of circulation and the moisture variables was identified.
 When the two levels are considered together, the optimal parameters of the circulation analogy are different.
@@
 
-GAs provide parametrizations of AMs that exceed the performance of the sequential calibration.
-In addition, it as been observed that the forecasts for days with strong precipitation were significantly more improved, which is clearly interesting in the framework of flood forecasting.
+GAs provide parameterizations of AMs that exceed the performance of the sequential calibration.
+In addition, it has been observed that the forecasts for days with strong precipitation were significantly more improved, which is clearly interesting in the framework of flood forecasting.
 
 This work is by far not exhaustive and means to open a door for new explorations of AMs with GAs.
-It becomes possible to even let the optimizer chose the meteorological variable to be used as predictor, as well as the analogy criteria.
+It is even possible to let the optimizer chose the meteorological variable to be used as predictor, as well as the analogy criteria.
 It is already possible to undertake such approach with our code.
@@
 \begin{figure}[htb]
+	\centerline{\includegraphics[width=8cm]{figures/table_crossing_z4_calib.pdf}}
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo, calibration period.}
+	\label{fig:crossing_4Zo_calib}
+\end{figure}
+
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=8cm]{figures/table_crossing_z4_valid.pdf}}
+	\caption{Same as Figure \ref{fig:crossing_4Zo_calib} but for the validation period.}
+	\label{fig:crossing_4Zo_valid}
+\end{figure}
+
+\begin{figure}[htb]
 	\centering
@@
 \begin{figure}[htb]
+	\centerline{\includegraphics[width=8cm]{figures/table_crossing_z4-hi2_calib.pdf}}
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo-2MIo, calibration period.}
+	\label{fig:crossing_4Zo-2MIo_calib}
+\end{figure}
+
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=8cm]{figures/table_crossing_z4-hi2_valid.pdf}}
+	\caption{Same as Figure \ref{fig:crossing_4Zo-2MIo_calib} but for the validation period.}
+	\label{fig:crossing_4Zo-2MIo_valid}
+\end{figure}
+
+\begin{figure}[htb]
 	\centerline{\includegraphics[width=\linewidth]{figures/figure_levels_weights.pdf}}

### 2015-11-25 Moving temporal window - HESS/template.tex
Addition of the template files for the moving temporal window article.

--- 2015-11-20 AtmoSwing - Geoscientific Model Development/template.tex
@@
 %% 2-Column Papers and Discussion Papers
-%\documentclass[gmd, manuscript]{copernicus}
-\documentclass[gmd]{copernicus}
+\documentclass[journal abbreviation, manuscript]{copernicus}
 
@@
 
+% Archives Animal Breeding (aab)
+% Atmospheric Chemistry and Physics (acp)
+% Advances in Geosciences (adgeo)
+% Advances in Statistical Climatology, Meteorology and Oceanography (ascmo)
+% Annales Geophysicae (angeo)
+% ASTRA Proceedings (ap)
+% Atmospheric Measurement Techniques (amt)
+% Advances in Radio Science (ars)
+% Advances in Science and Research (asr)
+% Biogeosciences (bg)
+% Climate of the Past (cp)
+% Drinking Water Engineering and Science (dwes)
+% Earth System Dynamics (esd)
+% Earth Surface Dynamics (esurf)
+% Earth System Science Data (essd)
+% Fossil Record (fr)
+% Geographica Helvetica (gh)
+% Geoscientific Instrumentation, Methods and Data Systems (gi)
 % Geoscientific Model Development (gmd)
+% Geothermal Energy Science (gtes)
 % Hydrology and Earth System Sciences (hess)
+% History of Geo- and Space Sciences (hgss)
+% Journal of Sensors and Sensor Systems (jsss)
+% Mechanical Sciences (ms)
+% Natural Hazards and Earth System Sciences (nhess)
+% Nonlinear Processes in Geophysics (npg)
+% Ocean Science (os)
+% Proceedings of the International Association of Hydrological Sciences (piahs)
+% Primate Biology (pb)
+% Scientific Drilling (sd)
+% SOIL (soil)
+% Solid Earth (se)
+% The Cryosphere (tc)
+% Web Ecology (we)
 
@@
 %\usepackage{algorithm}
+%\usepackage{amsthm}
 %\usepackage{float}
@@
 
-\title{AtmoSwing (v1.4): Analog Technique Model for Statistical weather forecastING}
+\title{TEXT}
 
@@
 
-\Author[1,2]{Pascal}{Horton}
-\Author[1]{Michel}{Jaboyedoff}
-\Author[3]{Charles}{Obled}
+\Author[]{}{}
+\Author[]{}{}
+\Author[]{}{}
 
-\affil[1]{University of Lausanne, Lausanne, Switzerland}
-\affil[2]{Terranum, Lausanne, Switzerland}
-\affil[3]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}
+\affil[]{ADDRESS}
+\affil[]{ADDRESS}
 
@@
 
-\runningtitle{AtmoSwing}
+\runningtitle{TEXT}
 
-\runningauthor{P. Horton et al.}
+\runningauthor{TEXT}
 
-\correspondence{Pascal Horton (pascal.horton@alumnil.unil.ch)}
+\correspondence{NAME (EMAIL)}
 
@@
 \begin{abstract}
-
-The analogue method allows forecasting local meteorological variables of interest (predictand), such as the daily precipitation, on the basis of synoptic variables (predictors).
-It relies on the fact that similar meteorological influences are likely to result in similar local effects.
-This statistical relationship is thus based on archives of observed data, and used in order to operationally forecast the coming days, or to evaluate future conditions under a changing climate.
-
-AtmoSwing is an open source software that implement the analogue method in a very flexible way, so that different variants can be handled dynamically, by parameterization trough XML files.
-It is made of 3 tools: the Forecaster to perform operational forecasts, the Viewer to display the results, and the Optimizer to establish the statistical relationship between the predictand and predictors.
-
-The Forecaster handles every required step internally, such as predictors downloading and parsing, grid interpolation, analogy sorting, without external scripts or file conversion.
-The processing of a forecast is extremely lightweight in terms of IT infrastructure; it can indeed run on almost any computer.
-
-The Viewer displays the forecasts in an interactive GIS environment.
-It contains several layers of syntheses and details in order to provide a quick overview of the potential critical situations in the coming days, as well as the possibility for the user to go into the details of the forecasted predictand and criteria distributions.
-Several tips coming from the literature are provided in order to help interpreting the forecasts.
-
-The Optimizer integrates the most used technique, that is a semi-automatic sequential approach, as well as Monte-Carlo analyses, and a global optimization technique by means of Genetic algorithms.
-It allows establishing the statistical relationship between predictors and predictands.
-
+TEXT
 \end{abstract}
@@
 \introduction  %% \introduction[modified heading if necessary]
+TEXT
 
-Reasoning by analogy is rather widespread in different domains of sciences or engineering.
-In hydrometeorology, it consists, given a certain situation, in looking into the past to retrieve situations that can be considered similar and therefore with consequences that may be expected similar to the situation at hand.
-By situation, we often think of the atmospheric situation over a rather wide domain, but it may also be the atmospheric profile at a radio-sounding station or the air-snow state at a given mountain observing station.
-By consequence, we often focus on one (or more) local variable of interest, such as the occurrence of hail, storm, avalanches, or the amount of wind or precipitation over a given region.
+\section{HEADING}
+TEXT
 
-As a general setting, the required ingredient are a couple of archives, one describing the situation through different variables, called predictors, and another one giving, for those situations, the value of the local variable of interest for engineering purpose, called predictand.
-Obviously, one understands that the longest and the richest the candidate archive of predictors, the more chance there will be to extract good analogues for a target situation in order to derive a conditional range of predictand values.
-As for the predictors, we can now hopefully rely on rich reanalysis products, commonly available over 40 years or more, and easily accessible.
+\subsection{HEADING}
+TEXT
 
-Usually, the predictand values could be derived in a rather physical-dynamic approach  by modeling the chain of processes linking the predictors to the predictand.
-However, the model may be extremely complex, time consuming, or some processes may be poorly known or parameterised.
-Conversely, the hope is that given the past archive of predictors, enough situations analogues to a target one could be found so that reasonable values will be found for the predictand, at a reasonable coding and computing-time costs.
-This is particularly true for a predictand much required in hydrometeorological applications, namely the precipitation amount over a given domain and time duration.
-The processes involved range from large scale dynamical states of the atmosphere down to very small scale microphysical processes, requiring models that are extremely complex, data-demanding, and time consuming.
-Therefore, with an appropriate set of archives, one may bypass all these modeling aspects by obtaining the predictand values observed from past analogue situations.
+\subsubsection{HEADING}
+TEXT
 
-The purpose of this paper is not to argue in favour or against this approach, which has proved to be used efficiently either in operational forecasting or more recently in climate studies, and which is capable of challenging more classical approaches based on meteorological modeling.
-In operational forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies, it is more and more used to downscale the results of global climate model simulation runs.
-In operational, it should however not to be considered as a substitution for numerical weather prediction models, but as a complement in order to get a fast and independent forecast that is known to be accurate several days in advance.
-It therefore enriches the analysis of a potential critical situation for flood forecasting, for example, and is very interesting in early warning.
+\conclusions  %% \conclusions[modified heading if necessary]
+TEXT
 
-However, how efficient and useful it may seem, this approach is not straightforward.
-Usually the type of predictand is imposed by some practical needs or constraints.
-Considering a precipitation variable, ones has to decide upon the duration of accumulation, (e.g.
-from 6-hourly to daily or several day totals) according for example to the size or response time of a the catchments to be managed.
-We must also consider the availability and quality of a long enough time series.
-Moreover, the analogy is restricted to a selection of variables at a specific time and over optimized spatial domains, that are compared by means of a chosen criteria that can rank the candidate days from the archive with a distance quantification.
-The approach appears predictand-specific but also dependent on the archive of predictors.
-Thus, the analogy is defined by many parameters (choice of the predictor variable, the temporal and spatial windows, and the number of analogues to consider) that are not straightforward to determine.
+\appendix
+\section{}    %% Appendix A
 
-We will first present the AM along with various implementations, as the optimal version of the method may vary with the location of interest, and as all these can be processed with AtmoSwing.
-The software will then be presented, and its modules detailed, such as the Forecaster and the Viewer that are tools for operational use, and the Optimizer that allows optimizing the method for a given predictand time series.
-
-\section{The analogue method}
-
-As AtmoSwing does not rely heavily on one variant of the analogue method (AM), but can implement different parametrization, we gathered here several references of possible implementations as well as the main evolution steps of the AM.
-This latter summarizes the improvements that were brought, as well as discontinued approaches that were found less relevant (such as the use of PCA on the predictors).
-
-\subsection{Principles}
-
-The AM is based on the principle that two similar synoptic situations may produce similar local effects \citep{Lorenz1956}.
-The perfect analogy does not exist, but sufficiently similar situations leading to similar effects can be identified.
-Thus, two states of the atmosphere that are alike are called analogues \citep{Lorenz1969}.
-To be relevant, this analogy must be selected by optimizing the following elements:
-
-\begin{itemize}
-	\item The analogy variable (the predictor) must contain synoptic information having indirect dependency with the local weather and the target variable (often the precipitation).
-	\item The spatial window is the domain on which the analogy variable is considered. The ideal size of this area is one that maximizes useful information.
-	\item The temporal window is the hour of day at which we consider the analogy variable. The analogy can be instantaneous (eg. 12~h~UTC) or averaged over a period (eg. 24~h).
-	\item The analogy period is the time of year in which similar situations are being sought. Thus, we compare situations with a similar distribution of solar energy \citep{Lorenz1969}.
-	\item The analogy criterion, needed to compare the variables on the chosen spatial and temporal windows, is a score used for ranking past situations according to their degree of similarity with the target situation \citep{Bontron2004}.
-	\item The ideal number of analogues situations is the best compromise in order to take into account local variability and to maximize useful synoptic information  \citep{Bontron2004}.
-\end{itemize}
-
-Because of the chaotic nature of the atmosphere, two analogue situations quickly diverge over time \citep{Lorenz1969}.
-Thus, the AM has strong limitations regarding the temporal extrapolation \citep{Bontron2004}.
-Numerical models being more capable of simulating the dynamic evolution of the atmosphere, the temporal extrapolation of the synoptic variables is left to them.
-The search for analogy aims thus at connecting the forecasted synoptic situation with a local predictand (temperature, precipitation ...), which is more difficult to simulate by numerical models.
-
-The AM is being used for many years at EDF (\'{E}lectricit\'{e} de France), to build precipitation and temperature scenarios \citep{Desaint2008a}.
-It is also operational at the Compagnie Nationale du Rh\^{o}ne (CNR, France) and some flood forecasting services (SPC) in France and Switzerland \citep{Marty2010,GarciaHernandez2009b,Horton2012}.
-
-\subsection{Data}
-\label{sec:data}
-
-The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series we want to forecast.
-
-Predictors are generally reanalysis datasets (as archive) and outputs of a global numerical weather prediction models for the target situation in operational forecasting.
-Reanalysis datasets, such as the NCEP/NCAR reanalysis I \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996}, the NCEP/DOE reanalysis II \citep{Kanamitsu2002}, ERA-40 \citep{Uppala2005} are often used and can be inputed in AtmoSwing.
-Other observed predictors can also be used, such as Sea Surface Temperature \citep[SST, ][]{Reynolds2007}.
-The predictors describing the target situation in operational forecasting can for example result from GFS \citep[Global Forecast System,][]{Kanamitsu1991,Kanamitsu1989}, which is operated by NCEP and NOAA.
-
-\citet{Bontron2004} determined that the length of the archive should be 30 years to forecast usual situations, and 40 years for intense events.
-He also highlighted the dependence between the optimal number of analogues and the archive size: the shorter the archive, the lower the number of analogues.
-By varying the resolution of the predictors grids, he concluded that the performance increase is not significant for the analogy of atmospheric circulation below a resolution of 5\textdegree.
-However, it seems more important for the second level of analogy on moisture, which are more local variables.
-\citet{BenDaoud2010} assessed the European reanalysis ERA-40 \citep{Uppala2005} with a resolution of 1.125\textdegree.
-He identified a slight performance improvement, but not substantial enough to really justify an archive change \citep{BenDaoud2008}.
-
-The predictand is the local meteorological variable of interest.
-It can be 6-houry data, or more often daily time series, but has to be consistent with the time step of the predictors (at least, not finer).
-The most used predictor is the daily precipitation, usually averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.
-These time series are frequently normalized by the precipitation value for a return period of 10~years \citep{Djerboua2001}.
-This normalization allows for an easier comparison between subregions subject to different precipitation regimes, and thus to better identify the most important contributions.
-Most users also apply a root square to this last ratio in order to reduce the weight of the extreme predictand values, but we generally don't.
-
-\subsection{Present structure}
-
-Although multiple variations of the AM exist, they generally share the same basics and the same structure.
-We want here to forecast the daily precipitation (the predictand) for a target day (at a defined lead time) and have long archives of both the predictand and predictor variables.
-The generic structure is the following:
-
-\begin{enumerate}
-	\item Preselection: to cope with seasonal effects, candidate dates are extracted from the archive within a period of four months centered around the target date, for every year of the archive.
-Alternatively, the candidate dates can be selected based on similar air temperature \citep{BenDaoud2010}.
-
-	\item First level of analogy: we subsample $N_{1}$ dates within all the candidates provided by the preselection, by means of an analogy ranking.
-The first level of analogy is always the atmospheric circulation when it comes to precipitation forecasting.
-We thus assess the similarity of the atmospheric circulation of our target date with all the situations provided by the preselection by means of the S1 criteria \citep[Eq.\ref{eq:S1}, ][see also section \ref{sec:method:evolution}]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
-
-	\begin{equation}
-	\label{eq:S1}
-	S1=100 \frac {\displaystyle \sum_{i} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
-	{\displaystyle \sum_{i} max\left\lbrace \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert \right\rbrace }
-	\end{equation}
-	where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points in the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
-The differences are processed separately in both directions.
-The smaller the S1 values are, the more similar the pressure fields.
-
-	The $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day. The number of analogues, $N_{1}$, is a parameter to calibrate.
-
-	\item Subsequent level(s) of analogy: we can then subsample once again the $N_{1}$ analogues on the basis of another variable in order to obtain a lower number of analogue dates, $N_{2}$.
-The S1 criterion is usually not relevant for other predictors that the atmospheric circulation.
-Other classic criteria represent absolute distances: Mean Absolute Error (MAE) and Root Mean Squared Error (RMSE), the latest being most often used.
-These are more relevant to compare moisture variables for example.
-
-	This process can be repeated, by subsampling a decreasing number of analogues, $N_{i}$, according to a ranking processed on various meteorological variables.
-
-	\item Probabilistic forecast: then, the daily observed precipitation amount (or another predictand of interest) of the $N_{i}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
-The empirical frequencies are processed for every value of the predictand, after classification, based on the Gringorten parameters (for a Gumbel or exponential law).
-
-\end{enumerate}
-
-\subsection{Proposed nomenclature}
-
-Variants of the AM parameterization are numerous and it is not always easy to reference them in a short and descriptive way.
-We thus propose a basic nomenclature (Figure \ref{figure:nomenclature}) in order to give an idea of the structure in a simple identifier.
-This one cannot describe all the parameters of the AM, but quickly illustrate the structure of the implementation.
-This is particularly useful when working with a global optimization method, where nothing is fixed but the very structure of the AM.
-
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/nomenclature.pdf}
-	\caption{Proposed structure for naming the parameterizations of the AM.}
-	\label{figure:nomenclature}
-\end{figure}
-
-The naming contains different blocs (separated by an hyphen) for the various levels of analogy.
-It starts with the specification of the preselection (P; can be omitted when comparing AMs with the same preselection approaches), which can be nowadays of 2 types:
-\begin{itemize}
-	\setlength\itemsep{-2px}
-	\item C: calendar period ($\pm 60$ days around the target date)
-	\item T: based on air temperature \citep{BenDaoud2010}
-\end{itemize}
-
-Then, the following levels of analogy are listed.
-They may start with an optional A (for analogy) when other methods are mixed into the parameterization \citep[see eg.
-][]{Chardon2014}.
-For every level of analogy, we first provide the number of variables used (combination of atmospheric levels and time of observation) and then give the short name of the variable (according eg to ECMWF conventions; in upper case), for example:
-\begin{itemize}
-	\setlength\itemsep{-2px}
-	\item Z : geopotential (circulation)
-	\item MI : moisture index (TPW * RH)
-	\item MF : moisture flux (V * TPW * RH)
-	\item TPW : total precipitable water
-	\item V : wind velocity
-	\item W : vertical velocity
-\end{itemize}
-
-In order to keep the identifier simple, no value of atmospheric level neither time of observation is specified.
-Moreover, the analogy criterion is not specified and is supposed to be S1 for Z and RMSE for the other variables.
-If anything changes from these conventions, it can be noted as a flag.
-The flag (lower case) can also give other information, such as the optimization method:
-\begin{itemize}
-	\setlength\itemsep{-2px}
-	\item sc : sequential calibration (can be omitted as considered as default, see section \ref{sec:atmoswing-calibration})
-	\item go (or just ''o'') : global optimization (by means of genetic algorithms for example)
-\end{itemize}
-
-This nomenclature can be adapted to specific needs, or simplified for a better readability (eg. by removing the specification of the preselection). Examples are provided in the following section.
-
-\subsection{Evolution of the method for precipitation forecasting}
-\label{sec:method:evolution}
-
-The evolution of the AM for precipitation forecasting led to several improvements.
-However, some of these are specific for a certain region and are not relevant for others, and some perform better depending on the lead time.
-Thereby, we cannot provide a single best parameterization for the AM, neither rank them from worst to best.
-We will thus provide some examples of parameterizations of the most recent AM variant, in the chronological order they appeared.
-The most common usage of the AM is for precipitation forecasting.
-Thus, the evolution presented hereafter focuses on this predictand.
-However, the AM, or an equivalent, was also used for short to medium term forecasting of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
-\citet{Guilbaud1997} performed a literature review about the use of the AM in long-term forecasting and identified operational applications for monthly forecasts in many countries, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal forecasts: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
-
-\citet{Lorenz1969} introduced the concept and established the basis of the AM.
-He considered looking for analogues on the geopotential field (at 200, 500 and 850~hPa) with a corrected Euclidean distance averaged on the 3 levels.
-In addition, the analogue situations were to belong to the same period of the year to be comparable in terms of distribution of solar energy.
-
-The use of the AM for operational forecasting of daily precipitation originates in the work of \citet{Duband1970, Duband1974, Duband1981}.
-It was then designed for operational forecasting at EDF (\'{E}lectricit\'{e} de France) in order to better manage water resources and flood risks.
-The geopotential height at 700~hPa and 00~h was used for its higher stability than the sea level pressure (SLP) field, and its sensitivity to the atmospheric disturbances \citep{Guilbaud1997}.
-However, the SLP at 06~h was also used for determining the intensity of precipitation, as well as the temperature at 700~hPa as indicator of the thermal state of the air mass \citep{Duband1974}.
-The data were then based on 37 radiosounding over Europe and condensed by a principal component analysis.
-The first 25 analogues on the geopotential at 700~hPa were considered, and multiple local regressions between precipitation, SLP, and the temperature at 700~hPa were established on these analogues before being applied to the target situation \citep{Guilbaud1997}.
-The archives were split by season to consider comparable situations in terms of distribution of solar energy \citep{Lorenz1969}.
-This initial rigid division into seasons was then transformed into a moving selection of more or less two months around the target date.
-The forecast was then performed only on the basis of observations and was temporally extrapolated to the following two days.
-After a few years, this statistical temporal extrapolation was abandoned in favor of a statistical adaptation using predictors resulting from an global numerical model, allowing a forecast over the following 4~days.
-
-Thereafter, the geopotential was considered at 1000~hPa and 700~hPa and the analogues selection was done in two stages: first according to an Euclidean distance in the space of the principal components of the geopotential field at 700~hPa, and then according to a correlation criterion (on the geopotential field at 700 and 1000~hPa, as well as on the thickness between these two levels) in order to remove days too dissimilar \citep{Guilbaud1997}.
-The regression approach to determining precipitation was eventually abandoned in favor of the probabilistic forecasting (synthesized by the percentiles 20, 60 and 90~\%), as it is performed today by interpolating linearly over the cumulative empirical distribution of daily precipitation measured at the analogue days \citep{Guilbaud1997, Guilbaud1998}.
-
-\citet{Wilson1980} sought the 20 best analogues on the geopotential field at 500 and 1000~hPa using the Teweles-Wobus (S1) criterion (Eq.
-\ref{eq:S1}), which allows for a comparison of the gradients and thus an analogy of the atmospheric circulation.
-\citet{Woodcock1980} used the same criterion on the SLP fields to select 50~analogues in order to forecast maximum daily temperatures.
-\citet{Yacowar1975} considered the 20 best analogues on the maximum of the sum of correlations on the two fields.
-This work has demonstrated the best performance of the AM compared to regression methods, as well as the interest to search for analogues on two (500 and 1000~hPa) geopotential fields combined \citep{Guilbaud1997}.
-
-\citet{Mandon1985} introduced a second level of analogy and assessed different variables, such as wind, moisture, air temperature, surface temperature of the Mediterranean, the product of wind and the 700~hPa moisture, as well as a second barometric criteria differentiated according to the season.
-\citet{Vallee1986} continued to work on the second level of analogy and considered the wind at 700~hPa \& 12~h in order to improve heavy precipitation events for a region in France susceptible to southerly flows.
-
-Taking advantage of higher-performance IT tools \citet{Guilbaud1997} stopped using PCA in order to work directly with the raw data interpolated on grids, which was an improvement, especially when considering the S1 criterion (already used for analogues selection by\citealp{Wilson1980} and \citealp{Woodcock1980}) instead of the Euclidean distance.
-This score gives importance to the similarity of atmospheric circulation rather than absolute values of the pressure field.
-After comparing this criterion to other criteria from the literature, or combinations of these, \citet{Guilbaud1998} found that S1 is the most efficient.
-They also pointed out the benefit of using 2 atmospheric levels, 1000~hPa (Z1000) and 700~hPa (Z700) or 500~hPa (Z500), instead of one (also instead of the thickness), and to also consider 2 temporal windows, 00~h and 24~h \citep{Obled2002}.
-The number of analogues considered is 50 (Table \ref{table:R0}).
-When using multiple predictors, they combined the criteria values calculated on each atmospheric level and each temporal window using an arithmetic mean.
-Finally, they also suggested using a second level of analogy on lower layers moisture and introduced the Ranked Probability Score \citep{Epstein1969} to assess the forecast quality, which was found to be more relevant that the Brier score \citep{Brier1950}.
-
-\begin{table}[htbp]
-	\caption{Method of type PC-4Z proposed by \citet{Guilbaud1997}.}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 00, 24~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
-		& Z700 $^{\dagger}$ & 00, 24~h & & \\ 
-		\bottomhline 
-	\end{tabular} 
-	\belowtable{$\dagger$ or Z500 as an alternative}
-	\label{table:R0}
-\end{table}
-
-\citet{Bontron2004} could benefit from the newly available NCEP/NCAR reanalysis data.
-This dataset being more homogeneous, much longer, and contained more variables than what was previously used, he could systematically assess a large selection of variables in the AM combined with different criteria.
-He thus confirmed the interest of the geopotential height along with the S1 criterion for the first level of analogy.
-He has also shown that the choice of the temporal window (time of observation) has a higher importance than the atmospheric level for the performance of the AM.
-By assessing multiple combinations of atmospheric levels and temporal windows, he concluded that the coupled geopotential heights at 1000~hPa (Z1000) \& 12~h and 500~hPa (Z500) \& 24~h provided the best performance for the studied region (Table \ref{table:R1}).
-The analogy on the atmospheric circulation proposed by \citet{Bontron2004} is still, at the time of writing, often used operationally, and considered as a reference for benchmarking new parameterizations \citep{Horton2012, BenDaoud2015}.
-
-\begin{table}[htbp]
-	\caption{Method of type PC-2Z proposed by \citet{Bontron2004}.}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline 
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
-		& Z500 & 24~h & & \\ 
-		\bottomhline 
-	\end{tabular} 
-	\label{table:R1}
-\end{table}
-
-\citep{Bontron2004} also assessed several variables for the second level of analogy and identified the moisture variables (precipitable water and relative humidity) and vertical velocity to be the most relevant.
-Finally, he found that a moisture index made of the product of relative humidity at 850~hPa (RH850) and total precipitable water (TPW) gave the best performance (Table \ref{table:R2}).
-This index does not represent an actual physical quantity, but expresses the water content of the column and its proximity to saturation.
-
-\begin{table}[htbp]
-	\caption{Method of type PC-2Z-2MI proposed by \citet{Bontron2004}.}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline 
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
-		& Z500 & 24~h & & \\ 
-		\middlehline
-		2 & TPW * RH850 & 12, 24~h & RMSE & 30 \\
-		\bottomhline 
-	\end{tabular} 
-	\label{table:R2}
-\end{table}
-
-He noted the relevance of defining different spatial windows for each region, rather than a single window to the entire territory.
-These windows are more able to represent the specific atmospheric influences for the region.
-In order to assess the forecast, he introduced the Continuous Ranked Probability Score \citep[CRPS, Eq.
-\ref{eq:CRPS}, ][]{Brown1974}, which discards the issue of determining classes as with the RPS previously in use.
-
-\citet{Gibergans-Baguena2007} implemented the AM for daily precipitation forecasts in Catalonia.
-They considered the geopotential at 700 and 1000~hPa, and the thickness between these two levels, to search for analogy of circulation, and then applied a second selection on local data from radiosonde: stability indexes, precipitable water, temperature, etc.
-
-\citet{Marty2010} tested other temporal windows for intraday application on the basis of a more comprehensive reanalysis dataset.
-He first proposed to change the hours of observation for both levels of analogy (both for 06~h and 18~h), and selected the 925~hPa level for the moisture analogy (Table \ref{table:R3a}).
-The selected hours and atmospheric levels were not available before.
-
-\begin{table}[htbp]
-	\caption{Method of type PC-2Z-2MI proposed by \citet{Marty2010}.}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline 
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{75} \\
-		& Z500 & 18~h & & \\ 
-		\middlehline
-		2 & TPW * RH925 & 06, 18~h & RMSE & 30 \\
-		\bottomhline 
-	\end{tabular} 
-	\label{table:R3a}
-\end{table}
-
-Then, \citet{Marty2010} changed the moisture index into the moisture flux by adding the wind velocity (V700 or V925) component in the multiplication.
-He considered this flux at 700~hPa or 925~hPa (Table \ref{table:R3b}).
-
-\begin{table}[htbp]
-	\caption{Method of type PC-2Z-2MF proposed by \citet{Marty2010}.}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline 
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{60} \\
-		& Z500 & 18~h & & \\ 
-		\middlehline
-		2 & V700 * TPW * RH700 $^{\dagger}$ & 06, 18~h & RMSE & 25 \\
-		\bottomhline 
-	\end{tabular} 
-	\belowtable{$\dagger$ or V925 * TPW * RH925 as an alternative}
-	\label{table:R3b}
-\end{table}
-
-\citet{BenDaoud2010} applied the AM in the context of large floodplains, out of an Alpine environment (Sa\^{o}ne, Seine).
-He evaluated several variables usually used in weather forecasting, amongst them the air temperature and the vertical velocity that presented a potential interest.
-The temperature (at the nearest grid point, on the 925~hPa (36~h) and 600~hPa (12~h) levels) could replace the rigid calendar preselection of $\pm$ 60 days around the target date by a more dynamic screening of similar situations in terms of air masses.
-The seasonal effect is indeed also present in the temperature data.
-The number of preselected dates is equivalent to the number of days we would have chosen with the calendar approach, and thus depends on the archive size: $N_{0} = 60 \cdot 2 \cdot n_{a}$ where $n_{a}$ is the number of years in the calibration period.
-\citet{BenDaoud2010} also reconsidered the parameters of the moisture index and ended up with both 925~hPa and 700~hPa levels, at 12~h and 24~h, or at every time step (6~h) between 06~h and 30~h (Table \ref{table:R4b}).
-
-\begin{table}[htbp]
-	\caption{Method of type P2T-2Z-4MI (or P2T-2Z-10MI for the alternative version), by \citet{BenDaoud2010}.}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline
-		\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
-		& T600 & 12~h & & \\ 
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
-		& Z500 & 24~h & & \\ 
-		\middlehline
-		\multirow{2}{*}{2} & TPW * RH925 & 12, 24~h $^{\dagger}$ & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
-		& TPW * RH700 & 12, 24~h $^{\dagger}$ & & \\ 
-		\bottomhline 
-	\end{tabular} 
-	\belowtable{$\dagger$ or 06-30~h as an alternative}
-	\label{table:R4b}
-\end{table}
-
-Subsequently, \citet{BenDaoud2010} added an additionally level of analogy, between the circulation and the moisture analogy (Table \ref{table:R5}), based on vertical velocity at 850~hPa (W850).
-This AM was developed for large plains in France, but was found to be not relevant for an Alpine environment where topography is mostly responsible for uplift of air masses \citep{Horton2012}.
-
-\begin{table}[htbp]
-	\caption{Method of type P2T-2Z-4W-4MI, by \citet{BenDaoud2010}.}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline
-		\multirow{2}{*}{0} & T925 (1 point) & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
-		& T600 (1 point) & 12~h & & \\ 
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{170} \\
-		& Z500 & 24~h & & \\ 
-		\middlehline
-		2 & W850 & 06-24~h & RMSE & 70 \\
-		\middlehline
-		\multirow{2}{*}{3} & TPW * RH925 & 12, 24~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
-		& TPW * RH700 & 12, 24~h & & \\
-		\bottomhline 
-	\end{tabular}
-	\label{table:R5}
-\end{table}
-
-\citet{Bliefernicht2010} proposed to add a weighting to the grid points of the predictor to overcome a comparison on a fixed-size window, and to give more importance to regions with relevant atmospheric circulation information.
-However, he noticed that there is a risk of overparametrization and a simplification of the weighting fields may be necessary, and that the performance was not stable between the calibration and the validation periods.
-He also compare the performance of the AM with a forecasting method based on a weather types approach, and concluded that the AM was more efficient.
-
-\citet{Horton2012} identified that the analogy on the atmospheric circulation may not be comprehensive, and that a significant gain was obtained by considering 4 atmospheric levels (1000, 850, 700, and 500~hPa at 12 or 24~h) instead of 2 (Table \ref{table:R6}).
-No number of analogues ($N_{1}$) was provided globally, as it was calibrated for every subregion.
-Considering a AM only based on the atmospheric circulation has an interest for operational forecasting, where moisture variables are less well forecasted over a lead time of a few days.
-An equivalent structure was also optimized by means of generic algorithms (PC-4Zgo), which is the topic of another paper.
-
-\begin{table}[htbp]
-	\caption{Method of type PC-4Z proposed by \citet{Horton2012}.}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline 
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{4}{*}{1} & Z1000 & 12~h & \multirow{4}{*}{S1} & \multirow{4}{*}{$N_{1}$} \\
-		& Z850 & 24~h & & \\ 
-		& Z700 & 12~h & & \\ 
-		& Z500 & 24~h & & \\ 
-		\bottomhline 
-	\end{tabular}
-	\label{table:R6}
-\end{table}
-
-\citet{Horton2012} also integrated an analogy on the moisture flux, after the circulation analogy on the 4 atmospheric levels (Table \ref{table:R7}).
-The number of analogues ($N_{1}$, $N_{2}$) were also calibrated for every subregion.
-Similarly, an equivalent structure was optimized (PC-4Zgo-2MIgo).
-
-\begin{table}[htbp]
-	\caption{Method of type PC-4Z-2MI, by \citet{Horton2012}.}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline 
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{4}{*}{1} & Z1000 & 12~h & \multirow{4}{*}{S1} & \multirow{4}{*}{$N_{1}$} \\
-		& Z850 & 24~h & & \\ 
-		& Z700 & 12~h & & \\ 
-		& Z500 & 24~h & & \\ 
-		\middlehline
-		2 & V700 * TPW * RH700 & 12, 24~h & RMSE & $N_{2}$ \\
-		\bottomhline 
-	\end{tabular}
-	\label{table:R7}
-\end{table}
-
-The optimal predictors vary from one region to another, along with the leading atmospheric processes.
-We will thus never get a unique parameterization of the AM valid for any place on earth, but the method needs to be adapted to the local conditions and to the size of the catchment of interest.
-Thus, there will always be local adaptations to be made for use in a new region.
-
-% TODO : Sabine
-% TODO : Jérémie Chardon
-
-\subsection{Discussion on the method}
-
-A version of the AM was evaluated during the project STARDEX \citep[\textit{STAtistical and Regional dynamical Downscaling of EXtremes for European regions}, see][]{Goodess2003, Stardex2005}.
-One of the project goals was to compare various downscaling methods for the determination of weather extremes, and the AM was selected among the most interesting from various techniques \citep{Maheras2005, Schmidli2007}.
-Its use as adaptation method of climate models is also the subject of a growing number of studies \citep{Zorita1999, Wetterhall2005, Wetterhall2007, Matulla2007, Chardon2014, Dayon2015}.
-
-\citet{Hamill2006} used an analogy based approach on the GFS reforecasts in order to correct systematic errors in the ensemble forecasts of temperature and precipitation.
-Indeed, the statistical approach showed some bias in estimates of the numerical model, which may have been adjusted by taking into account the intrinsic local climatology from the AM.
-Moreover, the under-dispersion of the ensemble forecast from the numerical model has been corrected using analogues \citep{Hamill2006}.
-Correction of ensemble forecast under-dispersion by means of the AM is also used operationally at EDF.
-
-\citet{Bliefernicht2010} observed that the performance of the AM is higher for winter than for summer.
-The relationship between synoptic predictors and local rainfall is lower in summer, due to convective precipitation that present a higher spatial variability and that depend on other parameters.
-Variables describing the synoptic circulation are indeed not able to predict the location of thunderstorm cells.
-This was also observed by \citet{BenDaoud2010}, who set up a specific model for the summer months (June 15 to September 15).
-
-One of the AM limitations is the need for a substantial archive of the predictand variable, for example measured precipitations.
-Without data on several decades, the AM is not applicable.
-Long predictor archives are also required, but this problem is usually solved with reanalysis data, which are not perfect in terms of homogeneity, but can be considered of sufficient quality.
-Moreover,  reanalysis data are available all around the world, which represent a great potential for the AM.
-Another issue, still about data, concerns the operational forecasting: predictors describing forecasted target situations and the ones from the archive are not fully homogeneous, as they usually don't result from the same model.
-It is therefore necessary to use robust predictors that depend from the numerical model characteristics at a minimum extent.
-
-Another limitation is the fact that extreme events may be under-represented in the considered sample of analogue dates.
-Indeed, in a limited weather archive, events with high return periods are not so numerous.
-Their number is certainly lower than the number of analogues we consider, which can introduce a bias in the forecast.
-There are however techniques to correct this bias \citep[see][]{Marty2010}.
-
-It is legitimate to raise the question of the relevance of an approach based on archives of past situations in a context of climate change.
-The first potential issue is a possible change in atmospheric circulation.
-\citep{Philipp2007} observed certain trends in the synoptic atmospheric circulation over Europe, but with moderate frequencies.
-Moreover, the basic laws governing the atmosphere behavior will not be transformed \citep{Hewitson1996}.
-The assumption is that a large part of local climate change will result from changes in intensity, frequency and persistence of synoptic variables, but with other characteristics substantially similar to the present situation \citep{Hewitson1996}.
-Thus, if the archive of weather situations is long enough, it is reasonable to assume that a large part of future situations is already represented, even those whose frequency will change under different climatic conditions \citep{Wetterhall2005}.
-In addition, climate change is relatively slow, and through continuous updating of the archive, the AM will incorporate new information progressively with no big discontinuity.
-
-\section{Software basics}
-
-AtmoSwing is made of 3 main modules (Figure \ref{figure:flowchart_modules_atmoswing}) that are standalone, but do share a common code basis: the Forecaster, to process the operational forecasting, the Viewer, to display the forecast in a GIS environment, and the Optimizer, to calibrate/optimize the statistical relationship defining the analogy for a given predictand time series.
-Separating the Forecaster and the Viewer allows to automate the forecast on a server and to quickly display the results locally.
-The code is written in object oriented C++ and relies on the wxWidgets \citep{Smart2006} library to provide a cross-platform native experience to users.
-The software can thus be compiled on MS Windows, Linux / Unix, Mac (OS X, iOS), both in 32-bit and 64-bit.
-
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/logo.pdf}
-	\caption{The AtmoSwing logo and its 3 modules: the Forecaster, the Viewer and the Optimizer.}
-	\label{figure:logo}
-\end{figure}
-
-The source code in under version control (with Mercurial), and is open source (on Bitbucket, www.atmoswing.org).
-Developments have been made with an approach of unit tests.
-A collection of 500+ tests are frequently evaluated and completed during development, in order to verify that code changes do not introduce regression.
-Every analogy criterion, prediction score, searching and sorting functions, data manipulation, and so on, is tested.
-The integration tests specific to the  AM rely on the results of another analogue sorting software developed in Grenoble.
-They result from a comparison work done with the help of R.
-Marty in order to ensure that the results of AtmoSwing are exactly equivalent to their model, given the same parameters and data.
-These tests are part of the checks carried out regularly, so that these results are always reproducible.
-
-\subsection{Modular approach}
-
-An AtmoSwing great strength is that it is designed to process analogy forecasting in a modular fashion.
-The structure of the AM (number of analogy levels, number of predictors) is built dynamically (Figure \ref{figure:flowchart_modules_atmoswing}), and nothing is fixed a priori.
-The software then performs successively as many analogy levels as the user specified, with all the predictors he wants.
-Each level of analogy processed results in an object containing target dates, analogue dates, values of the analogy criteria, and other data.
-This object can be saved in a NetCDF file and/or can be injected into a new analogy level.
-The whole structure of the AM is defined in an XML file generated by the user.
-Even the time step of the method (6 or 24~hours for example) is a dynamic parameter.
-
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/flowchart_modules_atmoswing.pdf}
-	\caption{Simplified organizational chart of the AM implementation in AtmoSwing.}
-	\label{figure:flowchart_modules_atmoswing}
-\end{figure}
-
-Each implementation of the AM (see section \ref{sec:method:evolution}) may enter this scheme, even if it consists of manipulated variables (e.g.
-moisture index).
-Various preprocessing functions are implemented, as the calculation of the moisture index or flux, multiplication operations or calculation of the gradients.
-The user can specify the preprocessing method and the predictors to use, dynamically, in the XML file.
-
-\subsection{Performance}
-
-Although processing an analogue forecast for a given target date is fast, when optimizing the AM, forecasts are processed over a long periods of several decades, which is time consuming.
-Thus, great effort has been made in order to reduce the processing time to a minimum.
-Waste of time were identified with profiling tools and cut down at different levels.
-The software also use the linear algebra library Eigen 3 \citep{Guennebaud2010} for calculations on vectors and matrices, which resulted in time saving.
-Obviously, multi-threading is also implemented.
-
-First, every identified redundancy has been removed.
-Then, when looking for a certain date or data, the search looks first in the proximity where it is likely to be found instead of exploring an entire array.
-Similar data are not loaded twice, but shared pointers are used.
-Many other improvements allowed saving time, for example the use of the quicksort method \citep{Hoare1962a} to sort the date vectors according to the values of analogy criteria.
-Different implementations were tested (many remain in the code as alternatives) in order to select the most efficient: for example, when storing analogue dates according to their criteria value, it is faster to insert them in a fixed-size array rather than storing them all and sorting the array subsequently.
-
-The major performance gains were obtained by:
-\vspace*{-2mm}
-\begin{itemize}
-	\setlength\itemsep{-2px}
-	\item reduction of the array sizes used in the calculations,
-	\item use of pointers (and therefore the decrease of data copies),
-	\item better search for dates in temporal vectors starting from the previous index,
-	\item better management of the analogue vectors,
-	\item preprocessed gradients on geopotential fields when using the S1 criteria,
-	\item and finally the implementation of parallel calculations (multi-threading).
-\end{itemize}
-
-\section{AtmoSwing Forecaster}
-
-The Forecaster module allows to process operational forecasts.
-This software processes a current or past forecasting, defined by an XML file.
-A list of parameterizations (defined by external XML files) is processed successively.
-The software can compiled with a GUI (), or without in order to be used on a headless server through a command line interface.
-Processing a forecast requires very low computing capabilities and can be done on a low-end computer.
-
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/atmoswing-forecaster.png}
-	\caption{Graphical user interface of the Forecaster module. A list of different parameterizations is being processed.}
-	\label{figure:atmoswing-forecaster-gui}
-\end{figure}
-
-The software first downloads the predictor describing the target situation, such as 1\textdegree\ GFS outputs \citep[Global Forecast System,][see section \ref{sec:data}]{Kanamitsu1991,Kanamitsu1989}.
-It then interpolates the gridded data to match the resolution of the archive (for example 2.5\textdegree\ in the case of the NCEP/NCAP reanalysis I).
-The analogues dates are next sought according to the provided parameterization, and the predictand data are associated with the corresponding dates.
-The results are finally saved in auto-describing NetCDF files.
-If required, a synthetic XML is generated for an easier integration on a web platform for example.
-Every step of the forecast, from the predictor downloading to the final results, is done in the software (and controlled through configuration), without use of external scripts (e.g.
-for data conversion).
-
-When using a parameterization of the AM, previously optimized in perfect prognosis \citep[optimization on the reanalysis dataset, without taking into account the uncertainty of operational forecasts,][]{Klein1963}, in operational forecasting, we should take into account the increasing uncertainty of the predictor with the lead time.
-An option, proposed by \citet{Thevenot2004}, is to increase the number of analogues with the lead time.
-These values should be optimized, for every lead time, by using reforecast data of the model considered for operational forecasting.
-
-The command-line interface allows to start the process for the most recent date, a selected past date, or the last $x$ days (as long as the predictors are available on the provider server).
-When there is nothing to process (no new predictor data available), the execution just stops, leading to no loss of computing resources.
-The recommended use is thus to set up a cron task on a Linux server in order to trigger the forecast every 30 minutes.
-When using GFS outputs, this would provide 4 forecasts a day with a reduced delay between GFS outputs availability and the analogue forecast.
-
-A user interface allows the creation of the precipitation database.
-Its generation consists in extracting the time series from text files in order to process them and save a database in the NetCDF format.
-During the process, Gumbel adjustments are automatically calculated in order to determine the values of different return periods.
-The time series are normalized by a selected return period (default 10~years) and their square root is eventually processed.
-The final database file contains both the raw and the normalized series, as well as characteristics of the gauging stations and some metadata.
-
-\section{AtmoSwing Viewer}
-
-\subsection{The graphical user interface }
-
-The Viewer module allows displaying the resulting forecast files in an interactive GIS environment (Figure \ref{figure:atmoswing-viewer-gui}).
-During the forecast, different parametrization variants of the same type of AM may be applied to a region; the reason being that some parameterizations may be specific for a subregion, when its meteorological influences differ, which is often the case even in relatively small catchments \citep{Horton2012}.
-The Viewer automatically gathers the similar AMs and provides a composite view of the optimal forecasts per subregion.
-The user can however choose to display a specific parameterization for the whole region, which is more consistent in terms of homogeneity of the analogue dates.
-
-\begin{figure*}[t]
-	\includegraphics[width=18cm]{figures/atmoswing-viewer.png}
-	\caption{Graphical user interface of the Viewer module (Elevation data from The Shuttle Radar Topography Mission (SRTM), and hydrological network from SwissTopo).}
-	\label{figure:atmoswing-viewer-gui}
-\end{figure*}
-
-The software provides several levels of synthesis of the forecasts.
-When it is opened, it automatically loads the most recent forecasts, eliminating the need to manually open files.
-It first offers a quick overview of possible alerts by means of color codes on the lead time switcher (upper right in the GUI, see Figure \ref{figure:atmoswing-viewer-gui}), which synthesizes the worst case scenario, or in the alarms panel (on the left part of the GUI).
-The alarms panel offers a synthesis of the higher forecasted values over the region, for the different AMs and the different lead times.
-By default, the colors are expressed relatively to 10-year return period values, for the $90^{th}$ percentile (can be changed in the preferences).
-This higher level of synthesis allows to quickly identify potential critical situations in the days ahead.
-
-Then, the user can explore the forecasts more in details, starting from the map provided by the GUI (Figure \ref{figure:atmoswing-viewer-gui}).
-The map display the forecast of the selected parameterization (upper left) and the selected lead time (upper right).
-The displayed AM is by default a composite of the parameterization variants for the region, but the user can choose a specific parameterization for the whole region by opening the tree view and selecting a child element.
-We also allowed a display of all lead times on a single map by means of a symbolic representation on a circular band with a box for every lead time (Figure \ref{figure:atmoswing-viewer-snail}).
-The number of boxes is dynamically adjusted to the number of lead times.
-This representation offers a global spatiotemporal display for a chosen parameterization.
-
-Color scales in the map are easily controlled by choosing the predictand ratio (raw value or ratio to different return periods) and the quantile of the distribution (on the left part of the GUI).
-Representation relatively to a return time better expresses the meaning of a certain precipitation amount for a given region, as climatology can be drastically different between two locations in a mountainous area, even if they are close to each other.
-All information relative to a rain gauge station (or stations groups), such as its location, its name, or the values of different return periods, are stored in the forecast files, in order to be displayable for end users who do not have the predictand database.
-
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/atmoswing-viewer-snail.png}
-	\caption{Visualization of multiple lead times on the map (Elevation data from the SRTM, and hydrological network from SwissTopo).}
-	\label{figure:atmoswing-viewer-snail}
-\end{figure}
-
-By clicking on a station (forecast points) on the map (or by selection in a dropdown list on the left), a new window appears with a plot of the forecasted time series (Figure \ref{figure:atmoswing-viewer-timeseries}).
-By default, the plot contains the usual 3 considered percentiles (90$^{th}$, 60$^{th}$, and 20$^{th}$), along with the 10 best analogues with a color code from yellow (10$^{th}$) to red (1$^{st}$).
-The 10 year return period is also displayed in order to put the forecast in perspective.
-The user can choose to hide any data or to display supplementary information (all analogues, all 10$^{th}$ percentiles, or all return periods) in the left panel.
-Traces of old forecasts are also automatically loaded and displayed in order to inform on the stability of the forecasts.
-
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/atmoswing-viewer-timeseries.png}
-	\caption{Visualization of the forecasted time series.}
-	\label{figure:atmoswing-viewer-timeseries}
-\end{figure}
-
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/atmoswing-viewer-distribution.png}
-	\caption{Visualization of the forecasted precipitation distribution for a given lead time.}
-	\label{figure:atmoswing-viewer-distribution}
-\end{figure}
-
-The user can even go into further details and display the predictand cumulative distribution for a given lead time (Figure \ref{figure:atmoswing-viewer-distribution}).
-This information is useful when working on extreme precipitation, as comparing the distribution of all analogues versus the 10 best analogues provides information in order to interpret the forecast (trend to under/overestimation).
-Distribution of the analogy criteria can also be displayed in order to identify eventual discontinuities in the criteria values.
-
-Finally, one can see the details of the analogue dates, along with the predictand and the criteria values in an interactive spreadsheet.
-
-AtmoSwing Viewer relies on workspaces to specify the path to the forecast directories and the GIS layers.
-Many GIS formats are supported thanks to the GDAL and VroomGIS libraries.
-One can have as many layers as desired, and can control their display properties.
-It is thus easy to switch from a forecast for a region to another by opening a workspace file (XML format).
-
-\subsection{Interpreting a precipitation forecast}
-
-\citet{Djerboua2001} applied the AM developed by \citet{Guilbaud1997} in operational forecasting as part of the MAP project \citep[\textit{Mesoscale Alpine Programme}, see][]{Binder1996} during the special observation period \citep{Bougeault2001}.
-He noted that the 60$^{th}$ percentile was better to forecast precipitation amounts for common situations, but for strong to extreme events, the 90$^{th}$ percentile turned out to be a better indicator.
-It is therefore necessary to pay particular attention to the 90$^{th}$ percentile which, when reaching high values, may be indicative of a situation related to extreme precipitations, due the presence of several analogue dates with significant observed precipitations amounts in the distribution \citep{Djerboua2001}.
-\citet{Bontron2004} made the same observation: he found the 60$^{th}$ percentile to be best for occurrence forecasting, but the 90$^{th}$ percentile to be the most informative in order to forecast medium to high precipitation amounts ($P > P10/10$, one tenth of the 10-year return period value).
-In this regard, operators should pay particular attention to the distribution of the best analogues.
-If, for example, it is shifted to higher values, there is a risk of under-estimating the event when considering the middle of the full distribution.
-
-\citet{Marty2010} applied several validation scores to the quantiles of the AM distribution in operational forecasting.
-He concluded that the detection of the precipitation occurrence was better predicted by median quantiles (50-70~\%), with an optimum to 60~\%.
-However, for significant rainfall, the 90$^{th}$ percentile gave the best performance.
-Comparing the results from the AM to an ensemble forecast, \citet{Marty2010} found the AM to be better than the considered ensembles, particularly for strong precipitation.
-The gain of the AM comes from a greater accuracy for a poorer sharpness, when the ensemble forecasts are very sharp, but lack a bit of accuracy.
-
-When comparing the performance of Meteo France numerical models along with the AM, \citet{Djerboua2001} concluded that the numerical models are better at predicting the current day, but the AM becomes more competitive for the following lead times.
-It is indeed very interesting in early warning approaches, as it is able to identify a potentially critical situation one week ahead.
-
-All AMs rely on atmospheric circulation information, while some add subsequent levels of analogy on moisture or other thermodynamic predictors (see section \ref{sec:method:evolution}).
-However, these subsequent predictors were found to be relevant only on the first 3~days, and not much further, due to higher uncertainties in their forecast.
-This was found to be the case of moisture indexes and vertical velocity.
-The user has to keep this aspect in mind when interpreting forecasts over a range of lead times.
-
-\section{AtmoSwing Optimizer}
-
-AtmoSwing Optimizer is a single tool that integrates different optimization methods, presented in section \ref{sec:atmoswing-calibration} to \ref{sec:atmoswing-optimization}.
-
-\subsection{Calibration framework}
-
-The calibration of the AM is usually carried out in a perfect prognosis \citep{Klein1959} framework \citep{BenDaoud2010, Bontron2004}.
-Perfect prognosis uses observed or reanalyzed data to calibrate the relationship between predictors and predictands.
-Then, when used in operational forecasting, this relationship is applied to global model forecasts, that contains larger uncertainties.
-This framework allow us to identify relationships that are as close as possible to the natural links between predictors and predictands, by reducing uncertainties related to numerical forecasting models.
-However, no model is perfect, and even reanalysis data contain a bias that cannot be ignored.
-For this reason, the statistical relationships identified in the perfect prognosis framework should be applied to model outputs that are as similar as possible to the model used to elaborate the reanalysis.
-
-Another reason for working in a perfect prognosis framework is that numerical models evolve continuously, and so does the forecast they provide.
-Considering re-forecasts would allow us to work on a homogeneous dataset, as they are regularly reprocessed with a defined version of the model.
-However, we would need to redo the calibration procedure every time a new version is available, in order to reduce the bias \citep{Wilson2002}.
-Moreover, the length of reanalyses datasets are usually much longer than reforecast datasets, which allows us to identify more robust relationships.
-The size of the archive is indeed an important criteria for the AM.
-
-The statistical relationship is established on a calibration period that is as long as possible.
-For every day of this period, a search for analogues is processed, the precipitation data are associated with the corresponding dates and a forecast score is calculated.
-During the search for analogues situations, 120 days around the target date are excluded (thus excluding data in the same year) in order to consider only truly independent candidates days.
-
-A validation period is always considered.
-It consists of an independent period that is never used as target neither candidate date.
-Validating the parameters of the AM is very important in order to avoid over-parametrization and thus to ensure that the statistical relationship is valid on another period.
-In order to account for climate change and the evolution of the measuring techniques, it is recommended to use a noncontinuous period for validating, distributed over the whole archive \citep{BenDaoud2010}.
-The user can thus specify a list of the years to keep for the validation and AtmoSwing Optimizer handles this aspect easily by both removing the validation years from possible candidate situations, and by automatically processing the validation score at the end of the optimization.
-
-\subsection{Implemented forecasts scores}
-
-Most often, the accuracy of the parameters for precipitations forecasting is evaluated by means of the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
-It is the only score we detail here (in section \ref{sec:prob_forecasts}).
-In addition, other scores are implemented in AtmoSwing Optimizer.
-The following sections list the scores presently available, but will not detail them.
-
-\subsubsection{Discrete deterministic forecasts}
-
-Deterministic forecasts consider no uncertainty.
-A single value is provided for a variable.
-The first group of this type of forecast is based on discrete values, also called categories.
-These scores are used, for example, to evaluate a deterministic prediction of threshold exceedance.
-In our case, the continuous probabilistic nature of an analogy forecast can be transformed into a discrete forecast by considering a threshold exceedance and a fixed percentile from the distribution.
-These scores rely on a contingency table, which is here a table containing the sums of observed / unobserved and predicted / unpredicted events \citep{Wilks2006}.
-On the basis of this table, multiple scores can be processed within AtmoSwing:
-
-\begin{itemize}
-	\setlength\itemsep{-1mm}
-	\item Proportion correct \citep{Finley1884}
-	\item Threat Score \citep{Gilbert1884}
-	\item Bias
-	\item False Alarm Ratio
-	\item Hit Rate or Probabiliy of Detection
-	\item False Alarm Rate
-	\item Heidke Skill Score \citep{Heidke1926}
-	\item Peirce Skill Score \citep{Peirce1884}
-	\item Gilbert Skill Score or Equitable Threat Score \citep{Gilbert1884}
-\end{itemize}
-
-\subsubsection{Continuous deterministic forecasts}
-
-The difference of the continuous deterministic forecasts compared to discrete ones is that they provide non-discrete values that must be evaluated with distance measures.
-In our application, the distribution of the analogues is summarized by a chosen percentile.
-Available scores are the following:
-
-\begin{itemize}
-	\setlength\itemsep{-1mm}
-	\item Mean Absolute Error
-	\item Root Mean Squared Error
-\end{itemize}
-
-\subsubsection{Discrete probabilistic forecasts}
-
-In the case of discrete probabilistic forecasts, we work with probabilities of occurrence or probability of belonging to a certain category. The implemented options are:
-
-\begin{itemize}
-	\setlength\itemsep{-1mm}
-	\item Brier Score \citep{Brier1950}
-	\item ROC diagramm \citep[Relative Operating Characteristic or Receiver Operating Characteristic,][]{Mason1982}
-	\item RPS \citep[Ranked Probability Score,][]{Epstein1969}
-	\item SEEPS \citep[Stable Equitable Error in Probability Space,][]{Rodwell2010,Rodwell2011}
-\end{itemize}
-
-\subsubsection{Continuous probabilistic forecasts}
-\label{sec:prob_forecasts}
-
-Continuous probabilistic forecasts of a variable are issued in the form of the expected statistical distribution for this variable.
-They are expressed either in terms of distribution or by probability density, which need to compared an observed value.
-This is the situation we meet when forecasting precipitations with the AM.
-
-We mainly rely on the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
-It allows assessing the predicted cumulative distribution functions $F(y)$, for example of the precipitation values from analogue situations, compared to the observed value $y^{0}$.
-The better the forecast, the smaller the score.
-The mean CRPS of a forecast series of length $n$ can be written:
-
-\begin{equation}
-\label{eq:CRPS}
-CRPS = \frac{1}{n} \sum_{i=1}^{n} \left(  \int_{-\infty}^{+\infty} \left[ F_{i}(y)-H_{i}(y-y_{i}^{0})\right]^{2} dy \right) 
-\end{equation}
-where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value 1 otherwise.
-The mean CRPS is averaged on the calibration, respectively the validation periods, on all days, may they be dry, slightly rainy or with heavy precipitation.
-
-This score is now commonly used for the evaluation of continuous variables prediction systems \citep{Casati2008, Marty2010}.
-To compare the value of the score in regard to a reference, we often consider its skill score value, and use the climatological distribution as the reference.
-The CRPSS (\textit{Continuous Ranked Probability Skill Score}) is thus defined as following:
-
-\begin{equation}
-\label{eq:CRPSS}
-CRPSS = \dfrac{CRPS-CRPS_{r}}{CRPS_{p}-CRPS_{r}} = 1-\dfrac{CRPS}{CRPS_{r}}
-\end{equation}
-where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect forecast (which implies $CRPS_{p}~=~0$).
-
-The CRPS can be decomposed into several indicators, also implemented into AtmoSwing Optimizer, such as:
-
-\begin{itemize}
-	\setlength\itemsep{-1mm}
-	\item Reliability \citep{Hersbach2000}
-	\item Resolution / uncertainty \citep{Hersbach2000}
-	\item Sharpness \citep{Bontron2004}
-	\item Accuracy \citep{Bontron2004}
-\end{itemize}
-
-Finally, the rank diagram \citep{Talagrand1997} and its accuracy as defined by \citet{Candille2005} are also available.
-
-\subsection{The sequential calibration}
-\label{sec:atmoswing-calibration}
-
-The calibration procedure that we call ''sequential'' or ''classic'', but which is also named ''optimization'' \cite[eg.
-by ][]{BenDaoud2015}, was developed by \citet{Bontron2004} at the LTHE laboratory (INPG, Grenoble).
-It is a semi-automatic procedure that determines the optimal parameters for the different variables of each level of analogy.
-The analogy levels (eg.
-the atmospheric circulation or moisture index) are calibrated sequentially.
-The procedure consists of the following steps \citep{Bontron2004}:
-
-\begin{enumerate}
-	\item Manual selection of the following parameters:
-	\begin{enumerate}
-		\item meteorological variable,
-		\item pressure level,
-		\item temporal window (hour of observation),
-		\item initial analogue numbers.
-	\end{enumerate}
-
-	\item For every level of analogy:
-	\begin{enumerate}
-		\item Identification of the most skilled unitary cell (1~point for moisture variables and 4 for the geopotential height when using the S1 criteria) over a large domain.
-Every point (or cell) of the full domain is assessed jointly on all predictors of the level of analogy (consisting generally of the same variable, but on different pressure levels and at different hours).
-		\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain.
-The detailed stages are the followings: (i) The unitary spatial window is expanded in every 4 directions successively.
-The performance score is processed for these 4 windows.
-(ii) Only the direction providing the best improvement is applied to our spatial window.
-(iii) From this new spatial window, an increase in every 4 directions is once again assessed, and the best improvement is applied.
-(iv) The spatial window grows up by repeating the previous steps, until no improvement is reached.
-		\item The number of analogue situations is optimized for the current level of analogy.
-		\item A new level of analogy can be added, based on other variables (such as the moisture index) on predefined pressure levels and time frames.
-The number of analogues for the next level of analogy is initiated at a chosen value.
-Then, the procedure starts again from step (a) for the new level.
-The parameters calibrated on the previous analogue levels are fixed and do not change (except the number of analogues, at the final stage).
-	\end{enumerate}
-	\item Finally, the numbers of analogues are re-assessed for the different levels of analogy. This is done iteratively by varying the number of analogues of each level in a systematic way.
-\end{enumerate}
-
-The calibration is thus done in successive steps, on a limited number of parameters.
-Previously calibrated parameters are generally not reassessed.
-The advantage of this method is that it is fast, it provides acceptable results, and it has low computing requirements.
-
-We added small improvements to this method, and named it ''classic+'', by allowing the spatial windows to do other moves, such as: (1) increase in 2 simultaneous directions, (2) decrease in 1 or 2 simultaneous directions, (3) expansion or contraction (in every direction), (4) shift of the window (without resizing) in 8 directions (including diagonals), and finally (5) all the moves described above, but with a factor of 2, 3, or more.
-For example, we try to increase by 2 units in one (or more) direction.
-This allows to skip one size that may not be optimal.
-These supplementary steps often result in spatial windows that are a bit different, but the performance gain is rather marginal.
-
-\subsection{Monte-Carlo analysis}
-
-A Monte-Carlo analysis is also implemented in AtmoSwing.
-It performs thousands assessments of random parameters within given ranges.
-This method is not efficient to find the best parameters set, but helps to better understand the sensitivity of the parameters.
-
-For example, a Monte-Carlo analysis was performed on the PC-2Z (Table \ref{table:R1}) AM for the southeastern crests on the upper Rh\^{o}ne catchment in Switzerland, with 10,000 random selections of its parameters according to a uniform law (the analysis was also performed in other subregions of the upper Rh\^{o}ne catchment in Switzerland, but the conclusions depicted here are similar).
-Unlike conventional calibration, the spatial windows on Z500 and Z1000 were not necessarily overlapping.
-Thus, 9 parameters were varying together (8 for the spatial windows and 1 for the number of analogues)
-
-Figure \ref{figure:monte_carlo_r1} presents the resulting scatter of random exploration of the parameters space, along with the results of the sequential calibration (red cross).
-Results are illustrated here for the 4 parameters defining the spatial window on Z500.
-Despite the high number of simulations, the upper portion of the distributions seems incomplete, and the score of the sequential calibration is not matched.
-Although the method is poor to find efficiently the best parameters, it is informative as to the shape of the scatter plots.
-
-The shape of the scatter plots from Figure \ref{figure:monte_carlo_r1} reveals a low sensitivity as to the exact location of the spatial windows.
-There is a maximum threshold for minimum longitudes and latitudes and, conversely, a minimum threshold for maximum latitudes and longitudes, but outside of these limits, the distribution slope is more gentle.
-A spatial window can thus be a bit larger than its optimal size without a significant drop in performance, as long as it includes at least one critical region.
-This was also observed by \citet{Bontron2004}, who noted that ''\textit{performance slowly decrease if we consider a slightly too large window, while the use of too small windows results in strong performance loss}''.
-The dilution of a part of the relevant synoptic information has therefore not necessarily a significant negative impact on performance, while ignoring some of this information leads to undesirable loss of performance.
-It is the same for the analogues number (not shown), for which, past an optimum, the upper slope of the distribution decreases slowly.
-
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/monte_carlo_r1.png}
-	\caption{Example of a Monte Carlo analysis on the PC-2Z (Table \ref{table:R1}) AM.
-Results are illustrated for the 4 parameters defining the spatial window on Z500, along with the results of the sequential calibration (red cross).}
-	\label{figure:monte_carlo_r1}
-\end{figure}
-
-The same analysis has been conducted on the AM with 2 levels of analogy, PC-2Z-2MI (Table \ref{table:R2}), and the results on the number of analogues on the 1st and the 2nd level are illustrated in Figure \ref{figure:monte_carlo_r2}.
-One can see that the AM is not very sensitive to the number of analogues on the first level of analogy, when considering a second level afterwards, as long as this number is not too small.
-The trend on the second level is more apparent, but a large tolerance seems possible.
-
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/monte_carlo_r2.png}
-	\caption{Example of a Monte Carlo analysis on the PC-2Z-2MI (Table \ref{table:R2}) AM.
-Results are illustrated for the number of analogues on the 1st and 2nd level of analogy, along with the results of the sequential calibration (red cross).}
-	\label{figure:monte_carlo_r2}
-\end{figure}
-
-The use of such a random method allows informing on the parameters sensitivity, and so on the importance of the expected precision of the calibration results.
-It helps understanding how different parameterizations can end up to relatively similar performances.
-Using Mote Carlo analyses allows to easily display the parameters sensitivity while allowing a high degree of freedom to the AM.
-
-\subsection{Global optimization}
-\label{sec:atmoswing-optimization}
-
-Due to limitations of the sequential approach, we decided to explore optimization techniques that can handle all parameters fully automatically.
-We first assessed the \citet{Nelder1965a} method, which was found to be unsuitable for this purpose.
-Because of the complexity of the AM and its non-linearity, a technique of global optimization is required.
-We thus implemented Genetic algorithms in AtmoSwing Optimizer in order to perform a global optimization of the AM.
-This allows for a fully automatic and objective optimization of the AM.
-However, as this topic is rather consequent and the code base is not yet released, it will be the subject of other publications \cite[see][]{Horton2016a, Horton2016b}.
-
-\conclusions[Conclusions and perspectives]
-
-Processing operational forecasts by means of AtmoSwing requests very low computing infrastructure and can provide useful information, such as early warning for extreme precipitation, in the case of an application in flood forecasting.
-The Forecaster is very flexible as it builds the desired method in a dynamic way, and can thus implement multiple variants of the AM.
-The Viewer offers a user-friendly display of the forecast, with different levels of synthesis and details.
-The Optimizer implements different optimization techniques, such as the sequential approach, a Monte-Carlo method, and a global optimization technique.
-
-Several additions would be nice to have in AtmoSwing for operational forecasting.
-The first one would be using outputs from multiple global NWP models within one forecast, namely making multi-models forecasts, in order to take into account the variability between various providers.
-In the same direction, \citet{Thevenot2004} showed the benefit of using ensembles of global NWP forecasts as input for the method.
-This approach takes into account the uncertainties on predictors from the global model.
-Its implementation is a combination of the selected analogue days associated with each of the traces.
-Rainfall distribution is then established on all analogues.
-The forecast on the ensemble was found to be more accurate than the deterministic control for a lead time of 4 days and more \citep{Thevenot2004}.
-
-Next, a bias correction should be implemented.
-\citet{Marty2010} has indeed observed that the frequency of the forecasted days without precipitation was biased and underestimated the actual frequency of zero precipitation.
-On the contrary, the frequency of the forecasted days with precipitation overestimated the observed frequencies.
-On this basis, \citet{Marty2010} proposed a bias correction technique, that should be implemented as well.
-This issue occurs in operational forecasting and was not observed in perfect prognosis.
-
-The analogue method evolves, but there are still many possibilities to be assessed. Amongst them, we can mention:
-
-\begin{itemize}
-	\item an optimization per season in order to get parameterizations specific to the leading processes during the period in question;
-	\item optimizations specific for extreme events, with an objective function tailored to the determination of the most critical situations;
-	\item a weighting of the predictor grids, in order to get free of fixed rectangular spatial windows;
-	\item assessment of potential indicators based on the properties of the distribution of all analogues or the 10 best, for example;
-	\item assessment of the relevance of an automatic interpretation of the distribution in order to provide the most likely expected value;
-\end{itemize}
-
-%\appendix
-%\section{}    %% Appendix A
-
-%\subsection{}     %% Appendix A1, A2, etc.
-
-\section*{Code availability}
-
-AtmoSwing is open source, under the CDDL license. It is developed under the Mercurial distributed revision control, and the source code can be found at:
-
-\begin{itemize}
-	\item http://www.atmoswing.org
-	\item https://bitbucket.org/atmoswing/atmoswing
-\end{itemize}
-
-To get access to the frozen version at the time of writing (v1.4.2), the following address can be used:
-
-\begin{itemize}
-	\item bitbucket.org/atmoswing/atmoswing/commits/tag/1.4.2
-\end{itemize}
+\subsection{}                               %% Appendix A1, A2, etc.
 
 \begin{acknowledgements}
-Thanks to Lucien Schreiber and Richard Metzger for their programming advices.
-Thanks to Renaud Marty for his active involvement in testing AtmoSwing against his code base.
-Thanks to Dominique B\'{e}rod for his support.
-
-Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
-The fruitful collaboration with the Laboratoire d?Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
-NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.
+TEXT
 \end{acknowledgements}
@@
 
-%\begin{thebibliography}{}
-%
-%\bibitem[AUTHOR(YEAR)]{LABEL}
-% Reference 1
-%
-%\bibitem[AUTHOR(YEAR)]{LABEL}
-% Reference 2
-%
-%\end{thebibliography}
+\begin{thebibliography}{}
 
-\bibliographystyle{copernicus}
-\bibliography{../_refs/_articles-atmoswing}
+\bibitem[AUTHOR(YEAR)]{LABEL}
+REFERENCE 1
+
+\bibitem[AUTHOR(YEAR)]{LABEL}
+REFERENCE 2
+
+\end{thebibliography}
 

### 2015-11-25 Moving temporal window - HESS/template.tex
Basic template data.

@@
 %% 2-Column Papers and Discussion Papers
-\documentclass[journal abbreviation, manuscript]{copernicus}
+%\documentclass[hess, manuscript]{copernicus}
+\documentclass[hess]{copernicus}
 
@@
 
-\title{TEXT}
+\title{Introducing a Moving Temporal Window in the Analogue Method for Precipitation Forecasting}
 
@@
 
-\Author[]{}{}
-\Author[]{}{}
-\Author[]{}{}
+\Author[1,2]{Pascal}{Horton}
+\Author[3]{Charles}{Obled}
+\Author[1]{Michel}{Jaboyedoff}
 
-\affil[]{ADDRESS}
-\affil[]{ADDRESS}
+\affil[1]{University of Lausanne, Lausanne, Switzerland}
+\affil[2]{Terranum, Lausanne, Switzerland}
+\affil[3]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}
 
@@
 
-\runningtitle{TEXT}
+\runningtitle{Moving Temporal Window in the AM}
 
-\runningauthor{TEXT}
+\runningauthor{P. Horton et al.}
 
-\correspondence{NAME (EMAIL)}
+\correspondence{Pascal Horton (pascal.horton@alumnil.unil.ch)}
 
@@
 \begin{acknowledgements}
-TEXT
+Thanks to Dominique B\'{e}rod for his support and to Renaud Marty for his fruitful collaboration over the years.
+Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
+The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
+NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.
+Precipitation time series provided by MeteoSwiss.
 \end{acknowledgements}
@@
 
-\begin{thebibliography}{}
-
-\bibitem[AUTHOR(YEAR)]{LABEL}
-REFERENCE 1
-
-\bibitem[AUTHOR(YEAR)]{LABEL}
-REFERENCE 2
-
-\end{thebibliography}
+\bibliographystyle{copernicus}
+\bibliography{../_refs/_articles-movingwindow}
 

### 2015-11-25 Moving temporal window - HESS/template.tex
Very rough addition of all the moving window content in french.

@@
 
+\usepackage[utf8]{inputenc}
+
 \begin{document}
@@
 
-\section{HEADING}
-TEXT
+La méthode des analogues est habituellement implémentée avec un pas de temps journalier, la disponibilité de longues archives de données pluviométriques journalières n'ayant pas d'équivalent à une résolution plus fine.
+Ce pas de temps nous contraint à chercher des situations analogues aux mêmes heures fixes de la journée, sans quoi nous ne saurions pas quelles valeurs de précipitations leur attribuer.
+Nous pouvons néanmoins nous attendre à ce que l'analogie des situations météorologiques n'ait pas lieu systématiquement à la même heure de la journée, et que de meilleures candidates soient trouvées en autorisant un certain décalage.
 
-\subsection{HEADING}
-TEXT
+\begin{figure*}[htb]
+	\begin{center}
+		\includegraphics[width=14cm]{figures/Illustration_fenetre_glissante.pdf}
+	\end{center}
+	\caption[Illustration du principe de la fenêtre temporelle glissante.]{Illustration du principe de la fenêtre temporelle glissante. }
+	\label{fig:Illustration_fenetre_glissante}
+\end{figure*}
 
-\subsubsection{HEADING}
-TEXT
+De premiers essais \citep{Finet2008} avaient porté sur la seule recherche de situations synoptiques analogues à une situation cible.
+Ils avaient montré que pour une situation cible 0-24~h~UTC, on pouvait obtenir de meilleures analogies synoptiques en acceptant des situations  ''glissées'' 6-30~h, 12-36~h ou 18-42~h plutôt que de se limiter à 0-24~h.
+Mais il n'avait pas été possible de constituer les archives pluviométriques correspondantes, c'est-à-dire qui soient décalées, elles-aussi, dans le but de quantifier d'éventuelles améliorations de la prévision de précipitations.
+
+Afin d'évaluer ce gain potentiel, nous avons donc d'abord traité les mesures des stations automatiques de résolution 10~minutes (voir section \ref{sec:donnees:reseau}) ayant une durée respectable (1982-2007), pour élaborer des séries de précipitations représentant des cumuls de 24~h, mais sur une fenêtre temporelle glissante.
+Cela veut dire que nous constituons une série de 24~h centrée sur chaque tranche de 6~h de la journée, ce dernier pas de temps étant la résolution des prédicteurs synoptiques (voir section \ref{sec:donnees:reanalyses1_ncep}).
+
+Une telle série présente certains avantages.
+Le premier étant que la compétence résultant de ce modèle sera comparable à celle établie précédemment, et que le gain d'une telle modification peut donc être directement évalué.
+Le second s'inscrit dans la perspective de création de ce genre de séries à partir de données journalières désagrégées (en 6~h) puis recomposées (en 24~h glissées), où les erreurs seront alors réduites par rapport à une série à pas de temps de 6~h.
+
+Nous ne disposons pas de séries temporelles sur des bassins à ces pas de temps infrajournalier, ni de stations automatiques suffisamment proches pour être regroupées.
+Nous travaillons donc sur les séries issues de 6 stations automatiques, à savoir Ulrichen, Zermatt, Visp, Montana, Sion et Aigle.
+La station du col du Grand-Saint-Bernard n'est pas intégrée à l'étude en raison de forts doutes émis par Jean-Michel Fallot (Université de Lausanne) sur l'homogénéité de ces données.
+
+Les situations cibles et leurs valeurs de précipitations observées (utilisées pour la validation) ne changent pas, puisque nous effectuons toujours la prévision pour une période fixe de la journée cible (6-30~h), comme précédemment.
+Ce sont les situations candidates qui, elles, deviennent 4~fois plus nombreuses (Figure \ref{fig:Illustration_fenetre_glissante}).
+
+La logique voudrait a priori que nous ne retenions qu'une tranche horaire, la meilleure, par date candidate.
+C'est-à-dire, si pour la date cible du 15 novembre 2006 (0-24~h), la meilleure analogue est le 5 décembre 1988 (12-36~h), alors, très certainement les périodes les plus proches (5 décembre 6-30~h et 18-42~h) sont aussi des analogues, certes inférieures en qualité, mais acceptables.
+La question se pose alors de les prendre ou de les rejeter.
+Une exclusion des mêmes dates a été testée de deux manières différentes:
+\begin{itemize}
+	\item par exclusion des moins bonnes analogues dans une période de $\pm$ 24~h;
+	\item par exclusion des moins bonnes analogues avec la même date.
+\end{itemize}
+Après plusieurs essais, il s'est avéré que n'imposer aucune restriction menait à de meilleures compétences, et ceci de manière significative et récurrente.
+Dans la suite de cette analyse, aucune de ces contraintes ne sera donc imposée.
+
+\section{Conséquences de la réduction de l'archive sur la compétence}
+
+La première étape consiste à évaluer la perte de compétence due à la simple réduction en durée de l'archive pour la méthode standard (donc avec des analogues 0-24~h fixes) lorsque l'on passe de 47~ans (1961-2008) à 25~ans (1982-2007).
+Les paramètres sont calibrés pour les méthodes R1 et R2 (Tables \ref{tab:fenetre_glissante:Resultats_R1_originaux} et \ref{tab:fenetre_glissante:Resultats_R2_originaux}) sur l'archive originale et sont conservés pour la suite des calculs.
+
+\begin{table}[htb]
+	\caption{Paramètres retenus pour l'analogie sur le géopotentiel à 500~hPa et 1000~hPa, et compétence de la méthode standard R1 sur l'archive complète.}
+	\begin{center}
+		\begin{tabular}{l c c c c c c }
+			\hline
+			\multirow{2}{*}{\textbf{Station}} & \textbf{Lon} & \textbf{Taille} & \textbf{Lat} & \textbf{Taille} & \multirow{2}{*}{\textbf{N$_{1}$}} & \textbf{CRPSS} \\ 
+			& \textbf{min} & \textbf{lon} & \textbf{min} & \textbf{lat} & & \textbf{(\%)} \\ 
+			\hline
+			Ulrichen & 0 & 17.5 & 42.5 & 5 & 40 & 30.73 \\ \hline
+			Zermatt & 0 & 20 & 37.5 & 12.5 & 35 & 23.87 \\ \hline
+			Visp & -2.5 & 22.5 & 40 & 7.5 & 30 & 25.11 \\ \hline
+			Montana & -2.5 & 20 & 40 & 7.5 & 40 & 32.55 \\ \hline
+			Sion & -2.5 & 20 & 40 & 7.5 & 40 & 26.23 \\ \hline
+			Aigle & -5 & 22.5 & 40 & 10 & 50 & 30.59 \\ \hline
+		\end{tabular}
+	\end{center}
+	\label{tab:fenetre_glissante:Resultats_R1_originaux}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Paramètres pour l'humidité et compétence de la méthode standard R2 sur l'archive complète.
+Les paramètres de circulation de la Table \ref{tab:fenetre_glissante:Resultats_R1_originaux} sont également valables pour cette méthode, exception faite du nombre d'analogues du premier niveau d'analogie dont les nouvelles valeurs sont données dans la 6ieme colonne du présent tableau (N$_{1}$).
+La 7ieme colonne (N$_{2}$) est ici le nombre d'analogues du deuxième niveau.}
+	\begin{center}
+		\begin{tabular}{l c c c c c c c }
+			\hline
+			\multirow{2}{*}{\textbf{Station}} & \textbf{Lon} & \textbf{Taille} & \textbf{Lat} & \textbf{Taille} & \multirow{2}{*}{\textbf{N$_{1}$}} & \multirow{2}{*}{\textbf{N$_{2}$}} & \textbf{CRPSS} \\ 
+			& \textbf{min} & \textbf{lon} & \textbf{min} & \textbf{lat} & & & \textbf{(\%)} \\ 
+			\hline
+			Ulrichen & 5 & 5 & 45 & 2.5 & 60 & 25 & 34.31 \\ \hline
+			Zermatt & 5 & 5 & 45 & 2.5 & 55 & 25 & 28.28 \\ \hline
+			Vis & 5 & 5 & 45 & 2.5 & 45 & 25 & 28.85 \\ \hline
+			Montana & 5 & 2.5 & 45 & 2.5 & 55 & 30 & 36.11 \\ \hline
+			Sion & 5 & 5 & 45 & 2.5 & 90 & 30 & 31.16 \\ \hline
+			Aigle & 7.5 & 0 & 45 & 2.5 & 100 & 35 & 35.82 \\ \hline
+		\end{tabular}
+	\end{center}
+	\label{tab:fenetre_glissante:Resultats_R2_originaux}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Influence de la réduction de l'archive sur la compétence en CRPS.
+Les résultats sont présentés pour les deux méthodes R1 et R2, et les différences sont exprimées en valeur absolue, ainsi que relativement au score de la période 1961-2008.}
+	\begin{center}
+		\begin{tabular}{l r r r r r r r r}
+			\hline
+			\multirow{3}{*}{\textbf{Station}} & \multicolumn{ 4}{c}{\textbf{CRPSS (\%) R1}} & \multicolumn{ 4}{c}{\textbf{CRPSS (\%) R2}} \\
+			& \multicolumn{ 2}{c}{\textbf{périodes}} & \multirow{2}{*}{\textbf{$\Delta$}} & \multirow{2}{*}{\textbf{Gain}} & \multicolumn{ 2}{c}{\textbf{périodes}} & \multirow{2}{*}{\textbf{$\Delta$}} & \multirow{2}{*}{\textbf{Gain}} \\
+			& \multicolumn{1}{c}{\textbf{61-08}} & \multicolumn{1}{c}{\textbf{82-07}} &  &  & \textbf{61-08} & \textbf{82-07} &  &  \\ 
+			\hline
+			Ulrichen & 30.73 & 29.37 & -1.36 & \textbf{-4.42} & 34.31 & 33.24 & -1.08 & \textbf{-3.13} \\ \hline
+			Zermatt & 23.87 & 22.20 & -1.67 & \textbf{-7.01} & 28.28 & 26.95 & -1.32 & \textbf{-4.68} \\ \hline
+			Visp & 25.11 & 23.23 & -1.89 & \textbf{-7.51} & 28.85 & 27.77 & -1.08 & \textbf{-3.74} \\ \hline
+			Montana & 32.55 & 30.79 & -1.76 & \textbf{-5.42} & 36.11 & 34.77 & -1.34 & \textbf{-3.71} \\ \hline
+			Sion & 26.23 & 24.78 & -1.45 & \textbf{-5.52} & 31.16 & 29.36 & -1.80 & \textbf{-5.77} \\ \hline
+			Aigle & 30.59 & 30.57 & -0.01 & \textbf{-0.05} & 35.82 & 35.95 & 0.13 & \textbf{0.35} \\ \hline
+		\end{tabular}
+	\end{center}
+	\label{tab:fenetre_glissante:Pertes_CRPSS}
+\end{table}
+
+L'impact du changement de la période de l'archive est résumé dans la Table \ref{tab:fenetre_glissante:Pertes_CRPSS} pour les méthodes R1 et R2.
+Comme attendu, une perte de compétence peut être observée pour chaque station, excepté pour celle d'Aigle, qui semble relativement indifférente à ce changement.
+Cette perte est significative, avec un maximum pour la méthode R1 de -1.89 points à Visp, soit une perte de 7.51~\%, et pour la méthode R2 de -1.80 points à Sion, soit -5.77~\%.
+Malgré cette diminution, les scores restent acceptables et constitueront la référence en fenêtre d'analogie fixe (0-24~h).
+
+\section{Influence de la fenêtre glissante sur les critères d'analogie}
+
+\subsection{Changements du critère du premier niveau d'analogie}
+
+La recherche d'analogues sur les champs de géopotentiel de la méthode R1 a donc à présent 4 fois plus de candidats possibles qu'auparavant, ce qui permet évidemment de trouver de meilleures analogues.
+
+\begin{figure*}[htb]
+	\begin{center}
+		\includegraphics[width=15cm]{figures/Graphique_fenetre_glissante_chmts_S1_analogues.pdf}
+	\end{center}
+	\caption{Changements dans les distributions du critère S1 de certaines analogues (la 1iere, la 5ieme, la 20ieme et la 40ieme), à la station d'Ulrichen, dû à la fenêtre temporelle glissante.}
+	\label{fig:Graphique_fenetre_glissante_chmts_S1_analogues}
+\end{figure*}
+
+La Figure \ref{fig:Graphique_fenetre_glissante_chmts_S1_analogues} présente les changements dans les distributions du critère S1 pour la 1iere, la 5ieme, la 20ieme et la 40ieme analogue à la station d'Ulrichen, avec une période cible de précipitations correspondant à celle d'origine, soit centrée sur 18~h~UTC (de 6~h~UTC à 6~h~UTC le lendemain).
+Les formes des distributions de l'approche classique et de la fenêtre temporelle glissante sont semblables, mais les valeurs du critère d'analogie sont réduites, donc meilleures.
+Une augmentation de la différence entre fenêtre fixe et fenêtre glissante de la première à la dernière analogue est identifiable, ce qui signifie que nous améliorons davantage les dernières analogues.
+Ce dernier effet est dû à l'accumulation des améliorations apportées par les nouvelles analogues dans la sélection.
+
+\begin{figure}[htb]
+	\begin{center}$
+		\begin{array}{c}
+		\includegraphics[width=8cm]{figures/Graphique_fenetre_glissante_chmts_S1_val.pdf} \\
+		\includegraphics[width=8cm]{figures/Graphique_fenetre_glissante_chmts_S1_gain.pdf}
+		\end{array}$
+	\end{center}
+	\caption{Synthèse du gain sur le critère S1 à la station d'Ulrichen, pour les différentes analogues, dû à la fenêtre temporelle glissante.
+(gauche) Quantiles de la distribution des valeurs de S1 avec (06h) et sans (24h) la fenêtre glissante.
+(droite) Quantiles des gains sur le critère S1 par l'utilisation de la fenêtre glissante.}
+	\label{fig:Graphique_fenetre_glissante_chmts_S1}
+\end{figure}
+
+Ces gains sont synthétisés dans la Figure \ref{fig:Graphique_fenetre_glissante_chmts_S1}, qui illustre les valeurs, pour S1, des quantiles pour toutes les analogues avec et sans la fenêtre glissante, ainsi que la distribution des gains réalisés pour l'ensemble des dates.
+Cela confirme que tous les quantiles semblent réduits de manière semblable (les distributions de S1 conservent leur forme) et que ce gain augmente constamment de la première à la dernière analogue (Figure \ref{fig:Graphique_fenetre_glissante_chmts_S1} gauche).
+
+Les statistiques des gains pour chaque date (Figure \ref{fig:Graphique_fenetre_glissante_chmts_S1} droite) présentent une médiane de la réduction qui démarre approximativement à 5~\% pour les premières analogues et termine à plus de 10~\% pour les dernières.
+Cette tendance à l'augmentation du gain sur le critère S1 avec le rang de l'analogue peut être expliquée par le fait que chaque gain effectué sur les premières analogues se répercute sur les suivantes.
+Inversement, le gain maximal décroît de 50~\% à 25~\%.
+Le gain minimal part de 0 pour atteindre une valeur située entre 2~\% et 3~\%, signifiant que tous les critères ont été améliorés.
+Les dates sélectionnées précédemment étant toujours disponibles, le critère S1 ne peut en effet que s'améliorer ou rester identique, mais en aucun cas se détériorer.
+Toutes les autres stations présentent une amélioration du critère S1 très proche, tant pour la forme des distributions que pour leur amplitude.
+
+\subsection{Influence du dynamisme de la situation atmosphérique}
+\label{sec:ameliorations:fenetre:S1_pluie}
+
+Nous pouvons supposer que des circulations peu dynamiques, telles que les fréquentes situations anticycloniques, ne seront pas radicalement améliorées par l'approche de la fenêtre temporelle glissante.
+À l'opposé, les situations dynamiques, telles que le passage d'une perturbation, ont une évolution temporelle bien marquée.
+En effet, la position des centres actifs et des courants évoluent de manière significative durant une journée.
+Nous pouvons donc nous attendre à améliorer ces journées-ci en autorisant la fenêtre d'analogie à glisser pour mieux correspondre à la situation cible.
+
+Nous allons chercher à vérifier cette assertion, mais nous ne pouvons pas aisément quantifier le dynamisme de la circulation atmosphérique d'une journée.
+Nous faisons donc l'hypothèse que plus un jour est pluvieux, plus la situation est dynamique.
+Les résultats de cette approche sont synthétisés dans la Figure \ref{fig:Graphique_fenetre_glissante_chmts_S1_seuils_precip} par les médianes de la réduction du critère S1 pour les jours avec une pluviométrie comprise entre deux seuils.
+Le nombre d'analogues étant réduit, les courbes ne sont pas aussi lisses que lors des analyses précédentes.
+Il en ressort néanmoins que le gain tend à augmenter pour les jours à plus forte pluviométrie.
+Cette observation est valable pour toutes nos stations et cela confirme notre intuition.
+
+\begin{figure}[htb]
+	\begin{center}
+		\includegraphics[width=12cm]{figures/Graphique_fenetre_glissante_chmts_S1_seuils_precip.pdf}
+	\end{center}
+	\caption{Distribution des gains sur la médiane du critère S1, dus à la fenêtre temporelle glissante, en fonction de seuils de précipitations à la station d'Ulrichen.}
+	\label{fig:Graphique_fenetre_glissante_chmts_S1_seuils_precip}
+\end{figure}
+
+\subsection{Effet saisonnier}
+\label{sec:ameliorations:fenetre:S1_saisons}
+
+La dynamique atmosphérique varie fortement d'une saison à l'autre, ce qui rejaillit sur les performances de la méthode des analogues, généralement moindres entre juin et août \citep{Bliefernicht2010}.
+Il fait donc sens de vérifier l'effet de l'introduction de la fenêtre temporelle glissante de manière distincte par saison.
+
+\begin{figure}[htb]
+	\begin{center}$
+		\begin{array}{c}
+		\includegraphics[width=8cm]{figures/Graphique_fenetre_glissante_chmts_S1_saisons_val.pdf} \\
+		\includegraphics[width=6cm]{figures/Graphique_fenetre_glissante_chmts_S1_saisons_gain.pdf}
+		\end{array}$
+	\end{center}
+	\caption{Effet saisonnier sur le critère S1 original pour la station d'Ulrichen et son gain dû à la fenêtre temporelle glissante.
+DJF: hiver, MAM: printemps, JJA: été, SON: automne.
+(gauche) Quantiles de la distribution des valeurs de S1 pour les différentes saisons avec la fenêtre temporelle originale de 24~h.
+(droite) Médianes des gains sur le critère S1 par l'utilisation de la fenêtre glissante pour les différentes saisons.}
+	\label{fig:Graphique_fenetre_glissante_chmts_S1_saisons}
+\end{figure}
+
+\begin{figure}[htb]
+	\includegraphics[width=8.3cm]{figures/Graphique_fenetre_glissante_heures_fct_saison.pdf}
+	\caption{Répartition des tranches horaires dans les dates analogues en fonction de la saison pour la station d'Ulrichen.}
+	\label{fig:Graphique_fenetre_glissante_heures_fct_saison}
+\end{figure}
+
+Un effet saisonnier peut être observé autant sur les distributions des critères que sur leurs gains (Figure \ref{fig:Graphique_fenetre_glissante_chmts_S1_saisons}).
+Les gains sont plus importants pour l'hiver que pour l'été.
+Une hypothèse est que les effets diurnes des mois d'été ont une influence notable sur la circulation atmosphérique, du moins dans les basses couches.
+Cet effet est donc calé sur le cycle journalier et nous trouvons déjà de bonnes analogues aux mêmes heures.
+
+Cette hypothèse a été vérifiée et est confirmée par la Figure \ref{fig:Graphique_fenetre_glissante_heures_fct_saison} qui démontre que le choix des différentes tranches horaires pour les mois d'hiver est relativement équilibré, ce qui change la sélection de 75~\% des dates analogues par rapport au 0-24~h initial, augmentant ainsi l'amélioration du critère S1.
+
+Au contraire, les mois d'été ont une préférence pour la tranche horaire initiale (hgt 500 24h \& hgt 1000 12h), dû aux effets diurnes plus marqués, ce qui diminue le potentiel d'amélioration des critères.
+Les autres saisons se situent entre ces deux extrêmes, de manière cohérente avec leurs gains observés (Figure \ref{fig:Graphique_fenetre_glissante_chmts_S1_saisons}).
+Cet effet saisonnier a pu être observé pour chaque station de manière très similaire et généralement encore plus marquée que pour Ulrichen.
+
+\subsection{Changements du critère du second niveau d'analogie}
+
+Lorsque nous considérons le second niveau d'analogie de la méthode R2, les situations candidates retenues ne sont pas plus nombreuses, mais les dates peuvent avoir changé.
+Ainsi, une réduction, mais également une augmentation du critère RMSE sont possibles.
+La Figure \ref{fig:Graphique_fenetre_glissante_chmts_RMSE}, pour la station d'Ulrichen, présente une très légère amélioration du critère de manière globale.
+Contrairement au critère S1, les quantiles des gains du RMSE sont répartis de manière relativement symétrique autour de zéro, ce qui révèle l'occurrence de pertes.
+À nouveau, les résultats des autres stations sont proches, avec un gain médian à zéro pour les premières analogues et croissant par la suite, mais jamais négatif.
+
+\begin{figure}[htb]
+	\begin{center}$
+		\begin{array}{c}
+		\includegraphics[width=8cm]{figures/Graphique_fenetre_glissante_chmts_RMSE_val.pdf} \\
+		\includegraphics[width=8cm]{figures/Graphique_fenetre_glissante_chmts_RMSE_gain.pdf}
+		\end{array}$
+	\end{center}
+	\caption{Synthèse des changements sur le critère RMSE à la station d'Ulrichen, pour les différentes analogues du second niveau d'analogie, dû à la fenêtre temporelle glissante.
+(gauche) Quantiles de la distribution des valeurs de RMSE avec (06h) et sans (24h) la fenêtre glissante.
+(droite) Quantiles des gains sur le critère RMSE par l'utilisation de la fenêtre glissante.}
+	\label{fig:Graphique_fenetre_glissante_chmts_RMSE}
+\end{figure}
+
+\section{Conséquences sur les scores de performance}
+
+Nous avons pu observer précédemment un gain systématique sur le critère d'analogie S1.
+Il nous reste donc à évaluer la conséquence de l'introduction de la fenêtre temporelle glissante sur les scores de performance de la nouvelle distribution de pluie prévue.
+Nous utilisons donc des séries temporelles de précipitations créées à cet effet.
+Celles-ci ont été établies par une moyenne mobile sur une durée de 24~h avec un pas de temps de 6~h.
+En conservant toujours les mêmes paramètres que précédemment (même domaine et même nombre d'analogues), ces valeurs sont attribuées à chaque date analogue.
+La série des dates cibles reste inchangée, puisque nous conservons la tranche horaire d'origine (6~h~UTC - 6~h~UTC le lendemain).
+
+Les CRPSS étant calculés sur la base de la même climatologie que précédemment, ils peuvent être comparés directement.
+Les gains en performance ainsi obtenus (Table \ref{tab:fenetre_glissante:Gains_CRPSS}) s'étalent de 2.31~\% à 9.31~\% pour le premier niveau d'analogie.
+Lorsque nous considérons le second niveau d'analogie, les gains sont globalement un peu supérieurs.
+Nous n'avons pas trouvé de relation entre l'amélioration du score et les gains du critère S1, ni avec la saison.
+
+\begin{table}[htb]
+	\caption{Gain en compétence du CRPS sur les deux niveaux d'analogie dû à l'introduction de la fenêtre temporelle glissante.}
+	\begin{center}
+		\begin{tabular}{l r r r r r r r r}
+			\hline
+			\multirow{3}{*}{\textbf{Station}} & \multicolumn{ 4}{c}{\textbf{CRPSS (\%) R1}} & \multicolumn{ 4}{c}{\textbf{CRPSS (\%) R2}} \\
+			& \multicolumn{ 2}{c}{\textbf{fenêtre temp}} & \multirow{2}{*}{\textbf{$\Delta$}} & \multirow{2}{*}{\textbf{Gain}} & \multicolumn{ 2}{c}{\textbf{fenêtre temp}} & \multirow{2}{*}{\textbf{$\Delta$}} & \multirow{2}{*}{\textbf{Gain}} \\
+			& \multicolumn{1}{c}{\textbf{std}} & \multicolumn{1}{c}{\textbf{gliss.}} &  &  & \textbf{std} & \textbf{gliss.} &  & \\ 
+			\hline
+			Ulrichen & 29.37 & 31.12 & 1.74 & \textbf{5.93} & 33.24 & 35.44 & 2.20 & \textbf{6.63} \\ \hline
+			Zermatt & 22.20 & 24.34 & 2.14 & \textbf{9.64} & 26.95 & 28.92 & 1.97 & \textbf{7.31} \\ \hline
+			Visp & 23.23 & 24.39 & 1.16 & \textbf{5.00} & 27.77 & 29.42 & 1.64 & \textbf{5.92} \\ \hline
+			Montana & 30.79 & 31.59 & 0.80 &\textbf{ 2.60} & 34.77 & 36.30 & 1.53 & \textbf{4.39} \\ \hline
+			Sion & 24.78 & 25.35 & 0.57 & \textbf{2.31} & 29.36 & 31.07 & 1.71 & \textbf{5.82} \\ \hline
+			Aigle & 30.57 & 31.78 & 1.21 & \textbf{3.95} & 35.95 & 38.11 & 2.16 & \textbf{6.00} \\ \hline
+		\end{tabular}
+	\end{center}
+	\label{tab:fenetre_glissante:Gains_CRPSS}
+\end{table}
+
+\subsection{Amélioration de différentes gammes de précipitations}
+\label{sec:ameliorations:fenetre:gammes_precip}
+
+\begin{figure}[htb]
+	\includegraphics[width=6cm]{figures/Graphique_fenetre_glissante_chmts_CRPS_seuils_precip.pdf}
+	\caption{Distribution des différences sur le score CRPSS dues à l'introduction de la fenêtre temporelle glissante en fonction de seuils de précipitations à la station d'Ulrichen.
+Les étoiles sont les moyennes des distributions.}
+	\label{fig:Graphique_fenetre_glissante_chmts_CRPS_seuils_precip}
+\end{figure}
+
+Nous avions observé dans la section \ref{sec:ameliorations:fenetre:S1_pluie} une amélioration du critère S1 pour les situations plus dynamiques, soit avec des valeurs de précipitations supérieures.
+Nous allons à présent mettre en relation les gains en CRPSS et les cumuls précipités.
+
+La Figure \ref{fig:Graphique_fenetre_glissante_chmts_CRPS_seuils_precip} synthétise ces gains pour la station d'Ulrichen, les autres stations se comportant de la même manière.
+Un étalement de la distribution avec l'augmentation du seuil de précipitations peut être observé.
+Cet effet s'explique en premier lieu par le fait que la valeur du CRPS est dépendante des quantités de précipitations des journées cibles.
+
+Un résultat plus intéressant est la tendance positive croissante de toute la distribution avec l'augmentation du seuil des précipitations.
+À partir du seuil de 10~mm, la moyenne et les quantiles du gain en CRPSS tendent à augmenter de manière significative.
+Il semble donc que nous améliorons les scores de performance des événements davantage pluvieux, en plus de leurs critères d'analogie.
+Le fait que les jours non pluvieux et les petits cumuls ne sont pas améliorés semble expliquer le gain peu probant lorsque nous considérons l'ensemble de la période.
+
+\subsection{Recalibration des paramètres}
+\label{sec:ameliorations:fenetre:recalibration}
+
+L'évaluation précédente du gain en score de performance a été établie avec les paramètres originaux.
+Nous pouvons néanmoins supposer que l'introduction de la fenêtre temporelle glissante modifie peut-être le choix optimal de la position et de la taille de la fenêtre spatiale idéale et change le nombre d'analogues comparativement à la méthode standard.
+La calibration a donc été effectuée à nouveau.
+
+\begin{table}[htb]
+	\caption{Paramètres pour les champs de géopotentiel à 500~hPa et 1000~hPa et compétence de la méthode R1 après calibration pour la fenêtre temporelle glissante.}
+	\begin{center}
+		\begin{tabular}{l c c c c c c c c }
+			\hline
+			\multirow{2}{*}{\textbf{Station}} & \textbf{Lon} & \textbf{Taille} & \textbf{Lat} & \textbf{Taille} & \multirow{2}{*}{\textbf{N$_{1}$}} & \textbf{CRPSS} & \multirow{2}{*}{\textbf{$\Delta$}} & \textbf{Gain} \\
+			& \textbf{min} & \textbf{lon} & \textbf{min} & \textbf{lat} &  & \textbf{(\%)} & & \textbf{(\%)} \\ 
+			\hline
+			Ulrichen & 0 & 17.5 & 42.5 & 7.5 & 50 & 31.58 & 2.20 & \textbf{7.50} \\ \hline
+			Zermatt & 0 & 17.5 & 40 & 10 & 55 & 24.71 & 2.51 & \textbf{11.32} \\ \hline
+			Visp & -2.5 & 22.5 & 40 & 10 & 55 & 25.08 & 1.85 & \textbf{7.96} \\ \hline
+			Montana & -2.5 & 17.5 & 42.5 & 5 & 55 & 32.22 & 1.43 & \textbf{4.65} \\ \hline
+			Sion & -2.5 & 17.5 & 37.5 & 12.5 & 55 & 26.07 & 1.29 & \textbf{5.19} \\ \hline
+			Aigle & -2.5 & 17.5 & 40 & 10 & 75 & 32.21 & 1.64 & \textbf{5.36} \\ \hline
+		\end{tabular}
+	\end{center}
+	\label{tab:fenetre_glissante:Resultats_R1_recalibration_fen_gliss}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Paramètres pour l'humidité et compétence de la méthode R2 après calibration pour la fenêtre temporelle glissante.
+Le nombre d'analogues du premier niveau d'analogie est donné dans la 6ieme colonne (N$_{1}$) et celui du second niveau dans la 7ieme colonne (N$_{2}$).}
+	\begin{center}
+		\begin{tabular}{l c c c c c c c c c }
+			\hline
+			\multirow{2}{*}{\textbf{Station}} & \textbf{Lon} & \textbf{Taille} & \textbf{Lat} & \textbf{Taille} & \multirow{2}{*}{\textbf{N$_{1}$}} & \multirow{2}{*}{\textbf{N$_{2}$}} & \textbf{CRPSS} &  \multirow{2}{*}{\textbf{$\Delta$}} & \textbf{Gain}\\
+			& \textbf{min} & \textbf{lon} & \textbf{min} & \textbf{lat} &  &  & \textbf{(\%)} & & \textbf{(\%)} \\ 
+			\hline
+			Ulrichen & 5 & 5 & 45 & 2.5 & 110 & 35 & 35.72 & 2.48 & \textbf{7.46} \\ \hline
+			Zermatt & 7.5 & 0 & 45 & 2.5 & 80 & 30 & 29.63 & 2.68 & \textbf{9.94} \\ \hline
+			Visp & 7.5 & 0 & 45 & 2.5 & 135 & 35 & 30.29 & 2.52 & \textbf{9.07} \\ \hline
+			Montana & 5 & 2.5 & 45 & 0 & 110 & 40 & 37.15 & 2.38 & \textbf{6.85} \\ \hline
+			Sion & 5 & 5 & 45 & 2.5 & 140 & 50 & 31.68 & 2.32 & \textbf{7.91} \\ \hline
+			Aigle & 5 & 2.5 & 45 & 0 & 135 & 45 & 38.50 & 2.55 & \textbf{7.10} \\ \hline
+		\end{tabular}
+	\end{center}
+	\label{tab:fenetre_glissante:Resultats_R2_recalibration_fen_gliss}
+\end{table}
+
+Des changements dans les paramètres optimaux des méthodes R1 (Table \ref{tab:fenetre_glissante:Resultats_R1_recalibration_fen_gliss}) et R2 (Table \ref{tab:fenetre_glissante:Resultats_R2_recalibration_fen_gliss}) peuvent être observés.
+Parmi ceux-ci, la dimension ouest-est des fenêtres spatiales du premier niveau tend à diminuer, les autres paramètres variant de diverses manières.
+Une constance est l'augmentation du nombre d'analogues après introduction de la fenêtre glissante, qui croît de 25~\% à 83~\% pour la méthode R1, et de 20~\% à 67~\% pour la méthode R2.
+Le nombre d'analogues du premier niveau de la méthode R2 atteint même le triple de sa valeur précédente pour la station de Visp.
+Le fait de pouvoir sélectionner des analogues de la même journée explique que nous sommes conduits à augmenter le nombre optimal d'analogues.
+La Figure \ref{fig:Graphique_fenetre_glissante_chmts_S1} nous a révélé que l'amélioration du critère d'analogie est croissante avec le rang des analogues.
+Nous accroissons donc le nombre de bonnes analogues de manière globale, tout en conservant certaines analogues dont le rang a augmenté.
+
+Cette augmentation du nombre d'analogues a un léger effet sur les performances des différentes classes de précipitations.
+L'analyse par classes (section \ref{sec:ameliorations:fenetre:gammes_precip}) a été effectuée à nouveau sur les analogues après recalibration.
+Les résultats sont globalement très semblables, mais nous pouvons distinguer une légère augmentation des performances des petites pluies au détriment des précipitations plus importantes.
+L'accroissement du nombre d'analogues est vraisemblablement responsable de cette différence dans la répartition des gains.
+
+Les valeurs des scores des méthodes R1 (Table \ref{tab:fenetre_glissante:Resultats_R1_recalibration_fen_gliss}) et R2 (Table \ref{tab:fenetre_glissante:Resultats_R2_recalibration_fen_gliss}) ont significativement augmenté après la recalibration.
+Avec l'introduction de la fenêtre temporelle glissante, nous regagnons en performance ce que nous avions alors perdu par la réduction de la longueur de l'archive.
+Dans notre cas, cette amélioration correspond approximativement à un doublement de la taille de l'archive.
+
+\subsection{Décomposition du score en finesse et justesse}
+
+Le score CRPS pouvant être décomposé en deux composantes, à savoir la finesse et la justesse, nous allons analyser l'effet de la fenêtre temporelle glissante sur chacune d'elles.
+Les résultats de la Table \ref{tab:fenetre_glissante:Resultats_justesse_finesse} étant exprimés par rapport au CRPS total, un changement de la finesse est donc quantifié par rapport à la somme de la finesse et de la justesse.
+En effet, ces deux composantes n'ont pas les mêmes gammes de valeurs, la justesse étant dans notre cas presque deux fois supérieure à la finesse.
+Puisque nous travaillons ici sur le CRPS et non le CRPSS, une amélioration de la prévision se traduit par une baisse du score.
+
+\begin{table}[h]
+	\caption{Changements en finesse (Fin.) et en justesse (Just.) relatifs au CRPS total, dus à l'introduction de la fenêtre temporelle glissante.
+Les changements sont présentés pour les méthodes R1 et R2, et pour les résultats sans et avec recalibration des paramètres.}
+	\begin{center}
+		\begin{tabular}{|l|r r|r r|r r|r r|}
+			\cline{2-9}
+			\multicolumn{1}{l}{} & \multicolumn{ 4}{|c|}{\textbf{Fenêtre glissante}} & \multicolumn{ 4}{c|}{\textbf{Fenêtre glissante}} \\
+			\multicolumn{1}{l}{} & \multicolumn{ 4}{|c|}{\textbf{sans recalibration}} & \multicolumn{ 4}{c|}{\textbf{avec recalibration}} \\
+			\multicolumn{1}{l}{} & \multicolumn{ 2}{|c|}{\textbf{R1}} & \multicolumn{ 2}{c|}{\textbf{R2}} & \multicolumn{ 2}{c|}{\textbf{R1}} & \multicolumn{ 2}{c|}{\textbf{R2}} \\
+			\multicolumn{1}{l}{} & \multicolumn{1}{|l}{\textbf{Fin.}} & \multicolumn{1}{l|}{\textbf{Just.}} & \multicolumn{1}{l}{\textbf{Fin.}} & \multicolumn{1}{l|}{\textbf{Just.}} & \multicolumn{1}{l}{\textbf{Fin.}} & \multicolumn{1}{l|}{\textbf{Just.}} & \multicolumn{1}{l}{\textbf{Fin.}} & \multicolumn{1}{l|}{\textbf{Just.}} \\
+			\multicolumn{1}{l}{} & \multicolumn{1}{|l}{\textbf{(\%)}} & \multicolumn{1}{l|}{\textbf{(\%)}} & \multicolumn{1}{l}{\textbf{(\%)}} & \multicolumn{1}{l|}{\textbf{(\%)}} & \multicolumn{1}{l}{\textbf{(\%)}} & \multicolumn{1}{l|}{\textbf{(\%)}} & \multicolumn{1}{l}{\textbf{(\%)}} & \multicolumn{1}{l|}{\textbf{(\%)}} \\ \hline
+			Ulrichen & 2.82 & -5.29 & 1.00 & -4.30 & 1.44 & -4.56 & -0.37 & -3.34 \\ \hline
+			Zermatt & 2.26 & -5.01 & 0.88 & -3.58 & 0.80 & -4.03 & 0.75 & -4.42 \\ \hline
+			Visp & 3.66 & -5.18 & 2.67 & -4.94 & 1.53 & -3.94 & 1.47 & -4.96 \\ \hline
+			Montana & 1.62 & -2.78 & 0.57 & -2.91 & -0.27 & -1.80 & 0.06 & -3.71 \\ \hline
+			Sion & 2.02 & -2.78 & 0.33 & -2.75 & 0.95 & -2.66 & -0.10 & -3.19 \\ \hline
+			Aigle & 0.52 & -2.26 & -1.20 & -2.17 & -0.35 & -2.01 & -2.08 & -1.90 \\ \hline
+		\end{tabular}
+	\end{center}
+	\label{tab:fenetre_glissante:Resultats_justesse_finesse}
+\end{table}
+
+\begin{figure*}[h]
+	\begin{center}$
+		\begin{array}{cccc}
+		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_justesse.pdf} & \hspace{-5mm}
+		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_finesse.pdf} & \hspace{-5mm}
+		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_justesse.pdf} & \hspace{-5mm}
+		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_finesse.pdf} \\
+		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_justesse_recalib.pdf} & \hspace{-5mm}
+		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_finesse_recalib.pdf} & \hspace{-5mm}
+		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_justesse_recalib.pdf} & \hspace{-5mm}
+		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_finesse_recalib.pdf} 
+		\end{array}$
+	\end{center}
+	\caption{Influence de la fenêtre temporelle glissante sur les composantes du CRPS (justesse et finesse), pour les méthodes R1 et R2.
+Les résultats sont présentés pour (haut) les paramètres originaux et (bas) recalibrés.
+Une amélioration de la prévision se traduit par une baisse du score.}
+	\label{fig:Graphique_fenetre_glissante_crps_comp}
+\end{figure*}
+
+Il apparaît que la finesse est moins bonne avec la fenêtre temporelle glissante, au profit de la justesse, et ceci pour les mêmes paramètres que la méthode standard, alors qu'elle décroît avec l'augmentation du nombre d'analogues après recalibration.
+La Figure \ref{fig:Graphique_fenetre_glissante_crps_comp}, illustrant les changements en finesse et justesse pour différentes gammes de précipitations à la station d'Ulrichen, présente cette même tendance.
+Nous y voyons également que le plus grand gain en justesse concerne les gammes de précipitations les plus importantes, que ce soit pour R1 ou R2.
+La fenêtre temporelle glissante ne permet donc pas d'améliorer la finesse, mais l'amélioration de la justesse est significative, et ceci notamment pour les jours de fortes précipitations.
+Cela signifie donc que le quantile 50~\% de la distribution prévue se rapproche des cumuls observés, mais que la distribution n'est pas plus condensée que précédemment.
+
+\section{Tentatives d'application à l'archive complète}
+
+L'amélioration apportée par la fenêtre temporelle glissante est intéressante, il serait donc profitable de pouvoir l'appliquer à notre archive complète.
+Malheureusement, il n'existe pas de données horaires avant 1982 nous permettant de disposer d'une archive compatible et correcte.
+Nous allons donc chercher à répartir les cumuls précipités sur la journée par une simple moyenne mobile ou en utilisant la chronologie d'un prédicteur lié à l'humidité en tant que proxy.
+
+\subsection{Série par moyenne mobile}
+
+La moyenne mobile est certainement la répartition la plus simple que nous pouvons effectuer.
+Elle consiste à distribuer les précipitations journalières concernées de manière proportionnelle dans les différentes tranches de la série 24~heures glissée (Figure \ref{fig:Illustration_series_6h_moyennes_mobiles}).
+Les résultats présentés dans la Table \ref{tab:fenetre_glissante:Resultats_moyenne_mobile} montrent clairement qu'une telle archive ne présente aucun intérêt, puisque les performances sont même inférieures à la méthode classique sans fenêtre temporelle glissante (Table \ref{tab:fenetre_glissante:Gains_CRPSS}).
+Nous perdons le gain d'une sélection plus fine des situations analogues du fait d'une archive pluviométrique de qualité médiocre.
+
+\begin{figure}[htb]
+	\begin{center}
+		\includegraphics[width=12cm]{figures/Illustration_series_6h_moyennes_mobiles.pdf}
+	\end{center}
+	\caption{Illustration de la création de séries de cumuls sur 24h glissés par moyenne mobile.}
+	\label{fig:Illustration_series_6h_moyennes_mobiles}
+\end{figure}
+
+\begin{table}[htb]
+	\caption{Performances de la fenêtre temporelle glissante avec une archive pluviométrique générée par moyenne mobile.
+Les résultats sont présentés pour les paramètres initiaux, ainsi que ceux issus de la recalibration de la section \ref{sec:ameliorations:fenetre:recalibration}}
+	\begin{center}
+		\begin{tabular*}{10cm}{@{\extracolsep{\fill}}lcccc}
+			\hline
+			\multirow{2}{*}{\textbf{Station}} & \multicolumn{ 2}{c}{\textbf{Fenêtre glissante}} & \multicolumn{ 2}{c}{\textbf{Avec recalibration}} \\
+			& \multicolumn{1}{c}{\textbf{R1}} & \multicolumn{1}{c}{\textbf{R2}} & \multicolumn{1}{c}{\textbf{R1}} & \multicolumn{1}{c}{\textbf{R2}} \\ \hline
+			Ulrichen & 29.13~\% & 33.15~\% & 29.61~\% & 33.45~\% \\ \hline
+			Zermatt & 22.17~\% & 26.72~\% & 22.80~\% & 27.43~\% \\ \hline
+			Visp & 22.32~\% & 27.01~\% & 22.89~\% & 28.04~\% \\ \hline
+			Montana & 29.41~\% & 33.83~\% & 30.24~\% & 34.55~\% \\ \hline
+			Sion & 22.98~\% & 28.57~\% & 23.41~\% & 29.15~\% \\ \hline
+			Aigle & 29.07~\% & 34.66~\% & 29.46~\% & 35.09~\% \\ \hline
+		\end{tabular*}
+	\end{center}
+	\label{tab:fenetre_glissante:Resultats_moyenne_mobile}
+\end{table}
+
+\subsection{Utilisation d'un proxy pour reconstituer la chronologie}
+
+Comme nous l'avons vu dans la section précédente, une série de précipitations reconstituée de manière simpliste nous fait perdre tout le gain de performance de la fenêtre temporelle glissante et ne présente alors aucun intérêt.
+Nous devons donc trouver un moyen de nous approcher de la chronologie réelle, pour une période (1961-1981) où nous ne disposons d'aucune série de précipitations continue avec une résolution plus fine.
+Il nous faut donc extraire de l'information de la répartition intrajournalière des pluies à partir d'une autre source de données.
+Un modèle de prévision météorologique régional serait en mesure d'apporter de l'information permettant de générer des séries de précipitations plus pertinentes.
+Malheureusement, de tels résultats ne sont pas disponibles sous forme de longues archives.
+Une alternative aux modèles régionaux est donnée par les réanalyses.
+Bien que celles-ci ont une résolution plus faible et n'intègrent que grossièrement les processus locaux, nous allons évaluer si elles rendent possible la transposition de la fenêtre temporelle glissante sur toute l'archive.
+
+La première étape consiste à déterminer quelle variable, de l'eau précipitable ou de l'humidité relative, est la plus corrélée avec la série de précipitations sur la période 1982-2007, et en quel point.
+Nous considérons les niveaux 1000~hPa, 925~hPa et 850~hPa pour l'humidité relative, et les points les plus proches du bassin (5\textdegree\ - 7.5\textdegree\ de longitude et 45\textdegree\ - 47.5\textdegree\ de latitude).
+Finalement, les points de grille des réanalyses étant relativement éloignés de nos stations, il est pertinent de rechercher la présence probable d'un décalage temporel entre les séries.
+
+Le point le plus pertinent ne sera probablement pas le même pour toutes les stations, puisque nous pouvons nous attendre à trouver l'optimum dans la direction des apports d'humidité principaux pour la station.
+Cette recherche doit donc être effectuée pour chacune de nos stations.
+Nous illustrons le principe avec la station de Zermatt.
+
+\begin{table}[htb]
+	\caption{Valeur du coefficient de détermination entre les séries reconstituées à l'aide d'un proxy et la série réelle à pas de temps de 6~h.
+Les proxys évalués sont l'eau précipitable et l'humidité relative à différents niveaux atmosphériques, en 4 points proches du bassin.
+Le coefficient de détermination le plus élevé est indiqué en gras.}
+	\begin{center}
+		\begin{tabular}{|l|rr|rrrrr|}
+			\cline{ 2- 8}
+			\multicolumn{1}{l}{} & \multicolumn{2}{|c|}{\textbf{Position}} &  \multicolumn{5}{c|}{\textbf{Décalage temporel}} \\
+			\multicolumn{1}{l}{} & \multicolumn{1}{|c}{\textbf{Lon}} & \multicolumn{1}{c|}{\textbf{Lat}} & \multicolumn{1}{c}{\textbf{-12h}} & \multicolumn{1}{c}{\textbf{-6h}} & \multicolumn{1}{c}{\textbf{0h}} & \multicolumn{1}{c}{\textbf{+6h}} & \multicolumn{1}{c|}{\textbf{+12h}} \\ \hline
+			\multirow{ 4}{*}{RHum 1000 hPa} & 5.0 & 47.5 & 0.668 & 0.669 & 0.684 & 0.683 & 0.670 \\
+			& 5.0 & 45.0 & 0.669 & 0.669 & 0.683 & 0.681 & 0.669 \\
+			& 7.5 & 47.5 & 0.662 & 0.673 & 0.691 & 0.682 & 0.673 \\
+			& 7.5 & 45.0 & 0.666 & 0.671 & 0.688 & 0.681 & 0.668 \\ \hline
+			\multirow{ 4}{*}{RHum 925 hPa} & 5.0 & 47.5 & 0.672 & 0.673 & 0.684 & 0.684 & 0.675 \\
+			& 5.0 & 45.0 & 0.674 & 0.674 & 0.683 & 0.682 & 0.672 \\
+			& 7.5 & 47.5 & 0.662 & 0.673 & 0.691 & 0.682 & 0.673 \\
+			& 7.5 & 45.0 & 0.666 & 0.671 & 0.689 & 0.681 & 0.668 \\ \hline
+			\multirow{ 4}{*}{RHum 850 hPa} & 5.0 & 47.5 & 0.675 & 0.675 & 0.679 & 0.678 & 0.671 \\
+			& 5.0 & 45.0 & 0.681 & 0.690 & 0.691 & 0.677 & 0.664 \\
+			& 7.5 & 47.5 & 0.665 & 0.680 & 0.693 & 0.683 & 0.675 \\
+			& 7.5 & 45.0 & 0.675 & 0.694 & 0.706 & 0.681 & 0.659 \\ \hline
+			\multirow{ 4}{*}{Eau precipitable} & 5.0 & 47.5 & 0.688 & 0.687 & 0.667 & 0.655 & 0.652 \\
+			& 5.0 & 45.0 & 0.697 & 0.699 & 0.669 & 0.644 & 0.644 \\
+			& 7.5 & 47.5 & 0.686 & 0.708 & 0.689 & 0.655 & 0.648 \\
+			& 7.5 & 45.0 & 0.696 & \textbf{0.721} & 0.696 & 0.643 & 0.636 \\ \hline
+		\end{tabular}
+	\end{center}
+	\label{tab:fenetre_glissante:Serie_proxy_correlations}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Valeurs des scores CRPSS pour Zermatt avec la série glissée reconstituée à l'aide d'un proxy météorologique.
+Les résultats sont présentés pour les deux périodes 1982-2007 et 1961-2008, pour les paramètres sans et avec recalibration, ainsi que pour les deux méthodes R1 et R2.}
+	\begin{center}
+		\begin{tabular*}{10cm}{@{\extracolsep{\fill}}lcccc}
+			\hline
+			\multirow{2}{*}{\textbf{Période}} & \multicolumn{ 2}{c}{\textbf{Sans recalibration}} & \multicolumn{ 2}{c}{\textbf{Avec recalibration}} \\
+			& \multicolumn{1}{c}{\textbf{R1}} & \textbf{R2} & \multicolumn{1}{c}{\textbf{R1}} & \textbf{R2} \\ \hline
+			1982-2007 & 22.57~\% & 27.11~\% & 23.14~\% & 27.71~\% \\ \hline
+			1961-2008 & 23.81~\% & 28.42~\% & 24.38~\% & 28.86~\% \\ \hline
+		\end{tabular*}
+	\end{center}
+	\label{tab:fenetre_glissante:Resultats_proxy_Zermatt}
+\end{table}
+
+Afin de déterminer quelle variable météorologique considérer, en quel point, et avec quel décalage horaire, chacune des séries générées doit être comparée à la série réelle.
+La Table \ref{tab:fenetre_glissante:Serie_proxy_correlations} présente les coefficients de détermination sur les valeurs non nulles entre les nouvelles séries reconstituées à l'aide du proxy et la série réelle de la station de Zermatt à pas de temps de 6~h sur la période 1982-2007.
+Le meilleur proxy est l'eau précipitable à 45\textdegree\ de latitude et 7.5\textdegree\ de longitude, avec un décalage temporel de -6~h; cela signifie que nous devons retarder de 6~h la chronologie du prédicteur afin de l'appliquer aux précipitations.
+Le coefficient de détermination de 0.721 est supérieur à celui de la série par moyenne mobile (0.698), ce qui nous confirme que nous avons ajouté un peu d'information à la série de précipitations, sans toutefois savoir si celle-ci est suffisante.
+
+La Table \ref{tab:fenetre_glissante:Resultats_proxy_Zermatt} présente les scores CRPSS obtenus par la série reconstituée à l'aide du proxy de l'eau précipitable au point optimal (Table \ref{tab:fenetre_glissante:Serie_proxy_correlations}).
+Nous observons une légère amélioration par rapport aux résultats obtenus avec la série de moyennes mobiles (Table \ref{tab:fenetre_glissante:Resultats_moyenne_mobile}), mais celle-ci est toujours relativement petite, et la plus grande partie du gain de la fenêtre temporelle glissante est perdue.
+
+Ces tentatives de transposition de la fenêtre temporelle glissante sur l'archive totale mettent en évidence l'importance de la temporalité réelle des précipitations.
+La fenêtre glissante est un gain, à condition que les séries de précipitations soient proches de l'observé.
+Sans information sur la chronologie des précipitations, il n'est pas pertinent d'appliquer cette modification à la méthode.
+Nous pouvons espérer que, dans le futur, des reprévisions par des modèles régionaux seront en mesure de nous apporter une chronologie des précipitations s'approchant de la réalité.
 
 \conclusions  %% \conclusions[modified heading if necessary]
-TEXT
+
+Comme \citet{Finet2008} l'avaient déjà été montré précédemment, nous gagnons en analogie synoptique en introduisant la fenêtre temporelle glissante.
+Pour ce qui est de la prévision des précipitations, nous regagnons en fenêtre glissante sur période réduite ce que nous avions perdu par rapport à la fenêtre fixe en raison de la réduction de l'archive.
+Dans notre cas, ce gain correspond au doublement de la taille de l'archive.
+
+Nous avons également démontré l'importance de la qualité de l'archive pluviométrique: nous gagnons en prévision des précipitations pour autant que la chronologie des pluies y soit proche de la réalité.
+Pour une archive reconstituée de manière grossière, les gains en performances de la fenêtre glissante ne se répercutent pas sur la prévision des pluies, bien que l'analogie synoptique soit meilleure.
+Il conviendra donc de maintenir l'objectif qui consiste à reconstruire des séries de précipitations passées de manière la plus réaliste possible, par exemple à l'aide d'un modèle météorologique régional.
+Lorsque de telles archives pluviométriques seront disponibles, l'ajout d'une fenêtre temporelle glissante en prévision par analogie montrera tout son intérêt.
 
@@
 \bibliographystyle{copernicus}
-\bibliography{../_refs/_articles-movingwindow}
+\bibliography{../_refs/_articles-moving-window}
 

### 2015-12-14 Moving temporal window - HESS/template.tex
Writing the Moving temporal window.

@@
 
-\title{Introducing a Moving Temporal Window in the Analogue Method for Precipitation Forecasting}
+\title{The Analogue Method for Precipitation Forecasting: Finding Better Analogue Situations at a Sub-Daily Time Step}
 
@@
 \introduction  %% \introduction[modified heading if necessary]
-TEXT
 
-La méthode des analogues est habituellement implémentée avec un pas de temps journalier, la disponibilité de longues archives de données pluviométriques journalières n'ayant pas d'équivalent à une résolution plus fine.
-Ce pas de temps nous contraint à chercher des situations analogues aux mêmes heures fixes de la journée, sans quoi nous ne saurions pas quelles valeurs de précipitations leur attribuer.
-Nous pouvons néanmoins nous attendre à ce que l'analogie des situations météorologiques n'ait pas lieu systématiquement à la même heure de la journée, et que de meilleures candidates soient trouvées en autorisant un certain décalage.
+%REWRITE
+
+Multiple variations of the methods exist, and most of them will not be detailed hereafter \cite[see][for more comprehensive listings]{Horton2016, BenDaoud2015}.
+However, there are mainly 2 parameterizations that are most often used for precipitation forecasting and that will be considered as reference: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
+
+The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:method_2Z}): the similarity of the atmospheric circulation of a target date with every day of the archive is assessed by processing the S1 criteria \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
+\citet{Bontron2005} showed that the geopotential height at 500~hPa (Z500) and 1000~hPa (Z1000) are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criteria performs better than scores based on absolute distances.
+The reason for such better results is that the S1 criteria allows comparing the circulation pattern, by means of the gradients, rather than the absolute value of the geopotential height.
+To cope with seasonal effects, candidate dates are extracted within a period of 4 months centered around the target date, for every year of the archive.
+Following the nomenclature proposed by \citet{Horton2016}, this method will be named 2Z.
+
+\begin{equation}
+\label{eq:S1}
+S1=100 \frac {\displaystyle \sum_{i} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
+{\displaystyle \sum_{i} max\left\lbrace \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert \right\rbrace }
+\end{equation}
+where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points of the gridded data describing the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
+The differences are processed separately in both directions.
+The smaller the S1 values, the more similar the pressure fields.
+
+\begin{table}[htb]
+	\caption{Parameters of the reference method on the atmospheric circulation (2Z).
+The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window).
+The criteria used for the current level of analogy is then provided, as well as the number of analogues.}
+	\footnotesize
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline
+			Level & Variable & Hour & Criteria & Nb \\ 
+			\hline 
+			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
+			& Z500 & 24~h & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:method_2Z}
+\end{table}
+
+The $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day.
+The number of analogues, $N_{1}$, is a parameter to calibrate.
+Then, the daily observed precipitation amount of the $N_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
+
+The other most know parametrization adds a second level of analogy on moisture variables (method 2Z-2MI, Table \ref{table:method_2Z-2MI}).
+The predictor that \citet{Bontron2004} found optimal for the France territory is a moisture index made of the product of the precipitable water with the relative humidity at 850~hPa (RH850).
+\cite{Horton2012a} confirmed that this index is also better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis considered independently.
+When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
+When a second level of analogy is added, a higher number of analogues is kept on the first level.
+
+\begin{table}[htb]
+	\caption{Parameters of the reference method with moisture variables (2Z-2MI). Same conventions as Table \ref{table:method_2Z}}
+	\footnotesize
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline 
+			Level & Variable & Hour & Criteria & Nb \\ 
+			\hline 
+			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
+			& Z500 & 24~h & & \\ 
+			\hline
+			\multirow{2}{*}{2} & TPW * RH850 & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{30} \\
+			& TPW * RH850 & 24~h & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:method_2Z-2MI}
+\end{table}
+
+%REWRITE
+
+%COMPLETE
+
+sliding time window (STW)
+
+The analogue method (AM) is usually implemented with a daily time step, due to the availability of long precipitation archives that have no equivalent to a finer resolution.
+Therefore, the analogues situations are compared on the basis of a daily time step, by comparing predictors at fixed hours of the day, otherwise we would not know what precipitation values to assign to them.
+However, we can expect that the analogy of the synoptic situations do not occur systematically at the same time of the day, and that better candidates can be found at different times.
+
+Previous tests showed the benefit, in terms of analogy criteria values, of searching for analogue synoptic situations at a finer time step, but without assessing the impact on the forecast skills \citep{Finet2008}.
+Archives of sub-daily precipitation datasets were not available on a long period in order to assess the improvement of the prediction.
+In order to assess this potential gain, precipitation data with a resolution of 10 minutes on a respectable archive length was used (section \ref{sec:data}).
+It was then aggregated in the form of 24~h totals, but at a 6-hourly time step, by means of a moving average (section \ref{sec:method}).
+
+One can question the interest of using daily totals when a 6-hourly precipitation series can be used.
+The first reason is that the 6-hourly time series generated by the AM may not represent well the dynamic of the accurate precipitation (results not shown), due to a smoothed signal.
+Then, sometimes we just don't need finer resolution than the daily time step.
+Finally, when using a reconstructed precipitation archive, the errors in intra-day precipitation distributions have a lesser impact.
+
+%COMPLETE
+
+\section{Study area and data}
+\label{sec:data}
+
+The study area is the upper Rh\^{o}ne catchment in Switzerland.
+Due to the low density of weather stations with high temporal resolution and long archives, no aggregation or catchment rainfall was processed.
+The time series (on the period 1982-2007) come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle.
+
+%WRITE
+
+%FIGURE
+
+\section{Method}
+\label{sec:method}
+
+In order to assess the benefit of searching analogue situations at a sub-daily time step, an appropriate time series is required.
+On the basis of high resolution time series (section \ref{sec:data}), 24~h totals were processed, but at a 6-hourly time step (temporal resolution of the reanalysis dataset), by means of a moving average.
+
+The target situations and their corresponding observed precipitation values (used for validation) do not change, because the forecast is always established for a fixed period of the target day (6-30~h), as before.
+The difference is that the candidates are 4~times more numerous (Figure \ref{fig:principle}).
 
@@
 	\end{center}
-	\caption[Illustration du principe de la fenêtre temporelle glissante.]{Illustration du principe de la fenêtre temporelle glissante. }
-	\label{fig:Illustration_fenetre_glissante}
+	\caption{Illustration of the principle of a sliding time window. }
+	\label{fig:principle}
 \end{figure*}
 
-De premiers essais \citep{Finet2008} avaient porté sur la seule recherche de situations synoptiques analogues à une situation cible.
-Ils avaient montré que pour une situation cible 0-24~h~UTC, on pouvait obtenir de meilleures analogies synoptiques en acceptant des situations  ''glissées'' 6-30~h, 12-36~h ou 18-42~h plutôt que de se limiter à 0-24~h.
-Mais il n'avait pas été possible de constituer les archives pluviométriques correspondantes, c'est-à-dire qui soient décalées, elles-aussi, dans le but de quantifier d'éventuelles améliorations de la prévision de précipitations.
+Logic suggests a priori that only one situation (the best) is selected per candidate day. An exclusion of the same dates was tested in two different ways: (1)
+by excluding the worse analogues in a period of $\pm$ 24~h, and (2) by excluding the worse analogues with the same date.
+After several tests, it turned out that no restrictions led to better skills, and this on a significant and recurring basis.
+Thus, no constraint was further used.
 
-Afin d'évaluer ce gain potentiel, nous avons donc d'abord traité les mesures des stations automatiques de résolution 10~minutes (voir section \ref{sec:donnees:reseau}) ayant une durée respectable (1982-2007), pour élaborer des séries de précipitations représentant des cumuls de 24~h, mais sur une fenêtre temporelle glissante.
-Cela veut dire que nous constituons une série de 24~h centrée sur chaque tranche de 6~h de la journée, ce dernier pas de temps étant la résolution des prédicteurs synoptiques (voir section \ref{sec:donnees:reanalyses1_ncep}).
+\section{Consequences of the archive reduction}
 
-Une telle série présente certains avantages.
-Le premier étant que la compétence résultant de ce modèle sera comparable à celle établie précédemment, et que le gain d'une telle modification peut donc être directement évalué.
-Le second s'inscrit dans la perspective de création de ce genre de séries à partir de données journalières désagrégées (en 6~h) puis recomposées (en 24~h glissées), où les erreurs seront alors réduites par rapport à une série à pas de temps de 6~h.
+As sub-daily precipitation time series are usually available on a shorter period than traditional daily time steps, the first assessment consists in assessing the loss of performance resulting from a reduction a 47~years archive (1961 to 2008) to 25~years (1982 to 2007).
+This change is assessed with the original method, without STW.
 
-Nous ne disposons pas de séries temporelles sur des bassins à ces pas de temps infrajournalier, ni de stations automatiques suffisamment proches pour être regroupées.
-Nous travaillons donc sur les séries issues de 6 stations automatiques, à savoir Ulrichen, Zermatt, Visp, Montana, Sion et Aigle.
-La station du col du Grand-Saint-Bernard n'est pas intégrée à l'étude en raison de forts doutes émis par Jean-Michel Fallot (Université de Lausanne) sur l'homogénéité de ces données.
-
-Les situations cibles et leurs valeurs de précipitations observées (utilisées pour la validation) ne changent pas, puisque nous effectuons toujours la prévision pour une période fixe de la journée cible (6-30~h), comme précédemment.
-Ce sont les situations candidates qui, elles, deviennent 4~fois plus nombreuses (Figure \ref{fig:Illustration_fenetre_glissante}).
-
-La logique voudrait a priori que nous ne retenions qu'une tranche horaire, la meilleure, par date candidate.
-C'est-à-dire, si pour la date cible du 15 novembre 2006 (0-24~h), la meilleure analogue est le 5 décembre 1988 (12-36~h), alors, très certainement les périodes les plus proches (5 décembre 6-30~h et 18-42~h) sont aussi des analogues, certes inférieures en qualité, mais acceptables.
-La question se pose alors de les prendre ou de les rejeter.
-Une exclusion des mêmes dates a été testée de deux manières différentes:
-\begin{itemize}
-	\item par exclusion des moins bonnes analogues dans une période de $\pm$ 24~h;
-	\item par exclusion des moins bonnes analogues avec la même date.
-\end{itemize}
-Après plusieurs essais, il s'est avéré que n'imposer aucune restriction menait à de meilleures compétences, et ceci de manière significative et récurrente.
-Dans la suite de cette analyse, aucune de ces contraintes ne sera donc imposée.
-
-\section{Conséquences de la réduction de l'archive sur la compétence}
-
-La première étape consiste à évaluer la perte de compétence due à la simple réduction en durée de l'archive pour la méthode standard (donc avec des analogues 0-24~h fixes) lorsque l'on passe de 47~ans (1961-2008) à 25~ans (1982-2007).
-Les paramètres sont calibrés pour les méthodes R1 et R2 (Tables \ref{tab:fenetre_glissante:Resultats_R1_originaux} et \ref{tab:fenetre_glissante:Resultats_R2_originaux}) sur l'archive originale et sont conservés pour la suite des calculs.
+Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
+The AM parameters were calibrated on the original archive (Tables \ref{table:method_2Z} and \ref{table:method_2Z-2MI}) and will be used thereafter.
 
 \begin{table}[htb]
-	\caption{Paramètres retenus pour l'analogie sur le géopotentiel à 500~hPa et 1000~hPa, et compétence de la méthode standard R1 sur l'archive complète.}
+	\caption{Calibrated parameters (spatial windows and number of analogues) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) and skill score (\%) of the method on the full archive.}
 	\begin{center}
-		\begin{tabular}{l c c c c c c }
+		\begin{tabular}{l c c c c }
 			\hline
-			\multirow{2}{*}{\textbf{Station}} & \textbf{Lon} & \textbf{Taille} & \textbf{Lat} & \textbf{Taille} & \multirow{2}{*}{\textbf{N$_{1}$}} & \textbf{CRPSS} \\ 
-			& \textbf{min} & \textbf{lon} & \textbf{min} & \textbf{lat} & & \textbf{(\%)} \\ 
+			\textbf{Station} & \textbf{Longitudes} & \textbf{Latitudes} & \textbf{N$_{1}$} & \textbf{CRPSS} \\
 			\hline
-			Ulrichen & 0 & 17.5 & 42.5 & 5 & 40 & 30.73 \\ \hline
-			Zermatt & 0 & 20 & 37.5 & 12.5 & 35 & 23.87 \\ \hline
-			Visp & -2.5 & 22.5 & 40 & 7.5 & 30 & 25.11 \\ \hline
-			Montana & -2.5 & 20 & 40 & 7.5 & 40 & 32.55 \\ \hline
-			Sion & -2.5 & 20 & 40 & 7.5 & 40 & 26.23 \\ \hline
-			Aigle & -5 & 22.5 & 40 & 10 & 50 & 30.59 \\ \hline
+			Ulrichen & 0 $\rightarrow$ 17.5 & 42.5 $\rightarrow$ 47.5 & 40 & 30.73 \\
+			Zermatt & 0 $\rightarrow$ 20 & 37.5 $\rightarrow$ 50 & 35 & 23.87 \\
+			Visp & -2.5 $\rightarrow$ 20 & 40 $\rightarrow$ 47.5 & 30 & 25.11 \\
+			Montana & -2.5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 47.5 & 40 & 32.55 \\
+			Sion & -2.5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 47.5 & 40 & 26.23 \\
+			Aigle & -5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 50 & 50 & 30.59 \\ 
+			\hline
 		\end{tabular}
 	\end{center}
-	\label{tab:fenetre_glissante:Resultats_R1_originaux}
+	\label{table:params_2Z}
 \end{table}
@@
 \begin{table}[htb]
-	\caption{Paramètres pour l'humidité et compétence de la méthode standard R2 sur l'archive complète.
-Les paramètres de circulation de la Table \ref{tab:fenetre_glissante:Resultats_R1_originaux} sont également valables pour cette méthode, exception faite du nombre d'analogues du premier niveau d'analogie dont les nouvelles valeurs sont données dans la 6ieme colonne du présent tableau (N$_{1}$).
-La 7ieme colonne (N$_{2}$) est ici le nombre d'analogues du deuxième niveau.}
+	\caption{Parameters of the moisture variables from the 2Z-2MI method and the corresponding skill score (\%) on the complete archive.
+The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z}, except the number of analogues of the first analogy level (N$_{1}$), which are here different.
+The $5^{th}$ column is the number of analogues for the second level (N$_{2}$).}
 	\begin{center}
-		\begin{tabular}{l c c c c c c c }
+		\begin{tabular}{l c c c c c }
 			\hline
-			\multirow{2}{*}{\textbf{Station}} & \textbf{Lon} & \textbf{Taille} & \textbf{Lat} & \textbf{Taille} & \multirow{2}{*}{\textbf{N$_{1}$}} & \multirow{2}{*}{\textbf{N$_{2}$}} & \textbf{CRPSS} \\ 
-			& \textbf{min} & \textbf{lon} & \textbf{min} & \textbf{lat} & & & \textbf{(\%)} \\ 
+			\textbf{Station} & \textbf{Longitudes} & \textbf{Latitudes} & \textbf{N$_{1}$} & \textbf{N$_{2}$} & \textbf{CRPSS} \\
 			\hline
-			Ulrichen & 5 & 5 & 45 & 2.5 & 60 & 25 & 34.31 \\ \hline
-			Zermatt & 5 & 5 & 45 & 2.5 & 55 & 25 & 28.28 \\ \hline
-			Vis & 5 & 5 & 45 & 2.5 & 45 & 25 & 28.85 \\ \hline
-			Montana & 5 & 2.5 & 45 & 2.5 & 55 & 30 & 36.11 \\ \hline
-			Sion & 5 & 5 & 45 & 2.5 & 90 & 30 & 31.16 \\ \hline
-			Aigle & 7.5 & 0 & 45 & 2.5 & 100 & 35 & 35.82 \\ \hline
+			Ulrichen & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 60 & 25 & 34.31 \\
+			Zermatt & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 55 & 25 & 28.28 \\
+			Visp & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 45 & 25 & 28.85 \\
+			Montana & 5 $\rightarrow$ 7.5 & 45 $\rightarrow$ 47.5 & 55 & 30 & 36.11 \\
+			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 90 & 30 & 31.16 \\
+			Aigle & 7.5 $\rightarrow$ 7.5 & 45 $\rightarrow$ 47.5 & 100 & 35 & 35.82 \\ 
+			\hline
 		\end{tabular}
 	\end{center}
-	\label{tab:fenetre_glissante:Resultats_R2_originaux}
+	\label{table:params_2Z-2MI}
 \end{table}
@@
 \begin{table}[htb]
-	\caption{Influence de la réduction de l'archive sur la compétence en CRPS.
-Les résultats sont présentés pour les deux méthodes R1 et R2, et les différences sont exprimées en valeur absolue, ainsi que relativement au score de la période 1961-2008.}
+	\caption{Influence of the archive reduction on the CRPSS. CRPSS values are provided for both considered methods and the differences are expressed in absolute value.}
 	\begin{center}
-		\begin{tabular}{l r r r r r r r r}
+		\begin{tabular}{l c c c c }
 			\hline
-			\multirow{3}{*}{\textbf{Station}} & \multicolumn{ 4}{c}{\textbf{CRPSS (\%) R1}} & \multicolumn{ 4}{c}{\textbf{CRPSS (\%) R2}} \\
-			& \multicolumn{ 2}{c}{\textbf{périodes}} & \multirow{2}{*}{\textbf{$\Delta$}} & \multirow{2}{*}{\textbf{Gain}} & \multicolumn{ 2}{c}{\textbf{périodes}} & \multirow{2}{*}{\textbf{$\Delta$}} & \multirow{2}{*}{\textbf{Gain}} \\
-			& \multicolumn{1}{c}{\textbf{61-08}} & \multicolumn{1}{c}{\textbf{82-07}} &  &  & \textbf{61-08} & \textbf{82-07} &  &  \\ 
+			\multirow{2}{*}{\textbf{Station}} & \multicolumn{2}{c}{\textbf{2Z}} & \multicolumn{2}{c}{\textbf{2Z-2MI}} \\
+			& \textbf{82-07} & \textbf{$\Delta$} & \textbf{82-07} & \textbf{$\Delta$} \\ 
 			\hline
-			Ulrichen & 30.73 & 29.37 & -1.36 & \textbf{-4.42} & 34.31 & 33.24 & -1.08 & \textbf{-3.13} \\ \hline
-			Zermatt & 23.87 & 22.20 & -1.67 & \textbf{-7.01} & 28.28 & 26.95 & -1.32 & \textbf{-4.68} \\ \hline
-			Visp & 25.11 & 23.23 & -1.89 & \textbf{-7.51} & 28.85 & 27.77 & -1.08 & \textbf{-3.74} \\ \hline
-			Montana & 32.55 & 30.79 & -1.76 & \textbf{-5.42} & 36.11 & 34.77 & -1.34 & \textbf{-3.71} \\ \hline
-			Sion & 26.23 & 24.78 & -1.45 & \textbf{-5.52} & 31.16 & 29.36 & -1.80 & \textbf{-5.77} \\ \hline
-			Aigle & 30.59 & 30.57 & -0.01 & \textbf{-0.05} & 35.82 & 35.95 & 0.13 & \textbf{0.35} \\ \hline
+			Ulrichen & 29.37 & -1.36 & 33.24 & -1.08 \\
+			Zermatt & 22.20 & -1.67 & 26.95 & -1.32 \\
+			Visp & 23.23 & -1.89 & 27.77 & -1.08 \\
+			Montana & 30.79 & -1.76 & 34.77 & -1.34 \\
+			Sion & 24.78 & -1.45 & 29.36 & -1.80 \\
+			Aigle & 30.57 & -0.01 & 35.95 & 0.13 \\ 
+			\hline
 		\end{tabular}
 	\end{center}
-	\label{tab:fenetre_glissante:Pertes_CRPSS}
+	\label{table:loss_reduction}
 \end{table}
 
-L'impact du changement de la période de l'archive est résumé dans la Table \ref{tab:fenetre_glissante:Pertes_CRPSS} pour les méthodes R1 et R2.
-Comme attendu, une perte de compétence peut être observée pour chaque station, excepté pour celle d'Aigle, qui semble relativement indifférente à ce changement.
-Cette perte est significative, avec un maximum pour la méthode R1 de -1.89 points à Visp, soit une perte de 7.51~\%, et pour la méthode R2 de -1.80 points à Sion, soit -5.77~\%.
-Malgré cette diminution, les scores restent acceptables et constitueront la référence en fenêtre d'analogie fixe (0-24~h).
+The impact of the change in the archive length is summarized in Table \ref{table:loss_reduction} for both 2Z and 2Z-2MI methods.
+As expected, a loss of performance can be observed for each station, except for that of Aigle, which seems relatively indifferent to this change.
+This loss is globally significant, with up to -1.89 points for Visp and the 2Z method.
 

### 2015-12-14 Moving temporal window - HESS/template.tex
Improving figures.

@@
 
-\begin{figure*}[htb]
+\begin{figure}[htb]
 	\begin{center}
-		\includegraphics[width=14cm]{figures/Illustration_fenetre_glissante.pdf}
+		\includegraphics[width=8.3cm]{figures/illustration_moving_window.pdf}
 	\end{center}
@@
 	\label{fig:principle}
-\end{figure*}
+\end{figure}
 
@@
 
-\section{Influence de la fenêtre glissante sur les critères d'analogie}
+\section{Influence on the analogy criteria}
 
-\subsection{Changements du critère du premier niveau d'analogie}
+\subsection{Changes in the atmospheric circulation analogy}
 
-La recherche d'analogues sur les champs de géopotentiel de la méthode R1 a donc à présent 4 fois plus de candidats possibles qu'auparavant, ce qui permet évidemment de trouver de meilleures analogues.
+When searching for analogues on the geopotential heights, as in the 2Z method, there are now 4 times more candidates than before, which obviously allows to find better matches.
 
@@
 	\begin{center}
-		\includegraphics[width=15cm]{figures/Graphique_fenetre_glissante_chmts_S1_analogues.pdf}
+		\includegraphics[width=15cm]{figures/changes_S1_analogues.png}
 	\end{center}
-	\caption{Changements dans les distributions du critère S1 de certaines analogues (la 1iere, la 5ieme, la 20ieme et la 40ieme), à la station d'Ulrichen, dû à la fenêtre temporelle glissante.}
-	\label{fig:Graphique_fenetre_glissante_chmts_S1_analogues}
+	\caption{Changes in the S1 criteria distributions of the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogue ranks for the Ulrichen station, due to the STW.}
+	\label{fig:changes_S1_analogues}
 \end{figure*}
 
-La Figure \ref{fig:Graphique_fenetre_glissante_chmts_S1_analogues} présente les changements dans les distributions du critère S1 pour la 1iere, la 5ieme, la 20ieme et la 40ieme analogue à la station d'Ulrichen, avec une période cible de précipitations correspondant à celle d'origine, soit centrée sur 18~h~UTC (de 6~h~UTC à 6~h~UTC le lendemain).
-Les formes des distributions de l'approche classique et de la fenêtre temporelle glissante sont semblables, mais les valeurs du critère d'analogie sont réduites, donc meilleures.
-Une augmentation de la différence entre fenêtre fixe et fenêtre glissante de la première à la dernière analogue est identifiable, ce qui signifie que nous améliorons davantage les dernières analogues.
-Ce dernier effet est dû à l'accumulation des améliorations apportées par les nouvelles analogues dans la sélection.
+Figure \ref{fig:changes_S1_analogues} presents the changes in the distributions of the S1 criterion for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogues for the Ulrichen station on the whole calibration period, due to introduction of the STW.
+The precipitation target remains at before, that is centered on 18~h~UTC (6~h~UTC to 6~h~UTC the next day).
+The shapes of the distributions of the conventional approach and the STW are similar, but the values of the analogy criteria are now reduced, therefore better.
+An increase in the difference between a fixed window and a sliding window is identifiable, which means that the last analogues are further improved.
+The latter effect is due to the accumulation of improvements brought by the new analogue situations in the selection.
 
@@
 		\begin{array}{c}
-		\includegraphics[width=8cm]{figures/Graphique_fenetre_glissante_chmts_S1_val.pdf} \\
-		\includegraphics[width=8cm]{figures/Graphique_fenetre_glissante_chmts_S1_gain.pdf}
+		\includegraphics[width=8.3cm]{figures/changes_S1_value.pdf} \\
+		\includegraphics[width=8.3cm]{figures/changes_S1_gain.pdf}
 		\end{array}$
 	\end{center}
-	\caption{Synthèse du gain sur le critère S1 à la station d'Ulrichen, pour les différentes analogues, dû à la fenêtre temporelle glissante.
-(gauche) Quantiles de la distribution des valeurs de S1 avec (06h) et sans (24h) la fenêtre glissante.
-(droite) Quantiles des gains sur le critère S1 par l'utilisation de la fenêtre glissante.}
-	\label{fig:Graphique_fenetre_glissante_chmts_S1}
+	\caption{Synthesis of the changes in the S1 criterion, due to the STW, for the Ulrichen station, depending on the ranks of the analogue.
+(top) Quantiles of the S1 distributions with (06h) and without (24h) the sliding window.
+(bottom) Quantiles of the relative improvements of the S1 criteria when using the sliding window.}
+	\label{fig:changes_S1}
 \end{figure}
 
-Ces gains sont synthétisés dans la Figure \ref{fig:Graphique_fenetre_glissante_chmts_S1}, qui illustre les valeurs, pour S1, des quantiles pour toutes les analogues avec et sans la fenêtre glissante, ainsi que la distribution des gains réalisés pour l'ensemble des dates.
-Cela confirme que tous les quantiles semblent réduits de manière semblable (les distributions de S1 conservent leur forme) et que ce gain augmente constamment de la première à la dernière analogue (Figure \ref{fig:Graphique_fenetre_glissante_chmts_S1} gauche).
+Ces gains sont synthétisés dans la Figure \ref{fig:changes_S1}, qui illustre les valeurs, pour S1, des quantiles pour toutes les analogues avec et sans la fenêtre glissante, ainsi que la distribution des gains réalisés pour l'ensemble des dates.
+Cela confirme que tous les quantiles semblent réduits de manière semblable (les distributions de S1 conservent leur forme) et que ce gain augmente constamment de la première à la dernière analogue (Figure \ref{fig:changes_S1} gauche).
 
-Les statistiques des gains pour chaque date (Figure \ref{fig:Graphique_fenetre_glissante_chmts_S1} droite) présentent une médiane de la réduction qui démarre approximativement à 5~\% pour les premières analogues et termine à plus de 10~\% pour les dernières.
+Les statistiques des gains pour chaque date (Figure \ref{fig:changes_S1} droite) présentent une médiane de la réduction qui démarre approximativement à 5~\% pour les premières analogues et termine à plus de 10~\% pour les dernières.
 Cette tendance à l'augmentation du gain sur le critère S1 avec le rang de l'analogue peut être expliquée par le fait que chaque gain effectué sur les premières analogues se répercute sur les suivantes.
@@
 	\begin{center}
-		\includegraphics[width=12cm]{figures/Graphique_fenetre_glissante_chmts_S1_seuils_precip.pdf}
+		\includegraphics[width=8.3cm]{figures/changes_S1_precip_threshold.pdf}
 	\end{center}
@@
 		\begin{array}{c}
-		\includegraphics[width=8cm]{figures/Graphique_fenetre_glissante_chmts_S1_saisons_val.pdf} \\
-		\includegraphics[width=6cm]{figures/Graphique_fenetre_glissante_chmts_S1_saisons_gain.pdf}
+		\includegraphics[width=8.3cm]{figures/Graphique_fenetre_glissante_chmts_S1_saisons_val.pdf} \\
+		\includegraphics[width=6.5cm]{figures/Graphique_fenetre_glissante_chmts_S1_saisons_gain.pdf}
 		\end{array}$
@@
 		\begin{array}{c}
-		\includegraphics[width=8cm]{figures/Graphique_fenetre_glissante_chmts_RMSE_val.pdf} \\
-		\includegraphics[width=8cm]{figures/Graphique_fenetre_glissante_chmts_RMSE_gain.pdf}
+		\includegraphics[width=8.3cm]{figures/Graphique_fenetre_glissante_chmts_RMSE_val.pdf} \\
+		\includegraphics[width=8.3cm]{figures/Graphique_fenetre_glissante_chmts_RMSE_gain.pdf}
 		\end{array}$

### 2015-12-14 Moving temporal window - HESS/template.tex
Addition of the disaggregation figure.

@@
 La moyenne mobile est certainement la répartition la plus simple que nous pouvons effectuer.
-Elle consiste à distribuer les précipitations journalières concernées de manière proportionnelle dans les différentes tranches de la série 24~heures glissée (Figure \ref{fig:Illustration_series_6h_moyennes_mobiles}).
+Elle consiste à distribuer les précipitations journalières concernées de manière proportionnelle dans les différentes tranches de la série 24~heures glissée (Figure \ref{fig:illustration_disaggregation}).
 Les résultats présentés dans la Table \ref{tab:fenetre_glissante:Resultats_moyenne_mobile} montrent clairement qu'une telle archive ne présente aucun intérêt, puisque les performances sont même inférieures à la méthode classique sans fenêtre temporelle glissante (Table \ref{tab:fenetre_glissante:Gains_CRPSS}).
@@
 	\begin{center}
-		\includegraphics[width=12cm]{figures/Illustration_series_6h_moyennes_mobiles.pdf}
+		\includegraphics[width=12cm]{figures/illustration_disaggregation.pdf}
 	\end{center}
 	\caption{Illustration de la création de séries de cumuls sur 24h glissés par moyenne mobile.}
-	\label{fig:Illustration_series_6h_moyennes_mobiles}
+	\label{fig:illustration_disaggregation}
 \end{figure}

### 2015-12-15 Moving temporal window - HESS/template.tex
Writing the Moving temporal window.

@@
 The time series (on the period 1982-2007) come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle.
+The results will often be presented arbitrarily for the Ulrichen station, but the results are exactly the same for all stations.
 
@@
 \begin{figure}[htb]
-	\begin{center}$
-		\begin{array}{c}
-		\includegraphics[width=8.3cm]{figures/changes_S1_value.pdf} \\
+	\begin{center}
+		\includegraphics[width=8.2cm]{figures/changes_S1_value.pdf} \\
 		\includegraphics[width=8.3cm]{figures/changes_S1_gain.pdf}
-		\end{array}$
 	\end{center}
-	\caption{Synthesis of the changes in the S1 criterion, due to the STW, for the Ulrichen station, depending on the ranks of the analogue.
+	\caption{Synthesis of the changes in the mean S1 criteria, due to the STW, for the Ulrichen station, depending on the ranks of the analogue.
 (top) Quantiles of the S1 distributions with (06h) and without (24h) the sliding window.
@@
 
-Ces gains sont synthétisés dans la Figure \ref{fig:changes_S1}, qui illustre les valeurs, pour S1, des quantiles pour toutes les analogues avec et sans la fenêtre glissante, ainsi que la distribution des gains réalisés pour l'ensemble des dates.
-Cela confirme que tous les quantiles semblent réduits de manière semblable (les distributions de S1 conservent leur forme) et que ce gain augmente constamment de la première à la dernière analogue (Figure \ref{fig:changes_S1} gauche).
+The improvements of the S1 criteria are summarized in Figure \ref{fig:changes_S1}, which shows (top) quantiles of the S1 criteria according to the analogue rank for the conventional method and the STW, and (bottom) quantiles of the relative reduction.
+This confirms that all quantile seem similarly reduced (S1 distributions keep their shape), and that this improvement is constantly increasing from the first to the last analogue (Figure \ref{fig:changes_S1} bottom).
 
-Les statistiques des gains pour chaque date (Figure \ref{fig:changes_S1} droite) présentent une médiane de la réduction qui démarre approximativement à 5~\% pour les premières analogues et termine à plus de 10~\% pour les dernières.
-Cette tendance à l'augmentation du gain sur le critère S1 avec le rang de l'analogue peut être expliquée par le fait que chaque gain effectué sur les premières analogues se répercute sur les suivantes.
-Inversement, le gain maximal décroît de 50~\% à 25~\%.
-Le gain minimal part de 0 pour atteindre une valeur située entre 2~\% et 3~\%, signifiant que tous les critères ont été améliorés.
-Les dates sélectionnées précédemment étant toujours disponibles, le critère S1 ne peut en effet que s'améliorer ou rester identique, mais en aucun cas se détériorer.
-Toutes les autres stations présentent une amélioration du critère S1 très proche, tant pour la forme des distributions que pour leur amplitude.
+The median of the S1 values reduction (Figure \ref{fig:changes_S1} bottom) starts approximately at 5~\% for the first analogue and reaches more than 10~\% for the last.
+This increasing trend with the analogue rank can be explained by the accumulation of better analogues in the distribution.
+The minimum improvement starts from 0 and reaches 2-3\%, meaning that the criteria has been improved for all analogue ranks of the distribution end.
+All other stations have a similar improvement of the S1 criteria, both in terms of distribution shape and amplitude.
 
-\subsection{Influence du dynamisme de la situation atmosphérique}
-\label{sec:ameliorations:fenetre:S1_pluie}
+\subsection{Influence of the weather situation}
+\label{sec:influence_precip}
 
-Nous pouvons supposer que des circulations peu dynamiques, telles que les fréquentes situations anticycloniques, ne seront pas radicalement améliorées par l'approche de la fenêtre temporelle glissante.
-À l'opposé, les situations dynamiques, telles que le passage d'une perturbation, ont une évolution temporelle bien marquée.
-En effet, la position des centres actifs et des courants évoluent de manière significative durant une journée.
-Nous pouvons donc nous attendre à améliorer ces journées-ci en autorisant la fenêtre d'analogie à glisser pour mieux correspondre à la situation cible.
+It can be assumed that the atmospheric conditions with a low dynamism, such as the frequent anticyclonic situations, will not be radically improved by the introduction of the STW.
+Conversely, dynamic situations, such as weather disturbances, have a well marked temporal evolution.
+Indeed, the position of the driving elements such as the low-pressure area and the fronts change significantly during a day.
+We can therefore expect to improve particularly these situations with a higher dynamism when introducing a STW, as we may find better matches to the target situation.
 
-Nous allons chercher à vérifier cette assertion, mais nous ne pouvons pas aisément quantifier le dynamisme de la circulation atmosphérique d'une journée.
-Nous faisons donc l'hypothèse que plus un jour est pluvieux, plus la situation est dynamique.
-Les résultats de cette approche sont synthétisés dans la Figure \ref{fig:Graphique_fenetre_glissante_chmts_S1_seuils_precip} par les médianes de la réduction du critère S1 pour les jours avec une pluviométrie comprise entre deux seuils.
-Le nombre d'analogues étant réduit, les courbes ne sont pas aussi lisses que lors des analyses précédentes.
-Il en ressort néanmoins que le gain tend à augmenter pour les jours à plus forte pluviométrie.
-Cette observation est valable pour toutes nos stations et cela confirme notre intuition.
+The dynamism of a given atmospheric condition cannot be easily quantified.
+We thus consider here the basic assumption that the more a day is rainy, the more dynamic the situation is.
+The results of this analysis are summarized in Figure \ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for days with precipitation between two thresholds.
+The number of analogues being reduced, the curves are not as smooth as in previous analyzes.
+It is nevertheless clear that the improvement tends to increase on days with higher precipitation.
+This is true for all our stations and confirms our intuition.
 
@@
 	\end{center}
-	\caption{Distribution des gains sur la médiane du critère S1, dus à la fenêtre temporelle glissante, en fonction de seuils de précipitations à la station d'Ulrichen.}
-	\label{fig:Graphique_fenetre_glissante_chmts_S1_seuils_precip}
+	\caption{Distribution of the median improvements of the S1 criteria, due to the STW, depending on precipitation thresholds at the Ulrichen station.}
+	\label{fig:changes_S1_precip_threshold}
 \end{figure}
 
-\subsection{Effet saisonnier}
-\label{sec:ameliorations:fenetre:S1_saisons}
+\subsection{Seasonal effect}
+\label{sec:seasonal_effect}
 
-La dynamique atmosphérique varie fortement d'une saison à l'autre, ce qui rejaillit sur les performances de la méthode des analogues, généralement moindres entre juin et août \citep{Bliefernicht2010}.
-Il fait donc sens de vérifier l'effet de l'introduction de la fenêtre temporelle glissante de manière distincte par saison.
+Atmospheric dynamics varies greatly from one season to another, which reflects on the performance of the AM that is generally lower between June and August \citep{Bliefernicht2010}.
+It therefore makes sense to verify the effect of the STW separately per season.
 
 \begin{figure}[htb]
-	\begin{center}$
-		\begin{array}{c}
-		\includegraphics[width=8.3cm]{figures/Graphique_fenetre_glissante_chmts_S1_saisons_val.pdf} \\
-		\includegraphics[width=6.5cm]{figures/Graphique_fenetre_glissante_chmts_S1_saisons_gain.pdf}
-		\end{array}$
+	\begin{center}
+		\includegraphics[width=7cm]{figures/changes_S1_seasons.pdf}
 	\end{center}
-	\caption{Effet saisonnier sur le critère S1 original pour la station d'Ulrichen et son gain dû à la fenêtre temporelle glissante.
-DJF: hiver, MAM: printemps, JJA: été, SON: automne.
-(gauche) Quantiles de la distribution des valeurs de S1 pour les différentes saisons avec la fenêtre temporelle originale de 24~h.
-(droite) Médianes des gains sur le critère S1 par l'utilisation de la fenêtre glissante pour les différentes saisons.}
-	\label{fig:Graphique_fenetre_glissante_chmts_S1_saisons}
+	\caption{Seasonal effect on the median reduction of the S1 criteria for the Ulrichen station due to the sliding time window. DJF: winter, MAM: spring, JJA: summer SON: fall.}
+	\label{fig:changes_S1_seasons}
 \end{figure}
@@
 \begin{figure}[htb]
-	\includegraphics[width=8.3cm]{figures/Graphique_fenetre_glissante_heures_fct_saison.pdf}
-	\caption{Répartition des tranches horaires dans les dates analogues en fonction de la saison pour la station d'Ulrichen.}
-	\label{fig:Graphique_fenetre_glissante_heures_fct_saison}
+	\includegraphics[width=8.3cm]{figures/hours_selection_per_season.pdf}
+	\caption{Distribution of the predictors hours in the selected analogue dates depending on the season, for the Ulrichen station.}
+	\label{fig:hours_selection_per_season}
 \end{figure}
 
-Un effet saisonnier peut être observé autant sur les distributions des critères que sur leurs gains (Figure \ref{fig:Graphique_fenetre_glissante_chmts_S1_saisons}).
-Les gains sont plus importants pour l'hiver que pour l'été.
-Une hypothèse est que les effets diurnes des mois d'été ont une influence notable sur la circulation atmosphérique, du moins dans les basses couches.
-Cet effet est donc calé sur le cycle journalier et nous trouvons déjà de bonnes analogues aux mêmes heures.
+A seasonal effect can be observed on the reduction of the S1 criteria due to the STW (Figure \ref{fig:changes_S1_seasons}).
+The improvements are greater for winter than summer.
+One hypothesis is that the diurnal effects of the summer months have an influence on the atmospheric circulation, at least in the lower layers.
+This effect is based on the daily cycle and good analogues for the same hours are already selected.
 
-Cette hypothèse a été vérifiée et est confirmée par la Figure \ref{fig:Graphique_fenetre_glissante_heures_fct_saison} qui démontre que le choix des différentes tranches horaires pour les mois d'hiver est relativement équilibré, ce qui change la sélection de 75~\% des dates analogues par rapport au 0-24~h initial, augmentant ainsi l'amélioration du critère S1.
+An analysis of the selected hours for the geopotential predictor seems to confirm this assumption (Figure \ref{fig:hours_selection_per_season}).
+It was found that the new choice of the temporal window in winter, when using the STW approach, is well balanced between the 4 options.
+This means a change of 75\% of the analogues selection compared to the conventional approach, which improves the circulation analogy.
 
-Au contraire, les mois d'été ont une préférence pour la tranche horaire initiale (hgt 500 24h \& hgt 1000 12h), dû aux effets diurnes plus marqués, ce qui diminue le potentiel d'amélioration des critères.
-Les autres saisons se situent entre ces deux extrêmes, de manière cohérente avec leurs gains observés (Figure \ref{fig:Graphique_fenetre_glissante_chmts_S1_saisons}).
-Cet effet saisonnier a pu être observé pour chaque station de manière très similaire et généralement encore plus marquée que pour Ulrichen.
+On the contrary, the summer months have a preference for the initial temporal window (Z500 24h \& Z1000 12h), due to more pronounced diurnal effects which reduces the potential for improvement of the criteria.
+Other seasons are between these two extremes, which is consistent with their respective improvements.
+This seasonal effect was observed for each station in a very similar way, and generally even with a larger amplitude than for Ulrichen.
 

### 2015-12-15 Moving temporal window - HESS/template.tex
Writing the Moving temporal window.

@@
 
-\runningtitle{Moving Temporal Window in the AM}
+\runningtitle{Finding Better Analogue Situations at a Sub-Daily Time Step}
 
@@
 			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 90 & 30 & 31.16 \\
-			Aigle & 7.5 $\rightarrow$ 7.5 & 45 $\rightarrow$ 47.5 & 100 & 35 & 35.82 \\ 
+			Aigle & 7.5 & 45 $\rightarrow$ 47.5 & 100 & 35 & 35.82 \\ 
 			\hline
@@
 	\end{center}
-	\caption{Synthesis of the changes in the mean S1 criteria, due to the STW, for the Ulrichen station, depending on the ranks of the analogue.
-(top) Quantiles of the S1 distributions with (06h) and without (24h) the sliding window.
+	\caption{Synthesis of the changes in the S1 criteria, due to the STW, for the Ulrichen station, depending on the ranks of the analogue.
+(top) Quantiles of the S1 distributions with and without the sliding window.
 (bottom) Quantiles of the relative improvements of the S1 criteria when using the sliding window.}
@@
 
-\subsection{Changements du critère du second niveau d'analogie}
+\subsection{Changes in the moisture analogy}
 
-Lorsque nous considérons le second niveau d'analogie de la méthode R2, les situations candidates retenues ne sont pas plus nombreuses, mais les dates peuvent avoir changé.
-Ainsi, une réduction, mais également une augmentation du critère RMSE sont possibles.
-La Figure \ref{fig:Graphique_fenetre_glissante_chmts_RMSE}, pour la station d'Ulrichen, présente une très légère amélioration du critère de manière globale.
-Contrairement au critère S1, les quantiles des gains du RMSE sont répartis de manière relativement symétrique autour de zéro, ce qui révèle l'occurrence de pertes.
-À nouveau, les résultats des autres stations sont proches, avec un gain médian à zéro pour les premières analogues et croissant par la suite, mais jamais négatif.
+When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the candidates situations are not more numerous, as we subsample in the previously $N_{1}$ selected analogues, but the dates may have changed.
+In contrast to earlier, both a reduction and an increase of the RMSE criterion values are possible.
+Figure \ref{fig:changes_RMSE} shows an almost insignificant improvement of the RMSE values.
+Unlike for the first level of analogy, the relative improvement of the RMSE values are distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
+Once again, the results for the other stations are similar.
 
 \begin{figure}[htb]
-	\begin{center}$
-		\begin{array}{c}
-		\includegraphics[width=8.3cm]{figures/Graphique_fenetre_glissante_chmts_RMSE_val.pdf} \\
-		\includegraphics[width=8.3cm]{figures/Graphique_fenetre_glissante_chmts_RMSE_gain.pdf}
-		\end{array}$
+	\begin{center}
+		\includegraphics[width=8.1cm]{figures/changes_RMSE_value.pdf} \\
+		\includegraphics[width=8.3cm]{figures/changes_RMSE_gain.pdf}
 	\end{center}
-	\caption{Synthèse des changements sur le critère RMSE à la station d'Ulrichen, pour les différentes analogues du second niveau d'analogie, dû à la fenêtre temporelle glissante.
-(gauche) Quantiles de la distribution des valeurs de RMSE avec (06h) et sans (24h) la fenêtre glissante.
-(droite) Quantiles des gains sur le critère RMSE par l'utilisation de la fenêtre glissante.}
-	\label{fig:Graphique_fenetre_glissante_chmts_RMSE}
+	\caption{Synthesis of the changes in the RMSE criteria, due to the STW, for the Ulrichen station, depending on the ranks of the analogue.
+(top) Quantiles of the RMSE distributions with and without the sliding window.
+(bottom) Quantiles of the relative improvements of the RMSE criteria when using the sliding window.}
+	\label{fig:changes_RMSE}
 \end{figure}
 
-\section{Conséquences sur les scores de performance}
+This result of a globally null improvement of the RMSE values does not mean that the 2Z-2MI method cannot be improved by the STW.
+It means that after the selection of the analogues situations in terms of the synoptic circulation, the new candidate dates do not allow to find better analogues in terms of moisture.
+However, the selected dates have changed in the first level of analogy, and thus also in the final selection, which can potentially improve the performance scores.
+
+\section{Impact on performance scores}
 
@@
 	\begin{center}
-		\begin{tabular}{l r r r r r r r r}
+		\begin{tabular}{l c c c c}
 			\hline
-			\multirow{3}{*}{\textbf{Station}} & \multicolumn{ 4}{c}{\textbf{CRPSS (\%) R1}} & \multicolumn{ 4}{c}{\textbf{CRPSS (\%) R2}} \\
-			& \multicolumn{ 2}{c}{\textbf{fenêtre temp}} & \multirow{2}{*}{\textbf{$\Delta$}} & \multirow{2}{*}{\textbf{Gain}} & \multicolumn{ 2}{c}{\textbf{fenêtre temp}} & \multirow{2}{*}{\textbf{$\Delta$}} & \multirow{2}{*}{\textbf{Gain}} \\
-			& \multicolumn{1}{c}{\textbf{std}} & \multicolumn{1}{c}{\textbf{gliss.}} &  &  & \textbf{std} & \textbf{gliss.} &  & \\ 
+			\multirow{2}{*}{\textbf{Station}} & \multicolumn{2}{c}{\textbf{2Z}} & \multicolumn{ 2}{c}{\textbf{2Z-2MI}} \\
+			& \textbf{STW} & \textbf{$\Delta$} & \textbf{STW} & \textbf{$\Delta$} \\
 			\hline
-			Ulrichen & 29.37 & 31.12 & 1.74 & \textbf{5.93} & 33.24 & 35.44 & 2.20 & \textbf{6.63} \\ \hline
-			Zermatt & 22.20 & 24.34 & 2.14 & \textbf{9.64} & 26.95 & 28.92 & 1.97 & \textbf{7.31} \\ \hline
-			Visp & 23.23 & 24.39 & 1.16 & \textbf{5.00} & 27.77 & 29.42 & 1.64 & \textbf{5.92} \\ \hline
-			Montana & 30.79 & 31.59 & 0.80 &\textbf{ 2.60} & 34.77 & 36.30 & 1.53 & \textbf{4.39} \\ \hline
-			Sion & 24.78 & 25.35 & 0.57 & \textbf{2.31} & 29.36 & 31.07 & 1.71 & \textbf{5.82} \\ \hline
-			Aigle & 30.57 & 31.78 & 1.21 & \textbf{3.95} & 35.95 & 38.11 & 2.16 & \textbf{6.00} \\ \hline
+			Ulrichen & 31.12 & 1.74 & 35.44 & 2.20 \\
+			Zermatt & 24.34 & 2.14 & 28.92 & 1.97 \\
+			Visp & 24.39 & 1.16 & 29.42 & 1.64 \\
+			Montana & 31.59 & 0.80 & 36.30 & 1.53 \\
+			Sion & 25.35 & 0.57 & 31.07 & 1.71 \\
+			Aigle & 31.78 & 1.21 & 38.11 & 2.16 \\ 
+			\hline
 		\end{tabular}
@@
 \begin{table}[htb]
-	\caption{Paramètres pour les champs de géopotentiel à 500~hPa et 1000~hPa et compétence de la méthode R1 après calibration pour la fenêtre temporelle glissante.}
+	\caption{Calibrated parameters (spatial windows and number of analogues) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) and skill score (\%) of the method with the STW approach.}
 	\begin{center}
-		\begin{tabular}{l c c c c c c c c }
+		\begin{tabular}{l c c c c c }
 			\hline
-			\multirow{2}{*}{\textbf{Station}} & \textbf{Lon} & \textbf{Taille} & \textbf{Lat} & \textbf{Taille} & \multirow{2}{*}{\textbf{N$_{1}$}} & \textbf{CRPSS} & \multirow{2}{*}{\textbf{$\Delta$}} & \textbf{Gain} \\
-			& \textbf{min} & \textbf{lon} & \textbf{min} & \textbf{lat} &  & \textbf{(\%)} & & \textbf{(\%)} \\ 
+			\textbf{Station} & \textbf{Longitudes} & \textbf{Latitudes} & \textbf{N$_{1}$} & \textbf{CRPSS} & \textbf{$\Delta$} \\
 			\hline
-			Ulrichen & 0 & 17.5 & 42.5 & 7.5 & 50 & 31.58 & 2.20 & \textbf{7.50} \\ \hline
-			Zermatt & 0 & 17.5 & 40 & 10 & 55 & 24.71 & 2.51 & \textbf{11.32} \\ \hline
-			Visp & -2.5 & 22.5 & 40 & 10 & 55 & 25.08 & 1.85 & \textbf{7.96} \\ \hline
-			Montana & -2.5 & 17.5 & 42.5 & 5 & 55 & 32.22 & 1.43 & \textbf{4.65} \\ \hline
-			Sion & -2.5 & 17.5 & 37.5 & 12.5 & 55 & 26.07 & 1.29 & \textbf{5.19} \\ \hline
-			Aigle & -2.5 & 17.5 & 40 & 10 & 75 & 32.21 & 1.64 & \textbf{5.36} \\ \hline
+			Ulrichen & 0 $\rightarrow$ 17.5 & 42.5 $\rightarrow$ 50 & 50 & 31.58 & 2.20 \\
+			Zermatt & 0 $\rightarrow$ 17.5 & 40 $\rightarrow$ 50 & 55 & 24.71 & 2.51 \\
+			Visp & -2.5 $\rightarrow$ 20 & 40 $\rightarrow$ 50 & 55 & 25.08 & 1.85 \\
+			Montana & -2.5 $\rightarrow$ 15 & 42.5 $\rightarrow$ 47.5 & 55 & 32.22 & 1.43 \\
+			Sion & -2.5 $\rightarrow$ 15 & 37.5 $\rightarrow$ 50 & 55 & 26.07 & 1.29 \\
+			Aigle & -2.5 $\rightarrow$ 15 & 40 $\rightarrow$ 50 & 75 & 32.21 & 1.64 \\
+			\hline
 		\end{tabular}
 	\end{center}
-	\label{tab:fenetre_glissante:Resultats_R1_recalibration_fen_gliss}
+	\label{table:params_2Z_new}
 \end{table}
@@
 \begin{table}[htb]
-	\caption{Paramètres pour l'humidité et compétence de la méthode R2 après calibration pour la fenêtre temporelle glissante.
-Le nombre d'analogues du premier niveau d'analogie est donné dans la 6ieme colonne (N$_{1}$) et celui du second niveau dans la 7ieme colonne (N$_{2}$).}
+	\caption{Parameters of the moisture variables from the 2Z-2MI method and the corresponding skill score (\%) with the STW approach.
+The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z_new}, except the number of analogues of the first analogy level (N$_{1}$), which are here different.
+The $5^{th}$ column is the number of analogues for the second level (N$_{2}$).}
 	\begin{center}
-		\begin{tabular}{l c c c c c c c c c }
+		\begin{tabular}{l c c c c c c }
 			\hline
-			\multirow{2}{*}{\textbf{Station}} & \textbf{Lon} & \textbf{Taille} & \textbf{Lat} & \textbf{Taille} & \multirow{2}{*}{\textbf{N$_{1}$}} & \multirow{2}{*}{\textbf{N$_{2}$}} & \textbf{CRPSS} &  \multirow{2}{*}{\textbf{$\Delta$}} & \textbf{Gain}\\
-			& \textbf{min} & \textbf{lon} & \textbf{min} & \textbf{lat} &  &  & \textbf{(\%)} & & \textbf{(\%)} \\ 
+			\textbf{Station} & \textbf{Longitudes} & \textbf{Latitudes} & \textbf{N$_{1}$} & \textbf{N$_{2}$} & \textbf{CRPSS} & \textbf{$\Delta$} \\
 			\hline
-			Ulrichen & 5 & 5 & 45 & 2.5 & 110 & 35 & 35.72 & 2.48 & \textbf{7.46} \\ \hline
-			Zermatt & 7.5 & 0 & 45 & 2.5 & 80 & 30 & 29.63 & 2.68 & \textbf{9.94} \\ \hline
-			Visp & 7.5 & 0 & 45 & 2.5 & 135 & 35 & 30.29 & 2.52 & \textbf{9.07} \\ \hline
-			Montana & 5 & 2.5 & 45 & 0 & 110 & 40 & 37.15 & 2.38 & \textbf{6.85} \\ \hline
-			Sion & 5 & 5 & 45 & 2.5 & 140 & 50 & 31.68 & 2.32 & \textbf{7.91} \\ \hline
-			Aigle & 5 & 2.5 & 45 & 0 & 135 & 45 & 38.50 & 2.55 & \textbf{7.10} \\ \hline
+			Ulrichen & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 110 & 35 & 35.72 & 2.48 \\
+			Zermatt & 7.5 & 45 $\rightarrow$ 47.5 & 80 & 30 & 29.63 & 2.68 \\
+			Visp & 7.5 & 45 $\rightarrow$ 47.5 & 135 & 35 & 30.29 & 2.52 \\
+			Montana & 5 $\rightarrow$ 7.5 & 45 & 110 & 40 & 37.15 & 2.38 \\
+			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 140 & 50 & 31.68 & 2.32 \\
+			Aigle & 5 $\rightarrow$ 7.5 & 45 & 135 & 45 & 38.50 & 2.55 \\ 
+			\hline
 		\end{tabular}
 	\end{center}
-	\label{tab:fenetre_glissante:Resultats_R2_recalibration_fen_gliss}
+	\label{table:params_2Z-2MI_new}
 \end{table}

### 2015-12-15 Moving temporal window - HESS/template.tex
Writing the Moving temporal window.

@@
 			\hline
-			\textbf{Station} & \textbf{Longitudes} & \textbf{Latitudes} & \textbf{N$_{1}$} & \textbf{CRPSS} \\
+			Station & Longitudes & Latitudes & N$_{1}$ & CRPSS \\
 			\hline
@@
 			\hline
-			\textbf{Station} & \textbf{Longitudes} & \textbf{Latitudes} & \textbf{N$_{1}$} & \textbf{N$_{2}$} & \textbf{CRPSS} \\
+			Station & Longitudes & Latitudes & N$_{1}$ & N$_{2}$ & CRPSS \\
 			\hline
@@
 			\hline
-			\multirow{2}{*}{\textbf{Station}} & \multicolumn{2}{c}{\textbf{2Z}} & \multicolumn{2}{c}{\textbf{2Z-2MI}} \\
-			& \textbf{82-07} & \textbf{$\Delta$} & \textbf{82-07} & \textbf{$\Delta$} \\ 
+			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
+			& 82-07 & $\Delta$ & 82-07 & $\Delta$ \\ 
 			\hline
@@
 
-Nous avons pu observer précédemment un gain systématique sur le critère d'analogie S1.
-Il nous reste donc à évaluer la conséquence de l'introduction de la fenêtre temporelle glissante sur les scores de performance de la nouvelle distribution de pluie prévue.
-Nous utilisons donc des séries temporelles de précipitations créées à cet effet.
-Celles-ci ont été établies par une moyenne mobile sur une durée de 24~h avec un pas de temps de 6~h.
-En conservant toujours les mêmes paramètres que précédemment (même domaine et même nombre d'analogues), ces valeurs sont attribuées à chaque date analogue.
-La série des dates cibles reste inchangée, puisque nous conservons la tranche horaire d'origine (6~h~UTC - 6~h~UTC le lendemain).
+A systematic improvement of the S1 values was previously observed.
+However, finding better analogue situations does not obligatory imply better forecast skills.
+Therefore, we have to assess the impact of the introduction of the sliding time window, and thus the selection of other analogue dates, on the performance scores.
+In order to perform this assessment, the 24~h-totals (moving average) at a 6-hourly time step were used (see section \ref{sec:data}).
+The target dates remain unchanged, since we keep the original time slot (6~h~UTC - 6~h~UTC the next day), and thus the performance scores can be directly compared with the former ones.
 
-Les CRPSS étant calculés sur la base de la même climatologie que précédemment, ils peuvent être comparés directement.
-Les gains en performance ainsi obtenus (Table \ref{tab:fenetre_glissante:Gains_CRPSS}) s'étalent de 2.31~\% à 9.31~\% pour le premier niveau d'analogie.
-Lorsque nous considérons le second niveau d'analogie, les gains sont globalement un peu supérieurs.
-Nous n'avons pas trouvé de relation entre l'amélioration du score et les gains du critère S1, ni avec la saison.
+The new performance scores are provided in Table \ref{table:CRPSS_STW}, along with the differences regarding the conventional method with the same archive length.
+The differences ranges from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.
+The introduction of the STW brings an improvement of the performance that is not very large, but that is nevertheless significant.
+Moreover, it requires no additional predictor.
+No relationship was found between the improvement of the score and the reduction of the S1 criteria, neither with the season.
 
 \begin{table}[htb]
-	\caption{Gain en compétence du CRPS sur les deux niveaux d'analogie dû à l'introduction de la fenêtre temporelle glissante.}
+	\caption{New CRPSS performance scores for both 2Z and 2Z-2MI methods obtained by the STW approach. The differences are expressed regarding the conventional method with the same archive length.}
 	\begin{center}
@@
 			\hline
-			\multirow{2}{*}{\textbf{Station}} & \multicolumn{2}{c}{\textbf{2Z}} & \multicolumn{ 2}{c}{\textbf{2Z-2MI}} \\
-			& \textbf{STW} & \textbf{$\Delta$} & \textbf{STW} & \textbf{$\Delta$} \\
+			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
+			& STW & $\Delta$ & STW & $\Delta$ \\
 			\hline
@@
 	\end{center}
-	\label{tab:fenetre_glissante:Gains_CRPSS}
+	\label{table:CRPSS_STW}
 \end{table}
 
-\subsection{Amélioration de différentes gammes de précipitations}
-\label{sec:ameliorations:fenetre:gammes_precip}
+\subsection{Improvement by precipitation threshold}
+\label{sec:improvement_CRPSS_precip_threshold}
+
+The S1 criteria was previously found to be improved to a greater extent for the most dynamic situations related with higher precipitation values (section \ref{sec:influence_precip}).
+The changes in terms of performance scores will now be assessed regarding precipitation thresholds.
+Figure \ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, other stations having the same behavior.
+
+The increasing positive trend of skill improvements regarding the precipitation threshold is significant and shows that the prediction of higher precipitation totals is further improved.
+Thus both the analogy criteria and the performance scores are improved to a greater extent for heavier precipitation events.
+On the contrary, the non-rainy days and small accumulations are not improved.
 
 \begin{figure}[htb]
-	\includegraphics[width=6cm]{figures/Graphique_fenetre_glissante_chmts_CRPS_seuils_precip.pdf}
-	\caption{Distribution des différences sur le score CRPSS dues à l'introduction de la fenêtre temporelle glissante en fonction de seuils de précipitations à la station d'Ulrichen.
-Les étoiles sont les moyennes des distributions.}
-	\label{fig:Graphique_fenetre_glissante_chmts_CRPS_seuils_precip}
+	\includegraphics[width=5cm]{figures/changes_CRPS_precip_threshold.pdf}
+	\caption{Differences of the CRPSS performance score, due to the introduction of the sliding time window, as a function of precipitation thresholds at the Ulrichen station.
+The stars represent averages.}
+	\label{fig:changes_CRPS_precip_threshold}
 \end{figure}
 
-Nous avions observé dans la section \ref{sec:ameliorations:fenetre:S1_pluie} une amélioration du critère S1 pour les situations plus dynamiques, soit avec des valeurs de précipitations supérieures.
-Nous allons à présent mettre en relation les gains en CRPSS et les cumuls précipités.
+\subsection{Recalibrating the parameters}
+\label{sec:recalibration}
 
-La Figure \ref{fig:Graphique_fenetre_glissante_chmts_CRPS_seuils_precip} synthétise ces gains pour la station d'Ulrichen, les autres stations se comportant de la même manière.
-Un étalement de la distribution avec l'augmentation du seuil de précipitations peut être observé.
-Cet effet s'explique en premier lieu par le fait que la valeur du CRPS est dépendante des quantités de précipitations des journées cibles.
-
-Un résultat plus intéressant est la tendance positive croissante de toute la distribution avec l'augmentation du seuil des précipitations.
-À partir du seuil de 10~mm, la moyenne et les quantiles du gain en CRPSS tendent à augmenter de manière significative.
-Il semble donc que nous améliorons les scores de performance des événements davantage pluvieux, en plus de leurs critères d'analogie.
-Le fait que les jours non pluvieux et les petits cumuls ne sont pas améliorés semble expliquer le gain peu probant lorsque nous considérons l'ensemble de la période.
-
-\subsection{Recalibration des paramètres}
-\label{sec:ameliorations:fenetre:recalibration}
-
-L'évaluation précédente du gain en score de performance a été établie avec les paramètres originaux.
-Nous pouvons néanmoins supposer que l'introduction de la fenêtre temporelle glissante modifie peut-être le choix optimal de la position et de la taille de la fenêtre spatiale idéale et change le nombre d'analogues comparativement à la méthode standard.
-La calibration a donc été effectuée à nouveau.
+The previous assessment of the performance improvement was established with the original parameters.
+However, one can assume that the introduction of the STW may change the optimum of some parameters.
+The calibration has then been performed again.
 
 \begin{table}[htb]
-	\caption{Calibrated parameters (spatial windows and number of analogues) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) and skill score (\%) of the method with the STW approach.}
+	\caption{Calibrated parameters (spatial windows and number of analogues) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) with the STW approach.}
 	\begin{center}
-		\begin{tabular}{l c c c c c }
+		\begin{tabular}{l c c c }
 			\hline
-			\textbf{Station} & \textbf{Longitudes} & \textbf{Latitudes} & \textbf{N$_{1}$} & \textbf{CRPSS} & \textbf{$\Delta$} \\
+			Station & Longitudes & Latitudes & N$_{1}$ \\
 			\hline
-			Ulrichen & 0 $\rightarrow$ 17.5 & 42.5 $\rightarrow$ 50 & 50 & 31.58 & 2.20 \\
-			Zermatt & 0 $\rightarrow$ 17.5 & 40 $\rightarrow$ 50 & 55 & 24.71 & 2.51 \\
-			Visp & -2.5 $\rightarrow$ 20 & 40 $\rightarrow$ 50 & 55 & 25.08 & 1.85 \\
-			Montana & -2.5 $\rightarrow$ 15 & 42.5 $\rightarrow$ 47.5 & 55 & 32.22 & 1.43 \\
-			Sion & -2.5 $\rightarrow$ 15 & 37.5 $\rightarrow$ 50 & 55 & 26.07 & 1.29 \\
-			Aigle & -2.5 $\rightarrow$ 15 & 40 $\rightarrow$ 50 & 75 & 32.21 & 1.64 \\
+			Ulrichen & 0 $\rightarrow$ 17.5 & 42.5 $\rightarrow$ 50 & 50 \\
+			Zermatt & 0 $\rightarrow$ 17.5 & 40 $\rightarrow$ 50 & 55 \\
+			Visp & -2.5 $\rightarrow$ 20 & 40 $\rightarrow$ 50 & 55 \\
+			Montana & -2.5 $\rightarrow$ 15 & 42.5 $\rightarrow$ 47.5 & 55 \\
+			Sion & -2.5 $\rightarrow$ 15 & 37.5 $\rightarrow$ 50 & 55 \\
+			Aigle & -2.5 $\rightarrow$ 15 & 40 $\rightarrow$ 50 & 75 \\
 			\hline
@@
 \begin{table}[htb]
-	\caption{Parameters of the moisture variables from the 2Z-2MI method and the corresponding skill score (\%) with the STW approach.
+	\caption{Parameters of the moisture variables from the 2Z-2MI method with the STW approach.
 The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z_new}, except the number of analogues of the first analogy level (N$_{1}$), which are here different.
@@
 	\begin{center}
-		\begin{tabular}{l c c c c c c }
+		\begin{tabular}{l c c c c }
 			\hline
-			\textbf{Station} & \textbf{Longitudes} & \textbf{Latitudes} & \textbf{N$_{1}$} & \textbf{N$_{2}$} & \textbf{CRPSS} & \textbf{$\Delta$} \\
+			Station & Longitudes & Latitudes & N$_{1}$ & N$_{2}$ \\
 			\hline
-			Ulrichen & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 110 & 35 & 35.72 & 2.48 \\
-			Zermatt & 7.5 & 45 $\rightarrow$ 47.5 & 80 & 30 & 29.63 & 2.68 \\
-			Visp & 7.5 & 45 $\rightarrow$ 47.5 & 135 & 35 & 30.29 & 2.52 \\
-			Montana & 5 $\rightarrow$ 7.5 & 45 & 110 & 40 & 37.15 & 2.38 \\
-			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 140 & 50 & 31.68 & 2.32 \\
-			Aigle & 5 $\rightarrow$ 7.5 & 45 & 135 & 45 & 38.50 & 2.55 \\ 
+			Ulrichen & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 110 & 35 \\
+			Zermatt & 7.5 & 45 $\rightarrow$ 47.5 & 80 & 30 \\
+			Visp & 7.5 & 45 $\rightarrow$ 47.5 & 135 & 35 \\
+			Montana & 5 $\rightarrow$ 7.5 & 45 & 110 & 40 \\
+			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 140 & 50 \\
+			Aigle & 5 $\rightarrow$ 7.5 & 45 & 135 & 45 \\ 
 			\hline
@@
 
-Des changements dans les paramètres optimaux des méthodes R1 (Table \ref{tab:fenetre_glissante:Resultats_R1_recalibration_fen_gliss}) et R2 (Table \ref{tab:fenetre_glissante:Resultats_R2_recalibration_fen_gliss}) peuvent être observés.
-Parmi ceux-ci, la dimension ouest-est des fenêtres spatiales du premier niveau tend à diminuer, les autres paramètres variant de diverses manières.
-Une constance est l'augmentation du nombre d'analogues après introduction de la fenêtre glissante, qui croît de 25~\% à 83~\% pour la méthode R1, et de 20~\% à 67~\% pour la méthode R2.
-Le nombre d'analogues du premier niveau de la méthode R2 atteint même le triple de sa valeur précédente pour la station de Visp.
-Le fait de pouvoir sélectionner des analogues de la même journée explique que nous sommes conduits à augmenter le nombre optimal d'analogues.
-La Figure \ref{fig:Graphique_fenetre_glissante_chmts_S1} nous a révélé que l'amélioration du critère d'analogie est croissante avec le rang des analogues.
-Nous accroissons donc le nombre de bonnes analogues de manière globale, tout en conservant certaines analogues dont le rang a augmenté.
+After recalibrating, some changes in the optimal parameters can be observed for both 2Z (Table \ref{table:params_2Z_new}) and 2Z-2MI methods (Table \ref{table:params_2Z-2MI_new}).
+Among these, the east-west dimension of the spatial windows of the circulation analogy tends to decrease.
+More significantly, the optimal number of analogues increases after introducing the STW, of a significant order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method.
+The number of analogues of the first analogy level of the 2Z-2MI method even reached three times its previous value for the Visp station.
+As we saw in Figure \ref{fig:changes_S1}, the improvement of the S1 criteria grows along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions.
+It seems thus profitable to widen the selection of analogues in order to keep also some whose rank has increased, as they appear to be also relevant to predict precipitation values.
+The number of good analogues is thus globally increased.
 
-Cette augmentation du nombre d'analogues a un léger effet sur les performances des différentes classes de précipitations.
-L'analyse par classes (section \ref{sec:ameliorations:fenetre:gammes_precip}) a été effectuée à nouveau sur les analogues après recalibration.
-Les résultats sont globalement très semblables, mais nous pouvons distinguer une légère augmentation des performances des petites pluies au détriment des précipitations plus importantes.
-L'accroissement du nombre d'analogues est vraisemblablement responsable de cette différence dans la répartition des gains.
+This increase in number of analogues has a slight effect on the performance of the different precipitation classes.
+The same analysis as in section \ref{sec:improvement_CRPSS_precip_threshold} has been performed again on the basis of the newly calibrated parameters.
+The results are generally very similar, but a slight performance increase of small precipitation values can be observed at the expense of higher amounts.
+The change in the analogues numbers is likely to be responsible for this difference in the performance distributions.
 
-Les valeurs des scores des méthodes R1 (Table \ref{tab:fenetre_glissante:Resultats_R1_recalibration_fen_gliss}) et R2 (Table \ref{tab:fenetre_glissante:Resultats_R2_recalibration_fen_gliss}) ont significativement augmenté après la recalibration.
-Avec l'introduction de la fenêtre temporelle glissante, nous regagnons en performance ce que nous avions alors perdu par la réduction de la longueur de l'archive.
-Dans notre cas, cette amélioration correspond approximativement à un doublement de la taille de l'archive.
+\begin{table}[htb]
+	\caption{Values of the CRPSS (\%) skill score for the newly calibrated parameters using the STW approach.
+The differences are expressed regarding the conventional method with the same archive length.}
+	\begin{center}
+		\begin{tabular}{l c c c c}
+			\hline
+			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
+			& STW & $\Delta$ & STW & $\Delta$ \\
+			\hline
+			Ulrichen & 31.58 & 2.20 & 35.72 & 2.48  \\
+			Zermatt & 24.71 & 2.51 & 29.63 & 2.68 \\
+			Visp & 25.08 & 1.85 & 30.29 & 2.52 \\
+			Montana & 32.22 & 1.43 & 37.15 & 2.38 \\
+			Sion & 26.07 & 1.29 & 31.68 & 2.32 \\
+			Aigle & 32.21 & 1.64 & 38.50 & 2.55 \\
+			\hline
+		\end{tabular}
+	\end{center}
+	\label{table:CRPSS_recalibration}
+\end{table}
+
+The values of the CRPSS scores for both methods (Table \ref{table:CRPSS_recalibration}) have significantly increased after recalibration.
+With the introduction of the sliding time window, we get back the performance loss related to the reduction of the archive length.
+In our case, this improvement is approximately a doubling of the archive size.
 

### 2015-12-15 Moving temporal window - HESS/template.tex
Writing the Moving temporal window.

@@
 
-\subsection{Décomposition du score en finesse et justesse}
+\subsection{Changes in sharpness and accuracy}
 
-Le score CRPS pouvant être décomposé en deux composantes, à savoir la finesse et la justesse, nous allons analyser l'effet de la fenêtre temporelle glissante sur chacune d'elles.
-Les résultats de la Table \ref{tab:fenetre_glissante:Resultats_justesse_finesse} étant exprimés par rapport au CRPS total, un changement de la finesse est donc quantifié par rapport à la somme de la finesse et de la justesse.
-En effet, ces deux composantes n'ont pas les mêmes gammes de valeurs, la justesse étant dans notre cas presque deux fois supérieure à la finesse.
-Puisque nous travaillons ici sur le CRPS et non le CRPSS, une amélioration de la prévision se traduit par une baisse du score.
+The CRPS score can be decomposed into two components, namely sharpness and accuracy.
+The impact of the STW has been analyzed on these components and the results can be found in Table \ref{table:CRPSS_decomposition_no_recalibration} for the original parameters and in Table \ref{table:CRPSS_decomposition_recalibration} for the re-calibrated methods.
+The changes are expressed relative to the total CRPS.
+Both components do not have the same value ranges: accuracy is in our case almost twice the sharpness values.
+Since the CRPS is considered here and not the CRPSS, improved prediction capacity results in a lower score.
+A decrease of the score is thus desirable.
 
 \begin{table}[h]
-	\caption{Changements en finesse (Fin.) et en justesse (Just.) relatifs au CRPS total, dus à l'introduction de la fenêtre temporelle glissante.
-Les changements sont présentés pour les méthodes R1 et R2, et pour les résultats sans et avec recalibration des paramètres.}
+	\caption{Changes in sharpness and accuracy relatively to the total CRPS, due to the introduction of the sliding time window.
+The changes are presented for both 2Z and 2Z-2MI methods with the original parameters.
+A decrease of the score is desirable.}
 	\begin{center}
-		\begin{tabular}{|l|r r|r r|r r|r r|}
-			\cline{2-9}
-			\multicolumn{1}{l}{} & \multicolumn{ 4}{|c|}{\textbf{Fenêtre glissante}} & \multicolumn{ 4}{c|}{\textbf{Fenêtre glissante}} \\
-			\multicolumn{1}{l}{} & \multicolumn{ 4}{|c|}{\textbf{sans recalibration}} & \multicolumn{ 4}{c|}{\textbf{avec recalibration}} \\
-			\multicolumn{1}{l}{} & \multicolumn{ 2}{|c|}{\textbf{R1}} & \multicolumn{ 2}{c|}{\textbf{R2}} & \multicolumn{ 2}{c|}{\textbf{R1}} & \multicolumn{ 2}{c|}{\textbf{R2}} \\
-			\multicolumn{1}{l}{} & \multicolumn{1}{|l}{\textbf{Fin.}} & \multicolumn{1}{l|}{\textbf{Just.}} & \multicolumn{1}{l}{\textbf{Fin.}} & \multicolumn{1}{l|}{\textbf{Just.}} & \multicolumn{1}{l}{\textbf{Fin.}} & \multicolumn{1}{l|}{\textbf{Just.}} & \multicolumn{1}{l}{\textbf{Fin.}} & \multicolumn{1}{l|}{\textbf{Just.}} \\
-			\multicolumn{1}{l}{} & \multicolumn{1}{|l}{\textbf{(\%)}} & \multicolumn{1}{l|}{\textbf{(\%)}} & \multicolumn{1}{l}{\textbf{(\%)}} & \multicolumn{1}{l|}{\textbf{(\%)}} & \multicolumn{1}{l}{\textbf{(\%)}} & \multicolumn{1}{l|}{\textbf{(\%)}} & \multicolumn{1}{l}{\textbf{(\%)}} & \multicolumn{1}{l|}{\textbf{(\%)}} \\ \hline
-			Ulrichen & 2.82 & -5.29 & 1.00 & -4.30 & 1.44 & -4.56 & -0.37 & -3.34 \\ \hline
-			Zermatt & 2.26 & -5.01 & 0.88 & -3.58 & 0.80 & -4.03 & 0.75 & -4.42 \\ \hline
-			Visp & 3.66 & -5.18 & 2.67 & -4.94 & 1.53 & -3.94 & 1.47 & -4.96 \\ \hline
-			Montana & 1.62 & -2.78 & 0.57 & -2.91 & -0.27 & -1.80 & 0.06 & -3.71 \\ \hline
-			Sion & 2.02 & -2.78 & 0.33 & -2.75 & 0.95 & -2.66 & -0.10 & -3.19 \\ \hline
-			Aigle & 0.52 & -2.26 & -1.20 & -2.17 & -0.35 & -2.01 & -2.08 & -1.90 \\ \hline
+		\begin{tabular}{l c c c c}
+			\hline
+			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
+			& Sharpness & Accuracy & Sharpness & Accuracy \\
+			\hline
+			Ulrichen & 2.82 & -5.29 & 1.00 & -4.30 \\
+			Zermatt & 2.26 & -5.01 & 0.88 & -3.58 \\
+			Visp & 3.66 & -5.18 & 2.67 & -4.94 \\
+			Montana & 1.62 & -2.78 & 0.57 & -2.91 \\
+			Sion & 2.02 & -2.78 & 0.33 & -2.75 \\
+			Aigle & 0.52 & -2.26 & -1.20 & -2.17 \\ 
+			\hline
 		\end{tabular}
 	\end{center}
-	\label{tab:fenetre_glissante:Resultats_justesse_finesse}
+	\label{table:CRPSS_decomposition_no_recalibration}
+\end{table}
+
+\begin{table}[h]
+	\caption{Same as Table \ref{table:CRPSS_decomposition_no_recalibration} but with the re-calibrated parameters.}
+	\begin{center}
+		\begin{tabular}{l c c c c}
+			\hline
+			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
+			& Sharpness & Accuracy & Sharpness & Accuracy \\
+			\hline
+			Ulrichen & 1.44 & -4.56 & -0.37 & -3.34 \\
+			Zermatt & 0.80 & -4.03 & 0.75 & -4.42 \\
+			Visp & 1.53 & -3.94 & 1.47 & -4.96 \\
+			Montana & -0.27 & -1.80 & 0.06 & -3.71 \\
+			Sion & 0.95 & -2.66 & -0.10 & -3.19 \\
+			Aigle & -0.35 & -2.01 & -2.08 & -1.90 \\ 
+			\hline
+		\end{tabular}
+	\end{center}
+	\label{table:CRPSS_decomposition_recalibration}
 \end{table}
@@
 		\begin{array}{cccc}
-		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_justesse.pdf} & \hspace{-5mm}
-		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_finesse.pdf} & \hspace{-5mm}
-		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_justesse.pdf} & \hspace{-5mm}
+		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_justesse.pdf} &
+		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_finesse.pdf} &
+		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_justesse.pdf} &
 		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_finesse.pdf} \\
-		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_justesse_recalib.pdf} & \hspace{-5mm}
-		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_finesse_recalib.pdf} & \hspace{-5mm}
-		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_justesse_recalib.pdf} & \hspace{-5mm}
+		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_justesse_recalib.pdf} &
+		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_finesse_recalib.pdf} &
+		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_justesse_recalib.pdf} &
 		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_finesse_recalib.pdf} 

### 2015-12-16 Moving temporal window - HESS/template.tex
Writing the Moving temporal window.

@@
 
-\begin{table}[h]
+\begin{table}[htb]
 	\caption{Changes in sharpness and accuracy relatively to the total CRPS, due to the introduction of the sliding time window.
@@
 
-\begin{table}[h]
+\begin{table}[htb]
 	\caption{Same as Table \ref{table:CRPSS_decomposition_no_recalibration} but with the re-calibrated parameters.}
@@
 
-\begin{figure*}[h]
+\begin{figure*}[htb]
 	\begin{center}$
 		\begin{array}{cccc}
-		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_justesse.pdf} &
-		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_finesse.pdf} &
-		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_justesse.pdf} &
-		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_finesse.pdf} \\
-		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_justesse_recalib.pdf} &
-		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_finesse_recalib.pdf} &
-		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_justesse_recalib.pdf} &
-		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_finesse_recalib.pdf} 
+		\includegraphics[width=4cm]{figures/component_2Z_accuracy.pdf} &
+		\includegraphics[width=4cm]{figures/component_2Z_sharpness.pdf} &
+		\includegraphics[width=4cm]{figures/component_2Z-2MI_accuracy.pdf} &
+		\includegraphics[width=4cm]{figures/component_2Z-2MI_sharpness.pdf} \\ \\
+		\includegraphics[width=4cm]{figures/component_2Z_accuracy_recalib.pdf} &
+		\includegraphics[width=4cm]{figures/component_2Z_sharpness_recalib.pdf} &
+		\includegraphics[width=4cm]{figures/component_2Z-2MI_accuracy_recalib.pdf} &
+		\includegraphics[width=4cm]{figures/component_2Z-2MI_sharpness_recalib.pdf} 
 		\end{array}$
 	\end{center}
-	\caption{Influence de la fenêtre temporelle glissante sur les composantes du CRPS (justesse et finesse), pour les méthodes R1 et R2.
-Les résultats sont présentés pour (haut) les paramètres originaux et (bas) recalibrés.
-Une amélioration de la prévision se traduit par une baisse du score.}
-	\label{fig:Graphique_fenetre_glissante_crps_comp}
+	\caption{Influence (\%) of the STW on the CRPS components (accuracy and sharpness) relatively to the total CRPS, for the 2Z and 2Z-2MI methods, according to different precipitation thresholds.
+The results are presented for (top) the original parameters, and (bottom) the recalibrated parameters.
+Improved prediction results in a lower score.}
+	\label{fig:CRPSS_decomposition_precip_thresholds}
 \end{figure*}
 
-Il apparaît que la finesse est moins bonne avec la fenêtre temporelle glissante, au profit de la justesse, et ceci pour les mêmes paramètres que la méthode standard, alors qu'elle décroît avec l'augmentation du nombre d'analogues après recalibration.
-La Figure \ref{fig:Graphique_fenetre_glissante_crps_comp}, illustrant les changements en finesse et justesse pour différentes gammes de précipitations à la station d'Ulrichen, présente cette même tendance.
-Nous y voyons également que le plus grand gain en justesse concerne les gammes de précipitations les plus importantes, que ce soit pour R1 ou R2.
-La fenêtre temporelle glissante ne permet donc pas d'améliorer la finesse, mais l'amélioration de la justesse est significative, et ceci notamment pour les jours de fortes précipitations.
-Cela signifie donc que le quantile 50~\% de la distribution prévue se rapproche des cumuls observés, mais que la distribution n'est pas plus condensée que précédemment.
+It appears that the sharpness is a bit inferior with the STW in favor of accuracy (Table \ref{table:CRPSS_decomposition_no_recalibration}).
+When using the recalibrated parameters, the components are a bit more balanced, but still the accuracy prevails on the sharpness (Table \ref{table:CRPSS_decomposition_recalibration}).
+Figure \ref{fig:CRPSS_decomposition_precip_thresholds} illustrates the changes (relative to the total CRPS) in sharpness and accuracy for different precipitation thresholds at the Ulrichen station.
+Be it for the 2Z or 2Z-2MI method, the original or the recalibrated parameters, the changes are similar: the improvements concern the accuracy over the sharpness, and this to a greater extent for significant precipitation events.
+The STW does not allow to improve the sharpness, but the improvement in accuracy is significant, and this especially for the days with heavy precipitation.
+In terms of the predicted precipitation distribution, it means that the median of the prediction is closer to the observed values, but the distribution is not more condensed than previously.
 
-\section{Tentatives d'application à l'archive complète}
+\section{Application attempts on the full archive}
 

### 2015-12-16 Moving temporal window - HESS/template.tex
Writing the moving temporal window: Proportional distribution.

@@
 
-L'amélioration apportée par la fenêtre temporelle glissante est intéressante, il serait donc profitable de pouvoir l'appliquer à notre archive complète.
-Malheureusement, il n'existe pas de données horaires avant 1982 nous permettant de disposer d'une archive compatible et correcte.
-Nous allons donc chercher à répartir les cumuls précipités sur la journée par une simple moyenne mobile ou en utilisant la chronologie d'un prédicteur lié à l'humidité en tant que proxy.
+The improvement provided by the STW is interesting, mainly for heavy precipitation events, and thus it would be profitable to be able to apply it to the complete archive.
+Unfortunately, there is no long precipitation time series available with a sub-daily time step.
+In order to reconstruct a longer archive of moving averages of 24~h-totals, different disaggregation approaches of the daily time series were assessed and are presented in the following sections.
 
-\subsection{Série par moyenne mobile}
+\subsection{Proportional distribution}
 
-La moyenne mobile est certainement la répartition la plus simple que nous pouvons effectuer.
-Elle consiste à distribuer les précipitations journalières concernées de manière proportionnelle dans les différentes tranches de la série 24~heures glissée (Figure \ref{fig:illustration_disaggregation}).
-Les résultats présentés dans la Table \ref{tab:fenetre_glissante:Resultats_moyenne_mobile} montrent clairement qu'une telle archive ne présente aucun intérêt, puisque les performances sont même inférieures à la méthode classique sans fenêtre temporelle glissante (Table \ref{tab:fenetre_glissante:Gains_CRPSS}).
-Nous perdons le gain d'une sélection plus fine des situations analogues du fait d'une archive pluviométrique de qualité médiocre.
+A proportional distribution is certainly the simplest approach that can be performed.
+It consists in allocating proportional parts of the original daily time series into a new moving average of 24~h-totals (Figure \ref{fig:illustration_disaggregation}).
+When using this reconstructed time series on the shorter period, the method performance was degraded (Table \ref{table:disaggregation_proportional} to compare to Table \ref{table:CRPSS_STW}) and was even below the conventional method without STW (Table \ref{table:loss_reduction}).
+The benefit of a better selection of the analogue situations is lost due to a precipitation archive of poor quality.
 
@@
 	\begin{center}
-		\includegraphics[width=12cm]{figures/illustration_disaggregation.pdf}
+		\includegraphics[width=8cm]{figures/illustration_disaggregation.pdf}
 	\end{center}
-	\caption{Illustration de la création de séries de cumuls sur 24h glissés par moyenne mobile.}
+	\caption{Illustration of the generation of 24~h-totals moving averages by means of a proportional distribution.}
 	\label{fig:illustration_disaggregation}
@@
 \begin{table}[htb]
-	\caption{Performances de la fenêtre temporelle glissante avec une archive pluviométrique générée par moyenne mobile.
-Les résultats sont présentés pour les paramètres initiaux, ainsi que ceux issus de la recalibration de la section \ref{sec:ameliorations:fenetre:recalibration}}
+	\caption{Values of the CRPSS (\%) skill score for the original and the recalibrated parameters using the STW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
 	\begin{center}
-		\begin{tabular*}{10cm}{@{\extracolsep{\fill}}lcccc}
+		\begin{tabular}{l c c c c}
 			\hline
-			\multirow{2}{*}{\textbf{Station}} & \multicolumn{ 2}{c}{\textbf{Fenêtre glissante}} & \multicolumn{ 2}{c}{\textbf{Avec recalibration}} \\
-			& \multicolumn{1}{c}{\textbf{R1}} & \multicolumn{1}{c}{\textbf{R2}} & \multicolumn{1}{c}{\textbf{R1}} & \multicolumn{1}{c}{\textbf{R2}} \\ \hline
-			Ulrichen & 29.13~\% & 33.15~\% & 29.61~\% & 33.45~\% \\ \hline
-			Zermatt & 22.17~\% & 26.72~\% & 22.80~\% & 27.43~\% \\ \hline
-			Visp & 22.32~\% & 27.01~\% & 22.89~\% & 28.04~\% \\ \hline
-			Montana & 29.41~\% & 33.83~\% & 30.24~\% & 34.55~\% \\ \hline
-			Sion & 22.98~\% & 28.57~\% & 23.41~\% & 29.15~\% \\ \hline
-			Aigle & 29.07~\% & 34.66~\% & 29.46~\% & 35.09~\% \\ \hline
-		\end{tabular*}
+			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
+			& original & recalib. & original & recalib. \\
+			\hline
+			Ulrichen & 29.13 & 29.61 & 33.15 & 33.45 \\
+			Zermatt & 22.17 & 22.80 & 26.72 & 27.43 \\
+			Visp & 22.32 & 22.89 & 27.01 & 28.04 \\
+			Montana & 29.41 & 30.24 & 33.83 & 34.55 \\
+			Sion & 22.98 & 23.41 & 28.57 & 29.15 \\
+			Aigle & 29.07 & 29.46 & 34.66 & 35.09 \\
+			\hline
+		\end{tabular}
 	\end{center}
-	\label{tab:fenetre_glissante:Resultats_moyenne_mobile}
+	\label{table:disaggregation_proportional}
 \end{table}

### 2015-12-16 Moving temporal window - HESS/template.tex
Writing the moving temporal window: Proxy variable.

@@
 
-\subsection{Utilisation d'un proxy pour reconstituer la chronologie}
+\subsection{Use of a proxy variable}
 
-Comme nous l'avons vu dans la section précédente, une série de précipitations reconstituée de manière simpliste nous fait perdre tout le gain de performance de la fenêtre temporelle glissante et ne présente alors aucun intérêt.
-Nous devons donc trouver un moyen de nous approcher de la chronologie réelle, pour une période (1961-1981) où nous ne disposons d'aucune série de précipitations continue avec une résolution plus fine.
-Il nous faut donc extraire de l'information de la répartition intrajournalière des pluies à partir d'une autre source de données.
-Un modèle de prévision météorologique régional serait en mesure d'apporter de l'information permettant de générer des séries de précipitations plus pertinentes.
-Malheureusement, de tels résultats ne sont pas disponibles sous forme de longues archives.
-Une alternative aux modèles régionaux est donnée par les réanalyses.
-Bien que celles-ci ont une résolution plus faible et n'intègrent que grossièrement les processus locaux, nous allons évaluer si elles rendent possible la transposition de la fenêtre temporelle glissante sur toute l'archive.
+As we saw in the previous section, the performance improvement brought by the STW is lost when using a simplistic precipitation time series.
+In order to get closer to the chronology of the accurate precipitation, the reconstruction procedure must rely on some informative variable.
+Data from the NCEP/NCAR reanalysis 1 (section \ref{sec:data}) was used in this perspective, despite their rough resolution.
 
-La première étape consiste à déterminer quelle variable, de l'eau précipitable ou de l'humidité relative, est la plus corrélée avec la série de précipitations sur la période 1982-2007, et en quel point.
-Nous considérons les niveaux 1000~hPa, 925~hPa et 850~hPa pour l'humidité relative, et les points les plus proches du bassin (5\textdegree\ - 7.5\textdegree\ de longitude et 45\textdegree\ - 47.5\textdegree\ de latitude).
-Finalement, les points de grille des réanalyses étant relativement éloignés de nos stations, il est pertinent de rechercher la présence probable d'un décalage temporel entre les séries.
-
-Le point le plus pertinent ne sera probablement pas le même pour toutes les stations, puisque nous pouvons nous attendre à trouver l'optimum dans la direction des apports d'humidité principaux pour la station.
-Cette recherche doit donc être effectuée pour chacune de nos stations.
-Nous illustrons le principe avec la station de Zermatt.
+The first step consisted in determining which variables from the precipitable water or the relative humidity (at 1000~hPa, 925~hPa or 850~hPa) produces the precipitation chronology that is the most correlated (on non-zero values) with the accurate 6-hourly precipitation time series on the period 1982-2007.
+The location of the most predictive point from the reanalysis grid had to be assessed (closest points: 5\textdegree\ - 7.5\textdegree\ longitude and 45\textdegree\ - 47.5\textdegree\ latitude), as well an eventual time lapse between both series, due to the significant distance separating the weather stations and the reanalysis grid point.
+The most relevant point will probably not be the same for all stations, since we can expect to find the optimum in the direction of the main moisture inflows for the station.
+This assessment must be carried out for each station.
 
 \begin{table}[htb]
-	\caption{Valeur du coefficient de détermination entre les séries reconstituées à l'aide d'un proxy et la série réelle à pas de temps de 6~h.
-Les proxys évalués sont l'eau précipitable et l'humidité relative à différents niveaux atmosphériques, en 4 points proches du bassin.
-Le coefficient de détermination le plus élevé est indiqué en gras.}
+	\caption{Value of the coefficient of determination between the reconstructed 6-hourly precipitation time series using the listed variables, and the accurate time series on the period 1982-2007.
+The grid points are the following (lon/lat): 1) 5\textdegree/47.5\textdegree, 2) 5\textdegree/45\textdegree, 3) 7.5\textdegree/47.5\textdegree, 4) 7.5\textdegree/45\textdegree.
+The highest coefficient of determination is indicated in bold.}
 	\begin{center}
-		\begin{tabular}{|l|rr|rrrrr|}
-			\cline{ 2- 8}
-			\multicolumn{1}{l}{} & \multicolumn{2}{|c|}{\textbf{Position}} &  \multicolumn{5}{c|}{\textbf{Décalage temporel}} \\
-			\multicolumn{1}{l}{} & \multicolumn{1}{|c}{\textbf{Lon}} & \multicolumn{1}{c|}{\textbf{Lat}} & \multicolumn{1}{c}{\textbf{-12h}} & \multicolumn{1}{c}{\textbf{-6h}} & \multicolumn{1}{c}{\textbf{0h}} & \multicolumn{1}{c}{\textbf{+6h}} & \multicolumn{1}{c|}{\textbf{+12h}} \\ \hline
-			\multirow{ 4}{*}{RHum 1000 hPa} & 5.0 & 47.5 & 0.668 & 0.669 & 0.684 & 0.683 & 0.670 \\
-			& 5.0 & 45.0 & 0.669 & 0.669 & 0.683 & 0.681 & 0.669 \\
-			& 7.5 & 47.5 & 0.662 & 0.673 & 0.691 & 0.682 & 0.673 \\
-			& 7.5 & 45.0 & 0.666 & 0.671 & 0.688 & 0.681 & 0.668 \\ \hline
-			\multirow{ 4}{*}{RHum 925 hPa} & 5.0 & 47.5 & 0.672 & 0.673 & 0.684 & 0.684 & 0.675 \\
-			& 5.0 & 45.0 & 0.674 & 0.674 & 0.683 & 0.682 & 0.672 \\
-			& 7.5 & 47.5 & 0.662 & 0.673 & 0.691 & 0.682 & 0.673 \\
-			& 7.5 & 45.0 & 0.666 & 0.671 & 0.689 & 0.681 & 0.668 \\ \hline
-			\multirow{ 4}{*}{RHum 850 hPa} & 5.0 & 47.5 & 0.675 & 0.675 & 0.679 & 0.678 & 0.671 \\
-			& 5.0 & 45.0 & 0.681 & 0.690 & 0.691 & 0.677 & 0.664 \\
-			& 7.5 & 47.5 & 0.665 & 0.680 & 0.693 & 0.683 & 0.675 \\
-			& 7.5 & 45.0 & 0.675 & 0.694 & 0.706 & 0.681 & 0.659 \\ \hline
-			\multirow{ 4}{*}{Eau precipitable} & 5.0 & 47.5 & 0.688 & 0.687 & 0.667 & 0.655 & 0.652 \\
-			& 5.0 & 45.0 & 0.697 & 0.699 & 0.669 & 0.644 & 0.644 \\
-			& 7.5 & 47.5 & 0.686 & 0.708 & 0.689 & 0.655 & 0.648 \\
-			& 7.5 & 45.0 & 0.696 & \textbf{0.721} & 0.696 & 0.643 & 0.636 \\ \hline
+		\begin{tabular}{l c c c c c c}
+			\hline
+			\multirow{2}{*}{Variable} & \multirow{2}{*}{Point} &  \multicolumn{5}{c}{Time lapse} \\
+			&  & -12h & -6h & 0h & +6h & +12h \\ 
+			\hline
+			\multirow{ 4}{*}{RH1000} & 1 & 0.668 & 0.669 & 0.684 & 0.683 & 0.670 \\
+			& 2 & 0.669 & 0.669 & 0.683 & 0.681 & 0.669 \\
+			& 3 & 0.662 & 0.673 & 0.691 & 0.682 & 0.673 \\
+			& 4 & 0.666 & 0.671 & 0.688 & 0.681 & 0.668 \\ \hline
+			\multirow{ 4}{*}{RH925} & 1 & 0.672 & 0.673 & 0.684 & 0.684 & 0.675 \\
+			& 2 & 0.674 & 0.674 & 0.683 & 0.682 & 0.672 \\
+			& 3 & 0.662 & 0.673 & 0.691 & 0.682 & 0.673 \\
+			& 4 & 0.666 & 0.671 & 0.689 & 0.681 & 0.668 \\ \hline
+			\multirow{ 4}{*}{RH850} & 1 & 0.675 & 0.675 & 0.679 & 0.678 & 0.671 \\
+			& 2 & 0.681 & 0.690 & 0.691 & 0.677 & 0.664 \\
+			& 3 & 0.665 & 0.680 & 0.693 & 0.683 & 0.675 \\
+			& 4 & 0.675 & 0.694 & 0.706 & 0.681 & 0.659 \\ \hline
+			\multirow{ 4}{*}{TCW} & 1 & 0.688 & 0.687 & 0.667 & 0.655 & 0.652 \\
+			& 2 & 0.697 & 0.699 & 0.669 & 0.644 & 0.644 \\
+			& 3 & 0.686 & 0.708 & 0.689 & 0.655 & 0.648 \\
+			& 4 & 0.696 & \textbf{0.721} & 0.696 & 0.643 & 0.636 \\ \hline
 		\end{tabular}
 	\end{center}
-	\label{tab:fenetre_glissante:Serie_proxy_correlations}
+	\label{table:proxy_correlations}
 \end{table}
@@
 \begin{table}[htb]
-	\caption{Valeurs des scores CRPSS pour Zermatt avec la série glissée reconstituée à l'aide d'un proxy météorologique.
-Les résultats sont présentés pour les deux périodes 1982-2007 et 1961-2008, pour les paramètres sans et avec recalibration, ainsi que pour les deux méthodes R1 et R2.}
+	\caption{Values of the CRPSS (\%) skill score for Zermatt, for the original and the recalibrated parameters using the STW approach on the disaggregated precipitation time series (short and long periods) by means of variables from the reanalysis.}
 	\begin{center}
-		\begin{tabular*}{10cm}{@{\extracolsep{\fill}}lcccc}
+		\begin{tabular}{l c c c c}
 			\hline
-			\multirow{2}{*}{\textbf{Période}} & \multicolumn{ 2}{c}{\textbf{Sans recalibration}} & \multicolumn{ 2}{c}{\textbf{Avec recalibration}} \\
-			& \multicolumn{1}{c}{\textbf{R1}} & \textbf{R2} & \multicolumn{1}{c}{\textbf{R1}} & \textbf{R2} \\ \hline
-			1982-2007 & 22.57~\% & 27.11~\% & 23.14~\% & 27.71~\% \\ \hline
-			1961-2008 & 23.81~\% & 28.42~\% & 24.38~\% & 28.86~\% \\ \hline
-		\end{tabular*}
+			\multirow{2}{*}{Period} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
+			& original & recalib. & original & recalib. \\
+			\hline
+			1982-2007 & 22.57 & 23.14 & 27.11 & 27.71 \\
+			1961-2008 & 23.81 & 24.38 & 28.42 & 28.86 \\
+			\hline
+		\end{tabular}
 	\end{center}
-	\label{tab:fenetre_glissante:Resultats_proxy_Zermatt}
+	\label{table:proxy_CRPSS}
 \end{table}
 
-Afin de déterminer quelle variable météorologique considérer, en quel point, et avec quel décalage horaire, chacune des séries générées doit être comparée à la série réelle.
-La Table \ref{tab:fenetre_glissante:Serie_proxy_correlations} présente les coefficients de détermination sur les valeurs non nulles entre les nouvelles séries reconstituées à l'aide du proxy et la série réelle de la station de Zermatt à pas de temps de 6~h sur la période 1982-2007.
-Le meilleur proxy est l'eau précipitable à 45\textdegree\ de latitude et 7.5\textdegree\ de longitude, avec un décalage temporel de -6~h; cela signifie que nous devons retarder de 6~h la chronologie du prédicteur afin de l'appliquer aux précipitations.
-Le coefficient de détermination de 0.721 est supérieur à celui de la série par moyenne mobile (0.698), ce qui nous confirme que nous avons ajouté un peu d'information à la série de précipitations, sans toutefois savoir si celle-ci est suffisante.
+The results of the correlation analyses (on non-zero values) between the new series reconstituted using the proxy and the actual series are illustrated in Table \ref{table:proxy_correlations} for Zermatt (on the short period, 1982-2007).
+The best proxy is the precipitable water at 45\textdegree\ latitude and 7.5\textdegree\ longitude, with a time offset of -6~h.
+The determination coefficient of 0.721 is higher than that of the series from the proportional distribution (0.698), which confirms that a little information was added to the series of precipitation.
 
-La Table \ref{tab:fenetre_glissante:Resultats_proxy_Zermatt} présente les scores CRPSS obtenus par la série reconstituée à l'aide du proxy de l'eau précipitable au point optimal (Table \ref{tab:fenetre_glissante:Serie_proxy_correlations}).
-Nous observons une légère amélioration par rapport aux résultats obtenus avec la série de moyennes mobiles (Table \ref{tab:fenetre_glissante:Resultats_moyenne_mobile}), mais celle-ci est toujours relativement petite, et la plus grande partie du gain de la fenêtre temporelle glissante est perdue.
+Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the reconstituted series using the proxy of precipitable water at the optimal point (Table \ref{table:proxy_correlations}).
+A slight improvement can be obtained compared to the proportional distribution method, but it is still relatively small, and most of the benefit of the STW is lost.
 
-Ces tentatives de transposition de la fenêtre temporelle glissante sur l'archive totale mettent en évidence l'importance de la temporalité réelle des précipitations.
-La fenêtre glissante est un gain, à condition que les séries de précipitations soient proches de l'observé.
-Sans information sur la chronologie des précipitations, il n'est pas pertinent d'appliquer cette modification à la méthode.
-Nous pouvons espérer que, dans le futur, des reprévisions par des modèles régionaux seront en mesure de nous apporter une chronologie des précipitations s'approchant de la réalité.
+These attempts to transpose the STW on the total archive highlight the importance of the actual chronology of rainfall.
+The sliding window is profitable, provided that the precipitation series are close to the observed one.
+Without precipitation series with an accurate sub-daily chronology, the introduction of a STW is not appropriate.
 

### 2015-12-16 Moving temporal window - HESS/template.tex
Writing the moving temporal window: Conclusions.

@@
 
-\section{Method}
+\section{The sliding time window approach}
 \label{sec:method}
@@
 Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
-The AM parameters were calibrated on the original archive (Tables \ref{table:method_2Z} and \ref{table:method_2Z-2MI}) and will be used thereafter.
+The AM parameters were calibrated using AtmoSwing \citep{Horton2016} on the original archive (Tables \ref{table:method_2Z} and \ref{table:method_2Z-2MI}) and will be used thereafter.
 
@@
 The first step consisted in determining which variables from the precipitable water or the relative humidity (at 1000~hPa, 925~hPa or 850~hPa) produces the precipitation chronology that is the most correlated (on non-zero values) with the accurate 6-hourly precipitation time series on the period 1982-2007.
-The location of the most predictive point from the reanalysis grid had to be assessed (closest points: 5\textdegree\ - 7.5\textdegree\ longitude and 45\textdegree\ - 47.5\textdegree\ latitude), as well an eventual time lapse between both series, due to the significant distance separating the weather stations and the reanalysis grid point.
+The location of the most predictive point from the reanalysis grid had to be assessed (closest points: 5\textdegree\~-~7.5\textdegree\ longitude and 45\textdegree\~-~47.5\textdegree\ latitude), as well an eventual time lapse between both series, due to the significant distance separating the weather stations and the reanalysis grid point.
 The most relevant point will probably not be the same for all stations, since we can expect to find the optimum in the direction of the main moisture inflows for the station.
@@
 
-Comme \citet{Finet2008} l'avaient déjà été montré précédemment, nous gagnons en analogie synoptique en introduisant la fenêtre temporelle glissante.
-Pour ce qui est de la prévision des précipitations, nous regagnons en fenêtre glissante sur période réduite ce que nous avions perdu par rapport à la fenêtre fixe en raison de la réduction de l'archive.
-Dans notre cas, ce gain correspond au doublement de la taille de l'archive.
+The AM is most often based on a daily time step, due to the availability of long precipitation archives.
+However, it is unlikely that two analogue synoptic situations, that evolve relatively quickly, would correspond optimally at the same hour of the day.
+It is thus more likely that a better match can be found at another time, which can change the selection of the analogues dates.
 
-Nous avons également démontré l'importance de la qualité de l'archive pluviométrique: nous gagnons en prévision des précipitations pour autant que la chronologie des pluies y soit proche de la réalité.
-Pour une archive reconstituée de manière grossière, les gains en performances de la fenêtre glissante ne se répercutent pas sur la prévision des pluies, bien que l'analogie synoptique soit meilleure.
-Il conviendra donc de maintenir l'objectif qui consiste à reconstruire des séries de précipitations passées de manière la plus réaliste possible, par exemple à l'aide d'un modèle météorologique régional.
-Lorsque de telles archives pluviométriques seront disponibles, l'ajout d'une fenêtre temporelle glissante en prévision par analogie montrera tout son intérêt.
+As \citet{Finet2008} had previously shown, the introduction of a sliding time window allows finding better analogue situations in terms of the atmospheric circulation.
+It has been here demonstrated that the improvement of the S1 criteria values is growing with the rank of the analogue.
+This is due to the accumulation of better analogues within the predicted distributions.
 
-\appendix
-\section{}    %% Appendix A
+The improvement of the circulation analogy was found to be more important for heavy precipitation events, which are generally related to more dynamic atmospheric situations.
+This dynamism implies more specific circulation patterns that are evolving more rapidly.
+Thus, a STW is found to be of particular interest in this kind of situation, and benefits the prediction of extreme precipitation events.
 
-\subsection{}                               %% Appendix A1, A2, etc.
+A seasonal effect has been highlighted, as the STW is more profitable for winter months than summer.
+The reason is likely that the diurnal cycle has a bigger effect in summer than in winter, which results in better analogues at the same time of the day.
+The preference for the same hours in summer has been demonstrated, whereas 75\% of the analogue situations are selected at a different time in winter.
+
+The impact of the STW on the prediction performance has never been assessed before, due to the shortcoming of long precipitation series at a sub-daily time step.
+We could evaluate the impact of the STW approach on a 25 years time series with a high temporal resolution.
+After the introduction of the STW, the performance scores increased of the same order of magnitude as if we doubled the length of the archive, in this case study.
+
+The parameters were then calibrated again, using the STW.
+Some parameters changed, the main difference being the number of analogues that was found optimal, which systematically and significantly increased compared to the original set.
+A wider selection of analogue situations, containing those whose rank decreased, seemed profitable for the prediction performance.
+The number of good analogues is thus globally increased.
+This change seems to benefit mainly the prediction of days with small precipitation totals.
+
+The importance of the quality of the precipitation archive was also demonstrated, as too simplistic reconstructions of 6-hourly time series lead to a loss of all the improvement brought by better analogue situations identified by the STW.
+The precipitation prediction is improved only when the precipitation chronology is close to the accurate one.
+Attempts to reconstruct longer time series based on a simplistic proportional distribution or using meteorological variables from the NCEP reanalysis 1 dataset as proxy did not succeed.
+
+Perspectives of using the STW rely on the availability of long precipitation series at a sub-daily time step and with high accuracy.
+The first source of such data is the simple fact that with time, these archives of high temporal resolution precipitation data are getting longer.
+The second source is the establishment of precipitation reanalysis at a country scale, or the use of reanalysis-driven RCMs (Regional Climate Models) or LAMs (Limited Area Models) on a long period.
+When such precipitation data will be available, the use of a STW in the AM should be considered for any application, especially when the prediction quality of extreme events are important.
 
@@
 Thanks to Dominique B\'{e}rod for his support and to Renaud Marty for his fruitful collaboration over the years.
+
 Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
+
 The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
-NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.
-Precipitation time series provided by MeteoSwiss.
+
+NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/. Precipitation time series provided by MeteoSwiss. 
 \end{acknowledgements}

### 2015-12-16 AtmoSwing - Geoscientific Model Development/template.tex
Writing the moving temporal window: Abstract.

@@
 
-The analogue method allows forecasting local meteorological variables of interest (predictand), such as the daily precipitation, on the basis of synoptic variables (predictors).
+The Analogue Method (AM) allows forecasting local meteorological variables of interest (predictand), such as the daily precipitation, on the basis of synoptic variables (predictors).
 It relies on the fact that similar meteorological influences are likely to result in similar local effects.

### 2015-12-16 Moving temporal window - HESS/template.tex
Writing the moving temporal window: Abstract.

@@
 \begin{abstract}
-TEXT
+The Analogue Method (AM) aims at forecasting local weather variables (predictands), such as the precipitation, by means of a statistical relationship with predictors at a synoptic scale.
+The analogy is assessed in the first place on the geopotential field by mean of a comparison of the gradients, in order to sample the days with a similar atmospheric circulation.
+
+The search for candidates situations, for a given target day, is usually undertaken by comparing the state of the atmosphere at fixed hours of the day.
+The constraint being the use of daily time series, due to the length of available archives they provide.
+However, it is unlikely that the best analogues happen at the very same hour, but may occur at different time of the day.
+In order to assess the potential of finding better analogues at a different times, a sliding time window (STW) has been introduced.
+
+The STW resulted in a better analogy of the atmospheric circulation, with improved values of the analogy criteria on the whole distribution of analogue dates.
+The improvement was found to grow with the analogue ranks due to an accumulation of more similar situations in the predicted distribution.
+Moreover, the improvement is even more important for days with heavy precipitation events, which are generally related to more dynamic atmospheric situations, where timing is more specific.
+
+A seasonal effect has also been identified, with larger improvements in winter that in summer, supposedly due to the stronger effect of the diurnal cycle in summer, which favors predictors at the same hours.
+
+The impact of the STW on the prediction performance has been assessed by means of a sub-daily precipitation series transformed into moving 24~h-totals at a 6-hourly time step.
+This resulted in an improvement of the prediction skills, which were even larger after recalibrating the AM parameters.
+
+Attempts to reconstruct longer precipitation series of running 24~h-totals by means of simple methods failed.
+It empathized the need to use time series with an accurate chronology.
+These should be available in a near future, either by means of growing observed time series, or by the establishment of precipitation reanalysis through regional modeling.
+Then, the use of a STW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.
+
 \end{abstract}
@@
 
-%REWRITE
+The Analogue Method (AM) is based on the principle that two relatively similar synoptic situations may produce relatively similar local effects, and can be called analogues \citep{Lorenz1956, Lorenz1969}.
+Multiple variations of the methods exist and listings can be found in \citet{Horton2016} or \citet{BenDaoud2015}.
+The versions that will be considered here are often used as references or benchmarks for various improvements.
+The first implementation relies on an analogy of the atmospheric circulation, and the other adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
 
-Multiple variations of the methods exist, and most of them will not be detailed hereafter \cite[see][for more comprehensive listings]{Horton2016, BenDaoud2015}.
-However, there are mainly 2 parameterizations that are most often used for precipitation forecasting and that will be considered as reference: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
-
-The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:method_2Z}): the similarity of the atmospheric circulation of a target date with every day of the archive is assessed by processing the S1 criteria \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
-\citet{Bontron2005} showed that the geopotential height at 500~hPa (Z500) and 1000~hPa (Z1000) are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criteria performs better than scores based on absolute distances.
-The reason for such better results is that the S1 criteria allows comparing the circulation pattern, by means of the gradients, rather than the absolute value of the geopotential height.
-To cope with seasonal effects, candidate dates are extracted within a period of 4 months centered around the target date, for every year of the archive.
+The first method is based on the analogy of the synoptic circulation (Table \ref{table:method_2Z}).
+When searching analogue situations for a target day, it starts by a preselection step, which is a selection of the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects.
+Then, the similarity of the atmospheric circulation of a target date with every day of the preselection is assessed by processing the S1 criteria \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
+The considered pressure levels are 500~hPa (Z500) and 1000~hPa (Z1000) \citep{Bontron2005}.
+The $N_{1}$ dates, which is a parameter to calibrate, with the lowest values of S1 are considered as analogues to the target day.
+Then, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
 Following the nomenclature proposed by \citet{Horton2016}, this method will be named 2Z.
@@
 			\hline 
-			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{$N_{1}$} \\
 			& Z500 & 24~h & & \\ 
@@
 
-The $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day.
-The number of analogues, $N_{1}$, is a parameter to calibrate.
-Then, the daily observed precipitation amount of the $N_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
-
-The other most know parametrization adds a second level of analogy on moisture variables (method 2Z-2MI, Table \ref{table:method_2Z-2MI}).
-The predictor that \citet{Bontron2004} found optimal for the France territory is a moisture index made of the product of the precipitable water with the relative humidity at 850~hPa (RH850).
-\cite{Horton2012a} confirmed that this index is also better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis considered independently.
+The second reference method adds a subsequent level of analogy on moisture variables (method 2Z-2MI, Table \ref{table:method_2Z-2MI}).
+This second predictor is a moisture index made of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850) \citep{Bontron2004}.
 When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
-When a second level of analogy is added, a higher number of analogues is kept on the first level.
+When a second level of analogy is added, a higher number of $N_{1}$ analogues is kept on the first level.
 
@@
 			\hline 
-			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{$N_{1}$} \\
 			& Z500 & 24~h & & \\ 
 			\hline
-			\multirow{2}{*}{2} & TPW * RH850 & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{30} \\
+			\multirow{2}{*}{2} & TPW * RH850 & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{2}$} \\
 			& TPW * RH850 & 24~h & & \\ 
@@
 
-%REWRITE
+To calibrate the method, the commonly used technique is a semi-automatic sequential procedure elaborated by \citet{Bontron2004}.
+AtmoSwing \citep{Horton2016}, which implements this technique was used in order to calibrate the parameters in the present study.
+The score that is most often used to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
+It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$.
+The better the forecast, the smaller the score.
+The mean CRPS of a forecast series of length $n$ can be written:
 
-%COMPLETE
+\begin{equation}
+\label{eq:CRPS}
+CRPS = \frac{1}{n} \sum_{i=1}^{n} \left(  \int_{-\infty}^{+\infty} \left[ F_{i}(y)-H_{i}(y-y_{i}^{0})\right]^{2} dy \right) 
+\end{equation}
+where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value 1 otherwise.
+The mean CRPS is averaged on the calibration, respectively the validation periods, on all days.
+\citet{Bontron2004} proposed a decomposition of this score into a sharpness and an accuracy terms.
 
-sliding time window (STW)
+In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution as the reference.
+The CRPSS (\textit{Continuous Ranked Probability Skill Score}) is thus defined as following:
 
-The analogue method (AM) is usually implemented with a daily time step, due to the availability of long precipitation archives that have no equivalent to a finer resolution.
-Therefore, the analogues situations are compared on the basis of a daily time step, by comparing predictors at fixed hours of the day, otherwise we would not know what precipitation values to assign to them.
+\begin{equation}
+\label{eq:CRPSS}
+CRPSS = \frac{CRPS-CRPS_{r}}{CRPS_{p}-CRPS_{r}} = 1-\frac{CRPS}{CRPS_{r}}
+\end{equation}
+where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect forecast (which implies $CRPS_{p}~=~0$). A better forecast is characterized by an increase in CRPSS.
+
+The AM is usually implemented with a daily time step, due to the availability of long precipitation archives that have no equivalent to a finer resolution.
+Therefore, the analogues situations are assessed on the basis of a daily time step, by comparing predictors at fixed hours of the day, otherwise we would not know what precipitation values to assign to them.
 However, we can expect that the analogy of the synoptic situations do not occur systematically at the same time of the day, and that better candidates can be found at different times.
+On this assumption, we introduced a sliding time window (STW) to allow searching for candidates at different hours of the day.
 
 Previous tests showed the benefit, in terms of analogy criteria values, of searching for analogue synoptic situations at a finer time step, but without assessing the impact on the forecast skills \citep{Finet2008}.
-Archives of sub-daily precipitation datasets were not available on a long period in order to assess the improvement of the prediction.
-In order to assess this potential gain, precipitation data with a resolution of 10 minutes on a respectable archive length was used (section \ref{sec:data}).
+In order to assess this potential improvement of the prediction, precipitation data with a resolution of 10 minutes on a respectable archive length was used (section \ref{sec:data}).
 It was then aggregated in the form of 24~h totals, but at a 6-hourly time step, by means of a moving average (section \ref{sec:method}).
@@
 
-%COMPLETE
-
 \section{Study area and data}
@@
 
-The study area is the upper Rh\^{o}ne catchment in Switzerland.
+The study area is the upper Rh\^{o}ne catchment in Switzerland \cite[study area of][]{Horton2012a}.
 Due to the low density of weather stations with high temporal resolution and long archives, no aggregation or catchment rainfall was processed.
-The time series (on the period 1982-2007) come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle.
-The results will often be presented arbitrarily for the Ulrichen station, but the results are exactly the same for all stations.
+The time series (on the period 1982-2007) come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle, which are subject to various meteorological influences \citep{Horton2012}.
+The results will thereafter be presented arbitrarily for the Ulrichen station, but they are equivalent for all stations.
 
-%WRITE
+Predictors are extracted from the NCEP/NCAR reanalysis I \citep{Kalnay1996} dataset with a 6-hourly temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree.
 
-%FIGURE
+% FIGURE (MAP)
 
-\section{The sliding time window approach}
+\section{The sliding time window (STW) approach}
 \label{sec:method}
@@
 	\caption{Synthesis of the changes in the S1 criteria, due to the STW, for the Ulrichen station, depending on the ranks of the analogue.
-(top) Quantiles of the S1 distributions with and without the sliding window.
-(bottom) Quantiles of the relative improvements of the S1 criteria when using the sliding window.}
+(top) Quantiles of the S1 distributions with and without the STW.
+(bottom) Quantiles of the relative improvements of the S1 criteria when using the STW.}
 	\label{fig:changes_S1}
@@
 	\end{center}
-	\caption{Seasonal effect on the median reduction of the S1 criteria for the Ulrichen station due to the sliding time window. DJF: winter, MAM: spring, JJA: summer SON: fall.}
+	\caption{Seasonal effect on the median reduction of the S1 criteria for the Ulrichen station due to the STW. DJF: winter, MAM: spring, JJA: summer SON: fall.}
 	\label{fig:changes_S1_seasons}
@@
 	\caption{Synthesis of the changes in the RMSE criteria, due to the STW, for the Ulrichen station, depending on the ranks of the analogue.
-(top) Quantiles of the RMSE distributions with and without the sliding window.
-(bottom) Quantiles of the relative improvements of the RMSE criteria when using the sliding window.}
+(top) Quantiles of the RMSE distributions with and without the STW.
+(bottom) Quantiles of the relative improvements of the RMSE criteria when using the STW.}
 	\label{fig:changes_RMSE}
@@
 However, finding better analogue situations does not obligatory imply better forecast skills.
-Therefore, we have to assess the impact of the introduction of the sliding time window, and thus the selection of other analogue dates, on the performance scores.
+Therefore, we have to assess the impact of the introduction of the STW, and thus the selection of other analogue dates, on the performance scores.
 In order to perform this assessment, the 24~h-totals (moving average) at a 6-hourly time step were used (see section \ref{sec:data}).
@@
 	\includegraphics[width=5cm]{figures/changes_CRPS_precip_threshold.pdf}
-	\caption{Differences of the CRPSS performance score, due to the introduction of the sliding time window, as a function of precipitation thresholds at the Ulrichen station.
-The stars represent averages.}
+	\caption{Differences of the CRPSS performance score, due to the introduction of the STW, as a function of precipitation thresholds at the Ulrichen station. The stars represent averages.}
 	\label{fig:changes_CRPS_precip_threshold}
@@
 The values of the CRPSS scores for both methods (Table \ref{table:CRPSS_recalibration}) have significantly increased after recalibration.
-With the introduction of the sliding time window, we get back the performance loss related to the reduction of the archive length.
+With the introduction of the STW, we get back the performance loss related to the reduction of the archive length.
 In our case, this improvement is approximately a doubling of the archive size.
@@
 \begin{table}[htb]
-	\caption{Changes in sharpness and accuracy relatively to the total CRPS, due to the introduction of the sliding time window.
+	\caption{Changes in sharpness and accuracy relatively to the total CRPS, due to the introduction of the STW.
 The changes are presented for both 2Z and 2Z-2MI methods with the original parameters.
@@
 These attempts to transpose the STW on the total archive highlight the importance of the actual chronology of rainfall.
-The sliding window is profitable, provided that the precipitation series are close to the observed one.
+The STW is profitable, provided that the precipitation series are close to the observed one.
 Without precipitation series with an accurate sub-daily chronology, the introduction of a STW is not appropriate.
@@
 
-As \citet{Finet2008} had previously shown, the introduction of a sliding time window allows finding better analogue situations in terms of the atmospheric circulation.
+As \citet{Finet2008} had previously shown, the introduction of a STW allows finding better analogue situations in terms of the atmospheric circulation.
 It has been here demonstrated that the improvement of the S1 criteria values is growing with the rank of the analogue.
@@
 The second source is the establishment of precipitation reanalysis at a country scale, or the use of reanalysis-driven RCMs (Regional Climate Models) or LAMs (Limited Area Models) on a long period.
-When such precipitation data will be available, the use of a STW in the AM should be considered for any application, especially when the prediction quality of extreme events are important.
+When such precipitation data will be available, the use of a STW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.
 

### 2015-12-17 Moving temporal window - HESS/template.tex
Removing the we...

@@
 The AM is usually implemented with a daily time step, due to the availability of long precipitation archives that have no equivalent to a finer resolution.
-Therefore, the analogues situations are assessed on the basis of a daily time step, by comparing predictors at fixed hours of the day, otherwise we would not know what precipitation values to assign to them.
-However, we can expect that the analogy of the synoptic situations do not occur systematically at the same time of the day, and that better candidates can be found at different times.
-On this assumption, we introduced a sliding time window (STW) to allow searching for candidates at different hours of the day.
+Therefore, the analogues situations are assessed on the basis of a daily time step, by comparing predictors at fixed hours of the day, otherwise one would not know what precipitation values to assign to them.
+However, it can be expected that the analogy of the synoptic situations do not occur systematically at the same time of the day, and that better candidates can be found at different times.
+On this assumption, a sliding time window (STW) was introduced to allow searching for candidates at different hours of the day.
 
@@
 The first reason is that the 6-hourly time series generated by the AM may not represent well the dynamic of the accurate precipitation (results not shown), due to a smoothed signal.
-Then, sometimes we just don't need finer resolution than the daily time step.
+Then, sometimes one just does not need finer resolution than the daily time step.
 Finally, when using a reconstructed precipitation archive, the errors in intra-day precipitation distributions have a lesser impact.
@@
 Indeed, the position of the driving elements such as the low-pressure area and the fronts change significantly during a day.
-We can therefore expect to improve particularly these situations with a higher dynamism when introducing a STW, as we may find better matches to the target situation.
+We can therefore expect to improve particularly these situations with a higher dynamism when introducing a STW, as better matches to the target situation may be found.
 
 The dynamism of a given atmospheric condition cannot be easily quantified.
-We thus consider here the basic assumption that the more a day is rainy, the more dynamic the situation is.
+A basic assumption is considered here, which stipulates that the more a day is rainy, the more dynamic the situation is.
 The results of this analysis are summarized in Figure \ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for days with precipitation between two thresholds.
@@
 
-When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the candidates situations are not more numerous, as we subsample in the previously $N_{1}$ selected analogues, but the dates may have changed.
+When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the candidates situations are not more numerous, as they are subsampled in the previously $N_{1}$ selected analogues, but the dates may have changed.
 In contrast to earlier, both a reduction and an increase of the RMSE criterion values are possible.
@@
 However, finding better analogue situations does not obligatory imply better forecast skills.
-Therefore, we have to assess the impact of the introduction of the STW, and thus the selection of other analogue dates, on the performance scores.
+Therefore, the impact of the introduction of the STW, and thus the selection of other analogue dates, has to be assessed on the performance scores.
 In order to perform this assessment, the 24~h-totals (moving average) at a 6-hourly time step were used (see section \ref{sec:data}).
-The target dates remain unchanged, since we keep the original time slot (6~h~UTC - 6~h~UTC the next day), and thus the performance scores can be directly compared with the former ones.
+The target dates remain unchanged, since the original time slot (6~h~UTC - 6~h~UTC the next day) is kept, and thus the performance scores can be directly compared with the former ones.
 
@@
 The values of the CRPSS scores for both methods (Table \ref{table:CRPSS_recalibration}) have significantly increased after recalibration.
-With the introduction of the STW, we get back the performance loss related to the reduction of the archive length.
+With the introduction of the STW, the performance loss related to the reduction of the archive length is retrieved.
 In our case, this improvement is approximately a doubling of the archive size.
@@
 
-As we saw in the previous section, the performance improvement brought by the STW is lost when using a simplistic precipitation time series.
+As demonstrated in the previous section, the performance improvement brought by the STW is lost when using a simplistic precipitation time series.
 In order to get closer to the chronology of the accurate precipitation, the reconstruction procedure must rely on some informative variable.
@@
 The location of the most predictive point from the reanalysis grid had to be assessed (closest points: 5\textdegree\~-~7.5\textdegree\ longitude and 45\textdegree\~-~47.5\textdegree\ latitude), as well an eventual time lapse between both series, due to the significant distance separating the weather stations and the reanalysis grid point.
-The most relevant point will probably not be the same for all stations, since we can expect to find the optimum in the direction of the main moisture inflows for the station.
+The most relevant point will probably not be the same for all stations, since one can expect to find the optimum in the direction of the main moisture inflows for the station.
 This assessment must be carried out for each station.
@@
 The impact of the STW on the prediction performance has never been assessed before, due to the shortcoming of long precipitation series at a sub-daily time step.
-We could evaluate the impact of the STW approach on a 25 years time series with a high temporal resolution.
-After the introduction of the STW, the performance scores increased of the same order of magnitude as if we doubled the length of the archive, in this case study.
+The impact of the STW approach could be assessed on a 25 years time series with a high temporal resolution.
+After the introduction of the STW, the performance scores increased of the same order of magnitude as if the length of the archive doubled, in this case study.
 

### 2015-12-18 Moving temporal window - HESS/template.tex
Personal corrections.

@@
 \begin{abstract}
-The Analogue Method (AM) aims at forecasting local weather variables (predictands), such as the precipitation, by means of a statistical relationship with predictors at a synoptic scale.
-The analogy is assessed in the first place on the geopotential field by mean of a comparison of the gradients, in order to sample the days with a similar atmospheric circulation.
+The Analogue Method (AM) aims at forecasting local weather variables (predictands), such as precipitations, by means of a statistical relationship with predictors at a synoptic scale.
+The analogy is generally assessed in the first place on the geopotential field by mean of a comparison of the gradients, in order to sample the days with a similar atmospheric circulation.
 
-The search for candidates situations, for a given target day, is usually undertaken by comparing the state of the atmosphere at fixed hours of the day.
+The search for candidate situations, for a given target day, is usually undertaken by comparing the state of the atmosphere at fixed hours of the day.
 The constraint being the use of daily time series, due to the length of available archives they provide.
-However, it is unlikely that the best analogues happen at the very same hour, but may occur at different time of the day.
-In order to assess the potential of finding better analogues at a different times, a sliding time window (STW) has been introduced.
+However, it is unlikely that the best analogy happens at the very same hour, but it may occur at a different time of the day.
+In order to assess the potential of finding better analogues at a different hour, a sliding time window (STW) has been introduced.
 
 The STW resulted in a better analogy of the atmospheric circulation, with improved values of the analogy criteria on the whole distribution of analogue dates.
-The improvement was found to grow with the analogue ranks due to an accumulation of more similar situations in the predicted distribution.
+The improvement was found to grow with the analogue ranks due to an accumulation of more similar situations in selection.
 Moreover, the improvement is even more important for days with heavy precipitation events, which are generally related to more dynamic atmospheric situations, where timing is more specific.
 
-A seasonal effect has also been identified, with larger improvements in winter that in summer, supposedly due to the stronger effect of the diurnal cycle in summer, which favors predictors at the same hours.
+A seasonal effect has also been identified, with larger improvements in winter than in summer, supposedly due to the stronger effect of the diurnal cycle in summer, which favors predictors at the same hour.
 
@@
 It empathized the need to use time series with an accurate chronology.
-These should be available in a near future, either by means of growing observed time series, or by the establishment of precipitation reanalysis through regional modeling.
+These should be available in a near future, either by means of growing observed archives, or by the establishment of precipitation reanalysis through regional modeling.
 Then, the use of a STW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.
@@
 
-The Analogue Method (AM) is based on the principle that two relatively similar synoptic situations may produce relatively similar local effects, and can be called analogues \citep{Lorenz1956, Lorenz1969}.
+The Analogue Method (AM) is based on the principle that two relatively similar synoptic situations may produce relatively similar local effects \citep{Lorenz1956, Lorenz1969}.
 Multiple variations of the methods exist and listings can be found in \citet{Horton2016} or \citet{BenDaoud2015}.
 The versions that will be considered here are often used as references or benchmarks for various improvements.
-The first implementation relies on an analogy of the atmospheric circulation, and the other adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
 
-The first method is based on the analogy of the synoptic circulation (Table \ref{table:method_2Z}).
+The first method is based on the analogy of the atmospheric circulation \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005, Marty2012}.
 When searching analogue situations for a target day, it starts by a preselection step, which is a selection of the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects.
-Then, the similarity of the atmospheric circulation of a target date with every day of the preselection is assessed by processing the S1 criteria \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
-The considered pressure levels are 500~hPa (Z500) and 1000~hPa (Z1000) \citep{Bontron2005}.
-The $N_{1}$ dates, which is a parameter to calibrate, with the lowest values of S1 are considered as analogues to the target day.
+Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the S1 criteria \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
+The considered pressure levels are 500~hPa (Z500) and 1000~hPa (Z1000).
+The $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day, $N_{1}$ being a parameter to calibrate.
 Then, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
@@
 To calibrate the method, the commonly used technique is a semi-automatic sequential procedure elaborated by \citet{Bontron2004}.
-AtmoSwing \citep{Horton2016}, which implements this technique was used in order to calibrate the parameters in the present study.
-The score that is most often used to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
+AtmoSwing \citep{Horton2016}, which implements this technique, was used in order to calibrate the parameters in the present study.
+The score that is most often considered to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
 It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$.
@@
 The AM is usually implemented with a daily time step, due to the availability of long precipitation archives that have no equivalent to a finer resolution.
-Therefore, the analogues situations are assessed on the basis of a daily time step, by comparing predictors at fixed hours of the day, otherwise one would not know what precipitation values to assign to them.
-However, it can be expected that the analogy of the synoptic situations do not occur systematically at the same time of the day, and that better candidates can be found at different times.
+Therefore, the analogue situations are assessed on the basis of a daily time step, by comparing predictors at fixed hours of the day, otherwise one would not know what precipitation values to assign to them.
+However, it can be expected that the analogy of the synoptic situations do not occur systematically at the same time of the day, and that better candidates can be found at a different hour.
 On this assumption, a sliding time window (STW) was introduced to allow searching for candidates at different hours of the day.
@@
 Previous tests showed the benefit, in terms of analogy criteria values, of searching for analogue synoptic situations at a finer time step, but without assessing the impact on the forecast skills \citep{Finet2008}.
-In order to assess this potential improvement of the prediction, precipitation data with a resolution of 10 minutes on a respectable archive length was used (section \ref{sec:data}).
-It was then aggregated in the form of 24~h totals, but at a 6-hourly time step, by means of a moving average (section \ref{sec:method}).
+In order to assess this potential improvement of the prediction, precipitation data with a resolution of 10 minutes, on a respectable archive length, was used (section \ref{sec:data}).
+It was then aggregated in the form of 24~h-totals, but at a 6-hourly time step, by means of a moving average (section \ref{sec:method}).
 
@@
 
+The changes due to the introduction of a STW was assessed first in regards to the analogy criteria improvement (section \ref{sec:influence_criteria}), and then in terms of precipitation prediction skill (section \ref{sec:influence_scores}).
+Finally, attempts were made to reconstruct longer 24~h-total precipitations series (section \ref{sec:attempts}).
+
 \section{Study area and data}
@@
 
-The study area is the upper Rh\^{o}ne catchment in Switzerland \cite[study area of][]{Horton2012a}.
-Due to the low density of weather stations with high temporal resolution and long archives, no aggregation or catchment rainfall was processed.
-The time series (on the period 1982-2007) come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle, which are subject to various meteorological influences \citep{Horton2012}.
+The study area is the upper Rh\^{o}ne catchment in Switzerland \cite[see also][]{Horton2012a}.
+Due to the low density of weather stations with high temporal resolution and long archives, no aggregated rainfall was processed.
+The time series (on the period 1982-2007) come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle (Figure \ref{fig:map}), which are subject to various meteorological influences \citep{Horton2012}.
 The results will thereafter be presented arbitrarily for the Ulrichen station, but they are equivalent for all stations.
+
+\begin{figure}[htb]
+	\begin{center}
+		\includegraphics[width=8.3cm]{figures/figure_map.pdf}
+	\end{center}
+	\caption{Position of the 6 weather stations of interest (Ulrichen, Zermatt, Visp, Montana, Sion and Aigle) in the study area.}
+	\label{fig:map}
+\end{figure}
 
@@
 
-In order to assess the benefit of searching analogue situations at a sub-daily time step, an appropriate time series is required.
-On the basis of high resolution time series (section \ref{sec:data}), 24~h totals were processed, but at a 6-hourly time step (temporal resolution of the reanalysis dataset), by means of a moving average.
+In order to assess the benefit of searching analogue situations at a sub-daily time step, an appropriate precipitation series is required.
+On the basis of high resolution time series (section \ref{sec:data}), 24~h-totals were processed, but at a 6-hourly time step (temporal resolution of the reanalysis dataset), by means of a moving 24~h-total.
 
@@
 
-Logic suggests a priori that only one situation (the best) is selected per candidate day. An exclusion of the same dates was tested in two different ways: (1)
+Logic suggests \textit{a priori} that only one situation (the best) is selected per candidate day. An exclusion of the same dates was tested in two different ways: (1)
 by excluding the worse analogues in a period of $\pm$ 24~h, and (2) by excluding the worse analogues with the same date.
@@
 
-As sub-daily precipitation time series are usually available on a shorter period than traditional daily time steps, the first assessment consists in assessing the loss of performance resulting from a reduction a 47~years archive (1961 to 2008) to 25~years (1982 to 2007).
+As sub-daily precipitation time series are usually available on a shorter period than traditional daily time steps, the first assessment consists in assessing the loss of performance resulting from a reduction of a 47~years archive (1961 to 2008) to 25~years (1982 to 2007).
 This change is assessed with the original method, without STW.
@@
 Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
-The AM parameters were calibrated using AtmoSwing \citep{Horton2016} on the original archive (Tables \ref{table:method_2Z} and \ref{table:method_2Z-2MI}) and will be used thereafter.
+The AM parameters were calibrated using AtmoSwing \citep{Horton2016} on the original archive (Tables \ref{table:params_2Z} and \ref{table:params_2Z-2MI}) and will be used thereafter.
 
@@
 \section{Influence on the analogy criteria}
+\label{sec:influence_criteria}
 
@@
 
-The median of the S1 values reduction (Figure \ref{fig:changes_S1} bottom) starts approximately at 5~\% for the first analogue and reaches more than 10~\% for the last.
+The median of the S1 values reduction (Figure \ref{fig:changes_S1} bottom) starts approximately at 5~\% for the first analogue and reaches more than 10~\% for the last one.
 This increasing trend with the analogue rank can be explained by the accumulation of better analogues in the distribution.
-The minimum improvement starts from 0 and reaches 2-3\%, meaning that the criteria has been improved for all analogue ranks of the distribution end.
+The minimum improvement starts from 0 and reaches 2-3\%, meaning that the criteria has been improved on most analogues for every day of the calibration period.
 All other stations have a similar improvement of the S1 criteria, both in terms of distribution shape and amplitude.
@@
 \section{Impact on performance scores}
+\label{sec:influence_scores}
 
 A systematic improvement of the S1 values was previously observed.
-However, finding better analogue situations does not obligatory imply better forecast skills.
-Therefore, the impact of the introduction of the STW, and thus the selection of other analogue dates, has to be assessed on the performance scores.
+However, finding better analogue situations does not obligatory imply better skills to predict the precipitation.
+Therefore, the impact of the STW introduction, and thus the selection of other analogue dates, has to be assessed on the performance scores.
 In order to perform this assessment, the 24~h-totals (moving average) at a 6-hourly time step were used (see section \ref{sec:data}).
@@
 The increasing positive trend of skill improvements regarding the precipitation threshold is significant and shows that the prediction of higher precipitation totals is further improved.
-Thus both the analogy criteria and the performance scores are improved to a greater extent for heavier precipitation events.
+Thus, both the analogy criteria and the performance scores are improved to a greater extent for heavier precipitation events.
 On the contrary, the non-rainy days and small accumulations are not improved.
@@
 With the introduction of the STW, the performance loss related to the reduction of the archive length is retrieved.
-In our case, this improvement is approximately a doubling of the archive size.
 
@@
 \section{Application attempts on the full archive}
+\label{sec:attempts}
 
@@
 Unfortunately, there is no long precipitation time series available with a sub-daily time step.
-In order to reconstruct a longer archive of moving averages of 24~h-totals, different disaggregation approaches of the daily time series were assessed and are presented in the following sections.
+In order to reconstruct a longer archive of moving 24~h-totals, different disaggregation approaches of the daily time series were assessed and are presented in the following sections.
 
@@
 The first step consisted in determining which variables from the precipitable water or the relative humidity (at 1000~hPa, 925~hPa or 850~hPa) produces the precipitation chronology that is the most correlated (on non-zero values) with the accurate 6-hourly precipitation time series on the period 1982-2007.
-The location of the most predictive point from the reanalysis grid had to be assessed (closest points: 5\textdegree\~-~7.5\textdegree\ longitude and 45\textdegree\~-~47.5\textdegree\ latitude), as well an eventual time lapse between both series, due to the significant distance separating the weather stations and the reanalysis grid point.
+The location of the most predictive point from the reanalysis grid had to be assessed (closest points: 5\textdegree\ and 7.5\textdegree\ longitude and 45\textdegree\ and 47.5\textdegree\ latitude), as well an eventual time lapse between both series, due to the significant distance separating the weather stations and the reanalysis grid point.
 The most relevant point will probably not be the same for all stations, since one can expect to find the optimum in the direction of the main moisture inflows for the station.
@@
 
-These attempts to transpose the STW on the total archive highlight the importance of the actual chronology of rainfall.
+These attempts to transpose the STW on the total archive highlight the importance of the actual rainfall chronology.
 The STW is profitable, provided that the precipitation series are close to the observed one.
@@
 The parameters were then calibrated again, using the STW.
-Some parameters changed, the main difference being the number of analogues that was found optimal, which systematically and significantly increased compared to the original set.
+Some parameters changed, the main difference being the number of analogues, which systematically and significantly increased compared to the original set.
 A wider selection of analogue situations, containing those whose rank decreased, seemed profitable for the prediction performance.
@@
 Attempts to reconstruct longer time series based on a simplistic proportional distribution or using meteorological variables from the NCEP reanalysis 1 dataset as proxy did not succeed.
+Other reanalysis datasets could eventually preform better.
 

### 2016-01-18 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Michel's corrections.

@@
 \end{equation}
-where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points of the gridded data describing the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
+where $\Delta \hat{z}_{i}$ is the difference in geopotential height between the \textit{i}th pair of adjacent points of the gridded data describing the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
 The differences are processed separately in both directions.
@@
 Using data independent from the CP to validate the results is very important in order to assess the robustness of the improvements and to avoid over-parametrization of the method.
+Parameters determined on the CP are then applied to the VP in order to obtain a performance score for the independent period.
 
@@
 The score was also calculated for three precipitation thresholds: P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_4Zo}).
-The gain in score increases with the precipitation threshold: in average, respectively for the different thresholds, 13.3\%, 15.4\% and 29.1\% for the CP and 7.9\%, 11.1\% and 34.5\% for the VP.
+The gain in score increases with the precipitation threshold: the relative improvement of the CRPSS is in average, respectively for the different thresholds, 13.3\%, 15.4\% and 29.1\% for the CP and 7.9\%, 11.1\% and 34.5\% for the VP.
 The optimization improves thus even more the forecasts for days with significant precipitation than usual days.

### 2016-01-21 AtmoSwing - Geoscientific Model Development/template.tex
Charle's corrections.

--- 2015-11-24 AtmoSwing - Geoscientific Model Development/template.tex
@@
 
-The analogue method allows forecasting local meteorological variables of interest (predictand), such as the daily precipitation, on the basis of synoptic variables (predictors).
+The Analogue Method allows forecasting local meteorological variables of interest (predictand), such as the daily precipitation, on the basis of synoptic variables (predictors).
 It relies on the fact that similar meteorological influences are likely to result in similar local effects.
@@
 
-AtmoSwing is an open source software that implements the analogue method in a very flexible way, so that different variants can be handled dynamically, by parameterization trough XML files.
+AtmoSwing is an open source software that implements the Analogue Method in a very flexible way, so that different variants can be handled dynamically, by parameterization through XML files.
 It is made of 3 tools: the Forecaster to perform operational forecasts, the Viewer to display the results, and the Optimizer to establish the relationship between the predictand and predictors.
 
-The Forecaster handles every required processing internally, such as predictors downloading and parsing, grid interpolation, analogy sorting, without external scripts or file conversion.
+The Forecaster handles every required processing internally, such as predictors downloading and reading, grid interpolation, analogy sorting, without external scripts or file conversion.
 The processing of a forecast is extremely lightweight in terms of IT infrastructure; it can indeed run on almost any computer.
@@
 In hydrometeorology, it consists, given a certain situation, in looking into the past to retrieve situations that can be considered similar and therefore with consequences that may be expected similar to the situation at hand.
-By situation, one often thinks of the atmospheric situation over a rather wide domain.
-By consequence, one often focuses on a local variable of interest, such as the occurrence of hail, storm, avalanches, or the amount of wind or precipitation over a given region.
-
-As a general setting, the required ingredient are a couple of archives, one describing the situation through different variables, called predictors, and another one giving, for those situations, the value of the local variable of interest for engineering purpose, called predictand.
+By situation, one often thinks of the atmospheric situation over a rather wide spatial domain.
+By consequence, one often focuses on a local variable of interest, such as the occurrence of hail, storm, avalanches, or the amount of wind or precipitation over a given region, cumulated on a given time period.
+
+As a general setting, the required ingredients are a couple of archives, one describing the situation through different variables, called predictors, and another one giving, for those situations, the value of the local variable of interest for engineering purpose, called predictand.
 Obviously, one understands that the longest and the richest the candidate archive of predictors, the more chance there will be to extract good analogues for a target situation in order to derive a conditional range of predictand values.
@@
 Usually, the predictand values could be derived in a rather physical-dynamic approach  by modeling the chain of processes linking the predictors to the predictand.
-However, the model may be extremely complex, time consuming, or some processes may be poorly known or parameterised.
-Conversely, given the past archive of predictors, enough situations analogues to a target one could be found so that reasonable values will be obtained for the predictand, at a reasonable coding and computing-time costs.
+The processes involved range from large scale dynamical states of the atmosphere down to very small scale microphysical processes, requiring models that are extremely complex, data-demanding, and time consuming.
+Conversely, given an appropriate set of predictors archives, enough situations analogous to a target one could be found so that reasonable values will be obtained for the predictand, at a reasonable coding and computing-time costs.
 This is particularly true for a predictand much required in hydrometeorological applications, namely the precipitation amount over a given domain and time duration.
-The processes involved range from large scale dynamical states of the atmosphere down to very small scale microphysical processes, requiring models that are extremely complex, data-demanding, and time consuming.
-Therefore, with an appropriate set of archives, one may bypass all these modeling aspects by obtaining the predictand values observed from past analogue situations.
+Incidentally, the forecast will be proposed as a statistical distribution based on the values taken by the predictand in the set of analogues selected, unless one considers only the single best analogue, which may not prove the most efficient.
 
@@
 In operational forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies, it is more and more used to downscale the results of global climate model simulation runs.
-In operational, it should however not be considered as a substitution for numerical weather prediction models, but as a complement in order to get a fast and independent forecast that is known to be accurate several days in advance.
+In operational, it should however not be considered as a substitute for numerical weather prediction models, but as a complement in order to get a fast and partly independent forecast that is known to be accurate several days in advance.
 It therefore enriches the analysis of a potential critical situation for flood forecasting, for example, and is very interesting in early warning.
@@
 Considering a precipitation variable, one has to decide upon the duration of accumulation, (e.g.
-from 6-hourly to daily or several day totals) according for example to the size or response time of a the catchments to be managed.
-The availability and quality of a long enough time series must also be considered.
+from 6-hourly to daily or several day totals) according for example to the size or response time of the catchments to be managed.
+The availability and quality of long enough time series must also be considered.
 Moreover, the analogy is restricted to a selection of variables at a specific time and over optimized spatial domains, that are compared by means of a chosen criteria that can rank the candidate days from the archive with a distance quantification.
@@
 
-The AM will first be presented along with various implementations (section \ref{sec:method}), as the optimal version of the method may vary with the location of interest, and as all these can be processed with AtmoSwing.
+The Analogue Method (AM) will first be presented along with various implementations (section \ref{sec:method}), as the optimal version of the method may vary with the location of interest, and as all these can be processed with AtmoSwing.
 The software will then be presented (section \ref{sec:atmoswing}), and its modules detailed, such as the Forecaster (section \ref{sec:forecaster}) and the Viewer (section \ref{sec:viewer}) that are tools for operational use, and the Optimizer (section \ref{sec:optimizer}) that allows optimizing the method for a given predictand time series.
 
-\section{The analogue method}
+\section{The Analogue Method}
 \label{sec:method}
 
-As AtmoSwing does not rely on one variant of the analogue method (AM), but can implement different parametrization, several examples of possible implementations are gathered here, as well as the main evolution steps of the AM.
+AtmoSwing does not rely on a single variant of the AM, but can implement different parameterizations.
+Thus, several examples of possible implementations are gathered here, as well as the main evolution steps of the AM.
 This latter summarizes the improvements that were brought, as well as discontinued approaches that were found less relevant (such as the use of PCA on the predictors).
@@
 	\item The analogy variable (the predictor) must contain synoptic information having indirect dependency with the local weather and the target predictand (often the precipitation).
-	\item The spatial window is the domain on which the analogy variable is considered. The ideal size of this area is one that maximizes useful information.
-	\item The temporal window is the hour of day at which the analogy variable is considered.
+	\item The spatial window is the domain on which the analogy variable is considered. The ideal size of this area is the one that maximizes useful information.
+	\item The temporal window is the hour, or a set of different hours, in the day at which the analogy variables are considered.
 	\item The preselection, which is often a period of the year in which similar situations are being sought.
@@
 Predictors are generally reanalysis datasets (as archive) and outputs of a global numerical weather prediction models for the target situation in operational forecasting.
-Reanalysis datasets, such as the NCEP/NCAR reanalysis I \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996}, the NCEP/DOE reanalysis II \citep{Kanamitsu2002}, ERA-40 \citep{Uppala2005} are often used and can be inputed in AtmoSwing.
+Reanalysis datasets, such as the NCEP/NCAR reanalysis I \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996}, the NCEP/DOE reanalysis II \citep{Kanamitsu2002}, ERA-40 \citep{Uppala2005} are often used and can be input in AtmoSwing.
 Other observed predictors can also be used, such as Sea Surface Temperature \citep[SST, ][]{Reynolds2007}.
@@
 
-\citet{Bontron2004} determined that the length of the archive should be 30 years to forecast usual situations, and 40 years for intense events.
+\citet{Bontron2004} proposed that the minimum length of the archive should be 30 years to forecast usual situations, and 40 years or more for intense events.
 He also highlighted the dependency between the optimal number of analogues and the archive size: the shorter the archive, the lower the number of analogues.
@@
 This normalization allows for an easier comparison between subregions subject to different precipitation regimes, and thus to better identify the most important contributions.
-Most users also apply a root square to this last ratio in order to reduce the weight of the extreme predictand values, but we generally don't, in order to let to extremes a certain importance.
+Most users also apply a root square to this last ratio in order to reduce the weight of the extreme predictand values, but we generally don't, in order to give extremes a certain weighting.
 
@@
 	\item First level of analogy: $N_{1}$ dates are subsampled within all the candidates provided by the preselection, by means of an analogy ranking.
-The first level of analogy is always the atmospheric circulation when it comes to precipitation forecasting.
-The similarity of the atmospheric circulation of the target date with the candidate situations is thus assessed on the geopotential by means of the S1 criteria \citep[Eq.\ref{eq:S1}, ][see also section \ref{sec:method:evolution}]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
+The first level of analogy is always based on the atmospheric circulation when it comes to precipitation forecasting.
+The similarity of the atmospheric circulation of the target date with the candidate situations is thus assessed on the geopotential by means of the S1 criteria \citep[Eq.\ref{eq:S1}, ][see also section \ref{sec:method:evolution}]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial gridded window.
 
@@
 
-	The $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day. The number of analogues, $N_{1}$, is a parameter to calibrate.
-
-	\item Subsequent level(s) of analogy: the $N_{1}$ analogues are subsampled once again on the basis of another variable in order to obtain a lower number of analogue dates, $N_{2}$.
+	The $N_{1}$ dates with the lowest values of S1 are considered as analogues, in terms of the general circulation, to the target day. The number of analogues, $N_{1}$, is a parameter to calibrate.
+
+	\item Subsequent level(s) of analogy: beyond the similarity of airflows, one may look for similarities in other variables of interest .
+Therefore, the $N_{1}$ analogues are subsampled once again on the basis of another variable in order to obtain a lower number of analogue dates, $N_{2}$.
 The S1 criterion is usually not relevant for other predictors that the atmospheric circulation.
@@
 
-	\item Probabilistic forecast: then, the daily observed precipitation amount (or another predictand of interest) of the $N_{i}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
-The empirical frequencies are processed for every value of the predictand, after classification, based on the Gringorten parameters (for a Gumbel or exponential law).
+	\item Probabilistic forecast: then, the (e.g.
+daily) observed precipitation amount (or another predictand of interest) of the $N_{i}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
+The empirical frequencies are processed for every value of the predictand, after classification, based on the Gringorten parameters (for a Gumbel or exponential law) and a probabilistic model can be fitted (e.g.
+Gamma function, or else).
 
@@
 Variants of the AM parameterization are numerous and it is not always easy to reference them in a short and descriptive way.
-We thus propose a basic nomenclature (Figure \ref{figure:nomenclature}) in order to express the structure in a simple identifier.
+We thus propose a basic nomenclature (Figure \ref{figure:nomenclature}) in order to express the structure into a simple identifier.
 This one cannot describe all the parameters of the AM, but quickly illustrate the structure of the implementation.
@@
 
+The most common usage of the AM is for precipitation forecasting.
+Thus, the evolution presented hereafter focuses on this predictand.
+However, the AM, or an equivalent, was also used for short to medium term forecasting of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+\citet{Guilbaud1997} performed a literature review about the use of the AM in long-term forecasting and identified operational applications for monthly forecasts in many countries, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal forecasts: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
+
 The evolution of the AM for precipitation forecasting led to several improvements.
@@
 Some examples of parameterizations of the most recent AM variant will thus be provided, in the chronological order they appeared.
-The most common usage of the AM is for precipitation forecasting.
-Thus, the evolution presented hereafter focuses on this predictand.
-However, the AM, or an equivalent, was also used for short to medium term forecasting of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
-\citet{Guilbaud1997} performed a literature review about the use of the AM in long-term forecasting and identified operational applications for monthly forecasts in many countries, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal forecasts: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
 
@@
 The geopotential height at 700~hPa and 00~h was used for its higher stability than the sea level pressure (SLP) field, and its sensitivity to the atmospheric disturbances \citep{Guilbaud1997}.
-However, the SLP at 06~h was also used for determining the precipitation intensity, as well as the temperature at 700~hPa as indicator of the thermal state of the air mass \citep{Duband1974}.
+However, the SLP at 06~h was also introduced for determining the precipitation intensity, as well as the temperature at 700~hPa as indicator of the thermal state of the air mass \citep{Duband1974}.
 The data were then based on 37 radiosounding over Europe and condensed by a principal component analysis.
@@
 The archives were split by season to consider comparable situations in terms of distribution of solar energy \citep{Lorenz1969}.
-This initial rigid division into seasons was then transformed into a moving selection of more or less two months around the target date.
-The forecast was then performed only on the basis of observations and was temporally extrapolated to the following two days.
-After a few years, this statistical temporal extrapolation was abandoned in favor of a statistical adaptation using predictors resulting from a numerical model, allowing a forecast over the following 4~days.
-
-Thereafter, the geopotential was considered at 1000~hPa and 700~hPa and the analogues selection was done in two stages: first according to an Euclidean distance in the space of the principal components of the geopotential field at 700~hPa, and then according to a correlation criterion (on the geopotential field at 700 and 1000~hPa, as well as on the thickness between these two levels) in order to remove days too dissimilar \citep{Guilbaud1997}.
-The regression approach to determining precipitation was eventually abandoned in favor of the probabilistic forecasting (synthesized by the percentiles 20, 60 and 90~\%), as it is performed today by interpolating linearly over the cumulative empirical distribution of daily precipitation measured at the analogue days \citep{Guilbaud1997, Guilbaud1998}.
+This initially rigid division into seasons was then transformed into a moving selection of more or less two months around the target date.
+The forecast was then performed only on the basis of radiosonde observations and was temporally extrapolated to the two following days.
+After a few years, this statistical temporal extrapolation was abandoned in favor of a statistical adaptation using synoptic predictors taken from a numerical model, allowing a forecast over the following 4~days.
+
+Thereafter, the geopotential was considered at 1000~hPa and 700~hPa and the analogues selection was done in two stages: first according to an Euclidean distance in the space of the principal components of the geopotential field at 700~hPa, and then according to a correlation criterion (on the geopotential field at 700 and 1000~hPa, as well as on the thickness between these two levels) in order to remove days close in distance but too dissimilar in pattern \citep{Guilbaud1997}.
+The local regression approach to determine precipitation was eventually abandoned in favor of the direct probabilistic forecasting (synthesized by the percentiles 20, 60 and 90~\%), as it is performed today by interpolating linearly over the cumulative empirical distribution of daily precipitation measured at the analogue days \citep{Guilbaud1997, Guilbaud1998}.
 
@@
 \ref{eq:S1}), which allows for a comparison of the gradients and thus an analogy of the atmospheric circulation.
-This work has demonstrated the best performance of the AM compared to regression methods, as well as the interest to search for analogues on two (500 and 1000~hPa) geopotential fields combined \citep{Guilbaud1997}.
+This work has demonstrated the best performance of the AM compared to classical regression based approaches.
 \citet{Woodcock1980} used the same criterion on the SLP fields to select 50~analogues in order to forecast maximum daily temperatures.
-
-\citet{Mandon1985} introduced a second level of analogy and assessed different variables, such as wind, moisture, air temperature, surface temperature of the Mediterranean, the product of wind and the 700~hPa moisture, as well as a second barometric criteria differentiated according to the season.
-\citet{Vallee1986} continued to work on the second level of analogy and considered the wind at 700~hPa \& 12~h in order to improve heavy precipitation events for a region in France susceptible to southerly flows.
-
-Taking advantage of higher-performance IT tools \citet{Guilbaud1997} stopped using PCA in order to work directly with the raw data interpolated on grids, which resulted in an improvement, especially when considering the S1 criterion (already used for analogues selection by \citealp{Wilson1980} and \citealp{Woodcock1980}) instead of the Euclidean distance.
-After comparing this criterion to other criteria from the literature, or combinations of these, \citet{Guilbaud1998} found that S1 is the most efficient.
+After comparing S1 to other criteria from the literature, or combinations of these, \citet{Guilbaud1998} confirmed that S1 is the most efficient.
 They also pointed out the benefit of using 2 atmospheric levels, 1000~hPa (Z1000) and 700~hPa (Z700) or 500~hPa (Z500), instead of one (also instead of the thickness), and to also consider 2 temporal windows, 00~h and 24~h \citep{Obled2002}.
-The number of analogues considered was 50 (Table \ref{table:R0}).
+
+\citet{Guilbaud1997} stopped using PCA in order to work directly with the raw data interpolated on grids, which resulted in an improvement, especially when considering the S1 criterion instead of the Euclidean distance.
+The number of analogues considered was 50.
 When using multiple predictors, they combined the criteria values calculated on each atmospheric level and each temporal window using an arithmetic mean.
-Finally, they also suggested using a second level of analogy on lower layers moisture and introduced the Ranked Probability Score \citep{Epstein1969} to assess the forecast quality, which was found to be more relevant that the Brier score \citep{Brier1950}.
+
+At the dawn of the new millennium, \citet{Bontron2004} could benefit from a real breakthrough, the newly available NCEP/NCAR reanalysis data.
+This dataset being more homogeneous, much longer, and containing more variables than what was previously used, he could systematically assess a large selection of variables in the AM combined with different criteria.
+He thus confirmed the interest of the geopotential height along with the S1 criterion for the first level of analogy.
+He has also shown that the choice of the temporal window (time of observation) has a higher importance than the atmospheric level for the performance of the AM for daily precipitations.
+By assessing multiple combinations of atmospheric levels and temporal windows, he concluded that the coupled geopotential heights at 1000~hPa (Z1000) \& 12~h and 500~hPa (Z500) \& 24~h provided the best performance for the studied region (Table \ref{table:R1}).
+The analogy on the atmospheric circulation proposed by \citet{Bontron2004} is still, at the time of writing, often used operationally, and considered as a reference for benchmarking new parameterizations \citep{Horton2012, BenDaoud2015}.
 
 \begin{table}[htbp]
-	\caption{Method of type PC-4Z proposed by \citet{Guilbaud1997}.
+	\caption{Method of type PC-2Z proposed by \citet{Bontron2004}.
 The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window).
 The criteria used for the current level of analogy is then provided, as well as the number of analogues.}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 00, 24~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
-		& Z700 $^{\dagger}$ & 00, 24~h & & \\ 
-		\bottomhline 
-	\end{tabular} 
-	\belowtable{$\dagger$ or Z500 as an alternative}
-	\label{table:R0}
-\end{table}
-
-\citet{Bontron2004} could benefit from the newly available NCEP/NCAR reanalysis data.
-This dataset being more homogeneous, much longer, and containing more variables than what was previously used, he could systematically assess a large selection of variables in the AM combined with different criteria.
-He thus confirmed the interest of the geopotential height along with the S1 criterion for the first level of analogy.
-He has also shown that the choice of the temporal window (time of observation) has a higher importance than the atmospheric level for the performance of the AM.
-By assessing multiple combinations of atmospheric levels and temporal windows, he concluded that the coupled geopotential heights at 1000~hPa (Z1000) \& 12~h and 500~hPa (Z500) \& 24~h provided the best performance for the studied region (Table \ref{table:R1}).
-The analogy on the atmospheric circulation proposed by \citet{Bontron2004} is still, at the time of writing, often used operationally, and considered as a reference for benchmarking new parameterizations \citep{Horton2012, BenDaoud2015}.
-
-\begin{table}[htbp]
-	\caption{Method of type PC-2Z proposed by \citet{Bontron2004}. Same conventions as Table \ref{table:R0}}
 	\begin{tabular}{ccccc}
@@
 
+\citet{Mandon1985} tried to introduce a second level of analogy and assessed different variables, such as wind, moisture, air temperature, surface temperature of the Mediterranean, the product of wind and the 700~hPa moisture, as well as a second barometric criteria differentiated according to the season.
+\citet{Vallee1986} continued to work on the second level of analogy and considered the wind at 700~hPa \& 12~h in order to improve heavy precipitation events for a region in France susceptible to southerly flows.
+
 \citet{Bontron2004} also assessed several variables for the second level of analogy and identified the moisture variables (precipitable water and relative humidity) and vertical velocity to be the most relevant.
 Finally, he found that a moisture index made of the product of relative humidity at 850~hPa (RH850) and total precipitable water (TPW) gave the best performance (Table \ref{table:R2}).
-This index does not represent an actual physical quantity, but expresses the water content of the column and its proximity to saturation.
+This index does not represent an actual physical quantity, but expresses the water content of the air column and its proximity to saturation.
 
 \begin{table}[htbp]
-	\caption{Method of type PC-2Z-2MI proposed by \citet{Bontron2004}. Same conventions as Table \ref{table:R0}}
+	\caption{Method of type PC-2Z-2MI proposed by \citet{Bontron2004}. Same conventions as Table \ref{table:R1}}
 	\begin{tabular}{ccccc}
@@
 
-He noted the relevance of defining different spatial windows for each region, rather than a single window to the entire territory.
-These windows are more able to represent the specific atmospheric influences for the region.
+He noted the relevance of defining different spatial windows for each region, rather than a single window for the entire territory.
+These windows are more able to represent the specific atmospheric influences for each region.
 In order to assess the forecast, he introduced the Continuous Ranked Probability Score \citep[CRPS, Eq.
-\ref{eq:CRPS}, ][]{Brown1974}, which discards the issue of determining classes as with the RPS previously in use.
+\ref{eq:CRPS}, ][]{Brown1974}, which discards the issue of determining classes as with the Ranked Probability Score \citep{Epstein1969} previously in use.
 
@@
 He first proposed to change the hours of observation for both levels of analogy (both for 06~h and 18~h), and selected the 925~hPa level for the moisture analogy (Table \ref{table:R3a}).
-The selected hours and atmospheric levels were not available before.
+The selected hours and atmospheric levels were not available before in the reanalysis dataset.
 
 \begin{table}[htbp]
-	\caption{Method of type PC-2Z-2MI proposed by \citet{Marty2010}. Same conventions as Table \ref{table:R0}}
+	\caption{Method of type PC-2Z-2MI proposed by \citet{Marty2010}. Same conventions as Table \ref{table:R1}}
 	\begin{tabular}{ccccc}
@@
 \begin{table}[htbp]
-	\caption{Method of type PC-2Z-2MF proposed by \citet{Marty2010}. Same conventions as Table \ref{table:R0}}
+	\caption{Method of type PC-2Z-2MF proposed by \citet{Marty2010}. Same conventions as Table \ref{table:R1}}
 	\begin{tabular}{ccccc}
@@
 \begin{table}[htbp]
-	\caption{Method of type P2T-2Z-4MI (or P2T-2Z-10MI for the alternative version), by \citet{BenDaoud2010}. Same conventions as Table \ref{table:R0}}
+	\caption{Method of type P2T-2Z-4MI (or P2T-2Z-10MI for the alternative version), by \citet{BenDaoud2010}. Same conventions as Table \ref{table:R1}}
 	\begin{tabular}{ccccc}
@@
 
-Subsequently, \citet{BenDaoud2010} added an additionally level of analogy, between the circulation and the moisture analogy (Table \ref{table:R5}), based on vertical velocity at 850~hPa (W850).
+Subsequently, \citet{BenDaoud2010} added an additional level of analogy, between the circulation and the moisture analogy (Table \ref{table:R5}), based on vertical velocity at 850~hPa (W850).
 This AM was developed for large floodplains in France, but was found to be not relevant for an Alpine environment where topography is mostly responsible for uplift of air masses \citep{Horton2012}.
@@
 \begin{table}[htbp]
-	\caption{Method of type P2T-2Z-4W-4MI, by \citet{BenDaoud2010}. Same conventions as Table \ref{table:R0}}
+	\caption{Method of type P2T-2Z-4W-4MI, by \citet{BenDaoud2010}. Same conventions as Table \ref{table:R1}}
 	\begin{tabular}{ccccc}
@@
 
-\citet{Bliefernicht2010} proposed to add a weighting to the grid points of the predictor to overcome a comparison on a fixed-size window, and to give more importance to regions with relevant atmospheric circulation information.
+\citet{Bliefernicht2010} proposed to add a weighting to each grid points of the predictor domain to overcome a comparison on a fixed-size window, and to give more importance to regions with relevant atmospheric circulation information.
 However, he noticed that there is a risk of overparametrization as the performance was not stable between the calibration and the validation periods, and a simplification of the weighting fields may be necessary.
-He also compare the performance of the AM with a forecasting method based on a weather types approach, and concluded that the AM was more efficient.
+He also compared the performance of the AM with a forecasting method based on a weather types approach, and concluded that the AM was more efficient.
 
 \citet{Horton2012} identified that the analogy on the atmospheric circulation may not be comprehensive, and that a significant gain was obtained by considering 4 atmospheric levels (1000, 850, 700, and 500~hPa at 12 or 24~h) instead of 2 (Table \ref{table:R6}).
-No number of analogues ($N_{1}$) was provided globally, as it was calibrated for every subregion.
-Considering an AM only based on the atmospheric circulation has an interest for operational forecasting, where moisture variables are less well forecasted for a lead time of a few days.
+The number of analogues ($N_{1}$) was not provided globally, as it was calibrated for every subregion.
+Considering an AM only based on the atmospheric circulation has an interest for operational forecasting, since moisture variables are less well forecasted for a lead time of a few days.
 An equivalent structure was also optimized by means of generic algorithms (PC-4Zgo), which is the topic of another paper \citep{Horton2016b}.
@@
 \begin{table}[htbp]
-	\caption{Method of type PC-4Z proposed by \citet{Horton2012}. Same conventions as Table \ref{table:R0}}
+	\caption{Method of type PC-4Z proposed by \citet{Horton2012}. Same conventions as Table \ref{table:R1}}
 	\begin{tabular}{ccccc}
@@
 \begin{table}[htbp]
-	\caption{Method of type PC-4Z-2MI, by \citet{Horton2012}. Same conventions as Table \ref{table:R0}}
+	\caption{Method of type PC-4Z-2MI, by \citet{Horton2012}. Same conventions as Table \ref{table:R1}}
 	\begin{tabular}{ccccc}
@@
 The optimal predictors vary from one region to another, along with the leading atmospheric processes.
-One will thus never get a unique parameterization of the AM valid for any place on earth, but the method needs to be adapted to the local conditions and to the size of the catchment of interest.
+One will thus never get a unique parameterization of the AM valid for any place on earth, but the method needs to be adapted to the local conditions, available data, and to the size of the catchment of interest.
 Thus, there will always be local adaptations to be made for use in a new region.
-
-% TODO : Sabine
-% TODO : Jérémie Chardon
 
@@
 \citet{Hamill2006} used an analogy based approach on the GFS reforecasts in order to correct systematic errors in the ensemble forecasts of temperature and precipitation.
-Indeed, the statistical approach showed some bias in estimates of the numerical model, which may have been adjusted by taking into account the intrinsic local climatology from the AM.
+Indeed, the statistical approach pointed at some bias in estimates of the numerical model, which may have been adjusted by taking into account the intrinsic local climatology from the AM.
 Moreover, the under-dispersion of the ensemble forecast from the numerical model has been corrected using analogues \citep{Hamill2006}.
@@
 \citet{Bliefernicht2010} observed that the performance of the AM is higher for winter than for summer.
-The relationship between synoptic predictors and local rainfall is lower in summer, due to convective precipitation that present a higher spatial variability and that depend on other parameters.
+The relationship between synoptic predictors and local rainfall is lower in summer, due to convective precipitations that present a higher spatial variability and that depend on other parameters.
 Variables describing the synoptic circulation are indeed not able to predict the location of thunderstorm cells.
@@
 
-One of the AM limitations is the need for a substantial archive of the predictand variable, for example measured precipitations.
+One of the AM limitations is the need for a substantial archive of the predictand variable, for example measured precipitations, that remain to be provided by the user.
 Without data on several decades, the AM is not applicable.
-Long predictor archives are also required, but this problem is usually solved with reanalysis data, which are not perfect in terms of homogeneity, but can be considered of sufficient quality.
-Moreover,  reanalysis data are available all around the world, which represent a great potential for the AM.
-Another issue, still about data, concerns the operational forecasting: predictors describing forecasted target situations and the ones from the archive are not fully homogeneous, as they usually don't result from the same model.
+Conversely, long predictor archives are also required, but this problem is now solved with reanalysis data, which may not be perfect in terms of homogeneity, but can be considered of sufficient quality.
+Moreover,  reanalysis data are available all around the world, which represent a great potential for the AM, and some are now extending to the whole 20$^{th}$ century.
+Another issue, still about data, concerns the operational forecasting: predictors describing forecasted target situations and the ones from the archive are not fully homogeneous, as they usually don't result from the same model and resolution.
 It is therefore necessary to use robust variables that depend from the numerical model characteristics at a minimum extent.
@@
 Indeed, in a limited weather archive, events with high return periods are not so numerous.
-Their number is certainly lower than the number of analogues considered, which can introduce a bias in the forecast.
+Their number is certainly lower than the standard number of analogues considered, which can introduce a bias in the forecast.
 There are however techniques to correct this bias \citep[see][]{Marty2010}.
 
-It is legitimate to raise the question of the relevance of an approach based on archives of past situations in a context of climate change.
+It is also legitimate to raise the question of the relevance of an approach based on archives of past situations in a context of climate change.
 The first potential issue is a possible change in atmospheric circulation.
@@
 Thus, if the archive of weather situations is long enough, it is reasonable to assume that a large part of future situations is already represented, even those whose frequency will change under different climatic conditions \citep{Wetterhall2005}.
-In addition, climate change is relatively slow, and through continuous updating of the archive, the AM will incorporate new information progressively with no big discontinuity.
+\citet{Dayon2015} has proven these assumptions to be accurate by showing the transferability in the future climate of the AM.
+They could demonstrate that the AM was able to predict the same trends in precipitations changes than Regional Climate Models.
+In addition, for operational use, climate change is relatively slow, and through continuous updating of the archive, the AM will incorporate new information progressively with no strong discontinuity.
+However, this may plea in favor of the approach proposed by \cite{BenDaoud2010} for defining the potential candidates to analogy: instead of considering a fixed period of two months before and after the target dates, one would prefer to select candidates that have approximately the same range of temperature.
 
@@
 
-\subsection{Modular approach}
+\subsection{Modular approach and implementation}
 
@@
 
-Each implementation of the AM (see section \ref{sec:method:evolution}) may enter this scheme, even if it consists of manipulated variables (e.g.
+Each implementation of the AM (see section \ref{sec:method:evolution}) may enter this scheme, even if it consists of preprocessed variables (e.g.
 moisture index).
@@
 
-Although processing an analogue forecast for a given target date is fast, when optimizing the AM, forecasts are processed over long periods of several decades, which is time consuming.
+Although processing an analogue forecast for a given target date is fast, when optimizing the AM, forecasts are re-processed over long periods of several decades, which may become very time consuming.
 Thus, great effort has been made in order to reduce the processing time to a minimum.
@@
 
-The Forecaster module allows to process operational forecasts.
-This software processes a current or past forecasting, defined by an XML file.
+The Forecaster module allows to process operational forecasts, defined by an XML file.
 A list of parameterizations is processed successively.
@@
 It then interpolates the gridded data to match the resolution of the archive (for example 2.5\textdegree\ in the case of the NCEP/NCAP reanalysis I).
-The analogues dates are next sought according to the provided parameterization, and the predictand data are associated with the corresponding dates.
+The analogues dates are next sought according to the selected parameterization, and the predictand data are associated with the corresponding dates.
 The results are finally saved in auto-describing NetCDF files.
@@
 
-When using a parameterization of the AM, previously optimized in perfect prognosis \citep[optimization on the reanalysis dataset, without taking into account the uncertainty of operational forecasts,][]{Klein1963}, in operational forecasting, one should take into account the increasing uncertainty of the predictor with the lead time.
-An available option, proposed by \citet{Thevenot2004}, is to increase the number of analogues with the lead time.
-These values should be optimized, for every lead time, by using reforecast data of the model considered for operational forecasting.
+When using a given parameterization of the AM, it has previously been optimized in a perfect prognosis context \citep[i.e.
+by optimizing on the reanalysis dataset; however, this does not take into account the uncertainty of the target situation when taken from operational forecasts of a NWP model,][]{Klein1963}.
+In operational forecasting, one should take into account the uncertainty of the predictor increasing with the lead time.
+A solution, presented in section \ref{sec:optimization-operational}, consists in increasing the number of analogue situations to keep with the lead time.
+This technique is available in AtmoSwing, as the number of analogues can be specified for every lead time, making such approach easily accessible.
 
@@
 When it is opened, it automatically loads the most recent forecasts, eliminating the need to manually open files.
-It first offers a quick overview of possible alerts by means of color codes on the lead time switcher (upper right in the GUI, see Figure \ref{figure:atmoswing-viewer-gui}), which synthesizes the worst case scenario, or in the alarms panel (on the left part of the GUI).
+It first offers a quick overview of possible alerts by means of color codes on the lead time switcher (upper right in the graphical user interface (GUI), see Figure \ref{figure:atmoswing-viewer-gui}), which synthesizes the worst case scenario, or in the alarms panel (on the left part of the GUI).
 The alarms panel offers a synthesis of the higher forecasted values over the region, for the different AMs and the different lead times.
@@
 The user can choose to hide any data or to display supplementary information (all analogues, all 10$^{th}$ percentiles, or all return periods) in the left panel.
-Traces of old forecasts are also automatically loaded and displayed in order to inform on the stability of the forecasts.
+Traces of previous days forecasts are also automatically loaded and displayed in order to inform on the stability of the forecasts.
 
@@
 \subsection{Interpreting a precipitation forecast}
+\label{sec:interpreting}
 
@@
 If, for example, it is shifted to higher values, there is a risk of under-estimating the event when considering the middle of the full distribution.
+Obviously, if the target situation has its best analogues with high precipitations, then this situation is likely to be rare.
+So, when collecting a fixed number of analogue situations, the worst ones are likely to be more common and will contribute to lower the resulting precipitation distribution, therefore a trend towards underestimation.
 
@@
 
-When comparing the performance of Meteo France numerical models along with the AM, \citet{Djerboua2001} concluded that the numerical models are better at predicting the current day, but the AM becomes more competitive for the following lead times.
-It is indeed very interesting in early warning approaches, as it is able to identify a potentially critical situation one week ahead.
+When comparing the performance of Meteo France numerical models along with the AM, \citet{Djerboua2001} concluded that the numerical models were at that time better at predicting the precipitation of the current day, but the AM became more competitive for the following lead times.
+It is indeed very interesting in early warning approaches, as it may able to identify a potentially critical situation one week ahead.
 
 All AMs rely on atmospheric circulation information, while some add subsequent levels of analogy on moisture or other thermodynamic predictors (see section \ref{sec:method:evolution}).
-However, these subsequent predictors were found to be relevant only on the first 3~days, and not much further, due to higher uncertainties in their forecast.
-This was found to be the case of moisture indexes and vertical velocity.
+However, these subsequent predictors were found to be relevant only on the first 3~days, and not much further, due to higher uncertainties in their forecast (see section \ref{sec:optimization-operational}).
+This was found to be the case for moisture indexes and vertical velocity.
 The user has to keep this aspect in mind when interpreting forecasts over a range of lead times.
@@
 AtmoSwing Optimizer is a single tool that integrates different optimization methods, presented in section \ref{sec:atmoswing-calibration} to \ref{sec:atmoswing-optimization}.
+Optimization is essentially performed in the calibration framework (section \ref{sec:calibration-framework}), where one tries to maximize (by means of performance scores, see section \ref{sec:forecasts-scores}) the information that can be extracted from the available predictors and predictand archives.
+
+However, in operational use, a further ingredient arises : the model from which the target synoptic situations are taken for the coming days, and the increasing uncertainty related to the lead time.
+Depending on the properties of these forecasts, the operational scheme has to be tuned (section \ref{sec:optimization-operational}).
 
 \subsection{Calibration framework}
+\label{sec:calibration-framework}
 
@@
 Perfect prognosis uses observed or reanalyzed data to calibrate the relationship between predictors and predictands.
-Then, when used in operational forecasting, this relationship is applied to global model forecasts, that contains larger uncertainties.
-This framework allow us to identify relationships that are as close as possible to the natural links between predictors and predictands, by reducing uncertainties related to numerical forecasting models.
-However, no model is perfect, and even reanalysis data contain a bias that cannot be ignored.
-For this reason, the statistical relationships identified in the perfect prognosis framework should be applied to model outputs that are as similar as possible to the model used to elaborate the reanalysis.
+As a result, this framework will identify and provide us with relationships that are as close as possible to the natural links between predictors and predictands.
+However, no model is perfect, and even reanalysis data may contain bias that cannot be ignored.
+The calibration process has to try to cope with such bias, but also with the data spatial resolution, that may be too rough for certain variables like humidity or vertical velocity.
+For these reasons, the statistical relationships identified in the perfect prognosis framework should hopefully be applied to new target situations (e.g.
+resulting from an operational NWP model) with characteristics as similar as possible to the those of the reanalyses.
 
@@
 The statistical relationship is established on a calibration period that is as long as possible.
-For every day of this period, a search for analogues is processed, the predictand data are associated with the corresponding dates and a forecast score is calculated.
+For every day of this period, a search for analogues is performed, the predictand data are associated with the corresponding dates and a forecast score is calculated.
 During the search for analogues situations, 120 days around the target date are excluded (thus excluding data in the same year) in order to consider only truly independent candidates days.
@@
 In order to account for climate change and the evolution of the measuring techniques, it is recommended to use a noncontinuous period for validating, distributed over the whole archive \citep{BenDaoud2010}.
-The user can thus specify a list of the years to keep for the validation and AtmoSwing Optimizer handles this aspect easily by both removing the validation years from possible candidate situations, and by automatically processing the validation score at the end of the optimization.
+The user can thus specify a list of the years to keep for the validation and AtmoSwing Optimizer handles this aspect easily by both removing the validation years from possible candidate situations, and by automatically processing the validation score on these years at the end of the optimization.
 
 \subsection{Implemented forecasts scores}
+\label{sec:forecasts-scores}
 
@@
 	\begin{enumerate}
-		\item meteorological variable,
-		\item pressure level,
-		\item temporal window (hour of observation),
-		\item initial analogue numbers.
+		\item meteorological variable (e.g. geopotential, temperature, relative humidity, etc.),
+		\item pressure level (e.g. 700 hPa, ...),
+		\item temporal window (hour of observation - e.g. 6, or 12~h~UTC),
+		\item initial analogue numbers (e.g. $N_{1}=50$).
 	\end{enumerate}
@@
 (iv) The spatial window grows up by repeating the previous steps, until no improvement is reached.
-		\item The number of analogue situations is optimized for the current level of analogy.
-		\item A new level of analogy can be added, based on other variables (such as the moisture index) on predefined pressure levels and time frames.
+		\item The number of analogue situations is then reconsidered and optimized for the current level of analogy.
+		\item A new level of analogy can then be added, based on other variables (such as the moisture index) on predefined pressure levels and time frames.
 The number of analogues for the next level of analogy is initiated at a chosen value.
 Then, the procedure starts again from step (a) for the new level.
-The parameters calibrated on the previous analogue levels are fixed and do not change (except the number of analogues, at the final stage).
+The parameters calibrated on the previous analogue levels are fixed and do not change (except the numbers of analogues of all levels of analogy, that are optimized once again at the final stage).
 	\end{enumerate}
@@
 It helps understanding how different parameterizations can end up to relatively similar performances.
-Using Mote Carlo analyses allows to easily display the parameters sensitivity while allowing a high degree of freedom to the AM.
+Using Monte Carlo analyses allows to easily display the AM parameters sensitivity.
 
@@
 
-Due to limitations of the sequential approach, we decided to explore optimization techniques that can handle all parameters fully automatically.
-The \citet{Nelder1965a} method was first assessed, but was found to be unsuitable for this purpose.
+Due to limitations in the sequential approach, we decided to explore optimization techniques that could handle all parameters fully automatically.
+The \citet{Nelder1965a} method was first assessed, but was found unsuitable for this purpose.
 Because of the complexity of the AM and its non-linearity, a technique of global optimization is required.
@@
 This allows for a fully automatic and objective optimization of the AM.
-However, as this topic is rather consequent and the code base is not yet released, it is the subject of other publications \cite[see][]{Horton2016a, Horton2016b}.
+However, as this topic is rather consequent, it is the subject of other coming publications \cite[see][]{Horton2016a, Horton2016b}.
+
+\subsection{Optimization for operational use}
+\label{sec:optimization-operational}
+
+Up to now, the AM has been optimized essentially by replaying past situations that were taken from a unique meteorological archive.
+Therefore, the synoptic variables have similar properties in terms of resolution, models that have processed them, etc...
+However, when it comes to operational forecasting, as already mentioned, the resulting AM will be applied to target situations that are no longer similar to the reanalyzed ones.
+They will be taken from global model forecasts, which may not be those used to elaborate the archive of reanalyzed situations.
+Thus, these new targets will display characteristics different from those of the archive, and will in particular contain larger uncertainties, especially at growing lead-times.
+
+Eventually, a meteorological variable that was proven to be a good predictor during the calibration of the AM may be poorly predicted by the forecast NWP model selected beyond a certain lead time.
+In this regards, it should be dropped after the lead time in question (see section \ref{sec:interpreting}).
+
+To assess and address these operational aspects, the best option is to collect a dataset of re-forecast from the specific NWP model selected.
+Then, distinct variants of AM parameterizations can be assessed on different lead times.
+For example, when using moisture variables for the second level of analogy, \citet{Thevenot2004} showed that beyond a lead time of 3 days, the AM with two levels did not do better that the one with a unique level of analogy.
+It comes from the fact that large scale geopotential variables are correctly predicted up to 8 or 10 days, while humidity variables are not, at least by the current version of the model considered.
+
+Next, we assume that for the synoptic variables used as predictors, the model forecasts have more uncertainties than the reanalyses, but no systematic bias.
+To optimize further the AM, it can be considered that the further the lead time, the more uncertain the synoptic forecasts and therefore the more uncertain the precipitation forecasts could be.
+This can been addressed by reconsidering, for each lead-time, the optimal number of analogues to select, for re-forecast data from a particular NWP model \citep{Thevenot2004}.
+The underlying idea is that if the model proves perfect, then the number of analogues should remain close to that obtained in the perfect progonosis framework.
+While if the forecast becomes irrelevant, for example at distant lead times, the AM should propose a forecast closer and closer to the climatological distribution of the predictand.
+The optimal number of analogue situations will thus increase with the lead time, and should be optimized for every lead time on the re-forecast dataset \citep[see][for the details]{Thevenot2004}.
+This option is implemented in AtmoSwing Forecaster (see section \ref{sec:forecaster}).
+
+It should be stressed that these operational aspects are dependent on the model used to provide the AM with synoptic forecasts, and on the availability of a re-forecast data to perform the tuning of the AM to this particular model.
 
@@
 
-Processing operational forecasts by means of AtmoSwing requests very low computing infrastructure and can provide useful information, such as early warning for extreme precipitation, in the case of an application in flood forecasting.
+Processing operational forecasts by means of AtmoSwing requests in the end very low computing infrastructure and can provide useful information, such as early warning for extreme precipitation, in the case of an application in flood forecasting.
 The Forecaster is very flexible as it builds the desired method in a dynamic way, and can thus implement multiple variants of the AM.
-The Viewer offers a user-friendly display of the forecast, with different levels of synthesis and details.
+The connection with open access NWP model such as GFS is easy and very efficient (data are collected quickly after being available, and processed in a few minutes).
+The Viewer offers a user-friendly display of the forecasts, with different levels of synthesis and details.
 The Optimizer implements different optimization techniques, such as the sequential approach, a Monte-Carlo method, and a global optimization technique.
-
-Several additions would be nice to have in AtmoSwing for operational forecasting.
+Obviously, it is used only occasionally for a given location: for a first implementation of an AM, in case of a change in the archive, or of a substantial updating, etc.
+
+Meanwhile, several additions would be nice to have in AtmoSwing for operational forecasting.
 The first one would be using outputs from multiple global NWP models within one forecast, namely making multi-models forecasts, in order to take into account the variability between various providers.
-In the same direction, \citet{Thevenot2004} showed the benefit of using ensembles of global NWP forecasts as input for the method.
+In the same direction, \citet{Thevenot2004} showed the benefit of using ensembles of global NWP forecasts as input for the method (in his case the 51 traces from the EFS of ECMWF).
 This approach takes into account the uncertainties on predictors from the global model.
@@
 
-The analogue method evolves, but there are still many possibilities to be assessed. Amongst them, one can mention:
+As it was shown in the historical section, the AM evolves, with the availability of new data, computer facilities and progress in NWP models, and still proves to bring complementary information on predictands like precipitation, for example at long lead time.
+Its interest in climatological downscaling has not been addressed in this paper but should be mentioned.
+However, there remain still many possibilities to be explored.
+Amongst them, one can mention:
 
@@
 	\item optimizations specific for extreme events, with an objective function tailored to the determination of the most critical situations;
+	\item a better insight in the role of the length of the archive, by using long reanalyses over the $20^{th}$ century;	
 	\item a weighting of the predictor grids, in order to get free of fixed rectangular spatial windows;

### 2016-01-21 Genetic algorithms - Journal of Climate/template.tex
Charle's corrections.

@@
 
-\abstract{The analogues method is based on a statistical relationship between synoptic atmospheric variables (predictors) and local weather (predictand), which we aim at forecasting.
+\abstract{The Analogue Method is based on a statistical relationship between synoptic atmospheric variables (predictors) and local weather (predictand), which we aim at forecasting.
 This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic sequential procedure.
@@
 
-The analogue method (AM) relies on the hypothesis that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Lorenz1956, Lorenz1969, Duband1970, Bontron2005}.
+The Analogue Method (AM) relies on the hypothesis that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Lorenz1956, Lorenz1969, Duband1970, Bontron2005}.
 The principle consists in sampling a certain number of past situations based on different atmospheric variables (predictors) in order to build a probabilistic forecast for a local weather variable of interest (predictand).
@@
 
-The purpose of this paper is not to present in details the AM and its different parametrizations, which can be found in \citet{Horton2016} or \citet{BenDaoud2015}.
-The concepts one needs to understand here are the following: the AM consists in searching a certain number of past situations in a meteorological archive (typically reanalysis) that are the most similar, according to an analogy criteria, and to extract the observed values of the local weather variable of interest from another archive (typically local time series) in order to build the empirical distribution considered as the probabilistic forecast for the target day.
-Predictors can be multiple: for example the geopotential height at different pressure levels on different temporal windows (time of observation).
-The method is usually made of multiple levels of analogy, leading to successive subsampling on predictors of different nature (eg.
+The purpose of this paper is not to present in details the AM and its different parameterizations, which can be found in \citet{Horton2016} or \citet{BenDaoud2015}.
+The concepts one needs to understand here are the following: the AM consists in searching a certain number of past situations in a meteorological archive (typically reanalysis datasets) that are the most similar, according to an analogy criteria, and to extract the observed values of the local weather variable of interest from another archive (typically local or basin averaged time series) in order to build the conditional empirical distribution considered as the probabilistic forecast for the target day.
+Predictors can be varied: for example the geopotential height at different pressure levels on different temporal windows (time of observation).
+The method is usually made of several levels of analogy, leading to successive subsampling on predictors of different nature (eg.
 atmospheric circulation, moisture variables, vertical motion, and air temperature).
 
-Even though the method is rather simple compared to numerical weather prediction models, it contains a certain number of parameters one needs to determine, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criteria itself, and finally the number of analogue situations to keep at each subsampling level.
-
-The AM needs to be adapted to every new region it is applied, because the leading meteorological influences are specific per region.
-Even the selection of the pressure levels and the temporal windows should be reconsidered, when not the variable itself.
-For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012a} found no interest in this variable in an Alpine environment, because the vertical motion, which is mainly controlled by orographic effects, was already well related to the atmospheric circulation itself.
+Even though the method is rather simple compared to numerical weather prediction (NWP) models, it contains a certain number of parameters one needs to determine, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criteria itself, and finally the number of analogue situations to keep at each subsampling level.
+
+The AM needs to be adapted to every new region considered, because the leading meteorological influences may be specific per region.
+Even the selection of the pressure levels and the temporal windows should be reconsidered, when not the predictor variable itself.
+For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012a} found it useless in an Alpine environment, because the vertical motion, which is mainly controlled by orographic effects, was already well related to the atmospheric circulation itself.
 
 Up to now, the optimization of the method has been undertaken by semi-automatic sequential calibration procedures \citep[see][for its definition]{Bontron2004, Horton2016}.
-However, the choice of predictor variables, pressure levels and temporal windows were still to be chosen manually before optimizing the spatial windows and the number of analogues.
-Testing multiple combinations of these can be cumbersome, especially when considering multiple predictors within the same level of analogy.
+However, the selection of predictor variables, pressure levels and temporal windows had still to be made manually before optimizing the spatial windows and the number of analogues.
+Testing multiple combinations of these is very combinatorial and becomes quickly cumbersome, especially when considering multiple predictors within the same level of analogy.
 Thus, optimizing the method with the sequential technique is laborious, as many combinations of predictors (variables, pressure levels, temporal windows) have to be assessed.
-Moreover, the sequential technique proceeds to the optimization sequentially, ignoring potential dependencies between the parameters of the method, may they be within a single level of analogy or between them.
-However, any dependency between them cannot be excluded, which could lead us to select another parametrization if calibrated together.
-Simultaneous calibration of all parameters has never been undertaken so far.
-Thus, due to its sequential approach, the risk of ending in a local optimum is high and can not be avoided.
+Moreover, proceeding to the optimization sequentially ignores potential dependencies between the parameters of the method, may they be within a single level of analogy or between them.
+However, such dependencies between them cannot be excluded, which could lead to another parametrization if calibrated together.
+However, simultaneous calibration of all parameters has never been undertaken so far.
+Thus, due to the sequential approach, the risk of ending in a local optimum is high and can not be avoided.
 Indeed, during the AM calibration it has been found that the resulting parameters may vary with initial choices (such as the number of analogues).
@@
 And later in his work: ''\textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution}''.
-\citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of the AM and concludes that one needs to be an expert to know their respective influence, their sensitivity and their nonlinear interactions.
+\citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of the AM and concludes that one needs to be an expert to have a sense of their respective influence, sensitivity and nonlinear interactions.
 \citet{BenDaoud2010}, when calibrating the AM, also stated that ''\textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously }''.
@@
 This technique did not provide satisfying results and failed at converging toward a unique solution.
-The parameter space of the AM is very complex and is not appropriate for a linear optimization technique.
+The parameter space of the AM is very complex and is inappropriate for a linear optimization technique.
 The conclusion was that global optimization techniques were necessary in order to calibrate AMs, as it is the only way to optimize all parameters of all analogy levels simultaneously.
 In addition, it can overcome the systematic manual assessments of all pressure levels and temporal windows.
-Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the pressure levels \citep[see][]{Horton2016b}, and the consideration of non-overlapping spatial windows between the pressure levels.
-The relevance of Genetic Algorithms (GAs) is presented here, which does not exclude that other global optimization techniques could also be successful.
-
-This article is not about discussing the details of the results of an optimization with GAs, but describing how to use GAs in order to successfully optimize AMs.
-Indeed, GAs variants are numerous and they always need to be tailored to the problem to be addressed.
+Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the pressure levels \citep[see][]{Horton2016b}, and the consideration of differentiated spatial windows between the pressure levels.
+The relevance of Genetic Algorithms (GAs) is presented here, which does not exclude that other global optimization techniques could eventually be successful.
+
+This article is not about discussing the details of the results of an optimization with GAs, but describing how GAs are to be used in order to successfully optimize AMs.
+Indeed, GAs variants are numerous and always need to be tailored to the problem addressed.
 This requires intensive and systematic comparisons of operators and options in order to identify the key factors leading the optimization and the respective sensitivity of the options.
-These analyses are presented here and result in recommendations for the use of GAs when applied to AMs.
-The demonstration of the benefit brought by such an approach in a specific case study is the topic of \citet{Horton2016b}.
-
-We will begin by presenting the concepts of GAs as well as the assessed operators (section \ref{sec:gas}).
+Such analyses are presented here and will result in recommendations for the use of GAs when applied to AMs.
+The demonstration of the benefit brought by such an approach on a specific case study is the topic of \citet{Horton2016b}.
+
+We will begin by presenting the concepts of GAs as well as the assessed operators (operations performed on the AM parameters; see section \ref{sec:gas}).
 The comparative analyses of the operators and their results are presented in section \ref{sec:assessment}, which lead us to the recommendations in section \ref{sec:recommendations}.
@@
 
-GAs are part of the family of Evolutionary Algorithms \citep{Back1993b, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
-GAs are the most used technique from Evolutionary Algorithms \citep{Back1993b}, and they are constantly improving \citep{Haupt2004}.
+GAs are part of the family of Evolutionary Algorithms \citep{Back1993b, Schwefel1993}, inspired by some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
+GAs are the most used technique among Evolutionary Algorithms \citep{Back1993b}, and they are constantly improving \citep{Haupt2004}.
 However, with time, the different methods of Evolutionary Algorithms tend to be similar and share many commonalities \citep{Back1996b, Haupt2004}.
@@
 GAs mimic the evolution of a population of individuals in a new environment, by applying rules based on natural processes, such as DNA mutation, chromosomes crossover, natural selection, etc.
-Generation after generation, the DNA mixes and the strong genes cumulate in some individuals \citep{Beasley1996a}.
-
-Applications of GAs are very diversified as they can handle many problems of various types \citep{Joines1996a}, even with very complex cost surfaces \citep{Haupt2004}.
-The objective function to optimize (often named fitness function in this context) can be of different types, only the resulting value is used for optimization.
-Indeed, these algorithms do not require any knowledge of the problem, but they must be adapted in order to perform optimally.
+Generation after generation, the DNA mixes and the best suited, or best adapted, genes cumulate in some individuals \citep{Beasley1996a}.
+
+Applications of GAs are diversified and can handle problems of various types \citep{Joines1996a}, even with very complex cost surfaces \citep{Haupt2004}.
+The objective function to optimize (often named fitness function in this context) can be of different types, but GAs must be adapted in order to perform optimally.
 
@@
 Exploration is characterized by a relatively high probability to assess the regions of the parameter space that have not yet been visited.
-This probability must be sufficiently large at the beginning of the optimization, so that the algorithm is capable of identifying the region where the global optimum is located.
+This probability must be sufficiently large at the beginning of the optimization, so that the algorithm is capable of identifying the region where the global optimum is likely located.
 Exploitation is characterized by a local search in an area of interest, and generally makes small movements.
@@
 The GAs optimize a population of $N$ individuals (parameter sets).
-Each individual contains a chromosome (parameters of the AM in this case).
-Genes are the parameters constituting the chromosome.
+Each individual contains a chromosome (set of parameters of the AM in this case).
+Genes are the individual parameters constituting the chromosome.
+They can be either categorical (e.g.
+geopotential, or temperature), discrete (e.g.
+number of analogues to select, from 1 to 40), or continuous.
 The floating-point representation \citep[instead of the canonical binary, see][]{Goldberg1989, Goldberg1990a, Holland1992b} of the genes was considered, as it was found more suited in multiple applications \citep{Michalewicz1996, Herrera1998a, Haupt2004, Back1996b, Gaffney2010a}.
@@
 There are numerous implementation variants of GAs, often optimal for a given problem \citep{Hart1991a, Schraudolph1992a}.
-The divergences are the operators implementation, through significantly different algorithms, which has an important effect on the results \citep{Gaffney2010a}.
-However, the structure of the method (Figure \ref{fig:structure_gas}) resulting from the work of \citet{Holland1992b} is common to most applications \citep{Back1993b}, and consists in the following steps:
+The divergences are in the operators implementation, through significantly different algorithms, which has an important effect on the results \citep{Gaffney2010a}.
+Here, operators are defined as the mechanisms that modify the values of the genes to try bringing individuals (or chromosomes) closer to an optimum of the fitness function.
+The structure of the method (Figure \ref{fig:structure_gas}) resulting from the work of \citet{Holland1992b} is common to most applications \citep{Back1993b}, and consists in the following steps:
 
@@
 	\item From this IG, couples are formed according to given rules.
-	\item These couples proceed to reproduction, or chromosome crossover, in order to mix their genes (parameters) according to the operator version.
-New children are generated in order to fill the IG back to $N$ individuals.
+	\item These couples proceed to reproduction, or chromosome crossover, in order to mix their genes (parameters) according to the selected operator version.
+New children are generated in order to refill the IG back to $N$ individuals.
 	\item Parents and children are then subject to mutation, where some genes get affected, meaning some parameter values are randomly changed.
@@
 
-The first step of the optimization is to generate the initial population.
-A population is a set of $N$ individuals (each of which represents a point in the space of potential solutions, a parameter set of the AM in this application) that are going to evolve.
-A generation is the population at a given time.
-
-A random initialization based on a uniform distribution is the most current version.
+The first step of the optimization is to generate an initial population.
+A population is a set of $N$ individuals (each of which represents, in this application, a parameter set of the AM and thus a point in the space of potential solutions) that are going to evolve.
+A generation is the population considered at a given time.
+
+A random initialization based on a uniform sampling is the most current version.
 The size $N$ of the population is often a compromise between the computation time and the quality of the solution.
-$N$ must allow sufficient sampling of the solutions field \citep{Beasley1996a}, and should thus vary as a function of chromosome size (ie the number of parameters to be optimized).
+$N$ must allow sufficient sampling of the solutions field \citep{Beasley1996a}, and should thus vary as a function of chromosome size (ie the number of genes or parameters to be optimized).
 
@@
 The selection allows to only keep a certain part of the population, usually half ($N/2$), which can access the IG (with $N_{IG}$ members).
-If $N_{IG}$ is too high, the reproduction rate is too low, whereas if it is too small, the strong traits of individuals do not have the ability to accumulate in the same chromosome \citep{Haupt2004}.
+If $N_{IG}$ is too high, the reproduction rate is too low, whereas if it is too small, the strong traits of individuals will not have the ability to accumulate in the same chromosome \citep{Haupt2004}.
 Several techniques exist, such as:
@@
 \begin{itemize}
-	\item $N_{IG}$-elitism \citep{Michalewicz1996}: the population is sorted according to the value of the objective function and only the better half is preserved.
+	\item $N_{IG}$-elitism \citep{Michalewicz1996}: the population is ranked according to the value of the objective function and only the better half is preserved.
 
@@
 \begin{itemize}
-	\item Rank pairing: individuals are gathered in pairs according to their rank (classified on the performance scores).
+	\item Rank pairing: individuals are gathered in pairs according to their rank (based on the performance scores).
 Consecutive ranks are put together (odd rows are associated with even rows).
@@
 To select a parent, a number of individuals (2 or 3) are randomly picked and the best is kept.
-This operation is performed twice, once for each partner.
-This approach imitates the breeding competition in nature \citep{Haupt2004}.
+This operation is performed twice, once for each partner and imitates the breeding competition in nature \citep{Haupt2004}.
 \end{itemize}
@@
 The combination of chromosomes is carried out using a crossover operator, thereby generating two offspring having characteristics derived from both parents.
-It allows a mixing of genes and accumulation of positive mutations.
+It allows a mixing of genes and a potential accumulation of positive mutations.
 
@@
 \begin{itemize}
-	\item Single-point crossover: a crossover point is randomly chosen for the pair. The genes (AM parameters) located after that point are exchanged in between the two chromosomes.
-
-	\item Two-point crossover: works like the single-point crossover, but there are two intersections defining the segments to exchange.
+	\item Single-point crossover: within the chromosome, a crossover point is randomly chosen for the pair.
+The genes (AM parameters) located after that point are exchanged in between the two chromosomes.
+
+	\item Two-point crossover: works like the single-point crossover, but there are two intersections defining the segments to be exchanged.
 This approach, which significantly extends the search space for the children, is considered more efficient than the previous \citep{Beasley1993a}.
 
-	\item Multiple-point crossover \citep{DeJong1975a}: it is a generalization of the previous, with a number of crossover points up to the number of genes.
+	\item Multiple-point crossover \citep{DeJong1975a}: a generalization of the previous, with a number of crossover points up to the number of genes.
 
@@
 
-The evaluated and developed mutation operators are the following:
+The evaluated and developed mutation operators are listed hereafter.
+They apply to genes made of continuous or discrete variables, but not categorical (eg meteorological variable or analogy criterion).
+In the latter case, the random choice of a new value is always based on a uniform distribution, without notion of distance in the parameters space.
 
@@
 	\item Non-uniform mutation \citep{Michalewicz1996}: two random numbers are picked based on a uniform law: $r_{1}$, which determines the direction of the change, and $r_{2}$, which determines its magnitude.
-The new value of the gene is given by the following equation:
+The new value of the gene is given by the following equation, according to a predefined number of generations:
 	\begin{equation}
@@
 
-When the gene to mutate is represented by a list of distinct values (eg meteorological variable or analogy criterion), the random choice of a new value is always based on a uniform distribution, without notion of distance in the parameters space.
-
 \subsubsection{Elitism}
@@
 This ensures the survival of the best individual so that a better solution is never lost.
-After the natural selection operator, if the best individual has not been selected, it is copied to the IG instead of an individual randomly picked.
-After mutation, if the best individual has mutated and if its new version has a lower performance score than the original, the latter is also reinserted in the IG instead of an individual randomly chosen.
+After the natural selection operator, if the previously best individual has not been selected, it is copied to the IG instead of an individual randomly picked.
+After mutation, if the previously best individual has mutated and if its new version has a lower performance score than the original, the latter is also reinserted in the IG instead of an individual randomly chosen.
 
@@
 For example, when a crossover or a mutation operation results in a parameter value standing out of the authorized bounds, it has to be brought back within the limits.
-Moreover, the parameters are of different nature: some are continuous, some are discretized, and finally, some are independent elements in an array, such as the selection of the meteorological variable.
+Moreover, the parameters are of different nature: some are continuous, some are discrete, and finally, some are categorical, i.e.
+independent elements in an array, such as the selection of the meteorological variable.
 New values resulting from the optimizer need to respect the type of data it represents.
@@
 
-The GAs parametrization, such as the mutation rate, population size, natural selection options, and so on, is difficult given the high number of existing variants, each developed for a specific problem \citep{Haupt2004, Costa2007a}.
+The GAs parametrization, i.e.
+the a priori choices such as the mutation rate, population size, natural selection options, etc, appears difficult given the high number of existing variants, each developed for a specific problem \citep{Haupt2004, Costa2007a}.
 The parametrization depends on the objective function, implementation variants, the range of the parameters to be optimized, and performance indicators.
-Thus, different studies suggest very different parametrization.
+Thus, different studies suggest very different parameterizations.
 
 \citet{DeJong1975a} and \citet{Grefenstette1986} compared different implementations and parametrizations of GAs on functions of varying complexity.
-They observed that a small population size improves the initial performance, while a large population improves long-term performance.
-They also observed that the ratio of the population to keep for the IG is around 50\% (45\% to 60\%).
-
-Values of the mutation rate varies broadly between the studies: from 0.001 \citep{DeJong1975a} to 0.2 \citep{Haupt2004}.
+They observed that a small population size improves the initial performance, while a large population improves latter performance.
+They also observed that the proportion of the population to keep for the IG is around 50\% (45\% to 60\%).
+
+Values of the mutation rate varies broadly between studies: from 0.001 \citep{DeJong1975a} to 0.2 \citep{Haupt2004}.
 \citet{Back1996b} showed that mutation rates higher than the usual ranges are more optimal at the beginning of the optimization, allowing further exploration.
-Incremental approaches with varying mutation rates are certainly more optimal but more complex to implement \citep{Back1996a, Back1996b}.
+Varying mutation rates are certainly more optimal but more complex to implement \citep{Back1996a, Back1996b}.
 
@@
 
-One of the goals being to make recommendations of parametrization in order to optimize the AM, a systematic procedure was adopted.
+One of our goals being to make recommendations of parametrization in view of optimizing the AM, a systematic procedure was adopted.
 The results are summarized hereafter \citep[see][for the details]{Horton2012a}.
@@
 In order to evaluate a combination of operators/options, 10 optimizations per parametrization of GAs were processed.
+Such assessment is not possible on the whole archive length, and had to be performed on a reduced period.
 The performances were characterized by four indicators: (i) mean performance score: average of the final scores of the 10 optimizations, (ii) convergence: the number of optimizations that converged to a supposed global optimum, (iii) number of generations: characterization of the convergence speed, and (iv) number of evaluations of the objective function: characterization of the required calculation time.
@@
 
-After a first overview of the results, GAs have quicky been proven successful at optimizing the AM.
-Indeed, the performance score of the sequential approach has been quickly exceeded without adding any new parameter to the method (Figure \ref{fig:gas_evolution_good}).
-Even GAs parametrization that will be further considered as inadequate (Figure \ref{fig:gas_evolution_bad}) did significantly better that the sequential approach.
+After a first overview of the results, GAs have quicky proved successful at optimizing the AM.
+The performance score of the sequential approach has been quickly exceeded without adding any new parameter to the method (Figure \ref{fig:gas_evolution_good}).
+Even GAs parameterizations that will be considered later as inadequate (Figure \ref{fig:gas_evolution_bad}) did significantly better that the sequential approach.
 The amplitude of the improvement is not the main outcome here.
-The most important point is that GAs are proven successful at optimizing AMs automatically, globally, and objectively.
+The most important point is that GAs proved successful at optimizing AMs automatically, globally, and objectively.
 
@@
 The results illustrate the effect of an operator when its contribution is isolated from the other operators.
-It means that we compare the effect of the studied operator when all the other operators are equivalent, while assessing multiple combinations.
-This contribution is then summarized relatively to the other options, as a percentage of gain/loss regarding the mean of all variants.
+It means that we analyze the effect of a given operator for equivalent conditions (same settings of other operators).
+Multiple combinations with other operators are assessed.
+This contribution is then summarized as a percentage of gain/loss regarding the mean of all variants, for equivalent external conditions.
 For example, to evaluate the performance of the uniform crossover operator, its performance is compared to the average of all crossover operators while retaining the same population size, the same mutation operators, natural selection, and selection of couples.
@@
 
-Analysis of crossover operators (Figure \ref{fig:operator_crossover_score}) reveal some slightly superior options, some inappropriate, and many averages.
+Analysis of crossover operators (Figure \ref{fig:operator_crossover_score}) reveal some slightly superior options, some inappropriate, and many average.
 Binary-like crossover (especially with 2 points of intersection, whether $\beta$ is shared or not) are significantly better than the others, especially in terms of convergence (not shown).
@@
 Having identified the leading role of the mutation operator, the next sensitivity analysis focused on it.
-Each of the 10 different implementations (see section \ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Table \ref{tab:assessed_mutation_operators}), bringing the number of its variations up to 109.
+Each of the 10 different implementations (see section \ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Table \ref{tab:assessed_mutation_operators}), bringing the number of variations up to 109.
 Some optimizations without any mutation were also performed as a reference.
@@
 The optimizer could choose the 2 pressure levels of the atmospheric circulation analogy (method with a single level of analogy).
-The resulting performance score \citep[CRPSS = skill score of the CRPS, see][]{Brown1974} is obviously superior to the one from the sequential calibration (red line on Figure \ref{fig:operator_mutation_score_atmlevel}).
+The resulting performance score \citep[CRPSS = skill score of the CRPS, see][]{Brown1974} is obviously superior to the one obtained by the sequential calibration (red line on Figure \ref{fig:operator_mutation_score_atmlevel}).
 For most options, it is also slightly better than the results from the optimization without selection of the pressure levels (blue line).
-A clear breakthrough of the performances was not expected, as the former selection of pressure levels results from intensive comparative work \citep{Bontron2004}.
+A clear breakthrough of the performances was not expected, as the former selection of pressure levels results already from intensive comparative work \citep{Bontron2004}.
 This application however demonstrates that, when correctly parametrized, GAs can automatically and successfully choose the pressure levels.
@@
 
-Next, a second level of analogy was added (Figure \ref{fig:operator_mutation_score_r2}) on moisture variables \citep[see][]{Bontron2004, Horton2016}.
+Next, a second level of analogy was proposed (Figure \ref{fig:operator_mutation_score_r2}) based on moisture variables \citep[see][]{Bontron2004, Horton2016}.
 GAs had to optimize both levels of analogy simultaneously.
-Once again, despite the difficulty to optimize simultaneously both levels of analogy, the results were better than the sequential calibration (red line on Figure \ref{fig:operator_mutation_score_r2}).
+Once again, despite the difficulty to do so, the results were better than the sequential calibration (red line on Figure \ref{fig:operator_mutation_score_r2}).
 And finally, a preselection on air temperature was added instead of the fixed calendar window, as proposed by \cite{BenDaoud2015}.
@@
 The main disadvantage of the non-uniform mutation is the number of parameters it requires, that are difficult to estimate a priori.
-The $\omega$ coefficient does not influence performance.
-The role of $G_{m}$ is rather difficult to judge, but does not seem essential.
-The mutation rate was found to be important.
-The difficulty is that the optimal value may be case-related.
+The mutation rate was found to be more important than the others.
+The difficulty is that its optimal value may be case-related.
 
@@
 In this application, the mutation operator has a leading effect and should be chosen with care.
-It may be wise to perform multiple optimizations and to consider these three operators in parallel in order to obtain results from options that are either sometimes more efficient or more robust.
+It may be wise to perform multiple optimizations and to consider these three operators in parallel in order to obtain results from options that are sometimes either more efficient or more robust.
 It is interesting to note that the three best techniques incorporate a notion of search distance.
@@
 
-The size of the population ($N$) has an effect on the performance of the optimization (Figure \ref{fig:option_taillepop_score}).
+The size of the population ($N$), i.e.
+the number of sets of AM parameters considered, has an effect on the performance of the optimization (Figure \ref{fig:option_taillepop_score}).
 A bigger population leads to better results, but also to significantly longer optimizations.
@@
 	\item $N\approx100$ for very simple implementations of the AM (1 level of analogy with 2 pressure levels),
-	\item $N\approx200$ for a bit more complex AM (1 level of analogy with 4 pressure levels, or 2 level of analogy with less pressure levels),
+	\item $N\approx200$ for a slightly more complex AM (1 level of analogy with 4 pressure levels, or 2 level of analogy with less pressure levels),
 	\item $N\approx500$ for significantly more complex AMs (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the moisture analogy).
@@
 
-The influence of the size of the IG (ratio of the total population) selected for mating was also assessed (Figure \ref{fig:option_popratio_score}).
+The influence of the size of the IG (proportion of the total population) selected for mating was also assessed (Figure \ref{fig:option_popratio_score}).
 It does not appear that this parameter is critical to the quality of the optimizations, provided it is not too big.
@@
 
-Optimizations by GAs on AMs of varying complexity were performed with a large number of combinations of operators in order to make recommendations for optimizing the AM. The conclusions are:
+Optimizations by GAs for AMs of varying complexities were performed with a large number of combinations of operators in order to make recommendations for optimizing the AM. The conclusions are:
 
@@
 It may be wise to consider the three mutation operators in parallel.
-It would then combine algorithms that are sometimes faster and other that are more robust.
 In order to be confident in the optimized AMs, we propose using a set of the following mutation operators:
@@
 Given the large number of existing operators and options, multiple variants were assessed systematically in order to identify which operators are important, and which variants work best for the AM.
-The mutation operator was identified as a key element for this application, and new variants that were found to be efficient were provided, such as the chromosome of adaptive search radius that is very robust (no control parameter).
+The mutation operator was identified as a key element for this application, and new variants that proved efficient were provided, such as the chromosome of adaptive search radius that is very robust (no control parameter).
 Recommendations were established for a relevant use of GAs for the optimization of AMs.
 
-It is not excluded that another global optimization method or other operators of GAs may perform better.
-The relevance of such approach has now been proven as it results in parametrization of AMs that are relevant and fully automatically, globally and objectively established.
+It is not excluded that another global optimization method or other operators of GAs may perform still better.
+However, the relevance of such an approach has now been proved as it results in parametrization of AMs that are relevant and fully automatically, globally and objectively established.
 A global optimization is the only way to take into account all the dependencies between parameters and levels of analogy.
 
-The global optimization approach allows easily adapting the AM to new regions by taking into account local meteorological influences, and has thus a great potential of use.
+The global optimization approach allows easily adapting the AM to new regions by potentially taking into account local meteorological influences, and has thus a great potential of use.
 Moreover, it allows exploring automatically datasets in order to extract the most relevant variables.

### 2016-01-25 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Charle's corrections.

@@
 
-\title{Using Genetic Algorithms to Optimize the Analogue Method for Precipitation Forecasting in the Swiss Alps}
+\title{Using Genetic Algorithms to Optimize the Analogue Method for Precipitation Downscaling in the Swiss Alps}
 
@@
 The analogue method is often used to forecast precipitation based on predictors variables provided by global models.
-The method samples a selection of days in the archives that are similar to the target day to forecast, and consider the corresponding observed precipitation (the predictand) as the conditional distribution for the target day.
+The method samples a selection of days in the archives that are similar to the target day to forecast, and consider the set of their corresponding observed precipitation (the predictand) as the conditional distribution for the target day.
 The relationship between predictors and predictands relies on some parameters that characterize how and where the similitude between two atmospheric situations is defined.
@@
 In this work, the global optimization is applied to the Rh\^{o}ne catchment in the Swiss Alps in order to show its interest and the relevance of the resulting parameters.
-Indeed, not only the performance increases, but the parameters are obtained automatically and objectively, which reduces effort-hours when adapting the method to a new region or for a new predictand.
+Indeed, not only the performance increases, but the parameters are obtained automatically and objectively, which reduces efforts invested in exploration attempts when adapting the method to a new region or for a new predictand.
 Moreover, the approach allows for new degrees of freedom, such as a weighting between the pressure levels and non overlapping spatial windows.
@@
 \begin{keyword}
-Precipitation\sep
+Precipitation forecast\sep
+Precipitation downscaling\sep
 Analogue method\sep
@@
 A certain number of parameters define the relationship between predictors and predictands, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criteria itself, and finally the number of analogue situations to keep at each subsampling level.
-These parameters are usually calibrated by means of a semi-automatic sequential procedure \citep[see][for the details]{Bontron2004, Horton2016}.
-This sequential approach has strong limitations: (i) it cannot automatically choose the pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it could not handle new degrees of freedom, such as a weighting between the pressure levels.
+These parameters are usually calibrated by means of a semi-automatic sequential procedure \citep[see][for the details]{Bontron2004, Horton2016}, i.e.
+by optimizing each single parameter one at a time, in an arbitrarily chosen order, with no or little reconsidering.
+This sequential approach has therefore strong limitations: (i) it cannot automatically choose the pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it could not easily handle new degrees of freedom, such as a weighting between the pressure levels.
 Thus, even if the processing involved is relatively fast, the sequential approach requires laborious assessments of predictors combinations (variables, pressure levels, temporal windows), and present a high risk of ending in a local optimum due to subjective initial choices and lack of consideration of parameters inter-dependencies.
@@
 An intensive assessment work resulted in recommendations of parametrization of GAs in order to optimize AMs successfully.
-The present paper is based on these recommendations and apply them to precipitation forecasting for the upper Rh\^{o}ne catchment in the Swiss Alps.
+The present paper is based on these recommendations and illustrate them on precipitation forecasting for the upper Rh\^{o}ne catchment in the Swiss Alps.
 It aims at proving the relevance of a fully-automatic, objective, and global, optimization technique for AMs.
@@
 To cope with seasonal effects, candidate dates are extracted within a period of 4 months centered around the target date, for every year of the archive.
-Following the nomenclature proposed by \citet{Horton2016}, this method will be named 2Z.
+Following the nomenclature proposed by \citet{Horton2016}, this method using two geopotential heights will be named 2Z.
 
@@
 where $\Delta \hat{z}_{i}$ is the difference in geopotential height between the \textit{i}th pair of adjacent points of the gridded data describing the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
-The differences are processed separately in both directions.
+The differences are processed separately in both directions over the selected spatial domain.
 The smaller the S1 values, the more similar the pressure fields.
@@
 When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
-When a second level of analogy is added, a higher number of analogues is kept on the first level.
+When a second level of analogy is added, a higher number of analogues $N_{1}$ is kept on the first level.
 
@@
 the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008.
-The time series from every available gauging station were averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.
+The time series from every available gauging station were averaged over subregions of approximately 500~km$^{2}$ in order to smooth local effects \citep{Obled2002, Marty2012}.
 
@@
 
-In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution as the reference.
+In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution of daily precipitation as the reference.
 The CRPSS (\textit{Continuous Ranked Probability Skill Score}) is thus defined as following:
@@
 
-Genetic Algorithms (GAs) were developed by \citet{Holland1992b} and popularized by \citet{Goldberg1989}.
+Genetic Algorithms (GAs) were developed by \citet{Holland1992b} and \citet{Goldberg1989}.
 They are part of Evolutionary Algorithms \citep{Back1993b, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
@@
 
-A population size of 500 individuals (parameter sets of the AM) was considered, and the optimization was stopped when the best individual (with the highest CRPSS performance score) did not evolve for 20 generations (cycles of the optimization).
+A population size of 500 individuals (parameter sets of the AM to be detailed hereunder) was considered, and the optimization was stopped when the best individual (with the highest CRPSS performance score) did not evolve for 20 generations (cycles of the optimization).
 
@@
 The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$.
-This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at providing a real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
+This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at allowing real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
 Even though the region is rather small, the meteorological influences related to extreme weather conditions varies substantially within it \citep[see][]{Horton2012}.
@@
 
-The analogy of the atmospheric circulation was optimized for the 10 subregions.
+The analogy of the atmospheric circulation was optimized for the 10 subregions  independently.
 We started from the most simple AM, and increased the complexity in order to identify the degrees of freedom that are of particular interest.
@@
 
-Parallel analyses showed that the analogy of circulation is incomplete, and that the geopotential still contains relevant data that can improve the statistical relationship.
+Parallel analyses showed that the analogy of circulation is incomplete, and that the geopotential still contains relevant information that can improve the statistical relationship.
 Therefore, a third predictor was added (still on the geopotential height) that the optimizer could use along with the previous parameters.
-There was no constraint on the predictors, so that the same pressure level could be selected multiple times.
+There was no constraint on the predictors, so that the same pressure level could be selected more than once.
 Some improvements were found on the score, both for the CP and the VP, confirming that this additional information is beneficial for the quality of the forecast.
@@
 
-Finally, a weighting of the criteria values per pressure level was added, which is also optimized by GAs.
+Finally, a weighting of the criteria values per pressure level was proposed, again optimized by GAs.
 The weighting operates in the combination of the S1 criteria processed on every level, which were previously averaged with equal weights.
@@
 The optimizer thus provided consistent selections of pressure levels and temporal windows, which depicts a significant preference in the AM, and the success of GAs to provide consistent results.
-The automatic selection of the pressure levels is a big advantage of a global optimization, as it is not possible to assess all combinations of 4 levels with the sequential calibration procedure.
+The automatic selection of the pressure levels is a big advantage in favor of a global optimization, as it is not possible to assess all combinations of 4 levels with the sequential calibration procedure.
 
@@
 The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the CP when they are calibrated for the given subregion (Figure \ref{fig:crossing_4Zo_calib}).
-However, the losses in CRPSS when exchanging the parameters are not of the same amplitude between the different subregions.
+However, the losses in CRPSS when exchanging the parameters are not of the same magnitude between the different subregions.
 Indeed, the Upper Rhone Valley (7) and moreover the Southeast ridges (8) seem to behave significantly differently.
@@
 Parameter sets from other subregions perform poorly for these subregions, and vice versa.
-This points to the importance of taking into account leading meteorological influences during discretization, that are not always best represented by the physical distance.
+This points at the importance of taking into account leading meteorological influences during discretization, that are not always best represented by the physical distance.
 Globally, the same pattern can be observed for the VP (Figure \ref{fig:crossing_4Zo_valid}), but in this case, minor improvements may be observed when crossing the parameters.
 The reason being that the independent VP contains other events that may be better forecasted by other parameter sets.
-The relative small differences in score between parameterizations indicate that even though the parameters may differ significantly, the performance may not be drastically affected.
+The relatively small differences in score between parameterizations indicate that even though the parameters may differ significantly, the performance may not be drastically affected.
 Even a change in the pressure level does not mean a radical drop of the score value.
-A different parametrization leads to a different selection of the analogue days, and thus to an improvement of the forecast of certain weather conditions at the expense of others.
-This raises the question of optimizing more specifically for extreme weather conditions in priority.
+A different parametrization may lead to a different selection of the analogue days, and thus to an improvement of the forecast under certain weather conditions at the expense of others.
 
-\section{Optimization of the moisture analogy}
+\section{Optimization of the analogy with moisture information}
 \label{sec:optim_moisture}
@@
 It is known that moisture variables as a second level of analogy do provide improvements to the method (section \ref{sec:analog_method}).
-The moisture index, which is a combination of the relative humidity and the precipitable water, has thus also been optimized.
-In order to do so, a constraint to the optimizer had to be introduced, so that it selects the same temporal window for both variables.
+The moisture index, which is a combination of the relative humidity and the precipitable water, has thus also to be optimized.
+In order to do so, a constraint to the optimizer had to be introduced, so as to select the same temporal window (time of observation) for both variables.
 
@@
 As previously, the optimized parameters differ from one subregion to another, and this even to a greater extent.
-Detailed examples are still provided for the Swiss Chablais subregion in Table \ref{table:params_GA_4Zo_2MIo} for 4Zo-2MIo.
+Detailed examples are again provided for the Swiss Chablais subregion in Table \ref{table:params_GA_4Zo_2MIo} for 4Zo-2MIo.
 The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_4Zo-2MIo} for 4Zo-2MIo, along with the selected pressure levels for both the circulation and the moisture analogy (Table \ref{table:levels_GA_4Zo_2MIo}).
@@
 This results in a relative improvements that ranges from 11.5 \% to 15.6 \% compared to the reference method on the moisture analogy (Table \ref{table:scores_diff}).
-As for 4Zo, the 4Zo-2MIo and 4Zo-4MIo methods present improvements of the forecast for significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
+As for 4Zo, the 4Zo-2MIo and 4Zo-4MIo methods present larger improvements in the forecast for significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
 The improvement are relatively similar for 4Zo-2MIo (Table \ref{table:scores_thresholds_4Zo-2MIo}) and 4Zo-4MIo (not shown), with slightly superior scores for the latter on small precipitation (P\(\geq\)1 mm : 17.7\% and 13.0\%) and extremes (P\(\geq\)0.5\(\cdot\)P10 : 23.7\% and 29.2\%).
@@
 When optimizing a method made of 2 levels of analogy, the introduction of moisture variables in the second level has an influence on the parameter values of the first level.
-This is first visible on the selection of the pressure levels for the circulation analogy, where the 1000~hPa that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) is now less chosen (once or even not at all) for both 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}) and 4Zo-4MIo (not shown).
+This is first visible on number $N_{1}$ of analogues to be selected on the first level, and on the selection of the pressure levels for the circulation analogy, where the 1000~hPa that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) is now less chosen (once or even not at all) for both 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}) and 4Zo-4MIo (not shown).
 There is indeed a shift of the previously selected 1000~hPa for higher levels, which is even slightly stronger with 4 moisture predictors than with 2.
@@
 However, even in this latter method, the 700~hPa and 600~hPa levels still hold 78 \% of the selection.
-It is thus more efficient, in terms of forecasting performance, to consider one of this level multiple times at different hours rather than using another pressure level.
+It is thus more efficient, in terms of forecasting performance, to consider one of this level several times at different hours rather than using another pressure level.
 Besides, the optimizer never chose the same pressure level at the same hour for any variable, even though it was allowed to do so.
@@
 The analysis of the parameters cross-compatibility (Figures \ref{fig:crossing_4Zo-2MIo_calib} and \ref{fig:crossing_4Zo-2MIo_valid}) is also very similar to the one on the circulation analogy only (results for 4Zo-4MIo not shown as very similar).
-The same pattern can be observed, with a drop of performance for the subregions under different meteorological influences.
+The same pattern can be observed, with a drop of performance for the subregions submitted to several different meteorological influences.
 However, the losses of performance are globally more important than before, suggesting that more complex methods with moisture variables are less transposable to another subregion, even though it is located within the same grid cell of the reanalysis dataset.
@@
 It seems to be the optimal number for the studied region.
-Beyond that value the validation score drops, revealing a lost in robustness due to over-parametrization.
+Beyond that value the validation score drops, revealing a loss in robustness due to over-parametrization.
 	\item The automatic and joint optimization of all parameters: the analogues number, the selection of the pressure levels and the temporal windows, and the spatial windows.
 These parameters are highly interdependent, so one needs to optimize them jointly in order to identify optimal combinations.
-Traditional calibration procedures based on a systematic assessment of every combination is no more possible when considering more than 2 pressure levels.
+Traditional calibration procedures based on a systematic assessment of every combination is not possible anymore when considering more than 2 pressure levels.
 	\item The introduction of distinct spatial windows between pressure levels.
 The synoptic circulation is characterized by features with very different scales depending on the height, and important information for predicting rainfall is not necessarily located in the same area from one level to another.
-The optimized spatial windows are consistent in between the subregions.
+However, the optimized spatial windows are consistent in between the subregions.
 	\item The weighting of the analogy criteria between different pressure levels.
@@
 
-GAs are very useful to optimize complex variants of the AM, and to assess new degrees of freedom that were not available so far.
+GAs have proved very useful to optimize complex variants of the AM, and to assess new degrees of freedom that were not available so far.
 However, it can be dangerous to add too many parameters to optimize.
@@
 We could also observe that the selection of the pressure level is not a parameter as discrete as we would have thought, and that choosing another level may have reduced consequences on the performance.
-This is particularly true for higher pressure levels and can be more critical for lower layers.
+This is particularly true for higher pressure levels but can be more critical for lower layers.
 It was thus interesting to sometimes get several sets of near-optimal parameters, but with some nuances, in order to get an idea of the sensitivity of the parameters for a given region, and to compare the score on the VP.
@@
 
-We tried to optimize the preselection period (the 4-months window) jointly with the other parameters, but no improvement was observed.
+We tried to optimize the preselection period (i.e.
+the 4-months window) jointly with the other parameters, but no improvement was observed.
 Optimizing the moisture flux, which is composed of the moisture index multiplied with the wind flux, was also assessed.
@@
 It is already possible to undertake such approach with our code.
-Moreover, the AM has been explored for decades for precipitation forecasting, but very few work analysis its potential for other predictands.
+Moreover, the AM has been explored for decades for precipitation forecasting, but very few works analyze its potential for other predictands.
 A global optimizer, such as GAs, can speed up this assessment significantly.

### 2016-01-27 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Addition of the analysis on the number of analogues.

@@
 \begin{table}[htb]
-	\caption{Pressure levels ($\sim$) automatically selected for the 4Zo method at the different subregions.}
+	\caption{Pressure levels ($\sim$) automatically selected for the 4Zo method at the different subregions. R represents the reference method (Table \ref{table:params_R1}).}
 	\footnotesize
@@
 			10 &   &   &   & $\sim$ & $\sim$ &   &   & $\sim \sim$ \\
+			\hline 	
+			R  &   &   & $\sim$ &   &   &   &   & $\sim$ \\
 			\hline 
@@
 The resulting CRPSS scores are provided in Table \ref{table:scores} and are in average 35.8 \% for the CP and 35.5 \% for the VP.
-The improvement of the CRPSS score relatively to the reference method on the atmospheric circulation is provided in Table \ref{table:scores_diff} and is in average 15.3 \% for the CP and 9.9 \% for the VP.
+The improvement of the CRPSS score relatively to the reference method on the atmospheric circulation (optimized by the sequential procedure) is provided in Table \ref{table:scores_diff} and is in average 15.3 \% for the CP and 9.9 \% for the VP.
 The score was also calculated for three precipitation thresholds: P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_4Zo}).
@@
 
-The scores show significant improvements for both the CP and the VP (Table \ref{table:scores_diff}).
+The scores show significant improvements for both the CP and the VP (Table \ref{table:scores_diff}) compared to the reference method optimized by the sequential procedure.
 Even more interestingly, the results for higher precipitation thresholds (Table \ref{table:scores_thresholds_4Zo}) show the largest improvements.
@@
 \begin{table}[htb]
-	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the 4Zo-2MIo method, at the different subregions.}
+	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the 4Zo-2MIo method, at the different subregions.
+R represents the reference method (Table \ref{table:params_R2})}
 	\footnotesize
@@
 			10 &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
+			\hline 
+			R &   &   & $\sim$ &   &   & $\bullet \bullet$ &   & $\sim$ \\
 			\hline 
@@
 The CRPSS scores of the optimized methods are provided in Table \ref{table:scores} and amounts to slightly more than 40 \% for both methods and for both periods.
-This results in a relative improvements that ranges from 11.5 \% to 15.6 \% compared to the reference method on the moisture analogy (Table \ref{table:scores_diff}).
+This results in a relative improvements that ranges from 11.5 \% to 15.6 \% compared to the reference method on the moisture analogy (Table \ref{table:scores_diff}) optimized with the sequential procedure.
 As for 4Zo, the 4Zo-2MIo and 4Zo-4MIo methods present larger improvements in the forecast for significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
@@
 When optimizing a method made of 2 levels of analogy, the introduction of moisture variables in the second level has an influence on the parameter values of the first level.
-This is first visible on number $N_{1}$ of analogues to be selected on the first level, and on the selection of the pressure levels for the circulation analogy, where the 1000~hPa that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) is now less chosen (once or even not at all) for both 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}) and 4Zo-4MIo (not shown).
+This is first visible on number $N_{1}$ of analogues to be selected on the first level, and on the selection of the pressure levels for the circulation analogy.
+As for the sequential procedure, the optimal value of $N_{1}$ increases when adding a second level of analogy (Figure \ref{fig:figure_nb_analogues}).
+One can also notice that the optimal number of analogues $N_{2}$ for the second level of analogy of 4Zo-2HIo is slightly inferior to $N_{1}$ from 4Zo, but very close.
+There is a relationship between the optimal values of $N_{1}$ from both methods: the higher the $N_{1}$ of the first method, the higher $N_{1}$ and $N_{2}$ of the second is (Figure \ref{fig:figure_nb_analogues_relationships}).
+This relationship is not to be considered perfectly robust and should not be transposed to another case study, but in this case, it relates the magnitudes of the numbers on the various levels and methods.
+The optimal final number of analogues do not vary much: $23 \leq N_{1} \leq 33$ for 4Zo and $21 \leq N_{2} \leq 28$ for 4Zo-2HIo.
+However, the optimal number of $N_{1}$ analogues of the first level of 4Zo-2HIo varies to a greater extent: $48 \leq N_{1} \leq 84$.
+In this latter, it may be problematic to consider a fixed and unique value for all regions.
+
+As for the pressure levels, the 1000~hPa that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) is now less chosen (once or even not at all) for both 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}) and 4Zo-4MIo (not shown).
 There is indeed a shift of the previously selected 1000~hPa for higher levels, which is even slightly stronger with 4 moisture predictors than with 2.
@@
 Besides, the optimizer never chose the same pressure level at the same hour for any variable, even though it was allowed to do so.
+The selected pressure levels for the analogy on the moisture index differ from the parameters resulting from the reference method optimized by the sequential procedure (Tables \ref{table:params_R2} and \ref{table:levels_GA_4Zo_2MIo}, last row).
+It is possible that the level 850~hPa is more optimal for the region for which the reference parameterization was established.
+However, this selection is usually not reconsidered when applying the sequential procedure.
 
@@
 The CRPSS scores were improved by considering the moisture information (Table \ref{table:scores}).
-The optimized methods also perform better than the reference method based on the moisture index (Table \ref{table:scores_diff}).
+The optimized methods also perform significantly better than the reference method based on the moisture index (Table \ref{table:scores_diff}) and optimized by the sequential procedure.
 However, there is no drastic difference between both 4Zo-2MIo and 4Zo-4MIo methods, which suggests that considering 4 moisture predictors is not necessary.
-When it comes to improvements for days with precipitation above the 3 thresholds (P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the forecast, mainly for heavy rainfall.
+When it comes to improvements for days with precipitation above the 3 thresholds (P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the forecast compared to reference method, mainly for heavy rainfall.
 
@@
 \begin{figure}[htb]
+	\centerline{\includegraphics[width=\linewidth]{figures/figure_nb_analogues.pdf}}
+	\caption{Number of analogues for the different regions and the various methods resulting from the optimization.
+Method 4Zo is made of a single level of analogy with $N_{1}$ analogues, whereas 4Zo-2HIo has two levels of analogy with respectively $N_{1}$ and $N_{2}$ analogues.}
+	\label{fig:figure_nb_analogues}
+\end{figure}
+
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=\linewidth]{figures/figure_nb_analogues_relationships.pdf}}
+	\caption{Relationships between the optimal number of analogues for both levels of the 4Zo-2HIo method and the corresponding ones for the unique level of the 4Zo method.}
+	\label{fig:figure_nb_analogues_relationships}
+\end{figure}
+
+\begin{figure}[htb]
 	\centering

### 2016-01-28 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Addition of plots for the CRPSS and the CRPS components.

@@
 \begin{table}[htb]
-	\caption{Same as Table \ref{table:scores}, but expressed as the CRPSS improvement (\%) compared to the reference methods.
-For 4Zo, the improvement is relative to the reference method on the atmospheric circulation (2Z, Table \ref{table:params_R1}).
-For 4Zo-2MIo and 4Zo-4MIo, the improvement is relative to the reference method on the circulation and moisture variables (2Z-2MI, Table \ref{table:params_R2}).}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline 
-			ID & \multicolumn{2}{c}{4Zo} & \multicolumn{2}{c}{4Zo-2MIo} & \multicolumn{2}{c}{4Zo-4MIo} \\ 
-			& CP & VP & CP & VP & CP & VP \\ 
-			\hline 
-			1 & 13.6 & 13.0 & 11.9 & 9.9 & 12.8 & 9.6 \\
-			2 & 13.3 & 7.5 & 11.2 & 9.4 & 12.5 & 10.8 \\
-			3 & 12.2 & 9.0 & 13.2 & 12.0 & 14.1 & 13.5 \\
-			4 & 14.2 & 10.5 & 12.4 & 10.6 & 14.5 & 12.5 \\
-			5 & 14.5 & 8.8 & 12.5 & 9.1 & 14.1 & 10.0 \\
-			6 & 13.3 & 8.6 & 11.5 & 8.2 & 14.1 & 8.4 \\
-			7 & 22.8 & 10.6 & 19.7 & 15.7 & 21.7 & 16.3 \\
-			8 & 20.7 & 11.9 & 19.2 & 13.5 & 20.8 & 14.0 \\
-			9 & 14.4 & 9.5 & 15.8 & 15.2 & 16.7 & 14.1 \\
-			10 & 14.2 & 9.4 & 12.9 & 11.2 & 14.6 & 11.8 \\
-			\hline
-			av. & 15.3 & 9.9 & 14.0 & 11.5 & 15.6 & 12.1 \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores_diff}
-\end{table}
-
-\begin{table}[htb]
 	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo method.}
@@
 \begin{figure}[htb]
+	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrpss_4Zo.pdf}}
+	\caption{CRPSS relative improvement of 4Zo compared to the reference methods 2Z (Table \ref{table:params_R1}) for the CP and the VP.}
+	\label{fig:figure_dcrpss_4Zo}
+\end{figure}
+
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrps_comp_4Zo.pdf}}
+	\caption{Changes in the CRPS components of 4Zo relatively to the total CRPS of the reference methods 2Z (Table \ref{table:params_R1}) for the CP and the VP.}
+	\label{fig:figure_dcrps_comp_4Zo}
+\end{figure}
+
+\begin{figure}[htb]
 	\centerline{\includegraphics[width=8cm]{figures/table_crossing_z4_calib.pdf}}
@@
 \begin{figure}[htb]
+	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrpss_4Zo-2HIo.pdf}}
+	\caption{CRPSS relative improvement of 4Zo-2HIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
+	\label{fig:figure_dcrpss_4Zo-2HIo}
+\end{figure}
+
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrpss_4Zo-4HIo.pdf}}
+	\caption{CRPSS relative improvement of 4Zo-4HIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
+	\label{fig:figure_dcrpss_4Zo-4HIo}
+\end{figure}
+
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrps_comp_4Zo-2HIo.pdf}}
+	\caption{Changes in the CRPS components of 4Zo-2HIo relatively to the total CRPS of the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
+	\label{fig:figure_dcrps_comp_4Zo-2HIo}
+\end{figure}
+
+\begin{figure}[htb]
 	\centerline{\includegraphics[width=8cm]{figures/table_crossing_z4-hi2_calib.pdf}}

### 2016-01-28 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Corrections in figures.

@@
 The resulting CRPSS scores are provided in Table \ref{table:scores} and are in average 35.8 \% for the CP and 35.5 \% for the VP.
-The improvement of the CRPSS score relatively to the reference method on the atmospheric circulation (optimized by the sequential procedure) is provided in Table \ref{table:scores_diff} and is in average 15.3 \% for the CP and 9.9 \% for the VP.
+The improvement of the CRPSS score relatively to the reference method on the atmospheric circulation (optimized by the sequential procedure) is illustrated in Figure \ref{fig:figure_dcrpss_4Zo} and is in average 15.3 \% for the CP and 9.9 \% for the VP.
 The score was also calculated for three precipitation thresholds: P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_4Zo}).
@@
 
-The scores show significant improvements for both the CP and the VP (Table \ref{table:scores_diff}) compared to the reference method optimized by the sequential procedure.
+The scores show significant improvements for both the CP and the VP (Figure \ref{fig:figure_dcrpss_4Zo}) compared to the reference method optimized by the sequential procedure.
 Even more interestingly, the results for higher precipitation thresholds (Table \ref{table:scores_thresholds_4Zo}) show the largest improvements.
 This is of particular interest in the framework of flood forecasting.
+
+The CRPS score was also discretized into its accuracy and sharpness components, as suggested by \citet{Bontron2004}.
+The changes in each of these components has been expressed relatively to the total CRPS value, of the 2Z reference method, in Figure \ref{fig:figure_dcrps_comp_4Zo} for the different regions and both the CP and the VP.
+One can see that the accuracy part is always improved to a greater extent than the sharpness, which can occasionally deteriorate.
+It means that the medians of the predicted precipitations distributions are closer to the observed value, whereas the spread of the distribution vary, but is in general a bit narrower.
 
@@
 
-The CRPSS scores of the optimized methods are provided in Table \ref{table:scores} and amounts to slightly more than 40 \% for both methods and for both periods.
-This results in a relative improvements that ranges from 11.5 \% to 15.6 \% compared to the reference method on the moisture analogy (Table \ref{table:scores_diff}) optimized with the sequential procedure.
+The CRPSS scores of the optimized methods are provided in Table \ref{table:scores} and amounts to slightly more than 40 \% in average for both methods and for both periods.
+This results in a relative improvements for 4Zo-2MIo that is in average 14.0 \% for the CP and 11.5 \% for the VP (Figure \ref{fig:figure_dcrpss_4Zo-2HIo}), compared to the reference method on the moisture analogy optimized with the sequential procedure.
+For 4Zo-4MIo, the average improvement is 15.6 \% for the CP and 12.1 \% for the VP (Figure \ref{fig:figure_dcrpss_4Zo-4HIo}).
+
 As for 4Zo, the 4Zo-2MIo and 4Zo-4MIo methods present larger improvements in the forecast for significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
@@
 As for the sequential procedure, the optimal value of $N_{1}$ increases when adding a second level of analogy (Figure \ref{fig:figure_nb_analogues}).
-One can also notice that the optimal number of analogues $N_{2}$ for the second level of analogy of 4Zo-2HIo is slightly inferior to $N_{1}$ from 4Zo, but very close.
+One can also notice that the optimal number of analogues $N_{2}$ for the second level of analogy of 4Zo-2MIo is slightly inferior to $N_{1}$ from 4Zo, but very close.
 There is a relationship between the optimal values of $N_{1}$ from both methods: the higher the $N_{1}$ of the first method, the higher $N_{1}$ and $N_{2}$ of the second is (Figure \ref{fig:figure_nb_analogues_relationships}).
 This relationship is not to be considered perfectly robust and should not be transposed to another case study, but in this case, it relates the magnitudes of the numbers on the various levels and methods.
-The optimal final number of analogues do not vary much: $23 \leq N_{1} \leq 33$ for 4Zo and $21 \leq N_{2} \leq 28$ for 4Zo-2HIo.
-However, the optimal number of $N_{1}$ analogues of the first level of 4Zo-2HIo varies to a greater extent: $48 \leq N_{1} \leq 84$.
-In this latter, it may be problematic to consider a fixed and unique value for all regions.
+The optimal final number of analogues do not vary much: $23 \leq N_{1} \leq 33$ for 4Zo and $21 \leq N_{2} \leq 28$ for 4Zo-2MIo.
+However, the optimal number of $N_{1}$ analogues of the first level of 4Zo-2MIo varies to a greater extent: $48 \leq N_{1} \leq 84$.
+In this latter method, it may be problematic to consider a fixed and unique value for all regions.
 
@@
 The CRPSS scores were improved by considering the moisture information (Table \ref{table:scores}).
-The optimized methods also perform significantly better than the reference method based on the moisture index (Table \ref{table:scores_diff}) and optimized by the sequential procedure.
+The optimized methods also perform significantly better than the reference method based on the moisture index (Figures \ref{fig:figure_dcrpss_4Zo-2HIo} and \ref{fig:figure_dcrpss_4Zo-2HIo}) optimized by the sequential procedure.
 However, there is no drastic difference between both 4Zo-2MIo and 4Zo-4MIo methods, which suggests that considering 4 moisture predictors is not necessary.
 When it comes to improvements for days with precipitation above the 3 thresholds (P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the forecast compared to reference method, mainly for heavy rainfall.
+
+As previously, the CRPS scores were discretized into their sharpness and accuracy components.
+The changes in each of these components, expressed relatively to the total CRPS values, is once again in favor of the accuracy over the sharpness (Figure \ref{fig:figure_dcrps_comp_4Zo-2HIo} for 4Zo-2MIo; 4Zo-4MIo not shown as similar).
 
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=\linewidth]{figures/figure_nb_analogues.pdf}}
-	\caption{Number of analogues for the different regions and the various methods resulting from the optimization.
-Method 4Zo is made of a single level of analogy with $N_{1}$ analogues, whereas 4Zo-2HIo has two levels of analogy with respectively $N_{1}$ and $N_{2}$ analogues.}
-	\label{fig:figure_nb_analogues}
-\end{figure}
-
-\begin{figure}[htb]
-	\centerline{\includegraphics[width=\linewidth]{figures/figure_nb_analogues_relationships.pdf}}
-	\caption{Relationships between the optimal number of analogues for both levels of the 4Zo-2HIo method and the corresponding ones for the unique level of the 4Zo method.}
-	\label{fig:figure_nb_analogues_relationships}
-\end{figure}
-
-\begin{figure}[htb]
 	\centering
@@
 	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrpss_4Zo-2HIo.pdf}}
-	\caption{CRPSS relative improvement of 4Zo-2HIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
+	\caption{CRPSS relative improvement of 4Zo-2MIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
 	\label{fig:figure_dcrpss_4Zo-2HIo}
@@
 	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrpss_4Zo-4HIo.pdf}}
-	\caption{CRPSS relative improvement of 4Zo-4HIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
+	\caption{CRPSS relative improvement of 4Zo-4MIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
 	\label{fig:figure_dcrpss_4Zo-4HIo}
@@
 	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrps_comp_4Zo-2HIo.pdf}}
-	\caption{Changes in the CRPS components of 4Zo-2HIo relatively to the total CRPS of the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
+	\caption{Changes in the CRPS components of 4Zo-2MIo relatively to the total CRPS of the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
 	\label{fig:figure_dcrps_comp_4Zo-2HIo}
+\end{figure}
+
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=\linewidth]{figures/figure_nb_analogues.pdf}}
+	\caption{Number of analogues for the different regions and the various methods resulting from the optimization.
+Method 4Zo is made of a single level of analogy with $N_{1}$ analogues, whereas 4Zo-2MIo has two levels of analogy with respectively $N_{1}$ and $N_{2}$ analogues.}
+	\label{fig:figure_nb_analogues}
+\end{figure}
+
+\begin{figure}[htb]
+	\centerline{\includegraphics[width=\linewidth]{figures/figure_nb_analogues_relationships.pdf}}
+	\caption{Relationships between the optimal number of analogues for both levels of the 4Zo-2MIo method and the corresponding ones for the unique level of the 4Zo method.}
+	\label{fig:figure_nb_analogues_relationships}
 \end{figure}

### 2016-02-05 AtmoSwing - Geoscientific Model Development/template.tex
Charle's corrections.
Michel's corrections.

@@
 
-\title{AtmoSwing (v1.4): Analog Technique Model for Statistical weather forecastING}
+\title{AtmoSwing (v1.4): Analogue Technique Model for Statistical weather forecastING}
 
@@
 As a general setting, the required ingredients are a couple of archives, one describing the situation through different variables, called predictors, and another one giving, for those situations, the value of the local variable of interest for engineering purpose, called predictand.
-Obviously, one understands that the longest and the richest the candidate archive of predictors, the more chance there will be to extract good analogues for a target situation in order to derive a conditional range of predictand values.
-As for the predictors, one can now hopefully rely on rich reanalysis products, commonly available over 40 years or more, and easily accessible.
 
@@
 This is particularly true for a predictand much required in hydrometeorological applications, namely the precipitation amount over a given domain and time duration.
-Incidentally, the forecast will be proposed as a statistical distribution based on the values taken by the predictand in the set of analogues selected, unless one considers only the single best analogue, which may not prove the most efficient.
-
-The purpose of this paper is not to argue in favour or against this approach, which has proved to be used efficiently either in operational forecasting or more recently in climate studies, and which is capable of challenging more classical approaches based on meteorological modeling.
-In operational forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies, it is more and more used to downscale the results of global climate model simulation runs.
-In operational, it should however not be considered as a substitute for numerical weather prediction models, but as a complement in order to get a fast and partly independent forecast that is known to be accurate several days in advance.
+Incidentally, the forecast will be proposed as a statistical distribution based on the values taken by the predictand in the set of analogues selected, unless one considers only the single best analogue, which may not prove the most efficient \citep{Bontron2005}.
+
+The AM, or an equivalent, was also used for short to medium term forecasting of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+\citet{Guilbaud1997} performed a literature review about the use of the AM in long-term forecasting and identified operational applications for monthly forecasts in many countries, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal forecasts: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
+
+The purpose of this paper is not to argue in favour or against this approach, which has proved to be used efficiently either in operational forecasting or more recently in climate studies \citep{Dayon2015}.
+\citet{Bliefernicht2010} compared the performance of the AM with a forecasting method based on a weather types approach, and concluded that the AM was more efficient.
+
+In operational forecasting, it has been used mainly by practitioners, notably hydropower companies \citep{Desaint2008a,BenDaoud2009,Obled2014} or flood forecasting services in France and Switzerland \citep{Marty2010,GarciaHernandez2009b,Horton2012}.
+It should however not be considered as a substitute for numerical weather prediction models, but as a complement in order to get a fast and partly independent forecast that is known to be accurate several days in advance.
 It therefore enriches the analysis of a potential critical situation for flood forecasting, for example, and is very interesting in early warning.
@@
 Thus, several examples of possible implementations are gathered here, as well as the main evolution steps of the AM.
-This latter summarizes the improvements that were brought, as well as discontinued approaches that were found less relevant (such as the use of PCA on the predictors).
+This latter summarizes the improvements that were brought, as well as discontinued approaches that were found less relevant.
 
@@
 
-The AM is being used for many years at EDF (\'{E}lectricit\'{e} de France), to build precipitation and temperature scenarios \citep{Desaint2008a}.
-It is also operational at the Compagnie Nationale du Rh\^{o}ne (CNR, France) and some flood forecasting services (SPC) in France and Switzerland \citep{Marty2010,GarciaHernandez2009b,Horton2012}.
-
 \subsection{Data}
 \label{sec:data}
-
-The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series one wants to forecast.
 
@@
 Other observed predictors can also be used, such as Sea Surface Temperature \citep[SST, ][]{Reynolds2007}.
+\citet{Bontron2004} proposed that the minimum length of the archive should be 30 years to forecast usual situations, and 40 years or more for intense events.
+
 The predictors describing the target situation in operational forecasting can, for example, result from GFS \citep[Global Forecast System,][]{Kanamitsu1991,Kanamitsu1989}, which is operated by NCEP and NOAA.
 
-\citet{Bontron2004} proposed that the minimum length of the archive should be 30 years to forecast usual situations, and 40 years or more for intense events.
-He also highlighted the dependency between the optimal number of analogues and the archive size: the shorter the archive, the lower the number of analogues.
-By varying the resolution of the predictors grids, he concluded that the performance increase is not significant for the analogy of atmospheric circulation below a resolution of 5\textdegree.
-However, it seems more important for the second level of analogy on moisture, which are more local variables.
-\citet{BenDaoud2010} assessed the European reanalysis ERA-40 \citep{Uppala2005} with a resolution of 1.125\textdegree.
-He identified a slight performance improvement, but not substantial enough to really justify an archive change \citep{BenDaoud2008}.
-
-The predictand is the local meteorological variable of interest.
-It can be 6-houry data, or more often daily time series, but has to be consistent with the time step of the predictors.
+The predictand can be 6-houry data, or more often daily time series.
 The most used predictand is the daily precipitation, usually averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.
@@
 The first level of analogy is always based on the atmospheric circulation when it comes to precipitation forecasting.
-The similarity of the atmospheric circulation of the target date with the candidate situations is thus assessed on the geopotential by means of the S1 criteria \citep[Eq.\ref{eq:S1}, ][see also section \ref{sec:method:evolution}]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial gridded window.
+The similarity of the atmospheric circulation of the target date with the candidate situations is thus assessed on the geopotential by means of the S1 criteria \citep[Eq.\ref{eq:S1}, ][see also section \ref{sec:method:references}]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial gridded window.
 
@@
 daily) observed precipitation amount (or another predictand of interest) of the $N_{i}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
-The empirical frequencies are processed for every value of the predictand, after classification, based on the Gringorten parameters (for a Gumbel or exponential law) and a probabilistic model can be fitted (e.g.
-Gamma function, or else).
+The empirical frequencies are processed for every value of the predictand, after classification, based on the Gringorten parameters \cite[for a Gumbel or exponential law][]{Gringorten1963} and a probabilistic model can be fitted \citep[e.g.
+Gamma function][]{Obled2002}.
+The forcast is often synthetized by the percentiles 20, 60 and 90~\% \citep{Guilbaud1997, Guilbaud1998}.
 
@@
 
-Then, the following levels of analogy are listed.
-They may start with an optional A (for analogy) when other methods are mixed into the parameterization \citep[see eg.
-][]{Chardon2014}.
+Then, the following levels of analogy are listed, which may start with an optional A (for analogy).
 For every level of analogy, the number of variables used (combination of atmospheric levels and time of observation) is first provided, and then the short name of the variable is given (according eg to ECMWF conventions; in upper case), for example:
@@
 	\item Z : geopotential (circulation)
+	\item TPW : total precipitable water
+	\item RH : relative humidity
+	\item V : wind velocity
+	\item W : vertical velocity
 	\item MI : moisture index (TPW * RH)
 	\item MF : moisture flux (V * TPW * RH)
-	\item TPW : total precipitable water
-	\item V : wind velocity
-	\item W : vertical velocity
 \end{itemize}
@@
 
-This nomenclature can be adapted to specific needs, or simplified for a better readability (eg. by removing the specification of the preselection). Examples are provided in the following section.
-
-\subsection{Evolution of the method for precipitation forecasting}
-\label{sec:method:evolution}
-
-The most common usage of the AM is for precipitation forecasting.
-Thus, the evolution presented hereafter focuses on this predictand.
-However, the AM, or an equivalent, was also used for short to medium term forecasting of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
-\citet{Guilbaud1997} performed a literature review about the use of the AM in long-term forecasting and identified operational applications for monthly forecasts in many countries, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal forecasts: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
-
-The evolution of the AM for precipitation forecasting led to several improvements.
-However, some of these are specific for a certain region and are not relevant for others, and some perform better depending on the lead time.
-Thereby, one cannot provide a single best parameterization for the AM, neither rank them from worst to best.
-Some examples of parameterizations of the most recent AM variant will thus be provided, in the chronological order they appeared.
-
-\citet{Lorenz1969} introduced the concept and established the basis of the AM.
-He considered looking for analogues on the geopotential field (at 200, 500 and 850~hPa) with a corrected Euclidean distance averaged on the 3 levels.
+This nomenclature can be adapted to specific needs, or simplified for a better readability (eg.
+by removing the specification of the preselection).
+For example, one of the most used parameterization established by \citet{Bontron2004} is composed of a first level of analogy on the geopotential height and a second on the moisture index and can thus be codified as PC-2Z-2MI.
+Other examples are provided in the following section.
+
+\subsection{Common variants for precipitation forecasting}
+\label{sec:method:references}
+
+Some examples of parameterizations of the most used or the most recent AM variants are provided hereunder.
+Some of these are more specific for a certain region and may not be relevant for others, and some perform better depending on the lead time.
+An extended history of the method's origin and its early evolution can be found in Appendix \ref{app:evolution}.
+
+The basis of the method was introduced by \citet{Lorenz1969}, who considered the analogy of the geopotential field on different pressure levels.
 In addition, the analogue situations were to belong to the same period of the year to be comparable in terms of distribution of solar energy.
-
-The use of the AM for operational forecasting of daily precipitation originates in the work of \citet{Duband1970, Duband1974, Duband1981}.
-It was then designed for operational forecasting at EDF (\'{E}lectricit\'{e} de France) in order to better manage water resources and flood risks.
-The geopotential height at 700~hPa and 00~h was used for its higher stability than the sea level pressure (SLP) field, and its sensitivity to the atmospheric disturbances \citep{Guilbaud1997}.
-However, the SLP at 06~h was also introduced for determining the precipitation intensity, as well as the temperature at 700~hPa as indicator of the thermal state of the air mass \citep{Duband1974}.
-The data were then based on 37 radiosounding over Europe and condensed by a principal component analysis.
-The first 25 analogues on the geopotential at 700~hPa were considered, and multiple local regressions between precipitation, SLP, and the temperature at 700~hPa were established on these analogues before being applied to the target situation \citep{Guilbaud1997}.
-The archives were split by season to consider comparable situations in terms of distribution of solar energy \citep{Lorenz1969}.
-This initially rigid division into seasons was then transformed into a moving selection of more or less two months around the target date.
-The forecast was then performed only on the basis of radiosonde observations and was temporally extrapolated to the two following days.
-After a few years, this statistical temporal extrapolation was abandoned in favor of a statistical adaptation using synoptic predictors taken from a numerical model, allowing a forecast over the following 4~days.
-
-Thereafter, the geopotential was considered at 1000~hPa and 700~hPa and the analogues selection was done in two stages: first according to an Euclidean distance in the space of the principal components of the geopotential field at 700~hPa, and then according to a correlation criterion (on the geopotential field at 700 and 1000~hPa, as well as on the thickness between these two levels) in order to remove days close in distance but too dissimilar in pattern \citep{Guilbaud1997}.
-The local regression approach to determine precipitation was eventually abandoned in favor of the direct probabilistic forecasting (synthesized by the percentiles 20, 60 and 90~\%), as it is performed today by interpolating linearly over the cumulative empirical distribution of daily precipitation measured at the analogue days \citep{Guilbaud1997, Guilbaud1998}.
-
-\citet{Wilson1980} sought the 20 best analogues on the geopotential field at 500 and 1000~hPa using the Teweles-Wobus (S1) criterion (Eq.
-\ref{eq:S1}), which allows for a comparison of the gradients and thus an analogy of the atmospheric circulation.
-This work has demonstrated the best performance of the AM compared to classical regression based approaches.
-\citet{Woodcock1980} used the same criterion on the SLP fields to select 50~analogues in order to forecast maximum daily temperatures.
-After comparing S1 to other criteria from the literature, or combinations of these, \citet{Guilbaud1998} confirmed that S1 is the most efficient.
-They also pointed out the benefit of using 2 atmospheric levels, 1000~hPa (Z1000) and 700~hPa (Z700) or 500~hPa (Z500), instead of one (also instead of the thickness), and to also consider 2 temporal windows, 00~h and 24~h \citep{Obled2002}.
-
-\citet{Guilbaud1997} stopped using PCA in order to work directly with the raw data interpolated on grids, which resulted in an improvement, especially when considering the S1 criterion instead of the Euclidean distance.
-The number of analogues considered was 50.
-When using multiple predictors, they combined the criteria values calculated on each atmospheric level and each temporal window using an arithmetic mean.
-
-At the dawn of the new millennium, \citet{Bontron2004} could benefit from a real breakthrough, the newly available NCEP/NCAR reanalysis data.
-This dataset being more homogeneous, much longer, and containing more variables than what was previously used, he could systematically assess a large selection of variables in the AM combined with different criteria.
-He thus confirmed the interest of the geopotential height along with the S1 criterion for the first level of analogy.
-He has also shown that the choice of the temporal window (time of observation) has a higher importance than the atmospheric level for the performance of the AM for daily precipitations.
-By assessing multiple combinations of atmospheric levels and temporal windows, he concluded that the coupled geopotential heights at 1000~hPa (Z1000) \& 12~h and 500~hPa (Z500) \& 24~h provided the best performance for the studied region (Table \ref{table:R1}).
+This preselection was later implemented as a moving selection of more or less two months around the target date.
+
+Several pressure levels were assessed by means of various criteria for the analogy on the geopotential field \citep{Duband1970, Duband1974, Duband1981, Guilbaud1997}.
+It was found to be important to compute the analogy on multiple pressure levels and different temporal windows \citep{Guilbaud1998, Obled2002}.
+The Teweles-Wobus (S1) criterion (Eq.
+\ref{eq:S1}), which allows for a comparison of the gradients and thus an analogy of the atmospheric circulation, was identified as the most suited criteria by different studies \citep{Wilson1980, Woodcock1980, Guilbaud1998, Bontron2004}.
+
+With a systematic assessment of the newly available NCEP/NCAR reanalysis data, \citet{Bontron2004} concluded that the coupled geopotential heights at 1000~hPa (Z1000) \& 12~h and 500~hPa (Z500) \& 24~h provided the best performance for the studied region (Table \ref{table:R1}).
 The analogy on the atmospheric circulation proposed by \citet{Bontron2004} is still, at the time of writing, often used operationally, and considered as a reference for benchmarking new parameterizations \citep{Horton2012, BenDaoud2015}.
+In order to assess the forecast, he introduced the Continuous Ranked Probability Score \citep[CRPS, Eq.
+\ref{eq:CRPS}, ][]{Brown1974}, which discards the issue of determining classes as with the Ranked Probability Score \citep{Epstein1969} previously in use.
 
@@
 
-\citet{Mandon1985} tried to introduce a second level of analogy and assessed different variables, such as wind, moisture, air temperature, surface temperature of the Mediterranean, the product of wind and the 700~hPa moisture, as well as a second barometric criteria differentiated according to the season.
-\citet{Vallee1986} continued to work on the second level of analogy and considered the wind at 700~hPa \& 12~h in order to improve heavy precipitation events for a region in France susceptible to southerly flows.
-
-\citet{Bontron2004} also assessed several variables for the second level of analogy and identified the moisture variables (precipitable water and relative humidity) and vertical velocity to be the most relevant.
-Finally, he found that a moisture index made of the product of relative humidity at 850~hPa (RH850) and total precipitable water (TPW) gave the best performance (Table \ref{table:R2}).
-This index does not represent an actual physical quantity, but expresses the water content of the air column and its proximity to saturation.
-
-\begin{table}[htbp]
-	\caption{Method of type PC-2Z-2MI proposed by \citet{Bontron2004}. Same conventions as Table \ref{table:R1}}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline 
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
-		& Z500 & 24~h & & \\ 
-		\middlehline
-		2 & TPW * RH850 & 12, 24~h & RMSE & 30 \\
-		\bottomhline 
-	\end{tabular} 
-	\label{table:R2}
-\end{table}
-
-He noted the relevance of defining different spatial windows for each region, rather than a single window for the entire territory.
-These windows are more able to represent the specific atmospheric influences for each region.
-In order to assess the forecast, he introduced the Continuous Ranked Probability Score \citep[CRPS, Eq.
-\ref{eq:CRPS}, ][]{Brown1974}, which discards the issue of determining classes as with the Ranked Probability Score \citep{Epstein1969} previously in use.
-
-\citet{Gibergans-Baguena2007} implemented the AM for daily precipitation forecasts in Catalonia.
-They considered the geopotential at 700 and 1000~hPa, and the thickness between these two levels, to search for analogy of circulation, and then applied a second selection on local data from radiosonde: stability indexes, precipitable water, temperature, etc.
-
-\citet{Marty2010} tested other temporal windows for intraday application on the basis of a more comprehensive reanalysis dataset.
-He first proposed to change the hours of observation for both levels of analogy (both for 06~h and 18~h), and selected the 925~hPa level for the moisture analogy (Table \ref{table:R3a}).
-The selected hours and atmospheric levels were not available before in the reanalysis dataset.
-
-\begin{table}[htbp]
-	\caption{Method of type PC-2Z-2MI proposed by \citet{Marty2010}. Same conventions as Table \ref{table:R1}}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline 
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{75} \\
-		& Z500 & 18~h & & \\ 
-		\middlehline
-		2 & TPW * RH925 & 06, 18~h & RMSE & 30 \\
-		\bottomhline 
-	\end{tabular} 
-	\label{table:R3a}
-\end{table}
-
-Then, \citet{Marty2010} changed the moisture index into the moisture flux by adding the wind velocity (V700 or V925) component in the multiplication.
-He considered this flux at 700~hPa or 925~hPa (Table \ref{table:R3b}).
-
-\begin{table}[htbp]
-	\caption{Method of type PC-2Z-2MF proposed by \citet{Marty2010}. Same conventions as Table \ref{table:R1}}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline 
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{60} \\
-		& Z500 & 18~h & & \\ 
-		\middlehline
-		2 & V700 * TPW * RH700 $^{\dagger}$ & 06, 18~h & RMSE & 25 \\
-		\bottomhline 
-	\end{tabular} 
-	\belowtable{$\dagger$ or V925 * TPW * RH925 as an alternative}
-	\label{table:R3b}
-\end{table}
-
-\citet{BenDaoud2010} applied the AM in the context of large floodplains (Sa\^{o}ne, Seine).
-He evaluated several variables usually used in weather forecasting, amongst them the air temperature and the vertical velocity that presented a potential interest.
-The temperature (at the nearest grid point, on the 925~hPa \& 36~h and 600~hPa \& 12~h levels) could replace the rigid calendar preselection of $\pm$ 60 days around the target date by a more dynamic screening of similar situations in terms of air masses.
-The seasonal effect is indeed also present in the temperature data.
-The number of preselected dates is equivalent to the number of days one would have chosen with the calendar approach, and thus depends on the archive size: $N_{0} = 60 \cdot 2 \cdot n_{a}$ where $n_{a}$ is the number of years in the calibration period.
-\citet{BenDaoud2010} also reconsidered the parameters of the moisture index and ended up with both 925~hPa and 700~hPa levels, at 12~h and 24~h, or at every time step (6~h) between 06~h and 30~h (Table \ref{table:R4b}).
-
-\begin{table}[htbp]
-	\caption{Method of type P2T-2Z-4MI (or P2T-2Z-10MI for the alternative version), by \citet{BenDaoud2010}. Same conventions as Table \ref{table:R1}}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline
-		\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
-		& T600 & 12~h & & \\ 
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
-		& Z500 & 24~h & & \\ 
-		\middlehline
-		\multirow{2}{*}{2} & TPW * RH925 & 12, 24~h $^{\dagger}$ & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
-		& TPW * RH700 & 12, 24~h $^{\dagger}$ & & \\ 
-		\bottomhline 
-	\end{tabular} 
-	\belowtable{$\dagger$ or 06-30~h as an alternative}
-	\label{table:R4b}
-\end{table}
-
-Subsequently, \citet{BenDaoud2010} added an additional level of analogy, between the circulation and the moisture analogy (Table \ref{table:R5}), based on vertical velocity at 850~hPa (W850).
-This AM was developed for large floodplains in France, but was found to be not relevant for an Alpine environment where topography is mostly responsible for uplift of air masses \citep{Horton2012}.
-
-\begin{table}[htbp]
-	\caption{Method of type P2T-2Z-4W-4MI, by \citet{BenDaoud2010}. Same conventions as Table \ref{table:R1}}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline
-		\multirow{2}{*}{0} & T925 (1 point) & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
-		& T600 (1 point) & 12~h & & \\ 
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{170} \\
-		& Z500 & 24~h & & \\ 
-		\middlehline
-		2 & W850 & 06-24~h & RMSE & 70 \\
-		\middlehline
-		\multirow{2}{*}{3} & TPW * RH925 & 12, 24~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
-		& TPW * RH700 & 12, 24~h & & \\
-		\bottomhline 
-	\end{tabular}
-	\label{table:R5}
-\end{table}
-
-\citet{Bliefernicht2010} proposed to add a weighting to each grid points of the predictor domain to overcome a comparison on a fixed-size window, and to give more importance to regions with relevant atmospheric circulation information.
-However, he noticed that there is a risk of overparametrization as the performance was not stable between the calibration and the validation periods, and a simplification of the weighting fields may be necessary.
-He also compared the performance of the AM with a forecasting method based on a weather types approach, and concluded that the AM was more efficient.
-
 \citet{Horton2012} identified that the analogy on the atmospheric circulation may not be comprehensive, and that a significant gain was obtained by considering 4 atmospheric levels (1000, 850, 700, and 500~hPa at 12 or 24~h) instead of 2 (Table \ref{table:R6}).
 The number of analogues ($N_{1}$) was not provided globally, as it was calibrated for every subregion.
-Considering an AM only based on the atmospheric circulation has an interest for operational forecasting, since moisture variables are less well forecasted for a lead time of a few days.
 An equivalent structure was also optimized by means of generic algorithms (PC-4Zgo), which is the topic of another paper \citep{Horton2016b}.
@@
 
+A second level of analogy based on thermodynamic variables was then introduced by \citet{Mandon1985, Vallee1986, Gibergans-Baguena2007}.
+After a systematic assessment, \citet{Bontron2004} pointed out that a moisture index (MI) made of the product of relative humidity at 850~hPa (RH850) and total precipitable water (TPW) gave the best performance (Table \ref{table:R2}).
+This index does not represent an actual physical quantity, but expresses the water content of the air column and its proximity to saturation.
+
+\begin{table}[htbp]
+	\caption{Method of type PC-2Z-2MI proposed by \citet{Bontron2004}. Same conventions as Table \ref{table:R1}}
+	\begin{tabular}{ccccc}
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline 
+		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+		\middlehline 
+		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
+		& Z500 & 24~h & & \\ 
+		\middlehline
+		2 & TPW * RH850 & 12, 24~h & RMSE & 30 \\
+		\bottomhline 
+	\end{tabular} 
+	\label{table:R2}
+\end{table}
+
+\citet{Marty2010} tested other temporal windows for intraday application on the basis of a more comprehensive reanalysis dataset.
+He first proposed to change the hours of observation for both levels of analogy (both for 06~h and 18~h), and selected the 925~hPa level for the moisture analogy (Table \ref{table:R3a}).
+The selected hours and atmospheric levels were not available before in the reanalysis dataset.
+
+\begin{table}[htbp]
+	\caption{Method of type PC-2Z-2MI proposed by \citet{Marty2010}. Same conventions as Table \ref{table:R1}}
+	\begin{tabular}{ccccc}
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline 
+		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+		\middlehline 
+		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{75} \\
+		& Z500 & 18~h & & \\ 
+		\middlehline
+		2 & TPW * RH925 & 06, 18~h & RMSE & 30 \\
+		\bottomhline 
+	\end{tabular} 
+	\label{table:R3a}
+\end{table}
+
+Then, \citet{Marty2010} changed the moisture index into the moisture flux by adding the wind velocity (V700 or V925) component in the multiplication.
+He considered this flux at 700~hPa or 925~hPa (Table \ref{table:R3b}).
+
+\begin{table}[htbp]
+	\caption{Method of type PC-2Z-2MF proposed by \citet{Marty2010}. Same conventions as Table \ref{table:R1}}
+	\begin{tabular}{ccccc}
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline 
+		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+		\middlehline 
+		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{60} \\
+		& Z500 & 18~h & & \\ 
+		\middlehline
+		2 & V700 * TPW * RH700 $^{\dagger}$ & 06, 18~h & RMSE & 25 \\
+		\bottomhline 
+	\end{tabular} 
+	\belowtable{$\dagger$ or V925 * TPW * RH925 as an alternative}
+	\label{table:R3b}
+\end{table}
+
+\citet{BenDaoud2010} applied the AM in the context of large floodplains (Sa\^{o}ne, Seine).
+He evaluated several variables usually used in weather forecasting, amongst them the air temperature and the vertical velocity that presented a potential interest.
+The temperature (at the nearest grid point, on the 925~hPa \& 36~h and 600~hPa \& 12~h levels) could replace the rigid calendar preselection of $\pm$ 60 days around the target date by a more dynamic screening of similar situations in terms of air masses.
+The seasonal effect is indeed also present in the temperature data.
+The number of preselected dates is equivalent to the number of days one would have chosen with the calendar approach, and thus depends on the archive size: $N_{0} = 60 \cdot 2 \cdot n_{a}$ where $n_{a}$ is the number of years in the calibration period.
+\citet{BenDaoud2010} also reconsidered the parameters of the moisture index and ended up with both 925~hPa and 700~hPa levels, at 12~h and 24~h, or at every time step (6~h) between 06~h and 30~h (Table \ref{table:R4b}).
+
+\begin{table}[htbp]
+	\caption{Method of type P2T-2Z-4MI (or P2T-2Z-10MI for the alternative version), by \citet{BenDaoud2010}. Same conventions as Table \ref{table:R1}}
+	\begin{tabular}{ccccc}
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline
+		\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
+		& T600 & 12~h & & \\ 
+		\middlehline 
+		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
+		& Z500 & 24~h & & \\ 
+		\middlehline
+		\multirow{2}{*}{2} & TPW * RH925 & 12, 24~h $^{\dagger}$ & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
+		& TPW * RH700 & 12, 24~h $^{\dagger}$ & & \\ 
+		\bottomhline 
+	\end{tabular} 
+	\belowtable{$\dagger$ or 06-30~h as an alternative}
+	\label{table:R4b}
+\end{table}
+
+Subsequently, \citet{BenDaoud2010} added an additional level of analogy, between the circulation and the moisture analogy (Table \ref{table:R5}), based on vertical velocity at 850~hPa (W850).
+This AM was developed for large floodplains in France, but was found to be not relevant for an Alpine environment where topography is mostly responsible for uplift of air masses \citep{Horton2012}.
+
+\begin{table}[htbp]
+	\caption{Method of type P2T-2Z-4W-4MI, by \citet{BenDaoud2010}. Same conventions as Table \ref{table:R1}}
+	\begin{tabular}{ccccc}
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline
+		\multirow{2}{*}{0} & T925 (1 point) & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
+		& T600 (1 point) & 12~h & & \\ 
+		\middlehline 
+		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{170} \\
+		& Z500 & 24~h & & \\ 
+		\middlehline
+		2 & W850 & 06-24~h & RMSE & 70 \\
+		\middlehline
+		\multirow{2}{*}{3} & TPW * RH925 & 12, 24~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
+		& TPW * RH700 & 12, 24~h & & \\
+		\bottomhline 
+	\end{tabular}
+	\label{table:R5}
+\end{table}
+
 \citet{Horton2012} also integrated an analogy on the moisture flux, after the circulation analogy on the 4 atmospheric levels (Table \ref{table:R7}).
-The number of analogues ($N_{1}$, $N_{2}$) were also calibrated for every subregion.
+The number of analogues ($N_{1}$, $N_{2}$) were calibrated for every subregion.
 Similarly, an equivalent structure was optimized \citep[PC-4Zgo-2MIgo,][]{Horton2016b}.
@@
 Moreover, the under-dispersion of the ensemble forecast from the numerical model has been corrected using analogues \citep{Hamill2006}.
-Correction of ensemble forecast under-dispersion by means of the AM is also used operationally at EDF.
+Correction of ensemble forecast under-dispersion by means of the AM is also used operationally at EDF (\'{E}lectricit\'{e} de France).
 
@@
 Developments have been made with a test driven development (TDD) approach.
-A collection of 500+ tests are frequently evaluated and completed during development, in order to verify that code changes do not introduce regression.
+A collection of more than 500 tests are frequently evaluated and completed during development, in order to verify that code changes do not introduce regression.
 Every analogy criterion, prediction score, searching and sorting functions, data manipulation, and so on, is tested.
-The integration tests specific to the  AM rely on the results of another analogue sorting software developed in Grenoble.
-They result from a comparison work done with the help of R.
-Marty in order to ensure that the results of AtmoSwing are exactly equivalent to their model, given the same parameters and data.
-These tests are part of the checks carried out regularly, so that these results are always reproducible.
+The integration tests specific to the AM rely on the results of another analogue sorting software developed at the LTHE - INPG university of Grenoble.
+They ensure that the results of AtmoSwing are exactly equivalent to their model, given the same parameters and data.
+These tests are part of the checks carried out regularly.
+
+A user interface allows the creation of the precipitation database.
+Its generation consists in extracting the time series from text files in order to process them and save a database in the NetCDF format.
+During the process, Gumbel adjustments are automatically calculated in order to determine the values corresponding to different return periods.
+The time series are normalized by a selected return period (default 10~years) and their square root is eventually processed.
+The final database file contains both the raw and the normalized series, as well as characteristics of the gauging stations and some metadata.
 
@@
 
-Each implementation of the AM (see section \ref{sec:method:evolution}) may enter this scheme, even if it consists of preprocessed variables (e.g.
+Each implementation of the AM (see section \ref{sec:method:references}) may enter this scheme, even if it consists of preprocessed variables (e.g.
 moisture index).
@@
 The software also use the linear algebra library Eigen 3 \citep{Guennebaud2010} for calculations on vectors and matrices, which resulted in time saving.
-Obviously, multi-threading is also implemented.
-
-First, every identified redundancy has been removed.
+Multi-threading is also implemented so that the search for analogue situations in the archive is distributed among the available threads.
+
+The code optimization consited in reducing the most significant processing time identified by means of profiling tools.
+First, every identified redundancy in processing has been removed.
 Then, when looking for a certain date or data, the search looks first in the proximity where it is likely to be found instead of exploring an entire array.
 Similar data are not loaded twice, but shared pointers are used.
-Many other improvements allowed saving time, for example the use of the quicksort method \citep{Hoare1962a} to sort the date vectors according to the values of analogy criteria.
+Many other improvements allowed saving more time, for example the use of the quicksort method \citep{Hoare1962a} to sort the date vectors according to the values of analogy criteria.
 Different implementations were tested (many remain in the code as alternatives) in order to select the most efficient: for example, when storing analogue dates according to their criteria value, it is faster to insert them in a fixed-size array rather than storing them all and sorting the array subsequently.
@@
 The software first downloads the predictor describing the target situation, such as 1\textdegree\ GFS outputs \citep[Global Forecast System,][see section \ref{sec:data}]{Kanamitsu1991,Kanamitsu1989}.
-It then interpolates the gridded data to match the resolution of the archive (for example 2.5\textdegree\ in the case of the NCEP/NCAP reanalysis I).
+It then interpolates linearly the gridded data to match the resolution of the archive (for example 2.5\textdegree\ in the case of the NCEP/NCAP reanalysis I).
 The analogues dates are next sought according to the selected parameterization, and the predictand data are associated with the corresponding dates.
@@
 When using a given parameterization of the AM, it has previously been optimized in a perfect prognosis context \citep[i.e.
-by optimizing on the reanalysis dataset; however, this does not take into account the uncertainty of the target situation when taken from operational forecasts of a NWP model,][]{Klein1963}.
+by optimizing on the reanalysis dataset; however, this does not take into account the uncertainty of the target situation when taken from operational forecasts of a Numerical Weather Prediction model,][]{Klein1963}.
 In operational forecasting, one should take into account the uncertainty of the predictor increasing with the lead time.
@@
 When using GFS outputs, this would provide 4 forecasts a day with a reduced delay between GFS outputs availability and the analogue forecast.
-
-A user interface allows the creation of the precipitation database.
-Its generation consists in extracting the time series from text files in order to process them and save a database in the NetCDF format.
-During the process, Gumbel adjustments are automatically calculated in order to determine the values corresponding to different return periods.
-The time series are normalized by a selected return period (default 10~years) and their square root is eventually processed.
-The final database file contains both the raw and the normalized series, as well as characteristics of the gauging stations and some metadata.
 
@@
 AtmoSwing Viewer relies on workspaces to specify the path to the forecast directories and the GIS layers.
-Many GIS formats are supported thanks to the GDAL and VroomGIS libraries.
+Many GIS formats are supported thanks to GDAL \cite[Geospatial Data Abstraction Library,][]{GDAL2014}.
 One can have as many layers as desired, and can control their display properties.
@@
 Comparing the results from the AM to an ensemble forecast, \citet{Marty2010} found the AM to be better than the considered ensembles, particularly for strong precipitation.
-The gain of the AM comes from a greater accuracy for a poorer sharpness, when the ensemble forecasts are very sharp, but lack a bit of accuracy.
-
-When comparing the performance of Meteo France numerical models along with the AM, \citet{Djerboua2001} concluded that the numerical models were at that time better at predicting the precipitation of the current day, but the AM became more competitive for the following lead times.
-It is indeed very interesting in early warning approaches, as it may able to identify a potentially critical situation one week ahead.
-
-All AMs rely on atmospheric circulation information, while some add subsequent levels of analogy on moisture or other thermodynamic predictors (see section \ref{sec:method:evolution}).
+
+All AMs rely on atmospheric circulation information, while some add subsequent levels of analogy on moisture or other thermodynamic predictors (see section \ref{sec:method:references}).
 However, these subsequent predictors were found to be relevant only on the first 3~days, and not much further, due to higher uncertainties in their forecast (see section \ref{sec:optimization-operational}).
@@
 The calibration procedure that we call ''sequential'' or ''classic'', but which is also named ''optimization'' \cite[eg.
-by ][]{BenDaoud2015}, was developed by \citet{Bontron2004} at the LTHE laboratory (INPG, Grenoble).
+by ][]{BenDaoud2015}, was developed at LTHE - INPG university of Grenoble \citep{Bontron2004}.
 It is a semi-automatic procedure that determines the optimal parameters for the different variables of each level of analogy.
@@
 	\item a better insight in the role of the length of the archive, by using long reanalyses over the $20^{th}$ century;	
-	\item a weighting of the predictor grids, in order to get free of fixed rectangular spatial windows;
+	\item a weighting of the predictor grids \citep[see][]{Bliefernicht2010};
 	\item assessment of potential indicators based on the properties of the distribution of all analogues or the 10 best, for example;
@@
 
-%\appendix
-%\section{}    %% Appendix A
-
-%\subsection{}     %% Appendix A1, A2, etc.
+\appendix
+\section{Origin and early evolution of the method for precipitation forecasting}    %% Appendix A
+\label{app:evolution}
+
+\citet{Lorenz1969} introduced the concept and established the basis of the AM.
+He considered looking for analogues on the geopotential field (at 200, 500 and 850~hPa) with a corrected Euclidean distance averaged on the 3 levels.
+
+The use of the AM for operational forecasting of daily precipitation originates in the work of \citet{Duband1970, Duband1974, Duband1981}.
+It was then designed for operational forecasting at EDF in order to better manage water resources and flood risks.
+The geopotential height at 700~hPa and 00~h was used for its higher stability than the sea level pressure (SLP) field, and its sensitivity to the atmospheric disturbances \citep{Guilbaud1997}.
+However, the SLP at 06~h was also introduced for determining the precipitation intensity, as well as the temperature at 700~hPa as indicator of the thermal state of the air mass \citep{Duband1974}.
+The data were then based on 37 radiosounding over Europe and condensed by a principal component analysis.
+The first 25 analogues on the geopotential at 700~hPa were considered, and multiple local regressions between precipitation, SLP, and the temperature at 700~hPa were established on these analogues before being applied to the target situation \citep{Guilbaud1997}.
+The archives were split by season to consider comparable situations in terms of distribution of solar energy \citep{Lorenz1969}.
+This initially rigid division into seasons was then transformed into a moving selection of more or less two months around the target date.
+The forecast was then performed only on the basis of radiosonde observations and was temporally extrapolated to the two following days.
+After a few years, this statistical temporal extrapolation was abandoned in favor of a statistical adaptation using synoptic predictors taken from a numerical model, allowing a forecast over the following 4~days.
+
+Thereafter, the geopotential was considered at 1000~hPa and 700~hPa and the analogues selection was done in two stages: first according to an Euclidean distance in the space of the principal components of the geopotential field at 700~hPa, and then according to a correlation criterion (on the geopotential field at 700 and 1000~hPa, as well as on the thickness between these two levels) in order to remove days close in distance but too dissimilar in pattern \citep{Guilbaud1997}.
+The local regression approach to determine precipitation was eventually abandoned in favor of the direct probabilistic forecasting (synthesized by the percentiles 20, 60 and 90~\%), as it is performed today by interpolating linearly over the cumulative empirical distribution of daily precipitation measured at the analogue days \citep{Guilbaud1997, Guilbaud1998}.
+
+\citet{Wilson1980} sought the 20 best analogues on the geopotential field at 500 and 1000~hPa using the Teweles-Wobus (S1) criterion (Eq.
+\ref{eq:S1}), which allows for a comparison of the gradients and thus an analogy of the atmospheric circulation.
+This work has demonstrated the best performance of the AM compared to classical regression based approaches.
+\citet{Woodcock1980} used the same criterion on the SLP fields to select 50~analogues in order to forecast maximum daily temperatures.
+After comparing S1 to other criteria from the literature, or combinations of these, \citet{Guilbaud1998} confirmed that S1 is the most efficient.
+They also pointed out the benefit of using 2 atmospheric levels, 1000~hPa (Z1000) and 700~hPa (Z700) or 500~hPa (Z500), instead of one (also instead of the thickness), and to also consider 2 temporal windows, 00~h and 24~h \citep{Obled2002}.
+
+\citet{Guilbaud1997} stopped using PCA in order to work directly with the raw data interpolated on grids, which resulted in an improvement, especially when considering the S1 criterion instead of the Euclidean distance.
+The number of analogues considered was 50.
+When using multiple predictors, they combined the criteria values calculated on each atmospheric level and each temporal window using an arithmetic mean.
+
+At the dawn of the new millennium, \citet{Bontron2004} could benefit from a real breakthrough, the newly available NCEP/NCAR reanalysis data.
+This dataset being more homogeneous, much longer, and containing more variables than what was previously used, he could systematically assess a large selection of variables in the AM combined with different criteria.
+He thus confirmed the interest of the geopotential height along with the S1 criterion for the first level of analogy.
+He has also shown that the choice of the temporal window (time of observation) has a higher importance than the atmospheric level for the performance of the AM for daily precipitations.
+By assessing multiple combinations of atmospheric levels and temporal windows, he concluded that the coupled geopotential heights at 1000~hPa (Z1000) \& 12~h and 500~hPa (Z500) \& 24~h provided the best performance for the studied region (Table \ref{table:R1}).
+
+\citet{Mandon1985} tried to introduce a second level of analogy and assessed different variables, such as wind, moisture, air temperature, surface temperature of the Mediterranean, the product of wind and the 700~hPa moisture, as well as a second barometric criteria differentiated according to the season.
+\citet{Vallee1986} continued to work on the second level of analogy and considered the wind at 700~hPa \& 12~h in order to improve heavy precipitation events for a region in France susceptible to southerly flows.
+
+\citet{Bontron2004} also assessed several variables for the second level of analogy and identified the moisture variables (precipitable water and relative humidity) and vertical velocity to be the most relevant.
+Finally, he found that a moisture index made of the product of relative humidity at 850~hPa (RH850) and total precipitable water (TPW) gave the best performance (Table \ref{table:R2}).
+He noted the relevance of defining different spatial windows for each region, rather than a single window for the entire territory.
+These windows are more able to represent the specific atmospheric influences for each region.
+He also highlighted the dependency between the optimal number of analogues and the archive size: the shorter the archive, the lower the number of analogues.
+
+By varying the resolution of the predictors grids, \citet{Bontron2004} concluded that the performance increase is not significant for the analogy of atmospheric circulation below a resolution of 5\textdegree.
+However, it seems more important for the second level of analogy on moisture, which are more local variables.
+\citet{BenDaoud2010} assessed the European reanalysis ERA-40 \citep{Uppala2005} with a resolution of 1.125\textdegree.
+He identified a slight performance improvement, but not substantial enough to really justify an archive change \citep{BenDaoud2008}.
+
+\citet{Gibergans-Baguena2007} implemented the AM for daily precipitation forecasts in Catalonia.
+They considered the geopotential at 700 and 1000~hPa, and the thickness between these two levels, to search for analogy of circulation, and then applied a second selection on local data from radiosonde: stability indexes, precipitable water, temperature, etc.
 
@@
 
-Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
+Thanks to the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton, the Water, Land and Sanitation Service of the Vaud Canton and the Swiss Federal Office for Environment (FOEV), who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
 The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
@@
 \bibliographystyle{copernicus}
-\bibliography{../_refs/_articles-atmoswing}
+\bibliography{refs}
 

### 2016-02-05 AtmoSwing - Geoscientific Model Development/template.tex
Update of the Copernicus Linux package.

@@
 %% 2-Column Papers and Discussion Papers
-%\documentclass[gmd, manuscript]{copernicus}
-\documentclass[gmd]{copernicus}
+\documentclass[gmd, manuscript]{copernicus}
+%\documentclass[gmd]{copernicus}
 
@@
 
-The purpose of this paper is not to argue in favour or against this approach, which has proved to be used efficiently either in operational forecasting or more recently in climate studies \citep{Dayon2015}.
+The purpose of this paper is not to argue in favour or against this approach, which has proved to be used efficiently either in operational forecasting \citep{Djerboua2001} or more recently in climate studies \citep{Dayon2015}.
 \citet{Bliefernicht2010} compared the performance of the AM with a forecasting method based on a weather types approach, and concluded that the AM was more efficient.

### 2016-02-05 AtmoSwing - Geoscientific Model Development/template.tex
Moving the tables and figures at the end of the document.
Setting correct figures and tables position.
Preparing for submission.

@@
 
-The Analogue Method (AM) will first be presented along with various implementations (section \ref{sec:method}), as the optimal version of the method may vary with the location of interest, and as all these can be processed with AtmoSwing.
-The software will then be presented (section \ref{sec:atmoswing}), and its modules detailed, such as the Forecaster (section \ref{sec:forecaster}) and the Viewer (section \ref{sec:viewer}) that are tools for operational use, and the Optimizer (section \ref{sec:optimizer}) that allows optimizing the method for a given predictand time series.
+The Analogue Method (AM) will first be presented along with various implementations (Sect.
+\ref{sec:method}), as the optimal version of the method may vary with the location of interest, and as all these can be processed with AtmoSwing.
+The software will then be presented (Sect.
+\ref{sec:atmoswing}), and its modules detailed, such as the Forecaster (Sect.
+\ref{sec:forecaster}) and the Viewer (Sect.
+\ref{sec:viewer}) that are tools for operational use, and the Optimizer (Sect.
+\ref{sec:optimizer}) that allows optimizing the method for a given predictand time series.
 
@@
 The first level of analogy is always based on the atmospheric circulation when it comes to precipitation forecasting.
-The similarity of the atmospheric circulation of the target date with the candidate situations is thus assessed on the geopotential by means of the S1 criteria \citep[Eq.\ref{eq:S1}, ][see also section \ref{sec:method:references}]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial gridded window.
+The similarity of the atmospheric circulation of the target date with the candidate situations is thus assessed on the geopotential by means of the S1 criteria \citep[Eq.
+(\ref{eq:S1}), ][see also Sect.
+\ref{sec:method:references}]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial gridded window.
 
@@
 This is particularly useful when working with a global optimization method, where nothing is fixed but the very structure of the AM.
-
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/nomenclature.pdf}
-	\caption{Proposed structure for naming the parameterizations of the AM.}
-	\label{figure:nomenclature}
-\end{figure}
 
@@
 	\setlength\itemsep{-2px}
-	\item sc : sequential calibration (can be omitted as considered as default, see section \ref{sec:atmoswing-calibration})
+	\item sc : sequential calibration (can be omitted as considered as default, see Sect. \ref{sec:atmoswing-calibration})
 	\item go (or just ''o'') : global optimization (by means of genetic algorithms for example)
@@
 
-\begin{table}[htbp]
-	\caption{Method of type PC-2Z proposed by \citet{Bontron2004}.
-The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window).
-The criteria used for the current level of analogy is then provided, as well as the number of analogues.}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline 
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
-		& Z500 & 24~h & & \\ 
-		\bottomhline 
-	\end{tabular} 
-	\label{table:R1}
-\end{table}
-
 \citet{Horton2012} identified that the analogy on the atmospheric circulation may not be comprehensive, and that a significant gain was obtained by considering 4 atmospheric levels (1000, 850, 700, and 500~hPa at 12 or 24~h) instead of 2 (Table \ref{table:R6}).
@@
 
-\begin{table}[htbp]
-	\caption{Method of type PC-4Z proposed by \citet{Horton2012}. Same conventions as Table \ref{table:R1}}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline 
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{4}{*}{1} & Z1000 & 12~h & \multirow{4}{*}{S1} & \multirow{4}{*}{$N_{1}$} \\
-		& Z850 & 24~h & & \\ 
-		& Z700 & 12~h & & \\ 
-		& Z500 & 24~h & & \\ 
-		\bottomhline 
-	\end{tabular}
-	\label{table:R6}
-\end{table}
-
 A second level of analogy based on thermodynamic variables was then introduced by \citet{Mandon1985, Vallee1986, Gibergans-Baguena2007}.
@@
 
-\begin{table}[htbp]
-	\caption{Method of type PC-2Z-2MI proposed by \citet{Bontron2004}. Same conventions as Table \ref{table:R1}}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline 
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
-		& Z500 & 24~h & & \\ 
-		\middlehline
-		2 & TPW * RH850 & 12, 24~h & RMSE & 30 \\
-		\bottomhline 
-	\end{tabular} 
-	\label{table:R2}
-\end{table}
-
 \citet{Marty2010} tested other temporal windows for intraday application on the basis of a more comprehensive reanalysis dataset.
@@
 
-\begin{table}[htbp]
-	\caption{Method of type PC-2Z-2MI proposed by \citet{Marty2010}. Same conventions as Table \ref{table:R1}}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline 
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{75} \\
-		& Z500 & 18~h & & \\ 
-		\middlehline
-		2 & TPW * RH925 & 06, 18~h & RMSE & 30 \\
-		\bottomhline 
-	\end{tabular} 
-	\label{table:R3a}
-\end{table}
-
 Then, \citet{Marty2010} changed the moisture index into the moisture flux by adding the wind velocity (V700 or V925) component in the multiplication.
 He considered this flux at 700~hPa or 925~hPa (Table \ref{table:R3b}).
-
-\begin{table}[htbp]
-	\caption{Method of type PC-2Z-2MF proposed by \citet{Marty2010}. Same conventions as Table \ref{table:R1}}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline 
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{60} \\
-		& Z500 & 18~h & & \\ 
-		\middlehline
-		2 & V700 * TPW * RH700 $^{\dagger}$ & 06, 18~h & RMSE & 25 \\
-		\bottomhline 
-	\end{tabular} 
-	\belowtable{$\dagger$ or V925 * TPW * RH925 as an alternative}
-	\label{table:R3b}
-\end{table}
 
@@
 
-\begin{table}[htbp]
-	\caption{Method of type P2T-2Z-4MI (or P2T-2Z-10MI for the alternative version), by \citet{BenDaoud2010}. Same conventions as Table \ref{table:R1}}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline
-		\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
-		& T600 & 12~h & & \\ 
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
-		& Z500 & 24~h & & \\ 
-		\middlehline
-		\multirow{2}{*}{2} & TPW * RH925 & 12, 24~h $^{\dagger}$ & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
-		& TPW * RH700 & 12, 24~h $^{\dagger}$ & & \\ 
-		\bottomhline 
-	\end{tabular} 
-	\belowtable{$\dagger$ or 06-30~h as an alternative}
-	\label{table:R4b}
-\end{table}
-
 Subsequently, \citet{BenDaoud2010} added an additional level of analogy, between the circulation and the moisture analogy (Table \ref{table:R5}), based on vertical velocity at 850~hPa (W850).
 This AM was developed for large floodplains in France, but was found to be not relevant for an Alpine environment where topography is mostly responsible for uplift of air masses \citep{Horton2012}.
-
-\begin{table}[htbp]
-	\caption{Method of type P2T-2Z-4W-4MI, by \citet{BenDaoud2010}. Same conventions as Table \ref{table:R1}}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline
-		\multirow{2}{*}{0} & T925 (1 point) & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
-		& T600 (1 point) & 12~h & & \\ 
-		\middlehline 
-		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{170} \\
-		& Z500 & 24~h & & \\ 
-		\middlehline
-		2 & W850 & 06-24~h & RMSE & 70 \\
-		\middlehline
-		\multirow{2}{*}{3} & TPW * RH925 & 12, 24~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
-		& TPW * RH700 & 12, 24~h & & \\
-		\bottomhline 
-	\end{tabular}
-	\label{table:R5}
-\end{table}
 
@@
 Similarly, an equivalent structure was optimized \citep[PC-4Zgo-2MIgo,][]{Horton2016b}.
-
-\begin{table}[htbp]
-	\caption{Method of type PC-4Z-2MI, by \citet{Horton2012}. Same conventions as Table \ref{table:R1}}
-	\begin{tabular}{ccccc}
-		\tophline
-		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
-		\middlehline 
-		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-		\middlehline 
-		\multirow{4}{*}{1} & Z1000 & 12~h & \multirow{4}{*}{S1} & \multirow{4}{*}{$N_{1}$} \\
-		& Z850 & 24~h & & \\ 
-		& Z700 & 12~h & & \\ 
-		& Z500 & 24~h & & \\ 
-		\middlehline
-		2 & V700 * TPW * RH700 & 12, 24~h & RMSE & $N_{2}$ \\
-		\bottomhline 
-	\end{tabular}
-	\label{table:R7}
-\end{table}
 
@@
 
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/logo.pdf}
-	\caption{The AtmoSwing logo and its 3 modules: the Forecaster, the Viewer and the Optimizer.}
-	\label{figure:logo}
-\end{figure}
-
 The source code in under version control (with Mercurial), and is open source (on Bitbucket, www.atmoswing.org).
@@
 
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/flowchart_modules_atmoswing.pdf}
-	\caption{Simplified organizational chart of the AM implementation in AtmoSwing.}
-	\label{figure:flowchart_modules_atmoswing}
-\end{figure}
-
-Each implementation of the AM (see section \ref{sec:method:references}) may enter this scheme, even if it consists of preprocessed variables (e.g.
+Each implementation of the AM (see Sect.
+\ref{sec:method:references}) may enter this scheme, even if it consists of preprocessed variables (e.g.
 moisture index).
@@
 
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/atmoswing-forecaster.png}
-	\caption{Graphical user interface of the Forecaster module. A list of different parameterizations is being processed.}
-	\label{figure:atmoswing-forecaster-gui}
-\end{figure}
-
-The software first downloads the predictor describing the target situation, such as 1\textdegree\ GFS outputs \citep[Global Forecast System,][see section \ref{sec:data}]{Kanamitsu1991,Kanamitsu1989}.
+The software first downloads the predictor describing the target situation, such as 1\textdegree\ GFS outputs \citep[Global Forecast System,][see Sect.
+\ref{sec:data}]{Kanamitsu1991,Kanamitsu1989}.
 It then interpolates linearly the gridded data to match the resolution of the archive (for example 2.5\textdegree\ in the case of the NCEP/NCAP reanalysis I).
@@
 In operational forecasting, one should take into account the uncertainty of the predictor increasing with the lead time.
-A solution, presented in section \ref{sec:optimization-operational}, consists in increasing the number of analogue situations to keep with the lead time.
+A solution, presented in Sect.
+\ref{sec:optimization-operational}, consists in increasing the number of analogue situations to keep with the lead time.
 This technique is available in AtmoSwing, as the number of analogues can be specified for every lead time, making such approach easily accessible.
@@
 The user can however choose to display a specific parameterization for the whole region, which is more consistent in terms of homogeneity of the analogue dates.
-
-\begin{figure*}[t]
-	\includegraphics[width=18cm]{figures/atmoswing-viewer.png}
-	\caption{Graphical user interface of the Viewer module (Elevation data from The Shuttle Radar Topography Mission (SRTM), and hydrological network from SwissTopo).}
-	\label{figure:atmoswing-viewer-gui}
-\end{figure*}
 
@@
 
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/atmoswing-viewer-snail.png}
-	\caption{Visualization of multiple lead times on the map (Elevation data from the SRTM, and hydrological network from SwissTopo).}
-	\label{figure:atmoswing-viewer-snail}
-\end{figure}
-
 By clicking on a station (forecast points) on the map (or by selection in a dropdown list on the left), a new window appears with a plot of the forecasted time series (Figure \ref{figure:atmoswing-viewer-timeseries}).
@@
 Traces of previous days forecasts are also automatically loaded and displayed in order to inform on the stability of the forecasts.
-
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/atmoswing-viewer-timeseries.png}
-	\caption{Visualization of the forecasted time series.}
-	\label{figure:atmoswing-viewer-timeseries}
-\end{figure}
-
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/atmoswing-viewer-distribution.png}
-	\caption{Visualization of the forecasted precipitation distribution for a given lead time.}
-	\label{figure:atmoswing-viewer-distribution}
-\end{figure}
 
@@
 
-All AMs rely on atmospheric circulation information, while some add subsequent levels of analogy on moisture or other thermodynamic predictors (see section \ref{sec:method:references}).
-However, these subsequent predictors were found to be relevant only on the first 3~days, and not much further, due to higher uncertainties in their forecast (see section \ref{sec:optimization-operational}).
+All AMs rely on atmospheric circulation information, while some add subsequent levels of analogy on moisture or other thermodynamic predictors (see Sect.
+\ref{sec:method:references}).
+However, these subsequent predictors were found to be relevant only on the first 3~days, and not much further, due to higher uncertainties in their forecast (see Sect.
+\ref{sec:optimization-operational}).
 This was found to be the case for moisture indexes and vertical velocity.
@@
 
-AtmoSwing Optimizer is a single tool that integrates different optimization methods, presented in section \ref{sec:atmoswing-calibration} to \ref{sec:atmoswing-optimization}.
-Optimization is essentially performed in the calibration framework (section \ref{sec:calibration-framework}), where one tries to maximize (by means of performance scores, see section \ref{sec:forecasts-scores}) the information that can be extracted from the available predictors and predictand archives.
+AtmoSwing Optimizer is a single tool that integrates different optimization methods, presented in Sect.
+\ref{sec:atmoswing-calibration} to \ref{sec:atmoswing-optimization}.
+Optimization is essentially performed in the calibration framework (Sect.
+\ref{sec:calibration-framework}), where one tries to maximize (by means of performance scores, see Sect.
+\ref{sec:forecasts-scores}) the information that can be extracted from the available predictors and predictand archives.
 
 However, in operational use, a further ingredient arises : the model from which the target synoptic situations are taken for the coming days, and the increasing uncertainty related to the lead time.
-Depending on the properties of these forecasts, the operational scheme has to be tuned (section \ref{sec:optimization-operational}).
+Depending on the properties of these forecasts, the operational scheme has to be tuned (Sect.
+\ref{sec:optimization-operational}).
 
@@
 Most often, the accuracy of the parameters for precipitations forecasting is evaluated by means of the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
-It is the only score that will be detailed hereafter (in section \ref{sec:prob_forecasts}).
+It is the only score that will be detailed hereafter (in Sect.
+\ref{sec:prob_forecasts}).
 In addition, other scores are implemented in AtmoSwing Optimizer.
@@
 
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/monte_carlo_r1.png}
-	\caption{Example of a Monte Carlo analysis on the PC-2Z (Table \ref{table:R1}) AM.
-Results are illustrated for the 4 parameters defining the spatial window on Z500, along with the results of the sequential calibration (red cross).}
-	\label{figure:monte_carlo_r1}
-\end{figure}
-
 The same analysis has been conducted on the AM with 2 levels of analogy, PC-2Z-2MI (Table \ref{table:R2}), and the results on the number of analogues on the 1st and the 2nd level are illustrated in Figure \ref{figure:monte_carlo_r2}.
@@
 The trend on the second level is more apparent, but a large tolerance seems possible.
-
-\begin{figure}[htbp]
-	\includegraphics[width=8.3cm]{figures/monte_carlo_r2.png}
-	\caption{Example of a Monte Carlo analysis on the PC-2Z-2MI (Table \ref{table:R2}) AM.
-Results are illustrated for the number of analogues on the 1st and 2nd level of analogy, along with the results of the sequential calibration (red cross).}
-	\label{figure:monte_carlo_r2}
-\end{figure}
 
@@
 Eventually, a meteorological variable that was proven to be a good predictor during the calibration of the AM may be poorly predicted by the forecast NWP model selected beyond a certain lead time.
-In this regards, it should be dropped after the lead time in question (see section \ref{sec:interpreting}).
+In this regards, it should be dropped after the lead time in question (see Sect.
+\ref{sec:interpreting}).
 
@@
 The optimal number of analogue situations will thus increase with the lead time, and should be optimized for every lead time on the re-forecast dataset \citep[see][for the details]{Thevenot2004}.
-This option is implemented in AtmoSwing Forecaster (see section \ref{sec:forecaster}).
+This option is implemented in AtmoSwing Forecaster (see Sect.
+\ref{sec:forecaster}).
 
@@
 	\item assessment of the relevance of an automatic interpretation of the distribution in order to provide the most likely expected value;
+\end{itemize}
+
+\section*{Code availability}
+
+AtmoSwing is open source, under the CDDL license. It is developed under the Mercurial distributed revision control, and the source code can be found at:
+
+\begin{itemize}
+	\item http://www.atmoswing.org
+	\item https://bitbucket.org/atmoswing/atmoswing
+\end{itemize}
+
+To get access to the frozen version at the time of writing (v1.4.2), the following address can be used:
+
+\begin{itemize}
+	\item bitbucket.org/atmoswing/atmoswing/commits/tag/1.4.2
 \end{itemize}
@@
 They considered the geopotential at 700 and 1000~hPa, and the thickness between these two levels, to search for analogy of circulation, and then applied a second selection on local data from radiosonde: stability indexes, precipitable water, temperature, etc.
-
-\section*{Code availability}
-
-AtmoSwing is open source, under the CDDL license. It is developed under the Mercurial distributed revision control, and the source code can be found at:
-
-\begin{itemize}
-	\item http://www.atmoswing.org
-	\item https://bitbucket.org/atmoswing/atmoswing
-\end{itemize}
-
-To get access to the frozen version at the time of writing (v1.4.2), the following address can be used:
-
-\begin{itemize}
-	\item bitbucket.org/atmoswing/atmoswing/commits/tag/1.4.2
-\end{itemize}
 
@@
 %
+
+\begin{figure}[t]
+	\includegraphics[width=8.3cm]{figures/fig01.pdf}
+	\caption{Proposed structure for naming the parameterizations of the AM.}
+	\label{figure:nomenclature}
+\end{figure}
+
+\begin{figure}[t]
+	\includegraphics[width=8.3cm]{figures/fig02.pdf}
+	\caption{The AtmoSwing logo and its 3 modules: the Forecaster, the Viewer and the Optimizer.}
+	\label{figure:logo}
+\end{figure}
+
+\begin{figure}[t]
+	\includegraphics[width=8.3cm]{figures/fig03.pdf}
+	\caption{Simplified organizational chart of the AM implementation in AtmoSwing.}
+	\label{figure:flowchart_modules_atmoswing}
+\end{figure}
+
+\begin{figure}[t]
+	\includegraphics[width=8.3cm]{figures/fig04.png}
+	\caption{Graphical user interface of the Forecaster module. A list of different parameterizations is being processed.}
+	\label{figure:atmoswing-forecaster-gui}
+\end{figure}
+
+\begin{figure*}[t]
+	\includegraphics[width=18cm]{figures/fig05.png}
+	\caption{Graphical user interface of the Viewer module (Elevation data from The Shuttle Radar Topography Mission (SRTM), and hydrological network from SwissTopo).}
+	\label{figure:atmoswing-viewer-gui}
+\end{figure*}
+
+\begin{figure}[t]
+	\includegraphics[width=8.3cm]{figures/fig06.png}
+	\caption{Visualization of multiple lead times on the map (Elevation data from the SRTM, and hydrological network from SwissTopo).}
+	\label{figure:atmoswing-viewer-snail}
+\end{figure}
+
+\begin{figure}[t]
+	\includegraphics[width=8.3cm]{figures/fig07.png}
+	\caption{Visualization of the forecasted time series.}
+	\label{figure:atmoswing-viewer-timeseries}
+\end{figure}
+
+\begin{figure}[t]
+	\includegraphics[width=8.3cm]{figures/fig08.png}
+	\caption{Visualization of the forecasted precipitation distribution for a given lead time.}
+	\label{figure:atmoswing-viewer-distribution}
+\end{figure}
+
+\begin{figure}[t]
+	\includegraphics[width=8.3cm]{figures/fig09.png}
+	\caption{Example of a Monte Carlo analysis on the PC-2Z (Table \ref{table:R1}) AM.
+Results are illustrated for the 4 parameters defining the spatial window on Z500, along with the results of the sequential calibration (red cross).}
+	\label{figure:monte_carlo_r1}
+\end{figure}
+
+\begin{figure}[t]
+	\includegraphics[width=8.3cm]{figures/fig10.png}
+	\caption{Example of a Monte Carlo analysis on the PC-2Z-2MI (Table \ref{table:R2}) AM.
+Results are illustrated for the number of analogues on the 1st and 2nd level of analogy, along with the results of the sequential calibration (red cross).}
+	\label{figure:monte_carlo_r2}
+\end{figure}
+
 %
@@
 %
+
+\begin{table}[t]
+	\caption{Method of type PC-2Z proposed by \citet{Bontron2004}.
+The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window).
+The criteria used for the current level of analogy is then provided, as well as the number of analogues.}
+	\begin{tabular}{ccccc}
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline 
+		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+		\middlehline 
+		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
+		& Z500 & 24~h & & \\ 
+		\bottomhline 
+	\end{tabular} 
+	\label{table:R1}
+\end{table}
+
+\begin{table}[t]
+	\caption{Method of type PC-4Z proposed by \citet{Horton2012}. Same conventions as Table \ref{table:R1}}
+	\begin{tabular}{ccccc}
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline 
+		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+		\middlehline 
+		\multirow{4}{*}{1} & Z1000 & 12~h & \multirow{4}{*}{S1} & \multirow{4}{*}{$N_{1}$} \\
+		& Z850 & 24~h & & \\ 
+		& Z700 & 12~h & & \\ 
+		& Z500 & 24~h & & \\ 
+		\bottomhline 
+	\end{tabular}
+	\label{table:R6}
+\end{table}
+
+\begin{table}[t]
+	\caption{Method of type PC-2Z-2MI proposed by \citet{Bontron2004}. Same conventions as Table \ref{table:R1}}
+	\begin{tabular}{ccccc}
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline 
+		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+		\middlehline 
+		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
+		& Z500 & 24~h & & \\ 
+		\middlehline
+		2 & TPW * RH850 & 12, 24~h & RMSE & 30 \\
+		\bottomhline 
+	\end{tabular} 
+	\label{table:R2}
+\end{table}
+
+\begin{table}[t]
+	\caption{Method of type PC-2Z-2MI proposed by \citet{Marty2010}. Same conventions as Table \ref{table:R1}}
+	\begin{tabular}{ccccc}
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline 
+		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+		\middlehline 
+		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{75} \\
+		& Z500 & 18~h & & \\ 
+		\middlehline
+		2 & TPW * RH925 & 06, 18~h & RMSE & 30 \\
+		\bottomhline 
+	\end{tabular} 
+	\label{table:R3a}
+\end{table}
+
+\begin{table}[t]
+	\caption{Method of type PC-2Z-2MF proposed by \citet{Marty2010}. Same conventions as Table \ref{table:R1}}
+	\begin{tabular}{ccccc}
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline 
+		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+		\middlehline 
+		\multirow{2}{*}{1} & Z1000 & 06~h & \multirow{2}{*}{S1} & \multirow{2}{*}{60} \\
+		& Z500 & 18~h & & \\ 
+		\middlehline
+		2 & V700 * TPW * RH700 $^{\dagger}$ & 06, 18~h & RMSE & 25 \\
+		\bottomhline 
+	\end{tabular} 
+	\belowtable{$\dagger$ or V925 * TPW * RH925 as an alternative}
+	\label{table:R3b}
+\end{table}
+
+\begin{table}[t]
+	\caption{Method of type P2T-2Z-4MI (or P2T-2Z-10MI for the alternative version), by \citet{BenDaoud2010}. Same conventions as Table \ref{table:R1}}
+	\begin{tabular}{ccccc}
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline
+		\multirow{2}{*}{0} & T925 & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
+		& T600 & 12~h & & \\ 
+		\middlehline 
+		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
+		& Z500 & 24~h & & \\ 
+		\middlehline
+		\multirow{2}{*}{2} & TPW * RH925 & 12, 24~h $^{\dagger}$ & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
+		& TPW * RH700 & 12, 24~h $^{\dagger}$ & & \\ 
+		\bottomhline 
+	\end{tabular} 
+	\belowtable{$\dagger$ or 06-30~h as an alternative}
+	\label{table:R4b}
+\end{table}
+
+\begin{table}[t]
+	\caption{Method of type P2T-2Z-4W-4MI, by \citet{BenDaoud2010}. Same conventions as Table \ref{table:R1}}
+	\begin{tabular}{ccccc}
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline
+		\multirow{2}{*}{0} & T925 (1 point) & 36~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{0}$} \\
+		& T600 (1 point) & 12~h & & \\ 
+		\middlehline 
+		\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{170} \\
+		& Z500 & 24~h & & \\ 
+		\middlehline
+		2 & W850 & 06-24~h & RMSE & 70 \\
+		\middlehline
+		\multirow{2}{*}{3} & TPW * RH925 & 12, 24~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{25} \\
+		& TPW * RH700 & 12, 24~h & & \\
+		\bottomhline 
+	\end{tabular}
+	\label{table:R5}
+\end{table}
+
+\begin{table}[t]
+	\caption{Method of type PC-4Z-2MI, by \citet{Horton2012}. Same conventions as Table \ref{table:R1}}
+	\begin{tabular}{ccccc}
+		\tophline
+		\textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
+		\middlehline 
+		0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+		\middlehline 
+		\multirow{4}{*}{1} & Z1000 & 12~h & \multirow{4}{*}{S1} & \multirow{4}{*}{$N_{1}$} \\
+		& Z850 & 24~h & & \\ 
+		& Z700 & 12~h & & \\ 
+		& Z500 & 24~h & & \\ 
+		\middlehline
+		2 & V700 * TPW * RH700 & 12, 24~h & RMSE & $N_{2}$ \\
+		\bottomhline 
+	\end{tabular}
+	\label{table:R7}
+\end{table}
+
 %
@@
 %
-%
-%%% CHEMICAL FORMULAS AND REACTIONS
-%
-%%% For formulas embedded in the text, please use \chem{}
-%
-%%% The reaction environment creates labels including the letter R, i.e. (R1), (R2), etc.
-%
-%\begin{reaction}
-%%% \rightarrow should be used for normal (one-way) chemical reactions
-%%% \rightleftharpoons should be used for equilibria
-%%% \leftrightarrow should be used for resonance structures
-%\end{reaction}
-%
-%
-%%% PHYSICAL UNITS
-%%%
-%%% Please use \unit{} and apply the exponential notation
 

### 2016-02-05 AtmoSwing - Geoscientific Model Development/template.tex
Preparing for submission.

@@
 
-The Optimizer integrates the common semi-automatic sequential approach, as well as Monte-Carlo analyses, and a global optimization technique by means of Genetic algorithms.
+The Optimizer integrates the common semi-automatic sequential approach, as well as Monte\textendash Carlo analyses, and a global optimization technique by means of Genetic algorithms.
 
@@
 Variants of the AM parameterization are numerous and it is not always easy to reference them in a short and descriptive way.
-We thus propose a basic nomenclature (Figure \ref{figure:nomenclature}) in order to express the structure into a simple identifier.
+We thus propose a basic nomenclature (Fig.
+\ref{figure:nomenclature}) in order to express the structure into a simple identifier.
 This one cannot describe all the parameters of the AM, but quickly illustrate the structure of the implementation.
@@
 It was found to be important to compute the analogy on multiple pressure levels and different temporal windows \citep{Guilbaud1998, Obled2002}.
-The Teweles-Wobus (S1) criterion (Eq.
+The Teweles\textendash Wobus (S1) criterion (Eq.
 \ref{eq:S1}), which allows for a comparison of the gradients and thus an analogy of the atmospheric circulation, was identified as the most suited criteria by different studies \citep{Wilson1980, Woodcock1980, Guilbaud1998, Bontron2004}.
@@
 
-AtmoSwing is made of 3 main modules (Figure \ref{figure:logo}) that are standalone, but do share a common code basis: the Forecaster, to process the operational forecasting, the Viewer, to display the forecast in a GIS environment, and the Optimizer, to calibrate/optimize the statistical relationship defining the analogy for a given predictand time series.
+AtmoSwing is made of 3 main modules (Fig.
+\ref{figure:logo}) that are standalone, but do share a common code basis: the Forecaster, to process the operational forecasting, the Viewer, to display the forecast in a GIS environment, and the Optimizer, to calibrate/optimize the statistical relationship defining the analogy for a given predictand time series.
 Separating the Forecaster and the Viewer allows to automate the forecast on a server and to quickly display the results locally.
@@
 Every analogy criterion, prediction score, searching and sorting functions, data manipulation, and so on, is tested.
-The integration tests specific to the AM rely on the results of another analogue sorting software developed at the LTHE - INPG university of Grenoble.
+The integration tests specific to the AM rely on the results of another analogue sorting software developed at the LTHE \textendash INPG university of Grenoble.
 They ensure that the results of AtmoSwing are exactly equivalent to their model, given the same parameters and data.
@@
 An AtmoSwing great strength is that it is designed to process analogy forecasting in a modular fashion.
-The structure of the AM (number of analogy levels, number of predictors) is built dynamically (Figure \ref{figure:flowchart_modules_atmoswing}), and nothing is fixed a priori.
+The structure of the AM (number of analogy levels, number of predictors) is built dynamically (Fig.
+\ref{figure:flowchart_modules_atmoswing}), and nothing is fixed a priori.
 The software then performs successively as many analogy levels as the user specified, with all the predictors he wants.
@@
 A list of parameterizations is processed successively.
-The software can be compiled with a GUI (graphical user interface, Figure \ref{figure:atmoswing-forecaster-gui}), or without in order to be used on a headless server through a command line interface.
+The software can be compiled with a GUI (graphical user interface, Fig.
+\ref{figure:atmoswing-forecaster-gui}), or without in order to be used on a headless server through a command line interface.
 Processing a forecast requires very low computing capabilities and can be done on a low-end computer.
@@
 
-The Viewer module allows displaying the resulting forecast files in an interactive GIS environment (Figure \ref{figure:atmoswing-viewer-gui}).
+The Viewer module allows displaying the resulting forecast files in an interactive GIS environment (Fig.
+\ref{figure:atmoswing-viewer-gui}).
 During the forecast, different parametrization variants of the same type of AM may be applied to a region; the reason being that some parameterizations may be specific for a subregion, when its meteorological influences differ, which is often the case even in relatively small catchments \citep{Horton2012}.
@@
 When it is opened, it automatically loads the most recent forecasts, eliminating the need to manually open files.
-It first offers a quick overview of possible alerts by means of color codes on the lead time switcher (upper right in the graphical user interface (GUI), see Figure \ref{figure:atmoswing-viewer-gui}), which synthesizes the worst case scenario, or in the alarms panel (on the left part of the GUI).
+It first offers a quick overview of possible alerts by means of color codes on the lead time switcher (upper right in the graphical user interface (GUI), see Fig.
+\ref{figure:atmoswing-viewer-gui}), which synthesizes the worst case scenario, or in the alarms panel (on the left part of the GUI).
 The alarms panel offers a synthesis of the higher forecasted values over the region, for the different AMs and the different lead times.
-By default, the colors are expressed relatively to 10-year return period values, for the $90^{th}$ percentile (can be changed in the preferences).
+By default, the colors are expressed relatively to 10~year return period values, for the $90^{th}$ percentile (can be changed in the preferences).
 This higher level of synthesis allows to quickly identify potential critical situations in the days ahead.
 
-Then, the user can explore the forecasts more in details, starting from the map provided by the GUI (Figure \ref{figure:atmoswing-viewer-gui}).
+Then, the user can explore the forecasts more in details, starting from the map provided by the GUI (Fig.
+\ref{figure:atmoswing-viewer-gui}).
 The map display the forecast of the selected parameterization (upper left) and the selected lead time (upper right).
 The displayed AM is by default a composite of the parameterization variants for the region, but the user can choose a specific parameterization for the whole region by opening the tree view and selecting a child element.
-We also allowed a display of all lead times on a single map by means of a symbolic representation on a circular band with a box for every lead time (Figure \ref{figure:atmoswing-viewer-snail}).
+We also allowed a display of all lead times on a single map by means of a symbolic representation on a circular band with a box for every lead time (Fig.
+\ref{figure:atmoswing-viewer-snail}).
 The number of boxes is dynamically adjusted to the number of lead times.
@@
 
-By clicking on a station (forecast points) on the map (or by selection in a dropdown list on the left), a new window appears with a plot of the forecasted time series (Figure \ref{figure:atmoswing-viewer-timeseries}).
-By default, the plot contains the usual 3 considered percentiles (90$^{th}$, 60$^{th}$, and 20$^{th}$), along with the 10 best analogues with a color code from yellow (10$^{th}$) to red (1$^{st}$).
+By clicking on a station (forecast points) on the map (or by selection in a dropdown list on the left), a new window appears with a plot of the forecasted time series (Fig.
+\ref{figure:atmoswing-viewer-timeseries}).
+By default, the plot contains the usual 3 considered percentiles (90$^{th}$, 60$^{th}$, and 20$^{th}$), along with the 10 best analogues with a color code from yellow (tenth) to red (first).
 The 10 year return period is also displayed in order to put the forecast in perspective.
@@
 
-The user can even go into further details and display the predictand cumulative distribution for a given lead time (Figure \ref{figure:atmoswing-viewer-distribution}).
+The user can even go into further details and display the predictand cumulative distribution for a given lead time (Fig.
+\ref{figure:atmoswing-viewer-distribution}).
 This is useful when working on extreme precipitation, as comparing the distribution of all analogues versus the 10 best analogues provides information in order to interpret the forecast (trend to under/overestimation).
@@
 It is therefore necessary to pay particular attention to the 90$^{th}$ percentile which, when reaching high values, may be indicative of a situation related to extreme precipitations, due the presence of several analogue dates with significant observed precipitations amounts in the distribution \citep{Djerboua2001}.
-\citet{Bontron2004} made the same observation: he found the 60$^{th}$ percentile to be best for occurrence forecasting, but the 90$^{th}$ percentile to be the most informative in order to forecast medium to high precipitation amounts ($P > P10/10$, one tenth of the 10-year return period value).
+\citet{Bontron2004} made the same observation: he found the 60$^{th}$ percentile to be best for occurrence forecasting, but the 90$^{th}$ percentile to be the most informative in order to forecast medium to high precipitation amounts ($P > P10/10$, one tenth of the 10~year return period value).
 In this regard, operators should pay particular attention to the distribution of the best analogues.
@@
 \citet{Marty2010} applied several validation scores to the quantiles of the AM distribution in operational forecasting.
-He concluded that the detection of the precipitation occurrence was better predicted by median quantiles (50-70~\%), with an optimum to 60~\%.
+He concluded that the detection of the precipitation occurrence was better predicted by median quantiles (50\textendash 70~\%), with an optimum to 60~\%.
 However, once again, for significant rainfall, the 90$^{th}$ percentile gave the best performance.
@@
 The calibration procedure that we call ''sequential'' or ''classic'', but which is also named ''optimization'' \cite[eg.
-by ][]{BenDaoud2015}, was developed at LTHE - INPG university of Grenoble \citep{Bontron2004}.
+by ][]{BenDaoud2015}, was developed at LTHE \textendash INPG university of Grenoble \citep{Bontron2004}.
 It is a semi-automatic procedure that determines the optimal parameters for the different variables of each level of analogy.
@@
 		\item pressure level (e.g. 700 hPa, ...),
-		\item temporal window (hour of observation - e.g. 6, or 12~h~UTC),
+		\item temporal window (hour of observation \textendash e.g. 6, or 12~h~UTC),
 		\item initial analogue numbers (e.g. $N_{1}=50$).
@@
 
-\subsection{Monte-Carlo analysis}
-
-A Monte-Carlo analysis is also implemented in AtmoSwing.
+\subsection{Monte\textendash Carlo analysis}
+
+A Monte\textendash Carlo analysis is also implemented in AtmoSwing.
 It performs thousands assessments of random parameters within given ranges.
@@
 
-For example, a Monte-Carlo analysis was performed on the PC-2Z (Table \ref{table:R1}) AM for the southeastern crests on the upper Rh\^{o}ne catchment in Switzerland, with 10,000 random selections of its parameters according to a uniform law (the analysis was also performed in other subregions of the upper Rh\^{o}ne catchment in Switzerland, but the conclusions depicted here are similar).
+For example, a Monte\textendash Carlo analysis was performed on the PC-2Z (Table \ref{table:R1}) AM for the southeastern crests on the upper Rh\^{o}ne catchment in Switzerland, with 10,000 random selections of its parameters according to a uniform law (the analysis was also performed in other subregions of the upper Rh\^{o}ne catchment in Switzerland, but the conclusions depicted here are similar).
 Unlike conventional calibration, the spatial windows on Z500 and Z1000 were not necessarily overlapping.
@@
 
-The shape of the scatter plots from Figure \ref{figure:monte_carlo_r1} reveals a low sensitivity as to the exact location of the spatial windows.
+The shape of the scatter plots from Fig.
+\ref{figure:monte_carlo_r1} reveals a low sensitivity as to the exact location of the spatial windows.
 There is a maximum threshold for minimum longitudes and latitudes and, inversely, a minimum threshold for maximum latitudes and longitudes, but outside of these limits, the distribution slope is more gentle.
@@
 
-The same analysis has been conducted on the AM with 2 levels of analogy, PC-2Z-2MI (Table \ref{table:R2}), and the results on the number of analogues on the 1st and the 2nd level are illustrated in Figure \ref{figure:monte_carlo_r2}.
+The same analysis has been conducted on the AM with 2 levels of analogy, PC-2Z-2MI (Table \ref{table:R2}), and the results on the number of analogues on the first and the second level are illustrated in Fig.
+\ref{figure:monte_carlo_r2}.
 One can see that the AM is not very sensitive to the number of analogues on the first level of analogy, when considering a second level afterwards, as long as this number is not too small.
@@
 The Viewer offers a user-friendly display of the forecasts, with different levels of synthesis and details.
-The Optimizer implements different optimization techniques, such as the sequential approach, a Monte-Carlo method, and a global optimization technique.
+The Optimizer implements different optimization techniques, such as the sequential approach, a Monte\textendash Carlo method, and a global optimization technique.
 Obviously, it is used only occasionally for a given location: for a first implementation of an AM, in case of a change in the archive, or of a substantial updating, etc.
@@
 
-\citet{Wilson1980} sought the 20 best analogues on the geopotential field at 500 and 1000~hPa using the Teweles-Wobus (S1) criterion (Eq.
+\citet{Wilson1980} sought the 20 best analogues on the geopotential field at 500 and 1000~hPa using the Teweles\textendash Wobus (S1) criterion (Eq.
 \ref{eq:S1}), which allows for a comparison of the gradients and thus an analogy of the atmospheric circulation.
@@
 	\includegraphics[width=8.3cm]{figures/fig09.png}
-	\caption{Example of a Monte Carlo analysis on the PC-2Z (Table \ref{table:R1}) AM.
+	\caption{Example of a Monte\textendash Carlo analysis on the PC-2Z (Table \ref{table:R1}) AM.
 Results are illustrated for the 4 parameters defining the spatial window on Z500, along with the results of the sequential calibration (red cross).}
@@
 	\includegraphics[width=8.3cm]{figures/fig10.png}
-	\caption{Example of a Monte Carlo analysis on the PC-2Z-2MI (Table \ref{table:R2}) AM.
-Results are illustrated for the number of analogues on the 1st and 2nd level of analogy, along with the results of the sequential calibration (red cross).}
+	\caption{Example of a Monte\textendash Carlo analysis on the PC-2Z-2MI (Table \ref{table:R2}) AM.
+Results are illustrated for the number of analogues on the first and second level of analogy, along with the results of the sequential calibration (red cross).}
 	\label{figure:monte_carlo_r2}
 \end{figure}
+
+\clearpage
 
@@
 \end{table}
+
+\clearpage
 
@@
 
+\clearpage
+
 \begin{table}[t]

### 2016-02-05 AtmoSwing - Geoscientific Model Development/template.tex
Personal corrections.

@@
 
-The Optimizer integrates the common semi-automatic sequential approach, as well as Monte\textendash Carlo analyses, and a global optimization technique by means of Genetic algorithms.
+The Optimizer integrates the common semi-automatic sequential approach, as well as Monte\textendash Carlo analyses, and a global optimization technique by means of Genetic Algorithms.
 
@@
 
-The AM, or an equivalent, was also used for short to medium term forecasting of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+In addition to precipitation forecasting, the Analogue Method (AM), or an equivalent, was also used for short to medium term forecasting of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
 \citet{Guilbaud1997} performed a literature review about the use of the AM in long-term forecasting and identified operational applications for monthly forecasts in many countries, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal forecasts: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
 
-The purpose of this paper is not to argue in favour or against this approach, which has proved to be used efficiently either in operational forecasting \citep{Djerboua2001} or more recently in climate studies \citep{Dayon2015}.
-\citet{Bliefernicht2010} compared the performance of the AM with a forecasting method based on a weather types approach, and concluded that the AM was more efficient.
-
 In operational forecasting, it has been used mainly by practitioners, notably hydropower companies \citep{Desaint2008a,BenDaoud2009,Obled2014} or flood forecasting services in France and Switzerland \citep{Marty2010,GarciaHernandez2009b,Horton2012}.
-It should however not be considered as a substitute for numerical weather prediction models, but as a complement in order to get a fast and partly independent forecast that is known to be accurate several days in advance.
+It should however not be considered as a substitute for Numerical Weather Prediction (NWP) models, but as a complement in order to get a fast and partly independent forecast that is known to be accurate several days in advance.
 It therefore enriches the analysis of a potential critical situation for flood forecasting, for example, and is very interesting in early warning.
@@
 
-The Analogue Method (AM) will first be presented along with various implementations (Sect.
-\ref{sec:method}), as the optimal version of the method may vary with the location of interest, and as all these can be processed with AtmoSwing.
+The AM will first be presented along with various implementations (Sect.
+\ref{sec:method}), as all these can be processed with AtmoSwing.
 The software will then be presented (Sect.
@@
 \ref{sec:viewer}) that are tools for operational use, and the Optimizer (Sect.
-\ref{sec:optimizer}) that allows optimizing the method for a given predictand time series.
+\ref{sec:optimizer}) that allows optimizing the method for a given predictand time series, may it be for operational forecasting or climate impact studies.
 
@@
 Thus, several examples of possible implementations are gathered here, as well as the main evolution steps of the AM.
-This latter summarizes the improvements that were brought, as well as discontinued approaches that were found less relevant.
 
@@
 	\item The analogy variable (the predictor) must contain synoptic information having indirect dependency with the local weather and the target predictand (often the precipitation).
+	\item The pressure level, or height, at which the analogy variable is considered.
 	\item The spatial window is the domain on which the analogy variable is considered. The ideal size of this area is the one that maximizes useful information.
-	\item The temporal window is the hour, or a set of different hours, in the day at which the analogy variables are considered.
+	\item The temporal window is the hour in the day, or a set of different hours, at which the analogy variables are considered.
 	\item The preselection, which is often a period of the year in which similar situations are being sought.
@@
 Numerical models being more capable of simulating the dynamic evolution of the atmosphere, the temporal extrapolation of the synoptic variables is left to them.
-The search for analogy aims thus at connecting the forecasted synoptic situation with a local predictand (temperature, precipitation ...), which is more difficult to simulate by numerical models.
+The search for analogy aims thus at connecting the forecasted synoptic situation with a local predictand (temperature, precipitation, etc), which is more difficult to simulate by numerical models.
 
@@
 This normalization allows for an easier comparison between subregions subject to different precipitation regimes, and thus to better identify the most important contributions.
-Most users also apply a root square to this last ratio in order to reduce the weight of the extreme predictand values, but we generally don't, in order to give extremes a certain weighting.
 
@@
 Although multiple variations of the AM exist, they generally share the same basics and the same structure.
-For example, let's say we want here to forecast the daily precipitation (the predictand) for a target day (at a defined lead time) and have long archives of both the predictand and predictor variables.
-The generic structure, illustrated for precipitation forecasting, is the following:
+For example, let's say we want here to forecast the daily precipitation for a target day, at a defined lead time.
+The generic structure is the following:
 
@@
 
-	\item Subsequent level(s) of analogy: beyond the similarity of airflows, one may look for similarities in other variables of interest .
+	\item Subsequent level(s) of analogy: beyond the similarity of airflows, one may look for similarities in other variables of interest, such as moisture variables.
 Therefore, the $N_{1}$ analogues are subsampled once again on the basis of another variable in order to obtain a lower number of analogue dates, $N_{2}$.
 The S1 criterion is usually not relevant for other predictors that the atmospheric circulation.
-Other classic criteria represent absolute distances: Mean Absolute Error (MAE) and Root Mean Squared Error (RMSE), the latest being most often used.
-These are more relevant to compare moisture variables for example.
-
-	This process can be repeated, by subsampling a decreasing number of analogues, $N_{i}$, according to a ranking processed on various meteorological variables.
+Classic criteria represent absolute distances: Mean Absolute Error (MAE) and Root Mean Squared Error (RMSE), the latest being most often used.
+
+	This process can be repeated, by subsampling a decreasing number of analogues, $N_{i}$, according to various meteorological variables.
 
@@
 daily) observed precipitation amount (or another predictand of interest) of the $N_{i}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
-The empirical frequencies are processed for every value of the predictand, after classification, based on the Gringorten parameters \cite[for a Gumbel or exponential law][]{Gringorten1963} and a probabilistic model can be fitted \citep[e.g.
-Gamma function][]{Obled2002}.
-The forcast is often synthetized by the percentiles 20, 60 and 90~\% \citep{Guilbaud1997, Guilbaud1998}.
+The empirical frequencies are processed for every value of the predictand, after classification, based on the Gringorten parameters \cite[for a Gumbel or exponential law; see][]{Gringorten1963} and a probabilistic model can be fitted \citep[e.g.
+Gamma function,][]{Obled2002}.
+The forcast is finally often synthetized by the percentiles 20, 60 and 90~\% \citep{Guilbaud1997, Guilbaud1998}.
 
@@
 
-Some examples of parameterizations of the most used or the most recent AM variants are provided hereunder.
+Some examples of parameterization of the most used or the most recent AM variants are provided hereunder.
 Some of these are more specific for a certain region and may not be relevant for others, and some perform better depending on the lead time.
@@
 The Teweles\textendash Wobus (S1) criterion (Eq.
-\ref{eq:S1}), which allows for a comparison of the gradients and thus an analogy of the atmospheric circulation, was identified as the most suited criteria by different studies \citep{Wilson1980, Woodcock1980, Guilbaud1998, Bontron2004}.
+\ref{eq:S1}), which allows for a comparison of the gradients, and thus an analogy of the atmospheric circulation, was identified as the most suited criteria by different studies \citep{Wilson1980, Woodcock1980, Guilbaud1998, Bontron2004}.
 
 With a systematic assessment of the newly available NCEP/NCAR reanalysis data, \citet{Bontron2004} concluded that the coupled geopotential heights at 1000~hPa (Z1000) \& 12~h and 500~hPa (Z500) \& 24~h provided the best performance for the studied region (Table \ref{table:R1}).
-The analogy on the atmospheric circulation proposed by \citet{Bontron2004} is still, at the time of writing, often used operationally, and considered as a reference for benchmarking new parameterizations \citep{Horton2012, BenDaoud2015}.
+The analogy on the atmospheric circulation proposed by \citet{Bontron2004} is still, at the time of writing, often used operationally, and considered as a reference for benchmarking new parameterizations \citep[see e.g.][]{Horton2012, BenDaoud2015}.
 In order to assess the forecast, he introduced the Continuous Ranked Probability Score \citep[CRPS, Eq.
@@
 
-A second level of analogy based on thermodynamic variables was then introduced by \citet{Mandon1985, Vallee1986, Gibergans-Baguena2007}.
+A second level of analogy based on thermodynamic variables was then introduced by \citet{Mandon1985}, \citet{Vallee1986}, and \citet{Gibergans-Baguena2007}.
 After a systematic assessment, \citet{Bontron2004} pointed out that a moisture index (MI) made of the product of relative humidity at 850~hPa (RH850) and total precipitable water (TPW) gave the best performance (Table \ref{table:R2}).
@@
 The selected hours and atmospheric levels were not available before in the reanalysis dataset.
-
 Then, \citet{Marty2010} changed the moisture index into the moisture flux by adding the wind velocity (V700 or V925) component in the multiplication.
 He considered this flux at 700~hPa or 925~hPa (Table \ref{table:R3b}).
+
+\citet{Horton2012} also integrated an analogy on the moisture flux, after the circulation analogy on the 4 atmospheric levels (Table \ref{table:R7}).
+The number of analogues ($N_{1}$, $N_{2}$) were calibrated for every subregion.
+Similarly, an equivalent structure was optimized \citep[PC-4Zgo-2MIgo,][]{Horton2016b}.
 
@@
 
-\citet{Horton2012} also integrated an analogy on the moisture flux, after the circulation analogy on the 4 atmospheric levels (Table \ref{table:R7}).
-The number of analogues ($N_{1}$, $N_{2}$) were calibrated for every subregion.
-Similarly, an equivalent structure was optimized \citep[PC-4Zgo-2MIgo,][]{Horton2016b}.
-
 The optimal predictors vary from one region to another, along with the leading atmospheric processes.
@@
 Its use as adaptation method of climate models is also the subject of a growing number of studies \citep{Zorita1999, Wetterhall2005, Wetterhall2007, Matulla2007, Chardon2014, Dayon2015}.
+\citet{Bliefernicht2010} obtained better results witht the AM than downscaling methods based on weather typing.
 

### 2016-02-07 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Preparing for submission.

@@
-\documentclass[5p]{elsarticle}
-%\documentclass[review]{elsarticle}
+%\documentclass[5p]{elsarticle}
+\documentclass[review]{elsarticle}
 
@@
 \usepackage{subcaption}
-%\usepackage{amsmath}
 
@@
 \begin{keyword}
-Precipitation forecast\sep
+Precipitation prediction\sep
 Precipitation downscaling\sep
@@
 
-Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
+Thanks to the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton, the Water, Land and Sanitation Service of the Vaud Canton and the Swiss Federal Office for Environment (FOEV) who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
 The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=\linewidth]{figures/figure_map.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/figure_map.pdf}}
 	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland. (source: Swisstopo)}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrpss_4Zo.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/figure_dcrpss_4Zo.pdf}}
 	\caption{CRPSS relative improvement of 4Zo compared to the reference methods 2Z (Table \ref{table:params_R1}) for the CP and the VP.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrps_comp_4Zo.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/figure_dcrps_comp_4Zo.pdf}}
 	\caption{Changes in the CRPS components of 4Zo relatively to the total CRPS of the reference methods 2Z (Table \ref{table:params_R1}) for the CP and the VP.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8cm]{figures/table_crossing_z4_calib.pdf}}
+	\centerline{\includegraphics[width=8.4cm]{figures/table_crossing_z4_calib.pdf}}
 	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo, calibration period.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8cm]{figures/table_crossing_z4_valid.pdf}}
+	\centerline{\includegraphics[width=8.4cm]{figures/table_crossing_z4_valid.pdf}}
 	\caption{Same as Figure \ref{fig:crossing_4Zo_calib} but for the validation period.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrpss_4Zo-2HIo.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/figure_dcrpss_4Zo-2HIo.pdf}}
 	\caption{CRPSS relative improvement of 4Zo-2MIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrpss_4Zo-4HIo.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/figure_dcrpss_4Zo-4HIo.pdf}}
 	\caption{CRPSS relative improvement of 4Zo-4MIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=\linewidth]{figures/figure_dcrps_comp_4Zo-2HIo.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/figure_dcrps_comp_4Zo-2HIo.pdf}}
 	\caption{Changes in the CRPS components of 4Zo-2MIo relatively to the total CRPS of the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=\linewidth]{figures/figure_nb_analogues.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/figure_nb_analogues.pdf}}
 	\caption{Number of analogues for the different regions and the various methods resulting from the optimization.
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=\linewidth]{figures/figure_nb_analogues_relationships.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/figure_nb_analogues_relationships.pdf}}
 	\caption{Relationships between the optimal number of analogues for both levels of the 4Zo-2MIo method and the corresponding ones for the unique level of the 4Zo method.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8cm]{figures/table_crossing_z4-hi2_calib.pdf}}
+	\centerline{\includegraphics[width=8.4cm]{figures/table_crossing_z4-hi2_calib.pdf}}
 	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo-2MIo, calibration period.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8cm]{figures/table_crossing_z4-hi2_valid.pdf}}
+	\centerline{\includegraphics[width=8.4cm]{figures/table_crossing_z4-hi2_valid.pdf}}
 	\caption{Same as Figure \ref{fig:crossing_4Zo-2MIo_calib} but for the validation period.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=\linewidth]{figures/figure_levels_weights.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/figure_levels_weights.pdf}}
 	\caption{Optimized weighting for the pressure levels of the 4Zo method.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=\linewidth]{figures/figure_levels_weights_average.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/figure_levels_weights_average.pdf}}
 	\caption{Averaged weighting for the pressure levels of the circulation analogy of the three methods.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=\linewidth]{figures/figure_evolution.pdf}}
+	\centerline{\includegraphics[width=7.5cm]{figures/figure_evolution.pdf}}
 	\caption{Example of the evolution of the performance score of the best individual over 8 independent optimizations.}

### 2016-02-07 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Merging images of the spatial windows.

@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 	\centerline{\includegraphics[width=8.8cm]{figures/figure_map.pdf}}
@@
 
-\begin{figure}[htb]
-	\centering
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_1.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_2.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_3.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_4.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_5.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_6.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_7.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_8.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_9.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/Spatial_windows_10.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4/legend.png}
-	\end{subfigure}
+\begin{figure}[t]
+	\centerline{\includegraphics[width=8.4cm]{figures/figure_spatial_win_z4.pdf}}
 	\caption{Optimized spatial windows for the 4Zo method (analogy of atmospheric circulation on 4 pressure levels).
@@
 \begin{figure}[htb]
-	\centering
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_1.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_2.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_3.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_4.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_5.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_6.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_7.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_8.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_9.png}
-	\end{subfigure}%
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/Spatial_windows_10.png}
-	\end{subfigure}
-	\begin{subfigure}{.5\columnwidth}
-		\centering
-		\includegraphics[width=4.2cm]{figures/spatial_win_z4-hi2/legend.png}
-	\end{subfigure}
+	\centerline{\includegraphics[width=8.8cm]{figures/figure_spatial_win_z4-hi2.pdf}}
 	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 2 pressure levels).

### 2016-02-07 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Renaming figures.

@@
 \usepackage{gensymb}
-\usepackage{subcaption}
 
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/figure_map.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig01.pdf}}
 	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland. (source: Swisstopo)}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.4cm]{figures/figure_spatial_win_z4.pdf}}
+	\centerline{\includegraphics[width=8.4cm]{figures/fig02.pdf}}
 	\caption{Optimized spatial windows for the 4Zo method (analogy of atmospheric circulation on 4 pressure levels).
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.8cm]{figures/figure_dcrpss_4Zo.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig03.pdf}}
 	\caption{CRPSS relative improvement of 4Zo compared to the reference methods 2Z (Table \ref{table:params_R1}) for the CP and the VP.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.8cm]{figures/figure_dcrps_comp_4Zo.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig04.pdf}}
 	\caption{Changes in the CRPS components of 4Zo relatively to the total CRPS of the reference methods 2Z (Table \ref{table:params_R1}) for the CP and the VP.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.4cm]{figures/table_crossing_z4_calib.pdf}}
+	\centerline{\includegraphics[width=8.4cm]{figures/fig05.pdf}}
 	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo, calibration period.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.4cm]{figures/table_crossing_z4_valid.pdf}}
+	\centerline{\includegraphics[width=8.4cm]{figures/fig06.pdf}}
 	\caption{Same as Figure \ref{fig:crossing_4Zo_calib} but for the validation period.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.8cm]{figures/figure_spatial_win_z4-hi2.pdf}}
+	\centerline{\includegraphics[width=8.4cm]{figures/fig07.pdf}}
 	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 2 pressure levels).
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.8cm]{figures/figure_dcrpss_4Zo-2HIo.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig08.pdf}}
 	\caption{CRPSS relative improvement of 4Zo-2MIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.8cm]{figures/figure_dcrpss_4Zo-4HIo.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig09.pdf}}
 	\caption{CRPSS relative improvement of 4Zo-4MIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.8cm]{figures/figure_dcrps_comp_4Zo-2HIo.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig10.pdf}}
 	\caption{Changes in the CRPS components of 4Zo-2MIo relatively to the total CRPS of the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.8cm]{figures/figure_nb_analogues.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig11.pdf}}
 	\caption{Number of analogues for the different regions and the various methods resulting from the optimization.
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.8cm]{figures/figure_nb_analogues_relationships.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig12.pdf}}
 	\caption{Relationships between the optimal number of analogues for both levels of the 4Zo-2MIo method and the corresponding ones for the unique level of the 4Zo method.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.4cm]{figures/table_crossing_z4-hi2_calib.pdf}}
+	\centerline{\includegraphics[width=8.4cm]{figures/fig13.pdf}}
 	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo-2MIo, calibration period.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.4cm]{figures/table_crossing_z4-hi2_valid.pdf}}
+	\centerline{\includegraphics[width=8.4cm]{figures/fig14.pdf}}
 	\caption{Same as Figure \ref{fig:crossing_4Zo-2MIo_calib} but for the validation period.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.8cm]{figures/figure_levels_weights.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig15.pdf}}
 	\caption{Optimized weighting for the pressure levels of the 4Zo method.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=8.8cm]{figures/figure_levels_weights_average.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig16.pdf}}
 	\caption{Averaged weighting for the pressure levels of the circulation analogy of the three methods.}
@@
 \begin{figure}[htb]
-	\centerline{\includegraphics[width=7.5cm]{figures/figure_evolution.pdf}}
+	\centerline{\includegraphics[width=7.5cm]{figures/fig17.pdf}}
 	\caption{Example of the evolution of the performance score of the best individual over 8 independent optimizations.}

### 2016-02-08 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Moving tables at the end of the document.
Personal corrections.

@@
 The analogue method is often used to forecast precipitation based on predictors variables provided by global models.
-The method samples a selection of days in the archives that are similar to the target day to forecast, and consider the set of their corresponding observed precipitation (the predictand) as the conditional distribution for the target day.
+The method samples a selection of days in the archives that are similar to the target day to predict, and consider the set of their corresponding observed precipitation (the predictand) as the conditional distribution for the target day.
 The relationship between predictors and predictands relies on some parameters that characterize how and where the similitude between two atmospheric situations is defined.
@@
 An intensive assessment work resulted in recommendations of parametrization of GAs in order to optimize AMs successfully.
-The present paper is based on these recommendations and illustrate them on precipitation forecasting for the upper Rh\^{o}ne catchment in the Swiss Alps.
+The present paper is based on these recommendations and illustrate them on precipitation predicting for the upper Rh\^{o}ne catchment in the Swiss Alps.
 It aims at proving the relevance of a fully-automatic, objective, and global, optimization technique for AMs.
-The applications are indeed numerous, as the AM has to be adapted to every new location it is applied, or to any new predictand it should forecast.
+The applications are indeed numerous, as the AM has to be adapted to every new location it is applied, or to any new predictand it should predict.
 
@@
 
-\begin{table}[htb]
-	\caption{Parameters of the reference method on the atmospheric circulation (2Z).
-The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window).
-The criteria used for the current level of analogy is then provided, as well as the number of analogues.}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccc}
-			\hline
-			Level & Variable & Hour & Criteria & Nb \\ 
-			\hline 
-			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
-			& Z500 & 24~h & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_R1}
-\end{table}
-
 The $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day.
@@
 
-\begin{table}[htb]
-	\caption{Parameters of the reference method with moisture variables (2Z-2MI). Same conventions as Table \ref{table:params_R1}}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccc}
-			\hline 
-			Level & Variable & Hour & Criteria & Nb \\ 
-			\hline 
-			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
-			& Z500 & 24~h & & \\ 
-			\hline
-			\multirow{2}{*}{2} & TPW * RH850 & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{30} \\
-			& TPW * RH850 & 24~h & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_R2}
-\end{table}
-
 \subsection{Data}
@@
 
-The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series one wants to forecast.
+The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series one wants to predict.
 
@@
 It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$.
-The better the forecast, the smaller the score.
-The mean CRPS of a forecast series of length $n$ can be written:
+The better the prediction, the smaller the score.
+The mean CRPS of a prediction series of length $n$ can be written:
 
@@
 \end{equation}
-where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect forecast (which implies $CRPS_{p}~=~0$). A better forecast is characterized by an increase in CRPSS.
+where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect prediction (which implies $CRPS_{p}~=~0$).
+A better prediction is characterized by an increase in CRPSS.
 
@@
 
-The reference method for the analogy of the atmospheric circulation (2Z, Table \ref{table:params_R1}), based on the 500 and 1000~hPa levels, was first considered.
+The reference method for the analogy of the atmospheric circulation (2Z, Table \ref{table:params_R1}), based on Z500 and Z1000, was first considered.
 The optimizer had to choose the number of analogues, both spatial windows with no overlapping constraint, as well as the temporal windows (hours of observation of the geopotential), what the sequential calibration cannot do.
@@
 The averaged relative improvement of the CRPSS is 5.63\% for the CP and 3.82\% for the VP.
-The pressure levels that were chosen are 500~hPa or 700~hPa for the upper level, and 925~hPa or 1000~hPa (most often) for the lower level.
+The pressure levels that were chosen are Z500 or Z700 for the upper level, and Z925 or Z1000 (most often) for the lower level.
 
@@
 There was no constraint on the predictors, so that the same pressure level could be selected more than once.
-Some improvements were found on the score, both for the CP and the VP, confirming that this additional information is beneficial for the quality of the forecast.
+Some improvements were found on the score, both for the CP and the VP, confirming that this additional information is beneficial for the quality of the prediction.
 We then tried with 4 predictors, and so on, up to 8.
@@
 
-\begin{table}[htb]
-	\caption{Parameters of the 4Zo method (analogy on 4 levels of the atmospheric circulation) optimized for the Chablais subregion.
-The columns are the following: L = level of analogy, V = meteorological variable, H = hour of observation or temporal window, D = domain or spatial window, W = weighting of the score for the selected pressure levels, C = criteria, N = number of analogues.}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline L & V & H & D & W & C & N \\ 
-			\hline 
-			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & -2.5 - 15.0 \degree E & \multirow{2}{*}{32\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{28} \\
-			& & & 37.5 - 57.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z700} & \multirow{2}{*}{24~h} & 2.5 - 10.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
-			& & & 42.5 - 45.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{6~h} & -5.0 - 15.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
-			& & & 42.5 - 47.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
-			& & & 40.0 - 50.0 \degree N & & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_GA_4Zo}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Pressure levels ($\sim$) automatically selected for the 4Zo method at the different subregions. R represents the reference method (Table \ref{table:params_R1}).}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline ID & 300 & 400 & 500 & 600 & 700 & 850 & 925 & 1000 \\ 
-			\hline 
-			1  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
-			2  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
-			3  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
-			4  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
-			5  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
-			6  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
-			7  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
-			8  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
-			9  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
-			10 &   &   &   & $\sim$ & $\sim$ &   &   & $\sim \sim$ \\
-			\hline 	
-			R  &   &   & $\sim$ &   &   &   &   & $\sim$ \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_4Zo}
-\end{table}
-
-\begin{table}[htb]
-	\caption{CRPSS score (\%) of the three optimized methods (4Zo is the atmospheric circulation analogy detailed in the present section; 4Zo-2MIo and 4Zo-4MIo add a second level of analogy on moisture indexes, as explained in section \ref{sec:optim_moisture}).}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline 
-			ID & \multicolumn{2}{c}{4Zo} & \multicolumn{2}{c}{4Zo-2MIo} & \multicolumn{2}{c}{4Zo-4MIo} \\ 
-			& CP & VP & CP & VP & CP & VP \\ 
-			\hline 
-			1 & 40.3 & 38.5 & 45.5 & 43.8 & 45.9 & 43.6 \\
-			2 & 37.8 & 34.9 & 42.4 & 40.8 & 42.9 & 41.3 \\
-			3 & 36.6 & 33.9 & 41.4 & 39.0 & 41.8 & 39.5 \\
-			4 & 31.2 & 30.8 & 36.1 & 36.4 & 36.8 & 37.1 \\
-			5 & 34.4 & 36.5 & 38.6 & 41.4 & 39.2 & 41.8 \\
-			6 & 37.0 & 39.9 & 41.0 & 44.5 & 41.9 & 44.6 \\
-			7 & 30.0 & 30.1 & 33.8 & 34.6 & 34.4 & 34.8 \\
-			8 & 37.7 & 40.1 & 40.7 & 43.1 & 41.2 & 43.3 \\
-			9 & 33.1 & 30.0 & 38.4 & 36.6 & 38.7 & 36.3 \\
-			10 & 40.0 & 40.0 & 42.6 & 42.9 & 43.3 & 43.2 \\
-			\hline
-			av. & 35.8 & 35.5 & 40.1 & 40.3 & 40.6 & 40.5 \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo method.}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline 
-			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\ 
-			& CP & VP & CP & VP & CP & VP \\ 
-			\hline 
-			1 & 10.2 & 9.4 & 8.5 & 7.9 & 17.0 & 14.2 \\ 
-			2 & 9.9 & 3.4 & 10.2 & 7.3 & 19.3 & 13.7 \\ 
-			3 & 13.3 & 10.5 & 13.3 & 10.9 & 19.7 & 9.7 \\ 
-			4 & 11.0 & 7.4 & 12.9 & 10.0 & 23.2 & 23.8 \\ 
-			5 & 8.6 & 4.2 & 10.9 & 6.2 & 25.2 & 23.8 \\ 
-			6 & 10.5 & 5.1 & 11.1 & 7.1 & 21.2 & 41.1 \\ 
-			7 & 24.3 & 12.4 & 33.1 & 26.0 & 71.2 & 104.3 \\ 
-			8 & 19.0 & 12.7 & 26.2 & 19.2 & 39.4 & 34.9 \\ 
-			9 & 12.4 & 6.8 & 13.8 & 9.9 & 24.9 & 48.1 \\ 
-			10 & 13.6 & 6.8 & 14.4 & 6.9 & 29.9 & 31.5 \\ 
-			\hline 
-			av. & 13.3 & 7.9 & 15.4 & 11.1 & 29.1 & 34.5 \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores_thresholds_4Zo}
-\end{table}
-
 The resulting CRPSS scores are provided in Table \ref{table:scores} and are in average 35.8 \% for the CP and 35.5 \% for the VP.
@@
 The gain in score increases with the precipitation threshold: the relative improvement of the CRPSS is in average, respectively for the different thresholds, 13.3\%, 15.4\% and 29.1\% for the CP and 7.9\%, 11.1\% and 34.5\% for the VP.
-The optimization improves thus even more the forecasts for days with significant precipitation than usual days.
+The optimization improves thus even more the prediction for days with significant precipitation than usual days.
 
@@
 The automatic selections of the pressure levels (Table \ref{table:levels_GA_4Zo}) and the temporal windows (not shown) for the analogy of circulation show a great homogeneity and are spatially consistent.
-First of all, the level 1000~hPa is always selected twice (the first time at 6 or 12~h, and the second always at 30~h) and the 700~hPa is selected once for every subregion (always at 24~h).
-The level which varies from one subregion to another is the upper level (however always at 12~h), which is 300~hPa for the North-West part of the catchment, 500~hPa for most of the subregions, and 600~hPa for the Conches Valley.
+First of all, the level Z1000 is always selected twice (the first time at 6 or 12~h, and the second always at 30~h) and Z700 is selected once for every subregion (always at 24~h).
+The level which varies from one subregion to another is the upper level (however always at 12~h), which is Z300 for the North-West part of the catchment, Z500 for most of the subregions, and Z600 for the Conches Valley.
 Its spatial distribution is however homogeneous.
 The optimizer thus provided consistent selections of pressure levels and temporal windows, which depicts a significant preference in the AM, and the success of GAs to provide consistent results.
-The automatic selection of the pressure levels is a big advantage in favor of a global optimization, as it is not possible to assess all combinations of 4 levels with the sequential calibration procedure.
+The automatic selection of the pressure levels is a big advantage in favor of a global optimization.
 
 The resulting spatial windows (Figure \ref{fig:spatial_windows_4Zo}) may look very diverse first, but there are significant similarities for subregions located within the same vicinity.
-The first 4 subregions are characterized by a large spatial window on the upper level, whereas it becomes smaller for the other subregions.
-For most subregions, the second level (700~hPa) is represented by thin and longitudinally extended domains.
-The third level (1000~hPa at 6 or 12~h) also contains longitudinally extended domains, but a bit larger.
-The last one (1000~hPa at 30~h) is rather large and squared.
+The first 4 subregions are characterized by a large spatial window on the upper level, whereas it is smaller elsewhere.
+For most subregions, the second level (Z700) is represented by thin and longitudinally extended domains.
+The third level (Z1000 at 6 or 12~h) also contains longitudinally extended domains, but a bit larger.
+The last one (Z1000 at 30~h) is rather large and squared.
 Subregions number 5 (Left side valleys) and 6 (Southern ridges) have exactly the same spatial windows, which suggest that they behave in a similar way and thus could have been merged.
@@
 The CRPS score was also discretized into its accuracy and sharpness components, as suggested by \citet{Bontron2004}.
-The changes in each of these components has been expressed relatively to the total CRPS value, of the 2Z reference method, in Figure \ref{fig:figure_dcrps_comp_4Zo} for the different regions and both the CP and the VP.
+The changes in each of these components has been illustrated in Figure \ref{fig:figure_dcrps_comp_4Zo} relatively to the total CRPS value of the 2Z reference method for the different regions and both the CP and the VP.
 One can see that the accuracy part is always improved to a greater extent than the sharpness, which can occasionally deteriorate.
@@
 
-The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the CP when they are calibrated for the given subregion (Figure \ref{fig:crossing_4Zo_calib}).
+The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the CP when they are optimized for a given subregion (Figure \ref{fig:crossing_4Zo_calib}).
 However, the losses in CRPSS when exchanging the parameters are not of the same magnitude between the different subregions.
-Indeed, the Upper Rhone Valley (7) and moreover the Southeast ridges (8) seem to behave significantly differently.
-This is indeed a climatological reality, as this subregion is the most sensitive to southerly flows \citep{Horton2012}.
-Parameter sets from other subregions perform poorly for these subregions, and vice versa.
+Indeed, the Upper Rhone Valley (7) and moreover the Southeast ridges (8) seem to behave significantly differently, likely due to their particular sensitivity to southerly flows \citep{Horton2012}.
 This points at the importance of taking into account leading meteorological influences during discretization, that are not always best represented by the physical distance.
-Globally, the same pattern can be observed for the VP (Figure \ref{fig:crossing_4Zo_valid}), but in this case, minor improvements may be observed when crossing the parameters.
-The reason being that the independent VP contains other events that may be better forecasted by other parameter sets.
-The relatively small differences in score between parameterizations indicate that even though the parameters may differ significantly, the performance may not be drastically affected.
+Globally, the same pattern can be observed for the VP (Figure \ref{fig:crossing_4Zo_valid}), but in this case, minor improvements may occur when crossing the parameters, due to the presence of other events in the VP that may be better predicted by a different parameter set.
+The relatively small gaps in score between parameterizations indicate that even though the parameters may differ significantly, the performance may not be drastically affected.
 Even a change in the pressure level does not mean a radical drop of the score value.
-A different parametrization may lead to a different selection of the analogue days, and thus to an improvement of the forecast under certain weather conditions at the expense of others.
+A different parametrization may lead to a distinct selection of analogue days, and thus to an improvement of the prediction under certain weather conditions at the expense of others.
 
@@
 
-\begin{table}[htb]
-	\caption{Parameters of the 4Zo-2MIo method (atmospheric circulation on 4 levels and moisture index on 2 levels), optimized for the Chablais subregion.
-Same conventions as Table \ref{table:params_GA_4Zo}.}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline L & V & H & D & W & C & N \\ 
-			\hline 
-			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & 0.0 - 15.0 \degree E & \multirow{2}{*}{23\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
-			& & & 42.5 - 55.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{25\%} & & \\ 
-			& & & 40.0 - 45.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
-			& & & 42.5 - 47.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
-			& & & 40.0 - 47.5 \degree N & & & \\ 
-			\hline 
-			\multirow{4}{*}{2} & TPW & \multirow{2}{*}{12~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{57\%} & \multirow{4}{*}{RMSE} & \multirow{4}{*}{25} \\
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{24~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{43\%} & & \\ 
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_GA_4Zo_2MIo}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the 4Zo-2MIo method, at the different subregions.
-R represents the reference method (Table \ref{table:params_R2})}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccccccc}
-			\hline ID & 300 & 400 & 500 & 600 & 700 & 850 & 925 & 1000 \\ 
-			\hline 
-			1  & $\sim$ &   & $\sim$ &   & $\bullet \bullet$  & $\sim$ &   & $\sim$ \\
-			2  & $\sim$ &   &   &   & $\sim \bullet \bullet$ & $\sim$ &   & $\sim$ \\
-			3  & $\sim$ &   &   &   & $\sim \bullet \bullet$ & $\sim$ & $\sim$ &   \\
-			4  &   &   & $\sim$ & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
-			5  &   & $\sim$ &   &   & $\sim \bullet \bullet$ &   & $\sim \sim$ &   \\
-			6  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
-			7  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
-			8  &   &   & $\sim$ & $\bullet$ & $\sim \bullet$ &   & $\sim \sim$ &   \\
-			9  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ & $\sim$ &   \\
-			10 &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
-			\hline 
-			R &   &   & $\sim$ &   &   & $\bullet \bullet$ &   & $\sim$ \\
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:levels_GA_4Zo_2MIo}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo-2MIo method.}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline 
-			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\  
-			& CP & VP & CP & VP & CP & VP \\ 
-			\hline 
-			1 & 12.6 & 9.3 & 12.4 & 9.7 & 15.8 & 11.0 \\
-			2 & 10.4 & 7.7 & 11.2 & 10.5 & 18.9 & 16.6 \\ 
-			3 & 14.5 & 11.6 & 14.1 & 11.4 & 18.7 & 14.6 \\ 
-			4 & 11.4 & 9.4 & 11.5 & 11.6 & 14.9 & 22.7 \\ 
-			5 & 11.8 & 8.0 & 12.2 & 8.9 & 12.0 & 12.8 \\ 
-			6 & 11.3 & 7.1 & 11.2 & 8.0 & 15.3 & 29.1 \\ 
-			7 & 20.5 & 15.5 & 25.2 & 24.0 & 43.0 & 79.5 \\
-			8 & 19.3 & 15.7 & 23.1 & 18.6 & 25.2 & 31.7 \\ 
-			9 & 17.0 & 15.4 & 17.4 & 16.5 & 23.7 & 39.4 \\ 
-			10 & 12.9 & 9.6 & 13.8 & 11.1 & 28.5 & 32.1 \\ 
-			\hline 
-			av. & 14.2 & 10.9 & 15.2 & 13.0 & 21.6 & 28.9 \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores_thresholds_4Zo-2MIo}
-\end{table}
-
 The CRPSS scores of the optimized methods are provided in Table \ref{table:scores} and amounts to slightly more than 40 \% in average for both methods and for both periods.
@@
 
-As for 4Zo, the 4Zo-2MIo and 4Zo-4MIo methods present larger improvements in the forecast for significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
+As for 4Zo, the 4Zo-2MIo and 4Zo-4MIo methods present larger improvements in the prediction for significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
 The improvement are relatively similar for 4Zo-2MIo (Table \ref{table:scores_thresholds_4Zo-2MIo}) and 4Zo-4MIo (not shown), with slightly superior scores for the latter on small precipitation (P\(\geq\)1 mm : 17.7\% and 13.0\%) and extremes (P\(\geq\)0.5\(\cdot\)P10 : 23.7\% and 29.2\%).
@@
 When optimizing a method made of 2 levels of analogy, the introduction of moisture variables in the second level has an influence on the parameter values of the first level.
-This is first visible on number $N_{1}$ of analogues to be selected on the first level, and on the selection of the pressure levels for the circulation analogy.
+This is first visible on the number $N_{1}$ of analogues to be selected on the first level, and on the selection of the pressure levels for the circulation analogy.
+
 As for the sequential procedure, the optimal value of $N_{1}$ increases when adding a second level of analogy (Figure \ref{fig:figure_nb_analogues}).
 One can also notice that the optimal number of analogues $N_{2}$ for the second level of analogy of 4Zo-2MIo is slightly inferior to $N_{1}$ from 4Zo, but very close.
-There is a relationship between the optimal values of $N_{1}$ from both methods: the higher the $N_{1}$ of the first method, the higher $N_{1}$ and $N_{2}$ of the second is (Figure \ref{fig:figure_nb_analogues_relationships}).
-This relationship is not to be considered perfectly robust and should not be transposed to another case study, but in this case, it relates the magnitudes of the numbers on the various levels and methods.
+There is a trend between the optimal analogue number values of both methods: the higher $N_{1}$ of the 4Zo method, the higher $N_{1}$ and $N_{2}$ of 4Zo-2MIo is (Figure \ref{fig:figure_nb_analogues_relationships}).
+This relationship is not to be considered perfectly robust and should not be transposed to another case study, but in this case, it relates the magnitudes of the $N_{1}$ and $N_{2}$ on the various levels and methods.
+
 The optimal final number of analogues do not vary much: $23 \leq N_{1} \leq 33$ for 4Zo and $21 \leq N_{2} \leq 28$ for 4Zo-2MIo.
@@
 
-As for the pressure levels, the 1000~hPa that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) is now less chosen (once or even not at all) for both 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}) and 4Zo-4MIo (not shown).
-There is indeed a shift of the previously selected 1000~hPa for higher levels, which is even slightly stronger with 4 moisture predictors than with 2.
+As for the pressure levels, Z1000 that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) is now less chosen (once or even not at all) for both 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}) and 4Zo-4MIo (not shown).
+There is indeed a shift of the previously selected Z1000 for higher levels, that is even slightly stronger with 4 moisture predictors than with 2.
 This change is likely due to the fact that when considering only the circulation analogy, the method tries to take into account information that can serve as proxy for moisture assessment, whereas it does not need it with the moisture index.
@@
 The selected pressure levels for the analogy on the moisture index are strongly centered around 700~hPa and 600~hPa.
-No other value has been selected when considering 2 pressure levels (Table \ref{table:levels_GA_4Zo_2MIo}), and when considering 4 levels, 850~hPa and 500~hPa are sometimes also selected (not shown).
+No other value has been selected when considering 2 pressure levels (Table \ref{table:levels_GA_4Zo_2MIo}), and when considering 4 levels, 850~hPa and 500~hPa were sometimes also selected (not shown).
 However, even in this latter method, the 700~hPa and 600~hPa levels still hold 78 \% of the selection.
-It is thus more efficient, in terms of forecasting performance, to consider one of this level several times at different hours rather than using another pressure level.
+It is thus more efficient, in terms of prediction performance, to consider one of this level several times at different hours rather than selecting another pressure level.
 Besides, the optimizer never chose the same pressure level at the same hour for any variable, even though it was allowed to do so.
@@
 The CRPSS scores were improved by considering the moisture information (Table \ref{table:scores}).
-The optimized methods also perform significantly better than the reference method based on the moisture index (Figures \ref{fig:figure_dcrpss_4Zo-2HIo} and \ref{fig:figure_dcrpss_4Zo-2HIo}) optimized by the sequential procedure.
+The optimized methods also perform significantly better than the reference method based on the moisture index (Figures \ref{fig:figure_dcrpss_4Zo-2HIo} and \ref{fig:figure_dcrpss_4Zo-4HIo}) optimized by the sequential procedure.
 However, there is no drastic difference between both 4Zo-2MIo and 4Zo-4MIo methods, which suggests that considering 4 moisture predictors is not necessary.
-When it comes to improvements for days with precipitation above the 3 thresholds (P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the forecast compared to reference method, mainly for heavy rainfall.
+When it comes to improvements for days with precipitation above the 3 thresholds (P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the prediction compared to the reference method, mainly for heavy rainfall.
 
 As previously, the CRPS scores were discretized into their sharpness and accuracy components.
-The changes in each of these components, expressed relatively to the total CRPS values, is once again in favor of the accuracy over the sharpness (Figure \ref{fig:figure_dcrps_comp_4Zo-2HIo} for 4Zo-2MIo; 4Zo-4MIo not shown as similar).
+The changes in each of these components, expressed relatively to the total CRPS values, is once again in favor of the accuracy over the sharpness (Figure \ref{fig:figure_dcrps_comp_4Zo-2HIo} for 4Zo-2MIo; 4Zo-4MIo not shown, but similar).
 
 The analysis of the parameters cross-compatibility (Figures \ref{fig:crossing_4Zo-2MIo_calib} and \ref{fig:crossing_4Zo-2MIo_valid}) is also very similar to the one on the circulation analogy only (results for 4Zo-4MIo not shown as very similar).
-The same pattern can be observed, with a drop of performance for the subregions submitted to several different meteorological influences.
-However, the losses of performance are globally more important than before, suggesting that more complex methods with moisture variables are less transposable to another subregion, even though it is located within the same grid cell of the reanalysis dataset.
-The meteorological influences should be taken into account.
+The same pattern can be observed, with a drop of performance for the subregions submitted to different meteorological influences.
+However, the losses of performance are globally more important than before, suggesting that more complex methods with moisture variables are less transposable to another subregion, even though both are located within the same grid cell of the reanalysis dataset.
 
@@
 GAs provide parameterizations of AMs that exceed the performance of the sequential calibration.
-In addition, it has been observed that the forecasts for days with strong precipitation were significantly more improved, which is clearly interesting in the framework of flood forecasting.
+In addition, it has been observed that the prediction for days with strong precipitation were significantly more improved, which is clearly interesting in the framework of flood forecasting.
 
@@
 
-\bibliography{../_refs/_articles-optimization}
+\bibliography{references}
+
+\clearpage
 
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 	\centerline{\includegraphics[width=8.8cm]{figures/fig03.pdf}}
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 	\centerline{\includegraphics[width=8.8cm]{figures/fig04.pdf}}
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 	\centerline{\includegraphics[width=8.4cm]{figures/fig05.pdf}}
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 	\centerline{\includegraphics[width=8.4cm]{figures/fig06.pdf}}
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 	\centerline{\includegraphics[width=8.4cm]{figures/fig07.pdf}}
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 	\centerline{\includegraphics[width=8.8cm]{figures/fig08.pdf}}
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 	\centerline{\includegraphics[width=8.8cm]{figures/fig09.pdf}}
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 	\centerline{\includegraphics[width=8.8cm]{figures/fig10.pdf}}
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 	\centerline{\includegraphics[width=8.8cm]{figures/fig11.pdf}}
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 	\centerline{\includegraphics[width=8.8cm]{figures/fig12.pdf}}
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 	\centerline{\includegraphics[width=8.4cm]{figures/fig13.pdf}}
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 	\centerline{\includegraphics[width=8.4cm]{figures/fig14.pdf}}
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 	\centerline{\includegraphics[width=8.8cm]{figures/fig15.pdf}}
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 	\centerline{\includegraphics[width=8.8cm]{figures/fig16.pdf}}
@@
 
-\begin{figure}[htb]
+\begin{figure}[t]
 	\centerline{\includegraphics[width=7.5cm]{figures/fig17.pdf}}
@@
 
+\clearpage
+
+%% TABLES
+
+\begin{table}[t]
+	\caption{Parameters of the reference method on the atmospheric circulation (2Z).
+The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window).
+The criteria used for the current level of analogy is then provided, as well as the number of analogues.}
+	\footnotesize
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline
+			Level & Variable & Hour & Criteria & Nb \\ 
+			\hline 
+			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
+			& Z500 & 24~h & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:params_R1}
+\end{table}
+
+\begin{table}[t]
+	\caption{Parameters of the reference method with moisture variables (2Z-2MI). Same conventions as Table \ref{table:params_R1}}
+	\footnotesize
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline 
+			Level & Variable & Hour & Criteria & Nb \\ 
+			\hline 
+			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
+			& Z500 & 24~h & & \\ 
+			\hline
+			\multirow{2}{*}{2} & TPW * RH850 & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{30} \\
+			& TPW * RH850 & 24~h & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:params_R2}
+\end{table}
+
+\begin{table}[t]
+	\caption{Parameters of the 4Zo method (analogy on 4 levels of the atmospheric circulation) optimized for the Chablais subregion.
+The columns are the following: L = level of analogy, V = meteorological variable, H = hour of observation or temporal window, D = domain or spatial window, W = weighting of the score for the selected pressure levels, C = criteria, N = number of analogues.}
+	\footnotesize
+	\begin{center}
+		\begin{tabular}{ccccccc}
+			\hline L & V & H & D & W & C & N \\ 
+			\hline 
+			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & -2.5 - 15.0 \degree E & \multirow{2}{*}{32\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{28} \\
+			& & & 37.5 - 57.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z700} & \multirow{2}{*}{24~h} & 2.5 - 10.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
+			& & & 42.5 - 45.0 \degree N & & & \\ 
+			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{6~h} & -5.0 - 15.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
+			& & & 42.5 - 47.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
+			& & & 40.0 - 50.0 \degree N & & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:params_GA_4Zo}
+\end{table}
+
+\begin{table}[t]
+	\caption{Pressure levels ($\sim$) automatically selected for the 4Zo method at the different subregions. R represents the reference method (Table \ref{table:params_R1}).}
+	\footnotesize
+	\begin{center}
+		\begin{tabular}{ccccccccc}
+			\hline ID & 300 & 400 & 500 & 600 & 700 & 850 & 925 & 1000 \\ 
+			\hline 
+			1  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
+			2  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
+			3  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
+			4  & $\sim$ &   &   &   & $\sim$ &   &   & $\sim \sim$ \\
+			5  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
+			6  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
+			7  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
+			8  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
+			9  &   &   & $\sim$ &   & $\sim$ &   &   & $\sim \sim$ \\
+			10 &   &   &   & $\sim$ & $\sim$ &   &   & $\sim \sim$ \\
+			\hline 	
+			R  &   &   & $\sim$ &   &   &   &   & $\sim$ \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:levels_GA_4Zo}
+\end{table}
+
+\begin{table}[t]
+	\caption{CRPSS score (\%) of the three optimized methods (4Zo is the atmospheric circulation analogy detailed in the present section; 4Zo-2MIo and 4Zo-4MIo add a second level of analogy on moisture indexes, as explained in section \ref{sec:optim_moisture}).}
+	\footnotesize
+	\begin{center}
+		\begin{tabular}{ccccccc}
+			\hline 
+			ID & \multicolumn{2}{c}{4Zo} & \multicolumn{2}{c}{4Zo-2MIo} & \multicolumn{2}{c}{4Zo-4MIo} \\ 
+			& CP & VP & CP & VP & CP & VP \\ 
+			\hline 
+			1 & 40.3 & 38.5 & 45.5 & 43.8 & 45.9 & 43.6 \\
+			2 & 37.8 & 34.9 & 42.4 & 40.8 & 42.9 & 41.3 \\
+			3 & 36.6 & 33.9 & 41.4 & 39.0 & 41.8 & 39.5 \\
+			4 & 31.2 & 30.8 & 36.1 & 36.4 & 36.8 & 37.1 \\
+			5 & 34.4 & 36.5 & 38.6 & 41.4 & 39.2 & 41.8 \\
+			6 & 37.0 & 39.9 & 41.0 & 44.5 & 41.9 & 44.6 \\
+			7 & 30.0 & 30.1 & 33.8 & 34.6 & 34.4 & 34.8 \\
+			8 & 37.7 & 40.1 & 40.7 & 43.1 & 41.2 & 43.3 \\
+			9 & 33.1 & 30.0 & 38.4 & 36.6 & 38.7 & 36.3 \\
+			10 & 40.0 & 40.0 & 42.6 & 42.9 & 43.3 & 43.2 \\
+			\hline
+			av. & 35.8 & 35.5 & 40.1 & 40.3 & 40.6 & 40.5 \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:scores}
+\end{table}
+
+\begin{table}[t]
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo method.}
+	\footnotesize
+	\begin{center}
+		\begin{tabular}{ccccccc}
+			\hline 
+			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\ 
+			& CP & VP & CP & VP & CP & VP \\ 
+			\hline 
+			1 & 10.2 & 9.4 & 8.5 & 7.9 & 17.0 & 14.2 \\ 
+			2 & 9.9 & 3.4 & 10.2 & 7.3 & 19.3 & 13.7 \\ 
+			3 & 13.3 & 10.5 & 13.3 & 10.9 & 19.7 & 9.7 \\ 
+			4 & 11.0 & 7.4 & 12.9 & 10.0 & 23.2 & 23.8 \\ 
+			5 & 8.6 & 4.2 & 10.9 & 6.2 & 25.2 & 23.8 \\ 
+			6 & 10.5 & 5.1 & 11.1 & 7.1 & 21.2 & 41.1 \\ 
+			7 & 24.3 & 12.4 & 33.1 & 26.0 & 71.2 & 104.3 \\ 
+			8 & 19.0 & 12.7 & 26.2 & 19.2 & 39.4 & 34.9 \\ 
+			9 & 12.4 & 6.8 & 13.8 & 9.9 & 24.9 & 48.1 \\ 
+			10 & 13.6 & 6.8 & 14.4 & 6.9 & 29.9 & 31.5 \\ 
+			\hline 
+			av. & 13.3 & 7.9 & 15.4 & 11.1 & 29.1 & 34.5 \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:scores_thresholds_4Zo}
+\end{table}
+
+\begin{table}[t]
+	\caption{Parameters of the 4Zo-2MIo method (atmospheric circulation on 4 levels and moisture index on 2 levels), optimized for the Chablais subregion.
+Same conventions as Table \ref{table:params_GA_4Zo}.}
+	\footnotesize
+	\begin{center}
+		\begin{tabular}{ccccccc}
+			\hline L & V & H & D & W & C & N \\ 
+			\hline 
+			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & 0.0 - 15.0 \degree E & \multirow{2}{*}{23\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
+			& & & 42.5 - 55.0 \degree N & & & \\ 
+			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{25\%} & & \\ 
+			& & & 40.0 - 45.0 \degree N & & & \\ 
+			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
+			& & & 42.5 - 47.5 \degree N & & & \\ 
+			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
+			& & & 40.0 - 47.5 \degree N & & & \\ 
+			\hline 
+			\multirow{4}{*}{2} & TPW & \multirow{2}{*}{12~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{57\%} & \multirow{4}{*}{RMSE} & \multirow{4}{*}{25} \\
+			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
+			& TPW & \multirow{2}{*}{24~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{43\%} & & \\ 
+			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:params_GA_4Zo_2MIo}
+\end{table}
+
+\begin{table}[t]
+	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the 4Zo-2MIo method, at the different subregions.
+R represents the reference method (Table \ref{table:params_R2})}
+	\footnotesize
+	\begin{center}
+		\begin{tabular}{ccccccccc}
+			\hline ID & 300 & 400 & 500 & 600 & 700 & 850 & 925 & 1000 \\ 
+			\hline 
+			1  & $\sim$ &   & $\sim$ &   & $\bullet \bullet$  & $\sim$ &   & $\sim$ \\
+			2  & $\sim$ &   &   &   & $\sim \bullet \bullet$ & $\sim$ &   & $\sim$ \\
+			3  & $\sim$ &   &   &   & $\sim \bullet \bullet$ & $\sim$ & $\sim$ &   \\
+			4  &   &   & $\sim$ & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
+			5  &   & $\sim$ &   &   & $\sim \bullet \bullet$ &   & $\sim \sim$ &   \\
+			6  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
+			7  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
+			8  &   &   & $\sim$ & $\bullet$ & $\sim \bullet$ &   & $\sim \sim$ &   \\
+			9  &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ & $\sim$ &   \\
+			10 &   & $\sim$ &   & $\bullet$ & $\sim \bullet$ & $\sim$ &   & $\sim$ \\
+			\hline 
+			R &   &   & $\sim$ &   &   & $\bullet \bullet$ &   & $\sim$ \\
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:levels_GA_4Zo_2MIo}
+\end{table}
+
+\begin{table}[t]
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo-2MIo method.}
+	\footnotesize
+	\begin{center}
+		\begin{tabular}{ccccccc}
+			\hline 
+			ID & \multicolumn{2}{c}{P\(\geq\)1 mm} & \multicolumn{2}{c}{P\(\geq\)0.1\(\cdot\)P10} & \multicolumn{2}{c}{P\(\geq\)0.5\(\cdot\)P10} \\  
+			& CP & VP & CP & VP & CP & VP \\ 
+			\hline 
+			1 & 12.6 & 9.3 & 12.4 & 9.7 & 15.8 & 11.0 \\
+			2 & 10.4 & 7.7 & 11.2 & 10.5 & 18.9 & 16.6 \\ 
+			3 & 14.5 & 11.6 & 14.1 & 11.4 & 18.7 & 14.6 \\ 
+			4 & 11.4 & 9.4 & 11.5 & 11.6 & 14.9 & 22.7 \\ 
+			5 & 11.8 & 8.0 & 12.2 & 8.9 & 12.0 & 12.8 \\ 
+			6 & 11.3 & 7.1 & 11.2 & 8.0 & 15.3 & 29.1 \\ 
+			7 & 20.5 & 15.5 & 25.2 & 24.0 & 43.0 & 79.5 \\
+			8 & 19.3 & 15.7 & 23.1 & 18.6 & 25.2 & 31.7 \\ 
+			9 & 17.0 & 15.4 & 17.4 & 16.5 & 23.7 & 39.4 \\ 
+			10 & 12.9 & 9.6 & 13.8 & 11.1 & 28.5 & 32.1 \\ 
+			\hline 
+			av. & 14.2 & 10.9 & 15.2 & 13.0 & 21.6 & 28.9 \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:scores_thresholds_4Zo-2MIo}
+\end{table}
+
 \end{document}

### 2016-02-08 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Editions for submission.

@@
 \begin{abstract}
-The analogue method is often used to forecast precipitation based on predictors variables provided by global models.
+The Analogue Method aims at predicting precipitation based on predictors variables provided by global models.
 The method samples a selection of days in the archives that are similar to the target day to predict, and consider the set of their corresponding observed precipitation (the predictand) as the conditional distribution for the target day.
@@
 This relationship is usually established by a semi-automatic sequential procedure that has strong limitations.
-A new global optimization approach relying on Genetic Algorithms can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
-It allows taking into account parameters inter-dependencies, adding new degrees of freedom, and choosing objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
+A new global optimization approach relying on Genetic Algorithms can optimize all parameters jointly and automatically, which is a breakthrough in the way the Analogue Method was calibrated until now.
+It allows taking into account parameters inter-dependencies, and selecting objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
 
-In this work, the global optimization is applied to the Rh\^{o}ne catchment in the Swiss Alps in order to show its interest and the relevance of the resulting parameters.
-Indeed, not only the performance increases, but the parameters are obtained automatically and objectively, which reduces efforts invested in exploration attempts when adapting the method to a new region or for a new predictand.
-Moreover, the approach allows for new degrees of freedom, such as a weighting between the pressure levels and non overlapping spatial windows.
+In this work, the global optimization is applied to the Rh\^{o}ne catchment, in the Swiss Alps.
+The performance scores are significantly increased compared to a reference method, and this even to a greater extent for days with high precipitation totals.
+The resulting parameters were found to be relevant and coherent between the different subregions of the catchment.
+Moreover, they are obtained automatically and objectively, which reduces efforts invested in exploration attempts when adapting the method to a new region or for a new predictand.
+In addition, the approach allows for new degrees of freedom, such as a weighting between the pressure levels, and non overlapping spatial windows.
 \end{abstract}
@@
 
-\section{The analogue method}
+\section{The Analogue Method}
 \label{sec:analog_method}
@@
 
-\section{Genetic algorithms}
+\section{Genetic Algorithms}
 \label{sec:gas}

### 2016-02-12 Genetic algorithms - Journal of Climate/template.tex
Preparing for submission.

@@
 
-\authors{Pascal Horton\correspondingauthor{Terranum, Rue de l'industrie 35 bis, 1030 Bussigny, Switzerland.}}
+\authors{Pascal Horton\correspondingauthor{Pascal Horton, Terranum, Rue de l'industrie 35 bis, 1030 Bussigny, Switzerland.}\thanks{Current affiliation: Terranum, Bussigny, Switzerland}}
 
@@
 
-\affiliation{University of Lausanne and Terranum, Lausanne, Switzerland}
+\affiliation{University of Lausanne, Lausanne, Switzerland}
 
@@
 Here, operators are defined as the mechanisms that modify the values of the genes to try bringing individuals (or chromosomes) closer to an optimum of the fitness function.
-The structure of the method (Figure \ref{fig:structure_gas}) resulting from the work of \citet{Holland1992b} is common to most applications \citep{Back1993b}, and consists in the following steps:
+The structure of the method (Fig.
+\ref{fig:structure_gas}) resulting from the work of \citet{Holland1992b} is common to most applications \citep{Back1993b}, and consists in the following steps:
 
@@
 
-\begin{figure}[htb]
-	\noindent\includegraphics[width=19pc,angle=0]{figures/figure_structure_gas.pdf}\\
-	\caption{Genetic Algorithms operational flowchart}
-	\label{fig:structure_gas}
-\end{figure}
-
 All considered operators and their options, applied to floating-point coding, are described in the following sections. Many other operators exist, but only the ones evaluated are presented.
@@
 After a first overview of the results, GAs have quicky proved successful at optimizing the AM.
-The performance score of the sequential approach has been quickly exceeded without adding any new parameter to the method (Figure \ref{fig:gas_evolution_good}).
-Even GAs parameterizations that will be considered later as inadequate (Figure \ref{fig:gas_evolution_bad}) did significantly better that the sequential approach.
+The performance score of the sequential approach has been quickly exceeded without adding any new parameter to the method (Fig.
+\ref{fig:gas_evolution_good}).
+Even GAs parameterizations that will be considered later as inadequate (Fig.
+\ref{fig:gas_evolution_bad}) did significantly better that the sequential approach.
 The amplitude of the improvement is not the main outcome here.
 The most important point is that GAs proved successful at optimizing AMs automatically, globally, and objectively.
-
-\begin{figure}[htb]
-	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{figures/gas_evolution_good.pdf}\\
-	\end{center}
-	\caption{Evolution of the score of the best individuals over generations for the 10 optimizations processed for a given parametrization.
-The green line (bottom) represents the score of the sequential approach and the blue one (top), the supposed global optimum.}
-	\label{fig:gas_evolution_good}
-\end{figure}
-
-\begin{figure}[htb]
-	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{figures/gas_evolution_bad.pdf}\\
-	\end{center}
-	\caption{Same as Figure \ref{fig:gas_evolution_good}, but for a GAs parametrization considered as less relevant.}
-	\label{fig:gas_evolution_bad}
-\end{figure}
 
@@
 
-\begin{table}[htbp]
+The performance of the couples selection operator are relatively close (Fig.
+\ref{fig:operator_selectcoupl_score}).
+Overall, the tournament selection with 3~candidates is slightly superior to others, along with the roulette wheel weighting.
+This last one is however a bit less effective in terms of convergence and number of evaluations (not shown).
+The couples selection operator has not a significant role in this application.
+
+Analysis of crossover operators (Fig.
+\ref{fig:operator_crossover_score}) reveal some slightly superior options, some inappropriate, and many average.
+Binary-like crossover (especially with 2 points of intersection, whether $\beta$ is shared or not) are significantly better than the others, especially in terms of convergence (not shown).
+Others operators can also be considered usable.
+
+\subsubsection{Mutation operator}
+\label{sec:assessment:mutation}
+
+Having identified the leading role of the mutation operator, the next sensitivity analysis focused on it.
+Each of the 10 different implementations (see section \ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Table \ref{tab:assessed_mutation_operators}), bringing the number of variations up to 109.
+Some optimizations without any mutation were also performed as a reference.
+Along with variants of the other operators \citep[see][for the details]{Horton2012a}, this resulted in 660 combinations (so 6,600 optimizations).
+
+Figure \ref{fig:operator_mutation_score} show the results of this analysis and illustrates the important role of the mutation on the performance of the optimizations.
+Those without mutation (last box on the figure) are inferior to most mutation operators, and the scale of the influence of this operator is significantly more important than those for the other options.
+The details of the analysis \citep[see][]{Horton2012a} show that the other reproduction operators seem of secondary importance.
+This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction, as well as other authors (see section \ref{sec:gas}.\ref{sec:gas:mutation}).
+
+The mutation operators based on a variable normal or variable uniform laws work very poorly and are difficult to configure.
+Many operators present more or less the same performance scores and require a variable amount of assessments.
+The convergence analysis \citep[see][]{Horton2012a} allows to highlight three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
+Thus, different optimizations were further performed using variants of these 3 operators (Table \ref{tab:assessed_mutation_operators_bis}).
+
+The first analysis was the optimization of the precipitation forecasting over a subcatchment (Binn-Simplon region) in the Swiss Alps (Fig.
+\ref{fig:operator_mutation_score_atmlevel}).
+The optimizer could choose the 2 pressure levels of the atmospheric circulation analogy (method with a single level of analogy).
+The resulting performance score \citep[CRPSS = skill score of the CRPS, see][]{Brown1974} is obviously superior to the one obtained by the sequential calibration (red line on Fig.
+\ref{fig:operator_mutation_score_atmlevel}).
+For most options, it is also slightly better than the results from the optimization without selection of the pressure levels (blue line).
+A clear breakthrough of the performances was not expected, as the former selection of pressure levels results already from intensive comparative work \citep{Bontron2004}.
+This application however demonstrates that, when correctly parametrized, GAs can automatically and successfully choose the pressure levels.
+However, some less relevant optimizations do not match the previous results.
+Through different applications, the automatic selection of the pressure level was shown to significantly increase the difficulty for GAs to converge to a unique solution, ideally the global optimum.
+A difficulty is that the pressure levels are considered within the optimization without continuity between values, and thus the approaches relying on distance in the parameters space, such as the search radius, cannot fully exploit the properties that make them efficient.
+However, even though the results show a certain variability, most of them present very good performance scores, despite different parameters of the AM.
+
+Then, the same optimization was performed, but for another region, sensitive to other meteorological influences (Fig.
+\ref{fig:operator_mutation_score_rhoneamont}), in order to assess eventual dependencies of the operator with the predictand.
+Even though differences can be observed with Fig.
+\ref{fig:operator_mutation_score_atmlevel}, it is globally the same options that perform better.
+
+Next, a second level of analogy was proposed (Fig.
+\ref{fig:operator_mutation_score_r2}) based on moisture variables \citep[see][]{Bontron2004, Horton2016}.
+GAs had to optimize both levels of analogy simultaneously.
+Once again, despite the difficulty to do so, the results were better than the sequential calibration (red line on Fig.
+\ref{fig:operator_mutation_score_r2}).
+And finally, a preselection on air temperature was added instead of the fixed calendar window, as proposed by \cite{BenDaoud2015}.
+The results show generally higher scores (Fig.
+\ref{fig:operator_mutation_score_r4}), demonstrating the success of the optimizer to take advantage of this new degree of freedom, and its capacity to handle optimization of 3 analogy levels jointly.
+Again, the most relevant options are generally the same.
+
+After analysis of the most relevant mutation operators, the following advice can be raised (detailed parametrization are provided in section \ref{sec:recommendations}):
+
+\begin{itemize}
+
+	\item \textit{Non-uniform mutation} \citep{Michalewicz1996}: this operator is good in terms of convergence, mainly when the number of parameters to optimize is rather low.
+The number of required evaluations, however, can be quite substantial.
+The main disadvantage of the non-uniform mutation is the number of parameters it requires, that are difficult to estimate a priori.
+The mutation rate was found to be more important than the others.
+The difficulty is that its optimal value may be case-related.
+
+	\item \textit{Chromosome of adaptive search radius} (new): unlike the previous one, this new operator is very robust, as it requires no option and is auto-adapting.
+It is interesting to notice that the insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).
+If one had to choose a single option for the mutation operator, we would recommend this one, as it was proven effective and needs no parameter.
+
+	\item \textit{Multi-scale mutation} (new): finally, the multi-scale mutation, which also performs pretty well, requires one parameter, the mutation rate.
+However, it can also be difficult to estimate a correct value a priori.
+
+\end{itemize}
+
+In this application, the mutation operator has a leading effect and should be chosen with care.
+It may be wise to perform multiple optimizations and to consider these three operators in parallel in order to obtain results from options that are sometimes either more efficient or more robust.
+It is interesting to note that the three best techniques incorporate a notion of search distance.
+It is likely that this notion is the key to these algorithms, for this application, and allows them to initially explore the parameter domain, and then to converge.
+The search radius in fact directly represents the notion of transition between exploration and exploitation, in our opinion more than a possible evolution of mutation rates.
+
+\subsubsection{Other options}
+
+The analysis of the natural selection operator (Fig.
+\ref{fig:operator_selectnat_score}) reveals a slight preference for the ratio-elitism compared to the tournament selection, but not so significant.
+This operator, or at least the two assessed versions, do not appear to significantly influence the optimization performances.
+
+The size of the population ($N$), i.e.
+the number of sets of AM parameters considered, has an effect on the performance of the optimization (Fig.
+\ref{fig:option_taillepop_score}).
+A bigger population leads to better results, but also to significantly longer optimizations.
+Indeed, the required number of evaluation, and thus the required time, is approximately proportional to the population size.
+The optimal size seems to depend on the complexity of the AM to optimize: a more complex AM (ie.
+with more degrees of freedom) requires a bigger population size.
+A rule of thumb based on a limited number of case studies (not shown here) is provided hereafter:
+
+\begin{itemize}
+	\item $N\approx100$ for very simple implementations of the AM (1 level of analogy with 2 pressure levels),
+	\item $N\approx200$ for a slightly more complex AM (1 level of analogy with 4 pressure levels, or 2 level of analogy with less pressure levels),
+	\item $N\approx500$ for significantly more complex AMs (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the moisture analogy).
+\end{itemize}
+
+The influence of the size of the IG (proportion of the total population) selected for mating was also assessed (Fig.
+\ref{fig:option_popratio_score}).
+It does not appear that this parameter is critical to the quality of the optimizations, provided it is not too big.
+A value of 50~\% seems a wise choice.
+
+\section{Recommended parametrization of GAs}
+\label{sec:recommendations}
+
+Optimizations by GAs for AMs of varying complexities were performed with a large number of combinations of operators in order to make recommendations for optimizing the AM. The conclusions are:
+
+\begin{itemize}
+	\item The population size should be in accordance with the complexity of the AM to optimize: from 100 for the simple ones, up to 500 for the most complex AMs.
+
+	\item The value of the ratio for the IG is not so important, and value of 50\% seems quite appropriate.
+
+	\item Ratio-elitism is slightly better than tournaments for the natural selection operator, but it is not decisive.
+
+	\item The performance of the operators for the couples selection perform relatively similarly.
+The roulette wheel weighting and the tournament selection are more efficient in terms of convergence and required number of evaluations.
+
+	\item Most crossover operators have relatively similar performance. Binary-like crossover with two points of intersection are better than others, especially for convergence.
+
+	\item Mutation has a clearly dominant influence.
+Three mutation operators stand out: the non-uniform mutation, the multi-scale mutation, and the chromosome of adaptive search radius.
+The latter is the most robust as it has no controlling parameter.
+
+\end{itemize}
+
+The optimization does not systematically converge to the global optimum (but still often nearby), which is why it is recommended to do several optimizations in parallel in order to compare the results, analyze the convergence, and keep the best.
+It may be wise to consider the three mutation operators in parallel.
+In order to be confident in the optimized AMs, we propose using a set of the following mutation operators:
+
+\begin{itemize}
+	\setlength\itemsep{-4px}
+	\item 1x non-uniform, $p_{mut}=0.05$, $G_{m}=50$, $\omega=0.1$
+	\item 1x non-uniform, $p_{mut}=0.05$, $G_{m}=100$, $\omega=0.1$
+	\item 1x non-uniform, $p_{mut}=0.1$, $G_{m}=100$, $\omega=0.1$
+	\item 1x multi-scale,  $p_{mut}=0.1$
+	\item 2x chromosome of adaptive search radius
+\end{itemize}
+
+\section{Conclusions}
+
+In order to automatically optimize the AM and to get rid of the limitations of the usual sequential calibration, GAs were evaluated.
+Given the large number of existing operators and options, multiple variants were assessed systematically in order to identify which operators are important, and which variants work best for the AM.
+The mutation operator was identified as a key element for this application, and new variants that proved efficient were provided, such as the chromosome of adaptive search radius that is very robust (no control parameter).
+Recommendations were established for a relevant use of GAs for the optimization of AMs.
+
+It is not excluded that another global optimization method or other operators of GAs may perform still better.
+However, the relevance of such an approach has now been proved as it results in parametrization of AMs that are relevant and fully automatically, globally and objectively established.
+A global optimization is the only way to take into account all the dependencies between parameters and levels of analogy.
+
+The global optimization approach allows easily adapting the AM to new regions by potentially taking into account local meteorological influences, and has thus a great potential of use.
+Moreover, it allows exploring automatically datasets in order to extract the most relevant variables.
+It is thus possible to try assessing other predictands, such as the temperature, the limit of snowfall, the occurrence of hail, or wind, while leaving the algorithms select the best variables and the associated parameters.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% ACKNOWLEDGMENTS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+\acknowledgments
+Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of.
+Thanks to Dominique B\'{e}rod for his support and to Michel Bierlaire for his advices on optimization methods.
+
+Thanks to the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton, the Water, Land and Sanitation Service of the Vaud Canton, and the Swiss Federal Office for Environment (FOEV) who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
+The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
+NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.
+Precipitation time series provided by MeteoSwiss.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% APPENDIXES
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% Use \appendix if there is only one appendix.
+%\appendix
+
+% Use \appendix[A], \appendix}[B], if you have multiple appendixes.
+%\appendix[A]
+
+%% Appendix title is necessary! For appendix title:
+%\appendixtitle{}
+
+%%% Appendix section numbering (note, skip \section and begin with \subsection)
+% \subsection{First primary heading}
+
+% \subsubsection{First secondary heading}
+
+% \paragraph{First tertiary heading}
+
+%% Important!
+%\appendcaption{<appendix letter and number>}{<caption>} 
+%must be used for figures and tables in appendixes, e.g.,
+%
+%\begin{figure}
+%\noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
+%\appendcaption{A1}{Caption here.}
+%\end{figure}
+%
+% All appendix figures/tables should be placed in order AFTER the main figures/tables, i.e., tables, appendix tables, figures, appendix figures.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% REFERENCES
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Make your BibTeX bibliography by using these commands:
+\bibliographystyle{ametsoc2014}
+\bibliography{references}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% TABLES
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Enter tables at the end of the document, before figures.
+%%
+%
+
+\begin{table}[t]
 	\caption{Assessed operator for couples selection.}
@@
 
-\begin{table}[htbp]
+\begin{table}[t]
 	\caption{Assessed operators for chromosome crossover.}
@@
 
-\begin{figure}[htb]
-	\begin{center}
-		\noindent\includegraphics[width=7cm,angle=0]{figures/operator_selectcoupl_score.pdf}\\
-	\end{center}
-	\caption{Influence of the couples selection operators (Table \ref{tab:assessed_couples_selection_operators}) on the optimization performance.
-The box extends from the lower to upper quartile values of the data, with a line at the median.
-The whiskers extend from the box to 1.5 times the interquartile range.
-Flier points are those past the end of the whiskers.
-The star represents the median.
-The gray box highlights the best options.}
-	\label{fig:operator_selectcoupl_score}
-\end{figure}
-
-\begin{figure*}[htb]
-	\begin{center}
-		\noindent\includegraphics[width=16cm,angle=0]{figures/operator_crossover_score.pdf}\\
-	\end{center}
-	\caption{Influence of the chromosome crossover operators (Table \ref{tab:assessed_crossover_operators}) on the optimization performance.
-Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
-	\label{fig:operator_crossover_score}
-\end{figure*}
-
-The performance of the couples selection operator are relatively close (Figure \ref{fig:operator_selectcoupl_score}).
-Overall, the tournament selection with 3~candidates is slightly superior to others, along with the roulette wheel weighting.
-This last one is however a bit less effective in terms of convergence and number of evaluations (not shown).
-The couples selection operator has not a significant role in this application.
-
-Analysis of crossover operators (Figure \ref{fig:operator_crossover_score}) reveal some slightly superior options, some inappropriate, and many average.
-Binary-like crossover (especially with 2 points of intersection, whether $\beta$ is shared or not) are significantly better than the others, especially in terms of convergence (not shown).
-Others operators can also be considered usable.
-
-\subsubsection{Mutation operator}
-\label{sec:assessment:mutation}
-
-Having identified the leading role of the mutation operator, the next sensitivity analysis focused on it.
-Each of the 10 different implementations (see section \ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Table \ref{tab:assessed_mutation_operators}), bringing the number of variations up to 109.
-Some optimizations without any mutation were also performed as a reference.
-Along with variants of the other operators \citep[see][for the details]{Horton2012a}, this resulted in 660 combinations (so 6,600 optimizations).
-
-\begin{table}[htbp]
+\begin{table}[t]
 	\caption{Assessed mutation operators with the number of variants considered (combination of parameters).}
@@
 
-\begin{figure}[htb]
-	\begin{center}
-		\noindent\includegraphics[width=7cm,angle=0]{figures/operator_mutation_score.pdf}\\
-	\end{center}
-	\caption{Influence of the mutation operators (Table \ref{tab:assessed_mutation_operators}) on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
-	\label{fig:operator_mutation_score}
-\end{figure}
-
-Figure \ref{fig:operator_mutation_score} show the results of this analysis and illustrates the important role of the mutation on the performance of the optimizations.
-Those without mutation (last box on the Figure) are inferior to most mutation operators, and the scale of the influence of this operator is significantly more important than those for the other options.
-The details of the analysis \citep[see][]{Horton2012a} show that the other reproduction operators seem of secondary importance.
-This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction, as well as other authors (see section \ref{sec:gas}.\ref{sec:gas:mutation}).
-
-The mutation operators based on a variable normal or variable uniform laws work very poorly and are difficult to configure.
-Many operators present more or less the same performance scores and require a variable amount of assessments.
-The convergence analysis \citep[see][]{Horton2012a} allows to highlight three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
-Thus, different optimizations were further performed using variants of these 3 operators (Table \ref{tab:assessed_mutation_operators_bis}).
-
-\begin{table}[htbp]
+\begin{table}[t]
 	\caption{Further assessments of mutation operators.}
@@
 
-\begin{figure*}[htb]
-	\begin{center}
-		\noindent\includegraphics[width=14cm,angle=0]{figures/operator_mutation_score_atmlevel.pdf}\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% FIGURES
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Enter figures at the end of the document, after tables.
+%%
+%
+
+\begin{figure}[t]
+	\begin{center}
+		\noindent\includegraphics[width=19pc,angle=0]{figures/figure_structure_gas.pdf}\\
+	\end{center}
+	\caption{Genetic Algorithms operational flowchart}
+	\label{fig:structure_gas}
+\end{figure}
+
+\begin{figure}[t]
+	\begin{center}
+		\noindent\includegraphics[width=19pc,angle=0]{figures/gas_evolution_good.pdf}\\
+	\end{center}
+	\caption{Evolution of the score of the best individuals over generations for the 10 optimizations processed for a given parametrization.
+The green line (bottom) represents the score of the sequential approach and the blue one (top), the supposed global optimum.}
+	\label{fig:gas_evolution_good}
+\end{figure}
+
+\begin{figure}[t]
+	\begin{center}
+		\noindent\includegraphics[width=19pc,angle=0]{figures/gas_evolution_bad.pdf}\\
+	\end{center}
+	\caption{Same as Fig. \ref{fig:gas_evolution_good}, but for a GAs parametrization considered as less relevant.}
+	\label{fig:gas_evolution_bad}
+\end{figure}
+
+\begin{figure}[t]
+	\begin{center}
+		\noindent\includegraphics[width=19pc,angle=0]{figures/operator_selectcoupl_score.pdf}\\
+	\end{center}
+	\caption{Influence of the couples selection operators (Table \ref{tab:assessed_couples_selection_operators}) on the optimization performance.
+The box extends from the lower to upper quartile values of the data, with a line at the median.
+The whiskers extend from the box to 1.5 times the interquartile range.
+Flier points are those past the end of the whiskers.
+The star represents the median.
+The gray box highlights the best options.}
+	\label{fig:operator_selectcoupl_score}
+\end{figure}
+
+\begin{figure*}[t]
+	\begin{center}
+		\noindent\includegraphics[width=39pc,angle=0]{figures/operator_crossover_score.pdf}\\
+	\end{center}
+	\caption{Influence of the chromosome crossover operators (Table \ref{tab:assessed_crossover_operators}) on the optimization performance.
+Same conventions as Fig.
+\ref{fig:operator_selectcoupl_score}.}
+	\label{fig:operator_crossover_score}
+\end{figure*}
+
+\begin{figure}[t]
+	\begin{center}
+		\noindent\includegraphics[width=19pc,angle=0]{figures/operator_mutation_score.pdf}\\
+	\end{center}
+	\caption{Influence of the mutation operators (Table \ref{tab:assessed_mutation_operators}) on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
+	\label{fig:operator_mutation_score}
+\end{figure}
+
+\begin{figure*}[t]
+	\begin{center}
+		\noindent\includegraphics[width=33pc,angle=0]{figures/operator_mutation_score_atmlevel.pdf}\\
 	\end{center}
@@
 The red line represents the score of the sequential calibration and the blue line, the score of the optimization without automatic selection of the pressure levels.
-Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+Same conventions as Fig.
+\ref{fig:operator_selectcoupl_score}.}
 	\label{fig:operator_mutation_score_atmlevel}
@@
 
-\begin{figure*}[htb]
-	\begin{center}
-		\noindent\includegraphics[width=14cm,angle=0]{figures/operator_mutation_score_rhoneamont.pdf}\\
-	\end{center}
-	\caption{Same as Figure \ref{fig:operator_mutation_score_atmlevel}, but for another region in the Swiss Alps (Bottom Rhone valley), with different atmospheric influences.}
+\begin{figure*}[t]
+	\begin{center}
+		\noindent\includegraphics[width=33pc,angle=0]{figures/operator_mutation_score_rhoneamont.pdf}\\
+	\end{center}
+	\caption{Same as Fig. \ref{fig:operator_mutation_score_atmlevel}, but for another region in the Swiss Alps (Bottom Rhone valley), with different atmospheric influences.}
 	\label{fig:operator_mutation_score_rhoneamont}
@@
 
-\begin{figure*}[htb]
-	\begin{center}
-		\noindent\includegraphics[width=14cm,angle=0]{figures/operator_mutation_score_r2.pdf}\\
-	\end{center}
-	\caption{Same as Figure \ref{fig:operator_mutation_score_atmlevel}, but with a second level of analogy on moisture variables.}
+\begin{figure*}[t]
+	\begin{center}
+		\noindent\includegraphics[width=33pc,angle=0]{figures/operator_mutation_score_r2.pdf}\\
+	\end{center}
+	\caption{Same as Fig. \ref{fig:operator_mutation_score_atmlevel}, but with a second level of analogy on moisture variables.}
 	\label{fig:operator_mutation_score_r2}
@@
 
-\begin{figure*}[htb]
-	\begin{center}
-		\noindent\includegraphics[width=14cm,angle=0]{figures/operator_mutation_score_r4.pdf}\\
-	\end{center}
-	\caption{Same as Figure \ref{fig:operator_mutation_score_r2}, but with a preselection on air temperature rather than a fixed calendar window.}
+\begin{figure*}[t]
+	\begin{center}
+		\noindent\includegraphics[width=33pc,angle=0]{figures/operator_mutation_score_r4.pdf}\\
+	\end{center}
+	\caption{Same as Fig. \ref{fig:operator_mutation_score_r2}, but with a preselection on air temperature rather than a fixed calendar window.}
 	\label{fig:operator_mutation_score_r4}
@@
 
-The first analysis was the optimization of the precipitation forecasting over a subcatchment (Binn-Simplon region) in the Swiss Alps (Figure \ref{fig:operator_mutation_score_atmlevel}).
-The optimizer could choose the 2 pressure levels of the atmospheric circulation analogy (method with a single level of analogy).
-The resulting performance score \citep[CRPSS = skill score of the CRPS, see][]{Brown1974} is obviously superior to the one obtained by the sequential calibration (red line on Figure \ref{fig:operator_mutation_score_atmlevel}).
-For most options, it is also slightly better than the results from the optimization without selection of the pressure levels (blue line).
-A clear breakthrough of the performances was not expected, as the former selection of pressure levels results already from intensive comparative work \citep{Bontron2004}.
-This application however demonstrates that, when correctly parametrized, GAs can automatically and successfully choose the pressure levels.
-However, some less relevant optimizations do not match the previous results.
-Through different applications, the automatic selection of the pressure level was shown to significantly increase the difficulty for GAs to converge to a unique solution, ideally the global optimum.
-A difficulty is that the pressure levels are considered within the optimization without continuity between values, and thus the approaches relying on distance in the parameters space, such as the search radius, cannot fully exploit the properties that make them efficient.
-However, even though the results show a certain variability, most of them present very good performance scores, despite different parameters of the AM.
-
-Then, the same optimization was performed, but for another region, sensitive to other meteorological influences (Figure \ref{fig:operator_mutation_score_rhoneamont}), in order to assess eventual dependencies of the operator with the predictand.
-Even though differences can be observed with Figure \ref{fig:operator_mutation_score_atmlevel}, it is globally the same options that perform better.
-
-Next, a second level of analogy was proposed (Figure \ref{fig:operator_mutation_score_r2}) based on moisture variables \citep[see][]{Bontron2004, Horton2016}.
-GAs had to optimize both levels of analogy simultaneously.
-Once again, despite the difficulty to do so, the results were better than the sequential calibration (red line on Figure \ref{fig:operator_mutation_score_r2}).
-And finally, a preselection on air temperature was added instead of the fixed calendar window, as proposed by \cite{BenDaoud2015}.
-The results show generally higher scores (Figure \ref{fig:operator_mutation_score_r4}), demonstrating the success of the optimizer to take advantage of this new degree of freedom, and its capacity to handle optimization of 3 analogy levels jointly.
-Again, the most relevant options are generally the same.
-
-After analysis of the most relevant mutation operators, the following advice can be raised (detailed parametrization are provided in section \ref{sec:recommendations}):
-
-\begin{itemize}
-
-	\item \textit{Non-uniform mutation} \citep{Michalewicz1996}: this operator is good in terms of convergence, mainly when the number of parameters to optimize is rather low.
-The number of required evaluations, however, can be quite substantial.
-The main disadvantage of the non-uniform mutation is the number of parameters it requires, that are difficult to estimate a priori.
-The mutation rate was found to be more important than the others.
-The difficulty is that its optimal value may be case-related.
-
-	\item \textit{Chromosome of adaptive search radius} (new): unlike the previous one, this new operator is very robust, as it requires no option and is auto-adapting.
-It is interesting to notice that the insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).
-If one had to choose a single option for the mutation operator, we would recommend this one, as it was proven effective and needs no parameter.
-
-	\item \textit{Multi-scale mutation} (new): finally, the multi-scale mutation, which also performs pretty well, requires one parameter, the mutation rate.
-However, it can also be difficult to estimate a correct value a priori.
-
-\end{itemize}
-
-In this application, the mutation operator has a leading effect and should be chosen with care.
-It may be wise to perform multiple optimizations and to consider these three operators in parallel in order to obtain results from options that are sometimes either more efficient or more robust.
-It is interesting to note that the three best techniques incorporate a notion of search distance.
-It is likely that this notion is the key to these algorithms, for this application, and allows them to initially explore the parameter domain, and then to converge.
-The search radius in fact directly represents the notion of transition between exploration and exploitation, in our opinion more than a possible evolution of mutation rates.
-
-\subsubsection{Other options}
-
-The analysis of the natural selection operator (Figure \ref{fig:operator_selectnat_score}) reveals a slight preference for the ratio-elitism compared to the tournament selection, but not so significant.
-This operator, or at least the two assessed versions, do not appear to significantly influence the optimization performances.
-
-\begin{figure}[htb]
-	\begin{center}
-		\noindent\includegraphics[width=4cm,angle=0]{figures/operator_selectnat_score.pdf}\\
-	\end{center}
-	\caption{Influence of the natural selection operators on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+\begin{figure}[t]
+	\begin{center}
+		\noindent\includegraphics[width=11pc,angle=0]{figures/operator_selectnat_score.pdf}\\
+	\end{center}
+	\caption{Influence of the natural selection operators on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
 	\label{fig:operator_selectnat_score}
@@
 
-The size of the population ($N$), i.e.
-the number of sets of AM parameters considered, has an effect on the performance of the optimization (Figure \ref{fig:option_taillepop_score}).
-A bigger population leads to better results, but also to significantly longer optimizations.
-Indeed, the required number of evaluation, and thus the required time, is approximately proportional to the population size.
-The optimal size seems to depend on the complexity of the AM to optimize: a more complex AM (ie.
-with more degrees of freedom) requires a bigger population size.
-A rule of thumb based on a limited number of case studies (not shown here) is provided hereafter:
-
-\begin{itemize}
-	\item $N\approx100$ for very simple implementations of the AM (1 level of analogy with 2 pressure levels),
-	\item $N\approx200$ for a slightly more complex AM (1 level of analogy with 4 pressure levels, or 2 level of analogy with less pressure levels),
-	\item $N\approx500$ for significantly more complex AMs (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the moisture analogy).
-\end{itemize}
-
-\begin{figure}[htb]
-	\begin{center}
-		\noindent\includegraphics[width=4cm,angle=0]{figures/option_taillepop_score.pdf}\\
-	\end{center}
-	\caption{Influence of the population size on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+\begin{figure}[t]
+	\begin{center}
+		\noindent\includegraphics[width=11pc,angle=0]{figures/option_taillepop_score.pdf}\\
+	\end{center}
+	\caption{Influence of the population size on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
 	\label{fig:option_taillepop_score}
@@
 
-The influence of the size of the IG (proportion of the total population) selected for mating was also assessed (Figure \ref{fig:option_popratio_score}).
-It does not appear that this parameter is critical to the quality of the optimizations, provided it is not too big.
-A value of 50~\% seems a wise choice.
-
-\begin{figure}[htb]
-	\begin{center}
-		\noindent\includegraphics[width=4cm,angle=0]{figures/option_popratio_score.pdf}\\
-	\end{center}
-	\caption{Influence of the intermediate population (IG) ratio on the optimization performance. Same conventions as Figure \ref{fig:operator_selectcoupl_score}.}
+\begin{figure}[t]
+	\begin{center}
+		\noindent\includegraphics[width=11pc,angle=0]{figures/option_popratio_score.pdf}\\
+	\end{center}
+	\caption{Influence of the intermediate population (IG) ratio on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
 	\label{fig:option_popratio_score}
@@
 
-\section{Recommended parametrization of GAs}
-\label{sec:recommendations}
-
-Optimizations by GAs for AMs of varying complexities were performed with a large number of combinations of operators in order to make recommendations for optimizing the AM. The conclusions are:
-
-\begin{itemize}
-	\item The population size should be in accordance with the complexity of the AM to optimize: from 100 for the simple ones, up to 500 for the most complex AMs.
-
-	\item The value of the ratio for the IG is not so important, and value of 50\% seems quite appropriate.
-
-	\item Ratio-elitism is slightly better than tournaments for the natural selection operator, but it is not decisive.
-
-	\item The performance of the operators for the couples selection perform relatively similarly.
-The roulette wheel weighting and the tournament selection are more efficient in terms of convergence and required number of evaluations.
-
-	\item Most crossover operators have relatively similar performance. Binary-like crossover with two points of intersection are better than others, especially for convergence.
-
-	\item Mutation has a clearly dominant influence.
-Three mutation operators stand out: the non-uniform mutation, the multi-scale mutation, and the chromosome of adaptive search radius.
-The latter is the most robust as it has no controlling parameter.
-
-\end{itemize}
-
-The optimization does not systematically converge to the global optimum (but still often nearby), which is why it is recommended to do several optimizations in parallel in order to compare the results, analyze the convergence, and keep the best.
-It may be wise to consider the three mutation operators in parallel.
-In order to be confident in the optimized AMs, we propose using a set of the following mutation operators:
-
-\begin{itemize}
-	\setlength\itemsep{-4px}
-	\item 1x non-uniform, $p_{mut}=0.05$, $G_{m}=50$, $\omega=0.1$
-	\item 1x non-uniform, $p_{mut}=0.05$, $G_{m}=100$, $\omega=0.1$
-	\item 1x non-uniform, $p_{mut}=0.1$, $G_{m}=100$, $\omega=0.1$
-	\item 1x multi-scale,  $p_{mut}=0.1$
-	\item 2x chromosome of adaptive search radius
-\end{itemize}
-
-\section{Conclusions}
-
-In order to automatically optimize the AM and to get rid of the limitations of the usual sequential calibration, GAs were evaluated.
-Given the large number of existing operators and options, multiple variants were assessed systematically in order to identify which operators are important, and which variants work best for the AM.
-The mutation operator was identified as a key element for this application, and new variants that proved efficient were provided, such as the chromosome of adaptive search radius that is very robust (no control parameter).
-Recommendations were established for a relevant use of GAs for the optimization of AMs.
-
-It is not excluded that another global optimization method or other operators of GAs may perform still better.
-However, the relevance of such an approach has now been proved as it results in parametrization of AMs that are relevant and fully automatically, globally and objectively established.
-A global optimization is the only way to take into account all the dependencies between parameters and levels of analogy.
-
-The global optimization approach allows easily adapting the AM to new regions by potentially taking into account local meteorological influences, and has thus a great potential of use.
-Moreover, it allows exploring automatically datasets in order to extract the most relevant variables.
-It is thus possible to try assessing other predictands, such as the temperature, the limit of snowfall, the occurrence of hail, or wind, while leaving the algorithms select the best variables and the associated parameters.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% ACKNOWLEDGMENTS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-\acknowledgments
-Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of.
-Thanks to Renaud Marty for his fruitful collaboration over the years.
-Thanks to Dominique B\'{e}rod for his support and to Michel Bierlaire for his advices on optimization methods.
-
-Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
-The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
-NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.
-Precipitation time series provided by MeteoSwiss.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% APPENDIXES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% Use \appendix if there is only one appendix.
-%\appendix
-
-% Use \appendix[A], \appendix}[B], if you have multiple appendixes.
-%\appendix[A]
-
-%% Appendix title is necessary! For appendix title:
-%\appendixtitle{}
-
-%%% Appendix section numbering (note, skip \section and begin with \subsection)
-% \subsection{First primary heading}
-
-% \subsubsection{First secondary heading}
-
-% \paragraph{First tertiary heading}
-
-%% Important!
-%\appendcaption{<appendix letter and number>}{<caption>} 
-%must be used for figures and tables in appendixes, e.g.,
-%
-%\begin{figure}
-%\noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
-%\appendcaption{A1}{Caption here.}
-%\end{figure}
-%
-% All appendix figures/tables should be placed in order AFTER the main figures/tables, i.e., tables, appendix tables, figures, appendix figures.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% REFERENCES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Make your BibTeX bibliography by using these commands:
-\bibliographystyle{ametsoc2014}
-% \bibliography{references}
-\bibliography{../_refs/_articles-gas}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% TABLES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Enter tables at the end of the document, before figures.
-%%
-%
-%\begin{table}[t]
-%\caption{This is a sample table caption and table layout.  Enter as many tables as
-%  necessary at the end of your manuscript. Table from Lorenz (1963).}\label{t1}
-%\begin{center}
-%\begin{tabular}{ccccrrcrc}
-%\hline\hline
-%$N$ & $X$ & $Y$ & $Z$\\
-%\hline
-% 0000 & 0000 & 0010 & 0000 \\
-% 0005 & 0004 & 0012 & 0000 \\
-% 0010 & 0009 & 0020 & 0000 \\
-% 0015 & 0016 & 0036 & 0002 \\
-% 0020 & 0030 & 0066 & 0007 \\
-% 0025 & 0054 & 0115 & 0024 \\
-%\hline
-%\end{tabular}
-%\end{center}
-%\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% FIGURES
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Enter figures at the end of the document, after tables.
-%%
-%
-%\begin{figure}[t]
-%  \noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
-%  \caption{Enter the caption for your figure here.  Repeat as
-%  necessary for each of your figures. Figure from \protect\cite{Knutti2008}.}\label{f1}
-%\end{figure}
-
 \end{document}

### 2016-02-15 Genetic algorithms - Journal of Climate/template.tex
Michel's corrections.

@@
 %\documentclass[twocol]{ametsoc}
+
+\usepackage{gensymb}
 
@@
 
-The purpose of this paper is not to present in details the AM and its different parameterizations, which can be found in \citet{Horton2016} or \citet{BenDaoud2015}.
-The concepts one needs to understand here are the following: the AM consists in searching a certain number of past situations in a meteorological archive (typically reanalysis datasets) that are the most similar, according to an analogy criteria, and to extract the observed values of the local weather variable of interest from another archive (typically local or basin averaged time series) in order to build the conditional empirical distribution considered as the probabilistic forecast for the target day.
-Predictors can be varied: for example the geopotential height at different pressure levels on different temporal windows (time of observation).
-The method is usually made of several levels of analogy, leading to successive subsampling on predictors of different nature (eg.
-atmospheric circulation, moisture variables, vertical motion, and air temperature).
-
 Even though the method is rather simple compared to numerical weather prediction (NWP) models, it contains a certain number of parameters one needs to determine, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criteria itself, and finally the number of analogue situations to keep at each subsampling level.
@@
 \citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of the AM and concludes that one needs to be an expert to have a sense of their respective influence, sensitivity and nonlinear interactions.
-\citet{BenDaoud2010}, when calibrating the AM, also stated that ''\textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously }''.
+\citet{BenDaoud2010}, when calibrating the AM, also stated that ''\textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously}''.
 
@@
 This requires intensive and systematic comparisons of operators and options in order to identify the key factors leading the optimization and the respective sensitivity of the options.
-Such analyses are presented here and will result in recommendations for the use of GAs when applied to AMs.
+Such analyses are presented here by application to the upper Rho\^{o}ne catchment in Switzerland, and will result in recommendations for the use of GAs when applied to AMs.
 The demonstration of the benefit brought by such an approach on a specific case study is the topic of \citet{Horton2016b}.
 
-We will begin by presenting the concepts of GAs as well as the assessed operators (operations performed on the AM parameters; see section \ref{sec:gas}).
-The comparative analyses of the operators and their results are presented in section \ref{sec:assessment}, which lead us to the recommendations in section \ref{sec:recommendations}.
+We will begin by presenting the basics of the AM (Sect.
+\ref{sec:am}) and the concepts of GAs as well as the assessed operators (operations performed on the AM parameters; see Sect.
+\ref{sec:gas}).
+The comparative analyses of the operators and their results are presented in Sect.
+\ref{sec:assessment}, which lead us to the recommendations in Sect.
+\ref{sec:recommendations}.
+
+\section{The Analogue Method}
+\label{sec:am}
+
+The purpose of this paper is not to present in details the AM and its different parameterizations, which can be found in \citet{Horton2016} or \citet{BenDaoud2015}.
+The concepts one needs to understand here are the following: the AM consists in searching a certain number of past situations in a meteorological archive (typically reanalysis datasets) that are the most similar, according to an analogy criteria, and to extract the observed values of the local weather variable of interest from another archive (typically local or basin averaged time series) in order to build the conditional empirical distribution considered as the probabilistic forecast for the target day.
+Predictors can be varied: for example the geopotential height at different pressure levels on different temporal windows (time of observation).
+The method is usually made of several levels of analogy, leading to successive subsampling on predictors of different nature (eg.
+atmospheric circulation, moisture variables, vertical motion, and air temperature).
+
+There are mainly 2 parameterizations that are most often used for precipitation forecasting: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
+
+The method based on the analogy of the synoptic circulation consists in the following steps: the similarity of the atmospheric circulation of a target date with every day of the archive is assessed by processing the S1 criteria \citep{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, on 2 different the geopotential heights (e.g.
+500 and 1000~hPa) and over a certain spatial window.
+To cope with seasonal effects, candidate dates are extracted within a period of 4 months centered around the target date, for every year of the archive.
+The $n_{1}$ (parameter to calibrate) dates with the lowest values of S1 are considered as analogues to the target day.
+Then, the daily observed precipitation amount of the $n_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
+
+The other current parametrization adds a second level of analogy on moisture variables, more specifically on a moisture index made of the product of the precipitable water with the relative humidity at a certain pressure level \citep[e.g.
+850~hPa, see][]{Bontron2004}.
+When adding a second level of analogy, $n_{2}$ dates are subsampled in the $n_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
+
+The score that is most often used to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
+It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$.
+The better the prediction, the smaller the score.
+The mean CRPS of a prediction series of length $l$ can be written:
+
+\begin{equation}
+\label{eq:CRPS}
+CRPS = \frac{1}{l} \sum_{i=1}^{l} \left(  \int_{-\infty}^{+\infty} \left[ F_{i}(y)-H_{i}(y-y_{i}^{0})\right]^{2} dy \right) 
+\end{equation}
+where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value 1 otherwise.
+The mean CRPS is averaged on the calibration, respectively the validation periods, on all days.
+
+In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution of daily precipitation as the reference.
+The CRPSS (\textit{Continuous Ranked Probability Skill Score}) is thus defined as following:
+
+\begin{equation}
+\label{eq:CRPSS}
+CRPSS = \frac{CRPS-CRPS_{r}}{CRPS_{p}-CRPS_{r}} = 1-\frac{CRPS}{CRPS_{r}}
+\end{equation}
+where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect prediction (which implies $CRPS_{p}~=~0$).
+A better prediction is characterized by an increase in CRPSS.
 
@@
 
-Genetic Algorithms (GAs) come from the world of stochastic optimization, more specifically from metaheuristic approaches.
+Genetic Algorithms \citep[GAs,][]{Holland1992b, Goldberg1989} come from the world of stochastic optimization, more specifically from metaheuristic approaches.
 These are stochastic iterative algorithms that behave like search algorithms by exploiting the characteristics of a problem and are particularly suitable for complex parameter spaces.
@@
 GAs are part of the family of Evolutionary Algorithms \citep{Back1993b, Schwefel1993}, inspired by some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
-GAs are the most used technique among Evolutionary Algorithms \citep{Back1993b}, and they are constantly improving \citep{Haupt2004}.
-However, with time, the different methods of Evolutionary Algorithms tend to be similar and share many commonalities \citep{Back1996b, Haupt2004}.
-
-The method was originally developed by \citet{Holland1992b} and popularized by \citet{Goldberg1989}.
 Unlike a linear or local optimization, GAs seek the global optimum on a complex surface, theoretically without restriction, but with no guarantee to reach it.
@@
 number of analogues to select, from 1 to 40), or continuous.
+For example, a chromosome may looks like:
+
+\begin{equation}
+[p_{i,j}, h_{i,j}, xw_{i,j}, xe_{i,j}, ys_{i,j}, yn_{i,j}, p_{i,j+1}, h_{i,j+1}, ..., n_{i}, ... p_{i+1,j}, h_{i+1,j}, ..., n_{i+1}, ...]
+\end{equation}
+where, for the level of analogy $i$ and the predictor number $j$, $p_{i,j}$ is the pressure level, $h_{i,j}$ is the hour of the day, $xw_{i,j}$ and $xe_{i,j}$ are the western and eastern longitudes of the spatial window, $ys_{i,j}$ and $yn_{i,j}$ are its southerly and northerly latitudes, and $n_{i,j}$ is the number of analogues.
+A chromosome for the simple AM on the circulation (Sect.
+\ref{sec:am}) only may be: $[500~hPa, 12~h, -2.5\degree, 15\degree, 40\degree, 55\degree, 1000~hPa, 24~h, 0\degree, 15\degree, 42.5\degree, 47.5\degree, 28]$
+
 The floating-point representation \citep[instead of the canonical binary, see][]{Goldberg1989, Goldberg1990a, Holland1992b} of the genes was considered, as it was found more suited in multiple applications \citep{Michalewicz1996, Herrera1998a, Haupt2004, Back1996b, Gaffney2010a}.
@@
 Its optimum configuration depends on the size of the chromosomes, of the properties of the objective function, and of the population size \citep{Back1992b}.
-This operator was implemented according to equation \ref{equation_mutation_uniformvariable}.
+This operator was implemented according to:
 	\begin{equation}
@@
 
-As the assessment (calculation of the objective function) of each member of the population of a generation is completely independent, it was performed in parallel on different processors of a computer, as suggested by \citet{Alliot2005}.
+As the assessment (calculation of the objective function) of each member of the population of a generation is completely independent, it was performed in parallel on different processors of a computer.
 In order to perform optimizations for multiple time series, the use of a cluster is a necessity, which our code allows.
@@
 
-Values of the mutation rate varies broadly between studies: from 0.001 \citep{DeJong1975a} to 0.2 \citep{Haupt2004}.
+Values of the mutation rate ($p$) varies broadly between studies: from 0.001 \citep{DeJong1975a} to 0.2 \citep{Haupt2004}.
 \citet{Back1996b} showed that mutation rates higher than the usual ranges are more optimal at the beginning of the optimization, allowing further exploration.
@@
 Having identified the leading role of the mutation operator, the next sensitivity analysis focused on it.
-Each of the 10 different implementations (see section \ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Table \ref{tab:assessed_mutation_operators}), bringing the number of variations up to 109.
+Each of the 10 different implementations (see Sect.
+\ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Table \ref{tab:assessed_mutation_operators}), bringing the number of variations up to 109.
 Some optimizations without any mutation were also performed as a reference.
@@
 The details of the analysis \citep[see][]{Horton2012a} show that the other reproduction operators seem of secondary importance.
-This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction, as well as other authors (see section \ref{sec:gas}.\ref{sec:gas:mutation}).
+This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction, as well as other authors (see Sect.
+\ref{sec:gas}.\ref{sec:gas:mutation}).
 
@@
 The optimizer could choose the 2 pressure levels of the atmospheric circulation analogy (method with a single level of analogy).
-The resulting performance score \citep[CRPSS = skill score of the CRPS, see][]{Brown1974} is obviously superior to the one obtained by the sequential calibration (red line on Fig.
+The resulting CRPSS performance score (Sect.
+\ref{sec:am}) is obviously superior to the one obtained by the sequential calibration (red line on Fig.
 \ref{fig:operator_mutation_score_atmlevel}).
@@
 
-After analysis of the most relevant mutation operators, the following advice can be raised (detailed parametrization are provided in section \ref{sec:recommendations}):
+After analysis of the most relevant mutation operators, the following advice can be raised (detailed parametrization are provided in Sect. \ref{sec:recommendations}):
 
@@
 	\end{center}
-	\caption{Influence of the couples selection operators (Table \ref{tab:assessed_couples_selection_operators}) on the optimization performance.
+	\caption{Influence of the couples selection operators (Table \ref{tab:assessed_couples_selection_operators}) on the optimization performance (improvement of the score).
 The box extends from the lower to upper quartile values of the data, with a line at the median.
@@
 	\end{center}
-	\caption{Influence of the chromosome crossover operators (Table \ref{tab:assessed_crossover_operators}) on the optimization performance.
+	\caption{Influence of the chromosome crossover operators (Table \ref{tab:assessed_crossover_operators}) on the optimization performance (improvement of the score).
 Same conventions as Fig.
@@
 	\end{center}
-	\caption{Same as Fig. \ref{fig:operator_mutation_score_atmlevel}, but for another region in the Swiss Alps (Bottom Rhone valley), with different atmospheric influences.}
+	\caption{Same as Fig. \ref{fig:operator_mutation_score_atmlevel}, but for another region in the Swiss Alps, with different atmospheric influences.}
 	\label{fig:operator_mutation_score_rhoneamont}

### 2016-02-15 Genetic algorithms - Journal of Climate/template.tex
Preparing for submission.

@@
 This calibration approach has strong limitations: it is made of successive steps and thus cannot handle parameters dependencies, and it cannot automatically optimize some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared.
-In order to surpass these limitations, a global optimization technique was assessed, namely genetic algorithms, which can optimize jointly all parameters of the method and get closer to a global optimum by taking into account the parameters dependencies.
+In order to surpass these limitations, a global optimization technique was assessed, namely Genetic Algorithms, which can optimize jointly all parameters of the method and get closer to a global optimum by taking into account the parameters dependencies.
 Moreover, it can choose objectively parameters that were previously manually assessed, and can take into account new degrees of freedom that were unthinkable before.
 These kind of optimization techniques need however to be tailored to the problem to solve.
-Multiple combinations of algorithms had to be assessed, and even new operators were developed, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of Genetic Algorithms to optimize the analogue method.
+Multiple combinations of algorithms had to be assessed, and even new operators were developed, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of Genetic Algorithms to optimize the Analogue Method.
 These recommendations are the main outcome of this work.
-It opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.
+It opens new perspective for the improvement of the Analogue Method, and its application to new regions or to new predictands.
 }
@@
 
-The AM needs to be adapted to every new region considered, because the leading meteorological influences may be specific per region.
+The AM needs to be adapted to every new region considered, because the leading meteorological influences may be location specific.
 Even the selection of the pressure levels and the temporal windows should be reconsidered, when not the predictor variable itself.
-For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012a} found it useless in an Alpine environment, because the vertical motion, which is mainly controlled by orographic effects, was already well related to the atmospheric circulation itself.
 
@@
 Thus, optimizing the method with the sequential technique is laborious, as many combinations of predictors (variables, pressure levels, temporal windows) have to be assessed.
-Moreover, proceeding to the optimization sequentially ignores potential dependencies between the parameters of the method, may they be within a single level of analogy or between them.
-However, such dependencies between them cannot be excluded, which could lead to another parametrization if calibrated together.
-However, simultaneous calibration of all parameters has never been undertaken so far.
+Moreover, proceeding to the optimization sequentially ignores potential dependencies between the parameters of the method, may they be within a single level of analogy or between them, which could lead to another parametrization if the parameters were calibrated together.
+Simultaneous calibration of all parameters has never been undertaken so far.
 Thus, due to the sequential approach, the risk of ending in a local optimum is high and can not be avoided.
@@
 This requires intensive and systematic comparisons of operators and options in order to identify the key factors leading the optimization and the respective sensitivity of the options.
-Such analyses are presented here by application to the upper Rho\^{o}ne catchment in Switzerland, and will result in recommendations for the use of GAs when applied to AMs.
+Such analyses are presented here by application to the upper Rh\^{o}ne catchment in Switzerland, and will result in recommendations for the use of GAs when applied to AMs.
 The demonstration of the benefit brought by such an approach on a specific case study is the topic of \citet{Horton2016b}.
@@
 \begin{equation}
-[p_{i,j}, h_{i,j}, xw_{i,j}, xe_{i,j}, ys_{i,j}, yn_{i,j}, p_{i,j+1}, h_{i,j+1}, ..., n_{i}, ... p_{i+1,j}, h_{i+1,j}, ..., n_{i+1}, ...]
-\end{equation}
-where, for the level of analogy $i$ and the predictor number $j$, $p_{i,j}$ is the pressure level, $h_{i,j}$ is the hour of the day, $xw_{i,j}$ and $xe_{i,j}$ are the western and eastern longitudes of the spatial window, $ys_{i,j}$ and $yn_{i,j}$ are its southerly and northerly latitudes, and $n_{i,j}$ is the number of analogues.
-A chromosome for the simple AM on the circulation (Sect.
-\ref{sec:am}) only may be: $[500~hPa, 12~h, -2.5\degree, 15\degree, 40\degree, 55\degree, 1000~hPa, 24~h, 0\degree, 15\degree, 42.5\degree, 47.5\degree, 28]$
+[p_{i,j}, h_{i,j}, \lambda w_{i,j}, \lambda e_{i,j}, \varphi s_{i,j}, \varphi n_{i,j}, p_{i,j+1}, h_{i,j+1}, ..., n_{i}, ... p_{i+1,j}, h_{i+1,j}, ..., n_{i+1}, ...]
+\end{equation}
+where, for the level of analogy $i$ and the predictor number $j$, $p_{i,j}$ is the pressure level, $h_{i,j}$ is the temporal window, $\lambda w_{i,j}$ and $\lambda e_{i,j}$ are the western and eastern longitudes of the spatial window, $\varphi s_{i,j}$ and $\varphi n_{i,j}$ are its southerly and northerly latitudes, and $n_{i,j}$ is the number of analogues.
+A chromosome for the simple AM on the atmospheric circulation only (Sect.
+\ref{sec:am}) may be: $[500~hPa, 12~h, -2.5\degree, 15\degree, 40\degree, 55\degree, 1000~hPa, 24~h, 0\degree, 15\degree, 42.5\degree, 47.5\degree, 28]$
 
@@
 	\item From this IG, couples are formed according to given rules.
-	\item These couples proceed to reproduction, or chromosome crossover, in order to mix their genes (parameters) according to the selected operator version.
+	\item These couples proceed to reproduction, or chromosome crossover, to mix their genes (parameters) according to the selected operator version.
 New children are generated in order to refill the IG back to $N$ individuals.
@@
 \begin{itemize}
-	\item Rank pairing: individuals are gathered in pairs according to their rank (based on the performance scores).
-Consecutive ranks are put together (odd rows are associated with even rows).
-This approach is easy to achieve, but does not look like a natural process.
+	\item Rank pairing: individuals are gathered in pairs according to their rank (based on the performance scores). Consecutive ranks are put together (odd rows are associated with even rows).
 
@@
 Each individual is associated with a sector of the wheel with a certain opening angle, which is its probability of selection.
-The probability assigned to the individuals is proportional to their fitness (objective function), so that the most adapted individuals have the greatest probability of reproduction.
+The probability ($p_{n}$) assigned to the individuals is proportional to their fitness (objective function), so that the most adapted individuals have the greatest probability of reproduction.
 There are two techniques for weighting the individuals of the IG:
@@
 
-	\textit{Roulette wheel weighting on fitness}: the selection probability is calculated based on the value of the objective function.
-The probability $p_{n}$ of each individual is calculated by the equation \ref{equation_mating_score_weighting}:
+	\textit{Roulette wheel weighting on fitness}: the selection probability is calculated based on the value of the objective function:
 	\begin{equation}
@@
 To reproduce the behaviour present in the original algorithms, which introduces new information, \citet{Haupt2004} propose an operator that combines standard crossover with an interpolation approach.
-The genes located after a crossover point are exchanged, but the gene located at the intersection is modified as follows (equation \ref{equation_mating_as_binary}):
+The genes located after a crossover point are exchanged, but the gene located at the intersection is modified according to:
 	\begin{equation}
@@
 
-	\item Blending method \citep{Radcliffe1991a}: in this approach, instead of exchanging the genes in between the chromosomes after one or multiple crossover points, these are combined by linear combination (equation \ref{equation_mating_blending_method}).
+	\item Blending method \citep{Radcliffe1991a}: in this approach, instead of exchanging the genes in between the chromosomes after one or multiple crossover points, these are combined by linear combination (Eq.
+\ref{equation_mating_blending_method}).
 The genes of the parents are blended together using a random value ($\beta$) that can be unique for the whole chromosome, or that can change for every gene.
@@
 	\item Linear crossover \citep{Wright1991a}: in order to allow the genes to take values outside the interval defined by the parents, a method of extrapolation is necessary.
-Linear crossover introduces such an approach, and produces three children from two parents, following equation \ref{equation_mating_linear_crossover}.
+Linear crossover introduces such an approach, and produces three children from two parents, following Eq.
+\ref{equation_mating_linear_crossover}.
 Less couples are required in order to fill up the population.
@@
 
-	\item Linear interpolation: unlike previous techniques, this technique does not rely on crossover points, but on a linear interpolation on every gene of the couple (equation \ref{equation_mating_linear_interpolation}).
+	\item Linear interpolation: unlike previous techniques, this technique does not rely on crossover points, but on a linear interpolation on every gene of the couple (Eq.
+\ref{equation_mating_linear_interpolation}).
 	\begin{equation}
@@
 	\item Variable normal mutation (new): with the same logic as the variable uniform mutation, a mutation operator was tested using a normal distribution with a variable mutation rate and standard deviation.
-The mutation rate is calculated with equation \ref{equation_mutation_uniformvariable}.
+The mutation rate is calculated with Eq.
+\ref{equation_mutation_uniformvariable}.
 On the same principle, the standard deviation decreases linearly over the generations:
@@
 The idea was to test an approach that combines both exploration and exploitation during the whole optimization.
-Thus, the search radius $r_{a}$ of equation \ref{equation_mutation_rayon_adaptatif} was considered as a random value for each individual, but restricted to 4 equiprobable values: 1, 0.5, 0.1, 0.02, which range from full exploration to fine exploitation.
+Thus, the search radius $r_{a}$ of Eq.
+\ref{equation_mutation_rayon_adaptatif} was considered as a random value for each individual, but restricted to 4 equiprobable values: 1, 0.5, 0.1, 0.02, which range from full exploration to fine exploitation.
 The only external parameter is the mutation rate which is fixed.
@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{figures/figure_structure_gas.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{figures/fig01.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{figures/gas_evolution_good.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{figures/fig02.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{figures/gas_evolution_bad.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{figures/fig03.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{figures/operator_selectcoupl_score.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{figures/fig04.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=39pc,angle=0]{figures/operator_crossover_score.pdf}\\
+		\noindent\includegraphics[width=39pc,angle=0]{figures/fig05.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{figures/operator_mutation_score.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{figures/fig06.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=33pc,angle=0]{figures/operator_mutation_score_atmlevel.pdf}\\
+		\noindent\includegraphics[width=33pc,angle=0]{figures/fig07.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=33pc,angle=0]{figures/operator_mutation_score_rhoneamont.pdf}\\
+		\noindent\includegraphics[width=33pc,angle=0]{figures/fig08.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=33pc,angle=0]{figures/operator_mutation_score_r2.pdf}\\
+		\noindent\includegraphics[width=33pc,angle=0]{figures/fig09.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=33pc,angle=0]{figures/operator_mutation_score_r4.pdf}\\
+		\noindent\includegraphics[width=33pc,angle=0]{figures/fig10.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=11pc,angle=0]{figures/operator_selectnat_score.pdf}\\
+		\noindent\includegraphics[width=11pc,angle=0]{figures/fig11.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=11pc,angle=0]{figures/option_taillepop_score.pdf}\\
+		\noindent\includegraphics[width=11pc,angle=0]{figures/fig12.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=11pc,angle=0]{figures/option_popratio_score.pdf}\\
+		\noindent\includegraphics[width=11pc,angle=0]{figures/fig13.pdf}\\
 	\end{center}

### 2016-02-15 Genetic algorithms - Journal of Climate/template.tex
Preparing for submission.

@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{figures/fig01.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{fig01.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{figures/fig02.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{fig02.pdf}\\
 	\end{center}
 	\caption{Evolution of the score of the best individuals over generations for the 10 optimizations processed for a given parametrization.
-The green line (bottom) represents the score of the sequential approach and the blue one (top), the supposed global optimum.}
+The continuous bottom line represents the score of the sequential approach and the dashed one (top), the supposed global optimum.}
 	\label{fig:gas_evolution_good}
@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{figures/fig03.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{fig03.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{figures/fig04.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{fig04.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=39pc,angle=0]{figures/fig05.pdf}\\
+		\noindent\includegraphics[width=39pc,angle=0]{fig05.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{figures/fig06.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{fig06.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=33pc,angle=0]{figures/fig07.pdf}\\
+		\noindent\includegraphics[width=33pc,angle=0]{fig07.pdf}\\
 	\end{center}
@@
 The predictand is precipitation over a subcatchment in the Swiss Alps (Binn-Simplon region).
-The red line represents the score of the sequential calibration and the blue line, the score of the optimization without automatic selection of the pressure levels.
+The continuous bottom line represents the score of the sequential calibration and the dashed superior line, the score of the optimization without automatic selection of the pressure levels.
 Same conventions as Fig.
@@
 	\begin{center}
-		\noindent\includegraphics[width=33pc,angle=0]{figures/fig08.pdf}\\
+		\noindent\includegraphics[width=33pc,angle=0]{fig08.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=33pc,angle=0]{figures/fig09.pdf}\\
+		\noindent\includegraphics[width=33pc,angle=0]{fig09.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=33pc,angle=0]{figures/fig10.pdf}\\
+		\noindent\includegraphics[width=33pc,angle=0]{fig10.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=11pc,angle=0]{figures/fig11.pdf}\\
+		\noindent\includegraphics[width=11pc,angle=0]{fig11.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=11pc,angle=0]{figures/fig12.pdf}\\
+		\noindent\includegraphics[width=11pc,angle=0]{fig12.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=11pc,angle=0]{figures/fig13.pdf}\\
+		\noindent\includegraphics[width=11pc,angle=0]{fig13.pdf}\\
 	\end{center}

### 2016-04-26 Moving temporal window - HESS/template.tex
Corrections from Charles.

@@
 \affil[1]{University of Lausanne, Lausanne, Switzerland}
-\affil[2]{Terranum, Lausanne, Switzerland}
+\affil[2]{Institute of Geography \& Oeschger Centre for Climate Change Research, University of Bern, Bern, Switzerland}
 \affil[3]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}
@@
 
-The search for candidate situations, for a given target day, is usually undertaken by comparing the state of the atmosphere at fixed hours of the day.
+The search for candidate situations, for a given target day, is usually undertaken by comparing the state of the atmosphere at fixed hours of the day, for both the target day and the candidate analogues.
 The constraint being the use of daily time series, due to the length of available archives they provide.
@@
 
-The STW resulted in a better analogy of the atmospheric circulation, with improved values of the analogy criteria on the whole distribution of analogue dates.
-The improvement was found to grow with the analogue ranks due to an accumulation of more similar situations in selection.
+The STW resulted in a better analogy in terms of the atmospheric circulation, with improved values of the analogy criteria on the whole distribution of analogue dates.
+The improvement was found to grow with the analogue ranks due to an accumulation of more similar situations in the selection.
 Moreover, the improvement is even more important for days with heavy precipitation events, which are generally related to more dynamic atmospheric situations, where timing is more specific.
 
-A seasonal effect has also been identified, with larger improvements in winter than in summer, supposedly due to the stronger effect of the diurnal cycle in summer, which favors predictors at the same hour.
+A seasonal effect has also been identified, with larger improvements in winter than in summer, supposedly due to the stronger effect of the diurnal cycle in summer, which favors predictors at the same hour for target and analogues.
 
@@
 
-Attempts to reconstruct longer precipitation series of running 24~h-totals by means of simple methods failed.
-It empathized the need to use time series with an accurate chronology.
-These should be available in a near future, either by means of growing observed archives, or by the establishment of precipitation reanalysis through regional modeling.
+However, attempts to reconstruct longer precipitation series of running 24~h-totals by means of simple methods failed.
+It emphasized the need to use time series with an appropriate chronology.
+These should be available in a near future, either by means of growing observed archives, or by the establishment of precipitation reanalyses through regional modeling.
 Then, the use of a STW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.
@@
 
-The first method is based on the analogy of the atmospheric circulation \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005, Marty2012}.
-When searching analogue situations for a target day, it starts by a preselection step, which is a selection of the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects.
-Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the S1 criteria \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
-The considered pressure levels are 500~hPa (Z500) and 1000~hPa (Z1000).
-The $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day, $N_{1}$ being a parameter to calibrate.
+The first method is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005, Marty2012}.
+Searching analogue situations for a target day starts by a preselection step of the potential candidate for analogy.
+Here, it has been limited to the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects.
+Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the S1 criteria \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window and at certain hours.
+
+In fact, the predictand is not an instantaneous value, but often an accumulation over a certain time period (eg.
+24 h for rainfall, taken from 6-30 h UTC).
+Therefore, the meteorological situation generating this accumulated rainfall is not instantaneous either, but is a continuous transition between changing circulation patterns.
+Thus, the observed predictors fields are considered at different time of the day, and at different heights.
+In our case, the geopotential height is considered at 1000~hPa (Z1000) at 12~h~UTC and 500~hPa (Z500) at 24~h~UTC.
+The selection of the observation time of the predictor was found by \citet{Bontron2004} to have a significant influence.
+Moreover, due to inter-correlation, selecting the optimal 2 pressure levels at 2 hours is not equivalent to combining the best time of both levels individually.
+
+Then, $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day, $N_{1}$ being a parameter to calibrate.
 Then, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
@@
 The mean CRPS is averaged on the calibration, respectively the validation periods, on all days.
-\citet{Bontron2004} proposed a decomposition of this score into a sharpness and an accuracy terms.
+\citet{Bontron2004} proposed a decomposition of this score interpreted into a sharpness and an accuracy terms.
 
@@
 
-The AM is usually implemented with a daily time step, due to the availability of long precipitation archives that have no equivalent to a finer resolution.
+The AM is usually implemented with a daily time step, due to the availability of long precipitation archives that have no equivalent at a finer resolution.
 Therefore, the analogue situations are assessed on the basis of a daily time step, by comparing predictors at fixed hours of the day, otherwise one would not know what precipitation values to assign to them.
-However, it can be expected that the analogy of the synoptic situations do not occur systematically at the same time of the day, and that better candidates can be found at a different hour.
+However, it can be expected that the analogy of the synoptic situations do not occur systematically at the same time of the day, and that better candidates can be found by shifting to a different hour.
 On this assumption, a sliding time window (STW) was introduced to allow searching for candidates at different hours of the day.
@@
 In order to assess this potential improvement of the prediction, precipitation data with a resolution of 10 minutes, on a respectable archive length, was used (section \ref{sec:data}).
-It was then aggregated in the form of 24~h-totals, but at a 6-hourly time step, by means of a moving average (section \ref{sec:method}).
+It was then aggregated in the form of 24~h-totals, but starting at different 6-hourly time step, by means of a moving average (section \ref{sec:method}).
 
@@
 Then, sometimes one just does not need finer resolution than the daily time step.
-Finally, when using a reconstructed precipitation archive, the errors in intra-day precipitation distributions have a lesser impact.
+Finally, when using a reconstructed precipitation archive, the errors in intra-day precipitation distributions have a lesser impact over 24~h daily totals.
 
@@
 The study area is the upper Rh\^{o}ne catchment in Switzerland \cite[see also][]{Horton2012a}.
-Due to the low density of weather stations with high temporal resolution and long archives, no aggregated rainfall was processed.
+Due to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed.
 The time series (on the period 1982-2007) come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle (Figure \ref{fig:map}), which are subject to various meteorological influences \citep{Horton2012}.
@@
 
-Logic suggests \textit{a priori} that only one situation (the best) is selected per candidate day. An exclusion of the same dates was tested in two different ways: (1)
-by excluding the worse analogues in a period of $\pm$ 24~h, and (2) by excluding the worse analogues with the same date.
-After several tests, it turned out that no restrictions led to better skills, and this on a significant and recurring basis.
-Thus, no constraint was further used.
+Based on some preliminary tests (not shown), no constraint was added in order to restrict the selection of multiple analogues within the same candidate dates.
 
@@
 The precipitation target remains at before, that is centered on 18~h~UTC (6~h~UTC to 6~h~UTC the next day).
-The shapes of the distributions of the conventional approach and the STW are similar, but the values of the analogy criteria are now reduced, therefore better.
+The shapes of the distributions of the conventional approach and the STW are similar, but the values of the analogy criteria are now reduced (shifted to the left), and therefore better.
 An increase in the difference between a fixed window and a sliding window is identifiable, which means that the last analogues are further improved.
@@
 This increasing trend with the analogue rank can be explained by the accumulation of better analogues in the distribution.
-The minimum improvement starts from 0 and reaches 2-3\%, meaning that the criteria has been improved on most analogues for every day of the calibration period.
+The minimum improvement starts from 0 and reaches 2-3\%, meaning that the criteria have been improved on most analogues for every day of the calibration period.
 All other stations have a similar improvement of the S1 criteria, both in terms of distribution shape and amplitude.
@@
 Conversely, dynamic situations, such as weather disturbances, have a well marked temporal evolution.
-Indeed, the position of the driving elements such as the low-pressure area and the fronts change significantly during a day.
-We can therefore expect to improve particularly these situations with a higher dynamism when introducing a STW, as better matches to the target situation may be found.
+Indeed, the position of the driving elements such as the low-pressure center and the fronts change significantly during a day.
+We can therefore expect to improve more significantly these situations with a higher dynamism when introducing a STW, as better matches to the target situation may be found.
 
@@
 A basic assumption is considered here, which stipulates that the more a day is rainy, the more dynamic the situation is.
-The results of this analysis are summarized in Figure \ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for days with precipitation between two thresholds.
-The number of analogues being reduced, the curves are not as smooth as in previous analyzes.
+The results of this analysis are summarized in Figure \ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for days with precipitation (organized into classes) between two thresholds.
+The number of cases per class being reduced, the curves are not as smooth as in previous analyzes.
 It is nevertheless clear that the improvement tends to increase on days with higher precipitation.
@@
 One hypothesis is that the diurnal effects of the summer months have an influence on the atmospheric circulation, at least in the lower layers.
-This effect is based on the daily cycle and good analogues for the same hours are already selected.
+This effect is based on the daily cycle and good analogues are essentially found for the same hours or time windows.
 
@@
 
-When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the candidates situations are not more numerous, as they are subsampled in the previously $N_{1}$ selected analogues, but the dates may have changed.
-In contrast to earlier, both a reduction and an increase of the RMSE criterion values are possible.
-Figure \ref{fig:changes_RMSE} shows an almost insignificant improvement of the RMSE values.
+When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidates situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogues, but their dates may have changed.
+In contrast to earlier, both a reduction or an increase of the RMSE analogy criterion values are possible.
+Indeed, Figure \ref{fig:changes_RMSE} shows an almost insignificant improvement of the RMSE values.
 Unlike for the first level of analogy, the relative improvement of the RMSE values are distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
@@
 It means that after the selection of the analogues situations in terms of the synoptic circulation, the new candidate dates do not allow to find better analogues in terms of moisture.
-However, the selected dates have changed in the first level of analogy, and thus also in the final selection, which can potentially improve the performance scores.
+However, the selected dates have changed in the first level of analogy, and thus also in the final selection, which can potentially improve the performance scores on the predictand.
 
@@
 
-\subsection{Improvement by precipitation threshold}
+\subsection{Improvement by precipitation classes}
 \label{sec:improvement_CRPSS_precip_threshold}
@@
 
-The previous assessment of the performance improvement was established with the original parameters.
+The previous assessment of the performance improvement was established with the original parameters optimized with a fixed time window.
 However, one can assume that the introduction of the STW may change the optimum of some parameters.
-The calibration has then been performed again.
+The calibration has then been reprocessed.
 
@@
 The number of analogues of the first analogy level of the 2Z-2MI method even reached three times its previous value for the Visp station.
+It seems as if the method perceive the increase in the archive length and diversity by allowing to extract more analogues.
 As we saw in Figure \ref{fig:changes_S1}, the improvement of the S1 criteria grows along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions.
@@
 The values of the CRPSS scores for both methods (Table \ref{table:CRPSS_recalibration}) have significantly increased after recalibration.
-With the introduction of the STW, the performance loss related to the reduction of the archive length is retrieved.
+With the introduction of the STW, the performance loss related to the reduction of the archive length is compensated.
 
@@
 The STW does not allow to improve the sharpness, but the improvement in accuracy is significant, and this especially for the days with heavy precipitation.
-In terms of the predicted precipitation distribution, it means that the median of the prediction is closer to the observed values, but the distribution is not more condensed than previously.
+In terms of the predicted precipitation distribution, it means that the median of the prediction is closer to the observed values, while the distribution is not more condensed than previously.
 
@@
 As demonstrated in the previous section, the performance improvement brought by the STW is lost when using a simplistic precipitation time series.
-In order to get closer to the chronology of the accurate precipitation, the reconstruction procedure must rely on some informative variable.
+In order to get closer to the chronology of the actual precipitation, the reconstruction procedure must rely on some informative variable.
 Data from the NCEP/NCAR reanalysis 1 (section \ref{sec:data}) was used in this perspective, despite their rough resolution.
@@
 Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the reconstituted series using the proxy of precipitable water at the optimal point (Table \ref{table:proxy_correlations}).
-A slight improvement can be obtained compared to the proportional distribution method, but it is still relatively small, and most of the benefit of the STW is lost.
+A slight improvement can be obtained compared to the proportional distribution method, but it is still relatively small, and most of the benefit of the STW is again lost.
 
@@
 The STW is profitable, provided that the precipitation series are close to the observed one.
-Without precipitation series with an accurate sub-daily chronology, the introduction of a STW is not appropriate.
+Without precipitation series with an accurate sub-daily chronology, the introduction of a STW remains fruitless.
 
@@
 When such precipitation data will be available, the use of a STW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.
+
+Another potential application of the STW is when the time step of interest is multi-daily, such as a precipitation total over 3 days.
+In this case, the daily predictors can be assessed in the same way it was here applied at a sub-daily time step, and long archives of daily precipitation totals can be used.
 

### 2016-04-26 Moving temporal window - HESS/template.tex
Removing a perspective in order to avoid being copied (from Charles).

@@
 
-Another potential application of the STW is when the time step of interest is multi-daily, such as a precipitation total over 3 days.
-In this case, the daily predictors can be assessed in the same way it was here applied at a sub-daily time step, and long archives of daily precipitation totals can be used.
-
 \begin{acknowledgements}

### 2016-05-18 Moving temporal window - HESS/template.tex
Corrections from Michel.

@@
 The search for candidate situations, for a given target day, is usually undertaken by comparing the state of the atmosphere at fixed hours of the day, for both the target day and the candidate analogues.
-The constraint being the use of daily time series, due to the length of available archives they provide.
+The constraint being the use of daily time series, due to the length of available archives they provide, and the unavailability of equivalent archives at a finer time step.
 However, it is unlikely that the best analogy happens at the very same hour, but it may occur at a different time of the day.
-In order to assess the potential of finding better analogues at a different hour, a sliding time window (STW) has been introduced.
+In order to assess the potential of finding better analogues at a different hour, a sliding time window (STW) has been introduced on a reduced archive of hourly precipitation totals.
 
@@
 Here, it has been limited to the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects.
-Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the S1 criteria \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window and at certain hours.
-
-In fact, the predictand is not an instantaneous value, but often an accumulation over a certain time period (eg.
-24 h for rainfall, taken from 6-30 h UTC).
-Therefore, the meteorological situation generating this accumulated rainfall is not instantaneous either, but is a continuous transition between changing circulation patterns.
-Thus, the observed predictors fields are considered at different time of the day, and at different heights.
-In our case, the geopotential height is considered at 1000~hPa (Z1000) at 12~h~UTC and 500~hPa (Z500) at 24~h~UTC.
-The selection of the observation time of the predictor was found by \citet{Bontron2004} to have a significant influence.
-Moreover, due to inter-correlation, selecting the optimal 2 pressure levels at 2 hours is not equivalent to combining the best time of both levels individually.
-
-Then, $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day, $N_{1}$ being a parameter to calibrate.
-Then, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
-Following the nomenclature proposed by \citet{Horton2016}, this method will be named 2Z.
+Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the S1 criteria \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window and at certain hours:
 
@@
 
+The predictand, here a 24~h precipitation total, results from meteorological situations that are continuous transitions between changing circulation patterns.
+Thus, the observed predictors fields, extracted from reanalysis datasets, are considered at different time of the day and at different heights.
+In our case, the geopotential height is considered at 1000~hPa (Z1000) at 12~h~UTC and 500~hPa (Z500) at 24~h~UTC.
+The selection of the observation time of the predictor was found by \citet{Bontron2004} to have a significant influence.
+
+Then, $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day, $N_{1}$ being a parameter to calibrate.
+Then, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
+Following the nomenclature proposed by \citet{Horton2016}, this method will be named 2Z.
+
 \begin{table}[htb]
@@
 where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value 1 otherwise.
-The mean CRPS is averaged on the calibration, respectively the validation periods, on all days.
 \citet{Bontron2004} proposed a decomposition of this score interpreted into a sharpness and an accuracy terms.
@@
 \end{equation}
-where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect forecast (which implies $CRPS_{p}~=~0$). A better forecast is characterized by an increase in CRPSS.
+where $CRPS_{r}$ is the CRPS value for the reference (climatological distribution) and $CRPS_{p}$ would be the one for a perfect forecast (which implies $CRPS_{p}~=~0$).
+A better forecast is characterized by an increase in CRPSS.
 
@@
 Therefore, the analogue situations are assessed on the basis of a daily time step, by comparing predictors at fixed hours of the day, otherwise one would not know what precipitation values to assign to them.
-However, it can be expected that the analogy of the synoptic situations do not occur systematically at the same time of the day, and that better candidates can be found by shifting to a different hour.
+However, it can be expected that the analogy of the synoptic situations does not occur systematically at the same time of the day, and that better candidates can be found by shifting to a different hour.
 On this assumption, a sliding time window (STW) was introduced to allow searching for candidates at different hours of the day.
@@
 In order to assess this potential improvement of the prediction, precipitation data with a resolution of 10 minutes, on a respectable archive length, was used (section \ref{sec:data}).
-It was then aggregated in the form of 24~h-totals, but starting at different 6-hourly time step, by means of a moving average (section \ref{sec:method}).
+It was then aggregated in the form of 24~h-totals, but starting at different 6-hourly time step, by means of a moving total (section \ref{sec:method}).
 
@@
 The results will thereafter be presented arbitrarily for the Ulrichen station, but they are equivalent for all stations.
+The precipitation time series were then aggregated by means of a moving 24~h-total (see next section).
 
@@
 
-% FIGURE (MAP)
-
 \section{The sliding time window (STW) approach}
@@
 	\end{center}
-	\caption{Illustration of the principle of a sliding time window. }
+	\caption{Illustration of the principle of a sliding time window. The bars illustrate the 24~h precipitation totals.}
 	\label{fig:principle}

### 2016-05-18 Moving temporal window - HESS/template.tex
Corrections from Michel.

@@
 \introduction  %% \introduction[modified heading if necessary]
+\label{sec:introduction}
 
@@
 Here, it has been limited to the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects.
-Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the S1 criteria \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window and at certain hours:
+Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the S1 criteria \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954}, which is a comparison of gradients, over a certain spatial window and at certain hours:
 
@@
 
-The second reference method adds a subsequent level of analogy on moisture variables (method 2Z-2MI, Table \ref{table:method_2Z-2MI}).
+The second reference method adds a subsequent level of analogy on moisture variables, compared by means of the root-mean-square error (RMSE) (method 2Z-2MI, Table \ref{table:method_2Z-2MI}).
 This second predictor is a moisture index made of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850) \citep{Bontron2004}.
@@
 	\end{center}
-	\caption{Illustration of the principle of a sliding time window. The bars illustrate the 24~h precipitation totals.}
+	\caption{Illustration of the principle of a sliding time window. The larger horizontal bars represent the 24~h precipitation totals.}
 	\label{fig:principle}
@@
 Figure \ref{fig:changes_S1_analogues} presents the changes in the distributions of the S1 criterion for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogues for the Ulrichen station on the whole calibration period, due to introduction of the STW.
-The precipitation target remains at before, that is centered on 18~h~UTC (6~h~UTC to 6~h~UTC the next day).
+The precipitation target remains as before, that is centered on 18~h~UTC (6~h~UTC to 6~h~UTC the next day).
 The shapes of the distributions of the conventional approach and the STW are similar, but the values of the analogy criteria are now reduced (shifted to the left), and therefore better.
@@
 
+\begin{figure}[htb]
+	\includegraphics[width=8.3cm]{figures/hours_selection_per_season_Visp.pdf}
+	\caption{Distribution of the predictors hours in the selected analogue dates depending on the season, for the Visp station.}
+	\label{fig:hours_selection_per_season_Visp}
+\end{figure}
+
 A seasonal effect can be observed on the reduction of the S1 criteria due to the STW (Figure \ref{fig:changes_S1_seasons}).
@@
 Other seasons are between these two extremes, which is consistent with their respective improvements.
-This seasonal effect was observed for each station in a very similar way, and generally even with a larger amplitude than for Ulrichen.
+This seasonal effect was observed for each station in a very similar way, and generally even with a slightly larger amplitude than for Ulrichen (see example of the Visp station in Figure \ref{fig:hours_selection_per_season_Visp}).
 
@@
 
-When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidates situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogues, but their dates may have changed.
+When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidates situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogues, but their dates have changed.
 In contrast to earlier, both a reduction or an increase of the RMSE analogy criterion values are possible.
@@
 
-The CRPS score can be decomposed into two components, namely sharpness and accuracy.
+The CRPS score can be decomposed into two components, namely sharpness and accuracy \citep[see][]{Bontron2004}.
 The impact of the STW has been analyzed on these components and the results can be found in Table \ref{table:CRPSS_decomposition_no_recalibration} for the original parameters and in Table \ref{table:CRPSS_decomposition_recalibration} for the re-calibrated methods.
@@
 	\end{center}
-	\caption{Illustration of the generation of 24~h-totals moving averages by means of a proportional distribution.}
+	\caption{Illustration of the generation of 24~h-totals moving averages by means of a proportional distribution. The colours refer to the corresponding day of the daily time series.}
 	\label{fig:illustration_disaggregation}
@@
 \begin{table}[htb]
-	\caption{Values of the CRPSS (\%) skill score for the original and the recalibrated parameters using the STW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
+	\caption{Values of the CRPSS (\%) skill score for the original and the recalibrated parameters (with the sequential method, as described in Section \ref{sec:introduction}) using the STW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
 	\begin{center}
@@
 \begin{table}[htb]
-	\caption{Values of the CRPSS (\%) skill score for Zermatt, for the original and the recalibrated parameters using the STW approach on the disaggregated precipitation time series (short and long periods) by means of variables from the reanalysis.}
+	\caption{Values of the CRPSS (\%) skill score for Zermatt, for the original and the recalibrated parameters (with the sequential method, as described in Section \ref{sec:introduction}) using the STW approach on the disaggregated precipitation time series (short and long periods) by means of variables from the reanalysis.}
 	\begin{center}

### 2016-05-18 Moving temporal window - HESS/template.tex
Preparation for submission.

@@
 %% 2-Column Papers and Discussion Papers
-%\documentclass[hess, manuscript]{copernicus}
-\documentclass[hess]{copernicus}
+\documentclass[hess, manuscript]{copernicus}
+%\documentclass[hess]{copernicus}
 
@@
 
-\begin{table}[htb]
-	\caption{Parameters of the reference method on the atmospheric circulation (2Z).
-The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window).
-The criteria used for the current level of analogy is then provided, as well as the number of analogues.}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccc}
-			\hline
-			Level & Variable & Hour & Criteria & Nb \\ 
-			\hline 
-			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{$N_{1}$} \\
-			& Z500 & 24~h & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:method_2Z}
-\end{table}
-
 The second reference method adds a subsequent level of analogy on moisture variables, compared by means of the root-mean-square error (RMSE) (method 2Z-2MI, Table \ref{table:method_2Z-2MI}).
@@
 When a second level of analogy is added, a higher number of $N_{1}$ analogues is kept on the first level.
-
-\begin{table}[htb]
-	\caption{Parameters of the reference method with moisture variables (2Z-2MI). Same conventions as Table \ref{table:method_2Z}}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccc}
-			\hline 
-			Level & Variable & Hour & Criteria & Nb \\ 
-			\hline 
-			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{$N_{1}$} \\
-			& Z500 & 24~h & & \\ 
-			\hline
-			\multirow{2}{*}{2} & TPW * RH850 & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{2}$} \\
-			& TPW * RH850 & 24~h & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:method_2Z-2MI}
-\end{table}
 
@@
 Previous tests showed the benefit, in terms of analogy criteria values, of searching for analogue synoptic situations at a finer time step, but without assessing the impact on the forecast skills \citep{Finet2008}.
-In order to assess this potential improvement of the prediction, precipitation data with a resolution of 10 minutes, on a respectable archive length, was used (section \ref{sec:data}).
-It was then aggregated in the form of 24~h-totals, but starting at different 6-hourly time step, by means of a moving total (section \ref{sec:method}).
+In order to assess this potential improvement of the prediction, precipitation data with a resolution of 10 minutes, on a respectable archive length, was used (Sect.
+\ref{sec:data}).
+It was then aggregated in the form of 24~h-totals, but starting at different 6-hourly time step, by means of a moving total (Sect.
+\ref{sec:method}).
 
@@
 
-The changes due to the introduction of a STW was assessed first in regards to the analogy criteria improvement (section \ref{sec:influence_criteria}), and then in terms of precipitation prediction skill (section \ref{sec:influence_scores}).
-Finally, attempts were made to reconstruct longer 24~h-total precipitations series (section \ref{sec:attempts}).
+The changes due to the introduction of a STW was assessed first in regards to the analogy criteria improvement (Sect.
+\ref{sec:influence_criteria}), and then in terms of precipitation prediction skill (Sect.
+\ref{sec:influence_scores}).
+Finally, attempts were made to reconstruct longer 24~h-total precipitations series (Sect.
+\ref{sec:attempts}).
 
@@
 Due to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed.
-The time series (on the period 1982-2007) come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle (Figure \ref{fig:map}), which are subject to various meteorological influences \citep{Horton2012}.
+The time series (on the period 1982-2007) come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle (Fig.
+\ref{fig:map}), which are subject to various meteorological influences \citep{Horton2012}.
 The results will thereafter be presented arbitrarily for the Ulrichen station, but they are equivalent for all stations.
@@
 
-\begin{figure}[htb]
-	\begin{center}
-		\includegraphics[width=8.3cm]{figures/figure_map.pdf}
-	\end{center}
-	\caption{Position of the 6 weather stations of interest (Ulrichen, Zermatt, Visp, Montana, Sion and Aigle) in the study area.}
-	\label{fig:map}
-\end{figure}
-
 Predictors are extracted from the NCEP/NCAR reanalysis I \citep{Kalnay1996} dataset with a 6-hourly temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree.
@@
 In order to assess the benefit of searching analogue situations at a sub-daily time step, an appropriate precipitation series is required.
-On the basis of high resolution time series (section \ref{sec:data}), 24~h-totals were processed, but at a 6-hourly time step (temporal resolution of the reanalysis dataset), by means of a moving 24~h-total.
+On the basis of high resolution time series (Sect.
+\ref{sec:data}), 24~h-totals were processed, but at a 6-hourly time step (temporal resolution of the reanalysis dataset), by means of a moving 24~h-total.
 
 The target situations and their corresponding observed precipitation values (used for validation) do not change, because the forecast is always established for a fixed period of the target day (6-30~h), as before.
-The difference is that the candidates are 4~times more numerous (Figure \ref{fig:principle}).
-
-\begin{figure}[htb]
-	\begin{center}
-		\includegraphics[width=8.3cm]{figures/illustration_moving_window.pdf}
-	\end{center}
-	\caption{Illustration of the principle of a sliding time window. The larger horizontal bars represent the 24~h precipitation totals.}
-	\label{fig:principle}
-\end{figure}
+The difference is that the candidates are 4~times more numerous (Fig.
+\ref{fig:principle}).
 
@@
 The AM parameters were calibrated using AtmoSwing \citep{Horton2016} on the original archive (Tables \ref{table:params_2Z} and \ref{table:params_2Z-2MI}) and will be used thereafter.
-
-\begin{table}[htb]
-	\caption{Calibrated parameters (spatial windows and number of analogues) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) and skill score (\%) of the method on the full archive.}
-	\begin{center}
-		\begin{tabular}{l c c c c }
-			\hline
-			Station & Longitudes & Latitudes & N$_{1}$ & CRPSS \\
-			\hline
-			Ulrichen & 0 $\rightarrow$ 17.5 & 42.5 $\rightarrow$ 47.5 & 40 & 30.73 \\
-			Zermatt & 0 $\rightarrow$ 20 & 37.5 $\rightarrow$ 50 & 35 & 23.87 \\
-			Visp & -2.5 $\rightarrow$ 20 & 40 $\rightarrow$ 47.5 & 30 & 25.11 \\
-			Montana & -2.5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 47.5 & 40 & 32.55 \\
-			Sion & -2.5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 47.5 & 40 & 26.23 \\
-			Aigle & -5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 50 & 50 & 30.59 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{table:params_2Z}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Parameters of the moisture variables from the 2Z-2MI method and the corresponding skill score (\%) on the complete archive.
-The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z}, except the number of analogues of the first analogy level (N$_{1}$), which are here different.
-The $5^{th}$ column is the number of analogues for the second level (N$_{2}$).}
-	\begin{center}
-		\begin{tabular}{l c c c c c }
-			\hline
-			Station & Longitudes & Latitudes & N$_{1}$ & N$_{2}$ & CRPSS \\
-			\hline
-			Ulrichen & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 60 & 25 & 34.31 \\
-			Zermatt & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 55 & 25 & 28.28 \\
-			Visp & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 45 & 25 & 28.85 \\
-			Montana & 5 $\rightarrow$ 7.5 & 45 $\rightarrow$ 47.5 & 55 & 30 & 36.11 \\
-			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 90 & 30 & 31.16 \\
-			Aigle & 7.5 & 45 $\rightarrow$ 47.5 & 100 & 35 & 35.82 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{table:params_2Z-2MI}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Influence of the archive reduction on the CRPSS. CRPSS values are provided for both considered methods and the differences are expressed in absolute value.}
-	\begin{center}
-		\begin{tabular}{l c c c c }
-			\hline
-			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
-			& 82-07 & $\Delta$ & 82-07 & $\Delta$ \\ 
-			\hline
-			Ulrichen & 29.37 & -1.36 & 33.24 & -1.08 \\
-			Zermatt & 22.20 & -1.67 & 26.95 & -1.32 \\
-			Visp & 23.23 & -1.89 & 27.77 & -1.08 \\
-			Montana & 30.79 & -1.76 & 34.77 & -1.34 \\
-			Sion & 24.78 & -1.45 & 29.36 & -1.80 \\
-			Aigle & 30.57 & -0.01 & 35.95 & 0.13 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{table:loss_reduction}
-\end{table}
 
@@
 When searching for analogues on the geopotential heights, as in the 2Z method, there are now 4 times more candidates than before, which obviously allows to find better matches.
-
-\begin{figure*}[htb]
-	\begin{center}
-		\includegraphics[width=15cm]{figures/changes_S1_analogues.png}
-	\end{center}
-	\caption{Changes in the S1 criteria distributions of the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogue ranks for the Ulrichen station, due to the STW.}
-	\label{fig:changes_S1_analogues}
-\end{figure*}
 
@@
 
-\begin{figure}[htb]
-	\begin{center}
-		\includegraphics[width=8.2cm]{figures/changes_S1_value.pdf} \\
-		\includegraphics[width=8.3cm]{figures/changes_S1_gain.pdf}
-	\end{center}
-	\caption{Synthesis of the changes in the S1 criteria, due to the STW, for the Ulrichen station, depending on the ranks of the analogue.
-(top) Quantiles of the S1 distributions with and without the STW.
-(bottom) Quantiles of the relative improvements of the S1 criteria when using the STW.}
-	\label{fig:changes_S1}
-\end{figure}
-
-The improvements of the S1 criteria are summarized in Figure \ref{fig:changes_S1}, which shows (top) quantiles of the S1 criteria according to the analogue rank for the conventional method and the STW, and (bottom) quantiles of the relative reduction.
-This confirms that all quantile seem similarly reduced (S1 distributions keep their shape), and that this improvement is constantly increasing from the first to the last analogue (Figure \ref{fig:changes_S1} bottom).
-
-The median of the S1 values reduction (Figure \ref{fig:changes_S1} bottom) starts approximately at 5~\% for the first analogue and reaches more than 10~\% for the last one.
+The improvements of the S1 criteria are summarized in Fig.
+\ref{fig:changes_S1}, which shows (top) quantiles of the S1 criteria according to the analogue rank for the conventional method and the STW, and (bottom) quantiles of the relative reduction.
+This confirms that all quantile seem similarly reduced (S1 distributions keep their shape), and that this improvement is constantly increasing from the first to the last analogue (Fig.
+\ref{fig:changes_S1} bottom).
+
+The median of the S1 values reduction (Fig.
+\ref{fig:changes_S1} bottom) starts approximately at 5~\% for the first analogue and reaches more than 10~\% for the last one.
 This increasing trend with the analogue rank can be explained by the accumulation of better analogues in the distribution.
@@
 A basic assumption is considered here, which stipulates that the more a day is rainy, the more dynamic the situation is.
-The results of this analysis are summarized in Figure \ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for days with precipitation (organized into classes) between two thresholds.
+The results of this analysis are summarized in Fig.
+\ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for days with precipitation (organized into classes) between two thresholds.
 The number of cases per class being reduced, the curves are not as smooth as in previous analyzes.
@@
 
-\begin{figure}[htb]
-	\begin{center}
-		\includegraphics[width=8.3cm]{figures/changes_S1_precip_threshold.pdf}
-	\end{center}
-	\caption{Distribution of the median improvements of the S1 criteria, due to the STW, depending on precipitation thresholds at the Ulrichen station.}
-	\label{fig:changes_S1_precip_threshold}
-\end{figure}
-
 \subsection{Seasonal effect}
@@
 
-\begin{figure}[htb]
-	\begin{center}
-		\includegraphics[width=7cm]{figures/changes_S1_seasons.pdf}
-	\end{center}
-	\caption{Seasonal effect on the median reduction of the S1 criteria for the Ulrichen station due to the STW. DJF: winter, MAM: spring, JJA: summer SON: fall.}
-	\label{fig:changes_S1_seasons}
-\end{figure}
-
-\begin{figure}[htb]
-	\includegraphics[width=8.3cm]{figures/hours_selection_per_season.pdf}
-	\caption{Distribution of the predictors hours in the selected analogue dates depending on the season, for the Ulrichen station.}
-	\label{fig:hours_selection_per_season}
-\end{figure}
-
-\begin{figure}[htb]
-	\includegraphics[width=8.3cm]{figures/hours_selection_per_season_Visp.pdf}
-	\caption{Distribution of the predictors hours in the selected analogue dates depending on the season, for the Visp station.}
-	\label{fig:hours_selection_per_season_Visp}
-\end{figure}
-
-A seasonal effect can be observed on the reduction of the S1 criteria due to the STW (Figure \ref{fig:changes_S1_seasons}).
+A seasonal effect can be observed on the reduction of the S1 criteria due to the STW (Fig.
+\ref{fig:changes_S1_seasons}).
 The improvements are greater for winter than summer.
@@
 
-An analysis of the selected hours for the geopotential predictor seems to confirm this assumption (Figure \ref{fig:hours_selection_per_season}).
+An analysis of the selected hours for the geopotential predictor seems to confirm this assumption (Fig.
+\ref{fig:hours_selection_per_season}).
 It was found that the new choice of the temporal window in winter, when using the STW approach, is well balanced between the 4 options.
@@
 Other seasons are between these two extremes, which is consistent with their respective improvements.
-This seasonal effect was observed for each station in a very similar way, and generally even with a slightly larger amplitude than for Ulrichen (see example of the Visp station in Figure \ref{fig:hours_selection_per_season_Visp}).
+This seasonal effect was observed for each station in a very similar way, and generally even with a slightly larger amplitude than for Ulrichen (see example of the Visp station in Fig.
+\ref{fig:hours_selection_per_season_Visp}).
 
@@
 In contrast to earlier, both a reduction or an increase of the RMSE analogy criterion values are possible.
-Indeed, Figure \ref{fig:changes_RMSE} shows an almost insignificant improvement of the RMSE values.
+Indeed, Fig.
+\ref{fig:changes_RMSE} shows an almost insignificant improvement of the RMSE values.
 Unlike for the first level of analogy, the relative improvement of the RMSE values are distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
 Once again, the results for the other stations are similar.
-
-\begin{figure}[htb]
-	\begin{center}
-		\includegraphics[width=8.1cm]{figures/changes_RMSE_value.pdf} \\
-		\includegraphics[width=8.3cm]{figures/changes_RMSE_gain.pdf}
-	\end{center}
-	\caption{Synthesis of the changes in the RMSE criteria, due to the STW, for the Ulrichen station, depending on the ranks of the analogue.
-(top) Quantiles of the RMSE distributions with and without the STW.
-(bottom) Quantiles of the relative improvements of the RMSE criteria when using the STW.}
-	\label{fig:changes_RMSE}
-\end{figure}
 
@@
 Therefore, the impact of the STW introduction, and thus the selection of other analogue dates, has to be assessed on the performance scores.
-In order to perform this assessment, the 24~h-totals (moving average) at a 6-hourly time step were used (see section \ref{sec:data}).
+In order to perform this assessment, the 24~h-totals (moving average) at a 6-hourly time step were used (see Sect.
+\ref{sec:data}).
 The target dates remain unchanged, since the original time slot (6~h~UTC - 6~h~UTC the next day) is kept, and thus the performance scores can be directly compared with the former ones.
@@
 
-\begin{table}[htb]
-	\caption{New CRPSS performance scores for both 2Z and 2Z-2MI methods obtained by the STW approach. The differences are expressed regarding the conventional method with the same archive length.}
-	\begin{center}
-		\begin{tabular}{l c c c c}
-			\hline
-			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
-			& STW & $\Delta$ & STW & $\Delta$ \\
-			\hline
-			Ulrichen & 31.12 & 1.74 & 35.44 & 2.20 \\
-			Zermatt & 24.34 & 2.14 & 28.92 & 1.97 \\
-			Visp & 24.39 & 1.16 & 29.42 & 1.64 \\
-			Montana & 31.59 & 0.80 & 36.30 & 1.53 \\
-			Sion & 25.35 & 0.57 & 31.07 & 1.71 \\
-			Aigle & 31.78 & 1.21 & 38.11 & 2.16 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{table:CRPSS_STW}
-\end{table}
-
 \subsection{Improvement by precipitation classes}
@@
 
-The S1 criteria was previously found to be improved to a greater extent for the most dynamic situations related with higher precipitation values (section \ref{sec:influence_precip}).
+The S1 criteria was previously found to be improved to a greater extent for the most dynamic situations related with higher precipitation values (Sect.
+\ref{sec:influence_precip}).
 The changes in terms of performance scores will now be assessed regarding precipitation thresholds.
-Figure \ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, other stations having the same behavior.
+Fig.
+\ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, other stations having the same behavior.
 
@@
 
-\begin{figure}[htb]
-	\includegraphics[width=5cm]{figures/changes_CRPS_precip_threshold.pdf}
-	\caption{Differences of the CRPSS performance score, due to the introduction of the STW, as a function of precipitation thresholds at the Ulrichen station. The stars represent averages.}
-	\label{fig:changes_CRPS_precip_threshold}
-\end{figure}
-
 \subsection{Recalibrating the parameters}
@@
 The calibration has then been reprocessed.
-
-\begin{table}[htb]
-	\caption{Calibrated parameters (spatial windows and number of analogues) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) with the STW approach.}
-	\begin{center}
-		\begin{tabular}{l c c c }
-			\hline
-			Station & Longitudes & Latitudes & N$_{1}$ \\
-			\hline
-			Ulrichen & 0 $\rightarrow$ 17.5 & 42.5 $\rightarrow$ 50 & 50 \\
-			Zermatt & 0 $\rightarrow$ 17.5 & 40 $\rightarrow$ 50 & 55 \\
-			Visp & -2.5 $\rightarrow$ 20 & 40 $\rightarrow$ 50 & 55 \\
-			Montana & -2.5 $\rightarrow$ 15 & 42.5 $\rightarrow$ 47.5 & 55 \\
-			Sion & -2.5 $\rightarrow$ 15 & 37.5 $\rightarrow$ 50 & 55 \\
-			Aigle & -2.5 $\rightarrow$ 15 & 40 $\rightarrow$ 50 & 75 \\
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{table:params_2Z_new}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Parameters of the moisture variables from the 2Z-2MI method with the STW approach.
-The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z_new}, except the number of analogues of the first analogy level (N$_{1}$), which are here different.
-The $5^{th}$ column is the number of analogues for the second level (N$_{2}$).}
-	\begin{center}
-		\begin{tabular}{l c c c c }
-			\hline
-			Station & Longitudes & Latitudes & N$_{1}$ & N$_{2}$ \\
-			\hline
-			Ulrichen & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 110 & 35 \\
-			Zermatt & 7.5 & 45 $\rightarrow$ 47.5 & 80 & 30 \\
-			Visp & 7.5 & 45 $\rightarrow$ 47.5 & 135 & 35 \\
-			Montana & 5 $\rightarrow$ 7.5 & 45 & 110 & 40 \\
-			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 140 & 50 \\
-			Aigle & 5 $\rightarrow$ 7.5 & 45 & 135 & 45 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{table:params_2Z-2MI_new}
-\end{table}
 
@@
 It seems as if the method perceive the increase in the archive length and diversity by allowing to extract more analogues.
-As we saw in Figure \ref{fig:changes_S1}, the improvement of the S1 criteria grows along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions.
+As we saw in Fig.
+\ref{fig:changes_S1}, the improvement of the S1 criteria grows along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions.
 It seems thus profitable to widen the selection of analogues in order to keep also some whose rank has increased, as they appear to be also relevant to predict precipitation values.
@@
 This increase in number of analogues has a slight effect on the performance of the different precipitation classes.
-The same analysis as in section \ref{sec:improvement_CRPSS_precip_threshold} has been performed again on the basis of the newly calibrated parameters.
+The same analysis as in Sect.
+\ref{sec:improvement_CRPSS_precip_threshold} has been performed again on the basis of the newly calibrated parameters.
 The results are generally very similar, but a slight performance increase of small precipitation values can be observed at the expense of higher amounts.
 The change in the analogues numbers is likely to be responsible for this difference in the performance distributions.
-
-\begin{table}[htb]
-	\caption{Values of the CRPSS (\%) skill score for the newly calibrated parameters using the STW approach.
-The differences are expressed regarding the conventional method with the same archive length.}
-	\begin{center}
-		\begin{tabular}{l c c c c}
-			\hline
-			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
-			& STW & $\Delta$ & STW & $\Delta$ \\
-			\hline
-			Ulrichen & 31.58 & 2.20 & 35.72 & 2.48  \\
-			Zermatt & 24.71 & 2.51 & 29.63 & 2.68 \\
-			Visp & 25.08 & 1.85 & 30.29 & 2.52 \\
-			Montana & 32.22 & 1.43 & 37.15 & 2.38 \\
-			Sion & 26.07 & 1.29 & 31.68 & 2.32 \\
-			Aigle & 32.21 & 1.64 & 38.50 & 2.55 \\
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{table:CRPSS_recalibration}
-\end{table}
 
@@
 
-\begin{table}[htb]
-	\caption{Changes in sharpness and accuracy relatively to the total CRPS, due to the introduction of the STW.
-The changes are presented for both 2Z and 2Z-2MI methods with the original parameters.
-A decrease of the score is desirable.}
-	\begin{center}
-		\begin{tabular}{l c c c c}
-			\hline
-			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
-			& Sharpness & Accuracy & Sharpness & Accuracy \\
-			\hline
-			Ulrichen & 2.82 & -5.29 & 1.00 & -4.30 \\
-			Zermatt & 2.26 & -5.01 & 0.88 & -3.58 \\
-			Visp & 3.66 & -5.18 & 2.67 & -4.94 \\
-			Montana & 1.62 & -2.78 & 0.57 & -2.91 \\
-			Sion & 2.02 & -2.78 & 0.33 & -2.75 \\
-			Aigle & 0.52 & -2.26 & -1.20 & -2.17 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{table:CRPSS_decomposition_no_recalibration}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Same as Table \ref{table:CRPSS_decomposition_no_recalibration} but with the re-calibrated parameters.}
-	\begin{center}
-		\begin{tabular}{l c c c c}
-			\hline
-			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
-			& Sharpness & Accuracy & Sharpness & Accuracy \\
-			\hline
-			Ulrichen & 1.44 & -4.56 & -0.37 & -3.34 \\
-			Zermatt & 0.80 & -4.03 & 0.75 & -4.42 \\
-			Visp & 1.53 & -3.94 & 1.47 & -4.96 \\
-			Montana & -0.27 & -1.80 & 0.06 & -3.71 \\
-			Sion & 0.95 & -2.66 & -0.10 & -3.19 \\
-			Aigle & -0.35 & -2.01 & -2.08 & -1.90 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{table:CRPSS_decomposition_recalibration}
-\end{table}
+It appears that the sharpness is a bit inferior with the STW in favor of accuracy (Table \ref{table:CRPSS_decomposition_no_recalibration}).
+When using the recalibrated parameters, the components are a bit more balanced, but still the accuracy prevails on the sharpness (Table \ref{table:CRPSS_decomposition_recalibration}).
+Fig.
+\ref{fig:CRPSS_decomposition_precip_thresholds} illustrates the changes (relative to the total CRPS) in sharpness and accuracy for different precipitation thresholds at the Ulrichen station.
+Be it for the 2Z or 2Z-2MI method, the original or the recalibrated parameters, the changes are similar: the improvements concern the accuracy over the sharpness, and this to a greater extent for significant precipitation events.
+The STW does not allow to improve the sharpness, but the improvement in accuracy is significant, and this especially for the days with heavy precipitation.
+In terms of the predicted precipitation distribution, it means that the median of the prediction is closer to the observed values, while the distribution is not more condensed than previously.
+
+\section{Application attempts on the full archive}
+\label{sec:attempts}
+
+The improvement provided by the STW is interesting, mainly for heavy precipitation events, and thus it would be profitable to be able to apply it to the complete archive.
+Unfortunately, there is no long precipitation time series available with a sub-daily time step.
+In order to reconstruct a longer archive of moving 24~h-totals, different disaggregation approaches of the daily time series were assessed and are presented in the following sections.
+
+\subsection{Proportional distribution}
+
+A proportional distribution is certainly the simplest approach that can be performed.
+It consists in allocating proportional parts of the original daily time series into a new moving average of 24~h-totals (Fig.
+\ref{fig:illustration_disaggregation}).
+When using this reconstructed time series on the shorter period, the method performance was degraded (Table \ref{table:disaggregation_proportional} to compare to Table \ref{table:CRPSS_STW}) and was even below the conventional method without STW (Table \ref{table:loss_reduction}).
+The benefit of a better selection of the analogue situations is lost due to a precipitation archive of poor quality.
+
+\subsection{Use of a proxy variable}
+
+As demonstrated in the previous section, the performance improvement brought by the STW is lost when using a simplistic precipitation time series.
+In order to get closer to the chronology of the actual precipitation, the reconstruction procedure must rely on some informative variable.
+Data from the NCEP/NCAR reanalysis 1 (Sect.
+\ref{sec:data}) was used in this perspective, despite their rough resolution.
+
+The first step consisted in determining which variables from the precipitable water or the relative humidity (at 1000~hPa, 925~hPa or 850~hPa) produces the precipitation chronology that is the most correlated (on non-zero values) with the accurate 6-hourly precipitation time series on the period 1982-2007.
+The location of the most predictive point from the reanalysis grid had to be assessed (closest points: 5\textdegree\ and 7.5\textdegree\ longitude and 45\textdegree\ and 47.5\textdegree\ latitude), as well an eventual time lapse between both series, due to the significant distance separating the weather stations and the reanalysis grid point.
+The most relevant point will probably not be the same for all stations, since one can expect to find the optimum in the direction of the main moisture inflows for the station.
+This assessment must be carried out for each station.
+
+The results of the correlation analyses (on non-zero values) between the new series reconstituted using the proxy and the actual series are illustrated in Table \ref{table:proxy_correlations} for Zermatt (on the short period, 1982-2007).
+The best proxy is the precipitable water at 45\textdegree\ latitude and 7.5\textdegree\ longitude, with a time offset of -6~h.
+The determination coefficient of 0.721 is higher than that of the series from the proportional distribution (0.698), which confirms that a little information was added to the series of precipitation.
+
+Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the reconstituted series using the proxy of precipitable water at the optimal point (Table \ref{table:proxy_correlations}).
+A slight improvement can be obtained compared to the proportional distribution method, but it is still relatively small, and most of the benefit of the STW is again lost.
+
+These attempts to transpose the STW on the total archive highlight the importance of the actual rainfall chronology.
+The STW is profitable, provided that the precipitation series are close to the observed one.
+Without precipitation series with an accurate sub-daily chronology, the introduction of a STW remains fruitless.
+
+\conclusions  %% \conclusions[modified heading if necessary]
+
+The AM is most often based on a daily time step, due to the availability of long precipitation archives.
+However, it is unlikely that two analogue synoptic situations, that evolve relatively quickly, would correspond optimally at the same hour of the day.
+It is thus more likely that a better match can be found at another time, which can change the selection of the analogues dates.
+
+As \citet{Finet2008} had previously shown, the introduction of a STW allows finding better analogue situations in terms of the atmospheric circulation.
+It has been here demonstrated that the improvement of the S1 criteria values is growing with the rank of the analogue.
+This is due to the accumulation of better analogues within the predicted distributions.
+
+The improvement of the circulation analogy was found to be more important for heavy precipitation events, which are generally related to more dynamic atmospheric situations.
+This dynamism implies more specific circulation patterns that are evolving more rapidly.
+Thus, a STW is found to be of particular interest in this kind of situation, and benefits the prediction of extreme precipitation events.
+
+A seasonal effect has been highlighted, as the STW is more profitable for winter months than summer.
+The reason is likely that the diurnal cycle has a bigger effect in summer than in winter, which results in better analogues at the same time of the day.
+The preference for the same hours in summer has been demonstrated, whereas 75\% of the analogue situations are selected at a different time in winter.
+
+The impact of the STW on the prediction performance has never been assessed before, due to the shortcoming of long precipitation series at a sub-daily time step.
+The impact of the STW approach could be assessed on a 25 years time series with a high temporal resolution.
+After the introduction of the STW, the performance scores increased of the same order of magnitude as if the length of the archive doubled, in this case study.
+
+The parameters were then calibrated again, using the STW.
+Some parameters changed, the main difference being the number of analogues, which systematically and significantly increased compared to the original set.
+A wider selection of analogue situations, containing those whose rank decreased, seemed profitable for the prediction performance.
+The number of good analogues is thus globally increased.
+This change seems to benefit mainly the prediction of days with small precipitation totals.
+
+The importance of the quality of the precipitation archive was also demonstrated, as too simplistic reconstructions of 6-hourly time series lead to a loss of all the improvement brought by better analogue situations identified by the STW.
+The precipitation prediction is improved only when the precipitation chronology is close to the accurate one.
+Attempts to reconstruct longer time series based on a simplistic proportional distribution or using meteorological variables from the NCEP reanalysis 1 dataset as proxy did not succeed.
+Other reanalysis datasets could eventually preform better.
+
+Perspectives of using the STW rely on the availability of long precipitation series at a sub-daily time step and with high accuracy.
+The first source of such data is the simple fact that with time, these archives of high temporal resolution precipitation data are getting longer.
+The second source is the establishment of precipitation reanalysis at a country scale, or the use of reanalysis-driven RCMs (Regional Climate Models) or LAMs (Limited Area Models) on a long period.
+When such precipitation data will be available, the use of a STW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.
+
+\begin{acknowledgements}
+Thanks to Dominique B\'{e}rod for his support and to Renaud Marty for his fruitful collaboration over the years.
+
+Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
+
+The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
+
+NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/. Precipitation time series provided by MeteoSwiss. 
+\end{acknowledgements}
+
+%% REFERENCES
+
+%% The reference list is compiled as follows:
+
+\bibliographystyle{copernicus}
+\bibliography{../_refs/_articles-moving-window}
+
+\begin{figure}[htb]
+	\begin{center}
+		\includegraphics[width=8.3cm]{figures/figure_map.pdf}
+	\end{center}
+	\caption{Position of the 6 weather stations of interest (Ulrichen, Zermatt, Visp, Montana, Sion and Aigle) in the study area.}
+	\label{fig:map}
+\end{figure}
+
+\begin{figure}[htb]
+	\begin{center}
+		\includegraphics[width=8.3cm]{figures/illustration_moving_window.pdf}
+	\end{center}
+	\caption{Illustration of the principle of a sliding time window. The larger horizontal bars represent the 24~h precipitation totals.}
+	\label{fig:principle}
+\end{figure}
+
+\begin{figure*}[htb]
+	\begin{center}
+		\includegraphics[width=15cm]{figures/changes_S1_analogues.png}
+	\end{center}
+	\caption{Changes in the S1 criteria distributions of the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogue ranks for the Ulrichen station, due to the STW.}
+	\label{fig:changes_S1_analogues}
+\end{figure*}
+
+\begin{figure}[htb]
+	\begin{center}
+		\includegraphics[width=8.2cm]{figures/changes_S1_value.pdf} \\
+		\includegraphics[width=8.3cm]{figures/changes_S1_gain.pdf}
+	\end{center}
+	\caption{Synthesis of the changes in the S1 criteria, due to the STW, for the Ulrichen station, depending on the ranks of the analogue.
+(top) Quantiles of the S1 distributions with and without the STW.
+(bottom) Quantiles of the relative improvements of the S1 criteria when using the STW.}
+	\label{fig:changes_S1}
+\end{figure}
+
+\begin{figure}[htb]
+	\begin{center}
+		\includegraphics[width=8.3cm]{figures/changes_S1_precip_threshold.pdf}
+	\end{center}
+	\caption{Distribution of the median improvements of the S1 criteria, due to the STW, depending on precipitation thresholds at the Ulrichen station.}
+	\label{fig:changes_S1_precip_threshold}
+\end{figure}
+
+\begin{figure}[htb]
+	\begin{center}
+		\includegraphics[width=7cm]{figures/changes_S1_seasons.pdf}
+	\end{center}
+	\caption{Seasonal effect on the median reduction of the S1 criteria for the Ulrichen station due to the STW. DJF: winter, MAM: spring, JJA: summer SON: fall.}
+	\label{fig:changes_S1_seasons}
+\end{figure}
+
+\begin{figure}[htb]
+	\includegraphics[width=8.3cm]{figures/hours_selection_per_season.pdf}
+	\caption{Distribution of the predictors hours in the selected analogue dates depending on the season, for the Ulrichen station.}
+	\label{fig:hours_selection_per_season}
+\end{figure}
+
+\begin{figure}[htb]
+	\includegraphics[width=8.3cm]{figures/hours_selection_per_season_Visp.pdf}
+	\caption{Distribution of the predictors hours in the selected analogue dates depending on the season, for the Visp station.}
+	\label{fig:hours_selection_per_season_Visp}
+\end{figure}
+
+\begin{figure}[htb]
+	\begin{center}
+		\includegraphics[width=8.1cm]{figures/changes_RMSE_value.pdf} \\
+		\includegraphics[width=8.3cm]{figures/changes_RMSE_gain.pdf}
+	\end{center}
+	\caption{Synthesis of the changes in the RMSE criteria, due to the STW, for the Ulrichen station, depending on the ranks of the analogue.
+(top) Quantiles of the RMSE distributions with and without the STW.
+(bottom) Quantiles of the relative improvements of the RMSE criteria when using the STW.}
+	\label{fig:changes_RMSE}
+\end{figure}
+
+\begin{figure}[htb]
+	\includegraphics[width=5cm]{figures/changes_CRPS_precip_threshold.pdf}
+	\caption{Differences of the CRPSS performance score, due to the introduction of the STW, as a function of precipitation thresholds at the Ulrichen station. The stars represent averages.}
+	\label{fig:changes_CRPS_precip_threshold}
+\end{figure}
 
@@
 
-It appears that the sharpness is a bit inferior with the STW in favor of accuracy (Table \ref{table:CRPSS_decomposition_no_recalibration}).
-When using the recalibrated parameters, the components are a bit more balanced, but still the accuracy prevails on the sharpness (Table \ref{table:CRPSS_decomposition_recalibration}).
-Figure \ref{fig:CRPSS_decomposition_precip_thresholds} illustrates the changes (relative to the total CRPS) in sharpness and accuracy for different precipitation thresholds at the Ulrichen station.
-Be it for the 2Z or 2Z-2MI method, the original or the recalibrated parameters, the changes are similar: the improvements concern the accuracy over the sharpness, and this to a greater extent for significant precipitation events.
-The STW does not allow to improve the sharpness, but the improvement in accuracy is significant, and this especially for the days with heavy precipitation.
-In terms of the predicted precipitation distribution, it means that the median of the prediction is closer to the observed values, while the distribution is not more condensed than previously.
-
-\section{Application attempts on the full archive}
-\label{sec:attempts}
-
-The improvement provided by the STW is interesting, mainly for heavy precipitation events, and thus it would be profitable to be able to apply it to the complete archive.
-Unfortunately, there is no long precipitation time series available with a sub-daily time step.
-In order to reconstruct a longer archive of moving 24~h-totals, different disaggregation approaches of the daily time series were assessed and are presented in the following sections.
-
-\subsection{Proportional distribution}
-
-A proportional distribution is certainly the simplest approach that can be performed.
-It consists in allocating proportional parts of the original daily time series into a new moving average of 24~h-totals (Figure \ref{fig:illustration_disaggregation}).
-When using this reconstructed time series on the shorter period, the method performance was degraded (Table \ref{table:disaggregation_proportional} to compare to Table \ref{table:CRPSS_STW}) and was even below the conventional method without STW (Table \ref{table:loss_reduction}).
-The benefit of a better selection of the analogue situations is lost due to a precipitation archive of poor quality.
-
 \begin{figure}[htb]
@@
 
-\begin{table}[htb]
-	\caption{Values of the CRPSS (\%) skill score for the original and the recalibrated parameters (with the sequential method, as described in Section \ref{sec:introduction}) using the STW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
+\clearpage
+
+\begin{table}[htb]
+	\caption{Parameters of the reference method on the atmospheric circulation (2Z).
+The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window).
+The criteria used for the current level of analogy is then provided, as well as the number of analogues.}
+	\footnotesize
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline
+			Level & Variable & Hour & Criteria & Nb \\ 
+			\hline 
+			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{$N_{1}$} \\
+			& Z500 & 24~h & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:method_2Z}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Parameters of the reference method with moisture variables (2Z-2MI). Same conventions as Table \ref{table:method_2Z}}
+	\footnotesize
+	\begin{center}
+		\begin{tabular}{ccccc}
+			\hline 
+			Level & Variable & Hour & Criteria & Nb \\ 
+			\hline 
+			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
+			\hline 
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{$N_{1}$} \\
+			& Z500 & 24~h & & \\ 
+			\hline
+			\multirow{2}{*}{2} & TPW * RH850 & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{2}$} \\
+			& TPW * RH850 & 24~h & & \\ 
+			\hline 
+		\end{tabular} 
+	\end{center}
+	\label{table:method_2Z-2MI}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Calibrated parameters (spatial windows and number of analogues) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) and skill score (\%) of the method on the full archive.}
+	\begin{center}
+		\begin{tabular}{l c c c c }
+			\hline
+			Station & Longitudes & Latitudes & N$_{1}$ & CRPSS \\
+			\hline
+			Ulrichen & 0 $\rightarrow$ 17.5 & 42.5 $\rightarrow$ 47.5 & 40 & 30.73 \\
+			Zermatt & 0 $\rightarrow$ 20 & 37.5 $\rightarrow$ 50 & 35 & 23.87 \\
+			Visp & -2.5 $\rightarrow$ 20 & 40 $\rightarrow$ 47.5 & 30 & 25.11 \\
+			Montana & -2.5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 47.5 & 40 & 32.55 \\
+			Sion & -2.5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 47.5 & 40 & 26.23 \\
+			Aigle & -5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 50 & 50 & 30.59 \\ 
+			\hline
+		\end{tabular}
+	\end{center}
+	\label{table:params_2Z}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Parameters of the moisture variables from the 2Z-2MI method and the corresponding skill score (\%) on the complete archive.
+The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z}, except the number of analogues of the first analogy level (N$_{1}$), which are here different.
+The $5^{th}$ column is the number of analogues for the second level (N$_{2}$).}
+	\begin{center}
+		\begin{tabular}{l c c c c c }
+			\hline
+			Station & Longitudes & Latitudes & N$_{1}$ & N$_{2}$ & CRPSS \\
+			\hline
+			Ulrichen & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 60 & 25 & 34.31 \\
+			Zermatt & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 55 & 25 & 28.28 \\
+			Visp & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 45 & 25 & 28.85 \\
+			Montana & 5 $\rightarrow$ 7.5 & 45 $\rightarrow$ 47.5 & 55 & 30 & 36.11 \\
+			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 90 & 30 & 31.16 \\
+			Aigle & 7.5 & 45 $\rightarrow$ 47.5 & 100 & 35 & 35.82 \\ 
+			\hline
+		\end{tabular}
+	\end{center}
+	\label{table:params_2Z-2MI}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Influence of the archive reduction on the CRPSS. CRPSS values are provided for both considered methods and the differences are expressed in absolute value.}
+	\begin{center}
+		\begin{tabular}{l c c c c }
+			\hline
+			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
+			& 82-07 & $\Delta$ & 82-07 & $\Delta$ \\ 
+			\hline
+			Ulrichen & 29.37 & -1.36 & 33.24 & -1.08 \\
+			Zermatt & 22.20 & -1.67 & 26.95 & -1.32 \\
+			Visp & 23.23 & -1.89 & 27.77 & -1.08 \\
+			Montana & 30.79 & -1.76 & 34.77 & -1.34 \\
+			Sion & 24.78 & -1.45 & 29.36 & -1.80 \\
+			Aigle & 30.57 & -0.01 & 35.95 & 0.13 \\ 
+			\hline
+		\end{tabular}
+	\end{center}
+	\label{table:loss_reduction}
+\end{table}
+
+\begin{table}[htb]
+	\caption{New CRPSS performance scores for both 2Z and 2Z-2MI methods obtained by the STW approach. The differences are expressed regarding the conventional method with the same archive length.}
+	\begin{center}
+		\begin{tabular}{l c c c c}
+			\hline
+			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
+			& STW & $\Delta$ & STW & $\Delta$ \\
+			\hline
+			Ulrichen & 31.12 & 1.74 & 35.44 & 2.20 \\
+			Zermatt & 24.34 & 2.14 & 28.92 & 1.97 \\
+			Visp & 24.39 & 1.16 & 29.42 & 1.64 \\
+			Montana & 31.59 & 0.80 & 36.30 & 1.53 \\
+			Sion & 25.35 & 0.57 & 31.07 & 1.71 \\
+			Aigle & 31.78 & 1.21 & 38.11 & 2.16 \\ 
+			\hline
+		\end{tabular}
+	\end{center}
+	\label{table:CRPSS_STW}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Calibrated parameters (spatial windows and number of analogues) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) with the STW approach.}
+	\begin{center}
+		\begin{tabular}{l c c c }
+			\hline
+			Station & Longitudes & Latitudes & N$_{1}$ \\
+			\hline
+			Ulrichen & 0 $\rightarrow$ 17.5 & 42.5 $\rightarrow$ 50 & 50 \\
+			Zermatt & 0 $\rightarrow$ 17.5 & 40 $\rightarrow$ 50 & 55 \\
+			Visp & -2.5 $\rightarrow$ 20 & 40 $\rightarrow$ 50 & 55 \\
+			Montana & -2.5 $\rightarrow$ 15 & 42.5 $\rightarrow$ 47.5 & 55 \\
+			Sion & -2.5 $\rightarrow$ 15 & 37.5 $\rightarrow$ 50 & 55 \\
+			Aigle & -2.5 $\rightarrow$ 15 & 40 $\rightarrow$ 50 & 75 \\
+			\hline
+		\end{tabular}
+	\end{center}
+	\label{table:params_2Z_new}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Parameters of the moisture variables from the 2Z-2MI method with the STW approach.
+The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z_new}, except the number of analogues of the first analogy level (N$_{1}$), which are here different.
+The $5^{th}$ column is the number of analogues for the second level (N$_{2}$).}
+	\begin{center}
+		\begin{tabular}{l c c c c }
+			\hline
+			Station & Longitudes & Latitudes & N$_{1}$ & N$_{2}$ \\
+			\hline
+			Ulrichen & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 110 & 35 \\
+			Zermatt & 7.5 & 45 $\rightarrow$ 47.5 & 80 & 30 \\
+			Visp & 7.5 & 45 $\rightarrow$ 47.5 & 135 & 35 \\
+			Montana & 5 $\rightarrow$ 7.5 & 45 & 110 & 40 \\
+			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 140 & 50 \\
+			Aigle & 5 $\rightarrow$ 7.5 & 45 & 135 & 45 \\ 
+			\hline
+		\end{tabular}
+	\end{center}
+	\label{table:params_2Z-2MI_new}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Values of the CRPSS (\%) skill score for the newly calibrated parameters using the STW approach.
+The differences are expressed regarding the conventional method with the same archive length.}
+	\begin{center}
+		\begin{tabular}{l c c c c}
+			\hline
+			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
+			& STW & $\Delta$ & STW & $\Delta$ \\
+			\hline
+			Ulrichen & 31.58 & 2.20 & 35.72 & 2.48  \\
+			Zermatt & 24.71 & 2.51 & 29.63 & 2.68 \\
+			Visp & 25.08 & 1.85 & 30.29 & 2.52 \\
+			Montana & 32.22 & 1.43 & 37.15 & 2.38 \\
+			Sion & 26.07 & 1.29 & 31.68 & 2.32 \\
+			Aigle & 32.21 & 1.64 & 38.50 & 2.55 \\
+			\hline
+		\end{tabular}
+	\end{center}
+	\label{table:CRPSS_recalibration}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Changes in sharpness and accuracy relatively to the total CRPS, due to the introduction of the STW.
+The changes are presented for both 2Z and 2Z-2MI methods with the original parameters.
+A decrease of the score is desirable.}
+	\begin{center}
+		\begin{tabular}{l c c c c}
+			\hline
+			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
+			& Sharpness & Accuracy & Sharpness & Accuracy \\
+			\hline
+			Ulrichen & 2.82 & -5.29 & 1.00 & -4.30 \\
+			Zermatt & 2.26 & -5.01 & 0.88 & -3.58 \\
+			Visp & 3.66 & -5.18 & 2.67 & -4.94 \\
+			Montana & 1.62 & -2.78 & 0.57 & -2.91 \\
+			Sion & 2.02 & -2.78 & 0.33 & -2.75 \\
+			Aigle & 0.52 & -2.26 & -1.20 & -2.17 \\ 
+			\hline
+		\end{tabular}
+	\end{center}
+	\label{table:CRPSS_decomposition_no_recalibration}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Same as Table \ref{table:CRPSS_decomposition_no_recalibration} but with the re-calibrated parameters.}
+	\begin{center}
+		\begin{tabular}{l c c c c}
+			\hline
+			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
+			& Sharpness & Accuracy & Sharpness & Accuracy \\
+			\hline
+			Ulrichen & 1.44 & -4.56 & -0.37 & -3.34 \\
+			Zermatt & 0.80 & -4.03 & 0.75 & -4.42 \\
+			Visp & 1.53 & -3.94 & 1.47 & -4.96 \\
+			Montana & -0.27 & -1.80 & 0.06 & -3.71 \\
+			Sion & 0.95 & -2.66 & -0.10 & -3.19 \\
+			Aigle & -0.35 & -2.01 & -2.08 & -1.90 \\ 
+			\hline
+		\end{tabular}
+	\end{center}
+	\label{table:CRPSS_decomposition_recalibration}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Values of the CRPSS (\%) skill score for the original and the recalibrated parameters (with the sequential method, as described in Sect.
+\ref{sec:introduction}) using the STW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
 	\begin{center}
@@
 \end{table}
-
-\subsection{Use of a proxy variable}
-
-As demonstrated in the previous section, the performance improvement brought by the STW is lost when using a simplistic precipitation time series.
-In order to get closer to the chronology of the actual precipitation, the reconstruction procedure must rely on some informative variable.
-Data from the NCEP/NCAR reanalysis 1 (section \ref{sec:data}) was used in this perspective, despite their rough resolution.
-
-The first step consisted in determining which variables from the precipitable water or the relative humidity (at 1000~hPa, 925~hPa or 850~hPa) produces the precipitation chronology that is the most correlated (on non-zero values) with the accurate 6-hourly precipitation time series on the period 1982-2007.
-The location of the most predictive point from the reanalysis grid had to be assessed (closest points: 5\textdegree\ and 7.5\textdegree\ longitude and 45\textdegree\ and 47.5\textdegree\ latitude), as well an eventual time lapse between both series, due to the significant distance separating the weather stations and the reanalysis grid point.
-The most relevant point will probably not be the same for all stations, since one can expect to find the optimum in the direction of the main moisture inflows for the station.
-This assessment must be carried out for each station.
 
@@
 \begin{table}[htb]
-	\caption{Values of the CRPSS (\%) skill score for Zermatt, for the original and the recalibrated parameters (with the sequential method, as described in Section \ref{sec:introduction}) using the STW approach on the disaggregated precipitation time series (short and long periods) by means of variables from the reanalysis.}
+	\caption{Values of the CRPSS (\%) skill score for Zermatt, for the original and the recalibrated parameters (with the sequential method, as described in Sect.
+\ref{sec:introduction}) using the STW approach on the disaggregated precipitation time series (short and long periods) by means of variables from the reanalysis.}
 	\begin{center}
@@
 \end{table}
-
-The results of the correlation analyses (on non-zero values) between the new series reconstituted using the proxy and the actual series are illustrated in Table \ref{table:proxy_correlations} for Zermatt (on the short period, 1982-2007).
-The best proxy is the precipitable water at 45\textdegree\ latitude and 7.5\textdegree\ longitude, with a time offset of -6~h.
-The determination coefficient of 0.721 is higher than that of the series from the proportional distribution (0.698), which confirms that a little information was added to the series of precipitation.
-
-Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the reconstituted series using the proxy of precipitable water at the optimal point (Table \ref{table:proxy_correlations}).
-A slight improvement can be obtained compared to the proportional distribution method, but it is still relatively small, and most of the benefit of the STW is again lost.
-
-These attempts to transpose the STW on the total archive highlight the importance of the actual rainfall chronology.
-The STW is profitable, provided that the precipitation series are close to the observed one.
-Without precipitation series with an accurate sub-daily chronology, the introduction of a STW remains fruitless.
-
-\conclusions  %% \conclusions[modified heading if necessary]
-
-The AM is most often based on a daily time step, due to the availability of long precipitation archives.
-However, it is unlikely that two analogue synoptic situations, that evolve relatively quickly, would correspond optimally at the same hour of the day.
-It is thus more likely that a better match can be found at another time, which can change the selection of the analogues dates.
-
-As \citet{Finet2008} had previously shown, the introduction of a STW allows finding better analogue situations in terms of the atmospheric circulation.
-It has been here demonstrated that the improvement of the S1 criteria values is growing with the rank of the analogue.
-This is due to the accumulation of better analogues within the predicted distributions.
-
-The improvement of the circulation analogy was found to be more important for heavy precipitation events, which are generally related to more dynamic atmospheric situations.
-This dynamism implies more specific circulation patterns that are evolving more rapidly.
-Thus, a STW is found to be of particular interest in this kind of situation, and benefits the prediction of extreme precipitation events.
-
-A seasonal effect has been highlighted, as the STW is more profitable for winter months than summer.
-The reason is likely that the diurnal cycle has a bigger effect in summer than in winter, which results in better analogues at the same time of the day.
-The preference for the same hours in summer has been demonstrated, whereas 75\% of the analogue situations are selected at a different time in winter.
-
-The impact of the STW on the prediction performance has never been assessed before, due to the shortcoming of long precipitation series at a sub-daily time step.
-The impact of the STW approach could be assessed on a 25 years time series with a high temporal resolution.
-After the introduction of the STW, the performance scores increased of the same order of magnitude as if the length of the archive doubled, in this case study.
-
-The parameters were then calibrated again, using the STW.
-Some parameters changed, the main difference being the number of analogues, which systematically and significantly increased compared to the original set.
-A wider selection of analogue situations, containing those whose rank decreased, seemed profitable for the prediction performance.
-The number of good analogues is thus globally increased.
-This change seems to benefit mainly the prediction of days with small precipitation totals.
-
-The importance of the quality of the precipitation archive was also demonstrated, as too simplistic reconstructions of 6-hourly time series lead to a loss of all the improvement brought by better analogue situations identified by the STW.
-The precipitation prediction is improved only when the precipitation chronology is close to the accurate one.
-Attempts to reconstruct longer time series based on a simplistic proportional distribution or using meteorological variables from the NCEP reanalysis 1 dataset as proxy did not succeed.
-Other reanalysis datasets could eventually preform better.
-
-Perspectives of using the STW rely on the availability of long precipitation series at a sub-daily time step and with high accuracy.
-The first source of such data is the simple fact that with time, these archives of high temporal resolution precipitation data are getting longer.
-The second source is the establishment of precipitation reanalysis at a country scale, or the use of reanalysis-driven RCMs (Regional Climate Models) or LAMs (Limited Area Models) on a long period.
-When such precipitation data will be available, the use of a STW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.
-
-\begin{acknowledgements}
-Thanks to Dominique B\'{e}rod for his support and to Renaud Marty for his fruitful collaboration over the years.
-
-Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
-
-The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
-
-NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/. Precipitation time series provided by MeteoSwiss. 
-\end{acknowledgements}
-
-%% REFERENCES
-
-%% The reference list is compiled as follows:
-
-\bibliographystyle{copernicus}
-\bibliography{../_refs/_articles-moving-window}
 

### 2016-05-23 Moving temporal window - HESS/template.tex
Changing mathematical variable names.

@@
 However, it is unlikely that the best analogy happens at the very same hour, but it may occur at a different time of the day.
-In order to assess the potential of finding better analogues at a different hour, a sliding time window (STW) has been introduced on a reduced archive of hourly precipitation totals.
-
-The STW resulted in a better analogy in terms of the atmospheric circulation, with improved values of the analogy criteria on the whole distribution of analogue dates.
+In order to assess the potential of finding better analogues at a different hour, a moving time window (MTW) has been introduced on a reduced archive of hourly precipitation totals.
+
+The MTW resulted in a better analogy in terms of the atmospheric circulation, with improved values of the analogy criteria on the whole distribution of analogue dates.
 The improvement was found to grow with the analogue ranks due to an accumulation of more similar situations in the selection.
@@
 
-The impact of the STW on the prediction performance has been assessed by means of a sub-daily precipitation series transformed into moving 24~h-totals at a 6-hourly time step.
+The impact of the MTW on the prediction performance has been assessed by means of a sub-daily precipitation series transformed into moving 24~h-totals at a 6-hourly time step.
 This resulted in an improvement of the prediction skills, which were even larger after recalibrating the AM parameters.
@@
 These should be available in a near future, either by means of growing observed archives, or by the establishment of precipitation reanalyses through regional modeling.
-Then, the use of a STW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.
+Then, the use of a MTW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.
 
@@
 Here, it has been limited to the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects.
-Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the S1 criteria \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954}, which is a comparison of gradients, over a certain spatial window and at certain hours:
+Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet[Eq.\ \ref{eq:S1}, ][]{Teweles1954} score ($S_{\text{TW}}$), which is a comparison of gradients, over a certain spatial window and at certain hours:
 
@@
 \label{eq:S1}
-S1=100 \frac {\displaystyle \sum_{i} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
+S_{\text{TW}}=100 \frac {\displaystyle \sum_{i} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
 {\displaystyle \sum_{i} max\left\lbrace \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert \right\rbrace }
@@
 The differences are processed separately in both directions.
-The smaller the S1 values, the more similar the pressure fields.
+The smaller the $S_{\text{TW}}$ values, the more similar the pressure fields.
 
@@
 
-Then, $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day, $N_{1}$ being a parameter to calibrate.
+Then, $N_{1}$ dates with the lowest values of $S_{\text{TW}}$ are considered as analogues to the target day, $N_{1}$ being a parameter to calibrate.
 Then, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
@@
 
-The second reference method adds a subsequent level of analogy on moisture variables, compared by means of the root-mean-square error (RMSE) (method 2Z-2MI, Table \ref{table:method_2Z-2MI}).
+The second reference method adds a subsequent level of analogy on moisture variables, compared by means of the root-mean-square error ($E_{\text{RMS}}$) (method 2Z-2MI, Table \ref{table:method_2Z-2MI}).
 This second predictor is a moisture index made of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850) \citep{Bontron2004}.
@@
 AtmoSwing \citep{Horton2016}, which implements this technique, was used in order to calibrate the parameters in the present study.
-The score that is most often considered to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
+The score that is most often considered to assess an AM performance is the Continuous Ranked Probability Score \citep[$S_{\text{CRP}}$,][]{Brown1974, Matheson1976, Hersbach2000}.
 It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$.
 The better the forecast, the smaller the score.
-The mean CRPS of a forecast series of length $n$ can be written:
+It is defined as follows:
 
@@
 \label{eq:CRPS}
-CRPS = \frac{1}{n} \sum_{i=1}^{n} \left(  \int_{-\infty}^{+\infty} \left[ F_{i}(y)-H_{i}(y-y_{i}^{0})\right]^{2} dy \right) 
+S_{\text{CRP}} = \int_{-\infty}^{+\infty} \left[ F(y)-\text{H}(y-y^{0})\right]^{2} \text{d}y ,  
 \end{equation}
-where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value 1 otherwise.
+where $\text{H}(y-y^{0})$ is the Heaviside function that is null when $y-y^{0}<0$, and has the value 1 otherwise.
 \citet{Bontron2004} proposed a decomposition of this score interpreted into a sharpness and an accuracy terms.
@@
 In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution as the reference.
-The CRPSS (\textit{Continuous Ranked Probability Skill Score}) is thus defined as following:
+The Continuous Ranked Probability Skill Score ($S_{\text{SCRP}}$) is thus defined as following:
 
@@
 \label{eq:CRPSS}
-CRPSS = \frac{CRPS-CRPS_{r}}{CRPS_{p}-CRPS_{r}} = 1-\frac{CRPS}{CRPS_{r}}
+S_{\text{SCRP}} = \frac{S_{\text{CRP}}-S_{\text{CRP}}^{r}}{S_{\text{CRP}}^{p}-S_{\text{CRP}}^{r}} = 1-\frac{S_{\text{CRP}}}{S_{\text{CRP}}^{r}}
 \end{equation}
-where $CRPS_{r}$ is the CRPS value for the reference (climatological distribution) and $CRPS_{p}$ would be the one for a perfect forecast (which implies $CRPS_{p}~=~0$).
-A better forecast is characterized by an increase in CRPSS.
+where $S_{\text{CRP}}^{r}$ is the $S_{\text{CRP}}$ value for the reference (climatological distribution) and $S_{\text{CRP}}^{p}$ would be the one for a perfect forecast (which implies $S_{\text{CRP}}^{p}~=~0$).
+A better forecast is characterized by an increase in $S_{\text{SCRP}}$.
 
@@
 However, it can be expected that the analogy of the synoptic situations does not occur systematically at the same time of the day, and that better candidates can be found by shifting to a different hour.
-On this assumption, a sliding time window (STW) was introduced to allow searching for candidates at different hours of the day.
+On this assumption, a moving time window (MTW) was introduced to allow searching for candidates at different hours of the day.
 
@@
 
-The changes due to the introduction of a STW was assessed first in regards to the analogy criteria improvement (Sect.
+The changes due to the introduction of a MTW was assessed first in regards to the analogy criteria improvement (Sect.
 \ref{sec:influence_criteria}), and then in terms of precipitation prediction skill (Sect.
@@
 
-\section{The sliding time window (STW) approach}
+\section{The moving time window (MTW) approach}
 \label{sec:method}
@@
 As sub-daily precipitation time series are usually available on a shorter period than traditional daily time steps, the first assessment consists in assessing the loss of performance resulting from a reduction of a 47~years archive (1961 to 2008) to 25~years (1982 to 2007).
-This change is assessed with the original method, without STW.
+This change is assessed with the original method, without MTW.
 
@@
 
-Figure \ref{fig:changes_S1_analogues} presents the changes in the distributions of the S1 criterion for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogues for the Ulrichen station on the whole calibration period, due to introduction of the STW.
+Figure \ref{fig:changes_S1_analogues} presents the changes in the distributions of the $S_{\text{TW}}$ criterion for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogues for the Ulrichen station on the whole calibration period, due to introduction of the MTW.
 The precipitation target remains as before, that is centered on 18~h~UTC (6~h~UTC to 6~h~UTC the next day).
-The shapes of the distributions of the conventional approach and the STW are similar, but the values of the analogy criteria are now reduced (shifted to the left), and therefore better.
-An increase in the difference between a fixed window and a sliding window is identifiable, which means that the last analogues are further improved.
+The shapes of the distributions of the conventional approach and the MTW are similar, but the values of the analogy criteria are now reduced (shifted to the left), and therefore better.
+An increase in the difference between a fixed window and a moving window is identifiable, which means that the last analogues are further improved.
 The latter effect is due to the accumulation of improvements brought by the new analogue situations in the selection.
 
-The improvements of the S1 criteria are summarized in Fig.
-\ref{fig:changes_S1}, which shows (top) quantiles of the S1 criteria according to the analogue rank for the conventional method and the STW, and (bottom) quantiles of the relative reduction.
-This confirms that all quantile seem similarly reduced (S1 distributions keep their shape), and that this improvement is constantly increasing from the first to the last analogue (Fig.
+The improvements of the $S_{\text{TW}}$ criteria are summarized in Fig.
+\ref{fig:changes_S1}, which shows (top) quantiles of the $S_{\text{TW}}$ criteria according to the analogue rank for the conventional method and the MTW, and (bottom) quantiles of the relative reduction.
+This confirms that all quantile seem similarly reduced ($S_{\text{TW}}$ distributions keep their shape), and that this improvement is constantly increasing from the first to the last analogue (Fig.
 \ref{fig:changes_S1} bottom).
 
-The median of the S1 values reduction (Fig.
+The median of the $S_{\text{TW}}$ values reduction (Fig.
 \ref{fig:changes_S1} bottom) starts approximately at 5~\% for the first analogue and reaches more than 10~\% for the last one.
@@
 The minimum improvement starts from 0 and reaches 2-3\%, meaning that the criteria have been improved on most analogues for every day of the calibration period.
-All other stations have a similar improvement of the S1 criteria, both in terms of distribution shape and amplitude.
+All other stations have a similar improvement of the $S_{\text{TW}}$ criteria, both in terms of distribution shape and amplitude.
 
@@
 
-It can be assumed that the atmospheric conditions with a low dynamism, such as the frequent anticyclonic situations, will not be radically improved by the introduction of the STW.
+It can be assumed that the atmospheric conditions with a low dynamism, such as the frequent anticyclonic situations, will not be radically improved by the introduction of the MTW.
 Conversely, dynamic situations, such as weather disturbances, have a well marked temporal evolution.
 Indeed, the position of the driving elements such as the low-pressure center and the fronts change significantly during a day.
-We can therefore expect to improve more significantly these situations with a higher dynamism when introducing a STW, as better matches to the target situation may be found.
+We can therefore expect to improve more significantly these situations with a higher dynamism when introducing a MTW, as better matches to the target situation may be found.
 
@@
 The results of this analysis are summarized in Fig.
-\ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for days with precipitation (organized into classes) between two thresholds.
+\ref{fig:changes_S1_precip_threshold} by the median reduction of $S_{\text{TW}}$ for days with precipitation (organized into classes) between two thresholds.
 The number of cases per class being reduced, the curves are not as smooth as in previous analyzes.
@@
 Atmospheric dynamics varies greatly from one season to another, which reflects on the performance of the AM that is generally lower between June and August \citep{Bliefernicht2010}.
-It therefore makes sense to verify the effect of the STW separately per season.
-
-A seasonal effect can be observed on the reduction of the S1 criteria due to the STW (Fig.
+It therefore makes sense to verify the effect of the MTW separately per season.
+
+A seasonal effect can be observed on the reduction of the $S_{\text{TW}}$ criteria due to the MTW (Fig.
 \ref{fig:changes_S1_seasons}).
@@
 \ref{fig:hours_selection_per_season}).
-It was found that the new choice of the temporal window in winter, when using the STW approach, is well balanced between the 4 options.
+It was found that the new choice of the temporal window in winter, when using the MTW approach, is well balanced between the 4 options.
 This means a change of 75\% of the analogues selection compared to the conventional approach, which improves the circulation analogy.
@@
 When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidates situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogues, but their dates have changed.
-In contrast to earlier, both a reduction or an increase of the RMSE analogy criterion values are possible.
+In contrast to earlier, both a reduction or an increase of the $E_{\text{RMS}}$ analogy criterion values are possible.
 Indeed, Fig.
-\ref{fig:changes_RMSE} shows an almost insignificant improvement of the RMSE values.
-Unlike for the first level of analogy, the relative improvement of the RMSE values are distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
+\ref{fig:changes_RMSE} shows an almost insignificant improvement of the $E_{\text{RMS}}$ values.
+Unlike for the first level of analogy, the relative improvement of the $E_{\text{RMS}}$ values are distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
 Once again, the results for the other stations are similar.
 
-This result of a globally null improvement of the RMSE values does not mean that the 2Z-2MI method cannot be improved by the STW.
+This result of a globally null improvement of the $E_{\text{RMS}}$ values does not mean that the 2Z-2MI method cannot be improved by the MTW.
 It means that after the selection of the analogues situations in terms of the synoptic circulation, the new candidate dates do not allow to find better analogues in terms of moisture.
@@
 
-A systematic improvement of the S1 values was previously observed.
+A systematic improvement of the $S_{\text{TW}}$ values was previously observed.
 However, finding better analogue situations does not obligatory imply better skills to predict the precipitation.
-Therefore, the impact of the STW introduction, and thus the selection of other analogue dates, has to be assessed on the performance scores.
+Therefore, the impact of the MTW introduction, and thus the selection of other analogue dates, has to be assessed on the performance scores.
 In order to perform this assessment, the 24~h-totals (moving average) at a 6-hourly time step were used (see Sect.
@@
 
-The new performance scores are provided in Table \ref{table:CRPSS_STW}, along with the differences regarding the conventional method with the same archive length.
+The new performance scores are provided in Table \ref{table:CRPSS_MTW}, along with the differences regarding the conventional method with the same archive length.
 The differences ranges from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.
-The introduction of the STW brings an improvement of the performance that is not very large, but that is nevertheless significant.
+The introduction of the MTW brings an improvement of the performance that is not very large, but that is nevertheless significant.
 Moreover, it requires no additional predictor.
-No relationship was found between the improvement of the score and the reduction of the S1 criteria, neither with the season.
+No relationship was found between the improvement of the score and the reduction of the $S_{\text{TW}}$ criteria, neither with the season.
 
@@
 
-The S1 criteria was previously found to be improved to a greater extent for the most dynamic situations related with higher precipitation values (Sect.
+The $S_{\text{TW}}$ criteria was previously found to be improved to a greater extent for the most dynamic situations related with higher precipitation values (Sect.
 \ref{sec:influence_precip}).
@@
 The previous assessment of the performance improvement was established with the original parameters optimized with a fixed time window.
-However, one can assume that the introduction of the STW may change the optimum of some parameters.
+However, one can assume that the introduction of the MTW may change the optimum of some parameters.
 The calibration has then been reprocessed.
@@
 Among these, the east-west dimension of the spatial windows of the circulation analogy tends to decrease.
-More significantly, the optimal number of analogues increases after introducing the STW, of a significant order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method.
+More significantly, the optimal number of analogues increases after introducing the MTW, of a significant order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method.
 The number of analogues of the first analogy level of the 2Z-2MI method even reached three times its previous value for the Visp station.
@@
 As we saw in Fig.
-\ref{fig:changes_S1}, the improvement of the S1 criteria grows along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions.
+\ref{fig:changes_S1}, the improvement of the $S_{\text{TW}}$ criteria grows along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions.
 It seems thus profitable to widen the selection of analogues in order to keep also some whose rank has increased, as they appear to be also relevant to predict precipitation values.
@@
 
-The values of the CRPSS scores for both methods (Table \ref{table:CRPSS_recalibration}) have significantly increased after recalibration.
-With the introduction of the STW, the performance loss related to the reduction of the archive length is compensated.
+The values of the $S_{\text{SCRP}}$ scores for both methods (Table \ref{table:CRPSS_recalibration}) have significantly increased after recalibration.
+With the introduction of the MTW, the performance loss related to the reduction of the archive length is compensated.
 
@@
 
-The CRPS score can be decomposed into two components, namely sharpness and accuracy \citep[see][]{Bontron2004}.
-The impact of the STW has been analyzed on these components and the results can be found in Table \ref{table:CRPSS_decomposition_no_recalibration} for the original parameters and in Table \ref{table:CRPSS_decomposition_recalibration} for the re-calibrated methods.
-The changes are expressed relative to the total CRPS.
+The $S_{\text{CRP}}$ score can be decomposed into two components, namely sharpness and accuracy \citep[see][]{Bontron2004}.
+The impact of the MTW has been analyzed on these components and the results can be found in Table \ref{table:CRPSS_decomposition_no_recalibration} for the original parameters and in Table \ref{table:CRPSS_decomposition_recalibration} for the re-calibrated methods.
+The changes are expressed relative to the total $S_{\text{CRP}}$.
 Both components do not have the same value ranges: accuracy is in our case almost twice the sharpness values.
-Since the CRPS is considered here and not the CRPSS, improved prediction capacity results in a lower score.
+Since the $S_{\text{CRP}}$ is considered here and not the $S_{\text{SCRP}}$, improved prediction capacity results in a lower score.
 A decrease of the score is thus desirable.
 
-It appears that the sharpness is a bit inferior with the STW in favor of accuracy (Table \ref{table:CRPSS_decomposition_no_recalibration}).
+It appears that the sharpness is a bit inferior with the MTW in favor of accuracy (Table \ref{table:CRPSS_decomposition_no_recalibration}).
 When using the recalibrated parameters, the components are a bit more balanced, but still the accuracy prevails on the sharpness (Table \ref{table:CRPSS_decomposition_recalibration}).
 Fig.
-\ref{fig:CRPSS_decomposition_precip_thresholds} illustrates the changes (relative to the total CRPS) in sharpness and accuracy for different precipitation thresholds at the Ulrichen station.
+\ref{fig:CRPSS_decomposition_precip_thresholds} illustrates the changes (relative to the total $S_{\text{CRP}}$) in sharpness and accuracy for different precipitation thresholds at the Ulrichen station.
 Be it for the 2Z or 2Z-2MI method, the original or the recalibrated parameters, the changes are similar: the improvements concern the accuracy over the sharpness, and this to a greater extent for significant precipitation events.
-The STW does not allow to improve the sharpness, but the improvement in accuracy is significant, and this especially for the days with heavy precipitation.
+The MTW does not allow to improve the sharpness, but the improvement in accuracy is significant, and this especially for the days with heavy precipitation.
 In terms of the predicted precipitation distribution, it means that the median of the prediction is closer to the observed values, while the distribution is not more condensed than previously.
@@
 
-The improvement provided by the STW is interesting, mainly for heavy precipitation events, and thus it would be profitable to be able to apply it to the complete archive.
+The improvement provided by the MTW is interesting, mainly for heavy precipitation events, and thus it would be profitable to be able to apply it to the complete archive.
 Unfortunately, there is no long precipitation time series available with a sub-daily time step.
@@
 \ref{fig:illustration_disaggregation}).
-When using this reconstructed time series on the shorter period, the method performance was degraded (Table \ref{table:disaggregation_proportional} to compare to Table \ref{table:CRPSS_STW}) and was even below the conventional method without STW (Table \ref{table:loss_reduction}).
+When using this reconstructed time series on the shorter period, the method performance was degraded (Table \ref{table:disaggregation_proportional} to compare to Table \ref{table:CRPSS_MTW}) and was even below the conventional method without MTW (Table \ref{table:loss_reduction}).
 The benefit of a better selection of the analogue situations is lost due to a precipitation archive of poor quality.
@@
 
-As demonstrated in the previous section, the performance improvement brought by the STW is lost when using a simplistic precipitation time series.
+As demonstrated in the previous section, the performance improvement brought by the MTW is lost when using a simplistic precipitation time series.
 In order to get closer to the chronology of the actual precipitation, the reconstruction procedure must rely on some informative variable.
@@
 
-Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the reconstituted series using the proxy of precipitable water at the optimal point (Table \ref{table:proxy_correlations}).
-A slight improvement can be obtained compared to the proportional distribution method, but it is still relatively small, and most of the benefit of the STW is again lost.
-
-These attempts to transpose the STW on the total archive highlight the importance of the actual rainfall chronology.
-The STW is profitable, provided that the precipitation series are close to the observed one.
-Without precipitation series with an accurate sub-daily chronology, the introduction of a STW remains fruitless.
+Table \ref{table:proxy_CRPSS} presents the $S_{\text{SCRP}}$ scores obtained by the reconstituted series using the proxy of precipitable water at the optimal point (Table \ref{table:proxy_correlations}).
+A slight improvement can be obtained compared to the proportional distribution method, but it is still relatively small, and most of the benefit of the MTW is again lost.
+
+These attempts to transpose the MTW on the total archive highlight the importance of the actual rainfall chronology.
+The MTW is profitable, provided that the precipitation series are close to the observed one.
+Without precipitation series with an accurate sub-daily chronology, the introduction of a MTW remains fruitless.
 
@@
 
-As \citet{Finet2008} had previously shown, the introduction of a STW allows finding better analogue situations in terms of the atmospheric circulation.
-It has been here demonstrated that the improvement of the S1 criteria values is growing with the rank of the analogue.
+As \citet{Finet2008} had previously shown, the introduction of a MTW allows finding better analogue situations in terms of the atmospheric circulation.
+It has been here demonstrated that the improvement of the $S_{\text{TW}}$ criteria values is growing with the rank of the analogue.
 This is due to the accumulation of better analogues within the predicted distributions.
@@
 This dynamism implies more specific circulation patterns that are evolving more rapidly.
-Thus, a STW is found to be of particular interest in this kind of situation, and benefits the prediction of extreme precipitation events.
-
-A seasonal effect has been highlighted, as the STW is more profitable for winter months than summer.
+Thus, a MTW is found to be of particular interest in this kind of situation, and benefits the prediction of extreme precipitation events.
+
+A seasonal effect has been highlighted, as the MTW is more profitable for winter months than summer.
 The reason is likely that the diurnal cycle has a bigger effect in summer than in winter, which results in better analogues at the same time of the day.
@@
 
-The impact of the STW on the prediction performance has never been assessed before, due to the shortcoming of long precipitation series at a sub-daily time step.
-The impact of the STW approach could be assessed on a 25 years time series with a high temporal resolution.
-After the introduction of the STW, the performance scores increased of the same order of magnitude as if the length of the archive doubled, in this case study.
-
-The parameters were then calibrated again, using the STW.
+The impact of the MTW on the prediction performance has never been assessed before, due to the shortcoming of long precipitation series at a sub-daily time step.
+The impact of the MTW approach could be assessed on a 25 years time series with a high temporal resolution.
+After the introduction of the MTW, the performance scores increased of the same order of magnitude as if the length of the archive doubled, in this case study.
+
+The parameters were then calibrated again, using the MTW.
 Some parameters changed, the main difference being the number of analogues, which systematically and significantly increased compared to the original set.
@@
 
-The importance of the quality of the precipitation archive was also demonstrated, as too simplistic reconstructions of 6-hourly time series lead to a loss of all the improvement brought by better analogue situations identified by the STW.
+The importance of the quality of the precipitation archive was also demonstrated, as too simplistic reconstructions of 6-hourly time series lead to a loss of all the improvement brought by better analogue situations identified by the MTW.
 The precipitation prediction is improved only when the precipitation chronology is close to the accurate one.
@@
 
-Perspectives of using the STW rely on the availability of long precipitation series at a sub-daily time step and with high accuracy.
+Perspectives of using the MTW rely on the availability of long precipitation series at a sub-daily time step and with high accuracy.
 The first source of such data is the simple fact that with time, these archives of high temporal resolution precipitation data are getting longer.
 The second source is the establishment of precipitation reanalysis at a country scale, or the use of reanalysis-driven RCMs (Regional Climate Models) or LAMs (Limited Area Models) on a long period.
-When such precipitation data will be available, the use of a STW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.
+When such precipitation data will be available, the use of a MTW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.
 
@@
 	\end{center}
-	\caption{Illustration of the principle of a sliding time window. The larger horizontal bars represent the 24~h precipitation totals.}
+	\caption{Illustration of the principle of a moving time window. The larger horizontal bars represent the 24~h precipitation totals.}
 	\label{fig:principle}
@@
 	\begin{center}
-		\includegraphics[width=15cm]{figures/changes_S1_analogues.png}
-	\end{center}
-	\caption{Changes in the S1 criteria distributions of the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogue ranks for the Ulrichen station, due to the STW.}
+		\includegraphics[width=15cm]{figures/changes_S1_analogues.pdf}
+	\end{center}
+	\caption{Changes in the $S_{\text{TW}}$ criteria distributions of the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogue ranks for the Ulrichen station, due to the MTW.}
 	\label{fig:changes_S1_analogues}
@@
 	\end{center}
-	\caption{Synthesis of the changes in the S1 criteria, due to the STW, for the Ulrichen station, depending on the ranks of the analogue.
-(top) Quantiles of the S1 distributions with and without the STW.
-(bottom) Quantiles of the relative improvements of the S1 criteria when using the STW.}
+	\caption{Synthesis of the changes in the $S_{\text{TW}}$ criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analogue.
+(top) Quantiles of the $S_{\text{TW}}$ distributions with and without the MTW.
+(bottom) Quantiles of the relative improvements of the S1 criteria when using the MTW.}
 	\label{fig:changes_S1}
@@
 	\end{center}
-	\caption{Distribution of the median improvements of the S1 criteria, due to the STW, depending on precipitation thresholds at the Ulrichen station.}
+	\caption{Distribution of the median improvements of the $S_{\text{TW}}$ criteria, due to the MTW, depending on precipitation thresholds at the Ulrichen station.}
 	\label{fig:changes_S1_precip_threshold}
@@
 	\end{center}
-	\caption{Seasonal effect on the median reduction of the S1 criteria for the Ulrichen station due to the STW. DJF: winter, MAM: spring, JJA: summer SON: fall.}
+	\caption{Seasonal effect on the median reduction of the $S_{\text{TW}}$ criteria for the Ulrichen station due to the MTW. DJF: winter, MAM: spring, JJA: summer SON: fall.}
 	\label{fig:changes_S1_seasons}
@@
 	\end{center}
-	\caption{Synthesis of the changes in the RMSE criteria, due to the STW, for the Ulrichen station, depending on the ranks of the analogue.
-(top) Quantiles of the RMSE distributions with and without the STW.
-(bottom) Quantiles of the relative improvements of the RMSE criteria when using the STW.}
+	\caption{Synthesis of the changes in the $E_{\text{RMS}}$ criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analogue.
+(top) Quantiles of the $E_{\text{RMS}}$ distributions with and without the MTW.
+(bottom) Quantiles of the relative improvements of the $E_{\text{RMS}}$ criteria when using the MTW.}
 	\label{fig:changes_RMSE}
@@
 	\includegraphics[width=5cm]{figures/changes_CRPS_precip_threshold.pdf}
-	\caption{Differences of the CRPSS performance score, due to the introduction of the STW, as a function of precipitation thresholds at the Ulrichen station. The stars represent averages.}
+	\caption{Differences of the $S_{\text{SCRP}}$ performance score, due to the introduction of the MTW, as a function of precipitation thresholds at the Ulrichen station. The stars represent averages.}
 	\label{fig:changes_CRPS_precip_threshold}
@@
 	\end{center}
-	\caption{Influence (\%) of the STW on the CRPS components (accuracy and sharpness) relatively to the total CRPS, for the 2Z and 2Z-2MI methods, according to different precipitation thresholds.
+	\caption{Influence (\%) of the MTW on the $S_{\text{CRP}}$ components (accuracy and sharpness) relatively to the total $S_{\text{CRP}}$, for the 2Z and 2Z-2MI methods, according to different precipitation thresholds.
 The results are presented for (top) the original parameters, and (bottom) the recalibrated parameters.
@@
 			\hline 
-			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{$N_{1}$} \\
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{$S_{\text{TW}}$} & \multirow{2}{*}{$N_{1}$} \\
 			& Z500 & 24~h & & \\ 
@@
 			\hline 
-			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{$N_{1}$} \\
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{$S_{\text{TW}}$} & \multirow{2}{*}{$N_{1}$} \\
 			& Z500 & 24~h & & \\ 
 			\hline
-			\multirow{2}{*}{2} & TPW * RH850 & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{2}$} \\
+			\multirow{2}{*}{2} & TPW * RH850 & 12~h & \multirow{2}{*}{$E_{\text{RMS}}$} & \multirow{2}{*}{$N_{2}$} \\
 			& TPW * RH850 & 24~h & & \\ 
@@
 			\hline
-			Station & Longitudes & Latitudes & N$_{1}$ & CRPSS \\
+			Station & Longitudes & Latitudes & $N_{1}$ & $S_{\text{SCRP}}$ \\
 			\hline
@@
 	\caption{Parameters of the moisture variables from the 2Z-2MI method and the corresponding skill score (\%) on the complete archive.
-The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z}, except the number of analogues of the first analogy level (N$_{1}$), which are here different.
-The $5^{th}$ column is the number of analogues for the second level (N$_{2}$).}
+The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z}, except the number of analogues of the first analogy level ($N_{1}$), which are here different.
+The $5^{th}$ column is the number of analogues for the second level ($N_{2}$).}
 	\begin{center}
@@
 			\hline
-			Station & Longitudes & Latitudes & N$_{1}$ & N$_{2}$ & CRPSS \\
+			Station & Longitudes & Latitudes & $N_{1}$ & $N_{2}$ & $S_{\text{SCRP}}$ \\
 			\hline
@@
 \begin{table}[htb]
-	\caption{Influence of the archive reduction on the CRPSS. CRPSS values are provided for both considered methods and the differences are expressed in absolute value.}
+	\caption{Influence of the archive reduction on the $S_{\text{SCRP}}$. $S_{\text{SCRP}}$ values are provided for both considered methods and the differences are expressed in absolute value.}
 	\begin{center}
@@
 \begin{table}[htb]
-	\caption{New CRPSS performance scores for both 2Z and 2Z-2MI methods obtained by the STW approach. The differences are expressed regarding the conventional method with the same archive length.}
+	\caption{New $S_{\text{SCRP}}$ performance scores for both 2Z and 2Z-2MI methods obtained by the MTW approach.
+The differences are expressed regarding the conventional method with the same archive length.}
 	\begin{center}
@@
 			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
-			& STW & $\Delta$ & STW & $\Delta$ \\
+			& MTW & $\Delta$ & MTW & $\Delta$ \\
 			\hline
@@
 	\end{center}
-	\label{table:CRPSS_STW}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Calibrated parameters (spatial windows and number of analogues) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) with the STW approach.}
+	\label{table:CRPSS_MTW}
+\end{table}
+
+\begin{table}[htb]
+	\caption{Calibrated parameters (spatial windows and number of analogues) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) with the MTW approach.}
 	\begin{center}
@@
 			\hline
-			Station & Longitudes & Latitudes & N$_{1}$ \\
+			Station & Longitudes & Latitudes & $N_{1}$ \\
 			\hline
@@
 \begin{table}[htb]
-	\caption{Parameters of the moisture variables from the 2Z-2MI method with the STW approach.
-The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z_new}, except the number of analogues of the first analogy level (N$_{1}$), which are here different.
-The $5^{th}$ column is the number of analogues for the second level (N$_{2}$).}
+	\caption{Parameters of the moisture variables from the 2Z-2MI method with the MTW approach.
+The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z_new}, except the number of analogues of the first analogy level ($N_{1}$), which are here different.
+The $5^{th}$ column is the number of analogues for the second level ($N_{2}$).}
 	\begin{center}
@@
 			\hline
-			Station & Longitudes & Latitudes & N$_{1}$ & N$_{2}$ \\
+			Station & Longitudes & Latitudes & $N_{1}$ & $N_{2}$ \\
 			\hline
@@
 \begin{table}[htb]
-	\caption{Values of the CRPSS (\%) skill score for the newly calibrated parameters using the STW approach.
+	\caption{Values of the $S_{\text{SCRP}}$ (\%) skill score for the newly calibrated parameters using the MTW approach.
 The differences are expressed regarding the conventional method with the same archive length.}
@@
 \begin{table}[htb]
-	\caption{Changes in sharpness and accuracy relatively to the total CRPS, due to the introduction of the STW.
+	\caption{Changes in sharpness and accuracy relatively to the total $S_{\text{CRP}}$, due to the introduction of the MTW.
 The changes are presented for both 2Z and 2Z-2MI methods with the original parameters.
@@
 \begin{table}[htb]
-	\caption{Values of the CRPSS (\%) skill score for the original and the recalibrated parameters (with the sequential method, as described in Sect.
-\ref{sec:introduction}) using the STW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
+	\caption{Values of the $S_{\text{SCRP}}$ (\%) skill score for the original and the recalibrated parameters (with the sequential method, as described in Sect.
+\ref{sec:introduction}) using the MTW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
 	\begin{center}
@@
 \begin{table}[htb]
-	\caption{Values of the CRPSS (\%) skill score for Zermatt, for the original and the recalibrated parameters (with the sequential method, as described in Sect.
-\ref{sec:introduction}) using the STW approach on the disaggregated precipitation time series (short and long periods) by means of variables from the reanalysis.}
+	\caption{Values of the $S_{\text{SCRP}}$ (\%) skill score for Zermatt, for the original and the recalibrated parameters (with the sequential method, as described in Sect.
+\ref{sec:introduction}) using the MTW approach on the disaggregated precipitation time series (short and long periods) by means of variables from the reanalysis.}
 	\begin{center}

### 2016-05-23 Moving temporal window - HESS/template.tex
Removing S1 equation.

@@
 Here, it has been limited to the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects.
-Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet[Eq.\ \ref{eq:S1}, ][]{Teweles1954} score ($S_{\text{TW}}$), which is a comparison of gradients, over a certain spatial window and at certain hours:
-
-\begin{equation}
-\label{eq:S1}
-S_{\text{TW}}=100 \frac {\displaystyle \sum_{i} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
-{\displaystyle \sum_{i} max\left\lbrace \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert \right\rbrace }
-\end{equation}
-where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points of the gridded data describing the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
-The differences are processed separately in both directions.
+Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score ($S_{\text{TW}}$), which is a comparison of gradients, over a certain spatial window and at certain hours.
 The smaller the $S_{\text{TW}}$ values, the more similar the pressure fields.

### 2016-05-23 Moving temporal window - HESS/template.tex
Changes in structure.

@@
 
-The changes due to the introduction of a MTW was assessed first in regards to the analogy criteria improvement (Sect.
+The MTW is explained in Sect.
+\ref{sec:method}.
+As this method requires sub-daily time series, the available archive length is reduced compared to more common daily measurements, which has some consequences on the performance score (Sect.
+\ref{sec:archive_reduction}).
+The benefit of introducing a MTW was assessed first in regards to the analogy criteria improvement (Sect.
 \ref{sec:influence_criteria}), and then in terms of precipitation prediction skill (Sect.
@@
 
-\section{Study area and data}
+\section{Data and method}
+
+\subsection{Study area and data}
 \label{sec:data}
@@
 
-\section{The moving time window (MTW) approach}
+\subsection{The moving time window (MTW) approach}
 \label{sec:method}
@@
 
-\section{Consequences of the archive reduction}
+\subsection{Consequences of the archive reduction}
+\label{sec:archive_reduction}
 
@@
 
-\section{Influence on the analogy criteria}
+\section{Results and discussion}
+
+\subsection{Influence on the analogy criteria}
 \label{sec:influence_criteria}
 
-\subsection{Changes in the atmospheric circulation analogy}
+\subsubsection{Changes in the atmospheric circulation analogy}
 
@@
 
-\subsection{Influence of the weather situation}
+\subsubsection{Influence of the weather situation}
 \label{sec:influence_precip}
@@
 
-\subsection{Seasonal effect}
+\subsubsection{Seasonal effect}
 \label{sec:seasonal_effect}
@@
 
-\subsection{Changes in the moisture analogy}
+\subsubsection{Changes in the moisture analogy}
 
@@
 
-\section{Impact on performance scores}
+\subsection{Impact on performance scores}
 \label{sec:influence_scores}
@@
 
-\subsection{Improvement by precipitation classes}
+\subsubsection{Improvement by precipitation classes}
 \label{sec:improvement_CRPSS_precip_threshold}
@@
 
-\subsection{Recalibrating the parameters}
+\subsubsection{Effect of recalibrating the parameters}
 \label{sec:recalibration}
@@
 
-\subsection{Changes in sharpness and accuracy}
+\subsubsection{Changes in sharpness and accuracy}
 

### 2016-05-26 AtmoSwing - Geoscientific Model Development/template.tex
Renaming figures to insert the new ones.

@@
 
-\citet{Horton2012} identified that the analogy on the atmospheric circulation may not be comprehensive, and that a significant gain was obtained by considering 4 atmospheric levels (1000, 850, 700, and 500~hPa at 12 or 24~h) instead of 2 (Table \ref{table:R6}).
+\citet{Horton2012} identified that the analogy on the atmospheric circulation may not be comprehensive in an alpine environment, and that a significant gain was obtained by considering 4 atmospheric levels (1000, 850, 700, and 500~hPa at 12 or 24~h) instead of 2 (Table \ref{table:R6}).
 The number of analogues ($N_{1}$) was not provided globally, as it was calibrated for every subregion.
@@
 	\includegraphics[width=8.3cm]{figures/fig02.pdf}
+	\caption{Performance scores, for the Swiss Alps, for different AM variants on a single level of analogy \citep{Horton2012a}.}
+	\label{figure:scores_1}
+\end{figure}
+
+\begin{figure}[t]
+	\includegraphics[width=8.3cm]{figures/fig03.pdf}
+	\caption{Performance scores, for the Swiss Alps, for different AM variants on multiple levels of analogy \citep{Horton2012a}.}
+	\label{figure:scores_2}
+\end{figure}
+
+\begin{figure}[t]
+	\includegraphics[width=8.3cm]{figures/fig04.pdf}
 	\caption{The AtmoSwing logo and its 3 modules: the Forecaster, the Viewer and the Optimizer.}
@@
 \begin{figure}[t]
-	\includegraphics[width=8.3cm]{figures/fig03.pdf}
+	\includegraphics[width=8.3cm]{figures/fig05.pdf}
 	\caption{Simplified organizational chart of the AM implementation in AtmoSwing.}
@@
 \begin{figure}[t]
-	\includegraphics[width=8.3cm]{figures/fig04.png}
+	\includegraphics[width=8.3cm]{figures/fig06.png}
 	\caption{Graphical user interface of the Forecaster module. A list of different parameterizations is being processed.}
@@
 \begin{figure*}[t]
-	\includegraphics[width=18cm]{figures/fig05.png}
+	\includegraphics[width=18cm]{figures/fig07.png}
 	\caption{Graphical user interface of the Viewer module (Elevation data from The Shuttle Radar Topography Mission (SRTM), and hydrological network from SwissTopo).}
@@
 \begin{figure}[t]
-	\includegraphics[width=8.3cm]{figures/fig06.png}
+	\includegraphics[width=8.3cm]{figures/fig08.png}
 	\caption{Visualization of multiple lead times on the map (Elevation data from the SRTM, and hydrological network from SwissTopo).}
@@
 \begin{figure}[t]
-	\includegraphics[width=8.3cm]{figures/fig07.png}
+	\includegraphics[width=8.3cm]{figures/fig09.png}
 	\caption{Visualization of the forecasted time series.}
@@
 \begin{figure}[t]
-	\includegraphics[width=8.3cm]{figures/fig08.png}
+	\includegraphics[width=8.3cm]{figures/fig10.png}
 	\caption{Visualization of the forecasted precipitation distribution for a given lead time.}
@@
 \begin{figure}[t]
-	\includegraphics[width=8.3cm]{figures/fig09.png}
+	\includegraphics[width=8.3cm]{figures/fig11.png}
 	\caption{Example of a Monte\textendash Carlo analysis on the PC-2Z (Table \ref{table:R1}) AM.
@@
 \begin{figure}[t]
-	\includegraphics[width=8.3cm]{figures/fig10.png}
+	\includegraphics[width=8.3cm]{figures/fig12.png}
 	\caption{Example of a Monte\textendash Carlo analysis on the PC-2Z-2MI (Table \ref{table:R2}) AM.

### 2016-05-27 AtmoSwing - Geoscientific Model Development/template.tex
Addition of the variables exploration analysis.

@@
 
+\section{Data and case study description}
+\label{sec:data_and_case_study}
+
+\subsection{Data}
+\label{sec:data}
+
+Predictors are generally reanalysis datasets (as archive) and outputs of a global numerical weather prediction models for the target situation in operational forecasting.
+Reanalysis datasets, such as the NCEP/NCAR reanalysis I \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996}, the NCEP/DOE reanalysis II \citep{Kanamitsu2002}, ERA-40 \citep{Uppala2005} are often used and can be input in AtmoSwing.
+Other observed predictors can also be used, such as Sea Surface Temperature \citep[SST, ][]{Reynolds2007}.
+\citet{Bontron2004} proposed that the minimum length of the archive should be 30 years to forecast usual situations, and 40 years or more for intense events.
+
+The predictors describing the target situation in operational forecasting can, for example, result from GFS \citep[Global Forecast System,][]{Kanamitsu1991,Kanamitsu1989}, which is operated by NCEP and NOAA.
+
+The predictand can be 6-houry data, or more often daily time series.
+The most used predictand is the daily precipitation, usually averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.
+These time series are frequently normalized by the precipitation value for a return period of 10~years \citep{Djerboua2001}.
+This normalization allows for an easier comparison between subregions subject to different precipitation regimes, and thus to better identify the most important contributions.
+
+\subsection{Case study description}
+\label{sec:case_study}
+
+Some results will be illustrated throughout this article for the alpine upper Rh\^{o}ne catchment in Switzerland (Fig.\ \ref{figure:map}).
+Even though the region is rather small (5524~km$^{2}$), the meteorological influences related to extreme weather conditions varies substantially within it \citep[see][]{Horton2012}.
+The gauging stations in the catchment were thus aggregated into 10~subregions (Fig.\ \ref{figure:map}): (1) Swiss Chablais, (2) Trient Valley, (3) West Bernese Alps, (4) Lower Rhone Valley, (5) Left side valleys, (6) Southern ridges, (7) Upper Rhone Valley, (8) Southeast ridges, (9) East Bernese Alps, and (10) Conches Valley.
+
 \section{The Analogue Method}
@@
 The search for analogy aims thus at connecting the forecasted synoptic situation with a local predictand (temperature, precipitation, etc), which is more difficult to simulate by numerical models.
-
-\subsection{Data}
-\label{sec:data}
-
-Predictors are generally reanalysis datasets (as archive) and outputs of a global numerical weather prediction models for the target situation in operational forecasting.
-Reanalysis datasets, such as the NCEP/NCAR reanalysis I \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996}, the NCEP/DOE reanalysis II \citep{Kanamitsu2002}, ERA-40 \citep{Uppala2005} are often used and can be input in AtmoSwing.
-Other observed predictors can also be used, such as Sea Surface Temperature \citep[SST, ][]{Reynolds2007}.
-\citet{Bontron2004} proposed that the minimum length of the archive should be 30 years to forecast usual situations, and 40 years or more for intense events.
-
-The predictors describing the target situation in operational forecasting can, for example, result from GFS \citep[Global Forecast System,][]{Kanamitsu1991,Kanamitsu1989}, which is operated by NCEP and NOAA.
-
-The predictand can be 6-houry data, or more often daily time series.
-The most used predictand is the daily precipitation, usually averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.
-These time series are frequently normalized by the precipitation value for a return period of 10~years \citep{Djerboua2001}.
-This normalization allows for an easier comparison between subregions subject to different precipitation regimes, and thus to better identify the most important contributions.
 
@@
 
-\citet{Horton2012} identified that the analogy on the atmospheric circulation may not be comprehensive in an alpine environment, and that a significant gain was obtained by considering 4 atmospheric levels (1000, 850, 700, and 500~hPa at 12 or 24~h) instead of 2 (Table \ref{table:R6}).
-The number of analogues ($N_{1}$) was not provided globally, as it was calibrated for every subregion.
+Every variable of the NCEP/NCAR reanalysis was systematically assessed for each of the identified subregions of the study area (Sect.
+\ref{sec:case_study}).
+The present assessment considers every subregion separately and optimizes the spatial window and the number of analogues for every combination of variables, pressure levels, times of observation, and subregions (using the sequential calibration tool implemented in AtmoSwing, see Sect.
+\ref{sec:atmoswing-calibration}).
+Even though the best predictors may vary from one place to another due to different meteorological influences (see Fig.
+\ref{figure:variable_exploration_Chablais} for the 30 best predictors for the Chablais region, and Fig.
+\ref{figure:variable_exploration_SE_crests} for the Southeast ridges), 2 main conclusions can be drawn from the NCEP/NCAR reanalysis dataset for the area of interest, that meet those from \citet{Bontron2004}: (1) the variables describing the atmospheric circulation (pressure fields or geopotential heights) are the ones with the highest prediction capacity (the precipitation rate is even rarely selected in the 30 best predictors), and (2) these are better when compared by means of the S1 criteria (asterisk in Fig.
+\ref{figure:variable_exploration_Chablais} and \ref{figure:variable_exploration_SE_crests}) instead of the RMSE.
+The reason for this latter point is the better representation of the atmospheric circulation information when considering the shape of a pressure field rather than its values.
+
+\citet{Horton2012} identified that the analogy on the atmospheric circulation as defined by \citet{Bontron2004} may not be comprehensive in an alpine environment, and that considering 4 atmospheric levels (1000, 850, 700, and 500~hPa at 12 or 24~h) instead of 2 could improve the performance (Table \ref{table:R6} -- the number of analogues $N_{1}$ was not provided globally, as it was calibrated for every subregion).
+The change in performance scores is illustrated in Fig.
+\ref{figure:scores_1} for the different subregions of the study area.
 An equivalent structure was also optimized by means of generic algorithms (PC-4Zgo), which is the topic of another paper \citep{Horton2016b}.
+As these new parametrizations provide performance gains for alpine catchments under varying meteorological influences (Fig.
+\ref{figure:scores_1}), they are recommended for operational use.
 
@@
 Similarly, an equivalent structure was optimized \citep[PC-4Zgo-2MIgo,][]{Horton2016b}.
+The change in the performance scores, for the method with 2 levels of analogy, is illustrated in Fig.
+\ref{figure:scores_2} for the study area.
+As previously, we would recommend using these new parametrizations for alpine catchments.
 
@@
 \citet{BenDaoud2010} also reconsidered the parameters of the moisture index and ended up with both 925~hPa and 700~hPa levels, at 12~h and 24~h, or at every time step (6~h) between 06~h and 30~h (Table \ref{table:R4b}).
+The performance of this parameterization for our case study is presented in Fig.
+\ref{figure:scores_2}.
 
@@
 \begin{figure}[t]
+	\includegraphics[width=8.3cm]{figures/map.pdf}
+	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland. (source: Swisstopo)}
+	\label{figure:map}
+\end{figure}
+
+\begin{figure}[t]
+	\includegraphics[width=7.5cm]{figures/variable_exploration_Chablais.pdf}
+	\caption{Performance score (CRPSS) of the 30 best variables from the NCEP/NCAR reanalysis dataset, when considered separately (no combination), for the Chablais region (Sect.
+\ref{sec:case_study}).
+The analogy criteria is S1 when there is an asterisk next to the variable name, and RMSE otherwise.
+Color illustrates the variable type: green = atmospheric circulation, blue = moisture, orange = temperature, yellow = radiation, purple = vertical velocity, and gray = other.
+SLP stands for sea level pressure, and Z for geopotential height}
+	\label{figure:variable_exploration_Chablais}
+\end{figure}
+
+\begin{figure}[t]
+	\includegraphics[width=7.5cm]{figures/variable_exploration_SE_crests.pdf}
+	\caption{Same as Fig. \ref{figure:variable_exploration_SE_crests}, but for the southeast ridges.}
+	\label{figure:variable_exploration_SE_crests}
+\end{figure}
+
+\begin{figure}[t]
 	\includegraphics[width=8.3cm]{figures/fig01.pdf}
@@
 	\includegraphics[width=8.3cm]{figures/fig03.pdf}
-	\caption{Performance scores, for the Swiss Alps, for different AM variants on multiple levels of analogy \citep{Horton2012a}.}
+	\caption{Performance scores, for the Swiss Alps, for different AM variants on multiple levels of analogy \citep{Horton2012a}. Same conventions as Fig. \ref{figure:scores_2}.}
 	\label{figure:scores_2}

### 2016-08-15 Genetic algorithms - Journal of Climate/template.tex
Corrections of the first reviewer.

@@
 
-\authors{Pascal Horton\correspondingauthor{Pascal Horton, Terranum, Rue de l'industrie 35 bis, 1030 Bussigny, Switzerland.}\thanks{Current affiliation: Terranum, Bussigny, Switzerland}}
+\authors{Pascal Horton\correspondingauthor{Pascal Horton, University of Bern, Hallerstrasse 12, 3012 Bern, Switzerland.}\thanks{Current affiliation: Institute of Geography \& Oeschger Centre for Climate Change Research, University of Bern, Switzerland}}
 
@@
 The AM needs to be adapted to every new region considered, because the leading meteorological influences may be location specific.
-Even the selection of the pressure levels and the temporal windows should be reconsidered, when not the predictor variable itself.
+Even the selection of the pressure levels and the temporal windows should be reconsidered, if not the predictor variable itself.
 
@@
 \begin{itemize}
-	\item Uniform mutation: The mutation rate is constant and equal for every gene of each individual; they all have the same probability to mutate.
+	\item Uniform mutation: The mutation rate ($p_{mut}$) is constant and equal for every gene of each individual; they all have the same probability to mutate.
 When a gene is selected for mutation, a new random value is assigned, according to a uniform law.
@@
 It allows isolating the effect of a parameter under different combinations of the other options.
-A procedure by stages was adopted, analyzing in details and in a systematic way every variants of the implemented operators, in combination with multiple other options and parameters in order to take into account eventual co-dependencies.
+A procedure by stages was adopted, analyzing in details and in a systematic way every variant of the implemented operators, in combination with multiple other options and parameters in order to take into account eventual co-dependencies.
 The goal here is not to focus on the performance score obtained through optimization, neither the values of the new optimized parameters \citep[covered in][]{Horton2016b}, but to explain how to use GAs to optimize AMs in an efficient way.
@@
 
-The mutation operators based on a variable normal or variable uniform laws work very poorly and are difficult to configure.
+The mutation operators based on variable normal or variable uniform laws work very poorly and are difficult to configure.
 Many operators present more or less the same performance scores and require a variable amount of assessments.
@@
 \end{itemize}
+
+where $p_{mut}$ is the mutation rate (or mutation probability), $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a threshold chosen by the user to maintain a minimum search radius when the number of generations $G>G_{m,r}$.
 

### 2016-08-15 Genetic algorithms - Journal of Climate/template.tex
Corrections of the first reviewer.

@@
 Many operators present more or less the same performance scores and require a variable amount of assessments.
-The convergence analysis \citep[see][]{Horton2012a} allows to highlight three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
+The convergence analysis \citep[see][]{Horton2012a} allows one to highlight three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
 Thus, different optimizations were further performed using variants of these 3 operators (Table \ref{tab:assessed_mutation_operators_bis}).

### 2016-08-17 AtmoSwing - Geoscientific Model Development/template.tex
Changing "analogue" for "analog".

@@
 
-\title{AtmoSwing (v1.4): Analogue Technique Model for Statistical weather forecastING}
+\title{AtmoSwing (v1.4): Analog Technique Model for Statistical weather forecastING}
 
@@
 
-The Analogue Method allows forecasting local meteorological variables of interest (predictand), such as the daily precipitation, on the basis of synoptic variables (predictors).
+The Analog Method allows forecasting local meteorological variables of interest (predictand), such as the daily precipitation, on the basis of synoptic variables (predictors).
 It relies on the fact that similar meteorological influences are likely to result in similar local effects.
@@
 
-AtmoSwing is an open source software that implements the Analogue Method in a very flexible way, so that different variants can be handled dynamically, by parameterization through XML files.
+AtmoSwing is an open source software that implements the Analog Method in a very flexible way, so that different variants can be handled dynamically, by parameterization through XML files.
 It is made of 3 tools: the Forecaster to perform operational forecasts, the Viewer to display the results, and the Optimizer to establish the relationship between the predictand and predictors.
@@
 This is particularly true for a predictand much required in hydrometeorological applications, namely the precipitation amount over a given domain and time duration.
-Incidentally, the forecast will be proposed as a statistical distribution based on the values taken by the predictand in the set of analogues selected, unless one considers only the single best analogue, which may not prove the most efficient \citep{Bontron2005}.
-
-In addition to precipitation forecasting, the Analogue Method (AM), or an equivalent, was also used for short to medium term forecasting of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+Incidentally, the forecast will be proposed as a statistical distribution based on the values taken by the predictand in the set of analogs selected, unless one considers only the single best analog, which may not prove the most efficient \citep{Bontron2005}.
+
+In addition to precipitation forecasting, the Analog Method (AM), or an equivalent, was also used for short to medium term forecasting of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
 \citet{Guilbaud1997} performed a literature review about the use of the AM in long-term forecasting and identified operational applications for monthly forecasts in many countries, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal forecasts: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
@@
 
-\section{The Analogue Method}
+\section{The Analog Method}
 \label{sec:method}
@@
 The perfect analogy does not exist, but sufficiently similar situations leading to similar effects can be identified.
-Thus, two states of the atmosphere that are alike are called analogues \citep{Lorenz1969}.
+Thus, two states of the atmosphere that are alike are called analogs \citep{Lorenz1969}.
 To be relevant, this analogy must be selected by optimizing the following elements:
@@
 	\item The analogy criterion, needed to compare the variables on the chosen spatial and temporal windows, is a score used for ranking past situations according to their degree of similarity with the target situation.
-	\item The ideal number of analogue situations is the best compromise in order to take into account local variability and to maximize useful synoptic information \citep{Bontron2004}.
+	\item The ideal number of analog situations is the best compromise in order to take into account local variability and to maximize useful synoptic information \citep{Bontron2004}.
 \end{itemize}
 
-Because of the chaotic nature of the atmosphere, two analogue situations quickly diverge over time \citep{Lorenz1969}.
+Because of the chaotic nature of the atmosphere, two analog situations quickly diverge over time \citep{Lorenz1969}.
 Thus, the AM has strong limitations regarding the temporal extrapolation \citep{Bontron2004}.
@@
 
-	The $N_{1}$ dates with the lowest values of S1 are considered as analogues, in terms of the general circulation, to the target day. The number of analogues, $N_{1}$, is a parameter to calibrate.
+	The $N_{1}$ dates with the lowest values of S1 are considered as analogs, in terms of the general circulation, to the target day. The number of analogs, $N_{1}$, is a parameter to calibrate.
 
 	\item Subsequent level(s) of analogy: beyond the similarity of airflows, one may look for similarities in other variables of interest, such as moisture variables.
-Therefore, the $N_{1}$ analogues are subsampled once again on the basis of another variable in order to obtain a lower number of analogue dates, $N_{2}$.
+Therefore, the $N_{1}$ analogs are subsampled once again on the basis of another variable in order to obtain a lower number of analog dates, $N_{2}$.
 The S1 criterion is usually not relevant for other predictors that the atmospheric circulation.
@@
 
-	This process can be repeated, by subsampling a decreasing number of analogues, $N_{i}$, according to various meteorological variables.
+	This process can be repeated, by subsampling a decreasing number of analogs, $N_{i}$, according to various meteorological variables.
 
@@
 The basis of the method was introduced by \citet{Lorenz1969}, who considered the analogy of the geopotential field on different pressure levels.
-In addition, the analogue situations were to belong to the same period of the year to be comparable in terms of distribution of solar energy.
+In addition, the analog situations were to belong to the same period of the year to be comparable in terms of distribution of solar energy.
 This preselection was later implemented as a moving selection of more or less two months around the target date.
@@
 \ref{sec:case_study}).
-The present assessment considers every subregion separately and optimizes the spatial window and the number of analogues for every combination of variables, pressure levels, times of observation, and subregions (using the sequential calibration tool implemented in AtmoSwing, see Sect.
+The present assessment considers every subregion separately and optimizes the spatial window and the number of analogs for every combination of variables, pressure levels, times of observation, and subregions (using the sequential calibration tool implemented in AtmoSwing, see Sect.
 \ref{sec:atmoswing-calibration}).
@@
 
-\citet{Horton2012} identified that the analogy on the atmospheric circulation as defined by \citet{Bontron2004} may not be comprehensive in an alpine environment, and that considering 4 atmospheric levels (1000, 850, 700, and 500~hPa at 12 or 24~h) instead of 2 could improve the performance (Table \ref{table:R6} -- the number of analogues $N_{1}$ was not provided globally, as it was calibrated for every subregion).
+\citet{Horton2012} identified that the analogy on the atmospheric circulation as defined by \citet{Bontron2004} may not be comprehensive in an alpine environment, and that considering 4 atmospheric levels (1000, 850, 700, and 500~hPa at 12 or 24~h) instead of 2 could improve the performance (Table \ref{table:R6} -- the number of analogs $N_{1}$ was not provided globally, as it was calibrated for every subregion).
 The change in performance scores is illustrated in Fig.
@@
 \citet{Horton2012} also integrated an analogy on the moisture flux, after the circulation analogy on the 4 atmospheric levels (Table \ref{table:R7}).
-The number of analogues ($N_{1}$, $N_{2}$) were calibrated for every subregion.
+The number of analogs ($N_{1}$, $N_{2}$) were calibrated for every subregion.
 Similarly, an equivalent structure was optimized \citep[PC-4Zgo-2MIgo,][]{Horton2016b}.
@@
 Indeed, the statistical approach pointed at some bias in estimates of the numerical model, which may have been adjusted by taking into account the intrinsic local climatology from the AM.
-Moreover, the under-dispersion of the ensemble forecast from the numerical model has been corrected using analogues \citep{Hamill2006}.
+Moreover, the under-dispersion of the ensemble forecast from the numerical model has been corrected using analogs \citep{Hamill2006}.
 Correction of ensemble forecast under-dispersion by means of the AM is also used operationally at EDF (\'{E}lectricit\'{e} de France).
@@
 
-Another limitation is the fact that extreme events may be under-represented in the considered sample of analogue dates.
+Another limitation is the fact that extreme events may be under-represented in the considered sample of analog dates.
 Indeed, in a limited weather archive, events with high return periods are not so numerous.
-Their number is certainly lower than the standard number of analogues considered, which can introduce a bias in the forecast.
+Their number is certainly lower than the standard number of analogs considered, which can introduce a bias in the forecast.
 There are however techniques to correct this bias \citep[see][]{Marty2010}.
@@
 Every analogy criterion, prediction score, searching and sorting functions, data manipulation, and so on, is tested.
-The integration tests specific to the AM rely on the results of another analogue sorting software developed at the LTHE \textendash INPG university of Grenoble.
+The integration tests specific to the AM rely on the results of another analog sorting software developed at the LTHE \textendash INPG university of Grenoble.
 They ensure that the results of AtmoSwing are exactly equivalent to their model, given the same parameters and data.
@@
 The software then performs successively as many analogy levels as the user specified, with all the predictors he wants.
-Each level of analogy processed results in an object containing target dates, analogue dates, values of the analogy criteria, and other data.
+Each level of analogy processed results in an object containing target dates, analog dates, values of the analogy criteria, and other data.
 This object can be saved in a NetCDF file and/or can be injected into a new analogy level.
@@
 
-Although processing an analogue forecast for a given target date is fast, when optimizing the AM, forecasts are re-processed over long periods of several decades, which may become very time consuming.
+Although processing an analog forecast for a given target date is fast, when optimizing the AM, forecasts are re-processed over long periods of several decades, which may become very time consuming.
 Thus, great effort has been made in order to reduce the processing time to a minimum.
@@
 The software also use the linear algebra library Eigen 3 \citep{Guennebaud2010} for calculations on vectors and matrices, which resulted in time saving.
-Multi-threading is also implemented so that the search for analogue situations in the archive is distributed among the available threads.
+Multi-threading is also implemented so that the search for analog situations in the archive is distributed among the available threads.
 
@@
 Many other improvements allowed saving more time, for example the use of the quicksort method \citep{Hoare1962a} to sort the date vectors according to the values of analogy criteria.
-Different implementations were tested (many remain in the code as alternatives) in order to select the most efficient: for example, when storing analogue dates according to their criteria value, it is faster to insert them in a fixed-size array rather than storing them all and sorting the array subsequently.
+Different implementations were tested (many remain in the code as alternatives) in order to select the most efficient: for example, when storing analog dates according to their criteria value, it is faster to insert them in a fixed-size array rather than storing them all and sorting the array subsequently.
 
@@
 	\item better search for dates in temporal vectors starting from the previous index (reduction of the range of the array to explore),
-	\item better management of the analogue vectors,
+	\item better management of the analog vectors,
 	\item preprocessed gradients on geopotential fields when using the S1 criteria,
@@
 It then interpolates linearly the gridded data to match the resolution of the archive (for example 2.5\textdegree\ in the case of the NCEP/NCAP reanalysis I).
-The analogues dates are next sought according to the selected parameterization, and the predictand data are associated with the corresponding dates.
+The analogs dates are next sought according to the selected parameterization, and the predictand data are associated with the corresponding dates.
 The results are finally saved in auto-describing NetCDF files.
@@
 A solution, presented in Sect.
-\ref{sec:optimization-operational}, consists in increasing the number of analogue situations to keep with the lead time.
-This technique is available in AtmoSwing, as the number of analogues can be specified for every lead time, making such approach easily accessible.
+\ref{sec:optimization-operational}, consists in increasing the number of analog situations to keep with the lead time.
+This technique is available in AtmoSwing, as the number of analogs can be specified for every lead time, making such approach easily accessible.
 
@@
 The recommended use is thus to set up a cron task on a Linux server in order to trigger the forecast every 30 minutes.
-When using GFS outputs, this would provide 4 forecasts a day with a reduced delay between GFS outputs availability and the analogue forecast.
+When using GFS outputs, this would provide 4 forecasts a day with a reduced delay between GFS outputs availability and the analog forecast.
 
@@
 The Viewer automatically gathers the similar AMs and provides a composite view of the optimal forecasts per subregion.
-The user can however choose to display a specific parameterization for the whole region, which is more consistent in terms of homogeneity of the analogue dates.
+The user can however choose to display a specific parameterization for the whole region, which is more consistent in terms of homogeneity of the analog dates.
 
@@
 \ref{figure:atmoswing-viewer-timeseries}).
-By default, the plot contains the usual 3 considered percentiles (90$^{th}$, 60$^{th}$, and 20$^{th}$), along with the 10 best analogues with a color code from yellow (tenth) to red (first).
+By default, the plot contains the usual 3 considered percentiles (90$^{th}$, 60$^{th}$, and 20$^{th}$), along with the 10 best analogs with a color code from yellow (tenth) to red (first).
 The 10 year return period is also displayed in order to put the forecast in perspective.
-The user can choose to hide any data or to display supplementary information (all analogues, all 10$^{th}$ percentiles, or all return periods) in the left panel.
+The user can choose to hide any data or to display supplementary information (all analogs, all 10$^{th}$ percentiles, or all return periods) in the left panel.
 Traces of previous days forecasts are also automatically loaded and displayed in order to inform on the stability of the forecasts.
@@
 \ref{figure:atmoswing-viewer-distribution}).
-This is useful when working on extreme precipitation, as comparing the distribution of all analogues versus the 10 best analogues provides information in order to interpret the forecast (trend to under/overestimation).
+This is useful when working on extreme precipitation, as comparing the distribution of all analogs versus the 10 best analogs provides information in order to interpret the forecast (trend to under/overestimation).
 Distribution of the analogy criteria (not shown) can also be displayed in order to identify eventual discontinuities in the criteria values.
 
-Finally, one can see the details of the analogue dates, along with the predictand and the criteria values in an interactive spreadsheet (not shown).
+Finally, one can see the details of the analog dates, along with the predictand and the criteria values in an interactive spreadsheet (not shown).
 
@@
 He noted that the 60$^{th}$ percentile was better to forecast precipitation amounts for common situations, but for strong to extreme events, the 90$^{th}$ percentile turned out to be a better indicator.
-It is therefore necessary to pay particular attention to the 90$^{th}$ percentile which, when reaching high values, may be indicative of a situation related to extreme precipitations, due the presence of several analogue dates with significant observed precipitations amounts in the distribution \citep{Djerboua2001}.
+It is therefore necessary to pay particular attention to the 90$^{th}$ percentile which, when reaching high values, may be indicative of a situation related to extreme precipitations, due the presence of several analog dates with significant observed precipitations amounts in the distribution \citep{Djerboua2001}.
 \citet{Bontron2004} made the same observation: he found the 60$^{th}$ percentile to be best for occurrence forecasting, but the 90$^{th}$ percentile to be the most informative in order to forecast medium to high precipitation amounts ($P > P10/10$, one tenth of the 10~year return period value).
-In this regard, operators should pay particular attention to the distribution of the best analogues.
+In this regard, operators should pay particular attention to the distribution of the best analogs.
 If, for example, it is shifted to higher values, there is a risk of under-estimating the event when considering the middle of the full distribution.
-Obviously, if the target situation has its best analogues with high precipitations, then this situation is likely to be rare.
-So, when collecting a fixed number of analogue situations, the worst ones are likely to be more common and will contribute to lower the resulting precipitation distribution, therefore a trend towards underestimation.
+Obviously, if the target situation has its best analogs with high precipitations, then this situation is likely to be rare.
+So, when collecting a fixed number of analog situations, the worst ones are likely to be more common and will contribute to lower the resulting precipitation distribution, therefore a trend towards underestimation.
 
@@
 The statistical relationship is established on a calibration period that is as long as possible.
-For every day of this period, a search for analogues is performed, the predictand data are associated with the corresponding dates and a forecast score is calculated.
-During the search for analogues situations, 120 days around the target date are excluded (thus excluding data in the same year) in order to consider only truly independent candidates days.
+For every day of this period, a search for analogs is performed, the predictand data are associated with the corresponding dates and a forecast score is calculated.
+During the search for analogs situations, 120 days around the target date are excluded (thus excluding data in the same year) in order to consider only truly independent candidates days.
 
@@
 The difference of the continuous deterministic forecasts compared to discrete ones is that they provide non-discrete values that must be evaluated with distance measures.
-In our application, the distribution of the analogues is summarized by a chosen percentile.
+In our application, the distribution of the analogs is summarized by a chosen percentile.
 Available scores are the following:
@@
 Most applications mainly rely on the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
-It allows assessing the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$.
+It allows assessing the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$.
 The better the forecast, the smaller the score.
@@
 		\item temporal window (hour of observation \textendash e.g. 6, or 12~h~UTC),
-		\item initial analogue numbers (e.g. $N_{1}=50$).
+		\item initial analog numbers (e.g. $N_{1}=50$).
 	\end{enumerate}
@@
 (iv) The spatial window grows up by repeating the previous steps, until no improvement is reached.
-		\item The number of analogue situations is then reconsidered and optimized for the current level of analogy.
+		\item The number of analog situations is then reconsidered and optimized for the current level of analogy.
 		\item A new level of analogy can then be added, based on other variables (such as the moisture index) on predefined pressure levels and time frames.
-The number of analogues for the next level of analogy is initiated at a chosen value.
+The number of analogs for the next level of analogy is initiated at a chosen value.
 Then, the procedure starts again from step (a) for the new level.
-The parameters calibrated on the previous analogue levels are fixed and do not change (except the numbers of analogues of all levels of analogy, that are optimized once again at the final stage).
+The parameters calibrated on the previous analog levels are fixed and do not change (except the numbers of analogs of all levels of analogy, that are optimized once again at the final stage).
 	\end{enumerate}
-	\item Finally, the numbers of analogues are re-assessed for the different levels of analogy. This is done iteratively by varying the number of analogues of each level in a systematic way.
+	\item Finally, the numbers of analogs are re-assessed for the different levels of analogy. This is done iteratively by varying the number of analogs of each level in a systematic way.
 \end{enumerate}
@@
 Unlike conventional calibration, the spatial windows on Z500 and Z1000 were not necessarily overlapping.
-Thus, 9 parameters were varying together (8 for the spatial windows and 1 for the number of analogues)
+Thus, 9 parameters were varying together (8 for the spatial windows and 1 for the number of analogs)
 
@@
 The dilution of a part of the relevant synoptic information has therefore not necessarily a significant negative impact on performance, while ignoring some of this information leads to undesirable loss of performance.
-It is the same for the analogues number (not shown), for which, past an optimum, the upper slope of the distribution decreases slowly.
-
-The same analysis has been conducted on the AM with 2 levels of analogy, PC-2Z-2MI (Table \ref{table:R2}), and the results on the number of analogues on the first and the second level are illustrated in Fig.
+It is the same for the analogs number (not shown), for which, past an optimum, the upper slope of the distribution decreases slowly.
+
+The same analysis has been conducted on the AM with 2 levels of analogy, PC-2Z-2MI (Table \ref{table:R2}), and the results on the number of analogs on the first and the second level are illustrated in Fig.
 \ref{figure:monte_carlo_r2}.
-One can see that the AM is not very sensitive to the number of analogues on the first level of analogy, when considering a second level afterwards, as long as this number is not too small.
+One can see that the AM is not very sensitive to the number of analogs on the first level of analogy, when considering a second level afterwards, as long as this number is not too small.
 The trend on the second level is more apparent, but a large tolerance seems possible.
@@
 To optimize further the AM, it can be considered that the further the lead time, the more uncertain the synoptic forecasts and therefore the more uncertain the precipitation forecasts could be.
-This can been addressed by reconsidering, for each lead-time, the optimal number of analogues to select, for re-forecast data from a particular NWP model \citep{Thevenot2004}.
-The underlying idea is that if the model proves perfect, then the number of analogues should remain close to that obtained in the perfect progonosis framework.
+This can been addressed by reconsidering, for each lead-time, the optimal number of analogs to select, for re-forecast data from a particular NWP model \citep{Thevenot2004}.
+The underlying idea is that if the model proves perfect, then the number of analogs should remain close to that obtained in the perfect progonosis framework.
 While if the forecast becomes irrelevant, for example at distant lead times, the AM should propose a forecast closer and closer to the climatological distribution of the predictand.
-The optimal number of analogue situations will thus increase with the lead time, and should be optimized for every lead time on the re-forecast dataset \citep[see][for the details]{Thevenot2004}.
+The optimal number of analog situations will thus increase with the lead time, and should be optimized for every lead time on the re-forecast dataset \citep[see][for the details]{Thevenot2004}.
 This option is implemented in AtmoSwing Forecaster (see Sect.
@@
 This approach takes into account the uncertainties on predictors from the global model.
-Its implementation is a combination of the selected analogue days associated with each of the traces.
-Rainfall distribution is then established on all analogues.
+Its implementation is a combination of the selected analog days associated with each of the traces.
+Rainfall distribution is then established on all analogs.
 The forecast on the ensemble was found to be more accurate than the deterministic control for a lead time of 4 days and more \citep{Thevenot2004}.
@@
 	\item a weighting of the predictor grids \citep[see][]{Bliefernicht2010};
-	\item assessment of potential indicators based on the properties of the distribution of all analogues or the 10 best, for example;
+	\item assessment of potential indicators based on the properties of the distribution of all analogs or the 10 best, for example;
 	\item assessment of the relevance of an automatic interpretation of the distribution in order to provide the most likely expected value;
@@
 \citet{Lorenz1969} introduced the concept and established the basis of the AM.
-He considered looking for analogues on the geopotential field (at 200, 500 and 850~hPa) with a corrected Euclidean distance averaged on the 3 levels.
+He considered looking for analogs on the geopotential field (at 200, 500 and 850~hPa) with a corrected Euclidean distance averaged on the 3 levels.
 
@@
 The data were then based on 37 radiosounding over Europe and condensed by a principal component analysis.
-The first 25 analogues on the geopotential at 700~hPa were considered, and multiple local regressions between precipitation, SLP, and the temperature at 700~hPa were established on these analogues before being applied to the target situation \citep{Guilbaud1997}.
+The first 25 analogs on the geopotential at 700~hPa were considered, and multiple local regressions between precipitation, SLP, and the temperature at 700~hPa were established on these analogs before being applied to the target situation \citep{Guilbaud1997}.
 The archives were split by season to consider comparable situations in terms of distribution of solar energy \citep{Lorenz1969}.
@@
 
-Thereafter, the geopotential was considered at 1000~hPa and 700~hPa and the analogues selection was done in two stages: first according to an Euclidean distance in the space of the principal components of the geopotential field at 700~hPa, and then according to a correlation criterion (on the geopotential field at 700 and 1000~hPa, as well as on the thickness between these two levels) in order to remove days close in distance but too dissimilar in pattern \citep{Guilbaud1997}.
-The local regression approach to determine precipitation was eventually abandoned in favor of the direct probabilistic forecasting (synthesized by the percentiles 20, 60 and 90~\%), as it is performed today by interpolating linearly over the cumulative empirical distribution of daily precipitation measured at the analogue days \citep{Guilbaud1997, Guilbaud1998}.
-
-\citet{Wilson1980} sought the 20 best analogues on the geopotential field at 500 and 1000~hPa using the Teweles\textendash Wobus (S1) criterion (Eq.
+Thereafter, the geopotential was considered at 1000~hPa and 700~hPa and the analogs selection was done in two stages: first according to an Euclidean distance in the space of the principal components of the geopotential field at 700~hPa, and then according to a correlation criterion (on the geopotential field at 700 and 1000~hPa, as well as on the thickness between these two levels) in order to remove days close in distance but too dissimilar in pattern \citep{Guilbaud1997}.
+The local regression approach to determine precipitation was eventually abandoned in favor of the direct probabilistic forecasting (synthesized by the percentiles 20, 60 and 90~\%), as it is performed today by interpolating linearly over the cumulative empirical distribution of daily precipitation measured at the analog days \citep{Guilbaud1997, Guilbaud1998}.
+
+\citet{Wilson1980} sought the 20 best analogs on the geopotential field at 500 and 1000~hPa using the Teweles\textendash Wobus (S1) criterion (Eq.
 \ref{eq:S1}), which allows for a comparison of the gradients and thus an analogy of the atmospheric circulation.
 This work has demonstrated the best performance of the AM compared to classical regression based approaches.
-\citet{Woodcock1980} used the same criterion on the SLP fields to select 50~analogues in order to forecast maximum daily temperatures.
+\citet{Woodcock1980} used the same criterion on the SLP fields to select 50~analogs in order to forecast maximum daily temperatures.
 After comparing S1 to other criteria from the literature, or combinations of these, \citet{Guilbaud1998} confirmed that S1 is the most efficient.
@@
 \citet{Guilbaud1997} stopped using PCA in order to work directly with the raw data interpolated on grids, which resulted in an improvement, especially when considering the S1 criterion instead of the Euclidean distance.
-The number of analogues considered was 50.
+The number of analogs considered was 50.
 When using multiple predictors, they combined the criteria values calculated on each atmospheric level and each temporal window using an arithmetic mean.
@@
 These windows are more able to represent the specific atmospheric influences for each region.
-He also highlighted the dependency between the optimal number of analogues and the archive size: the shorter the archive, the lower the number of analogues.
+He also highlighted the dependency between the optimal number of analogs and the archive size: the shorter the archive, the lower the number of analogs.
 
@@
 	\caption{Example of a Monte\textendash Carlo analysis on the PC-2Z-2MI (Table \ref{table:R2}) AM.
-Results are illustrated for the number of analogues on the first and second level of analogy, along with the results of the sequential calibration (red cross).}
+Results are illustrated for the number of analogs on the first and second level of analogy, along with the results of the sequential calibration (red cross).}
 	\label{figure:monte_carlo_r2}
@@
 The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window).
-The criteria used for the current level of analogy is then provided, as well as the number of analogues.}
+The criteria used for the current level of analogy is then provided, as well as the number of analogs.}
 	\begin{tabular}{ccccc}

### 2016-08-17 Genetic algorithms - Journal of Climate/template.tex
Changing "analogue" for "analog".

@@
 
-\title{Global Optimization of the Analogue Method by Means of Genetic Algorithms}
+\title{Global Optimization of the Analog Method by Means of Genetic Algorithms}
 
@@
 
-\abstract{The Analogue Method is based on a statistical relationship between synoptic atmospheric variables (predictors) and local weather (predictand), which we aim at forecasting.
+\abstract{The Analog Method is based on a statistical relationship between synoptic atmospheric variables (predictors) and local weather (predictand), which we aim at forecasting.
 This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic sequential procedure.
@@
 These kind of optimization techniques need however to be tailored to the problem to solve.
-Multiple combinations of algorithms had to be assessed, and even new operators were developed, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of Genetic Algorithms to optimize the Analogue Method.
+Multiple combinations of algorithms had to be assessed, and even new operators were developed, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of Genetic Algorithms to optimize the Analog Method.
 These recommendations are the main outcome of this work.
-It opens new perspective for the improvement of the Analogue Method, and its application to new regions or to new predictands.
+It opens new perspective for the improvement of the Analog Method, and its application to new regions or to new predictands.
 }
@@
 
-The Analogue Method (AM) relies on the hypothesis that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Lorenz1956, Lorenz1969, Duband1970, Bontron2005}.
+The Analog Method (AM) relies on the hypothesis that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Lorenz1956, Lorenz1969, Duband1970, Bontron2005}.
 The principle consists in sampling a certain number of past situations based on different atmospheric variables (predictors) in order to build a probabilistic forecast for a local weather variable of interest (predictand).
@@
 
-Even though the method is rather simple compared to numerical weather prediction (NWP) models, it contains a certain number of parameters one needs to determine, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criteria itself, and finally the number of analogue situations to keep at each subsampling level.
+Even though the method is rather simple compared to numerical weather prediction (NWP) models, it contains a certain number of parameters one needs to determine, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criteria itself, and finally the number of analog situations to keep at each subsampling level.
 
@@
 Up to now, the optimization of the method has been undertaken by semi-automatic sequential calibration procedures \citep[see][for its definition]{Bontron2004, Horton2016}.
-However, the selection of predictor variables, pressure levels and temporal windows had still to be made manually before optimizing the spatial windows and the number of analogues.
+However, the selection of predictor variables, pressure levels and temporal windows had still to be made manually before optimizing the spatial windows and the number of analogs.
 Testing multiple combinations of these is very combinatorial and becomes quickly cumbersome, especially when considering multiple predictors within the same level of analogy.
@@
 Thus, due to the sequential approach, the risk of ending in a local optimum is high and can not be avoided.
-Indeed, during the AM calibration it has been found that the resulting parameters may vary with initial choices (such as the number of analogues).
+Indeed, during the AM calibration it has been found that the resulting parameters may vary with initial choices (such as the number of analogs).
 
@@
 
-\section{The Analogue Method}
+\section{The Analog Method}
 \label{sec:am}
@@
 To cope with seasonal effects, candidate dates are extracted within a period of 4 months centered around the target date, for every year of the archive.
-The $n_{1}$ (parameter to calibrate) dates with the lowest values of S1 are considered as analogues to the target day.
+The $n_{1}$ (parameter to calibrate) dates with the lowest values of S1 are considered as analogs to the target day.
 Then, the daily observed precipitation amount of the $n_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
@@
 850~hPa, see][]{Bontron2004}.
-When adding a second level of analogy, $n_{2}$ dates are subsampled in the $n_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
+When adding a second level of analogy, $n_{2}$ dates are subsampled in the $n_{1}$ analogs on the atmospheric circulation, to end up with a smaller number of analog situations.
 
 The score that is most often used to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
-It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$.
+It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$.
 The better the prediction, the smaller the score.
@@
 geopotential, or temperature), discrete (e.g.
-number of analogues to select, from 1 to 40), or continuous.
+number of analogs to select, from 1 to 40), or continuous.
 For example, a chromosome may looks like:
@@
 \end{equation}
-where, for the level of analogy $i$ and the predictor number $j$, $p_{i,j}$ is the pressure level, $h_{i,j}$ is the temporal window, $\lambda w_{i,j}$ and $\lambda e_{i,j}$ are the western and eastern longitudes of the spatial window, $\varphi s_{i,j}$ and $\varphi n_{i,j}$ are its southerly and northerly latitudes, and $n_{i,j}$ is the number of analogues.
+where, for the level of analogy $i$ and the predictor number $j$, $p_{i,j}$ is the pressure level, $h_{i,j}$ is the temporal window, $\lambda w_{i,j}$ and $\lambda e_{i,j}$ are the western and eastern longitudes of the spatial window, $\varphi s_{i,j}$ and $\varphi n_{i,j}$ are its southerly and northerly latitudes, and $n_{i,j}$ is the number of analogs.
 A chromosome for the simple AM on the atmospheric circulation only (Sect.

### 2016-08-17 Moving temporal window - HESS/template.tex
Changing "analogue" for "analog".

@@
 
-\title{The Analogue Method for Precipitation Forecasting: Finding Better Analogue Situations at a Sub-Daily Time Step}
+\title{The Analog Method for Precipitation Forecasting: Finding Better Analog Situations at a Sub-Daily Time Step}
 
@@
 
-\runningtitle{Finding Better Analogue Situations at a Sub-Daily Time Step}
+\runningtitle{Finding Better Analog Situations at a Sub-Daily Time Step}
 
@@
 \begin{abstract}
-The Analogue Method (AM) aims at forecasting local weather variables (predictands), such as precipitations, by means of a statistical relationship with predictors at a synoptic scale.
+The Analog Method (AM) aims at forecasting local weather variables (predictands), such as precipitations, by means of a statistical relationship with predictors at a synoptic scale.
 The analogy is generally assessed in the first place on the geopotential field by mean of a comparison of the gradients, in order to sample the days with a similar atmospheric circulation.
 
-The search for candidate situations, for a given target day, is usually undertaken by comparing the state of the atmosphere at fixed hours of the day, for both the target day and the candidate analogues.
+The search for candidate situations, for a given target day, is usually undertaken by comparing the state of the atmosphere at fixed hours of the day, for both the target day and the candidate analogs.
 The constraint being the use of daily time series, due to the length of available archives they provide, and the unavailability of equivalent archives at a finer time step.
 However, it is unlikely that the best analogy happens at the very same hour, but it may occur at a different time of the day.
-In order to assess the potential of finding better analogues at a different hour, a moving time window (MTW) has been introduced on a reduced archive of hourly precipitation totals.
-
-The MTW resulted in a better analogy in terms of the atmospheric circulation, with improved values of the analogy criteria on the whole distribution of analogue dates.
-The improvement was found to grow with the analogue ranks due to an accumulation of more similar situations in the selection.
+In order to assess the potential of finding better analogs at a different hour, a moving time window (MTW) has been introduced on a reduced archive of hourly precipitation totals.
+
+The MTW resulted in a better analogy in terms of the atmospheric circulation, with improved values of the analogy criteria on the whole distribution of analog dates.
+The improvement was found to grow with the analog ranks due to an accumulation of more similar situations in the selection.
 Moreover, the improvement is even more important for days with heavy precipitation events, which are generally related to more dynamic atmospheric situations, where timing is more specific.
 
-A seasonal effect has also been identified, with larger improvements in winter than in summer, supposedly due to the stronger effect of the diurnal cycle in summer, which favors predictors at the same hour for target and analogues.
+A seasonal effect has also been identified, with larger improvements in winter than in summer, supposedly due to the stronger effect of the diurnal cycle in summer, which favors predictors at the same hour for target and analogs.
 
@@
 
-The Analogue Method (AM) is based on the principle that two relatively similar synoptic situations may produce relatively similar local effects \citep{Lorenz1956, Lorenz1969}.
+The Analog Method (AM) is based on the principle that two relatively similar synoptic situations may produce relatively similar local effects \citep{Lorenz1956, Lorenz1969}.
 Multiple variations of the methods exist and listings can be found in \citet{Horton2016} or \citet{BenDaoud2015}.
@@
 The first method is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005, Marty2012}.
-Searching analogue situations for a target day starts by a preselection step of the potential candidate for analogy.
+Searching analog situations for a target day starts by a preselection step of the potential candidate for analogy.
 Here, it has been limited to the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects.
@@
 
-Then, $N_{1}$ dates with the lowest values of $S_{\text{TW}}$ are considered as analogues to the target day, $N_{1}$ being a parameter to calibrate.
+Then, $N_{1}$ dates with the lowest values of $S_{\text{TW}}$ are considered as analogs to the target day, $N_{1}$ being a parameter to calibrate.
 Then, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
@@
 This second predictor is a moisture index made of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850) \citep{Bontron2004}.
-When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
-When a second level of analogy is added, a higher number of $N_{1}$ analogues is kept on the first level.
+When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogs on the atmospheric circulation, to end up with a smaller number of analog situations.
+When a second level of analogy is added, a higher number of $N_{1}$ analogs is kept on the first level.
 
@@
 The score that is most often considered to assess an AM performance is the Continuous Ranked Probability Score \citep[$S_{\text{CRP}}$,][]{Brown1974, Matheson1976, Hersbach2000}.
-It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$.
+It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$.
 The better the forecast, the smaller the score.
@@
 The AM is usually implemented with a daily time step, due to the availability of long precipitation archives that have no equivalent at a finer resolution.
-Therefore, the analogue situations are assessed on the basis of a daily time step, by comparing predictors at fixed hours of the day, otherwise one would not know what precipitation values to assign to them.
+Therefore, the analog situations are assessed on the basis of a daily time step, by comparing predictors at fixed hours of the day, otherwise one would not know what precipitation values to assign to them.
 However, it can be expected that the analogy of the synoptic situations does not occur systematically at the same time of the day, and that better candidates can be found by shifting to a different hour.
@@
 
-Previous tests showed the benefit, in terms of analogy criteria values, of searching for analogue synoptic situations at a finer time step, but without assessing the impact on the forecast skills \citep{Finet2008}.
+Previous tests showed the benefit, in terms of analogy criteria values, of searching for analog synoptic situations at a finer time step, but without assessing the impact on the forecast skills \citep{Finet2008}.
 In order to assess this potential improvement of the prediction, precipitation data with a resolution of 10 minutes, on a respectable archive length, was used (Sect.
@@
 Due to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed.
-The time series (on the period 1982-2007) come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle (Fig.
+The time series (on the period 1982--2007) come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle (Fig.
 \ref{fig:map}), which are subject to various meteorological influences \citep{Horton2012}.
@@
 
-In order to assess the benefit of searching analogue situations at a sub-daily time step, an appropriate precipitation series is required.
+In order to assess the benefit of searching analog situations at a sub-daily time step, an appropriate precipitation series is required.
 On the basis of high resolution time series (Sect.
@@
 
-The target situations and their corresponding observed precipitation values (used for validation) do not change, because the forecast is always established for a fixed period of the target day (6-30~h), as before.
+The target situations and their corresponding observed precipitation values (used for validation) do not change, because the forecast is always established for a fixed period of the target day (6--30~h), as before.
 The difference is that the candidates are 4~times more numerous (Fig.
@@
 
-Based on some preliminary tests (not shown), no constraint was added in order to restrict the selection of multiple analogues within the same candidate dates.
+Based on some preliminary tests (not shown), no constraint was added in order to restrict the selection of multiple analogs within the same candidate dates.
 
@@
 
-When searching for analogues on the geopotential heights, as in the 2Z method, there are now 4 times more candidates than before, which obviously allows to find better matches.
-
-Figure \ref{fig:changes_S1_analogues} presents the changes in the distributions of the $S_{\text{TW}}$ criterion for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogues for the Ulrichen station on the whole calibration period, due to introduction of the MTW.
+When searching for analogs on the geopotential heights, as in the 2Z method, there are now 4 times more candidates than before, which obviously allows to find better matches.
+
+Figure \ref{fig:changes_S1_analogs} presents the changes in the distributions of the $S_{\text{TW}}$ criterion for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogs for the Ulrichen station on the whole calibration period, due to introduction of the MTW.
 The precipitation target remains as before, that is centered on 18~h~UTC (6~h~UTC to 6~h~UTC the next day).
 The shapes of the distributions of the conventional approach and the MTW are similar, but the values of the analogy criteria are now reduced (shifted to the left), and therefore better.
-An increase in the difference between a fixed window and a moving window is identifiable, which means that the last analogues are further improved.
-The latter effect is due to the accumulation of improvements brought by the new analogue situations in the selection.
+An increase in the difference between a fixed window and a moving window is identifiable, which means that the last analogs are further improved.
+The latter effect is due to the accumulation of improvements brought by the new analog situations in the selection.
 
 The improvements of the $S_{\text{TW}}$ criteria are summarized in Fig.
-\ref{fig:changes_S1}, which shows (top) quantiles of the $S_{\text{TW}}$ criteria according to the analogue rank for the conventional method and the MTW, and (bottom) quantiles of the relative reduction.
-This confirms that all quantile seem similarly reduced ($S_{\text{TW}}$ distributions keep their shape), and that this improvement is constantly increasing from the first to the last analogue (Fig.
+\ref{fig:changes_S1}, which shows (top) quantiles of the $S_{\text{TW}}$ criteria according to the analog rank for the conventional method and the MTW, and (bottom) quantiles of the relative reduction.
+This confirms that all quantile seem similarly reduced ($S_{\text{TW}}$ distributions keep their shape), and that this improvement is constantly increasing from the first to the last analog (Fig.
 \ref{fig:changes_S1} bottom).
@@
 The median of the $S_{\text{TW}}$ values reduction (Fig.
-\ref{fig:changes_S1} bottom) starts approximately at 5~\% for the first analogue and reaches more than 10~\% for the last one.
-This increasing trend with the analogue rank can be explained by the accumulation of better analogues in the distribution.
-The minimum improvement starts from 0 and reaches 2-3\%, meaning that the criteria have been improved on most analogues for every day of the calibration period.
+\ref{fig:changes_S1} bottom) starts approximately at 5~\% for the first analog and reaches more than 10~\% for the last one.
+This increasing trend with the analog rank can be explained by the accumulation of better analogs in the distribution.
+The minimum improvement starts from 0 and reaches 2--3\%, meaning that the criteria have been improved on most analogs for every day of the calibration period.
 All other stations have a similar improvement of the $S_{\text{TW}}$ criteria, both in terms of distribution shape and amplitude.
@@
 One hypothesis is that the diurnal effects of the summer months have an influence on the atmospheric circulation, at least in the lower layers.
-This effect is based on the daily cycle and good analogues are essentially found for the same hours or time windows.
+This effect is based on the daily cycle and good analogs are essentially found for the same hours or time windows.
 
@@
 It was found that the new choice of the temporal window in winter, when using the MTW approach, is well balanced between the 4 options.
-This means a change of 75\% of the analogues selection compared to the conventional approach, which improves the circulation analogy.
-
-On the contrary, the summer months have a preference for the initial temporal window (Z500 24h \& Z1000 12h), due to more pronounced diurnal effects which reduces the potential for improvement of the criteria.
+This means a change of 75\% of the analogs selection compared to the conventional approach, which improves the circulation analogy.
+
+On the contrary, the summer months have a preference for the initial temporal window (Z500 24~h \& Z1000 12~h), due to more pronounced diurnal effects which reduces the potential for improvement of the criteria.
 Other seasons are between these two extremes, which is consistent with their respective improvements.
@@
 
-When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidates situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogues, but their dates have changed.
+When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidates situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogs, but their dates have changed.
 In contrast to earlier, both a reduction or an increase of the $E_{\text{RMS}}$ analogy criterion values are possible.
@@
 This result of a globally null improvement of the $E_{\text{RMS}}$ values does not mean that the 2Z-2MI method cannot be improved by the MTW.
-It means that after the selection of the analogues situations in terms of the synoptic circulation, the new candidate dates do not allow to find better analogues in terms of moisture.
+It means that after the selection of the analogs situations in terms of the synoptic circulation, the new candidate dates do not allow to find better analogs in terms of moisture.
 However, the selected dates have changed in the first level of analogy, and thus also in the final selection, which can potentially improve the performance scores on the predictand.
@@
 A systematic improvement of the $S_{\text{TW}}$ values was previously observed.
-However, finding better analogue situations does not obligatory imply better skills to predict the precipitation.
-Therefore, the impact of the MTW introduction, and thus the selection of other analogue dates, has to be assessed on the performance scores.
+However, finding better analog situations does not obligatory imply better skills to predict the precipitation.
+Therefore, the impact of the MTW introduction, and thus the selection of other analog dates, has to be assessed on the performance scores.
 In order to perform this assessment, the 24~h-totals (moving average) at a 6-hourly time step were used (see Sect.
 \ref{sec:data}).
-The target dates remain unchanged, since the original time slot (6~h~UTC - 6~h~UTC the next day) is kept, and thus the performance scores can be directly compared with the former ones.
+The target dates remain unchanged, since the original time slot (6~h~UTC -- 6~h~UTC the next day) is kept, and thus the performance scores can be directly compared with the former ones.
 
@@
 Among these, the east-west dimension of the spatial windows of the circulation analogy tends to decrease.
-More significantly, the optimal number of analogues increases after introducing the MTW, of a significant order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method.
-The number of analogues of the first analogy level of the 2Z-2MI method even reached three times its previous value for the Visp station.
-It seems as if the method perceive the increase in the archive length and diversity by allowing to extract more analogues.
+More significantly, the optimal number of analogs increases after introducing the MTW, of a significant order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method.
+The number of analogs of the first analogy level of the 2Z-2MI method even reached three times its previous value for the Visp station.
+It seems as if the method perceive the increase in the archive length and diversity by allowing to extract more analogs.
 As we saw in Fig.
-\ref{fig:changes_S1}, the improvement of the $S_{\text{TW}}$ criteria grows along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions.
-It seems thus profitable to widen the selection of analogues in order to keep also some whose rank has increased, as they appear to be also relevant to predict precipitation values.
-The number of good analogues is thus globally increased.
-
-This increase in number of analogues has a slight effect on the performance of the different precipitation classes.
+\ref{fig:changes_S1}, the improvement of the $S_{\text{TW}}$ criteria grows along with the rank of the analog, which shows an accumulation of better analog situations in the distributions.
+It seems thus profitable to widen the selection of analogs in order to keep also some whose rank has increased, as they appear to be also relevant to predict precipitation values.
+The number of good analogs is thus globally increased.
+
+This increase in number of analogs has a slight effect on the performance of the different precipitation classes.
 The same analysis as in Sect.
@@
 The results are generally very similar, but a slight performance increase of small precipitation values can be observed at the expense of higher amounts.
-The change in the analogues numbers is likely to be responsible for this difference in the performance distributions.
+The change in the analogs numbers is likely to be responsible for this difference in the performance distributions.
 
@@
 When using this reconstructed time series on the shorter period, the method performance was degraded (Table \ref{table:disaggregation_proportional} to compare to Table \ref{table:CRPSS_MTW}) and was even below the conventional method without MTW (Table \ref{table:loss_reduction}).
-The benefit of a better selection of the analogue situations is lost due to a precipitation archive of poor quality.
+The benefit of a better selection of the analog situations is lost due to a precipitation archive of poor quality.
 
@@
 The first step consisted in determining which variables from the precipitable water or the relative humidity (at 1000~hPa, 925~hPa or 850~hPa) produces the precipitation chronology that is the most correlated (on non-zero values) with the accurate 6-hourly precipitation time series on the period 1982-2007.
-The location of the most predictive point from the reanalysis grid had to be assessed (closest points: 5\textdegree\ and 7.5\textdegree\ longitude and 45\textdegree\ and 47.5\textdegree\ latitude), as well an eventual time lapse between both series, due to the significant distance separating the weather stations and the reanalysis grid point.
+The location of the most predictive point from the reanalysis grid had to be assessed (closest points: 5--7.5° E and 45--47.5° N), as well an eventual time lapse between both series, due to the significant distance separating the weather stations and the reanalysis grid point.
 The most relevant point will probably not be the same for all stations, since one can expect to find the optimum in the direction of the main moisture inflows for the station.
@@
 
-The results of the correlation analyses (on non-zero values) between the new series reconstituted using the proxy and the actual series are illustrated in Table \ref{table:proxy_correlations} for Zermatt (on the short period, 1982-2007).
-The best proxy is the precipitable water at 45\textdegree\ latitude and 7.5\textdegree\ longitude, with a time offset of -6~h.
+The results of the correlation analyses (on non-zero values) between the new series reconstituted using the proxy and the actual series are illustrated in Table \ref{table:proxy_correlations} for Zermatt (on the short period, 1982--2007).
+The best proxy is the precipitable water at 45° N and 7.5° E, with a time offset of -6~h.
 The determination coefficient of 0.721 is higher than that of the series from the proportional distribution (0.698), which confirms that a little information was added to the series of precipitation.
@@
 The AM is most often based on a daily time step, due to the availability of long precipitation archives.
-However, it is unlikely that two analogue synoptic situations, that evolve relatively quickly, would correspond optimally at the same hour of the day.
-It is thus more likely that a better match can be found at another time, which can change the selection of the analogues dates.
-
-As \citet{Finet2008} had previously shown, the introduction of a MTW allows finding better analogue situations in terms of the atmospheric circulation.
-It has been here demonstrated that the improvement of the $S_{\text{TW}}$ criteria values is growing with the rank of the analogue.
-This is due to the accumulation of better analogues within the predicted distributions.
+However, it is unlikely that two analog synoptic situations, that evolve relatively quickly, would correspond optimally at the same hour of the day.
+It is thus more likely that a better match can be found at another time, which can change the selection of the analogs dates.
+
+As \citet{Finet2008} had previously shown, the introduction of a MTW allows finding better analog situations in terms of the atmospheric circulation.
+It has been here demonstrated that the improvement of the $S_{\text{TW}}$ criteria values is growing with the rank of the analog.
+This is due to the accumulation of better analogs within the predicted distributions.
 
@@
 A seasonal effect has been highlighted, as the MTW is more profitable for winter months than summer.
-The reason is likely that the diurnal cycle has a bigger effect in summer than in winter, which results in better analogues at the same time of the day.
-The preference for the same hours in summer has been demonstrated, whereas 75\% of the analogue situations are selected at a different time in winter.
+The reason is likely that the diurnal cycle has a bigger effect in summer than in winter, which results in better analogs at the same time of the day.
+The preference for the same hours in summer has been demonstrated, whereas 75\% of the analog situations are selected at a different time in winter.
 
@@
 The parameters were then calibrated again, using the MTW.
-Some parameters changed, the main difference being the number of analogues, which systematically and significantly increased compared to the original set.
-A wider selection of analogue situations, containing those whose rank decreased, seemed profitable for the prediction performance.
-The number of good analogues is thus globally increased.
+Some parameters changed, the main difference being the number of analogs, which systematically and significantly increased compared to the original set.
+A wider selection of analog situations, containing those whose rank decreased, seemed profitable for the prediction performance.
+The number of good analogs is thus globally increased.
 This change seems to benefit mainly the prediction of days with small precipitation totals.
 
-The importance of the quality of the precipitation archive was also demonstrated, as too simplistic reconstructions of 6-hourly time series lead to a loss of all the improvement brought by better analogue situations identified by the MTW.
+The importance of the quality of the precipitation archive was also demonstrated, as too simplistic reconstructions of 6-hourly time series lead to a loss of all the improvement brought by better analog situations identified by the MTW.
 The precipitation prediction is improved only when the precipitation chronology is close to the accurate one.
@@
 	\end{center}
-	\caption{Changes in the $S_{\text{TW}}$ criteria distributions of the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogue ranks for the Ulrichen station, due to the MTW.}
-	\label{fig:changes_S1_analogues}
+	\caption{Changes in the $S_{\text{TW}}$ criteria distributions of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$ and (d) $40^{th}$ analog ranks for the Ulrichen station, due to the MTW.}
+	\label{fig:changes_S1_analogs}
 \end{figure*}
@@
 	\begin{center}
-		\includegraphics[width=8.2cm]{figures/changes_S1_value.pdf} \\
-		\includegraphics[width=8.3cm]{figures/changes_S1_gain.pdf}
-	\end{center}
-	\caption{Synthesis of the changes in the $S_{\text{TW}}$ criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analogue.
-(top) Quantiles of the $S_{\text{TW}}$ distributions with and without the MTW.
-(bottom) Quantiles of the relative improvements of the S1 criteria when using the MTW.}
+		\includegraphics[width=8.2cm]{figures/changes_S1_value_and_gain.pdf}
+	\end{center}
+	\caption{Synthesis of the changes in the $S_{\text{TW}}$ criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analog.
+(a) Quantiles of the $S_{\text{TW}}$ distributions with and without the MTW.
+(b) Quantiles of the relative improvements of the S1 criteria when using the MTW.}
 	\label{fig:changes_S1}
@@
 	\includegraphics[width=8.3cm]{figures/hours_selection_per_season.pdf}
-	\caption{Distribution of the predictors hours in the selected analogue dates depending on the season, for the Ulrichen station.}
+	\caption{Distribution of the predictors hours in the selected analog dates depending on the season, for the Ulrichen station.}
 	\label{fig:hours_selection_per_season}
@@
 	\includegraphics[width=8.3cm]{figures/hours_selection_per_season_Visp.pdf}
-	\caption{Distribution of the predictors hours in the selected analogue dates depending on the season, for the Visp station.}
+	\caption{Distribution of the predictors hours in the selected analog dates depending on the season, for the Visp station.}
 	\label{fig:hours_selection_per_season_Visp}
@@
 	\begin{center}
-		\includegraphics[width=8.1cm]{figures/changes_RMSE_value.pdf} \\
-		\includegraphics[width=8.3cm]{figures/changes_RMSE_gain.pdf}
-	\end{center}
-	\caption{Synthesis of the changes in the $E_{\text{RMS}}$ criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analogue.
-(top) Quantiles of the $E_{\text{RMS}}$ distributions with and without the MTW.
-(bottom) Quantiles of the relative improvements of the $E_{\text{RMS}}$ criteria when using the MTW.}
+		\includegraphics[width=8.1cm]{figures/changes_RMSE_value_and_gain.pdf}
+	\end{center}
+	\caption{Synthesis of the changes in the $E_{\text{RMS}}$ criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analog.
+(a) Quantiles of the $E_{\text{RMS}}$ distributions with and without the MTW.
+(b) Quantiles of the relative improvements of the $E_{\text{RMS}}$ criteria when using the MTW.}
 	\label{fig:changes_RMSE}
@@
 		\begin{array}{cccc}
-		\includegraphics[width=4cm]{figures/component_2Z_accuracy.pdf} &
-		\includegraphics[width=4cm]{figures/component_2Z_sharpness.pdf} &
-		\includegraphics[width=4cm]{figures/component_2Z-2MI_accuracy.pdf} &
-		\includegraphics[width=4cm]{figures/component_2Z-2MI_sharpness.pdf} \\ \\
-		\includegraphics[width=4cm]{figures/component_2Z_accuracy_recalib.pdf} &
-		\includegraphics[width=4cm]{figures/component_2Z_sharpness_recalib.pdf} &
-		\includegraphics[width=4cm]{figures/component_2Z-2MI_accuracy_recalib.pdf} &
-		\includegraphics[width=4cm]{figures/component_2Z-2MI_sharpness_recalib.pdf} 
+		\includegraphics[width=16cm]{figures/components.pdf}
 		\end{array}$
@@
 The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window).
-The criteria used for the current level of analogy is then provided, as well as the number of analogues.}
+The criteria used for the current level of analogy is then provided, as well as the number of analogs.}
 	\footnotesize
@@
 \begin{table}[htb]
-	\caption{Calibrated parameters (spatial windows and number of analogues) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) and skill score (\%) of the method on the full archive.}
+	\caption{Calibrated parameters (spatial windows and number of analogs) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) and skill score (\%) of the method on the full archive.}
 	\begin{center}
@@
 			\hline
-			Station & Longitudes & Latitudes & $N_{1}$ & $S_{\text{SCRP}}$ \\
+			Station & Long (° E) & Lat (° N) & $N_{1}$ & $S_{\text{SCRP}}$ \\
 			\hline
@@
 	\caption{Parameters of the moisture variables from the 2Z-2MI method and the corresponding skill score (\%) on the complete archive.
-The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z}, except the number of analogues of the first analogy level ($N_{1}$), which are here different.
-The $5^{th}$ column is the number of analogues for the second level ($N_{2}$).}
+The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z}, except the number of analogs of the first analogy level ($N_{1}$), which are here different.
+The $5^{th}$ column is the number of analogs for the second level ($N_{2}$).}
 	\begin{center}
@@
 			\hline
-			Station & Longitudes & Latitudes & $N_{1}$ & $N_{2}$ & $S_{\text{SCRP}}$ \\
+			Station & Long (° E) & Lat (° N) & $N_{1}$ & $N_{2}$ & $S_{\text{SCRP}}$ \\
 			\hline
@@
 \begin{table}[htb]
-	\caption{Calibrated parameters (spatial windows and number of analogues) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) with the MTW approach.}
+	\caption{Calibrated parameters (spatial windows and number of analogs) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) with the MTW approach.}
 	\begin{center}
@@
 			\hline
-			Station & Longitudes & Latitudes & $N_{1}$ \\
+			Station & Long (° E) & Lat (° N) & $N_{1}$ \\
 			\hline
@@
 	\caption{Parameters of the moisture variables from the 2Z-2MI method with the MTW approach.
-The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z_new}, except the number of analogues of the first analogy level ($N_{1}$), which are here different.
-The $5^{th}$ column is the number of analogues for the second level ($N_{2}$).}
+The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z_new}, except the number of analogs of the first analogy level ($N_{1}$), which are here different.
+The $5^{th}$ column is the number of analogs for the second level ($N_{2}$).}
 	\begin{center}
@@
 			\hline
-			Station & Longitudes & Latitudes & $N_{1}$ & $N_{2}$ \\
+			Station & Long (° E) & Lat (° N) & $N_{1}$ & $N_{2}$ \\
 			\hline
@@
 	\caption{Value of the coefficient of determination between the reconstructed 6-hourly precipitation time series using the listed variables, and the accurate time series on the period 1982-2007.
-The grid points are the following (lon/lat): 1) 5\textdegree/47.5\textdegree, 2) 5\textdegree/45\textdegree, 3) 7.5\textdegree/47.5\textdegree, 4) 7.5\textdegree/45\textdegree.
+The grid points are the following: 1) 5° E, 47.5° N, 2) 5° E, 45° N, 3) 7.5° E, 47.5° N, 4) 7.5° E, 45° N.
 The highest coefficient of determination is indicated in bold.}
@@
 			\multirow{2}{*}{Variable} & \multirow{2}{*}{Point} &  \multicolumn{5}{c}{Time lapse} \\
-			&  & -12h & -6h & 0h & +6h & +12h \\ 
+			&  & -12 h & -6 h & 0 h & +6 h & +12 h \\ 
 			\hline
@@
 			\hline
-			1982-2007 & 22.57 & 23.14 & 27.11 & 27.71 \\
-			1961-2008 & 23.81 & 24.38 & 28.42 & 28.86 \\
+			1982--2007 & 22.57 & 23.14 & 27.11 & 27.71 \\
+			1961--2008 & 23.81 & 24.38 & 28.42 & 28.86 \\
 			\hline

### 2016-08-17 Optimization case study - Journal of Hydrology/elsarticle-template.tex
Changing "analogue" for "analog".

@@
 
-\title{Using Genetic Algorithms to Optimize the Analogue Method for Precipitation Downscaling in the Swiss Alps}
+\title{Using Genetic Algorithms to Optimize the Analog Method for Precipitation Downscaling in the Swiss Alps}
 
@@
 \begin{abstract}
-The Analogue Method aims at predicting precipitation based on predictors variables provided by global models.
+The Analog Method aims at predicting precipitation based on predictors variables provided by global models.
 The method samples a selection of days in the archives that are similar to the target day to predict, and consider the set of their corresponding observed precipitation (the predictand) as the conditional distribution for the target day.
@@
 This relationship is usually established by a semi-automatic sequential procedure that has strong limitations.
-A new global optimization approach relying on Genetic Algorithms can optimize all parameters jointly and automatically, which is a breakthrough in the way the Analogue Method was calibrated until now.
+A new global optimization approach relying on Genetic Algorithms can optimize all parameters jointly and automatically, which is a breakthrough in the way the Analog Method was calibrated until now.
 It allows taking into account parameters inter-dependencies, and selecting objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
@@
 Precipitation downscaling\sep
-Analogue method\sep
+Analog method\sep
 Optimization\sep
@@
 
-The analogue method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1956, Lorenz1969}, that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Duband1970, Bontron2005}.
+The analog method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1956, Lorenz1969}, that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Duband1970, Bontron2005}.
 It aims at forecasting a predictand, often the daily precipitation \citep[eg.][]{Guilbaud1997, Bontron2005, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, BenDaoud2015}, on the basis of predictor variables describing the synoptic atmospheric circulation.
@@
 In this last case, although the GCM represents the large or regional scale evolutions of the atmosphere, it would be far too computer intensive to get down to variables such as precipitation at a rather small and representative scale.
-Therefore the idea is to rely on past observations to bypass these unaffordable small scale simulations and to go from the large scale situation proposed by the GCM to the end variables like precipitation by searching analogues in the archives.
+Therefore the idea is to rely on past observations to bypass these unaffordable small scale simulations and to go from the large scale situation proposed by the GCM to the end variables like precipitation by searching analogs in the archives.
 
 The method can be made of multiple successive subsampling steps, each of them relying on different meteorological variables.
-A certain number of parameters define the relationship between predictors and predictands, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criteria itself, and finally the number of analogue situations to keep at each subsampling level.
+A certain number of parameters define the relationship between predictors and predictands, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criteria itself, and finally the number of analog situations to keep at each subsampling level.
 These parameters are usually calibrated by means of a semi-automatic sequential procedure \citep[see][for the details]{Bontron2004, Horton2016}, i.e.
@@
 
-\section{The Analogue Method}
+\section{The Analog Method}
 \label{sec:analog_method}
@@
 
-The $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day.
-The number of analogues, $N_{1}$, is a parameter to calibrate.
+The $N_{1}$ dates with the lowest values of S1 are considered as analogs to the target day.
+The number of analogs, $N_{1}$, is a parameter to calibrate.
 Then, the daily observed precipitation amount of the $N_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
@@
 \cite{Horton2012a} confirmed that this index is also better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis considered independently.
-When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
-When a second level of analogy is added, a higher number of analogues $N_{1}$ is kept on the first level.
+When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogs on the atmospheric circulation, to end up with a smaller number of analog situations.
+When a second level of analogy is added, a higher number of analogs $N_{1}$ is kept on the first level.
 
@@
 The score that is most often used to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
-It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$.
+It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$.
 The better the prediction, the smaller the score.
@@
 The reference method for the analogy of the atmospheric circulation (2Z, Table \ref{table:params_R1}), based on Z500 and Z1000, was first considered.
-The optimizer had to choose the number of analogues, both spatial windows with no overlapping constraint, as well as the temporal windows (hours of observation of the geopotential), what the sequential calibration cannot do.
+The optimizer had to choose the number of analogs, both spatial windows with no overlapping constraint, as well as the temporal windows (hours of observation of the geopotential), what the sequential calibration cannot do.
 With these degrees of freedom, a relative CRPSS improvement of 3.97\% and 2.45\% in average was obtained for the CP and the VP respectively.
@@
 	\item the weights (4 degrees)
-	\item the number of analogues (1 degree).
+	\item the number of analogs (1 degree).
 \end{itemize}
@@
 Even a change in the pressure level does not mean a radical drop of the score value.
-A different parametrization may lead to a distinct selection of analogue days, and thus to an improvement of the prediction under certain weather conditions at the expense of others.
+A different parametrization may lead to a distinct selection of analog days, and thus to an improvement of the prediction under certain weather conditions at the expense of others.
 
@@
 When optimizing a method made of 2 levels of analogy, the introduction of moisture variables in the second level has an influence on the parameter values of the first level.
-This is first visible on the number $N_{1}$ of analogues to be selected on the first level, and on the selection of the pressure levels for the circulation analogy.
+This is first visible on the number $N_{1}$ of analogs to be selected on the first level, and on the selection of the pressure levels for the circulation analogy.
 
-As for the sequential procedure, the optimal value of $N_{1}$ increases when adding a second level of analogy (Figure \ref{fig:figure_nb_analogues}).
-One can also notice that the optimal number of analogues $N_{2}$ for the second level of analogy of 4Zo-2MIo is slightly inferior to $N_{1}$ from 4Zo, but very close.
-There is a trend between the optimal analogue number values of both methods: the higher $N_{1}$ of the 4Zo method, the higher $N_{1}$ and $N_{2}$ of 4Zo-2MIo is (Figure \ref{fig:figure_nb_analogues_relationships}).
+As for the sequential procedure, the optimal value of $N_{1}$ increases when adding a second level of analogy (Figure \ref{fig:figure_nb_analogs}).
+One can also notice that the optimal number of analogs $N_{2}$ for the second level of analogy of 4Zo-2MIo is slightly inferior to $N_{1}$ from 4Zo, but very close.
+There is a trend between the optimal analog number values of both methods: the higher $N_{1}$ of the 4Zo method, the higher $N_{1}$ and $N_{2}$ of 4Zo-2MIo is (Figure \ref{fig:figure_nb_analogs_relationships}).
 This relationship is not to be considered perfectly robust and should not be transposed to another case study, but in this case, it relates the magnitudes of the $N_{1}$ and $N_{2}$ on the various levels and methods.
 
-The optimal final number of analogues do not vary much: $23 \leq N_{1} \leq 33$ for 4Zo and $21 \leq N_{2} \leq 28$ for 4Zo-2MIo.
-However, the optimal number of $N_{1}$ analogues of the first level of 4Zo-2MIo varies to a greater extent: $48 \leq N_{1} \leq 84$.
+The optimal final number of analogs do not vary much: $23 \leq N_{1} \leq 33$ for 4Zo and $21 \leq N_{2} \leq 28$ for 4Zo-2MIo.
+However, the optimal number of $N_{1}$ analogs of the first level of 4Zo-2MIo varies to a greater extent: $48 \leq N_{1} \leq 84$.
 In this latter method, it may be problematic to consider a fixed and unique value for all regions.
@@
 Beyond that value the validation score drops, revealing a loss in robustness due to over-parametrization.
-	\item The automatic and joint optimization of all parameters: the analogues number, the selection of the pressure levels and the temporal windows, and the spatial windows.
+	\item The automatic and joint optimization of all parameters: the analogs number, the selection of the pressure levels and the temporal windows, and the spatial windows.
 These parameters are highly interdependent, so one needs to optimize them jointly in order to identify optimal combinations.
@@
 	\centerline{\includegraphics[width=8.8cm]{figures/fig11.pdf}}
-	\caption{Number of analogues for the different regions and the various methods resulting from the optimization.
-Method 4Zo is made of a single level of analogy with $N_{1}$ analogues, whereas 4Zo-2MIo has two levels of analogy with respectively $N_{1}$ and $N_{2}$ analogues.}
-	\label{fig:figure_nb_analogues}
+	\caption{Number of analogs for the different regions and the various methods resulting from the optimization.
+Method 4Zo is made of a single level of analogy with $N_{1}$ analogs, whereas 4Zo-2MIo has two levels of analogy with respectively $N_{1}$ and $N_{2}$ analogs.}
+	\label{fig:figure_nb_analogs}
 \end{figure}
@@
 	\centerline{\includegraphics[width=8.8cm]{figures/fig12.pdf}}
-	\caption{Relationships between the optimal number of analogues for both levels of the 4Zo-2MIo method and the corresponding ones for the unique level of the 4Zo method.}
-	\label{fig:figure_nb_analogues_relationships}
+	\caption{Relationships between the optimal number of analogs for both levels of the 4Zo-2MIo method and the corresponding ones for the unique level of the 4Zo method.}
+	\label{fig:figure_nb_analogs_relationships}
 \end{figure}
@@
 	\caption{Parameters of the 4Zo method (analogy on 4 levels of the atmospheric circulation) optimized for the Chablais subregion.
-The columns are the following: L = level of analogy, V = meteorological variable, H = hour of observation or temporal window, D = domain or spatial window, W = weighting of the score for the selected pressure levels, C = criteria, N = number of analogues.}
+The columns are the following: L = level of analogy, V = meteorological variable, H = hour of observation or temporal window, D = domain or spatial window, W = weighting of the score for the selected pressure levels, C = criteria, N = number of analogs.}
 	\footnotesize

### 2016-08-17 Genetic algorithms - Journal of Climate/template.tex
Changing the term forecast for prediction when relevant.

@@
 
-\abstract{The Analog Method is based on a statistical relationship between synoptic atmospheric variables (predictors) and local weather (predictand), which we aim at forecasting.
+\abstract{The Analog Method is based on a statistical relationship between synoptic atmospheric variables (predictors) and local weather (predictand), which we aim at predicting.
 This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic sequential procedure.
@@
 The Analog Method (AM) relies on the hypothesis that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Lorenz1956, Lorenz1969, Duband1970, Bontron2005}.
-The principle consists in sampling a certain number of past situations based on different atmospheric variables (predictors) in order to build a probabilistic forecast for a local weather variable of interest (predictand).
-The most common usage of the AM is for precipitation forecasting \citep[eg.][]{Guilbaud1997, Bontron2005, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, BenDaoud2015}, but AMs, or equivalent, were also used for short to medium term forecasting of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
-Applications for monthly forecasts in many countries also exist, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal forecasts: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
+The principle consists in sampling a certain number of past situations based on different atmospheric variables (predictors) in order to build a probabilistic prediction for a local weather variable of interest (predictand).
+The most common usage of the AM is for precipitation downscaling \citep[eg.][]{Guilbaud1997, Bontron2005, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, BenDaoud2015}, but AMs, or equivalent, were also used for downscaling of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+Applications for monthly time series in many countries also exist, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal predictions: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
 
@@
 The purpose of this paper is not to present in details the AM and its different parameterizations, which can be found in \citet{Horton2016} or \citet{BenDaoud2015}.
-The concepts one needs to understand here are the following: the AM consists in searching a certain number of past situations in a meteorological archive (typically reanalysis datasets) that are the most similar, according to an analogy criteria, and to extract the observed values of the local weather variable of interest from another archive (typically local or basin averaged time series) in order to build the conditional empirical distribution considered as the probabilistic forecast for the target day.
+The concepts one needs to understand here are the following: the AM consists in searching a certain number of past situations in a meteorological archive (typically reanalysis datasets) that are the most similar, according to an analogy criteria, and to extract the observed values of the local weather variable of interest from another archive (typically local or basin averaged time series) in order to build the conditional empirical distribution considered as the probabilistic prediction for the target day.
 Predictors can be varied: for example the geopotential height at different pressure levels on different temporal windows (time of observation).
@@
 
-There are mainly 2 parameterizations that are most often used for precipitation forecasting: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
+There are mainly 2 parameterizations that are most often used for precipitation downscaling: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
 
@@
 The $n_{1}$ (parameter to calibrate) dates with the lowest values of S1 are considered as analogs to the target day.
-Then, the daily observed precipitation amount of the $n_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
+Then, the daily observed precipitation amount of the $n_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day.
 
@@
 GAs are very computationally intensive because they require many evaluations of the objective function.
-These assessments are very long in this application, as they require calculating and assessing a forecast for every day of the calibration period, thus over several decades.
+These assessments are very long in this application, as they require calculating and assessing a prediction for every day of the calibration period, thus over several decades.
 In order to reduce the computation time, recalculating the performance score of an individual who has previously been evaluated and that has not changed was avoided.
@@
 
-The first analysis was the optimization of the precipitation forecasting over a subcatchment (Binn-Simplon region) in the Swiss Alps (Fig.
+The first analysis was the optimization of the precipitation downscaling over a subcatchment (Binn-Simplon region) in the Swiss Alps (Fig.
 \ref{fig:operator_mutation_score_atmlevel}).

### 2016-08-17 Moving temporal window - HESS/template.tex
Changing the term forecast for prediction when relevant.

@@
 \begin{abstract}
-The Analog Method (AM) aims at forecasting local weather variables (predictands), such as precipitations, by means of a statistical relationship with predictors at a synoptic scale.
+The Analog Method (AM) aims at predicting local weather variables (predictands), such as precipitations, by means of a statistical relationship with predictors at a synoptic scale.
 The analogy is generally assessed in the first place on the geopotential field by mean of a comparison of the gradients, in order to sample the days with a similar atmospheric circulation.
@@
 Then, $N_{1}$ dates with the lowest values of $S_{\text{TW}}$ are considered as analogs to the target day, $N_{1}$ being a parameter to calibrate.
-Then, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
+Then, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day.
 Following the nomenclature proposed by \citet{Horton2016}, this method will be named 2Z.
@@
 It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$.
-The better the forecast, the smaller the score.
+The better the prediction, the smaller the score.
 It is defined as follows:
@@
 \end{equation}
-where $S_{\text{CRP}}^{r}$ is the $S_{\text{CRP}}$ value for the reference (climatological distribution) and $S_{\text{CRP}}^{p}$ would be the one for a perfect forecast (which implies $S_{\text{CRP}}^{p}~=~0$).
-A better forecast is characterized by an increase in $S_{\text{SCRP}}$.
+where $S_{\text{CRP}}^{r}$ is the $S_{\text{CRP}}$ value for the reference (climatological distribution) and $S_{\text{CRP}}^{p}$ would be the one for a perfect prediction (which implies $S_{\text{CRP}}^{p}~=~0$).
+A better prediction is characterized by an increase in $S_{\text{SCRP}}$.
 
@@
 
-Previous tests showed the benefit, in terms of analogy criteria values, of searching for analog synoptic situations at a finer time step, but without assessing the impact on the forecast skills \citep{Finet2008}.
+Previous tests showed the benefit, in terms of analogy criteria values, of searching for analog synoptic situations at a finer time step, but without assessing the impact on the prediction skills \citep{Finet2008}.
 In order to assess this potential improvement of the prediction, precipitation data with a resolution of 10 minutes, on a respectable archive length, was used (Sect.
@@
 
-The target situations and their corresponding observed precipitation values (used for validation) do not change, because the forecast is always established for a fixed period of the target day (6--30~h), as before.
+The target situations and their corresponding observed precipitation values (used for validation) do not change, because the prediction is always established for a fixed period of the target day (6--30~h), as before.
 The difference is that the candidates are 4~times more numerous (Fig.

### 2016-08-18 AtmoSwing - GMD/template.tex
Changing directory structure.

--- 2016-08-17 AtmoSwing - Geoscientific Model Development/template.tex
@@
 
-\title{AtmoSwing (v1.4): Analog Technique Model for Statistical weather forecastING}
+\title{AtmoSwing (v1.4): Analog Technique Model for Statistical Weather downscalING}
 
@@
 
-The Analog Method allows forecasting local meteorological variables of interest (predictand), such as the daily precipitation, on the basis of synoptic variables (predictors).
+The Analog Method allows predicting local meteorological variables of interest (predictand), such as the daily precipitation, on the basis of synoptic variables (predictors).
 It relies on the fact that similar meteorological influences are likely to result in similar local effects.
@@
 
-In addition to precipitation forecasting, the Analog Method (AM), or an equivalent, was also used for short to medium term forecasting of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+In addition to precipitation prediction, the Analog Method (AM), or an equivalent, was also used for short to medium term prediction of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
 \citet{Guilbaud1997} performed a literature review about the use of the AM in long-term forecasting and identified operational applications for monthly forecasts in many countries, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal forecasts: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
@@
 Other observed predictors can also be used, such as Sea Surface Temperature \citep[SST, ][]{Reynolds2007}.
-\citet{Bontron2004} proposed that the minimum length of the archive should be 30 years to forecast usual situations, and 40 years or more for intense events.
+\citet{Bontron2004} proposed that the minimum length of the archive should be 30 years to predict usual situations, and 40 years or more for intense events.
 
@@
 	\item First level of analogy: $N_{1}$ dates are subsampled within all the candidates provided by the preselection, by means of an analogy ranking.
-The first level of analogy is always based on the atmospheric circulation when it comes to precipitation forecasting.
+The first level of analogy is always based on the atmospheric circulation when it comes to precipitation prediction.
 The similarity of the atmospheric circulation of the target date with the candidate situations is thus assessed on the geopotential by means of the S1 criteria \citep[Eq.
@@
 
-\subsection{Common variants for precipitation forecasting}
+\subsection{Common variants for precipitation prediction}
 \label{sec:method:references}
@@
 The analogy on the atmospheric circulation proposed by \citet{Bontron2004} is still, at the time of writing, often used operationally, and considered as a reference for benchmarking new parameterizations \citep[see e.g.][]{Horton2012, BenDaoud2015}.
-In order to assess the forecast, he introduced the Continuous Ranked Probability Score \citep[CRPS, Eq.
+In order to assess the prediction, he introduced the Continuous Ranked Probability Score \citep[CRPS, Eq.
 \ref{eq:CRPS}, ][]{Brown1974}, which discards the issue of determining classes as with the Ranked Probability Score \citep{Epstein1969} previously in use.
@@
 \citet{BenDaoud2010} applied the AM in the context of large floodplains (Sa\^{o}ne, Seine).
-He evaluated several variables usually used in weather forecasting, amongst them the air temperature and the vertical velocity that presented a potential interest.
+He evaluated several variables usually used in weather prediction, amongst them the air temperature and the vertical velocity that presented a potential interest.
 The temperature (at the nearest grid point, on the 925~hPa \& 36~h and 600~hPa \& 12~h levels) could replace the rigid calendar preselection of $\pm$ 60 days around the target date by a more dynamic screening of similar situations in terms of air masses.
@@
 
-An AtmoSwing great strength is that it is designed to process analogy forecasting in a modular fashion.
+An AtmoSwing great strength is that it is designed to process analogy downscaling in a modular fashion.
 The structure of the AM (number of analogy levels, number of predictors) is built dynamically (Fig.
@@
 
-Although processing an analog forecast for a given target date is fast, when optimizing the AM, forecasts are re-processed over long periods of several decades, which may become very time consuming.
+Although processing an analog forecast for a given target date is fast, when optimizing the AM, predictions are re-processed over long periods of several decades, which may become very time consuming.
 Thus, great effort has been made in order to reduce the processing time to a minimum.
@@
 It is therefore necessary to pay particular attention to the 90$^{th}$ percentile which, when reaching high values, may be indicative of a situation related to extreme precipitations, due the presence of several analog dates with significant observed precipitations amounts in the distribution \citep{Djerboua2001}.
-\citet{Bontron2004} made the same observation: he found the 60$^{th}$ percentile to be best for occurrence forecasting, but the 90$^{th}$ percentile to be the most informative in order to forecast medium to high precipitation amounts ($P > P10/10$, one tenth of the 10~year return period value).
+\citet{Bontron2004} made the same observation: he found the 60$^{th}$ percentile to be best for occurrence prediction, but the 90$^{th}$ percentile to be the most informative in order to forecast medium to high precipitation amounts ($P > P10/10$, one tenth of the 10~year return period value).
 In this regard, operators should pay particular attention to the distribution of the best analogs.
@@
 
-Another reason for working in a perfect prognosis framework is that numerical models evolve continuously, and so does the forecast they provide.
-Considering re-forecasts would allow us to work on a homogeneous dataset, as they are regularly reprocessed with a defined version of the model.
+Another reason for working in a perfect prognosis framework is that numerical models evolve continuously, and so does the prediction they provide.
+Considering reforecasts would allow us to work on a homogeneous dataset, as they are regularly reprocessed with a defined version of the model.
 However, one would need to redo the calibration procedure every time a new version is available, in order to reduce the bias \citep{Wilson2002}.
@@
 The statistical relationship is established on a calibration period that is as long as possible.
-For every day of this period, a search for analogs is performed, the predictand data are associated with the corresponding dates and a forecast score is calculated.
+For every day of this period, a search for analogs is performed, the predictand data are associated with the corresponding dates and a prediction score is calculated.
 During the search for analogs situations, 120 days around the target date are excluded (thus excluding data in the same year) in order to consider only truly independent candidates days.
@@
 
-\subsection{Implemented forecasts scores}
+\subsection{Implemented prediction scores}
 \label{sec:forecasts-scores}
 
-Most often, the accuracy of the parameters for precipitations forecasting is evaluated by means of the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
+Most often, the accuracy of the parameters for precipitations downscaling is evaluated by means of the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
 It is the only score that will be detailed hereafter (in Sect.
@@
 
-\subsubsection{Discrete deterministic forecasts}
-
-Deterministic forecasts consider no uncertainty.
+\subsubsection{Discrete deterministic predictions}
+
+Deterministic predictions consider no uncertainty.
 A single value is provided for a variable.
-The first group of this type of forecast is based on discrete values, also called categories.
+The first group of this type of prediction is based on discrete values, also called categories.
 These scores are used, for example, to evaluate a deterministic prediction of threshold exceedance.
-In our case, the continuous probabilistic nature of an analogy forecast can be transformed into a discrete forecast by considering a threshold exceedance and a fixed percentile from the distribution.
+In our case, the continuous probabilistic nature of an analogy prediction can be transformed into a discrete prediction by considering a threshold exceedance and a fixed percentile from the distribution.
 These scores rely on a contingency table, which is here a table containing the sums of observed / unobserved and predicted / unpredicted events \citep{Wilks2006}.
@@
 
-\subsubsection{Continuous deterministic forecasts}
-
-The difference of the continuous deterministic forecasts compared to discrete ones is that they provide non-discrete values that must be evaluated with distance measures.
+\subsubsection{Continuous deterministic predictions}
+
+The difference of the continuous deterministic predictions compared to discrete ones is that they provide non-discrete values that must be evaluated with distance measures.
 In our application, the distribution of the analogs is summarized by a chosen percentile.
@@
 
-\subsubsection{Discrete probabilistic forecasts}
-
-In the case of discrete probabilistic forecasts, one works with probabilities of occurrence or probability of belonging to a certain category. The implemented options are:
+\subsubsection{Discrete probabilistic predictions}
+
+In the case of discrete probabilistic predictions, one works with probabilities of occurrence or probability of belonging to a certain category. The implemented options are:
 
@@
 
-\subsubsection{Continuous probabilistic forecasts}
+\subsubsection{Continuous probabilistic predictions}
 \label{sec:prob_forecasts}
 
-Continuous probabilistic forecasts of a variable are issued in the form of the expected statistical distribution for this variable.
+Continuous probabilistic predictions of a variable are issued in the form of the expected statistical distribution for this variable.
 They are expressed either in terms of distribution or by probability density, which needs to be compared to an observed value.
-This is the situation one meets when forecasting precipitations with the AM.
+This is the situation one meets when downscaling precipitations with the AM.
 
@@
 It allows assessing the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$.
-The better the forecast, the smaller the score.
-The mean CRPS of a forecast series of length $n$ can be written:
+The better the prediction, the smaller the score.
+The mean CRPS of a prediction series of length $n$ can be written:
 
@@
 \end{equation}
-where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect forecast (which implies $CRPS_{p}~=~0$).
+where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect prediction (which implies $CRPS_{p}~=~0$).
 
@@
 
-To assess and address these operational aspects, the best option is to collect a dataset of re-forecast from the specific NWP model selected.
+To assess and address these operational aspects, the best option is to collect a dataset of reforecast from the specific NWP model selected.
 Then, distinct variants of AM parameterizations can be assessed on different lead times.
@@
 
-Next, we assume that for the synoptic variables used as predictors, the model forecasts have more uncertainties than the reanalyses, but no systematic bias.
+Next, we assume that for the synoptic variables used as predictors, the model predictions have more uncertainties than the reanalyses, but no systematic bias.
 To optimize further the AM, it can be considered that the further the lead time, the more uncertain the synoptic forecasts and therefore the more uncertain the precipitation forecasts could be.
-This can been addressed by reconsidering, for each lead-time, the optimal number of analogs to select, for re-forecast data from a particular NWP model \citep{Thevenot2004}.
+This can been addressed by reconsidering, for each lead-time, the optimal number of analogs to select, for reforecast data from a particular NWP model \citep{Thevenot2004}.
 The underlying idea is that if the model proves perfect, then the number of analogs should remain close to that obtained in the perfect progonosis framework.
-While if the forecast becomes irrelevant, for example at distant lead times, the AM should propose a forecast closer and closer to the climatological distribution of the predictand.
-The optimal number of analog situations will thus increase with the lead time, and should be optimized for every lead time on the re-forecast dataset \citep[see][for the details]{Thevenot2004}.
+While if the forecast becomes irrelevant, for example at distant lead times, the AM should propose a prediction closer and closer to the climatological distribution of the predictand.
+The optimal number of analog situations will thus increase with the lead time, and should be optimized for every lead time on the reforecast dataset \citep[see][for the details]{Thevenot2004}.
 This option is implemented in AtmoSwing Forecaster (see Sect.
@@
 
-It should be stressed that these operational aspects are dependent on the model used to provide the AM with synoptic forecasts, and on the availability of a re-forecast data to perform the tuning of the AM to this particular model.
+It should be stressed that these operational aspects are dependent on the model used to provide the AM with synoptic forecasts, and on the availability of a reforecast data to perform the tuning of the AM to this particular model.
 
@@
 This work has demonstrated the best performance of the AM compared to classical regression based approaches.
-\citet{Woodcock1980} used the same criterion on the SLP fields to select 50~analogs in order to forecast maximum daily temperatures.
+\citet{Woodcock1980} used the same criterion on the SLP fields to select 50~analogs in order to predict maximum daily temperatures.
 After comparing S1 to other criteria from the literature, or combinations of these, \citet{Guilbaud1998} confirmed that S1 is the most efficient.

### 2016-08-18 Optimization case study - JoH/elsarticle-template.tex
Changing directory structure.

--- 2016-08-17 Optimization case study - Journal of Hydrology/elsarticle-template.tex
@@
 The analog method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1956, Lorenz1969}, that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Duband1970, Bontron2005}.
-It aims at forecasting a predictand, often the daily precipitation \citep[eg.][]{Guilbaud1997, Bontron2005, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, BenDaoud2015}, on the basis of predictor variables describing the synoptic atmospheric circulation.
+It aims at predicting a predictand, often the daily precipitation \citep[eg.][]{Guilbaud1997, Bontron2005, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, BenDaoud2015}, on the basis of predictor variables describing the synoptic atmospheric circulation.
 Other predictands are also often considered \citep[see][for a non-exhaustive list]{Horton2016}.
@@
 Multiple variations of the methods exist, and most of them will not be detailed hereafter \cite[see][for more comprehensive listings]{Horton2016, BenDaoud2015}.
-However, there are mainly 2 parameterizations that are most often used for precipitation forecasting and that will be considered as reference: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
+However, there are mainly 2 parameterizations that are most often used for precipitation downscaling and that will be considered as reference: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
 
@@
 The number of analogs, $N_{1}$, is a parameter to calibrate.
-Then, the daily observed precipitation amount of the $N_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
+Then, the daily observed precipitation amount of the $N_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day.
 

### 2016-08-22 Genetic algorithms - MWR/template.tex
Using the analog method term more carefully...

--- 2016-08-17 Genetic algorithms - Journal of Climate/template.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% PREAMBLE
+%% PREAMBLE
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %% Start with one of the following:
-% DOUBLE-SPACED VERSION FOR SUBMISSION TO THE AMS
+%% DOUBLE-SPACED VERSION FOR SUBMISSION TO THE AMS
 \documentclass{ametsoc}
 
-% TWO-COLUMN JOURNAL PAGE LAYOUT---FOR AUTHOR USE ONLY
+%% TWO-COLUMN JOURNAL PAGE LAYOUT---FOR AUTHOR USE ONLY
 %\documentclass[twocol]{ametsoc}
@@
 
-\title{Global Optimization of the Analog Method by Means of Genetic Algorithms}
+\title{Global Optimization of an Analog Method by Means of Genetic Algorithms}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% ABSTRACT
+%% ABSTRACT
 %
@@
 
-\abstract{The Analog Method is based on a statistical relationship between synoptic atmospheric variables (predictors) and local weather (predictand), which we aim at predicting.
+\abstract{Analog methods are based on a statistical relationship between synoptic atmospheric variables (predictors) and local weather (predictand), which we aim at predicting.
 This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic sequential procedure.
@@
 These kind of optimization techniques need however to be tailored to the problem to solve.
-Multiple combinations of algorithms had to be assessed, and even new operators were developed, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of Genetic Algorithms to optimize the Analog Method.
+Multiple combinations of algorithms had to be assessed, and even new operators were developed, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of Genetic Algorithms to optimize sevral variants of analog methods.
 These recommendations are the main outcome of this work.
-It opens new perspective for the improvement of the Analog Method, and its application to new regions or to new predictands.
+It opens new perspective for the improvement of  analog methods, and their application to new regions or to new predictands.
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% MAIN BODY OF PAPER
+%% MAIN BODY OF PAPER
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The Analog Method (AM) relies on the hypothesis that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Lorenz1956, Lorenz1969, Duband1970, Bontron2005}.
+Analog methods (AMs) relies on the hypothesis that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Lorenz1956, Lorenz1969, Duband1970, Bontron2005}.
 The principle consists in sampling a certain number of past situations based on different atmospheric variables (predictors) in order to build a probabilistic prediction for a local weather variable of interest (predictand).
-The most common usage of the AM is for precipitation downscaling \citep[eg.][]{Guilbaud1997, Bontron2005, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, BenDaoud2015}, but AMs, or equivalent, were also used for downscaling of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+A common usage of AMs is for precipitation downscaling \citep[eg.][]{Guilbaud1997, Bontron2005, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, BenDaoud2015}, but AMs, or equivalent, were also used for downscaling of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
 Applications for monthly time series in many countries also exist, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal predictions: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
@@
 
-The AM needs to be adapted to every new region considered, because the leading meteorological influences may be location specific.
+AMs need to be adapted to every new region considered, because the leading meteorological influences may be location specific.
 Even the selection of the pressure levels and the temporal windows should be reconsidered, if not the predictor variable itself.
 
-Up to now, the optimization of the method has been undertaken by semi-automatic sequential calibration procedures \citep[see][for its definition]{Bontron2004, Horton2016}.
+Up to now, the optimization of the method has been undertaken by semi-automatic sequential calibration procedures \citep[see][for its definition]{Bontron2004}.
 However, the selection of predictor variables, pressure levels and temporal windows had still to be made manually before optimizing the spatial windows and the number of analogs.
@@
 Thus, due to the sequential approach, the risk of ending in a local optimum is high and can not be avoided.
-Indeed, during the AM calibration it has been found that the resulting parameters may vary with initial choices (such as the number of analogs).
+Indeed, during an AM calibration it has been found that the resulting parameters may vary with initial choices (such as the number of analogs).
 
@@
 And later in his work: ''\textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution}''.
-\citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of the AM and concludes that one needs to be an expert to have a sense of their respective influence, sensitivity and nonlinear interactions.
-\citet{BenDaoud2010}, when calibrating the AM, also stated that ''\textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously}''.
+\citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of an AM and concludes that one needs to be an expert to have a sense of their respective influence, sensitivity and nonlinear interactions.
+\citet{BenDaoud2010}, when calibrating an AM, also stated that ''\textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously}''.
 
@@
 This technique did not provide satisfying results and failed at converging toward a unique solution.
-The parameter space of the AM is very complex and is inappropriate for a linear optimization technique.
-The conclusion was that global optimization techniques were necessary in order to calibrate AMs, as it is the only way to optimize all parameters of all analogy levels simultaneously.
+The parameter space of AMs can be very complex and is inappropriate for a linear optimization technique.
+The conclusion was that global optimization techniques were necessary in order to calibrate most AM variants, as it is the only way to optimize all parameters of all analogy levels simultaneously.
 In addition, it can overcome the systematic manual assessments of all pressure levels and temporal windows.
-Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the pressure levels \citep[see][]{Horton2016b}, and the consideration of differentiated spatial windows between the pressure levels.
+Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the pressure levels, and the consideration of differentiated spatial windows between the pressure levels.
 The relevance of Genetic Algorithms (GAs) is presented here, which does not exclude that other global optimization techniques could eventually be successful.
 
-This article is not about discussing the details of the results of an optimization with GAs, but describing how GAs are to be used in order to successfully optimize AMs.
+This article is not about discussing the details of the results of an optimization with GAs, but describing how GAs are to be used in order to successfully optimize some AM variants.
 Indeed, GAs variants are numerous and always need to be tailored to the problem addressed.
 This requires intensive and systematic comparisons of operators and options in order to identify the key factors leading the optimization and the respective sensitivity of the options.
-Such analyses are presented here by application to the upper Rh\^{o}ne catchment in Switzerland, and will result in recommendations for the use of GAs when applied to AMs.
-The demonstration of the benefit brought by such an approach on a specific case study is the topic of \citet{Horton2016b}.
-
-We will begin by presenting the basics of the AM (Sect.
+Such analyses are presented here by application to the upper Rh\^{o}ne catchment in Switzerland, and will result in recommendations for the use of GAs when applied to several AM implementations.
+The demonstration of the benefit brought by such an approach on a specific case study is the topic of another coming paper.
+
+We will begin by presenting the basics of the considered AM variants (Sect.
 \ref{sec:am}) and the concepts of GAs as well as the assessed operators (operations performed on the AM parameters; see Sect.
@@
 
-\section{The Analog Method}
+\section{The considered analog method}
 \label{sec:am}
 
-The purpose of this paper is not to present in details the AM and its different parameterizations, which can be found in \citet{Horton2016} or \citet{BenDaoud2015}.
-The concepts one needs to understand here are the following: the AM consists in searching a certain number of past situations in a meteorological archive (typically reanalysis datasets) that are the most similar, according to an analogy criteria, and to extract the observed values of the local weather variable of interest from another archive (typically local or basin averaged time series) in order to build the conditional empirical distribution considered as the probabilistic prediction for the target day.
+% TODO: Add description of the method
+
+The concepts one needs to understand here are the following: AMs consist in searching a certain number of past situations in a meteorological archive (typically reanalysis datasets) that are the most similar, according to an analogy criteria, and to extract the observed values of the local weather variable of interest from another archive (typically local or basin averaged time series) in order to build the conditional empirical distribution considered as the probabilistic prediction for the target day.
 Predictors can be varied: for example the geopotential height at different pressure levels on different temporal windows (time of observation).
@@
 
-There are mainly 2 parameterizations that are most often used for precipitation downscaling: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
+Two parameterizations are often used for precipitation downscaling: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
 
@@
 
-The score that is most often used to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
+A score that has been often used to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
 It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$.
@@
 The GAs optimize a population of $N$ individuals (parameter sets).
-Each individual contains a chromosome (set of parameters of the AM in this case).
+Each individual contains a chromosome (set of parameters of our AM in this case).
 Genes are the individual parameters constituting the chromosome.
@@
 where, for the level of analogy $i$ and the predictor number $j$, $p_{i,j}$ is the pressure level, $h_{i,j}$ is the temporal window, $\lambda w_{i,j}$ and $\lambda e_{i,j}$ are the western and eastern longitudes of the spatial window, $\varphi s_{i,j}$ and $\varphi n_{i,j}$ are its southerly and northerly latitudes, and $n_{i,j}$ is the number of analogs.
-A chromosome for the simple AM on the atmospheric circulation only (Sect.
+A chromosome for a simple AM on the atmospheric circulation only (Sect.
 \ref{sec:am}) may be: $[500~hPa, 12~h, -2.5\degree, 15\degree, 40\degree, 55\degree, 1000~hPa, 24~h, 0\degree, 15\degree, 42.5\degree, 47.5\degree, 28]$
@@
 \begin{enumerate}
-	\item A population of $N$ individuals (parameter sets of the AM) is randomly generated, which constitutes the initial population.
+	\item A population of $N$ individuals (parameter sets of the AM to optimize) is randomly generated, which constitutes the initial population.
 	\item The fitness (performance score or objective function) of every individual is assessed.
@@
 The first step of the optimization is to generate an initial population.
-A population is a set of $N$ individuals (each of which represents, in this application, a parameter set of the AM and thus a point in the space of potential solutions) that are going to evolve.
+A population is a set of $N$ individuals (each of which represents, in this application, a parameter set of an AM and thus a point in the space of potential solutions) that are going to evolve.
 A generation is the population considered at a given time.
@@
 
-Other constraints exist in between the parameters, such as the temporal window of the moisture index \cite[see][]{Horton2016} that has to be consistent in between the relative humidity and the precipitable water.
+Other constraints exist in between the parameters, such as the temporal window of the moisture index that has to be consistent in between the relative humidity and the precipitable water.
 
@@
 
-One of our goals being to make recommendations of parametrization in view of optimizing the AM, a systematic procedure was adopted.
+One of our goals being to make recommendations of parametrization in view of optimizing AM variants, a systematic procedure was adopted.
 The results are summarized hereafter \citep[see][for the details]{Horton2012a}.
@@
 A procedure by stages was adopted, analyzing in details and in a systematic way every variant of the implemented operators, in combination with multiple other options and parameters in order to take into account eventual co-dependencies.
-The goal here is not to focus on the performance score obtained through optimization, neither the values of the new optimized parameters \citep[covered in][]{Horton2016b}, but to explain how to use GAs to optimize AMs in an efficient way.
+The goal here is not to focus on the performance score obtained through optimization, neither the values of the new optimized parameters (covered in another coming paper), but to explain how to use GAs to optimize AMs in an efficient way.
 
@@
 
-After a first overview of the results, GAs have quicky proved successful at optimizing the AM.
+After a first overview of the results, GAs have quicky proved successful at optimizing the considered AM implementations.
 The performance score of the sequential approach has been quickly exceeded without adding any new parameter to the method (Fig.
@@
 A difficulty is that the pressure levels are considered within the optimization without continuity between values, and thus the approaches relying on distance in the parameters space, such as the search radius, cannot fully exploit the properties that make them efficient.
-However, even though the results show a certain variability, most of them present very good performance scores, despite different parameters of the AM.
+However, even though the results show a certain variability, most of them present very good performance scores, despite different parameters of the AM considered.
 
@@
 Next, a second level of analogy was proposed (Fig.
-\ref{fig:operator_mutation_score_r2}) based on moisture variables \citep[see][]{Bontron2004, Horton2016}.
+\ref{fig:operator_mutation_score_r2}) based on moisture variables \citep[see][]{Bontron2004}.
 GAs had to optimize both levels of analogy simultaneously.
@@
 \begin{itemize}
-	\item $N\approx100$ for very simple implementations of the AM (1 level of analogy with 2 pressure levels),
+	\item $N\approx100$ for very simple AM implementations (1 level of analogy with 2 pressure levels),
 	\item $N\approx200$ for a slightly more complex AM (1 level of analogy with 4 pressure levels, or 2 level of analogy with less pressure levels),
@@
 
-Optimizations by GAs for AMs of varying complexities were performed with a large number of combinations of operators in order to make recommendations for optimizing the AM. The conclusions are:
+Optimizations by GAs for AMs of varying complexities were performed with a large number of combinations of operators in order to make recommendations for optimizing AMs. The conclusions are:
 
@@
 
-In order to automatically optimize the AM and to get rid of the limitations of the usual sequential calibration, GAs were evaluated.
-Given the large number of existing operators and options, multiple variants were assessed systematically in order to identify which operators are important, and which variants work best for the AM.
+In order to automatically optimize several AM variants and to get rid of the limitations of the usual sequential calibration, GAs were evaluated.
+Given the large number of existing operators and options, multiple variants were assessed systematically in order to identify which operators are important, and which variants work best for the considered AM implementations.
 The mutation operator was identified as a key element for this application, and new variants that proved efficient were provided, such as the chromosome of adaptive search radius that is very robust (no control parameter).
@@
 
-The global optimization approach allows easily adapting the AM to new regions by potentially taking into account local meteorological influences, and has thus a great potential of use.
+The global optimization approach allows easily adapting AMs to new regions by potentially taking into account local meteorological influences, and has thus a great potential of use.
 Moreover, it allows exploring automatically datasets in order to extract the most relevant variables.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% ACKNOWLEDGMENTS
+%% ACKNOWLEDGMENTS
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% APPENDIXES
+%% APPENDIXES
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% REFERENCES
+%% REFERENCES
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% TABLES
+%% TABLES
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% FIGURES
+%% FIGURES
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-09-01 Genetic algorithms - MWR/template.tex
GAs paper under correction.

@@
 This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic sequential procedure.
-This calibration approach has strong limitations: it is made of successive steps and thus cannot handle parameters dependencies, and it cannot automatically optimize some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared.
+This calibration approach has strong limitations: it is made of successive steps and thus cannot handle parameters dependencies, and it cannot automatically optimize some parameters, such as the selection of the pressure levels and the temporal windows (hour of observation of the predictor) on which the predictors are compared.
 In order to surpass these limitations, a global optimization technique was assessed, namely Genetic Algorithms, which can optimize jointly all parameters of the method and get closer to a global optimum by taking into account the parameters dependencies.
@@
 The principle consists in sampling a certain number of past situations based on different atmospheric variables (predictors) in order to build a probabilistic prediction for a local weather variable of interest (predictand).
-A common usage of AMs is for precipitation downscaling \citep[eg.][]{Guilbaud1997, Bontron2005, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, BenDaoud2015}, but AMs, or equivalent, were also used for downscaling of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+A common usage of AMs is for precipitation forecasting or downscaling \citep[eg.][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, Chardon2014, Dayon2015, Hamill2015b, BenDaoud2016}, but AMs, or equivalent, were also used to predict temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
 Applications for monthly time series in many countries also exist, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal predictions: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
 
-Even though the method is rather simple compared to numerical weather prediction (NWP) models, it contains a certain number of parameters one needs to determine, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criteria itself, and finally the number of analog situations to keep at each subsampling level.
+Even though the method is rather simple compared to numerical weather prediction (NWP) models, it contains a certain number of parameters one needs to determine, such as the choice of the predictor variable, its pressure level and temporal window (hour of observation of the predictor) to consider, the spatial domain to use for the comparison, as well as the analogy criteria itself, and finally the number of analog situations to keep at each subsampling level.
 
@@
 
-Up to now, the optimization of the method has been undertaken by semi-automatic sequential calibration procedures \citep[see][for its definition]{Bontron2004}.
-However, the selection of predictor variables, pressure levels and temporal windows had still to be made manually before optimizing the spatial windows and the number of analogs.
+A common approach to optimize the method is by means of a semi-automatic sequential calibration procedure, developed by \citet{Bontron2004}, also described in \citet{BenDaoud2016}, and extended by \citet{Radanovics2013}.
+It determines some parameters of the method, for each consecutive analogy level (eg.
+the atmospheric circulation or moisture index), sequentially.
+It starts by a manual selection of the meteorologic variable (e.g.
+geopotential height, relative humidity, etc.), the pressure level (e.g.
+500 hPa), the temporal window, and the initial analog number.
+Then, the spatial window on which the predictors are considered is optimized by an iterative growth of the domain, and the number of analogues is reassessed.
+A successive level of analogy can then be added and its spatial window optimized.
+Parameters of the preceding levels of analogy are not reassessed, except for the number of analogue situations to keep.
+
+The sequential calibration procedure thus allows optimizing a limited number of parameters, but the selection of predictor variables, pressure levels and temporal windows had still to be made manually before optimizing the spatial windows and the number of analogs.
 Testing multiple combinations of these is very combinatorial and becomes quickly cumbersome, especially when considering multiple predictors within the same level of analogy.
 Thus, optimizing the method with the sequential technique is laborious, as many combinations of predictors (variables, pressure levels, temporal windows) have to be assessed.
-Moreover, proceeding to the optimization sequentially ignores potential dependencies between the parameters of the method, may they be within a single level of analogy or between them, which could lead to another parametrization if the parameters were calibrated together.
+Moreover, proceeding to the optimization sequentially ignores potential dependencies between the parameters of the method, may they be within a single level of analogy or between them, which could lead to another configuration if the parameters were calibrated together.
 Simultaneous calibration of all parameters has never been undertaken so far.
@@
 
+Another optimization strategy has been proposed by \citet{Junk2015}, that allows for an automatic optimization of weights applied to the different predictors when processing the analogy criteria (distance function).
+Their strategy consists in a brute-force assessment of all possible combinations.
+This approach is possible in their analog method, as predictors are considered at a unique point (interpolated to the location of interest), at fixed hours, and at preselected pressure levels, leaving only the weights to optimize.
+In the presently used analogue method (described in section \ref{sec:am}), the number of parameters to optimize makes it impossible to proceed to a brute-force strategy.
+
 In order to overcome these limitations, two optimization techniques were assessed.
-First, \citet{Horton2012a} assessed the ability of the \citet{Nelder1965a} method based on a simplex approach.
+First, \citet{Horton2012a} assessed the ability of the \citet{Nelder1965a} method based on a simplex algorithm.
 This technique did not provide satisfying results and failed at converging toward a unique solution.
@@
 The relevance of Genetic Algorithms (GAs) is presented here, which does not exclude that other global optimization techniques could eventually be successful.
+If using GAs to optimize AMs is computationally intensive, once an AM is calibrated, its use in real-time operations it very fast and lightweight.
 
@@
 
-We will begin by presenting the basics of the considered AM variants (Sect.
-\ref{sec:am}) and the concepts of GAs as well as the assessed operators (operations performed on the AM parameters; see Sect.
-\ref{sec:gas}).
-The comparative analyses of the operators and their results are presented in Sect.
-\ref{sec:assessment}, which lead us to the recommendations in Sect.
-\ref{sec:recommendations}.
+We will begin by presenting the basics of the considered AM variants (section \ref{sec:am}) and the assessed GAs options (section \ref{sec:gas}).
+The comparative analyses of these options are presented in section \ref{sec:assessment}, which results in recommendations formulated in section \ref{sec:recommendations} and conclusions in section \ref{sec:conclusions}.
 
@@
 
-The concepts one needs to understand here are the following: AMs consist in searching a certain number of past situations in a meteorological archive (typically reanalysis datasets) that are the most similar, according to an analogy criteria, and to extract the observed values of the local weather variable of interest from another archive (typically local or basin averaged time series) in order to build the conditional empirical distribution considered as the probabilistic prediction for the target day.
+AMs consist in searching a certain number of past situations in a meteorological archive that are the most similar, according to an analogy criteria, and to extract the observed values of the local weather variable of interest from another archive (typically local or basin averaged time series) in order to build the conditional empirical distribution considered as the probabilistic prediction for the target day (the day one wants to predict).
+
+The present work takes place in the Perfect Prognosis framework \citep{Klein1963}, like the majority of AMs applications for precipitation prediction, and thus the meteorological archive from which the predictors are extracted is a reanalysis dataset.
+Oppositely, most applications for wind forecasting are based on a Model Output Statistics \citep[MOS, see][]{Glahn1972} context \citep[e.g.][]{DelleMonache2013, DelleMonache2011, Alessandrini2015, Junk2015, Junk2015c}.
+
 Predictors can be varied: for example the geopotential height at different pressure levels on different temporal windows (time of observation).
@@
 
-Two parameterizations are often used for precipitation downscaling: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
+Two variants are often used for precipitation downscaling: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
 
 The method based on the analogy of the synoptic circulation consists in the following steps: the similarity of the atmospheric circulation of a target date with every day of the archive is assessed by processing the S1 criteria \citep{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, on 2 different the geopotential heights (e.g.
-500 and 1000~hPa) and over a certain spatial window.
+500 and 1000~hPa) and over a certain spatial window:
+
+\begin{equation}
+\label{eq:S1}
+S1=100 \frac {\displaystyle \sum_{i} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
+{\displaystyle \sum_{i} max\left\lbrace \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert \right\rbrace }
+\end{equation}
+where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points from the grid of the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
+The differences are processed separately in both directions.
+The smaller the S1 values, the more similar the pressure fields.
+
 To cope with seasonal effects, candidate dates are extracted within a period of 4 months centered around the target date, for every year of the archive.
@@
 
-The other current parametrization adds a second level of analogy on moisture variables, more specifically on a moisture index made of the product of the precipitable water with the relative humidity at a certain pressure level \citep[e.g.
+The other current variant adds a second level of analogy on moisture variables, more specifically on a moisture index made of the product of the precipitable water with the relative humidity at a certain pressure level \citep[e.g.
 850~hPa, see][]{Bontron2004}.
@@
 
-A score that has been often used to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
+The CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000} has been often used to assess an AM performance \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}.
 It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$.
@@
 
-Genetic Algorithms \citep[GAs,][]{Holland1992b, Goldberg1989} come from the world of stochastic optimization, more specifically from metaheuristic approaches.
-These are stochastic iterative algorithms that behave like search algorithms by exploiting the characteristics of a problem and are particularly suitable for complex parameter spaces.
-
-GAs are part of the family of Evolutionary Algorithms \citep{Back1993b, Schwefel1993}, inspired by some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
-Unlike a linear or local optimization, GAs seek the global optimum on a complex surface, theoretically without restriction, but with no guarantee to reach it.
-
-\subsection{Basic concepts of the Genetic Algorithms}
-
-GAs mimic the evolution of a population of individuals in a new environment, by applying rules based on natural processes, such as DNA mutation, chromosomes crossover, natural selection, etc.
-Generation after generation, the DNA mixes and the best suited, or best adapted, genes cumulate in some individuals \citep{Beasley1996a}.
-
-Applications of GAs are diversified and can handle problems of various types \citep{Joines1996a}, even with very complex cost surfaces \citep{Haupt2004}.
-The objective function to optimize (often named fitness function in this context) can be of different types, but GAs must be adapted in order to perform optimally.
-
-Two conditions guarantee in theory the convergence to the global optimum \citep{Zitzler2004a}: (1) Parameters mutations that can allow to explore the entire parameter space, thereby ensures that any value can be achieved with a non-zero probability.
-(2) A rule of elitism ensuring that an optimal solution cannot be lost or damaged.
-
-A key element of the parametrization of GAs is finding the right balance between exploration and exploitation \citep{Back1992a, Smith1997a}.
+Genetic Algorithms \citep[GAs,][]{Holland1992b, Goldberg1989} are part of the family of Evolutionary Algorithms \citep{Back1993b, Schwefel1993}, inspired by some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
+Unlike a linear or local optimization, GAs seek the global optimum on complex surfaces, theoretically without restriction, but with no guarantee to reach it \citep{Haupt2004}.
+The objective function to optimize (often named fitness function in this context) can be of different types \citep{Joines1996a}, but GAs must be adapted in order to perform optimally.
+
+A key element of GAs configuration is finding the right balance between exploration and exploitation \citep{Back1992a, Smith1997a}.
 Exploration is characterized by a relatively high probability to assess the regions of the parameter space that have not yet been visited.
@@
 
-The GAs optimize a population of $N$ individuals (parameter sets).
+GAs optimize a population of $N$ individuals (parameter sets).
 Each individual contains a chromosome (set of parameters of our AM in this case).
@@
 They can be either categorical (e.g.
-geopotential, or temperature), discrete (e.g.
-number of analogs to select, from 1 to 40), or continuous.
-For example, a chromosome may looks like:
-
-\begin{equation}
-[p_{i,j}, h_{i,j}, \lambda w_{i,j}, \lambda e_{i,j}, \varphi s_{i,j}, \varphi n_{i,j}, p_{i,j+1}, h_{i,j+1}, ..., n_{i}, ... p_{i+1,j}, h_{i+1,j}, ..., n_{i+1}, ...]
-\end{equation}
-where, for the level of analogy $i$ and the predictor number $j$, $p_{i,j}$ is the pressure level, $h_{i,j}$ is the temporal window, $\lambda w_{i,j}$ and $\lambda e_{i,j}$ are the western and eastern longitudes of the spatial window, $\varphi s_{i,j}$ and $\varphi n_{i,j}$ are its southerly and northerly latitudes, and $n_{i,j}$ is the number of analogs.
-A chromosome for a simple AM on the atmospheric circulation only (Sect.
-\ref{sec:am}) may be: $[500~hPa, 12~h, -2.5\degree, 15\degree, 40\degree, 55\degree, 1000~hPa, 24~h, 0\degree, 15\degree, 42.5\degree, 47.5\degree, 28]$
-
-The floating-point representation \citep[instead of the canonical binary, see][]{Goldberg1989, Goldberg1990a, Holland1992b} of the genes was considered, as it was found more suited in multiple applications \citep{Michalewicz1996, Herrera1998a, Haupt2004, Back1996b, Gaffney2010a}.
+choice of the meteorological variable), discrete (e.g.
+number of analogs to select), or continuous.
 
 There are numerous implementation variants of GAs, often optimal for a given problem \citep{Hart1991a, Schraudolph1992a}.
-The divergences are in the operators implementation, through significantly different algorithms, which has an important effect on the results \citep{Gaffney2010a}.
+The differences are in the operators implementation, through significantly different algorithms, which has an important effect on the results \citep{Gaffney2010a}.
 Here, operators are defined as the mechanisms that modify the values of the genes to try bringing individuals (or chromosomes) closer to an optimum of the fitness function.
 The structure of the method (Fig.
-\ref{fig:structure_gas}) resulting from the work of \citet{Holland1992b} is common to most applications \citep{Back1993b}, and consists in the following steps:
-
-\begin{enumerate}
-	\item A population of $N$ individuals (parameter sets of the AM to optimize) is randomly generated, which constitutes the initial population.
-	\item The fitness (performance score or objective function) of every individual is assessed.
-	\item A natural selection is applied, after which only the best individuals remain, which constitutes the intermediate generation (IG).
-	\item From this IG, couples are formed according to given rules.
-	\item These couples proceed to reproduction, or chromosome crossover, to mix their genes (parameters) according to the selected operator version.
+\ref{fig:structure_gas}) resulting from the work of \citet{Holland1992b} is common to most applications \citep{Back1993b}, and consists in the following steps: (1) a population of $N$ individuals (parameter sets of the AM to optimize) is randomly generated, which constitutes the initial population.
+The fitness (performance score or objective function) of every individual is assessed.
+(2) A natural selection is applied, after which only the best individuals remain, which constitutes the intermediate generation (IG), from which (3) couples are formed according to given rules.
+Then, (4) these couples proceed to reproduction, or chromosome crossover, to mix their genes according to the selected operator version.
 New children are generated in order to refill the IG back to $N$ individuals.
-	\item Parents and children are then subject to mutation, where some genes get affected, meaning some parameter values are randomly changed.
-	\item The new formed generation is then re-assessed.
-	\item According to the ending criteria, the optimization ends or starts again for another iteration.
-\end{enumerate}
-
-All considered operators and their options, applied to floating-point coding, are described in the following sections. Many other operators exist, but only the ones evaluated are presented.
+(5) Parents and children are then subject to mutation, where some genes are randomly changed.
+Finally, (6) the new generation is then re-assessed, the best individual restored if degraded, and (7) according to the ending criteria, the optimization ends or starts again for another iteration.
+
+All considered operators and their options are described in the following sections (only briefly for operators with less importance).
+Many other operators exist, but only the ones evaluated are presented.
 
@@
 
-The first step of the optimization is to generate an initial population.
-A population is a set of $N$ individuals (each of which represents, in this application, a parameter set of an AM and thus a point in the space of potential solutions) that are going to evolve.
-A generation is the population considered at a given time.
-
-A random initialization based on a uniform sampling is the most current version.
+A random initialization based on a uniform sampling is the most current version of the initial population generation.
 The size $N$ of the population is often a compromise between the computation time and the quality of the solution.
@@
 
-Natural selection is performed on the basis of the values of the objective function.
+Natural selection is performed on the basis of the objective function values.
 The selection allows to only keep a certain part of the population, usually half ($N/2$), which can access the IG (with $N_{IG}$ members).
-If $N_{IG}$ is too high, the reproduction rate is too low, whereas if it is too small, the strong traits of individuals will not have the ability to accumulate in the same chromosome \citep{Haupt2004}.
 Several techniques exist, such as:
@@
 \begin{itemize}
-	\item $N_{IG}$-elitism \citep{Michalewicz1996}: the population is ranked according to the value of the objective function and only the better half is preserved.
-
-	\item Tournament selection \citep{Michalewicz1996, Zitzler2004a}: two individuals are randomly selected and fight.
-The one with the highest performance score is chosen, but with a certain probability, in order to reduce the selection pressure.
-This procedure is repeated until the IG is full.
-Individuals can be selected several times, and thus be represented several times in the IG.
+	\item $N_{IG}$-elitism \citep{Michalewicz1996}: only the better half is preserved.
+
+	\item Tournament selection \citep{Michalewicz1996, Zitzler2004a}: two individuals are randomly selected and the best one is chosen, but with a certain probability.
 \end{itemize}
@@
 
-Individuals of the IG can reproduce. It begins with the selection of pairs (the parents). The techniques implemented in this work are the following:
+Individuals of the IG can then reproduce, which begins with the selection of pairs (the parents). The techniques implemented in this work are the following:
 
 \begin{itemize}
-	\item Rank pairing: individuals are gathered in pairs according to their rank (based on the performance scores). Consecutive ranks are put together (odd rows are associated with even rows).
-
-	\item Random pairing: two individuals are randomly selected to form a couple, according to a uniform law.
-
-	\item Roulette wheel weighting: this technique refers to gambling, but with a biased roulette.
-Each individual is associated with a sector of the wheel with a certain opening angle, which is its probability of selection.
-The probability ($p_{n}$) assigned to the individuals is proportional to their fitness (objective function), so that the most adapted individuals have the greatest probability of reproduction.
-There are two techniques for weighting the individuals of the IG:
-
-	\textit{Roulette wheel weighting on rank}: the probability of each individual depends on its rank $n$:
-	\begin{equation}
-	p_{n}=\dfrac{N_{IG}-n+1}{\sum^{N_{IG}}_{n=1}n}
-	\label{equation_mating_rank_weighting}
-	\end{equation}
-
-	\textit{Roulette wheel weighting on fitness}: the selection probability is calculated based on the value of the objective function:
-	\begin{equation}
-	p_{n}=\frac{score_{n}-score_{N_{IG}}}{\sum_{n=1}^{N_{IG}} (score_{n}-score_{N_{IG}})}
-	\label{equation_mating_score_weighting}
-	\end{equation}
-	In this application, the last individual ($N_{IG}$) has zero probability of being selected.
-
-	\item Tournament selection: This operator is similar to the one used in natural selection, but is applied here for the successive selection of each parent.
-To select a parent, a number of individuals (2 or 3) are randomly picked and the best is kept.
-This operation is performed twice, once for each partner and imitates the breeding competition in nature \citep{Haupt2004}.
+	\item Rank pairing: individuals are gathered in pairs according to their rank.
+
+	\item Random pairing: individuals are randomly selected, according to a uniform law.
+
+	\item Roulette wheel selection \citep{Goldberg1989}: the selection probability assigned to the individuals is proportional to their fitness, so that the most adapted individuals have a greater probability of reproduction.
+There are two weighting techniques : the first one according to the rank, and the second on the fitness value.
+
+	\item Tournament selection: a number of individuals (2 or 3) are randomly picked and the best is kept, with a certain probability. This operation is performed twice, once for each partner.
 \end{itemize}
@@
 
-Once the two parents are selected for breeding, they combine their chromosomes and produce two children, bringing the number of individuals in the population back to $N$ (the parents also return back in the total population in order to complement the next generation).
+Once the two parents are selected for breeding, they combine their chromosomes and produce two children, bringing the number of individuals in the population back to $N$.
 The combination of chromosomes is carried out using a crossover operator, thereby generating two offspring having characteristics derived from both parents.
 It allows a mixing of genes and a potential accumulation of positive mutations.
-
 The evaluated crossover operators are the following:
@@
 \begin{itemize}
-	\item Single-point crossover: within the chromosome, a crossover point is randomly chosen for the pair.
-The genes (AM parameters) located after that point are exchanged in between the two chromosomes.
-
-	\item Two-point crossover: works like the single-point crossover, but there are two intersections defining the segments to be exchanged.
-This approach, which significantly extends the search space for the children, is considered more efficient than the previous \citep{Beasley1993a}.
+	\item Single-point crossover \citep{Goldberg1989}: the genes located after a randomly chosen point within the chromosome are exchanged in between the two parents.
+
+	\item Two-point crossover: similar to the single-point crossover, but with two intersections defining the segments to be exchanged, it is considered more efficient than the previous \citep{Beasley1993a}.
 
@@
 
-	\item Binary-like crossover \citep{Haupt2004}: chromosome crossover on a binary coding can generate new values for variables located at intersection points, since the crossovers are applied at the bit level, thus often within a gene.
-This is not the case for the floating-point representation, since the crossover is performed between the genes.
-To reproduce the behaviour present in the original algorithms, which introduces new information, \citet{Haupt2004} propose an operator that combines standard crossover with an interpolation approach.
+	\item Binary-like crossover \citep{Haupt2004}: in order to reproduce the behaviour present in the canonical crossover algorithm, which is applied to a binary representation of the genes \citep{Goldberg1989, Goldberg1990a, Herrera1998a}, \citet{Haupt2004} propose an operator that combines standard crossover with an interpolation approach.
 The genes located after a crossover point are exchanged, but the gene located at the intersection is modified according to:
@@
 	\end{equation}
-	where $g_{o1,n}$ and $g_{o2,n}$ are the $n$-th gene of the two new offspring, and $g_{p1,n}$ and $g_{p2,n}$ are those of the two parents. $\beta$ is a random value between 0 and 1.
-
-	\item Blending method \citep{Radcliffe1991a}: in this approach, instead of exchanging the genes in between the chromosomes after one or multiple crossover points, these are combined by linear combination (Eq.
-\ref{equation_mating_blending_method}).
-The genes of the parents are blended together using a random value ($\beta$) that can be unique for the whole chromosome, or that can change for every gene.
-The genes of the offspring are bounded by the genes of the parents, no value can be out of their range.
-	\begin{equation}
-	\left\lbrace \begin{array}{l} 
-	g_{o1,n} = \beta g_{p1,n} + (1-\beta)g_{p2,n} \\ 
-	g_{o2,n} = (1-\beta) g_{p1,n} + \beta g_{p2,n} \\
-	\end{array} \right.
-	\label{equation_mating_blending_method}
-	\end{equation}
-
-	\item Linear crossover \citep{Wright1991a}: in order to allow the genes to take values outside the interval defined by the parents, a method of extrapolation is necessary.
-Linear crossover introduces such an approach, and produces three children from two parents, following Eq.
-\ref{equation_mating_linear_crossover}.
-Less couples are required in order to fill up the population.
-	\begin{equation}
-	\left\lbrace \begin{array}{l} 
-	g_{o1,n} = 0.5 g_{p1,n} + 0.5 g_{p2,n} \\ 
-	g_{o2,n} = 1.5 g_{p1,n} - 0.5 g_{p2,n} \\ 
-	g_{e3,n} = - 0.5 g_{p1,n} + 1.5 g_{p2,n} \\ 
-	\end{array} \right.
-	\label{equation_mating_linear_crossover}
-	\end{equation}
-
-	\item Heuristic crossover \citep{Michalewicz1996}: it is a variation of the latter methods that relies on the following equation:
-	\begin{equation}
-	\left\lbrace \begin{array}{l} 
-	g_{o1,n} = \beta (g_{p1,n} - g_{p2,n}) + g_{p1,n} \\
-	g_{o2,n} = \beta (g_{p2,n} - g_{p1,n}) + g_{p2,n} \\
-	\end{array} \right.
-	\label{equation_mating_heuristic_crossover}
-	\end{equation}
-
-	\item Linear interpolation: unlike previous techniques, this technique does not rely on crossover points, but on a linear interpolation on every gene of the couple (Eq.
-\ref{equation_mating_linear_interpolation}).
-	\begin{equation}
-	\left\lbrace \begin{array}{l} 
-	c_{o1} = c_{p1} - \beta (c_{p1} - c_{p2}) \\
-	c_{o2} = c_{p2} + \beta (c_{p1} - c_{p2}) \\
-	\end{array} \right.
-	\label{equation_mating_linear_interpolation}
-	\end{equation}
-	where $c_{o1}$ and $c_{o2}$ are the full chromosomes of the offspring, and $c_{p1}$ an $c_{p2}$ are the ones of the parents.
-As before, $\beta$ is a random value between 0 and 1, and is here the same for every gene.
-
-	\item Free interpolation: this technique performs interpolation on each gene, like the previous one; but in this case, the weighting factor changes for each gene:
-	\begin{equation}
-	\left\lbrace \begin{array}{l} 
-	c_{o1} = c_{p1} - [\beta_{1} (g_{p1,1} - g_{p2,1}), \beta_{2} (g_{p1,2}\\
-	~~~~~~~~~~~~ - g_{p2,2}), ..., \beta_{Ng} (g_{p1,N_{g}} - g_{p2,N_{g}})] \\
-	c_{o2} = c_{p2} + [\beta_{1} (g_{p1,1} - g_{p2,1}), \beta_{2} (g_{p1,2}\\
-	~~~~~~~~~~~~ - g_{p2,2}), ..., \beta_{Ng} (g_{p1,N_{g}} - g_{p2,N_{g}})] \\
-	\end{array} \right.
-	\label{equation_mating_free_interpolation}
-	\end{equation}
-	where $N_{g}$ is the number of genes, and $\beta$ is here independent between the genes.
+	where $g_{o1,n}$ and $g_{o2,n}$ are the $n$-th gene of the two new offspring, and $g_{p1,n}$ and $g_{p2,n}$ are those of the two parents.
+$\beta$ is a random value between 0 and 1, that can be unique for the whole chromosome, or that can change for every gene.
+
+	\item Blending method \citep{Radcliffe1991a}: in this approach, instead of exchanging the genes in between the chromosomes after some crossover points, these are combined by linear combination, also using a random value $\beta$.
+
+	\item Linear crossover \citep{Wright1991a}: it widens the range of gene values, and produces three children from two parents.
+
+	\item Heuristic crossover \citep{Michalewicz1996}: it is a variation of the blending method.
+
+	\item Linear interpolation: unlike previous techniques, this one does not rely on crossover points, but on a linear interpolation on every gene of the couple, also using a random value $\beta$, which is the same for every gene.
+
+	\item Free interpolation: this technique performs interpolation on each gene, like the previous one; but in this case, the weighting factor $\beta$ changes for each gene.
 
@@
 
-The mutation operator is a direct modification of genes.
-In real coding, it is done by changing the gene values.
-Mutations add diversity to the population and prevent a freeze of the evolution, or a genetic drift to a local optimum.
-Thus, it makes the convergence to the global optimum theoretically possible \citep{Beasley1993a}, as they allow exploring beyond the current region of the parameter space by bringing new characteristics that were not present in the original population \citep{Haupt2004}.
-
-The evaluated and developed mutation operators are listed hereafter.
+The mutation operator is a direct modification of some gene values.
+It adds diversity to the population and prevents a freeze of the evolution, or a genetic drift to a local optimum.
+Thus, it makes the convergence to the global optimum theoretically possible \citep{Beasley1993a}, as it allows exploring beyond the current region of the parameters space by bringing new characteristics that were not present in the original population \citep{Haupt2004}.
+
+The evaluated and developed mutation operators are listed hereafter (equations are only provided for the operator versions that were found relevant; the user can refer to the corresponding literature for the details of the other options).
 They apply to genes made of continuous or discrete variables, but not categorical (eg meteorological variable or analogy criterion).
@@
 \begin{itemize}
-	\item Uniform mutation: The mutation rate ($p_{mut}$) is constant and equal for every gene of each individual; they all have the same probability to mutate.
+	\item Uniform mutation: the mutation rate ($p_{mut}$) is constant and equal for every gene of each individual; they all have the same probability to mutate.
 When a gene is selected for mutation, a new random value is assigned, according to a uniform law.
@@
 In most applications, the mutation rate decreases with the generations, in a deterministic and global (for all individuals) manner \citep{Back1992b}.
-Its optimum configuration depends on the size of the chromosomes, of the properties of the objective function, and of the population size \citep{Back1992b}.
-This operator was implemented according to:
-	\begin{equation}
-	p_{n,G} = p_{G_{0}}+\left( \dfrac{p_{G_{0}}-p_{G_{m,p}}}{G_{m,p}} \right) min\left\lbrace G,G_{m,p}\right\rbrace 
-	\label{equation_mutation_uniformvariable}
-	\end{equation}
-	where $p_{n,G}$ is the mutation rate (probability) of the gene $n$ for generation number $G$, $G_{m,p}$ is the maximum number of generations during which the mutation rate varies.
-$p_{G_{0}}$ is the initial mutation probability, and $p_{G_{m,p}}$ is the final one.
-$p_{G_{0}}$, $p_{G_{m,p}}$ and $G_{m,p}$ are the three controlling parameters of the operator.
-The evolution of the mutation rate is linear.
-
-	\item Constant normal mutation: many applications use normal distributions to generate new values. The gene $g$ that mutate becomes:
-	\begin{equation}
-	g' = N(g,\sigma^{2})
-	\label{equation_mutating_normal_distribution}
-	\end{equation}
-	where $\sigma$ is the standard deviation of the distribution, which has to be estimated.
-
-	\item Variable normal mutation (new): with the same logic as the variable uniform mutation, a mutation operator was tested using a normal distribution with a variable mutation rate and standard deviation.
-The mutation rate is calculated with Eq.
-\ref{equation_mutation_uniformvariable}.
-On the same principle, the standard deviation decreases linearly over the generations:
-	\begin{equation}
-	\sigma_{n,G} = \sigma_{G_{0}}+\left( \dfrac{\sigma_{G_{0}}-\sigma_{G_{m,\sigma}}}{G_{m,\sigma}} \right) min\left\lbrace G,G_{m,\sigma}\right\rbrace 
-	\label{equation_mutation_normalvariable}
-	\end{equation}
-	where $\sigma_{n,G}$ is the standard deviation of gene $n$ and generation number $G$, $\sigma_{G_{0}}$ is the initial standard deviation, $\sigma_{G_{m,\sigma}}$ is the final standard deviation, $G_{m,\sigma}$ is the maximum number of generations during which the standard deviation varies.
-$p_{G_{0}}$, $p_{G_{m,p}}$, $G_{m,p}$, $\sigma_{G_{0}}$, $\sigma_{G_{m,\sigma}}$ and $G_{m,\sigma}$ are the six parameters of the method.
+
+	\item Constant normal mutation: it uses normal distributions to generate new values of the gene, based on an estimated standard deviation.
+
+	\item Variable normal mutation \citep{Horton2012a}: with the same logic as the variable uniform mutation, a mutation operator was tested using a normal distribution with a variable mutation rate and standard deviation, that decrease linearly over the generations.
+This operator has 6 parameters.
 
@@
 The new value of the gene is given by the following equation, according to a predefined number of generations:
-	\begin{equation}
-	g_{n}^{'} = 
-	\left\lbrace \begin{array}{l l} 
-	g_{n} + \left(b_{n}-g_{n}\right) r_{2} \left(1 - \dfrac{G}{G_{m}} \right)^{2} & if \; r_{1} < 0.5 \\
-	g_{n} - \left(g_{n}-a_{n}\right) r_{2} \left(1 - \dfrac{G}{G_{m}} \right)^{2} & if \; r_{1} \geq 0.5 \\
-	\end{array} \right.
-	\label{equation_mutation_nonuniform_original}
-	\end{equation}
-	where $a_{n}$ is the is the lower bound of the $n$-th gene, $b_{n}$ its upper bound, $G$ the present generation, and $G_{m}$ the maximum number of generations.
-
-	This operator was adapted for this application, which is not based on a predefined number of generations:
 	\begin{equation}
@@
 	\end{array} \right.
-	\label{equation_mutation_nonuniform}
+	\label{equation_mutation_nonuniform_original}
 	\end{equation}
@@
 	\begin{equation}
-	\varphi = 1 - \min \left\lbrace \dfrac{G}{G_{m,r}}, 1 \right\rbrace \left(1-\omega\right)
+	\varphi = 1 - \dfrac{G}{G_{m}}
 	\end{equation}
 
+	where $a_{n}$ is the is the lower bound of the $n$-th gene, $b_{n}$ its upper bound, $G$ the present generation, and $G_{m}$ the maximum number of generations.
+
+	This operator was adapted for this application, which is not based on a predefined number of generations, by changing $\varphi$ with $\varphi'$:
+
+	\begin{equation}
+	\varphi' = 1 - \min \left\lbrace \dfrac{G}{G_{m,r}}, 1 \right\rbrace \left(1-\omega\right)
+	\end{equation}
+
 	where $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a threshold chosen by the user to maintain a minimum search radius when $G>G_{m,r}$.
-During the first generations, the exploration extent covers the entire parameter space.
+During the first generations, the exploration extent covers the entire parameters space.
 However, this area is reduced over generations, allowing exploitation of local solutions.
@@
 The idea is to distribute control parameters within individuals themselves, which partially decentralize control of the evolution.
-It allows reducing the parametrization of GAs and introducing a notion of self-management.
+It allows reducing the manual tuning of GAs and introduces a notion of self-management.
 The first approach is the introduction of a mutation rate per individual, that mutates itself under its own probability \citep{Back1992a}.
@@
 This search radius $r_{a}$, bounded between 0 and 1 (relatively to the parameters ranges), is also adaptive and behaves similarly to the adaptive mutation rates.
-In order to separate its evolution from the one of the mutation rate, its own value is considered initially as a self-mutation rate to eventually mutate before being used as a normalized search radius.
+In order to separate its evolution from the one of the mutation rate, its own value is also considered as a self-mutation rate to eventually mutate before being used as a normalized search radius.
 The value of a mutated gene is given by the following equation, which is a simplification of the non-uniform mutation:
@@
 The difference here is that each gene has a specific mutation rate.
-The main advantage is that the tuning of the mutation can be much more precise \citep{Smith1997a}.
+The main advantage is that the automatic tuning of the mutation can be much more precise \citep{Smith1997a}.
 A second chromosome containing the mutation rate for each gene of the first chromosome was therefore considered.
 The operations of mutation and self-mutation are similar to the case of the individual adaptive mutation rate, but in a distributed way, within the chromosome.
-Another difference is that the same crossover operations are applied as those applied to the first chromosome, and this for the same crossing points.
+Moreover, the same crossover operations are applied to this new chromosome, as those applied to the first chromosome, and this for the same crossing points.
 Thus, during an exchange of genes, children also inherit the mutation rates specific for each of these genes.
@@
 
-A process of elitism was introduced on the natural selection as well as on mutations.
+A process of elitism was considered after both the natural selection and mutations.
 This ensures the survival of the best individual so that a better solution is never lost.
@@
 The convergence check determines whether the solution is acceptable and if the algorithm may stop.
-The stopping criteria are not often well documented in GAs case studies.
 The optimization is here stopped if the best individual does not change for $x$ generations.
@@
 
+GAs are very computationally intensive because they require many evaluations of the objective function.
+These assessments are very long in this application, as they require calculating and assessing a prediction for every day of the calibration period, thus over several decades.
+In order to reduce the computation time, recalculating the performance score of an individual who has previously been evaluated and that has not changed was avoided.
+Thus, the score of each individual living in the selection was kept until it mutates.
+
+As the assessment (calculation of the objective function) of each member of the population of a generation is completely independent, it was performed in parallel on different processors of a computer.
+In order to perform optimizations for multiple time series, the use of a cluster is a necessity, which our code allows.
+
 Some constraints need to be taken into account.
@@
 New values resulting from the optimizer need to respect the type of data it represents.
-
-Other constraints exist in between the parameters, such as the temporal window of the moisture index that has to be consistent in between the relative humidity and the precipitable water.
-
-GAs are very computationally intensive because they require many evaluations of the objective function.
-These assessments are very long in this application, as they require calculating and assessing a prediction for every day of the calibration period, thus over several decades.
-In order to reduce the computation time, recalculating the performance score of an individual who has previously been evaluated and that has not changed was avoided.
-Thus, the score of each individual living in the selection was kept until it mutates.
-
-As the assessment (calculation of the objective function) of each member of the population of a generation is completely independent, it was performed in parallel on different processors of a computer.
-In order to perform optimizations for multiple time series, the use of a cluster is a necessity, which our code allows.
+Other constraints exist in between the parameters, e.g.
+the hours of observation of the relative humidity and the precipitable water predictors have to match when processing the moisture index.
 
@@
 
-The GAs parametrization, i.e.
-the a priori choices such as the mutation rate, population size, natural selection options, etc, appears difficult given the high number of existing variants, each developed for a specific problem \citep{Haupt2004, Costa2007a}.
-The parametrization depends on the objective function, implementation variants, the range of the parameters to be optimized, and performance indicators.
-Thus, different studies suggest very different parameterizations.
-
-\citet{DeJong1975a} and \citet{Grefenstette1986} compared different implementations and parametrizations of GAs on functions of varying complexity.
-They observed that a small population size improves the initial performance, while a large population improves latter performance.
-They also observed that the proportion of the population to keep for the IG is around 50\% (45\% to 60\%).
-
-Values of the mutation rate ($p$) varies broadly between studies: from 0.001 \citep{DeJong1975a} to 0.2 \citep{Haupt2004}.
-\citet{Back1996b} showed that mutation rates higher than the usual ranges are more optimal at the beginning of the optimization, allowing further exploration.
-Varying mutation rates are certainly more optimal but more complex to implement \citep{Back1996a, Back1996b}.
+The choice of GAs options, such as the mutation rate, population size, natural selection options, etc, appears difficult given the high number of existing variants, each developed for a specific problem \citep{Haupt2004, Costa2007a}.
+Thus, different studies suggest very different configurations \citep{DeJong1975a, Grefenstette1986, Back1996a, Back1996b}.
 
@@
 
-One of our goals being to make recommendations of parametrization in view of optimizing AM variants, a systematic procedure was adopted.
+One of our goals being to make recommendations of how to use GAs in view of optimizing AM variants, a systematic procedure was adopted.
 The results are summarized hereafter \citep[see][for the details]{Horton2012a}.
-Concepts were taken from the factorial design approach \citep[see eg.][]{Costa2005a,Costa2007a,Mariano2010a}, which is sometimes used for comparative analysis of different parametrizations of GAs.
+In order to compare different configurations of GAs, the factorial design approach was applied, in a similar way as \citet{Costa2005a,Costa2007a} and \citet{Mariano2010a}.
 It allows isolating the effect of a parameter under different combinations of the other options.
@@
 
-In order to evaluate a combination of operators/options, 10 optimizations per parametrization of GAs were processed.
+In order to evaluate a combination of operators/options, 10 optimizations per configuration of GAs were processed.
 Such assessment is not possible on the whole archive length, and had to be performed on a reduced period.
@@
 \ref{fig:gas_evolution_good}).
-Even GAs parameterizations that will be considered later as inadequate (Fig.
+Even GAs configurations that will be considered later as inadequate (Fig.
 \ref{fig:gas_evolution_bad}) did significantly better that the sequential approach.
@@
 \subsection{Results of the comparison}
+\label{sec:assessment:results}
 
@@
 From the very beginning of the assessments, the importance of the mutation operator was obvious \cite[see][for the details]{Horton2012a}, and its leading influence on the optimization performance was evident.
-Its role is analyzed later on.
+Its role is analyzed later on in section \ref{sec:assessment}.\ref{sec:assessment:results}.\ref{sec:assessment:mutation}.
 
@@
 Binary-like crossover (especially with 2 points of intersection, whether $\beta$ is shared or not) are significantly better than the others, especially in terms of convergence (not shown).
-Others operators can also be considered usable.
 
@@
 Having identified the leading role of the mutation operator, the next sensitivity analysis focused on it.
-Each of the 10 different implementations (see Sect.
-\ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Table \ref{tab:assessed_mutation_operators}), bringing the number of variations up to 109.
+Each of the 10 different implementations (see section \ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Table \ref{tab:assessed_mutation_operators}), bringing the number of variations up to 109.
 Some optimizations without any mutation were also performed as a reference.
@@
 Figure \ref{fig:operator_mutation_score} show the results of this analysis and illustrates the important role of the mutation on the performance of the optimizations.
-Those without mutation (last box on the figure) are inferior to most mutation operators, and the scale of the influence of this operator is significantly more important than those for the other options.
+Those without mutation (last box on Figure \ref{fig:operator_mutation_score}) are inferior to most mutation operators, and the scale of the influence of this operator is significantly more important than those for the other options.
 The details of the analysis \citep[see][]{Horton2012a} show that the other reproduction operators seem of secondary importance.
-This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction, as well as other authors (see Sect.
-\ref{sec:gas}.\ref{sec:gas:mutation}).
+This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction, as well as other authors (see section \ref{sec:gas}.\ref{sec:gas:mutation}).
 
@@
 The optimizer could choose the 2 pressure levels of the atmospheric circulation analogy (method with a single level of analogy).
-The resulting CRPSS performance score (Sect.
-\ref{sec:am}) is obviously superior to the one obtained by the sequential calibration (red line on Fig.
+The resulting CRPSS performance score (section \ref{sec:am}) is obviously superior to the one obtained by the sequential calibration (red line on Fig.
 \ref{fig:operator_mutation_score_atmlevel}).
@@
 A clear breakthrough of the performances was not expected, as the former selection of pressure levels results already from intensive comparative work \citep{Bontron2004}.
-This application however demonstrates that, when correctly parametrized, GAs can automatically and successfully choose the pressure levels.
+This application however demonstrates that, when correctly configured, GAs can automatically and successfully choose the pressure levels.
 However, some less relevant optimizations do not match the previous results.
@@
 \ref{fig:operator_mutation_score_r2}).
-And finally, a preselection on air temperature was added instead of the fixed calendar window, as proposed by \cite{BenDaoud2015}.
+And finally, a preselection on air temperature was added instead of the fixed calendar window, as proposed by \cite{BenDaoud2016}.
 The results show generally higher scores (Fig.
@@
 
-After analysis of the most relevant mutation operators, the following advice can be raised (detailed parametrization are provided in Sect. \ref{sec:recommendations}):
+After analysis of the most relevant mutation operators, the following advice can be raised (detailed options are provided in section \ref{sec:recommendations}):
 
@@
 
-	\item \textit{Non-uniform mutation} \citep{Michalewicz1996}: this operator is good in terms of convergence, mainly when the number of parameters to optimize is rather low.
+	\item \textit{Non-uniform mutation}: this operator is good in terms of convergence, mainly when the number of parameters to optimize is rather low.
 The number of required evaluations, however, can be quite substantial.
@@
 
-	\item \textit{Chromosome of adaptive search radius} (new): unlike the previous one, this new operator is very robust, as it requires no option and is auto-adapting.
+	\item \textit{Chromosome of adaptive search radius}: unlike the previous one, the proposed operator is very robust, as it requires no option and is auto-adapting.
 It is interesting to notice that the insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).
@@
 
-	\item \textit{Multi-scale mutation} (new): finally, the multi-scale mutation, which also performs pretty well, requires one parameter, the mutation rate.
+	\item \textit{Multi-scale mutation}: finally, the multi-scale mutation, which also performs pretty well, requires one parameter, the mutation rate.
 However, it can also be difficult to estimate a correct value a priori.
@@
 
-\section{Recommended parametrization of GAs}
+\section{Recommended configuration of GAs}
 \label{sec:recommendations}
@@
 \section{Conclusions}
+\label{sec:conclusions}
 
@@
 Recommendations were established for a relevant use of GAs for the optimization of AMs.
+If using GAs to optimize AMs is computationally intensive, once an AM is calibrated, its use in real-time operations it very fast and lightweight.
 
 It is not excluded that another global optimization method or other operators of GAs may perform still better.
-However, the relevance of such an approach has now been proved as it results in parametrization of AMs that are relevant and fully automatically, globally and objectively established.
+However, the relevance of such an approach has now been proved as it results in parameters of AMs that are relevant and fully automatically, globally and objectively established.
 A global optimization is the only way to take into account all the dependencies between parameters and levels of analogy.
@@
 	\end{center}
-	\caption{Genetic Algorithms operational flowchart}
+	\caption{Genetic Algorithms operational flowchart.}
 	\label{fig:structure_gas}
@@
 	\end{center}
-	\caption{Evolution of the score of the best individuals over generations for the 10 optimizations processed for a given parametrization.
-The continuous bottom line represents the score of the sequential approach and the dashed one (top), the supposed global optimum.}
+	\caption{Evolution of the score of the best individuals over generations for the 10 optimizations processed for a given configuration.
+The continuous bottom line represents the score of the sequential approach and the dashed one (top), the supposed global optimum.
+The circles represent the end of the optimization (when the best individual did not progress during 20 generations).}
 	\label{fig:gas_evolution_good}
@@
 	\end{center}
-	\caption{Same as Fig. \ref{fig:gas_evolution_good}, but for a GAs parametrization considered as less relevant.}
+	\caption{Same as Fig. \ref{fig:gas_evolution_good}, but for a GAs configuration considered as less relevant.}
 	\label{fig:gas_evolution_bad}

### 2016-09-02 Genetic algorithms - MWR/template.tex
Removing tables and adding more info in figures.

@@
 \subsection{Structure and operators}
+\label{sec:gas:operators}
 
@@
 \subsubsection{Natural selection}
+\label{sec:gas:nat_selection}
 
@@
 \subsubsection{Selection of the couples}
+\label{sec:gas:selection_couples}
 
@@
 \subsubsection{Chromosome crossover}
+\label{sec:gas:crossover}
 
@@
 
-Every combination of 6 options for the couples selection (Table \ref{tab:assessed_couples_selection_operators}) and 21 for the chromosome crossover operators (Table \ref{tab:assessed_crossover_operators}) were evaluated, along with variants of the other operators.
+Every combination of 6 options for the couples selection (Fig.
+\ref{fig:operator_selectcoupl_score}) and 21 for the chromosome crossover operators (Fig.
+\ref{fig:operator_crossover_score}) were evaluated, along with variants of the other operators.
 This resulted in 1,008 combinations, requiring 10,080 optimizations.
@@
 Having identified the leading role of the mutation operator, the next sensitivity analysis focused on it.
-Each of the 10 different implementations (see section \ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Table \ref{tab:assessed_mutation_operators}), bringing the number of variations up to 109.
+Each of the 10 different implementations (see section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Figure \ref{fig:operator_mutation_score}), bringing the number of variations up to 109.
 Some optimizations without any mutation were also performed as a reference.
@@
 The details of the analysis \citep[see][]{Horton2012a} show that the other reproduction operators seem of secondary importance.
-This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction, as well as other authors (see section \ref{sec:gas}.\ref{sec:gas:mutation}).
+This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction, as well as other authors (see section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:mutation}).
 
@@
 The convergence analysis \citep[see][]{Horton2012a} allows one to highlight three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
-Thus, different optimizations were further performed using variants of these 3 operators (Table \ref{tab:assessed_mutation_operators_bis}).
+Thus, different optimizations were further performed using variants of these 3 operators (Figures \ref{fig:operator_mutation_score_atmlevel}-\ref{fig:operator_mutation_score_r4}).
 
@@
 
-\begin{table}[t]
-	\caption{Assessed operator for couples selection.}
-	\begin{center}
-		\begin{tabular}{ll}
-			\hline\hline  & \textbf{Couples selection operators} \\ 
-			\hline 
-			A & Rank pairing \\ 
-			B & Random pairing \\ 
-			C & Roulette wheel weighting on rank \\ 
-			D & Roulette wheel weighting on fitness \\ 
-			E & Tournament selection (3 candidates) \\ 
-			F & Tournament selection (4 candidates) \\ 
-			\hline 
-		\end{tabular}
-	\end{center}
-	\label{tab:assessed_couples_selection_operators}
-\end{table}
-
-\begin{table}[t]
-	\caption{Assessed operators for chromosome crossover.}
-	\begin{center}
-		\begin{tabular}{ll}
-			\hline\hline  & \textbf{Chromosome crossover operators} \\ 
-			\hline 
-			1 & Single-point crossover \\
-			2 & Two-point crossover \\
-			3 & Multiple-point crossover (3 points) \\
-			4 & Multiple-point crossover (5 points) \\
-			5 & Uniform crossover \\
-			6 & Blending method (2 points, unshared $\beta$) \\
-			7 & Blending method (4 points, unshared $\beta$) \\
-			8 & Blending method (2 points, shared $\beta$) \\
-			9 & Blending method (4 points, shared $\beta$) \\
-			10 & Linear crossover (2 points) \\
-			11 & Linear crossover (4 points) \\
-			12 & Heuristic crossover (2 points, unshared $\beta$) \\
-			13 & Heuristic crossover (4 points, unshared $\beta$) \\
-			14 & Heuristic crossover (2 points, shared $\beta$) \\
-			15 & Heuristic crossover (4 points, shared $\beta$) \\
-			16 & Binary-like crossover (2 points, unshared $\beta$) \\
-			17 & Binary-like crossover (4 points, unshared $\beta$) \\
-			18 & Binary-like crossover (2 points, shared $\beta$) \\
-			19 & Binary-like crossover (4 points, shared $\beta$) \\
-			20 & Linear interpolation \\
-			21 & Free interpolation \\
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{tab:assessed_crossover_operators}
-\end{table}
-
-\begin{table}[t]
-	\caption{Assessed mutation operators with the number of variants considered (combination of parameters).}
-	\begin{center}
-		\begin{tabular}{llc}
-			\hline\hline  & \textbf{Mutation operator} & \textbf{Variants}\\ 
-			\hline 
-			1 & Uniform mutation & 3 \\
-			2 & Variable uniform mutation & 27 \\
-			3 & Constant normal mutation & 9 \\
-			4 & Variable normal mutation & 36 \\
-			5 & Non-uniform mutation & 27 \\
-			6 & Individual adaptive mutation rate & 1 \\
-			7 & Individual adaptive search radius & 1 \\
-			8 & Chromosome of adaptive mutation rate & 1 \\
-			9 & Chromosome of adaptive search radius & 1 \\
-			10 & Mutli-scale mutation & 3 \\
-			11 & No mutation & 1 \\
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{tab:assessed_mutation_operators}
-\end{table}
-
-\begin{table}[t]
-	\caption{Further assessments of mutation operators.}
-	\begin{center}
-		\begin{tabular}{llrrr}
-			\hline\hline  & \textbf{Mutation operator} & \textbf{$p_{mut}$} & \textbf{$G_{max}$} & \textbf{$\omega$}\\ 
-			\hline 1 & Non-uniform mutation & 0.01 & 50 & 0.1 \\
-			2 & Non-uniform mutation & 0.05 & 50 & 0.1 \\
-			3 & Non-uniform mutation & 0.1 & 50 & 0.1 \\
-			4 & Non-uniform mutation & 0.2 & 50 & 0.1 \\
-			5 & Non-uniform mutation & 0.4 & 50 & 0.1 \\
-			6 & Non-uniform mutation & 0.01 & 100 & 0.1 \\
-			7 & Non-uniform mutation & 0.05 & 100 & 0.1 \\
-			8 & Non-uniform mutation & 0.1 & 100 & 0.1 \\
-			9 & Non-uniform mutation & 0.2 & 100 & 0.1 \\
-			10 & Non-uniform mutation & 0.4 & 100 & 0.1 \\
-			11 & Mutli-scale mutation &  0.01 &&\\
-			12 & Mutli-scale mutation &  0.05 && \\
-			13 & Mutli-scale mutation &  0.1 && \\
-			14 & Mutli-scale mutation &  0.2 && \\
-			15 & Mutli-scale mutation &  0.4 && \\
-			16 & \multicolumn{4}{l}{Chromosome of adaptive search radius} \\
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{tab:assessed_mutation_operators_bis}
-\end{table}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	\end{center}
-	\caption{Influence of the couples selection operators (Table \ref{tab:assessed_couples_selection_operators}) on the optimization performance (improvement of the score).
+	\caption{Influence of the couples selection operators (section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:nat_selection}) on the optimization performance (improvement of the score).
 The box extends from the lower to upper quartile values of the data, with a line at the median.
@@
 	\end{center}
-	\caption{Influence of the chromosome crossover operators (Table \ref{tab:assessed_crossover_operators}) on the optimization performance (improvement of the score).
+	\caption{Influence of the chromosome crossover operators (section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:crossover}) on the optimization performance (improvement of the score).
+$\beta$s represent a shared $\beta$ parameter, and $\beta$u the unshared version.
 Same conventions as Fig.
@@
 	\end{center}
-	\caption{Influence of the mutation operators (Table \ref{tab:assessed_mutation_operators}) on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
+	\caption{Influence of the mutation operators (section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:mutation}) on the optimization performance.
+In parentheses is the number of variants considered (combination of options).
+Same conventions as Fig.
+\ref{fig:operator_selectcoupl_score}.}
 	\label{fig:operator_mutation_score}
@@
 	\end{center}
-	\caption{Influence of the mutation operators (Table \ref{tab:assessed_mutation_operators_bis}) on the optimization performance, leaving the optimizer choose the pressure level of the atmospheric circulation analogy (single level of analogy).
+	\caption{Influence of the mutation options (section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:mutation}) on the optimization performance, leaving the optimizer choose the pressure level of the atmospheric circulation analogy (single level of analogy).
+For the non-uniform mutation, $\omega=0.1$ in every case.
 The predictand is precipitation over a subcatchment in the Swiss Alps (Binn-Simplon region).

### 2016-09-02 Genetic algorithms - MWR/template.tex
GAs paper under correction.

@@
 In order to evaluate a combination of operators/options, 10 optimizations per configuration of GAs were processed.
-Such assessment is not possible on the whole archive length, and had to be performed on a reduced period.
+With all assessed combinations of GAs options, 21,630 optimizations were performed on an Intel Xeon based HPC cluster with 96 cpu, running Linux RedHat.
+Such assessment is not possible on the whole archive length, and had to be performed on a reduced period (5 years).
+The total resources needed for this comparison amounts to 229,539 h/cpu (26.2 years).
+One should remember that these intensive resources were needed in order to assess multiple combinations of GAs options in order to provide recommendations.
+Based on these, applying GAs to optimize AMs require some computational power, but not as much (the time needed is function of the archive length, the population number, the other GAs options, and the complexity of the AM to optimize).
+
 The performances were characterized by four indicators: (i) mean performance score: average of the final scores of the 10 optimizations, (ii) convergence: the number of optimizations that converged to a supposed global optimum, (iii) number of generations: characterization of the convergence speed, and (iv) number of evaluations of the objective function: characterization of the required calculation time.
@@
 The convergence analysis \citep[see][]{Horton2012a} allows one to highlight three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
-Thus, different optimizations were further performed using variants of these 3 operators (Figures \ref{fig:operator_mutation_score_atmlevel}-\ref{fig:operator_mutation_score_r4}).
+Thus, different optimizations (an additional 4,950) were further performed using variants of these 3 operators (Figures \ref{fig:operator_mutation_score_atmlevel}-\ref{fig:operator_mutation_score_r4}).
 
@@
 \ref{fig:operator_mutation_score_r2}) based on moisture variables \citep[see][]{Bontron2004}.
-GAs had to optimize both levels of analogy simultaneously.
-Once again, despite the difficulty to do so, the results were better than the sequential calibration (red line on Fig.
+GAs had to optimize both levels of analogy (on the geopotential height first, and then on the moisture index made of relative humidity and precipitable water) simultaneously.
+Once again, despite the difficulty to do so, the results were better than the sequential calibration (bottom line on Fig.
 \ref{fig:operator_mutation_score_r2}).
@@
 \ref{fig:option_taillepop_score}).
-A bigger population leads to better results, but also to significantly longer optimizations.
-Indeed, the required number of evaluation, and thus the required time, is approximately proportional to the population size.
+A bigger population leads to better results, but also to longer optimizations: the required number of evaluation, and thus the required time, is approximately proportional to the population size.
+Thus, if the population size is doubled, the time required for the optimization also nearly doubles (e.g., for a 5 years calibration period, approximately 4~h/cpu was needed when $N = 50$, and 14~h/cpu when $N = 200$).
 The optimal size seems to depend on the complexity of the AM to optimize: a more complex AM (ie.

### 2016-09-02 Genetic algorithms - MWR/template.tex
Adding description of the data and the study area.

@@
 
-\journal{jcli}
+\journal{mwr}
 
@@
 
-Even though the method is rather simple compared to numerical weather prediction (NWP) models, it contains a certain number of parameters one needs to determine, such as the choice of the predictor variable, its pressure level and temporal window (hour of observation of the predictor) to consider, the spatial domain to use for the comparison, as well as the analogy criteria itself, and finally the number of analog situations to keep at each subsampling level.
+Even though the method is rather simple, it contains a certain number of parameters one needs to determine, such as the choice of the predictor variable, its pressure level and temporal window (hour of observation of the predictor) to consider, the spatial domain to use for the comparison, as well as the analogy criteria itself, and finally the number of analog situations to keep at each subsampling level.
 
@@
 
-We will begin by presenting the basics of the considered AM variants (section \ref{sec:am}) and the assessed GAs options (section \ref{sec:gas}).
+We will begin by presenting the basics of the considered AM variants (section \ref{sec:method_data}) and the assessed GAs options (section \ref{sec:gas}).
 The comparative analyses of these options are presented in section \ref{sec:assessment}, which results in recommendations formulated in section \ref{sec:recommendations} and conclusions in section \ref{sec:conclusions}.
+
+\section{Case study and data}
+\label{sec:case_study_data}
+
+The study area is the alpine upper Rh\^{o}ne catchment in Switzerland (Fig.\ \ref{fig:map}).
+The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$.
+This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at allowing real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
+Based on different climatological analyses, the gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}).
+
+The overall aim of the project is to implement a real-time precipitation and discharge forecasting in the catchment.
+An AM is used to provide real-time probabilistic forecasts of precipitation, based on NWP outputs.
+However, before being applied in the forecasting context, the AM must be calibrated for the given region, which is done here in the Perfect Prognosis framework \citep{Klein1963}, like the majority of AMs calibration procedures for precipitation prediction cited previously \cite[with the exception of][]{Hamill2006,Hamill2015b}.
+
+\subsection{Data}
+\label{sec:data}
+
+The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series one wants to predict.
+
+Working in the Perfect Prognosis framework, the meteorological archive from which the predictors are extracted is a reanalysis dataset.
+Oppositely, other applications of AMs for wind forecasting are based on a Model Output Statistics \citep[MOS, see][]{Glahn1972} context, and thus use forecast archives or reforecast products \citep[e.g.][]{DelleMonache2013, DelleMonache2011, Alessandrini2015, Junk2015, Junk2015c}.
+
+In the present study, the NCEP-NCAR reanalysis I dataset \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} is used, but it could be any other reanalysis dataset.
+This dataset is relatively old, even though still widely used, and better results may be expected with more recent datasets.
+However, we can safely make the assumption that if the optimization technique works for this reanalysis dataset, it will also work on an improved one.
+
+The predictand (which is to be predicted) is here the daily precipitation (6~a.m.
+to 6~a.m.
+the next day) measured at the MeteoSwiss' stations network in the alpine upper Rh\^{o}ne catchment in Switzerland.
+The time series from every available gauging station were averaged over subregions of approximately 500~km$^{2}$ \citep[see][for the details]{Horton2012a} in order to smooth local effects \citep{Obled2002, Marty2012}.
 
@@
 
-% TODO: Add description of the method
+AMs are based on the principle that two similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}.
+Thus, they consist in searching a certain number of past situations in a meteorological archive that present similar properties for chosen predictors, according to an analogy criteria, in order to extract the observed values of the local weather variable of interest from another archive (predictand time series, see section \ref{sec:method_data}.\ref{sec:data}).
+Based on these analogue observations, the conditional empirical distribution considered as the probabilistic prediction for the target day (the day one wants to predict) is built.
 
-AMs consist in searching a certain number of past situations in a meteorological archive that are the most similar, according to an analogy criteria, and to extract the observed values of the local weather variable of interest from another archive (typically local or basin averaged time series) in order to build the conditional empirical distribution considered as the probabilistic prediction for the target day (the day one wants to predict).
-
-The present work takes place in the Perfect Prognosis framework \citep{Klein1963}, like the majority of AMs applications for precipitation prediction, and thus the meteorological archive from which the predictors are extracted is a reanalysis dataset.
-Oppositely, most applications for wind forecasting are based on a Model Output Statistics \citep[MOS, see][]{Glahn1972} context \citep[e.g.][]{DelleMonache2013, DelleMonache2011, Alessandrini2015, Junk2015, Junk2015c}.
-
-Predictors can be varied: for example the geopotential height at different pressure levels on different temporal windows (time of observation).
-The method is usually made of several levels of analogy, leading to successive subsampling on predictors of different nature (eg.
+Predictors, for precipitation prediction, can be varied: e.g.
+geopotential heights at different pressure levels and on different temporal windows (time of observation), humidity variables, etc \citep[see][for a more detailed list]{BenDaoud2016}.
+The method is often made of several levels of analogy, leading to successive subsampling on predictors of different nature (eg.
 atmospheric circulation, moisture variables, vertical motion, and air temperature).
 
-Two variants are often used for precipitation downscaling: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
+The basis of the AM implementation considered here is the following \citep[same approach as][]{Guilbaud1997, Bontron2005, Marty2012, Horton2012, Radanovics2013, Chardon2014, Dayon2015, BenDaoud2016}:
 
-The method based on the analogy of the synoptic circulation consists in the following steps: the similarity of the atmospheric circulation of a target date with every day of the archive is assessed by processing the S1 criteria \citep{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, on 2 different the geopotential heights (e.g.
-500 and 1000~hPa) and over a certain spatial window:
+\begin{enumerate}
+	\item Preselection: to cope with seasonal effects, $n_{0}$ candidate dates are extracted from the archive within a period of four months centered around the target date, for every year of the archive.
+Alternatively, the candidate dates can be selected based on similar air temperature \citep{BenDaoud2010}.
+
+	\item First level of analogy: $n_{1}$ dates are selected out of the preselected $n_{0}$, by means of an analogy ranking.
+The first level of analogy is often based on the atmospheric circulation when it comes to precipitation prediction.
+The similarity of the atmospheric circulation of the target date with the candidate situations is thus assessed on the geopotential height (at specific pressure levels, such as 500 and 1000~hPa, and over a certain spatial window, e.g.
+12~h and 24~h) by means of the S1 criteria \citep[Eq.
+(\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial gridded window.
+This criteria was found more relevant than Euclidean distances for pressure fields by different studies \citep{Wilson1980, Woodcock1980, Guilbaud1998, Bontron2004}.
 
@@
 
-To cope with seasonal effects, candidate dates are extracted within a period of 4 months centered around the target date, for every year of the archive.
-The $n_{1}$ (parameter to calibrate) dates with the lowest values of S1 are considered as analogs to the target day.
-Then, the daily observed precipitation amount of the $n_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day.
+	The $n_{1}$ dates with the lowest values of S1 are considered as analogs, in terms of the general circulation, to the target day. The analog number, $n_{1}$, is a parameter to calibrate.
 
-The other current variant adds a second level of analogy on moisture variables, more specifically on a moisture index made of the product of the precipitable water with the relative humidity at a certain pressure level \citep[e.g.
-850~hPa, see][]{Bontron2004}.
-When adding a second level of analogy, $n_{2}$ dates are subsampled in the $n_{1}$ analogs on the atmospheric circulation, to end up with a smaller number of analog situations.
+	\item Subsequent level(s) of analogy: beyond the similarity of airflows, one may look for similarities in other variables of interest, such as moisture variables.
+Therefore, the $n_{1}$ analogs are subsampled once again on the basis of another variable, in order to obtain a lower number of analog dates, $n_{2}$.
+When the predictor is not a pressure field, the analogy criteria usually represents absolute distances: Mean Absolute Error (MAE) and Root Mean Squared Error (RMSE), the latest being most often used.
 
-The CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000} has been often used to assess an AM performance \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}.
+	A second level of analogy based on thermodynamic variables was introduced by \citet{Vallee1986}, and \citet{Gibergans-Baguena2007}.
+After a systematic assessment, \citet{Bontron2004} pointed out that a moisture index made of the product of relative humidity at 850~hPa and total precipitable water gave the best performance.
+This index does not represent an actual physical quantity, but expresses the water content of the air column and its proximity to saturation.
+
+	This process can be repeated, by subsampling a decreasing number of analogs, $n_{i}$, according to various meteorological variables.
+
+	\item Probabilistic prediction of forecast: then, the (e.g.
+daily) observed precipitation amount of the $n_{i}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
+
+\end{enumerate}
+
+The parameters to be defined (manually or automatically), for every level of analogy, are the following:
+
+\begin{itemize}
+	\item The selection of meteorologic variables, the predictors, that must contain large scale information having direct or indirect dependency with the local weather and the target predictand.
+	\item The pressure level, or height, at which the predictor is considered.
+	\item The spatial window is the domain on which the predictor is considered. The ideal size of this area is the one that maximizes useful information and minimizes noise.
+	\item The temporal window is the hour in the day, or a set of different hours, at which the predictors are considered.
+	\item The analogy criterion, needed to compare the variables on the chosen spatial and temporal windows, is a distance measure used for ranking observed situations according to their degree of similarity with the target situation.
+	\item Eventual weights between the predictors \cite[e.g.][]{Horton2012a, Junk2015}
+	\item The ideal number of analog situations, which is the best compromise in order to take into account local variability and to maximize useful synoptic information \citep{Bontron2004}.
+\end{itemize}
+
+In order to calibrate the method, the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000} has been often used to assess the AM performance \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}.
 It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$.
@@
 
+In the present study, the choice of the meteorological variables considered as predictors is still set a priori.
+Then, for every level of analogy, GAs have to optimize jointly (i) the spatial windows (position and size; different between the pressure levels), (ii) the temporal windows (hours of observation of the predictors), (iii) the number of analog situations, and (iv) later on, the selection of the pressure levels (two, in this case).
+The first experiments are on a single level of analogy (on the geopotential height, see section \ref{sec:method_data}), and a second level (on moisture) is added further on in section \ref{sec:assessment}.\ref{sec:assessment:results}.\ref{sec:assessment:mutation}.
+
 \subsection{Comparison process}
@@
 A procedure by stages was adopted, analyzing in details and in a systematic way every variant of the implemented operators, in combination with multiple other options and parameters in order to take into account eventual co-dependencies.
-The goal here is not to focus on the performance score obtained through optimization, neither the values of the new optimized parameters (covered in another coming paper), but to explain how to use GAs to optimize AMs in an efficient way.
 
@@
 After a first overview of the results, GAs have quicky proved successful at optimizing the considered AM implementations.
-The performance score of the sequential approach has been quickly exceeded without adding any new parameter to the method (Fig.
+Figure \ref{fig:gas_evolution_good} shows the evolution of the score of the best individuals over generations for 10 optimizations processed for a given configuration of GAs (same operators options).
+7 out of 10 optimizations reach the supposed global optimum (dashed line at the top of the plot) after 40 to 55 generations, which is not the best performance we observed later on.
+The performance score of the sequential approach (bottom line) has been quickly exceeded without adding any new parameter to the method (Fig.
 \ref{fig:gas_evolution_good}).
-Even GAs configurations that will be considered later as inadequate (Fig.
-\ref{fig:gas_evolution_bad}) did significantly better that the sequential approach.
-The amplitude of the improvement is not the main outcome here.
-The most important point is that GAs proved successful at optimizing AMs automatically, globally, and objectively.
+The improvement is about 8.8\% in this case, which is substantial.
+
+Even GAs configurations that will be considered later as inadequate, because they did not reach the supposed global optimum (Fig.
+\ref{fig:gas_evolution_bad}), did significantly better that the sequential approach.
+GAs proved promising at optimizing AMs automatically, globally, and objectively.
 
@@
 Having identified the leading role of the mutation operator, the next sensitivity analysis focused on it.
-Each of the 10 different implementations (see section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Figure \ref{fig:operator_mutation_score}), bringing the number of variations up to 109.
+Each of the 10 different implementations (see section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Fig.
+\ref{fig:operator_mutation_score}), bringing the number of variations up to 109.
 Some optimizations without any mutation were also performed as a reference.
@@
 The optimizer could choose the 2 pressure levels of the atmospheric circulation analogy (method with a single level of analogy).
-The resulting CRPSS performance score (section \ref{sec:am}) is obviously superior to the one obtained by the sequential calibration (red line on Fig.
+The resulting CRPSS performance score (section \ref{sec:method_data}.\ref{sec:am}) is obviously superior to the one obtained by the sequential calibration (red line on Fig.
 \ref{fig:operator_mutation_score_atmlevel}).
@@
 \begin{figure}[t]
+	\centerline{\includegraphics[width=19pc,angle=0]{fig01.pdf}}
+	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland, and its discretization in 10 subregions:	(1) Swiss Chablais, (2) Trient Valley, (3) West Bernese Alps, (4) Lower Rhone Valley, (5) Left side valleys, (6) Southern ridges, (7) Upper Rhone Valley, (8) Southeast ridges, (9) East Bernese Alps, (10) Conches Valley.
+(source: Swisstopo)}
+	\label{fig:map}
+\end{figure}
+
+\begin{figure}[t]
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{fig01.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{fig02.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{fig02.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{fig03.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{fig03.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{fig04.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{fig04.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{fig05.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=39pc,angle=0]{fig05.pdf}\\
+		\noindent\includegraphics[width=39pc,angle=0]{fig06.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{fig06.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{fig07.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=33pc,angle=0]{fig07.pdf}\\
+		\noindent\includegraphics[width=33pc,angle=0]{fig08.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=33pc,angle=0]{fig08.pdf}\\
+		\noindent\includegraphics[width=33pc,angle=0]{fig09.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=33pc,angle=0]{fig09.pdf}\\
+		\noindent\includegraphics[width=33pc,angle=0]{fig10.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=33pc,angle=0]{fig10.pdf}\\
+		\noindent\includegraphics[width=33pc,angle=0]{fig11.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=11pc,angle=0]{fig11.pdf}\\
+		\noindent\includegraphics[width=11pc,angle=0]{fig12.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=11pc,angle=0]{fig12.pdf}\\
+		\noindent\includegraphics[width=11pc,angle=0]{fig13.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=11pc,angle=0]{fig13.pdf}\\
+		\noindent\includegraphics[width=11pc,angle=0]{fig14.pdf}\\
 	\end{center}

### 2016-09-02 Genetic algorithms - MWR/template.tex
GAs paper under correction.

@@
 
-We will begin by presenting the basics of the considered AM variants (section \ref{sec:method_data}) and the assessed GAs options (section \ref{sec:gas}).
+The document starts by presenting the case study area and the data (section \ref{sec:case_study_data}), the basics of the considered AM variants (section \ref{sec:am}), and the assessed GAs options (section \ref{sec:gas}).
 The comparative analyses of these options are presented in section \ref{sec:assessment}, which results in recommendations formulated in section \ref{sec:recommendations} and conclusions in section \ref{sec:conclusions}.
@@
 AMs are based on the principle that two similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}.
-Thus, they consist in searching a certain number of past situations in a meteorological archive that present similar properties for chosen predictors, according to an analogy criteria, in order to extract the observed values of the local weather variable of interest from another archive (predictand time series, see section \ref{sec:method_data}.\ref{sec:data}).
+Thus, they consist in searching a certain number of past situations in a meteorological archive that present similar properties for chosen predictors, according to an analogy criteria, in order to extract the observed values of the local weather variable of interest from another archive (predictand time series, see section \ref{sec:case_study_data}.\ref{sec:data}).
 Based on these analogue observations, the conditional empirical distribution considered as the probabilistic prediction for the target day (the day one wants to predict) is built.
@@
 Then, for every level of analogy, GAs have to optimize jointly (i) the spatial windows (position and size; different between the pressure levels), (ii) the temporal windows (hours of observation of the predictors), (iii) the number of analog situations, and (iv) later on, the selection of the pressure levels (two, in this case).
-The first experiments are on a single level of analogy (on the geopotential height, see section \ref{sec:method_data}), and a second level (on moisture) is added further on in section \ref{sec:assessment}.\ref{sec:assessment:results}.\ref{sec:assessment:mutation}.
+The first experiments are on a single level of analogy (on the geopotential height, see section \ref{sec:am}), and a second level (on moisture) is added further on in section \ref{sec:assessment}.\ref{sec:assessment:results}.\ref{sec:assessment:mutation}.
 
@@
 The optimizer could choose the 2 pressure levels of the atmospheric circulation analogy (method with a single level of analogy).
-The resulting CRPSS performance score (section \ref{sec:method_data}.\ref{sec:am}) is obviously superior to the one obtained by the sequential calibration (red line on Fig.
+The resulting CRPSS performance score (section \ref{sec:am}) is obviously superior to the one obtained by the sequential calibration (red line on Fig.
 \ref{fig:operator_mutation_score_atmlevel}).

### 2016-09-06 Genetic algorithms - MWR/template.tex
GAs paper under correction.

@@
 A common usage of AMs is for precipitation forecasting or downscaling \citep[eg.][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, Chardon2014, Dayon2015, Hamill2015b, BenDaoud2016}, but AMs, or equivalent, were also used to predict temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
-Applications for monthly time series in many countries also exist, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal predictions: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
 
-Even though the method is rather simple, it contains a certain number of parameters one needs to determine, such as the choice of the predictor variable, its pressure level and temporal window (hour of observation of the predictor) to consider, the spatial domain to use for the comparison, as well as the analogy criteria itself, and finally the number of analog situations to keep at each subsampling level.
+Even though the method is rather simple, it contains several parameters to optimize, such as the choice of the predictor variables, at certain pressure levels and times of the day, the spatial domains used for the comparison, as well as the analogy criteria (distance measure), and finally the number of analog situations to keep.
 
@@
 In addition, it can overcome the systematic manual assessments of all pressure levels and temporal windows.
-Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the pressure levels, and the consideration of differentiated spatial windows between the pressure levels.
-The relevance of Genetic Algorithms (GAs) is presented here, which does not exclude that other global optimization techniques could eventually be successful.
+Finally, it allows assessing new degrees of freedom, such as the use of differentiated spatial windows between the pressure levels.
+The relevance of Genetic Algorithms (GAs) is presented here, which does not exclude that other global optimization techniques could also work.
 If using GAs to optimize AMs is computationally intensive, once an AM is calibrated, its use in real-time operations it very fast and lightweight.
@@
 geopotential heights at different pressure levels and on different temporal windows (time of observation), humidity variables, etc \citep[see][for a more detailed list]{BenDaoud2016}.
-The method is often made of several levels of analogy, leading to successive subsampling on predictors of different nature (eg.
+The method often contains several levels of analogy, which are successive subsampling on predictors of different nature (eg.
 atmospheric circulation, moisture variables, vertical motion, and air temperature).
@@
 12~h and 24~h) by means of the S1 criteria \citep[Eq.
-(\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial gridded window.
+(\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
 This criteria was found more relevant than Euclidean distances for pressure fields by different studies \citep{Wilson1980, Woodcock1980, Guilbaud1998, Bontron2004}.
@@
 \end{equation}
-where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect prediction (which implies $CRPS_{p}~=~0$).
-A better prediction is characterized by an increase in CRPSS.
+where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect prediction (which implies $CRPS_{p}~=~0$). An increase in CRPSS means a better prediction.
 
@@
 Exploitation is characterized by a local search in an area of interest, and generally makes small movements.
-The latter is interesting to refine the results at the end of the optimization.
+The latter aims at finding small improvements at the end of the optimization.
 
@@
 
-GAs optimize a population of $N$ individuals (parameter sets).
-Each individual contains a chromosome (set of parameters of our AM in this case).
+GAs optimize a population of $N$ individuals.
+Each individual contains a chromosome, which is here a vector of the AM parameters.
 Genes are the individual parameters constituting the chromosome.
@@
 
-The mutation operator is a direct modification of some gene values.
+The mutation operator modifies some gene values.
 It adds diversity to the population and prevents a freeze of the evolution, or a genetic drift to a local optimum.
@@
 As the assessment (calculation of the objective function) of each member of the population of a generation is completely independent, it was performed in parallel on different processors of a computer.
-In order to perform optimizations for multiple time series, the use of a cluster is a necessity, which our code allows.
+In order to perform optimizations for multiple time series, the use of a cluster is a necessity.
 
@@
 For example, when a crossover or a mutation operation results in a parameter value standing out of the authorized bounds, it has to be brought back within the limits.
-Moreover, the parameters are of different nature: some are continuous, some are discrete, and finally, some are categorical, i.e.
-independent elements in an array, such as the selection of the meteorological variable.
+Moreover, the parameters are of different types: continuous, discrete, or categorical (e.g.
+the selection of the meteorological variable).
 New values resulting from the optimizer need to respect the type of data it represents.
@@
 
-One of our goals being to make recommendations of how to use GAs in view of optimizing AM variants, a systematic procedure was adopted.
+As one of our goals is to make recommendations on how to use GAs in order to optimize different AM variants, a systematic procedure was adopted.
 The results are summarized hereafter \citep[see][for the details]{Horton2012a}.
@@
 
-The performances were characterized by four indicators: (i) mean performance score: average of the final scores of the 10 optimizations, (ii) convergence: the number of optimizations that converged to a supposed global optimum, (iii) number of generations: characterization of the convergence speed, and (iv) number of evaluations of the objective function: characterization of the required calculation time.
+The performances were characterized by four indicators: (i) mean performance score: average of the final scores of the 10 optimizations, (ii) convergence: the number of optimizations that converged, (iii) number of generations: characterization of the convergence speed, and (iv) number of evaluations of the objective function: characterization of the required calculation time.
 
@@
 
-After a first overview of the results, GAs have quicky proved successful at optimizing the considered AM implementations.
+After a first quick assessment, GAs were found to be successful at optimizing the considered AM implementations.
 Figure \ref{fig:gas_evolution_good} shows the evolution of the score of the best individuals over generations for 10 optimizations processed for a given configuration of GAs (same operators options).
-7 out of 10 optimizations reach the supposed global optimum (dashed line at the top of the plot) after 40 to 55 generations, which is not the best performance we observed later on.
+7 out of 10 optimizations converged to the global optimum (dashed line at the top of the plot) after 40 to 55 generations, which is not the best performance we observed later on.
 The performance score of the sequential approach (bottom line) has been quickly exceeded without adding any new parameter to the method (Fig.
@@
 
-Even GAs configurations that will be considered later as inadequate, because they did not reach the supposed global optimum (Fig.
+Even GAs configurations that will be considered later as inadequate, because they did not reach the global optimum (Fig.
 \ref{fig:gas_evolution_bad}), did significantly better that the sequential approach.
@@
 Having identified the leading role of the mutation operator, the next sensitivity analysis focused on it.
-Each of the 10 different implementations (see section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:mutation}) was tested, with different parameters for those who require some (Fig.
+The 10 different implementations (see section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:mutation}) were tested, with different options (Fig.
 \ref{fig:operator_mutation_score}), bringing the number of variations up to 109.
@@
 The details of the analysis \citep[see][]{Horton2012a} show that the other reproduction operators seem of secondary importance.
-This observation is in line with the work of \citet{Back1996a}, who argues for the importance of mutation over reproduction, as well as other authors (see section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:mutation}).
+This observation is in line with the conclusions made by several other authors (see section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:mutation}).
 
@@
 
-Then, the same optimization was performed, but for another region, sensitive to other meteorological influences (Fig.
+% TODO: add region name and ref to map
+The same experiment was performed for another region, which is sensitive to other meteorological influences (Fig.
 \ref{fig:operator_mutation_score_rhoneamont}), in order to assess eventual dependencies of the operator with the predictand.
@@
 
-The optimization does not systematically converge to the global optimum (but still often nearby), which is why it is recommended to do several optimizations in parallel in order to compare the results, analyze the convergence, and keep the best.
+The optimization does not systematically converge to the global optimum (but often close to it), which is why it is recommended to do several optimizations in parallel in order to compare the results, analyze the convergence, and keep the best.
 It may be wise to consider the three mutation operators in parallel.
@@
 
-It is not excluded that another global optimization method or other operators of GAs may perform still better.
-However, the relevance of such an approach has now been proved as it results in parameters of AMs that are relevant and fully automatically, globally and objectively established.
+It is not excluded that another global optimization method or other operators of GAs may perform even better.
+Still, the relevance of global optimization techniques for AMs has now been proved as they result in parameters of AMs that are relevant and fully automatically, globally and objectively established.
 A global optimization is the only way to take into account all the dependencies between parameters and levels of analogy.

### 2016-09-06 Genetic algorithms - MWR/template.tex
Adding results of the confidence interval analysis.

@@
 With all assessed combinations of GAs options, 21,630 optimizations were performed on an Intel Xeon based HPC cluster with 96 cpu, running Linux RedHat.
-Such assessment is not possible on the whole archive length, and had to be performed on a reduced period (5 years).
+Such assessment is not possible on the whole archive length, and had to be performed on a reduced calibration period : 5 years, from 1998 to 2002, but looking for analog dates on a 48 years period (1961-2008).
 The total resources needed for this comparison amounts to 229,539 h/cpu (26.2 years).
@@
 
-\subsection{Success of the approach}
+\subsection{Convergence}
 
@@
 where $p_{mut}$ is the mutation rate (or mutation probability), $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a threshold chosen by the user to maintain a minimum search radius when the number of generations $G>G_{m,r}$.
+
+\subsection{Illustration of application}
+
+Ref: 95\%   ( 0.2921,  0.3494 )  
+Optimized: 95\%   ( 0.3521,  0.4011 )
 

### 2016-09-06 Genetic algorithms - MWR/ressources/analyses/confidence intervals/bootstrap.r

@@ -1,0 +1,35 @@
+# Based on http://stats.stackexchange.com/questions/112829/how-do-i-calculate-confidence-intervals-for-a-non-normal-distribution
+library(ncdf4)
+library(boot) 
+
+rm(list=ls())
+
+#fileName <- "scores_reference.nc"
+fileName <- "scores_optimized.nc"
+
+# Open file
+ncFile <- nc_open(fileName)
+
+scores <- ncvar_get(
+  ncFile,
+  varid = "forecast_scores"
+)
+
+scoresMean <- mean(scores)
+
+# Function to obtain the mean
+Bmean <- function(data, indices) {
+  d <- data[indices] # allows boot to select sample 
+  return(mean(d))
+} 
+
+# Bootstrapping with 1000 replications 
+results <- boot(data=scores, statistic=Bmean, R=10000)
+
+# View results
+results 
+plot(results)
+
+# Get 95% confidence interval 
+ci <- boot.ci(results, conf = c(0.90, 0.95), type="basic")
+print(ci)

### 2016-09-06 Genetic algorithms - MWR/ressources/analyses/confidence intervals/resources/bootstrap_ex3.r

@@ -1,0 +1,25 @@
+rm(list=ls())
+# Simulated data
+set.seed(123)
+data0 = rgamma(383,5,3)
+mean(data0) # Sample mean
+
+hist(data0) # Histogram of the data
+
+library(boot) 
+
+# function to obtain the mean
+Bmean <- function(data, indices) {
+  d <- data[indices] # allows boot to select sample 
+  return(mean(d))
+} 
+
+# bootstrapping with 1000 replications 
+results <- boot(data=data0, statistic=Bmean, R=1000)
+
+# view results
+results 
+plot(results)
+
+# get 95% confidence interval 
+boot.ci(results, type=c("norm", "basic", "perc", "bca"))

### 2016-09-06 Genetic algorithms - MWR/template.tex
Completion of the corrections.

@@
 %\documentclass[twocol]{ametsoc}
+
+% TODO: check all references to sections
+% TODO: reduce font size in plots
 
@@
 
-\title{Global Optimization of an Analog Method by Means of Genetic Algorithms}
+\title{Global Optimization of an analog method by Means of Genetic Algorithms}
 
@@
 The document starts by presenting the case study area and the data (section \ref{sec:case_study_data}), the basics of the considered AM variants (section \ref{sec:am}), and the assessed GAs options (section \ref{sec:gas}).
-The comparative analyses of these options are presented in section \ref{sec:assessment}, which results in recommendations formulated in section \ref{sec:recommendations} and conclusions in section \ref{sec:conclusions}.
+The comparative analyses of these options are presented in section \ref{sec:assessment}, which results in recommendations formulated in section \ref{sec:use} and conclusions in section \ref{sec:conclusions}.
 
@@
 
-Even GAs configurations that will be considered later as inadequate, because they did not reach the global optimum (Fig.
-\ref{fig:gas_evolution_bad}), did significantly better that the sequential approach.
-GAs proved promising at optimizing AMs automatically, globally, and objectively.
+Even GAs configurations that will be later rejected, because they did not converge (Fig.
+\ref{fig:gas_evolution_bad}), did still significantly better that the sequential approach.
+GAs showed a promising potential at optimizing AMs automatically, globally, and objectively.
 
@@
 
-% TODO: add region name and ref to map
-The same experiment was performed for another region, which is sensitive to other meteorological influences (Fig.
+The same experiment was performed for another region (Swiss Chablais, see Fig.
+\ref{fig:map}), which is sensitive to other meteorological influences (Fig.
 \ref{fig:operator_mutation_score_rhoneamont}), in order to assess eventual dependencies of the operator with the predictand.
@@
 
-After analysis of the most relevant mutation operators, the following advice can be raised (detailed options are provided in section \ref{sec:recommendations}):
+After analysis of the most relevant mutation operators, the following advice can be raised (detailed options are provided in section \ref{sec:use}.\ref{sec:recommendations}):
 
@@
 
-\section{Recommended configuration of GAs}
+\section{Use of GAs ot optimize AMs}
+\label{sec:use}
+
+\subsection{Recommended configuration of GAs}
 \label{sec:recommendations}
@@
 
-Ref: 95\%   ( 0.2921,  0.3494 )  
-Optimized: 95\%   ( 0.3521,  0.4011 )
+In order to illustrate the gain achievable by the optimization on the considered AM, the Southeast ridges region of the alpine Rhône catchment has been optimized for the whole calibration period (40 years in the 1961-2008 period, leaving out 8 years for validation), instead of the smaller 5-years period.
+
+The optimizer could select the geopotential height at 4 pressure levels, at any time of the day, on unconstrained spatial windows.
+Moreover, a weighting was introduced in the combination of the criteria processed on each pressure level \citep[such as][]{Horton2012a, Junk2015}.
+In this case, no new meteorological variable was added, and the method still contains a unique level of analogy.
+
+The performance (CRPSS) of the reference method calibrated by means of the sequential procedure amounts to 32.00\%, with a 0.95 confidence interval (assessed by bootstrapping on 10,000 samples) of (29.21\%; 34.94\%).
+The method optimized by means of GAs reaches a performance of 37.62\%, with a 0.95 confidence interval of (35.21\%; 40.11\%).
+The resulting gain is thus statistically significant.
+The results on all subregions and the physical meaning of the optimized parameters will be discussed in a coming paper.
 

### 2016-09-06 Genetic algorithms - MWR/template.tex
Correcting the abstract.

@@
 \abstract{Analog methods are based on a statistical relationship between synoptic atmospheric variables (predictors) and local weather (predictand), which we aim at predicting.
-This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic sequential procedure.
-This calibration approach has strong limitations: it is made of successive steps and thus cannot handle parameters dependencies, and it cannot automatically optimize some parameters, such as the selection of the pressure levels and the temporal windows (hour of observation of the predictor) on which the predictors are compared.
-In order to surpass these limitations, a global optimization technique was assessed, namely Genetic Algorithms, which can optimize jointly all parameters of the method and get closer to a global optimum by taking into account the parameters dependencies.
-Moreover, it can choose objectively parameters that were previously manually assessed, and can take into account new degrees of freedom that were unthinkable before.
+This relationship is expressed through many parameters that are often calibrated by means of a semi-automatic sequential procedure.
+This calibration approach is fast, but has strong limitations: it is made of successive steps and thus cannot handle parameters dependencies, and it cannot automatically optimize some parameters, such as the selection of the pressure levels and the temporal windows (hour(s) of the day) on which the predictors are compared.
+In order to surpass these limitations, a global optimization technique was assessed, namely Genetic Algorithms, which can optimize jointly all parameters of the method and can get closer to a global optimum, by taking into account the parameters dependencies.
+Moreover, it can choose objectively parameters that were previously manually assessed, and can take into account new degrees of freedom.
 These kind of optimization techniques need however to be tailored to the problem to solve.
-Multiple combinations of algorithms had to be assessed, and even new operators were developed, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of Genetic Algorithms to optimize sevral variants of analog methods.
+Multiple combinations of algorithms had to be assessed, and even new operators were developed, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of Genetic Algorithms to optimize several variants of analog methods.
 These recommendations are the main outcome of this work.

### 2016-09-07 Moving temporal window - HESS/corrections/5 - Reply to referee 1.tex
Finalizing the replies to referees for the HESS article.

\documentclass[]{letter}

\begin{document}

First of all, thank you for carefully reading the manuscript and for the constructive feedback.

Some referee comments are recalled in italics and followed by the authors’ responses. Others are addressed here, but without being recalled. The technical corrections or rephrasing are not discussed here, but will be performed.

\begin{itemize}
	\item Introduction: The structure will be changed and the description of the method moved into “Data and method”. Additional references will be added, and different variations will be presented, instead of relying on another papers to cover the literature review. The introduction will thus be rewritten.

	\item \textit{The issue discussed in the manuscript goes beyond this “fixed/moving” window issue. It more generally consider influence of the size of the data set (including the length of the archive) on the prediction skill. I am not aware of works that explored this issue but references to those, if any, and associated results have to be presented in the introduction.}

	The issue of the archive length will be better described, according to the relevant literature.

	\item \textit{The final objective of the work is to increase the prediction skill of the method. Other means are possible for this. They should be also mentioned.}

	We will mention other means to increase the prediction skill in the introduction.

	\item MTW strategy vs longer archive: We agree that the MTW might not be as performant as a 4 times longer archive, for the reasons provided. We indeed observed a gain in performance similar to doubling the archive. Your point on the transient climate is also interesting. We will add a discussion on these aspects in the paper.

	\item Number of analogs: we totally agree with the referee that when the choice of the predictors or the parameters are improved, leading to a better prediction, the optimal number of analog situations thus decreases. However, when the length of the archive increases, the optimal number of analogs increases too, for a better performance, up to a certain threshold. This has been demonstrated in the PhD of G. Bontron (2004, p. 227), and we can also see it in Fig.7 of Hamill et al. (2006). This increase in the number of analog situations results objectively in better performance skills in our case. The MTW enriches the pool of available situations, even though they are not fully independent. We will improve the clarity of this analysis. It is true though that the choice of predictors can be improved and auxiliary predictors are missing. The chosen methods are not the most recent ones, but are benchmarks as they have been used by several studies as a references. A note on that will be added.

	\item \textit{Explain both terms of the decomposition. Another well-known decomposition of the CRPSS is that of Herbasch. Please mention it also and clarify the advantage of that of Bontron. It is not clear at this stage.}

	We will remove the analysis of the sharpness and accuracy, as it brings unneeded complexity without being very instructive.

	\item \textit{Why using a non conventional notation for the CRPS score. Please use the classical one (CRPSS) or justify}

	It is the journal convention (“Multi-letter variables should be avoided. Instead use single-letter variables with subscript (e.g. ERMS instead of RMSE, or ET instead of ET).”) and we were asked to change the notation of the CRPS this way. We agree that is an unusual notation for this score… We are very open to change back these notations, if the editor says so.

	\item Resolution of the atmospheric reanalysis: it was shown by some studies that the resolution of the reanalysis dataset does not improve significantly the performance of the analogy of the atmospheric circulation. However, a full analysis of this aspect is out of the scope of this publication, and is a topic we are working on right now. Nevertheless, we can make the assumption that it does not alter the fact that we can find better analog situations at different hours of the day.

	\item Seasonal stratification: yes, we consider a seasonal stratification. It is mentioned in l. 36-39. This should be more clear after the change in the paper structure.

	\item \textit{You use the mean intensity of rainfall as a proxy of “dynamism of the atmospheric situation”. Another proxy could be the intensity of the variations within the geopotential fields (e.g. mean gradient value). Why did you not explore this? It would better fit to your “dynamism” concept.}

	Yes, that could be a possibility. However, even though the link between the dynamism and the precipitation amount is not direct, the interest in analyzing it this way is that it highlights improvements we are directly interested in: a better prediction of high precipitation amounts. This will be rephrased to focus more on the precipitation thresholds rather than the dynamism of the circulation pattern.

	\item Sharpness and accuracy: We will remove the analysis of the sharpness and accuracy, as mentioned previously.

	\item Figure 11: this figure is complex and not very instructive. It will be removed along with the sharpness and accuracy analysis.

	\item Tables: we agree that there are many tables. We will remove some unanalyzed data, such as the spatial windows in Tables 3, 4, 7, and 8 in order to group the remaining information. Tables 10 and 11 will also be removed along with the sharpness and accuracy analysis.

	\item The other unmentioned detailed issues will be fixed
\end{itemize}

\end{document}

### 2016-09-07 Moving temporal window - HESS/corrections/5 - Reply to referee 3.tex
Finalizing the replies to referees for the HESS article.

\documentclass[]{letter}

\begin{document}

We would like to thank referee 3 for his detailed and relevant review.

Some referee comments are recalled in italics and followed by the authors’ responses. Others are addressed here, but without being recalled. The technical corrections or rephrasing are not discussed here, but will be performed.

\begin{itemize}

	\item Introduction: as replied to referee \#1, the introduction will be rewritten, with an improved literature review and context description. The method description will be moved to the methods section.

	\item \textit{The title wrongly suggests that these conclusions are valid only in a forecasting context, while they actually have much more general implications.}

	We agree that the application of the MTW is not limited to forecasting. The title will be changed to the more generic term of “downscaling”.

	\item The structure will be improved, with a better separation of methods, results and discussion.

	\item \textit{Notations: Please use conventional abbreviations for commonly used quantities: Teweles-Wobus Score $\rightarrow$ TWS or S1, continuous ranked probability (skill) score $\rightarrow$ CRP(S)S, root mean square error $\rightarrow$ RMSE}

	It is the journal convention (“Multi-letter variables should be avoided. Instead use single-letter variables with subscript (e.g. ERMS instead of RMSE, or ET instead of ET).”) and we were asked to change the notation of these scores this way. We agree that these are unusual notations and are very open to change back these notations if the editor say so.

	\item The number of tables will be decreased, as explained to referee \#1: “We will remove some unanalyzed data, such as the spatial windows in Tables 3, 4, 7, and 8 in order to group the remaining information. Tables 10 and 11 will also be removed along with the sharpness and accuracy analysis, which is not very informative.”

	\item \textit{L15-17: Is it not rather because heavy precipitation events are rarer?}

	We cannot exclude this argument, and it might be a mix of both factors. We will add a note on that aspect.

	\item \textit{L24-25: I don’t understand}

	This reports to section 4, but might not be necessary in the abstract as it brings some confusion.

	\item \textit{L63: What are the parameters to calibrate? Please list them.}

	More details will be provided on the calibration procedure.

	\item \textit{L70: Please either provide a peer-reviewed reference for this decomposition or detail it here.}

	We will drop the analysis of the CRPS decomposition, as it brings complexity without being very informative.

	\item \textit{L76: Please detail the computation of the climatological distribution.}

	A description will be added.

	\item \textit{L93-94: I don’t understand.}

	This will be dropped as it relies on partial analysis.

	\item \textit{L113-114: Please justify the use of such an outdated global reanalysis (I understand this is partly for having a long time coverage). And add also the potential of using more recent and products with higher quality to the discussion.}

	See answer to referee \#1. These points will be addressed in the discussion.

	\item \textit{L168-174: This analysis is done for different classes of precipitation values. Whether this relates to the intensity of circulation dynamics is another issue.}

	We will reformulate this section.

	\item \textit{L192-193: Figure 8 is not necessary. Please remove of put it in a supplementary material.}

	The figure will be removed.

	\item \textit{L219-220, “No relationship [: : :] criteria”: I don’t understand.}

	This will be removed.

	\item \textit{L246-250: Is it shown somewhere in the manuscript?}

	No it is not shown, as the figure globally is very similar to Fig. 10.

	\item \textit{L350-354: Given recent studies on RCM biases, I have serious doubts that RCM precipitation is reliable enough for it to be use as observed series in this context.}

	We agree with the referee and will change this sentence.

	\item Figure 11: We will drop the analysis of the CRPS decomposition, as it brings complexity without being very informative.

	\item Table 13: The choice for preselecting these 4 points should be somehow justified.
	You are right. These are simply the points surrounding the catchment. It will be explained.

	\item The other unmentioned issues will be fixed

\end{itemize}

\end{document}

### 2016-09-12 Genetic algorithms - MWR/template.tex
Reading and improving the paper.

@@
 
-\title{Global Optimization of an analog method by Means of Genetic Algorithms}
+\title{Global Optimization of an Analog Method by Means of Genetic Algorithms}
 
@@
 
-\abstract{Analog methods are based on a statistical relationship between synoptic atmospheric variables (predictors) and local weather (predictand), which we aim at predicting.
-This relationship is expressed through many parameters that are often calibrated by means of a semi-automatic sequential procedure.
-This calibration approach is fast, but has strong limitations: it is made of successive steps and thus cannot handle parameters dependencies, and it cannot automatically optimize some parameters, such as the selection of the pressure levels and the temporal windows (hour(s) of the day) on which the predictors are compared.
+\abstract{Analog methods are based on a statistical relationship between synoptic meteorological variables (predictors) and local weather (predictand, which are to be predicted), which is defined by several parameters that are often calibrated by means of a semi-automatic sequential procedure.
+This calibration approach is fast, but has strong limitations: it is made of successive steps and thus cannot handle all parameters dependencies, and it cannot automatically optimize some parameters, such as the selection of the pressure levels and the temporal windows (hour(s) of the day) on which the predictors are compared.
 In order to surpass these limitations, a global optimization technique was assessed, namely Genetic Algorithms, which can optimize jointly all parameters of the method and can get closer to a global optimum, by taking into account the parameters dependencies.
-Moreover, it can choose objectively parameters that were previously manually assessed, and can take into account new degrees of freedom.
-These kind of optimization techniques need however to be tailored to the problem to solve.
-Multiple combinations of algorithms had to be assessed, and even new operators were developed, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of Genetic Algorithms to optimize several variants of analog methods.
-These recommendations are the main outcome of this work.
-It opens new perspective for the improvement of analog methods, and their application to new regions or to new predictands.
+Moreover, it can objectively calibrate parameters that were previously manually assessed, and can take into account new degrees of freedom.
+Genetic Algorithms need however to be tailored to the addressed problem.
+Multiple combinations of algorithms were assessed, and new ones were developed (e.g.
+the \textit{chromosome of adaptive search radius} which was found to be very robust), in order to make recommendations for the use of Genetic Algorithms to optimize several variants of analog methods.
+A global optimization approach opens new perspective for the improvement of analog methods, and their application to new regions or to new predictands.
 }
@@
 
-Analog methods (AMs) relies on the hypothesis that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Lorenz1956, Lorenz1969, Duband1970, Bontron2005}.
-The principle consists in sampling a certain number of past situations based on different atmospheric variables (predictors) in order to build a probabilistic prediction for a local weather variable of interest (predictand).
-A common usage of AMs is for precipitation forecasting or downscaling \citep[eg.][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, Chardon2014, Dayon2015, Hamill2015b, BenDaoud2016}, but AMs, or equivalent, were also used to predict temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
-
-Even though the method is rather simple, it contains several parameters to optimize, such as the choice of the predictor variables, at certain pressure levels and times of the day, the spatial domains used for the comparison, as well as the analogy criteria (distance measure), and finally the number of analog situations to keep.
+Analog methods (AMs) rely on the hypothesis that similar situations in terms of the atmospheric circulation are likely to lead to similar local weather \citep{Lorenz1956, Lorenz1969, Duband1970, Bontron2005}.
+They consist in sampling a certain number of past situations based on different synoptic-scale meteorological variables (predictors) in order to build a probabilistic prediction for a local weather variable of interest (predictand).
+A common usage of AMs is for operational precipitation forecasting \citep[eg.][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Hamill2015b, BenDaoud2016}, or more recently for precipitation downscaling in a climate perspective \citep[eg.][]{Radanovics2013, Chardon2014, Dayon2015}.
+However, AMs or equivalent were also used to predict temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+
+Even though the method is rather simple, it contains several parameters to optimize, such as the choice of the predictor variables, the pressure levels and temporal windows (hour(s) of the day) on which the predictors are compared, the spatial domains used for the comparison, as well as the analogy criteria (distance measure), and finally, the number of analog situations to retain.
 
@@
 Even the selection of the pressure levels and the temporal windows should be reconsidered, if not the predictor variable itself.
+Thus, before being applied in a forecasting or downscaling context, AMs must be calibrated for the given region, which is done here in the Perfect Prognosis framework \citep{Klein1963}, like the majority of AMs calibration procedures for precipitation prediction cited previously \cite[with the exception of][]{Hamill2006,Hamill2015b}.
 
 A common approach to optimize the method is by means of a semi-automatic sequential calibration procedure, developed by \citet{Bontron2004}, also described in \citet{BenDaoud2016}, and extended by \citet{Radanovics2013}.
-It determines some parameters of the method, for each consecutive analogy level (eg.
-the atmospheric circulation or moisture index), sequentially.
-It starts by a manual selection of the meteorologic variable (e.g.
-geopotential height, relative humidity, etc.), the pressure level (e.g.
-500 hPa), the temporal window, and the initial analog number.
-Then, the spatial window on which the predictors are considered is optimized by an iterative growth of the domain, and the number of analogues is reassessed.
+It determines some parameters of the method, sequentially for each consecutive analogy level (eg.
+on the atmospheric circulation or on a moisture index).
+It starts by a manual selection of the meteorological variables (e.g.
+geopotential height, relative humidity, etc.), the pressure levels, the temporal windows, and the initial analog numbers.
+Then, the spatial window on which the predictors are compared is optimized by an iterative growth of the domain, and the number of analogs is finally reassessed.
 A successive level of analogy can then be added and its spatial window optimized.
-Parameters of the preceding levels of analogy are not reassessed, except for the number of analogue situations to keep.
-
-The sequential calibration procedure thus allows optimizing a limited number of parameters, but the selection of predictor variables, pressure levels and temporal windows had still to be made manually before optimizing the spatial windows and the number of analogs.
+Parameters of the preceding levels of analogy are not reassessed, except for the number of analog situations to keep.
+
+The sequential calibration procedure thus allows optimizing a limited number of parameters (spatial windows and analog numbers), but the selection of predictor variables, pressure levels and temporal windows have still to be made manually.
 Testing multiple combinations of these is very combinatorial and becomes quickly cumbersome, especially when considering multiple predictors within the same level of analogy.
-Thus, optimizing the method with the sequential technique is laborious, as many combinations of predictors (variables, pressure levels, temporal windows) have to be assessed.
+Thus, optimizing AMs by means of the sequential technique is laborious when little knowledge on the predictor-predictand relationship or the leading meteorological influences is available.
+Indeed, many combinations of parameters (predictor variables, pressure levels, temporal windows) have to be assessed.
 Moreover, proceeding to the optimization sequentially ignores potential dependencies between the parameters of the method, may they be within a single level of analogy or between them, which could lead to another configuration if the parameters were calibrated together.
-Simultaneous calibration of all parameters has never been undertaken so far.
-Thus, due to the sequential approach, the risk of ending in a local optimum is high and can not be avoided.
-Indeed, during an AM calibration it has been found that the resulting parameters may vary with initial choices (such as the number of analogs).
+Thus, the risk of ending in a local optimum is high and can not be avoided.
 
@@
 And later in his work: ''\textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution}''.
-\citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of an AM and concludes that one needs to be an expert to have a sense of their respective influence, sensitivity and nonlinear interactions.
+\citet{Bliefernicht2010} has also faced the combinatorial issue of AMs parameters and concluded that one needs to be an expert to have a sense of their respective influence, sensitivity and nonlinear interactions.
 \citet{BenDaoud2010}, when calibrating an AM, also stated that ''\textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously}''.
-
-Another optimization strategy has been proposed by \citet{Junk2015}, that allows for an automatic optimization of weights applied to the different predictors when processing the analogy criteria (distance function).
+Simultaneous calibration of all parameters has never been undertaken so far.
+
+Another optimization strategy has been proposed by \citet{Junk2015}, and allows for an automatic calibration of weights applied to the different predictors when processing the analogy criteria (distance function).
 Their strategy consists in a brute-force assessment of all possible combinations.
-This approach is possible in their analog method, as predictors are considered at a unique point (interpolated to the location of interest), at fixed hours, and at preselected pressure levels, leaving only the weights to optimize.
-In the presently used analogue method (described in section \ref{sec:am}), the number of parameters to optimize makes it impossible to proceed to a brute-force strategy.
+This approach is possible in their implementation, as predictors are considered at a unique point (interpolated to the location of interest), at fixed hours, and at preselected pressure levels, leaving only the weights to be optimized.
+In the presently used AM (described in section \ref{sec:am}), the number of parameters to optimize makes it impossible to proceed to a brute-force strategy.
 
@@
 The parameter space of AMs can be very complex and is inappropriate for a linear optimization technique.
-The conclusion was that global optimization techniques were necessary in order to calibrate most AM variants, as it is the only way to optimize all parameters of all analogy levels simultaneously.
-In addition, it can overcome the systematic manual assessments of all pressure levels and temporal windows.
-Finally, it allows assessing new degrees of freedom, such as the use of differentiated spatial windows between the pressure levels.
+Thus, global optimization techniques are likely to be necessary in order to calibrate most AM variants, as they can optimize all parameters of all analogy levels simultaneously.
+In addition, they can overcome the systematic manual assessments of all pressure levels and temporal windows.
+Finally, they allow testing new degrees of freedom in AMs.
 The relevance of Genetic Algorithms (GAs) is presented here, which does not exclude that other global optimization techniques could also work.
-If using GAs to optimize AMs is computationally intensive, once an AM is calibrated, its use in real-time operations it very fast and lightweight.
-
-This article is not about discussing the details of the results of an optimization with GAs, but describing how GAs are to be used in order to successfully optimize some AM variants.
-Indeed, GAs variants are numerous and always need to be tailored to the problem addressed.
+If using GAs to optimize AMs is computationally intensive, once an AM is calibrated, its use in real-time operations or climate downscaling is very fast and lightweight.
+
+This paper is not about discussing the details of the results of an optimization with GAs, but describing how GAs are to be used in order to successfully optimize several AMs.
+Indeed, GAs variants are numerous and always need to be tailored to the addressed problem.
 This requires intensive and systematic comparisons of operators and options in order to identify the key factors leading the optimization and the respective sensitivity of the options.
-Such analyses are presented here by application to the upper Rh\^{o}ne catchment in Switzerland, and will result in recommendations for the use of GAs when applied to several AM implementations.
-The demonstration of the benefit brought by such an approach on a specific case study is the topic of another coming paper.
-
-The document starts by presenting the case study area and the data (section \ref{sec:case_study_data}), the basics of the considered AM variants (section \ref{sec:am}), and the assessed GAs options (section \ref{sec:gas}).
-The comparative analyses of these options are presented in section \ref{sec:assessment}, which results in recommendations formulated in section \ref{sec:use} and conclusions in section \ref{sec:conclusions}.
+Such analyzes are presented here and will result in recommendations for the use of GAs to optimize several AM implementations.
+The in-depth analysis of the benefit brought by such an approach on a specific case study is the topic of another coming paper.
+
+The document starts by presenting the case study area and the data (section \ref{sec:case_study_data}), the considered AM variants (section \ref{sec:am}), and the assessed GAs options (section \ref{sec:gas}).
+The comparative analyzes of these options are presented in section \ref{sec:assessment}, which results in recommendations formulated in section \ref{sec:use} and conclusions in section \ref{sec:conclusions}.
 
@@
 The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$.
-This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at allowing real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
-Based on different climatological analyses, the gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}).
-
-The overall aim of the project is to implement a real-time precipitation and discharge forecasting in the catchment.
-An AM is used to provide real-time probabilistic forecasts of precipitation, based on NWP outputs.
-However, before being applied in the forecasting context, the AM must be calibrated for the given region, which is done here in the Perfect Prognosis framework \citep{Klein1963}, like the majority of AMs calibration procedures for precipitation prediction cited previously \cite[with the exception of][]{Hamill2006,Hamill2015b}.
+Based on different climatological analyzes \cite[see][for the details]{Horton2012a}, the gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}).
+
+The study area is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at providing real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
+AMs are used to provide real-time probabilistic precipitation forecasts, based on NWP outputs.
 
@@
 
-The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series one wants to predict.
-
-Working in the Perfect Prognosis framework, the meteorological archive from which the predictors are extracted is a reanalysis dataset.
-Oppositely, other applications of AMs for wind forecasting are based on a Model Output Statistics \citep[MOS, see][]{Glahn1972} context, and thus use forecast archives or reforecast products \citep[e.g.][]{DelleMonache2013, DelleMonache2011, Alessandrini2015, Junk2015, Junk2015c}.
+AMs rely on two types of data: predictors, that are meteorological variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series one wants to predict.
+
+When working in the Perfect Prognosis framework \citep{Klein1963}, the meteorological archive from which the predictors are extracted is usually a reanalysis dataset.
+Oppositely, other applications of AMs for wind forecasting are based on a Model Output Statistics context \citep[MOS, see][]{Glahn1972}, and thus use forecast archives or reforecast products \citep[e.g.][]{DelleMonache2013, DelleMonache2011, Alessandrini2015, Junk2015, Junk2015c}.
 
@@
 to 6~a.m.
-the next day) measured at the MeteoSwiss' stations network in the alpine upper Rh\^{o}ne catchment in Switzerland.
+the next day) measured at the MeteoSwiss' stations network in the catchment of interest.
 The time series from every available gauging station were averaged over subregions of approximately 500~km$^{2}$ \citep[see][for the details]{Horton2012a} in order to smooth local effects \citep{Obled2002, Marty2012}.
+The time series need to be split into a calibration and an independent validation periods.
 
@@
 Thus, they consist in searching a certain number of past situations in a meteorological archive that present similar properties for chosen predictors, according to an analogy criteria, in order to extract the observed values of the local weather variable of interest from another archive (predictand time series, see section \ref{sec:case_study_data}.\ref{sec:data}).
-Based on these analogue observations, the conditional empirical distribution considered as the probabilistic prediction for the target day (the day one wants to predict) is built.
-
-Predictors, for precipitation prediction, can be varied: e.g.
-geopotential heights at different pressure levels and on different temporal windows (time of observation), humidity variables, etc \citep[see][for a more detailed list]{BenDaoud2016}.
+Based on these analog observations, the conditional empirical distribution considered as the probabilistic prediction for the target day (the day one wants to predict) is built.
+
+Predictors for precipitation prediction, can be varied: e.g.
+geopotential height at different pressure levels and temporal windows, humidity variables, etc \citep[see][for a more detailed list of predictors]{BenDaoud2016}.
 The method often contains several levels of analogy, which are successive subsampling on predictors of different nature (eg.
@@
 	\item Preselection: to cope with seasonal effects, $n_{0}$ candidate dates are extracted from the archive within a period of four months centered around the target date, for every year of the archive.
-Alternatively, the candidate dates can be selected based on similar air temperature \citep{BenDaoud2010}.
+Alternatively, the candidate dates can be selected based on similar air temperature \citep[see][]{BenDaoud2016}.
 
 	\item First level of analogy: $n_{1}$ dates are selected out of the preselected $n_{0}$, by means of an analogy ranking.
-The first level of analogy is often based on the atmospheric circulation when it comes to precipitation prediction.
-The similarity of the atmospheric circulation of the target date with the candidate situations is thus assessed on the geopotential height (at specific pressure levels, such as 500 and 1000~hPa, and over a certain spatial window, e.g.
-12~h and 24~h) by means of the S1 criteria \citep[Eq.
-(\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
-This criteria was found more relevant than Euclidean distances for pressure fields by different studies \citep{Wilson1980, Woodcock1980, Guilbaud1998, Bontron2004}.
+The first level of analogy for precipitation prediction is often based on the atmospheric circulation.
+The similarity of the atmospheric circulation of the target date with the candidate situations is assessed on the geopotential height (at specific pressure levels, such as 500 and 1000~hPa, and over a certain spatial window, e.g.
+12~h and 24~h) by means of the S1 criteria \citep[eq.
+(\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a defined spatial window.
+The S1 criteria was found more relevant than Euclidean distances for pressure fields by different studies \citep{Wilson1980, Woodcock1980, Guilbaud1998, Bontron2004}.
 
@@
 
-	The $n_{1}$ dates with the lowest values of S1 are considered as analogs, in terms of the general circulation, to the target day. The analog number, $n_{1}$, is a parameter to calibrate.
-
-	\item Subsequent level(s) of analogy: beyond the similarity of airflows, one may look for similarities in other variables of interest, such as moisture variables.
+	The $n_{1}$ dates with the lowest values of S1 are considered as analog situations, in terms of the atmospheric circulation, to the target day. The analog number $n_{1}$ is a parameter to calibrate.
+
+	\item Subsequent level(s) of analogy: beyond the similarity of airflows, one may look for analogies in other variables of interest, such as moisture variables.
 Therefore, the $n_{1}$ analogs are subsampled once again on the basis of another variable, in order to obtain a lower number of analog dates, $n_{2}$.
@@
 
-	This process can be repeated, by subsampling a decreasing number of analogs, $n_{i}$, according to various meteorological variables.
-
-	\item Probabilistic prediction of forecast: then, the (e.g.
-daily) observed precipitation amount of the $n_{i}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
+	This process can be repeated, by subsampling a decreasing number of analog dates, $n_{i}$, according to various meteorological variables.
+
+	\item Probabilistic prediction: then, the daily observed precipitation amounts of the $n_{i}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
 
@@
 \begin{itemize}
-	\item The selection of meteorologic variables, the predictors, that must contain large scale information having direct or indirect dependency with the local weather and the target predictand.
-	\item The pressure level, or height, at which the predictor is considered.
-	\item The spatial window is the domain on which the predictor is considered. The ideal size of this area is the one that maximizes useful information and minimizes noise.
-	\item The temporal window is the hour in the day, or a set of different hours, at which the predictors are considered.
+	\item The selection of meteorological variables (predictors) that contain synoptic scale information having direct or indirect dependency with the target predictand.
+	\item The pressure level, or height, at which the predictor is selected.
+	\item The temporal window is the hour(s) of the day at which the predictors are considered.
+	\item The spatial window is the domain on which predictors are compared. The ideal size of this area is the one that maximizes useful information and minimizes noise.
 	\item The analogy criterion, needed to compare the variables on the chosen spatial and temporal windows, is a distance measure used for ranking observed situations according to their degree of similarity with the target situation.
@@
 
-In order to calibrate the method, the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000} has been often used to assess the AM performance \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}.
+In order to calibrate the method, the Continuous Ranked Probability Score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} has often been used to assess AMs performances \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}.
 It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$.
@@
 \end{equation}
-where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value 1 otherwise.
-The mean CRPS is averaged on the calibration, respectively the validation periods, on all days.
+where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value 1 otherwise. The mean CRPS is averaged on the calibration, respectively the validation periods.
 
@@
 \label{eq:CRPSS}
-CRPSS = \frac{CRPS-CRPS_{r}}{CRPS_{p}-CRPS_{r}} = 1-\frac{CRPS}{CRPS_{r}}
+CRPSS = 1-\frac{CRPS}{CRPS_{r}}
 \end{equation}
-where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect prediction (which implies $CRPS_{p}~=~0$). An increase in CRPSS means a better prediction.
+where $CRPS_{r}$ is the score value for the reference. An increase in CRPSS means a better prediction.
 

### 2016-09-12 Genetic algorithms - MWR/template.tex
Reading and improving the paper.

@@
 Genetic Algorithms \citep[GAs,][]{Holland1992b, Goldberg1989} are part of the family of Evolutionary Algorithms \citep{Back1993b, Schwefel1993}, inspired by some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
-Unlike a linear or local optimization, GAs seek the global optimum on complex surfaces, theoretically without restriction, but with no guarantee to reach it \citep{Haupt2004}.
+Unlike linear or local optimizations, GAs seek the global optimum on complex surfaces, theoretically without restriction, but with no guarantee to reach it \citep{Haupt2004}.
 The objective function to optimize (often named fitness function in this context) can be of different types \citep{Joines1996a}, but GAs must be adapted in order to perform optimally.
@@
 choice of the meteorological variable), discrete (e.g.
-number of analogs to select), or continuous.
+number of analog dates to select), or continuous.
 
 There are numerous implementation variants of GAs, often optimal for a given problem \citep{Hart1991a, Schraudolph1992a}.
-The differences are in the operators implementation, through significantly different algorithms, which has an important effect on the results \citep{Gaffney2010a}.
+The differences are found in the implementation of the operators, through significantly different algorithms, which has an important effect on the results \citep{Gaffney2010a}.
 Here, operators are defined as the mechanisms that modify the values of the genes to try bringing individuals (or chromosomes) closer to an optimum of the fitness function.
@@
 The fitness (performance score or objective function) of every individual is assessed.
-(2) A natural selection is applied, after which only the best individuals remain, which constitutes the intermediate generation (IG), from which (3) couples are formed according to given rules.
+(2) A natural selection is applied, after which only the best individuals remain, constituting the intermediate generation (IG), from which (3) couples are formed according to given rules.
 Then, (4) these couples proceed to reproduction, or chromosome crossover, to mix their genes according to the selected operator version.
@@
 The size $N$ of the population is often a compromise between the computation time and the quality of the solution.
-$N$ must allow sufficient sampling of the solutions field \citep{Beasley1996a}, and should thus vary as a function of chromosome size (ie the number of genes or parameters to be optimized).
+$N$ must allow sufficient sampling of the solutions field \citep{Beasley1996a}, and should thus vary as a function of the chromosome size (ie the number of genes or parameters to be optimized).
 
@@
 
-	\item Two-point crossover: similar to the single-point crossover, but with two intersections defining the segments to be exchanged, it is considered more efficient than the previous \citep{Beasley1993a}.
+	\item Two-point crossover: similar to the single-point crossover, but with two intersections defining the segments to be exchanged.
+It is considered more efficient than the previous \citep{Beasley1993a}.
 
@@
 
-	\item Binary-like crossover \citep{Haupt2004}: in order to reproduce the behaviour present in the canonical crossover algorithm, which is applied to a binary representation of the genes \citep{Goldberg1989, Goldberg1990a, Herrera1998a}, \citet{Haupt2004} propose an operator that combines standard crossover with an interpolation approach.
+	\item Binary-like crossover \citep{Haupt2004}: in order to reproduce the behaviour present in the canonical crossover algorithm, which is applied to a binary representation of the genes \citep{Goldberg1989, Goldberg1990a, Herrera1998a}, \citet{Haupt2004} proposed an operator that combines the standard crossover operation with an interpolation approach.
 The genes located after a crossover point are exchanged, but the gene located at the intersection is modified according to:
@@
 The combination of strong genes by the operator of chromosomes crossover is theoretically the most important operating mechanism in the conventional GAs \citep{Holland1992b,Back1993b}.
-However, many studies identify the mutation process as main operator, and crossovers as secondary \citep[see][]{Back1992a, Back1996a, Back1996b, Smith1997a, Deb1999, Costa2005a, Costa2007a}.
+However, many studies identified the mutation process as the main operator, and crossovers as secondary \citep[see][]{Back1992a, Back1996a, Back1996b, Smith1997a, Deb1999, Costa2005a, Costa2007a}.
 
@@
 
-The evaluated and developed mutation operators are listed hereafter (equations are only provided for the operator versions that were found relevant; the user can refer to the corresponding literature for the details of the other options).
-They apply to genes made of continuous or discrete variables, but not categorical (eg meteorological variable or analogy criterion).
+The evaluated and developed mutation operators are listed hereafter (equations are only provided for the operator versions that were found relevant; the reader can refer to the corresponding literature for the details of the other options).
+They apply to genes made of continuous or discrete variables, but not categorical (e.g.
+choice of the meteorological variable or analogy criterion).
 In the latter case, the random choice of a new value is always based on a uniform distribution, without notion of distance in the parameters space.
@@
 
-	where $a_{n}$ is the is the lower bound of the $n$-th gene, $b_{n}$ its upper bound, $G$ the present generation, and $G_{m}$ the maximum number of generations.
+	where $a_{n}$ is the lower bound of the $n$-th gene, $b_{n}$ its upper bound, $G$ the present generation, and $G_{m}$ the maximum number of generations.
 
@@
 
-	where $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a threshold chosen by the user to maintain a minimum search radius when $G>G_{m,r}$.
+	where $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a chosen threshold to maintain a minimum search radius when $G>G_{m,r}$.
 During the first generations, the exploration extent covers the entire parameters space.
@@
 	\item Individual adaptive mutation rate \citep{Back1992a}: based on the ideas of Evolution Strategies \citep[see][]{Rechenberg1973, Schwefel1981}, \citet{Back1992a} introduced a concept of self-adaptive GAs.
-The idea is to distribute control parameters within individuals themselves, which partially decentralize control of the evolution.
+The idea is to distribute the control parameters within the individuals themselves, which partially decentralizes the control of the evolution.
 It allows reducing the manual tuning of GAs and introduces a notion of self-management.
@@
 
-	\item Individual adaptive search radius (new): based on the ideas of the non-uniform mutation, a search radius was introduced in the approach of individual adaptive mutation rates.
-This search radius $r_{a}$, bounded between 0 and 1 (relatively to the parameters ranges), is also adaptive and behaves similarly to the adaptive mutation rates.
+	\item Individual adaptive search radius: based on the ideas of the non-uniform mutation, we introduced a search radius in the approach of individual adaptive mutation rates.
+This search radius $r_{a}$, bounded between 0 and 1 (relatively to the parameter ranges), is also adaptive and behaves similarly to the adaptive mutation rates.
 In order to separate its evolution from the one of the mutation rate, its own value is also considered as a self-mutation rate to eventually mutate before being used as a normalized search radius.
@@
 	\end{equation}
-	where $r_{1}$ and $r_{2}$ are randomly selected, in the same way as for the non-uniform mutation. No external parameter is therefore necessary.
+	where $r_{1}$ and $r_{2}$ are randomly selected, such as in the non-uniform mutation. No external parameter is therefore necessary.
 
@@
 The operations of mutation and self-mutation are similar to the case of the individual adaptive mutation rate, but in a distributed way, within the chromosome.
-Moreover, the same crossover operations are applied to this new chromosome, as those applied to the first chromosome, and this for the same crossing points.
+Moreover, the same crossover operations are applied to this new chromosome, as those applied to the main chromosome, and this for the same crossing points.
 Thus, during an exchange of genes, children also inherit the mutation rates specific for each of these genes.
 
-	\item Chromosome of adaptive search radius (new): this operator combines the operations of the chromosome of adaptive mutation rate to the adaptive search radius approach.
+	\item Chromosome of adaptive search radius: in this operator, we combined the operations of the chromosome of adaptive mutation rate to the adaptive search radius approach.
 Similarly, an individual has 3 chromosomes: the first containing the values to be optimized, the second the distributed mutation rate, and the last one, the distributed search radius.
-Again, no external parameters are required.
-
-	\item Multi-scale mutation (new): finally, another approach was developed that is also based on the search radius concept.
+Again, no external parameter is required.
+
+	\item Multi-scale mutation: finally, we developed another approach that is also based on the search radius concept.
 However, the latter is not decreasing with time.
 Methods based on a reduction of the mutation rate or radius simulate a transition from the exploration phase to the exploitation one.
-The idea was to test an approach that combines both exploration and exploitation during the whole optimization.
+The idea here was to test an approach that combines both exploration and exploitation during the whole optimization.
 Thus, the search radius $r_{a}$ of Eq.
-\ref{equation_mutation_rayon_adaptatif} was considered as a random value for each individual, but restricted to 4 equiprobable values: 1, 0.5, 0.1, 0.02, which range from full exploration to fine exploitation.
+\ref{equation_mutation_rayon_adaptatif} was considered as a random value for each individual, but restricted to 4 equiprobable values: 1, 0.5, 0.1, 0.02, so a range from full exploration to fine exploitation.
 The only external parameter is the mutation rate which is fixed.
@@
 
-A process of elitism was considered after both the natural selection and mutations.
+A process of elitism was introduced after both the natural selection and mutations.
 This ensures the survival of the best individual so that a better solution is never lost.
@@
 The optimization is here stopped if the best individual does not change for $x$ generations.
-This value should not be too low to allow the algorithm to escape from a local optima.
-In addition, the rate of improvement decreases with the progression of the optimization.
+This value should not be too low to allow the algorithm to escape from a local optima, and because the rate of improvement decreases with the progression of the optimization.
 It is thus common that the best individual does not evolve over several generations when getting closer to the global solution.
@@
 GAs are very computationally intensive because they require many evaluations of the objective function.
-These assessments are very long in this application, as they require calculating and assessing a prediction for every day of the calibration period, thus over several decades.
-In order to reduce the computation time, recalculating the performance score of an individual who has previously been evaluated and that has not changed was avoided.
+These assessments are relatively long (couple of seconds) in this application, as they require calculating and assessing a prediction for every day of the calibration period, thus over several decades.
+In order to reduce the computation time, the performance score of an individual who has previously been evaluated, and that has not changed, was preserved.
 Thus, the score of each individual living in the selection was kept until it mutates.
 
-As the assessment (calculation of the objective function) of each member of the population of a generation is completely independent, it was performed in parallel on different processors of a computer.
+As the calculation of the objective function of each member of the population of a generation is completely independent, they were performed in parallel on different processors of a computer.
 In order to perform optimizations for multiple time series, the use of a cluster is a necessity.
@@
 the selection of the meteorological variable).
-New values resulting from the optimizer need to respect the type of data it represents.
+New values resulting from the optimizer need to respect the type of data they represent.
 Other constraints exist in between the parameters, e.g.
-the hours of observation of the relative humidity and the precipitable water predictors have to match when processing the moisture index.
+the temporal windows of the relative humidity and the precipitable water predictors have to match when processing the moisture index.
 
@@
 
-In the present study, the choice of the meteorological variables considered as predictors is still set a priori.
+In the present study, the choice of the meteorological variables (predictors) is still performed manually.
 Then, for every level of analogy, GAs have to optimize jointly (i) the spatial windows (position and size; different between the pressure levels), (ii) the temporal windows (hours of observation of the predictors), (iii) the number of analog situations, and (iv) later on, the selection of the pressure levels (two, in this case).

### 2016-09-13 Genetic algorithms - MWR/template.tex
Reading and improving the paper.

@@
 
-The choice of GAs options, such as the mutation rate, population size, natural selection options, etc, appears difficult given the high number of existing variants, each developed for a specific problem \citep{Haupt2004, Costa2007a}.
+The choice of GAs options, such as the mutation rate, population size, natural selection, etc, appears difficult given the high number of existing variants, each developed for a specific problem \citep{Haupt2004, Costa2007a}.
 Thus, different studies suggest very different configurations \citep{DeJong1975a, Grefenstette1986, Back1996a, Back1996b}.
@@
 In the present study, the choice of the meteorological variables (predictors) is still performed manually.
-Then, for every level of analogy, GAs have to optimize jointly (i) the spatial windows (position and size; different between the pressure levels), (ii) the temporal windows (hours of observation of the predictors), (iii) the number of analog situations, and (iv) later on, the selection of the pressure levels (two, in this case).
-The first experiments are on a single level of analogy (on the geopotential height, see section \ref{sec:am}), and a second level (on moisture) is added further on in section \ref{sec:assessment}.\ref{sec:assessment:results}.\ref{sec:assessment:mutation}.
+Then, GAs have to optimize jointly, for all levels of analogy, (i) the spatial windows (position and size; different between the pressure levels), (ii) the temporal windows (hours of observation of the predictors), (iii) the number of analog situations, and (iv) later on, the selection of the pressure levels (two, in this case).
+The first experiments consider a single level of analogy (on the geopotential height, see section \ref{sec:am}), and a second level (on moisture) is added further on in section \ref{sec:assessment}.\ref{sec:assessment:results}.\ref{sec:assessment:mutation}.
 
@@
 
-As one of our goals is to make recommendations on how to use GAs in order to optimize different AM variants, a systematic procedure was adopted.
+A goal of the present paper being to make recommendations on the use of GAs in order to optimize different AM variants, a systematic procedure was adopted.
 The results are summarized hereafter \citep[see][for the details]{Horton2012a}.
-In order to compare different configurations of GAs, the factorial design approach was applied, in a similar way as \citet{Costa2005a,Costa2007a} and \citet{Mariano2010a}.
+In order to compare different configurations of GAs, a factorial design approach was applied, in a similar way as \citet{Costa2005a,Costa2007a} and \citet{Mariano2010a}.
 It allows isolating the effect of a parameter under different combinations of the other options.
-A procedure by stages was adopted, analyzing in details and in a systematic way every variant of the implemented operators, in combination with multiple other options and parameters in order to take into account eventual co-dependencies.
 
 In order to evaluate a combination of operators/options, 10 optimizations per configuration of GAs were processed.
-With all assessed combinations of GAs options, 21,630 optimizations were performed on an Intel Xeon based HPC cluster with 96 cpu, running Linux RedHat.
+With all combinations of GAs options, 21,630 optimizations were performed on an Intel Xeon based HPC cluster with 96 cpu, running Linux RedHat.
 Such assessment is not possible on the whole archive length, and had to be performed on a reduced calibration period : 5 years, from 1998 to 2002, but looking for analog dates on a 48 years period (1961-2008).
-The total resources needed for this comparison amounts to 229,539 h/cpu (26.2 years).
+The total resources needed for this comparison amount to 229,539 h/cpu (26.2 years/cpu).
 One should remember that these intensive resources were needed in order to assess multiple combinations of GAs options in order to provide recommendations.
-Based on these, applying GAs to optimize AMs require some computational power, but not as much (the time needed is function of the archive length, the population number, the other GAs options, and the complexity of the AM to optimize).
+Based on these, applying GAs to optimize AMs require some computational power, but not as much (the time needed is function of the archive length, the population number, GAs options, and the complexity of the AM to optimize).
 
@@
 Figure \ref{fig:gas_evolution_good} shows the evolution of the score of the best individuals over generations for 10 optimizations processed for a given configuration of GAs (same operators options).
-7 out of 10 optimizations converged to the global optimum (dashed line at the top of the plot) after 40 to 55 generations, which is not the best performance we observed later on.
+7 out of 10 optimizations converged to the global optimum (dashed line at the top of the plot in Figure \ref{fig:gas_evolution_good}) after 40 to 55 generations, which is not the best performance we observed later on.
 The performance score of the sequential approach (bottom line) has been quickly exceeded without adding any new parameter to the method (Fig.
@@
 
-The results illustrate the effect of an operator when its contribution is isolated from the other operators.
-It means that we analyze the effect of a given operator for equivalent conditions (same settings of other operators).
-Multiple combinations with other operators are assessed.
+The results of the factorial design procedure illustrate the effect of an operator when its contribution is isolated from the other operators.
+It means that we analyze the effect of a given operator for equivalent conditions (same settings of other operators), while assessing multiple combinations of these.
 This contribution is then summarized as a percentage of gain/loss regarding the mean of all variants, for equivalent external conditions.
-For example, to evaluate the performance of the uniform crossover operator, its performance is compared to the average of all crossover operators while retaining the same population size, the same mutation operators, natural selection, and selection of couples.
+For example, to evaluate the performance of the uniform crossover operator, its performance is compared to the average of all crossover operators, while retaining the same population size, the same mutation, natural selection, and couples selection operators.
 
@@
 
-The performance of the couples selection operator are relatively close (Fig.
+The performances of the couples selection operators are relatively close (Fig.
 \ref{fig:operator_selectcoupl_score}).
@@
 
-Analysis of crossover operators (Fig.
-\ref{fig:operator_crossover_score}) reveal some slightly superior options, some inappropriate, and many average.
-Binary-like crossover (especially with 2 points of intersection, whether $\beta$ is shared or not) are significantly better than the others, especially in terms of convergence (not shown).
+As for crossover operators (Fig.
+\ref{fig:operator_crossover_score}), binary-like crossover (especially with 2 points of intersection, whether $\beta$ is shared or not) is a bit better than the others, especially in terms of convergence (not shown).
 
@@
 
-Figure \ref{fig:operator_mutation_score} show the results of this analysis and illustrates the important role of the mutation on the performance of the optimizations.
-Those without mutation (last box on Figure \ref{fig:operator_mutation_score}) are inferior to most mutation operators, and the scale of the influence of this operator is significantly more important than those for the other options.
+Figure \ref{fig:operator_mutation_score} show the results of this analysis and illustrates the important role of mutation on the optimization performance.
+Configurations without mutation (last box on Figure \ref{fig:operator_mutation_score}) are inferior to most mutation operators, and the magnitude of this operator influence is significantly higher than those of the other options.
 The details of the analysis \citep[see][]{Horton2012a} show that the other reproduction operators seem of secondary importance.
@@
 
-The mutation operators based on variable normal or variable uniform laws work very poorly and are difficult to configure.
+The mutation operators based on variable normal or variable uniform laws work very poorly here and are difficult to configure.
 Many operators present more or less the same performance scores and require a variable amount of assessments.
-The convergence analysis \citep[see][]{Horton2012a} allows one to highlight three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
+The convergence analysis \citep[see][]{Horton2012a} allows to highlight three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
 Thus, different optimizations (an additional 4,950) were further performed using variants of these 3 operators (Figures \ref{fig:operator_mutation_score_atmlevel}-\ref{fig:operator_mutation_score_r4}).
 
-The first analysis was the optimization of the precipitation downscaling over a subcatchment (Binn-Simplon region) in the Swiss Alps (Fig.
+The first analysis was the optimization of the precipitation prediction over a subcatchment (Binn-Simplon region) in the Swiss Alps (Fig.
 \ref{fig:operator_mutation_score_atmlevel}).
-The optimizer could choose the 2 pressure levels of the atmospheric circulation analogy (method with a single level of analogy).
-The resulting CRPSS performance score (section \ref{sec:am}) is obviously superior to the one obtained by the sequential calibration (red line on Fig.
+The optimizer could also choose the 2 pressure levels of the atmospheric circulation analogy (method with a single level of analogy).
+The resulting CRPSS performance score (section \ref{sec:am}) is obviously superior to the one obtained by the sequential calibration (bottom line on Fig.
 \ref{fig:operator_mutation_score_atmlevel}).
-For most options, it is also slightly better than the results from the optimization without selection of the pressure levels (blue line).
-A clear breakthrough of the performances was not expected, as the former selection of pressure levels results already from intensive comparative work \citep{Bontron2004}.
+For most options, it is also slightly better than the results from the optimization without selection of the pressure levels (dashed line).
+A clear breakthrough of the performances was not expected, as the former selection of pressure levels results from intensive comparative work \citep{Bontron2004}.
 This application however demonstrates that, when correctly configured, GAs can automatically and successfully choose the pressure levels.
-However, some less relevant optimizations do not match the previous results.
-Through different applications, the automatic selection of the pressure level was shown to significantly increase the difficulty for GAs to converge to a unique solution, ideally the global optimum.
-A difficulty is that the pressure levels are considered within the optimization without continuity between values, and thus the approaches relying on distance in the parameters space, such as the search radius, cannot fully exploit the properties that make them efficient.
-However, even though the results show a certain variability, most of them present very good performance scores, despite different parameters of the AM considered.
+However, the automatic selection of the pressure levels significantly increases the difficulty for GAs to converge to a unique solution, ideally the global optimum.
+An likely explanation is that the pressure levels are considered as categorical values within the optimization (sampled with a uniform law), and thus the approaches relying on distance in the parameters space, such as the search radius, cannot fully exploit the properties that make them efficient.
+However, even though the results show a certain variability, most of them present very good performance scores, despite different selection of AM parameters.
 
@@
 \ref{fig:map}), which is sensitive to other meteorological influences (Fig.
-\ref{fig:operator_mutation_score_rhoneamont}), in order to assess eventual dependencies of the operator with the predictand.
+\ref{fig:operator_mutation_score_rhoneamont}), in order to assess eventual dependencies of the operators with the predictand.
 Even though differences can be observed with Fig.
@@
 
-Next, a second level of analogy was proposed (Fig.
-\ref{fig:operator_mutation_score_r2}) based on moisture variables \citep[see][]{Bontron2004}.
-GAs had to optimize both levels of analogy (on the geopotential height first, and then on the moisture index made of relative humidity and precipitable water) simultaneously.
-Once again, despite the difficulty to do so, the results were better than the sequential calibration (bottom line on Fig.
+Next, a second level of analogy was introduced (Fig.
+\ref{fig:operator_mutation_score_r2}) based on moisture variables (section \ref{sec:am}).
+GAs had to optimize both levels of analogy (geopotential height and moisture index) simultaneously.
+Once again, the results were better than the sequential calibration (bottom line on Fig.
 \ref{fig:operator_mutation_score_r2}).
@@
 The results show generally higher scores (Fig.
-\ref{fig:operator_mutation_score_r4}), demonstrating the success of the optimizer to take advantage of this new degree of freedom, and its capacity to handle optimization of 3 analogy levels jointly.
-Again, the most relevant options are generally the same.
-
-After analysis of the most relevant mutation operators, the following advice can be raised (detailed options are provided in section \ref{sec:use}.\ref{sec:recommendations}):
+\ref{fig:operator_mutation_score_r4}), demonstrating the success of the optimizer to take advantage of this new degree of freedom, and its ability to handle optimization of 3 analogy levels jointly.
+Again, the most relevant options are globally the same.
+
+After these various tests of the mutation operators relevance, the following advices can be raised (detailed options are provided in section \ref{sec:use}.\ref{sec:recommendations}):
 
@@
 It is interesting to note that the three best techniques incorporate a notion of search distance.
-It is likely that this notion is the key to these algorithms, for this application, and allows them to initially explore the parameter domain, and then to converge.
+It is likely that this notion is the key to these algorithms, for this application, and allows them to initially explore the parameter space, and then to converge.
 The search radius in fact directly represents the notion of transition between exploration and exploitation, in our opinion more than a possible evolution of mutation rates.
@@
 \ref{fig:operator_selectnat_score}) reveals a slight preference for the ratio-elitism compared to the tournament selection, but not so significant.
-This operator, or at least the two assessed versions, do not appear to significantly influence the optimization performances.
-
-The size of the population ($N$), i.e.
-the number of sets of AM parameters considered, has an effect on the performance of the optimization (Fig.
+This operator, or at least the two assessed versions, do not appear to significantly influence the optimization performance.
+
+The size of the population ($N$) has an effect on the optimization performance (Fig.
 \ref{fig:option_taillepop_score}).
 A bigger population leads to better results, but also to longer optimizations: the required number of evaluation, and thus the required time, is approximately proportional to the population size.
-Thus, if the population size is doubled, the time required for the optimization also nearly doubles (e.g., for a 5 years calibration period, approximately 4~h/cpu was needed when $N = 50$, and 14~h/cpu when $N = 200$).
+Thus, if the population size is doubled, the time required for the optimization also nearly doubles (e.g., for a 5 years calibration period, approximately 4~h/cpu were needed when $N = 50$, and 14~h/cpu when $N = 200$).
 The optimal size seems to depend on the complexity of the AM to optimize: a more complex AM (ie.
@@
 
-\section{Use of GAs ot optimize AMs}
+\section{Use of GAs to optimize AMs}
 \label{sec:use}
@@
 
-Optimizations by GAs for AMs of varying complexities were performed with a large number of combinations of operators in order to make recommendations for optimizing AMs. The conclusions are:
+Optimizations by GAs of AMs of varying complexities were performed with a large number of combinations of operators in order to make recommendations for optimizing AMs (section \ref{sec:assessment}).
+The conclusions are:
 
@@
 
-	\item The value of the ratio for the IG is not so important, and value of 50\% seems quite appropriate.
+	\item The value of the IG ratio is not so important; a value of 50\% seems appropriate.
 
@@
 
-	\item The performance of the operators for the couples selection perform relatively similarly.
+	\item The performance of the operators for the couples selection are relatively equivalent.
 The roulette wheel weighting and the tournament selection are more efficient in terms of convergence and required number of evaluations.
 
-	\item Most crossover operators have relatively similar performance. Binary-like crossover with two points of intersection are better than others, especially for convergence.
+	\item Most crossover operators have relatively similar performance, but the binary-like crossover with two points of intersection is a bit better, especially for convergence.
 
@@
 	\setlength\itemsep{-4px}
-	\item 1x non-uniform, $p_{mut}=0.05$, $G_{m}=50$, $\omega=0.1$
-	\item 1x non-uniform, $p_{mut}=0.05$, $G_{m}=100$, $\omega=0.1$
-	\item 1x non-uniform, $p_{mut}=0.1$, $G_{m}=100$, $\omega=0.1$
+	\item 1x non-uniform, $p_{mut}=0.05$, $G_{m,r}=50$, $\omega=0.1$
+	\item 1x non-uniform, $p_{mut}=0.05$, $G_{m,r}=100$, $\omega=0.1$
+	\item 1x non-uniform, $p_{mut}=0.1$, $G_{m,r}=100$, $\omega=0.1$
 	\item 1x multi-scale,  $p_{mut}=0.1$
@@
 
-In order to illustrate the gain achievable by the optimization on the considered AM, the Southeast ridges region of the alpine Rhône catchment has been optimized for the whole calibration period (40 years in the 1961-2008 period, leaving out 8 years for validation), instead of the smaller 5-years period.
+In order to illustrate the gain achievable by GAs on an AM, the Southeast ridges region of the alpine Rh\^{o}ne catchment (Fig.
+\ref{fig:map}) has been optimized for the whole calibration period (40 years in the 1961-2008 period, leaving out 8 years for validation), instead of the smaller 5-years period.
 
@@
 Moreover, a weighting was introduced in the combination of the criteria processed on each pressure level \citep[such as][]{Horton2012a, Junk2015}.
-In this case, no new meteorological variable was added, and the method still contains a unique level of analogy.
+In this case, no new meteorological variable was added, and the method still contained a unique level of analogy.
 
@@
 Given the large number of existing operators and options, multiple variants were assessed systematically in order to identify which operators are important, and which variants work best for the considered AM implementations.
-The mutation operator was identified as a key element for this application, and new variants that proved efficient were provided, such as the chromosome of adaptive search radius that is very robust (no control parameter).
+The mutation operator was identified as a key element for this application, and new variants that proved efficient were developed, such as the chromosome of adaptive search radius that is very robust (no control parameter).
 Recommendations were established for a relevant use of GAs for the optimization of AMs.
@@
 It is not excluded that another global optimization method or other operators of GAs may perform even better.
-Still, the relevance of global optimization techniques for AMs has now been proved as they result in parameters of AMs that are relevant and fully automatically, globally and objectively established.
+Still, the relevance of global optimization techniques for AMs has now been proven, as they provide relevant AM parameters that are automatically, globally and objectively established.
 A global optimization is the only way to take into account all the dependencies between parameters and levels of analogy.
@@
 The global optimization approach allows easily adapting AMs to new regions by potentially taking into account local meteorological influences, and has thus a great potential of use.
-Moreover, it allows exploring automatically datasets in order to extract the most relevant variables.
-It is thus possible to try assessing other predictands, such as the temperature, the limit of snowfall, the occurrence of hail, or wind, while leaving the algorithms select the best variables and the associated parameters.
+Moreover, it can be used to explore automatically datasets in order to extract the most relevant variables.
+It would be thus easier to assess other predictands, such as the temperature, the limit of snowfall, the occurrence of hail, etc, while leaving the algorithms select the best variables and the associated parameters.
 

### 2016-09-13 Genetic algorithms - MWR/template.tex
Correcting tenses.

@@
 the \textit{chromosome of adaptive search radius} which was found to be very robust), in order to make recommendations for the use of Genetic Algorithms to optimize several variants of analog methods.
-A global optimization approach opens new perspective for the improvement of analog methods, and their application to new regions or to new predictands.
+A global optimization approach opens new perspectives for the improvement of analog methods, and their application to new regions or to new predictands.
 }
@@
 A common usage of AMs is for operational precipitation forecasting \citep[eg.][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Hamill2015b, BenDaoud2016}, or more recently for precipitation downscaling in a climate perspective \citep[eg.][]{Radanovics2013, Chardon2014, Dayon2015}.
-However, AMs or equivalent were also used to predict temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+However, AMs or equivalent are also used to predict temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
 
@@
 
-Another optimization strategy has been proposed by \citet{Junk2015}, and allows for an automatic calibration of weights applied to the different predictors when processing the analogy criteria (distance function).
+Another optimization strategy is proposed by \citet{Junk2015}, and allows for an automatic calibration of weights applied to the different predictors when processing the analogy criteria (distance function).
 Their strategy consists in a brute-force assessment of all possible combinations.
@@
 
-This paper is not about discussing the details of the results of an optimization with GAs, but describing how GAs are to be used in order to successfully optimize several AMs.
+This paper specifically describes how GAs are to be used in order to successfully optimize several AMs.
 Indeed, GAs variants are numerous and always need to be tailored to the addressed problem.
 This requires intensive and systematic comparisons of operators and options in order to identify the key factors leading the optimization and the respective sensitivity of the options.
-Such analyzes are presented here and will result in recommendations for the use of GAs to optimize several AM implementations.
+Such analyzes are presented here and result in recommendations for the use of GAs to optimize several AM implementations.
 The in-depth analysis of the benefit brought by such an approach on a specific case study is the topic of another coming paper.
@@
 
-The study area is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at providing real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
+This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at providing real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
 AMs are used to provide real-time probabilistic precipitation forecasts, based on NWP outputs.
@@
 
-In the present study, the NCEP-NCAR reanalysis I dataset \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} is used, but it could be any other reanalysis dataset.
+In the present study, the NCEP-NCAR reanalysis I dataset \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} was used, but it could have been any other reanalysis dataset.
 This dataset is relatively old, even though still widely used, and better results may be expected with more recent datasets.
@@
 
-The predictand (which is to be predicted) is here the daily precipitation (6~a.m.
+The predictand (which is to be predicted) was here the daily precipitation (6~a.m.
 to 6~a.m.
@@
 (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a defined spatial window.
-The S1 criteria was found more relevant than Euclidean distances for pressure fields by different studies \citep{Wilson1980, Woodcock1980, Guilbaud1998, Bontron2004}.
+The S1 criteria is found more relevant than Euclidean distances for pressure fields by different studies \citep{Wilson1980, Woodcock1980, Guilbaud1998, Bontron2004}.
 
@@
 	A second level of analogy based on thermodynamic variables was introduced by \citet{Vallee1986}, and \citet{Gibergans-Baguena2007}.
-After a systematic assessment, \citet{Bontron2004} pointed out that a moisture index made of the product of relative humidity at 850~hPa and total precipitable water gave the best performance.
+After a systematic assessment of variables, \citet{Bontron2004} pointed out that a moisture index made of the product of relative humidity at 850~hPa and total precipitable water gives the best performance.
 This index does not represent an actual physical quantity, but expresses the water content of the air column and its proximity to saturation.
@@
 
-In order to calibrate the method, the Continuous Ranked Probability Score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} has often been used to assess AMs performances \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}.
+In order to calibrate the method, the Continuous Ranked Probability Score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} is often used to assess AMs performances \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}.
 It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$.
@@
 
-	\item Binary-like crossover \citep{Haupt2004}: in order to reproduce the behaviour present in the canonical crossover algorithm, which is applied to a binary representation of the genes \citep{Goldberg1989, Goldberg1990a, Herrera1998a}, \citet{Haupt2004} proposed an operator that combines the standard crossover operation with an interpolation approach.
+	\item Binary-like crossover \citep{Haupt2004}: in order to reproduce the behaviour present in the canonical crossover algorithm, which is applied to a binary representation of the genes \citep{Goldberg1989, Goldberg1990a, Herrera1998a}, \citet{Haupt2004} propose an operator that combines the standard crossover operation with an interpolation approach.
 The genes located after a crossover point are exchanged, but the gene located at the intersection is modified according to:
@@
 The combination of strong genes by the operator of chromosomes crossover is theoretically the most important operating mechanism in the conventional GAs \citep{Holland1992b,Back1993b}.
-However, many studies identified the mutation process as the main operator, and crossovers as secondary \citep[see][]{Back1992a, Back1996a, Back1996b, Smith1997a, Deb1999, Costa2005a, Costa2007a}.
+However, many studies identify the mutation process as the main operator, and crossovers as secondary \citep[see][]{Back1992a, Back1996a, Back1996b, Smith1997a, Deb1999, Costa2005a, Costa2007a}.
 
@@
 This ensures the survival of the best individual so that a better solution is never lost.
-After the natural selection operator, if the previously best individual has not been selected, it is copied to the IG instead of an individual randomly picked.
-After mutation, if the previously best individual has mutated and if its new version has a lower performance score than the original, the latter is also reinserted in the IG instead of an individual randomly chosen.
+After the natural selection operator, if the previously best individual has not been selected, it was copied to the IG instead of an individual randomly picked.
+After mutation, if the previously best individual has mutated and if its new version has a lower performance score than the original, the latter was also reinserted in the IG instead of an individual randomly chosen.
 
@@
 The convergence check determines whether the solution is acceptable and if the algorithm may stop.
-The optimization is here stopped if the best individual does not change for $x$ generations.
+The optimization was here stopped if the best individual did not change for $x$ generations.
 This value should not be too low to allow the algorithm to escape from a local optima, and because the rate of improvement decreases with the progression of the optimization.
@@
 GAs are very computationally intensive because they require many evaluations of the objective function.
-These assessments are relatively long (couple of seconds) in this application, as they require calculating and assessing a prediction for every day of the calibration period, thus over several decades.
-In order to reduce the computation time, the performance score of an individual who has previously been evaluated, and that has not changed, was preserved.
-Thus, the score of each individual living in the selection was kept until it mutates.
-
-As the calculation of the objective function of each member of the population of a generation is completely independent, they were performed in parallel on different processors of a computer.
+These assessments are take some time (couple of seconds) in this application, as they require calculating and assessing a prediction for every day of the calibration period, thus over several decades.
+In order to reduce the computation time, the performance score of an individual who had previously been evaluated, and that had not changed, was preserved.
+Thus, the score of each individual living in the selection was kept until it mutated.
+
+As the calculation of the objective function of each member of the population of a generation is completely independent, they were processed in parallel on different cpus.
 In order to perform optimizations for multiple time series, the use of a cluster is a necessity.
@@
 
-In the present study, the choice of the meteorological variables (predictors) is still performed manually.
-Then, GAs have to optimize jointly, for all levels of analogy, (i) the spatial windows (position and size; different between the pressure levels), (ii) the temporal windows (hours of observation of the predictors), (iii) the number of analog situations, and (iv) later on, the selection of the pressure levels (two, in this case).
-The first experiments consider a single level of analogy (on the geopotential height, see section \ref{sec:am}), and a second level (on moisture) is added further on in section \ref{sec:assessment}.\ref{sec:assessment:results}.\ref{sec:assessment:mutation}.
+In the present study, the choice of the meteorological variables (predictors) was still performed manually.
+Then, GAs had to optimize jointly, for all levels of analogy, (i) the spatial windows (position and size; different between the pressure levels), (ii) the temporal windows (hours of observation of the predictors), (iii) the number of analog situations, and (iv) later on, the selection of the pressure levels (two, in this case).
+The first experiments considered a single level of analogy (on the geopotential height, see section \ref{sec:am}), and a second level (on moisture) was added further on in section \ref{sec:assessment}.\ref{sec:assessment:results}.\ref{sec:assessment:mutation}.
 
@@
 
-A goal of the present paper being to make recommendations on the use of GAs in order to optimize different AM variants, a systematic procedure was adopted.
+The main goal of the present paper being to make recommendations on the use of GAs in order to optimize different AM variants, a systematic procedure was adopted.
 The results are summarized hereafter \citep[see][for the details]{Horton2012a}.
@@
 With all combinations of GAs options, 21,630 optimizations were performed on an Intel Xeon based HPC cluster with 96 cpu, running Linux RedHat.
-Such assessment is not possible on the whole archive length, and had to be performed on a reduced calibration period : 5 years, from 1998 to 2002, but looking for analog dates on a 48 years period (1961-2008).
+Such assessment was not possible on the whole archive length, and had to be performed on a reduced calibration period: 5 years, from 1998 to 2002, but looking for analog dates on a 48 years period (1961-2008).
 The total resources needed for this comparison amount to 229,539 h/cpu (26.2 years/cpu).
@@
 \ref{fig:gas_evolution_good}).
-The improvement is about 8.8\% in this case, which is substantial.
-
-Even GAs configurations that will be later rejected, because they did not converge (Fig.
+The improvement was about 8.8\% in this case, which is substantial.
+
+Even GAs configurations that were later rejected, because they did not converge (Fig.
 \ref{fig:gas_evolution_bad}), did still significantly better that the sequential approach.
@@
 The results of the factorial design procedure illustrate the effect of an operator when its contribution is isolated from the other operators.
-It means that we analyze the effect of a given operator for equivalent conditions (same settings of other operators), while assessing multiple combinations of these.
-This contribution is then summarized as a percentage of gain/loss regarding the mean of all variants, for equivalent external conditions.
-For example, to evaluate the performance of the uniform crossover operator, its performance is compared to the average of all crossover operators, while retaining the same population size, the same mutation, natural selection, and couples selection operators.
+It means that we analyzed the effect of a given operator for equivalent conditions (same settings of other operators), while assessing multiple combinations of these.
+This contribution was then summarized as a percentage of gain/loss regarding the mean of all variants, for equivalent external conditions.
+For example, to evaluate the performance of the uniform crossover operator, its performance was compared to the average of all crossover operators, while retaining the same population size, the same mutation, natural selection, and couples selection operators.
 
@@
 
-The performances of the couples selection operators are relatively close (Fig.
+The performances of the couples selection operators were relatively close (Fig.
 \ref{fig:operator_selectcoupl_score}).
-Overall, the tournament selection with 3~candidates is slightly superior to others, along with the roulette wheel weighting.
-This last one is however a bit less effective in terms of convergence and number of evaluations (not shown).
-The couples selection operator has not a significant role in this application.
+Overall, the tournament selection with 3~candidates was slightly superior to others, along with the roulette wheel weighting.
+This last one was however a bit less effective in terms of convergence and number of evaluations (not shown).
+The couples selection operator had no significant role in this application.
 
 As for crossover operators (Fig.
-\ref{fig:operator_crossover_score}), binary-like crossover (especially with 2 points of intersection, whether $\beta$ is shared or not) is a bit better than the others, especially in terms of convergence (not shown).
+\ref{fig:operator_crossover_score}), binary-like crossover (especially with 2 points of intersection, whether $\beta$ is shared or not) was a bit better than the others, especially in terms of convergence (not shown).
 
@@
 Figure \ref{fig:operator_mutation_score} show the results of this analysis and illustrates the important role of mutation on the optimization performance.
-Configurations without mutation (last box on Figure \ref{fig:operator_mutation_score}) are inferior to most mutation operators, and the magnitude of this operator influence is significantly higher than those of the other options.
-The details of the analysis \citep[see][]{Horton2012a} show that the other reproduction operators seem of secondary importance.
+Configurations without mutation (last box on Figure \ref{fig:operator_mutation_score}) were inferior to most mutation operators, and the magnitude of this operator influence was significantly higher than those of the other options.
+The details of the analysis \citep[see][]{Horton2012a} showed that the other reproduction operators seem of secondary importance.
 This observation is in line with the conclusions made by several other authors (see section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:mutation}).
 
-The mutation operators based on variable normal or variable uniform laws work very poorly here and are difficult to configure.
-Many operators present more or less the same performance scores and require a variable amount of assessments.
-The convergence analysis \citep[see][]{Horton2012a} allows to highlight three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
+The mutation operators based on variable normal or variable uniform laws worked very poorly here and were difficult to configure.
+Many operators presented more or less the same performance scores and required a variable amount of assessments.
+The convergence analysis \citep[see][]{Horton2012a} allowed to highlight three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
 Thus, different optimizations (an additional 4,950) were further performed using variants of these 3 operators (Figures \ref{fig:operator_mutation_score_atmlevel}-\ref{fig:operator_mutation_score_r4}).
@@
 The optimizer could also choose the 2 pressure levels of the atmospheric circulation analogy (method with a single level of analogy).
-The resulting CRPSS performance score (section \ref{sec:am}) is obviously superior to the one obtained by the sequential calibration (bottom line on Fig.
+The resulting CRPSS performance score (section \ref{sec:am}) was obviously superior to the one obtained by the sequential calibration (bottom line on Fig.
 \ref{fig:operator_mutation_score_atmlevel}).
-For most options, it is also slightly better than the results from the optimization without selection of the pressure levels (dashed line).
+For most options, it was also slightly better than the results from the optimization without selection of the pressure levels (dashed line).
 A clear breakthrough of the performances was not expected, as the former selection of pressure levels results from intensive comparative work \citep{Bontron2004}.
 This application however demonstrates that, when correctly configured, GAs can automatically and successfully choose the pressure levels.
-However, the automatic selection of the pressure levels significantly increases the difficulty for GAs to converge to a unique solution, ideally the global optimum.
-An likely explanation is that the pressure levels are considered as categorical values within the optimization (sampled with a uniform law), and thus the approaches relying on distance in the parameters space, such as the search radius, cannot fully exploit the properties that make them efficient.
-However, even though the results show a certain variability, most of them present very good performance scores, despite different selection of AM parameters.
+However, the automatic selection of the pressure levels significantly increased the difficulty for GAs to converge to a unique solution, ideally the global optimum.
+A likely explanation is that the pressure levels were considered as categorical values within the optimization (sampled with a uniform law), and thus the approaches relying on distance in the parameters space, such as the search radius, could not fully exploit the properties that made them efficient.
+However, even though the results showed a certain variability, most of them presented very good performance scores, despite different selection of AM parameters.
 
@@
 \ref{fig:operator_mutation_score_rhoneamont}), in order to assess eventual dependencies of the operators with the predictand.
-Even though differences can be observed with Fig.
+Even though differences can be observed in Fig.
 \ref{fig:operator_mutation_score_atmlevel}, it is globally the same options that perform better.
@@
 And finally, a preselection on air temperature was added instead of the fixed calendar window, as proposed by \cite{BenDaoud2016}.
-The results show generally higher scores (Fig.
+The results showed generally higher scores (Fig.
 \ref{fig:operator_mutation_score_r4}), demonstrating the success of the optimizer to take advantage of this new degree of freedom, and its ability to handle optimization of 3 analogy levels jointly.
-Again, the most relevant options are globally the same.
+Again, the most relevant options were globally the same.
 
@@
 
-	\item \textit{Non-uniform mutation}: this operator is good in terms of convergence, mainly when the number of parameters to optimize is rather low.
+	\item \textit{Non-uniform mutation}: this operator was good in terms of convergence, mainly when the number of parameters to optimize is rather low.
 The number of required evaluations, however, can be quite substantial.
@@
 	\item \textit{Chromosome of adaptive search radius}: unlike the previous one, the proposed operator is very robust, as it requires no option and is auto-adapting.
-It is interesting to notice that the insertion of an extra chromosome representing the search radius gives better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).
+It is interesting to notice that the insertion of an extra chromosome representing the search radius gave better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).
 If one had to choose a single option for the mutation operator, we would recommend this one, as it was proven effective and needs no parameter.
 
-	\item \textit{Multi-scale mutation}: finally, the multi-scale mutation, which also performs pretty well, requires one parameter, the mutation rate.
+	\item \textit{Multi-scale mutation}: finally, the multi-scale mutation, which also performed pretty well, requires one parameter, the mutation rate.
 However, it can also be difficult to estimate a correct value a priori.
@@
 The analysis of the natural selection operator (Fig.
-\ref{fig:operator_selectnat_score}) reveals a slight preference for the ratio-elitism compared to the tournament selection, but not so significant.
-This operator, or at least the two assessed versions, do not appear to significantly influence the optimization performance.
-
-The size of the population ($N$) has an effect on the optimization performance (Fig.
+\ref{fig:operator_selectnat_score}) revealed a slight preference for the ratio-elitism compared to the tournament selection, but not so significant.
+This operator, or at least the two assessed versions, did not appear to significantly influence the optimization performance.
+
+The size of the population ($N$) had an effect on the optimization performance (Fig.
 \ref{fig:option_taillepop_score}).
-A bigger population leads to better results, but also to longer optimizations: the required number of evaluation, and thus the required time, is approximately proportional to the population size.
-Thus, if the population size is doubled, the time required for the optimization also nearly doubles (e.g., for a 5 years calibration period, approximately 4~h/cpu were needed when $N = 50$, and 14~h/cpu when $N = 200$).
+A bigger population led to better results, but also to longer optimizations: the required number of evaluation, and thus the required time, was approximately proportional to the population size.
+Thus, if the population size doubled, the time required for the optimization also nearly doubled (e.g., for a 5 years calibration period, approximately 4~h/cpu were needed when $N = 50$, and 14~h/cpu when $N = 200$).
 The optimal size seems to depend on the complexity of the AM to optimize: a more complex AM (ie.
@@
 \ref{fig:option_popratio_score}).
-It does not appear that this parameter is critical to the quality of the optimizations, provided it is not too big.
+This option had little influence on the performance of the optimizations.
 A value of 50~\% seems a wise choice.
@@
 
-The optimization does not systematically converge to the global optimum (but often close to it), which is why it is recommended to do several optimizations in parallel in order to compare the results, analyze the convergence, and keep the best.
+The optimization did not systematically converge to the global optimum (but often close to it), which is why it is recommended to do several optimizations in parallel in order to compare the results, analyze the convergence, and keep the best.
 It may be wise to consider the three mutation operators in parallel.
@@
 
-In order to illustrate the gain achievable by GAs on an AM, the Southeast ridges region of the alpine Rh\^{o}ne catchment (Fig.
-\ref{fig:map}) has been optimized for the whole calibration period (40 years in the 1961-2008 period, leaving out 8 years for validation), instead of the smaller 5-years period.
+In order to illustrate the gain achievable by GAs on an AM, precipitation prediction for the Southeast ridges region of the alpine Rh\^{o}ne catchment (Fig.
+\ref{fig:map}) was optimized for the whole calibration period (40 years in the 1961-2008 period, leaving out 8 years for validation), instead of the smaller 5-years period.
 
@@
 The performance (CRPSS) of the reference method calibrated by means of the sequential procedure amounts to 32.00\%, with a 0.95 confidence interval (assessed by bootstrapping on 10,000 samples) of (29.21\%; 34.94\%).
-The method optimized by means of GAs reaches a performance of 37.62\%, with a 0.95 confidence interval of (35.21\%; 40.11\%).
+The method optimized by means of GAs reached a performance of 37.62\%, with a 0.95 confidence interval of (35.21\%; 40.11\%).
 The resulting gain is thus statistically significant.

### 2016-09-13 Genetic algorithms - MWR/template.tex
Changing references to sections.

@@
 
-% TODO: check all references to sections
 % TODO: reduce font size in plots
+% TODO: AMS guidelines
 
@@
 \section{Introduction}
-\label{section_intro}
+\label{sec:intro}
 
@@
 AMs are based on the principle that two similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}.
-Thus, they consist in searching a certain number of past situations in a meteorological archive that present similar properties for chosen predictors, according to an analogy criteria, in order to extract the observed values of the local weather variable of interest from another archive (predictand time series, see section \ref{sec:case_study_data}.\ref{sec:data}).
+Thus, they consist in searching a certain number of past situations in a meteorological archive that present similar properties for chosen predictors, according to an analogy criteria, in order to extract the observed values of the local weather variable of interest from another archive (predictand time series, see section \ref{sec:case_study_data}\ref{sec:data}).
 Based on these analog observations, the conditional empirical distribution considered as the probabilistic prediction for the target day (the day one wants to predict) is built.
@@
 	\end{array} \right.
-	\label{equation_mating_as_binary}
+	\label{eq:binary_like_crossover}
 	\end{equation}
@@
 	\end{array} \right.
-	\label{equation_mutation_nonuniform_original}
+	\label{eq:nonuniform_mutation}
 	\end{equation}
@@
 	\end{array} \right.
-	\label{equation_mutation_rayon_adaptatif}
+	\label{eq:adaptive_search_radius_mutation}
 	\end{equation}
@@
 Then, GAs had to optimize jointly, for all levels of analogy, (i) the spatial windows (position and size; different between the pressure levels), (ii) the temporal windows (hours of observation of the predictors), (iii) the number of analog situations, and (iv) later on, the selection of the pressure levels (two, in this case).
-The first experiments considered a single level of analogy (on the geopotential height, see section \ref{sec:am}), and a second level (on moisture) was added further on in section \ref{sec:assessment}.\ref{sec:assessment:results}.\ref{sec:assessment:mutation}.
+The first experiments considered a single level of analogy (on the geopotential height, see section \ref{sec:am}), and a second level (on moisture) was added further on in section \ref{sec:assessment}\ref{sec:assessment:results}\ref{sec:assessment:mutation}.
 
@@
 Figure \ref{fig:gas_evolution_good} shows the evolution of the score of the best individuals over generations for 10 optimizations processed for a given configuration of GAs (same operators options).
-7 out of 10 optimizations converged to the global optimum (dashed line at the top of the plot in Figure \ref{fig:gas_evolution_good}) after 40 to 55 generations, which is not the best performance we observed later on.
+7 out of 10 optimizations converged to the global optimum (dashed line at the top of the plot in Fig.
+\ref{fig:gas_evolution_good}) after 40 to 55 generations, which is not the best performance we observed later on.
 The performance score of the sequential approach (bottom line) has been quickly exceeded without adding any new parameter to the method (Fig.
@@
 From the very beginning of the assessments, the importance of the mutation operator was obvious \cite[see][for the details]{Horton2012a}, and its leading influence on the optimization performance was evident.
-Its role is analyzed later on in section \ref{sec:assessment}.\ref{sec:assessment:results}.\ref{sec:assessment:mutation}.
+Its role is analyzed later on in section \ref{sec:assessment}\ref{sec:assessment:results}\ref{sec:assessment:mutation}.
 
@@
 Having identified the leading role of the mutation operator, the next sensitivity analysis focused on it.
-The 10 different implementations (see section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:mutation}) were tested, with different options (Fig.
+The 10 different implementations (see section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:mutation}) were tested, with different options (Fig.
 \ref{fig:operator_mutation_score}), bringing the number of variations up to 109.
@@
 Figure \ref{fig:operator_mutation_score} show the results of this analysis and illustrates the important role of mutation on the optimization performance.
-Configurations without mutation (last box on Figure \ref{fig:operator_mutation_score}) were inferior to most mutation operators, and the magnitude of this operator influence was significantly higher than those of the other options.
+Configurations without mutation (last box on Fig.
+\ref{fig:operator_mutation_score}) were inferior to most mutation operators, and the magnitude of this operator influence was significantly higher than those of the other options.
 The details of the analysis \citep[see][]{Horton2012a} showed that the other reproduction operators seem of secondary importance.
-This observation is in line with the conclusions made by several other authors (see section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:mutation}).
+This observation is in line with the conclusions made by several other authors (see section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:mutation}).
 
@@
 The convergence analysis \citep[see][]{Horton2012a} allowed to highlight three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
-Thus, different optimizations (an additional 4,950) were further performed using variants of these 3 operators (Figures \ref{fig:operator_mutation_score_atmlevel}-\ref{fig:operator_mutation_score_r4}).
+Thus, different optimizations (an additional 4,950) were further performed using variants of these 3 operators (Fig.
+\ref{fig:operator_mutation_score_atmlevel}-\ref{fig:operator_mutation_score_r4}).
 
@@
 
-After these various tests of the mutation operators relevance, the following advices can be raised (detailed options are provided in section \ref{sec:use}.\ref{sec:recommendations}):
+After these various tests of the mutation operators relevance, the following advices can be raised (detailed options are provided in section \ref{sec:use}\ref{sec:recommendations}):
 
@@
 	\end{center}
-	\caption{Influence of the couples selection operators (section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:nat_selection}) on the optimization performance (improvement of the score).
+	\caption{Influence of the couples selection operators (section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:nat_selection}) on the optimization performance (improvement of the score).
 The box extends from the lower to upper quartile values of the data, with a line at the median.
@@
 	\end{center}
-	\caption{Influence of the chromosome crossover operators (section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:crossover}) on the optimization performance (improvement of the score).
+	\caption{Influence of the chromosome crossover operators (section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:crossover}) on the optimization performance (improvement of the score).
 $\beta$s represent a shared $\beta$ parameter, and $\beta$u the unshared version.
@@
 	\end{center}
-	\caption{Influence of the mutation operators (section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:mutation}) on the optimization performance.
+	\caption{Influence of the mutation operators (section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:mutation}) on the optimization performance.
 In parentheses is the number of variants considered (combination of options).
@@
 	\end{center}
-	\caption{Influence of the mutation options (section \ref{sec:gas}.\ref{sec:gas:operators}.\ref{sec:gas:mutation}) on the optimization performance, leaving the optimizer choose the pressure level of the atmospheric circulation analogy (single level of analogy).
+	\caption{Influence of the mutation options (section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:mutation}) on the optimization performance, leaving the optimizer choose the pressure level of the atmospheric circulation analogy (single level of analogy).
 For the non-uniform mutation, $\omega=0.1$ in every case.

### 2016-09-13 Genetic algorithms - MWR/template.tex
Reducing font sizes in plots.
Minor updates.

@@
 
-% TODO: reduce font size in plots
 % TODO: AMS guidelines
+% TODO: compléter DOI
 
@@
 For the non-uniform mutation, $\omega=0.1$ in every case.
-The predictand is precipitation over a subcatchment in the Swiss Alps (Binn-Simplon region).
 The continuous bottom line represents the score of the sequential calibration and the dashed superior line, the score of the optimization without automatic selection of the pressure levels.
@@
 	\end{center}
-	\caption{Same as Fig. \ref{fig:operator_mutation_score_atmlevel}, but for another region in the Swiss Alps, with different atmospheric influences.}
+	\caption{Same as Fig. \ref{fig:operator_mutation_score_atmlevel}, but for another region in the Swiss Alps (Swiss Chablais), with different atmospheric influences.}
 	\label{fig:operator_mutation_score_rhoneamont}
@@
 	\end{center}
-	\caption{Influence of the intermediate population (IG) ratio on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
+	\caption{Influence of the intermediate generation (IG) ratio on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
 	\label{fig:option_popratio_score}

### 2016-09-14 Genetic algorithms - MWR/template.tex
Edition following AMS guidelines.

@@
 %\documentclass[twocol]{ametsoc}
-
-% TODO: AMS guidelines
-% TODO: compléter DOI
 
@@
 Genetic Algorithms need however to be tailored to the addressed problem.
-Multiple combinations of algorithms were assessed, and new ones were developed (e.g.
-the \textit{chromosome of adaptive search radius} which was found to be very robust), in order to make recommendations for the use of Genetic Algorithms to optimize several variants of analog methods.
+Multiple combinations of algorithms were assessed, and new ones were developed (e.g., the \textit{chromosome of adaptive search radius} which was found to be very robust), in order to make recommendations for the use of Genetic Algorithms to optimize several variants of analog methods.
 A global optimization approach opens new perspectives for the improvement of analog methods, and their application to new regions or to new predictands.
@@
 They consist in sampling a certain number of past situations based on different synoptic-scale meteorological variables (predictors) in order to build a probabilistic prediction for a local weather variable of interest (predictand).
-A common usage of AMs is for operational precipitation forecasting \citep[eg.][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Hamill2015b, BenDaoud2016}, or more recently for precipitation downscaling in a climate perspective \citep[eg.][]{Radanovics2013, Chardon2014, Dayon2015}.
+A common usage of AMs is for operational precipitation forecasting \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Hamill2015b, BenDaoud2016}, or more recently for precipitation downscaling in a climate perspective \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015}.
 However, AMs or equivalent are also used to predict temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
@@
 A common approach to optimize the method is by means of a semi-automatic sequential calibration procedure, developed by \citet{Bontron2004}, also described in \citet{BenDaoud2016}, and extended by \citet{Radanovics2013}.
-It determines some parameters of the method, sequentially for each consecutive analogy level (eg.
-on the atmospheric circulation or on a moisture index).
-It starts by a manual selection of the meteorological variables (e.g.
-geopotential height, relative humidity, etc.), the pressure levels, the temporal windows, and the initial analog numbers.
+It determines some parameters of the method, sequentially for each consecutive analogy level (e.g., on the atmospheric circulation or on a moisture index).
+It starts by a manual selection of the meteorological variables (e.g., geopotential height, relative humidity, etc.), the pressure levels, the temporal windows, and the initial analog numbers.
 Then, the spatial window on which the predictors are compared is optimized by an iterative growth of the domain, and the number of analogs is finally reassessed.
@@
 When creating the sequential calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters and wrote: ''\textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent.
-We will present our results by first searching the best variable [note: e.g.
-selection of the pressure level and the temporal window for the geopotential height] on a chosen spatial window, and next, the best window for the chosen variable.
+We will present our results by first searching the best variable (e.g., selection of the pressure level and the temporal window for the geopotential height) on a chosen spatial window, and next, the best window for the chosen variable.
 However, even by repeating the process, are we sure to obtain the optimal combination?}''.
@@
 When working in the Perfect Prognosis framework \citep{Klein1963}, the meteorological archive from which the predictors are extracted is usually a reanalysis dataset.
-Oppositely, other applications of AMs for wind forecasting are based on a Model Output Statistics context \citep[MOS, see][]{Glahn1972}, and thus use forecast archives or reforecast products \citep[e.g.][]{DelleMonache2013, DelleMonache2011, Alessandrini2015, Junk2015, Junk2015c}.
+Oppositely, other applications of AMs for wind forecasting are based on a Model Output Statistics context \citep[MOS, see][]{Glahn1972}, and thus use forecast archives or reforecast products \citep[e.g.,][]{DelleMonache2013, DelleMonache2011, Alessandrini2015, Junk2015, Junk2015c}.
 
@@
 
-The predictand (which is to be predicted) was here the daily precipitation (6~a.m.
-to 6~a.m.
-the next day) measured at the MeteoSwiss' stations network in the catchment of interest.
+The predictand (which is to be predicted) was here the daily precipitation (0540~UTC to 0540~UTC the following day) measured at the MeteoSwiss' stations network in the catchment of interest.
 The time series from every available gauging station were averaged over subregions of approximately 500~km$^{2}$ \citep[see][for the details]{Horton2012a} in order to smooth local effects \citep{Obled2002, Marty2012}.
@@
 
-Predictors for precipitation prediction, can be varied: e.g.
-geopotential height at different pressure levels and temporal windows, humidity variables, etc \citep[see][for a more detailed list of predictors]{BenDaoud2016}.
-The method often contains several levels of analogy, which are successive subsampling on predictors of different nature (eg.
-atmospheric circulation, moisture variables, vertical motion, and air temperature).
+Predictors for precipitation prediction, can be varied: e.g., geopotential height at different pressure levels and temporal windows, humidity variables, etc \citep[see][for a more detailed list of predictors]{BenDaoud2016}.
+The method often contains several levels of analogy, which are successive subsampling on predictors of different nature (e.g., atmospheric circulation, moisture variables, vertical motion, and air temperature).
 
@@
 The first level of analogy for precipitation prediction is often based on the atmospheric circulation.
-The similarity of the atmospheric circulation of the target date with the candidate situations is assessed on the geopotential height (at specific pressure levels, such as 500 and 1000~hPa, and over a certain spatial window, e.g.
-12~h and 24~h) by means of the S1 criteria \citep[eq.
+The similarity of the atmospheric circulation of the target date with the candidate situations is assessed on the geopotential height (at specific pressure levels, such as 500 and 1000~hPa, and over a certain spatial window, e.g., 12~h and 24~h) by means of the S1 criteria \citep[Eq.
 (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a defined spatial window.
@@
 	S1=100 \frac {\displaystyle \sum_{i} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
-	{\displaystyle \sum_{i} max\left\lbrace \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert \right\rbrace }
+	{\displaystyle \sum_{i} max( \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert ) }
 	\end{equation}
@@
 	\item The analogy criterion, needed to compare the variables on the chosen spatial and temporal windows, is a distance measure used for ranking observed situations according to their degree of similarity with the target situation.
-	\item Eventual weights between the predictors \cite[e.g.][]{Horton2012a, Junk2015}
+	\item Eventual weights between the predictors \cite[e.g.,][]{Horton2012a, Junk2015}
 	\item The ideal number of analog situations, which is the best compromise in order to take into account local variability and to maximize useful synoptic information \citep{Bontron2004}.
@@
 \label{eq:CRPS}
-CRPS = \frac{1}{l} \sum_{i=1}^{l} \left(  \int_{-\infty}^{+\infty} \left[ F_{i}(y)-H_{i}(y-y_{i}^{0})\right]^{2} dy \right) 
+CRPS = \frac{1}{l} \sum_{i=1}^{l} \left\{  \int_{-\infty}^{+\infty} \left[ F_{i}(y)-H_{i}(y-y_{i}^{0})\right]^{2} dy \right\} 
 \end{equation}
-where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value 1 otherwise. The mean CRPS is averaged on the calibration, respectively the validation periods.
+where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value one otherwise. The mean CRPS is averaged on the calibration, respectively the validation periods.
 
@@
 Genes are the individual parameters constituting the chromosome.
-They can be either categorical (e.g.
-choice of the meteorological variable), discrete (e.g.
-number of analog dates to select), or continuous.
+They can be either categorical (e.g., choice of the meteorological variable), discrete (e.g., number of analog dates to select), or continuous.
 
@@
 
-	\item Tournament selection: a number of individuals (2 or 3) are randomly picked and the best is kept, with a certain probability. This operation is performed twice, once for each partner.
+	\item Tournament selection: a number of individuals (two or three) are randomly picked and the best is kept, with a certain probability. This operation is performed twice, once for each partner.
 \end{itemize}
@@
 	where $g_{o1,n}$ and $g_{o2,n}$ are the $n$-th gene of the two new offspring, and $g_{p1,n}$ and $g_{p2,n}$ are those of the two parents.
-$\beta$ is a random value between 0 and 1, that can be unique for the whole chromosome, or that can change for every gene.
+$\beta$ is a random value between zero and one, that can be unique for the whole chromosome, or that can change for every gene.
 
@@
 The evaluated and developed mutation operators are listed hereafter (equations are only provided for the operator versions that were found relevant; the reader can refer to the corresponding literature for the details of the other options).
-They apply to genes made of continuous or discrete variables, but not categorical (e.g.
-choice of the meteorological variable or analogy criterion).
+They apply to genes made of continuous or discrete variables, but not categorical (e.g., choice of the meteorological variable or analogy criterion).
 In the latter case, the random choice of a new value is always based on a uniform distribution, without notion of distance in the parameters space.
@@
 	\item Variable normal mutation \citep{Horton2012a}: with the same logic as the variable uniform mutation, a mutation operator was tested using a normal distribution with a variable mutation rate and standard deviation, that decrease linearly over the generations.
-This operator has 6 parameters.
+This operator has six parameters.
 
@@
 	\begin{equation}
-	\varphi' = 1 - \min \left\lbrace \dfrac{G}{G_{m,r}}, 1 \right\rbrace \left(1-\omega\right)
+	\varphi' = 1 - \min \left( \dfrac{G}{G_{m,r}}, 1 \right) \left(1-\omega\right)
 	\end{equation}
@@
 	\item Individual adaptive search radius: based on the ideas of the non-uniform mutation, we introduced a search radius in the approach of individual adaptive mutation rates.
-This search radius $r_{a}$, bounded between 0 and 1 (relatively to the parameter ranges), is also adaptive and behaves similarly to the adaptive mutation rates.
+This search radius $r_{a}$, bounded between zero and one (relatively to the parameter ranges), is also adaptive and behaves similarly to the adaptive mutation rates.
 In order to separate its evolution from the one of the mutation rate, its own value is also considered as a self-mutation rate to eventually mutate before being used as a normalized search radius.
@@
 	\item Chromosome of adaptive search radius: in this operator, we combined the operations of the chromosome of adaptive mutation rate to the adaptive search radius approach.
-Similarly, an individual has 3 chromosomes: the first containing the values to be optimized, the second the distributed mutation rate, and the last one, the distributed search radius.
+Similarly, an individual has three chromosomes: the first containing the values to be optimized, the second the distributed mutation rate, and the last one, the distributed search radius.
 Again, no external parameter is required.
@@
 Thus, the search radius $r_{a}$ of Eq.
-\ref{equation_mutation_rayon_adaptatif} was considered as a random value for each individual, but restricted to 4 equiprobable values: 1, 0.5, 0.1, 0.02, so a range from full exploration to fine exploitation.
+(\ref{eq:adaptive_search_radius_mutation}) was considered as a random value for each individual, but restricted to four equiprobable values: 1, 0.5, 0.1, 0.02, so a range from full exploration to fine exploitation.
 The only external parameter is the mutation rate which is fixed.
@@
 For example, when a crossover or a mutation operation results in a parameter value standing out of the authorized bounds, it has to be brought back within the limits.
-Moreover, the parameters are of different types: continuous, discrete, or categorical (e.g.
-the selection of the meteorological variable).
+Moreover, the parameters are of different types: continuous, discrete, or categorical (e.g., the selection of the meteorological variable).
 New values resulting from the optimizer need to respect the type of data they represent.
-Other constraints exist in between the parameters, e.g.
-the temporal windows of the relative humidity and the precipitable water predictors have to match when processing the moisture index.
+Other constraints exist in between the parameters, e.g., the temporal windows of the relative humidity and the precipitable water predictors have to match when processing the moisture index.
 
@@
 In order to evaluate a combination of operators/options, 10 optimizations per configuration of GAs were processed.
-With all combinations of GAs options, 21,630 optimizations were performed on an Intel Xeon based HPC cluster with 96 cpu, running Linux RedHat.
-Such assessment was not possible on the whole archive length, and had to be performed on a reduced calibration period: 5 years, from 1998 to 2002, but looking for analog dates on a 48 years period (1961-2008).
-The total resources needed for this comparison amount to 229,539 h/cpu (26.2 years/cpu).
+With all combinations of GAs options, 21~630 optimizations were performed on an Intel Xeon based HPC cluster with 96 cpu, running Linux RedHat.
+Such assessment was not possible on the whole archive length, and had to be performed on a reduced calibration period: five years, from 1998 to 2002, but looking for analog dates on a 48 years period (1961-2008).
+The total resources needed for this comparison amount to 229~539 h cpu (26.2 yr cpu).
 One should remember that these intensive resources were needed in order to assess multiple combinations of GAs options in order to provide recommendations.
@@
 Figure \ref{fig:gas_evolution_good} shows the evolution of the score of the best individuals over generations for 10 optimizations processed for a given configuration of GAs (same operators options).
-7 out of 10 optimizations converged to the global optimum (dashed line at the top of the plot in Fig.
+Seven out of 10 optimizations converged to the global optimum (dashed line at the top of the plot in Fig.
 \ref{fig:gas_evolution_good}) after 40 to 55 generations, which is not the best performance we observed later on.
@@
 
-Every combination of 6 options for the couples selection (Fig.
+Every combination of six options for the couples selection (Fig.
 \ref{fig:operator_selectcoupl_score}) and 21 for the chromosome crossover operators (Fig.
 \ref{fig:operator_crossover_score}) were evaluated, along with variants of the other operators.
-This resulted in 1,008 combinations, requiring 10,080 optimizations.
+This resulted in 1~008 combinations, requiring 10~080 optimizations.
 
@@
 \ref{fig:operator_selectcoupl_score}).
-Overall, the tournament selection with 3~candidates was slightly superior to others, along with the roulette wheel weighting.
+Overall, the tournament selection with three candidates was slightly superior to others, along with the roulette wheel weighting.
 This last one was however a bit less effective in terms of convergence and number of evaluations (not shown).
@@
 As for crossover operators (Fig.
-\ref{fig:operator_crossover_score}), binary-like crossover (especially with 2 points of intersection, whether $\beta$ is shared or not) was a bit better than the others, especially in terms of convergence (not shown).
+\ref{fig:operator_crossover_score}), binary-like crossover (especially with two points of intersection, whether $\beta$ is shared or not) was a bit better than the others, especially in terms of convergence (not shown).
 
@@
 Some optimizations without any mutation were also performed as a reference.
-Along with variants of the other operators \citep[see][for the details]{Horton2012a}, this resulted in 660 combinations (so 6,600 optimizations).
+Along with variants of the other operators \citep[see][for the details]{Horton2012a}, this resulted in 660 combinations (so 6~600 optimizations).
 
@@
 The convergence analysis \citep[see][]{Horton2012a} allowed to highlight three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
-Thus, different optimizations (an additional 4,950) were further performed using variants of these 3 operators (Fig.
+Thus, different optimizations (an additional 4~950) were further performed using variants of these three operators (Fig.
 \ref{fig:operator_mutation_score_atmlevel}-\ref{fig:operator_mutation_score_r4}).
@@
 \ref{fig:operator_mutation_score_atmlevel}).
-The optimizer could also choose the 2 pressure levels of the atmospheric circulation analogy (method with a single level of analogy).
+The optimizer could also choose the two pressure levels of the atmospheric circulation analogy (method with a single level of analogy).
 The resulting CRPSS performance score (section \ref{sec:am}) was obviously superior to the one obtained by the sequential calibration (bottom line on Fig.
@@
 \ref{fig:operator_mutation_score_rhoneamont}), in order to assess eventual dependencies of the operators with the predictand.
-Even though differences can be observed in Fig.
+Even though differences can be observed with Fig.
 \ref{fig:operator_mutation_score_atmlevel}, it is globally the same options that perform better.
@@
 The results showed generally higher scores (Fig.
-\ref{fig:operator_mutation_score_r4}), demonstrating the success of the optimizer to take advantage of this new degree of freedom, and its ability to handle optimization of 3 analogy levels jointly.
+\ref{fig:operator_mutation_score_r4}), demonstrating the success of the optimizer to take advantage of this new degree of freedom, and its ability to handle optimization of three analogy levels jointly.
 Again, the most relevant options were globally the same.
@@
 A bigger population led to better results, but also to longer optimizations: the required number of evaluation, and thus the required time, was approximately proportional to the population size.
-Thus, if the population size doubled, the time required for the optimization also nearly doubled (e.g., for a 5 years calibration period, approximately 4~h/cpu were needed when $N = 50$, and 14~h/cpu when $N = 200$).
-The optimal size seems to depend on the complexity of the AM to optimize: a more complex AM (ie.
-with more degrees of freedom) requires a bigger population size.
+Thus, if the population size doubled, the time required for the optimization also nearly doubled (e.g., for a five years calibration period, approximately 4~h cpu were needed when $N = 50$, and 14~h cpu when $N = 200$).
+The optimal size seems to depend on the complexity of the AM to optimize: a more complex AM (i.e., with more degrees of freedom) requires a bigger population size.
 A rule of thumb based on a limited number of case studies (not shown here) is provided hereafter:
@@
 \begin{itemize}
-	\item $N\approx100$ for very simple AM implementations (1 level of analogy with 2 pressure levels),
-	\item $N\approx200$ for a slightly more complex AM (1 level of analogy with 4 pressure levels, or 2 level of analogy with less pressure levels),
-	\item $N\approx500$ for significantly more complex AMs (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the moisture analogy).
+	\item $N\approx100$ for very simple AM implementations (one level of analogy with two pressure levels),
+	\item $N\approx200$ for a slightly more complex AM (one level of analogy with four pressure levels, or two level of analogy with less pressure levels),
+	\item $N\approx500$ for significantly more complex AMs (two to three levels of analogy with four pressure levels for the atmospheric circulation, and two to four levels for the moisture analogy).
 \end{itemize}
@@
 	\setlength\itemsep{-4px}
-	\item 1x non-uniform, $p_{mut}=0.05$, $G_{m,r}=50$, $\omega=0.1$
-	\item 1x non-uniform, $p_{mut}=0.05$, $G_{m,r}=100$, $\omega=0.1$
-	\item 1x non-uniform, $p_{mut}=0.1$, $G_{m,r}=100$, $\omega=0.1$
-	\item 1x multi-scale,  $p_{mut}=0.1$
-	\item 2x chromosome of adaptive search radius
+	\item once the non-uniform mutation, with $p_{mut}=0.05$, $G_{m,r}=50$, $\omega=0.1$
+	\item once the non-uniform mutation, with $p_{mut}=0.05$, $G_{m,r}=100$, $\omega=0.1$
+	\item once the non-uniform mutation, with $p_{mut}=0.1$, $G_{m,r}=100$, $\omega=0.1$
+	\item once the multi-scale mutation, with  $p_{mut}=0.1$
+	\item twice the chromosome of adaptive search radius
 \end{itemize}
@@
 In order to illustrate the gain achievable by GAs on an AM, precipitation prediction for the Southeast ridges region of the alpine Rh\^{o}ne catchment (Fig.
-\ref{fig:map}) was optimized for the whole calibration period (40 years in the 1961-2008 period, leaving out 8 years for validation), instead of the smaller 5-years period.
-
-The optimizer could select the geopotential height at 4 pressure levels, at any time of the day, on unconstrained spatial windows.
+\ref{fig:map}) was optimized for the whole calibration period (40 years in the 1961-2008 period, leaving out 8 years for validation), instead of the smaller five years period.
+
+The optimizer could select the geopotential height at four pressure levels, at any time of the day, on unconstrained spatial windows.
 Moreover, a weighting was introduced in the combination of the criteria processed on each pressure level \citep[such as][]{Horton2012a, Junk2015}.
@@
 
-The performance (CRPSS) of the reference method calibrated by means of the sequential procedure amounts to 32.00\%, with a 0.95 confidence interval (assessed by bootstrapping on 10,000 samples) of (29.21\%; 34.94\%).
+The performance (CRPSS) of the reference method calibrated by means of the sequential procedure amounts to 32.00\%, with a 0.95 confidence interval (assessed by bootstrapping on 10~000 samples) of (29.21\%; 34.94\%).
 The method optimized by means of GAs reached a performance of 37.62\%, with a 0.95 confidence interval of (35.21\%; 40.11\%).

### 2016-09-22 AtmoSwing - GMD/template.tex
Adding todos.
Minor improvements of the AtmoSwing paper.

@@
 % Hydrology and Earth System Sciences (hess)
+
+% TODO: read again
+% TODO: add more references
+% TODO: remove appendix ?
+% TODO: add all reanalysis datasets
+% TODO: add forecasts performances
+% TODO: review: While the authors show a good command of the Analogue Technique and of its applications, it is not clear from the manuscript which predictors should be used for the forecast of alpine precipitations.
+The authors present two sets, that of Bontron (2004) and of Horton et al.
+(2012).
+An evaluation (or a summary, if already done elsewhere) of the relative merits of the two methods should be shown,
+% TODO: relative merits of the metrics used (S1 or RMSE) are not explained
+% TODO: article doesn't present any evaluation or validation of the precipitation fields/data or alerts provided by AtmoSwing
+% TODO: the article is too general and descriptive and should detail the specifics of the present implementation of the Analogue Technique.
+% TODO: Another point (though not a reason for rejection) is about the practical use for forecasters: as the authors rightly pointed out, it is impossible to apply analogue techniques directly on NWP forecasts of meteorological parameters, since the analogues are provided by other models, with different resolution.
+A coherent (I.e with the same model version and resolution) and long enough period of NWP forecasts can be hard to come by, especially for rare episodes.
+This may restrain the practical use of AtmoSwing for operational precipitation and flood forecasts.
+Maybe the authors could comment on that?
 
@@
 
-\title{AtmoSwing (v1.4): Analog Technique Model for Statistical Weather downscalING}
+\title{AtmoSwing (v1.4): Analog Technique Model for Statistical Weather forecastING and downscalING}
 
@@
 
-The Analog Method allows predicting local meteorological variables of interest (predictand), such as the daily precipitation, on the basis of synoptic variables (predictors).
-It relies on the fact that similar meteorological influences are likely to result in similar local effects.
+Analog methods (AMs) allow predicting local meteorological variables of interest (predictand), such as the daily precipitation, on the basis of synoptic variables (predictors).
+They rely on the fact that similar meteorological influences are likely to result in similar local effects.
 This statistical relationship is thus based on archives of observed data, and used in order to operationally forecast the coming days, or to evaluate future conditions under a changing climate.
 
-AtmoSwing is an open source software that implements the Analog Method in a very flexible way, so that different variants can be handled dynamically, by parameterization through XML files.
+AtmoSwing is an open source software that implements different AM variants in a very flexible way, so that different variants can be handled dynamically, by parameterization through XML files.
 It is made of 3 tools: the Forecaster to perform operational forecasts, the Viewer to display the results, and the Optimizer to establish the relationship between the predictand and predictors.
@@
 
-In addition to precipitation prediction, the Analog Method (AM), or an equivalent, was also used for short to medium term prediction of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+In addition to precipitation prediction, analog methods (AMs), or equivalent, were also used for short to medium term prediction of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
 \citet{Guilbaud1997} performed a literature review about the use of the AM in long-term forecasting and identified operational applications for monthly forecasts in many countries, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal forecasts: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.
 
-In operational forecasting, it has been used mainly by practitioners, notably hydropower companies \citep{Desaint2008a,BenDaoud2009,Obled2014} or flood forecasting services in France and Switzerland \citep{Marty2010,GarciaHernandez2009b,Horton2012}.
-It should however not be considered as a substitute for Numerical Weather Prediction (NWP) models, but as a complement in order to get a fast and partly independent forecast that is known to be accurate several days in advance.
-It therefore enriches the analysis of a potential critical situation for flood forecasting, for example, and is very interesting in early warning.
+In operational forecasting, they have been used mainly by practitioners, notably hydropower companies \citep{Desaint2008a,BenDaoud2009,Obled2014} or flood forecasting services in France and Switzerland \citep{Marty2010,GarciaHernandez2009b,Horton2012}.
+They should however not be considered as a substitute for Numerical Weather Prediction (NWP) models, but as a complement in order to get a fast and partly independent forecast that is known to be accurate several days in advance.
+They therefore enrich the analysis of a potential critical situation for flood forecasting, for example, and are very interesting in early warning.
 
@@
 
-\section{The Analog Method}
+\section{Analog methods}
 \label{sec:method}
@@
 
-To get access to the frozen version at the time of writing (v1.4.2), the following address can be used:
+To get access to the frozen version at the time of writing (v1.4.3), the following address can be used:
 
 \begin{itemize}
-	\item bitbucket.org/atmoswing/atmoswing/commits/tag/1.4.2
+	\item bitbucket.org/atmoswing/atmoswing/commits/tag/1.4.3
 \end{itemize}

### 2016-09-22 Genetic algorithms - MWR/corrections/5 - Elsevier editing/20160914121105.681-template_corrected.tex
Elsevier english edition.

%% Version 4.3.2, 25 August 2014
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template.tex --  LaTeX-based template for submissions to the 
% American Meteorological Society
%
% Template developed by Amy Hendrickson, 2013, TeXnology Inc., 
% amyh@texnology.com, http://www.texnology.com
% following earlier work by Brian Papa, American Meteorological Society
%
% Email questions to latex@ametsoc.org.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Start with one of the following:
%% DOUBLE-SPACED VERSION FOR SUBMISSION TO THE AMS
\documentclass{ametsoc}

%% TWO-COLUMN JOURNAL PAGE LAYOUT---FOR AUTHOR USE ONLY
%\documentclass[twocol]{ametsoc}

\usepackage{gensymb}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% To be entered only if twocol option is used

\journal{mwr}

%  Please choose a journal abbreviation to use above from the following list:
% 
%   jamc     (Journal of Applied Meteorology and Climatology)
%   jtech     (Journal of Atmospheric and Oceanic Technology)
%   jhm      (Journal of Hydrometeorology)
%   jpo     (Journal of Physical Oceanography)
%   jas      (Journal of Atmospheric Sciences)	
%   jcli      (Journal of Climate)
%   mwr      (Monthly Weather Review)
%   wcas      (Weather, Climate, and Society)
%   waf       (Weather and Forecasting)
%   bams (Bulletin of the American Meteorological Society)
%   ei    (Earth Interactions)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Citations should be of the form ``author year''  not ``author, year''
\bibpunct{(}{)}{;}{a}{}{,}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% To be entered by author:

%% May use \\ to break lines in title:

\title{Global Optimization of an Analog Method by Means of Genetic Algorithms}

%%% Enter authors' names, as you see in this example:
%%% Use \correspondingauthor{} and \thanks{Current Affiliation:...}
%%% immediately following the appropriate author.
%%%
%%% Note that the \correspondingauthor{} command is NECESSARY.
%%% The \thanks{} commands are OPTIONAL.

    %\authors{Author One\correspondingauthor{Author One, 
    % American Meteorological Society, 
    % 45 Beacon St., Boston, MA 02108.}
% and Author Two\thanks{Current affiliation: American Meteorological Society, 
    % 45 Beacon St., Boston, MA 02108.}}

\authors{Pascal Horton\correspondingauthor{Pascal Horton, University of Bern, Hallerstrasse 12, 3012 Bern, Switzerland.}\thanks{Current affiliation: Institute of Geography \& Oeschger Centre for Climate Change Research, University of Bern, Switzerland}}

%% Follow this form:
    % \affiliation{American Meteorological Society, 
    % Boston, Massachusetts.}

\affiliation{University of Lausanne, Lausanne, Switzerland}

%% Follow this form:
    %\email{latex@ametsoc.org}

\email{pascal.horton@alumnil.unil.ch}

%% If appropriate, add additional authors, different affiliations:
    %\extraauthor{Extra Author}
    %\extraaffil{Affiliation, City, State/Province, Country}

\extraauthor{Michel Jaboyedoff}
\extraaffil{University of Lausanne, Lausanne, Switzerland}

%% May repeat for a additional authors/affiliations:

%\extraauthor{}
%\extraaffil{}

\extraauthor{Charles Obled}
\extraaffil{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ABSTRACT
%
% Enter your abstract here
% Abstracts should not exceed 250 words in length!
%
% For BAMS authors only: If your article requires a Capsule Summary, please place the capsule text at the end of your abstract
% and identify it as the capsule. Example: This is the end of the abstract. (Capsule Summary) This is the capsule summary.

\abstract{Analog methods are based on a statistical relationship between synoptic meteorological variables (predictors) and local weather (predictand, to be predicted). This relationship is defined by several parameters, which are often calibrated by means of a semi-automatic sequential procedure. This calibration approach is fast, but has strong limitations. It proceeds through successive steps, and thus cannot handle all parameters dependencies. Furthermore, it cannot automatically optimize some parameters, such as the selection of pressure levels and temporal windows (hours of the day) at which the predictors are compared.
In order to overcome these limitations, the global optimization technique of genetic algorithms is considered, which can jointly optimize all parameters of the method, and get closer to a global optimum, by taking into account the dependencies of the parameters. Moreover, it can objectively calibrate parameters that were previously assessed manually, and can take into account new degrees of freedom.
However, genetic algorithms must be tailored to the problem under consideration. Multiple combinations of algorithms are assessed, and new combinations are developed (e.g., the \textit{chromosome of adaptive search radius}, which is found to be very robust), in order to provide recommendations regarding the use of genetic algorithms for optimizing several variants of analog methods. A global optimization approach provides new perspectives for the improvement of analog methods, and for their application to new regions or new predictands.
}

\begin{document}

%% Necessary!
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MAIN BODY OF PAPER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

%% In all cases, if there is only one entry of this type within
%% the higher level heading, use the star form: 
%%
% \section{Section title}
% \subsection*{subsection}
% text...
% \section{Section title}

%vs

% \section{Section title}
% \subsection{subsection one}
% text...
% \subsection{subsection two}
% \section{Section title}

%%%
% \section{First primary heading}

% \subsection{First secondary heading}

% \subsubsection{First tertiary heading}

% \paragraph{First quaternary heading}

\section{Introduction}
\label{sec:intro}

Analog methods (AMs) rely on the hypothesis that similar situations, in terms of atmospheric circulation, are likely to result in similar local weather conditions \citep{Lorenz1956, Lorenz1969, Duband1970, Bontron2005}. These methods consist of sampling a certain number of past situations, based on different synoptic-scale meteorological variables (predictors), in order to construct a probabilistic prediction for a local weather variable of interest (predictand). Some common usages of AMs are for operational precipitation forecasting \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Hamill2015b, BenDaoud2016}, or more recently for precipitation downscaling in a climate perspective \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015}. However, AMs or equivalent methods are also employed to predict temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectories of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.

Although the method is rather simple, it contains several parameters to be optimized, such as the choice of the predictor variables, pressure levels and temporal windows (hours of the day) at which the predictors are compared along with the spatial domains used for the comparison, the analogy criteria (distance measure), and finally the number of analog situations to retain.

AMs must be adapted to every new considered region because the leading meteorological influences may be location-specific. Even the selection of the pressure levels and the temporal windows should be reconsidered, if not the predictor variable itself. Thus, before being applied in a forecasting or downscaling context, AMs must be calibrated for the given region, which is performed here in the perfect prognosis framework \citep{Klein1963}, in line with the majority of previously cited AM calibration procedures for precipitation predictions \cite[with the exception of][]{Hamill2006,Hamill2015b}.

A common approach to optimizing this method is by means of a semi-automatic sequential calibration procedure, which was developed by \citet{Bontron2004}, and is also described in \citet{BenDaoud2016} and extended by \citet{Radanovics2013}. This determines some parameters of the method sequentially for each consecutive analogy level (e.g., on the atmospheric circulation or on a moisture index). This begins with a manual selection of the meteorological variables (e.g., geopotential height and relative humidity), the pressure levels, the temporal windows, and the initial analog numbers. Then, the spatial window at which the predictors are compared is optimized through an iterative growth of the domain, and the number of analogs is finally reassessed. A succeeding level of analogy can then be introduced, and its spatial window be optimized. The parameters of the preceding levels of analogy are not reassessed, except for the number of analog situations to preserve.

Thus, the sequential calibration procedure allows the optimization of a limited number of parameters (spatial windows and analog numbers), but the selection of predictor variables, pressure levels, and temporal windows must still be made manually. Testing multiple combinations of these presents a very combinatorial problem, which quickly becomes cumbersome, especially when considering multiple predictors within the same level of analogy. Thus, optimizing AMs by means of this sequential technique is laborious if little knowledge is available regarding the predictor-predictand relationship or the leading meteorological influences. Indeed, many combinations of parameters (predictor variables, pressure levels, and temporal windows) must be assessed. Moreover, proceeding to the optimization sequentially ignores potential dependencies between the parameters of the method, whether they are within a single level of analogy or between multiple levels, which could lead to another configuration if the parameters were calibrated together. Thus, there is a high risk of ending in a local optimum, and this cannot be avoided.

When creating this sequential calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters, and wrote: ''\textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent. We will present our results by first searching the best variable (e.g., selection of the pressure level and the temporal window for the geopotential height) on a chosen spatial window, and next, the best window for the chosen variable. However, even by repeating the process, are we sure to obtain the optimal combination?}'' Later in his work, he also wrote: ''\textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution}.'' \citet{Bliefernicht2010} has also confronted the combinatorial issue for the parameters of AMs, and concluded that one must be an expert in order to have a sense of their respective influence, sensitivity, and nonlinear interactions. When calibrating an AM, \citet{BenDaoud2010} also stated that ''\textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously}.'' The simultaneous calibration of all parameters has not been undertaken so far.

Another optimization strategy, proposed by \citet{Junk2015}, allows for an automatic calibration of weights applied to the different predictors when processing the analogy criteria (distance function). Their strategy consists of a brute-force assessment of all possible combinations. This approach is possible in their implementation, because predictors are considered at a unique point (interpolated to the location of interest), at fixed hours, and at preselected pressure levels, leaving only the weights to be optimized. In the presently employed AM (described in Section \ref{sec:am}), the number of parameters to optimize makes it impossible to proceed with a brute-force strategy.

In order to overcome these limitations, two optimization techniques have been assessed. First, \citet{Horton2012a} assessed the ability of the method of \citet{Nelder1965a}, based on a simplex algorithm. This technique did not provide satisfying results, and failed to converge toward a unique solution. The parameter space of the AMs can be very complex, and is inappropriate for a linear optimization technique. Thus, global optimization techniques are likely to be necessary in order to calibrate most AM variants, as they can optimize all parameters of all analogy levels simultaneously. In addition, they can avoid the systematic manual assessments of all pressure levels and temporal windows. Finally, they allow the testing of new degrees of freedom in AMs. The relevance of genetic algorithms (GAs) is described here, which does not exclude that other global optimization techniques could also work. Although using GAs to optimize AMs may be computationally intensive, once an AM is calibrated its employment in real-time operations or climate downscaling is very fast and lightweight.

This paper specifically describes how GAs should be used in order to successfully optimize several AMs. Indeed, the variants of Gas are numerous, and always need to be tailored to the addressed problem. This requires intensive and systematic comparisons of operators and options, in order to identify the key factors influencing the optimization, and the respective sensitivity of the options. Such analyses are presented here, resulting in recommendations for the use of GAs to optimize several AM implementations. The in-depth analysis of the benefits of such an approach in a specific case study will be the topic of a forthcoming paper.

This document begins by presenting the area of the case study and the relevant data (Section \ref{sec:case_study_data}), the considered AM variants (Section \ref{sec:am}), and the assessed GA options (Section \ref{sec:gas}). Comparative analyses of these options are presented in Section \ref{sec:assessment}, leading to the recommendations formulated in Section \ref{sec:use}, and finally the conclusions presented in Section \ref{sec:conclusions}.

\section{Case study and data}
\label{sec:case_study_data}

The area of the study is the alpine upper Rh\^{o}ne catchment in Switzerland (Fig.\ \ref{fig:map}). The altitude ranges from 372 to 4634~m.a.s.l., and the area is 5524~km$^{2}$. Based on various climatological analyses \cite[see][for the details]{Horton2012a}, the gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}).

This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project, which aims to provide real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}. AMs are used to provide real-time probabilistic precipitation forecasts, based on NWP outputs.

\subsection{Data}
\label{sec:data}

AMs rely on two types of data: predictors, which are meteorological variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series that is to be predicted.

When working in the perfect prognosis framework \citep{Klein1963}, the meteorological archive from which the predictors are extracted is usually a reanalysis dataset. Conversely, other applications of AMs to wind forecasting are based on a model output statistics method \citep[MOS, see][]{Glahn1972}, and thus employ forecast archives or reforecast products \citep[e.g.,][]{DelleMonache2013, DelleMonache2011, Alessandrini2015, Junk2015, Junk2015c}.

In the present study, the NCEP-NCAR reanalysis I dataset \citep[six-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} is employed, but this could be replaced with any other reanalysis dataset. This dataset is relatively old, although it is still widely used, and better results may be expected with more recent datasets. However, we can safely assume that if an optimization technique works for this reanalysis dataset, it will also work for an improved one.

Here, the predictand (which is to be predicted) is the daily precipitation (0540~UTC to 0540~UTC the following day) measured at the MeteoSwiss network of stations in the catchment of interest. The time series from every available gauging station were averaged over subregions of approximately 500~km$^{2}$ \citep[see][for details]{Horton2012a} in order to smooth local effects \citep{Obled2002, Marty2012}. The time series must be split into calibration and independent validation periods.

\section{The considered analog method}
\label{sec:am}

AMs are based on the principle that two similar synoptic situations may result in similar local effects \citep{Lorenz1956, Lorenz1969}. Thus, they consist in searching for a certain number of past situations in a meteorological archive that present similar properties for chosen predictors, according to an analogy criteria, in order to extract the observed values of the local weather variable of interest from another archive (predictand time series, see Section \ref{sec:case_study_data}\ref{sec:data}). Based on these analog observations, the conditional empirical distribution to be considered as the probabilistic prediction for the target day (the day one wishes to predict) is constructed.

Predictors for precipitation predictions can be varied. For example, the geopotential height at different pressure levels and temporal windows, or humidity variables \citep[see][for a more detailed list of predictors]{BenDaoud2016}. This method often contains several levels of analogy, which constitute of successive subsamplings on predictors of different natures (e.g., atmospheric circulation, moisture variables, vertical motion, and air temperature).

The basis of the AM implementation considered here is the following \citep[the same approach as][]{Guilbaud1997, Bontron2005, Marty2012, Horton2012, Radanovics2013, Chardon2014, Dayon2015, BenDaoud2016}:

\begin{enumerate}
	\item Preselection: To cope with seasonal effects, $n_{0}$ candidate dates are extracted from the archive within a period of four months centered around the target date, for every year of the archive. Alternatively, the candidate dates can be selected based on similar air temperatures \citep[see][]{BenDaoud2016}.

	\item First level of analogy: $n_{1}$ dates are selected out of the preselected $n_{0}$, by means of an analogy ranking. The first level of analogy for precipitation prediction is often based on the atmospheric circulation. The similarity between the atmospheric circulation of the target date and the candidate situations is assessed in terms of the geopotential height (at specific pressure levels, such as 500 and 1000~hPa, and over a certain spatial window, e.g., 12~h and 24~h) by means of the S1 criteria \citep[Eq. (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients over a defined spatial window. Various studies have found the S1 criteria to be more relevant than Euclidean distances for pressure fields \citep{Wilson1980, Woodcock1980, Guilbaud1998, Bontron2004}.

	\begin{equation}
	\label{eq:S1}
	S1=100 \frac {\displaystyle \sum_{i} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
	{\displaystyle \sum_{i} max( \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert ) }
	\end{equation}
	where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points from the grid of the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation. The differences are processed separately in both directions. The smaller the S1 values, the more similar the pressure fields are.

	The $n_{1}$ dates with the lowest S1 values are considered as analog situations, in terms of the atmospheric circulation, for the target day. The analog number $n_{1}$ is a parameter to be calibrated.

	\item Subsequent level(s) of analogy: Beyond the similarity of airflows, one may look for analogies in other variables of interest, such as moisture variables. Therefore, the $n_{1}$ analogs are subsampled once more on the basis of another variable, in order to obtain a lower number of analog dates, $n_{2}$. When the predictor is not a pressure field, the analogy criteria usually represents absolute distances to the mean absolute error (MAE) or root mean squared error (RMSE), with the latter being most often employed.

	A second level of analogy, based on thermodynamic variables, was introduced by \citet{Vallee1986} and \citet{Gibergans-Baguena2007}. After a systematic assessment of variables, \citet{Bontron2004} pointed out that a moisture index consisting of the product of relative humidity at 850~hPa and total precipitable water achieves the best performance. This index does not represent an actual physical quantity, but expresses the water content of the air column and its proximity to saturation.

	This process can be repeated by subsampling a decreasing number of analog dates, $n_{i}$, according to various meteorological variables.

	\item Probabilistic prediction: Then, the daily observed amounts of precipitation for the $n_{i}$ resulting dates provide the empirical conditional distribution, considered as the probabilistic forecast for the target day.

\end{enumerate}

The parameters to be defined (manually or automatically), for every level of analogy, are as follows:

\begin{itemize}
	\item The selection of meteorological variables (predictors), containing synoptic scale information, and having a direct or indirect dependency with the target predictand.
	\item The pressure level, or height, at which the predictor is selected.
	\item The temporal window is the hour(s) of the day at which the predictors are considered.
	\item The spatial window is the domain on which predictors are compared. The ideal size of this area is that which maximizes the useful information and minimizes noise.
	\item The analogy criterion, needed to compare the variables on the chosen spatial and temporal windows, is a distance measure, used to rank observed situations according to their degree of similarity with the target situation.
	\item Eventual weights between the predictors \cite[e.g.,][]{Horton2012a, Junk2015}.
	\item The ideal number of analog situations, which is the best compromise in order to take into account local variability and maximize useful synoptic information \citep{Bontron2004}.
\end{itemize}

In order to calibrate the method, the continuous ranked probability score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} is often employed to assess the performances of AMs \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}. This allows the evaluation of predicted cumulative distribution functions $F(y)$. For example, of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$. The better the prediction, the smaller the score. The mean CRPS of a prediction series of length $l$ can be written as follows:

\begin{equation}
\label{eq:CRPS}
CRPS = \frac{1}{l} \sum_{i=1}^{l} \left\{  \int_{-\infty}^{+\infty} \left[ F_{i}(y)-H_{i}(y-y_{i}^{0})\right]^{2} dy \right\} 
\end{equation}
where $H(y-y_{i}^{0})$ is the Heaviside function, which is zero when $y-y_{i}^{0}<0$ and has a value of one otherwise. The mean CRPS is averaged over the calibrations for the respective validation periods.

In order to compare the value of the score with regard to a reference, one often considers its skill score expression, and employs the climatological distribution of daily precipitation as the reference. The CRPSS (\textit{continuous ranked probability skill score}) is thus defined as follows:

\begin{equation}
\label{eq:CRPSS}
CRPSS = 1-\frac{CRPS}{CRPS_{r}}
\end{equation}
where $CRPS_{r}$ is the score value for the reference. An increase in the CRPSS indicates a better prediction.

\section{Assessed genetic algorithm variants}
\label{sec:gas}

Genetic algorithms \citep[GAs,][]{Holland1992b, Goldberg1989} are part of the family of evolutionary algorithms \citep{Back1993b, Schwefel1993}, which are inspired by some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection. Unlike linear or local optimizations, GAs seek the global optimum on complex surfaces, theoretically without restriction, but with no guarantee of reaching it \citep{Haupt2004}. The objective function to be optimized (often named the fitness function in this context) can be of various types \citep{Joines1996a}, but GAs must be adapted in order to perform optimally.

A key element of the configuration of GAs is to determine the correct balance between exploration and exploitation \citep{Back1992a, Smith1997a}. Exploration is characterized by a relatively high probability of assessing the regions of the parameter space that have not yet been visited. This probability must be sufficiently large at the beginning of the optimization, so that the algorithm is capable of identifying the region where the global optimum is likely to be located. Exploitation is characterized by a local search in an area of interest, and generally makes small movements. The latter aims at finding small improvements at the end of the optimization.

\subsection{Structure and operators}
\label{sec:gas:operators}

GAs optimize a population of $N$ individuals. Each individual contains a chromosome, which here is a vector of the AM parameters. Genes are the individual parameters constituting the chromosome. These can be categorical (e.g., choice of the meteorological variable), discrete (e.g., number of analog dates to select), or continuous.

There are numerous implementation variants of GAs, which are often optimal for a given problem \citep{Hart1991a, Schraudolph1992a}. The differences are found in the implementation of the operators, through significantly different algorithms, which has an important effect on the results \citep{Gaffney2010a}. Here, operators are defined as the mechanisms that modify the values of the genes, to try to bring individuals (or chromosomes) closer to an optimum of the fitness function. The structure of the method (Fig. \ref{fig:structure_gas}) that results from the work of \citet{Holland1992b} is common to most applications \citep{Back1993b}, and consists of the following steps. (1) A population of $N$ individuals (parameter sets of the AM to be optimized) is randomly generated, which constitutes the initial population. The fitness (performance score or objective function) of every individual is assessed. (2) A natural selection algorithm is applied, after which only the best individuals remain. This constitutes the intermediate generation (IG), from which (3) couples are formed according to given rules. Then, (4) these couples proceed to the reproduction or chromosome crossover stage, to mix their genes according to the selected operator version. New children are generated, in order to refill the IG back to $N$ individuals. (5) Parents and children are then subjected to mutation, where some genes are randomly changed. Finally, (6) the new generation is then re-assessed, with the best individual restored if degraded. Then, (7) according to the ending criteria, the optimization either ends or begins again for another iteration.

All of the considered operators and their options are described in the following sections (only briefly for operators of less importance). Many other operators exist, but only those that are evaluated are described here.

\subsubsection{Genesis of the population}

The most current version of the initial population generation is a random initialization based on a uniform sampling. The size $N$ of the population is often a compromise between the computation time and the quality of the solution. The chosen $N$ must allow sufficient sampling of the solutions field \citep{Beasley1996a}, and thus should vary as a function of the chromosome size (i.e., the number of genes or parameters to be optimized).

\subsubsection{Natural selection}
\label{sec:gas:nat_selection}

Natural selection is performed on the basis of the objective function values. The selection allows for only a certain portion of the population to be kept, usually half ($N/2$), which can access the IG (with $N_{IG}$ members). Several techniques exist, such as:

\begin{itemize}
	\item $N_{IG}$-elitism \citep{Michalewicz1996}: Only the better half is preserved.

	\item Tournament selection \citep{Michalewicz1996, Zitzler2004a}: Two individuals are randomly selected, and the best of these is chosen, but with a certain probability.
\end{itemize}

\subsubsection{Selection of the couples}
\label{sec:gas:selection_couples}

Individuals of the IG can then reproduce, which begins with the selection of pairs (the parents). The techniques implemented in this study are the following:

\begin{itemize}
	\item Rank pairing: Individuals are gathered into pairs according to their ranks.

	\item Random pairing: Individuals are randomly selected, according to a uniform law.

	\item Roulette wheel selection \citep{Goldberg1989}: The selection probability assigned to each individual is proportional to their fitness, so that the most adapted individuals have a greater probability of reproduction. There are two weighting techniques. The first proceeds according to the rank, and the second according to the fitness value.

	\item Tournament selection: A number of individuals (two or three) are randomly picked, and the best is kept, with a certain probability. This operation is performed twice, once for each partner.
\end{itemize}

\subsubsection{Chromosome crossover}
\label{sec:gas:crossover}

Once the two parents have been selected for breeding, they combine their chromosomes and produce two children, bringing the number of individuals in the population back to $N$. The combination of chromosomes is carried out using a crossover operator, thereby generating two offspring that have characteristics derived from both parents. This allows the mixing of genes, and the potential accumulation of positive mutations. The evaluated crossover operators are the following:

\begin{itemize}
	\item Single-point crossover \citep{Goldberg1989}: The genes located after a randomly chosen point within the chromosome are exchanged between the two parents.

	\item Two-point crossover: Similar to the single-point crossover, but with two intersections defining the segments to be exchanged. This is considered to be more efficient than the previous method \citep{Beasley1993a}.

	\item Multiple-point crossover \citep{DeJong1975a}: A generalization of the previous method, with any number of crossover points up to the number of genes.

	\item Uniform crossover \citep{Syswerda1989}: For each gene of the chromosome, a random decision is made to exchange the values between the parents or not.

	\item Binary-like crossover \citep{Haupt2004}: In order to reproduce the behavior present in the canonical crossover algorithm, which is applied to a binary representation of the genes \citep{Goldberg1989, Goldberg1990a, Herrera1998a}, \citet{Haupt2004} propose an operator that combines the standard crossover operation with an interpolation approach. The genes located after a crossover point are exchanged, but the gene located at the intersection is modified according to the following:
	\begin{equation}
	\left\lbrace \begin{array}{l} 
	g_{o1,n} = g_{p1,n} - \beta (g_{p1,n} - g_{p2,n}) \\
	g_{o2,n} = g_{p2,n} + \beta (g_{p1,n} - g_{p2,n}) \\
	\end{array} \right.
	\label{eq:binary_like_crossover}
	\end{equation}
	where $g_{o1,n}$ and $g_{o2,n}$ are the $n$-th genes of the two new offspring, and $g_{p1,n}$ and $g_{p2,n}$ are those of the two parents. Furthermore, $\beta$ is a random value between zero and one, which can either be unique for the whole chromosome or can change for every gene.

	\item Blending method \citep{Radcliffe1991a}: In this approach, instead of exchanging the genes between the chromosomes after some crossover points, they are combined through a linear combination, also using a random value $\beta$.

	\item Linear crossover \citep{Wright1991a}: This widens the range of gene values, and produces three children from two parents.

	\item Heuristic crossover \citep{Michalewicz1996}: This is a variation of the blending method.

	\item Linear interpolation: Unlike the previous techniques, this one does not rely on crossover points, but rather on a linear interpolation on every gene of the couple. This also uses a random value $\beta$, which is the same for every gene.

	\item Free interpolation: This technique performs interpolation on each gene, like the previous one. However, in this case the weighting factor $\beta$ changes for each gene.

\end{itemize}

\subsubsection{Mutation}
\label{sec:gas:mutation}

The combination of strong genes through the chromosomes crossover operation is theoretically the most important operating mechanism in conventional GAs \citep{Holland1992b,Back1993b}. However, many studies identify the mutation process as the key operator, and crossovers as secondary \citep[see][]{Back1992a, Back1996a, Back1996b, Smith1997a, Deb1999, Costa2005a, Costa2007a}.

The mutation operator modifies some gene values. It adds diversity to the population, and prevents a freeze of the evolution, or a genetic drift to a local optimum. Thus, it makes the convergence to the global optimum theoretically possible \citep{Beasley1993a}, as it allows exploration beyond the current region of the parameters space by introducing new characteristics that were not present in the original population \citep{Haupt2004}.

The evaluated and developed mutation operators are listed in the following (equations are only provided for the operator versions that were found to be relevant, the reader may refer to the corresponding literature for details regarding the other options). These apply to genes formed of continuous or discrete variables, but not those that are categorical (e.g., the choice of the meteorological variable or analogy criterion). In the latter case, the random choice of a new value is always based on a uniform distribution, without a notion of distance in the parameters space.

\begin{itemize}
	\item Uniform mutation: The mutation rate ($p_{mut}$) is constant and equal for every gene of each individual. They each have the same probability of mutating. When a gene is selected for mutation, a new random value is assigned, according to a uniform law.

	\item Variable uniform mutation \citep{Fogarty1989}: A variable mutation rate over the generations was first suggested by \citet{Holland1992b}, and evaluated by \citet{Fogarty1989}. In most applications, the mutation rate decreases with each generation, in a deterministic and global (for all individuals) manner \citep{Back1992b}.

	\item Constant normal mutation: This method employs normal distributions to generate new values of the gene, based on an estimated standard deviation.

	\item Variable normal mutation \citep{Horton2012a}: With the same logic as the variable uniform mutation, a mutation operator is tested using a normal distribution with a variable mutation rate and standard deviation, which decrease linearly over generations. This operator has six parameters.

	\item Non-uniform mutation \citep{Michalewicz1996}: Two random numbers are chosen based on a uniform law: $r_{1}$, which determines the direction of the change, and $r_{2}$, which determines its magnitude. The new value of the gene is given by the following equation, according to a predefined number of generations:
	\begin{equation}
	g_{n}^{'} = 
	\left\lbrace \begin{array}{l l} 
	g_{n} + \left(b_{n}-g_{n}\right) r_{2} \varphi^{2} & if \; r_{1} < 0.5 \\
	g_{n} - \left(g_{n}-a_{n}\right) r_{2} \varphi^{2} & if \; r_{1} \geq 0.5 \\
	\end{array} \right.
	\label{eq:nonuniform_mutation}
	\end{equation}

	with

	\begin{equation}
	\varphi = 1 - \dfrac{G}{G_{m}}
	\end{equation}

	where $a_{n}$ and $b_{n}$ are the lower and upper bounds, respectively, of the $n$-th gene, $G$ is the present generation, and $G_{m}$ is the maximum number of generations.

	This operator is adapted for this application, which is not based on a predefined number of generations, by swapping $\varphi$ with $\varphi'$:

	\begin{equation}
	\varphi' = 1 - \min \left( \dfrac{G}{G_{m,r}}, 1 \right) \left(1-\omega\right)
	\end{equation}

	where $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a chosen threshold to maintain a minimum search radius when $G>G_{m,r}$. During the first generations, the extent of the exploration covers the entire parameters space. However, this area is reduced over generations, allowing the exploitation of local solutions.

	\item Individual adaptive mutation rate \citep{Back1992a}: Based on the ideas of evolution strategies \citep[see][]{Rechenberg1973, Schwefel1981}, \citet{Back1992a} introduced the concept of self-adaptive GAs. The idea is to distribute the control parameters within the individuals themselves, which partially decentralizes the control of the evolution. This allows for a reduction in the manual tuning of GAs, and introduces a notion of self-management. The first approach is the introduction of a mutation rate for each individual, which mutates itself under its own probability \citep{Back1992a}. Then, the resulting new rate is employed to mutate the genes of the individual. Thus, as this rate decreases it has a lower probability of being mutated itself. Mutations are performed according to a constant uniform distribution. The initial mutation rates are randomly chosen \citep{Back1992a}, and the method has no parameters. Other approaches exist for introducing a self-adaptation \citep[see][]{Smith1997a, Deb1999, Deb2001a}.

	\item Individual adaptive search radius: Based on the ideas of non-uniform mutation, we introduce a search radius to the approach of individual adaptive mutation rates. This search radius $r_{a}$, bounded between zero and one (relative to the parameter ranges), is also adaptive, and behaves similarly to the adaptive mutation rates. In order to separate its evolution from that of the mutation rate, its own value is also considered as a self-mutation rate for eventually mutating before being used as a normalized search radius. The value of a mutated gene is given by the following equation, which is a simplification of the non-uniform mutation:
	\begin{equation}
	g_{n}^{'} = 
	\left\lbrace \begin{array}{l l} 
	g_{n} + \left(b_{n}-g_{n}\right) r_{2} r_{a} & if \; r_{1} < 0.5 \\
	g_{n} - \left(g_{n}-a_{n}\right) r_{2} r_{a} & if \; r_{1} \geq 0.5 \\
	\end{array} \right.
	\label{eq:adaptive_search_radius_mutation}
	\end{equation}
	where $r_{1}$ and $r_{2}$ are randomly selected, such as in non-uniform mutation. Therefore, no external parameter is necessary.

	\item Chromosome of adaptive mutation rate \citep[or \textit{n adaptative mutation rate},][]{Back1992a}: Analogously to the individual adaptive mutation rate, this approach leaves the control of the evolution rate to individuals. The difference here is that each gene has a specific mutation rate. The main advantage is that the automatic tuning of the mutation can be made much more precise \citep{Smith1997a}. Thus, a second chromosome containing the mutation rate for each gene of the first chromosome is considered. The operations of mutation and self-mutation are similar to the case of the individual adaptive mutation rate, but proceed in a distributed manner within the chromosome. Moreover, the same crossover operations are applied to this new chromosome as to the main chromosome, and for the same crossing points. Thus, during an exchange of genes, children also inherit the mutation rates specific to each of these genes.

	\item Chromosome of adaptive search radius: In this operator, we combine the operations of the chromosome of adaptive mutation rate with the adaptive search radius approach. Similarly, an individual has three chromosomes. The first contains the values to be optimized, the second the distributed mutation rate, and the third the distributed search radius. Again, no external parameter is required.

	\item Multi-scale mutation: Finally, we develop another approach that is also based on the search radius concept. However, in this one the rate does not decrease with time. Methods based on a reduction of the mutation rate or radius simulate a transition from the exploration phase to the exploitation phase. Here, the idea is to test an approach that combines both exploration and exploitation during the whole optimization process. Thus, the search radius $r_{a}$ of Eq. (\ref{eq:adaptive_search_radius_mutation}) is considered as a random value for each individual, but restricted to four equiprobable values, 1, 0.5, 0.1, and 0.02, representing a range from full exploration to fine exploitation. The only external parameter is the mutation rate, which is fixed.

\end{itemize}

\subsubsection{Elitism}

The process of elitism is introduced after both natural selection and mutations. This ensures the survival of the best individual, so that a superior solution is never lost. After the natural selection operation, if the previous best individual has not been selected, then it is copied to the IG in place of a randomly selected individual. After mutation, if the previous best individual has mutated and its new version has a lower performance score than the original, then the original is also reinserted in the IG in place of a randomly selected individual.

\subsubsection{Ending the optimization}

The convergence check determines whether the solution is acceptable, and if the algorithm may stop. Here, the optimization is stopped if the best individual does not change for $x$ generations. This value should not be too low, in order to allow the algorithm to escape from local optima, and because the rate of improvement decreases with the progression of the optimization. Thus, it is common that the best individual does not evolve over several generations when getting closer to the global solution. A value of $x=20$ generations is chosen.

\subsection{Implementation and constraints}

GAs are computationally very intensive because they require many evaluations of the objective function. These assessments require some time (a couple of seconds each) in this application, as they require the calculation and assessment of a prediction for every day of the calibration period, which spans several decades. In order to reduce the computation time, the performance score of an individual, who has previously been evaluated and has not changed, is preserved. Thus, the score of each individual living in the selection is preserved until it mutates.

Because the calculation of the objective function for each member of the population of a generation is completely independent, they are processed in parallel on different CPUs. In order to perform optimizations for multiple time series, the use of a cluster is necessary.

Some constraints must be taken into account. For example, when a crossover or mutation operation results in a parameter value that is outside of the authorized bounds, this must be brought back within the limits. Moreover, the parameters are of different types: continuous, discrete, or categorical (e.g., the selection of the meteorological variable). New values resulting from the optimizer need to respect the type of data that they represent. Other constraints exist between the parameters, e.g., the temporal windows of the relative humidity and the precipitable water predictors must match when processing the moisture index.

\section{Assessment process and results}
\label{sec:assessment}

Choosing GA options, such as the mutation rate, population size, natural and selection, appears to be difficult given the high number of existing variants, each developed for a specific problem \citep{Haupt2004, Costa2007a}. Thus, different studies suggest significantly different configurations \citep{DeJong1975a, Grefenstette1986, Back1996a, Back1996b}.

In the present study, the choice of meteorological variables (predictors) was still performed manually. Then, GAs were required to jointly optimize, for all levels of analogy, (i) the spatial windows (position and size, which differ between the pressure levels), (ii) the temporal windows (hours of observation of the predictors), (iii) the number of analog situations, and (iv) the selection of the pressure levels (two in this case). The first experiments considered a single level of analogy (on the geopotential height, see Section \ref{sec:am}), and a second level (on moisture) was added later in Section \ref{sec:assessment}\ref{sec:assessment:results}\ref{sec:assessment:mutation}.

\subsection{Comparison process}

With the main goal of the present paper being to provide recommendations regarding the use of GAs to optimize different AM variants, a systematic procedure was adopted. The results are summarized in the following \citep[see][for the details]{Horton2012a}. In order to compare different configurations of GAs, a factorial design approach was applied, in a similar manner as in \citet{Costa2005a,Costa2007a} and \citet{Mariano2010a}. This allows the isolation of the effects of a parameter under different combinations of the other options.

In order to evaluate a combination of operators/options, 10 optimizations were processed per configuration of GAs. For all combinations of GA options, 21~630 optimizations were performed on an Intel Xeon based HPC cluster with 96 CPU, running Linux RedHat. Such an assessment was not possible on the whole archive length, and had to be performed on a reduced calibration period of five years from 1998 to 2002, while looking for analog dates over a 48 year period (1961-2008). The total resources required for this comparison amounted to 229~539 h CPU (26.2 years CPU). One should remember that these intensive resources were required in order to assess multiple combinations of GA options, in order to provide recommendations. Based on these, applying GAs to optimize AMs requires some computational power, but not as much (the required time is a function of the archive length, the population number, GA options, and the complexity of the AM to be optimized).

The performances were characterized by four indicators: (i) mean performance score: average of the final scores of the 10 optimizations, (ii) convergence: the number of optimizations that converged, (iii) number of generations: characterization of the convergence speed, and (iv) number of evaluations of the objective function: characterization of the required calculation time.

\subsection{Convergence}

After a first quick assessment, GAs were found to be successful in optimizing the considered AM implementations. Figure \ref{fig:gas_evolution_good} illustrates the evolution of the score of the best individual over progressive generations for the 10 optimizations processed for a given configuration of GAs (with the same operator options). Seven out of 10 optimizations converged to the global optimum (dashed line at the top of the plot in Fig. \ref{fig:gas_evolution_good}) after between 40 and 55 generations, which is not the best performance we will observe. The performance score of the sequential approach (bottom line) was quickly exceeded, without introducing any new parameters to the method (Fig. \ref{fig:gas_evolution_good}). The improvement was around 8.8\% in this case, which is substantial.

Even GA configurations that were later rejected, because they did not converge (Fig. \ref{fig:gas_evolution_bad}), performed significantly better than the sequential approach. GAs displayed a promising potential for optimizing AMs automatically, globally, and objectively.

\subsection{Results of the comparison}
\label{sec:assessment:results}

The results of the factorial design procedure illustrate the effect of an operator when its contribution is isolated from the other operators. This means that we analyzed the effects of a given operator for equivalent conditions (with the same settings for other operators), while assessing multiple combinations of these. This contribution was then summarized as a percentage of gain/loss with respect to the mean of all variants, for equivalent external conditions. For example, to evaluate the performance of the uniform crossover operator, its performance was compared to the average of all crossover operators, while retaining the same population size, same mutation, natural selection, and couples selection operators.

From the start of the assessments, the importance of the mutation operator was obvious \cite[see][for details]{Horton2012a}, and its leading influence on the optimization performance was evident. Its role is analyzed later, in Section \ref{sec:assessment}\ref{sec:assessment:results}\ref{sec:assessment:mutation}.

\subsubsection{Breeding operators}

Each combination of the six options for the couples selection (Fig. \ref{fig:operator_selectcoupl_score}) and 21 options for the chromosome crossover operators (Fig. \ref{fig:operator_crossover_score}) was evaluated, along with variants of the other operators. This resulted in 1008 combinations, requiring 10080 optimizations.

The performances of the couples selection operators were relatively similar (Fig. \ref{fig:operator_selectcoupl_score}). Overall, the tournament selection with three candidates performed slightly better than the others, along with the roulette wheel weighting. However, the latter was a little less effective in terms of convergence and the number of evaluations (not shown). The couples selection operator played no significant role in this application.

As for the crossover operators (Fig. \ref{fig:operator_crossover_score}), binary-like crossover (especially with two points of intersection, whether $\beta$ is shared or not) performed slightly better than the others, especially in terms of convergence (not shown).

\subsubsection{Mutation operator}
\label{sec:assessment:mutation}

Having identified the leading role of the mutation operator, the following sensitivity analysis focuses on it. The 10 different implementations (see Section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:mutation}) were tested with different options (Fig. \ref{fig:operator_mutation_score}), bringing the number of variations to 109. Some optimizations with no mutation were also performed as a reference. Along with variants of the other operators \citep[see][for details]{Horton2012a}, this resulted in 660 combinations (and so 6600 optimizations).

Figure \ref{fig:operator_mutation_score} presents the results of this analysis, and illustrates the important role of mutation on the optimization performance. Configurations without mutation (the last box in Fig. \ref{fig:operator_mutation_score}) achieved an inferior performance compared to most mutation operators, and the magnitude of this operator influence was significantly higher than those of the other options. The details of the analysis \citep[see][]{Horton2012a} indicate that the other reproduction operators seem to be of secondary importance. This observation is in line with the conclusions reached by several other authors (see Section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:mutation}).

The mutation operators based on variable normal or variable uniform laws performed particularly poorly here, and were difficult to configure. Many operators presented more or less similar performance scores, and required a variable amount of assessments. The convergence analysis \citep[see][]{Horton2012a} highlighted the three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation. Thus, further optimizations (an additional 4950) were performed, using variants of these three operators (Fig. \ref{fig:operator_mutation_score_atmlevel}-\ref{fig:operator_mutation_score_r4}).

The first analysis was the optimization of the precipitation prediction over a subcatchment (the Binn-Simplon region) in the Swiss Alps (Fig. \ref{fig:operator_mutation_score_atmlevel}). The optimizer also chose the two pressure levels of the atmospheric circulation analogy (this method has a single level of analogy). The resulting CRPSS performance score (see Section \ref{sec:am}) was obviously superior to that obtained using the sequential calibration (bottom line in Fig. \ref{fig:operator_mutation_score_atmlevel}). For most options, it also achieved slightly better results than the optimization without the selection of the pressure levels (dashed line). A clear breakthrough in the performance was not expected, as the former selection of pressure levels is the result of intensive comparative work \citep{Bontron2004}. However, this application demonstrates that when correctly configured, GAs can automatically and successfully choose the pressure levels. However, the automatic selection of the pressure levels significantly increased the difficulty for the GAs to converge to a unique solution, ideally the global optimum. A likely explanation for this is that the pressure levels were considered as categorical values within the optimization (sampled with a uniform law), and thus the approaches relying on a distance in the parameters space, such as the search radius, could not fully exploit the properties that made them efficient. However, even though the results exhibit a certain variability, most of them present very good performance scores, despite different selections of the AM parameters.

The same experiment was performed for another region (Swiss Chablais, see Fig. \ref{fig:map}), which is sensitive to other meteorological influences (Fig. \ref{fig:operator_mutation_score_rhoneamont}), in order to assess the eventual dependencies of the operators with the predictand. Even though differences can be observed with Fig. \ref{fig:operator_mutation_score_atmlevel}, the same options perform better globally.

Next, a second level of analogy was introduced (Fig. \ref{fig:operator_mutation_score_r2}), based on moisture variables (see Section \ref{sec:am}). The GAs had to optimize both levels of analogy (geopotential height and moisture index) simultaneously. Once again, the results were better than those for the sequential calibration (bottom line on Fig. \ref{fig:operator_mutation_score_r2}). Finally, a preselection of air temperature was added, instead of the fixed calendar window, as proposed by \cite{BenDaoud2016}. The results showed generally higher scores (Fig. \ref{fig:operator_mutation_score_r4}), demonstrating the success of the optimizer in taking advantage of this new degree of freedom, and its ability to handle the optimization of three analogy levels simultaneously. Again, the most relevant options were the same globally.

Following these various tests of the relevance of the mutation operators, the following advice can be presented (detailed options are provided in Section \ref{sec:use}\ref{sec:recommendations}):

\begin{itemize}

	\item \textit{Non-uniform mutation}: This operator performed well in terms of convergence, mainly when the number of parameters to optimize was rather low. However, the number of required evaluations can be fairly substantial. The main disadvantage of the non-uniform mutation is the number of parameters it requires, which are difficult to estimate a priori. The mutation rate was found to be more important than for the others. The difficulty is that its optimal value may be case-related.

	\item \textit{Chromosome of adaptive search radius}: Unlike in the above case, this proposed operator is very robust, as it requires no options and is auto-adapting. It is interesting to note that the insertion of an extra chromosome representing the search radius resulted in a better performance than other self-adaptive operators (such as the chromosome of adaptive mutation rate). If one had to choose a single option for the mutation operator, we would recommend this one, as it was proven effective and requires no parameter.

	\item \textit{Multi-scale mutation}: Finally, the multi-scale mutation, which also performed fairly well, requires one parameter, the mutation rate. However, it can also be difficult to estimate a correct value a priori.

\end{itemize}

For this application, the mutation operator has a leading effect, and should be chosen with care. It may be wise to perform multiple optimizations, and to consider these three operators in parallel, in order to obtain results from options that are sometimes either more efficient or more robust. It is interesting to note that the three best techniques incorporate a notion of search distance. It is likely that this notion is the key to these algorithms in this application, and allows them to initially explore the parameter space and then converge. In fact, the search radius directly represents the notion of transition between exploration and exploitation, in our opinion more than a possible evolution of mutation rates.

\subsubsection{Other options}

The analysis of the natural selection operator (Fig. \ref{fig:operator_selectnat_score}) revealed a slight preference for ratio-elitism compared to the tournament selection, but this was not very significant. This operator, or at least the two assessed versions, did not appear to significantly influence the optimization performance.

The size of the population ($N$) had an effect on the optimization performance (Fig. \ref{fig:option_taillepop_score}). A bigger population led to better results, but also to longer optimizations. The required number of evaluations, and thus the required time, was approximately proportional to the population size. Thus, if the population size doubled, then the time required for the optimization also nearly doubled (e.g., for a five year calibration period, approximately 4~h CPU were required when $N = 50$, and 14~h CPU when $N = 200$). The optimal size seems to depend on the complexity of the AM to be optimized. A more complex AM (i.e., with more degrees of freedom) requires a bigger population size. A rule of thumb based on a limited number of case studies (not presented here) is provided as follows:

\begin{itemize}
	\item $N\approx100$ for very simple AM implementations (one level of analogy with two pressure levels),
	\item $N\approx200$ for a slightly more complex AM (one level of analogy with four pressure levels, or two levels of analogy with fewer pressure levels),
	\item $N\approx500$ for significantly more complex AMs (two or three levels of analogy with four pressure levels for the atmospheric circulation, and two to four levels for the moisture analogy).
\end{itemize}

The influence of the size of the IG (proportion of the total population) selected for mating was also assessed (Fig. \ref{fig:option_popratio_score}). This option had little influence on the performance of the optimizations. A value of 50~\% seems to be a wise choice.

\section{Use of GAs to optimize AMs}
\label{sec:use}

\subsection{Recommended configuration of GAs}
\label{sec:recommendations}

Optimizations using GAs of AMs of varying complexities were performed with a large number of combinations of operators, in order to make recommendations for optimizing AMs (see Section \ref{sec:assessment}). The conclusions are as follows:

\begin{itemize}
	\item The population size should be in accordance with the complexity of the AM to be optimized, ranging from 100 for simple cases up to 500 for the most complex AMs.

	\item The value of the IG ratio is not significantly important. A value of 50\% seems appropriate.

	\item Ratio-elitism performs slightly better than tournaments for the natural selection operator, but this is not decisive.

	\item The performance of the operators for the couples selection are relatively similar. The roulette wheel weighting and the tournament selection are more efficient in terms of the convergence and required number of evaluations.

	\item Most of the crossover operators yield a relatively similar performance, but the binary-like crossover with two points of intersection is slightly better, especially in terms of convergence.

	\item Mutation clearly yields a dominant influence. Three mutation operators stand out: the non-uniform mutation, multi-scale mutation, and chromosome of adaptive search radius. The latter is the most robust, as it has no controlling parameter.

\end{itemize}

The optimization did not systematically converge to the global optimum (but often close to it), which is why it is recommended to performs several optimizations in parallel in order to compare the results, analyze the convergence, and keep the best configuration. It may be wise to consider the three mutation operators in parallel. In order to be confident in the optimized AMs, we propose using a set of the following mutation operators:

\begin{itemize}
	\setlength\itemsep{-4px}
	\item the non-uniform mutation once, with $p_{mut}=0.05$, $G_{m,r}=50$, $\omega=0.1$
	\item the non-uniform mutation once, with $p_{mut}=0.05$, $G_{m,r}=100$, $\omega=0.1$
	\item the non-uniform mutation once, with $p_{mut}=0.1$, $G_{m,r}=100$, $\omega=0.1$
	\item the multi-scale mutation once, with  $p_{mut}=0.1$
	\item the chromosome of adaptive search radius twice
\end{itemize}

where $p_{mut}$ is the mutation rate (or mutation probability), $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a threshold chosen by the user in order to maintain a minimum search radius when the number of generations $G>G_{m,r}$.

\subsection{Illustration of application}

In order to illustrate the achievable gain by using GAs on an AM, precipitation prediction for the southeast ridges region of the alpine Rh\^{o}ne catchment (Fig. \ref{fig:map}) was optimized for the whole calibration period (40 years in the period 1961-2008, with eight years omitted for validation), instead of the smaller five year period.

The optimizer could select the geopotential height at four pressure levels, at any time of day, on unconstrained spatial windows. Moreover, a weighting was introduced to the combination of the criteria processed on each pressure level \citep[such as in][]{Horton2012a, Junk2015}. In this case, no new meteorological variable was added, and the method still contained a unique level of analogy.

The performance (CRPSS) of the reference method, calibrated by means of the sequential procedure, amounts to 32.00\%, with a 0.95 confidence interval (assessed by bootstrapping on 10000 samples) of (29.21\%; 34.94\%). The method optimized by means of GAs achieved a performance of 37.62\%, with a 0.95 confidence interval of (35.21\%; 40.11\%). Thus, the resulting gain is statistically significant. The results on all subregions and the physical meaning of the optimized parameters will be discussed in a forthcoming paper.

\section{Conclusions}
\label{sec:conclusions}

In order to automatically optimize several AM variants, and to avoid the limitations of the usual sequential calibration, GAs were evaluated. Given the large number of existing operators and options, multiple variants were assessed systematically in order to identify which operators are important, and which variants perform best for the considered AM implementations. The mutation operator was identified as a key element for this application, and new variants were developed that proved efficient, such as the chromosome of adaptive search radius, which is considerably robust (with no control parameter). Recommendations were established for the relevant employment of GAs for optimizing AMs. Although using GAs to optimize AMs may be computationally intensive, once an AM is calibrated, its use in real-time operations it very fast and lightweight.

The possibility that that a different global optimization method or other operators of GAs may perform even better cannot be excluded. Still, the relevance of global optimization techniques for AMs has now been proven, as they provide relevant AM parameters that are automatically, globally, and objectively established. A global optimization is the only way to take into account all of the dependencies between parameters and levels of analogy.

The global optimization approach allows the easy adaptation of AMs to new regions by potentially taking into account local meteorological influences, and thus has a significant potential for application. Moreover, it can be employed to automatically explore datasets, in order to extract the most relevant variables. Thus, this method can make it easier to assess other predictands, such as the temperature, limit of snowfall, or occurrence of hail, while allowing the algorithms to select the best variables and associated parameters.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\acknowledgments
Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of. Thanks to Dominique B\'{e}rod for his support, and to Michel Bierlaire for his advice regarding optimization methods.

Thanks to the Roads and Water Courses Service, Energy and Water Power Service of the Wallis Canton, the Water, Land and Sanitation Service of the Vaud Canton, and the Swiss Federal Office for Environment (FOEV), who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project, which started this research. The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation. NCEP reanalysis data was provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/. Precipitation time series were provided by MeteoSwiss.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% APPENDIXES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Use \appendix if there is only one appendix.
%\appendix

% Use \appendix[A], \appendix}[B], if you have multiple appendixes.
%\appendix[A]

%% Appendix title is necessary! For appendix title:
%\appendixtitle{}

%%% Appendix section numbering (note, skip \section and begin with \subsection)
% \subsection{First primary heading}

% \subsubsection{First secondary heading}

% \paragraph{First tertiary heading}

%% Important!
%\appendcaption{<appendix letter and number>}{<caption>} 
%must be used for figures and tables in appendixes, e.g.,
%
%\begin{figure}
%\noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
%\appendcaption{A1}{Caption here.}
%\end{figure}
%
% All appendix figures/tables should be placed in order AFTER the main figures/tables, i.e., tables, appendix tables, figures, appendix figures.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Make your BibTeX bibliography by using these commands:
\bibliographystyle{ametsoc2014}
\bibliography{references}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TABLES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Enter tables at the end of the document, before figures.
%%
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% FIGURES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Enter figures at the end of the document, after tables.
%%
%

\begin{figure}[t]
	\centerline{\includegraphics[width=19pc,angle=0]{fig01.pdf}}
	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland, and its discretization into 10 subregions:	(1) Swiss Chablais, (2) Trient Valley, (3) West Bernese Alps, (4) Lower Rhone Valley, (5) Left side valleys, (6) Southern ridges, (7) Upper Rhone Valley, (8) Southeast ridges, (9) East Bernese Alps, (10) Conches Valley. (source: Swisstopo)}
	\label{fig:map}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=19pc,angle=0]{fig02.pdf}\\
	\end{center}
	\caption{Genetic algorithms operational flowchart.}
	\label{fig:structure_gas}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=19pc,angle=0]{fig03.pdf}\\
	\end{center}
	\caption{Evolution of the score of the best individual over each generation for the 10 optimizations processed for a given configuration. The continuous bottom line represents the score of the sequential approach, and the dashed line (top) shows the supposed global optimum. The circles represent the end of the optimization (when the best individual did not progress during 20 generations).}
	\label{fig:gas_evolution_good}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=19pc,angle=0]{fig04.pdf}\\
	\end{center}
	\caption{Same as Fig. \ref{fig:gas_evolution_good}, but for a GA configuration considered to be less relevant.}
	\label{fig:gas_evolution_bad}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=19pc,angle=0]{fig05.pdf}\\
	\end{center}
	\caption{Influence of the couples selection operators (Section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:nat_selection}) on the optimization performance (improvement of the score). The box extends from the lower to upper quartile values of the data, with a line at the median. The whiskers extend from the box to 1.5 times the interquartile range. Flier points are those past the end of the whiskers. The star represents the median. The gray box highlights the best options.}
	\label{fig:operator_selectcoupl_score}
\end{figure}

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=39pc,angle=0]{fig06.pdf}\\
	\end{center}
	\caption{Influence of the chromosome crossover operators (Section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:crossover}) on the optimization performance (improvement of the score).  $\beta$s represent a shared $\beta$ parameter, and $\beta$u the unshared version. The same conventions apply as in Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:operator_crossover_score}
\end{figure*}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=19pc,angle=0]{fig07.pdf}\\
	\end{center}
	\caption{Influence of the mutation operators (Section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:mutation}) on the optimization performance. In parentheses is the number of variants considered (combination of options). The same conventions apply as in Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:operator_mutation_score}
\end{figure}

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=33pc,angle=0]{fig08.pdf}\\
	\end{center}
	\caption{Influence of the mutation options (Section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:mutation}) on the optimization performance, letting the optimizer choose the pressure level of the atmospheric circulation analogy (single level of analogy). For the non-uniform mutation, $\omega=0.1$ in every case. The continuous bottom line represents the score of the sequential calibration, and the dashed superior line is the score of the optimization without automatic selection of the pressure levels. The same conventions apply as in Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:operator_mutation_score_atmlevel}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=33pc,angle=0]{fig09.pdf}\\
	\end{center}
	\caption{Same as Fig. \ref{fig:operator_mutation_score_atmlevel}, but for another region in the Swiss Alps (Swiss Chablais), with different atmospheric influences.}
	\label{fig:operator_mutation_score_rhoneamont}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=33pc,angle=0]{fig10.pdf}\\
	\end{center}
	\caption{Same as Fig. \ref{fig:operator_mutation_score_atmlevel}, but with a second level of analogy on moisture variables.}
	\label{fig:operator_mutation_score_r2}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\noindent\includegraphics[width=33pc,angle=0]{fig11.pdf}\\
	\end{center}
	\caption{Same as Fig. \ref{fig:operator_mutation_score_r2}, but with a preselection on air temperature rather than a fixed calendar window.}
	\label{fig:operator_mutation_score_r4}
\end{figure*}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=11pc,angle=0]{fig12.pdf}\\
	\end{center}
	\caption{Influence of the natural selection operators on the optimization performance. The same conventions apply as in Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:operator_selectnat_score}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=11pc,angle=0]{fig13.pdf}\\
	\end{center}
	\caption{Influence of the population size on the optimization performance. The same conventions apply as in Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:option_taillepop_score}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\noindent\includegraphics[width=11pc,angle=0]{fig14.pdf}\\
	\end{center}
	\caption{Influence of the intermediate generation (IG) ratio on the optimization performance. The same conventions apply as in Fig. \ref{fig:operator_selectcoupl_score}.}
	\label{fig:option_popratio_score}
\end{figure}

\end{document}

### 2016-09-22 Genetic algorithms - MWR/template.tex
Elsevier english edition.

@@
 
-\abstract{Analog methods are based on a statistical relationship between synoptic meteorological variables (predictors) and local weather (predictand, which are to be predicted), which is defined by several parameters that are often calibrated by means of a semi-automatic sequential procedure.
-This calibration approach is fast, but has strong limitations: it is made of successive steps and thus cannot handle all parameters dependencies, and it cannot automatically optimize some parameters, such as the selection of the pressure levels and the temporal windows (hour(s) of the day) on which the predictors are compared.
-In order to surpass these limitations, a global optimization technique was assessed, namely Genetic Algorithms, which can optimize jointly all parameters of the method and can get closer to a global optimum, by taking into account the parameters dependencies.
-Moreover, it can objectively calibrate parameters that were previously manually assessed, and can take into account new degrees of freedom.
-Genetic Algorithms need however to be tailored to the addressed problem.
-Multiple combinations of algorithms were assessed, and new ones were developed (e.g., the \textit{chromosome of adaptive search radius} which was found to be very robust), in order to make recommendations for the use of Genetic Algorithms to optimize several variants of analog methods.
-A global optimization approach opens new perspectives for the improvement of analog methods, and their application to new regions or to new predictands.
+\abstract{Analog methods are based on a statistical relationship between synoptic meteorological variables (predictors) and local weather (predictand, to be predicted).
+This relationship is defined by several parameters, which are often calibrated by means of a semi-automatic sequential procedure.
+This calibration approach is fast, but has strong limitations.
+It proceeds through successive steps, and thus cannot handle all parameters dependencies.
+Furthermore, it cannot automatically optimize some parameters, such as the selection of pressure levels and temporal windows (hours of the day) at which the predictors are compared.
+In order to overcome these limitations, the global optimization technique of genetic algorithms is considered, which can jointly optimize all parameters of the method, and get closer to a global optimum, by taking into account the dependencies of the parameters.
+Moreover, it can objectively calibrate parameters that were previously assessed manually, and can take into account new degrees of freedom.
+However, genetic algorithms must be tailored to the problem under consideration.
+Multiple combinations of algorithms were assessed, and new algorithms were developed (e.g., the \textit{chromosome of adaptive search radius}, which is found to be very robust), in order to provide recommendations regarding the use of genetic algorithms for optimizing several variants of analog methods.
+A global optimization approach provides new perspectives for the improvement of analog methods, and for their application to new regions or new predictands.
 }
@@
 
-Analog methods (AMs) rely on the hypothesis that similar situations in terms of the atmospheric circulation are likely to lead to similar local weather \citep{Lorenz1956, Lorenz1969, Duband1970, Bontron2005}.
-They consist in sampling a certain number of past situations based on different synoptic-scale meteorological variables (predictors) in order to build a probabilistic prediction for a local weather variable of interest (predictand).
-A common usage of AMs is for operational precipitation forecasting \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Hamill2015b, BenDaoud2016}, or more recently for precipitation downscaling in a climate perspective \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015}.
-However, AMs or equivalent are also used to predict temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+Analog methods (AMs) rely on the hypothesis that similar situations, in terms of atmospheric circulation, are likely to result in similar local weather conditions \citep{Lorenz1956, Lorenz1969, Duband1970, Bontron2005}.
+These methods consist of sampling a certain number of past situations, based on different synoptic-scale meteorological variables (predictors), in order to construct a probabilistic prediction for a local weather variable of interest (predictand).
+Some common usages of AMs are for operational precipitation forecasting \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Hamill2015b, BenDaoud2016}, or more recently for precipitation downscaling in a climate perspective \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015}.
+However, AMs or equivalent methods are also employed to predict temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectories of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
 
-Even though the method is rather simple, it contains several parameters to optimize, such as the choice of the predictor variables, the pressure levels and temporal windows (hour(s) of the day) on which the predictors are compared, the spatial domains used for the comparison, as well as the analogy criteria (distance measure), and finally, the number of analog situations to retain.
+Although the method is rather simple, it contains several parameters to be optimized, such as the choice of the predictor variables, pressure levels and temporal windows (hours of the day) at which the predictors are compared along with the spatial domains used for the comparison, the analogy criteria (distance measure), and finally the number of analog situations to retain.
 
-AMs need to be adapted to every new region considered, because the leading meteorological influences may be location specific.
+AMs must be adapted to every new considered region because the leading meteorological influences may be location-specific.
 Even the selection of the pressure levels and the temporal windows should be reconsidered, if not the predictor variable itself.
-Thus, before being applied in a forecasting or downscaling context, AMs must be calibrated for the given region, which is done here in the Perfect Prognosis framework \citep{Klein1963}, like the majority of AMs calibration procedures for precipitation prediction cited previously \cite[with the exception of][]{Hamill2006,Hamill2015b}.
+Thus, before being applied in a forecasting or downscaling context, AMs must be calibrated for the given region, which is performed here in the perfect prognosis framework \citep{Klein1963}, in line with the majority of previously cited AM calibration procedures for precipitation predictions \cite[with the exception of][]{Hamill2006,Hamill2015b}.
 
-A common approach to optimize the method is by means of a semi-automatic sequential calibration procedure, developed by \citet{Bontron2004}, also described in \citet{BenDaoud2016}, and extended by \citet{Radanovics2013}.
-It determines some parameters of the method, sequentially for each consecutive analogy level (e.g., on the atmospheric circulation or on a moisture index).
-It starts by a manual selection of the meteorological variables (e.g., geopotential height, relative humidity, etc.), the pressure levels, the temporal windows, and the initial analog numbers.
-Then, the spatial window on which the predictors are compared is optimized by an iterative growth of the domain, and the number of analogs is finally reassessed.
-A successive level of analogy can then be added and its spatial window optimized.
-Parameters of the preceding levels of analogy are not reassessed, except for the number of analog situations to keep.
+A common approach to optimizing this method is by means of a semi-automatic sequential calibration procedure, which was developed by \citet{Bontron2004}, and is also described in \citet{BenDaoud2016} and extended by \citet{Radanovics2013}.
+This one determines some parameters of the method sequentially for each consecutive analogy level (e.g., on the atmospheric circulation or on a moisture index).
+It begins with a manual selection of the meteorological variables (e.g., geopotential height and relative humidity), the pressure levels, the temporal windows, and the initial analog numbers.
+Then, the spatial window over which the predictors are compared is optimized through an iterative growth of the domain, and the number of analogs is finally reassessed.
+A successive level of analogy can then be introduced, and its spatial window be optimized.
+The parameters of the preceding levels of analogy are not reassessed, except for the number of analog situations to preserve.
 
-The sequential calibration procedure thus allows optimizing a limited number of parameters (spatial windows and analog numbers), but the selection of predictor variables, pressure levels and temporal windows have still to be made manually.
-Testing multiple combinations of these is very combinatorial and becomes quickly cumbersome, especially when considering multiple predictors within the same level of analogy.
-Thus, optimizing AMs by means of the sequential technique is laborious when little knowledge on the predictor-predictand relationship or the leading meteorological influences is available.
-Indeed, many combinations of parameters (predictor variables, pressure levels, temporal windows) have to be assessed.
-Moreover, proceeding to the optimization sequentially ignores potential dependencies between the parameters of the method, may they be within a single level of analogy or between them, which could lead to another configuration if the parameters were calibrated together.
-Thus, the risk of ending in a local optimum is high and can not be avoided.
+Thus, the sequential calibration procedure allows the optimization of a limited number of parameters (spatial windows and analog numbers), but the selection of predictor variables, pressure levels, and temporal windows must still be made manually.
+Testing multiple combinations of these presents a very combinatorial problem, which quickly becomes cumbersome, especially when considering multiple predictors within the same level of analogy.
+Thus, optimizing AMs by means of this sequential technique is laborious if little knowledge is available regarding the predictor-predictand relationship or the leading meteorological influences.
+Indeed, many combinations of parameters (predictor variables, pressure levels, and temporal windows) must be assessed.
+Moreover, proceeding to the optimization sequentially ignores potential dependencies between the parameters of the method, whether they are within a single level of analogy or between multiple levels, which could lead to another configuration if the parameters were calibrated together.
+Thus, there is a high risk of ending in a local optimum, and this cannot be avoided.
 
-When creating the sequential calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters and wrote: ''\textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent.
+When creating this sequential calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters, and wrote: ''\textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent.
 We will present our results by first searching the best variable (e.g., selection of the pressure level and the temporal window for the geopotential height) on a chosen spatial window, and next, the best window for the chosen variable.
-However, even by repeating the process, are we sure to obtain the optimal combination?}''.
-And later in his work: ''\textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution}''.
-\citet{Bliefernicht2010} has also faced the combinatorial issue of AMs parameters and concluded that one needs to be an expert to have a sense of their respective influence, sensitivity and nonlinear interactions.
-\citet{BenDaoud2010}, when calibrating an AM, also stated that ''\textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously}''.
-Simultaneous calibration of all parameters has never been undertaken so far.
+However, even by repeating the process, are we sure to obtain the optimal combination?}'' Later in his work, he also wrote: ''\textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution}.'' \citet{Bliefernicht2010} has also confronted the combinatorial issue for the parameters of AMs, and concluded that one must be an expert in order to have a sense of their respective influence, sensitivity, and nonlinear interactions.
+When calibrating an AM, \citet{BenDaoud2010} also stated that ''\textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously}.'' The simultaneous calibration of all parameters has not been undertaken so far.
 
-Another optimization strategy is proposed by \citet{Junk2015}, and allows for an automatic calibration of weights applied to the different predictors when processing the analogy criteria (distance function).
-Their strategy consists in a brute-force assessment of all possible combinations.
-This approach is possible in their implementation, as predictors are considered at a unique point (interpolated to the location of interest), at fixed hours, and at preselected pressure levels, leaving only the weights to be optimized.
-In the presently used AM (described in section \ref{sec:am}), the number of parameters to optimize makes it impossible to proceed to a brute-force strategy.
+Another optimization strategy, proposed by \citet{Junk2015}, allows for an automatic calibration of weights applied to the different predictors when processing the analogy criteria (distance function).
+Their strategy consists of a brute-force assessment of all possible combinations.
+This approach is possible in their implementation, because predictors are considered at a unique point (interpolated to the location of interest), at fixed hours, and at preselected pressure levels, leaving only the weights to be optimized.
+In the presently employed AM (described in section \ref{sec:am}), the number of parameters to optimize makes it impossible to proceed with a brute-force strategy.
 
-In order to overcome these limitations, two optimization techniques were assessed.
-First, \citet{Horton2012a} assessed the ability of the \citet{Nelder1965a} method based on a simplex algorithm.
-This technique did not provide satisfying results and failed at converging toward a unique solution.
-The parameter space of AMs can be very complex and is inappropriate for a linear optimization technique.
+In order to overcome these limitations, two optimization techniques have been assessed.
+First, \citet{Horton2012a} assessed the ability of the method of \citet{Nelder1965a}, based on a simplex algorithm.
+This technique did not provide satisfying results, and failed to converge toward a unique solution.
+The parameter space of the AMs can be very complex, and is inappropriate for a linear optimization technique.
 Thus, global optimization techniques are likely to be necessary in order to calibrate most AM variants, as they can optimize all parameters of all analogy levels simultaneously.
-In addition, they can overcome the systematic manual assessments of all pressure levels and temporal windows.
-Finally, they allow testing new degrees of freedom in AMs.
-The relevance of Genetic Algorithms (GAs) is presented here, which does not exclude that other global optimization techniques could also work.
-If using GAs to optimize AMs is computationally intensive, once an AM is calibrated, its use in real-time operations or climate downscaling is very fast and lightweight.
+In addition, they can avoid the systematic manual assessments of all pressure levels and temporal windows.
+Finally, they allow the testing of new degrees of freedom in AMs.
+The relevance of genetic algorithms (GAs) is demonstrated here, which does not exclude that other global optimization techniques could also work.
+Although using GAs to optimize AMs may be computationally intensive, once an AM is calibrated its employment in real-time operations or climate downscaling is very fast and lightweight.
 
-This paper specifically describes how GAs are to be used in order to successfully optimize several AMs.
-Indeed, GAs variants are numerous and always need to be tailored to the addressed problem.
-This requires intensive and systematic comparisons of operators and options in order to identify the key factors leading the optimization and the respective sensitivity of the options.
-Such analyzes are presented here and result in recommendations for the use of GAs to optimize several AM implementations.
-The in-depth analysis of the benefit brought by such an approach on a specific case study is the topic of another coming paper.
+This paper specifically describes how GAs should be used in order to successfully optimize several AMs.
+Indeed, the variants of GAs are numerous, and always need to be tailored to the addressed problem.
+This requires intensive and systematic comparisons of operators and options, in order to identify the key factors influencing the optimization, and the respective sensitivity of the options.
+Such analyses are presented here, resulting in recommendations for the use of GAs to optimize several AM implementations.
+The in-depth analysis of the benefits of such an approach in a specific case study will be the topic of a forthcoming paper.
 
-The document starts by presenting the case study area and the data (section \ref{sec:case_study_data}), the considered AM variants (section \ref{sec:am}), and the assessed GAs options (section \ref{sec:gas}).
-The comparative analyzes of these options are presented in section \ref{sec:assessment}, which results in recommendations formulated in section \ref{sec:use} and conclusions in section \ref{sec:conclusions}.
+This document begins by presenting the area of the case study and the relevant data (section \ref{sec:case_study_data}), the considered AM variants (section \ref{sec:am}), and the assessed GA options (section \ref{sec:gas}).
+Comparative analyses of these options are presented in section \ref{sec:assessment}, leading to the recommendations formulated in section \ref{sec:use}, and finally the conclusions presented in section \ref{sec:conclusions}.
 
@@
 
-The study area is the alpine upper Rh\^{o}ne catchment in Switzerland (Fig.\ \ref{fig:map}).
-The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$.
-Based on different climatological analyzes \cite[see][for the details]{Horton2012a}, the gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}).
+The area of the study is the alpine upper Rh\^{o}ne catchment in Switzerland (Fig.\ \ref{fig:map}).
+The altitude ranges from 372 to 4634~m.a.s.l., and the area is 5524~km$^{2}$.
+Based on various climatological analyses \cite[see][for the details]{Horton2012a}, the gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}).
 
-This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at providing real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
-AMs are used to provide real-time probabilistic precipitation forecasts, based on NWP outputs.
+This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project, which aims to provide real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
+AMs are used to provide real-time probabilistic precipitation forecasts, based on NWP (Numerical Weather Prediction) models outputs.
 
@@
 
-AMs rely on two types of data: predictors, that are meteorological variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series one wants to predict.
+AMs rely on two types of data: predictors, which are meteorological variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series that is to be predicted.
 
-When working in the Perfect Prognosis framework \citep{Klein1963}, the meteorological archive from which the predictors are extracted is usually a reanalysis dataset.
-Oppositely, other applications of AMs for wind forecasting are based on a Model Output Statistics context \citep[MOS, see][]{Glahn1972}, and thus use forecast archives or reforecast products \citep[e.g.,][]{DelleMonache2013, DelleMonache2011, Alessandrini2015, Junk2015, Junk2015c}.
+When working in the perfect prognosis framework \citep{Klein1963}, the meteorological archive from which the predictors are extracted is usually a reanalysis dataset.
+Conversely, other applications of AMs for wind forecasting are based on a Model Output Statistics framework \citep[MOS, see][]{Glahn1972}, and thus employ forecast archives or reforecast products \citep[e.g.,][]{DelleMonache2013, DelleMonache2011, Alessandrini2015, Junk2015, Junk2015c}.
 
-In the present study, the NCEP-NCAR reanalysis I dataset \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} was used, but it could have been any other reanalysis dataset.
-This dataset is relatively old, even though still widely used, and better results may be expected with more recent datasets.
-However, we can safely make the assumption that if the optimization technique works for this reanalysis dataset, it will also work on an improved one.
+In the present study, the NCEP-NCAR reanalysis I dataset \citep[six-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} is employed, but this could be replaced with any other reanalysis dataset.
+This dataset is relatively old, although it is still widely used, and better results may be expected with more recent datasets.
+However, we can safely assume that if an optimization technique works for this reanalysis dataset, it will also work for an improved one.
 
-The predictand (which is to be predicted) was here the daily precipitation (0540~UTC to 0540~UTC the following day) measured at the MeteoSwiss' stations network in the catchment of interest.
-The time series from every available gauging station were averaged over subregions of approximately 500~km$^{2}$ \citep[see][for the details]{Horton2012a} in order to smooth local effects \citep{Obled2002, Marty2012}.
-The time series need to be split into a calibration and an independent validation periods.
+Here, the predictand (which is to be predicted) is the daily precipitation (0540~UTC to 0540~UTC the following day) measured at the MeteoSwiss network of stations in the catchment of interest.
+The time series from every available gauging station were averaged over subregions of approximately 500~km$^{2}$ \citep[see][for details]{Horton2012a} in order to smooth local effects \citep{Obled2002, Marty2012}.
+The time series must be split into calibration and independent validation periods.
 
@@
 
-AMs are based on the principle that two similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}.
-Thus, they consist in searching a certain number of past situations in a meteorological archive that present similar properties for chosen predictors, according to an analogy criteria, in order to extract the observed values of the local weather variable of interest from another archive (predictand time series, see section \ref{sec:case_study_data}\ref{sec:data}).
-Based on these analog observations, the conditional empirical distribution considered as the probabilistic prediction for the target day (the day one wants to predict) is built.
+AMs are based on the principle that two similar synoptic situations may result in similar local effects \citep{Lorenz1956, Lorenz1969}.
+Thus, they consist in searching for a certain number of past situations in a meteorological archive that present similar properties for chosen predictors, according to an analogy criteria, in order to extract the observed values of the local weather variable of interest from another archive (predictand time series, see section \ref{sec:case_study_data}\ref{sec:data}).
+Based on these analog observations, the conditional empirical distribution to be considered as the probabilistic prediction for the target day (the day one wishes to predict) is constructed.
 
-Predictors for precipitation prediction, can be varied: e.g., geopotential height at different pressure levels and temporal windows, humidity variables, etc \citep[see][for a more detailed list of predictors]{BenDaoud2016}.
-The method often contains several levels of analogy, which are successive subsampling on predictors of different nature (e.g., atmospheric circulation, moisture variables, vertical motion, and air temperature).
+Predictors for precipitation predictions can be varied.
+For example, the geopotential height at different pressure levels and temporal windows, or humidity variables \citep[see][for a more detailed list of predictors]{BenDaoud2016}.
+This method often contains several levels of analogy, which constitute of successive subsamplings on predictors of different natures (e.g., atmospheric circulation, moisture variables, vertical motion, and air temperature).
 
-The basis of the AM implementation considered here is the following \citep[same approach as][]{Guilbaud1997, Bontron2005, Marty2012, Horton2012, Radanovics2013, Chardon2014, Dayon2015, BenDaoud2016}:
+The basis of the AM implementation considered here is the following \citep[the same approach as][]{Guilbaud1997, Bontron2005, Marty2012, Horton2012, Radanovics2013, Chardon2014, Dayon2015, BenDaoud2016}:
 
 \begin{enumerate}
-	\item Preselection: to cope with seasonal effects, $n_{0}$ candidate dates are extracted from the archive within a period of four months centered around the target date, for every year of the archive.
-Alternatively, the candidate dates can be selected based on similar air temperature \citep[see][]{BenDaoud2016}.
+	\item Preselection: To cope with seasonal effects, $n_{0}$ candidate dates are extracted from the archive within a period of four months centered around the target date, for every year of the archive.
+Alternatively, the candidate dates can be selected based on similar air temperatures \citep[see][]{BenDaoud2016}.
 
@@
 The first level of analogy for precipitation prediction is often based on the atmospheric circulation.
-The similarity of the atmospheric circulation of the target date with the candidate situations is assessed on the geopotential height (at specific pressure levels, such as 500 and 1000~hPa, and over a certain spatial window, e.g., 12~h and 24~h) by means of the S1 criteria \citep[Eq.
-(\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a defined spatial window.
-The S1 criteria is found more relevant than Euclidean distances for pressure fields by different studies \citep{Wilson1980, Woodcock1980, Guilbaud1998, Bontron2004}.
+The similarity between the atmospheric circulation of the target date and the candidate situations is assessed based on the geopotential height (at specific pressure levels, such as 500 and 1000~hPa, and over a certain spatial window, e.g., 12~h and 24~h) by means of the S1 criteria \citep[Eq.
+(\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients over a defined spatial window.
+Various studies have found the S1 criteria to be more relevant than Euclidean distances for pressure fields \citep{Wilson1980, Woodcock1980, Guilbaud1998, Bontron2004}.
 
@@
 The differences are processed separately in both directions.
-The smaller the S1 values, the more similar the pressure fields.
+The smaller the S1 values, the more similar the pressure fields are.
 
-	The $n_{1}$ dates with the lowest values of S1 are considered as analog situations, in terms of the atmospheric circulation, to the target day. The analog number $n_{1}$ is a parameter to calibrate.
+	The $n_{1}$ dates with the lowest S1 values are considered as analog situations, in terms of the atmospheric circulation, for the target day.
+The analog number $n_{1}$ is a parameter to be calibrated.
 
-	\item Subsequent level(s) of analogy: beyond the similarity of airflows, one may look for analogies in other variables of interest, such as moisture variables.
-Therefore, the $n_{1}$ analogs are subsampled once again on the basis of another variable, in order to obtain a lower number of analog dates, $n_{2}$.
-When the predictor is not a pressure field, the analogy criteria usually represents absolute distances: Mean Absolute Error (MAE) and Root Mean Squared Error (RMSE), the latest being most often used.
+	\item Subsequent level(s) of analogy: Beyond the similarity of airflows, one may look for analogies in other variables of interest, such as moisture variables.
+Therefore, the $n_{1}$ analogs are subsampled once more on the basis of another variable, in order to obtain a lower number of analog dates, $n_{2}$.
+When the predictor is not a pressure field, the analogy criteria usually represents absolute distances, such as mean absolute error (MAE) or root mean squared error (RMSE), with the latter being most often employed.
 
-	A second level of analogy based on thermodynamic variables was introduced by \citet{Vallee1986}, and \citet{Gibergans-Baguena2007}.
-After a systematic assessment of variables, \citet{Bontron2004} pointed out that a moisture index made of the product of relative humidity at 850~hPa and total precipitable water gives the best performance.
+	A second level of analogy, based on thermodynamic variables, was introduced by \citet{Vallee1986} and \citet{Gibergans-Baguena2007}.
+After a systematic assessment of variables, \citet{Bontron2004} pointed out that a moisture index consisting of the product of relative humidity at 850~hPa and total precipitable water achieves the best performance.
 This index does not represent an actual physical quantity, but expresses the water content of the air column and its proximity to saturation.
 
-	This process can be repeated, by subsampling a decreasing number of analog dates, $n_{i}$, according to various meteorological variables.
+	This process can be repeated by subsampling a decreasing number of analog dates, $n_{i}$, according to various meteorological variables.
 
-	\item Probabilistic prediction: then, the daily observed precipitation amounts of the $n_{i}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.
+	\item Probabilistic prediction: Then, the daily observed amounts of precipitation for the $n_{i}$ resulting dates provide the empirical conditional distribution, considered as the probabilistic forecast for the target day.
 
@@
 
-The parameters to be defined (manually or automatically), for every level of analogy, are the following:
+The parameters to be defined (manually or automatically), for every level of analogy, are:
 
 \begin{itemize}
-	\item The selection of meteorological variables (predictors) that contain synoptic scale information having direct or indirect dependency with the target predictand.
+	\item The selection of meteorological variables (predictors), containing synoptic scale information, and having a direct or indirect dependency with the target predictand.
 	\item The pressure level, or height, at which the predictor is selected.
 	\item The temporal window is the hour(s) of the day at which the predictors are considered.
-	\item The spatial window is the domain on which predictors are compared. The ideal size of this area is the one that maximizes useful information and minimizes noise.
-	\item The analogy criterion, needed to compare the variables on the chosen spatial and temporal windows, is a distance measure used for ranking observed situations according to their degree of similarity with the target situation.
-	\item Eventual weights between the predictors \cite[e.g.,][]{Horton2012a, Junk2015}
-	\item The ideal number of analog situations, which is the best compromise in order to take into account local variability and to maximize useful synoptic information \citep{Bontron2004}.
+	\item The spatial window is the domain on which predictors are compared. The ideal size of this area is that which maximizes the useful information and minimizes noise.
+	\item The analogy criterion, needed to compare the variables on the chosen spatial and temporal windows, is a distance measure, used to rank observed situations according to their degree of similarity with the target situation.
+	\item Eventual weights between the predictors \cite[e.g.,][]{Horton2012a, Junk2015}.
+	\item The ideal number of analog situations, which is the best compromise in order to take into account local variability and maximize useful synoptic information \citep{Bontron2004}.
 \end{itemize}
 
-In order to calibrate the method, the Continuous Ranked Probability Score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} is often used to assess AMs performances \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}.
-It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$.
+In order to calibrate the method, the continuous ranked probability score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} is often employed to assess the performances of AMs \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}.
+This allows the evaluation of predicted cumulative distribution functions $F(y)$, e.g., of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$.
 The better the prediction, the smaller the score.
-The mean CRPS of a prediction series of length $l$ can be written:
+The mean CRPS of a prediction series of length $l$ can be written as follows:
 
@@
 \end{equation}
-where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value one otherwise. The mean CRPS is averaged on the calibration, respectively the validation periods.
+where $H(y-y_{i}^{0})$ is the Heaviside function, which is zero when $y-y_{i}^{0}<0$ and has a value of one otherwise. The mean CRPS is averaged over the calibration or the validation period.
 
-In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution of daily precipitation as the reference.
-The CRPSS (\textit{Continuous Ranked Probability Skill Score}) is thus defined as following:
+In order to compare the value of the score with regard to a reference, one often considers its skill score expression, and employs the climatological distribution of daily precipitation as the reference.
+The CRPSS (\textit{continuous ranked probability skill score}) is thus defined as follows:
 
@@
 \end{equation}
-where $CRPS_{r}$ is the score value for the reference. An increase in CRPSS means a better prediction.
+where $CRPS_{r}$ is the score value for the reference. An increase in the CRPSS indicates a better prediction.
 
-\section{Assessed Genetic Algorithms variants}
+\section{Assessed genetic algorithm variants}
 \label{sec:gas}
 
-Genetic Algorithms \citep[GAs,][]{Holland1992b, Goldberg1989} are part of the family of Evolutionary Algorithms \citep{Back1993b, Schwefel1993}, inspired by some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
-Unlike linear or local optimizations, GAs seek the global optimum on complex surfaces, theoretically without restriction, but with no guarantee to reach it \citep{Haupt2004}.
-The objective function to optimize (often named fitness function in this context) can be of different types \citep{Joines1996a}, but GAs must be adapted in order to perform optimally.
+Genetic algorithms \citep[GAs,][]{Holland1992b, Goldberg1989} are part of the family of evolutionary algorithms \citep{Back1993b, Schwefel1993}, which are inspired by some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
+Unlike linear or local optimizations, GAs seek the global optimum on complex surfaces, theoretically without restriction, but with no guarantee of reaching it \citep{Haupt2004}.
+The objective function to be optimized (often named the fitness function in this context) can be of various types \citep{Joines1996a}, but GAs must be adapted in order to perform optimally.
 
-A key element of GAs configuration is finding the right balance between exploration and exploitation \citep{Back1992a, Smith1997a}.
-Exploration is characterized by a relatively high probability to assess the regions of the parameter space that have not yet been visited.
-This probability must be sufficiently large at the beginning of the optimization, so that the algorithm is capable of identifying the region where the global optimum is likely located.
+A key element of the configuration of GAs is to determine the correct balance between exploration and exploitation \citep{Back1992a, Smith1997a}.
+Exploration is characterized by a relatively high probability of assessing the regions of the parameter space that have not yet been visited.
+This probability must be sufficiently large at the beginning of the optimization, so that the algorithm is capable of identifying the region where the global optimum is likely to be located.
 Exploitation is characterized by a local search in an area of interest, and generally makes small movements.
@@
 GAs optimize a population of $N$ individuals.
-Each individual contains a chromosome, which is here a vector of the AM parameters.
+Each individual contains a chromosome, which here is a vector of the AM parameters.
 Genes are the individual parameters constituting the chromosome.
-They can be either categorical (e.g., choice of the meteorological variable), discrete (e.g., number of analog dates to select), or continuous.
+These can be categorical (e.g., choice of the meteorological variable), discrete (e.g., number of analog dates to select), or continuous.
 
-There are numerous implementation variants of GAs, often optimal for a given problem \citep{Hart1991a, Schraudolph1992a}.
+There are numerous implementation variants of GAs, which are often optimal for a given problem \citep{Hart1991a, Schraudolph1992a}.
 The differences are found in the implementation of the operators, through significantly different algorithms, which has an important effect on the results \citep{Gaffney2010a}.
-Here, operators are defined as the mechanisms that modify the values of the genes to try bringing individuals (or chromosomes) closer to an optimum of the fitness function.
+Here, operators are defined as the mechanisms that modify the values of the genes, to try to bring individuals (or chromosomes) closer to an optimum of the fitness function.
 The structure of the method (Fig.
-\ref{fig:structure_gas}) resulting from the work of \citet{Holland1992b} is common to most applications \citep{Back1993b}, and consists in the following steps: (1) a population of $N$ individuals (parameter sets of the AM to optimize) is randomly generated, which constitutes the initial population.
+\ref{fig:structure_gas}) that results from the work of \citet{Holland1992b} is common to most applications \citep{Back1993b}, and consists of the following steps.
+(1) A population of $N$ individuals (parameter sets of the AM to be optimized) is randomly generated, which constitutes the initial population.
 The fitness (performance score or objective function) of every individual is assessed.
-(2) A natural selection is applied, after which only the best individuals remain, constituting the intermediate generation (IG), from which (3) couples are formed according to given rules.
-Then, (4) these couples proceed to reproduction, or chromosome crossover, to mix their genes according to the selected operator version.
-New children are generated in order to refill the IG back to $N$ individuals.
-(5) Parents and children are then subject to mutation, where some genes are randomly changed.
-Finally, (6) the new generation is then re-assessed, the best individual restored if degraded, and (7) according to the ending criteria, the optimization ends or starts again for another iteration.
+(2) A natural selection algorithm is applied, after which only the best individuals remain.
+This constitutes the intermediate generation (IG), from which (3) couples are formed according to given rules.
+Then, (4) these couples proceed to the reproduction or chromosome crossover stage, to mix their genes according to the selected operator version.
+New children are generated, in order to refill the IG back to $N$ individuals.
+(5) Parents and children are then subjected to mutation, where some genes are randomly changed.
+Finally, (6) the new generation is then re-assessed, and the best individual restored if degraded.
+Then, (7) according to the ending criteria, the optimization either ends or begins again for another iteration.
 
-All considered operators and their options are described in the following sections (only briefly for operators with less importance).
-Many other operators exist, but only the ones evaluated are presented.
+All of the considered operators and their options are described in the following sections (only briefly for operators of less importance).
+Many other operators exist, but only those that are evaluated are described here.
 
@@
 
-A random initialization based on a uniform sampling is the most current version of the initial population generation.
+The most current version of the initial population generation is a random initialization based on a uniform sampling.
 The size $N$ of the population is often a compromise between the computation time and the quality of the solution.
-$N$ must allow sufficient sampling of the solutions field \citep{Beasley1996a}, and should thus vary as a function of the chromosome size (ie the number of genes or parameters to be optimized).
+The chosen $N$ must allow sufficient sampling of the solutions field \citep{Beasley1996a}, and thus should vary as a function of the chromosome size (i.e., the number of genes or parameters to be optimized).
 
@@
 Natural selection is performed on the basis of the objective function values.
-The selection allows to only keep a certain part of the population, usually half ($N/2$), which can access the IG (with $N_{IG}$ members).
+The selection allows for only a certain portion of the population to be kept, usually half ($N/2$), which can access the IG (with $N_{IG}$ members).
 Several techniques exist, such as:
@@
 \begin{itemize}
-	\item $N_{IG}$-elitism \citep{Michalewicz1996}: only the better half is preserved.
+	\item $N_{IG}$-elitism \citep{Michalewicz1996}: Only the better half is preserved.
 
-	\item Tournament selection \citep{Michalewicz1996, Zitzler2004a}: two individuals are randomly selected and the best one is chosen, but with a certain probability.
+	\item Tournament selection \citep{Michalewicz1996, Zitzler2004a}: Two individuals are randomly selected, and the best of these is chosen, but with a certain probability.
 \end{itemize}
@@
 
-Individuals of the IG can then reproduce, which begins with the selection of pairs (the parents). The techniques implemented in this work are the following:
+Individuals of the IG can then reproduce, which begins with the selection of pairs (the parents). The techniques implemented in this study are the following:
 
 \begin{itemize}
-	\item Rank pairing: individuals are gathered in pairs according to their rank.
+	\item Rank pairing: Individuals are gathered into pairs according to their ranks.
 
-	\item Random pairing: individuals are randomly selected, according to a uniform law.
+	\item Random pairing: Individuals are randomly selected, according to a uniform law.
 
-	\item Roulette wheel selection \citep{Goldberg1989}: the selection probability assigned to the individuals is proportional to their fitness, so that the most adapted individuals have a greater probability of reproduction.
-There are two weighting techniques : the first one according to the rank, and the second on the fitness value.
+	\item Roulette wheel selection \citep{Goldberg1989}: The selection probability assigned to each individual is proportional to its fitness, so that the most adapted individuals have a greater probability of reproduction.
+There are two weighting techniques.
+The first proceeds according to the rank, and the second according to the fitness value.
 
-	\item Tournament selection: a number of individuals (two or three) are randomly picked and the best is kept, with a certain probability. This operation is performed twice, once for each partner.
+	\item Tournament selection: A number of individuals (two or three) are randomly picked, and the best is kept, with a certain probability. This operation is performed twice, once for each partner.
 \end{itemize}
@@
 
-Once the two parents are selected for breeding, they combine their chromosomes and produce two children, bringing the number of individuals in the population back to $N$.
-The combination of chromosomes is carried out using a crossover operator, thereby generating two offspring having characteristics derived from both parents.
-It allows a mixing of genes and a potential accumulation of positive mutations.
+Once the two parents have been selected for breeding, they combine their chromosomes and produce two children, bringing the number of individuals in the population back to $N$.
+The combination of chromosomes is carried out using a crossover operator, thereby generating two offspring that have characteristics derived from both parents.
+This allows the mixing of genes, and the potential accumulation of positive mutations.
 The evaluated crossover operators are the following:
@@
 \begin{itemize}
-	\item Single-point crossover \citep{Goldberg1989}: the genes located after a randomly chosen point within the chromosome are exchanged in between the two parents.
+	\item Single-point crossover \citep{Goldberg1989}: The genes located after a randomly chosen point within the chromosome are exchanged between the two parents.
 
-	\item Two-point crossover: similar to the single-point crossover, but with two intersections defining the segments to be exchanged.
-It is considered more efficient than the previous \citep{Beasley1993a}.
+	\item Two-point crossover: Similar to the single-point crossover, but with two intersections defining the segments to be exchanged.
+This is considered to be more efficient than the previous method \citep{Beasley1993a}.
 
-	\item Multiple-point crossover \citep{DeJong1975a}: a generalization of the previous, with a number of crossover points up to the number of genes.
+	\item Multiple-point crossover \citep{DeJong1975a}: A generalization of the previous method, with any number of crossover points up to the number of genes.
 
-	\item Uniform crossover \citep{Syswerda1989}: for each gene of the chromosome, it is randomly chosen to exchange or not the values between the parents.
+	\item Uniform crossover \citep{Syswerda1989}: For each gene of the chromosome, a random decision is made to exchange the values between the parents or not.
 
-	\item Binary-like crossover \citep{Haupt2004}: in order to reproduce the behaviour present in the canonical crossover algorithm, which is applied to a binary representation of the genes \citep{Goldberg1989, Goldberg1990a, Herrera1998a}, \citet{Haupt2004} propose an operator that combines the standard crossover operation with an interpolation approach.
-The genes located after a crossover point are exchanged, but the gene located at the intersection is modified according to:
+	\item Binary-like crossover \citep{Haupt2004}: In order to reproduce the behavior present in the canonical crossover algorithm, which is applied to a binary representation of the genes \citep{Goldberg1989, Goldberg1990a, Herrera1998a}, \citet{Haupt2004} propose an operator that combines the standard crossover operation with an interpolation approach.
+The genes located after a crossover point are exchanged, but the gene located at the intersection is modified according to the following:
 	\begin{equation}
@@
 	\end{equation}
-	where $g_{o1,n}$ and $g_{o2,n}$ are the $n$-th gene of the two new offspring, and $g_{p1,n}$ and $g_{p2,n}$ are those of the two parents.
-$\beta$ is a random value between zero and one, that can be unique for the whole chromosome, or that can change for every gene.
+	where $g_{o1,n}$ and $g_{o2,n}$ are the $n$-th genes of the two new offspring, and $g_{p1,n}$ and $g_{p2,n}$ are those of the two parents.
+Furthermore, $\beta$ is a random value between zero and one, which can either be unique for the whole chromosome or can change for every gene.
 
-	\item Blending method \citep{Radcliffe1991a}: in this approach, instead of exchanging the genes in between the chromosomes after some crossover points, these are combined by linear combination, also using a random value $\beta$.
+	\item Blending method \citep{Radcliffe1991a}: In this approach, instead of exchanging the genes between the chromosomes after some crossover points, they are combined through a linear combination, also using a random value $\beta$.
 
-	\item Linear crossover \citep{Wright1991a}: it widens the range of gene values, and produces three children from two parents.
+	\item Linear crossover \citep{Wright1991a}: This widens the range of gene values, and produces three children from two parents.
 
-	\item Heuristic crossover \citep{Michalewicz1996}: it is a variation of the blending method.
+	\item Heuristic crossover \citep{Michalewicz1996}: This is a variation of the blending method.
 
-	\item Linear interpolation: unlike previous techniques, this one does not rely on crossover points, but on a linear interpolation on every gene of the couple, also using a random value $\beta$, which is the same for every gene.
+	\item Linear interpolation: Unlike the previous techniques, this one does not rely on crossover points, but rather on a linear interpolation on every gene of the couple.
+This also uses a random value $\beta$, which is the same for every gene.
 
-	\item Free interpolation: this technique performs interpolation on each gene, like the previous one; but in this case, the weighting factor $\beta$ changes for each gene.
+	\item Free interpolation: This technique performs interpolation on each gene, like the previous one. However, in this case the weighting factor $\beta$ changes for each gene.
 
@@
 
-The combination of strong genes by the operator of chromosomes crossover is theoretically the most important operating mechanism in the conventional GAs \citep{Holland1992b,Back1993b}.
-However, many studies identify the mutation process as the main operator, and crossovers as secondary \citep[see][]{Back1992a, Back1996a, Back1996b, Smith1997a, Deb1999, Costa2005a, Costa2007a}.
+The combination of strong genes through the chromosomes crossover operation is theoretically the most important operating mechanism in conventional GAs \citep{Holland1992b,Back1993b}.
+However, many studies identify the mutation process as the key operator, and crossovers as secondary \citep[see][]{Back1992a, Back1996a, Back1996b, Smith1997a, Deb1999, Costa2005a, Costa2007a}.
 
 The mutation operator modifies some gene values.
-It adds diversity to the population and prevents a freeze of the evolution, or a genetic drift to a local optimum.
-Thus, it makes the convergence to the global optimum theoretically possible \citep{Beasley1993a}, as it allows exploring beyond the current region of the parameters space by bringing new characteristics that were not present in the original population \citep{Haupt2004}.
+It adds diversity to the population, and prevents a freeze of the evolution, or a genetic drift to a local optimum.
+Thus, it makes the convergence to the global optimum theoretically possible \citep{Beasley1993a}, as it allows exploration beyond the current region of the parameters space by introducing new characteristics that were not present in the original population \citep{Haupt2004}.
 
-The evaluated and developed mutation operators are listed hereafter (equations are only provided for the operator versions that were found relevant; the reader can refer to the corresponding literature for the details of the other options).
-They apply to genes made of continuous or discrete variables, but not categorical (e.g., choice of the meteorological variable or analogy criterion).
-In the latter case, the random choice of a new value is always based on a uniform distribution, without notion of distance in the parameters space.
+The evaluated and developed mutation operators are listed in the following (equations are only provided for the operator versions that were found to be relevant, the reader may refer to the corresponding literature for details regarding the other options).
+These apply to genes formed of continuous or discrete variables, but not to those that are categorical (e.g., the choice of the meteorological variable or analogy criterion).
+In the latter case, the random choice of a new value is always based on a uniform distribution, without a notion of distance in the parameters space.
 
 \begin{itemize}
-	\item Uniform mutation: the mutation rate ($p_{mut}$) is constant and equal for every gene of each individual; they all have the same probability to mutate.
+	\item Uniform mutation: The mutation rate ($p_{mut}$) is constant and equal for every gene of each individual.
+They each have the same probability of mutating.
 When a gene is selected for mutation, a new random value is assigned, according to a uniform law.
 
-	\item Variable uniform mutation \citep{Fogarty1989}: a variable mutation rate over the generations was first suggested by \citet{Holland1992b} and evaluated by \citet{Fogarty1989}.
-In most applications, the mutation rate decreases with the generations, in a deterministic and global (for all individuals) manner \citep{Back1992b}.
+	\item Variable uniform mutation \citep{Fogarty1989}: A variable mutation rate over the generations was first suggested by \citet{Holland1992b}, and evaluated by \citet{Fogarty1989}.
+In most applications, the mutation rate decreases with each generation, in a deterministic and global (for all individuals) manner \citep{Back1992b}.
 
-	\item Constant normal mutation: it uses normal distributions to generate new values of the gene, based on an estimated standard deviation.
+	\item Constant normal mutation: This method employs normal distributions to generate new values of the gene, based on an estimated standard deviation.
 
-	\item Variable normal mutation \citep{Horton2012a}: with the same logic as the variable uniform mutation, a mutation operator was tested using a normal distribution with a variable mutation rate and standard deviation, that decrease linearly over the generations.
+	\item Variable normal mutation \citep{Horton2012a}: With the same logic as the variable uniform mutation, a mutation operator is tested using a normal distribution with a variable mutation rate and standard deviation, which decrease linearly over generations.
 This operator has six parameters.
 
-	\item Non-uniform mutation \citep{Michalewicz1996}: two random numbers are picked based on a uniform law: $r_{1}$, which determines the direction of the change, and $r_{2}$, which determines its magnitude.
+	\item Non-uniform mutation \citep{Michalewicz1996}: Two random numbers are chosen based on a uniform law: $r_{1}$, which determines the direction of the change, and $r_{2}$, which determines its magnitude.
 The new value of the gene is given by the following equation, according to a predefined number of generations:
@@
 
-	where $a_{n}$ is the lower bound of the $n$-th gene, $b_{n}$ its upper bound, $G$ the present generation, and $G_{m}$ the maximum number of generations.
+	where $a_{n}$ and $b_{n}$ are the lower and upper bounds, respectively, of the $n$-th gene, $G$ is the present generation, and $G_{m}$ is the maximum number of generations.
 
-	This operator was adapted for this application, which is not based on a predefined number of generations, by changing $\varphi$ with $\varphi'$:
+	This operator is adapted for this application, which is not based on a predefined number of generations, by swapping $\varphi$ with $\varphi'$:
 
@@
 	where $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a chosen threshold to maintain a minimum search radius when $G>G_{m,r}$.
-During the first generations, the exploration extent covers the entire parameters space.
-However, this area is reduced over generations, allowing exploitation of local solutions.
+During the first generations, the extent of the exploration covers the entire parameters space.
+However, this area is reduced over generations, allowing the exploitation of local solutions.
 
-	\item Individual adaptive mutation rate \citep{Back1992a}: based on the ideas of Evolution Strategies \citep[see][]{Rechenberg1973, Schwefel1981}, \citet{Back1992a} introduced a concept of self-adaptive GAs.
+	\item Individual adaptive mutation rate \citep{Back1992a}: Based on the ideas of evolution strategies \citep[see][]{Rechenberg1973, Schwefel1981}, \citet{Back1992a} introduced the concept of self-adaptive GAs.
 The idea is to distribute the control parameters within the individuals themselves, which partially decentralizes the control of the evolution.
-It allows reducing the manual tuning of GAs and introduces a notion of self-management.
-The first approach is the introduction of a mutation rate per individual, that mutates itself under its own probability \citep{Back1992a}.
-Then, the eventual new rate is used to mutate the genes of the individual.
-Thus, as this rate decreases, it will have less probability of being itself mutated.
+This allows for a reduction in the manual tuning of GAs, and introduces a notion of self-management.
+The first approach is the introduction of a mutation rate for each individual, which mutates itself under its own probability \citep{Back1992a}.
+Then, the resulting new rate is employed to mutate the genes of the individual.
+Thus, as this rate decreases it has a lower probability of being mutated itself.
 Mutations are performed according to a constant uniform distribution.
-The initial mutation rates are randomly chosen \citep{Back1992a} and the method has no parameter.
-Other approaches exist to introduce a self-adaptation \citep[see][]{Smith1997a, Deb1999, Deb2001a}.
+The initial mutation rates are randomly chosen \citep{Back1992a}, and the method has no parameters.
+Other approaches exist for introducing a self-adaptation \citep[see][]{Smith1997a, Deb1999, Deb2001a}.
 
-	\item Individual adaptive search radius: based on the ideas of the non-uniform mutation, we introduced a search radius in the approach of individual adaptive mutation rates.
-This search radius $r_{a}$, bounded between zero and one (relatively to the parameter ranges), is also adaptive and behaves similarly to the adaptive mutation rates.
-In order to separate its evolution from the one of the mutation rate, its own value is also considered as a self-mutation rate to eventually mutate before being used as a normalized search radius.
+	\item Individual adaptive search radius: Based on the ideas of non-uniform mutation, we introduce a search radius to the approach of individual adaptive mutation rates.
+This search radius $r_{a}$, bounded between zero and one (relative to the parameter ranges), is also adaptive, and behaves similarly to the adaptive mutation rates.
+In order to separate its evolution from that of the mutation rate, its own value is also considered as a self-mutation rate for eventually mutating before being used as a normalized search radius.
 The value of a mutated gene is given by the following equation, which is a simplification of the non-uniform mutation:
@@
 	\end{equation}
-	where $r_{1}$ and $r_{2}$ are randomly selected, such as in the non-uniform mutation. No external parameter is therefore necessary.
+	where $r_{1}$ and $r_{2}$ are randomly selected, such as in non-uniform mutation. Therefore, no external parameter is necessary.
 
-	\item Chromosome of adaptive mutation rate \citep[or \textit{n adaptative mutation rate},][]{Back1992a}: analogously to the individual adaptive mutation rate, this approach leaves the control of the evolution rate to the individuals themselves.
+	\item Chromosome of adaptive mutation rate \citep[or \textit{n adaptative mutation rate},][]{Back1992a}: Analogously to the individual adaptive mutation rate, this approach leaves the control of the evolution rate to individuals.
 The difference here is that each gene has a specific mutation rate.
-The main advantage is that the automatic tuning of the mutation can be much more precise \citep{Smith1997a}.
-A second chromosome containing the mutation rate for each gene of the first chromosome was therefore considered.
-The operations of mutation and self-mutation are similar to the case of the individual adaptive mutation rate, but in a distributed way, within the chromosome.
-Moreover, the same crossover operations are applied to this new chromosome, as those applied to the main chromosome, and this for the same crossing points.
-Thus, during an exchange of genes, children also inherit the mutation rates specific for each of these genes.
+The main advantage is that the automatic tuning of the mutation can be made much more precise \citep{Smith1997a}.
+Thus, a second chromosome containing the mutation rate for each gene of the first chromosome is considered.
+The operations of mutation and self-mutation are similar to the case of the individual adaptive mutation rate, but proceed in a distributed manner within the chromosome.
+Moreover, the same crossover operations are applied to this new chromosome as to the main chromosome, and for the same crossing points.
+Thus, during an exchange of genes, children also inherit the mutation rates specific to each of these genes.
 
-	\item Chromosome of adaptive search radius: in this operator, we combined the operations of the chromosome of adaptive mutation rate to the adaptive search radius approach.
-Similarly, an individual has three chromosomes: the first containing the values to be optimized, the second the distributed mutation rate, and the last one, the distributed search radius.
+	\item Chromosome of adaptive search radius: In this operator, we combine the operations of the chromosome of adaptive mutation rate with the adaptive search radius approach.
+Similarly, an individual has three chromosomes.
+The first contains the values to be optimized, the second the distributed mutation rate, and the third the distributed search radius.
 Again, no external parameter is required.
 
-	\item Multi-scale mutation: finally, we developed another approach that is also based on the search radius concept.
-However, the latter is not decreasing with time.
-Methods based on a reduction of the mutation rate or radius simulate a transition from the exploration phase to the exploitation one.
-The idea here was to test an approach that combines both exploration and exploitation during the whole optimization.
+	\item Multi-scale mutation: Finally, we developed another approach that is also based on the search radius concept.
+However, in this one the radius does not decrease with time.
+Methods based on a reduction of the mutation rate or radius simulate a transition from the exploration phase to the exploitation phase.
+Here, the idea is to test an approach that combines both exploration and exploitation during the whole optimization process.
 Thus, the search radius $r_{a}$ of Eq.
-(\ref{eq:adaptive_search_radius_mutation}) was considered as a random value for each individual, but restricted to four equiprobable values: 1, 0.5, 0.1, 0.02, so a range from full exploration to fine exploitation.
-The only external parameter is the mutation rate which is fixed.
+(\ref{eq:adaptive_search_radius_mutation}) is considered as a random value for each individual, but restricted to four equiprobable values, 1, 0.5, 0.1, and 0.02, representing a range from full exploration to fine exploitation.
+The only external parameter is the mutation rate, which is fixed.
 
@@
 
-A process of elitism was introduced after both the natural selection and mutations.
-This ensures the survival of the best individual so that a better solution is never lost.
-After the natural selection operator, if the previously best individual has not been selected, it was copied to the IG instead of an individual randomly picked.
-After mutation, if the previously best individual has mutated and if its new version has a lower performance score than the original, the latter was also reinserted in the IG instead of an individual randomly chosen.
+The process of elitism is introduced after both natural selection and mutations.
+This ensures the survival of the best individual, so that a superior solution is never lost.
+After the natural selection operation, if the previous best individual has not been selected, then it is copied to the IG in place of a randomly selected individual.
+After mutation, if the previous best individual has mutated and its new version has a lower performance score than the original, then the original is also reinserted in the IG in place of a randomly selected individual.
 
@@
 
-The convergence check determines whether the solution is acceptable and if the algorithm may stop.
-The optimization was here stopped if the best individual did not change for $x$ generations.
-This value should not be too low to allow the algorithm to escape from a local optima, and because the rate of improvement decreases with the progression of the optimization.
-It is thus common that the best individual does not evolve over several generations when getting closer to the global solution.
-A value of $x=20$ generations was chosen.
+The convergence check determines whether the solution is acceptable, and if the algorithm may stop.
+Here, the optimization is stopped if the best individual does not change for $x$ generations.
+This value should not be too low, in order to allow the algorithm to escape from local optima, and because the rate of improvement decreases with the progression of the optimization.
+Thus, it is common that the best individual does not evolve over several generations when getting closer to the global solution.
+A value of $x=20$ generations is chosen.
 
@@
 
-GAs are very computationally intensive because they require many evaluations of the objective function.
-These assessments are take some time (couple of seconds) in this application, as they require calculating and assessing a prediction for every day of the calibration period, thus over several decades.
-In order to reduce the computation time, the performance score of an individual who had previously been evaluated, and that had not changed, was preserved.
-Thus, the score of each individual living in the selection was kept until it mutated.
+GAs are computationally very intensive because they require many evaluations of the objective function.
+These assessments require some time (a couple of seconds each) in this application, as they require the calculation and assessment of a prediction for every day of the calibration period, which spans several decades.
+In order to reduce the computation time, the performance score of an individual, who has previously been evaluated and has not changed, is preserved.
+Thus, the score of each individual living in the selection is preserved until it mutates.
 
-As the calculation of the objective function of each member of the population of a generation is completely independent, they were processed in parallel on different cpus.
-In order to perform optimizations for multiple time series, the use of a cluster is a necessity.
+Because the calculation of the objective function for each member of the population of a generation is completely independent, they are processed in parallel on different CPUs.
+In order to perform optimizations for multiple time series, the use of a cluster is necessary.
 
-Some constraints need to be taken into account.
-For example, when a crossover or a mutation operation results in a parameter value standing out of the authorized bounds, it has to be brought back within the limits.
+Some constraints must be taken into account.
+For example, when a crossover or mutation operation results in a parameter value that is outside of the authorized bounds, this must be brought back within the limits.
 Moreover, the parameters are of different types: continuous, discrete, or categorical (e.g., the selection of the meteorological variable).
-New values resulting from the optimizer need to respect the type of data they represent.
-Other constraints exist in between the parameters, e.g., the temporal windows of the relative humidity and the precipitable water predictors have to match when processing the moisture index.
+New values resulting from the optimizer need to respect the type of data that they represent.
+Other constraints exist between the parameters, e.g., the temporal windows of the relative humidity and the precipitable water predictors must match when processing the moisture index.
 
@@
 
-The choice of GAs options, such as the mutation rate, population size, natural selection, etc, appears difficult given the high number of existing variants, each developed for a specific problem \citep{Haupt2004, Costa2007a}.
-Thus, different studies suggest very different configurations \citep{DeJong1975a, Grefenstette1986, Back1996a, Back1996b}.
+Choosing GA options, such as the mutation rate, population size, natural and selection, appears to be difficult given the high number of existing variants, each developed for a specific problem \citep{Haupt2004, Costa2007a}.
+Thus, different studies suggest significantly different configurations \citep{DeJong1975a, Grefenstette1986, Back1996a, Back1996b}.
 
-In the present study, the choice of the meteorological variables (predictors) was still performed manually.
-Then, GAs had to optimize jointly, for all levels of analogy, (i) the spatial windows (position and size; different between the pressure levels), (ii) the temporal windows (hours of observation of the predictors), (iii) the number of analog situations, and (iv) later on, the selection of the pressure levels (two, in this case).
-The first experiments considered a single level of analogy (on the geopotential height, see section \ref{sec:am}), and a second level (on moisture) was added further on in section \ref{sec:assessment}\ref{sec:assessment:results}\ref{sec:assessment:mutation}.
+In the present study, the choice of meteorological variables (predictors) was still performed manually.
+Then, GAs were required to jointly optimize, for all levels of analogy, (i) the spatial windows (position and size, which can differ between the pressure levels), (ii) the temporal windows (hours of observation of the predictors), (iii) the number of analog situations, and (iv) eventually the selection of the pressure levels (two in this case).
+The first experiments considered a single level of analogy (on the geopotential height, see section \ref{sec:am}), and a second level (on moisture) was added later in section \ref{sec:assessment}\ref{sec:assessment:results}\ref{sec:assessment:mutation}.
 
@@
 
-The main goal of the present paper being to make recommendations on the use of GAs in order to optimize different AM variants, a systematic procedure was adopted.
-The results are summarized hereafter \citep[see][for the details]{Horton2012a}.
-In order to compare different configurations of GAs, a factorial design approach was applied, in a similar way as \citet{Costa2005a,Costa2007a} and \citet{Mariano2010a}.
-It allows isolating the effect of a parameter under different combinations of the other options.
+With the main goal of the present paper being to provide recommendations regarding the use of GAs to optimize different AM variants, a systematic procedure was adopted.
+The results are summarized in the following \citep[see][for the details]{Horton2012a}.
+In order to compare different configurations of GAs, a factorial design approach was applied, in a similar manner as in \citet{Costa2005a,Costa2007a} and \citet{Mariano2010a}.
+This allows the isolation of the effects of a parameter under different combinations of the other options.
 
-In order to evaluate a combination of operators/options, 10 optimizations per configuration of GAs were processed.
-With all combinations of GAs options, 21~630 optimizations were performed on an Intel Xeon based HPC cluster with 96 cpu, running Linux RedHat.
-Such assessment was not possible on the whole archive length, and had to be performed on a reduced calibration period: five years, from 1998 to 2002, but looking for analog dates on a 48 years period (1961-2008).
-The total resources needed for this comparison amount to 229~539 h cpu (26.2 yr cpu).
-One should remember that these intensive resources were needed in order to assess multiple combinations of GAs options in order to provide recommendations.
-Based on these, applying GAs to optimize AMs require some computational power, but not as much (the time needed is function of the archive length, the population number, GAs options, and the complexity of the AM to optimize).
+In order to evaluate a combination of operators/options, 10 optimizations were processed per configuration of GAs.
+For all combinations of GA options, 21~630 optimizations were performed on an Intel Xeon based HPC (High-performance computing) cluster with 96 CPU, running Linux RedHat.
+Such an assessment was not possible on the whole archive length, and had to be performed on a reduced calibration period of five years from 1998 to 2002, while looking for analog dates over a 48 year period (1961-2008).
+The total resources required for this comparison amounted to 229~539 h CPU (26.2 years CPU).
+One should remember that these intensive resources were required in order to assess multiple combinations of GA options, in order to provide recommendations.
+Based on these, applying GAs to optimize AMs requires some computational power, but not as much (the required time is a function of the archive length, the population number, GA options, and the complexity of the AM to be optimized).
 
@@
 
-After a first quick assessment, GAs were found to be successful at optimizing the considered AM implementations.
-Figure \ref{fig:gas_evolution_good} shows the evolution of the score of the best individuals over generations for 10 optimizations processed for a given configuration of GAs (same operators options).
+After a first quick assessment, GAs were found to be successful in optimizing the considered AM implementations.
+Figure \ref{fig:gas_evolution_good} illustrates the evolution of the score of the best individual over progressive generations for the 10 optimizations processed for a given configuration of GAs (with the same operator options).
 Seven out of 10 optimizations converged to the global optimum (dashed line at the top of the plot in Fig.
-\ref{fig:gas_evolution_good}) after 40 to 55 generations, which is not the best performance we observed later on.
-The performance score of the sequential approach (bottom line) has been quickly exceeded without adding any new parameter to the method (Fig.
+\ref{fig:gas_evolution_good}) after between 40 and 55 generations, which is not the best performance we will observe.
+The performance score of the sequential approach (bottom line) was quickly exceeded, without introducing any new parameters to the method (Fig.
 \ref{fig:gas_evolution_good}).
-The improvement was about 8.8\% in this case, which is substantial.
+The improvement was around 8.8\% in this case, which is substantial.
 
-Even GAs configurations that were later rejected, because they did not converge (Fig.
-\ref{fig:gas_evolution_bad}), did still significantly better that the sequential approach.
-GAs showed a promising potential at optimizing AMs automatically, globally, and objectively.
+Even GA configurations that were later rejected, because they did not converge (Fig.
+\ref{fig:gas_evolution_bad}), performed significantly better than the sequential approach.
+GAs displayed a promising potential for optimizing AMs automatically, globally, and objectively.
 
@@
 The results of the factorial design procedure illustrate the effect of an operator when its contribution is isolated from the other operators.
-It means that we analyzed the effect of a given operator for equivalent conditions (same settings of other operators), while assessing multiple combinations of these.
-This contribution was then summarized as a percentage of gain/loss regarding the mean of all variants, for equivalent external conditions.
-For example, to evaluate the performance of the uniform crossover operator, its performance was compared to the average of all crossover operators, while retaining the same population size, the same mutation, natural selection, and couples selection operators.
+This means that we analyzed the effects of a given operator for equivalent conditions (with the same settings for other operators), while assessing multiple combinations of these.
+This contribution was then summarized as a percentage of gain/loss with respect to the mean of all variants, for equivalent external conditions.
+For example, to evaluate the performance of the uniform crossover operator, its performance was compared to the average of all crossover operators, while retaining the same population size, same mutation, natural selection, and couples selection operators.
 
-From the very beginning of the assessments, the importance of the mutation operator was obvious \cite[see][for the details]{Horton2012a}, and its leading influence on the optimization performance was evident.
-Its role is analyzed later on in section \ref{sec:assessment}\ref{sec:assessment:results}\ref{sec:assessment:mutation}.
+From the start of the assessments, the importance of the mutation operator was obvious \cite[see][for details]{Horton2012a}, and its leading influence on the optimization performance was evident.
+Its role is analyzed later, in section \ref{sec:assessment}\ref{sec:assessment:results}\ref{sec:assessment:mutation}.
 
@@
 
-Every combination of six options for the couples selection (Fig.
-\ref{fig:operator_selectcoupl_score}) and 21 for the chromosome crossover operators (Fig.
-\ref{fig:operator_crossover_score}) were evaluated, along with variants of the other operators.
+Each combination of the six options for the couples selection (Fig.
+\ref{fig:operator_selectcoupl_score}) and 21 options for the chromosome crossover operators (Fig.
+\ref{fig:operator_crossover_score}) was evaluated, along with variants of the other operators.
 This resulted in 1~008 combinations, requiring 10~080 optimizations.
 
-The performances of the couples selection operators were relatively close (Fig.
+The performances of the couples selection operators were relatively similar (Fig.
 \ref{fig:operator_selectcoupl_score}).
-Overall, the tournament selection with three candidates was slightly superior to others, along with the roulette wheel weighting.
-This last one was however a bit less effective in terms of convergence and number of evaluations (not shown).
-The couples selection operator had no significant role in this application.
+Overall, the tournament selection with three candidates performed slightly better than the others, along with the roulette wheel weighting.
+However, the latter was a little less effective in terms of convergence and the number of evaluations (not shown).
+The couples selection operator played no significant role in this application.
 
-As for crossover operators (Fig.
-\ref{fig:operator_crossover_score}), binary-like crossover (especially with two points of intersection, whether $\beta$ is shared or not) was a bit better than the others, especially in terms of convergence (not shown).
+As for the crossover operators (Fig.
+\ref{fig:operator_crossover_score}), binary-like crossover (especially with two points of intersection, whether $\beta$ is shared or not) performed slightly better than the others, especially in terms of convergence (not shown).
 
@@
 
-Having identified the leading role of the mutation operator, the next sensitivity analysis focused on it.
-The 10 different implementations (see section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:mutation}) were tested, with different options (Fig.
-\ref{fig:operator_mutation_score}), bringing the number of variations up to 109.
-Some optimizations without any mutation were also performed as a reference.
-Along with variants of the other operators \citep[see][for the details]{Horton2012a}, this resulted in 660 combinations (so 6~600 optimizations).
+Having identified the leading role of the mutation operator, the following sensitivity analysis focuses on it.
+The 10 different implementations (see section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:mutation}) were tested with different options (Fig.
+\ref{fig:operator_mutation_score}), bringing the number of variations to 109.
+Some optimizations with no mutation were also performed as a reference.
+Along with variants of the other operators \citep[see][for details]{Horton2012a}, this resulted in 660 combinations (and so 6~600 optimizations).
 
-Figure \ref{fig:operator_mutation_score} show the results of this analysis and illustrates the important role of mutation on the optimization performance.
-Configurations without mutation (last box on Fig.
-\ref{fig:operator_mutation_score}) were inferior to most mutation operators, and the magnitude of this operator influence was significantly higher than those of the other options.
-The details of the analysis \citep[see][]{Horton2012a} showed that the other reproduction operators seem of secondary importance.
-This observation is in line with the conclusions made by several other authors (see section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:mutation}).
+Figure \ref{fig:operator_mutation_score} presents the results of this analysis, and illustrates the important role of mutation on the optimization performance.
+Configurations without mutation (the last box in Fig.
+\ref{fig:operator_mutation_score}) achieved an inferior performance compared to most mutation operators, and the magnitude of this operator influence was significantly higher than those of the other options.
+The details of the analysis \citep[see][]{Horton2012a} indicate that the other reproduction operators seem to be of secondary importance.
+This observation is in line with the conclusions reached by several other authors (see section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:mutation}).
 
-The mutation operators based on variable normal or variable uniform laws worked very poorly here and were difficult to configure.
-Many operators presented more or less the same performance scores and required a variable amount of assessments.
-The convergence analysis \citep[see][]{Horton2012a} allowed to highlight three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
-Thus, different optimizations (an additional 4~950) were further performed using variants of these three operators (Fig.
+The mutation operators based on variable normal or variable uniform laws performed particularly poorly here, and were difficult to configure.
+Many operators presented more or less similar performance scores, and required a variable amount of assessments.
+The convergence analysis \citep[see][]{Horton2012a} highlighted the three best operators: non-uniform mutation, chromosome of adaptive search radius, and multi-scale mutation.
+Thus, further optimizations (an additional 4~950) were performed, using variants of these three operators (Fig.
 \ref{fig:operator_mutation_score_atmlevel}-\ref{fig:operator_mutation_score_r4}).
 
-The first analysis was the optimization of the precipitation prediction over a subcatchment (Binn-Simplon region) in the Swiss Alps (Fig.
+The first analysis was the optimization of the precipitation prediction over a subcatchment (the Binn-Simplon region) in the Swiss Alps (Fig.
 \ref{fig:operator_mutation_score_atmlevel}).
-The optimizer could also choose the two pressure levels of the atmospheric circulation analogy (method with a single level of analogy).
-The resulting CRPSS performance score (section \ref{sec:am}) was obviously superior to the one obtained by the sequential calibration (bottom line on Fig.
+The optimizer also chose the two pressure levels of the atmospheric circulation analogy (this method has a single level of analogy).
+The resulting CRPSS performance score (see section \ref{sec:am}) was obviously superior to that obtained using the sequential calibration (bottom line in Fig.
 \ref{fig:operator_mutation_score_atmlevel}).
-For most options, it was also slightly better than the results from the optimization without selection of the pressure levels (dashed line).
-A clear breakthrough of the performances was not expected, as the former selection of pressure levels results from intensive comparative work \citep{Bontron2004}.
-This application however demonstrates that, when correctly configured, GAs can automatically and successfully choose the pressure levels.
-However, the automatic selection of the pressure levels significantly increased the difficulty for GAs to converge to a unique solution, ideally the global optimum.
-A likely explanation is that the pressure levels were considered as categorical values within the optimization (sampled with a uniform law), and thus the approaches relying on distance in the parameters space, such as the search radius, could not fully exploit the properties that made them efficient.
-However, even though the results showed a certain variability, most of them presented very good performance scores, despite different selection of AM parameters.
+For most options, it also achieved slightly better results than the optimization without the selection of the pressure levels (dashed line).
+A clear breakthrough in the performance was not expected, as the former selection of pressure levels is the result of intensive comparative work \citep{Bontron2004}.
+However, this application demonstrates that when correctly configured, GAs can automatically and successfully choose the pressure levels.
+However, the automatic selection of the pressure levels significantly increased the difficulty for the GAs to converge to a unique solution, ideally the global optimum.
+A likely explanation for this is that the pressure levels were considered as categorical values within the optimization (sampled with a uniform law), and thus the approaches relying on a distance in the parameters space, such as the search radius, could not fully exploit the properties that made them efficient.
+However, even though the results exhibit a certain variability, most of them present very good performance scores, despite different selections of the AM parameters.
 
@@
 \ref{fig:map}), which is sensitive to other meteorological influences (Fig.
-\ref{fig:operator_mutation_score_rhoneamont}), in order to assess eventual dependencies of the operators with the predictand.
+\ref{fig:operator_mutation_score_rhoneamont}), in order to assess the eventual dependencies of the operators with the predictand.
 Even though differences can be observed with Fig.
-\ref{fig:operator_mutation_score_atmlevel}, it is globally the same options that perform better.
+\ref{fig:operator_mutation_score_atmlevel}, the same options perform better globally.
 
 Next, a second level of analogy was introduced (Fig.
-\ref{fig:operator_mutation_score_r2}) based on moisture variables (section \ref{sec:am}).
-GAs had to optimize both levels of analogy (geopotential height and moisture index) simultaneously.
-Once again, the results were better than the sequential calibration (bottom line on Fig.
+\ref{fig:operator_mutation_score_r2}), based on moisture variables (see section \ref{sec:am}).
+The GAs had to optimize both levels of analogy (geopotential height and moisture index) simultaneously.
+Once again, the results were better than those for the sequential calibration (bottom line on Fig.
 \ref{fig:operator_mutation_score_r2}).
-And finally, a preselection on air temperature was added instead of the fixed calendar window, as proposed by \cite{BenDaoud2016}.
+Finally, a preselection based on air temperature was added, instead of the fixed calendar window, as proposed by \cite{BenDaoud2016}.
 The results showed generally higher scores (Fig.
-\ref{fig:operator_mutation_score_r4}), demonstrating the success of the optimizer to take advantage of this new degree of freedom, and its ability to handle optimization of three analogy levels jointly.
-Again, the most relevant options were globally the same.
+\ref{fig:operator_mutation_score_r4}), demonstrating the success of the optimizer in taking advantage of this new degree of freedom, and its ability to handle the optimization of three analogy levels simultaneously.
+Again, the most relevant options were the same globally.
 
-After these various tests of the mutation operators relevance, the following advices can be raised (detailed options are provided in section \ref{sec:use}\ref{sec:recommendations}):
+Following these various tests of the relevance of the mutation operators, the following advice can be presented (detailed options are provided in section \ref{sec:use}\ref{sec:recommendations}):
 
@@
 
-	\item \textit{Non-uniform mutation}: this operator was good in terms of convergence, mainly when the number of parameters to optimize is rather low.
-The number of required evaluations, however, can be quite substantial.
-The main disadvantage of the non-uniform mutation is the number of parameters it requires, that are difficult to estimate a priori.
-The mutation rate was found to be more important than the others.
+	\item \textit{Non-uniform mutation}: This operator performed well in terms of convergence, mainly when the number of parameters to optimize was rather low.
+However, the number of required evaluations can be fairly substantial.
+The main disadvantage of the non-uniform mutation is the number of parameters it requires, which are difficult to estimate a priori.
+The mutation rate was found to be more important than for the others.
 The difficulty is that its optimal value may be case-related.
 
-	\item \textit{Chromosome of adaptive search radius}: unlike the previous one, the proposed operator is very robust, as it requires no option and is auto-adapting.
-It is interesting to notice that the insertion of an extra chromosome representing the search radius gave better performance than other self-adaptive operators (such as, for example, the chromosome of adaptive mutation rate).
-If one had to choose a single option for the mutation operator, we would recommend this one, as it was proven effective and needs no parameter.
+	\item \textit{Chromosome of adaptive search radius}: Unlike in the above case, this proposed operator is very robust, as it requires no options and is auto-adapting.
+It is interesting to note that the insertion of an extra chromosome representing the search radius resulted in a better performance than other self-adaptive operators (such as the chromosome of adaptive mutation rate).
+If one had to choose a single option for the mutation operator, we would recommend this one, as it was proven effective and requires no parameter.
 
-	\item \textit{Multi-scale mutation}: finally, the multi-scale mutation, which also performed pretty well, requires one parameter, the mutation rate.
+	\item \textit{Multi-scale mutation}: Finally, the multi-scale mutation, which also performed fairly well, requires one parameter, the mutation rate.
 However, it can also be difficult to estimate a correct value a priori.
@@
 
-In this application, the mutation operator has a leading effect and should be chosen with care.
-It may be wise to perform multiple optimizations and to consider these three operators in parallel in order to obtain results from options that are sometimes either more efficient or more robust.
+For this application, the mutation operator has a leading effect, and should be chosen with care.
+It may be wise to perform multiple optimizations, and to consider these three operators in parallel, in order to obtain results from options that are sometimes either more efficient or more robust.
 It is interesting to note that the three best techniques incorporate a notion of search distance.
-It is likely that this notion is the key to these algorithms, for this application, and allows them to initially explore the parameter space, and then to converge.
-The search radius in fact directly represents the notion of transition between exploration and exploitation, in our opinion more than a possible evolution of mutation rates.
+It is likely that this notion is the key to these algorithms in this application, and allows them to initially explore the parameter space and then converge.
+In fact, the search radius directly represents the notion of transition between exploration and exploitation, in our opinion more than a possible evolution of mutation rates.
 
@@
 The analysis of the natural selection operator (Fig.
-\ref{fig:operator_selectnat_score}) revealed a slight preference for the ratio-elitism compared to the tournament selection, but not so significant.
+\ref{fig:operator_selectnat_score}) revealed a slight preference for ratio-elitism compared to the tournament selection, but this was not very significant.
 This operator, or at least the two assessed versions, did not appear to significantly influence the optimization performance.
@@
 \ref{fig:option_taillepop_score}).
-A bigger population led to better results, but also to longer optimizations: the required number of evaluation, and thus the required time, was approximately proportional to the population size.
-Thus, if the population size doubled, the time required for the optimization also nearly doubled (e.g., for a five years calibration period, approximately 4~h cpu were needed when $N = 50$, and 14~h cpu when $N = 200$).
-The optimal size seems to depend on the complexity of the AM to optimize: a more complex AM (i.e., with more degrees of freedom) requires a bigger population size.
-A rule of thumb based on a limited number of case studies (not shown here) is provided hereafter:
+A bigger population led to better results, but also to longer optimizations.
+The required number of evaluations, and thus the required time, was approximately proportional to the population size.
+Thus, if the population size doubled, then the time required for the optimization also nearly doubled (e.g., for a five year calibration period, approximately 4~h CPU were required when $N = 50$, and 14~h CPU when $N = 200$).
+The optimal size seems to depend on the complexity of the AM to be optimized.
+A more complex AM (i.e., with more degrees of freedom) requires a bigger population size.
+A rule of thumb based on a limited number of case studies (not presented here) is provided as follows:
 
@@
 	\item $N\approx100$ for very simple AM implementations (one level of analogy with two pressure levels),
-	\item $N\approx200$ for a slightly more complex AM (one level of analogy with four pressure levels, or two level of analogy with less pressure levels),
-	\item $N\approx500$ for significantly more complex AMs (two to three levels of analogy with four pressure levels for the atmospheric circulation, and two to four levels for the moisture analogy).
+	\item $N\approx200$ for a slightly more complex AM (one level of analogy with four pressure levels, or two levels of analogy with fewer pressure levels),
+	\item $N\approx500$ for significantly more complex AMs (two or three levels of analogy with four pressure levels for the atmospheric circulation, and two to four levels for the moisture analogy).
 \end{itemize}
@@
 This option had little influence on the performance of the optimizations.
-A value of 50~\% seems a wise choice.
+A value of 50~\% seems to be a wise choice.
 
@@
 
-Optimizations by GAs of AMs of varying complexities were performed with a large number of combinations of operators in order to make recommendations for optimizing AMs (section \ref{sec:assessment}).
-The conclusions are:
+Optimizations using GAs of AMs of varying complexities were performed with a large number of combinations of operators, in order to make recommendations for optimizing AMs (see section \ref{sec:assessment}).
+The conclusions are as follows:
 
 \begin{itemize}
-	\item The population size should be in accordance with the complexity of the AM to optimize: from 100 for the simple ones, up to 500 for the most complex AMs.
+	\item The population size should be in accordance with the complexity of the AM to be optimized, ranging from 100 for simple cases up to 500 for the most complex AMs.
 
-	\item The value of the IG ratio is not so important; a value of 50\% seems appropriate.
+	\item The value of the IG ratio is not significantly important. A value of 50\% seems appropriate.
 
-	\item Ratio-elitism is slightly better than tournaments for the natural selection operator, but it is not decisive.
+	\item Ratio-elitism performs slightly better than tournaments for the natural selection operator, but this is not decisive.
 
-	\item The performance of the operators for the couples selection are relatively equivalent.
-The roulette wheel weighting and the tournament selection are more efficient in terms of convergence and required number of evaluations.
+	\item The performance of the operators for the couples selection are relatively similar.
+The roulette wheel weighting and the tournament selection are more efficient in terms of the convergence and required number of evaluations.
 
-	\item Most crossover operators have relatively similar performance, but the binary-like crossover with two points of intersection is a bit better, especially for convergence.
+	\item Most of the crossover operators yield a relatively similar performance, but the binary-like crossover with two points of intersection is slightly better, especially in terms of convergence.
 
-	\item Mutation has a clearly dominant influence.
-Three mutation operators stand out: the non-uniform mutation, the multi-scale mutation, and the chromosome of adaptive search radius.
-The latter is the most robust as it has no controlling parameter.
+	\item Mutation clearly yields a dominant influence.
+Three mutation operators stand out: the non-uniform mutation, multi-scale mutation, and chromosome of adaptive search radius.
+The latter is the most robust, as it has no controlling parameter.
 
@@
 
-The optimization did not systematically converge to the global optimum (but often close to it), which is why it is recommended to do several optimizations in parallel in order to compare the results, analyze the convergence, and keep the best.
+The optimization did not systematically converge to the global optimum (but often close to it), which is why it is recommended to performs several optimizations in parallel in order to compare the results, analyze the convergence, and keep the best configuration.
 It may be wise to consider the three mutation operators in parallel.
@@
 	\setlength\itemsep{-4px}
-	\item once the non-uniform mutation, with $p_{mut}=0.05$, $G_{m,r}=50$, $\omega=0.1$
-	\item once the non-uniform mutation, with $p_{mut}=0.05$, $G_{m,r}=100$, $\omega=0.1$
-	\item once the non-uniform mutation, with $p_{mut}=0.1$, $G_{m,r}=100$, $\omega=0.1$
-	\item once the multi-scale mutation, with  $p_{mut}=0.1$
-	\item twice the chromosome of adaptive search radius
+	\item the non-uniform mutation once, with $p_{mut}=0.05$, $G_{m,r}=50$, $\omega=0.1$
+	\item the non-uniform mutation once, with $p_{mut}=0.05$, $G_{m,r}=100$, $\omega=0.1$
+	\item the non-uniform mutation once, with $p_{mut}=0.1$, $G_{m,r}=100$, $\omega=0.1$
+	\item the multi-scale mutation once, with  $p_{mut}=0.1$
+	\item the chromosome of adaptive search radius twice
 \end{itemize}
 
-where $p_{mut}$ is the mutation rate (or mutation probability), $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a threshold chosen by the user to maintain a minimum search radius when the number of generations $G>G_{m,r}$.
+where $p_{mut}$ is the mutation rate (or mutation probability), $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a threshold chosen by the user in order to maintain a minimum search radius when the number of generations $G>G_{m,r}$.
 
@@
 
-In order to illustrate the gain achievable by GAs on an AM, precipitation prediction for the Southeast ridges region of the alpine Rh\^{o}ne catchment (Fig.
-\ref{fig:map}) was optimized for the whole calibration period (40 years in the 1961-2008 period, leaving out 8 years for validation), instead of the smaller five years period.
+In order to illustrate the achievable gain by using GAs on an AM, precipitation prediction for the southeast ridges region of the alpine Rh\^{o}ne catchment (Fig.
+\ref{fig:map}) was optimized for the whole calibration period (40 years in the period 1961-2008, with eight years omitted for validation), instead of the smaller five year period.
 
-The optimizer could select the geopotential height at four pressure levels, at any time of the day, on unconstrained spatial windows.
-Moreover, a weighting was introduced in the combination of the criteria processed on each pressure level \citep[such as][]{Horton2012a, Junk2015}.
+The optimizer could select the geopotential height at four pressure levels, at any time of day, on unconstrained spatial windows.
+Moreover, a weighting was introduced to the combination of the criteria processed on each pressure level \citep[such as in][]{Horton2012a, Junk2015}.
 In this case, no new meteorological variable was added, and the method still contained a unique level of analogy.
 
-The performance (CRPSS) of the reference method calibrated by means of the sequential procedure amounts to 32.00\%, with a 0.95 confidence interval (assessed by bootstrapping on 10~000 samples) of (29.21\%; 34.94\%).
-The method optimized by means of GAs reached a performance of 37.62\%, with a 0.95 confidence interval of (35.21\%; 40.11\%).
-The resulting gain is thus statistically significant.
-The results on all subregions and the physical meaning of the optimized parameters will be discussed in a coming paper.
+The performance (CRPSS) of the reference method, calibrated by means of the sequential procedure, amounts to 32.00\%, with a 0.95 confidence interval (assessed by bootstrapping on 10~000 samples) of (29.21\%; 34.94\%).
+The method optimized by means of GAs achieved a performance of 37.62\%, with a 0.95 confidence interval of (35.21\%; 40.11\%).
+Thus, the resulting gain is statistically significant.
+The results on all subregions and the physical meaning of the optimized parameters will be discussed in a forthcoming paper.
 
@@
 
-In order to automatically optimize several AM variants and to get rid of the limitations of the usual sequential calibration, GAs were evaluated.
-Given the large number of existing operators and options, multiple variants were assessed systematically in order to identify which operators are important, and which variants work best for the considered AM implementations.
-The mutation operator was identified as a key element for this application, and new variants that proved efficient were developed, such as the chromosome of adaptive search radius that is very robust (no control parameter).
-Recommendations were established for a relevant use of GAs for the optimization of AMs.
-If using GAs to optimize AMs is computationally intensive, once an AM is calibrated, its use in real-time operations it very fast and lightweight.
+In order to automatically optimize several AM variants, and to avoid the limitations of the usual sequential calibration, GAs were evaluated.
+Given the large number of existing operators and options, multiple variants were assessed systematically in order to identify which operators are important, and which variants perform best for the considered AM implementations.
+The mutation operator was identified as a key element for this application, and new variants were developed that proved efficient, such as the chromosome of adaptive search radius, which is considerably robust (with no control parameter).
+Recommendations were established for the relevant employment of GAs for optimizing AMs.
+Although using GAs to optimize AMs may be computationally intensive, once an AM is calibrated, its use in real-time operations it very fast and lightweight.
 
-It is not excluded that another global optimization method or other operators of GAs may perform even better.
-Still, the relevance of global optimization techniques for AMs has now been proven, as they provide relevant AM parameters that are automatically, globally and objectively established.
-A global optimization is the only way to take into account all the dependencies between parameters and levels of analogy.
+The possibility that a different global optimization method or other operators of GAs may perform even better cannot be excluded.
+Still, the relevance of global optimization techniques for AMs has now been proven, as they provide relevant AM parameters that are automatically, globally, and objectively established.
+A global optimization is the only way to take into account all of the dependencies between parameters and levels of analogy.
 
-The global optimization approach allows easily adapting AMs to new regions by potentially taking into account local meteorological influences, and has thus a great potential of use.
-Moreover, it can be used to explore automatically datasets in order to extract the most relevant variables.
-It would be thus easier to assess other predictands, such as the temperature, the limit of snowfall, the occurrence of hail, etc, while leaving the algorithms select the best variables and the associated parameters.
+The global optimization approach allows the easy adaptation of AMs to new regions by potentially taking into account local meteorological influences, and thus has a significant potential for application.
+Moreover, it can be employed to automatically explore datasets, in order to extract the most relevant variables.
+Thus, this method can make it easier to assess other predictands, such as the temperature, limit of snowfall, or occurrence of hail, while allowing the algorithms to select the best variables and associated parameters.
 
@@
 Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of.
-Thanks to Dominique B\'{e}rod for his support and to Michel Bierlaire for his advices on optimization methods.
+Thanks to Dominique B\'{e}rod for his support, and to Michel Bierlaire for his advice regarding optimization methods.
 
-Thanks to the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton, the Water, Land and Sanitation Service of the Vaud Canton, and the Swiss Federal Office for Environment (FOEV) who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
+Thanks to the Roads and Water Courses Service, Energy and Water Power Service of the Wallis Canton, the Water, Land and Sanitation Service of the Vaud Canton, and the Swiss Federal Office for Environment (FOEV), who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project, which started this research.
 The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
-NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.
-Precipitation time series provided by MeteoSwiss.
+NCEP reanalysis data was provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.
+Precipitation time series were provided by MeteoSwiss.
 
@@
 	\centerline{\includegraphics[width=19pc,angle=0]{fig01.pdf}}
-	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland, and its discretization in 10 subregions:	(1) Swiss Chablais, (2) Trient Valley, (3) West Bernese Alps, (4) Lower Rhone Valley, (5) Left side valleys, (6) Southern ridges, (7) Upper Rhone Valley, (8) Southeast ridges, (9) East Bernese Alps, (10) Conches Valley.
+	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland, and its discretization into 10 subregions:	(1) Swiss Chablais, (2) Trient Valley, (3) West Bernese Alps, (4) Lower Rhone Valley, (5) Left side valleys, (6) Southern ridges, (7) Upper Rhone Valley, (8) Southeast ridges, (9) East Bernese Alps, (10) Conches Valley.
 (source: Swisstopo)}
@@
 	\end{center}
-	\caption{Genetic Algorithms operational flowchart.}
+	\caption{Genetic algorithms operational flowchart.}
 	\label{fig:structure_gas}
@@
 	\end{center}
-	\caption{Evolution of the score of the best individuals over generations for the 10 optimizations processed for a given configuration.
-The continuous bottom line represents the score of the sequential approach and the dashed one (top), the supposed global optimum.
+	\caption{Evolution of the score of the best individual over each generation for the 10 optimizations processed for a given configuration.
+The continuous bottom line represents the score of the sequential approach, and the dashed line (top) shows the supposed global optimum.
 The circles represent the end of the optimization (when the best individual did not progress during 20 generations).}
@@
 	\end{center}
-	\caption{Same as Fig. \ref{fig:gas_evolution_good}, but for a GAs configuration considered as less relevant.}
+	\caption{Same as Fig. \ref{fig:gas_evolution_good}, but for a GA configuration considered to be less relevant.}
 	\label{fig:gas_evolution_bad}
@@
 $\beta$s represent a shared $\beta$ parameter, and $\beta$u the unshared version.
-Same conventions as Fig.
+The same conventions apply as in Fig.
 \ref{fig:operator_selectcoupl_score}.}
@@
 In parentheses is the number of variants considered (combination of options).
-Same conventions as Fig.
+The same conventions apply as in Fig.
 \ref{fig:operator_selectcoupl_score}.}
@@
 	\end{center}
-	\caption{Influence of the mutation options (section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:mutation}) on the optimization performance, leaving the optimizer choose the pressure level of the atmospheric circulation analogy (single level of analogy).
+	\caption{Influence of the mutation options (section \ref{sec:gas}\ref{sec:gas:operators}\ref{sec:gas:mutation}) on the optimization performance, letting the optimizer choose the pressure level of the atmospheric circulation analogy (single level of analogy).
 For the non-uniform mutation, $\omega=0.1$ in every case.
-The continuous bottom line represents the score of the sequential calibration and the dashed superior line, the score of the optimization without automatic selection of the pressure levels.
-Same conventions as Fig.
+The continuous bottom line represents the score of the sequential calibration, and the dashed superior line is the score of the optimization without automatic selection of the pressure levels.
+The same conventions apply as in Fig.
 \ref{fig:operator_selectcoupl_score}.}
@@
 	\end{center}
-	\caption{Influence of the natural selection operators on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
+	\caption{Influence of the natural selection operators on the optimization performance. The same conventions apply as in Fig. \ref{fig:operator_selectcoupl_score}.}
 	\label{fig:operator_selectnat_score}
@@
 	\end{center}
-	\caption{Influence of the population size on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
+	\caption{Influence of the population size on the optimization performance. The same conventions apply as in Fig. \ref{fig:operator_selectcoupl_score}.}
 	\label{fig:option_taillepop_score}
@@
 	\end{center}
-	\caption{Influence of the intermediate generation (IG) ratio on the optimization performance. Same conventions as Fig. \ref{fig:operator_selectcoupl_score}.}
+	\caption{Influence of the intermediate generation (IG) ratio on the optimization performance. The same conventions apply as in Fig. \ref{fig:operator_selectcoupl_score}.}
 	\label{fig:option_popratio_score}

### 2016-09-22 Genetic algorithms - MWR/template.tex
Obled's corrections.

@@
 This dataset is relatively old, although it is still widely used, and better results may be expected with more recent datasets.
-However, we can safely assume that if an optimization technique works for this reanalysis dataset, it will also work for an improved one.
+However, we can safely assume that if an optimization technique works for this reanalysis dataset, it will also work for an improved one, although the resulting parameters might differ.
 
@@
 
-AMs are based on the principle that two similar synoptic situations may result in similar local effects \citep{Lorenz1956, Lorenz1969}.
-Thus, they consist in searching for a certain number of past situations in a meteorological archive that present similar properties for chosen predictors, according to an analogy criteria, in order to extract the observed values of the local weather variable of interest from another archive (predictand time series, see section \ref{sec:case_study_data}\ref{sec:data}).
+AMs are based on the principle that two similar synoptic situations over a certain domain may result in similar local effects \citep{Lorenz1956, Lorenz1969}.
+Thus, they consist in searching for a certain number of past situations in a meteorological archive that present similar properties for chosen predictors, according to an analogy criterion, in order to extract the observed values of the local weather variable of interest from another archive (predictand time series, see section \ref{sec:case_study_data}\ref{sec:data}).
 Based on these analog observations, the conditional empirical distribution to be considered as the probabilistic prediction for the target day (the day one wishes to predict) is constructed.
@@
 Predictors for precipitation predictions can be varied.
-For example, the geopotential height at different pressure levels and temporal windows, or humidity variables \citep[see][for a more detailed list of predictors]{BenDaoud2016}.
+For example, geopotential heights at different pressure levels and temporal windows, or humidity variables \citep[see][for a more detailed list of predictors]{BenDaoud2016}.
 This method often contains several levels of analogy, which constitute of successive subsamplings on predictors of different natures (e.g., atmospheric circulation, moisture variables, vertical motion, and air temperature).
@@
 The first level of analogy for precipitation prediction is often based on the atmospheric circulation.
-The similarity between the atmospheric circulation of the target date and the candidate situations is assessed based on the geopotential height (at specific pressure levels, such as 500 and 1000~hPa, and over a certain spatial window, e.g., 12~h and 24~h) by means of the S1 criteria \citep[Eq.
-(\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients over a defined spatial window.
-Various studies have found the S1 criteria to be more relevant than Euclidean distances for pressure fields \citep{Wilson1980, Woodcock1980, Guilbaud1998, Bontron2004}.
+The similarity between the atmospheric circulation of the target date and the candidate situations is assessed based on geopotential heights (at specific pressure levels, such as 500 and 1000~hPa, and at different hours, e.g., 12~h and 24~h) by means of the S1 criterion \citep[Eq.
+(\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}.
+This criterion is a comparison of gradients over a defined spatial window.
+Various studies have found the S1 criterion to be more relevant than Euclidean distances for pressure fields \citep{Wilson1980, Woodcock1980, Guilbaud1998, Bontron2004}.
 
@@
 Therefore, the $n_{1}$ analogs are subsampled once more on the basis of another variable, in order to obtain a lower number of analog dates, $n_{2}$.
-When the predictor is not a pressure field, the analogy criteria usually represents absolute distances, such as mean absolute error (MAE) or root mean squared error (RMSE), with the latter being most often employed.
+When the predictor is not a pressure field, the analogy criterion usually represents absolute distances, such as mean absolute error (MAE) or root mean squared error (RMSE), with the latter being most often employed.
 
@@
 
-	This process can be repeated by subsampling a decreasing number of analog dates, $n_{i}$, according to various meteorological variables.
-
-	\item Probabilistic prediction: Then, the daily observed amounts of precipitation for the $n_{i}$ resulting dates provide the empirical conditional distribution, considered as the probabilistic forecast for the target day.
+	This process can be repeated by subsampling a decreasing number of analog dates, $n_{i}$, when introducing successively more meteorological variables.
+
+	\item Probabilistic prediction: Then, the daily observed amounts of precipitation for the $n_{i}$ resulting dates provide an empirical conditional distribution, considered as the probabilistic forecast for the target day, eventually after the fitting of a probability law.
 
@@
 	\item The temporal window is the hour(s) of the day at which the predictors are considered.
-	\item The spatial window is the domain on which predictors are compared. The ideal size of this area is that which maximizes the useful information and minimizes noise.
+	\item The spatial window is the domain on which predictors are compared.
+The ideal size of this area is that which maximizes the useful information and minimizes noise.
+It may differ according to the meteorological variable used or to the number of analogy levels.
 	\item The analogy criterion, needed to compare the variables on the chosen spatial and temporal windows, is a distance measure, used to rank observed situations according to their degree of similarity with the target situation.
 	\item Eventual weights between the predictors \cite[e.g.,][]{Horton2012a, Junk2015}.
-	\item The ideal number of analog situations, which is the best compromise in order to take into account local variability and maximize useful synoptic information \citep{Bontron2004}.
+	\item The optimal number of analog situations, which is the best compromise in order to take into account local variability and maximize useful synoptic information \citep{Bontron2004}.
 \end{itemize}
@@
 Finally, (6) the new generation is then re-assessed, and the best individual restored if degraded.
-Then, (7) according to the ending criteria, the optimization either ends or begins again for another iteration.
+Then, (7) according to the ending criterion, the optimization either ends or begins again for another iteration.
 
@@
 Because the calculation of the objective function for each member of the population of a generation is completely independent, they are processed in parallel on different CPUs.
-In order to perform optimizations for multiple time series, the use of a cluster is necessary.
-
-Some constraints must be taken into account.
+In order to perform optimizations for multiple time series, the use of a computer cluster is necessary.
+
+Some constraints must also be taken into account.
 For example, when a crossover or mutation operation results in a parameter value that is outside of the authorized bounds, this must be brought back within the limits.
 Moreover, the parameters are of different types: continuous, discrete, or categorical (e.g., the selection of the meteorological variable).
-New values resulting from the optimizer need to respect the type of data that they represent.
 Other constraints exist between the parameters, e.g., the temporal windows of the relative humidity and the precipitable water predictors must match when processing the moisture index.
@@
 
-In the present study, the choice of meteorological variables (predictors) was still performed manually.
+In the present study, the choice of meteorological variables (predictors) was still imposed.
 Then, GAs were required to jointly optimize, for all levels of analogy, (i) the spatial windows (position and size, which can differ between the pressure levels), (ii) the temporal windows (hours of observation of the predictors), (iii) the number of analog situations, and (iv) eventually the selection of the pressure levels (two in this case).
-The first experiments considered a single level of analogy (on the geopotential height, see section \ref{sec:am}), and a second level (on moisture) was added later in section \ref{sec:assessment}\ref{sec:assessment:results}\ref{sec:assessment:mutation}.
+The first experiments considered a single level of analogy (on geopotential heights, see section \ref{sec:am}), and a second level (on moisture) was added later in section \ref{sec:assessment}\ref{sec:assessment:results}\ref{sec:assessment:mutation}.
 
@@
 One should remember that these intensive resources were required in order to assess multiple combinations of GA options, in order to provide recommendations.
-Based on these, applying GAs to optimize AMs requires some computational power, but not as much (the required time is a function of the archive length, the population number, GA options, and the complexity of the AM to be optimized).
+Based on these, applying GAs to optimize AMs requires some computational power, but to a lesser extent (the required time is a function of the archive length, the population number, GA options, and the complexity of the AM to be optimized).
 
@@
 Seven out of 10 optimizations converged to the global optimum (dashed line at the top of the plot in Fig.
-\ref{fig:gas_evolution_good}) after between 40 and 55 generations, which is not the best performance we will observe.
+\ref{fig:gas_evolution_good}) after between 40 and 55 generations, which is not even the best performance we will observe.
 The performance score of the sequential approach (bottom line) was quickly exceeded, without introducing any new parameters to the method (Fig.
@@
 
-The results of the factorial design procedure illustrate the effect of an operator when its contribution is isolated from the other operators.
+The results of the factorial design procedure illustrate the effect of an operator (e.g., mutation) when its contribution is isolated from the other operators.
 This means that we analyzed the effects of a given operator for equivalent conditions (with the same settings for other operators), while assessing multiple combinations of these.
@@
 However, the latter was a little less effective in terms of convergence and the number of evaluations (not shown).
-The couples selection operator played no significant role in this application.
+To summarize, the couples selection operator played no significant role in this application.
 
@@
 
-The mutation operators based on variable normal or variable uniform laws performed particularly poorly here, and were difficult to configure.
+The mutation operators based on variable normal or variable uniform laws performed particularly poorly here, and were difficult to setup.
 Many operators presented more or less similar performance scores, and required a variable amount of assessments.
@@
 \ref{fig:operator_mutation_score_r2}), based on moisture variables (see section \ref{sec:am}).
-The GAs had to optimize both levels of analogy (geopotential height and moisture index) simultaneously.
+The GAs had to optimize both levels of analogy (geopotential heights and moisture index) simultaneously.
 Once again, the results were better than those for the sequential calibration (bottom line on Fig.
@@
 
-The size of the population ($N$) had an effect on the optimization performance (Fig.
+The size of the population ($N$, the number of initial parameter sets) had an effect on the optimization performance (Fig.
 \ref{fig:option_taillepop_score}).
@@
 
-The optimizer could select the geopotential height at four pressure levels, at any time of day, on unconstrained spatial windows.
+The optimizer could select geopotential heights at four pressure levels, at any time of day, on unconstrained spatial windows.
 Moreover, a weighting was introduced to the combination of the criteria processed on each pressure level \citep[such as in][]{Horton2012a, Junk2015}.
@@
 The global optimization approach allows the easy adaptation of AMs to new regions by potentially taking into account local meteorological influences, and thus has a significant potential for application.
-Moreover, it can be employed to automatically explore datasets, in order to extract the most relevant variables.
+Moreover, it can be employed to automatically explore new datasets, in order to extract the most relevant variables.
 Thus, this method can make it easier to assess other predictands, such as the temperature, limit of snowfall, or occurrence of hail, while allowing the algorithms to select the best variables and associated parameters.

### 2016-09-26 Genetic algorithms - MWR/template.tex
Michel's corrections.

@@
 
-\authors{Pascal Horton\correspondingauthor{Pascal Horton, University of Bern, Hallerstrasse 12, 3012 Bern, Switzerland.}\thanks{Current affiliation: Institute of Geography \& Oeschger Centre for Climate Change Research, University of Bern, Switzerland}}
+\authors{Pascal Horton\correspondingauthor{Pascal Horton, University of Bern, Hallerstrasse 12, 3012 Bern, Switzerland.}\thanks{Current affiliation: Oeschger Centre for Climate Change Research and Institute of Geography, University of Bern, Bern, Switzerland}}
 
@@
 
-\affiliation{University of Lausanne, Lausanne, Switzerland}
+\affiliation{University of Lausanne, Lausanne, Switzerland and Oeschger Centre for Climate Change Research and Institute of Geography, University of Bern, Bern, Switzerland}
 
@@
 
-\email{pascal.horton@alumnil.unil.ch}
+\email{pascal.horton@giub.unibe.ch}
 
@@
 (5) Parents and children are then subjected to mutation, where some genes are randomly changed.
-Finally, (6) the new generation is then re-assessed, and the best individual restored if degraded.
+Finally, (6) the new generation is then re-assessed, and the best individual restored if degraded (so that a superior solution is never lost).
 Then, (7) according to the ending criterion, the optimization either ends or begins again for another iteration.
@@
 
-Individuals of the IG can then reproduce, which begins with the selection of pairs (the parents). The techniques implemented in this study are the following:
+Individuals of the IG can then reproduce, which begins with the selection of pairs (the parents). The techniques implemented in this study are the following (see Fig. \ref{fig:illustration_couples}):
 
@@
 This allows the mixing of genes, and the potential accumulation of positive mutations.
-The evaluated crossover operators are the following:
+The evaluated crossover operators are the following (see Fig.
+\ref{fig:illustration_crossover}):
 
@@
 In order to evaluate a combination of operators/options, 10 optimizations were processed per configuration of GAs.
-For all combinations of GA options, 21~630 optimizations were performed on an Intel Xeon based HPC (High-performance computing) cluster with 96 CPU, running Linux RedHat.
+For all combinations of GA options, 21~630 optimizations were performed on a small Intel Xeon based HPC (High-performance computing) cluster with 8 nodes (Xeon 5670, 2.97 GHz, 12 cores), running Linux RedHat.
 Such an assessment was not possible on the whole archive length, and had to be performed on a reduced calibration period of five years from 1998 to 2002, while looking for analog dates over a 48 year period (1961-2008).
-The total resources required for this comparison amounted to 229~539 h CPU (26.2 years CPU).
+The total resources required for this comparison amounted to 229~539 h CPU.
 One should remember that these intensive resources were required in order to assess multiple combinations of GA options, in order to provide recommendations.
@@
 The analysis of the natural selection operator (Fig.
-\ref{fig:operator_selectnat_score}) revealed a slight preference for ratio-elitism compared to the tournament selection, but this was not very significant.
+\ref{fig:operator_selectnat_score}) revealed a slight preference for ratio-elitism compared to the tournament selection (section \ref{sec:gas:nat_selection}), but this was not very significant.
 This operator, or at least the two assessed versions, did not appear to significantly influence the optimization performance.
@@
 It may be wise to consider the three mutation operators in parallel.
-In order to be confident in the optimized AMs, we propose using a set of the following mutation operators:
+In order to be confident in the optimized AMs, we propose using a set of the following mutation operators, where $p_{mut}$ is the mutation rate (or mutation probability), $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a threshold chosen by the user in order to maintain a minimum search radius when the number of generations $G>G_{m,r}$:
 
@@
 
-where $p_{mut}$ is the mutation rate (or mutation probability), $G_{m,r}$ is the maximum number of generations during which the magnitude of the research varies, and $\omega$ is a threshold chosen by the user in order to maintain a minimum search radius when the number of generations $G>G_{m,r}$.
-
 \subsection{Illustration of application}
@@
 	\end{center}
+	\caption{Illustration of the different couples selection variants assessed in this study. Distributions on the left illustrate the probability of selection depending on the rank of the individual.}
+	\label{fig:illustration_couples}
+\end{figure}
+
+\begin{figure}[t]
+	\begin{center}
+		\noindent\includegraphics[width=33pc,angle=0]{fig03.pdf}\\
+	\end{center}
+	\caption{Illustration of the different chromosome crossover variants assessed in this study.}
+	\label{fig:illustration_crossover}
+\end{figure}
+
+\begin{figure}[t]
+	\begin{center}
+		\noindent\includegraphics[width=19pc,angle=0]{fig04.pdf}\\
+	\end{center}
 	\caption{Genetic algorithms operational flowchart.}
@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{fig03.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{fig05.pdf}\\
 	\end{center}
@@
 The continuous bottom line represents the score of the sequential approach, and the dashed line (top) shows the supposed global optimum.
-The circles represent the end of the optimization (when the best individual did not progress during 20 generations).}
+The circles represent the end of the optimization (when the best individual did not progress during 20 generations).
+Seven out of 10 optimizations converged to the global optimum.}
 	\label{fig:gas_evolution_good}
@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{fig04.pdf}\\
-	\end{center}
-	\caption{Same as Fig. \ref{fig:gas_evolution_good}, but for a GA configuration considered to be less relevant.}
+		\noindent\includegraphics[width=19pc,angle=0]{fig06.pdf}\\
+	\end{center}
+	\caption{Same as Fig.
+\ref{fig:gas_evolution_good}, but for a GA configuration considered to be less relevant and later rejected, because the optimizations did not converge.
+However, it still performed significantly better than the sequential approach (continuous bottom line).}
 	\label{fig:gas_evolution_bad}
@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{fig05.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{fig07.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=39pc,angle=0]{fig06.pdf}\\
+		\noindent\includegraphics[width=39pc,angle=0]{fig08.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=19pc,angle=0]{fig07.pdf}\\
+		\noindent\includegraphics[width=19pc,angle=0]{fig09.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=33pc,angle=0]{fig08.pdf}\\
+		\noindent\includegraphics[width=33pc,angle=0]{fig10.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=33pc,angle=0]{fig09.pdf}\\
+		\noindent\includegraphics[width=33pc,angle=0]{fig11.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=33pc,angle=0]{fig10.pdf}\\
+		\noindent\includegraphics[width=33pc,angle=0]{fig12.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=33pc,angle=0]{fig11.pdf}\\
+		\noindent\includegraphics[width=33pc,angle=0]{fig13.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=11pc,angle=0]{fig12.pdf}\\
+		\noindent\includegraphics[width=11pc,angle=0]{fig14.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=11pc,angle=0]{fig13.pdf}\\
+		\noindent\includegraphics[width=11pc,angle=0]{fig15.pdf}\\
 	\end{center}
@@
 	\begin{center}
-		\noindent\includegraphics[width=11pc,angle=0]{fig14.pdf}\\
+		\noindent\includegraphics[width=11pc,angle=0]{fig16.pdf}\\
 	\end{center}

### 2016-09-26 Genetic algorithms - MWR/template.tex
Update of the Acknowledgments.

@@
 
-Thanks to the Roads and Water Courses Service, Energy and Water Power Service of the Wallis Canton, the Water, Land and Sanitation Service of the Vaud Canton, and the Swiss Federal Office for Environment (FOEV), who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project, which started this research.
+This research has been initiated within the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project, financed by the Roads and Water Courses Service, Energy and Water Power Service of the Wallis Canton, the Water, Land and Sanitation Service of the Vaud Canton, and the Swiss Federal Office for Environment (FOEV).
+The present work has been performed after the project and was supported by the University of Lausanne and partially self-financed by the authors.
+
 The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.

### 2016-10-13 Moving temporal window - HESS/template.tex
Adding the replies to referees.
Removing the sharpness and accuracy analysis.

@@
 
-\title{The Analog Method for Precipitation Forecasting: Finding Better Analog Situations at a Sub-Daily Time Step}
+\title{The Analog Method for Precipitation Downscaling: Finding Better Analog Situations at a Sub-Daily Time Step}
 
@@
 where $\text{H}(y-y^{0})$ is the Heaviside function that is null when $y-y^{0}<0$, and has the value 1 otherwise.
-\citet{Bontron2004} proposed a decomposition of this score interpreted into a sharpness and an accuracy terms.
 
@@
 
-\subsubsection{Changes in sharpness and accuracy}
-
-The $S_{\text{CRP}}$ score can be decomposed into two components, namely sharpness and accuracy \citep[see][]{Bontron2004}.
-The impact of the MTW has been analyzed on these components and the results can be found in Table \ref{table:CRPSS_decomposition_no_recalibration} for the original parameters and in Table \ref{table:CRPSS_decomposition_recalibration} for the re-calibrated methods.
-The changes are expressed relative to the total $S_{\text{CRP}}$.
-Both components do not have the same value ranges: accuracy is in our case almost twice the sharpness values.
-Since the $S_{\text{CRP}}$ is considered here and not the $S_{\text{SCRP}}$, improved prediction capacity results in a lower score.
-A decrease of the score is thus desirable.
-
-It appears that the sharpness is a bit inferior with the MTW in favor of accuracy (Table \ref{table:CRPSS_decomposition_no_recalibration}).
-When using the recalibrated parameters, the components are a bit more balanced, but still the accuracy prevails on the sharpness (Table \ref{table:CRPSS_decomposition_recalibration}).
-Fig.
-\ref{fig:CRPSS_decomposition_precip_thresholds} illustrates the changes (relative to the total $S_{\text{CRP}}$) in sharpness and accuracy for different precipitation thresholds at the Ulrichen station.
-Be it for the 2Z or 2Z-2MI method, the original or the recalibrated parameters, the changes are similar: the improvements concern the accuracy over the sharpness, and this to a greater extent for significant precipitation events.
-The MTW does not allow to improve the sharpness, but the improvement in accuracy is significant, and this especially for the days with heavy precipitation.
-In terms of the predicted precipitation distribution, it means that the median of the prediction is closer to the observed values, while the distribution is not more condensed than previously.
-
 \section{Application attempts on the full archive}
@@
 \end{figure}
-
-\begin{figure*}[htb]
-	\begin{center}$
-		\begin{array}{cccc}
-		\includegraphics[width=16cm]{figures/components.pdf}
-		\end{array}$
-	\end{center}
-	\caption{Influence (\%) of the MTW on the $S_{\text{CRP}}$ components (accuracy and sharpness) relatively to the total $S_{\text{CRP}}$, for the 2Z and 2Z-2MI methods, according to different precipitation thresholds.
-The results are presented for (top) the original parameters, and (bottom) the recalibrated parameters.
-Improved prediction results in a lower score.}
-	\label{fig:CRPSS_decomposition_precip_thresholds}
-\end{figure*}
 
@@
 	\label{table:CRPSS_recalibration}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Changes in sharpness and accuracy relatively to the total $S_{\text{CRP}}$, due to the introduction of the MTW.
-The changes are presented for both 2Z and 2Z-2MI methods with the original parameters.
-A decrease of the score is desirable.}
-	\begin{center}
-		\begin{tabular}{l c c c c}
-			\hline
-			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
-			& Sharpness & Accuracy & Sharpness & Accuracy \\
-			\hline
-			Ulrichen & 2.82 & -5.29 & 1.00 & -4.30 \\
-			Zermatt & 2.26 & -5.01 & 0.88 & -3.58 \\
-			Visp & 3.66 & -5.18 & 2.67 & -4.94 \\
-			Montana & 1.62 & -2.78 & 0.57 & -2.91 \\
-			Sion & 2.02 & -2.78 & 0.33 & -2.75 \\
-			Aigle & 0.52 & -2.26 & -1.20 & -2.17 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{table:CRPSS_decomposition_no_recalibration}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Same as Table \ref{table:CRPSS_decomposition_no_recalibration} but with the re-calibrated parameters.}
-	\begin{center}
-		\begin{tabular}{l c c c c}
-			\hline
-			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
-			& Sharpness & Accuracy & Sharpness & Accuracy \\
-			\hline
-			Ulrichen & 1.44 & -4.56 & -0.37 & -3.34 \\
-			Zermatt & 0.80 & -4.03 & 0.75 & -4.42 \\
-			Visp & 1.53 & -3.94 & 1.47 & -4.96 \\
-			Montana & -0.27 & -1.80 & 0.06 & -3.71 \\
-			Sion & 0.95 & -2.66 & -0.10 & -3.19 \\
-			Aigle & -0.35 & -2.01 & -2.08 & -1.90 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{table:CRPSS_decomposition_recalibration}
 \end{table}

### 2016-10-13 Moving temporal window - HESS/template.tex
Removing some tables.

@@
 Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
-The AM parameters were calibrated using AtmoSwing \citep{Horton2016} on the original archive (Tables \ref{table:params_2Z} and \ref{table:params_2Z-2MI}) and will be used thereafter.
+The AM parameters were calibrated using AtmoSwing \citep{Horton2016} on the original archive (Tables \ref{table:performance}) and will be used thereafter.
 
@@
 
-After recalibrating, some changes in the optimal parameters can be observed for both 2Z (Table \ref{table:params_2Z_new}) and 2Z-2MI methods (Table \ref{table:params_2Z-2MI_new}).
+After recalibrating, some changes in the optimal number of analogs can be observed for both 2Z and 2Z-2MI methods (Table \ref{table:nb_analogs_new}).
 Among these, the east-west dimension of the spatial windows of the circulation analogy tends to decrease.
@@
 \begin{table}[htb]
-	\caption{Calibrated parameters (spatial windows and number of analogs) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) and skill score (\%) of the method on the full archive.}
+	\caption{Number of analogs (of the first and the second level of analogy, respectively $N_{1}$ and $N_{2}$) and skill score (\%) of the method based on the atmospheric circulation only (method 2Z), and the one with a second level of analogy on moisture variables (2Z-2MI), on the full archive.}
 	\begin{center}
-		\begin{tabular}{l c c c c }
+		\begin{tabular}{l c c c c c }
 			\hline
-			Station & Long (° E) & Lat (° N) & $N_{1}$ & $S_{\text{SCRP}}$ \\
+			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{3}{c}{2Z-2MI} \\
+			& $N_{1}$ & $S_{\text{SCRP}}$ & $N_{1}$ & $N_{2}$ & $S_{\text{SCRP}}$ \\ 
 			\hline
-			Ulrichen & 0 $\rightarrow$ 17.5 & 42.5 $\rightarrow$ 47.5 & 40 & 30.73 \\
-			Zermatt & 0 $\rightarrow$ 20 & 37.5 $\rightarrow$ 50 & 35 & 23.87 \\
-			Visp & -2.5 $\rightarrow$ 20 & 40 $\rightarrow$ 47.5 & 30 & 25.11 \\
-			Montana & -2.5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 47.5 & 40 & 32.55 \\
-			Sion & -2.5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 47.5 & 40 & 26.23 \\
-			Aigle & -5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 50 & 50 & 30.59 \\ 
+			Ulrichen & 40 & 30.73 & 60 & 25 & 34.31 \\
+			Zermatt & 35 & 23.87 & 55 & 25 & 28.28 \\
+			Visp & 30 & 25.11 & 45 & 25 & 28.85 \\
+			Montana & 40 & 32.55 & 55 & 30 & 36.11 \\
+			Sion & 40 & 26.23 & 90 & 30 & 31.16 \\
+			Aigle & 50 & 30.59 & 100 & 35 & 35.82 \\ 
 			\hline
@@
 	\end{center}	
-	\label{table:params_2Z}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Parameters of the moisture variables from the 2Z-2MI method and the corresponding skill score (\%) on the complete archive.
-The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z}, except the number of analogs of the first analogy level ($N_{1}$), which are here different.
-The $5^{th}$ column is the number of analogs for the second level ($N_{2}$).}
-	\begin{center}
-		\begin{tabular}{l c c c c c }
-			\hline
-			Station & Long (° E) & Lat (° N) & $N_{1}$ & $N_{2}$ & $S_{\text{SCRP}}$ \\
-			\hline
-			Ulrichen & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 60 & 25 & 34.31 \\
-			Zermatt & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 55 & 25 & 28.28 \\
-			Visp & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 45 & 25 & 28.85 \\
-			Montana & 5 $\rightarrow$ 7.5 & 45 $\rightarrow$ 47.5 & 55 & 30 & 36.11 \\
-			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 90 & 30 & 31.16 \\
-			Aigle & 7.5 & 45 $\rightarrow$ 47.5 & 100 & 35 & 35.82 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{table:params_2Z-2MI}
+	\label{table:performance}
 \end{table}
@@
 \begin{table}[htb]
-	\caption{Calibrated parameters (spatial windows and number of analogs) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) with the MTW approach.}
+	\caption{Number of analogs (of the first and the second level of analogy, respectively $N_{1}$ and $N_{2}$) of the method based on the atmospheric circulation only (method 2Z), and the one with a second level of analogy on moisture variables (2Z-2MI), using the MTW approach.}
 	\begin{center}
@@
 			\hline
-			Station & Long (° E) & Lat (° N) & $N_{1}$ \\
+			\multirow{2}{*}{Station} & \multicolumn{1}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
+			& $N_{1}$ & $N_{1}$ & $N_{2}$ \\ 
 			\hline
-			Ulrichen & 0 $\rightarrow$ 17.5 & 42.5 $\rightarrow$ 50 & 50 \\
-			Zermatt & 0 $\rightarrow$ 17.5 & 40 $\rightarrow$ 50 & 55 \\
-			Visp & -2.5 $\rightarrow$ 20 & 40 $\rightarrow$ 50 & 55 \\
-			Montana & -2.5 $\rightarrow$ 15 & 42.5 $\rightarrow$ 47.5 & 55 \\
-			Sion & -2.5 $\rightarrow$ 15 & 37.5 $\rightarrow$ 50 & 55 \\
-			Aigle & -2.5 $\rightarrow$ 15 & 40 $\rightarrow$ 50 & 75 \\
+			Ulrichen & 50 & 110 & 35 \\
+			Zermatt & 55 & 80 & 30 \\
+			Visp & 55 & 135 & 35 \\
+			Montana & 55 & 110 & 40 \\
+			Sion & 55 & 140 & 50 \\
+			Aigle & 75 & 135 & 45 \\ 
 			\hline
@@
 	\end{center}	
-	\label{table:params_2Z_new}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Parameters of the moisture variables from the 2Z-2MI method with the MTW approach.
-The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z_new}, except the number of analogs of the first analogy level ($N_{1}$), which are here different.
-The $5^{th}$ column is the number of analogs for the second level ($N_{2}$).}
-	\begin{center}
-		\begin{tabular}{l c c c c }
-			\hline
-			Station & Long (° E) & Lat (° N) & $N_{1}$ & $N_{2}$ \\
-			\hline
-			Ulrichen & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 110 & 35 \\
-			Zermatt & 7.5 & 45 $\rightarrow$ 47.5 & 80 & 30 \\
-			Visp & 7.5 & 45 $\rightarrow$ 47.5 & 135 & 35 \\
-			Montana & 5 $\rightarrow$ 7.5 & 45 & 110 & 40 \\
-			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 140 & 50 \\
-			Aigle & 5 $\rightarrow$ 7.5 & 45 & 135 & 45 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{table:params_2Z-2MI_new}
+	\label{table:nb_analogs_new}
 \end{table}

### 2016-11-07 Moving temporal window - HESS/template.tex
Minor edits.
Working on the HESS paper corrections.

@@
 %% Journal Abbreviations (Please use the same for Discussion Papers and Final Revised Papers)
-
-% Archives Animal Breeding (aab)
-% Atmospheric Chemistry and Physics (acp)
-% Advances in Geosciences (adgeo)
-% Advances in Statistical Climatology, Meteorology and Oceanography (ascmo)
-% Annales Geophysicae (angeo)
-% ASTRA Proceedings (ap)
-% Atmospheric Measurement Techniques (amt)
-% Advances in Radio Science (ars)
-% Advances in Science and Research (asr)
-% Biogeosciences (bg)
-% Climate of the Past (cp)
-% Drinking Water Engineering and Science (dwes)
-% Earth System Dynamics (esd)
-% Earth Surface Dynamics (esurf)
-% Earth System Science Data (essd)
-% Fossil Record (fr)
-% Geographica Helvetica (gh)
-% Geoscientific Instrumentation, Methods and Data Systems (gi)
-% Geoscientific Model Development (gmd)
-% Geothermal Energy Science (gtes)
 % Hydrology and Earth System Sciences (hess)
-% History of Geo- and Space Sciences (hgss)
-% Journal of Sensors and Sensor Systems (jsss)
-% Mechanical Sciences (ms)
-% Natural Hazards and Earth System Sciences (nhess)
-% Nonlinear Processes in Geophysics (npg)
-% Ocean Science (os)
-% Proceedings of the International Association of Hydrological Sciences (piahs)
-% Primate Biology (pb)
-% Scientific Drilling (sd)
-% SOIL (soil)
-% Solid Earth (se)
-% The Cryosphere (tc)
-% Web Ecology (we)
-
-%% \usepackage commands included in the copernicus.cls:
-%\usepackage[german, english]{babel}
-%\usepackage{tabularx}
-%\usepackage{cancel}
-%\usepackage{multirow}
-%\usepackage{supertabular}
-%\usepackage{algorithmic}
-%\usepackage{algorithm}
-%\usepackage{amsthm}
-%\usepackage{float}
-%\usepackage{subfig}
-%\usepackage{rotating}
 
@@
 
-% \Author[affil]{given_name}{surname}
-
 \Author[1,2]{Pascal}{Horton}
@@
 
-\affil[1]{University of Lausanne, Lausanne, Switzerland}
-\affil[2]{Institute of Geography \& Oeschger Centre for Climate Change Research, University of Bern, Bern, Switzerland}
+\affil[1]{Institute of Earth Sciences, University of Lausanne, Lausanne, Switzerland}
+\affil[2]{Oeschger Centre for Climate Change Research \& Institute of Geography, University of Bern, Bern, Switzerland}
 \affil[3]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}
-
-%% The [] brackets identify the author with the corresponding affiliation. 1, 2, 3, etc. should be inserted.
 
@@
 
+The AM is usually implemented with a daily time step, due to the availability of long precipitation archives that have no equivalent at a finer resolution.
+Therefore, the analog situations are assessed on the basis of a daily time step, by comparing predictors at fixed hours of the day, otherwise one would not know what precipitation values to assign to them.
+However, it can be expected that the analogy of the synoptic situations does not occur systematically at the same time of the day, and that better candidates can be found by shifting to a different hour.
+On this assumption, a moving time window (MTW) was introduced to allow searching for candidates at different hours of the day.
+
+Previous tests showed the benefit, in terms of analogy criteria values, of searching for analog synoptic situations at a finer time step, but without assessing the impact on the prediction skills \citep{Finet2008}.
+
+The MTW is explained in Sect.
+\ref{sec:mtw}.
+As this method requires sub-daily time series, the available archive length is reduced compared to more common daily measurements, which has some consequences on the performance score (Sect.
+\ref{sec:archive_reduction}).
+The benefit of introducing a MTW was assessed first in regards to the analogy criteria improvement (Sect.
+\ref{sec:influence_criteria}), and then in terms of precipitation prediction skill (Sect.
+\ref{sec:influence_scores}).
+Finally, the results are discussed in Sect.
+\ref{sec:discussion}.
+
+%TODO: complete !!
+
+\section{Data and methods}
+
+\subsection{Study area and data}
+\label{sec:data}
+
+The study area is the upper Rh\^{o}ne catchment in Switzerland \cite[see also][]{Horton2012a}.
+Due to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed.
+The time series (on the period 1982--2007) come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle (Fig.
+\ref{fig:map}), which are subject to various meteorological influences \citep{Horton2012}.
+The results will thereafter be presented arbitrarily for the Ulrichen station, but they are equivalent for all stations.
+The precipitation time series were then aggregated by means of a moving 24~h-total (see next section).
+
+Predictors are extracted from the NCEP/NCAR reanalysis I \citep{Kalnay1996} dataset with a 6-hourly temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree.
+This dataset is now relatively old, but still often used (see discussion).
+
+\subsection{The considered analog method}
+\label{sec:analog_method}
+
 The first method is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005, Marty2012}.
@@
 
+\subsection{Calibration of the analog method}
+\label{sec:calibration}
+
 To calibrate the method, the commonly used technique is a semi-automatic sequential procedure elaborated by \citet{Bontron2004}.
-AtmoSwing \citep{Horton2016}, which implements this technique, was used in order to calibrate the parameters in the present study.
+
+\subsection{The moving time window (MTW) approach}
+\label{sec:mtw}
+
+In order to assess the benefit of searching analog situations at a sub-daily time step, an appropriate precipitation series is required.
+On the basis of high resolution time series (Sect.
+\ref{sec:data}), 24~h-totals were processed, but at a 6-hourly time step (temporal resolution of the reanalysis dataset), by means of a moving 24~h-total.
+
+The target situations and their corresponding observed precipitation values (used for validation) do not change, because the prediction is always established for a fixed period of the target day (6--30~h), as before.
+The difference is that the candidates are 4~times more numerous (Fig.
+\ref{fig:principle}).
+
+Based on some preliminary tests (not shown), no constraint was added in order to restrict the selection of multiple analogs within the same candidate dates.
+
+In order to assess this potential improvement of the prediction, precipitation data with a resolution of 10 minutes, on a respectable archive length, was used (Sect.
+\ref{sec:data}).
+It was then aggregated in the form of 24~h-totals, but starting at different 6-hourly time step, by means of a moving total.
+
+\subsection{Performance score}
+\label{sec:performance}
+
 The score that is most often considered to assess an AM performance is the Continuous Ranked Probability Score \citep[$S_{\text{CRP}}$,][]{Brown1974, Matheson1976, Hersbach2000}.
@@
 
-The AM is usually implemented with a daily time step, due to the availability of long precipitation archives that have no equivalent at a finer resolution.
-Therefore, the analog situations are assessed on the basis of a daily time step, by comparing predictors at fixed hours of the day, otherwise one would not know what precipitation values to assign to them.
-However, it can be expected that the analogy of the synoptic situations does not occur systematically at the same time of the day, and that better candidates can be found by shifting to a different hour.
-On this assumption, a moving time window (MTW) was introduced to allow searching for candidates at different hours of the day.
+Finding better analog situations does not obligatory imply better skills to predict the precipitation.
+Therefore, the impact of the MTW introduction, and thus the selection of other analog dates, has to be assessed on the performance scores.
+In order to perform this assessment, the 24~h-totals (moving average) at a 6-hourly time step were used (see Sect.
+\ref{sec:data}).
+The target dates remain unchanged, since the original time slot (6~h~UTC -- 6~h~UTC the next day) is kept, and thus the performance scores can be directly compared with the former ones.
 
-Previous tests showed the benefit, in terms of analogy criteria values, of searching for analog synoptic situations at a finer time step, but without assessing the impact on the prediction skills \citep{Finet2008}.
-In order to assess this potential improvement of the prediction, precipitation data with a resolution of 10 minutes, on a respectable archive length, was used (Sect.
-\ref{sec:data}).
-It was then aggregated in the form of 24~h-totals, but starting at different 6-hourly time step, by means of a moving total (Sect.
-\ref{sec:method}).
-
-One can question the interest of using daily totals when a 6-hourly precipitation series can be used.
-The first reason is that the 6-hourly time series generated by the AM may not represent well the dynamic of the accurate precipitation (results not shown), due to a smoothed signal.
-Then, sometimes one just does not need finer resolution than the daily time step.
-Finally, when using a reconstructed precipitation archive, the errors in intra-day precipitation distributions have a lesser impact over 24~h daily totals.
-
-The MTW is explained in Sect.
-\ref{sec:method}.
-As this method requires sub-daily time series, the available archive length is reduced compared to more common daily measurements, which has some consequences on the performance score (Sect.
-\ref{sec:archive_reduction}).
-The benefit of introducing a MTW was assessed first in regards to the analogy criteria improvement (Sect.
-\ref{sec:influence_criteria}), and then in terms of precipitation prediction skill (Sect.
-\ref{sec:influence_scores}).
-Finally, attempts were made to reconstruct longer 24~h-total precipitations series (Sect.
-\ref{sec:attempts}).
-
-\section{Data and method}
-
-\subsection{Study area and data}
-\label{sec:data}
-
-The study area is the upper Rh\^{o}ne catchment in Switzerland \cite[see also][]{Horton2012a}.
-Due to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed.
-The time series (on the period 1982--2007) come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle (Fig.
-\ref{fig:map}), which are subject to various meteorological influences \citep{Horton2012}.
-The results will thereafter be presented arbitrarily for the Ulrichen station, but they are equivalent for all stations.
-The precipitation time series were then aggregated by means of a moving 24~h-total (see next section).
-
-Predictors are extracted from the NCEP/NCAR reanalysis I \citep{Kalnay1996} dataset with a 6-hourly temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree.
-
-\subsection{The moving time window (MTW) approach}
-\label{sec:method}
-
-In order to assess the benefit of searching analog situations at a sub-daily time step, an appropriate precipitation series is required.
-On the basis of high resolution time series (Sect.
-\ref{sec:data}), 24~h-totals were processed, but at a 6-hourly time step (temporal resolution of the reanalysis dataset), by means of a moving 24~h-total.
-
-The target situations and their corresponding observed precipitation values (used for validation) do not change, because the prediction is always established for a fixed period of the target day (6--30~h), as before.
-The difference is that the candidates are 4~times more numerous (Fig.
-\ref{fig:principle}).
-
-Based on some preliminary tests (not shown), no constraint was added in order to restrict the selection of multiple analogs within the same candidate dates.
+\section{Results}
 
@@
 Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
-The AM parameters were calibrated using AtmoSwing \citep{Horton2016} on the original archive (Tables \ref{table:performance}) and will be used thereafter.
+The AM parameters were calibrated on the original archive (Tables \ref{table:performance}) and will be used thereafter.
 
@@
 This loss is globally significant, with up to -1.89 points for Visp and the 2Z method.
-
-\section{Results and discussion}
 
@@
 
+\subsubsection{Changes per precipitation classes}
+\label{sec:influence_precip}
+
+The impact of the MTW on the analogy criteria has been decomposed per precipitation classes.
+The results of this analysis are summarized in Fig.
+\ref{fig:changes_S1_precip_threshold} by the median reduction of $S_{\text{TW}}$ for days with precipitation (organized into classes) between two thresholds.
+The number of cases per class being reduced, the curves are not as smooth as in previous analyzes.
+It is nevertheless clear that the improvement tends to increase on days with higher precipitation.
+This is true for all our stations.
+
+\subsubsection{Changes per season}
+\label{sec:seasonal_effect}
+
+Atmospheric dynamics varies greatly from one season to another, which reflects on the performance of the AM that is generally lower between June and August \citep{Bliefernicht2010}.
+It therefore makes sense to verify the effect of the MTW separately per season.
+
+A seasonal effect can be observed on the reduction of the $S_{\text{TW}}$ criteria due to the MTW (Fig. \ref{fig:changes_S1_seasons}). The improvements are greater for winter than summer.
+
+\subsubsection{Changes in the moisture analogy}
+
+When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidates situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogs, but their dates have changed.
+In contrast to earlier, both a reduction or an increase of the $E_{\text{RMS}}$ analogy criterion values are possible.
+Indeed, Fig.
+\ref{fig:changes_RMSE} shows an almost insignificant improvement of the $E_{\text{RMS}}$ values.
+Unlike for the first level of analogy, the relative improvement of the $E_{\text{RMS}}$ values are distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
+Once again, the results for the other stations are similar.
+
+\subsection{Impact on performance scores}
+\label{sec:influence_scores}
+
+A systematic improvement of the $S_{\text{TW}}$ values was previously observed.
+
+The new performance scores are provided in Table \ref{table:CRPSS_MTW}, along with the differences regarding the conventional method with the same archive length.
+The differences ranges from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.
+The introduction of the MTW brings an improvement of the performance that is not very large, but that is nevertheless significant.
+Moreover, it requires no additional predictor.
+No relationship was found between the improvement of the score and the reduction of the $S_{\text{TW}}$ criteria, neither with the season.
+
+\subsubsection{Improvement per precipitation classes}
+\label{sec:improvement_CRPSS_precip_threshold}
+
+The $S_{\text{TW}}$ criteria was previously found to be improved to a greater extent for the most dynamic situations related with higher precipitation values (Sect.
+\ref{sec:influence_precip}).
+The changes in terms of performance scores will now be assessed regarding precipitation thresholds.
+Fig.
+\ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, other stations having the same behavior.
+
+The increasing positive trend of skill improvements regarding the precipitation threshold is significant and shows that the prediction of higher precipitation totals is further improved.
+Thus, both the analogy criteria and the performance scores are improved to a greater extent for heavier precipitation events.
+On the contrary, the non-rainy days and small accumulations are not improved.
+
+\subsubsection{Recalibration of the AM parameters}
+\label{sec:recalibration}
+
+The previous assessment of the performance improvement was established with the original parameters optimized with a fixed time window.
+However, one can assume that the introduction of the MTW may change the optimum of some parameters.
+The calibration has then been reprocessed.
+
+After recalibrating, some changes in the optimal number of analogs can be observed for both 2Z and 2Z-2MI methods (Table \ref{table:nb_analogs_new}).
+Among these, the east-west dimension of the spatial windows of the circulation analogy tends to decrease (not shown).
+More significantly, the optimal number of analogs increases after introducing the MTW, of a significant order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method.
+The number of analogs of the first analogy level of the 2Z-2MI method even reached three times its previous value for the Visp station.
+
+This increase in number of analogs has a slight effect on the performance of the different precipitation classes.
+The same analysis as in Sect.
+\ref{sec:improvement_CRPSS_precip_threshold} has been performed again on the basis of the newly calibrated parameters.
+The results are generally very similar, but a slight performance increase of small precipitation values can be observed at the expense of higher amounts.
+The change in the analogs numbers is likely to be responsible for this difference in the performance distributions.
+
+The values of the $S_{\text{SCRP}}$ scores for both methods (Table \ref{table:CRPSS_recalibration}) have significantly increased after recalibration.
+
+\section{Discussion}
+\label{sec:discussion}
+
+\subsection{Improvement of the atmospheric circulation analogy}
+
 The median of the $S_{\text{TW}}$ values reduction (Fig.
@@
 
-\subsubsection{Influence of the weather situation}
-\label{sec:influence_precip}
+\subsection{Improvement of the moisture analogy}
+
+This result of a globally null improvement of the $E_{\text{RMS}}$ values does not mean that the 2Z-2MI method cannot be improved by the MTW.
+It means that after the selection of the analogs situations in terms of the synoptic circulation, the new candidate dates do not allow to find better analogs in terms of moisture.
+However, the selected dates have changed in the first level of analogy, and thus also in the final selection, which can potentially improve the performance scores on the predictand.
+
+With the introduction of the MTW, the performance loss related to the reduction of the archive length is compensated.
+
+\subsection{Impact of the MTW per precipitation classes}
 
@@
 
-The dynamism of a given atmospheric condition cannot be easily quantified.
-A basic assumption is considered here, which stipulates that the more a day is rainy, the more dynamic the situation is.
-The results of this analysis are summarized in Fig.
-\ref{fig:changes_S1_precip_threshold} by the median reduction of $S_{\text{TW}}$ for days with precipitation (organized into classes) between two thresholds.
-The number of cases per class being reduced, the curves are not as smooth as in previous analyzes.
-It is nevertheless clear that the improvement tends to increase on days with higher precipitation.
-This is true for all our stations and confirms our intuition.
+The dynamism of a given atmospheric condition cannot be easily quantified. A basic assumption is considered here, which stipulates that the more a day is rainy, the more dynamic the situation is.
 
-\subsubsection{Seasonal effect}
-\label{sec:seasonal_effect}
+\subsection{Seasonal effect}
 
-Atmospheric dynamics varies greatly from one season to another, which reflects on the performance of the AM that is generally lower between June and August \citep{Bliefernicht2010}.
-It therefore makes sense to verify the effect of the MTW separately per season.
-
-A seasonal effect can be observed on the reduction of the $S_{\text{TW}}$ criteria due to the MTW (Fig.
-\ref{fig:changes_S1_seasons}).
-The improvements are greater for winter than summer.
 One hypothesis is that the diurnal effects of the summer months have an influence on the atmospheric circulation, at least in the lower layers.
@@
 
-\subsubsection{Changes in the moisture analogy}
+\subsection{Increase in number of analog situations}
 
-When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidates situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogs, but their dates have changed.
-In contrast to earlier, both a reduction or an increase of the $E_{\text{RMS}}$ analogy criterion values are possible.
-Indeed, Fig.
-\ref{fig:changes_RMSE} shows an almost insignificant improvement of the $E_{\text{RMS}}$ values.
-Unlike for the first level of analogy, the relative improvement of the $E_{\text{RMS}}$ values are distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
-Once again, the results for the other stations are similar.
-
-This result of a globally null improvement of the $E_{\text{RMS}}$ values does not mean that the 2Z-2MI method cannot be improved by the MTW.
-It means that after the selection of the analogs situations in terms of the synoptic circulation, the new candidate dates do not allow to find better analogs in terms of moisture.
-However, the selected dates have changed in the first level of analogy, and thus also in the final selection, which can potentially improve the performance scores on the predictand.
-
-\subsection{Impact on performance scores}
-\label{sec:influence_scores}
-
-A systematic improvement of the $S_{\text{TW}}$ values was previously observed.
-However, finding better analog situations does not obligatory imply better skills to predict the precipitation.
-Therefore, the impact of the MTW introduction, and thus the selection of other analog dates, has to be assessed on the performance scores.
-In order to perform this assessment, the 24~h-totals (moving average) at a 6-hourly time step were used (see Sect.
-\ref{sec:data}).
-The target dates remain unchanged, since the original time slot (6~h~UTC -- 6~h~UTC the next day) is kept, and thus the performance scores can be directly compared with the former ones.
-
-The new performance scores are provided in Table \ref{table:CRPSS_MTW}, along with the differences regarding the conventional method with the same archive length.
-The differences ranges from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.
-The introduction of the MTW brings an improvement of the performance that is not very large, but that is nevertheless significant.
-Moreover, it requires no additional predictor.
-No relationship was found between the improvement of the score and the reduction of the $S_{\text{TW}}$ criteria, neither with the season.
-
-\subsubsection{Improvement by precipitation classes}
-\label{sec:improvement_CRPSS_precip_threshold}
-
-The $S_{\text{TW}}$ criteria was previously found to be improved to a greater extent for the most dynamic situations related with higher precipitation values (Sect.
-\ref{sec:influence_precip}).
-The changes in terms of performance scores will now be assessed regarding precipitation thresholds.
-Fig.
-\ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, other stations having the same behavior.
-
-The increasing positive trend of skill improvements regarding the precipitation threshold is significant and shows that the prediction of higher precipitation totals is further improved.
-Thus, both the analogy criteria and the performance scores are improved to a greater extent for heavier precipitation events.
-On the contrary, the non-rainy days and small accumulations are not improved.
-
-\subsubsection{Effect of recalibrating the parameters}
-\label{sec:recalibration}
-
-The previous assessment of the performance improvement was established with the original parameters optimized with a fixed time window.
-However, one can assume that the introduction of the MTW may change the optimum of some parameters.
-The calibration has then been reprocessed.
-
-After recalibrating, some changes in the optimal number of analogs can be observed for both 2Z and 2Z-2MI methods (Table \ref{table:nb_analogs_new}).
-Among these, the east-west dimension of the spatial windows of the circulation analogy tends to decrease.
-More significantly, the optimal number of analogs increases after introducing the MTW, of a significant order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method.
-The number of analogs of the first analogy level of the 2Z-2MI method even reached three times its previous value for the Visp station.
 It seems as if the method perceive the increase in the archive length and diversity by allowing to extract more analogs.
@@
 
-This increase in number of analogs has a slight effect on the performance of the different precipitation classes.
-The same analysis as in Sect.
-\ref{sec:improvement_CRPSS_precip_threshold} has been performed again on the basis of the newly calibrated parameters.
-The results are generally very similar, but a slight performance increase of small precipitation values can be observed at the expense of higher amounts.
-The change in the analogs numbers is likely to be responsible for this difference in the performance distributions.
+\subsection{Why not just making a 6-hourly prediction ?}
 
-The values of the $S_{\text{SCRP}}$ scores for both methods (Table \ref{table:CRPSS_recalibration}) have significantly increased after recalibration.
-With the introduction of the MTW, the performance loss related to the reduction of the archive length is compensated.
+One can question the interest of using daily totals when a 6-hourly precipitation series can be used.
+The first reason is that the 6-hourly time series generated by the AM may not represent well the dynamic of the accurate precipitation (results not shown), due to a smoothed signal.
+Then, sometimes one just does not need finer resolution than the daily time step.
+Finally, when using a reconstructed precipitation archive, the errors in intra-day precipitation distributions have a lesser impact over 24~h daily totals.
 
-\section{Application attempts on the full archive}
-\label{sec:attempts}
+\subsection{On the use of an old reanalysis dataset}
+
+The considered reanalysis dataset, which is the NCEP/NCAR reanalysis I \citep{Kalnay1996}, is relatively old and has a coarse resolution.
+Newer reanalysis dataset could have been used to achieve this study, and might have resulted in higher performance scores.
+However, one can assume that the gain observed here by introducing a MTW should also be found for a better reanalysis dataset, especially if the information of the atmospheric circulation is more accurate.
+
+\subsection{Is a simple reconstructed archive useful for the MTW ?}
 
@@
 Unfortunately, there is no long precipitation time series available with a sub-daily time step.
-In order to reconstruct a longer archive of moving 24~h-totals, different disaggregation approaches of the daily time series were assessed and are presented in the following sections.
-
-\subsection{Proportional distribution}
+In order to reconstruct a longer archive of moving 24~h-totals, different disaggregation approaches of the daily time series were assessed.
 
@@
 
-\subsection{Use of a proxy variable}
+\subsection{Can a proxy variable help reconstruct a better archive ?}
 
@@
 
-The first step consisted in determining which variables from the precipitable water or the relative humidity (at 1000~hPa, 925~hPa or 850~hPa) produces the precipitation chronology that is the most correlated (on non-zero values) with the accurate 6-hourly precipitation time series on the period 1982-2007.
-The location of the most predictive point from the reanalysis grid had to be assessed (closest points: 5--7.5° E and 45--47.5° N), as well an eventual time lapse between both series, due to the significant distance separating the weather stations and the reanalysis grid point.
-The most relevant point will probably not be the same for all stations, since one can expect to find the optimum in the direction of the main moisture inflows for the station.
-This assessment must be carried out for each station.
+The best proxy variable was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series on the period 1982-2007.
+Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and by allowing a time lapse between both series in order to take into account the significant distance separating the weather stations and the reanalysis grid point (details not shown).
+The best proxy for the Zermatt station is the precipitable water at 45° N and 7.5° E, with a time offset of -6~h.
 
-The results of the correlation analyses (on non-zero values) between the new series reconstituted using the proxy and the actual series are illustrated in Table \ref{table:proxy_correlations} for Zermatt (on the short period, 1982--2007).
-The best proxy is the precipitable water at 45° N and 7.5° E, with a time offset of -6~h.
-The determination coefficient of 0.721 is higher than that of the series from the proportional distribution (0.698), which confirms that a little information was added to the series of precipitation.
-
-Table \ref{table:proxy_CRPSS} presents the $S_{\text{SCRP}}$ scores obtained by the reconstituted series using the proxy of precipitable water at the optimal point (Table \ref{table:proxy_correlations}).
+Table \ref{table:proxy_CRPSS} presents the $S_{\text{SCRP}}$ scores obtained by the reconstituted series using the proxy of precipitable water.
 A slight improvement can be obtained compared to the proportional distribution method, but it is still relatively small, and most of the benefit of the MTW is again lost.
+A more recent reanalysis archive with more accurate moisture variables might produce better proxies.
 
@@
 \bibliographystyle{copernicus}
-\bibliography{../_refs/_articles-moving-window}
+\bibliography{../_refs/4_articles-2016_HESS_moving-window}
 
@@
 \begin{table}[htb]
-	\caption{Value of the coefficient of determination between the reconstructed 6-hourly precipitation time series using the listed variables, and the accurate time series on the period 1982-2007.
-The grid points are the following: 1) 5° E, 47.5° N, 2) 5° E, 45° N, 3) 7.5° E, 47.5° N, 4) 7.5° E, 45° N.
-The highest coefficient of determination is indicated in bold.}
-	\begin{center}
-		\begin{tabular}{l c c c c c c}
-			\hline
-			\multirow{2}{*}{Variable} & \multirow{2}{*}{Point} &  \multicolumn{5}{c}{Time lapse} \\
-			&  & -12 h & -6 h & 0 h & +6 h & +12 h \\ 
-			\hline
-			\multirow{ 4}{*}{RH1000} & 1 & 0.668 & 0.669 & 0.684 & 0.683 & 0.670 \\
-			& 2 & 0.669 & 0.669 & 0.683 & 0.681 & 0.669 \\
-			& 3 & 0.662 & 0.673 & 0.691 & 0.682 & 0.673 \\
-			& 4 & 0.666 & 0.671 & 0.688 & 0.681 & 0.668 \\ \hline
-			\multirow{ 4}{*}{RH925} & 1 & 0.672 & 0.673 & 0.684 & 0.684 & 0.675 \\
-			& 2 & 0.674 & 0.674 & 0.683 & 0.682 & 0.672 \\
-			& 3 & 0.662 & 0.673 & 0.691 & 0.682 & 0.673 \\
-			& 4 & 0.666 & 0.671 & 0.689 & 0.681 & 0.668 \\ \hline
-			\multirow{ 4}{*}{RH850} & 1 & 0.675 & 0.675 & 0.679 & 0.678 & 0.671 \\
-			& 2 & 0.681 & 0.690 & 0.691 & 0.677 & 0.664 \\
-			& 3 & 0.665 & 0.680 & 0.693 & 0.683 & 0.675 \\
-			& 4 & 0.675 & 0.694 & 0.706 & 0.681 & 0.659 \\ \hline
-			\multirow{ 4}{*}{TCW} & 1 & 0.688 & 0.687 & 0.667 & 0.655 & 0.652 \\
-			& 2 & 0.697 & 0.699 & 0.669 & 0.644 & 0.644 \\
-			& 3 & 0.686 & 0.708 & 0.689 & 0.655 & 0.648 \\
-			& 4 & 0.696 & \textbf{0.721} & 0.696 & 0.643 & 0.636 \\ \hline
-		\end{tabular}
-	\end{center}
-	\label{table:proxy_correlations}
-\end{table}
-
-\begin{table}[htb]
 	\caption{Values of the $S_{\text{SCRP}}$ (\%) skill score for Zermatt, for the original and the recalibrated parameters (with the sequential method, as described in Sect.

### 2016-11-07 AtmoSwing - GMD/template.tex
Updating affiliations.

@@
 
-\Author[1,2]{Pascal}{Horton}
+\Author[1,2,3]{Pascal}{Horton}
 \Author[1]{Michel}{Jaboyedoff}
-\Author[3]{Charles}{Obled}
-
-\affil[1]{University of Lausanne, Lausanne, Switzerland}
-\affil[2]{Terranum, Lausanne, Switzerland}
-\affil[3]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}
+\Author[4]{Charles}{Obled}
+
+\affil[1]{Institute of Earth Sciences, University of Lausanne, Lausanne, Switzerland}
+\affil[2]{Oeschger Centre for Climate Change Research \& Institute of Geography, University of Bern, Bern, Switzerland}
+\affil[3]{Terranum SARL, Bussigny, Switzerland}
+\affil[4]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}
 

### 2016-11-07 Genetic algorithms - MWR/template.tex
Updating affiliations.

@@
 
-\affiliation{University of Lausanne, Lausanne, Switzerland and Oeschger Centre for Climate Change Research and Institute of Geography, University of Bern, Bern, Switzerland}
+\affiliation{Institute of Earth Sciences, University of Lausanne, Switzerland and Oeschger Centre for Climate Change Research and Institute of Geography, University of Bern, Switzerland}
 

### 2016-11-07 Optimization case study - JoH/elsarticle-template.tex
Updating affiliations.

@@
 %% Group authors per affiliation:
-\author[unil,terranum]{Pascal Horton\corref{mycorrespondingauthor}}
+\author[unil,unibe,terranum]{Pascal Horton\corref{mycorrespondingauthor}}
 \cortext[mycorrespondingauthor]{Corresponding author}
@@
 
-\address[unil]{University of Lausanne, Lausanne, Switzerland}
-\address[terranum]{Terranum, Rue de l'industrie 35 bis, 1030 Bussigny, Switzerland}
+\address[unil]{Institute of Earth Sciences, University of Lausanne, Lausanne, Switzerland}
+\address[unibe]{Oeschger Centre for Climate Change Research \& Institute of Geography, University of Bern, Bern, Switzerland}
+\address[terranum]{Terranum SARL, Bussigny, Switzerland}
 \address[lthe]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}

### 2016-11-07 AtmoSwing - GMD/template.tex
Updating affiliations.

@@
 
-\affil[1]{Institute of Earth Sciences, University of Lausanne, Lausanne, Switzerland}
-\affil[2]{Oeschger Centre for Climate Change Research \& Institute of Geography, University of Bern, Bern, Switzerland}
+\affil[1]{University of Lausanne, Institute of Earth Sciences, Lausanne, Switzerland}
+\affil[2]{University of Bern, Oeschger Centre for Climate Change Research, Institute of Geography, Bern, Switzerland}
 \affil[3]{Terranum SARL, Bussigny, Switzerland}

### 2016-11-07 Genetic algorithms - MWR/template.tex
Updating affiliations.

--- 2016-09-26 Genetic algorithms - MWR/template.tex
@@
 
-\affiliation{University of Lausanne, Lausanne, Switzerland and Oeschger Centre for Climate Change Research and Institute of Geography, University of Bern, Bern, Switzerland}
+\affiliation{University of Lausanne, Institute of Earth Sciences, Lausanne, Switzerland and University of Bern, Oeschger Centre for Climate Change Research, Institute of Geography, Bern, Switzerland}
 
@@
 \extraauthor{Michel Jaboyedoff}
-\extraaffil{University of Lausanne, Lausanne, Switzerland}
+\extraaffil{University of Lausanne, Institute of Earth Sciences, Lausanne, Switzerland}
 

### 2016-11-07 Moving temporal window - HESS/template.tex
Updating affiliations.

@@
 
-\affil[1]{Institute of Earth Sciences, University of Lausanne, Lausanne, Switzerland}
-\affil[2]{Oeschger Centre for Climate Change Research \& Institute of Geography, University of Bern, Bern, Switzerland}
+\affil[1]{University of Lausanne, Institute of Earth Sciences, Lausanne, Switzerland}
+\affil[2]{University of Bern, Oeschger Centre for Climate Change Research, Institute of Geography, Bern, Switzerland}
 \affil[3]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}
@@
 The Analog Method (AM) is based on the principle that two relatively similar synoptic situations may produce relatively similar local effects \citep{Lorenz1956, Lorenz1969}.
-Multiple variations of the methods exist and listings can be found in \citet{Horton2016} or \citet{BenDaoud2015}.
+Multiple variations of the methods exist and listings can be found in \citet{BenDaoud2016}.
 The versions that will be considered here are often used as references or benchmarks for various improvements.
@@
 Then, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day.
-Following the nomenclature proposed by \citet{Horton2016}, this method will be named 2Z.
+This method will be named 2Z further on.
 

### 2016-11-07 Optimization case study - JoH/elsarticle-template.tex
Updating affiliations.

@@
 
-\address[unil]{Institute of Earth Sciences, University of Lausanne, Lausanne, Switzerland}
-\address[unibe]{Oeschger Centre for Climate Change Research \& Institute of Geography, University of Bern, Bern, Switzerland}
+\address[unil]{University of Lausanne, Institute of Earth Sciences, Lausanne, Switzerland}
+\address[unibe]{University of Bern, Oeschger Centre for Climate Change Research, Institute of Geography, Bern, Switzerland}
 \address[terranum]{Terranum SARL, Bussigny, Switzerland}

### 2016-11-08 Moving temporal window - HESS/template.tex
Return to CRPS, RMSE and S1 in the text.

@@
 Here, it has been limited to the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects.
-Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score ($S_{\text{TW}}$), which is a comparison of gradients, over a certain spatial window and at certain hours.
-The smaller the $S_{\text{TW}}$ values, the more similar the pressure fields.
+Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1), which is a comparison of gradients, over a certain spatial window and at certain hours.
+The smaller the S1 values, the more similar the pressure fields.
 
@@
 
-Then, $N_{1}$ dates with the lowest values of $S_{\text{TW}}$ are considered as analogs to the target day, $N_{1}$ being a parameter to calibrate.
+Then, $N_{1}$ dates with the lowest values of S1 are considered as analogs to the target day, $N_{1}$ being a parameter to calibrate.
 Then, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day.
@@
 
-The second reference method adds a subsequent level of analogy on moisture variables, compared by means of the root-mean-square error ($E_{\text{RMS}}$) (method 2Z-2MI, Table \ref{table:method_2Z-2MI}).
+The second reference method adds a subsequent level of analogy on moisture variables, compared by means of the root-mean-square error (RMSE) (method 2Z-2MI, Table \ref{table:method_2Z-2MI}).
 This second predictor is a moisture index made of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850) \citep{Bontron2004}.
@@
 
-The score that is most often considered to assess an AM performance is the Continuous Ranked Probability Score \citep[$S_{\text{CRP}}$,][]{Brown1974, Matheson1976, Hersbach2000}.
+The score that is most often considered to assess an AM performance is the Continuous Ranked Probability Score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000}.
 It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$.
@@
 In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution as the reference.
-The Continuous Ranked Probability Skill Score ($S_{\text{SCRP}}$) is thus defined as following:
+The Continuous Ranked Probability Skill Score (CRPSS) is thus defined as following:
 
@@
 where $S_{\text{CRP}}^{r}$ is the $S_{\text{CRP}}$ value for the reference (climatological distribution) and $S_{\text{CRP}}^{p}$ would be the one for a perfect prediction (which implies $S_{\text{CRP}}^{p}~=~0$).
-A better prediction is characterized by an increase in $S_{\text{SCRP}}$.
+A better prediction is characterized by an increase in CRPSS.
 
@@
 
-Figure \ref{fig:changes_S1_analogs} presents the changes in the distributions of the $S_{\text{TW}}$ criterion for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogs for the Ulrichen station on the whole calibration period, due to introduction of the MTW.
+Figure \ref{fig:changes_S1_analogs} presents the changes in the distributions of the S1 criterion for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogs for the Ulrichen station on the whole calibration period, due to introduction of the MTW.
 The precipitation target remains as before, that is centered on 18~h~UTC (6~h~UTC to 6~h~UTC the next day).
@@
 
-The improvements of the $S_{\text{TW}}$ criteria are summarized in Fig.
-\ref{fig:changes_S1}, which shows (top) quantiles of the $S_{\text{TW}}$ criteria according to the analog rank for the conventional method and the MTW, and (bottom) quantiles of the relative reduction.
-This confirms that all quantile seem similarly reduced ($S_{\text{TW}}$ distributions keep their shape), and that this improvement is constantly increasing from the first to the last analog (Fig.
+The improvements of the S1 criteria are summarized in Fig.
+\ref{fig:changes_S1}, which shows (top) quantiles of the S1 criteria according to the analog rank for the conventional method and the MTW, and (bottom) quantiles of the relative reduction.
+This confirms that all quantile seem similarly reduced (S1 distributions keep their shape), and that this improvement is constantly increasing from the first to the last analog (Fig.
 \ref{fig:changes_S1} bottom).
@@
 The results of this analysis are summarized in Fig.
-\ref{fig:changes_S1_precip_threshold} by the median reduction of $S_{\text{TW}}$ for days with precipitation (organized into classes) between two thresholds.
+\ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for days with precipitation (organized into classes) between two thresholds.
 The number of cases per class being reduced, the curves are not as smooth as in previous analyzes.
@@
 
-A seasonal effect can be observed on the reduction of the $S_{\text{TW}}$ criteria due to the MTW (Fig. \ref{fig:changes_S1_seasons}). The improvements are greater for winter than summer.
+A seasonal effect can be observed on the reduction of the S1 criteria due to the MTW (Fig. \ref{fig:changes_S1_seasons}). The improvements are greater for winter than summer.
 
@@
 When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidates situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogs, but their dates have changed.
-In contrast to earlier, both a reduction or an increase of the $E_{\text{RMS}}$ analogy criterion values are possible.
+In contrast to earlier, both a reduction or an increase of the RMSE analogy criterion values are possible.
 Indeed, Fig.
-\ref{fig:changes_RMSE} shows an almost insignificant improvement of the $E_{\text{RMS}}$ values.
-Unlike for the first level of analogy, the relative improvement of the $E_{\text{RMS}}$ values are distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
+\ref{fig:changes_RMSE} shows an almost insignificant improvement of the RMSE values.
+Unlike for the first level of analogy, the relative improvement of the RMSE values are distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
 Once again, the results for the other stations are similar.
@@
 
-A systematic improvement of the $S_{\text{TW}}$ values was previously observed.
+A systematic improvement of the S1 values was previously observed.
 
@@
 Moreover, it requires no additional predictor.
-No relationship was found between the improvement of the score and the reduction of the $S_{\text{TW}}$ criteria, neither with the season.
+No relationship was found between the improvement of the score and the reduction of the S1 criteria, neither with the season.
 
@@
 
-The $S_{\text{TW}}$ criteria was previously found to be improved to a greater extent for the most dynamic situations related with higher precipitation values (Sect.
+The S1 criteria was previously found to be improved to a greater extent for the most dynamic situations related with higher precipitation values (Sect.
 \ref{sec:influence_precip}).
@@
 
-The values of the $S_{\text{SCRP}}$ scores for both methods (Table \ref{table:CRPSS_recalibration}) have significantly increased after recalibration.
+The values of the CRPSS scores for both methods (Table \ref{table:CRPSS_recalibration}) have significantly increased after recalibration.
 
@@
 
-The median of the $S_{\text{TW}}$ values reduction (Fig.
+The median of the S1 values reduction (Fig.
 \ref{fig:changes_S1} bottom) starts approximately at 5~\% for the first analog and reaches more than 10~\% for the last one.
@@
 The minimum improvement starts from 0 and reaches 2--3\%, meaning that the criteria have been improved on most analogs for every day of the calibration period.
-All other stations have a similar improvement of the $S_{\text{TW}}$ criteria, both in terms of distribution shape and amplitude.
+All other stations have a similar improvement of the S1 criteria, both in terms of distribution shape and amplitude.
 
@@
 
-This result of a globally null improvement of the $E_{\text{RMS}}$ values does not mean that the 2Z-2MI method cannot be improved by the MTW.
+This result of a globally null improvement of the RMSE values does not mean that the 2Z-2MI method cannot be improved by the MTW.
 It means that after the selection of the analogs situations in terms of the synoptic circulation, the new candidate dates do not allow to find better analogs in terms of moisture.
@@
 As we saw in Fig.
-\ref{fig:changes_S1}, the improvement of the $S_{\text{TW}}$ criteria grows along with the rank of the analog, which shows an accumulation of better analog situations in the distributions.
+\ref{fig:changes_S1}, the improvement of the S1 criteria grows along with the rank of the analog, which shows an accumulation of better analog situations in the distributions.
 It seems thus profitable to widen the selection of analogs in order to keep also some whose rank has increased, as they appear to be also relevant to predict precipitation values.
@@
 
-Table \ref{table:proxy_CRPSS} presents the $S_{\text{SCRP}}$ scores obtained by the reconstituted series using the proxy of precipitable water.
+Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the reconstituted series using the proxy of precipitable water.
 A slight improvement can be obtained compared to the proportional distribution method, but it is still relatively small, and most of the benefit of the MTW is again lost.
@@
 As \citet{Finet2008} had previously shown, the introduction of a MTW allows finding better analog situations in terms of the atmospheric circulation.
-It has been here demonstrated that the improvement of the $S_{\text{TW}}$ criteria values is growing with the rank of the analog.
+It has been here demonstrated that the improvement of the S1 criteria values is growing with the rank of the analog.
 This is due to the accumulation of better analogs within the predicted distributions.
@@
 	\end{center}
-	\caption{Changes in the $S_{\text{TW}}$ criteria distributions of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$ and (d) $40^{th}$ analog ranks for the Ulrichen station, due to the MTW.}
+	\caption{Changes in the S1 criteria distributions of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$ and (d) $40^{th}$ analog ranks for the Ulrichen station, due to the MTW.}
 	\label{fig:changes_S1_analogs}
@@
 	\end{center}
-	\caption{Synthesis of the changes in the $S_{\text{TW}}$ criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analog.
-(a) Quantiles of the $S_{\text{TW}}$ distributions with and without the MTW.
+	\caption{Synthesis of the changes in the S1 criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analog.
+(a) Quantiles of the S1 distributions with and without the MTW.
 (b) Quantiles of the relative improvements of the S1 criteria when using the MTW.}
@@
 	\end{center}
-	\caption{Distribution of the median improvements of the $S_{\text{TW}}$ criteria, due to the MTW, depending on precipitation thresholds at the Ulrichen station.}
+	\caption{Distribution of the median improvements of the S1 criteria, due to the MTW, depending on precipitation thresholds at the Ulrichen station.}
 	\label{fig:changes_S1_precip_threshold}
@@
 	\end{center}
-	\caption{Seasonal effect on the median reduction of the $S_{\text{TW}}$ criteria for the Ulrichen station due to the MTW. DJF: winter, MAM: spring, JJA: summer SON: fall.}
+	\caption{Seasonal effect on the median reduction of the S1 criteria for the Ulrichen station due to the MTW. DJF: winter, MAM: spring, JJA: summer SON: fall.}
 	\label{fig:changes_S1_seasons}
@@
 	\end{center}
-	\caption{Synthesis of the changes in the $E_{\text{RMS}}$ criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analog.
-(a) Quantiles of the $E_{\text{RMS}}$ distributions with and without the MTW.
-(b) Quantiles of the relative improvements of the $E_{\text{RMS}}$ criteria when using the MTW.}
+	\caption{Synthesis of the changes in the RMSE criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analog.
+(a) Quantiles of the RMSE distributions with and without the MTW.
+(b) Quantiles of the relative improvements of the RMSE criteria when using the MTW.}
 	\label{fig:changes_RMSE}
@@
 	\includegraphics[width=5cm]{figures/changes_CRPS_precip_threshold.pdf}
-	\caption{Differences of the $S_{\text{SCRP}}$ performance score, due to the introduction of the MTW, as a function of precipitation thresholds at the Ulrichen station. The stars represent averages.}
+	\caption{Differences of the CRPSS performance score, due to the introduction of the MTW, as a function of precipitation thresholds at the Ulrichen station. The stars represent averages.}
 	\label{fig:changes_CRPS_precip_threshold}
@@
 			\hline 
-			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{$S_{\text{TW}}$} & \multirow{2}{*}{$N_{1}$} \\
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{$N_{1}$} \\
 			& Z500 & 24~h & & \\ 
@@
 			\hline 
-			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{$S_{\text{TW}}$} & \multirow{2}{*}{$N_{1}$} \\
+			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{$N_{1}$} \\
 			& Z500 & 24~h & & \\ 
 			\hline
-			\multirow{2}{*}{2} & TPW * RH850 & 12~h & \multirow{2}{*}{$E_{\text{RMS}}$} & \multirow{2}{*}{$N_{2}$} \\
+			\multirow{2}{*}{2} & TPW * RH850 & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{2}$} \\
 			& TPW * RH850 & 24~h & & \\ 
@@
 			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{3}{c}{2Z-2MI} \\
-			& $N_{1}$ & $S_{\text{SCRP}}$ & $N_{1}$ & $N_{2}$ & $S_{\text{SCRP}}$ \\ 
+			& $N_{1}$ & CRPSS & $N_{1}$ & $N_{2}$ & CRPSS \\ 
 			\hline
@@
 \begin{table}[htb]
-	\caption{Influence of the archive reduction on the $S_{\text{SCRP}}$. $S_{\text{SCRP}}$ values are provided for both considered methods and the differences are expressed in absolute value.}
+	\caption{Influence of the archive reduction on the CRPSS. CRPSS values are provided for both considered methods and the differences are expressed in absolute value.}
 	\begin{center}
@@
 \begin{table}[htb]
-	\caption{New $S_{\text{SCRP}}$ performance scores for both 2Z and 2Z-2MI methods obtained by the MTW approach.
-The differences are expressed regarding the conventional method with the same archive length.}
+	\caption{New CRPSS performance scores for both 2Z and 2Z-2MI methods obtained by the MTW approach. The differences are expressed regarding the conventional method with the same archive length.}
 	\begin{center}
@@
 \begin{table}[htb]
-	\caption{Values of the $S_{\text{SCRP}}$ (\%) skill score for the newly calibrated parameters using the MTW approach.
+	\caption{Values of the CRPSS (\%) skill score for the newly calibrated parameters using the MTW approach.
 The differences are expressed regarding the conventional method with the same archive length.}
@@
 \begin{table}[htb]
-	\caption{Values of the $S_{\text{SCRP}}$ (\%) skill score for the original and the recalibrated parameters (with the sequential method, as described in Sect.
+	\caption{Values of the CRPSS (\%) skill score for the original and the recalibrated parameters (with the sequential method, as described in Sect.
 \ref{sec:introduction}) using the MTW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
@@
 \begin{table}[htb]
-	\caption{Values of the $S_{\text{SCRP}}$ (\%) skill score for Zermatt, for the original and the recalibrated parameters (with the sequential method, as described in Sect.
+	\caption{Values of the CRPSS (\%) skill score for Zermatt, for the original and the recalibrated parameters (with the sequential method, as described in Sect.
 \ref{sec:introduction}) using the MTW approach on the disaggregated precipitation time series (short and long periods) by means of variables from the reanalysis.}

### 2016-11-08 Moving temporal window - HESS/template.tex
Improvement of the CRPSS plots.

@@
 \begin{figure}[htb]
+	\includegraphics[width=8.3cm]{figures/plots_CRPSS_2Z.pdf}
+	\caption{Performance score (CRPS, \%) of the analog method on the atmospheric circulation, at the different stations, for (dashed) the full archive, i.e.
+1961-2008, (yellow) the reduced archive, i.e.
+1982-2007, (blue) the introduction of the MTW on the reduced archive, and (green) the recalibration of the AM parameters with the MTW.}
+	\label{fig:plots_CRPSS_2Z}
+\end{figure}
+
+\begin{figure}[htb]
+	\includegraphics[width=8.3cm]{figures/plots_CRPSS_2Z-2MI.pdf}
+	\caption{Same as Figure \ref{fig:plots_CRPSS_2Z}, but for the analog method with a second level on the moisture variables.}
+	\label{fig:plots_CRPSS_2Z-2MI}
+\end{figure}
+
+\begin{figure}[htb]
 	\includegraphics[width=5cm]{figures/changes_CRPS_precip_threshold.pdf}

### 2016-11-09 Moving temporal window - HESS/template.tex
Killing some tables.

@@
 Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
-The AM parameters were calibrated on the original archive (Tables \ref{table:performance}) and will be used thereafter.
+The AM parameters were calibrated on the original archive (Tables \ref{table:analog_nb}) and will be used thereafter.
 
-The impact of the change in the archive length is summarized in Table \ref{table:loss_reduction} for both 2Z and 2Z-2MI methods.
+The impact of the change in the archive length is visible in Fig.
+\ref{fig:plots_CRPSS_2Z} for the 2Z method and in Fig.
+\ref{fig:plots_CRPSS_2Z-2MI} for the 2Z-2MI method.
 As expected, a loss of performance can be observed for each station, except for that of Aigle, which seems relatively indifferent to this change.
@@
 
-The new performance scores are provided in Table \ref{table:CRPSS_MTW}, along with the differences regarding the conventional method with the same archive length.
+The new performance scores are provided in Fig.
+\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}, along with the differences regarding the conventional method with the same archive length.
 The differences ranges from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.
@@
 
-After recalibrating, some changes in the optimal number of analogs can be observed for both 2Z and 2Z-2MI methods (Table \ref{table:nb_analogs_new}).
+After recalibrating, some changes in the optimal number of analogs can be observed for both 2Z and 2Z-2MI methods (Table \ref{table:analog_nb}).
 Among these, the east-west dimension of the spatial windows of the circulation analogy tends to decrease (not shown).
@@
 
-The values of the CRPSS scores for both methods (Table \ref{table:CRPSS_recalibration}) have significantly increased after recalibration.
+The values of the CRPSS scores for both methods (Fig. \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}) have significantly increased after recalibration.
 
@@
 \ref{fig:illustration_disaggregation}).
-When using this reconstructed time series on the shorter period, the method performance was degraded (Table \ref{table:disaggregation_proportional} to compare to Table \ref{table:CRPSS_MTW}) and was even below the conventional method without MTW (Table \ref{table:loss_reduction}).
+When using this reconstructed time series on the shorter period, the method performance was degraded and was even below the conventional method without MTW (Table \ref{table:disaggregation_proportional} to compare to Fig.
+\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}).
 The benefit of a better selection of the analog situations is lost due to a precipitation archive of poor quality.
@@
 	\includegraphics[width=8.3cm]{figures/plots_CRPSS_2Z.pdf}
-	\caption{Performance score (CRPS, \%) of the analog method on the atmospheric circulation, at the different stations, for (dashed) the full archive, i.e.
+	\caption{Performance score (CRPSS, \%) of the AM on the atmospheric circulation, at the different stations, for (dashed) the full archive, i.e.
 1961-2008, (yellow) the reduced archive, i.e.
-1982-2007, (blue) the introduction of the MTW on the reduced archive, and (green) the recalibration of the AM parameters with the MTW.}
+1982-2007, (blue) the introduction of the MTW on the reduced archive, and (green) the recalibrated parameters of the AM with the MTW.}
 	\label{fig:plots_CRPSS_2Z}
@@
 \begin{table}[htb]
-	\caption{Number of analogs (of the first and the second level of analogy, respectively $N_{1}$ and $N_{2}$) and skill score (\%) of the method based on the atmospheric circulation only (method 2Z), and the one with a second level of analogy on moisture variables (2Z-2MI), on the full archive.}
+	\caption{Number of analogs (of the first and the second level of analogy, respectively $N_{1}$ and $N_{2}$) of the method based on the atmospheric circulation only (method 2Z), and the one with a second level of analogy on moisture variables (2Z-2MI), on the full archive (Standard) and after recalibration using the MTW (MTW-r).}
 	\begin{center}
-		\begin{tabular}{l c c c c c }
+		\begin{tabular}{l c c c c c c }
 			\hline
-			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{3}{c}{2Z-2MI} \\
-			& $N_{1}$ & CRPSS & $N_{1}$ & $N_{2}$ & CRPSS \\ 
+			\multirow{3}{*}{Station} & \multicolumn{3}{c}{Standard} & \multicolumn{3}{c}{MTW-r} \\
+			& 2Z & \multicolumn{2}{c}{2Z-2MI} & 2Z & \multicolumn{2}{c}{2Z-2MI}\\
+			& $N_{1}$ & $N_{1}$ & $N_{2}$ & $N_{1}$ & $N_{1}$ & $N_{2}$\\ 
 			\hline
-			Ulrichen & 40 & 30.73 & 60 & 25 & 34.31 \\
-			Zermatt & 35 & 23.87 & 55 & 25 & 28.28 \\
-			Visp & 30 & 25.11 & 45 & 25 & 28.85 \\
-			Montana & 40 & 32.55 & 55 & 30 & 36.11 \\
-			Sion & 40 & 26.23 & 90 & 30 & 31.16 \\
-			Aigle & 50 & 30.59 & 100 & 35 & 35.82 \\ 
+			Ulrichen & 40 & 60 & 25 & 50 & 110 & 35\\
+			Zermatt & 35 & 55 & 25 & 55 & 80 & 30\\
+			Visp & 30 & 45 & 25 & 55 & 135 & 35\\
+			Montana & 40 & 55 & 30 & 55 & 110 & 40\\
+			Sion & 40 & 90 & 30 & 55 & 140 & 50\\
+			Aigle & 50 & 100 & 35 & 75 & 135 & 45\\ 
 			\hline
@@
 	\end{center}	
-	\label{table:performance}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Influence of the archive reduction on the CRPSS. CRPSS values are provided for both considered methods and the differences are expressed in absolute value.}
-	\begin{center}
-		\begin{tabular}{l c c c c }
-			\hline
-			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
-			& 82-07 & $\Delta$ & 82-07 & $\Delta$ \\ 
-			\hline
-			Ulrichen & 29.37 & -1.36 & 33.24 & -1.08 \\
-			Zermatt & 22.20 & -1.67 & 26.95 & -1.32 \\
-			Visp & 23.23 & -1.89 & 27.77 & -1.08 \\
-			Montana & 30.79 & -1.76 & 34.77 & -1.34 \\
-			Sion & 24.78 & -1.45 & 29.36 & -1.80 \\
-			Aigle & 30.57 & -0.01 & 35.95 & 0.13 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{table:loss_reduction}
-\end{table}
-
-\begin{table}[htb]
-	\caption{New CRPSS performance scores for both 2Z and 2Z-2MI methods obtained by the MTW approach. The differences are expressed regarding the conventional method with the same archive length.}
-	\begin{center}
-		\begin{tabular}{l c c c c}
-			\hline
-			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
-			& MTW & $\Delta$ & MTW & $\Delta$ \\
-			\hline
-			Ulrichen & 31.12 & 1.74 & 35.44 & 2.20 \\
-			Zermatt & 24.34 & 2.14 & 28.92 & 1.97 \\
-			Visp & 24.39 & 1.16 & 29.42 & 1.64 \\
-			Montana & 31.59 & 0.80 & 36.30 & 1.53 \\
-			Sion & 25.35 & 0.57 & 31.07 & 1.71 \\
-			Aigle & 31.78 & 1.21 & 38.11 & 2.16 \\ 
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{table:CRPSS_MTW}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Number of analogs (of the first and the second level of analogy, respectively $N_{1}$ and $N_{2}$) of the method based on the atmospheric circulation only (method 2Z), and the one with a second level of analogy on moisture variables (2Z-2MI), using the MTW approach.}
-	\begin{center}
-		\begin{tabular}{l c c c }
-			\hline
-			\multirow{2}{*}{Station} & \multicolumn{1}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
-			& $N_{1}$ & $N_{1}$ & $N_{2}$ \\ 
-			\hline
-			Ulrichen & 50 & 110 & 35 \\
-			Zermatt & 55 & 80 & 30 \\
-			Visp & 55 & 135 & 35 \\
-			Montana & 55 & 110 & 40 \\
-			Sion & 55 & 140 & 50 \\
-			Aigle & 75 & 135 & 45 \\ 
-			\hline
-		\end{tabular}
-	\end{center}	
-	\label{table:nb_analogs_new}
-\end{table}
-
-\begin{table}[htb]
-	\caption{Values of the CRPSS (\%) skill score for the newly calibrated parameters using the MTW approach.
-The differences are expressed regarding the conventional method with the same archive length.}
-	\begin{center}
-		\begin{tabular}{l c c c c}
-			\hline
-			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
-			& MTW & $\Delta$ & MTW & $\Delta$ \\
-			\hline
-			Ulrichen & 31.58 & 2.20 & 35.72 & 2.48  \\
-			Zermatt & 24.71 & 2.51 & 29.63 & 2.68 \\
-			Visp & 25.08 & 1.85 & 30.29 & 2.52 \\
-			Montana & 32.22 & 1.43 & 37.15 & 2.38 \\
-			Sion & 26.07 & 1.29 & 31.68 & 2.32 \\
-			Aigle & 32.21 & 1.64 & 38.50 & 2.55 \\
-			\hline
-		\end{tabular}
-	\end{center}
-	\label{table:CRPSS_recalibration}
+	\label{table:analog_nb}
 \end{table}

### 2016-11-10 Moving temporal window - HESS/template.tex
HESS paper under corrections.

@@
 Searching analog situations for a target day starts by a preselection step of the potential candidate for analogy.
-Here, it has been limited to the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects.
+Here, it has been limited to the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects (seasonal stratification).
 Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1), which is a comparison of gradients, over a certain spatial window and at certain hours.
@@
 where $S_{\text{CRP}}^{r}$ is the $S_{\text{CRP}}$ value for the reference (climatological distribution) and $S_{\text{CRP}}^{p}$ would be the one for a perfect prediction (which implies $S_{\text{CRP}}^{p}~=~0$).
-A better prediction is characterized by an increase in CRPSS.
+A better prediction is characterized by an increase in CRPSS: $S_{\text{SCRP}}~=~1$ for a perfect prediction, and $S_{\text{SCRP}}~<~0$ for a prediction with a lower skill than the reference.
 
@@
 
-When searching for analogs on the geopotential heights, as in the 2Z method, there are now 4 times more candidates than before, which obviously allows to find better matches.
+When searching for analogs on the geopotential heights, as in the 2Z method, there are now 4 times more candidates (even though not fully independent) than before, which obviously allows to find better matches.
 
-Figure \ref{fig:changes_S1_analogs} presents the changes in the distributions of the S1 criterion for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogs for the Ulrichen station on the whole calibration period, due to introduction of the MTW.
+Figure \ref{fig:changes_S1_analogs} presents the changes in the distributions of the S1 criterion for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analog situations for the Ulrichen station on the whole calibration period (1961-2008), due to introduction of the MTW.
 The precipitation target remains as before, that is centered on 18~h~UTC (6~h~UTC to 6~h~UTC the next day).
 The shapes of the distributions of the conventional approach and the MTW are similar, but the values of the analogy criteria are now reduced (shifted to the left), and therefore better.
-An increase in the difference between a fixed window and a moving window is identifiable, which means that the last analogs are further improved.
-The latter effect is due to the accumulation of improvements brought by the new analog situations in the selection.
+For analogs with higher ranks (e.g.
+$20^{th}$ or $40^{th}$), the difference between the two distributions is larger than for the first ranks, which means that the improvement increases with the rank of the analogs.
+This is due to the accumulation of improvements brought by the new analog situations in the selection.
 
@@
 When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidates situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogs, but their dates have changed.
-In contrast to earlier, both a reduction or an increase of the RMSE analogy criterion values are possible.
+In contrast to the AM on the atmospheric circulation only, both a reduction or an increase of the RMSE analogy criterion values are possible here with the MTW compared to the static approach.
 Indeed, Fig.
@@
 
-A systematic improvement of the S1 values was previously observed.
+A systematic improvement of the analogy criteria values was previously observed.
 
 The new performance scores are provided in Fig.
-\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}, along with the differences regarding the conventional method with the same archive length.
-The differences ranges from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.
-The introduction of the MTW brings an improvement of the performance that is not very large, but that is nevertheless significant.
-Moreover, it requires no additional predictor.
-No relationship was found between the improvement of the score and the reduction of the S1 criteria, neither with the season.
+\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI} for the 2Z and 2Z-2MI methods respectively.
+The gains, relatively to the static approach on the reduced archive, range from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.
 
@@
 
-The increasing positive trend of skill improvements regarding the precipitation threshold is significant and shows that the prediction of higher precipitation totals is further improved.
-Thus, both the analogy criteria and the performance scores are improved to a greater extent for heavier precipitation events.
-On the contrary, the non-rainy days and small accumulations are not improved.
+The performance score is improved for days with higher precipitation after the introduction of the MTW. On the contrary, non-rainy days and small accumulations are not improved.
 
@@
 
-After recalibrating, some changes in the optimal number of analogs can be observed for both 2Z and 2Z-2MI methods (Table \ref{table:analog_nb}).
-Among these, the east-west dimension of the spatial windows of the circulation analogy tends to decrease (not shown).
-More significantly, the optimal number of analogs increases after introducing the MTW, of a significant order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method.
+After recalibrating, changes in the AM parameters can be observed for both 2Z and 2Z-2MI methods.
+Among these, the zonal extent of the spatial windows of the circulation analogy tends to decrease (not shown).
+More significantly, the optimal number of analogs increases after introducing the MTW, of a significant order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method (Table \ref{table:analog_nb}).
 The number of analogs of the first analogy level of the 2Z-2MI method even reached three times its previous value for the Visp station.
 
-This increase in number of analogs has a slight effect on the performance of the different precipitation classes.
-The same analysis as in Sect.
-\ref{sec:improvement_CRPSS_precip_threshold} has been performed again on the basis of the newly calibrated parameters.
-The results are generally very similar, but a slight performance increase of small precipitation values can be observed at the expense of higher amounts.
-The change in the analogs numbers is likely to be responsible for this difference in the performance distributions.
-
-The values of the CRPSS scores for both methods (Fig. \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}) have significantly increased after recalibration.
+The values of the CRPSS scores for both methods (Fig.
+\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}) have significantly increased after recalibration.
+When analyzing the change in performance per precipitation classes, the results (not shown) are very similar to what was observed in Sect.
+\ref{sec:improvement_CRPSS_precip_threshold}, with a slight performance increase of small precipitation values can be observed at the expense of higher amounts.
 
@@
 
+The introduction of the MTW brings an improvement of the performance that is not very large, but that is nevertheless significant.
+Moreover, it requires no additional predictor.
+More complex methods with additional levels of analogy and more predictors do increase the performance score, and the MTW could also be applied in these situations as it is likely to improve the analogy of the atmospheric circulation anyway.
+
+No relationship was found between the improvement of the score and the reduction of the S1 criteria, neither with the season.
+
 \subsection{Impact of the MTW per precipitation classes}
 
-It can be assumed that the atmospheric conditions with a low dynamism, such as the frequent anticyclonic situations, will not be radically improved by the introduction of the MTW.
-Conversely, dynamic situations, such as weather disturbances, have a well marked temporal evolution.
+Both the analogy criteria (Sect.
+\ref{sec:influence_precip}) and the performance scores (Sect.
+\ref{sec:improvement_CRPSS_precip_threshold}) are improved to a greater extent for heavier precipitation events.
+This is likely due to the fact that higher precipitation events are a consequence of atmospheric conditions with a higher dynamism, such as weather disturbances, which have a well marked temporal evolution.
 Indeed, the position of the driving elements such as the low-pressure center and the fronts change significantly during a day.
 We can therefore expect to improve more significantly these situations with a higher dynamism when introducing a MTW, as better matches to the target situation may be found.
-
-The dynamism of a given atmospheric condition cannot be easily quantified. A basic assumption is considered here, which stipulates that the more a day is rainy, the more dynamic the situation is.
+On the opposite, days with a low dynamism of the atmospheric circulation, such as anticyclonic situations, will not be radically improved by the introduction of the MTW.
 
@@
 
-\subsection{Increase in number of analog situations}
+\subsection{On the increase in number of analogs}
 
-It seems as if the method perceive the increase in the archive length and diversity by allowing to extract more analogs.
+After the recalibration of the method with the MTW, the optimal analog numbers were significantly higher than for the original method.
+
 As we saw in Fig.
@@
 
-\subsection{Why not just making a 6-hourly prediction ?}
+The change in the analogs numbers is likely to be responsible for this difference in the performance distributions. --> thresholds
 
-One can question the interest of using daily totals when a 6-hourly precipitation series can be used.
-The first reason is that the 6-hourly time series generated by the AM may not represent well the dynamic of the accurate precipitation (results not shown), due to a smoothed signal.
-Then, sometimes one just does not need finer resolution than the daily time step.
+\subsection{Why not just making a 6-hourly predictions ?}
+
+One can question the interest of using moving daily totals when 6-hourly precipitation series can be predicted instead.
+A first reason is that the 6-hourly time series generated by the AM might not represent accurately the intra-daily precipitation distribution (results not shown).
+Or, sometimes one just does not need finer resolution than the daily time step, eventually using another disaggregation technique afterwards.
 Finally, when using a reconstructed precipitation archive, the errors in intra-day precipitation distributions have a lesser impact over 24~h daily totals.
@@
 However, one can assume that the gain observed here by introducing a MTW should also be found for a better reanalysis dataset, especially if the information of the atmospheric circulation is more accurate.
+Indeed, a better dataset does not negatively influence the fact that one can find better analog situations at other hours of the day rather than at fixed hours.
+A comparative analysis of several reanalysis dataset within the AM is under work and will be the topic of a dedicated paper.
 

### 2016-11-15 Moving temporal window - HESS/template.tex
HESS paper under corrections.

@@
 \begin{abstract}
-The Analog Method (AM) aims at predicting local weather variables (predictands), such as precipitations, by means of a statistical relationship with predictors at a synoptic scale.
-The analogy is generally assessed in the first place on the geopotential field by mean of a comparison of the gradients, in order to sample the days with a similar atmospheric circulation.
+The Analog Method (AM) aims at predicting local weather variables (predictands), such as precipitation, by means of a statistical relationship with predictors at a synoptic scale.
+The analogy is generally first assessed on the geopotential field gradients, in order to sample days with a similar atmospheric circulation.
+Other predictors, such as moisture variables, can also be added in a successive level of analogy.
 
 The search for candidate situations, for a given target day, is usually undertaken by comparing the state of the atmosphere at fixed hours of the day, for both the target day and the candidate analogs.
-The constraint being the use of daily time series, due to the length of available archives they provide, and the unavailability of equivalent archives at a finer time step.
+The constraint is the use of daily time series, due to the length of available archives they provide, and the unavailability of equivalent archives at a finer time step.
 However, it is unlikely that the best analogy happens at the very same hour, but it may occur at a different time of the day.
@@
 Multiple variations of the methods exist and listings can be found in \citet{BenDaoud2016}.
-The versions that will be considered here are often used as references or benchmarks for various improvements.
 
 The AM is usually implemented with a daily time step, due to the availability of long precipitation archives that have no equivalent at a finer resolution.
-Therefore, the analog situations are assessed on the basis of a daily time step, by comparing predictors at fixed hours of the day, otherwise one would not know what precipitation values to assign to them.
+Therefore, the analog situations are assessed on the basis of a daily time step, by comparing predictors at fixed hours of the day.
 However, it can be expected that the analogy of the synoptic situations does not occur systematically at the same time of the day, and that better candidates can be found by shifting to a different hour.
@@
 The results will thereafter be presented arbitrarily for the Ulrichen station, but they are equivalent for all stations.
-The precipitation time series were then aggregated by means of a moving 24~h-total (see next section).
 
@@
 
-The predictand, here a 24~h precipitation total, results from meteorological situations that are continuous transitions between changing circulation patterns.
-Thus, the observed predictors fields, extracted from reanalysis datasets, are considered at different time of the day and at different heights.
+The predictand, here a 24~h precipitation total (6~h~UTC to 6~h~UTC the next day), results from meteorological situations that are continuous transitions between changing circulation patterns.
+Thus, the observed predictors fields, extracted from reanalysis datasets, are considered at different hours and at different heights.
 In our case, the geopotential height is considered at 1000~hPa (Z1000) at 12~h~UTC and 500~hPa (Z500) at 24~h~UTC.
-The selection of the observation time of the predictor was found by \citet{Bontron2004} to have a significant influence.
+The selection of the time of the day at which the predictors are selected was found by \citet{Bontron2004} to have a significant influence.
 
@@
 When a second level of analogy is added, a higher number of $N_{1}$ analogs is kept on the first level.
-
-\subsection{Calibration of the analog method}
-\label{sec:calibration}
-
-To calibrate the method, the commonly used technique is a semi-automatic sequential procedure elaborated by \citet{Bontron2004}.
-
-\subsection{The moving time window (MTW) approach}
-\label{sec:mtw}
-
-In order to assess the benefit of searching analog situations at a sub-daily time step, an appropriate precipitation series is required.
-On the basis of high resolution time series (Sect.
-\ref{sec:data}), 24~h-totals were processed, but at a 6-hourly time step (temporal resolution of the reanalysis dataset), by means of a moving 24~h-total.
-
-The target situations and their corresponding observed precipitation values (used for validation) do not change, because the prediction is always established for a fixed period of the target day (6--30~h), as before.
-The difference is that the candidates are 4~times more numerous (Fig.
-\ref{fig:principle}).
-
-Based on some preliminary tests (not shown), no constraint was added in order to restrict the selection of multiple analogs within the same candidate dates.
-
-In order to assess this potential improvement of the prediction, precipitation data with a resolution of 10 minutes, on a respectable archive length, was used (Sect.
-\ref{sec:data}).
-It was then aggregated in the form of 24~h-totals, but starting at different 6-hourly time step, by means of a moving total.
 
@@
 \end{equation}
-where $S_{\text{CRP}}^{r}$ is the $S_{\text{CRP}}$ value for the reference (climatological distribution) and $S_{\text{CRP}}^{p}$ would be the one for a perfect prediction (which implies $S_{\text{CRP}}^{p}~=~0$).
+where $S_{\text{CRP}}^{r}$ is the $S_{\text{CRP}}$ value for the reference (climatological distribution \textendash\ i.e.
+the distribution of all precipitation values from the corresponding archive) and $S_{\text{CRP}}^{p}$ would be the one for a perfect prediction (which implies $S_{\text{CRP}}^{p}~=~0$).
 A better prediction is characterized by an increase in CRPSS: $S_{\text{SCRP}}~=~1$ for a perfect prediction, and $S_{\text{SCRP}}~<~0$ for a prediction with a lower skill than the reference.
@@
 The target dates remain unchanged, since the original time slot (6~h~UTC -- 6~h~UTC the next day) is kept, and thus the performance scores can be directly compared with the former ones.
+
+\subsection{The moving time window (MTW) approach}
+\label{sec:mtw}
+
+In order to assess the benefit of searching analog situations at a sub-daily time step, an appropriate precipitation series is required.
+On the basis of high resolution time series (Sect.
+\ref{sec:data}), 24~h-totals were processed, but at a 6-hourly time step (temporal resolution of the reanalysis dataset), by means of a moving 24~h-total.
+
+The target situations and their corresponding observed precipitation values do not change, because the prediction is always established for a fixed period of the target day (6~h~UTC to 6~h~UTC the next day), as before.
+The difference is that the candidates are 4~times more numerous (Fig.
+\ref{fig:principle}).
+
+No constraint was added in order to restrict the selection of multiple analogs within the same candidate dates.
+
+In order to assess this potential improvement of the prediction, precipitation data with a resolution of 10 minutes, on a respectable archive length, was used (Sect.
+\ref{sec:data}).
+It was then aggregated in the form of 24~h-totals, but starting at different 6-hourly time step, by means of a moving total.
+
+\subsection{Calibration of the analog method}
+\label{sec:calibration}
+
+To calibrate the method, the semi-automatic sequential procedure elaborated by \citet{Bontron2004} was used \cite[see also ][]{BenDaoud2016}.
+The analogy levels (eg.
+the atmospheric circulation or moisture index) are calibrated sequentially.
+The parameters calibrated by this approach, for every level of analogy, are the spatial windows on which the predictors are compared and the number of analogs.
+The procedure consists of the following steps \citep{Bontron2004}:
+
+\begin{enumerate}
+	\item Manual selection of the following parameters:
+	\begin{enumerate}
+		\item meteorological variable (e.g. geopotential height, temperature, relative humidity, etc.),
+		\item pressure level (e.g. 500 hPa, ...),
+		\item temporal window (hour of the day \textendash\ e.g. 6, or 12~h~UTC),
+		\item initial analog numbers (e.g. $N_{1}=50$).
+	\end{enumerate}
+
+	\item For every level of analogy:
+	\begin{enumerate}
+		\item Identification of the most skilled unitary cell (1~point for moisture variables and 4 for the geopotential height when using the S1 criteria) over a large domain.
+Every point (or cell) of the full domain is assessed jointly on all predictors of the level of analogy (consisting generally of the same variable, but on different pressure levels and at different hours).
+		\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain.
+The spatial window grows up by repeating the previous steps, until no improvement is reached.
+		\item The number of analog situations is then reconsidered and optimized for the current level of analogy.
+		\item A new level of analogy can then be added, based on other variables (such as the moisture index) at chosen pressure levels and hours of the day.
+The number of analogs for the next level of analogy is initiated at a chosen value.
+Then, the procedure starts again from step (a) for the new level.
+The parameters calibrated on the previous analog levels are fixed and do not change (except the numbers of analogs of every level of analogy, that are optimized once again at the final stage).
+	\end{enumerate}
+	\item Finally, the numbers of analogs are re-assessed for the different levels of analogy. This is done iteratively by varying the number of analogs of each level in a systematic way.
+\end{enumerate}
+
+The calibration is thus done in successive steps, on a limited number of parameters. Previously calibrated parameters are generally not reassessed.
 
@@
 $20^{th}$ or $40^{th}$), the difference between the two distributions is larger than for the first ranks, which means that the improvement increases with the rank of the analogs.
-This is due to the accumulation of improvements brought by the new analog situations in the selection.
 
@@
 \ref{fig:changes_S1}, which shows (top) quantiles of the S1 criteria according to the analog rank for the conventional method and the MTW, and (bottom) quantiles of the relative reduction.
-This confirms that all quantile seem similarly reduced (S1 distributions keep their shape), and that this improvement is constantly increasing from the first to the last analog (Fig.
+This confirms that all quantiles are similarly reduced (S1 distributions keep their shape), and that this improvement is constantly increasing from the first to the last analog (Fig.
 \ref{fig:changes_S1} bottom).
@@
 
-The S1 criteria was previously found to be improved to a greater extent for the most dynamic situations related with higher precipitation values (Sect.
+The S1 criteria was previously found to be improved to a greater extent for higher precipitation values (Sect.
 \ref{sec:influence_precip}).
@@
 Other seasons are between these two extremes, which is consistent with their respective improvements.
-This seasonal effect was observed for each station in a very similar way, and generally even with a slightly larger amplitude than for Ulrichen (see example of the Visp station in Fig.
-\ref{fig:hours_selection_per_season_Visp}).
+This seasonal effect was observed for each station in a very similar way, and generally even with a slightly larger amplitude than for Ulrichen.
 
@@
 
-\subsection{Is a simple reconstructed archive useful for the MTW ?}
+\subsection{Is a simple reconstructed precipitation archive useful for the MTW ?}
 
@@
 
-\subsection{Can a proxy variable help reconstruct a better archive ?}
+\subsection{Can a proxy variable help reconstruct a better precipitation archive ?}
 
@@
 Attempts to reconstruct longer time series based on a simplistic proportional distribution or using meteorological variables from the NCEP reanalysis 1 dataset as proxy did not succeed.
-Other reanalysis datasets could eventually preform better.
+Other reanalysis datasets could eventually perform better.
 
 Perspectives of using the MTW rely on the availability of long precipitation series at a sub-daily time step and with high accuracy.
-The first source of such data is the simple fact that with time, these archives of high temporal resolution precipitation data are getting longer.
+First, these archives of high temporal resolution precipitation data are increasing now with time.
 The second source is the establishment of precipitation reanalysis at a country scale, or the use of reanalysis-driven RCMs (Regional Climate Models) or LAMs (Limited Area Models) on a long period.
@@
 	\label{fig:hours_selection_per_season}
-\end{figure}
-
-\begin{figure}[htb]
-	\includegraphics[width=8.3cm]{figures/hours_selection_per_season_Visp.pdf}
-	\caption{Distribution of the predictors hours in the selected analog dates depending on the season, for the Visp station.}
-	\label{fig:hours_selection_per_season_Visp}
 \end{figure}

### 2016-11-16 Moving temporal window - HESS/template.tex
HESS paper under corrections.

@@
 
-Finding better analog situations does not obligatory imply better skills to predict the precipitation.
-Therefore, the impact of the MTW introduction, and thus the selection of other analog dates, has to be assessed on the performance scores.
-In order to perform this assessment, the 24~h-totals (moving average) at a 6-hourly time step were used (see Sect.
-\ref{sec:data}).
-The target dates remain unchanged, since the original time slot (6~h~UTC -- 6~h~UTC the next day) is kept, and thus the performance scores can be directly compared with the former ones.
-
 \subsection{The moving time window (MTW) approach}
@@
 It was then aggregated in the form of 24~h-totals, but starting at different 6-hourly time step, by means of a moving total.
+
+Finding better analog situations does not necessarily imply better skills to predict the precipitation.
+Therefore, the impact of the MTW introduction, and thus the selection of other analog dates, has to be assessed on the performance scores.
+In order to perform this assessment, the 24~h-totals (moving average) at a 6-hourly time step were used (see Sect.
+\ref{sec:data}).
+The target dates remain unchanged, since the original time slot (6~h~UTC -- 6~h~UTC the next day) is kept, and thus the performance scores can be directly compared with the former ones.
+
+\subsection{Reconstruction of a precipitation archive}
+\label{sec:reconstruction}
+
+The improvement provided by the MTW is interesting, mainly for heavy precipitation events, and thus it would be profitable to be able to apply it to the complete archive.
+Unfortunately, there is no long precipitation time series available with a sub-daily time step.
+In order to reconstruct a longer archive of moving 24~h-totals, different disaggregation approaches of the daily time series were assessed.
+
+A proportional distribution is certainly the simplest approach that can be performed.
+It consists in allocating proportional parts of the original daily time series into a new moving average of 24~h-totals (Fig.
+\ref{fig:illustration_disaggregation}).
+
+As demonstrated in the previous section, the performance improvement brought by the MTW is lost when using a simplistic precipitation time series.
+In order to get closer to the chronology of the actual precipitation, the reconstruction procedure must rely on some informative variable.
+Data from the NCEP/NCAR reanalysis 1 (Sect.
+\ref{sec:data}) was used in this perspective, despite their rough resolution.
 
@@
 The precipitation target remains as before, that is centered on 18~h~UTC (6~h~UTC to 6~h~UTC the next day).
-The shapes of the distributions of the conventional approach and the MTW are similar, but the values of the analogy criteria are now reduced (shifted to the left), and therefore better.
+The shape of the distributions of the conventional approach and the MTW are similar, but the values of the analogy criteria are now reduced (shifted to the left), and therefore better.
 For analogs with higher ranks (e.g.
@@
 
-The new performance scores are provided in Fig.
+The new performance scores (CRPSS) are provided in Fig.
 \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI} for the 2Z and 2Z-2MI methods respectively.
@@
 
+\subsection{Using a reconstructed archive}
+
+When using this reconstructed time series on the shorter period, the method performance was degraded and was even below the conventional method without MTW (Table \ref{table:disaggregation_proportional} to compare to Fig.
+\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}).
+
+The best proxy variable was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series on the period 1982-2007.
+Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and by allowing a time lapse between both series in order to take into account the significant distance separating the weather stations and the reanalysis grid point (details not shown).
+The best proxy for the Zermatt station is the precipitable water at 45° N and 7.5° E, with a time offset of -6~h (Table \ref{table:proxy_correlations}).
+
+Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the reconstituted series using the proxy of precipitable water.
+
 \section{Discussion}
@@
 
-No relationship was found between the improvement of the score and the reduction of the S1 criteria, neither with the season.
-
 \subsection{Impact of the MTW per precipitation classes}
@@
 \ref{sec:improvement_CRPSS_precip_threshold}) are improved to a greater extent for heavier precipitation events.
-This is likely due to the fact that higher precipitation events are a consequence of atmospheric conditions with a higher dynamism, such as weather disturbances, which have a well marked temporal evolution.
+This is likely due to the fact that higher precipitation events are a consequence of atmospheric conditions with a higher dynamics, such as weather disturbances, which have a well marked temporal evolution.
 Indeed, the position of the driving elements such as the low-pressure center and the fronts change significantly during a day.
-We can therefore expect to improve more significantly these situations with a higher dynamism when introducing a MTW, as better matches to the target situation may be found.
-On the opposite, days with a low dynamism of the atmospheric circulation, such as anticyclonic situations, will not be radically improved by the introduction of the MTW.
+We can therefore expect to improve more significantly these situations with a higher dynamics when introducing a MTW, as better matches to the target situation may be found.
+On the opposite, days with a low dynamics of the atmospheric circulation, such as anticyclonic situations, will not be radically improved by the introduction of the MTW.
 
@@
 
-\subsection{Is a simple reconstructed precipitation archive useful for the MTW ?}
+\subsection{Relevance of the simple reconstructed precipitation archive}
 
-The improvement provided by the MTW is interesting, mainly for heavy precipitation events, and thus it would be profitable to be able to apply it to the complete archive.
-Unfortunately, there is no long precipitation time series available with a sub-daily time step.
-In order to reconstruct a longer archive of moving 24~h-totals, different disaggregation approaches of the daily time series were assessed.
-
-A proportional distribution is certainly the simplest approach that can be performed.
-It consists in allocating proportional parts of the original daily time series into a new moving average of 24~h-totals (Fig.
-\ref{fig:illustration_disaggregation}).
-When using this reconstructed time series on the shorter period, the method performance was degraded and was even below the conventional method without MTW (Table \ref{table:disaggregation_proportional} to compare to Fig.
-\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}).
 The benefit of a better selection of the analog situations is lost due to a precipitation archive of poor quality.
 
-\subsection{Can a proxy variable help reconstruct a better precipitation archive ?}
-
-As demonstrated in the previous section, the performance improvement brought by the MTW is lost when using a simplistic precipitation time series.
-In order to get closer to the chronology of the actual precipitation, the reconstruction procedure must rely on some informative variable.
-Data from the NCEP/NCAR reanalysis 1 (Sect.
-\ref{sec:data}) was used in this perspective, despite their rough resolution.
-
-The best proxy variable was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series on the period 1982-2007.
-Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and by allowing a time lapse between both series in order to take into account the significant distance separating the weather stations and the reanalysis grid point (details not shown).
-The best proxy for the Zermatt station is the precipitable water at 45° N and 7.5° E, with a time offset of -6~h.
-
-Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the reconstituted series using the proxy of precipitable water.
 A slight improvement can be obtained compared to the proportional distribution method, but it is still relatively small, and most of the benefit of the MTW is again lost.
@@
 The improvement of the circulation analogy was found to be more important for heavy precipitation events, which are generally related to more dynamic atmospheric situations.
-This dynamism implies more specific circulation patterns that are evolving more rapidly.
+This dynamic implies more specific circulation patterns that are evolving more rapidly.
 Thus, a MTW is found to be of particular interest in this kind of situation, and benefits the prediction of extreme precipitation events.
@@
 The second source is the establishment of precipitation reanalysis at a country scale, or the use of reanalysis-driven RCMs (Regional Climate Models) or LAMs (Limited Area Models) on a long period.
-When such precipitation data will be available, the use of a MTW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.
+Even though outputs from these models might be biased or not accurate enough, information on the timing of the precipitation events could be useful in order to disaggregate stations timeseries.
+When precipitation data with accurate time distribution will be available, the use of a MTW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.
 
@@
 \begin{table}[htb]
+	\caption{Value of the coefficient of determination between the reconstructed 6-hourly precipitation time series using the listed variables, and the accurate time series on the period 1982-2007.
+The grid points surrounding the region are the following: 1) 5° E, 47.5° N, 2) 5° E, 45° N, 3) 7.5° E, 47.5° N, 4) 7.5° E, 45° N.
+The highest coefficient of determination is indicated in bold.}
+	\begin{center}
+		\begin{tabular}{l c c c c c c}
+			\hline
+			\multirow{2}{*}{Variable} & \multirow{2}{*}{Point} &  \multicolumn{5}{c}{Time lapse} \\
+			&  & -12 h & -6 h & 0 h & +6 h & +12 h \\ 
+			\hline
+			\multirow{ 4}{*}{RH1000} & 1 & 0.668 & 0.669 & 0.684 & 0.683 & 0.670 \\
+			& 2 & 0.669 & 0.669 & 0.683 & 0.681 & 0.669 \\
+			& 3 & 0.662 & 0.673 & 0.691 & 0.682 & 0.673 \\
+			& 4 & 0.666 & 0.671 & 0.688 & 0.681 & 0.668 \\ \hline
+			\multirow{ 4}{*}{RH925} & 1 & 0.672 & 0.673 & 0.684 & 0.684 & 0.675 \\
+			& 2 & 0.674 & 0.674 & 0.683 & 0.682 & 0.672 \\
+			& 3 & 0.662 & 0.673 & 0.691 & 0.682 & 0.673 \\
+			& 4 & 0.666 & 0.671 & 0.689 & 0.681 & 0.668 \\ \hline
+			\multirow{ 4}{*}{RH850} & 1 & 0.675 & 0.675 & 0.679 & 0.678 & 0.671 \\
+			& 2 & 0.681 & 0.690 & 0.691 & 0.677 & 0.664 \\
+			& 3 & 0.665 & 0.680 & 0.693 & 0.683 & 0.675 \\
+			& 4 & 0.675 & 0.694 & 0.706 & 0.681 & 0.659 \\ \hline
+			\multirow{ 4}{*}{TCW} & 1 & 0.688 & 0.687 & 0.667 & 0.655 & 0.652 \\
+			& 2 & 0.697 & 0.699 & 0.669 & 0.644 & 0.644 \\
+			& 3 & 0.686 & 0.708 & 0.689 & 0.655 & 0.648 \\
+			& 4 & 0.696 & \textbf{0.721} & 0.696 & 0.643 & 0.636 \\ \hline
+		\end{tabular}
+	\end{center}
+	\label{table:proxy_correlations}
+\end{table}
+
+\begin{table}[htb]
 	\caption{Values of the CRPSS (\%) skill score for Zermatt, for the original and the recalibrated parameters (with the sequential method, as described in Sect.

### 2016-11-16 Moving temporal window - HESS/template.tex
HESS paper under corrections.

@@
 
-The study area is the upper Rh\^{o}ne catchment in Switzerland \cite[see also][]{Horton2012a}.
+The study area is the upper Rh\^{o}ne catchment in Switzerland.
+Precipitation time series (at an hourly time step, on the period 1982--2007) come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle (Fig.
+\ref{fig:map}), which are subject to various meteorological influences \citep{Horton2012}.
 Due to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed.
-The time series (on the period 1982--2007) come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle (Fig.
-\ref{fig:map}), which are subject to various meteorological influences \citep{Horton2012}.
-The results will thereafter be presented arbitrarily for the Ulrichen station, but they are equivalent for all stations.
+The results will thereafter be presented arbitrarily for the Ulrichen station, but are equivalent for all stations.
 
-Predictors are extracted from the NCEP/NCAR reanalysis I \citep{Kalnay1996} dataset with a 6-hourly temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree.
-This dataset is now relatively old, but still often used (see discussion).
+Synoptic-scale variables, used as predictors, are extracted from the NCEP/NCAR reanalysis I \citep{Kalnay1996} dataset with a 6-hourly temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree.
+This dataset is now relatively old, but still often used (see discussion in Sect.
+\ref{sec:old_reanalysis}).
 
@@
 
-The first method is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005, Marty2012}.
-Searching analog situations for a target day starts by a preselection step of the potential candidate for analogy.
-Here, it has been limited to the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects (seasonal stratification).
-Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1), which is a comparison of gradients, over a certain spatial window and at certain hours.
+The first considered AM is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005, Marty2012}.
+Searching for analog situations to a target day starts by a seasonal stratification through a preselection step of the potential candidates for analogy.
+The restriction is here a search for analog days within a 4 months window centered on the target date, for every year of the archive.
+Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1), which is a comparison of gradients, on geopotential heights over a certain spatial window and at certain hours.
 The smaller the S1 values, the more similar the pressure fields.
 
-The predictand, here a 24~h precipitation total (6~h~UTC to 6~h~UTC the next day), results from meteorological situations that are continuous transitions between changing circulation patterns.
-Thus, the observed predictors fields, extracted from reanalysis datasets, are considered at different hours and at different heights.
-In our case, the geopotential height is considered at 1000~hPa (Z1000) at 12~h~UTC and 500~hPa (Z500) at 24~h~UTC.
-The selection of the time of the day at which the predictors are selected was found by \citet{Bontron2004} to have a significant influence.
+The predictand, here a 24~h precipitation total (classically from 6~h~UTC to 6~h~UTC the next day), results from meteorological situations that are continuous transitions between changing circulation patterns.
+Thus, the predictor data, extracted from reanalysis datasets, are considered at different hours of the day.
+Based on \citet{Bontron2005}, geopotential heights are thus compared at 1000~hPa (Z1000) at 12~h~UTC and 500~hPa (Z500) at 24~h~UTC.
+The time of the day at which the predictors are selected was found by \citet{Bontron2004} to have a significant influence.
 
-Then, $N_{1}$ dates with the lowest values of S1 are considered as analogs to the target day, $N_{1}$ being a parameter to calibrate.
-Then, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day.
+Then, $N_{1}$ dates with the lowest values of S1 are considered as analogs to the target day, $N_{1}$ being a parameter to calibrate (see Sect.
+\ref{sec:calibration}).
+Finally, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day.
 This method will be named 2Z further on.
 
-The second reference method adds a subsequent level of analogy on moisture variables, compared by means of the root-mean-square error (RMSE) (method 2Z-2MI, Table \ref{table:method_2Z-2MI}).
-This second predictor is a moisture index made of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850) \citep{Bontron2004}.
-When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogs on the atmospheric circulation, to end up with a smaller number of analog situations.
+The second reference method (2Z-2MI, Table \ref{table:method_2Z-2MI}) adds a subsequent level of analogy on moisture variables, compared by means of the root-mean-square error (RMSE).
+The additional predictor is a moisture index made of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850) \citep{Bontron2004}.
+When adding a second level of analogy, $N_{2}$ dates are subsampled from the $N_{1}$ analogs on the atmospheric circulation, to end up with a smaller number of analog situations.
 When a second level of analogy is added, a higher number of $N_{1}$ analogs is kept on the first level.
@@
 
-The score that is most often considered to assess an AM performance is the Continuous Ranked Probability Score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000}.
+In order to assess the performance of AMs, the continuous ranked probability score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} is often employed \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}.
 It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$.
@@
 
-In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution as the reference.
-The Continuous Ranked Probability Skill Score (CRPSS) is thus defined as following:
+In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution (i.e.
+the distribution of all precipitation values from the corresponding archive) as the reference.
+The continuous ranked probability skill score (CRPSS) is thus defined as follows:
 
@@
 \end{equation}
-where $S_{\text{CRP}}^{r}$ is the $S_{\text{CRP}}$ value for the reference (climatological distribution \textendash\ i.e.
-the distribution of all precipitation values from the corresponding archive) and $S_{\text{CRP}}^{p}$ would be the one for a perfect prediction (which implies $S_{\text{CRP}}^{p}~=~0$).
+where $S_{\text{CRP}}^{r}$ is the $S_{\text{CRP}}$ value for the reference (climatological distribution) and $S_{\text{CRP}}^{p}$ would be the one for a perfect prediction (which implies $S_{\text{CRP}}^{p}~=~0$).
 A better prediction is characterized by an increase in CRPSS: $S_{\text{SCRP}}~=~1$ for a perfect prediction, and $S_{\text{SCRP}}~<~0$ for a prediction with a lower skill than the reference.
@@
 
-To calibrate the method, the semi-automatic sequential procedure elaborated by \citet{Bontron2004} was used \cite[see also ][]{BenDaoud2016}.
+To calibrate the method, the semi-automatic sequential procedure elaborated by \citet{Bontron2004} was used \cite[see also ][]{Horton2012a, BenDaoud2016}.
 The analogy levels (eg.
@@
 \subsection{On the use of an old reanalysis dataset}
+\label{sec:old_reanalysis}
 

### 2016-11-16 Moving temporal window - HESS/template.tex
HESS paper under corrections.

@@
 The study area is the upper Rh\^{o}ne catchment in Switzerland.
-Precipitation time series (at an hourly time step, on the period 1982--2007) come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle (Fig.
+Precipitation time series come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle (Fig.
 \ref{fig:map}), which are subject to various meteorological influences \citep{Horton2012}.
+The data are available at an hourly time step on 25~years (1982 to 2007), and were also obtained at a daily time step on 47~years (1961 to 2008).
 Due to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed.
@@
 
+The moving time window (MTW) technique aims at finding better analog situations at different hours of the day rather than comparing the predictors at fixed hours.
+Thus, instead of looking for analogs at a 24-hourly time step, they are sought at the time step matching the predictor temporal resolution, which is here 6-hourly (Fig.
+\ref{fig:principle}).
+
+The target situations and their corresponding observed precipitation values do not change, because the prediction is always established for a fixed period of the target day (6~h~UTC to 6~h~UTC the next day), as before.
+The difference is that the candidates are 4~times more numerous (even though they are not fully independent).
+No constraint was added in order to restrict the selection of multiple analogs within the same candidate dates.
+
 In order to assess the benefit of searching analog situations at a sub-daily time step, an appropriate precipitation series is required.
 On the basis of high resolution time series (Sect.
-\ref{sec:data}), 24~h-totals were processed, but at a 6-hourly time step (temporal resolution of the reanalysis dataset), by means of a moving 24~h-total.
+\ref{sec:data}), 24~h-totals were processed, but at a 6-hourly time step, by means of a moving 24~h-total.
+As sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~years archive (1961 to 2008) to 25~years (1982 to 2007) needs to be assessed.
 
-The target situations and their corresponding observed precipitation values do not change, because the prediction is always established for a fixed period of the target day (6~h~UTC to 6~h~UTC the next day), as before.
-The difference is that the candidates are 4~times more numerous (Fig.
-\ref{fig:principle}).
-
-No constraint was added in order to restrict the selection of multiple analogs within the same candidate dates.
-
-In order to assess this potential improvement of the prediction, precipitation data with a resolution of 10 minutes, on a respectable archive length, was used (Sect.
-\ref{sec:data}).
-It was then aggregated in the form of 24~h-totals, but starting at different 6-hourly time step, by means of a moving total.
-
-Finding better analog situations does not necessarily imply better skills to predict the precipitation.
-Therefore, the impact of the MTW introduction, and thus the selection of other analog dates, has to be assessed on the performance scores.
-In order to perform this assessment, the 24~h-totals (moving average) at a 6-hourly time step were used (see Sect.
-\ref{sec:data}).
-The target dates remain unchanged, since the original time slot (6~h~UTC -- 6~h~UTC the next day) is kept, and thus the performance scores can be directly compared with the former ones.
-
-\subsection{Reconstruction of a precipitation archive}
+\subsection{Reconstruction of a longer precipitation archive}
 \label{sec:reconstruction}
 
-The improvement provided by the MTW is interesting, mainly for heavy precipitation events, and thus it would be profitable to be able to apply it to the complete archive.
-Unfortunately, there is no long precipitation time series available with a sub-daily time step.
-In order to reconstruct a longer archive of moving 24~h-totals, different disaggregation approaches of the daily time series were assessed.
+Applying the MTW technique involve the need of sub-daily precipitation timeseries.
+However, such data are not available on long periods.
+As the AM benefits from long archives, it would be profitable to be able to apply the MTW to a longer archive.
+Thus, in order to reconstruct a longer archive of moving 24~h-totals, two simple disaggregation approaches of the daily time series were assessed.
 
-A proportional distribution is certainly the simplest approach that can be performed.
-It consists in allocating proportional parts of the original daily time series into a new moving average of 24~h-totals (Fig.
+The first technique is a proportional distribution, where the observed daily precipitation is considered constant during the measuring period (6~h~UTC to 6~h~UTC the next day).
+It then consists in allocating proportional parts of the original daily time series into a new moving average of 24~h-totals (Fig.
 \ref{fig:illustration_disaggregation}).
 
-As demonstrated in the previous section, the performance improvement brought by the MTW is lost when using a simplistic precipitation time series.
-In order to get closer to the chronology of the actual precipitation, the reconstruction procedure must rely on some informative variable.
+The second approach aims at getting closer to the chronology of the actual precipitation by relying on some informative variable during the reconstruction procedure.
+The best proxy variable is identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series on the period 1982-2007.
+Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and by allowing a time lapse between both series in order to take into account the significant distance separating the weather stations and the reanalysis grid point.
 Data from the NCEP/NCAR reanalysis 1 (Sect.
@@
 
-To calibrate the method, the semi-automatic sequential procedure elaborated by \citet{Bontron2004} was used \cite[see also ][]{Horton2012a, BenDaoud2016}.
+To calibrate the method, the semi-automatic sequential procedure elaborated by \citet{Bontron2004} was used \cite[see also ][]{Horton2012a, Radanovics2013, BenDaoud2016}.
 The analogy levels (eg.
@@
 		\item Identification of the most skilled unitary cell (1~point for moisture variables and 4 for the geopotential height when using the S1 criteria) over a large domain.
-Every point (or cell) of the full domain is assessed jointly on all predictors of the level of analogy (consisting generally of the same variable, but on different pressure levels and at different hours).
+Every point (or cell) of the full domain is assessed on all predictors of the level of analogy jointly (consisting generally of the same variable, but on different pressure levels and at different hours).
 		\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain.
@@
 		\item The number of analog situations is then reconsidered and optimized for the current level of analogy.
+	\end{enumerate}
 	\item A new level of analogy can then be added, based on other variables (such as the moisture index) at chosen pressure levels and hours of the day.
 The number of analogs for the next level of analogy is initiated at a chosen value.
-Then, the procedure starts again from step (a) for the new level.
-The parameters calibrated on the previous analog levels are fixed and do not change (except the numbers of analogs of every level of analogy, that are optimized once again at the final stage).
-	\end{enumerate}
+Then, the procedure starts again from step (2) for the new level.
+The parameters calibrated on the previous analog levels are fixed and do not change.
 	\item Finally, the numbers of analogs are re-assessed for the different levels of analogy. This is done iteratively by varying the number of analogs of each level in a systematic way.
@@
 
-The calibration is thus done in successive steps, on a limited number of parameters. Previously calibrated parameters are generally not reassessed.
+The calibration is thus done in successive steps, on a limited number of parameters.
+Previously calibrated parameters are generally not reassessed (except for the number of analogs).
+More advanced techniques, such as using Genetic Algorithms \citep{Horton2016}, exist, but are out of the scope of the present study.
 
@@
 
-As sub-daily precipitation time series are usually available on a shorter period than traditional daily time steps, the first assessment consists in assessing the loss of performance resulting from a reduction of a 47~years archive (1961 to 2008) to 25~years (1982 to 2007).
-This change is assessed with the original method, without MTW.
+The performance loss resulting from a reduction of a 47~years archive (1961 to 2008, corresponding to the daily time series) to 25~years (1982 to 2007, corresponding to the hourly time series) was assessed with the original method, without MTW.
+Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
+The AM parameters were calibrated on the original archive (see resulting analog numbers in Tables \ref{table:analog_nb}) and will be used thereafter.
 
-Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
-The AM parameters were calibrated on the original archive (Tables \ref{table:analog_nb}) and will be used thereafter.
-
-The impact of the change in the archive length is visible in Fig.
+The impact of the archive reduction can be seen in Fig.
 \ref{fig:plots_CRPSS_2Z} for the 2Z method and in Fig.
@@
 
-The best proxy variable was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series on the period 1982-2007.
-Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and by allowing a time lapse between both series in order to take into account the significant distance separating the weather stations and the reanalysis grid point (details not shown).
-The best proxy for the Zermatt station is the precipitable water at 45° N and 7.5° E, with a time offset of -6~h (Table \ref{table:proxy_correlations}).
+ (details not shown). The best proxy for the Zermatt station is the precipitable water at 45° N and 7.5° E, with a time offset of -6~h (Table \ref{table:proxy_correlations}).
 
@@
 All other stations have a similar improvement of the S1 criteria, both in terms of distribution shape and amplitude.
+
+Finding better analog situations does not necessarily imply better skills to predict the precipitation.
 
@@
 The benefit of a better selection of the analog situations is lost due to a precipitation archive of poor quality.
+
+As demonstrated in the previous section, the performance improvement brought by the MTW is lost when using a simplistic precipitation time series.
 

### 2016-11-17 Moving temporal window - HESS/template.tex
HESS paper under corrections.

@@
 
-The MTW resulted in a better analogy in terms of the atmospheric circulation, with improved values of the analogy criteria on the whole distribution of analog dates.
+The MTW resulted in a better analogy in terms of the atmospheric circulation, with improved values of the analogy criterion on the whole distribution of analog dates.
 The improvement was found to grow with the analog ranks due to an accumulation of more similar situations in the selection.
@@
 
-Previous tests showed the benefit, in terms of analogy criteria values, of searching for analog synoptic situations at a finer time step, but without assessing the impact on the prediction skills \citep{Finet2008}.
+Previous tests showed the benefit, in terms of analogy criterion values, of searching for analog synoptic situations at a finer time step, but without assessing the impact on the prediction skills \citep{Finet2008}.
 
@@
 \ref{sec:archive_reduction}).
-The benefit of introducing a MTW was assessed first in regards to the analogy criteria improvement (Sect.
+The benefit of introducing a MTW was assessed first in regards to the analogy criterion improvement (Sect.
 \ref{sec:influence_criteria}), and then in terms of precipitation prediction skill (Sect.
@@
 	\begin{enumerate}
-		\item Identification of the most skilled unitary cell (1~point for moisture variables and 4 for the geopotential height when using the S1 criteria) over a large domain.
+		\item Identification of the most skilled unitary cell (1~point for moisture variables and 4 for the geopotential height when using the S1 criterion) over a large domain.
 Every point (or cell) of the full domain is assessed on all predictors of the level of analogy jointly (consisting generally of the same variable, but on different pressure levels and at different hours).
@@
 
-The performance loss resulting from a reduction of a 47~years archive (1961 to 2008, corresponding to the daily time series) to 25~years (1982 to 2007, corresponding to the hourly time series) was assessed with the original method, without MTW.
+The performance loss resulting from a reduction of a 47~years archive (1961 to 2008, corresponding to the daily time series) to 25~years (1982 to 2007, corresponding to the hourly time series, see Sect.
+\ref{sec:mtw}) was assessed with the original method, without MTW.
 Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
@@
 
-\subsection{Influence on the analogy criteria}
+\subsection{Influence on the analogy criterion}
 \label{sec:influence_criteria}
@@
 
-When searching for analogs on the geopotential heights, as in the 2Z method, there are now 4 times more candidates (even though not fully independent) than before, which obviously allows to find better matches.
-
-Figure \ref{fig:changes_S1_analogs} presents the changes in the distributions of the S1 criterion for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analog situations for the Ulrichen station on the whole calibration period (1961-2008), due to introduction of the MTW.
-The precipitation target remains as before, that is centered on 18~h~UTC (6~h~UTC to 6~h~UTC the next day).
-The shape of the distributions of the conventional approach and the MTW are similar, but the values of the analogy criteria are now reduced (shifted to the left), and therefore better.
+When searching for analogs in the first level of analogy, such as on the geopotential heights in the 2Z method (Sect.
+\ref{sec:analog_method}), there are 4 times more candidates (even though not fully independent) with the MTW than before (Sect.
+\ref{sec:mtw}).
+Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions of the analogy criterion (S1) for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analog rank at the Ulrichen station on the whole calibration period (1961-2008 -- we can use the full period here, as we do not consider precipitation at this stage), due to introduction of the MTW.
+The shape of the distributions of the conventional approach and the MTW are similar, but the values of the analogy criterion are now reduced (shifted to the left), and therefore better.
 For analogs with higher ranks (e.g.
@@
 
-The improvements of the S1 criteria are summarized in Fig.
-\ref{fig:changes_S1}, which shows (top) quantiles of the S1 criteria according to the analog rank for the conventional method and the MTW, and (bottom) quantiles of the relative reduction.
+The improvements of the S1 criterion with the rank of the analogs are summarized in Fig.
+\ref{fig:changes_S1}, which shows (top) quantiles of the S1 criterion for the conventional method and the MTW, and (bottom) quantiles of the relative reduction (meaning improvement) due to the MTW.
 This confirms that all quantiles are similarly reduced (S1 distributions keep their shape), and that this improvement is constantly increasing from the first to the last analog (Fig.
@@
 
-The impact of the MTW on the analogy criteria has been decomposed per precipitation classes.
-The results of this analysis are summarized in Fig.
+The impact of the MTW on the analogy criterion has been analyzed per precipitation classes.
+The results are summarized in Fig.
 \ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for days with precipitation (organized into classes) between two thresholds.
@@
 Atmospheric dynamics varies greatly from one season to another, which reflects on the performance of the AM that is generally lower between June and August \citep{Bliefernicht2010}.
-It therefore makes sense to verify the effect of the MTW separately per season.
-
-A seasonal effect can be observed on the reduction of the S1 criteria due to the MTW (Fig. \ref{fig:changes_S1_seasons}). The improvements are greater for winter than summer.
+The effect of the MTW on the S1 criterion per season is presented in Fig.
+\ref{fig:changes_S1_seasons}.
+Differences between the seasons are substantial.
+The improvements are greater for winter than summer.
 
@@
 
-When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidates situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogs, but their dates have changed.
+When adding the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogs, but their dates have changed.
 In contrast to the AM on the atmospheric circulation only, both a reduction or an increase of the RMSE analogy criterion values are possible here with the MTW compared to the static approach.
@@
 
-\subsection{Impact on performance scores}
+\subsection{Impact on the prediction relevance}
 \label{sec:influence_scores}
 
-A systematic improvement of the analogy criteria values was previously observed.
-
 The new performance scores (CRPSS) are provided in Fig.
-\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI} for the 2Z and 2Z-2MI methods respectively.
-The gains, relatively to the static approach on the reduced archive, range from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.
+\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI} for the 2Z and 2Z-2MI methods respectively, on the reduced archive (1982--2007).
+The gains, relatively to the static approach on the same archive, range from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.
 
@@
 
-The S1 criteria was previously found to be improved to a greater extent for higher precipitation values (Sect.
+The S1 criterion was previously found to be improved to a greater extent for higher precipitation values (Sect.
 \ref{sec:influence_precip}).
-The changes in terms of performance scores will now be assessed regarding precipitation thresholds.
+The changes in terms of performance scores are now also assessed per precipitation classes.
 Fig.
 \ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, other stations having the same behavior.
-
-The performance score is improved for days with higher precipitation after the introduction of the MTW. On the contrary, non-rainy days and small accumulations are not improved.
+The performance score is improved for days with higher precipitation after the introduction of the MTW.
+On the contrary, non-rainy days and small precipitation values are not improved.
 
@@
 The previous assessment of the performance improvement was established with the original parameters optimized with a fixed time window.
-However, one can assume that the introduction of the MTW may change the optimum of some parameters.
-The calibration has then been reprocessed.
+However, one can assume that the introduction of the MTW might change the optimum value of some parameters.
+The calibration (see Sect.
+\ref{sec:calibration}) has then been reprocessed.
 
@@
 Among these, the zonal extent of the spatial windows of the circulation analogy tends to decrease (not shown).
-More significantly, the optimal number of analogs increases after introducing the MTW, of a significant order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method (Table \ref{table:analog_nb}).
+More significantly, the optimal number of analogs increases after introducing the MTW, of a considerable order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method (Table \ref{table:analog_nb}).
 The number of analogs of the first analogy level of the 2Z-2MI method even reached three times its previous value for the Visp station.
@@
 When analyzing the change in performance per precipitation classes, the results (not shown) are very similar to what was observed in Sect.
-\ref{sec:improvement_CRPSS_precip_threshold}, with a slight performance increase of small precipitation values can be observed at the expense of higher amounts.
+\ref{sec:improvement_CRPSS_precip_threshold}, with a slight performance increase of small precipitation values that can be observed at the expense of higher amounts.
 
 \subsection{Using a reconstructed archive}
+\label{sec:reconstruction_results}
 
-When using this reconstructed time series on the shorter period, the method performance was degraded and was even below the conventional method without MTW (Table \ref{table:disaggregation_proportional} to compare to Fig.
+When using the first reconstructed time series (on the reduced period), based on the proportional distribution (see Sect.
+\ref{sec:reconstruction}), the AM performance was degraded and was even below the conventional method without MTW (Table \ref{table:disaggregation_proportional} to compare to Fig.
 \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}).
 
- (details not shown). The best proxy for the Zermatt station is the precipitable water at 45° N and 7.5° E, with a time offset of -6~h (Table \ref{table:proxy_correlations}).
-
+For the second approach, the synoptic proxy to use for the temporal disaggregation of the daily time series had to be identified first.
+The results are illustrated for the Zermatt station.
+Amongst the considered moisture variables (see Sect.
+\ref{sec:reconstruction}), the best proxy was the precipitable water at 45° N and 7.5° E, with a time offset of -6~h (Table \ref{table:proxy_correlations}).
 Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the reconstituted series using the proxy of precipitable water.
@@
 
-\subsection{Improvement of the atmospheric circulation analogy}
+\subsection{Improvement of the selection of analog situations}
 
-The median of the S1 values reduction (Fig.
+On the first level of analogy, the median of the S1 values reduction (Fig.
 \ref{fig:changes_S1} bottom) starts approximately at 5~\% for the first analog and reaches more than 10~\% for the last one.
-This increasing trend with the analog rank can be explained by the accumulation of better analogs in the distribution.
-The minimum improvement starts from 0 and reaches 2--3\%, meaning that the criteria have been improved on most analogs for every day of the calibration period.
-All other stations have a similar improvement of the S1 criteria, both in terms of distribution shape and amplitude.
+This increase of improvements with the analog rank can be explained by the accumulation of better analogs in the distribution.
+The curve representing the minimum improvement is quickly slightly superior to zero, meaning that the criteria have been improved on most analogs for every day of the calibration period.
+All other stations have a similar improvement of the S1 criterion, both in terms of distribution shape and amplitude.
+The introduction of the MTW allows finding better analog situations in the first level of analogy, resulting in a selection of days with more similar atmospheric circulation.
+
+When adding a second level of analogy on moisture variables, the criteria values (RMSE) are not improved by the MTW as the number of candidates is not higher (still the $N_{1}$ days selected in the first level of analogy).
+However, this result of a globally null improvement of the RMSE values does not mean that the 2Z-2MI method cannot be improved by the MTW.
+It means that after the selection of the analog situations in terms of the synoptic circulation, the new candidate dates do not allow to find better analogs in terms of moisture.
+However, the selected dates have changed in the first level of analogy, and thus also in the final selection, which can potentially improve the prediction skill.
+
+\subsection{Improvement of the precipitation prediction}
 
 Finding better analog situations does not necessarily imply better skills to predict the precipitation.
-
-\subsection{Improvement of the moisture analogy}
-
-This result of a globally null improvement of the RMSE values does not mean that the 2Z-2MI method cannot be improved by the MTW.
-It means that after the selection of the analogs situations in terms of the synoptic circulation, the new candidate dates do not allow to find better analogs in terms of moisture.
-However, the selected dates have changed in the first level of analogy, and thus also in the final selection, which can potentially improve the performance scores on the predictand.
-
+This had to be assessed and the MTW was found to improve the skill of the precipitation prediction for both the 2Z and 2Z-2MI methods (Fig.
+\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}).
+The improvement of the performance is not very large, but is nevertheless substantial.
+Moreover, it requires no additional predictor.
 With the introduction of the MTW, the performance loss related to the reduction of the archive length is compensated.
 
-The introduction of the MTW brings an improvement of the performance that is not very large, but that is nevertheless significant.
-Moreover, it requires no additional predictor.
-More complex methods with additional levels of analogy and more predictors do increase the performance score, and the MTW could also be applied in these situations as it is likely to improve the analogy of the atmospheric circulation anyway.
-
-\subsection{Impact of the MTW per precipitation classes}
+More complex methods with additional levels of analogy and more predictors do increase the performance score, and the MTW could also be applied in these situations, as it is likely to improve the analogy of the atmospheric circulation anyway.
 
@@
 \ref{sec:improvement_CRPSS_precip_threshold}) are improved to a greater extent for heavier precipitation events.
-This is likely due to the fact that higher precipitation events are a consequence of atmospheric conditions with a higher dynamics, such as weather disturbances, which have a well marked temporal evolution.
+This is likely due to the fact that higher precipitation events are a consequence of atmospheric conditions with a greater dynamics, such as weather disturbances, which have a well marked temporal evolution.
 Indeed, the position of the driving elements such as the low-pressure center and the fronts change significantly during a day.
-We can therefore expect to improve more significantly these situations with a higher dynamics when introducing a MTW, as better matches to the target situation may be found.
+Moreover, these situations are less numerous than anticyclonic situations, which makes it less likely to find very good analogs at the same time of the day.
+We can therefore expect to improve more significantly these situations with a greater dynamics when introducing a MTW, as better matches to the target situation may be found.
 On the opposite, days with a low dynamics of the atmospheric circulation, such as anticyclonic situations, will not be radically improved by the introduction of the MTW.
@@
 
+Section \ref{sec:seasonal_effect} and Fig.
+\ref{fig:changes_S1_seasons} revealed a difference of the improvement of the S1 criterion according to the season, with greater improvements for winter than summer.
 One hypothesis is that the diurnal effects of the summer months have an influence on the atmospheric circulation, at least in the lower layers.
@@
 This means a change of 75\% of the analogs selection compared to the conventional approach, which improves the circulation analogy.
-
-On the contrary, the summer months have a preference for the initial temporal window (Z500 24~h \& Z1000 12~h), due to more pronounced diurnal effects which reduces the potential for improvement of the criteria.
+On the contrary, the summer months have a preference for the initial temporal window (Z500 24~h \& Z1000 12~h), likely due to more pronounced diurnal effects which reduces the potential for improvement of the criteria.
 Other seasons are between these two extremes, which is consistent with their respective improvements.
@@
 
-After the recalibration of the method with the MTW, the optimal analog numbers were significantly higher than for the original method.
-
+After the recalibration of the AMs with the MTW, the optimal analog numbers were significantly higher than for the original methods (see Sect.
+\ref{sec:recalibration} and Fig.
+\ref{table:analog_nb}).
 As we saw in Fig.
-\ref{fig:changes_S1}, the improvement of the S1 criteria grows along with the rank of the analog, which shows an accumulation of better analog situations in the distributions.
+\ref{fig:changes_S1}, the improvement of the S1 criterion grows along with the rank of the analog, which shows an accumulation of better analog situations in the distributions.
 It seems thus profitable to widen the selection of analogs in order to keep also some whose rank has increased, as they appear to be also relevant to predict precipitation values.
@@
 
-The change in the analogs numbers is likely to be responsible for this difference in the performance distributions. --> thresholds
+A higher number of analogs generally means, with an archive of fixed length, a poorer analogy.
+Indeed, when the choice of the predictors or the parameters are improved, leading to a better prediction, the optimal number of analog situations decreases.
+However, when the length of the archive increases, the optimal number of analogs increases too, for a better performance, up to a certain threshold (\citealt{Bontron2004}, see also Fig.
+7 of \citealt{Hamill2006a}).
+The observed increases in the number of analog situations with the MTW result in better performance skills, as it can be seen as an inflation of the archive.
+The MTW enriches the pool of available situations, even though they are not fully independent.
 
@@
 A first reason is that the 6-hourly time series generated by the AM might not represent accurately the intra-daily precipitation distribution (results not shown).
-Or, sometimes one just does not need finer resolution than the daily time step, eventually using another disaggregation technique afterwards.
+Also, sometimes one just does not need finer resolution than the daily time step, eventually using another disaggregation technique afterwards.
 Finally, when using a reconstructed precipitation archive, the errors in intra-day precipitation distributions have a lesser impact over 24~h daily totals.
@@
 
-\subsection{Relevance of the simple reconstructed precipitation archive}
+\subsection{Relevance of the reconstructed precipitation archives}
 
-The benefit of a better selection of the analog situations is lost due to a precipitation archive of poor quality.
-
-As demonstrated in the previous section, the performance improvement brought by the MTW is lost when using a simplistic precipitation time series.
-
-A slight improvement can be obtained compared to the proportional distribution method, but it is still relatively small, and most of the benefit of the MTW is again lost.
+The two simple methods assessed to reconstruct precipitation archives (Sect.
+\ref{sec:reconstruction}) did not result in valuable outputs (Sect.
+\ref{sec:reconstruction_results}).
+Indeed, the performance improvement brought by the MTW is lost due to a precipitation archive of poor quality.
+A slight improvement can be obtained for the second method relying on a proxy variable compared to the proportional distribution method, but it is still relatively small, and most of the benefit of the MTW is lost.
 A more recent reanalysis archive with more accurate moisture variables might produce better proxies.
@@
 The MTW is profitable, provided that the precipitation series are close to the observed one.
-Without precipitation series with an accurate sub-daily chronology, the introduction of a MTW remains fruitless.
+Without precipitation series with an accurate sub-daily chronology, the introduction of a MTW does not improve the precipitation prediction.
 
@@
 However, it is unlikely that two analog synoptic situations, that evolve relatively quickly, would correspond optimally at the same hour of the day.
-It is thus more likely that a better match can be found at another time, which can change the selection of the analogs dates.
+It is thus probable that better matches can be found at another time, which can change the selection of the analogs dates.
 
 As \citet{Finet2008} had previously shown, the introduction of a MTW allows finding better analog situations in terms of the atmospheric circulation.
-It has been here demonstrated that the improvement of the S1 criteria values is growing with the rank of the analog.
+It has been here demonstrated that the improvement of the S1 criterion values is growing with the rank of the analog.
 This is due to the accumulation of better analogs within the predicted distributions.
 
-The improvement of the circulation analogy was found to be more important for heavy precipitation events, which are generally related to more dynamic atmospheric situations.
-This dynamic implies more specific circulation patterns that are evolving more rapidly.
-Thus, a MTW is found to be of particular interest in this kind of situation, and benefits the prediction of extreme precipitation events.
+The improvement of the circulation analogy was found to be more important for heavy precipitation events, which are generally related to more dynamic atmospheric situations and are less frequent in the archive.
+This dynamism implies more specific circulation patterns that are evolving more rapidly.
+Thus, a MTW is found to be of particular interest in this kind of situation, and benefits the prediction of heavier precipitation events.
 
@@
 
-The impact of the MTW on the prediction performance has never been assessed before, due to the shortcoming of long precipitation series at a sub-daily time step.
-The impact of the MTW approach could be assessed on a 25 years time series with a high temporal resolution.
+The impact of the MTW on the prediction skill has never been assessed before, due to the shortcoming of long precipitation series at a sub-daily time step.
+The impact of the MTW approach was assessed on a 25 years time series with a high temporal resolution.
 After the introduction of the MTW, the performance scores increased of the same order of magnitude as if the length of the archive doubled, in this case study.
@@
 A wider selection of analog situations, containing those whose rank decreased, seemed profitable for the prediction performance.
-The number of good analogs is thus globally increased.
+The number of good analogs is thus globally increased, in the same way as if the archive length increased.
 This change seems to benefit mainly the prediction of days with small precipitation totals.
 
-The importance of the quality of the precipitation archive was also demonstrated, as too simplistic reconstructions of 6-hourly time series lead to a loss of all the improvement brought by better analog situations identified by the MTW.
+The importance of the quality of the precipitation archive was also demonstrated, as too simplistic reconstructions of 6-hourly time series lead to a loss of all the improvement brought by the MTW.
 The precipitation prediction is improved only when the precipitation chronology is close to the accurate one.
@@
 First, these archives of high temporal resolution precipitation data are increasing now with time.
-The second source is the establishment of precipitation reanalysis at a country scale, or the use of reanalysis-driven RCMs (Regional Climate Models) or LAMs (Limited Area Models) on a long period.
-Even though outputs from these models might be biased or not accurate enough, information on the timing of the precipitation events could be useful in order to disaggregate stations timeseries.
+Another possible source of such archives is the establishment of precipitation reanalysis at a country scale, or the use of reanalysis-driven RCMs (Regional Climate Models) or LAMs (Limited Area Models) on a long period.
+Even though outputs from these models might be biased or not accurate enough, information on the timing of the precipitation events could be useful in order to disaggregate stations time series.
 When precipitation data with accurate time distribution will be available, the use of a MTW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.
@@
 \begin{acknowledgements}
-Thanks to Dominique B\'{e}rod for his support and to Renaud Marty for his fruitful collaboration over the years.
-
 Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
+Thanks to Dominique B\'{e}rod for his support.
 
@@
 	\end{center}
-	\caption{Changes in the S1 criteria distributions of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$ and (d) $40^{th}$ analog ranks for the Ulrichen station, due to the MTW.}
+	\caption{Changes in the S1 criterion distributions of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$ and (d) $40^{th}$ analog ranks for the Ulrichen station, due to the MTW.}
 	\label{fig:changes_S1_analogs}
@@
 	\end{center}
-	\caption{Synthesis of the changes in the S1 criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analog.
+	\caption{Synthesis of the changes in the S1 criterion, due to the MTW, for the Ulrichen station, depending on the ranks of the analog.
 (a) Quantiles of the S1 distributions with and without the MTW.
-(b) Quantiles of the relative improvements of the S1 criteria when using the MTW.}
+(b) Quantiles of the relative improvements of the S1 criterion when using the MTW.}
 	\label{fig:changes_S1}
@@
 	\end{center}
-	\caption{Distribution of the median improvements of the S1 criteria, due to the MTW, depending on precipitation thresholds at the Ulrichen station.}
+	\caption{Distribution of the median improvements of the S1 criterion, due to the MTW, depending on precipitation thresholds at the Ulrichen station.}
 	\label{fig:changes_S1_precip_threshold}
@@
 	\end{center}
-	\caption{Seasonal effect on the median reduction of the S1 criteria for the Ulrichen station due to the MTW. DJF: winter, MAM: spring, JJA: summer SON: fall.}
+	\caption{Seasonal effect on the median reduction of the S1 criterion for the Ulrichen station due to the MTW. DJF: winter, MAM: spring, JJA: summer SON: fall.}
 	\label{fig:changes_S1_seasons}
@@
 	\end{center}
-	\caption{Synthesis of the changes in the RMSE criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analog.
+	\caption{Synthesis of the changes in the RMSE criterion, due to the MTW, for the Ulrichen station, depending on the ranks of the analog.
 (a) Quantiles of the RMSE distributions with and without the MTW.
-(b) Quantiles of the relative improvements of the RMSE criteria when using the MTW.}
+(b) Quantiles of the relative improvements of the RMSE criterion when using the MTW.}
 	\label{fig:changes_RMSE}
@@
 The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window).
-The criteria used for the current level of analogy is then provided, as well as the number of analogs.}
+The criterion used for the current level of analogy is then provided, as well as the number of analogs.}
 	\footnotesize
@@
 			\hline
-			Level & Variable & Hour & Criteria & Nb \\ 
+			Level & Variable & Hour & Criterion & Nb \\ 
 			\hline 
@@
 			\hline 
-			Level & Variable & Hour & Criteria & Nb \\ 
+			Level & Variable & Hour & Criterion & Nb \\ 
 			\hline 

### 2016-11-22 Moving temporal window - HESS/template.tex
HESS paper under corrections.
New version of the introduction.

@@
 
-The Analog Method (AM) is based on the principle that two relatively similar synoptic situations may produce relatively similar local effects \citep{Lorenz1956, Lorenz1969}.
-Multiple variations of the methods exist and listings can be found in \citet{BenDaoud2016}.
+Analog methods (AMs) are based on the hypothesis that two relatively similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}.
+They are part of the statistical downscaling methods \cite{Maraun2010}.
+They consist in finding past situations that are similar, in terms of the atmospheric circulation or other synoptic predictors, to the target day of interest.
+Then, the local weather variables of interest (predictand) that were observed at the analog dates are used to construct a probabilistic prediction for the target day \citep{Duband1970, Bontron2005}.
+Multiple variations of the methods exist \citep[a non exhaustive listing can be found in][]{BenDaoud2016}.
+AMs are used for operational precipitation forecasting \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Hamill2015, BenDaoud2016}, as well as precipitation downscaling in a climate perspective \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015}.
+Other applications focus on temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectories of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
 
-The AM is usually implemented with a daily time step, due to the availability of long precipitation archives that have no equivalent at a finer resolution.
+AMs are usually implemented with a daily time step (see references above), due to the availability of long precipitation archives that have no equivalent at a finer resolution.
 Therefore, the analog situations are assessed on the basis of a daily time step, by comparing predictors at fixed hours of the day.
@@
 On this assumption, a moving time window (MTW) was introduced to allow searching for candidates at different hours of the day.
-
 Previous tests showed the benefit, in terms of analogy criterion values, of searching for analog synoptic situations at a finer time step, but without assessing the impact on the prediction skills \citep{Finet2008}.
 
-The MTW is explained in Sect.
-\ref{sec:mtw}.
-As this method requires sub-daily time series, the available archive length is reduced compared to more common daily measurements, which has some consequences on the performance score (Sect.
-\ref{sec:archive_reduction}).
+The time step at which the MTW is applied depends on the time step of the predictor variables.
+In the present study, a 6-hourly reanalysis dataset is used, which is a standard temporal resolution.
+Thus, additionally to eventually finding better analogs, the MTW also increases the archive length.
+However, despite having four times more candidate situations, the quantity of new information is not expected to be as important, due to significant autocorrelation between successive situations at a 6-hourly time step.
+The quality of the analogy depends on the archive length to a certain extent \cite{Ruosteenoja1988, Vandendool1994}.
+Thus, the reduction of the archive length necessary to the MTW, due to the reduced availability of sub-daily precipitation time series, is expected to decrease the AM performance, whereas the archive inflation brought by the MTW is expected to contribute to an increase in performance.
+
+Section \ref{sec:data_methods} presents the context of the present study as well as data and methods, including the proposed MTW technique.
+The impact of the reduction of the archive and the improvements brought by the MTW are assessed in Sect.
+\ref{sec:results}.
 The benefit of introducing a MTW was assessed first in regards to the analogy criterion improvement (Sect.
@@
 
-%TODO: complete !!
-
 \section{Data and methods}
+\label{sec:data_methods}
 
@@
 \section{Results}
+\label{sec:results}
 

### 2016-11-24 Moving temporal window - HESS/template.tex
New version of the introduction.

@@
 
-\title{The Analog Method for Precipitation Downscaling: Finding Better Analog Situations at a Sub-Daily Time Step}
+\title{The Analog Method for Precipitation Prediction: Finding Better Analog Situations at a Sub-Daily Time Step}
 
@@
 The improvement was found to grow with the analog ranks due to an accumulation of more similar situations in the selection.
-Moreover, the improvement is even more important for days with heavy precipitation events, which are generally related to more dynamic atmospheric situations, where timing is more specific.
+Moreover, the improvement is even more important for days with heavy precipitation events, which are generally related to more dynamic atmospheric situations, where timing is more specific, and which are less present in the archive.
 
@@
 
-However, attempts to reconstruct longer precipitation series of running 24~h-totals by means of simple methods failed.
-It emphasized the need to use time series with an appropriate chronology.
+However, the MTW requires sub-daily precipitation time series, which are generally available on a shorter period than daily precipitation archives.
+Thus, two simple temporal disaggregation methods were assessed in order to make longer archives usable with the MTW.
+The assessed approaches were not successful, which emphasized the need to use time series with an appropriate chronology.
 These should be available in a near future, either by means of growing observed archives, or by the establishment of precipitation reanalyses through regional modeling.
-Then, the use of a MTW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.
+Then, the use of a MTW in the AM should be considered for any application, and in any context, let it be operational forecasting or climate-related studies
 
@@
 They consist in finding past situations that are similar, in terms of the atmospheric circulation or other synoptic predictors, to the target day of interest.
-Then, the local weather variables of interest (predictand) that were observed at the analog dates are used to construct a probabilistic prediction for the target day \citep{Duband1970, Bontron2005}.
+Then, the local weather variables of interest (predictand) that were observed at the analog dates are used to construct a probabilistic prediction for the target day \citep{Duband1970, Zorita1999}.
 Multiple variations of the methods exist \citep[a non exhaustive listing can be found in][]{BenDaoud2016}.
-AMs are used for operational precipitation forecasting \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Hamill2015, BenDaoud2016}, as well as precipitation downscaling in a climate perspective \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015}.
+AMs are used for operational precipitation forecasting, either in the context of flood forecasting or hydropower production \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as precipitation downscaling in a climate perspective \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015}.
 Other applications focus on temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectories of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
 
-AMs are usually implemented with a daily time step (see references above), due to the availability of long precipitation archives that have no equivalent at a finer resolution.
-Therefore, the analog situations are assessed on the basis of a daily time step, by comparing predictors at fixed hours of the day.
+The spatial transferability of the method was recently analyzed in depth \citep{Chardon2014}.
+A great advantage of AMs is that they create realistic events, because they were observed, with consistent spatial distribution, as long as the analog dates chosen for a region are the same.
+The temporal transferability has also been the topic of recent studies, may it be for past or future climates \citep{Dayon2015, Caillouet2016}.
+
+\citet{Ruosteenoja1988} and \citet{Vandendool1994} have put a major effort into analyzing the influence of the archive length on the quality of the analogy.
+They have highlighted a three-way relationship between the quality of the analogy, the archive length and the size of the spatial domain (of degrees of freedom): errors increase with a bigger domain, but decrease with a longer archive.
+They demonstrated that it is not possible to find good analogues on the whole northern hemisphere with a 100 years archive (and even for much higher orders of magnitude).
+For that reason, smaller spatial windows are always considered to look for analogues, and the archive length is maximized.
+
+Thus, due to the availability of long precipitation archives at a daily time step that have no equivalent at a finer resolution, AMs are usually implemented on a daily basis (see references above).
+Therefore, the analog situations are assessed by comparing predictors at fixed hours of the day.
 However, it can be expected that the analogy of the synoptic situations does not occur systematically at the same time of the day, and that better candidates can be found by shifting to a different hour.
@@
 
-The time step at which the MTW is applied depends on the time step of the predictor variables.
-In the present study, a 6-hourly reanalysis dataset is used, which is a standard temporal resolution.
-Thus, additionally to eventually finding better analogs, the MTW also increases the archive length.
-However, despite having four times more candidate situations, the quantity of new information is not expected to be as important, due to significant autocorrelation between successive situations at a 6-hourly time step.
-The quality of the analogy depends on the archive length to a certain extent \cite{Ruosteenoja1988, Vandendool1994}.
+The MTW allows finding analog situations at different hours of the day, which can also be seen as an inflation of the archive length.
+However, despite having $x$ time more candidate situations, the quantity of new information is not expected to be as important as a $x$ time longer archive, due to significant autocorrelation between successive situations.
+Nevertheless, if the MTW can improve the prediction skill of the AM, it means that it does bring some new information from the archive.
 Thus, the reduction of the archive length necessary to the MTW, due to the reduced availability of sub-daily precipitation time series, is expected to decrease the AM performance, whereas the archive inflation brought by the MTW is expected to contribute to an increase in performance.
+
+Other possibilities exist in order to increase the prediction skill of AMs.
+A classical approach is to add new predictors or new successive levels of analogy \citep[see e.g.][]{Horton2012a, BenDaoud2016, Caillouet2016}.
+AMs can also be combined with other methods \citep[see e.g.][]{Chardon2014}.
+Another possibility is to a global optimization technique, such as genetic algorithms, in order to better optimize the method and to add new options \citep{Horton2016}.
+However, the MTW technique is not in competition with other approaches, but can be combined with these.
+Indeed, as most of them rely on the atmospheric circulation in the first level of analogy, the application of a MTW should lead to similar conclusions.
 
@@
 
+More complex AMs exist, with additional predictors \citep[see e.g.][]{Horton2012a, BenDaoud2016, Caillouet2016}.
+The MTW can also be applied on these, as they generally rely on a similarity of the atmospheric circulation in the first level of analogy, but it is easier to interpret the impact of the MTW on more basic methods.
+
 \subsection{Performance score}
@@
 However, such data are not available on long periods.
-As the AM benefits from long archives, it would be profitable to be able to apply the MTW to a longer archive.
+As the AM benefits from long archives, it would be profitable to be able to apply the MTW to a longer archive (here, 1961 to 2008).
 Thus, in order to reconstruct a longer archive of moving 24~h-totals, two simple disaggregation approaches of the daily time series were assessed.
@@
 \ref{sec:data}) was used in this perspective, despite their rough resolution.
+Then, once the best proxy has been selected, its temporal profile is used in order to disaggregate the precipitation time series on the long archive period.
 
@@
 With the introduction of the MTW, the performance loss related to the reduction of the archive length is compensated.
+It is here of the same order of magnitude as if the length of the archive doubled.
+Note that despite the number of candidate situations are four times higher, the gains seem to be lower than for a quadrupled archive length.
+The likely reason is that an actual longer archive contains more atmospheric situations that might have been less observed on a shorter period.
+Moreover, high correlations between sub-daily circulation patterns are expected.
+The MTW thus does not create four times more independent data, but the increase in information is nevertheless substantial.
+In this regards, a reanalysis dataset with a higher temporal resolution might not improve the performance significantly than a 6-hourly.
+On the other hand, reducing the MTW to a 12-hourly time step might reduce redundancy in the archive, but might also reduce the chance of finding better analog situations, as circulation patterns can evolve substantially in 12~hours.
+
+Moreover, in a transient climate, an eventual non-stationarity of the link between predictors and precipitation might discard the relevance of analogs from far in the past, and thus increase the relevance of using a more recent and shorter archive rather than a long one.
+In such case, the archive inflation brought by the MTW is also relevant.
 
@@
 On the opposite, days with a low dynamics of the atmospheric circulation, such as anticyclonic situations, will not be radically improved by the introduction of the MTW.
+
+We just mentioned that the MTW improves the prediction of heavier precipitation events.
+However, it will have no effect on the prediction of extreme events that were not yet observed, and therefore are not present in the archive.
+Extremes in AMs can be modeled e.g.
+by extrapolation of a truncated exponential or gamma distribution fitted on the analog values \citep{Obled2002}.
+Another possible approach is by combining AMs with other methods \citep[e.g.][]{Chardon2014}.
+However, this goes beyond the scope of the present study, as prediction of unobserved extremes are not modified by the MTW.
 
@@
 7 of \citealt{Hamill2006a}).
-The observed increases in the number of analog situations with the MTW result in better performance skills, as it can be seen as an inflation of the archive.
-The MTW enriches the pool of available situations, even though they are not fully independent.
+The observed increases in the number of analog situations with the MTW result in better performance skills for a given method, as it can be seen as an inflation of the archive.
+However, if new relevant predictors were added to the method, the number of analogs would then decrease.
 
@@
 A comparative analysis of several reanalysis dataset within the AM is under work and will be the topic of a dedicated paper.
+
+%TODO: : it was shown by some studies that the resolution of the reanalysis dataset does not improve significantly the performance of the analogy of the atmospheric circulation.
+However, a full analysis of this aspect is out of the scope of this publication, and is a topic we are working on right now.
+Nevertheless, we can make the assumption that it does not alter the fact that we can find better analog situations at different hours of the day.
 
@@
 Even though outputs from these models might be biased or not accurate enough, information on the timing of the precipitation events could be useful in order to disaggregate stations time series.
-When precipitation data with accurate time distribution will be available, the use of a MTW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.
+When precipitation data with accurate time distribution will be available, the use of a MTW in the AM should be considered for any application, and in any context, let it be operational forecasting or climate-related studies.
 
@@
 NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/. Precipitation time series provided by MeteoSwiss.
+
+The authors would also like to acknowledge the work anonymous reviewers, which contributed to improving this paper. 
 \end{acknowledgements}

### 2016-11-24 Moving temporal window - HESS/template.tex
Correction of tenses.

@@
 The improvement was found to grow with the analog ranks due to an accumulation of more similar situations in the selection.
-Moreover, the improvement is even more important for days with heavy precipitation events, which are generally related to more dynamic atmospheric situations, where timing is more specific, and which are less present in the archive.
+Moreover, the improvement was even more important for days with heavy precipitation events, which are generally related to more dynamic atmospheric situations, where timing is more specific, and which are less present in the archive.
 
@@
 These should be available in a near future, either by means of growing observed archives, or by the establishment of precipitation reanalyses through regional modeling.
-Then, the use of a MTW in the AM should be considered for any application, and in any context, let it be operational forecasting or climate-related studies
+Then, the use of a MTW in the AM can be considered for any application, and in any context, let it be operational forecasting or climate-related studies
 
@@
 Analog methods (AMs) are based on the hypothesis that two relatively similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}.
-They are part of the statistical downscaling methods \cite{Maraun2010}.
+They are part of statistical downscaling methods \cite{Maraun2010}.
 They consist in finding past situations that are similar, in terms of the atmospheric circulation or other synoptic predictors, to the target day of interest.
@@
 
-The spatial transferability of the method was recently analyzed in depth \citep{Chardon2014}.
-A great advantage of AMs is that they create realistic events, because they were observed, with consistent spatial distribution, as long as the analog dates chosen for a region are the same.
+The spatial transferability of the method is analyzed in \citet{Chardon2014}.
+A great advantage of AMs is that they create realistic events, as they are based on observed situations, with consistent spatial distribution, as long as the analog dates chosen for a region are the same.
 The temporal transferability has also been the topic of recent studies, may it be for past or future climates \citep{Dayon2015, Caillouet2016}.
 
-\citet{Ruosteenoja1988} and \citet{Vandendool1994} have put a major effort into analyzing the influence of the archive length on the quality of the analogy.
-They have highlighted a three-way relationship between the quality of the analogy, the archive length and the size of the spatial domain (of degrees of freedom): errors increase with a bigger domain, but decrease with a longer archive.
-They demonstrated that it is not possible to find good analogues on the whole northern hemisphere with a 100 years archive (and even for much higher orders of magnitude).
-For that reason, smaller spatial windows are always considered to look for analogues, and the archive length is maximized.
+\citet{Ruosteenoja1988} and \citet{Vandendool1994} analyze the influence of the archive length on the quality of the analogy.
+They highlight a three-way relationship between the quality of the analogy, the archive length and the size of the spatial domain (of degrees of freedom): errors increase with a bigger domain, but decrease with a longer archive.
+They demonstrate that it is not possible to find good analogues on the whole northern hemisphere with a 100 years archive (and even for much higher orders of magnitude).
+For that reason, smaller spatial windows are always considered to search for analogues, and the archive length is maximized.
 
@@
 The MTW allows finding analog situations at different hours of the day, which can also be seen as an inflation of the archive length.
-However, despite having $x$ time more candidate situations, the quantity of new information is not expected to be as important as a $x$ time longer archive, due to significant autocorrelation between successive situations.
+However, despite having $x$ time more candidate situations, the quantity of new information is not expected to be as important as a $x$ time longer archive, due to significant correlation between successive situations.
 Nevertheless, if the MTW can improve the prediction skill of the AM, it means that it does bring some new information from the archive.
-Thus, the reduction of the archive length necessary to the MTW, due to the reduced availability of sub-daily precipitation time series, is expected to decrease the AM performance, whereas the archive inflation brought by the MTW is expected to contribute to an increase in performance.
+Thus, if the reduction of the archive length necessary to the MTW, due to the reduced availability of sub-daily precipitation time series, is expected to decrease the AM performance, the archive inflation brought by the MTW is expected to contribute to an increase in performance.
 
@@
 AMs can also be combined with other methods \citep[see e.g.][]{Chardon2014}.
-Another possibility is to a global optimization technique, such as genetic algorithms, in order to better optimize the method and to add new options \citep{Horton2016}.
+Another possibility is to use a global optimization technique, such as genetic algorithms, in order to better optimize the method and to add new options \citep{Horton2016}.
 However, the MTW technique is not in competition with other approaches, but can be combined with these.
@@
 
-Section \ref{sec:data_methods} presents the context of the present study as well as data and methods, including the proposed MTW technique.
+Section \ref{sec:data_methods} presents the context of the study as well as data and methods, including the proposed MTW technique.
 The impact of the reduction of the archive and the improvements brought by the MTW are assessed in Sect.
@@
 \ref{fig:map}), which are subject to various meteorological influences \citep{Horton2012}.
-The data are available at an hourly time step on 25~years (1982 to 2007), and were also obtained at a daily time step on 47~years (1961 to 2008).
+The data were available at an hourly time step on 25~years (1982 to 2007), and were also obtained at a daily time step on 47~years (1961 to 2008).
 Due to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed.
-The results will thereafter be presented arbitrarily for the Ulrichen station, but are equivalent for all stations.
+The results will thereafter be presented arbitrarily for the Ulrichen station, but were equivalent for all stations.
 
-Synoptic-scale variables, used as predictors, are extracted from the NCEP/NCAR reanalysis I \citep{Kalnay1996} dataset with a 6-hourly temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree.
+Synoptic-scale variables, used as predictors, were extracted from the NCEP/NCAR reanalysis I \citep{Kalnay1996} dataset with a 6-hourly temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree.
 This dataset is now relatively old, but still often used (see discussion in Sect.
@@
 Based on \citet{Bontron2005}, geopotential heights are thus compared at 1000~hPa (Z1000) at 12~h~UTC and 500~hPa (Z500) at 24~h~UTC.
-The time of the day at which the predictors are selected was found by \citet{Bontron2004} to have a significant influence.
+The time of the day at which the predictors are selected is found by \citet{Bontron2004} to have a significant influence.
 
@@
 
-Applying the MTW technique involve the need of sub-daily precipitation timeseries.
-However, such data are not available on long periods.
-As the AM benefits from long archives, it would be profitable to be able to apply the MTW to a longer archive (here, 1961 to 2008).
-Thus, in order to reconstruct a longer archive of moving 24~h-totals, two simple disaggregation approaches of the daily time series were assessed.
+It would be profitable to be able to apply the MTW to a longer archive (here, 1961 to 2008), rather than being limited to the reduced period corresponding to the sub-daily precipitation data.
+Thus, in order to reconstruct a longer archive of moving 24~h-totals, two simple disaggregation approaches of the daily precipitation time series were assessed.
 
-The first technique is a proportional distribution, where the observed daily precipitation is considered constant during the measuring period (6~h~UTC to 6~h~UTC the next day).
-It then consists in allocating proportional parts of the original daily time series into a new moving average of 24~h-totals (Fig.
+The first technique was a proportional distribution, where the observed daily precipitations were considered constant during the measuring period (6~h~UTC to 6~h~UTC the next day).
+It then consisted in allocating proportional parts of the original daily time series into a new moving average of 24~h-totals (Fig.
 \ref{fig:illustration_disaggregation}).
 
-The second approach aims at getting closer to the chronology of the actual precipitation by relying on some informative variable during the reconstruction procedure.
-The best proxy variable is identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series on the period 1982-2007.
+The second approach aimed at getting closer to the chronology of the actual precipitation by relying on some informative variable during the reconstruction procedure.
+The best proxy variable was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series on the period 1982-2007.
 Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and by allowing a time lapse between both series in order to take into account the significant distance separating the weather stations and the reanalysis grid point.
@@
 \ref{sec:data}) was used in this perspective, despite their rough resolution.
-Then, once the best proxy has been selected, its temporal profile is used in order to disaggregate the precipitation time series on the long archive period.
+Then, once the best proxy has been selected, its temporal profile was used in order to disaggregate the precipitation time series on the long archive period.
 
@@
 Previously calibrated parameters are generally not reassessed (except for the number of analogs).
-More advanced techniques, such as using Genetic Algorithms \citep{Horton2016}, exist, but are out of the scope of the present study.
+More advanced techniques, such as using genetic algorithms \citep{Horton2016}, exist, but are out of the scope of the present study.
 
@@
 Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
-The AM parameters were calibrated on the original archive (see resulting analog numbers in Tables \ref{table:analog_nb}) and will be used thereafter.
+The AM parameters were calibrated on the original archive (see resulting analog numbers in Tables \ref{table:analog_nb}) and were be used thereafter.
 
@@
 \ref{fig:plots_CRPSS_2Z-2MI} for the 2Z-2MI method.
-As expected, a loss of performance can be observed for each station, except for that of Aigle, which seems relatively indifferent to this change.
-This loss is globally significant, with up to -1.89 points for Visp and the 2Z method.
+As expected, a loss of performance could be observed for each station, except for that of Aigle, which seemed relatively indifferent to this change.
+This loss was globally significant, with up to -1.89 points for Visp and the 2Z method.
 
@@
 \ref{sec:mtw}).
-Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions of the analogy criterion (S1) for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analog rank at the Ulrichen station on the whole calibration period (1961-2008 -- we can use the full period here, as we do not consider precipitation at this stage), due to introduction of the MTW.
-The shape of the distributions of the conventional approach and the MTW are similar, but the values of the analogy criterion are now reduced (shifted to the left), and therefore better.
+Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions of the analogy criterion (S1) for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analog rank at the Ulrichen station on the whole calibration period (1961-2008 -- the full period could be used here, as precipitation were not considered at this stage), due to introduction of the MTW.
+The shape of the distributions of the conventional approach and the MTW were found to be similar, but the values of the analogy criterion were reduced (shifted to the left), and therefore better.
 For analogs with higher ranks (e.g.
-$20^{th}$ or $40^{th}$), the difference between the two distributions is larger than for the first ranks, which means that the improvement increases with the rank of the analogs.
+$20^{th}$ or $40^{th}$), the difference between the two distributions was larger than for the first ranks, which means that the improvement increased with the rank of the analogs.
 
@@
 \ref{fig:changes_S1}, which shows (top) quantiles of the S1 criterion for the conventional method and the MTW, and (bottom) quantiles of the relative reduction (meaning improvement) due to the MTW.
-This confirms that all quantiles are similarly reduced (S1 distributions keep their shape), and that this improvement is constantly increasing from the first to the last analog (Fig.
+This confirms that all quantiles were similarly reduced (S1 distributions keep their shape), and that this improvement was constantly increasing from the first to the last analog (Fig.
 \ref{fig:changes_S1} bottom).
@@
 The number of cases per class being reduced, the curves are not as smooth as in previous analyzes.
-It is nevertheless clear that the improvement tends to increase on days with higher precipitation.
-This is true for all our stations.
+It is nevertheless clear that the improvement were more important on days with higher precipitation.
+It was the same for all other stations.
 
@@
 \ref{fig:changes_S1_seasons}.
-Differences between the seasons are substantial.
-The improvements are greater for winter than summer.
+Differences between the seasons were substantial.
+The improvements were greater for winter than summer.
 
@@
 
-When adding the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogs, but their dates have changed.
-In contrast to the AM on the atmospheric circulation only, both a reduction or an increase of the RMSE analogy criterion values are possible here with the MTW compared to the static approach.
+When adding the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations did not increase, as they were subsampled in the previously $N_{1}$ selected analogs, but their dates have changed.
+In contrast to the AM on the atmospheric circulation only, both a reduction or an increase of the RMSE analogy criterion values were possible here with the MTW compared to the static approach.
 Indeed, Fig.
 \ref{fig:changes_RMSE} shows an almost insignificant improvement of the RMSE values.
-Unlike for the first level of analogy, the relative improvement of the RMSE values are distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
-Once again, the results for the other stations are similar.
+Unlike for the first level of analogy, the relative improvement of the RMSE values were distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
+Once again, the results for the other stations were similar.
 
@@
 \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI} for the 2Z and 2Z-2MI methods respectively, on the reduced archive (1982--2007).
-The gains, relatively to the static approach on the same archive, range from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.
+The gains, relatively to the static approach on the same archive, ranged from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.
 
@@
 \ref{sec:influence_precip}).
-The changes in terms of performance scores are now also assessed per precipitation classes.
+The changes in terms of performance scores were then also assessed per precipitation classes.
 Fig.
 \ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, other stations having the same behavior.
-The performance score is improved for days with higher precipitation after the introduction of the MTW.
-On the contrary, non-rainy days and small precipitation values are not improved.
+The performance score was improved for days with higher precipitation after the introduction of the MTW.
+On the contrary, non-rainy days and small precipitation values were not improved.
 
@@
 
-After recalibrating, changes in the AM parameters can be observed for both 2Z and 2Z-2MI methods.
-Among these, the zonal extent of the spatial windows of the circulation analogy tends to decrease (not shown).
-More significantly, the optimal number of analogs increases after introducing the MTW, of a considerable order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method (Table \ref{table:analog_nb}).
+After recalibrating, changes in the AM parameters could be observed for both 2Z and 2Z-2MI methods.
+Among these, the zonal extent of the spatial windows of the circulation analogy decrease a bit (not shown).
+More significantly, the optimal number of analogs increased after introducing the MTW, of a considerable order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method (Table \ref{table:analog_nb}).
 The number of analogs of the first analogy level of the 2Z-2MI method even reached three times its previous value for the Visp station.
@@
 \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}) have significantly increased after recalibration.
-When analyzing the change in performance per precipitation classes, the results (not shown) are very similar to what was observed in Sect.
+When analyzing the change in performance per precipitation classes, the results (not shown) were very similar to what was observed in Sect.
 \ref{sec:improvement_CRPSS_precip_threshold}, with a slight performance increase of small precipitation values that can be observed at the expense of higher amounts.
@@
 On the first level of analogy, the median of the S1 values reduction (Fig.
-\ref{fig:changes_S1} bottom) starts approximately at 5~\% for the first analog and reaches more than 10~\% for the last one.
+\ref{fig:changes_S1} bottom) started approximately at 5~\% for the first analog and reached more than 10~\% for the last one.
 This increase of improvements with the analog rank can be explained by the accumulation of better analogs in the distribution.
 The curve representing the minimum improvement is quickly slightly superior to zero, meaning that the criteria have been improved on most analogs for every day of the calibration period.
-All other stations have a similar improvement of the S1 criterion, both in terms of distribution shape and amplitude.
-The introduction of the MTW allows finding better analog situations in the first level of analogy, resulting in a selection of days with more similar atmospheric circulation.
+All other stations had a similar improvement of the S1 criterion, both in terms of distribution shape and amplitude.
+The introduction of the MTW allowed finding better analog situations in the first level of analogy, resulting in a selection of days with more similar atmospheric circulation.
 
-When adding a second level of analogy on moisture variables, the criteria values (RMSE) are not improved by the MTW as the number of candidates is not higher (still the $N_{1}$ days selected in the first level of analogy).
+When adding a second level of analogy on moisture variables, the criteria values (RMSE) were not improved by the MTW as the number of candidates was not higher (still the $N_{1}$ days selected in the first level of analogy).
 However, this result of a globally null improvement of the RMSE values does not mean that the 2Z-2MI method cannot be improved by the MTW.
-It means that after the selection of the analog situations in terms of the synoptic circulation, the new candidate dates do not allow to find better analogs in terms of moisture.
+It means that after the selection of the analog situations in terms of the synoptic circulation, the new candidate dates did not allow to find better analogs in terms of moisture.
 However, the selected dates have changed in the first level of analogy, and thus also in the final selection, which can potentially improve the prediction skill.
@@
 \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}).
-The improvement of the performance is not very large, but is nevertheless substantial.
-Moreover, it requires no additional predictor.
-With the introduction of the MTW, the performance loss related to the reduction of the archive length is compensated.
-It is here of the same order of magnitude as if the length of the archive doubled.
-Note that despite the number of candidate situations are four times higher, the gains seem to be lower than for a quadrupled archive length.
-The likely reason is that an actual longer archive contains more atmospheric situations that might have been less observed on a shorter period.
+Moreover, it required no additional predictor.
+With the introduction of the MTW, the performance loss related to the reduction of the archive length was compensated.
+It was here of the same order of magnitude as if the length of the archive doubled.
+Note that despite the number of candidate situations were four times higher, the gains seem to be lower than for a quadrupled archive length.
+The likely reason is that an actual longer archive would contain more atmospheric situations that might have been less observed on a shorter period.
 Moreover, high correlations between sub-daily circulation patterns are expected.
-The MTW thus does not create four times more independent data, but the increase in information is nevertheless substantial.
-In this regards, a reanalysis dataset with a higher temporal resolution might not improve the performance significantly than a 6-hourly.
+The MTW thus did not create four times more independent data, but the increase in information was nevertheless substantial.
+In this regards, a reanalysis dataset with a higher temporal resolution might not improve the performance significantly more than a 6-hourly dataset.
 On the other hand, reducing the MTW to a 12-hourly time step might reduce redundancy in the archive, but might also reduce the chance of finding better analog situations, as circulation patterns can evolve substantially in 12~hours.
@@
 \ref{sec:influence_precip}) and the performance scores (Sect.
-\ref{sec:improvement_CRPSS_precip_threshold}) are improved to a greater extent for heavier precipitation events.
+\ref{sec:improvement_CRPSS_precip_threshold}) were improved to a greater extent for heavier precipitation events.
 This is likely due to the fact that higher precipitation events are a consequence of atmospheric conditions with a greater dynamics, such as weather disturbances, which have a well marked temporal evolution.
@@
 It was found that the new choice of the temporal window in winter, when using the MTW approach, is well balanced between the 4 options.
-This means a change of 75\% of the analogs selection compared to the conventional approach, which improves the circulation analogy.
-On the contrary, the summer months have a preference for the initial temporal window (Z500 24~h \& Z1000 12~h), likely due to more pronounced diurnal effects which reduces the potential for improvement of the criteria.
-Other seasons are between these two extremes, which is consistent with their respective improvements.
+This means a change of 75\% of the analogs selection compared to the conventional approach, which improved the circulation analogy.
+On the contrary, days in summer months had a preference for the initial temporal window (Z500 24~h \& Z1000 12~h), likely due to more pronounced diurnal effects which reduces the potential for improvement of the criteria.
+Other seasons were between these two extremes, which is consistent with their respective improvements.
 This seasonal effect was observed for each station in a very similar way, and generally even with a slightly larger amplitude than for Ulrichen.
@@
 As we saw in Fig.
-\ref{fig:changes_S1}, the improvement of the S1 criterion grows along with the rank of the analog, which shows an accumulation of better analog situations in the distributions.
+\ref{fig:changes_S1}, the improvement of the S1 criterion grew along with the rank of the analog, which shows an accumulation of better analog situations in the distributions.
 It seems thus profitable to widen the selection of analogs in order to keep also some whose rank has increased, as they appear to be also relevant to predict precipitation values.
-The number of good analogs is thus globally increased.
+The number of good analogs was thus globally increased.
 
@@
 7 of \citealt{Hamill2006a}).
-The observed increases in the number of analog situations with the MTW result in better performance skills for a given method, as it can be seen as an inflation of the archive.
+The observed increases in the number of analog situations with the MTW resulted in better performance skills for a given method, as it can be seen as an inflation of the archive.
 However, if new relevant predictors were added to the method, the number of analogs would then decrease.
@@
 \ref{sec:reconstruction_results}).
-Indeed, the performance improvement brought by the MTW is lost due to a precipitation archive of poor quality.
-A slight improvement can be obtained for the second method relying on a proxy variable compared to the proportional distribution method, but it is still relatively small, and most of the benefit of the MTW is lost.
+Indeed, the performance improvement brought by the MTW was lost due to a precipitation archive of poor quality.
+A slight improvement could be obtained for the second method relying on a proxy variable compared to the proportional distribution method, but it was still relatively small, and most of the benefit of the MTW was lost.
 A more recent reanalysis archive with more accurate moisture variables might produce better proxies.
 
-These attempts to transpose the MTW on the total archive highlight the importance of the actual rainfall chronology.
+These attempts to transpose the MTW on the total archive highlighted the importance of the actual rainfall chronology.
 The MTW is profitable, provided that the precipitation series are close to the observed one.
@@
 As \citet{Finet2008} had previously shown, the introduction of a MTW allows finding better analog situations in terms of the atmospheric circulation.
-It has been here demonstrated that the improvement of the S1 criterion values is growing with the rank of the analog.
-This is due to the accumulation of better analogs within the predicted distributions.
+It has been here demonstrated that the improvement of the S1 criterion values was growing with the rank of the analog.
+This was due to the accumulation of better analogs within the predicted distributions.
 
@@
 This dynamism implies more specific circulation patterns that are evolving more rapidly.
-Thus, a MTW is found to be of particular interest in this kind of situation, and benefits the prediction of heavier precipitation events.
+Thus, a MTW was found to be of particular interest in this kind of situation, and benefits the prediction of heavier precipitation events.
 
-A seasonal effect has been highlighted, as the MTW is more profitable for winter months than summer.
+A seasonal effect has been highlighted, as the MTW was more profitable for winter months than summer.
 The reason is likely that the diurnal cycle has a bigger effect in summer than in winter, which results in better analogs at the same time of the day.
-The preference for the same hours in summer has been demonstrated, whereas 75\% of the analog situations are selected at a different time in winter.
+The preference for the same hours in summer has been demonstrated, whereas 75\% of the analog situations were selected at a different time in winter.
 
@@
 A wider selection of analog situations, containing those whose rank decreased, seemed profitable for the prediction performance.
-The number of good analogs is thus globally increased, in the same way as if the archive length increased.
+The number of good analogs was thus globally increased, in the same way as if the archive length increased.
 This change seems to benefit mainly the prediction of days with small precipitation totals.
@@
 Attempts to reconstruct longer time series based on a simplistic proportional distribution or using meteorological variables from the NCEP reanalysis 1 dataset as proxy did not succeed.
-Other reanalysis datasets could eventually perform better.
+Other reanalysis datasets with more accurate moisture variables could eventually perform better.
 
@@
 Even though outputs from these models might be biased or not accurate enough, information on the timing of the precipitation events could be useful in order to disaggregate stations time series.
-When precipitation data with accurate time distribution will be available, the use of a MTW in the AM should be considered for any application, and in any context, let it be operational forecasting or climate-related studies.
+When precipitation data with accurate time distribution will be available, the use of a MTW in the AM can be considered for any application, and in any context, let it be operational forecasting or climate-related studies.
 

### 2016-11-24 Moving temporal window - HESS/template.tex
Updating the discussion on the use of an old reanalysis dataset.

@@
 Newer reanalysis dataset could have been used to achieve this study, and might have resulted in higher performance scores.
-However, one can assume that the gain observed here by introducing a MTW should also be found for a better reanalysis dataset, especially if the information of the atmospheric circulation is more accurate.
-Indeed, a better dataset does not negatively influence the fact that one can find better analog situations at other hours of the day rather than at fixed hours.
+However, \cite{BenDaoud2009} showed that the sensitivity of the method to the reanalysis dataset is rather small.
+This is particularly true for simple AMs that mainly rely on the atmospheric circulation, which is already well defined at a coarser resolution.
+That might not be the case of more elaborated methods relying on thermodynamic data.
 A comparative analysis of several reanalysis dataset within the AM is under work and will be the topic of a dedicated paper.
 
-%TODO: : it was shown by some studies that the resolution of the reanalysis dataset does not improve significantly the performance of the analogy of the atmospheric circulation.
-However, a full analysis of this aspect is out of the scope of this publication, and is a topic we are working on right now.
-Nevertheless, we can make the assumption that it does not alter the fact that we can find better analog situations at different hours of the day.
+Moreover, one can assume that the gain observed here by introducing a MTW should also be found for a better reanalysis dataset.
+Indeed, a better dataset does not negatively influence the fact that one can find better analog situations at other hours of the day rather than at fixed hours.
 

### 2016-11-24 Moving temporal window - HESS/template.tex
Corrections of the HESS paper.

@@
 \usepackage[utf8]{inputenc}
+
+%TODO: check figs and table captions
+%TODO: order figs
+%TODO: english editing
+%TODO: analogs
+%TODO: perspective Obled: MTW without precip -> indicator
 
@@
 The Analog Method (AM) aims at predicting local weather variables (predictands), such as precipitation, by means of a statistical relationship with predictors at a synoptic scale.
-The analogy is generally first assessed on the geopotential field gradients, in order to sample days with a similar atmospheric circulation.
+The analogy is generally first assessed on gradients of geopotential fields, in order to sample days with a similar atmospheric circulation.
 Other predictors, such as moisture variables, can also be added in a successive level of analogy.
@@
 The search for candidate situations, for a given target day, is usually undertaken by comparing the state of the atmosphere at fixed hours of the day, for both the target day and the candidate analogs.
-The constraint is the use of daily time series, due to the length of available archives they provide, and the unavailability of equivalent archives at a finer time step.
-However, it is unlikely that the best analogy happens at the very same hour, but it may occur at a different time of the day.
+The main reason is the use of daily precipitation time series, due to the length of their available archives, and the unavailability of equivalent archives at a finer time step.
+However, it is unlikely for the best analogy to happen at the very same hour, as it may occur at a different time of the day.
 In order to assess the potential of finding better analogs at a different hour, a moving time window (MTW) has been introduced on a reduced archive of hourly precipitation totals.
@@
 The MTW resulted in a better analogy in terms of the atmospheric circulation, with improved values of the analogy criterion on the whole distribution of analog dates.
-The improvement was found to grow with the analog ranks due to an accumulation of more similar situations in the selection.
-Moreover, the improvement was even more important for days with heavy precipitation events, which are generally related to more dynamic atmospheric situations, where timing is more specific, and which are less present in the archive.
+The improvement was found to grow with the analog rank due to an accumulation of more similar situations in the selection.
+A seasonal effect has also been identified, with larger improvements in winter than in summer, supposedly due to stronger diurnal cycles in summer, which favor predictors at the same hour for the target and analog days.
 
-A seasonal effect has also been identified, with larger improvements in winter than in summer, supposedly due to the stronger effect of the diurnal cycle in summer, which favors predictors at the same hour for target and analogs.
-
-The impact of the MTW on the prediction performance has been assessed by means of a sub-daily precipitation series transformed into moving 24~h-totals at a 6-hourly time step.
-This resulted in an improvement of the prediction skills, which were even larger after recalibrating the AM parameters.
+The impact of the MTW on the prediction skill has been assessed by means of a sub-daily precipitation series transformed into moving 24~h-totals at a 6-hourly time step.
+The prediction skill was found to be improved by the MTW, and even more after recalibrating the AM parameters.
+Moreover, the improvement was greater for days with heavy precipitation, which are generally related to more dynamic atmospheric situations, where timing is more specific, and which are less present in the archive.
 
@@
 The assessed approaches were not successful, which emphasized the need to use time series with an appropriate chronology.
-These should be available in a near future, either by means of growing observed archives, or by the establishment of precipitation reanalyses through regional modeling.
-Then, the use of a MTW in the AM can be considered for any application, and in any context, let it be operational forecasting or climate-related studies
+These should be available in a near future, either by means of growing archives of measurements, or by the establishment of regional precipitation reanalyzes.
+Then, the use of a MTW in AMs can be considered for any application, and in any context, let it be operational forecasting or climate-related studies.
 
@@
 Analog methods (AMs) are based on the hypothesis that two relatively similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}.
-They are part of statistical downscaling methods \cite{Maraun2010}.
-They consist in finding past situations that are similar, in terms of the atmospheric circulation or other synoptic predictors, to the target day of interest.
+They are part of statistical downscaling methods \citep{Maraun2010}, and consist in finding past situations that are similar, in terms of the atmospheric circulation or other synoptic predictors, to the target day of interest.
 Then, the local weather variables of interest (predictand) that were observed at the analog dates are used to construct a probabilistic prediction for the target day \citep{Duband1970, Zorita1999}.
-Multiple variations of the methods exist \citep[a non exhaustive listing can be found in][]{BenDaoud2016}.
+Multiple variations of the method exist \citep[a non-exhaustive listing can be found in][]{BenDaoud2016}.
 AMs are used for operational precipitation forecasting, either in the context of flood forecasting or hydropower production \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as precipitation downscaling in a climate perspective \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015}.
@@
 The spatial transferability of the method is analyzed in \citet{Chardon2014}.
-A great advantage of AMs is that they create realistic events, as they are based on observed situations, with consistent spatial distribution, as long as the analog dates chosen for a region are the same.
+A great advantage of AMs is that they create realistic precipitation patterns, as they are based on observed situations, with consistent spatial distribution, as long as the analog dates chosen for a region are the same.
 The temporal transferability has also been the topic of recent studies, may it be for past or future climates \citep{Dayon2015, Caillouet2016}.
 
-\citet{Ruosteenoja1988} and \citet{Vandendool1994} analyze the influence of the archive length on the quality of the analogy.
-They highlight a three-way relationship between the quality of the analogy, the archive length and the size of the spatial domain (of degrees of freedom): errors increase with a bigger domain, but decrease with a longer archive.
+\citet{Ruosteenoja1988} and \citet{Vandendool1994} have analyzed the influence of the archive length on the quality of the analogy.
+They highlight a three-way relationship between the quality of the analogy, the archive length and the size of the spatial domain (or degrees of freedom): errors increase with a bigger domain, but decrease with a longer archive.
 They demonstrate that it is not possible to find good analogues on the whole northern hemisphere with a 100 years archive (and even for much higher orders of magnitude).
@@
 The MTW allows finding analog situations at different hours of the day, which can also be seen as an inflation of the archive length.
-However, despite having $x$ time more candidate situations, the quantity of new information is not expected to be as important as a $x$ time longer archive, due to significant correlation between successive situations.
-Nevertheless, if the MTW can improve the prediction skill of the AM, it means that it does bring some new information from the archive.
+However, despite having $x$ time more candidate situations, the quantity of new information is not expected to be as important as a $x$ time longer archive, due to significant correlation between successive situations within the same day.
+Nevertheless, if the MTW can improve the prediction skill of the AM, it means that it does extract new information from the archive.
 Thus, if the reduction of the archive length necessary to the MTW, due to the reduced availability of sub-daily precipitation time series, is expected to decrease the AM performance, the archive inflation brought by the MTW is expected to contribute to an increase in performance.
@@
 AMs can also be combined with other methods \citep[see e.g.][]{Chardon2014}.
-Another possibility is to use a global optimization technique, such as genetic algorithms, in order to better optimize the method and to add new options \citep{Horton2016}.
+Another possibility is to use a global optimization technique, such as genetic algorithms, in order to better optimize the method and to add new parameters \citep{Horton2016}.
 However, the MTW technique is not in competition with other approaches, but can be combined with these.
@@
 Finally, the results are discussed in Sect.
-\ref{sec:discussion}.
+\ref{sec:discussion} and the conclusions are found in Sect.
+\ref{sec:conclusions}.
 
@@
 \ref{fig:map}), which are subject to various meteorological influences \citep{Horton2012}.
-The data were available at an hourly time step on 25~years (1982 to 2007), and were also obtained at a daily time step on 47~years (1961 to 2008).
+The data were available at an hourly time step on 25~years (1982 to 2007), and were also obtained at a daily time step (from 6~h~UTC to 6~h~UTC the next day) on 47~years (1961 to 2008).
 Due to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed.
@@
 
-Synoptic-scale variables, used as predictors, were extracted from the NCEP/NCAR reanalysis I \citep{Kalnay1996} dataset with a 6-hourly temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree.
-This dataset is now relatively old, but still often used (see discussion in Sect.
+Synoptic-scale variables, used as predictors, were extracted from the NCEP/NCAR reanalysis I dataset \citep{Kalnay1996} with a 6-hourly temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree.
+This dataset is now relatively old, but it is not expected to affect the conclusions of the present study (see discussion in Sect.
 \ref{sec:old_reanalysis}).
@@
 
-The predictand, here a 24~h precipitation total (classically from 6~h~UTC to 6~h~UTC the next day), results from meteorological situations that are continuous transitions between changing circulation patterns.
-Thus, the predictor data, extracted from reanalysis datasets, are considered at different hours of the day.
+The predictor variables, extracted from reanalysis datasets, are considered at different hours of the day.
 Based on \citet{Bontron2005}, geopotential heights are thus compared at 1000~hPa (Z1000) at 12~h~UTC and 500~hPa (Z500) at 24~h~UTC.
@@
 
-The target situations and their corresponding observed precipitation values do not change, because the prediction is always established for a fixed period of the target day (6~h~UTC to 6~h~UTC the next day), as before.
+The target situations and their corresponding observed precipitation values do not change, because the prediction is still established on a daily basis, for a fixed period of the target day (6~h~UTC to 6~h~UTC the next day), as before.
 The difference is that the candidates are 4~times more numerous (even though they are not fully independent).
@@
 In order to assess the benefit of searching analog situations at a sub-daily time step, an appropriate precipitation series is required.
-On the basis of high resolution time series (Sect.
+On the basis of high temporal resolution time series (Sect.
 \ref{sec:data}), 24~h-totals were processed, but at a 6-hourly time step, by means of a moving 24~h-total.
@@
 
-It would be profitable to be able to apply the MTW to a longer archive (here, 1961 to 2008), rather than being limited to the reduced period corresponding to the sub-daily precipitation data.
+It would be profitable to be able to apply the MTW to a longer archive (here, 1961 to 2008), rather than being limited to the reduced period corresponding to the sub-daily precipitation data (cf.
+previous section).
 Thus, in order to reconstruct a longer archive of moving 24~h-totals, two simple disaggregation approaches of the daily precipitation time series were assessed.
@@
 
-The second approach aimed at getting closer to the chronology of the actual precipitation by relying on some informative variable during the reconstruction procedure.
+The second approach aimed at getting closer to the chronology of the actual precipitation by relying on some informative variables during the reconstruction procedure.
+Data from the NCEP/NCAR reanalysis 1 (Sect.
+\ref{sec:data}) were used in this perspective, despite their rough resolution.
+Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and by allowing a time lapse between both series in order to take into account the significant distance separating the weather stations and the reanalysis grid point.
 The best proxy variable was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series on the period 1982-2007.
-Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and by allowing a time lapse between both series in order to take into account the significant distance separating the weather stations and the reanalysis grid point.
-Data from the NCEP/NCAR reanalysis 1 (Sect.
-\ref{sec:data}) was used in this perspective, despite their rough resolution.
-Then, once the best proxy has been selected, its temporal profile was used in order to disaggregate the precipitation time series on the long archive period.
+Then, once the best proxy has been selected, its temporal profile was used in order to disaggregate the daily precipitation time series.
 
@@
 
-To calibrate the method, the semi-automatic sequential procedure elaborated by \citet{Bontron2004} was used \cite[see also ][]{Horton2012a, Radanovics2013, BenDaoud2016}.
-The analogy levels (eg.
+The semi-automatic sequential procedure elaborated by \citet{Bontron2004} was used to calibrate the AM \cite[see also ][]{Radanovics2013, BenDaoud2016}.
+The analogy levels (e.g.
 the atmospheric circulation or moisture index) are calibrated sequentially.
@@
 		\item Identification of the most skilled unitary cell (1~point for moisture variables and 4 for the geopotential height when using the S1 criterion) over a large domain.
-Every point (or cell) of the full domain is assessed on all predictors of the level of analogy jointly (consisting generally of the same variable, but on different pressure levels and at different hours).
+Every point (or cell) of the full domain is assessed on all predictors of the level of analogy, jointly (consisting generally of the same variable, but on different pressure levels and at different hours).
 		\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain.
@@
 The parameters calibrated on the previous analog levels are fixed and do not change.
-	\item Finally, the numbers of analogs are re-assessed for the different levels of analogy. This is done iteratively by varying the number of analogs of each level in a systematic way.
+	\item Finally, the numbers of analogs for the different levels of analogy are re-assessed. This is done iteratively by varying the number of analogs of each level in a systematic way.
 \end{enumerate}
@@
 
-The performance loss resulting from a reduction of a 47~years archive (1961 to 2008, corresponding to the daily time series) to 25~years (1982 to 2007, corresponding to the hourly time series, see Sect.
+The performance loss resulting from the reduction of a 47~years archive (1961 to 2008, corresponding to the daily time series) to 25~years (1982 to 2007, corresponding to the hourly time series, see Sect.
 \ref{sec:mtw}) was assessed with the original method, without MTW.
 Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
-The AM parameters were calibrated on the original archive (see resulting analog numbers in Tables \ref{table:analog_nb}) and were be used thereafter.
+The AM parameters were calibrated on the original archive (see resulting analog numbers in Tables \ref{table:analog_nb}) and were used thereafter.
 
@@
 \subsubsection{Changes in the atmospheric circulation analogy}
+\label{sec:perf_2Z}
 
@@
 Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions of the analogy criterion (S1) for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analog rank at the Ulrichen station on the whole calibration period (1961-2008 -- the full period could be used here, as precipitation were not considered at this stage), due to introduction of the MTW.
-The shape of the distributions of the conventional approach and the MTW were found to be similar, but the values of the analogy criterion were reduced (shifted to the left), and therefore better.
+The shape of the distributions of the conventional approach and the MTW were found to be similar, but the values of the analogy criterion were reduced (shifted to the left), and were therefore better.
 For analogs with higher ranks (e.g.
@@
 
-The impact of the MTW on the analogy criterion has been analyzed per precipitation classes.
+The impact of the MTW on the analogy criterion has been analyzed per precipitation classes (for the target day).
 The results are summarized in Fig.
@@
 It is nevertheless clear that the improvement were more important on days with higher precipitation.
-It was the same for all other stations.
+Once again, the results for the other stations were similar.
 
@@
 \ref{fig:changes_S1_seasons}.
-Differences between the seasons were substantial.
-The improvements were greater for winter than summer.
+Differences between the seasons were substantial, with greater improvements for winter than summer.
 
 \subsubsection{Changes in the moisture analogy}
+\label{sec:perf_2Z-2MI}
 
-When adding the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations did not increase, as they were subsampled in the previously $N_{1}$ selected analogs, but their dates have changed.
+When adding the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations did not increase, as they were conditioned by the $N_{1}$ previously selected analogs, but their dates have changed.
 In contrast to the AM on the atmospheric circulation only, both a reduction or an increase of the RMSE analogy criterion values were possible here with the MTW compared to the static approach.
@@
 \ref{fig:changes_RMSE} shows an almost insignificant improvement of the RMSE values.
-Unlike for the first level of analogy, the relative improvement of the RMSE values were distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
-Once again, the results for the other stations were similar.
+Unlike for the first level of analogy, the relative changes of the RMSE values were distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
 
@@
 Fig.
-\ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, other stations having the same behavior.
+\ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, the other stations having the same behavior.
 The performance score was improved for days with higher precipitation after the introduction of the MTW.
@@
 Among these, the zonal extent of the spatial windows of the circulation analogy decrease a bit (not shown).
-More significantly, the optimal number of analogs increased after introducing the MTW, of a considerable order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method (Table \ref{table:analog_nb}).
+More significantly, the optimal number of analogs increased after introducing the MTW, of a considerable order of magnitude: 25~\% to 83~\% for the 2Z method, and 20~\% to 67~\% for the final selection of the 2Z-2MI method (Table \ref{table:analog_nb}).
 The number of analogs of the first analogy level of the 2Z-2MI method even reached three times its previous value for the Visp station.
@@
 For the second approach, the synoptic proxy to use for the temporal disaggregation of the daily time series had to be identified first.
-The results are illustrated for the Zermatt station.
+The results are illustrated this time for the Zermatt station.
 Amongst the considered moisture variables (see Sect.
 \ref{sec:reconstruction}), the best proxy was the precipitable water at 45° N and 7.5° E, with a time offset of -6~h (Table \ref{table:proxy_correlations}).
-Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the reconstituted series using the proxy of precipitable water.
+Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the disaggregated series using the proxy of precipitable water.
 
@@
 
-On the first level of analogy, the median of the S1 values reduction (Fig.
-\ref{fig:changes_S1} bottom) started approximately at 5~\% for the first analog and reached more than 10~\% for the last one.
-This increase of improvements with the analog rank can be explained by the accumulation of better analogs in the distribution.
-The curve representing the minimum improvement is quickly slightly superior to zero, meaning that the criteria have been improved on most analogs for every day of the calibration period.
-All other stations had a similar improvement of the S1 criterion, both in terms of distribution shape and amplitude.
+On the first level of analogy, the improvement of the S1 criterion (Fig.
+\ref{fig:changes_S1} bottom) started approximately at 5~\% for the first analog and reached more than 10~\% for the last one (Sect.
+\ref{sec:perf_2Z}).
+This increase of improvements with the analog rank can be explained by the accumulation of better analogs in the selection.
+The curve representing the minimum improvement is quickly slightly superior to zero, meaning that the criteria have been improved on most analog ranks for every day of the calibration period.
+All other stations had a similar improvement of the S1 criterion, both in terms of the distribution shape and amplitude.
 The introduction of the MTW allowed finding better analog situations in the first level of analogy, resulting in a selection of days with more similar atmospheric circulation.
 
-When adding a second level of analogy on moisture variables, the criteria values (RMSE) were not improved by the MTW as the number of candidates was not higher (still the $N_{1}$ days selected in the first level of analogy).
+When adding a second level of analogy on moisture variables, the criteria values (RMSE) were not improved by the MTW (Sect.
+\ref{sec:perf_2Z-2MI}), as the number of candidates was not higher (still the $N_{1}$ days selected in the first level of analogy).
 However, this result of a globally null improvement of the RMSE values does not mean that the 2Z-2MI method cannot be improved by the MTW.
 It means that after the selection of the analog situations in terms of the synoptic circulation, the new candidate dates did not allow to find better analogs in terms of moisture.
-However, the selected dates have changed in the first level of analogy, and thus also in the final selection, which can potentially improve the prediction skill.
+However, the selected dates have changed in the first level of analogy, and thus also in the final selection, which did improve the prediction skill (Sect.
+\ref{sec:influence_scores}).
 
@@
 
-Finding better analog situations does not necessarily imply better skills to predict the precipitation.
-This had to be assessed and the MTW was found to improve the skill of the precipitation prediction for both the 2Z and 2Z-2MI methods (Fig.
-\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}).
+The MTW was found to improve the skill of the precipitation prediction for both the 2Z and 2Z-2MI methods (Fig.
+\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}, Sect.
+\ref{sec:influence_scores}).
 Moreover, it required no additional predictor.
@@
 It was here of the same order of magnitude as if the length of the archive doubled.
-Note that despite the number of candidate situations were four times higher, the gains seem to be lower than for a quadrupled archive length.
+Note that despite the number of candidate situations being four times higher, the gains seem to be lower than for a quadrupled archive length.
 The likely reason is that an actual longer archive would contain more atmospheric situations that might have been less observed on a shorter period.
@@
 \ref{sec:influence_precip}) and the performance scores (Sect.
-\ref{sec:improvement_CRPSS_precip_threshold}) were improved to a greater extent for heavier precipitation events.
-This is likely due to the fact that higher precipitation events are a consequence of atmospheric conditions with a greater dynamics, such as weather disturbances, which have a well marked temporal evolution.
+\ref{sec:improvement_CRPSS_precip_threshold}) were improved to a greater extent for days with heavier precipitation.
+This is likely due to the fact that higher precipitation events are a consequence of atmospheric conditions with greater dynamics, such as weather disturbances, which have a well-marked temporal evolution.
 Indeed, the position of the driving elements such as the low-pressure center and the fronts change significantly during a day.
 Moreover, these situations are less numerous than anticyclonic situations, which makes it less likely to find very good analogs at the same time of the day.
-We can therefore expect to improve more significantly these situations with a greater dynamics when introducing a MTW, as better matches to the target situation may be found.
-On the opposite, days with a low dynamics of the atmospheric circulation, such as anticyclonic situations, will not be radically improved by the introduction of the MTW.
+We can therefore expect to improve more significantly these situations with greater dynamics when introducing a MTW, as better matches to the target situation may be found.
+On the opposite, days with low dynamics of the atmospheric circulation, such as anticyclonic situations, will not be radically improved by the introduction of the MTW.
 
-We just mentioned that the MTW improves the prediction of heavier precipitation events.
+We just mentioned that the MTW improved the prediction of days with heavier precipitation.
 However, it will have no effect on the prediction of extreme events that were not yet observed, and therefore are not present in the archive.
@@
 One hypothesis is that the diurnal effects of the summer months have an influence on the atmospheric circulation, at least in the lower layers.
-This effect is based on the daily cycle and good analogs are essentially found for the same hours or time windows.
+This effect is in phase with the daily cycle and good analogs are essentially found for the same hours.
 
@@
 It was found that the new choice of the temporal window in winter, when using the MTW approach, is well balanced between the 4 options.
-This means a change of 75\% of the analogs selection compared to the conventional approach, which improved the circulation analogy.
+This means a change of 75\% of the analogs selection compared to the conventional approach.
 On the contrary, days in summer months had a preference for the initial temporal window (Z500 24~h \& Z1000 12~h), likely due to more pronounced diurnal effects which reduces the potential for improvement of the criteria.
@@
 
-After the recalibration of the AMs with the MTW, the optimal analog numbers were significantly higher than for the original methods (see Sect.
+After the recalibration of the AMs with the MTW, the optimal analog numbers were significantly higher than in the original methods (see Sect.
 \ref{sec:recalibration} and Fig.
@@
 \ref{fig:changes_S1}, the improvement of the S1 criterion grew along with the rank of the analog, which shows an accumulation of better analog situations in the distributions.
-It seems thus profitable to widen the selection of analogs in order to keep also some whose rank has increased, as they appear to be also relevant to predict precipitation values.
+It seems thus profitable to widen the selection of analogs in order to also keep some whose rank has increased, as they appear to be also relevant to predict precipitation values.
 The number of good analogs was thus globally increased.
@@
 7 of \citealt{Hamill2006a}).
-The observed increases in the number of analog situations with the MTW resulted in better performance skills for a given method, as it can be seen as an inflation of the archive.
+The observed increase in the number of analog situations with the MTW resulted in better performance skills for a given method, as it can be seen as an inflation of the archive.
 However, if new relevant predictors were added to the method, the number of analogs would then decrease.
@@
 \conclusions  %% \conclusions[modified heading if necessary]
+\label{sec:conclusions}
 
-The AM is most often based on a daily time step, due to the availability of long precipitation archives.
-However, it is unlikely that two analog synoptic situations, that evolve relatively quickly, would correspond optimally at the same hour of the day.
+AMs are most often based on a daily time step, due to the availability of long precipitation archives.
+However, it is unlikely that two analog synoptic situations, that evolve relatively quickly, would correspond optimally at the same hours of the day.
 It is thus probable that better matches can be found at another time, which can change the selection of the analogs dates.
@@
 
-The improvement of the circulation analogy was found to be more important for heavy precipitation events, which are generally related to more dynamic atmospheric situations and are less frequent in the archive.
-This dynamism implies more specific circulation patterns that are evolving more rapidly.
+The improvement of the circulation analogy was found to be more important for days with heavier precipitation, which are generally related to more dynamic atmospheric situations and are less frequent in the archive.
+These situations have more specific circulation patterns that are evolving more rapidly.
 Thus, a MTW was found to be of particular interest in this kind of situation, and benefits the prediction of heavier precipitation events.
@@
 The impact of the MTW on the prediction skill has never been assessed before, due to the shortcoming of long precipitation series at a sub-daily time step.
-The impact of the MTW approach was assessed on a 25 years time series with a high temporal resolution.
+It was here assessed on a 25 years time series with a high temporal resolution.
 After the introduction of the MTW, the performance scores increased of the same order of magnitude as if the length of the archive doubled, in this case study.
@@
 First, these archives of high temporal resolution precipitation data are increasing now with time.
-Another possible source of such archives is the establishment of precipitation reanalysis at a country scale, or the use of reanalysis-driven RCMs (Regional Climate Models) or LAMs (Limited Area Models) on a long period.
+Another possible source of such archives is the establishment of precipitation reanalysis at a regional scale, or the use of reanalysis-driven RCMs (Regional Climate Models) or LAMs (Limited Area Models) on a long period.
 Even though outputs from these models might be biased or not accurate enough, information on the timing of the precipitation events could be useful in order to disaggregate stations time series.

### 2016-11-24 Moving temporal window - HESS/template.tex
My last HESS corrections.

@@
 
-%TODO: check figs and table captions
-%TODO: order figs
 %TODO: english editing
-%TODO: analogs
 %TODO: perspective Obled: MTW without precip -> indicator
@@
 They highlight a three-way relationship between the quality of the analogy, the archive length and the size of the spatial domain (or degrees of freedom): errors increase with a bigger domain, but decrease with a longer archive.
-They demonstrate that it is not possible to find good analogues on the whole northern hemisphere with a 100 years archive (and even for much higher orders of magnitude).
-For that reason, smaller spatial windows are always considered to search for analogues, and the archive length is maximized.
+They demonstrate that it is not possible to find good analogs on the whole northern hemisphere with a 100 years archive (and even for much higher orders of magnitude).
+For that reason, smaller spatial windows are always considered to search for analogs, and the archive length is maximized.
 
@@
 
+\begin{figure}[htb]
+	\begin{center}
+		\includegraphics[width=8cm]{figures/illustration_disaggregation.pdf}
+	\end{center}
+	\caption{Illustration of the generation of 24~h-totals moving averages by means of a proportional distribution. The colours refer to the corresponding day of the daily time series.}
+	\label{fig:illustration_disaggregation}
+\end{figure}
+
+\begin{figure}[htb]
+	\includegraphics[width=8.3cm]{figures/plots_CRPSS_2Z.pdf}
+	\caption{Performance score (CRPSS, \%) of the AM on the atmospheric circulation, at the different stations, for (dashed) the full archive, i.e.
+1961-2008, (yellow) the reduced archive, i.e.
+1982-2007, (blue) the introduction of the MTW on the reduced archive, and (green) the recalibrated parameters of the AM with the MTW.}
+	\label{fig:plots_CRPSS_2Z}
+\end{figure}
+
+\begin{figure}[htb]
+	\includegraphics[width=8.3cm]{figures/plots_CRPSS_2Z-2MI.pdf}
+	\caption{Same as Figure \ref{fig:plots_CRPSS_2Z}, but for the analog method with a second level on the moisture variables.}
+	\label{fig:plots_CRPSS_2Z-2MI}
+\end{figure}
+
 \begin{figure*}[htb]
@@
 	\end{center}
-	\caption{Changes in the S1 criterion distributions of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$ and (d) $40^{th}$ analog ranks for the Ulrichen station, due to the MTW.}
+	\caption{Changes in the S1 criterion distributions, due to the MTW, of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$ and (d) $40^{th}$ analog ranks for the Ulrichen station.}
 	\label{fig:changes_S1_analogs}
@@
 	\end{center}
-	\caption{Synthesis of the changes in the S1 criterion, due to the MTW, for the Ulrichen station, depending on the ranks of the analog.
+	\caption{Synthesis of the changes in the S1 criterion, due to the MTW, for the Ulrichen station, depending on the rank of the analog.
 (a) Quantiles of the S1 distributions with and without the MTW.
@@
 \begin{figure}[htb]
-	\includegraphics[width=8.3cm]{figures/hours_selection_per_season.pdf}
-	\caption{Distribution of the predictors hours in the selected analog dates depending on the season, for the Ulrichen station.}
-	\label{fig:hours_selection_per_season}
-\end{figure}
-
-\begin{figure}[htb]
 	\begin{center}
@@
 	\end{center}
-	\caption{Synthesis of the changes in the RMSE criterion, due to the MTW, for the Ulrichen station, depending on the ranks of the analog.
+	\caption{Synthesis of the changes in the RMSE criterion, due to the MTW, for the Ulrichen station, depending on the rank of the analog.
 (a) Quantiles of the RMSE distributions with and without the MTW.
@@
 	\label{fig:changes_RMSE}
-\end{figure}
-
-\begin{figure}[htb]
-	\includegraphics[width=8.3cm]{figures/plots_CRPSS_2Z.pdf}
-	\caption{Performance score (CRPSS, \%) of the AM on the atmospheric circulation, at the different stations, for (dashed) the full archive, i.e.
-1961-2008, (yellow) the reduced archive, i.e.
-1982-2007, (blue) the introduction of the MTW on the reduced archive, and (green) the recalibrated parameters of the AM with the MTW.}
-	\label{fig:plots_CRPSS_2Z}
-\end{figure}
-
-\begin{figure}[htb]
-	\includegraphics[width=8.3cm]{figures/plots_CRPSS_2Z-2MI.pdf}
-	\caption{Same as Figure \ref{fig:plots_CRPSS_2Z}, but for the analog method with a second level on the moisture variables.}
-	\label{fig:plots_CRPSS_2Z-2MI}
 \end{figure}
@@
 \begin{figure}[htb]
-	\begin{center}
-		\includegraphics[width=8cm]{figures/illustration_disaggregation.pdf}
-	\end{center}
-	\caption{Illustration of the generation of 24~h-totals moving averages by means of a proportional distribution. The colours refer to the corresponding day of the daily time series.}
-	\label{fig:illustration_disaggregation}
+	\includegraphics[width=8.3cm]{figures/hours_selection_per_season.pdf}
+	\caption{Distribution of the predictors hours in the selected analog dates depending on the season, for the Ulrichen station.}
+	\label{fig:hours_selection_per_season}
 \end{figure}
@@
 \begin{table}[htb]
-	\caption{Values of the CRPSS (\%) skill score for the original and the recalibrated parameters (with the sequential method, as described in Sect.
-\ref{sec:introduction}) using the MTW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
+	\caption{Values of the CRPSS (\%) score for the original and the recalibrated parameters (with the sequential method, as described in Sect.
+\ref{sec:calibration}) using the MTW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
 	\begin{center}

### 2016-12-01 Optimization case study - JoH/elsarticle-template.tex
JoH paper under correction.

@@
 \begin{abstract}
-The Analog Method aims at predicting precipitation based on predictors variables provided by global models.
+Analog methods aim at predicting precipitation based on synoptic predictors provided by general circulation models or numerical weather prediction models.
 The method samples a selection of days in the archives that are similar to the target day to predict, and consider the set of their corresponding observed precipitation (the predictand) as the conditional distribution for the target day.
-The relationship between predictors and predictands relies on some parameters that characterize how and where the similitude between two atmospheric situations is defined.
+The relationship between predictors and predictands relies on some parameters that characterize how and where the similitude between two atmos+pheric situations is defined.
 
-This relationship is usually established by a semi-automatic sequential procedure that has strong limitations.
-A new global optimization approach relying on Genetic Algorithms can optimize all parameters jointly and automatically, which is a breakthrough in the way the Analog Method was calibrated until now.
+This relationship is usually established by a semi-automatic sequential procedure that has strong limitations: (i) it cannot automatically choose the pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it could not easily handle new degrees of freedom.
+A new global optimization approach relying on genetic algorithms can optimize all parameters jointly and automatically, which is a breakthrough in the way the analog method was calibrated until now.
 It allows taking into account parameters inter-dependencies, and selecting objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
@@
 
-The analog method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1956, Lorenz1969}, that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Duband1970, Bontron2005}.
-It aims at predicting a predictand, often the daily precipitation \citep[eg.][]{Guilbaud1997, Bontron2005, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, BenDaoud2015}, on the basis of predictor variables describing the synoptic atmospheric circulation.
-Other predictands are also often considered \citep[see][for a non-exhaustive list]{Horton2016}.
+The analog method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1956, Lorenz1969}, that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Duband1970}.
+It uses predictor variables describing the synoptic atmospheric circulation in order to predict local-scale predictands of interest.
+It is often used to predict daily precipitation, either in an operational forecasting context \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Hamill2015, BenDaoud2016}, or a climate context \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015, Raynaud2016b}.
+Other predictands are also considered, such as precipitation radar images \citep{Panziera2011,Foresti2015a}, temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016, Raynaud2016b}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, and radiation \citep{Bois1981, Raynaud2016b}.
 
 In operational forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies, it is used to downscale the results of global climate model (GCM) simulation runs.
-In this last case, although the GCM represents the large or regional scale evolutions of the atmosphere, it would be far too computer intensive to get down to variables such as precipitation at a rather small and representative scale.
+In this last case, although the GCM represents the large or regional scale evolutions of the atmosphere, it would be far too computer intensive to resolve variables such as precipitation at a rather small and representative scale.
 Therefore the idea is to rely on past observations to bypass these unaffordable small scale simulations and to go from the large scale situation proposed by the GCM to the end variables like precipitation by searching analogs in the archives.
 
-The method can be made of multiple successive subsampling steps, each of them relying on different meteorological variables.
-A certain number of parameters define the relationship between predictors and predictands, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criteria itself, and finally the number of analog situations to keep at each subsampling level.
-These parameters are usually calibrated by means of a semi-automatic sequential procedure \citep[see][for the details]{Bontron2004, Horton2016}, i.e.
-by optimizing each single parameter one at a time, in an arbitrarily chosen order, with no or little reconsidering.
-This sequential approach has therefore strong limitations: (i) it cannot automatically choose the pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it could not easily handle new degrees of freedom, such as a weighting between the pressure levels.
-Thus, even if the processing involved is relatively fast, the sequential approach requires laborious assessments of predictors combinations (variables, pressure levels, temporal windows), and present a high risk of ending in a local optimum due to subjective initial choices and lack of consideration of parameters inter-dependencies.
+The method can be designed with multiple successive subsampling steps, each of them relying on different meteorological variables.
+A certain number of parameters define the relationship between predictors and predictands, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criterion itself, and finally the number of analog situations to keep at each subsampling level.
+These parameters are usually calibrated by means of a semi-automatic sequential procedure \citep[see][for the details]{Bontron2004, Radanovics2013, Horton2016a}, i.e.
+by optimizing each single parameter one at a time, in an arbitrarily chosen order, with no or little reassessment.
+This sequential approach has therefore strong limitations: (i) it cannot automatically choose the optimal pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it could not easily handle new degrees of freedom, such as a weighting between the pressure levels.
+Thus, even if the processing involved is relatively fast, the sequential approach requires laborious assessments of predictors combinations (variables, pressure levels, temporal windows), and presents a high risk of ending in a local optimum due to subjective initial choices and lack of consideration of parameter inter-dependencies.
+Other calibration methods exist for specific applications, such as the radar images \citep{Panziera2011, Foresti2015a}.
 
-With the perspective to overcome these limitations, a global optimization by Genetic Algorithms (GAs) was introduced by \citet{Horton2016a}.
+With the perspective to overcome these limitations, a global optimization by genetic algorithms (GAs) was introduced by \citet{Horton2016}.
 An intensive assessment work resulted in recommendations of parametrization of GAs in order to optimize AMs successfully.
-The present paper is based on these recommendations and illustrate them on precipitation predicting for the upper Rh\^{o}ne catchment in the Swiss Alps.
+The present paper is based on these recommendations and illustrate them for precipitation prediction for the upper Rh\^{o}ne catchment in the Swiss Alps.
 It aims at proving the relevance of a fully-automatic, objective, and global, optimization technique for AMs.
@@
 
-A short overview of AMs is presented in section \ref{sec:analog_method}, as well as a summary of Genetic Algorithms in section \ref{sec:gas}.
+A short overview of AMs is presented in section \ref{sec:analog_method}, as well as a summary of genetic algorithms in section \ref{sec:gas}.
 Section \ref{sec:case_study} describes the case study area.
@@
 
-Multiple variations of the methods exist, and most of them will not be detailed hereafter \cite[see][for more comprehensive listings]{Horton2016, BenDaoud2015}.
+Multiple variations of the methods exist, and most of them will not be detailed hereafter \cite[see][for more comprehensive listings]{BenDaoud2016}.
 However, there are mainly 2 parameterizations that are most often used for precipitation downscaling and that will be considered as reference: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
 
-The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): the similarity of the atmospheric circulation of a target date with every day of the archive is assessed by processing the S1 criteria \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window.
-\citet{Bontron2005} showed that the geopotential height at 500~hPa (Z500) and 1000~hPa (Z1000) are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criteria performs better than scores based on absolute distances.
-The reason for such better results is that the S1 criteria allows comparing the circulation pattern, by means of the gradients, rather than the absolute value of the geopotential height.
-To cope with seasonal effects, candidate dates are extracted within a period of 4 months centered around the target date, for every year of the archive.
-Following the nomenclature proposed by \citet{Horton2016}, this method using two geopotential heights will be named 2Z.
+The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): the similarity of the atmospheric circulation of a target date with every day of the archive is assessed by processing the S1 criterion \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window:
 
@@
 where $\Delta \hat{z}_{i}$ is the difference in geopotential height between the \textit{i}th pair of adjacent points of the gridded data describing the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
-The differences are processed separately in both directions over the selected spatial domain.
+The differences are processed separately in both North and East directions over the selected spatial domain.
 The smaller the S1 values, the more similar the pressure fields.
+
+\citet{Bontron2005} showed that the geopotential height at 500~hPa (Z500) and 1000~hPa (Z1000) are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criterion performs better than scores based on absolute distances.
+The reason for such better results is that the S1 criterion allows comparing the circulation pattern, by means of the gradients, rather than the absolute value of the geopotential height, which represent better the flow direction.
+To cope with seasonal effects, candidate dates are extracted within a period of 4 months centered around the target date, for every year of the archive.
+This method using two geopotential heights will be named 2Z.
 
@@
 When a second level of analogy is added, a higher number of analogs $N_{1}$ is kept on the first level.
+Moisture fields are not as well predicted by NWP models as pressure variables.
+It means that the 2Z-2MI method, when used in real-time forecasting, is very dependent on the skill of the NWP model in predicting moisture fields, and thus is often used on limited lead times.
 
@@
 
-Predictors are generally reanalysis datasets.
+Predictors are generally extracted from reanalysis datasets.
 NCEP-NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} are used here, but it could be any other reanalysis dataset.
@@
 The time series from every available gauging station were averaged over subregions of approximately 500~km$^{2}$ in order to smooth local effects \citep{Obled2002, Marty2012}.
+It helps accounting for local variability, mainly when convective processes are involved, which increases slightly the prediction skill.
 
@@
 
+The performance assessment in the present context consists in verifying the prediction of an ensemble-probabilistic technique.
 The score that is most often used to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
@@
 
-In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution of daily precipitation as the reference.
+In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution of precipitation from the entire archive as the reference.
 The CRPSS (\textit{Continuous Ranked Probability Skill Score}) is thus defined as following:
@@
 
-Genetic Algorithms (GAs) were developed by \citet{Holland1992b} and \citet{Goldberg1989}.
+Genetic algorithms (GAs) were developed by \citet{Holland1992b} and \citet{Goldberg1989}.
 They are part of Evolutionary Algorithms \citep{Back1993b, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
-GAs seek the global optimum on a complex surface, theoretically without restriction.
+GAs seek the global optimum on a complex surface, theoretically without restriction, which is of interest for AMs, that are characterized by a complex high-dimensional error function having multiple local optima.
 Practically, GAs allow rapidly approaching satisfactory solutions, but they do not provide the optimum solution for sure \citep{Zitzler2004a}.
 It is indeed mainly a matter of time.
-When the optimizer gets closer to the global optimum, any new improvement takes more time to appear (see for example Figure \ref{fig:evolution}), and the final adjustment of the parameters is very time consuming \citep{Back1993a}.
+When the optimizer gets closer to the global optimum, any new improvement takes more time to appear (see for example the slow-down of the improvements over generations in Figure \ref{fig:evolution}), and the final adjustment of the parameters is very time consuming \citep{Back1993a}.
 For problems that require a significant amount of time in order to evaluate the objective function, as in the case of AMs, the number of generations has to be limited in order to get reasonable processing time.
@@
 
-The optimizations were performed based on the recommended GAs parametrization for AMs as described in \citet{Horton2016a}.
-As the optimization is mostly sensitive to the mutation operator (that randomly changes some values in the parameters sets), parallel optimizations are considered with variants of this operator, according to \citet{Horton2016a}:
+The optimizations were performed based on the recommended GAs parametrization for AMs as described in \citet{Horton2016}.
+As the optimization is mostly sensitive to the mutation operator (that randomly changes some values in the parameters sets), parallel optimizations are considered with variants of this operator, according to \citet{Horton2016}:
 
@@
 	\item 3x non-uniform mutation \citep{Michalewicz1996} with varying parameters,
-	\item 1x multi-scale mutation \citep{Horton2016a},
-	\item 2x chromosome of adaptive search radius \citep{Horton2016a}
+	\item 1x multi-scale mutation \citep{Horton2016},
+	\item 2x chromosome of adaptive search radius \citep{Horton2016}
 \end{itemize}
@@
 Even though the region is rather small, the meteorological influences related to extreme weather conditions varies substantially within it \citep[see][]{Horton2012}.
+Indeed, a high spatial variability exists, which is due to the complex orography of the region.
 Based on different climatological analyses, the gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}) :
@@
 	\item Lower Rhone Valley
-	\item Left side valleys
+	\item Southern valleys
 	\item Southern ridges
@@
 Thus, the tested parametrization evolved iteratively in complexity.
-The detailed results of the intermediate stages are not provided \citep[see][for the details]{Horton2012a}.
+The detailed results of the intermediate stages are not provided in this paper \citep[see][for the details]{Horton2012a}.
 
@@
 The optimizer had to choose the number of analogs, both spatial windows with no overlapping constraint, as well as the temporal windows (hours of observation of the geopotential), what the sequential calibration cannot do.
-With these degrees of freedom, a relative CRPSS improvement of 3.97\% and 2.45\% in average was obtained for the CP and the VP respectively.
+With these degrees of freedom, a relative CRPSS improvement of 3.97\% and 2.45\% in average was obtained for the CP and the VP respectively, with regard to the reference method based on Z500 and Z1000.
 Some tests showed that most of the gains are due to the non-overlapping spatial windows.
-This is not a tremendous improvement, but it demonstrated that the optimizer was able to get relevant parameters.
+This is not a large improvement, but it demonstrated that the optimizer was able to get relevant parameters.
 
-Then, an additional degree of freedom was provided to the GAs by letting them choose the pressure levels along with the other parameters, which is also a non-automated process in the sequential calibration.
+Then, an additional degree of freedom was provided to the GAs by letting them choose the pressure levels along with the other parameters (analog numbers, spatial and temporal windows), which is also a non-automated process in the sequential calibration.
 This degree of freedom increased the optimization time and may decrease the number of simulations that converge to a single solution.
@@
 We then tried with 4 predictors, and so on, up to 8.
-Every time a new predictor to optimize was added, the score on the CP increased, but always more to a smaller extent.
+Every time a new predictor to optimize was added, the score on the CP increased, but in a reduced amount.
 However, the score value on the VP dropped after 4 predictors, revealing an over-parametrization of the method, and thus a lack of robustness.
 Considering 4 predictors is optimal for this case study, since the gain in CRPSS is significant.
-It cannot be excluded that another number would prevail in another region under other meteorological conditions.
+It cannot be excluded that another number would prevail in another region than the upper Rh\^{o}ne catchemnt, under other meteorological conditions.
 
-Finally, a weighting of the criteria values per pressure level was proposed, again optimized by GAs.
+Finally, a weighting of the analogy criteria values per pressure level was proposed, again optimized by GAs.
 The weighting operates in the combination of the S1 criteria processed on every level, which were previously averaged with equal weights.
@@
 
-The chosen method for the atmospheric circulation analogy, based on 4 levels of the geopotential, and that will be name 4Zo, is made of the following degrees of freedom:
+The chosen method for the atmospheric circulation analogy, based on 4 levels of the geopotential, and that will be named 4Zo, is made of the following degrees of freedom:
 
@@
 
-To assess the parameters cross-compatibility, those optimized for one subregion were applied to the others.
+To assess the parameters cross-compatibility, and the spatial coherence of the resulting parameters, those optimized for one subregion were applied to the others.
 The resulting losses or gains of the CRPSS are displayed in Figure \ref{fig:crossing_4Zo_calib} for the CP and in Figure \ref{fig:crossing_4Zo_valid} for the VP.
@@
 Its spatial distribution is however homogeneous.
-The optimizer thus provided consistent selections of pressure levels and temporal windows, which depicts a significant preference in the AM, and the success of GAs to provide consistent results.
+The optimizer thus provided consistent selections of pressure levels and temporal windows.
 The automatic selection of the pressure levels is a big advantage in favor of a global optimization.
@@
 The last one (Z1000 at 30~h) is rather large and squared.
-Subregions number 5 (Left side valleys) and 6 (Southern ridges) have exactly the same spatial windows, which suggest that they behave in a similar way and thus could have been merged.
+Subregions number 5 (Southern valleys) and 6 (Southern ridges) have exactly the same spatial windows, which suggest that they behave in a similar way and thus could have been merged.
 This similarity is a good sign for the accuracy of the optimized parameters.
@@
 When optimizing a method made of 2 levels of analogy, the introduction of moisture variables in the second level has an influence on the parameter values of the first level.
+It means that the two levels of analogy bring complementary information, and are thus not independent.
 This is first visible on the number $N_{1}$ of analogs to be selected on the first level, and on the selection of the pressure levels for the circulation analogy.
@@
 As for the pressure levels, Z1000 that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) is now less chosen (once or even not at all) for both 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}) and 4Zo-4MIo (not shown).
-There is indeed a shift of the previously selected Z1000 for higher levels, that is even slightly stronger with 4 moisture predictors than with 2.
+There is indeed a vertical shift of the previously selected Z1000 for higher levels, that is even slightly stronger with 4 moisture predictors than with 2.
 This change is likely due to the fact that when considering only the circulation analogy, the method tries to take into account information that can serve as proxy for moisture assessment, whereas it does not need it with the moisture index.
@@
 The convergence of parallel optimizations decreases when the method to optimize becomes more and more complex.
-The optimizer do not always converge to the exact global optimum, but to its surroundings.
+The optimizer does not always converge to the exact global optimum, but to its surroundings.
 This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that one has to stop it before the end, due to the required processing time (see Figure \ref{fig:evolution} as example).
 The resulting parameters may sometimes present non negligible differences, even though the score is almost similar.
-Through some Monte-Carlo analyses of the parameter space properties of the AM, \citet{Horton2012a} showed that some parameters of the method have a wide range of acceptable values \citep[see also][]{Horton2016}.
+Through some Monte-Carlo analyses of the parameter space properties of the AM, \citet{Horton2012a} showed that some parameters of the method have a wide range of acceptable values.
 The spatial windows, for example, can be larger than the optimal size without much impact on the score, while they cannot be smaller \citep[see also][]{Bontron2004}.
@@
 GAs are relatively heavy on processing and require an IT infrastructure capable of performing thousands hours of calculations.
-However, they automatically optimize all parameters of the AM, what the sequential calibration does not allow.
+However, they automatically optimize all parameters of the AM, what is not possible with the sequential calibration.
 Therefore, much human time is saved, that was previously required to assess successively numerous combinations of parameters (particularly the selection of the pressure levels and the temporal windows).
@@
 
-A parametric dependence between the analogy of circulation and the moisture variables was identified.
+A dependence in the selected parameters between the analogy of circulation and the moisture variables was identified.
 When the two levels are considered together, the optimal parameters of the circulation analogy are different.
@@
 GAs provide parameterizations of AMs that exceed the performance of the sequential calibration.
-In addition, it has been observed that the prediction for days with strong precipitation were significantly more improved, which is clearly interesting in the framework of flood forecasting.
+In addition, it has been observed that the prediction for days with strong precipitation were improved to a greater extent, which is clearly interesting in the framework of flood forecasting.
 
@@
 It is already possible to undertake such approach with our code.
-Moreover, the AM has been explored for decades for precipitation forecasting, but very few works analyze its potential for other predictands.
+Moreover, the AM has been explored for decades for precipitation forecasting, but not as intensively for other predictands.
 A global optimizer, such as GAs, can speed up this assessment significantly.
@@
 
+The authors would also like to acknowledge the work Loris Foresti and another anonymous reviewer, which contributed to improving this paper.
+
 \section*{References}
 
-\bibliography{references}
+%\bibliography{references}
+\bibliography{../_refs/4_articles-2016_JoH_optimizations}
 
@@
 	\caption{Parameters of the reference method on the atmospheric circulation (2Z).
-The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window).
-The criteria used for the current level of analogy is then provided, as well as the number of analogs.}
+The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation within the target day (temporal window).
+The criterion used for the current level of analogy is then provided, as well as the number of analogs.}
 	\footnotesize
@@
 	\caption{Parameters of the 4Zo method (analogy on 4 levels of the atmospheric circulation) optimized for the Chablais subregion.
-The columns are the following: L = level of analogy, V = meteorological variable, H = hour of observation or temporal window, D = domain or spatial window, W = weighting of the score for the selected pressure levels, C = criteria, N = number of analogs.}
+The columns are the following: L = level of analogy, V = meteorological variable, H = hour of observation within the target day, D = domain or spatial window, W = weighting of the score for the selected pressure levels, C = criterion, N = number of analogs.}
 	\footnotesize
@@
 \begin{table}[t]
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo method.}
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo method, compared to the reference method.}
 	\footnotesize
@@
 \begin{table}[t]
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo-2MIo method.}
+	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo-2MIo method, compared to the reference method.}
 	\footnotesize

### 2016-12-01 Moving temporal window - HESS/template.tex
Elsevier edition.

@@
 %% Please use the following documentclass and Journal Abbreviations for Discussion Papers and Final Revised Papers.
+
+%TODO: check references: complete, doi, etc
 
@@
 
-%TODO: english editing
-%TODO: perspective Obled: MTW without precip -> indicator
-
 \begin{document}
@@
 
-\title{The Analog Method for Precipitation Prediction: Finding Better Analog Situations at a Sub-Daily Time Step}
+	\title{The Analogue Method for Precipitation Prediction: Finding Better Analogue Situations at a Sub-Daily Time Step}
 
@@
 
-\runningtitle{Finding Better Analog Situations at a Sub-Daily Time Step}
+	\runningtitle{Finding Better Analogue Situations at a Sub-Daily Time Step}
 
@@
 	\begin{abstract}
-The Analog Method (AM) aims at predicting local weather variables (predictands), such as precipitation, by means of a statistical relationship with predictors at a synoptic scale.
-The analogy is generally first assessed on gradients of geopotential fields, in order to sample days with a similar atmospheric circulation.
+		Analogue methods (AM) predict local weather variables (predictands), such as precipitation, by means of a statistical relationship with predictors at a synoptic scale.
+The analogy is generally assessed on gradients of geopotential fields first, in order to sample days with a similar atmospheric circulation.
 Other predictors, such as moisture variables, can also be added in a successive level of analogy.
 
-The search for candidate situations, for a given target day, is usually undertaken by comparing the state of the atmosphere at fixed hours of the day, for both the target day and the candidate analogs.
-The main reason is the use of daily precipitation time series, due to the length of their available archives, and the unavailability of equivalent archives at a finer time step.
-However, it is unlikely for the best analogy to happen at the very same hour, as it may occur at a different time of the day.
-In order to assess the potential of finding better analogs at a different hour, a moving time window (MTW) has been introduced on a reduced archive of hourly precipitation totals.
+		The search for candidate situations for a given target day is usually undertaken by comparing the state of the atmosphere at fixed hours of the day for both the target day and the candidate analogues.
+The main reason is the use of daily precipitation time series due to the length of their available archives, and the unavailability of equivalent archives at a finer time step.
+However, it is unlikely for the best analogy to occur at the very same hour, as it may occur at a different time of day.
+In order to assess the potential for finding better analogues at a different hour, a moving time window (MTW) has been introduced on a reduced archive of hourly precipitation totals.
 
-The MTW resulted in a better analogy in terms of the atmospheric circulation, with improved values of the analogy criterion on the whole distribution of analog dates.
-The improvement was found to grow with the analog rank due to an accumulation of more similar situations in the selection.
-A seasonal effect has also been identified, with larger improvements in winter than in summer, supposedly due to stronger diurnal cycles in summer, which favor predictors at the same hour for the target and analog days.
+		The MTW resulted in a better analogy in terms of the atmospheric circulation, with improved values of the analogy criterion on the entire distribution of analogue dates.
+The improvement was found to grow with the analogue rank due to an accumulation of better analogues in the selection.
+A seasonal effect has also been identified, with larger improvements in winter than in summer, supposedly due to stronger diurnal cycles in summer that favour predictors at the same hour for the target and analogue days.
 
-The impact of the MTW on the prediction skill has been assessed by means of a sub-daily precipitation series transformed into moving 24~h-totals at a 6-hourly time step.
-The prediction skill was found to be improved by the MTW, and even more after recalibrating the AM parameters.
-Moreover, the improvement was greater for days with heavy precipitation, which are generally related to more dynamic atmospheric situations, where timing is more specific, and which are less present in the archive.
+		The impact of the MTW on prediction skill has been assessed by means of a sub-daily precipitation series transformed into moving 24-h totals at 6-h time steps.
+The prediction skill was found to have improved by the MTW, and even to a greater extent after recalibrating the AM parameters.
+Moreover, the improvement was greater for days with heavy precipitation, which are generally related to more dynamic atmospheric situations where timing is more specific and which are fewer in the archive.
 
-However, the MTW requires sub-daily precipitation time series, which are generally available on a shorter period than daily precipitation archives.
-Thus, two simple temporal disaggregation methods were assessed in order to make longer archives usable with the MTW.
-The assessed approaches were not successful, which emphasized the need to use time series with an appropriate chronology.
-These should be available in a near future, either by means of growing archives of measurements, or by the establishment of regional precipitation reanalyzes.
-Then, the use of a MTW in AMs can be considered for any application, and in any context, let it be operational forecasting or climate-related studies.
+		However, the MTW requires a sub-daily precipitation time series, which is generally available for a shorter period than daily precipitation archives.
+Therefore, two simple temporal disaggregation methods were assessed in order to make longer archives usable with the MTW.
+The assessed approaches were not successful, emphasizing the need to use time series with an appropriate chronology.
+These should be available in the near future, either by means of growing archives of measurements or by the establishment of regional precipitation reanalysis data.
+The use of an MTW in the AM could then be considered for any application and in any context, may it be for operational forecasting or climate-related studies.
 
@@
 
-Analog methods (AMs) are based on the hypothesis that two relatively similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}.
-They are part of statistical downscaling methods \citep{Maraun2010}, and consist in finding past situations that are similar, in terms of the atmospheric circulation or other synoptic predictors, to the target day of interest.
-Then, the local weather variables of interest (predictand) that were observed at the analog dates are used to construct a probabilistic prediction for the target day \citep{Duband1970, Zorita1999}.
+	Analogue methods (AMs) are based on the hypothesis that two relatively similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}.
+They are statistical downscaling methods \citep{Maraun2010} and consist of finding past situations that are similar in terms of the atmospheric circulation or other synoptic predictors to the target day of interest.
+The local weather variables of interest (predictand) that were observed at the analogue dates are used to construct a probabilistic prediction for the target day \citep{Duband1970, Zorita1999}.
 Multiple variations of the method exist \citep[a non-exhaustive listing can be found in][]{BenDaoud2016}.
-AMs are used for operational precipitation forecasting, either in the context of flood forecasting or hydropower production \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as precipitation downscaling in a climate perspective \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015}.
+The AMs are used for operational precipitation forecasting, either in the context of flood forecasting or hydropower production \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as in precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}.
 Other applications focus on temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectories of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
 
-The spatial transferability of the method is analyzed in \citet{Chardon2014}.
-A great advantage of AMs is that they create realistic precipitation patterns, as they are based on observed situations, with consistent spatial distribution, as long as the analog dates chosen for a region are the same.
-The temporal transferability has also been the topic of recent studies, may it be for past or future climates \citep{Dayon2015, Caillouet2016}.
+	The spatial transferability of the method is analysed in \citet{Chardon2014}.
+A great advantage of AMs is that they create realistic precipitation patterns, since they are based on observed situations with consistent spatial distribution, as long as the analogue dates chosen for a region are the same.
+Their temporal transferability has also been the topic of recent studies for past or future climates \citep{Dayon2015, Caillouet2016}.
 
-\citet{Ruosteenoja1988} and \citet{Vandendool1994} have analyzed the influence of the archive length on the quality of the analogy.
-They highlight a three-way relationship between the quality of the analogy, the archive length and the size of the spatial domain (or degrees of freedom): errors increase with a bigger domain, but decrease with a longer archive.
-They demonstrate that it is not possible to find good analogs on the whole northern hemisphere with a 100 years archive (and even for much higher orders of magnitude).
-For that reason, smaller spatial windows are always considered to search for analogs, and the archive length is maximized.
+	\citet{Ruosteenoja1988} and \citet{Vandendool1994} have analysed the influence of the archive length on the quality of the analogy.
+They highlighted a three-way relationship between the quality of the analogy, the archive length, and the size of the spatial domain (or degrees of freedom): errors increase with a bigger domain, but decrease with a longer archive.
+They demonstrated that it is not possible to find good analogues over the whole northern hemisphere with a 100 year archive (and even for much higher orders of magnitude).
+For that reason, smaller spatial windows are always considered when searching for analogues, and the archive length is maximized.
 
-Thus, due to the availability of long precipitation archives at a daily time step that have no equivalent at a finer resolution, AMs are usually implemented on a daily basis (see references above).
-Therefore, the analog situations are assessed by comparing predictors at fixed hours of the day.
-However, it can be expected that the analogy of the synoptic situations does not occur systematically at the same time of the day, and that better candidates can be found by shifting to a different hour.
-On this assumption, a moving time window (MTW) was introduced to allow searching for candidates at different hours of the day.
-Previous tests showed the benefit, in terms of analogy criterion values, of searching for analog synoptic situations at a finer time step, but without assessing the impact on the prediction skills \citep{Finet2008}.
+	Therefore, due to the availability of long precipitation archives at a daily time step that have no equivalent at a finer resolution, AMs are usually implemented on a daily basis.
+Therefore, the analogue situations are assessed by comparing predictors at fixed hours of the day.
+However, it can be expected that the analogy of the synoptic situations does not occur systematically at the same time of the day and that better candidates can be found by shifting to a different hour.
+With this assumption, a moving time window (MTW) was introduced to allow the search for candidates at different hours of the day.
+Previous tests showed the benefit, in terms of analogy criterion values, of searching for analogue synoptic situations at a finer time step, but without assessing the impact on the prediction skill \citep{Finet2008}.
 
-The MTW allows finding analog situations at different hours of the day, which can also be seen as an inflation of the archive length.
-However, despite having $x$ time more candidate situations, the quantity of new information is not expected to be as important as a $x$ time longer archive, due to significant correlation between successive situations within the same day.
+	The MTW finds analogue situations at different hours of the day, which can also be seen as an inflation of the archive length.
+However, despite having $x$ time more candidate situations, the quantity of new information is not expected to be as important as a $x$ time longer archive due to significant correlation between successive situations within the same day.
 Nevertheless, if the MTW can improve the prediction skill of the AM, it means that it does extract new information from the archive.
-Thus, if the reduction of the archive length necessary to the MTW, due to the reduced availability of sub-daily precipitation time series, is expected to decrease the AM performance, the archive inflation brought by the MTW is expected to contribute to an increase in performance.
+Therefore, if the reduction of the archive length needed by the MTW, due to the reduced availability of a sub-daily precipitation time series, is expected to decrease the AM performance, the archive inflation brought by the MTW is expected to contribute to an increase in performance.
 
-Other possibilities exist in order to increase the prediction skill of AMs.
+	Other possibilities exist for increasing the prediction skill of the AMs.
 A classical approach is to add new predictors or new successive levels of analogy \citep[see e.g.][]{Horton2012a, BenDaoud2016, Caillouet2016}.
@@
 Another possibility is to use a global optimization technique, such as genetic algorithms, in order to better optimize the method and to add new parameters \citep{Horton2016}.
-However, the MTW technique is not in competition with other approaches, but can be combined with these.
+However, the MTW technique is not in competition with other approaches and can be combined with these.
 Indeed, as most of them rely on the atmospheric circulation in the first level of analogy, the application of a MTW should lead to similar conclusions.
 
-Section \ref{sec:data_methods} presents the context of the study as well as data and methods, including the proposed MTW technique.
+	Section \ref{sec:data_methods} presents the context of the study as well as the data and methods, including the proposed MTW technique.
 The impact of the reduction of the archive and the improvements brought by the MTW are assessed in Sect.
 \ref{sec:results}.
-The benefit of introducing a MTW was assessed first in regards to the analogy criterion improvement (Sect.
-\ref{sec:influence_criteria}), and then in terms of precipitation prediction skill (Sect.
+The benefits of introducing a MTW were assessed first in regards to the analogy criterion improvement (Sect.
+\ref{sec:influence_criteria}) and then in terms of precipitation prediction skill (Sect.
 \ref{sec:influence_scores}).
 Finally, the results are discussed in Sect.
-\ref{sec:discussion} and the conclusions are found in Sect.
+\ref{sec:discussion}, and the conclusions are found in Sect.
 \ref{sec:conclusions}.
@@
 	The study area is the upper Rh\^{o}ne catchment in Switzerland.
-Precipitation time series come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle (Fig.
-\ref{fig:map}), which are subject to various meteorological influences \citep{Horton2012}.
-The data were available at an hourly time step on 25~years (1982 to 2007), and were also obtained at a daily time step (from 6~h~UTC to 6~h~UTC the next day) on 47~years (1961 to 2008).
+Precipitation time series come from six automatic weather stations, viz., Ulrichen, Zermatt, Visp, Montana, Sion, and Aigle (Fig.
+\ref{fig:map}) that are subject to various meteorological influences \citep{Horton2012}.
+The data were available at an hourly time step for 25~years (1982 to 2007) and were also obtained at a daily time step (from 6~h~UTC to 6~h~UTC the next day) for 47~years (1961 to 2008).
 Due to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed.
-The results will thereafter be presented arbitrarily for the Ulrichen station, but were equivalent for all stations.
+The results will hereafter be presented arbitrarily for the Ulrichen station but are equivalent for all stations.
 
-Synoptic-scale variables, used as predictors, were extracted from the NCEP/NCAR reanalysis I dataset \citep{Kalnay1996} with a 6-hourly temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree.
+	Synoptic-scale variables, used as predictors, were extracted from the NCEP/NCAR reanalysis I dataset \citep{Kalnay1996} with a 6-hour temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree.
 This dataset is now relatively old, but it is not expected to affect the conclusions of the present study (see discussion in Sect.
@@
 
-\subsection{The considered analog method}
+	\subsection{The considered analogue method}
 	\label{sec:analog_method}
@@
 	The first considered AM is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005, Marty2012}.
-Searching for analog situations to a target day starts by a seasonal stratification through a preselection step of the potential candidates for analogy.
-The restriction is here a search for analog days within a 4 months window centered on the target date, for every year of the archive.
-Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1), which is a comparison of gradients, on geopotential heights over a certain spatial window and at certain hours.
-The smaller the S1 values, the more similar the pressure fields.
+Searching for analogue situations to a target day starts by a seasonal stratification through a preselection step of the potential candidates for analogy.
+The restriction is a search for analogue days within a 4-month window centred on the target date for every year of the archive.
+The similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1) that is a comparison of gradients on geopotential heights over a certain spatial window and at certain hours.
+With smaller S1 values, there is greater similarity in the pressure fields.
 
-The predictor variables, extracted from reanalysis datasets, are considered at different hours of the day.
-Based on \citet{Bontron2005}, geopotential heights are thus compared at 1000~hPa (Z1000) at 12~h~UTC and 500~hPa (Z500) at 24~h~UTC.
+	The predictor variables extracted from reanalysis datasets are considered at different hours of the day.
+Based on \citet{Bontron2005}, geopotential heights are compared at 1000~hPa (Z1000) at 12~h~UTC and 500~hPa (Z500) at 24~h~UTC.
 The time of the day at which the predictors are selected is found by \citet{Bontron2004} to have a significant influence.
 
-Then, $N_{1}$ dates with the lowest values of S1 are considered as analogs to the target day, $N_{1}$ being a parameter to calibrate (see Sect.
+	Then, $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day, $N_{1}$ being a parameter to calibrate (see Sect.
 \ref{sec:calibration}).
 Finally, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day.
-This method will be named 2Z further on.
+This method will be named 2Z.
 
-The second reference method (2Z-2MI, Table \ref{table:method_2Z-2MI}) adds a subsequent level of analogy on moisture variables, compared by means of the root-mean-square error (RMSE).
-The additional predictor is a moisture index made of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850) \citep{Bontron2004}.
-When adding a second level of analogy, $N_{2}$ dates are subsampled from the $N_{1}$ analogs on the atmospheric circulation, to end up with a smaller number of analog situations.
-When a second level of analogy is added, a higher number of $N_{1}$ analogs is kept on the first level.
+	The second reference method (2Z-2MI, Table \ref{table:method_2Z-2MI}) adds a subsequent level of analogy with moisture variables, compared by means of the root-mean-square error (RMSE).
+The additional predictor is a moisture index composed of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850) \citep{Bontron2004}.
+When adding a second level of analogy, $N_{2}$ dates are subsampled from the $N_{1}$ analogues on the atmospheric circulation, resulting in a smaller number of analogue situations.
+When a second level of analogy is added, a higher number of $N_{1}$ analogues is kept on the first level.
 
-More complex AMs exist, with additional predictors \citep[see e.g.][]{Horton2012a, BenDaoud2016, Caillouet2016}.
-The MTW can also be applied on these, as they generally rely on a similarity of the atmospheric circulation in the first level of analogy, but it is easier to interpret the impact of the MTW on more basic methods.
+	More complex AMs exist with additional predictors \citep[see e.g.][]{Horton2012a, BenDaoud2016, Caillouet2016}.
+The MTW can also be applied to these, as they generally rely on a similarity of the atmospheric circulation in the first level of analogy.
+However, it is easier to interpret the impact of the MTW using more basic methods.
 
@@
 	In order to assess the performance of AMs, the continuous ranked probability score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} is often employed \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}.
-It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$.
-The better the prediction, the smaller the score.
+It allows the evaluation of the predicted cumulative distribution functions $F(y)$ of the precipitation values $y$ from analogue situations compared to the observed value $y^{0}$.
+A better prediction has a smaller score.
 It is defined as follows:
@@
 	\end{equation}
-where $\text{H}(y-y^{0})$ is the Heaviside function that is null when $y-y^{0}<0$, and has the value 1 otherwise.
+	where $\text{H}(y-y^{0})$ is the Heaviside function that is null when $y-y^{0}<0$ and has the value of 1 otherwise.
 
-In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution (i.e.
-the distribution of all precipitation values from the corresponding archive) as the reference.
-The continuous ranked probability skill score (CRPSS) is thus defined as follows:
+	In order to compare the value of the score in regard to a reference, one often considers its skill score expression and uses the climatological distribution (i.e., the distribution of all precipitation values from the corresponding archive) as the reference.
+The continuous ranked probability skill score (CRPSS) is defined as follows:
 
@@
 	\end{equation}
-where $S_{\text{CRP}}^{r}$ is the $S_{\text{CRP}}$ value for the reference (climatological distribution) and $S_{\text{CRP}}^{p}$ would be the one for a perfect prediction (which implies $S_{\text{CRP}}^{p}~=~0$).
-A better prediction is characterized by an increase in CRPSS: $S_{\text{SCRP}}~=~1$ for a perfect prediction, and $S_{\text{SCRP}}~<~0$ for a prediction with a lower skill than the reference.
+	where $S_{\text{CRP}}^{r}$ is the $S_{\text{CRP}}$ value for the reference (climatological distribution) and $S_{\text{CRP}}^{p}$ is for a perfect prediction (which implies $S_{\text{CRP}}^{p}~=~0$).
+A better prediction is characterized by an increase in CRPSS: $S_{\text{SCRP}}~=~1$ for a perfect prediction and $S_{\text{SCRP}}~<~0$ for a prediction with a lower skill than the reference.
 
@@
 
-The moving time window (MTW) technique aims at finding better analog situations at different hours of the day rather than comparing the predictors at fixed hours.
-Thus, instead of looking for analogs at a 24-hourly time step, they are sought at the time step matching the predictor temporal resolution, which is here 6-hourly (Fig.
+	The moving time window (MTW) technique aims at finding better analogue situations at different hours of the day rather than comparing the predictors at fixed hours.
+Therefore, instead of looking for analogues at a 24-hourly time step, they are sought at the time step matching the predictor temporal resolution which is a 6-hour time step in this study (Fig.
 \ref{fig:principle}).
 
-The target situations and their corresponding observed precipitation values do not change, because the prediction is still established on a daily basis, for a fixed period of the target day (6~h~UTC to 6~h~UTC the next day), as before.
-The difference is that the candidates are 4~times more numerous (even though they are not fully independent).
-No constraint was added in order to restrict the selection of multiple analogs within the same candidate dates.
+	The target situations and their corresponding observed precipitation values do not change because the prediction is still established on a daily basis for a fixed period of the target day (6~h~UTC to 6~h~UTC the next day) as before.
+The difference is that the candidates are four times more numerous (even though they are not fully independent).
+No constraint was added in order to restrict the selection of multiple analogues within the same candidate dates.
 
-In order to assess the benefit of searching analog situations at a sub-daily time step, an appropriate precipitation series is required.
+	In order to assess the benefit of searching for analogue situations at a sub-daily time step, an appropriate precipitation series is required.
 On the basis of high temporal resolution time series (Sect.
-\ref{sec:data}), 24~h-totals were processed, but at a 6-hourly time step, by means of a moving 24~h-total.
-As sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~years archive (1961 to 2008) to 25~years (1982 to 2007) needs to be assessed.
+\ref{sec:data}), 24~h-totals were processed at a 6-hour time step by means of a moving 24~h-total.
+Since sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~year archive (1961 to 2008) to 25~years (1982 to 2007) needs to be assessed.
 
@@
 previous section).
-Thus, in order to reconstruct a longer archive of moving 24~h-totals, two simple disaggregation approaches of the daily precipitation time series were assessed.
+Therefore, in order to reconstruct a longer archive of moving 24~h-totals, two simple disaggregation approaches of the daily precipitation time series were assessed.
 
 	The first technique was a proportional distribution, where the observed daily precipitations were considered constant during the measuring period (6~h~UTC to 6~h~UTC the next day).
-It then consisted in allocating proportional parts of the original daily time series into a new moving average of 24~h-totals (Fig.
+Proportional parts of the original daily time series were allocated into a new moving average of 24~h-totals (Fig.
 \ref{fig:illustration_disaggregation}).
@@
 Data from the NCEP/NCAR reanalysis 1 (Sect.
-\ref{sec:data}) were used in this perspective, despite their rough resolution.
-Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and by allowing a time lapse between both series in order to take into account the significant distance separating the weather stations and the reanalysis grid point.
-The best proxy variable was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series on the period 1982-2007.
-Then, once the best proxy has been selected, its temporal profile was used in order to disaggregate the daily precipitation time series.
+\ref{sec:data}) were used for this purpose, despite their rough resolution.
+Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and a time lapse between both series was allowed to take into account the significant distance separating the weather stations and the reanalysis grid point.
+The best proxy variable was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series over the period 1982-2007.
+Once the best proxy had been selected, its temporal profile was used in order to disaggregate the daily precipitation time series.
 
-\subsection{Calibration of the analog method}
+	\subsection{Calibration of the analogue method}
 	\label{sec:calibration}
@@
 the atmospheric circulation or moisture index) are calibrated sequentially.
-The parameters calibrated by this approach, for every level of analogy, are the spatial windows on which the predictors are compared and the number of analogs.
+The parameters calibrated by this approach, for every level of analogy, are the spatial windows on which the predictors are compared and the number of analogues.
 The procedure consists of the following steps \citep{Bontron2004}:
@@
 			\item pressure level (e.g. 500 hPa, ...),
-		\item temporal window (hour of the day \textendash\ e.g. 6, or 12~h~UTC),
-		\item initial analog numbers (e.g. $N_{1}=50$).
+			\item temporal window (hour of the day \textendash\ e.g. 6 or 12~h~UTC),
+			\item initial analogue numbers (e.g. $N_{1}=50$).
 		\end{enumerate}
@@
 		\begin{enumerate}
-		\item Identification of the most skilled unitary cell (1~point for moisture variables and 4 for the geopotential height when using the S1 criterion) over a large domain.
-Every point (or cell) of the full domain is assessed on all predictors of the level of analogy, jointly (consisting generally of the same variable, but on different pressure levels and at different hours).
+			\item Identification of the most skilled unitary cell (one point for moisture variables and four for the geopotential height when using the S1 criterion) over a large domain.
+Every point (or cell) of the full domain is assessed on all predictors of the level of analogy, jointly (consisting generally of the same variable but on different pressure levels and at different hours).
 			\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain.
-The spatial window grows up by repeating the previous steps, until no improvement is reached.
-		\item The number of analog situations is then reconsidered and optimized for the current level of analogy.
+The spatial window grows by repeating the previous steps until no improvement is reached.
+			\item The number of analogue situations is then reconsidered and optimized for the current level of analogy.
 		\end{enumerate}
 		\item A new level of analogy can then be added, based on other variables (such as the moisture index) at chosen pressure levels and hours of the day.
-The number of analogs for the next level of analogy is initiated at a chosen value.
-Then, the procedure starts again from step (2) for the new level.
-The parameters calibrated on the previous analog levels are fixed and do not change.
-	\item Finally, the numbers of analogs for the different levels of analogy are re-assessed. This is done iteratively by varying the number of analogs of each level in a systematic way.
+The number of analogues for the next level of analogy is initiated at a chosen value.
+The procedure starts again from step 2 (calibration of the spatial window and the number of analogues) for the new level.
+The parameters calibrated on the previous analogue levels are fixed and do not change.
+		\item Finally, the numbers of analogues for the different levels of analogy are reassessed. This is done iteratively by varying the number of analogues of each level in a systematic way.
 	\end{enumerate}
 
-The calibration is thus done in successive steps, on a limited number of parameters.
-Previously calibrated parameters are generally not reassessed (except for the number of analogs).
-More advanced techniques, such as using genetic algorithms \citep{Horton2016}, exist, but are out of the scope of the present study.
+	The calibration is done in successive steps with a limited number of parameters.
+Previously calibrated parameters are generally not reassessed (except for the number of analogues).
+More advanced techniques, such as using genetic algorithms \citep{Horton2016}, exist but are out of the scope of the present study.
 
@@
 
-The performance loss resulting from the reduction of a 47~years archive (1961 to 2008, corresponding to the daily time series) to 25~years (1982 to 2007, corresponding to the hourly time series, see Sect.
-\ref{sec:mtw}) was assessed with the original method, without MTW.
+	The performance loss resulting from the reduction of a 47~year archive (1961 to 2008, corresponding to the daily time series) to 25~years (1982 to 2007, corresponding to the hourly time series in Sect.
+\ref{sec:mtw}) was assessed with the original method without MTW.
 Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
-The AM parameters were calibrated on the original archive (see resulting analog numbers in Tables \ref{table:analog_nb}) and were used thereafter.
+The AM parameters were calibrated on the original archive (see resulting analogue numbers in Tables \ref{table:analog_nb}) and were used thereafter.
 
@@
 \ref{fig:plots_CRPSS_2Z-2MI} for the 2Z-2MI method.
-As expected, a loss of performance could be observed for each station, except for that of Aigle, which seemed relatively indifferent to this change.
+As expected, a loss of performance was observed for each station, except for that of Aigle, which seemed relatively indifferent to this change.
 This loss was globally significant, with up to -1.89 points for Visp and the 2Z method.
@@
 
-When searching for analogs in the first level of analogy, such as on the geopotential heights in the 2Z method (Sect.
-\ref{sec:analog_method}), there are 4 times more candidates (even though not fully independent) with the MTW than before (Sect.
+	When searching for analogues in the first level of analogy, such as on the geopotential heights in the 2Z method (Sect.
+\ref{sec:analog_method}), there are four times more candidates (even though not fully independent) with the MTW than before (Sect.
 \ref{sec:mtw}).
-Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions of the analogy criterion (S1) for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analog rank at the Ulrichen station on the whole calibration period (1961-2008 -- the full period could be used here, as precipitation were not considered at this stage), due to introduction of the MTW.
-The shape of the distributions of the conventional approach and the MTW were found to be similar, but the values of the analogy criterion were reduced (shifted to the left), and were therefore better.
-For analogs with higher ranks (e.g.
-$20^{th}$ or $40^{th}$), the difference between the two distributions was larger than for the first ranks, which means that the improvement increased with the rank of the analogs.
+Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions of the analogy criterion (S1) for the $1^{st}$, $5^{th}$, $20^{th}$, and $40^{th}$ analogue rank at the Ulrichen station over the whole calibration period (1961-2008 -- the full period could be used here, as precipitation was not considered at this stage), due to introduction of the MTW.
+The shape of the distributions of the conventional approach and the MTW were found to be similar, but the values of the analogy criterion were reduced (shifted to the left) and were, therefore, better.
+For analogues with higher ranks (e.g.
+$20^{th}$ or $40^{th}$), the difference between the two distributions was larger than for the first ranks, which means that the improvement increased with the rank of the analogues.
 
-The improvements of the S1 criterion with the rank of the analogs are summarized in Fig.
-\ref{fig:changes_S1}, which shows (top) quantiles of the S1 criterion for the conventional method and the MTW, and (bottom) quantiles of the relative reduction (meaning improvement) due to the MTW.
-This confirms that all quantiles were similarly reduced (S1 distributions keep their shape), and that this improvement was constantly increasing from the first to the last analog (Fig.
+	The improvements of the S1 criterion with the rank of the analogues are summarized in Fig.
+\ref{fig:changes_S1}, which shows (top) quantiles of the S1 criterion for the conventional method and the MTW and (bottom) quantiles of the relative reduction (meaning improvement) due to the MTW.
+This confirms that all quantiles were similarly reduced (S1 distributions keep their shape), and that this improvement was constantly increasing from the first to the last analogue (Fig.
 \ref{fig:changes_S1} bottom).
 
-\subsubsection{Changes per precipitation classes}
+	\subsubsection{Changes per precipitation class}
 	\label{sec:influence_precip}
 
-The impact of the MTW on the analogy criterion has been analyzed per precipitation classes (for the target day).
-The results are summarized in Fig.
-\ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for days with precipitation (organized into classes) between two thresholds.
-The number of cases per class being reduced, the curves are not as smooth as in previous analyzes.
-It is nevertheless clear that the improvement were more important on days with higher precipitation.
+	The impact of the MTW on the analogy criterion has been analysed per precipitation classes (for the target day).
+The results are summarised in Fig.
+\ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for the days with precipitation (organized into classes) between two thresholds.
+With the number of cases per class being reduced, the curves are not as smooth as in previous analyses.
+It is nevertheless clear that the improvements were larger on days with higher precipitation.
 Once again, the results for the other stations were similar.
@@
 
-Atmospheric dynamics varies greatly from one season to another, which reflects on the performance of the AM that is generally lower between June and August \citep{Bliefernicht2010}.
+	Atmospheric dynamics vary greatly from one season to another, reflecting on the performance of the AM that is generally lower between June and August \citep{Bliefernicht2010}.
 The effect of the MTW on the S1 criterion per season is presented in Fig.
@@
 
-When adding the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations did not increase, as they were conditioned by the $N_{1}$ previously selected analogs, but their dates have changed.
-In contrast to the AM on the atmospheric circulation only, both a reduction or an increase of the RMSE analogy criterion values were possible here with the MTW compared to the static approach.
+	When adding the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations did not increase, as they were conditioned by the $N_{1}$ previously selected analogues, but their dates had changed.
+In contrast to the AM on the atmospheric circulation only, both a reduction or an increase of the RMSE analogy criterion values were possible with the MTW compared to the static approach.
 Indeed, Fig.
 \ref{fig:changes_RMSE} shows an almost insignificant improvement of the RMSE values.
-Unlike for the first level of analogy, the relative changes of the RMSE values were distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
+Unlike the first level of analogy, the relative changes of the RMSE values were distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
 
-\subsection{Impact on the prediction relevance}
+	\subsection{Impact on prediction skill}
 	\label{sec:influence_scores}
@@
 	The new performance scores (CRPSS) are provided in Fig.
-\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI} for the 2Z and 2Z-2MI methods respectively, on the reduced archive (1982--2007).
-The gains, relatively to the static approach on the same archive, ranged from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.
+\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI} for the 2Z and 2Z-2MI methods, respectively, for the reduced archive (1982--2007).
+The gains relative to the static approach on the same archive ranged from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.
 
@@
 
-The S1 criterion was previously found to be improved to a greater extent for higher precipitation values (Sect.
+	The S1 criterion was previously found to show greater improvement for higher precipitation values (Sect.
 \ref{sec:influence_precip}).
-The changes in terms of performance scores were then also assessed per precipitation classes.
+The changes in terms of performance scores were also assessed for the precipitation classes.
 Fig.
-\ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, the other stations having the same behavior.
+\ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, with the other stations having the same behaviour.
 The performance score was improved for days with higher precipitation after the introduction of the MTW.
-On the contrary, non-rainy days and small precipitation values were not improved.
+In contrast, for non-rainy days and small precipitation values, the performance scores were not improved.
 
-\subsubsection{Recalibration of the AM parameters}
+	\subsubsection{Recalibration of AM parameters}
 	\label{sec:recalibration}
@@
 The calibration (see Sect.
-\ref{sec:calibration}) has then been reprocessed.
+\ref{sec:calibration}) should then be reprocessed.
 
-After recalibrating, changes in the AM parameters could be observed for both 2Z and 2Z-2MI methods.
-Among these, the zonal extent of the spatial windows of the circulation analogy decrease a bit (not shown).
-More significantly, the optimal number of analogs increased after introducing the MTW, of a considerable order of magnitude: 25~\% to 83~\% for the 2Z method, and 20~\% to 67~\% for the final selection of the 2Z-2MI method (Table \ref{table:analog_nb}).
-The number of analogs of the first analogy level of the 2Z-2MI method even reached three times its previous value for the Visp station.
+	After recalibrating, changes in the AM parameters could be observed for both the 2Z and 2Z-2MI methods.
+Among these, the zonal extent of the spatial windows of the circulation analogy decreased slightly (not shown).
+More significantly, the optimal number of analogues increased after introducing the MTW by a considerable magnitude: 25~\% to 83~\% for the 2Z method and 20~\% to 67~\% for the final selection of the 2Z-2MI method (Table \ref{table:analog_nb}).
+The number of analogues of the first analogy level of the 2Z-2MI method reached three times its previous value for the Visp station.
 
@@
 \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}) have significantly increased after recalibration.
-When analyzing the change in performance per precipitation classes, the results (not shown) were very similar to what was observed in Sect.
-\ref{sec:improvement_CRPSS_precip_threshold}, with a slight performance increase of small precipitation values that can be observed at the expense of higher amounts.
+When analysing the change in performance per precipitation class, the results (not shown) were very similar to the observations in Sect.
+\ref{sec:improvement_CRPSS_precip_threshold}, with a slight performance increase for small precipitation values that can be observed at the expense of higher amounts, due to the higher number of analogues.
 
@@
 
-When using the first reconstructed time series (on the reduced period), based on the proportional distribution (see Sect.
+	When using the first reconstructed time series (for the reduced period) based on the proportional distribution (see Sect.
 \ref{sec:reconstruction}), the AM performance was degraded and was even below the conventional method without MTW (Table \ref{table:disaggregation_proportional} to compare to Fig.
@@
 
-For the second approach, the synoptic proxy to use for the temporal disaggregation of the daily time series had to be identified first.
+	For the second approach, the synoptic proxy for the temporal disaggregation of the daily time series had to be identified first.
 The results are illustrated this time for the Zermatt station.
-Amongst the considered moisture variables (see Sect.
-\ref{sec:reconstruction}), the best proxy was the precipitable water at 45° N and 7.5° E, with a time offset of -6~h (Table \ref{table:proxy_correlations}).
+Among the considered moisture variables (see Sect.
+\ref{sec:reconstruction}), the best proxy was the precipitable water at 45° N and 7.5° E, with a time offset of 6~h (Table \ref{table:proxy_correlations}).
 Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the disaggregated series using the proxy of precipitable water.
@@
 
-\subsection{Improvement of the selection of analog situations}
+	\subsection{Improvement of the selection of analogue situations}
 
-On the first level of analogy, the improvement of the S1 criterion (Fig.
-\ref{fig:changes_S1} bottom) started approximately at 5~\% for the first analog and reached more than 10~\% for the last one (Sect.
+	For the first level of analogy, the improvement of the S1 criterion (Fig.
+\ref{fig:changes_S1} bottom) started approximately at 5~\% for the first analogue and reached more than 10~\% for the last (Sect.
 \ref{sec:perf_2Z}).
-This increase of improvements with the analog rank can be explained by the accumulation of better analogs in the selection.
-The curve representing the minimum improvement is quickly slightly superior to zero, meaning that the criteria have been improved on most analog ranks for every day of the calibration period.
-All other stations had a similar improvement of the S1 criterion, both in terms of the distribution shape and amplitude.
-The introduction of the MTW allowed finding better analog situations in the first level of analogy, resulting in a selection of days with more similar atmospheric circulation.
+This increase in improvement with the analogue rank can be explained by the accumulation of better analogues in the selection.
+The curve representing the minimum improvement is mostly superior to zero, meaning that the criteria have been improved on most analogue ranks for every day of the calibration period.
+All other stations had a similar improvement in the S1 criterion, both in terms of the distribution shape and amplitude.
+The introduction of the MTW allowed finding better analogue situations in the first level of analogy, resulting in a selection of days with better similarity in atmospheric circulation.
 
-When adding a second level of analogy on moisture variables, the criteria values (RMSE) were not improved by the MTW (Sect.
+	When adding a second level of analogy with moisture variables, the criteria values (RMSE) were not improved by the MTW (Sect.
 \ref{sec:perf_2Z-2MI}), as the number of candidates was not higher (still the $N_{1}$ days selected in the first level of analogy).
 However, this result of a globally null improvement of the RMSE values does not mean that the 2Z-2MI method cannot be improved by the MTW.
-It means that after the selection of the analog situations in terms of the synoptic circulation, the new candidate dates did not allow to find better analogs in terms of moisture.
-However, the selected dates have changed in the first level of analogy, and thus also in the final selection, which did improve the prediction skill (Sect.
+It means that after the selection of the analogue situations for the synoptic circulation, the new candidate dates did not provide better analogues in terms of moisture.
+However, the selected dates have changed in the first level of analogy and also in the final selection, and thus the distributions of precipitation values were different, which did improve the prediction skill (Sect.
 \ref{sec:influence_scores}).
 
-\subsection{Improvement of the precipitation prediction}
+	\subsection{Improvement of precipitation prediction}
 
@@
 Moreover, it required no additional predictor.
-With the introduction of the MTW, the performance loss related to the reduction of the archive length was compensated.
-It was here of the same order of magnitude as if the length of the archive doubled.
-Note that despite the number of candidate situations being four times higher, the gains seem to be lower than for a quadrupled archive length.
-The likely reason is that an actual longer archive would contain more atmospheric situations that might have been less observed on a shorter period.
+With the introduction of the MTW, the performance loss related to the reduction of the archive length was negated.
+It was in this case of the same magnitude as if the length of the archive doubled.
+Note, that despite the number of candidate situations being four times higher, the gains seem to be lower than for a quadrupled archive length.
+The likely reason is that an actual longer archive would contain more atmospheric situations that might have been observed less frequently during a shorter period.
 Moreover, high correlations between sub-daily circulation patterns are expected.
-The MTW thus did not create four times more independent data, but the increase in information was nevertheless substantial.
+The MTW, therefore, did not create four times more independent data, but the increase in information was nevertheless substantial.
 In this regards, a reanalysis dataset with a higher temporal resolution might not improve the performance significantly more than a 6-hourly dataset.
-On the other hand, reducing the MTW to a 12-hourly time step might reduce redundancy in the archive, but might also reduce the chance of finding better analog situations, as circulation patterns can evolve substantially in 12~hours.
+In contrast, reducing the MTW to a 12-hour time step might reduce redundancy in the archive, but might also reduce the chance of finding better analogue situations, as circulation patterns can evolve substantially in 12~hours.
 
-Moreover, in a transient climate, an eventual non-stationarity of the link between predictors and precipitation might discard the relevance of analogs from far in the past, and thus increase the relevance of using a more recent and shorter archive rather than a long one.
-In such case, the archive inflation brought by the MTW is also relevant.
+	Moreover, in a transient climate, an eventual nonstationarity of the link between predictors and precipitation might discard the relevance of analogues from the distant past and increase the relevance of using a more recent and shorter archive rather than a long one.
+In such cases, the archive inflation brought by the MTW is also relevant.
 
@@
 This is likely due to the fact that higher precipitation events are a consequence of atmospheric conditions with greater dynamics, such as weather disturbances, which have a well-marked temporal evolution.
-Indeed, the position of the driving elements such as the low-pressure center and the fronts change significantly during a day.
-Moreover, these situations are less numerous than anticyclonic situations, which makes it less likely to find very good analogs at the same time of the day.
-We can therefore expect to improve more significantly these situations with greater dynamics when introducing a MTW, as better matches to the target situation may be found.
-On the opposite, days with low dynamics of the atmospheric circulation, such as anticyclonic situations, will not be radically improved by the introduction of the MTW.
+Indeed, the position of the driving elements, such as the low pressure centres and the fronts, change significantly during a day.
+These situations are less numerous than anticyclonic situations, which makes it less likely to find very good analogues at the same time of the day.
+We can, therefore, expect to improve these situations with greater dynamics more significantly when introducing a MTW, as better matches to the target situation may be found.
+In contrast, days with low dynamics in the atmospheric circulation, such as anticyclonic situations, will not be radically improved by the introduction of the MTW.
 
-We just mentioned that the MTW improved the prediction of days with heavier precipitation.
-However, it will have no effect on the prediction of extreme events that were not yet observed, and therefore are not present in the archive.
-Extremes in AMs can be modeled e.g.
-by extrapolation of a truncated exponential or gamma distribution fitted on the analog values \citep{Obled2002}.
+	We just mentioned that the MTW improved the prediction for days with heavier precipitation.
+However, it will have no effect on the prediction of extreme events that were not yet observed and are, therefore, not present in the archive.
+The extremes in AMs can be modelled by, for example, extrapolation of a truncated exponential or gamma distribution fitted to the analogue values \citep{Obled2002}.
 Another possible approach is by combining AMs with other methods \citep[e.g.][]{Chardon2014}.
@@
 	Section \ref{sec:seasonal_effect} and Fig.
-\ref{fig:changes_S1_seasons} revealed a difference of the improvement of the S1 criterion according to the season, with greater improvements for winter than summer.
-One hypothesis is that the diurnal effects of the summer months have an influence on the atmospheric circulation, at least in the lower layers.
-This effect is in phase with the daily cycle and good analogs are essentially found for the same hours.
+\ref{fig:changes_S1_seasons} revealed a difference in the improvement of the S1 criterion according to the season, with greater improvements for winter than summer.
+One hypothesis is that the diurnal effects of the summer months have an influence on the atmospheric circulation at least in the lower layers.
+This effect is in phase with the daily cycle, and good analogues are essentially found for the same hours.
 
@@
 \ref{fig:hours_selection_per_season}).
-It was found that the new choice of the temporal window in winter, when using the MTW approach, is well balanced between the 4 options.
-This means a change of 75\% of the analogs selection compared to the conventional approach.
-On the contrary, days in summer months had a preference for the initial temporal window (Z500 24~h \& Z1000 12~h), likely due to more pronounced diurnal effects which reduces the potential for improvement of the criteria.
-Other seasons were between these two extremes, which is consistent with their respective improvements.
-This seasonal effect was observed for each station in a very similar way, and generally even with a slightly larger amplitude than for Ulrichen.
+It was found that the new choice of the temporal window in winter, when using the MTW approach, is well balanced between the four options.
+This means a change of 75~\% of the analogues selected compared to the conventional approach.
+On the contrary, the days during the summer months had a preference for the initial temporal window (Z500 24~h \& Z1000 12~h), likely due to more pronounced diurnal effects, which reduced the potential for improvement of the criteria.
+The other seasons were between these two extremes, which is consistent with their respective improvements.
+This seasonal effect was observed for each station in a very similar way and even with slightly larger amplitude than for Ulrichen.
 
-\subsection{On the increase in number of analogs}
+	\subsection{On the increase in the number of analogues}
 
-After the recalibration of the AMs with the MTW, the optimal analog numbers were significantly higher than in the original methods (see Sect.
+	After the recalibration of the AMs with the MTW, the optimal analogue numbers were significantly higher than in the original methods (see Sect.
 \ref{sec:recalibration} and Fig.
 \ref{table:analog_nb}).
-As we saw in Fig.
-\ref{fig:changes_S1}, the improvement of the S1 criterion grew along with the rank of the analog, which shows an accumulation of better analog situations in the distributions.
-It seems thus profitable to widen the selection of analogs in order to also keep some whose rank has increased, as they appear to be also relevant to predict precipitation values.
-The number of good analogs was thus globally increased.
+As shown in Fig.
+\ref{fig:changes_S1}, the improvement of the S1 criterion grew along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions.
+It seems profitable to widen the selection of analogues in order to also keep some whose rank has increased, as they appear to be relevant to the prediction of the precipitation values.
+The number of good analogues was globally increased.
 
-A higher number of analogs generally means, with an archive of fixed length, a poorer analogy.
-Indeed, when the choice of the predictors or the parameters are improved, leading to a better prediction, the optimal number of analog situations decreases.
-However, when the length of the archive increases, the optimal number of analogs increases too, for a better performance, up to a certain threshold (\citealt{Bontron2004}, see also Fig.
-7 of \citealt{Hamill2006a}).
-The observed increase in the number of analog situations with the MTW resulted in better performance skills for a given method, as it can be seen as an inflation of the archive.
-However, if new relevant predictors were added to the method, the number of analogs would then decrease.
+	A higher number of analogues generally means, with an archive of fixed length, a poorer analogy.
+Indeed, when the choice of the predictors or the parameters are improved, leading to a better prediction, the optimal number of analogue situations decreases.
+However, when the length of the archive increases, the optimal number of analogues increases too for a better performance up to a certain threshold \citep[][]{Bontron2004, Hamill2006a }.
+The observed increase in the number of analogue situations with the MTW resulted in better performance skills for a given method, as it can be seen as an inflation of the archive.
+However, if new relevant predictors were added to the method, the number of analogues would then decrease.
 
-\subsection{Why not just making a 6-hourly predictions ?}
+	\subsection{Why not just make 6-hourly predictions?}
 
 	One can question the interest of using moving daily totals when 6-hourly precipitation series can be predicted instead.
-A first reason is that the 6-hourly time series generated by the AM might not represent accurately the intra-daily precipitation distribution (results not shown).
-Also, sometimes one just does not need finer resolution than the daily time step, eventually using another disaggregation technique afterwards.
-Finally, when using a reconstructed precipitation archive, the errors in intra-day precipitation distributions have a lesser impact over 24~h daily totals.
+However, the 6-hourly time series generated by the AM might not represent accurately the intra-daily precipitation distribution (results not shown).
+In addition, sometimes a resolution finer than the daily time step is not needed and another disaggregation technique may be used afterwards.
+Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact than 24~h daily totals.
 
@@
 	The considered reanalysis dataset, which is the NCEP/NCAR reanalysis I \citep{Kalnay1996}, is relatively old and has a coarse resolution.
-Newer reanalysis dataset could have been used to achieve this study, and might have resulted in higher performance scores.
+Newer reanalysis datasets could have been used in this study and might have resulted in higher performance scores.
 However, \cite{BenDaoud2009} showed that the sensitivity of the method to the reanalysis dataset is rather small.
 This is particularly true for simple AMs that mainly rely on the atmospheric circulation, which is already well defined at a coarser resolution.
-That might not be the case of more elaborated methods relying on thermodynamic data.
-A comparative analysis of several reanalysis dataset within the AM is under work and will be the topic of a dedicated paper.
+That might not be the case in more elaborate methods relying on thermodynamic data.
+A comparative analysis of several reanalysis datasets within the AM is being conducted and will be the topic of a dedicated study.
 
 	Moreover, one can assume that the gain observed here by introducing a MTW should also be found for a better reanalysis dataset.
-Indeed, a better dataset does not negatively influence the fact that one can find better analog situations at other hours of the day rather than at fixed hours.
+Indeed, a better dataset does not negatively influence the fact that one can find better analogue situations at other hours of the day rather than at fixed hours.
 
@@
 	These attempts to transpose the MTW on the total archive highlighted the importance of the actual rainfall chronology.
-The MTW is profitable, provided that the precipitation series are close to the observed one.
-Without precipitation series with an accurate sub-daily chronology, the introduction of a MTW does not improve the precipitation prediction.
+The MTW is beneficial, provided that the precipitation series are close to the observed one.
+Without a precipitation series with an accurate sub-daily chronology, the introduction of a MTW does not improve the precipitation prediction.
 
@@
 
-AMs are most often based on a daily time step, due to the availability of long precipitation archives.
-However, it is unlikely that two analog synoptic situations, that evolve relatively quickly, would correspond optimally at the same hours of the day.
-It is thus probable that better matches can be found at another time, which can change the selection of the analogs dates.
+	The AMs are most often based on a daily time step due to the availability of long precipitation archives.
+However, it is unlikely that two analogue synoptic situations, that evolve relatively quickly, would correspond optimally at the same hours of the day.
+It is probable that better matches can be found at another time, which can change the selection of the analogue dates.
 
-As \citet{Finet2008} had previously shown, the introduction of a MTW allows finding better analog situations in terms of the atmospheric circulation.
-It has been here demonstrated that the improvement of the S1 criterion values was growing with the rank of the analog.
-This was due to the accumulation of better analogs within the predicted distributions.
+	As \citet{Finet2008} had previously shown, the introduction of a MTW allows finding better analogue situations in terms of the atmospheric circulation.
+It has been demonstrated in this study that the improvement of the S1 criterion values was growing with the rank of the analogue.
+This was due to the accumulation of better analogues within the predicted distributions.
 
@@
 These situations have more specific circulation patterns that are evolving more rapidly.
-Thus, a MTW was found to be of particular interest in this kind of situation, and benefits the prediction of heavier precipitation events.
+Therefore, a MTW was found to be of particular interest in this kind of situation, benefiting the prediction of heavier precipitation events.
 
-A seasonal effect has been highlighted, as the MTW was more profitable for winter months than summer.
-The reason is likely that the diurnal cycle has a bigger effect in summer than in winter, which results in better analogs at the same time of the day.
-The preference for the same hours in summer has been demonstrated, whereas 75\% of the analog situations were selected at a different time in winter.
+	A seasonal effect has been highlighted, as the MTW was more profitable for winter than summer.
+The reason is likely that the diurnal cycle has a bigger effect in summer than in winter which results in better analogues at the same time of the day.
+The preference for the same hours in summer has been demonstrated; whereas, 75~\% of the analogue situations were selected at a different time in winter.
 
-The impact of the MTW on the prediction skill has never been assessed before, due to the shortcoming of long precipitation series at a sub-daily time step.
-It was here assessed on a 25 years time series with a high temporal resolution.
-After the introduction of the MTW, the performance scores increased of the same order of magnitude as if the length of the archive doubled, in this case study.
+	The impact of the MTW on the prediction skill was never assessed before due to the shortcoming of long precipitation series at a sub-daily time step.
+Here, it was assessed for a 25~year time series with a high temporal resolution.
+After the introduction of the MTW, the performance scores increased at the same magnitude as if the length of the archive doubled.
 
 	The parameters were then calibrated again, using the MTW.
-Some parameters changed, the main difference being the number of analogs, which systematically and significantly increased compared to the original set.
-A wider selection of analog situations, containing those whose rank decreased, seemed profitable for the prediction performance.
-The number of good analogs was thus globally increased, in the same way as if the archive length increased.
-This change seems to benefit mainly the prediction of days with small precipitation totals.
+Some parameters changed, with the main difference being the number of analogues, which systematically and significantly increased compared to the original set.
+A wider selection of analogue situations, containing those whose rank decreased, seemed beneficial for the prediction performance.
+The number of good analogues was globally increased in the same way as if the archive length increased.
+This change seems to benefit the prediction of days with small precipitation totals.
 
-The importance of the quality of the precipitation archive was also demonstrated, as too simplistic reconstructions of 6-hourly time series lead to a loss of all the improvement brought by the MTW.
+	The importance of the quality of the precipitation archive was also demonstrated, as simplistic reconstructions of 6-hourly time series led to a loss of all the improvement brought by the MTW.
 The precipitation prediction is improved only when the precipitation chronology is close to the accurate one.
-Attempts to reconstruct longer time series based on a simplistic proportional distribution or using meteorological variables from the NCEP reanalysis 1 dataset as proxy did not succeed.
+Attempts to reconstruct longer time series based on simplistic proportional distributions or by using meteorological variables from the NCEP reanalysis 1 dataset as proxy did not succeed.
 Other reanalysis datasets with more accurate moisture variables could eventually perform better.
 
-Perspectives of using the MTW rely on the availability of long precipitation series at a sub-daily time step and with high accuracy.
-First, these archives of high temporal resolution precipitation data are increasing now with time.
-Another possible source of such archives is the establishment of precipitation reanalysis at a regional scale, or the use of reanalysis-driven RCMs (Regional Climate Models) or LAMs (Limited Area Models) on a long period.
-Even though outputs from these models might be biased or not accurate enough, information on the timing of the precipitation events could be useful in order to disaggregate stations time series.
-When precipitation data with accurate time distribution will be available, the use of a MTW in the AM can be considered for any application, and in any context, let it be operational forecasting or climate-related studies.
+	The use of the MTW relies on the availability of long precipitation series at a sub-daily time step and with high accuracy.
+First, these archives of high temporal resolution precipitation data are increasing over time.
+Another possible source of such archives is the establishment of precipitation reanalysis at a regional scale or the use of reanalysis-driven regional climate models or limited area models over a long period.
+Even though outputs from these models might be biased or not accurate enough, information regarding the timing of the precipitation events could be useful in disaggregating the station time series.
+When precipitation data with accurate time distributions are available, the use of a MTW in the AM can be considered for any application and in any context, including operational forecasting or climate-related studies.
 
 	\begin{acknowledgements}
-Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
+		We thank the Swiss Federal Office for Environment (FOEV), the Roads and Water Courses Service, Energy and Water Power Service of the Wallis Canton, and the Water, Land, and Sanitation Service of the Vaud Canton which financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project that started this research.
 Thanks to Dominique B\'{e}rod for his support.
@@
 
-The authors would also like to acknowledge the work anonymous reviewers, which contributed to improving this paper. 
+		The authors would also like to acknowledge the work of anonymous reviewers that contributed to improving this manuscript. 
 	\end{acknowledgements}
@@
 		\end{center}
-	\caption{Position of the 6 weather stations of interest (Ulrichen, Zermatt, Visp, Montana, Sion and Aigle) in the study area.}
+		\caption{Position of the six weather stations of interest (Ulrichen, Zermatt, Visp, Montana, Sion, and Aigle) in the study area.}
 		\label{fig:map}
@@
 		\end{center}
-	\caption{Illustration of the generation of 24~h-totals moving averages by means of a proportional distribution. The colours refer to the corresponding day of the daily time series.}
+		\caption{Illustration of the generation of 24~h total moving averages by means of a proportional distribution. The colours refer to the corresponding day of the daily time series.}
 		\label{fig:illustration_disaggregation}
@@
 		\includegraphics[width=8.3cm]{figures/plots_CRPSS_2Z.pdf}
-	\caption{Performance score (CRPSS, \%) of the AM on the atmospheric circulation, at the different stations, for (dashed) the full archive, i.e.
-1961-2008, (yellow) the reduced archive, i.e.
-1982-2007, (blue) the introduction of the MTW on the reduced archive, and (green) the recalibrated parameters of the AM with the MTW.}
+		\caption{Performance score (CRPSS, \%) of the AM on the atmospheric circulation at the different stations for (dashed) the full archive, i.e.
+1961-2008; (yellow) the reduced archive, i.e.
+1982-2007; (blue) the introduction of the MTW on the reduced archive; and (green) the recalibrated parameters of the AM with the MTW.}
 		\label{fig:plots_CRPSS_2Z}
@@
 		\includegraphics[width=8.3cm]{figures/plots_CRPSS_2Z-2MI.pdf}
-	\caption{Same as Figure \ref{fig:plots_CRPSS_2Z}, but for the analog method with a second level on the moisture variables.}
+		\caption{Same as Figure \ref{fig:plots_CRPSS_2Z}, but for the analogue method with a second level with the moisture variables.}
 		\label{fig:plots_CRPSS_2Z-2MI}
@@
 		\end{center}
-	\caption{Changes in the S1 criterion distributions, due to the MTW, of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$ and (d) $40^{th}$ analog ranks for the Ulrichen station.}
+		\caption{Changes in the S1 criterion distributions due to the MTW of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$, and (d) $40^{th}$ analogue ranks for the Ulrichen station.}
 		\label{fig:changes_S1_analogs}
@@
 		\end{center}
-	\caption{Synthesis of the changes in the S1 criterion, due to the MTW, for the Ulrichen station, depending on the rank of the analog.
+		\caption{Synthesis of the changes in the S1 criterion due to the MTW for the Ulrichen station depending on the rank of the analogue.
 (a) Quantiles of the S1 distributions with and without the MTW.
@@
 		\end{center}
-	\caption{Distribution of the median improvements of the S1 criterion, due to the MTW, depending on precipitation thresholds at the Ulrichen station.}
+		\caption{Distribution of the median improvements of the S1 criterion due to the MTW depending on precipitation thresholds at the Ulrichen station.}
 		\label{fig:changes_S1_precip_threshold}
@@
 		\end{center}
-	\caption{Seasonal effect on the median reduction of the S1 criterion for the Ulrichen station due to the MTW. DJF: winter, MAM: spring, JJA: summer SON: fall.}
+		\caption{Seasonal effect on the median reduction of the S1 criterion for the Ulrichen station due to the MTW. DJF: winter, MAM: spring, JJA: summer, and SON: fall.}
 		\label{fig:changes_S1_seasons}
@@
 		\end{center}
-	\caption{Synthesis of the changes in the RMSE criterion, due to the MTW, for the Ulrichen station, depending on the rank of the analog.
+		\caption{Synthesis of the changes in the RMSE criterion due to the MTW for the Ulrichen station depending on the rank of the analogue.
 (a) Quantiles of the RMSE distributions with and without the MTW.
@@
 		\includegraphics[width=5cm]{figures/changes_CRPS_precip_threshold.pdf}
-	\caption{Differences of the CRPSS performance score, due to the introduction of the MTW, as a function of precipitation thresholds at the Ulrichen station. The stars represent averages.}
+		\caption{Differences of the CRPSS performance score due to the introduction of the MTW as a function of precipitation thresholds at the Ulrichen station. The stars represent averages.}
 		\label{fig:changes_CRPS_precip_threshold}
@@
 		\includegraphics[width=8.3cm]{figures/hours_selection_per_season.pdf}
-	\caption{Distribution of the predictors hours in the selected analog dates depending on the season, for the Ulrichen station.}
+		\caption{Distribution of the predictor hours on the selected analogue dates depending on the season for the Ulrichen station.}
 		\label{fig:hours_selection_per_season}
@@
 	\begin{table}[htb]
-	\caption{Parameters of the reference method on the atmospheric circulation (2Z).
-The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window).
-The criterion used for the current level of analogy is then provided, as well as the number of analogs.}
+		\caption{Parameters for the reference method on the atmospheric circulation (2Z).
+The first column is the level of analogy (0 for preselection), the second column is the meteorological variable, and then its hour of observation (temporal window).
+The criterion used for the current level of analogy is then provided, as well as the number of analogues.}
 		\footnotesize
@@
 	\begin{table}[htb]
-	\caption{Number of analogs (of the first and the second level of analogy, respectively $N_{1}$ and $N_{2}$) of the method based on the atmospheric circulation only (method 2Z), and the one with a second level of analogy on moisture variables (2Z-2MI), on the full archive (Standard) and after recalibration using the MTW (MTW-r).}
+		\caption{Number of analogues (of the first and second level of analogy, respectively, $N_{1}$ and $N_{2}$) of the method based on the atmospheric circulation only (method 2Z), the method with a second level of analogy with moisture variables (2Z-2MI) on the full archive (Standard), and after recalibration using the MTW (MTW-r).}
 		\begin{center}
@@
 	\begin{table}[htb]
-	\caption{Value of the coefficient of determination between the reconstructed 6-hourly precipitation time series using the listed variables, and the accurate time series on the period 1982-2007.
-The grid points surrounding the region are the following: 1) 5° E, 47.5° N, 2) 5° E, 45° N, 3) 7.5° E, 47.5° N, 4) 7.5° E, 45° N.
+		\caption{Value of the coefficient of determination between the reconstructed 6-hourly precipitation time series using the listed variables and the accurate time series for the period 1982-2007.
+The grid points surrounding the region are: 1) 5° E, 47.5° N; 2) 5° E, 45° N; 3) 7.5° E, 47.5° N; and 4) 7.5° E, 45° N.
 The highest coefficient of determination is indicated in bold.}
@@
 	\begin{table}[htb]
-	\caption{Values of the CRPSS (\%) skill score for Zermatt, for the original and the recalibrated parameters (with the sequential method, as described in Sect.
+		\caption{Values of the CRPSS (\%) skill score for Zermatt for the original and the recalibrated parameters (with the sequential method, as described in Sect.
 \ref{sec:introduction}) using the MTW approach on the disaggregated precipitation time series (short and long periods) by means of variables from the reanalysis.}
@@
 	%%%
-%%% The different columns must be seperated with a & command and should
+	%%% The different columns must be separated with a & command and should
 	%%% end with \\ to identify the column brake.
@@
 	%%% Multiplication signs are typeset using the LaTeX commands \times (for vector products, grids, and exponential notations) or \cdot
-%%% The character * should not be applied as mutliplication sign
+	%%% The character * should not be applied as multiplication sign
 	%

### 2016-12-05 Moving temporal window - HESS/template.tex
Michel's corrections.

@@
 \usepackage[utf8]{inputenc}
+\usepackage{scrextend}
 
@@
 Multiple variations of the method exist \citep[a non-exhaustive listing can be found in][]{BenDaoud2016}.
-The AMs are used for operational precipitation forecasting, either in the context of flood forecasting or hydropower production \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as in precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}.
+The AMs are used for operational precipitation forecasting, either in the context of weather forecasting, flood forecasting, or hydropower production \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as in precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}.
 Other applications focus on temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectories of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
@@
 The restriction is a search for analogue days within a 4-month window centred on the target date for every year of the archive.
-The similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1) that is a comparison of gradients on geopotential heights over a certain spatial window and at certain hours.
+The similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1) that is a comparison of gradients on geopotential heights over a certain spatial window and at certain hours:
+
+	\begin{equation}
+	\label{eq:S1}
+	S_{1}=100 \frac {\displaystyle \sum_{i}^{m} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
+	{\displaystyle \sum_{i}^{m} max( \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert ) }
+	\end{equation}
+	where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points from the grid of the target situation, $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation, and $m$ is the number of pairs of adjacent points in the grid.
+The differences are processed separately in both directions.
 With smaller S1 values, there is greater similarity in the pressure fields.
@@
 
-	The second reference method (2Z-2MI, Table \ref{table:method_2Z-2MI}) adds a subsequent level of analogy with moisture variables, compared by means of the root-mean-square error (RMSE).
+	The second reference method (2Z-2MI, Table \ref{table:method_2Z-2MI}) adds a subsequent level of analogy with moisture variables, compared by means of the root-mean-square error (RMSE):
+
+	\begin{equation}
+	\label{eq:RMSE}
+	E_{RMS}= \sqrt[]{ \frac{1}{n} \sum_{i=1}^{n}(\hat{v}_{i} - v_{i})^{2}} 
+	\end{equation}
+	where $\hat{v}_{i}$ is the \textit{i}th predictor value from the grid of the target situation, $v_{i}$ is the corresponding observed value in the candidate situation, and $n$ is the number of points in the grid.
+
 	The additional predictor is a moisture index composed of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850) \citep{Bontron2004}.
@@
 Data from the NCEP/NCAR reanalysis 1 (Sect.
-\ref{sec:data}) were used for this purpose, despite their rough resolution.
+\ref{sec:data}) were used for this purpose, despite their rough resolution (2.5\degree).
 Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and a time lapse between both series was allowed to take into account the significant distance separating the weather stations and the reanalysis grid point.
@@
 The parameters calibrated by this approach, for every level of analogy, are the spatial windows on which the predictors are compared and the number of analogues.
-The procedure consists of the following steps \citep{Bontron2004}:
+The procedure, as defined by \citet{Bontron2004}, consists of the following steps:
 
@@
 As expected, a loss of performance was observed for each station, except for that of Aigle, which seemed relatively indifferent to this change.
-This loss was globally significant, with up to -1.89 points for Visp and the 2Z method.
+This loss was globally significant, with up to -1.89 points (\% of CRPSS) for Visp and the 2Z method.
 
@@
 \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI} for the 2Z and 2Z-2MI methods, respectively, for the reduced archive (1982--2007).
-The gains relative to the static approach on the same archive ranged from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.
+The gains relative to the static approach on the same archive ranged from 0.57 to 2.14 points (\% of CRPSS) for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.
 
@@
 Indeed, when the choice of the predictors or the parameters are improved, leading to a better prediction, the optimal number of analogue situations decreases.
-However, when the length of the archive increases, the optimal number of analogues increases too for a better performance up to a certain threshold \citep[][]{Bontron2004, Hamill2006a }.
+However, when the length of the archive increases, the optimal number of analogues increases too for a better performance up to a certain threshold \citep[][]{Bontron2004, Hamill2006a}.
 The observed increase in the number of analogue situations with the MTW resulted in better performance skills for a given method, as it can be seen as an inflation of the archive.
@@
 
+	\appendix
+	\section{Acronyms}    %% Appendix A
+
+	\begin{labeling}{2Z-2MI}
+		\item [2Z] Name of the analogue method of the atmospheric circulation
+		\item [2Z-2MI] Name of the analogue method composed of a first level on the atmospheric circulation and a second level on a moisture index
+		\item [AM] Analog method
+		\item [CRPS] Continuous ranked probability score
+		\item [CRPSS] Continuous ranked probability skill score
+		\item [MTW] Moving time window
+		\item [NCAR] National Center for Atmospheric Research
+		\item [NCEP] National Center for Environmental Prediction
+		\item [RH850] Relative humidity at 850 hPa
+		\item [RMSE] Root-mean-square error
+		\item [S1] Teweles and Wobus (1954) score
+		\item [TPW] Total precipitable water
+		\item [Z1000] Geopotential height at 1000 hPa
+		\item [Z500] Geopotential height at 500 hPa
+	\end{labeling}
+
 	\begin{acknowledgements}
@@
 		\end{center}
-		\caption{Illustration of the principle of a moving time window. The larger horizontal bars represent the 24~h precipitation totals.}
+		\caption{Illustration of the principle of a moving time window.
+The target situation is the same for the conventional approach and the MTW, while the candidate situations are four times more numerous with the MTW.
+The larger horizontal bars represent the 24~h precipitation totals.}
 		\label{fig:principle}

### 2016-12-05 Moving temporal window - HESS/template.tex
Obled's corrections.

@@
 The main reason is the use of daily precipitation time series due to the length of their available archives, and the unavailability of equivalent archives at a finer time step.
-However, it is unlikely for the best analogy to occur at the very same hour, as it may occur at a different time of day.
+However, it is unlikely for the best analogy to occur at the very same hour, while it may be found with a time shift of some hours as it may occur at a different time of day.
 In order to assess the potential for finding better analogues at a different hour, a moving time window (MTW) has been introduced on a reduced archive of hourly precipitation totals.
@@
 The prediction skill was found to have improved by the MTW, and even to a greater extent after recalibrating the AM parameters.
-Moreover, the improvement was greater for days with heavy precipitation, which are generally related to more dynamic atmospheric situations where timing is more specific and which are fewer in the archive.
+Moreover, the improvement was greater for days with heavy precipitation, which are generally related to more dynamic atmospheric situations where timing is more specific and which are fewer in the meteorological archive.
 
@@
 The assessed approaches were not successful, emphasizing the need to use time series with an appropriate chronology.
-These should be available in the near future, either by means of growing archives of measurements or by the establishment of regional precipitation reanalysis data.
+These should be available in the near future, either by means of growing archives of measurements or by the establishment of regional precipitation reanalysis data at sub-daily time step.
 The use of an MTW in the AM could then be considered for any application and in any context, may it be for operational forecasting or climate-related studies.
@@
 
-	\citet{Ruosteenoja1988} and \citet{Vandendool1994} have analysed the influence of the archive length on the quality of the analogy.
+	The method requires two different archives.
+The first is a meteorological archive describing the state of the atmosphere at a synoptic scale, such as reanalysis datasets.
+The second is an archive of the target variable to be forecast, here precipitation.
+This archive is made of precipitation cumulated over a certain time duration, most often daily but sometimes sub-daily, either at a target station or integrated over a target catchment.
+Obviously, the period to be used is limited to the smallest period common to the two archives.
+
+	\citet{Ruosteenoja1988} and \citet{Vandendool1994} have analysed the influence of the length of the meteorological archive on the quality of the analogy.
 They highlighted a three-way relationship between the quality of the analogy, the archive length, and the size of the spatial domain (or degrees of freedom): errors increase with a bigger domain, but decrease with a longer archive.
 They demonstrated that it is not possible to find good analogues over the whole northern hemisphere with a 100 year archive (and even for much higher orders of magnitude).
+Hopefully, it appears that for the aim of predicting precipitation over point stations or catchments of some 100 or 1000 km\texttwosuperior, there is no need to consider meteorological domains larger than 10\textdegree\ to 20\textdegree.
 For that reason, smaller spatial windows are always considered when searching for analogues, and the archive length is maximized.
@@
 \ref{sec:results}.
-The benefits of introducing a MTW were assessed first in regards to the analogy criterion improvement (Sect.
+The benefits of introducing a MTW were assessed first in regards to the analogy criterion improvement between synoptic situations (Sect.
 \ref{sec:influence_criteria}) and then in terms of precipitation prediction skill (Sect.
@@
 
-	The moving time window (MTW) technique aims at finding better analogue situations at different hours of the day rather than comparing the predictors at fixed hours.
+	The moving time window (MTW) technique aims at finding better analogue situations at different hours of the day rather than comparing the predictors at the same fixed hours.
+If the target situation is kept at 12 and 24~h~UTC for Z1000 and Z500 respectively, candidate situations are not only considered at 12 and 24~h~UTC, but at other hours by allowing a time shift.
 Therefore, instead of looking for analogues at a 24-hourly time step, they are sought at the time step matching the predictor temporal resolution which is a 6-hour time step in this study (Fig.
@@
 	The target situations and their corresponding observed precipitation values do not change because the prediction is still established on a daily basis for a fixed period of the target day (6~h~UTC to 6~h~UTC the next day) as before.
-The difference is that the candidates are four times more numerous (even though they are not fully independent).
+The difference is that the candidates are four times as many (even though they are not fully independent) as in the conventional approach.
 No constraint was added in order to restrict the selection of multiple analogues within the same candidate dates.
@@
 \ref{sec:data}), 24~h-totals were processed at a 6-hour time step by means of a moving 24~h-total.
-Since sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~year archive (1961 to 2008) to 25~years (1982 to 2007) needs to be assessed.
+Since sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~year archive (1961 to 2008) to 25~years (1982 to 2007) can be expected.
+However, the competition between the loss of performance due to a smaller archive length and the potentially better analogy between target and MTW candidates needs to be assessed.
 
@@
 
-	It would be profitable to be able to apply the MTW to a longer archive (here, 1961 to 2008), rather than being limited to the reduced period corresponding to the sub-daily precipitation data (cf.
+	It would be profitable to be able to apply the MTW to a longer archive (here, 1961 to 2008), rather than being limited to the reduced period where the sub-daily precipitation data are available (cf.
 previous section).
@@
 The spatial window grows by repeating the previous steps until no improvement is reached.
-			\item The number of analogue situations is then reconsidered and optimized for the current level of analogy.
+			\item The number of analogue situations N1 is then reconsidered and optimized for the current level of analogy.
 		\end{enumerate}
 		\item A new level of analogy can then be added, based on other variables (such as the moisture index) at chosen pressure levels and hours of the day.
-The number of analogues for the next level of analogy is initiated at a chosen value.
+The number of analogues for the next level of analogy, N2, is initiated at a chosen value.
 The procedure starts again from step 2 (calibration of the spatial window and the number of analogues) for the new level.
 The parameters calibrated on the previous analogue levels are fixed and do not change.
-		\item Finally, the numbers of analogues for the different levels of analogy are reassessed. This is done iteratively by varying the number of analogues of each level in a systematic way.
+		\item Finally, the numbers of analogues N1 and N2 for the different levels of analogy are reassessed. This is done iteratively by varying the number of analogues of each level in a systematic way.
 	\end{enumerate}
@@
 
-	\subsection{Influence on the analogy criterion}
+	\subsection{Influence of the MTW on the analogy criterion}
 	\label{sec:influence_criteria}
@@
 	When searching for analogues in the first level of analogy, such as on the geopotential heights in the 2Z method (Sect.
-\ref{sec:analog_method}), there are four times more candidates (even though not fully independent) with the MTW than before (Sect.
+\ref{sec:analog_method}), there are four times as many candidates (even though not fully independent) with the MTW than before (Sect.
 \ref{sec:mtw}).
@@
 With the number of cases per class being reduced, the curves are not as smooth as in previous analyses.
-It is nevertheless clear that the improvements were larger on days with higher precipitation.
-Once again, the results for the other stations were similar.
+It is nevertheless clear that the improvements were larger for days with higher precipitation.
+Once again, the results for all the other stations were similar.
 
@@
 
-	\subsection{Impact on prediction skill}
+	\subsection{Impact of the MTW on prediction skill}
 	\label{sec:influence_scores}
 
-	The new performance scores (CRPSS) are provided in Fig.
+	The new performance scores (CRPSS) of the precipitation prediction are provided in Fig.
 \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI} for the 2Z and 2Z-2MI methods, respectively, for the reduced archive (1982--2007).
@@
 \ref{sec:influence_precip}).
-The changes in terms of performance scores were also assessed for the precipitation classes.
+The changes in terms of prediction skill were also assessed for the precipitation classes.
 Fig.
@@
 Among these, the zonal extent of the spatial windows of the circulation analogy decreased slightly (not shown).
-More significantly, the optimal number of analogues increased after introducing the MTW by a considerable magnitude: 25~\% to 83~\% for the 2Z method and 20~\% to 67~\% for the final selection of the 2Z-2MI method (Table \ref{table:analog_nb}).
-The number of analogues of the first analogy level of the 2Z-2MI method reached three times its previous value for the Visp station.
+More significantly, the optimal number of analogues N1 and N2 increased after introducing the MTW by a considerable magnitude (Table \ref{table:analog_nb}): 25~\% to 83~\% for the 2Z method and 20~\% to 67~\% for the final selection of the 2Z-2MI method.
+The number of analogues N1 of the first analogy level of the 2Z-2MI method reached three times its previous value for the Visp station (N1=135 instead of 45; Table \ref{table:analog_nb}).
 
@@
 	\label{sec:reconstruction_results}
+
+	The reconstructed time series cover the full period.
+However, they were first assessed using the MTW on the reduced period in order be comparable with the real sub-daily precipitation time series, and thus to evaluate their relevance and the possible loss in performance score.
 
@@
 	For the first level of analogy, the improvement of the S1 criterion (Fig.
-\ref{fig:changes_S1} bottom) started approximately at 5~\% for the first analogue and reached more than 10~\% for the last (Sect.
+\ref{fig:changes_S1} bottom) started approximately at 5~\% for the first analogue and reached more than 10~\% for the last (40$^{th}$) (Sect.
 \ref{sec:perf_2Z}).
-This increase in improvement with the analogue rank can be explained by the accumulation of better analogues in the selection.
+This increase in improvement with the analogue rank can be explained by the accumulation of better analogues in the selection, with new better situations pushing previous analogues to higher ranks.
 The curve representing the minimum improvement is mostly superior to zero, meaning that the criteria have been improved on most analogue ranks for every day of the calibration period.
 All other stations had a similar improvement in the S1 criterion, both in terms of the distribution shape and amplitude.
-The introduction of the MTW allowed finding better analogue situations in the first level of analogy, resulting in a selection of days with better similarity in atmospheric circulation.
+The introduction of the MTW allows finding better analogue situations in the first level of analogy, resulting in a selection of days with better similarity in atmospheric circulation.
 
@@
 Moreover, it required no additional predictor.
-With the introduction of the MTW, the performance loss related to the reduction of the archive length was negated.
+With the introduction of the MTW, the performance loss related to the reduction of the archive length was negated (considering a 25 year archive of sub-daily data; the difference could be higher with a shorter archive).
 It was in this case of the same magnitude as if the length of the archive doubled.
@@
 Moreover, high correlations between sub-daily circulation patterns are expected.
-The MTW, therefore, did not create four times more independent data, but the increase in information was nevertheless substantial.
+The MTW, therefore, did not create four times as many independent data, but the increase in information was nevertheless substantial.
 In this regards, a reanalysis dataset with a higher temporal resolution might not improve the performance significantly more than a 6-hourly dataset.
@@
 
-	We just mentioned that the MTW improved the prediction for days with heavier precipitation.
-However, it will have no effect on the prediction of extreme events that were not yet observed and are, therefore, not present in the archive.
+	The MTW improved the prediction for days with heavier precipitation, and should improve the prediction of extremes due to better analogue situations, but also due to possible new extreme values resulting from 24-h totals with a certain time shift.
+However, even though the distribution of analogue precipitation values should move towards the targeted extreme, providing a better prediction, the MTW itself does not allow to predict extreme events that were not yet observed and are, therefore, not present in the archive.
 The extremes in AMs can be modelled by, for example, extrapolation of a truncated exponential or gamma distribution fitted to the analogue values \citep{Obled2002}.
 Another possible approach is by combining AMs with other methods \citep[e.g.][]{Chardon2014}.
-However, this goes beyond the scope of the present study, as prediction of unobserved extremes are not modified by the MTW.
+From this perspective, the MTW might increase the prediction of extremes as it improves the distribution of precipitation values for days with higher precipitation, on which post-treatment techniques rely.
+However, this goes beyond the scope of the present study.
 
@@
 
-	The considered reanalysis dataset, which is the NCEP/NCAR reanalysis I \citep{Kalnay1996}, is relatively old and has a coarse resolution.
+	The considered reanalysis dataset, which is the NCEP/NCAR reanalysis I \citep{Kalnay1996}, is relatively old and has a coarse resolution (2.5\degree).
 Newer reanalysis datasets could have been used in this study and might have resulted in higher performance scores.
@@
 
-	The use of the MTW relies on the availability of long precipitation series at a sub-daily time step and with high accuracy.
+	The use of the MTW relies partly on the availability of long precipitation series at a sub-daily time step and with high accuracy.
 First, these archives of high temporal resolution precipitation data are increasing over time.
@@
 When precipitation data with accurate time distributions are available, the use of a MTW in the AM can be considered for any application and in any context, including operational forecasting or climate-related studies.
+
+	Finally, since long meteorological archives are more and more available, the improvements proposed by the MTW especially for days or sequences of heavy precipitation may be interesting even without long continuous precipitation archives.
+For example, recent target day may have synoptic similarity with situations from the early twentieth century, for which no continuous daily precipitation archive is available.
+However, some of those days with strong precipitation events may be documented, either qualitatively in the daily press or more quantatively in flood reports.
+Nevertheless, it is worth to known that the situation at hand has such analogue in the far past.
 
@@
 		\item [2Z-2MI] Name of the analogue method composed of a first level on the atmospheric circulation and a second level on a moisture index
-		\item [AM] Analog method
+		\item [AM] Analogue method
 		\item [CRPS] Continuous ranked probability score
@@
 		\caption{Illustration of the principle of a moving time window.
-The target situation is the same for the conventional approach and the MTW, while the candidate situations are four times more numerous with the MTW.
+The target situation is the same for the conventional approach and the MTW, while the candidate situations are four times as many with the MTW.
 The larger horizontal bars represent the 24~h precipitation totals.}

### 2016-12-06 Moving temporal window - HESS/template.tex
Addition of the references.
Addition of a paragraph in the discussion.

@@
 
-%TODO: check references: complete, doi, etc
+%TODO: journal abbreviations
+%TODO: read again
 
@@
 
+	The introduction of the MTW improved the selection of synoptic analogues.
+Independently of its impact on the prediction skill for precipitation, or the availability of a predictand time series with sub-daily time step, this improvement has a potential for application on long meteorological archives.
+For example, when processing forecasts for a target day with synoptic similarity with situations from the past related to extreme weather, even though no precipitation archive is available.
+Indeed, some of those days with strong precipitation events may be documented, either qualitatively in the daily press or more quantitatively in flood reports.
+It is thus worth to known that the situation at hand has such analogue in the past.
+Another possible application is a quality assessment of the selection of analogues on a shorter period, where precipitation data with a high temporal resolution is available.
+Indeed, if the selection of analogues with the MTW on the long period differ from the selection on the short period, this may point out a sub-optimal forecast.
+Finally, other predictands might not need sub-daily total values, but point observations (e.g.
+hail, or extreme wind gusts).
+
 	\subsection{Improvement of precipitation prediction}
@@
 For example, recent target day may have synoptic similarity with situations from the early twentieth century, for which no continuous daily precipitation archive is available.
-However, some of those days with strong precipitation events may be documented, either qualitatively in the daily press or more quantatively in flood reports.
+However, some of those days with strong precipitation events may be documented, either qualitatively in the daily press or more quantitatively in flood reports.
 Nevertheless, it is worth to known that the situation at hand has such analogue in the far past.
@@
 	\bibliographystyle{copernicus}
-	\bibliography{../_refs/4_articles-2016_HESS_moving-window}
+	\bibliography{references}
 

### 2016-12-06 Moving temporal window - HESS/template.tex
Last personnal corrections.

@@
 	\begin{abstract}
-		Analogue methods (AM) predict local weather variables (predictands), such as precipitation, by means of a statistical relationship with predictors at a synoptic scale.
-The analogy is generally assessed on gradients of geopotential fields first, in order to sample days with a similar atmospheric circulation.
+		Analogue methods (AMs) predict local weather variables (predictands), such as precipitation, by means of a statistical relationship with predictors at a synoptic scale.
+The analogy is generally assessed on gradients of geopotential heights first, in order to sample days with a similar atmospheric circulation.
 Other predictors, such as moisture variables, can also be added in a successive level of analogy.
@@
 The main reason is the use of daily precipitation time series due to the length of their available archives, and the unavailability of equivalent archives at a finer time step.
-However, it is unlikely for the best analogy to occur at the very same hour, while it may be found with a time shift of some hours as it may occur at a different time of day.
-In order to assess the potential for finding better analogues at a different hour, a moving time window (MTW) has been introduced on a reduced archive of hourly precipitation totals.
+However, it is unlikely for the best analogy to occur at the very same hour, while it may be found with a time shift of some hours as it can occur at a different time of day.
+In order to assess the potential for finding better analogues at a different hour, a moving time window (MTW) has been introduced.
 
@@
 
-		However, the MTW requires a sub-daily precipitation time series, which is generally available for a shorter period than daily precipitation archives.
+		However, in order to produce quantitative precipitation predictions the MTW requires sub-daily precipitation time series, which are generally available for a shorter period than daily precipitation archives.
 Therefore, two simple temporal disaggregation methods were assessed in order to make longer archives usable with the MTW.
@@
 These should be available in the near future, either by means of growing archives of measurements or by the establishment of regional precipitation reanalysis data at sub-daily time step.
-The use of an MTW in the AM could then be considered for any application and in any context, may it be for operational forecasting or climate-related studies.
+
+		The use of the MTW in the AM can already be considered now for several applications in different contexts, may it be for operational forecasting or climate-related studies.
 
@@
 	Analogue methods (AMs) are based on the hypothesis that two relatively similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}.
-They are statistical downscaling methods \citep{Maraun2010} and consist of finding past situations that are similar in terms of the atmospheric circulation or other synoptic predictors to the target day of interest.
+They are statistical downscaling methods \citep{Maraun2010} and consist of finding past situations that are similar to the target day of interest in terms of the atmospheric circulation or other synoptic predictors.
 The local weather variables of interest (predictand) that were observed at the analogue dates are used to construct a probabilistic prediction for the target day \citep{Duband1970, Zorita1999}.
 Multiple variations of the method exist \citep[a non-exhaustive listing can be found in][]{BenDaoud2016}.
-The AMs are used for operational precipitation forecasting, either in the context of weather forecasting, flood forecasting, or hydropower production \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as in precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}.
+The AMs are used for operational precipitation forecasting, either in the context of weather forecasting, flood forecasting, or hydropower production \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as for precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}.
 Other applications focus on temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectories of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
 
-	The spatial transferability of the method is analysed in \citet{Chardon2014}.
+	The spatial transferability of the method is analysed in \citet{Chardon2014} and \citet{Radanovics2013}.
 A great advantage of AMs is that they create realistic precipitation patterns, since they are based on observed situations with consistent spatial distribution, as long as the analogue dates chosen for a region are the same.
+Moreover, they can provide multivariate predictions that are physically consistent \citep{Raynaud2016b}.
 Their temporal transferability has also been the topic of recent studies for past or future climates \citep{Dayon2015, Caillouet2016}.
@@
 	Therefore, due to the availability of long precipitation archives at a daily time step that have no equivalent at a finer resolution, AMs are usually implemented on a daily basis.
-Therefore, the analogue situations are assessed by comparing predictors at fixed hours of the day.
+Consequently, the analogue situations are assessed by comparing predictors at fixed hours of the day.
 However, it can be expected that the analogy of the synoptic situations does not occur systematically at the same time of the day and that better candidates can be found by shifting to a different hour.
@@
 
-	Synoptic-scale variables, used as predictors, were extracted from the NCEP/NCAR reanalysis I dataset \citep{Kalnay1996} with a 6-hour temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree.
+	Synoptic-scale variables, used as predictors, were extracted from the NCEP/NCAR reanalysis 1 dataset \citep{Kalnay1996} with a 6-hour temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree.
 This dataset is now relatively old, but it is not expected to affect the conclusions of the present study (see discussion in Sect.
@@
 
-	The first considered AM is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005, Marty2012}.
+	The first considered AM is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005}.
 Searching for analogue situations to a target day starts by a seasonal stratification through a preselection step of the potential candidates for analogy.
@@
 If the target situation is kept at 12 and 24~h~UTC for Z1000 and Z500 respectively, candidate situations are not only considered at 12 and 24~h~UTC, but at other hours by allowing a time shift.
-Therefore, instead of looking for analogues at a 24-hourly time step, they are sought at the time step matching the predictor temporal resolution which is a 6-hour time step in this study (Fig.
+Therefore, instead of looking for analogues at a 24-h time step, they are sought at the time step matching the predictor temporal resolution which is a 6-h time step in this study (Fig.
 \ref{fig:principle}).
@@
 
-	In order to assess the benefit of searching for analogue situations at a sub-daily time step, an appropriate precipitation series is required.
+	In order to assess the benefit of searching for analogue situations at a sub-daily time step for quantitative precipitation prediction, an appropriate precipitation series is required.
 On the basis of high temporal resolution time series (Sect.
-\ref{sec:data}), 24~h-totals were processed at a 6-hour time step by means of a moving 24~h-total.
+\ref{sec:data}), 24-h totals were processed at a 6-hour time step by means of a moving 24-h total.
 Since sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~year archive (1961 to 2008) to 25~years (1982 to 2007) can be expected.
@@
 previous section).
-Therefore, in order to reconstruct a longer archive of moving 24~h-totals, two simple disaggregation approaches of the daily precipitation time series were assessed.
+Therefore, in order to reconstruct a longer archive of moving 24-h totals, two simple disaggregation approaches of the daily precipitation time series were assessed.
 
 	The first technique was a proportional distribution, where the observed daily precipitations were considered constant during the measuring period (6~h~UTC to 6~h~UTC the next day).
-Proportional parts of the original daily time series were allocated into a new moving average of 24~h-totals (Fig.
+Proportional parts of the original daily time series were allocated into a new moving average of 24-h totals (Fig.
 \ref{fig:illustration_disaggregation}).
@@
 		\begin{enumerate}
-			\item Identification of the most skilled unitary cell (one point for moisture variables and four for the geopotential height when using the S1 criterion) over a large domain.
+			\item Identification of the most skilled unitary cell (one point for moisture variables and four for geopotential heights when using the S1 criterion) over a large domain.
 Every point (or cell) of the full domain is assessed on all predictors of the level of analogy, jointly (consisting generally of the same variable but on different pressure levels and at different hours).
@@
 The spatial window grows by repeating the previous steps until no improvement is reached.
-			\item The number of analogue situations N1 is then reconsidered and optimized for the current level of analogy.
+			\item The number of analogue situations $N_{1}$ is then reconsidered and optimized for the current level of analogy.
 		\end{enumerate}
 		\item A new level of analogy can then be added, based on other variables (such as the moisture index) at chosen pressure levels and hours of the day.
-The number of analogues for the next level of analogy, N2, is initiated at a chosen value.
+The number of analogues for the next level of analogy, $N_{2}$, is initiated at a chosen value.
 The procedure starts again from step 2 (calibration of the spatial window and the number of analogues) for the new level.
 The parameters calibrated on the previous analogue levels are fixed and do not change.
-		\item Finally, the numbers of analogues N1 and N2 for the different levels of analogy are reassessed. This is done iteratively by varying the number of analogues of each level in a systematic way.
+		\item Finally, the numbers of analogues $N_{1}$ and $N_{2}$ for the different levels of analogy are reassessed.
+This is done iteratively by varying the number of analogues of each level in a systematic way.
 	\end{enumerate}
@@
 
-	The improvements of the S1 criterion with the rank of the analogues are summarized in Fig.
-\ref{fig:changes_S1}, which shows (top) quantiles of the S1 criterion for the conventional method and the MTW and (bottom) quantiles of the relative reduction (meaning improvement) due to the MTW.
+	The improvements of the analogy with the rank of the analogues are summarized in Fig.
+\ref{fig:changes_S1}, which shows (top) quantiles of the S1 criterion for the conventional method and the MTW, and (bottom) quantiles of the relative reduction (meaning improvement) due to the MTW.
 This confirms that all quantiles were similarly reduced (S1 distributions keep their shape), and that this improvement was constantly increasing from the first to the last analogue (Fig.
@@
 Among these, the zonal extent of the spatial windows of the circulation analogy decreased slightly (not shown).
-More significantly, the optimal number of analogues N1 and N2 increased after introducing the MTW by a considerable magnitude (Table \ref{table:analog_nb}): 25~\% to 83~\% for the 2Z method and 20~\% to 67~\% for the final selection of the 2Z-2MI method.
-The number of analogues N1 of the first analogy level of the 2Z-2MI method reached three times its previous value for the Visp station (N1=135 instead of 45; Table \ref{table:analog_nb}).
+More significantly, the optimal number of analogues $N_{1}$ and $N_{2}$ increased after introducing the MTW by a considerable magnitude (Table \ref{table:analog_nb}): 25~\% to 83~\% for the 2Z method and 20~\% to 67~\% for the final selection of the 2Z-2MI method.
+The number of analogues $N_{1}$ of the first analogy level of the 2Z-2MI method reached three times its previous value for the Visp station ($N_{1}$~=~135 instead of 45; Table \ref{table:analog_nb}).
 
@@
 
-	When using the first reconstructed time series (for the reduced period) based on the proportional distribution (see Sect.
+	When using the first reconstructed time series based on the proportional distribution (see Sect.
 \ref{sec:reconstruction}), the AM performance was degraded and was even below the conventional method without MTW (Table \ref{table:disaggregation_proportional} to compare to Fig.
@@
 Among the considered moisture variables (see Sect.
-\ref{sec:reconstruction}), the best proxy was the precipitable water at 45° N and 7.5° E, with a time offset of 6~h (Table \ref{table:proxy_correlations}).
-Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the disaggregated series using the proxy of precipitable water.
+\ref{sec:reconstruction}), the best proxy was the precipitable water at 45° N and 7.5° E, with a time offset of -6~h (Table \ref{table:proxy_correlations}).
+Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the disaggregated series using the proxy of precipitable water which are also lower than the conventional method.
 
@@
 Another possible application is a quality assessment of the selection of analogues on a shorter period, where precipitation data with a high temporal resolution is available.
-Indeed, if the selection of analogues with the MTW on the long period differ from the selection on the short period, this may point out a sub-optimal forecast.
+Indeed, if the selection of analogues with the MTW on the long period, for a specific target day, differ from the selection on the short period, this may point out a sub-optimal forecast.
 Finally, other predictands might not need sub-daily total values, but point observations (e.g.
-hail, or extreme wind gusts).
+hail, or extreme wind gusts), which make them easier to use with the MTW.
 
@@
 It was in this case of the same magnitude as if the length of the archive doubled.
-Note, that despite the number of candidate situations being four times higher, the gains seem to be lower than for a quadrupled archive length.
+Note, that despite the number of candidate situations being four times as many, the gains seem to be lower than for a quadrupled archive length.
 The likely reason is that an actual longer archive would contain more atmospheric situations that might have been observed less frequently during a shorter period.
@@
 In such cases, the archive inflation brought by the MTW is also relevant.
-
-	More complex methods with additional levels of analogy and more predictors do increase the performance score, and the MTW could also be applied in these situations, as it is likely to improve the analogy of the atmospheric circulation anyway.
 
@@
 Another possible approach is by combining AMs with other methods \citep[e.g.][]{Chardon2014}.
-From this perspective, the MTW might increase the prediction of extremes as it improves the distribution of precipitation values for days with higher precipitation, on which post-treatment techniques rely.
+From this perspective, the MTW might improve the prediction of extremes as it improves the distribution of precipitation values for days with higher precipitation, on which post-treatment techniques rely.
 However, this goes beyond the scope of the present study.
@@
 
-	An analysis of the selected hours for the geopotential predictor seems to confirm this assumption (Fig.
+	An analysis of the selected hours for the geopotential height predictor seems to confirm this assumption (Fig.
 \ref{fig:hours_selection_per_season}).
@@
 	After the recalibration of the AMs with the MTW, the optimal analogue numbers were significantly higher than in the original methods (see Sect.
-\ref{sec:recalibration} and Fig.
-\ref{table:analog_nb}).
+\ref{sec:recalibration} and Table \ref{table:analog_nb}).
 As shown in Fig.
@@
 However, when the length of the archive increases, the optimal number of analogues increases too for a better performance up to a certain threshold \citep[][]{Bontron2004, Hamill2006a}.
-The observed increase in the number of analogue situations with the MTW resulted in better performance skills for a given method, as it can be seen as an inflation of the archive.
+The observed increase in the number of analogue situations with the MTW resulted in better performance skills for the given methods, as it can be seen as an inflation of the archive.
 However, if new relevant predictors were added to the method, the number of analogues would then decrease.
@@
 In addition, sometimes a resolution finer than the daily time step is not needed and another disaggregation technique may be used afterwards.
-Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact than 24~h daily totals.
+Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact than 24-h daily totals.
 
@@
 
-	The considered reanalysis dataset, which is the NCEP/NCAR reanalysis I \citep{Kalnay1996}, is relatively old and has a coarse resolution (2.5\degree).
+	The considered reanalysis dataset, which is the NCEP/NCAR reanalysis 1 \citep{Kalnay1996}, is relatively old and has a coarse resolution (2.5\degree).
 Newer reanalysis datasets could have been used in this study and might have resulted in higher performance scores.
@@
 \ref{sec:reconstruction_results}).
-Indeed, the performance improvement brought by the MTW was lost due to a precipitation archive of poor quality.
+Indeed, the performance improvement brought by the MTW was lost due to the poor quality of the precipitation archives.
 A slight improvement could be obtained for the second method relying on a proxy variable compared to the proportional distribution method, but it was still relatively small, and most of the benefit of the MTW was lost.
@@
 Here, it was assessed for a 25~year time series with a high temporal resolution.
-After the introduction of the MTW, the performance scores increased at the same magnitude as if the length of the archive doubled.
+After the introduction of the MTW, the performance scores increased of the same magnitude as if the length of the archive doubled.
 
@@
 Even though outputs from these models might be biased or not accurate enough, information regarding the timing of the precipitation events could be useful in disaggregating the station time series.
-When precipitation data with accurate time distributions are available, the use of a MTW in the AM can be considered for any application and in any context, including operational forecasting or climate-related studies.
-
-	Finally, since long meteorological archives are more and more available, the improvements proposed by the MTW especially for days or sequences of heavy precipitation may be interesting even without long continuous precipitation archives.
+
+	Finally, since long meteorological archives (reanalysis datasets) are more and more available, the improvements proposed by the MTW especially for days with heavy precipitation may be interesting even without long continuous precipitation archives.
 For example, recent target day may have synoptic similarity with situations from the early twentieth century, for which no continuous daily precipitation archive is available.
@@
 Nevertheless, it is worth to known that the situation at hand has such analogue in the far past.
+
+	The use of the MTW in the AM can already be considered now for several applications in different contexts, may it be for operational forecasting or climate-related studies.
 
@@
 		\end{center}
-		\caption{Position of the six weather stations of interest (Ulrichen, Zermatt, Visp, Montana, Sion, and Aigle) in the study area.}
+		\caption{Position of the six weather stations of interest (Ulrichen, Zermatt, Visp, Montana, Sion, and Aigle) in the upper Rh\^{o}ne catchment in Switzerland.}
 		\label{fig:map}
@@
 The target situation is the same for the conventional approach and the MTW, while the candidate situations are four times as many with the MTW.
-The larger horizontal bars represent the 24~h precipitation totals.}
+The larger horizontal bars represent the 24-h precipitation totals.}
 		\label{fig:principle}
@@
 		\end{center}
-		\caption{Illustration of the generation of 24~h total moving averages by means of a proportional distribution. The colours refer to the corresponding day of the daily time series.}
+		\caption{Illustration of the generation of 24-h total moving averages by means of a proportional distribution. The colours refer to the corresponding day of the daily time series.}
 		\label{fig:illustration_disaggregation}
@@
 		\includegraphics[width=8.3cm]{figures/plots_CRPSS_2Z.pdf}
-		\caption{Performance score (CRPSS, \%) of the AM on the atmospheric circulation at the different stations for (dashed) the full archive, i.e.
+		\caption{Performance score (CRPSS) of the AM on the atmospheric circulation at the different stations for (dashed) the full archive, i.e.
 1961-2008; (yellow) the reduced archive, i.e.
@@
 		\end{center}
-		\caption{Changes in the S1 criterion distributions due to the MTW of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$, and (d) $40^{th}$ analogue ranks for the Ulrichen station.}
+		\caption{Changes in the S1 criterion distributions due to the MTW of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$, and (d) $40^{th}$ analogue ranks for the Ulrichen station over the whole calibration period (1961-2008).}
 		\label{fig:changes_S1_analogs}
@@
 		\includegraphics[width=8.3cm]{figures/hours_selection_per_season.pdf}
-		\caption{Distribution of the predictor hours on the selected analogue dates depending on the season for the Ulrichen station.}
+		\caption{Distribution of the predictor hours on the selected analogue dates, when using the MTW, depending on the season for the Ulrichen station.}
 		\label{fig:hours_selection_per_season}
@@
 	\begin{table}[htb]
-		\caption{Number of analogues (of the first and second level of analogy, respectively, $N_{1}$ and $N_{2}$) of the method based on the atmospheric circulation only (method 2Z), the method with a second level of analogy with moisture variables (2Z-2MI) on the full archive (Standard), and after recalibration using the MTW (MTW-r).}
+		\caption{Optimal number of analogues (of the first and second level of analogy, respectively, $N_{1}$ and $N_{2}$) of the method based on the atmospheric circulation only (method 2Z) and the method with a second level of analogy with moisture variables (2Z-2MI) on the full archive (Standard), and after recalibration using the MTW (MTW-r).}
 		\begin{center}
@@
 	\begin{table}[htb]
-		\caption{Values of the CRPSS (\%) skill score for Zermatt for the original and the recalibrated parameters (with the sequential method, as described in Sect.
-\ref{sec:introduction}) using the MTW approach on the disaggregated precipitation time series (short and long periods) by means of variables from the reanalysis.}
+		\caption{Values of the CRPSS (\%) score for Zermatt for the original and the recalibrated parameters (with the sequential method, as described in Sect.
+\ref{sec:introduction}) using the MTW approach on the disaggregated precipitation time series (short and long periods) by means of proxy variables from the reanalysis dataset.}
 		\begin{center}

### 2016-12-06 Moving temporal window - HESS/template.tex
Renaming figures.

@@
 %% Please use the following documentclass and Journal Abbreviations for Discussion Papers and Final Revised Papers.
-
-%TODO: journal abbreviations
-%TODO: read again
 
@@
 
-	Synoptic-scale variables, used as predictors, were extracted from the NCEP/NCAR reanalysis 1 dataset \citep{Kalnay1996} with a 6-hour temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree.
+	Synoptic-scale variables, used as predictors, were extracted from the NCEP/NCAR reanalysis 1 dataset \citep{Kalnay1996} with a 6-hour temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\textdegree.
 This dataset is now relatively old, but it is not expected to affect the conclusions of the present study (see discussion in Sect.
@@
 Data from the NCEP/NCAR reanalysis 1 (Sect.
-\ref{sec:data}) were used for this purpose, despite their rough resolution (2.5\degree).
+\ref{sec:data}) were used for this purpose, despite their rough resolution (2.5\textdegree).
 Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and a time lapse between both series was allowed to take into account the significant distance separating the weather stations and the reanalysis grid point.
@@
 Among the considered moisture variables (see Sect.
-\ref{sec:reconstruction}), the best proxy was the precipitable water at 45° N and 7.5° E, with a time offset of -6~h (Table \ref{table:proxy_correlations}).
+\ref{sec:reconstruction}), the best proxy was the precipitable water at 45\textdegree\ N and 7.5\textdegree\ E, with a time offset of -6~h (Table \ref{table:proxy_correlations}).
 Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the disaggregated series using the proxy of precipitable water which are also lower than the conventional method.
@@
 
-	The considered reanalysis dataset, which is the NCEP/NCAR reanalysis 1 \citep{Kalnay1996}, is relatively old and has a coarse resolution (2.5\degree).
+	The considered reanalysis dataset, which is the NCEP/NCAR reanalysis 1 \citep{Kalnay1996}, is relatively old and has a coarse resolution (2.5\textdegree).
 Newer reanalysis datasets could have been used in this study and might have resulted in higher performance scores.
@@
 		\begin{center}
-			\includegraphics[width=8.3cm]{figures/figure_map.pdf}
+			\includegraphics[width=8.3cm]{fig01.pdf}
 		\end{center}
@@
 		\begin{center}
-			\includegraphics[width=8.3cm]{figures/illustration_moving_window.pdf}
+			\includegraphics[width=8.3cm]{fig02.pdf}
 		\end{center}
@@
 		\begin{center}
-			\includegraphics[width=8cm]{figures/illustration_disaggregation.pdf}
+			\includegraphics[width=8cm]{fig03.pdf}
 		\end{center}
@@
 	\begin{figure}[htb]
-		\includegraphics[width=8.3cm]{figures/plots_CRPSS_2Z.pdf}
+		\includegraphics[width=8.3cm]{fig04.pdf}
 		\caption{Performance score (CRPSS) of the AM on the atmospheric circulation at the different stations for (dashed) the full archive, i.e.
@@
 	\begin{figure}[htb]
-		\includegraphics[width=8.3cm]{figures/plots_CRPSS_2Z-2MI.pdf}
+		\includegraphics[width=8.3cm]{fig05.pdf}
 		\caption{Same as Figure \ref{fig:plots_CRPSS_2Z}, but for the analogue method with a second level with the moisture variables.}
@@
 		\begin{center}
-			\includegraphics[width=15cm]{figures/changes_S1_analogues.pdf}
+			\includegraphics[width=15cm]{fig06.pdf}
 		\end{center}
@@
 		\begin{center}
-			\includegraphics[width=8.2cm]{figures/changes_S1_value_and_gain.pdf}
+			\includegraphics[width=8.2cm]{fig07.pdf}
 		\end{center}
@@
 		\begin{center}
-			\includegraphics[width=8.3cm]{figures/changes_S1_precip_threshold.pdf}
+			\includegraphics[width=8.3cm]{fig08.pdf}
 		\end{center}
@@
 		\begin{center}
-			\includegraphics[width=7cm]{figures/changes_S1_seasons.pdf}
+			\includegraphics[width=7cm]{fig09.pdf}
 		\end{center}
@@
 		\begin{center}
-			\includegraphics[width=8.1cm]{figures/changes_RMSE_value_and_gain.pdf}
+			\includegraphics[width=8.1cm]{fig10.pdf}
 		\end{center}
@@
 	\begin{figure}[htb]
-		\includegraphics[width=5cm]{figures/changes_CRPS_precip_threshold.pdf}
+		\includegraphics[width=5cm]{fig11.pdf}
 		\caption{Differences of the CRPSS performance score due to the introduction of the MTW as a function of precipitation thresholds at the Ulrichen station. The stars represent averages.}
@@
 	\begin{figure}[htb]
-		\includegraphics[width=8.3cm]{figures/hours_selection_per_season.pdf}
+		\includegraphics[width=8.3cm]{fig12.pdf}
 		\caption{Distribution of the predictor hours on the selected analogue dates, when using the MTW, depending on the season for the Ulrichen station.}
@@
 		\caption{Value of the coefficient of determination between the reconstructed 6-hourly precipitation time series using the listed variables and the accurate time series for the period 1982-2007.
-The grid points surrounding the region are: 1) 5° E, 47.5° N; 2) 5° E, 45° N; 3) 7.5° E, 47.5° N; and 4) 7.5° E, 45° N.
+The grid points surrounding the region are: 1) 5\textdegree\ E, 47.5\textdegree\ N; 2) 5\textdegree\ E, 45\textdegree\ N; 3) 7.5\textdegree\ E, 47.5\textdegree\ N; and 4) 7.5\textdegree\ E, 45\textdegree\ N.
 The highest coefficient of determination is indicated in bold.}

### 2016-12-06 Moving temporal window - HESS/template.tex
Corrections related to author's guidelines.

@@
 
-	\linenumbers
-
-	\title{The Analogue Method for Precipitation Prediction: Finding Better Analogue Situations at a Sub-Daily Time Step}
+	\title{The analogue method for precipitation prediction: finding better analogue situations at a sub-daily time step}
 
@@
 
-	\runningtitle{Finding Better Analogue Situations at a Sub-Daily Time Step}
+	\runningtitle{Finding better analogue situations at a sub-daily time step}
 
@@
 
-		The impact of the MTW on prediction skill has been assessed by means of a sub-daily precipitation series transformed into moving 24-h totals at 6-h time steps.
+		The impact of the MTW on prediction skill has been assessed by means of a sub-daily precipitation series transformed into moving 24h totals at 6h time steps.
 The prediction skill was found to have improved by the MTW, and even to a greater extent after recalibrating the AM parameters.
@@
 \ref{fig:map}) that are subject to various meteorological influences \citep{Horton2012}.
-The data were available at an hourly time step for 25~years (1982 to 2007) and were also obtained at a daily time step (from 6~h~UTC to 6~h~UTC the next day) for 47~years (1961 to 2008).
+The data were available at an hourly time step for 25~years (1982\textendash 2007) and were also obtained at a daily time step (from 6:00~UTC to 6:00~UTC the next day) for 47~years (1961\textendash 2008).
 Due to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed.
@@
 
-	Synoptic-scale variables, used as predictors, were extracted from the NCEP/NCAR reanalysis 1 dataset \citep{Kalnay1996} with a 6-hour temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\textdegree.
+	Synoptic-scale variables, used as predictors, were extracted from the NCEP/NCAR reanalysis 1 dataset \citep{Kalnay1996} with a 6h temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\textdegree.
 This dataset is now relatively old, but it is not expected to affect the conclusions of the present study (see discussion in Sect.
@@
 	The predictor variables extracted from reanalysis datasets are considered at different hours of the day.
-Based on \citet{Bontron2005}, geopotential heights are compared at 1000~hPa (Z1000) at 12~h~UTC and 500~hPa (Z500) at 24~h~UTC.
+Based on \citet{Bontron2005}, geopotential heights are compared at 1000~hPa (Z1000) at 12:00~UTC and 500~hPa (Z500) at 24:00~UTC.
 The time of the day at which the predictors are selected is found by \citet{Bontron2004} to have a significant influence.
@@
 	The moving time window (MTW) technique aims at finding better analogue situations at different hours of the day rather than comparing the predictors at the same fixed hours.
-If the target situation is kept at 12 and 24~h~UTC for Z1000 and Z500 respectively, candidate situations are not only considered at 12 and 24~h~UTC, but at other hours by allowing a time shift.
-Therefore, instead of looking for analogues at a 24-h time step, they are sought at the time step matching the predictor temporal resolution which is a 6-h time step in this study (Fig.
+If the target situation is kept at 12:00 and 24:00~UTC for Z1000 and Z500 respectively, candidate situations are not only considered at 12:00 and 24:00~UTC, but at other hours by allowing a time shift.
+Therefore, instead of looking for analogues at a 24h time step, they are sought at the time step matching the predictor temporal resolution which is a 6h time step in this study (Fig.
 \ref{fig:principle}).
 
-	The target situations and their corresponding observed precipitation values do not change because the prediction is still established on a daily basis for a fixed period of the target day (6~h~UTC to 6~h~UTC the next day) as before.
-The difference is that the candidates are four times as many (even though they are not fully independent) as in the conventional approach.
+	The target situations and their corresponding observed precipitation values do not change because the prediction is still established on a daily basis for a fixed period of the target day (6:00~UTC to 6:00~UTC the next day) as before.
+The difference is that the candidates are 4 times as many (even though they are not fully independent) as in the conventional approach.
 No constraint was added in order to restrict the selection of multiple analogues within the same candidate dates.
@@
 On the basis of high temporal resolution time series (Sect.
-\ref{sec:data}), 24-h totals were processed at a 6-hour time step by means of a moving 24-h total.
-Since sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~year archive (1961 to 2008) to 25~years (1982 to 2007) can be expected.
+\ref{sec:data}), 24h totals were processed at a 6h time step by means of a moving 24h total.
+Since sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~year archive (1961\textendash 2008) to 25~years (1982\textendash 2007) can be expected.
 However, the competition between the loss of performance due to a smaller archive length and the potentially better analogy between target and MTW candidates needs to be assessed.
@@
 
-	It would be profitable to be able to apply the MTW to a longer archive (here, 1961 to 2008), rather than being limited to the reduced period where the sub-daily precipitation data are available (cf.
+	It would be profitable to be able to apply the MTW to a longer archive (here, 1961\textendash 2008), rather than being limited to the reduced period where the sub-daily precipitation data are available (cf.
 previous section).
-Therefore, in order to reconstruct a longer archive of moving 24-h totals, two simple disaggregation approaches of the daily precipitation time series were assessed.
-
-	The first technique was a proportional distribution, where the observed daily precipitations were considered constant during the measuring period (6~h~UTC to 6~h~UTC the next day).
-Proportional parts of the original daily time series were allocated into a new moving average of 24-h totals (Fig.
+Therefore, in order to reconstruct a longer archive of moving 24h totals, two simple disaggregation approaches of the daily precipitation time series were assessed.
+
+	The first technique was a proportional distribution, where the observed daily precipitations were considered constant during the measuring period (6:00~UTC to 6:00~UTC the next day).
+Proportional parts of the original daily time series were allocated into a new moving average of 24h totals (Fig.
 \ref{fig:illustration_disaggregation}).
@@
 Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and a time lapse between both series was allowed to take into account the significant distance separating the weather stations and the reanalysis grid point.
-The best proxy variable was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series over the period 1982-2007.
+The best proxy variable was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series over the period 1982\textendash 2007.
 Once the best proxy had been selected, its temporal profile was used in order to disaggregate the daily precipitation time series.
@@
 			\item pressure level (e.g. 500 hPa, ...),
-			\item temporal window (hour of the day \textendash\ e.g. 6 or 12~h~UTC),
+			\item temporal window (hour of the day \textendash\ e.g. 6:00 or 12:00~UTC),
 			\item initial analogue numbers (e.g. $N_{1}=50$).
@@
 
-	The performance loss resulting from the reduction of a 47~year archive (1961 to 2008, corresponding to the daily time series) to 25~years (1982 to 2007, corresponding to the hourly time series in Sect.
+	The performance loss resulting from the reduction of a 47~year archive (1961\textendash 2008, corresponding to the daily time series) to 25~years (1982\textendash 2007, corresponding to the hourly time series in Sect.
 \ref{sec:mtw}) was assessed with the original method without MTW.
@@
 As expected, a loss of performance was observed for each station, except for that of Aigle, which seemed relatively indifferent to this change.
-This loss was globally significant, with up to -1.89 points (\% of CRPSS) for Visp and the 2Z method.
+This loss was globally significant, with up to \textendash 1.89 points (\% of CRPSS) for Visp and the 2Z method.
 
@@
 	When searching for analogues in the first level of analogy, such as on the geopotential heights in the 2Z method (Sect.
-\ref{sec:analog_method}), there are four times as many candidates (even though not fully independent) with the MTW than before (Sect.
+\ref{sec:analog_method}), there are 4 times as many candidates (even though not fully independent) with the MTW than before (Sect.
 \ref{sec:mtw}).
-Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions of the analogy criterion (S1) for the $1^{st}$, $5^{th}$, $20^{th}$, and $40^{th}$ analogue rank at the Ulrichen station over the whole calibration period (1961-2008 -- the full period could be used here, as precipitation was not considered at this stage), due to introduction of the MTW.
+Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions of the analogy criterion (S1) for the $1^{st}$, $5^{th}$, $20^{th}$, and $40^{th}$ analogue rank at the Ulrichen station over the whole calibration period (1961\textendash 2008 \textendash\ the full period could be used here, as precipitation was not considered at this stage), due to introduction of the MTW.
 The shape of the distributions of the conventional approach and the MTW were found to be similar, but the values of the analogy criterion were reduced (shifted to the left) and were, therefore, better.
@@
 	The new performance scores (CRPSS) of the precipitation prediction are provided in Fig.
-\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI} for the 2Z and 2Z-2MI methods, respectively, for the reduced archive (1982--2007).
+\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI} for the 2Z and 2Z-2MI methods, respectively, for the reduced archive (1982\textendash 2007).
 The gains relative to the static approach on the same archive ranged from 0.57 to 2.14 points (\% of CRPSS) for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.
@@
 Among the considered moisture variables (see Sect.
-\ref{sec:reconstruction}), the best proxy was the precipitable water at 45\textdegree\ N and 7.5\textdegree\ E, with a time offset of -6~h (Table \ref{table:proxy_correlations}).
+\ref{sec:reconstruction}), the best proxy was the precipitable water at 45\textdegree\ N and 7.5\textdegree\ E, with a time offset of \textendash 6~h (Table \ref{table:proxy_correlations}).
 Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the disaggregated series using the proxy of precipitable water which are also lower than the conventional method.
@@
 It was in this case of the same magnitude as if the length of the archive doubled.
-Note, that despite the number of candidate situations being four times as many, the gains seem to be lower than for a quadrupled archive length.
+Note, that despite the number of candidate situations being 4 times as many, the gains seem to be lower than for a quadrupled archive length.
 The likely reason is that an actual longer archive would contain more atmospheric situations that might have been observed less frequently during a shorter period.
 Moreover, high correlations between sub-daily circulation patterns are expected.
-The MTW, therefore, did not create four times as many independent data, but the increase in information was nevertheless substantial.
+The MTW, therefore, did not create 4 times as many independent data, but the increase in information was nevertheless substantial.
 In this regards, a reanalysis dataset with a higher temporal resolution might not improve the performance significantly more than a 6-hourly dataset.
@@
 
-	The MTW improved the prediction for days with heavier precipitation, and should improve the prediction of extremes due to better analogue situations, but also due to possible new extreme values resulting from 24-h totals with a certain time shift.
+	The MTW improved the prediction for days with heavier precipitation, and should improve the prediction of extremes due to better analogue situations, but also due to possible new extreme values resulting from 24h totals with a certain time shift.
 However, even though the distribution of analogue precipitation values should move towards the targeted extreme, providing a better prediction, the MTW itself does not allow to predict extreme events that were not yet observed and are, therefore, not present in the archive.
@@
 In addition, sometimes a resolution finer than the daily time step is not needed and another disaggregation technique may be used afterwards.
-Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact than 24-h daily totals.
+Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact than 24h daily totals.
 
@@
 
+	\competinginterests{The authors declare that they have no conflict of interest.}
+
 	\begin{acknowledgements}
@@
 		\caption{Illustration of the principle of a moving time window.
-The target situation is the same for the conventional approach and the MTW, while the candidate situations are four times as many with the MTW.
-The larger horizontal bars represent the 24-h precipitation totals.}
+The target situation is the same for the conventional approach and the MTW, while the candidate situations are 4 times as many with the MTW.
+The larger horizontal bars represent the 24h precipitation totals.}
 		\label{fig:principle}
@@
 		\end{center}
-		\caption{Illustration of the generation of 24-h total moving averages by means of a proportional distribution. The colours refer to the corresponding day of the daily time series.}
+		\caption{Illustration of the generation of 24h total moving averages by means of a proportional distribution. The colours refer to the corresponding day of the daily time series.}
 		\label{fig:illustration_disaggregation}
@@
 		\caption{Performance score (CRPSS) of the AM on the atmospheric circulation at the different stations for (dashed) the full archive, i.e.
-1961-2008; (yellow) the reduced archive, i.e.
-1982-2007; (blue) the introduction of the MTW on the reduced archive; and (green) the recalibrated parameters of the AM with the MTW.}
+1961\textendash 2008; (yellow) the reduced archive, i.e.
+1982\textendash 2007; (blue) the introduction of the MTW on the reduced archive; and (green) the recalibrated parameters of the AM with the MTW.}
 		\label{fig:plots_CRPSS_2Z}
@@
 		\end{center}
-		\caption{Changes in the S1 criterion distributions due to the MTW of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$, and (d) $40^{th}$ analogue ranks for the Ulrichen station over the whole calibration period (1961-2008).}
+		\caption{Changes in the S1 criterion distributions due to the MTW of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$, and (d) $40^{th}$ analogue ranks for the Ulrichen station over the whole calibration period (1961\textendash 2008).}
 		\label{fig:changes_S1_analogs}
@@
 		\end{center}
-		\caption{Distribution of the median improvements of the S1 criterion due to the MTW depending on precipitation thresholds at the Ulrichen station.}
+		\caption{Distribution of the median improvements of the S1 criterion due to the MTW depending on daily precipitation thresholds at the Ulrichen station.}
 		\label{fig:changes_S1_precip_threshold}
@@
 		\includegraphics[width=5cm]{fig11.pdf}
-		\caption{Differences of the CRPSS performance score due to the introduction of the MTW as a function of precipitation thresholds at the Ulrichen station. The stars represent averages.}
+		\caption{Differences of the CRPSS performance score due to the introduction of the MTW as a function of daily precipitation thresholds at the Ulrichen station. The stars represent averages.}
 		\label{fig:changes_CRPS_precip_threshold}
@@
 	\begin{table}[htb]
-		\caption{Value of the coefficient of determination between the reconstructed 6-hourly precipitation time series using the listed variables and the accurate time series for the period 1982-2007.
+		\caption{Value of the coefficient of determination between the reconstructed 6-hourly precipitation time series using the listed variables and the accurate time series for the period 1982\textendash 2007.
 The grid points surrounding the region are: 1) 5\textdegree\ E, 47.5\textdegree\ N; 2) 5\textdegree\ E, 45\textdegree\ N; 3) 7.5\textdegree\ E, 47.5\textdegree\ N; and 4) 7.5\textdegree\ E, 45\textdegree\ N.
@@
 				\multirow{2}{*}{Variable} & \multirow{2}{*}{Point} &  \multicolumn{5}{c}{Time lapse} \\
-				&  & -12 h & -6 h & 0 h & +6 h & +12 h \\ 
+				&  & \textendash 12 h & \textendash 6 h & 0 h & +6 h & +12 h \\ 
 				\hline
@@
 				\hline
-				1982--2007 & 22.57 & 23.14 & 27.11 & 27.71 \\
-				1961--2008 & 23.81 & 24.38 & 28.42 & 28.86 \\
+				1982\textendash 2007 & 22.57 & 23.14 & 27.11 & 27.71 \\
+				1961\textendash 2008 & 23.81 & 24.38 & 28.42 & 28.86 \\
 				\hline

### 2016-12-06 Moving temporal window - HESS/corrections/3 - Submitted and corrected version.tex
Addition of the original version.

%% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
%% ---------------------------------
%% This template should be used for copernicus.cls
%% The class file and some style files are bundled in the Copernicus Latex Package which can be downloaded from the different journal webpages.
%% For further assistance please contact the Copernicus Publications at: publications@copernicus.org
%% http://publications.copernicus.org

%% Please use the following documentclass and Journal Abbreviations for Discussion Papers and Final Revised Papers.

%% 2-Column Papers and Discussion Papers
\documentclass[hess, manuscript]{copernicus}
%\documentclass[hess]{copernicus}

%% Journal Abbreviations (Please use the same for Discussion Papers and Final Revised Papers)

% Archives Animal Breeding (aab)
% Atmospheric Chemistry and Physics (acp)
% Advances in Geosciences (adgeo)
% Advances in Statistical Climatology, Meteorology and Oceanography (ascmo)
% Annales Geophysicae (angeo)
% ASTRA Proceedings (ap)
% Atmospheric Measurement Techniques (amt)
% Advances in Radio Science (ars)
% Advances in Science and Research (asr)
% Biogeosciences (bg)
% Climate of the Past (cp)
% Drinking Water Engineering and Science (dwes)
% Earth System Dynamics (esd)
% Earth Surface Dynamics (esurf)
% Earth System Science Data (essd)
% Fossil Record (fr)
% Geographica Helvetica (gh)
% Geoscientific Instrumentation, Methods and Data Systems (gi)
% Geoscientific Model Development (gmd)
% Geothermal Energy Science (gtes)
% Hydrology and Earth System Sciences (hess)
% History of Geo- and Space Sciences (hgss)
% Journal of Sensors and Sensor Systems (jsss)
% Mechanical Sciences (ms)
% Natural Hazards and Earth System Sciences (nhess)
% Nonlinear Processes in Geophysics (npg)
% Ocean Science (os)
% Proceedings of the International Association of Hydrological Sciences (piahs)
% Primate Biology (pb)
% Scientific Drilling (sd)
% SOIL (soil)
% Solid Earth (se)
% The Cryosphere (tc)
% Web Ecology (we)

%% \usepackage commands included in the copernicus.cls:
%\usepackage[german, english]{babel}
%\usepackage{tabularx}
%\usepackage{cancel}
%\usepackage{multirow}
%\usepackage{supertabular}
%\usepackage{algorithmic}
%\usepackage{algorithm}
%\usepackage{amsthm}
%\usepackage{float}
%\usepackage{subfig}
%\usepackage{rotating}

\usepackage[utf8]{inputenc}

\begin{document}

\linenumbers

\title{The Analogue Method for Precipitation Forecasting: Finding Better Analogue Situations at a Sub-Daily Time Step}

% \Author[affil]{given_name}{surname}

\Author[1,2]{Pascal}{Horton}
\Author[3]{Charles}{Obled}
\Author[1]{Michel}{Jaboyedoff}

\affil[1]{University of Lausanne, Lausanne, Switzerland}
\affil[2]{Institute of Geography \& Oeschger Centre for Climate Change Research, University of Bern, Bern, Switzerland}
\affil[3]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}

%% The [] brackets identify the author with the corresponding affiliation. 1, 2, 3, etc. should be inserted.

\runningtitle{Finding Better Analogue Situations at a Sub-Daily Time Step}

\runningauthor{P. Horton et al.}

\correspondence{Pascal Horton (pascal.horton@alumnil.unil.ch)}

\received{}
\pubdiscuss{} %% only important for two-stage journals
\revised{}
\accepted{}
\published{}

%% These dates will be inserted by Copernicus Publications during the typesetting process.

\firstpage{1}

\maketitle

\begin{abstract}
The Analogue Method (AM) aims at forecasting local weather variables (predictands), such as precipitations, by means of a statistical relationship with predictors at a synoptic scale. The analogy is generally assessed in the first place on the geopotential field by mean of a comparison of the gradients, in order to sample the days with a similar atmospheric circulation.

The search for candidate situations, for a given target day, is usually undertaken by comparing the state of the atmosphere at fixed hours of the day, for both the target day and the candidate analogues. The constraint being the use of daily time series, due to the length of available archives they provide, and the unavailability of equivalent archives at a finer time step. However, it is unlikely that the best analogy happens at the very same hour, but it may occur at a different time of the day. In order to assess the potential of finding better analogues at a different hour, a moving time window (MTW) has been introduced on a reduced archive of hourly precipitation totals.

The MTW resulted in a better analogy in terms of the atmospheric circulation, with improved values of the analogy criteria on the whole distribution of analogue dates. The improvement was found to grow with the analogue ranks due to an accumulation of more similar situations in the selection. Moreover, the improvement is even more important for days with heavy precipitation events, which are generally related to more dynamic atmospheric situations, where timing is more specific.

A seasonal effect has also been identified, with larger improvements in winter than in summer, supposedly due to the stronger effect of the diurnal cycle in summer, which favors predictors at the same hour for target and analogues.

The impact of the MTW on the prediction performance has been assessed by means of a sub-daily precipitation series transformed into moving 24~h-totals at a 6-hourly time step. This resulted in an improvement of the prediction skills, which were even larger after recalibrating the AM parameters.

However, attempts to reconstruct longer precipitation series of running 24~h-totals by means of simple methods failed. It emphasized the need to use time series with an appropriate chronology. These should be available in a near future, either by means of growing observed archives, or by the establishment of precipitation reanalyses through regional modeling. Then, the use of a MTW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.

\end{abstract}

\introduction  %% \introduction[modified heading if necessary]
\label{sec:introduction}

The Analogue Method (AM) is based on the principle that two relatively similar synoptic situations may produce relatively similar local effects \citep{Lorenz1956, Lorenz1969}. Multiple variations of the methods exist and listings can be found in \citet{Horton2016} or \citet{BenDaoud2015}. The versions that will be considered here are often used as references or benchmarks for various improvements.

The first method is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005, Marty2012}. Searching analogue situations for a target day starts by a preselection step of the potential candidate for analogy. Here, it has been limited to the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects. Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score ($S_{\text{TW}}$), which is a comparison of gradients, over a certain spatial window and at certain hours. The smaller the $S_{\text{TW}}$ values, the more similar the pressure fields.

The predictand, here a 24~h precipitation total, results from meteorological situations that are continuous transitions between changing circulation patterns. Thus, the observed predictors fields, extracted from reanalysis datasets, are considered at different time of the day and at different heights. In our case, the geopotential height is considered at 1000~hPa (Z1000) at 12~h~UTC and 500~hPa (Z500) at 24~h~UTC. The selection of the observation time of the predictor was found by \citet{Bontron2004} to have a significant influence.

Then, $N_{1}$ dates with the lowest values of $S_{\text{TW}}$ are considered as analogues to the target day, $N_{1}$ being a parameter to calibrate. Then, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day. Following the nomenclature proposed by \citet{Horton2016}, this method will be named 2Z.

The second reference method adds a subsequent level of analogy on moisture variables, compared by means of the root-mean-square error ($E_{\text{RMS}}$) (method 2Z-2MI, Table \ref{table:method_2Z-2MI}). This second predictor is a moisture index made of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850) \citep{Bontron2004}. When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations. When a second level of analogy is added, a higher number of $N_{1}$ analogues is kept on the first level.

To calibrate the method, the commonly used technique is a semi-automatic sequential procedure elaborated by \citet{Bontron2004}. AtmoSwing \citep{Horton2016}, which implements this technique, was used in order to calibrate the parameters in the present study. The score that is most often considered to assess an AM performance is the Continuous Ranked Probability Score \citep[$S_{\text{CRP}}$,][]{Brown1974, Matheson1976, Hersbach2000}. It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$. The better the forecast, the smaller the score. It is defined as follows:

\begin{equation}
\label{eq:CRPS}
S_{\text{CRP}} = \int_{-\infty}^{+\infty} \left[ F(y)-\text{H}(y-y^{0})\right]^{2} \text{d}y ,  
\end{equation}
where $\text{H}(y-y^{0})$ is the Heaviside function that is null when $y-y^{0}<0$, and has the value 1 otherwise. \citet{Bontron2004} proposed a decomposition of this score interpreted into a sharpness and an accuracy terms.

In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution as the reference. The Continuous Ranked Probability Skill Score ($S_{\text{SCRP}}$) is thus defined as following:

\begin{equation}
\label{eq:CRPSS}
S_{\text{SCRP}} = \frac{S_{\text{CRP}}-S_{\text{CRP}}^{r}}{S_{\text{CRP}}^{p}-S_{\text{CRP}}^{r}} = 1-\frac{S_{\text{CRP}}}{S_{\text{CRP}}^{r}}
\end{equation}
where $S_{\text{CRP}}^{r}$ is the $S_{\text{CRP}}$ value for the reference (climatological distribution) and $S_{\text{CRP}}^{p}$ would be the one for a perfect forecast (which implies $S_{\text{CRP}}^{p}~=~0$). A better forecast is characterized by an increase in $S_{\text{SCRP}}$.

The AM is usually implemented with a daily time step, due to the availability of long precipitation archives that have no equivalent at a finer resolution. Therefore, the analogue situations are assessed on the basis of a daily time step, by comparing predictors at fixed hours of the day, otherwise one would not know what precipitation values to assign to them. However, it can be expected that the analogy of the synoptic situations does not occur systematically at the same time of the day, and that better candidates can be found by shifting to a different hour. On this assumption, a moving time window (MTW) was introduced to allow searching for candidates at different hours of the day.

Previous tests showed the benefit, in terms of analogy criteria values, of searching for analogue synoptic situations at a finer time step, but without assessing the impact on the forecast skills \citep{Finet2008}. In order to assess this potential improvement of the prediction, precipitation data with a resolution of 10 minutes, on a respectable archive length, was used (Sect. \ref{sec:data}). It was then aggregated in the form of 24~h-totals, but starting at different 6-hourly time step, by means of a moving total (Sect. \ref{sec:method}).

One can question the interest of using daily totals when a 6-hourly precipitation series can be used. The first reason is that the 6-hourly time series generated by the AM may not represent well the dynamic of the accurate precipitation (results not shown), due to a smoothed signal. Then, sometimes one just does not need finer resolution than the daily time step. Finally, when using a reconstructed precipitation archive, the errors in intra-day precipitation distributions have a lesser impact over 24~h daily totals.

The MTW is explained in Sect. \ref{sec:method}. As this method requires sub-daily time series, the available archive length is reduced compared to more common daily measurements, which has some consequences on the performance score (Sect. \ref{sec:archive_reduction}). The benefit of introducing a MTW was assessed first in regards to the analogy criteria improvement (Sect. \ref{sec:influence_criteria}), and then in terms of precipitation prediction skill (Sect. \ref{sec:influence_scores}). Finally, attempts were made to reconstruct longer 24~h-total precipitations series (Sect. \ref{sec:attempts}).

\section{Data and method}

\subsection{Study area and data}
\label{sec:data}

The study area is the upper Rh\^{o}ne catchment in Switzerland \cite[see also][]{Horton2012a}. Due to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed. The time series (on the period 1982--2007) come from 6 automatic weather stations, namely Ulrichen, Zermatt, Visp, Montana, Sion and Aigle (Fig. \ref{fig:map}), which are subject to various meteorological influences \citep{Horton2012}. The results will thereafter be presented arbitrarily for the Ulrichen station, but they are equivalent for all stations. The precipitation time series were then aggregated by means of a moving 24~h-total (see next section).

Predictors are extracted from the NCEP/NCAR reanalysis I \citep{Kalnay1996} dataset with a 6-hourly temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree.

\subsection{The moving time window (MTW) approach}
\label{sec:method}

In order to assess the benefit of searching analogue situations at a sub-daily time step, an appropriate precipitation series is required. On the basis of high resolution time series (Sect. \ref{sec:data}), 24~h-totals were processed, but at a 6-hourly time step (temporal resolution of the reanalysis dataset), by means of a moving 24~h-total.

The target situations and their corresponding observed precipitation values (used for validation) do not change, because the forecast is always established for a fixed period of the target day (6--30~h), as before. The difference is that the candidates are 4~times more numerous (Fig. \ref{fig:principle}).

Based on some preliminary tests (not shown), no constraint was added in order to restrict the selection of multiple analogues within the same candidate dates.

\subsection{Consequences of the archive reduction}
\label{sec:archive_reduction}

As sub-daily precipitation time series are usually available on a shorter period than traditional daily time steps, the first assessment consists in assessing the loss of performance resulting from a reduction of a 47~years archive (1961 to 2008) to 25~years (1982 to 2007). This change is assessed with the original method, without MTW.

Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered. The AM parameters were calibrated using AtmoSwing \citep{Horton2016} on the original archive (Tables \ref{table:params_2Z} and \ref{table:params_2Z-2MI}) and will be used thereafter.

The impact of the change in the archive length is summarized in Table \ref{table:loss_reduction} for both 2Z and 2Z-2MI methods. As expected, a loss of performance can be observed for each station, except for that of Aigle, which seems relatively indifferent to this change. This loss is globally significant, with up to -1.89 points for Visp and the 2Z method.

\section{Results and discussion}

\subsection{Influence on the analogy criteria}
\label{sec:influence_criteria}

\subsubsection{Changes in the atmospheric circulation analogy}

When searching for analogues on the geopotential heights, as in the 2Z method, there are now 4 times more candidates than before, which obviously allows to find better matches.

Figure \ref{fig:changes_S1_analogues} presents the changes in the distributions of the $S_{\text{TW}}$ criterion for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogues for the Ulrichen station on the whole calibration period, due to introduction of the MTW. The precipitation target remains as before, that is centered on 18~h~UTC (6~h~UTC to 6~h~UTC the next day). The shapes of the distributions of the conventional approach and the MTW are similar, but the values of the analogy criteria are now reduced (shifted to the left), and therefore better. An increase in the difference between a fixed window and a moving window is identifiable, which means that the last analogues are further improved. The latter effect is due to the accumulation of improvements brought by the new analogue situations in the selection.

The improvements of the $S_{\text{TW}}$ criteria are summarized in Fig. \ref{fig:changes_S1}, which shows (top) quantiles of the $S_{\text{TW}}$ criteria according to the analogue rank for the conventional method and the MTW, and (bottom) quantiles of the relative reduction. This confirms that all quantile seem similarly reduced ($S_{\text{TW}}$ distributions keep their shape), and that this improvement is constantly increasing from the first to the last analogue (Fig. \ref{fig:changes_S1} bottom).

The median of the $S_{\text{TW}}$ values reduction (Fig. \ref{fig:changes_S1} bottom) starts approximately at 5~\% for the first analogue and reaches more than 10~\% for the last one. This increasing trend with the analogue rank can be explained by the accumulation of better analogues in the distribution. The minimum improvement starts from 0 and reaches 2--3\%, meaning that the criteria have been improved on most analogues for every day of the calibration period. All other stations have a similar improvement of the $S_{\text{TW}}$ criteria, both in terms of distribution shape and amplitude.

\subsubsection{Influence of the weather situation}
\label{sec:influence_precip}

It can be assumed that the atmospheric conditions with a low dynamism, such as the frequent anticyclonic situations, will not be radically improved by the introduction of the MTW. Conversely, dynamic situations, such as weather disturbances, have a well marked temporal evolution. Indeed, the position of the driving elements such as the low-pressure center and the fronts change significantly during a day. We can therefore expect to improve more significantly these situations with a higher dynamism when introducing a MTW, as better matches to the target situation may be found.

The dynamism of a given atmospheric condition cannot be easily quantified. A basic assumption is considered here, which stipulates that the more a day is rainy, the more dynamic the situation is. The results of this analysis are summarized in Fig. \ref{fig:changes_S1_precip_threshold} by the median reduction of $S_{\text{TW}}$ for days with precipitation (organized into classes) between two thresholds. The number of cases per class being reduced, the curves are not as smooth as in previous analyzes. It is nevertheless clear that the improvement tends to increase on days with higher precipitation. This is true for all our stations and confirms our intuition.

\subsubsection{Seasonal effect}
\label{sec:seasonal_effect}

Atmospheric dynamics varies greatly from one season to another, which reflects on the performance of the AM that is generally lower between June and August \citep{Bliefernicht2010}. It therefore makes sense to verify the effect of the MTW separately per season.

A seasonal effect can be observed on the reduction of the $S_{\text{TW}}$ criteria due to the MTW (Fig. \ref{fig:changes_S1_seasons}). The improvements are greater for winter than summer. One hypothesis is that the diurnal effects of the summer months have an influence on the atmospheric circulation, at least in the lower layers. This effect is based on the daily cycle and good analogues are essentially found for the same hours or time windows.

An analysis of the selected hours for the geopotential predictor seems to confirm this assumption (Fig. \ref{fig:hours_selection_per_season}). It was found that the new choice of the temporal window in winter, when using the MTW approach, is well balanced between the 4 options. This means a change of 75\% of the analogues selection compared to the conventional approach, which improves the circulation analogy.

On the contrary, the summer months have a preference for the initial temporal window (Z500 24~h \& Z1000 12~h), due to more pronounced diurnal effects which reduces the potential for improvement of the criteria. Other seasons are between these two extremes, which is consistent with their respective improvements. This seasonal effect was observed for each station in a very similar way, and generally even with a slightly larger amplitude than for Ulrichen (see example of the Visp station in Fig. \ref{fig:hours_selection_per_season_Visp}).

\subsubsection{Changes in the moisture analogy}

When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidates situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogues, but their dates have changed. In contrast to earlier, both a reduction or an increase of the $E_{\text{RMS}}$ analogy criterion values are possible. Indeed, Fig. \ref{fig:changes_RMSE} shows an almost insignificant improvement of the $E_{\text{RMS}}$ values. Unlike for the first level of analogy, the relative improvement of the $E_{\text{RMS}}$ values are distributed relatively symmetrically around zero, with improvements and losses of the same amplitude. Once again, the results for the other stations are similar.

This result of a globally null improvement of the $E_{\text{RMS}}$ values does not mean that the 2Z-2MI method cannot be improved by the MTW. It means that after the selection of the analogues situations in terms of the synoptic circulation, the new candidate dates do not allow to find better analogues in terms of moisture. However, the selected dates have changed in the first level of analogy, and thus also in the final selection, which can potentially improve the performance scores on the predictand.

\subsection{Impact on performance scores}
\label{sec:influence_scores}

A systematic improvement of the $S_{\text{TW}}$ values was previously observed. However, finding better analogue situations does not obligatory imply better skills to predict the precipitation. Therefore, the impact of the MTW introduction, and thus the selection of other analogue dates, has to be assessed on the performance scores. In order to perform this assessment, the 24~h-totals (moving average) at a 6-hourly time step were used (see Sect. \ref{sec:data}). The target dates remain unchanged, since the original time slot (6~h~UTC -- 6~h~UTC the next day) is kept, and thus the performance scores can be directly compared with the former ones.

The new performance scores are provided in Table \ref{table:CRPSS_MTW}, along with the differences regarding the conventional method with the same archive length. The differences ranges from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method. The introduction of the MTW brings an improvement of the performance that is not very large, but that is nevertheless significant. Moreover, it requires no additional predictor. No relationship was found between the improvement of the score and the reduction of the $S_{\text{TW}}$ criteria, neither with the season.

\subsubsection{Improvement by precipitation classes}
\label{sec:improvement_CRPSS_precip_threshold}

The $S_{\text{TW}}$ criteria was previously found to be improved to a greater extent for the most dynamic situations related with higher precipitation values (Sect. \ref{sec:influence_precip}). The changes in terms of performance scores will now be assessed regarding precipitation thresholds. Fig. \ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, other stations having the same behavior.

The increasing positive trend of skill improvements regarding the precipitation threshold is significant and shows that the prediction of higher precipitation totals is further improved. Thus, both the analogy criteria and the performance scores are improved to a greater extent for heavier precipitation events. On the contrary, the non-rainy days and small accumulations are not improved.

\subsubsection{Effect of recalibrating the parameters}
\label{sec:recalibration}

The previous assessment of the performance improvement was established with the original parameters optimized with a fixed time window. However, one can assume that the introduction of the MTW may change the optimum of some parameters. The calibration has then been reprocessed.

After recalibrating, some changes in the optimal parameters can be observed for both 2Z (Table \ref{table:params_2Z_new}) and 2Z-2MI methods (Table \ref{table:params_2Z-2MI_new}). Among these, the east-west dimension of the spatial windows of the circulation analogy tends to decrease. More significantly, the optimal number of analogues increases after introducing the MTW, of a significant order of magnitude: 25~\% to 83~\% for the 2Z method and 20~\% 67~\% for the 2Z-2MI method. The number of analogues of the first analogy level of the 2Z-2MI method even reached three times its previous value for the Visp station. It seems as if the method perceive the increase in the archive length and diversity by allowing to extract more analogues. As we saw in Fig. \ref{fig:changes_S1}, the improvement of the $S_{\text{TW}}$ criteria grows along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions. It seems thus profitable to widen the selection of analogues in order to keep also some whose rank has increased, as they appear to be also relevant to predict precipitation values. The number of good analogues is thus globally increased.

This increase in number of analogues has a slight effect on the performance of the different precipitation classes. The same analysis as in Sect. \ref{sec:improvement_CRPSS_precip_threshold} has been performed again on the basis of the newly calibrated parameters. The results are generally very similar, but a slight performance increase of small precipitation values can be observed at the expense of higher amounts. The change in the analogues numbers is likely to be responsible for this difference in the performance distributions.

The values of the $S_{\text{SCRP}}$ scores for both methods (Table \ref{table:CRPSS_recalibration}) have significantly increased after recalibration. With the introduction of the MTW, the performance loss related to the reduction of the archive length is compensated.

\subsubsection{Changes in sharpness and accuracy}

The $S_{\text{CRP}}$ score can be decomposed into two components, namely sharpness and accuracy \citep[see][]{Bontron2004}. The impact of the MTW has been analyzed on these components and the results can be found in Table \ref{table:CRPSS_decomposition_no_recalibration} for the original parameters and in Table \ref{table:CRPSS_decomposition_recalibration} for the re-calibrated methods. The changes are expressed relative to the total $S_{\text{CRP}}$. Both components do not have the same value ranges: accuracy is in our case almost twice the sharpness values. Since the $S_{\text{CRP}}$ is considered here and not the $S_{\text{SCRP}}$, improved prediction capacity results in a lower score. A decrease of the score is thus desirable.

It appears that the sharpness is a bit inferior with the MTW in favor of accuracy (Table \ref{table:CRPSS_decomposition_no_recalibration}). When using the recalibrated parameters, the components are a bit more balanced, but still the accuracy prevails on the sharpness (Table \ref{table:CRPSS_decomposition_recalibration}). Fig. \ref{fig:CRPSS_decomposition_precip_thresholds} illustrates the changes (relative to the total $S_{\text{CRP}}$) in sharpness and accuracy for different precipitation thresholds at the Ulrichen station. Be it for the 2Z or 2Z-2MI method, the original or the recalibrated parameters, the changes are similar: the improvements concern the accuracy over the sharpness, and this to a greater extent for significant precipitation events. The MTW does not allow to improve the sharpness, but the improvement in accuracy is significant, and this especially for the days with heavy precipitation. In terms of the predicted precipitation distribution, it means that the median of the prediction is closer to the observed values, while the distribution is not more condensed than previously.

\section{Application attempts on the full archive}
\label{sec:attempts}

The improvement provided by the MTW is interesting, mainly for heavy precipitation events, and thus it would be profitable to be able to apply it to the complete archive. Unfortunately, there is no long precipitation time series available with a sub-daily time step. In order to reconstruct a longer archive of moving 24~h-totals, different disaggregation approaches of the daily time series were assessed and are presented in the following sections.

\subsection{Proportional distribution}

A proportional distribution is certainly the simplest approach that can be performed. It consists in allocating proportional parts of the original daily time series into a new moving average of 24~h-totals (Fig. \ref{fig:illustration_disaggregation}). When using this reconstructed time series on the shorter period, the method performance was degraded (Table \ref{table:disaggregation_proportional} to compare to Table \ref{table:CRPSS_MTW}) and was even below the conventional method without MTW (Table \ref{table:loss_reduction}). The benefit of a better selection of the analogue situations is lost due to a precipitation archive of poor quality.

\subsection{Use of a proxy variable}

As demonstrated in the previous section, the performance improvement brought by the MTW is lost when using a simplistic precipitation time series. In order to get closer to the chronology of the actual precipitation, the reconstruction procedure must rely on some informative variable. Data from the NCEP/NCAR reanalysis 1 (Sect. \ref{sec:data}) was used in this perspective, despite their rough resolution.

The first step consisted in determining which variables from the precipitable water or the relative humidity (at 1000~hPa, 925~hPa or 850~hPa) produces the precipitation chronology that is the most correlated (on non-zero values) with the accurate 6-hourly precipitation time series on the period 1982-2007. The location of the most predictive point from the reanalysis grid had to be assessed (closest points: 5--7.5° E and 45--47.5° N), as well an eventual time lapse between both series, due to the significant distance separating the weather stations and the reanalysis grid point. The most relevant point will probably not be the same for all stations, since one can expect to find the optimum in the direction of the main moisture inflows for the station. This assessment must be carried out for each station.

The results of the correlation analyses (on non-zero values) between the new series reconstituted using the proxy and the actual series are illustrated in Table \ref{table:proxy_correlations} for Zermatt (on the short period, 1982--2007). The best proxy is the precipitable water at 45° N and 7.5° E, with a time offset of -6~h. The determination coefficient of 0.721 is higher than that of the series from the proportional distribution (0.698), which confirms that a little information was added to the series of precipitation.

Table \ref{table:proxy_CRPSS} presents the $S_{\text{SCRP}}$ scores obtained by the reconstituted series using the proxy of precipitable water at the optimal point (Table \ref{table:proxy_correlations}). A slight improvement can be obtained compared to the proportional distribution method, but it is still relatively small, and most of the benefit of the MTW is again lost.

These attempts to transpose the MTW on the total archive highlight the importance of the actual rainfall chronology. The MTW is profitable, provided that the precipitation series are close to the observed one. Without precipitation series with an accurate sub-daily chronology, the introduction of a MTW remains fruitless.

\conclusions  %% \conclusions[modified heading if necessary]

The AM is most often based on a daily time step, due to the availability of long precipitation archives. However, it is unlikely that two analogue synoptic situations, that evolve relatively quickly, would correspond optimally at the same hour of the day. It is thus more likely that a better match can be found at another time, which can change the selection of the analogues dates.

As \citet{Finet2008} had previously shown, the introduction of a MTW allows finding better analogue situations in terms of the atmospheric circulation. It has been here demonstrated that the improvement of the $S_{\text{TW}}$ criteria values is growing with the rank of the analogue. This is due to the accumulation of better analogues within the predicted distributions.

The improvement of the circulation analogy was found to be more important for heavy precipitation events, which are generally related to more dynamic atmospheric situations. This dynamism implies more specific circulation patterns that are evolving more rapidly. Thus, a MTW is found to be of particular interest in this kind of situation, and benefits the prediction of extreme precipitation events.

A seasonal effect has been highlighted, as the MTW is more profitable for winter months than summer. The reason is likely that the diurnal cycle has a bigger effect in summer than in winter, which results in better analogues at the same time of the day. The preference for the same hours in summer has been demonstrated, whereas 75\% of the analogue situations are selected at a different time in winter.

The impact of the MTW on the prediction performance has never been assessed before, due to the shortcoming of long precipitation series at a sub-daily time step. The impact of the MTW approach could be assessed on a 25 years time series with a high temporal resolution. After the introduction of the MTW, the performance scores increased of the same order of magnitude as if the length of the archive doubled, in this case study.

The parameters were then calibrated again, using the MTW. Some parameters changed, the main difference being the number of analogues, which systematically and significantly increased compared to the original set. A wider selection of analogue situations, containing those whose rank decreased, seemed profitable for the prediction performance. The number of good analogues is thus globally increased. This change seems to benefit mainly the prediction of days with small precipitation totals.

The importance of the quality of the precipitation archive was also demonstrated, as too simplistic reconstructions of 6-hourly time series lead to a loss of all the improvement brought by better analogue situations identified by the MTW. The precipitation prediction is improved only when the precipitation chronology is close to the accurate one. Attempts to reconstruct longer time series based on a simplistic proportional distribution or using meteorological variables from the NCEP reanalysis 1 dataset as proxy did not succeed. Other reanalysis datasets could eventually preform better.

Perspectives of using the MTW rely on the availability of long precipitation series at a sub-daily time step and with high accuracy. The first source of such data is the simple fact that with time, these archives of high temporal resolution precipitation data are getting longer. The second source is the establishment of precipitation reanalysis at a country scale, or the use of reanalysis-driven RCMs (Regional Climate Models) or LAMs (Limited Area Models) on a long period. When such precipitation data will be available, the use of a MTW in the AM should be considered for any application, especially when the prediction quality of extreme events is important.

\begin{acknowledgements}
Thanks to Dominique B\'{e}rod for his support and to Renaud Marty for his fruitful collaboration over the years.

Thanks to the Swiss Federal Office for Environment (FOEV), the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton and the Water, Land and Sanitation Service of the Vaud Canton who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.

The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.

NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/. Precipitation time series provided by MeteoSwiss. 
\end{acknowledgements}

%% REFERENCES

%% The reference list is compiled as follows:

\bibliographystyle{copernicus}
\bibliography{../_refs/_articles-moving-window}

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.3cm]{figures/figure_map.pdf}
	\end{center}
	\caption{Position of the 6 weather stations of interest (Ulrichen, Zermatt, Visp, Montana, Sion and Aigle) in the study area.}
	\label{fig:map}
\end{figure}

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.3cm]{figures/illustration_moving_window.pdf}
	\end{center}
	\caption{Illustration of the principle of a moving time window. The larger horizontal bars represent the 24~h precipitation totals.}
	\label{fig:principle}
\end{figure}

\begin{figure*}[htb]
	\begin{center}
		\includegraphics[width=15cm]{figures/changes_S1_analogues.pdf}
	\end{center}
	\caption{Changes in the $S_{\text{TW}}$ criteria distributions of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$ and (d) $40^{th}$ analogue ranks for the Ulrichen station, due to the MTW.}
	\label{fig:changes_S1_analogues}
\end{figure*}

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.2cm]{figures/changes_S1_value_and_gain.pdf}
	\end{center}
	\caption{Synthesis of the changes in the $S_{\text{TW}}$ criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analogue. (a) Quantiles of the $S_{\text{TW}}$ distributions with and without the MTW. (b) Quantiles of the relative improvements of the S1 criteria when using the MTW.}
	\label{fig:changes_S1}
\end{figure}

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.3cm]{figures/changes_S1_precip_threshold.pdf}
	\end{center}
	\caption{Distribution of the median improvements of the $S_{\text{TW}}$ criteria, due to the MTW, depending on precipitation thresholds at the Ulrichen station.}
	\label{fig:changes_S1_precip_threshold}
\end{figure}

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=7cm]{figures/changes_S1_seasons.pdf}
	\end{center}
	\caption{Seasonal effect on the median reduction of the $S_{\text{TW}}$ criteria for the Ulrichen station due to the MTW. DJF: winter, MAM: spring, JJA: summer SON: fall.}
	\label{fig:changes_S1_seasons}
\end{figure}

\begin{figure}[htb]
	\includegraphics[width=8.3cm]{figures/hours_selection_per_season.pdf}
	\caption{Distribution of the predictors hours in the selected analogue dates depending on the season, for the Ulrichen station.}
	\label{fig:hours_selection_per_season}
\end{figure}

\begin{figure}[htb]
	\includegraphics[width=8.3cm]{figures/hours_selection_per_season_Visp.pdf}
	\caption{Distribution of the predictors hours in the selected analogue dates depending on the season, for the Visp station.}
	\label{fig:hours_selection_per_season_Visp}
\end{figure}

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.1cm]{figures/changes_RMSE_value_and_gain.pdf}
	\end{center}
	\caption{Synthesis of the changes in the $E_{\text{RMS}}$ criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analogue. (a) Quantiles of the $E_{\text{RMS}}$ distributions with and without the MTW. (b) Quantiles of the relative improvements of the $E_{\text{RMS}}$ criteria when using the MTW.}
	\label{fig:changes_RMSE}
\end{figure}

\begin{figure}[htb]
	\includegraphics[width=5cm]{figures/changes_CRPS_precip_threshold.pdf}
	\caption{Differences of the $S_{\text{SCRP}}$ performance score, due to the introduction of the MTW, as a function of precipitation thresholds at the Ulrichen station. The stars represent averages.}
	\label{fig:changes_CRPS_precip_threshold}
\end{figure}

\begin{figure*}[htb]
	\begin{center}$
		\begin{array}{cccc}
		\includegraphics[width=16cm]{figures/components.pdf}
		\end{array}$
	\end{center}
	\caption{Influence (\%) of the MTW on the $S_{\text{CRP}}$ components (accuracy and sharpness) relatively to the total $S_{\text{CRP}}$, for the 2Z and 2Z-2MI methods, according to different precipitation thresholds. The results are presented for (top) the original parameters, and (bottom) the recalibrated parameters. Improved prediction results in a lower score.}
	\label{fig:CRPSS_decomposition_precip_thresholds}
\end{figure*}

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8cm]{figures/illustration_disaggregation.pdf}
	\end{center}
	\caption{Illustration of the generation of 24~h-totals moving averages by means of a proportional distribution. The colours refer to the corresponding day of the daily time series.}
	\label{fig:illustration_disaggregation}
\end{figure}

\clearpage

\begin{table}[htb]
	\caption{Parameters of the reference method on the atmospheric circulation (2Z). The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window). The criteria used for the current level of analogy is then provided, as well as the number of analogues.}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccc}
			\hline
			Level & Variable & Hour & Criteria & Nb \\ 
			\hline 
			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{$S_{\text{TW}}$} & \multirow{2}{*}{$N_{1}$} \\
			& Z500 & 24~h & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:method_2Z}
\end{table}

\begin{table}[htb]
	\caption{Parameters of the reference method with moisture variables (2Z-2MI). Same conventions as Table \ref{table:method_2Z}}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccc}
			\hline 
			Level & Variable & Hour & Criteria & Nb \\ 
			\hline 
			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{$S_{\text{TW}}$} & \multirow{2}{*}{$N_{1}$} \\
			& Z500 & 24~h & & \\ 
			\hline
			\multirow{2}{*}{2} & TPW * RH850 & 12~h & \multirow{2}{*}{$E_{\text{RMS}}$} & \multirow{2}{*}{$N_{2}$} \\
			& TPW * RH850 & 24~h & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:method_2Z-2MI}
\end{table}

\begin{table}[htb]
	\caption{Calibrated parameters (spatial windows and number of analogues) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) and skill score (\%) of the method on the full archive.}
	\begin{center}
		\begin{tabular}{l c c c c }
			\hline
			Station & Long (° E) & Lat (° N) & $N_{1}$ & $S_{\text{SCRP}}$ \\
			\hline
			Ulrichen & 0 $\rightarrow$ 17.5 & 42.5 $\rightarrow$ 47.5 & 40 & 30.73 \\
			Zermatt & 0 $\rightarrow$ 20 & 37.5 $\rightarrow$ 50 & 35 & 23.87 \\
			Visp & -2.5 $\rightarrow$ 20 & 40 $\rightarrow$ 47.5 & 30 & 25.11 \\
			Montana & -2.5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 47.5 & 40 & 32.55 \\
			Sion & -2.5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 47.5 & 40 & 26.23 \\
			Aigle & -5 $\rightarrow$ 17.5 & 40 $\rightarrow$ 50 & 50 & 30.59 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:params_2Z}
\end{table}

\begin{table}[htb]
	\caption{Parameters of the moisture variables from the 2Z-2MI method and the corresponding skill score (\%) on the complete archive. The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z}, except the number of analogues of the first analogy level ($N_{1}$), which are here different. The $5^{th}$ column is the number of analogues for the second level ($N_{2}$).}
	\begin{center}
		\begin{tabular}{l c c c c c }
			\hline
			Station & Long (° E) & Lat (° N) & $N_{1}$ & $N_{2}$ & $S_{\text{SCRP}}$ \\
			\hline
			Ulrichen & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 60 & 25 & 34.31 \\
			Zermatt & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 55 & 25 & 28.28 \\
			Visp & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 45 & 25 & 28.85 \\
			Montana & 5 $\rightarrow$ 7.5 & 45 $\rightarrow$ 47.5 & 55 & 30 & 36.11 \\
			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 90 & 30 & 31.16 \\
			Aigle & 7.5 & 45 $\rightarrow$ 47.5 & 100 & 35 & 35.82 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:params_2Z-2MI}
\end{table}

\begin{table}[htb]
	\caption{Influence of the archive reduction on the $S_{\text{SCRP}}$. $S_{\text{SCRP}}$ values are provided for both considered methods and the differences are expressed in absolute value.}
	\begin{center}
		\begin{tabular}{l c c c c }
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
			& 82-07 & $\Delta$ & 82-07 & $\Delta$ \\ 
			\hline
			Ulrichen & 29.37 & -1.36 & 33.24 & -1.08 \\
			Zermatt & 22.20 & -1.67 & 26.95 & -1.32 \\
			Visp & 23.23 & -1.89 & 27.77 & -1.08 \\
			Montana & 30.79 & -1.76 & 34.77 & -1.34 \\
			Sion & 24.78 & -1.45 & 29.36 & -1.80 \\
			Aigle & 30.57 & -0.01 & 35.95 & 0.13 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:loss_reduction}
\end{table}

\begin{table}[htb]
	\caption{New $S_{\text{SCRP}}$ performance scores for both 2Z and 2Z-2MI methods obtained by the MTW approach. The differences are expressed regarding the conventional method with the same archive length.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& MTW & $\Delta$ & MTW & $\Delta$ \\
			\hline
			Ulrichen & 31.12 & 1.74 & 35.44 & 2.20 \\
			Zermatt & 24.34 & 2.14 & 28.92 & 1.97 \\
			Visp & 24.39 & 1.16 & 29.42 & 1.64 \\
			Montana & 31.59 & 0.80 & 36.30 & 1.53 \\
			Sion & 25.35 & 0.57 & 31.07 & 1.71 \\
			Aigle & 31.78 & 1.21 & 38.11 & 2.16 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:CRPSS_MTW}
\end{table}

\begin{table}[htb]
	\caption{Calibrated parameters (spatial windows and number of analogues) for the analogy on the geopotential at 500~hPa and 1000~hPa (method 2Z) with the MTW approach.}
	\begin{center}
		\begin{tabular}{l c c c }
			\hline
			Station & Long (° E) & Lat (° N) & $N_{1}$ \\
			\hline
			Ulrichen & 0 $\rightarrow$ 17.5 & 42.5 $\rightarrow$ 50 & 50 \\
			Zermatt & 0 $\rightarrow$ 17.5 & 40 $\rightarrow$ 50 & 55 \\
			Visp & -2.5 $\rightarrow$ 20 & 40 $\rightarrow$ 50 & 55 \\
			Montana & -2.5 $\rightarrow$ 15 & 42.5 $\rightarrow$ 47.5 & 55 \\
			Sion & -2.5 $\rightarrow$ 15 & 37.5 $\rightarrow$ 50 & 55 \\
			Aigle & -2.5 $\rightarrow$ 15 & 40 $\rightarrow$ 50 & 75 \\
			\hline
		\end{tabular}
	\end{center}
	\label{table:params_2Z_new}
\end{table}

\begin{table}[htb]
	\caption{Parameters of the moisture variables from the 2Z-2MI method with the MTW approach. The parameters for the atmospheric circulation are the same as in Table \ref{table:params_2Z_new}, except the number of analogues of the first analogy level ($N_{1}$), which are here different. The $5^{th}$ column is the number of analogues for the second level ($N_{2}$).}
	\begin{center}
		\begin{tabular}{l c c c c }
			\hline
			Station & Long (° E) & Lat (° N) & $N_{1}$ & $N_{2}$ \\
			\hline
			Ulrichen & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 110 & 35 \\
			Zermatt & 7.5 & 45 $\rightarrow$ 47.5 & 80 & 30 \\
			Visp & 7.5 & 45 $\rightarrow$ 47.5 & 135 & 35 \\
			Montana & 5 $\rightarrow$ 7.5 & 45 & 110 & 40 \\
			Sion & 5 $\rightarrow$ 10 & 45 $\rightarrow$ 47.5 & 140 & 50 \\
			Aigle & 5 $\rightarrow$ 7.5 & 45 & 135 & 45 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:params_2Z-2MI_new}
\end{table}

\begin{table}[htb]
	\caption{Values of the $S_{\text{SCRP}}$ (\%) skill score for the newly calibrated parameters using the MTW approach. The differences are expressed regarding the conventional method with the same archive length.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& MTW & $\Delta$ & MTW & $\Delta$ \\
			\hline
			Ulrichen & 31.58 & 2.20 & 35.72 & 2.48  \\
			Zermatt & 24.71 & 2.51 & 29.63 & 2.68 \\
			Visp & 25.08 & 1.85 & 30.29 & 2.52 \\
			Montana & 32.22 & 1.43 & 37.15 & 2.38 \\
			Sion & 26.07 & 1.29 & 31.68 & 2.32 \\
			Aigle & 32.21 & 1.64 & 38.50 & 2.55 \\
			\hline
		\end{tabular}
	\end{center}
	\label{table:CRPSS_recalibration}
\end{table}

\begin{table}[htb]
	\caption{Changes in sharpness and accuracy relatively to the total $S_{\text{CRP}}$, due to the introduction of the MTW. The changes are presented for both 2Z and 2Z-2MI methods with the original parameters. A decrease of the score is desirable.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
			& Sharpness & Accuracy & Sharpness & Accuracy \\
			\hline
			Ulrichen & 2.82 & -5.29 & 1.00 & -4.30 \\
			Zermatt & 2.26 & -5.01 & 0.88 & -3.58 \\
			Visp & 3.66 & -5.18 & 2.67 & -4.94 \\
			Montana & 1.62 & -2.78 & 0.57 & -2.91 \\
			Sion & 2.02 & -2.78 & 0.33 & -2.75 \\
			Aigle & 0.52 & -2.26 & -1.20 & -2.17 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:CRPSS_decomposition_no_recalibration}
\end{table}

\begin{table}[htb]
	\caption{Same as Table \ref{table:CRPSS_decomposition_no_recalibration} but with the re-calibrated parameters.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
			& Sharpness & Accuracy & Sharpness & Accuracy \\
			\hline
			Ulrichen & 1.44 & -4.56 & -0.37 & -3.34 \\
			Zermatt & 0.80 & -4.03 & 0.75 & -4.42 \\
			Visp & 1.53 & -3.94 & 1.47 & -4.96 \\
			Montana & -0.27 & -1.80 & 0.06 & -3.71 \\
			Sion & 0.95 & -2.66 & -0.10 & -3.19 \\
			Aigle & -0.35 & -2.01 & -2.08 & -1.90 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:CRPSS_decomposition_recalibration}
\end{table}

\begin{table}[htb]
	\caption{Values of the $S_{\text{SCRP}}$ (\%) skill score for the original and the recalibrated parameters (with the sequential method, as described in Sect. \ref{sec:introduction}) using the MTW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& original & recalib. & original & recalib. \\
			\hline
			Ulrichen & 29.13 & 29.61 & 33.15 & 33.45 \\
			Zermatt & 22.17 & 22.80 & 26.72 & 27.43 \\
			Visp & 22.32 & 22.89 & 27.01 & 28.04 \\
			Montana & 29.41 & 30.24 & 33.83 & 34.55 \\
			Sion & 22.98 & 23.41 & 28.57 & 29.15 \\
			Aigle & 29.07 & 29.46 & 34.66 & 35.09 \\
			\hline
		\end{tabular}
	\end{center}
	\label{table:disaggregation_proportional}
\end{table}

\begin{table}[htb]
	\caption{Value of the coefficient of determination between the reconstructed 6-hourly precipitation time series using the listed variables, and the accurate time series on the period 1982-2007. The grid points are the following: 1) 5° E, 47.5° N, 2) 5° E, 45° N, 3) 7.5° E, 47.5° N, 4) 7.5° E, 45° N. The highest coefficient of determination is indicated in bold.}
	\begin{center}
		\begin{tabular}{l c c c c c c}
			\hline
			\multirow{2}{*}{Variable} & \multirow{2}{*}{Point} &  \multicolumn{5}{c}{Time lapse} \\
			&  & -12 h & -6 h & 0 h & +6 h & +12 h \\ 
			\hline
			\multirow{ 4}{*}{RH1000} & 1 & 0.668 & 0.669 & 0.684 & 0.683 & 0.670 \\
			& 2 & 0.669 & 0.669 & 0.683 & 0.681 & 0.669 \\
			& 3 & 0.662 & 0.673 & 0.691 & 0.682 & 0.673 \\
			& 4 & 0.666 & 0.671 & 0.688 & 0.681 & 0.668 \\ \hline
			\multirow{ 4}{*}{RH925} & 1 & 0.672 & 0.673 & 0.684 & 0.684 & 0.675 \\
			& 2 & 0.674 & 0.674 & 0.683 & 0.682 & 0.672 \\
			& 3 & 0.662 & 0.673 & 0.691 & 0.682 & 0.673 \\
			& 4 & 0.666 & 0.671 & 0.689 & 0.681 & 0.668 \\ \hline
			\multirow{ 4}{*}{RH850} & 1 & 0.675 & 0.675 & 0.679 & 0.678 & 0.671 \\
			& 2 & 0.681 & 0.690 & 0.691 & 0.677 & 0.664 \\
			& 3 & 0.665 & 0.680 & 0.693 & 0.683 & 0.675 \\
			& 4 & 0.675 & 0.694 & 0.706 & 0.681 & 0.659 \\ \hline
			\multirow{ 4}{*}{TCW} & 1 & 0.688 & 0.687 & 0.667 & 0.655 & 0.652 \\
			& 2 & 0.697 & 0.699 & 0.669 & 0.644 & 0.644 \\
			& 3 & 0.686 & 0.708 & 0.689 & 0.655 & 0.648 \\
			& 4 & 0.696 & \textbf{0.721} & 0.696 & 0.643 & 0.636 \\ \hline
		\end{tabular}
	\end{center}
	\label{table:proxy_correlations}
\end{table}

\begin{table}[htb]
	\caption{Values of the $S_{\text{SCRP}}$ (\%) skill score for Zermatt, for the original and the recalibrated parameters (with the sequential method, as described in Sect. \ref{sec:introduction}) using the MTW approach on the disaggregated precipitation time series (short and long periods) by means of variables from the reanalysis.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Period} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& original & recalib. & original & recalib. \\
			\hline
			1982--2007 & 22.57 & 23.14 & 27.11 & 27.71 \\
			1961--2008 & 23.81 & 24.38 & 28.42 & 28.86 \\
			\hline
		\end{tabular}
	\end{center}
	\label{table:proxy_CRPSS}
\end{table}

%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
%% authors experienced with BibTeX only have to include the following two lines:
%%
%% \bibliographystyle{copernicus}
%% \bibliography{example.bib}
%%
%% URLs and DOIs can be entered in your BibTeX file as:
%%
%% URL = {http://www.xyz.org/~jones/idx_g.htm}
%% DOI = {10.5194/xyz}

%% LITERATURE CITATIONS
%%
%% command                        & example result
%% \citet{jones90}|               & Jones et al. (1990)
%% \citep{jones90}|               & (Jones et al., 1990)
%% \citep{jones90,jones93}|       & (Jones et al., 1990, 1993)
%% \citep[p.~32]{jones90}|        & (Jones et al., 1990, p.~32)
%% \citep[e.g.,][]{jones90}|      & (e.g., Jones et al., 1990)
%% \citep[e.g.,][p.~32]{jones90}| & (e.g., Jones et al., 1990, p.~32)
%% \citeauthor{jones90}|          & Jones et al.
%% \citeyear{jones90}|            & 1990

%% FIGURES

%% ONE-COLUMN FIGURES

%%f
%\begin{figure}[t]
%\includegraphics[width=8.3cm]{FILE NAME}
%\caption{TEXT}
%\end{figure}
%
%%% TWO-COLUMN FIGURES
%
%%f
%\begin{figure*}[t]
%\includegraphics[width=12cm]{FILE NAME}
%\caption{TEXT}
%\end{figure*}
%
%
%%% TABLES
%%%
%%% The different columns must be seperated with a & command and should
%%% end with \\ to identify the column brake.
%
%%% ONE-COLUMN TABLE
%
%%t
%\begin{table}[t]
%\caption{TEXT}
%\begin{tabular}{column = lcr}
%\tophline
%
%\middlehline
%
%\bottomhline
%\end{tabular}
%\belowtable{} % Table Footnotes
%\end{table}
%
%%% TWO-COLUMN TABLE
%
%%t
%\begin{table*}[t]
%\caption{TEXT}
%\begin{tabular}{column = lcr}
%\tophline
%
%\middlehline
%
%\bottomhline
%\end{tabular}
%\belowtable{} % Table Footnotes
%\end{table*}
%
%
%%% NUMBERING OF FIGURES AND TABLES
%%%
%%% If figures and tables must be numbered 1a, 1b, etc. the following command
%%% should be inserted before the begin{} command.
%
%\addtocounter{figure}{-1}\renewcommand{\thefigure}{\arabic{figure}a}
%
%
%%% MATHEMATICAL EXPRESSIONS
%
%%% All papers typeset by Copernicus Publications follow the math typesetting regulations
%%% given by the IUPAC Green Book (IUPAC: Quantities, Units and Symbols in Physical Chemistry,
%%% 2nd Edn., Blackwell Science, available at: http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf, 1993).
%%%
%%% Physical quantities/variables are typeset in italic font (t for time, T for Temperature)
%%% Indices which are not defined are typeset in italic font (x, y, z, a, b, c)
%%% Items/objects which are defined are typeset in roman font (Car A, Car B)
%%% Descriptions/specifications which are defined by itself are typeset in roman font (abs, rel, ref, tot, net, ice)
%%% Abbreviations from 2 letters are typeset in roman font (RH, LAI)
%%% Vectors are identified in bold italic font using \vec{x}
%%% Matrices are identified in bold roman font
%%% Multiplication signs are typeset using the LaTeX commands \times (for vector products, grids, and exponential notations) or \cdot
%%% The character * should not be applied as mutliplication sign
%
%
%%% EQUATIONS
%
%%% Single-row equation
%
%\begin{equation}
%
%\end{equation}
%
%%% Multiline equation
%
%\begin{align}
%& 3 + 5 = 8\\
%& 3 + 5 = 8\\
%& 3 + 5 = 8
%\end{align}
%
%
%%% MATRICES
%
%\begin{matrix}
%x & y & z\\
%x & y & z\\
%x & y & z\\
%\end{matrix}
%
%
%%% ALGORITHM
%
%\begin{algorithm}
%\caption{…}
%\label{a1}
%\begin{algorithmic}
%…
%\end{algorithmic}
%\end{algorithm}
%
%
%%% CHEMICAL FORMULAS AND REACTIONS
%
%%% For formulas embedded in the text, please use \chem{}
%
%%% The reaction environment creates labels including the letter R, i.e. (R1), (R2), etc.
%
%\begin{reaction}
%%% \rightarrow should be used for normal (one-way) chemical reactions
%%% \rightleftharpoons should be used for equilibria
%%% \leftrightarrow should be used for resonance structures
%\end{reaction}
%
%
%%% PHYSICAL UNITS
%%%
%%% Please use \unit{} and apply the exponential notation

\end{document}

### 2016-12-06 Moving temporal window - HESS/corrections/7 - Submitted version.tex
Submission of the corrections.

--- 2016-12-06 Moving temporal window - HESS/template.tex
@@
 Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
-The AM parameters were calibrated on the original archive (see resulting analogue numbers in Tables \ref{table:analog_nb}) and were used thereafter.
+The AM parameters were calibrated on the original archive (see resulting analogue numbers in Table \ref{table:analog_nb}) and were used thereafter.
 
@@
 	The introduction of the MTW improved the selection of synoptic analogues.
-Independently of its impact on the prediction skill for precipitation, or the availability of a predictand time series with sub-daily time step, this improvement has a potential for application on long meteorological archives.
-For example, when processing forecasts for a target day with synoptic similarity with situations from the past related to extreme weather, even though no precipitation archive is available.
+Independently of its impact on the prediction skill for precipitation, or the availability of a predictand time series with sub-daily time step, this improvement has a potential in itself for application on long meteorological archives.
+For example, when processing forecasts for a target day showing synoptic similarity with situations from the past related to extreme weather, even if for them no precipitation archive is available.
 Indeed, some of those days with strong precipitation events may be documented, either qualitatively in the daily press or more quantitatively in flood reports.
-It is thus worth to known that the situation at hand has such analogue in the past.
+It is thus worth to known that the situation at hand has had such analogue in the past.
 Another possible application is a quality assessment of the selection of analogues on a shorter period, where precipitation data with a high temporal resolution is available.
@@
 However, some of those days with strong precipitation events may be documented, either qualitatively in the daily press or more quantitatively in flood reports.
-Nevertheless, it is worth to known that the situation at hand has such analogue in the far past.
+Nevertheless, it is worth to known that the situation at hand has had such analogue in the far past.
 

### 2016-12-20 Optimization case study - JoH/elsarticle-template.tex
JoH paper under correction.

@@
 
-A short overview of AMs is presented in section \ref{sec:analog_method}, as well as a summary of genetic algorithms in section \ref{sec:gas}.
+A short overview of AMs is presented in section \ref{sec:data_methods}, as well as a summary of genetic algorithms in section \ref{sec:gas}.
 Section \ref{sec:case_study} describes the case study area.
@@
 
-\section{The Analog Method}
-\label{sec:analog_method}
+\section{Data and methods}
+\label{sec:data_methods}
 
-\subsection{References}
+\subsection{Case study description}
+\label{sec:case_study}
+
+The study area is the alpine upper Rh\^{o}ne catchment in Switzerland (Fig.\ \ref{fig:map}).
+The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$.
+This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at allowing real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
+Even though the region is rather small, the meteorological influences related to extreme weather conditions varies substantially within it \citep[see][]{Horton2012}.
+Indeed, a high spatial variability exists, which is due to the complex orography of the region.
+Based on different climatological analyses, the gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}) :
+
+\begin{enumerate}
+	\item Swiss Chablais
+	\item Trient Valley
+	\item West Bernese Alps
+	\item Lower Rhone Valley
+	\item Southern valleys
+	\item Southern ridges
+	\item Upper Rhone Valley
+	\item Southeast ridges
+	\item East Bernese Alps
+	\item Conches Valley
+\end{enumerate}
+
+The 48 years precipitation dataset (see section \ref{sec:intro}.\ref{sec:data}) was divided into a calibration period (CP) and a validation period (VP).
+Using data independent from the CP to validate the results is very important in order to assess the robustness of the improvements and to avoid over-parametrization of the method.
+Parameters determined on the CP are then applied to the VP in order to obtain a performance score for the independent period.
+
+In order to reduce potential bias related to trends linked to climate change or to the evolution in measurement techniques, the selection of the VP is evenly distributed over the entire series \citep{BenDaoud2010}.
+Thus, one year every six years were selected for validation, which represents a total of 8 years for the VP and 40 for CP.
+The choice of the sequence was made in order to have similar statistical characteristics between the CP and the VP.
+
+\subsection{Data}
+\label{sec:data}
+
+The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series one wants to predict.
+
+Predictors are generally extracted from reanalysis datasets.
+NCEP-NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} are used here, but it could be any other reanalysis dataset.
+
+The predictand (which is to be predicted) is here the daily precipitation (6~a.m.
+to 6~a.m.
+the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008.
+The time series from every available gauging station were averaged over subregions of approximately 500~km$^{2}$ in order to smooth local effects \citep{Obled2002, Marty2012}.
+It helps accounting for local variability, mainly when convective processes are involved, which increases slightly the prediction skill.
+
+\subsection{The analog method}
 \label{sec:references}
@@
 
-\subsection{Data}
-\label{sec:data}
-
-The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series one wants to predict.
-
-Predictors are generally extracted from reanalysis datasets.
-NCEP-NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} are used here, but it could be any other reanalysis dataset.
-
-The predictand (which is to be predicted) is here the daily precipitation (6~a.m.
-to 6~a.m.
-the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008.
-The time series from every available gauging station were averaged over subregions of approximately 500~km$^{2}$ in order to smooth local effects \citep{Obled2002, Marty2012}.
-It helps accounting for local variability, mainly when convective processes are involved, which increases slightly the prediction skill.
-
 \subsection{Performance assessment}
@@
 
-\section{Genetic Algorithms}
+\subsection{Sequential calibration}
+\label{sec:sequential}
+
+AMs are usually calibrated by a semi-automatic sequential procedure elaborated by \citet{Bontron2004} \cite[see also ][]{Radanovics2013, BenDaoud2016}.
+The calibration technique optimizes the spatial windows on which the predictors are compared and the number of analogues, for every level of analogy, by maximizing the performance score.
+However, the different analogy levels are calibrated sequentially, and the meteorological variables, the pressure levels and the temporal windows are chosen manually.
+The procedure, as defined by \citet{Bontron2004}, consists of the following steps:
+
+\begin{enumerate}
+	\item Manual selection of the following parameters:
+	\begin{enumerate}
+		\item meteorological variable,
+		\item pressure level,
+		\item temporal window (hour of the day),
+		\item initial analogue numbers.
+	\end{enumerate}
+
+	\item For every level of analogy:
+	\begin{enumerate}
+		\item Identification of the most skilled unitary cell of all predictors jointly of the analogy level, over a large domain, by a full scanning of the grid.
+		\item From this most skilled cell, the spatial window is expanded by successive iterations in the direction of greater performance gain until no improvement is reached.
+		\item The number of analogue situations $N_{1}$ is then reconsidered and optimized for the current level of analogy.
+	\end{enumerate}
+	\item A new level of analogy can then be added, based on other variables (such as the moisture index) with chosen pressure levels, temporal windows, and initial number of analogues $N_{2}$.
+The procedure starts again from step 2 (calibration of the spatial window and the number of analogues) for the new level.
+The parameters calibrated on the previous analogy levels are fixed and do not change.
+	\item Finally, the numbers of analogues $N_{1}$ and $N_{2}$ for the different levels of analogy are reassessed by systematic increments.
+\end{enumerate}
+
+The calibration is done in successive steps with a limited number of parameters. Previously calibrated parameters are generally not reassessed (except for the number of analogues).
+
+This procedure was used to calibrate the methods that were considered as references to further assess the ability of genetic algorithms to outperform the classic approach.
+
+\subsection{Genetic algorithms}
 \label{sec:gas}
@@
 
-\section{Case study description}
-\label{sec:case_study}
-
-The study area is the alpine upper Rh\^{o}ne catchment in Switzerland (Fig.\ \ref{fig:map}).
-The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$.
-This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at allowing real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
-Even though the region is rather small, the meteorological influences related to extreme weather conditions varies substantially within it \citep[see][]{Horton2012}.
-Indeed, a high spatial variability exists, which is due to the complex orography of the region.
-Based on different climatological analyses, the gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}) :
-
-\begin{enumerate}
-	\item Swiss Chablais
-	\item Trient Valley
-	\item West Bernese Alps
-	\item Lower Rhone Valley
-	\item Southern valleys
-	\item Southern ridges
-	\item Upper Rhone Valley
-	\item Southeast ridges
-	\item East Bernese Alps
-	\item Conches Valley
-\end{enumerate}
-
-The 48 years precipitation dataset (see section \ref{sec:intro}.\ref{sec:data}) was divided into a calibration period (CP) and a validation period (VP).
-Using data independent from the CP to validate the results is very important in order to assess the robustness of the improvements and to avoid over-parametrization of the method.
-Parameters determined on the CP are then applied to the VP in order to obtain a performance score for the independent period.
-
-In order to reduce potential bias related to trends linked to climate change or to the evolution in measurement techniques, the selection of the VP is evenly distributed over the entire series \citep{BenDaoud2010}.
-Thus, one year every six years were selected for validation, which represents a total of 8 years for the VP and 40 for CP.
-The choice of the sequence was made in order to have similar statistical characteristics between the CP and the VP.
-
 \section{Optimization of the circulation analogy}
@@
 The reference method for the analogy of the atmospheric circulation (2Z, Table \ref{table:params_R1}), based on Z500 and Z1000, was first considered.
-The optimizer had to choose the number of analogs, both spatial windows with no overlapping constraint, as well as the temporal windows (hours of observation of the geopotential), what the sequential calibration cannot do.
+The optimizer had to choose simulatneously the number of analogs, both spatial windows with no overlapping constraint (they can differ from one pressure level to another), as well as the temporal windows (hours of observation of the geopotential), which cannot be achieved with the sequential calibration technique.
 With these degrees of freedom, a relative CRPSS improvement of 3.97\% and 2.45\% in average was obtained for the CP and the VP respectively, with regard to the reference method based on Z500 and Z1000.
@@
 This is of particular interest in the framework of flood forecasting.
+The further improvement of days with higher precipitation totals is likely related to the fact that larger values contribute more to the CRPS score, which means that better predicting these days results in significant increase of the performance score.
 
@@
 
-It is known that moisture variables as a second level of analogy do provide improvements to the method (section \ref{sec:analog_method}).
+It is known that moisture variables as a second level of analogy do provide improvements to the method (section \ref{sec:references}).
 The moisture index, which is a combination of the relative humidity and the precipitable water, has thus also to be optimized.
@@
 In this regard, a cross-validation technique may be advisable.
+However, as solutions identified at different regions of the parameters space might provide sufficiently good performance, an ensemble of these could be used, instead of a unique solution.
+These could account for the parameters uncertainty of the AM and increase the sample size contributing to the empirical distribution of precipitation values.
 An approach that can also be recommended is to first explore a wide range of the parameter space with some optimizations, and to narrow it according to the results for more targeted optimizations that are likely to go faster and to perform better.

### 2016-12-21 Optimization case study - JoH/elsarticle-template.tex
JoH paper under correction. Removing tables and figures.

@@
 
-\title{Using Genetic Algorithms to Optimize the Analog Method for Precipitation Downscaling in the Swiss Alps}
+\title{Using Genetic Algorithms to Optimize the Analogue Method for Precipitation Prediction in the Swiss Alps}
 
@@
 \begin{abstract}
-Analog methods aim at predicting precipitation based on synoptic predictors provided by general circulation models or numerical weather prediction models.
+Analogue methods aim at predicting precipitation based on synoptic predictors provided by general circulation models or numerical weather prediction models.
 The method samples a selection of days in the archives that are similar to the target day to predict, and consider the set of their corresponding observed precipitation (the predictand) as the conditional distribution for the target day.
@@
 This relationship is usually established by a semi-automatic sequential procedure that has strong limitations: (i) it cannot automatically choose the pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it could not easily handle new degrees of freedom.
-A new global optimization approach relying on genetic algorithms can optimize all parameters jointly and automatically, which is a breakthrough in the way the analog method was calibrated until now.
+A new global optimization approach relying on genetic algorithms can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
 It allows taking into account parameters inter-dependencies, and selecting objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
@@
 Precipitation downscaling\sep
-Analog method\sep
+Analogue method\sep
 Optimization\sep
@@
 
-The analog method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1956, Lorenz1969}, that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Duband1970}.
+The analogue method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1956, Lorenz1969}, that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Duband1970}.
 It uses predictor variables describing the synoptic atmospheric circulation in order to predict local-scale predictands of interest.
@@
 
-In operational forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies, it is used to downscale the results of global climate model (GCM) simulation runs.
-In this last case, although the GCM represents the large or regional scale evolutions of the atmosphere, it would be far too computer intensive to resolve variables such as precipitation at a rather small and representative scale.
-Therefore the idea is to rely on past observations to bypass these unaffordable small scale simulations and to go from the large scale situation proposed by the GCM to the end variables like precipitation by searching analogs in the archives.
+In operational forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies, it is used to downscale the outputs of general circulation model (GCM) or regional climate models (RCMs) simulation runs \citep{Dayon2015} or to reconstruct past weather conditions \citep{Caillouet2016}.
+In future climate studies, RCMs are often used to dynamically downscale precipitation to a local scale.
+However, even though the relevance of RCMs'outputs increases, precipitation processes are parametrized and a bias correction of the outputs is still often required.
+Moreover, their application is computer intensive and cannot cover the full range of GCMs products.
+Therefore the idea is to rely on past observations to bypass the small scale simulations and to go from the large scale situation to the end variables like precipitation by searching analogues in the archives.
+
+A big advantage of AMs is that they create realistic precipitation patterns for a region, provided that the analogue dates are the same, since they are based on observed situations with consistent spatial distribution \citep{Radanovics2013, Chardon2014}.
+For the same reason, they can also provide multivariate predictions that are physically consistent \citep{Raynaud2016b}.
 
 The method can be designed with multiple successive subsampling steps, each of them relying on different meteorological variables.
-A certain number of parameters define the relationship between predictors and predictands, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criterion itself, and finally the number of analog situations to keep at each subsampling level.
+A certain number of parameters define the relationship between predictors and predictands, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criterion itself, and finally the number of analogue situations to keep at each subsampling level.
 These parameters are usually calibrated by means of a semi-automatic sequential procedure \citep[see][for the details]{Bontron2004, Radanovics2013, Horton2016a}, i.e.
@@
 
-With the perspective to overcome these limitations, a global optimization by genetic algorithms (GAs) was introduced by \citet{Horton2016}.
-An intensive assessment work resulted in recommendations of parametrization of GAs in order to optimize AMs successfully.
-The present paper is based on these recommendations and illustrate them for precipitation prediction for the upper Rh\^{o}ne catchment in the Swiss Alps.
+With the perspective to overcome these limitations, a global optimization by genetic algorithms (GAs) was introduced.
+An intensive assessment work resulted in recommendations of parametrization of GAs in order to optimize AMs successfully \citet{Horton2016}.
+The present paper is based on these recommendations and apply them for precipitation prediction for the upper Rh\^{o}ne catchment in the Swiss Alps.
 It aims at proving the relevance of a fully-automatic, objective, and global, optimization technique for AMs.
@@
 
-\subsection{The analog method}
+\subsection{The analogue method}
 \label{sec:references}
@@
 
-The $N_{1}$ dates with the lowest values of S1 are considered as analogs to the target day.
-The number of analogs, $N_{1}$, is a parameter to calibrate.
+The $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day.
+The number of analogues, $N_{1}$, is a parameter to calibrate.
 Then, the daily observed precipitation amount of the $N_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day.
@@
 \cite{Horton2012a} confirmed that this index is also better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis considered independently.
-When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogs on the atmospheric circulation, to end up with a smaller number of analog situations.
-When a second level of analogy is added, a higher number of analogs $N_{1}$ is kept on the first level.
+When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
+When a second level of analogy is added, a higher number of analogues $N_{1}$ is kept on the first level.
 Moisture fields are not as well predicted by NWP models as pressure variables.
@@
 The score that is most often used to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
-It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$.
+It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$.
 The better the prediction, the smaller the score.
@@
 The reference method for the analogy of the atmospheric circulation (2Z, Table \ref{table:params_R1}), based on Z500 and Z1000, was first considered.
-The optimizer had to choose simulatneously the number of analogs, both spatial windows with no overlapping constraint (they can differ from one pressure level to another), as well as the temporal windows (hours of observation of the geopotential), which cannot be achieved with the sequential calibration technique.
+The optimizer had to choose simulatneously the number of analogues, both spatial windows with no overlapping constraint (they can differ from one pressure level to another), as well as the temporal windows (hours of observation of the geopotential), which cannot be achieved with the sequential calibration technique.
 With these degrees of freedom, a relative CRPSS improvement of 3.97\% and 2.45\% in average was obtained for the CP and the VP respectively, with regard to the reference method based on Z500 and Z1000.
@@
 
-Then, an additional degree of freedom was provided to the GAs by letting them choose the pressure levels along with the other parameters (analog numbers, spatial and temporal windows), which is also a non-automated process in the sequential calibration.
+Then, an additional degree of freedom was provided to the GAs by letting them choose the pressure levels along with the other parameters (analogue numbers, spatial and temporal windows), which is also a non-automated process in the sequential calibration.
 This degree of freedom increased the optimization time and may decrease the number of simulations that converge to a single solution.
@@
 	\item the weights (4 degrees)
-	\item the number of analogs (1 degree).
+	\item the number of analogues (1 degree).
 \end{itemize}
@@
 The resulting optimized parameters for 4Zo vary from one subregion to another.
-An example of the detailed parameters is provided for the Swiss Chablais in Table \ref{table:params_GA_4Zo}.
 The optimized spatial windows are given for every subregion in Figure \ref{fig:spatial_windows_4Zo}, and the selected pressure levels in Table~\ref{table:levels_GA_4Zo}.
@@
 
-The CRPS score was also discretized into its accuracy and sharpness components, as suggested by \citet{Bontron2004}.
-The changes in each of these components has been illustrated in Figure \ref{fig:figure_dcrps_comp_4Zo} relatively to the total CRPS value of the 2Z reference method for the different regions and both the CP and the VP.
-One can see that the accuracy part is always improved to a greater extent than the sharpness, which can occasionally deteriorate.
-It means that the medians of the predicted precipitations distributions are closer to the observed value, whereas the spread of the distribution vary, but is in general a bit narrower.
-
 The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the CP when they are optimized for a given subregion (Figure \ref{fig:crossing_4Zo_calib}).
 However, the losses in CRPSS when exchanging the parameters are not of the same magnitude between the different subregions.
-Indeed, the Upper Rhone Valley (7) and moreover the Southeast ridges (8) seem to behave significantly differently, likely due to their particular sensitivity to southerly flows \citep{Horton2012}.
+Indeed, the Upper Rhone Valley (7) and moreover the Southeast ridges (8) seem to behave significantly differently.
+These two regions have different climate properties than the others as they are particularly sensitive to southerly flows.
+Indeed, almost all heavy precipitation events occurred under a southerly regime, such as the Liguria, Piémont and Aosta regions in Italy, whereas the other subregions of the catchment had heavy precipitation events mainly under a westerly regime \citep{Horton2012}.
+Thus, as the performance score is significantly influenced by heavy precipitation values, the parameters for the different subregions are optimized to better predict these days.
+It can then be expected that the optimal parameters differ between these two subregions and the other ones.
 This points at the importance of taking into account leading meteorological influences during discretization, that are not always best represented by the physical distance.
+
 Globally, the same pattern can be observed for the VP (Figure \ref{fig:crossing_4Zo_valid}), but in this case, minor improvements may occur when crossing the parameters, due to the presence of other events in the VP that may be better predicted by a different parameter set.
@@
 Even a change in the pressure level does not mean a radical drop of the score value.
-A different parametrization may lead to a distinct selection of analog days, and thus to an improvement of the prediction under certain weather conditions at the expense of others.
+A different parametrization may lead to a distinct selection of analogue days, and thus to an improvement of the prediction under certain weather conditions at the expense of others.
 
@@
 As previously, the optimized parameters differ from one subregion to another, and this even to a greater extent.
-Detailed examples are again provided for the Swiss Chablais subregion in Table \ref{table:params_GA_4Zo_2MIo} for 4Zo-2MIo.
 The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_4Zo-2MIo} for 4Zo-2MIo, along with the selected pressure levels for both the circulation and the moisture analogy (Table \ref{table:levels_GA_4Zo_2MIo}).
@@
 It means that the two levels of analogy bring complementary information, and are thus not independent.
-This is first visible on the number $N_{1}$ of analogs to be selected on the first level, and on the selection of the pressure levels for the circulation analogy.
+This is first visible on the number $N_{1}$ of analogues to be selected on the first level, and on the selection of the pressure levels for the circulation analogy.
 
 As for the sequential procedure, the optimal value of $N_{1}$ increases when adding a second level of analogy (Figure \ref{fig:figure_nb_analogs}).
-One can also notice that the optimal number of analogs $N_{2}$ for the second level of analogy of 4Zo-2MIo is slightly inferior to $N_{1}$ from 4Zo, but very close.
-There is a trend between the optimal analog number values of both methods: the higher $N_{1}$ of the 4Zo method, the higher $N_{1}$ and $N_{2}$ of 4Zo-2MIo is (Figure \ref{fig:figure_nb_analogs_relationships}).
+One can also notice that the optimal number of analogues $N_{2}$ for the second level of analogy of 4Zo-2MIo is slightly inferior to $N_{1}$ from 4Zo, but very close.
+There is a trend between the optimal analogue number values of both methods: the higher $N_{1}$ of the 4Zo method, the higher $N_{1}$ and $N_{2}$ of 4Zo-2MIo is (Figure \ref{fig:figure_nb_analogs_relationships}).
 This relationship is not to be considered perfectly robust and should not be transposed to another case study, but in this case, it relates the magnitudes of the $N_{1}$ and $N_{2}$ on the various levels and methods.
 
-The optimal final number of analogs do not vary much: $23 \leq N_{1} \leq 33$ for 4Zo and $21 \leq N_{2} \leq 28$ for 4Zo-2MIo.
-However, the optimal number of $N_{1}$ analogs of the first level of 4Zo-2MIo varies to a greater extent: $48 \leq N_{1} \leq 84$.
+The optimal final number of analogues do not vary much: $23 \leq N_{1} \leq 33$ for 4Zo and $21 \leq N_{2} \leq 28$ for 4Zo-2MIo.
+However, the optimal number of $N_{1}$ analogues of the first level of 4Zo-2MIo varies to a greater extent: $48 \leq N_{1} \leq 84$.
 In this latter method, it may be problematic to consider a fixed and unique value for all regions.
@@
 
-As previously, the CRPS scores were discretized into their sharpness and accuracy components.
-The changes in each of these components, expressed relatively to the total CRPS values, is once again in favor of the accuracy over the sharpness (Figure \ref{fig:figure_dcrps_comp_4Zo-2HIo} for 4Zo-2MIo; 4Zo-4MIo not shown, but similar).
-
 The analysis of the parameters cross-compatibility (Figures \ref{fig:crossing_4Zo-2MIo_calib} and \ref{fig:crossing_4Zo-2MIo_valid}) is also very similar to the one on the circulation analogy only (results for 4Zo-4MIo not shown as very similar).
@@
 However, the losses of performance are globally more important than before, suggesting that more complex methods with moisture variables are less transposable to another subregion, even though both are located within the same grid cell of the reanalysis dataset.
+Moisture fields have greater variability than pressure fields, and thus a change in the spatial windows can have a greater impact on the method performance.
+Indeed, the two regions with the lowest cross-compatibility are the Upper Rhone Valley (7) and the Southeast ridges (8), which have similar optimal pressure levels and temporal windows to other regions, but have rather different spatial windows on the moisture predictor.
 
@@
 Beyond that value the validation score drops, revealing a loss in robustness due to over-parametrization.
-	\item The automatic and joint optimization of all parameters: the analogs number, the selection of the pressure levels and the temporal windows, and the spatial windows.
+	\item The automatic and joint optimization of all parameters: the analogues number, the selection of the pressure levels and the temporal windows, and the spatial windows.
 These parameters are highly interdependent, so one needs to optimize them jointly in order to identify optimal combinations.
-Traditional calibration procedures based on a systematic assessment of every combination is not possible anymore when considering more than 2 pressure levels.
+Indeed, there is a strong interdependence between space and time in the atmospheric circulation, so that e.g.
+the spatial window should move upstream the main atmospheric flow for earlier temporal windows.	Traditional calibration procedures based on a systematic assessment of every combination is not possible anymore when considering more than 2 pressure levels.
 	\item The introduction of distinct spatial windows between pressure levels.
@@
 Indeed, the optimizer will probably use them to successfully improve the calibration score, but the validation control remains very important in order to determine if one is actually improving the method, or if it is being over-parametrized.
+Moreover, it might not always be desirable to increase the number of degrees of freedom, and some constraints (e.g.
+same weighting of the analogy criteria between different pressure levels) can be justified.
+However, one should first assess the consequence of a constraint before establishing it.
+In this sense, even though not all degrees of freedom can be found useful, GAs allow assessing their influence.
 
@@
 
-We tried to optimize the preselection period (i.e.
-the 4-months window) jointly with the other parameters, but no improvement was observed.
+We tried to optimize the length of the preselection period (i.e.
+the seasonal stratification, which was a 4-month window until now) jointly with the other parameters, but no improvement was observed.
 Optimizing the moisture flux, which is composed of the moisture index multiplied with the wind flux, was also assessed.
@@
 The ability to optimize jointly all parameters is important given the strong dependencies between them and between the levels of analogy.
+
+AMs optimized with GAs show an improvement of the prediction for days with heavier precipitation, including extremes.
+However, even though the distribution of analogue precipitation values moved towards the targeted extreme, no new extreme values were added to the sample of candidate situations.
+The extremes in AMs can be modelled by, for example, extrapolation of a truncated exponential or gamma distribution fitted to the analogue values \citep{Obled2002}.
+Another possible approach is by combining AMs with other methods \citep[e.g.][]{Chardon2014}.
 
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig04.pdf}}
-	\caption{Changes in the CRPS components of 4Zo relatively to the total CRPS of the reference methods 2Z (Table \ref{table:params_R1}) for the CP and the VP.}
-	\label{fig:figure_dcrps_comp_4Zo}
-\end{figure}
-
-\begin{figure}[t]
 	\centerline{\includegraphics[width=8.4cm]{figures/fig05.pdf}}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig10.pdf}}
-	\caption{Changes in the CRPS components of 4Zo-2MIo relatively to the total CRPS of the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
-	\label{fig:figure_dcrps_comp_4Zo-2HIo}
-\end{figure}
-
-\begin{figure}[t]
 	\centerline{\includegraphics[width=8.8cm]{figures/fig11.pdf}}
-	\caption{Number of analogs for the different regions and the various methods resulting from the optimization.
-Method 4Zo is made of a single level of analogy with $N_{1}$ analogs, whereas 4Zo-2MIo has two levels of analogy with respectively $N_{1}$ and $N_{2}$ analogs.}
+	\caption{Number of analogues for the different regions and the various methods resulting from the optimization.
+Method 4Zo is made of a single level of analogy with $N_{1}$ analogues, whereas 4Zo-2MIo has two levels of analogy with respectively $N_{1}$ and $N_{2}$ analogues.}
 	\label{fig:figure_nb_analogs}
@@
 	\centerline{\includegraphics[width=8.8cm]{figures/fig12.pdf}}
-	\caption{Relationships between the optimal number of analogs for both levels of the 4Zo-2MIo method and the corresponding ones for the unique level of the 4Zo method.}
+	\caption{Relationships between the optimal number of analogues for both levels of the 4Zo-2MIo method and the corresponding ones for the unique level of the 4Zo method.}
 	\label{fig:figure_nb_analogs_relationships}
@@
 The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation within the target day (temporal window).
-The criterion used for the current level of analogy is then provided, as well as the number of analogs.}
+The criterion used for the current level of analogy is then provided, as well as the number of analogues.}
 	\footnotesize
@@
 	\label{table:params_R2}
-\end{table}
-
-\begin{table}[t]
-	\caption{Parameters of the 4Zo method (analogy on 4 levels of the atmospheric circulation) optimized for the Chablais subregion.
-The columns are the following: L = level of analogy, V = meteorological variable, H = hour of observation within the target day, D = domain or spatial window, W = weighting of the score for the selected pressure levels, C = criterion, N = number of analogs.}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline L & V & H & D & W & C & N \\ 
-			\hline 
-			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & -2.5 - 15.0 \degree E & \multirow{2}{*}{32\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{28} \\
-			& & & 37.5 - 57.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z700} & \multirow{2}{*}{24~h} & 2.5 - 10.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
-			& & & 42.5 - 45.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{6~h} & -5.0 - 15.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
-			& & & 42.5 - 47.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
-			& & & 40.0 - 50.0 \degree N & & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_GA_4Zo}
 \end{table}
@@
 \begin{table}[t]
-	\caption{Parameters of the 4Zo-2MIo method (atmospheric circulation on 4 levels and moisture index on 2 levels), optimized for the Chablais subregion.
-Same conventions as Table \ref{table:params_GA_4Zo}.}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline L & V & H & D & W & C & N \\ 
-			\hline 
-			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
-			\hline 
-			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & 0.0 - 15.0 \degree E & \multirow{2}{*}{23\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
-			& & & 42.5 - 55.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{25\%} & & \\ 
-			& & & 40.0 - 45.0 \degree N & & & \\ 
-			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
-			& & & 42.5 - 47.5 \degree N & & & \\ 
-			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
-			& & & 40.0 - 47.5 \degree N & & & \\ 
-			\hline 
-			\multirow{4}{*}{2} & TPW & \multirow{2}{*}{12~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{57\%} & \multirow{4}{*}{RMSE} & \multirow{4}{*}{25} \\
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			& TPW & \multirow{2}{*}{24~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{43\%} & & \\ 
-			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:params_GA_4Zo_2MIo}
-\end{table}
-
-\begin{table}[t]
 	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the 4Zo-2MIo method, at the different subregions.

### 2016-12-21 Optimization case study - JoH/elsarticle-template.tex
Update of figures for JoH.

@@
 One can also notice that the optimal number of analogues $N_{2}$ for the second level of analogy of 4Zo-2MIo is slightly inferior to $N_{1}$ from 4Zo, but very close.
-There is a trend between the optimal analogue number values of both methods: the higher $N_{1}$ of the 4Zo method, the higher $N_{1}$ and $N_{2}$ of 4Zo-2MIo is (Figure \ref{fig:figure_nb_analogs_relationships}).
-This relationship is not to be considered perfectly robust and should not be transposed to another case study, but in this case, it relates the magnitudes of the $N_{1}$ and $N_{2}$ on the various levels and methods.
+There is globally a tendency between the optimal analogue number values of both methods: $N_{1}$ of the 4Zo method, and $N_{1}$ and $N_{2}$ of 4Zo-2MIo tend to be higher or lower altogether for a given region.
 
@@
 	\centerline{\includegraphics[width=8.8cm]{figures/fig03.pdf}}
-	\caption{CRPSS relative improvement of 4Zo compared to the reference methods 2Z (Table \ref{table:params_R1}) for the CP and the VP.}
-	\label{fig:figure_dcrpss_4Zo}
+	\caption{Performance score (CRPSS) of the reference methods 2Z (Table \ref{table:params_R1}) and the optimized 4Zo method for the CP and the VP for every subregion.}
+	\label{fig:figure_crpss_4Zo}
 \end{figure}
@@
 	\centerline{\includegraphics[width=8.4cm]{figures/fig05.pdf}}
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo, calibration period.}
-	\label{fig:crossing_4Zo_calib}
-\end{figure}
-
-\begin{figure}[t]
-	\centerline{\includegraphics[width=8.4cm]{figures/fig06.pdf}}
-	\caption{Same as Figure \ref{fig:crossing_4Zo_calib} but for the validation period.}
-	\label{fig:crossing_4Zo_valid}
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo, calibration and validation periods.}
+	\label{fig:crossing_4Zo}
 \end{figure}
@@
 	\centerline{\includegraphics[width=8.8cm]{figures/fig08.pdf}}
-	\caption{CRPSS relative improvement of 4Zo-2MIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
-	\label{fig:figure_dcrpss_4Zo-2HIo}
-\end{figure}
-
-\begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig09.pdf}}
-	\caption{CRPSS relative improvement of 4Zo-4MIo compared to the reference methods 2Z-2MI (Table \ref{table:params_R2}) for the CP and the VP.}
-	\label{fig:figure_dcrpss_4Zo-4HIo}
+	\caption{Performance score (CRPSS) of the reference methods 2Z-2MI (Table \ref{table:params_R2}) and the optimized 4Zo-2MIo method for the CP and the VP for every subregion.}
+	\label{fig:figure_crpss_4Zo-2HIo}
 \end{figure}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig12.pdf}}
-	\caption{Relationships between the optimal number of analogues for both levels of the 4Zo-2MIo method and the corresponding ones for the unique level of the 4Zo method.}
-	\label{fig:figure_nb_analogs_relationships}
-\end{figure}
-
-\begin{figure}[t]
 	\centerline{\includegraphics[width=8.4cm]{figures/fig13.pdf}}
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo-2MIo, calibration period.}
-	\label{fig:crossing_4Zo-2MIo_calib}
-\end{figure}
-
-\begin{figure}[t]
-	\centerline{\includegraphics[width=8.4cm]{figures/fig14.pdf}}
-	\caption{Same as Figure \ref{fig:crossing_4Zo-2MIo_calib} but for the validation period.}
-	\label{fig:crossing_4Zo-2MIo_valid}
-\end{figure}
-
-\begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig15.pdf}}
-	\caption{Optimized weighting for the pressure levels of the 4Zo method.}
-	\label{fig:levels_weights}
+	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo-2MIo, calibration and validation periods.}
+	\label{fig:crossing_4Zo-2MIo}
 \end{figure}
@@
 	\centerline{\includegraphics[width=8.8cm]{figures/fig16.pdf}}
-	\caption{Averaged weighting for the pressure levels of the circulation analogy of the three methods.}
+	\caption{Distribution of the optimal weights for the predictors of the first level of analogy (geopotential heights) of the 4Zo, 4Zo-2MIo, and 4Zo-4MIo methods.
+The results are those of the 10 subregions.
+The geopotential heights are sorted by increasing pressure and hour.}
 	\label{fig:levels_weights_average}
@@
 	\label{table:levels_GA_4Zo}
-\end{table}
-
-\begin{table}[t]
-	\caption{CRPSS score (\%) of the three optimized methods (4Zo is the atmospheric circulation analogy detailed in the present section; 4Zo-2MIo and 4Zo-4MIo add a second level of analogy on moisture indexes, as explained in section \ref{sec:optim_moisture}).}
-	\footnotesize
-	\begin{center}
-		\begin{tabular}{ccccccc}
-			\hline 
-			ID & \multicolumn{2}{c}{4Zo} & \multicolumn{2}{c}{4Zo-2MIo} & \multicolumn{2}{c}{4Zo-4MIo} \\ 
-			& CP & VP & CP & VP & CP & VP \\ 
-			\hline 
-			1 & 40.3 & 38.5 & 45.5 & 43.8 & 45.9 & 43.6 \\
-			2 & 37.8 & 34.9 & 42.4 & 40.8 & 42.9 & 41.3 \\
-			3 & 36.6 & 33.9 & 41.4 & 39.0 & 41.8 & 39.5 \\
-			4 & 31.2 & 30.8 & 36.1 & 36.4 & 36.8 & 37.1 \\
-			5 & 34.4 & 36.5 & 38.6 & 41.4 & 39.2 & 41.8 \\
-			6 & 37.0 & 39.9 & 41.0 & 44.5 & 41.9 & 44.6 \\
-			7 & 30.0 & 30.1 & 33.8 & 34.6 & 34.4 & 34.8 \\
-			8 & 37.7 & 40.1 & 40.7 & 43.1 & 41.2 & 43.3 \\
-			9 & 33.1 & 30.0 & 38.4 & 36.6 & 38.7 & 36.3 \\
-			10 & 40.0 & 40.0 & 42.6 & 42.9 & 43.3 & 43.2 \\
-			\hline
-			av. & 35.8 & 35.5 & 40.1 & 40.3 & 40.6 & 40.5 \\ 
-			\hline 
-		\end{tabular} 
-	\end{center}
-	\label{table:scores}
 \end{table}

### 2016-12-21 Optimization case study - JoH/elsarticle-template.tex
Renaming files.
JoH paper under correction.

@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.4cm]{figures/fig05.pdf}}
+	\centerline{\includegraphics[width=8.4cm]{figures/fig04.pdf}}
 	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo, calibration and validation periods.}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.4cm]{figures/fig07.pdf}}
+	\centerline{\includegraphics[width=8.4cm]{figures/fig05.pdf}}
 	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 2 pressure levels).
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig08.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig06.pdf}}
 	\caption{Performance score (CRPSS) of the reference methods 2Z-2MI (Table \ref{table:params_R2}) and the optimized 4Zo-2MIo method for the CP and the VP for every subregion.}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig11.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig07.pdf}}
 	\caption{Number of analogues for the different regions and the various methods resulting from the optimization.
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.4cm]{figures/fig13.pdf}}
+	\centerline{\includegraphics[width=8.4cm]{figures/fig08.pdf}}
 	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo-2MIo, calibration and validation periods.}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig16.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig09.pdf}}
 	\caption{Distribution of the optimal weights for the predictors of the first level of analogy (geopotential heights) of the 4Zo, 4Zo-2MIo, and 4Zo-4MIo methods.
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=7.5cm]{figures/fig17.pdf}}
+	\centerline{\includegraphics[width=7.5cm]{figures/fig10.pdf}}
 	\caption{Example of the evolution of the performance score of the best individual over 8 independent optimizations.}
@@
 \begin{table}[t]
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo method, compared to the reference method.}
+	\caption{Relative improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo method, compared to the reference method.}
 	\footnotesize
@@
 \begin{table}[t]
-	\caption{Improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo-2MIo method, compared to the reference method.}
+	\caption{Relative improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo-2MIo method, compared to the reference method.}
 	\footnotesize

### 2016-12-21 Optimization case study - JoH/elsarticle-template.tex
JoH paper under correction.

@@
 
-The resulting CRPSS scores are provided in Table \ref{table:scores} and are in average 35.8 \% for the CP and 35.5 \% for the VP.
-The improvement of the CRPSS score relatively to the reference method on the atmospheric circulation (optimized by the sequential procedure) is illustrated in Figure \ref{fig:figure_dcrpss_4Zo} and is in average 15.3 \% for the CP and 9.9 \% for the VP.
-The score was also calculated for three precipitation thresholds: P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_4Zo}).
-The gain in score increases with the precipitation threshold: the relative improvement of the CRPSS is in average, respectively for the different thresholds, 13.3\%, 15.4\% and 29.1\% for the CP and 7.9\%, 11.1\% and 34.5\% for the VP.
+The resulting CRPSS scores are provided in Figure \ref{fig:figure_crpss_4Zo} and are in average 35.8~\% for the CP and 35.5~\% for the VP, comparatively to 31.1~\% and 32.3~\% respectively for the reference method on the atmospheric circulation (optimized by the sequential procedure).
+The score was also calculated for three precipitation thresholds: P\(\geq\)1~mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_4Zo}).
+The gain in score increases with the precipitation threshold: the relative improvement of the CRPSS is in average, respectively for the different thresholds, 13.3~\%, 15.4~\% and 29.1~\% for the CP and 7.9~\%, 11.~1\% and 34.5~\% for the VP.
 The optimization improves thus even more the prediction for days with significant precipitation than usual days.
@@
 To assess the parameters cross-compatibility, and the spatial coherence of the resulting parameters, those optimized for one subregion were applied to the others.
-The resulting losses or gains of the CRPSS are displayed in Figure \ref{fig:crossing_4Zo_calib} for the CP and in Figure \ref{fig:crossing_4Zo_valid} for the VP.
+The resulting losses or gains of the CRPSS are displayed in Figure \ref{fig:crossing_4Zo}.
 
@@
 
-The scores show significant improvements for both the CP and the VP (Figure \ref{fig:figure_dcrpss_4Zo}) compared to the reference method optimized by the sequential procedure.
+The scores show non-negligible improvements for both the CP and the VP (Figure \ref{fig:figure_crpss_4Zo}) compared to the reference method optimized by the sequential procedure.
 Even more interestingly, the results for higher precipitation thresholds (Table \ref{table:scores_thresholds_4Zo}) show the largest improvements.
@@
 
-The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the CP when they are optimized for a given subregion (Figure \ref{fig:crossing_4Zo_calib}).
+The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the CP when they are optimized for a given subregion (Figure \ref{fig:crossing_4Zo} top).
 However, the losses in CRPSS when exchanging the parameters are not of the same magnitude between the different subregions.
@@
 
-Globally, the same pattern can be observed for the VP (Figure \ref{fig:crossing_4Zo_valid}), but in this case, minor improvements may occur when crossing the parameters, due to the presence of other events in the VP that may be better predicted by a different parameter set.
+Globally, the same pattern can be observed for the VP (Figure \ref{fig:crossing_4Zo} bottom), but in this case, minor improvements may occur when crossing the parameters, due to the presence of other events in the VP that may be better predicted by a different parameter set.
 The relatively small gaps in score between parameterizations indicate that even though the parameters may differ significantly, the performance may not be drastically affected.
@@
 
-The CRPSS scores of the optimized methods are provided in Table \ref{table:scores} and amounts to slightly more than 40 \% in average for both methods and for both periods.
-This results in a relative improvements for 4Zo-2MIo that is in average 14.0 \% for the CP and 11.5 \% for the VP (Figure \ref{fig:figure_dcrpss_4Zo-2HIo}), compared to the reference method on the moisture analogy optimized with the sequential procedure.
-For 4Zo-4MIo, the average improvement is 15.6 \% for the CP and 12.1 \% for the VP (Figure \ref{fig:figure_dcrpss_4Zo-4HIo}).
+The CRPSS scores of the optimized 4Zo-2MIo method are provided in Figure \ref{fig:figure_crpss_4Zo-2HIo} and amounts in average to 40~\% (CP) and 40.3~\% (VP), compared to 35.2~\% (CP) and 36.2~\% (VP) for the reference method on the moisture analogy optimized with the sequential procedure.
+The score for the 4Zo-4MIo method are relatively close, with 40.6~\% for both the CP and the VP (not shown as very similar repartition as Figure \ref{fig:figure_crpss_4Zo-2HIo}).
 
-As for 4Zo, the 4Zo-2MIo and 4Zo-4MIo methods present larger improvements in the prediction for significant rainfall (thresholds P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
-The improvement are relatively similar for 4Zo-2MIo (Table \ref{table:scores_thresholds_4Zo-2MIo}) and 4Zo-4MIo (not shown), with slightly superior scores for the latter on small precipitation (P\(\geq\)1 mm : 17.7\% and 13.0\%) and extremes (P\(\geq\)0.5\(\cdot\)P10 : 23.7\% and 29.2\%).
+As for 4Zo, the 4Zo-2MIo and 4Zo-4MIo methods present larger improvements in the prediction for significant rainfall (thresholds P\(\geq\)1~mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
+The improvement are relatively similar for 4Zo-2MIo (Table \ref{table:scores_thresholds_4Zo-2MIo}) and 4Zo-4MIo (not shown), with slightly superior scores for the latter on small precipitation (P\(\geq\)1~mm : 17.7~\% and 13.0~\%) and extremes (P\(\geq\)0.5\(\cdot\)P10 : 23.7~\% and 29.2~\%).
 
-The parameters cross-compatibility has also been assessed for the methods with moisture variables, and are shown in Figures \ref{fig:crossing_4Zo-2MIo_calib} and \ref{fig:crossing_4Zo-2MIo_valid} for the method 4Zo-2MIo (not shown for 4Zo-4MIo, but similar).
+The parameters cross-compatibility has also been assessed for the methods with moisture variables, and are shown in Figure \ref{fig:crossing_4Zo-2MIo} for the method 4Zo-2MIo (not shown for 4Zo-4MIo, but similar).
 
@@
 
-The CRPSS scores were improved by considering the moisture information (Table \ref{table:scores}).
-The optimized methods also perform significantly better than the reference method based on the moisture index (Figures \ref{fig:figure_dcrpss_4Zo-2HIo} and \ref{fig:figure_dcrpss_4Zo-4HIo}) optimized by the sequential procedure.
+The CRPSS scores were improved by considering the moisture information (Figure \ref{fig:figure_crpss_4Zo-2HIo} to be compared with Figure \ref{fig:figure_crpss_4Zo}).
+The optimized methods also perform significantly better than the reference method based on the moisture index optimized by the sequential procedure.
 However, there is no drastic difference between both 4Zo-2MIo and 4Zo-4MIo methods, which suggests that considering 4 moisture predictors is not necessary.
-When it comes to improvements for days with precipitation above the 3 thresholds (P\(\geq\)1 mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the prediction compared to the reference method, mainly for heavy rainfall.
+When it comes to improvements for days with precipitation above the 3 thresholds (P\(\geq\)1~mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the prediction compared to the reference method, mainly for heavy rainfall.
 
-The analysis of the parameters cross-compatibility (Figures \ref{fig:crossing_4Zo-2MIo_calib} and \ref{fig:crossing_4Zo-2MIo_valid}) is also very similar to the one on the circulation analogy only (results for 4Zo-4MIo not shown as very similar).
+The analysis of the parameters cross-compatibility (Figure \ref{fig:crossing_4Zo-2MIo}) is also very similar to the one on the circulation analogy only (results for 4Zo-4MIo not shown as very similar).
 The same pattern can be observed, with a drop of performance for the subregions submitted to different meteorological influences.
@@
 It can be influenced by the variability of the geopotential with altitude, and the change of some levels significance with the targeted region.
-There is a trend for the weighting of circulation predictors to decrease with the increase in pressure, as one can see in Figure \ref{fig:levels_weights} for the method 4Zo, and in Figure \ref{fig:levels_weights_average} for the averages over the 3 methods.
+There is a trend for the weighting of circulation predictors to decrease with the increase in pressure, as one can see in Figure \ref{fig:levels_weights_average} for the three optimized methods.
 However, the values stay around equity.

### 2016-12-22 Optimization case study - JoH/elsarticle-template.tex
JoH paper under correction.

@@
 It uses predictor variables describing the synoptic atmospheric circulation in order to predict local-scale predictands of interest.
-It is often used to predict daily precipitation, either in an operational forecasting context \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Hamill2015, BenDaoud2016}, or a climate context \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015, Raynaud2016b}.
+It is often used to predict daily precipitation, either in an operational forecasting context \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Hamill2015, BenDaoud2016, Horton2016a}, or a climate context \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015, Raynaud2016b}.
 Other predictands are also considered, such as precipitation radar images \citep{Panziera2011,Foresti2015a}, temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016, Raynaud2016b}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, and radiation \citep{Bois1981, Raynaud2016b}.
@@
 A certain number of parameters define the relationship between predictors and predictands, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criterion itself, and finally the number of analogue situations to keep at each subsampling level.
-These parameters are usually calibrated by means of a semi-automatic sequential procedure \citep[see][for the details]{Bontron2004, Radanovics2013, Horton2016a}, i.e.
+These parameters are usually calibrated by means of a semi-automatic sequential procedure \citep[see][for the details]{Bontron2004, Radanovics2013}, i.e.
 by optimizing each single parameter one at a time, in an arbitrarily chosen order, with no or little reassessment.
@@
 The same pattern can be observed, with a drop of performance for the subregions submitted to different meteorological influences.
-However, the losses of performance are globally more important than before, suggesting that more complex methods with moisture variables are less transposable to another subregion, even though both are located within the same grid cell of the reanalysis dataset.
+However, the losses of performance are globally more important than before, suggesting that more complex methods with moisture variables are less transposable to another subregion (consistent with the observations of \citet{Chardon2014}), even though both are located within the same grid cell of the reanalysis dataset.
 Moisture fields have greater variability than pressure fields, and thus a change in the spatial windows can have a greater impact on the method performance.
 Indeed, the two regions with the lowest cross-compatibility are the Upper Rhone Valley (7) and the Southeast ridges (8), which have similar optimal pressure levels and temporal windows to other regions, but have rather different spatial windows on the moisture predictor.
+
+Predictors based on moisture variables do significantly increase the prediction skill, and are thus recommended, as long as they are reliable.
+In real-time forecasting, the reliability depends on the lead time: for lead times superior to 3-4 days the uncertainties related to moisture variables from NWP models are fairly high, which reduce the relevance of methods relying on this information.
+In climate studies, it mainly depends on the coherence of the climatologies between the archive and the model outputs.
+One should however not establish an AM with moisture variables for a too large region, as the transferability is reduced \citep[see also][]{Chardon2014}.
 

### 2016-12-22 Optimization case study - JoH/elsarticle-template.tex
JoH paper under correction.

@@
 \usepackage{gensymb}
+
+%TODO: read again
+%TODO: tenses
+%TODO: Elsevier english editing
+%TODO: more hydrology
 
@@
 \address[unibe]{University of Bern, Oeschger Centre for Climate Change Research, Institute of Geography, Bern, Switzerland}
-\address[terranum]{Terranum SARL, Bussigny, Switzerland}
 \address[lthe]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}
@@
 \begin{abstract}
-Analogue methods aim at predicting precipitation based on synoptic predictors provided by general circulation models or numerical weather prediction models.
+Analogue methods provide a statistical precipitation prediction based on synoptic predictors supplied by general circulation models or numerical weather prediction models.
 The method samples a selection of days in the archives that are similar to the target day to predict, and consider the set of their corresponding observed precipitation (the predictand) as the conditional distribution for the target day.
-The relationship between predictors and predictands relies on some parameters that characterize how and where the similitude between two atmos+pheric situations is defined.
+The relationship between predictors and predictands relies on some parameters that characterize how and where the similitude between two atmospheric situations is defined.
 
-This relationship is usually established by a semi-automatic sequential procedure that has strong limitations: (i) it cannot automatically choose the pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it could not easily handle new degrees of freedom.
+This relationship is usually established by a semi-automatic sequential procedure that has strong limitations: (i) it cannot automatically choose the pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it cannot easily handle new degrees of freedom.
 A new global optimization approach relying on genetic algorithms can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
@@
 
-In this work, the global optimization is applied to the Rh\^{o}ne catchment, in the Swiss Alps.
-The performance scores are significantly increased compared to a reference method, and this even to a greater extent for days with high precipitation totals.
+In this work, the global optimization was applied to the Rh\^{o}ne catchment in the Swiss Alps.
+The performance scores increased compared to reference methods, and this even to a greater extent for days with high precipitation totals.
 The resulting parameters were found to be relevant and coherent between the different subregions of the catchment.
-Moreover, they are obtained automatically and objectively, which reduces efforts invested in exploration attempts when adapting the method to a new region or for a new predictand.
-In addition, the approach allows for new degrees of freedom, such as a weighting between the pressure levels, and non overlapping spatial windows.
+Moreover, they were obtained automatically and objectively, which reduces efforts invested in exploration attempts when adapting the method to a new region or for a new predictand.
+In addition, the approach allowed for new degrees of freedom, such as a weighting between the pressure levels, and non overlapping spatial windows.
 \end{abstract}
@@
 \begin{keyword}
-Precipitation prediction\sep
-Precipitation downscaling\sep
-Analogue method\sep
-Optimization\sep
-Genetic algorithms\sep
+precipitation prediction\sep
+analogue method\sep
+optimization\sep
+genetic algorithms\sep
 Alpine climate
@@
 
-The analogue method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1956, Lorenz1969}, that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Duband1970}.
+The analogue method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1956, Lorenz1969} that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Duband1970}.
 It uses predictor variables describing the synoptic atmospheric circulation in order to predict local-scale predictands of interest.
-It is often used to predict daily precipitation, either in an operational forecasting context \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Hamill2015, BenDaoud2016, Horton2016a}, or a climate context \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015, Raynaud2016b}.
+It is often used to predict daily precipitation, either in an operational forecasting context \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Horton2016a, Hamill2015, BenDaoud2016} or a climate context \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015, Raynaud2016b}.
 Other predictands are also considered, such as precipitation radar images \citep{Panziera2011,Foresti2015a}, temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016, Raynaud2016b}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, and radiation \citep{Bois1981, Raynaud2016b}.
 
-In operational forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies, it is used to downscale the outputs of general circulation model (GCM) or regional climate models (RCMs) simulation runs \citep{Dayon2015} or to reconstruct past weather conditions \citep{Caillouet2016}.
+In operational forecasting it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies it is used to downscale the outputs of general circulation model (GCM) or regional climate models (RCMs) simulation runs \citep{Dayon2015} or to reconstruct past weather conditions \citep{Caillouet2016}.
 In future climate studies, RCMs are often used to dynamically downscale precipitation to a local scale.
-However, even though the relevance of RCMs'outputs increases, precipitation processes are parametrized and a bias correction of the outputs is still often required.
-Moreover, their application is computer intensive and cannot cover the full range of GCMs products.
-Therefore the idea is to rely on past observations to bypass the small scale simulations and to go from the large scale situation to the end variables like precipitation by searching analogues in the archives.
+However, even though the relevance of RCMs'outputs increases, a bias correction of the outputs is still often required, particularly in complex terrain.
+Moreover, their application is computer intensive, which makes it difficult to cover all combinations of climate scenarios and GCMs.
+Therefore, the idea is to rely on past observations to bypass the small scale simulations and to go from the large scale situation to the end variables like precipitation by searching analogues in the archives.
 
@@
 A certain number of parameters define the relationship between predictors and predictands, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criterion itself, and finally the number of analogue situations to keep at each subsampling level.
-These parameters are usually calibrated by means of a semi-automatic sequential procedure \citep[see][for the details]{Bontron2004, Radanovics2013}, i.e.
+These parameters are usually calibrated by means of a semi-automatic sequential procedure \citep{Bontron2004, Radanovics2013}, i.e.
 by optimizing each single parameter one at a time, in an arbitrarily chosen order, with no or little reassessment.
-This sequential approach has therefore strong limitations: (i) it cannot automatically choose the optimal pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it could not easily handle new degrees of freedom, such as a weighting between the pressure levels.
+This sequential approach has therefore strong limitations: (i) it cannot automatically choose the optimal pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it cannot easily handle new degrees of freedom, such as a weighting between the pressure levels.
 Thus, even if the processing involved is relatively fast, the sequential approach requires laborious assessments of predictors combinations (variables, pressure levels, temporal windows), and presents a high risk of ending in a local optimum due to subjective initial choices and lack of consideration of parameter inter-dependencies.
-Other calibration methods exist for specific applications, such as the radar images \citep{Panziera2011, Foresti2015a}.
+Other calibration methods exist for specific applications, such as radar images \citep{Panziera2011, Foresti2015a}.
 
 With the perspective to overcome these limitations, a global optimization by genetic algorithms (GAs) was introduced.
-An intensive assessment work resulted in recommendations of parametrization of GAs in order to optimize AMs successfully \citet{Horton2016}.
-The present paper is based on these recommendations and apply them for precipitation prediction for the upper Rh\^{o}ne catchment in the Swiss Alps.
-It aims at proving the relevance of a fully-automatic, objective, and global, optimization technique for AMs.
-The applications are indeed numerous, as the AM has to be adapted to every new location it is applied, or to any new predictand it should predict.
+An intensive assessment work resulted in recommendations of parametrization of GAs in order to optimize AMs successfully \citep{Horton2016}.
+The present paper is based on these recommendations and apply them for precipitation prediction for the upper Rh\^{o}ne catchment in the Swiss Alps, using AMs of varying complexity.
+It aims at illustrating the relevance of a fully-automatic, objective, and global, optimization technique for AMs.
+The applications are indeed numerous, as AMs have to be adapted to every new location they are applied, or to any new predictand they should predict.
 
-A short overview of AMs is presented in section \ref{sec:data_methods}, as well as a summary of genetic algorithms in section \ref{sec:gas}.
-Section \ref{sec:case_study} describes the case study area.
-The results are first detailed for the optimization of the analogy on the atmospheric circulation only (section \ref{sec:optim_circul}), before being extended to a method adding a second level of analogy on moisture variables (section \ref{sec:optim_moisture}).
+Data, AMs, and the optimization techniques (sequential and GAs) are presented in section \ref{sec:data_methods}.
+The results are first given for the optimization of the analogy of the atmospheric circulation only (section \ref{sec:optim_circul}), before being extended to a method adding a second level of analogy on moisture variables (section \ref{sec:optim_moisture}).
 General discussions (section \ref{sec:discussion}) and conclusions (section \ref{sec:conclusions}) follow.
@@
 The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$.
-This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at allowing real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
-Even though the region is rather small, the meteorological influences related to extreme weather conditions varies substantially within it \citep[see][]{Horton2012}.
-Indeed, a high spatial variability exists, which is due to the complex orography of the region.
+This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
+Even though the region is rather small, the meteorological influences related to extreme weather conditions vary substantially within it \citep[see][]{Horton2012}.
+Indeed, a high spatial variability exists, which is due to the complex orography of the region, and the mix of various meteorological influences.
 Based on different climatological analyses, the gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}) :
@@
 
-The 48 years precipitation dataset (see section \ref{sec:intro}.\ref{sec:data}) was divided into a calibration period (CP) and a validation period (VP).
-Using data independent from the CP to validate the results is very important in order to assess the robustness of the improvements and to avoid over-parametrization of the method.
-Parameters determined on the CP are then applied to the VP in order to obtain a performance score for the independent period.
-
-In order to reduce potential bias related to trends linked to climate change or to the evolution in measurement techniques, the selection of the VP is evenly distributed over the entire series \citep{BenDaoud2010}.
-Thus, one year every six years were selected for validation, which represents a total of 8 years for the VP and 40 for CP.
-The choice of the sequence was made in order to have similar statistical characteristics between the CP and the VP.
-
 \subsection{Data}
@@
 
-The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series one wants to predict.
+The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather variable one wants to predict.
 
@@
 It helps accounting for local variability, mainly when convective processes are involved, which increases slightly the prediction skill.
+
+The 48 years precipitation dataset (see section \ref{sec:data}) was divided into a calibration period (CP) and a validation period (VP).
+Using data independent from the CP to validate the results is very important in order to assess the robustness of the proposed improvements and to avoid over-parametrization of the method.
+
+In order to reduce potential bias related to trends linked to climate change or to the evolution in measurement techniques, the selection of the VP is evenly distributed over the entire series \citep{BenDaoud2010}.
+Thus, one year every six years were selected for validation, which represents a total of 8 years for the VP and 40 for CP.
+The choice of the sequence was made in order to have similar statistical characteristics between the CP and the VP.
 

### 2017-01-10 Optimization case study - JoH/elsarticle-template.tex
Analysis of the optimal number of predictors.

@@
 Parallel analyses showed that the analogy of circulation is incomplete, and that the geopotential still contains relevant information that can improve the statistical relationship.
-Therefore, a third predictor was added (still on the geopotential height) that the optimizer could use along with the previous parameters.
+Therefore, a third followed by a fourth predictor were added (still on the geopotential height) that the optimizer could use along with the previous parameters.
 There was no constraint on the predictors, so that the same pressure level could be selected more than once.
 Some improvements were found on the score, both for the CP and the VP, confirming that this additional information is beneficial for the quality of the prediction.
-We then tried with 4 predictors, and so on, up to 8.
-Every time a new predictor to optimize was added, the score on the CP increased, but in a reduced amount.
-However, the score value on the VP dropped after 4 predictors, revealing an over-parametrization of the method, and thus a lack of robustness.
-Considering 4 predictors is optimal for this case study, since the gain in CRPSS is significant.
-It cannot be excluded that another number would prevail in another region than the upper Rh\^{o}ne catchemnt, under other meteorological conditions.
 
@@
 
+The number of predictor was then successively increased up to ten, considering the weighting of the analogy criteria values.
+The addition of predictors constantly (for both the CP and the VP) improved the prediction skill only up to four predictors (Figure \ref{fig:figure_nb_levels}).
+Afterwards, the score on the VP is more variable, showing eventually even a decrease, which revealed an over-parametrization of the method, and thus a lack of robustness.
+After four predictors, the score on the CP does not increase substantially, and might even present some local decrease due to increasing difficulty for the optimizer to converge.
+Considering four predictors is considered optimal for this case study, since the gain in CRPSS is significant, and the model remains relatively simple.
+It cannot be excluded that another number would prevail in another region than the upper Rh\^{o}ne catchemnt, under other meteorological conditions, or with another reanalysis dataset.
+
 \subsection{Which parameters are optimized ?}
 
-The chosen method for the atmospheric circulation analogy, based on 4 levels of the geopotential, and that will be named 4Zo, is made of the following degrees of freedom:
+The chosen method for the atmospheric circulation analogy, based on four levels of the geopotential, and that will be named 4Zo, is made of the following degrees of freedom:
 
@@
 The resulting spatial windows (Figure \ref{fig:spatial_windows_4Zo}) may look very diverse first, but there are significant similarities for subregions located within the same vicinity.
-The first 4 subregions are characterized by a large spatial window on the upper level, whereas it is smaller elsewhere.
+The first four subregions are characterized by a large spatial window on the upper level, whereas it is smaller elsewhere.
 For most subregions, the second level (Z700) is represented by thin and longitudinally extended domains.
@@
 
-Two methods were assessed: one with 2 moisture predictors (moisture index on 2 pressure levels or at 2 different hours) named 4Zo-2MIo, and one with 4 moisture predictors named 4Zo-4MIo.
-When introducing 2 predictors for the moisture analogy, the number of degrees of freedom raises to 42, and to 54 with 4 predictors.
+Two methods were assessed: one with 2 moisture predictors (moisture index on 2 pressure levels or at 2 different hours) named 4Zo-2MIo, and one with four moisture predictors named 4Zo-4MIo.
+When introducing two predictors for the moisture analogy, the number of degrees of freedom raises to 42, and to 54 with four predictors.
 
@@
 As for the pressure levels, Z1000 that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) is now less chosen (once or even not at all) for both 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}) and 4Zo-4MIo (not shown).
-There is indeed a vertical shift of the previously selected Z1000 for higher levels, that is even slightly stronger with 4 moisture predictors than with 2.
+There is indeed a vertical shift of the previously selected Z1000 for higher levels, that is even slightly stronger with four moisture predictors than with 2.
 This change is likely due to the fact that when considering only the circulation analogy, the method tries to take into account information that can serve as proxy for moisture assessment, whereas it does not need it with the moisture index.
@@
 The selected pressure levels for the analogy on the moisture index are strongly centered around 700~hPa and 600~hPa.
-No other value has been selected when considering 2 pressure levels (Table \ref{table:levels_GA_4Zo_2MIo}), and when considering 4 levels, 850~hPa and 500~hPa were sometimes also selected (not shown).
+No other value has been selected when considering two pressure levels (Table \ref{table:levels_GA_4Zo_2MIo}), and when considering four levels, 850~hPa and 500~hPa were sometimes also selected (not shown).
 However, even in this latter method, the 700~hPa and 600~hPa levels still hold 78 \% of the selection.
@@
 The optimized spatial windows for the atmospheric circulation have also changed (Figure \ref{fig:spatial_windows_4Zo-2MIo}; results of 4Zo-4MIo are not shown but present the same trends).
-The very large domains on the upper level of the 4 first subregions are not present anymore, and more variability can be observed.
+The very large domains on the upper level of the four first subregions are not present anymore, and more variability can be observed.
 The selected points for the analogy on the moisture index are always located nearby the catchment, including at least 1 of the nearest points from the reanalysis dataset, and the spatial windows are relatively small.
@@
 The optimized methods also perform significantly better than the reference method based on the moisture index optimized by the sequential procedure.
-However, there is no drastic difference between both 4Zo-2MIo and 4Zo-4MIo methods, which suggests that considering 4 moisture predictors is not necessary.
+However, there is no drastic difference between both 4Zo-2MIo and 4Zo-4MIo methods, which suggests that considering four moisture predictors is not necessary.
 When it comes to improvements for days with precipitation above the 3 thresholds (P\(\geq\)1~mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the prediction compared to the reference method, mainly for heavy rainfall.
@@
 \begin{itemize}
-	\item Using 4 pressure levels for the analogy of circulation.
-It seems to be the optimal number for the studied region.
-Beyond that value the validation score drops, revealing a loss in robustness due to over-parametrization.
+	\item Using four pressure levels for the analogy of circulation.
+It seems to be an optimal number for the studied region, afterwards the validation score is more variable, revealing a loss in robustness due to over-parametrization.
 	\item The automatic and joint optimization of all parameters: the analogues number, the selection of the pressure levels and the temporal windows, and the spatial windows.
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.4cm]{figures/fig02.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig02.pdf}}
+	\caption{Performance score (CRPSS) on the CP and the VP for three stations (1 - Swiss Chablais, 5 - Southern valleys, 8 - Southeast ridges) when varying the number of geopotential height levels available to the optimizer.}
+	\label{fig:figure_nb_levels}
+\end{figure}
+
+\begin{figure}[t]
+	\centerline{\includegraphics[width=8.4cm]{figures/fig03.pdf}}
 	\caption{Optimized spatial windows for the 4Zo method (analogy of atmospheric circulation on 4 pressure levels).
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig03.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig04.pdf}}
 	\caption{Performance score (CRPSS) of the reference methods 2Z (Table \ref{table:params_R1}) and the optimized 4Zo method for the CP and the VP for every subregion.}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.4cm]{figures/fig04.pdf}}
+	\centerline{\includegraphics[width=8.4cm]{figures/fig05.pdf}}
 	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo, calibration and validation periods.}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.4cm]{figures/fig05.pdf}}
+	\centerline{\includegraphics[width=8.4cm]{figures/fig06.pdf}}
 	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 2 pressure levels).
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig06.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig07.pdf}}
 	\caption{Performance score (CRPSS) of the reference methods 2Z-2MI (Table \ref{table:params_R2}) and the optimized 4Zo-2MIo method for the CP and the VP for every subregion.}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig07.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig08.pdf}}
 	\caption{Number of analogues for the different regions and the various methods resulting from the optimization.
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.4cm]{figures/fig08.pdf}}
+	\centerline{\includegraphics[width=8.4cm]{figures/fig09.pdf}}
 	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo-2MIo, calibration and validation periods.}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig09.pdf}}
+	\centerline{\includegraphics[width=8.8cm]{figures/fig10.pdf}}
 	\caption{Distribution of the optimal weights for the predictors of the first level of analogy (geopotential heights) of the 4Zo, 4Zo-2MIo, and 4Zo-4MIo methods.
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=7.5cm]{figures/fig10.pdf}}
+	\centerline{\includegraphics[width=7.5cm]{figures/fig11.pdf}}
 	\caption{Example of the evolution of the performance score of the best individual over 8 independent optimizations.}

### 2017-01-10 Optimization case study - JoH/elsarticle-template.tex
Obled's corrections.

@@
 
-This relationship is usually established by a semi-automatic sequential procedure that has strong limitations: (i) it cannot automatically choose the pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it cannot easily handle new degrees of freedom.
+This relationship is usually established by a semi-automatic sequential procedure that has strong limitations: (i) it cannot automatically choose the pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters, and (iii) it cannot easily handle new degrees of freedom.
 A new global optimization approach relying on genetic algorithms can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
@@
 It uses predictor variables describing the synoptic atmospheric circulation in order to predict local-scale predictands of interest.
-It is often used to predict daily precipitation, either in an operational forecasting context \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Horton2016a, Hamill2015, BenDaoud2016} or a climate context \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015, Raynaud2016b}.
+It is often used to predict daily precipitation, either in an operational forecasting context \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Horton2016a, Hamill2015, BenDaoud2016} or a climate downscaling context \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015, Raynaud2016b}.
 Other predictands are also considered, such as precipitation radar images \citep{Panziera2011,Foresti2015a}, temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016, Raynaud2016b}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, and radiation \citep{Bois1981, Raynaud2016b}.
 
-In operational forecasting it has been used mainly by practitioners, notably hydropower companies or flood forecasting services, while in climate studies it is used to downscale the outputs of general circulation model (GCM) or regional climate models (RCMs) simulation runs \citep{Dayon2015} or to reconstruct past weather conditions \citep{Caillouet2016}.
+In operational forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services.
+They need to anticipate water yields or to issue early flood warnings several days in advance.
+The classical forecasting chain consists in using limited area models (e.g.
+AROME, or COSMO) forced by global NWP (numerical weather prediction) models with a lower resolution.
+However, their use require very important processing capacities, and the resulting forecast still present large uncertainties and biases.
+Although these outputs are essential, they can be supplemented by other sources of forecasts providing useful information.
+In contrast to local NWP models, AMs can transform at low cost the synoptic-scale information provided by the global NWP into precipitation forecasts, by using the natural local behavior in response to synoptic-scale influence stored in the archive of observed precipitation.
+Running an AM approach is so quick that it can search for analogues for every day up to 10 days ahead, eventually for the different traces of an ensemble forecast and/or issued by different NWP models (e.g.
+NOAA-GFS or ECMWF-IFS), in a matter of minutes.
+
+In climate studies it is used to downscale the outputs of general circulation model (GCM) or regional climate models (RCMs) simulation runs \citep{Dayon2015} or to reconstruct past weather conditions \citep{Caillouet2016}.
 In future climate studies, RCMs are often used to dynamically downscale precipitation to a local scale.
@@
 
-A big advantage of AMs is that they create realistic precipitation patterns for a region, provided that the analogue dates are the same, since they are based on observed situations with consistent spatial distribution \citep{Radanovics2013, Chardon2014}.
+Beyond being computationally inexpensive, another big advantage of AMs is that they create realistic precipitation patterns for a region, provided that the analogue dates are the same, since they are based on observed situations with consistent spatial distribution \citep{Radanovics2013, Chardon2014}.
 For the same reason, they can also provide multivariate predictions that are physically consistent \citep{Raynaud2016b}.
 
-The method can be designed with multiple successive subsampling steps, each of them relying on different meteorological variables.
+The method can be designed with multiple successive subsampling steps, or analogy levels, each of them relying on different meteorological variables.
 A certain number of parameters define the relationship between predictors and predictands, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criterion itself, and finally the number of analogue situations to keep at each subsampling level.
@@
 by optimizing each single parameter one at a time, in an arbitrarily chosen order, with no or little reassessment.
-This sequential approach has therefore strong limitations: (i) it cannot automatically choose the optimal pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it cannot easily handle new degrees of freedom, such as a weighting between the pressure levels.
+This sequential approach has therefore strong limitations: (i) it cannot automatically choose the optimal pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it cannot easily handle new degrees of freedom, such as a possible weighting between the pressure levels.
 Thus, even if the processing involved is relatively fast, the sequential approach requires laborious assessments of predictors combinations (variables, pressure levels, temporal windows), and presents a high risk of ending in a local optimum due to subjective initial choices and lack of consideration of parameter inter-dependencies.
@@
 Indeed, a high spatial variability exists, which is due to the complex orography of the region, and the mix of various meteorological influences.
-Based on different climatological analyses, the gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}) :
+Based on different climatological analyses, the precipitation gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}) :
 
@@
 Predictors are generally extracted from reanalysis datasets.
-NCEP-NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} are used here, but it could be any other reanalysis dataset.
+NCEP-NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} is used here, but it could be any other reanalysis dataset.
 
@@
 the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008.
-The time series from every available gauging station were averaged over subregions of approximately 500~km$^{2}$ in order to smooth local effects \citep{Obled2002, Marty2012}.
+The time series from every available gauging station were averaged over the ten subregions of approximately 500~km$^{2}$ each in order to smooth local effects \citep{Obled2002, Marty2012}.
 It helps accounting for local variability, mainly when convective processes are involved, which increases slightly the prediction skill.
+
+It must be stressed that the predictand here is a temporally cumulated variable, compared to the meteorological predictors, which may be considered instantaneous.
+Depending on the duration of the accumulation period (here 24h, but could have been 6, 12, 24h, or more), the choice of predictors will vary.
 
@@
 
-The other most know parametrization adds a second level of analogy on moisture variables (method 2Z-2MI, Table \ref{table:params_R2}).
+The other most known parametrization adds a second level of analogy on moisture variables (method 2Z-2MI, Table \ref{table:params_R2}).
 The predictor that \citet{Bontron2004} found optimal for the France territory is a moisture index made of the product of the precipitable water with the relative humidity at 850~hPa (RH850).
 \cite{Horton2012a} confirmed that this index is also better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis considered independently.
-When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
-When a second level of analogy is added, a higher number of analogues $N_{1}$ is kept on the first level.
+When adding a second level of analogy, $N_{2}$ dates are subsampled within the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
+When this second level of analogy is added, a higher number of analogues $N_{1}$ is kept on the first level.
 Moisture fields are not as well predicted by NWP models as pressure variables.
-It means that the 2Z-2MI method, when used in real-time forecasting, is very dependent on the skill of the NWP model in predicting moisture fields, and thus is often used on limited lead times.
+It means that the 2Z-2MI method, when used in real-time forecasting, is very dependent on the skill of the NWP model in predicting moisture fields, and thus its use is often restricted to the first lead times.
 
@@
 The performance assessment in the present context consists in verifying the prediction of an ensemble-probabilistic technique.
+The set of precipitations values collected with each analogue can be considered as a sample drawn from the conditional distribution associated with the current circulation.
 The score that is most often used to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
@@
 
+Note however that the choice of the reference does not matter so much, since we shall consider more its relative increase or decrease rather than the CRPSS absolute value in order to assess a possible improvement.
+
 \subsection{Sequential calibration}
@@
 	\begin{enumerate}
-		\item Identification of the most skilled unitary cell of all predictors jointly of the analogy level, over a large domain, by a full scanning of the grid.
+		\item Identification, for the analogy level considered, of the most skilled unitary cell of all predictors jointly, over a large domain, by a full scanning of the grid.
 		\item From this most skilled cell, the spatial window is expanded by successive iterations in the direction of greater performance gain until no improvement is reached.
@@
 It is indeed mainly a matter of time.
-When the optimizer gets closer to the global optimum, any new improvement takes more time to appear (see for example the slow-down of the improvements over generations in Figure \ref{fig:evolution}), and the final adjustment of the parameters is very time consuming \citep{Back1993a}.
+When the optimizer gets closer to the global optimum, any new improvement takes more time to appear (see for example the slow-down of the improvements over generations in Figure \ref{fig:evolution}), and the final adjustment of the parameters can be very time consuming \citep{Back1993a}.
 For problems that require a significant amount of time in order to evaluate the objective function, as in the case of AMs, the number of generations has to be limited in order to get reasonable processing time.
-Thus, different acceptable solutions can result from one or more optimizations \citep{Holland1992b}.
-This is a strength and a weakness of GAs: they are very good at exploring complex parameter spaces in order to identify the most promising areas, but they will not necessarily always find the best solution with the optimal values of all parameters \citep{Holland1992b}.
+Thus, different acceptable solutions can result from one or more optimization runs \citep{Holland1992b}.
+This is both a strength and a weakness of GAs: they are very good at exploring complex parameter spaces in order to identify the most promising areas, but they will not necessarily always find the best solution with the optimal values of all parameters \citep{Holland1992b}.
 
-The optimizations were performed based on the recommended GAs parametrization for AMs as described in \citet{Horton2016}.
+The optimizations were here performed based on the recommended GAs parametrization for AMs as described in \citet{Horton2016}.
 As the optimization is mostly sensitive to the mutation operator (that randomly changes some values in the parameters sets), parallel optimizations are considered with variants of this operator, according to \citet{Horton2016}:
@@
 
-A population size of 500 individuals (parameter sets of the AM to be detailed hereunder) was considered, and the optimization was stopped when the best individual (with the highest CRPSS performance score) did not evolve for 20 generations (cycles of the optimization).
+A population size of 500 individuals (i.e.
+parameter sets of the AM to be detailed hereunder) was considered, and the optimization was stopped when the best individual (with the highest CRPSS performance score) did not evolve for 20 generations (cycles of the optimization).
 
@@
 The reference method for the analogy of the atmospheric circulation (2Z, Table \ref{table:params_R1}), based on Z500 and Z1000, was first considered.
-The optimizer had to choose simulatneously the number of analogues, both spatial windows with no overlapping constraint (they can differ from one pressure level to another), as well as the temporal windows (hours of observation of the geopotential), which cannot be achieved with the sequential calibration technique.
-With these degrees of freedom, a relative CRPSS improvement of 3.97\% and 2.45\% in average was obtained for the CP and the VP respectively, with regard to the reference method based on Z500 and Z1000.
+The optimizer had to choose simulatneously the number of analogues, both spatial windows with no overlapping constraint (i.e.
+they can differ from one pressure level to another), as well as the temporal windows (hours of observation of the geopotential), which cannot be achieved with the sequential calibration technique.
+With these degrees of freedom, a relative CRPSS improvement of 3.97\% and 2.45\% in average was obtained for the CP and the VP respectively, with regard to the reference (sequential) method based on Z500 and Z1000.
 Some tests showed that most of the gains are due to the non-overlapping spatial windows.
-This is not a large improvement, but it demonstrated that the optimizer was able to get relevant parameters.
+This may not be seen as a large improvement, but it demonstrated that the optimizer was able to get relevant parameters.
 
@@
 However, most solutions were very close in terms of score.
-The averaged relative improvement of the CRPSS is 5.63\% for the CP and 3.82\% for the VP.
+The averaged relative improvement of the CRPSS is now 5.63\% for the CP and 3.82\% for the VP.
 The pressure levels that were chosen are Z500 or Z700 for the upper level, and Z925 or Z1000 (most often) for the lower level.
@@
 Considering four predictors is considered optimal for this case study, since the gain in CRPSS is significant, and the model remains relatively simple.
-It cannot be excluded that another number would prevail in another region than the upper Rh\^{o}ne catchemnt, under other meteorological conditions, or with another reanalysis dataset.
+It cannot be excluded that another number would prevail in another region than the upper Rh\^{o}ne catchment, under other meteorological conditions, or with another reanalysis dataset.
 
@@
 First of all, the level Z1000 is always selected twice (the first time at 6 or 12~h, and the second always at 30~h) and Z700 is selected once for every subregion (always at 24~h).
-The level which varies from one subregion to another is the upper level (however always at 12~h), which is Z300 for the North-West part of the catchment, Z500 for most of the subregions, and Z600 for the Conches Valley.
-Its spatial distribution is however homogeneous.
+The level which varies from one subregion to another is the upper level (however always at 12~h), which is Z300 for the North-West part of the catchment, Z500 for most of the subregions, and Z600 for the Conches Valley, and is so spatially consistent.
 The optimizer thus provided consistent selections of pressure levels and temporal windows.
@@
 These two regions have different climate properties than the others as they are particularly sensitive to southerly flows.
-Indeed, almost all heavy precipitation events occurred under a southerly regime, such as the Liguria, Piémont and Aosta regions in Italy, whereas the other subregions of the catchment had heavy precipitation events mainly under a westerly regime \citep{Horton2012}.
+Indeed, almost all heavy precipitation events occurred under a southerly regime, such as the Liguria, Piedmont and Aosta regions in Italy, whereas the other subregions of the catchment had heavy precipitation events mainly under a westerly regime \citep{Horton2012}.
 Thus, as the performance score is significantly influenced by heavy precipitation values, the parameters for the different subregions are optimized to better predict these days.
 It can then be expected that the optimal parameters differ between these two subregions and the other ones.
-This points at the importance of taking into account leading meteorological influences during discretization, that are not always best represented by the physical distance.
+This points at the importance of taking into account leading meteorological influences during discretization, that are not always best represented by the geographical distance.
 
@@
 
-The optimal final number of analogues do not vary much: $23 \leq N_{1} \leq 33$ for 4Zo and $21 \leq N_{2} \leq 28$ for 4Zo-2MIo.
+The optimal final numbers of analogues do not vary much: $23 \leq N_{1} \leq 33$ for 4Zo and $21 \leq N_{2} \leq 28$ for 4Zo-2MIo.
 However, the optimal number of $N_{1}$ analogues of the first level of 4Zo-2MIo varies to a greater extent: $48 \leq N_{1} \leq 84$.
@@
 
-As for the pressure levels, Z1000 that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) is now less chosen (once or even not at all) for both 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}) and 4Zo-4MIo (not shown).
+As for the pressure levels, Z1000 that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) is now less often chosen (once or even not at all) for both 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}) and 4Zo-4MIo (not shown).
 There is indeed a vertical shift of the previously selected Z1000 for higher levels, that is even slightly stronger with four moisture predictors than with 2.
@@
 When it comes to the moisture analogy, there is a clear trend to select 12~h and 24~h when considering 2 predictors.
+However, it must be remembered that this holds for our predictand, the accumulated precipitation over 06-30~h~UTC, and that it is expected to differ if we change the window (e.g.
+00-24~h~UTC) or its duration.
 
@@
 Predictors based on moisture variables do significantly increase the prediction skill, and are thus recommended, as long as they are reliable.
-In real-time forecasting, the reliability depends on the lead time: for lead times superior to 3-4 days the uncertainties related to moisture variables from NWP models are fairly high, which reduce the relevance of methods relying on this information.
-In climate studies, it mainly depends on the coherence of the climatologies between the archive and the model outputs.
+In real-time forecasting, their reliability depends on the lead time: for lead times superior to 3-4 days the uncertainties related to moisture variables from NWP models becomes fairly high, which reduces the relevance of methods relying on this information.
+In climate downscaling studies, it mainly depends on the coherence of the climatologies between the archive and the GCM model outputs.
 One should however not establish an AM with moisture variables for a too large region, as the transferability is reduced \citep[see also][]{Chardon2014}.
@@
 
-The optimization of the AM by means of GAs has been undertaken in stages by releasing progressively new degrees of freedom.
+The optimization of the AM by means of GAs has been undertaken in successive stages by releasing progressively new degrees of freedom.
 This approach allowed us to differentiate the contributions to performance gains, as well as to identify possible over-parametrization.
-The main improvements for the present case study are due to the following factors:
+The main improvements obtained in the present case study are due to the following factors:
 
 \begin{itemize}
-	\item Using four pressure levels for the analogy of circulation.
-It seems to be an optimal number for the studied region, afterwards the validation score is more variable, revealing a loss in robustness due to over-parametrization.
+	\item Using four pressure levels for the analogy of circulation seems to be an optimal number for the studied region, length of archive available, and target predictand considered.
+Beyond four, the validation score is more variable, revealing a loss in robustness due to over-parametrization.
 	\item The automatic and joint optimization of all parameters: the analogues number, the selection of the pressure levels and the temporal windows, and the spatial windows.
@@
 Finally, the discretization in subregions is an important process and should be handled with care.
-Indeed, the physical distance is not always the leading factor to define a subregion.
+Indeed, the geographical distance is not always the leading factor to define a subregion.
 For example, the Southeast ridges subregion do not behave like its surrounding and differ in its parametrization, due to different leading meteorological influences.
@@
 
-AMs optimized with GAs show an improvement of the prediction for days with heavier precipitation, including extremes.
-However, even though the distribution of analogue precipitation values moved towards the targeted extreme, no new extreme values were added to the sample of candidate situations.
-The extremes in AMs can be modelled by, for example, extrapolation of a truncated exponential or gamma distribution fitted to the analogue values \citep{Obled2002}.
+Furthermore, AMs optimized with GAs show an improvement of the prediction for days with heavier precipitation, including extremes.
+Even though no new extreme value is added to the existing precipitation archive, the distribution of analogue precipitation values for a target situation can move towards the targeted extreme by sampling better candidate situations.
+Then, the subset of precipitation values collected on the analogue dates can be considered as a sample of the conditional distribution of precipitation associated with this situation.
+A truncated exponential or a gamma distribution model can be fitted and extrapolated to extreme values not contained in the sample or even in the whole precipitation archive \citep{Obled2002}.
 Another possible approach is by combining AMs with other methods \citep[e.g.][]{Chardon2014}.

### 2017-01-11 Optimization case study - JoH/elsarticle-template.tex
Correction of the tenses.

@@
 %TODO: read again
-%TODO: tenses
 %TODO: Elsevier english editing
 %TODO: more hydrology
+%TODO: relative improvement of the crpss...
 
@@
 This relationship is usually established by a semi-automatic sequential procedure that has strong limitations: (i) it cannot automatically choose the pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters, and (iii) it cannot easily handle new degrees of freedom.
-A new global optimization approach relying on genetic algorithms can optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
-It allows taking into account parameters inter-dependencies, and selecting objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
+In this work, a global optimization approach relying on genetic algorithms could optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
+It allowed taking into account parameters inter-dependencies, and selecting objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
 
-In this work, the global optimization was applied to the Rh\^{o}ne catchment in the Swiss Alps.
+The global optimization was applied to some variants of the analogue method for the Rh\^{o}ne catchment in the Swiss Alps.
 The performance scores increased compared to reference methods, and this even to a greater extent for days with high precipitation totals.
@@
 Moreover, they were obtained automatically and objectively, which reduces efforts invested in exploration attempts when adapting the method to a new region or for a new predictand.
-In addition, the approach allowed for new degrees of freedom, such as a weighting between the pressure levels, and non overlapping spatial windows.
+In addition, the approach allowed for new degrees of freedom, such as a possible weighting between the pressure levels, and non overlapping spatial windows.
 \end{abstract}
@@
 
-In operational forecasting, it has been used mainly by practitioners, notably hydropower companies or flood forecasting services.
+In operational forecasting, it is used mainly by practitioners, notably hydropower companies or flood forecasting services.
 They need to anticipate water yields or to issue early flood warnings several days in advance.
@@
 The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$.
-This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
+This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aimed at real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
 Even though the region is rather small, the meteorological influences related to extreme weather conditions vary substantially within it \citep[see][]{Horton2012}.
-Indeed, a high spatial variability exists, which is due to the complex orography of the region, and the mix of various meteorological influences.
+Indeed, a high spatial variability of the precipitation climatology exists, which is due to the complex orography of the region, and the mix of various meteorological influences.
 Based on different climatological analyses, the precipitation gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}) :
@@
 
-The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather variable one wants to predict.
+AMs rely on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather variable one wants to predict.
 
 Predictors are generally extracted from reanalysis datasets.
-NCEP-NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} is used here, but it could be any other reanalysis dataset.
+NCEP-NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} was used here, but it could have been any other reanalysis dataset.
 
@@
 
-In order to reduce potential bias related to trends linked to climate change or to the evolution in measurement techniques, the selection of the VP is evenly distributed over the entire series \citep{BenDaoud2010}.
+In order to reduce potential bias related to trends linked to climate change or to the evolution in measurement techniques, the selection of the VP was evenly distributed over the entire series \citep{BenDaoud2010}.
 Thus, one year every six years were selected for validation, which represents a total of 8 years for the VP and 40 for CP.
@@
 Multiple variations of the methods exist, and most of them will not be detailed hereafter \cite[see][for more comprehensive listings]{BenDaoud2016}.
-However, there are mainly 2 parameterizations that are most often used for precipitation downscaling and that will be considered as reference: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
+However, there are mainly two parameterizations that are most often used for precipitation downscaling and that were considered as reference: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
 
@@
 
-\citet{Bontron2005} showed that the geopotential height at 500~hPa (Z500) and 1000~hPa (Z1000) are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criterion performs better than scores based on absolute distances.
+\citet{Bontron2005} show that the geopotential height at 500~hPa (Z500) and 1000~hPa (Z1000) are the best first predictors of the NCEP/NCAR reanalysis I dataset, and that the S1 criterion performs better than scores based on absolute distances.
 The reason for such better results is that the S1 criterion allows comparing the circulation pattern, by means of the gradients, rather than the absolute value of the geopotential height, which represent better the flow direction.
@@
 The predictor that \citet{Bontron2004} found optimal for the France territory is a moisture index made of the product of the precipitable water with the relative humidity at 850~hPa (RH850).
-\cite{Horton2012a} confirmed that this index is also better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis considered independently.
+\cite{Horton2012a} confirms that this index is also better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis I considered independently.
 When adding a second level of analogy, $N_{2}$ dates are subsampled within the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
@@
 With these degrees of freedom, a relative CRPSS improvement of 3.97\% and 2.45\% in average was obtained for the CP and the VP respectively, with regard to the reference (sequential) method based on Z500 and Z1000.
-Some tests showed that most of the gains are due to the non-overlapping spatial windows.
+Some tests showed that most of the gains were due to the non-overlapping spatial windows.
 This may not be seen as a large improvement, but it demonstrated that the optimizer was able to get relevant parameters.
@@
 
-Parallel analyses showed that the analogy of circulation is incomplete, and that the geopotential still contains relevant information that can improve the statistical relationship.
+Parallel analyses showed that the analogy of circulation is incomplete, and that geopotential heights still contain relevant information that can improve the statistical relationship.
 Therefore, a third followed by a fourth predictor were added (still on the geopotential height) that the optimizer could use along with the previous parameters.
@@
 The weighting operates in the combination of the S1 criteria processed on every level, which were previously averaged with equal weights.
-The role of this new degree of freedom is to give more weight to the levels with greater predictive capacity, and to consider the geopotential variability changes with altitude.
+The role of this new degree of freedom is to give more weight to the levels with greater predictive capacity, and to consider the differences in the geopotential height variability with altitude.
 
 The number of predictor was then successively increased up to ten, considering the weighting of the analogy criteria values.
-The addition of predictors constantly (for both the CP and the VP) improved the prediction skill only up to four predictors (Figure \ref{fig:figure_nb_levels}).
-Afterwards, the score on the VP is more variable, showing eventually even a decrease, which revealed an over-parametrization of the method, and thus a lack of robustness.
-After four predictors, the score on the CP does not increase substantially, and might even present some local decrease due to increasing difficulty for the optimizer to converge.
-Considering four predictors is considered optimal for this case study, since the gain in CRPSS is significant, and the model remains relatively simple.
+The addition of predictors globally improved the prediction skill (for both the CP and the VP) only up to four predictors (Figure \ref{fig:figure_nb_levels}).
+Afterwards, the score on the VP was more variable, showing eventually even a decrease, which revealed an over-parametrization of the method, and thus a lack of robustness.
+After four predictors, the score on the CP did not increase substantially, and could even present some local decrease due to increasing difficulty for the optimizer to converge.
+Selecting four predictors was considered optimal for this case study, since the gain in CRPSS was significant, and the model remained relatively simple.
 It cannot be excluded that another number would prevail in another region than the upper Rh\^{o}ne catchment, under other meteorological conditions, or with another reanalysis dataset.
@@
 
-The chosen method for the atmospheric circulation analogy, based on four levels of the geopotential, and that will be named 4Zo, is made of the following degrees of freedom:
+The chosen method for the atmospheric circulation analogy, based on four levels of the geopotential, and that will be named 4Zo, was made of the following degrees of freedom:
 
@@
 
-This sums up to 29 degrees of freedom that are optimized simultaneously.
+This sums up to 29 degrees of freedom that were optimized simultaneously.
 
@@
 
-The resulting CRPSS scores are provided in Figure \ref{fig:figure_crpss_4Zo} and are in average 35.8~\% for the CP and 35.5~\% for the VP, comparatively to 31.1~\% and 32.3~\% respectively for the reference method on the atmospheric circulation (optimized by the sequential procedure).
+The resulting CRPSS scores are provided in Figure \ref{fig:figure_crpss_4Zo} and were in average 35.8~\% for the CP and 35.5~\% for the VP, comparatively to 31.1~\% and 32.3~\% respectively for the reference method on the atmospheric circulation (optimized by the sequential procedure).
 The score was also calculated for three precipitation thresholds: P\(\geq\)1~mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_4Zo}).
-The gain in score increases with the precipitation threshold: the relative improvement of the CRPSS is in average, respectively for the different thresholds, 13.3~\%, 15.4~\% and 29.1~\% for the CP and 7.9~\%, 11.~1\% and 34.5~\% for the VP.
-The optimization improves thus even more the prediction for days with significant precipitation than usual days.
+The gain in score increased with the precipitation threshold: the relative improvement of the CRPSS was in average, respectively for the different thresholds, 13.3~\%, 15.4~\% and 29.1~\% for the CP and 7.9~\%, 11.~1\% and 34.5~\% for the VP.
+The optimization improved thus even more the prediction for days with significant precipitation than usual days.
 
@@
 
-The automatic selections of the pressure levels (Table \ref{table:levels_GA_4Zo}) and the temporal windows (not shown) for the analogy of circulation show a great homogeneity and are spatially consistent.
-First of all, the level Z1000 is always selected twice (the first time at 6 or 12~h, and the second always at 30~h) and Z700 is selected once for every subregion (always at 24~h).
-The level which varies from one subregion to another is the upper level (however always at 12~h), which is Z300 for the North-West part of the catchment, Z500 for most of the subregions, and Z600 for the Conches Valley, and is so spatially consistent.
+The automatic selections of the pressure levels (Table \ref{table:levels_GA_4Zo}) and the temporal windows (not shown) for the analogy of circulation showed a great homogeneity and were spatially consistent.
+First of all, the level Z1000 was always selected twice (the first time at 6 or 12~h, and the second always at 30~h) and Z700 was selected once for every subregion (always at 24~h).
+The level which varied from one subregion to another, however in a spatially consistent way, was the upper level (however always at 12~h), which was Z300 for the North-West part of the catchment, Z500 for most of the other subregions, and Z600 for the Conches Valley.
 The optimizer thus provided consistent selections of pressure levels and temporal windows.
@@
 The resulting spatial windows (Figure \ref{fig:spatial_windows_4Zo}) may look very diverse first, but there are significant similarities for subregions located within the same vicinity.
-The first four subregions are characterized by a large spatial window on the upper level, whereas it is smaller elsewhere.
-For most subregions, the second level (Z700) is represented by thin and longitudinally extended domains.
-The third level (Z1000 at 6 or 12~h) also contains longitudinally extended domains, but a bit larger.
-The last one (Z1000 at 30~h) is rather large and squared.
-Subregions number 5 (Southern valleys) and 6 (Southern ridges) have exactly the same spatial windows, which suggest that they behave in a similar way and thus could have been merged.
+The first four subregions were characterized by a large spatial window on the upper level, whereas it was smaller elsewhere.
+For most subregions, the second level (Z700) was represented by thin and longitudinally extended domains.
+The third level (Z1000 at 6 or 12~h) also contained longitudinally extended domains, but a bit larger.
+The last one (Z1000 at 30~h) was rather large and squared.
+Subregions number 5 (Southern valleys) and 6 (Southern ridges) had exactly the same spatial windows, which suggest that they behave in a similar way and thus could have been merged.
 This similarity is a good sign for the accuracy of the optimized parameters.
 
-The scores show non-negligible improvements for both the CP and the VP (Figure \ref{fig:figure_crpss_4Zo}) compared to the reference method optimized by the sequential procedure.
-Even more interestingly, the results for higher precipitation thresholds (Table \ref{table:scores_thresholds_4Zo}) show the largest improvements.
+The scores showed non-negligible improvements for both the CP and the VP (Figure \ref{fig:figure_crpss_4Zo}) compared to the reference method optimized by the sequential procedure.
+Even more interestingly, the results for higher precipitation thresholds (Table \ref{table:scores_thresholds_4Zo}) showed the largest improvements.
 This is of particular interest in the framework of flood forecasting.
@@
 
-The analysis of the parameters cross-compatibility shows that obviously, the parameters are optimal on the CP when they are optimized for a given subregion (Figure \ref{fig:crossing_4Zo} top).
-However, the losses in CRPSS when exchanging the parameters are not of the same magnitude between the different subregions.
-Indeed, the Upper Rhone Valley (7) and moreover the Southeast ridges (8) seem to behave significantly differently.
+The analysis of the parameters cross-compatibility showed that obviously, the parameters were optimal on the CP when they were optimized for a given subregion (Figure \ref{fig:crossing_4Zo} top).
+However, the losses in CRPSS when exchanging the parameters were not of the same magnitude between the different subregions.
+Indeed, the Upper Rhone Valley (7) and moreover the Southeast ridges (8) seemed to behave significantly differently.
 These two regions have different climate properties than the others as they are particularly sensitive to southerly flows.
@@
 
-Globally, the same pattern can be observed for the VP (Figure \ref{fig:crossing_4Zo} bottom), but in this case, minor improvements may occur when crossing the parameters, due to the presence of other events in the VP that may be better predicted by a different parameter set.
-The relatively small gaps in score between parameterizations indicate that even though the parameters may differ significantly, the performance may not be drastically affected.
-Even a change in the pressure level does not mean a radical drop of the score value.
+Globally, the same pattern could be observed for the VP (Figure \ref{fig:crossing_4Zo} bottom), but in this case, minor improvements could occur when crossing the parameters, due to the presence of other events in the VP that might have been better predicted by a different parameter set.
+The relatively small gaps in score between parameterizations indicated that even though the parameters might differ significantly, the performance might not be drastically affected.
+Even a change in the pressure level did not mean a radical drop of the score value.
 A different parametrization may lead to a distinct selection of analogue days, and thus to an improvement of the prediction under certain weather conditions at the expense of others.
@@
 Two methods were assessed: one with 2 moisture predictors (moisture index on 2 pressure levels or at 2 different hours) named 4Zo-2MIo, and one with four moisture predictors named 4Zo-4MIo.
-When introducing two predictors for the moisture analogy, the number of degrees of freedom raises to 42, and to 54 with four predictors.
+When introducing two predictors for the moisture analogy, the number of degrees of freedom raised to 42, and to 54 with four predictors.
 
-The optimization was processed on both levels of analogy simultaneously. This implies that the analogy of the atmospheric circulation may change due to the new moisture information.
+The optimization was processed on both levels of analogy simultaneously. This implies that the analogy of the atmospheric circulation could change due to the new moisture information.
 
@@
 
-Due to significant similarities between the results from 4Zo-2MIo and 4Zo-4MIo, the latter will only be partly shown in order to improve readability.
+Due to significant similarities between the results from 4Zo-2MIo and 4Zo-4MIo, the latter will only be partly shown.
 
-As previously, the optimized parameters differ from one subregion to another, and this even to a greater extent.
+As previously, the optimized parameters differed from one subregion to another, and this even to a greater extent.
 The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_4Zo-2MIo} for 4Zo-2MIo, along with the selected pressure levels for both the circulation and the moisture analogy (Table \ref{table:levels_GA_4Zo_2MIo}).
 
-The CRPSS scores of the optimized 4Zo-2MIo method are provided in Figure \ref{fig:figure_crpss_4Zo-2HIo} and amounts in average to 40~\% (CP) and 40.3~\% (VP), compared to 35.2~\% (CP) and 36.2~\% (VP) for the reference method on the moisture analogy optimized with the sequential procedure.
-The score for the 4Zo-4MIo method are relatively close, with 40.6~\% for both the CP and the VP (not shown as very similar repartition as Figure \ref{fig:figure_crpss_4Zo-2HIo}).
+The CRPSS scores of the optimized 4Zo-2MIo method are provided in Figure \ref{fig:figure_crpss_4Zo-2HIo} and amounted in average to 40~\% (CP) and 40.3~\% (VP), compared to 35.2~\% (CP) and 36.2~\% (VP) for the reference method on the moisture analogy optimized with the sequential procedure.
+The score for the 4Zo-4MIo method were relatively close, with 40.6~\% for both the CP and the VP (not shown as very similar repartition as Figure \ref{fig:figure_crpss_4Zo-2HIo}).
 
-As for 4Zo, the 4Zo-2MIo and 4Zo-4MIo methods present larger improvements in the prediction for significant rainfall (thresholds P\(\geq\)1~mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
-The improvement are relatively similar for 4Zo-2MIo (Table \ref{table:scores_thresholds_4Zo-2MIo}) and 4Zo-4MIo (not shown), with slightly superior scores for the latter on small precipitation (P\(\geq\)1~mm : 17.7~\% and 13.0~\%) and extremes (P\(\geq\)0.5\(\cdot\)P10 : 23.7~\% and 29.2~\%).
+As for 4Zo, the 4Zo-2MIo and 4Zo-4MIo methods presented larger improvements in the prediction for significant rainfall (thresholds P\(\geq\)1~mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
+The improvement were relatively similar for 4Zo-2MIo (Table \ref{table:scores_thresholds_4Zo-2MIo}) and 4Zo-4MIo (not shown), with slightly superior scores for the latter on small precipitation (P\(\geq\)1~mm : 17.7~\% and 13.0~\%) and extremes (P\(\geq\)0.5\(\cdot\)P10 : 23.7~\% and 29.2~\%).
 
@@
 
-When optimizing a method made of 2 levels of analogy, the introduction of moisture variables in the second level has an influence on the parameter values of the first level.
+When optimizing a method made of 2 levels of analogy, the introduction of moisture variables in the second level had an influence on the parameter values of the first level.
 It means that the two levels of analogy bring complementary information, and are thus not independent.
@@
 
-As for the sequential procedure, the optimal value of $N_{1}$ increases when adding a second level of analogy (Figure \ref{fig:figure_nb_analogs}).
-One can also notice that the optimal number of analogues $N_{2}$ for the second level of analogy of 4Zo-2MIo is slightly inferior to $N_{1}$ from 4Zo, but very close.
-There is globally a tendency between the optimal analogue number values of both methods: $N_{1}$ of the 4Zo method, and $N_{1}$ and $N_{2}$ of 4Zo-2MIo tend to be higher or lower altogether for a given region.
+As for the sequential procedure, the optimal value of $N_{1}$ increased when adding a second level of analogy (Figure \ref{fig:figure_nb_analogs}).
+One can also notice that the optimal number of analogues $N_{2}$ for the second level of analogy of 4Zo-2MIo was slightly inferior to $N_{1}$ from 4Zo, but very close.
+There was globally a tendency between the optimal analogue number values of both methods: $N_{1}$ of the 4Zo method, and $N_{1}$ and $N_{2}$ of 4Zo-2MIo tended to be higher or lower altogether for a given region.
 
-The optimal final numbers of analogues do not vary much: $23 \leq N_{1} \leq 33$ for 4Zo and $21 \leq N_{2} \leq 28$ for 4Zo-2MIo.
-However, the optimal number of $N_{1}$ analogues of the first level of 4Zo-2MIo varies to a greater extent: $48 \leq N_{1} \leq 84$.
+The optimal final numbers of analogues did not vary much: $23 \leq N_{1} \leq 33$ for 4Zo and $21 \leq N_{2} \leq 28$ for 4Zo-2MIo.
+However, the optimal number of $N_{1}$ analogues of the first level of 4Zo-2MIo varied to a greater extent: $48 \leq N_{1} \leq 84$.
 In this latter method, it may be problematic to consider a fixed and unique value for all regions.
 
-As for the pressure levels, Z1000 that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) is now less often chosen (once or even not at all) for both 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}) and 4Zo-4MIo (not shown).
-There is indeed a vertical shift of the previously selected Z1000 for higher levels, that is even slightly stronger with four moisture predictors than with 2.
-This change is likely due to the fact that when considering only the circulation analogy, the method tries to take into account information that can serve as proxy for moisture assessment, whereas it does not need it with the moisture index.
+As for the pressure levels, Z1000 that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) was here less often chosen (once or even not at all) for both 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}) and 4Zo-4MIo (not shown).
+There was indeed a vertical shift of the previously selected Z1000 for higher levels, that was even slightly stronger with four moisture predictors than with two.
+This change is likely due to the fact that when considering only the circulation analogy, the method tried to take into account information that can serve as proxy for moisture assessment, whereas it did not need it with the moisture index.
 This aspect has never been demonstrated before, as sequential calibration tools do not allow it.
-It can only be assessed by a global optimization technique that can tune jointly both levels of analogy.
+It can only be assessed by a global optimization technique that can work jointly on both levels of analogy.
 
-The selected pressure levels for the analogy on the moisture index are strongly centered around 700~hPa and 600~hPa.
-No other value has been selected when considering two pressure levels (Table \ref{table:levels_GA_4Zo_2MIo}), and when considering four levels, 850~hPa and 500~hPa were sometimes also selected (not shown).
-However, even in this latter method, the 700~hPa and 600~hPa levels still hold 78 \% of the selection.
-It is thus more efficient, in terms of prediction performance, to consider one of this level several times at different hours rather than selecting another pressure level.
+The selected pressure levels for the analogy on the moisture index were strongly centered around 700~hPa and 600~hPa.
+No other value was selected when considering two pressure levels (Table \ref{table:levels_GA_4Zo_2MIo}), and when considering four levels, 850~hPa and 500~hPa were sometimes also selected (not shown).
+However, even in this latter method, the 700~hPa and 600~hPa levels still held 78 \% of the selection.
+It was thus more efficient, in terms of prediction performance, to consider one of this level several times at different hours rather than selecting another pressure level.
 Besides, the optimizer never chose the same pressure level at the same hour for any variable, even though it was allowed to do so.
-The selected pressure levels for the analogy on the moisture index differ from the parameters resulting from the reference method optimized by the sequential procedure (Tables \ref{table:params_R2} and \ref{table:levels_GA_4Zo_2MIo}, last row).
+The selected pressure levels for the analogy on the moisture index differed from the parameters resulting from the reference method optimized by the sequential procedure (Tables \ref{table:params_R2} and \ref{table:levels_GA_4Zo_2MIo}, last row).
 It is possible that the level 850~hPa is more optimal for the region for which the reference parameterization was established.
@@
 
-The selection of the temporal windows for the atmospheric circulation is similar to the preceding optimization (in the order of increasing pressure: 12~h, 24/30~h, 12~h, 30~h), but sometimes with a bit more variability.
-When it comes to the moisture analogy, there is a clear trend to select 12~h and 24~h when considering 2 predictors.
-However, it must be remembered that this holds for our predictand, the accumulated precipitation over 06-30~h~UTC, and that it is expected to differ if we change the window (e.g.
+The selection of the temporal windows for the atmospheric circulation was similar to the preceding optimization (in the order of increasing pressure: 12~h, 24/30~h, 12~h, 30~h), but sometimes with a bit more variability.
+When it comes to the moisture analogy, there was a clear trend to select 12~h and 24~h when considering 2 predictors.
+However, it must be remembered that this holds for our predictand, the accumulated precipitation over 06-30~h~UTC, and that it is expected to differ if we change the temporal window (e.g.
 00-24~h~UTC) or its duration.
@@
 The optimized spatial windows for the atmospheric circulation have also changed (Figure \ref{fig:spatial_windows_4Zo-2MIo}; results of 4Zo-4MIo are not shown but present the same trends).
-The very large domains on the upper level of the four first subregions are not present anymore, and more variability can be observed.
-The selected points for the analogy on the moisture index are always located nearby the catchment, including at least 1 of the nearest points from the reanalysis dataset, and the spatial windows are relatively small.
+The very large domains on the upper level of the four first subregions were not present anymore, and more variability could be observed.
+The selected points for the analogy on the moisture index were always located nearby the catchment, including at least 1 of the nearest points from the reanalysis dataset, and the spatial windows were relatively small.
 Thus, for this case study, there is no need to look for distant moisture information and the search could be reduced to a smaller domain.
@@
 The CRPSS scores were improved by considering the moisture information (Figure \ref{fig:figure_crpss_4Zo-2HIo} to be compared with Figure \ref{fig:figure_crpss_4Zo}).
-The optimized methods also perform significantly better than the reference method based on the moisture index optimized by the sequential procedure.
-However, there is no drastic difference between both 4Zo-2MIo and 4Zo-4MIo methods, which suggests that considering four moisture predictors is not necessary.
+The optimized methods also performed significantly better than the reference method based on the moisture index optimized by the sequential procedure.
+However, there was no drastic difference between both 4Zo-2MIo and 4Zo-4MIo methods, which suggests that considering four moisture predictors is not necessary.
 When it comes to improvements for days with precipitation above the 3 thresholds (P\(\geq\)1~mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the prediction compared to the reference method, mainly for heavy rainfall.
 
-The analysis of the parameters cross-compatibility (Figure \ref{fig:crossing_4Zo-2MIo}) is also very similar to the one on the circulation analogy only (results for 4Zo-4MIo not shown as very similar).
-The same pattern can be observed, with a drop of performance for the subregions submitted to different meteorological influences.
-However, the losses of performance are globally more important than before, suggesting that more complex methods with moisture variables are less transposable to another subregion (consistent with the observations of \citet{Chardon2014}), even though both are located within the same grid cell of the reanalysis dataset.
+The analysis of the parameters cross-compatibility (Figure \ref{fig:crossing_4Zo-2MIo}) was also very similar to the one on the circulation analogy only (results for 4Zo-4MIo not shown as very similar).
+The same pattern could be observed, with a drop of performance for the subregions submitted to different meteorological influences.
+However, the losses of performance were globally more important than before, suggesting that more complex methods with moisture variables are less transposable to another subregion (consistent with the observations of \citet{Chardon2014}), even though both were located within the same grid cell of the reanalysis dataset.
 Moisture fields have greater variability than pressure fields, and thus a change in the spatial windows can have a greater impact on the method performance.
-Indeed, the two regions with the lowest cross-compatibility are the Upper Rhone Valley (7) and the Southeast ridges (8), which have similar optimal pressure levels and temporal windows to other regions, but have rather different spatial windows on the moisture predictor.
+Indeed, the two regions with the lowest cross-compatibility with the others were the Upper Rhone Valley (7) and the Southeast ridges (8), which had similar optimal pressure levels and temporal windows to other regions, but had rather different spatial windows on the moisture predictor.
 
@@
 \begin{itemize}
-	\item Using four pressure levels for the analogy of circulation seems to be an optimal number for the studied region, length of archive available, and target predictand considered.
-Beyond four, the validation score is more variable, revealing a loss in robustness due to over-parametrization.
+	\item Using four pressure levels for the analogy of circulation seemed to be an optimal number for the studied region, length of archive available, and target predictand considered.
+Beyond four, the validation score was more variable, revealing a loss in robustness due to over-parametrization.
 	\item The automatic and joint optimization of all parameters: the analogues number, the selection of the pressure levels and the temporal windows, and the spatial windows.
@@
 It can be influenced by the variability of the geopotential with altitude, and the change of some levels significance with the targeted region.
-There is a trend for the weighting of circulation predictors to decrease with the increase in pressure, as one can see in Figure \ref{fig:levels_weights_average} for the three optimized methods.
-However, the values stay around equity.
+There was a trend for the weighting of circulation predictors to decrease with the increase in pressure, as one can see in Figure \ref{fig:levels_weights_average} for the three optimized methods.
+However, the values stayed around equity.
 This may not be the most influencing factor, and we may suggest to remove it first when trying to reduce the number of degrees of freedom.
@@
 
-The convergence of parallel optimizations decreases when the method to optimize becomes more and more complex.
+The convergence of parallel optimizations decreased when the method to optimize becomes more and more complex.
 The optimizer does not always converge to the exact global optimum, but to its surroundings.
 This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that one has to stop it before the end, due to the required processing time (see Figure \ref{fig:evolution} as example).
-The resulting parameters may sometimes present non negligible differences, even though the score is almost similar.
+The resulting parameters might sometimes present non negligible differences, even though the score was almost similar.
 Through some Monte-Carlo analyses of the parameter space properties of the AM, \citet{Horton2012a} showed that some parameters of the method have a wide range of acceptable values.
@@
 
-Furthermore, AMs optimized with GAs show an improvement of the prediction for days with heavier precipitation, including extremes.
+Furthermore, AMs optimized with GAs showed an improvement of the prediction for days with heavier precipitation, including extremes.
 Even though no new extreme value is added to the existing precipitation archive, the distribution of analogue precipitation values for a target situation can move towards the targeted extreme by sampling better candidate situations.
@@
 
-The parameters resulting from the optimization by GAs are very consistent in terms of selection of the pressure levels, and the temporal and spatial windows.
-There are clear trends or even identical results for subregions under similar meteorological influences, which confirm that the optimized parameters are coherent, despite an eventual first impression of a great variability in the spatial windows.
-When adding moisture variables, the results show a higher variability, but remains highly acceptable and coherent.
+The parameters resulting from the optimization by GAs were very consistent in terms of selection of the pressure levels, and the temporal and spatial windows.
+There were clear trends or even identical results for subregions under similar meteorological influences, which confirm that the optimized parameters were coherent, despite an eventual first impression of a great variability in the spatial windows.
+When adding moisture variables, the results showed a higher variability, but remained highly acceptable and coherent.
 
@@
 A dependence in the selected parameters between the analogy of circulation and the moisture variables was identified.
-When the two levels are considered together, the optimal parameters of the circulation analogy are different.
+When the two levels are considered together, the optimal parameters of the circulation analogy were different.
 This complexity can only be exploited in a suitable manner by global optimization methods.
 
-For the present case study, there seems to be an optimum number of pressure levels to consider for the analogy of circulation, which is four, before losing performance in validation.
-The analogy of circulation has also been improved by introducing a weighting between pressure levels, and considering independent spatial windows between levels.
+For the present case study, there seemed to be an optimum number of pressure levels to consider for the analogy of circulation, which is four, before losing consistency of the real gains.
+The analogy of circulation was improved by introducing a weighting between pressure levels, and considering independent spatial windows between pressure levels.
 
-GAs provide parameterizations of AMs that exceed the performance of the sequential calibration.
+GAs provided parameterizations of AMs that exceeded the performance of the sequential calibration.
 In addition, it has been observed that the prediction for days with strong precipitation were improved to a greater extent, which is clearly interesting in the framework of flood forecasting.
@@
 This work is by far not exhaustive and means to open a door for new explorations of AMs with GAs.
-It is even possible to let the optimizer chose the meteorological variable to be used as predictor, as well as the analogy criteria.
-It is already possible to undertake such approach with our code.
+It is even possible to let the optimizer chose the meteorological variable to be used as predictor, as well as the analogy criteria, which is the topic of work in progress.
 Moreover, the AM has been explored for decades for precipitation forecasting, but not as intensively for other predictands.

### 2017-01-11 Optimization case study - JoH/elsarticle-template.tex
Reading again the JoH paper.

@@
 %TODO: Elsevier english editing
-%TODO: more hydrology
 %TODO: relative improvement of the crpss...
+%TODO: homogenize hours: 6 a.m. or 06 h ??
 
@@
 This relationship is usually established by a semi-automatic sequential procedure that has strong limitations: (i) it cannot automatically choose the pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters, and (iii) it cannot easily handle new degrees of freedom.
-In this work, a global optimization approach relying on genetic algorithms could optimize all parameters jointly and automatically, which is a breakthrough in the way the analogue method was calibrated until now.
-It allowed taking into account parameters inter-dependencies, and selecting objectively some parameters that were manually selected beforehand (such as the pressure levels and the temporal windows of the predictor variables).
+In this work, a global optimization approach relying on genetic algorithms could optimize all parameters jointly and automatically.
+It allowed taking into account parameters inter-dependencies, and selecting objectively some parameters that were manually selected beforehand, which e.g.
+obviates the need of assessing a high number of combinations of the pressure levels and the temporal windows of the predictor variables.
 
@@
 
-The analogue method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1956, Lorenz1969} that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Duband1970}.
+The analogue method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1956, Lorenz1969} that similar situations in terms of the atmospheric circulation are likely to lead to similar local weather \citep{Duband1970}.
 It uses predictor variables describing the synoptic atmospheric circulation in order to predict local-scale predictands of interest.
@@
 
-In operational forecasting, it is used mainly by practitioners, notably hydropower companies or flood forecasting services.
+In real-time forecasting, it is used mainly by practitioners, notably hydropower companies or flood forecasting services.
 They need to anticipate water yields or to issue early flood warnings several days in advance.
@@
 Although these outputs are essential, they can be supplemented by other sources of forecasts providing useful information.
-In contrast to local NWP models, AMs can transform at low cost the synoptic-scale information provided by the global NWP into precipitation forecasts, by using the natural local behavior in response to synoptic-scale influence stored in the archive of observed precipitation.
-Running an AM approach is so quick that it can search for analogues for every day up to 10 days ahead, eventually for the different traces of an ensemble forecast and/or issued by different NWP models (e.g.
+In contrast to local NWP models, AMs can transform at low cost the synoptic-scale information provided by the global NWP model into precipitation forecasts, by using the natural local behavior in response to synoptic-scale influence stored in the archive of observed precipitation.
+Running an AM approach is so quick that it can search for analogues for every day up to ten days ahead, eventually for the different traces of an ensemble forecast and/or issued by different NWP models (e.g.
 NOAA-GFS or ECMWF-IFS), in a matter of minutes.
 
-In climate studies it is used to downscale the outputs of general circulation model (GCM) or regional climate models (RCMs) simulation runs \citep{Dayon2015} or to reconstruct past weather conditions \citep{Caillouet2016}.
+In climate studies AMs are used to downscale the outputs of general circulation model (GCM) or regional climate models (RCMs) simulation runs \citep{Dayon2015} or to reconstruct past weather conditions \citep{Caillouet2016}.
 In future climate studies, RCMs are often used to dynamically downscale precipitation to a local scale.
 However, even though the relevance of RCMs'outputs increases, a bias correction of the outputs is still often required, particularly in complex terrain.
-Moreover, their application is computer intensive, which makes it difficult to cover all combinations of climate scenarios and GCMs.
-Therefore, the idea is to rely on past observations to bypass the small scale simulations and to go from the large scale situation to the end variables like precipitation by searching analogues in the archives.
+Moreover, their application is computer-intensive, which makes it difficult to cover all combinations of climate scenarios and GCMs.
+Therefore, the idea is to bypass the small scale simulations and to go from the large scale situation to the end variables like precipitation by statistical downscaling \citep{Maraun2010}.
 
@@
 Indeed, a high spatial variability of the precipitation climatology exists, which is due to the complex orography of the region, and the mix of various meteorological influences.
-Based on different climatological analyses, the precipitation gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}) :
+Based on different climatological analyses, the precipitation gauging stations in the catchment were clustered in ten subregions (Fig.\ \ref{fig:map}) :
 
@@
 Predictors are generally extracted from reanalysis datasets.
-NCEP-NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} was used here, but it could have been any other reanalysis dataset.
+The NCEP-NCAR reanalysis I \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} was used here, but it could have been any other reanalysis dataset.
 
@@
 the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008.
-The time series from every available gauging station were averaged over the ten subregions of approximately 500~km$^{2}$ each in order to smooth local effects \citep{Obled2002, Marty2012}.
+The time series from every available gauging station were averaged over the ten subregions (Fig.\ \ref{fig:map}) of approximately 500~km$^{2}$ each in order to smooth local effects \citep{Obled2002, Marty2012}.
 It helps accounting for local variability, mainly when convective processes are involved, which increases slightly the prediction skill.
 
-It must be stressed that the predictand here is a temporally cumulated variable, compared to the meteorological predictors, which may be considered instantaneous.
-Depending on the duration of the accumulation period (here 24h, but could have been 6, 12, 24h, or more), the choice of predictors will vary.
+It must be stressed that the predictand is here sa temporally cumulated variable, compared to the meteorological predictors, which may be considered instantaneous.
+Depending on the duration of the accumulation period (here 24~h, but could have been 6, 12~h, or more than 24~h), the choice of predictors will vary.
 
-The 48 years precipitation dataset (see section \ref{sec:data}) was divided into a calibration period (CP) and a validation period (VP).
+The 48 years precipitation dataset was divided into a calibration period (CP) and a validation period (VP).
 Using data independent from the CP to validate the results is very important in order to assess the robustness of the proposed improvements and to avoid over-parametrization of the method.
@@
 In order to reduce potential bias related to trends linked to climate change or to the evolution in measurement techniques, the selection of the VP was evenly distributed over the entire series \citep{BenDaoud2010}.
-Thus, one year every six years were selected for validation, which represents a total of 8 years for the VP and 40 for CP.
+Thus, one year every six years was selected for validation, which represents a total of 8 years for the VP and 40 for CP.
 The choice of the sequence was made in order to have similar statistical characteristics between the CP and the VP.
@@
 
-Multiple variations of the methods exist, and most of them will not be detailed hereafter \cite[see][for more comprehensive listings]{BenDaoud2016}.
-However, there are mainly two parameterizations that are most often used for precipitation downscaling and that were considered as reference: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
+Multiple variations of the analogue method exist, and most of them will not be detailed hereafter \cite[see][for more comprehensive listings]{BenDaoud2016}.
+However, there are mainly two parameterizations that are most often used for precipitation prediction and that were considered as reference: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
 
@@
 \citet{Bontron2005} show that the geopotential height at 500~hPa (Z500) and 1000~hPa (Z1000) are the best first predictors of the NCEP/NCAR reanalysis I dataset, and that the S1 criterion performs better than scores based on absolute distances.
-The reason for such better results is that the S1 criterion allows comparing the circulation pattern, by means of the gradients, rather than the absolute value of the geopotential height, which represent better the flow direction.
-To cope with seasonal effects, candidate dates are extracted within a period of 4 months centered around the target date, for every year of the archive.
+The reason for such better results is that the S1 criterion allows comparing the circulation patterns, by means of the gradients, rather than the absolute value of the geopotential height, which represent better the flow direction.
+To cope with seasonal effects, candidate dates are extracted within a period of four months centered around the target date, for every year of the archive.
 This method using two geopotential heights will be named 2Z.
@@
 The other most known parametrization adds a second level of analogy on moisture variables (method 2Z-2MI, Table \ref{table:params_R2}).
-The predictor that \citet{Bontron2004} found optimal for the France territory is a moisture index made of the product of the precipitable water with the relative humidity at 850~hPa (RH850).
+The predictor that \citet{Bontron2004} found optimal for the France territory is a moisture index made of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850).
 \cite{Horton2012a} confirms that this index is also better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis I considered independently.
@@
 Moisture fields are not as well predicted by NWP models as pressure variables.
-It means that the 2Z-2MI method, when used in real-time forecasting, is very dependent on the skill of the NWP model in predicting moisture fields, and thus its use is often restricted to the first lead times.
+It implies that the 2Z-2MI method, when used in real-time forecasting, is very dependent on the skill of the NWP model in predicting moisture fields, and thus its use is often restricted to the first lead times.
 
@@
 In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution of precipitation from the entire archive as the reference.
-The CRPSS (\textit{Continuous Ranked Probability Skill Score}) is thus defined as following:
+The CRPSS (Continuous Ranked Probability Skill Score) is thus defined as following:
 
@@
 
-Note however that the choice of the reference does not matter so much, since we shall consider more its relative increase or decrease rather than the CRPSS absolute value in order to assess a possible improvement.
+Note however that the choice of the reference does not matter so much when assessing potential improvements of the method, since we shall consider more its relative increase or decrease rather than the CRPSS absolute value.
 
@@
 AMs are usually calibrated by a semi-automatic sequential procedure elaborated by \citet{Bontron2004} \cite[see also ][]{Radanovics2013, BenDaoud2016}.
-The calibration technique optimizes the spatial windows on which the predictors are compared and the number of analogues, for every level of analogy, by maximizing the performance score.
+The calibration technique optimizes the spatial windows on which the predictors are compared and the number of analogues, for every level of analogy, by maximizing the performance score (CRPSS).
 However, the different analogy levels are calibrated sequentially, and the meteorological variables, the pressure levels and the temporal windows are chosen manually.
@@
 
-This procedure was used to calibrate the methods that were considered as references to further assess the ability of genetic algorithms to outperform the classic approach.
+This procedure was used to calibrate the methods that were here considered as references to further assess the ability of genetic algorithms to outperform the classic approach.
 
@@
 When the optimizer gets closer to the global optimum, any new improvement takes more time to appear (see for example the slow-down of the improvements over generations in Figure \ref{fig:evolution}), and the final adjustment of the parameters can be very time consuming \citep{Back1993a}.
-For problems that require a significant amount of time in order to evaluate the objective function, as in the case of AMs, the number of generations has to be limited in order to get reasonable processing time.
+For problems that require a significant amount of time in order to evaluate the objective function, as in the case of AMs (because it needs to make a prediction for every day of the CP), the number of generations has to be limited in order to get reasonable processing time.
 Thus, different acceptable solutions can result from one or more optimization runs \citep{Holland1992b}.
@@
 
-The analogy of the atmospheric circulation was optimized for the 10 subregions  independently.
+The analogy of the atmospheric circulation was optimized for the ten subregions (Section \ref{sec:case_study})  independently.
 We started from the most simple AM, and increased the complexity in order to identify the degrees of freedom that are of particular interest.
@@
 they can differ from one pressure level to another), as well as the temporal windows (hours of observation of the geopotential), which cannot be achieved with the sequential calibration technique.
-With these degrees of freedom, a relative CRPSS improvement of 3.97\% and 2.45\% in average was obtained for the CP and the VP respectively, with regard to the reference (sequential) method based on Z500 and Z1000.
+The performance score (CRPSS) was slightly improved, with these limited degrees of freedom, in regards to the 2Z reference method calibrated with the sequential procedure.
 Some tests showed that most of the gains were due to the non-overlapping spatial windows.
-This may not be seen as a large improvement, but it demonstrated that the optimizer was able to get relevant parameters.
+It demonstrated that the optimizer was able to get relevant parameters for a simple method.
 
 Then, an additional degree of freedom was provided to the GAs by letting them choose the pressure levels along with the other parameters (analogue numbers, spatial and temporal windows), which is also a non-automated process in the sequential calibration.
-This degree of freedom increased the optimization time and may decrease the number of simulations that converge to a single solution.
-However, most solutions were very close in terms of score.
-The averaged relative improvement of the CRPSS is now 5.63\% for the CP and 3.82\% for the VP.
-The pressure levels that were chosen are Z500 or Z700 for the upper level, and Z925 or Z1000 (most often) for the lower level.
+This degree of freedom increased the optimization time and might decrease the number of simulations that converge to a single solution.
+However, most solutions were very close in terms of the performance score, which was improved further.
+The selected pressure levels were Z500 or Z700 for the upper level, and Z925 or Z1000 (most often) for the lower level.
 
 Parallel analyses showed that the analogy of circulation is incomplete, and that geopotential heights still contain relevant information that can improve the statistical relationship.
-Therefore, a third followed by a fourth predictor were added (still on the geopotential height) that the optimizer could use along with the previous parameters.
+Therefore, a third, followed by a fourth predictor were added (still only geopotential heights).
 There was no constraint on the predictors, so that the same pressure level could be selected more than once.
-Some improvements were found on the score, both for the CP and the VP, confirming that this additional information is beneficial for the quality of the prediction.
+Further improvements were found on the performance score, both for the CP and the VP, confirming that this additional information was beneficial for the quality of the prediction.
 
@@
 
-The number of predictor was then successively increased up to ten, considering the weighting of the analogy criteria values.
+The number of predictors (still only geopotential heights) was then successively increased up to ten, considering the weighting of the analogy criteria values.
 The addition of predictors globally improved the prediction skill (for both the CP and the VP) only up to four predictors (Figure \ref{fig:figure_nb_levels}).
@@
 After four predictors, the score on the CP did not increase substantially, and could even present some local decrease due to increasing difficulty for the optimizer to converge.
-Selecting four predictors was considered optimal for this case study, since the gain in CRPSS was significant, and the model remained relatively simple.
+Selecting four predictors (geopotential heights) was considered optimal for this case study, since the gain in CRPSS was significant, and the model remained relatively simple.
 It cannot be excluded that another number would prevail in another region than the upper Rh\^{o}ne catchment, under other meteorological conditions, or with another reanalysis dataset.
@@
 
-The chosen method for the atmospheric circulation analogy, based on four levels of the geopotential, and that will be named 4Zo, was made of the following degrees of freedom:
+The chosen method for the atmospheric circulation analogy, based on four predictors of geopotential heights, and that will be named 4Zo (o for optimized), was made of the following degrees of freedom:
 
@@
 	\setlength\itemsep{-4px}
-	\item the selection of the pressure levels (4 degrees)
-	\item the temporal windows (4 degrees)
-	\item the spatial windows (4x4 degrees)
-	\item the weights (4 degrees)
+	\item the selection of the pressure levels (4 degrees),
+	\item the temporal windows (4 degrees),
+	\item the spatial windows (4x4 degrees),
+	\item the weights (4 degrees),
 	\item the number of analogues (1 degree).
@@
 
-The resulting CRPSS scores are provided in Figure \ref{fig:figure_crpss_4Zo} and were in average 35.8~\% for the CP and 35.5~\% for the VP, comparatively to 31.1~\% and 32.3~\% respectively for the reference method on the atmospheric circulation (optimized by the sequential procedure).
+The resulting CRPSS scores are provided in Figure \ref{fig:figure_crpss_4Zo} and were in average 35.8~\% for the CP and 35.5~\% for the VP, comparatively to 31.1~\% and 32.3~\% respectively for the reference method 2Z on the atmospheric circulation (optimized by the sequential procedure).
 The score was also calculated for three precipitation thresholds: P\(\geq\)1~mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_4Zo}).
@@
 The first four subregions were characterized by a large spatial window on the upper level, whereas it was smaller elsewhere.
-For most subregions, the second level (Z700) was represented by thin and longitudinally extended domains.
-The third level (Z1000 at 6 or 12~h) also contained longitudinally extended domains, but a bit larger.
-The last one (Z1000 at 30~h) was rather large and squared.
+For most subregions, the second level (Z700) was compared on thin and longitudinally extended spatial windows.
+The third level (Z1000 at 6 or 12~h) also had longitudinally extended domains, but a bit larger.
+The last one (Z1000 at 30~h) had rather large and squared windows.
 Subregions number 5 (Southern valleys) and 6 (Southern ridges) had exactly the same spatial windows, which suggest that they behave in a similar way and thus could have been merged.
@@
 
-The scores showed non-negligible improvements for both the CP and the VP (Figure \ref{fig:figure_crpss_4Zo}) compared to the reference method optimized by the sequential procedure.
+The performance scores showed non-negligible improvements for both the CP and the VP (Figure \ref{fig:figure_crpss_4Zo}) compared to the 2Z reference method optimized by the sequential procedure.
 Even more interestingly, the results for higher precipitation thresholds (Table \ref{table:scores_thresholds_4Zo}) showed the largest improvements.
 This is of particular interest in the framework of flood forecasting.
-The further improvement of days with higher precipitation totals is likely related to the fact that larger values contribute more to the CRPS score, which means that better predicting these days results in significant increase of the performance score.
+The further improvement of days with higher precipitation totals is likely related to the fact that larger values contribute more to the CRPS score, which means that better predicting these days results in significant increase of the global performance score.
 
-The analysis of the parameters cross-compatibility showed that obviously, the parameters were optimal on the CP when they were optimized for a given subregion (Figure \ref{fig:crossing_4Zo} top).
+The analysis of the parameters cross-compatibility showed that obviously the parameters were optimal on the CP for the subregion for which they were optimized (Figure \ref{fig:crossing_4Zo} top).
 However, the losses in CRPSS when exchanging the parameters were not of the same magnitude between the different subregions.
 Indeed, the Upper Rhone Valley (7) and moreover the Southeast ridges (8) seemed to behave significantly differently.
-These two regions have different climate properties than the others as they are particularly sensitive to southerly flows.
-Indeed, almost all heavy precipitation events occurred under a southerly regime, such as the Liguria, Piedmont and Aosta regions in Italy, whereas the other subregions of the catchment had heavy precipitation events mainly under a westerly regime \citep{Horton2012}.
-Thus, as the performance score is significantly influenced by heavy precipitation values, the parameters for the different subregions are optimized to better predict these days.
+These two regions have different climatic properties than the others as they are particularly sensitive to southerly flows.
+Indeed, almost all heavy precipitation events occurred under a southerly regime, such as in the Liguria, Piedmont and Aosta regions in Italy, whereas the other subregions of the catchment had extreme events mainly under a westerly regime \citep{Horton2012}.
+Thus, as the performance score is significantly influenced by heavy precipitation values, the parameters for the different subregions are likely optimized to better predict these days.
 It can then be expected that the optimal parameters differ between these two subregions and the other ones.
-This points at the importance of taking into account leading meteorological influences during discretization, that are not always best represented by the geographical distance.
+This points at the importance of taking into account leading meteorological influences during precipitation stations clustering, that are not always best represented by the geographical distance.
 
 Globally, the same pattern could be observed for the VP (Figure \ref{fig:crossing_4Zo} bottom), but in this case, minor improvements could occur when crossing the parameters, due to the presence of other events in the VP that might have been better predicted by a different parameter set.
-The relatively small gaps in score between parameterizations indicated that even though the parameters might differ significantly, the performance might not be drastically affected.
+The relatively small differences in score between parameterizations indicated that even though the parameters might differ significantly, the performance might not be drastically affected.
 Even a change in the pressure level did not mean a radical drop of the score value.
@@
 
-Two methods were assessed: one with 2 moisture predictors (moisture index on 2 pressure levels or at 2 different hours) named 4Zo-2MIo, and one with four moisture predictors named 4Zo-4MIo.
+Two methods were assessed: one with two moisture predictors (moisture index on two pressure levels or at two different hours) named 4Zo-2MIo, and one with four moisture predictors named 4Zo-4MIo.
 When introducing two predictors for the moisture analogy, the number of degrees of freedom raised to 42, and to 54 with four predictors.
@@
 
-When optimizing a method made of 2 levels of analogy, the introduction of moisture variables in the second level had an influence on the parameter values of the first level.
+When optimizing a method made of two levels of analogy, the introduction of moisture variables in the second level had an influence on the parameter values of the first level.
 It means that the two levels of analogy bring complementary information, and are thus not independent.
@@
 The selection of the temporal windows for the atmospheric circulation was similar to the preceding optimization (in the order of increasing pressure: 12~h, 24/30~h, 12~h, 30~h), but sometimes with a bit more variability.
-When it comes to the moisture analogy, there was a clear trend to select 12~h and 24~h when considering 2 predictors.
+When it comes to the moisture analogy, there was a clear trend to select 12~h and 24~h when considering two predictors.
 However, it must be remembered that this holds for our predictand, the accumulated precipitation over 06-30~h~UTC, and that it is expected to differ if we change the temporal window (e.g.
@@
 The very large domains on the upper level of the four first subregions were not present anymore, and more variability could be observed.
-The selected points for the analogy on the moisture index were always located nearby the catchment, including at least 1 of the nearest points from the reanalysis dataset, and the spatial windows were relatively small.
+The selected points for the analogy on the moisture index were always located nearby the catchment, including at least one of the nearest points from the reanalysis dataset, and the spatial windows were relatively small.
 Thus, for this case study, there is no need to look for distant moisture information and the search could be reduced to a smaller domain.
@@
 However, there was no drastic difference between both 4Zo-2MIo and 4Zo-4MIo methods, which suggests that considering four moisture predictors is not necessary.
-When it comes to improvements for days with precipitation above the 3 thresholds (P\(\geq\)1~mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the prediction compared to the reference method, mainly for heavy rainfall.
+When it comes to improvements for days with precipitation above the three thresholds (P\(\geq\)1~mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the prediction compared to the reference method, mainly for heavy rainfall.
 
@@
 Indeed, there is a strong interdependence between space and time in the atmospheric circulation, so that e.g.
-the spatial window should move upstream the main atmospheric flow for earlier temporal windows.	Traditional calibration procedures based on a systematic assessment of every combination is not possible anymore when considering more than 2 pressure levels.
+the spatial window should move upstream the main atmospheric flow for earlier temporal windows.	Traditional calibration procedures based on a systematic assessment of every combination is not possible anymore when considering more than two pressure levels.
 	\item The introduction of distinct spatial windows between pressure levels.
@@
 As it has been observed, methods with a higher complexity that integrate moisture predictors are less transposable than simpler ones.
-It was also noticed in another unpublished work, that it is by far better to optimize for 2 subregions jointly rather than to optimize on one and to apply its parametrization to the other.
+It was also noticed in another unpublished work, that it is by far better to optimize for two subregions jointly rather than to optimize on one and to apply its parametrization to the other.
 Finally, the discretization in subregions is an important process and should be handled with care.
@@
 	\centerline{\includegraphics[width=8.4cm]{figures/fig03.pdf}}
-	\caption{Optimized spatial windows for the 4Zo method (analogy of atmospheric circulation on 4 pressure levels).
+	\caption{Optimized spatial windows for the 4Zo method (analogy of atmospheric circulation on four pressure levels).
 The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
@@
 	\centerline{\includegraphics[width=8.4cm]{figures/fig06.pdf}}
-	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on 4 pressure levels and the analogy on the moisture index on 2 pressure levels).
+	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on four pressure levels and the analogy on the moisture index on two pressure levels).
 The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
@@
 	\caption{Distribution of the optimal weights for the predictors of the first level of analogy (geopotential heights) of the 4Zo, 4Zo-2MIo, and 4Zo-4MIo methods.
-The results are those of the 10 subregions.
+The results are those of the ten subregions.
 The geopotential heights are sorted by increasing pressure and hour.}

### 2017-01-18 Moving temporal window - HESS/template.tex
Minor edits.

@@
 %% Please use the following documentclass and Journal Abbreviations for Discussion Papers and Final Revised Papers.
+
+%TODO: change CRPSS from % to 0.x ?
 
@@
 The procedure starts again from step 2 (calibration of the spatial window and the number of analogues) for the new level.
-The parameters calibrated on the previous analogue levels are fixed and do not change.
+The parameters calibrated on the previous analogy levels are fixed and do not change.
 		\item Finally, the numbers of analogues $N_{1}$ and $N_{2}$ for the different levels of analogy are reassessed.

### 2017-01-18 Optimization case study - JoH/elsarticle-template.tex
Changes to check.

@@
 Parallel analyses showed that the analogy of circulation is incomplete, and that geopotential heights still contain relevant information that can improve the statistical relationship.
-Therefore, a third, followed by a fourth predictor were added (still only geopotential heights).
+Therefore, a third, followed by a fourth circulation predictor were added (still only geopotential heights).
 There was no constraint on the predictors, so that the same pressure level could be selected more than once.
@@
 
-The number of predictors (still only geopotential heights) was then successively increased up to ten, considering the weighting of the analogy criteria values.
-The addition of predictors globally improved the prediction skill (for both the CP and the VP) only up to four predictors (Figure \ref{fig:figure_nb_levels}).
+The number of circulation predictors (still only geopotential heights) was then successively increased up to ten, considering the weighting of the analogy criteria values.
+The addition of circulation predictors globally improved the prediction skill (for both the CP and the VP) only up to four predictors (Figure \ref{fig:figure_nb_levels}).
 Afterwards, the score on the VP was more variable, showing eventually even a decrease, which revealed an over-parametrization of the method, and thus a lack of robustness.
 After four predictors, the score on the CP did not increase substantially, and could even present some local decrease due to increasing difficulty for the optimizer to converge.
-Selecting four predictors (geopotential heights) was considered optimal for this case study, since the gain in CRPSS was significant, and the model remained relatively simple.
+Selecting four circulation predictors (geopotential heights) was considered optimal for this case study, since the gain in CRPSS was significant, and the model remained relatively simple.
 It cannot be excluded that another number would prevail in another region than the upper Rh\^{o}ne catchment, under other meteorological conditions, or with another reanalysis dataset.
@@
 
-The chosen method for the atmospheric circulation analogy, based on four predictors of geopotential heights, and that will be named 4Zo (o for optimized), was made of the following degrees of freedom:
+The chosen method for the atmospheric circulation analogy, based on four circulation predictors (geopotential heights), and that will be named 4Zo (o for optimized), was made of the following degrees of freedom:
 
@@
 
-Globally, the same pattern could be observed for the VP (Figure \ref{fig:crossing_4Zo} bottom), but in this case, minor improvements could occur when crossing the parameters, due to the presence of other events in the VP that might have been better predicted by a different parameter set.
+Globally, the same cross-compatibility structure could be observed for the VP (Figure \ref{fig:crossing_4Zo} bottom), but in this case, minor improvements were occasionally observed when crossing the parameters, due to the presence of other events in the VP that might be better predicted by a different parameter set.
 The relatively small differences in score between parameterizations indicated that even though the parameters might differ significantly, the performance might not be drastically affected.
@@
 When introducing two predictors for the moisture analogy, the number of degrees of freedom raised to 42, and to 54 with four predictors.
+However, there was no substantial difference in the performance scores between both 4Zo-2MIo and 4Zo-4MIo methods, which suggests that considering four moisture predictors is not necessary.
+For this reason, only the results of 4Zo-2MIo are presented.
 
@@
 
-\subsection{Results for 4Zo-2MIo and 4Zo-4MIo methods}
-
-Due to significant similarities between the results from 4Zo-2MIo and 4Zo-4MIo, the latter will only be partly shown.
+\subsection{Results for the 4Zo-2MIo method}
 
@@
 
-The CRPSS scores of the optimized 4Zo-2MIo method are provided in Figure \ref{fig:figure_crpss_4Zo-2HIo} and amounted in average to 40~\% (CP) and 40.3~\% (VP), compared to 35.2~\% (CP) and 36.2~\% (VP) for the reference method on the moisture analogy optimized with the sequential procedure.
-The score for the 4Zo-4MIo method were relatively close, with 40.6~\% for both the CP and the VP (not shown as very similar repartition as Figure \ref{fig:figure_crpss_4Zo-2HIo}).
-
-As for 4Zo, the 4Zo-2MIo and 4Zo-4MIo methods presented larger improvements in the prediction for significant rainfall (thresholds P\(\geq\)1~mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10).
-The improvement were relatively similar for 4Zo-2MIo (Table \ref{table:scores_thresholds_4Zo-2MIo}) and 4Zo-4MIo (not shown), with slightly superior scores for the latter on small precipitation (P\(\geq\)1~mm : 17.7~\% and 13.0~\%) and extremes (P\(\geq\)0.5\(\cdot\)P10 : 23.7~\% and 29.2~\%).
-
-The parameters cross-compatibility has also been assessed for the methods with moisture variables, and are shown in Figure \ref{fig:crossing_4Zo-2MIo} for the method 4Zo-2MIo (not shown for 4Zo-4MIo, but similar).
+The CRPSS scores of the optimized 4Zo-2MIo method are provided in Figure \ref{fig:figure_crpss_4Zo-2HIo} and amounted in average to 40~\% (CP) and 40.3~\% (VP), compared to 35.2~\% (CP) and 36.2~\% (VP) for the reference method 2Z-2MI on the moisture analogy optimized with the sequential procedure.
+The parameters cross-compatibility are shown in Figure \ref{fig:crossing_4Zo-2MIo}.
+As for 4Zo, the 4Zo-2MIo method presented larger improvements in the prediction of significant rainfall (Table \ref{table:scores_thresholds_4Zo-2MIo}).
 
@@
 This is first visible on the number $N_{1}$ of analogues to be selected on the first level, and on the selection of the pressure levels for the circulation analogy.
+If the change in the optimal value of $N_{1}$ was already known, a change of the optimal pressure levels for the circulation analogy has never been identified before.
 
@@
 One can also notice that the optimal number of analogues $N_{2}$ for the second level of analogy of 4Zo-2MIo was slightly inferior to $N_{1}$ from 4Zo, but very close.
-There was globally a tendency between the optimal analogue number values of both methods: $N_{1}$ of the 4Zo method, and $N_{1}$ and $N_{2}$ of 4Zo-2MIo tended to be higher or lower altogether for a given region.
+There is globally a common tendency between the optimal analogue number values of both methods: $N_{1}$ of the 4Zo method, and $N_{1}$ and $N_{2}$ of 4Zo-2MIo tend to be higher or lower altogether for a given region.
 
 The optimal final numbers of analogues did not vary much: $23 \leq N_{1} \leq 33$ for 4Zo and $21 \leq N_{2} \leq 28$ for 4Zo-2MIo.
-However, the optimal number of $N_{1}$ analogues of the first level of 4Zo-2MIo varied to a greater extent: $48 \leq N_{1} \leq 84$.
+However, the optimal number of the $N_{1}$ analogues of the first level of 4Zo-2MIo varied to a greater extent: $48 \leq N_{1} \leq 84$.
 In this latter method, it may be problematic to consider a fixed and unique value for all regions.
 
-As for the pressure levels, Z1000 that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) was here less often chosen (once or even not at all) for both 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}) and 4Zo-4MIo (not shown).
+As for the pressure levels, Z1000 that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) was here less often chosen (once or even not at all) for 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}).
 There was indeed a vertical shift of the previously selected Z1000 for higher levels, that was even slightly stronger with four moisture predictors than with two.
 This change is likely due to the fact that when considering only the circulation analogy, the method tried to take into account information that can serve as proxy for moisture assessment, whereas it did not need it with the moisture index.
-This aspect has never been demonstrated before, as sequential calibration tools do not allow it.
-It can only be assessed by a global optimization technique that can work jointly on both levels of analogy.
+This can only be assessed by a global optimization technique that can work jointly on both levels of analogy.
 
 The selected pressure levels for the analogy on the moisture index were strongly centered around 700~hPa and 600~hPa.
-No other value was selected when considering two pressure levels (Table \ref{table:levels_GA_4Zo_2MIo}), and when considering four levels, 850~hPa and 500~hPa were sometimes also selected (not shown).
-However, even in this latter method, the 700~hPa and 600~hPa levels still held 78 \% of the selection.
-It was thus more efficient, in terms of prediction performance, to consider one of this level several times at different hours rather than selecting another pressure level.
+No other value was selected when considering two moisture predictors (Table \ref{table:levels_GA_4Zo_2MIo}).
+It was sometimes more efficient, in terms of prediction performance, to consider the moisture at 700~hPa twice, but at different hours, rather than selecting another pressure level.
 Besides, the optimizer never chose the same pressure level at the same hour for any variable, even though it was allowed to do so.
-The selected pressure levels for the analogy on the moisture index differed from the parameters resulting from the reference method optimized by the sequential procedure (Tables \ref{table:params_R2} and \ref{table:levels_GA_4Zo_2MIo}, last row).
-It is possible that the level 850~hPa is more optimal for the region for which the reference parameterization was established.
-However, this selection is usually not reconsidered when applying the sequential procedure.
+The selected pressure levels for the moisture analogy differed from the reference method (Tables \ref{table:params_R2} and \ref{table:levels_GA_4Zo_2MIo}, last row).
 
-The selection of the temporal windows for the atmospheric circulation was similar to the preceding optimization (in the order of increasing pressure: 12~h, 24/30~h, 12~h, 30~h), but sometimes with a bit more variability.
-When it comes to the moisture analogy, there was a clear trend to select 12~h and 24~h when considering two predictors.
-However, it must be remembered that this holds for our predictand, the accumulated precipitation over 06-30~h~UTC, and that it is expected to differ if we change the temporal window (e.g.
-00-24~h~UTC) or its duration.
+The selection of the temporal windows for the atmospheric circulation was similar to the preceding optimization (in the order of increasing pressure: 12~h, 24/30~h, 12~h, 30~h), but sometimes with some variability.
+When it comes to the moisture analogy, there was a clear tendency to select 12~h and 24~h.
+However, it must be remembered that this holds for our predictand, the accumulated precipitation over 06-30~h~UTC, and that it is expected to differ if the temporal window changes (e.g.
+00-24~h~UTC, or another accumulation duration).
 
-The optimized spatial windows for the atmospheric circulation have also changed (Figure \ref{fig:spatial_windows_4Zo-2MIo}; results of 4Zo-4MIo are not shown but present the same trends).
+The optimized spatial windows for the atmospheric circulation have also changed (Figure \ref{fig:spatial_windows_4Zo-2MIo}).
 The very large domains on the upper level of the four first subregions were not present anymore, and more variability could be observed.
-The selected points for the analogy on the moisture index were always located nearby the catchment, including at least one of the nearest points from the reanalysis dataset, and the spatial windows were relatively small.
+The selected points for the moisture analogy were always located nearby the catchment, including at least one of the nearest points from the reanalysis dataset, and the spatial windows were relatively small.
 Thus, for this case study, there is no need to look for distant moisture information and the search could be reduced to a smaller domain.
@@
 The CRPSS scores were improved by considering the moisture information (Figure \ref{fig:figure_crpss_4Zo-2HIo} to be compared with Figure \ref{fig:figure_crpss_4Zo}).
-The optimized methods also performed significantly better than the reference method based on the moisture index optimized by the sequential procedure.
-However, there was no drastic difference between both 4Zo-2MIo and 4Zo-4MIo methods, which suggests that considering four moisture predictors is not necessary.
+The optimized method also performed significantly better than the 2Z-2MI reference method optimized by the sequential procedure.
 When it comes to improvements for days with precipitation above the three thresholds (P\(\geq\)1~mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the prediction compared to the reference method, mainly for heavy rainfall.
 
-The analysis of the parameters cross-compatibility (Figure \ref{fig:crossing_4Zo-2MIo}) was also very similar to the one on the circulation analogy only (results for 4Zo-4MIo not shown as very similar).
+The analysis of the parameters cross-compatibility (Figure \ref{fig:crossing_4Zo-2MIo}) was also very similar to the one on the circulation analogy only.
 The same pattern could be observed, with a drop of performance for the subregions submitted to different meteorological influences.
@@
 In climate downscaling studies, it mainly depends on the coherence of the climatologies between the archive and the GCM model outputs.
-One should however not establish an AM with moisture variables for a too large region, as the transferability is reduced \citep[see also][]{Chardon2014}.
+One should however not establish an AM with moisture variables for a too large region, as the transferability is reduced \citep[see][for alternative approaches]{Chardon2014}.
 
@@
 This approach allowed us to differentiate the contributions to performance gains, as well as to identify possible over-parametrization.
-The main improvements obtained in the present case study are due to the following factors:
+The main improvements obtained in the present case study are due to the following elementss:
 
 \begin{itemize}
-	\item Using four pressure levels for the analogy of circulation seemed to be an optimal number for the studied region, length of archive available, and target predictand considered.
+	\item Using four pressure levels for the circulation analogy seemed to be an optimal number for the studied region, length of archive available, and target predictand considered.
 Beyond four, the validation score was more variable, revealing a loss in robustness due to over-parametrization.
@@
 Indeed, there is a strong interdependence between space and time in the atmospheric circulation, so that e.g.
-the spatial window should move upstream the main atmospheric flow for earlier temporal windows.	Traditional calibration procedures based on a systematic assessment of every combination is not possible anymore when considering more than two pressure levels.
+the spatial window should move upstream the main atmospheric flow for earlier temporal windows.
 	\item The introduction of distinct spatial windows between pressure levels.
-The synoptic circulation is characterized by features with very different scales depending on the height, and important information for predicting rainfall is not necessarily located in the same area from one level to another.
-However, the optimized spatial windows are consistent in between the subregions.
+The synoptic circulation is characterized by features with very different scales depending on the height, and important information for predicting precipitation is not necessarily located in the same area from one level to another.
 	\item The weighting of the analogy criteria between different pressure levels.
-It can be influenced by the variability of the geopotential with altitude, and the change of some levels significance with the targeted region.
-There was a trend for the weighting of circulation predictors to decrease with the increase in pressure, as one can see in Figure \ref{fig:levels_weights_average} for the three optimized methods.
+It can be influenced by the variability of the geopotential height with altitude, or the levels significance in regards to the meteorological processes specific to a region.
+There is a trend for the weighting of circulation predictors to decrease with the increase in pressure, as one can see in Figure \ref{fig:levels_weights_average} for the three optimized methods.
 However, the values stayed around equity.
@@
 However, it can be dangerous to add too many parameters to optimize.
-Indeed, the optimizer will probably use them to successfully improve the calibration score, but the validation control remains very important in order to determine if one is actually improving the method, or if it is being over-parametrized.
+Indeed, the optimizer will probably use them to successfully improve the calibration score, so the validation control remains very important in order to determine if one is actually improving the method, or if it is being over-parametrized.
 Moreover, it might not always be desirable to increase the number of degrees of freedom, and some constraints (e.g.
@@
 In this sense, even though not all degrees of freedom can be found useful, GAs allow assessing their influence.
+Finally, GAs could be used in order to identify e.g.
+the best couples of spatial and temporal windows, to later create a simpler regional method.
 
-The convergence of parallel optimizations decreased when the method to optimize becomes more and more complex.
-The optimizer does not always converge to the exact global optimum, but to its surroundings.
+The convergence of parallel optimizations decreased when the method to optimize became more and more complex.
+The optimizer did not always converge to the exact global optimum, but to its surroundings.
 This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that one has to stop it before the end, due to the required processing time (see Figure \ref{fig:evolution} as example).
@@
 Furthermore, AMs optimized with GAs showed an improvement of the prediction for days with heavier precipitation, including extremes.
-Even though no new extreme value is added to the existing precipitation archive, the distribution of analogue precipitation values for a target situation can move towards the targeted extreme by sampling better candidate situations.
+Even though no new extreme value was added to the existing precipitation archive, the distribution of analogue precipitation values for a target situation can move towards the targeted extreme by sampling better candidate situations.
 Then, the subset of precipitation values collected on the analogue dates can be considered as a sample of the conditional distribution of precipitation associated with this situation.
@@
 Moreover, it contains several manual systematic assessment, such as the selection of the pressure levels and the temporal windows.
-GAs, however, can select the pressure levels and the time windows automatically, which can save a considerable amount of human time.
+GAs, however, can select the pressure levels and the temporal windows automatically, which can save a considerable amount of human time.
 A great advantage of a global optimization is its ability to approach or reach optimal parameter values when they are considered jointly.
 
-A dependence in the selected parameters between the analogy of circulation and the moisture variables was identified.
-When the two levels are considered together, the optimal parameters of the circulation analogy were different.
+A dependence in the selected parameters between the circulation analogy and the moisture variables was identified.
+When the two analogy levels are considered together, the optimal parameters of the circulation analogy changed.
 This complexity can only be exploited in a suitable manner by global optimization methods.
 
-For the present case study, there seemed to be an optimum number of pressure levels to consider for the analogy of circulation, which is four, before losing consistency of the real gains.
-The analogy of circulation was improved by introducing a weighting between pressure levels, and considering independent spatial windows between pressure levels.
+For the present case study, there seemed to be an optimum number of pressure levels to consider for the circulation analogy, which is four, before losing consistency of the real gains.
+The circulation analogy was improved by introducing a weighting between pressure levels, and considering independent spatial windows between pressure levels.
 
 GAs provided parameterizations of AMs that exceeded the performance of the sequential calibration.
-In addition, it has been observed that the prediction for days with strong precipitation were improved to a greater extent, which is clearly interesting in the framework of flood forecasting.
+In addition, it has been observed that the prediction for days with strong precipitation were improved to a greater extent, which is clearly interesting in the context of flood forecasting.
 
@@
 It is even possible to let the optimizer chose the meteorological variable to be used as predictor, as well as the analogy criteria, which is the topic of work in progress.
-Moreover, the AM has been explored for decades for precipitation forecasting, but not as intensively for other predictands.
+Moreover, the AM has been explored for decades for precipitation prediction, but not as intensively for other predictands.
 A global optimizer, such as GAs, can speed up this assessment significantly.
@@
 	\centerline{\includegraphics[width=8.8cm]{figures/fig02.pdf}}
-	\caption{Performance score (CRPSS) on the CP and the VP for three stations (1 - Swiss Chablais, 5 - Southern valleys, 8 - Southeast ridges) when varying the number of geopotential height levels available to the optimizer.}
+	\caption{Performance score (CRPSS) on the CP and the VP for three stations (1 - Swiss Chablais; 5 - Southern valleys; 8 - Southeast ridges) when varying the number of geopotential height levels available to the optimizer.}
 	\label{fig:figure_nb_levels}
@@
 	\centerline{\includegraphics[width=8.4cm]{figures/fig03.pdf}}
-	\caption{Optimized spatial windows for the 4Zo method (analogy of atmospheric circulation on four pressure levels).
-The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
+	\caption{Optimized spatial windows for the 4Zo method (analogy of the atmospheric circulation on four pressure levels).}
 	\label{fig:spatial_windows_4Zo}
@@
 	\centerline{\includegraphics[width=8.4cm]{figures/fig06.pdf}}
-	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on four pressure levels and the analogy on the moisture index on two pressure levels).
-The pressure levels are ordered by increasing pressure and increasing time for the same levels.}
+	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on four pressure levels and the analogy on the moisture index on two pressure levels).}
 	\label{fig:spatial_windows_4Zo-2MIo}
@@
 	\centerline{\includegraphics[width=8.8cm]{figures/fig08.pdf}}
-	\caption{Number of analogues for the different regions and the various methods resulting from the optimization.
+	\caption{Optimal numbers of analogues for the different regions and the two methods, resulting from the optimization.
 Method 4Zo is made of a single level of analogy with $N_{1}$ analogues, whereas 4Zo-2MIo has two levels of analogy with respectively $N_{1}$ and $N_{2}$ analogues.}
@@
 	\centerline{\includegraphics[width=8.8cm]{figures/fig10.pdf}}
-	\caption{Distribution of the optimal weights for the predictors of the first level of analogy (geopotential heights) of the 4Zo, 4Zo-2MIo, and 4Zo-4MIo methods.
+	\caption{Distribution of the optimal weights for the predictors of the first level of analogy (geopotential heights) of the (blue) 4Zo, (red) 4Zo-2MIo, and (green) 4Zo-4MIo methods.
 The results are those of the ten subregions.
@@
 \begin{table}[t]
-	\caption{Pressure levels ($\sim$) automatically selected for the 4Zo method at the different subregions. R represents the reference method (Table \ref{table:params_R1}).}
+	\caption{Pressure levels ($\sim$) automatically selected for the 4Zo method at the different subregions (ID). R represents the 2Z reference method (Table \ref{table:params_R1}).}
 	\footnotesize
@@
 \begin{table}[t]
-	\caption{Relative improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo method, compared to the reference method.}
+	\caption{Relative improvement (\%) of the CRPSS for different precipitation thresholds for the optimized 4Zo method, compared to the reference method.}
 	\footnotesize
@@
 \begin{table}[t]
-	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the analogy of moisture ($\bullet$) of the 4Zo-2MIo method, at the different subregions.
-R represents the reference method (Table \ref{table:params_R2})}
+	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the moisture analogy ($\bullet$) of the 4Zo-2MIo method, at the different subregions (ID).
+R represents the 2Z-2MI reference method (Table \ref{table:params_R2})}
 	\footnotesize

### 2017-01-23 Optimization case study - JoH/corrections/5 - English editing.tex
Elsevier english editing.

--- 2017-01-18 Optimization case study - JoH/elsarticle-template.tex
@@
 Analogue methods provide a statistical precipitation prediction based on synoptic predictors supplied by general circulation models or numerical weather prediction models.
-The method samples a selection of days in the archives that are similar to the target day to predict, and consider the set of their corresponding observed precipitation (the predictand) as the conditional distribution for the target day.
-The relationship between predictors and predictands relies on some parameters that characterize how and where the similitude between two atmospheric situations is defined.
+The method samples a selection of days in the archives that are similar to the target day to be predicted, and consider their set of corresponding observed precipitation (the predictand) as the conditional distribution for the target day.
+The relationship between the predictors and predictands relies on some parameters that characterize how and where the similarity between two atmospheric situations is defined.
 
-This relationship is usually established by a semi-automatic sequential procedure that has strong limitations: (i) it cannot automatically choose the pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters, and (iii) it cannot easily handle new degrees of freedom.
-In this work, a global optimization approach relying on genetic algorithms could optimize all parameters jointly and automatically.
-It allowed taking into account parameters inter-dependencies, and selecting objectively some parameters that were manually selected beforehand, which e.g.
-obviates the need of assessing a high number of combinations of the pressure levels and the temporal windows of the predictor variables.
+This relationship is usually established by a semi-automatic sequential procedure that has strong limitations: (i) it cannot automatically choose the pressure levels and temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between parameters, and (iii) it cannot easily handle new degrees of freedom.
+In this work, a global optimization approach relying on genetic algorithms was able to optimize all parameters jointly and automatically.
+It allowed consideration of parameter inter-dependencies, and objective selection of some parameters that were manually selected beforehand, which, among other things, obviates the need to assess a large number of combinations of pressure levels and temporal windows of predictor variables.
 
 The global optimization was applied to some variants of the analogue method for the Rh\^{o}ne catchment in the Swiss Alps.
-The performance scores increased compared to reference methods, and this even to a greater extent for days with high precipitation totals.
+The performance scores increased compared to reference methods, especially for days with high precipitation totals.
 The resulting parameters were found to be relevant and coherent between the different subregions of the catchment.
-Moreover, they were obtained automatically and objectively, which reduces efforts invested in exploration attempts when adapting the method to a new region or for a new predictand.
-In addition, the approach allowed for new degrees of freedom, such as a possible weighting between the pressure levels, and non overlapping spatial windows.
+Moreover, they were obtained automatically and objectively, which reduces the effort that needs to be invested in exploration attempts when adapting the method to a new region or for a new predictand.
+In addition, the approach allowed for new degrees of freedom, such as a possible weighting between pressure levels, and non-overlapping spatial windows.
 \end{abstract}
@@
 
-The analogue method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1956, Lorenz1969} that similar situations in terms of the atmospheric circulation are likely to lead to similar local weather \citep{Duband1970}.
+The analogue method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1956, Lorenz1969} that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Duband1970}.
 It uses predictor variables describing the synoptic atmospheric circulation in order to predict local-scale predictands of interest.
-It is often used to predict daily precipitation, either in an operational forecasting context \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Horton2016a, Hamill2015, BenDaoud2016} or a climate downscaling context \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015, Raynaud2016b}.
+It is often used to predict daily precipitation, either in an operational forecasting context \citep[e.g.][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Horton2016a, Hamill2015, BenDaoud2016} or a climate downscaling context \citep[e.g.
+][]{Radanovics2013, Chardon2014, Dayon2015, Raynaud2016b}.
 Other predictands are also considered, such as precipitation radar images \citep{Panziera2011,Foresti2015a}, temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016, Raynaud2016b}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, and radiation \citep{Bois1981, Raynaud2016b}.
 
-In real-time forecasting, it is used mainly by practitioners, notably hydropower companies or flood forecasting services.
-They need to anticipate water yields or to issue early flood warnings several days in advance.
-The classical forecasting chain consists in using limited area models (e.g.
+In real-time forecasting, it is used mainly by practitioners, notably hydropower companies or flood forecasting services, that need to anticipate water yields or issue early flood warnings several days in advance.
+The classical forecasting chain consists of using limited area models (e.g.
 AROME, or COSMO) forced by global NWP (numerical weather prediction) models with a lower resolution.
-However, their use require very important processing capacities, and the resulting forecast still present large uncertainties and biases.
+However, their use requires very important processing capacities, and the resulting forecast still presents large uncertainties and biases.
 Although these outputs are essential, they can be supplemented by other sources of forecasts providing useful information.
-In contrast to local NWP models, AMs can transform at low cost the synoptic-scale information provided by the global NWP model into precipitation forecasts, by using the natural local behavior in response to synoptic-scale influence stored in the archive of observed precipitation.
-Running an AM approach is so quick that it can search for analogues for every day up to ten days ahead, eventually for the different traces of an ensemble forecast and/or issued by different NWP models (e.g.
+In contrast to local NWP models, AMs can transform at low cost the synoptic-scale information provided by the global NWP model into precipitation forecasts, by using the natural local behaviour in response to synoptic-scale influences stored in the archive of observed precipitation.
+Running an AM approach is fast enough that it can search for analogues for each day, up to ten days ahead, eventually for the different traces of an ensemble forecast and/or those issued by different NWP models (e.g.
 NOAA-GFS or ECMWF-IFS), in a matter of minutes.
 
-In climate studies AMs are used to downscale the outputs of general circulation model (GCM) or regional climate models (RCMs) simulation runs \citep{Dayon2015} or to reconstruct past weather conditions \citep{Caillouet2016}.
+In climate studies, AMs are used to downscale the outputs of a general circulation model (GCM) or regional climate model (RCM) simulation runs \citep{Dayon2015} or to reconstruct past weather conditions \citep{Caillouet2016}.
 In future climate studies, RCMs are often used to dynamically downscale precipitation to a local scale.
-However, even though the relevance of RCMs'outputs increases, a bias correction of the outputs is still often required, particularly in complex terrain.
+However, even though the relevance of RCMs' outputs increases, a bias correction of the outputs is often still required, particularly in complex terrain.
 Moreover, their application is computer-intensive, which makes it difficult to cover all combinations of climate scenarios and GCMs.
-Therefore, the idea is to bypass the small scale simulations and to go from the large scale situation to the end variables like precipitation by statistical downscaling \citep{Maraun2010}.
+Therefore, the idea is to bypass the small-scale simulations and to go from the large-scale situation to the end variables such as precipitation by statistical downscaling \citep{Maraun2010}.
 
@@
 The method can be designed with multiple successive subsampling steps, or analogy levels, each of them relying on different meteorological variables.
-A certain number of parameters define the relationship between predictors and predictands, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criterion itself, and finally the number of analogue situations to keep at each subsampling level.
+A certain number of parameters define the relationship between predictors and predictands, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criterion itself, and finally, the number of analogue situations to keep at each subsampling level.
 These parameters are usually calibrated by means of a semi-automatic sequential procedure \citep{Bontron2004, Radanovics2013}, i.e.
-by optimizing each single parameter one at a time, in an arbitrarily chosen order, with no or little reassessment.
-This sequential approach has therefore strong limitations: (i) it cannot automatically choose the optimal pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it cannot easily handle new degrees of freedom, such as a possible weighting between the pressure levels.
-Thus, even if the processing involved is relatively fast, the sequential approach requires laborious assessments of predictors combinations (variables, pressure levels, temporal windows), and presents a high risk of ending in a local optimum due to subjective initial choices and lack of consideration of parameter inter-dependencies.
+by optimizing each single parameter, one at a time, in an arbitrarily chosen order, with no or little reassessment.
+This sequential approach therefore has strong limitations: (i) it cannot automatically choose the optimal pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it cannot easily handle new degrees of freedom, such as a possible weighting between the pressure levels.
+Thus, even if the processing involved is relatively fast, the sequential approach requires laborious assessments of predictor combinations (variables, pressure levels, temporal windows), and presents a high risk of ending in a local optimum because of subjective initial choices and lack of consideration of parameter inter-dependencies.
 Other calibration methods exist for specific applications, such as radar images \citep{Panziera2011, Foresti2015a}.
 
-With the perspective to overcome these limitations, a global optimization by genetic algorithms (GAs) was introduced.
-An intensive assessment work resulted in recommendations of parametrization of GAs in order to optimize AMs successfully \citep{Horton2016}.
-The present paper is based on these recommendations and apply them for precipitation prediction for the upper Rh\^{o}ne catchment in the Swiss Alps, using AMs of varying complexity.
-It aims at illustrating the relevance of a fully-automatic, objective, and global, optimization technique for AMs.
+Aiming to overcome these limitations, a global optimization by genetic algorithms (GAs) was introduced.
+An intensive assessment resulted in recommendations to parametrize GAs in order to optimize AMs successfully \citep{Horton2016}.
+The present paper is based on these recommendations, and applies them to precipitation prediction for the upper Rh\^{o}ne catchment in the Swiss Alps, using AMs of varying complexity.
+It aims at illustrating the relevance of a fully automatic, objective, and global, optimization technique for AMs.
 The applications are indeed numerous, as AMs have to be adapted to every new location they are applied, or to any new predictand they should predict.
 
-Data, AMs, and the optimization techniques (sequential and GAs) are presented in section \ref{sec:data_methods}.
-The results are first given for the optimization of the analogy of the atmospheric circulation only (section \ref{sec:optim_circul}), before being extended to a method adding a second level of analogy on moisture variables (section \ref{sec:optim_moisture}).
-General discussions (section \ref{sec:discussion}) and conclusions (section \ref{sec:conclusions}) follow.
+The data, AMs, and optimization techniques (sequential and GAs) are presented in Section \ref{sec:data_methods}.
+The results are first given for the optimization of the analogy of atmospheric circulation only (Section \ref{sec:optim_circul}), before being extended to a method adding a second level of analogy on moisture variables (Section \ref{sec:optim_moisture}).
+General discussions (Section \ref{sec:discussion}) and conclusions (Section \ref{sec:conclusions}) follow.
 
@@
 The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$.
-This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aimed at real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
+This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project aimed at real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
 Even though the region is rather small, the meteorological influences related to extreme weather conditions vary substantially within it \citep[see][]{Horton2012}.
-Indeed, a high spatial variability of the precipitation climatology exists, which is due to the complex orography of the region, and the mix of various meteorological influences.
-Based on different climatological analyses, the precipitation gauging stations in the catchment were clustered in ten subregions (Fig.\ \ref{fig:map}) :
+Indeed, a high spatial variability of precipitation climatology exists, which is due to the complex orography of the region, and the mix of various meteorological influences.
+Based on different climatological analyses, the precipitation gauge stations in the catchment were clustered in ten subregions (Fig.\ \ref{fig:map}):
 
@@
 
-AMs rely on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather variable one wants to predict.
+AMs rely on two types of data: predictors, which are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather variable one wants to predict.
 
@@
 to 6~a.m.
-the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008.
-The time series from every available gauging station were averaged over the ten subregions (Fig.\ \ref{fig:map}) of approximately 500~km$^{2}$ each in order to smooth local effects \citep{Obled2002, Marty2012}.
-It helps accounting for local variability, mainly when convective processes are involved, which increases slightly the prediction skill.
+the next day) measured at the MeteoSwiss network stations, for the period 1961--2008 .
+The time series from every available gauge station were averaged over the ten subregions (Fig.\ \ref{fig:map}), which were approximately 500~km$^{2}$ each, in order to smooth local effects \citep{Obled2002, Marty2012}.
+This helps account for local variability, mainly when convective processes are involved, which slightly increases the prediction skill.
 
-It must be stressed that the predictand is here sa temporally cumulated variable, compared to the meteorological predictors, which may be considered instantaneous.
-Depending on the duration of the accumulation period (here 24~h, but could have been 6, 12~h, or more than 24~h), the choice of predictors will vary.
+It must be stressed that the predictand here is a temporally cumulated variable, compared to the meteorological predictors, which may be considered instantaneous.
+Depending on the duration of the accumulation period (here 24~h, but could have been 6~h, 12~h, or more than 24~h), the choice of predictors will vary.
 
-The 48 years precipitation dataset was divided into a calibration period (CP) and a validation period (VP).
-Using data independent from the CP to validate the results is very important in order to assess the robustness of the proposed improvements and to avoid over-parametrization of the method.
+The 48-yr precipitation dataset was divided into a calibration period (CP) and a validation period (VP).
+Using data independent of the CP to validate the results is very important in order to assess the robustness of the proposed improvements and to avoid over-parametrization of the method.
 
-In order to reduce potential bias related to trends linked to climate change or to the evolution in measurement techniques, the selection of the VP was evenly distributed over the entire series \citep{BenDaoud2010}.
-Thus, one year every six years was selected for validation, which represents a total of 8 years for the VP and 40 for CP.
-The choice of the sequence was made in order to have similar statistical characteristics between the CP and the VP.
+In order to reduce potential biases related to trends linked to climate change or to the evolution in measurement techniques, the selection of the VP was evenly distributed over the entire series \citep{BenDaoud2010}.
+Thus, one out of every six years was selected for validation, which represents a total of 8 years for the VP and 40 for the CP.
+This choice of sequence was made in order to have similar statistical characteristics between the CP and VP.
 
-\subsection{The analogue method}
+\subsection{Analogue method}
 \label{sec:references}
 
-Multiple variations of the analogue method exist, and most of them will not be detailed hereafter \cite[see][for more comprehensive listings]{BenDaoud2016}.
-However, there are mainly two parameterizations that are most often used for precipitation prediction and that were considered as reference: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
+Multiple variations of the analogue method exist, most of which are not detailed here \cite[see][for a more comprehensive listing]{BenDaoud2016}.
+However, there are mainly two parameterizations that are most often used for precipitation prediction and that are considered as reference: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
 
-The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): the similarity of the atmospheric circulation of a target date with every day of the archive is assessed by processing the S1 criterion \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window:
+The method based on the analogy of synoptic circulation consists of the following steps (Table \ref{table:params_R1}): the similarity of the atmospheric circulation of a target date with every day of the archive is assessed by processing the S1 criterion \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window:
 
@@
 \end{equation}
-where $\Delta \hat{z}_{i}$ is the difference in geopotential height between the \textit{i}th pair of adjacent points of the gridded data describing the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
+where $\Delta \hat{z}_{i}$ is the difference in geopotential height between the \textit{i}-th pair of adjacent points of gridded data describing the target situation, and $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation.
 The differences are processed separately in both North and East directions over the selected spatial domain.
@@
 \citet{Bontron2005} show that the geopotential height at 500~hPa (Z500) and 1000~hPa (Z1000) are the best first predictors of the NCEP/NCAR reanalysis I dataset, and that the S1 criterion performs better than scores based on absolute distances.
-The reason for such better results is that the S1 criterion allows comparing the circulation patterns, by means of the gradients, rather than the absolute value of the geopotential height, which represent better the flow direction.
-To cope with seasonal effects, candidate dates are extracted within a period of four months centered around the target date, for every year of the archive.
-This method using two geopotential heights will be named 2Z.
+The reason for such better results is that the S1 criterion allows comparison of the circulation patterns, by means of the gradients, rather than the absolute value of the geopotential height, which better represent the flow direction.
+To cope with seasonal effects, candidate dates are extracted within a period of four months centred around the target date, for every year of the archive.
+This method using two geopotential heights is named 2Z.
 
@@
 The number of analogues, $N_{1}$, is a parameter to calibrate.
-Then, the daily observed precipitation amount of the $N_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day.
+Then, the daily observed precipitation amount for the $N_{1}$ resulting dates provide the empirical conditional distribution, considered as the probabilistic prediction for the target day.
 
-The other most known parametrization adds a second level of analogy on moisture variables (method 2Z-2MI, Table \ref{table:params_R2}).
-The predictor that \citet{Bontron2004} found optimal for the France territory is a moisture index made of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850).
+The other most well-known parametrization adds a second level of analogy on the moisture variables (method 2Z-2MI, Table \ref{table:params_R2}).
+The predictor that \citet{Bontron2004} found optimal for France is a moisture index made of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850).
 \cite{Horton2012a} confirms that this index is also better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis I considered independently.
-When adding a second level of analogy, $N_{2}$ dates are subsampled within the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations.
+When adding a second level of analogy, $N_{2}$ dates are subsampled within the $N_{1}$ analogues of the atmospheric circulation, to end up with a smaller number of analogue situations.
 When this second level of analogy is added, a higher number of analogues $N_{1}$ is kept on the first level.
-Moisture fields are not as well predicted by NWP models as pressure variables.
-It implies that the 2Z-2MI method, when used in real-time forecasting, is very dependent on the skill of the NWP model in predicting moisture fields, and thus its use is often restricted to the first lead times.
+Moisture fields are not as well-predicted by NWP models as pressure variables.
+This implies that the 2Z-2MI method, when used in real-time forecasting, is very dependent on the skill of the NWP model in predicting moisture fields, and thus its use is often restricted to the first lead times.
 
@@
 
-The performance assessment in the present context consists in verifying the prediction of an ensemble-probabilistic technique.
-The set of precipitations values collected with each analogue can be considered as a sample drawn from the conditional distribution associated with the current circulation.
+The performance assessment in the present context consists of verifying the prediction of an ensemble probabilistic technique.
+The set of precipitation values collected with each analogue can be considered as a sample drawn from the conditional distribution associated with the current circulation.
 The score that is most often used to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}.
-It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$.
+It allows evaluating the predicted cumulative distribution functions $F(y)$, for example, of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$.
 The better the prediction, the smaller the score.
-The mean CRPS of a prediction series of length $n$ can be written:
+The mean CRPS of a prediction series of length $n$ can be written as:
 
@@
 where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value 1 otherwise.
-The mean CRPS is averaged on the calibration, respectively the validation periods, on all days.
+The mean CRPS is averaged on the calibration, respectively, the validation periods, on all days .
 
-In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution of precipitation from the entire archive as the reference.
-The CRPSS (Continuous Ranked Probability Skill Score) is thus defined as following:
+In order to compare the value of the score relative to a reference, one often considers its skill score expression, and uses the climatological distribution of precipitation from the entire archive as the reference.
+The CRPSS (Continuous Ranked Probability Skill Score) is thus defined as follows:
 
@@
 
-Note however that the choice of the reference does not matter so much when assessing potential improvements of the method, since we shall consider more its relative increase or decrease rather than the CRPSS absolute value.
+Note, however, that the choice of reference does not matter so much when assessing potential improvements of the method, since we consider more its relative increase or decrease rather than the CRPSS absolute value.
 
@@
 
-AMs are usually calibrated by a semi-automatic sequential procedure elaborated by \citet{Bontron2004} \cite[see also ][]{Radanovics2013, BenDaoud2016}.
-The calibration technique optimizes the spatial windows on which the predictors are compared and the number of analogues, for every level of analogy, by maximizing the performance score (CRPSS).
-However, the different analogy levels are calibrated sequentially, and the meteorological variables, the pressure levels and the temporal windows are chosen manually.
+AMs are usually calibrated by a semi-automatic sequential procedure, as elaborated by \citet{Bontron2004} \cite[see also ][]{Radanovics2013, BenDaoud2016}.
+The calibration technique optimizes the spatial windows in which the predictors are compared and the number of analogues for every level of analogy, by maximizing the performance score (CRPSS).
+However, the different analogy levels are calibrated sequentially, and the meteorological variables, pressure levels, and temporal windows are chosen manually.
 The procedure, as defined by \citet{Bontron2004}, consists of the following steps:
@@
 	\begin{enumerate}
-		\item meteorological variable,
-		\item pressure level,
-		\item temporal window (hour of the day),
-		\item initial analogue numbers.
+		\item Meteorological variable
+		\item Pressure level
+		\item Temporal window (hour of the day)
+		\item Initial analogue numbers
 	\end{enumerate}
@@
 	\end{enumerate}
-	\item A new level of analogy can then be added, based on other variables (such as the moisture index) with chosen pressure levels, temporal windows, and initial number of analogues $N_{2}$.
+	\item A new level of analogy can then be added, based on other variables (such as the moisture index) with the chosen pressure levels, temporal windows, and initial number of analogues $N_{2}$.
 The procedure starts again from step 2 (calibration of the spatial window and the number of analogues) for the new level.
@@
 Genetic algorithms (GAs) were developed by \citet{Holland1992b} and \citet{Goldberg1989}.
-They are part of Evolutionary Algorithms \citep{Back1993b, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
-GAs seek the global optimum on a complex surface, theoretically without restriction, which is of interest for AMs, that are characterized by a complex high-dimensional error function having multiple local optima.
-Practically, GAs allow rapidly approaching satisfactory solutions, but they do not provide the optimum solution for sure \citep{Zitzler2004a}.
+They are part of the Evolutionary Algorithms \citep{Back1993b, Schwefel1993}, which were inspired by some mechanisms in biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
+GAs seek the global optimum on a complex surface, theoretically without restriction, which is of interest for AMs, which are characterized by a complex high-dimensional error function having multiple local optima.
+Practically, GAs allow rapidly approaching satisfactory solutions, but they are not guaranteed to provide the optimum solution \citep{Zitzler2004a}.
 It is indeed mainly a matter of time.
 When the optimizer gets closer to the global optimum, any new improvement takes more time to appear (see for example the slow-down of the improvements over generations in Figure \ref{fig:evolution}), and the final adjustment of the parameters can be very time consuming \citep{Back1993a}.
-For problems that require a significant amount of time in order to evaluate the objective function, as in the case of AMs (because it needs to make a prediction for every day of the CP), the number of generations has to be limited in order to get reasonable processing time.
+For problems that require a significant amount of time to evaluate the objective function, as in the case of AMs (because it needs to make a prediction for every day of the CP), the number of generations has to be limited in order to ensure a reasonable processing time.
 Thus, different acceptable solutions can result from one or more optimization runs \citep{Holland1992b}.
-This is both a strength and a weakness of GAs: they are very good at exploring complex parameter spaces in order to identify the most promising areas, but they will not necessarily always find the best solution with the optimal values of all parameters \citep{Holland1992b}.
+This is both a strength and a weakness of GAs: they are very good at exploring complex parameter spaces in order to identify the most promising areas, but they will not necessarily always find the best solution with the optimal values for all parameters \citep{Holland1992b}.
 
-The optimizations were here performed based on the recommended GAs parametrization for AMs as described in \citet{Horton2016}.
-As the optimization is mostly sensitive to the mutation operator (that randomly changes some values in the parameters sets), parallel optimizations are considered with variants of this operator, according to \citet{Horton2016}:
+The optimizations here were performed based on the recommended GA parametrization for AMs as described in \citet{Horton2016}.
+As the optimization is mostly sensitive to the mutation operator (that randomly changes some values in the parameter sets), parallel optimizations are considered with variants of this operator, according to \citet{Horton2016}:
 
 \begin{itemize}
-	\item 3x non-uniform mutation \citep{Michalewicz1996} with varying parameters,
-	\item 1x multi-scale mutation \citep{Horton2016},
-	\item 2x chromosome of adaptive search radius \citep{Horton2016}
+	\item 3x non-uniform mutation \citep{Michalewicz1996} with varying parameters
+	\item 1x multi-scale mutation \citep{Horton2016}
+	\item 2x chromosome of adaptive search radius \citep{Horton2016}.
 \end{itemize}
@@
 A population size of 500 individuals (i.e.
-parameter sets of the AM to be detailed hereunder) was considered, and the optimization was stopped when the best individual (with the highest CRPSS performance score) did not evolve for 20 generations (cycles of the optimization).
+parameter sets of the AM to be detailed below) was considered, and the optimization was stopped when the best individual (with the highest CRPSS performance score) did not evolve for 20 generations (cycles of optimization).
 
-\section{Optimization of the circulation analogy}
+\section{Optimization of circulation analogy}
 \label{sec:optim_circul}
@@
 The analogy of the atmospheric circulation was optimized for the ten subregions (Section \ref{sec:case_study}) independently.
-We started from the most simple AM, and increased the complexity in order to identify the degrees of freedom that are of particular interest.
+We started from the simplest AM, and increased the complexity in order to identify the degrees of freedom that are of particular interest.
 Thus, the tested parametrization evolved iteratively in complexity.
@@
 The reference method for the analogy of the atmospheric circulation (2Z, Table \ref{table:params_R1}), based on Z500 and Z1000, was first considered.
-The optimizer had to choose simulatneously the number of analogues, both spatial windows with no overlapping constraint (i.e.
+The optimizer had to choose simultaneously the number of analogues, both spatial windows with no overlapping constraint (i.e.
 they can differ from one pressure level to another), as well as the temporal windows (hours of observation of the geopotential), which cannot be achieved with the sequential calibration technique.
-The performance score (CRPSS) was slightly improved, with these limited degrees of freedom, in regards to the 2Z reference method calibrated with the sequential procedure.
+The performance score (CRPSS) was slightly improved, with these limited degrees of freedom, relative to the 2Z reference method calibrated with the sequential procedure.
 Some tests showed that most of the gains were due to the non-overlapping spatial windows.
-It demonstrated that the optimizer was able to get relevant parameters for a simple method.
+This demonstrated that the optimizer was able to obtain relevant parameters for a simple method.
 
 Then, an additional degree of freedom was provided to the GAs by letting them choose the pressure levels along with the other parameters (analogue numbers, spatial and temporal windows), which is also a non-automated process in the sequential calibration.
-This degree of freedom increased the optimization time and might decrease the number of simulations that converge to a single solution.
-However, most solutions were very close in terms of the performance score, which was improved further.
+This degree of freedom increased the optimization time, and might decrease the number of simulations that converge to a single solution.
+However, most solutions were very close in terms of the performance score, which was further improved.
 The selected pressure levels were Z500 or Z700 for the upper level, and Z925 or Z1000 (most often) for the lower level.
@@
 There was no constraint on the predictors, so that the same pressure level could be selected more than once.
-Further improvements were found on the performance score, both for the CP and the VP, confirming that this additional information was beneficial for the quality of the prediction.
+Further improvements were found in the performance score, both for the CP and the VP, confirming that this additional information was beneficial for the quality of the prediction.
 
@@
 The addition of circulation predictors globally improved the prediction skill (for both the CP and the VP) only up to four predictors (Figure \ref{fig:figure_nb_levels}).
-Afterwards, the score on the VP was more variable, showing eventually even a decrease, which revealed an over-parametrization of the method, and thus a lack of robustness.
-After four predictors, the score on the CP did not increase substantially, and could even present some local decrease due to increasing difficulty for the optimizer to converge.
+Afterwards, the score on the VP was more variable, eventually even showing a decrease, which revealed an over-parametrization of the method, and thus a lack of robustness.
+After four predictors, the score for the CP did not increase substantially, and even presented a local decrease due to increasing difficulty for the optimizer to converge.
 Selecting four circulation predictors (geopotential heights) was considered optimal for this case study, since the gain in CRPSS was significant, and the model remained relatively simple.
-It cannot be excluded that another number would prevail in another region than the upper Rh\^{o}ne catchment, under other meteorological conditions, or with another reanalysis dataset.
+It cannot be ruled out that another number would prevail in a region other than the upper Rh\^{o}ne catchment, under other meteorological conditions, or with another reanalysis dataset.
 
-\subsection{Which parameters are optimized ?}
+\subsection{Which parameters are optimized?}
 
-The chosen method for the atmospheric circulation analogy, based on four circulation predictors (geopotential heights), and that will be named 4Zo (o for optimized), was made of the following degrees of freedom:
+The chosen method for the atmospheric circulation analogy, based on four circulation predictors (geopotential heights), and which is named 4Zo (o for optimized), was based on the following degrees of freedom:
 
@@
 	\setlength\itemsep{-4px}
-	\item the selection of the pressure levels (4 degrees),
-	\item the temporal windows (4 degrees),
-	\item the spatial windows (4x4 degrees),
-	\item the weights (4 degrees),
-	\item the number of analogues (1 degree).
+	\item selection of pressure levels (4 degrees)
+	\item temporal windows (4 degrees)
+	\item spatial windows (4 x 4 degrees)
+	\item weights (4 degrees)
+	\item number of analogues (1 degree).
 \end{itemize}
 
-This sums up to 29 degrees of freedom that were optimized simultaneously.
+This adds up to 29 degrees of freedom that were optimized simultaneously.
 
-\subsection{Results for the 4Zo method}
+\subsection{Results for 4Zo method}
 
@@
 
-The resulting CRPSS scores are provided in Figure \ref{fig:figure_crpss_4Zo} and were in average 35.8~\% for the CP and 35.5~\% for the VP, comparatively to 31.1~\% and 32.3~\% respectively for the reference method 2Z on the atmospheric circulation (optimized by the sequential procedure).
-The score was also calculated for three precipitation thresholds: P\(\geq\)1~mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_4Zo}).
-The gain in score increased with the precipitation threshold: the relative improvement of the CRPSS was in average, respectively for the different thresholds, 13.3~\%, 15.4~\% and 29.1~\% for the CP and 7.9~\%, 11.~1\% and 34.5~\% for the VP.
-The optimization improved thus even more the prediction for days with significant precipitation than usual days.
+The resulting CRPSS scores are provided in Figure \ref{fig:figure_crpss_4Zo} and were on average 35.8\% for the CP and 35.5\% for the VP, compared to 31.1\% and 32.3\%, respectively, for the reference method 2Z on the atmospheric circulation (optimized by the sequential procedure).
+The score was also calculated for three precipitation thresholds: P \(\geq\) 1~mm, P \(\geq\) 0.1\(\cdot\)P10, and P \(\geq\) 0.5\(\cdot\)P10, P10 being the daily precipitation with a 10~year return period (Table \ref{table:scores_thresholds_4Zo}).
+The gain in score increased with the precipitation threshold: the relative improvement of the CRPSS was, on average, for the different thresholds, 13.3\%, 15.4\%, and 29.1\% for the CP and 7.9\%, 11.1\%, and 34.5\% for the VP.
+The optimization thus improved the prediction even more for days with significant precipitation than for the usual days.
 
-To assess the parameters cross-compatibility, and the spatial coherence of the resulting parameters, those optimized for one subregion were applied to the others.
+To assess the parameters’ cross-compatibility and the spatial coherence of the resulting parameters, those optimized for one subregion were applied to the others.
 The resulting losses or gains of the CRPSS are displayed in Figure \ref{fig:crossing_4Zo}.
@@
 
-The automatic selections of the pressure levels (Table \ref{table:levels_GA_4Zo}) and the temporal windows (not shown) for the analogy of circulation showed a great homogeneity and were spatially consistent.
+The automatic selections of pressure levels (Table \ref{table:levels_GA_4Zo}) and temporal windows (not shown) for the analogy of circulation showed a great homogeneity and were spatially consistent.
 First of all, the level Z1000 was always selected twice (the first time at 6 or 12~h, and the second always at 30~h) and Z700 was selected once for every subregion (always at 24~h).
-The level which varied from one subregion to another, however in a spatially consistent way, was the upper level (however always at 12~h), which was Z300 for the North-West part of the catchment, Z500 for most of the other subregions, and Z600 for the Conches Valley.
+The level that varied from one subregion to another, albeit in a spatially consistent way, was the upper level (always at 12~h), which was Z300 for the north-west part of the catchment, Z500 for most of the other subregions, and Z600 for the Conches Valley.
 The optimizer thus provided consistent selections of pressure levels and temporal windows.
-The automatic selection of the pressure levels is a big advantage in favor of a global optimization.
+The automatic selection of pressure levels is a big advantage in favour of global optimization.
 
@@
 For most subregions, the second level (Z700) was compared on thin and longitudinally extended spatial windows.
-The third level (Z1000 at 6 or 12~h) also had longitudinally extended domains, but a bit larger.
+The third level (Z1000 at 6 or 12~h) also had longitudinally extended domains, but were slightly larger.
 The last one (Z1000 at 30~h) had rather large and squared windows.
-Subregions number 5 (Southern valleys) and 6 (Southern ridges) had exactly the same spatial windows, which suggest that they behave in a similar way and thus could have been merged.
+Subregions number 5 (southern valleys) and 6 (southern ridges) had exactly the same spatial windows, which suggests that they behave in a similar way and thus could have been merged.
 This similarity is a good sign for the accuracy of the optimized parameters.
 
-The performance scores showed non-negligible improvements for both the CP and the VP (Figure \ref{fig:figure_crpss_4Zo}) compared to the 2Z reference method optimized by the sequential procedure.
+The performance scores showed non-negligible improvements for both the CP and VP (Figure \ref{fig:figure_crpss_4Zo}) compared to the 2Z reference method optimized by the sequential procedure.
 Even more interestingly, the results for higher precipitation thresholds (Table \ref{table:scores_thresholds_4Zo}) showed the largest improvements.
 This is of particular interest in the framework of flood forecasting.
-The further improvement of days with higher precipitation totals is likely related to the fact that larger values contribute more to the CRPS score, which means that better predicting these days results in significant increase of the global performance score.
+The further improvement of days with higher precipitation totals is likely related to the fact that larger values contribute more to the CRPS score, which means that better predicting these days results in significant increase in the global performance score.
 
-The analysis of the parameters cross-compatibility showed that obviously the parameters were optimal on the CP for the subregion for which they were optimized (Figure \ref{fig:crossing_4Zo} top).
-However, the losses in CRPSS when exchanging the parameters were not of the same magnitude between the different subregions.
-Indeed, the Upper Rhone Valley (7) and moreover the Southeast ridges (8) seemed to behave significantly differently.
-These two regions have different climatic properties than the others as they are particularly sensitive to southerly flows.
-Indeed, almost all heavy precipitation events occurred under a southerly regime, such as in the Liguria, Piedmont and Aosta regions in Italy, whereas the other subregions of the catchment had extreme events mainly under a westerly regime \citep{Horton2012}.
+The analysis of the parameters’ cross-compatibility showed that the parameters were obviously optimal on the CP for the subregion for which they were optimized (Figure \ref{fig:crossing_4Zo} top).
+However, the losses in CRPSS when exchanging the parameters were not of the same magnitude among the different subregions.
+Indeed, the Upper Rhone Valley (7) and, moreover, the southeast ridges (8) seemed to behave significantly differently.
+These two regions have different climatic properties than the others, as they are particularly sensitive to southerly flows.
+Indeed, almost all heavy precipitation events occurred under a southerly regime, such as in the Liguria, Piedmont, and Aosta regions in Italy, whereas the other subregions of the catchment had extreme events mainly under a westerly regime \citep{Horton2012}.
 Thus, as the performance score is significantly influenced by heavy precipitation values, the parameters for the different subregions are likely optimized to better predict these days.
-It can then be expected that the optimal parameters differ between these two subregions and the other ones.
-This points at the importance of taking into account leading meteorological influences during precipitation stations clustering, that are not always best represented by the geographical distance.
+It can then be expected that the optimal parameters differ between these two subregions and the others.
+This points at the importance of taking into account leading meteorological influences during precipitation station clustering, which are not always best represented by geographical distance.
 
-Globally, the same cross-compatibility structure could be observed for the VP (Figure \ref{fig:crossing_4Zo} bottom), but in this case, minor improvements were occasionally observed when crossing the parameters, due to the presence of other events in the VP that might be better predicted by a different parameter set.
-The relatively small differences in score between parameterizations indicated that even though the parameters might differ significantly, the performance might not be drastically affected.
-Even a change in the pressure level did not mean a radical drop of the score value.
+Globally, the same cross-compatibility structure could be observed for the VP (Figure \ref{fig:crossing_4Zo} bottom), but in this case, minor improvements were occasionally observed when crossing the parameters, because of the presence of other events in the VP that might be better predicted by a different parameter set.
+The relatively small differences in scores between parameterizations indicated that even though the parameters might differ significantly, the performance might not be drastically affected.
+Even a change in the pressure level did not mean a radical drop in the score value.
 A different parametrization may lead to a distinct selection of analogue days, and thus to an improvement of the prediction under certain weather conditions at the expense of others.
 
-\section{Optimization of the analogy with moisture information}
+\section{Optimization of analogy with moisture information}
 \label{sec:optim_moisture}
@@
 It is known that moisture variables as a second level of analogy do provide improvements to the method (section \ref{sec:references}).
-The moisture index, which is a combination of the relative humidity and the precipitable water, has thus also to be optimized.
-In order to do so, a constraint to the optimizer had to be introduced, so as to select the same temporal window (time of observation) for both variables.
+The moisture index, which is a combination of the relative humidity and precipitable water, has thus also to be optimized.
+In order to do so, a constraint on the optimizer had to be introduced, so as to select the same temporal window (time of observation) for both variables.
 
-Two methods were assessed: one with two moisture predictors (moisture index on two pressure levels or at two different hours) named 4Zo-2MIo, and one with four moisture predictors named 4Zo-4MIo.
-When introducing two predictors for the moisture analogy, the number of degrees of freedom raised to 42, and to 54 with four predictors.
+Two methods were assessed: one with two moisture predictors (moisture index on two pressure levels or at two different hours), named 4Zo-2MIo, and one with four moisture predictors, named 4Zo-4MIo.
+When introducing two predictors for the moisture analogy, the number of degrees of freedom increased to 42, and to 54 with four predictors.
 However, there was no substantial difference in the performance scores between both 4Zo-2MIo and 4Zo-4MIo methods, which suggests that considering four moisture predictors is not necessary.
@@
 
-The optimization was processed on both levels of analogy simultaneously. This implies that the analogy of the atmospheric circulation could change due to the new moisture information.
+The optimization was processed on both levels of analogy simultaneously. This implies that the analogy of the atmospheric circulation could change because of the new moisture information.
 
-\subsection{Results for the 4Zo-2MIo method}
+\subsection{Results for 4Zo-2MIo method}
 
-As previously, the optimized parameters differed from one subregion to another, and this even to a greater extent.
-The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_4Zo-2MIo} for 4Zo-2MIo, along with the selected pressure levels for both the circulation and the moisture analogy (Table \ref{table:levels_GA_4Zo_2MIo}).
+As seen previously, the optimized parameters differed from one subregion to another, but to an even greater extent.
+The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_4Zo-2MIo} for 4Zo-2MIo, along with the selected pressure levels for both the circulation and moisture analogy (Table \ref{table:levels_GA_4Zo_2MIo}).
 
-The CRPSS scores of the optimized 4Zo-2MIo method are provided in Figure \ref{fig:figure_crpss_4Zo-2HIo} and amounted in average to 40~\% (CP) and 40.3~\% (VP), compared to 35.2~\% (CP) and 36.2~\% (VP) for the reference method 2Z-2MI on the moisture analogy optimized with the sequential procedure.
-The parameters cross-compatibility are shown in Figure \ref{fig:crossing_4Zo-2MIo}.
+The CRPSS scores of the optimized 4Zo-2MIo method are provided in Figure \ref{fig:figure_crpss_4Zo-2HIo} and amounted on average to 40\% (CP) and 40.3\% (VP), compared to 35.2\% (CP) and 36.2\% (VP) for the reference method 2Z-2MI on the moisture analogy optimized with the sequential procedure.
+The parameters’ cross-compatibilities are shown in Figure \ref{fig:crossing_4Zo-2MIo}.
 As for 4Zo, the 4Zo-2MIo method presented larger improvements in the prediction of significant rainfall (Table \ref{table:scores_thresholds_4Zo-2MIo}).
@@
 
-When optimizing a method made of two levels of analogy, the introduction of moisture variables in the second level had an influence on the parameter values of the first level.
-It means that the two levels of analogy bring complementary information, and are thus not independent.
-This is first visible on the number $N_{1}$ of analogues to be selected on the first level, and on the selection of the pressure levels for the circulation analogy.
-If the change in the optimal value of $N_{1}$ was already known, a change of the optimal pressure levels for the circulation analogy has never been identified before.
+When optimizing a method consisting of two levels of analogy, the introduction of moisture variables in the second level has an influence on the parameter values of the first level.
+This means that the two levels of analogy bring complementary information, and are thus not independent.
+This is first visible in the number $N_{1}$ of analogues to be selected on the first level, and in the selection of the pressure levels for the circulation analogy.
+If the change in the optimal value of $N_{1}$ was already known, a change in the optimal pressure levels for the circulation analogy has never been identified before.
 
 As for the sequential procedure, the optimal value of $N_{1}$ increased when adding a second level of analogy (Figure \ref{fig:figure_nb_analogs}).
-One can also notice that the optimal number of analogues $N_{2}$ for the second level of analogy of 4Zo-2MIo was slightly inferior to $N_{1}$ from 4Zo, but very close.
-There is globally a common tendency between the optimal analogue number values of both methods: $N_{1}$ of the 4Zo method, and $N_{1}$ and $N_{2}$ of 4Zo-2MIo tend to be higher or lower altogether for a given region.
+One can also see that the optimal number of analogues $N_{2}$ for the second level of analogy of 4Zo-2MIo was slightly inferior to $N_{1}$ from 4Zo, but very close.
+There is a globally common tendency between the optimal analogue number values of both methods: $N_{1}$ of the 4Zo method, and $N_{1}$ and $N_{2}$ of 4Zo-2MIo tend to be higher or lower together for a given region.
 
@@
 
-As for the pressure levels, Z1000 that was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) was here less often chosen (once or even not at all) for 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}).
-There was indeed a vertical shift of the previously selected Z1000 for higher levels, that was even slightly stronger with four moisture predictors than with two.
-This change is likely due to the fact that when considering only the circulation analogy, the method tried to take into account information that can serve as proxy for moisture assessment, whereas it did not need it with the moisture index.
+As for the pressure levels, Z1000, which was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) was here less often chosen (once or even not at all) for 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}).
+There was indeed a vertical shift in the previously selected Z1000 for higher levels that was even slightly stronger with four moisture predictors than with two.
+This change is likely due to the fact that when considering only the circulation analogy, the method tried to take into account information that can serve as a proxy for moisture assessment, whereas it did not need it with the moisture index.
 This can only be assessed by a global optimization technique that can work jointly on both levels of analogy.
 
-The selected pressure levels for the analogy on the moisture index were strongly centered around 700~hPa and 600~hPa.
+The selected pressure levels for the analogy of the moisture index were strongly centred around 700~hPa and 600~hPa.
 No other value was selected when considering two moisture predictors (Table \ref{table:levels_GA_4Zo_2MIo}).
@@
 
-The selection of the temporal windows for the atmospheric circulation was similar to the preceding optimization (in the order of increasing pressure: 12~h, 24/30~h, 12~h, 30~h), but sometimes with some variability.
+The selection of temporal windows for atmospheric circulation was similar to the preceding optimization (in order of increasing pressure: 12~h, 24/30~h, 12~h, 30~h), but sometimes with some variability.
 When it comes to the moisture analogy, there was a clear tendency to select 12~h and 24~h.
-However, it must be remembered that this holds for our predictand, the accumulated precipitation over 06-30~h~UTC, and that it is expected to differ if the temporal window changes (e.g.
-00-24~h~UTC, or another accumulation duration).
+However, it must be remembered that this holds for our predictand, the accumulated precipitation over 06--30~h~UTC, and that it is expected to differ if the temporal window changes (e.g.
+00--24~h~UTC, or another accumulation duration).
 
 The optimized spatial windows for the atmospheric circulation have also changed (Figure \ref{fig:spatial_windows_4Zo-2MIo}).
-The very large domains on the upper level of the four first subregions were not present anymore, and more variability could be observed.
-The selected points for the moisture analogy were always located nearby the catchment, including at least one of the nearest points from the reanalysis dataset, and the spatial windows were relatively small.
-Thus, for this case study, there is no need to look for distant moisture information and the search could be reduced to a smaller domain.
+The very large domains on the upper level of the first four subregions were not present anymore, and more variability could be observed.
+The selected points for the moisture analogy were always located near the catchment, including at least one of the nearest points from the reanalysis dataset, and the spatial windows were relatively small.
+Thus, for this case study, there is no need to look for distant moisture information, and the search could be reduced to a smaller domain.
 
@@
 The optimized method also performed significantly better than the 2Z-2MI reference method optimized by the sequential procedure.
-When it comes to improvements for days with precipitation above the three thresholds (P\(\geq\)1~mm, P\(\geq\)0.1\(\cdot\)P10 and P\(\geq\)0.5\(\cdot\)P10), the conclusion is the same as before, that is a significant improvement of the prediction compared to the reference method, mainly for heavy rainfall.
+When it comes to improvements for days with precipitation above the three thresholds (P\(\geq\)1~mm, P \(\geq\) 0.1\(\cdot\)P10, and P \(\geq\) 0.5\(\cdot\)P10), the conclusion is the same as before, that is, a significant improvement in the prediction compared to the reference method, mainly for heavy rainfall.
 
-The analysis of the parameters cross-compatibility (Figure \ref{fig:crossing_4Zo-2MIo}) was also very similar to the one on the circulation analogy only.
+The analysis of the parameters’ cross-compatibility (Figure \ref{fig:crossing_4Zo-2MIo}) was also very similar to the one of the circulation analogy only.
 The same pattern could be observed, with a drop of performance for the subregions submitted to different meteorological influences.
-However, the losses of performance were globally more important than before, suggesting that more complex methods with moisture variables are less transposable to another subregion (consistent with the observations of \citet{Chardon2014}), even though both were located within the same grid cell of the reanalysis dataset.
+However, the losses in performance were globally more important than before, suggesting that more complex methods with moisture variables are less transposable to another subregion (consistent with the observations of \citet{Chardon2014}), even though both were located within the same grid cell of the reanalysis dataset.
 Moisture fields have greater variability than pressure fields, and thus a change in the spatial windows can have a greater impact on the method performance.
-Indeed, the two regions with the lowest cross-compatibility with the others were the Upper Rhone Valley (7) and the Southeast ridges (8), which had similar optimal pressure levels and temporal windows to other regions, but had rather different spatial windows on the moisture predictor.
+Indeed, the two regions with the lowest cross-compatibility with the others were the upper Rhone Valley (7) and the southeast ridges (8), which had similar optimal pressure levels and temporal windows to other regions, but had rather different spatial windows on the moisture predictor.
 
 Predictors based on moisture variables do significantly increase the prediction skill, and are thus recommended, as long as they are reliable.
-In real-time forecasting, their reliability depends on the lead time: for lead times superior to 3-4 days the uncertainties related to moisture variables from NWP models becomes fairly high, which reduces the relevance of methods relying on this information.
+In real-time forecasting, their reliability depends on the lead time: for lead times superior to 3--4 days, the uncertainties related to moisture variables from NWP models become fairly high, which reduces the relevance of methods relying on this information.
 In climate downscaling studies, it mainly depends on the coherence of the climatologies between the archive and the GCM model outputs.
-One should however not establish an AM with moisture variables for a too large region, as the transferability is reduced \citep[see][for alternative approaches]{Chardon2014}.
+One should, however, not establish an AM with moisture variables for too large a region, as the transferability is reduced \citep[see][for alternative approaches]{Chardon2014}.
 
@@
 This approach allowed us to differentiate the contributions to performance gains, as well as to identify possible over-parametrization.
-The main improvements obtained in the present case study are due to the following elementss:
+The main improvements obtained in the present case study are due to the following elements:
 
@@
 Beyond four, the validation score was more variable, revealing a loss in robustness due to over-parametrization.
-	\item The automatic and joint optimization of all parameters: the analogues number, the selection of the pressure levels and the temporal windows, and the spatial windows.
+	\item The automatic and joint optimization of all parameters: the analogue numbers, selection of pressure levels and temporal windows, and spatial windows.
 These parameters are highly interdependent, so one needs to optimize them jointly in order to identify optimal combinations.
-Indeed, there is a strong interdependence between space and time in the atmospheric circulation, so that e.g.
-the spatial window should move upstream the main atmospheric flow for earlier temporal windows.
+Indeed, there is a strong interdependence between space and time in the atmospheric circulation, so that, e.g.
+the spatial window should move upstream in the main atmospheric flow for earlier temporal windows.
 	\item The introduction of distinct spatial windows between pressure levels.
@@
 	\item The weighting of the analogy criteria between different pressure levels.
-It can be influenced by the variability of the geopotential height with altitude, or the levels significance in regards to the meteorological processes specific to a region.
-There is a trend for the weighting of circulation predictors to decrease with the increase in pressure, as one can see in Figure \ref{fig:levels_weights_average} for the three optimized methods.
-However, the values stayed around equity.
-This may not be the most influencing factor, and we may suggest to remove it first when trying to reduce the number of degrees of freedom.
-	\item The joint optimization of the circulation and moisture analogy levels, that are usually calibrated successively.
-We have been able to demonstrate that there is a dependency between the analogy levels, and that in order to approach the optimal parameters, one must consider them jointly.
+This can be influenced by the variability of the geopotential height with altitude, or the levels of significance in regards to the meteorological processes specific to a region.
+There is a trend in the weighting of circulation predictors to decrease with the increase in pressure, as one can see in Figure \ref{fig:levels_weights_average} for the three optimized methods.
+However, the values remained approximately equal.
+This may not be the most influencing factor, and we may suggest removing it first when trying to reduce the degrees of freedom.
+	\item The joint optimization of the circulation and moisture analogy levels, which are usually calibrated successively.
+We were able to demonstrate that there is a dependency between the analogy levels, and that in order to approach the optimal parameters, one must consider them jointly.
 \end{itemize}
 
-GAs have proved very useful to optimize complex variants of the AM, and to assess new degrees of freedom that were not available so far.
+GAs have proved very useful to optimize complex variants of the AM, and to assess new degrees of freedom that were not available thus far.
 However, it can be dangerous to add too many parameters to optimize.
 Indeed, the optimizer will probably use them to successfully improve the calibration score, so the validation control remains very important in order to determine if one is actually improving the method, or if it is being over-parametrized.
-Moreover, it might not always be desirable to increase the number of degrees of freedom, and some constraints (e.g.
+Moreover, it might not always be desirable to increase the degrees of freedom, and some constraints (e.g.
 same weighting of the analogy criteria between different pressure levels) can be justified.
 However, one should first assess the consequence of a constraint before establishing it.
-In this sense, even though not all degrees of freedom can be found useful, GAs allow assessing their influence.
-Finally, GAs could be used in order to identify e.g.
-the best couples of spatial and temporal windows, to later create a simpler regional method.
+In this sense, even though not all degrees of freedom are useful, GAs allow us to assess their influence.
+Finally, GAs could be used to identify, among other things, the best pairs of spatial and temporal windows, in order to later create a simpler regional method.
 
-The convergence of parallel optimizations decreased when the method to optimize became more and more complex.
+The convergence of parallel optimizations decreased when the optimization method became more and more complex.
 The optimizer did not always converge to the exact global optimum, but to its surroundings.
-This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that one has to stop it before the end, due to the required processing time (see Figure \ref{fig:evolution} as example).
-The resulting parameters might sometimes present non negligible differences, even though the score was almost similar.
-Through some Monte-Carlo analyses of the parameter space properties of the AM, \citet{Horton2012a} showed that some parameters of the method have a wide range of acceptable values.
+This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that one has to stop it before the end, because of the required processing time (see Figure \ref{fig:evolution} as an example).
+The resulting parameters might sometimes present non-negligible differences, even though the score is similar.
+Through Monte-Carlo analyses of the parameter space properties of the AM, \citet{Horton2012a} showed that some parameters of the method have a wide range of acceptable values.
 The spatial windows, for example, can be larger than the optimal size without much impact on the score, while they cannot be smaller \citep[see also][]{Bontron2004}.
-We could also observe that the selection of the pressure level is not a parameter as discrete as we would have thought, and that choosing another level may have reduced consequences on the performance.
-This is particularly true for higher pressure levels but can be more critical for lower layers.
-It was thus interesting to sometimes get several sets of near-optimal parameters, but with some nuances, in order to get an idea of the sensitivity of the parameters for a given region, and to compare the score on the VP.
+We also observed that the selection of pressure level is not a parameter as discrete as we would have thought, and that choosing another level may have reduced the consequences on the performance.
+This is particularly true for higher pressure levels, but can be more critical for lower layers.
+It was thus interesting to sometimes obtain several sets of near-optimal parameters, but with some nuances, in order to get an idea of the sensitivity of the parameters for a given region, and to compare the score for the VP.
 In this regard, a cross-validation technique may be advisable.
-However, as solutions identified at different regions of the parameters space might provide sufficiently good performance, an ensemble of these could be used, instead of a unique solution.
-These could account for the parameters uncertainty of the AM and increase the sample size contributing to the empirical distribution of precipitation values.
+However, as solutions identified at different regions of the parameter space might provide sufficiently good performance, an ensemble of these could be used, instead of a unique solution.
+These could account for the parameters’ uncertainty in the AM and increases in the sample size contributing to the empirical distribution of precipitation values.
 An approach that can also be recommended is to first explore a wide range of the parameter space with some optimizations, and to narrow it according to the results for more targeted optimizations that are likely to go faster and to perform better.
@@
 We tried to optimize the length of the preselection period (i.e.
-the seasonal stratification, which was a 4-month window until now) jointly with the other parameters, but no improvement was observed.
-Optimizing the moisture flux, which is composed of the moisture index multiplied with the wind flux, was also assessed.
+the seasonal stratification, which was a 4-month window leading up to the present ) jointly with the other parameters, but no improvement was observed.
+Optimizing the moisture flux, which is composed of the moisture index multiplied by the wind flux, was also assessed.
 However, the results were not better than when considering the moisture index alone.
@@
 
-As it has been observed, methods with a higher complexity that integrate moisture predictors are less transposable than simpler ones.
-It was also noticed in another unpublished work, that it is by far better to optimize for two subregions jointly rather than to optimize on one and to apply its parametrization to the other.
+As has been observed, methods with higher complexity that integrate moisture predictors are less transposable than simpler ones.
+It was also noticed in another unpublished work, that it is by far better to optimize for two subregions jointly than to optimize on one and to apply its parametrization to the other.
 Finally, the discretization in subregions is an important process and should be handled with care.
 Indeed, the geographical distance is not always the leading factor to define a subregion.
-For example, the Southeast ridges subregion do not behave like its surrounding and differ in its parametrization, due to different leading meteorological influences.
+For example, the southeast ridges subregion does not behave like its surroundings, and differs in its parametrization because of different leading meteorological influences.
 
-GAs are relatively heavy on processing and require an IT infrastructure capable of performing thousands hours of calculations.
-However, they automatically optimize all parameters of the AM, what is not possible with the sequential calibration.
-Therefore, much human time is saved, that was previously required to assess successively numerous combinations of parameters (particularly the selection of the pressure levels and the temporal windows).
-The ability to optimize jointly all parameters is important given the strong dependencies between them and between the levels of analogy.
+GAs are relatively heavy on processing and require an IT infrastructure capable of performing thousands of hours of calculations.
+However, they automatically optimize all parameters of the AM, which is not possible with sequential calibration.
+Therefore, much human time, previously required to successively assess numerous combinations of parameters (particularly the selection of pressure levels and temporal windows),is saved.
+The ability to jointly optimize all parameters is important given the strong dependencies between them and between the levels of analogy.
 
-Furthermore, AMs optimized with GAs showed an improvement of the prediction for days with heavier precipitation, including extremes.
+Furthermore, AMs optimized with GAs showed an improvement in predictions for days with heavier precipitation, including extremes.
 Even though no new extreme value was added to the existing precipitation archive, the distribution of analogue precipitation values for a target situation can move towards the targeted extreme by sampling better candidate situations.
 Then, the subset of precipitation values collected on the analogue dates can be considered as a sample of the conditional distribution of precipitation associated with this situation.
-A truncated exponential or a gamma distribution model can be fitted and extrapolated to extreme values not contained in the sample or even in the whole precipitation archive \citep{Obled2002}.
-Another possible approach is by combining AMs with other methods \citep[e.g.][]{Chardon2014}.
+A truncated exponential or a gamma distribution model can be fit and extrapolated to extreme values not contained in the sample or even in the whole precipitation archive \citep{Obled2002}.
+Another possible approach is to combine AMs with other methods \citep[e.g.][]{Chardon2014}.
 
@@
 
-The parameters resulting from the optimization by GAs were very consistent in terms of selection of the pressure levels, and the temporal and spatial windows.
-There were clear trends or even identical results for subregions under similar meteorological influences, which confirm that the optimized parameters were coherent, despite an eventual first impression of a great variability in the spatial windows.
+The parameters resulting from the optimization by GAs were very consistent in terms of the selection of pressure levels and temporal and spatial windows.
+There were clear trends or even identical results for subregions under similar meteorological influences, which confirm that the optimized parameters were coherent, despite an eventual first impression of great variability in the spatial windows.
 When adding moisture variables, the results showed a higher variability, but remained highly acceptable and coherent.
 
-Strong dependencies between the parameters of the AM could be observed.
+Strong dependencies between the parameters of the AM were observed.
 Thus, the sequential calibration, which optimizes the parameters successively, may not lead to the optimal combination.
-Moreover, it contains several manual systematic assessment, such as the selection of the pressure levels and the temporal windows.
-GAs, however, can select the pressure levels and the temporal windows automatically, which can save a considerable amount of human time.
+Moreover, it contains several manual systematic assessments, such as the selection of pressure levels and temporal windows.
+GAs, however, can automatically select pressure levels and temporal windows, which can save a considerable amount of human time.
 A great advantage of a global optimization is its ability to approach or reach optimal parameter values when they are considered jointly.
 
-A dependence in the selected parameters between the circulation analogy and the moisture variables was identified.
+A dependence in the selected parameters between the circulation analogy and moisture variables was identified.
 When the two analogy levels are considered together, the optimal parameters of the circulation analogy changed.
@@
 
-GAs provided parameterizations of AMs that exceeded the performance of the sequential calibration.
+GAs provided parameterizations of AMs that exceeded the performance of sequential calibration.
 In addition, it has been observed that the prediction for days with strong precipitation were improved to a greater extent, which is clearly interesting in the context of flood forecasting.
 
-This work is by far not exhaustive and means to open a door for new explorations of AMs with GAs.
-It is even possible to let the optimizer chose the meteorological variable to be used as predictor, as well as the analogy criteria, which is the topic of work in progress.
+This work is by no means exhaustive, and is meant to open a door to new explorations of AMs with GAs.
+It is even possible to let the optimizer chose the meteorological variable to be used as a predictor, as well as the analogy criteria, which is the topic of work in progress.
 Moreover, the AM has been explored for decades for precipitation prediction, but not as intensively for other predictands.
-A global optimizer, such as GAs, can speed up this assessment significantly.
+A global optimizer, such as a GA, can speed up this assessment significantly.
 
 \section*{Acknowledgments}
-Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of.
-Thanks to Renaud Marty for his fruitful collaboration over the years.
-Thanks to Dominique B\'{e}rod for his support.
+We thank Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he administers.
+We also thank Renaud Marty for fruitful collaboration over the years, and Dominique B\'{e}rod for his support.
 
-Thanks to the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton, the Water, Land and Sanitation Service of the Vaud Canton and the Swiss Federal Office for Environment (FOEV) who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
-The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
-NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.
-Precipitation time series provided by MeteoSwiss.
+We thank the Roads and Water courses Service, the Energy and Water Power Service of the Wallis Canton, the Water, Land and Sanitation Service of the Vaud Canton, and the Swiss Federal Office for Environment (FOEV) for financing the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
+Fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
+NCEP reanalysis data were provided by NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, via their website at http://www.esrl.noaa.gov/psd/.
+The precipitation time series were provided by MeteoSwiss.
 
-The authors would also like to acknowledge the work Loris Foresti and another anonymous reviewer, which contributed to improving this paper.
+The authors would also like to acknowledge the work of Loris Foresti and another anonymous reviewer, which contributed to improving this paper.
 
@@
 	\centerline{\includegraphics[width=8.8cm]{figures/fig01.pdf}}
-	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland. (source: Swisstopo)}
+	\caption{Location of alpine Rh\^{o}ne catchment in Switzerland. (source: Swisstopo)}
 	\label{fig:map}
@@
 	\centerline{\includegraphics[width=8.8cm]{figures/fig02.pdf}}
-	\caption{Performance score (CRPSS) on the CP and the VP for three stations (1 - Swiss Chablais; 5 - Southern valleys; 8 - Southeast ridges) when varying the number of geopotential height levels available to the optimizer.}
+	\caption{Performance score (CRPSS) for CP and VP for three stations (1 - Swiss Chablais; 5 - Southern valleys; 8 - Southeast ridges) when varying the number of geopotential height levels available to the optimizer.}
 	\label{fig:figure_nb_levels}
@@
 	\centerline{\includegraphics[width=8.4cm]{figures/fig03.pdf}}
-	\caption{Optimized spatial windows for the 4Zo method (analogy of the atmospheric circulation on four pressure levels).}
+	\caption{Optimized spatial windows for 4Zo method (analogy of atmospheric circulation on four pressure levels).}
 	\label{fig:spatial_windows_4Zo}
@@
 	\centerline{\includegraphics[width=8.8cm]{figures/fig04.pdf}}
-	\caption{Performance score (CRPSS) of the reference methods 2Z (Table \ref{table:params_R1}) and the optimized 4Zo method for the CP and the VP for every subregion.}
+	\caption{Performance score (CRPSS) of reference methods 2Z (Table \ref{table:params_R1}) and optimized 4Zo method for CP and VP for every subregion.}
 	\label{fig:figure_crpss_4Zo}
@@
 	\centerline{\includegraphics[width=8.4cm]{figures/fig05.pdf}}
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo, calibration and validation periods.}
+	\caption{Losses or gains (in \%) in CRPSS from applying optimized parameters for the series in columns to those in rows. Method 4Zo, calibration and validation periods.}
 	\label{fig:crossing_4Zo}
@@
 	\centerline{\includegraphics[width=8.4cm]{figures/fig06.pdf}}
-	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on four pressure levels and the analogy on the moisture index on two pressure levels).}
+	\caption{Optimized spatial windows for 4Zo-2MIo method (analogy of atmospheric circulation on four pressure levels and analogy on the moisture index on two pressure levels).}
 	\label{fig:spatial_windows_4Zo-2MIo}
@@
 	\centerline{\includegraphics[width=8.8cm]{figures/fig07.pdf}}
-	\caption{Performance score (CRPSS) of the reference methods 2Z-2MI (Table \ref{table:params_R2}) and the optimized 4Zo-2MIo method for the CP and the VP for every subregion.}
+	\caption{Performance score (CRPSS) of reference methods 2Z-2MI (Table \ref{table:params_R2}) and optimized 4Zo-2MIo method for CP and VP for every subregion.}
 	\label{fig:figure_crpss_4Zo-2HIo}
@@
 	\centerline{\includegraphics[width=8.8cm]{figures/fig08.pdf}}
-	\caption{Optimal numbers of analogues for the different regions and the two methods, resulting from the optimization.
-Method 4Zo is made of a single level of analogy with $N_{1}$ analogues, whereas 4Zo-2MIo has two levels of analogy with respectively $N_{1}$ and $N_{2}$ analogues.}
+	\caption{Optimal numbers of analogues for different regions and the two methods, resulting from optimization.
+Method 4Zo is made of a single level of analogy with $N_{1}$ analogues, whereas 4Zo-2MIo has two levels of analogy with $N_{1}$ and $N_{2}$ analogues.}
 	\label{fig:figure_nb_analogs}
@@
 	\centerline{\includegraphics[width=8.4cm]{figures/fig09.pdf}}
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo-2MIo, calibration and validation periods.}
+	\caption{Losses or gains (in \%) of the CRPSS from applying optimized parameters for the series in columns to those in rows. Method 4Zo-2MIo, calibration and validation periods.}*****
 	\label{fig:crossing_4Zo-2MIo}
@@
 	\centerline{\includegraphics[width=8.8cm]{figures/fig10.pdf}}
-	\caption{Distribution of the optimal weights for the predictors of the first level of analogy (geopotential heights) of the (blue) 4Zo, (red) 4Zo-2MIo, and (green) 4Zo-4MIo methods.
-The results are those of the ten subregions.
-The geopotential heights are sorted by increasing pressure and hour.}
+	\caption{Distribution of optimal weights for predictors of first level of analogy (geopotential heights) of (blue) 4Zo, (red) 4Zo-2MIo, and (green) 4Zo-4MIo methods.
+Results are for the ten subregions.
+Geopotential heights are sorted by increasing pressure and hour.}
 	\label{fig:levels_weights_average}
@@
 	\centerline{\includegraphics[width=7.5cm]{figures/fig11.pdf}}
-	\caption{Example of the evolution of the performance score of the best individual over 8 independent optimizations.}
+	\caption{Example of evolution of performance score of the best individual over eight independent optimizations.}
 	\label{fig:evolution}
@@
 \begin{table}[t]
-	\caption{Parameters of the reference method on the atmospheric circulation (2Z).
-The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation within the target day (temporal window).
-The criterion used for the current level of analogy is then provided, as well as the number of analogues.}
+	\caption{Parameters of reference method on atmospheric circulation (2Z).
+First column is level of analogy (0 for preselection); subsequent columns list meteorological variable, its hour of observation within the target day (temporal window), criterion used for current level of analogy, and number of analogues.}
 	\footnotesize
@@
 \begin{table}[t]
-	\caption{Parameters of the reference method with moisture variables (2Z-2MI). Same conventions as Table \ref{table:params_R1}}
+	\caption{Parameters of reference method with moisture variables (2Z-2MI). Conventions are the same as in Table \ref{table:params_R1}}
 	\footnotesize
@@
 \begin{table}[t]
-	\caption{Pressure levels ($\sim$) automatically selected for the 4Zo method at the different subregions (ID). R represents the 2Z reference method (Table \ref{table:params_R1}).}
+	\caption{Pressure levels ($\sim$) automatically selected for 4Zo method for different subregions (ID). R represents 2Z reference method (Table \ref{table:params_R1}).}
 	\footnotesize
@@
 \begin{table}[t]
-	\caption{Relative improvement (\%) of the CRPSS for different precipitation thresholds for the optimized 4Zo method, compared to the reference method.}
+	\caption{Relative improvement (\%) in CRPSS for different precipitation thresholds for optimized 4Zo method, compared to reference method.}
 	\footnotesize
@@
 \begin{table}[t]
-	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the moisture analogy ($\bullet$) of the 4Zo-2MIo method, at the different subregions (ID).
-R represents the 2Z-2MI reference method (Table \ref{table:params_R2})}
+	\caption{Atmospheric levels automatically selected for analogy of atmospheric circulation ($\sim$) and moisture analogy ($\bullet$) of 4Zo-2MIo method, for different subregions (ID).
+R represents 2Z-2MI reference method (Table \ref{table:params_R2})}
 	\footnotesize
@@
 \begin{table}[t]
-	\caption{Relative improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo-2MIo method, compared to the reference method.}
+	\caption{Relative improvement (\%) in CRPSS for different precipitations thresholds for optimized 4Zo-2MIo method, compared to reference method.}
 	\footnotesize

### 2017-01-23 Optimization case study - JoH/elsarticle-template.tex
Reordering figures.

@@
 	Analogue methods provide a statistical precipitation prediction based on synoptic predictors supplied by general circulation models or numerical weather prediction models.
-The method samples a selection of days in the archives that are similar to the target day to predict, and consider the set of their corresponding observed precipitation (the predictand) as the conditional distribution for the target day.
-The relationship between predictors and predictands relies on some parameters that characterize how and where the similitude between two atmospheric situations is defined.
+The method samples a selection of days in the archives that are similar to the target day to be predicted, and consider their set of corresponding observed precipitation (the predictand) as the conditional distribution for the target day.
+The relationship between the predictors and predictands relies on some parameters that characterize how and where the similarity between two atmospheric situations is defined.
 
-This relationship is usually established by a semi-automatic sequential procedure that has strong limitations: (i) it cannot automatically choose the pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters, and (iii) it cannot easily handle new degrees of freedom.
-In this work, a global optimization approach relying on genetic algorithms could optimize all parameters jointly and automatically.
-It allowed taking into account parameters inter-dependencies, and selecting objectively some parameters that were manually selected beforehand, which e.g.
-obviates the need of assessing a high number of combinations of the pressure levels and the temporal windows of the predictor variables.
+	This relationship is usually established by a semi-automatic sequential procedure that has strong limitations: (i) it cannot automatically choose the pressure levels and temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between parameters, and (iii) it cannot easily handle new degrees of freedom.
+In this work, a global optimization approach relying on genetic algorithms was able to optimize all parameters jointly and automatically.
+It allowed consideration of parameter inter-dependencies, and objective selection of some parameters that were manually selected beforehand, which obviates the need to assess a large number of combinations of pressure levels and temporal windows of predictor variables.
 
 	The global optimization was applied to some variants of the analogue method for the Rh\^{o}ne catchment in the Swiss Alps.
-The performance scores increased compared to reference methods, and this even to a greater extent for days with high precipitation totals.
+The performance scores increased compared to reference methods, especially for days with high precipitation totals.
 The resulting parameters were found to be relevant and coherent between the different subregions of the catchment.
-Moreover, they were obtained automatically and objectively, which reduces efforts invested in exploration attempts when adapting the method to a new region or for a new predictand.
-In addition, the approach allowed for new degrees of freedom, such as a possible weighting between the pressure levels, and non overlapping spatial windows.
+Moreover, they were obtained automatically and objectively, which reduces the effort that needs to be invested in exploration attempts when adapting the method to a new region or for a new predictand.
+In addition, the approach allowed for new degrees of freedom, such as a possible weighting between pressure levels, and non-overlapping spatial windows.
 \end{abstract}
@@
 
-The analogue method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1956, Lorenz1969} that similar situations in terms of the atmospheric circulation are likely to lead to similar local weather \citep{Duband1970}.
+The analogue method (AM) is a downscaling technique based on the idea expressed by \citet{Lorenz1956, Lorenz1969} that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Duband1970}.
 It uses predictor variables describing the synoptic atmospheric circulation in order to predict local-scale predictands of interest.
-It is often used to predict daily precipitation, either in an operational forecasting context \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Horton2016a, Hamill2015, BenDaoud2016} or a climate downscaling context \citep[e.g.,][]{Radanovics2013, Chardon2014, Dayon2015, Raynaud2016b}.
+It is often used to predict daily precipitation, either in an operational forecasting context \citep[e.g.][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Horton2016a, Hamill2015, BenDaoud2016} or a climate downscaling context \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015, Raynaud2016b}.
 Other predictands are also considered, such as precipitation radar images \citep{Panziera2011,Foresti2015a}, temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016, Raynaud2016b}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, and radiation \citep{Bois1981, Raynaud2016b}.
 
-In real-time forecasting, it is used mainly by practitioners, notably hydropower companies or flood forecasting services.
-They need to anticipate water yields or to issue early flood warnings several days in advance.
-The classical forecasting chain consists in using limited area models (e.g.
+In real-time forecasting, it is used mainly by practitioners, notably hydropower companies or flood forecasting services, that need to anticipate water yields or issue early flood warnings several days in advance.
+The classical forecasting chain consists of using limited area models (e.g.
 AROME, or COSMO) forced by global NWP (numerical weather prediction) models with a lower resolution.
-However, their use require very important processing capacities, and the resulting forecast still present large uncertainties and biases.
+However, their use requires very important processing capacities, and the resulting forecast still presents large uncertainties and biases.
 Although these outputs are essential, they can be supplemented by other sources of forecasts providing useful information.
-In contrast to local NWP models, AMs can transform at low cost the synoptic-scale information provided by the global NWP model into precipitation forecasts, by using the natural local behavior in response to synoptic-scale influence stored in the archive of observed precipitation.
-Running an AM approach is so quick that it can search for analogues for every day up to ten days ahead, eventually for the different traces of an ensemble forecast and/or issued by different NWP models (e.g.
+In contrast to local NWP models, AMs can transform at low cost the synoptic-scale information provided by the global NWP model into precipitation forecasts, by using the natural local behaviour in response to synoptic-scale influences stored in the archive of observed precipitation.
+Running an AM approach is fast enough that it can search for analogues for each day, up to ten days ahead, eventually for the different traces of an ensemble forecast and/or those issued by different NWP models (e.g.
 NOAA-GFS or ECMWF-IFS), in a matter of minutes.
 
-In climate studies AMs are used to downscale the outputs of general circulation model (GCM) or regional climate models (RCMs) simulation runs \citep{Dayon2015} or to reconstruct past weather conditions \citep{Caillouet2016}.
+In climate studies, AMs are used to downscale the outputs of a general circulation model (GCM) or regional climate model (RCM) simulation runs \citep{Dayon2015} or to reconstruct past weather conditions \citep{Caillouet2016}.
 In future climate studies, RCMs are often used to dynamically downscale precipitation to a local scale.
-However, even though the relevance of RCMs'outputs increases, a bias correction of the outputs is still often required, particularly in complex terrain.
+However, even though the relevance of RCMs' outputs increases, a bias correction of the outputs is often still required, particularly in complex terrain.
 Moreover, their application is computer-intensive, which makes it difficult to cover all combinations of climate scenarios and GCMs.
-Therefore, the idea is to bypass the small scale simulations and to go from the large scale situation to the end variables like precipitation by statistical downscaling \citep{Maraun2010}.
+Therefore, the idea is to bypass the small-scale simulations and to go from the large-scale situation to the end variables such as precipitation by statistical downscaling \citep{Maraun2010}.
 
@@
 The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$.
-This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aimed at real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
+This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project, which aimed at real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}.
 Even though the region is rather small, the meteorological influences related to extreme weather conditions vary substantially within it \citep[see][]{Horton2012}.
-Indeed, a high spatial variability of the precipitation climatology exists, which is due to the complex orography of the region, and the mix of various meteorological influences.
-Based on different climatological analyses, the precipitation gauging stations in the catchment were clustered in ten subregions (Fig.\ \ref{fig:map}) :
+Indeed, a high spatial variability of precipitation climatology exists, which is due to the complex orography of the region, and the mix of various meteorological influences.
+Based on different climatological analyses, the precipitation gauge stations in the catchment were clustered in ten subregions (Fig.\ \ref{fig:map}):
 
@@
 to 6~a.m.
-the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008.
-The time series from every available gauging station were averaged over the ten subregions (Fig.\ \ref{fig:map}) of approximately 500~km$^{2}$ each in order to smooth local effects \citep{Obled2002, Marty2012}.
-It helps accounting for local variability, mainly when convective processes are involved, which increases slightly the prediction skill.
+the next day) measured at the MeteoSwiss network stations, for the period 1961--2008.
+The time series from every available gauge station were averaged over the ten subregions (Fig.\ \ref{fig:map}), which were approximately 500~km$^{2}$ each, in order to smooth local effects \citep{Obled2002, Marty2012}.
+This helps account for local variability, mainly when convective processes are involved, which slightly increases the prediction skill.
 
-It must be stressed that the predictand is here sa temporally cumulated variable, compared to the meteorological predictors, which may be considered instantaneous.
-Depending on the duration of the accumulation period (here 24~h, but could have been 6, 12~h, or more than 24~h), the choice of predictors will vary.
+It must be stressed that the predictand here is a temporally cumulated variable, compared to the meteorological predictors, which may be considered instantaneous.
+Depending on the duration of the accumulation period (here 24~h, but could have been 6~h, 12~h, or more than 24~h), the choice of predictors will vary.
 
-The 48 years precipitation dataset was divided into a calibration period (CP) and a validation period (VP).
-Using data independent from the CP to validate the results is very important in order to assess the robustness of the proposed improvements and to avoid over-parametrization of the method.
+The 48-yr precipitation dataset was divided into a calibration period (CP) and a validation period (VP).
+Using data independent of the CP to validate the results is very important in order to assess the robustness of the proposed improvements and to avoid over-parametrization of the method.
 
-In order to reduce potential bias related to trends linked to climate change or to the evolution in measurement techniques, the selection of the VP was evenly distributed over the entire series \citep{BenDaoud2010}.
-Thus, one year every six years was selected for validation, which represents a total of 8 years for the VP and 40 for CP.
-The choice of the sequence was made in order to have similar statistical characteristics between the CP and the VP.
+In order to reduce potential biases related to trends linked to climate change or to the evolution in measurement techniques, the selection of the VP was evenly distributed over the entire series \citep{BenDaoud2010}.
+Thus, one out of every six years was selected for validation, which represents a total of 8 years for the VP and 40 for the CP.
+This choice of sequence was made in order to have similar statistical characteristics between the CP and VP.
 
@@
 
-Multiple variations of the analogue method exist, and most of them will not be detailed hereafter \cite[see][for more comprehensive listings]{BenDaoud2016}.
-However, there are mainly two parameterizations that are most often used for precipitation prediction and that were considered as reference: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
+Multiple variations of the analogue method exist, most of which are not detailed here \cite[see][for a more comprehensive listing]{BenDaoud2016}.
+However, there are mainly two parameterizations that are most often used for precipitation prediction and that are considered as reference: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.
 
-The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): the similarity of the atmospheric circulation of a target date with every day of the archive is assessed by processing the S1 criterion \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window:
+The method based on the analogy of synoptic circulation consists of the following steps (Table \ref{table:params_R1}): the similarity of the atmospheric circulation of a target date with every day of the archive is assessed by processing the S1 criterion \citep[Eq.\ \ref{eq:S1}, ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window:
 
@@
 \citet{Bontron2005} show that the geopotential height at 500~hPa (Z500) and 1000~hPa (Z1000) are the best first predictors of the NCEP/NCAR reanalysis I dataset, and that the S1 criterion performs better than scores based on absolute distances.
-The reason for such better results is that the S1 criterion allows comparing the circulation patterns, by means of the gradients, rather than the absolute value of the geopotential height, which represent better the flow direction.
-To cope with seasonal effects, candidate dates are extracted within a period of four months centered around the target date, for every year of the archive.
-This method using two geopotential heights will be named 2Z.
+The reason for such better results is that the S1 criterion allows comparison of the circulation patterns, by means of the gradients, rather than the absolute value of the geopotential height, which better represent the flow direction.
+To cope with seasonal effects, candidate dates are extracted within a period of four months centred around the target date, for every year of the archive.
+This method using two geopotential heights is named here 2Z.
 
@@
 where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value 1 otherwise.
-The mean CRPS is averaged on the calibration, respectively the validation periods, on all days.
 
-In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution of precipitation from the entire archive as the reference.
-The CRPSS (Continuous Ranked Probability Skill Score) is thus defined as following:
+In order to compare the value of the score relative to a reference, one often considers its skill score expression, and uses the climatological distribution of precipitation from the entire archive as the reference.
+The CRPSS (Continuous Ranked Probability Skill Score) is thus defined as follows:
 
@@
 	\end{enumerate}
-	\item A new level of analogy can then be added, based on other variables (such as the moisture index) with chosen pressure levels, temporal windows, and initial number of analogues $N_{2}$.
+	\item A new level of analogy can then be added, based on other variables (such as the moisture index) with some chosen pressure levels, temporal windows, and initial number of analogues $N_{2}$.
 The procedure starts again from step 2 (calibration of the spatial window and the number of analogues) for the new level.
@@
 Genetic algorithms (GAs) were developed by \citet{Holland1992b} and \citet{Goldberg1989}.
-They are part of Evolutionary Algorithms \citep{Back1993b, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
-GAs seek the global optimum on a complex surface, theoretically without restriction, which is of interest for AMs, that are characterized by a complex high-dimensional error function having multiple local optima.
-Practically, GAs allow rapidly approaching satisfactory solutions, but they do not provide the optimum solution for sure \citep{Zitzler2004a}.
+They are part of the Evolutionary Algorithms \citep{Back1993b, Schwefel1993}, which were inspired by some mechanisms in biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
+GAs seek the global optimum on a complex surface, theoretically without restriction, which is of interest for AMs, which are characterized by a complex high-dimensional error function having multiple local optima.
+Practically, GAs allow rapidly approaching satisfactory solutions, but they are not guaranteed to provide the optimum solution \citep{Zitzler2004a}.
 It is indeed mainly a matter of time.
-When the optimizer gets closer to the global optimum, any new improvement takes more time to appear (see for example the slow-down of the improvements over generations in Figure \ref{fig:evolution}), and the final adjustment of the parameters can be very time consuming \citep{Back1993a}.
-For problems that require a significant amount of time in order to evaluate the objective function, as in the case of AMs (because it needs to make a prediction for every day of the CP), the number of generations has to be limited in order to get reasonable processing time.
+When the optimizer gets closer to the global optimum, any new improvement takes more time to appear, and the final adjustment of the parameters can be very time consuming \citep{Back1993a}.
+For problems that require a significant amount of time to evaluate the objective function, as in the case of AMs (because it needs to make a prediction for every day of the CP), the number of generations has to be limited in order to ensure a reasonable processing time.
 Thus, different acceptable solutions can result from one or more optimization runs \citep{Holland1992b}.
-This is both a strength and a weakness of GAs: they are very good at exploring complex parameter spaces in order to identify the most promising areas, but they will not necessarily always find the best solution with the optimal values of all parameters \citep{Holland1992b}.
+This is both a strength and a weakness of GAs: they are very good at exploring complex parameter spaces in order to identify the most promising areas, but they will not necessarily always find the best solution with the optimal values for all parameters \citep{Holland1992b}.
 
-The optimizations were here performed based on the recommended GAs parametrization for AMs as described in \citet{Horton2016}.
-As the optimization is mostly sensitive to the mutation operator (that randomly changes some values in the parameters sets), parallel optimizations are considered with variants of this operator, according to \citet{Horton2016}:
+The optimizations here were performed based on the recommended GA parametrization for AMs as described in \citet{Horton2016}.
+As the optimization is mostly sensitive to the mutation operator (that randomly changes some values in the parameter sets), parallel optimizations are considered with variants of this operator, according to \citet{Horton2016}:
 
 \begin{itemize}
-	\item 3x non-uniform mutation \citep{Michalewicz1996} with varying parameters,
-	\item 1x multi-scale mutation \citep{Horton2016},
-	\item 2x chromosome of adaptive search radius \citep{Horton2016}
+	\item 3x non-uniform mutation \citep{Michalewicz1996} with varying parameters
+	\item 1x multi-scale mutation \citep{Horton2016}
+	\item 2x chromosome of adaptive search radius \citep{Horton2016}.
 \end{itemize}
@@
 A population size of 500 individuals (i.e.
-parameter sets of the AM to be detailed hereunder) was considered, and the optimization was stopped when the best individual (with the highest CRPSS performance score) did not evolve for 20 generations (cycles of the optimization).
+parameter sets of the AM to be detailed below) was considered, and the optimization was stopped when the best individual (with the highest CRPSS performance score) did not evolve for 20 generations (cycles of optimization).
 
@@
 The addition of circulation predictors globally improved the prediction skill (for both the CP and the VP) only up to four predictors (Figure \ref{fig:figure_nb_levels}).
-Afterwards, the score on the VP was more variable, showing eventually even a decrease, which revealed an over-parametrization of the method, and thus a lack of robustness.
-After four predictors, the score on the CP did not increase substantially, and could even present some local decrease due to increasing difficulty for the optimizer to converge.
+Afterwards, the score on the VP was more variable, eventually even showing a decrease, which revealed an over-parametrization of the method, and thus a lack of robustness.
+After four predictors, the score for the CP did not increase substantially, and even presented a local decrease due to increasing difficulty for the optimizer to converge.
 Selecting four circulation predictors (geopotential heights) was considered optimal for this case study, since the gain in CRPSS was significant, and the model remained relatively simple.
-It cannot be excluded that another number would prevail in another region than the upper Rh\^{o}ne catchment, under other meteorological conditions, or with another reanalysis dataset.
+It cannot be ruled out that another number would prevail in a region other than the upper Rh\^{o}ne catchment, under other meteorological conditions, or with another reanalysis dataset.
 
-\subsection{Which parameters are optimized ?}
+\subsection{Which parameters are optimized?}
 
-The chosen method for the atmospheric circulation analogy, based on four circulation predictors (geopotential heights), and that will be named 4Zo (o for optimized), was made of the following degrees of freedom:
+The chosen method for the atmospheric circulation analogy, based on four circulation predictors (geopotential heights), and which is here named 4Zo (o for optimized), was based on the following degrees of freedom:
 
@@
 	\setlength\itemsep{-4px}
-	\item the selection of the pressure levels (4 degrees),
-	\item the temporal windows (4 degrees),
-	\item the spatial windows (4x4 degrees),
-	\item the weights (4 degrees),
-	\item the number of analogues (1 degree).
+	\item selection of pressure levels (4 degrees)
+	\item temporal windows (4 degrees)
+	\item spatial windows (4 x 4 degrees)
+	\item weights (4 degrees)
+	\item number of analogues (1 degree).
 \end{itemize}
 
-This sums up to 29 degrees of freedom that were optimized simultaneously.
+This adds up to 29 degrees of freedom that were optimized simultaneously.
 
@@
 For most subregions, the second level (Z700) was compared on thin and longitudinally extended spatial windows.
-The third level (Z1000 at 6 or 12~h) also had longitudinally extended domains, but a bit larger.
+The third level (Z1000 at 6 or 12~h) also had longitudinally extended domains, which were slightly larger.
 The last one (Z1000 at 30~h) had rather large and squared windows.
-Subregions number 5 (Southern valleys) and 6 (Southern ridges) had exactly the same spatial windows, which suggest that they behave in a similar way and thus could have been merged.
+Subregions number 5 (southern valleys) and 6 (southern ridges) had exactly the same spatial windows, which suggests that they behave in a similar way and thus could have been merged.
 This similarity is a good sign for the accuracy of the optimized parameters.
 
-The performance scores showed non-negligible improvements for both the CP and the VP (Figure \ref{fig:figure_crpss_4Zo}) compared to the 2Z reference method optimized by the sequential procedure.
+The performance scores showed non-negligible improvements for both the CP and VP (Figure \ref{fig:figure_crpss_4Zo}) compared to the 2Z reference method optimized by the sequential procedure.
 Even more interestingly, the results for higher precipitation thresholds (Table \ref{table:scores_thresholds_4Zo}) showed the largest improvements.
 This is of particular interest in the framework of flood forecasting.
-The further improvement of days with higher precipitation totals is likely related to the fact that larger values contribute more to the CRPS score, which means that better predicting these days results in significant increase of the global performance score.
+The further improvement of days with higher precipitation totals is likely related to the fact that larger values contribute more to the CRPS score, which means that better predicting these days results in significant increase in the global performance score.
 
-The analysis of the parameters cross-compatibility showed that obviously the parameters were optimal on the CP for the subregion for which they were optimized (Figure \ref{fig:crossing_4Zo} top).
-However, the losses in CRPSS when exchanging the parameters were not of the same magnitude between the different subregions.
-Indeed, the Upper Rhone Valley (7) and moreover the Southeast ridges (8) seemed to behave significantly differently.
-These two regions have different climatic properties than the others as they are particularly sensitive to southerly flows.
-Indeed, almost all heavy precipitation events occurred under a southerly regime, such as in the Liguria, Piedmont and Aosta regions in Italy, whereas the other subregions of the catchment had extreme events mainly under a westerly regime \citep{Horton2012}.
+The analysis of the parameters’ cross-compatibility showed that the parameters were obviously optimal on the CP for the subregion for which they were optimized (Figure \ref{fig:crossing_4Zo} top).
+However, the losses in CRPSS when exchanging the parameters were not of the same magnitude among the different subregions.
+Indeed, the Upper Rhone Valley (7) and, moreover, the southeast ridges (8) seemed to behave significantly differently.
+These two regions have different climatic properties than the others, as they are particularly sensitive to southerly flows.
+Indeed, almost all heavy precipitation events occurred under a southerly regime, such as in the Liguria, Piedmont, and Aosta regions in Italy, whereas the other subregions of the catchment had extreme events mainly under a westerly regime \citep{Horton2012}.
 Thus, as the performance score is significantly influenced by heavy precipitation values, the parameters for the different subregions are likely optimized to better predict these days.
-It can then be expected that the optimal parameters differ between these two subregions and the other ones.
-This points at the importance of taking into account leading meteorological influences during precipitation stations clustering, that are not always best represented by the geographical distance.
+It can then be expected that the optimal parameters differ between these two subregions and the others.
+This points at the importance of taking into account leading meteorological influences during precipitation station clustering, which are not always best represented by geographical distance.
 
-Globally, the same cross-compatibility structure could be observed for the VP (Figure \ref{fig:crossing_4Zo} bottom), but in this case, minor improvements were occasionally observed when crossing the parameters, due to the presence of other events in the VP that might be better predicted by a different parameter set.
-The relatively small differences in score between parameterizations indicated that even though the parameters might differ significantly, the performance might not be drastically affected.
-Even a change in the pressure level did not mean a radical drop of the score value.
+Globally, the same cross-compatibility structure could be observed for the VP (Figure \ref{fig:crossing_4Zo} bottom), but in this case, minor improvements were occasionally observed when crossing the parameters, because of the presence of other events in the VP that might be better predicted by a different parameter set.
+The relatively small differences in scores between parameterizations indicated that even though the parameters might differ significantly, the performance might not be drastically affected.
+Even a change in the pressure level did not mean a radical drop in the score value.
 A different parametrization may lead to a distinct selection of analogue days, and thus to an improvement of the prediction under certain weather conditions at the expense of others.
@@
 
-The optimization was processed on both levels of analogy simultaneously. This implies that the analogy of the atmospheric circulation could change due to the new moisture information.
+The optimization was processed on both levels of analogy simultaneously. This implies that the analogy of the atmospheric circulation could change because of the new moisture information.
 
@@
 
-As previously, the optimized parameters differed from one subregion to another, and this even to a greater extent.
-The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_4Zo-2MIo} for 4Zo-2MIo, along with the selected pressure levels for both the circulation and the moisture analogy (Table \ref{table:levels_GA_4Zo_2MIo}).
+As seen previously, the optimized parameters differed from one subregion to another, but to an even greater extent.
+The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_4Zo-2MIo} for 4Zo-2MIo, along with the selected pressure levels for both the circulation and moisture analogy (Table \ref{table:levels_GA_4Zo_2MIo}).
 
-The CRPSS scores of the optimized 4Zo-2MIo method are provided in Figure \ref{fig:figure_crpss_4Zo-2HIo} and amounted in average to 40~\% (CP) and 40.3~\% (VP), compared to 35.2~\% (CP) and 36.2~\% (VP) for the reference method 2Z-2MI on the moisture analogy optimized with the sequential procedure.
-The parameters cross-compatibility are shown in Figure \ref{fig:crossing_4Zo-2MIo}.
+The CRPSS scores of the optimized 4Zo-2MIo method are provided in Figure \ref{fig:figure_crpss_4Zo-2HIo} and amounted on average to 40\% (CP) and 40.3\% (VP), compared to 35.2\% (CP) and 36.2\% (VP) for the reference method 2Z-2MI on the moisture analogy optimized with the sequential procedure.
+The parameters’ cross-compatibilities are shown in Figure \ref{fig:crossing_4Zo-2MIo}.
 As for 4Zo, the 4Zo-2MIo method presented larger improvements in the prediction of significant rainfall (Table \ref{table:scores_thresholds_4Zo-2MIo}).
@@
 Beyond four, the validation score was more variable, revealing a loss in robustness due to over-parametrization.
-	\item The automatic and joint optimization of all parameters: the analogues number, the selection of the pressure levels and the temporal windows, and the spatial windows.
+	\item The automatic and joint optimization of all parameters: the analogue numbers, selection of pressure levels and temporal windows, and spatial windows.
 These parameters are highly interdependent, so one needs to optimize them jointly in order to identify optimal combinations.
-Indeed, there is a strong interdependence between space and time in the atmospheric circulation, so that e.g.
+Indeed, there is a strong interdependence between space and time in the atmospheric circulation, so that, e.g.
 the spatial window should move upstream the main atmospheric flow for earlier temporal windows.
@@
 	\item The weighting of the analogy criteria between different pressure levels.
-It can be influenced by the variability of the geopotential height with altitude, or the levels significance in regards to the meteorological processes specific to a region.
-There is a trend for the weighting of circulation predictors to decrease with the increase in pressure, as one can see in Figure \ref{fig:levels_weights_average} for the three optimized methods.
-However, the values stayed around equity.
-This may not be the most influencing factor, and we may suggest to remove it first when trying to reduce the number of degrees of freedom.
-	\item The joint optimization of the circulation and moisture analogy levels, that are usually calibrated successively.
-We have been able to demonstrate that there is a dependency between the analogy levels, and that in order to approach the optimal parameters, one must consider them jointly.
+This can be influenced by the variability of the geopotential height with altitude, or the levels of significance in regards to the meteorological processes specific to a region.
+There is a trend in the weighting of circulation predictors to decrease with the increase in pressure, as one can see in Figure \ref{fig:levels_weights_average} for the three optimized methods.
+However, the values remained approximately equal.
+This may not be the most influencing factor, and we may suggest removing it first when trying to reduce the degrees of freedom.
+	\item The joint optimization of the circulation and moisture analogy levels, which are usually calibrated successively.
+We were able to demonstrate that there is a dependency between the analogy levels, and that in order to approach the optimal parameters, one must consider them jointly.
 \end{itemize}
 
-GAs have proved very useful to optimize complex variants of the AM, and to assess new degrees of freedom that were not available so far.
+GAs have proved very useful to optimize complex variants of the AM, and to assess new degrees of freedom that were not available thus far.
 However, it can be dangerous to add too many parameters to optimize.
 Indeed, the optimizer will probably use them to successfully improve the calibration score, so the validation control remains very important in order to determine if one is actually improving the method, or if it is being over-parametrized.
-Moreover, it might not always be desirable to increase the number of degrees of freedom, and some constraints (e.g.
+Moreover, it might not always be desirable to increase the degrees of freedom, and some constraints (e.g.
 same weighting of the analogy criteria between different pressure levels) can be justified.
 However, one should first assess the consequence of a constraint before establishing it.
-In this sense, even though not all degrees of freedom can be found useful, GAs allow assessing their influence.
-Finally, GAs could be used in order to identify e.g.
-the best couples of spatial and temporal windows, to later create a simpler regional method.
+In this sense, even though not all degrees of freedom are useful, GAs allow us to assess their influence.
+Finally, GAs could be used to identify, among other things, the best pairs of spatial and temporal windows, in order to later create a simpler regional method.
 
-The convergence of parallel optimizations decreased when the method to optimize became more and more complex.
+The convergence of parallel optimizations decreased when the AM to optimize became more and more complex.
 The optimizer did not always converge to the exact global optimum, but to its surroundings.
-This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that one has to stop it before the end, due to the required processing time (see Figure \ref{fig:evolution} as example).
-The resulting parameters might sometimes present non negligible differences, even though the score was almost similar.
-Through some Monte-Carlo analyses of the parameter space properties of the AM, \citet{Horton2012a} showed that some parameters of the method have a wide range of acceptable values.
+This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that one has to stop it before the end, because of the required processing time (see Figure \ref{fig:evolution} as an example).
+The resulting parameters might sometimes present non-negligible differences, even though the score is similar.
+Through Monte-Carlo analyses of the parameter space properties of the AM, \citet{Horton2012a} showed that some parameters of the method have a wide range of acceptable values.
 The spatial windows, for example, can be larger than the optimal size without much impact on the score, while they cannot be smaller \citep[see also][]{Bontron2004}.
-We could also observe that the selection of the pressure level is not a parameter as discrete as we would have thought, and that choosing another level may have reduced consequences on the performance.
-This is particularly true for higher pressure levels but can be more critical for lower layers.
-It was thus interesting to sometimes get several sets of near-optimal parameters, but with some nuances, in order to get an idea of the sensitivity of the parameters for a given region, and to compare the score on the VP.
+We also observed that the selection of pressure level is not a parameter as discrete as we would have thought, and that choosing another level may have reduced the consequences on the performance.
+This is particularly true for higher pressure levels, but can be more critical for lower layers.
+It was thus interesting to sometimes obtain several sets of near-optimal parameters, but with some nuances, in order to get an idea of the sensitivity of the parameters for a given region, and to compare the score for the VP.
 In this regard, a cross-validation technique may be advisable.
-However, as solutions identified at different regions of the parameters space might provide sufficiently good performance, an ensemble of these could be used, instead of a unique solution.
-These could account for the parameters uncertainty of the AM and increase the sample size contributing to the empirical distribution of precipitation values.
+However, as solutions identified at different regions of the parameter space might provide sufficiently good performance, an ensemble of these could be used, instead of a unique solution.
+These could account for the parameters’ uncertainty in the AM, and could also increase the sample size contributing to the empirical distribution of precipitation values.
 An approach that can also be recommended is to first explore a wide range of the parameter space with some optimizations, and to narrow it according to the results for more targeted optimizations that are likely to go faster and to perform better.
@@
 We tried to optimize the length of the preselection period (i.e.
-the seasonal stratification, which was a 4-month window until now) jointly with the other parameters, but no improvement was observed.
-Optimizing the moisture flux, which is composed of the moisture index multiplied with the wind flux, was also assessed.
+the seasonal stratification, which is a 4-month window) jointly with the other parameters, but no improvement was observed.
+Optimizing the moisture flux, which is composed of the moisture index multiplied by the wind flux, was also assessed.
 However, the results were not better than when considering the moisture index alone.
@@
 
-As it has been observed, methods with a higher complexity that integrate moisture predictors are less transposable than simpler ones.
-It was also noticed in another unpublished work, that it is by far better to optimize for two subregions jointly rather than to optimize on one and to apply its parametrization to the other.
+As has been observed, methods with higher complexity that integrate moisture predictors are less transposable than simpler ones.
+It was also noticed in another unpublished work, that it is by far better to optimize for two subregions jointly than to optimize on one and to apply its parametrization to the other.
 Finally, the discretization in subregions is an important process and should be handled with care.
 Indeed, the geographical distance is not always the leading factor to define a subregion.
-For example, the Southeast ridges subregion do not behave like its surrounding and differ in its parametrization, due to different leading meteorological influences.
+For example, the southeast ridges subregion does not behave like its surroundings, and differs in its parametrization because of different leading meteorological influences.
 
-GAs are relatively heavy on processing and require an IT infrastructure capable of performing thousands hours of calculations.
-However, they automatically optimize all parameters of the AM, what is not possible with the sequential calibration.
-Therefore, much human time is saved, that was previously required to assess successively numerous combinations of parameters (particularly the selection of the pressure levels and the temporal windows).
-The ability to optimize jointly all parameters is important given the strong dependencies between them and between the levels of analogy.
+GAs are relatively heavy on processing and require an IT infrastructure capable of performing thousands of hours of calculations.
+However, they automatically optimize all parameters of the AM, which is not possible with the sequential calibration.
+Therefore, much human time, previously required to successively assess numerous combinations of parameters (particularly the selection of pressure levels and temporal windows), is saved.
+The ability to jointly optimize all parameters is important given the strong dependencies between them and between the levels of analogy.
 
-Furthermore, AMs optimized with GAs showed an improvement of the prediction for days with heavier precipitation, including extremes.
+Furthermore, AMs optimized with GAs showed an improvement in predictions for days with heavier precipitation, including extremes.
 Even though no new extreme value was added to the existing precipitation archive, the distribution of analogue precipitation values for a target situation can move towards the targeted extreme by sampling better candidate situations.
 Then, the subset of precipitation values collected on the analogue dates can be considered as a sample of the conditional distribution of precipitation associated with this situation.
-A truncated exponential or a gamma distribution model can be fitted and extrapolated to extreme values not contained in the sample or even in the whole precipitation archive \citep{Obled2002}.
-Another possible approach is by combining AMs with other methods \citep[e.g.][]{Chardon2014}.
+A truncated exponential or a gamma distribution model can be fit and extrapolated to extreme values not contained in the sample or even in the whole precipitation archive \citep{Obled2002}.
+Another possible approach is to combine AMs with other methods \citep[e.g.][]{Chardon2014}.
 
@@
 
-This work is by far not exhaustive and means to open a door for new explorations of AMs with GAs.
-It is even possible to let the optimizer chose the meteorological variable to be used as predictor, as well as the analogy criteria, which is the topic of work in progress.
+This work is by no means exhaustive, and is meant to open a door to new explorations of AMs with GAs.
+It is even possible to let the optimizer chose the meteorological variable to be used as a predictor, as well as the analogy criteria, which is the topic of work in progress.
 Moreover, the AM has been explored for decades for precipitation prediction, but not as intensively for other predictands.
-A global optimizer, such as GAs, can speed up this assessment significantly.
+A global optimizer, such as a GA, can speed up this assessment significantly.
 
 \section*{Acknowledgments}
-Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of.
-Thanks to Renaud Marty for his fruitful collaboration over the years.
-Thanks to Dominique B\'{e}rod for his support.
+We thank Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he administers.
+We also thank Renaud Marty for fruitful collaboration over the years, and Dominique B\'{e}rod for his support.
 
-Thanks to the Roads and Water courses Service, Energy and Water Power Service of the Wallis Canton, the Water, Land and Sanitation Service of the Vaud Canton and the Swiss Federal Office for Environment (FOEV) who financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
-The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
-NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/.
-Precipitation time series provided by MeteoSwiss.
+We thank the Roads and Water courses Service, the Energy and Water Power Service of the Wallis Canton, the Water, Land and Sanitation Service of the Vaud Canton, and the Swiss Federal Office for Environment (FOEV) for financing the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
+Fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
+NCEP reanalysis data were provided by NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, via their website at http://www.esrl.noaa.gov/psd/.
+The precipitation time series were provided by MeteoSwiss.
 
-The authors would also like to acknowledge the work Loris Foresti and another anonymous reviewer, which contributed to improving this paper.
+The authors would also like to acknowledge the work of Loris Foresti and another anonymous reviewer, which contributed to improving this paper.
 
@@
 	\centerline{\includegraphics[width=8.8cm]{figures/fig04.pdf}}
-	\caption{Performance score (CRPSS) of the reference methods 2Z (Table \ref{table:params_R1}) and the optimized 4Zo method for the CP and the VP for every subregion.}
+	\caption{Performance score (CRPSS) of the reference method 2Z (Table \ref{table:params_R1}) and the optimized 4Zo method for CP and VP for every subregion.}
 	\label{fig:figure_crpss_4Zo}
@@
 	\centerline{\includegraphics[width=8.4cm]{figures/fig06.pdf}}
-	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on four pressure levels and the analogy on the moisture index on two pressure levels).}
+	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on four pressure levels and analogy on the moisture index on two pressure levels).}
 	\label{fig:spatial_windows_4Zo-2MIo}
@@
 	\centerline{\includegraphics[width=8.8cm]{figures/fig07.pdf}}
-	\caption{Performance score (CRPSS) of the reference methods 2Z-2MI (Table \ref{table:params_R2}) and the optimized 4Zo-2MIo method for the CP and the VP for every subregion.}
+	\caption{Performance score (CRPSS) of the reference method 2Z-2MI (Table \ref{table:params_R2}) and the optimized 4Zo-2MIo method for CP and VP for every subregion.}
 	\label{fig:figure_crpss_4Zo-2HIo}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig08.pdf}}
-	\caption{Optimal numbers of analogues for the different regions and the two methods, resulting from the optimization.
-Method 4Zo is made of a single level of analogy with $N_{1}$ analogues, whereas 4Zo-2MIo has two levels of analogy with respectively $N_{1}$ and $N_{2}$ analogues.}
+	\centerline{\includegraphics[width=8.4cm]{figures/fig08.pdf}}
+	\caption{Losses or gains (in \%) of the CRPSS from applying optimized parameters for the series in columns to those in rows. Method 4Zo-2MIo, calibration and validation periods.}
+	\label{fig:crossing_4Zo-2MIo}
+\end{figure}
+
+\begin{figure}[t]
+	\centerline{\includegraphics[width=8.8cm]{figures/fig09.pdf}}
+	\caption{Optimal numbers of analogues for the different regions and the two methods, resulting from optimization.
+Method 4Zo is made of a single level of analogy with $N_{1}$ analogues, whereas 4Zo-2MIo has two levels of analogy with $N_{1}$ and $N_{2}$ analogues.}
 	\label{fig:figure_nb_analogs}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.4cm]{figures/fig09.pdf}}
-	\caption{Losses or gains (in \%) of the CRPSS by applying the optimized parameters for the series in column to those in line. Method 4Zo-2MIo, calibration and validation periods.}
-	\label{fig:crossing_4Zo-2MIo}
-\end{figure}
-
-\begin{figure}[t]
 	\centerline{\includegraphics[width=8.8cm]{figures/fig10.pdf}}
-	\caption{Distribution of the optimal weights for the predictors of the first level of analogy (geopotential heights) of the (blue) 4Zo, (red) 4Zo-2MIo, and (green) 4Zo-4MIo methods.
-The results are those of the ten subregions.
-The geopotential heights are sorted by increasing pressure and hour.}
+	\caption{Distribution of optimal weights for the predictors of the first level of analogy (geopotential heights) of (blue) 4Zo, (red) 4Zo-2MIo, and (green) 4Zo-4MIo methods.
+Results are for the ten subregions.
+Geopotential heights are sorted by increasing pressure and hour.}
 	\label{fig:levels_weights_average}
@@
 	\centerline{\includegraphics[width=7.5cm]{figures/fig11.pdf}}
-	\caption{Example of the evolution of the performance score of the best individual over 8 independent optimizations.}
+	\caption{Example of evolution of the performance score of the best individual over eight independent optimizations.}
 	\label{fig:evolution}
@@
 \begin{table}[t]
-	\caption{Parameters of the reference method on the atmospheric circulation (2Z).
-The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation within the target day (temporal window).
-The criterion used for the current level of analogy is then provided, as well as the number of analogues.}
+	\caption{Parameters of the reference method on atmospheric circulation (2Z).
+First column is level of analogy (0 for preselection); subsequent columns list meteorological variable, its hour of observation within the target day (temporal window), criterion used for current level of analogy, and number of analogues.}
 	\footnotesize
@@
 \begin{table}[t]
-	\caption{Parameters of the reference method with moisture variables (2Z-2MI). Same conventions as Table \ref{table:params_R1}}
+	\caption{Parameters of the reference method with moisture variables (2Z-2MI). Conventions are the same as in Table \ref{table:params_R1}}
 	\footnotesize
@@
 \begin{table}[t]
-	\caption{Pressure levels ($\sim$) automatically selected for the 4Zo method at the different subregions (ID). R represents the 2Z reference method (Table \ref{table:params_R1}).}
+	\caption{Pressure levels ($\sim$) automatically selected for the 4Zo method for different subregions (ID). R represents the 2Z reference method (Table \ref{table:params_R1}).}
 	\footnotesize
@@
 \begin{table}[t]
-	\caption{Relative improvement (\%) of the CRPSS for different precipitation thresholds for the optimized 4Zo method, compared to the reference method.}
+	\caption{Relative improvement (\%) in CRPSS for different precipitation thresholds for the optimized 4Zo method, compared to the reference method.}
 	\footnotesize
@@
 \begin{table}[t]
-	\caption{Atmospheric levels automatically selected for the analogy of the atmospheric circulation ($\sim$) and the moisture analogy ($\bullet$) of the 4Zo-2MIo method, at the different subregions (ID).
+	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation ($\sim$) and moisture analogy ($\bullet$) of the 4Zo-2MIo method, for different subregions (ID).
 R represents the 2Z-2MI reference method (Table \ref{table:params_R2})}
@@
 \begin{table}[t]
-	\caption{Relative improvement (\%) of the CRPSS for different precipitations thresholds for the optimized 4Zo-2MIo method, compared to the reference method.}
+	\caption{Relative improvement (\%) in CRPSS for different precipitations thresholds for the optimized 4Zo-2MIo method, compared to the reference method.}
 	\footnotesize

### 2017-01-23 Optimization case study - JoH/elsarticle-template.tex
Updating figures sizes.

@@
 The optimizer did not always converge to the exact global optimum, but to its surroundings.
-This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that one has to stop it before the end, because of the required processing time (see Figure \ref{fig:evolution} as an example).
+This is related to the fact that the optimization slows down when it gets closer to the global optimum, and that one has to stop it before the end, because of the required processing time (see for example the slow-down of the improvements over generations in Figure \ref{fig:evolution}).
 The resulting parameters might sometimes present non-negligible differences, even though the score is similar.
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig01.pdf}}
+	\centerline{\includegraphics[width=9cm]{figures/fig01.pdf}}
 	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland. (source: Swisstopo)}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig02.pdf}}
+	\centerline{\includegraphics[width=9cm]{figures/fig02.pdf}}
 	\caption{Performance score (CRPSS) for CP and VP for three stations (1 - Swiss Chablais; 5 - Southern valleys; 8 - Southeast ridges) when varying the number of geopotential height levels available to the optimizer.}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig04.pdf}}
+	\centerline{\includegraphics[width=9cm]{figures/fig04.pdf}}
 	\caption{Performance score (CRPSS) of the reference method 2Z (Table \ref{table:params_R1}) and the optimized 4Zo method for CP and VP for every subregion.}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig07.pdf}}
+	\centerline{\includegraphics[width=9cm]{figures/fig07.pdf}}
 	\caption{Performance score (CRPSS) of the reference method 2Z-2MI (Table \ref{table:params_R2}) and the optimized 4Zo-2MIo method for CP and VP for every subregion.}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig09.pdf}}
+	\centerline{\includegraphics[width=9cm]{figures/fig09.pdf}}
 	\caption{Optimal numbers of analogues for the different regions and the two methods, resulting from optimization.
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.8cm]{figures/fig10.pdf}}
+	\centerline{\includegraphics[width=9cm]{figures/fig10.png}}
 	\caption{Distribution of optimal weights for the predictors of the first level of analogy (geopotential heights) of (blue) 4Zo, (red) 4Zo-2MIo, and (green) 4Zo-4MIo methods.

### 2017-03-17 Moving temporal window - HESS/template.tex
Removing some references from the intro.

@@
 The AMs are used for operational precipitation forecasting, either in the context of weather forecasting, flood forecasting, or hydropower production \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as for precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}.
-Other applications focus on temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectories of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.
+Other applications focus on temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}.
 
@@
 \ref{sec:old_reanalysis}).
+
+	\citep{Poli2016}
 

### 2017-03-21 Moving temporal window - HESS/template.tex
Updating the MTW figures.

@@
 
-	Synoptic-scale variables, used as predictors, were extracted from the NCEP/NCAR reanalysis 1 dataset \citep{Kalnay1996} with a 6h temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\textdegree.
-This dataset is now relatively old, but it is not expected to affect the conclusions of the present study (see discussion in Sect.
-\ref{sec:old_reanalysis}).
-
-	\citep{Poli2016}
+	Synoptic-scale variables, used as predictors, were extracted from the ERA-20C reanalysis dataset \citep{Poli2016} with a 3h temporal resolution, and a spatial resolution of 1\textdegree.
+The study was originally performed on the NCEP/NCAR reanalysis 1 dataset \citep{Kalnay1996}, and the conclusions were similar.
+The main advantage of the ERA-20C is that it allows testing the relevance of the MTW at a 3h time step.
 
@@
 However, the competition between the loss of performance due to a smaller archive length and the potentially better analogy between target and MTW candidates needs to be assessed.
-
-	\subsection{Reconstruction of a longer precipitation archive}
-	\label{sec:reconstruction}
-
-	It would be profitable to be able to apply the MTW to a longer archive (here, 1961\textendash 2008), rather than being limited to the reduced period where the sub-daily precipitation data are available (cf.
-previous section).
-Therefore, in order to reconstruct a longer archive of moving 24h totals, two simple disaggregation approaches of the daily precipitation time series were assessed.
-
-	The first technique was a proportional distribution, where the observed daily precipitations were considered constant during the measuring period (6:00~UTC to 6:00~UTC the next day).
-Proportional parts of the original daily time series were allocated into a new moving average of 24h totals (Fig.
-\ref{fig:illustration_disaggregation}).
-
-	The second approach aimed at getting closer to the chronology of the actual precipitation by relying on some informative variables during the reconstruction procedure.
-Data from the NCEP/NCAR reanalysis 1 (Sect.
-\ref{sec:data}) were used for this purpose, despite their rough resolution (2.5\textdegree).
-Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and a time lapse between both series was allowed to take into account the significant distance separating the weather stations and the reanalysis grid point.
-The best proxy variable was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series over the period 1982\textendash 2007.
-Once the best proxy had been selected, its temporal profile was used in order to disaggregate the daily precipitation time series.
 
@@
 
-	\subsection{Consequences of the archive reduction}
-	\label{sec:archive_reduction}
-
-	The performance loss resulting from the reduction of a 47~year archive (1961\textendash 2008, corresponding to the daily time series) to 25~years (1982\textendash 2007, corresponding to the hourly time series in Sect.
-\ref{sec:mtw}) was assessed with the original method without MTW.
-Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
-The AM parameters were calibrated on the original archive (see resulting analogue numbers in Table \ref{table:analog_nb}) and were used thereafter.
-
-	The impact of the archive reduction can be seen in Fig.
-\ref{fig:plots_CRPSS_2Z} for the 2Z method and in Fig.
-\ref{fig:plots_CRPSS_2Z-2MI} for the 2Z-2MI method.
-As expected, a loss of performance was observed for each station, except for that of Aigle, which seemed relatively indifferent to this change.
-This loss was globally significant, with up to \textendash 1.89 points (\% of CRPSS) for Visp and the 2Z method.
-
 	\subsection{Influence of the MTW on the analogy criterion}
@@
 	\label{sec:discussion}
+
+	\subsection{Consequences of the archive reduction}
+	\label{sec:archive_reduction}
+
+	The performance loss resulting from the reduction of a 47~year archive (1961\textendash 2008, corresponding to the daily time series) to 25~years (1982\textendash 2007, corresponding to the hourly time series in Sect.
+\ref{sec:mtw}) was assessed with the original method without MTW.
+Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
+The AM parameters were calibrated on the original archive (see resulting analogue numbers in Table \ref{table:analog_nb}) and were used thereafter.
+
+	The impact of the archive reduction can be seen in Fig.
+\ref{fig:plots_CRPSS_2Z} for the 2Z method and in Fig.
+\ref{fig:plots_CRPSS_2Z-2MI} for the 2Z-2MI method.
+As expected, a loss of performance was observed for each station, except for that of Aigle, which seemed relatively indifferent to this change.
+This loss was globally significant, with up to \textendash 1.89 points (\% of CRPSS) for Visp and the 2Z method.
 
@@
 
-	\subsection{Relevance of the reconstructed precipitation archives}
+	\subsection{Reconstruction of a longer precipitation archive}
+	\label{sec:reconstruction}
+
+	It would be profitable to be able to apply the MTW to a longer archive (here, 1961\textendash 2008), rather than being limited to the reduced period where the sub-daily precipitation data are available (cf.
+previous section).
+Therefore, in order to reconstruct a longer archive of moving 24h totals, two simple disaggregation approaches of the daily precipitation time series were assessed.
+
+	The first technique was a proportional distribution, where the observed daily precipitations were considered constant during the measuring period (6:00~UTC to 6:00~UTC the next day).
+Proportional parts of the original daily time series were allocated into a new moving average of 24h totals.
+
+	The second approach aimed at getting closer to the chronology of the actual precipitation by relying on some informative variables during the reconstruction procedure.
+Data from the NCEP/NCAR reanalysis 1 (Sect.
+\ref{sec:data}) were used for this purpose, despite their rough resolution (2.5\textdegree).
+Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and a time lapse between both series was allowed to take into account the significant distance separating the weather stations and the reanalysis grid point.
+The best proxy variable was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series over the period 1982\textendash 2007.
+Once the best proxy had been selected, its temporal profile was used in order to disaggregate the daily precipitation time series.
 
@@
 		\begin{center}
-			\includegraphics[width=8.3cm]{fig02.pdf}
+			\includegraphics[width=8cm]{fig02.pdf}
 		\end{center}
@@
 	\begin{figure}[htb]
-		\begin{center}
-			\includegraphics[width=8cm]{fig03.pdf}
-		\end{center}
-		\caption{Illustration of the generation of 24h total moving averages by means of a proportional distribution. The colours refer to the corresponding day of the daily time series.}
-		\label{fig:illustration_disaggregation}
-	\end{figure}
-
-	\begin{figure}[htb]
-		\includegraphics[width=8.3cm]{fig04.pdf}
+		\includegraphics[width=8.3cm]{fig03.pdf}
 		\caption{Performance score (CRPSS) of the AM on the atmospheric circulation at the different stations for (dashed) the full archive, i.e.
@@
 	\begin{figure}[htb]
-		\includegraphics[width=8.3cm]{fig05.pdf}
+		\includegraphics[width=8.3cm]{fig04.pdf}
 		\caption{Same as Figure \ref{fig:plots_CRPSS_2Z}, but for the analogue method with a second level with the moisture variables.}
@@
 		\begin{center}
-			\includegraphics[width=15cm]{fig06.pdf}
-		\end{center}
-		\caption{Changes in the S1 criterion distributions due to the MTW of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$, and (d) $40^{th}$ analogue ranks for the Ulrichen station over the whole calibration period (1961\textendash 2008).}
+			\includegraphics[width=17cm]{fig05.pdf}
+		\end{center}
+		\caption{Changes in the S1 criterion distributions due to the introduction of a MTW with a 12~h, 6~h or 3~h time step.
+Distributions are provided for (a) the $1^{st}$, (b) $15^{th}$, and (c) $30^{th}$ analogue ranks for the Ulrichen station.}
 		\label{fig:changes_S1_analogs}
@@
 		\begin{center}
-			\includegraphics[width=8.2cm]{fig07.pdf}
-		\end{center}
-		\caption{Synthesis of the changes in the S1 criterion due to the MTW for the Ulrichen station depending on the rank of the analogue.
-(a) Quantiles of the S1 distributions with and without the MTW.
+			\includegraphics[width=8.2cm]{fig06.pdf}
+		\end{center}
+		\caption{Synthesis of the changes in the S1 criterion due to the MTW (with a 12~h, 6~h, and 3~h time step) for the Ulrichen station depending on the rank of the analogue.
+(a) Quantiles of the S1 distributions corresponding to the MTW with different time steps (24~h is the standard approach without MTW).
 (b) Quantiles of the relative improvements of the S1 criterion when using the MTW.}
@@
 		\begin{center}
-			\includegraphics[width=8.3cm]{fig08.pdf}
+			\includegraphics[width=8.3cm]{fig07.pdf}
 		\end{center}
@@
 		\begin{center}
-			\includegraphics[width=7cm]{fig09.pdf}
+			\includegraphics[width=8.3cm]{fig08.pdf}
 		\end{center}
@@
 		\begin{center}
-			\includegraphics[width=8.1cm]{fig10.pdf}
+			\includegraphics[width=8.1cm]{fig09.pdf}
 		\end{center}
@@
 	\begin{figure}[htb]
-		\includegraphics[width=5cm]{fig11.pdf}
+		\includegraphics[width=5cm]{fig10.pdf}
 		\caption{Differences of the CRPSS performance score due to the introduction of the MTW as a function of daily precipitation thresholds at the Ulrichen station. The stars represent averages.}
@@
 	\begin{figure}[htb]
-		\includegraphics[width=8.3cm]{fig12.pdf}
+		\includegraphics[width=8.3cm]{fig11.pdf}
 		\caption{Distribution of the predictor hours on the selected analogue dates, when using the MTW, depending on the season for the Ulrichen station.}

### 2017-03-24 Moving temporal window - HESS/template.tex
Changing the structure of the Data and methods section.

@@
 \ref{fig:map}) that are subject to various meteorological influences \citep{Horton2012}.
-The data were available at an hourly time step for 25~years (1982\textendash 2007) and were also obtained at a daily time step (from 6:00~UTC to 6:00~UTC the next day) for 47~years (1961\textendash 2008).
+The data were available at an hourly time step for 29~years (1982\textendash 2010) and were also obtained at a daily time step (from 6:00~UTC to 6:00~UTC the next day) for 50~years (1961\textendash 2010).
 Due to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed.
@@
 
-	Synoptic-scale variables, used as predictors, were extracted from the ERA-20C reanalysis dataset \citep{Poli2016} with a 3h temporal resolution, and a spatial resolution of 1\textdegree.
+	Synoptic-scale variables, used as predictors, were extracted from two of the most recent global reanalysis datasets: the european ERA-20C \citep{Poli2016} with a 3h temporal resolution, and a spatial resolution of 1\textdegree, and MERRA-2, from NASA, with a 6h temporal resolution and a spatial resolution of 0.625\textdegree x 0.5\textdegree.
 The study was originally performed on the NCEP/NCAR reanalysis 1 dataset \citep{Kalnay1996}, and the conclusions were similar.
-The main advantage of the ERA-20C is that it allows testing the relevance of the MTW at a 3h time step.
+ERA-20C is build by assimilating only surface observations, and is thus available on a long period (1900\textendash 2010).
+On the contrary, MERRA-2 is build by assimilating observations at higher levels and from more sensors, including satellite data, but is then more limited in time (1980\textendash present).
+It is of interest to consider these two datasets, as they represent different kind of products and are thus an interesting basis to assess the relevance of a MTW.
+The specific advantages of ERA-20C is that it allows testing the relevance of the MTW at a 3h time step, and covers a long period.
+On the other hand, MERRA-2 has a higher spatial resolution and can be expected to be more correct at higher levels of the atmosphere.
 
-	\subsection{The considered analogue method}
+	\subsection{The considered analogue methods}
 	\label{sec:analog_method}
@@
 However, it is easier to interpret the impact of the MTW using more basic methods.
+
+	\subsection{Calibration of the analogue method}
+	\label{sec:calibration}
+
+	The semi-automatic sequential procedure elaborated by \citet{Bontron2004} was used to calibrate the AM \cite[see also ][]{Radanovics2013, BenDaoud2016}.
+The analogy levels (e.g.
+the atmospheric circulation or moisture index) are calibrated sequentially.
+The parameters calibrated by this approach, for every level of analogy, are the spatial windows on which the predictors are compared and the number of analogues.
+The procedure, as defined by \citet{Bontron2004}, consists of the following steps:
+
+	\begin{enumerate}
+		\item Manual selection of the following parameters:
+		\begin{enumerate}
+			\item meteorological variable (e.g. geopotential height, temperature, relative humidity, etc.),
+			\item pressure level (e.g. 500 hPa, ...),
+			\item temporal window (hour of the day \textendash\ e.g. 6:00 or 12:00~UTC),
+			\item initial analogue numbers (e.g. $N_{1}=50$).
+		\end{enumerate}
+
+		\item For every level of analogy:
+		\begin{enumerate}
+			\item Identification of the most skilled unitary cell (one point for moisture variables and four for geopotential heights when using the S1 criterion) over a large domain.
+Every point (or cell) of the full domain is assessed on all predictors of the level of analogy, jointly (consisting generally of the same variable but on different pressure levels and at different hours).
+			\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain.
+The spatial window grows by repeating the previous steps until no improvement is reached.
+			\item The number of analogue situations $N_{1}$ is then reconsidered and optimized for the current level of analogy.
+		\end{enumerate}
+		\item A new level of analogy can then be added, based on other variables (such as the moisture index) at chosen pressure levels and hours of the day.
+The number of analogues for the next level of analogy, $N_{2}$, is initiated at a chosen value.
+The procedure starts again from step 2 (calibration of the spatial window and the number of analogues) for the new level.
+The parameters calibrated on the previous analogy levels are fixed and do not change.
+		\item Finally, the numbers of analogues $N_{1}$ and $N_{2}$ for the different levels of analogy are reassessed.
+This is done iteratively by varying the number of analogues of each level in a systematic way.
+	\end{enumerate}
+
+	The calibration is done in successive steps with a limited number of parameters.
+Previously calibrated parameters are generally not reassessed (except for the number of analogues).
+More advanced techniques, such as using genetic algorithms \citep{Horton2016}, exist but are out of the scope of the present study.
 
@@
 However, the competition between the loss of performance due to a smaller archive length and the potentially better analogy between target and MTW candidates needs to be assessed.
-
-	\subsection{Calibration of the analogue method}
-	\label{sec:calibration}
-
-	The semi-automatic sequential procedure elaborated by \citet{Bontron2004} was used to calibrate the AM \cite[see also ][]{Radanovics2013, BenDaoud2016}.
-The analogy levels (e.g.
-the atmospheric circulation or moisture index) are calibrated sequentially.
-The parameters calibrated by this approach, for every level of analogy, are the spatial windows on which the predictors are compared and the number of analogues.
-The procedure, as defined by \citet{Bontron2004}, consists of the following steps:
-
-	\begin{enumerate}
-		\item Manual selection of the following parameters:
-		\begin{enumerate}
-			\item meteorological variable (e.g. geopotential height, temperature, relative humidity, etc.),
-			\item pressure level (e.g. 500 hPa, ...),
-			\item temporal window (hour of the day \textendash\ e.g. 6:00 or 12:00~UTC),
-			\item initial analogue numbers (e.g. $N_{1}=50$).
-		\end{enumerate}
-
-		\item For every level of analogy:
-		\begin{enumerate}
-			\item Identification of the most skilled unitary cell (one point for moisture variables and four for geopotential heights when using the S1 criterion) over a large domain.
-Every point (or cell) of the full domain is assessed on all predictors of the level of analogy, jointly (consisting generally of the same variable but on different pressure levels and at different hours).
-			\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain.
-The spatial window grows by repeating the previous steps until no improvement is reached.
-			\item The number of analogue situations $N_{1}$ is then reconsidered and optimized for the current level of analogy.
-		\end{enumerate}
-		\item A new level of analogy can then be added, based on other variables (such as the moisture index) at chosen pressure levels and hours of the day.
-The number of analogues for the next level of analogy, $N_{2}$, is initiated at a chosen value.
-The procedure starts again from step 2 (calibration of the spatial window and the number of analogues) for the new level.
-The parameters calibrated on the previous analogy levels are fixed and do not change.
-		\item Finally, the numbers of analogues $N_{1}$ and $N_{2}$ for the different levels of analogy are reassessed.
-This is done iteratively by varying the number of analogues of each level in a systematic way.
-	\end{enumerate}
-
-	The calibration is done in successive steps with a limited number of parameters.
-Previously calibrated parameters are generally not reassessed (except for the number of analogues).
-More advanced techniques, such as using genetic algorithms \citep{Horton2016}, exist but are out of the scope of the present study.
 
@@
 		\begin{center}
-			\includegraphics[width=8.2cm]{fig06.pdf}
+			\includegraphics[width=8.3cm]{fig06.pdf}
 		\end{center}
@@
 		\begin{center}
-			\includegraphics[width=8.1cm]{fig09.pdf}
+			\includegraphics[width=8.3cm]{fig09.pdf}
 		\end{center}
@@
 	\begin{figure}[htb]
-		\includegraphics[width=5cm]{fig10.pdf}
+		\includegraphics[width=8.3cm]{fig10.pdf}
 		\caption{Differences of the CRPSS performance score due to the introduction of the MTW as a function of daily precipitation thresholds at the Ulrichen station. The stars represent averages.}
@@
 	\begin{figure}[htb]
-		\includegraphics[width=8.3cm]{fig11.pdf}
+		\includegraphics[width=7.5cm]{fig11.pdf}
 		\caption{Distribution of the predictor hours on the selected analogue dates, when using the MTW, depending on the season for the Ulrichen station.}

### 2017-03-24 Moving temporal window - HESS/template.tex
Replacing the table for the number of analogues by a figure.

@@
 Among these, the zonal extent of the spatial windows of the circulation analogy decreased slightly (not shown).
-More significantly, the optimal number of analogues $N_{1}$ and $N_{2}$ increased after introducing the MTW by a considerable magnitude (Table \ref{table:analog_nb}): 25~\% to 83~\% for the 2Z method and 20~\% to 67~\% for the final selection of the 2Z-2MI method.
-The number of analogues $N_{1}$ of the first analogy level of the 2Z-2MI method reached three times its previous value for the Visp station ($N_{1}$~=~135 instead of 45; Table \ref{table:analog_nb}).
+More significantly, the optimal number of analogues $N_{1}$ and $N_{2}$ increased after introducing the MTW by a considerable magnitude (Fig.
+\ref{fig:analog_nb}): 25~\% to 83~\% for the 2Z method and 20~\% to 67~\% for the final selection of the 2Z-2MI method.
+The number of analogues $N_{1}$ of the first analogy level of the 2Z-2MI method reached three times its previous value for the Visp station ($N_{1}$~=~135 instead of 45; Fig.
+\ref{fig:analog_nb}).
 
@@
 Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
-The AM parameters were calibrated on the original archive (see resulting analogue numbers in Table \ref{table:analog_nb}) and were used thereafter.
+The AM parameters were calibrated on the original archive (see resulting analogue numbers in Fig.
+\ref{fig:analog_nb}) and were used thereafter.
 
@@
 	After the recalibration of the AMs with the MTW, the optimal analogue numbers were significantly higher than in the original methods (see Sect.
-\ref{sec:recalibration} and Table \ref{table:analog_nb}).
+\ref{sec:recalibration} and Fig.
+\ref{fig:analog_nb}).
 As shown in Fig.
@@
 
+	\begin{figure}[htb]
+	\includegraphics[width=7.5cm]{fig12.pdf}
+	\caption{Optimal number of analogues (of the first and second level of analogy, respectively, $N_{1}$ and $N_{2}$) of the method based on the atmospheric circulation only (method 2Z) and the method with a second level of analogy with moisture variables (2Z-2MI) on the full archive (Standard), and after recalibration using the MTW (MTW-r).}
+	\label{fig:analog_nb}
+	\end{figure}
+
 	\clearpage
@@
 		\label{table:method_2Z-2MI}
-	\end{table}
-
-	\begin{table}[htb]
-		\caption{Optimal number of analogues (of the first and second level of analogy, respectively, $N_{1}$ and $N_{2}$) of the method based on the atmospheric circulation only (method 2Z) and the method with a second level of analogy with moisture variables (2Z-2MI) on the full archive (Standard), and after recalibration using the MTW (MTW-r).}
-		\begin{center}
-			\begin{tabular}{l c c c c c c }
-				\hline
-				\multirow{3}{*}{Station} & \multicolumn{3}{c}{Standard} & \multicolumn{3}{c}{MTW-r} \\
-				& 2Z & \multicolumn{2}{c}{2Z-2MI} & 2Z & \multicolumn{2}{c}{2Z-2MI}\\
-				& $N_{1}$ & $N_{1}$ & $N_{2}$ & $N_{1}$ & $N_{1}$ & $N_{2}$\\ 
-				\hline
-				Ulrichen & 40 & 60 & 25 & 50 & 110 & 35\\
-				Zermatt & 35 & 55 & 25 & 55 & 80 & 30\\
-				Visp & 30 & 45 & 25 & 55 & 135 & 35\\
-				Montana & 40 & 55 & 30 & 55 & 110 & 40\\
-				Sion & 40 & 90 & 30 & 55 & 140 & 50\\
-				Aigle & 50 & 100 & 35 & 75 & 135 & 45\\ 
-				\hline
-			\end{tabular}
-		\end{center}	
-		\label{table:analog_nb}
 	\end{table}

### 2017-03-24 Moving temporal window - HESS/template.tex
HESS paper under work.

@@
 %% Please use the following documentclass and Journal Abbreviations for Discussion Papers and Final Revised Papers.
-
-%TODO: change CRPSS from % to 0.x ?
 
@@
 The benefits of introducing a MTW were assessed first in regards to the analogy criterion improvement between synoptic situations (Sect.
-\ref{sec:influence_criteria}) and then in terms of precipitation prediction skill (Sect.
+\ref{sec:influence_analogue_dates}) and then in terms of precipitation prediction skill (Sect.
 \ref{sec:influence_scores}).
@@
 On the contrary, MERRA-2 is build by assimilating observations at higher levels and from more sensors, including satellite data, but is then more limited in time (1980\textendash present).
-It is of interest to consider these two datasets, as they represent different kind of products and are thus an interesting basis to assess the relevance of a MTW.
-The specific advantages of ERA-20C is that it allows testing the relevance of the MTW at a 3h time step, and covers a long period.
+It is of interest to assess the relevance of a MTW with these two datasets, as they represent different kind of products.
+The specific advantages of ERA-20C is that it allows testing a MTW with a 3h time step, and it covers a long period.
 On the other hand, MERRA-2 has a higher spatial resolution and can be expected to be more correct at higher levels of the atmosphere.
@@
 
+	AMs rely on parameters that need to be defined for every level of analogy.
+Here, the selection of the meteorological variables used as predictors, as well as their corresponding analogy criteria, pressure level, and hour of the day will be identical to the methods 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) described above.
+The parameters that are here calibrated are:
+
+	\begin{itemize}
+		\item The spatial windows, which are the domains on which predictors are compared.
+There is a spatial window specific to each level of analogy.
+It will thus differ between circulation and moisture variables.
+		\item The optimal number of analog situations for every level of analogy.
+	\end{itemize}
+
 	The semi-automatic sequential procedure elaborated by \citet{Bontron2004} was used to calibrate the AM \cite[see also ][]{Radanovics2013, BenDaoud2016}.
@@
 	\begin{enumerate}
-		\item Manual selection of the following parameters:
-		\begin{enumerate}
-			\item meteorological variable (e.g. geopotential height, temperature, relative humidity, etc.),
-			\item pressure level (e.g. 500 hPa, ...),
-			\item temporal window (hour of the day \textendash\ e.g. 6:00 or 12:00~UTC),
-			\item initial analogue numbers (e.g. $N_{1}=50$).
-		\end{enumerate}
-
 		\item For every level of analogy:
@@
 The spatial window grows by repeating the previous steps until no improvement is reached.
-			\item The number of analogue situations $N_{1}$ is then reconsidered and optimized for the current level of analogy.
+			\item The number of analogue situations $N_{1}$, which was initially set at an arbitrary value, is then reconsidered and optimized for the current level of analogy.
 		\end{enumerate}
@@
 The number of analogues for the next level of analogy, $N_{2}$, is initiated at a chosen value.
-The procedure starts again from step 2 (calibration of the spatial window and the number of analogues) for the new level.
+The procedure starts again from step 1 (calibration of the spatial window and the number of analogues) for the new level.
 The parameters calibrated on the previous analogy levels are fixed and do not change.
@@
 
-	The calibration is done in successive steps with a limited number of parameters.
+	The calibration is done in successive steps with a limited number of parameters in order to minimize the objective function (CRPS, Eq.
+\ref{eq:CRPS}).
 Previously calibrated parameters are generally not reassessed (except for the number of analogues).
-More advanced techniques, such as using genetic algorithms \citep{Horton2016}, exist but are out of the scope of the present study.
+More advanced techniques, such as using genetic algorithms \citep{Horton2017}, exist but are out of the scope of the present study.
 
-	\subsection{Performance score}
-	\label{sec:performance}
+	The 29-yr hourly precipitation dataset was divided into a calibration period (CP) and a validation period (VP), in order to assess the robustness of the proposed improvements on independent data.
+The selection of the VP was evenly distributed over the entire series \citep{BenDaoud2010} to reduce potential biases related to trends linked to climate change or to the evolution in measurement techniques.
+Thus, one out of every five years was selected for validation, which represents a total of 6 years for the VP and 23 for the CP.
 
-	In order to assess the performance of AMs, the continuous ranked probability score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} is often employed \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}.
+	The continuous ranked probability score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} is often employed in order to assess the performance of AMs \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}.
 It allows the evaluation of the predicted cumulative distribution functions $F(y)$ of the precipitation values $y$ from analogue situations compared to the observed value $y^{0}$.
@@
 
-	In order to compare the value of the score in regard to a reference, one often considers its skill score expression and uses the climatological distribution (i.e., the distribution of all precipitation values from the corresponding archive) as the reference.
-The continuous ranked probability skill score (CRPSS) is defined as follows:
-
-	\begin{equation}
-	\label{eq:CRPSS}
-	S_{\text{SCRP}} = \frac{S_{\text{CRP}}-S_{\text{CRP}}^{r}}{S_{\text{CRP}}^{p}-S_{\text{CRP}}^{r}} = 1-\frac{S_{\text{CRP}}}{S_{\text{CRP}}^{r}}
-	\end{equation}
-	where $S_{\text{CRP}}^{r}$ is the $S_{\text{CRP}}$ value for the reference (climatological distribution) and $S_{\text{CRP}}^{p}$ is for a perfect prediction (which implies $S_{\text{CRP}}^{p}~=~0$).
-A better prediction is characterized by an increase in CRPSS: $S_{\text{SCRP}}~=~1$ for a perfect prediction and $S_{\text{SCRP}}~<~0$ for a prediction with a lower skill than the reference.
-
 	\subsection{The moving time window (MTW) approach}
@@
 If the target situation is kept at 12:00 and 24:00~UTC for Z1000 and Z500 respectively, candidate situations are not only considered at 12:00 and 24:00~UTC, but at other hours by allowing a time shift.
-Therefore, instead of looking for analogues at a 24h time step, they are sought at the time step matching the predictor temporal resolution which is a 6h time step in this study (Fig.
+Therefore, instead of looking for analogues at a 24h time step, they are sought at the time step matching the predictor temporal resolution.
+The ERA-20C dataset made here possible to test a MTW with a 12h, 6h, or 3h time step (named respectively 12h-MTW, 6h-MTW, 3h-MTW hereafter; Fig.
 \ref{fig:principle}).
@@
 	The target situations and their corresponding observed precipitation values do not change because the prediction is still established on a daily basis for a fixed period of the target day (6:00~UTC to 6:00~UTC the next day) as before.
-The difference is that the candidates are 4 times as many (even though they are not fully independent) as in the conventional approach.
+The difference is that the candidates are 2 (12h-MTW), 4 (6h-MTW), or 8 (3h-MTW) times as many (even though they are not fully independent) as in the conventional approach.
 No constraint was added in order to restrict the selection of multiple analogues within the same candidate dates.
@@
 On the basis of high temporal resolution time series (Sect.
-\ref{sec:data}), 24h totals were processed at a 6h time step by means of a moving 24h total.
-Since sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~year archive (1961\textendash 2008) to 25~years (1982\textendash 2007) can be expected.
-However, the competition between the loss of performance due to a smaller archive length and the potentially better analogy between target and MTW candidates needs to be assessed.
+\ref{sec:data}), 24h totals were processed at time steps matching the MTW by means of a moving 24h total on the period 1982-2010.
 
@@
 
-	\subsection{Influence of the MTW on the analogy criterion}
-	\label{sec:influence_criteria}
+	The AMs were applied to both ERA-20C and MERRA-2 datasets.
+Most results are presented for the ERA-20C dataset, as it allows testing a 3h-MTW, but would lead to similar conclusions with MERRA-2.
+The impact of an MTW was assessed on two different basis:
+	\begin{itemize}
+		\item Original parameters: The AMs were initially calibrated for each station based on the classic 24-hr approach.
+Then, the MTW was introduced into the AMs, but the parameters (spatial windows and number of analogues) were not reassessed.
+The analogy is the same and thus initial analogue dates should be found in the new distribution, along with new dates provided by the MTW.
+		\item Recalibrated: The parameters of the AMs were reassessed after the introduction of the MTW at different time steps.
+This allowed to improve the prediction skill of the AMs by adapting to the new information available through the MTW.
+The characterization of the analogy might thus change (different spatial windows and number of analogues).
+	\end{itemize}
+
+	The MTW is expected to have an impact on both the selection of analogue dates and the prediction skill. Both will be analyzed separately hereafter.
+
+	\subsection{Influence of the MTW on the selection of analogue dates}
+	\label{sec:influence_analogue_dates}
+
+	\subsubsection{Changes in the analogy criteria distributions}
+	\label{sec:changes_distributions}
 
@@
 \ref{fig:changes_S1} bottom).
-
-	\subsubsection{Changes per precipitation class}
-	\label{sec:influence_precip}
-
-	The impact of the MTW on the analogy criterion has been analysed per precipitation classes (for the target day).
-The results are summarised in Fig.
-\ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for the days with precipitation (organized into classes) between two thresholds.
-With the number of cases per class being reduced, the curves are not as smooth as in previous analyses.
-It is nevertheless clear that the improvements were larger for days with higher precipitation.
-Once again, the results for all the other stations were similar.
-
-	\subsubsection{Changes per season}
-	\label{sec:seasonal_effect}
-
-	Atmospheric dynamics vary greatly from one season to another, reflecting on the performance of the AM that is generally lower between June and August \citep{Bliefernicht2010}.
-The effect of the MTW on the S1 criterion per season is presented in Fig.
-\ref{fig:changes_S1_seasons}.
-Differences between the seasons were substantial, with greater improvements for winter than summer.
-
-	\subsubsection{Changes in the moisture analogy}
-	\label{sec:perf_2Z-2MI}
-
-	When adding the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations did not increase, as they were conditioned by the $N_{1}$ previously selected analogues, but their dates had changed.
-In contrast to the AM on the atmospheric circulation only, both a reduction or an increase of the RMSE analogy criterion values were possible with the MTW compared to the static approach.
-Indeed, Fig.
-\ref{fig:changes_RMSE} shows an almost insignificant improvement of the RMSE values.
-Unlike the first level of analogy, the relative changes of the RMSE values were distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
-
-	\subsection{Impact of the MTW on prediction skill}
-	\label{sec:influence_scores}
-
-	The new performance scores (CRPSS) of the precipitation prediction are provided in Fig.
-\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI} for the 2Z and 2Z-2MI methods, respectively, for the reduced archive (1982\textendash 2007).
-The gains relative to the static approach on the same archive ranged from 0.57 to 2.14 points (\% of CRPSS) for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method.
-
-	\subsubsection{Improvement per precipitation classes}
-	\label{sec:improvement_CRPSS_precip_threshold}
-
-	The S1 criterion was previously found to show greater improvement for higher precipitation values (Sect.
-\ref{sec:influence_precip}).
-The changes in terms of prediction skill were also assessed for the precipitation classes.
-Fig.
-\ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, with the other stations having the same behaviour.
-The performance score was improved for days with higher precipitation after the introduction of the MTW.
-In contrast, for non-rainy days and small precipitation values, the performance scores were not improved.
-
-	\subsubsection{Recalibration of AM parameters}
-	\label{sec:recalibration}
-
-	The previous assessment of the performance improvement was established with the original parameters optimized with a fixed time window.
-However, one can assume that the introduction of the MTW might change the optimum value of some parameters.
-The calibration (see Sect.
-\ref{sec:calibration}) should then be reprocessed.
-
-	After recalibrating, changes in the AM parameters could be observed for both the 2Z and 2Z-2MI methods.
-Among these, the zonal extent of the spatial windows of the circulation analogy decreased slightly (not shown).
-More significantly, the optimal number of analogues $N_{1}$ and $N_{2}$ increased after introducing the MTW by a considerable magnitude (Fig.
-\ref{fig:analog_nb}): 25~\% to 83~\% for the 2Z method and 20~\% to 67~\% for the final selection of the 2Z-2MI method.
-The number of analogues $N_{1}$ of the first analogy level of the 2Z-2MI method reached three times its previous value for the Visp station ($N_{1}$~=~135 instead of 45; Fig.
-\ref{fig:analog_nb}).
-
-	The values of the CRPSS scores for both methods (Fig.
-\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}) have significantly increased after recalibration.
-When analysing the change in performance per precipitation class, the results (not shown) were very similar to the observations in Sect.
-\ref{sec:improvement_CRPSS_precip_threshold}, with a slight performance increase for small precipitation values that can be observed at the expense of higher amounts, due to the higher number of analogues.
-
-	\subsection{Using a reconstructed archive}
-	\label{sec:reconstruction_results}
-
-	The reconstructed time series cover the full period.
-However, they were first assessed using the MTW on the reduced period in order be comparable with the real sub-daily precipitation time series, and thus to evaluate their relevance and the possible loss in performance score.
-
-	When using the first reconstructed time series based on the proportional distribution (see Sect.
-\ref{sec:reconstruction}), the AM performance was degraded and was even below the conventional method without MTW (Table \ref{table:disaggregation_proportional} to compare to Fig.
-\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}).
-
-	For the second approach, the synoptic proxy for the temporal disaggregation of the daily time series had to be identified first.
-The results are illustrated this time for the Zermatt station.
-Among the considered moisture variables (see Sect.
-\ref{sec:reconstruction}), the best proxy was the precipitable water at 45\textdegree\ N and 7.5\textdegree\ E, with a time offset of \textendash 6~h (Table \ref{table:proxy_correlations}).
-Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the disaggregated series using the proxy of precipitable water which are also lower than the conventional method.
-
-	\section{Discussion}
-	\label{sec:discussion}
-
-	\subsection{Consequences of the archive reduction}
-	\label{sec:archive_reduction}
-
-	The performance loss resulting from the reduction of a 47~year archive (1961\textendash 2008, corresponding to the daily time series) to 25~years (1982\textendash 2007, corresponding to the hourly time series in Sect.
-\ref{sec:mtw}) was assessed with the original method without MTW.
-Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
-The AM parameters were calibrated on the original archive (see resulting analogue numbers in Fig.
-\ref{fig:analog_nb}) and were used thereafter.
-
-	The impact of the archive reduction can be seen in Fig.
-\ref{fig:plots_CRPSS_2Z} for the 2Z method and in Fig.
-\ref{fig:plots_CRPSS_2Z-2MI} for the 2Z-2MI method.
-As expected, a loss of performance was observed for each station, except for that of Aigle, which seemed relatively indifferent to this change.
-This loss was globally significant, with up to \textendash 1.89 points (\% of CRPSS) for Visp and the 2Z method.
-
-	\subsection{Improvement of the selection of analogue situations}
 
@@
 
-	\subsection{Improvement of precipitation prediction}
+	\subsubsection{Changes per precipitation class}
+	\label{sec:influence_precip}
+
+	The impact of the MTW on the analogy criterion has been analysed per precipitation classes (for the target day).
+The results are summarised in Fig.
+\ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for the days with precipitation (organized into classes) between two thresholds.
+With the number of cases per class being reduced, the curves are not as smooth as in previous analyses.
+It is nevertheless clear that the improvements were larger for days with higher precipitation.
+Once again, the results for all the other stations were similar.
+
+	\subsubsection{Changes per season}
+	\label{sec:seasonal_effect}
+
+	Atmospheric dynamics vary greatly from one season to another, reflecting on the performance of the AM that is generally lower between June and August \citep{Bliefernicht2010}.
+The effect of the MTW on the S1 criterion per season is presented in Fig.
+\ref{fig:changes_S1_seasons}.
+Differences between the seasons were substantial, with greater improvements for winter than summer.
+
+	Section \ref{sec:seasonal_effect} and Fig.
+\ref{fig:changes_S1_seasons} revealed a difference in the improvement of the S1 criterion according to the season, with greater improvements for winter than summer.
+One hypothesis is that the diurnal effects of the summer months have an influence on the atmospheric circulation at least in the lower layers.
+This effect is in phase with the daily cycle, and good analogues are essentially found for the same hours.
+
+	An analysis of the selected hours for the geopotential height predictor seems to confirm this assumption (Fig.
+\ref{fig:hours_selection_per_season}).
+It was found that the new choice of the temporal window in winter, when using the MTW approach, is well balanced between the four options.
+This means a change of 75~\% of the analogues selected compared to the conventional approach.
+On the contrary, the days during the summer months had a preference for the initial temporal window (Z500 24~h \& Z1000 12~h), likely due to more pronounced diurnal effects, which reduced the potential for improvement of the criteria.
+The other seasons were between these two extremes, which is consistent with their respective improvements.
+This seasonal effect was observed for each station in a very similar way and even with slightly larger amplitude than for Ulrichen.
+
+	\subsubsection{Changes in the moisture analogy}
+	\label{sec:perf_2Z-2MI}
+
+	When adding the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations did not increase, as they were conditioned by the $N_{1}$ previously selected analogues, but their dates had changed.
+In contrast to the AM on the atmospheric circulation only, both a reduction or an increase of the RMSE analogy criterion values were possible with the MTW compared to the static approach.
+Indeed, Fig.
+\ref{fig:changes_RMSE} shows an almost insignificant improvement of the RMSE values.
+Unlike the first level of analogy, the relative changes of the RMSE values were distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
+
+	\subsection{Impact of the MTW on prediction skill}
+	\label{sec:influence_scores}
+
+	The new performance scores (CRPS) of the precipitation prediction are provided in Fig.
+\ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI} for the 2Z and 2Z-2MI methods, respectively, for the reduced archive (1982\textendash 2007).
 
 	The MTW was found to improve the skill of the precipitation prediction for both the 2Z and 2Z-2MI methods (Fig.
-\ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}, Sect.
+\ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI}, Sect.
 \ref{sec:influence_scores}).
@@
 \ref{sec:influence_precip}) and the performance scores (Sect.
-\ref{sec:improvement_CRPSS_precip_threshold}) were improved to a greater extent for days with heavier precipitation.
+\ref{sec:improvement_CRPS_precip_threshold}) were improved to a greater extent for days with heavier precipitation.
 This is likely due to the fact that higher precipitation events are a consequence of atmospheric conditions with greater dynamics, such as weather disturbances, which have a well-marked temporal evolution.
@@
 
-	\subsection{Seasonal effect}
+	\subsubsection{Improvement per precipitation classes}
+	\label{sec:improvement_CRPS_precip_threshold}
 
-	Section \ref{sec:seasonal_effect} and Fig.
-\ref{fig:changes_S1_seasons} revealed a difference in the improvement of the S1 criterion according to the season, with greater improvements for winter than summer.
-One hypothesis is that the diurnal effects of the summer months have an influence on the atmospheric circulation at least in the lower layers.
-This effect is in phase with the daily cycle, and good analogues are essentially found for the same hours.
+	The S1 criterion was previously found to show greater improvement for higher precipitation values (Sect.
+\ref{sec:influence_precip}).
+The changes in terms of prediction skill were also assessed for the precipitation classes.
+Fig.
+\ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, with the other stations having the same behaviour.
+The performance score was improved for days with higher precipitation after the introduction of the MTW.
+In contrast, for non-rainy days and small precipitation values, the performance scores were not improved.
 
-	An analysis of the selected hours for the geopotential height predictor seems to confirm this assumption (Fig.
-\ref{fig:hours_selection_per_season}).
-It was found that the new choice of the temporal window in winter, when using the MTW approach, is well balanced between the four options.
-This means a change of 75~\% of the analogues selected compared to the conventional approach.
-On the contrary, the days during the summer months had a preference for the initial temporal window (Z500 24~h \& Z1000 12~h), likely due to more pronounced diurnal effects, which reduced the potential for improvement of the criteria.
-The other seasons were between these two extremes, which is consistent with their respective improvements.
-This seasonal effect was observed for each station in a very similar way and even with slightly larger amplitude than for Ulrichen.
+	\subsubsection{Recalibration of AM parameters}
+	\label{sec:recalibration}
+
+	The previous assessment of the performance improvement was established with the original parameters optimized with a fixed time window.
+However, one can assume that the introduction of the MTW might change the optimum value of some parameters.
+The calibration (see Sect.
+\ref{sec:calibration}) should then be reprocessed.
+
+	After recalibrating, changes in the AM parameters could be observed for both the 2Z and 2Z-2MI methods.
+Among these, the zonal extent of the spatial windows of the circulation analogy decreased slightly (not shown).
+More significantly, the optimal number of analogues $N_{1}$ and $N_{2}$ increased after introducing the MTW by a considerable magnitude (Fig.
+\ref{fig:analog_nb}): 25~\% to 83~\% for the 2Z method and 20~\% to 67~\% for the final selection of the 2Z-2MI method.
+The number of analogues $N_{1}$ of the first analogy level of the 2Z-2MI method reached three times its previous value for the Visp station ($N_{1}$~=~135 instead of 45; Fig.
+\ref{fig:analog_nb}).
+
+	The values of the CRPS scores for both methods (Fig.
+\ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI}) have significantly increased after recalibration.
+When analysing the change in performance per precipitation class, the results (not shown) were very similar to the observations in Sect.
+\ref{sec:improvement_CRPS_precip_threshold}, with a slight performance increase for small precipitation values that can be observed at the expense of higher amounts, due to the higher number of analogues.
+
+	\section{Discussion}
+	\label{sec:discussion}
+
+	\subsection{Consequences of the archive reduction}
+	\label{sec:archive_reduction}
+
+	Since sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~year archive (1961\textendash 2008) to 25~years (1982\textendash 2007) can be expected.
+However, the competition between the loss of performance due to a smaller archive length and the potentially better analogy between target and MTW candidates needs to be assessed.
+
+	The performance loss resulting from the reduction of a 47~year archive (1961\textendash 2008, corresponding to the daily time series) to 25~years (1982\textendash 2007, corresponding to the hourly time series in Sect.
+\ref{sec:mtw}) was assessed with the original method without MTW.
+Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
+The AM parameters were calibrated on the original archive (see resulting analogue numbers in Fig.
+\ref{fig:analog_nb}) and were used thereafter.
+
+	The impact of the archive reduction can be seen in Fig.
+\ref{fig:plots_CRPS_2Z} for the 2Z method and in Fig.
+\ref{fig:plots_CRPS_2Z-2MI} for the 2Z-2MI method.
+As expected, a loss of performance was observed for each station, except for that of Aigle, which seemed relatively indifferent to this change.
+This loss was globally significant, with up to \textendash 1.89 points (\% of CRPS) for Visp and the 2Z method.
 
@@
 
-	\subsection{On the use of an old reanalysis dataset}
-	\label{sec:old_reanalysis}
-
-	The considered reanalysis dataset, which is the NCEP/NCAR reanalysis 1 \citep{Kalnay1996}, is relatively old and has a coarse resolution (2.5\textdegree).
-Newer reanalysis datasets could have been used in this study and might have resulted in higher performance scores.
-However, \cite{BenDaoud2009} showed that the sensitivity of the method to the reanalysis dataset is rather small.
-This is particularly true for simple AMs that mainly rely on the atmospheric circulation, which is already well defined at a coarser resolution.
-That might not be the case in more elaborate methods relying on thermodynamic data.
-A comparative analysis of several reanalysis datasets within the AM is being conducted and will be the topic of a dedicated study.
-
-	Moreover, one can assume that the gain observed here by introducing a MTW should also be found for a better reanalysis dataset.
-Indeed, a better dataset does not negatively influence the fact that one can find better analogue situations at other hours of the day rather than at fixed hours.
-
 	\subsection{Reconstruction of a longer precipitation archive}
@@
 Once the best proxy had been selected, its temporal profile was used in order to disaggregate the daily precipitation time series.
+
+	The reconstructed time series cover the full period.
+However, they were first assessed using the MTW on the reduced period in order be comparable with the real sub-daily precipitation time series, and thus to evaluate their relevance and the possible loss in performance score.
+
+	When using the first reconstructed time series based on the proportional distribution (see Sect.
+\ref{sec:reconstruction}), the AM performance was degraded and was even below the conventional method without MTW.
+
+	For the second approach, the synoptic proxy for the temporal disaggregation of the daily time series had to be identified first.
+The results are illustrated this time for the Zermatt station.
+Among the considered moisture variables (see Sect.
+\ref{sec:reconstruction}), the best proxy was the precipitable water at 45\textdegree\ N and 7.5\textdegree\ E, with a time offset of \textendash 6~h.
+xx presents the CRPS scores obtained by the disaggregated series using the proxy of precipitable water which are also lower than the conventional method.
 
@@
 		\item [AM] Analogue method
+		\item [CP] Calibration period
 		\item [CRPS] Continuous ranked probability score
-		\item [CRPSS] Continuous ranked probability skill score
 		\item [MTW] Moving time window
@@
 		\item [TPW] Total precipitable water
+		\item [VP] Validation period
 		\item [Z1000] Geopotential height at 1000 hPa
@@
 		\includegraphics[width=8.3cm]{fig03.pdf}
-		\caption{Performance score (CRPSS) of the AM on the atmospheric circulation at the different stations for (dashed) the full archive, i.e.
+		\caption{Performance score (CRPS) of the AM on the atmospheric circulation at the different stations for (dashed) the full archive, i.e.
 1961\textendash 2008; (yellow) the reduced archive, i.e.
 1982\textendash 2007; (blue) the introduction of the MTW on the reduced archive; and (green) the recalibrated parameters of the AM with the MTW.}
-		\label{fig:plots_CRPSS_2Z}
+		\label{fig:plots_CRPS_2Z}
 	\end{figure}
@@
 		\includegraphics[width=8.3cm]{fig04.pdf}
-		\caption{Same as Figure \ref{fig:plots_CRPSS_2Z}, but for the analogue method with a second level with the moisture variables.}
-		\label{fig:plots_CRPSS_2Z-2MI}
+		\caption{Same as Figure \ref{fig:plots_CRPS_2Z}, but for the analogue method with a second level with the moisture variables.}
+		\label{fig:plots_CRPS_2Z-2MI}
 	\end{figure}
@@
 		\includegraphics[width=8.3cm]{fig10.pdf}
-		\caption{Differences of the CRPSS performance score due to the introduction of the MTW as a function of daily precipitation thresholds at the Ulrichen station. The stars represent averages.}
+		\caption{Differences of the CRPS performance score due to the introduction of the MTW as a function of daily precipitation thresholds at the Ulrichen station. The stars represent averages.}
 		\label{fig:changes_CRPS_precip_threshold}
@@
 		\label{table:method_2Z-2MI}
-	\end{table}
-
-	\begin{table}[htb]
-		\caption{Values of the CRPSS (\%) score for the original and the recalibrated parameters (with the sequential method, as described in Sect.
-\ref{sec:calibration}) using the MTW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
-		\begin{center}
-			\begin{tabular}{l c c c c}
-				\hline
-				\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
-				& original & recalib. & original & recalib. \\
-				\hline
-				Ulrichen & 29.13 & 29.61 & 33.15 & 33.45 \\
-				Zermatt & 22.17 & 22.80 & 26.72 & 27.43 \\
-				Visp & 22.32 & 22.89 & 27.01 & 28.04 \\
-				Montana & 29.41 & 30.24 & 33.83 & 34.55 \\
-				Sion & 22.98 & 23.41 & 28.57 & 29.15 \\
-				Aigle & 29.07 & 29.46 & 34.66 & 35.09 \\
-				\hline
-			\end{tabular}
-		\end{center}
-		\label{table:disaggregation_proportional}
-	\end{table}
-
-	\begin{table}[htb]
-		\caption{Value of the coefficient of determination between the reconstructed 6-hourly precipitation time series using the listed variables and the accurate time series for the period 1982\textendash 2007.
-The grid points surrounding the region are: 1) 5\textdegree\ E, 47.5\textdegree\ N; 2) 5\textdegree\ E, 45\textdegree\ N; 3) 7.5\textdegree\ E, 47.5\textdegree\ N; and 4) 7.5\textdegree\ E, 45\textdegree\ N.
-The highest coefficient of determination is indicated in bold.}
-		\begin{center}
-			\begin{tabular}{l c c c c c c}
-				\hline
-				\multirow{2}{*}{Variable} & \multirow{2}{*}{Point} &  \multicolumn{5}{c}{Time lapse} \\
-				&  & \textendash 12 h & \textendash 6 h & 0 h & +6 h & +12 h \\ 
-				\hline
-				\multirow{ 4}{*}{RH1000} & 1 & 0.668 & 0.669 & 0.684 & 0.683 & 0.670 \\
-				& 2 & 0.669 & 0.669 & 0.683 & 0.681 & 0.669 \\
-				& 3 & 0.662 & 0.673 & 0.691 & 0.682 & 0.673 \\
-				& 4 & 0.666 & 0.671 & 0.688 & 0.681 & 0.668 \\ \hline
-				\multirow{ 4}{*}{RH925} & 1 & 0.672 & 0.673 & 0.684 & 0.684 & 0.675 \\
-				& 2 & 0.674 & 0.674 & 0.683 & 0.682 & 0.672 \\
-				& 3 & 0.662 & 0.673 & 0.691 & 0.682 & 0.673 \\
-				& 4 & 0.666 & 0.671 & 0.689 & 0.681 & 0.668 \\ \hline
-				\multirow{ 4}{*}{RH850} & 1 & 0.675 & 0.675 & 0.679 & 0.678 & 0.671 \\
-				& 2 & 0.681 & 0.690 & 0.691 & 0.677 & 0.664 \\
-				& 3 & 0.665 & 0.680 & 0.693 & 0.683 & 0.675 \\
-				& 4 & 0.675 & 0.694 & 0.706 & 0.681 & 0.659 \\ \hline
-				\multirow{ 4}{*}{TCW} & 1 & 0.688 & 0.687 & 0.667 & 0.655 & 0.652 \\
-				& 2 & 0.697 & 0.699 & 0.669 & 0.644 & 0.644 \\
-				& 3 & 0.686 & 0.708 & 0.689 & 0.655 & 0.648 \\
-				& 4 & 0.696 & \textbf{0.721} & 0.696 & 0.643 & 0.636 \\ \hline
-			\end{tabular}
-		\end{center}
-		\label{table:proxy_correlations}
-	\end{table}
-
-	\begin{table}[htb]
-		\caption{Values of the CRPSS (\%) score for Zermatt for the original and the recalibrated parameters (with the sequential method, as described in Sect.
-\ref{sec:introduction}) using the MTW approach on the disaggregated precipitation time series (short and long periods) by means of proxy variables from the reanalysis dataset.}
-		\begin{center}
-			\begin{tabular}{l c c c c}
-				\hline
-				\multirow{2}{*}{Period} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
-				& original & recalib. & original & recalib. \\
-				\hline
-				1982\textendash 2007 & 22.57 & 23.14 & 27.11 & 27.71 \\
-				1961\textendash 2008 & 23.81 & 24.38 & 28.42 & 28.86 \\
-				\hline
-			\end{tabular}
-		\end{center}
-		\label{table:proxy_CRPSS}
 	\end{table}

### 2017-03-27 Moving temporal window - HESS/template.tex
HESS paper under work.

@@
 Therefore, if the reduction of the archive length needed by the MTW, due to the reduced availability of a sub-daily precipitation time series, is expected to decrease the AM performance, the archive inflation brought by the MTW is expected to contribute to an increase in performance.
+
+	%TODO: improve
+	One can question the interest of using moving daily totals when 6-hourly precipitation series can be predicted instead.
+However, the 6-hourly time series generated by the AM might not represent accurately the intra-daily precipitation distribution (results not shown).
+In addition, sometimes a resolution finer than the daily time step is not needed and another disaggregation technique may be used afterwards.
+Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact than 24h daily totals.
 
@@
 		\item Recalibrated: The parameters of the AMs were reassessed after the introduction of the MTW at different time steps.
-This allowed to improve the prediction skill of the AMs by adapting to the new information available through the MTW.
-The characterization of the analogy might thus change (different spatial windows and number of analogues).
+Indeed, one can assume that the introduction of the MTW might change the optimum value of some parameters (different spatial windows and number of analogues).
+The calibration (see Sect.
+\ref{sec:calibration}) was then be reprocessed to adapt the AMs to the new information available through the MTW.
+The main difference was the increase of the optimal number of analogues, which is discussed in Sect.
+\ref{sec:increase_analognb}.
 	\end{itemize}
@@
 
-	\subsubsection{Changes in the analogy criteria distributions}
-	\label{sec:changes_distributions}
+	First, the impact of the MTW on the selection of analogue dates is analyzed, independently of any precipitation data.
+This was done on the period 1982-2010, but could have been done on a longer period, as no sub-daily precipitation series is required at this stage.
+The results are presented for the Ulrichen station, but are very similar for all other stations.
+The original parameters were used here when assessing the impact of the MTW, no recalibration of the parameters took place.
 
-	\subsubsection{Changes in the atmospheric circulation analogy}
-	\label{sec:perf_2Z}
+	\subsubsection{Analogy of the atmospheric circulation}
+	\label{sec:changes_analogy_circul}
 
 	When searching for analogues in the first level of analogy, such as on the geopotential heights in the 2Z method (Sect.
-\ref{sec:analog_method}), there are 4 times as many candidates (even though not fully independent) with the MTW than before (Sect.
+\ref{sec:analog_method}), there are up to eight times as many candidates (even though not fully independent) with the MTW than before (Sect.
 \ref{sec:mtw}).
-Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions of the analogy criterion (S1) for the $1^{st}$, $5^{th}$, $20^{th}$, and $40^{th}$ analogue rank at the Ulrichen station over the whole calibration period (1961\textendash 2008 \textendash\ the full period could be used here, as precipitation was not considered at this stage), due to introduction of the MTW.
-The shape of the distributions of the conventional approach and the MTW were found to be similar, but the values of the analogy criterion were reduced (shifted to the left) and were, therefore, better.
+Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions, over the whole period, of the analogy criterion (S1) for the $1^{st}$, $15^{th}$, and $30^{th}$ analogue rank, due to introduction of an MTW with a 12h, 6h, or 3h time step.
+The shape of the distributions of the conventional approach and the MTWs were found to be similar, but the values of the analogy criterion were gradually reduced (shifted to the left) with smaller time steps MTWs and were, therefore, better.
+The circulation analogy seems to improve regularly with the doubling of the MTW time steps.
 For analogues with higher ranks (e.g.
-$20^{th}$ or $40^{th}$), the difference between the two distributions was larger than for the first ranks, which means that the improvement increased with the rank of the analogues.
+$15^{th}$ or $30^{th}$), the difference between the two distributions was larger than for the first rank, which means that the improvement increased with the rank of the analogues.
 
 	The improvements of the analogy with the rank of the analogues are summarized in Fig.
-\ref{fig:changes_S1}, which shows (top) quantiles of the S1 criterion for the conventional method and the MTW, and (bottom) quantiles of the relative reduction (meaning improvement) due to the MTW.
+\ref{fig:changes_S1}, which shows (top) quantiles of the S1 criterion for the conventional method and the MTWs at different time steps, and (bottom) quantiles of the relative reduction (meaning improvement) due to the MTWs.
 This confirms that all quantiles were similarly reduced (S1 distributions keep their shape), and that this improvement was constantly increasing from the first to the last analogue (Fig.
 \ref{fig:changes_S1} bottom).
+This increase in improvement with the analogue rank can be explained by the accumulation of better analogues in the selection, with new better situations pushing previous analogues to higher ranks.
+One can also see the regularity of the improvements brought by decreasing time steps.
+The introduction of the MTW allows finding better analogue situations in the first level of analogy, resulting in a selection of days with better similarity in atmospheric circulation.
+Moreover, this improvement is superior for MTWs with a smaller time step.
 
-	For the first level of analogy, the improvement of the S1 criterion (Fig.
-\ref{fig:changes_S1} bottom) started approximately at 5~\% for the first analogue and reached more than 10~\% for the last (40$^{th}$) (Sect.
-\ref{sec:perf_2Z}).
-This increase in improvement with the analogue rank can be explained by the accumulation of better analogues in the selection, with new better situations pushing previous analogues to higher ranks.
-The curve representing the minimum improvement is mostly superior to zero, meaning that the criteria have been improved on most analogue ranks for every day of the calibration period.
-All other stations had a similar improvement in the S1 criterion, both in terms of the distribution shape and amplitude.
-The introduction of the MTW allows finding better analogue situations in the first level of analogy, resulting in a selection of days with better similarity in atmospheric circulation.
-
-	When adding a second level of analogy with moisture variables, the criteria values (RMSE) were not improved by the MTW (Sect.
-\ref{sec:perf_2Z-2MI}), as the number of candidates was not higher (still the $N_{1}$ days selected in the first level of analogy).
-However, this result of a globally null improvement of the RMSE values does not mean that the 2Z-2MI method cannot be improved by the MTW.
-It means that after the selection of the analogue situations for the synoptic circulation, the new candidate dates did not provide better analogues in terms of moisture.
-However, the selected dates have changed in the first level of analogy and also in the final selection, and thus the distributions of precipitation values were different, which did improve the prediction skill (Sect.
-\ref{sec:influence_scores}).
-
-	The introduction of the MTW improved the selection of synoptic analogues.
-Independently of its impact on the prediction skill for precipitation, or the availability of a predictand time series with sub-daily time step, this improvement has a potential in itself for application on long meteorological archives.
-For example, when processing forecasts for a target day showing synoptic similarity with situations from the past related to extreme weather, even if for them no precipitation archive is available.
-Indeed, some of those days with strong precipitation events may be documented, either qualitatively in the daily press or more quantitatively in flood reports.
-It is thus worth to known that the situation at hand has had such analogue in the past.
-Another possible application is a quality assessment of the selection of analogues on a shorter period, where precipitation data with a high temporal resolution is available.
-Indeed, if the selection of analogues with the MTW on the long period, for a specific target day, differ from the selection on the short period, this may point out a sub-optimal forecast.
-Finally, other predictands might not need sub-daily total values, but point observations (e.g.
-hail, or extreme wind gusts), which make them easier to use with the MTW.
-
-	\subsubsection{Changes per precipitation class}
-	\label{sec:influence_precip}
-
-	The impact of the MTW on the analogy criterion has been analysed per precipitation classes (for the target day).
+	The impact of the MTW on the analogy criterion has been analysed per precipitation classes (for the target day) for a 6h-MTW and a 3h-MTW.
 The results are summarised in Fig.
@@
 With the number of cases per class being reduced, the curves are not as smooth as in previous analyses.
-It is nevertheless clear that the improvements were larger for days with higher precipitation.
-Once again, the results for all the other stations were similar.
+It is nevertheless clear that the improvements were larger for days with higher precipitation, for both the 6h-MTW and the 3h-MTW.
 
-	\subsubsection{Changes per season}
-	\label{sec:seasonal_effect}
+	The effect of the MTW on the S1 criterion has been decomposed per season and is presented in Fig.
+\ref{fig:changes_S1_seasons}.
+Differences between the seasons are substantial, with greater improvements for winter than summer.
+An analysis of the selected hours for the geopotential height predictor was then performed for the MTW with different time steps (Fig.
+\ref{fig:hours_selection_per_season}).
+It was found that the new choice of the temporal window in winter, when using the MTW approach, is more balanced between the different hours of the day (more regular repartition), and this for all time steps.
+This means a change in selection of a greater part of the analogue dates compared to the conventional approach.
+On the contrary, the days during the summer months had a preference for the initial temporal window (Z500 24~h \& Z1000 12~h), likely due to more pronounced diurnal effects, which reduced the potential for improvement of the criteria.
+This effect is in phase with the daily cycle, and good analogues are essentially found for the same hours.
+When a 3h-MTW is used, the time step following the initial temporal window (so Z500 27~h \& Z1000 15~h) is almost as often selected for all seasons.
+However, it can be considered as relatively similar in terms of the solar influence.
+The other seasons were between these two extremes, which is consistent with their respective improvements.
 
-	Atmospheric dynamics vary greatly from one season to another, reflecting on the performance of the AM that is generally lower between June and August \citep{Bliefernicht2010}.
-The effect of the MTW on the S1 criterion per season is presented in Fig.
-\ref{fig:changes_S1_seasons}.
-Differences between the seasons were substantial, with greater improvements for winter than summer.
-
-	Section \ref{sec:seasonal_effect} and Fig.
-\ref{fig:changes_S1_seasons} revealed a difference in the improvement of the S1 criterion according to the season, with greater improvements for winter than summer.
-One hypothesis is that the diurnal effects of the summer months have an influence on the atmospheric circulation at least in the lower layers.
-This effect is in phase with the daily cycle, and good analogues are essentially found for the same hours.
-
-	An analysis of the selected hours for the geopotential height predictor seems to confirm this assumption (Fig.
-\ref{fig:hours_selection_per_season}).
-It was found that the new choice of the temporal window in winter, when using the MTW approach, is well balanced between the four options.
-This means a change of 75~\% of the analogues selected compared to the conventional approach.
-On the contrary, the days during the summer months had a preference for the initial temporal window (Z500 24~h \& Z1000 12~h), likely due to more pronounced diurnal effects, which reduced the potential for improvement of the criteria.
-The other seasons were between these two extremes, which is consistent with their respective improvements.
-This seasonal effect was observed for each station in a very similar way and even with slightly larger amplitude than for Ulrichen.
-
-	\subsubsection{Changes in the moisture analogy}
-	\label{sec:perf_2Z-2MI}
+	\subsubsection{Moisture analogy}
+	\label{sec:changes_analogy_moisture}
 
@@
 In contrast to the AM on the atmospheric circulation only, both a reduction or an increase of the RMSE analogy criterion values were possible with the MTW compared to the static approach.
-Indeed, Fig.
-\ref{fig:changes_RMSE} shows an almost insignificant improvement of the RMSE values.
-Unlike the first level of analogy, the relative changes of the RMSE values were distributed relatively symmetrically around zero, with improvements and losses of the same amplitude.
+The results of the second level of analogy are presented in Fig.
+\ref{fig:changes_RMSE}, and show no improvement of the RMSE values, whatever the MTW time step.
+Unlike the first level of analogy, the relative changes of the RMSE values were distributed relatively symmetrically around zero.
 
-	\subsection{Impact of the MTW on prediction skill}
+	The criteria values (RMSE) of the second level of analogy (moisture variables) were not improved by the MTW, as the number of candidates was not higher (still the $N_{1}$ days selected in the first level of analogy).
+However, this result of a globally null improvement of the RMSE values does not mean that the 2Z-2MI method cannot be improved by the MTW.
+It means that after the selection of the analogue situations for the synoptic circulation, the new candidate dates did not provide better analogues in terms of moisture.
+However, the selected dates have changed in the first level of analogy and also in the final selection, and thus the distributions of precipitation values were different.
+
+	\subsection{Impact of the MTW on the prediction skill}
 	\label{sec:influence_scores}
 
-	The new performance scores (CRPS) of the precipitation prediction are provided in Fig.
-\ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI} for the 2Z and 2Z-2MI methods, respectively, for the reduced archive (1982\textendash 2007).
+	The change in the performance score (CRPS) of the precipitation prediction are provided in Fig.
+\ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI} for the 2Z and 2Z-2MI methods, respectively.
+The AMs were here recalibrated on the CP, and assessed on the independent VP.
+The score was processed for each station and both reanalysis datasets.
+For ERA-20C, the 12h-MTW, 6h-MTW, and 3h-MTW could be assessed, while only the two first could be processed with the MERRA-2 dataset.
+
+	The MTW improves the precipitation prediction, as at least from a 6h-MTW the CRPS decreases for all stations, both on the CP and the VP.
+The VP shows a greater variability, likely related to the short period it represents (6 yr).
+The prediction skill on the CP is almost always improved further by reducing the time step of the MTW, but not of the same magnitude.
+For ERA-20C, the magnitude of the improvement of 2Z on the CP is relatively reduced when using a 3h-MTW instead of a 6h-MTW, and the variablility on the VP increases.
+However, as it was shown in Fig.
+\ref{fig:changes_S1}, the distribution of analogue dates was improved relatively equally for every reduction of the MTW time step.
+A possible explanation could be that the AMs rely on the geopotential at 500~hPa, while the ERA-20C dataset was build by only assimilating surface observations.
+Thus, the timing of the atmospheric circulation at higher pressure levels might not be completely in phase with the real perturbation systems that are linked with the observed precipitations.
+The MTW with the MERRA-2 dataset and the 2Z method also shows a certain slope break after the 12h-MTW, that could not be explained, and that is less important for the 2Z-2MI method.
+However, the 12h-MTW shows an important variability for the 2Z-2MI method and the MERRA-2 dataset.
+	Based on these results, the use of ERA-20C seems to be a better choice in order to apply an MTW, at least for the studied region.
+
+	The S1 criterion was previously found to show greater improvement for days with higher precipitation values (Sect.
+\ref{sec:influence_precip}).
+The changes in terms of prediction skill were also assessed for the precipitation classes.
+Fig.
+\ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, on the original parameters.
+The performance score was improved (reduced CRPS) for days with higher precipitation after the introduction of the MTW.
+In contrast, for non-rainy days and small precipitation values, the performance scores were not improved.
+The recalibration of the parameters tends to reduce the spread of the changes in CRPS, but with a slight loss in performance for the most rainy days.
+
+	%TODO: on the CP or the VP ? -> test on VP before/after recalib
+
+	\section{Discussion}
+	\label{sec:discussion}
+
+	\subsection{A better prediction of heavy precipitation}
+
+	Both the analogy criteria (Sect.
+\ref{sec:changes_analogy_circul}) and the performance scores (Sect.
+\ref{sec:influence_scores}) were improved to a greater extent for days with heavier precipitation.
+This is likely due to the fact that higher precipitation events are a consequence of atmospheric conditions with greater dynamics, such as weather disturbances, which have a well-marked temporal evolution.
+Indeed, the position of the driving elements, such as the low pressure centres and the fronts, change significantly during a day.
+These situations are less numerous than anticyclonic situations, which makes it less likely to find very good analogues at the same time of the day.
+We can, therefore, expect to improve these situations with greater dynamics more significantly when introducing a MTW, as better matches to the target situation may be found.
+In contrast, days with low dynamics in the atmospheric circulation, such as anticyclonic situations, will not be radically improved by the introduction of the MTW.
+
+	The MTW improved the prediction for days with heavier precipitation, and should improve the prediction of extremes due to better analogue situations, but also due to possible new extreme values resulting from 24h totals with a certain time shift.
+However, even though the distribution of analogue precipitation values should move towards the targeted extreme, providing a better prediction, the MTW itself does not allow to predict extreme events that were not yet observed and are, therefore, not present in the archive.
+The extremes in AMs can be modelled by, for example, extrapolation of a truncated exponential or gamma distribution fitted to the analogue values \citep{Obled2002}.
+Another possible approach is by combining AMs with other methods \citep[e.g.][]{Chardon2014}.
+From this perspective, the MTW might improve the prediction of extremes as it improves the distribution of precipitation values for days with higher precipitation, on which post-treatment techniques rely.
+However, this goes beyond the scope of the present study.
+
+	\subsection{The relationship between the MTW time step and the number of analogues}
+	\label{sec:increase_analognb}
+
+	When recalibrating the AMs with MTWs of different time steps, the optimal number of analogues changed for both 2Z and 2Z-2MI methods.
+$N_{1}$ and $N_{2}$, from the first and the second level of analogy, tend to significantly increase with the reduction of the time step of the MTW (Fig.
+\ref{fig:analog_nb}).
+When using ERA-20C, all optimal numbers of analogues (for the different analogy levels) tend in average to double when using a 6h-MTW instead of the classic approach, and to even triple when using a 3h-MTW.
+These higher numbers of analogues were objectivel chosen by the calibration procedure (Sect.
+\ref{sec:calibration}) in order to increase the prediction skill of the methods.
+
+	A higher number of analogues generally means, with an archive of fixed length, a poorer analogy.
+Indeed, when the choice of the predictors or the parameters are improved, leading to a better prediction, the optimal number of analogue situations decreases.
+However, when the length of the archive increases, the optimal number of analogues increases too for a better performance up to a certain threshold \citep[][]{Bontron2004, Hamill2006a}.
+The observed increase in the number of analogue situations with the MTW resulted in better performance skills for the given methods, as it can be seen as an inflation of the archive.
+However, if new relevant predictors were added to the method, the number of analogues would then decrease.
+
+	As shown in Fig.
+\ref{fig:changes_S1}, the improvement of the S1 criterion grows along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions.
+It seems profitable to widen the selection of analogues in order to also keep some whose rank has increased, as they appear to be relevant to the prediction of the precipitation values.
+The number of good analogues was globally increased.
+
+	\subsection{Inflation of the precipitation archive}
+	\label{sec:archive_reduction}
+
+	%TODO: do calculations of the conequence of the archive reduction
+	%TODO: rewrite this section
+
+	Since sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~year archive (1961\textendash 2008) to 25~years (1982\textendash 2007) can be expected.
+However, the competition between the loss of performance due to a smaller archive length and the potentially better analogy between target and MTW candidates needs to be assessed.
+
+	The performance loss resulting from the reduction of a 47~year archive (1961\textendash 2008, corresponding to the daily time series) to 25~years (1982\textendash 2007, corresponding to the hourly time series in Sect.
+\ref{sec:mtw}) was assessed with the original method without MTW.
+Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
+The AM parameters were calibrated on the original archive (see resulting analogue numbers in Fig.
+\ref{fig:analog_nb}) and were used thereafter.
+
+	The impact of the archive reduction can be seen in Fig.
+\ref{fig:plots_CRPS_2Z} for the 2Z method and in Fig.
+\ref{fig:plots_CRPS_2Z-2MI} for the 2Z-2MI method.
+As expected, a loss of performance was observed for each station, except for that of Aigle, which seemed relatively indifferent to this change.
+This loss was globally significant, with up to \textendash 1.89 points (\% of CRPS) for Visp and the 2Z method.
 
@@
 
-	Both the analogy criteria (Sect.
-\ref{sec:influence_precip}) and the performance scores (Sect.
-\ref{sec:improvement_CRPS_precip_threshold}) were improved to a greater extent for days with heavier precipitation.
-This is likely due to the fact that higher precipitation events are a consequence of atmospheric conditions with greater dynamics, such as weather disturbances, which have a well-marked temporal evolution.
-Indeed, the position of the driving elements, such as the low pressure centres and the fronts, change significantly during a day.
-These situations are less numerous than anticyclonic situations, which makes it less likely to find very good analogues at the same time of the day.
-We can, therefore, expect to improve these situations with greater dynamics more significantly when introducing a MTW, as better matches to the target situation may be found.
-In contrast, days with low dynamics in the atmospheric circulation, such as anticyclonic situations, will not be radically improved by the introduction of the MTW.
-
-	The MTW improved the prediction for days with heavier precipitation, and should improve the prediction of extremes due to better analogue situations, but also due to possible new extreme values resulting from 24h totals with a certain time shift.
-However, even though the distribution of analogue precipitation values should move towards the targeted extreme, providing a better prediction, the MTW itself does not allow to predict extreme events that were not yet observed and are, therefore, not present in the archive.
-The extremes in AMs can be modelled by, for example, extrapolation of a truncated exponential or gamma distribution fitted to the analogue values \citep{Obled2002}.
-Another possible approach is by combining AMs with other methods \citep[e.g.][]{Chardon2014}.
-From this perspective, the MTW might improve the prediction of extremes as it improves the distribution of precipitation values for days with higher precipitation, on which post-treatment techniques rely.
-However, this goes beyond the scope of the present study.
-
-	\subsubsection{Improvement per precipitation classes}
-	\label{sec:improvement_CRPS_precip_threshold}
-
-	The S1 criterion was previously found to show greater improvement for higher precipitation values (Sect.
-\ref{sec:influence_precip}).
-The changes in terms of prediction skill were also assessed for the precipitation classes.
-Fig.
-\ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, with the other stations having the same behaviour.
-The performance score was improved for days with higher precipitation after the introduction of the MTW.
-In contrast, for non-rainy days and small precipitation values, the performance scores were not improved.
-
-	\subsubsection{Recalibration of AM parameters}
-	\label{sec:recalibration}
-
-	The previous assessment of the performance improvement was established with the original parameters optimized with a fixed time window.
-However, one can assume that the introduction of the MTW might change the optimum value of some parameters.
-The calibration (see Sect.
-\ref{sec:calibration}) should then be reprocessed.
-
-	After recalibrating, changes in the AM parameters could be observed for both the 2Z and 2Z-2MI methods.
-Among these, the zonal extent of the spatial windows of the circulation analogy decreased slightly (not shown).
-More significantly, the optimal number of analogues $N_{1}$ and $N_{2}$ increased after introducing the MTW by a considerable magnitude (Fig.
-\ref{fig:analog_nb}): 25~\% to 83~\% for the 2Z method and 20~\% to 67~\% for the final selection of the 2Z-2MI method.
-The number of analogues $N_{1}$ of the first analogy level of the 2Z-2MI method reached three times its previous value for the Visp station ($N_{1}$~=~135 instead of 45; Fig.
-\ref{fig:analog_nb}).
-
-	The values of the CRPS scores for both methods (Fig.
-\ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI}) have significantly increased after recalibration.
-When analysing the change in performance per precipitation class, the results (not shown) were very similar to the observations in Sect.
-\ref{sec:improvement_CRPS_precip_threshold}, with a slight performance increase for small precipitation values that can be observed at the expense of higher amounts, due to the higher number of analogues.
-
-	\section{Discussion}
-	\label{sec:discussion}
-
-	\subsection{Consequences of the archive reduction}
-	\label{sec:archive_reduction}
-
-	Since sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~year archive (1961\textendash 2008) to 25~years (1982\textendash 2007) can be expected.
-However, the competition between the loss of performance due to a smaller archive length and the potentially better analogy between target and MTW candidates needs to be assessed.
-
-	The performance loss resulting from the reduction of a 47~year archive (1961\textendash 2008, corresponding to the daily time series) to 25~years (1982\textendash 2007, corresponding to the hourly time series in Sect.
-\ref{sec:mtw}) was assessed with the original method without MTW.
-Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
-The AM parameters were calibrated on the original archive (see resulting analogue numbers in Fig.
-\ref{fig:analog_nb}) and were used thereafter.
-
-	The impact of the archive reduction can be seen in Fig.
-\ref{fig:plots_CRPS_2Z} for the 2Z method and in Fig.
-\ref{fig:plots_CRPS_2Z-2MI} for the 2Z-2MI method.
-As expected, a loss of performance was observed for each station, except for that of Aigle, which seemed relatively indifferent to this change.
-This loss was globally significant, with up to \textendash 1.89 points (\% of CRPS) for Visp and the 2Z method.
-
-	\subsection{On the increase in the number of analogues}
-
-	After the recalibration of the AMs with the MTW, the optimal analogue numbers were significantly higher than in the original methods (see Sect.
-\ref{sec:recalibration} and Fig.
-\ref{fig:analog_nb}).
-As shown in Fig.
-\ref{fig:changes_S1}, the improvement of the S1 criterion grew along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions.
-It seems profitable to widen the selection of analogues in order to also keep some whose rank has increased, as they appear to be relevant to the prediction of the precipitation values.
-The number of good analogues was globally increased.
-
-	A higher number of analogues generally means, with an archive of fixed length, a poorer analogy.
-Indeed, when the choice of the predictors or the parameters are improved, leading to a better prediction, the optimal number of analogue situations decreases.
-However, when the length of the archive increases, the optimal number of analogues increases too for a better performance up to a certain threshold \citep[][]{Bontron2004, Hamill2006a}.
-The observed increase in the number of analogue situations with the MTW resulted in better performance skills for the given methods, as it can be seen as an inflation of the archive.
-However, if new relevant predictors were added to the method, the number of analogues would then decrease.
-
-	\subsection{Why not just make 6-hourly predictions?}
-
-	One can question the interest of using moving daily totals when 6-hourly precipitation series can be predicted instead.
-However, the 6-hourly time series generated by the AM might not represent accurately the intra-daily precipitation distribution (results not shown).
-In addition, sometimes a resolution finer than the daily time step is not needed and another disaggregation technique may be used afterwards.
-Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact than 24h daily totals.
-
-	\subsection{Reconstruction of a longer precipitation archive}
+	\subsection{Reconstruction of a long precipitation archive suitable for the MTW}
 	\label{sec:reconstruction}
@@
 Without a precipitation series with an accurate sub-daily chronology, the introduction of a MTW does not improve the precipitation prediction.
+
+	The introduction of the MTW improved the selection of synoptic analogues.
+Independently of its impact on the prediction skill for precipitation, or the availability of a predictand time series with sub-daily time step, this improvement has a potential in itself for application on long meteorological archives.
+For example, when processing forecasts for a target day showing synoptic similarity with situations from the past related to extreme weather, even if for them no precipitation archive is available.
+Indeed, some of those days with strong precipitation events may be documented, either qualitatively in the daily press or more quantitatively in flood reports.
+It is thus worth to known that the situation at hand has had such analogue in the past.
+Another possible application is a quality assessment of the selection of analogues on a shorter period, where precipitation data with a high temporal resolution is available.
+Indeed, if the selection of analogues with the MTW on the long period, for a specific target day, differ from the selection on the short period, this may point out a sub-optimal forecast.
+Finally, other predictands might not need sub-daily total values, but point observations (e.g.
+hail, or extreme wind gusts), which make them easier to use with the MTW.
 
@@
 
-	\begin{figure}[htb]
-		\includegraphics[width=8.3cm]{fig03.pdf}
-		\caption{Performance score (CRPS) of the AM on the atmospheric circulation at the different stations for (dashed) the full archive, i.e.
-1961\textendash 2008; (yellow) the reduced archive, i.e.
-1982\textendash 2007; (blue) the introduction of the MTW on the reduced archive; and (green) the recalibrated parameters of the AM with the MTW.}
-		\label{fig:plots_CRPS_2Z}
-	\end{figure}
-
-	\begin{figure}[htb]
-		\includegraphics[width=8.3cm]{fig04.pdf}
-		\caption{Same as Figure \ref{fig:plots_CRPS_2Z}, but for the analogue method with a second level with the moisture variables.}
-		\label{fig:plots_CRPS_2Z-2MI}
-	\end{figure}
-
 	\begin{figure*}[htb]
@@
 	\begin{figure}[htb]
+		\includegraphics[width=7.5cm]{fig11.pdf}
+		\caption{Distribution of the predictor hours on the selected analogue dates, when using the MTW, depending on the season for the Ulrichen station.}
+		\label{fig:hours_selection_per_season}
+	\end{figure}
+
+	\begin{figure}[htb]
 		\begin{center}
@@
 	\begin{figure}[htb]
+		\includegraphics[width=8.3cm]{fig03.pdf}
+		\caption{Performance score (CRPS) of the AM on the atmospheric circulation at the different stations for (dashed) the full archive, i.e.
+1961\textendash 2008; (yellow) the reduced archive, i.e.
+1982\textendash 2007; (blue) the introduction of the MTW on the reduced archive; and (green) the recalibrated parameters of the AM with the MTW.}
+		\label{fig:plots_CRPS_2Z}
+	\end{figure}
+
+	\begin{figure}[htb]
+		\includegraphics[width=8.3cm]{fig04.pdf}
+		\caption{Same as Figure \ref{fig:plots_CRPS_2Z}, but for the analogue method with a second level with the moisture variables.}
+		\label{fig:plots_CRPS_2Z-2MI}
+	\end{figure}
+
+	\begin{figure}[htb]
 		\includegraphics[width=8.3cm]{fig10.pdf}
@@
 		\label{fig:changes_CRPS_precip_threshold}
-	\end{figure}
-
-	\begin{figure}[htb]
-		\includegraphics[width=7.5cm]{fig11.pdf}
-		\caption{Distribution of the predictor hours on the selected analogue dates, when using the MTW, depending on the season for the Ulrichen station.}
-		\label{fig:hours_selection_per_season}
 	\end{figure}

### 2017-03-27 Moving temporal window - HESS/template.tex
HESS paper under work.

@@
 It will thus differ between circulation and moisture variables.
-		\item The optimal number of analog situations for every level of analogy.
+		\item The optimal number of analogue situations for every level of analogy.
 	\end{itemize}
@@
 
-	%TODO: on the CP or the VP ? -> test on VP before/after recalib
-
 	\section{Discussion}
@@
 
-	\subsection{Inflation of the precipitation archive}
+	\subsection{Inflation of the archive}
 	\label{sec:archive_reduction}
 
-	%TODO: do calculations of the conequence of the archive reduction
-	%TODO: rewrite this section
+	Since sub-daily precipitation time series are often available on a shorter period than daily ones, this implies a reduction of the archive length at disposal for the search of analogue situations.
+This usually has a negative consequence on the skill of precipitation prediction.
+The role of the archive length has been assessed on the ERA-20C dataset and is presented in Fig.
+\ref{fig:plots_archive_length} for both 2Z and 2Z-2MI methods, using the conventional approach (24h windows).
+As expected, the performance of the method globally increases with the length of the archive.
+The best performances are found with a 44 yr archive, corresponding to the period 1961--2010, minus the 6 years of independant data set apart for validation.
+This addition of 21~yr of archive to the original 23~yr results in an improvement of both 2Z and 2Z-2MI methods that is of the same order of magnitude as the introduction of a 6h-MTW (Fig.
+\ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI}).
+The 3h-MTW resulted in similar performance for the 2Z method and slight improvements for the 2Z-2MI method.
 
-	Since sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~year archive (1961\textendash 2008) to 25~years (1982\textendash 2007) can be expected.
-However, the competition between the loss of performance due to a smaller archive length and the potentially better analogy between target and MTW candidates needs to be assessed.
-
-	The performance loss resulting from the reduction of a 47~year archive (1961\textendash 2008, corresponding to the daily time series) to 25~years (1982\textendash 2007, corresponding to the hourly time series in Sect.
-\ref{sec:mtw}) was assessed with the original method without MTW.
-Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered.
-The AM parameters were calibrated on the original archive (see resulting analogue numbers in Fig.
-\ref{fig:analog_nb}) and were used thereafter.
-
-	The impact of the archive reduction can be seen in Fig.
-\ref{fig:plots_CRPS_2Z} for the 2Z method and in Fig.
-\ref{fig:plots_CRPS_2Z-2MI} for the 2Z-2MI method.
-As expected, a loss of performance was observed for each station, except for that of Aigle, which seemed relatively indifferent to this change.
-This loss was globally significant, with up to \textendash 1.89 points (\% of CRPS) for Visp and the 2Z method.
-
-	The MTW was found to improve the skill of the precipitation prediction for both the 2Z and 2Z-2MI methods (Fig.
-\ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI}, Sect.
-\ref{sec:influence_scores}).
-Moreover, it required no additional predictor.
-With the introduction of the MTW, the performance loss related to the reduction of the archive length was negated (considering a 25 year archive of sub-daily data; the difference could be higher with a shorter archive).
-It was in this case of the same magnitude as if the length of the archive doubled.
+	As the MTW provides additional situations to the pool of possible analogues, it can be seen as an inflation of the archive.
+With the introduction of the MTW, the performance loss related to an eventual reduction of the archive length (to meet the length of the subdaily precipitation archive) was compensated.
+A 6h-MTW brought gains of the same magnitude as if the length of the archive doubled.
 Note, that despite the number of candidate situations being 4 times as many, the gains seem to be lower than for a quadrupled archive length.
@@
 The MTW, therefore, did not create 4 times as many independent data, but the increase in information was nevertheless substantial.
-In this regards, a reanalysis dataset with a higher temporal resolution might not improve the performance significantly more than a 6-hourly dataset.
-In contrast, reducing the MTW to a 12-hour time step might reduce redundancy in the archive, but might also reduce the chance of finding better analogue situations, as circulation patterns can evolve substantially in 12~hours.
 
+	Many reanalysis datasets start in the 80s due to availability of satellite data, and are thus more accurate than reanalysis datasets based on conventional data, but provide a shorter archive length.
+When using such an archive, the MTW approach shows a certain potential to enrich the pool of possible analogues.
 Moreover, in a transient climate, an eventual nonstationarity of the link between predictors and precipitation might discard the relevance of analogues from the distant past and increase the relevance of using a more recent and shorter archive rather than a long one.
@@
 
-	It would be profitable to be able to apply the MTW to a longer archive (here, 1961\textendash 2008), rather than being limited to the reduced period where the sub-daily precipitation data are available (cf.
-previous section).
-Therefore, in order to reconstruct a longer archive of moving 24h totals, two simple disaggregation approaches of the daily precipitation time series were assessed.
+	As we saw in Sect.
+\ref{sec:archive_reduction}, the skills of AMs improve with the length of the archive.
+It would then be even more profitable to apply the MTW to the longest archive possible, rather than being limited to the period where the sub-daily precipitation data are available.
+Therefore, in order to reconstruct longer archives of moving 24h totals, disaggregation techniques might be used.
+Where, two simple disaggregation approaches of the daily precipitation time series were assessed.
 
@@
 Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and a time lapse between both series was allowed to take into account the significant distance separating the weather stations and the reanalysis grid point.
-The best proxy variable was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series over the period 1982\textendash 2007.
+The best proxy variable, which was precipitable water, was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series.
 Once the best proxy had been selected, its temporal profile was used in order to disaggregate the daily precipitation time series.
 
-	The reconstructed time series cover the full period.
-However, they were first assessed using the MTW on the reduced period in order be comparable with the real sub-daily precipitation time series, and thus to evaluate their relevance and the possible loss in performance score.
-
-	When using the first reconstructed time series based on the proportional distribution (see Sect.
-\ref{sec:reconstruction}), the AM performance was degraded and was even below the conventional method without MTW.
-
-	For the second approach, the synoptic proxy for the temporal disaggregation of the daily time series had to be identified first.
-The results are illustrated this time for the Zermatt station.
-Among the considered moisture variables (see Sect.
-\ref{sec:reconstruction}), the best proxy was the precipitable water at 45\textdegree\ N and 7.5\textdegree\ E, with a time offset of \textendash 6~h.
-xx presents the CRPS scores obtained by the disaggregated series using the proxy of precipitable water which are also lower than the conventional method.
-
-	The two simple methods assessed to reconstruct precipitation archives (Sect.
-\ref{sec:reconstruction}) did not result in valuable outputs (Sect.
-\ref{sec:reconstruction_results}).
+	These two simple methods assessed to reconstruct precipitation archives did not result in valuable outputs (results not shown).
 Indeed, the performance improvement brought by the MTW was lost due to the poor quality of the precipitation archives.
 A slight improvement could be obtained for the second method relying on a proxy variable compared to the proportional distribution method, but it was still relatively small, and most of the benefit of the MTW was lost.
-A more recent reanalysis archive with more accurate moisture variables might produce better proxies.
+Another reanalysis dataset with more accurate moisture variables might produce better proxies.
 
@@
 		\includegraphics[width=8.3cm]{fig03.pdf}
-		\caption{Performance score (CRPS) of the AM on the atmospheric circulation at the different stations for (dashed) the full archive, i.e.
-1961\textendash 2008; (yellow) the reduced archive, i.e.
-1982\textendash 2007; (blue) the introduction of the MTW on the reduced archive; and (green) the recalibrated parameters of the AM with the MTW.}
+		\caption{Change in performance score (CRPS -- lower is better) of the 2Z method at the different stations for MTW of varying time steps relatively to the conventional approach (24h).
+Results are provided for ERA-20C on (a) the CP and (b) the VP, as well as for MERRA-2 on (c) the CP and (d) the VP.}
 		\label{fig:plots_CRPS_2Z}
@@
 		\includegraphics[width=8.3cm]{fig04.pdf}
-		\caption{Same as Figure \ref{fig:plots_CRPS_2Z}, but for the analogue method with a second level with the moisture variables.}
+		\caption{Same as Figure \ref{fig:plots_CRPS_2Z}, but for the 2Z-2MI method.}
 		\label{fig:plots_CRPS_2Z-2MI}
@@
 		\includegraphics[width=7.5cm]{fig12.pdf}
-	\caption{Optimal number of analogues (of the first and second level of analogy, respectively, $N_{1}$ and $N_{2}$) of the method based on the atmospheric circulation only (method 2Z) and the method with a second level of analogy with moisture variables (2Z-2MI) on the full archive (Standard), and after recalibration using the MTW (MTW-r).}
+		\caption{Optimal number of analogues (of the first and second level of analogy, respectively, $N_{1}$ and $N_{2}$) of the (a) 2Z and (b, c) 2Z-2MI methods after recalibration using the MTW.}
 		\label{fig:analog_nb}
+	\end{figure}
+
+	\begin{figure}[htb]
+		\includegraphics[width=8.3cm]{fig13.pdf}
+		\caption{Change in performance score (CRPS -- lower is better) of the (a, b) 2Z and (c, d) 2Z-2MI methods at the different stations on the (a, c) CP and (b, d) VP, for an increasing archive length with the conventional approach (24h windows).}
+		\label{fig:plots_archive_length}
 	\end{figure}

### 2017-03-27 Moving temporal window - HESS/template.tex
HESS paper under work.

@@
 		The search for candidate situations for a given target day is usually undertaken by comparing the state of the atmosphere at fixed hours of the day for both the target day and the candidate analogues.
-The main reason is the use of daily precipitation time series due to the length of their available archives, and the unavailability of equivalent archives at a finer time step.
-However, it is unlikely for the best analogy to occur at the very same hour, while it may be found with a time shift of some hours as it can occur at a different time of day.
+This is a consequence of using daily precipitation time series, which are available on longer periods than subdaily data.
+However, it is unlikely for the best analogy to occur at the very same hour.
+A better analogue situation may be found with a time shift of some hours as it can occur at a different time of day.
 In order to assess the potential for finding better analogues at a different hour, a moving time window (MTW) has been introduced.
@@
 
-	Analogue methods (AMs) are based on the hypothesis that two relatively similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}.
-They are statistical downscaling methods \citep{Maraun2010} and consist of finding past situations that are similar to the target day of interest in terms of the atmospheric circulation or other synoptic predictors.
+	The	Analogue method (AM) is based on the hypothesis that two relatively similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}.
+It is a statistical downscaling methods \citep{Maraun2010} and consist of finding past situations that are similar to the target day of interest in terms of the atmospheric circulation or other synoptic predictors.
 The local weather variables of interest (predictand) that were observed at the analogue dates are used to construct a probabilistic prediction for the target day \citep{Duband1970, Zorita1999}.
@@
 The AMs are used for operational precipitation forecasting, either in the context of weather forecasting, flood forecasting, or hydropower production \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as for precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}.
-Other applications focus on temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}.
-
-	The spatial transferability of the method is analysed in \citet{Chardon2014} and \citet{Radanovics2013}.
-A great advantage of AMs is that they create realistic precipitation patterns, since they are based on observed situations with consistent spatial distribution, as long as the analogue dates chosen for a region are the same.
-Moreover, they can provide multivariate predictions that are physically consistent \citep{Raynaud2016b}.
+Other applications focus on temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, and solar power \citep{Alessandrini2015a, Bessa2015}.
+AMs can provide multivariate predictions that are physically consistent \citep{Raynaud2016b}.
+Their spatial transferability is analysed in \citet{Chardon2014} and \citet{Radanovics2013}.
 Their temporal transferability has also been the topic of recent studies for past or future climates \citep{Dayon2015, Caillouet2016}.
@@
 The first is a meteorological archive describing the state of the atmosphere at a synoptic scale, such as reanalysis datasets.
-The second is an archive of the target variable to be forecast, here precipitation.
+The second is an archive of the target variable to be predicted, here precipitation.
 This archive is made of precipitation cumulated over a certain time duration, most often daily but sometimes sub-daily, either at a target station or integrated over a target catchment.
@@
 They highlighted a three-way relationship between the quality of the analogy, the archive length, and the size of the spatial domain (or degrees of freedom): errors increase with a bigger domain, but decrease with a longer archive.
-They demonstrated that it is not possible to find good analogues over the whole northern hemisphere with a 100 year archive (and even for much higher orders of magnitude).
-Hopefully, it appears that for the aim of predicting precipitation over point stations or catchments of some 100 or 1000 km\texttwosuperior, there is no need to consider meteorological domains larger than 10\textdegree\ to 20\textdegree.
-For that reason, smaller spatial windows are always considered when searching for analogues, and the archive length is maximized.
+For that reason, limited spatial windows are always considered when searching for analogues, and the archive length is maximized.
 
@@
 
+	One can question the interest of using moving daily totals when 6-hourly precipitation series can be predicted instead.
+However, the 6-hourly time series generated by the AM might not represent accurately the intra-daily precipitation distribution.
+In addition, sometimes a resolution finer than the daily time step is not needed and another disaggregation technique may be used afterwards.
+Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact than 24h daily totals.
+
 	The MTW finds analogue situations at different hours of the day, which can also be seen as an inflation of the archive length.
@@
 Nevertheless, if the MTW can improve the prediction skill of the AM, it means that it does extract new information from the archive.
-Therefore, if the reduction of the archive length needed by the MTW, due to the reduced availability of a sub-daily precipitation time series, is expected to decrease the AM performance, the archive inflation brought by the MTW is expected to contribute to an increase in performance.
-
-	%TODO: improve
-	One can question the interest of using moving daily totals when 6-hourly precipitation series can be predicted instead.
-However, the 6-hourly time series generated by the AM might not represent accurately the intra-daily precipitation distribution (results not shown).
-In addition, sometimes a resolution finer than the daily time step is not needed and another disaggregation technique may be used afterwards.
-Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact than 24h daily totals.
 
@@
 AMs can also be combined with other methods \citep[see e.g.][]{Chardon2014}.
-Another possibility is to use a global optimization technique, such as genetic algorithms, in order to better optimize the method and to add new parameters \citep{Horton2016}.
+Another possibility is to use a global optimization technique, such as genetic algorithms, in order to better optimize the method and to add new parameters \citep{Horton2017}.
 However, the MTW technique is not in competition with other approaches and can be combined with these.
-Indeed, as most of them rely on the atmospheric circulation in the first level of analogy, the application of a MTW should lead to similar conclusions.
 
 	Section \ref{sec:data_methods} presents the context of the study as well as the data and methods, including the proposed MTW technique.
-The impact of the reduction of the archive and the improvements brought by the MTW are assessed in Sect.
-\ref{sec:results}.
-The benefits of introducing a MTW were assessed first in regards to the analogy criterion improvement between synoptic situations (Sect.
+The benefits of introducing a MTW were assessed first in regards to the improvement of the analogue dates selection (Sect.
 \ref{sec:influence_analogue_dates}) and then in terms of precipitation prediction skill (Sect.
@@
 	More complex AMs exist with additional predictors \citep[see e.g.][]{Horton2012a, BenDaoud2016, Caillouet2016}.
-The MTW can also be applied to these, as they generally rely on a similarity of the atmospheric circulation in the first level of analogy.
+The MTW can also be applied to these.
 However, it is easier to interpret the impact of the MTW using more basic methods.
@@
 		\begin{enumerate}
-			\item Identification of the most skilled unitary cell (one point for moisture variables and four for geopotential heights when using the S1 criterion) over a large domain.
+			\item Identification of the most skilled unitary cell (one point for moisture variables and four for geopotential heights in order to process the gradients) over a large domain.
 Every point (or cell) of the full domain is assessed on all predictors of the level of analogy, jointly (consisting generally of the same variable but on different pressure levels and at different hours).
@@
 	The moving time window (MTW) technique aims at finding better analogue situations at different hours of the day rather than comparing the predictors at the same fixed hours.
-If the target situation is kept at 12:00 and 24:00~UTC for Z1000 and Z500 respectively, candidate situations are not only considered at 12:00 and 24:00~UTC, but at other hours by allowing a time shift.
-Therefore, instead of looking for analogues at a 24h time step, they are sought at the time step matching the predictor temporal resolution.
-The ERA-20C dataset made here possible to test a MTW with a 12h, 6h, or 3h time step (named respectively 12h-MTW, 6h-MTW, 3h-MTW hereafter; Fig.
+The target situation (the day to predict) is still the same as in the conventional approach, that is a daily precipitation total between 06:00 and 30:00~UTC, characterized by predictors which are e.g.
+Z1000 and Z500 at 12:00 and 24:00~UTC respectively.
+The difference is that candidate situations are not only considered at the same time (e.g.
+12:00 and 24:00~UTC), but at other hours by allowing a time shift.
+Therefore, instead of looking for analogues at a 24h time step, they are sought at the time step matching the predictor temporal resolution (Fig.
 \ref{fig:principle}).
+The ERA-20C dataset made here possible to test a MTW with a 12h, 6h, or 3h time step (named respectively 12h-MTW, 6h-MTW, 3h-MTW hereafter).
+Thus, the candidates are 2 (12h-MTW), 4 (6h-MTW), or 8 (3h-MTW) times as many (even though they are not fully independent) as in the conventional approach.
 
-	The target situations and their corresponding observed precipitation values do not change because the prediction is still established on a daily basis for a fixed period of the target day (6:00~UTC to 6:00~UTC the next day) as before.
-The difference is that the candidates are 2 (12h-MTW), 4 (6h-MTW), or 8 (3h-MTW) times as many (even though they are not fully independent) as in the conventional approach.
-No constraint was added in order to restrict the selection of multiple analogues within the same candidate dates.
-
+	The target situations and their corresponding observed precipitation values do not change.
+We then aim at predicting the exact same time series for the MTW and the conventional approach, so that the performance scores can be directly compared.
 In order to assess the benefit of searching for analogue situations at a sub-daily time step for quantitative precipitation prediction, an appropriate precipitation series is required.
@@
 \ref{sec:mtw}).
-Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions, over the whole period, of the analogy criterion (S1) for the $1^{st}$, $15^{th}$, and $30^{th}$ analogue rank, due to introduction of an MTW with a 12h, 6h, or 3h time step.
+Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions, for target dates over the whole period, of the analogy criterion (S1) for the $1^{st}$, $15^{th}$, and $30^{th}$ analogue rank, due to introduction of an MTW with a 12h, 6h, or 3h time step.
 The shape of the distributions of the conventional approach and the MTWs were found to be similar, but the values of the analogy criterion were gradually reduced (shifted to the left) with smaller time steps MTWs and were, therefore, better.
@@
 
-	When adding the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations did not increase, as they were conditioned by the $N_{1}$ previously selected analogues, but their dates had changed.
+	When adding the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations did not increase (when using the original parameters), as they were conditioned by the $N_{1}$ previously selected analogues, but their dates had changed.
 In contrast to the AM on the atmospheric circulation only, both a reduction or an increase of the RMSE analogy criterion values were possible with the MTW compared to the static approach.
@@
 	The criteria values (RMSE) of the second level of analogy (moisture variables) were not improved by the MTW, as the number of candidates was not higher (still the $N_{1}$ days selected in the first level of analogy).
+The use of an MTW does not increase the sample size in this case, the second level of analogy only subsamples in the dates provided by the first level.
 However, this result of a globally null improvement of the RMSE values does not mean that the 2Z-2MI method cannot be improved by the MTW.
@@
 \ref{sec:data}) were used for this purpose, despite their rough resolution (2.5\textdegree).
-Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment, and a time lapse between both series was allowed to take into account the significant distance separating the weather stations and the reanalysis grid point.
+Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment.
+Precipitation time series from the reanalysis was not considered due to the presence of zeros, which may not always match with the prediction, leading to an undefined temporal repartition.
+A time lapse (-12h to +12h) between both series was allowed to take into account the significant distance separating the weather stations and the reanalysis grid point.
 The best proxy variable, which was precipitable water, was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series.
@@
 		\end{center}
-		\caption{Changes in the S1 criterion distributions due to the introduction of a MTW with a 12~h, 6~h or 3~h time step.
+		\caption{Changes in the S1 criterion distributions due to the introduction of a MTW with a 12h, 6h or 3h time step.
 Distributions are provided for (a) the $1^{st}$, (b) $15^{th}$, and (c) $30^{th}$ analogue ranks for the Ulrichen station.}
@@
 		\end{center}
-		\caption{Synthesis of the changes in the S1 criterion due to the MTW (with a 12~h, 6~h, and 3~h time step) for the Ulrichen station depending on the rank of the analogue.
-(a) Quantiles of the S1 distributions corresponding to the MTW with different time steps (24~h is the standard approach without MTW).
+		\caption{Synthesis of the changes in the S1 criterion due to the MTW (with a 12h, 6h, and 3h time step) for the Ulrichen station depending on the rank of the analogue.
+(a) Quantiles of the S1 distributions corresponding to the MTW with different time steps (24h is the standard approach without MTW).
 (b) Quantiles of the relative improvements of the S1 criterion when using the MTW.}

### 2017-03-28 Moving temporal window - HESS/template.tex
HESS paper under work.

@@
 On the other hand, MERRA-2 has a higher spatial resolution and can be expected to be more correct at higher levels of the atmosphere.
+The variables extracted from these datasets are geopotential heights at 500~hPa (Z500) and 1000~hPa (Z1000), as well as the total precipitable water (TPW) and the relative humidity at 850~hPa (RH850).
 
@@
 
-	The S1 criterion was previously found to show greater improvement for days with higher precipitation values (Sect.
-\ref{sec:influence_precip}).
-The changes in terms of prediction skill were also assessed for the precipitation classes.
-Fig.
-\ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, on the original parameters.
-The performance score was improved (reduced CRPS) for days with higher precipitation after the introduction of the MTW.
-In contrast, for non-rainy days and small precipitation values, the performance scores were not improved.
-The recalibration of the parameters tends to reduce the spread of the changes in CRPS, but with a slight loss in performance for the most rainy days.
+	The introduction of an MTW was previously found to show greater improvement of the S1 criterion for days with higher precipitation values (Sect.
+\ref{sec:changes_analogy_circul}).
+The impact of the MTW was then assessed in terms of change of prediction skill, on the whole period, per precipitation classes (for the target day).
+Figure \ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, using the original parameters with the MTW.
+It shows that, after the introduction of the MTW, the performance score was in average further improved (reduced CRPS) for days with higher precipitation than for non-rainy days and small precipitation values.
+When recalibrating the parameters using the MTW, the spread of the changes in CRPS tended to decrease, but with a slight loss in performance for the most rainy days.
 

### 2017-03-29 Moving temporal window - HESS/template.tex
Renaming figures.
Analyzing the reliability diagrams.

@@
 
+	Reliability diagrams were also performed on the VP for both the 2Z and 2Z-2MI methods and for the exceedence of percentiles 80~\% (P80 -- 4~mm), 90~\% (P90 -- 9.5~mm), and 95~\% (P95 -- 17.5~mm) at the Ulrichen station (Fig.
+\ref{fig:reliability_diagrams}).
+Reliability diagrams plot the observed frequency against the predicted probability of a binary event -- a threshold exceedence in our case.	For perfectly calibrated predictions, the curve should be as close as possible to the diagonal.
+The VP only contains six years (Sect.
+\ref{sec:data_methods}), and thus higher variability is present for higher thresholds, the curves being smoother and closer to the diagonals for the CP, which is longer.
+Figure \ref{fig:reliability_diagrams} shows that the MTW improved the reliability for both 2Z and 2Z-2MI methods and for all thresholds, as the curves move toward the diagonal with a decreasing MTW time step.
+For P80, the 3h-MTW predictions fits very well the observations.
+When considering higher thresholds, the 2Z-2MI method is generall better than 2Z.
+The case of a P95 threshold shows a conditional dry bias associated with larger forecast probabilities for the considered AMs, which is however substantially reduced by the 3h-MTW.
+This conditional dry bias means here that the AM did not predict the event with a probability equal to 1 for example for 2Z.
+Obtaining a probability of 1 would mean that all analogue dates for a certain target date would be above the threshold.
+As the number of analogue dates is 30 in this case, it becomes less likely to have 30 values above the threshold when it increases.
+This issue is the topic of an ongoing work.
+However, as one can see in Figure \ref{fig:reliability_diagrams}e\&d, the introduction of an MTW, especially with a 3h timse step, improves partly this missmatch.
+
 	\section{Discussion}
@@
 		\begin{center}
-			\includegraphics[width=17cm]{fig05.pdf}
+			\includegraphics[width=17cm]{fig03.pdf}
 		\end{center}
@@
 		\begin{center}
-			\includegraphics[width=8.3cm]{fig06.pdf}
+			\includegraphics[width=8.3cm]{fig04.pdf}
 		\end{center}
@@
 		\begin{center}
-			\includegraphics[width=8.3cm]{fig07.pdf}
+			\includegraphics[width=8.3cm]{fig05.pdf}
 		\end{center}
@@
 		\begin{center}
-			\includegraphics[width=8.3cm]{fig08.pdf}
+			\includegraphics[width=8.3cm]{fig06.pdf}
 		\end{center}
@@
 	\begin{figure}[htb]
-		\includegraphics[width=7.5cm]{fig11.pdf}
+		\includegraphics[width=7.5cm]{fig07.pdf}
 		\caption{Distribution of the predictor hours on the selected analogue dates, when using the MTW, depending on the season for the Ulrichen station.}
@@
 		\begin{center}
-			\includegraphics[width=8.3cm]{fig09.pdf}
+			\includegraphics[width=8.3cm]{fig08.pdf}
 		\end{center}
@@
 	\begin{figure}[htb]
-		\includegraphics[width=8.3cm]{fig03.pdf}
+		\includegraphics[width=8.3cm]{fig09.pdf}
 		\caption{Change in performance score (CRPS -- lower is better) of the 2Z method at the different stations for MTW of varying time steps relatively to the conventional approach (24h).
@@
 	\begin{figure}[htb]
-		\includegraphics[width=8.3cm]{fig04.pdf}
+		\includegraphics[width=8.3cm]{fig10.pdf}
 		\caption{Same as Figure \ref{fig:plots_CRPS_2Z}, but for the 2Z-2MI method.}
@@
 	\begin{figure}[htb]
-		\includegraphics[width=8.3cm]{fig10.pdf}
+		\includegraphics[width=8.3cm]{fig11.pdf}
 		\caption{Differences of the CRPS performance score due to the introduction of the MTW as a function of daily precipitation thresholds at the Ulrichen station. The stars represent averages.}
@@
 
+	\begin{figure*}[htb]
+		\begin{center}
+			\includegraphics[width=14cm]{fig12.pdf}
+		\end{center}
+		\caption{Reliability diagrams for the (a, c, e) 2Z method and (b, d, f) the 2Z-2MI method and the prediction of the exceedence of percentiles (a, b) 80~\%, (c, d) 90~\% and (e, f) 95~\% at the Ulrichen station.
+The percentiles were processed on the whole period and the plots were established on the VP only.
+The conventional method (24h) is provided as well as the 12h-MTW, 6h-MTW and 3h-MTW.}
+		\label{fig:reliability_diagrams}
+	\end{figure*}
+
 	\begin{figure}[htb]
-		\includegraphics[width=7.5cm]{fig12.pdf}
+		\includegraphics[width=7.5cm]{fig13.pdf}
 		\caption{Optimal number of analogues (of the first and second level of analogy, respectively, $N_{1}$ and $N_{2}$) of the (a) 2Z and (b, c) 2Z-2MI methods after recalibration using the MTW.}
@@
 	\begin{figure}[htb]
-		\includegraphics[width=8.3cm]{fig13.pdf}
+		\includegraphics[width=8.3cm]{fig14.pdf}
 		\caption{Change in performance score (CRPS -- lower is better) of the (a, b) 2Z and (c, d) 2Z-2MI methods at the different stations on the (a, c) CP and (b, d) VP, for an increasing archive length with the conventional approach (24h windows).}

### 2017-03-29 Moving temporal window - HESS/template.tex
Updating figures.

@@
 	Section \ref{sec:data_methods} presents the context of the study as well as the data and methods, including the proposed MTW technique.
-The benefits of introducing a MTW were assessed first in regards to the improvement of the analogue dates selection (Sect.
+The benefits of introducing an MTW were assessed first in regards to the improvement of the analogue dates selection (Sect.
 \ref{sec:influence_analogue_dates}) and then in terms of precipitation prediction skill (Sect.
@@
 On the contrary, MERRA-2 is build by assimilating observations at higher levels and from more sensors, including satellite data, but is then more limited in time (1980\textendash present).
-It is of interest to assess the relevance of a MTW with these two datasets, as they represent different kind of products.
-The specific advantages of ERA-20C is that it allows testing a MTW with a 3h time step, and it covers a long period.
+It is of interest to assess the relevance of an MTW with these two datasets, as they represent different kind of products.
+The specific advantages of ERA-20C is that it allows testing an MTW with a 3h time step, and it covers a long period.
 On the other hand, MERRA-2 has a higher spatial resolution and can be expected to be more correct at higher levels of the atmosphere.
@@
 \ref{fig:principle}).
-The ERA-20C dataset made here possible to test a MTW with a 12h, 6h, or 3h time step (named respectively 12h-MTW, 6h-MTW, 3h-MTW hereafter).
+The ERA-20C dataset made here possible to test an MTW with a 12h, 6h, or 3h time step (named respectively 12h-MTW, 6h-MTW, 3h-MTW hereafter).
 Thus, the candidates are 2 (12h-MTW), 4 (6h-MTW), or 8 (3h-MTW) times as many (even though they are not fully independent) as in the conventional approach.
@@
 These situations are less numerous than anticyclonic situations, which makes it less likely to find very good analogues at the same time of the day.
-We can, therefore, expect to improve these situations with greater dynamics more significantly when introducing a MTW, as better matches to the target situation may be found.
+We can, therefore, expect to improve these situations with greater dynamics more significantly when introducing an MTW, as better matches to the target situation may be found.
 In contrast, days with low dynamics in the atmospheric circulation, such as anticyclonic situations, will not be radically improved by the introduction of the MTW.
@@
 The MTW is beneficial, provided that the precipitation series are close to the observed one.
-Without a precipitation series with an accurate sub-daily chronology, the introduction of a MTW does not improve the precipitation prediction.
+Without a precipitation series with an accurate sub-daily chronology, the introduction of an MTW does not improve the precipitation prediction.
 
@@
 
-	As \citet{Finet2008} had previously shown, the introduction of a MTW allows finding better analogue situations in terms of the atmospheric circulation.
+	As \citet{Finet2008} had previously shown, the introduction of an MTW allows finding better analogue situations in terms of the atmospheric circulation.
 It has been demonstrated in this study that the improvement of the S1 criterion values was growing with the rank of the analogue.
@@
 These situations have more specific circulation patterns that are evolving more rapidly.
-Therefore, a MTW was found to be of particular interest in this kind of situation, benefiting the prediction of heavier precipitation events.
+Therefore, an MTW was found to be of particular interest in this kind of situation, benefiting the prediction of heavier precipitation events.
 
@@
 		\end{center}
-		\caption{Position of the six weather stations of interest (Ulrichen, Zermatt, Visp, Montana, Sion, and Aigle) in the upper Rh\^{o}ne catchment in Switzerland.}
+		\caption{Position of the six weather stations of interest (Aigle, Montana, Sion, Ulrichen, Visp, and Zermatt) in the upper Rh\^{o}ne catchment in Switzerland.}
 		\label{fig:map}
@@
 		\end{center}
-		\caption{Illustration of the principle of a moving time window.
-The target situation is the same for the conventional approach and the MTW, while the candidate situations are 4 times as many with the MTW.
-The larger horizontal bars represent the 24h precipitation totals.}
+		\caption{Illustration of the principle of a moving time window (MTW).
+The target situation is the same for the conventional approach and the MTW, while the candidate situations are 2, 4, or 8 times as many with the MTW.
+The horizontal bars represent the 24h precipitation totals, with their associated predictors being listed on the right hand side.}
 		\label{fig:principle}
@@
 		\end{center}
-		\caption{Changes in the S1 criterion distributions due to the introduction of a MTW with a 12h, 6h or 3h time step.
-Distributions are provided for (a) the $1^{st}$, (b) $15^{th}$, and (c) $30^{th}$ analogue ranks for the Ulrichen station.}
+		\caption{Changes in the S1 criterion distributions due to the introduction of an MTW with a 12h, 6h or 3h time step.
+Distributions are provided for (a) the $1^{st}$, (b) $15^{th}$, and (c) $30^{th}$ analogue ranks for all days of the CP at the Ulrichen station.}
 		\label{fig:changes_S1_analogs}
@@
 		\caption{Synthesis of the changes in the S1 criterion due to the MTW (with a 12h, 6h, and 3h time step) for the Ulrichen station depending on the rank of the analogue.
-(a) Quantiles of the S1 distributions corresponding to the MTW with different time steps (24h is the standard approach without MTW).
-(b) Quantiles of the relative improvements of the S1 criterion when using the MTW.}
+(a) Quantiles of the S1 distributions corresponding to the MTW with different time steps (24h is the conventional approach without MTW).
+(b) Quantiles of the relative improvements of the S1 criterion when using the MTW, compared to the conventional approach.}
 		\label{fig:changes_S1}
@@
 		\end{center}
-		\caption{Distribution of the median improvements of the S1 criterion due to the MTW depending on daily precipitation thresholds at the Ulrichen station.}
+		\caption{Distribution of the median improvements of the S1 criterion due to the (a) 3h-MTW and (b) 6h-MTW, depending on daily precipitation thresholds at the Ulrichen station.}
 		\label{fig:changes_S1_precip_threshold}
@@
 		\includegraphics[width=7.5cm]{fig07.pdf}
-		\caption{Distribution of the predictor hours on the selected analogue dates, when using the MTW, depending on the season for the Ulrichen station.}
+		\caption{Distribution of the predictor hours on the selected analogue dates for the Ulrichen station when using a (a) 12h-MTW, (b) 6h-MTW, and (c) 3h-MTW, depending on the season.}
 		\label{fig:hours_selection_per_season}
@@
 		\includegraphics[width=8.3cm]{fig11.pdf}
-		\caption{Differences of the CRPS performance score due to the introduction of the MTW as a function of daily precipitation thresholds at the Ulrichen station. The stars represent averages.}
+		\caption{Differences of the CRPS performance score (lower is better) at the Ulrichen station due to the introduction of the MTW as a function of different daily precipitation thresholds (for the target date).
+The results are provided for (a, b) the 2Z method and (c, d) the 2Z-2MI method, and with a (a, c) 6h-MTW and a (b, d) 3h-MTW.
+The stars represent averages.}
 		\label{fig:changes_CRPS_precip_threshold}
@@
 		\end{center}
-		\caption{Reliability diagrams for the (a, c, e) 2Z method and (b, d, f) the 2Z-2MI method and the prediction of the exceedence of percentiles (a, b) 80~\%, (c, d) 90~\% and (e, f) 95~\% at the Ulrichen station.
-The percentiles were processed on the whole period and the plots were established on the VP only.
-The conventional method (24h) is provided as well as the 12h-MTW, 6h-MTW and 3h-MTW.}
+		\caption{Reliability diagrams for (a, c, e) the 2Z (b, d, f) the 2Z-2MI methods and the prediction of the exceedence of percentiles (a, b) 80~\%, (c, d) 90~\%, and (e, f) 95~\% at the Ulrichen station on the VP.
+The conventional approach (24h) is provided as well as the 12h-MTW, 6h-MTW and 3h-MTW.}
 		\label{fig:reliability_diagrams}
@@
 	\begin{figure}[htb]
-		\includegraphics[width=7.5cm]{fig13.pdf}
+		\includegraphics[width=8.3cm]{fig13.pdf}
 		\caption{Optimal number of analogues (of the first and second level of analogy, respectively, $N_{1}$ and $N_{2}$) of the (a) 2Z and (b, c) 2Z-2MI methods after recalibration using the MTW.}
@@
 		\caption{Parameters for the reference method on the atmospheric circulation (2Z).
-The first column is the level of analogy (0 for preselection), the second column is the meteorological variable, and then its hour of observation (temporal window).
+The first column is the level of analogy (0 for preselection), the second column is the meteorological variable, and then its hour of observation.
 The criterion used for the current level of analogy is then provided, as well as the number of analogues.}

### 2017-03-29 Moving temporal window - HESS/template.tex
HESS paper under work.

@@
 
-		The impact of the MTW on prediction skill has been assessed by means of a sub-daily precipitation series transformed into moving 24h totals at 6h time steps.
-The prediction skill was found to have improved by the MTW, and even to a greater extent after recalibrating the AM parameters.
-Moreover, the improvement was greater for days with heavy precipitation, which are generally related to more dynamic atmospheric situations where timing is more specific and which are fewer in the meteorological archive.
+		The impact of the MTW on the prediction skill has been assessed by means of a sub-daily precipitation series transformed into moving 24h totals at 12h, 6h, and 3h time steps.
+The prediction skill was found to have improved by the MTW, as well as the reliability of the prediction.
+Moreover, the improvements were greater for days with heavy precipitation, which are generally related to more dynamic atmospheric situations where timing is more specific and which are fewer in the meteorological archive.
 
-		However, in order to produce quantitative precipitation predictions the MTW requires sub-daily precipitation time series, which are generally available for a shorter period than daily precipitation archives.
-Therefore, two simple temporal disaggregation methods were assessed in order to make longer archives usable with the MTW.
-The assessed approaches were not successful, emphasizing the need to use time series with an appropriate chronology.
-These should be available in the near future, either by means of growing archives of measurements or by the establishment of regional precipitation reanalysis data at sub-daily time step.
-
-		The use of the MTW in the AM can already be considered now for several applications in different contexts, may it be for operational forecasting or climate-related studies.
+		Both improvements of the analogy criterion and the performance scores were found to be higher for MTWs with a smaller time step (3h).
+A 3h-MTW provides 8 times more candidate situations, even though not fully independent.
+As the MTW provides additional situations to the pool of possible analogues, it can be seen as an inflation of the archive.
+The technique being very simple and easily applicable, it should be considered for several applications in different contexts, may it be for operational forecasting or climate-related studies.
 

### 2017-03-31 Moving temporal window - HESS/template.tex
HESS corrections.

@@
 	The Analogue method (AM) is based on the hypothesis that two relatively similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}.
-It is a statistical downscaling methods \citep{Maraun2010} and consist of finding past situations that are similar to the target day of interest in terms of the atmospheric circulation or other synoptic predictors.
+It is a statistical downscaling methods \citep[see][for other methods]{Maraun2010} and consist of finding past situations that are similar to the target day of interest in terms of the atmospheric circulation or other synoptic predictors.
 The local weather variables of interest (predictand) that were observed at the analogue dates are used to construct a probabilistic prediction for the target day \citep{Duband1970, Zorita1999}.
 Multiple variations of the method exist \citep[a non-exhaustive listing can be found in][]{BenDaoud2016}.
-The AMs are used for operational precipitation forecasting, either in the context of weather forecasting, flood forecasting, or hydropower production \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as for precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}.
-Other applications focus on temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, and solar power \citep{Alessandrini2015a, Bessa2015}.
+The AMs are used for operational precipitation forecasting, either in the context of weather forecasting, flood forecasting, or hydropower production \citep[e.g.,][]{Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as for precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}.
 AMs can provide multivariate predictions that are physically consistent \citep{Raynaud2016b}.
@@
 The second is an archive of the target variable to be predicted, here precipitation.
-This archive is made of precipitation cumulated over a certain time duration, most often daily but sometimes sub-daily, either at a target station or integrated over a target catchment.
+It is most often made of daily precipitation totals at a target station or integrated over a target catchment.
 Obviously, the period to be used is limited to the smallest period common to the two archives.
@@
 
-	One can question the interest of using moving daily totals when 6-hourly precipitation series can be predicted instead.
-However, the 6-hourly time series generated by the AM might not represent accurately the intra-daily precipitation distribution.
+	One can question the interest of using moving daily totals when for example 6-hourly precipitation series can be predicted instead.
+However, the 6-hourly time series generated by the AM might not represent accurately the intra-daily precipitation distribution or variability.
 In addition, sometimes a resolution finer than the daily time step is not needed and another disaggregation technique may be used afterwards.
-Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact than 24h daily totals.
+Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact on 24h totals than 6h totals.
 
 	The MTW finds analogue situations at different hours of the day, which can also be seen as an inflation of the archive length.
-However, despite having $x$ time more candidate situations, the quantity of new information is not expected to be as important as a $x$ time longer archive due to significant correlation between successive situations within the same day.
+However, despite having $x$ time more candidate situations, the quantity of new information is not expected to be as important as an $x$ time longer archive due to significant correlation between successive situations within the same day.
 Nevertheless, if the MTW can improve the prediction skill of the AM, it means that it does extract new information from the archive.
@@
 
-	Synoptic-scale variables, used as predictors, were extracted from two of the most recent global reanalysis datasets: the european ERA-20C \citep{Poli2016} with a 3h temporal resolution, and a spatial resolution of 1\textdegree, and MERRA-2, from NASA, with a 6h temporal resolution and a spatial resolution of 0.625\textdegree x 0.5\textdegree.
+	Synoptic-scale variables, used as predictors, were extracted from two of the most recent global reanalysis datasets: the european ERA-20C \citep{Poli2016} with a 3h temporal resolution and a spatial resolution of 1\textdegree, and MERRA-2 from NASA with a 6h temporal resolution and a spatial resolution of 0.625\textdegree x 0.5\textdegree.
 The study was originally performed on the NCEP/NCAR reanalysis 1 dataset \citep{Kalnay1996}, and the conclusions were similar.
@@
 The specific advantages of ERA-20C is that it allows testing an MTW with a 3h time step, and it covers a long period.
-On the other hand, MERRA-2 has a higher spatial resolution and can be expected to be more correct at higher levels of the atmosphere.
-The variables extracted from these datasets are geopotential heights at 500~hPa (Z500) and 1000~hPa (Z1000), as well as the total precipitable water (TPW) and the relative humidity at 850~hPa (RH850).
+On the other hand, MERRA-2 has a higher spatial resolution and can be expected to be more accurate at higher levels of the atmosphere.
+The variables extracted from these datasets were geopotential heights at 500~hPa (Z500) and 1000~hPa (Z1000), as well as the total precipitable water (TPW) and the relative humidity at 850~hPa (RH850).
 
@@
 
-	The first considered AM is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005}.
+	The first considered AM is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z};][]{Obled2002, Bontron2005}.
 Searching for analogue situations to a target day starts by a seasonal stratification through a preselection step of the potential candidates for analogy.
@@
 
-	The second reference method (2Z-2MI, Table \ref{table:method_2Z-2MI}) adds a subsequent level of analogy with moisture variables, compared by means of the root-mean-square error (RMSE):
+	The second reference method \citep[2Z-2MI, Table \ref{table:method_2Z-2MI};][]{Bontron2005} adds a subsequent level of analogy with moisture variables, compared by means of the root-mean-square error (RMSE):
 
@@
 	AMs rely on parameters that need to be defined for every level of analogy.
-Here, the selection of the meteorological variables used as predictors, as well as their corresponding analogy criteria, pressure level, and hour of the day will be identical to the methods 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) described above.
-The parameters that are here calibrated are:
+Here, the selection of the meteorological variables used as predictors, as well as their corresponding analogy criteria, pressure level, and hour of the day, were considered identical to the methods 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) described above.
+The parameters that were here calibrated are:
 
@@
 
-	The semi-automatic sequential procedure elaborated by \citet{Bontron2004} was used to calibrate the AM \cite[see also ][]{Radanovics2013, BenDaoud2016}.
+	The semi-automatic sequential procedure elaborated by \citet{Bontron2004} was used to calibrate the AM \cite[see also][]{Radanovics2013, BenDaoud2016}.
 The analogy levels (e.g.
@@
 Every point (or cell) of the full domain is assessed on all predictors of the level of analogy, jointly (consisting generally of the same variable but on different pressure levels and at different hours).
-			\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain.
-The spatial window grows by repeating the previous steps until no improvement is reached.
+			\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain. The spatial window grows until no improvement is reached.
 			\item The number of analogue situations $N_{1}$, which was initially set at an arbitrary value, is then reconsidered and optimized for the current level of analogy.
@@
 
-	The 29-yr hourly precipitation dataset was divided into a calibration period (CP) and a validation period (VP), in order to assess the robustness of the proposed improvements on independent data.
+	The 29-yr hourly precipitation dataset was divided into a calibration period (CP) and a validation period (VP) in order to assess the robustness of the proposed improvements on independent data.
 The selection of the VP was evenly distributed over the entire series \citep{BenDaoud2010} to reduce potential biases related to trends linked to climate change or to the evolution in measurement techniques.
-Thus, one out of every five years was selected for validation, which represents a total of 6 years for the VP and 23 for the CP.
+Thus, one out of every five years was selected for validation, which represents a total of 6~yr for the VP and 23~yr for the CP.
 
@@
 	The moving time window (MTW) technique aims at finding better analogue situations at different hours of the day rather than comparing the predictors at the same fixed hours.
-The target situation (the day to predict) is still the same as in the conventional approach, that is a daily precipitation total between 06:00 and 30:00~UTC, characterized by predictors which are e.g.
-Z1000 and Z500 at 12:00 and 24:00~UTC respectively.
-The difference is that candidate situations are not only considered at the same time (e.g.
-12:00 and 24:00~UTC), but at other hours by allowing a time shift.
+The target situation (the day to predict) is still the same as in the conventional approach, that is a daily precipitation total between 06:00 and 30:00~UTC, characterized by predictors which are here Z1000 and Z500 at 12:00 and 24:00~UTC respectively.
+The difference is that candidate situations are not only considered at the same time (12:00 and 24:00~UTC), but at other hours by allowing a time shift.
 Therefore, instead of looking for analogues at a 24h time step, they are sought at the time step matching the predictor temporal resolution (Fig.
@@
 In order to assess the benefit of searching for analogue situations at a sub-daily time step for quantitative precipitation prediction, an appropriate precipitation series is required.
-On the basis of high temporal resolution time series (Sect.
+On the basis of hourly time series (Sect.
 \ref{sec:data}), 24h totals were processed at time steps matching the MTW by means of a moving 24h total on the period 1982-2010.
@@
 	\begin{itemize}
-		\item Original parameters: The AMs were initially calibrated for each station based on the classic 24-hr approach.
+		\item Original parameters: The AMs were initially calibrated for each station based on the conventional 24h approach.
 Then, the MTW was introduced into the AMs, but the parameters (spatial windows and number of analogues) were not reassessed.
-The analogy is the same and thus initial analogue dates should be found in the new distribution, along with new dates provided by the MTW.
+The analogy was then identical, with the only difference that the MTW had more candidate at disposal.
 		\item Recalibrated: The parameters of the AMs were reassessed after the introduction of the MTW at different time steps.
 Indeed, one can assume that the introduction of the MTW might change the optimum value of some parameters (different spatial windows and number of analogues).
-The calibration (see Sect.
+The calibration (Sect.
 \ref{sec:calibration}) was then be reprocessed to adapt the AMs to the new information available through the MTW.
-The main difference was the increase of the optimal number of analogues, which is discussed in Sect.
+The main difference was the increase in the optimal number of analogues, which is discussed in Sect.
 \ref{sec:increase_analognb}.
@@
 
-	The MTW is expected to have an impact on both the selection of analogue dates and the prediction skill. Both will be analyzed separately hereafter.
+	The MTW is expected to have an impact on both the selection of analogue dates and the prediction skill. Both are analyzed separately hereafter.
 
@@
 
-	First, the impact of the MTW on the selection of analogue dates is analyzed, independently of any precipitation data.
+	First, the impact of the MTW on the selection of analogue dates was analyzed, independently of any precipitation data.
 This was done on the period 1982-2010, but could have been done on a longer period, as no sub-daily precipitation series is required at this stage.
-The results are presented for the Ulrichen station, but are very similar for all other stations.
+The results are presented for the Ulrichen station, but were very similar for all other stations.
 The original parameters were used here when assessing the impact of the MTW, no recalibration of the parameters took place.
@@
 	When searching for analogues in the first level of analogy, such as on the geopotential heights in the 2Z method (Sect.
-\ref{sec:analog_method}), there are up to eight times as many candidates (even though not fully independent) with the MTW than before (Sect.
+\ref{sec:analog_method}), there were up to eight times as many candidates (even though not fully independent) with the MTW than before (Sect.
 \ref{sec:mtw}).
-Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions, for target dates over the whole period, of the analogy criterion (S1) for the $1^{st}$, $15^{th}$, and $30^{th}$ analogue rank, due to introduction of an MTW with a 12h, 6h, or 3h time step.
+Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions, for target dates over the CP, of the analogy criterion (S1) for the $1^{st}$, $15^{th}$, and $30^{th}$ analogue rank, due to introduction of an MTW with a 12h, 6h, or 3h time step.
 The shape of the distributions of the conventional approach and the MTWs were found to be similar, but the values of the analogy criterion were gradually reduced (shifted to the left) with smaller time steps MTWs and were, therefore, better.
-The circulation analogy seems to improve regularly with the doubling of the MTW time steps.
+The circulation analogy was here regularly improved with the doubling of the MTW time step.
 For analogues with higher ranks (e.g.
@@
 \ref{fig:changes_S1}, which shows (top) quantiles of the S1 criterion for the conventional method and the MTWs at different time steps, and (bottom) quantiles of the relative reduction (meaning improvement) due to the MTWs.
-This confirms that all quantiles were similarly reduced (S1 distributions keep their shape), and that this improvement was constantly increasing from the first to the last analogue (Fig.
+This confirms that this improvement is constantly increasing from the first to the last analogue (Fig.
 \ref{fig:changes_S1} bottom).
-This increase in improvement with the analogue rank can be explained by the accumulation of better analogues in the selection, with new better situations pushing previous analogues to higher ranks.
+It can be explained by the accumulation of better analogues in the selection, with new better situations pushing previous analogues to higher ranks.
 One can also see the regularity of the improvements brought by decreasing time steps.
-The introduction of the MTW allows finding better analogue situations in the first level of analogy, resulting in a selection of days with better similarity in atmospheric circulation.
-Moreover, this improvement is superior for MTWs with a smaller time step.
+The introduction of the MTW allows finding better analogue situations in the first level of analogy, resulting in a selection of days with here a better similarity in the atmospheric circulation.
+This improvement is superior for MTWs with a smaller time step.
 
@@
 \ref{fig:hours_selection_per_season}).
-It was found that the new choice of the temporal window in winter, when using the MTW approach, is more balanced between the different hours of the day (more regular repartition), and this for all time steps.
-This means a change in selection of a greater part of the analogue dates compared to the conventional approach.
-On the contrary, the days during the summer months had a preference for the initial temporal window (Z500 24~h \& Z1000 12~h), likely due to more pronounced diurnal effects, which reduced the potential for improvement of the criteria.
-This effect is in phase with the daily cycle, and good analogues are essentially found for the same hours.
-When a 3h-MTW is used, the time step following the initial temporal window (so Z500 27~h \& Z1000 15~h) is almost as often selected for all seasons.
-However, it can be considered as relatively similar in terms of the solar influence.
-The other seasons were between these two extremes, which is consistent with their respective improvements.
+It was found that the new choice of the temporal window in winter is more balanced between the different hours of the day (more regular repartition), and this for all MTW time steps.
+This means a change in selection of a greater portion of the analogue dates compared to the conventional approach.
+On the contrary, the days in summer had a preference for the initial temporal window (Z500 24~h \& Z1000 12~h).
+It is likely due to more pronounced diurnal effects, which reduced the potential for improvement of the criteria.
+These effects are in phase with the daily cycle, and good analogues were essentially found for the same hours.
+When a 3h-MTW was used, the time step following the initial temporal window (so Z500 27~h \& Z1000 15~h) was almost as often selected as the initial one for all seasons.
+It can be considered as relatively similar in terms of the solar influence.
+The other seasons were between these two extremes, which is consistent with their respective improvements in S1.
 
@@
 
-	The criteria values (RMSE) of the second level of analogy (moisture variables) were not improved by the MTW, as the number of candidates was not higher (still the $N_{1}$ days selected in the first level of analogy).
-The use of an MTW does not increase the sample size in this case, the second level of analogy only subsamples in the dates provided by the first level.
+	These criterion values were not improved by the MTW because the number of candidates was not higher (still the $N_{1}$ days selected in the first level of analogy).
+The use of an MTW did not increase the sample size in this case, as the second level of analogy only subsamples in the dates provided by the first level.
 However, this result of a globally null improvement of the RMSE values does not mean that the 2Z-2MI method cannot be improved by the MTW.
-It means that after the selection of the analogue situations for the synoptic circulation, the new candidate dates did not provide better analogues in terms of moisture.
-However, the selected dates have changed in the first level of analogy and also in the final selection, and thus the distributions of precipitation values were different.
+It means that after the selection of the analogue dates for the synoptic circulation, the new candidate dates did not provide better analogues in terms of moisture.
+However, the selected dates have changed in the first level of analogy and also in the final selection, and thus the distributions of precipitation values were different, which can have an impact on the performance of the precipitation prediction.
 
-	\subsection{Impact of the MTW on the prediction skill}
+	\subsection{Impact of the MTW on the precipitation prediction}
 	\label{sec:influence_scores}
 
-	The change in the performance score (CRPS) of the precipitation prediction are provided in Fig.
+	The changes in the performance score (CRPS) of the precipitation prediction are provided in Fig.
 \ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI} for the 2Z and 2Z-2MI methods, respectively.
@@
 
-	The MTW improves the precipitation prediction, as at least from a 6h-MTW the CRPS decreases for all stations, both on the CP and the VP.
-The VP shows a greater variability, likely related to the short period it represents (6 yr).
-The prediction skill on the CP is almost always improved further by reducing the time step of the MTW, but not of the same magnitude.
-For ERA-20C, the magnitude of the improvement of 2Z on the CP is relatively reduced when using a 3h-MTW instead of a 6h-MTW, and the variablility on the VP increases.
+	The MTW improved the precipitation prediction, as the CRPS globally decreased for all stations, both on the CP and the VP.
+The VP showed a greater variability, likely related to the short period it represents (6 yr).
+The prediction skill on the CP was almost always improved further by reducing the time step of the MTW, but not of the same magnitude.
+For ERA-20C, the magnitude of the improvement of 2Z on the CP was relatively reduced when using a 3h-MTW instead of a 6h-MTW, and the variablility on the VP increased.
 However, as it was shown in Fig.
-\ref{fig:changes_S1}, the distribution of analogue dates was improved relatively equally for every reduction of the MTW time step.
-A possible explanation could be that the AMs rely on the geopotential at 500~hPa, while the ERA-20C dataset was build by only assimilating surface observations.
-Thus, the timing of the atmospheric circulation at higher pressure levels might not be completely in phase with the real perturbation systems that are linked with the observed precipitations.
-The MTW with the MERRA-2 dataset and the 2Z method also shows a certain slope break after the 12h-MTW, that could not be explained, and that is less important for the 2Z-2MI method.
-However, the 12h-MTW shows an important variability for the 2Z-2MI method and the MERRA-2 dataset.
-Based on these results, the use of ERA-20C seems to be a better choice in order to apply an MTW, at least for the studied region.
+\ref{fig:changes_S1}, the selection of analogue dates was improved relatively equally for every reduction of the MTW time step.
+A possible reason could be that the ERA-20C dataset was build by only assimilating surface observations, while the AMs rely on the geopotential at 500~hPa.
+Thus, the timing of the atmospheric circulation at higher pressure levels might not be completely in phase with the real perturbation systems that caused the observed precipitations.
+The MTW with the MERRA-2 dataset and the 2Z method also showed a certain slope break after the 12h-MTW, that could not be explained, and that is less important for the 2Z-2MI method.
+However, the 12h-MTW resulted in important variability for the 2Z-2MI method and the MERRA-2 dataset.
 
@@
 \ref{sec:changes_analogy_circul}).
-The impact of the MTW was then assessed in terms of change of prediction skill, on the whole period, per precipitation classes (for the target day).
+The impact of the MTW was then assessed in terms of change of prediction performance per precipitation classes (for the target day).
 Figure \ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, using the original parameters with the MTW.
 It shows that, after the introduction of the MTW, the performance score was in average further improved (reduced CRPS) for days with higher precipitation than for non-rainy days and small precipitation values.
-When recalibrating the parameters using the MTW, the spread of the changes in CRPS tended to decrease, but with a slight loss in performance for the most rainy days.
+When recalibrating the parameters using the MTW, the spread of the changes in CRPS tended to decrease, but with a slight loss in performance for the most rainy days (not shown).
 
@@
 \ref{fig:reliability_diagrams}).
-Reliability diagrams plot the observed frequency against the predicted probability of a binary event -- a threshold exceedence in our case.	For perfectly calibrated predictions, the curve should be as close as possible to the diagonal.
+Reliability diagrams plot the observed frequency against the predicted probability of a binary event -- a threshold exceedence in this case.
+For perfectly calibrated predictions, the curve should be as close as possible to the diagonal.
 The VP only contains six years (Sect.
-\ref{sec:data_methods}), and thus higher variability is present for higher thresholds, the curves being smoother and closer to the diagonals for the CP, which is longer.
-Figure \ref{fig:reliability_diagrams} shows that the MTW improved the reliability for both 2Z and 2Z-2MI methods and for all thresholds, as the curves move toward the diagonal with a decreasing MTW time step.
-For P80, the 3h-MTW predictions fits very well the observations.
-When considering higher thresholds, the 2Z-2MI method is generall better than 2Z.
-The case of a P95 threshold shows a conditional dry bias associated with larger forecast probabilities for the considered AMs, which is however substantially reduced by the 3h-MTW.
-This conditional dry bias means here that the AM did not predict the event with a probability equal to 1 for example for 2Z.
-Obtaining a probability of 1 would mean that all analogue dates for a certain target date would be above the threshold.
+\ref{sec:data_methods}), and thus higher variability is present for higher thresholds, the curves being smoother and closer to the diagonals for the CP, which is longer (not shown).
+Figure \ref{fig:reliability_diagrams} shows that the MTW improved the reliability for both 2Z and 2Z-2MI methods and for all thresholds, as the curves moved toward the diagonal with a decreasing MTW time step.
+For P80, the 3h-MTW predictions fited very well the observed frequency.
+When considering higher thresholds, the 2Z-2MI method is generally better than 2Z.
+The case of a P95 threshold shows a conditional dry bias associated with larger forecast probabilities for the considered AMs, which was however substantially reduced by the 3h-MTW.
+This conditional dry bias means for example here that the AM did not predict the event with a probability equal to 1 for 2Z.
+Obtaining a predicted probability of exceedence of 1 would mean that all analogue dates for a certain target date would be above the threshold.
 As the number of analogue dates is 30 in this case, it becomes less likely to have 30 values above the threshold when it increases.
 This issue is the topic of an ongoing work.
-However, as one can see in Figure \ref{fig:reliability_diagrams}e\&d, the introduction of an MTW, especially with a 3h timse step, improves partly this missmatch.
+However, as one can see in Figure \ref{fig:reliability_diagrams} (bottom), the introduction of an MTW, especially with a 3h timse step, improves partly this missmatch.
 
@@
 When using ERA-20C, all optimal numbers of analogues (for the different analogy levels) tend in average to double when using a 6h-MTW instead of the classic approach, and to even triple when using a 3h-MTW.
-These higher numbers of analogues were objectivel chosen by the calibration procedure (Sect.
+These higher numbers of analogues were objectively chosen by the calibration procedure (Sect.
 \ref{sec:calibration}) in order to increase the prediction skill of the methods.
+
+	As shown in Fig.
+\ref{fig:changes_S1}, the improvement of the S1 criterion grows along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions.
+It seems profitable to widen the selection of analogues in order to also keep some whose rank has increased, as they appear to be relevant to the prediction of the precipitation values.
+The number of good analogues was globally increased.
 
@@
 The observed increase in the number of analogue situations with the MTW resulted in better performance skills for the given methods, as it can be seen as an inflation of the archive.
-However, if new relevant predictors were added to the method, the number of analogues would then decrease.
-
-	As shown in Fig.
-\ref{fig:changes_S1}, the improvement of the S1 criterion grows along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions.
-It seems profitable to widen the selection of analogues in order to also keep some whose rank has increased, as they appear to be relevant to the prediction of the precipitation values.
-The number of good analogues was globally increased.
+However, if new relevant predictors were added to the method, the number of analogues would then decrease again.
 
@@
 \ref{fig:plots_archive_length} for both 2Z and 2Z-2MI methods, using the conventional approach (24h windows).
-As expected, the performance of the method globally increases with the length of the archive.
-The best performances are found with a 44 yr archive, corresponding to the period 1961--2010, minus the 6 years of independant data set apart for validation.
-This addition of 21~yr of archive to the original 23~yr results in an improvement of both 2Z and 2Z-2MI methods that is of the same order of magnitude as the introduction of a 6h-MTW (Fig.
+As expected, the performance of the method globally increased with the length of the archive.
+The best performances were found with a 44~yr archive, corresponding to the period 1961--2010, minus the 6 years of independant VP.
+This addition of 21~yr of archive to the original 23~yr resulted in an improvement of both 2Z and 2Z-2MI methods that was of the same order of magnitude as the introduction of a 6h-MTW (Fig.
 \ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI}).
-The 3h-MTW resulted in similar performance for the 2Z method and slight improvements for the 2Z-2MI method.
+The 3h-MTW resulted in similar performance for the 2Z method and slightly superior improvements for the 2Z-2MI method.
 
@@
 With the introduction of the MTW, the performance loss related to an eventual reduction of the archive length (to meet the length of the subdaily precipitation archive) was compensated.
-A 6h-MTW brought gains of the same magnitude as if the length of the archive doubled.
-Note, that despite the number of candidate situations being 4 times as many, the gains seem to be lower than for a quadrupled archive length.
+A 6h-MTW brought gains of the same magnitude as if the length of the archive almost doubled.
+Note, that despite the number of candidate situations being in this case 4 times as many, the gains seem to be lower than for a quadrupled archive length.
 The likely reason is that an actual longer archive would contain more atmospheric situations that might have been observed less frequently during a shorter period.
 Moreover, high correlations between sub-daily circulation patterns are expected.
-The MTW, therefore, did not create 4 times as many independent data, but the increase in information was nevertheless substantial.
 
-	Many reanalysis datasets start in the 80s due to availability of satellite data, and are thus more accurate than reanalysis datasets based on conventional data, but provide a shorter archive length.
+	Many reanalysis datasets start in the 80s due to availability of satellite data, and are thus more accurate than reanalysis datasets based on conventional data only, but they provide shorter archives.
 When using such an archive, the MTW approach shows a certain potential to enrich the pool of possible analogues.
@@
 	As we saw in Sect.
-\ref{sec:archive_reduction}, the skills of AMs improve with the length of the archive.
-It would then be even more profitable to apply the MTW to the longest archive possible, rather than being limited to the period where the sub-daily precipitation data are available.
+\ref{sec:archive_reduction}, the skills of AMs improved with the length of the archive.
+It would then be even more profitable to apply the MTW to the longest archive possible, rather than being limited to the period where sub-daily precipitation data are available.
 Therefore, in order to reconstruct longer archives of moving 24h totals, disaggregation techniques might be used.
-Where, two simple disaggregation approaches of the daily precipitation time series were assessed.
+Here, two simple disaggregation approaches of the daily precipitation time series were assessed.
 
@@
 
-	The second approach aimed at getting closer to the chronology of the actual precipitation by relying on some informative variables during the reconstruction procedure.
-Data from the NCEP/NCAR reanalysis 1 (Sect.
-\ref{sec:data}) were used for this purpose, despite their rough resolution (2.5\textdegree).
+	The second approach aimed at getting closer to the chronology of the actual precipitation by relying on some informative proxy variables during the reconstruction procedure.
+Data from the NCEP/NCAR reanalysis 1 were used for this purpose.
 Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment.
-Precipitation time series from the reanalysis was not considered due to the presence of zeros, which may not always match with the prediction, leading to an undefined temporal repartition.
+Precipitation time series from the reanalysis were not considered due to the presence of zeros, which may not always match with the prediction, leading to an undefined temporal repartition.
 A time lapse (-12h to +12h) between both series was allowed to take into account the significant distance separating the weather stations and the reanalysis grid point.
@@
 
-	These two simple methods assessed to reconstruct precipitation archives did not result in valuable outputs (results not shown).
+	These two simple methods did not result in valuable outputs (results not shown).
 Indeed, the performance improvement brought by the MTW was lost due to the poor quality of the precipitation archives.
@@
 
-	The introduction of the MTW improved the selection of synoptic analogues.
-Independently of its impact on the prediction skill for precipitation, or the availability of a predictand time series with sub-daily time step, this improvement has a potential in itself for application on long meteorological archives.
-For example, when processing forecasts for a target day showing synoptic similarity with situations from the past related to extreme weather, even if for them no precipitation archive is available.
-Indeed, some of those days with strong precipitation events may be documented, either qualitatively in the daily press or more quantitatively in flood reports.
-It is thus worth to known that the situation at hand has had such analogue in the past.
-Another possible application is a quality assessment of the selection of analogues on a shorter period, where precipitation data with a high temporal resolution is available.
-Indeed, if the selection of analogues with the MTW on the long period, for a specific target day, differ from the selection on the short period, this may point out a sub-optimal forecast.
-Finally, other predictands might not need sub-daily total values, but point observations (e.g.
-hail, or extreme wind gusts), which make them easier to use with the MTW.
-
 	\conclusions  %% \conclusions[modified heading if necessary]
@@
 However, it is unlikely that two analogue synoptic situations, that evolve relatively quickly, would correspond optimally at the same hours of the day.
-It is probable that better matches can be found at another time, which can change the selection of the analogue dates.
+It is probable that better matches may be found at another hour, which can change the selection of the analogue dates.
 
 	As \citet{Finet2008} had previously shown, the introduction of an MTW allows finding better analogue situations in terms of the atmospheric circulation.
-It has been demonstrated in this study that the improvement of the S1 criterion values was growing with the rank of the analogue.
+Using recent reanalysis datasets, MTWs with 12h, 6h, and 3h time steps were assessed.
+It has been demonstrated here that the improvement of the S1 criterion values was growing with the rank of the analogue.
 This was due to the accumulation of better analogues within the predicted distributions.
+The improvement of the S1 criterion increased for smaller MTW time steps.
 
-	The improvement of the circulation analogy was found to be more important for days with heavier precipitation, which are generally related to more dynamic atmospheric situations and are less frequent in the archive.
+	A seasonal effect has been highlighted, as the MTW was more profitable for winter than summer.
+The reason is likely that the diurnal cycle has a bigger effect in summer than in winter which results in better analogues at the same time of the day.
+The preference for the same hours in summer has been demonstrated; whereas, a large part of the analogue situations were selected at a different time in winter.
+
+	The MTW improved the precipitation prediction, as the CRPS globally decreased for all stations, both on the CP and the VP.
+The prediction skill on the CP was almost always improved further by reducing the time step of the MTW, but not of the same magnitude.
+Results on the VP showed globally the same trends, but with more variability.
+It was also shown that the reliability of the considered AMs improved for the prediction of different threshold exceedences, especially with a 3h-MTW.
+
+	Both improvements of the analogy criterion and the performance scores were found to be higher for MTWs with a smaller time step (3h).
+A 3h-MTW provides 8 times more candidate situations, even though not fully independent.
+As the MTW provides additional situations to the pool of possible analogues, it can be seen as an inflation of the archive.
+
+	The improvement of the circulation analogy and the change in performance of the precipitation prediction was found to be more important for days with heavier precipitation.
+These are generally related to more dynamic atmospheric situations and are less frequent in the archive.
 These situations have more specific circulation patterns that are evolving more rapidly.
@@
 
-	A seasonal effect has been highlighted, as the MTW was more profitable for winter than summer.
-The reason is likely that the diurnal cycle has a bigger effect in summer than in winter which results in better analogues at the same time of the day.
-The preference for the same hours in summer has been demonstrated; whereas, 75~\% of the analogue situations were selected at a different time in winter.
-
-	The impact of the MTW on the prediction skill was never assessed before due to the shortcoming of long precipitation series at a sub-daily time step.
-Here, it was assessed for a 25~year time series with a high temporal resolution.
-After the introduction of the MTW, the performance scores increased of the same magnitude as if the length of the archive doubled.
-
-	The parameters were then calibrated again, using the MTW.
-Some parameters changed, with the main difference being the number of analogues, which systematically and significantly increased compared to the original set.
-A wider selection of analogue situations, containing those whose rank decreased, seemed beneficial for the prediction performance.
-The number of good analogues was globally increased in the same way as if the archive length increased.
-This change seems to benefit the prediction of days with small precipitation totals.
-
-	The importance of the quality of the precipitation archive was also demonstrated, as simplistic reconstructions of 6-hourly time series led to a loss of all the improvement brought by the MTW.
+	The importance of the quality of the precipitation archive was also demonstrated, as simplistic reconstructions of subdaily time series led to a loss of all the improvement brought by the MTW.
 The precipitation prediction is improved only when the precipitation chronology is close to the accurate one.
@@
 
-	Finally, since long meteorological archives (reanalysis datasets) are more and more available, the improvements proposed by the MTW especially for days with heavy precipitation may be interesting even without long continuous precipitation archives.
-For example, recent target day may have synoptic similarity with situations from the early twentieth century, for which no continuous daily precipitation archive is available.
-However, some of those days with strong precipitation events may be documented, either qualitatively in the daily press or more quantitatively in flood reports.
-Nevertheless, it is worth to known that the situation at hand has had such analogue in the far past.
+	The introduction of the MTW improved the selection of synoptic analogues.
+Independently of its impact on the prediction skill for precipitation, or the availability of a predictand time series with sub-daily time step, this improvement has a potential in itself for application on long meteorological archives.
+For example, when processing forecasts for a target day showing synoptic similarity with known situations from the past related to extreme weather, even if for them no precipitation archive is available.
+It is thus worth to known that the situation at hand has had such analogue in the past.
+Another possible application is a quality assessment of the selection of analogues on a shorter period, where sub-daily precipitation data is available.
+Indeed, if the selection of analogues with the MTW on a long period, for a specific target day, differ from the selection on the short period, this may point out a sub-optimal forecast.
+Finally, other predictands might not need sub-daily total values, but point observations (e.g.
+hail, or extreme wind gusts), which make them easier to use with the MTW.
 
-	The use of the MTW in the AM can already be considered now for several applications in different contexts, may it be for operational forecasting or climate-related studies.
+	The technique being very simple and easily applicable, it should be considered for several applications in different contexts, may it be for operational forecasting or climate-related studies.
 
@@
 		\caption{Differences of the CRPS performance score (lower is better) at the Ulrichen station due to the introduction of the MTW as a function of different daily precipitation thresholds (for the target date).
-The results are provided for (a, b) the 2Z method and (c, d) the 2Z-2MI method, and with a (a, c) 6h-MTW and a (b, d) 3h-MTW.
+The results are provided for (top) the 2Z method and (bottom) the 2Z-2MI method, and with a (left) 6h-MTW and a (right) 3h-MTW.
 The stars represent averages.}
@@
 		\end{center}
-		\caption{Reliability diagrams for (a, c, e) the 2Z (b, d, f) the 2Z-2MI methods and the prediction of the exceedence of percentiles (a, b) 80~\%, (c, d) 90~\%, and (e, f) 95~\% at the Ulrichen station on the VP.
+		\caption{Reliability diagrams for (left) the 2Z (right) the 2Z-2MI methods and the prediction of the exceedence of percentiles (top) 80~\%, (middle) 90~\%, and (bottom) 95~\% at the Ulrichen station on the VP.
 The conventional approach (24h) is provided as well as the 12h-MTW, 6h-MTW and 3h-MTW.}
@@
 		\includegraphics[width=8.3cm]{fig14.pdf}
-		\caption{Change in performance score (CRPS -- lower is better) of the (a, b) 2Z and (c, d) 2Z-2MI methods at the different stations on the (a, c) CP and (b, d) VP, for an increasing archive length with the conventional approach (24h windows).}
+		\caption{Change in performance score (CRPS -- lower is better) of the (top) 2Z and (bottom) 2Z-2MI methods at the different stations on the (left) CP and (right) VP, for an increasing archive length with the conventional approach (24h windows).}
 		\label{fig:plots_archive_length}

### 2017-03-31 Optimization case study - JoH/elsarticle-template.tex
Updating references.
Journal abbreviations and doi.
Working on the figures of JoH.

@@
 \usepackage{gensymb}
-
-%TODO: read again
-%TODO: Elsevier english editing
-%TODO: relative improvement of the crpss...
-%TODO: homogenize hours: 6 a.m. or 06 h ??
 
@@
 It is often used to predict daily precipitation, either in an operational forecasting context \citep[e.g.][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Horton2016a, Hamill2015, BenDaoud2016} or a climate downscaling context \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015, Raynaud2016b}.
-Other predictands are also considered, such as precipitation radar images \citep{Panziera2011,Foresti2015a}, temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016, Raynaud2016b}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, and radiation \citep{Bois1981, Raynaud2016b}.
+Other predictands are also considered, such as precipitation radar images \citep{Panziera2011,Foresti2015a}, temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016, Raynaud2016b}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, and solar radiation or power production \citep{Alessandrini2015a, Bessa2015, Raynaud2016b}.
 
@@
 Although these outputs are essential, they can be supplemented by other sources of forecasts providing useful information.
-In contrast to local NWP models, AMs can transform at low cost the synoptic-scale information provided by the global NWP model into precipitation forecasts, by using the natural local behaviour in response to synoptic-scale influences stored in the archive of observed precipitation.
-Running an AM approach is fast enough that it can search for analogues for each day, up to ten days ahead, eventually for the different traces of an ensemble forecast and/or those issued by different NWP models (e.g.
-NOAA-GFS or ECMWF-IFS), in a matter of minutes.
+In contrast to local NWP models, AMs can transform at low cost the synoptic-scale information provided by the global NWP model into precipitation forecasts.
+They rely on the inherent relationship between the synoptic-scale influences and the related local weather that can be exploited from the archive of observed precipitation.
+Running an AM approach is fast enough that it can search for analogues for each day, up to ten days ahead, in a matter of seconds to minutes.
+It can eventually use the different members of an ensemble forecast and/or those issued by different NWP models (e.g.
+NOAA-GFS or ECMWF-IFS).
 
@@
 
-Beyond being computationally inexpensive, another big advantage of AMs is that they create realistic precipitation patterns for a region, provided that the analogue dates are the same, since they are based on observed situations with consistent spatial distribution \citep{Radanovics2013, Chardon2014}.
-For the same reason, they can also provide multivariate predictions that are physically consistent \citep{Raynaud2016b}.
+The spatial transferability of AMs is analysed in \citet{Chardon2014} and \citet{Radanovics2013}, and their temporal transferability in \citet{Dayon2015} and \citet{Caillouet2016}.
+The physical consistency of multivariate predictions is presented in  \citet{Raynaud2016b}.
 
@@
 
-\subsection{Case study description}
+\subsection{Description of study area}
 \label{sec:case_study}
@@
 The time series from every available gauge station were averaged over the ten subregions (Fig.\ \ref{fig:map}), which were approximately 500~km$^{2}$ each, in order to smooth local effects \citep{Obled2002, Marty2012}.
-This helps account for local variability, mainly when convective processes are involved, which slightly increases the prediction skill.
+This helps accounting for local variability, mainly when convective processes are involved, which slightly increases the prediction skill.
 
@@
 
-\citet{Bontron2005} show that the geopotential height at 500~hPa (Z500) and 1000~hPa (Z1000) are the best first predictors of the NCEP/NCAR reanalysis I dataset, and that the S1 criterion performs better than scores based on absolute distances.
+\citet{Bontron2005} showed that the geopotential height at 500~hPa (Z500) and 1000~hPa (Z1000) are the best first predictors of the NCEP/NCAR reanalysis I dataset, and that the S1 criterion performs better than scores based on absolute distances.
 The reason for such better results is that the S1 criterion allows comparison of the circulation patterns, by means of the gradients, rather than the absolute value of the geopotential height, which better represent the flow direction.
@@
 When this second level of analogy is added, a higher number of analogues $N_{1}$ is kept on the first level.
-Moisture fields are not as well-predicted by NWP models as pressure variables.
-This implies that the 2Z-2MI method, when used in real-time forecasting, is very dependent on the skill of the NWP model in predicting moisture fields, and thus its use is often restricted to the first lead times.
+Prediction of moisture fields by NWP models are more model-dependent and more uncertain than pressure variables.
+This implies that the 2Z-2MI method, when used in real-time forecasting, is very dependent on the skill of the NWP model in predicting moisture fields.
+Therefore its use is often restricted to the first lead times.
 
@@
 		\item Temporal window (hour of the day)
-		\item Initial analogue numbers
+		\item Number of analogues
 	\end{enumerate}
@@
 The parameters calibrated on the previous analogy levels are fixed and do not change.
-	\item Finally, the numbers of analogues $N_{1}$ and $N_{2}$ for the different levels of analogy are reassessed by systematic increments.
+	\item Finally, the numbers of analogues $N_{1}$ and $N_{2}$ for the different levels of analogy are reassessed.
+This is done iteratively by varying the number of analogues of each level in a systematic way.
 \end{enumerate}
@@
 
-Then, an additional degree of freedom was provided to the GAs by letting them choose the pressure levels along with the other parameters (analogue numbers, spatial and temporal windows), which is also a non-automated process in the sequential calibration.
+Then, an additional degree of freedom was provided to the GAs by letting them choose the pressure levels along with the other parameters (number of analogues, spatial and temporal windows), which is also a non-automated process in the sequential calibration.
 This degree of freedom increased the optimization time, and might decrease the number of simulations that converge to a single solution.
@@
 One can also see that the optimal number of analogues $N_{2}$ for the second level of analogy of 4Zo-2MIo was slightly inferior to $N_{1}$ from 4Zo, but very close.
-There is a globally common tendency between the optimal analogue number values of both methods: $N_{1}$ of the 4Zo method, and $N_{1}$ and $N_{2}$ of 4Zo-2MIo tend to be higher or lower together for a given region.
+There is a globally common tendency between the optimal number of analogues of both methods: $N_{1}$ of the 4Zo method, and $N_{1}$ and $N_{2}$ of 4Zo-2MIo tend to be higher or lower together for a given region.
 
@@
 Beyond four, the validation score was more variable, revealing a loss in robustness due to over-parametrization.
-	\item The automatic and joint optimization of all parameters: the analogue numbers, selection of pressure levels and temporal windows, and spatial windows.
+	\item The automatic and joint optimization of all parameters: the number of analogues, selection of pressure levels and temporal windows, and spatial windows.
 These parameters are highly interdependent, so one needs to optimize them jointly in order to identify optimal combinations.
@@
 
-%\bibliography{references}
-\bibliography{../_refs/4_articles-2016_JoH_optimizations}
+\bibliography{references}
 
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=9cm]{figures/fig01.pdf}}
-	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland. (source: Swisstopo)}
+	\centerline{\includegraphics[width=7.9cm]{fig01.pdf}}
+	\caption{Location of the alpine Rh\^{o}ne catchment in Switzerland and its discretization into ten subregions. (source: Swisstopo)}
 	\label{fig:map}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=9cm]{figures/fig02.pdf}}
-	\caption{Performance score (CRPSS) for CP and VP for three stations (1 - Swiss Chablais; 5 - Southern valleys; 8 - Southeast ridges) when varying the number of geopotential height levels available to the optimizer.}
+	\centerline{\includegraphics[width=7.9cm]{fig02.pdf}}
+	\caption{Performance score (CRPSS) for CP and VP for three regions (1 - Swiss Chablais; 5 - Southern valleys; 8 - Southeast ridges) when varying the number of geopotential height levels available to the optimizer.}
 	\label{fig:figure_nb_levels}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.4cm]{figures/fig03.pdf}}
-	\caption{Optimized spatial windows for the 4Zo method (analogy of the atmospheric circulation on four pressure levels).}
+	\centerline{\includegraphics[width=7.9cm]{fig03.pdf}}
+	\caption{Optimized spatial windows for each region for the 4Zo method (analogy of the atmospheric circulation on four pressure levels).
+The spatial windows are different from a pressure level to another.}
 	\label{fig:spatial_windows_4Zo}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=9cm]{figures/fig04.pdf}}
+	\centerline{\includegraphics[width=7.9cm]{fig04.pdf}}
 	\caption{Performance score (CRPSS) of the reference method 2Z (Table \ref{table:params_R1}) and the optimized 4Zo method for CP and VP for every subregion.}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.4cm]{figures/fig05.pdf}}
+	\centerline{\includegraphics[width=7.9cm]{fig05.pdf}}
 	\caption{Losses or gains (in \%) in CRPSS from applying optimized parameters for the series in columns to those in rows. Method 4Zo, calibration and validation periods.}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.4cm]{figures/fig06.pdf}}
+	\centerline{\includegraphics[width=7.9cm]{fig06.pdf}}
 	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on four pressure levels and analogy on the moisture index on two pressure levels).}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=9cm]{figures/fig07.pdf}}
+	\centerline{\includegraphics[width=7.9cm]{fig07.pdf}}
 	\caption{Performance score (CRPSS) of the reference method 2Z-2MI (Table \ref{table:params_R2}) and the optimized 4Zo-2MIo method for CP and VP for every subregion.}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=8.4cm]{figures/fig08.pdf}}
+	\centerline{\includegraphics[width=7.9cm]{fig08.pdf}}
 	\caption{Losses or gains (in \%) of the CRPSS from applying optimized parameters for the series in columns to those in rows. Method 4Zo-2MIo, calibration and validation periods.}
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=9cm]{figures/fig09.pdf}}
+	\centerline{\includegraphics[width=7.9cm]{fig09.pdf}}
 	\caption{Optimal numbers of analogues for the different regions and the two methods, resulting from optimization.
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=9cm]{figures/fig10.png}}
+	\centerline{\includegraphics[width=7.9cm]{fig10.pdf}}
 	\caption{Distribution of optimal weights for the predictors of the first level of analogy (geopotential heights) of (blue) 4Zo, (red) 4Zo-2MIo, and (green) 4Zo-4MIo methods.
@@
 \begin{figure}[t]
-	\centerline{\includegraphics[width=7.5cm]{figures/fig11.pdf}}
+	\centerline{\includegraphics[width=7.9cm]{fig11.pdf}}
 	\caption{Example of evolution of the performance score of the best individual over eight independent optimizations.}

### 2017-03-31 Optimization case study - JoH/elsarticle-template.tex
Requested corrections for JoH.

@@
 It uses predictor variables describing the synoptic atmospheric circulation in order to predict local-scale predictands of interest.
-It is often used to predict daily precipitation, either in an operational forecasting context \citep[e.g.][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Horton2016a, Hamill2015, BenDaoud2016} or a climate downscaling context \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015, Raynaud2016b}.
+It is often used to predict daily precipitation, either in an operational forecasting context \citep[e.g.][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Hamill2015, BenDaoud2016} or a climate downscaling context \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015, Raynaud2016b}.
 Other predictands are also considered, such as precipitation radar images \citep{Panziera2011,Foresti2015a}, temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016, Raynaud2016b}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, and solar radiation or power production \citep{Alessandrini2015a, Bessa2015, Raynaud2016b}.
@@
 Aiming to overcome these limitations, a global optimization by genetic algorithms (GAs) was introduced.
-An intensive assessment resulted in recommendations to parametrize GAs in order to optimize AMs successfully \citep{Horton2016}.
+An intensive assessment resulted in recommendations to parametrize GAs in order to optimize AMs successfully \citep{Horton2017}.
 The present paper is based on these recommendations, and applies them to precipitation prediction for the upper Rh\^{o}ne catchment in the Swiss Alps, using AMs of varying complexity.
@@
 The parameters calibrated on the previous analogy levels are fixed and do not change.
-	\item Finally, the numbers of analogues $N_{1}$ and $N_{2}$ for the different levels of analogy are reassessed.
+	\item Finally, the number of analogues $N_{1}$ and $N_{2}$ for the different levels of analogy are reassessed.
 This is done iteratively by varying the number of analogues of each level in a systematic way.
@@
 
-The optimizations here were performed based on the recommended GA parametrization for AMs as described in \citet{Horton2016}.
-As the optimization is mostly sensitive to the mutation operator (that randomly changes some values in the parameter sets), parallel optimizations are considered with variants of this operator, according to \citet{Horton2016}:
+The optimizations here were performed based on the recommended GA parametrization for AMs as described in \citet{Horton2017}.
+As the optimization is mostly sensitive to the mutation operator (that randomly changes some values in the parameter sets), parallel optimizations are considered with variants of this operator, according to \citet{Horton2017}:
 
@@
 	\item 3x non-uniform mutation \citep{Michalewicz1996} with varying parameters
-	\item 1x multi-scale mutation \citep{Horton2016}
-	\item 2x chromosome of adaptive search radius \citep{Horton2016}.
+	\item 1x multi-scale mutation \citep{Horton2017}
+	\item 2x chromosome of adaptive search radius \citep{Horton2017}.
 \end{itemize}
@@
 The first four subregions were characterized by a large spatial window on the upper level, whereas it was smaller elsewhere.
-For most subregions, the second level (Z700) was compared on thin and longitudinally extended spatial windows.
+For most subregions, the second level (Z700) was characterized by thin and longitudinally extended spatial windows.
 The third level (Z1000 at 6 or 12~h) also had longitudinally extended domains, which were slightly larger.
@@
 
-Globally, the same cross-compatibility structure could be observed for the VP (Figure \ref{fig:crossing_4Zo} bottom), but in this case, minor improvements were occasionally observed when crossing the parameters, because of the presence of other events in the VP that might be better predicted by a different parameter set.
+Globally, the same cross-compatibility structure could be observed for the VP (Figure \ref{fig:crossing_4Zo} bottom), but in this case, minor improvements were occasionally observed when switching the parameters, because of the presence of other events in the VP that might be better predicted by a different parameter set.
 The relatively small differences in scores between parameterizations indicated that even though the parameters might differ significantly, the performance might not be drastically affected.
@@
 This is first visible in the number $N_{1}$ of analogues to be selected on the first level, and in the selection of the pressure levels for the circulation analogy.
-If the change in the optimal value of $N_{1}$ was already known, a change in the optimal pressure levels for the circulation analogy has never been identified before.
+A change in the optimal value of $N_{1}$ was already known and taken into account in the 2Z-2MI method (Table \ref{table:params_R2}) for example.
+However, a change in the optimal pressure levels for the circulation analogy is a new result that has never been highlighted before.
 
@@
 
-The optimal final numbers of analogues did not vary much: $23 \leq N_{1} \leq 33$ for 4Zo and $21 \leq N_{2} \leq 28$ for 4Zo-2MIo.
+The optimal final number of analogues did not vary much: $23 \leq N_{1} \leq 33$ for 4Zo and $21 \leq N_{2} \leq 28$ for 4Zo-2MIo.
 However, the optimal number of the $N_{1}$ analogues of the first level of 4Zo-2MIo varied to a greater extent: $48 \leq N_{1} \leq 84$.
@@
 As for the pressure levels, Z1000, which was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) was here less often chosen (once or even not at all) for 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}).
-There was indeed a vertical shift in the previously selected Z1000 for higher levels that was even slightly stronger with four moisture predictors than with two.
+There was indeed a vertical shift in the previously selected Z1000 for lower pressure levels that was even slightly stronger with four moisture predictors than with two.
 This change is likely due to the fact that when considering only the circulation analogy, the method tried to take into account information that can serve as a proxy for moisture assessment, whereas it did not need it with the moisture index.
@@
 The analysis of the parameters’ cross-compatibility (Figure \ref{fig:crossing_4Zo-2MIo}) was also very similar to the one of the circulation analogy only.
-The same pattern could be observed, with a drop of performance for the subregions submitted to different meteorological influences.
+The same pattern could be observed, with a drop of performance for the subregions characterized by different meteorological influences.
 However, the losses in performance were globally more important than before, suggesting that more complex methods with moisture variables are less transposable to another subregion (consistent with the observations of \citet{Chardon2014}), even though both were located within the same grid cell of the reanalysis dataset.
@@
 Beyond four, the validation score was more variable, revealing a loss in robustness due to over-parametrization.
-	\item The automatic and joint optimization of all parameters: the number of analogues, selection of pressure levels and temporal windows, and spatial windows.
+	\item The automatic and joint optimization of all parameters: the number of analogues, selection of pressure levels, temporal and spatial windows.
 These parameters are highly interdependent, so one needs to optimize them jointly in order to identify optimal combinations.
@@
 	\item The joint optimization of the circulation and moisture analogy levels, which are usually calibrated successively.
-We were able to demonstrate that there is a dependency between the analogy levels, and that in order to approach the optimal parameters, one must consider them jointly.
+We were able to demonstrate that there is a dependency between the analogy levels, and that in order to find the optimal parameters, one must consider them jointly.
 \end{itemize}
 
-GAs have proved very useful to optimize complex variants of the AM, and to assess new degrees of freedom that were not available thus far.
+GAs have proved very useful to optimize complex variants of the AM, and to assess new degrees of freedom that were not available so far.
 However, it can be dangerous to add too many parameters to optimize.
@@
 The spatial windows, for example, can be larger than the optimal size without much impact on the score, while they cannot be smaller \citep[see also][]{Bontron2004}.
-We also observed that the selection of pressure level is not a parameter as discrete as we would have thought, and that choosing another level may have reduced the consequences on the performance.
+We also observed that the selection of pressure levels is not a parameter as discrete as we would have thought, as sometimes choosing another level had reduced impact on the performance.
 This is particularly true for higher pressure levels, but can be more critical for lower layers.
@@
 In this regard, a cross-validation technique may be advisable.
-However, as solutions identified at different regions of the parameter space might provide sufficiently good performance, an ensemble of these could be used, instead of a unique solution.
+However, as solutions identified in different regions of the parameter space might provide sufficiently good performance, an ensemble of these could be used, instead of a unique solution.
 These could account for the parameters’ uncertainty in the AM, and could also increase the sample size contributing to the empirical distribution of precipitation values.
@@
 
-GAs are relatively heavy on processing and require an IT infrastructure capable of performing thousands of hours of calculations.
+GAs are relatively heavy on processing and require an IT infrastructure capable of performing thousands of hours of calculations (Here, an single optimization over 100~generations took almost 300 h CPU on a small Intel Xeon based High-performance computing cluster -- with Xeon 5670, 2.97 GHz, 12 cores -- running Linux RedHat).
 However, they automatically optimize all parameters of the AM, which is not possible with the sequential calibration.
@@
 
+Analogue methods are usually calibrated by a semi-automatic sequential procedure that has strong limitations: (i) it cannot automatically choose the pressure levels and temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between parameters, and (iii) it cannot easily handle new degrees of freedom.
+Here, a global optimization approach relying on genetic algorithms was able to optimize all parameters jointly and automatically.
+It allowed objective selection of some parameters that were manually selected beforehand.
+
 The parameters resulting from the optimization by GAs were very consistent in terms of the selection of pressure levels and temporal and spatial windows.
-There were clear trends or even identical results for subregions under similar meteorological influences, which confirm that the optimized parameters were coherent, despite an eventual first impression of great variability in the spatial windows.
+There was a good coherence and even identical results for subregions under similar meteorological influences, which confirm that the optimized parameters were coherent, despite an eventual first impression of great variability in the spatial windows.
 When adding moisture variables, the results showed a higher variability, but remained highly acceptable and coherent.
@@
 	\centerline{\includegraphics[width=7.9cm]{fig02.pdf}}
-	\caption{Performance score (CRPSS) for CP and VP for three regions (1 - Swiss Chablais; 5 - Southern valleys; 8 - Southeast ridges) when varying the number of geopotential height levels available to the optimizer.}
+	\caption{Performance score (CRPSS) for CP and VP for three subregions (1 - Swiss Chablais; 5 - Southern valleys; 8 - Southeast ridges) when varying the number of geopotential height levels available to the optimizer.}
 	\label{fig:figure_nb_levels}
@@
 	\caption{Optimized spatial windows for each region for the 4Zo method (analogy of the atmospheric circulation on four pressure levels).
-The spatial windows are different from a pressure level to another.}
+The spatial windows, on which the S1 analogy criterion is processed, are different from a pressure level to another.}
 	\label{fig:spatial_windows_4Zo}
@@
 	\centerline{\includegraphics[width=7.9cm]{fig04.pdf}}
-	\caption{Performance score (CRPSS) of the reference method 2Z (Table \ref{table:params_R1}) and the optimized 4Zo method for CP and VP for every subregion.}
+	\caption{Performance score (CRPSS) of the reference method 2Z (Table \ref{table:params_R1}) and the optimized 4Zo method for the CP and VP for every subregion.}
 	\label{fig:figure_crpss_4Zo}
@@
 	\centerline{\includegraphics[width=7.9cm]{fig06.pdf}}
-	\caption{Optimized spatial windows for the 4Zo-2MIo method (analogy of atmospheric circulation on four pressure levels and analogy on the moisture index on two pressure levels).}
+	\caption{Same as Fig. \ref{fig:spatial_windows_4Zo} but for the 4Zo-2MIo method (analogy of atmospheric circulation on four pressure levels and analogy on the moisture index on two pressure levels).}
 	\label{fig:spatial_windows_4Zo-2MIo}
@@
 	\centerline{\includegraphics[width=7.9cm]{fig07.pdf}}
-	\caption{Performance score (CRPSS) of the reference method 2Z-2MI (Table \ref{table:params_R2}) and the optimized 4Zo-2MIo method for CP and VP for every subregion.}
+	\caption{Performance score (CRPSS) of the reference method 2Z-2MI (Table \ref{table:params_R2}) and the optimized 4Zo-2MIo method for the CP and VP for every subregion.}
 	\label{fig:figure_crpss_4Zo-2HIo}
@@
 	\centerline{\includegraphics[width=7.9cm]{fig09.pdf}}
-	\caption{Optimal numbers of analogues for the different regions and the two methods, resulting from optimization.
+	\caption{Optimal number of analogues for the different subregions and the two methods, resulting from optimization.
 Method 4Zo is made of a single level of analogy with $N_{1}$ analogues, whereas 4Zo-2MIo has two levels of analogy with $N_{1}$ and $N_{2}$ analogues.}
@@
 	\caption{Distribution of optimal weights for the predictors of the first level of analogy (geopotential heights) of (blue) 4Zo, (red) 4Zo-2MIo, and (green) 4Zo-4MIo methods.
-Results are for the ten subregions.
-Geopotential heights are sorted by increasing pressure and hour.}
+Results are aggregated for the ten subregions.
+Predictors are sorted by increasing pressure and hour (when a pressure level is selected twice).}
 	\label{fig:levels_weights_average}
@@
 \begin{table}[t]
-	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation ($\sim$) and moisture analogy ($\bullet$) of the 4Zo-2MIo method, for different subregions (ID).
+	\caption{Pressure levels automatically selected for the analogy of atmospheric circulation ($\sim$) and moisture analogy ($\bullet$) of the 4Zo-2MIo method, for different subregions (ID).
 R represents the 2Z-2MI reference method (Table \ref{table:params_R2})}

### 2017-04-05 Optimization case study - JoH/corrections/8 - Submitted version.tex
Submission of the JoH paper.

--- 2017-03-31 Optimization case study - JoH/elsarticle-template.tex
@@
 
-	This relationship is usually established by a semi-automatic sequential procedure that has strong limitations: (i) it cannot automatically choose the pressure levels and temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between parameters, and (iii) it cannot easily handle new degrees of freedom.
+	This relationship is usually established by a semi-automatic sequential procedure that has strong limitations: (i) it cannot automatically choose the pressure levels and temporal windows (hour of the day) for a given meteorological variable, (ii) it cannot handle dependencies between parameters, and (iii) it cannot easily handle new degrees of freedom.
 In this work, a global optimization approach relying on genetic algorithms was able to optimize all parameters jointly and automatically.
-It allowed consideration of parameter inter-dependencies, and objective selection of some parameters that were manually selected beforehand, which obviates the need to assess a large number of combinations of pressure levels and temporal windows of predictor variables.
 
@@
 Moreover, they were obtained automatically and objectively, which reduces the effort that needs to be invested in exploration attempts when adapting the method to a new region or for a new predictand.
+For example, it obviates the need to assess a large number of combinations of pressure levels and temporal windows of predictor variables that were manually selected beforehand.
+The optimization could also take into account parameter inter-dependencies.
 In addition, the approach allowed for new degrees of freedom, such as a possible weighting between pressure levels, and non-overlapping spatial windows.
@@
 The method can be designed with multiple successive subsampling steps, or analogy levels, each of them relying on different meteorological variables.
-A certain number of parameters define the relationship between predictors and predictands, such as the choice of the predictor variable, its pressure level and temporal window to consider, the spatial domain to use for the comparison, as well as the analogy criterion itself, and finally, the number of analogue situations to keep at each subsampling level.
+A certain number of parameters define the relationship between predictors and predictands, such as the choice of the predictor variable, its pressure level and temporal window (hour of the day) to consider, the spatial domain to use for the comparison, as well as the analogy criterion itself, and finally, the number of analogue situations to keep at each subsampling level.
 These parameters are usually calibrated by means of a semi-automatic sequential procedure \citep{Bontron2004, Radanovics2013}, i.e.
@@
 This sequential approach therefore has strong limitations: (i) it cannot automatically choose the optimal pressure levels and the temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between the parameters within a level of analogy, and even less between them, and (iii) it cannot easily handle new degrees of freedom, such as a possible weighting between the pressure levels.
-Thus, even if the processing involved is relatively fast, the sequential approach requires laborious assessments of predictor combinations (variables, pressure levels, temporal windows), and presents a high risk of ending in a local optimum because of subjective initial choices and lack of consideration of parameter inter-dependencies.
+Thus, even if the processing involved is relatively fast, the sequential approach requires laborious assessments of predictor combinations (variables, pressure levels, temporal windows).
+Moreover, it presents a high risk of ending in a local optimum because of subjective initial choices and lack of consideration of parameter inter-dependencies.
 Other calibration methods exist for specific applications, such as radar images \citep{Panziera2011, Foresti2015a}.
@@
 The number of analogues, $N_{1}$, is a parameter to calibrate.
-Then, the daily observed precipitation amount for the $N_{1}$ resulting dates provide the empirical conditional distribution, considered as the probabilistic prediction for the target day.
+Then, the daily observed precipitation amount for the $N_{1}$ selected dates provide the empirical conditional distribution, considered as the probabilistic prediction for the target day.
 
@@
 The predictor that \citet{Bontron2004} found optimal for France is a moisture index made of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850).
-\cite{Horton2012a} confirms that this index is also better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis I considered independently.
+\cite{Horton2012a} confirmed that this index is also better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis I considered independently.
 When adding a second level of analogy, $N_{2}$ dates are subsampled within the $N_{1}$ analogues of the atmospheric circulation, to end up with a smaller number of analogue situations.
@@
 
-AMs are usually calibrated by a semi-automatic sequential procedure, as elaborated by \citet{Bontron2004} \cite[see also ][]{Radanovics2013, BenDaoud2016}.
+AMs are usually calibrated by a semi-automatic sequential procedure, as elaborated by \citet{Bontron2004} \cite[see also][]{Radanovics2013, BenDaoud2016}.
 The calibration technique optimizes the spatial windows in which the predictors are compared and the number of analogues for every level of analogy, by maximizing the performance score (CRPSS).
@@
 They are part of the Evolutionary Algorithms \citep{Back1993b, Schwefel1993}, which were inspired by some mechanisms in biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection.
-GAs seek the global optimum on a complex surface, theoretically without restriction, which is of interest for AMs, which are characterized by a complex high-dimensional error function having multiple local optima.
+GAs seek the global optimum on a complex surface, theoretically without restriction.
+This is of interest for AMs, which are characterized by a complex high-dimensional error function having multiple local optima.
 Practically, GAs allow rapidly approaching satisfactory solutions, but they are not guaranteed to provide the optimum solution \citep{Zitzler2004a}.
@@
 A population size of 500 individuals (i.e.
-parameter sets of the AM to be detailed below) was considered, and the optimization was stopped when the best individual (with the highest CRPSS performance score) did not evolve for 20 generations (cycles of optimization).
+parameter sets of the AM) was considered, and the optimization was stopped when the best individual (with the highest CRPSS performance score) did not evolve for 20 generations (cycles of optimization).
 
@@
 The optimizer had to choose simultaneously the number of analogues, both spatial windows with no overlapping constraint (i.e.
-they can differ from one pressure level to another), as well as the temporal windows (hours of observation of the geopotential), which cannot be achieved with the sequential calibration technique.
+they can differ from one pressure level to another), as well as the temporal windows (hours of observation of the geopotential height), which cannot be achieved with the sequential calibration technique.
 The performance score (CRPSS) was slightly improved, with these limited degrees of freedom, relative to the 2Z reference method calibrated with the sequential procedure.
@@
 The number of circulation predictors (still only geopotential heights) was then successively increased up to ten, considering the weighting of the analogy criteria values.
-The addition of circulation predictors globally improved the prediction skill (for both the CP and the VP) only up to four predictors (Figure \ref{fig:figure_nb_levels}).
+The addition of circulation predictors substantially improved the prediction skill (for both the CP and the VP) only up to four predictors (Figure \ref{fig:figure_nb_levels}).
 Afterwards, the score on the VP was more variable, eventually even showing a decrease, which revealed an over-parametrization of the method, and thus a lack of robustness.
-After four predictors, the score for the CP did not increase substantially, and even presented a local decrease due to increasing difficulty for the optimizer to converge.
+The score for the CP might also present local decreases when many predictors are involved, due to increasing difficulty for the optimizer to converge.
 Selecting four circulation predictors (geopotential heights) was considered optimal for this case study, since the gain in CRPSS was significant, and the model remained relatively simple.
@@
 However, the losses in CRPSS when exchanging the parameters were not of the same magnitude among the different subregions.
-Indeed, the Upper Rhone Valley (7) and, moreover, the southeast ridges (8) seemed to behave significantly differently.
+Indeed, the Upper Rhone Valley (7) and, moreover, the southeast ridges (8) seemed to behave differently.
 These two regions have different climatic properties than the others, as they are particularly sensitive to southerly flows.
@@
 The moisture index, which is a combination of the relative humidity and precipitable water, has thus also to be optimized.
-In order to do so, a constraint on the optimizer had to be introduced, so as to select the same temporal window (time of observation) for both variables.
+In order to do so, a constraint on the optimizer had to be introduced, so as to select the same temporal window (hour of the day) for both variables.
 
@@
 
-As seen previously, the optimized parameters differed from one subregion to another, but to an even greater extent.
+As previously, the optimized parameters differed from one subregion to another, but to an even greater extent.
 The resulting spatial windows are displayed in Figure \ref{fig:spatial_windows_4Zo-2MIo} for 4Zo-2MIo, along with the selected pressure levels for both the circulation and moisture analogy (Table \ref{table:levels_GA_4Zo_2MIo}).
@@
 This is first visible in the number $N_{1}$ of analogues to be selected on the first level, and in the selection of the pressure levels for the circulation analogy.
-A change in the optimal value of $N_{1}$ was already known and taken into account in the 2Z-2MI method (Table \ref{table:params_R2}) for example.
+A change in the optimal value of $N_{1}$ was already known and taken into account in the 2Z-2MI method (Table \ref{table:params_R2}).
 However, a change in the optimal pressure levels for the circulation analogy is a new result that has never been highlighted before.
@@
 One can also see that the optimal number of analogues $N_{2}$ for the second level of analogy of 4Zo-2MIo was slightly inferior to $N_{1}$ from 4Zo, but very close.
-There is a globally common tendency between the optimal number of analogues of both methods: $N_{1}$ of the 4Zo method, and $N_{1}$ and $N_{2}$ of 4Zo-2MIo tend to be higher or lower together for a given region.
+There is a globally common tendency between the optimal number of analogues of both methods: $N_{1}$ of the 4Zo method, and $N_{1}$ and $N_{2}$ of 4Zo-2MIo tend to be higher or lower together for a given subregion.
 
@@
 As for the pressure levels, Z1000, which was previously systematically selected twice (Table \ref{table:levels_GA_4Zo}) was here less often chosen (once or even not at all) for 4Zo-2MIo (Table \ref{table:levels_GA_4Zo_2MIo}).
-There was indeed a vertical shift in the previously selected Z1000 for lower pressure levels that was even slightly stronger with four moisture predictors than with two.
+There was indeed a vertical shift in the previously selected Z1000 for lower pressure levels that was even slightly stronger with four moisture predictors than with two (not shown).
 This change is likely due to the fact that when considering only the circulation analogy, the method tried to take into account information that can serve as a proxy for moisture assessment, whereas it did not need it with the moisture index.
@@
 When it comes to the moisture analogy, there was a clear tendency to select 12~h and 24~h.
-However, it must be remembered that this holds for our predictand, the accumulated precipitation over 06--30~h~UTC, and that it is expected to differ if the temporal window changes (e.g.
-00--24~h~UTC, or another accumulation duration).
 
@@
 We also observed that the selection of pressure levels is not a parameter as discrete as we would have thought, as sometimes choosing another level had reduced impact on the performance.
-This is particularly true for higher pressure levels, but can be more critical for lower layers.
+This is particularly true for levels at higher altitude, but can be more critical for lower layers.
 It was thus interesting to sometimes obtain several sets of near-optimal parameters, but with some nuances, in order to get an idea of the sensitivity of the parameters for a given region, and to compare the score for the VP.
@@
 
-As has been observed, methods with higher complexity that integrate moisture predictors are less transposable than simpler ones.
+Methods with higher complexity that integrate moisture predictors are less transposable than simpler ones.
 It was also noticed in another unpublished work, that it is by far better to optimize for two subregions jointly than to optimize on one and to apply its parametrization to the other.
 Finally, the discretization in subregions is an important process and should be handled with care.
-Indeed, the geographical distance is not always the leading factor to define a subregion.
+Indeed, the physical distance is not always the leading factor to define a subregion.
 For example, the southeast ridges subregion does not behave like its surroundings, and differs in its parametrization because of different leading meteorological influences.
 
-GAs are relatively heavy on processing and require an IT infrastructure capable of performing thousands of hours of calculations (Here, an single optimization over 100~generations took almost 300 h CPU on a small Intel Xeon based High-performance computing cluster -- with Xeon 5670, 2.97 GHz, 12 cores -- running Linux RedHat).
+GAs are relatively heavy on processing and require an IT infrastructure capable of performing thousands of hours of calculations (Here, a single optimization over 100~generations took almost 300 h CPU on a small Intel Xeon based high-performance computing cluster -- with Xeon 5670, 2.97 GHz, 12 cores -- running Linux RedHat).
 However, they automatically optimize all parameters of the AM, which is not possible with the sequential calibration.
@@
 
-Analogue methods are usually calibrated by a semi-automatic sequential procedure that has strong limitations: (i) it cannot automatically choose the pressure levels and temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between parameters, and (iii) it cannot easily handle new degrees of freedom.
+AMs are usually calibrated by a semi-automatic sequential procedure that has strong limitations: (i) it cannot automatically choose the pressure levels and temporal windows for a given meteorological variable, (ii) it cannot handle dependencies between parameters, and (iii) it cannot easily handle new degrees of freedom.
 Here, a global optimization approach relying on genetic algorithms was able to optimize all parameters jointly and automatically.
-It allowed objective selection of some parameters that were manually selected beforehand.
+It allowed objective selection of some parameters that were manually assessed beforehand.
 
@@
 
-For the present case study, there seemed to be an optimum number of pressure levels to consider for the circulation analogy, which is four, before losing consistency of the real gains.
+For the present case study, there seemed to be an optimum number of pressure levels to consider for the circulation analogy, which was four, before losing consistency of the real gains.
 The circulation analogy was improved by introducing a weighting between pressure levels, and considering independent spatial windows between pressure levels.
@@
 GAs provided parameterizations of AMs that exceeded the performance of the sequential calibration.
-In addition, it has been observed that the prediction for days with strong precipitation were improved to a greater extent, which is clearly interesting in the context of flood forecasting.
+In addition, it has been observed that the prediction for days with strong precipitation were improved to a greater extent, which is clearly interesting in a hydrological context.
 
-This work is by no means exhaustive, and is meant to open a door to new explorations of AMs with GAs.
+This work is by no means exhaustive, and is meant to open a door to new explorations of AMs with GAs or other global optimization techniquess.
 It is even possible to let the optimizer chose the meteorological variable to be used as a predictor, as well as the analogy criteria, which is the topic of work in progress.
 Moreover, the AM has been explored for decades for precipitation prediction, but not as intensively for other predictands.
-A global optimizer, such as a GA, can speed up this assessment significantly.
+A global optimizer, such as a GAs, can speed up this assessment significantly.
 
@@
 	\centerline{\includegraphics[width=7.9cm]{fig02.pdf}}
-	\caption{Performance score (CRPSS) for CP and VP for three subregions (1 - Swiss Chablais; 5 - Southern valleys; 8 - Southeast ridges) when varying the number of geopotential height levels available to the optimizer.}
+	\caption{Performance score (CRPSS) for CP and VP for three subregions (1 - Swiss Chablais; 5 - Southern valleys; 8 - Southeast ridges) when varying the number of geopotential height predictors available to the optimizer.}
 	\label{fig:figure_nb_levels}
@@
 	\centerline{\includegraphics[width=7.9cm]{fig03.pdf}}
-	\caption{Optimized spatial windows for each region for the 4Zo method (analogy of the atmospheric circulation on four pressure levels).
+	\caption{Optimized spatial windows for each region for the 4Zo method (analogy of the atmospheric circulation).
 The spatial windows, on which the S1 analogy criterion is processed, are different from a pressure level to another.}
@@
 	\centerline{\includegraphics[width=7.9cm]{fig06.pdf}}
-	\caption{Same as Fig. \ref{fig:spatial_windows_4Zo} but for the 4Zo-2MIo method (analogy of atmospheric circulation on four pressure levels and analogy on the moisture index on two pressure levels).}
+	\caption{Same as Fig. \ref{fig:spatial_windows_4Zo} but for the 4Zo-2MIo method (analogy of atmospheric circulation and of the moisture index).}
 	\label{fig:spatial_windows_4Zo-2MIo}

### 2017-04-05 Optimization case study - JoH/elsarticle-template.tex
Submission of the JoH paper.

@@
 %% Group authors per affiliation:
-\author[unil,unibe,terranum]{Pascal Horton\corref{mycorrespondingauthor}}
+\author[unil,unibe]{Pascal Horton\corref{mycorrespondingauthor}}
 \cortext[mycorrespondingauthor]{Corresponding author}

### 2017-04-05 Moving temporal window - HESS/corrections/9 - Elsevier editing.tex
Elsevier editing for HESS.

%% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
%% ---------------------------------
%% This template should be used for copernicus.cls
%% The class file and some style files are bundled in the Copernicus Latex Package which can be downloaded from the different journal webpages.
%% For further assistance please contact the Copernicus Publications at: publications@copernicus.org
%% http://publications.copernicus.org

%% Please use the following documentclass and Journal Abbreviations for Discussion Papers and Final Revised Papers.

%% 2-Column Papers and Discussion Papers
\documentclass[hess, manuscript]{copernicus}
%\documentclass[hess]{copernicus}

%% Journal Abbreviations (Please use the same for Discussion Papers and Final Revised Papers)
% Hydrology and Earth System Sciences (hess)

\usepackage[utf8]{inputenc}
\usepackage{scrextend}

\begin{document}

	\title{The analogue method for precipitation prediction: finding better analogue situations at a sub-daily time step}

	\Author[1,2]{Pascal}{Horton}
	\Author[3]{Charles}{Obled}
	\Author[1]{Michel}{Jaboyedoff}

	\affil[1]{University of Lausanne, Institute of Earth Sciences, Lausanne, Switzerland}
	\affil[2]{University of Bern, Oeschger Centre for Climate Change Research, Institute of Geography, Bern, Switzerland}
	\affil[3]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}

	\runningtitle{Finding better analogue situations at a sub-daily time step}

	\runningauthor{P. Horton et al.}

	\correspondence{Pascal Horton (pascal.horton@alumnil.unil.ch)}

	\received{}
	\pubdiscuss{} %% only important for two-stage journals
	\revised{}
	\accepted{}
	\published{}

	%% These dates will be inserted by Copernicus Publications during the typesetting process.

	\firstpage{1}

	\maketitle

	\begin{abstract}
		Analogue methods (AMs) predict local weather variables (predictands) such as precipitation by means of a statistical relationship with predictors at a synoptic scale. The analogy is generally assessed on gradients of geopotential heights first in order to sample days with a similar atmospheric circulation. Other predictors such as moisture variables can also be added in a successive level of analogy.

		The search for candidate situations for a given target day is usually undertaken by comparing the state of the atmosphere at fixed hours of the day for both the target day and the candidate analogues. This is a consequence of using daily precipitation time series, which are available on longer periods than sub-daily data. However, it is unlikely for the best analogy to occur at the exact same hour. A better analogue situation may be found with a time shift of several hours because it can occur at different times of the day. In order to assess the potential for finding better analogues at a different hour, a moving time window (MTW) has been introduced.

		The MTW resulted in a better analogy in terms of the atmospheric circulation and showed improved values of the analogy criterion on the entire distribution of analogue dates. The improvement was found to increase with the analogue rank owing to an accumulation of better analogues in the selection. A seasonal effect has also been identified, with larger improvements shown in winter than in summer. This can be attributed to stronger diurnal cycles in summer that favour predictors at the same hour for the target and analogue days.

		The impact of the MTW on the prediction skill has been assessed by means of a sub-daily precipitation series transformed into moving 24 h totals at 12-h, 6-h, and 3-h time steps. The prediction skill was improved by the MTW, as was the reliability of the prediction. Moreover, the improvements were greater for days with heavy precipitation, which are generally related to more dynamic atmospheric situations in which the timing is more specific and fewer records are available in the meteorological archive.

		The improvements of the analogy criterion and the performance scores were both found to be higher for MTWs with a smaller time step  of 3 h. A 3-h MTW provides eight times more candidate situations even though they are not fully independent. Because the MTW provides additional situations to the pool of possible analogues, it can be considered as an inflation of the archive. Because this technique is very simple and easily applicable, it should be considered for several applications in different contexts, particularly for operational forecasting or climate-related studies.

	\end{abstract}

	\introduction  %% \introduction[modified heading if necessary]
	\label{sec:introduction}

	The analogue method (AM) is based on the hypothesis that two relatively similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}. It is a statistical downscaling method \citep[see][for other methods]{Maraun2010} and consists of finding past situations that are similar to the target day of interest in terms of atmospheric circulation or other synoptic predictors. Referred to as the predictand, the local weather variables of interest which were observed at the analogue dates are used to construct a probabilistic prediction for the target day \citep{Duband1970, Zorita1999}. Multiple variations of this method have been reported \citep{BenDaoud2016}. AMs are used for operational precipitation forecasting in the context of weather forecasting, flood forecasting, and hydropower production \citep[e.g.,][]{Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as for precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}. AMs can provide multivariate predictions which are physically consistent \citep{Raynaud2016b}. Their spatial transferability is analysed in \citet{Chardon2014} and \citet{Radanovics2013}, and their temporal transferability has been discussed in recent studies for past or future climates \citep{Dayon2015, Caillouet2016}.

	The method requires two different archives. The first is a meteorological archive describing the state of the atmosphere at a synoptic scale, such as reanalysis datasets. The second is an archive of the target variable to be predicted, which in this study is precipitation, usually composed of daily precipitation totals at a target station or integrated over a target catchment. Obviously, the period to be used is limited to the smallest period common to the two archives.

	\citet{Ruosteenoja1988} and \citet{Vandendool1994} analysed the influence of the length of the meteorological archive on the quality of the analogy. They highlighted a three-way relationship among the quality of the analogy, the archive length, and the size of the spatial domain (or degrees of freedom) and determined that errors increase with a larger domain but decrease with a longer archive. For that reason, limited spatial windows are always considered when searching for analogues, and the archive length is maximised.

	Therefore, owing to the availability of long precipitation archives at a daily time step that have no equivalent at a finer resolution, AMs are usually implemented on a daily basis, and the analogue situations are assessed by comparing predictors at fixed hours of the day. However, it can be expected that the analogy of the synoptic situations does not occur systematically at the same time of the day and that better candidates can be found by shifting to a different hour. With this assumption, a moving time window (MTW) was introduced to allow the search for candidates at different hours of the day. Previous tests have showed the benefit, in terms of analogy criterion values, of searching for analogue synoptic situations at a finer time step, although such research did not assess the impact on the prediction skill \citep{Finet2008}.

	One can question the interest of using moving daily totals when, for example, 6-h precipitation series can be predicted instead. However, the 6-h time series generated by the AM might not accurately represent the intra-daily precipitation distribution or variability. In addition, sometimes a resolution finer than the daily time step is not needed, and another disaggregation technique may be used afterwards. Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact on 24-h totals than on 6-h totals.

	The MTW finds analogue situations at different hours of the day, which can also be considered as an inflation of the archive length. However, despite having $x$ times more candidate situations, the quantity of new information is not expected to be as important as an $x$-ime longer archive owing to significant correlation between successive situations within the same day. Nevertheless, if the MTW can improve the prediction skill of the AM, it can extract new information from the archive.

	Other possibilities exist for increasing the prediction skill of the AMs. A classical approach is to add new predictors or new successive levels of analogy \citep[e.g.][]{Horton2012a, BenDaoud2016, Caillouet2016}. AMs can also be combined with other methods \citep[e.g.][]{Chardon2014}. Another possibility is to use a global optimization technique, such as genetic algorithms, in order to better optimize the method and to add new parameters \citep{Horton2017}. However, the MTW technique is not in competition with other approaches and can be combined with them.

	Section \ref{sec:data_methods} presents the context of the study as well as the data and methods, including the proposed MTW technique. The benefits of introducing an MTW are assessed first regarding the improvement of the analogue date selection (Sect. \ref{sec:influence_analogue_dates}) and then in terms of precipitation prediction skill (Sect. \ref{sec:influence_scores}). Finally, the results are discussed in Sect. \ref{sec:discussion}, and the conclusions are found in Sect. \ref{sec:conclusions}.

	\section{Data and methods}
	\label{sec:data_methods}

	\subsection{Study area and data}
	\label{sec:data}

	The study area is the upper Rh\^{o}ne catchment in Switzerland. The precipitation time series were obtained from six automatic weather stations, Ulrichen, Zermatt, Visp, Montana, Sion, and Aigle (Fig. \ref{fig:map}), that are subject to various meteorological influences \citep{Horton2012}. The data were available at an hourly time step for 29 years (1982\textendash 2010) and were also obtained at a daily time step of 06:00 UTC to 06:00 UTC the following day for 50 years (1961\textendash 2010). Owing to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed. The results are presented arbitrarily for the Ulrichen station but are equivalent for all stations.

	Synoptic-scale variables used as predictors were extracted from two of the most recent global reanalysis datasets: the European Center for Medium Range Weather Forecasting 20th century reanalysis (ERA-20C) \citep{Poli2016}, with 3-h temporal resolution and a spatial resolution of 1\textdegree, and Modern-Era Retrospective Analysis for Research and Applications, Version 2 (MERRA-2), from the National Aeronautics and Space Administration (NASA), with a 6-h temporal resolution and a spatial resolution of 0.625\textdegree × 0.5\textdegree. The study was originally performed on the National Centers for Environmental Prediction/National Center for Atmospheric Research (NCEP/NCAR) reanalysis 1 dataset \citep{Kalnay1996}; the conclusions were similar. ERA-20C is built by assimilating only surface observations and is thus available for long periods (1900\textendash 2010). On the contrary, MERRA-2 is built by assimilating observations at higher levels and from more sensors including satellite data, but it is more limited in time (1980\textendash present). It is of interest to assess the relevance of an MTW with these two datasets because they represent different types of products. The specific advantages of ERA-20C are that it allows for testing an MTW with a 3-h time step, and it covers a long period. On the contrary, MERRA-2 has a higher spatial resolution and can be expected to be more accurate at higher levels of the atmosphere. The variables extracted from these datasets were geopotential heights at 500 hPa (Z500) and 1000 hPa (Z1000), the total precipitable water (TPW), and the relative humidity at 850 hPa (RH850).

	\subsection{The considered analogue methods}
	\label{sec:analog_method}

	The first considered AM is based on the analogy of atmospheric circulation only \citep[Table \ref{table:method_2Z};][]{Obled2002, Bontron2005}. Before searching for analogue situations for a target day, seasonal stratification is conducted through preselection of the potential candidates for analogy. The search is restricted to analogue days within a four-month window centred on the target date for every year of the archive. The similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1), which is a comparison of gradients of geopotential heights over a particular spatial window and at certain hours:

	\begin{equation}
	\label{eq:S1}
	S_{1}=100 \frac {\displaystyle \sum_{i}^{m} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
	{\displaystyle \sum_{i}^{m} max( \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert ) }
	\end{equation}
where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points from the grid of the target situation, $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation, and $m$ is the number of pairs of adjacent points in the grid. The differences are processed separately in both directions. With smaller S1 values, there is greater similarity in the pressure fields.

	The predictor variables extracted from reanalysis datasets are considered at different hours of the day. Based on \citet{Bontron2005}, geopotential heights are compared at 1000 hPa (Z1000) at 12:00 UTC and at 500 hPa (Z500) at 24:00 UTC. The time of the day at which the predictors are selected has a significant influence \citet{Bontron2004}.

	Then, $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day, where $N_{1}$ is a calibration parameter ( Sect. \ref{sec:calibration}). Finally, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day. This method is referred to as 2Z.

	The second reference method \citep[2Z-2MI, Table \ref{table:method_2Z-2MI};][]{Bontron2005} adds a subsequent level of analogy with moisture variables and is compared by means of the root—mean--square error (RMSE):

	\begin{equation}
	\label{eq:RMSE}
	E_{RMS}= \sqrt[]{ \frac{1}{n} \sum_{i=1}^{n}(\hat{v}_{i} - v_{i})^{2}} 
	\end{equation}
where $\hat{v}_{i}$ is the \textit{i}th predictor value from the grid of the target situation, $v_{i}$ is the corresponding observed value in the candidate situation, and $n$ is the number of points in the grid.

	The additional predictor is a moisture index composed of the product of the total precipitable water (TPW) with the relative humidity at 850 hPa (RH850) \citep{Bontron2004}. When adding a second level of analogy, $N_{2}$ dates are subsampled from the $N_{1}$ analogues on the atmospheric circulation, resulting in a smaller number of analogue situations. Moreover, when a second level of analogy is added, a higher number of $N_{1}$ analogues is kept on the first level.

	More complex AMs exist with additional predictors \citep[e.g.][]{Horton2012a, BenDaoud2016, Caillouet2016}. The MTW can also be applied to these; however, it is easier to interpret the impact of the MTW by using more basic methods.

	\subsection{Calibration of the analogue method}
	\label{sec:calibration}

	AMs rely on parameters that need to be defined for every level of analogy. Here, the selection of the meteorological variables used as predictors, as well as their corresponding analogy criteria, pressure level, and hour of the day, were considered to be identical to those used in methods 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) described above. The parameters calibrated in this study are listed below.

	\begin{itemize}
		\item Spatial windows, which are the domains in which the predictors are compared. A spatial window is specific to each level of analogy; thus, the value differs among circulation and moisture variables.
		\item The optimal number of analogue situations for every level of analogy.
	\end{itemize}

	The semi-automatic sequential procedure discussed by \citet{Bontron2004} was used to calibrate the AM \cite{Radanovics2013, BenDaoud2016}. The analogy levels (e.g. the atmospheric circulation or moisture index) are calibrated sequentially. The spatial windows on which the predictors are compared and the number of analogues are the parameters calibrated by this approach for every level of analogy. The procedure, as defined by \citet{Bontron2004}, consists of the following steps:

	\begin{enumerate}
		\item For every level of analogy
		\begin{enumerate}
			\item Identification of the most skilled unitary cell over a large domain, where one point is given for moisture variables and four are given for geopotential heights in order to process the gradients. Every point or cell of the full domain is jointly assessed on all predictors of the level of analogy consisting generally of the same variable but on different pressure levels and at different hours.
			\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain. The spatial window increases until no improvement is reached.
			\item The number of analogue situations $N_{1}$, which was initially set as an arbitrary value, is then reconsidered and optimised for the current level of analogy.
		\end{enumerate}
		\item A new level of analogy can then be added based on other variables such as the moisture index at chosen pressure levels and hours of the day. The number of analogues for the next level of analogy, $N_{2}$, is initiated at a chosen value. The procedure starts again from step 1 (calibration of the spatial window and the number of analogues) for the new level. The parameters calibrated on the previous analogy levels are fixed and do not change. 
		\item Finally, the numbers of analogues $N_{1}$ and $N_{2}$ for the different levels of analogy are reassessed. This is performed iteratively by varying the number of analogues of each level in a systematic manner.
	\end{enumerate}

	The calibration is performed in successive steps with a limited number of parameters in order to minimize the objective function (CRPS, Eq. \ref{eq:CRPS}). Except for the number of analogues, previously calibrated parameters are generally not reassessed. More advanced techniques such as using genetic algorithms \citep{Horton2017} exist but are beyond the scope of the present study.

	The 29-year hourly precipitation dataset was divided into a calibration period (CP) and a validation period (VP) in order to assess the robustness of the proposed improvements on independent data. The selection of the VP was evenly distributed over the entire series \citep{BenDaoud2010} to reduce potential biases related to trends linked to climate change or to evolution in the measurement techniques. Thus, 1 out of every 5 years was selected for validation, which represents a total of 6 years for the VP and 23 years for the CP.

	The continuous ranked probability score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} is often employed in order to assess the performance of AMs \citep[e.g.][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}. This allows for evaluation of the predicted cumulative distribution functions $F(y)$ of the precipitation values $y$ from analogue situations compared with the observed value $y^{0}$; a better prediction has a smaller score. This process is defined as

	\begin{equation}
	\label{eq:CRPS}
	S_{\text{CRP}} = \int_{-\infty}^{+\infty} \left[ F(y)-\text{H}(y-y^{0})\right]^{2} \text{d}y ,  
	\end{equation}
where $\text{H}(y-y^{0})$ is the Heaviside function, which is null when $y-y^{0}<0$ and has the value of 1 otherwise.

	\subsection{The moving time window approach}
	\label{sec:mtw}

	The MTW technique is used to find better analogue situations at different hours of the day rather than comparing the predictors at the same fixed hours. The target situation, or the day for prediction, is still the same as that in the conventional approach: a daily precipitation total between 06:00 and 30:00 UTC characterised by predictors, which in this case are Z1000 and Z500 at 12:00 and 24:00 UTC, respectively. The difference is that candidate situations are considered not only at the same time (12:00 and 24:00 UTC), but also at other hours by allowing a time shift. Therefore, instead of looking for analogues at a 24-h time step, they are sought at the time step matching the predictor temporal resolution (Fig. \ref{fig:principle}). The ERA-20C dataset used here to test an MTW with 12-h, 6-h, or 3-h time steps, which are referred to as 12-h MTW, 6-h MTW, and 3-hr MTW, respectively. Thus, the candidates are two (12-h MTW), four (6-h MTW), or eight (3-h MTW) times as many  as in the conventional approach even though they are not fully independent.

	The target situations and their corresponding observed precipitation values do not change. We attempted to predict the exact same time series for the MTW and the conventional approach so that the performance scores can be directly compared. In order to assess the benefit of searching for analogue situations at a sub-daily time step for quantitative precipitation prediction, an appropriate precipitation series is required. On the basis of the hourly time series (Sect. \ref{sec:data}), 24-h totals were processed at time steps matching the MTW by means of a moving 24-h total on the period 1982--2010.

	\section{Results}
	\label{sec:results}

	The AMs were applied to both ERA-20C and MERRA-2 datasets. Most of the results are presented for the ERA-20C dataset because it allows for testing a 3-h MTW, although similar conclusions can be found by using MERRA-2. The impact of an MTW was assessed on the two bases given below.
	\begin{itemize}
		\item Original parameters: The AMs were initially calibrated for each station based on the conventional 24-h approach. Then, the MTW was introduced into the AMs, but the parameters (spatial windows and number of analogues) were not reassessed. The analogy was then identical, except for the fact that the MTW had more candidates at disposal.
		\item Recalibrated: The parameters of the AMs were reassessed after the introduction of the MTW at different time steps. Indeed, one can assume that the introduction of the MTW might change the optimum value of some parameters (different spatial windows and number of analogues). The calibration (Sect. \ref{sec:calibration}) was then reprocessed to adapt the AMs to the new information available through the MTW. The main difference was the increase in the optimal number of analogues, which is discussed in Sect. \ref{sec:increase_analognb}.
	\end{itemize}

	The MTW is expected to affect both the selection of analogue dates and the prediction skill. Both are analysed separately hereafter.

	\subsection{Influence of the MTW on the selection of analogue dates}
	\label{sec:influence_analogue_dates}

	First, the impact of the MTW on the selection of analogue dates was analysed independently of precipitation data. This was conducted for the period 1982--2010, although a longer period could have been used because no sub-daily precipitation series is required at this stage. The results are presented for the Ulrichen station, but were very similar for all other stations. The original parameters were used when assessing the impact of the MTW; no recalibration of the parameters was conducted.

	\subsubsection{Analogy of the atmospheric circulation}
	\label{sec:changes_analogy_circul}

	When searching for analogues in the first level of analogy, such as on the geopotential heights in the 2Z method (Sect. \ref{sec:analog_method}), up to eight times as many candidates  were provided with the MTW than before even though they are not fully independent (Sect. \ref{sec:mtw}). Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions, for target dates over the CP, of the analogy criterion (S1) for the $1^{st}$, $15^{th}$, and $30^{th}$ analogue rank owing due to the introduction of an MTW with a 12-h, 6-h, or 3-h time step. The shapes of the distributions of the conventional approach and the MTWs were found to be similar. However, the values of the analogy criterion were gradually reduced and were shifted to the left with smaller MTW time steps and were therefore better. The circulation analogy was regularly improved with the doubling of the MTW time step. For analogues with higher ranks (e.g. $15^{th}$ or $30^{th}$), the difference between the two distributions was larger than that for the first rank, which means that the improvement increased with the rank of the analogue.

	The improvements of the analogy with the rank of the analogues are summarised in Fig. \ref{fig:changes_S1}, which shows the quantiles of the S1 criterion for the conventional method and the MTWs at different time steps (top) and those of the relative reduction indicating improvement owing to the MTWs (bottom). This confirms that the improvement constantly increased from the first to the last analogue (Fig. \ref{fig:changes_S1} bottom). This theory can be explained by the accumulation of better analogues in the selection, whereby the new, better situations push the previous analogues to higher ranks. The regularity of the improvements brought by decreasing time steps is also evident. The introduction of the MTW enables better analogue situations to be found in the first level of the analogy, resulting in the selection of days with better similarity in the atmospheric circulation. This improvement was superior for MTWs with a smaller time step.

	The impact of the MTW on the analogy criterion has been analysed per precipitation class, or the target day, for 6-h and 3-h MTWs. The results are summarised in Fig. \ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for the days with precipitation between two thresholds. With a reduction in the number of cases per class, the curves were not as smooth as those in the previous analyses. It is nevertheless clear that the improvements were larger for days with higher precipitation for both the 6-h and 3h MTW.

	The effect of the MTW on the S1 criterion was been decomposed per season and is presented in Fig. \ref{fig:changes_S1_seasons}. The differences among the seasons were substantial, with greater improvements shown for winter than summer. Analysis of the selected hours for the geopotential height predictor was then performed for the MTW with different time steps (Fig. \ref{fig:hours_selection_per_season}). The new choice of the temporal window in winter was more balanced between the different hours of the day, showing more regular repartition, and thus for all MTW time steps. This indicates a change in selection of a greater portion of the analogue dates in this method than that in the conventional approach. On the contrary, the days in summer showed a preference for the initial temporal window (Z500, 24 h and Z1000, 12 h). This is likely attributed to the more pronounced diurnal effects, which reduced the potential for improvement of the criteria. These effects are in phase with the daily cycle, and good analogues were essentially found for the same hours. When a 3-h MTW was used, the time step following the initial temporal window (Z500, 27 h and Z1000, 15 h) was selected almost as often as the initial values for all seasons. This result can be considered as relatively similar in terms of the solar influence. The other seasons were between these two extremes, which is consistent with their respective improvements in S1.

	\subsubsection{Moisture analogy}
	\label{sec:changes_analogy_moisture}

	When adding the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations did not increase when using the original parameters because they were conditioned by the $N_{1}$ previously selected analogues; however, their dates changed. In contrast to the AM on the atmospheric circulation only, both a reduction and an increase in the RMSE analogy criterion values were possible with the MTW compared with the static approach. The results of the second level of analogy, presented in Fig. \ref{fig:changes_RMSE}, showed no improvement in RMSE values regardless of the MTW time step. Unlike the first level of analogy, the relative changes in the RMSE values were distributed relatively symmetrically around zero.

	These criterion values were not improved by the MTW because the number of candidates was not higher; the $N_{1}$ days are the same as those selected in the first level of analogy. The use of an MTW did not increase the sample size in this case because the second level of analogy included only subsamples in the dates provided by the first level. However, this result of a globally null improvement in the RMSE values does not mean that the 2Z-2MI method cannot be improved by the MTW. After selection of the analogue dates for the synoptic circulation, the new candidate dates did not provide better analogues in terms of moisture. However, the selected dates changed in the first level of analogy and in the final selection; thus, the distributions of precipitation values were different, which can affect the performance of the precipitation prediction.

	\subsection{Impact of the MTW on the precipitation prediction}
	\label{sec:influence_scores}

	The changes in the performance score (CRPS) of the precipitation prediction are provided in Fig. \ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI} for the 2Z and 2Z-2MI methods, respectively. The AMs were recalibrated on the CP and were assessed on the independent VP. The score was processed for each station and both reanalysis datasets. For ERA-20C, the 12-h MTW, 6-h MTW, and 3-h MTW could be assessed, whereas only the two first could be processed with the MERRA-2 dataset.

	The MTW improved the precipitation prediction because the CRPS globally decreased for all stations, both for the CP and the VP. The VP showed greater variability, which is likely related to its short period of six years. The prediction skill for the CP was almost always improved further by reducing the time step of the MTW, but not at the same magnitude. For ERA-20C, the magnitude of the improvement of 2Z for the CP was relatively reduced when using a 3-h MTW instead of a 6-h MTW, and the variability for the VP increased. However, as shown in Fig. \ref{fig:changes_S1}, the selection of analogue dates was improved relatively equally for every reduction of the MTW time step. A possible reason is that the ERA-20C dataset was built by assimilating only surface observations, whereas the AMs rely on the geopotential height at 500 hPa. Thus, the timing of the atmospheric circulation at higher pressure levels might not be completely in phase with the actual perturbation systems which caused the observed precipitations. The MTW with the MERRA-2 dataset and the 2Z method also showed a certain slope break after the 12-h MTW that could not be explained and was less important for the 2Z-2MI method. However, the 12-h MTW resulted in important variability for the 2Z-2MI method and the MERRA-2 dataset.

	The introduction of an MTW was previously found to show greater improvement of the S1 criterion for days with higher precipitation values (Sect. \ref{sec:changes_analogy_circul}). The impact of the MTW was then assessed in terms of changes in prediction performance per precipitation class for the target day. Figure \ref{fig:changes_CRPS_precip_threshold} synthesises these differences for the Ulrichen station by using the original parameters with the MTW. After the introduction of the MTW, the performance score was generally further improved with reduced CRPS for days with higher precipitation than for non-rainy days and small precipitation values. When recalibrating the parameters using the MTW, the spread of the changes in CRPS tended to decrease, although a slight loss in performance was noted for the most rainy days (not shown).

	Reliability diagrams were also created for the VP for both 2Z and 2Z-2MI methods and for percentiles exceeding 80~\% (P80, 4 mm), 90~\% (P90, 9.5 mm), and 95~\% (P95, 17.5 mm) at the Ulrichen station (Fig. \ref{fig:reliability_diagrams}). These diagrams plot the observed frequency against the predicted probability of a binary event, which in this case is threshold exceedance. For perfectly calibrated predictions, the curve should be as close as possible to the diagonal. The VP contains only six years (Sect. \ref{sec:data_methods}); therefore, higher variability is present for higher thresholds, and the curves are smoother and closer to the diagonals for the CP, which is longer (not shown). Figure \ref{fig:reliability_diagrams} shows that the MTW improved the reliability for both 2Z and 2Z-2MI methods and for all thresholds because the curves moved towards the diagonal with decreasing MTW time steps. For P80, the 3-h MTW predictions fit very well the observed frequency. When considering higher thresholds, the 2Z-2MI method was generally better than 2Z. The case of the P95 threshold showed a conditional dry bias associated with larger forecast probabilities for the considered AMs; however, this was substantially reduced by the 3-h MTW. This conditional dry bias means that the AM did not predict the event with a probability equal to 1 for 2Z. Obtaining a predicted probability of exceedance of 1 would mean that all analogue dates for a certain target date would be above the threshold. The number of analogue dates is 30 in this case; it is less likely to have 30 values above the threshold when the MTW increases. This issue is the topic of ongoing research. However, as shown in Figure \ref{fig:reliability_diagrams}, the introduction of an MTW, especially with a 3-h time step, improves this mismatch to some degree.

	\section{Discussion}
	\label{sec:discussion}

	\subsection{Better prediction of heavy precipitation}

	Both the analogy criteria (Sect. \ref{sec:changes_analogy_circul}) and the performance scores (Sect. \ref{sec:influence_scores}) were improved to a greater extent for days with heavier precipitation. This is likely attributed to the fact that higher precipitation events are a consequence of atmospheric conditions with greater dynamics such as weather disturbances, which have well-marked temporal evolution. Indeed, the position of the driving elements, such as the low-pressure centres and the fronts, change significantly during the course of a day. These situations are less numerous than anticyclonic situations, which makes it less likely to find very good analogues at the same time of the day. We can, therefore, expect to more significantly improve these situations with greater dynamics when introducing an MTW because better matches to the target situation may be found. In contrast, days with low dynamics in atmospheric circulation, such as anticyclonic situations, will not be radically improved by the introduction of the MTW.

	The MTW improved the prediction for days with heavier precipitation, Therefore, it should improve the prediction of extremes owing to better analogue situations and to possible new extreme values resulting from 24 h totals with a certain time shift. However, even though the distribution of analogue precipitation values should move towards the targeted extreme to provide better prediction, the MTW itself does not enable prediction of extreme events that were not yet observed and are therefore not present in the archive. The extremes in AMs can be modelled by extrapolation of a truncated exponential or gamma distribution fitted to the analogue values \citep{Obled2002}. Another possible approach is to combine AMs with other methods \citep[e.g.][]{Chardon2014}. From this perspective, the MTW might improve the prediction of extremes because it improves the distribution of precipitation values for days with higher precipitation, on which post-treatment techniques rely. However, this topic is beyond the scope of the present study.

	\subsection{The relationship between the MTW time step and the number of analogues}
	\label{sec:increase_analognb}

	When recalibrating the AMs with MTWs of different time steps, the optimal number of analogues changed for both 2Z and 2Z-2MI methods. $N_{1}$ and $N_{2}$, from the first and the second level of analogy, tended to significantly increase with a reduced MTW time step (Fig. \ref{fig:analog_nb}). When using ERA-20C, all optimal numbers of analogues for the different analogy levels tended to double when using a 6-h MTW instead of the classic approach and to even triple when using a 3-h MTW. These higher numbers of analogues were objectively chosen by using the calibration procedure (Sect. \ref{sec:calibration}) in order to increase the prediction skill of the methods.

	As shown in Fig. \ref{fig:changes_S1}, the improvement of the S1 criterion increases along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions. Widening the selection of analogues appears to be beneficial for keeping some with increased rank because they appear to be relevant in predicting the precipitation values. The number of good analogues was globally increased.

	A higher number of analogues generally resulted in a poorer analogy with an archive of fixed length. Indeed, when the choice of the predictors or the parameters improved, leading to a better prediction, the optimal number of analogue situations decreased. However, when the length of the archive increased, the optimal number of analogues also increased for better performance up to a certain threshold \citep[][]{Bontron2004, Hamill2006a}. The observed increase in the number of analogue situations with the MTW resulted in better performance skills for the given methods because it can be considered as an inflation of the archive. However, if new relevant predictors were added to the method, the number of analogues would then decrease again.

	\subsection{Inflation of the archive}
	\label{sec:archive_reduction}

	Because sub-daily precipitation time series are often available on a shorter period than daily, a reduction of the archive length at disposal is implied in the search of analogue situations. This usually has a negative consequence on the skill of precipitation prediction. The role of the archive length was assessed on the ERA-20C dataset and is presented in Fig. \ref{fig:plots_archive_length} for both 2Z and 2Z-2MI methods using the conventional approach of 24-h windows. As expected, the performance of the method globally increased with the length of the archive. The best performances were found with a 44-year archive, which corresponds to the period 1961--2010 minus the 6 years of independent VP. This addition of 21 years of archive to the original 23 years resulted in an improvement of both 2Z and 2Z-2MI methods that was of the same order of magnitude as the introduction of a 6-h-MTW (Fig. \ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI}). The 3-h MTW resulted in similar performance for the 2Z method and slightly superior improvements for the 2Z-2MI method.

	As previously stated, the MTW can be considered as an inflation of the archive because it provides additional situations to the pool of possible analogues. With the introduction of the MTW, the performance loss related to an eventual reduction of the archive length to meet the length of the sub-daily precipitation archive was compensated. A 6-h MTW brought gains of the same magnitude similar to an almost double archive length. However, it should be noted that despite the number of candidate situations, which in this case is four times the original number, the gains appear to be lower than those for a quadrupled archive length. The likely reason is that an actual longer archive would contain more atmospheric situations that might have been observed less frequently during a shorter period. Moreover, high correlations between sub-daily circulation patterns are expected.

	Many reanalysis datasets begin in the 80s owing to availability of satellite data and are thus more accurate than reanalysis datasets based on conventional data only; however, they provide shorter archives. When using such an archive, the MTW approach shows a certain potential for enriching the pool of possible analogues. Moreover, in a transient climate, the eventual nonstationarity of the link between predictors and precipitation might discard the relevance of analogues from the distant past and can increase the relevance of using a more recent and shorter archive rather than a long one. In such cases, the archive inflation brought by the MTW is also relevant.

	\subsection{Reconstruction of a long precipitation archive suitable for the MTW}
	\label{sec:reconstruction}

	As discussed in Sect. \ref{sec:archive_reduction}, the skills of AMs improved with the length of the archive. It would then be even more profitable to apply the MTW to the longest archive possible rather than being limited to the period in which sub-daily precipitation data are available. Therefore, in order to reconstruct longer archives of moving 24-h totals, disaggregation techniques can be used. In this study, two simple disaggregation approaches of the daily precipitation time series were assessed.

	The first technique is a proportional distribution in which the observed daily precipitations were considered to be constant during the measurement period of 06:00 UTC to 06:00 UTC the following day. The proportional parts of the original daily time series were allocated into a new moving average of 24 h totals.

	The second approach was used to obtain data that are closer to the chronology of the actual precipitation by relying on informative proxy variables during the reconstruction procedure. Data from NCEP/NCAR reanalysis 1 were used for this purpose. Precipitable water and relative humidity at 1000 hPa, 925 hPa, or 850 hPa were assessed at the four points surrounding the catchment. Precipitation time series from the reanalysis were not considered owing to the presence of zeros, which may not always match the prediction; this can lead to an undefined temporal repartition. A time lapse of -12 h to +12 h between both series was allocated to consider the significant distance separating the weather stations and the reanalysis grid point. The best proxy variable, precipitable water, was identified through correlation analyses on non-zero values with the 6-h precipitation time series. When the best proxy was selected, its temporal profile was used in order to disaggregate the daily precipitation time series.

	These two simple methods did not result in valuable outputs (results not shown). Indeed, the performance improvement brought by the MTW was lost owing to the poor quality of the precipitation archives. A slight improvement was obtained for the second method which relied on a proxy variable rather than the proportional distribution method. However, this  improvement was relatively small, and most of the benefit of the MTW was lost. Another reanalysis dataset with more accurate moisture variables could produce better proxies.

	These attempts to transpose the MTW on the total archive highlight the importance of the actual rainfall chronology. The MTW is beneficial if the precipitation series are close to the observed values. In the absence of a precipitation series with accurate sub-daily chronology, the introduction of an MTW does not improve the precipitation prediction.

	\conclusions  %% \conclusions[modified heading if necessary]
	\label{sec:conclusions}

	The AMs are most often based on a daily time step owing to the availability of long precipitation archives. However, it is unlikely that two analogue synoptic situations which evolve relatively quickly would correspond optimally at the same hours of the day. It is probable that better matches may be found at a different hour, which can change the selection of the analogue dates.

	As shown in previous research \citet{Finet2008}, the introduction of an MTW enables better analogue situations to be obtained in terms of atmospheric circulation. Using recent reanalysis datasets, MTWs with 12-h, 6-h, and 3-h time steps were assessed in the present study. Improvement in the S1 criterion values increased with the rank of the analogue owing to the accumulation of better analogues within the predicted distributions. Moreover, the improvement in the S1 criterion increased for smaller MTW time steps.

	A seasonal effect was highlighted such that the MTW was more profitable for winter than for summer. A likely reason is that the diurnal cycle has a greater effect in summer than in winter, which results in better analogues at the same time of the day. The preference for the same hours in summer has been demonstrated, whereas a large part of the analogue situations were selected at a different time in winter.

	The MTW improved the precipitation prediction, with the CRPS showing a global decrease for all stations for both the CP and VP. The prediction skill for the CP was almost always improved further by reducing the time step of the MTW, but the magnitude differed. The results for the VP showed the same global trends but had more variability. Moreover, the reliability of the considered AMs improved for the prediction of different threshold exceedances, especially with a 3-h MTW.

	Improvements of the analogy criterion and the performance scores were both found to be higher for MTWs with a smaller time step of 3 h. A 3-h MTW provided eight times more candidate situations, although they were not fully independent. Because the MTW provides additional situations to the pool of possible analogues, it can be considered as an inflation of the archive.

	The improvement in the circulation analogy and the change in performance of the precipitation prediction was found to be more important for days with heavier precipitation. These results are generally related to more dynamic atmospheric situations and are less frequent in the archive. These situations have more specific circulation patterns that are evolving more rapidly. Therefore, an MTW was found to be of particular interest in this type of situation and is beneficial for the prediction of heavier precipitation events.

	The importance of the quality of the precipitation archive was also demonstrated because simplistic reconstructions of sub-daily time series led to a loss of all the improvement brought by the MTW. The precipitation prediction improved only when the precipitation chronology was close to the accurate values. Attempts to reconstruct longer time series based on simplistic proportional distributions or by using meteorological variables from the NCEP reanalysis 1 dataset as a proxy were not successful. Other reanalysis datasets with more accurate moisture variables could show better performance.

	The use of the MTW relies partly on the availability of long precipitation series at a sub-daily time step and with high accuracy. The precipitation data archives of high temporal resolution have increased over time. Other possible sources of such archives is the establishment of precipitation reanalysis at a regional scale in addition to the use of reanalysis-driven regional climate models or limited area models over a long period. Even though outputs from these models might be biased or not accurate enough, information regarding the timing of the precipitation events could be useful in disaggregating the station time series.

	The introduction of the MTW improved the selection of synoptic analogues. Regardless of its impact on the prediction skill for precipitation or the availability of a predictand time series with a sub-daily time step, this improvement has the potential for application to long meteorological archives. For example, when processing forecasts for a target day showing synoptic similarity with known situations from the past related to extreme weather, they can be used even if no precipitation archive is available. Thus, it is worth knowing whether the situation at hand correlates to such an analogue in the past. Another possible application is quality assessment of the selection of analogues on a shorter period, where sub-daily precipitation data are available. Indeed, if the selection of analogues with the MTW on a long period for a specific target day differs from the selection for a short period, a sub-optimal forecast could be obtained. Finally, although other predictands might not need sub-daily total values, point observations such as hail or extreme wind gusts make them easier to use with the MTW.

	The technique is very simple and easily applicable. Therefore, it should be considered for several applications in different contexts, particularly for operational forecasting or climate-related studies.

	\appendix
	\section{Acronyms}    %% Appendix A

	\begin{labeling}{2Z-2MI}
		\item [2Z] Name of analogue method of atmospheric circulation
		\item [2Z-2MI] Name of analogue method composed of a first level on atmospheric circulation and a second level on a moisture index
		\item [AM] Analogue method
		\item [CP] Calibration period
		\item [CRPS] Continuous ranked probability score
		\item [MTW] Moving time window
		\item [NCAR] National Center for Atmospheric Research
		\item [NCEP] National Center for Environmental Prediction
		\item [RH850] Relative humidity at 850 hPa
		\item [RMSE] Root--mean--square error
		\item [S1] Teweles and Wobus (1954) score
		\item [TPW] Total precipitable water
		\item [VP] Validation period
		\item [Z1000] Geopotential height at 1000 hPa
		\item [Z500] Geopotential height at 500 hPa
	\end{labeling}

	\competinginterests{The authors declare that they have no conflict of interest.}

	\begin{acknowledgements}
		The authors thank the Swiss Federal Office for Environment (FOEV), the Roads and Water Courses Service, Energy and Water Power Service of the Wallis Canton, and the Water, Land, and Sanitation Service of the Vaud Canton which financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research. Thanks are also extended to Dominique B\'{e}rod for his support.

		The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible by the Herbette Foundation.

		NCEP reanalysis data were obtained from the Web site of the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, at http://www.esrl.noaa.gov/psd/. Precipitation time series were provided by MeteoSwiss.

		The authors would also like to acknowledge the work of anonymous reviewers who contributed to improving this manuscript. 
	\end{acknowledgements}

	%% REFERENCES

	%% The reference list is compiled as follows:

	\bibliographystyle{copernicus}
	\bibliography{references}

	\begin{figure}[htb]
		\begin{center}
			\includegraphics[width=8.3cm]{fig01.pdf}
		\end{center}
		\caption{Position of the six weather stations of interest (Aigle, Montana, Sion, Ulrichen, Visp, and Zermatt) in the upper Rh\^{o}ne catchment in Switzerland.}
		\label{fig:map}
	\end{figure}

	\begin{figure}[htb]
		\begin{center}
			\includegraphics[width=8cm]{fig02.pdf}
		\end{center}
		\caption{Illustration of the principle of a moving time window (MTW). The target situation is the same for the conventional approach and the MTW, although the candidate situations with the MTW are two, four, or eight times as many. The horizontal bars represent the 24h precipitation totals; their associated predictors are listed on the right-hand side.}
		\label{fig:principle}
	\end{figure}

	\begin{figure*}[htb]
		\begin{center}
			\includegraphics[width=17cm]{fig03.pdf}
		\end{center}
		\caption{Changes in S1 criterion distributions owing to the introduction of an MTW with a 12-h, 6-h, or 3-h time step. Distributions are provided for (a) the $1^{st}$, (b) $15^{th}$, and (c) $30^{th}$ analogue ranks for all days of the CP at the Ulrichen station.}
		\label{fig:changes_S1_analogs}
	\end{figure*}

	\begin{figure}[htb]
		\begin{center}
			\includegraphics[width=8.3cm]{fig04.pdf}
		\end{center}
		\caption{Synthesis of the changes in the S1 criterion owing to the MTW with 12-h, 6-h, and 3-h time steps for the Ulrichen station depending on the rank of the analogue. (a) Quantiles of the S1 distributions corresponding to the MTW with different time steps; 24-h is the conventional approach without MTW. (b) Quantiles of the relative improvements of the S1 criterion when using the MTW compared with the conventional approach.}
		\label{fig:changes_S1}
	\end{figure}

	\begin{figure}[htb]
		\begin{center}
			\includegraphics[width=8.3cm]{fig05.pdf}
		\end{center}
		\caption{Distribution of the median improvements of the S1 criterion owing to the (a) 3-h MTW and (b) 6-h MTW, depending the on daily precipitation thresholds at the Ulrichen station.}
		\label{fig:changes_S1_precip_threshold}
	\end{figure}

	\begin{figure}[htb]
		\begin{center}
			\includegraphics[width=8.3cm]{fig06.pdf}
		\end{center}
		\caption{Seasonal effect on the median reduction of the S1 criterion for the Ulrichen station owing to the MTW. DJF: winter; MAM: spring; JJA: summer; SON: fall.}
		\label{fig:changes_S1_seasons}
	\end{figure}

	\begin{figure}[htb]
		\includegraphics[width=7.5cm]{fig07.pdf}
		\caption{Distribution of the predictor hours on the selected analogue dates for the Ulrichen station when using a (a) 12-h MTW, (b) 6-h MTW, and (c) 3-h MTW, depending on the season.}
		\label{fig:hours_selection_per_season}
	\end{figure}

	\begin{figure}[htb]
		\begin{center}
			\includegraphics[width=8.3cm]{fig08.pdf}
		\end{center}
		\caption{Synthesis of the changes in the RMSE criterion owing to the MTW for the Ulrichen station, depending on the rank of the analogue. (a) Quantiles of the RMSE distributions with and without the MTW. (b) Quantiles of the relative improvements of the RMSE criterion when using the MTW.}
		\label{fig:changes_RMSE}
	\end{figure}

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig09.pdf}
		\caption{Changes in performance score (CRPS) of the 2Z method at the different stations for MTW of varying time steps relative to the conventional approach of 24 h. Results are provided for ERA-20C for the (a) CP and (b) VP as well as for MERRA-2 for the (c) CP and (d) VP. Lower CRPS values indicate better performance.}
		\label{fig:plots_CRPS_2Z}
	\end{figure}

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig10.pdf}
		\caption{Same as Figure \ref{fig:plots_CRPS_2Z} but for the 2Z-2MI method.}
		\label{fig:plots_CRPS_2Z-2MI}
	\end{figure}

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig11.pdf}
		\caption{Differences in the CRPS values at the Ulrichen station owing to the introduction of the MTW as a function of different daily precipitation thresholds for the target date. The results are provided for the 2Z method (top) and the 2Z-2MI method (bottom) with a 6-h MTW (left) and a 3-h MTW (right). Stars represent averages. Lower CRPS values indicate better improvements.}
		\label{fig:changes_CRPS_precip_threshold}
	\end{figure}

	\begin{figure*}[htb]
		\begin{center}
			\includegraphics[width=14cm]{fig12.pdf}
		\end{center}
		\caption{Reliability diagrams for the 2Z (left) and 2Z-2MI (right) methods and the prediction of percentile exceedance of 80~\% (top), 90~\% (middle), and 95~\% (bottom) at the Ulrichen station for the VP. The conventional approach of 24 h is provided as well as the 12-h, 6-h, and 3-h MTWs.}
		\label{fig:reliability_diagrams}
	\end{figure*}

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig13.pdf}
		\caption{Optimal number of analogues of the first and second levels of analogy, $N_{1}$ and $N_{2}$, respectively, for the (a) 2Z and (b), (c) 2Z-2MI methods after recalibration using the MTW.}
		\label{fig:analog_nb}
	\end{figure}

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{fig14.pdf}
		\caption{Change in performance score (CRPS) of the 2Z (top)  and 2Z-2MI (bottom) methods at the different stations for the CP (left) and VP (right) for an increasing archive length with the conventional approach of 24-h window. Lower CRPS scores indicate better results.}
		\label{fig:plots_archive_length}
	\end{figure}

	\clearpage

	\begin{table}[htb]
		\caption{Parameters for the reference method on the atmospheric circulation (2Z). The first column shows the level of analogy (0 for preselection), and the second column shown the meteorological variable and its hour of observation. The criterion used for the current level of analogy is also provided as well as the number of analogues.}
		\footnotesize
		\begin{center}
			\begin{tabular}{ccccc}
				\hline
				Level & Variable & Hour & Criterion & Nb \\ 
				\hline 
				0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
				\hline 
				\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{$N_{1}$} \\
				& Z500 & 24~h & & \\ 
				\hline 
			\end{tabular} 
		\end{center}
		\label{table:method_2Z}
	\end{table}

	\begin{table}[htb]
		\caption{Parameters of the reference method with moisture variables (2Z-2MI). The conventions are the same as those in Table \ref{table:method_2Z}}
		\footnotesize
		\begin{center}
			\begin{tabular}{ccccc}
				\hline 
				Level & Variable & Hour & Criterion & Nb \\ 
				\hline 
				0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
				\hline 
				\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{$N_{1}$} \\
				& Z500 & 24~h & & \\ 
				\hline
				\multirow{2}{*}{2} & TPW * RH850 & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{2}$} \\
				& TPW * RH850 & 24~h & & \\ 
				\hline 
			\end{tabular} 
		\end{center}
		\label{table:method_2Z-2MI}
	\end{table}

	%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
	%% authors experienced with BibTeX only have to include the following two lines:
	%%
	%% \bibliographystyle{copernicus}
	%% \bibliography{example.bib}
	%%
	%% URLs and DOIs can be entered in your BibTeX file as:
	%%
	%% URL = {http://www.xyz.org/~jones/idx_g.htm}
	%% DOI = {10.5194/xyz}

	%% LITERATURE CITATIONS
	%%
	%% command                        & example result
	%% \citet{jones90}|               & Jones et al. (1990)
	%% \citep{jones90}|               & (Jones et al., 1990)
	%% \citep{jones90,jones93}|       & (Jones et al., 1990, 1993)
	%% \citep[p.~32]{jones90}|        & (Jones et al., 1990, p.~32)
	%% \citep[e.g.,][]{jones90}|      & (e.g., Jones et al., 1990)
	%% \citep[e.g.,][p.~32]{jones90}| & (e.g., Jones et al., 1990, p.~32)
	%% \citeauthor{jones90}|          & Jones et al.
	%% \citeyear{jones90}|            & 1990

	%% FIGURES

	%% ONE-COLUMN FIGURES

	%%f
	%\begin{figure}[t]
	%\includegraphics[width=8.3cm]{FILE NAME}
	%\caption{TEXT}
	%\end{figure}
	%
	%%% TWO-COLUMN FIGURES
	%
	%%f
	%\begin{figure*}[t]
	%\includegraphics[width=12cm]{FILE NAME}
	%\caption{TEXT}
	%\end{figure*}
	%
	%
	%%% TABLES
	%%%
	%%% The different columns must be separated with a & command and should
	%%% end with \\ to identify the column brake.
	%
	%%% ONE-COLUMN TABLE
	%
	%%t
	%\begin{table}[t]
	%\caption{TEXT}
	%\begin{tabular}{column = lcr}
	%\tophline
	%
	%\middlehline
	%
	%\bottomhline
	%\end{tabular}
	%\belowtable{} % Table Footnotes
	%\end{table}
	%
	%%% TWO-COLUMN TABLE
	%
	%%t
	%\begin{table*}[t]
	%\caption{TEXT}
	%\begin{tabular}{column = lcr}
	%\tophline
	%
	%\middlehline
	%
	%\bottomhline
	%\end{tabular}
	%\belowtable{} % Table Footnotes
	%\end{table*}
	%
	%
	%%% NUMBERING OF FIGURES AND TABLES
	%%%
	%%% If figures and tables must be numbered 1a, 1b, etc. the following command
	%%% should be inserted before the begin{} command.
	%
	%\addtocounter{figure}{-1}\renewcommand{\thefigure}{\arabic{figure}a}
	%
	%
	%%% MATHEMATICAL EXPRESSIONS
	%
	%%% All papers typeset by Copernicus Publications follow the math typesetting regulations
	%%% given by the IUPAC Green Book (IUPAC: Quantities, Units and Symbols in Physical Chemistry,
	%%% 2nd Edn., Blackwell Science, available at: http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf, 1993).
	%%%
	%%% Physical quantities/variables are typeset in italic font (t for time, T for Temperature)
	%%% Indices which are not defined are typeset in italic font (x, y, z, a, b, c)
	%%% Items/objects which are defined are typeset in roman font (Car A, Car B)
	%%% Descriptions/specifications which are defined by itself are typeset in roman font (abs, rel, ref, tot, net, ice)
	%%% Abbreviations from 2 letters are typeset in roman font (RH, LAI)
	%%% Vectors are identified in bold italic font using \vec{x}
	%%% Matrices are identified in bold roman font
	%%% Multiplication signs are typeset using the LaTeX commands \times (for vector products, grids, and exponential notations) or \cdot
	%%% The character * should not be applied as multiplication sign
	%
	%
	%%% EQUATIONS
	%
	%%% Single-row equation
	%
	%\begin{equation}
	%
	%\end{equation}
	%
	%%% Multiline equation
	%
	%\begin{align}
	%& 3 + 5 = 8\\
	%& 3 + 5 = 8\\
	%& 3 + 5 = 8
	%\end{align}
	%
	%
	%%% MATRICES
	%
	%\begin{matrix}
	%x & y & z\\
	%x & y & z\\
	%x & y & z\\
	%\end{matrix}
	%
	%
	%%% ALGORITHM
	%
	%\begin{algorithm}
	%\caption{…}
	%\label{a1}
	%\begin{algorithmic}
	%…
	%\end{algorithmic}
	%\end{algorithm}
	%
	%
	%%% CHEMICAL FORMULAS AND REACTIONS
	%
	%%% For formulas embedded in the text, please use \chem{}
	%
	%%% The reaction environment creates labels including the letter R, i.e. (R1), (R2), etc.
	%
	%\begin{reaction}
	%%% \rightarrow should be used for normal (one-way) chemical reactions
	%%% \rightleftharpoons should be used for equilibria
	%%% \leftrightarrow should be used for resonance structures
	%\end{reaction}
	%
	%
	%%% PHYSICAL UNITS
	%%%
	%%% Please use \unit{} and apply the exponential notation

\end{document}

### 2017-04-05 Moving temporal window - HESS/template.tex
Elsevier editing for HESS.

@@
 	\begin{abstract}
-		Analogue methods (AMs) predict local weather variables (predictands), such as precipitation, by means of a statistical relationship with predictors at a synoptic scale.
-The analogy is generally assessed on gradients of geopotential heights first, in order to sample days with a similar atmospheric circulation.
-Other predictors, such as moisture variables, can also be added in a successive level of analogy.
+		Analogue methods (AMs) predict local weather variables (predictands) such as precipitation by means of a statistical relationship with predictors at a synoptic scale.
+The analogy is generally assessed on gradients of geopotential heights first to sample days with a similar atmospheric circulation.
+Other predictors such as moisture variables can also be added in a successive level of analogy.
 
 		The search for candidate situations for a given target day is usually undertaken by comparing the state of the atmosphere at fixed hours of the day for both the target day and the candidate analogues.
-This is a consequence of using daily precipitation time series, which are available on longer periods than subdaily data.
-However, it is unlikely for the best analogy to occur at the very same hour.
-A better analogue situation may be found with a time shift of some hours as it can occur at a different time of day.
+This is a consequence of using daily precipitation time series, which are available on longer periods than sub-daily data.
+However, it is unlikely for the best analogy to occur at the exact same hour.
+A better analogue situation may be found with a time shift of several hours because it can occur at different times of the day.
 In order to assess the potential for finding better analogues at a different hour, a moving time window (MTW) has been introduced.
 
-		The MTW resulted in a better analogy in terms of the atmospheric circulation, with improved values of the analogy criterion on the entire distribution of analogue dates.
-The improvement was found to grow with the analogue rank due to an accumulation of better analogues in the selection.
-A seasonal effect has also been identified, with larger improvements in winter than in summer, supposedly due to stronger diurnal cycles in summer that favour predictors at the same hour for the target and analogue days.
+		The MTW resulted in a better analogy in terms of the atmospheric circulation and showed improved values of the analogy criterion on the entire distribution of analogue dates.
+The improvement was found to increase with the analogue rank owing to an accumulation of better analogues in the selection.
+A seasonal effect has also been identified, with larger improvements shown in winter than in summer.
+This may be attributed to stronger diurnal cycles in summer that favour predictors at the same hour for the target and analogue days.
 
-		The impact of the MTW on the prediction skill has been assessed by means of a sub-daily precipitation series transformed into moving 24h totals at 12h, 6h, and 3h time steps.
-The prediction skill was found to have improved by the MTW, as well as the reliability of the prediction.
-Moreover, the improvements were greater for days with heavy precipitation, which are generally related to more dynamic atmospheric situations where timing is more specific and which are fewer in the meteorological archive.
+		The impact of the MTW on the prediction skill has been assessed by means of a sub-daily precipitation series transformed into moving 24 h totals at 12-h, 6-h, and 3-h time steps.
+The prediction skill was improved by the MTW, as was the reliability of the prediction.
+Moreover, the improvements were greater for days with heavy precipitation, which are generally related to more dynamic atmospheric situations in which the timing is more specific and fewer records are available in the meteorological archive.
 
-		Both improvements of the analogy criterion and the performance scores were found to be higher for MTWs with a smaller time step (3h).
-A 3h-MTW provides 8 times more candidate situations, even though not fully independent.
-As the MTW provides additional situations to the pool of possible analogues, it can be seen as an inflation of the archive.
-The technique being very simple and easily applicable, it should be considered for several applications in different contexts, may it be for operational forecasting or climate-related studies.
+		The improvements of the analogy criterion and the performance scores were both found to be higher for MTWs with a smaller time step  of 3 h.
+A 3-h MTW provides eight times more candidate situations even though they are not fully independent.
+Because the MTW provides additional situations to the pool of possible analogues, it can be considered as an inflation of the archive.
+Because this technique is very simple and easily applicable, it should be considered for several applications in different contexts, such as operational forecasting or climate-related studies.
 
@@
 
-	The Analogue method (AM) is based on the hypothesis that two relatively similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}.
-It is a statistical downscaling methods \citep[see][for other methods]{Maraun2010} and consist of finding past situations that are similar to the target day of interest in terms of the atmospheric circulation or other synoptic predictors.
-The local weather variables of interest (predictand) that were observed at the analogue dates are used to construct a probabilistic prediction for the target day \citep{Duband1970, Zorita1999}.
-Multiple variations of the method exist \citep[a non-exhaustive listing can be found in][]{BenDaoud2016}.
-The AMs are used for operational precipitation forecasting, either in the context of weather forecasting, flood forecasting, or hydropower production \citep[e.g.,][]{Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as for precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}.
-AMs can provide multivariate predictions that are physically consistent \citep{Raynaud2016b}.
-Their spatial transferability is analysed in \citet{Chardon2014} and \citet{Radanovics2013}.
-Their temporal transferability has also been the topic of recent studies for past or future climates \citep{Dayon2015, Caillouet2016}.
+	The analogue method (AM) is a statistical downscaling method based on the hypothesis that two relatively similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}.
+Other statistical downscaling methods for climate studies can be found in \citet{Maraun2010}.
+The AM consists of finding past situations that are similar to the target day of interest in terms of atmospheric circulation or other synoptic predictors.
+Referred to as the predictand, the local weather variables of interest which were observed at the analogue dates are used to construct a probabilistic prediction for the target day \citep{Duband1970, Zorita1999}.
+Multiple variations of this method have been reported \citep{BenDaoud2016}.
+AMs are used for operational precipitation forecasting in the context of weather forecasting, flood forecasting, and hydropower production \citep[e.g.,][]{Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as for precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}.
+AMs can provide multivariate predictions which are physically consistent \citep{Raynaud2016b}.
+Their spatial transferability is analysed in \citet{Chardon2014} and \citet{Radanovics2013}, and their temporal transferability has been discussed in recent studies for past or future climates \citep{Dayon2015, Caillouet2016}.
 
@@
 The first is a meteorological archive describing the state of the atmosphere at a synoptic scale, such as reanalysis datasets.
-The second is an archive of the target variable to be predicted, here precipitation.
-It is most often made of daily precipitation totals at a target station or integrated over a target catchment.
+The second is an archive of the target variable to be predicted, which in this study is precipitation, usually composed of daily precipitation totals at a target station or integrated over a target catchment.
 Obviously, the period to be used is limited to the smallest period common to the two archives.
 
-	\citet{Ruosteenoja1988} and \citet{Vandendool1994} have analysed the influence of the length of the meteorological archive on the quality of the analogy.
-They highlighted a three-way relationship between the quality of the analogy, the archive length, and the size of the spatial domain (or degrees of freedom): errors increase with a bigger domain, but decrease with a longer archive.
-For that reason, limited spatial windows are always considered when searching for analogues, and the archive length is maximized.
+	\citet{Ruosteenoja1988} and \citet{Vandendool1994} analysed the influence of the length of the meteorological archive on the quality of the analogy.
+They highlighted a three-way relationship among the quality of the analogy, the archive length, and the size of the spatial domain (or degrees of freedom) and determined that errors increase with a larger domain but decrease with a longer archive.
+For that reason, limited spatial windows are always considered when searching for analogues, and the archive length is maximised.
 
-	Therefore, due to the availability of long precipitation archives at a daily time step that have no equivalent at a finer resolution, AMs are usually implemented on a daily basis.
-Consequently, the analogue situations are assessed by comparing predictors at fixed hours of the day.
+	Therefore, owing to the availability of long precipitation archives at a daily time step that have no equivalent at a finer resolution, AMs are usually implemented on a daily basis, and the analogue situations are assessed by comparing predictors at fixed hours of the day.
 However, it can be expected that the analogy of the synoptic situations does not occur systematically at the same time of the day and that better candidates can be found by shifting to a different hour.
 With this assumption, a moving time window (MTW) was introduced to allow the search for candidates at different hours of the day.
-Previous tests showed the benefit, in terms of analogy criterion values, of searching for analogue synoptic situations at a finer time step, but without assessing the impact on the prediction skill \citep{Finet2008}.
+Previous tests have showed the benefit, in terms of analogy criterion values, of searching for analogue synoptic situations at a finer time step, although such research did not assess the impact on the prediction skill \citep{Finet2008}.
 
-	One can question the interest of using moving daily totals when for example 6-hourly precipitation series can be predicted instead.
-However, the 6-hourly time series generated by the AM might not represent accurately the intra-daily precipitation distribution or variability.
-In addition, sometimes a resolution finer than the daily time step is not needed and another disaggregation technique may be used afterwards.
-Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact on 24h totals than 6h totals.
+	One can question the interest of using moving daily totals when, for example, 6-h precipitation series can be predicted instead.
+However, the 6-h time series generated by the AM might not accurately represent the intra-daily precipitation distribution or variability.
+In addition, sometimes a resolution finer than the daily time step is not needed, and another disaggregation technique may be used afterwards.
+Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact on 24-h totals than on 6-h totals.
 
-	The MTW finds analogue situations at different hours of the day, which can also be seen as an inflation of the archive length.
-However, despite having $x$ time more candidate situations, the quantity of new information is not expected to be as important as an $x$ time longer archive due to significant correlation between successive situations within the same day.
-Nevertheless, if the MTW can improve the prediction skill of the AM, it means that it does extract new information from the archive.
+	The MTW finds analogue situations at different hours of the day, which can also be considered as an inflation of the archive length.
+However, despite having e.g.
+eight times more candidate situations, the quantity of new information is not expected to be as important as an eight time longer archive owing to significant correlation between successive situations within the same day.
+Nevertheless, if the MTW can improve the prediction skill of the AM, it can extract new information from the archive.
 
 	Other possibilities exist for increasing the prediction skill of the AMs.
-A classical approach is to add new predictors or new successive levels of analogy \citep[see e.g.][]{Horton2012a, BenDaoud2016, Caillouet2016}.
-AMs can also be combined with other methods \citep[see e.g.][]{Chardon2014}.
+A classical approach is to add new predictors or new successive levels of analogy \citep[e.g.][]{Horton2012a, BenDaoud2016, Caillouet2016}.
+AMs can also be combined with other methods \citep[e.g.][]{Chardon2014}.
 Another possibility is to use a global optimization technique, such as genetic algorithms, in order to better optimize the method and to add new parameters \citep{Horton2017}.
-However, the MTW technique is not in competition with other approaches and can be combined with these.
+However, the MTW technique is not in competition with other approaches and can be combined with them.
 
 	Section \ref{sec:data_methods} presents the context of the study as well as the data and methods, including the proposed MTW technique.
-The benefits of introducing an MTW were assessed first in regards to the improvement of the analogue dates selection (Sect.
+The benefits of introducing an MTW are assessed first regarding the improvement of the analogue date selection (Sect.
 \ref{sec:influence_analogue_dates}) and then in terms of precipitation prediction skill (Sect.
@@
 	The study area is the upper Rh\^{o}ne catchment in Switzerland.
-Precipitation time series come from six automatic weather stations, viz., Ulrichen, Zermatt, Visp, Montana, Sion, and Aigle (Fig.
-\ref{fig:map}) that are subject to various meteorological influences \citep{Horton2012}.
-The data were available at an hourly time step for 29~years (1982\textendash 2010) and were also obtained at a daily time step (from 6:00~UTC to 6:00~UTC the next day) for 50~years (1961\textendash 2010).
-Due to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed.
-The results will hereafter be presented arbitrarily for the Ulrichen station but are equivalent for all stations.
+The precipitation time series were obtained from six automatic weather stations, Ulrichen, Zermatt, Visp, Montana, Sion, and Aigle (Fig.
+\ref{fig:map}), that are subject to various meteorological influences \citep{Horton2012}.
+The data were available at an hourly time step for 29 years (1982\textendash 2010) and were also obtained at a daily time step of 06:00 UTC to 06:00 UTC the following day for 50 years (1961\textendash 2010).
+Owing to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed.
+The results are presented arbitrarily for the Ulrichen station but are equivalent for all stations.
 
-	Synoptic-scale variables, used as predictors, were extracted from two of the most recent global reanalysis datasets: the european ERA-20C \citep{Poli2016} with a 3h temporal resolution and a spatial resolution of 1\textdegree, and MERRA-2 from NASA with a 6h temporal resolution and a spatial resolution of 0.625\textdegree x 0.5\textdegree.
-The study was originally performed on the NCEP/NCAR reanalysis 1 dataset \citep{Kalnay1996}, and the conclusions were similar.
-ERA-20C is build by assimilating only surface observations, and is thus available on a long period (1900\textendash 2010).
-On the contrary, MERRA-2 is build by assimilating observations at higher levels and from more sensors, including satellite data, but is then more limited in time (1980\textendash present).
-It is of interest to assess the relevance of an MTW with these two datasets, as they represent different kind of products.
-The specific advantages of ERA-20C is that it allows testing an MTW with a 3h time step, and it covers a long period.
-On the other hand, MERRA-2 has a higher spatial resolution and can be expected to be more accurate at higher levels of the atmosphere.
-The variables extracted from these datasets were geopotential heights at 500~hPa (Z500) and 1000~hPa (Z1000), as well as the total precipitable water (TPW) and the relative humidity at 850~hPa (RH850).
+	Synoptic-scale variables used as predictors were extracted from two of the most recent global reanalysis datasets: the European Center for Medium Range Weather Forecasting 20th century reanalysis (ERA-20C) \citep{Poli2016}, with 3-h temporal resolution and a spatial resolution of 1\textdegree, and Modern-Era Retrospective Analysis for Research and Applications, Version 2 (MERRA-2), from the National Aeronautics and Space Administration (NASA), with a 6-h temporal resolution and a spatial resolution of 0.625\textdegree × 0.5\textdegree.
+The study was originally performed on the National Centers for Environmental Prediction/National Center for Atmospheric Research (NCEP/NCAR) reanalysis 1 dataset \citep{Kalnay1996}; the conclusions were similar.
+ERA-20C is built by assimilating only surface observations and is thus available for long periods (1900\textendash 2010).
+On the contrary, MERRA-2 is built by assimilating observations at higher levels and from more sensors including satellite data, but it is more limited in time (1980\textendash present).
+It is of interest to assess the relevance of an MTW with these two datasets because they represent different types of products.
+The specific advantages of ERA-20C are that it allows for testing an MTW with a 3-h time step, and it covers a long period.
+On the contrary, MERRA-2 has a higher spatial resolution and can be expected to be more accurate at higher levels of the atmosphere.
+The variables extracted from these datasets were geopotential heights at 500 hPa (Z500) and 1000 hPa (Z1000), the total precipitable water (TPW), and the relative humidity at 850 hPa (RH850).
 
@@
 
-	The first considered AM is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z};][]{Obled2002, Bontron2005}.
-Searching for analogue situations to a target day starts by a seasonal stratification through a preselection step of the potential candidates for analogy.
-The restriction is a search for analogue days within a 4-month window centred on the target date for every year of the archive.
-The similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1) that is a comparison of gradients on geopotential heights over a certain spatial window and at certain hours:
+	The first considered AM is based on the analogy of atmospheric circulation only \citep[Table \ref{table:method_2Z};][]{Obled2002, Bontron2005}.
+Before searching for analogue situations for a target day, seasonal stratification is conducted through preselection of the potential candidates for analogy.
+The search is restricted to analogue days within a four-month window centred on the target date for every year of the archive.
+The similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1), which is a comparison of gradients of geopotential heights over a particular spatial window and at certain hours:
 
@@
 	S_{1}=100 \frac {\displaystyle \sum_{i}^{m} \vert \Delta\hat{z}_{i} - \Delta z_{i} \vert}
-	{\displaystyle \sum_{i}^{m} max( \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert ) }
+	{\displaystyle \sum_{i}^{m} max( \vert \Delta\hat{z}_{i} \vert , \vert \Delta z_{i} \vert ) } ,
 	\end{equation}
@@
 	The predictor variables extracted from reanalysis datasets are considered at different hours of the day.
-Based on \citet{Bontron2005}, geopotential heights are compared at 1000~hPa (Z1000) at 12:00~UTC and 500~hPa (Z500) at 24:00~UTC.
-The time of the day at which the predictors are selected is found by \citet{Bontron2004} to have a significant influence.
+Based on \citet{Bontron2005}, geopotential heights are compared at 1000 hPa (Z1000) at 12:00 UTC and at 500 hPa (Z500) at 24:00 UTC.
+The time of the day at which the predictors are selected has a significant influence \citet{Bontron2004}.
 
-	Then, $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day, $N_{1}$ being a parameter to calibrate (see Sect.
+	Then, $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day, where $N_{1}$ is a calibration parameter ( Sect.
 \ref{sec:calibration}).
 Finally, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day.
-This method will be named 2Z.
+This method is referred to as 2Z.
 
-	The second reference method \citep[2Z-2MI, Table \ref{table:method_2Z-2MI};][]{Bontron2005} adds a subsequent level of analogy with moisture variables, compared by means of the root-mean-square error (RMSE):
+	The second reference method \citep[2Z-2MI, Table \ref{table:method_2Z-2MI};][]{Bontron2005} adds a subsequent level of analogy with moisture variables and is compared by means of the root--mean--square error (RMSE):
 
@@
 	\label{eq:RMSE}
-	E_{RMS}= \sqrt[]{ \frac{1}{n} \sum_{i=1}^{n}(\hat{v}_{i} - v_{i})^{2}} 
+	E_{RMS}= \sqrt[]{ \frac{1}{n} \sum_{i=1}^{n}(\hat{v}_{i} - v_{i})^{2}} ,
 	\end{equation}
@@
 
-	The additional predictor is a moisture index composed of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850) \citep{Bontron2004}.
+	The additional predictor is a moisture index composed of the product of the total precipitable water (TPW) with the relative humidity at 850 hPa (RH850) \citep{Bontron2004}.
 When adding a second level of analogy, $N_{2}$ dates are subsampled from the $N_{1}$ analogues on the atmospheric circulation, resulting in a smaller number of analogue situations.
-When a second level of analogy is added, a higher number of $N_{1}$ analogues is kept on the first level.
+Moreover, when a second level of analogy is added, a higher number of $N_{1}$ analogues is kept on the first level.
 
-	More complex AMs exist with additional predictors \citep[see e.g.][]{Horton2012a, BenDaoud2016, Caillouet2016}.
-The MTW can also be applied to these.
-However, it is easier to interpret the impact of the MTW using more basic methods.
+	More complex AMs exist with additional predictors \citep[e.g.][]{Horton2012a, BenDaoud2016, Caillouet2016}.
+The MTW can also be applied to these; however, it is easier to interpret the impact of the MTW by using more basic methods.
 
@@
 	AMs rely on parameters that need to be defined for every level of analogy.
-Here, the selection of the meteorological variables used as predictors, as well as their corresponding analogy criteria, pressure level, and hour of the day, were considered identical to the methods 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) described above.
-The parameters that were here calibrated are:
+Here, the selection of the meteorological variables used as predictors, as well as their corresponding analogy criteria, pressure level, and hour of the day, were considered to be identical to those used in methods 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) described above.
+The parameters calibrated in this study are listed below.
 
 	\begin{itemize}
-		\item The spatial windows, which are the domains on which predictors are compared.
-There is a spatial window specific to each level of analogy.
-It will thus differ between circulation and moisture variables.
+		\item Spatial windows, which are the domains in which the predictors are compared.
+A spatial window is specific to each level of analogy; thus, its extent differs among circulation and moisture variables.
 		\item The optimal number of analogue situations for every level of analogy.
@@
 
-	The semi-automatic sequential procedure elaborated by \citet{Bontron2004} was used to calibrate the AM \cite[see also][]{Radanovics2013, BenDaoud2016}.
+	The semi-automatic sequential procedure discussed by \citet{Bontron2004} was used to calibrate the AM \cite{Radanovics2013, BenDaoud2016}.
 The analogy levels (e.g.
 the atmospheric circulation or moisture index) are calibrated sequentially.
-The parameters calibrated by this approach, for every level of analogy, are the spatial windows on which the predictors are compared and the number of analogues.
+The spatial windows on which the predictors are compared and the number of analogues are the parameters calibrated by this approach for every level of analogy.
 The procedure, as defined by \citet{Bontron2004}, consists of the following steps:
@@
 	\begin{enumerate}
-		\item For every level of analogy:
+		\item For every level of analogy
 		\begin{enumerate}
-			\item Identification of the most skilled unitary cell (one point for moisture variables and four for geopotential heights in order to process the gradients) over a large domain.
-Every point (or cell) of the full domain is assessed on all predictors of the level of analogy, jointly (consisting generally of the same variable but on different pressure levels and at different hours).
-			\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain. The spatial window grows until no improvement is reached.
-			\item The number of analogue situations $N_{1}$, which was initially set at an arbitrary value, is then reconsidered and optimized for the current level of analogy.
+			\item Identification of the most skilled unitary cell of the predictor data over a large domain.
+Every point or cell of the full domain is jointly assessed on all predictors of the level of analogy consisting generally of the same variable but on different pressure levels and at different hours.
+			\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain.
+The spatial window increases until no improvement is reached.
+			\item The number of analogue situations $N_{1}$, which was initially set as an arbitrary value, is then reconsidered and optimised for the current level of analogy.
 		\end{enumerate}
-		\item A new level of analogy can then be added, based on other variables (such as the moisture index) at chosen pressure levels and hours of the day.
+		\item A new level of analogy can then be added based on other variables such as the moisture index at chosen pressure levels and hours of the day.
 The number of analogues for the next level of analogy, $N_{2}$, is initiated at a chosen value.
@@
 		\item Finally, the numbers of analogues $N_{1}$ and $N_{2}$ for the different levels of analogy are reassessed.
-This is done iteratively by varying the number of analogues of each level in a systematic way.
+This is performed iteratively by varying the number of analogues of each level in a systematic manner.
 	\end{enumerate}
 
-	The calibration is done in successive steps with a limited number of parameters in order to minimize the objective function (CRPS, Eq.
+	The calibration is performed in successive steps with a limited number of parameters in order to minimize the objective function (CRPS, Eq.
 \ref{eq:CRPS}).
-Previously calibrated parameters are generally not reassessed (except for the number of analogues).
-More advanced techniques, such as using genetic algorithms \citep{Horton2017}, exist but are out of the scope of the present study.
+Except for the number of analogues, previously calibrated parameters are generally not reassessed.
+More advanced techniques such as using genetic algorithms \citep{Horton2017} exist but are beyond the scope of the present study.
 
-	The 29-yr hourly precipitation dataset was divided into a calibration period (CP) and a validation period (VP) in order to assess the robustness of the proposed improvements on independent data.
-The selection of the VP was evenly distributed over the entire series \citep{BenDaoud2010} to reduce potential biases related to trends linked to climate change or to the evolution in measurement techniques.
-Thus, one out of every five years was selected for validation, which represents a total of 6~yr for the VP and 23~yr for the CP.
+	The 29-year hourly precipitation dataset was divided into a calibration period (CP) and a validation period (VP) in order to assess the robustness of the proposed improvements on independent data.
+The selection of the VP was evenly distributed over the entire series \citep{BenDaoud2010} to reduce potential biases related to trends linked to climate change or to evolution in the measurement techniques.
+Thus, 1 out of every 5 years was selected for validation, which represents a total of 6 years for the VP and 23 years for the CP.
 
-	The continuous ranked probability score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} is often employed in order to assess the performance of AMs \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}.
-It allows the evaluation of the predicted cumulative distribution functions $F(y)$ of the precipitation values $y$ from analogue situations compared to the observed value $y^{0}$.
-A better prediction has a smaller score.
-It is defined as follows:
+	The continuous ranked probability score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} is often employed in order to assess the performance of AMs \citep[e.g.][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}.
+This allows for evaluation of the predicted cumulative distribution functions $F(y)$ of the precipitation values $y$ from analogue situations compared with the observed value $y^{0}$; a better prediction has a smaller score.
+This score is defined as
 
@@
 	\end{equation}
-	where $\text{H}(y-y^{0})$ is the Heaviside function that is null when $y-y^{0}<0$ and has the value of 1 otherwise.
+	where $\text{H}(y-y^{0})$ is the Heaviside function, which is null when $y-y^{0}<0$ and has the value of 1 otherwise.
 
-	\subsection{The moving time window (MTW) approach}
+	\subsection{The moving time window approach}
 	\label{sec:mtw}
 
-	The moving time window (MTW) technique aims at finding better analogue situations at different hours of the day rather than comparing the predictors at the same fixed hours.
-The target situation (the day to predict) is still the same as in the conventional approach, that is a daily precipitation total between 06:00 and 30:00~UTC, characterized by predictors which are here Z1000 and Z500 at 12:00 and 24:00~UTC respectively.
-The difference is that candidate situations are not only considered at the same time (12:00 and 24:00~UTC), but at other hours by allowing a time shift.
-Therefore, instead of looking for analogues at a 24h time step, they are sought at the time step matching the predictor temporal resolution (Fig.
+	The MTW technique is used to find better analogue situations at different hours of the day rather than comparing the predictors at the same fixed hours.
+The target situation (the day to predict) is still the same as that in the conventional approach: a daily precipitation total between 06:00 and 30:00 UTC characterised by predictors, which in this case are Z1000 and Z500 at 12:00 and 24:00 UTC, respectively.
+The difference is that candidate situations are considered not only at the same time (12:00 and 24:00 UTC), but also at other hours by allowing a time shift.
+Therefore, instead of looking for analogues at a 24-h time step, they are sought at the time step matching the predictor temporal resolution (Fig.
 \ref{fig:principle}).
-The ERA-20C dataset made here possible to test an MTW with a 12h, 6h, or 3h time step (named respectively 12h-MTW, 6h-MTW, 3h-MTW hereafter).
-Thus, the candidates are 2 (12h-MTW), 4 (6h-MTW), or 8 (3h-MTW) times as many (even though they are not fully independent) as in the conventional approach.
+The ERA-20C dataset used here to test an MTW with 12-h, 6-h, or 3-h time steps, which are referred to as 12-h MTW, 6-h MTW, and 3-hr MTW, respectively.
+Thus, the candidates are two (12-h MTW), four (6-h MTW), or eight (3-h MTW) times as many  as in the conventional approach even though they are not fully independent.
 
 	The target situations and their corresponding observed precipitation values do not change.
-We then aim at predicting the exact same time series for the MTW and the conventional approach, so that the performance scores can be directly compared.
+The predictions are established for the exact same time series for the MTW and the conventional approach so that the performance scores can be directly compared.
 In order to assess the benefit of searching for analogue situations at a sub-daily time step for quantitative precipitation prediction, an appropriate precipitation series is required.
-On the basis of hourly time series (Sect.
-\ref{sec:data}), 24h totals were processed at time steps matching the MTW by means of a moving 24h total on the period 1982-2010.
+On the basis of the hourly time series (Sect.
+\ref{sec:data}), 24-h totals were processed at time steps matching the MTW by means of a moving 24-h total on the period 1982--2010.
 
@@
 	The AMs were applied to both ERA-20C and MERRA-2 datasets.
-Most results are presented for the ERA-20C dataset, as it allows testing a 3h-MTW, but would lead to similar conclusions with MERRA-2.
-The impact of an MTW was assessed on two different basis:
+Most of the results are presented for the ERA-20C dataset because it allows for testing a 3-h MTW, although similar conclusions can be found by using MERRA-2.
+The impact of an MTW was assessed on the two bases given below.
 	\begin{itemize}
-		\item Original parameters: The AMs were initially calibrated for each station based on the conventional 24h approach.
+		\item Original parameters: The AMs were initially calibrated for each station based on the conventional 24-h approach.
 Then, the MTW was introduced into the AMs, but the parameters (spatial windows and number of analogues) were not reassessed.
-The analogy was then identical, with the only difference that the MTW had more candidate at disposal.
+The analogy was then identical, except for the fact that the MTW had more candidates at disposal.
 		\item Recalibrated: The parameters of the AMs were reassessed after the introduction of the MTW at different time steps.
@@
 The calibration (Sect.
-\ref{sec:calibration}) was then be reprocessed to adapt the AMs to the new information available through the MTW.
+\ref{sec:calibration}) was then reprocessed to adapt the AMs to the new information available through the MTW.
 The main difference was the increase in the optimal number of analogues, which is discussed in Sect.
@@
 
-	The MTW is expected to have an impact on both the selection of analogue dates and the prediction skill. Both are analyzed separately hereafter.
+	The MTW is expected to affect both the selection of analogue dates and the prediction skill. Both are analysed separately hereafter.
 
@@
 
-	First, the impact of the MTW on the selection of analogue dates was analyzed, independently of any precipitation data.
-This was done on the period 1982-2010, but could have been done on a longer period, as no sub-daily precipitation series is required at this stage.
+	First, the impact of the MTW on the selection of analogue dates was analysed independently of precipitation data.
+This was conducted for the period 1982--2010, although a longer period could have been used because no sub-daily precipitation series is required at this stage.
 The results are presented for the Ulrichen station, but were very similar for all other stations.
-The original parameters were used here when assessing the impact of the MTW, no recalibration of the parameters took place.
+The original parameters were used when assessing the impact of the MTW; no recalibration of the parameters was conducted.
 
@@
 	When searching for analogues in the first level of analogy, such as on the geopotential heights in the 2Z method (Sect.
-\ref{sec:analog_method}), there were up to eight times as many candidates (even though not fully independent) with the MTW than before (Sect.
+\ref{sec:analog_method}), up to eight times as many candidates were provided with the MTW than before even though they are not fully independent (Sect.
 \ref{sec:mtw}).
-Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions, for target dates over the CP, of the analogy criterion (S1) for the $1^{st}$, $15^{th}$, and $30^{th}$ analogue rank, due to introduction of an MTW with a 12h, 6h, or 3h time step.
-The shape of the distributions of the conventional approach and the MTWs were found to be similar, but the values of the analogy criterion were gradually reduced (shifted to the left) with smaller time steps MTWs and were, therefore, better.
-The circulation analogy was here regularly improved with the doubling of the MTW time step.
+Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions, for target dates over the CP, of the analogy criterion (S1) for the $1^{st}$, $15^{th}$, and $30^{th}$ analogue rank due to the introduction of an MTW with a 12-h, 6-h, or 3-h time step.
+The shapes of the distributions of the conventional approach and the MTWs were found to be similar.
+However, the values of the analogy criterion were gradually reduced (shifted to the left) with smaller MTW time steps and were therefore better.
+The circulation analogy was regularly improved with the doubling of the MTW time step.
 For analogues with higher ranks (e.g.
-$15^{th}$ or $30^{th}$), the difference between the two distributions was larger than for the first rank, which means that the improvement increased with the rank of the analogues.
+$15^{th}$ or $30^{th}$), the difference between the two distributions was larger than that for the first rank, which means that the improvement increased with the rank of the analogue.
 
-	The improvements of the analogy with the rank of the analogues are summarized in Fig.
-\ref{fig:changes_S1}, which shows (top) quantiles of the S1 criterion for the conventional method and the MTWs at different time steps, and (bottom) quantiles of the relative reduction (meaning improvement) due to the MTWs.
-This confirms that this improvement is constantly increasing from the first to the last analogue (Fig.
+	The improvements of the analogy with the rank of the analogues are summarised in Fig.
+\ref{fig:changes_S1}, which shows the quantiles of the S1 criterion for the conventional method and the MTWs at different time steps (top) and those of the relative reduction indicating improvement owing to the MTWs (bottom).
+This confirms that the improvement constantly increased from the first to the last analogue (Fig.
 \ref{fig:changes_S1} bottom).
-It can be explained by the accumulation of better analogues in the selection, with new better situations pushing previous analogues to higher ranks.
-One can also see the regularity of the improvements brought by decreasing time steps.
-The introduction of the MTW allows finding better analogue situations in the first level of analogy, resulting in a selection of days with here a better similarity in the atmospheric circulation.
-This improvement is superior for MTWs with a smaller time step.
+This can be explained by the accumulation of better analogues in the selection, whereby the new, better situations push the previous analogues to higher ranks.
+The regularity of the improvements brought by decreasing time steps is also evident.
+The introduction of the MTW enables better analogue situations to be found in the first level of analogy, resulting in the selection of days with better similarity in the atmospheric circulation.
+This improvement was superior for MTWs with a smaller time step.
 
-	The impact of the MTW on the analogy criterion has been analysed per precipitation classes (for the target day) for a 6h-MTW and a 3h-MTW.
+	The impact of the MTW on the analogy criterion has been analysed per precipitation class, for the target day, for 6-h and 3-h MTWs.
 The results are summarised in Fig.
-\ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for the days with precipitation (organized into classes) between two thresholds.
-With the number of cases per class being reduced, the curves are not as smooth as in previous analyses.
-It is nevertheless clear that the improvements were larger for days with higher precipitation, for both the 6h-MTW and the 3h-MTW.
+\ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for the days with precipitation between two thresholds.
+With a reduction in the number of cases per class, the curves were not as smooth as those in the previous analyses.
+It is nevertheless clear that the improvements were larger for days with higher precipitation for both the 6-h and 3-h MTW.
 
-	The effect of the MTW on the S1 criterion has been decomposed per season and is presented in Fig.
+	The effect of the MTW on the S1 criterion was decomposed per season and is presented in Fig.
 \ref{fig:changes_S1_seasons}.
-Differences between the seasons are substantial, with greater improvements for winter than summer.
-An analysis of the selected hours for the geopotential height predictor was then performed for the MTW with different time steps (Fig.
+The differences among the seasons were substantial, with greater improvements shown for winter than summer.
+Analysis of the selected hours for the geopotential height predictor was then performed for the MTW with different time steps (Fig.
 \ref{fig:hours_selection_per_season}).
-It was found that the new choice of the temporal window in winter is more balanced between the different hours of the day (more regular repartition), and this for all MTW time steps.
-This means a change in selection of a greater portion of the analogue dates compared to the conventional approach.
-On the contrary, the days in summer had a preference for the initial temporal window (Z500 24~h \& Z1000 12~h).
-It is likely due to more pronounced diurnal effects, which reduced the potential for improvement of the criteria.
+The new choice of the temporal window in winter was more balanced between the different hours of the day, showing more regular repartition, for all MTW time steps.
+This indicates a change in selection of a greater portion of the analogue dates in this method than that in the conventional approach.
+On the contrary, the days in summer showed a preference for the initial temporal window (Z500, 24 h and Z1000, 12 h).
+This is likely attributed to the more pronounced diurnal effects, which reduced the potential for improvement of the criteria.
 These effects are in phase with the daily cycle, and good analogues were essentially found for the same hours.
-When a 3h-MTW was used, the time step following the initial temporal window (so Z500 27~h \& Z1000 15~h) was almost as often selected as the initial one for all seasons.
-It can be considered as relatively similar in terms of the solar influence.
+When a 3-h MTW was used, the time step following the initial temporal window (Z500, 27 h and Z1000, 15 h) was selected almost as often as the initial values for all seasons.
+This temporal window can be considered as relatively similar in terms of the solar influence.
 The other seasons were between these two extremes, which is consistent with their respective improvements in S1.
@@
 
-	When adding the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations did not increase (when using the original parameters), as they were conditioned by the $N_{1}$ previously selected analogues, but their dates had changed.
-In contrast to the AM on the atmospheric circulation only, both a reduction or an increase of the RMSE analogy criterion values were possible with the MTW compared to the static approach.
-The results of the second level of analogy are presented in Fig.
-\ref{fig:changes_RMSE}, and show no improvement of the RMSE values, whatever the MTW time step.
-Unlike the first level of analogy, the relative changes of the RMSE values were distributed relatively symmetrically around zero.
+	When adding the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations did not increase when using the original parameters because they were conditioned by the $N_{1}$ previously selected analogues; however, their dates changed.
+In contrast to the AM on the atmospheric circulation only, both a reduction and an increase in the RMSE analogy criterion values were possible with the MTW compared with the static approach.
+The results of the second level of analogy, presented in Fig.
+\ref{fig:changes_RMSE}, showed no improvement in RMSE values regardless of the MTW time step.
+Unlike the first level of analogy, the relative changes in the RMSE values were distributed relatively symmetrically around zero.
 
-	These criterion values were not improved by the MTW because the number of candidates was not higher (still the $N_{1}$ days selected in the first level of analogy).
-The use of an MTW did not increase the sample size in this case, as the second level of analogy only subsamples in the dates provided by the first level.
-However, this result of a globally null improvement of the RMSE values does not mean that the 2Z-2MI method cannot be improved by the MTW.
-It means that after the selection of the analogue dates for the synoptic circulation, the new candidate dates did not provide better analogues in terms of moisture.
-However, the selected dates have changed in the first level of analogy and also in the final selection, and thus the distributions of precipitation values were different, which can have an impact on the performance of the precipitation prediction.
+	These criterion values were not improved by the MTW because the number of candidates ($N_{1}$) was not higher.
+The use of an MTW did not increase the sample size in this case because the second level of analogy consists in subsampling in the dates provided by the first level.
+However, this result of a globally null improvement in the RMSE values does not mean that the 2Z-2MI method cannot be improved by the MTW.
+After selection of the analogue dates for the synoptic circulation, the new candidate dates did not provide better analogues in terms of moisture.
+However, the selected dates changed in the first level of analogy and in the final selection; thus, the distributions of precipitation values were different, which can impact the performance of the precipitation prediction.
 
@@
 \ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI} for the 2Z and 2Z-2MI methods, respectively.
-The AMs were here recalibrated on the CP, and assessed on the independent VP.
+The AMs were recalibrated on the CP and were assessed on the independent VP.
 The score was processed for each station and both reanalysis datasets.
-For ERA-20C, the 12h-MTW, 6h-MTW, and 3h-MTW could be assessed, while only the two first could be processed with the MERRA-2 dataset.
+For ERA-20C, the 12-h MTW, 6-h MTW, and 3-h MTW could be assessed, whereas only the two first could be processed with the MERRA-2 dataset.
 
-	The MTW improved the precipitation prediction, as the CRPS globally decreased for all stations, both on the CP and the VP.
-The VP showed a greater variability, likely related to the short period it represents (6 yr).
-The prediction skill on the CP was almost always improved further by reducing the time step of the MTW, but not of the same magnitude.
-For ERA-20C, the magnitude of the improvement of 2Z on the CP was relatively reduced when using a 3h-MTW instead of a 6h-MTW, and the variablility on the VP increased.
-However, as it was shown in Fig.
+	The MTW improved the precipitation prediction because the CRPS globally decreased for all stations, both for the CP and the VP.
+The VP showed greater variability, which is likely related to its short period of six years.
+The prediction skill for the CP was almost always improved further by reducing the time step of the MTW, but not at the same magnitude.
+For ERA-20C, the magnitude of the improvement of 2Z for the CP was relatively reduced when using a 3-h MTW instead of a 6-h MTW, and the variability for the VP increased.
+However, as shown in Fig.
 \ref{fig:changes_S1}, the selection of analogue dates was improved relatively equally for every reduction of the MTW time step.
-A possible reason could be that the ERA-20C dataset was build by only assimilating surface observations, while the AMs rely on the geopotential at 500~hPa.
-Thus, the timing of the atmospheric circulation at higher pressure levels might not be completely in phase with the real perturbation systems that caused the observed precipitations.
-The MTW with the MERRA-2 dataset and the 2Z method also showed a certain slope break after the 12h-MTW, that could not be explained, and that is less important for the 2Z-2MI method.
-However, the 12h-MTW resulted in important variability for the 2Z-2MI method and the MERRA-2 dataset.
+A possible reason is that the ERA-20C dataset was built by assimilating only surface observations, whereas the AMs rely on the geopotential height at 500 hPa.
+Thus, the timing of the atmospheric circulation at higher pressure levels might not be completely in phase with the actual perturbation systems which caused the observed precipitations.
+The MTW with the MERRA-2 dataset and the 2Z method also showed a certain slope break after the 12-h MTW that could not be explained and was less important for the 2Z-2MI method.
+However, the 12-h MTW resulted in important variability for the 2Z-2MI method and the MERRA-2 dataset.
 
@@
 \ref{sec:changes_analogy_circul}).
-The impact of the MTW was then assessed in terms of change of prediction performance per precipitation classes (for the target day).
-Figure \ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, using the original parameters with the MTW.
-It shows that, after the introduction of the MTW, the performance score was in average further improved (reduced CRPS) for days with higher precipitation than for non-rainy days and small precipitation values.
-When recalibrating the parameters using the MTW, the spread of the changes in CRPS tended to decrease, but with a slight loss in performance for the most rainy days (not shown).
+The impact of the MTW was then assessed in terms of changes in prediction performance per precipitation class for the target day.
+Figure \ref{fig:changes_CRPS_precip_threshold} synthesises these differences for the Ulrichen station by using the original parameters with the MTW.
+After the introduction of the MTW, the performance score was generally further improved with reduced CRPS for days with higher precipitation than for non-rainy days and small precipitation values.
+When recalibrating the parameters using the MTW, the spread of the changes in CRPS tended to decrease, although a slight loss in performance was noted for the most rainy days (not shown).
 
-	Reliability diagrams were also performed on the VP for both the 2Z and 2Z-2MI methods and for the exceedence of percentiles 80~\% (P80 -- 4~mm), 90~\% (P90 -- 9.5~mm), and 95~\% (P95 -- 17.5~mm) at the Ulrichen station (Fig.
+	Reliability diagrams were also created for the VP for both 2Z and 2Z-2MI methods and for the exceedance of percentiles 80~\% (P80, 4 mm), 90~\% (P90, 9.5 mm), and 95~\% (P95, 17.5 mm) at the Ulrichen station (Fig.
 \ref{fig:reliability_diagrams}).
-Reliability diagrams plot the observed frequency against the predicted probability of a binary event -- a threshold exceedence in this case.
+These diagrams plot the observed frequency against the predicted probability of a binary event, which in this case is threshold exceedance.
 For perfectly calibrated predictions, the curve should be as close as possible to the diagonal.
-The VP only contains six years (Sect.
-\ref{sec:data_methods}), and thus higher variability is present for higher thresholds, the curves being smoother and closer to the diagonals for the CP, which is longer (not shown).
-Figure \ref{fig:reliability_diagrams} shows that the MTW improved the reliability for both 2Z and 2Z-2MI methods and for all thresholds, as the curves moved toward the diagonal with a decreasing MTW time step.
-For P80, the 3h-MTW predictions fited very well the observed frequency.
-When considering higher thresholds, the 2Z-2MI method is generally better than 2Z.
-The case of a P95 threshold shows a conditional dry bias associated with larger forecast probabilities for the considered AMs, which was however substantially reduced by the 3h-MTW.
-This conditional dry bias means for example here that the AM did not predict the event with a probability equal to 1 for 2Z.
-Obtaining a predicted probability of exceedence of 1 would mean that all analogue dates for a certain target date would be above the threshold.
-As the number of analogue dates is 30 in this case, it becomes less likely to have 30 values above the threshold when it increases.
-This issue is the topic of an ongoing work.
-However, as one can see in Figure \ref{fig:reliability_diagrams} (bottom), the introduction of an MTW, especially with a 3h timse step, improves partly this missmatch.
+The VP contains only six years (Sect.
+\ref{sec:data_methods}); therefore, higher variability is present for higher thresholds, and the curves are smoother and closer to the diagonals for the CP, which is longer (not shown).
+Figure \ref{fig:reliability_diagrams} shows that the MTW improved the reliability for both 2Z and 2Z-2MI methods and for all thresholds because the curves moved towards the diagonal with decreasing MTW time steps.
+For P80, the 3-h MTW predictions fit very well the observed frequency.
+When considering higher thresholds, the 2Z-2MI method was generally better than 2Z.
+The case of the P95 threshold showed a conditional dry bias associated with larger forecast probabilities for the considered AMs; however, this was substantially reduced by the 3-h MTW.
+This conditional dry bias means that the AM did not predict the event with a probability equal to 1 for 2Z.
+Obtaining a predicted probability of exceedance of 1 would mean that all analogue dates for a certain target date would be above the threshold.
+The number of analogue dates being 30 in this case, it is less likely to have 30 values above the threshold when this one increases.
+This issue is the topic of ongoing research.
+However, as shown in Figure \ref{fig:reliability_diagrams}, the introduction of an MTW, especially with a 3-h time step, improves this mismatch to some degree.
 
@@
 
-	\subsection{A better prediction of heavy precipitation}
+	\subsection{Better prediction of heavy precipitation}
 
@@
 \ref{sec:influence_scores}) were improved to a greater extent for days with heavier precipitation.
-This is likely due to the fact that higher precipitation events are a consequence of atmospheric conditions with greater dynamics, such as weather disturbances, which have a well-marked temporal evolution.
-Indeed, the position of the driving elements, such as the low pressure centres and the fronts, change significantly during a day.
+This is likely attributed to the fact that higher precipitation events are a consequence of atmospheric conditions with greater dynamics such as weather disturbances, which have well-marked temporal evolution.
+Indeed, the position of the driving elements, such as the low-pressure centres and the fronts, change significantly during the course of a day.
 These situations are less numerous than anticyclonic situations, which makes it less likely to find very good analogues at the same time of the day.
-We can, therefore, expect to improve these situations with greater dynamics more significantly when introducing an MTW, as better matches to the target situation may be found.
-In contrast, days with low dynamics in the atmospheric circulation, such as anticyclonic situations, will not be radically improved by the introduction of the MTW.
+We can, therefore, expect to more significantly improve these situations with greater dynamics when introducing an MTW because better matches to the target situation may be found.
+In contrast, days with low dynamics in atmospheric circulation, such as anticyclonic situations, will not be radically improved by the introduction of the MTW.
 
-	The MTW improved the prediction for days with heavier precipitation, and should improve the prediction of extremes due to better analogue situations, but also due to possible new extreme values resulting from 24h totals with a certain time shift.
-However, even though the distribution of analogue precipitation values should move towards the targeted extreme, providing a better prediction, the MTW itself does not allow to predict extreme events that were not yet observed and are, therefore, not present in the archive.
-The extremes in AMs can be modelled by, for example, extrapolation of a truncated exponential or gamma distribution fitted to the analogue values \citep{Obled2002}.
-Another possible approach is by combining AMs with other methods \citep[e.g.][]{Chardon2014}.
-From this perspective, the MTW might improve the prediction of extremes as it improves the distribution of precipitation values for days with higher precipitation, on which post-treatment techniques rely.
-However, this goes beyond the scope of the present study.
+	The MTW improved the prediction for days with heavier precipitation.
+Therefore, it should improve the prediction of extremes owing to better analogue situations and to possible new extreme values resulting from 24 h totals with a certain time shift.
+However, even though the distribution of analogue precipitation values should move towards the targeted extreme to provide better prediction, the MTW itself does not enable prediction of extreme events that were not yet observed and are therefore not present in the archive.
+The extremes in AMs can be modelled by extrapolation of a truncated exponential or gamma distribution fitted to the analogue values \citep{Obled2002}.
+Another possible approach is to combine AMs with other methods \citep[e.g.][]{Chardon2014}.
+From this perspective, the MTW might improve the prediction of extremes because it improves the distribution of precipitation values for days with higher precipitation, on which post-treatment techniques rely.
+However, this topic is beyond the scope of the present study.
 
@@
 	When recalibrating the AMs with MTWs of different time steps, the optimal number of analogues changed for both 2Z and 2Z-2MI methods.
-$N_{1}$ and $N_{2}$, from the first and the second level of analogy, tend to significantly increase with the reduction of the time step of the MTW (Fig.
+$N_{1}$ and $N_{2}$, from the first and the second level of analogy, tended to significantly increase with a reduced MTW time step (Fig.
 \ref{fig:analog_nb}).
-When using ERA-20C, all optimal numbers of analogues (for the different analogy levels) tend in average to double when using a 6h-MTW instead of the classic approach, and to even triple when using a 3h-MTW.
-These higher numbers of analogues were objectively chosen by the calibration procedure (Sect.
+When using ERA-20C, all optimal numbers of analogues for the different analogy levels tended to double when using a 6-h MTW instead of the classic approach and to even triple when using a 3-h MTW.
+These higher numbers of analogues were objectively chosen by using the calibration procedure (Sect.
 \ref{sec:calibration}) in order to increase the prediction skill of the methods.
@@
 	As shown in Fig.
-\ref{fig:changes_S1}, the improvement of the S1 criterion grows along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions.
-It seems profitable to widen the selection of analogues in order to also keep some whose rank has increased, as they appear to be relevant to the prediction of the precipitation values.
-The number of good analogues was globally increased.
+\ref{fig:changes_S1}, the improvement of the S1 criterion increases along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions.
+Widening the selection of analogues appears to be beneficial for keeping some with increased rank because they appear to be relevant in predicting the precipitation values.
+Thus, the number of good analogues was globally increased.
 
-	A higher number of analogues generally means, with an archive of fixed length, a poorer analogy.
-Indeed, when the choice of the predictors or the parameters are improved, leading to a better prediction, the optimal number of analogue situations decreases.
-However, when the length of the archive increases, the optimal number of analogues increases too for a better performance up to a certain threshold \citep[][]{Bontron2004, Hamill2006a}.
-The observed increase in the number of analogue situations with the MTW resulted in better performance skills for the given methods, as it can be seen as an inflation of the archive.
+	A higher number of analogues generally implies a poorer analogy with an archive of fixed length.
+Indeed, when the choice of the predictors or the parameters improve, leading to a better prediction, the optimal number of analogue situations decreases.
+However, when the length of the archive increases, the optimal number of analogues also increases for better performance up to a certain threshold \citep[][]{Bontron2004, Hamill2006a}.
+The observed increase in the number of analogue situations with the MTW resulted in better performance skills for the given methods because it can be considered as an inflation of the archive.
 However, if new relevant predictors were added to the method, the number of analogues would then decrease again.
@@
 
-	Since sub-daily precipitation time series are often available on a shorter period than daily ones, this implies a reduction of the archive length at disposal for the search of analogue situations.
+	Because sub-daily precipitation time series are often available on a shorter period than daily, a reduction of the archive length at disposal is necessary.
 This usually has a negative consequence on the skill of precipitation prediction.
-The role of the archive length has been assessed on the ERA-20C dataset and is presented in Fig.
-\ref{fig:plots_archive_length} for both 2Z and 2Z-2MI methods, using the conventional approach (24h windows).
+The role of the archive length was assessed on the ERA-20C dataset and is presented in Fig.
+\ref{fig:plots_archive_length} for both 2Z and 2Z-2MI methods using the conventional approach of 24-h windows.
 As expected, the performance of the method globally increased with the length of the archive.
-The best performances were found with a 44~yr archive, corresponding to the period 1961--2010, minus the 6 years of independant VP.
-This addition of 21~yr of archive to the original 23~yr resulted in an improvement of both 2Z and 2Z-2MI methods that was of the same order of magnitude as the introduction of a 6h-MTW (Fig.
+The best performances were found with a 44-year archive, which corresponds to the period 1961--2010 minus the 6 years of independent VP.
+This addition of 21 years of archive to the original 23 years resulted in an improvement of both 2Z and 2Z-2MI methods that was of the same order of magnitude as the introduction of a 6-h MTW (Fig.
 \ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI}).
-The 3h-MTW resulted in similar performance for the 2Z method and slightly superior improvements for the 2Z-2MI method.
+The 3-h MTW resulted in similar performance for the 2Z method and slightly superior improvements for the 2Z-2MI method.
 
-	As the MTW provides additional situations to the pool of possible analogues, it can be seen as an inflation of the archive.
-With the introduction of the MTW, the performance loss related to an eventual reduction of the archive length (to meet the length of the subdaily precipitation archive) was compensated.
-A 6h-MTW brought gains of the same magnitude as if the length of the archive almost doubled.
-Note, that despite the number of candidate situations being in this case 4 times as many, the gains seem to be lower than for a quadrupled archive length.
+	As previously stated, the MTW can be considered as an inflation of the archive because it provides additional situations to the pool of possible analogues.
+With the introduction of the MTW, the performance loss related to an eventual reduction of the archive length to meet the length of the sub-daily precipitation archive was compensated.
+A 6-h MTW brought gains of the same magnitude similar to an almost double archive length.
+However, it should be noted that despite the number of candidate situations, which in this case is four times the original number, the gains appear to be lower than those for a quadrupled archive length.
 The likely reason is that an actual longer archive would contain more atmospheric situations that might have been observed less frequently during a shorter period.
@@
 
-	Many reanalysis datasets start in the 80s due to availability of satellite data, and are thus more accurate than reanalysis datasets based on conventional data only, but they provide shorter archives.
-When using such an archive, the MTW approach shows a certain potential to enrich the pool of possible analogues.
-Moreover, in a transient climate, an eventual nonstationarity of the link between predictors and precipitation might discard the relevance of analogues from the distant past and increase the relevance of using a more recent and shorter archive rather than a long one.
+	Many reanalysis datasets begin in the 80s owing to availability of satellite data and are thus more accurate than reanalysis datasets based on conventional data only; however, they provide shorter archives.
+When using such an archive, the MTW approach shows a certain potential for enriching the pool of possible analogues.
+Moreover, in a transient climate, the eventual nonstationarity of the link between predictors and precipitation might discard the relevance of analogues from the distant past and can increase the relevance of using a more recent and shorter archive rather than a long one.
 In such cases, the archive inflation brought by the MTW is also relevant.
@@
 
-	As we saw in Sect.
+	As discussed in Sect.
 \ref{sec:archive_reduction}, the skills of AMs improved with the length of the archive.
-It would then be even more profitable to apply the MTW to the longest archive possible, rather than being limited to the period where sub-daily precipitation data are available.
-Therefore, in order to reconstruct longer archives of moving 24h totals, disaggregation techniques might be used.
-Here, two simple disaggregation approaches of the daily precipitation time series were assessed.
+It would then be even more profitable to apply the MTW to the longest archive possible rather than being limited to the period in which sub-daily precipitation data are available.
+Therefore, in order to reconstruct longer archives of moving 24-h totals, disaggregation techniques can be used.
+In this study, two simple disaggregation approaches of the daily precipitation time series were assessed.
 
-	The first technique was a proportional distribution, where the observed daily precipitations were considered constant during the measuring period (6:00~UTC to 6:00~UTC the next day).
-Proportional parts of the original daily time series were allocated into a new moving average of 24h totals.
+	The first technique is a proportional distribution in which the observed daily precipitations were considered to be constant during the measurement period of 06:00 UTC to 06:00 UTC the following day.
+The proportional parts of the original daily time series were allocated into a new moving average of 24 h totals.
 
-	The second approach aimed at getting closer to the chronology of the actual precipitation by relying on some informative proxy variables during the reconstruction procedure.
-Data from the NCEP/NCAR reanalysis 1 were used for this purpose.
-Precipitable water and relative humidity (at 1000~hPa, 925~hPa or 850~hPa) were assessed at the four points surrounding the catchment.
-Precipitation time series from the reanalysis were not considered due to the presence of zeros, which may not always match with the prediction, leading to an undefined temporal repartition.
-A time lapse (-12h to +12h) between both series was allowed to take into account the significant distance separating the weather stations and the reanalysis grid point.
-The best proxy variable, which was precipitable water, was identified by means of a correlation analyses (on non-zero values) with the 6-hourly precipitation time series.
-Once the best proxy had been selected, its temporal profile was used in order to disaggregate the daily precipitation time series.
+	The second approach was used to obtain data that are closer to the chronology of the actual precipitation by relying on informative proxy variables during the reconstruction procedure.
+Data from NCEP/NCAR reanalysis 1 were used for this purpose.
+Precipitable water and relative humidity at 1000 hPa, 925 hPa, or 850 hPa were assessed at the four points surrounding the catchment.
+Precipitation time series from the reanalysis were not considered due to the presence of zeros, which may not always match the prediction; this can lead to an undefined temporal repartition.
+Time lapses from -12 h to +12 h between both series were introduced to consider the significant distance separating the weather stations and the reanalysis grid point.
+The best proxy variable, precipitable water, was identified through correlation analyses on non-zero values with the 6-h precipitation time series.
+When the best proxy was selected, its temporal profile was used to disaggregate the daily precipitation time series.
 
@@
 Indeed, the performance improvement brought by the MTW was lost due to the poor quality of the precipitation archives.
-A slight improvement could be obtained for the second method relying on a proxy variable compared to the proportional distribution method, but it was still relatively small, and most of the benefit of the MTW was lost.
-Another reanalysis dataset with more accurate moisture variables might produce better proxies.
+A slight improvement was obtained for the second method which relied on a proxy variable rather than the proportional distribution method.
+However, this  improvement was relatively small, and most of the benefit of the MTW was lost.
+Another reanalysis dataset with more accurate moisture variables could produce better proxies.
 
-	These attempts to transpose the MTW on the total archive highlighted the importance of the actual rainfall chronology.
-The MTW is beneficial, provided that the precipitation series are close to the observed one.
-Without a precipitation series with an accurate sub-daily chronology, the introduction of an MTW does not improve the precipitation prediction.
+	These attempts to transpose the MTW on the total archive highlight the importance of the actual rainfall chronology.
+The MTW is beneficial if the precipitation series are close to the observed values.
+In the absence of a precipitation series with accurate sub-daily chronology, the introduction of an MTW does not improve the precipitation prediction.
 
@@
 
-	The AMs are most often based on a daily time step due to the availability of long precipitation archives.
-However, it is unlikely that two analogue synoptic situations, that evolve relatively quickly, would correspond optimally at the same hours of the day.
-It is probable that better matches may be found at another hour, which can change the selection of the analogue dates.
+	The AMs are most often based on a daily time step owing to the availability of long precipitation archives.
+However, it is unlikely that two analogue synoptic situations which evolve relatively quickly would correspond optimally at the same hours of the day.
+It is probable that better matches may be found at a different hour, which can change the selection of the analogue dates.
 
-	As \citet{Finet2008} had previously shown, the introduction of an MTW allows finding better analogue situations in terms of the atmospheric circulation.
-Using recent reanalysis datasets, MTWs with 12h, 6h, and 3h time steps were assessed.
-It has been demonstrated here that the improvement of the S1 criterion values was growing with the rank of the analogue.
-This was due to the accumulation of better analogues within the predicted distributions.
-The improvement of the S1 criterion increased for smaller MTW time steps.
+	As shown in previous research \citep{Finet2008}, the introduction of an MTW enables better analogue situations in terms of atmospheric circulation to be obtained.
+Using recent reanalysis datasets, MTWs with 12-h, 6-h, and 3-h time steps were assessed in the present study.
+Improvement in the S1 criterion values increased with the rank of the analogue owing to the accumulation of better analogues within the predicted distributions.
+Moreover, the improvement in the S1 criterion increased further for smaller MTW time steps.
 
-	A seasonal effect has been highlighted, as the MTW was more profitable for winter than summer.
-The reason is likely that the diurnal cycle has a bigger effect in summer than in winter which results in better analogues at the same time of the day.
-The preference for the same hours in summer has been demonstrated; whereas, a large part of the analogue situations were selected at a different time in winter.
+	A seasonal effect was highlighted such that the MTW was more profitable for winter than for summer.
+A likely reason is that the diurnal cycle has a greater effect in summer than in winter, which results in better analogues at the same time of the day.
+The preference for the same hours in summer has been demonstrated, whereas a large part of the analogue situations were selected at a different time in winter.
 
-	The MTW improved the precipitation prediction, as the CRPS globally decreased for all stations, both on the CP and the VP.
-The prediction skill on the CP was almost always improved further by reducing the time step of the MTW, but not of the same magnitude.
-Results on the VP showed globally the same trends, but with more variability.
-It was also shown that the reliability of the considered AMs improved for the prediction of different threshold exceedences, especially with a 3h-MTW.
+	The MTW improved the precipitation prediction, with the CRPS showing a global decrease for all stations for both the CP and VP.
+The prediction skill for the CP was almost always improved further by reducing the time step of the MTW, but the magnitude differed.
+The results for the VP showed the same global trends but had more variability.
+Moreover, the reliability of the considered AMs improved for the prediction of different threshold exceedances, especially with a 3-h MTW.
 
-	Both improvements of the analogy criterion and the performance scores were found to be higher for MTWs with a smaller time step (3h).
-A 3h-MTW provides 8 times more candidate situations, even though not fully independent.
-As the MTW provides additional situations to the pool of possible analogues, it can be seen as an inflation of the archive.
+	Improvements of the analogy criterion and the performance scores were both found to be higher for MTWs with a smaller time step of 3 h.
+A 3-h MTW provided eight times more candidate situations, although they were not fully independent.
+Because the MTW provides additional situations to the pool of possible analogues, it can be considered as an inflation of the archive.
 
-	The improvement of the circulation analogy and the change in performance of the precipitation prediction was found to be more important for days with heavier precipitation.
-These are generally related to more dynamic atmospheric situations and are less frequent in the archive.
+	The improvement in the circulation analogy and the change in performance of the precipitation prediction was found to be more important for days with heavier precipitation.
+These days are generally related to more dynamic atmospheric situations and are less frequent in the archive.
 These situations have more specific circulation patterns that are evolving more rapidly.
-Therefore, an MTW was found to be of particular interest in this kind of situation, benefiting the prediction of heavier precipitation events.
+Therefore, an MTW was found to be of particular interest in this type of situation and is beneficial for the prediction of heavier precipitation events.
 
-	The importance of the quality of the precipitation archive was also demonstrated, as simplistic reconstructions of subdaily time series led to a loss of all the improvement brought by the MTW.
-The precipitation prediction is improved only when the precipitation chronology is close to the accurate one.
-Attempts to reconstruct longer time series based on simplistic proportional distributions or by using meteorological variables from the NCEP reanalysis 1 dataset as proxy did not succeed.
-Other reanalysis datasets with more accurate moisture variables could eventually perform better.
+	The importance of the quality of the precipitation archive was also demonstrated because simplistic reconstructions of sub-daily time series led to a loss of all the improvement brought by the MTW.
+The precipitation prediction improved only when the precipitation chronology was close to the accurate values.
+Attempts to reconstruct longer time series based on simplistic proportional distributions or by using meteorological variables from the NCEP reanalysis 1 dataset as a proxy were not successful.
+Other reanalysis datasets with more accurate moisture variables could show better performance.
 
 	The use of the MTW relies partly on the availability of long precipitation series at a sub-daily time step and with high accuracy.
-First, these archives of high temporal resolution precipitation data are increasing over time.
-Another possible source of such archives is the establishment of precipitation reanalysis at a regional scale or the use of reanalysis-driven regional climate models or limited area models over a long period.
+The precipitation data archives of high temporal resolution have increased over time.
+Other possible sources of such archives is the establishment of precipitation reanalysis at a regional scale in addition to the use of reanalysis-driven regional climate models or limited area models over a long period.
 Even though outputs from these models might be biased or not accurate enough, information regarding the timing of the precipitation events could be useful in disaggregating the station time series.
@@
 	The introduction of the MTW improved the selection of synoptic analogues.
-Independently of its impact on the prediction skill for precipitation, or the availability of a predictand time series with sub-daily time step, this improvement has a potential in itself for application on long meteorological archives.
-For example, when processing forecasts for a target day showing synoptic similarity with known situations from the past related to extreme weather, even if for them no precipitation archive is available.
-It is thus worth to known that the situation at hand has had such analogue in the past.
-Another possible application is a quality assessment of the selection of analogues on a shorter period, where sub-daily precipitation data is available.
-Indeed, if the selection of analogues with the MTW on a long period, for a specific target day, differ from the selection on the short period, this may point out a sub-optimal forecast.
-Finally, other predictands might not need sub-daily total values, but point observations (e.g.
-hail, or extreme wind gusts), which make them easier to use with the MTW.
+Regardless of its impact on the prediction skill for precipitation or the availability of a predictand time series with a sub-daily time step, this improvement has the potential for application to long meteorological archives.
+For example, when processing forecasts for a target day showing synoptic similarity with known situations from the past related to extreme weather, it can be used even if no precipitation archive is available.
+Thus, it is worth knowing whether the situation at hand had such an analogue in the past.
+Another possible application is quality assessment of the selection of analogues on a shorter period, where sub-daily precipitation data are available.
+Indeed, if the selection of analogues with the MTW on a long period for a specific target day differs from the selection for the shorter period, a sub-optimal forecast could be identified.
+Finally, some other predictands might not need sub-daily total values but point observations such as hail or extreme wind gusts, which make them easier to use with the MTW.
 
-	The technique being very simple and easily applicable, it should be considered for several applications in different contexts, may it be for operational forecasting or climate-related studies.
+	The technique is very simple and easily applicable. Therefore, it should be considered for several applications in different contexts, such as operational forecasting or climate-related studies.
 
@@
 	\begin{labeling}{2Z-2MI}
-		\item [2Z] Name of the analogue method of the atmospheric circulation
-		\item [2Z-2MI] Name of the analogue method composed of a first level on the atmospheric circulation and a second level on a moisture index
+		\item [2Z] Name of the analogue method of atmospheric circulation
+		\item [2Z-2MI] Name of the analogue method composed of a first level on atmospheric circulation and a second level on a moisture index
 		\item [AM] Analogue method
@@
 		\item [RH850] Relative humidity at 850 hPa
-		\item [RMSE] Root-mean-square error
+		\item [RMSE] Root--mean--square error
 		\item [S1] Teweles and Wobus (1954) score
@@
 	\begin{acknowledgements}
-		We thank the Swiss Federal Office for Environment (FOEV), the Roads and Water Courses Service, Energy and Water Power Service of the Wallis Canton, and the Water, Land, and Sanitation Service of the Vaud Canton which financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project that started this research.
-Thanks to Dominique B\'{e}rod for his support.
+		The authors thank the Swiss Federal Office for Environment (FOEV), the Roads and Water Courses Service, Energy and Water Power Service of the Wallis Canton, and the Water, Land, and Sanitation Service of the Vaud Canton which financed the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me des Rivi\`{e}res Valaisannes et de leurs Effets) project which started this research.
+Thanks are also extended to Dominique B\'{e}rod for his support.
 
-		The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible thanks to the Herbette Foundation.
+		The fruitful collaboration with the Laboratoire d'Etude des Transferts en Hydrologie et Environnement of the Grenoble Institute of Technology (G-INP) was made possible by the Herbette Foundation.
 
-		NCEP reanalysis data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, from their Web site at http://www.esrl.noaa.gov/psd/. Precipitation time series provided by MeteoSwiss.
+		NCEP reanalysis data were obtained from the Web site of the NOAA/OAR/ESRL PSD, Boulder, Colorado, USA, at http://www.esrl.noaa.gov/psd/. Precipitation time series were provided by MeteoSwiss.
 
-		The authors would also like to acknowledge the work of anonymous reviewers that contributed to improving this manuscript. 
+		The authors would also like to acknowledge the work of anonymous reviewers who contributed to improving this manuscript. 
 	\end{acknowledgements}
@@
 		\caption{Illustration of the principle of a moving time window (MTW).
-The target situation is the same for the conventional approach and the MTW, while the candidate situations are 2, 4, or 8 times as many with the MTW.
-The horizontal bars represent the 24h precipitation totals, with their associated predictors being listed on the right hand side.}
+The target situation is the same for the conventional approach and the MTW, although the candidate situations with the MTW are two, four, or eight times as many.
+The horizontal bars represent the 24h precipitation totals; their associated predictors are listed on the right-hand side.}
 		\label{fig:principle}
@@
 		\end{center}
-		\caption{Changes in the S1 criterion distributions due to the introduction of an MTW with a 12h, 6h or 3h time step.
+		\caption{Changes in S1 criterion distributions owing to the introduction of an MTW with a 12-h, 6-h, or 3-h time step.
 Distributions are provided for (a) the $1^{st}$, (b) $15^{th}$, and (c) $30^{th}$ analogue ranks for all days of the CP at the Ulrichen station.}
@@
 		\end{center}
-		\caption{Synthesis of the changes in the S1 criterion due to the MTW (with a 12h, 6h, and 3h time step) for the Ulrichen station depending on the rank of the analogue.
-(a) Quantiles of the S1 distributions corresponding to the MTW with different time steps (24h is the conventional approach without MTW).
-(b) Quantiles of the relative improvements of the S1 criterion when using the MTW, compared to the conventional approach.}
+		\caption{Synthesis of the changes in the S1 criterion owing to the MTW with 12-h, 6-h, and 3-h time steps for the Ulrichen station depending on the rank of the analogue.
+(a) Quantiles of the S1 distributions corresponding to the MTW with different time steps; 24-h is the conventional approach without MTW.
+(b) Quantiles of the relative improvements of the S1 criterion when using the MTW compared with the conventional approach.}
 		\label{fig:changes_S1}
@@
 		\end{center}
-		\caption{Distribution of the median improvements of the S1 criterion due to the (a) 3h-MTW and (b) 6h-MTW, depending on daily precipitation thresholds at the Ulrichen station.}
+		\caption{Distribution of the median improvements of the S1 criterion owing to the (a) 3-h MTW and (b) 6-h MTW, depending the on daily precipitation thresholds at the Ulrichen station.}
 		\label{fig:changes_S1_precip_threshold}
@@
 		\end{center}
-		\caption{Seasonal effect on the median reduction of the S1 criterion for the Ulrichen station due to the MTW. DJF: winter, MAM: spring, JJA: summer, and SON: fall.}
+		\caption{Seasonal effect on the median reduction of the S1 criterion for the Ulrichen station owing to the MTW. DJF: winter; MAM: spring; JJA: summer; SON: fall.}
 		\label{fig:changes_S1_seasons}
@@
 		\includegraphics[width=7.5cm]{fig07.pdf}
-		\caption{Distribution of the predictor hours on the selected analogue dates for the Ulrichen station when using a (a) 12h-MTW, (b) 6h-MTW, and (c) 3h-MTW, depending on the season.}
+		\caption{Distribution of the predictor hours on the selected analogue dates for the Ulrichen station when using a (a) 12-h MTW, (b) 6-h MTW, and (c) 3-h MTW, depending on the season.}
 		\label{fig:hours_selection_per_season}
@@
 		\end{center}
-		\caption{Synthesis of the changes in the RMSE criterion due to the MTW for the Ulrichen station depending on the rank of the analogue.
+		\caption{Synthesis of the changes in the RMSE criterion owing to the MTW for the Ulrichen station, depending on the rank of the analogue.
 (a) Quantiles of the RMSE distributions with and without the MTW.
@@
 		\includegraphics[width=8.3cm]{fig09.pdf}
-		\caption{Change in performance score (CRPS -- lower is better) of the 2Z method at the different stations for MTW of varying time steps relatively to the conventional approach (24h).
-Results are provided for ERA-20C on (a) the CP and (b) the VP, as well as for MERRA-2 on (c) the CP and (d) the VP.}
+		\caption{Changes in performance score (CRPS) of the 2Z method at the different stations for MTW of varying time steps relative to the conventional approach of 24 h.
+Results are provided for ERA-20C for the (a) CP and (b) VP as well as for MERRA-2 for the (c) CP and (d) VP.
+Lower CRPS values indicate better performance.}
 		\label{fig:plots_CRPS_2Z}
@@
 		\includegraphics[width=8.3cm]{fig10.pdf}
-		\caption{Same as Figure \ref{fig:plots_CRPS_2Z}, but for the 2Z-2MI method.}
+		\caption{Same as Figure \ref{fig:plots_CRPS_2Z} but for the 2Z-2MI method.}
 		\label{fig:plots_CRPS_2Z-2MI}
@@
 		\includegraphics[width=8.3cm]{fig11.pdf}
-		\caption{Differences of the CRPS performance score (lower is better) at the Ulrichen station due to the introduction of the MTW as a function of different daily precipitation thresholds (for the target date).
-The results are provided for (top) the 2Z method and (bottom) the 2Z-2MI method, and with a (left) 6h-MTW and a (right) 3h-MTW.
-The stars represent averages.}
+		\caption{Differences in the CRPS values at the Ulrichen station owing to the introduction of the MTW as a function of different daily precipitation thresholds for the target date.
+The results are provided for the 2Z method (top) and the 2Z-2MI method (bottom) with a 6-h MTW (left) and a 3-h MTW (right).
+Stars represent averages.
+Lower CRPS values indicate better improvements.}
 		\label{fig:changes_CRPS_precip_threshold}
@@
 		\end{center}
-		\caption{Reliability diagrams for (left) the 2Z (right) the 2Z-2MI methods and the prediction of the exceedence of percentiles (top) 80~\%, (middle) 90~\%, and (bottom) 95~\% at the Ulrichen station on the VP.
-The conventional approach (24h) is provided as well as the 12h-MTW, 6h-MTW and 3h-MTW.}
+		\caption{Reliability diagrams for the 2Z (left) and 2Z-2MI (right) methods and the prediction of the exceedance of percentiles 80~\% (top), 90~\% (middle), and 95~\% (bottom) at the Ulrichen station for the VP.
+The conventional approach of 24 h is provided as well as the 12-h, 6-h, and 3-h MTWs.}
 		\label{fig:reliability_diagrams}
@@
 		\includegraphics[width=8.3cm]{fig13.pdf}
-		\caption{Optimal number of analogues (of the first and second level of analogy, respectively, $N_{1}$ and $N_{2}$) of the (a) 2Z and (b, c) 2Z-2MI methods after recalibration using the MTW.}
+		\caption{Optimal number of analogues of the first and second levels of analogy, $N_{1}$ and $N_{2}$, respectively, for the (a) 2Z and (b), (c) 2Z-2MI methods after recalibration using the MTW.}
 		\label{fig:analog_nb}
@@
 		\includegraphics[width=8.3cm]{fig14.pdf}
-		\caption{Change in performance score (CRPS -- lower is better) of the (top) 2Z and (bottom) 2Z-2MI methods at the different stations on the (left) CP and (right) VP, for an increasing archive length with the conventional approach (24h windows).}
+		\caption{Change in performance score (CRPS) of the 2Z (top)  and 2Z-2MI (bottom) methods at the different stations for the CP (left) and VP (right) for an increasing archive length with the conventional approach of 24-h window.
+Lower CRPS scores indicate better results.}
 		\label{fig:plots_archive_length}
@@
 		\caption{Parameters for the reference method on the atmospheric circulation (2Z).
-The first column is the level of analogy (0 for preselection), the second column is the meteorological variable, and then its hour of observation.
-The criterion used for the current level of analogy is then provided, as well as the number of analogues.}
+The first column shows the level of analogy (0 for preselection).
+The following columns shown the meteorological variable and its hour of observation, the criterion used for the current level of analogy, and the number of analogues.}
 		\footnotesize
@@
 	\begin{table}[htb]
-		\caption{Parameters of the reference method with moisture variables (2Z-2MI). Same conventions as Table \ref{table:method_2Z}}
+		\caption{Parameters of the reference method with moisture variables (2Z-2MI). The conventions are the same as those in Table \ref{table:method_2Z}}
 		\footnotesize

### 2017-04-06 Moving temporal window - HESS/template.tex
Adding acronyms.
Charle's corrections.

@@
 \usepackage{scrextend}
+
+%TODO: change e.g. 6-h MTW in the figures
 
@@
 
-		The search for candidate situations for a given target day is usually undertaken by comparing the state of the atmosphere at fixed hours of the day for both the target day and the candidate analogues.
-This is a consequence of using daily precipitation time series, which are available on longer periods than sub-daily data.
-However, it is unlikely for the best analogy to occur at the exact same hour.
-A better analogue situation may be found with a time shift of several hours because it can occur at different times of the day.
+		The search for candidate situations similar to a given target day is usually undertaken by comparing the state of the atmosphere at fixed hours of the day for both the target day and the candidate analogues.
+This is a consequence of using standard daily precipitation time series, which are available over longer periods than sub-daily data.
+However, it is unlikely for the best analogy to occur at the exact same hour for the target and candidate situations.
+A better analogue situation may be found with a time shift of several hours since a better fit can occur at different times of the day.
 In order to assess the potential for finding better analogues at a different hour, a moving time window (MTW) has been introduced.
 
-		The MTW resulted in a better analogy in terms of the atmospheric circulation and showed improved values of the analogy criterion on the entire distribution of analogue dates.
+		The MTW resulted in a better analogy in terms of the atmospheric circulation and showed improved values of the analogy criterion on the entire distribution of the extracted analogue dates.
 The improvement was found to increase with the analogue rank owing to an accumulation of better analogues in the selection.
 A seasonal effect has also been identified, with larger improvements shown in winter than in summer.
-This may be attributed to stronger diurnal cycles in summer that favour predictors at the same hour for the target and analogue days.
+This may be attributed to stronger diurnal cycles in summer that favour predictors taken at the same hour for the target and analogue days.
 
-		The impact of the MTW on the prediction skill has been assessed by means of a sub-daily precipitation series transformed into moving 24 h totals at 12-h, 6-h, and 3-h time steps.
+		The impact of the MTW on the precipitation prediction skill has been assessed by means of a sub-daily precipitation series transformed into moving 24 h totals at 12-h, 6-h, and 3-h time steps.
 The prediction skill was improved by the MTW, as was the reliability of the prediction.
@@
 
-		The improvements of the analogy criterion and the performance scores were both found to be higher for MTWs with a smaller time step  of 3 h.
+		The improvements of the analogy criterion and the performance scores on precipitation were both found to be higher for MTWs with a smaller time step  of 3 h.
 A 3-h MTW provides eight times more candidate situations even though they are not fully independent.
-Because the MTW provides additional situations to the pool of possible analogues, it can be considered as an inflation of the archive.
+Because the MTW provides additional situations to the pool of possible analogues, it can be considered as an inflation of the meteorological archive.
 Because this technique is very simple and easily applicable, it should be considered for several applications in different contexts, such as operational forecasting or climate-related studies.
@@
 	The method requires two different archives.
-The first is a meteorological archive describing the state of the atmosphere at a synoptic scale, such as reanalysis datasets.
-The second is an archive of the target variable to be predicted, which in this study is precipitation, usually composed of daily precipitation totals at a target station or integrated over a target catchment.
+The first is a meteorological archive describing the state of the atmosphere at a synoptic scale, such as reanalysis datasets, at different hours of the day.
+The second is an archive of the target variable to be predicted, which is usually standard daily precipitation totals from 06:00 UTC to 06:00 UTC the following day either at a target station or integrated over a target catchment.
 Obviously, the period to be used is limited to the smallest period common to the two archives.
@@
 
-	Therefore, owing to the availability of long precipitation archives at a daily time step that have no equivalent at a finer resolution, AMs are usually implemented on a daily basis, and the analogue situations are assessed by comparing predictors at fixed hours of the day.
-However, it can be expected that the analogy of the synoptic situations does not occur systematically at the same time of the day and that better candidates can be found by shifting to a different hour.
+	Therefore, owing to the availability of long precipitation archives at a daily time step that have no equivalent at a finer resolution, AMs are usually implemented on a daily basis.
+Given the cumulative aspect of the predictand, the corresponding meteorological situation is characterized by several predictors taken at different but fixed hours of the day, and the analogue situations are assessed by comparing these same predictors at the same fixed hours of the day.
+However, it can be expected that the best analogy of the synoptic situations does not occur systematically at the same time of the day and that better candidates can be found by shifting to different hours.
 With this assumption, a moving time window (MTW) was introduced to allow the search for candidates at different hours of the day.
-Previous tests have showed the benefit, in terms of analogy criterion values, of searching for analogue synoptic situations at a finer time step, although such research did not assess the impact on the prediction skill \citep{Finet2008}.
+Previous tests have showed the benefit, in terms of analogy criterion values, of searching for analogue synoptic situations at a finer time step, although such research did not assess the impact on the prediction skill of a specific predictand \citep{Finet2008}.
 
-	One can question the interest of using moving daily totals when, for example, 6-h precipitation series can be predicted instead.
-However, the 6-h time series generated by the AM might not accurately represent the intra-daily precipitation distribution or variability.
-In addition, sometimes a resolution finer than the daily time step is not needed, and another disaggregation technique may be used afterwards.
-Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact on 24-h totals than on 6-h totals.
-
-	The MTW finds analogue situations at different hours of the day, which can also be considered as an inflation of the archive length.
+	The proposed MTW finds analogue situations at different hours of the day, which can also be considered as an inflation of the archive length.
 However, despite having e.g.
@@
 \ref{fig:map}), that are subject to various meteorological influences \citep{Horton2012}.
-The data were available at an hourly time step for 29 years (1982\textendash 2010) and were also obtained at a daily time step of 06:00 UTC to 06:00 UTC the following day for 50 years (1961\textendash 2010).
+The data were available at an hourly time step for 29 years (1982\textendash 2010) and were also obtained at a standard daily time step of 06:00 UTC to 06:00 UTC the following day for 50 years (1961\textendash 2010).
 Owing to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed.
@@
 
-	The additional predictor is a moisture index composed of the product of the total precipitable water (TPW) with the relative humidity at 850 hPa (RH850) \citep{Bontron2004}.
+	The additional predictor is a moisture index composed of the product of the total precipitable water (TPW) with the relative humidity at 850 hPa (RH850) at 12:00 UTC and 24:00 UTC \citep{Bontron2004}.
 When adding a second level of analogy, $N_{2}$ dates are subsampled from the $N_{1}$ analogues on the atmospheric circulation, resulting in a smaller number of analogue situations.
@@
 	AMs rely on parameters that need to be defined for every level of analogy.
-Here, the selection of the meteorological variables used as predictors, as well as their corresponding analogy criteria, pressure level, and hour of the day, were considered to be identical to those used in methods 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) described above.
+Here, the selection of the meteorological variables used as predictors, as well as their corresponding pressure level and hour of the day, were considered to be identical to those used in methods 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) described above.
 The parameters calibrated in this study are listed below.
@@
 	The target situations and their corresponding observed precipitation values do not change.
-The predictions are established for the exact same time series for the MTW and the conventional approach so that the performance scores can be directly compared.
-In order to assess the benefit of searching for analogue situations at a sub-daily time step for quantitative precipitation prediction, an appropriate precipitation series is required.
+The predictions are established for the exact same precipitation time series for both the MTW and the conventional approach so that the performance scores can be directly compared.
+In order to assess the benefit of searching for analogue situations at a sub-daily time step for quantitative precipitation prediction, an appropriate precipitation archive is required.
 On the basis of the hourly time series (Sect.
-\ref{sec:data}), 24-h totals were processed at time steps matching the MTW by means of a moving 24-h total on the period 1982--2010.
+\ref{sec:data}), 24-h totals were processed at time steps matching the MTW by building moving 24-h totals on the period 1982--2010, starting at 0, 3, ..., 21 h UTC instead of 6 h UTC as for the standard archive.
 
@@
 Most of the results are presented for the ERA-20C dataset because it allows for testing a 3-h MTW, although similar conclusions can be found by using MERRA-2.
-The impact of an MTW was assessed on the two bases given below.
+The impact of an MTW approach was assessed on the two bases given below.
 	\begin{itemize}
-		\item Original parameters: The AMs were initially calibrated for each station based on the conventional 24-h approach.
+		\item Original parameters: The AMs were initially calibrated for each station based on the conventional fixed 24-h approach.
 Then, the MTW was introduced into the AMs, but the parameters (spatial windows and number of analogues) were not reassessed.
@@
 \ref{sec:calibration}) was then reprocessed to adapt the AMs to the new information available through the MTW.
-The main difference was the increase in the optimal number of analogues, which is discussed in Sect.
+The main difference was the increase in the optimal number of analogues to retain, which is discussed in Sect.
 \ref{sec:increase_analognb}.
@@
 The introduction of the MTW enables better analogue situations to be found in the first level of analogy, resulting in the selection of days with better similarity in the atmospheric circulation.
-This improvement was superior for MTWs with a smaller time step.
+This improvement was superior for MTWs with a smaller time step, which obviously allows better matching.
 
@@
 
-	The MTW improved the precipitation prediction because the CRPS globally decreased for all stations, both for the CP and the VP.
-The VP showed greater variability, which is likely related to its short period of six years.
+	The MTW did improve the precipitation prediction because the CRPS globally decreased for all stations, both for the CP and the VP.
+The VP showed greater variability, which is likely related to its shorter period of six years.
 The prediction skill for the CP was almost always improved further by reducing the time step of the MTW, but not at the same magnitude.
@@
 	The MTW improved the prediction for days with heavier precipitation.
-Therefore, it should improve the prediction of extremes owing to better analogue situations and to possible new extreme values resulting from 24 h totals with a certain time shift.
+Therefore, it should improve the prediction of extremes owing to selection of better analogue situations and to addition of possible new extreme precipitation values resulting from moving 24 h totals with a certain time shift.
 However, even though the distribution of analogue precipitation values should move towards the targeted extreme to provide better prediction, the MTW itself does not enable prediction of extreme events that were not yet observed and are therefore not present in the archive.
-The extremes in AMs can be modelled by extrapolation of a truncated exponential or gamma distribution fitted to the analogue values \citep{Obled2002}.
+However, the extremes in AMs can be modelled by extrapolation of a truncated exponential or gamma distribution fitted to the analogue values \citep{Obled2002}.
 Another possible approach is to combine AMs with other methods \citep[e.g.][]{Chardon2014}.
@@
 	A higher number of analogues generally implies a poorer analogy with an archive of fixed length.
-Indeed, when the choice of the predictors or the parameters improve, leading to a better prediction, the optimal number of analogue situations decreases.
-However, when the length of the archive increases, the optimal number of analogues also increases for better performance up to a certain threshold \citep[][]{Bontron2004, Hamill2006a}.
-The observed increase in the number of analogue situations with the MTW resulted in better performance skills for the given methods because it can be considered as an inflation of the archive.
-However, if new relevant predictors were added to the method, the number of analogues would then decrease again.
+Indeed, when the choice of the predictors or the parameters improve, leading to a better prediction, the optimal number of analogue situations tends to decrease.
+However, when the length of the archive increases, the optimal number of analogues also tends to increase for better performance up to a certain threshold \citep[][]{Bontron2004, Hamill2006a}.
+The observed increase in the number of analogue situations with the MTW resulting in better performance skills for the given methods can therefore be considered as an inflation of the archive.
 
@@
 
-	Because sub-daily precipitation time series are often available on a shorter period than daily, a reduction of the archive length at disposal is necessary.
+	Because sub-daily precipitation time series are often available over a shorter period than daily, a reduction of the overall archive length at disposal is necessary.
 This usually has a negative consequence on the skill of precipitation prediction.
 The role of the archive length was assessed on the ERA-20C dataset and is presented in Fig.
-\ref{fig:plots_archive_length} for both 2Z and 2Z-2MI methods using the conventional approach of 24-h windows.
+\ref{fig:plots_archive_length} for both 2Z and 2Z-2MI methods using the conventional approach of fixed 24-h windows.
 As expected, the performance of the method globally increased with the length of the archive.
@@
 	As previously stated, the MTW can be considered as an inflation of the archive because it provides additional situations to the pool of possible analogues.
-With the introduction of the MTW, the performance loss related to an eventual reduction of the archive length to meet the length of the sub-daily precipitation archive was compensated.
+With the introduction of the MTW, the performance loss related to an eventual reduction of the archive length to meet the length of the sub-daily precipitation archive was indeed compensated.
 A 6-h MTW brought gains of the same magnitude similar to an almost double archive length.
@@
 The likely reason is that an actual longer archive would contain more atmospheric situations that might have been observed less frequently during a shorter period.
-Moreover, high correlations between sub-daily circulation patterns are expected.
+Moreover, rather strong serial correlations between successive sub-daily circulation patterns are expected.
 
@@
 In such cases, the archive inflation brought by the MTW is also relevant.
+
+	One can question the interest of using moving daily totals when, for example, 6-h precipitation series can be predicted instead.
+However, the 6-h time series generated by the AM might not accurately represent the intra-daily precipitation distribution or variability.
+In addition, sometimes a resolution finer than the daily time step is not needed, and another disaggregation technique may be used afterwards.
+Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact on 24-h totals than on 6-h totals.
 
@@
 It would then be even more profitable to apply the MTW to the longest archive possible rather than being limited to the period in which sub-daily precipitation data are available.
-Therefore, in order to reconstruct longer archives of moving 24-h totals, disaggregation techniques can be used.
+Therefore, the idea is to reconstruct longer archives of moving 24-h totals from existing standard daily precipitation series.
+For this purpose, disaggregation techniques can be used.
 In this study, two simple disaggregation approaches of the daily precipitation time series were assessed.
 
-	The first technique is a proportional distribution in which the observed daily precipitations were considered to be constant during the measurement period of 06:00 UTC to 06:00 UTC the following day.
-The proportional parts of the original daily time series were allocated into a new moving average of 24 h totals.
+	The first technique is a proportional distribution in which the observed daily precipitations were considered to be constant during the measurement period of 06:00 h UTC to 06:00 h UTC the following day.
+The proportional parts of the original daily time series were allocated into a new moving average of 24 h totals (e.g.
+a 00:00 -- 24:00 h UTC total would be made of \textonequarter\ of the standard precipitation of day one and \textthreequarters\ of day two).
 
@@
 	These two simple methods did not result in valuable outputs (results not shown).
-Indeed, the performance improvement brought by the MTW was lost due to the poor quality of the precipitation archives.
+Indeed, the performance improvement brought by the MTW was lost due to the poor quality of the reconstructed precipitation archives.
 A slight improvement was obtained for the second method which relied on a proxy variable rather than the proportional distribution method.
@@
 
-	These attempts to transpose the MTW on the total archive highlight the importance of the actual rainfall chronology.
+	These attempts to transpose the MTW on the (usually) longest meteorological archive highlight the importance of the actual rainfall chronology.
 The MTW is beneficial if the precipitation series are close to the observed values.
@@
 	The AMs are most often based on a daily time step owing to the availability of long precipitation archives.
-However, it is unlikely that two analogue synoptic situations which evolve relatively quickly would correspond optimally at the same hours of the day.
+However, it is unlikely that two analogue synoptic situations which evolve relatively quickly would match optimally at the same hours of the day.
 It is probable that better matches may be found at a different hour, which can change the selection of the analogue dates.
@@
 		\item [CRPS] Continuous ranked probability score
+		\item [ERA-20C] European Center for Medium Range Weather Forecasting 20th century reanalysis
+		\item [MERRA-2] Modern-Era Retrospective Analysis for Research and Applications, Version 2
 		\item [MTW] Moving time window

### 2017-04-07 Moving temporal window - HESS/template.tex
Fixing figures units.
Personal corrections.

@@
 
-%TODO: change e.g. 6-h MTW in the figures
-
 \begin{document}
@@
 
-	\affil[1]{University of Lausanne, Institute of Earth Sciences, Lausanne, Switzerland}
-	\affil[2]{University of Bern, Oeschger Centre for Climate Change Research, Institute of Geography, Bern, Switzerland}
-	\affil[3]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}
+	\affil[1]{Institute of Earth Sciences, University of Lausanne, Lausanne, Switzerland}
+	\affil[2]{Oeschger Centre for Climate Change Research and Institute of Geography, University of Bern, Bern, Switzerland}
+	\affil[3]{Laboratoire d'\'{e}tude des Transferts en Hydrologie et Environnement (LTHE), Universit\'{e} de Grenoble-Alpes, Grenoble, France}
 
@@
 A 3-h MTW provides eight times more candidate situations even though they are not fully independent.
-Because the MTW provides additional situations to the pool of possible analogues, it can be considered as an inflation of the meteorological archive.
+Since the MTW provides additional situations to the pool of possible analogues, it can be considered as an inflation of the meteorological archive.
 Because this technique is very simple and easily applicable, it should be considered for several applications in different contexts, such as operational forecasting or climate-related studies.
@@
 
-	The proposed MTW finds analogue situations at different hours of the day, which can also be considered as an inflation of the archive length.
-However, despite having e.g.
-eight times more candidate situations, the quantity of new information is not expected to be as important as an eight time longer archive owing to significant correlation between successive situations within the same day.
-Nevertheless, if the MTW can improve the prediction skill of the AM, it can extract new information from the archive.
-
 	Other possibilities exist for increasing the prediction skill of the AMs.
@@
 
+	The outline of this paper is as follows.
 Section \ref{sec:data_methods} presents the context of the study as well as the data and methods, including the proposed MTW technique.
@@
 \ref{sec:conclusions}.
+A list of the acronyms and their definitions is provided in appendix A.
 
@@
 Owing to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed.
-The results are presented arbitrarily for the Ulrichen station but are equivalent for all stations.
 
 	Synoptic-scale variables used as predictors were extracted from two of the most recent global reanalysis datasets: the European Center for Medium Range Weather Forecasting 20th century reanalysis (ERA-20C) \citep{Poli2016}, with 3-h temporal resolution and a spatial resolution of 1\textdegree, and Modern-Era Retrospective Analysis for Research and Applications, Version 2 (MERRA-2), from the National Aeronautics and Space Administration (NASA), with a 6-h temporal resolution and a spatial resolution of 0.625\textdegree × 0.5\textdegree.
+MERRA-2 is an update for the first MERRA reanalysis \citep{Rienecker2011}.
 The study was originally performed on the National Centers for Environmental Prediction/National Center for Atmospheric Research (NCEP/NCAR) reanalysis 1 dataset \citep{Kalnay1996}; the conclusions were similar.
-ERA-20C is built by assimilating only surface observations and is thus available for long periods (1900\textendash 2010).
+ERA-20C is built by assimilating only surface observations and is thus available for a long period (1900\textendash 2010).
 On the contrary, MERRA-2 is built by assimilating observations at higher levels and from more sensors including satellite data, but it is more limited in time (1980\textendash present).
@@
 Based on \citet{Bontron2005}, geopotential heights are compared at 1000 hPa (Z1000) at 12:00 UTC and at 500 hPa (Z500) at 24:00 UTC.
-The time of the day at which the predictors are selected has a significant influence \citet{Bontron2004}.
+The time of the day at which the predictors are selected has a significant influence \citep{Bontron2004}.
 
-	Then, $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day, where $N_{1}$ is a calibration parameter ( Sect.
+	Then, $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day, where $N_{1}$ needs to be calibrated (Sect.
 \ref{sec:calibration}).
@@
 
-	The second reference method \citep[2Z-2MI, Table \ref{table:method_2Z-2MI};][]{Bontron2005} adds a subsequent level of analogy with moisture variables and is compared by means of the root--mean--square error (RMSE):
+	The second reference method \citep[2Z-2MI, Table \ref{table:method_2Z-2MI};][]{Bontron2005} adds a subsequent level of analogy with moisture variables, which are compared by means of the root--mean--square error (RMSE):
 
@@
 
-	The semi-automatic sequential procedure discussed by \citet{Bontron2004} was used to calibrate the AM \cite{Radanovics2013, BenDaoud2016}.
+	The semi-automatic sequential procedure discussed by \citet{Bontron2004} was used to calibrate the AM \citep{Radanovics2013, BenDaoud2016}.
 The analogy levels (e.g.
 the atmospheric circulation or moisture index) are calibrated sequentially.
-The spatial windows on which the predictors are compared and the number of analogues are the parameters calibrated by this approach for every level of analogy.
 The procedure, as defined by \citet{Bontron2004}, consists of the following steps:
@@
 			\item Identification of the most skilled unitary cell of the predictor data over a large domain.
-Every point or cell of the full domain is jointly assessed on all predictors of the level of analogy consisting generally of the same variable but on different pressure levels and at different hours.
+Every point or cell of the full domain is jointly assessed on the predictors of the current level of analogy.
 			\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain.
 The spatial window increases until no improvement is reached.
-			\item The number of analogue situations $N_{1}$, which was initially set as an arbitrary value, is then reconsidered and optimised for the current level of analogy.
+			\item The number of analogue situations $N_{1}$, which was initially set to an arbitrary value, is then reconsidered and optimised for the current level of analogy.
 		\end{enumerate}
@@
 
-	The calibration is performed in successive steps with a limited number of parameters in order to minimize the objective function (CRPS, Eq.
+	The calibration is performed in successive steps and aims at minimizing the objective function (CRPS, Eq.
 \ref{eq:CRPS}).
@@
 
-	The continuous ranked probability score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} is often employed in order to assess the performance of AMs \citep[e.g.][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}.
+	The continuous ranked probability score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} is often employed to assess the performance of AMs \citep[e.g.][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}.
 This allows for evaluation of the predicted cumulative distribution functions $F(y)$ of the precipitation values $y$ from analogue situations compared with the observed value $y^{0}$; a better prediction has a smaller score.
@@
 \ref{fig:principle}).
-The ERA-20C dataset used here to test an MTW with 12-h, 6-h, or 3-h time steps, which are referred to as 12-h MTW, 6-h MTW, and 3-hr MTW, respectively.
+The ERA-20C dataset was used here to test an MTW with 12-h, 6-h, or 3-h time steps, which are referred to as 12-h MTW, 6-h MTW, and 3-hr MTW, respectively.
 Thus, the candidates are two (12-h MTW), four (6-h MTW), or eight (3-h MTW) times as many  as in the conventional approach even though they are not fully independent.
@@
 	The target situations and their corresponding observed precipitation values do not change.
-The predictions are established for the exact same precipitation time series for both the MTW and the conventional approach so that the performance scores can be directly compared.
+The predictions are asessed on the exact same precipitation time series for both the MTW and the conventional approach so that the performance scores can be directly compared.
 In order to assess the benefit of searching for analogue situations at a sub-daily time step for quantitative precipitation prediction, an appropriate precipitation archive is required.
 On the basis of the hourly time series (Sect.
-\ref{sec:data}), 24-h totals were processed at time steps matching the MTW by building moving 24-h totals on the period 1982--2010, starting at 0, 3, ..., 21 h UTC instead of 6 h UTC as for the standard archive.
+\ref{sec:data}), 24-h totals were processed at time steps matching the MTW by building moving 24-h totals on the period 1982--2010, for example starting at 0, 3, ..., 21 h UTC instead of 6 h UTC as for the standard archive.
 
@@
 
-	The AMs were applied to both ERA-20C and MERRA-2 datasets.
+	The considered AMs were applied to both ERA-20C and MERRA-2 datasets.
 Most of the results are presented for the ERA-20C dataset because it allows for testing a 3-h MTW, although similar conclusions can be found by using MERRA-2.
@@
 The calibration (Sect.
-\ref{sec:calibration}) was then reprocessed to adapt the AMs to the new information available through the MTW.
+\ref{sec:calibration}) was then reprocessed to adapt the AM parameters to the new information available through the MTW.
 The main difference was the increase in the optimal number of analogues to retain, which is discussed in Sect.
@@
 
-	The MTW is expected to affect both the selection of analogue dates and the prediction skill. Both are analysed separately hereafter.
+	The MTW is expected to affect both the selection of analogue dates and the prediction skill.
+Both are analysed separately hereafter.
+The results are presented for the Ulrichen station, but were very similar for all other stations.
 
@@
 This was conducted for the period 1982--2010, although a longer period could have been used because no sub-daily precipitation series is required at this stage.
-The results are presented for the Ulrichen station, but were very similar for all other stations.
 The original parameters were used when assessing the impact of the MTW; no recalibration of the parameters was conducted.
@@
 The new choice of the temporal window in winter was more balanced between the different hours of the day, showing more regular repartition, for all MTW time steps.
-This indicates a change in selection of a greater portion of the analogue dates in this method than that in the conventional approach.
+This indicates a change in selection of a greater portion of the analogue dates for winter.
 On the contrary, the days in summer showed a preference for the initial temporal window (Z500, 24 h and Z1000, 12 h).
@@
 	When adding the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations did not increase when using the original parameters because they were conditioned by the $N_{1}$ previously selected analogues; however, their dates changed.
-In contrast to the AM on the atmospheric circulation only, both a reduction and an increase in the RMSE analogy criterion values were possible with the MTW compared with the static approach.
+In contrast to the AM on the atmospheric circulation only, both a reduction and an increase in the RMSE analogy criterion values were possible with the MTW compared with the conventional fixed approach.
 The results of the second level of analogy, presented in Fig.
@@
 The VP showed greater variability, which is likely related to its shorter period of six years.
-The prediction skill for the CP was almost always improved further by reducing the time step of the MTW, but not at the same magnitude.
+The prediction skill for the CP was almost always improved further by reducing the time step of the MTW, but not of the same magnitude.
 For ERA-20C, the magnitude of the improvement of 2Z for the CP was relatively reduced when using a 3-h MTW instead of a 6-h MTW, and the variability for the VP increased.
@@
 
-	Reliability diagrams were also created for the VP for both 2Z and 2Z-2MI methods and for the exceedance of percentiles 80~\% (P80, 4 mm), 90~\% (P90, 9.5 mm), and 95~\% (P95, 17.5 mm) at the Ulrichen station (Fig.
+	Reliability diagrams were also created for the VP for both 2Z and 2Z-2MI methods and for the exceedance of all days percentiles 80~\% (P80, 4 mm), 90~\% (P90, 9.5 mm), and 95~\% (P95, 17.5 mm) at the Ulrichen station (Fig.
 \ref{fig:reliability_diagrams}).
 These diagrams plot the observed frequency against the predicted probability of a binary event, which in this case is threshold exceedance.
-For perfectly calibrated predictions, the curve should be as close as possible to the diagonal.
+For perfectly calibrated predictions, the curve should be along the diagonal.
 The VP contains only six years (Sect.
@@
 The number of analogue dates being 30 in this case, it is less likely to have 30 values above the threshold when this one increases.
-This issue is the topic of ongoing research.
+This issue has been addressed by \cite{Marty2010} who proposed a bias correction method for the AM.
 However, as shown in Figure \ref{fig:reliability_diagrams}, the introduction of an MTW, especially with a 3-h time step, improves this mismatch to some degree.
@@
 A 3-h MTW provided eight times more candidate situations, although they were not fully independent.
-Because the MTW provides additional situations to the pool of possible analogues, it can be considered as an inflation of the archive.
+Because the MTW provides additional situations to the pool of possible analogues, it can be considered as an inflation of the archive, which can be interesting in several applications.
 
@@
 The precipitation prediction improved only when the precipitation chronology was close to the accurate values.
-Attempts to reconstruct longer time series based on simplistic proportional distributions or by using meteorological variables from the NCEP reanalysis 1 dataset as a proxy were not successful.
+Attempts to reconstruct longer time series based on simplistic proportional distributions or by using meteorological variables from the NCEP/NCAR reanalysis 1 dataset as a proxy were not successful.
 Other reanalysis datasets with more accurate moisture variables could show better performance.

### 2017-05-05 Moving temporal window - HESS/template.tex
HESS minor corrections under work.

@@
 A classical approach is to add new predictors or new successive levels of analogy \citep[e.g.][]{Horton2012a, BenDaoud2016, Caillouet2016}.
-AMs can also be combined with other methods \citep[e.g.][]{Chardon2014}.
+AMs can also be combined with other methods \citep[e.g.][]{Chardon2017}.
 Another possibility is to use a global optimization technique, such as genetic algorithms, in order to better optimize the method and to add new parameters \citep{Horton2017}.
@@
 
-	The second reference method \citep[2Z-2MI, Table \ref{table:method_2Z-2MI};][]{Bontron2005} adds a subsequent level of analogy with moisture variables, which are compared by means of the root--mean--square error (RMSE):
+	The second reference method \citep[2Z-2MI, Table \ref{table:method_2Z-2MI};][]{Bontron2005} adds a subsequent level of analogy with moisture variables, which are compared by means of the root--mean--square error (RMSE) criteria:
 
@@
 	\label{eq:RMSE}
-	E_{RMS}= \sqrt[]{ \frac{1}{n} \sum_{i=1}^{n}(\hat{v}_{i} - v_{i})^{2}} ,
+	C_{RMSE}= \sqrt[]{ \frac{1}{n} \sum_{i=1}^{n}(\hat{v}_{i} - v_{i})^{2}} ,
 	\end{equation}
@@
 	\label{eq:CRPS}
-	S_{\text{CRP}} = \int_{-\infty}^{+\infty} \left[ F(y)-\text{H}(y-y^{0})\right]^{2} \text{d}y ,  
+	S_{\text{CRPS}} = \int_{-\infty}^{+\infty} \left[ F(y)-\text{H}(y-y^{0})\right]^{2} \text{d}y ,  
 	\end{equation}
@@
 	The improvements of the analogy with the rank of the analogues are summarised in Fig.
-\ref{fig:changes_S1}, which shows the quantiles of the S1 criterion for the conventional method and the MTWs at different time steps (top) and those of the relative reduction indicating improvement owing to the MTWs (bottom).
-This confirms that the improvement constantly increased from the first to the last analogue (Fig.
-\ref{fig:changes_S1} bottom).
-This can be explained by the accumulation of better analogues in the selection, whereby the new, better situations push the previous analogues to higher ranks.
-The regularity of the improvements brought by decreasing time steps is also evident.
-The introduction of the MTW enables better analogue situations to be found in the first level of analogy, resulting in the selection of days with better similarity in the atmospheric circulation.
+\ref{fig:changes_S1}, which shows the quantiles of the S1 criterion for the conventional method and the MTWs at different time steps (top) and those of the increasing improvement owing to the MTWs (bottom).
+The increase of the improvement with the rank of the analogue can be explained by the accumulation of better analogues in the selection, whereby the new, better situations push the previous analogues to higher ranks.
+The introduction of the MTW enables better analogue situations to be found in the first level of analogy.
 This improvement was superior for MTWs with a smaller time step, which obviously allows better matching.
@@
 The VP showed greater variability, which is likely related to its shorter period of six years.
-The prediction skill for the CP was almost always improved further by reducing the time step of the MTW, but not of the same magnitude.
+The prediction skill for the CP was almost always improved further by reducing the time step of the MTW, but not of the same magnitude for every time step.
 For ERA-20C, the magnitude of the improvement of 2Z for the CP was relatively reduced when using a 3-h MTW instead of a 6-h MTW, and the variability for the VP increased.
@@
 After the introduction of the MTW, the performance score was generally further improved with reduced CRPS for days with higher precipitation than for non-rainy days and small precipitation values.
+This can be expected, as the CRPS values are higher when the precipitation amount to be predicted is higher.
 When recalibrating the parameters using the MTW, the spread of the changes in CRPS tended to decrease, although a slight loss in performance was noted for the most rainy days (not shown).
@@
 \ref{sec:changes_analogy_circul}) and the performance scores (Sect.
-\ref{sec:influence_scores}) were improved to a greater extent for days with heavier precipitation.
+\ref{sec:influence_scores}) were improved to a greater extent for days with heavier precipitation (which are related to higher CRPS values).
 This is likely attributed to the fact that higher precipitation events are a consequence of atmospheric conditions with greater dynamics such as weather disturbances, which have well-marked temporal evolution.
@@
 However, the extremes in AMs can be modelled by extrapolation of a truncated exponential or gamma distribution fitted to the analogue values \citep{Obled2002}.
-Another possible approach is to combine AMs with other methods \citep[e.g.][]{Chardon2014}.
+Another possible approach is to combine AMs with other methods \citep[e.g.][]{Chardon2017}.
 From this perspective, the MTW might improve the prediction of extremes because it improves the distribution of precipitation values for days with higher precipitation, on which post-treatment techniques rely.
@@
 When using ERA-20C, all optimal numbers of analogues for the different analogy levels tended to double when using a 6-h MTW instead of the classic approach and to even triple when using a 3-h MTW.
-These higher numbers of analogues were objectively chosen by using the calibration procedure (Sect.
-\ref{sec:calibration}) in order to increase the prediction skill of the methods.
 
@@
 	As previously stated, the MTW can be considered as an inflation of the archive because it provides additional situations to the pool of possible analogues.
-With the introduction of the MTW, the performance loss related to an eventual reduction of the archive length to meet the length of the sub-daily precipitation archive was indeed compensated.
 A 6-h MTW brought gains of the same magnitude similar to an almost double archive length.
@@
 The likely reason is that an actual longer archive would contain more atmospheric situations that might have been observed less frequently during a shorter period.
-Moreover, rather strong serial correlations between successive sub-daily circulation patterns are expected.
+Moreover, consecutive intra-daily situations are expected to be correlated and thus to present redundant information.
 
@@
 In such cases, the archive inflation brought by the MTW is also relevant.
-
-	One can question the interest of using moving daily totals when, for example, 6-h precipitation series can be predicted instead.
-However, the 6-h time series generated by the AM might not accurately represent the intra-daily precipitation distribution or variability.
-In addition, sometimes a resolution finer than the daily time step is not needed, and another disaggregation technique may be used afterwards.
-Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact on 24-h totals than on 6-h totals.
 
@@
 It would then be even more profitable to apply the MTW to the longest archive possible rather than being limited to the period in which sub-daily precipitation data are available.
-Therefore, the idea is to reconstruct longer archives of moving 24-h totals from existing standard daily precipitation series.
+One possible approach to get such long time series is to reconstruct moving 24-h totals from existing standard daily precipitation series (06:00 h UTC to 06:00 h UTC the following day).
 For this purpose, disaggregation techniques can be used.
-In this study, two simple disaggregation approaches of the daily precipitation time series were assessed.
+In this study, we considered the interest of such reconstruction approach using in turn two simple disaggregation methods.
 
-	The first technique is a proportional distribution in which the observed daily precipitations were considered to be constant during the measurement period of 06:00 h UTC to 06:00 h UTC the following day.
+	The first technique is a proportional distribution in which the observed daily precipitations were considered to be constant during the measurement period.
 The proportional parts of the original daily time series were allocated into a new moving average of 24 h totals (e.g.

### 2017-05-08 Moving temporal window - HESS/template.tex
HESS minor corrections.

@@
 Data from NCEP/NCAR reanalysis 1 were used for this purpose.
-Precipitable water and relative humidity at 1000 hPa, 925 hPa, or 850 hPa were assessed at the four points surrounding the catchment.
+Precipitable water and relative humidity at 1000 hPa, 925 hPa, or 850 hPa were assessed at the four points surrounding the catchment and at different times of the day.
 Precipitation time series from the reanalysis were not considered due to the presence of zeros, which may not always match the prediction; this can lead to an undefined temporal repartition.
-Time lapses from -12 h to +12 h between both series were introduced to consider the significant distance separating the weather stations and the reanalysis grid point.
-The best proxy variable, precipitable water, was identified through correlation analyses on non-zero values with the 6-h precipitation time series.
+The best proxy variable, precipitable water, was identified through correlation analyses with the 6-h precipitation time series on the period 1982--2007 (on non-zero precipitation values).
 When the best proxy was selected, its temporal profile was used to disaggregate the daily precipitation time series.
@@
 Indeed, the performance improvement brought by the MTW was lost due to the poor quality of the reconstructed precipitation archives.
-A slight improvement was obtained for the second method which relied on a proxy variable rather than the proportional distribution method.
-However, this  improvement was relatively small, and most of the benefit of the MTW was lost.
+The second method which relied on a proxy variable performed slightly better than the proportional distribution method, but not enough to obtain a relevant time series.
 Another reanalysis dataset with more accurate moisture variables could produce better proxies.
@@
 
-	Improvements of the analogy criterion and the performance scores were both found to be higher for MTWs with a smaller time step of 3 h.
-A 3-h MTW provided eight times more candidate situations, although they were not fully independent.
-Because the MTW provides additional situations to the pool of possible analogues, it can be considered as an inflation of the archive, which can be interesting in several applications.
-
 	The improvement in the circulation analogy and the change in performance of the precipitation prediction was found to be more important for days with heavier precipitation.
@@
 
-	The importance of the quality of the precipitation archive was also demonstrated because simplistic reconstructions of sub-daily time series led to a loss of all the improvement brought by the MTW.
-The precipitation prediction improved only when the precipitation chronology was close to the accurate values.
-Attempts to reconstruct longer time series based on simplistic proportional distributions or by using meteorological variables from the NCEP/NCAR reanalysis 1 dataset as a proxy were not successful.
-Other reanalysis datasets with more accurate moisture variables could show better performance.
+	Improvements of the analogy criterion and the performance scores were both found to be higher for MTWs with a smaller time step of 3 h.
+A 3-h MTW provided eight times more candidate situations, although they were not fully independent.
+Because the MTW provides additional situations to the pool of possible analogues, it can be considered as an inflation of the archive, which can be interesting in several applications.
 
-	The use of the MTW relies partly on the availability of long precipitation series at a sub-daily time step and with high accuracy.
-The precipitation data archives of high temporal resolution have increased over time.
-Other possible sources of such archives is the establishment of precipitation reanalysis at a regional scale in addition to the use of reanalysis-driven regional climate models or limited area models over a long period.
-Even though outputs from these models might be biased or not accurate enough, information regarding the timing of the precipitation events could be useful in disaggregating the station time series.
+	It is desirable for the AM to have available the biggest pool of candidate analogues.
+By inflating the archive, the MTW contributes to enriching this pool.
+However, the use of the MTW relies partly on precipitation series at a sub-daily time step, which are available for the last decades.
+It would then be even more profitable to apply the MTW to the longest archive possible rather than being limited to the recent period.
+Attempts to reconstruct longer sub-daily precipitation time series based on simple disaggregation methods were not successful, which demonstrated the importance of the quality of the precipitation archive to be used in the MTW technique.
+The precipitation prediction provided by the MTW improved only when the precipitation chronology was close to the accurate values.
+More advanced disaggregation methods might provide suitable sub-daily time series.
+Alternatively, another option could be to combine both the MTW and the classical approach and to look for analogue situations at a sub-daily time step from the 80's and at a daily time step for the antecedent years.
+Finally, some other predictands might not need sub-daily total values but point observations such as the occurrence of hail or extreme wind gusts, which make them easier to use with the MTW as no disaggregation is needed.
 
 	The introduction of the MTW improved the selection of synoptic analogues.
-Regardless of its impact on the prediction skill for precipitation or the availability of a predictand time series with a sub-daily time step, this improvement has the potential for application to long meteorological archives.
-For example, when processing forecasts for a target day showing synoptic similarity with known situations from the past related to extreme weather, it can be used even if no precipitation archive is available.
-Thus, it is worth knowing whether the situation at hand had such an analogue in the past.
-Another possible application is quality assessment of the selection of analogues on a shorter period, where sub-daily precipitation data are available.
-Indeed, if the selection of analogues with the MTW on a long period for a specific target day differs from the selection for the shorter period, a sub-optimal forecast could be identified.
-Finally, some other predictands might not need sub-daily total values but point observations such as hail or extreme wind gusts, which make them easier to use with the MTW.
+Regardless of the availability of precipitation series at a sub-daily time step, the MTW can be used to provide a better diagnostic of the weather situation of the target date.
+It can be used for example to identify analogue dates related to extreme weather conditions in historical databases.
 

### 2017-05-12 Moving temporal window - HESS/template.tex
Obled's corrections.

@@
 	\end{equation}
-	where $\Delta \hat{z}_{i}$ is the forecast geopotential height difference between the \textit{i}th pair of adjacent points from the grid of the target situation, $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation, and $m$ is the number of pairs of adjacent points in the grid.
+	where $\Delta \hat{z}_{i}$ is the geopotential height difference between the \textit{i}th pair of adjacent points from the grid of the target situation, $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation, and $m$ is the number of pairs of adjacent points in the grid.
 The differences are processed separately in both directions.
@@
 Finally, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day.
-This method is referred to as 2Z.
+This method based on two geopotential height fields is referred to as 2Z.
 
@@
 
-	The additional predictor is a moisture index composed of the product of the total precipitable water (TPW) with the relative humidity at 850 hPa (RH850) at 12:00 UTC and 24:00 UTC \citep{Bontron2004}.
+	The additional predictor is a moisture index (MI) composed of the product of the total precipitable water (TPW) with the relative humidity at 850 hPa (RH850) at 12:00 UTC and 24:00 UTC \citep{Bontron2004}.
 When adding a second level of analogy, $N_{2}$ dates are subsampled from the $N_{1}$ analogues on the atmospheric circulation, resulting in a smaller number of analogue situations.
@@
 
-	The calibration is performed in successive steps and aims at minimizing the objective function (CRPS, Eq.
+	The calibration is performed in successive steps and aims at minimizing the objective function described below (CRPS, Eq.
 \ref{eq:CRPS}).
@@
 The target situation (the day to predict) is still the same as that in the conventional approach: a daily precipitation total between 06:00 and 30:00 UTC characterised by predictors, which in this case are Z1000 and Z500 at 12:00 and 24:00 UTC, respectively.
-The difference is that candidate situations are considered not only at the same time (12:00 and 24:00 UTC), but also at other hours by allowing a time shift.
-Therefore, instead of looking for analogues at a 24-h time step, they are sought at the time step matching the predictor temporal resolution (Fig.
+The difference is that candidate situations are considered not only at the same time (12:00 and 24:00 UTC), but also at other hours by allowing a time shift, according to the temporal resolution of the predictor (Fig.
 \ref{fig:principle}).
@@
 The predictions are asessed on the exact same precipitation time series for both the MTW and the conventional approach so that the performance scores can be directly compared.
-In order to assess the benefit of searching for analogue situations at a sub-daily time step for quantitative precipitation prediction, an appropriate precipitation archive is required.
+However, in order to assess the benefit of searching for analogue situations at a sub-daily time step for quantitative precipitation prediction, an appropriate precipitation archive is required.
 On the basis of the hourly time series (Sect.
@@
 \ref{sec:mtw}).
-Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions, for target dates over the CP, of the analogy criterion (S1) for the $1^{st}$, $15^{th}$, and $30^{th}$ analogue rank due to the introduction of an MTW with a 12-h, 6-h, or 3-h time step.
+Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions, for target dates over the CP, of the analogy criterion (S1) for the $1^{st}$, $15^{th}$, and $30^{th}$ analogue rank due to the introduction of an MTW with a 12-h, 6-h, or 3-h time step respectively.
 The shapes of the distributions of the conventional approach and the MTWs were found to be similar.
@@
 The results are summarised in Fig.
-\ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for the days with precipitation between two thresholds.
+\ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for the days with precipitation between two a priori selected thresholds.
 With a reduction in the number of cases per class, the curves were not as smooth as those in the previous analyses.
@@
 
-	These criterion values were not improved by the MTW because the number of candidates ($N_{1}$) was not higher.
+	These criterion values were not improved by the MTW because the available number of candidates ($N_{1}$) was not higher.
 The use of an MTW did not increase the sample size in this case because the second level of analogy consists in subsampling in the dates provided by the first level.
@@
 When considering higher thresholds, the 2Z-2MI method was generally better than 2Z.
-The case of the P95 threshold showed a conditional dry bias associated with larger forecast probabilities for the considered AMs; however, this was substantially reduced by the 3-h MTW.
+The case of the P95 threshold showed a conditional dry bias associated with larger probabilities for the considered AMs; however, this was substantially reduced by the 3-h MTW.
 This conditional dry bias means that the AM did not predict the event with a probability equal to 1 for 2Z.
@@
 This issue has been addressed by \cite{Marty2010} who proposed a bias correction method for the AM.
-However, as shown in Figure \ref{fig:reliability_diagrams}, the introduction of an MTW, especially with a 3-h time step, improves this mismatch to some degree.
+However, as shown in Figure \ref{fig:reliability_diagrams}, the introduction of an MTW, especially with a 3-h time step, already improves this mismatch to some degree.
 
@@
 	Both the analogy criteria (Sect.
-\ref{sec:changes_analogy_circul}) and the performance scores (Sect.
+\ref{sec:changes_analogy_circul}) quantifying the synoptic similarity and the performance scores of precipitation prediction (Sect.
 \ref{sec:influence_scores}) were improved to a greater extent for days with heavier precipitation (which are related to higher CRPS values).
@@
 However, even though the distribution of analogue precipitation values should move towards the targeted extreme to provide better prediction, the MTW itself does not enable prediction of extreme events that were not yet observed and are therefore not present in the archive.
-However, the extremes in AMs can be modelled by extrapolation of a truncated exponential or gamma distribution fitted to the analogue values \citep{Obled2002}.
+However, the extremes in AMs can be modelled by extrapolation of a truncated exponential or gamma distribution fitted to the analogue values \citep{Obled2002}, and precipitation values can be proposed for non observed low probabilities.
 Another possible approach is to combine AMs with other methods \citep[e.g.][]{Chardon2017}.
@@
 Data from NCEP/NCAR reanalysis 1 were used for this purpose.
-Precipitable water and relative humidity at 1000 hPa, 925 hPa, or 850 hPa were assessed at the four points surrounding the catchment and at different times of the day.
-Precipitation time series from the reanalysis were not considered due to the presence of zeros, which may not always match the prediction; this can lead to an undefined temporal repartition.
+Precipitable water and relative humidity at 1000 hPa, 925 hPa, or 850 hPa were assessed at the four points surrounding the study area and at different times of the day.
+Precipitation time series from the reanalysis were not considered as potential proxy due to the presence of numerous zeros, which may not always match the prediction; this can lead to an undefined temporal repartition.
 The best proxy variable, precipitable water, was identified through correlation analyses with the 6-h precipitation time series on the period 1982--2007 (on non-zero precipitation values).
@@
 
-	These two simple methods did not result in valuable outputs (results not shown).
+	These two simple (and rather crude) methods did not result in valuable outputs (results not shown).
 Indeed, the performance improvement brought by the MTW was lost due to the poor quality of the reconstructed precipitation archives.
@@
 	These attempts to transpose the MTW on the (usually) longest meteorological archive highlight the importance of the actual rainfall chronology.
-The MTW is beneficial if the precipitation series are close to the observed values.
+The MTW is beneficial if the reconstructed precipitation series are close to the observed values.
 In the absence of a precipitation series with accurate sub-daily chronology, the introduction of an MTW does not improve the precipitation prediction.
@@
 Because the MTW provides additional situations to the pool of possible analogues, it can be considered as an inflation of the archive, which can be interesting in several applications.
+Indeed, the most accurate reanalysis datasets are limited to the satellite era starting in the 80s, and thus provide shorter archives than reanalysis datasets based on conventional data only.
+When using such an archive, the MTW approach allows enriching the pool of possible analogues.
+Moreover, using the MTW approach in the context of a transient climate, where the eventual nonstationarity of the link between predictors and precipitation might discard the relevance of analogues from the distant past, allows relying on a more recent and shorter archive rather than a long one.
 
@@
 By inflating the archive, the MTW contributes to enriching this pool.
-However, the use of the MTW relies partly on precipitation series at a sub-daily time step, which are available for the last decades.
+However, the use of the MTW relies partly on precipitation series at a sub-daily time step, which are available only for the last decades.
 It would then be even more profitable to apply the MTW to the longest archive possible rather than being limited to the recent period.

### 2017-05-12 Moving temporal window - HESS/template.tex
Personal corrections.

@@
 The prediction skill was improved by the MTW, as was the reliability of the prediction.
-Moreover, the improvements were greater for days with heavy precipitation, which are generally related to more dynamic atmospheric situations in which the timing is more specific and fewer records are available in the meteorological archive.
+Moreover, the improvements were greater for days with heavy precipitation, which are generally related to more dynamic atmospheric situations in which the timing is more specific and for which fewer records are available in the meteorological archive.
 
@@
 The first is a meteorological archive describing the state of the atmosphere at a synoptic scale, such as reanalysis datasets, at different hours of the day.
-The second is an archive of the target variable to be predicted, which is usually standard daily precipitation totals from 06:00 UTC to 06:00 UTC the following day either at a target station or integrated over a target catchment.
+The second is an archive of the target variable to be predicted, which is usually standard daily precipitation totals from 06:00 h UTC to 06:00 h UTC the following day either at a target station or integrated over a target catchment.
 Obviously, the period to be used is limited to the smallest period common to the two archives.
@@
 	Other possibilities exist for increasing the prediction skill of the AMs.
-A classical approach is to add new predictors or new successive levels of analogy \citep[e.g.][]{Horton2012a, BenDaoud2016, Caillouet2016}.
+A classical approach is to add new predictors or new successive levels of analogy \citep[e.g.][]{Bontron2004, Horton2012a, BenDaoud2016, Caillouet2016}.
 AMs can also be combined with other methods \citep[e.g.][]{Chardon2017}.
-Another possibility is to use a global optimization technique, such as genetic algorithms, in order to better optimize the method and to add new parameters \citep{Horton2017}.
+Another possibility is to use a global optimization technique, such as genetic algorithms, in order to better optimize the method and to add new parameters \citep{Horton2017, Horton2017b}.
 However, the MTW technique is not in competition with other approaches and can be combined with them.
@@
 \ref{fig:map}), that are subject to various meteorological influences \citep{Horton2012}.
-The data were available at an hourly time step for 29 years (1982\textendash 2010) and were also obtained at a standard daily time step of 06:00 UTC to 06:00 UTC the following day for 50 years (1961\textendash 2010).
+The data were available at an hourly time step for 29 years (1982\textendash 2010) and were also obtained at a standard daily time step of 06:00 h UTC to 06:00 h UTC the following day for 50 years (1961\textendash 2010).
 Owing to the low density of weather stations with high temporal resolution and long archives, no spatially aggregated rainfall was processed.
@@
 Before searching for analogue situations for a target day, seasonal stratification is conducted through preselection of the potential candidates for analogy.
-The search is restricted to analogue days within a four-month window centred on the target date for every year of the archive.
+The search is restricted to days within a four-month window centred on the target date for every year of the archive.
 The similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1), which is a comparison of gradients of geopotential heights over a particular spatial window and at certain hours:
@@
 	\end{equation}
-	where $\Delta \hat{z}_{i}$ is the geopotential height difference between the \textit{i}th pair of adjacent points from the grid of the target situation, $\Delta z_{i}$ is the corresponding observed geopotential height difference in the candidate situation, and $m$ is the number of pairs of adjacent points in the grid.
+	where $\Delta \hat{z}_{i}$ is the geopotential height difference between the \textit{i}th pair of adjacent points from the grid of the target situation, $\Delta z_{i}$ is the corresponding geopotential height difference in the candidate situation, and $m$ is the number of pairs of adjacent points in the grid.
 The differences are processed separately in both directions.
@@
 	The predictor variables extracted from reanalysis datasets are considered at different hours of the day.
-Based on \citet{Bontron2005}, geopotential heights are compared at 1000 hPa (Z1000) at 12:00 UTC and at 500 hPa (Z500) at 24:00 UTC.
+Based on \citet{Bontron2005}, geopotential heights are compared at 1000 hPa (Z1000) at 12:00 h UTC and at 500 hPa (Z500) at 24:00 h UTC.
 The time of the day at which the predictors are selected has a significant influence \citep{Bontron2004}.
@@
 
-	The additional predictor is a moisture index (MI) composed of the product of the total precipitable water (TPW) with the relative humidity at 850 hPa (RH850) at 12:00 UTC and 24:00 UTC \citep{Bontron2004}.
+	The additional predictor is a moisture index (MI) composed of the product of the total precipitable water (TPW) with the relative humidity at 850 hPa (RH850) at 12:00 h UTC and 24:00 h UTC \citep{Bontron2004}.
 When adding a second level of analogy, $N_{2}$ dates are subsampled from the $N_{1}$ analogues on the atmospheric circulation, resulting in a smaller number of analogue situations.
@@
 	The semi-automatic sequential procedure discussed by \citet{Bontron2004} was used to calibrate the AM \citep{Radanovics2013, BenDaoud2016}.
+The AtmoSwing-optimizer software (www.atmoswing.org) was used to perform the calibration.
 The analogy levels (e.g.
@@
 Except for the number of analogues, previously calibrated parameters are generally not reassessed.
-More advanced techniques such as using genetic algorithms \citep{Horton2017} exist but are beyond the scope of the present study.
+More advanced techniques such as using genetic algorithms \citep{Horton2017, Horton2017b} exist but are beyond the scope of the present study.
 
@@
 	The MTW technique is used to find better analogue situations at different hours of the day rather than comparing the predictors at the same fixed hours.
-The target situation (the day to predict) is still the same as that in the conventional approach: a daily precipitation total between 06:00 and 30:00 UTC characterised by predictors, which in this case are Z1000 and Z500 at 12:00 and 24:00 UTC, respectively.
-The difference is that candidate situations are considered not only at the same time (12:00 and 24:00 UTC), but also at other hours by allowing a time shift, according to the temporal resolution of the predictor (Fig.
+The target situation (the day to predict) is still the same as that in the conventional approach: a daily precipitation total between 06:00 h UTC and 06:00 h UTC the following day characterised by predictors, which in this case are Z1000 and Z500 at 12:00 and 24:00 h UTC, respectively.
+The difference is that candidate situations are considered not only at the same time (12:00 and 24:00 h UTC), but also at other hours by allowing a time shift, according to the temporal resolution of the predictor (Fig.
 \ref{fig:principle}).
@@
 However, the values of the analogy criterion were gradually reduced (shifted to the left) with smaller MTW time steps and were therefore better.
-The circulation analogy was regularly improved with the doubling of the MTW time step.
+The circulation analogy was regularly improved with the halving of the MTW time step.
 For analogues with higher ranks (e.g.
@@
 
-	The impact of the MTW on the analogy criterion has been analysed per precipitation class, for the target day, for 6-h and 3-h MTWs.
+	The impact of the MTW on the analogy criterion has also been analysed per precipitation class, for the target day, for 6-h and 3-h MTWs.
 The results are summarised in Fig.
@@
 
-	The effect of the MTW on the S1 criterion was decomposed per season and is presented in Fig.
+	The effect of the MTW on the S1 criterion was decomposed per season, which is presented in Fig.
 \ref{fig:changes_S1_seasons}.
@@
 
-	When adding the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations did not increase when using the original parameters because they were conditioned by the $N_{1}$ previously selected analogues; however, their dates changed.
+	When adding the second level of analogy on moisture variables of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations for this level did not increase when using the original parameters because they were conditioned by the $N_{1}$ previously selected analogues; however, their dates changed.
 In contrast to the AM on the atmospheric circulation only, both a reduction and an increase in the RMSE analogy criterion values were possible with the MTW compared with the conventional fixed approach.
@@
 
-	These criterion values were not improved by the MTW because the available number of candidates ($N_{1}$) was not higher.
+	These criterion values were not improved by the MTW because the available number of candidate situations ($N_{1}$) was not higher.
 The use of an MTW did not increase the sample size in this case because the second level of analogy consists in subsampling in the dates provided by the first level.
 However, this result of a globally null improvement in the RMSE values does not mean that the 2Z-2MI method cannot be improved by the MTW.
-After selection of the analogue dates for the synoptic circulation, the new candidate dates did not provide better analogues in terms of moisture.
-However, the selected dates changed in the first level of analogy and in the final selection; thus, the distributions of precipitation values were different, which can impact the performance of the precipitation prediction.
+Indeed, the selected dates changed in the first level of analogy and in the final selection; thus, the distributions of precipitation values were different, which can impact the performance of the precipitation prediction.
 
@@
 
-	The changes in the performance score (CRPS) of the precipitation prediction are provided in Fig.
+	The changes in the performance score (CRPS, Eq.
+\ref{eq:CRPS}) of the precipitation prediction are provided in Fig.
 \ref{fig:plots_CRPS_2Z} and \ref{fig:plots_CRPS_2Z-2MI} for the 2Z and 2Z-2MI methods, respectively.
@@
 The MTW with the MERRA-2 dataset and the 2Z method also showed a certain slope break after the 12-h MTW that could not be explained and was less important for the 2Z-2MI method.
-However, the 12-h MTW resulted in important variability for the 2Z-2MI method and the MERRA-2 dataset.
+However, the 12-h MTW resulted in important variability for the 2Z-2MI method and the MERRA-2 dataset on the VP.
 
@@
 
-	Both the analogy criteria (Sect.
-\ref{sec:changes_analogy_circul}) quantifying the synoptic similarity and the performance scores of precipitation prediction (Sect.
+	Both the analogy criteria quantifying the synoptic similarity (Sect.
+\ref{sec:changes_analogy_circul}) and the performance scores of precipitation prediction (Sect.
 \ref{sec:influence_scores}) were improved to a greater extent for days with heavier precipitation (which are related to higher CRPS values).
@@
 	When recalibrating the AMs with MTWs of different time steps, the optimal number of analogues changed for both 2Z and 2Z-2MI methods.
-$N_{1}$ and $N_{2}$, from the first and the second level of analogy, tended to significantly increase with a reduced MTW time step (Fig.
+$N_{1}$ and $N_{2}$, from the first and the second level of analogy respectively, tended to significantly increase with a reduced MTW time step (Fig.
 \ref{fig:analog_nb}).
@@
 	As previously stated, the MTW can be considered as an inflation of the archive because it provides additional situations to the pool of possible analogues.
-A 6-h MTW brought gains of the same magnitude similar to an almost double archive length.
-However, it should be noted that despite the number of candidate situations, which in this case is four times the original number, the gains appear to be lower than those for a quadrupled archive length.
+A 6-h MTW brought gains of the same magnitude as an almost double archive length.
+However, it should be noted that despite the number of candidate situations being four times the original number with a 6-h MTW, the gains appear to be lower than those for a quadrupled archive length.
 The likely reason is that an actual longer archive would contain more atmospheric situations that might have been observed less frequently during a shorter period.
@@
 	The first technique is a proportional distribution in which the observed daily precipitations were considered to be constant during the measurement period.
-The proportional parts of the original daily time series were allocated into a new moving average of 24 h totals (e.g.
+Proportional parts of the original daily time series were allocated into a new moving average of 24 h totals (e.g.
 a 00:00 -- 24:00 h UTC total would be made of \textonequarter\ of the standard precipitation of day one and \textthreequarters\ of day two).
 
-	The second approach was used to obtain data that are closer to the chronology of the actual precipitation by relying on informative proxy variables during the reconstruction procedure.
+	The second approach aimed at obtaining data that are closer to the chronology of the actual precipitation by relying on informative proxy variables during the reconstruction procedure.
 Data from NCEP/NCAR reanalysis 1 were used for this purpose.
@@
 The best proxy variable, precipitable water, was identified through correlation analyses with the 6-h precipitation time series on the period 1982--2007 (on non-zero precipitation values).
-When the best proxy was selected, its temporal profile was used to disaggregate the daily precipitation time series.
+Once the best proxy selected, its temporal profile was used to disaggregate the daily precipitation time series.
 
@@
 	The AMs are most often based on a daily time step owing to the availability of long precipitation archives.
-However, it is unlikely that two analogue synoptic situations which evolve relatively quickly would match optimally at the same hours of the day.
+However, it is unlikely that two analogue synoptic situations which evolve relatively quickly would match optimally at the same hour of the day.
 It is probable that better matches may be found at a different hour, which can change the selection of the analogue dates.
@@
 	A seasonal effect was highlighted such that the MTW was more profitable for winter than for summer.
-A likely reason is that the diurnal cycle has a greater effect in summer than in winter, which results in better analogues at the same time of the day.
+A likely reason is that the diurnal cycle having a greater effect in summer than in winter, better analogues are found at the same time of the day.
 The preference for the same hours in summer has been demonstrated, whereas a large part of the analogue situations were selected at a different time in winter.
@@
 	The MTW improved the precipitation prediction, with the CRPS showing a global decrease for all stations for both the CP and VP.
-The prediction skill for the CP was almost always improved further by reducing the time step of the MTW, but the magnitude differed.
+The prediction skill for the CP was almost always improved further by reducing the time step of the MTW.
 The results for the VP showed the same global trends but had more variability.
@@
 Because the MTW provides additional situations to the pool of possible analogues, it can be considered as an inflation of the archive, which can be interesting in several applications.
-Indeed, the most accurate reanalysis datasets are limited to the satellite era starting in the 80s, and thus provide shorter archives than reanalysis datasets based on conventional data only.
-When using such an archive, the MTW approach allows enriching the pool of possible analogues.
-Moreover, using the MTW approach in the context of a transient climate, where the eventual nonstationarity of the link between predictors and precipitation might discard the relevance of analogues from the distant past, allows relying on a more recent and shorter archive rather than a long one.
+For example, the most accurate reanalysis datasets are limited to the satellite era starting in the 80s, and thus provide shorter archives than reanalysis datasets based on conventional data only.
+Or, in the context of a transient climate, where the eventual nonstationarity of the link between predictors and precipitation might discard the relevance of analogues from the distant past, using the MTW approach allows relying on a more recent and shorter archive rather than a long one.
 
@@
 
-	The technique is very simple and easily applicable. Therefore, it should be considered for several applications in different contexts, such as operational forecasting or climate-related studies.
+	The MTW technique is very simple and easily applicable. Therefore, it should be considered for several applications in different contexts, such as operational forecasting or climate-related studies.
 

### 2017-05-12 Moving temporal window - HESS/corrections/10 - Corrected version.tex
Submision of the HESS minor revisions.

--- 2017-05-08 Moving temporal window - HESS/template.tex
@@
 A classical approach is to add new predictors or new successive levels of analogy \citep[e.g.][]{Horton2012a, BenDaoud2016, Caillouet2016}.
-AMs can also be combined with other methods \citep[e.g.][]{Chardon2017}.
+AMs can also be combined with other methods \citep[e.g.][]{Chardon2014}.
 Another possibility is to use a global optimization technique, such as genetic algorithms, in order to better optimize the method and to add new parameters \citep{Horton2017}.
@@
 	The improvements of the analogy with the rank of the analogues are summarised in Fig.
-\ref{fig:changes_S1}, which shows the quantiles of the S1 criterion for the conventional method and the MTWs at different time steps (top) and those of the increasing improvement owing to the MTWs (bottom).
-The increase of the improvement with the rank of the analogue can be explained by the accumulation of better analogues in the selection, whereby the new, better situations push the previous analogues to higher ranks.
-The introduction of the MTW enables better analogue situations to be found in the first level of analogy.
+\ref{fig:changes_S1}, which shows the quantiles of the S1 criterion for the conventional method and the MTWs at different time steps (top) and those of the relative reduction indicating improvement owing to the MTWs (bottom).
+This confirms that the improvement constantly increased from the first to the last analogue (Fig.
+\ref{fig:changes_S1} bottom).
+This can be explained by the accumulation of better analogues in the selection, whereby the new, better situations push the previous analogues to higher ranks.
+The regularity of the improvements brought by decreasing time steps is also evident.
+The introduction of the MTW enables better analogue situations to be found in the first level of analogy, resulting in the selection of days with better similarity in the atmospheric circulation.
 This improvement was superior for MTWs with a smaller time step, which obviously allows better matching.
@@
 The VP showed greater variability, which is likely related to its shorter period of six years.
-The prediction skill for the CP was almost always improved further by reducing the time step of the MTW, but not of the same magnitude for every time step.
+The prediction skill for the CP was almost always improved further by reducing the time step of the MTW, but not of the same magnitude.
 For ERA-20C, the magnitude of the improvement of 2Z for the CP was relatively reduced when using a 3-h MTW instead of a 6-h MTW, and the variability for the VP increased.
@@
 After the introduction of the MTW, the performance score was generally further improved with reduced CRPS for days with higher precipitation than for non-rainy days and small precipitation values.
-This can be expected, as the CRPS values are higher when the precipitation amount to be predicted is higher.
 When recalibrating the parameters using the MTW, the spread of the changes in CRPS tended to decrease, although a slight loss in performance was noted for the most rainy days (not shown).
@@
 \ref{sec:changes_analogy_circul}) and the performance scores (Sect.
-\ref{sec:influence_scores}) were improved to a greater extent for days with heavier precipitation (which are related to higher CRPS values).
+\ref{sec:influence_scores}) were improved to a greater extent for days with heavier precipitation.
 This is likely attributed to the fact that higher precipitation events are a consequence of atmospheric conditions with greater dynamics such as weather disturbances, which have well-marked temporal evolution.
@@
 However, the extremes in AMs can be modelled by extrapolation of a truncated exponential or gamma distribution fitted to the analogue values \citep{Obled2002}.
-Another possible approach is to combine AMs with other methods \citep[e.g.][]{Chardon2017}.
+Another possible approach is to combine AMs with other methods \citep[e.g.][]{Chardon2014}.
 From this perspective, the MTW might improve the prediction of extremes because it improves the distribution of precipitation values for days with higher precipitation, on which post-treatment techniques rely.
@@
 When using ERA-20C, all optimal numbers of analogues for the different analogy levels tended to double when using a 6-h MTW instead of the classic approach and to even triple when using a 3-h MTW.
+These higher numbers of analogues were objectively chosen by using the calibration procedure (Sect.
+\ref{sec:calibration}) in order to increase the prediction skill of the methods.
 
@@
 	As previously stated, the MTW can be considered as an inflation of the archive because it provides additional situations to the pool of possible analogues.
+With the introduction of the MTW, the performance loss related to an eventual reduction of the archive length to meet the length of the sub-daily precipitation archive was indeed compensated.
 A 6-h MTW brought gains of the same magnitude similar to an almost double archive length.
@@
 The likely reason is that an actual longer archive would contain more atmospheric situations that might have been observed less frequently during a shorter period.
-Moreover, consecutive intra-daily situations are expected to be correlated and thus to present redundant information.
+Moreover, rather strong serial correlations between successive sub-daily circulation patterns are expected.
 
@@
 It would then be even more profitable to apply the MTW to the longest archive possible rather than being limited to the period in which sub-daily precipitation data are available.
-One possible approach to get such long time series is to reconstruct moving 24-h totals from existing standard daily precipitation series (06:00 h UTC to 06:00 h UTC the following day).
+Therefore, the idea is to reconstruct longer archives of moving 24-h totals from existing standard daily precipitation series.
 For this purpose, disaggregation techniques can be used.
-In this study, we considered the interest of such reconstruction approach using in turn two simple disaggregation methods.
+In this study, two simple disaggregation approaches of the daily precipitation time series were assessed.
 
-	The first technique is a proportional distribution in which the observed daily precipitations were considered to be constant during the measurement period.
+	The first technique is a proportional distribution in which the observed daily precipitations were considered to be constant during the measurement period of 06:00 h UTC to 06:00 h UTC the following day.
 The proportional parts of the original daily time series were allocated into a new moving average of 24 h totals (e.g.
@@
 Data from NCEP/NCAR reanalysis 1 were used for this purpose.
-Precipitable water and relative humidity at 1000 hPa, 925 hPa, or 850 hPa were assessed at the four points surrounding the catchment and at different times of the day.
+Precipitable water and relative humidity at 1000 hPa, 925 hPa, or 850 hPa were assessed at the four points surrounding the catchment.
 Precipitation time series from the reanalysis were not considered due to the presence of zeros, which may not always match the prediction; this can lead to an undefined temporal repartition.
-The best proxy variable, precipitable water, was identified through correlation analyses with the 6-h precipitation time series on the period 1982--2007 (on non-zero precipitation values).
+Time lapses from -12 h to +12 h between both series were introduced to consider the significant distance separating the weather stations and the reanalysis grid point.
+The best proxy variable, precipitable water, was identified through correlation analyses on non-zero values with the 6-h precipitation time series.
 When the best proxy was selected, its temporal profile was used to disaggregate the daily precipitation time series.
@@
 Indeed, the performance improvement brought by the MTW was lost due to the poor quality of the reconstructed precipitation archives.
-The second method which relied on a proxy variable performed slightly better than the proportional distribution method, but not enough to obtain a relevant time series.
+A slight improvement was obtained for the second method which relied on a proxy variable rather than the proportional distribution method.
+However, this  improvement was relatively small, and most of the benefit of the MTW was lost.
 Another reanalysis dataset with more accurate moisture variables could produce better proxies.
@@
 
+	Improvements of the analogy criterion and the performance scores were both found to be higher for MTWs with a smaller time step of 3 h.
+A 3-h MTW provided eight times more candidate situations, although they were not fully independent.
+Because the MTW provides additional situations to the pool of possible analogues, it can be considered as an inflation of the archive, which can be interesting in several applications.
+
 	The improvement in the circulation analogy and the change in performance of the precipitation prediction was found to be more important for days with heavier precipitation.
@@
 
-	Improvements of the analogy criterion and the performance scores were both found to be higher for MTWs with a smaller time step of 3 h.
-A 3-h MTW provided eight times more candidate situations, although they were not fully independent.
-Because the MTW provides additional situations to the pool of possible analogues, it can be considered as an inflation of the archive, which can be interesting in several applications.
+	The importance of the quality of the precipitation archive was also demonstrated because simplistic reconstructions of sub-daily time series led to a loss of all the improvement brought by the MTW.
+The precipitation prediction improved only when the precipitation chronology was close to the accurate values.
+Attempts to reconstruct longer time series based on simplistic proportional distributions or by using meteorological variables from the NCEP/NCAR reanalysis 1 dataset as a proxy were not successful.
+Other reanalysis datasets with more accurate moisture variables could show better performance.
 
-	It is desirable for the AM to have available the biggest pool of candidate analogues.
-By inflating the archive, the MTW contributes to enriching this pool.
-However, the use of the MTW relies partly on precipitation series at a sub-daily time step, which are available for the last decades.
-It would then be even more profitable to apply the MTW to the longest archive possible rather than being limited to the recent period.
-Attempts to reconstruct longer sub-daily precipitation time series based on simple disaggregation methods were not successful, which demonstrated the importance of the quality of the precipitation archive to be used in the MTW technique.
-The precipitation prediction provided by the MTW improved only when the precipitation chronology was close to the accurate values.
-More advanced disaggregation methods might provide suitable sub-daily time series.
-Alternatively, another option could be to combine both the MTW and the classical approach and to look for analogue situations at a sub-daily time step from the 80's and at a daily time step for the antecedent years.
-Finally, some other predictands might not need sub-daily total values but point observations such as the occurrence of hail or extreme wind gusts, which make them easier to use with the MTW as no disaggregation is needed.
+	The use of the MTW relies partly on the availability of long precipitation series at a sub-daily time step and with high accuracy.
+The precipitation data archives of high temporal resolution have increased over time.
+Other possible sources of such archives is the establishment of precipitation reanalysis at a regional scale in addition to the use of reanalysis-driven regional climate models or limited area models over a long period.
+Even though outputs from these models might be biased or not accurate enough, information regarding the timing of the precipitation events could be useful in disaggregating the station time series.
 
 	The introduction of the MTW improved the selection of synoptic analogues.
-Regardless of the availability of precipitation series at a sub-daily time step, the MTW can be used to provide a better diagnostic of the weather situation of the target date.
-It can be used for example to identify analogue dates related to extreme weather conditions in historical databases.
+Regardless of its impact on the prediction skill for precipitation or the availability of a predictand time series with a sub-daily time step, this improvement has the potential for application to long meteorological archives.
+For example, when processing forecasts for a target day showing synoptic similarity with known situations from the past related to extreme weather, it can be used even if no precipitation archive is available.
+Thus, it is worth knowing whether the situation at hand had such an analogue in the past.
+Another possible application is quality assessment of the selection of analogues on a shorter period, where sub-daily precipitation data are available.
+Indeed, if the selection of analogues with the MTW on a long period for a specific target day differs from the selection for the shorter period, a sub-optimal forecast could be identified.
+Finally, some other predictands might not need sub-daily total values but point observations such as hail or extreme wind gusts, which make them easier to use with the MTW.
 

### 2017-05-22 Moving temporal window - HESS/template.tex
Last technical corrections for HESS.

@@
 Since the MTW provides additional situations to the pool of possible analogues, it can be considered as an inflation of the meteorological archive.
-Because this technique is very simple and easily applicable, it should be considered for several applications in different contexts, such as operational forecasting or climate-related studies.
+Because this technique is simple and easily applicable, it should be considered for several applications in different contexts, such as operational forecasting or climate-related studies.
 
@@
 Multiple variations of this method have been reported \citep{BenDaoud2016}.
-AMs are used for operational precipitation forecasting in the context of weather forecasting, flood forecasting, and hydropower production \citep[e.g.,][]{Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as for precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}.
+AMs are used for operational precipitation forecasting in the context of weather forecasting \citep[e.g.,][]{Hamill2006, Hamill2015, BenDaoud2016}, flood forecasting \citep[e.g.,][]{Bontron2005, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012}, and hydropower production \citep[e.g.,][]{Desaint2008a}, as well as for precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}.
 AMs can provide multivariate predictions which are physically consistent \citep{Raynaud2016b}.
@@
 The search is restricted to days within a four-month window centred on the target date for every year of the archive.
-The similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1), which is a comparison of gradients of geopotential heights over a particular spatial window and at certain hours:
+The similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score ($S_{1}$), which is a comparison of gradients of geopotential heights over a particular spatial window and at certain hours:
 
@@
 The differences are processed separately in both directions.
-With smaller S1 values, there is greater similarity in the pressure fields.
+With smaller $S_{1}$ values, there is greater similarity in the pressure fields.
 
@@
 Based on \citet{Bontron2005}, geopotential heights are compared at 1000 hPa (Z1000) at 12:00 h UTC and at 500 hPa (Z500) at 24:00 h UTC.
-The time of the day at which the predictors are selected has a significant influence \citep{Bontron2004}.
+The time of the day for which the predictors are selected has a significant influence \citep{Bontron2004}.
 
-	Then, $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day, where $N_{1}$ needs to be calibrated (Sect.
+	Then, $N_{1}$ dates with the lowest values of $S_{1}$ are considered as analogues to the target day, where $N_{1}$ needs to be calibrated (Sect.
 \ref{sec:calibration}).
@@
 Both are analysed separately hereafter.
-The results are presented for the Ulrichen station, but were very similar for all other stations.
+The results are presented for the Ulrichen station, but were similar for all other stations.
 
@@
 \ref{sec:mtw}).
-Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions, for target dates over the CP, of the analogy criterion (S1) for the $1^{st}$, $15^{th}$, and $30^{th}$ analogue rank due to the introduction of an MTW with a 12-h, 6-h, or 3-h time step respectively.
+Figure \ref{fig:changes_S1_analogs} shows the changes in the distributions, for target dates over the CP, of the analogy criterion ($S_{1}$) for the $1^{st}$, $15^{th}$, and $30^{th}$ analogue rank due to the introduction of an MTW with a 12-h, 6-h, or 3-h time step respectively.
 The shapes of the distributions of the conventional approach and the MTWs were found to be similar.
@@
 	The improvements of the analogy with the rank of the analogues are summarised in Fig.
-\ref{fig:changes_S1}, which shows the quantiles of the S1 criterion for the conventional method and the MTWs at different time steps (top) and those of the increasing improvement owing to the MTWs (bottom).
+\ref{fig:changes_S1}, which shows the quantiles of the $S_{1}$ criterion for the conventional method and the MTWs at different time steps (top) and those of the increasing improvement owing to the MTWs (bottom).
 The increase of the improvement with the rank of the analogue can be explained by the accumulation of better analogues in the selection, whereby the new, better situations push the previous analogues to higher ranks.
@@
 The results are summarised in Fig.
-\ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for the days with precipitation between two a priori selected thresholds.
+\ref{fig:changes_S1_precip_threshold} by the median reduction of $S_{1}$ for the days with precipitation between two a priori selected thresholds.
 With a reduction in the number of cases per class, the curves were not as smooth as those in the previous analyses.
@@
 
-	The effect of the MTW on the S1 criterion was decomposed per season, which is presented in Fig.
+	The effect of the MTW on the $S_{1}$ criterion was decomposed per season, which is presented in Fig.
 \ref{fig:changes_S1_seasons}.
@@
 This temporal window can be considered as relatively similar in terms of the solar influence.
-The other seasons were between these two extremes, which is consistent with their respective improvements in S1.
+The other seasons were between these two extremes, which is consistent with their respective improvements in $S_{1}$.
 
@@
 
-	When adding the second level of analogy on moisture variables of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations for this level did not increase when using the original parameters because they were conditioned by the $N_{1}$ previously selected analogues; however, their dates changed.
+	When adding the second level of analogy on moisture variables of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidate situations for this level did not increase when using the original parameters because the candidate situations were conditioned by the $N_{1}$ previously selected analogues; however, their dates changed due to the introduction of the MTW on the first level of analogy.
 In contrast to the AM on the atmospheric circulation only, both a reduction and an increase in the RMSE analogy criterion values were possible with the MTW compared with the conventional fixed approach.
@@
 
-	The introduction of an MTW was previously found to show greater improvement of the S1 criterion for days with higher precipitation values (Sect.
+	The introduction of an MTW was previously found to show greater improvement of the $S_{1}$ criterion for days with higher precipitation values (Sect.
 \ref{sec:changes_analogy_circul}).
@@
 Figure \ref{fig:reliability_diagrams} shows that the MTW improved the reliability for both 2Z and 2Z-2MI methods and for all thresholds because the curves moved towards the diagonal with decreasing MTW time steps.
-For P80, the 3-h MTW predictions fit very well the observed frequency.
+For P80, the 3-h MTW predictions fit well the observed frequency.
 When considering higher thresholds, the 2Z-2MI method was generally better than 2Z.
@@
 	As shown in Fig.
-\ref{fig:changes_S1}, the improvement of the S1 criterion increases along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions.
+\ref{fig:changes_S1}, the improvement of the $S_{1}$ criterion increases along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions.
 Widening the selection of analogues appears to be beneficial for keeping some with increased rank because they appear to be relevant in predicting the precipitation values.
@@
 Using recent reanalysis datasets, MTWs with 12-h, 6-h, and 3-h time steps were assessed in the present study.
-Improvement in the S1 criterion values increased with the rank of the analogue owing to the accumulation of better analogues within the predicted distributions.
-Moreover, the improvement in the S1 criterion increased further for smaller MTW time steps.
+Improvement in the $S_{1}$ criterion values increased with the rank of the analogue owing to the accumulation of better analogues within the predicted distributions.
+Moreover, the improvement in the $S_{1}$ criterion increased further for smaller MTW time steps.
 
@@
 
-	The MTW technique is very simple and easily applicable. Therefore, it should be considered for several applications in different contexts, such as operational forecasting or climate-related studies.
+	The MTW technique is simple and easily applicable. Therefore, it should be considered for several applications in different contexts, such as operational forecasting or climate-related studies.
 
@@
 		\item [RMSE] Root--mean--square error
-		\item [S1] Teweles and Wobus (1954) score
+		\item [$S_{1}$] Teweles and Wobus (1954) score
 		\item [TPW] Total precipitable water
@@
 
-		The authors would also like to acknowledge the work of anonymous reviewers who contributed to improving this manuscript. 
+		The authors would also like to acknowledge the work of anonymous reviewers and the editor who contributed to improving this manuscript. 
 	\end{acknowledgements}
@@
 		\end{center}
-		\caption{Changes in S1 criterion distributions owing to the introduction of an MTW with a 12-h, 6-h, or 3-h time step.
+		\caption{Changes in $S_{1}$ criterion distributions owing to the introduction of an MTW with a 12-h, 6-h, or 3-h time step.
 Distributions are provided for (a) the $1^{st}$, (b) $15^{th}$, and (c) $30^{th}$ analogue ranks for all days of the CP at the Ulrichen station.}
@@
 		\end{center}
-		\caption{Synthesis of the changes in the S1 criterion owing to the MTW with 12-h, 6-h, and 3-h time steps for the Ulrichen station depending on the rank of the analogue.
-(a) Quantiles of the S1 distributions corresponding to the MTW with different time steps; 24-h is the conventional approach without MTW.
-(b) Quantiles of the relative improvements of the S1 criterion when using the MTW compared with the conventional approach.}
+		\caption{Synthesis of the changes in the $S_{1}$ criterion owing to the MTW with 12-h, 6-h, and 3-h time steps for the Ulrichen station depending on the rank of the analogue.
+(a) Quantiles of the $S_{1}$ distributions corresponding to the MTW with different time steps; 24-h is the conventional approach without MTW.
+(b) Quantiles of the relative improvements of the $S_{1}$ criterion when using the MTW compared with the conventional approach.}
 		\label{fig:changes_S1}
@@
 		\end{center}
-		\caption{Distribution of the median improvements of the S1 criterion owing to the (a) 3-h MTW and (b) 6-h MTW, depending the on daily precipitation thresholds at the Ulrichen station.}
+		\caption{Distribution of the median improvements of the $S_{1}$ criterion owing to the (a) 3-h MTW and (b) 6-h MTW, depending the on daily precipitation thresholds at the Ulrichen station.}
 		\label{fig:changes_S1_precip_threshold}
@@
 		\end{center}
-		\caption{Seasonal effect on the median reduction of the S1 criterion for the Ulrichen station owing to the MTW. DJF: winter; MAM: spring; JJA: summer; SON: fall.}
+		\caption{Seasonal effect on the median reduction of the $S_{1}$ criterion for the Ulrichen station owing to the MTW. DJF: winter; MAM: spring; JJA: summer; SON: fall.}
 		\label{fig:changes_S1_seasons}
@@
 				\hline 
-				\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{$N_{1}$} \\
+				\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{$S_{1}$} & \multirow{2}{*}{$N_{1}$} \\
 				& Z500 & 24~h & & \\ 
